### 2016-02-08 draft/ms.tex
Start to work on the draft

% Version 0; preprint format; Written by SH

\documentclass[preprint]{aastex}
\usepackage{emulateapj5}
\usepackage{apjfonts}
\usepackage{amssymb, amsmath}
\usepackage{graphicx}
\usepackage{CJK}
\DeclareGraphicsExtensions{.pdf,.png,.jpg}
\bibliographystyle{apj}

\input psfig.tex

%%%%%%%%%%%%: User Defined Commands %%%%%%%%%%%%

\newdimen\digitwidth    % These five lines change the meaning of
\setbox1=\hbox{0}       % " in the same way, so that it leaves as
\digitwidth=\wd1        % much space as a digit. (Note: All digits
\catcode`"=\active      % are the same width).

% Luis's Definitions
\def\arcsec{{\prime\prime}}
\def\arcmin{{\prime}}
\def\degree{{\circ}}
\def"{\kern\digitwidth}
\def\h{\hskip -3 mm}
\def\aa{{A\&A}}
\def\aas{{ A\&AS}}
\def\aj{{AJ}}
\def\al{$\alpha$}
\def\bet{$\beta$}
\def\amin{$^\prime$}
\def\annrev{{ARA\&A}}
\def\apj{{ApJ}}
\def\apjs{{ApJS}}
\def\asec{$^{\prime\prime}$}
\def\deg{$^{\circ}$}
\def\ddeg{{\rlap.}$^{\circ}$}
\def\dsec{{\rlap.}$^{\prime\prime}$}
\def\cc{cm$^{-3}$}
\def\etal{{\ et al.~}}
\def\flamb{erg s$^{-1}$ cm$^{-2}$ \AA$^{-1}$}
\def\flux{erg s$^{-1}$ cm$^{-2}$}
\def\fnu{erg s$^{-1}$ cm$^{-2}$ Hz$^{-1}$}
\def\hst{{\it HST}}
\def\kms{km s$^{-1}$}
\def\lamb{$\lambda$}
\def\lax{{$\mathrel{\hbox{\rlap{\hbox{\lower4pt\hbox{$\sim$}}}\hbox{$<$}}}$}}
\def\gax{{$\mathrel{\hbox{\rlap{\hbox{\lower4pt\hbox{$\sim$}}}\hbox{$>$}}}$}}
\def\simlt{\lower.5ex\hbox{$\; \buildrel < \over \sim \;$}}
\def\simgt{\lower.5ex\hbox{$\; \buildrel > \over \sim \;$}}
\def\micron{{$\mu$m}}
\def\mnras{{MNRAS}}
\def\nat{{Nature}}
\def\pasp{{PASP}}
\def\perang{\AA$^{-1}$}
\def\peryr{yr$^{-1}$}
\def\pp{\parshape 2 0truein 6.1truein .3truein 5.5truein}
\def\reference{\noindent\pp}
\def\refindent{\par\noindent\parskip=2pt\hangindent=3pc\hangafter=1 }
\def\sb{mag~arcsec$^{-2}$}
\def\solum{$L_\odot$}
\def\solmass{$M_\odot$}
\def\sigs{$\sigma_*$}
\newcommand{\lt}{<}
\newcommand{\gt}{>}

%Song Huang's definition 
\def\galfit{{\tt GALFIT}}
\def\ser{{S\'{e}rsic\ }}

%%%%%%%%%%%%: Header and Version %%%%%%%%%%%%

\slugcomment{Draft version 0}
\shorttitle{ENVIRONMENT DEPENDENCE OF MASS-SIZE RELATION}
\shortauthors{HUANG ET AL.}

\begin{document}

\begin{CJK*}{UTF8}{gbsn}

%%%%%%%%%%%%: Title and Affiliations %%%%%%%%%%%%

\title{The Environmental Dependence of Structures for Massive Galaxies
from the Hyper-Suprime Camera Survey}

\author{Song Huang (黄崧)\altaffilmark{1} Alexie Leauthaud\altaffilmark{1}, 
Kevin Bundy\altaffilmark{1}, and You}
\date{}

\altaffiltext{1}{Kavli Institute for the Physics and Mathematics of the
Universe, Todai Institutes for Advanced Study, the University of Tokyo (Kavli
IPMU, WPI), Kashiwa 277-8583, Japan}

%%%%%%%%%%%%: Abstract and Keywords %%%%%%%%%%%%

\begin{abstract}

  Many recent observations and numerical simulations suggest that nearby
  massive, early-type galaxies are formed through a ``two-phase'' process.  In
  the proposed second phase, the extended stellar envelope was accumulated
  through many dry mergers. (XX TODO)

\end{abstract}
\keywords{galaxies: elliptical and lenticular, cD --- galaxies: formation --- 
          galaxies: photometry --- galaxies: structure --- galaxies: surveys}

\maketitle

%%%%%%%%%%%%: Main Text %%%%%%%%%%%%

\section{Introduction}

\section{Sample and Data Reduction}

\section{Results}

\section{Discussion}

\section{Summary}

%%%%%%%%%%: Acknowledge %%%%%%%%%%

\acknowledgements

  1. Acknowledgements for HSC 
  2. Acknowledgements for Kevin and Alexie's funding 
  3. Acknowledgements for the Python libraries

  Funding for SDSS-III has been provided by the Alfred P. Sloan Foundation, the
  Participating Institutions, the National Science Foundation, and the U.S.
  Department of Energy. The SDSS-III web site is http://www.sdss3.org.  SDSS-III
  is managed by the Astrophysical Research Consortium for the Participating
  Institutions of the SDSS-III Collaboration including the University of
  Arizona, the Brazilian Participation Group, Brookhaven National Laboratory,
  University of Cambridge, University of Florida, the French Participation
  Group, the German Participation Group, the Instituto de Astrofisica de
  Canarias, the Michigan State/Notre Dame/JINA Participation Group, Johns
  Hopkins University, Lawrence Berkeley National Laboratory, Max Planck
  Institute for Astrophysics, New Mexico State University, New York University,
  Ohio State University, Pennsylvania State University, University of
  Portsmouth, Princeton University, the Spanish Participation Group, University
  of Tokyo, University of Utah, Vanderbilt University, University of Virginia,
  University of Washington, and Yale University.

%%%%%%%%%%: Bibligraphic Section %%%%%%%%%%

%\begin{thebibliography}{}

  %\bibitem[Arnold et al.(2011)]{2011ApJ...736L..26A} Arnold, J.~A., Romanowsky,
    %A.~J., Brodie, J.~P., et al.\ 2011, \apjl, 736, LL26

%\end{thebibliography}{}

\bibliography{redbcg}

%%%%%%%%%%: Appendix Section %%%%%%%%%%%%

\appendix

\section{A. Atlas of 1-D Profiles}

%%%%%%%%%%%%: Figures Section %%%%%%%%%%%%

% Fig. 1
\clearpage
\figurenum{1}
\begin{figure}
    \centering 
    \includegraphics[width=16.5cm]{fig/fig1.png}
    \caption{
   Cartoons that illustrate the basic idea of the proposed method for the
   estimation of average merger mass ratio.  The style is adopted from Faber\etal (2007).
   The upper panels show the basic
   picture of the ``two-phase'' formation scenario. The lower panel describes
   a general picture for the evolution of massive galaxies on the
   $M_{\ast}$-color plane.  After massive ETGs were quenched, they quickly
   moved to the red-sequence, and gradually evolved along it as they are
   becoming redder due to the aging of stellar population, and more massive due
   to the accumulation of extended stellar envelope through many minor (dry)
   mergers.  Since the stellar content of smaller system should have lower
   metallicity, the outer envelope naturally has a bluer color compared to inner
   region.  And, such color difference reflects the average mass ratio of all
   mergers that contribute to the second phase of evolution.  Larger color
   difference means more stellar material came from smaller galaxies, hence
   makes minor merger more important.  
   }
   \label{figure:1}
\end{figure}

%%%%%%%%%%%%: End of the File %%%%%%%%%%%%

\end{CJK*}

\clearpage

%%%%%%%%%%%: Possible Tables %%%%%%%%%%%%%
%\input{table1.tex}

\end{document}

### 2016-06-17 draft/ms.tex
Update of outline 16/06/17

@@
 \documentclass[preprint]{aastex}
+
+% Packages
 \usepackage{emulateapj5}
@@
 \usepackage{CJK}
+\usepackage[usenames]{color}
+
+% Figure extention
 \DeclareGraphicsExtensions{.pdf,.png,.jpg}
 \bibliographystyle{apj}
-
 \input psfig.tex
@@
 
-\newdimen\digitwidth    % These five lines change the meaning of
-\setbox1=\hbox{0}       % " in the same way, so that it leaves as
-\digitwidth=\wd1        % much space as a digit. (Note: All digits
-\catcode`"=\active      % are the same width).
-
-% Luis's Definitions
+% Song Huang's definition 
 \def\arcsec{{\prime\prime}}
@@
 \def\degree{{\circ}}
-\def"{\kern\digitwidth}
 \def\h{\hskip -3 mm}
@@
 \newcommand{\gt}{>}
-
-%Song Huang's definition 
 \def\galfit{{\tt GALFIT}}
 \def\ser{{S\'{e}rsic\ }}
+\def\redm{\texttt{redMaPPer}}
+\def\redbcg{$\Lambda \ge 30$}
+\def\nonbcg{$\Lambda < 30$}
+
+% Commenting:
+\newcommand{\todo}[1]{\textcolor{red}{\textbf{TODO: #1}}}
+\newcommand{\plan}[1]{\textcolor{cyan}{#1}}
+\newcommand{\addref}[1]{\textcolor{red}{REF}}
+\newcommand{\comment}[2]{\textcolor{blue}{\textbf{[Comment (#1): #2]}}}
+\newcommand{\song}[1]{\textcolor{magenta}{\textbf{[Song: #1]}}}
+\newcommand{\alexie}[1]{\textcolor{blue}{\textbf{[Alexie: #1]}}}
+\newcommand{\kevin}[1]{\textcolor{green}{\textbf{[Kevin: #1]}}}
 
@@
 \slugcomment{Draft version 0}
+\email{song.huang@ipmu.jp}
 \shorttitle{ENVIRONMENT DEPENDENCE OF MASS-SIZE RELATION}
@@
 \title{The Environmental Dependence of Structures for Massive Galaxies
-from the Hyper-Suprime Camera Survey}
+from the Hyper Suprime-Cam Survey}
 
-\author{Song Huang (黄崧)\altaffilmark{1} Alexie Leauthaud\altaffilmark{1}, 
-Kevin Bundy\altaffilmark{1}, and You}
+\author{Song Huang (黄崧)\altaffilmark{1} 
+        Alexie Leauthaud\altaffilmark{1}, 
+        Kevin Bundy\altaffilmark{1},
+        Michael Strauss\altaffilmark{2},
+        Yen-Ting Lin\altaffilmark{3},
+        Rachel Mandelbaum\altaffilmark{4}
+        }
 \date{}
@@
 \altaffiltext{1}{Kavli Institute for the Physics and Mathematics of the 
-Universe, Todai Institutes for Advanced Study, the University of Tokyo (Kavli
-IPMU, WPI), Kashiwa 277-8583, Japan}
+    Universe, The University of Tokyo Institutes for Advanced Study, 
+    the University of Tokyo (Kavli IPMU, WPI), Kashiwa 277-8583, Japan}
+\altaffiltext{2}{Princeton University Observatory, 
+    Peyton Hall, Princeton, NJ 08544, USA}
+\altaffiltext{3}{Institute of Astronomy and Astrophysics, Academia Sinica, 
+    P.O.~Box 23-141, Taipei 10617, Taiwan}
+\altaffiltext{4}{Carnegie-Mellon University \todo{correct affiliation here}}
 
@@
 \begin{abstract}
-
-  Many recent observations and numerical simulations suggest that nearby
-  massive, early-type galaxies are formed through a ``two-phase'' process.  In
-  the proposed second phase, the extended stellar envelope was accumulated
-  through many dry mergers. (XX TODO)
-
+    \todo{Place holder; This is the abstract for talk}\\
+    Under the most popular formation scenario, the structures of massive central galaxies
+    depend on environment at fixed stellar mass due to different assembly histories shaped
+    by their host halos. Yet, clear evidence of such effect is still lacking. Using deep,
+    multi-band images for a large sample of massive galaxies at 0.2 < z < 0.5 from the
+    Hyper Suprime-Cam (HSC) survey, we discover subtle, but systematic structural
+    difference for massive galaxies in low and high mass haloes. The differences are
+    consistent with richer merger history in more massive halos. We show that the average
+    profiles of mass, shape, and color, along with relations among masses within different
+    radius (as proxy of mass assembled at different time) can help us gain more insights
+    of their assembly history, and the weak lensing analysis enabled by HSC survey further
+    helps us connect the differences we find to the average halo properties.
 \end{abstract}
@@
 
+%% ------------------------------------------------------------------------------------ %% 
 \section{Introduction}
 
-\section{Sample and Data Reduction}
+    \plan{Scientific Background}
+    \begin{itemize}
+        \item \plan{Massive galaxies are important cosmic probe and unique labs to study 
+            galaxy evolution.} 
+        \item \plan{Briefly explain why massive early-type galaxies are important through 
+            the difficulties of stellar-halo mass relation and stellar mass function at the 
+            high-mass end.}
+        \item \plan{Brief summary of the current understanding of thieir cosmic assembly 
+            history.}
+        \item \plan{Explain why we should care about the environment, and why we expect to 
+            see some environemtnal dependence in the structure and other properties of
+            massive galaxies.}
+        \item \plan{Brief review of the current observations.  It is still not clear 
+            whether there is a clear environmental dependence.}
+    \end{itemize}
+
+    \plan{Observational difficulties (a.k.a Why we need HSC)}
+    \begin{itemize}
+        \item \plan{Explain why it is important to study the mass distribution of 
+            massive galaxies out to large physical radius; and, given their unique light 
+            profiles, why it is more difficult to study them compared to late-type 
+            galaxies.}
+        \item \plan{Very brief summary of past observational efforts, and why they are not 
+            good enough (Not enough number of really massive galaxy; Shallow images; 
+            Background subtraction issue; and stacking analysis can be dangerous as while)}
+    \end{itemize}
+
+    \plan{Basica idea of this work}
+    \begin{itemize}
+        \item \plan{Here we take advantages of the ambitious Hyper-Suprime camera 
+            survey....}
+    \end{itemize}
+
+    The paper is organized as follows. Section~2 gives a brief overview of the HSC
+    observation and data reduction.  We will also summarize the process of sample
+    selection.  In Section~3, we will describe the method for deriving the stellar mass 
+    surface density profile.  The main results are summarized in Section~4.  Section~5 
+    provides discussions of the assumptions used in this work, the potentially interesting
+    physical implications, and several future improvements, ending with a sumary in
+    Section~6.
+
+    Within this work, we assume $H_0$ = 70~km~s$^{-1}$ Mpc$^{-1}$, ${\Omega}_m=0.3$, and
+    ${\Omega}_{\Lambda}=0.7$.
+
+%% ------------------------------------------------------------------------------------ %%
+
+\section{Observations and Sample Selection}
+
+\subsection{The Hyper Suprime-Cam Survey}
+
+    \todo{Brief introduction, see the same section in other people's work} \\
+
+    This work makes use of the internal data release \texttt{S15B}, which covers $\sim 100$
+    square of degree of sky in all 5-band to the required depth of \texttt{WIDE} survey.
+
+    \todo{The following part is borrowed from Chan's work; Need to re-write}\\
+    HSC is the new prime-focus camera on the 8.2-m Subaru telescope located at Mauna Kea, 
+    Hawaii.  The field of view (FOV) is 1.5 deg in diameter (\addref: Miyazaki\etal 2012) 
+    which is ten times larger than the FOV of Suprime-Cam (\addref: Miyazaki\etal 2002). 
+    The HSC Subaru Strategic Program (SSP) survey consists of three layers with different 
+    depths: wide, deep and ultra-deep. The wide survey will cover $\sim1400$ deg$^2$ to 
+    $r\sim26$ mag in {\it grizY} broad bands.
+
+    The data are processed with \texttt{hscPipe 4.0.1}, a derivative of the Large Synoptic 
+    Survey Telescope (LSST) pipeline (\addref: Ivezic\etal 2008, Axelrod\etal 2010), 
+    modified for use with Suprime-Cam and Hyper Suprime-Cam.  The photometric calibration 
+    is based on data obtained from the Panoramic Survey Telescope and Rapid Response 
+    System (Pan-STARRS) 1 imaging survey (\addref: Schlafly\etal 2012, Tonry\etal 2012, 
+    Magnier\etal 2013).
+
+    The pixel scale of the reduced images in the data releases is 0.168$\arcsec$.
+
+    \plan{\textbf{Fig.1}: Comparison of SDSS and HSC color image}
+
+\subsection{Candidates of massive galaxies}
+
+    \plan{Selection of the \texttt{PHOTO} sample}
+    \begin{itemize}
+        \item \plan{\texttt{PRIMARY} detection: In the inner region of the \texttt{Tract}
+            and \textt{Patch}; has no \texttt{CHILD}.}
+        \item \plan{Require the galaxy to be detected in all 5-band}
+        \item \plan{For $i$-band detection, we require the object is covered by at least 
+            4 \texttt{Visit}.}
+        \item \plan{Has useful \texttt{cModel} photometry in all 5-band}
+        \item \plan{$i$-band \texttt{cModel} magnitude brigther than 21.0 mag (justify this 
+            later}
+        \item \plan{Has to be extended object.}
+        \item \plan{Has reliable central position and shape using SDSS algorithm}
+        \item \plan{Typical quality cuts in $griz$-band.}
+    \end{itemize}
+
+    \plan{Selection of the \texttt{SPECZ} sample}
+    \begin{itemize}
+        \item \plan{Brief summary of the HSC spec-z catalog.}
+        \item \plan{Internal catalog match results in 121998 galaxies}
+        \item \plan{Brief break down of the spec-z sample; Most of the spectroscopic 
+            redshift come from SDSS/BOSS and GAMA survey}
+        \item \plan{Only keep objects at $z < 0.6$} \todo{Justify this later}
+    \end{itemize}
+
+\subsection{Central galaxies of $\Lambda > 20$ haloes using the \redm clusters}
+
+    To select the central galaxies of cluster-level dark matter haloes, we make use of the 
+    \redm cluster catalog \footnote{See: http://risa.stanford.edu/redmapper/}.
+
+    \plan{Match to the \redm catalog}
+    \begin{itemize}
+        \item \plan{For this work, we use the \redm catalog based on SDSS DR8 
+            photometry.} \todo{Need some explanation}
+        \item \plan{Match with the \texttt{PHOTO} sample using a 1.0$\arcsec$
+            matching radius, results in 704 clusters. (Justify this matching radius)}
+        \item \plan{Select the \redm clusters at $z < 0.6$.}
+        \item \plan{There is a small population of central galaxies from \redm that
+            are within the HSC footprint, but does not have matched photometry, 
+            briefly explain them}
+    \end{itemize}
+
+\subsection{Galaxies in $\Lambda < 20$ haloes}
+
+    \begin{itemize}
+        \item \plan{Remove the galaxy that is close to any \redm cluster}
+        \item \plan{Remove the galaxy that is close to any bright star} 
+            \todo{Justify why we do not do this to the \redm central sample}
+    \end{itemize}
+
+%% ------------------------------------------------------------------------------------ %%
+
+\section{Data Reduction}
+
+\subsection{1-D surface brightness profile}
+
+    \plan{Basica ideas}
+    \begin{itemize}
+        \item \plan{Briefly explain that 1-D surface brightness profile is a very old 
+            fashion, but robust and straightforward way to describe the light or mass 
+            distribution of a galaxy.  Although it is not exactly ``model-independent'', 
+            it indeed has the advantages of not easily affected by complex substrctures 
+            within the galaxy comparing with the more popular 2-D modelling method. }
+        \item \plan{Due to the uniquely extended nature of the light distributions of 
+            these massive ETGs, it is still unclear which is the most appropriate 2-D 
+            model for them (Can not be well described by 1-\ser model). }
+    \end{itemize}
+
+    \plan{Step by step description}
+    \begin{itemize}
+        \item \plan{Generation of cutout image in multiple bands}: \\
+            \begin{enumerate}
+                \item \plan{Choice of image size: make sure that the cutout covers out 
+                    to at least 500 kpc from the center of the galaxy.}
+                \item \plan{Also generate the bad pixel masks, and the reconstructed 
+                    PSF model for the galaxy center.}
+            \end{enumerate}
+        \item \plan{Generation of object masks}: \\
+            \begin{enumerate}
+                \item \plan{Briefly explain why we need to our own photometry instead 
+                    of just using the cModel results from the HSC pipeline.}
+                \item \plan{We need two kinds of masks: mask of all objects that will 
+                    be used to measure the sky value; mask of objects expect for the 
+                    central galaxy we want to derive surface brightness profile.  
+                    Briefly describe their requirements.}
+                \item \plan{Object detection using \texttt{SEP} Python library.}
+            \end{enumerate}
+        \item \textbf{Re-measurement and correction of sky background}:
+    \end{itemize}
+
+\subsection{Average mass-to-light ratio}
+
+    \begin{itemize}
+        \item \plan{Briefly explain the method to convert surface brightness profiles 
+            into mass density profile, focusing on the key assumptions.}
+        \item \plan{Describe the SED fitting process.}    
+        \item \plan{Briefly discuss the impact of choices of SSP model, IMF, priors of 
+            parameters for SED fitting}
+    \end{itemize}
+
+\subsection{Basic properties of the sample}
+
+    \begin{itemize}
+        \item \plan{Compare stellar mass from integration of 1-D profile and the 
+            \texttt{cModel} photometry}
+        \item \plan{Stellar mass, redshift, K-corrected color distributions.}
+        \item \plan{Red sequence properties}    
+        \item \plan{Potential ``contaminations'' from disc galaxies}
+    \end{itemize}
+
+    \todo{Justify why we can assume most very massive galaxies in \nonbcg haloes are
+        central galaxies}
+
+%% ------------------------------------------------------------------------------------ %%
 
@@
 
+\subsection{Impact of deep photometry on the luminosity and stellar mass function}
+
+\subsection{Comparison of stellar mass density profiles}
+
+    \plan{Brief summary of the process of sample matching}
+
+\subsubsection{Using stellar mass derived from the GAMA survey}
+
+\subsubsection{Using stellar mass within 10 kpc aperture}
+
+\subsubsection{Using stellar mass within 100 kpc aperture}
+
+\subsection{Relations between stellar mass within different physical apertures}
+
+\subsection{$M_{\ast}-R_{\mathrm{50}}$ relation}
+
+%% ------------------------------------------------------------------------------------ %%
+
 \section{Discussion}
+
+\subsection{Implications on assembly history of massive galaxies}
+
+    \plan{Comparison of mass profiles with previous studies at high redsfhit}
+
+\subsection{Ellipticity profiles}
+
+\subsection{The impact of $M/L$ gradient}
+
+\subsection{Massive satellites of the $\Lambda > 20$ haloes}
+\song{TBD: optional}
+
+\subsection{Connection and difference with the Intra-Cluster Light}
+
+\subsection{Future improvements}
+
+    \begin{enumerate}
+        \item \plan{Improvements of HSC data reduction: better sky modelling; 
+            \texttt{redMaPPer} clusters using HSC photometry.}
+        \item \plan{Comparison with 2-D image modelling method.}
+        \item \plan{``Correct'' the PSF smeearing effect at the center with the help of 
+            residual correct 2-D model.}
+    \end{enumerate}
+
+%% ------------------------------------------------------------------------------------ %%
 
@@
 
-%%%%%%%%%%: Acknowledge %%%%%%%%%%
+%% ------------------------------------------------------------------------------------ %%
 
@@
 
-  1. Acknowledgements for HSC 
-  2. Acknowledgements for Kevin and Alexie's funding 
-  3. Acknowledgements for the Python libraries
+  The Hyper Suprime-Cam (HSC) collaboration includes the astronomical
+  communities of Japan and Taiwan, and Princeton University.  The HSC
+  instrumentation and software were developed by the National
+  Astronomical Observatory of Japan (NAOJ), the Kavli Institute for the
+  Physics and Mathematics of the Universe (Kavli IPMU), the University
+  of Tokyo, the High Energy Accelerator Research Organization (KEK), the
+  Academia Sinica Institute for Astronomy and Astrophysics in Taiwan
+  (ASIAA), and Princeton University.  Funding was contributed by the FIRST 
+  program from Japanese Cabinet Office, the Ministry of Education, Culture, 
+  Sports, Science and Technology (MEXT), the Japan Society for the 
+  Promotion of Science (JSPS),  Japan Science and Technology Agency 
+  (JST),  the Toray Science  Foundation, NAOJ, Kavli IPMU, KEK, ASIAA,  
+  and Princeton University.
 
@@
 
+  \todo{Full acknowledgement}\\
+  \begin{itemize}
+      \item Acknowledgements for Kevin and Alexie's funding 
+      \item Acknowledgements for the Python libraries
+  \end{itemize}
+
 %%%%%%%%%%: Bibligraphic Section %%%%%%%%%%
@@
 
-\bibliography{redbcg}
+\bibliography{hsc_massive.bbl}
+\bibliographystyle{apj}
 
@@
 
-\section{A. Atlas of 1-D Profiles}
+\section{A. Extraction of 1-D surface brightness profile}
+
+\section{B. Derive average mass-to-light ratio using \texttt{iSEDFit}}
 
@@
     \centering 
-    \includegraphics[width=16.5cm]{fig/fig1.png}
-    \caption{
-   Cartoons that illustrate the basic idea of the proposed method for the
-   estimation of average merger mass ratio.  The style is adopted from Faber\etal (2007).
-   The upper panels show the basic
-   picture of the ``two-phase'' formation scenario. The lower panel describes
-   a general picture for the evolution of massive galaxies on the
-   $M_{\ast}$-color plane.  After massive ETGs were quenched, they quickly
-   moved to the red-sequence, and gradually evolved along it as they are
-   becoming redder due to the aging of stellar population, and more massive due
-   to the accumulation of extended stellar envelope through many minor (dry)
-   mergers.  Since the stellar content of smaller system should have lower
-   metallicity, the outer envelope naturally has a bluer color compared to inner
-   region.  And, such color difference reflects the average mass ratio of all
-   mergers that contribute to the second phase of evolution.  Larger color
-   difference means more stellar material came from smaller galaxies, hence
-   makes minor merger more important.  
-   }
+    \includegraphics[width=15.5cm]{fig/fig1.png}
+    \caption{Figure.1\todo{Caption}}
     \label{figure:1}
+\end{figure}
+
+% Fig. 2
+\clearpage
+\figurenum{2}
+\begin{figure}
+    \centering 
+    \includegraphics[width=13.5cm]{fig/massive_s15b_g15_sample.png}
+    \caption{Figure.2\todo{Caption}}
+    \label{figure:2}
+\end{figure}
+
+% Fig. 3
+\clearpage
+\figurenum{3}
+\begin{figure}
+    \centering 
+    \includegraphics[width=13.5cm]{fig/massive_s15b_zuse_hist1.png}
+    \caption{Figure.3\todo{Caption}}
+    \label{figure:3}
+\end{figure}
+
+% Fig. 4
+\clearpage
+\figurenum{4}
+\begin{figure}
+    \centering 
+    \includegraphics[width=15.5cm]{fig/redbcg_1_HSC-I_full_imgsub_ellip_default_sum.png}
+    \caption{Figure.4\todo{Caption}}
+    \label{figure:4}
+\end{figure}
+
+% Fig. 5
+\clearpage
+\figurenum{5}
+\begin{figure}
+    \centering 
+    \includegraphics[width=14.0cm]{fig/redbcg_1_HSC-I_full_imgsub_ellip_default_compare.png}
+    \caption{Figure.5\todo{Caption}}
+    \label{figure:5}
 \end{figure}

### 2016-07-23 draft/draft_v0.tex
Start to work on sample selection section

--- 2016-06-17 draft/ms.tex
@@
 \def\ser{{S\'{e}rsic\ }}
-\def\redm{\texttt{redMaPPer}}
+\def\redm{\texttt{redMaPPer\ }}
 \def\redbcg{$\Lambda \ge 30$}
 \def\nonbcg{$\Lambda < 30$}
+\def\logms{$\log (M_{\star}/M_{\odot})$}
+\def\logmh{$\log (M_{\mathrm{Halo}}/M_{\odot})$}
 
@@
 \newcommand{\plan}[1]{\textcolor{cyan}{#1}}
-\newcommand{\addref}[1]{\textcolor{red}{REF}}
+\newcommand{\addref}{{\textcolor{red}{REF}}}
 \newcommand{\comment}[2]{\textcolor{blue}{\textbf{[Comment (#1): #2]}}}
@@
 \begin{abstract}
-    \todo{Place holder; This is the abstract for talk}\\
+    \todo{Place holder; This is the abstract used for giving a talk.}\\
     Under the most popular formation scenario, the structures of massive central galaxies
@@
             high-mass end.}
-        \item \plan{Brief summary of the current understanding of thieir cosmic assembly 
+        \item \plan{Brief summary of the current understanding of their cosmic assembly 
             history.}
@@
     provides discussions of the assumptions used in this work, the potentially interesting
-    physical implications, and several future improvements, ending with a sumary in
+    physical implications, and several future improvements, ending with a summary in
     Section~6.
 
-    Within this work, we assume $H_0$ = 70~km~s$^{-1}$ Mpc$^{-1}$, ${\Omega}_m=0.3$, and
-    ${\Omega}_{\Lambda}=0.7$.
+    All the magnitudes used here are in AB system (\addref).  
+    Within this work, we assume $H_0$ = 70~km~s$^{-1}$ Mpc$^{-1}$, ${\Omega}_m=0.3$, 
+    and ${\Omega}_{\Lambda}=0.7$.
 
@@
 
-    \todo{Brief introduction, see the same section in other people's work} \\
+    The Subaru Strategic Program (SSP, \addref ) makes use of the new prime-focus 
+    camera, the Hyper Suprime-Cam (HSC; \addref: Miyazaki\etal 2012), on the 8.2-m 
+    Subaru telescope at Mauna Kea.  
+    Taking advantage of the large field of view (FoV; 1.5 deg in diameter) of HSC, 
+    this ambitious multi-layer photometric survey will cover $\sim 1400$ deg$^2$ of 
+    sky in 5 broad bands (\textit{g r i z Y}) to the depth of $r \sim 26$ mag in the 
+    \texttt{WIDE} part in the next few years.  
+    This work is based on the internal data release \texttt{S15B}, which covers 
+    $\sim 100$ square of degree of sky in all 5-band to the required depth of 
+    \texttt{WIDE} survey.  
+    The regions covered by this release are overlapped with several previous 
+    spectroscopic survey (e.g. SDSS/BOSS \addref; GAMA \addref).
 
-    This work makes use of the internal data release \texttt{S15B}, which covers $\sim 100$
-    square of degree of sky in all 5-band to the required depth of \texttt{WIDE} survey.
+    The data are processed with \texttt{hscPipe 4.0.1}, a derivative of the Large 
+    Synoptic Survey Telescope (LSST) pipeline (\addref: Ivezic\etal 2008,
+    Axelrod\etal 2010), modified for use with Suprime-Cam and Hyper Suprime-Cam.  
+    \texttt{hscPipe} first bias subtract, flat field, model background, and 
+    perform object detection and measurement on the single exposure data. 
+    Then, different exposures are warped onto a common World Coordinate System 
+    (WCS) and combined into final images with improved signal-to-noise ratio 
+    (SNR) after astrometric and photometric calibration.  
+    The pixel scale of the combined images is 0.168$\arcsec$.
+    The photometric calibration is based on data obtained from the Panoramic 
+    Survey Telescope and Rapid Response System (Pan-STARRS) 1 imaging survey 
+    (\addref: Schlafly\etal 2012, Tonry\etal 2012, Magnier\etal 2013). 
+    To achieve consistent deblending and photometry across all bands, the 
+    \texttt{hscPipe} will perform multi-band post-processing on the combined 
+    images.  
+    The footprints and peaks of detected sources on each band will be 
+    merged into a single catalog.    
+    This consistent set of peaks and footprints is used as starting point 
+    for deblend and measure objects on the combined images of each band.  
+    These measurements are then merged into a reference catalog. 
+    After fixing the centroids, shape, and other non-amplitude parameters 
+    of every object in this catalog, \texttt{hscPipe} will derive forced 
+    photometry measurements at each band. 
+    Details of \texttt{hscPipe} and the multi-band processing method will 
+    be presented in \addref (Bosch\etal 2017?).
 
-    \todo{The following part is borrowed from Chan's work; Need to re-write}\\
-    HSC is the new prime-focus camera on the 8.2-m Subaru telescope located at Mauna Kea, 
-    Hawaii.  The field of view (FOV) is 1.5 deg in diameter (\addref: Miyazaki\etal 2012) 
-    which is ten times larger than the FOV of Suprime-Cam (\addref: Miyazaki\etal 2002). 
-    The HSC Subaru Strategic Program (SSP) survey consists of three layers with different 
-    depths: wide, deep and ultra-deep. The wide survey will cover $\sim1400$ deg$^2$ to 
-    $r\sim26$ mag in {\it grizY} broad bands.
+    In Figure 1, we compare the false color ({\tt gri}) images of three nearby 
+    massive ETGs from both SDSS and HSC surveys.  
+    The images are generated using similar scaling and color schemes, and clearly 
+    demonstrate HSC's capability to reach to low surface brightness domain.  
+    In $i$-band (ignoring the slight difference in filter response curve), the 
+    HSC \texttt{WIDE} image is $2.5$-$3.0$ magnitude deeper than SDSS on average.  
+    This gives us huge advantage in exploring the outskirt of massive ETGs given 
+    their extended, shallow outer surface brightness profiles.
 
-    The data are processed with \texttt{hscPipe 4.0.1}, a derivative of the Large Synoptic 
-    Survey Telescope (LSST) pipeline (\addref: Ivezic\etal 2008, Axelrod\etal 2010), 
-    modified for use with Suprime-Cam and Hyper Suprime-Cam.  The photometric calibration 
-    is based on data obtained from the Panoramic Survey Telescope and Rapid Response 
-    System (Pan-STARRS) 1 imaging survey (\addref: Schlafly\etal 2012, Tonry\etal 2012, 
-    Magnier\etal 2013).
+    Motivated by the requirement of weak lensing analysis, the $i$-band data 
+    typically has the best seeing in all five bands (the median seeing is around 
+    FWHM$\sim 0.8\arcsec$).  Therefore, we will mostly use the $i$-band images
+    to study the structure of galaxies.
 
-    The pixel scale of the reduced images in the data releases is 0.168$\arcsec$.
+\subsection{Massive central galaxies in different environments}
 
-    \plan{\textbf{Fig.1}: Comparison of SDSS and HSC color image}
+    The main scientific goal of this work is to investigate mass assembly history 
+    of massive, central ETGs, and its dependence on environments (or host dark halo 
+    mass) through their the spatial distribution of stellar mass.
 
-\subsection{Candidates of massive galaxies}
+    To achieve this goal, we will select \logms$ > 11.5$ massive central 
+    galaxies within host halo mass larger and smaller than \logmh$= 14.0$
+    at $0.2 < z < 0.5$.  
+    As both $M_{\star}$-$M_{\mathrm{Halo}}$ relation and stellar mass function 
+    are still quite uncertain at \logms$ > 11.5$, it is of great interest to 
+    investigate the structure of galaxies in this region carefully.
+    And, this stellar mass cut can greatly reduce the contamination of 
+    satellites (e.g. \addref: van~Uitert\etal 2016).  
+    Meanwhile, under the adopted cosmology, $1\arcsec$ equals 3.3 and 6.1 kpc 
+    at redshit 0.2 and 0.5.  
+    Hence, our redshift bin enables us to reliable measure the total stellar 
+    mass within the inner 5 to 10 kpc (where the ``in-situ'' component should 
+    still dominates) of massive galaxies at the high redshift end assuming the
+    typical seeing of data. 
+    At the same time, the depth of the data still allows to study the very 
+    outskirt ($\sim 100$ kpc) of these galaxies at $z\sim 0.5$.  
+    Also, such limits on mass and redshift ensure us a sizable sample while let 
+    us safely ignore any significant structural evolution (no star formation, 
+    lower merger rate \etal. e.g. \addref).
+
+    Based on recent constraints of $M_{\star}$-$M_{\mathrm{Halo}}$ 
+    relation (e.g. \addref), above \logms$ = 11.5$, there is a large scatter 
+    of halo mass at fixed stellar mass.  
+    At \logmh$<14.0$, these massive galaxies are mostly the centrals of small 
+    groups; while at \logmh$>14.0$, they start to become the centrals of very 
+    massive groups and galaxy clusters.   
+    Limited by the sample size and the capability of measureing halo mass for 
+    individual central galaxy, we will simply separate the sample into two 
+    broad halo mass bins with the help of the \redm cluster catalog 
+    \footnote{See: http://risa.stanford.edu/redmapper/} (
+    \texttt{v5.10}, e.g. \addref: Rykoff\etal 2014; Rozo\etal 2015b).
+    These clusters are selected from the SDSS DR8 photometric data 
+    using overdensity of red-sequence galaxies. 
+    For each cluster, the catalog provides robust estimations of 
+    photometric redshift $z_{\Lambda}$ and richness $\Lambda$, along with 
+    the best candidate of the central galaxy (the one with the highest 
+    central probability \texttt{P\_CEN}).
+    Information about the identified member candidates is also provided 
+    separately. 
+    Please see Rozo\etal (2014, 2015a, 2015b) for more details about the 
+    performance of the \redm cluster catalog.      
+    Several works (e.g. Li\etal 2015; Saro\etal 2015; Farahi\etal 2016; 
+    Simet\etal 2016) have tried to calibrate the $M_{200c}-\Lambda$ relation 
+    using different methods.
+    Despite the slightly different calibrations derived, it is safe to 
+    assume that most clusters identified by \redm ($\Lambda > 20$) have
+    $\log (M_{200c}/M_{\odot}) \geq 14.0$.  
+    Considering the typical uncertainty of richness, and the fact that 
+    \redm catalog starts to become incomplete toward low richness 
+    ($\Lambda < 40$) end at $z > 0.33$, we will focus on the $\Lambda > 30$
+    clusters in this work.  
+    Based on the calibrations from Farahi\etal (2016) or Simet\etal (2016), 
+    such richness cut gives us haloes with 
+    $M_{200c} \geq 1.56\pm0.35 \times 10^{14} M_{\odot}$ or 
+    $M_{200c} \geq 1.60\pm0.11 \times 10^{14} M_{\odot}$.  
+    Therefore, \redm can provide us a sample of massive central galaxies in
+    \logmh$\geq 14.0$ haloes.  
+    And, we assume that, in the same footprints and redshift range, the 
+    \logms$\geq 11.5$ galaxies outside \redm clusters are most likely to be 
+    the central of \logmh$< 14.0$ haloes.
+
+    According to Leauthaud\etal (2016), all $0.2 < z < 0.5$ and \logms$\geq 11.5$
+    galaxies should have $i_{\mathrm{SDSS, cModel}} \leq 21.0$ mag. 
+    Ignoring the tiny difference in response curves between SDSS and HSC 
+    $i$-band filters, we started by selecting all galaxies with 
+    $i_{\mathrm{HSC, cModel}} \leq 21.5$ in the regions that are covered 
+    in all five filters, and have already reached the expected depth of 
+    \texttt{WIDE} survey.  
+    The details of the HSC \texttt{cModel} photometry, and its performence
+    will be described in Bosch\etal in. prep. 
+    It is quite similar to the SDSS \texttt{cModel} in principle as it also 
+    fits the total flux of an object using a combination of de~Vaucouleur 
+    and exponential components after the PSF convolution is considered.  
+    In our selection, we require well defined centroids and \texttt{cModel} 
+    magnitude in all five bands. 
+    \song{Should we discuss the impact of failed cModel photometry?}
+    A series of quality control cuts are applied to remove objects that are 
+    affected by saturation, cosmic ray, other optical artefacts.  
+    After these cuts, a total number of \plan{N1} galaxies left in the 
+    sample () \todo{Finish this part}  
+    (This sample will be referred as \texttt{phoAll}).
+
+    We match this sample with the central galaxies of \redm catalogs using 
+    a $2.0\arcsec$ radius, and it results in \plan{N2} galaxies.  
+    A small fraction of \redm centrals in the our footprints do not have 
+    matched object in our sample due to severe contamination from optical 
+    artefacts or bleeding trails from saturated objects.  
+    And slight change of the mathcing radius has no impact of this sample.  
+    For galaxy in this sample (will be referred as \texttt{redBCG}), 
+    the photometric redshift of the cluster is available for each of them; 
+    while for \plan of them, the spectroscopic redshift from SDSS DR8 is 
+    also provided by \redm catalog when available.
+
+    For the vast majority of galaxies that are not the centrals of very massive
+    haloes, we need other sources for their redshfit estimations. 
+    Although there has been many efforts for deriving photometric redshift 
+    (photo-$z$) using HSC five-band photometry, it is still a working progress 
+    now, and its performence at $z \leq 0.5$ is expected to be less satisfying 
+    due to the lack of information at the shorter wavelength side of the 
+    4000$\AA$ break.  
+    Therefore, we will only rely on external spectroscopic redshifts (spec-$z$)
+    for this work.  
+    The HSC database compiles a catalog of external spec-$z$ for this data 
+    release by matching the detected objects with public data of several 
+    spectroscopic surveys (e.g. SDSS/BOSS \addref; GAMA \addref; PRIMUS \addref;
+    \etal). 
+    Duplicated matches from different sources are merged through interal 
+    matching using $0.5\arcsec$ radius.
+
+    We match the \texttt{phoAll} sample with this external spec-$z$ catalog 
+    using a $1.0 \arcsec$ radius, and it leads to \plan{N3} results. 
+    There are \plan{N4} objects at $0.2 \leq z \leq 0.5$.   
+    The \texttt{redBCG} sample is also matched in the same way. 
+    For ...
+    \todo{Finish it...}
 

### 2016-07-24 draft/build.sh
Fix the bib file

@@ -1,0 +1,4 @@
+pdflatex draft_v0
+bibtex draft_v0
+pdflatex draft_v0
+pdflatex draft_v0

### 2016-07-24 draft/draft_v0.tex
Minor update

@@
 \usepackage{CJK}
+\usepackage{natbib}
+\usepackage{hyperref}
 \usepackage[usenames]{color}
+
+% Package Settings
+\bibliographystyle{apj}
+\hypersetup{colorlinks=true,
+            citecolor=cyan,
+            linkcolor=cyan,
+            filecolor=magenta,      
+            urlcolor=cyan}
+\urlstyle{same}
 
@@
 \DeclareGraphicsExtensions{.pdf,.png,.jpg}
-\bibliographystyle{apj}
 \input psfig.tex
@@
 \def\cc{cm$^{-3}$}
-\def\etal{{\ et al.~}}
 \def\flamb{erg s$^{-1}$ cm$^{-2}$ \AA$^{-1}$}
@@
 \def\fnu{erg s$^{-1}$ cm$^{-2}$ Hz$^{-1}$}
-\def\hst{{\it HST}}
+\def\hst{{\textit{HST}}}
 \def\kms{km s$^{-1}$}
@@
 \def\peryr{yr$^{-1}$}
-\def\pp{\parshape 2 0truein 6.1truein .3truein 5.5truein}
 \def\reference{\noindent\pp}
@@
 \newcommand{\gt}{>}
+
+\def\etal{{\ et al.~}}
 \def\galfit{{\tt GALFIT}}
 \def\ser{{S\'{e}rsic\ }}
-\def\redm{\texttt{redMaPPer\ }}
+\def\redm{\texttt{redMaPPer}~}
 \def\redbcg{$\Lambda \ge 30$}
@@
 % Commenting:
-\newcommand{\todo}[1]{\textcolor{red}{\textbf{TODO: #1}}}
+\newcommand{\todo}[1]{\textcolor{red}{\textbf{TODO:~#1}}}
 \newcommand{\plan}[1]{\textcolor{cyan}{#1}}
 \newcommand{\addref}{{\textcolor{red}{REF}}}
-\newcommand{\comment}[2]{\textcolor{blue}{\textbf{[Comment (#1): #2]}}}
+\newcommand{\note}[2]{\textcolor{blue}{\textbf{[Comment (#1): #2]}}}
 \newcommand{\song}[1]{\textcolor{magenta}{\textbf{[Song: #1]}}}
@@
     Universe, The University of Tokyo Institutes for Advanced Study, 
-    the University of Tokyo (Kavli IPMU, WPI), Kashiwa 277-8583, Japan}
+    the University of Tokyo (Kavli IPMU, WPI), Kashiwa 277--8583, Japan}
 \altaffiltext{2}{Princeton University Observatory, 
@@
 \altaffiltext{3}{Institute of Astronomy and Astrophysics, Academia Sinica, 
-    P.O.~Box 23-141, Taipei 10617, Taiwan}
+    P.O.~Box 23--141, Taipei 10617, Taiwan}
 \altaffiltext{4}{Carnegie-Mellon University \todo{correct affiliation here}}
@@
         \item \plan{Here we take advantages of the ambitious Hyper-Suprime camera 
-            survey....}
+            survey\ldots}
     \end{itemize}
@@
 
-    All the magnitudes used here are in AB system (\addref).  
+    All the magnitudes used here are in AB system (\addref), and are corrected 
+    for Galactic extinction using calibrations from \citet{Schlafly11}.
     Within this work, we assume $H_0$ = 70~km~s$^{-1}$ Mpc$^{-1}$, ${\Omega}_m=0.3$, 
@@
 
-    The Subaru Strategic Program (SSP, \addref ) makes use of the new prime-focus 
-    camera, the Hyper Suprime-Cam (HSC; \addref: Miyazaki\etal 2012), on the 8.2-m 
-    Subaru telescope at Mauna Kea.  
-    Taking advantage of the large field of view (FoV; 1.5 deg in diameter) of HSC, 
-    this ambitious multi-layer photometric survey will cover $\sim 1400$ deg$^2$ of 
-    sky in 5 broad bands (\textit{g r i z Y}) to the depth of $r \sim 26$ mag in the 
-    \texttt{WIDE} part in the next few years.  
-    This work is based on the internal data release \texttt{S15B}, which covers 
-    $\sim 100$ square of degree of sky in all 5-band to the required depth of 
-    \texttt{WIDE} survey.  
-    The regions covered by this release are overlapped with several previous 
-    spectroscopic survey (e.g. SDSS/BOSS \addref; GAMA \addref).
+    The Subaru Strategic Program (SSP, \addref) makes use of the new prime-focus camera,
+    the Hyper Suprime-Cam (HSC;~\addref: Miyazaki\etal 2012), on the 8.2-m Subaru
+    telescope at Mauna Kea.  
+    Taking advantage of the large field of view (FoV;~1.5 deg in diameter) of HSC, this
+    ambitious multi-layer photometric survey will cover $\sim 1400$ deg$^2$ of sky in 5
+    broad bands (\textit{g r i z Y}) to the depth of $r \sim 26$ mag in the \texttt{WIDE}
+    part in the next few years.  
+    This work is based on the internal data release \texttt{S15B}, which covers $\sim 100$
+    square of degree of sky in all 5-band to the required depth of \texttt{WIDE} survey.  
+    The regions covered by this release are overlapped with several previous spectroscopic
+    survey (e.g. SDSS/BOSS \addref; GAMA \addref).
 
-    The data are processed with \texttt{hscPipe 4.0.1}, a derivative of the Large 
-    Synoptic Survey Telescope (LSST) pipeline (\addref: Ivezic\etal 2008,
-    Axelrod\etal 2010), modified for use with Suprime-Cam and Hyper Suprime-Cam.  
-    \texttt{hscPipe} first bias subtract, flat field, model background, and 
-    perform object detection and measurement on the single exposure data. 
-    Then, different exposures are warped onto a common World Coordinate System 
-    (WCS) and combined into final images with improved signal-to-noise ratio 
-    (SNR) after astrometric and photometric calibration.  
-    The pixel scale of the combined images is 0.168$\arcsec$.
-    The photometric calibration is based on data obtained from the Panoramic 
-    Survey Telescope and Rapid Response System (Pan-STARRS) 1 imaging survey 
-    (\addref: Schlafly\etal 2012, Tonry\etal 2012, Magnier\etal 2013). 
-    To achieve consistent deblending and photometry across all bands, the 
-    \texttt{hscPipe} will perform multi-band post-processing on the combined 
-    images.  
-    The footprints and peaks of detected sources on each band will be 
-    merged into a single catalog.    
-    This consistent set of peaks and footprints is used as starting point 
-    for deblend and measure objects on the combined images of each band.  
-    These measurements are then merged into a reference catalog. 
-    After fixing the centroids, shape, and other non-amplitude parameters 
-    of every object in this catalog, \texttt{hscPipe} will derive forced 
-    photometry measurements at each band. 
-    Details of \texttt{hscPipe} and the multi-band processing method will 
-    be presented in \addref (Bosch\etal 2017?).
+    The data are processed with \texttt{hscPipe 4.0.1}, a derivative of the Large Synoptic
+    Survey Telescope (LSST) pipeline (\addref: Ivezic\etal~2008, Axelrod\etal 2010),
+    modified for use with Suprime-Cam and Hyper Suprime-Cam.  
+    \texttt{hscPipe} first bias subtract, flat field, model background, and perform object
+    detection and measurement on the single exposure data. 
+    Then, different exposures are warped onto a common World Coordinate System (WCS) and
+    combined into final images with improved signal-to-noise ratio (SNR) after astrometric
+    and photometric calibration.  
+    The pixel scale of the combined images is 0.168$\arcsec$.  The photometric calibration
+    is based on data obtained from the Panoramic Survey Telescope and Rapid Response
+    System (Pan-STARRS) 1 imaging survey (\addref: Schlafly\etal 2012, Tonry\etal 2012,
+    Magnier\etal 2013). 
+    To achieve consistent deblending and photometry across all bands, the \texttt{hscPipe}
+    will perform multi-band post-processing on the combined images.  
+    The footprints and peaks of detected sources on each band will be merged into a single
+    catalog.    
+    This consistent set of peaks and footprints is used as starting point for deblend and
+    measure objects on the combined images of each band.  
+    These measurements are then merged into a reference catalog.  After fixing the
+    centroids, shape, and other non-amplitude parameters of every object in this catalog,
+    \texttt{hscPipe} will derive forced photometry measurements at each band. 
+    Details of \texttt{hscPipe} and the multi-band processing method will be presented in
+    \addref (Bosch\etal 2017?).
 
-    In Figure 1, we compare the false color ({\tt gri}) images of three nearby 
-    massive ETGs from both SDSS and HSC surveys.  
+    In Figure 1, we compare the false color ({\tt gri}) images of three nearby massive
+    ETGs from both SDSS and HSC surveys.  
     The images are generated using similar scaling and color schemes, and clearly
     demonstrate HSC's capability to reach to low surface brightness domain.  
-    In $i$-band (ignoring the slight difference in filter response curve), the 
-    HSC \texttt{WIDE} image is $2.5$-$3.0$ magnitude deeper than SDSS on average.  
-    This gives us huge advantage in exploring the outskirt of massive ETGs given 
-    their extended, shallow outer surface brightness profiles.
+    In $i$-band (ignoring the slight difference in filter response curve), the HSC
+    \texttt{WIDE} image is $2.5$-$3.0$ magnitude deeper than SDSS on average.  
+    This gives us huge advantage in exploring the outskirt of massive ETGs given their
+    extended, shallow outer surface brightness profiles.
 
-    Motivated by the requirement of weak lensing analysis, the $i$-band data 
-    typically has the best seeing in all five bands (the median seeing is around 
-    FWHM$\sim 0.8\arcsec$).  Therefore, we will mostly use the $i$-band images
-    to study the structure of galaxies.
+    Motivated by the requirement of weak lensing analysis, the $i$-band data typically has
+    the best seeing in all five bands (the median seeing is around FWHM$\sim 0.8\arcsec$).
+    Therefore, we will mostly use the $i$-band images to study the structure of galaxies.
 
-\subsection{Massive central galaxies in different environments}
+\subsection{Massive Central Galaxies in Different Environments}
 
-    The main scientific goal of this work is to investigate mass assembly history 
-    of massive, central ETGs, and its dependence on environments (or host dark halo 
-    mass) through their the spatial distribution of stellar mass.
+    The main scientific goal of this work is to investigate mass assembly history of
+    massive, central ETGs, and its dependence on environments (or host dark halo mass)
+    through their the spatial distribution of stellar mass.
 
-    To achieve this goal, we will select \logms$ > 11.5$ massive central 
-    galaxies within host halo mass larger and smaller than \logmh$= 14.0$
-    at $0.2 < z < 0.5$.  
-    As both $M_{\star}$-$M_{\mathrm{Halo}}$ relation and stellar mass function 
-    are still quite uncertain at \logms$ > 11.5$, it is of great interest to 
-    investigate the structure of galaxies in this region carefully.
-    And, this stellar mass cut can greatly reduce the contamination of 
-    satellites (e.g. \addref: van~Uitert\etal 2016).  
-    Meanwhile, under the adopted cosmology, $1\arcsec$ equals 3.3 and 6.1 kpc 
-    at redshit 0.2 and 0.5.  
-    Hence, our redshift bin enables us to reliable measure the total stellar 
-    mass within the inner 5 to 10 kpc (where the ``in-situ'' component should 
-    still dominates) of massive galaxies at the high redshift end assuming the
-    typical seeing of data. 
-    At the same time, the depth of the data still allows to study the very 
-    outskirt ($\sim 100$ kpc) of these galaxies at $z\sim 0.5$.  
-    Also, such limits on mass and redshift ensure us a sizable sample while let 
-    us safely ignore any significant structural evolution (no star formation, 
-    lower merger rate \etal. e.g. \addref).
+    To achieve this goal, we will select \logms$ > 11.5$ massive central galaxies within
+    host halo mass larger and smaller than \logmh$= 14.0$ at $0.2 < z < 0.5$.  
+    As both $M_{\star}$-$M_{\mathrm{Halo}}$ relation and stellar mass function are still
+    quite uncertain at \logms$ > 11.5$, it is of great interest to investigate the
+    structure of galaxies in this region carefully.
+    And, this stellar mass cut can greatly reduce the contamination of satellites (e.g.
+    \addref: van~Uitert\etal 2016).  
+    Meanwhile, under the adopted cosmology, $1\arcsec$ equals 3.3 and 6.1 kpc at redshit
+    0.2 and 0.5.  
+    Hence, our redshift bin enables us to reliable measure the total stellar mass within
+    the inner 5 to 10 kpc (where the ``in-situ'' component should still dominates) of
+    massive galaxies at the high redshift end assuming the typical seeing of data. 
+    At the same time, the depth of the data still allows to study the very outskirt ($\sim
+    100$ kpc) of these galaxies at $z\sim 0.5$.  Also, such limits on mass and redshift
+    ensure us a sizable sample while let us safely ignore any significant structural
+    evolution (no star formation, lower merger rate \etal e.g. \addref).
 
-    Based on recent constraints of $M_{\star}$-$M_{\mathrm{Halo}}$ 
-    relation (e.g. \addref), above \logms$ = 11.5$, there is a large scatter 
-    of halo mass at fixed stellar mass.  
-    At \logmh$<14.0$, these massive galaxies are mostly the centrals of small 
-    groups; while at \logmh$>14.0$, they start to become the centrals of very 
-    massive groups and galaxy clusters.   
-    Limited by the sample size and the capability of measureing halo mass for 
-    individual central galaxy, we will simply separate the sample into two 
-    broad halo mass bins with the help of the \redm cluster catalog 
-    \footnote{See: http://risa.stanford.edu/redmapper/} (
-    \texttt{v5.10}, e.g. \addref: Rykoff\etal 2014; Rozo\etal 2015b).
-    These clusters are selected from the SDSS DR8 photometric data 
-    using overdensity of red-sequence galaxies. 
-    For each cluster, the catalog provides robust estimations of 
-    photometric redshift $z_{\Lambda}$ and richness $\Lambda$, along with 
-    the best candidate of the central galaxy (the one with the highest 
-    central probability \texttt{P\_CEN}).
-    Information about the identified member candidates is also provided 
-    separately. 
-    Please see Rozo\etal (2014, 2015a, 2015b) for more details about the 
-    performance of the \redm cluster catalog.      
-    Several works (e.g. Li\etal 2015; Saro\etal 2015; Farahi\etal 2016; 
-    Simet\etal 2016) have tried to calibrate the $M_{200c}-\Lambda$ relation 
-    using different methods.
-    Despite the slightly different calibrations derived, it is safe to 
-    assume that most clusters identified by \redm ($\Lambda > 20$) have
-    $\log (M_{200c}/M_{\odot}) \geq 14.0$.  
-    Considering the typical uncertainty of richness, and the fact that 
-    \redm catalog starts to become incomplete toward low richness 
-    ($\Lambda < 40$) end at $z > 0.33$, we will focus on the $\Lambda > 30$
-    clusters in this work.  
+    Based on recent constraints of $M_{\star}$-$M_{\mathrm{Halo}}$ relation (e.g.
+    \addref), above \logms$ = 11.5$, there is a large scatter of halo mass at fixed
+    stellar mass.  
+    At \logmh$<14.0$, these massive galaxies are mostly the centrals of small groups;
+    while at \logmh$>14.0$, they start to become the centrals of very massive groups and
+    galaxy clusters.   
+    Limited by the sample size and the capability of measureing halo mass for individual
+    central galaxy, we will simply separate the sample into two broad halo mass bins with
+    the help of the \redm cluster catalog\footnote{See:
+    http://risa.stanford.edu/redmapper/} ( \texttt{v5.10}, e.g. \addref: Rykoff\etal 2014;
+    Rozo\etal 2015b).
+    These clusters are selected from the SDSS DR8 photometric data using overdensity of
+    red-sequence galaxies. 
+    For each cluster, the catalog provides robust estimations of photometric redshift
+    $z_{\Lambda}$ and richness $\Lambda$, along with the best candidate of the central
+    galaxy (the one with the highest central probability \texttt{P\_CEN}).
+    Information about the identified member candidates is also provided separately. 
+    Please see Rozo\etal (2014, 2015a, 2015b) for more details about the performance of
+    the \redm cluster catalog.      
+    Several works (e.g. Li\etal 2015; Saro\etal 2015; Farahi\etal 2016; Simet\etal 2016)
+    have tried to calibrate the $M_{200c}-\Lambda$ relation using different methods.
+    Despite the slightly different calibrations derived, it is safe to assume that most
+    clusters identified by \redm ($\Lambda > 20$) have $\log (M_{200c}/M_{\odot}) \geq
+    14.0$.  
+    Considering the typical uncertainty of richness, and the fact that \redm catalog
+    starts to become incomplete toward low richness ($\Lambda < 40$) end at $z > 0.33$, we
+    will focus on the $\Lambda > 30$ clusters in this work.  
     Based on the calibrations from Farahi\etal (2016) or Simet\etal (2016), 
@@
     $M_{200c} \geq 1.60\pm0.11 \times 10^{14} M_{\odot}$.  
-    Therefore, \redm can provide us a sample of massive central galaxies in
-    \logmh$\geq 14.0$ haloes.  
-    And, we assume that, in the same footprints and redshift range, the 
-    \logms$\geq 11.5$ galaxies outside \redm clusters are most likely to be 
-    the central of \logmh$< 14.0$ haloes.
+    Therefore, \redm can provide us a sample of massive central galaxies in \logmh$\geq
+    14.0$ haloes.  
+    And, we assume that, in the same footprints and redshift range, the \logms$\geq 11.5$
+    galaxies outside \redm clusters are most likely to be the central of \logmh$< 14.0$
+    haloes.
 
-    According to Leauthaud\etal (2016), all $0.2 < z < 0.5$ and \logms$\geq 11.5$
-    galaxies should have $i_{\mathrm{SDSS, cModel}} \leq 21.0$ mag. 
-    Ignoring the tiny difference in response curves between SDSS and HSC 
-    $i$-band filters, we started by selecting all galaxies with 
-    $i_{\mathrm{HSC, cModel}} \leq 21.5$ in the regions that are covered 
-    in all five filters, and have already reached the expected depth of 
-    \texttt{WIDE} survey.  
-    The details of the HSC \texttt{cModel} photometry, and its performence
-    will be described in Bosch\etal in. prep. 
-    It is quite similar to the SDSS \texttt{cModel} in principle as it also 
-    fits the total flux of an object using a combination of de~Vaucouleur 
-    and exponential components after the PSF convolution is considered.  
-    In our selection, we require well defined centroids and \texttt{cModel} 
-    magnitude in all five bands. 
+    According to Leauthaud\etal (2016), all $0.2 < z < 0.5$ and \logms$\geq 11.5$ galaxies
+    should have $i_{\mathrm{SDSS, cModel}} \leq 21.0$ mag.  Ignoring the tiny difference
+    in response curves between SDSS and HSC $i$-band filters, we started by selecting all
+    galaxies with $i_{\mathrm{HSC, cModel}} \leq 21.5$ in the regions that are covered in
+    all five filters, and have already reached the expected depth of \texttt{WIDE} survey.  
+    %% The SQL search is saved as "sample.sql" 
+    %% The master catalog used here is "dr1_wide_galaxy_icmodel_21.5.fits"
+    %%   The original catalogs contain 2275477 objects
+    The details of the HSC \texttt{cModel} photometry, and its performence will be
+    described in \addref Bosch\etal in.\ prep. 
+    It is quite similar to the SDSS \texttt{cModel} in principle as it also fits the total
+    flux of an object using a combination of de~Vaucouleur and exponential components
+    after the PSF convolution is considered.  
+    For this work, we select objects that are classified as extended, have well defined 
+    centroids, do not fail during the deblending process, and have \texttt{cModel} 
+    magnitudes in all five bands. 
     \song{Should we discuss the impact of failed cModel photometry?} 
-    A series of quality control cuts are applied to remove objects that are 
-    affected by saturation, cosmic ray, other optical artefacts.  
-    After these cuts, a total number of \plan{N1} galaxies left in the 
-    sample () \todo{Finish this part}  
-    (This sample will be referred as \texttt{phoAll}).
+    A series of quality control cuts are applied to remove objects that are affected by 
+    saturation, cosmic ray, other optical artefacts; and the ones that are too close to 
+    the edge of the field in all five bands 
+    (each criterion affects less than 8\% of the entire sample).
+    After these cuts, a total number of 1760845 galaxies left in the sample.
+    This sample will be referred as \texttt{hscPho}. 
+    %% Saved as "dr1_wide_galaxy_hscPho.fits"
 
-    We match this sample with the central galaxies of \redm catalogs using 
-    a $2.0\arcsec$ radius, and it results in \plan{N2} galaxies.  
-    A small fraction of \redm centrals in the our footprints do not have 
-    matched object in our sample due to severe contamination from optical 
-    artefacts or bleeding trails from saturated objects.  
+    We match this sample with the central galaxies of \redm catalogs using a $1.0\arcsec$
+    radius, and it results in 704 galaxies.  
+    %% Saved as "dr1_redbcg_hsc_sdss_gama_1arcsec.fits"
+    A small fraction of \redm centrals in the our footprints do not have matched object in
+    our sample due to severe contamination from optical artefacts or bleeding trails from
+    saturated objects.  
     And slight change of the mathcing radius has no impact of this sample.  
-    For galaxy in this sample (will be referred as \texttt{redBCG}), 
-    the photometric redshift of the cluster is available for each of them; 
-    while for \plan of them, the spectroscopic redshift from SDSS DR8 is 
-    also provided by \redm catalog when available.
+    For galaxy in this sample, the photometric redshift of the cluster is available for
+    each of them; and for 72\% of them, the spectroscopic redshift from SDSS DR8 is also
+    provided by \redm catalog when available. 
+    This sample of will be referred as \texttt{redBCG} in the rest of the paper.
 
-    For the vast majority of galaxies that are not the centrals of very massive
-    haloes, we need other sources for their redshfit estimations. 
-    Although there has been many efforts for deriving photometric redshift 
-    (photo-$z$) using HSC five-band photometry, it is still a working progress 
-    now, and its performence at $z \leq 0.5$ is expected to be less satisfying 
-    due to the lack of information at the shorter wavelength side of the 
-    4000$\AA$ break.  
-    Therefore, we will only rely on external spectroscopic redshifts (spec-$z$)
-    for this work.  
-    The HSC database compiles a catalog of external spec-$z$ for this data 
-    release by matching the detected objects with public data of several 
-    spectroscopic surveys (e.g. SDSS/BOSS \addref; GAMA \addref; PRIMUS \addref;
-    \etal). 
-    Duplicated matches from different sources are merged through interal 
-    matching using $0.5\arcsec$ radius.
+    For the vast majority of galaxies that are not the centrals of very massive haloes, we
+    need other sources for their redshfit estimations. 
+    Although there has been many efforts for deriving photometric redshift (photo-$z$)
+    using HSC five-band photometry, it is still a working progress now, and its
+    performence at $z \leq 0.5$ is expected to be less satisfying due to the lack of
+    information at the shorter wavelength side of the 4000$\AA$ break.  
+    Therefore, we will only rely on external spectroscopic redshifts (spec-$z$) for this
+    work.  
+    The HSC database compiles a catalog of external spec-$z$ for this data release by
+    matching the detected objects with public data of several spectroscopic surveys (e.g.
+    SDSS/BOSS \addref; GAMA \addref; PRIMUS \addref; \etal). 
+    Duplicated matches from different sources are merged through interal matching using
+    $0.5\arcsec$ radius. 
+    For each object, the quality information of the spec-$z$ from different catalogs are 
+    homogenized into a single flag that indicates whether the redshfit is secure, and 
+    only secure spec-$z$ are used in this work. 
+    %% This is catalog: "dr1_specz_use.fits"
 
-    We match the \texttt{phoAll} sample with this external spec-$z$ catalog 
-    using a $1.0 \arcsec$ radius, and it leads to \plan{N3} results. 
-    There are \plan{N4} objects at $0.2 \leq z \leq 0.5$.   
-    The \texttt{redBCG} sample is also matched in the same way. 
-    For ...
-    \todo{Finish it...}
+    We match the \texttt{hscPho} sample with this external spec-$z$ catalog using a 
+    $1.0 \arcsec$ radius, and it leads to 116813 matched objects.  
+    %% Saved as "dr1_wide_galaxy_icmodel_21.5.fits"
+    Among these matches, there are 42696 objects at $0.2 \leq z \leq 0.5$. 
+    Most of these redshifts come from either SDSS or GAMA survey.
+    To further exclude contamination from satellite galaxies, we aggressively remove 
+    all galaxies that could be associated with the \redm clusters from this catalog.  
+    First, the catalog of \texttt{redBCG} central galaxies is merged with the catalog  
+    of their member galaxies. 
+    Then, through cross matching using $1.0 \arcsec$ radius, all \texttt{hscPho} galaxies 
+    that are within 2.5 Mpc of projected distance to any of cluster member are removed 
+    from the catalog.  
+    After this step, 29973 galaxies are left in the sample. 
+    We will refer this sample as \texttt{nonBCG} later.
+    %% Saved as "dr1_nonbcg_use_sed5b.fits"
 
-    \plan{Selection of the \texttt{PHOTO} sample}
-    \begin{itemize}
-        \item \plan{\texttt{PRIMARY} detection: In the inner region of the \texttt{Tract}
-            and \textt{Patch}; has no \texttt{CHILD}.}
-        \item \plan{Require the galaxy to be detected in all 5-band}
-        \item \plan{For $i$-band detection, we require the object is covered by at least 
-            4 \texttt{Visit}.}
-        \item \plan{Has useful \texttt{cModel} photometry in all 5-band}
-        \item \plan{$i$-band \texttt{cModel} magnitude brigther than 21.0 mag (justify this 
-            later}
-        \item \plan{Has to be extended object.}
-        \item \plan{Has reliable central position and shape using SDSS algorithm}
-        \item \plan{Typical quality cuts in $griz$-band.}
-    \end{itemize}
+    The \texttt{redBCG} sample is also matched with external spec-$z$ catalog in the same
+    way, and we update the redshift of the central galaxies with external spec-$z$ when 
+    it is available.  
+    For the unmatched ones, only 3 of them have spec-$z$ provided by the \redm catalog 
+    (most likely due to different criteria during the selection of spec-$z$ sample).
+    For the rest, we will use the photo-$z$ of the cluster from the \redm catalog instead.
+    At $0.2 \leq z \leq 0.5$, there are 375 central galaxies left in the \texttt{redBCG} 
+    sample. 
+    Among them, 67 (17.9\%) of them do not have spec-$z$.
+    Using the central galaxis have both spec- and photo-$z$, we estimate the median 
+    absolute redshift difference $|z_{\mathrm{Photo}} - z_{\mathrm{Spec}}|$ is 
+    $\sim 0.01$ (only 12 have absolute difference larger than 0.05; and the largest 
+    difference is $\sim 0.12$).
+    Such quality is good enough for the purpose of this work. 
+    %% Saved as "dr1_redbcg_use_sed5b.fits"
 
-    \plan{Selection of the \texttt{SPECZ} sample}
-    \begin{itemize}
-        \item \plan{Brief summary of the HSC spec-z catalog.}
-        \item \plan{Internal catalog match results in 121998 galaxies}
-        \item \plan{Brief break down of the spec-z sample; Most of the spectroscopic 
-            redshift come from SDSS/BOSS and GAMA survey}
-        \item \plan{Only keep objects at $z < 0.6$} \todo{Justify this later}
-    \end{itemize}
+\subsection{Stellar Masses from SED Fitting}
 
-\subsection{Central galaxies of $\Lambda > 20$ haloes using the \redm clusters}
-
-    To select the central galaxies of cluster-level dark matter haloes, we make use of the 
-    \redm cluster catalog \footnote{See: http://risa.stanford.edu/redmapper/}.
-
-    \plan{Match to the \redm catalog}
-    \begin{itemize}
-        \item \plan{For this work, we use the \redm catalog based on SDSS DR8 
-            photometry.} \todo{Need some explanation}
-        \item \plan{Match with the \texttt{PHOTO} sample using a 1.0$\arcsec$
-            matching radius, results in 704 clusters. (Justify this matching radius)}
-        \item \plan{Select the \redm clusters at $z < 0.6$.}
-        \item \plan{There is a small population of central galaxies from \redm that
-            are within the HSC footprint, but does not have matched photometry, 
-            briefly explain them}
-    \end{itemize}
+    To further select galaxies that are truly very massive central galaxies, we use 
+    broadband Spectral Engergy Distributions (SEDs) fitting method (see \addref 
+    Walcher\etal 2011 for a recent review) to derive stellar mass
+    of our samples, and provide $k$-corrected photometry.
 
@@
 
-  The Hyper Suprime-Cam (HSC) collaboration includes the astronomical
-  communities of Japan and Taiwan, and Princeton University.  The HSC
-  instrumentation and software were developed by the National
-  Astronomical Observatory of Japan (NAOJ), the Kavli Institute for the
-  Physics and Mathematics of the Universe (Kavli IPMU), the University
-  of Tokyo, the High Energy Accelerator Research Organization (KEK), the
-  Academia Sinica Institute for Astronomy and Astrophysics in Taiwan
-  (ASIAA), and Princeton University.  Funding was contributed by the FIRST 
-  program from Japanese Cabinet Office, the Ministry of Education, Culture, 
-  Sports, Science and Technology (MEXT), the Japan Society for the 
-  Promotion of Science (JSPS),  Japan Science and Technology Agency 
-  (JST),  the Toray Science  Foundation, NAOJ, Kavli IPMU, KEK, ASIAA,  
-  and Princeton University.
+  The Hyper Suprime-Cam (HSC) collaboration includes the astronomical communities of Japan
+  and Taiwan, and Princeton University.  The HSC instrumentation and software were
+  developed by the National Astronomical Observatory of Japan (NAOJ), the Kavli Institute
+  for the Physics and Mathematics of the Universe (Kavli IPMU), the University of Tokyo,
+  the High Energy Accelerator Research Organization (KEK), the Academia Sinica Institute
+  for Astronomy and Astrophysics in Taiwan (ASIAA), and Princeton University.  Funding was
+  contributed by the FIRST program from Japanese Cabinet Office, the Ministry of
+  Education, Culture, Sports, Science and Technology (MEXT), the Japan Society for the
+  Promotion of Science (JSPS),  Japan Science and Technology Agency (JST),  the Toray
+  Science  Foundation, NAOJ, Kavli IPMU, KEK, ASIAA,  and Princeton University.
 
   Funding for SDSS-III has been provided by the Alfred P. Sloan Foundation, the
-  Participating Institutions, the National Science Foundation, and the U.S.
-  Department of Energy. The SDSS-III web site is http://www.sdss3.org.  SDSS-III
-  is managed by the Astrophysical Research Consortium for the Participating
-  Institutions of the SDSS-III Collaboration including the University of
-  Arizona, the Brazilian Participation Group, Brookhaven National Laboratory,
-  University of Cambridge, University of Florida, the French Participation
-  Group, the German Participation Group, the Instituto de Astrofisica de
-  Canarias, the Michigan State/Notre Dame/JINA Participation Group, Johns
-  Hopkins University, Lawrence Berkeley National Laboratory, Max Planck
-  Institute for Astrophysics, New Mexico State University, New York University,
-  Ohio State University, Pennsylvania State University, University of
-  Portsmouth, Princeton University, the Spanish Participation Group, University
-  of Tokyo, University of Utah, Vanderbilt University, University of Virginia,
-  University of Washington, and Yale University.
+  Participating Institutions, the National Science Foundation, and the U.S.  Department of
+  Energy. The SDSS-III web site is http://www.sdss3.org.  SDSS-III is managed by the
+  Astrophysical Research Consortium for the Participating Institutions of the SDSS-III
+  Collaboration including the University of Arizona, the Brazilian Participation Group,
+  Brookhaven National Laboratory, University of Cambridge, University of Florida, the
+  French Participation Group, the German Participation Group, the Instituto de Astrofisica
+  de Canarias, the Michigan State/Notre Dame/JINA Participation Group, Johns Hopkins
+  University, Lawrence Berkeley National Laboratory, Max Planck Institute for
+  Astrophysics, New Mexico State University, New York University, Ohio State University,
+  Pennsylvania State University, University of Portsmouth, Princeton University, the
+  Spanish Participation Group, University of Tokyo, University of Utah, Vanderbilt
+  University, University of Virginia, University of Washington, and Yale University.
 
@@
 
+  This research made use of 
+  \href{http://www.astropy.org/}{Astropy}, a community-developed 
+  core Python package for Astronomy (Astropy Collaboration, 2013; 
+  \href{https://github.com/kbarbary/sep}{sep} 
+  Source Extraction and Photometry in Python \citep{PythonSEP}.
+
 %%%%%%%%%%: Bibligraphic Section %%%%%%%%%%
 
-%\begin{thebibliography}{}
-
-  %\bibitem[Arnold et al.(2011)]{2011ApJ...736L..26A} Arnold, J.~A., Romanowsky,
-    %A.~J., Brodie, J.~P., et al.\ 2011, \apjl, 736, LL26
-
-%\end{thebibliography}{}
-
-\bibliography{hsc_massive.bbl}
-\bibliographystyle{apj}
+\bibliography{redbcg}
 
@@
 
+\label{lastpage}
 \end{document}

### 2016-09-30 draft/chan_template/GamaPaper.tex
Recent update of draft and notebooks

\documentclass[apj]{emulateapj}

\newcommand{\boldsymbol}[1]{\mbox{\boldmath{${#1}$}}}

% Bibliography stuff:
\usepackage{natbib}
\usepackage[usenames]{color}
%\usepackage{fixltx2e}

%shortcuts:
\newcommand{\bd}{\begin{displaymath}}
\newcommand{\ed}{\end{displaymath}}
\newcommand{\be}{\begin{equation}}
\newcommand{\ee}{\end{equation}}
\newcommand{\beaa}{\begin{eqnarray*}}
\newcommand{\eeaa}{\end{eqnarray*}}
\newcommand{\bea}{\begin{eqnarray}}
\newcommand{\eea}{\end{eqnarray}}

% Notation definitions - need math environment!:
% ==============================================

\newcommand\anguita{COSMOS\,5921$+$0638}

\def\hst{\textit{HST}}

\def\zl{z_{\rm l}}
\def\zs{z_{\rm s}}

\def\kms {\rm km\,s^{-1}}
\def\kmsMpc {\rm km\,s^{-1}\,Mpc^{-1}}

\def\rein{r_{\rm ein}}

\def\zmag{m_{\rm z}}
\def\chitah{{\sc Chitah}}

% References:
\newcommand{\sref}[1]{Section~\ref{#1}}
\newcommand{\fref}[1]{Figure~\ref{#1}}
\newcommand{\fsref}[1]{Figures~\ref{#1}}
\newcommand{\tref}[1]{Table~\ref{#1}}
\newcommand{\eref}[1]{Equation~(\ref{#1})}

% General editing:
\newcommand{\degt}{\mathrm{deg}}
\newcommand{\arcmint}{\mathrm{arcmin}}
\newcommand{\arcsect}{\mathrm{arcsec}}
\def\eg{{e.g.,}}
\def\ie{{i.e.,}}
%

% Commenting:
\newcommand{\todo}[2]{\textcolor{red}{\textbf{TODO (#1): #2}}}
\newcommand{\comment}[2]{\textcolor{cyan}{\textbf{[Comment (#1): #2]}}}
\newcommand{\sherry}[1]{\textcolor{cyan}{\textbf{[Comment (Sherry): #1]}}}
% ------------------------------------------------------------------------------

\begin{document}

\title{Galaxy-scale gravitational lens candidates from the Hyper Suprime-Cam imaging survey and the Galaxy And Mass Assembly spectroscopic survey}

\author{
James H.~H.~Chan\altaffilmark{1,2},
Sherry H.~Suyu\altaffilmark{3,2},
Anupreeta More\altaffilmark{4},
Masamune Oguri\altaffilmark{5,6,7},
Tzihong Chiueh\altaffilmark{1,8,9},
Jean Coupon\altaffilmark{10},
Bau-Ching~Hsieh\altaffilmark{2},
Yutaka Komiyama\altaffilmark{11,12},
Satoshi Miyazaki\altaffilmark{11,12},
Hitoshi Murayama\altaffilmark{5,11,12},
Atsushi J.~Nishizawa\altaffilmark{15},
Paul Price\altaffilmark{16},
Philip J.~Tait\altaffilmark{17},
Tsuyoshi Terai\altaffilmark{17},
Yousuke Utsumi\altaffilmark{18},
Shiang-Yu Wang\altaffilmark{2}
}
%
\altaffiltext{1}{Department of Physics, National Taiwan University, Taipei 10617, Taiwan}
\altaffiltext{2}{Institute of Astronomy and Astrophysics, Academia Sinica, P.O.~Box 23-141, Taipei 10617, Taiwan}
\altaffiltext{3}{Max-Planck-Institut f{\"u}r Astrophysik, Karl-Schwarzschild-Str. 1, 85741 Garching, Germany}
\altaffiltext{4}{Kavli IPMU (WPI), UTIAS, The University of Tokyo, Kashiwa, Chiba 277-8583, Japan }
\altaffiltext{5}{Kavli Institute for the Physics and Mathematics of the Universe (Kavli IPMU, WPI), University of Tokyo, 5-1-5 Kashi- wanoha, Kashiwa-shi, Chiba 277-8583, Japan}
\altaffiltext{6}{Research Center for the Early Universe, University of Tokyo, 7-3-1 Hongo, Bunkyo-ku, Tokyo 113-0033, Japan}
\altaffiltext{7}{Department of Physics, University of Tokyo, 7-3-1 Hongo, Bunkyo-ku, Tokyo 113-0033, Japan}
\altaffiltext{8}{Institute of Astrophysics, National Taiwan University, 10617 Taipei, Taiwan}
\altaffiltext{9}{Center for Theoretical Sciences, National Taiwan University, 10617 Taipei, Taiwan}
\altaffiltext{10}{Astronomical Observatory of the University of Geneva, ch. d'Ecogia 16, CH-1290 Versoix, Switzerland}

\altaffiltext{11}{University of California, Berkeley, CA 94720, USA}
\altaffiltext{12}{Lawrence Berkeley National Laboratory, MS 50A-5104, Berkeley, CA 94720. USA}

\altaffiltext{13}{National Astronomical Observatory of Japan, 2-21-1 Osawa, Mitaka, Tokyo 181-8588, Japan}
\altaffiltext{14}{Department of Astronomy, School of Science, SOKENDAI (The Graduate University for Advanced Studies), Mitaka, Tokyo 181-8588}
\altaffiltext{15}{Institute for Advanced Research, Nagoya University, Furocho Chikusa Nagoya Aichi 4648602, Japan}
\altaffiltext{16}{Princeton University Observatory, Peyton Hall, Princeton, NJ 08544, USA}
\altaffiltext{17}{National Astronomical Observatory of Japan, 650 North A'ohoku Place, Hilo, HI 96720, USA}
\altaffiltext{18}{Hiroshima Astrophysical Science Center, Hiroshima University, 1-3-1 Kagamiyama, Higashi-Hiroshima, Hiroshima 739-8526, Japan}

\email{d00222002@ntu.edu.tw}
\shorttitle{New lenses from HSC survey}
\shortauthors{Chan, Suyu, More et al.}

%-------------------------------------------------------------------------------

\begin{abstract}

We present a list of galaxy-scale lens candidates including a highly probable interacting galaxy-scale lens 
in the Hyper Suprime-Cam (HSC) imaging survey. 
We combine HSC imaging with the blended-spectra catalog from the Galaxy And Mass Assembly (GAMA) survey to identify lens candidates, 
and use lens mass modeling to confirm the candidates.
We find 46 matches between the HSC S14A\_0b imaging data release and the GAMA catalog.
Ten of them are probable lens systems according to their morphology and redshifts.
There is one system with an interacting galaxy pair, HSC J084928+000949, that has a valid mass model.
We predict the total mass enclosed by the Einstein radius of $\sim0.72$\arcsec ($\sim1.65$\,kpc) for this new expected lens system to be $\sim10^{10.59}\,M_{\odot}$.
Using the photometry in the {\it grizy} bands of the HSC survey and stellar population synthesis modeling with a Salpeter stellar initial mass function, 
we estimate the stellar mass within the Einstein radius to be $\sim10^{10.46}\,M_{\odot}$. 
We thus find a dark matter mass fraction within the Einstein radius of $\sim25\%$.
Further spectroscopy or high-resolution imaging would allow confirmation of the nature of these lens candidates.
The particular system with the interacting galaxy pair, if confirmed, would provide an opportunity to study the interplay between dark matter and stars as galaxies build up through hierarchical mergers.

\end{abstract}

\keywords{}

%-------------------------------------------------------------------------------

\section{Introduction} 
\label{sec:intro}

Strong gravitational lensing is a powerful tool for measuring the mass distribution from galaxies to galaxy clusters.
Understanding the interplay between dark matter and baryons at galactic/sub-galactic scales is crucial to study the formation and evolution of galaxies.
Moreover, the signal from background source objects is magnified so we can make use of this information to probe the high-redshift universe.

Strong lens systems are rare, however. A lensing phenomenon happens 
when a massive foreground deflector is sufficiently well aligned along the line of sight to background source galaxies.
Searches for strongly lensed galaxies have been carried out extensively in large imaging and spectroscopic surveys, including 
the Sloan Lens ACS Survey \citep[SLACS; \eg][]{BoltonEtal06SLACS}, 
the CFHTLS\footnote{Canada-France-Hawaii Telescope Legacy Survey.  See http://www.cfht.hawaii.edu/Science/CFHLS/ and links therein for a comprehensive description.} 
Strong Lensing Legacy Survey \citep[SL2S; \eg][]{CabanacEtal07, GavazziEtal12,MoreEtal12, SonnenfeldEtal13a,SonnenfeldEtal13b},
the BOSS Emission-line Lens Survey \cite[BELLS; \eg][]{BrownsteinEtal12,BoltonEtal12a},
the \hst\ Archive Galaxy-scale Gravitational Lens Search \citep[HAGGLeS;][]{MarshallEtal09}, 
\textit{Herschel} ATLAS \citep[H-ATLAS; \eg][]{NegrelloEtal10,GonzalezNuevoEtal12}, and the South Pole Telescope \citep[SPT; \eg][]{VieiraEtal13,HezavehEtal13}. 
Through these galaxy-galaxy strong lens surveys, there are now a couple of hundreds of strong lenses with different source populations.

In this work, we identify strong lens candidates from the Galaxy And Mass Assembly (GAMA) blended spectra catalog \citep{HolwerdaEtal15} 
and visually inspect their Hyper Suprime-Cam (HSC) images to prune the candidates further. 
With high image quality in the HSC survey, we can discern foreground lens and background source with \chitah\ \citep{ChanEtal15} using color information, 
and further reconstruct the lens mass distribution and lensed source surface brightness  
with the lens modeling software GLEE  \citep{Suyu&Halkola10, SuyuEtal12}. 
Our philosophy is to use lens modeling to confirm lens candidates (as advocated by, \eg\ \citeauthor{MarshallEtal09} \citeyear{MarshallEtal09}), 
since a lens system must be explainable by a physical lens mass model. 
Through lens mass modeling, we report ten probable lens candidates, and one of them is a highly probable interacting galaxy-scale lens system.

This paper is organized as follows. 
In \sref{sec:observation} we overview the observational data with spectroscopy and imaging. 
The procedure of lens examination is described in \sref{sec:method}. 
We list probable lens candidates in \sref{sec:candidates}.
In \sref{sec:summary}, conclusions are drawn and future prospect is discussed.

%-------------------------------------------------------------------------------

\section{Observation}
\label{sec:observation}

We summarize the spectroscopic and imaging observations 
of the new lens candidates in GAMA and HSC surveys in \sref{subsec:catalog} and \sref{subsec:imaging} respectively.

\subsection{GAMA blended spectra catalog}
\label{subsec:catalog}
The GAMA survey has spectroscopic redshifts of ~300,000 galaxies down to $r<19.8$ mag over ~286 deg$^2$ 
with the upgraded 2dF spectrograph AAOmega on the Anglo-Australian Telescope 
\citep{DriverEtal09,DriverEtal11,BaldryEtal10}. 
The fiber size is 2\arcsec\ in diameter projected on the sky 
\citep{HopkinsEtal13}.
In the GAMA survey pipeline, \citet{BaldryEtal14} developed a fully automatic algorithm, AUTOZ, 
which measures redshift using a cross-correlation method for both absorption-line and emission-line features.

An object with blended spectra is likely to be a lens candidate. 
\citet{HolwerdaEtal15} have classified the blended spectra by the best-fit passive/emission-line templates
and have listed 280 objects whose features 
of blended spectra are separated by at least 600 km/s.
They visually inspected the images of candidates in the Sloan Digital Sky Survey (SDSS) and Kilo Degreee Survey (KiDS) and obtained 
104 lens candidates and 176 occulting galaxy pairs. 
The catalog provides useful information for us to further classify some of the lens candidates based on the HSC imaging survey with better image quality.

%-------------------------------------------------------------------------------
\subsection{HSC imaging}
\label{subsec:imaging}

HSC is the new prime-focus camera
on the 8.2-m Subaru telescope located at Mauna Kea, Hawaii. 
The field of view (FOV) is 1.5 deg in diameter \citep{MiyazakiEtal12} which is ten times larger than the FOV of Suprime-Cam \citep{MiyazakiEtal02}. 
The HSC Subaru Strategic Program (SSP) survey consists of three layers with different depths: wide, deep and ultra-deep. 
The wide survey will cover $\sim1400$ deg$^2$ to $r\sim26$ mag in {\it grizy} broad bands.
We identify and model candidates in the internal early data release S14A\_0b (XMM, GAMA09h, VVDS) 
of the HSC imaging survey.

The data are processed with hscPipe 3.4.1, a derivative of the 
the Large Synoptic Survey Telescope (LSST) pipeline \citep{IvezicEtal08,AxelrodEtal10}, modified for use with Suprime-Cam and Hyper Suprime-Cam.
The photometric calibration is based on data obtained from the Panoramic Survey Telescope and Rapid Response System (Pan-STARRS) 1 imaging survey \citep{SchlaflyEtal12,TonryEtal12,MagnierEtal13}.
We use HSC SSP 
data release S15A reduced with hscPipe 3.8.5, which was released near the final stages of our analysis, to update our lens models of the 
candidates identified in S14A\_0b. 
The pixel scale of the reduced images in the data releases is 0.168\arcsec.

%-------------------------------------------------------------------------------
\section{Method}
\label{sec:method}

\begin{figure*}
\centering
\includegraphics[scale=0.7]{figure/new_lens.eps}
\caption{
The highly probable lens system from HSC survey: HSC J084928+000949. 
The {\it riz} composite cutout in $25\arcsec \times 25\arcsec$ shows clearly the interacting feature in panel (a). 
Panel (b) is the central $5\arcsec \times 5\arcsec$ region of the {\it riz} composite.
\chitah\ separates the light components in panel (b) into the lens light (panel (c)) and lensed arcs of the background source (panel (d)) using color information.
The GAMA spectroscopic redshifts are $(z_1, z_2) = (0.128^{\rm P},0.603^{\rm E})$,  where P and E stand for ``Passive galaxy'' and ``Emission-line galaxies'', respectively.
}
\label{fig:new_lens}
\end{figure*}

To further confirm the lens candidates in the GAMA blended spectra catalog, we visually select objects based on their morphology and redshift information.
Moreover, we try to reconstruct background sources via lens modeling.
If a candidate is a lens system, its reconstructed source components should be well described by regular looking galaxies.
In other words, we can confirm a system to be a lens if we can find a physically sensible model 
for the foreground lens mass distribution and the background source surface brightness.

\subsection{Selection via morphology and redshift information}
\label{subsec:selection}

We start with the 280 objects from the GAMA blended spectra catalog, and find 46 of these are in the footprint of the HSC early data release S14A\_0b.
We employ \chitah\ \citep{ChanEtal15} to disentangle lens and lensed-source components based on color information.
\chitah\ combines two image cutouts, one from the bluer bands ({\it g} or {\it r}) and one from the redder bands ({\it z} or {\it y}), to produce a ``foreground lens image'' and a ``lensed arc image of the background source''. 
\chitah\ chooses the band with a narrower PSF from the two bluer bands, and similarly from the two redder bands.
By selecting the cutouts with narrower PSFs, \chitah\ produces the sharpest possible images of the lens and lensed arcs.
We show in \fref{fig:new_lens}(c) and (d) an example of the lens light and lensed arc separation, respectively.

Furthermore, \citet{HolwerdaEtal15} also provided two galaxies' redshifts of each lens candidate 
which allow us to predict image separations, $\vartheta_{\rm sep}$, with a fiducial velocity dispersion of $\sigma\sim250$km/s, 
\be
  \vartheta_{\rm sep} = 8 \pi {\sigma^2 D_{\rm LS} \over c^2 D_{\rm S}},
\ee
where $D_{\rm LS}$ is the angular diameter distance between the lens and the source and $D_{\rm S}$ is the angular distance between us and the source. 
Those lens candidates with lens/source redshift values that are too close are excluded 
since the image separations are too small ($\vartheta_{\rm sep} < 1.0\arcsec$) and difficult to resolve in the HSC images. 
We also empirically rule out the candidates that have no lensed arc features 
and only 10 candidates remain.
In other words, when the lensed-arc feature can be seen such as that shown in \fref{fig:new_lens}(d), 
we then try to model the lens mass distribution and source surface brightness of the system.

\subsection{Lens model}
\label{subsec:model}

To confirm the lensing nature of the 10 probable candidates, we use the lens modeling software GLEE, developed by A.~Halkola and S.~H.~Suyu \citep{Suyu&Halkola10, SuyuEtal12},
to fit the lens light and lensed-source components. 
Lens light components show stellar distributions of lens galaxies, which can be well described by S{\'e}rsic profiles \citep{Sersic63}:
\be
\label{eq:sersic}
I(\theta_1,\theta_2) = A \exp \left[ -k \left (\left(\frac{\sqrt{\theta_1^2 +
      \theta_2^2/q_{\rm L}^2}}{R_{\rm eff}}\right) ^ {1/n_{\rm
    s}} - 1 \right) \right],
\ee
where $(\theta_1,\theta_2)$ are image coordinates, $A$ is the amplitude, $k$ is a constant such that $R_{\rm eff}$ is the effective (half-light) radius, $q_{\rm L}$ is the axis ratio, and $n_{\rm s}$ is the S{\'e}rsic index.  To fit to the lens light image from \chitah, we have as additional parameters the centroid $(\theta_{\rm 1c},\theta_{\rm 2c})$ and the position angle of the S{\'e}rsic distribution.
%
For the lens galaxy's dimensionless surface mass density (the total mass distribution, including baryons and dark matter), 
we adopt pseudo-isothermal elliptic mass distribution \citep[PIEMD;][]{Kassiola&Kovner93} with a vanishing core:
\be
\label{eq:piemd}
\kappa(\theta_1, \theta_2) = \frac{\rein}{2\sqrt{\frac{{\theta_1^2}}{(1+\epsilon)^2}+\frac{\theta_2^2}{(1-\epsilon)^2}}},
\ee
$\rein$ is the Einstein radius of the lens (that is related to the strength of the lens) and $\epsilon$ is the ellipticity that is related to the axis ratio $q$ by $\epsilon \equiv (1-q)/(1+q)$.  
%

We first model the lens light produced in the color-difference image as shown in \fref{fig:new_lens}(c) to obtain the S{\'e}rsic parameters, particularly the centroid and position angle. 
We then model the lensed arcs to constrain simultaneously the source surface brightness on a grid of pixels and the lens mass parameters of PIEMD.  
We adopt the curvature form of regularization on the source grid, 
and Gaussian priors on the centroid ($\sim$0.05\arcsec), the axis ratio ($\sim$0.1), and the  position angle ($\sim$3 deg) of the PIEMD based on the fitted S{\'e}rsic parameters.  
We allow the Einstein radius to vary with uniform prior.
We use GLEE to confirm the lensing nature for those systems that have sensible source surface brightness and lens mass model parameters, as detailed next.

\section{Gravitational lens candidates from HSC survey}
\label{sec:candidates}
There are ten candidates that show lensed features.
We cannot obtain reasonable lens models with GLEE for nine of them, due to e.g.~$\rein$ that are too small/large or inverted sources that appear unphysical as a result of the limited number of image pixels.
We list these nine lens candidates in \sref{subsec:all_cand}.
We consider one candidate that is highly probable since we can obtain a sensible lens model with GLEE and discuss it in \sref{subsec:newlens}.

\subsection{Lens candidates}   
\label{subsec:all_cand}

The lens candidates are listed in \fref{fig:candidates} and \tref{tab:list} for future confirmation. 
We identify a probable binary lens system in J023143$-$045313.
J084552$+$011156 and J084406$+$013853 are likely disky lenses.
Some of the candidates are low-redshift lenses, such as J084202$+$010115, J085005$+$021740 and J085029$+$001533.
These candidates are worth inspecting with higher-resolution 
imaging, 
as they complement nicely the existing samples of lenses at higher redshifts, \eg\ SLACS, SL2S and BELLS.

\begin{figure*}
\centering
\includegraphics[scale=1.0]{figure/candidates.eps}
\caption{The nine probable lens candidates from the combination of GAMA spectroscopy and HSC SSP imaging.
For each candidate, we show on the left a 25\arcsec$\times$25\arcsec cutout and on the right a 5\arcsec$\times$5\arcsec cutout of the {\it riz} color image.
The spectral types of each candidate is denoted after the redshifts, where ``P'' stands for ``passive galaxies'' and ``E'' stands for ``emission-line galaxies''. 
J023143$-$045313 is a probable binary lens system. 
J084552$+$011156 and J084406$+$013853 are likely disky lenses.
Some of them are low-redshift lenses, such as J084202$+$010115, J085005$+$021740 and J085029$+$001533. 
}
\label{fig:candidates}
\end{figure*}

\begin{table}
\caption{The catalog of lens candidates selected from GAMA in the HSC survey} 
\label{tab:list}
\begin{center}
\begin{tabular}{lccc}
\hline
 HSC id & RA & DEC & ($z_1,z_2$) \\ \hline
HSC J084928$+$000949\textsuperscript{\dag} & 132.36771 &   $\phantom{-}0.16360$&  ($0.128^{\rm P}$, $0.603^{\rm E}$) \\
HSC J021535$-$063305     &$ 33.89513$ & $-6.55139$&  ($0.217^{\rm P}$, $0.749^{\rm E}$) \\
HSC J022511$-$045033     &$ 36.29463$ & $-4.84248$&  ($0.309^{\rm E}$, $0.460^{\rm E}$) \\
HSC J023143$-$045313     &$ 37.92875$ & $-4.88681$&  ($0.189^{\rm P}$, $0.716^{\rm E}$) \\
HSC J084552$+$011156     &$131.46746$ & $\phantom{-} 1.19884$&  ($0.146^{\rm P}$, $0.716^{\rm P}$) \\
HSC J084406$+$013853     &$131.02333$ & $\phantom{-} 1.64814$&  ($0.164^{\rm P}$, $0.229^{\rm E}$) \\
HSC J084202$+$010115     &$130.50925$ & $\phantom{-} 1.02071$&  ($0.077^{\rm P}$, $0.699^{\rm E}$) \\
HSC J083805$+$012325     &$129.51933$ & $\phantom{-} 1.39028$&  ($0.240^{\rm E}$, $0.419^{\rm E}$) \\
HSC J085005$+$021740     &$132.51888$ & $\phantom{-} 2.29438$&  ($0.108^{\rm P}$, $0.457^{\rm E}$) \\
HSC J085029$+$001533     &$132.62096$ & $\phantom{-} 0.25907$&  ($0.200^{\rm E}$, $0.054^{\rm P}$) \\ 
\hline
\end{tabular}
\end{center}
\dag The highly probable lens system via lens modeling.
The Einstein radius is $\rein\sim0.72\arcsec$. 
The total mass within the Einstein radius is $M_{\rm tot} \sim 10^{10.59} M_{\odot}$. 
The stellar mass is $M_* \sim 10^{10.46} M_{\odot}$ including dust extinction. 
\end{table}

\subsection{A promising interacting-galaxy lens candidate from HSC survey}
\label{subsec:newlens}

\begin{figure*}
\centering
\includegraphics[angle=0,scale=0.7]{figure/spectrum.eps}
\caption{
Blended spectra of HSC J084928+000949 (black line). Red and magenta dashed lines show the emission and absorption lines at $z_1 = 0.128$ respectively. 
Blue and cyan dot-dashed lines show the emission and absorption lines at $z_2 = 0.603$ respectively.}
\label{fig:spec}
\end{figure*}

In this work, we identify one very promising lens candidate, HSC J084928+000949, from HSC survey via lens modeling.
The result is shown in \fref{fig:new_lens}.
\chitah\ separates lens light and lensed arcs using {\it g}-band cutout instead of {\it r}-band cutout which has bad pixels,
even though the {\it r}-band PSF is narrower than that of the {\it g}-band.
The coordinate is (RA, DEC) = (132.36771, 0.16360). 
We also notice that this candidate is an interacting galaxy-pair which is an important aspect of galaxy evolution \citep[\eg][]{HopkinsEtal06,LotzEtal08}.
Gravitational lensing provides an independent constraint on dark matter distribution. 
Hence, it can help us to study the interplay between dark matter and baryonic components \citep[\eg][]{BarnabeEtal11,SonnenfeldEtal15}.

We also check the GAMA spectra shown in \fref{fig:spec} \citep{LiskeEtal15} to verify that it is blended of two galaxies at different redshifts.
The two galaxy types are emission line galaxy ($z_2\sim0.603$) and passive galaxy ($z_1\sim0.128$) \citep{HolwerdaEtal15}. 
We indicate the emission and absorption lines at $z_1 = 0.128$ as red and magenta dashed lines, respectively, 
and the the emission and absorption lines at $z_2 = 0.603$ as blue and cyan dot-dashed lines, respectively.  
We also note that this probable lens galaxy appears to be merging with another one in \fref{fig:new_lens}(a).

\begin{figure}
\centering
\includegraphics[scale=0.4]{figure/lens_model.eps}
\caption{The result from lens modeling of the highly probable lens HSC J084928+000949. We model the lensed-arc feature in the masked region 
shown in the top-left panel. 
The predicted lensed-arc of the best-fitting model is shown in the top-right panel. The normalized image residuals are shown in the bottom-left panel.
We can see clearly a compact source galaxy in the bottom-right panel. 
The critical line (blue) and the caustics (red) predicted by our lens model are drawn in the top-right and bottom-right panels, respectively. 
} 
\label{fig:lens_model}
\end{figure}

The result from GLEE is shown in \fref{fig:lens_model}. 
We model the lensed-arc feature in the masked region shown in the top-left panel. 
The predicted lensed arc of the best fitting model is shown in the top-right panel and the normalized image residuals are shown in the bottom-left panel.
We can clearly see a single source in the bottom-right panel based on the lens model with 
$\rein = 0\arcsec.72\pm^{0.04}_{0.02}$.
The critical line (blue) and the caustics (red) predicted by our lens model are drawn in the top-right and bottom-right panels, respectively. 
%
Even though we have a sensible lens mass model of J084928+000949, we classify this object as a highly probably lens system rather than a definite lens. 
Spectroscopically there are two sources at distinct redshifts. 
However, since the GAMA spectroscopy does not have sufficient spatial resolution and the foreground lens galaxy also shows emission lines,  
it is not fully clear whether the background source has multiply lensed images. 
For the purpose of lens modeling, we have decided to use certain bluish features as lensed images of the background source, 
but high-resolution imaging or spatially resolved spectroscopy is needed to unambiguously confirm this potential lens system.

Based on our current best-fit model of J084928$+$000949, we compute the total mass within the Einstein radius through
$M_{\rm tot}(<\rein)= \pi (D_{\rm L}\rein)^2 \Sigma_{\rm cr}$,
where $D_{\rm L}$ is the angular distance between us and the lens, and $\Sigma_{\rm cr} = c^2 D_{\rm L}/4\pi G D_{\rm LS}D_{\rm S}$ is the critical surface mass density. 
The total mass for this highly probable lens system is $\log(M_{\rm tot}(<\rein)/M_\odot)=10.59\pm^{0.05}_{0.02}$.
We estimate the magnitudes in all {\it grizy} bands of the lens galaxy within a circular aperture of radius $\rein$:  
$m_g=20.66\pm0.02$, $m_r=19.53\pm0.02$, $m_i=18.98\pm0.02$, $m_z=18.57\pm0.03$, and $m_y=18.47\pm0.02$.  
With the same method in \cite{OguriEtal14} using \cite{Bruzual&Charlot03} stellar population synthesis model,
we calculate the stellar mass 
$\log(M_*/M_\odot)=10.46\pm0.08$
including additional parameter on dust extinction at the galaxy
redshift. The value is derived using Salpeter initial mass funcion
(IMF). We note that we obtain similar stellar mass of
$\log(M_*/M_\odot)=10.50\pm0.08$
even if we do not include the dust extinction. 
From this analysis we can infer the dark matter fraction within the Einstein radius to be $\sim 25\%$, which is comparable to those
in SLACS and SL2S 
\citep{BarnabeEtal11,AugerEtal10,SonnenfeldEtal15}.

\section{Summary and Discussions}
\label{sec:summary}

Using the GAMA blended spectra catalog, we find 46 matches in HSC early data release S14A\_0b.
We use \chitah\ to separate lens light and lensed arc components. 
We identified 10 lens candidates via redshift information and morphology.
To further confirm these lens candidates, we use GLEE to model the lensed arc components.
After our examinations of the modeling results, we draw the following conclusions:

\begin{enumerate}
  \item  We identify 10 lens candidates via redshift information and morphology. 
  \item  Through lens model fitting and examining the spectrum, we consider one system, HSC J084928+000949, as a highly probable lens. The Einstein radius $\rein$ is around 0.72\arcsec.
  \item  The highly probable lens is an interacting system which allows us to study the interplay between dark matter and stars.
  \item  For the highly probable lens, the dark matter fraction within $\rein$ is $\sim 25\%$.
\end{enumerate}

After the first successful identification of a list of lens candidates including one highly probable lens system, we expect to 
confirm more strongly lensed galaxies in future data releases. 
Higher-resolution imaging (via, \eg\ adaptive optics), or spatially resolved spectroscopy would be helpful to confirm further the nature of these candidates.
The new interacting lens candidate is very valuable and with follow-up observation it would provide a great opportunity to study 
the interplay between dark matter and also the hierarchical formation/evolution of galaxies.

%-------------------------------------------------------------------------------

\section*{Acknowledgments}

We thank Ying-Tung Chen and Li-Hwai Lin for useful discussions.
J.H.H.C.~would like to thank Chih-Fan Chen and Kenneth Wong for algorithm support.
J.H.H.C.~and S.H.S.~gratefully acknowledge support by the Ministry of Science and Technology in Taiwan via grant MOST-103-2112-M-001-003-MY3, and support by the Max Planck Society through the Max Planck Research Group for S.H.S.
T.C.~acknowledges the Ministry of Science and Technology in Taiwan via grant MOST-103-2112-M-002-020-MY3.
%  
A.M.~is supported by World Premier International Research Center Initiative (WPIInitiative), MEXT, Japan, 
and also acknowledges the support of the Japan Society for Promotion of Science (JSPS) fellowship.
%
M.O.~acknowledges support in part by World Premier International
Research Center Initiative (WPI Initiative), MEXT, Japan, and
Grant-in-Aid for Scientific Research from the JSPS (26800093).
%
The Hyper Suprime-Cam (HSC) collaboration includes the astronomical
communities of Japan and Taiwan, and Princeton University.  The HSC
instrumentation was built by the National Astronomical Observatory of
Japan (NAOJ), the Kavli Institute for the Physics and Mathematics of
the Universe (Kavli IPMU), the University of Tokyo, the High Energy
Accelerator Research Organization (KEK), and the Academia Sinica
Institute for Astronomy and Astrophysics in Taiwan (ASIAA).  Funding
was contributed by the Ministry of Education, Culture, Sports, Science
and Technology (MEXT), the Japan Society for the Promotion of Science
(JSPS), NAOJ, Kavli IPMU, KEK, ASIAA, and Princeton University.
%
This paper makes use of software developed for the Large Synoptic Survey Telescope. We thank the LSST Project for making their code available as free software at http://dm.lsstcorp.org.
The Pan-STARRS1 Surveys (PS1) have been made possible through contributions of the Institute for Astronomy, the University of Hawaii, the Pan-STARRS Project Office, the Max-Planck Society and its participating institutes, the Max Planck Institute for Astronomy, Heidelberg and the Max Planck Institute for Extraterrestrial Physics, Garching, The Johns Hopkins University, Durham University, the University of Edinburgh, Queen's University Belfast, the Harvard-Smithsonian Center for Astrophysics, the Las Cumbres Observatory Global Telescope Network Incorporated, the National Central University of Taiwan, the Space Telescope Science Institute, the National Aeronautics and Space Administration under Grant No. NNX08AR22G issued through the Planetary Science Division of the NASA Science Mission Directorate, the National Science Foundation under Grant No. AST-1238877, the University of Maryland, and Eotvos Lorand University (ELTE).
%

%-------------------------------------------------------------------------------
% bibliography:

\bibliography{GamaPaper.bib}
\bibliographystyle{apj}

%-------------------------------------------------------------------------------

\label{lastpage}
\end{document}

%===============================================================================

### 2016-09-30 draft/draft_v0.tex
Recent update of draft and notebooks

@@
 \def\sb{mag~arcsec$^{-2}$}
-\def\solum{$L_\odot$}
-\def\solmass{$M_\odot$}
+\def\lsun{$L_\odot$}
+\def\msun{$M_\odot$}
 \def\sigs{$\sigma_*$}
@@
 \def\ser{{S\'{e}rsic\ }}
-\def\redm{\texttt{redMaPPer}~}
-\def\redbcg{$\Lambda \ge 30$}
-\def\nonbcg{$\Lambda < 30$}
-\def\logms{$\log (M_{\star}/M_{\odot})$}
-\def\logmh{$\log (M_{\mathrm{Halo}}/M_{\odot})$}
+\def\redm{\texttt{redMaPPer}}
+\def\redbcg{{$\Lambda \ge 30$}}
+\def\nonbcg{{$\Lambda < 20$}}
+\def\logms{{$\log (M_{\star}/M_{\odot})$}~}
+\def\mstar{{$M_{\star}$}~}
+\def\logmh{{$\log (M_{\mathrm{Halo}}/M_{\odot})$}~}
+\def\m2l{{$M_{\star}/L_{\star}$}~}
 
@@
         \item \plan{Explain why we should care about the environment, and why we expect to 
-            see some environemtnal dependence in the structure and other properties of
+            see some environmental dependence in the structure and other properties of
             massive galaxies.}
@@
 
-    \plan{Basica idea of this work}
+    \plan{Basic idea of this work}
     \begin{itemize}
@@
 
-    All the magnitudes used here are in AB system (\addref), and are corrected 
+    All the magnitudes used here are in AB system (\citealt{Oke1983}), and are corrected 
     for Galactic extinction using calibrations from \citet{Schlafly11}.
@@
     The Subaru Strategic Program (SSP, \addref) makes use of the new prime-focus camera,
-    the Hyper Suprime-Cam (HSC;~\addref: Miyazaki\etal 2012), on the 8.2-m Subaru
+    the Hyper Suprime-Cam (HSC;~\citealt{Miyazaki2012}), on the 8.2-m Subaru
     telescope at Mauna Kea.  
@@
     The regions covered by this release are overlapped with several previous spectroscopic
-    survey (e.g. SDSS/BOSS \addref; GAMA \addref).
+    survey (e.g. SDSS/BOSS: \citealt{Eisenstein2011}, \citealt{Alam2015}; 
+    GAMA: \citealt{Driver2011}, \citealt{Liske2015}).
 
     The data are processed with \texttt{hscPipe 4.0.1}, a derivative of the Large Synoptic
-    Survey Telescope (LSST) pipeline (\addref: Ivezic\etal~2008, Axelrod\etal 2010),
+    Survey Telescope (LSST) pipeline (e.g. \citealt{Ivezic2008}; \citealt{Axelrod2010}),
     modified for use with Suprime-Cam and Hyper Suprime-Cam.  
@@
     and photometric calibration.  
-    The pixel scale of the combined images is 0.168$\arcsec$.  The photometric calibration
-    is based on data obtained from the Panoramic Survey Telescope and Rapid Response
-    System (Pan-STARRS) 1 imaging survey (\addref: Schlafly\etal 2012, Tonry\etal 2012,
-    Magnier\etal 2013). 
+    The pixel scale of the combined images is $0.168^{\arcsec}$.  
+    The photometric calibration is based on data obtained from the Panoramic Survey 
+    Telescope and Rapid Response System (Pan-STARRS) 1 imaging survey 
+    (\citealt{Schlafly2012}, \citealt{Tonry2012}, \citealt{Magnier2013}). 
     To achieve consistent deblending and photometry across all bands, the \texttt{hscPipe}
@@
     Details of \texttt{hscPipe} and the multi-band processing method will be presented in
-    \addref (Bosch\etal 2017?).
+    \addref~(Bosch\etal~in prep.).
 
@@
     Motivated by the requirement of weak lensing analysis, the $i$-band data typically has
-    the best seeing in all five bands (the median seeing is around FWHM$\sim 0.8\arcsec$).
+    the best seeing in all five bands (the median seeing is around 
+    FWHM$\sim 0.8^{\arcsec}$).
     Therefore, we will mostly use the $i$-band images to study the structure of galaxies.
@@
     To achieve this goal, we will select \logms$ > 11.5$ massive central galaxies within
-    host halo mass larger and smaller than \logmh$= 14.0$ at $0.2 < z < 0.5$.  
+    host halo mass larger and smaller than \logmh$= 14.0$ at $0.3 < z < 0.5$.  
     As both $M_{\star}$-$M_{\mathrm{Halo}}$ relation and stellar mass function are still
@@
     And, this stellar mass cut can greatly reduce the contamination of satellites (e.g.
-    \addref: van~Uitert\etal 2016).  
-    Meanwhile, under the adopted cosmology, $1\arcsec$ equals 3.3 and 6.1 kpc at redshit
-    0.2 and 0.5.  
-    Hence, our redshift bin enables us to reliable measure the total stellar mass within
-    the inner 5 to 10 kpc (where the ``in-situ'' component should still dominates) of
-    massive galaxies at the high redshift end assuming the typical seeing of data. 
+    \citealt{vanUitert2016}).  
+    Meanwhile, under the adopted cosmology, $1.0^{\arcsec}$ equals 4.4 and 6.1 kpc at 
+    redshit 0.3 and 0.5.  
+    Therefore, this redshift range enables us to reliable measure the total stellar mass 
+    within the inner 5 to 10 kpc (where the ``in-situ'' component should still dominates) 
+    of massive galaxies at the high redshift end assuming the typical seeing of HSC data. 
     At the same time, the depth of the data still allows to study the very outskirt ($\sim
-    100$ kpc) of these galaxies at $z\sim 0.5$.  Also, such limits on mass and redshift
-    ensure us a sizable sample while let us safely ignore any significant structural
-    evolution (no star formation, lower merger rate \etal e.g. \addref).
+    100$ kpc) of these galaxies at $z\sim 0.5$.  
+    Also, such limits on mass and redshift ensure us a sizeable sample while let us 
+    safely ignore significant mass growth and structural evolution 
+    (no star formation, lower merger rate \etal~e.g.
+    \citealt{Bellstedt2016}, \citealt{Inagaki2015}; but also see \citealt{Bai2014}; 
+    more discussion about this in Section~5).
 
-    Based on recent constraints of $M_{\star}$-$M_{\mathrm{Halo}}$ relation (e.g.
-    \addref), above \logms$ = 11.5$, there is a large scatter of halo mass at fixed
-    stellar mass.  
+    Based on recent constraints of $M_{\star}$-$M_{\mathrm{Halo}}$ relation 
+    (e.g. \citealt{Leauthaud2012}, \citealt{Behroozi2013}, \citealt{Kravtsov2014}), 
+    above \logms$ = 11.5$, there is a large scatter of halo mass at fixed stellar mass.  
     At \logmh$<14.0$, these massive galaxies are mostly the centrals of small groups;
@@
     galaxy clusters.   
-    Limited by the sample size and the capability of measureing halo mass for individual
+    Limited by the sample size and the capability of measuring halo mass for individual
     central galaxy, we will simply separate the sample into two broad halo mass bins with
-    the help of the \redm cluster catalog\footnote{See:
-    http://risa.stanford.edu/redmapper/} ( \texttt{v5.10}, e.g. \addref: Rykoff\etal 2014;
-    Rozo\etal 2015b).
+    the help of the \redm{} cluster catalog\footnote{See:
+    http://risa.stanford.edu/redmapper/} (\texttt{v5.10}, e.g. \citealt{Rykoff2014};
+    \citealt{Rozo2015b}).
     These clusters are selected from the SDSS DR8 photometric data using overdensity of
@@
     Information about the identified member candidates is also provided separately. 
-    Please see Rozo\etal (2014, 2015a, 2015b) for more details about the performance of
-    the \redm cluster catalog.      
-    Several works (e.g. Li\etal 2015; Saro\etal 2015; Farahi\etal 2016; Simet\etal 2016)
-    have tried to calibrate the $M_{200c}-\Lambda$ relation using different methods.
+    Please see \citet{Rozo2014}, \citet{Rozo2015a}, \citet{Rozo2015b} for more details 
+    about the performance of the \redm~cluster catalog.      
+    Several works (e.g. \citealt{Saro2015}; \citealt{Farahi2016}; \citealt{Simet2016})
+    have tried to calibrate the $M_{200, c}-\Lambda$ relation using different methods.
     Despite the slightly different calibrations derived, it is safe to assume that most
-    clusters identified by \redm ($\Lambda > 20$) have $\log (M_{200c}/M_{\odot}) \geq
+    clusters identified by \redm~($\Lambda > 20$) have $\log (M_{200,c}/M_{\odot}) \geq
     14.0$.  
-    Considering the typical uncertainty of richness, and the fact that \redm catalog
+    Considering the typical uncertainty of richness, and the fact that \redm~catalog
     starts to become incomplete toward low richness ($\Lambda < 40$) end at $z > 0.33$, we
     will focus on the $\Lambda > 30$ clusters in this work.  
-    Based on the calibrations from Farahi\etal (2016) or Simet\etal (2016), 
+    Based on the calibrations from \citet{Farahi2016} or \citet{Simet2016}, 
     such richness cut gives us haloes with 
@@
     $M_{200c} \geq 1.60\pm0.11 \times 10^{14} M_{\odot}$.  
-    Therefore, \redm can provide us a sample of massive central galaxies in \logmh$\geq
+    Therefore, \redm~can provide us a sample of massive central galaxies in \logmh$\geq
     14.0$ haloes.  
     And, we assume that, in the same footprints and redshift range, the \logms$\geq 11.5$
-    galaxies outside \redm clusters are most likely to be the central of \logmh$< 14.0$
+    galaxies outside \redm~clusters are most likely to be the central of \logmh$< 14.0$
     haloes.
 
-    According to Leauthaud\etal (2016), all $0.2 < z < 0.5$ and \logms$\geq 11.5$ galaxies
+    According to Leauthaud\etal~(2016), all $0.3 < z < 0.5$ and \logms$\geq 11.5$ galaxies
     should have $i_{\mathrm{SDSS, cModel}} \leq 21.0$ mag.  Ignoring the tiny difference
@@
     The details of the HSC \texttt{cModel} photometry, and its performence will be
-    described in \addref Bosch\etal in.\ prep. 
+    described in \addref~Bosch\etal~in.\ prep. 
     It is quite similar to the SDSS \texttt{cModel} in principle as it also fits the total
@@
     A series of quality control cuts are applied to remove objects that are affected by 
-    saturation, cosmic ray, other optical artefacts; and the ones that are too close to 
+    saturation, cosmic ray, other optical artifacts; and the ones that are too close to 
     the edge of the field in all five bands 
@@
 
-    We match this sample with the central galaxies of \redm catalogs using a $1.0\arcsec$
-    radius, and it results in 704 galaxies.  
+    We match this sample with the central galaxies of \redm~catalogs using a 
+    $1.0^{\arcsec}$ radius, and it results in 704 galaxies.  
     %% Saved as "dr1_redbcg_hsc_sdss_gama_1arcsec.fits"
-    A small fraction of \redm centrals in the our footprints do not have matched object in
-    our sample due to severe contamination from optical artefacts or bleeding trails from
+    A small fraction of \redm~centrals in the our footprints do not have matched object in
+    our sample due to severe contamination from optical artifacts or bleeding trails from
     saturated objects.  
-    And slight change of the mathcing radius has no impact of this sample.  
+    And slight change of the matching radius has no impact of this sample.  
     For galaxy in this sample, the photometric redshift of the cluster is available for
     each of them; and for 72\% of them, the spectroscopic redshift from SDSS DR8 is also
-    provided by \redm catalog when available. 
+    provided by \redm~catalog when available. 
     This sample of will be referred as \texttt{redBCG} in the rest of the paper.
@@
     For the vast majority of galaxies that are not the centrals of very massive haloes, we
-    need other sources for their redshfit estimations. 
+    need other sources for their redshift estimations. 
     Although there has been many efforts for deriving photometric redshift (photo-$z$)
     using HSC five-band photometry, it is still a working progress now, and its
-    performence at $z \leq 0.5$ is expected to be less satisfying due to the lack of
+    performance at $z \leq 0.5$ is expected to be less satisfying due to the lack of
     information at the shorter wavelength side of the 4000$\AA$ break.  
@@
     matching the detected objects with public data of several spectroscopic surveys (e.g.
-    SDSS/BOSS \addref; GAMA \addref; PRIMUS \addref; \etal). 
-    Duplicated matches from different sources are merged through interal matching using
-    $0.5\arcsec$ radius. 
+    SDSS/BOSS; GAMA). 
+    Duplicated matches from different sources are merged through internal matching using
+    $0.5^{\arcsec}$ radius. 
     For each object, the quality information of the spec-$z$ from different catalogs are 
-    homogenized into a single flag that indicates whether the redshfit is secure, and 
+    homogenized into a single flag that indicates whether the redshift is secure, and 
     only secure spec-$z$ are used in this work. 
@@
     We match the \texttt{hscPho} sample with this external spec-$z$ catalog using a 
-    $1.0 \arcsec$ radius, and it leads to 116813 matched objects.  
+    $1.0^{\arcsec}$ radius, and it leads to 116813 matched objects.  
     %% Saved as "dr1_wide_galaxy_icmodel_21.5.fits"
-    Among these matches, there are 42696 objects at $0.2 \leq z \leq 0.5$. 
+    Among these matches, there are 42696 objects at $0.3 \leq z \leq 0.5$. 
     Most of these redshifts come from either SDSS or GAMA survey.
     To further exclude contamination from satellite galaxies, we aggressively remove 
-    all galaxies that could be associated with the \redm clusters from this catalog.  
+    all galaxies that could be associated with the \redm~clusters from this catalog.  
     First, the catalog of \texttt{redBCG} central galaxies is merged with the catalog  
     of their member galaxies. 
-    Then, through cross matching using $1.0 \arcsec$ radius, all \texttt{hscPho} galaxies 
-    that are within 2.5 Mpc of projected distance to any of cluster member are removed 
-    from the catalog.  
+    Then, through cross matching using $1.0^{\arcsec}$ radius, all \texttt{hscPho} 
+    galaxies that are within 2.5 Mpc of projected distance to any of cluster member 
+    are removed from the catalog.  
     After this step, 29973 galaxies are left in the sample. 
@@
     it is available.  
-    For the unmatched ones, only 3 of them have spec-$z$ provided by the \redm catalog 
+    For the unmatched ones, 3 of them have spec-$z$ of BCG provided by the \redm~catalog 
     (most likely due to different criteria during the selection of spec-$z$ sample).
-    For the rest, we will use the photo-$z$ of the cluster from the \redm catalog instead.
-    At $0.2 \leq z \leq 0.5$, there are 375 central galaxies left in the \texttt{redBCG} 
+    For the rest, we use the photo-$z$ of the cluster from the \redm~catalog instead.
+    At $0.3 \leq z \leq 0.5$, there are 375 central galaxies left in the \texttt{redBCG} 
     sample. 
-    Among them, 67 (17.9\%) of them do not have spec-$z$.
-    Using the central galaxis have both spec- and photo-$z$, we estimate the median 
+    Among them, 67 (17.9\%) do not have spec-$z$.
+    Using the central galaxies that have both spec- and photo-$z$, we estimate the median 
     absolute redshift difference $|z_{\mathrm{Photo}} - z_{\mathrm{Spec}}|$ is 
@@
     difference is $\sim 0.12$).  
-    Such quality is good enough for the purpose of this work. 
+    Therefore, we expect the mixture of \redm photo-$z$ and spec-$z$ results in no bias 
+    for the \texttt{redBCG} sample given the goal of this work.
+
+    At the same time, the spec-$z$ for both \texttt{redBCG} and \texttt{nonBCG} samples
+    both come from a heterogeneous catalog, which mainly consists of spec-$z$ from 
+    SDSS/BOSS and GAMA survey. 
+    All the current HSC \texttt{WIDE} footprints overlap with the SDSS/BOSS survey, 
+    which is the most important spec-$z$ sources for this work.  
+    As the main scientific goal of BOSS survey is to use the spatial distribution of
+    Luminous Red Galaxies (LRG) to map the large scale structure, it selects a large
+    sample of massive ETGs in our redshift range.  
+    However, due to the complex selection criteria for different subsamples (e.g.\ 
+    the LOWZ and CMASS), its \mstar completeness is not easy to estimate.  
+    Recently, through comparing with the Stripe 82 Massive Galaxy Catalog
+    (\texttt{S82-MGC}; \citealt{Bundy2015}), \citet{Leauthaud2016} suggests that the 
+    BOSS spec-$z$ is about 80\% complete at \logms$\geq 11.6$ at $0.3 < z < 0.5$. 
+    The current \texttt{WIDE} data also greatly overlap with the GAMA survey in the
+    G09, G12, and G15 fields. 
+    Thanks to the optimized spatial completeness and deeper limit magnitude in 
+    $r$-band ($\sim 19.8$ mag) of the GAMA survey, it provides 14\% of additional
+    spec-$z$ for our samples.  
+    However, due to the selection on fixed magnitude, its \mstar completeness 
+    strongly depends on redshift and optical color.  
+    According to \citet{Taylor2011} (e.g.\ their Figure~6), the 80\% completeness 
+    increases from $10^{10.8}$\msun at $z\sim 0.3$ to $10^{12.0}$\msun at $z\sim 0.5$.
+    Although there must be systematic differences between the above two works, 
+    we can expect a reasonable overall \mstar completeness ($\sim 80$\%) for our 
+    samples at \logms$\geq 11.6$.  
+    Later, we will further investigate the \mstar completeness and the impact of deeper
+    photometry on total stellar mass estimate. 
+    Considering the subtle differences in sources of redshift and \mstar completeness   
+    between the \texttt{redBCG} and \texttt{nonBCG} samples, we will carefully 
+    match them in the \mstar-$z$ space before any comparison is conducted.    
     %% Saved as "dr1_redbcg_use_sed5b.fits"
@@
     To further select galaxies that are truly very massive central galaxies, we use 
-    broadband Spectral Engergy Distributions (SEDs) fitting method (see \addref 
-    Walcher\etal 2011 for a recent review) to derive stellar mass
-    of our samples, and provide $k$-corrected photometry.
+    the broadband Spectral Energy Distributions (SEDs) fitting (see 
+    \citealt{Walcher2011} for a recent review) code 
+    \texttt{iSEDFit}\footnote{http://www.sos.siena.edu/~jmoustakas/isedfit/} 
+    (\citealt{Moustakas2013}) to provide estimations of average stellar 
+    mass-to-light ratio (\m2l) and $k$-corrected photometry of our 
+    sample. 
+    \texttt{iSEDFit} takes a simplified Bayesian approach. 
+    In general, it first generates a large grid of SEDs from synthetic stellar 
+    population models by drawing randomly from the prior distributions of relevant 
+    parameters (e.g.\ age, metallicity, dust extinction, and star formation history).
+    Based on these models, it uses the observed photometry and redshift to 
+    compute the statistical likelihood, and generate the posterior probability 
+    distribution (PDF) functions of each parameter.  
+    To get the best estimate of certain parameter, \texttt{iSEDFit} ``integrates'' 
+    the full PDF over all the other ``nuisance'' parameters.
+    Then, the median value of the resulting marginalized PDF is used as the best
+    value, while the 1-$\sigma$ uncertainty is derived from the cumulative PDF.
+    Please refer to \citet{Moustakas2013} for technical details and performance of     
+    \texttt{iSEDFit}. 
+    In this work, we derive average \m2l using the Flexible Stellar Population 
+    Synthesis\footnote{http://scholar.harvard.edu/cconroy/sps-models}
+    (FSPS; \texttt{v2.4}; \citealt{FSPS}, \citealt{Conroy2010}) model based on 
+    the MILES\footnote{http://www.iac.es/proyecto/miles/pages/stellar-libraries/miles-library.php}
+    (\citealt{MILES1}, \citealt{MILES2}) stellar library and \citet{Chabrier2003} 
+    IMF between 0.1 to 100 \msun. 
+    We use the delayed-$\tau$ model with stochastic star burst as the form of 
+    star formation history (SFH).  
+    We adopt flat distribution between 0.5 to 14.0 Gyrs as prior for the look-back 
+    time when the star formation turned on. 
+    The exponential delayed time-scale ($\tau$) is allowed to change between 
+    0.1 to 3.0 with equal probability.  
+    The chance of random star burst is set at 0.2 for every 2 Gyrs. 
+    The duration of the star burst is draw from a logarithmic distribution 
+    between 0.03 to 0.3 Gyr; and the mass fraction formed in the burst is from 
+    a logarithmic distribution between 0.01 and 1.0.  
+    Such form of SFH is generally considered to be appropriate for massive 
+    quiescent galaxies at low redshift (e.g. \citealt{Kauffmann2003}). 
+    For stellar metallicity, we assume flat distribution between 0.004 to 
+    0.03 (which is the highest metallicity allowed by FSPS models).  
+    And, the \citet{Calzetti2000} extinction law is adopted with a order two 
+    Gamma distribution of $A_{V}$ between 0 to 2 magnitude.  
+    To achieve reasonably good sampling across these parameters, we generate 
+    250000 models using \texttt{iSEDFit}.
 
-\subsection{Galaxies in $\Lambda < 20$ haloes}
+    In principle, these choices of priors could leave systematic effects in 
+    the estimate of stellar mass (e.g.\ \citealt{Bernardi2016b}). 
+    For low-$z$ massive ETGs like the ones in our sample, the details form of 
+    SFH, importance of random star burst, and the dust extinction should not be 
+    major concern.  
+    However, the choices of stellar population models and IMF can still 
+    change the results systematically. 
+    More discussions on this can be found in Appendix~A. 
+    In short: 
+    \begin{enumerate}
+        \item Both \texttt{FSPS+MILES} and \texttt{BC03} (\citealt{BC03} models 
+            still have difficulties recovering the optical color involving filters 
+            at the red end (e.g~$i-$Y), which could relate to the challenge for 
+            modern stellar population models to reproduce the optical color-color 
+            relation of red-sequence galaxies (e.g. \citealt{MIUSCAT2}), or the 
+            shallower photometry of HSC-Y band data. 
+        \item The \texttt{BC03} provides slightly better overall ${\chi}^2$ and 
+            systematically smaller \mstar than the \texttt{FSPS+MILES} models.  
+            However, it is possible that the \texttt{BC03} model tends to 
+            underestimate the \m2l for a fraction of them as the estimate 
+            stellar age is unrealistically young for red, massive galaxies.  
+            Therefore, we still use the \texttt{FSPS+MILES} model as the fiducial 
+            one.  But, switching to the \texttt{BC03} model will not change any 
+            key result in this work. 
+        \item The usage of \citet{Salpeter1955} IMF results in systematically 
+            higher \mstar (on average $+0.25$ dex of \logms).  
+            Although there are multiple lines of evidence that favor Salpeter 
+            or even more ``bottom-heavy'' IMF in the most massive ETGs 
+            (e.g. \citealt{Conroy2012}; \citealt{Cappellari2012}), we still 
+            present the main results using Chabrier IMF to accommodate galaxies 
+            with lower \mstar in the sample, and to be as consistent as possible 
+            with a few other works.  
+            Also, the choice of IMF does not impact our results qualitatively.     
+    \end{enumerate}
 
-    \begin{itemize}
-        \item \plan{Remove the galaxy that is close to any \redm cluster}
-        \item \plan{Remove the galaxy that is close to any bright star} 
-            \todo{Justify why we do not do this to the \redm central sample}
-    \end{itemize}
+    Besides the priors for stellar population properties, different treatments of 
+    the light profile and accuracy of sky background subtraction are also important
+    for the estimate of \mstar as they strongly impact the estimate of total luminosity
+    (e.g.\ \citealt{Bernardi2013} and \citealt{DSouza2015}).  
+    At the depth of SDSS, the default \texttt{cModel} photometry is already shown to 
+    be not very accurate at high-\mstar end (e.g. \citealt{Meert2015}; 
+    \citealt{Bernardi2016a}) as it does not capture the extended envelope of these 
+    galaxies. 
+    As for HSC, it is much more challenging for \texttt{cModel} to recover the total 
+    luminosity of massive ETGs since the stellar envelope becomes even more 
+    extended for neither de~Vaucouleur or exponential model to reproduce.  
+    However, the HSC \texttt{cModel} under the force-photometry mode can measure 
+    \textbf{average} color of the galaxy with great accuracy (e.g. Huang\etal~in prep.~), 
+    and provide us a reliable SED to estimate the \textbf{average} \m2l. 
+    Considering this, we separate the process of estimating the total \mstar of 
+    massive ETGs in our sample into two steps:
+
+    \begin{enumerate}
+        \item Firstly, using the redshift and \texttt{cModel} magnitude in five bands, 
+            we derive an initial estimate of the \mstar of the galaxy.  
+            More importantly, we derive the \textbf{average} \m2l in $i$-band of the 
+            galaxy, and use the best-fit SED to provide $k$-correction to the photometry.  
+        \item In the next section, we will derive better estimate of total \mstar using 
+            the more accurate total luminosity in $i$-band from integration of carefully 
+            measured 1-D surface brightness profile, and the average \m2l from the SED
+            fitting.  
+    \end{enumerate}
+
+    We choose $i$-band because it typically has the best seeing and image quality among 
+    all five bands, and within our redshift range, the $i$-band data can still be seen 
+    as reasonable tracer of underlying stellar mass distributions in rest-frame 
+    (at least for massive ETGs).
+    In practice, the accuracy of this approach depends on the reliability of the average
+    \m2l, and whether the \m2l of the extended envelope missed by \texttt{cModel} is 
+    similar to the average \m2l from the inner part.  
+    It is well known that massive ETGs have negative optical color gradient which 
+    indicates a gradient of \m2l (e.g.~\citealt{LaBarbera2012}; \citealt{DSouza2015}). 
+    Although the color gradient at the very outskirt are still not well quantified, 
+    it is believed to be smooth and shallow, which is favoured by our method.  
+    Also, since we focus on the comparison between the \texttt{redBCG} and 
+    \texttt{nonBCG}, our results should remain intact as long as there is no significant
+    differences of color gradient between these two samples. 
+    We will discuss more later but the initial result suggests that this is indeed the 
+    case.  
+    In principle, this is similar to the method adopted by the GAMA survey 
+    (\citealt{Taylor2011}), where the average \m2l comes from SED fitting of 
+    PSF-matched aperture photometry from multi-band photometry while the better total
+    luminosity relies on multi-band \ser model fitting (\citealt{Kelvin2012}).
+
+    \song{Not sure if we want to show this here, but just leave it here for now.}
+    The basic results from \texttt{iSEDFit} are summarized in Figure~2, where we compare
+    the relations between initial estimates of \mstar and (both luminosity and 
+    star formation weighted) stellar age, metallicity, and dust extinction. 
+    As expected, most galaxies in our samples are 
+    $\log(M_{\star,\ \mathrm{ini}}/M_{\odot}) \geq 11.2$ massive galaxies that have 
+    old age, high metallicity ($1.5 \times Z_{\odot}$ is the highest metallicity allowed), 
+    and low dust extinction.  
+    Given that we only have photometry from five optical bands, degeneracies among 
+    age, metallicity, and dust extinction are naturally expected.  
+    We will not use them for any scientific reason in this work, but to show that they
+    behave reasonably.
+
+    Currently, the \texttt{cModel} photometry heavily underestimates the 
+    flux errors of bright objects like the low-$z$ massive galaxies in our samples 
+    since it only considers the statistical error of the data, not the systematic 
+    uncertainties within the model-fitting process.  
+    Therefore such flux errors are not useful here as they leads to strongly biased
+    PDF for \mstar.  
+    Photometric tests using simulated galaxies suggest that, even at the very bright 
+    end, the average accuracy of \texttt{cModel} photometry is not better than 1\%.  
+    Based on that, we supply \texttt{iSEDFit} with simplified flux errors assuming 
+    $S/N = 100$ for $riz$ bands, and $S/N = 80$ for $gY$ bands (that typically 
+    have shallower images).  
+    Given such assumption, the typical uncertainty of \logms for both samples is 
+    around 0.08 to 0.10 dex at the high-\mstar end.
+
+    From the \texttt{iSEDFit} results, we also derive the $k$-corrected luminosity and 
+    colors.  
+    \song{Will modify the Fig3c to only show the g-r and g-z color, and remove the 
+    dashed vertical lines, replace them with single vertical line indicating logm=11.6; 
+    r-z and i-y are just to show the problem of SED fitting at the red end}
+    In Figure~3, we show the $M_{\star,\ \mathrm{ini}}$-color relations for 
+    $k$-corrected $g-r$ and $g-z$ colors, and compare their distributions for 
+    \texttt{redBCG} and \texttt{nonBCG} samples at 
+    $\log(M_{\star,\ \mathrm{ini}}/M_{\odot}) \geq 11.5$.  
+    At high-\mstar end, both samples follow the same, tight red-sequence without much 
+    contamination from the ``blue cloud''.  
+    No apparent offset between the color distributions of the two samples at fixed 
+    \mstar also suggests that, within the region traced by \texttt{cModel}, the 
+    average stellar population of massive central galaxy does not significantly depends 
+    on host halo mass (or environment), which is consistent with recent result
+    (e.g.~\citealt{Park2007}).
+
+\subsection{Comparison with \texttt{S82-MGC}}
+
+    Given the heterogeneous sources of redshift for both samples, we further 
+    investigate the \mstar completeness issue by comparing with galaxies in the 
+    common regions with the \texttt{S82-MGC} sample. 
+    The \texttt{S82-MGC} sample matches the deeper SDSS photometric data in the 
+    Stripe 82 region (\citealt{Annis2014}) with the near infrared data from the 
+    United Kingdom Infrared Telescope Infrared Deep Sky Survey (UKIDSS; 
+    \citealt{Lawrence2007}). 
+    With the help of deeper photometry and accurate photo-$z$, the \texttt{S82-MGC}
+    sample is complete to \logms$\geq 11.2$ at $z<0.7$, making it perfect sample
+    to verify the completeness of our samples.
+
+    We first match our \texttt{hscPho} sample with \texttt{S82-MGC}, 
+    and get 42090 common galaxies. 
+    Adopting the \texttt{ZBEST} in \texttt{S82-MGC} catalog, there are 20453 
+    of them at $0.3 < z < 0.5$ (referred as \texttt{s82Pho} sample).  
+    To eliminate any possible systematic, we fit their HSC \texttt{cModel} SED 
+    in exactly the same way with our \texttt{redBCG} and \texttt{nonBCG} samples 
+    to get their \mstar. 
+    The \mstar from five-band HSC SED shows very good correlation with the 
+    \texttt{S82-MGC} SED (five optical bands from SDSS and NIR data from UKIDSS)
+    fitting \mstar (\texttt{S82-MGC} also used \texttt{iSEDFit}, with slightly 
+    different priors).
+
+    Then, we compute the volume number densities of galaxies with different stellar 
+    masses for \texttt{redBCG}, \texttt{nonBCG}, and \texttt{s82Pho} samples using 
+    a naive estimate of the current survey area (99 deg$^2$ for full-color, full-depth
+    areas; we do not care about the absolute number density here, but only the 
+    relative trends with stellar mass).  
+    We also estimate the uncertainties of these distributions by bootstrap resampling 
+    the PDF of \logms 10000 times.
+
+    We show the comparison in Figure~4.  
+    Given the completeness of the \texttt{S82-MGC}, we treat the distribution of 
+    \texttt{s82Pho} sample (green) at high-\mstar end as the ``intrinsic SMF''.
+    The distribution of \texttt{nonBCG} sample starts to deviates from the 
+    \texttt{s82Pho} one below \logms$< 11.6$, suggesting small level of incompleteness. 
+    For the \texttt{redBCG} sample, its ``SMF'' behaves quite differently with the 
+    \texttt{s82Pho} one albeit its \mstar completeness should be better thanks 
+    to the photo-$z$ from \redm catalog.  
+    Since these massive central galaxies are rare objects at low-$z$, and
+    are likely hosted by very massive haloes with a narrow \logmh distribution, 
+    such different behaviour could be intrinsic. 
+    We notice that the density distribution of \texttt{redBCG} sample also turns 
+    over around \logms$\sim 11.5$.  
+    It is safe to conclude that, above this mass threshold (before any total luminosity 
+    correction), our \texttt{redBCG} and \texttt{nonBCG} samples both have reasonably 
+    high completeness.  
+    Even so, we still match their \logms distributions carefully to performance 
+    fair comparison.
 
@@
 
-\subsection{1-D surface brightness profile}
+\subsection{1-D Surface Brightness Profile}
 
-    \plan{Basica ideas}
+    % were derived from the outer- most isophotes of the galaxies after ellipse 
+    % fitting was performed using the IRAF task ellipse (Jedrzejewski 1987).
+    As mentioned in the introduction section, although 2-D model fitting
+
+    \plan{Basic ideas}
     \begin{itemize}
@@
             distribution of a galaxy.  Although it is not exactly ``model-independent'', 
-            it indeed has the advantages of not easily affected by complex substrctures 
-            within the galaxy comparing with the more popular 2-D modelling method. }
+            it indeed has the advantages of not easily affected by complex substructures 
+            within the galaxy comparing with the more popular 2-D modeling method. }
         \item \plan{Due to the uniquely extended nature of the light distributions of 
             these massive ETGs, it is still unclear which is the most appropriate 2-D 
-            model for them (Can not be well described by 1-\ser model). }
+            model for them (Can not be well described by 1-\ser~model). }
     \end{itemize}
@@
 
-\subsection{Average mass-to-light ratio}
-
-    \begin{itemize}
-        \item \plan{Briefly explain the method to convert surface brightness profiles 
-            into mass density profile, focusing on the key assumptions.}
-        \item \plan{Describe the SED fitting process.}    
-        \item \plan{Briefly discuss the impact of choices of SSP model, IMF, priors of 
-            parameters for SED fitting}
-    \end{itemize}
-
-\subsection{Basic properties of the sample}
+\subsection{Stellar Mass Corrected for Total Luminosity}
 
@@
 
-    \todo{Justify why we can assume most very massive galaxies in \nonbcg haloes are
+    \todo{Justify why we can assume most very massive galaxies in \nonbcg~haloes are
         central galaxies}
@@
 
-\subsection{Implications on assembly history of massive galaxies}
+\subsection{Implications on Assembly History of Massive Galaxies}
 
@@
 
-\subsection{Ellipticity profiles}
+\subsection{Ellipticity Profiles}
 
-\subsection{The impact of $M/L$ gradient}
+\subsection{The Impact of $M/L$ Gradient}
+
+\subsection{\mstar and Structural Evolution between $0.3 < z < 0.5$}
+
+\subsection{Impact from ``Fossil Galaxies''}
+
+    ``Fossil galaxy'' is the most massive galaxy in a ``fossil group/cluster''
+    system.
+    According to the commonly adopted definition, ``fossil'' systems are the 
+    group or cluster with high X-ray luminosity and large magnitude gap between 
+    the two brightest galaxies (\addref: Ponman1994; Jones2003). 
+    Both observations and simulations suggest that they could represent the 
+    final stage of the hierarchical merging process in a group/cluster mass
+    halo that is formed at very early epoch (e.g. \addref: 
+    Khosroshahi2004, 2007; DOnghia2005; Dariush2007).
+    Under this interpretation, at fixed halo mass, the central galaxy of 
+    a fossil system typically has larger stellar mass than the one in normal 
+    system (e.g. Harrison2012), as it has ``consumed'' most satellites 
+    early on; 
+    However, the ``low richness'' of a fossil system makes it difficult for 
+    red-sequence finder like \redm~to reliably identify 
+    (e.g. Figure~17 of Sadibekova2014).  
+    If some massive ETGs in our \texttt{nonBCG} sample are actual the centrals 
+    galaxies of fossil clusters, it could bias our conclusions about the 
+    relation between strcutre and ``environment''.
+
+    Although it is possible that fossil systems formed earlier than normal 
+    clusters, the difference in detailed merging history is still unclear, 
+    hence it is hard to imagine the structural differences between fossil 
+    central galaxies and regular BCGs with same \mstar.  
+    Naively speaking, more frequent mergers for fossil centrals should result 
+    in more extended stellar envelope.  
+    However, the distributions of epoch and mass-ratio of those mergers also 
+    matter.
+
+    The lack of any difference in stellar population properties may suggest 
+    It is still not clear how the mass assembly history of fossil central
+
+\subsection{Connection and Difference with the Intra-Cluster Light}
 
 \subsection{Massive satellites of the $\Lambda > 20$ haloes}
-\song{TBD: optional}
-
-\subsection{Connection and difference with the Intra-Cluster Light}
+\song{TBD:optional}
 
@@
     \begin{enumerate}
-        \item \plan{Improvements of HSC data reduction: better sky modelling; 
+        \item \plan{Improvements of HSC data reduction: better sky modeling; 
             \texttt{redMaPPer} clusters using HSC photometry.}
-        \item \plan{Comparison with 2-D image modelling method.}
-        \item \plan{``Correct'' the PSF smeearing effect at the center with the help of 
+        \item \plan{Comparison with 2-D image modeling method.}
+        \item \plan{``Correct'' the PSF smearing effect at the center with the help of 
             residual correct 2-D model.}
@@
 \acknowledgements
-
   The Hyper Suprime-Cam (HSC) collaboration includes the astronomical communities of Japan
@@
   \href{http://www.astropy.org/}{Astropy}, a community-developed 
-  core Python package for Astronomy (Astropy Collaboration, 2013; 
+  core Python package for Astronomy (Astropy Collaboration, 2013); 
   \href{https://github.com/kbarbary/sep}{sep} 
@@
 
-%%%%%%%%%%: Bibligraphic Section %%%%%%%%%%
+%%%%%%%%%%: Bibliographic Section %%%%%%%%%%
 
@@
 
-\section{A. Extraction of 1-D surface brightness profile}
+\section{A. Derive average mass-to-light ratio using \texttt{iSEDFit}}
 
-\section{B. Derive average mass-to-light ratio using \texttt{iSEDFit}}
+\section{B. Extraction of 1-D surface brightness profile}
 
@@
     \includegraphics[width=15.5cm]{fig/fig1.png}
-    \caption{Figure.1\todo{Caption}}
-    \label{figure:1}
+    \caption{Figure.1\todo{Caption}}\label{figure:1}
 \end{figure}
@@
 \clearpage
-\figurenum{2}
+\figurenum{2a}
 \begin{figure}
     \centering 
-    \includegraphics[width=13.5cm]{fig/massive_s15b_g15_sample.png}
-    \caption{Figure.2\todo{Caption}}
-    \label{figure:2}
+    \includegraphics[width=11.5cm]{fig/dr1_redbcg_use_sed5b_fsps2_logm_plots}
+    \caption{Figure.2a\todo{Caption}}\label{figure:2a}
+\end{figure}
+
+\figurenum{2b}
+\begin{figure}
+    \centering 
+    \includegraphics[width=11.5cm]{fig/dr1_nonbcg_use_sed5b_fsps2_logm_plots}
+    \caption{Figure.2b\todo{Caption}}\label{figure:2b}
 \end{figure}
@@
 \clearpage
-\figurenum{3}
+\figurenum{3a}
 \begin{figure}
     \centering 
-    \includegraphics[width=13.5cm]{fig/massive_s15b_zuse_hist1.png}
-    \caption{Figure.3\todo{Caption}}
-    \label{figure:3}
+    \includegraphics[width=10.5cm]{fig/dr1_redbcg_isedfit_mass_fsps1_sbpsum_imgsub_use_grKcor_hist}
+    \caption{Figure.3a\todo{Caption}}\label{figure:3a}
+\end{figure}
+
+\figurenum{3b}
+\begin{figure}
+    \centering 
+    \includegraphics[width=10.5cm]{fig/dr1_redbcg_isedfit_mass_fsps1_sbpsum_imgsub_use_gzKcor_hist}
+    \caption{Figure.3b\todo{Caption}}\label{figure:3b}
+\end{figure}
+
+\figurenum{3c}
+\begin{figure}
+    \centering 
+    \includegraphics[width=12.5cm]{fig/dr1_redbcg_isedfit_mass_fsps1_sbpsum_imgsub_use_mass_color}
+    \caption{Figure.3c\todo{Caption}}\label{figure:3c}
 \end{figure}
@@
     \centering 
-    \includegraphics[width=15.5cm]{fig/redbcg_1_HSC-I_full_imgsub_ellip_default_sum.png}
-    \caption{Figure.4\todo{Caption}}
-    \label{figure:4}
+    \includegraphics[width=14.5cm]{fig/dr1_redbcg_isedfit_mass_fsps1_sbpsum_imgsub_use_logm_distribution_s82}
+    \caption{Figure.4\todo{Caption}}\label{figure:4}
 \end{figure}
@@
     \centering 
+    \includegraphics[width=15.5cm]{fig/redbcg_1_HSC-I_full_imgsub_ellip_default_sum.png}
+    \caption{Figure.5\todo{Caption}}\label{figure:5}
+\end{figure}
+
+% Fig. 6
+\clearpage
+\figurenum{6}
+\begin{figure}
+    \centering 
     \includegraphics[width=14.0cm]{fig/redbcg_1_HSC-I_full_imgsub_ellip_default_compare.png}
-    \caption{Figure.5\todo{Caption}}
-    \label{figure:5}
+    \caption{Figure.6\todo{Caption}}\label{figure:6}
 \end{figure}

### 2016-09-30 draft/ms.tex
Recent update of draft and notebooks

--- 2016-02-08 draft/ms.tex
@@
 \usepackage{CJK}
+\usepackage{natbib}
+\usepackage{hyperref}
+\usepackage[usenames]{color}
+
+% Package Settings
+\bibliographystyle{apj}
+\hypersetup{colorlinks=true,
+            citecolor=cyan,
+            linkcolor=cyan,
+            filecolor=magenta,      
+            urlcolor=cyan}
+\urlstyle{same}
+
+% Figure extention
 \DeclareGraphicsExtensions{.pdf,.png,.jpg}
-\bibliographystyle{apj}
-
 \input psfig.tex
@@
 
-%Song Huang's definition 
+\def\etal{{\ et al.~}}
 \def\galfit{{\tt GALFIT}}
 \def\ser{{S\'{e}rsic\ }}
+\def\redm{\texttt{redMaPPer}}
+\def\cmodel{\texttt{cModel}}
+\def\redbcg{{$\lambda \ge 30$}}
+\def\nonbcg{{$\lambda < 20$}}
+\def\logms{{$\log (M_{\star}/M_{\odot})$}~}
+\def\mstar{{$M_{\star}$}~}
+\def\logmh{{$\log (M_{\mathrm{Halo}}/M_{\odot})$}~}
+\def\mcmodel{{$M_{\star,\mathrm{cModel}}$}~}
+\def\mtot{{$M_{\star,100\mathrm{kpc}}$}~}
+\def\minn{{$M_{\star,10\mathrm{kpc}}$}~}
+\def\m2l{{$M_{\star}/L_{\star}$}~}
+\def\rbcg{\texttt{redBCG}}
+\def\nbcg{\texttt{nonBCG}}
+
+% Commenting:
+\newcommand{\todo}[1]{\textcolor{red}{\textbf{TODO:~#1}}}
+\newcommand{\plan}[1]{\textcolor{cyan}{#1}}
+\newcommand{\addref}{{\textcolor{red}{REF}}}
+\newcommand{\note}[2]{\textcolor{blue}{\textbf{[Comment (#1): #2]}}}
+\newcommand{\song}[1]{\textcolor{magenta}{\textbf{[Song: #1]}}}
+\newcommand{\alexie}[1]{\textcolor{blue}{\textbf{[Alexie: #1]}}}
+\newcommand{\kevin}[1]{\textcolor{green}{\textbf{[Kevin: #1]}}}
 
@@
 
-\slugcomment{Draft version 0}
+\slugcomment{Draft version -1}
+\email{song.huang@ipmu.jp}
 \shorttitle{ENVIRONMENT DEPENDENCE OF MASS-SIZE RELATION}
@@
 
-\title{The Environmental Dependence of Structures for Massive Galaxies
-from the Hyper-Suprime Camera Survey}
+\title{The Environment and Structure of Massive Central Galaxies
+using the Subaru Hyper Suprime-Cam Survey}
 
-\author{Song Huang (黄崧)\altaffilmark{1} Alexie Leauthaud\altaffilmark{1}, 
-Kevin Bundy\altaffilmark{1}, and You}
+\author{Song Huang (黄崧)\altaffilmark{1} 
+        Alexie Leauthaud\altaffilmark{1}, 
+        Kevin Bundy\altaffilmark{1},
+        Michael Strauss\altaffilmark{2},
+        Yen-Ting Lin\altaffilmark{3},
+        Rachel Mandelbaum\altaffilmark{4}
+        }
 \date{}
@@
 \altaffiltext{1}{Kavli Institute for the Physics and Mathematics of the 
-Universe, Todai Institutes for Advanced Study, the University of Tokyo (Kavli
-IPMU, WPI), Kashiwa 277-8583, Japan}
+    Universe, The University of Tokyo Institutes for Advanced Study, 
+    the University of Tokyo (Kavli IPMU, WPI), Kashiwa 277--8583, Japan}
+\altaffiltext{2}{Princeton University Observatory, 
+    Peyton Hall, Princeton, NJ 08544, USA}
+\altaffiltext{3}{Institute of Astronomy and Astrophysics, Academia Sinica, 
+    P.O.~Box 23--141, Taipei 10617, Taiwan}
+\altaffiltext{4}{Carnegie-Mellon University \todo{correct affiliation here}}
 
@@
 
-  Many recent observations and numerical simulations suggest that nearby
-  massive, early-type galaxies are formed through a ``two-phase'' process.  In
-  the proposed second phase, the extended stellar envelope was accumulated
-  through many dry mergers. (XX TODO)
+    Although the environmental dependence of structures for massive central 
+    galaxies is predicted by the promising hierarchical assembly model, 
+    observations at low redshift seem to find no convincing evidence for that. 
+    With the help of deep $i$-band images of a large sample of massive central 
+    galaxies at $0.3 < z < 0.5$ from the Subaru Hyper Suprime-Cam (HSC) survey, 
+    we map their stellar mass distributions out to radius larger than $100$ kpc, 
+    and discover subtle, but systematic and robust structural differences that 
+    depend on halo mass. 
+    At fixed stellar mass within 100 kpc, the massive central galaxies in more 
+    massive ($M_{200,c}$ \gax $1.6\times 10^{14} M_{\odot}$) halos have a 
+    slightly flattened inner profile within $\sim 15$-$20$ kpc, and a more prominent 
+    outer envelope compared to ones in less massive 
+    ($M_{200,c}$ \gax $8.7\times 10^{13} M_{\odot}$) halos.
+    For centrals with $M_{\star} > 10^{11.5} M_{\odot}$, the ones in more massive 
+    halos show very significant excess of mass in the outskirt when the two samples 
+    are matched using proxies of mass assembled at $z > 1$. 
+    Such differences are broadly consistent with richer recent merging history 
+    for more massive halos. 
+    We suggest that the relation between total stellar mass and mass within inner 5 
+    or 10 kpc is potentially interesting for diagnosing the role played by host halo 
+    in shaping the structures of massive central galaxies. 
+    These results also highlight the importance of deep photometry and the usage of 
+    detailed structural information in the study of the assembly history of galaxies.
+
+    % We also show that the radial profiles of ellipticity and optical color, along with 
+    % the preliminary weak lensing signals will enable us gain more insights about the 
+    % evolution of massive galaxies.
 
@@
 
+%% ------------------------------------------------------------------------------------ %% 
 \section{Introduction}
 
-\section{Sample and Data Reduction}
+    \plan{Scientific Background}
+    \begin{itemize}
+        \item \plan{Massive galaxies are important cosmic probe and unique labs to study 
+            galaxy evolution.} 
+        \item \plan{Briefly explain why massive early-type galaxies are important through 
+            the difficulties of stellar-halo mass relation and stellar mass function at the 
+            high-mass end.}
+        \item \plan{Brief summary of the current understanding of their cosmic assembly 
+            history.}
+        \item \plan{Explain why we should care about the environment, and why we expect to 
+            see some environmental dependence in the structure and other properties of
+            massive galaxies.}
+        \item \plan{Brief review of the current observations.  It is still not clear 
+            whether there is a clear environmental dependence.}
+    \end{itemize}
+
+    \plan{Observational difficulties (a.k.a Why we need HSC)}
+    \begin{itemize}
+        \item \plan{Explain why it is important to study the mass distribution of 
+            massive galaxies out to large physical radius; and, given their unique light 
+            profiles, why it is more difficult to study them compared to late-type 
+            galaxies.}
+        \item \plan{Very brief summary of past observational efforts, and why they are not 
+            good enough (Not enough number of really massive galaxy; Shallow images; 
+            Background subtraction issue; and stacking analysis can be dangerous as while)}
+    \end{itemize}
+
+    \plan{Basic idea of this work}
+    \begin{itemize}
+        \item \plan{Here we take advantages of the ambitious Hyper-Suprime camera 
+            survey\ldots}
+    \end{itemize}
+
+    To achieve this goal, we will select \logms$ > 11.5$ massive central galaxies within
+    host halo mass larger and smaller than \logmh$= 14.0$ at $0.3 < z < 0.5$.  
+    As both $M_{\star}$-$M_{\mathrm{Halo}}$ relation and stellar mass function are still
+    quite uncertain at \logms$ > 11.5$, it is of great interest to investigate the
+    structure of galaxies in this region carefully. 
+    Under the adopted cosmology, $1.0^{\arcsec}$ equals 4.4 and 6.1 kpc at redshift 0.3 
+    and 0.5.  
+    Therefore, this redshift range enables us to reliable measure the total stellar mass 
+    within the inner 5 to 10 kpc (where the ``in-situ'' component should still dominates) 
+    of massive galaxies at the high redshift end assuming the typical seeing of HSC data. 
+    At the same time, the depth of the HSC image allows to map the stellar distribution 
+    of these galaxies out to $\sim 100$ kpc at $z\sim 0.5$.  
+    Within these stellar mass and redshift range, we can select a large sample of 
+    galaxies from the current $\sim 100$ square degree of HSC data, and safely ignore 
+    significant mass growth and structural evolution (no star formation, 
+    lower merger rate \etal~e.g.\ \citealt{Bellstedt2016}, \citealt{Inagaki2015}; 
+    but also see \citealt{Bai2014}; more discussion about this in Section~5).
+
+    The paper is organized as follows. Section~2 gives a brief overview of the HSC
+    observation and data reduction.  We will also summarize the process of sample
+    selection.  In Section~3, we will describe the method for deriving the stellar mass 
+    surface density profile.  The main results are summarized in Section~4.  Section~5 
+    provides discussions of the assumptions used in this work, the potentially interesting
+    physical implications, and several future improvements, ending with a summary in
+    Section~6.
+
+    All the magnitudes used here are in AB system (\citealt{Oke1983}), and are corrected 
+    for Galactic extinction using calibrations from \citet{Schlafly11}.
+    Within this work, we assume $H_0$ = 70~km~s$^{-1}$ Mpc$^{-1}$, ${\Omega}_m=0.3$, 
+    and ${\Omega}_{\lambda}=0.7$.
+
+%% ------------------------------------------------------------------------------------ %%
+
+\section{Data And Sample Selection}
+
+\subsection{The Hyper Suprime-Cam Survey}
+
+    The Subaru Strategic Program (SSP, \addref) makes use of the new prime-focus camera,
+    the Hyper Suprime-Cam (HSC;~\citealt{Miyazaki2012}), on the 8.2-m Subaru
+    telescope at Mauna Kea.  
+    Taking advantage of the large field of view (FoV;~1.5 deg in diameter) of HSC, this
+    ambitious multi-layer photometric survey will cover $\sim 1400$ deg$^2$ of sky in 5
+    broad bands (\textit{g r i z Y}) to the depth of $r \sim 26$ mag in the \texttt{WIDE}
+    part in the next few years.  
+    This work is based on the internal data release \texttt{S15B}, which covers $\sim 100$
+    square of degree of sky in all 5-band to the required depth of \texttt{WIDE} survey.  
+    The regions covered by this release are overlapped with several previous spectroscopic
+    survey (e.g.\ SDSS/BOSS: \citealt{Eisenstein2011}, \citealt{Alam2015}; 
+    GAMA: \citealt{Driver2011}, \citealt{Liske2015}).
+
+    The data are processed with \texttt{hscPipe 4.0.1}, a derivative of the Large Synoptic
+    Survey Telescope (LSST) pipeline (e.g.\ \citealt{Ivezic2008}; \citealt{Axelrod2010}),
+    modified for use with Suprime-Cam and Hyper Suprime-Cam.  
+    \texttt{hscPipe} first bias subtract, flat field, model background, and perform object
+    detection and measurement on the single exposure data. 
+    Then, different exposures are warped onto a common World Coordinate System (WCS) and
+    combined into final images with improved signal-to-noise ratio (SNR) after astrometric
+    and photometric calibration.  
+    The pixel scale of the combined images is $0.168^{\arcsec}$.  
+    The photometric calibration is based on data obtained from the Panoramic Survey 
+    Telescope and Rapid Response System (Pan-STARRS) 1 imaging survey 
+    (\citealt{Schlafly2012}, \citealt{Tonry2012}, \citealt{Magnier2013}). 
+    To achieve consistent deblending and photometry across all bands, the \texttt{hscPipe}
+    will perform multi-band post-processing on the combined images.  
+    The footprints and peaks of detected sources on each band will be merged into a single
+    catalog.    
+    This consistent set of peaks and footprints is used as starting point for deblend and
+    measure objects on the combined images of each band.  
+    These measurements are then merged into a reference catalog.  After fixing the
+    centroids, shape, and other non-amplitude parameters of every object in this catalog,
+    \texttt{hscPipe} will derive forced photometry measurements at each band. 
+    Details of \texttt{hscPipe} and the multi-band processing method will be presented in
+    \addref~(Bosch\etal~in prep.).
+
+    In Figure 1, we compare the false color ({\tt gri}) images of nearby massive
+    galaxies from both SDSS and HSC surveys.  
+    The RGB images are generated using similar scaling and color schemes, and clearly
+    demonstrate the capability of HSC to map the stellar distribution out to the very 
+    outskirt of these massive galaxies, where important fossil records about their 
+    recent assembly history are stored.   
+    In $i$-band (ignoring the slight difference in filter response curve), the HSC
+    \texttt{WIDE} image is on average $3.0$-$4.0$ magnitude deeper than SDSS, which 
+    gives us significant advantage in studying massive ETGs given their extended, shallow 
+    outer surface brightness profiles.
+
+    Motivated by the requirement of weak lensing analysis, the $i$-band data typically has
+    the best seeing in all five bands (the median seeing is around 
+    FWHM$\sim 0.7^{\arcsec}$).
+    Therefore, we will mostly use the $i$-band images to study the structure of galaxies.
+
+\subsection{\redm{} cluster catalog}
+
+    In order to select the central galaxies from cluster level dark matter halos 
+    (e.g.\ $> 10^{14} M_{\odot}$), we make use of the \redm{} cluster 
+    catalog\footnote{See: http://risa.stanford.edu/redmapper/} 
+    (\texttt{v5.10}, e.g.\ \citealt{Rykoff2014}; \citealt{Rozo2015b}).
+    These clusters are selected from the SDSS DR8 photometric data using overdensity of
+    red-sequence galaxies. 
+    For each cluster, the catalog provides robust estimations of photometric redshift
+    $z_{\lambda}$ and richness $\lambda$, along with the best candidate of the central
+    galaxy (the one with the highest central probability \texttt{P\_CEN}).
+    Information about the identified member candidates is also provided separately. 
+    Please see \citet{Rozo2014}, \citet{Rozo2015a}, \citet{Rozo2015b} for more details 
+    about the performance of the \redm~cluster catalog.      
+    Several works (e.g.\ \citealt{Saro2015}; \citealt{Farahi2016}; \citealt{Simet2016})
+    have tried to calibrate the $M_{200, c}-\lambda$ relation using different methods.
+    Despite the slightly different calibrations derived, it is safe to assume that most
+    clusters identified by \redm~($\lambda > 20$) have $\log (M_{200,c}/M_{\odot}) \geq
+    14.0$.  
+    Considering the typical uncertainty of richness, and the fact that \redm~catalog
+    starts to become incomplete toward low richness ($\lambda < 40$) end at $z > 0.33$, we
+    will focus on the $\lambda > 30$ clusters in this work.  
+    Based on the calibrations from \citet{Farahi2016} or \citet{Simet2016}, 
+    such richness cut gives us haloes with 
+    $M_{200c} \geq 1.56\pm0.35 \times 10^{14} M_{\odot}$ or 
+    $M_{200c} \geq 1.60\pm0.11 \times 10^{14} M_{\odot}$.  
+    Therefore, \redm~can provide us a sample of massive central galaxies in \logmh$\geq
+    14.0$ haloes.
+
+\subsection{Initial Selection of Massive Galaxies}
+
+    We begin by making an initial selection of massive galaxies with reliable redshift from 
+    the HSC survey.  
+    The goal is to have a parent sample that contains a reasonably complete sample of 
+    \logms$\geq 11.5$ galaxies at $0.3 < z < 0.5$. 
+    According to Leauthaud\etal~(2016), such galaxies should have 
+    $i_{\mathrm{SDSS, cModel}} \leq 21.0$ mag.
+    Therefore, we first select all galaxies with $i_{\mathrm{HSC, cModel}} \leq 21.5$ 
+    \footnote{Difference of response curves between SDSS $i$ and HSC $i$ filter is tiny}
+    in regions that are covered by all five bands, and have reached the expected depth 
+    of \texttt{WIDE} survey.  
+    %% The SQL search is saved as "sample.sql" 
+    %% The master catalog used here is "dr1_wide_galaxy_icmodel_21.5.fits"
+    %%   The original catalogs contain 2275477 objects
+    The HSC \texttt{cModel} photometry is similar to the SDSS \texttt{cModel} algorithm.  
+    It fits the flux distribution of an object using a combination of de~Vaucouleur and 
+    exponential components after the PSF convolution is considered.  
+    For more details about the algorithm, please see Bosch\etal~in prep.~; and its 
+    performance has been tested using synthetic objects (Huang\etal~in prep.~). 
+    Although the overall performance of HSC \cmodel photometry is accurate down to very 
+    faint magnitude, it tends to underestimate the total flux of massive ETGs 
+    (will discuss this in details later). 
+    This is partially caused by issues with deblending process (see more discussion in 
+    Bosch\etal~in prep.~), but also reflects the intrinsic limitation of \cmodel, 
+    as the real flux distributions of massive galaxies are often too extended to be 
+    modeled this way at the depth of HSC images.  
+    For this reason, we will perform careful photometric measurements to derive 
+    more accurate total luminosity and stellar mass, and the sample selected here 
+    serves as an initial one for us to work on.
+
+    We select objects that are classified as galaxies, have well defined centroids, 
+    are deblended successfully, and have \texttt{cModel} magnitudes in all five bands. 
+    After a few more quality control criteria (saturation, cosmic-ray, optical artifact)
+    are applied\footnote{each criterion affects less than 8\% of the entire sample}, 
+    we select 1760845 galaxies in this sample that will be referred as \texttt{hscPho}. 
+    %% Saved as "dr1_wide_galaxy_hscPho.fits"
+
+    As reliable photometric redshift using HSC photometry is still a working progress, 
+    we only use objects with either spectroscopic redshift or robust red-sequence 
+    photo-$z$ from the \redm{} catalog.  
+    We first match the \texttt{hscPho} sample with the external spec-$z$ catalog 
+    compiled by HSC database\footnote{It is created by matching HSC objects with 
+    public data of several spectroscopic surveys (e.g.\ SDSS/BOSS; GAMA). 
+    Duplicated matches from different sources are merged through internal matching 
+    using $0.5^{\arcsec}$ radius. 
+    For each object, the quality information of the spec-$z$ from different catalogs are 
+    homogenized into a single flag that indicates whether the redshift is secure, and 
+    only secure spec-$z$ are used in this work.}
+    %% This is catalog: "dr1_specz_use.fits"
+    with a $1.0^{\arcsec}$ radius, and it leads to 116813 matched objects, and 
+    42696 objects are at $0.3 \leq z \leq 0.5$.
+    %% Saved as "dr1_wide_galaxy_icmodel_21.5.fits"
+    Most of these redshifts come from either SDSS/BOSS or GAMA survey.
+    For objects without external spec-$z$, we also match the sample with the \redm{}
+    catalog, and add objects with useful red-sequence photo-$z$ ($z_{\lambda}$)
+    back in.      
+    Together, this gives us a sample of bright galaxies with useful redshift.
+
+\subsection{Massive Central Galaxies from Low and High Mass Halos}
+
+    Based on recent constraints of $M_{\star}$-$M_{\mathrm{Halo}}$ relation 
+    (e.g.\ \citealt{Leauthaud2012}, \citealt{Behroozi2013}, \citealt{Kravtsov2014}), 
+    massive galaxies with \logms$ > 11.5$ are hosted by dark matter halos with a 
+    large range of mass. 
+    Although we can not measure halo mass for individual galaxy, we can still broadly 
+    separate them into galaxies in small groups (\logmh$<14.0$) and large groups/clusters
+    (\logmh$>14.0$), and investigate their stellar mass distributions.
+
+    % We match this sample with the central galaxies of \redm~catalogs using a 
+    % $1.0^{\arcsec}$ radius, and it results in 704 galaxies.  
+    %% Saved as "dr1_redbcg_hsc_sdss_gama_1arcsec.fits"
+    We first match the initial sample of massive galaxies with the central galaxies 
+    in \redm{} catalog with $1.0^{\arcsec}$ radius, which results in 375 matched ones at 
+    $0.3 \leq z \leq 0.5$.  
+    We will refer this sample of \textbf{central galaxies in \logmh$\ge 14.0$ halos} as 
+    \texttt{redBCG} in this work.
+    A small fraction of \redm~centrals within HSC footprints do not have matched object 
+    due to severe contamination from optical artifacts.
+    Spec-$z$ is not available for 67 (17.9\%) of the sample, but their $z_{\lambda}$ 
+    should be very accurate (median $|z_{\lambda} - z_{\mathrm{Spec}}|$ is about 0.01 
+    for the ones with spec-$z$).
+    The median richness ($\lambda$) of these clusters is $\sim 32$, corresponding to 
+    halo mass of $M_{200,c}\sim 1.7\times 10^{14} h^{-1} M_{\odot}$. 
+    Given the uncertainty of richness estimate using shallow SDSS photometry, we 
+    mainly focus on the centrals of clusters that have $\lambda > 30$ 
+    ($M_{200,c}> 1.7\times 10^{14} h^{-1} M_{\odot}$).
+    %% Saved as "dr1_redbcg_use_sed5b.fits"
+
+    Then, we matched the initial sample with both the central and satellite galaxy catalogs 
+    of \redm{} using a physical radius of 2.5 Mpc and absolute redshift difference of 
+    0.05 (using $z_{\lambda}$ for all members).  
+    By removing all the matched objects, we aggressively exclude galaxies that are 
+    associated with these massive halos.  
+    The rest 29973 galaxies should mostly live in \logmh$< 14.0$ halos, and the real 
+    \logms$ > 11.5$ ones among them should be dominated by central galaxies of these 
+    halos as the satellite contamination is very low at such high mass end 
+    (e.g.\citealt{vanUitert2016}).
+    We will refer this sample of \textbf{central galaxies in \logmh$< 14.0$ halos} as 
+    \texttt{nonBCG} later.
+    %% Saved as "dr1_nonbcg_use_sed5b.fits"
+
+    It is worth noting that, at $0.3 < z < 0.5$, most redshifts in both \texttt{redBCG} 
+    and \texttt{nonBCG} come from GAMA and SDSS/BOSS survey.  
+    The current sample partially overlaps with the GAMA survey, which reaches 
+    to $\sim 19.8$ mag in $r$-band, and provides us unique spec-$z$ for 14\% of the 
+    entire initial sample. 
+    According to \citet{Taylor2011} (e.g.\ their Figure~6), at $z\sim 0.3$, the GAMA 
+    sample is 80\% complete down to $10^{10.8}$\msun; but only 80\% complete to 
+    $10^{12.0}$\msun at $z\sim 0.5$. 
+    Meanwhile, the BOSS survey provides us the majority of spec-$z$ in our samples.  
+    Due to the complex selection criteria for different subsamples within the BOSS
+    survey (e.g.\ the LOWZ and CMASS), its \mstar completeness is hard to estimate.  
+    Recently, through comparing with the Stripe 82 Massive Galaxy Catalog
+    (\texttt{S82-MGC}; \citealt{Bundy2015}), \citet{Leauthaud2016} suggests that the 
+    BOSS spec-$z$ is about 80\% complete at \logms$\geq 11.6$ at $0.3 < z < 0.5$. 
+    Despite the difference in photometry and stellar mass estimates, we can expect 
+    our samples are reasonably complete above \logms$\geq 11.6$.
+    We will further address the \mstar completeness issue more carefully with the 
+    help of the photo-$z$ from the \texttt{S82-MGC} sample (see Section~4.3).
+
+%% ------------------------------------------------------------------------------------ %%
+
+\section{Measurements of 1-D Surface Brightness Profile}
+
+\subsection{1-D Surface Brightness Profile}
+
+    To estimate the total luminosity of massive galaxies, and measure their 
+    one-dimensional stellar mass density profiles, we perform elliptical isophotes 
+    fitting using the IRAF task \texttt{Ellipse} (Jedrzejewski 1987).  
+    Compared to the popular two-dimensional model fitting method, the isophote fitting
+    approach is much less sensitive to the choice of model type, number of components, 
+    and initial guesses of free parameters; is also less affected by the uncertainties 
+    of the sky background subtraction.  
+    This is particularly important for the massive ellipticals in our sample.  
+    The much deeper depth of the HSC images reveal much more extended structures, 
+    but also make it impossible and inappropriate to fit these galaxies with single 
+    \ser component as it often requires uncomfortably high \ser index (e.g.\ $>6.0$), 
+    can not fit the center of massive galaxies well, and can not account for the 
+    radial variation of ellipticity and position angle. 
+    In principle, their surface brightness distributions can be described by models 
+    with multiple components (e.g \citealt{Huang2013a}; \citealt{Huang2013b}).  
+    However, these models still suffer from issues like sensitivity to background 
+    subtraction, internal degeneracies of parameters, and choice of best number of 
+    components.  
+    Their robustness and physical meanings still deserve more investigations. 
+    Therefore, we think the 1-D method suits the scientific goal of this work better.
+
+    We first generate large cut-out images for galaxies in our samples, and make sure
+    the image covers to at least 750 kpc from the center of the galaxy in radius, so 
+    we can safely assume that we cover the entire galaxy while still have enough space 
+    to estimate the background.  
+    We also reconstruct the PSF model using the central coordinate of the galaxy, and 
+    generate bad pixel mask. 
+    We choose $i$-band as the default band to extract 1-D surface brightness profile 
+    since it has the best seeing among all five bands, and can still serve as good 
+    stellar mass distribution tracer at $0.3 < z < 0.5$.  
+    Although $z$ and Y-band should suffer less from potential internal dust extinction
+    and radial variation of mass-to-light ratio, the sky background is much higher in 
+    these two bands, and the seeing conditions are often considerably worse than 
+    $i$-band.
+
+    Then we use a customized photometric procedures based on \texttt{SEP} Python library
+    to create object mask before we run \texttt{Ellipse}.  
+    The current HSC pipeline still has difficulties dealing with regions around bright 
+    galaxies as the extended wings from bright objects result in overestimated S/N that
+    leads to ``over-deblending'' issue.  
+    Our customized pipeline is more flexible since we can run \texttt{SExtractor}-like
+    measurements twice using different configurations for background subtraction, 
+    detection, and deblending.  
+    Global background, low-detection threshold, and conservative deblending help detects
+    all the large, bright, or diffuse objects; while very small background box size and 
+    aggressive deblending together can help detect the faint objects that are on the 
+    extended envelope of bright galaxies or close to the galaxy center.  
+    The catalogs from these two steps are merged after the target galaxy at the center 
+    is identified and removed. 
+    To mask out most fluxes from other objects, we convolved the pixel segmentation of 
+    each object with a Gaussian kernel to increase its size.  
+    Then, these expanded pixel segmentations are merged with the bad pixel mask into a 
+    binary object mask.  
+    This method works very well for early-type galaxy that has smooth structural 
+    features.
+
+    Meanwhile, we also generate a mask of all objects detected by above procedures with 
+    a much more aggressive masking method (larger Gaussian kernel size).  
+    We treat the unmasked pixels as ``sky pixels'', and rebin them using 6x6 box size.
+    Then we use the median value of each box to generate the statistics of sky background.
+    As expected, we often see negative median values in the distribution of sky pixels 
+    around our massive galaxies as the HSC pipeline tends to slightly over-subtract 
+    the background\footnote{This is similar to what happened to SDSS as shown in 
+    \citealt{Blanton2011}, but at a lesser level.  The sky background of each CCD 
+    is modeled using a Chebyshev-polynomial fit to the pixels that do not belong to 
+    any object after they are smoothed}. 
+    As this over-subtraction often leads to unphysical truncation of surface brightness 
+    profile, we provide an ad-hoc fix using a \texttt{SExtractor}-like background model 
+    created by \texttt{SEP} with 200$x$200 background box size.  
+    Such model can capture the overall negative sky value, modify the median sky pixel 
+    value very close to zero, and remove flux of nearby objects that are not perfectly 
+    masked out by our object mask.
+
+    Using the background-corrected cutout image and the mask, we run \texttt{Ellipse} 
+    based on strategy very similar to \citep{Li2012}.  
+    In summary, we start with \texttt{Ellipse} run with free central position and free
+    geometry, then gradually constrain its behavior, and eventually extract 1-D 
+    surface brightness profile along the major photometric axis using isophotes with 
+    fixed center and shape.
+    The 4th Fourier modes are included to fit the isophote better. 
+    In this way, we can extract the radial changes of the photometric ``barycenter'', 
+    ellipticity, position angle, and overall isophotal shape (more ``disky'' or 
+    ``boxy'', e.g.\ \citealt{Kormendy2009}) of these galaxies at the same time.  
+    At low surface brightness regime, the final profile can be sensitive to several 
+    configuration parameters of \texttt{Ellipse}.  
+    After some tests, we choose to use 0.1 dex in logarithm as the step in semi-major 
+    axis length between successive ellipses, and we use the median pixel value over the
+    elliptical annulus after rejecting outlier pixels twice with $3\sigma$-clipping.
+    These parameters are selected to make the final profile less affected by any nearby
+    objects, and please see Appendix.~B for more details about the extraction of 
+    1-D profile. 
+    Fig.~5 shows one example of the 1-D measurement, where we also compare the profile 
+    of the galaxy with the PSF profile extracted using circular aperture.
+
+    It is worth noting that, can not extract reliable 1-D profiles for a small fraction 
+    of massive galaxies in both samples due to masked-out center that is caused by 
+    either physical (e.g.\ late-stage major merger) or unphysical (e.g.\ nearby foreground 
+    galaxy or bright star) reasons.  
+    For the physically interacting ones, it might be worth studying whether their 
+    profiles are different with the relaxed ones, but we have to rely on 2-D 
+    decomposition technique for that.
+
+    We correct the surface brightness profiles for Galactic extinction and 
+    cosmological dimming, and then integrate them to a series of radii to get the 
+    luminosity within different physical apertures.  
+    Although the 1-D profile from our $i$-band image can reach to as deep as 
+    30 \sb, we often see sudden truncation or large fluctuation of profiles 
+    at the very low surface brightness part due to uncertainty from background 
+    subtraction or contamination from other objects.  
+    Therefore, we only consider the profiles above 28.5 \sb reliable in this 
+    work.  
+    Using this conservative estimate, we can reliably estimate total luminosity 
+    within $\sim 120$ kpc aperture, which is enough for this work.
+
+    We also apply the isophotes derived on $i$-band images to other bands in 
+    ``force-photometry'' mode \texttt{Ellipse} run to get rough estimates of 
+    color profiles.  
+    Without taking the difference in seeing and background into account, 
+    these color profiles can not be used for physical discussion. 
+    But with the help of $K$-correction from the next section, we show that there 
+    is no systematic difference in color gradient between \texttt{redBCG} and 
+    \texttt{nonBCG} sample.
+
+%% ------------------------------------------------------------------------------------ %%
+
+\section{Stellar Masses and Stellar Mass Density Profiles}
+
+\subsection{Stellar Masses from SED Fitting}
+
+    As mentioned earlier, we estimate the total stellar mass and the stellar mass 
+    density profiles by applying the average \m2l of the galaxy to the 1-D luminosity 
+    profiles we just extracted. 
+    We use the broadband Spectral Energy Distributions (SEDs) fitting 
+    (see \citealt{Walcher2011} for a recent review) code 
+    \texttt{iSEDFit}\footnote{http://www.sos.siena.edu/~jmoustakas/isedfit/} 
+    (\citealt{Moustakas2013}) to estimate the average \m2l and $k$-corrections using
+    five band \cmodel photometry. 
+    The \cmodel photometry not only takes the PSF convolution into account, but 
+    also fixes the model parameters of both de~Vaucouleur and exponential components 
+    to the ones from a reference filter (mostly $i$ band) except for their amplitudes.
+    Therefore, it provides accurate \emph{average} color of the galaxy despite it tends 
+    to underestimate the total flux (e.g.\ Huang\etal~in prep.~).
+
+    \texttt{iSEDFit} takes a simplified Bayesian approach. 
+    In short, it first generates a large grid of SEDs from synthetic stellar 
+    population models by drawing randomly from the prior distributions of relevant 
+    parameters (e.g.\ age, metallicity, dust extinction, and star formation history).
+    Based on these models, it uses the observed photometry and redshift to 
+    compute the statistical likelihood, and generate the posterior probability 
+    distribution (PDF) functions of each parameter.  
+    To get the best estimate of certain parameter, \texttt{iSEDFit} ``integrates'' 
+    the full PDF over all the other ``nuisance'' parameters.
+    Then, the median value of the resulting marginalized PDF is used as the best
+    value, while the 1-$\sigma$ uncertainty is derived from the cumulative PDF.
+    Please refer to \citet{Moustakas2013} for technical details and performance of     
+    \texttt{iSEDFit}.
+
+    In this work, we derive average \m2l using the Flexible Stellar Population 
+    Synthesis\footnote{http://scholar.harvard.edu/cconroy/sps-models}
+    (FSPS; \texttt{v2.4}; \citealt{FSPS}, \citealt{Conroy2010}) model based on 
+    the MILES\footnote{http://www.iac.es/proyecto/miles/pages/stellar-libraries/miles-library.php}
+    (\citealt{MILES1}, \citealt{MILES2}) stellar library and \citet{Chabrier2003} 
+    IMF between 0.1 to 100 \msun. 
+    We use the delayed-$\tau$ model with stochastic star burst as the form of 
+    star formation history (SFH), and choose a set of reasonable parameters 
+    after some tests.  
+    Such form of SFH is appropriate for massive quiescent galaxies at low redshift 
+    (e.g.\ \citealt{Kauffmann2003}). 
+    For stellar metallicity, we assume flat distribution between 0.004 to 
+    0.03 (which is the highest metallicity allowed by FSPS models).  
+    And, the \citet{Calzetti2000} extinction law is adopted with a order two 
+    Gamma distribution of $A_{V}$ between 0 to 2 magnitude.
+    And, since most galaxies in both samples are red, quiescent galaxies, the 
+    results are not very sensitive to parameters related to SFH and internal 
+    dust extinction. 
+    To achieve reasonably good sampling across these parameters, we generate 
+    250000 models.
+
+    We construct five band SED using \cmodel magnitude corrected for the Galactic 
+    extinction. 
+    As for the photometric error, the current \texttt{cModel} photometry 
+    underestimates the flux errors of these massive galaxies as it only includes 
+    statistical error, not the systematic uncertainties from the model-fitting procedure.  
+    From tests using synthetic objects, we find that the average accuracy of 
+    \texttt{cModel} photometry at bright end is hardly better than 1\% when the 
+    systematic uncertainties are included. 
+    Therefore, we supply \texttt{iSEDFit} with simplified flux errors assuming 
+    $S/N = 100$ for $riz$ bands, and $S/N = 80$ for $gY$ bands (that typically 
+    have shallower depth and higher background noise).  
+    Given such assumption, the typical uncertainty of \logms for both samples is 
+    around 0.08 to 0.10 dex at the high-\mstar end. 
+    Please see Appendix.~B for more details about the discussion of the SED fitting
+    results.  
+    In Fig.~3, we show an example of SED fitting result. 
+    \song{Not sure if we need to show one example, but put one here for now.}
+
+\subsection{Comparison with \texttt{S82-MGC}}
+
+    Given the heterogeneous redshift resources of both samples, we further 
+    investigate the \mstar completeness issue by comparing with galaxies in the 
+    common regions with the \texttt{S82-MGC} sample. 
+    The \texttt{S82-MGC} sample matches the deeper SDSS photometric data in the 
+    Stripe 82 region (\citealt{Annis2014}) with the near infrared data from the 
+    United Kingdom Infrared Telescope Infrared Deep Sky Survey (UKIDSS; 
+    \citealt{Lawrence2007}). 
+    With the help of deeper photometry and accurate photo-$z$, the \texttt{S82-MGC}
+    sample is complete to \logms$\geq 11.2$ at $z<0.7$, making it perfect sample
+    to verify the completeness of our samples.
+
+    We match the \texttt{hscPho} sample with \texttt{S82-MGC}, and get 20453 
+    common galaxies at $0.3 < z < 0.5$ (referred as \texttt{s82Pho} sample).  
+    We estimate their stellar mass using \texttt{cModel} SED in exactly the same
+    way, and the \mstar from HSC shows good correlation with the 
+    \texttt{S82-MGC} SED (five optical bands from SDSS and NIR data from UKIDSS)
+    fitting \mstar (\texttt{S82-MGC} also used \texttt{iSEDFit}, with slightly 
+    different priors).  
+    Then we estimate the volume densities distributions of galaxies in 
+    \texttt{redBCG}, \texttt{nonBCG}, and \texttt{s82Pho} samples (Fig.~4)
+    using rough values of the survey areas they occupied 
+    (as we only care about the relative shapes of the density distributions). 
+    %We also estimate the uncertainties of these distributions by bootstrap resampling 
+    %the PDF of \logms 10000 times. 
+    The distribution of \texttt{nonBCG} sample starts to deviates from the 
+    \texttt{s82Pho} one below \logms$< 11.6$, indicating that the sample starts 
+    to become incomplete within $0.3 < z < 0.5$. 
+    As for the \texttt{redBCG} sample, their mass completeness should be better 
+    thanks to the reliable $z_{\lambda}$ from \redm{} catalog; and its log-normal 
+    behaviour is consistent with the mass function of galaxies located in a 
+    narrow halo mass bin (\addref).   
+    After accounting for the correction for total luminosity, this suggests that
+    at least the \texttt{nonBCG} sample is not perfectly complete below 
+    \logms$< 11.7$.  
+    This is most likely due to the incompleteness of the BOSS spec-$z$ sample.
+    Although it is unlikely that such incompleteness will bias the results of 
+    our comparisons, we will bear this in mind, and match the two samples 
+    carefully in \logms and redshift space before comparing them.
+
+\subsection{Stellar Mass Corrected for Total Luminosity}
+
+    Using the best-fit stellar mass from \texttt{iSEDFit} (referred as \mcmodel), 
+    we estimate the average \m2l in $i$-band, then use that \m2l to convert the 
+    1-D luminosity density profiles into stellar mass density profiles; and 
+    also convert the luminosity within 10 and 100 kpc apertures into 
+    corresponding stellar mass estimates (referred as \minn and \mtot). 
+    From now, we use \mtot as the new proxy of ``total'' stellar mass of these 
+    galaxies.  
+    And we also derive the $k$-corrected luminosity and colors from the results.
+    In Appendix.~B, we also show the outputs like the average stellar age, 
+    metallicity, and internal dust extinction all behave reasonably for both 
+    samples, but will not use them for further scientific analysis.
+
+    As expected, the integration of 1-D profile out to very large radius help 
+    recover more luminosity (stellar mass) compared to the \cmodel results.
+    We highlight this in the left panel of Fig.~5 as we show the distributions 
+    of differences between \mtot and \mcmodel, and their relations to the \mtot.  
+    For both samples, we see the ``extra mass'' recovered by 1-D photometry 
+    increases with \mtot, therefore this improvement impacts the \texttt{redBCG}
+    sample more.  
+    This is basically consistent with the fact that the structure of massive ETGs 
+    depends on its stellar mass in a way that more massive ones tends to be 
+    more extended (e.g.\ \addref).  
+    Apparently, such mass-dependent difference between \mtot and \mcmodel will 
+    result in difference of the SMF. 
+    As the slope and normalization of SMF at high mass end is very sensitive 
+    to both cosmology and interesting baryonic processes such as AGN feedback
+    (\addref), they are particularly important in constraining the galaxy evolution
+    model, and therefore became the center of some intense arguments (\addref).  
+    Although the jury is still out on this topic, it has become clear that 
+    popular results using SDSS photometry (\addref) underestimate the total 
+    luminosity (stellar mass) of massive ETGs.  
+    However, past works (e.g.\ \addref) often relied on either stacking of 
+    shallow images or the extrapolation of models to investigate this effect. 
+    Using the deep HSC images, we have the potential to answer this question 
+    much better. 
+    Detailed studies of SMF deserves more careful investigations of many 
+    systematic issues (e.g.\ \addref), so we just show the impact of the 
+    ``extra mass'' on the volume density distributions of both samples 
+    (Fig.~5, right panel).  
+    Generally speaking, the stellar mass corrected for total luminosity 
+    shifts the distribution toward the higher mass end, and slightly modify
+    the slope. 
+    People who want to use HSC photometry or other \cmodel-like photometry to 
+    study the properties and evolution of SMF should be aware of such effect.
+
+    As mentioned earlier, our assumption of using an average \m2l ignores its
+    radial variation.   
+    It is well known that massive ETGs have negative optical color gradient which 
+    indicates a gradient of \m2l (e.g.\ \citealt{LaBarbera2012}; \citealt{DSouza2015}),
+    but the gradient is smooth and shallow out to a few times of the effective 
+    radius (color gradient at the very outskirt is still not well quantified). 
+    And, for the comparison between the \texttt{redBCG} and \texttt{nonBCG} samples, 
+    Our results should remain intact as long as there is no significant
+    differences of color gradient between these two samples.
+    We will discuss this more later, but initial results do suggest a smooth color
+    gradient out to very large radius, and there is no systematic difference in 
+    color gradients of the two samples.  
+    Both suggest that the average \m2l approach should work reasonably well for
+    our goals.
+    And, we should mention that our approach is in principle very similar to the 
+    method adopted by the GAMA survey (\citealt{Taylor2011}), where the average 
+    \m2l comes from SED fitting of PSF-matched aperture photometry while the 
+    more accurate total luminosity relies on multi-band \ser model fitting 
+    (\citealt{Kelvin2012}).
+
+    \todo{Since we put 1-D profile in front of this section, we need to have a 
+    summary of the final samples, as a fraction of them does not have 1-D profile.}
+
+    In Fig.~5, we show the \mtot-color relations using both $k$-corrected $g-r$ 
+    and $g-z$ colors for \texttt{redBCG} and \texttt{nonBCG} samples. 
+    Both samples follow the same tight red-sequence without much contamination 
+    from the ``blue cloud''.
+    At fixed \mtot, not apparent offset is seen in the distributions of optical
+    colors between the two samples, which suggests both samples come from old, 
+    quiescent galaxies with similar stellar population.  
+    This is also consistent with the work that found the average stellar 
+    population of massive central galaxy does not depends on halo mass 
+    (e.g.\ \citealt{Park2007}).  
+    To look into the potential environmental dependence of structure, we will 
+    focus on the mass range of $11.6 \le$\mtot$\le 11.9$, where both samples 
+    should have reasonable completeness, and the mass distributions of the two 
+    samples overlap the most.  
+    Within this \mtot range, the \texttt{redBCG} and \texttt{nonBCG} samples 
+    still show difference in their redshift distributions.  
+    We will address this before we compare their average stellar mass 
+    density profiles.
+
+%% ------------------------------------------------------------------------------------ %%
 
@@
 
+\subsection{$M_{\ast}-$Size Relations}
+
+    As most of the past works on the environmental dependence of structures for 
+    massive galaxies often focus on the scaling relation between stellar mass
+    and effective radius (or half-light radius, e.g.\ \addref), we first show 
+    similar relations for both \texttt{redBCG} and \texttt{nonBCG} samples
+    (Fig.~8, upper panel), and compare them with the relation for central 
+    galaxies in \citealt{HCompany13} (HC13) at $z<0.09$, also with the relation 
+    from \citealt{vanderWel2014} (vdW14) for ETGs at $z\sim 0.25$ using HST.
+
+    Since we do not perform model fitting, the half-light radius 
+    ($R_{\mathrm{50}}$) is defined as the radius along the major axis that 
+    encloses 50\% of luminosity within 100 kpc, and is derived using the 
+    luminosity curve-of-growth. 
+    In principle, the 1-D estimate of R50 is uncertain due to PSF smearing 
+    effect and the choice of maximum luminosity radius. 
+    In cases of the very massive ETGs in our samples, their $R_{\mathrm{50}}$ 
+    are large enough to avoid the influence of PSF; and, as the luminosity 
+    profiles at 100 kpc already reach to very low surface brightness, the 
+    $R_{\mathrm{50}}$ is quite stable using slightly different definition of 
+    maximum luminosity (we explored luminosity within 120, 150 kpc, and within 
+    the maximum radius of the profiles, the results are the same). 
+    At the same time, comparing with $R_{\mathrm{e}}$ extracted from 2-D 
+    models, the 1-D $R_{\mathrm{50}}$ has the advantage of being less sensitive 
+    to the background subtraction uncertainty, and independent of the choice 
+    of model.
+
+    Both HC13 and vdW14 estimate $R_{\mathrm{e}}$ using 2-D single-\ser model 
+    fitting to SDSS and HST images; and their stellar masses are derived from 
+    SED fitting using BC03 (\citealt{BC03}) synthetic population model. 
+    vdW14 assumed the same Chabrier IMF while HC13 used the Kroupa IMF. 
+    We empirically correct the systematic caused by different IMF choices by 
+    applying a -0.03 dex shift.  
+    As shown in Appendix.~B, we noticed an average 0.1 dex decrease of stellar 
+    mass when using BC03 model instead of the FSPS one, therefore, we also 
+    increase the stellar masses in HC13 and vdW14 accordingly. 
+    Despite these differences, the mass-size relations for both \texttt{redBCG} 
+    and \texttt{nonBCG} follow the relation from HC13 with a very similar 
+    slope.
+    The relation from vdW14 shows a clear offset that could be caused by 
+    systematics in measurements of both stellar mass and effective radius, 
+    The important point is that, just like many previous results, the central 
+    galaxies from lower- and higher-mass halos seem to follow very similar 
+    mass-size relation\footnote{Limited by the narrow mass range and the small
+    sample size of \texttt{redBCG}, we do not attempt to fit the relations}.  
+    This seems to reinforce the view that, at low redshift, environment 
+    plays a marginal (if there is any) role in determining the structure
+    of massive galaxies.
+
+    However, as we mentioned in the introduction, the lack of difference on
+    the mass-size relation could be caused by 
+    (1) insufficient depth of the image; 
+    (2) that effective radius is a biased parameter that can not reflect the 
+    subtle environmental dependence.  
+    The deep HSC images should solve problem (1), but we still need to 
+    rule out the second possibility by looking into more structural details.
+
+\subsection{Comparison of Surface Mass Density Profiles}
+
+\subsubsection{Internal Comparison and Comparison with Previous Works}
+
+    Compared to the scaling relations, the stellar mass density profiles 
+    contain more useful structural details that can help us diagnose the 
+    environmental effect.  
+    Before the actual comparisons, we first show the general properties 
+    of these 1-D profiles by separating both samples into different bins 
+    of \mtot and redshift, also by comparing them with results from 
+    literature (Fig.~9).   
+    For profiles in each bin, we derive the median profile along with its 
+    uncertainty using bootstrap resampling method (5000 times). 
+    The left panel of Fig.~9 focuses on different mass bins.  
+    As expected, for both samples, higher \mtot moves the median mass 
+    density profile upward a little in the inner region, but makes it 
+    more extended in the outer part.
+    In the mass range we explored ($\ge 10^{11.2} M_{\odot}$), most of these 
+    ETGs are slow-rotating (e.g.\ \citealt{Cappellari13b}) giant ellipticals 
+    with boxy inner isophotal shape (e.g.\ \citealt{Kormendy2009}), and 
+    flattened density profile at the center (e.g.\ \citealt{Lauer07}), 
+    but their structure in the outskirt clearly does \textbf{NOT} response 
+    to stellar mass increase in a self-similar way.
+
+    In principe, this is consistent with result from HST observations of 
+    BCGs at $0.3 < z <0.9$ (\citealt{Bai2014}) and the claimed positive 
+    correlation between luminosity and \ser index
+    (e.g.\ \citealt{Savorgnan13})\footnote{But it does not mean such high 
+    \ser index model works well for massive ETGs as they fail at the inner-most 
+    region dramatically, and can not explain the radial variation of 
+    isophotal shape}; it is also consistent with the picture that more 
+    massive ETGs experienced more recent (minor) mergers.
+
+    At the same time, such behaviour should make us very cautious about 
+    any indication of ``environmental dependence of structure'' as it 
+    may be degenerate with difference caused by stellar mass when the 
+    two samples are not perfectly matched in mass.  
+    This is exactly what we see in the median profiles of \texttt{redBCG}
+    and \texttt{nonBCG} in the same mass bins. 
+    Although the comparison shows that \texttt{redBCG} shows much more 
+    extended outer envelope than \texttt{nonBCG}, the very similar profile
+    in the inner $\sim 10$ kpc reveals that this is dominated by the 
+    different mass distributions in two samples.
+
+    In the middle panel of Fig.~9, we compare these median profiles with 
+    a few past works.  
+    \citep{Huang2013a}, derived the median stellar mass density profile 
+    for a small sample of very nearby ellipticals from the 
+    Carnegie-Irvine Galaxy Survey (CGS, \citealt{CGS1}).
+    Individual profile and total luminosity were derived from 
+    three-component 2-D models that describe both very inner and outer 
+    luminosity distributions of these galaxies accurately. 
+    The average stellar mass of this sample is around $10^{11.3} M_{\odot}$.
+    Due to the proximity of this sample ($< 100$ Mpc), the average profile 
+    is unaffected by seeing within $\sim 1$ kpc.
+    Most galaxies of the CGS sample are not in any cluster.
+    The median profile qualitatively agrees with the median profile of 
+    \texttt{nonBCG} in the low mass bin, especially in the inner region. 
+    Outside the inner 15 kpc, the CGS median profile shows a slightly more
+    prominent outer envelope.  
+    While this could simply reflect the small size of CGS sample ($\sim 30$),
+    interestingly, it is also consistent with the expectation if the 
+    mild mass growth from $z\sim 0.4$ mostly happened at the outskirt.   
+    The CGS images are already slightly deeper than SDSS images in $r$-band,
+    however, the median profile can only reach to $\sim 50$ kpc (with much 
+    larger uncertainty compared to this work) for ETGs within $\sim 100$ Mpc.
+    Such comparison clearly highlights the improvement made by the deep HSC 
+    images as individual profile of $z\sim 0.5$ galaxy is reliable out to 
+    at least 100 kpc.
+
+    At the similar redshift with our sample, we compare with mass density 
+    profile extracted from stacked images of massive ETGs at $0.25 < z < 0.50$ 
+    using HST/ACS images (\citealt{Patel2013}).  
+    These galaxies are selected at constant cumulative number density, and 
+    as progenitors of $z=0$ massive ETGs.  
+    The average stellar mass is $\sim 10^{11.2} M_{\odot}$ according to 
+    their estimates.  
+    However, given the shallower depth of the ACS images and the usage of the 
+    BC03 model (each could cause -0.1 dex mass offset compared to this work), 
+    this sample should be comparable to the \texttt{nonBCG} sample in the
+    lowest mass bin, and the comparison of their median profiles does reflect
+    that.  
+    Moreover, since the profile from HST/ACS image is not bothered by PSF 
+    within 1 Kpc, the comparison illustrates that the HSC median profiles 
+    in our redshift range are indeed not affected by seeing outside the 
+    shaded region. 
+    In fact, as we suggested, our estimate is quite conservative, the profiles 
+    within 5 kpc should be reliable.
+
+    Besides these observations, we also compare with the predicted average 
+    stellar mass density profile for central galaxies of massive halos 
+    ($13.5 < \log M_{200,c} < 14.0$) in simulation (\citealt{Cooper13}). 
+    This is achieved by combining the detailed assembly information of halos 
+    from dark-matter-only simulation with semi-analytic model and 
+    particle-tagging technique (\citealt{Cooper10}).
+    Although the physical resolution and detailed baryonic processes are 
+    not as ``realistic'' as state-of-art hydro-simulation, it is very 
+    efficient in providing rough stellar mass distributions for large number 
+    of massive halos. 
+    Without any adjustment, the profile is quite similar to the \texttt{nonBCG}
+    sample in the $11.5 < \log M_{\star} < 11.7$ bin within inner 20 kpc; 
+    but it predicts a too significant outer envelope for its average halo mass.
+    Without going into details to find the cause of such discrepancy in this 
+    work, the comparison already suggests that the comparison between deep 
+    observed mass density profiles with the ones from modern simulations is 
+    going to be quite interesting, especially in the outskirt.
+
+    The right panel of Fig.~9 focus on the impact of redshift distribution
+    by grouping the $11.6 \le \log M_{\star} < 11.9$ \texttt{redBCG} and 
+    \texttt{nonBCG} into two redshift bins.  
+    Under the same seeing condition, galaxy at higher redshift suffers 
+    more from PSF smearing effect in the central region; and the cosmological 
+    dimming of surface brightness also makes the outer region more difficult 
+    to measure.
+    As shown here, although the median profiles of the same sample in two 
+    redshift bins follow each other very well at the outer part, they 
+    start to differ in the central region as the one from higher redshift bin
+    ends up with a more flattened profile compared to the one for lower 
+    redshift bin. 
+    In the same redshift bin, median profiles of \texttt{redBCG} and 
+    \texttt{nonBCG} are very similar in the region affected by seeing.   
+    Therefore, when comparing structures of massive galaxies using 
+    ground-base images, it is also important to make sure different samples 
+    share similar redshift distributions.
+
+\subsubsection{Matched Samples Using $M_{\star}$ from the GAMA survey}
+
+    As the sky coverage of this release greatly overlaps with the GAMA survey,
+    we start the detailed comparison with an external check using the stellar
+    mass estimated by \citep{Taylor2011}. 
+    The purpose is still to investigate the impact of deeper photometry on 
+    the analysis of structure of massive galaxies.  
+    The stellar masses of GAMA galaxies are initially derived through careful 
+    optical-SED fitting (BC03 model; Chabrier IMF) using the PSF-matched 
+    aperture photometry.  
+    Then they were corrected for the total luminosity estimated using single-\ser 
+    2-D model to multi-band images (\citealt{Kelvin2012}).  
+    We separate the \texttt{redBCG} and \texttt{nonBCG} galaxies that also have 
+    spec-$z$ and stellar mass in GAMA DR2 (\citealt{Liske2015}).
+    Most of galaxies in these subsamples have $z < 0.40$.
+
+    To compare the median mass density profiles of these two subsamples, we 
+    need to make sure that they share as similar as possible distributions in 
+    at least stellar mass ($M_{\star, \mathrm{GAMA}}$) and redshift. 
+    To achieve this, we match the \texttt{redBCG} sample that always has 
+    smaller size to the \texttt{nonBCG} galaxies by searching for the $N$ 
+    nearest neighbours on the $M_{\star, \mathrm{GAMA}}$-$z$ plane using the
+    KDTree algorithm provided by \texttt{scikit-learn} Python package 
+    (\citealt{scikit-learn}). 
+    As we only keep unique \texttt{nonBCG} galaxy in the matched sample, 
+    we manually adjust the value of $N$ to achieve the most similar distribution. 
+    In case that the distribution of mass or redshift for \texttt{redBCG} is 
+    bi-model, we also try to split the sample into two, and match them separately.
+    Normally $N$ is between 3 to 8.
+
+    In Fig.~10, we show the results of matches for subsamples using 
+    $M_{\star, \mathrm{GAMA}}$.  
+    To increase the number of available \texttt{redBCG} to match, we loosen 
+    its selection criteria to $\lambda \ge 20$ and $P_{\mathrm{CEN}} \ge 0.6$.
+    Based on the distributions of the two samples at the $M_{\star, \mathrm{GAMA}}$-$z$ 
+    plane, and their overlapped region, we match them in two bins of 
+    $M_{\star, \mathrm{GAMA}}$ that have slightly different redshift ranges. 
+    Besides the 2-D distributions, we also use the histograms and kernel 
+    density distributions (KDE) of mass and redshift, along with their median values 
+    and interquartile ranges to evaluate the similarity between the samples. 
+    For stellar mass, its KDE is generated using a Gaussian kernel with width 
+    equals to the typical uncertainty of the mass estimate (0.06-0.10); and 
+    for redshift, we choose 0.025 as the width of the Gaussian kernel. 
+    For the samples in two $M_{\star, \mathrm{GAMA}}$, the matches appear to be
+    very good.  
+    We also check the distributions of $k$-corrected optical colors of the two 
+    samples, just to confirm that their average colors are similar as while.
+
+    In Fig.~11, we show the individual profiles, median profiles along with their 
+    uncertainties derived using 5000 times bootstrap resampling, and the relative 
+    difference between the profile of the \texttt{redBCG} and \texttt{nonBCG} 
+    subsamples.  
+    It is very clear that, for both mass bins, the \texttt{redBCG} has a much 
+    more extended outer envelope, while its profile inside $\sim 10$ kpc is 
+    very close to the \texttt{nonBCG} one.  
+    This is inconsistent with the matched distributions of their ``total'' 
+    stellar mass, and reveals potential issue with the stellar mass estimated 
+    by GAMA.
+    We can reproduce very similar results using the luminosity density profiles 
+    (with or without $k$-correction) of these matched samples, which suggests 
+    that the main problem does not lie in the estimate of \m2l, but in the 
+    measurement of total luminosity using single-\ser model.
+
+    This highlights the importance of deep optical images in studying the 
+    structure of massive galaxies.
+
+    As both estimates of $M_{\star, \mathrm{GAMA}}$ and $\lambda$ can have 
+    noticeable uncertainty, the sizes of both samples are quite small, and 
+    the distributions of individual profile in two samples overlap even in the
+    outskirt, we also perform a simple statistical test to prove the significance 
+    of the differences between the profiles.  
+    Assuming that there are $N_{\mathrm{r}}$ \texttt{redBCG} and 
+    $N_{\mathrm{n}}$ \texttt{nonBCG}, we put these two samples together, and 
+    randomly draw $N_{\mathrm{r}}$ galaxies with putting-back from the mixed 
+    sample; then we compute the difference between the median profile of the
+    random sample and the one for original \texttt{nonBCG} sample; repeat this 
+    procedure 2000 times so that it can provide us the statistical distribution 
+    of the difference. 
+    In cases of these $M_{\star, \mathrm{GAMA}}$-matched samples, the differences
+    of median profiles are very robust.
+
+\subsubsection{Matched Samples Using \mtot}
+
+    Finally, we....
+
+\subsubsection{Matched Samples Using \minn}
+
+\subsection{Relations between stellar mass within different physical apertures}
+
+%% ------------------------------------------------------------------------------------ %%
+
 \section{Discussion}
 
-\section{Summary}
+\subsection{The Impact of $M/L$ Gradient}
 
-%%%%%%%%%%: Acknowledge %%%%%%%%%%
+\subsection{Ellipticity Profiles}
+
+\subsection{Massive Satellites of the $\lambda > 20$ Haloes}
+\song{TBD:optional}
+
+\subsection{Implications on Assembly History of Massive Galaxies}
+
+    \plan{Comparison of mass profiles with previous studies at high redshift}
+
+\subsection{\mstar and Structural Evolution between $0.3 < z < 0.5$}
+
+\subsection{Impact from ``Fossil Galaxies''}
+
+    ``Fossil galaxy'' is the most massive galaxy in a ``fossil group/cluster''
+    system.
+    According to the commonly adopted definition, ``fossil'' systems are the 
+    group or cluster with high X-ray luminosity and large magnitude gap between 
+    the two brightest galaxies (\addref: Ponman1994; Jones2003). 
+    Both observations and simulations suggest that they could represent the 
+    final stage of the hierarchical merging process in a group/cluster mass
+    halo that is formed at very early epoch (e.g.\ \addref: 
+    Khosroshahi2004, 2007; DOnghia2005; Dariush2007).
+    Under this interpretation, at fixed halo mass, the central galaxy of 
+    a fossil system typically has larger stellar mass than the one in normal 
+    system (e.g.\ Harrison2012), as it has ``consumed'' most satellites 
+    early on; 
+    However, the ``low richness'' of a fossil system makes it difficult for 
+    red-sequence finder like \redm~to reliably identify 
+    (e.g.\ Figure~17 of Sadibekova2014).  
+    If some massive ETGs in our \texttt{nonBCG} sample are actual the centrals 
+    galaxies of fossil clusters, it could bias our conclusions about the 
+    relation between strucutre and ``environment''.
+
+    Although it is possible that fossil systems formed earlier than normal 
+    clusters, the difference in detailed merging history is still unclear, 
+    hence it is hard to imagine the structural differences between fossil 
+    central galaxies and regular BCGs with same \mstar.  
+    Naively speaking, more frequent mergers for fossil centrals should result 
+    in more extended stellar envelope.  
+    However, the distributions of epoch and mass-ratio of those mergers also 
+    matter.
+
+    The lack of any difference in stellar population properties may suggest 
+    It is still not clear how the mass assembly history of fossil central
+
+\subsection{Potential Impact from the Intra-Cluster/Group Light}
+
+    As the \rbcg\ sample moves into the galaxy cluster regime in term of halo 
+    mass, it is inevitable to discuss the impact of the (in)famous
+    intra-cluster light component to our results.
+
+%% ------------------------------------------------------------------------------------ %%
+
+\section{Summary and Future Plans}
+
+    With the help of the high quality, deep optical images provided by the 
+    HSC survey,
+
+\subsection{Future improvements}
+
+    \begin{enumerate}
+        \item \plan{Improvements of HSC data reduction: better sky modeling; 
+            \texttt{redMaPPer} clusters using HSC photometry.}
+        \item \plan{Comparison with 2-D image modeling method.}
+        \item \plan{``Correct'' the PSF smearing effect at the center with the help of 
+            residual correct 2-D model.}
+    \end{enumerate}
+
+%% ------------------------------------------------------------------------------------ %%
 
 \acknowledgements
-
-  1. Acknowledgements for HSC 
-  2. Acknowledgements for Kevin and Alexie's funding 
-  3. Acknowledgements for the Python libraries
+  The Hyper Suprime-Cam (HSC) collaboration includes the astronomical communities of Japan
+  and Taiwan, and Princeton University.  The HSC instrumentation and software were
+  developed by the National Astronomical Observatory of Japan (NAOJ), the Kavli Institute
+  for the Physics and Mathematics of the Universe (Kavli IPMU), the University of Tokyo,
+  the High Energy Accelerator Research Organization (KEK), the Academia Sinica Institute
+  for Astronomy and Astrophysics in Taiwan (ASIAA), and Princeton University.  Funding was
+  contributed by the FIRST program from Japanese Cabinet Office, the Ministry of
+  Education, Culture, Sports, Science and Technology (MEXT), the Japan Society for the
+  Promotion of Science (JSPS),  Japan Science and Technology Agency (JST),  the Toray
+  Science  Foundation, NAOJ, Kavli IPMU, KEK, ASIAA,  and Princeton University.
 
   Funding for SDSS-III has been provided by the Alfred P. Sloan Foundation, the
-  Participating Institutions, the National Science Foundation, and the U.S.
-  Department of Energy. The SDSS-III web site is http://www.sdss3.org.  SDSS-III
-  is managed by the Astrophysical Research Consortium for the Participating
-  Institutions of the SDSS-III Collaboration including the University of
-  Arizona, the Brazilian Participation Group, Brookhaven National Laboratory,
-  University of Cambridge, University of Florida, the French Participation
-  Group, the German Participation Group, the Instituto de Astrofisica de
-  Canarias, the Michigan State/Notre Dame/JINA Participation Group, Johns
-  Hopkins University, Lawrence Berkeley National Laboratory, Max Planck
-  Institute for Astrophysics, New Mexico State University, New York University,
-  Ohio State University, Pennsylvania State University, University of
-  Portsmouth, Princeton University, the Spanish Participation Group, University
-  of Tokyo, University of Utah, Vanderbilt University, University of Virginia,
-  University of Washington, and Yale University.
+  Participating Institutions, the National Science Foundation, and the U.S.  Department of
+  Energy. The SDSS-III web site is http://www.sdss3.org.  SDSS-III is managed by the
+  Astrophysical Research Consortium for the Participating Institutions of the SDSS-III
+  Collaboration including the University of Arizona, the Brazilian Participation Group,
+  Brookhaven National Laboratory, University of Cambridge, University of Florida, the
+  French Participation Group, the German Participation Group, the Instituto de Astrofisica
+  de Canarias, the Michigan State/Notre Dame/JINA Participation Group, Johns Hopkins
+  University, Lawrence Berkeley National Laboratory, Max Planck Institute for
+  Astrophysics, New Mexico State University, New York University, Ohio State University,
+  Pennsylvania State University, University of Portsmouth, Princeton University, the
+  Spanish Participation Group, University of Tokyo, University of Utah, Vanderbilt
+  University, University of Virginia, University of Washington, and Yale University.
 
-%%%%%%%%%%: Bibligraphic Section %%%%%%%%%%
+  \todo{Full acknowledgement}\\
+  \begin{itemize}
+      \item \plan{Acknowledgements for Kevin and Alexie's funding}
+      \item \plan{Acknowledgements for the Python libraries}
+  \end{itemize}
 
-%\begin{thebibliography}{}
+  This research made use of 
+  \href{http://www.astropy.org/}{Astropy}, a community-developed 
+      core Python package for Astronomy (\citealt{astropy13}); 
+  \href{http://scikit-learn.org/stable/index.html}{scikit-learn},
+      a machine-learning library in Python (\citealt{scikit-learn}) 
+  \href{https://github.com/kbarbary/sep}{sep} 
+      Source Extraction and Photometry in Python (\citealt{PythonSEP}).
 
-  %\bibitem[Arnold et al.(2011)]{2011ApJ...736L..26A} Arnold, J.~A., Romanowsky,
-    %A.~J., Brodie, J.~P., et al.\ 2011, \apjl, 736, LL26
-
-%\end{thebibliography}{}
+%%%%%%%%%%: Bibliographic Section %%%%%%%%%%
 
@@
 
-\section{A. Atlas of 1-D Profiles}
+\section{A. Extraction of 1-D surface brightness profile}
+
+\section{B. Derive average mass-to-light ratio using \texttt{iSEDFit}}
+
+    We adopt flat distribution between 0.5 to 14.0 Gyrs as prior for the look-back 
+    time when the star formation turned on. 
+    The exponential delayed time-scale ($\tau$) is allowed to change between 
+    0.1 to 3.0 with equal probability.  
+    The chance of random star burst is set at 0.2 for every 2 Gyrs. 
+    The duration of the star burst is draw from a logarithmic distribution 
+    between 0.03 to 0.3 Gyr; and the mass fraction formed in the burst is from 
+    a logarithmic distribution between 0.01 and 1.0.
+
+    In principle, these choices of priors could leave systematic effects in 
+    the estimate of stellar mass (e.g.\ \citealt{Bernardi2016b}). 
+    For low-$z$ massive ETGs like the ones in our sample, the details form of 
+    SFH, importance of random star burst, and the dust extinction should not be 
+    major concern.  
+    However, the choices of stellar population models and IMF can still 
+    change the results systematically. 
+    More discussions on this can be found in Appendix~A. 
+    In short: 
+    \begin{enumerate}
+        \item Both \texttt{FSPS+MILES} and \texttt{BC03} (\citealt{BC03} models 
+            still have difficulties recovering the optical color involving filters 
+            at the red end (e.g~$i-$Y), which could relate to the challenge for 
+            modern stellar population models to reproduce the optical color-color 
+            relation of red-sequence galaxies (e.g.\ \citealt{MIUSCAT2}), or the 
+            shallower photometry of HSC-Y band data. 
+        \item The \texttt{BC03} provides slightly better overall ${\chi}^2$ and 
+            systematically smaller \mstar than the \texttt{FSPS+MILES} models.  
+            However, it is possible that the \texttt{BC03} model tends to 
+            underestimate the \m2l for a fraction of them as the estimate 
+            stellar age is unrealistically young for red, massive galaxies.  
+            Therefore, we still use the \texttt{FSPS+MILES} model as the fiducial 
+            one.  But, switching to the \texttt{BC03} model will not change any 
+            key result in this work. 
+        \item The usage of \citet{Salpeter1955} IMF results in systematically 
+            higher \mstar (on average $+0.25$ dex of \logms).  
+            Although there are multiple lines of evidence that favor Salpeter 
+            or even more ``bottom-heavy'' IMF in the most massive ETGs 
+            (e.g.\ \citealt{Conroy2012}; \citealt{Cappellari2012}), we still 
+            present the main results using Chabrier IMF to accommodate galaxies 
+            with lower \mstar in the sample, and to be as consistent as possible 
+            with a few other works.  
+            Also, the choice of IMF does not impact our results qualitatively.     
+    \end{enumerate}
+
+    Besides the priors for stellar population properties, different treatments of 
+    the light profile and accuracy of sky background subtraction are also important
+    for the estimate of \mstar as they strongly impact the estimate of total luminosity
+    (e.g.\ \citealt{Bernardi2013} and \citealt{DSouza2015}).  
+    At the depth of SDSS, the default \texttt{cModel} photometry is already shown to 
+    be not very accurate at high-\mstar end (e.g.\ \citealt{Meert2015}; 
+    \citealt{Bernardi2016a}) as it does not capture the extended envelope of these 
+    galaxies. 
+    As for HSC, it is much more challenging for \texttt{cModel} to recover the total 
+    luminosity of massive ETGs since the stellar envelope becomes even more 
+    extended for neither de~Vaucouleur or exponential model to reproduce.  
+    However, the HSC \texttt{cModel} under the force-photometry mode can measure 
+    \textbf{average} color of the galaxy with great accuracy (e.g.\ Huang\etal~in prep.~), 
+    and provide us a reliable SED to estimate the \textbf{average} \m2l. 
+    Considering this, we separate the process of estimating the total \mstar of 
+    massive ETGs in our sample into two steps:
+
+    \begin{enumerate}
+        \item Firstly, using the redshift and \texttt{cModel} magnitude in five bands, 
+            we derive an initial estimate of the \mstar of the galaxy.  
+            More importantly, we derive the \textbf{average} \m2l in $i$-band of the 
+            galaxy, and use the best-fit SED to provide $k$-correction to the photometry.  
+        \item In the next section, we will derive better estimate of total \mstar using 
+            the more accurate total luminosity in $i$-band from integration of carefully 
+            measured 1-D surface brightness profile, and the average \m2l from the SED
+            fitting.  
+    \end{enumerate}
+
+    The basic results from \texttt{iSEDFit} are summarized in Figure~2, where we compare
+    the relations between initial estimates of \mstar and (both luminosity and 
+    star formation weighted) stellar age, metallicity, and dust extinction. 
+    As expected, most galaxies in our samples are 
+    $\log(M_{\star,\ \mathrm{ini}}/M_{\odot}) \geq 11.2$ massive galaxies that have 
+    old age, high metallicity ($1.5 \times Z_{\odot}$ is the highest metallicity allowed), 
+    and low dust extinction.  
+    Given that we only have photometry from five optical bands, degeneracies among 
+    age, metallicity, and dust extinction are naturally expected.  
+    We will not use them for any scientific reason in this work, but to show that they
+    behave reasonably.
 
@@
     \centering 
-    \includegraphics[width=16.5cm]{fig/fig1.png}
-    \caption{
-   Cartoons that illustrate the basic idea of the proposed method for the
-   estimation of average merger mass ratio.  The style is adopted from Faber\etal (2007).
-   The upper panels show the basic
-   picture of the ``two-phase'' formation scenario. The lower panel describes
-   a general picture for the evolution of massive galaxies on the
-   $M_{\ast}$-color plane.  After massive ETGs were quenched, they quickly
-   moved to the red-sequence, and gradually evolved along it as they are
-   becoming redder due to the aging of stellar population, and more massive due
-   to the accumulation of extended stellar envelope through many minor (dry)
-   mergers.  Since the stellar content of smaller system should have lower
-   metallicity, the outer envelope naturally has a bluer color compared to inner
-   region.  And, such color difference reflects the average mass ratio of all
-   mergers that contribute to the second phase of evolution.  Larger color
-   difference means more stellar material came from smaller galaxies, hence
-   makes minor merger more important.  
-   }
-   \label{figure:1}
+    \includegraphics[width=15.5cm]{fig/redbcg_color.png}
+    \caption{\todo{Remake this figure}: Comparison of RGB 3-color images 
+    of nearby massive elliptical galaxies using SDSS and HSC images.  
+    The images are generated using $gri$ band images according to the algorithm 
+    of \citep{Lupton2004} with arcsinh stretch.  
+    It is clear that the depth of HSC image help map the stellar distributions 
+    out to much larger radius, and revel more details in the outskirts compared 
+    to the SDSS ones.}\label{figure:1}
+\end{figure}
+
+% Fig. 2
+\clearpage
+\figurenum{2}
+\begin{figure}
+    \centering 
+    \includegraphics[width=15.5cm]{fig/redbcg_ellipse_example.png}
+    \caption{Figure.2\todo{Caption}}\label{figure:2}
+\end{figure}
+
+% Fig. 3
+\clearpage
+\figurenum{3}
+\begin{figure}
+    \centering 
+    \includegraphics[width=10.5cm]{fig/redbcg_isedfit_example}
+    \caption{Figure.3\todo{Caption}}\label{figure:3}
+\end{figure}
+
+% Fig. 4
+\clearpage
+\figurenum{4}
+\begin{figure}
+    \centering 
+    \includegraphics[width=14.5cm]{fig/redbcg_hsc_s82}
+    \caption{Figure.4\todo{Caption}}\label{figure:4}
+\end{figure}
+
+% Fig. 5
+\clearpage
+\figurenum{5}
+\begin{figure}
+    \centering 
+    \includegraphics[width=18.5cm]{fig/redbcg_lf_smf}
+    \caption{Figure.5\todo{Caption}}\label{figure:5}
+\end{figure}
+
+% Fig. 6
+\clearpage
+\figurenum{6}
+\begin{figure}
+    \centering 
+    \includegraphics[width=12.5cm]{fig/redbcg_mass_color}
+    \caption{Figure.6\todo{Caption}}\label{figure:6}
+\end{figure}
+
+% Fig. 7
+\clearpage
+\figurenum{7}
+\begin{figure}
+    \centering 
+    \includegraphics[width=12.5cm]{fig/redbcg_mass_z_hist}
+    \caption{Figure.7\todo{Caption}}\label{figure:7}
+\end{figure}
+
+% Fig. 8
+\clearpage
+\figurenum{8}
+\begin{figure}
+    \centering 
+    \includegraphics[width=14.0cm]{fig/redbcg_mass_r50}
+    \caption{Figure.8\todo{Caption}}\label{figure:8}
+\end{figure}
+
+% Fig. 9
+\clearpage
+\figurenum{9}
+\begin{figure}
+    \centering 
+    \includegraphics[width=18.5cm]{fig/redbcg_avg_prof}
+    \caption{Figure.9\todo{Caption}}\label{figure:9}
+\end{figure}
+
+% Fig. 10
+\clearpage
+\figurenum{10}
+\begin{figure}
+    \centering 
+    \includegraphics[width=16.0cm]{fig/redbcg_prof_gama_1}
+    \caption{Figure.10\todo{Caption}}\label{figure:10}
+\end{figure}
+
+% Fig. 11
+\clearpage
+\figurenum{11}
+\begin{figure}
+    \centering 
+    \includegraphics[width=18.0cm]{fig/redbcg_prof_gama_2}
+    \caption{Figure.11\todo{Caption}}\label{figure:11}
+\end{figure}
+
+% Fig. A1
+\clearpage
+\figurenum{A1}
+\begin{figure}
+    \centering 
+    \includegraphics[width=14.0cm]{fig/redbcg_1_HSC-I_full_imgsub_ellip_default_compare.png}
+    \caption{Figure.A1\todo{Caption}}\label{figure:A1}
+\end{figure}
+
+% Fig. B1
+\clearpage
+\figurenum{2a}
+\begin{figure}
+    \centering 
+    \includegraphics[width=11.5cm]{fig/dr1_redbcg_use_sed5b_fsps2_logm_plots}
+    \caption{Figure.2a\todo{Caption}}\label{figure:2a}
+\end{figure}
+
+\figurenum{2b}
+\begin{figure}
+    \centering 
+    \includegraphics[width=11.5cm]{fig/dr1_nonbcg_use_sed5b_fsps2_logm_plots}
+    \caption{Figure.2b\todo{Caption}}\label{figure:2b}
 \end{figure}

### 2016-09-30 draft/build.sh

@@ -1,4 +1,4 @@
-pdflatex draft_v0
-bibtex draft_v0
-pdflatex draft_v0
-pdflatex draft_v0
+pdflatex ms
+bibtex ms
+pdflatex ms
+pdflatex ms

### 2016-12-04 draft/ms_v0.tex
version 0

% Version 0; preprint format; Written by SH
% Version 1; emulateapj format; Edited by SH and AL

%\documentclass[twocolumn]{aastex6}
\documentclass{emulateapj}

% Packages
%\usepackage{emulateapj5}
\usepackage{apjfonts}
\usepackage{amssymb, amsmath}
\usepackage{graphicx}
\usepackage{CJK}
\usepackage{natbib}
\usepackage{hyperref}
\usepackage{float}
\usepackage[usenames]{color}

% Package Settings
\bibliographystyle{apj}
\hypersetup{colorlinks=true,
            citecolor=cyan,
            linkcolor=cyan,
            filecolor=magenta,      
            urlcolor=cyan}
\urlstyle{same}

% Figure extention
\DeclareGraphicsExtensions{.pdf,.png,.jpg}
\input psfig.tex

%%%%%%%%%%%%: User Defined Commands %%%%%%%%%%%%

% Song Huang's definition 
\def\arcsec{{\prime\prime}}
\def\arcmin{{\prime}}
\def\degree{{\circ}}
\def\h{\hskip -3 mm}
\def\aa{{A\&A}}
\def\aas{{ A\&AS}}
\def\aj{{AJ}}
\def\al{$\alpha$}
\def\bet{$\beta$}
\def\amin{$^\prime$}
\def\annrev{{ARA\&A}}
\def\apj{{ApJ}}
\def\apjs{{ApJS}}
\def\asec{$^{\prime\prime}$}
\def\deg{$^{\circ}$}
\def\ddeg{{\rlap.}$^{\circ}$}
\def\dsec{{\rlap.}$^{\prime\prime}$}
\def\cc{cm$^{-3}$}
\def\flamb{erg s$^{-1}$ cm$^{-2}$ \AA$^{-1}$}
\def\flux{erg s$^{-1}$ cm$^{-2}$}
\def\fnu{erg s$^{-1}$ cm$^{-2}$ Hz$^{-1}$}
\def\hst{{\textit{HST}}}
\def\kms{km s$^{-1}$}
\def\lamb{$\lambda$}
\def\lax{{$\mathrel{\hbox{\rlap{\hbox{\lower4pt\hbox{$\sim$}}}\hbox{$<$}}}$}}
\def\gax{{$\mathrel{\hbox{\rlap{\hbox{\lower4pt\hbox{$\sim$}}}\hbox{$>$}}}$}}
\def\simlt{\lower.5ex\hbox{$\; \buildrel < \over \sim \;$}}
\def\simgt{\lower.5ex\hbox{$\; \buildrel > \over \sim \;$}}
\def\micron{{$\mu$m}}
\def\mnras{{MNRAS}}
\def\nat{{Nature}}
\def\pasp{{PASP}}
\def\perang{\AA$^{-1}$}
\def\peryr{yr$^{-1}$}
\def\reference{\noindent\pp}
\def\refindent{\par\noindent\parskip=2pt\hangindent=3pc\hangafter=1 }
\def\sb{mag~arcsec$^{-2}$}
\def\lsun{$L_\odot$}
\def\msun{$M_\odot$}
\def\sigs{$\sigma_*$}
\newcommand{\lt}{<}
\newcommand{\gt}{>}

\def\etal{{\ et al.~}}
\def\galfit{{\tt GALFIT}}
\def\ser{{S\'{e}rsic\ }}
\def\redm{\texttt{redMaPPer}}
\def\cmodel{\texttt{cModel}}
% Samples
\def\rbcg{\texttt{cenHighMh}}
\def\nbcg{\texttt{cenLowMh}}
\def\redbcg{{$\lambda \ge 30$}}
\def\nonbcg{{$\lambda < 20$}}
% Mass related 
\def\mstar{{$M_{\star}$}}
\def\mhalo{{$M_{\mathrm{halo}}$}}
\def\logms{{$\log (M_{\star}/M_{\odot})$}}
\def\logmh{{$\log (M_{\mathrm{Halo}}/M_{\odot})$}}

\def\minn{{$M_{\star,10\mathrm{kpc}}$}}
\def\mtot{{$M_{\star,100\mathrm{kpc}}$}}
\def\mout{{$M_{\star,150\mathrm{kpc}}$}}
\def\mgama{{$M_{\star,\mathrm{GAMA}}$}}
\def\mcmodel{{$M_{\star,\mathrm{cModel}}$}}

\def\logminn{{$\log (M_{\star,10\mathrm{kpc}}/M_{\odot})$}}
\def\logmtot{{$\log (M_{\star,100\mathrm{kpc}}/M_{\odot})$}}
\def\logmout{{$\log (M_{\star,150\mathrm{kpc}}/M_{\odot})$}}
\def\logmgama{{$\log (M_{\star,mathrm{GAMA}}/M_{\odot})$}}
\def\logmcmodel{{$\log (M_{\star,mathrm{cModel}}/M_{\odot})$}}

\def\m2l{{$M_{\star}/L_{\star}$}}
\def\mden{{$\mu_{\star}$}}

% Commenting:
\newcommand{\xxx}[1]{\textcolor{red}{\textbf{XXX}}}
\newcommand{\todo}[1]{\textcolor{red}{\textbf{TODO:~#1}}}
\newcommand{\plan}[1]{\textcolor{cyan}{#1}}
\newcommand{\addref}{{\textcolor{red}{REF}}}
\newcommand{\note}[2]{\textcolor{blue}{\textbf{[Comment (#1): #2]}}}
\newcommand{\song}[1]{\textcolor{magenta}{\textbf{[Song: #1]}}}
\newcommand{\alexie}[1]{\textcolor{blue}{\textbf{[Alexie: #1]}}}
\newcommand{\kevin}[1]{\textcolor{green}{\textbf{[Kevin: #1]}}}

%%%%%%%%%%%%: Header and Version %%%%%%%%%%%%

\shorttitle{ENVIRONMENT DEPENDENCE OF MASS-SIZE RELATION}
\shortauthors{HUANG ET AL.}
\slugcomment{Draft version 0}

\begin{document}

\begin{CJK*}{UTF8}{gbsn}

%%%%%%%%%%%%: Title and Affiliations %%%%%%%%%%%%

%\title{The Environment and Structure of Massive Central Galaxies
%       using the Subaru Hyper Suprime-Cam Survey}

\title{First Detection of the Enviromental Dependence of the Masses, Sizes, and Structures of Massive Galaxies }

\author{Song Huang (黄崧)\altaffilmark{1}, 
        HSC collaboration\altaffilmark{1}}

%        \author{Song Huang (黄崧)\altaffilmark{1} 
%        Alexie Leauthaud\altaffilmark{1}, 
%        Kevin Bundy\altaffilmark{1},
%        Michael Strauss\altaffilmark{2},
%        Yen-Ting Lin\altaffilmark{3},
%        Rachel Mandelbaum\altaffilmark{4}
%        }

\email{song.huang@ipmu.jp}

\date{}

\altaffiltext{1}{Kavli Institute for the Physics and Mathematics of the 
    Universe, The University of Tokyo Institutes for Advanced Study, 
    the University of Tokyo (Kavli IPMU, WPI), Kashiwa 277--8583, Japan}

%\altaffiltext{2}{Princeton University Observatory, 
%    Peyton Hall, Princeton, NJ 08544, USA}
%\altaffiltext{3}{Institute of Astronomy and Astrophysics, Academia Sinica, 
%    P.O.~Box 23--141, Taipei 10617, Taiwan}
%\altaffiltext{4}{Carnegie-Mellon University \todo{correct affiliation here}}

%%%%%%%%%%%%: Abstract and Keywords %%%%%%%%%%%%

\begin{abstract}

    Although the environmental dependence of structures for massive central 
    galaxies is predicted by the promising hierarchical assembly model, 
    observations at low redshift seem to find no convincing evidence for that. 
    With the help of deep $i$-band images of a large sample of massive central 
    galaxies at $0.3 < z < 0.5$ from the Subaru Hyper Suprime-Cam (HSC) survey, 
    we map their stellar mass distributions out to radius larger than $100$ kpc, 
    and discover subtle, but systematic and robust structural differences that 
    depend on halo mass. 
    At fixed stellar mass within 100 kpc, the massive central galaxies in more 
    massive ($M_{200m} > 1.6\times 10^{14} M_{\odot}$) halos have a 
    slightly flattened inner profile within $\sim 15$-$20$ kpc, and a more prominent 
    outer envelope compared to ones in less massive 
    ($M_{200m}>8.7\times 10^{13} M_{\odot}$) halos.
    For centrals with $M_{\star} > 10^{11.5} M_{\odot}$, the ones in more massive 
    halos show very significant excess of mass in the outskirt when the two samples 
    are matched using proxies of mass assembled at $z > 1$. 
    Such differences are broadly consistent with richer recent merging history 
    for more massive halos. 
    We suggest that the relation between total stellar mass and mass within inner 5 
    or 10 kpc is potentially interesting for diagnosing the role played by host halo 
    in shaping the structures of massive central galaxies. 
    These results also highlight the importance of deep photometry and the usage of 
    detailed structural information in the study of the assembly history of galaxies.

\end{abstract}
\keywords{galaxies: elliptical and lenticular, cD --- galaxies: formation --- 
          galaxies: photometry --- galaxies: structure --- galaxies: surveys}

\maketitle

%%%%%%%%%%%%: Main Text %%%%%%%%%%%%

%% ------------------------------------------------------------------------------------ %% 
    \begin{figure*}[t!]
        \centering 
        \includegraphics[width=\textwidth]{fig/redbcg_sdss_compare}
        \caption{A comparison between the imaging quality of SDSS and HSC Wide for a sample 
        	of nearby massive elliptical galaxies at $0.2 < z < 0.5$.  
            These images are generated using $gri$ band images with an arcsinh stretch 
            \citep{Lupton2004}. 
            The HSC Wide layer is $3.0$-$4.0$ magnitudes deeper than SDSS which is 
            critical in order to map the outskirts of ETGs out to large radii.}
        \label{fig:sdss_compare}
    \end{figure*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
\section{Introduction}
    \label{sec:intro}

    \plan{Scientific Background}
    \begin{itemize}
        \item \plan{Massive galaxies are important cosmic probe and unique labs to study 
            galaxy evolution.} 
        \item \plan{Briefly explain why massive early-type galaxies are important through 
            the difficulties of stellar-halo mass relation and stellar mass function at the 
            high-mass end.}
        \item \plan{Brief summary of the current understanding of their cosmic assembly 
            history.}
        \item \plan{Explain why we should care about the environment, and why we expect to 
            see some environmental dependence in the structure and other properties of
            massive galaxies.}
        \item \plan{Brief review of the current observations.  It is still not clear 
            whether there is a clear environmental dependence.}
    \end{itemize}

    \plan{Observational difficulties (a.k.a Why we need HSC)}
    \begin{itemize}
        \item \plan{Explain why it is important to study the mass distribution of 
            massive galaxies out to large physical radius; and, given their unique light 
            profiles, why it is more difficult to study them compared to late-type 
            galaxies.}
        \item \plan{Very brief summary of past observational efforts, and why they are not 
            good enough (Not enough number of really massive galaxy; Shallow images; 
            Background subtraction issue; and stacking analysis can be dangerous as while)}
    \end{itemize}

    \plan{Basic idea of this work}
    \begin{itemize}
        \item \plan{Here we take advantages of the ambitious Hyper-Suprime camera 
            survey\ldots}
    \end{itemize}

\alexie{Because the text is long, at this point in the introduction, let's give reader an overview of our methodology. Let's sim for one or two succint paragraphs. That way they will begin the paper having a better idea of what we want to achieve. We will want to give them some key ideas here. 1) Quality of the HSC data (Reference Fig 1 here) 2) we want to look for enviromental differences, we'll use  a cluster catalog to divide into halo mass bins, 3) define the concepts of M10 and M100 (and reference Fig 10 here). You sort of have the elements in place below, by needs more editing and reorganizing.}

\alexie{Bring Fig 1 and Fig 10 here so they are the two first figures.}

	\song{Ok, will do; I will just say Fig 10 demonstrate the stellar mass and structural 
    	diversity of the massive galaxies}

    To achieve this goal, we select a large sample of massive central galaxies within
    halos that are more or less massive than \logmh{}$\sim 14.0$ at $0.3 < z < 0.5$ 
    from the current $\sim 100$ square degree of HSC data.
    As indicated by the $M_{\star}$-$M_{\mathrm{Halo}}$ relation, at the same \mstar{}, 
    massive central galaxies with similar morphology can live in halos within large range 
    of \mhalo{}, therefore it is very interesting to look into the influence of their halos 
    on the structure of these galaxies. 
    Under the adopted cosmology, $1.0^{\arcsec}$ equals 4.4 and 6.1 kpc at redshift 0.3 
    and 0.5.  
    In this redshift range, we can reliably measure the total stellar mass within the 
    inner 5 to 10 kpc (where the ``in-situ'' stellar component should dominate) given 
    the typical seeing, while still be able to map their stellar distributions out to 
    $\sim 100$ kpc at $z\sim 0.5$ given the imaging depth of these HSC data.
    Also, we can safely ignore significant mass growth and structural evolution 
    (no star formation, lower merger rate \etal~e.g.\ \citealt{Bellstedt2016},
    \citealt{Inagaki2015}; but also see \citealt{Bai2014}) 
    with our redshift and \mstar{} ranges.

    The paper is organized as follows. Section\ref{sec:data} gives a brief overview of 
    the HSC observation and data reduction, along with the summary of the data selection
    processes.  
    Then, we will explain the procedures for extracting 1-D surface brightness profiles 
    (Section \ref{sec:ellipse}) and estimating stellar mass (Section \ref{sec:mstar}) in
    details.   
    We will present the main results in Section \ref{sec:result}, and discuss the several 
    related technical and scientific issues in Section \ref{sec:discussion}, ending with
    summary and future plans in Section \ref{sec:summary}.

    All the magnitudes used here are in AB system (\citealt{Oke1983}), and are corrected 
    for Galactic extinction using calibrations from \citet{Schlafly11}.
    In this work, we assume $H_0$ = 70~km~s$^{-1}$ Mpc$^{-1}$, ${\Omega}_m=0.3$, 
    and ${\Omega}_{\lambda}=0.7$. 
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
    \begin{figure*}[bt]
        \centering 
        \includegraphics[width=\textwidth]{fig/redbcg_ellipse_example}
        \caption{Left: example of the 1-D surface brightness and ellipticity profile 
            for a massive galaxy at $z=0.23$ in $i$-band using \texttt{Ellipse}. 
            In this work, we always show the radial profile in $R^{1/4}$ scale as it 
            is the most appropriate one to show the structural details of massive 
            ETGs at both inner and outer regions. 
            The dash-line shows the surface brightness profile after correcting the 
            background. 
            We also plot the brightness profile of the PSF model normalized at the 
            central surface brightness of the galaxy to highlight the region affected 
            by seeing. 
            On the top panel, the dash line shows the ellipticity used for the final 
            isophote.~~~ 
            Right: the masked $i$-band image of this galaxy with the isophotes extracted 
            by \texttt{Ellipse} overlaid. 
            The thick, green isophote highlights the one with $\mu_{i}\sim 28.5$~\sb.}
            \song{Will update completely, takes a little bit longer}
            %\alexie{Can we add physical radii at the top left since $R^{1/4}$ is not 
            %    very intuitive. On the right hand side, why show the background as blue, 
            %    instead of showing the actual image of the galaxy with masks overlaid? 
            %    Add units to x axis of right hand side. 
            %    Red text on left hand side, replace with "1D profile of a $10^{xx}$ 
            %    M$_{\odot}$ galaxy at $z=xx$}.}
        \label{fig:ellipse}
    \end{figure*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
\section{Data And Sample Selection}
    \label{sec:data}

\subsection{The Hyper Suprime-Cam Survey}
    \label{ssec:hsc}

    The Subaru Strategic Program (SSP, \addref) makes use of the new prime-focus camera,
    the Hyper Suprime-Cam (HSC;~\citealt{Miyazaki2012}), on the 8.2-m Subaru telescope at 
    Mauna Kea. 
    This ambitious multi-layer photometric survey takes advantage of the large field of 
    view (FoV;~1.5 deg in diameter) of HSC and will cover $\sim 1400$ deg$^2$ of sky in 5
    broad bands (\textit{g r i z Y}) to the depth of $r \sim 26$ mag in the \texttt{WIDE}. 
    This work is based on the internal data release \texttt{S15B}, which covers 
    $\sim 100$square of degree of sky in all 5-band to full \texttt{WIDE} depth.  
    The regions covered by this release overlap with a number of spectroscopic surveys 
    (e.g.\ SDSS/BOSS: \citealt{Eisenstein2011}, \citealt{Alam2015}; 
    GAMA: \citealt{Driver2011}, \citealt{Liske2015}).

   The HSC \texttt{WIDE} survey is $3.0$-$4.0$ magnitudes deeper in the $i$-band 
    than SDSS. 
    Combined with the excellent imaging resolution (median $i$-band seeing is 0.6"), 
    and the wide area, this makes the HSC wide layer a tremendous data set to perform a 
    large statistical study of surface brightness profiles of ETGs out to large radii. 
    Fig.\ref{fig:sdss_compare} illustrated the quality of HSC imaging compared to SDSS 
    for a sample of low redshift ETGs. 
    Fig.\ref{fig:sdss_compare} clearly demonstrates that the HSC Wide survey is well 
    suited for mapping the stellar distribution of massive galaxies out to large radii 
    and will be a powerful data set to explore the assembly history of ETGs.

	The HSC $i$-band images typically have the best seeing in all five bands because of 
    strict requirements determined by weak lensing science. 
    We will therefore use the $i$-band images to measure the stellar distributions of 
    massive galaxies.

%% ------------------------------------------------------------------------------------ %% 
\subsection{The HSC galaxy catalog and photometry measurements}
    \label{sec:pipeline}

    The HSC SSP data are processed with \texttt{hscPipe 4.0.1}, a derivative of the Large 
    Synoptic Survey Telescope (LSST) pipeline (e.g.\ \citealt{Juric2015}; 
    \citealt{Axelrod2010}), modified for HSC. 
    \texttt{hscPipe} first performs a number of tasks at the single exposure level 
    (bias subtraction, flat fielding, background modeling, object detection and 
    measurements). 
    Then pipeline perform astrometric and photometric calibration for each single 
    expoures. 
    After that, the \texttt{hscPipe} warp different exposures on to a common
    World Coordinate System (WCS), combine them into coadded images with improved 
    signal-to-noise ratio ($S/N$), and update the images with better astrometric and 
    photometric calibrations at the same time using the common stars among different
    exposures.
    The pixel scale of the combined images is $0.168^{\arcsec}$.  
    The photometric calibration is based on data from the Panoramic Survey Telescope 
    and Rapid Response System (Pan-STARRS) 1 imaging survey 
    (\citealt{Schlafly2012}, \citealt{Tonry2012}, \citealt{Magnier2013}). 
    To achieve consistent deblending and photometry across all bands, \texttt{hscPipe} 
    performs multi-band post-processing at the coadd level. 
    First, the \texttt{hscPipe} performs object detection again on the coadd images
    in each band independently, and identify the above-threshold region (referred as 
    ``footprint'') and the flux peak within it for each source. 
    ``footprints'' and peaks from different bands are then merged together before 
    the \texttt{hscPipe} deblend and measure them in each band. 
    Later, \texttt{hscPipe} selects a ``reference band'' for each object based on the 
    $S/N$ in different bands (for most galaxies in this work, it is the $i$-band). 
    After fixing the centroids, shape, and other non-amplitude parameters of each 
    object in this reference catalog, \texttt{hscPipe} perform forced photometry 
    on the coadd image in each band.
    The PSF and galaxy model fluxes measured in the forced photometry approach are the
    best for color measurements.  
    Please refer to \citet{BoschInPrep} for more details of the \texttt{hscPipe} and 
    the multi-band processing method.

    The HSC \cmodel{} algorithm is similar to the SDSS \cmodel{} one.  
    It fits the flux distribution of an object using a combination of de~Vaucouleur and 
    exponential components after considering the PSF convolution.  
    For more details about the algorithm, please see Bosch\etal~in prep.~.
    We have tested its performance using synthetic objects (Huang\etal~in prep.~), and 
    the results indicate that, generally speaking, the HSC \cmodel{} photometry is 
    accurate down to $i >25.0$ mag.  
    However, for massive ETGs with extended stellar distributions, \cmodel{} currently 
    systematically underestimates their total flux.
    This problem indicates the intrinsic limitation of \cmodel{} as it is incapable of
    modeling profiles that are extremely extended in the outskirt at the depth of 
    HSC survey. 
    At the same time, issues with the deblender also worsen the situation. 
    As the image becomes much deeper, it also significantly increases the fraction 
    objects that are blended with others, and makes reliable deblending process 
    a very challenging problem especially for massive ETGs where satellites and 
    background galaxies often blend with the low surface brightness stellar envelope.
    To make sure the reliable detection of faint objects close to the detection limit, 
    the deblending method implemented by the \texttt{hscPipe} now tends to 
    ``over-deblend'' the surrounding areas of bright galaxies, and further results in 
    under-estimated total flux of massive ETGs (more discussion in 
    Bosch\etal~in prep.~).  
    For these reasons, we will perform customized photometric measurements to derive 
    more accurate total luminosity and stellar mass. 
    We only use the HSC \cmodel{} photometry in the initial selection of parent 
    sample.

%% ------------------------------------------------------------------------------------ %% 
\subsection{Initial Massive Galaxy Sample}
    \label{ssec:initial}

    Because of the caveats that apply to \texttt{hscPipe} measurements for bright 
    galaxies, we will use custom made software to measure the luminosity profiles of
    massive galaxies. 
    Our first step is use the HSC galaxy catalog to create an initial sample of massive
    galaxies that is complete to \xxx{} at $z < 0.5$. 
    We will then use custom made software to re-measure luminosities for all galaxies 
    in this sample. 
    Based on Leauthaud\etal~(2016), most \logms{}$\geq 11.5$ galaxies should have 
    $i_{\mathrm{SDSS, cModel}} \leq 21.0$ mag.
    So we first select all galaxies with $i_{\mathrm{HSC, cModel}} \leq 21.5$ 
    \footnote{We neglect the insignificant differences between the response curves of
    SDSS-$i$ and HSC-$i$ filters}
    in regions that have reached the required depth of \texttt{WIDE} survey in all 
    five bands. 
    %% The SQL search is saved as "sample.sql" 
    %% The master catalog used here is "dr1_wide_galaxy_icmodel_21.5.fits"
    %%   The original catalogs contain 2275477 objects

    We select extended objects that have no error in deblending process, well defined 
    centroids, and \texttt{cModel} magnitudes in all five bands. 
    After removing the objects that have pixel affected by saturation, cosmic-ray, and 
    other optical artefact \footnote{each criterion affects less than 8\% of the entire
    sample}, we select 1760845 galaxies that will be referred as \texttt{hscPho}. 
    %% Saved as "dr1_wide_galaxy_hscPho.fits"

    As reliable photometric redshift using HSC photometry is still a working progress, 
    we only use objects with either available spectroscopic redshift or robust 
    red-sequence photo-$z$ from the \redm{} catalog (see Section \ref{ssec:redmapper}).  
    We first match the \texttt{hscPho} sample with the external spec-$z$ catalog 
    compiled by the HSC database\footnote{It is created by matching HSC objects with 
    public data of several spectroscopic surveys (e.g.\ SDSS/BOSS; GAMA). 
    Duplicated matches from different sources are merged through internal matching 
    using $0.5^{\arcsec}$ radius. 
    For each object, the quality information of the spec-$z$ from different catalogs 
    are homogenized into a single flag that indicates whether the redshift is secure, 
    and only secure spec-$z$ are used in this work.}
    %% This is catalog: "dr1_specz_use.fits"
    using $1.0^{\arcsec}$ radius.
    At $0.2 \leq z \leq 0.5$, most redshifts in the HSC spec-$z$ catalog come from 
    SDSS/BOSS and GAMA surveys.  
    The BOSS survey provides the majority of spec-$z$ in this work.  
    Due to the complex selection criteria for different subsamples within the BOSS
    survey (e.g.\ the \texttt{LOWZ} and \texttt{CMASS}), it is not easy to estimate 
    its \mstar{} completeness.  
    Recently, through comparing with the deeper Stripe 82 Massive Galaxy Catalog
    (\texttt{S82-MGC}; \citealt{Bundy2015}), \citet{Leauthaud2016} suggests that the 
    BOSS spec-$z$ is about 80\% complete at \logms{}$\geq 11.6$ at $0.3 < z < 0.5$. 
    The GAMA survey, which partially overlaps with the HSC footprint, provides 
    additional 14\% unique spec-$z$. 
    Based on \citet{Taylor2011} (e.g.\ their Fig.~6), at $z\sim 0.3$, the GAMA 
    sample is 80\% complete down to $10^{10.8}$\msun; but only 80\% complete to 
    $10^{12.0}$\msun at $z\sim 0.5$. 
    Despite the difference in \mstar{} estimates, we can expect 
    our sample should be quite complete above \logms{}$\geq 11.5$-$11.6$.
    We will further address the issue of \mstar{}-completeness more carefully 
    using the common sample with \texttt{S82-MGC} (see Section\ref{ssec:s82}).

    Among the 116813 matched objects, 42696 are at $0.2 \leq z \leq 0.5$.
    %% Saved as "dr1_wide_galaxy_icmodel_21.5.fits"
    The majority of these redshifts come from either SDSS or BOSS data.  
    GAMA survey contributes another $\sim 14$\%. 
    For objects without external spec-$z$, we match them with the central galaxies 
    from \redm{} catalog using $2.0^{\arcsec}$ radius. 
    The matched objects with useful red-sequence photo-$z$ ($z_{\lambda}$) are also 
    included in the final sample of bright galaxies with reliable redshift between 
    $0.2 \leq z \leq 0.5$
    (will be referred as \texttt{hscZ}).
    As we will show later (see Section \ref{ssec:future}), to ensure reasonable 
    \mstar{}-completeness at the high-\mstar{} end, and make sure the samples we 
    want to compare have well overlapped redshift distributions, we will focus on 
    the galaxies at $0.3 \leq z \leq 0.5$.

%% ------------------------------------------------------------------------------------ %%  
\subsection{\redm{}{} cluster catalog}
    \label{ssec:redmapper}

    In this paper, our study focuses on galaxies which are located at the center of
    their dark matter halos. To limit our sample to central galaxies, we use 
    \texttt{v5.10} of the \redm{}{} cluster 
    catalog\footnote{See: http://risa.stanford.edu/redmapper/} 
    (e.g.\ \citealt{Rykoff2014}; \citealt{Rozo2015b}). 
    These authors have developed a well-tested red-sequence cluster finder that has been 
    run on SDSS DR8 (\citealt{SDSSDR8}) photometric data. 
    For each cluster, the catalog provides a photometric redshift estimate $z_{\lambda}$, 
    a richness $\lambda$, and identified the most likely central
    galaxy (this is the galaxies with the highest value of the central probability 
    $P_{\mathrm{Cen}}$). 
    A list of member galaxies for each cluster, and associated membership probabilities, 
    is also provided. 
    Details about the performance of the \redm{}~cluster catalog can be found in 
    \citet{Rozo2014}, \citet{Rozo2015a}, and \citet{Rozo2015b}. 
    Several studies have published calibrations between the \redm{}~richness estimate, 
    $\lambda$, and halo mass (e.g.\ \citealt{Saro2015}; \citealt{Farahi2016}; 
    \citealt{Simet2016}). 
    The results of these studies are in good agreement and indicate that clusters 
    identified by \redm{}~($\lambda > 20$) have $\log (M_{200,c}/M_{\odot}) \geq 14.0$. 
    Therefore, the \redm{} catalog helps us group the massive central galaxies into 
    samples with different average \mhalo{}.  
    And, to select reliable candidates of central galaxies, we only include the ones 
    with high probability of being the central galaxy ($P_{\mathrm{CEN}} \geq 0.7$).

    Although the \redm{} catalog provides us a good sample of central galaxies in 
    massive halos, the typical uncertainty of $\lambda$ estimate is still at 
    $\sim 5$-10 level.  
    In addition, due to the depth and resolution of SDSS images, the \redm{} catalog 
    becomes slightly incomplete at lower richness ($\lambda < 40$) end at $z > 0.33$.
    To reduce the impacts from uncertain richness and incomplete selection of 
    massive halos, we will focus on a sample of central galaxies in halos with 
    $\lambda > 30$. 
    This will also help up enhance the \mhalo{} contrast in the structural comparison.     
    Based on the calibration in \citet{Simet2016}, the $\lambda \geq 20$ sample should
    have halo mass ($M_{200m}$) more massive than $10^{14.0} M_{\odot}$.  
    For the $\lambda \geq 30$ sample, they should live in halo more massive than
    $10^{14.2} M_{\odot}$ using the same calibration. 
    And, we can confirm that the results presented later do not depend on the choice 
    of $\lambda$ boundary here. 
    For the massive central galaxies that are not in these cluster-level halos, 
    we unfortunately can not estimate their \mhalo{} individually, but it is safe 
    to assume they should have $\log (M_{200m}/M_{\odot}) < 14.0$.     
    %\textcolor{red}{but sometimes we make cuts at $\lambda<20$ and $\lambda>30$. 
    %Is it confusing to have several different thresholds? Need to give a Motivation 
    %for using different numbers here.}

%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}[bt!]
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_smf_new}
      \caption{\textbf{Left:}: We compre the \mstar{} volume-density distributions of 
      	  \rbcg{} (red) and \nbcg{} (black) galaxies using stellar mass based on 
          \mcmodel{} (dash) and \mtot{} (solid) to highlight the increase of \mstar{}
          due to different methods.  
          Here we also show the volume-density distributions of the \texttt{S82-MGC} 
          galaxies (green) to evaluate the \mstar{}-completeness. 
          The vertical line highlight \logms{}$=11.6$ before correcting the \mstar{} using
          total luminosity from 1-D profile.~~
          \textbf{Right:} We plot \mtot{} against the difference between \mtot{} and 
          \mcmodel{} for the \rbcg{} (red squares; color indicates redshift) and \nbcg{}
          (grey dots) galaxies. 
          Two vertical lines highlight the $11.6<$\logmtot{}$<11.9$ mass range where the
          two samples overlap the most.
          We also show the historgrams of the mass differences for galaxies with 
          $11.6<$\logmtot{}$<11.9$ on the right side. 
          \song{The figure is updated, but I think the histogram on the right side is 
          useful; 1) it shows the average mass difference clearly; 2) shows the differences
          between the two samples; Also try to update the caption, let me know what do you 
          think. And, I think the left panel should stay here, because we need to discuss 
          the mass completness here; the discussion section can use another figure where 
          we overplot other people's SMF; we just need some caveats.}
          \alexie{Simplfy the caption here. What is the main message we are trying to convey. 
          I think the point of this figure is to show that cmodel is underestimated. 
          Focus on that message. Some information here is un-necessary. 
          Also looks make some changes to this Figure: 1) right. Remove the right hand 
          histograms. 2) I ont think we learn much by the color coding. Just use a single 
          color (less explaning to do). Label using your names cenLowMh and cenHighMh}}
      \label{fig:smf1}
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
\subsection{Massive Central Galaxies from Low and High Mass Halos}
    \label{ssec:mass_central}

    Based on recent constraints of $M_{\star}$-$M_{\mathrm{Halo}}$ relation 
    (e.g.\ \citealt{Leauthaud2012}, \citealt{Behroozi2013}, \citealt{Kravtsov2014}), 
    the \mhalo{} of \logms{}$ > 11.0$ galaxies has a large scatter at fixed \mstar{}.            
    Although we can not yet measure \mhalo{} individually, we can still broadly 
    separate them into galaxies in small groups (\logmh{}$<14.0$) and 
    large groups/clusters (\logmh{}$>14.0$), and investigate the 
    ``environmental''-dependence of their structures.

    % We match this sample with the central galaxies of \redm{}~catalogs using a 
    % $1.0^{\arcsec}$ radius, and it results in 704 galaxies.  
    %% Saved as "dr1_redbcg_hsc_sdss_gama_1arcsec.fits"
    Firstly, we match the \texttt{hscZ} sample with the massive central galaxies of 
    \redm{} clusters with $\lambda \geq 20$ and $P_{\mathrm{0.7}} \geq 0.7$ using 
    $1.0^{\arcsec}$ radius. 
    This step finds 375 matched galaxies at $0.2 \leq z \leq 0.5$ 
    (among them 282 are at $0.3 \leq z \leq 0.5$).  
    We will refer these \textbf{central galaxies in more massive halos} as \rbcg{} 
    sample from now on.
    A small fraction of \redm{} centrals within the HSC footprints are missing  
    due to severe contamination from optical artifacts or bright stars.
    Spec-$z$ is not available for 67 (17.9\%) galaxies in the sample, but their 
    $z_{\lambda}$ should be very accurate (median $|z_{\lambda} - z_{\mathrm{Spec}}|$ is 
    about 0.01 for the ones with spec-$z$).
    The median richness ($\lambda$) of these clusters is $\sim 32$, corresponding to 
    halo mass of $M_{200m}\sim 1.7\times 10^{14} h^{-1} M_{\odot}$. 
    Among these central galaxies, 222 are in clusters with $\lambda \geq 30$. 
    When focusing on this subsample, the median richness is $\sim 41$, corresponding 
    to halos with $M_{200m} \sim 2.2\times 10^{14} h^{-1} M_{\odot}$. 
    Meanwhile, only 15\% of \rbcg{} sample lives in clusters with $\lambda \geq 50$
    ($M_{200m} \sim 3.0\times 10^{14} h^{-1} M_{\odot}$).   
    Therefore, the current \rbcg{} sample is not dominated by very massive clusters 
    with \mhalo{}$>10^{15} M_{\odot}$.  
    %% Saved as "dr1_redbcg_use_sed5b.fits"

    Assuming that the \redm{} catalog correctly identifies all halos with 
    $M_{200m}\sim 1.0\times 10^{14} h^{-1} M_{\odot}$ in the current footprint,
    the unmatched massive galaxies from the above step should be dominated by central 
    galaxies of less massive halos and massive satellites galaxies.  
    To select a purer sample of massive centrals in $M_{200m}<10^{14} h^{-1} M_{\odot}$
    halos, we identify and remove any galaxy that is too close to 
    \emph{any cluster member} in \redm{} catalog in both radius and redshift direction.

    \alexie{This is a rather strange procedure, I think we need to change it (referee and readers will complain!). What we really want to do is to remove any galaxies that have $r<R200$ in projection (from the galaxy with the highest value of Pcen) and remove galaxies within some deltaz of the cluster redshift. The cluster redshift is more well determined than the redshift estiamte of any cluster member. In short, what we are doing here is cutting out a cylindar arond the most likley BCG. The deltaz value can be motivated by the cluster redshift uncertainty from the redmapper papers. The only remaining question is then what radius to use around clusters. To get that number here is what we need to do. 1) Start with Eq 12 and Table 3 in Simet et al. For each cluster, assign a value of M200m (halo mass defined as 200 time background) to each cluster. 3) we then need to estimate the cluster radius R200m (or R200b, same thing). To do this, we need to use a mass-concentration relation. I'm pretty sure there is an easy command to do this in Python using the python package "colossus" by bendikt diemer. Download it and see if youc an get it to work. If it doens't look obvious after 30 min, I can do it on my end using my own code. But good for you to know how to do this. We can simply use the mass-concentration realtion from Benedikts work. 4) Now for every cluster you have R200m. And you define the low halo mass central sample as ones that are not within any cylindar around any cluster. Sorry, I know this might mean re-doing everything.....let's discuss by Skype if this is a major issue.}

    For each \redm{} cluster member, we remove objects within a cylinder region 
    around it from the remaining sample. 
    Such cylinder is defined by 1) physical radius of 3.0 Mpc at the red-sequence 
    redshift of the cluster; 2) $|z - z_{\lambda}| \leq 0.05$ as 
    \nbcg{} later.

    However, we should note that the \nbcg{} sample at this stage spans a large range
    in \mstar{}, extending towards \logms{}$<10^{11}$.  
    Therefore, we should expect contamination from satellites in \logmh{}$< 14.0$ halos
    at certain degree.  
    Later, after we update the total \mstar{} of them, we will mainly focus on the 
    \nbcg{} galaxies at high mass end, especially the ones at \logms{}$ > 11.5$. 
    Based on observational constraints (e.g. \citealt{vanUitert2016}), we can neglect 
    satellite contamination at such high \mstar{} range. 
    %% Saved as "dr1_nonbcg_use_sed5b.fits"

\subsection{Summary of Sample Construction}
    \label{ssec:sample}

    In summary, from the $\sim 100$ deg$^2$ deep HSC images, we select a large sample
    of massive central galaxies with reliable redshift information, and broadly separate 
    them into two groups with different \mhalo{}.  
    To help you go through the results, here are a few key points to keep in mind:

    \begin{itemize}
        \item \texttt{hscPho} sample: this parent sample consists of bright galaxies 
            with $i_{\mathrm{cModel}} \leq 21.0$, good quality images and reliable 
            \texttt{cModel} photometry in all five HSC bands in the \texttt{S15B} 
            data release. 
        \item \texttt{hscZ} sample: through matching the \texttt{hscPho} sample with 
            spectroscopic redshifts from surveys like SDSS/BOSS and GAMA, or accurate 
            red-sequence photometric redshift in the \redm{} catalog, we come up with 
            a large sample of bright galaxies with reliable redshift information. 
        \item \rbcg{} sample: we select a sample of 375 galaxies at $0.2 \leq z \leq 0.5$
            that are identified as central galaxies in $\lambda > 30$ \redm{} clusters. 
            The most reliable ones ($P_{\mathrm{Cen}} >0.7$) among 
            them will represent the central galaxies in very massive halos
            (\logmh{}$\geq 14.0$). 
        \item \nbcg{} sample: after excluding all the galaxies that are close to any 
            \redm{} clusters in both radial and redshift directions from the 
            \texttt{hscZ} sample, we have 29973 bright galaxies at $0.2 \leq z \leq 0.5$.
            With the help of \mstar{} estimates via SED fitting (see Section 
            \ref{ssec:isedfit}), we consider the massive ones among them as the 
            candidates of central galaxies in halos with \logmh{}$<14.0$.  
        \item To compare the \rbcg{} and \nbcg{} samples carefully, we will focus on 
            the redshift range at $0.3 \leq z \leq 0.5$ where their redshift 
            distributions greatly overlap and both samples have acceptable
            \mstar-completeness (see Section \ref{ssec:s82}).  
            Also, during the comparison of structures, we will mainly 
            \song{Will use $>30$ sample as default later; will update the figure first, 
            then correct the number of galaxies when I go through the text again.}
            \alexie{Why mainly use here? We have defined the high mass sample to be above this cut. Lets use $\lambda>30$ everywhere! Making more samples will make readers confused.} use \rbcg{} 
            galaxies with $\lambda > 30$ to ensure that they are from more massive 
            halos than the ones in \nbcg{} sample.
    \end{itemize}

%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
\section{Measurements of 1-D Surface Brightness Profile}
    \label{sec:ellipse}

    To estimate the total luminosity of massive galaxies, and measure their 
    one-dimensional stellar mass density (\mden{}) profiles, we perform elliptical 
    isophotes fitting using the IRAF task \texttt{Ellipse} (Jedrzejewski 1987).  
    Compared to the popular two-dimensional model fitting method, the isophote fitting
    approach is much less sensitive to the choice of model, number of components, 
    and the initial guesses of free parameters. 
    It is also less affected by the uncertainty of sky background subtraction.  
    This is particularly important for the massive ellipticals in our sample.  
    The much deeper HSC image reveals significantly more extended structures, 
    while also make it inappropriate to fit these galaxies with simple model like 
    the de~Vaucouleurs model or single \ser component model. 
    Such models fail to fit the central region and the stellar halo of massive 
    galaxies simultaneously, and also can not account for the radial variation of 
    ellipticity and position angle. 
    In principle, such massive galaxies can still be described using more complex 
    models (e.g \citealt{Huang2013a}; \citealt{Huang2013b}).  
    However, they are still very sensitive to background subtraction. 
    And it becomes even more difficult to choose initial parameters, and investigate
    the degeneracies among parameters. 
    Although it is certainly worth exploring in the future, we decide that the 1-D 
    method suits the goal of this work better.

    We first prepare large $i$-band cut-out images around these massive galaxies 
    that cover at least 750 kpc in radius, along with the bad pixel masks, and the 
    PSF model reconstructed using the central coordinates. 
    While they include all the visible light of the galaxy, they also leave enough 
    space to evaluate the background subtraction. 
    We choose to use $i$-band images not only considering their excellent seeing
    condition, but also because they trace the stellar distributions of massive 
    galaxies at $0.3 \leq z \leq 0.5$ reasonably well (fall between rest-frame $g$ 
    and $r$ band), and they suffer less from background uncertainty, which is crucial 
    for studying the outskirt of massive ETGs.  
    Although $z$ and Y-band should be better \mden{} tracer, the sky background 
    is much higher and the seeing is considerably worse on average.

    Secondly, using the \texttt{SEP} Python library, we perform \texttt{SExtractor}-like
    background estimation and object detections using different configurations to 
    overcome the ``over-deblending'' challenge met by the \texttt{hscPipe}. 
    Combining detections using different backgrounds and $S/N$ thresholds, 
    we correctly obtain the footprints of all objects, even of the ones that are 
    very close to the center of bright galaxies.
    For the rest objects, we convert their footprints into a mask image for the
    \texttt{Ellipse} procedure after increasing their sizes adaptively based on the 
    brightness and distance to the massive galaxy. 
    We achieve this via convolving the individual footprint with a Gaussian kernel
    so that we can conservatively exclude pixels affected by this object while still 
    making the mask follow the shape of the object. 
    Meanwhile, we create a more aggressive mask of \emph{all} objects in the same 
    approach, median-rebin the remaining pixels using a $6x6$ pixels box, and take 
    the peak value (or mode) of the distribution of these rebinned ``sky'' pixels 
    as the average background value around these bright galaxies.
    As expected, we often found slightly negative value that indicate over-subtraction 
    of background at certain degree. 
    In \texttt{hscPipe}, the background on each CCD is modeled with a 
    Chebyshev-polynomial fit to the smoothed image after excluding pixels with $S/N >5$.
    This algorithm suffer less than the SDSS version (e.g.\ see \citealt{Blanton2011}),
    but still over-subtract background around very bright object. 
    For our massive galaxies, such over-subtracted background creates artifactual
    truncation or steeper surface brightness profile.
    We therefore provide an ad hoc fix using a \texttt{SExtractor}-style background 
    model ($200x200$ pixels background box size, and 6 pixels median filtering size of 
    sky boxes) via running \texttt{SEP} on the image with all objects masked out.
    This model can account for the slightly over-subtracted background at very large 
    scale, shift the distribution of rebinned ``sky'' pixels to 0, and do not affect the 
    intrinsic flux distribution of our target.

    Finally, we run \texttt{Ellipse} on the background-corrected image following similar 
    strategy of \citep{Li2012}.
    In short, we start with free centroid and shape of each isophote, then gradually 
    constrain their behaviors, and eventually extract 1-D surface brightness profile 
    along the major axis using isophotes with fixed centroid and shape.
    The 4th Fourier modes are included to fit the isophote better. 
    In this way, we can extract the radial changes of the centroid, ellipticity, 
    position angle, and average isophotal distortions (more ``disky'' or ``boxy'', 
    e.g.\ \citealt{Kormendy2009}) along with the surface brightness profile.  
    Fig.\ref{fig:ellipse} shows an example of the 1-D surface brightness and 
    ellipticity profile for a massive galaxy at $z\sim0.2$ along with its masked 
    image and a subset of isophotes.  
    Appendix\ref{app:A} includes more details about the \texttt{Ellipse} procedure.

    %At low surface brightness regime, the final profile can be sensitive to several 
    %configuration parameters of \texttt{Ellipse}.  
    %After some tests, we choose to use 0.1 dex in logarithm as the step in semi-major 
    %axis length between successive ellipses, and we use the median pixel value over the
    %elliptical annulus after rejecting outlier pixels twice with $3\sigma$-clipping.
    %These parameters are selected to make the final profile less affected by any nearby
    %objects, and please see Appendix.~B for more details about the extraction of 
    %1-D profile.

    For physical (e.g.\ late-stage major merger) and unphysical (e.g.\ nearby 
    foreground galaxy or bright star) reasons, we can not extract reliable 1-D 
    profiles for small fraction of massive galaxies due to heavily masked out 
    central region. 
    This issue reflects an intrinsic limitation of the 1-D method. 
    It affects $48/375$ \rbcg{} galaxies, and a smaller fraction of \nbcg{} ones. 
    It is worth noting that this excludes most massive galaxies in major merger 
    process from the analysis. 
    We will come back to them in the future using 2-D modeling method.

    We correct these surface brightness profiles for Galactic extinction and 
    cosmological dimming, then integrate them to various radius to get the 
    luminosity within different physical apertures.  
    Although the $i$-band 1-D profile can in principle reach to $\sim 30$ \sb, 
    we notice the profiles at very low surface brightness part are often less 
    reliable by showing truncation or large fluctuation that are due to either 
    background uncertainty or contamination from bright neighbours.
    We therefore only consider the $<28.5$ \sb part of the profile here. 
    This conservative choice already allows us to study the region out to 
    $\sim 120$ kpc for massive galaxies in this sample.

    %We also apply the isophotes from $i$-band images to other bands in 
    %``force-photometry'' mode \texttt{Ellipse} run to get rough estimates of 
    %color profiles.  
    %Without taking the difference in seeing and background into account, 
    %these color profiles can not be used for physical discussion. 
    %But with the help of $K$-correction from the next section, we show that there 
    %is no systematic difference in color gradient between \rbcg{} and 
    %\nbcg{} sample.

%% ------------------------------------------------------------------------------------ %%

\section{Stellar Masses and Stellar Mass Density Profiles}
    \label{sec:mstar}

\subsection{Stellar Masses from SED Fitting}
    \label{ssec:isedfit}

    To convert the luminosity into stellar mass estimates, we assume that these massive 
    galaxies can be well described by an average \m2l{}. 
    This is a reasonable assumption considering that they are ETGs that are dominated by 
    old stellar population and are known to have shallow color gradients. 
    We will further justify this point using the average color profiles in Section
    \ref{sec:discussion}.

    We use the broadband Spectral Energy Distributions (SEDs) fitting 
    (see \citealt{Walcher2011} for a recent review) code 
    \texttt{iSEDFit}\footnote{http://www.sos.siena.edu/~jmoustakas/isedfit/} 
    (\citealt{Moustakas13}) to estimate the average \m2l{} and $k$-corrections using
    5-band HSC \cmodel{} fluxes under forced-photometry mode. 
    Although \cmodel{} tends to underestimate the total flux for bright, extended 
    objects, the forced-photometry results still provides accurate \emph{average} color 
    of the galaxy as it constrains the behaviour of the model using the optimized 
    reference one and taks the PSF convolution into account
    (e.g.\ Huang\etal~in prep.~).

    \texttt{iSEDFit} takes a simplified Bayesian approach. 
    In short, it first generates a large grid of SEDs from synthetic stellar population 
    models by drawing randomly from the prior distributions of relevant parameters 
    (e.g.\ age, metallicity, dust extinction, and star formation history).
    Based on these models, it uses the observed photometry and redshift to compute the 
    statistical likelihood, and generate the posterior probability distribution (PDF) 
    functions of each parameter.  
    To get the best estimate of certain parameter, \texttt{iSEDFit} ``integrates'' the 
    full PDF over all the other ``nuisance'' parameters.
    Then, the median value of the resulting marginalized PDF is used as the best value, 
    while the 1-$\sigma$ uncertainty is derived from the cumulative PDF. 
    Please refer to \citet{Moustakas13} for technical details and performance of 
    \texttt{iSEDFit}.

%% ------------------------------------------------------------------------------------ %% 
    In this work, we derive average \m2l{} using the Flexible Stellar Population 
    Synthesis\footnote{http://scholar.harvard.edu/cconroy/sps-models}
    (FSPS; \texttt{v2.4}; \citealt{FSPS}, \citealt{Conroy2010}) model based on the MILES
    \footnote{http://www.iac.es/proyecto/miles/pages/stellar-libraries/miles-library.php}
    (\citealt{MILES1}, \citealt{MILES2}) stellar library and \citet{Chabrier2003} 
    IMF between 0.1 to 100 \msun. 
    We use a delayed-$\tau$ model with stochastic star burst as the form of star 
    formation history (SFH), and choose a set of reasonable parameters after some tests.  
    Such form of SFH is appropriate for massive galaxies at low redshift 
    (e.g.\ \citealt{Kauffmann2003}). 
    For stellar metallicity, we assume flat distribution between 0.004 to 0.03 (which is 
    the highest metallicity allowed by FSPS models).  
    And, we adopt the \citet{Calzetti2000} extinction law with a order two Gamma 
    distribution of $A_{V}$ between 0 to 2 magnitude.
    Since most galaxies in both samples are red, quiescent galaxies, the results are 
    not very sensitive to parameters related to SFH and internal dust extinction. 
    To achieve reasonable sampling across these parameters, we generate 250000 models.

    We construct five band SED using the forced-photometry \cmodel{} magnitude corrected 
    for the Galactic extinction. 
    As for the photometric error, the current \cmodel{} photometry underestimates 
    the flux errors of bright galaxies as it only includes statistical error, not the 
    systematic uncertainties in the model-fitting process.  
    From tests of synthetic objects, we find that the average accuracy of \cmodel{} 
    photometry for bright galaxy is roughtly at 1\% level. 
    Therefore, we supply \texttt{iSEDFit} with simplified flux errors assuming $S/N = 100$ 
    for $riz$ bands, and $S/N = 80$ for $gY$ bands (on average, images in $gY$ bands are 
    shallower in depth and/or have higher background noise).  
    The typical uncertainty of \logms{} for both samples is around 0.08-0.10 dex at the 
    high-\mstar{} end. 
    Please see Appendix\ref{app:B} for more detailed discussions of the SED fitting
    results.  
    %In Fig.~3, we show an example of SED fitting result. 
    %\song{Not sure if we need to show one example, but put one here for now.}

%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}[t!]
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_sample_stats}
      \caption{\textbf{Left}: The \logms{}-$g-r$ color relation of the \rbcg{} 
          (red circle; detaield format is the same with the right panel of 
          Fig.\ref{fig:smf1}) and \nbcg{} (grey dots) samples.
          We apply the $k$-corrections from \texttt{iSEDFit} fitting to the colors.~~
          \textbf{Middle}: the histograms of \mtot{} for the \rbcg{} (orange-red) and 
          \nbcg{} (grey-black) samples at both $z>0.2$ (step-filled histogram) and 
          $0.3 \leq z \leq 0.5$ (stepped histogram). 
          The vertical lines in both left and middle figures highlight the 
          $11.6<$\logmtot{}$<11.9$ mass range that will be used in the comparison of 
          the \mtot{}-matched samples.~~
          \textbf{Right}: the histograms of the redshift for the \rbcg{} and 
          \nbcg{} galaxies in both \logmtot$>11.2$ and $11.6<$\logmtot{}$<11.9$
          mass bins.
          The vertical lines highlights the $0.3\leq z \leq 0.5$ redshift range 
          \song{Will move to new Appendix later; but the figures are updated here; 
          I will make sure to use consistent symbols, colors, and legends.}
          \alexie{Move this figure to the appendix. It is not clear to be that we need this Figure anyway. We can say that we make matched samples in the text. I think that is enough. If the referee wants to see the Figure, we can show him or her. But I think it just adds clutter.}.
      }
      \label{fig:sample_stats}
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

\subsection{Comparison with \texttt{S82-MGC}}
    \label{ssec:s82}

    Given the heterogeneous nature of the redshift resources for these samples, we 
    further investigate their \mstar{} completeness via comparing with galaxies that are 
    in common with the \texttt{S82-MGC} sample. 
    The \texttt{S82-MGC} sample matches the deeper SDSS photometric data in the Stripe 82 
    region (\citealt{Annis2014}) with the near infrared data from the United Kingdom 
    Infrared Telescope Infrared Deep Sky Survey (UKIDSS; \citealt{Lawrence2007}). 
    The deeper photometry and better photo-$z$ make the \texttt{S82-MGC} sample complete 
    to \logms{}$\geq 11.2$ at $z<0.7$.

    The match between the \texttt{hscPho} sample and the \texttt{S82-MGC} one results in 
    20453 galaxies at $0.3 \leq z \leq 0.5$ (referred as \texttt{s82Pho} sample).  
    We estimate their \mstar{} using \texttt{cModel} SED in exactly the same way. 
    The \mstar{} using HSC photometry shows tight correlation with ones based on the
    \texttt{S82-MGC} SED (five optical bands from SDSS and NIR data from UKIDSS; and 
    \texttt{S82-MGC} also used \texttt{iSEDFit} under slightly different assumptions).  
    Then we estimate the volume densities distributions of galaxies in \rbcg{}, \nbcg{}, 
    and \texttt{s82Pho} samples (left panel of Fig.\ref{fig:smf1}) using rough estimates 
    of the survey areas they occupied (since we only care about the relative shapes of 
    the density distributions). 
    And, we estimate the uncertanties of these distributions using a 10000 times 
    bootstrap resampling. 
    The distribution of \nbcg{} sample starts to deviates from the \texttt{s82Pho} one 
    below \logms{}$< 11.6$, indicating that the sample starts to become incomplete within
    $0.3 \leq z \leq 0.5$. 
    As for the \rbcg{} sample, their mass completeness should be better thanks to the 
    reliable \redm{} $z_{\lambda}$. 
    Its behaviour is quite consistent with the mass function of galaxies in massive 
    halos with a narrow \mhalo{} distribution (\addref).   
    Later, we will see that the \cmodel{} photometry on average underestimate the 
    \mstar{} of galaxies with \logms{}$>11.5$ by $-0.1$ dex.
    Therefore, we conclude that the \nbcg{} becomes not perfectly complete below 
    \logms{}$< 11.7$.  
    This is most likely due to the incompleteness of the BOSS spec-$z$ sample. 
    Although it is unlikely that the incompleteness will bias the results of our 
    comparisons, we will bear this in mind, and match the two samples carefully in 
    \logms{} and redshift space before comparing them.

%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}[bt!]
      \centering 
      \includegraphics[width=\textwidth]{fig/average_mass_profiles_fsps1_A}
      \caption{
      	\song{The figures are updated as you suggested; But I want to point out that
        the two samples have different mass completeness (\rbcg{} has photo-$z$ ones), and 
        I simply combine them.  The table at the end will be updated, and I will provide 
        the average profiles from our key figures too.}
      	\alexie{I have a suggestion that I think will make this figure more simple and wil also help with the structure of the text. In the left hand side, don't bin by $\lambda$. Instead, only make mass bins. That way you don't have to worry about getting into the matched samples at this point because you wont be showing the enviromental dependence. And when comparing on the rigth hand side, it is not clear which lines we want to compare with (are previous results for BCgs, for field galaxies,...? readers don't know). I think it will be a more straightforward comparison just to show the stellar mass bins here. For our stellar mass bins, you only need the labels for our data once on the left hand side.}. 
      	Left: Median \mden{} profiles of galaxies in different \mtot{} bins:
      	[11.4, 11.6] (short-dashed line), [11.6, 11.8] (solid line), and 
      	[11.8, 12.0] (long-dashed line). 
      	Here we combine the \rbcg{} and \nbcg{} samples, and we also show a random subset 
      	of individual profiles in the background.
      	The shaded region highlights the region that could be affected by PSF.
        Two vertical lines label the radius of 10 kpc (thin, dotted line) and
        100 kpc (thick, dash line). ~~~ 
        Right: comparison between the average \mden{} profiles with the ones from 
        previous observations and simulations, including: 
        1) average profile of massive elliptical galaxies at $z\sim 0$ from 
        \citet[][Cyan, solid]{Huang2013a}; 
        2) average profile of massive galaxies at $0.25 \leq z < 0.50$ observed by 
        \textit{HST} from \citet[][Red, long-dashed]{Patel2013} ;
        3) average radial stellar distribuitions in massive halos using simulation and 
        particle tagging method (\citealt{Cooper13}; Purple, short-dashed).}
      \label{fig:avg_prof}
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}[t!]
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_prof_m100A}
      \caption{\alexie{So this is our main figure, right? We really need to make this stand out. Remove all the matched sample plots on the left (appendix?). We only need to say we do the matched samples in the text, we don't need a figure to back this up. Then, you have a seperate figure for $M10$. Why not combine the two into a single four panel figure? I think that would capture the main result pretty well, and show M10 and M100 side by side.} Comparison of the \mden{} profiles for \mtot{}-matched samples of \rbcg{}
      (orange to red) and \nbcg{} (grey to black) galaxies within $11.6<$\logms{}$<11.9$.
      \textbf{Left figure} shows the details of the \mtot{}-matching process.  
      On the top panel, we show the overall distributions of \rbcg{} (light orange boxes) 
      and \nbcg{} (light grey dots) galaxies on the \mtot{}-$z$ plane.  
      And, we match the two sample in the \mtot{}-$z$ space outlined by the shaded region.
      We highlight the \rbcg{} galaxies in this region using bigger boxes in red frames, 
      whose size reflects the $P_{\mathrm{Cen}}$ value.  
      We also color-code them using the richness ($\lambda$) of the host cluster. 
      The matched \nbcg{} galaxies are highlighted using darker color and bigger dots. 
      To further evaluate the matching results, we show the distributions of \mtot{} 
      (middle panel) and redshift (bottom panel) separately. 
      On both panesl, we show the histograms along with their kernel density 
      distributions.  
      And, on the top of each panel, two sets of short vertical lines highlight the median 
      value (solid) and the inter-quartile (dash) of each distribution.~~~
      \textbf{The figure on the right} shows the results of the profile comparison.  
      On its upper panel, we show the \mden{} profile of each galaxy using very light 
      color in the background.  
      We highlight the median profile and its corresponding uncertainties using thick 
      solid line with darker color and shaded region. 
      Other formats are the same with Fig.\ref{fig:avg_prof}.
      Meanwhile, we hightligh the difference between the median profiles and its 
      uncertainty on the bottom panel (brown solid line and shaded region).
      To test the significance of the differential profile, we perform statistical tests 
      by comparing the median profiles of two random groups that are drawn from the 
      mixed sample, and have the same sizes with the matched \rbcg{} and \nbcg{} ones.
      Repeating this process many times, the median random differential profile 
      (black solid line), their 1-$\sigma$ (dark-grey shaded region) and 3-$\sigma$
      (light-grey shaded region) are highlighted.
      \song{Will make a new 4 panels figures here; but I want to make some changes as 
      if we simply put the current ones together, it looks bad...}}  
      \label{fig:prof_m100_A}
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

\subsection{Stellar Mass Corrected for Total Luminosity}
    \label{ssec:mtotal}

    Using the best-fit stellar mass from \texttt{iSEDFit} (referred as \mcmodel{}), 
    we estimate the average \m2l{} in $i$-band, then use that \m2l{} to convert the 
    1-D luminosity density profiles into stellar mass density profiles; and 
    also convert the luminosity within 10 and 100 kpc apertures into 
    corresponding stellar mass estimates (referred as \minn{} and \mtot{}). 
    From now, we use \mtot{} as the new proxy of ``total'' stellar mass of these 
    galaxies.  
    And we also derive the $k$-corrected luminosity and colors from the results.
    In Appendix\ref{app:B}, we also show the outputs like the average stellar age, 
    metallicity, and internal dust extinction all behave reasonably for both 
    samples, but will not use them for further scientific analysis.

    As expected, the integration of 1-D profile out to very large radius help 
    recover more luminosity (stellar mass) compared to the \cmodel{} results.
    We highlight this in the right panel of Fig.\ref{fig:smf1} as we show the 
    distributions of differences between \mtot{} and \mcmodel{}, and their relations 
    to the \mtot{}.  
    For both samples, we see the ``extra mass'' recovered by 1-D photometry 
    increases with \mtot{}, therefore this improvement impacts the \rbcg{}
    sample more.  
    This is basically consistent with the fact that the structure of massive ETGs 
    depends on its stellar mass in a way that more massive ones tends to be 
    more extended (e.g.\ \addref).  
    Apparently, such mass-dependent difference between \mtot{} and \mcmodel{} will 
    result in difference of the SMF. 
    As the slope and normalization of SMF at high mass end is very sensitive 
    to both cosmology and interesting baryonic processes such as AGN feedback
    (\addref), they are particularly important in constraining the galaxy evolution
    model, and therefore became the center of some intense arguments (\addref).  
    Although the jury is still out on this topic, it has become clear that 
    popular results using SDSS photometry (\addref) underestimate the total 
    luminosity (stellar mass) of massive ETGs.  
    However, past works (e.g.\ \addref) often relied on either stacking of 
    shallow images or the extrapolation of models to investigate this effect. 
    Using the deep HSC images, we have the potential to answer this question 
    much better. 
    Detailed studies of SMF deserves more careful investigations of many 
    systematic issues (e.g.\ \addref), so we just show the impact of the 
    ``extra mass'' on the volume density distributions of both samples 
    (Fig.\ref{fig:smf1}, left panel).  
    Generally speaking, the stellar mass corrected for total luminosity 
    shifts the distribution toward the higher mass end, and slightly modify
    the slope. 
    People who want to use HSC photometry or other \cmodel{}-like photometry to 
    study the properties and evolution of SMF should be aware of such effect.

    As mentioned earlier, our assumption of using an average \m2l{} ignores its
    radial variation.   
    It is well known that massive ETGs have negative optical color gradient which 
    indicates a gradient of \m2l{} (e.g.\ \citealt{LaBarbera2012}; \citealt{DSouza2015}),
    but the gradient is smooth and shallow out to a few times of the effective 
    radius (color gradient at the very outskirt is still not well quantified). 
    And, for the comparison between the \rbcg{} and \nbcg{} samples, 
    Our results should remain intact as long as there is no significant
    differences of color gradient between these two samples.
    We will discuss this more later, but initial results do suggest a smooth color
    gradient out to very large radius, and there is no systematic difference in 
    color gradients of the two samples.  
    Both suggest that the average \m2l{} approach should work reasonably well for
    our goals.

    And, we should mention that our approach is in principle very similar to the 
    one adopted by the GAMA survey (\citealt{Taylor2011}), where they start with 
    \mstar{} estimated using average \m2l{} from SED fitting results of
    PSF-matched aperture photometry, and later correct it with better estimate 
    of total luminosity.  
    However, the GAMA survey relied on multi-band single-\ser model fitting on 
    the SDSS images to get total luminosity (\citealt{Kelvin2012}). 
    It is therefore interesting to compare the \mstar{} (\mgama{} v.s. \mtot{})
    estimates for galaxies in common, given the differences in data and method. 
    Please see the Appendix\ref{app:C} for more details. 
    In short, we notice systematic differences between the two \mstar{} estimates, 
    and it is likely that the GAMA models miss fluxes in the stellar halo that 
    is beyond the depth of SDSS image.

    In the left figure of Fig.\ref{fig:sample_stats}, we show the \mtot{}-color 
    relations using the $k$-corrected $g-r$ color for the \rbcg{} and \nbcg{} 
    samples. 
    Both samples follow the same tight red-sequence with very little contamination 
    from star-forming galaxy in the ``blue cloud''.
    And, at fixed \mtot{}, we see little offset in color distributions of the two 
    samples suggesting that both samples consist of old quiescent galaxies with 
    similar average stellar population properties.  
    This is consistent with previous result that suggests the average stellar 
    population of massive central galaxy does not depend on \mhalo{} 
    (e.g.\ \citealt{Park2007}).  
    To look into the potential environmental dependence of structure, we will 
    focus on the mass range of $11.6 \le$\logmtot{}$\le 11.9$, where both samples 
    have acceptable completeness, and their \mtot{} distributions greatly overlap
    (see the normalized distributions of \mtot{} in the middle panel of 
    Fig.\ref{fig:sample_stats}). 
    Due to the different sources of redshift for the \rbcg{} and \nbcg{} samples, 
    the two samples have quite different redshift distributions 
    (right figure of Fig.\ref{fig:sample_stats}).
    Even within the $11.6 \le$\logmtot{}$\le 11.9$ mass bin, the redshift
    differences still differ from each other a little bit.  
    Apparently, the redshift distribution of the \nbcg{} sample skews toward 
    higher-$z$ end, primarily due to the contribution of BOSS spec-$z$.
    This could lead bias into the comparison of \mden{} profiles and other 
    properties between the two sample (please see Appendix\ref{app:D} for more 
    details).  
    We will address this via matching the two samples in \mtot{} and redshift
    distributions carefully before the comparisons.

%% ------------------------------------------------------------------------------------ %%

\section{Results}
    \label{sec:result}

\subsection{Comparison of Surface Mass Density Profiles}
    \label{ssec:sbp_compare}

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}[t!]
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_prof_m100B}
      \caption{Comparisons of the \mden{} profiles for \rbcg{} (orange-red) and \nbcg{} 
      	(grey-black) galaxies that are matched using proxies of total \mstar{}. 
        The formats are in consistent with the right figure of Fig.\ref{fig:prof_m100_A}.
        The differences are, here, the samples are matched in slightly differnt ways. 
        From left to right: a) using samples at lower redshift ($0.3 < z < 0.4$); 
        b) using \rbcg{} sample with $\lambda > 20$ instead of 30; 
        c) using \mstar{} within 150 kpc instead of 100 kpc.
        The results are broadly consistent with the one in Fig.\ref{fig:prof_m100_A}.
        \song{Considering to move to a new Appendix.} \alexie{This Figure can be moved to an appendix. It can also be summarized by saying in the main part of the paper that "we have tested that our results are robust to, the choice of the redshift range, the lower $\lambda$ cut, .....". I think it is probably enough to simple say this in the text. Not 1oo percent convinced you need a figure to abck this up.}}
      \label{fig:prof_m100_B}
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

\subsubsection{Internal Comparison and Comparison with Previous Works}
    \label{sssec:sbp_inter}

    As discussed earlier, although the mass-size scaling relation has been intensely 
    discussed related to the topic of environmental dependence of structure, it may not be 
    the best tool to investigate this problem.    
    Compared to the simple scaling relation, the detailed stellar mass density profiles 
    contain much richer structural details that can help us diagnose the role played by 
    different physical processes, including the environmental effect.

    Before the actual comparisons, we first show the general properties 
    of these 1-D profiles by separating both samples into different bins 
    of \mtot{} and redshift, also by comparing them with results from 
    literature (Fig.\ref{fig:avg_prof}).   
    For profiles in each bin, we derive the median profile along with its 
    uncertainty using bootstrap resampling method (5000 times). 
    The left panel of Fig.\ref{fig:avg_prof} focuses on different mass bins.  
    As expected, for both samples, higher \mtot{} moves the median mass 
    density profile upward a little in the inner region, but makes it 
    more extended in the outer part.
    In the mass range we explored ($\ge 10^{11.2} M_{\odot}$), most of these 
    ETGs are slow-rotating (e.g.\ \citealt{Cappellari13b}) giant ellipticals 
    with boxy inner isophotal shape (e.g.\ \citealt{Kormendy2009}), and 
    flattened density profile at the center (e.g.\ \citealt{Lauer07}), 
    but their structure in the outskirt clearly does \textbf{NOT} response 
    to stellar mass increase in a self-similar way.

    In principe, this is consistent with result from HST observations of 
    BCGs at $0.3 < z <0.9$ (\citealt{Bai2014}) and the claimed positive 
    correlation between luminosity and \ser index
    (e.g.\ \citealt{Savorgnan13})\footnote{But it does not mean such high 
    \ser index model works well for massive ETGs as they fail at the inner-most 
    region dramatically, and can not explain the radial variation of 
    isophotal shape}; it is also consistent with the picture that more 
    massive ETGs experienced more recent (minor) mergers.

\alexie{My comment in Figre \ref{{fig:avg_prof}} wil make this part unnecessary and will improve the flow of the paper.}    At the same time, such behaviour should make us very cautious about 
    any indication of ``environmental dependence of structure'' as it 
    may be degenerate with difference caused by stellar mass when the 
    two samples are not perfectly matched in mass.  
    This is exactly what we see in the median profiles of \rbcg{}
    and \nbcg{} in the same mass bins. 
    Although the comparison shows that \rbcg{} shows much more 
    extended outer envelope than \nbcg{}, the very similar profile
    in the inner $\sim 10$ kpc reveals that this is dominated by the 
    different mass distributions in two samples.

    In the right panel of Fig.\ref{fig:avg_prof}, we compare these median 
    profiles with a few past works.  
    \citep{Huang2013a}, derived the median stellar mass density profile 
    for a small sample of very nearby ellipticals from the 
    Carnegie-Irvine Galaxy Survey (CGS, \citealt{CGS1}).
    Individual profile and total luminosity were derived from 
    three-component 2-D models that describe both very inner and outer 
    luminosity distributions of these galaxies accurately. 
    The average stellar mass of this sample is around $10^{11.3} M_{\odot}$.
    Due to the proximity of this sample ($< 100$ Mpc), the average profile 
    is unaffected by seeing within $\sim 1$ kpc.
    Most galaxies of the CGS sample are not in any cluster.
    The median profile qualitatively agrees with the median profile of 
    \nbcg{} in the low mass bin, especially in the inner region. 
    Outside the inner 15 kpc, the CGS median profile shows a slightly more
    prominent outer envelope.  
    While this could simply reflect the small size of CGS sample ($\sim 30$),
    interestingly, it is also consistent with the expectation if the 
    mild mass growth from $z\sim 0.4$ mostly happened at the outskirt.   
    The CGS images are already slightly deeper than SDSS images in $r$-band,
    however, the median profile can only reach to $\sim 50$ kpc (with much 
    larger uncertainty compared to this work) for ETGs within $\sim 100$ Mpc.
    Such comparison clearly highlights the improvement made by the deep HSC 
    images as individual profile of $z\sim 0.5$ galaxy is reliable out to 
    at least 100 kpc.

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}[t]
      \centering 
      \includegraphics[width=14.0cm]{fig/redbcg_prof_m100C}
      \caption{Comparisons of the \mden{} profiles for \rbcg{} (orange-red) and \nbcg{} 
      	(grey-black) galaxies in lower (left; [11.5,11.70]) and higher 
        (right; [11.7, 11.9]) \mtot{} bins. 
        Other formats are in consistent with the right figure of 
        Fig.\ref{fig:prof_m100_A}.
        The difference in median profiles is more significant in higher \mtot{} bin.}
      \label{fig:prof_m100_C}
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

    At the similar redshift with our sample, we compare with mass density 
    profile extracted from stacked images of massive ETGs at $0.25 < z < 0.50$ 
    using HST/ACS images (\citealt{Patel2013}).  
    These galaxies are selected at constant cumulative number density, and 
    as progenitors of $z=0$ massive ETGs.  
    The average stellar mass is $\sim 10^{11.2} M_{\odot}$ according to 
    their estimates.  
    However, given the shallower depth of the ACS images and the usage of the 
    BC03 model (each could cause -0.1 dex mass offset compared to this work), 
    this sample should be comparable to the \nbcg{} sample in the
    lowest mass bin, and the comparison of their median profiles does reflect
    that.  
    Moreover, since the profile from HST/ACS image is not bothered by PSF 
    within 1 Kpc, the comparison illustrates that the HSC median profiles 
    in our redshift range are indeed not affected by seeing outside the 
    shaded region. 
    In fact, as we suggested, our estimate is quite conservative, the profiles 
    within 5 kpc should be reliable.

    Besides these observations, we also compare with the predicted average 
    stellar mass density profile for central galaxies of massive halos 
    ($13.5 < \log M_{200,c} < 14.0$) in simulation (\citealt{Cooper13}). 
    This is achieved by combining the detailed assembly information of halos 
    from dark-matter-only simulation with semi-analytic model and 
    particle-tagging technique (\citealt{Cooper10}).
    Although the physical resolution and detailed baryonic processes are 
    not as ``realistic'' as state-of-art hydro-simulation, it is very 
    efficient in providing rough stellar mass distributions for large number 
    of massive halos. 
    Without any adjustment, the profile is quite similar to the \nbcg{}
    sample in the $11.5 < \log M_{\star} < 11.7$ bin within inner 20 kpc; 
    but it predicts a too significant outer envelope for its average halo mass.
    Without going into details to find the cause of such discrepancy in this 
    work, the comparison already suggests that the comparison between deep 
    observed mass density profiles with the ones from modern simulations is 
    going to be quite interesting, especially in the outskirt.

    We summarize the median profiles in Fig.\ref{fig:avg_prof} in Table.~1,
    and all the above median profiles are available  
    \href{https://github.com/dr-guangtou/hsc_cenHighMh/tree/master/profiles}{here}.

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}[t!]
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_prof_m10C}
      \caption{\alexie{There is a lot of redundancy in the Figures. I'm going to suggest to bring all the main figures together in a 4 panel figure?}. Comparisons of \mden{} profiles of \rbcg{} (orange-red) and \nbcg{} 
          (grey-black) samples that are matched using \minn{} instead of \mtot{}. 
          We perform the match at $11.2<\log (M_{\star,10\ \mathrm{kpc}}/M_{\odot})<11.6$.
          \textbf{Left figure} shows the matching results in the same format with 
          the left figure of Fig.\ref{fig:prof_m100_A}.  
          The only difference is \mtot{} is replaced by \minn{}. ~~~
          \textbf{Middle figure} summarizes the profile comparisons in the same format 
          with the right figure of Fig.\ref{fig:prof_m100_A}.~~~
          \textbf{Right figure} is very similar to the middle one, except we show the 
          profiles that are normalized using the \minn{} value to highlight the 
          scatters of \mden{} at different radius. 
          \alexie{the tow figures actually look pretty similar. I think most people will not notice the difference. Pick one and go with that. I guess I have a preference for the unnormalized one. Your mathced sampeles take care of the reason we made the normalized versions. (mean mass was different between samples.)}
          \song{Ok, will only use the unnormalized ones later; The point of normalized one is to 
          reduce the effect of the \mstar{} width of the mass bin; it is useful when I 
          discuss the dispersion of \mden{} at outer radius; I could simply emphasis that 
          in the text, or put some figures in the Appendix....how many appendix is too
          many}}
      \label{fig:prof_m10_A}
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %%

\subsubsection{Matched Samples Using \mtot{} \alexie{This it not the right title for this section!! The point here is not to make matched samples. The point here is to look at the enviromental signature.}}
    \label{sssec:sbp_mtot}

\alexie{Most of the text below describing the procedure for making the mathced samples can go into an appendix. It distracts from your main results! And people have been making mathced samples for years!! Most of the text in between the red text can be moved else where or simplified.}

  \textcolor{red}{FROM HERE}

  As stellar mass is considered the most important parameter in determining the 
    structure and other properties of massive galaxies, it is crucial to make sure 
    the comparison is conducted at ``fixed stellar mass''. 
    And, since we directly compare the stellar mass distributions across very large 
    range in radius, it is also important to make sure that differences in physical 
    size of PSF (for more discussion on this issue, please see Appendix\ref{app:C}) 
    and imaging depth do not affect the result.    
    In practice, we achieve these by matching the \rbcg{} and \nbcg{} samples in 
    the distributions of \mstar{} and redshift in the mass range where both 
    samples have decent completeness.  
    Since the \rbcg{} sample is much smaller in size, we match the \nbcg{} sample to it 
    by searching for the $N$ nearest neighbours on the $M_{\star}$-redshift 
    plane using the KDTree algorithm provided by \texttt{scikit-learn} Python 
    library (\citealt{scikit-learn}). 
    The quality of the matched sample is evaluated by not just the median values 
    of stellar mass and redshift, but also the kernel density distributions (KDE) 
    of these two properties.
    For \mstar{}, we use a Gaussian kernel with width equals to the typical 
    uncertainty of the mass estimate (0.06-0.10);
    and for redshift, we choose 0.025 as the width of the Gaussian kernel. 
    As we only keep unique \nbcg{} galaxies in the matched sample, we manually adjust 
    the value of $N$ to achieve the most similar distribution. 
    In case that the distribution of stellar mass or redshift for \rbcg{} is 
    bi-model, we also try to split the sample into two, and match them separately.
    Normally $N$ is between 3 to 8.

    \mstar{} within different radius traces different physical processes and 
    different epochs in the assembly history.  
    In this section, we match the two samples using our proxy of ``total'' stellar 
    mass, which is the \mstar{} within 100 kpc radius.  
    This choice reflects the stellar mass distributions we can safely measure using 
    model-independent approach given the current depth of the image and the accuracy 
    of sky background subtraction.
    For galaxies at $11.6 \leq \log(M_{\star}/M_{\odot}) < 11.9$, 100 kpc equals to 
    5-8 times of their effective radius, hence should enclose most their stellar mass.
    Also, for a fraction of massive \rbcg{} galaxies, the intra-group/cluster light
    (IGL/ICL) could dominate their mass profiles outside 100 kpc (\addref), and 
    complicate the comparison with the \nbcg{} galaxies.  
    We will discuss these issues later in Section \ref{sec:discussion}, but in 
    conclusion, the proxy of total \mstar{} and the potential ICL component should 
    not affect the results.

    \textcolor{red}{TO HERE}

    \alexie{This is more how you should start your paragraph! It can be as simple as "We match the sample (see appendix) and show the results in Figure xx.}
    \song{Got it! will update later}
    We show the results of the comparison in Fig.\ref{fig:prof_m100_A}. 
    The left panel highlights the properties of the matched \rbcg{} and \nbcg{} 
    samples.
    Given the typical uncertainty of stellar mass, the two samples are well 
    matched in \mtot{}; and their redshift distributions are broadly 
    consistent with each other.  
    We also check their distributions of $k$-corrected colors ($g-r$), and confirm 
    that they have very similar average color distributions as well.  
    For the 45 \rbcg{} galaxies, we have 229 unique \nbcg{} galaxies in the 
    matched sample.
    On the right side, we plot the individual stellar mass density (\mden{}) profile 
    of \rbcg{} and \nbcg{} galaxies along with the median profiles of both samples. 
    The uncertainties of the median profiles are derived using 5000 times of 
    bootstrap resampling.
    As one can see, we can comfortably trace the \mstar{} distribution of these massive 
    galaxies out to 100 kpc at individual level, which gives us huge advantage in 
    studying the statistical properties of their outer envelopes. 
    Mass profile out to such large radius was only available for large sample of 
    massive galaxies through image stacking method (\addref) which suffers from certain
    systematic issues. 
    Although the \mden{} profiles of many galaxies extend well beyond the 100 kpc radius, 
    we notice that some profiles show sign of unphysical truncation that is caused 
    by inaccurate background subtraction.  
    Therefore, we will not include profiles outside 100 kpc in the comparison, even 
    though the median profiles within 200 kpc still behave normally.

    Once we match the distributions of \mtot{}, the \mden{} profiles of massive 
    galaxies in the \rbcg{} and \nbcg{} samples \textbf{greatly overlap with each 
    other over the entire radius range}. 
    At fixed ``total'' stellar mass, massive central galaxies of more massive 
    halos do not form a unique population comparing to the ones from less massive 
    halos in term of the stellar mass distributions.

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}[t!]
      \centering 
      \includegraphics[width=16.0cm]{fig/redbcg_m100_m10_compare}
      \caption{Three-color images for a subsample of massive galaxies at similar redshift
      		($\sim 0.4$), and with similar \mstar{} inside inner 10 kpc (indicated by the 
            dash-line cicle on top-left figure; 
            $11.2<\log (M_{\star,10\ \mathrm{kpc}}/M_{\odot})<11.3$). 
            However, they span quite a large range in \mstar{} within 100 kpc 
            (highlighted by the solid bar on the top-left figure). 
            From top-left to bottom-right, their \mtot{} increases from 
            $10^{11.2} M_{\odot}$ to $10^{11.7} M_{\odot}$.
            The three galaxies from \rbcg{} sample are highlighted via red frames.}
      \label{fig:m100_m10_color}
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

    At the same time, thanks to the high quality individual profile from HSC image, 
    we can also spot interesting differences in the median profiles of the \mtot{} 
    matched \rbcg{} and \nbcg{} samples.  
    In details, it seems that central galaxy in more massive halos tends to have 
    a slightly flattened inner density profile and possess more significant outer 
    envelope.   
    To highlight such subtle structural features, we show the difference between 
    the two median profiles and its uncertainty in the bottom panel. 
    Given the noticeable uncertainties of \mtot{} and $\lambda$, and the current small 
    sample sizes, we also perform statistical test to confirm the robustness of the
    result: we mix the $N_{\mathrm{r}}$ \rbcg{} galaxies and the $N_{\mathrm{n}}$ \nbcg{}
    ones together, then randomly draw $N_{\mathrm{r}}$ galaxies with putting-back, 
    compute the difference between the median profile of this sample and the \nbcg{} 
    sample, and repeat this process 2000 times.  
    Comparing with the statistical distributions of the differential profiles from 
    this test (grey shaded region), we can now conclude that the structural 
    differences between \rbcg{} and \nbcg{} samples are much more significant than 
    any statistical fluctuation given the current samples.  
    And, apparently, the ``transition radius'' where the median profiles of \rbcg{} 
    and \nbcg{} sample have the same \mden{} is $\sim 15$-20 kpc, which is quite 
    close to the expected $R_{\mathrm{e}}$ of ETGs at this stellar mass.

    To further test the robustness of this interesting result, we repeat above 
    procedures to samples with slightly different definition.  
    The results are shown in Fig.\ref{fig:prof_m100_B}: 
    (a). At higher redshift, the profile is more affected by the seeing at inner 
    region, and by the imaging depth in the outskirt.  
    Therefore, in the left panel, we compare the \rbcg{} and \nbcg{} samples at 
    $0.3 \leq z < 0.4$, and the results are very similar.
    (b). We also make the comparison using a \rbcg{} sample with lower average 
    halo mass ($\lambda \geq 20$), the results are still stable (middle panel). 
    We also check whether the structural differences are driven by small fraction 
    of \rbcg{} galaxies in very massive clusters.  
    After removing the \rbcg{} galaxies in clusters with $\lambda \geq 40$, the 
    differences are as significant as above.  
    (c). As noted before, the \mtot{} is just a proxy of the total stellar mass. 
    Given the differences we find, at fixed \mtot{}, \rbcg{} galaxy tends to have 
    more prominent outer envelope outside 100 kpc than the \nbcg{} one. 
    Hence their real ``total'' stellar mass could also be slightly larger, and 
    result in bias in the comparison.  
    In the right panel, we make the comparison using the maximum stellar mass from 
    the integration of the \mden{} profile instead of the \mtot{}.
    In this case, the differences between the median profiles become slightly 
    less significant as expected.  
    But the systematic trends, especially the differences in the low mass density 
    outskirt are still very stable.  
    All these tests confirm that we robustly detect subtle, but systematic 
    structural dependence on halo mass of massive galaxies.   
    The fact that it requires such careful comparison to reliably reveal any 
    potential halo mass dependence already suggests that the role environment
    played in shaping these massive galaxies is not crucially important.  
    At the same time, the systematic differences we find, especially the more 
    extended stellar envelope of massive central galaxy in more massive halos, 
    seem to be consistent with the expectation of richer (minor) merging history
    in denser environment. 
    We will discuss these more in Section \ref{sec:discussion}.

    We also explore the possible \mtot{} dependence of such difference.  
    Limited by the small sample we have, we can only afford to separate the 
    samples into two \mtot{} bins 
    ($11.5 \leq \log (M_{\star,\ 10\mathrm{kpc}}/M_{\odot}) < 11.7$ and 
     $11.7 \leq \log (M_{\star,\ 10\mathrm{kpc}}/M_{\odot}) < 11.9$).  
    After performing the same procedures of sample matching and comparison, 
    we show the results in Fig.\ref{fig:prof_m100_C}.  
    Although the smaller sample leads to larger statistical uncertainties, 
    it is still interesting to see that the structural differences seem to 
    be more significant in the higher \mtot{} bin.  
    For the lower \mtot{} bin, the difference in the inner region becomes quite 
    uncertain, while there is still evidence that suggest difference in the 
    outskirt.  
    This result also has interesting implications in studying the assembly 
    of massive galaxies, and is worth further investigation with larger sample
    in the future.

%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure}[bt!]
      \centering 
      \includegraphics[width=\columnwidth]{fig/redbcg_prof_m10B}
      \caption{Comparisons of unnormalized \mden{} profiles of 
      	  $\log (M_{\star,100\ \mathrm{kpc}}/M_{\odot}>11.5$ \rbcg{} (orange-red) 
      	  and \nbcg{} (grey-black) samples that are matched using \minn{}.
          Except for the difference in \mtot{}-limit of both samples, other formats are 
          the same with the middle figure of Fig.\ref{fig:prof_m10_A}.
          \song{The reason I did this test is because the \minn{} matched \nbcg{} 
          sample without any constraint will have a lot of galaxies with 
          \mtot{}$<10^{11.5} M_{\odot}$ in the sample; They are in the 
          \mtot{}-incomplete range, and it is harder to argue that they have similar 
          mass in the `in-situ' component with the \rbcg{} ones. 
          If you think this is weird, another choice is to do the match at \minn{} in 
          between [11.4, 11.6], so that most galaxies have 
          \mtot{}$>10^{11.5} M_{\odot}$.}}
      \label{fig:prof_m10_B}
  \end{figure}
%% ------------------------------------------------------------------------------------ %%

\subsubsection{Matched Samples Using \minn{}}
    \label{sssec:sbp_minn}

    \song{Got it! will update later}
    \alexie{This paragraph goes in the discussions section. The results section should be "We now do this to the data and here is the Figure"} As suggested by the popular two-phase formation scenario of massive galaxies, 
    the inner 5-10 kpc of these galaxies (within 0.5-1$xR_{\mathrm{e}}$) is 
    dominated by stars formed in intensive dissipative processes at high redshift, 
    and is less affected by the succeeding merging events.  
    This picture is broadly supported by the redshift evolution of \mden{} profile
    of massive galaxies (\addref), structure decomposition of nearby massive galaxies 
    (\addref), and their radial distributions of stellar population (\addref).      
    Certainly, major merger can induce violent relaxation process that modifies the 
    stellar mass distribution even in the central region, and must happen to 
    these massive galaxies in last 6-8 Gyrs, it may not invalidate the above assumption.
    For galaxy this massive, the last major merger event is highly likely to be
    non-dissipative, and the redistribution of stars is basically according to their 
    binding energy in the host halo.  
    The inner region of the final merger remnant is still mostly composed 
    of the ``in-situ'' stars from the two progenitors.

    Therefore, it is interesting to compare the \rbcg{} and \nbcg{} samples that are 
    matched using mass within the inner region.  
    In this work, we choose to use the mass within inner 10 kpc (\minn{}). 
    As we can see in previous profile comparison, \minn{} is not affected by the 
    physical size of PSF out to $z=0.5$.  
    We use the same procedure to match the \nbcg{} galaxies to the \rbcg{} ones using 
    \minn{} (within $11.2 \leq \log (M_{\star,\ 10\mathrm{kpc}}/M_{\odot}) < 11.6$) 
    and redshift ($0.3 \leq z < 0.5$).  
    For the 56 galaxies in this \rbcg{} sample, we achieve excellent matching 
    result using 375 \nbcg{} galaxies (see Fig.\ref{fig:prof_m10_A}).  
    Using the same method, we show their individual profiles, and the comparison of 
    their median \mden{} profiles in Fig.\ref{fig:prof_m10_A}.  
    Unlike the \mtot{} matched samples, here we see very striking differences that 
    are already very significant even without any statistical test.     
    As we can see, when matched using \minn{}, the \mden{} profiles of \rbcg{} and 
    \nbcg{} galaxies have quite similar \mden{} profiles in the inner 5-10 kpc, 
    in great contrast of the differences at outer region where the \rbcg{} galaxies 
    show much more extended envelope.      
    Besides the difference in the median profiles, it is also worth discussing 
    the distributions of individual \mden{} profiles. 
    Combining the \rbcg{} and \nbcg{} samples together, it is easy to notice that 
    the dynamical range of \mden{} at fixed radius is much larger in the outskirt. 
    This becomes even more clear when we further normalize each profile using 
    the \minn{} value (see Fig.\ref{fig:prof_m10_A}).   
    For both \rbcg{} and \nbcg{} samples, we find that their outer \mden{} profiles 
    clearly show much larger diversity comparing to the inner region.

    Putting together, these results indicate that massive central galaxies with 
    similar \minn{} and inner mass profiles can span a huge range in total stellar 
    mass, and can have very different mass distributions in the outskirt. 
    We further highlight this by showing the 3-color images of randomly selected 
    massive central galaxies (see Fig.\ref{fig:m100_m10_color}) that 
    have similar \minn{} 
    ($11.1 \leq \log (M_{\star,\ 10\mathrm{kpc}}/M_{\odot}) < 11.2$)
    but different \mtot{}.   
    From the top-left to the bottom-right, the \mtot{} of these galaxies increases
    from $10^{11.22} M_{\odot}$ to $10^{11.75} M_{\odot}$.

    Since the two samples are matched using \minn{}, the \nbcg{} sample starts to 
    include galaxies with 
    $11.2 \leq \log (M_{\star,\ 100\mathrm{kpc}}/M_{\odot}) < 11.6$.  
    On one hand, they are likely to be the central galaxies in halos that are 
    much smaller than the ones in \nbcg{} sample, which still mostly consists of 
    galaxies with $\log (M_{\star,\ 100\mathrm{kpc}}/M_{\odot}) \geq 11.6$.  
    Hence, above results may hint that the outer \mden{} profile of central galaxy 
    could have a clear dependence on the halo mass.
    This is a very interesting clue that deserves more investigations including 
    comparison with simulations.  
    But, on the other hand, we need to recognize that the mass completeness of 
    our current \nbcg{} sample is still not satisfying; and in this lower \mtot{} 
    range, small fraction of satellite contamination should be expected even 
    though we already excluded satellites in known cluster using the \redm{} catalog. 
    To naively test the robustness of these results, we match the two samples using 
    \minn{} again, but only include galaxies with 
    $\log (M_{\star,\ 100\mathrm{kpc}}/M_{\odot}) \geq 11.5$.  
    Comparison between these two more complete, purer samples of massive 
    central galaxies at fixed \minn{} reveals very similar behavior
    \footnote{In fact, their median profiles become even more similar in the 
    inner region} (see Fig.\ref{fig:prof_m10_B}), supporting the robustness of the 
    results.  
    And, we also try to match the two samples using mass within 5 and 15 kpc 
    instead, the results are also very similar.

%% ------------------------------------------------------------------------------------ %%

\subsection{Explore Different Scaling Relations}
    \label{ssec:scaling}

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure}[bt!]
      \centering 
      \includegraphics[width=\columnwidth]{fig/redbcg_mass_r50}
      \caption{The \mstar{}-size relations for \rbcg{} (orange-red circles) and \nbcg{} 
          (grey dots) galaxies. 
          Here we use the \mtot{} as proxy of total \mstar{}, and use the 
          $R_{\mathrm{50}}$ derived from the 1-D profile as size estimate. 
          The size and color coding for \rbcg{} galaxies are the same with the right panel 
          of Fig.\ref{fig:smf1}.  
          And two vertical lines highlight the $11.6<$\logms{}$<11.9$ mass range.
          We also compare these distributions with the relation for nearby central 
          galaxies of massive groups from \citet{HCompany13} (green, long dashed line). 
          The \mstar{} and $R_{\mathrm{e}}$ are estimated via different methods in these
          works. 
          We also illustrate best-fit \mstar{}-$R_{50}$ relations for \rbcg{} (red, solid 
          line)and \nbcg{} (grey, dash line) galaxies that have \logmtot{}$\geq 11.6$.
          The shaded regions in lighter color show the 1-$\sigma$ uncertainties of these 
          relations.
          Please refer to the text for detailed comparisons.}
      \label{fig:mass_r50}
  \end{figure}
%% ------------------------------------------------------------------------------------ %%

\subsubsection{$M_{\ast}-$size relation}
    \label{sssec:mass_size}

    The scaling relation between \mstar{} and effective radius (or half-light radius) 
    was the focus of past investigations of the structural evolution (e.g. \addref) and 
    the environmental dependence of structures for massive galaxies (e.g. \addref{}). 
    So far, the results are quite confusing as no clear evidence of environmental 
    dependence has been found at low redshift using various definitions of ``size''. 
    Also, at high redshift, the results can be even controversial
    (e.g. \addref).  
    As the deep HSC images have already help us reveal subtle, but systematic structural
    differences in massive central galaxies that may depend on the environment, we should 
    expect to see such evidence on the mass-size relation. 
    Here, we briefly discuss the mass-size relations of \rbcg{} and \nbcg{}
    galaxies (Fig.\ref{fig:mass_r50}).

    We choose to use the \mtot{} as the proxy of ``total'' \mstar{}, and use the 
    half-light radius ($R_{\mathrm{50}}$) that is defined as the radius enclosing 50\% of 
    luminosity within 100 kpc as the ``size'' to evaluate the relation.
    And, we use the curve-of-growth of luminosity from the \texttt{Ellipse} run on 
    $i$-band images to estimate the $R_{\mathrm{50}}$ here.
    In principle, such approach is more sensitive to issues like the smearing effect of 
    PSF and the choice of aperture for maximum luminosity than the 2-D fitting method.
    For the massive galaxies in this work, their apparent sizes are always sufficiently 
    large at $0.3 \geq z \geq 0.5$ so that the $R_{\mathrm{50}}$ measurement is not 
    bothered by PSF.   
    And, the 1-D method has the advantages of being less affected by accuracy of background
    subtraction, structural details, and model assumptions.

    We show the distributions of \rbcg{} and \nbcg{} galaxies on the mass-size plane.  
    On top of the clear correlations for both sample, the distributions of $R_{\mathrm{50}}$ 
    for \rbcg{} and \nbcg{} samples greatly overlap with each other over the \mtot{} range
    between $10^{11.6}$ and $10^{11.9} M_{\odot}$. 
    Meanwhile, it seems that the \rbcg{} galaxies do have a slightly higher 
    $R_{\mathrm{50}}$. 
    For the \mtot{} matched samples used in Fig.\ref{fig:prof_m100_A}, the median 
    $\log (R_{\mathrm{50}}/\mathrm{kpc})$ values for the \rbcg{} and \nbcg{} are 
    $1.22\pm 0.02$ ($\sim 17.4\pm 0.75$ kpc) and $1.09\pm 0.01$ 
    ($\sim 12.3\pm0.3$ kpc), which confirm the above observation and is consistent with 
    the differences seen in Fig.\ref{fig:prof_m100_A}. 
    However, all previous works that we are aware of did not match the mass (and redshift) 
    distributions between different samples, and often focus on the form of the 
    \logms{}-$\log R_{\mathrm{e}}$ relation.  
    Here, we try to derive the best-fit parameters for the 
    \logmtot{}-$\log (R_{\mathrm{50}}/\mathrm{kpc})$ relations of galaxies with 
    \logmtot{}$\geq 11.6$ using MCMC-sampling method via the ensemble sampler 
    \texttt{emcee} (\citealt{Emcee}). 
    Using initial guesses based on maximum likelihood estimates, and assuming reasonable 
    flat priors, we derive best-fit relation for the massive \rbcg{} galaxies:

    \begin{equation}
        \begin{aligned}
        \log (R_{\mathrm{50}}/\mathrm{kpc}) = & (0.73\pm0.13) \times \log (M_{\star, 100\ \mathrm{kpc}}/M_{\odot}) \\ & -(7.49\pm1.56)
        \end{aligned}
    \end{equation}

    \noindent And for the massive \nbcg{} galaxies, we have:

    \begin{equation}
        \begin{aligned}
        \log (R_{\mathrm{50}}/\mathrm{kpc}) = & (0.68\pm0.06) \times \log (M_{\star, 100\ \mathrm{kpc}}/M_{\odot}) \\ & -(6.88\pm0.75)
        \end{aligned}
    \end{equation}

    \noindent As shown in Fig.\ref{fig:mass_r50}, at the high-mass end, the two relations 
    have consistent slopes within their uncertainties, but different normalizations. 
    Extending the fitting to the full \logmtot{} range does not change this result. 
    We also explore mass-size relations for our samples using \mstar{} within different 
    radius (e.g. 120, 150 kpc) and the $R_{\mathrm{50}}$ derived within these apertures, 
    and find consistent results.

    We qualitatively compare our results with the one for $z\leq 0.09$ central ETGs in  
    $14\le$\logmh{}$<15$ halos from \citealt{HCompany13} (HC13; green solid line).
    HSC13 use the group catalog by \citet{Yang2007} to estimate \logmh{}. 
    They estimate the 2-D $R_{\mathrm{e}}$ using single-\ser{} model fitting to SDSS images,
    and derive \mstar{} based on SED fitting using the BC03 (\citealt{BC03}) synthetic 
    population model.
    We empirically convert their \mstar{} from the Kroupa IMF to the Chabrier one 
    used in this work by applying a constant -0.03 shift to their values. 
    We also increase the \mstar{} in HC13 by $+0.1$dex to account for the systematic 
    difference between their BC03 and our FSPS model (see Appendix \ref{app:B}). 
    In HC13, the authors found no difference among the mass-size distributions for 
    central galaxies in halos across $12.5\le$\logmh{}$<15.0$. 
    Despite all the systematic differences, the mass-size distributions for both \rbcg{} 
    and \nbcg{} galaxies follow the HC13 relation reasonably well (with slightly
    shallower slopes) even at \logmtot{}$< 11.6$ where our samples start to become 
    incomplete.

    In short, we confirm that the massive central galaxies in this work generally 
    follow the mass-size relation of massive ETGs at low-$z$.
    And, more importantly, we find evidence of differences in the mass-size relations for 
    massive central galaxies of halos with different \mhalo{}. 
    The difference we saw at \logmtot{}$\geq 11.6$ is in line with the conclusion that
    central galaxies in denser environment have slightly larger size comparing to the 
    ones from less-dense environment at fixed \mstar{}.

    This suggests that the previous, inconclusive results on whether the 
    mass-size relation of massive ETGs depends on environment could be due to 
    either the inadequate depth of the image, or the inappropriate model assumptions 
    adopted during the fitting (or both).  
    It would be interesting to revisit this issues using 2-D models based on deep HSC 
    images as the next step.
    It is worth noting that our results are based on massive galaxies at $z\sim 0.4$, 
    while the sample of HC13 has $z<0.09$.
    Although here we can not address the interesting issue of redshift evolution of 
    mass-size relation, the ``evolutionary path'' of massive central galaxies from 
    different environments on this mass-size plane is certainly an intriguing issue. 
    If the \rbcg{} galaxies have a richer merging history than the \nbcg{} ones, 
    perhaps we should expect more significant differences on their mass-size 
    relations and average \mden{} profiles at $z\sim 0$ using deeper image. 
    On the other hand, if the \nbcg{} galaxies could assemble more \mstar{} through minor 
    mergers in the last 3-4 Gyrs, they could ``catch-up'' with the \rbcg{} galaxies 
    a little bit on the mass-size plane. 
    Potentially, we could make some predictions on this issue using the frequency of 
    tidal features and properties of satellites around our \rbcg{} and \nbcg{} 
    galaxies in the near future.

%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}[t]
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_m100_m10_new}
      \caption{\textbf{(a)}: Distributions of galaxies on the 
          \mtot{}-$\Delta (\log M_{\star})_{100\mathrm{kpc}-10\mathrm{kpc}}$ plane. 
          All \rbcg{} (open red boxes) and \nbcg{} (light, grey dots) galaxies 
          are shown in the background. 
          The \mtot{}-matched samples between $11.6<$\logms{}$<11.9$ (between two 
          vertical lines) are highlighted (\rbcg{}: solid red boxes; 
          \nbcg{}: bigger grey dots). 
          We also show the median values (solid triangular and hexagon), and the
          distributions of $\Delta (\log M_{\star})_{100\mathrm{kpc}-10\mathrm{kpc}}$
          (both histograms and kernel density distributions on the right).
          The best scaling relations for \rbcg{} (red, solid) and 
          \nbcg{} (grey, dashed) galaxies along with their uncertainties 
          are illustrated as well.~~
          \textbf{(b)}: Distributions of galaxies on the 
          $\Delta (\log M_{\star})_{100\mathrm{kpc}-10\mathrm{kpc}}$-\minn{} plane.~~
          \textbf{(c)}: Distributions of galaxies on the 
          $\Delta (\log M_{\star})_{100\mathrm{kpc}-10\mathrm{kpc}}$-\mtot{} plane.
          But, this time, we highlight the \rbcg{} and \nbcg{} samples that are 
          matched using \minn{} instead of \mtot{}.~~
          \textbf{(c)}: Relations between \mtot{} and \minn{}. 
          Other formats of figure (b), (c), and (d) are very similar with figure (a).}
      \label{fig:m100_m10_A}
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

\subsubsection{Relations between stellar mass within different physical apertures}
    \label{sssec:m100_m10}

    We just show that the mass-size relation of massive central galaxies could also 
    depend on the mass of their host halos, and here we explore relationships between 
    \mstar{} within different apertures as alternative tools to help
    us better understand the relationship between halo mass and assembly history of 
    massive galaxies.  
    Here we focus on \mtot{}, \minn{}, and also the logarithmic mass differences 
    between them ($\Delta \log M$, reflecting \mstar{} ratio). 
    Comparing to the mass-size relation, such relations are not affected by the ambiguous 
    definition of ``size''; and comparing to the detailed \mden{} profiles, 
    it is much easier to apply these relations to larger samples and compare with 
    results from simulations.

    We show the results in Fig.\ref{fig:m100_m10_A}.  
    In panel (a), we plot the \mtot{} with $\Delta \log M$ for both the\rbcg{} 
    and \nbcg{} samples. 
    As expected, these two parameters well trace each other over the entire 
    \mtot{} range, indicating that more massive central galaxies have larger 
    fraction of total \mstar{} in the outer part. 
    Suggested in Fig.\ref{fig:prof_m100_C}, the structural differences related to 
    \mhalo{} seem to be more significant in higher \mstar{} bin. 
    We therefore highlight the \mtot{}-matched \rbcg{} and \nbcg{} galaxies at 
    $11.7 \leq$\logmtot$< 11.9$. 
    Although their $\Delta \log M$ distributions still greatly overlap within 
    this \mtot{} range, the median values (big, outlined symbols with error bars),
    and their kernel-density distributions clearly point out systematic difference. 
    Consistent, but slightly smaller, difference also exists for \mtot{}-matched 
    samples at $11.6 \leq$\logmtot$< 11.9$. 
    At the same time, the comparisons in Fig.\ref{fig:prof_m100_A} and 
    Fig.\ref{fig:prof_m100_C} also suggest that the \mtot{}-matched \rbcg{} galaxies 
    have lower \minn{} than the \nbcg{} sample, which is clearly shown by panel (b)
    where we plot $\Delta \log M$ with \minn{} for the \mtot{}-matched samples.
    For the \nbcg{} sample, the correlation between between $\Delta \log M$ and \minn{}
    is much weaker than the one in panel (a), yet it is still visible.  
    However, for our \rbcg{} sample, we see no overall correlation between 
    $\Delta \log M$ and \minn{}.  
    We also construct $\Delta \log M$ using logarithmic mass differences between 
    100 and 30 (or 50) kpc, and the results are very similar.  
    In fact, the average differences between the \mtot{}-matched \rbcg{} and \nbcg{} 
    samples become more significant when mass within 30 (or 50) kpc is used.        
    These reflect the structural differences we found in Fig.\ref{fig:prof_m100_A}: 
    at fixed \mtot{}, central galaxies with higher \mhalo{} tend to have even higher 
    fraction of \mstar{} stored between 10 and 100 kpc.

    In panel (c), we show the relationship between $\Delta \log M$ and \mtot{}, 
    and highlight the \minn{}-matched samples presented in Fig.\ref{fig:prof_m10_A} 
    and Fig.\ref{fig:prof_m10_B}. 
    Using the histograms of \mtot{} and their median values of the \minn{}-matched
    samples, we clearly identify the impact from the much more extended outer envelope 
    hosted by \rbcg{} galaxies.

    Finally, in panel (d), we plot \mtot{} against \minn{} directly.  
    The median values and statistical distributions of \minn{} for the \mtot{}-matched 
    samples highlight the structural difference at fixed \mtot{} again.  
    All the \mhalo{}-dependence of structures we discussed above are clearly 
    displayed here along the directions of both x- and y-axis.
    Firstly, within the \mtot{} range we explored, the \rbcg{} galaxies tend to have 
    lower mass within the inner 10 kpc; and such difference seems to become more 
    significant at higher \mtot{}. 
    As seen from the median \mden{} profiles, this is due to the shallower overall
    profile of \rbcg galaxy, and indicates that the slopes of both inner and outer
    \mden{} profiles of massive central galaxies may depend on \mhalo{}. 
    Secondly, for massive central galaxies that form similar amount of stars through
    the dissipative processes during the ``in-situ'' phase (approximated by \minn{}), 
    their \mtot{} distributions at lower redshift depend on \mhalo{} in a way that the
    ones in more massive halos can develop much more prominent stellar envelope thanks 
    to the more complex mass assembly history.

    But, more importantly, it is intriguing to see that the distributions of \rbcg{} and
    \nbcg{} galaxies on this 2-D plane seem to be offset with each other. 
    At least at the high mass end, the central galaxies in more and less massive halos 
    seem to follow relations between \mtot{} and \minn{} with similar slopes, but 
    different normalizations.  
    Instead of subjectively grouping galaxies into different bins of \mtot{} or \minn{}, 
    such scaling relation brings us a more generic view of the environmental 
    dependence of structure, and could become an interesting tool to investigate the 
    connection between halo mass, assembly history, and the structure of massive galaxies.
    On Fig.\ref{fig:m100_m10_A} (d), we illustrate the \logmtot{}-\logminn{} relations 
    at \logmtot$\geq 11.6$ that are derived using MCMC sampling method.  
    For \rbcg{} galaxies, the best-fit relation is:

    \begin{equation}
        \begin{aligned}
        \log (M_{\star, 10\ \mathrm{kpc}}/M_{\odot}) = & (0.48\pm0.06) \times \log (M_{\star, 100\ \mathrm{kpc}}/M_{\odot}) \\ & +(5.72\pm0.75).
        \end{aligned}
    \end{equation}

    \noindent While for the \nbcg{} ones within the same \mtot{} range, we have:

    \begin{equation}
        \begin{aligned}
        \log (M_{\star, 10\ \mathrm{kpc}}/M_{\odot}) = & (0.56\pm0.03) \times \log (M_{\star, 100\ \mathrm{kpc}}/M_{\odot}) \\ & +(4.82\pm0.30).
        \end{aligned}
    \end{equation}

    The same relation using the full \mtot{} range will results in a even shallower 
    slope for the \rbcg{} galaxies. 
    And, replacing the \minn{} with \mstar{} within 5 or 15 kpc apertures does not change 
    our conclusion. 
    In fact, the relation using $M_{\star, 5\ \mathrm{kpc}}$ shows more significant 
    \mhalo{} dependence at the high-mass end. 
    Unfortunately, due to the impact from PSF, the $M_{\star, 5\ \mathrm{kpc}}$ values 
    are slightly less reliable than the \minn{} ones. 
    Samples at lower redshift, images from space telescope, and 2-D modeling method can 
    all help us pushing this investigation further insider smaller physical aperture 
    that perhaps can provide us better surrogate of \mstar{} from the ``in-situ'' phase.

    Besides the systematic offset, it seems that the \rbcg{} galaxies could have 
    larger scatter of \minn{} at high-mass end. 
    Limited by our capability to estimate the mass and other properties of halos 
    at individual level, we can not further quantify this potential \mhalo{}-dependence 
    here.
    Within the \rbcg{} sample, we do not find any evidence of dependence on the richness 
    ($\lambda$) of the cluster even the \redm{} richness should traces \mhalo{}
    reasonably well.
    In the current sample, most of the \rbcg{} galaxies are centrals of clusters with 
    $30 \leq \lambda \leq 40$, and only small fraction comes from more massive clusters.  
    Together with the small sample size, the uncertainties of richness from shallow SDSS
    images, and the intrinsic scatter of the $\lambda$-\mhalo{} relation may conspire to 
    hide more detailed \mhalo{}-dependence.

    The evidence of \mhalo{}-dependence of structure in massive galaxies could be caused 
    by different processes, it is therefore of great interest for us to dig deeper by 
    comparing the galaxies at higher redshift or from numerical simulations (e.g. see 
    Fig.1 of \citealt{Wellons2016b}) on the \mtot{}-\minn{} or similar planes.

%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure}[bt!]
      \centering 
      \includegraphics[width=\columnwidth]{fig/redbcg_discussion_1}
      \caption{Comparison of the average \mden{} profiles of massive galaxies in the 
          two lower \mtot{} bins from Fig.\ref{fig:avg_prof} with other observations 
          and simulations, focusing on the inner region. 
          The format is similar with the right panel of Fig.\ref{fig:avg_prof}.
          We include: 
          1) the average \mden{} profile of inner component from structure 
          decomposition of massive elliptical galaxies at $z\sim 0$ from 
          \citet[][Cyan, solid]{Huang2013a}; 
          2) the average \mden{} profile of massive galaxies at $1.0 < z < 1.5$ 
          from \textit{HST} observations in \citet[][Red, dashed]{Patel2013}; 
          3) the average \mden{} profile of the ``in-situ'' stellar components in 
          simulated massive halos from \citet[][Purple, dot-dashed]{Cooper13};
          4) the \mden{} profile of the very massive cD galaxy at $z\sim 1.1$ 
          discovered by \citet[][Yellow, dashed]{Liu2013} in the Hubble 
          Ultra-Deep Field.}
      \label{fig:discussion_1}
  \end{figure}
%% ------------------------------------------------------------------------------------ %%

\section{Discussions}
    \label{sec:discussion}

    \alexie{In some point of the paper (in the results section). We need to say what the difference is between M100 and the mass that you would get if you extrapolated outwards. How different is M100 potentially from a "total mass"?}
    \song{Yes, I can say a few words about that. I will send you with a figure that shows 
    the mass differences between 150 kpc and 100 kpc; At 150 kpc, we are already pushing 
    it to region where the photometry is uncertain, and affected by background subtraction.
    Most of the current works on ICL are in region smaller than this. 
    The key is 1) the mass increase is small, $<0.1$ dex, same level with the mass 
    uncertainty; 2) still depends on \mtot{}, more massive ones have more 
    extended outer profiles, hence more massive in outer regions.  
    Using 2-D fitting will give you higher stellar mass, as it extrapolates to 
    very large radius, but you have to assume at that radius, the profile follows
    the model defined at inner region, which is kind of dangereous as we show here.
    I could say this is worth exploring in the future.}
    In the past decade, the mass assembly and structural evolution of massive ETGs 
    remains as an active topic.  
    More and more convincing observations of massive galaxies at high redshift reveal that
    the progenitors of massive elliptical galaxies are quite different in structure
    comparing with their local decedents (e.g. \addref{}).  
    Collectively, they need to increase their ``size'' ($R_{\mathrm{e}}$) by a factor of 
    2 to 4 (e.g. \addref{}) without changing their inner \mden profile (e.g. \addref{})
    and central stellar velocity dispersion (e.g. \addref{}) much in the last 8-10 Gyrs.  
    Owing mainly to better numerical simulations, the challenge of ``size''-evolution 
    seems to be eased by the promising ``two-phase'' scenario under the framework of 
    hierarchical formation of galaxy (e.g.\addref{}). 
    Under this picture, the inner region of massive galaxies mostly consist of stars 
    formed within the halo of the main progenitor through intense dissipative processes 
    at high redshift.  
    Later, after the active star formation is quenched in these massive systems, their 
    mass assembly history becomes dominated by accretions of satellites.  
    Based on the prediction of merger tree and current understanding of satellite 
    population around massive galaxies, most these merging events are likely to be 
    minor ones, and without involving much gas dissipation.  
    Since such minor, dry merger basically redistributes stars onto the outer envelope 
    of the central galaxy, it becomes the most promising solution to the ``size-evolution''
    puzzle.  
    However, it raises additional questions at the same time. 
    The most pressing one would be the expected ``environmental''-dependence of structures 
    of massive central galaxies. 
    As minor merger is expected to be more frequent in denser environment, the mass assembly 
    history and \mstar{} distribution of central galaxies should show dependence on \mhalo{}
    or even other properties of the host halo.  
    For instance, centrals in more and less massive halos could have different 
    slopes and/or scatters in their mass-size relation (e.g. \addref{}).  
    Yet, no clear evidence of such dependence has been found. 
    In this work, taking advantage of the deep photometry from the HSC survey and looking 
    into the detailed \mden{} profiles, we clearly see evidence that the \textbf{structure
    of massive central galaxies, both the inner and outer parts, does show dependence on 
    the halo mass}. 
    Here, we briefly discuss the physical causes of this dependence, potential caveats, 
    and more scientific implications.

    Firstly, the comparisons of the \mden{} profiles suggest that \textbf{\mhalo{} does 
    not play a central role in shaping the structure of massive central galaxies}.  
    It appears that massive central galaxies at \logms{}$\geq 11.5$ were shaped by 
    same physical processes in more and less massive halos.  
    At both fixed \mtot{} and \minn{}, centrals from cluster-level halos do not form a 
    unique population. 
    Instead, their individual \mden{} profiles greatly overlap with the ones in halos of 
    small group. 
    At similar \mtot{}, even their median \mden{} profiles only show quite subtle 
    differences. 
    For the \rbcg{} sample, this is similar to the results of \citep{Zhao2015} that 
    a considerable fraction of nearby BCGs (34\%) does not fall into the ``cD'' class.
    From the smooth distributions of \mden{} profiles on Fig.\ref{fig:prof_m100_A} 
    and Fig.\ref{fig:prof_m10_A}, it is even harder to draw a clear difference 
    between ``cD'' galaxy and ``normal elliptical''.

    At the same time, \textbf{the \mhalo{}-dependence we found do fit the expectations 
    of the ``two-phase'' scenario at first glance}. 
    For central galaxies with similar stellar mass at the end of the first phase, 
    their subsequent, accretion-dominated mass assembly naturally relates to \mhalo{}, 
    which determines the number and mass distributions of satellites. 
    Therefore, centrals of more massive halos should accumulate more extended stellar 
    envelope during the second phase, exactly as we find in the \mden{} profile 
    comparison of the \minn{}-matched samples (see Fig.\ref{fig:prof_m10_A}).
    Under the ``two-phase'' formation scenario, the stellar content of massive galaxies
    can be broadly separated into the ``in-situ'' and ``accreted'' components. 
    At fixed \mtot{}, the differences of median \mden{} profiles could reflect 
    different relative fraction of these two components. 
    Recent simulations indicate that (1) the fraction of accreted stars could have 
    a steep correlation with total stellar mass; (2) for \logms$\geq 11.5$ galaxies,
    the accreted component starts to dominate within the $R_{\mathrm{e}}$.  
    Given that (1) the ``transition radius'' between the two median profiles is around
    15-20 kpc (see Fig.\ref{fig:prof_m100_A}); and (2) the differences become more 
    significant at higher mass end, it is likely the \mhalo{}-dependence of structure
    at fixed total stellar mass is driven by the higher fraction of accreted stars 
    in more massive halos.  
    To confirm this inference, in Fig.\ref{fig:discussion_1}, we compare the median 
    \mden{} profiles of the \mtot{}-matched \rbcg{} and \nbcg{} samples at 
    $11.5\leq$\logms{}$<11.7$ with the median profiles of 
    (1) massive ETGs at $1.0 < z < 1.5$ that are considered the progenitors of 
    $\sim 10^{11.5} M_{\odot}$ ETGs at $z=0$ (\citealt{Patel2013}).  
    After this redshift range, their mass growth should be dominated by mergers.  
    (2) inner components of $z=0$ $10^{11.4} M_{\odot}$ ellipticals from 2-D decomposition
    (\citealt{Huang2013a}). 
    \citep{Huang2013b} showed that these structures are quite similar to the compact 
    progenitors at higher redshift in many aspects.  
    (3) the ``in-situ'' components of simulated galaxies in massive halo of 
    \citep{Cooper13} using particle-tagging technique (the inner few kpc is quite 
    uncertain due to the resolution).  
    Regardless the small difference in median \mstar{} and details in \m2l{} estimates, 
    the comparison first confirms that \minn{} is indeed not a bad proxy of the in-situ 
    mass; meanwhile, it also highlights that structural difference between \rbcg{} and 
    \nbcg{} are driven by region that is not dominated by ``in-situ'' stars. 
    Since most of these samples in comparison are not as extreme as the massive 
    \rbcg{} galaxies, we also compare with a uniquely massive BCG at high redshift: 
    a $10^{11.4} M_{\odot}$ BCGs with distinctive envelope at $z\sim 1.1$ 
    (\citealt{Liu2013}).  
    It is interesting to see that its \mden{} profile follows the median profile of 
    \rbcg{} nicely until 20 kpc; then it becomes much steeper in the outskirt.  
    This is quite consistent with the expectation that the inner part of the BCGs 
    should be well developed at $z\sim 1$, but the extended stellar envelope is still 
    assembling.

    Also, it is worth noting that the relative flatten inner \mden{} profile of \rbcg{}
    at fixed \mtot{} could be an interesting feature, although we currently lack of the 
    resolution to investigate region $\leq 3$ kpc.  
    It is known that major-merger induced coalesce of super-massive black hoes (SMBHs)
    can create flattened inner profile (e.g. \citealt{Milosavljvi2002}), and recent 
    discoveries of massive BCGs with very large core 
    (a few kpc; e.g. \citealt{Postman2012, LopezCruz2014}) further complicate the picture.
    On Fig.\ref{fig:m100_m10_A}, there are a few \rbcg{} galaxies with quite low 
    \minn{} at high \mtot{} end. 
    After examining their images, we conclude the low \minn{} is not caused by problematic
    photometry or exceptionally bad seeing; they could also be massive BCGs with very 
    flattened inner \mden{} profiles.  
    Besides the SMBH-merger theory, strong adiabatic expansion induced by strong AGN 
    feedback was proposed to modify the inner mass distribution (e.g. \citealt{Fan2008}). 
    The potential impact of these processes to massive galaxies, and their dependence on 
    halo mass would be an interesting topic to investigate in the future.

	\song{I agree that this can be part of the results; but the profiles here are not as 
    reliable as the \mden{} profiles for technical reason; I put it here as a teaser, as 
    it is better to deal with them using 2-D fitting.}
\alexie{This paragraph shoud go in the results section. Indeed, here you are presenting a result that you measured. And what is the main message / lesson that we learn from this paragraph and figure? We sort of jumped rather abruptly from the enviromental dependence to ellipticity and color profles. Transition needs more motivation. A discussion of the implcations of this figure could go in the discussion section.}    As a start, we only focused on the 1-D \mden{} profile derived from $i$-band image.  
    We should not forget that the multi-band, 2-D HSC images of these massive galaxies 
    actually contain much more useful information, particularly the shapes and colors 
    of different stellar components.  
    Strictly speaking, to extract these information reliably, we need to rely on better 
    background subtraction and 2-D modelling method.  
    But, as a motivation, we shows initial results from 1-D analysis in 
    Fig.\ref{fig:discussion_2}.  
    The ellipticity profile is extracted from \texttt{Ellipse} run on $i$-band image 
    with free geometric parameters. 
    After reducing the $g$- and $r$-band images of our galaxies in consistent way with 
    the $i$-band ones, we simply apply the $i$-band isophotes to images in these two 
    bands without matching the seeing to extract color profiles. 
    All the color profiles are corrected for Galactic extinction and $k$-correction 
    using \texttt{iSEDFit} results. 
    We show the median ellipticity, $g-r$, and $g-i$ color profiles of the 
    \mtot{}-matched (\minn{}-matched) samples of \rbcg{} and \nbcg{} galaxies on the 
    left (right) panel; and also compare them with median profiles from stacking 
    analysis of SDSS galaxies with similar \mstar{} 
    (\citealt{LaBarbera2010, Tal2011, DSouza2014}) excluding the inner and outer regions 
    affected by seeing and uncertainty of background subtraction.  
    For the \mtot{}-matched samples on the left, we notice that the median ellipticity 
    profiles follow the stacked ones well between 5 to 30-50 kpc, but are not plateaued
    at larger radius.  
    Since they are the median of individually measured ellipticity profiles, they do 
    not suffer the systematics in stacking analysis, and are better at reflecting the 
    intrinsic profiles.  
    In consistent with the 2-D decomposition results in \citep{Huang2013a}, the 
    projected \mstar{} distributions in massive galaxies become increasingly elongated 
    at larger radius.  
    We notice no significant difference between the \rbcg{} and \nbcg{} samples, 
    except for maybe some hints that centrals in more massive halos becomes slightly 
    more elliptical at very large radius.  
    For the median color profiles, we see shallow and negative gradients of both 
    $g-r$ and $g-i$ colors as expected. 
    More importantly, the \rbcg{} and \nbcg{} samples show very consistent color 
    gradients, which confirms that using average color to derive \m2l{} of both 
    samples will not bias the comparison of \mden{} profiles.  
    Without conversion between the HSC and SDSS filter systems, our median color 
    profiles appear to be little steeper than the stacked ones from SDSS.  
    The exactly cause of this difference is not clear, although it could also be 
    due to the systematics in the stacking process. 
    As for the \minn{}-matched samples on the right, it becomes very clear that the 
    extended envelopes hosted by \rbcg{} galaxies have much higher ellipticity, and 
    redder $g-i$ colors than the outskirts of \nbcg{} ones at similar \minn{}.  
    All these preliminary results point out that, by including these information 
    into consideration, we will have a more complete view of the connection between 
    halo/environment and structure of massive central galaxies.

    \song{Ok, I'll see how to make it happen; this sounds abrupt since I used 
    to have several subsections in the discussion section.}
    \alexie{The beginning part of this paragraph sounds to me like the summary section. You could move part of this to summary and put it in bullet piont format.}. In the end, we want to emphasis once more \textbf{the importance of deep image 
    and appropriate method of photometry in studying the structure and assembly 
    history of galaxies}. 
    With the help of deep HSC images, we reliably reveal the extended stellar 
    structures around large sample of massive central galaxies out to more than 
    100 kpc.  
    And, using model-independent method, we found that 
    (1) previous de~Vaucouleur or single-\ser{} modeling method on shallower SDSS
    images underestimates the total mass of massive galaxies; 
    (2) even using deep HSC images, photometric method like \cmodel{} also tends 
    to underestimate the mass. 
    For these massive central galaxies, their extended mass distributions are 
    simply beyond the capability of the simply modeling method.  
    In addition, since the slope and mass contribution of the outer envelope 
    depend on not only the total stellar mass, but also likely the halo mass. 
    Applying the same oversimplified model to galaxies across a large range of 
    mass and environment could result in both underestimated and biased mass 
    estimates that can stop us getting accurate stellar mass function at the 
    high-mass end and studying potential environmental dependence of structures. 
    Moreover, these results also raise crucial questions like: 
    \textbf{What is the definition of ``total'' stellar mass of galaxy? 
    And, what is the most informative definition of stellar mass in the studies 
    of galaxy evolution?}.  \alexie{I think we can expand the discussion around this topic. We'd like to say somehting about the impact of total luminosity on the SMF. How about moving the left hand of Figure 3 here? What is the current volume of your data set compared to the volume of SDSS? I think we should emphasize the impact of stellar mass estimate on the SMF, especialy the large impact it has for BCGs}.
    \song{As mentioned earlier, I can expand the discussion easily with the help 
    from another figure, comparing with SMF from other people's work?//}

    \alexie{I thought of another interesting aspect to add to the discussion. This I think is perhaps a nice angle to discuss. The total luminosity of a galaxy has an impact on abundance matching. Do you have the "luminosity" that you would get for each galaxy if you assumed a single sersic fit for example? If so, we could do the following. Assume a one-to-one mapping between halo mass and your M100. Then plot Mhalo versus the stellar mass inferred from either cmodel of the single sersic fit. Then we can quote the scatter in $\log(M_*)$ at fixed Mhalo that this introduces. This figure will be very relevent for the Santa Barabara workshop!}
    \song{We do not have results from single Sersic models; at least not reliable enough 
    to be used here, mostly because single Sersic works terribly for these galaxies.
    We do have \mcmodel{}, but sorry that I failed to follows the logic here, basically this is 
    the difference between \mtot{} and \mcmodel{} expressed in a different way, and I am not 
    sure the scatter is due to the scatter of the mhalo-mstar relation, as the cModel 
    ones are underestimated due to technical reasons; We can bin the \rbcg{} galaxies 
    into a narrow $\lambda$ bin thoug, e.g. $30< \lambda < 40$, and see the scatter of 
    \mcmodel{}, \minn{}, and \mtot{}. We can certaintly shows that the scatter is larger 
    for mass using larger radius.  I think this point is important for the discussion
    of the intrinsic scatter of the mhalo-mstar relation, and at very similar mhalo,
    the outer structure may trace other properties of the halo. Let me know what do 
    you think.\\}

    \alexie{Finally, another quick discussion paragraph could be related to finding BCGs. It would be interesting to have a plot of the magnitude gap between Pcen1 and Pcen 2 (the most likely and the second most likely central) with cmodel versus your estimates. It would be nice to show that having a better luminosty estimate will enable you to identify the BCG better (is this true?)}.
    \song{This is interesting, and I don't know if it is true. It requires more works as 
    I do not have the profiles for all PCEN2 galaxies, I only do it when they are more 
    massive than the threshold.  Can we save this for later, I mean, after we send around 
    the draft.  Although I do compare the structures of really massive satellites in 
    these clusters with the \nbcg{} galaxies, and the results show little difference,
    basically shows that the structure difference could be unique for central galaxies. 
    I originally show a figure for this, and will send you along the e-mail.}

    In this work, we choose mass enclosed by different, but fixed physical 
    apertures, and find promising scientific applications for massive galaxies. 
    But, we recognize that they may not be the best choice. 
    For instance, central galaxies of massive halos like BCGs are known to be
    surrounded by diffuse stellar component that does not follow the potential 
    of the central galaxy (the intra-cluster light, or ICL; e.g. \addref{}).
    In theory, it can contribute a large amount of stellar mass out to very 
    large radius (e.g. \addref{}).  
    Using the definition of \mtot{}, we can not separate the potential 
    contribution of ICL in our \rbcg{} galaxies; and this could make complicate
    the discussion of environmental dependence.  \alexie{I am not sure I agree here. What is the "ICL"? How can is physically be defined? Can one robustly distinguish an "ICL" component from the galaxy component and how? Is the ICL similar to the "cD" enveloppe in the sense that we use these words all the time, but in practice, these are just one extrema of a continous galaxy population?}
    Since most of the \rbcg{} galaxies in our sample belong to low-mass cluster 
    like the Virgo or Fornax, we do not expect the ICL component can makes a 
    smooth and significant contribution to the \mden{} profiles (e.g. \addref{}).
    Even removing all \rbcg{} galaxies in $\lambda > 40$ clusters will not change 
    our findings.  
    However, it is still important to ask whether should we include the ICL when 
    estimating the mass of central galaxies in massive halos.  \alexie{But what is the ICL?}
    \song{The observational definiiton is very vague; and the theoretical one is 
    very hard to achieve through observation, basically the stars that follows the 
    potential of the clsuter.}
    And, if the answer is no, which is the best way to separate the ICL component? 
    In literature, most works studied ICL by subtracting the model for inner part
    of the central galaxy (e.g. \addref{}).  
    As we show in this work, when extended stellar envelopes are revealed around 
    massive galaxies in large range of stellar and halo mass, we may have to 
    reconsider this approach \alexie{I agree with this phrase, this is good to point out.}.
    \song{I think I understand your point here. The thing with ICL is that any 
    conclusion so far is quite uncertain, so I can reorganize this paragraph, 
    point out the interesting question first, discuss it a little bit, but also 
    shows a caveat that say ICL could play a role here, and if it does, how could 
    they change our results.}

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}[t!]
      \centering 
      \includegraphics[width=17.0cm]{fig/redbcg_discussion_2}
      \caption{\alexie{Seems to me that this goes in the results section?} Comparisons of the radial profiles for ellipticity and optical colors 
      	for \mtot{}-matched (left figure) and \minn{}-matched (right figure) of 
        \rbcg{} (orange-red) and \nbcg{} (grey-black) samples. 
        The formats are very similar to the figure for \mden{} profile 
        (e.g. right figure of Fig.\ref{fig:prof_m100_A)}. 
        On each side, from top to bottom, we show the elliptical profile, and the 
        color profile using $g-r$ and $g-i$ color. 
        Since the individual profile of these properties has very large uncertain in the 
        outskirt, we block the region at large radii where we think the median profiles 
        are still unreliable using a dark, shaded box.
        We also compare these results with previous results based on SDSS images. 
        They are: 
        1) Ellipticity profile of stacked image of large sample of red galaxies at 
        $z\sim 0.4$ from \citet{Tal2011}, with and without PSF correction 
        (solid and dotted blue lines on top panel); 
        2) Ellipticity and $g-r$ color profiles from stacking analysis of nearby massive 
        galaxies with high concentration index ($C>2.6$) in \citet[][blue dash lines 
        on the top and middle panels]{DSouza2014}; 
        3) average $g-r$ and $g-i$ color profiles for a large sample of nearby 
        elliptical galaxies in \citet[][blue, solid lines on the middle and bottom 
        panels]{LaBarbera2010}.}
      \label{fig:discussion_2}
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

%\subsection{Impact from ``Fossil Galaxies''}
%
%    ``Fossil galaxy'' is the most massive galaxy in a ``fossil group/cluster''
%    system.
%    According to the commonly adopted definition, ``fossil'' systems are the 
%    group or cluster with high X-ray luminosity and large magnitude gap between 
%    the two brightest galaxies (\addref: Ponman1994; Jones2003). 
%    Both observations and simulations suggest that they could represent the 
%    final stage of the hierarchical merging process in a group/cluster mass
%    halo that is formed at very early epoch (e.g.\ \addref: 
%    Khosroshahi2004, 2007; DOnghia2005; Dariush2007).
%    Under this interpretation, at fixed halo mass, the central galaxy of 
%    a fossil system typically has larger stellar mass than the one in normal 
%    system (e.g.\ Harrison2012), as it has ``consumed'' most satellites 
%    early on; 
%    However, the ``low richness'' of a fossil system makes it difficult for 
%    red-sequence finder like \redm{}~to reliably identify 
%    (e.g.\ Figure~17 of Sadibekova2014).  
%    If some massive ETGs in our \nbcg{} sample are actual the centrals 
%    galaxies of fossil clusters, it could bias our conclusions about the 
%    relation between structure and ``environment''.  
%    
%    Although it is possible that fossil systems formed earlier than normal 
%    clusters, the difference in detailed merging history is still unclear, 
%    hence it is hard to imagine the structural differences between fossil 
%    central galaxies and regular BCGs with same \mstar{}.  
%    Naively speaking, more frequent mergers for fossil centrals should result 
%    in more extended stellar envelope.  
%    However, the distributions of epoch and mass-ratio of those mergers also 
%    matter. 
%    
%    The lack of any difference in stellar population properties may suggest 
%    It is still not clear how the mass assembly history of fossil central

%% ------------------------------------------------------------------------------------ %%

\section{Summary and Future Plans}
    \label{sec:summary}
\alexie{In this section, put a bullet list summarizing our main findings.}
	\song{Ok, will do}

    In this work, we use the deep $i$-band images from the Subaru HSC survey to 
    study the role played by halo mass in determining the mass assembly history and 
    stellar structures of very massive galaxies--the most impressive outcomes of 
    the hierarchical formation process.
    We map the stellar mass distributions of a large sample of massive central 
    galaxies at $0.3 < z < 0.5$ out to $>100$ kpc. 
    With the help of this impressive dataset, we uncover the very extended stellar 
    envelope around massive central galaxies with great accuracy. 
    We also reveal that, the ``total'' \mstar{} of massive galaxies can be significantly 
    underestimated if shallow image and/or inappropriate model is used, which can 
    lead to systematics in the study of stellar mass function and other important 
    topics.

    More importantly, we discover subtle, but systematic, and robust structural 
    differences in massive galaxies that depend on \mhalo{} through comparisons
    of their \mden{} profiles. 
    On average, at fixed \mstar{} within 100 kpc, the massive central galaxies in 
    more massive ($M_{200,m}$ \gax $1.6\times 10^{14} M_{\odot}$) halos show shallower 
    inner \mden{} profile within $\sim 15$-$20$ kpc, and a more prominent outer 
    envelope comparing to the ones in less massive 
    ($M_{200,c}$ \gax $8.7\times 10^{13} M_{\odot}$) halos.
    Also, at the same \mstar{} within inner 10 kpc--a proxy of the \mstar{} assembled 
    through the ``in-situ'' channel, we show that the ones in more massive halos 
    possess much more extended stellar halos in the outskirts.  
    Such differences are broadly consistent with the prediction of the ``two-phase''
    formation scenario of massive galaxies: the ones in more massive halos have 
    experienced more minor, dry mergers that accumulate more stars at large radius. 
    Meanwhile, we also suspect the differences in the inner profiles at fixed \mstar{} 
    or \mhalo{} may help us understand more about the impact from major merger or 
    AGN feedback. 
    We further suggest that the relation between \mtot{} and \minn{}\footnote{or other 
    even better proxies of total \mstar{} and the mass formed in the ``in-situ'' phase.} 
    is potentially interesting in diagnosing the assembly history of massive galaxies 
    and their host halos.

	%\subsection{Future Improvements}
    %\label{ssec:future}
    These results also highlight the advantages of HSC survey in studying the evolution 
    of massive galaxies.
    By the finish of this paper, the HSC survey will have already doubled its sky 
    coverage to $\sim 200$ deg$^2$, and can provide a much larger sample of massive 
    central galaxies. 
    At the same time, we will work on better data reduction of HSC images by 
    improving the deblending in crowded region and the accuracy of background 
    subtraction as they can help provide more reliable SED fitting results, and 
    push the photometric limit toward to even lower surface brightness level.

    Right now, we still rely on the \redm{} catalog from SDSS and spectroscopic 
    redshift from SDSS and BOSS.  
    Running \redm{} algorithm or similar group/cluster finder using HSC catalogs 
    will greatly help us extend the discussion of halo mass to lower mass and 
    higher redshift regimes. 
    Better identifications and measurements of satellites in massive halos will 
    also open up the possibility to study ``environment'' within the halo: e.g. 
    Compare the structures of satellites in massive halos and centrals in less 
    massive ones at similar stellar mass.

    Another key technical improvement would be to apply carefully designed 2-D 
    photometric modeling to these massive galaxies.  
    Using the same principle in \citealt{Huang2013a}, we will gradually build up 
    the complexity, and explore different models to fit these massive galaxies 
    better.  
    These 2-D models can help us removing the impact from seeing, and dealing with 
    the uncertainties of sky subtraction, so that we can measure the stellar mass 
    distributions to both smaller and larger radii. 
    Applying these models to multiband images with reasonable constraints (e.g. 
    \citealt{Huang2016}), we can characterize color gradients, and to achieve better
    estimates of total stellar mass.

    Primarily designed as a cosmological survey, the deep imaging depth and 
    excellent $i$-band seeing of HSC can greatly improve the weak lensing analysis 
    of massive galaxies. 
    Therefore, our next major goal will be to investigate trends between halo 
    properties and galaxy properties by measuring the weak lensing signal for samples 
    binned by properties such as \minn{}, \mtot{}, cluster richness, and magnitude gap.
    Joining the stellar mass distributions and the weak lensing signals together, 
    we can explore tracers that are sensitive to a range of physical processes 
    (strength and type of AGN feedback, merger rate, typical mass ratio of mergers
    \etal). 
    To help us have better physical insights, we will directly compare our results 
    with predictions from cosmological hydro-simulations such as 
    Illustris (\addref{}), Eagle (\addref{}), or \textit{Horizon-AGN}.

%% ------------------------------------------------------------------------------------ %%

\acknowledgements

  % HSC part
  The Hyper Suprime-Cam (HSC) collaboration includes the astronomical communities of Japan
  and Taiwan, and Princeton University.  The HSC instrumentation and software were
  developed by the National Astronomical Observatory of Japan (NAOJ), the Kavli Institute
  for the Physics and Mathematics of the Universe (Kavli IPMU), the University of Tokyo,
  the High Energy Accelerator Research Organization (KEK), the Academia Sinica Institute
  for Astronomy and Astrophysics in Taiwan (ASIAA), and Princeton University.  Funding was
  contributed by the FIRST program from Japanese Cabinet Office, the Ministry of
  Education, Culture, Sports, Science and Technology (MEXT), the Japan Society for the
  Promotion of Science (JSPS), Japan Science and Technology Agency (JST),  the Toray
  Science  Foundation, NAOJ, Kavli IPMU, KEK, ASIAA, and Princeton University.

  % SDSS part
  Funding for SDSS-III has been provided by the Alfred P. Sloan Foundation, the
  Participating Institutions, the National Science Foundation, and the U.S.  Department of
  Energy. The SDSS-III web site is http://www.sdss3.org.  SDSS-III is managed by the
  Astrophysical Research Consortium for the Participating Institutions of the SDSS-III
  Collaboration including the University of Arizona, the Brazilian Participation Group,
  Brookhaven National Laboratory, University of Cambridge, University of Florida, the
  French Participation Group, the German Participation Group, the Instituto de Astrofisica
  de Canarias, the Michigan State/Notre Dame/JINA Participation Group, Johns Hopkins
  University, Lawrence Berkeley National Laboratory, Max Planck Institute for
  Astrophysics, New Mexico State University, New York University, Ohio State University,
  Pennsylvania State University, University of Portsmouth, Princeton University, the
  Spanish Participation Group, University of Tokyo, University of Utah, Vanderbilt
  University, University of Virginia, University of Washington, and Yale University.

  % Pan-STARRS1 part
  The Pan-STARRS1 Surveys (PS1) have been made possible through contributions of the 
  Institute for Astronomy, the University of Hawaii, the Pan-STARRS Project Office, 
  the Max-Planck Society and its participating institutes, the Max Planck Institute 
  for Astronomy, Heidelberg and the Max Planck Institute for Extraterrestrial Physics, 
  Garching, The Johns Hopkins University, Durham University, the University of Edinburgh, 
  Queen's University Belfast, the Harvard-Smithsonian Center for Astrophysics, the Las 
  Cumbres Observatory Global Telescope Network Incorporated, the National Central 
  University of Taiwan, the Space Telescope Science Institute, the National Aeronautics 
  and Space Administration under Grant No. NNX08AR22G issued through the Planetary 
  Science Division of the NASA Science Mission Directorate, the National Science 
  Foundation under Grant No. AST-1238877, the University of Maryland, and Eotvos 
  Lorand University (ELTE).

  % LSST software
  This paper makes use of software developed for the Large Synoptic Survey 
  Telescope. We thank the LSST Project for making their code available as free 
  software at http://dm.lsstcorp.org.

  % Software
  This research made use of:
  \href{http://www.stsci.edu/institute/software_hardware/pyraf/stsci\_python}{\texttt{STSCI\_PYTHON}},
      a general astronomical data analysis infrastructure in Python. 
      \texttt{STSCI\_PYTHON} is a product of the Space Telescope Science Institute, 
      which is operated by AURA for NASA;
  \href{http://www.scipy.org/}{\texttt{SciPy}},
      an open source scientific tools for Python (\citealt{SciPy});
  \href{http://www.numpy.org/}{\texttt{NumPy}}, 
      a fundamental package for scientific computing with Python (\citealt{NumPy});
  \href{http://matplotlib.org/}{\texttt{Matplotlib}}, 
      a 2-D plotting library for Python (\citealt{Matplotlib});
  \href{http://www.astropy.org/}{\texttt{Astropy}}, a community-developed 
      core Python package for Astronomy (\citealt{AstroPy}); 
  \href{http://scikit-learn.org/stable/index.html}{\texttt{scikit-learn}},
      a machine-learning library in Python (\citealt{scikit-learn}); 
  \href{http://www.astroml.org/}{\texttt{astroML}}, 
      a machine learning library for astrophysics (\citealt{astroML});
  \href{https://ipython.org}{\texttt{IPython}}, 
      an interactive computing system for Python (\citealt{IPython});
  \href{https://github.com/kbarbary/sep}{\texttt{sep}} 
      Source Extraction and Photometry in Python (\citealt{PythonSEP});
  \href{https://jiffyclub.github.io/palettable/}{\texttt{palettable}},
      color palettes for Python;
  \href{http://dan.iel.fm/emcee/current/}{\texttt{emcee}}, 
      Seriously Kick-Ass MCMC in Python.

%%%%%%%%%%: Bibliographic Section %%%%%%%%%%

\bibliography{redbcg}

%%%%%%%%%%: Appendix Section %%%%%%%%%%%%

\appendix

%% ------------------------------------------------------------------------------------ %%

\section{A. Extraction of 1-D surface brightness profile} 
    \label{app:A}

%% ------------------------------------------------------------------------------------ %% 
    \figurenum{A1}
    \begin{figure*}[hbt!]
        \centering 
        \includegraphics[width=\textwidth]{fig/redbcg_ellipse_tech}
        \caption{\textbf{Left:} Example of the object-mask built for the \texttt{Ellipse}
            run for a typical massive galaxy in the sample. 
            All the shaded regions are masked out. 
            The three dash lines (red, inner one and two blue ones) around the target 
            at the center outlines the three radius we defined using the flux radius 
            of the target.  
            We increase the mask size for objects detected in different regions 
            separated by these apertures (which are outlined by solid, elliptical 
            apertures with different colors) using slightly different criteria.~~
            \textbf{Middle:}: The flux profile that is zoomed into the near-zero flux 
            range (top panel), and the curve-of-growth of the magnitude for the example
            massive galaxy.  
            To highlight the importance of correcting sky background, we show the profiles 
            using both images with (red, solid line) and without (black, dash line) 
            ad-hoc background correction. 
            On the top panel, besides the horizontal line that highlights the zero flux 
            level, we also show the uncertainty of the sky background estimate via 
            grey-shaded region.  
            On the bottom panel, two horizontal lines indicate the magnitudes 
            corresponding to total (solid) and half flux (dash) using the 
            background-corrected profile. ~~
            \textbf{Right:} compare the 1-D surface brightness profiles for the same 
            example galaxy extracted using different mask 
            (smaller masking region: red, dash line; larger masks: blue, dash line), 
            or different \texttt{Ellipse} settings
            (more aggressive pixel-clipping: cyan, dash line; 
             larger step in radius: green, dash line; 
             using mean flux along the isophote instead of median: purple, dash line)
            with the one using the default configuration (black, solid line).}
        \label{figure:A1}
    \end{figure*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %%

\section{B. Estimate average {$M_{\star}/L_{\star}$} using \texttt{iSEDFit}} 
    \label{app:B}

%% ------------------------------------------------------------------------------------ %% 
    \figurenum{B1}
    \begin{figure*}[bt!]
        \begin{center}
        \includegraphics[width=\textwidth]{fig/redbcg_isedfit_example.pdf}
        \caption{Left: example output figure from \texttt{iSEDFit} that shows the SED 
        	fitting results. 
            The open-boxes show the observed fluxes in 5-band, and the solid, blue-dots
            show the best-fitted results, along with the high-resolution spectrum for
            this model recontructed using the synthetic spectra from \texttt{FSPS}. 
            Top-left corner shows the best-fit stellar population parameters, and 
            bottom-right corner shows the ID, redshift of this object, and reduced 
            $\chi^2$ of the best-fit model.~~~
            Right: the Posterior distributions of a few key parameters.
            From top-left to bottom right are: 1) stellar mass (\logms{}); 2) age of the 
            population (mass and star-formation rate weighted) in Gyr; 3) star formation 
            rate ($\log\ \mathrm{SFR}\ (M_{\odot}/\mathrm{yr})$; instant one and the one 
            averaged over the previous 100 Myr; 4) stellar metallicity 
            ($\mathrm{Z}/\mathrm{Z}_{\odot}$); 5) dust extinction ($\mathrm{A}_V$ in mag);
            6) birthrate parameter ($\log\ b$; averaged over previous 100 and 1000 Myr).}
        \label{fig:ised}
        \end{center}
    \end{figure*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
    \figurenum{B2}
    \begin{figure*}[hbt!]
        \begin{center}
        \includegraphics[width=\textwidth]{fig/redbcg_isedfit_2.pdf}
        \caption{Relationships between \mstar{} and certain stellar population 
            parameter using \texttt{iSEDfit}. 
            The left figures are for the \rbcg{} sample, while the right ones are 
            for the \nbcg{} sample. 
            They are both color-coded using the mass-weighted stellar age. 
            The four stellar population properties shown here are: 
            1) mass-weighted stellar age in Gyr (top-left); 
            2) SFR-weighted stellar age in Gyr (bottom-left); 
            3) mass-weighted stellar metallicity in unit of solar value (top-right);
            4) dust extinction value in magnitude (bottom-right).}
        \label{fig:ised_2}
        \end{center}
    \end{figure*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
    \figurenum{B3}
    \begin{figure*}[hbt!]
        \begin{center}
        \includegraphics[width=\textwidth]{fig/redbcg_isedfit_3.pdf}
        \caption{Comparisons of \mstar{} estimated by \texttt{iSEDFit} using different
            assumptions. 
            In each figure, we plot the default \mstar{} values against their 
            differences with the results using other models. 
            The top (bottom) row shows comparisons for the \rbcg{} (\nbcg{}) sample. 
            The results involved here are labeled: 
            (A): default one; 
            (B): using the Salpeter IMF instead of the Chabrier one (Left column);
            (C): using the BC03 synthetic population model instead of the FSPS one
                 (Middle column);
            (D): assume that there is no dust extinction (Right column). 
            On each figure, a horizontal line shows the zero difference level, along
            with the grey shaded region that highlights the typical uncertainty of 
            the \mstar{}-differences. 
            We also show the histogram of the \mstar{}-differences on the right.}
        \label{fig:ised_3}
        \end{center}
    \end{figure*}
%% ------------------------------------------------------------------------------------ %%

    We adopt flat distribution between 0.5 to 14.0 Gyrs as prior for the look-back 
    time when the star formation turned on. 
    The exponential delayed time-scale ($\tau$) is allowed to change between 
    0.1 to 3.0 with equal probability.  
    The chance of random star burst is set at 0.2 for every 2 Gyrs. 
    The duration of the star burst is draw from a logarithmic distribution 
    between 0.03 to 0.3 Gyr; and the mass fraction formed in the burst is from 
    a logarithmic distribution between 0.01 and 1.0.

    In principle, these choices of priors could leave systematic effects in 
    the estimate of stellar mass (e.g.\ \citealt{Bernardi2016b}). 
    For low-$z$ massive ETGs like the ones in our sample, the details form of 
    SFH, importance of random star burst, and the dust extinction should not be 
    major concern.  
    However, the choices of stellar population models and IMF can still 
    change the results systematically. 
    More discussions on this can be found in Appendix~A. 
    In short: 
    \begin{enumerate}
        \item Both \texttt{FSPS+MILES} and \texttt{BC03} (\citealt{BC03} models 
            still have difficulties recovering the optical color involving filters 
            at the red end (e.g~$i-$Y), which could relate to the challenge for 
            modern stellar population models to reproduce the optical color-color 
            relation of red-sequence galaxies (e.g.\ \citealt{MIUSCAT2}), or the 
            shallower photometry of HSC-Y band data. 
        \item The \texttt{BC03} provides slightly better overall ${\chi}^2$ and 
            systematically smaller \mstar{} than the \texttt{FSPS+MILES} models.  
            However, it is possible that the \texttt{BC03} model tends to 
            underestimate the \m2l{} for a fraction of them as the estimate 
            stellar age is unrealistically young for red, massive galaxies.  
            Therefore, we still use the \texttt{FSPS+MILES} model as the fiducial 
            one.  But, switching to the \texttt{BC03} model will not change any 
            key result in this work. 
        \item The usage of \citet{Salpeter1955} IMF results in systematically 
            higher \mstar{} (on average $+0.25$ dex of \logms{}).  
            Although there are multiple lines of evidence that favor Salpeter 
            or even more ``bottom-heavy'' IMF in the most massive ETGs 
            (e.g.\ \citealt{Conroy2012}; \citealt{Cappellari2012}), we still 
            present the main results using Chabrier IMF to accommodate galaxies 
            with lower \mstar{} in the sample, and to be as consistent as possible 
            with a few other works.  
            Also, the choice of IMF does not impact our results qualitatively.     
    \end{enumerate}

    Besides the priors for stellar population properties, different treatments of 
    the light profile and accuracy of sky background subtraction are also important
    for the estimate of \mstar{} as they strongly impact the estimate of total luminosity
    (e.g.\ \citealt{Bernardi2013} and \citealt{DSouza2015}).  
    At the depth of SDSS, the default \texttt{cModel} photometry is already shown to 
    be not very accurate at high-\mstar{} end (e.g.\ \citealt{Meert2015}; 
    \citealt{Bernardi2016a}) as it does not capture the extended envelope of these 
    galaxies. 
    As for HSC, it is much more challenging for \texttt{cModel} to recover the total 
    luminosity of massive ETGs since the stellar envelope becomes even more 
    extended for neither de~Vaucouleur or exponential model to reproduce.  
    However, the HSC \texttt{cModel} under the force-photometry mode can measure 
    \textbf{average} color of the galaxy with great accuracy (e.g.\ Huang\etal~in prep.~), 
    and provide us a reliable SED to estimate the \textbf{average} \m2l{}. 
    Considering this, we separate the process of estimating the total \mstar{} of 
    massive ETGs in our sample into two steps:

    \begin{enumerate}
        \item Firstly, using the redshift and \texttt{cModel} magnitude in five bands, 
            we derive an initial estimate of the \mstar{} of the galaxy.  
            More importantly, we derive the \textbf{average} \m2l{} in $i$-band of the 
            galaxy, and use the best-fit SED to provide $k$-correction to the photometry.  
        \item In the next section, we will derive better estimate of total \mstar{} using 
            the more accurate total luminosity in $i$-band from integration of carefully 
            measured 1-D surface brightness profile, and the average \m2l{} from the SED
            fitting.  
    \end{enumerate}

    The basic results from \texttt{iSEDFit} are summarized in Figure~2, where we compare
    the relations between initial estimates of \mstar{} and (both luminosity and 
    star formation weighted) stellar age, metallicity, and dust extinction. 
    As expected, most galaxies in our samples are 
    $\log(M_{\star,\ \mathrm{ini}}/M_{\odot}) \geq 11.2$ massive galaxies that have 
    old age, high metallicity ($1.5 \times Z_{\odot}$ is the highest metallicity allowed), 
    and low dust extinction.  
    Given that we only have photometry from five optical bands, degeneracies among 
    age, metallicity, and dust extinction are naturally expected.  
    We will not use them for any scientific reason in this work, but to show that they
    behave reasonably.

%% ------------------------------------------------------------------------------------ %%

\section{C. Comparison of \mden{} profiles using \mstar{} from the GAMA survey}
    \label{app:C}

%% ------------------------------------------------------------------------------------ %% 
\figurenum{C1}
\begin{figure*}[hbt!]
    \centering 
    \includegraphics[width=\textwidth]{fig/redbcg_prof_gama_new}
    \caption{\textbf{Left:} comparison of \mstar{} estimated by the GAMA survey and 
    the ones in this work for the same galaxies. 
    We plot the \logmgama{} against the difference between \logmtot{} and \logmgama{}. 
    The format is very similar to the right panel of Fig. \ref{fig:smf1}, except that
    we color-code the \rbcg{} galaxies (orange-red) using the \ser{} index measured by 
    GAMA using \galfit{} on SDSS image. 
    The two vertical lines highlight the mass range $11.4 \leq$\logmgama{}$<11.9$ that
    is used for the comparison later.~~
    \textbf{Middle and Right figures:} we compare the \mden{} profiles of \rbcg{} 
    (orange-red) and \nbcg{} (grey-black) galaxies using the samples matched on the 
    \mgama{}-$z$ plane at $11.4 \leq$\logmgama{}$<11.9$ and $0.28 \leq z < 0.4$. 
    The formats for figure (b) and (c) are very similar to Fig.\ref{fig:prof_m100_A}.}
    \label{figure:C1}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

    As the sky coverage of this release greatly overlaps with the GAMA survey,
    we start the detailed comparison with an external check using the stellar
    mass estimated by \citep{Taylor2011}. 
    The purpose is still to investigate the impact of deeper photometry on 
    the analysis of structure of massive galaxies.  
    The stellar masses of GAMA galaxies are initially derived through careful 
    optical-SED fitting (BC03 model; Chabrier IMF) using the PSF-matched 
    aperture photometry.  
    Then they were corrected for the total luminosity estimated using single-\ser{}
    2-D model to multi-band images (\citealt{Kelvin2012}).  
    We separate the \rbcg{} and \nbcg{} galaxies that also have 
    spec-$z$ and stellar mass in GAMA DR2 (\citealt{Liske2015}).
    Most of galaxies in these subsamples have $z < 0.40$.

    % Move the section about matching to Mtot matched section

    In Fig.~10, we show the results of matches for subsamples using 
    $M_{\star, \mathrm{GAMA}}$.  
    To increase the number of available \rbcg{} to match, we loosen 
    its selection criteria to $\lambda \ge 20$ and $P_{\mathrm{CEN}} \ge 0.6$.
    Based on the distributions of the two samples at the $M_{\star, \mathrm{GAMA}}$-$z$ 
    plane, and their overlapped region, we match them in two bins of 
    $M_{\star, \mathrm{GAMA}}$ that have slightly different redshift ranges. 
    %% moved
    For the samples in two $M_{\star, \mathrm{GAMA}}$, the matches appear to be
    very good.

    In Fig.~11, we show the individual profiles, median profiles along with their 
    uncertainties derived using 5000 times bootstrap resampling, and the relative 
    difference between the profile of the \rbcg{} and \nbcg{} 
    subsamples.  
    It is very clear that, for both mass bins, the \rbcg{} has a much 
    more extended outer envelope, while its profile inside $\sim 10$ kpc is 
    very close to the \nbcg{} one.  
    This is inconsistent with the matched distributions of their ``total'' 
    stellar mass, and reveals potential issue with the stellar mass estimated 
    by GAMA.
    We can reproduce very similar results using the luminosity density profiles 
    (with or without $k$-correction) of these matched samples, which suggests 
    that the main problem does not lie in the estimate of \m2l{}, but in the 
    measurement of total luminosity using single-\ser model.  
    This highlights the importance of deep optical images in studying the 
    structure of massive galaxies.

        In cases of these $M_{\star, \mathrm{GAMA}}$-matched samples, the differences
    of median profiles are very robust.

%% ------------------------------------------------------------------------------------ %%

\section{D. Comparisons of \mden{} profiles in different redshift bins}
    \label{app:D}

%% ------------------------------------------------------------------------------------ %% 
\figurenum{D1}
\begin{figure}[htb!]
    \centering 
    \includegraphics[width=8.5cm]{fig/average_mass_profiles_fsps1_B}
    \caption{Comparison of \mden{} profiles of \rbcg{} (orange-red) and \nbcg{} 
        (grey-black) at $11.6 \le$\logmtot$< 11.9$ in redshift bins of 
        $0.3\leq z<0.4$ (solid lines) and $0.4\leq z<0.5$ (dash lines). 
        We show the individual profile in the background using much thinner line, 
        and highlight the median profiles using thicker line and darker color.
        Other formats are exactly the same with the left figure of 
        Fig.\ref{fig:avg_prof}.}
    \label{fig:D1}
\end{figure}    
%% ------------------------------------------------------------------------------------ %%

    As the massive galaxies in our samples span quite a bit in both redshift and \mtot{}, 
    it is important to evaluate the impact from PSF on the \mden{} profiles at different 
    redshift. 
    In Fig.\ref{fig:D1}, we group the \rbcg{} and \nbcg{} galaxies at  
    $11.6 \le$\logmtot$< 11.9$ into two $z$ bins ($0.3\leq z<0.4$ and 
    $0.4\leq z<0.5$). 
    We did not match the \mtot{} distributions in two $z$ bins, so slight difference in 
    average \mtot{} can be expected. 
    With the same seeing condition, the \mden{} profile of galaxy at higher redshift is 
    more vulnerable to the PSF smearing effect in the center, while suffers more in the 
    outskirt due to cosmological dimming and background noise.  
    Fig.\ref{fig:D1} clearly shows that, although the median profiles of the same sample 
    in two redshift bins follow each other well outside 10 kpc, they start to differ in 
    the central 2-3 kpc as the one from higher redshift bin has more flattened profile 
    due to PSF smearing effect.  
    Meanwhile, we notice that the median profiles of \rbcg{} and \nbcg{} in the 
    same $z$ bin are very similar to each other in the region affected by seeing.   
    This comparison confirms the radius range that is sensitive to seeing and 
    redshift distribution is well constrained within the grey-shaded area.
    It also suggests that it is important to match the redshift distributions between 
    samples before we can compare their \mden{} profiles or other properties at inner 
    region, as we did in this work. 
    In the outskirt, within 100-150 kpc, we see no difference in the median \mden{} 
    profiles caused by redshift distributions. 
    We therefore conclude that it is safe to study the \mden{} profile within this 
    radius range for massive galaxies at $z<0.5$ using HSC images.

%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
%% Table.1 
%% ------------------------------------------------------------------------------------ %% 
\clearpage
\include{table1}

%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
%%%%%%%%%%%%: End of the File %%%%%%%%%%%%
%% ------------------------------------------------------------------------------------ %%

\end{CJK*}

\clearpage

\label{lastpage}

\end{document}
%% ------------------------------------------------------------------------------------ %%

### 2016-12-04 draft/ms_v1.tex
version 0

--- 2016-12-04 draft/ms_v0.tex
@@
 \usepackage{float}
-\usepackage[usenames]{color}
+\usepackage[usenames, dvipsnames]{color}
 
@@
 \newcommand{\kevin}[1]{\textcolor{green}{\textbf{[Kevin: #1]}}}
+\newcommand{\update}[1]{\textcolor{Bittersweet}{#1}}
 
@@
 
-\title{First Detection of the Enviromental Dependence of the Masses, Sizes, and Structures of Massive Galaxies }
+\title{First Detection of the Environmental Dependence of the Structures of Massive Galaxies }
 
@@
         HSC collaboration\altaffilmark{1}}   
-
 %        \author{Song Huang (黄崧)\altaffilmark{1} 
@@
     the University of Tokyo (Kavli IPMU, WPI), Kashiwa 277--8583, Japan}
-
 %\altaffiltext{2}{Princeton University Observatory, 
@@
 %% ------------------------------------------------------------------------------------ %% 
+  \begin{figure*}[t!]
+      \centering 
+      \includegraphics[width=\textwidth]{fig/redbcg_m100_m10_compare}
+      \caption{Three-color images for a subsample of massive galaxies at similar redshift
+      		($\sim 0.4$), and with similar \mstar{} inside inner 10 kpc (indicated by the 
+            dash-line cicle on top-left figure; 
+            $11.2<\log (M_{\star,10\ \mathrm{kpc}}/M_{\odot})<11.3$). 
+            However, they span quite a large range in \mstar{} within 100 kpc 
+            (highlighted by the solid bar on the top-left figure). 
+            From top-left to bottom-right, their \mtot{} increases from 
+            $10^{11.2} M_{\odot}$ to $10^{11.7} M_{\odot}$.
+            The three galaxies from \rbcg{} sample are highlighted via red frames.
+            }
+      \label{fig:m100_m10_color}
+  \end{figure*}
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
 \section{Introduction}
@@
         \item \plan{Briefly explain why massive early-type galaxies are important through 
-            the difficulties of stellar-halo mass relation and stellar mass function at the 
-            high-mass end.}
+            the difficulties of stellar-halo mass relation and stellar mass function at 
+            the high-mass end.}
         \item \plan{Brief summary of the current understanding of their cosmic assembly 
@@
 
-\alexie{Because the text is long, at this point in the introduction, let's give reader an overview of our methodology.
-Let's sim for one or two succint paragraphs.
-That way they will begin the paper having a better idea of what we want to achieve.
-We will want to give them some key ideas here.
-1) Quality of the HSC data (Reference Fig 1 here) 2) we want to look for enviromental differences, we'll use  a cluster catalog to divide into halo mass bins, 3) define the concepts of M10 and M100 (and reference Fig 10 here).
-You sort of have the elements in place below, by needs more editing and reorganizing.}
-
-\alexie{Bring Fig 1 and Fig 10 here so they are the two first figures.}
-
-	\song{Ok, will do; I will just say Fig 10 demonstrate the stellar mass and structural 
-    	diversity of the massive galaxies}
-
-    To achieve this goal, we select a large sample of massive central galaxies within
-    halos that are more or less massive than \logmh{}$\sim 14.0$ at $0.3 < z < 0.5$ 
-    from the current $\sim 100$ square degree of HSC data.
-    As indicated by the $M_{\star}$-$M_{\mathrm{Halo}}$ relation, at the same \mstar{}, 
-    massive central galaxies with similar morphology can live in halos within large range 
-    of \mhalo{}, therefore it is very interesting to look into the influence of their halos 
-    on the structure of these galaxies. 
-    Under the adopted cosmology, $1.0^{\arcsec}$ equals 4.4 and 6.1 kpc at redshift 0.3 
-    and 0.5.  
-    In this redshift range, we can reliably measure the total stellar mass within the 
-    inner 5 to 10 kpc (where the ``in-situ'' stellar component should dominate) given 
-    the typical seeing, while still be able to map their stellar distributions out to 
-    $\sim 100$ kpc at $z\sim 0.5$ given the imaging depth of these HSC data.
-    Also, we can safely ignore significant mass growth and structural evolution 
+    \update{Here, we take advantage of the excellent image quality of the HSC survey, and 
+    investigate the potential environmental dependence of structure for massive galaxies 
+    vial comparing the surface \mstar{} density profiles and structural scaling relations 
+    between massive central galaxies in different environments. 
+    As shown in Fig.\ref{fig:sdss_compare}, the HSC $i$-band images are typically 3-4 
+    magnitude deeper than SDSS ones, and have much better seeing condition 
+    (median FWHM$\sim 0.6^{\arcsec}$), hence they are perfect for mapping the \mstar{}
+    distributions of massive galaxies out to very large radius. 
+    With the help of a cluster catalog, we select a large sample of massive central 
+    galaxies in halos that are more or less massive than \logmh{}$\sim 14.0$ at 
+    $0.3 < z < 0.5$ from the available $\sim 100$ square degree of HSC data.}
+
+    \update{Due to the difficulty in appropriately modeling the \mstar{} distributions of 
+    massive galaxies out to their very outskirts, we focus on \mstar{} within two different 
+    physical apertures in this work:}
+
+    \begin{itemize}
+        \item \update{\mstar{} within 10 kpc, \minn{}: according to the ``two-phase'' 
+            scenario, the ``in-situ'' star-formation quickly built up the inner, dense 
+            core of massive ETGs.  
+            Based on recent observations and simulations (e.g.~\citealt{vanDokkum2010}; 
+            \citealt{RodriguezGomez2016}), the in-situ 
+            component distributes mostly within the effect radius ($R_{\mathrm{e}}$, 
+            or 5-10 kpc) in massive galaxies.  
+            Here we use \minn{} as a proxy of the \mstar{} formed in the ``in-situ''
+            phase.  Although it is an empirical choice, the detailed comparison of 
+            \mden{} profiles later suggests it indeed helps reveal interesting 
+            environmental dependence.  
+            Under the adopted cosmology, $1.0^{\arcsec}$ in radius equals 4.4 and 6.1 kpc 
+            at redshift 0.3 and 0.5.  
+            We can reliably measure \minn{} without being bothered by smearing effect
+            of seeing.}
+        \item \update{\mstar{} within 100 kpc, \mtot{}: for massive galaxies in this work, 
+            100 kpc aperture reaches to 5-10 $\times R_{\mathrm{e}}$ and very low 
+            \mden{} region, hence can be treated as proxy of the ``total'' \mstar{}. 
+            Limited by the accuracy of background subtraction, the \mden{} profile 
+            of outer region can not be reliably recovered for massive galaxies across 
+            our redshift range. 
+            Although not perfect, \mtot{} is still a much better tracer of total 
+            \mstar{} than the model-dependent ones using shallower images.}
+    \end{itemize}
+
+    \update{Massive central galaxies in this work show an intriguing diversity on the 
+    plane defined by these two metrics.  
+    We preview this using Fig.\ref{fig:m100_m10_color}, which shows a subsample of 
+    massive galaxies at $z\sim 0.4$ that share very similar value of \minn{}, but show 
+    a large range of outer structures. 
+    Assuming galaxies at the same \minn{} have similar amount stars in the in-situ 
+    component, it is of great interest to investigate the relation between their 
+    environments and outer envelopes that are assembled at later time. 
+    It is worth noting that, although a circular aperture is shown on 
+    Fig.\ref{fig:m100_m10_color}, we always use elliptical apertures that follow the 
+    average isophotal shape for photometry in this work.}
+    And, within our choices of redshift and \mstar{} ranges, we can safely ignore 
+    significant mass growth and structural evolution 
     (no star formation, lower merger rate \etal~e.g.\ \citealt{Bellstedt2016},
@@
     massive galaxies. 
-    Our first step is use the HSC galaxy catalog to create an initial sample of massive
-    galaxies that is complete to \xxx{} at $z < 0.5$. 
+    \update{
+    As the first step, we select the initial sample of massive galaxies at $z < 0.5$
+    from the HSC photometric catalog.}
     We will then use custom made software to re-measure luminosities for all galaxies 
@@
     (will be referred as \texttt{hscZ}).
-    As we will show later (see Section \ref{ssec:future}), to ensure reasonable 
+    As we will mention at the end of the paper, to ensure reasonable 
     \mstar{}-completeness at the high-\mstar{} end, and make sure the samples we 
@@
       \includegraphics[width=\textwidth]{fig/redbcg_smf_new}
-      \caption{\textbf{Left:}: We compre the \mstar{} volume-density distributions of 
-      	  \rbcg{} (red) and \nbcg{} (black) galaxies using stellar mass based on 
-          \mcmodel{} (dash) and \mtot{} (solid) to highlight the increase of \mstar{}
-          due to different methods.  
-          Here we also show the volume-density distributions of the \texttt{S82-MGC} 
-          galaxies (green) to evaluate the \mstar{}-completeness. 
-          The vertical line highlight \logms{}$=11.6$ before correcting the \mstar{} using
-          total luminosity from 1-D profile.~~
-          \textbf{Right:} We plot \mtot{} against the difference between \mtot{} and 
-          \mcmodel{} for the \rbcg{} (red squares; color indicates redshift) and \nbcg{}
-          (grey dots) galaxies. 
-          Two vertical lines highlight the $11.6<$\logmtot{}$<11.9$ mass range where the
-          two samples overlap the most.
-          We also show the historgrams of the mass differences for galaxies with 
-          $11.6<$\logmtot{}$<11.9$ on the right side. 
-          \song{The figure is updated, but I think the histogram on the right side is 
-          useful; 1) it shows the average mass difference clearly; 2) shows the differences
-          between the two samples; Also try to update the caption, let me know what do you 
-          think. And, I think the left panel should stay here, because we need to discuss 
-          the mass completness here; the discussion section can use another figure where 
-          we overplot other people's SMF; we just need some caveats.}
-          \alexie{Simplfy the caption here. What is the main message we are trying to convey. 
-          I think the point of this figure is to show that cmodel is underestimated. 
-          Focus on that message. Some information here is un-necessary. 
-          Also looks make some changes to this Figure: 1) right. Remove the right hand 
-          histograms. 2) I ont think we learn much by the color coding. Just use a single 
-          color (less explaning to do). Label using your names cenLowMh and cenHighMh}}
+      \caption{\textbf{Left:} Difference between \mcmodel{} and \mtot{} for central
+      	galaxies in halos smaller than $10^{14}$ M$_{\odot}$ (grey dots) and in
+        halos larger than $10^{14}$ M$_{\odot}$ (red squares). 
+        On average, \mcmodel{} underestimates the total stellar mass of massive 
+        galaxies by 0.1 dex and the difference can exceed 0.2 dex. 
+        Vertical histograms indicate the mass difference for galaxies with
+        $11.6<$\logmtot{}$<11.9$. 
+        \textbf{Right:}: Impact of using \mcmodel{} on the galaxy stellar mass
+        function. 
+        Dashed lines correspond to the SMF computed using \mcmodel{} as an estimate
+        of the total luminosty whereas solid lines correspond to the SMF computed
+        using the total luminosity from our 1-D profile modeling. 
+        The impact on the SMF can exceed 0.2 dex for massive centrals living in
+        halos larger than $10^{14}$ M$_{\odot}$ (red lines).}
       \label{fig:smf1}
   \end{figure*}
+
+%           We compre the \mstar{} volume-density distributions of 
+%      	  \rbcg{} (red) and \nbcg{} (black) galaxies using stellar mass based on 
+%          \mcmodel{} (dash) and \mtot{} (solid) to highlight the increase of \mstar{}
+%          due to different methods.  
+%          Here we also show the volume-density distributions of the \texttt{S82-MGC} 
+%          galaxies (green) to evaluate the \mstar{}-completeness. 
+%          The vertical line highlight \logms{}$=11.6$ before correcting the \mstar{} using
+%          total luminosity from 1-D profile.~~
+
 %% ------------------------------------------------------------------------------------ %%
@@
     galaxies of less massive halos and massive satellites galaxies.  
+    \update{
     To select a purer sample of massive centrals in $M_{200m}<10^{14} h^{-1} M_{\odot}$
-    halos, we identify and remove any galaxy that is too close to 
-    \emph{any cluster member} in \redm{} catalog in both radius and redshift direction.
-
-    \alexie{This is a rather strange procedure, I think we need to change it (referee and readers will complain!).
+    halos, we identify and remove all galaxies within a cylinder region around the 
+    the central galaxies in \redm{} catalog.
+    We choose to use the $R_{200m}$ as the radius of the cylinder. 
+    For each cluster, we convert the richness estimates into $M_{200m}$ using the 
+    calibration in \citep{Simet2016}, then estimate the $R_{200m}$ using $M_{200m}$
+    and the mass-concentration relation in \citep{Diemer2015}. 
+    For the thickness of the cylinder, we use twice the uncertainty of the photometric 
+    redshift error of each cluster.  
+    At $0.3 < z < 0.5$, such uncertainty is between 0.015 to 0.025, which are more than 
+    enough to exclude cluster member.}
+    \song{The actual number waits to be updated}
+
+    %\alexie{This is a rather strange procedure, I think we need to change it (referee and readers will complain!).
 What we really want to do is to remove any galaxies that have $r<R200$ in projection (from the galaxy with the highest value of Pcen) and remove galaxies within some deltaz of the cluster redshift.
@@
 Sorry, I know this might mean re-doing everything.....let's discuss by Skype if this is a major issue.}
-
-    For each \redm{} cluster member, we remove objects within a cylinder region 
-    around it from the remaining sample. 
-    Such cylinder is defined by 1) physical radius of 3.0 Mpc at the red-sequence 
-    redshift of the cluster; 2) $|z - z_{\lambda}| \leq 0.05$ as 
-    \nbcg{} later.
 
@@
             \mstar-completeness (see Section \ref{ssec:s82}).  
-            Also, during the comparison of structures, we will mainly 
-            \song{Will use $>30$ sample as default later; will update the figure first, 
-            then correct the number of galaxies when I go through the text again.}
-            \alexie{Why mainly use here? We have defined the high mass sample to be above this cut. Lets use $\lambda>30$ everywhere! Making more samples will make readers confused.} use \rbcg{} 
-            galaxies with $\lambda > 30$ to ensure that they are from more massive 
-            halos than the ones in \nbcg{} sample.
+            \update{Although we use the $\lambda > 30$ sample for structural comparison, 
+            in the Appendix.\ref{app:robust}, we show that the results will not change 
+            if we include central galaxies of $20 < \lambda \leq 30$ clusters in the 
+            \rbcg{} sample.}
     \end{itemize}
@@
     image and a subset of isophotes.  
-    Appendix\ref{app:A} includes more details about the \texttt{Ellipse} procedure.
+    Appendix.\ref{app:A} includes more details about the \texttt{Ellipse} procedure.
 
@@
     high-\mstar{} end. 
-    Please see Appendix\ref{app:B} for more detailed discussions of the SED fitting
+    Please see Appendix.\ref{app:B} for more detailed discussions of the SED fitting
     results.  
@@
 
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %% 
-  \begin{figure*}[t!]
-      \centering 
-      \includegraphics[width=\textwidth]{fig/redbcg_sample_stats}
-      \caption{\textbf{Left}: The \logms{}-$g-r$ color relation of the \rbcg{} 
-          (red circle; detaield format is the same with the right panel of 
-          Fig.\ref{fig:smf1}) and \nbcg{} (grey dots) samples.
-          We apply the $k$-corrections from \texttt{iSEDFit} fitting to the colors.~~
-          \textbf{Middle}: the histograms of \mtot{} for the \rbcg{} (orange-red) and 
-          \nbcg{} (grey-black) samples at both $z>0.2$ (step-filled histogram) and 
-          $0.3 \leq z \leq 0.5$ (stepped histogram). 
-          The vertical lines in both left and middle figures highlight the 
-          $11.6<$\logmtot{}$<11.9$ mass range that will be used in the comparison of 
-          the \mtot{}-matched samples.~~
-          \textbf{Right}: the histograms of the redshift for the \rbcg{} and 
-          \nbcg{} galaxies in both \logmtot$>11.2$ and $11.6<$\logmtot{}$<11.9$
-          mass bins.
-          The vertical lines highlights the $0.3\leq z \leq 0.5$ redshift range 
-          \song{Will move to new Appendix later; but the figures are updated here; 
-          I will make sure to use consistent symbols, colors, and legends.}
-          \alexie{Move this figure to the appendix.
-It is not clear to be that we need this Figure anyway.
-We can say that we make matched samples in the text.
-I think that is enough.
-If the referee wants to see the Figure, we can show him or her.
-But I think it just adds clutter.}.
-      }
-      \label{fig:sample_stats}
-  \end{figure*}
 %% ------------------------------------------------------------------------------------ %%
@@
       \caption{
-      	\song{The figures are updated as you suggested; But I want to point out that
-        the two samples have different mass completeness (\rbcg{} has photo-$z$ ones), and 
-        I simply combine them.  The table at the end will be updated, and I will provide 
-        the average profiles from our key figures too.}
-      	\alexie{I have a suggestion that I think will make this figure more simple and wil also help with the structure of the text.
-In the left hand side, don't bin by $\lambda$.
-Instead, only make mass bins.
-That way you don't have to worry about getting into the matched samples at this point because you wont be showing the enviromental dependence.
-And when comparing on the rigth hand side, it is not clear which lines we want to compare with (are previous results for BCgs, for field galaxies,...?
-readers don't know).
-I think it will be a more straightforward comparison just to show the stellar mass bins here.
-For our stellar mass bins, you only need the labels for our data once on the left hand side.}.
       	Left: Median \mden{} profiles of galaxies in different \mtot{} bins:
@@
       \centering 
-      \includegraphics[width=\textwidth]{fig/redbcg_prof_m100A}
-      \caption{\alexie{So this is our main figure, right?
-We really need to make this stand out.
-Remove all the matched sample plots on the left (appendix?).
-We only need to say we do the matched samples in the text, we don't need a figure to back this up.
-Then, you have a seperate figure for $M10$.
-Why not combine the two into a single four panel figure?
-I think that would capture the main result pretty well, and show M10 and M100 side by side.} Comparison of the \mden{} profiles for \mtot{}-matched samples of \rbcg{}
-      (orange to red) and \nbcg{} (grey to black) galaxies within $11.6<$\logms{}$<11.9$.
-      \textbf{Left figure} shows the details of the \mtot{}-matching process.  
-      On the top panel, we show the overall distributions of \rbcg{} (light orange boxes) 
-      and \nbcg{} (light grey dots) galaxies on the \mtot{}-$z$ plane.  
-      And, we match the two sample in the \mtot{}-$z$ space outlined by the shaded region.
-      We highlight the \rbcg{} galaxies in this region using bigger boxes in red frames, 
-      whose size reflects the $P_{\mathrm{Cen}}$ value.  
-      We also color-code them using the richness ($\lambda$) of the host cluster. 
-      The matched \nbcg{} galaxies are highlighted using darker color and bigger dots. 
-      To further evaluate the matching results, we show the distributions of \mtot{} 
-      (middle panel) and redshift (bottom panel) separately. 
-      On both panesl, we show the histograms along with their kernel density 
-      distributions.  
-      And, on the top of each panel, two sets of short vertical lines highlight the median 
-      value (solid) and the inter-quartile (dash) of each distribution.~~~
-      \textbf{The figure on the right} shows the results of the profile comparison.  
+      \includegraphics[width=\textwidth]{fig/redbcg_prof_1}
+      \update{
+      Comparison of the \mden{} profiles for \mtot{}-matched ($11.6<$\logmtot{}$<11.9$) 
+      and \minn{}-matched ($11.2<$\logminn{}$<11.6$) samples 
+      of \rbcg{} (orange to red) and \nbcg{} (grey to black) galaxies.
+      \textbf{Left} shows the results for the \mtot{}-matched samples.
+      For details of the matching process, please see Appendix.\ref{app:match}.  
       On its upper panel, we show the \mden{} profile of each galaxy using very light 
@@
       Other formats are the same with Fig.\ref{fig:avg_prof}.
-      Meanwhile, we hightligh the difference between the median profiles and its 
+      Meanwhile, we highlight the difference between the median profiles and its 
       uncertainty on the bottom panel (brown solid line and shaded region).
@@
       mixed sample, and have the same sizes with the matched \rbcg{} and \nbcg{} ones.
-      Repeating this process many times, the median random differential profile 
-      (black solid line), their 1-$\sigma$ (dark-grey shaded region) and 3-$\sigma$
-      (light-grey shaded region) are highlighted.
-      \song{Will make a new 4 panels figures here; but I want to make some changes as 
-      if we simply put the current ones together, it looks bad...}}  
+      Repeating this process many times, the median of these random differential 
+      profiles (black solid line), the 1-$\sigma$ (dark-grey shaded region) and 3-$\sigma$
+      (light-grey shaded region) uncertainties are shown on the bottom panel as well. 
+      A darker vertical dash-line highlights the 100 kpc radius.~~
+      \textbf{Right} shows the results for the \minn{}-matched samples. 
+      The format is exactly the same with the left one, except that the darker vertical 
+      dash-line now highlights the 10 kpc radius.}
       \label{fig:prof_m100_A}
@@
     And we also derive the $k$-corrected luminosity and colors from the results.
-    In Appendix\ref{app:B}, we also show the outputs like the average stellar age, 
+    In Appendix.\ref{app:B}, we also show the outputs like the average stellar age, 
     metallicity, and internal dust extinction all behave reasonably for both 
@@
     estimates for galaxies in common, given the differences in data and method. 
-    Please see the Appendix\ref{app:C} for more details. 
+    Please see the Appendix.\ref{app:C} for more details. 
     In short, we notice systematic differences between the two \mstar{} estimates, 
@@
 
-    In the left figure of Fig.\ref{fig:sample_stats}, we show the \mtot{}-color 
-    relations using the $k$-corrected $g-r$ color for the \rbcg{} and \nbcg{} 
-    samples. 
-    Both samples follow the same tight red-sequence with very little contamination 
-    from star-forming galaxy in the ``blue cloud''.
-    And, at fixed \mtot{}, we see little offset in color distributions of the two 
-    samples suggesting that both samples consist of old quiescent galaxies with 
-    similar average stellar population properties.  
-    This is consistent with previous result that suggests the average stellar 
-    population of massive central galaxy does not depend on \mhalo{} 
-    (e.g.\ \citealt{Park2007}).  
-    To look into the potential environmental dependence of structure, we will 
-    focus on the mass range of $11.6 \le$\logmtot{}$\le 11.9$, where both samples 
-    have acceptable completeness, and their \mtot{} distributions greatly overlap
-    (see the normalized distributions of \mtot{} in the middle panel of 
-    Fig.\ref{fig:sample_stats}). 
-    Due to the different sources of redshift for the \rbcg{} and \nbcg{} samples, 
-    the two samples have quite different redshift distributions 
-    (right figure of Fig.\ref{fig:sample_stats}).
-    Even within the $11.6 \le$\logmtot{}$\le 11.9$ mass bin, the redshift
-    differences still differ from each other a little bit.  
-    Apparently, the redshift distribution of the \nbcg{} sample skews toward 
-    higher-$z$ end, primarily due to the contribution of BOSS spec-$z$.
-    This could lead bias into the comparison of \mden{} profiles and other 
-    properties between the two sample (please see Appendix\ref{app:D} for more 
-    details).  
-    We will address this via matching the two samples in \mtot{} and redshift
-    distributions carefully before the comparisons.
+    \update{In Appendix.\ref{app:basic}, we summarize the basic statistics of 
+    the \rbcg{} and \nbcg{} samples.  In general:}
+
+    \begin{itemize}
+        \item \update{The two samples follow the same, tight ``red-sequence'' 
+            defined by $k$-corrected colors.}
+        \item \update{The redshift distributions are reasonably similar in 
+            $0.3 < z < 0.5$, but the difference can still bias the comparison of
+            \mden{} profiles.}
+        \item \update{Although their \mtot{} overlaps a lot between 
+            $11.6 <$\logmtot{}$< 11.9$, the relative distributions within this 
+            bin are still very different.}
+        \item \update{The distributions of \minn{} overlaps the most between 
+            $11.2 <$\logminn{}$< 11.6$, but the relative distributions also 
+            show difference within this \minn{} range.}
+    \end{itemize}
+
+    \update{To compare their structural details, we will focus on \rbcg{} and 
+    \nbcg{} galaxies with $11.6 \le$\logmtot{}$\le 11.9$.  
+    Both samples have reasonable completeness in this \mtot{} range
+    (see Fig.\ref{fig:smf1}).
+    In light of the differences in distributions of \mtot{}, \minn{}, and redshift, 
+    we will carefully match these properties between the \rbcg{} and \nbcg{}
+    samples to make sure the comparison is fair and meaningful.  
+    Please see the next section and Appendix.\ref{app:match} for more details.}
 
@@
 
-%% ------------------------------------------------------------------------------------ %% 
-  \begin{figure*}[t!]
-      \centering 
-      \includegraphics[width=\textwidth]{fig/redbcg_prof_m100B}
-      \caption{Comparisons of the \mden{} profiles for \rbcg{} (orange-red) and \nbcg{} 
-      	(grey-black) galaxies that are matched using proxies of total \mstar{}. 
-        The formats are in consistent with the right figure of Fig.\ref{fig:prof_m100_A}.
-        The differences are, here, the samples are matched in slightly differnt ways. 
-        From left to right: a) using samples at lower redshift ($0.3 < z < 0.4$); 
-        b) using \rbcg{} sample with $\lambda > 20$ instead of 30; 
-        c) using \mstar{} within 150 kpc instead of 100 kpc.
-        The results are broadly consistent with the one in Fig.\ref{fig:prof_m100_A}.
-        \song{Considering to move to a new Appendix.} \alexie{This Figure can be moved to an appendix.
-It can also be summarized by saying in the main part of the paper that "we have tested that our results are robust to, the choice of the redshift range, the lower $\lambda$ cut, .....".
-I think it is probably enough to simple say this in the text.
-Not 1oo percent convinced you need a figure to abck this up.}}
-      \label{fig:prof_m100_B}
-  \end{figure*}
-%% ------------------------------------------------------------------------------------ %%
-
 \subsubsection{Internal Comparison and Comparison with Previous Works}
@@
 
-    As discussed earlier, although the mass-size scaling relation has been intensely 
-    discussed related to the topic of environmental dependence of structure, it may not be 
-    the best tool to investigate this problem.    
+    \song{Due to the change of figure, this section has been updated slightly}
+
+    As discussed earlier, although the mass-size scaling relation has been intensively 
+    discussed when it comes to the topic of environmental dependence of structure, 
+    it may not be the best tool to investigate this problem.    
     Compared to the simple scaling relation, the detailed stellar mass density profiles 
@@
 
-    Before the actual comparisons, we first show the general properties 
-    of these 1-D profiles by separating both samples into different bins 
-    of \mtot{} and redshift, also by comparing them with results from 
-    literature (Fig.\ref{fig:avg_prof}).   
-    For profiles in each bin, we derive the median profile along with its 
+    \update{
+    Before dive into more details, we first show the average \mden{} of massive galaxies 
+    at $0.3 < z < 0.5$ in three \mtot{} bins after mixing the \rbcg{} and \nbcg{} 
+    samples together\footnote{Knowing that the two samples have different levels of 
+    completeness, here we simply mean to show the general properties of massive galaxies.
+    In the first two \mtot{} bins, the \nbcg{} galaxies dominate the number; while in
+    the highest \mtot{} bin, the two samples have roughly the same size.}.   
+    For \mden{} profiles in each \mtot{} bin, we derive the median profile along with its 
     uncertainty using bootstrap resampling method (5000 times). 
-    The left panel of Fig.\ref{fig:avg_prof} focuses on different mass bins.  
-    As expected, for both samples, higher \mtot{} moves the median mass 
-    density profile upward a little in the inner region, but makes it 
-    more extended in the outer part.
-    In the mass range we explored ($\ge 10^{11.2} M_{\odot}$), most of these 
-    ETGs are slow-rotating (e.g.\ \citealt{Cappellari13b}) giant ellipticals 
-    with boxy inner isophotal shape (e.g.\ \citealt{Kormendy2009}), and 
-    flattened density profile at the center (e.g.\ \citealt{Lauer07}), 
-    but their structure in the outskirt clearly does \textbf{NOT} response 
-    to stellar mass increase in a self-similar way.
-
-    In principe, this is consistent with result from HST observations of 
-    BCGs at $0.3 < z <0.9$ (\citealt{Bai2014}) and the claimed positive 
-    correlation between luminosity and \ser index
-    (e.g.\ \citealt{Savorgnan13})\footnote{But it does not mean such high 
-    \ser index model works well for massive ETGs as they fail at the inner-most 
-    region dramatically, and can not explain the radial variation of 
-    isophotal shape}; it is also consistent with the picture that more 
-    massive ETGs experienced more recent (minor) mergers.
-
-\alexie{My comment in Figre \ref{{fig:avg_prof}} wil make this part unnecessary and will improve the flow of the paper.}    At the same time, such behaviour should make us very cautious about 
-    any indication of ``environmental dependence of structure'' as it 
-    may be degenerate with difference caused by stellar mass when the 
-    two samples are not perfectly matched in mass.  
-    This is exactly what we see in the median profiles of \rbcg{}
-    and \nbcg{} in the same mass bins. 
-    Although the comparison shows that \rbcg{} shows much more 
-    extended outer envelope than \nbcg{}, the very similar profile
-    in the inner $\sim 10$ kpc reveals that this is dominated by the 
-    different mass distributions in two samples.
-
-    In the right panel of Fig.\ref{fig:avg_prof}, we compare these median 
-    profiles with a few past works.  
-    \citep{Huang2013a}, derived the median stellar mass density profile 
-    for a small sample of very nearby ellipticals from the 
-    Carnegie-Irvine Galaxy Survey (CGS, \citealt{CGS1}).
-    Individual profile and total luminosity were derived from 
-    three-component 2-D models that describe both very inner and outer 
-    luminosity distributions of these galaxies accurately. 
+    In the left panel of Fig.\ref{fig:avg_prof}, we can see that the higher \mtot{} 
+    shifts the median \mden{} profile up a little bit in the inner region, but makes 
+    the outskirt significantly more prominent. 
+    Most of these very massive galaxies ($\ge 10^{11.4} M_{\odot}$) should be 
+    slow-rotating (e.g.\ \citealt{Cappellari13b}) giant ellipticals with ``boxy'' inner 
+    isophotal shape (e.g.\ \citealt{Kormendy2009}), and slightly flattened \mden{} profile 
+    around the center (e.g.\ \citealt{Lauer07}).
+    But their structures in the outskirt clearly does \textbf{NOT} response to the 
+    increase of ``total'' stellar mass in a self-similar way.}
+
+    In principe, this is consistent with result from HST observations of BCGs at 
+    $0.3 < z <0.9$ (\citealt{Bai2014}) and the claimed positive correlation between 
+    luminosity and \ser index (e.g.\ \citealt{Savorgnan13})\footnote{But it does not mean 
+    such high \ser index model works well for massive ETGs as they fail at the inner-most 
+    region dramatically, and can not explain the radial variation of isophotal shape}; 
+    it is also consistent with the picture that more massive ETGs experienced more recent 
+    (minor) mergers.
+
+    %At the same time, such behaviour should make us very cautious about 
+    %any indication of ``environmental dependence of structure'' as it 
+    %may be degenerate with difference caused by stellar mass when the 
+    %two samples are not perfectly matched in mass.  
+    %This is exactly what we see in the median profiles of \rbcg{}
+    %and \nbcg{} in the same mass bins. 
+    %Although the comparison shows that \rbcg{} shows much more 
+    %extended outer envelope than \nbcg{}, the very similar profile
+    %in the inner $\sim 10$ kpc reveals that this is dominated by the 
+    %different mass distributions in two samples.
+
+    In the right panel of Fig.\ref{fig:avg_prof}, we compare these median profiles with 
+    a few past works.  
+    \citep{Huang2013a}, derived the median \mden{} profile for a small sample of very nearby 
+    ellipticals from the Carnegie-Irvine Galaxy Survey (CGS, \citealt{CGS1}).
+    Individual profile and total luminosity were derived from three-component 2-D models 
+    that describe both very inner and outer luminosity distributions of these galaxies 
+    accurately. 
     The average stellar mass of this sample is around $10^{11.3} M_{\odot}$.
-    Due to the proximity of this sample ($< 100$ Mpc), the average profile 
-    is unaffected by seeing within $\sim 1$ kpc.
+    Due to the proximity of this sample ($< 100$ Mpc), the average profile is unaffected by 
+    seeing within $\sim 1$ kpc.
     Most galaxies of the CGS sample are not in any cluster.
-    The median profile qualitatively agrees with the median profile of 
-    \nbcg{} in the low mass bin, especially in the inner region. 
-    Outside the inner 15 kpc, the CGS median profile shows a slightly more
-    prominent outer envelope.  
-    While this could simply reflect the small size of CGS sample ($\sim 30$),
-    interestingly, it is also consistent with the expectation if the 
-    mild mass growth from $z\sim 0.4$ mostly happened at the outskirt.   
+    The median profile qualitatively agrees with the median profile in the lowest 
+    \mtot{} bin, especially in the inner region. 
+    Outside the inner 15 kpc, the CGS median profile shows a slightly more prominent 
+    outer envelope.  
+    While this could simply be due to the small size of the CGS sample ($\sim 30$),
+    interestingly, it is also consistent with the expectation if the mild mass growth 
+    from $z\sim 0.4$ to $z=0$ mostly happened in the outskirt.   
     The CGS images are already slightly deeper than SDSS images in $r$-band,
-    however, the median profile can only reach to $\sim 50$ kpc (with much 
-    larger uncertainty compared to this work) for ETGs within $\sim 100$ Mpc.
-    Such comparison clearly highlights the improvement made by the deep HSC 
-    images as individual profile of $z\sim 0.5$ galaxy is reliable out to 
-    at least 100 kpc.
+    however, the median profile can only reach to $\sim 50$ kpc (with much larger 
+    uncertainty compared to this work) for ETGs within $\sim 100$ Mpc.
+    Such comparison clearly highlights the improvement made by the deep HSC images as 
+    individual profile of $z\sim 0.5$ galaxy is reliable out to at least 100 kpc.
 
@@
       \centering 
-      \includegraphics[width=14.0cm]{fig/redbcg_prof_m100C}
+      \includegraphics[width=\textwidth]{fig/redbcg_prof_2}
       \caption{Comparisons of the \mden{} profiles for \rbcg{} (orange-red) and \nbcg{} 
@@
         Fig.\ref{fig:prof_m100_A}.
-        The difference in median profiles is more significant in higher \mtot{} bin.}
+        The difference in median profiles is more significant in higher \mtot{} bin.
+        \song{Figure has been updated, but need to update the caption.}
+        }
       \label{fig:prof_m100_C}
@@
 
-    At the similar redshift with our sample, we compare with mass density 
-    profile extracted from stacked images of massive ETGs at $0.25 < z < 0.50$ 
-    using HST/ACS images (\citealt{Patel2013}).  
-    These galaxies are selected at constant cumulative number density, and 
-    as progenitors of $z=0$ massive ETGs.  
-    The average stellar mass is $\sim 10^{11.2} M_{\odot}$ according to 
-    their estimates.  
-    However, given the shallower depth of the ACS images and the usage of the 
-    BC03 model (each could cause -0.1 dex mass offset compared to this work), 
-    this sample should be comparable to the \nbcg{} sample in the
-    lowest mass bin, and the comparison of their median profiles does reflect
-    that.  
-    Moreover, since the profile from HST/ACS image is not bothered by PSF 
-    within 1 Kpc, the comparison illustrates that the HSC median profiles 
-    in our redshift range are indeed not affected by seeing outside the 
-    shaded region. 
-    In fact, as we suggested, our estimate is quite conservative, the profiles 
-    within 5 kpc should be reliable.
-
-    Besides these observations, we also compare with the predicted average 
-    stellar mass density profile for central galaxies of massive halos 
-    ($13.5 < \log M_{200,c} < 14.0$) in simulation (\citealt{Cooper13}). 
-    This is achieved by combining the detailed assembly information of halos 
-    from dark-matter-only simulation with semi-analytic model and 
-    particle-tagging technique (\citealt{Cooper10}).
-    Although the physical resolution and detailed baryonic processes are 
-    not as ``realistic'' as state-of-art hydro-simulation, it is very 
-    efficient in providing rough stellar mass distributions for large number 
-    of massive halos. 
-    Without any adjustment, the profile is quite similar to the \nbcg{}
-    sample in the $11.5 < \log M_{\star} < 11.7$ bin within inner 20 kpc; 
-    but it predicts a too significant outer envelope for its average halo mass.
-    Without going into details to find the cause of such discrepancy in this 
-    work, the comparison already suggests that the comparison between deep 
-    observed mass density profiles with the ones from modern simulations is 
-    going to be quite interesting, especially in the outskirt.
+    \citet{Patel2013} extracted the median \mden{} profile of massive ETGs in a similar 
+    redshift range with this work ($0.25 < z < 0.50$) using the stacked \textit{HST}/ACS
+    images. 
+    These galaxies are selected at a constant cumulative number density that makes them  
+    good candidates of progenitors of $z=0$ massive ETGs.  
+    The median \mstar{} is $\sim 10^{11.2} M_{\odot}$ according to their estimates.  
+    However, given the shallower depth of the ACS images and the usage of the BC03 model 
+    (each could cause -0.1 dex mass offset compared to this work), this sample should be 
+    comparable to the galaxies in the lowest \mtot{} bin, and the comparison of their 
+    median profiles does reflect that.  
+    Moreover, the superb resolution of the \textit{HST}/ACS image makes the \mden{} 
+    profile unaffected by PSF even within inner 1 kpc, hence the comparison illustrates 
+    that the HSC profiles within our redshift range are indeed not bothered by 
+    seeing outside the shaded region, and \minn{} should be very reliable.
+    In fact, even \mstar{} within 5 kpc should be available for comparison.
+
+    Besides these observations, we also compare with the predicted average \mden{} 
+    profile of central galaxies in very massive halos 
+    ($13.5 < \log M_{200,c} < 14.0$) from cosmological simulation (\citealt{Cooper13}). 
+    This is achieved by combining the detailed assembly information of halos from the 
+    dark-matter-only simulation with semi-analytic model and particle-tagging technique 
+    (\citealt{Cooper10}).
+    Although the physical resolution and detailed baryonic processes are not as 
+    ``realistic'' as state-of-art hydro-simulation, it is very efficient in providing 
+    rough stellar mass distributions in a large sample of massive halos. 
+    Without any adjustment, the profile is already quite similar to the median \mden{}
+    profile of galaxies in the $11.6 <$\logmtot{}$< 11.8$ bin within 30-40 kpc. 
+    But the simulation seems to predict too significant envelope at larger radius for 
+    this average halo mass. 
+    Although we will not dig into the detailed causes of such differences, it already 
+    highlights that the comparison between deep \mden{} profiles from observations 
+    and the predicted ones in simulations can be very interesting, especially in the 
+    outskirt that was rarely discussed using previous data.
 
@@
 
-\subsubsection{Matched Samples Using \mtot{} \alexie{This it not the right title for this section!!
-The point here is not to make matched samples.
-The point here is to look at the enviromental signature.}}
+\subsubsection{Environmental dependence of \mden{} profiles at fixed \mtot{}}
     \label{sssec:sbp_mtot}
 
-\alexie{Most of the text below describing the procedure for making the mathced samples can go into an appendix.
-It distracts from your main results!
-And people have been making mathced samples for years!!
-Most of the text in between the red text can be moved else where or simplified.}
-
-  \textcolor{red}{FROM HERE}
-
-  As stellar mass is considered the most important parameter in determining the 
-    structure and other properties of massive galaxies, it is crucial to make sure 
-    the comparison is conducted at ``fixed stellar mass''. 
-    And, since we directly compare the stellar mass distributions across very large 
-    range in radius, it is also important to make sure that differences in physical 
-    size of PSF (for more discussion on this issue, please see Appendix\ref{app:C}) 
-    and imaging depth do not affect the result.    
-    In practice, we achieve these by matching the \rbcg{} and \nbcg{} samples in 
-    the distributions of \mstar{} and redshift in the mass range where both 
-    samples have decent completeness.  
-    Since the \rbcg{} sample is much smaller in size, we match the \nbcg{} sample to it 
-    by searching for the $N$ nearest neighbours on the $M_{\star}$-redshift 
-    plane using the KDTree algorithm provided by \texttt{scikit-learn} Python 
-    library (\citealt{scikit-learn}). 
-    The quality of the matched sample is evaluated by not just the median values 
-    of stellar mass and redshift, but also the kernel density distributions (KDE) 
-    of these two properties.
-    For \mstar{}, we use a Gaussian kernel with width equals to the typical 
-    uncertainty of the mass estimate (0.06-0.10);
-    and for redshift, we choose 0.025 as the width of the Gaussian kernel. 
-    As we only keep unique \nbcg{} galaxies in the matched sample, we manually adjust 
-    the value of $N$ to achieve the most similar distribution. 
-    In case that the distribution of stellar mass or redshift for \rbcg{} is 
-    bi-model, we also try to split the sample into two, and match them separately.
-    Normally $N$ is between 3 to 8.
-
-    \mstar{} within different radius traces different physical processes and 
-    different epochs in the assembly history.  
-    In this section, we match the two samples using our proxy of ``total'' stellar 
-    mass, which is the \mstar{} within 100 kpc radius.  
-    This choice reflects the stellar mass distributions we can safely measure using 
-    model-independent approach given the current depth of the image and the accuracy 
-    of sky background subtraction.
-    For galaxies at $11.6 \leq \log(M_{\star}/M_{\odot}) < 11.9$, 100 kpc equals to 
-    5-8 times of their effective radius, hence should enclose most their stellar mass.
-    Also, for a fraction of massive \rbcg{} galaxies, the intra-group/cluster light
-    (IGL/ICL) could dominate their mass profiles outside 100 kpc (\addref), and 
-    complicate the comparison with the \nbcg{} galaxies.  
-    We will discuss these issues later in Section \ref{sec:discussion}, but in 
-    conclusion, the proxy of total \mstar{} and the potential ICL component should 
-    not affect the results.
-
-    \textcolor{red}{TO HERE}
-
-    \alexie{This is more how you should start your paragraph! It can be as simple as "We match the sample (see appendix) and show the results in Figure xx.}
-    \song{Got it! will update later}
+    \song{Still need a little bit text here}
+
     We show the results of the comparison in Fig.\ref{fig:prof_m100_A}. 
@@
     halos in term of the stellar mass distributions.
-
-%% ------------------------------------------------------------------------------------ %% 
-  \begin{figure*}[t!]
-      \centering 
-      \includegraphics[width=16.0cm]{fig/redbcg_m100_m10_compare}
-      \caption{Three-color images for a subsample of massive galaxies at similar redshift
-      		($\sim 0.4$), and with similar \mstar{} inside inner 10 kpc (indicated by the 
-            dash-line cicle on top-left figure; 
-            $11.2<\log (M_{\star,10\ \mathrm{kpc}}/M_{\odot})<11.3$). 
-            However, they span quite a large range in \mstar{} within 100 kpc 
-            (highlighted by the solid bar on the top-left figure). 
-            From top-left to bottom-right, their \mtot{} increases from 
-            $10^{11.2} M_{\odot}$ to $10^{11.7} M_{\odot}$.
-            The three galaxies from \rbcg{} sample are highlighted via red frames.}
-      \label{fig:m100_m10_color}
-  \end{figure*}
-%% ------------------------------------------------------------------------------------ %%
 
@@
 
-%% ------------------------------------------------------------------------------------ %% 
-  \begin{figure}[bt!]
-      \centering 
-      \includegraphics[width=\columnwidth]{fig/redbcg_prof_m10B}
-      \caption{Comparisons of unnormalized \mden{} profiles of 
-      	  $\log (M_{\star,100\ \mathrm{kpc}}/M_{\odot}>11.5$ \rbcg{} (orange-red) 
-      	  and \nbcg{} (grey-black) samples that are matched using \minn{}.
-          Except for the difference in \mtot{}-limit of both samples, other formats are 
-          the same with the middle figure of Fig.\ref{fig:prof_m10_A}.
-          \song{The reason I did this test is because the \minn{} matched \nbcg{} 
-          sample without any constraint will have a lot of galaxies with 
-          \mtot{}$<10^{11.5} M_{\odot}$ in the sample; They are in the 
-          \mtot{}-incomplete range, and it is harder to argue that they have similar 
-          mass in the `in-situ' component with the \rbcg{} ones. 
-          If you think this is weird, another choice is to do the match at \minn{} in 
-          between [11.4, 11.6], so that most galaxies have 
-          \mtot{}$>10^{11.5} M_{\odot}$.}}
-      \label{fig:prof_m10_B}
-  \end{figure}
-%% ------------------------------------------------------------------------------------ %%
-
 \subsubsection{Matched Samples Using \minn{}}
@@
     We also increase the \mstar{} in HC13 by $+0.1$dex to account for the systematic 
-    difference between their BC03 and our FSPS model (see Appendix \ref{app:B}). 
+    difference between their BC03 and our FSPS model (see Appendix.\ref{app:B}). 
     In HC13, the authors found no difference among the mass-size distributions for 
@@
 
-	\song{I agree that this can be part of the results; but the profiles here are not as 
-    reliable as the \mden{} profiles for technical reason; I put it here as a teaser, as 
-    it is better to deal with them using 2-D fitting.}
+    \song{Will make a short sub-section in the results for these}
 \alexie{This paragraph shoud go in the results section.
@@
 
+    \alexie{Yes, the only thing that I just realized and pointed out in the ealier SMF figure is that to compare the SMF, we need to include everything, not just centrals.
+There are two options: 1) just show the impact on the SMF for centrals (the figure you have already) or 2) include all the galaxies and compared with previous work.
+I think that 2) is a paper inself and is beyond the scope of the papers (it becomes "Mission Creep").}
+
     \alexie{I thought of another interesting aspect to add to the discussion.
@@
 
+    \alexie{THe same idea holds if we use our M100 mass and cmodel.
+The points is just to evaluate how much extra scatter you introduce because of many people simple use naive luninosities when they do abundance mathcing.
+Your previous figures show that the luminosities of massive galaxies may be severaly underestiamted.
+How much impact does this have on abundance mathcing?
+How much extra scatter does it introduce?}
+
     \alexie{Finally, another quick discussion paragraph could be related to finding BCGs.
@@
     the draft.  Although I do compare the structures of really massive satellites in 
-    these clusters with the \nbcg{} galaxies, and the results show little difference,
-    basically shows that the structure difference could be unique for central galaxies. 
+    these clusters with the \nbcg{} galaxies, and the results show little difference,    basically shows that the structure difference could be unique for central galaxies. 
     I originally show a figure for this, and will send you along the e-mail.}
+
+    \alexie{If it is too much, work, skip this idea! We dont want mission creep.}
 
@@
     very hard to achieve through observation, basically the stars that follows the 
-    potential of the clsuter.}
+    potential of the clsuter.} \alexie{Exactly. Which is why I think we dont want to go into a big discussion on this.}
     And, if the answer is no, which is the best way to separate the ICL component? 
@@
     they change our results.}
+
+    \alexie{I'm saying more than that. I'm saying that I don't beleive that there is necessarly a firm distinction between the galaxy and the "ICL". Might be easier to chat about this on Skype.}
 
@@
   \href{http://dan.iel.fm/emcee/current/}{\texttt{emcee}}, 
-      Seriously Kick-Ass MCMC in Python.
+      Seriously Kick-Ass MCMC in Python;
+  \href{http://bdiemer.bitbucket.org/}{\texttt{Colossus}}, 
+      COsmology, haLO and large-Scale StrUcture toolS (\citealt{Colossus}).
 
@@
 
-\section{A. Extraction of 1-D surface brightness profile} 
+\section{A. Basic Statistical Properties of the Sample} 
+	\label{app:basic}
+    \song{New appendix! Figure and caption also updated.}
+
+    In the top-left figure of Fig.\ref{fig:sample_stats}, we show the \mtot{}-color 
+    relations using the $k$-corrected $g-r$ color for the \rbcg{} and \nbcg{} 
+    samples. 
+    Both samples follow the same tight ``red-sequence'' with very little contamination 
+    from star-forming galaxy in the ``blue cloud''.
+    And, at fixed \mtot{}, we see little offset in color distributions of the two 
+    samples suggesting that both samples consist of old quiescent galaxies with 
+    similar average stellar population properties.  
+    This is consistent with previous result that suggests the average stellar 
+    population of massive central galaxy does not depend on \mhalo{} 
+    (e.g.\ \citealt{Park2007}).  
+    To look into the potential environmental dependence of structure, we will 
+    focus on the mass range of $11.6 \le$\logmtot{}$\le 11.9$, where both samples 
+    have acceptable completeness, and their \mtot{} distributions greatly overlap
+    (see the normalized distributions of \mtot{} in the bottom-left panel of 
+    Fig.\ref{fig:sample_stats}). 
+    The similar situation applies to the \minn{} distributions as well, where 
+    the two samples overlap the most within $11.2 \le$\logmtot{}$\le 11.6$, but 
+    have quite different relative distributions.
+
+    Due to the different sources of redshift for the \rbcg{} and \nbcg{} samples, 
+    the two samples have somewhat different redshift distributions 
+    (right figure of Fig.\ref{fig:sample_stats}), even within the 
+    $11.6 \le$\logmtot{}$\le 11.9$ mass bin.  
+    Apparently, the redshift distribution of the \nbcg{} sample skews toward 
+    higher-$z$ end, primarily due to the contribution of BOSS spec-$z$.
+    This could bias the comparison of \mden{} profiles and other properties 
+    (please see Appendix\ref{app:D} for more details).  
+    We will address this via matching the two samples in both mass and redshift
+    distributions carefully before any comparison (see Appendix~\ref{app:match}).
+
+%% ------------------------------------------------------------------------------------ %% 
+  \begin{figure*}[t!]
+      \centering 
+      \includegraphics[width=16.5cm]{fig/redbcg_sample_stats}
+      \caption{\textbf{Top-left}: The \logms{}-$g-r$ color relation of the \rbcg{} 
+          (red circle; detaield format is the same with the right panel of 
+          Fig.\ref{fig:smf1}) and \nbcg{} (grey dots) samples.
+          We apply the $k$-corrections from \texttt{iSEDFit} fitting to the colors.~~          
+          \textbf{Top-right}: the histograms of the redshift for the \rbcg{} and 
+          \nbcg{} galaxies in both \logmtot$>11.2$ and $11.6<$\logmtot{}$<11.9$
+          mass bins.
+          The vertical lines highlights the $0.3\leq z \leq 0.5$ redshift range.~~
+          \textbf{Bottom-left}: the histograms of \mtot{} for the \rbcg{} (orange-red) 
+          and \nbcg{} (grey-black) samples at both $z>0.2$ (step-filled histogram) and 
+          $0.3 \leq z \leq 0.5$ (stepped histogram). 
+          The vertical lines in both top-left and bottom-left figures highlight the 
+          $11.6<$\logmtot{}$<11.9$ mass range that will be used in the comparison of 
+          the \mtot{}-matched samples.~~
+          \textbf{Bottom-right}: the histograms of \minn{} in similar format. 
+          Here the vertical lines highlight the 
+          $11.2<$\logminn{}$<11.6$ mass range that is used for comparison.
+      }
+      \label{fig:sample_stats}
+  \end{figure*}
+%% ------------------------------------------------------------------------------------ %%
+
+\section{B. Extraction of 1-D surface brightness profile} 
     \label{app:A}
@@
 
-\section{B. Estimate average {$M_{\star}/L_{\star}$} using \texttt{iSEDFit}} 
+\section{C. Estimate average {$M_{\star}/L_{\star}$} using \texttt{iSEDFit}} 
     \label{app:B}
@@
 
-\section{C. Comparison of \mden{} profiles using \mstar{} from the GAMA survey}
+\section{D. Comparison of \mden{} profiles using \mstar{} from the GAMA survey}
     \label{app:C}
@@
 
-\section{D. Comparisons of \mden{} profiles in different redshift bins}
+\section{E. Comparisons of \mden{} profiles in different redshift bins}
     \label{app:D}
@@
 
+\section{F. Match the \rbcg{} and \nbcg{} samples in \mstar{} and redshift distributions}
+    \label{app:match}
+
+%    \textbf{Left figure} shows the details of the \mtot{}-matching process.  
+%      On the top panel, we show the overall distributions of \rbcg{} (light orange boxes) 
+%      and \nbcg{} (light grey dots) galaxies on the \mtot{}-$z$ plane.  
+%      And, we match the two sample in the \mtot{}-$z$ space outlined by the shaded region.
+%      We highlight the \rbcg{} galaxies in this region using bigger boxes in red frames, 
+%      whose size reflects the $P_{\mathrm{Cen}}$ value.  
+%      We also color-code them using the richness ($\lambda$) of the host cluster. 
+%      The matched \nbcg{} galaxies are highlighted using darker color and bigger dots. 
+%      To further evaluate the matching results, we show the distributions of \mtot{} 
+%      (middle panel) and redshift (bottom panel) separately. 
+%      On both panesl, we show the histograms along with their kernel density 
+%      distributions.  
+%      And, on the top of each panel, two sets of short vertical lines highlight the median 
+%      value (solid) and the inter-quartile (dash) of each distribution.~~~
+
+    \song{Still need a figure and some adjustments}
+
+    As stellar mass is considered the most important parameter in determining the 
+    structure and other properties of massive galaxies, it is crucial to make sure 
+    the comparison is conducted at ``fixed stellar mass''. 
+    And, since we directly compare the stellar mass distributions across very large 
+    range in radius, it is also important to make sure that differences in physical 
+    size of PSF (for more discussion on this issue, please see Appendix\ref{app:C}) 
+    and imaging depth do not affect the result.    
+    In practice, we achieve these by matching the \rbcg{} and \nbcg{} samples in 
+    the distributions of \mstar{} and redshift in the mass range where both 
+    samples have decent completeness.  
+    Since the \rbcg{} sample is much smaller in size, we match the \nbcg{} sample to it 
+    by searching for the $N$ nearest neighbours on the $M_{\star}$-redshift 
+    plane using the KDTree algorithm provided by \texttt{scikit-learn} Python 
+    library (\citealt{scikit-learn}). 
+    The quality of the matched sample is evaluated by not just the median values 
+    of stellar mass and redshift, but also the kernel density distributions (KDE) 
+    of these two properties.
+    For \mstar{}, we use a Gaussian kernel with width equals to the typical 
+    uncertainty of the mass estimate (0.06-0.10);
+    and for redshift, we choose 0.025 as the width of the Gaussian kernel. 
+    As we only keep unique \nbcg{} galaxies in the matched sample, we manually adjust 
+    the value of $N$ to achieve the most similar distribution. 
+    In case that the distribution of stellar mass or redshift for \rbcg{} is 
+    bi-model, we also try to split the sample into two, and match them separately.
+    Normally $N$ is between 3 to 8.
+
+    \mstar{} within different radius traces different physical processes and 
+    different epochs in the assembly history.  
+    In this section, we match the two samples using our proxy of ``total'' stellar 
+    mass, which is the \mstar{} within 100 kpc radius.  
+    This choice reflects the stellar mass distributions we can safely measure using 
+    model-independent approach given the current depth of the image and the accuracy 
+    of sky background subtraction.
+    For galaxies at $11.6 \leq \log(M_{\star}/M_{\odot}) < 11.9$, 100 kpc equals to 
+    5-8 times of their effective radius, hence should enclose most their stellar mass.
+    Also, for a fraction of massive \rbcg{} galaxies, the intra-group/cluster light
+    (IGL/ICL) could dominate their mass profiles outside 100 kpc (\addref), and 
+    complicate the comparison with the \nbcg{} galaxies.  
+    We will discuss these issues later in Section \ref{sec:discussion}, but in 
+    conclusion, the proxy of total \mstar{} and the potential ICL component should 
+    not affect the results.
+
+\section{G. Robustness of the \mden{} Differences} 
+	\label{app:robust}
+
+    \song{Need some text!}
+
+%% ------------------------------------------------------------------------------------ %% 
+  \begin{figure*}[t!]
+      \centering 
+      \includegraphics[width=\textwidth]{fig/redbcg_prof_3}
+      \caption{Comparisons of the \mden{} profiles for \rbcg{} (orange-red) and \nbcg{} 
+      	(grey-black) galaxies that are matched using proxies of total \mstar{}. 
+        The formats are in consistent with the right figure of Fig.\ref{fig:prof_m100_A}.
+        The differences are, here, the samples are matched in slightly differnt ways. 
+        From left to right: a) using samples at lower redshift ($0.3 < z < 0.4$); 
+        b) using \rbcg{} sample with $\lambda > 20$ instead of 30; 
+        c) using \mstar{} within 150 kpc instead of 100 kpc.
+        The results are broadly consistent with the one in Fig.\ref{fig:prof_m100_A}.}
+      \label{fig:prof_m100_B}
+  \end{figure*}
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
+  \begin{figure*}[t]
+      \centering 
+      \includegraphics[width=\textwidth]{fig/redbcg_prof_4}
+      \caption{Comparisons of unnormalized \mden{} profiles of 
+      	  $\log (M_{\star,100\ \mathrm{kpc}}/M_{\odot}>11.5$ \rbcg{} (orange-red) 
+      	  and \nbcg{} (grey-black) samples that are matched using \minn{}.
+          Except for the difference in \mtot{}-limit of both samples, other formats are 
+          the same with the middle figure of Fig.\ref{fig:prof_m10_A}.
+          \song{Update the figure, but need to work on text and caption.}
+          }
+      \label{fig:prof_m10_B}
+  \end{figure*}
 %% ------------------------------------------------------------------------------------ %%
@@
 
+\song{To be updated}
+
 %% ------------------------------------------------------------------------------------ %%

### 2016-12-06 draft/ms_v1.tex
Update 12/06

@@
 \def\minn{{$M_{\star,10\mathrm{kpc}}$}}
+\def\meff{{$M_{\star,15\mathrm{kpc}}$}} 
 \def\mtot{{$M_{\star,100\mathrm{kpc}}$}}
 \def\mout{{$M_{\star,150\mathrm{kpc}}$}}
+\def\mmax{{$M_{\star,\mathrm{Max}}$}}
 \def\mgama{{$M_{\star,\mathrm{GAMA}}$}}
@@
 \def\logmout{{$\log (M_{\star,150\mathrm{kpc}}/M_{\odot})$}}
+\def\logmmax{{$\log (M_{\star,\mathrm{Max}}/M_{\odot})$}}
 \def\logmgama{{$\log (M_{\star,mathrm{GAMA}}/M_{\odot})$}}
@@
             phase.  Although it is an empirical choice, the detailed comparison of 
-            \mden{} profiles later suggests it indeed helps reveal interesting 
-            environmental dependence.  
+            the stellar mass surface density (\mden{}) profiles later suggests it indeed 
+            helps reveal interesting environmental dependence.  
             Under the adopted cosmology, $1.0^{\arcsec}$ in radius equals 4.4 and 6.1 kpc 
@@
       \caption{
-      	Left: Median \mden{} profiles of galaxies in different \mtot{} bins:
+      	\textbf{Left}: Median \mden{} profiles of galaxies in different \mtot{} bins:
       	[11.4, 11.6] (short-dashed line), [11.6, 11.8] (solid line), and 
@@
         100 kpc (thick, dash line). ~~~ 
-        Right: comparison between the average \mden{} profiles with the ones from 
-        previous observations and simulations, including: 
+        \textbf{Right}: comparison between the average \mden{} profiles with the ones 
+        from previous observations and simulations, including: 
         1) average profile of massive elliptical galaxies at $z\sim 0$ from 
@@
       \includegraphics[width=\textwidth]{fig/redbcg_prof_1}
+      \caption{
           \update{
@@
           and \minn{}-matched ($11.2<$\logminn{}$<11.6$) samples 
-      of \rbcg{} (orange to red) and \nbcg{} (grey to black) galaxies.
+          of \rbcg{} (orange to red) and \nbcg{} (grey to black) galaxies.~~
           \textbf{Left} shows the results for the \mtot{}-matched samples.
@@
           dash-line now highlights the 10 kpc radius.}
-      \label{fig:prof_m100_A}
+      }
+      \label{fig:prof_1} 
   \end{figure*}
@@
 
-    \song{Due to the change of figure, this section has been updated slightly}
-
     As discussed earlier, although the mass-size scaling relation has been intensively 
@@
     uncertainty using bootstrap resampling method (5000 times). 
-    In the left panel of Fig.\ref{fig:avg_prof}, we can see that the higher \mtot{} 
-    shifts the median \mden{} profile up a little bit in the inner region, but makes 
-    the outskirt significantly more prominent. 
+    As one can see in the left panel of Fig.\ref{fig:avg_prof}, we can comfortably trace 
+    the \mstar{} distribution of these massive galaxies out to 100 kpc 
+    \textbf{individually}, which gives us huge advantage in studying the statistical 
+    properties of their outer envelopes. 
+    We can see that the higher \mtot{} shifts the median \mden{} profile up a little bit 
+    in the inner region, but makes the outskirt significantly more prominent. 
     Most of these very massive galaxies ($\ge 10^{11.4} M_{\odot}$) should be 
@@
       \includegraphics[width=\textwidth]{fig/redbcg_prof_2}
-      \caption{Comparisons of the \mden{} profiles for \rbcg{} (orange-red) and \nbcg{} 
-      	(grey-black) galaxies in lower (left; [11.5,11.70]) and higher 
-        (right; [11.7, 11.9]) \mtot{} bins. 
-        Other formats are in consistent with the right figure of 
-        Fig.\ref{fig:prof_m100_A}.
-        The difference in median profiles is more significant in higher \mtot{} bin.
-        \song{Figure has been updated, but need to update the caption.}
-        }
-      \label{fig:prof_m100_C}
+      \caption{Comparisons of the \mden{} profiles for \mtot{}-matched \rbcg{} 
+          (orange-red) and \nbcg{} (grey-black) galaxies in lower (left; [11.5,11.70]) 
+          and higher (right; [11.7, 11.9]) \mtot{} bins. 
+          Other formats are in consistent with the right figure of Fig.\ref{fig:prof_1}.
+          The difference in median profiles is more significant in higher \mtot{} bin.}
+      \label{fig:prof_2}
   \end{figure*}
@@
 %% ------------------------------------------------------------------------------------ %%
-  \begin{figure*}[t!]
-      \centering 
-      \includegraphics[width=\textwidth]{fig/redbcg_prof_m10C}
-      \caption{\alexie{There is a lot of redundancy in the Figures.
-I'm going to suggest to bring all the main figures together in a 4 panel figure?}.
-Comparisons of \mden{} profiles of \rbcg{} (orange-red) and \nbcg{}
-          (grey-black) samples that are matched using \minn{} instead of \mtot{}. 
-          We perform the match at $11.2<\log (M_{\star,10\ \mathrm{kpc}}/M_{\odot})<11.6$.
-          \textbf{Left figure} shows the matching results in the same format with 
-          the left figure of Fig.\ref{fig:prof_m100_A}.  
-          The only difference is \mtot{} is replaced by \minn{}. ~~~
-          \textbf{Middle figure} summarizes the profile comparisons in the same format 
-          with the right figure of Fig.\ref{fig:prof_m100_A}.~~~
-          \textbf{Right figure} is very similar to the middle one, except we show the 
-          profiles that are normalized using the \minn{} value to highlight the 
-          scatters of \mden{} at different radius. 
-          \alexie{the tow figures actually look pretty similar.
-I think most people will not notice the difference.
-Pick one and go with that.
-I guess I have a preference for the unnormalized one.
-Your mathced sampeles take care of the reason we made the normalized versions.
-(mean mass was different between samples.)}
-          \song{Ok, will only use the unnormalized ones later; The point of normalized one is to 
-          reduce the effect of the \mstar{} width of the mass bin; it is useful when I 
-          discuss the dispersion of \mden{} at outer radius; I could simply emphasis that 
-          in the text, or put some figures in the Appendix....how many appendix is too
-          many}}
-      \label{fig:prof_m10_A}
-  \end{figure*}
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %%
 
@@
 
-    \song{Still need a little bit text here}
-
-    We show the results of the comparison in Fig.\ref{fig:prof_m100_A}. 
-    The left panel highlights the properties of the matched \rbcg{} and \nbcg{} 
-    samples.
-    Given the typical uncertainty of stellar mass, the two samples are well 
-    matched in \mtot{}; and their redshift distributions are broadly 
-    consistent with each other.  
+    \update{
+    We show the results of the comparison in Fig.\ref{fig:prof_1} after 
+    carefully matching the \rbcg{} sample with smaller size to the \nbcg{} samples 
+    within $0.3 < z < 0.5$ and $11.6 < $\logmtot{}$<11.9$ vial searching for the $N$ 
+    nearest neighbours on the $M_{\star}$-redshift plane using the KDTree algorithm. 
+    The details of the procedure and the evaluation of the matching quality can be 
+    found in Appendix.\ref{app:match}. 
+    In summary, given the typical uncertainty of stellar mass, the two samples are well 
+    matched in \mtot{}; and their redshift distributions are broadly consistent with 
+    each other, hence we can perform meaning comparison of their average structures at 
+    ``fixed stellar mass'' (median \logmtot{}$\sim 11.74$).    
     We also check their distributions of $k$-corrected colors ($g-r$), and confirm 
-    that they have very similar average color distributions as well.  
+    that they have similar color distributions as well.}
+
     For the 45 \rbcg{} galaxies, we have 229 unique \nbcg{} galaxies in the 
     matched sample.
-    On the right side, we plot the individual stellar mass density (\mden{}) profile 
+    \update{
+    On the left side of Fig.\ref{fig:prof_1}, we plot the individual \mden{} profile 
     of \rbcg{} and \nbcg{} galaxies along with the median profiles of both samples.
@@
     bootstrap resampling.
-    As one can see, we can comfortably trace the \mstar{} distribution of these massive 
-    galaxies out to 100 kpc at individual level, which gives us huge advantage in 
-    studying the statistical properties of their outer envelopes. 
-    Mass profile out to such large radius was only available for large sample of 
-    massive galaxies through image stacking method (\addref) which suffers from certain
-    systematic issues. 
+    The \mden{} profile out to such large radius was only available for large sample of 
+    massive galaxies through image stacking method (e.g. \citep{Tal2011, DSouza2015}) 
+    which suffers from certain systematic issues.}
     Although the \mden{} profiles of many galaxies extend well beyond the 100 kpc radius, 
@@
     other over the entire radius range}. 
-    At fixed ``total'' stellar mass, massive central galaxies of more massive 
+    At fixed ``total'' stellar mass, massive central galaxies in more massive 
     halos do not form a unique population comparing to the ones from less massive 
-    halos in term of the stellar mass distributions.
-
-    At the same time, thanks to the high quality individual profile from HSC image, 
-    we can also spot interesting differences in the median profiles of the \mtot{} 
-    matched \rbcg{} and \nbcg{} samples.  
-    In details, it seems that central galaxy in more massive halos tends to have 
-    a slightly flattened inner density profile and possess more significant outer 
-    envelope.   
+    halos in term of their radial \mstar{} distributions. 
+    \update{
+    This partially explains why the previous works have trouble finding any clear 
+    environmental dependence of structure.}
+
+    At the same time, thanks to the high-quality individual profile from HSC image, 
+    we can also spot interesting differences in the median profiles of the 
+    \mtot{}-matched \rbcg{} and \nbcg{} samples.  
+    In details, it seems that the central galaxies in more massive halos tend to 
+    have slightly flattened inner \mden{} profiles while also possess more significant 
+    outer stellar envelope.   
     To highlight such subtle structural features, we show the difference between 
     the two median profiles and its uncertainty in the bottom panel. 
-    Given the noticeable uncertainties of \mtot{} and $\lambda$, and the current small 
-    sample sizes, we also perform statistical test to confirm the robustness of the
-    result: we mix the $N_{\mathrm{r}}$ \rbcg{} galaxies and the $N_{\mathrm{n}}$ \nbcg{}
-    ones together, then randomly draw $N_{\mathrm{r}}$ galaxies with putting-back, 
-    compute the difference between the median profile of this sample and the \nbcg{} 
-    sample, and repeat this process 2000 times.  
+    Given the noticeable uncertainties of \mtot{} and $\lambda$, along with the 
+    small size of the current \rbcg{} sample, we perform statistical test to confirm 
+    the robustness of the result: we mix the $N_{\mathrm{r}}$ \rbcg{} galaxies and 
+    the $N_{\mathrm{n}}$ \mtot{}-matched \nbcg{} ones together, then randomly draw 
+    $N_{\mathrm{r}}$ galaxies with putting-back, compute the difference between the 
+    median profile of this sample and the \nbcg{} sample. 
+    \update{
+    After repeating this process 2000 times, we can evaluate the possibility that 
+    the systematic differences in median \mden{} profiles can be reproduced by random 
+    selection of massive galaxies.
     Comparing with the statistical distributions of the differential profiles from 
     this test (grey shaded region), we can now conclude that the structural 
-    differences between \rbcg{} and \nbcg{} samples are much more significant than 
-    any statistical fluctuation given the current samples.  
-    And, apparently, the ``transition radius'' where the median profiles of \rbcg{} 
+    differences between \rbcg{} and \nbcg{} samples are significant.}
+    Apparently, the ``transition radius'' where the median profiles of \rbcg{} 
     and \nbcg{} sample have the same \mden{} is $\sim 15$-20 kpc, which is quite 
-    close to the expected $R_{\mathrm{e}}$ of ETGs at this stellar mass.
-
-    To further test the robustness of this interesting result, we repeat above 
-    procedures to samples with slightly different definition.  
-    The results are shown in Fig.\ref{fig:prof_m100_B}: 
-    (a). At higher redshift, the profile is more affected by the seeing at inner 
+    close to the expected $R_{\mathrm{e}}$ of ETGs at this \mtot{} (please see 
+    next section for details).
+
+    To further test the robustness of this interesting result, we apply the above 
+    procedures to \mtot{}-matched samples with slightly different definitions.  
+    The results are shown in Fig.\ref{fig:prof_3} in Appendix.\ref{app:robust}: 
+    (a). At higher redshift, the profile is affected more by the seeing at inner 
     region, and by the imaging depth in the outskirt.  
-    Therefore, in the left panel, we compare the \rbcg{} and \nbcg{} samples at 
+    Therefore, we compare the matched \rbcg{} and \nbcg{} samples within 
     $0.3 \leq z < 0.4$, and the results are very similar.
@@
     Given the differences we find, at fixed \mtot{}, \rbcg{} galaxy tends to have 
-    more prominent outer envelope outside 100 kpc than the \nbcg{} one. 
+    slightly more prominent outer envelope outside 100 kpc than the \nbcg{} one. 
     Hence their real ``total'' stellar mass could also be slightly larger, and 
-    result in bias in the comparison.  
-    In the right panel, we make the comparison using the maximum stellar mass from 
+    bias the comparison.  
+    Therefore, we make a similar comparison using the maximum \mstar{} from 
     the integration of the \mden{} profile instead of the \mtot{}.
+    \update{
     In this case, the differences between the median profiles become slightly 
-    less significant as expected.  
+    less significant as expected (a fraction of \rbcg{} galaxies become more 
+    massive, and is not included in the \logmtot{}$< 11.9$ mass bin). 
     But the systematic trends, especially the differences in the low mass density 
-    outskirt are still very stable.  
-    All these tests confirm that we robustly detect subtle, but systematic 
-    structural dependence on halo mass of massive galaxies.   
-    The fact that it requires such careful comparison to reliably reveal any 
-    potential halo mass dependence already suggests that the role environment
-    played in shaping these massive galaxies is not crucially important.  
+    outskirt are still very robust. 
+    We will further discuss this in Section \ref{sec:discussion}. 
+    Considering the uncertainty of \mden{} profiles outside 100 kpc, the 
+    feasibility of applying the average \m2l{} to stars in the extreme outskirt, 
+    and the contribution of the diffuse stellar components that trace the halo, 
+    we think that our results are stable.}
+
+    \textbf{All these tests confirm that we robustly detect subtle, but systematic 
+    \mhalo{}-dependence (environmental dependence) of structure in massive, 
+    central galaxies.}
+    \update{
+    Interestingly, the fact the it takes much better data and really cautious 
+    comparison to detect such systematic difference seems to suggest that the role 
+    played by environment in shaping the structure of central galaxies may not be 
+    that crucial in the \mhalo{} and \mstar{} ranges we discussed.}
+
     At the same time, the systematic differences we find, especially the more 
@@
     in denser environment. 
-    We will discuss these more in Section \ref{sec:discussion}.
+    \update{
+    Predicted by the ``two-phase'' scenario, the non-dissipative mergers, especially 
+    the minor ones, should mainly deposit stellar mass in the outskirts, help 
+    build the stellar halo while do not change the inner \mden{} profiles very 
+    much (e.g. \citealt{Hilz2013}, \citealt{Oogi2013}).}
 
@@
     Limited by the small sample we have, we can only afford to separate the 
-    samples into two \mtot{} bins 
+    samples into two \mtot{} bins, and extend to slightly lower \mtot{} bound 
     ($11.5 \leq \log (M_{\star,\ 10\mathrm{kpc}}/M_{\odot}) < 11.7$ and 
@@
     After performing the same procedures of sample matching and comparison, 
-    we show the results in Fig.\ref{fig:prof_m100_C}.  
+    we show the results in Fig.\ref{fig:prof_2}.   
     Although the smaller sample leads to larger statistical uncertainties, 
@@
     For the lower \mtot{} bin, the difference in the inner region becomes quite 
-    uncertain, while there is still evidence that suggest difference in the 
-    outskirt.  
-    This result also has interesting implications in studying the assembly 
-    of massive galaxies, and is worth further investigation with larger sample
-    in the future.
-
-%% ------------------------------------------------------------------------------------ %%
-
-\subsubsection{Matched Samples Using \minn{}}
+    uncertain, while there is still evidence of difference in the outskirt.  
+    This result also has interesting implications in the assembly history
+    of massive galaxies, and is worth more investigations with larger samples
+    in the near future.
+
+%% ------------------------------------------------------------------------------------ %%
+
+\subsubsection{Environmental dependence of \mden{} profiles at fixed \minn{}}
     \label{sssec:sbp_minn}
 
-    \song{Got it! will update later}
-    \alexie{This paragraph goes in the discussions section.
-The results section should be "We now do this to the data and here is the Figure"} As suggested by the popular two-phase formation scenario of massive galaxies,
-    the inner 5-10 kpc of these galaxies (within 0.5-1$xR_{\mathrm{e}}$) is 
-    dominated by stars formed in intensive dissipative processes at high redshift, 
-    and is less affected by the succeeding merging events.  
-    This picture is broadly supported by the redshift evolution of \mden{} profile
-    of massive galaxies (\addref), structure decomposition of nearby massive galaxies 
-    (\addref), and their radial distributions of stellar population (\addref).      
-    Certainly, major merger can induce violent relaxation process that modifies the 
-    stellar mass distribution even in the central region, and must happen to 
-    these massive galaxies in last 6-8 Gyrs, it may not invalidate the above assumption.
-    For galaxy this massive, the last major merger event is highly likely to be
-    non-dissipative, and the redistribution of stars is basically according to their 
-    binding energy in the host halo.  
-    The inner region of the final merger remnant is still mostly composed 
-    of the ``in-situ'' stars from the two progenitors.
-
-    Therefore, it is interesting to compare the \rbcg{} and \nbcg{} samples that are 
-    matched using mass within the inner region.  
-    In this work, we choose to use the mass within inner 10 kpc (\minn{}). 
-    As we can see in previous profile comparison, \minn{} is not affected by the 
-    physical size of PSF out to $z=0.5$.  
-    We use the same procedure to match the \nbcg{} galaxies to the \rbcg{} ones using 
-    \minn{} (within $11.2 \leq \log (M_{\star,\ 10\mathrm{kpc}}/M_{\odot}) < 11.6$) 
-    and redshift ($0.3 \leq z < 0.5$).  
+    \update{Here, we compare the median \mden{} profiles of \rbcg{} and \nbcg{} galaxies
+    after matching the two samples using \minn{} ($11.2 <$\logminn{}$ < 11.6$) and 
+    redshift ($0.3 < z < 0.5$).
+    We use the same matching procedure as in the previous section, and also put its 
+    evaluation in Appendix.\ref{app:match}.
+    As mentioned in the beginning, here we use \minn{} as the proxy of the 
+    \mstar{} of the ``in-situ'' component. 
+    We will discuss this assumption more in the Section~\ref{sec:discussion}, but 
+    observations and simulations seem to support this claim in general. 
+    In the previous section, we investigate the environmental dependence of structure 
+    using ``total'' \mstar{}; here, we compare the massive galaxies in low- and 
+    high-mass halos that share similar amount of ``in-situ'' component.}
+
+    \update{
+    As we can see in Fig.\ref{fig:prof_1} and the Appendix.\ref{app:D}, the \minn{} is 
+    not affected by the physical size of PSF out to $z=0.5$.  
     For the 56 galaxies in this \rbcg{} sample, we achieve excellent matching 
-    result using 375 \nbcg{} galaxies (see Fig.\ref{fig:prof_m10_A}).  
+    result using 375 \nbcg{} galaxies (see Fig.\ref{fig:match}; 
+    median \logminn{}$\sim 11.35$).  
     Using the same method, we show their individual profiles, and the comparison of 
-    their median \mden{} profiles in Fig.\ref{fig:prof_m10_A}.  
+    their median \mden{} profiles on the right side of Fig.\ref{fig:prof_1}.}
+
     Unlike the \mtot{} matched samples, here we see very striking differences that 
     are already very significant even without any statistical test.     
-    As we can see, when matched using \minn{}, the \mden{} profiles of \rbcg{} and 
-    \nbcg{} galaxies have quite similar \mden{} profiles in the inner 5-10 kpc, 
-    in great contrast of the differences at outer region where the \rbcg{} galaxies 
-    show much more extended envelope.      
-    Besides the difference in the median profiles, it is also worth discussing 
+    \update{
+    It is easy to see that, when matched at the same \minn{}, the \mden{} profiles of 
+    \rbcg{} and \nbcg{} galaxies are quite similar in the inner 5-10 kpc.
+    However, outside inner 10-15 kpc, the \rbcg{} galaxies show much more prominent
+    stellar envelope.}     
+    Besides the differences in the median profiles, it is also worth discussing 
     the distributions of individual \mden{} profiles. 
-    Combining the \rbcg{} and \nbcg{} samples together, it is easy to notice that 
-    the dynamical range of \mden{} at fixed radius is much larger in the outskirt. 
-    This becomes even more clear when we further normalize each profile using 
-    the \minn{} value (see Fig.\ref{fig:prof_m10_A}).   
-    For both \rbcg{} and \nbcg{} samples, we find that their outer \mden{} profiles 
-    clearly show much larger diversity comparing to the inner region.
-
-    Putting together, these results indicate that massive central galaxies with 
-    similar \minn{} and inner mass profiles can span a huge range in total stellar 
-    mass, and can have very different mass distributions in the outskirt. 
-    We further highlight this by showing the 3-color images of randomly selected 
-    massive central galaxies (see Fig.\ref{fig:m100_m10_color}) that 
-    have similar \minn{} 
+    \update{
+    Combining the \rbcg{} and \nbcg{} samples together, we should notice that 
+    the slope of the \mden{} profile inside 10 kpc is quite uniform, and the dynamic 
+    range of the \mden{} values is pretty small. 
+    On the other hand, the outer \mden{} profiles of massive central galaxies 
+    can have a larger range of slopes. 
+    The ones from more massive halos on average have shallower outer \mden{} 
+    profiles, which is in qualitative agreement with recent simulation results 
+    (e.g. \citealt{Pillepich2014}).
+    And, for both \rbcg{} and \nbcg{} samples, we find their outer profiles 
+    clearly have much larger dynamic range of \mden{} values at fixed radius.
+    This interesting diversity is also clearly illustrated by 
+    Fig.\ref{fig:m100_m10_color}, where we show the 3-color images of randomly 
+    selected massive central galaxies that have similar \minn{} 
     ($11.1 \leq \log (M_{\star,\ 10\mathrm{kpc}}/M_{\odot}) < 11.2$)
@@
     From the top-left to the bottom-right, the \mtot{} of these galaxies increases
-    from $10^{11.22} M_{\odot}$ to $10^{11.75} M_{\odot}$.
-
-    Since the two samples are matched using \minn{}, the \nbcg{} sample starts to 
-    include galaxies with 
-    $11.2 \leq \log (M_{\star,\ 100\mathrm{kpc}}/M_{\odot}) < 11.6$.  
-    On one hand, they are likely to be the central galaxies in halos that are 
-    much smaller than the ones in \nbcg{} sample, which still mostly consists of 
-    galaxies with $\log (M_{\star,\ 100\mathrm{kpc}}/M_{\odot}) \geq 11.6$.  
-    Hence, above results may hint that the outer \mden{} profile of central galaxy 
-    could have a clear dependence on the halo mass.
-    This is a very interesting clue that deserves more investigations including 
-    comparison with simulations.  
-    But, on the other hand, we need to recognize that the mass completeness of 
-    our current \nbcg{} sample is still not satisfying; and in this lower \mtot{} 
-    range, small fraction of satellite contamination should be expected even 
-    though we already excluded satellites in known cluster using the \redm{} catalog. 
-    To naively test the robustness of these results, we match the two samples using 
-    \minn{} again, but only include galaxies with 
-    $\log (M_{\star,\ 100\mathrm{kpc}}/M_{\odot}) \geq 11.5$.  
-    Comparison between these two more complete, purer samples of massive 
-    central galaxies at fixed \minn{} reveals very similar behavior
-    \footnote{In fact, their median profiles become even more similar in the 
-    inner region} (see Fig.\ref{fig:prof_m10_B}), supporting the robustness of the 
+    from $10^{11.22} M_{\odot}$ to $10^{11.75} M_{\odot}$.}
+
+    \update{
+    Putting together, these results indicate that massive central galaxies with 
+    similar \mstar{} in the ``in-situ'' components share very similar radial 
+    \mstar{} distributions in the inner region. 
+    Given the highly dissipative nature of the ``in-situ'' phase, this is consistent
+    with the prediction that dissipative process like intense star-formation or 
+    wet-merger should create de~Vaucouleur-like ($n\sim 4$) \mden{} profile
+    (e.g. \citealt{Hopkins2008}).
+    On the other hand, the outer envelope of massive galaxies should be slowly 
+    assembled through non-dissipative accretion process, where merger history 
+    should play a essential role.  
+    Therefore, it is reasonable to see that the central galaxy of more massive 
+    halo has more significant stellar envelope than the one from lower mass 
+    halo at fixed \mstar{} of their ``in-situ'' components.
+    }
+
+    \update{
+    Despite that the structural contrast is very clear using the median \mden{} 
+    profile, we still perform a serious of tests to verify the robustness of the 
     results. 
-    And, we also try to match the two samples using mass within 5 and 15 kpc 
-    instead, the results are also very similar.
+    Changing the redshift range or the lower $\lambda$ bound of the \rbcg{} sample 
+    has no impact in the significance of the results; 
+    Replacing the \minn{} with the \mstar{} within 5 or 15 kpc will result in 
+    very similar differences; 
+    And, unlike the \mtot{}-matched samples, spitting the samples into two \minn{} 
+    bins (above and below \logminn{}$=11.4$) reveals no apparent \minn{}-dependence 
+    of the structural differences.
+    During the comparison, we notice that there is still tiny structural difference
+    within 10 kpc (right figure of Fig.\ref{fig:prof_1}).
+    When we match the two samples using both \minn{} and \meff{}, we notice that 
+    inner median \mden{} profiles within 10 kpc becomes extremely similar 
+    (see Fig.\ref{fig:match} in Appendix.\ref{app:match}), while the differences 
+    in the outer part remain the same. 
+    Hence, for \rbcg{} and \nbcg{} galaxies that share not only the same inner mass, 
+    but also the same inner \mden{} profiles, we still see significant environmental 
+    dependence in their overall structure.}
+
+    \update{
+    When we match the two samples using \minn{}, the matched samples have 
+    different \mtot{} distributions (median \logmtot{}$\sim 11.78$; 
+    median \logmtot{}$\sim 11.64$).  
+    Although it is still safe to say that they represent very massive central 
+    galaxies, we also notice that the \nbcg{} sample starts to include galaxies with 
+    $11.2 \leq$\logmtot{}$< 11.6$. 
+    For one thing, our samples start to become quite incomplete below 
+    \logmtot{}$\sim 11.5$-11.6; the satellite contamination could also increases
+    toward lower \mtot{} end.  
+    More importantly, when the \mtot{} becomes very different, it is no longer 
+    comfortable to assume that they can share very similar ``in-situ'' components 
+    even at the same \minn{}, as they could be in different phases of evolution.
+    Therefore, we also match the two samples using \minn{} again, but only include the 
+    massive ones with \logmtot{}$\geq 11.5$.  
+    Comparison between these more complete, purer samples of massive central galaxies 
+    shows very similar structural differences again (see the right side of 
+    Fig.\ref{fig:match} in Appendix.\ref{app:match}).
+    In fact, their median profiles become even more similar in the inner region,
+    suggesting that the results are very robust.}
+
+    \update{
+    The median profiles shown in Fig.\ref{fig:prof_1} are available in 
+    Table.1.}
+
+%% ------------------------------------------------------------------------------------ %%
+
+\subsection{Comparisons of ellipticity and optical-color profiles}
+    \label{ssec:ell_color}
+
+%% ------------------------------------------------------------------------------------ %% 
+  \begin{figure*}[t!]
+      \centering 
+      \includegraphics[width=\textwidth]{fig/redbcg_discussion_2}
+      \caption{Comparisons of the radial profiles for ellipticity and optical colors 
+      	for \mtot{}-matched (\textbf{left figure}) and \minn{}-matched 
+      	(\textbf{right figure}) of \rbcg{} (orange-red) and \nbcg{} (grey-black) samples. 
+        The formats are very similar to the figure for \mden{} profile 
+        (e.g. right figure of Fig.\ref{fig:prof_1}). 
+        On each side, from top to bottom, we show the elliptical profile, and the 
+        color profile using $g-r$ and $g-i$ color. 
+        Since the individual profile of these properties has very large uncertain in the 
+        outskirt, we block the region at large radii where we think the median profiles 
+        are still unreliable using a dark, shaded box.
+        We also compare these results with previous results based on SDSS images. 
+        They are: 
+        1) Ellipticity profile of the stacked image of a large sample of red galaxies at 
+        $z\sim 0.4$ from \citet{Tal2011} with PSF correction 
+        (solid blue line on top panel); 
+        2) Ellipticity and $g-r$ color profiles from stacking analysis of nearby massive 
+        galaxies with high concentration index ($C>2.6$) in \citet[][blue dash lines 
+        on the top and middle panels]{DSouza2014}; 
+        3) average $g-r$ and $g-i$ color profiles for a large sample of nearby 
+        elliptical galaxies in \citet[][blue, solid lines on the middle and bottom 
+        panels]{LaBarbera2010}.}
+      \label{fig:ell_color}
+  \end{figure*}
+%% ------------------------------------------------------------------------------------ %%
+
+    \update{
+    In the above section, we focus on the 1-D \mden{} profiles that are based on 
+    $i$-band image along. 
+    Although they already help us reveal interesting structural differences, we 
+    should not forget that the multi-band, 2-D HSC images of massive galaxies 
+    contain more information. 
+    Among them, the shapes and colors of different stellar components are particularly 
+    important to look into.
+    Here, we extract the radial profiles of ellipticity and $k$-corrected optical colors
+    of galaxies in both \mtot{}-matched and \minn{}-matched samples (used in 
+    Fig.\ref{fig:prof_1}) using \texttt{Ellipse}, and compare the average profiles between
+    the \rbcg{} and \nbcg{} samples for two main purposes:}
+
+    \begin{enumerate}
+        \item \update{Since we derive the \mden{} profiles using average isophotal 
+            shape, if these massive galaxies have steep or complicated elliptical 
+            profiles, or the two samples share very different elliptical profiles, 
+            the comparison of the average \mden{} profiles could be biased.
+            Therefore, we want to verify that photometry using average isophotal 
+            shape is appropriate for these samples. 
+            We extract ellipticity profiles in $i$-band using \texttt{Ellipse} by 
+            setting the geometric parameters free while forcing all isophotes share 
+            the same center.}
+        \item \update{As emphasized earlier, we apply the average \m2l{} to derive 
+            \mstar{} of these massive galaxies knowing that the \m2l{} changes with 
+            radius.  Although this may not be a critical issue when deriving ``total''
+            \mstar{}, it certainly can bias the comparisons of \mden{} profiles when 
+            two samples have very different \m2l{} profiles. 
+            So we want to confirm that the application of average \m2l{} is reasonable
+            using the optical color profiles as tracer of \m2l{}.  
+            After preparing the images in other bands in the same way with $i$-band 
+            ones, we derive color profiles by applying the isophotes from $i$-band 
+            to other images in a ``forced photometry'' mode.}
+    \end{enumerate}
+
+    \update{
+    Strictly speaking, we need better background subtraction and 2-D modeling method 
+    to accurately recover these information. 
+    But the straightforward methods applied here are sufficient for these purposes. 
+    We make no correction to the differences in background subtraction and PSF in 
+    different bands, therefore, we will simply ignore the shape and color information 
+    in the inner-most region and very low surface brightness regime. 
+    The profiles between 5-50 kpc should be useful. 
+    Here we only consider $g$ and $r$ band data as the ones in $z$ and Y-band are 
+    often shallower, have worse seeing, and suffer more from background subtraction 
+    issues. 
+    We apply Galactic extinction and $k$-correction to both $g-r$ and $g-i$ color 
+    profiles; the $k$-correction values are also from \texttt{iSEDFit} results.
+    We show the average ellipticity, $g-r$, and $g-i$ color profiles for the 
+    \mtot{}-matched (\minn{}-matched) samples of \rbcg{} and \nbcg{} galaxies on the 
+    left (right) side of \ref{fig:ell_color}, and also compare them with previous 
+    estimates that are based on stacking analysis of SDSS galaxies 
+    (e.g. \citealt{LaBarbera2010, Tal2011, DSouza2014}).}
+
+    \update{
+    Firstly, it is easy to see that massive central galaxies on average have positive 
+    ellipticity profiles. 
+    The ellipticity slowly, but steadily increase with radius from $e\le 0.2$ around 
+    5-10 kpc to $e\sim 0.3$ at 40-50 kpc.  
+    For the \mtot{}-matched samples, their ellipticity profiles trace each other 
+    very well all the way to 50 kpc (2-3$\times R_{\mathrm{e}}$ for their \mstar{}); 
+    there might be hints that the \rbcg{} ones have higher ellipticity at larger 
+    radius, but the isophotal fits with free geometry become very unstable at such 
+    low surface brightness region. 
+    This confirms that the comparisons of \mden{} profiles using average isophotal 
+    shape is reasonable. 
+    On the other hands, when matched using \minn{}, the \rbcg{} galaxies show 
+    systematically higher ellipticity than the \ncbg{} ones at $r > 10$ kpc, despite 
+    the ellipticity profiles at inner region are still very similar. 
+    Since the average ellipticity value is still quite low, and the slope of the 
+    profile is very shallow, the differences in ellipticity profiles will not affect 
+    the significant differences in \mden{} profiles. 
+    And it further hints different assembly histories of the outer envelopes of
+    central galaxies in different environments. 
+    These results are in consistent with the ones from 2-D decomposition in
+    \citep{Huang2013a}: the outer envelopes of massive ETGs have higher ellipticity 
+    than the inner, ``in-situ'' dominated region; and become more elongated with 
+    \mstar{}. 
+    As for the ellipticity profile, although it contains interesting information 
+    regarding the assembly history, it is difficult to estimate them down to very 
+    large radius. 
+    \citet{Tal2011} stacked the SDSS images of a large sample of Luminous Red 
+    Galaxies (LRGs) at $z\sim 0.4$, and extract the ellipticity profile after 
+    correcting the PSF convolution effect.   
+    Its slope is much shallower than the average ones using HSC images, despite the 
+    two samples are at similar redshift and are quite comparable. 
+    The poorer seeing condition of SDSS image plus the systematics in the stacking 
+    process can easily explain this. 
+    \citet{DSouza2015} performed similar stacking analysis for a large sample of very 
+    nearby ETGs.  
+    The ellipticity profile is quite consistent with our average ones within 5-10 
+    kpc, but become much shallower at outer region.  
+    The lower average \mstar{} of their sample and/or the uncertainties in the 
+    stacking analysis may explain this.  
+    This highlights the advantages of the high-resolution, deep HSC images again,
+    and it would be very interesting to compare with numerical simulations. 
+    }
+
+    \update{ 
+    Secondly, we see shallow and negative gradients of average $g-r$ and $g-i$ color 
+    profiles for both \rbcg{} and \nbcg{} galaxies after excluding the unreliable 
+    regions. 
+    On the left of Fig.\ref{fig:ell_color}, we see that the \rbcg{} and \nbcg{} 
+    samples share very similar color profiles from 5-50 kpc. 
+    This is very good news for using average \m2l{} in the comparisons of \mden{}
+    profiles: although the \mden{} profiles may not be perfectly accurate, there 
+    should be no bias when comparing the average profiles of \rbcg{} and \nbcg{} 
+    samples.
+    On the right side of Fig.\ref{fig:ell_color}, the situation is very similar 
+    as the slopes of color gradients are basically the same for two samples; 
+    although there might be some evidence that, when matched at similar \mstar{} 
+    of the ``in-situ'' component, the \rbcg{} galaxies tend to have slightly redder
+    envelopes than the \nbcg{} ones. 
+    This is worth further investigation, especially vial multi-band, 2-D 
+    decomposition method. 
+    Ignoring the tiny differences between the corresponding HSC and SDSS filters, 
+    we see quite consistent $g-r$ color profiles; but the $g-i$ profiles become 
+    slightly steeper using HSC images. 
+    Although the exact cause of this difference is not clear, it is worth noting that
+    the SDSS $i$-band images suffer from the ``red-halo'' effect of extended PSF 
+    wing (e.g. \citealt{Wu2005}, \citealt{Tal2011}) which could make the color 
+    at larger radius appear redder.
+    Thank to the thickness of the CCD, the HSC $i$-band images do not have this 
+    problem, hence can provide more accurate color estimates.
+    }
+
+    \update{
+    Although the 1-D analysis is not perfect, these preliminary results already 
+    point out the importance and benefits of including multiband, 2-D information 
+    into account. 
+    Now we know that, for massive central galaxies with similar \mtot{}, the average 
+    \mden{} profiles show subtle dependence on halo mass, while the color and 
+    ellipticity profiles are very stable.  
+    On the other hands, for central galaxies that have the same \mstar{}, ellipticity 
+    and color profiles within 10 kpc, their outer envelopes appears to be strongly 
+    depend on environments. 
+    }
 
@@
           $R_{\mathrm{50}}$ derived from the 1-D profile as size estimate. 
-          The size and color coding for \rbcg{} galaxies are the same with the right panel 
-          of Fig.\ref{fig:smf1}.  
-          And two vertical lines highlight the $11.6<$\logms{}$<11.9$ mass range.
-          We also compare these distributions with the relation for nearby central 
-          galaxies of massive groups from \citet{HCompany13} (green, long dashed line). 
-          The \mstar{} and $R_{\mathrm{e}}$ are estimated via different methods in these
-          works. 
-          We also illustrate best-fit \mstar{}-$R_{50}$ relations for \rbcg{} (red, solid 
-          line)and \nbcg{} (grey, dash line) galaxies that have \logmtot{}$\geq 11.6$.
-          The shaded regions in lighter color show the 1-$\sigma$ uncertainties of these 
-          relations.
-          Please refer to the text for detailed comparisons.}
+          Two vertical lines highlight the $11.6<$\logms{}$<11.9$ mass bin.
+          We visualize the best-fit \mstar{}-$R_{\mathrm{50}}$ relations of \rbcg{} 
+          (red, solid line) and \nbcg{} (grey, dash line) galaxies at high-\mstar{} end.
+          The shaded regions in lighter colors show the 1-$\sigma$ uncertainties
+          from MCMC sampling. 
+          We also compare with the \mstar{}-$R_{\mathrm{50}}$ relation for nearby central 
+          galaxies in massive groups from \citet{HCompany13} (green, long dashed line). 
+          Please refer to the text for more details.}
       \label{fig:mass_r50}
@@
 
-    The scaling relation between \mstar{} and effective radius (or half-light radius) 
-    was the focus of past investigations of the structural evolution (e.g. \addref) and 
-    the environmental dependence of structures for massive galaxies (e.g. \addref{}). 
+    The scaling relation between \mstar{} and effective radius (or half-light radius;
+    $R_{\mathrm{e}}$ or $R_{\mathrm{50}}$) 
+    was the focus of previous investigations of the structural evolution 
+    (e.g. \citealt{Shankar2013}; \citealt{Leja2013}, \citealt{vdWel2014}) and 
+    the environmental dependence of structures for massive galaxies 
+    (e.g. \citealt{Weinmann2009}, \citealt{Nair2010}, \citealt{HCompany13}, 
+    \citealt{Cerbrian2014}). 
     So far, the results are quite confusing as no clear evidence of environmental 
     dependence has been found at low redshift using various definitions of ``size''. 
-    Also, at high redshift, the results can be even controversial
-    (e.g. \addref).  
-    As the deep HSC images have already help us reveal subtle, but systematic structural
-    differences in massive central galaxies that may depend on the environment, we should 
-    expect to see such evidence on the mass-size relation. 
-    Here, we briefly discuss the mass-size relations of \rbcg{} and \nbcg{}
-    galaxies (Fig.\ref{fig:mass_r50}).
+    And the observations become controversial at intermediate and high redshift
+    (e.g. \citealt{MCooper2012}, \citealt{Papovich2012}, \citealt{Kelkar2015}).
+    \update{
+    Through careful comparisons of \mden{} profiles at fixed \mtot{} and \minn{}, 
+    we clearly show that the structure of massive central galaxies at $0.3 < z < 0.5$
+    depend on the halo mass in a subtle but systematic manner. 
+    Therefore, we also expect to see such evidence on the \mstar{}-size relations 
+    of \rbcg{} and \nbcg{} galaxies (see Fig.\ref{fig:mass_r50}).}
 
     We choose to use the \mtot{} as the proxy of ``total'' \mstar{}, and use the 
-    half-light radius ($R_{\mathrm{50}}$) that is defined as the radius enclosing 50\% of 
-    luminosity within 100 kpc as the ``size'' to evaluate the relation.
-    And, we use the curve-of-growth of luminosity from the \texttt{Ellipse} run on 
+    radius that encloses 50\% of luminosity within 100 kpc ($R_{\mathrm{50}}$) as 
+    the ``size'' to evaluate the relation.
+    We use the curve-of-growth of luminosity from the \texttt{Ellipse} run on 
     $i$-band images to estimate the $R_{\mathrm{50}}$ here.
-    In principle, such approach is more sensitive to issues like the smearing effect of 
-    PSF and the choice of aperture for maximum luminosity than the 2-D fitting method.
-    For the massive galaxies in this work, their apparent sizes are always sufficiently 
-    large at $0.3 \geq z \geq 0.5$ so that the $R_{\mathrm{50}}$ measurement is not 
-    bothered by PSF.   
-    And, the 1-D method has the advantages of being less affected by accuracy of background
-    subtraction, structural details, and model assumptions.
-
-    We show the distributions of \rbcg{} and \nbcg{} galaxies on the mass-size plane.  
-    On top of the clear correlations for both sample, the distributions of $R_{\mathrm{50}}$ 
-    for \rbcg{} and \nbcg{} samples greatly overlap with each other over the \mtot{} range
-    between $10^{11.6}$ and $10^{11.9} M_{\odot}$. 
+    This 1-D approach is more sensitive to issues like the smearing effect of PSF and 
+    the choice of aperture for maximum luminosity than the 2-D fitting method.
+    But, for the massive galaxies in this work, their apparent sizes are always 
+    sufficiently large at $0.3 \geq z \geq 0.5$ so that the $R_{\mathrm{50}}$ 
+    measurements are not bothered by seeing.  
+    At the same time, this 1-D method has the advantages of being less affected by the 
+    accuracy of background subtraction, structural details, and model assumptions.
+
+    On Fig.\ref{fig:mass_r50}, we see clear \mstar{}-size relations for both samples.  
+    At fixed \mtot{}, the distributions of $R_{\mathrm{50}}$ for the \rbcg{} and
+    \nbcg{} galaxies greatly overlap.  
     Meanwhile, it seems that the \rbcg{} galaxies do have a slightly higher 
     $R_{\mathrm{50}}$. 
-    For the \mtot{} matched samples used in Fig.\ref{fig:prof_m100_A}, the median 
+    For the \mtot{}-matched samples used in Fig.\ref{fig:prof_1}, the median 
     $\log (R_{\mathrm{50}}/\mathrm{kpc})$ values for the \rbcg{} and \nbcg{} are 
@@
     ($\sim 12.3\pm0.3$ kpc), which confirm the above observation and is consistent with 
-    the differences seen in Fig.\ref{fig:prof_m100_A}. 
-    However, all previous works that we are aware of did not match the mass (and redshift) 
-    distributions between different samples, and often focus on the form of the 
-    \logms{}-$\log R_{\mathrm{e}}$ relation.  
+    the differences seen in Fig.\ref{fig:prof_1}. 
+    However, most previous works that we are aware of did not match the \mstar{} 
+    and redshift distributions between different samples, and often focused on the shape 
+    of the \logms{}-$\log R_{\mathrm{e}}$ relation.  
     Here, we try to derive the best-fit parameters for the 
@@
     Using initial guesses based on maximum likelihood estimates, and assuming reasonable 
-    flat priors, we derive best-fit relation for the massive \rbcg{} galaxies:
+    flat priors, we derive best-fit relations for the massive \rbcg{} galaxies:
 
@@
     $14\le$\logmh{}$<15$ halos from \citealt{HCompany13} (HC13; green solid line).
-    HSC13 use the group catalog by \citet{Yang2007} to estimate \logmh{}. 
-    They estimate the 2-D $R_{\mathrm{e}}$ using single-\ser{} model fitting to SDSS images,
-    and derive \mstar{} based on SED fitting using the BC03 (\citealt{BC03}) synthetic 
-    population model.
+    HSC13 used the group catalog by \citet{Yang2007} to estimate \logmh{}. 
+    They estimated the 2-D $R_{\mathrm{e}}$ using single-\ser{} model fitting to SDSS 
+    images, and derived \mstar{} based on SED fitting using the BC03 (\citealt{BC03}) 
+    synthetic population model.
     We empirically convert their \mstar{} from the Kroupa IMF to the Chabrier one 
-    used in this work by applying a constant -0.03 shift to their values. 
+    used in this work by applying a constant -0.05 shift to their values (see 
+    \citealt{Bernardi2016}). 
     We also increase the \mstar{} in HC13 by $+0.1$dex to account for the systematic 
@@
     In short, we confirm that the massive central galaxies in this work generally 
-    follow the mass-size relation of massive ETGs at low-$z$.
-    And, more importantly, we find evidence of differences in the mass-size relations for 
-    massive central galaxies of halos with different \mhalo{}. 
-    The difference we saw at \logmtot{}$\geq 11.6$ is in line with the conclusion that
-    central galaxies in denser environment have slightly larger size comparing to the 
-    ones from less-dense environment at fixed \mstar{}.
-
-    This suggests that the previous, inconclusive results on whether the 
-    mass-size relation of massive ETGs depends on environment could be due to 
-    either the inadequate depth of the image, or the inappropriate model assumptions 
-    adopted during the fitting (or both).  
-    It would be interesting to revisit this issues using 2-D models based on deep HSC 
+    follow the \mstar{}-size relation for massive ETGs at low-$z$.
+    \update{
+    More importantly, we find that the \mstar{}-size relations at high-\mstar{} end 
+    depends on \mhalo{}, suggesting that the central galaxies in denser environment 
+    (higher \mhalo{}) have slightly larger $R_{\mathrm{50}}$ comparing to the 
+    ones from smaller haloes at fixed \mtot{}. 
+    }
+
+    It would be interesting to revisit this topic using 2-D models based on deep HSC 
     images as the next step.
@@
     while the sample of HC13 has $z<0.09$.
-    Although here we can not address the interesting issue of redshift evolution of 
-    mass-size relation, the ``evolutionary path'' of massive central galaxies from 
-    different environments on this mass-size plane is certainly an intriguing issue. 
-    If the \rbcg{} galaxies have a richer merging history than the \nbcg{} ones, 
-    perhaps we should expect more significant differences on their mass-size 
-    relations and average \mden{} profiles at $z\sim 0$ using deeper image. 
-    On the other hand, if the \nbcg{} galaxies could assemble more \mstar{} through minor 
-    mergers in the last 3-4 Gyrs, they could ``catch-up'' with the \rbcg{} galaxies 
-    a little bit on the mass-size plane. 
-    Potentially, we could make some predictions on this issue using the frequency of 
-    tidal features and properties of satellites around our \rbcg{} and \nbcg{} 
-    galaxies in the near future.
+    \update{
+    Although here we can not study the redshift evolution of \mstar{}-size relation 
+    here, it will be interesting to see whether the structural evolution of massive
+    galaxies between $z\sim 0.4$ and $0.0$ also depends on environment. 
+    If the \rbcg{} galaxies experienced more megers than the \nbcg{} ones during this 
+    time, we should expect that \mstar{}-size relation shows stronger environmental 
+    dependence at $z\sim 0.0$ using deeper image than SDSS.} 
+    On the other hand, if the \nbcg{} galaxies could assemble more \mstar{} through
+    minor mergers in the last 3-4 Gyrs, they could potentially ``catch-up'' with the 
+    \rbcg{} galaxies on the \mstar{}-size plane, and makes it harder to find the 
+    environmental dependence in nearby universe.
+    In principle, we can make uses of the frequency of tidal features and the numbers 
+    of satellites around our \rbcg{} and \nbcg{} galaxies to make some predictions 
+    in the near future.
 
@@
 
-    We just show that the mass-size relation of massive central galaxies could also 
-    depend on the mass of their host halos, and here we explore relationships between 
+    We just show that the \mstar{}-size relation of massive central galaxies also 
+    depends on the \mhalo{} or environment, and now we explore relationships between 
     \mstar{} within different apertures as alternative tools to help
-    us better understand the relationship between halo mass and assembly history of 
+    us better understand the relationship between \mhalo{} and the assembly history of 
     massive galaxies.  
@@
     between them ($\Delta \log M$, reflecting \mstar{} ratio). 
-    Comparing to the mass-size relation, such relations are not affected by the ambiguous 
-    definition of ``size''; and comparing to the detailed \mden{} profiles, 
-    it is much easier to apply these relations to larger samples and compare with 
-    results from simulations.
+    Comparing to the \mstar{}-size relation, such relations are not affected by the 
+    ambiguous definition of ``size''; and comparing to the detailed \mden{} profiles, 
+    it is much easier to apply these relations to larger samples or to compare with 
+    simulations.
 
@@
     and \nbcg{} samples. 
-    As expected, these two parameters well trace each other over the entire 
-    \mtot{} range, indicating that more massive central galaxies have larger 
-    fraction of total \mstar{} in the outer part. 
-    Suggested in Fig.\ref{fig:prof_m100_C}, the structural differences related to 
-    \mhalo{} seem to be more significant in higher \mstar{} bin. 
+    As expected, these two parameters well trace each other over the entire range of
+    \mtot{}, indicating that more massive central galaxies have larger 
+    fraction of total \mstar{} in their outskirts. 
+    Suggested in Fig.\ref{fig:prof_2}, the structural differences related to 
+    \mhalo{} seem to be more significant in the higher \mstar{} bin. 
     We therefore highlight the \mtot{}-matched \rbcg{} and \nbcg{} galaxies at 
     $11.7 \leq$\logmtot$< 11.9$. 
-    Although their $\Delta \log M$ distributions still greatly overlap within 
-    this \mtot{} range, the median values (big, outlined symbols with error bars),
-    and their kernel-density distributions clearly point out systematic difference. 
+    Although the $\Delta \log M$ distributions still greatly overlap at high-\mtot{} 
+    end, their median values (big, outlined symbols with error bars),
+    and kernel-density distributions clearly reveal systematic difference. 
     Consistent, but slightly smaller, difference also exists for \mtot{}-matched 
     samples at $11.6 \leq$\logmtot$< 11.9$.
-    At the same time, the comparisons in Fig.\ref{fig:prof_m100_A} and 
-    Fig.\ref{fig:prof_m100_C} also suggest that the \mtot{}-matched \rbcg{} galaxies 
-    have lower \minn{} than the \nbcg{} sample, which is clearly shown by panel (b)
-    where we plot $\Delta \log M$ with \minn{} for the \mtot{}-matched samples.
-    For the \nbcg{} sample, the correlation between between $\Delta \log M$ and \minn{}
-    is much weaker than the one in panel (a), yet it is still visible.  
-    However, for our \rbcg{} sample, we see no overall correlation between 
-    $\Delta \log M$ and \minn{}.  
+
+    At the same time, the comparisons in Fig.\ref{fig:prof_1} and 
+    Fig.\ref{fig:prof_2} also suggest that the \mtot{}-matched \rbcg{} galaxies 
+    have lower \minn{} than the \nbcg{} sample. 
+    \update{
+    When we plot $\Delta \log M$ with \minn{} for the \mtot{}-matched samples in 
+    panel (b), we can easily confirm this result.
+    The correlation between $\Delta \log M$ and \minn{} is quite weak for the 
+    \nbcg{} galaxies, but still visible. 
+    However, we see no apparent correlation between $\Delta \log M$ and \minn{} 
+    for the \rbcg{} galaxies. 
     We also construct $\Delta \log M$ using logarithmic mass differences between 
     100 and 30 (or 50) kpc, and the results are very similar.   
-    In fact, the average differences between the \mtot{}-matched \rbcg{} and \nbcg{} 
-    samples become more significant when mass within 30 (or 50) kpc is used.        
-    These reflect the structural differences we found in Fig.\ref{fig:prof_m100_A}: 
-    at fixed \mtot{}, central galaxies with higher \mhalo{} tend to have even higher 
-    fraction of \mstar{} stored between 10 and 100 kpc.
-
-    In panel (c), we show the relationship between $\Delta \log M$ and \mtot{}, 
-    and highlight the \minn{}-matched samples presented in Fig.\ref{fig:prof_m10_A} 
-    and Fig.\ref{fig:prof_m10_B}. 
-    Using the histograms of \mtot{} and their median values of the \minn{}-matched
-    samples, we clearly identify the impact from the much more extended outer envelope 
-    hosted by \rbcg{} galaxies.
+    These reflect the structural differences we found in Fig.\ref{fig:prof_1}: 
+    at fixed \mtot{}, central galaxy in more massive halo tende to have even higher 
+    fraction of \mstar{} stored between 10 and 100 kpc than the one from smaller 
+    haloes.}
+
+    In panel (c), we show the relationship between \mtot{} and $\Delta \log M$ 
+    again, but highlight the \minn{}-matched samples showed in right panel of 
+    Fig.\ref{fig:prof_1}. 
+    \update{
+    Their distributions clearly show the impact of the much more prominent outer 
+    envelope hosted by \rbcg{} galaxies through the differences in \mtot{} and 
+    $\Delta \log M$ of the \minn{}-matched samples.
+    }
 
     Finally, in panel (d), we plot \mtot{} against \minn{} directly.  
-    The median values and statistical distributions of \minn{} for the \mtot{}-matched 
-    samples highlight the structural difference at fixed \mtot{} again.  
-    All the \mhalo{}-dependence of structures we discussed above are clearly 
-    displayed here along the directions of both x- and y-axis.
-    Firstly, within the \mtot{} range we explored, the \rbcg{} galaxies tend to have 
-    lower mass within the inner 10 kpc; and such difference seems to become more 
-    significant at higher \mtot{}. 
-    As seen from the median \mden{} profiles, this is due to the shallower overall
-    profile of \rbcg galaxy, and indicates that the slopes of both inner and outer
-    \mden{} profiles of massive central galaxies may depend on \mhalo{}. 
-    Secondly, for massive central galaxies that form similar amount of stars through
-    the dissipative processes during the ``in-situ'' phase (approximated by \minn{}), 
-    their \mtot{} distributions at lower redshift depend on \mhalo{} in a way that the
-    ones in more massive halos can develop much more prominent stellar envelope thanks 
-    to the more complex mass assembly history.
-
-    But, more importantly, it is intriguing to see that the distributions of \rbcg{} and
-    \nbcg{} galaxies on this 2-D plane seem to be offset with each other. 
-    At least at the high mass end, the central galaxies in more and less massive halos 
-    seem to follow relations between \mtot{} and \minn{} with similar slopes, but 
-    different normalizations.  
-    Instead of subjectively grouping galaxies into different bins of \mtot{} or \minn{}, 
-    such scaling relation brings us a more generic view of the environmental 
-    dependence of structure, and could become an interesting tool to investigate the 
-    connection between halo mass, assembly history, and the structure of massive galaxies.
-    On Fig.\ref{fig:m100_m10_A} (d), we illustrate the \logmtot{}-\logminn{} relations 
+    It is intriguing to see that the distributions of \rbcg{} and \nbcg{} galaxies 
+    on this 2-D plane seem to be offset with each other. 
+    At least at the high mass end, the central galaxies in more and less massive 
+    halos seem to follow \mtot{}-\minn{} relations with similar slopes, but different 
+    normalizations.  
+    Instead of ``arbitrarily'' grouping galaxies into different bins of \mtot{} or 
+    \minn{}, such scaling relation brings us a more generic view of the environmental 
+    dependence of structure, and could help us better investigate the relations among 
+    halo mass, assembly history, and the structure of massive galaxies.
+    On Fig.\ref{fig:m100_m10_A} (d), we illustrate the \mtot{}-\minn{} relations 
     at \logmtot$\geq 11.6$ that are derived using MCMC sampling method.  
@@
 
-    \noindent While for the \nbcg{} ones within the same \mtot{} range, we have:
+    \noindent In the same range of \mtot{}, the best-fit relation for \nbcg{} is:
 
@@
 
-    The same relation using the full \mtot{} range will results in a even shallower 
-    slope for the \rbcg{} galaxies. 
-    And, replacing the \minn{} with \mstar{} within 5 or 15 kpc apertures does not change 
-    our conclusion. 
+    Fitting this relation in the full \mtot{} range results in even shallower slope for 
+    the \rbcg{} galaxies. 
+    Also, replacing the \minn{} with \mstar{} within 5 or 15 kpc apertures does not change 
+    our conclusions. 
     In fact, the relation using $M_{\star, 5\ \mathrm{kpc}}$ shows more significant 
     \mhalo{} dependence at the high-mass end. 
-    Unfortunately, due to the impact from PSF, the $M_{\star, 5\ \mathrm{kpc}}$ values 
-    are slightly less reliable than the \minn{} ones. 
-    Samples at lower redshift, images from space telescope, and 2-D modeling method can 
-    all help us pushing this investigation further insider smaller physical aperture 
-    that perhaps can provide us better surrogate of \mstar{} from the ``in-situ'' phase.
-
-    Besides the systematic offset, it seems that the \rbcg{} galaxies could have 
-    larger scatter of \minn{} at high-mass end. 
-    Limited by our capability to estimate the mass and other properties of halos 
-    at individual level, we can not further quantify this potential \mhalo{}-dependence 
-    here.
-    Within the \rbcg{} sample, we do not find any evidence of dependence on the richness 
-    ($\lambda$) of the cluster even the \redm{} richness should traces \mhalo{}
-    reasonably well.
+    Unfortunately, due to the impact of PSF, the $M_{\star, 5\ \mathrm{kpc}}$ values 
+    are less reliable than \minn{}. 
+    \update{
+    Samples at lower redshift, images with higher spatial resolution, and 2-D modeling 
+    analysis can help us push the investigation further into smaller radius, and help 
+    us develop better proxy for the \mstar{} of the ``in-situ'' component.  
+    }
+
+    \update{
+    Limited by our capability to estimate \mhalo{} with better accuracy or individually, 
+    we can not further quantify this \mhalo{}-dependence here.
+    Albeit that the \redm{} richness ($\lambda$) traces \mhalo{} reasonably well, 
+    we do not find any clear correlation with $\lambda$ within the \rbcg{} galaxies.
+    }
     In the current sample, most of the \rbcg{} galaxies are centrals of clusters with 
-    $30 \leq \lambda \leq 40$, and only small fraction comes from more massive clusters.  
-    Together with the small sample size, the uncertainties of richness from shallow SDSS
+    $30 \leq \lambda \leq 40$, and only a small fraction comes from more massive clusters.  
+    Therefore, the small sample size, the uncertainties of richness from shallow SDSS
     images, and the intrinsic scatter of the $\lambda$-\mhalo{} relation may conspire to 
-    hide more detailed \mhalo{}-dependence.
-
-    The evidence of \mhalo{}-dependence of structure in massive galaxies could be caused 
-    by different processes, it is therefore of great interest for us to dig deeper by 
-    comparing the galaxies at higher redshift or from numerical simulations (e.g. see 
-    Fig.1 of \citealt{Wellons2016b}) on the \mtot{}-\minn{} or similar planes.
-
+    stop us from extracting more information from this \mhalo{}-dependence.
+
+    \update{
+    The \mhalo{}-dependence of structure in massive central galaxies could be the result 
+    of many different physical processes. 
+    It would be very interesting to compare with progenitors of these massive 
+    galaxies at higher redshift and with the results of numerical simulations (e.g. see 
+    Fig.1 of \citealt{Wellons2016b}) vial the \mtot{}-\minn{} or similar relations.
+    }
+
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
+  \begin{figure*}[t]
+      \centering 
+      \includegraphics[width=\textwidth]{fig/redbcg_discussion_5}
+      \caption{
+      \update{
+          \textbf{Left}: Relation between \mtot{} and the logarithmic mass difference 
+          between \mmax{} and \mtot{} for both \rbcg{} (red square) and \nbcg{} 
+          (grey dot) galaxies.  The format is very similar to the left figure of 
+          Fig.\ref{fig:smf1}.~~
+          \textbf{Right}: The stellar mass volume-density distributions of massive galaxies 
+          after combining the \rbcg{} and \nbcg{} samples together, using both 
+          \mtot{} (black solid line) and \mmax{} (black dash line). 
+          The uncertainty for distribution using \mtot{} is shown in grey shaded region.  
+          Here, we also compare the distributions with SMF from previous works: 
+          (a): SDSS galaxies at $z\sim 0.1$ from \citet{Bernardi2013}; the \mstar{} is 
+          based on photometry from 2-D \ser{}$+$Exponential model fitting; 
+          (b): SDSS galaxies at $z\sim 0.1$ from \citet{Moustakas13} based on 
+          improved SDSS \texttt{cModel} photometry; 
+          (c): \texttt{S82-MGC} galaxies at $0.15 < z< 0.43$ from 
+          \citet{Leauthaud2016} based on PSF-matched SDSS-UKIDSS photometry.
+          Please see text for more details of the comparison.
+          }}
+      \label{fig:discussion_1}
+  \end{figure*}
 %% ------------------------------------------------------------------------------------ %%
@@
           Ultra-Deep Field.}
-      \label{fig:discussion_1}
+      \label{fig:discussion_2}
   \end{figure}
@@
 
-    \alexie{In some point of the paper (in the results section).
-We need to say what the difference is between M100 and the mass that you would get if you extrapolated outwards.
-How different is M100 potentially from a "total mass"?}
-    \song{Yes, I can say a few words about that. I will send you with a figure that shows 
-    the mass differences between 150 kpc and 100 kpc; At 150 kpc, we are already pushing 
-    it to region where the photometry is uncertain, and affected by background subtraction.
-    Most of the current works on ICL are in region smaller than this. 
-    The key is 1) the mass increase is small, $<0.1$ dex, same level with the mass 
-    uncertainty; 2) still depends on \mtot{}, more massive ones have more 
-    extended outer profiles, hence more massive in outer regions.  
-    Using 2-D fitting will give you higher stellar mass, as it extrapolates to 
-    very large radius, but you have to assume at that radius, the profile follows
-    the model defined at inner region, which is kind of dangereous as we show here.
-    I could say this is worth exploring in the future.}
     In the past decade, the mass assembly and structural evolution of massive ETGs 
@@
     a considerable fraction of nearby BCGs (34\%) does not fall into the ``cD'' class.
-    From the smooth distributions of \mden{} profiles on Fig.\ref{fig:prof_m100_A} 
-    and Fig.\ref{fig:prof_m10_A}, it is even harder to draw a clear difference 
+    From the smooth distributions of \mden{} profiles on Fig.\ref{fig:prof_1} 
+    and Fig.\ref{fig:prof_4}, it is even harder to draw a clear difference 
     between ``cD'' galaxy and ``normal elliptical''.
@@
     envelope during the second phase, exactly as we find in the \mden{} profile 
-    comparison of the \minn{}-matched samples (see Fig.\ref{fig:prof_m10_A}).
+    comparison of the \minn{}-matched samples (see Fig.\ref{fig:prof_4}).
     Under the ``two-phase'' formation scenario, the stellar content of massive galaxies
@@
     Given that (1) the ``transition radius'' between the two median profiles is around
-    15-20 kpc (see Fig.\ref{fig:prof_m100_A}); and (2) the differences become more 
+    15-20 kpc (see Fig.\ref{fig:prof_1}); and (2) the differences become more 
     significant at higher mass end, it is likely the \mhalo{}-dependence of structure
@@
     It is known that major-merger induced coalesce of super-massive black hoes (SMBHs)
-    can create flattened inner profile (e.g. \citealt{Milosavljvi2002}), and recent 
+    can create flattened inner profile (e.g. \citealt{Milosavljevi2002}), and recent 
     discoveries of massive BCGs with very large core 
@@
 
-    \song{Will make a short sub-section in the results for these}
-\alexie{This paragraph shoud go in the results section.
-Indeed, here you are presenting a result that you measured.
-And what is the main message / lesson that we learn from this paragraph and figure?
-We sort of jumped rather abruptly from the enviromental dependence to ellipticity and color profles.
-Transition needs more motivation.
-A discussion of the implcations of this figure could go in the discussion section.}    As a start, we only focused on the 1-D \mden{} profile derived from $i$-band image.
-    We should not forget that the multi-band, 2-D HSC images of these massive galaxies 
-    actually contain much more useful information, particularly the shapes and colors 
-    of different stellar components.  
-    Strictly speaking, to extract these information reliably, we need to rely on better 
-    background subtraction and 2-D modelling method.  
-    But, as a motivation, we shows initial results from 1-D analysis in 
-    Fig.\ref{fig:discussion_2}.  
-    The ellipticity profile is extracted from \texttt{Ellipse} run on $i$-band image 
-    with free geometric parameters. 
-    After reducing the $g$- and $r$-band images of our galaxies in consistent way with 
-    the $i$-band ones, we simply apply the $i$-band isophotes to images in these two 
-    bands without matching the seeing to extract color profiles. 
-    All the color profiles are corrected for Galactic extinction and $k$-correction 
-    using \texttt{iSEDFit} results. 
-    We show the median ellipticity, $g-r$, and $g-i$ color profiles of the 
-    \mtot{}-matched (\minn{}-matched) samples of \rbcg{} and \nbcg{} galaxies on the 
-    left (right) panel; and also compare them with median profiles from stacking 
-    analysis of SDSS galaxies with similar \mstar{} 
-    (\citealt{LaBarbera2010, Tal2011, DSouza2014}) excluding the inner and outer regions 
-    affected by seeing and uncertainty of background subtraction.  
-    For the \mtot{}-matched samples on the left, we notice that the median ellipticity 
-    profiles follow the stacked ones well between 5 to 30-50 kpc, but are not plateaued
-    at larger radius.  
-    Since they are the median of individually measured ellipticity profiles, they do 
-    not suffer the systematics in stacking analysis, and are better at reflecting the 
-    intrinsic profiles.  
-    In consistent with the 2-D decomposition results in \citep{Huang2013a}, the 
-    projected \mstar{} distributions in massive galaxies become increasingly elongated 
-    at larger radius.  
-    We notice no significant difference between the \rbcg{} and \nbcg{} samples, 
-    except for maybe some hints that centrals in more massive halos becomes slightly 
-    more elliptical at very large radius.  
-    For the median color profiles, we see shallow and negative gradients of both 
-    $g-r$ and $g-i$ colors as expected. 
-    More importantly, the \rbcg{} and \nbcg{} samples show very consistent color 
-    gradients, which confirms that using average color to derive \m2l{} of both 
-    samples will not bias the comparison of \mden{} profiles.  
-    Without conversion between the HSC and SDSS filter systems, our median color 
-    profiles appear to be little steeper than the stacked ones from SDSS.  
-    The exactly cause of this difference is not clear, although it could also be 
-    due to the systematics in the stacking process. 
-    As for the \minn{}-matched samples on the right, it becomes very clear that the 
-    extended envelopes hosted by \rbcg{} galaxies have much higher ellipticity, and 
-    redder $g-i$ colors than the outskirts of \nbcg{} ones at similar \minn{}.  
-    All these preliminary results point out that, by including these information 
-    into consideration, we will have a more complete view of the connection between 
-    halo/environment and structure of massive central galaxies.
+    \song{Move a big paragraph to Results}
 
@@
 
-%% ------------------------------------------------------------------------------------ %% 
-  \begin{figure*}[t!]
-      \centering 
-      \includegraphics[width=17.0cm]{fig/redbcg_discussion_2}
-      \caption{\alexie{Seems to me that this goes in the results section?} Comparisons of the radial profiles for ellipticity and optical colors 
-      	for \mtot{}-matched (left figure) and \minn{}-matched (right figure) of 
-        \rbcg{} (orange-red) and \nbcg{} (grey-black) samples. 
-        The formats are very similar to the figure for \mden{} profile 
-        (e.g. right figure of Fig.\ref{fig:prof_m100_A)}. 
-        On each side, from top to bottom, we show the elliptical profile, and the 
-        color profile using $g-r$ and $g-i$ color. 
-        Since the individual profile of these properties has very large uncertain in the 
-        outskirt, we block the region at large radii where we think the median profiles 
-        are still unreliable using a dark, shaded box.
-        We also compare these results with previous results based on SDSS images. 
-        They are: 
-        1) Ellipticity profile of stacked image of large sample of red galaxies at 
-        $z\sim 0.4$ from \citet{Tal2011}, with and without PSF correction 
-        (solid and dotted blue lines on top panel); 
-        2) Ellipticity and $g-r$ color profiles from stacking analysis of nearby massive 
-        galaxies with high concentration index ($C>2.6$) in \citet[][blue dash lines 
-        on the top and middle panels]{DSouza2014}; 
-        3) average $g-r$ and $g-i$ color profiles for a large sample of nearby 
-        elliptical galaxies in \citet[][blue, solid lines on the middle and bottom 
-        panels]{LaBarbera2010}.}
-      \label{fig:discussion_2}
-  \end{figure*}
-%% ------------------------------------------------------------------------------------ %%
+%    As suggested by the popular two-phase formation scenario of massive galaxies, 
+%    the inner 5-10 kpc of these galaxies (within 0.5-1$xR_{\mathrm{e}}$) is 
+%    dominated by stars formed in intensive dissipative processes at high redshift, 
+%    and is less affected by the succeeding merging events.  
+%    This picture is broadly supported by the redshift evolution of \mden{} profile
+%    of massive galaxies (\addref), structure decomposition of nearby massive galaxies 
+%    (\addref), and their radial distributions of stellar population (\addref).      
+%    Certainly, major merger can induce violent relaxation process that modifies the 
+%    stellar mass distribution even in the central region, and must happen to 
+%    these massive galaxies in last 6-8 Gyrs, it may not invalidate the above assumption.
+%    For galaxy this massive, the last major merger event is highly likely to be
+%    non-dissipative, and the redistribution of stars is basically according to their 
+%    binding energy in the host halo.  
+%    The inner region of the final merger remnant is still mostly composed 
+%    of the ``in-situ'' stars from the two progenitors.
 
@@
     \label{sec:summary}
-\alexie{In this section, put a bullet list summarizing our main findings.}
-	\song{Ok, will do}
-
-    In this work, we use the deep $i$-band images from the Subaru HSC survey to 
-    study the role played by halo mass in determining the mass assembly history and 
-    stellar structures of very massive galaxies--the most impressive outcomes of 
-    the hierarchical formation process.
-    We map the stellar mass distributions of a large sample of massive central 
-    galaxies at $0.3 < z < 0.5$ out to $>100$ kpc. 
-    With the help of this impressive dataset, we uncover the very extended stellar 
-    envelope around massive central galaxies with great accuracy. 
-    We also reveal that, the ``total'' \mstar{} of massive galaxies can be significantly 
-    underestimated if shallow image and/or inappropriate model is used, which can 
-    lead to systematics in the study of stellar mass function and other important 
-    topics.
-
-    More importantly, we discover subtle, but systematic, and robust structural 
-    differences in massive galaxies that depend on \mhalo{} through comparisons
-    of their \mden{} profiles. 
-    On average, at fixed \mstar{} within 100 kpc, the massive central galaxies in 
-    more massive ($M_{200,m}$ \gax $1.6\times 10^{14} M_{\odot}$) halos show shallower 
-    inner \mden{} profile within $\sim 15$-$20$ kpc, and a more prominent outer 
-    envelope comparing to the ones in less massive 
-    ($M_{200,c}$ \gax $8.7\times 10^{13} M_{\odot}$) halos.
-    Also, at the same \mstar{} within inner 10 kpc--a proxy of the \mstar{} assembled 
-    through the ``in-situ'' channel, we show that the ones in more massive halos 
-    possess much more extended stellar halos in the outskirts.  
-    Such differences are broadly consistent with the prediction of the ``two-phase''
-    formation scenario of massive galaxies: the ones in more massive halos have 
-    experienced more minor, dry mergers that accumulate more stars at large radius. 
-    Meanwhile, we also suspect the differences in the inner profiles at fixed \mstar{} 
-    or \mhalo{} may help us understand more about the impact from major merger or 
-    AGN feedback. 
-    We further suggest that the relation between \mtot{} and \minn{}\footnote{or other 
-    even better proxies of total \mstar{} and the mass formed in the ``in-situ'' phase.} 
-    is potentially interesting in diagnosing the assembly history of massive galaxies 
-    and their host halos.
+
+    \update{ 
+    In this work, we study the how environment (halo mass) affects the structures and
+    assembly history of massive central galaxies using deep images from the Subaru HSC 
+    survey.
+    With the help of these high-quality data, we map the stellar mass distributions of 
+    large numbers of massive central galaxies at $0.3 < z < 0.5$ out to $>100$ kpc, 
+    and discussing their environmental dependence after grouping them into centrals of 
+    halos more and less massive than \mhalo{}$\sim 10^{14} M_{\odot}$. 
+    The main results here are:}
+
+    \begin{enumerate}
+        \item \update{
+            We find that the ``total'' \mstar{} of these massive galaxies could be 
+            significantly underestimated when shallow image (e.g. the SDSS ones) 
+            and/or imperfect model assumption (e.g. the \texttt{cModel}) are used.
+            In different with previous works, this result does not depend on stacking 
+            analysis or any parametric model. 
+            Moreover, the level of such underestimation could also depend on the 
+            stellar mass. 
+            This should be carefully taken into account when discussing important 
+            topics like the stellar mass function and its evolution.
+            }
+        \item \update{
+            At fixed \mstar{} within 100 kpc, we find that the massive central 
+            galaxies in more and less massive halos have subtle, but systematic 
+            differences in their \mden{} profiles when their ellipticity and optical 
+            color profiles are very similar. 
+            On average, the ones from denser environments have slightly shallower 
+            inner \mden{} profiles while showing more prominent outer envelope.
+            }
+        \item \update{
+            Meanwhile, when matched at the same \mstar{} within inner 10 kpc--a 
+            proxy of the \mstar{} formed in the the ``in-situ'' channel, we find 
+            that the ones in more massive halos possess much more extended stellar 
+            envelope in the outskirts than the ones in smaller halos when the 
+            \mden{}, ellipticity, and optical color profiles inside 10 kpc show 
+            no dependence on environment. 
+            }
+        \item \update{
+            The \mstar{}-size relation also reflects the subtle environmental 
+            dependence as the central galaxies from more massive halos have 
+            slightly higher $R_{\mathrm{50}}$ at fixed \mtot{}. 
+            We further suggest that the relation between \mtot{} and 
+            \minn{}\footnote{or any better proxy of total \mstar{} and the mass 
+            formed in the ``in-situ'' phase.} can be useful tool in diagnosing the
+            assembly history of these massive galaxies and its relation to their 
+            dark matter halos. 
+            }
+    \end{enumerate}
 
@@
     %\label{ssec:future}
-    These results also highlight the advantages of HSC survey in studying the evolution 
-    of massive galaxies.
-    By the finish of this paper, the HSC survey will have already doubled its sky 
-    coverage to $\sim 200$ deg$^2$, and can provide a much larger sample of massive 
+    These results are broadly consistent with the prediction of the ``two-phase''
+    scenario: the massive central galaxies in more massive halos should experience 
+    more minor, dry mergers that accumulate more stars in the outskirts. 
+    These results also highlight the advantages of HSC survey in studying the 
+    evolution of massive galaxies.
+    Upon finishing this work, the HSC survey has already doubled its sky 
+    coverage to $\sim 200$ deg$^2$, and provides a much larger sample of massive 
     central galaxies. 
     At the same time, we will work on better data reduction of HSC images by 
-    improving the deblending in crowded region and the accuracy of background 
-    subtraction as they can help provide more reliable SED fitting results, and 
-    push the photometric limit toward to even lower surface brightness level.
+    improving the deblending in crowded regions and the accuracy of background 
+    subtraction. 
+    This can help provide more reliable SED fitting results, and push the 
+    photometric limit to even lower surface brightness.
 
@@
     redshift from SDSS and BOSS.  
-    Running \redm{} algorithm or similar group/cluster finder using HSC catalogs 
-    will greatly help us extend the discussion of halo mass to lower mass and 
-    higher redshift regimes. 
-    Better identifications and measurements of satellites in massive halos will 
-    also open up the possibility to study ``environment'' within the halo: e.g. 
-    Compare the structures of satellites in massive halos and centrals in less 
-    massive ones at similar stellar mass.
-
-    Another key technical improvement would be to apply carefully designed 2-D 
-    photometric modeling to these massive galaxies.  
-    Using the same principle in \citealt{Huang2013a}, we will gradually build up 
-    the complexity, and explore different models to fit these massive galaxies 
+    Running \redm{} algorithm or similar group/cluster finder on HSC catalogs 
+    can greatly help us extend the discussion to lower \mhalo{} and higher 
+    redshift. 
+    Better selection of satellites in massive halos will also open up the 
+    possibility to study ``environment'' within the halo.
+    It is interesting to see whether there is any structural difference
+    between central and satellite galaxy at similar \mstar{}.
+
+    We will work on careful 2-D photometric modeling to these massive galaxies.
+    Under the same principle outlined by \citealt{Huang2013a}, we will explore 
+    different models, and gradually build up the complexity to fit these galaxies 
     better.
-    These 2-D models can help us removing the impact from seeing, and dealing with 
-    the uncertainties of sky subtraction, so that we can measure the stellar mass 
-    distributions to both smaller and larger radii. 
-    Applying these models to multiband images with reasonable constraints (e.g. 
-    \citealt{Huang2016}), we can characterize color gradients, and to achieve better
-    estimates of total stellar mass.
-
-    Primarily designed as a cosmological survey, the deep imaging depth and 
-    excellent $i$-band seeing of HSC can greatly improve the weak lensing analysis 
-    of massive galaxies. 
-    Therefore, our next major goal will be to investigate trends between halo 
-    properties and galaxy properties by measuring the weak lensing signal for samples 
-    binned by properties such as \minn{}, \mtot{}, cluster richness, and magnitude gap.
+    With the 2-D modeling approach, we can deal with the seeing and background
+    subtraction easier, and provide better maps the stellar mass distributions. 
+    We are also working on characterizing the color distributions of these 
+    galaxies better via multi-band modeling with reasonable constraints (e.g. 
+    \citealt{Huang2016}).
+
+    Primarily designed as a cosmological endeavor, the HSC survey has excellent 
+    images to greatly improve the the weak lensing analysis of massive galaxies. 
+    The next major step will be to investigate the connections between massive 
+    galaxies and their halos with the help of the weak lensing signals for 
+    different groups of massive galaxies (e.g. binned by \mtot{}, \minn{}, 
+    size\etal).
     Joining the stellar mass distributions and the weak lensing signals together, 
-    we can explore tracers that are sensitive to a range of physical processes 
+    we can trace the impacts from a series of physical processes 
     (strength and type of AGN feedback, merger rate, typical mass ratio of mergers
@@
     with predictions from cosmological hydro-simulations such as 
-    Illustris (\addref{}), Eagle (\addref{}), or \textit{Horizon-AGN}.
+    Illustris (\citealt{Vogelsberger2014}, \citealt{Genel2014}), 
+    EAGLE (\citealt{Schaye2015}, \citealt{Crain2015}), 
+    or \textit{Horizon-AGN} (\citealt{Dubois2014}).
 
@@
   % HSC part
-  The Hyper Suprime-Cam (HSC) collaboration includes the astronomical communities of Japan
-  and Taiwan, and Princeton University.  The HSC instrumentation and software were
+  The Hyper Suprime-Cam (HSC) collaboration includes the astronomical communities of 
+  Japan and Taiwan, and Princeton University.  The HSC instrumentation and software were
   developed by the National Astronomical Observatory of Japan (NAOJ), the Kavli Institute
@@
   the High Energy Accelerator Research Organization (KEK), the Academia Sinica Institute
-  for Astronomy and Astrophysics in Taiwan (ASIAA), and Princeton University.  Funding was
-  contributed by the FIRST program from Japanese Cabinet Office, the Ministry of
-  Education, Culture, Sports, Science and Technology (MEXT), the Japan Society for the
-  Promotion of Science (JSPS), Japan Science and Technology Agency (JST),  the Toray
-  Science  Foundation, NAOJ, Kavli IPMU, KEK, ASIAA, and Princeton University.
+  for Astronomy and Astrophysics in Taiwan (ASIAA), and Princeton University.  
+  Funding was contributed by the FIRST program from Japanese Cabinet Office, the Ministry 
+  of Education, Culture, Sports, Science and Technology (MEXT), the Japan Society for 
+  the Promotion of Science (JSPS), Japan Science and Technology Agency (JST), the
+  Toray Science Foundation, NAOJ, Kavli IPMU, KEK, ASIAA, and Princeton University.
 
@@
 	\label{app:basic}
-    \song{New appendix! Figure and caption also updated.}
-
+
+    \update{
     In the top-left figure of Fig.\ref{fig:sample_stats}, we show the \mtot{}-color 
@@
     the two samples overlap the most within $11.2 \le$\logmtot{}$\le 11.6$, but 
-    have quite different relative distributions.
-
+    have quite different relative distributions.}
+
+    \update{
     Due to the different sources of redshift for the \rbcg{} and \nbcg{} samples, 
@@
     We will address this via matching the two samples in both mass and redshift
-    distributions carefully before any comparison (see Appendix~\ref{app:match}).
+    distributions carefully before any comparison (see Appendix~\ref{app:match}).}
 
@@
       \includegraphics[width=16.5cm]{fig/redbcg_sample_stats}
-      \caption{\textbf{Top-left}: The \logms{}-$g-r$ color relation of the \rbcg{} 
+      \caption{
+          \update{
+          \textbf{Top-left}: The \logms{}-$g-r$ color relation of the \rbcg{} 
           (red circle; detaield format is the same with the right panel of 
@@
           Here the vertical lines highlight the 
-          $11.2<$\logminn{}$<11.6$ mass range that is used for comparison.
+          $11.2<$\logminn{}$<11.6$ mass range that is used for comparison.}
       }
@@
     \label{app:A}
-
-%% ------------------------------------------------------------------------------------ %% 
-    \figurenum{A1}
+%% ------------------------------------------------------------------------------------ %% 
     \begin{figure*}[hbt!]
@@
             with the one using the default configuration (black, solid line).}
+            \song{Figure will be updated}
         \label{figure:A1}
@@
 %% ------------------------------------------------------------------------------------ %% 
-    \figurenum{B1}
     \begin{figure*}[bt!]
@@
 %% ------------------------------------------------------------------------------------ %% 
-    \figurenum{B2}
     \begin{figure*}[hbt!]
@@
 %% ------------------------------------------------------------------------------------ %% 
-    \figurenum{B3}
     \begin{figure*}[hbt!]
@@
 %% ------------------------------------------------------------------------------------ %% 
-\figurenum{C1}
 \begin{figure*}[hbt!]
@@
     \includegraphics[width=\textwidth]{fig/redbcg_prof_gama_new}
-    \caption{\textbf{Left:} comparison of \mstar{} estimated by the GAMA survey and 
-    the ones in this work for the same galaxies. 
+    \caption{
+        \update{
+        \textbf{Left:} comparison of \mstar{} estimated by the GAMA survey and 
+        the \mtot{} using HSC images in this work. 
         We plot the \logmgama{} against the difference between \logmtot{} and \logmgama{}. 
-    The format is very similar to the right panel of Fig. \ref{fig:smf1}, except that
-    we color-code the \rbcg{} galaxies (orange-red) using the \ser{} index measured by 
-    GAMA using \galfit{} on SDSS image. 
-    The two vertical lines highlight the mass range $11.4 \leq$\logmgama{}$<11.9$ that
-    is used for the comparison later.~~
-    \textbf{Middle and Right figures:} we compare the \mden{} profiles of \rbcg{} 
-    (orange-red) and \nbcg{} (grey-black) galaxies using the samples matched on the 
+        The format is very similar to the left panel of Fig.\ref{fig:smf1}. 
+        The two vertical lines highlight the mass range $11.4 \leq$\logmgama{}$<11.8$ 
+        that is used for the comparison.~~
+        \textbf{Right:} we compare the \mden{} profiles of \rbcg{} (orange-red) and 
+        \nbcg{} (grey-black) galaxies using the samples matched on the 
         \mgama{}-$z$ plane at $11.4 \leq$\logmgama{}$<11.9$ and $0.28 \leq z < 0.4$. 
-    The formats for figure (b) and (c) are very similar to Fig.\ref{fig:prof_m100_A}.}
-    \label{figure:C1}
+        The format is very similar to the ones in Fig.\ref{fig:prof_1}.}
+        }
+    \label{fig:gama}
 \end{figure*}
@@
 
-    In Fig.~11, we show the individual profiles, median profiles along with their 
+    In Fig.\ref{fig:gama}, we show the individual profiles, median profiles along with their 
     uncertainties derived using 5000 times bootstrap resampling, and the relative 
@@
 %% ------------------------------------------------------------------------------------ %% 
-\figurenum{D1}
 \begin{figure}[htb!]
     \centering 
-    \includegraphics[width=8.5cm]{fig/average_mass_profiles_fsps1_B}
+    \includegraphics[width=13.0cm]{fig/redbcg_avg_prof_z}
     \caption{Comparison of \mden{} profiles of \rbcg{} (orange-red) and \nbcg{} 
@@
 
-%    \textbf{Left figure} shows the details of the \mtot{}-matching process.  
-%      On the top panel, we show the overall distributions of \rbcg{} (light orange boxes) 
-%      and \nbcg{} (light grey dots) galaxies on the \mtot{}-$z$ plane.  
-%      And, we match the two sample in the \mtot{}-$z$ space outlined by the shaded region.
-%      We highlight the \rbcg{} galaxies in this region using bigger boxes in red frames, 
-%      whose size reflects the $P_{\mathrm{Cen}}$ value.  
-%      We also color-code them using the richness ($\lambda$) of the host cluster. 
-%      The matched \nbcg{} galaxies are highlighted using darker color and bigger dots. 
-%      To further evaluate the matching results, we show the distributions of \mtot{} 
-%      (middle panel) and redshift (bottom panel) separately. 
-%      On both panesl, we show the histograms along with their kernel density 
-%      distributions.  
-%      And, on the top of each panel, two sets of short vertical lines highlight the median 
-%      value (solid) and the inter-quartile (dash) of each distribution.~~~
-
-    \song{Still need a figure and some adjustments}
+%% ------------------------------------------------------------------------------------ %% 
+\begin{figure*}[hbt!]
+    \centering 
+    \includegraphics[width=\textwidth]{fig/redbcg_match}
+    \caption{\textbf{Left figure} shows the details of the \mtot{}-matching process, 
+        corresponding to the results shown in the left figure of   
+        On the top panel, we show the overall distributions of \rbcg{} (light orange boxes) 
+        and \nbcg{} (light grey dots) galaxies on the \mtot{}-$z$ plane.  
+        And, we match the two sample in the \mtot{}-$z$ space outlined by the shaded region.
+        We highlight the \rbcg{} galaxies in this region using bigger boxes in red frames, 
+        whose size reflects the $P_{\mathrm{Cen}}$ value.  
+        We also color-code them using the richness ($\lambda$) of the host cluster. 
+        The matched \nbcg{} galaxies are highlighted using darker color and bigger dots. 
+        To further evaluate the matching results, we show the distributions of \mtot{} 
+        (middle panel) and redshift (bottom panel) separately. 
+        On both panesl, we show the histograms along with their kernel density 
+        distributions.  
+        And, on the top of each panel, two sets of short vertical lines highlight the median 
+        value (solid) and the inter-quartile (dash) of each distribution.~~~
+        \textbf{Right figure} shows the similar matching results for the \minn{}-matched
+        samples used for the right figure of Fig.\ref{fig:prof_1}.
+        The format is exactly the same as the left one, except the \minn{} replaces the 
+        \mtot{} in the top and middle panels.}
+    \label{fig:match}
+\end{figure*}
+%% ------------------------------------------------------------------------------------ %%
+
+    \song{Still need some adjustments}
 
@@
     range in radius, it is also important to make sure that differences in physical 
-    size of PSF (for more discussion on this issue, please see Appendix\ref{app:C}) 
+    size of PSF (for more discussion on this issue, please see Appendix.\ref{app:C}) 
     and imaging depth do not affect the result.    
@@
       	(grey-black) galaxies that are matched using proxies of total \mstar{}. 
-        The formats are in consistent with the right figure of Fig.\ref{fig:prof_m100_A}.
+        The formats are in consistent with the right figure of Fig.\ref{fig:prof_1}.
         The differences are, here, the samples are matched in slightly differnt ways. 
@@
         c) using \mstar{} within 150 kpc instead of 100 kpc.
-        The results are broadly consistent with the one in Fig.\ref{fig:prof_m100_A}.}
-      \label{fig:prof_m100_B}
+        The results are broadly consistent with the one in Fig.\ref{fig:prof_1}.}
+      \label{fig:prof_3} 
   \end{figure*}
@@
 %% ------------------------------------------------------------------------------------ %% 
-  \begin{figure*}[t]
+  \begin{figure*}[t!]
       \centering 
       \includegraphics[width=\textwidth]{fig/redbcg_prof_4}
-      \caption{Comparisons of unnormalized \mden{} profiles of 
-      	  $\log (M_{\star,100\ \mathrm{kpc}}/M_{\odot}>11.5$ \rbcg{} (orange-red) 
-      	  and \nbcg{} (grey-black) samples that are matched using \minn{}.
-          Except for the difference in \mtot{}-limit of both samples, other formats are 
-          the same with the middle figure of Fig.\ref{fig:prof_m10_A}.
-          \song{Update the figure, but need to work on text and caption.}
-          }
-      \label{fig:prof_m10_B}
+      \caption{Comparisons of the \mden{} profiles for \rbcg{} (orange-red) and \nbcg{} 
+          (grey-black) galaxies that are matched using the \mstar{} enclosed in the 
+          inner region. 
+          Left panel shows the results after matching the \minn{} and \meff{} together, 
+          and the right panel shows the results when only the \logmtot{}$\ge 11.5$
+          \rbcg{} and \nbcg{} galaxies are included.
+          Other formats are in consistent with the right figure of Fig.\ref{fig:prof_1}.}
+      \label{fig:prof_4} 
   \end{figure*}
@@
 
-\song{To be updated}
-
 %% ------------------------------------------------------------------------------------ %%

### 2017-01-16 draft/ms_v2.tex
New Tex draft

--- 2016-12-06 draft/ms_v1.tex
@@
 \DeclareGraphicsExtensions{.pdf,.png,.jpg}
-\input psfig.tex
 
@@
 \newcommand{\alexie}[1]{\textcolor{blue}{\textbf{[Alexie: #1]}}}
-\newcommand{\kevin}[1]{\textcolor{green}{\textbf{[Kevin: #1]}}}
+\newcommand{\rewrite}[1]{\textcolor{green}{\textbf{[Rewrite: #1]}}}
+
 \newcommand{\update}[1]{\textcolor{Bittersweet}{#1}}
+%\newcommand{\update}[1]{#1}
 
@@
 
-\title{First Detection of the Environmental Dependence of the Structures of Massive Galaxies }
+\title{Environmental Dependence of the Structures of Massive Central 
+       Galaxies at $z=0.4$ ....... or ... A Detection of the Enviromental Dependence of The Stellar Halos of Massive Galaxies}
 
@@
 
-    Although the environmental dependence of structures for massive central 
-    galaxies is predicted by the promising hierarchical assembly model, 
-    observations at low redshift seem to find no convincing evidence for that. 
-    With the help of deep $i$-band images of a large sample of massive central 
-    galaxies at $0.3 < z < 0.5$ from the Subaru Hyper Suprime-Cam (HSC) survey, 
-    we map their stellar mass distributions out to radius larger than $100$ kpc, 
-    and discover subtle, but systematic and robust structural differences that 
-    depend on halo mass. 
-    At fixed stellar mass within 100 kpc, the massive central galaxies in more 
-    massive ($M_{200m} > 1.6\times 10^{14} M_{\odot}$) halos have a 
-    slightly flattened inner profile within $\sim 15$-$20$ kpc, and a more prominent 
-    outer envelope compared to ones in less massive 
-    ($M_{200m}>8.7\times 10^{13} M_{\odot}$) halos.
-    For centrals with $M_{\star} > 10^{11.5} M_{\odot}$, the ones in more massive 
-    halos show very significant excess of mass in the outskirt when the two samples 
-    are matched using proxies of mass assembled at $z > 1$. 
-    Such differences are broadly consistent with richer recent merging history 
-    for more massive halos. 
-    We suggest that the relation between total stellar mass and mass within inner 5 
-    or 10 kpc is potentially interesting for diagnosing the role played by host halo 
-    in shaping the structures of massive central galaxies. 
-    These results also highlight the importance of deep photometry and the usage of 
-    detailed structural information in the study of the assembly history of galaxies.
+    The promising hierarchical assembly scenario of massive galaxies suggest the 
+    structure of these galaxies should depend on their environments or halo mass.
+    Yet, at low redshift, observations find no clear evidence for that. 
+    Here, using the deep images from the Subaru Hyper Suprime-Cam (HSC) survey,
+    we map the stellar mass distributions of massive galaxies at $0.3 < z < 0.5$ 
+    out to the very outskirt, and detect subtle, but robust structural differences 
+    that depend on halo mass for central galaxies at high mass end. 
+    With the help of the \redm{} catalog, we separate these massive galaxies 
+    into centrals of halos that are more and less massive than 
+    $M_{200m}\sim 10^{14} M_{\odot}$.
+    For centrals with similar stellar mass within 100 kpc, the ones from 
+    more massive halos on average have slightly more flattened inner profile 
+    within $\sim 10$-$20$ kpc, and more prominent outer envelope.
+    Meanwhile, when matched at the same stellar mass within inner 10 kpc--a 
+    proxy of the mass of the in-situ component, the massive centrals of more  
+    massive halos show much more significant outer stellar envelopes.    
+    We also see that these two samples of massive galaxies follow slightly 
+    different mass-size relation and the relationship between the stellar mass 
+    within 100 and 10 kpc.
+    Such differences in structure are broadly consistent with the expectation that
+    central galaxy from more massive halo should have more complex merging history.
+    These results highlight the importance of deep photometry in the study of 
+    the assembly history of massive galaxies.
 
@@
       \includegraphics[width=\textwidth]{fig/redbcg_m100_m10_compare}
-      \caption{Three-color images for a subsample of massive galaxies at similar redshift
-      		($\sim 0.4$), and with similar \mstar{} inside inner 10 kpc (indicated by the 
+      \caption{Three-color images for a subsample of massive galaxies at $z\sim 0.4$, and with similar values for their stellar masses within a fixed 10 kpc radius (indicated by the 
             dash-line cicle on top-left figure; 
             $11.2<\log (M_{\star,10\ \mathrm{kpc}}/M_{\odot})<11.3$).
-            However, they span quite a large range in \mstar{} within 100 kpc 
-            (highlighted by the solid bar on the top-left figure). 
-            From top-left to bottom-right, their \mtot{} increases from 
-            $10^{11.2} M_{\odot}$ to $10^{11.7} M_{\odot}$.
-            The three galaxies from \rbcg{} sample are highlighted via red frames.
+Galaxies are rank ordered from top to bottom and from left to right by their mass within 100 kpc which varies from $10^{11.2} M_{\odot}$ to $10^{11.7} M_{\odot}$.
+At fixed "inner" mass $M_{\star,10}$, massive galaxies display a large diversity in their outer profiles.
+Red boxes indicate galaxies in halos more massive then xxxxx.
 }
@@
         \caption{Left: example of the 1-D surface brightness and ellipticity profile 
-            for a massive galaxy at $z=0.23$ in $i$-band using \texttt{Ellipse}. 
-            In this work, we always show the radial profile in $R^{1/4}$ scale as it 
-            is the most appropriate one to show the structural details of massive 
-            ETGs at both inner and outer regions. 
-            The dash-line shows the surface brightness profile after correcting the 
-            background. 
+            for a massive galaxy at $z=0.23$ in the $i$-band using \texttt{Ellipse}. 
+            In this work, we always show the radial profile using a $R^{1/4}$ scaling on the x-axis.
+By using this scaline, ETGs that follow exact de Vaucouleurs profiles with have luminosity profiles that appear on stright lines in our Figures.
+The dash-line shows the surface brightness profile after correcting the background \alexie{no dashed line?}.
 We also plot the brightness profile of the PSF model normalized at the
             central surface brightness of the galaxy to highlight the region affected 
-            by seeing. 
+            by seeing. The grey shaded region highlights the region most affect by seeing ($r<$xxx kpc).
             On the top panel, the dash line shows the ellipticity used for the final 
-            isophote.~~~ 
-            Right: the masked $i$-band image of this galaxy with the isophotes extracted 
-            by \texttt{Ellipse} overlaid. 
-            The thick, green isophote highlights the one with $\mu_{i}\sim 28.5$~\sb.}
-            \song{Will update completely, takes a little bit longer}
+            isophote. Right: the masked $i$-band image of this galaxy with the isophotes extracted 
+            by \texttt{Ellipse}. The thick dotted line highlights the isophote with $\mu_{i}\sim 28.5$~\sb.}
             %\alexie{Can we add physical radii at the top left since $R^{1/4}$ is not 
@@
     Mauna Kea. 
-    This ambitious multi-layer photometric survey takes advantage of the large field of 
-    view (FoV;~1.5 deg in diameter) of HSC and will cover $\sim 1400$ deg$^2$ of sky in 5
-    broad bands (\textit{g r i z Y}) to the depth of $r \sim 26$ mag in the \texttt{WIDE}. 
+    The ambitious multi-layer HSC survey takes advantage of the large field of 
+    view (FoV;~1.5 deg in diameter) of this camera and will cover $\sim 1400$ deg$^2$ in 5
+    broad bands (\textit{g r i z Y}) to a limting depth of $r \sim 26$ mag in the \texttt{WIDE} layer. 
     This work is based on the internal data release \texttt{S15B}, which covers 
-    $\sim 100$square of degree of sky in all 5-band to full \texttt{WIDE} depth.  
+    $\sim 100$square of degree in all 5-band to full \texttt{WIDE} depth.  
     The regions covered by this release overlap with a number of spectroscopic surveys 
@@
     than SDSS. 
-    Combined with the excellent imaging resolution (median $i$-band seeing is 0.6"), 
-    and the wide area, this makes the HSC wide layer a tremendous data set to perform a 
-    large statistical study of surface brightness profiles of ETGs out to large radii. 
-    Fig.\ref{fig:sdss_compare} illustrated the quality of HSC imaging compared to SDSS 
-    for a sample of low redshift ETGs. 
-    Fig.\ref{fig:sdss_compare} clearly demonstrates that the HSC Wide survey is well 
-    suited for mapping the stellar distribution of massive galaxies out to large radii 
-    and will be a powerful data set to explore the assembly history of ETGs.
-
-	The HSC $i$-band images typically have the best seeing in all five bands because of 
-    strict requirements determined by weak lensing science. 
+    Combined with the excellent imaging resolution (the median $i$-band seeing is 0.6"), 
+    and the wide area, the HSC survey represents a tremendous data set to perform a 
+    large statistical study of the surface brightness profiles of ETGs out to large radii. Fig.\ref{fig:sdss_compare} illustrates the quality of HSC imaging compared to SDSS 
+    for a sample of low redshift ETGs and shows that HSc survey data are well 
+    suited for mapping the stellar distribution of massive galaxies out to large radii.
+
+	HSC $i$-band images typically have the best seeing comapred to other bands because of 
+    strict requirements driven by weak lensing science. 
     We will therefore use the $i$-band images to measure the stellar distributions of 
@@
 %% ------------------------------------------------------------------------------------ %% 
-\subsection{The HSC galaxy catalog and photometry measurements}
+\subsection{HSC Data Processing}
     \label{sec:pipeline}
 
-    The HSC SSP data are processed with \texttt{hscPipe 4.0.1}, a derivative of the Large 
+The full details of the HSC data processing can be found in \citet{BoschInPrep} and are briefly summarized here. The HSC SSP data are processed with \texttt{hscPipe 4.0.1}, a derivative of the Large 
     Synoptic Survey Telescope (LSST) pipeline (e.g.\ \citealt{Juric2015}; 
@@
     (bias subtraction, flat fielding, background modeling, object detection and 
-    measurements). 
-    Then pipeline perform astrometric and photometric calibration for each single 
-    expoures. 
-    After that, the \texttt{hscPipe} warp different exposures on to a common
-    World Coordinate System (WCS), combine them into coadded images with improved 
-    signal-to-noise ratio ($S/N$), and update the images with better astrometric and 
-    photometric calibrations at the same time using the common stars among different
-    exposures.
-    The pixel scale of the combined images is $0.168^{\arcsec}$.  
-    The photometric calibration is based on data from the Panoramic Survey Telescope 
+    measurements). Astrometric and photometric calibration is performed at the single exposure level. \texttt{hscPipe} then warps different exposures on to a common
+    World Coordinate System (WCS) and combines them into coadded images. At this stage, \texttt{hscPipe} updates the images with a better astrometric and 
+    photometric calibration using stars that are common among between exposures.
+
+    The pixel scale of the combined images is $0.168^{\arcsec}$. Photometric calibration is based on data from the Panoramic Survey Telescope 
     and Rapid Response System (Pan-STARRS) 1 imaging survey 
@@
     To achieve consistent deblending and photometry across all bands, \texttt{hscPipe} 
-    performs multi-band post-processing at the coadd level. 
-    First, the \texttt{hscPipe} performs object detection again on the coadd images
-    in each band independently, and identify the above-threshold region (referred as 
-    ``footprint'') and the flux peak within it for each source. 
-    ``footprints'' and peaks from different bands are then merged together before 
-    the \texttt{hscPipe} deblend and measure them in each band. 
-    Later, \texttt{hscPipe} selects a ``reference band'' for each object based on the 
-    $S/N$ in different bands (for most galaxies in this work, it is the $i$-band). 
+    performs multi-band post-processing at the coadd level. First, \texttt{hscPipe} performs object detection on coadd images
+    in each band independently and for each source records the flux peak and the above-threshold region (referred as 
+    a ``footprint'').
+Next, ``footprints'' and peaks from different bands are merged together before performing deblending and measurements.
+Finally, \texttt{hscPipe} selects a ``reference band'' for each object based on the
+    $S/N$ in different bands (for most galaxies in this work, the reference band is the $i$-band). 
     After fixing the centroids, shape, and other non-amplitude parameters of each 
     object in this reference catalog, \texttt{hscPipe} perform forced photometry 
-    on the coadd image in each band.
-    The PSF and galaxy model fluxes measured in the forced photometry approach are the
-    best for color measurements.  
-    Please refer to \citet{BoschInPrep} for more details of the \texttt{hscPipe} and 
-    the multi-band processing method.
-
-    The HSC \cmodel{} algorithm is similar to the SDSS \cmodel{} one.  
-    It fits the flux distribution of an object using a combination of de~Vaucouleur and 
-    exponential components after considering the PSF convolution.  
-    For more details about the algorithm, please see Bosch\etal~in prep.~.
-    We have tested its performance using synthetic objects (Huang\etal~in prep.~), and 
+    on the coadd image in each band. This forced photometry approach is optimized to yield accurate galaxy colors.
+
+    For each galaxy, \texttt{hscPipe} measures a \cmodel{} magnitude using an approach that is similar to SDSS (\ref{}) (Bosch\etal~in prep.~).
+However, as opposed to SDSS, the HSC \cmodel{} is based on forced photometry which means that it can be used to accurately measure both the \textit{fluxes and colors of galaxies}.
+The HSC \cmodel{} algorithm fits the flux distribution of each object using a combination of a de~Vaucouleur and
+    an exponential component and accounts for the PSF. The performance of this algorithm has been testing using synthetic objects (Huang\etal~in prep.~) and 
     the results indicate that, generally speaking, the HSC \cmodel{} photometry is 
     accurate down to $i >25.0$ mag.  
-    However, for massive ETGs with extended stellar distributions, \cmodel{} currently 
-    systematically underestimates their total flux.
-    This problem indicates the intrinsic limitation of \cmodel{} as it is incapable of
-    modeling profiles that are extremely extended in the outskirt at the depth of 
-    HSC survey. 
-    At the same time, issues with the deblender also worsen the situation. 
-    As the image becomes much deeper, it also significantly increases the fraction 
-    objects that are blended with others, and makes reliable deblending process 
-    a very challenging problem especially for massive ETGs where satellites and 
-    background galaxies often blend with the low surface brightness stellar envelope.
-    To make sure the reliable detection of faint objects close to the detection limit, 
-    the deblending method implemented by the \texttt{hscPipe} now tends to 
-    ``over-deblend'' the surrounding areas of bright galaxies, and further results in 
-    under-estimated total flux of massive ETGs (more discussion in 
+    However, \cmodel{} currently systematically underestimates the total fluxes of massive ETGs with extended stellar distributions.
+This problem indicates an intrinsic limitation of \cmodel{} as it is incapable of
+    modeling profiles with extremely extended outskirts, a problem that is exacerbated at the depth of 
+    the HSC survey.
+In addition, at the depth of the HSC survey, accurate deblending in the vicinity of large ETGs where satellites and background galaxies often blend with the low surface brightness stellar envelope is a challenign problem.
+The deblending method implemented by the \texttt{hscPipe} currently tends to
+    ``over-deblend'' the outskirts of bright galaxies and leads to un under-estimation of the the total flux of massive ETGs (more discussion in 
     Bosch\etal~in prep.~).
-    For these reasons, we will perform customized photometric measurements to derive 
-    more accurate total luminosity and stellar mass. 
-    We only use the HSC \cmodel{} photometry in the initial selection of parent 
-    sample.
+For these reasons, our results will be based on custom developed code to measure the luminosities and stellar masses of massive galaxies.
+We use the HSC \texttt{hscPipe} photometry for two purposes: 1) to perform a first broad sample selection, and 2) for galaxy colors.
+\alexie{Shouldn't we be using the aperture photometry here ????
+Are we doing teh right thing here??
+Please check.
+Need a simple sanity check to show that the resutls are robust.
+Check using your own color estimates?}.
 
@@
 
-    Because of the caveats that apply to \texttt{hscPipe} measurements for bright 
-    galaxies, we will use custom made software to measure the luminosity profiles of
-    massive galaxies. 
-    \update{
-    As the first step, we select the initial sample of massive galaxies at $z < 0.5$
-    from the HSC photometric catalog.}
-    We will then use custom made software to re-measure luminosities for all galaxies 
-    in this sample. 
-    Based on Leauthaud\etal~(2016), most \logms{}$\geq 11.5$ galaxies should have 
-    $i_{\mathrm{SDSS, cModel}} \leq 21.0$ mag.
-    So we first select all galaxies with $i_{\mathrm{HSC, cModel}} \leq 21.5$ 
+    \alexie{Try to be more succinct and improve the logical flow in sections 2.3, 2.4, and 2.5. Readers don't care about the process! You should be able to trim these sections.}
+
+    \alexie{We never say anything about Spirals? Are all galaxies in this selection early types? Are there any extra morphology cuts? We need to mention this somewhere.}
+
+    \update{
+    We begin by using a broad luminosity cut to select an initial sample of massive galaxies at $z < 0.5$
+    from the HSC photometric catalog.} Based on Leauthaud\etal~(2016), galaxies with \logms{}$\geq 11.5$ have 
+    $i_{\mathrm{SDSS, cModel}} \leq 21.0$ mag. We therefore select our initla smaple to be brighter than  $i_{\mathrm{HSC, cModel}} \leq 21.5$ 
     \footnote{We neglect the insignificant differences between the response curves of
-    SDSS-$i$ and HSC-$i$ filters}
-    in regions that have reached the required depth of \texttt{WIDE} survey in all 
+    SDSS-$i$ and HSC-$i$ filters} and also limit our sample to regions that have reached the required depth of the \texttt{WIDE} survey in all 
     five bands. 
@@
 
-    We select extended objects that have no error in deblending process, well defined 
-    centroids, and \texttt{cModel} magnitudes in all five bands. 
-    After removing the objects that have pixel affected by saturation, cosmic-ray, and 
-    other optical artefact \footnote{each criterion affects less than 8\% of the entire
-    sample}, we select 1760845 galaxies that will be referred as \texttt{hscPho}. 
+    We further select extended objects with no deblending errors, with well defined 
+    centroids, and with \texttt{cModel} magnitudes in all five bands. 
+    After removing objects that have pixels affected by saturation, cosmic-rays, or 
+    other optical artefact \footnote{each criterion removes less than 8\% of the entire
+    sample} \alexie{Actually, 8 percent is not small if we want to condsider the number densities.
+Let's re-evaulate the impact of these cuts for the 16B data with FDFC}.
+This sample corresponds to 1760845 galaxies and will be referred as \texttt{hscPho}.
+
     %% Saved as "dr1_wide_galaxy_hscPho.fits"
 
-    As reliable photometric redshift using HSC photometry is still a working progress, 
-    we only use objects with either available spectroscopic redshift or robust 
+    We limit our study to the very high mass end where a majority of galaxies have either a  spectroscopic redshift or a robust 
     red-sequence photo-$z$ from the \redm{} catalog (see Section \ref{ssec:redmapper}).  
-    We first match the \texttt{hscPho} sample with the external spec-$z$ catalog 
-    compiled by the HSC database\footnote{It is created by matching HSC objects with 
-    public data of several spectroscopic surveys (e.g.\ SDSS/BOSS; GAMA). 
-    Duplicated matches from different sources are merged through internal matching 
-    using $0.5^{\arcsec}$ radius. 
-    For each object, the quality information of the spec-$z$ from different catalogs 
-    are homogenized into a single flag that indicates whether the redshift is secure, 
-    and only secure spec-$z$ are used in this work.}
+    We match the \texttt{hscPho} sample with a spec-$z$ catalog 
+    compiled by the HSC team\footnote{It is created by matching HSC objects with all publicly available spectroscopic redshifts (e.g.\ SDSS/BOSS; GAMA).
+The spec-z quality flag from different catalogs
+    are homogenized into a single flag that indicates whether the redshift is secure (\ref{} Cite a paper from the photo team where this is described?).
+Only galaxies with secure spec-$z$s are used in this work \alexie{Ned to be precise here.
+We also use redshifts from redmapper so this statement isn;t quite right}}.
+To ensure reasonable
+    \mstar{}-completeness at the high-\mstar{} end we focus on the redshift range $0.3 \leq z \leq 0.5$. 
     %% This is catalog: "dr1_specz_use.fits"
-    using $1.0^{\arcsec}$ radius.
-    At $0.2 \leq z \leq 0.5$, most redshifts in the HSC spec-$z$ catalog come from 
-    SDSS/BOSS and GAMA surveys.  
-    The BOSS survey provides the majority of spec-$z$ in this work.  
-    Due to the complex selection criteria for different subsamples within the BOSS
-    survey (e.g.\ the \texttt{LOWZ} and \texttt{CMASS}), it is not easy to estimate 
-    its \mstar{} completeness.  
-    Recently, through comparing with the deeper Stripe 82 Massive Galaxy Catalog
-    (\texttt{S82-MGC}; \citealt{Bundy2015}), \citet{Leauthaud2016} suggests that the 
-    BOSS spec-$z$ is about 80\% complete at \logms{}$\geq 11.6$ at $0.3 < z < 0.5$. 
-    The GAMA survey, which partially overlaps with the HSC footprint, provides 
-    additional 14\% unique spec-$z$. 
-    Based on \citet{Taylor2011} (e.g.\ their Fig.~6), at $z\sim 0.3$, the GAMA 
-    sample is 80\% complete down to $10^{10.8}$\msun; but only 80\% complete to 
-    $10^{12.0}$\msun at $z\sim 0.5$. 
-    Despite the difference in \mstar{} estimates, we can expect 
-    our sample should be quite complete above \logms{}$\geq 11.5$-$11.6$.
-    We will further address the issue of \mstar{}-completeness more carefully 
-    using the common sample with \texttt{S82-MGC} (see Section\ref{ssec:s82}).
-
-    Among the 116813 matched objects, 42696 are at $0.2 \leq z \leq 0.5$.
-    %% Saved as "dr1_wide_galaxy_icmodel_21.5.fits"
-    The majority of these redshifts come from either SDSS or BOSS data.  
-    GAMA survey contributes another $\sim 14$\%. 
-    For objects without external spec-$z$, we match them with the central galaxies 
+
+        \alexie{Please rewrite the section below.
+It would be better to first say that you further supplements with redmapper redshifts.
+And then simply quote the overall number at the end after making the redshift cut.
+Need to work on logical flow of text!}.
+
+  In addition to the specz-s mentioned above, we also include objects which have a red-sequence photo-$z$ from the \redm{} catalog within the range $0.2 \leq z \leq 0.5$ .........and need to say one sentance about the accuracy of the red sequence redshifts and why this is tolerable for our work
+
+    \rewrite{For objects without external spec-$z$, we match them with the central galaxies 
     from \redm{} catalog using $2.0^{\arcsec}$ radius. 
@@
     $0.2 \leq z \leq 0.5$
-    (will be referred as \texttt{hscZ}).
-    As we will mention at the end of the paper, to ensure reasonable 
-    \mstar{}-completeness at the high-\mstar{} end, and make sure the samples we 
-    want to compare have well overlapped redshift distributions, we will focus on 
-    the galaxies at $0.3 \leq z \leq 0.5$.
+    (will be referred as \texttt{hscZ}).   From our initial sample, 42696 are at $0.2 \leq z \leq 0.5$.}
+    %% Saved as "dr1_wide_galaxy_icmodel_21.5.fits"
+
+    The BOSS and SDSS "legacy" LRG samples provide the majority of spec-$z$ for this work. By comparing with the Stripe 82 Massive Galaxy Catalog
+    (\texttt{S82-MGC}; \citealt{Bundy2015}), \citet{Leauthaud2016} have measured the stellar mass completness of the combined BOSS and SDSS samples.
+They estimate that the BOSS spec-$z$ is about 80\% complete at \logms{}$\geq 11.6$ at $0.3 < z < 0.5$.
+The GAMA survey, which partially overlaps with the HSC footprint, supplements our spec-z sample by 14\%.
+\alexie{and redmapper redshifts add another xx percent.} Based on \citet{Taylor2011} (e.g.\ their Fig.~6), at $z\sim 0.3$, the GAMA
+    sample is 80\% complete down to $10^{10.8}$\msun; but only 80\% complete to 
+    $10^{12.0}$\msun at $z\sim 0.5$.
+We can therfore expect our sample to be roughly stellar-mass complete above \logms{}$\geq 11.5$-$11.6$.
+This question will be addressed more carefully using the overlap region between HSC and the \texttt{S82-MGC} in Section\ref{ssec:s82}.
 
@@
 
-    In this paper, our study focuses on galaxies which are located at the center of
+    Our study focuses on galaxies which are located at the center of
     their dark matter halos. To limit our sample to central galaxies, we use 
@@
     For each cluster, the catalog provides a photometric redshift estimate $z_{\lambda}$, 
-    a richness $\lambda$, and identified the most likely central
-    galaxy (this is the galaxies with the highest value of the central probability 
+    a richness $\lambda$, and identifies the most likely central
+    galaxy (this is the galaxy with the highest central probability value
     $P_{\mathrm{Cen}}$).
-    A list of member galaxies for each cluster, and associated membership probabilities, 
-    is also provided. 
+The \redm{}{} catalog also provides a list of member galaxies for each cluster and associated membership probabilities.
 Details about the performance of the \redm{}~cluster catalog can be found in
@@
     The results of these studies are in good agreement and indicate that clusters 
-    identified by \redm{}~($\lambda > 20$) have $\log (M_{200,c}/M_{\odot}) \geq 14.0$. 
-    Therefore, the \redm{} catalog helps us group the massive central galaxies into 
-    samples with different average \mhalo{}.  
-    And, to select reliable candidates of central galaxies, we only include the ones 
-    with high probability of being the central galaxy ($P_{\mathrm{CEN}} \geq 0.7$).
+    identified by \redm{}~ with $\lambda > 20$ have $\log (M_{200m}/M_{\odot}) \geq 14.0$. 
+    Therefore, the \redm{} catalog helps us group massive central galaxies into samples with different average \mhalo{}.
+\alexie{Here is looks like you are making a cut on pcen.
+But what about galaxies that are not in these clusters?
+You do not have a pcen value!
+So this phrase needs to be rewritten or moved elsewhere.}\rewrite{To select reliable candidates of central galaxies, we only include the ones
+    with high probability of being the central galaxy ($P_{\mathrm{CEN}} \geq 0.7$)}.
 
     Although the \redm{} catalog provides us a good sample of central galaxies in 
-    massive halos, the typical uncertainty of $\lambda$ estimate is still at 
+    massive halos, the typical uncertainty of $\lambda$ estimate is still at the
     $\sim 5$-10 level.  
     In addition, due to the depth and resolution of SDSS images, the \redm{} catalog 
-    becomes slightly incomplete at lower richness ($\lambda < 40$) end at $z > 0.33$.
-    To reduce the impacts from uncertain richness and incomplete selection of 
-    massive halos, we will focus on a sample of central galaxies in halos with 
+    becomes slightly incomplete at lower richness ($\lambda < 40$) at $z > 0.33$.
+    To reduce the impact of this effect, we will focus on a sample of central galaxies in halos with 
     $\lambda > 30$. 
-    This will also help up enhance the \mhalo{} contrast in the structural comparison.     
-    Based on the calibration in \citet{Simet2016}, the $\lambda \geq 20$ sample should
-    have halo mass ($M_{200m}$) more massive than $10^{14.0} M_{\odot}$.  
-    For the $\lambda \geq 30$ sample, they should live in halo more massive than
-    $10^{14.2} M_{\odot}$ using the same calibration. 
-    And, we can confirm that the results presented later do not depend on the choice 
-    of $\lambda$ boundary here. 
+    Based on the calibration of \citet{Simet2016}, the $\lambda \geq 30$ sample should
+    have halo mass ($M_{200m}$) more massive than $10^{14.2} M_{\odot}$. We have checked that none of our results depend on this choice of the $\lambda$ boundary.
+
     For the massive central galaxies that are not in these cluster-level halos, 
@@
     to assume they should have $\log (M_{200m}/M_{\odot}) < 14.0$.
-    %\textcolor{red}{but sometimes we make cuts at $\lambda<20$ and $\lambda>30$. 
-    %Is it confusing to have several different thresholds? Need to give a Motivation 
-    %for using different numbers here.}
 
@@
 %% ------------------------------------------------------------------------------------ %% 
-\subsection{Massive Central Galaxies from Low and High Mass Halos}
+\subsection{Massive Central Galaxies in Low and High Mass Halos}
     \label{ssec:mass_central}
+
+    \alexie{This section can be synthesized and condensed. Try to be more succinct!}
 
@@
     the \mhalo{} of \logms{}$ > 11.0$ galaxies has a large scatter at fixed \mstar{}.
-    Although we can not yet measure \mhalo{} individually, we can still broadly 
-    separate them into galaxies in small groups (\logmh{}$<14.0$) and 
-    large groups/clusters (\logmh{}$>14.0$), and investigate the 
-    ``environmental''-dependence of their structures.
+This means that our sample of massive galaxies spans a wide range of halos masses.
+We use the \redm{} catalog to separate our sample into two samples with halos masses above and below \logmh{}$<14.0$ \alexie{14.2 no?}.
 
@@
     %% Saved as "dr1_redbcg_hsc_sdss_gama_1arcsec.fits"
-    Firstly, we match the \texttt{hscZ} sample with the massive central galaxies of 
-    \redm{} clusters with $\lambda \geq 20$ and $P_{\mathrm{0.7}} \geq 0.7$ using 
-    $1.0^{\arcsec}$ radius. 
-    This step finds 375 matched galaxies at $0.2 \leq z \leq 0.5$ 
+
+   We match the \texttt{hscZ} sample with the massive central galaxies of 
+    \redm{} clusters with $\lambda \geq 20$ \alexie{20 or 30... confusing here} and $P_{\mathrm{0.7}} \geq 0.7$ using 
+    $1.0^{\arcsec}$ radius \alexie{mathcing radius not important}.
+
+     \alexie{confusing paragraph.
+The remapper redshift accuracy should be moved to the specz section.
+Why do we care about the number above 0.3?
+I'd remove those kind of details, they just make the reader confused.}
+
+    \rewrite{This step finds 375 matched galaxies at $0.2 \leq z \leq 0.5$ 
     (among them 282 are at $0.3 \leq z \leq 0.5$).  
@@
     Therefore, the current \rbcg{} sample is not dominated by very massive clusters 
-    with \mhalo{}$>10^{15} M_{\odot}$.  
+    with \mhalo{}$>10^{15} M_{\odot}$.  }
     %% Saved as "dr1_redbcg_use_sed5b.fits"
 
-    Assuming that the \redm{} catalog correctly identifies all halos with 
+    \rewrite{Assuming that the \redm{} catalog correctly identifies all halos with 
     $M_{200m}\sim 1.0\times 10^{14} h^{-1} M_{\odot}$ in the current footprint,
@@
     At $0.3 < z < 0.5$, such uncertainty is between 0.015 to 0.025, which are more than 
-    enough to exclude cluster member.}
-    \song{The actual number waits to be updated}
+    enough to exclude cluster member.}}
+    % TODO: The actual number waits to be updated}
 
@@
 
-    In summary, from the $\sim 100$ deg$^2$ deep HSC images, we select a large sample
+    Using $\sim 100$ deg$^2$ of HSC data, we select a large sample
     of massive central galaxies with reliable redshift information, and broadly separate 
-    them into two groups with different \mhalo{}.  
-    To help you go through the results, here are a few key points to keep in mind:
+    them into two groups with different \mhalo{}. The following is a summary of our sample construction.
 
@@
             candidates of central galaxies in halos with \logmh{}$<14.0$.  
-        \item To compare the \rbcg{} and \nbcg{} samples carefully, we will focus on 
-            the redshift range at $0.3 \leq z \leq 0.5$ where their redshift 
-            distributions greatly overlap and both samples have acceptable
-            \mstar-completeness (see Section \ref{ssec:s82}).  
-            \update{Although we use the $\lambda > 30$ sample for structural comparison, 
-            in the Appendix.\ref{app:robust}, we show that the results will not change 
-            if we include central galaxies of $20 < \lambda \leq 30$ clusters in the 
-            \rbcg{} sample.}
     \end{itemize}
+
+We now proceed to measure the luminosities and stellar mass profiles for all galaxies in this sample.
 
@@
     one-dimensional stellar mass density (\mden{}) profiles, we perform elliptical 
-    isophotes fitting using the IRAF task \texttt{Ellipse} (Jedrzejewski 1987).  
+    isophotes fitting using the IRAF \texttt{Ellipse} algorithm (Jedrzejewski 1987).  
     Compared to the popular two-dimensional model fitting method, the isophote fitting
-    approach is much less sensitive to the choice of model, number of components, 
+    approach is insensitive to the choice of a model (one versus two sersics for example), the number of components, 
     and the initial guesses of free parameters.
-    It is also less affected by the uncertainty of sky background subtraction.  
+It is also less affected by uncertainties related to background subtraction.
 This is particularly important for the massive ellipticals in our sample.
-    The much deeper HSC image reveals significantly more extended structures, 
-    while also make it inappropriate to fit these galaxies with simple model like 
-    the de~Vaucouleurs model or single \ser component model. 
-    Such models fail to fit the central region and the stellar halo of massive 
-    galaxies simultaneously, and also can not account for the radial variation of 
-    ellipticity and position angle. 
-    In principle, such massive galaxies can still be described using more complex 
-    models (e.g \citealt{Huang2013a}; \citealt{Huang2013b}).  
-    However, they are still very sensitive to background subtraction. 
-    And it becomes even more difficult to choose initial parameters, and investigate
-    the degeneracies among parameters. 
-    Although it is certainly worth exploring in the future, we decide that the 1-D 
-    method suits the goal of this work better.
-
-    We first prepare large $i$-band cut-out images around these massive galaxies 
-    that cover at least 750 kpc in radius, along with the bad pixel masks, and the 
-    PSF model reconstructed using the central coordinates. 
-    While they include all the visible light of the galaxy, they also leave enough 
-    space to evaluate the background subtraction. 
-    We choose to use $i$-band images not only considering their excellent seeing
-    condition, but also because they trace the stellar distributions of massive 
-    galaxies at $0.3 \leq z \leq 0.5$ reasonably well (fall between rest-frame $g$ 
-    and $r$ band), and they suffer less from background uncertainty, which is crucial 
-    for studying the outskirt of massive ETGs.  
-    Although $z$ and Y-band should be better \mden{} tracer, the sky background 
-    is much higher and the seeing is considerably worse on average.
-
-    Secondly, using the \texttt{SEP} Python library, we perform \texttt{SExtractor}-like
-    background estimation and object detections using different configurations to 
-    overcome the ``over-deblending'' challenge met by the \texttt{hscPipe}. 
-    Combining detections using different backgrounds and $S/N$ thresholds, 
-    we correctly obtain the footprints of all objects, even of the ones that are 
-    very close to the center of bright galaxies.
-    For the rest objects, we convert their footprints into a mask image for the
-    \texttt{Ellipse} procedure after increasing their sizes adaptively based on the 
-    brightness and distance to the massive galaxy. 
-    We achieve this via convolving the individual footprint with a Gaussian kernel
-    so that we can conservatively exclude pixels affected by this object while still 
-    making the mask follow the shape of the object. 
-    Meanwhile, we create a more aggressive mask of \emph{all} objects in the same 
-    approach, median-rebin the remaining pixels using a $6x6$ pixels box, and take 
-    the peak value (or mode) of the distribution of these rebinned ``sky'' pixels 
-    as the average background value around these bright galaxies.
-    As expected, we often found slightly negative value that indicate over-subtraction 
-    of background at certain degree. 
+Massive ETGs imaged at the depth of HSC are not well modeled by simple models such as the de~Vaucouleurs model or a single \ser component model.
+These models will fail to simultaneously capture the profile in both the inner and the outter region and these models also cannot account for any radial variations in ellipticity and position angle.
+In principle, massive galaxies can still be described using more complex
+    models (e.g \citealt{Huang2013a}; \citealt{Huang2013b}) but these multi model fits are quite sensitive to the background subtraction.
+For this paper, we opt to for the model independent 1-D approach and we will only study galaxies in the radial range where we are not sensitive to either the PSF ($r<5$ kpc) or the background subtraction ($r>100$ kpc).
+
+    We prepare large $i$-band cut-out images each galaxy in our sample that extend to at least 750 kpc in radius, along with the bad pixel mask, and the 
+    PSF model reconstructed at the central coordinate. These cut-outs include all the visible light of the galaxy while leaving enough space to evaluate the background level. 
+    We choose to use $i$-band images because they have excellent seeing, but also because they trace the stellar distributions of massive 
+    galaxies at $0.3 \leq z \leq 0.5$ reasonably well (the observed i-band corresponds to a rest-frame $g$ or $r$ band), and they suffer less from background uncertainty (because the sky is brighter in z and y).
+The $z$ and Y-bands will be better tracers of \mden{}, but the sky background in these bands
+    is much higher and the seeing is not as good as the i-band.
+
+    For each cut-out, we perform \texttt{SExtractor}-like background estimation and object detection using the \texttt{SEP} Python library.
+Out set up is designed to avoid the ``over-deblending'' problem that exists with \texttt{hscPipe}.
+We use several different backgrounds and $S/N$ thresholds, to identify the footprints of all objects, even those that are very close to the centers of bright galaxies.
+We create two masks for the \texttt{Ellipse} procedure.
+The first mask corresponds to the footprints of neighbouring galaxies.
+At this stage, we create a fiducial mask as well as a more aggresive mask to test for the impact of masking (see Appendix xxxx).
+The second mask is designed to measured the background level and masks out both the central (target) galaxy as well as neighbours.
+After appplying this mask to the cutout, we evalute the background level after smoothing over $6x6$  pixels (see Appendix xxxxx).
+This yields the global sky values over the cutout as well as the uncertainty in the sky.
+Based on the global uncertainty in the sky, at the depth of HSC wide, we should in pinciple be able to measure surface brightness profiles to $\sim 30$ \sb.
+However, in practice, we can only reach $<28.5$ \sb due to the uncertainties in modeling the sky.
+
+    % Appendix
+    %We achieve this via convolving the individual footprint with a Gaussian kernel
+    %so that we can conservatively exclude pixels affected by this object while still 
+    %making the mask follow the shape of the object.  
+    %Meanwhile, we create a more aggressive mask of \emph{all} objects in the same 
+    %approach,
+
+     %median-rebin the remaining pixels using a $6x6$ pixels box, and take 
+    %the peak value (or mode) of the distribution of these rebinned ``sky'' pixels 
+    %as the average background value around these bright galaxies.
+
+    We find that the global sky values is often slightly negative value indicate that hscpipe typically tends to over-subtract the sky.
 In \texttt{hscPipe}, the background on each CCD is modeled with a
-    Chebyshev-polynomial fit to the smoothed image after excluding pixels with $S/N >5$.
+    Chebyshev-polynomial that is fit to the smoothed image after excluding pixels with $S/N >5$.
     This algorithm suffer less than the SDSS version (e.g.\ see \citealt{Blanton2011}),
@@
     For our massive galaxies, such over-subtracted background creates artifactual
-    truncation or steeper surface brightness profile.
-    We therefore provide an ad hoc fix using a \texttt{SExtractor}-style background 
-    model ($200x200$ pixels background box size, and 6 pixels median filtering size of 
-    sky boxes) via running \texttt{SEP} on the image with all objects masked out.
-    This model can account for the slightly over-subtracted background at very large 
-    scale, shift the distribution of rebinned ``sky'' pixels to 0, and do not affect the 
-    intrinsic flux distribution of our target.
-
-    Finally, we run \texttt{Ellipse} on the background-corrected image following similar 
-    strategy of \citep{Li2012}.
-    In short, we start with free centroid and shape of each isophote, then gradually 
-    constrain their behaviors, and eventually extract 1-D surface brightness profile 
-    along the major axis using isophotes with fixed centroid and shape.
-    The 4th Fourier modes are included to fit the isophote better. 
-    In this way, we can extract the radial changes of the centroid, ellipticity, 
-    position angle, and average isophotal distortions (more ``disky'' or ``boxy'', 
-    e.g.\ \citealt{Kormendy2009}) along with the surface brightness profile.  
-    Fig.\ref{fig:ellipse} shows an example of the 1-D surface brightness and 
-    ellipticity profile for a massive galaxy at $z\sim0.2$ along with its masked 
-    image and a subset of isophotes.  
+    truncation or steeper surface brightness profile. We attempt to correct for sky for the oversubtraction that results from \texttt{hscPipe} using a method described in Appedix xxx.
+
+    % Appendix
+    %We therefore provide an ad hoc fix using a \texttt{SExtractor}-style background 
+    %model ($200x200$ pixels background box size, and 6 pixels median filtering size of 
+    %sky boxes) via running \texttt{SEP} on the image with all objects masked out.
+    %This model can account for the slightly over-subtracted background at very large 
+    %scale, shift the distribution of rebinned ``sky'' pixels to 0, and do not affect the 
+    %intrinsic flux distribution of our target.
+
+    Finally, we run \texttt{Ellipse} on the background-corrected cut-out following a similar methodology as \citep{Li2012}.
+In short, we start with a free centroid and shape (ellipticty and position angle) for each isophote.
+We then fix the centroid and then estimate the mean ellipticty and position angles of all isophotes.
+Finally, we extract a 1-D surface brightness profile along the major axis using the mean ellipticy and position angle.
+In practice, we run \texttt{Ellipse} allowing for more sophisticated shapes than a simple ellipse (more ``disky'' or ``boxy'', e.g.\ \citealt{Kormendy2009}).
 Appendix.\ref{app:A} includes more details about the \texttt{Ellipse} procedure.
-
-    %At low surface brightness regime, the final profile can be sensitive to several 
-    %configuration parameters of \texttt{Ellipse}.  
-    %After some tests, we choose to use 0.1 dex in logarithm as the step in semi-major 
-    %axis length between successive ellipses, and we use the median pixel value over the
-    %elliptical annulus after rejecting outlier pixels twice with $3\sigma$-clipping.
-    %These parameters are selected to make the final profile less affected by any nearby
-    %objects, and please see Appendix.~B for more details about the extraction of 
-    %1-D profile.
+We correct these surface brightness profiles for Galactic extinction and
+    cosmological dimming, then integrate them to various radius to get the 
+    luminosity within different physical apertures. Fig.\ref{fig:ellipse} shows an example of the 1-D surface brightness and 
+    ellipticity profile for a massive galaxy at $z\sim0.2$ together with the mask image and a subset of isophotes.
+
+    %The 4th Fourier modes are included to fit the isophote better. 
+    %In this way, we can extract the radial changes of the centroid, ellipticity, 
+    %position angle, and average isophotal distortions (more ``disky'' or ``boxy'', 
+    %e.g.\ \citealt{Kormendy2009}) along with the surface brightness profile.
+
+    We find that our 1-D profiles start begin to show unphsical behaviours (truncation or large fluctuations) at surface brightness levels of about $>28.5$ \sb.
+We therefore only consider regions above $<28.5$ \sb.
+    This conservative choice already allows us to measure light profiles out to $\sim 120$ kpc.
 
@@
     foreground galaxy or bright star) reasons, we can not extract reliable 1-D 
-    profiles for small fraction of massive galaxies due to heavily masked out 
-    central region. 
-    This issue reflects an intrinsic limitation of the 1-D method. 
-    It affects $48/375$ \rbcg{} galaxies, and a smaller fraction of \nbcg{} ones. 
+    profiles for small fraction of massive galaxies because their central regions are heavily masked. This is an intrinsic limitation of the 1-D method. 
+    It affects $48/375$ of the\rbcg{} galaxies, and a smaller fraction of \nbcg{} ones. 
     It is worth noting that this excludes most massive galaxies in major merger 
@@
 
-    We correct these surface brightness profiles for Galactic extinction and 
-    cosmological dimming, then integrate them to various radius to get the 
-    luminosity within different physical apertures.  
-    Although the $i$-band 1-D profile can in principle reach to $\sim 30$ \sb, 
-    we notice the profiles at very low surface brightness part are often less 
-    reliable by showing truncation or large fluctuation that are due to either 
-    background uncertainty or contamination from bright neighbours.
-    We therefore only consider the $<28.5$ \sb part of the profile here. 
-    This conservative choice already allows us to study the region out to 
-    $\sim 120$ kpc for massive galaxies in this sample.
-
-    %We also apply the isophotes from $i$-band images to other bands in 
-    %``force-photometry'' mode \texttt{Ellipse} run to get rough estimates of 
-    %color profiles.  
-    %Without taking the difference in seeing and background into account, 
-    %these color profiles can not be used for physical discussion. 
-    %But with the help of $K$-correction from the next section, we show that there 
-    %is no systematic difference in color gradient between \rbcg{} and 
-    %\nbcg{} sample.
-
 %% ------------------------------------------------------------------------------------ %%
@@
 
-\subsection{Stellar Masses from SED Fitting}
+    \alexie{Shold the color gradients stuff go here?? (I don't know.)}
+
+\subsection{Mass-to-light ratios from SED Fitting}
     \label{ssec:isedfit}
 
-    To convert the luminosity into stellar mass estimates, we assume that these massive 
+    To convert luminosities into stellar mass, we assume that these massive 
     galaxies can be well described by an average \m2l{}. 
     This is a reasonable assumption considering that they are ETGs that are dominated by 
-    old stellar population and are known to have shallow color gradients. 
-    We will further justify this point using the average color profiles in Section
+    old stellar populations and are known to have shallow color gradients. 
+    We will further justify this point by measuring their average color profiles in Section xxxxxx
     \ref{sec:discussion}.
@@
     (\citealt{Moustakas13}) to estimate the average \m2l{} and $k$-corrections using
-    5-band HSC \cmodel{} fluxes under forced-photometry mode. 
+    5-band HSC \cmodel{} fluxes. 
     Although \cmodel{} tends to underestimate the total flux for bright, extended 
-    objects, the forced-photometry results still provides accurate \emph{average} color 
-    of the galaxy as it constrains the behaviour of the model using the optimized 
-    reference one and taks the PSF convolution into account
+    objects, it still yields an accurate \emph{average} color 
+    of the galaxy as it is based on forced photomery and also takes the PSF convolution into account
     (e.g.\ Huang\etal~in prep.~).
@@
     Based on these models, it uses the observed photometry and redshift to compute the 
-    statistical likelihood, and generate the posterior probability distribution (PDF) 
-    functions of each parameter.  
-    To get the best estimate of certain parameter, \texttt{iSEDFit} ``integrates'' the 
+    statistical likelihood, and generates the posterior probability distribution (PDF) 
+    functions for each parameter.  
+    To get the best estimate of a given parameter, \texttt{iSEDFit} ``integrates'' the 
     full PDF over all the other ``nuisance'' parameters.
-    Then, the median value of the resulting marginalized PDF is used as the best value, 
-    while the 1-$\sigma$ uncertainty is derived from the cumulative PDF. 
-    Please refer to \citet{Moustakas13} for technical details and performance of 
-    \texttt{iSEDFit}.
+    Then, the median value and the 1-$\sigma$ uncertainty are derived based on the marginalized PDF. Please refer to \citet{Moustakas13} for technical details.
 
@@
     \footnote{http://www.iac.es/proyecto/miles/pages/stellar-libraries/miles-library.php}
-    (\citealt{MILES1}, \citealt{MILES2}) stellar library and \citet{Chabrier2003} 
+    (\citealt{MILES1}, \citealt{MILES2}) stellar library and assuming a \citet{Chabrier2003} 
     IMF between 0.1 to 100 \msun.
-    We use a delayed-$\tau$ model with stochastic star burst as the form of star 
-    formation history (SFH), and choose a set of reasonable parameters after some tests.  
-    Such form of SFH is appropriate for massive galaxies at low redshift 
+The star formation history (SFH) is assumed to follow a delayed-$\tau$ model with stochastic star bursts (see Appendix xx).
+This SFH is appropriate for massive galaxies at low redshifts
     (e.g.\ \citealt{Kauffmann2003}). 
-    For stellar metallicity, we assume flat distribution between 0.004 to 0.03 (which is 
-    the highest metallicity allowed by FSPS models).  
-    And, we adopt the \citet{Calzetti2000} extinction law with a order two Gamma 
-    distribution of $A_{V}$ between 0 to 2 magnitude.
-    Since most galaxies in both samples are red, quiescent galaxies, the results are 
-    not very sensitive to parameters related to SFH and internal dust extinction. 
+    For stellar metallicity, we assume a flat distribution between 0.004 to 0.03 (the highest value allowed by FSPS). We adopt the \citet{Calzetti2000} extinction law with a order two Gamma 
+    distribution of $A_{V}$ between 0 to 2 magnitude. A majority of our galaxies are red and quiescent and our results are 
+    not very sensitive to parameters related to the SFH or the internal dust extinction. 
     To achieve reasonable sampling across these parameters, we generate 250000 models.
 
-    We construct five band SED using the forced-photometry \cmodel{} magnitude corrected 
-    for the Galactic extinction. 
-    As for the photometric error, the current \cmodel{} photometry underestimates 
-    the flux errors of bright galaxies as it only includes statistical error, not the 
-    systematic uncertainties in the model-fitting process.  
-    From tests of synthetic objects, we find that the average accuracy of \cmodel{} 
-    photometry for bright galaxy is roughtly at 1\% level. 
+    We construct five band SEDs using the forced-photometry \cmodel{} magnitudes corrected 
+    for Galactic extinction.
+\cmodel{} only accounts for the statistical error on the flux measurement but does not account for systematic uncertainties in the model-fitting process.
+It therefore underestimates the flux errors of bright galaxies.
+Based on tests using synthetic objects, we find that the average accuracy of \cmodel{} for bright galaxy is roughly at the 1\% level.
 Therefore, we supply \texttt{iSEDFit} with simplified flux errors assuming $S/N = 100$
-    for $riz$ bands, and $S/N = 80$ for $gY$ bands (on average, images in $gY$ bands are 
+    for the $riz$ bands, and $S/N = 80$ for the $gY$ bands (on average, images in $gY$ bands are 
     shallower in depth and/or have higher background noise).  
-    The typical uncertainty of \logms{} for both samples is around 0.08-0.10 dex at the 
-    high-\mstar{} end. 
+    The typical uncertainty of \logms{} is around 0.08-0.10 dex at $M* \sim xxxx$ end. 
     Please see Appendix.\ref{app:B} for more detailed discussions of the SED fitting
     results.
+
     %In Fig.~3, we show an example of SED fitting result. 
@@
 
-\subsection{Comparison with \texttt{S82-MGC}}
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
+  \begin{figure*}[bt!]
+      \centering 
+      \includegraphics[width=\textwidth]{fig/average_mass_profiles_fsps1_A}
+      \caption{
+      	\textbf{Left}: Median \mden{} profiles of galaxies in different \mtot{} bins:
+      	[11.4, 11.6] (short-dashed line), [11.6, 11.8] (solid line), and 
+      	[11.8, 12.0] (long-dashed line). 
+      	Here we combine the \rbcg{} and \nbcg{} samples, and we also show a random subset 
+      	of individual profiles in the background.
+      	The shaded region highlights the region that could be affected by PSF.
+        Two vertical lines label the radius of 10 kpc (thin, dotted line) and
+        100 kpc (thick, dash line). ~~~ 
+        \textbf{Right}: comparison between the average \mden{} profiles with the ones 
+        from previous observations and simulations, including: 
+        1) average profile of massive elliptical galaxies at $z\sim 0$ from 
+        \citet[][Cyan, solid]{Huang2013a}; 
+        2) average profile of massive galaxies at $0.25 \leq z < 0.50$ observed by 
+        \textit{HST} from \citet[][Red, long-dashed]{Patel2013} ;
+        3) average radial stellar distribuitions in massive halos using simulation and 
+        particle tagging method (\citealt{Cooper13}; Purple, short-dashed).}
+      \label{fig:avg_prof}
+  \end{figure*}
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
+  \begin{figure*}[t!]
+      \centering 
+      \includegraphics[width=\textwidth]{fig/redbcg_prof_1}
+      \caption{
+          \update{
+          Comparison of the \mden{} profiles for \mtot{}-matched ($11.6<$\logmtot{}$<11.9$) 
+          and \minn{}-matched ($11.2<$\logminn{}$<11.6$) samples 
+          of \rbcg{} (orange to red) and \nbcg{} (grey to black) galaxies.~~
+          \textbf{Left} shows the results for the \mtot{}-matched samples.
+          For details of the matching process, please see Appendix.\ref{app:match}.  
+          On its upper panel, we show the \mden{} profile of each galaxy using very light 
+          color in the background.  
+          We highlight the median profile and its corresponding uncertainties using thick 
+          solid line with darker color and shaded region. 
+          Other formats are the same with Fig.\ref{fig:avg_prof}.
+          Meanwhile, we highlight the difference between the median profiles and its 
+          uncertainty on the bottom panel (brown solid line and shaded region).
+          To test the significance of the differential profile, we perform statistical tests 
+          by comparing the median profiles of two random groups that are drawn from the 
+          mixed sample, and have the same sizes with the matched \rbcg{} and \nbcg{} ones.
+          Repeating this process many times, the median of these random differential 
+          profiles (black solid line), the 1-$\sigma$ (dark-grey shaded region) and 3-$\sigma$
+          (light-grey shaded region) uncertainties are shown on the bottom panel as well. 
+          A darker vertical dash-line highlights the 100 kpc radius.~~
+          \textbf{Right} shows the results for the \minn{}-matched samples. 
+          The format is exactly the same with the left one, except that the darker vertical 
+          dash-line now highlights the 10 kpc radius.}
+      }
+      \label{fig:prof_1} 
+  \end{figure*}
+%% ------------------------------------------------------------------------------------ %%
+
+\subsection{Stellar Mass Density Profiles and Total Stellar Masses}
+    \label{ssec:mtotal}
+
+    \alexie{Did not make edits}
+
+    Using the best-fit stellar mass from \texttt{iSEDFit} (referred as \mcmodel{}), 
+    we estimate the average \m2l{} in $i$-band, then use that \m2l{} to convert the 
+    1-D luminosity density profiles into stellar mass density profiles; and 
+    also convert the luminosity within 10 and 100 kpc apertures into 
+    corresponding stellar mass estimates (referred as \minn{} and \mtot{}). 
+    From now, we use \mtot{} as the new proxy of ``total'' stellar mass of these 
+    galaxies.  
+    And we also derive the $k$-corrected luminosity and colors from the results.
+    In Appendix.\ref{app:B}, we also show the outputs like the average stellar age, 
+    metallicity, and internal dust extinction all behave reasonably for both 
+    samples, but will not use them for further scientific analysis.
+
+    As expected, the integration of 1-D profile out to very large radius help 
+    recover more luminosity (stellar mass) compared to the \cmodel{} results. This will shown in Section xx.
+
+    As mentioned earlier, our assumption of using an average \m2l{} ignores its
+    radial variation.   
+    It is well known that massive ETGs have negative optical color gradient which 
+    indicates a gradient of \m2l{} (e.g.\ \citealt{LaBarbera2012}; \citealt{DSouza2015}),
+    but the gradient is smooth and shallow out to a few times of the effective 
+    radius (color gradient at the very outskirt is still not well quantified). 
+    And, for the comparison between the \rbcg{} and \nbcg{} samples, 
+    Our results should remain intact as long as there is no significant
+    differences of color gradient between these two samples.
+    We will discuss this more later, but initial results do suggest a smooth color
+    gradient out to very large radius, and there is no systematic difference in 
+    color gradients of the two samples.  
+    Both suggest that the average \m2l{} approach should work reasonably well for
+    our goals.
+
+    And, we should mention that our approach is in principle very similar to the 
+    one adopted by the GAMA survey (\citealt{Taylor2011}), where they start with 
+    \mstar{} estimated using average \m2l{} from SED fitting results of
+    PSF-matched aperture photometry, and later correct it with better estimate 
+    of total luminosity.  
+    However, the GAMA survey relied on multi-band single-\ser model fitting on 
+    the SDSS images to get total luminosity (\citealt{Kelvin2012}). 
+    It is therefore interesting to compare the \mstar{} (\mgama{} v.s. \mtot{})
+    estimates for galaxies in common, given the differences in data and method. 
+    Please see the Appendix.\ref{app:C} for more details. 
+    In short, we notice systematic differences between the two \mstar{} estimates, 
+    and it is likely that the GAMA models miss fluxes in the stellar halo that 
+    is beyond the depth of SDSS image.
+
+    \update{In Appendix.\ref{app:basic}, we summarize the basic statistics of 
+    the \rbcg{} and \nbcg{} samples.  In general:}
+
+    %\begin{itemize}
+    %    \item \update{The two samples follow the same, tight ``red-sequence'' 
+    %        defined by $k$-corrected colors.}
+    %    \item \update{The redshift distributions are reasonably similar in 
+    %        $0.3 < z < 0.5$, but the difference can still bias the comparison of
+    %        \mden{} profiles.}
+    %    \item \update{Although their \mtot{} overlaps a lot between 
+    %        $11.6 <$\logmtot{}$< 11.9$, the relative distributions within this 
+    %        bin are still very different.}
+    %    \item \update{The distributions of \minn{} overlaps the most between 
+    %        $11.2 <$\logminn{}$< 11.6$, but the relative distributions also 
+    %        show difference within this \minn{} range.}
+    %\end{itemize}
+
+%% ------------------------------------------------------------------------------------ %%
+
+\section{Results}
+    \label{sec:result}
+
+    \subsection{Stellar Mass Completeness}
+
+    Here we refer to the comparison with Stripe 82 and just say that we are complete to xxx.
+
+    \update{To compare their structural details, we will focus on \rbcg{} and 
+    \nbcg{} galaxies with $11.6 \le$\logmtot{}$\le 11.9$.  
+    Both samples have reasonable completeness in this \mtot{} range
+    (see Fig.\ref{fig:smf1}).
+    In light of the differences in distributions of \mtot{}, \minn{}, and redshift, 
+    we will carefully match these properties between the \rbcg{} and \nbcg{}
+    samples to make sure the comparison is fair and meaningful.  
+    Please see the next section and Appendix.\ref{app:match} for more details.}
+
+    \subsection{Need a title}
     \label{ssec:s82}
 
-    Given the heterogeneous nature of the redshift resources for these samples, we 
+Here we show the luminosty difference and impact on SMF.
+
+We highlight this in the right panel of Fig.\ref{fig:smf1} as we show the 
+    distributions of differences between \mtot{} and \mcmodel{}, and their relations 
+    to the \mtot{}.  
+    For both samples, we see the ``extra mass'' recovered by 1-D photometry 
+    increases with \mtot{}, therefore this improvement impacts the \rbcg{}
+    sample more.  
+    This is basically consistent with the fact that the structure of massive ETGs 
+    depends on its stellar mass in a way that more massive ones tends to be 
+    more extended (e.g.\ \addref).  
+    Apparently, such mass-dependent difference between \mtot{} and \mcmodel{} will 
+    result in difference of the SMF. 
+    \alexie{Discussion!!} As the slope and normalization of SMF at high mass end is very sensitive 
+    to both cosmology and interesting baryonic processes such as AGN feedback
+    (\addref), they are particularly important in constraining the galaxy evolution
+    model, and therefore became the center of some intense arguments (\addref).  
+    Although the jury is still out on this topic, it has become clear that 
+    popular results using SDSS photometry (\addref) underestimate the total 
+    luminosity (stellar mass) of massive ETGs.  
+    However, past works (e.g.\ \addref) often relied on either stacking of 
+    shallow images or the extrapolation of models to investigate this effect. 
+    Using the deep HSC images, we have the potential to answer this question 
+    much better. 
+    Detailed studies of SMF deserves more careful investigations of many 
+    systematic issues (e.g.\ \addref), so we just show the impact of the 
+    ``extra mass'' on the volume density distributions of both samples 
+    (Fig.\ref{fig:smf1}, left panel).  
+    Generally speaking, the stellar mass corrected for total luminosity 
+    shifts the distribution toward the higher mass end, and slightly modify
+    the slope. 
+    People who want to use HSC photometry or other \cmodel{}-like photometry to 
+    study the properties and evolution of SMF should be aware of such effect.
+
+    \rewrite{Given the heterogeneous nature of the redshift resources for these samples, we 
     further investigate their \mstar{} completeness via comparing with galaxies that are 
@@
     The deeper photometry and better photo-$z$ make the \texttt{S82-MGC} sample complete 
-    to \logms{}$\geq 11.2$ at $z<0.7$.
-
-    The match between the \texttt{hscPho} sample and the \texttt{S82-MGC} one results in 
+    to \logms{}$\geq 11.2$ at $z<0.7$.}
+
+    \rewrite{The match between the \texttt{hscPho} sample and the \texttt{S82-MGC} one results in 
     20453 galaxies at $0.3 \leq z \leq 0.5$ (referred as \texttt{s82Pho} sample).  
@@
     comparisons, we will bear this in mind, and match the two samples carefully in 
-    \logms{} and redshift space before comparing them.
-
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %% 
-  \begin{figure*}[bt!]
-      \centering 
-      \includegraphics[width=\textwidth]{fig/average_mass_profiles_fsps1_A}
-      \caption{
-      	\textbf{Left}: Median \mden{} profiles of galaxies in different \mtot{} bins:
-      	[11.4, 11.6] (short-dashed line), [11.6, 11.8] (solid line), and 
-      	[11.8, 12.0] (long-dashed line). 
-      	Here we combine the \rbcg{} and \nbcg{} samples, and we also show a random subset 
-      	of individual profiles in the background.
-      	The shaded region highlights the region that could be affected by PSF.
-        Two vertical lines label the radius of 10 kpc (thin, dotted line) and
-        100 kpc (thick, dash line). ~~~ 
-        \textbf{Right}: comparison between the average \mden{} profiles with the ones 
-        from previous observations and simulations, including: 
-        1) average profile of massive elliptical galaxies at $z\sim 0$ from 
-        \citet[][Cyan, solid]{Huang2013a}; 
-        2) average profile of massive galaxies at $0.25 \leq z < 0.50$ observed by 
-        \textit{HST} from \citet[][Red, long-dashed]{Patel2013} ;
-        3) average radial stellar distribuitions in massive halos using simulation and 
-        particle tagging method (\citealt{Cooper13}; Purple, short-dashed).}
-      \label{fig:avg_prof}
-  \end{figure*}
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %% 
-  \begin{figure*}[t!]
-      \centering 
-      \includegraphics[width=\textwidth]{fig/redbcg_prof_1}
-      \caption{
-          \update{
-          Comparison of the \mden{} profiles for \mtot{}-matched ($11.6<$\logmtot{}$<11.9$) 
-          and \minn{}-matched ($11.2<$\logminn{}$<11.6$) samples 
-          of \rbcg{} (orange to red) and \nbcg{} (grey to black) galaxies.~~
-          \textbf{Left} shows the results for the \mtot{}-matched samples.
-          For details of the matching process, please see Appendix.\ref{app:match}.  
-          On its upper panel, we show the \mden{} profile of each galaxy using very light 
-          color in the background.  
-          We highlight the median profile and its corresponding uncertainties using thick 
-          solid line with darker color and shaded region. 
-          Other formats are the same with Fig.\ref{fig:avg_prof}.
-          Meanwhile, we highlight the difference between the median profiles and its 
-          uncertainty on the bottom panel (brown solid line and shaded region).
-          To test the significance of the differential profile, we perform statistical tests 
-          by comparing the median profiles of two random groups that are drawn from the 
-          mixed sample, and have the same sizes with the matched \rbcg{} and \nbcg{} ones.
-          Repeating this process many times, the median of these random differential 
-          profiles (black solid line), the 1-$\sigma$ (dark-grey shaded region) and 3-$\sigma$
-          (light-grey shaded region) uncertainties are shown on the bottom panel as well. 
-          A darker vertical dash-line highlights the 100 kpc radius.~~
-          \textbf{Right} shows the results for the \minn{}-matched samples. 
-          The format is exactly the same with the left one, except that the darker vertical 
-          dash-line now highlights the 10 kpc radius.}
-      }
-      \label{fig:prof_1} 
-  \end{figure*}
-%% ------------------------------------------------------------------------------------ %%
-
-\subsection{Stellar Mass Corrected for Total Luminosity}
-    \label{ssec:mtotal}
-
-    Using the best-fit stellar mass from \texttt{iSEDFit} (referred as \mcmodel{}), 
-    we estimate the average \m2l{} in $i$-band, then use that \m2l{} to convert the 
-    1-D luminosity density profiles into stellar mass density profiles; and 
-    also convert the luminosity within 10 and 100 kpc apertures into 
-    corresponding stellar mass estimates (referred as \minn{} and \mtot{}). 
-    From now, we use \mtot{} as the new proxy of ``total'' stellar mass of these 
-    galaxies.  
-    And we also derive the $k$-corrected luminosity and colors from the results.
-    In Appendix.\ref{app:B}, we also show the outputs like the average stellar age, 
-    metallicity, and internal dust extinction all behave reasonably for both 
-    samples, but will not use them for further scientific analysis.
-
-    As expected, the integration of 1-D profile out to very large radius help 
-    recover more luminosity (stellar mass) compared to the \cmodel{} results.
-    We highlight this in the right panel of Fig.\ref{fig:smf1} as we show the 
-    distributions of differences between \mtot{} and \mcmodel{}, and their relations 
-    to the \mtot{}.  
-    For both samples, we see the ``extra mass'' recovered by 1-D photometry 
-    increases with \mtot{}, therefore this improvement impacts the \rbcg{}
-    sample more.  
-    This is basically consistent with the fact that the structure of massive ETGs 
-    depends on its stellar mass in a way that more massive ones tends to be 
-    more extended (e.g.\ \addref).  
-    Apparently, such mass-dependent difference between \mtot{} and \mcmodel{} will 
-    result in difference of the SMF. 
-    As the slope and normalization of SMF at high mass end is very sensitive 
-    to both cosmology and interesting baryonic processes such as AGN feedback
-    (\addref), they are particularly important in constraining the galaxy evolution
-    model, and therefore became the center of some intense arguments (\addref).  
-    Although the jury is still out on this topic, it has become clear that 
-    popular results using SDSS photometry (\addref) underestimate the total 
-    luminosity (stellar mass) of massive ETGs.  
-    However, past works (e.g.\ \addref) often relied on either stacking of 
-    shallow images or the extrapolation of models to investigate this effect. 
-    Using the deep HSC images, we have the potential to answer this question 
-    much better. 
-    Detailed studies of SMF deserves more careful investigations of many 
-    systematic issues (e.g.\ \addref), so we just show the impact of the 
-    ``extra mass'' on the volume density distributions of both samples 
-    (Fig.\ref{fig:smf1}, left panel).  
-    Generally speaking, the stellar mass corrected for total luminosity 
-    shifts the distribution toward the higher mass end, and slightly modify
-    the slope. 
-    People who want to use HSC photometry or other \cmodel{}-like photometry to 
-    study the properties and evolution of SMF should be aware of such effect.
-
-    As mentioned earlier, our assumption of using an average \m2l{} ignores its
-    radial variation.   
-    It is well known that massive ETGs have negative optical color gradient which 
-    indicates a gradient of \m2l{} (e.g.\ \citealt{LaBarbera2012}; \citealt{DSouza2015}),
-    but the gradient is smooth and shallow out to a few times of the effective 
-    radius (color gradient at the very outskirt is still not well quantified). 
-    And, for the comparison between the \rbcg{} and \nbcg{} samples, 
-    Our results should remain intact as long as there is no significant
-    differences of color gradient between these two samples.
-    We will discuss this more later, but initial results do suggest a smooth color
-    gradient out to very large radius, and there is no systematic difference in 
-    color gradients of the two samples.  
-    Both suggest that the average \m2l{} approach should work reasonably well for
-    our goals.
-
-    And, we should mention that our approach is in principle very similar to the 
-    one adopted by the GAMA survey (\citealt{Taylor2011}), where they start with 
-    \mstar{} estimated using average \m2l{} from SED fitting results of
-    PSF-matched aperture photometry, and later correct it with better estimate 
-    of total luminosity.  
-    However, the GAMA survey relied on multi-band single-\ser model fitting on 
-    the SDSS images to get total luminosity (\citealt{Kelvin2012}). 
-    It is therefore interesting to compare the \mstar{} (\mgama{} v.s. \mtot{})
-    estimates for galaxies in common, given the differences in data and method. 
-    Please see the Appendix.\ref{app:C} for more details. 
-    In short, we notice systematic differences between the two \mstar{} estimates, 
-    and it is likely that the GAMA models miss fluxes in the stellar halo that 
-    is beyond the depth of SDSS image.
-
-    \update{In Appendix.\ref{app:basic}, we summarize the basic statistics of 
-    the \rbcg{} and \nbcg{} samples.  In general:}
-
-    \begin{itemize}
-        \item \update{The two samples follow the same, tight ``red-sequence'' 
-            defined by $k$-corrected colors.}
-        \item \update{The redshift distributions are reasonably similar in 
-            $0.3 < z < 0.5$, but the difference can still bias the comparison of
-            \mden{} profiles.}
-        \item \update{Although their \mtot{} overlaps a lot between 
-            $11.6 <$\logmtot{}$< 11.9$, the relative distributions within this 
-            bin are still very different.}
-        \item \update{The distributions of \minn{} overlaps the most between 
-            $11.2 <$\logminn{}$< 11.6$, but the relative distributions also 
-            show difference within this \minn{} range.}
-    \end{itemize}
-
-    \update{To compare their structural details, we will focus on \rbcg{} and 
-    \nbcg{} galaxies with $11.6 \le$\logmtot{}$\le 11.9$.  
-    Both samples have reasonable completeness in this \mtot{} range
-    (see Fig.\ref{fig:smf1}).
-    In light of the differences in distributions of \mtot{}, \minn{}, and redshift, 
-    we will carefully match these properties between the \rbcg{} and \nbcg{}
-    samples to make sure the comparison is fair and meaningful.  
-    Please see the next section and Appendix.\ref{app:match} for more details.}
-
-%% ------------------------------------------------------------------------------------ %%
-
-\section{Results}
-    \label{sec:result}
-
-\subsection{Comparison of Surface Mass Density Profiles}
+    \logms{} and redshift space before comparing them}.
+
+\subsection{Surface Mass Density Profiles}
     \label{ssec:sbp_compare}
 
-\subsubsection{Internal Comparison and Comparison with Previous Works}
+\subsubsection{Mass Dependent Profiles}
     \label{sssec:sbp_inter}
@@
     different physical processes, including the environmental effect.
+
+    \alexie{dont conceptually separate into two samples at this stage,}
 
@@
     As one can see in the left panel of Fig.\ref{fig:avg_prof}, we can comfortably trace 
-    the \mstar{} distribution of these massive galaxies out to 100 kpc 
+    the \mstar{} distribution of these massive galaxies out to 100 kpc \alexie{or 120??? Make the same numbers everywhere.}
     \textbf{individually}, which gives us huge advantage in studying the statistical 
@@
 
-    In principe, this is consistent with result from HST observations of BCGs at 
+    \alexie{Sounds more like Discussion section} In principe, this is consistent with result from HST observations of BCGs at 
     $0.3 < z <0.9$ (\citealt{Bai2014}) and the claimed positive correlation between 
@@
       \includegraphics[width=\textwidth]{fig/redbcg_prof_2}
-      \caption{Comparisons of the \mden{} profiles for \mtot{}-matched \rbcg{} 
+      \caption{\alexie{Remvoe or move to Appendix} Comparisons of the \mden{} profiles for \mtot{}-matched \rbcg{} 
           (orange-red) and \nbcg{} (grey-black) galaxies in lower (left; [11.5,11.70]) 
@@
 
-\subsubsection{Environmental dependence of \mden{} profiles at fixed \mtot{}}
+\subsubsection{Environmental dependence}
     \label{sssec:sbp_mtot}
 
+\alexie{Merge the two following into ONE section. AND cut it down by half. Sythetisoize.}
+
     \update{
     We show the results of the comparison in Fig.\ref{fig:prof_1} after 
-    carefully matching the \rbcg{} sample with smaller size to the \nbcg{} samples 
+    carefully matching the \nbcg{} sample with larger size to the \rbcg{} samples 
     within $0.3 < z < 0.5$ and $11.6 < $\logmtot{}$<11.9$ vial searching for the $N$ 
@@
     The details of the procedure and the evaluation of the matching quality can be 
-    found in Appendix.\ref{app:match}. 
+    found in Appendix.\ref{app:match} (see Fig.\ref{fig:match}.
+    Here, we choose to use the \mstar{} within 100 kpc as a proxy of the ``total''
+    stellar mass.  
+    This choice reflects the radius range of the \mden{} profile that we can safely 
+    measure in a model independent manner given the current depth of the image and 
+    the accuracy of sky background subtraction.
+    For galaxies with $11.6 < $\logmtot{}$<11.9$, 100 kpc equals to 5-8 times of their 
+    effective radius, hence should enclose most their \mstar{}.
+    %Also, for a small fraction of massive \rbcg{} galaxies that are from rich clusters, 
+    %the intra-group/cluster light (IGL/ICL) could contribute a lot to the observed 
+    %\mden{} profile, and complicate the comparison with the \nbcg{} galaxies.  
+    %We will discuss these issues in more details in Section \ref{sec:discussion}.
     In summary, given the typical uncertainty of stellar mass, the two samples are well 
@@
     We also check their distributions of $k$-corrected colors ($g-r$), and confirm 
-    that they have similar color distributions as well.}
+    that they have similar color distributions as well.
+    }
 
@@
 
+    \alexie{This is not a seperate section.}
+
     \update{Here, we compare the median \mden{} profiles of \rbcg{} and \nbcg{} galaxies
@@
     \label{ssec:ell_color}
+
+    \alexie{On the fence about this section. Is it all important???}
 
@@
     On the other hands, when matched using \minn{}, the \rbcg{} galaxies show 
-    systematically higher ellipticity than the \ncbg{} ones at $r > 10$ kpc, despite 
+    systematically higher ellipticity than the \nbcg{} ones at $r > 10$ kpc, despite 
     the ellipticity profiles at inner region are still very similar. 
@@
 
-\subsection{Explore Different Scaling Relations}
+\subsection{Environmental Dependence of Scaling Relations}
     \label{ssec:scaling}
@@
 %% ------------------------------------------------------------------------------------ %% 
-  \begin{figure}[bt!]
+  \begin{figure*}[bt!]
       \centering 
-      \includegraphics[width=\columnwidth]{fig/redbcg_mass_r50}
-      \caption{The \mstar{}-size relations for \rbcg{} (orange-red circles) and \nbcg{} 
-          (grey dots) galaxies. 
+      \includegraphics[width=\textwidth]{fig/redbcg_scaling_relation}
+      \caption{\textbf{Left}: The \mstar{}-size relations for \rbcg{} 
+          (orange squares) and \nbcg{} (grey dots) galaxies. 
           Here we use the \mtot{} as proxy of total \mstar{}, and use the 
@@
           galaxies in massive groups from \citet{HCompany13} (green, long dashed line). 
-          Please refer to the text for more details.}
-      \label{fig:mass_r50}
-  \end{figure}
+          Please refer to the text for more details.~
+          \textbf{Right:} The relations between \mtot{} and \minn{} for the 
+          \rbcg{} and \nbcg{} galaxies, along with the best-fit scaling relations for 
+          both samples.  The format is the same with the left one.
+          }
+      \label{fig:scaling_relation} 
+  \end{figure*}
 %% ------------------------------------------------------------------------------------ %%
@@
     \update{
-    Through careful comparisons of \mden{} profiles at fixed \mtot{} and \minn{}, 
-    we clearly show that the structure of massive central galaxies at $0.3 < z < 0.5$
-    depend on the halo mass in a subtle but systematic manner. 
-    Therefore, we also expect to see such evidence on the \mstar{}-size relations 
-    of \rbcg{} and \nbcg{} galaxies (see Fig.\ref{fig:mass_r50}).}
-
-    We choose to use the \mtot{} as the proxy of ``total'' \mstar{}, and use the 
+    Since comparisons of \mden{} profiles reveal that the structure of massive central 
+    galaxies indeed shows dependence on halo mass or environment, we expect to find 
+    similar evidence on the \mstar{}-size relations (see the left panel of 
+    Fig.\ref{fig:scaling_relation}).
+    }
+
+    We use the \mtot{} as the proxy of ``total'' \mstar{}, and the 
     radius that encloses 50\% of luminosity within 100 kpc ($R_{\mathrm{50}}$) as 
     the ``size'' to evaluate the relation.
-    We use the curve-of-growth of luminosity from the \texttt{Ellipse} run on 
-    $i$-band images to estimate the $R_{\mathrm{50}}$ here.
-    This 1-D approach is more sensitive to issues like the smearing effect of PSF and 
-    the choice of aperture for maximum luminosity than the 2-D fitting method.
-    But, for the massive galaxies in this work, their apparent sizes are always 
-    sufficiently large at $0.3 \geq z \geq 0.5$ so that the $R_{\mathrm{50}}$ 
-    measurements are not bothered by seeing.  
-    At the same time, this 1-D method has the advantages of being less affected by the 
-    accuracy of background subtraction, structural details, and model assumptions.
-
-    On Fig.\ref{fig:mass_r50}, we see clear \mstar{}-size relations for both samples.  
+    \update{
+    We derive the $R_{\mathrm{50}}$ using the $i$-band curve-of-growth. 
+    Since the massive galaxies in this sample are large enough, we do not need to 
+    worry about the seeing correction here. 
+    Meanwhile, the 1-D method is less affected by the accuracy of background 
+    subtraction and structural details.
+    }
+
+%    We use the curve-of-growth of luminosity from the \texttt{Ellipse} run on 
+%    $i$-band images to estimate the $R_{\mathrm{50}}$ here.
+%    This 1-D approach is more sensitive to issues like the smearing effect of PSF and 
+%    the choice of aperture for maximum luminosity than the 2-D fitting method.
+%    But, for the massive galaxies in this work, their apparent sizes are always 
+%    sufficiently large at $0.3 \geq z \geq 0.5$ so that the $R_{\mathrm{50}}$ 
+%    measurements are not bothered by seeing.  
+%    At the same time, this 1-D method has the advantages of being less affected by the 
+%    accuracy of background subtraction, structural details, and model assumptions.
+
+    On the left of Fig.\ref{fig:scaling_relation}, we see clear \mstar{}-size relations for both samples.  
     At fixed \mtot{}, the distributions of $R_{\mathrm{50}}$ for the \rbcg{} and
@@
 
-    \noindent As shown in Fig.\ref{fig:mass_r50}, at the high-mass end, the two relations 
+    \noindent As shown in Fig.\ref{fig:scaling_relation}, at the high-mass end, the two relations 
     have consistent slopes within their uncertainties, but different normalizations. 
@@
 
-%% ------------------------------------------------------------------------------------ %% 
-  \begin{figure*}[t]
-      \centering 
-      \includegraphics[width=\textwidth]{fig/redbcg_m100_m10_new}
-      \caption{\textbf{(a)}: Distributions of galaxies on the 
-          \mtot{}-$\Delta (\log M_{\star})_{100\mathrm{kpc}-10\mathrm{kpc}}$ plane. 
-          All \rbcg{} (open red boxes) and \nbcg{} (light, grey dots) galaxies 
-          are shown in the background. 
-          The \mtot{}-matched samples between $11.6<$\logms{}$<11.9$ (between two 
-          vertical lines) are highlighted (\rbcg{}: solid red boxes; 
-          \nbcg{}: bigger grey dots). 
-          We also show the median values (solid triangular and hexagon), and the
-          distributions of $\Delta (\log M_{\star})_{100\mathrm{kpc}-10\mathrm{kpc}}$
-          (both histograms and kernel density distributions on the right).
-          The best scaling relations for \rbcg{} (red, solid) and 
-          \nbcg{} (grey, dashed) galaxies along with their uncertainties 
-          are illustrated as well.~~
-          \textbf{(b)}: Distributions of galaxies on the 
-          $\Delta (\log M_{\star})_{100\mathrm{kpc}-10\mathrm{kpc}}$-\minn{} plane.~~
-          \textbf{(c)}: Distributions of galaxies on the 
-          $\Delta (\log M_{\star})_{100\mathrm{kpc}-10\mathrm{kpc}}$-\mtot{} plane.
-          But, this time, we highlight the \rbcg{} and \nbcg{} samples that are 
-          matched using \minn{} instead of \mtot{}.~~
-          \textbf{(c)}: Relations between \mtot{} and \minn{}. 
-          Other formats of figure (b), (c), and (d) are very similar with figure (a).}
-      \label{fig:m100_m10_A}
-  \end{figure*}
-%% ------------------------------------------------------------------------------------ %%
+%%% ------------------------------------------------------------------------------------ %% 
+%  \begin{figure*}[t]
+%      \centering 
+%      \includegraphics[width=\textwidth]{fig/redbcg_m100_m10_new}
+%      \caption{\textbf{(a)}: Distributions of galaxies on the 
+%          \mtot{}-$\Delta (\log M_{\star})_{100\mathrm{kpc}-10\mathrm{kpc}}$ plane. 
+%          All \rbcg{} (open red boxes) and \nbcg{} (light, grey dots) galaxies 
+%          are shown in the background. 
+%          The \mtot{}-matched samples between $11.6<$\logms{}$<11.9$ (between two 
+%          vertical lines) are highlighted (\rbcg{}: solid red boxes; 
+%          \nbcg{}: bigger grey dots). 
+%          We also show the median values (solid triangular and hexagon), and the
+%          distributions of $\Delta (\log M_{\star})_{100\mathrm{kpc}-10\mathrm{kpc}}$
+%          (both histograms and kernel density distributions on the right).
+%          The best scaling relations for \rbcg{} (red, solid) and 
+%          \nbcg{} (grey, dashed) galaxies along with their uncertainties 
+%          are illustrated as well.~~
+%          \textbf{(b)}: Distributions of galaxies on the 
+%          $\Delta (\log M_{\star})_{100\mathrm{kpc}-10\mathrm{kpc}}$-\minn{} plane.~~
+%          \textbf{(c)}: Distributions of galaxies on the 
+%          $\Delta (\log M_{\star})_{100\mathrm{kpc}-10\mathrm{kpc}}$-\mtot{} plane.
+%          But, this time, we highlight the \rbcg{} and \nbcg{} samples that are 
+%          matched using \minn{} instead of \mtot{}.~~
+%          \textbf{(d)}: Relations between \mtot{} and \minn{}. 
+%          Other formats of figure (b), (c), and (d) are very similar with figure (a).}
+%      \label{fig:scaling_relation}
+%  \end{figure*} 
+%%% ------------------------------------------------------------------------------------ %%
 
@@
 
-    We show the results in Fig.\ref{fig:m100_m10_A}.  
+    We show the results in Fig.\ref{fig:scaling_relation}.  
     In panel (a), we plot the \mtot{} with $\Delta \log M$ for both the\rbcg{} 
@@
     halo mass, assembly history, and the structure of massive galaxies.
-    On Fig.\ref{fig:m100_m10_A} (d), we illustrate the \mtot{}-\minn{} relations 
+    On Fig.\ref{fig:scaling_relation} (d), we illustrate the \mtot{}-\minn{} relations 
     at \logmtot$\geq 11.6$ that are derived using MCMC sampling method.  
@@
     the \rbcg{} galaxies. 
-    Also, replacing the \minn{} with \mstar{} within 5 or 15 kpc apertures does not change 
-    our conclusions. 
+    Also, replacing the \minn{} with \mstar{} within 5 or 15 kpc apertures does not 
+    change our conclusions. 
     In fact, the relation using $M_{\star, 5\ \mathrm{kpc}}$ shows more significant 
@@
 
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %% 
-  \begin{figure*}[t]
-      \centering 
-      \includegraphics[width=\textwidth]{fig/redbcg_discussion_5}
-      \caption{
-      \update{
-          \textbf{Left}: Relation between \mtot{} and the logarithmic mass difference 
-          between \mmax{} and \mtot{} for both \rbcg{} (red square) and \nbcg{} 
-          (grey dot) galaxies.  The format is very similar to the left figure of 
-          Fig.\ref{fig:smf1}.~~
-          \textbf{Right}: The stellar mass volume-density distributions of massive galaxies 
-          after combining the \rbcg{} and \nbcg{} samples together, using both 
-          \mtot{} (black solid line) and \mmax{} (black dash line). 
-          The uncertainty for distribution using \mtot{} is shown in grey shaded region.  
-          Here, we also compare the distributions with SMF from previous works: 
-          (a): SDSS galaxies at $z\sim 0.1$ from \citet{Bernardi2013}; the \mstar{} is 
-          based on photometry from 2-D \ser{}$+$Exponential model fitting; 
-          (b): SDSS galaxies at $z\sim 0.1$ from \citet{Moustakas13} based on 
-          improved SDSS \texttt{cModel} photometry; 
-          (c): \texttt{S82-MGC} galaxies at $0.15 < z< 0.43$ from 
-          \citet{Leauthaud2016} based on PSF-matched SDSS-UKIDSS photometry.
-          Please see text for more details of the comparison.
-          }}
-      \label{fig:discussion_1}
-  \end{figure*}
 %% ------------------------------------------------------------------------------------ %%
@@
           Ultra-Deep Field.}
-      \label{fig:discussion_2}
+      \label{fig:discussion_1}
   \end{figure}
@@
 
-    In the past decade, the mass assembly and structural evolution of massive ETGs 
-    remains as an active topic.  
-    More and more convincing observations of massive galaxies at high redshift reveal that
-    the progenitors of massive elliptical galaxies are quite different in structure
-    comparing with their local decedents (e.g. \addref{}).  
-    Collectively, they need to increase their ``size'' ($R_{\mathrm{e}}$) by a factor of 
-    2 to 4 (e.g. \addref{}) without changing their inner \mden profile (e.g. \addref{})
-    and central stellar velocity dispersion (e.g. \addref{}) much in the last 8-10 Gyrs.  
-    Owing mainly to better numerical simulations, the challenge of ``size''-evolution 
-    seems to be eased by the promising ``two-phase'' scenario under the framework of 
-    hierarchical formation of galaxy (e.g.\addref{}). 
-    Under this picture, the inner region of massive galaxies mostly consist of stars 
-    formed within the halo of the main progenitor through intense dissipative processes 
-    at high redshift.  
-    Later, after the active star formation is quenched in these massive systems, their 
-    mass assembly history becomes dominated by accretions of satellites.  
-    Based on the prediction of merger tree and current understanding of satellite 
-    population around massive galaxies, most these merging events are likely to be 
-    minor ones, and without involving much gas dissipation.  
-    Since such minor, dry merger basically redistributes stars onto the outer envelope 
-    of the central galaxy, it becomes the most promising solution to the ``size-evolution''
-    puzzle.  
-    However, it raises additional questions at the same time. 
-    The most pressing one would be the expected ``environmental''-dependence of structures 
-    of massive central galaxies. 
-    As minor merger is expected to be more frequent in denser environment, the mass assembly 
-    history and \mstar{} distribution of central galaxies should show dependence on \mhalo{}
-    or even other properties of the host halo.  
-    For instance, centrals in more and less massive halos could have different 
-    slopes and/or scatters in their mass-size relation (e.g. \addref{}).  
-    Yet, no clear evidence of such dependence has been found. 
-    In this work, taking advantage of the deep photometry from the HSC survey and looking 
-    into the detailed \mden{} profiles, we clearly see evidence that the \textbf{structure
-    of massive central galaxies, both the inner and outer parts, does show dependence on 
-    the halo mass}. 
-    Here, we briefly discuss the physical causes of this dependence, potential caveats, 
-    and more scientific implications.
-
-    Firstly, the comparisons of the \mden{} profiles suggest that \textbf{\mhalo{} does 
-    not play a central role in shaping the structure of massive central galaxies}.  
-    It appears that massive central galaxies at \logms{}$\geq 11.5$ were shaped by 
-    same physical processes in more and less massive halos.  
-    At both fixed \mtot{} and \minn{}, centrals from cluster-level halos do not form a 
+    \update{
+    In the past decade, the mass assembly history and structural evolution of massive 
+    ETGs remain an active topic.  
+    More convincing evidence from observations of massive galaxies at high redshift 
+    suggest that the progenitors of massive elliptical galaxies today are quite different 
+    in structural properties (e.g. \citealt{Bezanson2009}, \citealt{vanDokkum2010}).  
+    Collectively, they need to increase their ``size'' ($R_{\mathrm{e}}$) by a factor 
+    of 2 to 4 (e.g. \citealt{Newman2012}, \citealt{vdWel2014}), perhaps decrease the 
+    central stellar velocity dispersion a little (e.g. \citealt{vandeSande2011}, 
+    \citealt{Belli2014}) without changing their inner \mden{} profiles too much 
+    (e.g. \citealt{Szomoru2012}, \citealt{Patel2013}) and  in the last 8-10 Gyrs.  
+    With the help from better simulations, the promising ``two-phase'' formation 
+    scenario seems to be able to deal with these challenges well (e.g. 
+    \citealt{Oser2010}, \citealt{Oser2012}).
+    However, it raises additional questions.
+    As the massive central galaxies in more massive halos should have different mass 
+    assembly history, experience more (minor) mergers than the ones in smaller halos, 
+    we expect to see certain structural properties depend on ``environment''. 
+    Interestingly, although hints of such dependence have been noticed at high redshift 
+    (e.g. \citealt{Papovich2012}, \citealt{Delaye2014}), no clear evidence has been found 
+    at low redshift (e.g. \citealt{Nair2010}, \citealt{HCompany13}). 
+    In this work, taking advantage of the deep photometry from the HSC survey, we 
+    detect subtle but robust evidence that suggests the \textbf{structure
+    of massive central galaxies, both the inner and outer parts, depends on the mass of
+    their host halos at $0.3 < z < 0.5$}. 
+    Here, we briefly discuss its physical origin, potential caveats, and more scientific 
+    implications.  
+    }
+
+    Firstly, the comparisons of the \mden{} profiles suggest that \textbf{\mhalo{} plays
+    a subtle role in shaping the structure of massive central galaxies}.  
+    It appears that massive central galaxies at \logms{}$\geq 11.5$ were shaped by more 
+    or less the same physical processes.  
+    At the fixed \mtot{} and \minn{}, centrals from cluster-level halos do not form a 
     unique population. 
-    Instead, their individual \mden{} profiles greatly overlap with the ones in halos of 
-    small group. 
-    At similar \mtot{}, even their median \mden{} profiles only show quite subtle 
+    Instead, their individual \mden{} profiles greatly overlap with the ones from smaller 
+    halos.
+    At similar \mtot{}, even their median \mden{} profiles only show very subtle 
     differences. 
-    For the \rbcg{} sample, this is similar to the results of \citep{Zhao2015} that 
-    a considerable fraction of nearby BCGs (34\%) does not fall into the ``cD'' class.
+    For the \rbcg{} sample, this results is similar to \citep{Zhao2015} where these 
+    authors found a considerable fraction of nearby BCGs (34\%) does not fall into 
+    the ``cD'' class.
+    \update{
     From the smooth distributions of \mden{} profiles on Fig.\ref{fig:prof_1} 
-    and Fig.\ref{fig:prof_4}, it is even harder to draw a clear difference 
+    and Fig.\ref{fig:prof_4}, it becomes even harder to draw a meaningful line  
     between ``cD'' galaxy and ``normal elliptical''. 
+    For ETGs above certain \mstar{}, it seems more physical to treat their outer 
+    envelopes as the ``accreted'' components from a series of merging events. 
+    And, the differences in their assembly histories lead to outer \mden{} profiles 
+    with a variety of slopes. 
+    }
 
@@
     of the ``two-phase'' scenario at first glance}. 
-    For central galaxies with similar stellar mass at the end of the first phase, 
-    their subsequent, accretion-dominated mass assembly naturally relates to \mhalo{}, 
-    which determines the number and mass distributions of satellites. 
+    For central galaxies with similar \mstar{} at the end of the first phase, 
+    their subsequent, accretion-dominated assembly histories naturally relate to 
+    \mhalo{}, which determines the number and mass distributions of satellites. 
     Therefore, centrals of more massive halos should accumulate more extended stellar 
-    envelope during the second phase, exactly as we find in the \mden{} profile 
+    envelopes during the second phase, exactly as what we find in the \mden{} profile 
     comparison of the \minn{}-matched samples (see Fig.\ref{fig:prof_4}).
-    Under the ``two-phase'' formation scenario, the stellar content of massive galaxies
-    can be broadly separated into the ``in-situ'' and ``accreted'' components. 
-    At fixed \mtot{}, the differences of median \mden{} profiles could reflect 
-    different relative fraction of these two components. 
-    Recent simulations indicate that (1) the fraction of accreted stars could have 
-    a steep correlation with total stellar mass; (2) for \logms$\geq 11.5$ galaxies,
+    Recent simulations indicate that (1) the fraction of accreted stars increases 
+    steeply with total \mstar{}; (2) for \logms{}$\geq 11.5$ galaxies,
     the accreted component starts to dominate within the $R_{\mathrm{e}}$.  
-    Given that (1) the ``transition radius'' between the two median profiles is around
-    15-20 kpc (see Fig.\ref{fig:prof_1}); and (2) the differences become more 
-    significant at higher mass end, it is likely the \mhalo{}-dependence of structure
-    at fixed total stellar mass is driven by the higher fraction of accreted stars 
-    in more massive halos.  
-    To confirm this inference, in Fig.\ref{fig:discussion_1}, we compare the median 
-    \mden{} profiles of the \mtot{}-matched \rbcg{} and \nbcg{} samples at 
-    $11.5\leq$\logms{}$<11.7$ with the median profiles of 
-    (1) massive ETGs at $1.0 < z < 1.5$ that are considered the progenitors of 
+    During the profile comparison between the \mtot{} dominated samples, we notice 
+    that (1) the ``transition radius'' between the two median profiles is around
+    15-20 kpc, which is similar to their $R_{\mathrm{e}}$ (see Fig.\ref{fig:prof_1}); 
+    and (2) the differences between the median profiles become more significant at 
+    higher \mtot{} end.
+    Therefore, it seems that the \mhalo{}-dependence of structure at fixed \mtot{} 
+    is driven by the higher fraction of accreted stars in massive central galaxies
+    of more massive halos. 
+    \update{
+    In Fig.\ref{fig:discussion_1}, we compare the median \mden{} profiles of the 
+    combined \rbcg{} and \nbcg{} samples in two \mtot{} bins 
+    ($11.4\leq$\logmtot{}$<11.6$ and $11.6\leq$\logmtot{}$<11.8$) with the median profiles 
+    of (1) massive ETGs at $1.0 < z < 1.5$ that are considered the progenitors of 
     $\sim 10^{11.5} M_{\odot}$ ETGs at $z=0$ (\citealt{Patel2013}).  
-    After this redshift range, their mass growth should be dominated by mergers.  
-    (2) inner components of $z=0$ $10^{11.4} M_{\odot}$ ellipticals from 2-D decomposition
-    (\citealt{Huang2013a}). 
-    \citep{Huang2013b} showed that these structures are quite similar to the compact 
-    progenitors at higher redshift in many aspects.  
-    (3) the ``in-situ'' components of simulated galaxies in massive halo of 
+    After $z\sim 1.5$, the mass growth of these galaxies should be dominated by mergers 
+    and accretions. 
+    (2) the inner components of $10^{11.4} M_{\odot}$ ellipticals at $z\sim 0$ from 2-D 
+    decomposition (\citealt{Huang2013a}). 
+    \citep{Huang2013b} showed that these components are quite similar to the compact 
+    progenitors at high redshift in many aspects.
+    } 
+    (3) the ``in-situ'' components of simulated galaxies in massive halos from 
     \citep{Cooper13} using particle-tagging technique (the inner few kpc is quite 
     uncertain due to the resolution).  
-    Regardless the small difference in median \mstar{} and details in \m2l{} estimates, 
-    the comparison first confirms that \minn{} is indeed not a bad proxy of the in-situ 
-    mass; meanwhile, it also highlights that structural difference between \rbcg{} and 
-    \nbcg{} are driven by region that is not dominated by ``in-situ'' stars. 
-    Since most of these samples in comparison are not as extreme as the massive 
-    \rbcg{} galaxies, we also compare with a uniquely massive BCG at high redshift: 
-    a $10^{11.4} M_{\odot}$ BCGs with distinctive envelope at $z\sim 1.1$ 
+    Regardless of the systematic difference in median \mstar{} and details in 
+    \m2l{} estimates\footnote{We convert the \mden{} profiles to the same Chabrier 
+    IMF}, the comparison confirms that \minn{} is indeed a reasonable proxy of the 
+    ``in-situ'' mass.  Meanwhile, it also highlights that the structural differences 
+    between \rbcg{} and \nbcg{} are likely driven by processes that are not related 
+    to the ``in-situ'' phase. 
+    \update{
+    Most of these literatures that we compare with are not dominated by the extremely 
+    massive ones in the our sample, so the actual \mden{} median profile of the ``in-situ'' 
+    components for \rbcg{} and \nbcg{} galaxies could be closer to the median profiles 
+    shown in Fig.\ref{fig:discussion_1}.
+    }
+    Here, we also compare with a uniquely massive BCG at high redshift: 
+    a $\sim 10^{11.4} M_{\odot}$ BCG with distinctive ``cD''-like envelope at $z\sim 1.1$ 
     (\citealt{Liu2013}).  
     It is interesting to see that its \mden{} profile follows the median profile of 
-    \rbcg{} nicely until 20 kpc; then it becomes much steeper in the outskirt.  
-    This is quite consistent with the expectation that the inner part of the BCGs 
-    should be well developed at $z\sim 1$, but the extended stellar envelope is still 
-    assembling.
-
-    Also, it is worth noting that the relative flatten inner \mden{} profile of \rbcg{}
-    at fixed \mtot{} could be an interesting feature, although we currently lack of the 
-    resolution to investigate region $\leq 3$ kpc.  
-    It is known that major-merger induced coalesce of super-massive black hoes (SMBHs)
-    can create flattened inner profile (e.g. \citealt{Milosavljevi2002}), and recent 
-    discoveries of massive BCGs with very large core 
-    (a few kpc; e.g. \citealt{Postman2012, LopezCruz2014}) further complicate the picture.
-    On Fig.\ref{fig:m100_m10_A}, there are a few \rbcg{} galaxies with quite low 
+    $11.6\leq$\logmtot{}$<11.8$ massive galaxies reasonably inside 10-15 kpc; 
+    then the profile becomes much steeper in the outskirt.  
+    This is consistent with the expectation that the inner part of massive BCGs should 
+    be well developed at $z\sim 1$, but the extended stellar envelope is still assembling.
+
+%% ------------------------------------------------------------------------------------ %% 
+  \begin{figure*}[t]
+      \centering 
+      \includegraphics[width=\textwidth]{fig/redbcg_discussion_5}
+      \caption{
+      \update{
+          \textbf{Left}: Relation between \mtot{} and the logarithmic mass difference 
+          between \mmax{} and \mtot{} for both \rbcg{} (red square) and \nbcg{} 
+          (grey dot) galaxies.  The format is very similar to the left figure of 
+          Fig.\ref{fig:smf1}.~~
+          \textbf{Right}: The stellar mass volume-density distributions of massive galaxies 
+          after combining the \rbcg{} and \nbcg{} samples together, using both 
+          \mtot{} (black solid line) and \mmax{} (black dash line). 
+          The uncertainty for distribution using \mtot{} is shown in grey shaded region.  
+          Here, we also compare the distributions with SMF from previous works: 
+          (a): SDSS galaxies at $z\sim 0.1$ from \citet{Bernardi2013}; the \mstar{} is 
+          based on photometry from 2-D \ser{}$+$Exponential model fitting; 
+          (b): SDSS galaxies at $z\sim 0.1$ from \citet{Moustakas13} based on 
+          improved SDSS \texttt{cModel} photometry; 
+          (c): \texttt{S82-MGC} galaxies at $0.15 < z< 0.43$ from 
+          \citet{Leauthaud2016} based on PSF-matched SDSS-UKIDSS photometry.
+          Please see text for more details of the comparison.
+          }}
+      \label{fig:discussion_2}
+  \end{figure*}
+%% ------------------------------------------------------------------------------------ %%
+
+    \update{
+    Although we do not have the spatial resolution to investigate the structural 
+    difference at $\leq 3$ kpc, it is an interesting topic to keep in mind since we do 
+    notice evidence that at fixed \mtot{}, \rbcg{} galaxy tends to have lower \mstar{} 
+    within inner 5-10 kpc and flattened inner \mden{} profile. 
+    }
+    Major-merger induced coalesce of super-massive black hoes (SMBHs) can create flattened 
+    inner profile (e.g. \citealt{Milosavljevi2002}), and recent discoveries of massive 
+    BCGs with very large core (a few kpc; e.g. \citealt{Postman2012, LopezCruz2014}) 
+    further complicate the picture.
+    On Fig.\ref{fig:scaling_relation}, there are a few \rbcg{} galaxies with quite low 
     \minn{} at high \mtot{} end. 
-    After examining their images, we conclude the low \minn{} is not caused by problematic
-    photometry or exceptionally bad seeing; they could also be massive BCGs with very 
-    flattened inner \mden{} profiles.  
-    Besides the SMBH-merger theory, strong adiabatic expansion induced by strong AGN 
+    After examining them individually, we conclude that the low \minn{} is not caused 
+    by problematic photometry or exceptionally bad seeing. 
+    They could also be massive BCGs with very flattened inner \mden{} profiles.  
+    Besides the SMBH-merger theory, strong adiabatic expansion induced by powerful AGN 
     feedback was proposed to modify the inner mass distribution (e.g. \citealt{Fan2008}). 
-    The potential impact of these processes to massive galaxies, and their dependence on 
-    halo mass would be an interesting topic to investigate in the future.
-
-    \song{Move a big paragraph to Results}
-
-    \song{Ok, I'll see how to make it happen; this sounds abrupt since I used 
-    to have several subsections in the discussion section.}
-    \alexie{The beginning part of this paragraph sounds to me like the summary section.
-You could move part of this to summary and put it in bullet piont format.}.
-In the end, we want to emphasis once more \textbf{the importance of deep image
-    and appropriate method of photometry in studying the structure and assembly 
-    history of galaxies}. 
-    With the help of deep HSC images, we reliably reveal the extended stellar 
-    structures around large sample of massive central galaxies out to more than 
-    100 kpc.  
-    And, using model-independent method, we found that 
-    (1) previous de~Vaucouleur or single-\ser{} modeling method on shallower SDSS
-    images underestimates the total mass of massive galaxies; 
-    (2) even using deep HSC images, photometric method like \cmodel{} also tends 
-    to underestimate the mass. 
-    For these massive central galaxies, their extended mass distributions are 
-    simply beyond the capability of the simply modeling method.  
-    In addition, since the slope and mass contribution of the outer envelope 
-    depend on not only the total stellar mass, but also likely the halo mass. 
-    Applying the same oversimplified model to galaxies across a large range of 
-    mass and environment could result in both underestimated and biased mass 
-    estimates that can stop us getting accurate stellar mass function at the 
-    high-mass end and studying potential environmental dependence of structures. 
-    Moreover, these results also raise crucial questions like: 
-    \textbf{What is the definition of ``total'' stellar mass of galaxy? 
-    And, what is the most informative definition of stellar mass in the studies 
-    of galaxy evolution?}.
-\alexie{I think we can expand the discussion around this topic.
-We'd like to say somehting about the impact of total luminosity on the SMF.
-How about moving the left hand of Figure 3 here?
-What is the current volume of your data set compared to the volume of SDSS?
-I think we should emphasize the impact of stellar mass estimate on the SMF, especialy the large impact it has for BCGs}.
-    \song{As mentioned earlier, I can expand the discussion easily with the help 
-    from another figure, comparing with SMF from other people's work?//}
-
-    \alexie{Yes, the only thing that I just realized and pointed out in the ealier SMF figure is that to compare the SMF, we need to include everything, not just centrals.
-There are two options: 1) just show the impact on the SMF for centrals (the figure you have already) or 2) include all the galaxies and compared with previous work.
-I think that 2) is a paper inself and is beyond the scope of the papers (it becomes "Mission Creep").}
-
-    \alexie{I thought of another interesting aspect to add to the discussion.
-This I think is perhaps a nice angle to discuss.
-The total luminosity of a galaxy has an impact on abundance matching.
-Do you have the "luminosity" that you would get for each galaxy if you assumed a single sersic fit for example?
-If so, we could do the following.
-Assume a one-to-one mapping between halo mass and your M100.
-Then plot Mhalo versus the stellar mass inferred from either cmodel of the single sersic fit.
-Then we can quote the scatter in $\log(M_*)$ at fixed Mhalo that this introduces.
-This figure will be very relevent for the Santa Barabara workshop!}
-    \song{We do not have results from single Sersic models; at least not reliable enough 
-    to be used here, mostly because single Sersic works terribly for these galaxies.
-    We do have \mcmodel{}, but sorry that I failed to follows the logic here, basically this is 
-    the difference between \mtot{} and \mcmodel{} expressed in a different way, and I am not 
-    sure the scatter is due to the scatter of the mhalo-mstar relation, as the cModel 
-    ones are underestimated due to technical reasons; We can bin the \rbcg{} galaxies 
-    into a narrow $\lambda$ bin thoug, e.g. $30< \lambda < 40$, and see the scatter of 
-    \mcmodel{}, \minn{}, and \mtot{}. We can certaintly shows that the scatter is larger 
-    for mass using larger radius.  I think this point is important for the discussion
-    of the intrinsic scatter of the mhalo-mstar relation, and at very similar mhalo,
-    the outer structure may trace other properties of the halo. Let me know what do 
-    you think.\\}
-
-    \alexie{THe same idea holds if we use our M100 mass and cmodel.
-The points is just to evaluate how much extra scatter you introduce because of many people simple use naive luninosities when they do abundance mathcing.
-Your previous figures show that the luminosities of massive galaxies may be severaly underestiamted.
-How much impact does this have on abundance mathcing?
-How much extra scatter does it introduce?}
-
-    \alexie{Finally, another quick discussion paragraph could be related to finding BCGs.
-It would be interesting to have a plot of the magnitude gap between Pcen1 and Pcen 2 (the most likely and the second most likely central) with cmodel versus your estimates.
-It would be nice to show that having a better luminosty estimate will enable you to identify the BCG better (is this true?)}.
-    \song{This is interesting, and I don't know if it is true. It requires more works as 
-    I do not have the profiles for all PCEN2 galaxies, I only do it when they are more 
-    massive than the threshold.  Can we save this for later, I mean, after we send around 
-    the draft.  Although I do compare the structures of really massive satellites in 
-    these clusters with the \nbcg{} galaxies, and the results show little difference,    basically shows that the structure difference could be unique for central galaxies. 
-    I originally show a figure for this, and will send you along the e-mail.}
-
-    \alexie{If it is too much, work, skip this idea! We dont want mission creep.}
-
-    In this work, we choose mass enclosed by different, but fixed physical 
-    apertures, and find promising scientific applications for massive galaxies. 
-    But, we recognize that they may not be the best choice. 
-    For instance, central galaxies of massive halos like BCGs are known to be
-    surrounded by diffuse stellar component that does not follow the potential 
-    of the central galaxy (the intra-cluster light, or ICL; e.g. \addref{}).
-    In theory, it can contribute a large amount of stellar mass out to very 
-    large radius (e.g. \addref{}).  
-    Using the definition of \mtot{}, we can not separate the potential 
-    contribution of ICL in our \rbcg{} galaxies; and this could make complicate
-    the discussion of environmental dependence.
-\alexie{I am not sure I agree here.
-What is the "ICL"?
-How can is physically be defined?
-Can one robustly distinguish an "ICL" component from the galaxy component and how?
-Is the ICL similar to the "cD" enveloppe in the sense that we use these words all the time, but in practice, these are just one extrema of a continous galaxy population?}
-    Since most of the \rbcg{} galaxies in our sample belong to low-mass cluster 
-    like the Virgo or Fornax, we do not expect the ICL component can makes a 
-    smooth and significant contribution to the \mden{} profiles (e.g. \addref{}).
-    Even removing all \rbcg{} galaxies in $\lambda > 40$ clusters will not change 
-    our findings.  
-    However, it is still important to ask whether should we include the ICL when 
-    estimating the mass of central galaxies in massive halos.  \alexie{But what is the ICL?}
-    \song{The observational definiiton is very vague; and the theoretical one is 
-    very hard to achieve through observation, basically the stars that follows the 
-    potential of the clsuter.} \alexie{Exactly. Which is why I think we dont want to go into a big discussion on this.}
-    And, if the answer is no, which is the best way to separate the ICL component? 
-    In literature, most works studied ICL by subtracting the model for inner part
-    of the central galaxy (e.g. \addref{}).  
-    As we show in this work, when extended stellar envelopes are revealed around 
-    massive galaxies in large range of stellar and halo mass, we may have to 
-    reconsider this approach \alexie{I agree with this phrase, this is good to point out.}.
-    \song{I think I understand your point here. The thing with ICL is that any 
-    conclusion so far is quite uncertain, so I can reorganize this paragraph, 
-    point out the interesting question first, discuss it a little bit, but also 
-    shows a caveat that say ICL could play a role here, and if it does, how could 
-    they change our results.}
-
-    \alexie{I'm saying more than that. I'm saying that I don't beleive that there is necessarly a firm distinction between the galaxy and the "ICL". Might be easier to chat about this on Skype.}
+    The potential impact of these processes, and their dependence on halo mass would be 
+    an interesting topic to investigate in the future.
+
+    \update{
+    At last, we need to emphasis again that \textbf{even with very high-quality, 
+    deep imaging data, it is still very tricky to measure the ``total'' \mstar{} of 
+    these massive galaxies.}
+    There is no easy definition of ``total'' \mstar{}, both in theory and in practice. 
+    In this work, we choose to use the \mstar{} enclosed by very large, but fixed 
+    physical radius along the major photometric axis (100 kpc) as the proxy of 
+    ``total'' \mstar{}.
+    We demonstrate that this straightforward approach has the advantage of not 
+    being bothered by uncertainties in model assumptions when comparing with 2-D 
+    modeling method. 
+    This is particularly important for these massive galaxies at this imaging depth,
+    as they are intrinsically more complex than single-\ser{} model, and have very 
+    extended structure that is always hard to model. 
+    However, it is still not necessarily the best choice despite that we found 
+    interesting results vial this definition.
+    On the left of Fig.\ref{fig:discussion_2}, we compare the \mstar{} integrated within 
+    100 kpc radius and the maximum radius allowed by the profile. 
+    It is worth noting that at very large radius, the \mden{} profiles suffer from 
+    uncertainties of background subtraction and contaminations from the low
+    surface brightness envelope of nearby galaxies, which are parts of the reasons 
+    why we choose 100 kpc in the first place. 
+    Although the \mmax{} may not be very accurate, we can see that the stellar 
+    distributions of these massive galaxies certainly do not stop at 100 kpc 
+    (also see Fig.\ref{fig:avg_prof} and Fig.\ref{fig:prof_1}). 
+    The average mass growth outside 100 kpc is quite small (average: $\sim 0.04$ dex),
+    we can see it depends on \mtot{} and slightly on environment. 
+    For our results, we have verify their robustness against the choice of maximum 
+    radius by replacing \mtot{} with \mmax{}. 
+    But, this can still be an important issue when it comes to topic that is very 
+    sensitive to the \mstar{} value: e.g.~the slope and evolution of stellar mass 
+    function at high-massive end. 
+    On the right side of Fig.\ref{fig:discussion_2}, we show the \mstar{} 
+    volume-density distributions of the combined \rbcg{} and \nbcg{} samples using 
+    both \mtot{} and \mmax{}.  
+    Apparently, the slope of the very high-mass end ($> 10^{11.8} M_{\odot}$) is quite 
+    sensitive to even very small change of \mstar{}.
+    }
+
+    \update{ 
+    To further highlight the importance of this issue, we also compare our 
+    volume-density distributions with published SMFs:  
+    (1). SMF for SDSS-\textit{GALEX} sample of $z\sim 0.1$ galaxies from 
+    \citep{Moustakas13}. 
+    The total luminosity is based on SDSS \cmodel{} one; the \m2l{} is derived 
+    vial SED fitting results from \texttt{iSEDfit}, and the assumptions are very similar 
+    to the ones used in this work. 
+    (2). SMF for $z\sim 0.1$ SDSS galaxies from \citep{Bernardi2013}. 
+    The total luminosity is based on 2-D \texttt{SerExp} models (\ser{}$+$
+    Exponential disk model; integrated to infinity), which systematically recover 
+    more flux comparing with the \cmodel{} ones at high-luminosity end. 
+    The \m2l{} is also from SED fitting assuming a Chabrier IMF.  
+    (3). SMF for $0.15 < z < 0.30$ galaxies from the \texttt{S82-MGC} sample from 
+    \citep{Leauthaud2016}.  The authors use PSF-corrected aperture photometry, and 
+    SED fitting using \texttt{iSEDfit} to estimate \mstar{}. 
+    It is worth noting here that careful comparison of SMF is beyond the scope of 
+    this work, one should carefully separate the systematic uncertainties from 
+    photometry and assumptions of stellar population models (e.g. \citealt{Bernardi2016})
+    Here, we will only focus on slope of the SMF at very high-mass end. 
+    And since all \mstar{} are based on similar SED fitting procedure assuming the same
+    IMF, differences in photometry (``total'' luminosity) should dominate the 
+    differences in SMF. 
+    We can see that, even at low-$z$, the SMF is still quite uncertain just due to 
+    uncertainties in photometry. 
+    The ones using \cmodel{} and small aperture photometry often show steeper slope 
+    at high-mass end as they can not capture the flux in the extended envelopes. 
+    For the \texttt{SerExp} one, due to the more careful treatment of image fitting 
+    process and the flexibility of the \ser{} model, it is not surprising that it can 
+    recover more flux.  
+    However, when comparing with our results, it is interesting to see that the 
+    result from \citep{Bernardi2013} shows even shallower slope at high-mass end.  
+    This could be due to many issues: e.g. integration to infinity overpredicts the 
+    \mstar{} in the outskirt; high \ser{} index may lead to overestimate of \mstar{} 
+    in the central region; or simply because the models for these massive galaxies have 
+    larger uncertainties when shallower SDSS images are used. 
+    This issue deserves more attention, and we will investigate into this more through 
+    different definitions of ``total'' \mstar{}, including the ones from 2-D models.  
+    And, it is also worth mentioning that, in this work, we do not separate the 
+    potential intra-cluster light component (ICL; e.g. \addref{}), but rather treat 
+    the stellar distributions out to 100 kpc as a physically integrated and connected 
+    structure.  
+    So far, the best case study of ICL comes from the extremely deep images of the 
+    Virgo cluster (e.g. \citealt{Mihos2016}). 
+    It reveals that the stellar halo of the BCG can smoothly extend beyond 100 kpc, 
+    and the growth of the ICL component is indeed connected to the assembly of the 
+    central galaxy.
+    For our \rbcg{} galaxies, we also do not find evidence that there is a 
+    separated stellar component in the very outskirt. 
+    The \mden{}, ellipticity, and optical color all show very smooth variation 
+    against radius.  
+    Given that there is no physically motivated definition of ICL when it comes
+    to isolate the ICL component using just the photometric data, we think this topic 
+    is beyond the scope of this work, and save it for discussion in the near future.  
+    }
+
+%    \update{
+%    Another issue when measuring the ``total'' \mstar{} of massive galaxies, especially 
+%    the ones from dense environments, is the impact from the intra-cluster light 
+%    component (ICL; e.g. \addref{}).  
+%    As stars that follow the gravitational potential of the halo rather than the 
+%    central galaxy, they can contribute a lot to the \mstar{} budget in the inner 
+%    region of massive clusters based on simulations (e.g. \addref{}); and their 
+%    origin and evolution are still considered as open question (e.g. \addref{}). 
+%    However, it is almost impossible to apply the ``physical'' definition of ICL
+%    to photometric data alone; and it is still not clear whether this component has 
+%    clear difference with the extended ``cD'' envelopes of massive BCGs. 
+%    Although some observational constraints support the idea that the \mstar{} fraction
+%    of the ICL component is quite large (e.g. \addref{}), these works often adopte
+%    naive model assumption for ICL or can not prove the physical differences between 
+%    the ICL and outskirts of BCGs. 
+%    In case that ICL does contribute a lot to the \mden{} profiles of \rbcg{} galaxies 
+%    inside 100 kpc, it could mean that the environmental dependence of structures may 
+%    not be that clear, or it is only reflected in the ICL component, not the main body
+%    of the central galaxy. 
+%    However, we need to point out: 
+%    (1). observations seem to suggest that, even in very massive clusters, ICL 
+%    starts to dominate the \mden{} profile outside 80-100 kpc 
+%    (e.g. \addref{} Zibetti et al. 2005; Bernardi et al. 2007; Lauer et al. 2007). 
+%    That is also one of the reasons to choose 100 kpc instead of larger radius when
+%    estimating ``total'' \mstar{}. 
+%    (2). most of the \redm{} cluster in this work are not very massive ones. 
+%    For those low-mass clusters, the contribution from ICL may not be that significant.
+%    For instance, in Virgo cluster, extremely deep photometry reveals that the ICL 
+%    component mainly consists of many separated structures (e.g. ``tail'', ``plume''),  
+%    but not in the form of a giant envelope that surrounds the BCG (e.g. \addref{}). 
+%    This situation may apply to many of our \rbcg{} galaxies. 
+%    Moreover, our results remain safe even when after excluding all the central galaxies 
+%    of clusters richer than $\lambda > 40$.
+%    }
+
+    % TODO: Discussion about abundance matching 
+%    \alexie{I thought of another interesting aspect to add to the discussion. 
+%        This I think is perhaps a nice angle to discuss. 
+%        The total luminosity of a galaxy has an impact on abundance matching. 
+%        Do you have the "luminosity" that you would get for each galaxy if you
+%        assumed a single sersic fit for example? 
+%        If so, we could do the following. 
+%        Assume a one-to-one mapping between halo mass and your M100. 
+%        Then plot Mhalo versus the stellar mass inferred from either cmodel of 
+%        the single sersic fit. 
+%        Then we can quote the scatter in $\log(M_*)$ at fixed Mhalo that this 
+%        introduces. 
+%        This figure will be very relevent for the Santa Barabara workshop!}
+%    \song{We do not have results from single Sersic models; 
+%        at least not reliable enough to be used here, mostly because single Sersic 
+%        works terribly for these galaxies.
+%        We do have \mcmodel{}, but sorry that I failed to follows the logic here, 
+%        basically this is the difference between \mtot{} and \mcmodel{} expressed 
+%        in a different way, and I am not sure the scatter is due to the scatter of 
+%        the mhalo-mstar relation, as the cModel ones are underestimated due to 
+%        technical reasons; We can bin the \rbcg{} galaxies into a narrow $\lambda$ 
+%        bin thoug, e.g. $30< \lambda < 40$, and see the scatter of 
+%        \mcmodel{}, \minn{}, and \mtot{}. We can certaintly shows that the scatter is larger 
+%        for mass using larger radius.  I think this point is important for the discussion
+%        of the intrinsic scatter of the mhalo-mstar relation, and at very similar mhalo,
+%        the outer structure may trace other properties of the halo. Let me know what do 
+%        you think.\\}
+%    \alexie{The same idea holds if we use our M100 mass and cmodel. 
+%        The points is just to evaluate how much extra scatter you introduce because 
+%        of many people simple use naive luninosities when they do abundance mathcing. 
+%        Your previous figures show that the luminosities of massive galaxies may be 
+%        severaly underestiamted. How much impact does this have on abundance mathcing? 
+%        How much extra scatter does it introduce?}
+
+    % TODO: Discussion of BCG finding
+%    \alexie{Finally, another quick discussion paragraph could be related to finding BCGs. 
+%        It would be interesting to have a plot of the magnitude gap between Pcen1 and Pcen 2 
+%        (the most likely and the second most likely central) with cmodel versus your 
+%        estimates. It would be nice to show that having a better luminosty estimate will 
+%        enable you to identify the BCG better (is this true?)}.
+%    \song{This is interesting, and I don't know if it is true. It requires more works as 
+%        I do not have the profiles for all PCEN2 galaxies, I only do it when they are more 
+%        massive than the threshold.  Can we save this for later, I mean, after we send around 
+%        the draft.  Although I do compare the structures of really massive satellites in 
+%        these clusters with the \nbcg{} galaxies, and the results show little difference,    
+%        basically shows that the structure difference could be unique for central galaxies. 
+%        I originally show a figure for this, and will send you along the e-mail.}
+%    \alexie{If it is too much, work, skip this idea! We dont want mission creep.}
 
@@
     %\label{ssec:future}
-    These results are broadly consistent with the prediction of the ``two-phase''
-    scenario: the massive central galaxies in more massive halos should experience 
-    more minor, dry mergers that accumulate more stars in the outskirts. 
+    %These results are broadly consistent with the prediction of the ``two-phase''
+    %scenario: the massive central galaxies in more massive halos should experience 
+    %more minor, dry mergers that accumulate more stars in the outskirts. 
+    \update{
     These results also highlight the advantages of HSC survey in studying the 
@@
     central galaxies. 
-    At the same time, we will work on better data reduction of HSC images by 
-    improving the deblending in crowded regions and the accuracy of background 
-    subtraction. 
-    This can help provide more reliable SED fitting results, and push the 
-    photometric limit to even lower surface brightness.
-
-    Right now, we still rely on the \redm{} catalog from SDSS and spectroscopic 
-    redshift from SDSS and BOSS.  
-    Running \redm{} algorithm or similar group/cluster finder on HSC catalogs 
-    can greatly help us extend the discussion to lower \mhalo{} and higher 
-    redshift. 
-    Better selection of satellites in massive halos will also open up the 
-    possibility to study ``environment'' within the halo.
-    It is interesting to see whether there is any structural difference
-    between central and satellite galaxy at similar \mstar{}.
-
-    We will work on careful 2-D photometric modeling to these massive galaxies.
-    Under the same principle outlined by \citealt{Huang2013a}, we will explore 
-    different models, and gradually build up the complexity to fit these galaxies 
-    better.
-    With the 2-D modeling approach, we can deal with the seeing and background
-    subtraction easier, and provide better maps the stellar mass distributions. 
-    We are also working on characterizing the color distributions of these 
-    galaxies better via multi-band modeling with reasonable constraints (e.g. 
-    \citealt{Huang2016}).
-
-    Primarily designed as a cosmological endeavor, the HSC survey has excellent 
-    images to greatly improve the the weak lensing analysis of massive galaxies. 
-    The next major step will be to investigate the connections between massive 
-    galaxies and their halos with the help of the weak lensing signals for 
-    different groups of massive galaxies (e.g. binned by \mtot{}, \minn{}, 
-    size\etal).
-    Joining the stellar mass distributions and the weak lensing signals together, 
-    we can trace the impacts from a series of physical processes 
-    (strength and type of AGN feedback, merger rate, typical mass ratio of mergers
-    \etal). 
-    To help us have better physical insights, we will directly compare our results 
-    with predictions from cosmological hydro-simulations such as 
+    In the near future, besides using larger samples directly selected using the 
+    HSC photometry and photometric redshift,
+    we will improve the modeling of massive galaxies through careful 2-D method 
+    (e.g.\ \citealt{Huang2013a}) and by including multiband data 
+    (e.g.\ \citealt{Huang2016}).  
+    We will also try to get more physical insights with the help of the HSC weak 
+    lensing analysis and comparisons with cosmological hydro-simulations such as 
     Illustris (\citealt{Vogelsberger2014}, \citealt{Genel2014}), 
@@
     or \textit{Horizon-AGN} (\citealt{Dubois2014}).
+    }
+
+%    At the same time, we will work on better data reduction of HSC images by 
+%    improving the deblending in crowded regions and the accuracy of background 
+%    subtraction. 
+%    This can help provide more reliable SED fitting results, and push the 
+%    photometric limit to even lower surface brightness.  
+%    
+%    Right now, we still rely on the \redm{} catalog from SDSS and spectroscopic 
+%    redshift from SDSS and BOSS.  
+%    Running \redm{} algorithm or similar group/cluster finder on HSC catalogs 
+%    can greatly help us extend the discussion to lower \mhalo{} and higher 
+%    redshift. 
+%    Better selection of satellites in massive halos will also open up the 
+%    possibility to study ``environment'' within the halo.
+%    It is interesting to see whether there is any structural difference
+%    between central and satellite galaxy at similar \mstar{}.
+%    
+%    We will work on careful 2-D photometric modeling to these massive galaxies.
+%    Under the same principle outlined by \citealt{Huang2013a}, we will explore 
+%    different models, and gradually build up the complexity to fit these galaxies 
+%    better.
+%    With the 2-D modeling approach, we can deal with the seeing and background
+%    subtraction easier, and provide better maps the stellar mass distributions. 
+%    We are also working on characterizing the color distributions of these 
+%    galaxies better via multi-band modeling with reasonable constraints (e.g. 
+%    \citealt{Huang2016}). 
+%    
+%    Primarily designed as a cosmological endeavor, the HSC survey has excellent 
+%    images to greatly improve the the weak lensing analysis of massive galaxies. 
+%    The next major step will be to investigate the connections between massive 
+%    galaxies and their halos with the help of the weak lensing signals for 
+%    different groups of massive galaxies (e.g. binned by \mtot{}, \minn{}, 
+%    size\etal).
+%    Joining the stellar mass distributions and the weak lensing signals together, 
+%    we can trace the impacts from a series of physical processes 
+%    (strength and type of AGN feedback, merger rate, typical mass ratio of mergers
+%    \etal). 
+%    To help us have better physical insights, we will directly compare our results 
+%    with predictions from cosmological hydro-simulations such as 
+%    Illustris (\citealt{Vogelsberger2014}, \citealt{Genel2014}), 
+%    EAGLE (\citealt{Schaye2015}, \citealt{Crain2015}), 
+%    or \textit{Horizon-AGN} (\citealt{Dubois2014}).
 
@@
 \acknowledgements
+
+  % Personal 
+  SH thanks F.S.Liu for sharing the data from his work.
 
@@
     \label{app:A}
+
+    \update{
+    Here, we briefly describe the procedure to extract 1-D surface brightness profile 
+    of our massive galaxies using \texttt{Ellipse}.
+    }
+
+    %At low surface brightness regime, the final profile can be sensitive to several 
+    %configuration parameters of \texttt{Ellipse}.  
+    %After some tests, we choose to use 0.1 dex in logarithm as the step in semi-major 
+    %axis length between successive ellipses, and we use the median pixel value over the
+    %elliptical annulus after rejecting outlier pixels twice with $3\sigma$-clipping.
+    %These parameters are selected to make the final profile less affected by any nearby
+    %objects, and please see Appendix.~B for more details about the extraction of 
+    %1-D profile.
+
+    %We also apply the isophotes from $i$-band images to other bands in 
+    %``force-photometry'' mode \texttt{Ellipse} run to get rough estimates of 
+    %color profiles.  
+    %Without taking the difference in seeing and background into account, 
+    %these color profiles can not be used for physical discussion. 
+    %But with the help of $K$-correction from the next section, we show that there 
+    %is no systematic difference in color gradient between \rbcg{} and 
+    %\nbcg{} sample.
+
 %% ------------------------------------------------------------------------------------ %% 
@@
             show the best-fitted results, along with the high-resolution spectrum for
-            this model recontructed using the synthetic spectra from \texttt{FSPS}. 
+            this model reconstructed using the synthetic spectra from \texttt{FSPS}. 
             Top-left corner shows the best-fit stellar population parameters, and 
@@
         \includegraphics[width=\textwidth]{fig/redbcg_isedfit_2.pdf}
-        \caption{Relationships between \mstar{} and certain stellar population 
-            parameter using \texttt{iSEDfit}. 
-            The left figures are for the \rbcg{} sample, while the right ones are 
+        \caption{Relationships between \mstar{} and other stellar population 
+            parameters using the results from \texttt{iSEDfit}. 
+            The \textbf{left} figures are for the \rbcg{} sample, and the 
+            \textbf{righ}t ones are 
             for the \nbcg{} sample. 
-            They are both color-coded using the mass-weighted stellar age. 
-            The four stellar population properties shown here are: 
-            1) mass-weighted stellar age in Gyr (top-left); 
-            2) SFR-weighted stellar age in Gyr (bottom-left); 
-            3) mass-weighted stellar metallicity in unit of solar value (top-right);
-            4) dust extinction value in magnitude (bottom-right).}
+            They are both color-coded using the redshift of the object, while 
+            their sizes reflect the magnitude differences in $i$-band between 
+            the observed and best-fit value. 
+            The four stellar population properties are: 
+            1) \textbf{Top-left}: mass-weighted stellar age in Gyr; 
+            2) \textbf{Bottom-left}: \m2l{} in $i$-band; 
+            3) \textbf{Top-right}: mass-weighted stellar metallicity in unit of Solar 
+            value;
+            4) \textbf{bottom-right}: dust extinction values in magnitude.}
         \label{fig:ised_2}
@@
             assumptions. 
-            In each figure, we plot the default \mstar{} values against their 
-            differences with the results using other models. 
-            The top (bottom) row shows comparisons for the \rbcg{} (\nbcg{}) sample. 
-            The results involved here are labeled: 
+            In each figure, we plot the \mstar{} from default model against their 
+            differences with other models. 
+            The top (bottom) row shows the comparisons of the \rbcg{} (\nbcg{}) sample. 
+            The four models involved here are labeled as: 
             (A): default one; 
-            (B): using the Salpeter IMF instead of the Chabrier one (Left column);
+            (B): using the Salpeter IMF instead of the Chabrier one 
+                (\textbf{Left column});
             (C): using the BC03 synthetic population model instead of the FSPS one
-                 (Middle column);
-            (D): assume that there is no dust extinction (Right column). 
-            On each figure, a horizontal line shows the zero difference level, along
-            with the grey shaded region that highlights the typical uncertainty of 
-            the \mstar{}-differences. 
-            We also show the histogram of the \mstar{}-differences on the right.}
+                (\textbf{Middle column});
+            (D): assume that there is no dust extinction (\textbf{Right column}). 
+            On each figure, the grey shaded region highlights the uncertainty 
+            of the $\log($\logms{}$)$ using typical \mstar{} uncertainties from 
+            both sides. 
+            For each comparison, we highlight the median $\chi^{2}$ value, and the fraction
+            of galaxies with $\chi^{2} > 10.0$ at the top. 
+            We also show the histogram of the \mstar{}-differences on the right panel.}
         \label{fig:ised_3}
@@
 %% ------------------------------------------------------------------------------------ %% 
-\begin{figure*}[hbt!]
+\begin{figure*}[bt!]
     \centering 
@@
 
-        In cases of these $M_{\star, \mathrm{GAMA}}$-matched samples, the differences
-    of median profiles are very robust.
-
 %% ------------------------------------------------------------------------------------ %%
@@
 %% ------------------------------------------------------------------------------------ %% 
-\begin{figure}[htb!]
+\begin{figure}[tb!]
     \centering 
@@
         Fig.\ref{fig:avg_prof}.}
-    \label{fig:D1}
+    \label{fig:avg_prof_z}
 \end{figure}    
@@
 
-    As the massive galaxies in our samples span quite a bit in both redshift and \mtot{}, 
-    it is important to evaluate the impact from PSF on the \mden{} profiles at different 
-    redshift. 
-    In Fig.\ref{fig:D1}, we group the \rbcg{} and \nbcg{} galaxies at  
-    $11.6 \le$\logmtot$< 11.9$ into two $z$ bins ($0.3\leq z<0.4$ and 
-    $0.4\leq z<0.5$). 
-    We did not match the \mtot{} distributions in two $z$ bins, so slight difference in 
-    average \mtot{} can be expected. 
-    With the same seeing condition, the \mden{} profile of galaxy at higher redshift is 
-    more vulnerable to the PSF smearing effect in the center, while suffers more in the 
-    outskirt due to cosmological dimming and background noise.  
-    Fig.\ref{fig:D1} clearly shows that, although the median profiles of the same sample 
-    in two redshift bins follow each other well outside 10 kpc, they start to differ in 
-    the central 2-3 kpc as the one from higher redshift bin has more flattened profile 
-    due to PSF smearing effect.  
+    \update{
+    As the massive galaxies in this work span a redshift range that can not be ignored, 
+    it is important to evaluate the impact from PSF and imaging depth on the \mden{} 
+    profiles at different redshift. 
+    In Fig.\ref{fig:avg_prof_z}, we group the \rbcg{} and \nbcg{} galaxies withn 
+    $11.6 \le$\logmtot$< 11.9$ into two $z$ bins ($0.3\leq z<0.4$ and $0.4\leq z<0.5$). 
+    }
+
+    \update{
+    With similar seeing, the \mden{} profile of galaxy at higher redshift is more 
+    vulnerable to the PSF smearing effect in the center. 
+    Also, at the same imaging depth, it is harder to reach to the same \mden{} level
+    in the outskirt due to cosmological dimming and background noise.  
+    Fig.\ref{fig:avg_prof_z} shows that, although the median profiles for the same sample 
+    in two redshift bins follow each other very well outside 10 kpc, they become quite
+    different in the central 3-4 kpc. 
+    The one from the higher redshift bin becomes more flattened due to PSF smearing 
+    effect.  
     Meanwhile, we notice that the median profiles of \rbcg{} and \nbcg{} in the 
-    same $z$ bin are very similar to each other in the region affected by seeing.   
-    This comparison confirms the radius range that is sensitive to seeing and 
-    redshift distribution is well constrained within the grey-shaded area.
-    It also suggests that it is important to match the redshift distributions between 
-    samples before we can compare their \mden{} profiles or other properties at inner 
-    region, as we did in this work. 
-    In the outskirt, within 100-150 kpc, we see no difference in the median \mden{} 
-    profiles caused by redshift distributions. 
-    We therefore conclude that it is safe to study the \mden{} profile within this 
-    radius range for massive galaxies at $z<0.5$ using HSC images.
+    same $z$ bin are very similar in the central region affected by seeing.   
+    }
+
+    \update{
+    This comparison confirms that the redshift range and difference in seeing do not 
+    bother the \mden{} comparison outside inner 5 kpc.
+    And it demonstrates the importance is to match the redshift distributions between 
+    samples before we can compare the \mden{} profiles in the inner region. 
+    In the outskirt, we see no difference in the median \mden{} profiles that may be 
+    related to the redshift range and relative background level. 
+    We therefore conclude it is safe to study the \mden{} profile within 100 kpc for 
+    massive galaxies at $z < 0.5$ via deep HSC images.
+    }
 
@@
 
-    \song{Still need some adjustments}
-
-    As stellar mass is considered the most important parameter in determining the 
-    structure and other properties of massive galaxies, it is crucial to make sure 
-    the comparison is conducted at ``fixed stellar mass''. 
-    And, since we directly compare the stellar mass distributions across very large 
-    range in radius, it is also important to make sure that differences in physical 
-    size of PSF (for more discussion on this issue, please see Appendix.\ref{app:C}) 
-    and imaging depth do not affect the result.    
-    In practice, we achieve these by matching the \rbcg{} and \nbcg{} samples in 
-    the distributions of \mstar{} and redshift in the mass range where both 
-    samples have decent completeness.  
-    Since the \rbcg{} sample is much smaller in size, we match the \nbcg{} sample to it 
-    by searching for the $N$ nearest neighbours on the $M_{\star}$-redshift 
-    plane using the KDTree algorithm provided by \texttt{scikit-learn} Python 
-    library (\citealt{scikit-learn}). 
-    The quality of the matched sample is evaluated by not just the median values 
-    of stellar mass and redshift, but also the kernel density distributions (KDE) 
-    of these two properties.
-    For \mstar{}, we use a Gaussian kernel with width equals to the typical 
-    uncertainty of the mass estimate (0.06-0.10);
-    and for redshift, we choose 0.025 as the width of the Gaussian kernel. 
-    As we only keep unique \nbcg{} galaxies in the matched sample, we manually adjust 
-    the value of $N$ to achieve the most similar distribution. 
-    In case that the distribution of stellar mass or redshift for \rbcg{} is 
+    \update{
+    As we mentioned a few times, it is crucial to match the distributions of stellar 
+    mass between two samples before we can safely compare their structural properties.
+    And, according to Appendix.\ref{app:D} and Fig.\ref{fig:avg_prof_z}, we should match 
+    the redshift distributions at the same time to compare the \mden{} profiles directly.
+    We achieve these by matching the \rbcg{} and \nbcg{} samples in their distributions 
+    of \mtot{} (or \minn{}) and redshift within reasonable ranges.  
+    Since the \rbcg{} sample normally has smaller size, we match the \nbcg{} sample to it 
+    by searching for the $N$-nearest neighbours on the $M_{\star}$-redshift plane 
+    using the KDTree algorithm provided by the \texttt{scikit-learn} Python library 
+    (\citealt{scikit-learn}). 
+    We evaluate the quality of the matching results not just through the median \mstar{}
+    and redshift values, bu also via the the distributions of these parameters 
+    (both histograms and kernel density distributions) 
+    For \mstar{}, we use a Gaussian kernel with width that is close to the typical 
+    uncertainty of the mass estimate (0.06-0.10.
+    And for redshift, we choose 0.025 as the width of the Gaussian kernel. 
+    As we only keep the unique \nbcg{} galaxies in the matched sample, we manually 
+    adjust the value of $N$ to achieve the best match. 
+    When the distribution of \mstar{} or redshift of the \rbcg{} sample is clearly
     bi-model, we also try to split the sample into two, and match them separately.
     Normally $N$ is between 3 to 8.
-
-    \mstar{} within different radius traces different physical processes and 
-    different epochs in the assembly history.  
-    In this section, we match the two samples using our proxy of ``total'' stellar 
-    mass, which is the \mstar{} within 100 kpc radius.  
-    This choice reflects the stellar mass distributions we can safely measure using 
-    model-independent approach given the current depth of the image and the accuracy 
-    of sky background subtraction.
-    For galaxies at $11.6 \leq \log(M_{\star}/M_{\odot}) < 11.9$, 100 kpc equals to 
-    5-8 times of their effective radius, hence should enclose most their stellar mass.
-    Also, for a fraction of massive \rbcg{} galaxies, the intra-group/cluster light
-    (IGL/ICL) could dominate their mass profiles outside 100 kpc (\addref), and 
-    complicate the comparison with the \nbcg{} galaxies.  
-    We will discuss these issues later in Section \ref{sec:discussion}, but in 
-    conclusion, the proxy of total \mstar{} and the potential ICL component should 
-    not affect the results.
+    }
+
+    \update{
+    In Fig.\ref{fig:match}, we demonstrate this process using the matching results for 
+    the \mtot{}-matched samples in Fig.\ref{fig:prof_1} (Left) and the \minn{}-matched 
+    samples in Fig.\ref{fig:prof_1} (Right). 
+    As one can see, the two samples are well matched in the distributions of \mtot{}
+    (or \minn{}) and redshift.  
+    For all the \mden{} comparisons in this work, we match the samples in the same 
+    way, and achieve matching results with similar quality. 
+    }
 
@@
 
-    \song{Need some text!}
+    \update{
+    In Fig.\ref{fig:prof_1} and Fig.\ref{fig:prof_2}, we compare the \mden{} profiles of 
+    \mtot{}- and \minn{}-matched samples of \rbcg{} and \nbcg{} galaxies. 
+    Although we carefully choose the mass, redshift, and richness ranges to compare with, 
+    it is still worth verifying the robustness of these results through changing these 
+    criteria a little. 
+    We show the results of these tests in Fig.\ref{fig:prof_3} and Fig.\ref{fig:prof_4}, 
+    and describe them in the text. 
+    }
+
+    \update{
+    For the \mtot{}-matched samples, we show the results of the following tests: 
+    }
+
+    \begin{enumerate}
+        \item \update{
+            Match the \rbcg{} and \nbcg{} samples in a lower redshift bins 
+            ($0.30 < z < 0.42$), and in the same \mtot{} bin (Left). 
+            The samples become slightly smaller, hence the uncertainty in their 
+            median profiles should be larger.  But the results are the same.
+            }
+        \item \update{
+            Including the \rbcg{} galaxies from poorer clusters ($20 < \lambda < 30$).
+            Considering the uncertainty of the $\lambda$ estimates, this makes the 
+            \rbcg{} and \nbcg{} samples overlap more in their \mhalo{}.  
+            As expected, this makes the differences in the inner region slightly less
+            significant, but the overall results are the same. 
+            } 
+        \item \update{
+            In stead of using \mtot{}, we are using the \mmax{} value, which is the 
+            maximum stellar mass by integrating the \mden{} profiles to the largest 
+            radius allowed by the image.  
+            It may suffer from the uncertainties of the background subtraction and 
+            potential contaminations from the outskirts of nearby bright galaxies. 
+            Also, it may include contribution from the ICL component for a fraction 
+            of \rbcg{} galaxies. 
+            As discussed in the Section.\ref{sec:discussion}, this on average increases 
+            the \mstar{} value by a little bit; and it seems that the \rbcg{} on average
+            increases more compared to the \nbcg{} ones in the same \mtot{} bin. 
+            Since this shifts the mass of all galaxies toward the higher-mass end a 
+            little, we increase the upper limit of mass by 0.05 dex too. 
+            The differences in the \mden{} profiles remain very similar.
+            }
+    \end{enumerate}
+
+    \update{
+    We also test the robustness of the \mtot{}-matched results using the samples with 
+    spectroscopic redshift, the samples in the three GAMA fields, and the \rbcg{} samples 
+    after excluding the ones from rich clusters ($\lambda > 40$).  
+    Limited by the space, we do not show the results here, but they all demonstrate the 
+    robustness of the results very well. 
+    }
+
+    \update{
+    For the \minn{}-matched samples, we test the robustness of the results shown in 
+    Fig.\ref{fig:prof_2} by: 
+    }
+
+    \begin{enumerate}
+        \item \update{
+            matching the two samples using both \minn{} and the \mstar{} within 15 kpc 
+            at the same time.  
+            This makes the two median \mden{} profiles very similar inside 10-15 
+            kpc, while the result in the outskirt remains the same.
+            }
+        \item \update{
+            to make sure the two samples are comparable in their overall assembly history,
+            only including the very massive galaxies that have \logmtot{}$>11.5$. 
+            This reduces the sample sizes, and also exclude a fraction of \nbcg{} galaxies
+            that are less massive and more ``compact''.  
+            This does not bother the result at all.
+            }
+    \end{enumerate}
 

### 2017-01-16 draft/ms_v3.tex
New Tex draft

--- 2017-01-16 draft/ms_v2.tex
@@
 % Version 1; emulateapj format; Edited by SH and AL
+% Version 2; emulateapj format; Edited by SH and AL
 
@@
 \DeclareGraphicsExtensions{.pdf,.png,.jpg}
+%\input psfig.tex
 
@@
 \newcommand{\alexie}[1]{\textcolor{blue}{\textbf{[Alexie: #1]}}}
-\newcommand{\rewrite}[1]{\textcolor{green}{\textbf{[Rewrite: #1]}}}
-
+\newcommand{\kevin}[1]{\textcolor{green}{\textbf{[Kevin: #1]}}}
 \newcommand{\update}[1]{\textcolor{Bittersweet}{#1}}
@@
 \shortauthors{HUANG ET AL.}
-\slugcomment{Draft version 0}
+\slugcomment{Draft version 2}
 
@@
 
-\title{Environmental Dependence of the Structures of Massive Central 
-       Galaxies at $z=0.4$ ....... or ... A Detection of the Enviromental Dependence of The Stellar Halos of Massive Galaxies}
+%\title{Environmental Dependence of the Structures of Massive Central 
+%       Galaxies at $0.3 < z < 0.5$}
+
+\title{A Detection of the Environmental Dependence of the Stellar Halos of 
+       Massive Central Galaxies}
 
@@
       \includegraphics[width=\textwidth]{fig/redbcg_m100_m10_compare}
-      \caption{Three-color images for a subsample of massive galaxies at $z\sim 0.4$, and with similar values for their stellar masses within a fixed 10 kpc radius (indicated by the 
+      \caption{Three-color images for a subsample of massive galaxies at similar redshift
+      		($\sim 0.4$), and with similar \mstar{} inside inner 10 kpc (indicated by the 
             dash-line cicle on top-left figure; 
             $11.2<\log (M_{\star,10\ \mathrm{kpc}}/M_{\odot})<11.3$). 
-Galaxies are rank ordered from top to bottom and from left to right by their mass within 100 kpc which varies from $10^{11.2} M_{\odot}$ to $10^{11.7} M_{\odot}$.
-At fixed "inner" mass $M_{\star,10}$, massive galaxies display a large diversity in their outer profiles.
-Red boxes indicate galaxies in halos more massive then xxxxx.
+            However, they span quite a large range in \mstar{} within 100 kpc 
+            (highlighted by the solid bar on the top-left figure). 
+            From top-left to bottom-right, their \mtot{} increases from 
+            $10^{11.2} M_{\odot}$ to $10^{11.7} M_{\odot}$.
+            The three galaxies from \rbcg{} sample are highlighted via red frames.
             }
@@
     \end{itemize}
+
+    \update{
+    In the past decade, the mass assembly history and structural evolution of massive 
+    ETGs remain an active topic.  
+    More convincing evidence from observations of massive galaxies at high redshift 
+    suggest that the progenitors of massive elliptical galaxies today are quite different 
+    in structural properties (e.g. \citealt{Bezanson2009}, \citealt{vanDokkum2010}).  
+    Collectively, they need to increase their ``size'' ($R_{\mathrm{e}}$) by a factor 
+    of 2 to 4 (e.g. \citealt{Newman2012}, \citealt{vdWel2014}), perhaps decrease the 
+    central stellar velocity dispersion a little (e.g. \citealt{vandeSande2011}, 
+    \citealt{Belli2014}) without changing their inner \mden{} profiles too much 
+    (e.g. \citealt{Szomoru2012}, \citealt{Patel2013}) and  in the last 8-10 Gyrs.  
+    With the help from better simulations, the promising ``two-phase'' formation 
+    scenario seems to be able to deal with these challenges well (e.g. 
+    \citealt{Oser2010}, \citealt{Oser2012}).
+    However, it raises additional questions.
+    As the massive central galaxies in more massive halos should have different mass 
+    assembly history, experience more (minor) mergers than the ones in smaller halos, 
+    we expect to see certain structural properties depend on ``environment''. 
+    Interestingly, although hints of such dependence have been noticed at high redshift 
+    (e.g. \citealt{Papovich2012}, \citealt{Delaye2014}), no clear evidence has been found 
+    at low redshift (e.g. \citealt{Nair2010}, \citealt{HCompany13}). 
+    }
 
@@
         \caption{Left: example of the 1-D surface brightness and ellipticity profile 
-            for a massive galaxy at $z=0.23$ in the $i$-band using \texttt{Ellipse}. 
-            In this work, we always show the radial profile using a $R^{1/4}$ scaling on the x-axis.
-By using this scaline, ETGs that follow exact de Vaucouleurs profiles with have luminosity profiles that appear on stright lines in our Figures.
-The dash-line shows the surface brightness profile after correcting the background \alexie{no dashed line?}.
+            for a massive galaxy at $z=0.23$ in $i$-band using \texttt{Ellipse}. 
+            In this work, we always show the radial profile in $R^{1/4}$ scale as it 
+            is the most appropriate one to show the structural details of massive 
+            ETGs at both inner and outer regions. 
+            The dash-line shows the surface brightness profile after correcting the 
+            background. 
             We also plot the brightness profile of the PSF model normalized at the 
             central surface brightness of the galaxy to highlight the region affected 
-            by seeing. The grey shaded region highlights the region most affect by seeing ($r<$xxx kpc).
+            by seeing. 
             On the top panel, the dash line shows the ellipticity used for the final 
-            isophote. Right: the masked $i$-band image of this galaxy with the isophotes extracted 
-            by \texttt{Ellipse}. The thick dotted line highlights the isophote with $\mu_{i}\sim 28.5$~\sb.}
-            %\alexie{Can we add physical radii at the top left since $R^{1/4}$ is not 
-            %    very intuitive. On the right hand side, why show the background as blue, 
-            %    instead of showing the actual image of the galaxy with masks overlaid? 
-            %    Add units to x axis of right hand side. 
-            %    Red text on left hand side, replace with "1D profile of a $10^{xx}$ 
-            %    M$_{\odot}$ galaxy at $z=xx$}.}
+            isophote.~~~ 
+            Right: the masked $i$-band image of this galaxy with the isophotes extracted 
+            by \texttt{Ellipse} overlaid. 
+            The thick, green isophote highlights the one with $\mu_{i}\sim 28.5$~\sb.}
         \label{fig:ellipse}
@@
     Mauna Kea. 
-    The ambitious multi-layer HSC survey takes advantage of the large field of 
-    view (FoV;~1.5 deg in diameter) of this camera and will cover $\sim 1400$ deg$^2$ in 5
-    broad bands (\textit{g r i z Y}) to a limting depth of $r \sim 26$ mag in the \texttt{WIDE} layer. 
+    This ambitious multi-layer photometric survey takes advantage of the large field of 
+    view (FoV;~1.5 deg in diameter) of HSC and will cover $\sim 1400$ deg$^2$ of sky in 5
+    broad bands (\textit{g r i z Y}) to the depth of $r \sim 26$ mag in the \texttt{WIDE}. 
     This work is based on the internal data release \texttt{S15B}, which covers 
-    $\sim 100$square of degree in all 5-band to full \texttt{WIDE} depth.  
+    $\sim 100$square of degree of sky in all 5-band to full \texttt{WIDE} depth.  
     The regions covered by this release overlap with a number of spectroscopic surveys 
@@
     than SDSS. 
-    Combined with the excellent imaging resolution (the median $i$-band seeing is 0.6"), 
-    and the wide area, the HSC survey represents a tremendous data set to perform a 
-    large statistical study of the surface brightness profiles of ETGs out to large radii. Fig.\ref{fig:sdss_compare} illustrates the quality of HSC imaging compared to SDSS 
-    for a sample of low redshift ETGs and shows that HSc survey data are well 
-    suited for mapping the stellar distribution of massive galaxies out to large radii.
-
-	HSC $i$-band images typically have the best seeing comapred to other bands because of 
-    strict requirements driven by weak lensing science. 
+    Combined with the excellent imaging resolution (median $i$-band seeing is 0.6"), 
+    and the wide area, this makes the HSC wide layer a tremendous data set to perform a 
+    large statistical study of surface brightness profiles of ETGs out to large radii. 
+    Fig.\ref{fig:sdss_compare} illustrated the quality of HSC imaging compared to SDSS 
+    for a sample of low redshift ETGs. 
+    Fig.\ref{fig:sdss_compare} clearly demonstrates that the HSC Wide survey is well 
+    suited for mapping the stellar distribution of massive galaxies out to large radii 
+    and will be a powerful data set to explore the assembly history of ETGs.
+
+	The HSC $i$-band images typically have the best seeing in all five bands because of 
+    strict requirements determined by weak lensing science. 
     We will therefore use the $i$-band images to measure the stellar distributions of 
@@
 %% ------------------------------------------------------------------------------------ %% 
-\subsection{HSC Data Processing}
+\subsection{The HSC galaxy catalog and photometry measurements}
     \label{sec:pipeline}
 
-The full details of the HSC data processing can be found in \citet{BoschInPrep} and are briefly summarized here. The HSC SSP data are processed with \texttt{hscPipe 4.0.1}, a derivative of the Large 
+    The HSC SSP data are processed with \texttt{hscPipe 4.0.1}, a derivative of the Large 
     Synoptic Survey Telescope (LSST) pipeline (e.g.\ \citealt{Juric2015}; 
@@
     (bias subtraction, flat fielding, background modeling, object detection and 
-    measurements). Astrometric and photometric calibration is performed at the single exposure level. \texttt{hscPipe} then warps different exposures on to a common
-    World Coordinate System (WCS) and combines them into coadded images. At this stage, \texttt{hscPipe} updates the images with a better astrometric and 
-    photometric calibration using stars that are common among between exposures.
-
-    The pixel scale of the combined images is $0.168^{\arcsec}$. Photometric calibration is based on data from the Panoramic Survey Telescope 
+    measurements). 
+    Then pipeline perform astrometric and photometric calibration for each single 
+    expoures. 
+    After that, the \texttt{hscPipe} warp different exposures on to a common
+    World Coordinate System (WCS), combine them into coadded images with improved 
+    signal-to-noise ratio ($S/N$), and update the images with better astrometric and 
+    photometric calibrations at the same time using the common stars among different
+    exposures.
+    The pixel scale of the combined images is $0.168^{\arcsec}$.  
+    The photometric calibration is based on data from the Panoramic Survey Telescope 
     and Rapid Response System (Pan-STARRS) 1 imaging survey 
@@
     To achieve consistent deblending and photometry across all bands, \texttt{hscPipe} 
-    performs multi-band post-processing at the coadd level. First, \texttt{hscPipe} performs object detection on coadd images
-    in each band independently and for each source records the flux peak and the above-threshold region (referred as 
-    a ``footprint'').
-Next, ``footprints'' and peaks from different bands are merged together before performing deblending and measurements.
-Finally, \texttt{hscPipe} selects a ``reference band'' for each object based on the
-    $S/N$ in different bands (for most galaxies in this work, the reference band is the $i$-band). 
+    performs multi-band post-processing at the coadd level. 
+    First, the \texttt{hscPipe} performs object detection again on the coadd images
+    in each band independently, and identify the above-threshold region (referred as 
+    ``footprint'') and the flux peak within it for each source. 
+    ``footprints'' and peaks from different bands are then merged together before 
+    the \texttt{hscPipe} deblend and measure them in each band. 
+    Later, \texttt{hscPipe} selects a ``reference band'' for each object based on the 
+    $S/N$ in different bands (for most galaxies in this work, it is the $i$-band). 
     After fixing the centroids, shape, and other non-amplitude parameters of each 
     object in this reference catalog, \texttt{hscPipe} perform forced photometry 
-    on the coadd image in each band. This forced photometry approach is optimized to yield accurate galaxy colors.
-
-    For each galaxy, \texttt{hscPipe} measures a \cmodel{} magnitude using an approach that is similar to SDSS (\ref{}) (Bosch\etal~in prep.~).
-However, as opposed to SDSS, the HSC \cmodel{} is based on forced photometry which means that it can be used to accurately measure both the \textit{fluxes and colors of galaxies}.
-The HSC \cmodel{} algorithm fits the flux distribution of each object using a combination of a de~Vaucouleur and
-    an exponential component and accounts for the PSF. The performance of this algorithm has been testing using synthetic objects (Huang\etal~in prep.~) and 
+    on the coadd image in each band.
+    The PSF and galaxy model fluxes measured in the forced photometry approach are the
+    best for color measurements.  
+    Please refer to \citet{BoschInPrep} for more details of the \texttt{hscPipe} and 
+    the multi-band processing method.
+
+    The HSC \cmodel{} algorithm is similar to the SDSS \cmodel{} one.  
+    It fits the flux distribution of an object using a combination of de~Vaucouleur and 
+    exponential components after considering the PSF convolution.  
+    For more details about the algorithm, please see Bosch\etal~in prep.~.
+    We have tested its performance using synthetic objects (Huang\etal~in prep.~), and 
     the results indicate that, generally speaking, the HSC \cmodel{} photometry is 
     accurate down to $i >25.0$ mag.  
-    However, \cmodel{} currently systematically underestimates the total fluxes of massive ETGs with extended stellar distributions.
-This problem indicates an intrinsic limitation of \cmodel{} as it is incapable of
-    modeling profiles with extremely extended outskirts, a problem that is exacerbated at the depth of 
-    the HSC survey.
-In addition, at the depth of the HSC survey, accurate deblending in the vicinity of large ETGs where satellites and background galaxies often blend with the low surface brightness stellar envelope is a challenign problem.
-The deblending method implemented by the \texttt{hscPipe} currently tends to
-    ``over-deblend'' the outskirts of bright galaxies and leads to un under-estimation of the the total flux of massive ETGs (more discussion in 
+    However, for massive ETGs with extended stellar distributions, \cmodel{} currently 
+    systematically underestimates their total flux.
+    This problem indicates the intrinsic limitation of \cmodel{} as it is incapable of
+    modeling profiles that are extremely extended in the outskirt at the depth of 
+    HSC survey. 
+    At the same time, issues with the deblender also worsen the situation. 
+    As the image becomes much deeper, it also significantly increases the fraction 
+    objects that are blended with others, and makes reliable deblending process 
+    a very challenging problem especially for massive ETGs where satellites and 
+    background galaxies often blend with the low surface brightness stellar envelope.
+    To make sure the reliable detection of faint objects close to the detection limit, 
+    the deblending method implemented by the \texttt{hscPipe} now tends to 
+    ``over-deblend'' the surrounding areas of bright galaxies, and further results in 
+    under-estimated total flux of massive ETGs (more discussion in 
     Bosch\etal~in prep.~).  
-For these reasons, our results will be based on custom developed code to measure the luminosities and stellar masses of massive galaxies.
-We use the HSC \texttt{hscPipe} photometry for two purposes: 1) to perform a first broad sample selection, and 2) for galaxy colors.
-\alexie{Shouldn't we be using the aperture photometry here ????
-Are we doing teh right thing here??
-Please check.
-Need a simple sanity check to show that the resutls are robust.
-Check using your own color estimates?}.
+    For these reasons, we will perform customized photometric measurements to derive 
+    more accurate total luminosity and stellar mass. 
+    We only use the HSC \cmodel{} photometry in the initial selection of parent 
+    sample.
 
@@
 
-    \alexie{Try to be more succinct and improve the logical flow in sections 2.3, 2.4, and 2.5. Readers don't care about the process! You should be able to trim these sections.}
-
-    \alexie{We never say anything about Spirals? Are all galaxies in this selection early types? Are there any extra morphology cuts? We need to mention this somewhere.}
-
-    \update{
-    We begin by using a broad luminosity cut to select an initial sample of massive galaxies at $z < 0.5$
-    from the HSC photometric catalog.} Based on Leauthaud\etal~(2016), galaxies with \logms{}$\geq 11.5$ have 
-    $i_{\mathrm{SDSS, cModel}} \leq 21.0$ mag. We therefore select our initla smaple to be brighter than  $i_{\mathrm{HSC, cModel}} \leq 21.5$ 
+    Because of the caveats that apply to \texttt{hscPipe} measurements for bright 
+    galaxies, we will use custom made software to measure the luminosity profiles of
+    massive galaxies. 
+    \update{
+    As the first step, we select the initial sample of massive galaxies at $z < 0.5$
+    from the HSC photometric catalog.}
+    We will then use custom made software to re-measure luminosities for all galaxies 
+    in this sample. 
+    Based on Leauthaud\etal~(2016), most \logms{}$\geq 11.5$ galaxies should have 
+    $i_{\mathrm{SDSS, cModel}} \leq 21.0$ mag.
+    So we first select all galaxies with $i_{\mathrm{HSC, cModel}} \leq 21.5$ 
     \footnote{We neglect the insignificant differences between the response curves of
-    SDSS-$i$ and HSC-$i$ filters} and also limit our sample to regions that have reached the required depth of the \texttt{WIDE} survey in all 
+    SDSS-$i$ and HSC-$i$ filters}
+    in regions that have reached the required depth of \texttt{WIDE} survey in all 
     five bands. 
@@
 
-    We further select extended objects with no deblending errors, with well defined 
-    centroids, and with \texttt{cModel} magnitudes in all five bands. 
-    After removing objects that have pixels affected by saturation, cosmic-rays, or 
-    other optical artefact \footnote{each criterion removes less than 8\% of the entire
-    sample} \alexie{Actually, 8 percent is not small if we want to condsider the number densities.
-Let's re-evaulate the impact of these cuts for the 16B data with FDFC}.
-This sample corresponds to 1760845 galaxies and will be referred as \texttt{hscPho}.
-
+    We select extended objects that have no error in deblending process, well defined 
+    centroids, and \texttt{cModel} magnitudes in all five bands. 
+    After removing the objects that have pixel affected by saturation, cosmic-ray, and 
+    other optical artefact \footnote{each criterion affects less than 8\% of the entire
+    sample}, we select 1760845 galaxies that will be referred as \texttt{hscPho}. 
     %% Saved as "dr1_wide_galaxy_hscPho.fits"
 
-    We limit our study to the very high mass end where a majority of galaxies have either a  spectroscopic redshift or a robust 
+    As reliable photometric redshift using HSC photometry is still a working progress, 
+    we only use objects with either available spectroscopic redshift or robust 
     red-sequence photo-$z$ from the \redm{} catalog (see Section \ref{ssec:redmapper}).  
-    We match the \texttt{hscPho} sample with a spec-$z$ catalog 
-    compiled by the HSC team\footnote{It is created by matching HSC objects with all publicly available spectroscopic redshifts (e.g.\ SDSS/BOSS; GAMA).
-The spec-z quality flag from different catalogs
-    are homogenized into a single flag that indicates whether the redshift is secure (\ref{} Cite a paper from the photo team where this is described?).
-Only galaxies with secure spec-$z$s are used in this work \alexie{Ned to be precise here.
-We also use redshifts from redmapper so this statement isn;t quite right}}.
-To ensure reasonable
-    \mstar{}-completeness at the high-\mstar{} end we focus on the redshift range $0.3 \leq z \leq 0.5$. 
+    We first match the \texttt{hscPho} sample with the external spec-$z$ catalog 
+    compiled by the HSC database\footnote{It is created by matching HSC objects with 
+    public data of several spectroscopic surveys (e.g.\ SDSS/BOSS; GAMA). 
+    Duplicated matches from different sources are merged through internal matching 
+    using $0.5^{\arcsec}$ radius. 
+    For each object, the quality information of the spec-$z$ from different catalogs 
+    are homogenized into a single flag that indicates whether the redshift is secure, 
+    and only secure spec-$z$ are used in this work.}
     %% This is catalog: "dr1_specz_use.fits"
-
-        \alexie{Please rewrite the section below.
-It would be better to first say that you further supplements with redmapper redshifts.
-And then simply quote the overall number at the end after making the redshift cut.
-Need to work on logical flow of text!}.
-
-  In addition to the specz-s mentioned above, we also include objects which have a red-sequence photo-$z$ from the \redm{} catalog within the range $0.2 \leq z \leq 0.5$ .........and need to say one sentance about the accuracy of the red sequence redshifts and why this is tolerable for our work
-
-    \rewrite{For objects without external spec-$z$, we match them with the central galaxies 
+    using $1.0^{\arcsec}$ radius.
+    At $0.2 \leq z \leq 0.5$, most redshifts in the HSC spec-$z$ catalog come from 
+    SDSS/BOSS and GAMA surveys.  
+    The BOSS survey provides the majority of spec-$z$ in this work.  
+    Due to the complex selection criteria for different subsamples within the BOSS
+    survey (e.g.\ the \texttt{LOWZ} and \texttt{CMASS}), it is not easy to estimate 
+    its \mstar{} completeness.  
+    Recently, through comparing with the deeper Stripe 82 Massive Galaxy Catalog
+    (\texttt{S82-MGC}; \citealt{Bundy2015}), \citet{Leauthaud2016} suggests that the 
+    BOSS spec-$z$ is about 80\% complete at \logms{}$\geq 11.6$ at $0.3 < z < 0.5$. 
+    The GAMA survey, which partially overlaps with the HSC footprint, provides 
+    additional 14\% unique spec-$z$. 
+    Based on \citet{Taylor2011} (e.g.\ their Fig.~6), at $z\sim 0.3$, the GAMA 
+    sample is 80\% complete down to $10^{10.8}$\msun; but only 80\% complete to 
+    $10^{12.0}$\msun at $z\sim 0.5$. 
+    Despite the difference in \mstar{} estimates, we can expect 
+    our sample should be quite complete above \logms{}$\geq 11.5$-$11.6$.
+    We will further address the issue of \mstar{}-completeness more carefully 
+    using the common sample with \texttt{S82-MGC} (see Section\ref{ssec:s82}).
+
+    Among the 116813 matched objects, 42696 are at $0.2 \leq z \leq 0.5$.
+    %% Saved as "dr1_wide_galaxy_icmodel_21.5.fits"
+    The majority of these redshifts come from either SDSS or BOSS data.  
+    GAMA survey contributes another $\sim 14$\%. 
+    For objects without external spec-$z$, we match them with the central galaxies 
     from \redm{} catalog using $2.0^{\arcsec}$ radius. 
@@
     $0.2 \leq z \leq 0.5$
-    (will be referred as \texttt{hscZ}).   From our initial sample, 42696 are at $0.2 \leq z \leq 0.5$.}
-    %% Saved as "dr1_wide_galaxy_icmodel_21.5.fits"
-
-    The BOSS and SDSS "legacy" LRG samples provide the majority of spec-$z$ for this work. By comparing with the Stripe 82 Massive Galaxy Catalog
-    (\texttt{S82-MGC}; \citealt{Bundy2015}), \citet{Leauthaud2016} have measured the stellar mass completness of the combined BOSS and SDSS samples.
-They estimate that the BOSS spec-$z$ is about 80\% complete at \logms{}$\geq 11.6$ at $0.3 < z < 0.5$.
-The GAMA survey, which partially overlaps with the HSC footprint, supplements our spec-z sample by 14\%.
-\alexie{and redmapper redshifts add another xx percent.} Based on \citet{Taylor2011} (e.g.\ their Fig.~6), at $z\sim 0.3$, the GAMA
-    sample is 80\% complete down to $10^{10.8}$\msun; but only 80\% complete to 
-    $10^{12.0}$\msun at $z\sim 0.5$.
-We can therfore expect our sample to be roughly stellar-mass complete above \logms{}$\geq 11.5$-$11.6$.
-This question will be addressed more carefully using the overlap region between HSC and the \texttt{S82-MGC} in Section\ref{ssec:s82}.
+    (will be referred as \texttt{hscZ}).
+    As we will mention at the end of the paper, to ensure reasonable 
+    \mstar{}-completeness at the high-\mstar{} end, and make sure the samples we 
+    want to compare have well overlapped redshift distributions, we will focus on 
+    the galaxies at $0.3 \leq z \leq 0.5$.
 
@@
 
-    Our study focuses on galaxies which are located at the center of
+    In this paper, our study focuses on galaxies which are located at the center of
     their dark matter halos. To limit our sample to central galaxies, we use 
@@
     For each cluster, the catalog provides a photometric redshift estimate $z_{\lambda}$, 
-    a richness $\lambda$, and identifies the most likely central
-    galaxy (this is the galaxy with the highest central probability value
+    a richness $\lambda$, and identified the most likely central
+    galaxy (this is the galaxies with the highest value of the central probability 
     $P_{\mathrm{Cen}}$). 
-The \redm{}{} catalog also provides a list of member galaxies for each cluster and associated membership probabilities.
+    A list of member galaxies for each cluster, and associated membership probabilities, 
+    is also provided. 
     Details about the performance of the \redm{}~cluster catalog can be found in 
@@
     The results of these studies are in good agreement and indicate that clusters 
-    identified by \redm{}~ with $\lambda > 20$ have $\log (M_{200m}/M_{\odot}) \geq 14.0$. 
-    Therefore, the \redm{} catalog helps us group massive central galaxies into samples with different average \mhalo{}.
-\alexie{Here is looks like you are making a cut on pcen.
-But what about galaxies that are not in these clusters?
-You do not have a pcen value!
-So this phrase needs to be rewritten or moved elsewhere.}\rewrite{To select reliable candidates of central galaxies, we only include the ones
-    with high probability of being the central galaxy ($P_{\mathrm{CEN}} \geq 0.7$)}.
+    identified by \redm{}~($\lambda > 20$) have $\log (M_{200m}/M_{\odot}) \geq 14.0$. 
+    Therefore, the \redm{} catalog helps us group the massive central galaxies into 
+    samples with different average \mhalo{}.  
+    And, to select reliable candidates of central galaxies, we only include the ones 
+    with high probability of being the central galaxy ($P_{\mathrm{CEN}} \geq 0.7$).
 
     Although the \redm{} catalog provides us a good sample of central galaxies in 
-    massive halos, the typical uncertainty of $\lambda$ estimate is still at the
+    massive halos, the typical uncertainty of $\lambda$ estimate is still at 
     $\sim 5$-10 level.  
     In addition, due to the depth and resolution of SDSS images, the \redm{} catalog 
-    becomes slightly incomplete at lower richness ($\lambda < 40$) at $z > 0.33$.
-    To reduce the impact of this effect, we will focus on a sample of central galaxies in halos with 
+    becomes slightly incomplete at lower richness ($\lambda < 40$) end at $z > 0.33$.
+    To reduce the impacts from uncertain richness and incomplete selection of 
+    massive halos, we will focus on a sample of central galaxies in halos with 
     $\lambda > 30$. 
-    Based on the calibration of \citet{Simet2016}, the $\lambda \geq 30$ sample should
-    have halo mass ($M_{200m}$) more massive than $10^{14.2} M_{\odot}$. We have checked that none of our results depend on this choice of the $\lambda$ boundary.
-
+    This will also help up enhance the \mhalo{} contrast in the structural comparison.     
+    Based on the calibration in \citet{Simet2016}, the $\lambda \geq 20$ sample should
+    have halo mass ($M_{200m}$) more massive than $10^{14.0} M_{\odot}$.  
+    For the $\lambda \geq 30$ sample, they should live in halo more massive than
+    $10^{14.2} M_{\odot}$ using the same calibration. 
+    And, we can confirm that the results presented later do not depend on the choice 
+    of $\lambda$ boundary here. 
     For the massive central galaxies that are not in these cluster-level halos, 
@@
     to assume they should have $\log (M_{200m}/M_{\odot}) < 14.0$.     
+    %\textcolor{red}{but sometimes we make cuts at $\lambda<20$ and $\lambda>30$. 
+    %Is it confusing to have several different thresholds? Need to give a Motivation 
+    %for using different numbers here.}
 
@@
 %% ------------------------------------------------------------------------------------ %% 
-\subsection{Massive Central Galaxies in Low and High Mass Halos}
+\subsection{Massive Central Galaxies from Low and High Mass Halos}
     \label{ssec:mass_central}
-
-    \alexie{This section can be synthesized and condensed. Try to be more succinct!}
 
@@
     the \mhalo{} of \logms{}$ > 11.0$ galaxies has a large scatter at fixed \mstar{}.            
-This means that our sample of massive galaxies spans a wide range of halos masses.
-We use the \redm{} catalog to separate our sample into two samples with halos masses above and below \logmh{}$<14.0$ \alexie{14.2 no?}.
+    Although we can not yet measure \mhalo{} individually, we can still broadly 
+    separate them into galaxies in small groups (\logmh{}$<14.0$) and 
+    large groups/clusters (\logmh{}$>14.0$), and investigate the 
+    ``environmental''-dependence of their structures.
 
@@
     %% Saved as "dr1_redbcg_hsc_sdss_gama_1arcsec.fits"
-
-   We match the \texttt{hscZ} sample with the massive central galaxies of 
-    \redm{} clusters with $\lambda \geq 20$ \alexie{20 or 30... confusing here} and $P_{\mathrm{0.7}} \geq 0.7$ using 
-    $1.0^{\arcsec}$ radius \alexie{mathcing radius not important}.
-
-     \alexie{confusing paragraph.
-The remapper redshift accuracy should be moved to the specz section.
-Why do we care about the number above 0.3?
-I'd remove those kind of details, they just make the reader confused.}
-
-    \rewrite{This step finds 375 matched galaxies at $0.2 \leq z \leq 0.5$ 
+    Firstly, we match the \texttt{hscZ} sample with the massive central galaxies of 
+    \redm{} clusters with $\lambda \geq 20$ and $P_{\mathrm{0.7}} \geq 0.7$ using 
+    $1.0^{\arcsec}$ radius. 
+    This step finds 375 matched galaxies at $0.2 \leq z \leq 0.5$ 
     (among them 282 are at $0.3 \leq z \leq 0.5$).  
@@
     Therefore, the current \rbcg{} sample is not dominated by very massive clusters 
-    with \mhalo{}$>10^{15} M_{\odot}$.  }
+    with \mhalo{}$>10^{15} M_{\odot}$.  
     %% Saved as "dr1_redbcg_use_sed5b.fits"
 
-    \rewrite{Assuming that the \redm{} catalog correctly identifies all halos with 
+    Assuming that the \redm{} catalog correctly identifies all halos with 
     $M_{200m}\sim 1.0\times 10^{14} h^{-1} M_{\odot}$ in the current footprint,
@@
     At $0.3 < z < 0.5$, such uncertainty is between 0.015 to 0.025, which are more than 
-    enough to exclude cluster member.}}
+    enough to exclude cluster member.}
     % TODO: The actual number waits to be updated}
@@
 
-    Using $\sim 100$ deg$^2$ of HSC data, we select a large sample
+    In summary, from the $\sim 100$ deg$^2$ deep HSC images, we select a large sample
     of massive central galaxies with reliable redshift information, and broadly separate 
-    them into two groups with different \mhalo{}. The following is a summary of our sample construction.
+    them into two groups with different \mhalo{}.  
+    To help you go through the results, here are a few key points to keep in mind:
 
@@
             candidates of central galaxies in halos with \logmh{}$<14.0$.  
+        \item To compare the \rbcg{} and \nbcg{} samples carefully, we will focus on 
+            the redshift range at $0.3 \leq z \leq 0.5$ where their redshift 
+            distributions greatly overlap and both samples have acceptable
+            \mstar-completeness (see Section \ref{ssec:s82}).  
+            \update{Although we use the $\lambda > 30$ sample for structural comparison, 
+            in the Appendix.\ref{app:robust}, we show that the results will not change 
+            if we include central galaxies of $20 < \lambda \leq 30$ clusters in the 
+            \rbcg{} sample.}
     \end{itemize}
-
-We now proceed to measure the luminosities and stellar mass profiles for all galaxies in this sample.
 
@@
     one-dimensional stellar mass density (\mden{}) profiles, we perform elliptical 
-    isophotes fitting using the IRAF \texttt{Ellipse} algorithm (Jedrzejewski 1987).  
+    isophotes fitting using the IRAF task \texttt{Ellipse} (Jedrzejewski 1987).  
     Compared to the popular two-dimensional model fitting method, the isophote fitting
-    approach is insensitive to the choice of a model (one versus two sersics for example), the number of components, 
+    approach is much less sensitive to the choice of model, number of components, 
     and the initial guesses of free parameters. 
-It is also less affected by uncertainties related to background subtraction.
+    It is also less affected by the uncertainty of sky background subtraction.  
     This is particularly important for the massive ellipticals in our sample.  
-Massive ETGs imaged at the depth of HSC are not well modeled by simple models such as the de~Vaucouleurs model or a single \ser component model.
-These models will fail to simultaneously capture the profile in both the inner and the outter region and these models also cannot account for any radial variations in ellipticity and position angle.
-In principle, massive galaxies can still be described using more complex
-    models (e.g \citealt{Huang2013a}; \citealt{Huang2013b}) but these multi model fits are quite sensitive to the background subtraction.
-For this paper, we opt to for the model independent 1-D approach and we will only study galaxies in the radial range where we are not sensitive to either the PSF ($r<5$ kpc) or the background subtraction ($r>100$ kpc).
-
-    We prepare large $i$-band cut-out images each galaxy in our sample that extend to at least 750 kpc in radius, along with the bad pixel mask, and the 
-    PSF model reconstructed at the central coordinate. These cut-outs include all the visible light of the galaxy while leaving enough space to evaluate the background level. 
-    We choose to use $i$-band images because they have excellent seeing, but also because they trace the stellar distributions of massive 
-    galaxies at $0.3 \leq z \leq 0.5$ reasonably well (the observed i-band corresponds to a rest-frame $g$ or $r$ band), and they suffer less from background uncertainty (because the sky is brighter in z and y).
-The $z$ and Y-bands will be better tracers of \mden{}, but the sky background in these bands
-    is much higher and the seeing is not as good as the i-band.
-
-    For each cut-out, we perform \texttt{SExtractor}-like background estimation and object detection using the \texttt{SEP} Python library.
-Out set up is designed to avoid the ``over-deblending'' problem that exists with \texttt{hscPipe}.
-We use several different backgrounds and $S/N$ thresholds, to identify the footprints of all objects, even those that are very close to the centers of bright galaxies.
-We create two masks for the \texttt{Ellipse} procedure.
-The first mask corresponds to the footprints of neighbouring galaxies.
-At this stage, we create a fiducial mask as well as a more aggresive mask to test for the impact of masking (see Appendix xxxx).
-The second mask is designed to measured the background level and masks out both the central (target) galaxy as well as neighbours.
-After appplying this mask to the cutout, we evalute the background level after smoothing over $6x6$  pixels (see Appendix xxxxx).
-This yields the global sky values over the cutout as well as the uncertainty in the sky.
-Based on the global uncertainty in the sky, at the depth of HSC wide, we should in pinciple be able to measure surface brightness profiles to $\sim 30$ \sb.
-However, in practice, we can only reach $<28.5$ \sb due to the uncertainties in modeling the sky.
-
-    % Appendix
-    %We achieve this via convolving the individual footprint with a Gaussian kernel
-    %so that we can conservatively exclude pixels affected by this object while still 
-    %making the mask follow the shape of the object.  
-    %Meanwhile, we create a more aggressive mask of \emph{all} objects in the same 
-    %approach,
-
-     %median-rebin the remaining pixels using a $6x6$ pixels box, and take 
-    %the peak value (or mode) of the distribution of these rebinned ``sky'' pixels 
-    %as the average background value around these bright galaxies.
-
-    We find that the global sky values is often slightly negative value indicate that hscpipe typically tends to over-subtract the sky.
+    The much deeper HSC image reveals significantly more extended structures, 
+    while also make it inappropriate to fit these galaxies with simple model like 
+    the de~Vaucouleurs model or single \ser component model. 
+    Such models fail to fit the central region and the stellar halo of massive 
+    galaxies simultaneously, and also can not account for the radial variation of 
+    ellipticity and position angle. 
+    In principle, such massive galaxies can still be described using more complex 
+    models (e.g \citealt{Huang2013a}; \citealt{Huang2013b}).  
+    However, they are still very sensitive to background subtraction. 
+    And it becomes even more difficult to choose initial parameters, and investigate
+    the degeneracies among parameters. 
+    Although it is certainly worth exploring in the future, we decide that the 1-D 
+    method suits the goal of this work better.
+
+    We first prepare large $i$-band cut-out images around these massive galaxies 
+    that cover at least 750 kpc in radius, along with the bad pixel masks, and the 
+    PSF model reconstructed using the central coordinates. 
+    While they include all the visible light of the galaxy, they also leave enough 
+    space to evaluate the background subtraction. 
+    We choose to use $i$-band images not only considering their excellent seeing
+    condition, but also because they trace the stellar distributions of massive 
+    galaxies at $0.3 \leq z \leq 0.5$ reasonably well (fall between rest-frame $g$ 
+    and $r$ band), and they suffer less from background uncertainty, which is crucial 
+    for studying the outskirt of massive ETGs.  
+    Although $z$ and Y-band should be better \mden{} tracer, the sky background 
+    is much higher and the seeing is considerably worse on average.
+
+    Secondly, using the \texttt{SEP} Python library, we perform \texttt{SExtractor}-like
+    background estimation and object detections using different configurations to 
+    overcome the ``over-deblending'' challenge met by the \texttt{hscPipe}. 
+    Combining detections using different backgrounds and $S/N$ thresholds, 
+    we correctly obtain the footprints of all objects, even of the ones that are 
+    very close to the center of bright galaxies.
+    For the rest objects, we convert their footprints into a mask image for the
+    \texttt{Ellipse} procedure after increasing their sizes adaptively based on the 
+    brightness and distance to the massive galaxy. 
+    We achieve this via convolving the individual footprint with a Gaussian kernel
+    so that we can conservatively exclude pixels affected by this object while still 
+    making the mask follow the shape of the object. 
+    Meanwhile, we create a more aggressive mask of \emph{all} objects in the same 
+    approach, median-rebin the remaining pixels using a $6x6$ pixels box, and take 
+    the peak value (or mode) of the distribution of these rebinned ``sky'' pixels 
+    as the average background value around these bright galaxies.
+    As expected, we often found slightly negative value that indicate over-subtraction 
+    of background at certain degree. 
     In \texttt{hscPipe}, the background on each CCD is modeled with a 
-    Chebyshev-polynomial that is fit to the smoothed image after excluding pixels with $S/N >5$.
+    Chebyshev-polynomial fit to the smoothed image after excluding pixels with $S/N >5$.
     This algorithm suffer less than the SDSS version (e.g.\ see \citealt{Blanton2011}),
@@
     For our massive galaxies, such over-subtracted background creates artifactual
-    truncation or steeper surface brightness profile. We attempt to correct for sky for the oversubtraction that results from \texttt{hscPipe} using a method described in Appedix xxx.
-
-    % Appendix
-    %We therefore provide an ad hoc fix using a \texttt{SExtractor}-style background 
-    %model ($200x200$ pixels background box size, and 6 pixels median filtering size of 
-    %sky boxes) via running \texttt{SEP} on the image with all objects masked out.
-    %This model can account for the slightly over-subtracted background at very large 
-    %scale, shift the distribution of rebinned ``sky'' pixels to 0, and do not affect the 
-    %intrinsic flux distribution of our target.
-
-    Finally, we run \texttt{Ellipse} on the background-corrected cut-out following a similar methodology as \citep{Li2012}.
-In short, we start with a free centroid and shape (ellipticty and position angle) for each isophote.
-We then fix the centroid and then estimate the mean ellipticty and position angles of all isophotes.
-Finally, we extract a 1-D surface brightness profile along the major axis using the mean ellipticy and position angle.
-In practice, we run \texttt{Ellipse} allowing for more sophisticated shapes than a simple ellipse (more ``disky'' or ``boxy'', e.g.\ \citealt{Kormendy2009}).
+    truncation or steeper surface brightness profile.
+    We therefore provide an ad hoc fix using a \texttt{SExtractor}-style background 
+    model ($200x200$ pixels background box size, and 6 pixels median filtering size of 
+    sky boxes) via running \texttt{SEP} on the image with all objects masked out.
+    This model can account for the slightly over-subtracted background at very large 
+    scale, shift the distribution of rebinned ``sky'' pixels to 0, and do not affect the 
+    intrinsic flux distribution of our target.
+
+    Finally, we run \texttt{Ellipse} on the background-corrected image following similar 
+    strategy of \citep{Li2012}.
+    In short, we start with free centroid and shape of each isophote, then gradually 
+    constrain their behaviors, and eventually extract 1-D surface brightness profile 
+    along the major axis using isophotes with fixed centroid and shape.
+    The 4th Fourier modes are included to fit the isophote better. 
+    In this way, we can extract the radial changes of the centroid, ellipticity, 
+    position angle, and average isophotal distortions (more ``disky'' or ``boxy'', 
+    e.g.\ \citealt{Kormendy2009}) along with the surface brightness profile.  
+    Fig.\ref{fig:ellipse} shows an example of the 1-D surface brightness and 
+    ellipticity profile for a massive galaxy at $z\sim0.2$ along with its masked 
+    image and a subset of isophotes.  
     Appendix.\ref{app:A} includes more details about the \texttt{Ellipse} procedure.
-We correct these surface brightness profiles for Galactic extinction and
-    cosmological dimming, then integrate them to various radius to get the 
-    luminosity within different physical apertures. Fig.\ref{fig:ellipse} shows an example of the 1-D surface brightness and 
-    ellipticity profile for a massive galaxy at $z\sim0.2$ together with the mask image and a subset of isophotes.
-
-    %The 4th Fourier modes are included to fit the isophote better. 
-    %In this way, we can extract the radial changes of the centroid, ellipticity, 
-    %position angle, and average isophotal distortions (more ``disky'' or ``boxy'', 
-    %e.g.\ \citealt{Kormendy2009}) along with the surface brightness profile.
-
-    We find that our 1-D profiles start begin to show unphsical behaviours (truncation or large fluctuations) at surface brightness levels of about $>28.5$ \sb.
-We therefore only consider regions above $<28.5$ \sb.
-    This conservative choice already allows us to measure light profiles out to $\sim 120$ kpc.
 
@@
     foreground galaxy or bright star) reasons, we can not extract reliable 1-D 
-    profiles for small fraction of massive galaxies because their central regions are heavily masked. This is an intrinsic limitation of the 1-D method. 
-    It affects $48/375$ of the\rbcg{} galaxies, and a smaller fraction of \nbcg{} ones. 
+    profiles for small fraction of massive galaxies due to heavily masked out 
+    central region. 
+    This issue reflects an intrinsic limitation of the 1-D method. 
+    It affects $48/375$ \rbcg{} galaxies, and a smaller fraction of \nbcg{} ones. 
     It is worth noting that this excludes most massive galaxies in major merger 
@@
 
+    We correct these surface brightness profiles for Galactic extinction and 
+    cosmological dimming, then integrate them to various radius to get the 
+    luminosity within different physical apertures.  
+    Although the $i$-band 1-D profile can in principle reach to $\sim 30$ \sb, 
+    we notice the profiles at very low surface brightness part are often less 
+    reliable by showing truncation or large fluctuation that are due to either 
+    background uncertainty or contamination from bright neighbours.
+    We therefore only consider the $<28.5$ \sb part of the profile here. 
+    This conservative choice already allows us to study the region out to 
+    $\sim 120$ kpc for massive galaxies in this sample.
+
 %% ------------------------------------------------------------------------------------ %%
@@
 
-    \alexie{Shold the color gradients stuff go here?? (I don't know.)}
-
-\subsection{Mass-to-light ratios from SED Fitting}
+\subsection{Stellar Masses from SED Fitting}
     \label{ssec:isedfit}
 
-    To convert luminosities into stellar mass, we assume that these massive 
+    To convert the luminosity into stellar mass estimates, we assume that these massive 
     galaxies can be well described by an average \m2l{}. 
     This is a reasonable assumption considering that they are ETGs that are dominated by 
-    old stellar populations and are known to have shallow color gradients. 
-    We will further justify this point by measuring their average color profiles in Section xxxxxx
+    old stellar population and are known to have shallow color gradients. 
+    We will further justify this point using the average color profiles in Section
     \ref{sec:discussion}.
@@
     (\citealt{Moustakas13}) to estimate the average \m2l{} and $k$-corrections using
-    5-band HSC \cmodel{} fluxes. 
+    5-band HSC \cmodel{} fluxes under forced-photometry mode. 
     Although \cmodel{} tends to underestimate the total flux for bright, extended 
-    objects, it still yields an accurate \emph{average} color 
-    of the galaxy as it is based on forced photomery and also takes the PSF convolution into account
+    objects, the forced-photometry results still provides accurate \emph{average} color 
+    of the galaxy as it constrains the behaviour of the model using the optimized 
+    reference one and taks the PSF convolution into account
     (e.g.\ Huang\etal~in prep.~).
@@
     Based on these models, it uses the observed photometry and redshift to compute the 
-    statistical likelihood, and generates the posterior probability distribution (PDF) 
-    functions for each parameter.  
-    To get the best estimate of a given parameter, \texttt{iSEDFit} ``integrates'' the 
+    statistical likelihood, and generate the posterior probability distribution (PDF) 
+    functions of each parameter.  
+    To get the best estimate of certain parameter, \texttt{iSEDFit} ``integrates'' the 
     full PDF over all the other ``nuisance'' parameters.
-    Then, the median value and the 1-$\sigma$ uncertainty are derived based on the marginalized PDF. Please refer to \citet{Moustakas13} for technical details.
+    Then, the median value of the resulting marginalized PDF is used as the best value, 
+    while the 1-$\sigma$ uncertainty is derived from the cumulative PDF. 
+    Please refer to \citet{Moustakas13} for technical details and performance of 
+    \texttt{iSEDFit}.
 
@@
     \footnote{http://www.iac.es/proyecto/miles/pages/stellar-libraries/miles-library.php}
-    (\citealt{MILES1}, \citealt{MILES2}) stellar library and assuming a \citet{Chabrier2003} 
+    (\citealt{MILES1}, \citealt{MILES2}) stellar library and \citet{Chabrier2003} 
     IMF between 0.1 to 100 \msun. 
-The star formation history (SFH) is assumed to follow a delayed-$\tau$ model with stochastic star bursts (see Appendix xx).
-This SFH is appropriate for massive galaxies at low redshifts
+    We use a delayed-$\tau$ model with stochastic star burst as the form of star 
+    formation history (SFH), and choose a set of reasonable parameters after some tests.  
+    Such form of SFH is appropriate for massive galaxies at low redshift 
     (e.g.\ \citealt{Kauffmann2003}). 
-    For stellar metallicity, we assume a flat distribution between 0.004 to 0.03 (the highest value allowed by FSPS). We adopt the \citet{Calzetti2000} extinction law with a order two Gamma 
-    distribution of $A_{V}$ between 0 to 2 magnitude. A majority of our galaxies are red and quiescent and our results are 
-    not very sensitive to parameters related to the SFH or the internal dust extinction. 
+    For stellar metallicity, we assume flat distribution between 0.004 to 0.03 (which is 
+    the highest metallicity allowed by FSPS models).  
+    And, we adopt the \citet{Calzetti2000} extinction law with a order two Gamma 
+    distribution of $A_{V}$ between 0 to 2 magnitude.
+    Since most galaxies in both samples are red, quiescent galaxies, the results are 
+    not very sensitive to parameters related to SFH and internal dust extinction. 
     To achieve reasonable sampling across these parameters, we generate 250000 models.
 
-    We construct five band SEDs using the forced-photometry \cmodel{} magnitudes corrected 
-    for Galactic extinction.
-\cmodel{} only accounts for the statistical error on the flux measurement but does not account for systematic uncertainties in the model-fitting process.
-It therefore underestimates the flux errors of bright galaxies.
-Based on tests using synthetic objects, we find that the average accuracy of \cmodel{} for bright galaxy is roughly at the 1\% level.
+    We construct five band SED using the forced-photometry \cmodel{} magnitude corrected 
+    for the Galactic extinction. 
+    As for the photometric error, the current \cmodel{} photometry underestimates 
+    the flux errors of bright galaxies as it only includes statistical error, not the 
+    systematic uncertainties in the model-fitting process.  
+    From tests of synthetic objects, we find that the average accuracy of \cmodel{} 
+    photometry for bright galaxy is roughtly at 1\% level. 
     Therefore, we supply \texttt{iSEDFit} with simplified flux errors assuming $S/N = 100$ 
-    for the $riz$ bands, and $S/N = 80$ for the $gY$ bands (on average, images in $gY$ bands are 
+    for $riz$ bands, and $S/N = 80$ for $gY$ bands (on average, images in $gY$ bands are 
     shallower in depth and/or have higher background noise).  
-    The typical uncertainty of \logms{} is around 0.08-0.10 dex at $M* \sim xxxx$ end. 
+    The typical uncertainty of \logms{} for both samples is around 0.08-0.10 dex at the 
+    high-\mstar{} end. 
     Please see Appendix.\ref{app:B} for more detailed discussions of the SED fitting
     results.  
-
     %In Fig.~3, we show an example of SED fitting result. 
@@
 
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %% 
-  \begin{figure*}[bt!]
-      \centering 
-      \includegraphics[width=\textwidth]{fig/average_mass_profiles_fsps1_A}
-      \caption{
-      	\textbf{Left}: Median \mden{} profiles of galaxies in different \mtot{} bins:
-      	[11.4, 11.6] (short-dashed line), [11.6, 11.8] (solid line), and 
-      	[11.8, 12.0] (long-dashed line). 
-      	Here we combine the \rbcg{} and \nbcg{} samples, and we also show a random subset 
-      	of individual profiles in the background.
-      	The shaded region highlights the region that could be affected by PSF.
-        Two vertical lines label the radius of 10 kpc (thin, dotted line) and
-        100 kpc (thick, dash line). ~~~ 
-        \textbf{Right}: comparison between the average \mden{} profiles with the ones 
-        from previous observations and simulations, including: 
-        1) average profile of massive elliptical galaxies at $z\sim 0$ from 
-        \citet[][Cyan, solid]{Huang2013a}; 
-        2) average profile of massive galaxies at $0.25 \leq z < 0.50$ observed by 
-        \textit{HST} from \citet[][Red, long-dashed]{Patel2013} ;
-        3) average radial stellar distribuitions in massive halos using simulation and 
-        particle tagging method (\citealt{Cooper13}; Purple, short-dashed).}
-      \label{fig:avg_prof}
-  \end{figure*}
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %% 
-  \begin{figure*}[t!]
-      \centering 
-      \includegraphics[width=\textwidth]{fig/redbcg_prof_1}
-      \caption{
-          \update{
-          Comparison of the \mden{} profiles for \mtot{}-matched ($11.6<$\logmtot{}$<11.9$) 
-          and \minn{}-matched ($11.2<$\logminn{}$<11.6$) samples 
-          of \rbcg{} (orange to red) and \nbcg{} (grey to black) galaxies.~~
-          \textbf{Left} shows the results for the \mtot{}-matched samples.
-          For details of the matching process, please see Appendix.\ref{app:match}.  
-          On its upper panel, we show the \mden{} profile of each galaxy using very light 
-          color in the background.  
-          We highlight the median profile and its corresponding uncertainties using thick 
-          solid line with darker color and shaded region. 
-          Other formats are the same with Fig.\ref{fig:avg_prof}.
-          Meanwhile, we highlight the difference between the median profiles and its 
-          uncertainty on the bottom panel (brown solid line and shaded region).
-          To test the significance of the differential profile, we perform statistical tests 
-          by comparing the median profiles of two random groups that are drawn from the 
-          mixed sample, and have the same sizes with the matched \rbcg{} and \nbcg{} ones.
-          Repeating this process many times, the median of these random differential 
-          profiles (black solid line), the 1-$\sigma$ (dark-grey shaded region) and 3-$\sigma$
-          (light-grey shaded region) uncertainties are shown on the bottom panel as well. 
-          A darker vertical dash-line highlights the 100 kpc radius.~~
-          \textbf{Right} shows the results for the \minn{}-matched samples. 
-          The format is exactly the same with the left one, except that the darker vertical 
-          dash-line now highlights the 10 kpc radius.}
-      }
-      \label{fig:prof_1} 
-  \end{figure*}
-%% ------------------------------------------------------------------------------------ %%
-
-\subsection{Stellar Mass Density Profiles and Total Stellar Masses}
-    \label{ssec:mtotal}
-
-    \alexie{Did not make edits}
-
-    Using the best-fit stellar mass from \texttt{iSEDFit} (referred as \mcmodel{}), 
-    we estimate the average \m2l{} in $i$-band, then use that \m2l{} to convert the 
-    1-D luminosity density profiles into stellar mass density profiles; and 
-    also convert the luminosity within 10 and 100 kpc apertures into 
-    corresponding stellar mass estimates (referred as \minn{} and \mtot{}). 
-    From now, we use \mtot{} as the new proxy of ``total'' stellar mass of these 
-    galaxies.  
-    And we also derive the $k$-corrected luminosity and colors from the results.
-    In Appendix.\ref{app:B}, we also show the outputs like the average stellar age, 
-    metallicity, and internal dust extinction all behave reasonably for both 
-    samples, but will not use them for further scientific analysis.
-
-    As expected, the integration of 1-D profile out to very large radius help 
-    recover more luminosity (stellar mass) compared to the \cmodel{} results. This will shown in Section xx.
-
-    As mentioned earlier, our assumption of using an average \m2l{} ignores its
-    radial variation.   
-    It is well known that massive ETGs have negative optical color gradient which 
-    indicates a gradient of \m2l{} (e.g.\ \citealt{LaBarbera2012}; \citealt{DSouza2015}),
-    but the gradient is smooth and shallow out to a few times of the effective 
-    radius (color gradient at the very outskirt is still not well quantified). 
-    And, for the comparison between the \rbcg{} and \nbcg{} samples, 
-    Our results should remain intact as long as there is no significant
-    differences of color gradient between these two samples.
-    We will discuss this more later, but initial results do suggest a smooth color
-    gradient out to very large radius, and there is no systematic difference in 
-    color gradients of the two samples.  
-    Both suggest that the average \m2l{} approach should work reasonably well for
-    our goals.
-
-    And, we should mention that our approach is in principle very similar to the 
-    one adopted by the GAMA survey (\citealt{Taylor2011}), where they start with 
-    \mstar{} estimated using average \m2l{} from SED fitting results of
-    PSF-matched aperture photometry, and later correct it with better estimate 
-    of total luminosity.  
-    However, the GAMA survey relied on multi-band single-\ser model fitting on 
-    the SDSS images to get total luminosity (\citealt{Kelvin2012}). 
-    It is therefore interesting to compare the \mstar{} (\mgama{} v.s. \mtot{})
-    estimates for galaxies in common, given the differences in data and method. 
-    Please see the Appendix.\ref{app:C} for more details. 
-    In short, we notice systematic differences between the two \mstar{} estimates, 
-    and it is likely that the GAMA models miss fluxes in the stellar halo that 
-    is beyond the depth of SDSS image.
-
-    \update{In Appendix.\ref{app:basic}, we summarize the basic statistics of 
-    the \rbcg{} and \nbcg{} samples.  In general:}
-
-    %\begin{itemize}
-    %    \item \update{The two samples follow the same, tight ``red-sequence'' 
-    %        defined by $k$-corrected colors.}
-    %    \item \update{The redshift distributions are reasonably similar in 
-    %        $0.3 < z < 0.5$, but the difference can still bias the comparison of
-    %        \mden{} profiles.}
-    %    \item \update{Although their \mtot{} overlaps a lot between 
-    %        $11.6 <$\logmtot{}$< 11.9$, the relative distributions within this 
-    %        bin are still very different.}
-    %    \item \update{The distributions of \minn{} overlaps the most between 
-    %        $11.2 <$\logminn{}$< 11.6$, but the relative distributions also 
-    %        show difference within this \minn{} range.}
-    %\end{itemize}
-
-%% ------------------------------------------------------------------------------------ %%
-
-\section{Results}
-    \label{sec:result}
-
-    \subsection{Stellar Mass Completeness}
-
-    Here we refer to the comparison with Stripe 82 and just say that we are complete to xxx.
-
-    \update{To compare their structural details, we will focus on \rbcg{} and 
-    \nbcg{} galaxies with $11.6 \le$\logmtot{}$\le 11.9$.  
-    Both samples have reasonable completeness in this \mtot{} range
-    (see Fig.\ref{fig:smf1}).
-    In light of the differences in distributions of \mtot{}, \minn{}, and redshift, 
-    we will carefully match these properties between the \rbcg{} and \nbcg{}
-    samples to make sure the comparison is fair and meaningful.  
-    Please see the next section and Appendix.\ref{app:match} for more details.}
-
-    \subsection{Need a title}
+\subsection{Comparison with \texttt{S82-MGC}}
     \label{ssec:s82}
 
-Here we show the luminosty difference and impact on SMF.
-
-We highlight this in the right panel of Fig.\ref{fig:smf1} as we show the 
-    distributions of differences between \mtot{} and \mcmodel{}, and their relations 
-    to the \mtot{}.  
-    For both samples, we see the ``extra mass'' recovered by 1-D photometry 
-    increases with \mtot{}, therefore this improvement impacts the \rbcg{}
-    sample more.  
-    This is basically consistent with the fact that the structure of massive ETGs 
-    depends on its stellar mass in a way that more massive ones tends to be 
-    more extended (e.g.\ \addref).  
-    Apparently, such mass-dependent difference between \mtot{} and \mcmodel{} will 
-    result in difference of the SMF. 
-    \alexie{Discussion!!} As the slope and normalization of SMF at high mass end is very sensitive 
-    to both cosmology and interesting baryonic processes such as AGN feedback
-    (\addref), they are particularly important in constraining the galaxy evolution
-    model, and therefore became the center of some intense arguments (\addref).  
-    Although the jury is still out on this topic, it has become clear that 
-    popular results using SDSS photometry (\addref) underestimate the total 
-    luminosity (stellar mass) of massive ETGs.  
-    However, past works (e.g.\ \addref) often relied on either stacking of 
-    shallow images or the extrapolation of models to investigate this effect. 
-    Using the deep HSC images, we have the potential to answer this question 
-    much better. 
-    Detailed studies of SMF deserves more careful investigations of many 
-    systematic issues (e.g.\ \addref), so we just show the impact of the 
-    ``extra mass'' on the volume density distributions of both samples 
-    (Fig.\ref{fig:smf1}, left panel).  
-    Generally speaking, the stellar mass corrected for total luminosity 
-    shifts the distribution toward the higher mass end, and slightly modify
-    the slope. 
-    People who want to use HSC photometry or other \cmodel{}-like photometry to 
-    study the properties and evolution of SMF should be aware of such effect.
-
-    \rewrite{Given the heterogeneous nature of the redshift resources for these samples, we 
+    Given the heterogeneous nature of the redshift resources for these samples, we 
     further investigate their \mstar{} completeness via comparing with galaxies that are 
@@
     The deeper photometry and better photo-$z$ make the \texttt{S82-MGC} sample complete 
-    to \logms{}$\geq 11.2$ at $z<0.7$.}
-
-    \rewrite{The match between the \texttt{hscPho} sample and the \texttt{S82-MGC} one results in 
+    to \logms{}$\geq 11.2$ at $z<0.7$.
+
+    The match between the \texttt{hscPho} sample and the \texttt{S82-MGC} one results in 
     20453 galaxies at $0.3 \leq z \leq 0.5$ (referred as \texttt{s82Pho} sample).  
@@
     comparisons, we will bear this in mind, and match the two samples carefully in 
-    \logms{} and redshift space before comparing them}.
-
-\subsection{Surface Mass Density Profiles}
+    \logms{} and redshift space before comparing them.
+
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
+  \begin{figure*}[bt!]
+      \centering 
+      \includegraphics[width=\textwidth]{fig/average_mass_profiles_fsps1_A}
+      \caption{
+      	\textbf{Left}: Median \mden{} profiles of galaxies in different \mtot{} bins:
+      	[11.4, 11.6] (short-dashed line), [11.6, 11.8] (solid line), and 
+      	[11.8, 12.0] (long-dashed line). 
+      	Here we combine the \rbcg{} and \nbcg{} samples, and we also show a random subset 
+      	of individual profiles in the background.
+      	The shaded region highlights the region that could be affected by PSF.
+        Two vertical lines label the radius of 10 kpc (thin, dotted line) and
+        100 kpc (thick, dash line). ~~~ 
+        \textbf{Right}: comparison between the average \mden{} profiles with the ones 
+        from previous observations and simulations, including: 
+        1) average profile of massive elliptical galaxies at $z\sim 0$ from 
+        \citet[][Cyan, solid]{Huang2013a}; 
+        2) average profile of massive galaxies at $0.25 \leq z < 0.50$ observed by 
+        \textit{HST} from \citet[][Red, long-dashed]{Patel2013} ;
+        3) average radial stellar distribuitions in massive halos using simulation and 
+        particle tagging method (\citealt{Cooper13}; Purple, short-dashed).}
+      \label{fig:avg_prof}
+  \end{figure*}
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
+  \begin{figure*}[t!]
+      \centering 
+      \includegraphics[width=\textwidth]{fig/redbcg_prof_1}
+      \caption{
+          \update{
+          Comparison of the \mden{} profiles for \mtot{}-matched ($11.6<$\logmtot{}$<11.9$) 
+          and \minn{}-matched ($11.2<$\logminn{}$<11.6$) samples 
+          of \rbcg{} (orange to red) and \nbcg{} (grey to black) galaxies.~~
+          \textbf{Left} shows the results for the \mtot{}-matched samples.
+          For details of the matching process, please see Appendix.\ref{app:match}.  
+          On its upper panel, we show the \mden{} profile of each galaxy using very light 
+          color in the background.  
+          We highlight the median profile and its corresponding uncertainties using thick 
+          solid line with darker color and shaded region. 
+          Other formats are the same with Fig.\ref{fig:avg_prof}.
+          Meanwhile, we highlight the difference between the median profiles and its 
+          uncertainty on the bottom panel (brown solid line and shaded region).
+          To test the significance of the differential profile, we perform statistical tests 
+          by comparing the median profiles of two random groups that are drawn from the 
+          mixed sample, and have the same sizes with the matched \rbcg{} and \nbcg{} ones.
+          Repeating this process many times, the median of these random differential 
+          profiles (black solid line), the 1-$\sigma$ (dark-grey shaded region) and 3-$\sigma$
+          (light-grey shaded region) uncertainties are shown on the bottom panel as well. 
+          A darker vertical dash-line highlights the 100 kpc radius.~~
+          \textbf{Right} shows the results for the \minn{}-matched samples. 
+          The format is exactly the same with the left one, except that the darker vertical 
+          dash-line now highlights the 10 kpc radius.}
+      }
+      \label{fig:prof_1} 
+  \end{figure*}
+%% ------------------------------------------------------------------------------------ %%
+
+\subsection{Stellar Mass Corrected for Total Luminosity}
+    \label{ssec:mtotal}
+
+    Using the best-fit stellar mass from \texttt{iSEDFit} (referred as \mcmodel{}), 
+    we estimate the average \m2l{} in $i$-band, then use that \m2l{} to convert the 
+    1-D luminosity density profiles into stellar mass density profiles; and 
+    also convert the luminosity within 10 and 100 kpc apertures into 
+    corresponding stellar mass estimates (referred as \minn{} and \mtot{}). 
+    From now, we use \mtot{} as the new proxy of ``total'' stellar mass of these 
+    galaxies.  
+    And we also derive the $k$-corrected luminosity and colors from the results.
+    In Appendix.\ref{app:B}, we also show the outputs like the average stellar age, 
+    metallicity, and internal dust extinction all behave reasonably for both 
+    samples, but will not use them for further scientific analysis.
+
+    As expected, the integration of 1-D profile out to very large radius help 
+    recover more luminosity (stellar mass) compared to the \cmodel{} results.
+    We highlight this in the right panel of Fig.\ref{fig:smf1} as we show the 
+    distributions of differences between \mtot{} and \mcmodel{}, and their relations 
+    to the \mtot{}.  
+    For both samples, we see the ``extra mass'' recovered by 1-D photometry 
+    increases with \mtot{}, therefore this improvement impacts the \rbcg{}
+    sample more.  
+    This is basically consistent with the fact that the structure of massive ETGs 
+    depends on its stellar mass in a way that more massive ones tends to be 
+    more extended (e.g.\ \addref).  
+    Apparently, such mass-dependent difference between \mtot{} and \mcmodel{} will 
+    result in difference of the SMF. 
+    As the slope and normalization of SMF at high mass end is very sensitive 
+    to both cosmology and interesting baryonic processes such as AGN feedback
+    (\addref), they are particularly important in constraining the galaxy evolution
+    model, and therefore became the center of some intense arguments (\addref).  
+    Although the jury is still out on this topic, it has become clear that 
+    popular results using SDSS photometry (\addref) underestimate the total 
+    luminosity (stellar mass) of massive ETGs.  
+    However, past works (e.g.\ \addref) often relied on either stacking of 
+    shallow images or the extrapolation of models to investigate this effect. 
+    Using the deep HSC images, we have the potential to answer this question 
+    much better. 
+    Detailed studies of SMF deserves more careful investigations of many 
+    systematic issues (e.g.\ \addref), so we just show the impact of the 
+    ``extra mass'' on the volume density distributions of both samples 
+    (Fig.\ref{fig:smf1}, left panel).  
+    Generally speaking, the stellar mass corrected for total luminosity 
+    shifts the distribution toward the higher mass end, and slightly modify
+    the slope. 
+    People who want to use HSC photometry or other \cmodel{}-like photometry to 
+    study the properties and evolution of SMF should be aware of such effect.
+
+    As mentioned earlier, our assumption of using an average \m2l{} ignores its
+    radial variation.   
+    It is well known that massive ETGs have negative optical color gradient which 
+    indicates a gradient of \m2l{} (e.g.\ \citealt{LaBarbera2012}; \citealt{DSouza2015}),
+    but the gradient is smooth and shallow out to a few times of the effective 
+    radius (color gradient at the very outskirt is still not well quantified). 
+    And, for the comparison between the \rbcg{} and \nbcg{} samples, 
+    Our results should remain intact as long as there is no significant
+    differences of color gradient between these two samples.
+    We will discuss this more later, but initial results do suggest a smooth color
+    gradient out to very large radius, and there is no systematic difference in 
+    color gradients of the two samples.  
+    Both suggest that the average \m2l{} approach should work reasonably well for
+    our goals.
+
+    And, we should mention that our approach is in principle very similar to the 
+    one adopted by the GAMA survey (\citealt{Taylor2011}), where they start with 
+    \mstar{} estimated using average \m2l{} from SED fitting results of
+    PSF-matched aperture photometry, and later correct it with better estimate 
+    of total luminosity.  
+    However, the GAMA survey relied on multi-band single-\ser model fitting on 
+    the SDSS images to get total luminosity (\citealt{Kelvin2012}). 
+    It is therefore interesting to compare the \mstar{} (\mgama{} v.s. \mtot{})
+    estimates for galaxies in common, given the differences in data and method. 
+    Please see the Appendix.\ref{app:C} for more details. 
+    In short, we notice systematic differences between the two \mstar{} estimates, 
+    and it is likely that the GAMA models miss fluxes in the stellar halo that 
+    is beyond the depth of SDSS image.
+
+    \update{In Appendix.\ref{app:basic}, we summarize the basic statistics of 
+    the \rbcg{} and \nbcg{} samples.  In general:}
+
+    \begin{itemize}
+        \item \update{The two samples follow the same, tight ``red-sequence'' 
+            defined by $k$-corrected colors.}
+        \item \update{The redshift distributions are reasonably similar in 
+            $0.3 < z < 0.5$, but the difference can still bias the comparison of
+            \mden{} profiles.}
+        \item \update{Although their \mtot{} overlaps a lot between 
+            $11.6 <$\logmtot{}$< 11.9$, the relative distributions within this 
+            bin are still very different.}
+        \item \update{The distributions of \minn{} overlaps the most between 
+            $11.2 <$\logminn{}$< 11.6$, but the relative distributions also 
+            show difference within this \minn{} range.}
+    \end{itemize}
+
+    \update{To compare their structural details, we will focus on \rbcg{} and 
+    \nbcg{} galaxies with $11.6 \le$\logmtot{}$\le 11.9$.  
+    Both samples have reasonable completeness in this \mtot{} range
+    (see Fig.\ref{fig:smf1}).
+    In light of the differences in distributions of \mtot{}, \minn{}, and redshift, 
+    we will carefully match these properties between the \rbcg{} and \nbcg{}
+    samples to make sure the comparison is fair and meaningful.  
+    Please see the next section and Appendix.\ref{app:match} for more details.}
+
+%% ------------------------------------------------------------------------------------ %%
+
+\section{Results}
+    \label{sec:result}
+
+\subsection{Comparison of Surface Mass Density Profiles}
     \label{ssec:sbp_compare}
 
-\subsubsection{Mass Dependent Profiles}
+\subsubsection{Internal Comparison and Comparison with Previous Works}
     \label{sssec:sbp_inter}
@@
     different physical processes, including the environmental effect.
-
-    \alexie{dont conceptually separate into two samples at this stage,}
 
@@
     As one can see in the left panel of Fig.\ref{fig:avg_prof}, we can comfortably trace 
-    the \mstar{} distribution of these massive galaxies out to 100 kpc \alexie{or 120??? Make the same numbers everywhere.}
+    the \mstar{} distribution of these massive galaxies out to 100 kpc 
     \textbf{individually}, which gives us huge advantage in studying the statistical 
@@
 
-    \alexie{Sounds more like Discussion section} In principe, this is consistent with result from HST observations of BCGs at 
+    In principe, this is consistent with result from HST observations of BCGs at 
     $0.3 < z <0.9$ (\citealt{Bai2014}) and the claimed positive correlation between 
@@
       \includegraphics[width=\textwidth]{fig/redbcg_prof_2}
-      \caption{\alexie{Remvoe or move to Appendix} Comparisons of the \mden{} profiles for \mtot{}-matched \rbcg{} 
+      \caption{Comparisons of the \mden{} profiles for \mtot{}-matched \rbcg{} 
           (orange-red) and \nbcg{} (grey-black) galaxies in lower (left; [11.5,11.70]) 
@@
 
-\subsubsection{Environmental dependence}
+\subsubsection{Environmental dependence of \mden{} profiles at fixed \mtot{}}
     \label{sssec:sbp_mtot}
-
-\alexie{Merge the two following into ONE section. AND cut it down by half. Sythetisoize.}
 
@@
 
-    \alexie{This is not a seperate section.}
-
     \update{Here, we compare the median \mden{} profiles of \rbcg{} and \nbcg{} galaxies
@@
     \label{ssec:ell_color}
-
-    \alexie{On the fence about this section. Is it all important???}
 
@@
 
-%    We use the curve-of-growth of luminosity from the \texttt{Ellipse} run on 
-%    $i$-band images to estimate the $R_{\mathrm{50}}$ here.
-%    This 1-D approach is more sensitive to issues like the smearing effect of PSF and 
-%    the choice of aperture for maximum luminosity than the 2-D fitting method.
-%    But, for the massive galaxies in this work, their apparent sizes are always 
-%    sufficiently large at $0.3 \geq z \geq 0.5$ so that the $R_{\mathrm{50}}$ 
-%    measurements are not bothered by seeing.  
-%    At the same time, this 1-D method has the advantages of being less affected by the 
-%    accuracy of background subtraction, structural details, and model assumptions.
-
-    On the left of Fig.\ref{fig:scaling_relation}, we see clear \mstar{}-size relations for both samples.  
-    At fixed \mtot{}, the distributions of $R_{\mathrm{50}}$ for the \rbcg{} and
-    \nbcg{} galaxies greatly overlap.  
-    Meanwhile, it seems that the \rbcg{} galaxies do have a slightly higher 
-    $R_{\mathrm{50}}$. 
-    For the \mtot{}-matched samples used in Fig.\ref{fig:prof_1}, the median 
-    $\log (R_{\mathrm{50}}/\mathrm{kpc})$ values for the \rbcg{} and \nbcg{} are 
-    $1.22\pm 0.02$ ($\sim 17.4\pm 0.75$ kpc) and $1.09\pm 0.01$ 
-    ($\sim 12.3\pm0.3$ kpc), which confirm the above observation and is consistent with 
-    the differences seen in Fig.\ref{fig:prof_1}. 
-    However, most previous works that we are aware of did not match the \mstar{} 
-    and redshift distributions between different samples, and often focused on the shape 
-    of the \logms{}-$\log R_{\mathrm{e}}$ relation.  
-    Here, we try to derive the best-fit parameters for the 
+    \update{
+    On the left of Fig.\ref{fig:scaling_relation}, we see that massive galaxies from 
+    both samples follow a tight \mstar{}-size relation that is consistent with the 
+    literature. 
+    Here, we compare with the relation for $z\leq 0.09$ central ETGs in  
+    $14\le$\logmh{}$<15$ halos from \citealt{HCompany13} (HC13; cyan dashed line) after 
+    empirically correcting the \mstar{} to the same IMF and stellar population model. 
+    Although HC13 derived \mstar{} and effective radius using \ser{} model, we find
+    a very similar relation.  
+    In HC13, the authors found no difference in the \mstar{}-size relations for 
+    central galaxies from different halo mass.
+    Using HSC data, although the \rbcg{} and \nbcg{} galaxies still greatly overlap 
+    each other along the relation, we find evidence that the \rbcg{} galaxy is on 
+    average larger than the \nbcg{} ones at fixed \mtot{}, which is consistent with 
+    the results from comparing the \mden{} profiles. 
+    The median $R_{\mathrm{50}}$ for the \mtot{}-matched \rbcg{} (\nbcg{}) sample 
+    used in Fig.\ref{fig:prof_1} \rbcg{} is $\sim 17.4\pm 0.75$ kpc 
+    ($\sim 12.3\pm0.3$ kpc).
+    }
+    We also derive the best-fit parameters for the 
     \logmtot{}-$\log (R_{\mathrm{50}}/\mathrm{kpc})$ relations of galaxies with 
@@
     \texttt{emcee} (\citealt{Emcee}). 
-    Using initial guesses based on maximum likelihood estimates, and assuming reasonable 
-    flat priors, we derive best-fit relations for the massive \rbcg{} galaxies:
+    Using initial guesses based on maximum likelihood estimates, and reasonable 
+    flat priors, we derive the best-fit relations for the massive \rbcg{} galaxies:
 
@@
 
-    \noindent And for the massive \nbcg{} galaxies, we have:
+    \noindent and for the massive \nbcg{} galaxies:
 
@@
 
-    \noindent As shown in Fig.\ref{fig:scaling_relation}, at the high-mass end, the two relations 
-    have consistent slopes within their uncertainties, but different normalizations. 
-    Extending the fitting to the full \logmtot{} range does not change this result. 
-    We also explore mass-size relations for our samples using \mstar{} within different 
-    radius (e.g. 120, 150 kpc) and the $R_{\mathrm{50}}$ derived within these apertures, 
-    and find consistent results.
-
-    We qualitatively compare our results with the one for $z\leq 0.09$ central ETGs in  
-    $14\le$\logmh{}$<15$ halos from \citealt{HCompany13} (HC13; green solid line).
-    HSC13 used the group catalog by \citet{Yang2007} to estimate \logmh{}. 
-    They estimated the 2-D $R_{\mathrm{e}}$ using single-\ser{} model fitting to SDSS 
-    images, and derived \mstar{} based on SED fitting using the BC03 (\citealt{BC03}) 
-    synthetic population model.
-    We empirically convert their \mstar{} from the Kroupa IMF to the Chabrier one 
-    used in this work by applying a constant -0.05 shift to their values (see 
-    \citealt{Bernardi2016}). 
-    We also increase the \mstar{} in HC13 by $+0.1$dex to account for the systematic 
-    difference between their BC03 and our FSPS model (see Appendix.\ref{app:B}). 
-    In HC13, the authors found no difference among the mass-size distributions for 
-    central galaxies in halos across $12.5\le$\logmh{}$<15.0$. 
-    Despite all the systematic differences, the mass-size distributions for both \rbcg{} 
-    and \nbcg{} galaxies follow the HC13 relation reasonably well (with slightly
-    shallower slopes) even at \logmtot{}$< 11.6$ where our samples start to become 
-    incomplete.
-
-    In short, we confirm that the massive central galaxies in this work generally 
-    follow the \mstar{}-size relation for massive ETGs at low-$z$.
-    \update{
-    More importantly, we find that the \mstar{}-size relations at high-\mstar{} end 
-    depends on \mhalo{}, suggesting that the central galaxies in denser environment 
-    (higher \mhalo{}) have slightly larger $R_{\mathrm{50}}$ comparing to the 
-    ones from smaller haloes at fixed \mtot{}. 
-    }
-
-    It would be interesting to revisit this topic using 2-D models based on deep HSC 
-    images as the next step.
-    It is worth noting that our results are based on massive galaxies at $z\sim 0.4$, 
-    while the sample of HC13 has $z<0.09$.
-    \update{
-    Although here we can not study the redshift evolution of \mstar{}-size relation 
-    here, it will be interesting to see whether the structural evolution of massive
-    galaxies between $z\sim 0.4$ and $0.0$ also depends on environment. 
-    If the \rbcg{} galaxies experienced more megers than the \nbcg{} ones during this 
-    time, we should expect that \mstar{}-size relation shows stronger environmental 
-    dependence at $z\sim 0.0$ using deeper image than SDSS.} 
-    On the other hand, if the \nbcg{} galaxies could assemble more \mstar{} through
+    \noindent 
+    \update{
+    the two relations share similar slopes within the uncertainties, but have 
+    different normalizations. 
+    And \mstar{}-size relations using \mstar{} within larger radius (e.g. 150 kpc) and the 
+    corresponding $R_{\mathrm{50}}$ show similar result.
+    }
+
+    \update{
+    This result clearly confirms the predicted environmental dependence of 
+    \mstar{}-size relation. 
+    Although it is beyond the scope of this work, whether the size evolution also 
+    depends on halo mass would be interesting to discuss. 
+    It is worth noting that our results are for massive galaxies at $z\sim 0.4$, 
+    while the sample of HC13 is at $z<0.09$. 
+    If the \rbcg{} galaxies experienced more mergers during this period, the 
+    \mstar{}-size relation shows stronger environmental dependence at $z\sim 0.0$. 
+    However, if the \nbcg{} galaxies can assemble more \mstar{} through
     minor mergers in the last 3-4 Gyrs, they could potentially ``catch-up'' with the 
-    \rbcg{} galaxies on the \mstar{}-size plane, and makes it harder to find the 
-    environmental dependence in nearby universe.
-    In principle, we can make uses of the frequency of tidal features and the numbers 
-    of satellites around our \rbcg{} and \nbcg{} galaxies to make some predictions 
-    in the near future.
-
-%% ------------------------------------------------------------------------------------ %%
-
-%%% ------------------------------------------------------------------------------------ %% 
-%  \begin{figure*}[t]
-%      \centering 
-%      \includegraphics[width=\textwidth]{fig/redbcg_m100_m10_new}
-%      \caption{\textbf{(a)}: Distributions of galaxies on the 
-%          \mtot{}-$\Delta (\log M_{\star})_{100\mathrm{kpc}-10\mathrm{kpc}}$ plane. 
-%          All \rbcg{} (open red boxes) and \nbcg{} (light, grey dots) galaxies 
-%          are shown in the background. 
-%          The \mtot{}-matched samples between $11.6<$\logms{}$<11.9$ (between two 
-%          vertical lines) are highlighted (\rbcg{}: solid red boxes; 
-%          \nbcg{}: bigger grey dots). 
-%          We also show the median values (solid triangular and hexagon), and the
-%          distributions of $\Delta (\log M_{\star})_{100\mathrm{kpc}-10\mathrm{kpc}}$
-%          (both histograms and kernel density distributions on the right).
-%          The best scaling relations for \rbcg{} (red, solid) and 
-%          \nbcg{} (grey, dashed) galaxies along with their uncertainties 
-%          are illustrated as well.~~
-%          \textbf{(b)}: Distributions of galaxies on the 
-%          $\Delta (\log M_{\star})_{100\mathrm{kpc}-10\mathrm{kpc}}$-\minn{} plane.~~
-%          \textbf{(c)}: Distributions of galaxies on the 
-%          $\Delta (\log M_{\star})_{100\mathrm{kpc}-10\mathrm{kpc}}$-\mtot{} plane.
-%          But, this time, we highlight the \rbcg{} and \nbcg{} samples that are 
-%          matched using \minn{} instead of \mtot{}.~~
-%          \textbf{(d)}: Relations between \mtot{} and \minn{}. 
-%          Other formats of figure (b), (c), and (d) are very similar with figure (a).}
-%      \label{fig:scaling_relation}
-%  \end{figure*} 
-%%% ------------------------------------------------------------------------------------ %%
-
-\subsubsection{Relations between stellar mass within different physical apertures}
+    \rbcg{} galaxies on the \mstar{}-size plane, and makes the environmental 
+    dependence weaker.
+    }
+
+%% ------------------------------------------------------------------------------------ %%
+
+\subsubsection{Relation between \mtot{} and \minn{}}
     \label{sssec:m100_m10}
 
-    We just show that the \mstar{}-size relation of massive central galaxies also 
-    depends on the \mhalo{} or environment, and now we explore relationships between 
-    \mstar{} within different apertures as alternative tools to help
-    us better understand the relationship between \mhalo{} and the assembly history of 
-    massive galaxies.  
-    Here we focus on \mtot{}, \minn{}, and also the logarithmic mass differences 
-    between them ($\Delta \log M$, reflecting \mstar{} ratio). 
-    Comparing to the \mstar{}-size relation, such relations are not affected by the 
-    ambiguous definition of ``size''; and comparing to the detailed \mden{} profiles, 
-    it is much easier to apply these relations to larger samples or to compare with 
-    simulations.
-
-    We show the results in Fig.\ref{fig:scaling_relation}.  
-    In panel (a), we plot the \mtot{} with $\Delta \log M$ for both the\rbcg{} 
-    and \nbcg{} samples. 
-    As expected, these two parameters well trace each other over the entire range of
-    \mtot{}, indicating that more massive central galaxies have larger 
-    fraction of total \mstar{} in their outskirts. 
-    Suggested in Fig.\ref{fig:prof_2}, the structural differences related to 
-    \mhalo{} seem to be more significant in the higher \mstar{} bin. 
-    We therefore highlight the \mtot{}-matched \rbcg{} and \nbcg{} galaxies at 
-    $11.7 \leq$\logmtot$< 11.9$. 
-    Although the $\Delta \log M$ distributions still greatly overlap at high-\mtot{} 
-    end, their median values (big, outlined symbols with error bars),
-    and kernel-density distributions clearly reveal systematic difference. 
-    Consistent, but slightly smaller, difference also exists for \mtot{}-matched 
-    samples at $11.6 \leq$\logmtot$< 11.9$.
-
-    At the same time, the comparisons in Fig.\ref{fig:prof_1} and 
-    Fig.\ref{fig:prof_2} also suggest that the \mtot{}-matched \rbcg{} galaxies 
-    have lower \minn{} than the \nbcg{} sample. 
-    \update{
-    When we plot $\Delta \log M$ with \minn{} for the \mtot{}-matched samples in 
-    panel (b), we can easily confirm this result.
-    The correlation between $\Delta \log M$ and \minn{} is quite weak for the 
-    \nbcg{} galaxies, but still visible. 
-    However, we see no apparent correlation between $\Delta \log M$ and \minn{} 
-    for the \rbcg{} galaxies. 
-    We also construct $\Delta \log M$ using logarithmic mass differences between 
-    100 and 30 (or 50) kpc, and the results are very similar.   
-    These reflect the structural differences we found in Fig.\ref{fig:prof_1}: 
-    at fixed \mtot{}, central galaxy in more massive halo tende to have even higher 
-    fraction of \mstar{} stored between 10 and 100 kpc than the one from smaller 
-    haloes.}
-
-    In panel (c), we show the relationship between \mtot{} and $\Delta \log M$ 
-    again, but highlight the \minn{}-matched samples showed in right panel of 
-    Fig.\ref{fig:prof_1}. 
-    \update{
-    Their distributions clearly show the impact of the much more prominent outer 
-    envelope hosted by \rbcg{} galaxies through the differences in \mtot{} and 
-    $\Delta \log M$ of the \minn{}-matched samples.
-    }
-
-    Finally, in panel (d), we plot \mtot{} against \minn{} directly.  
-    It is intriguing to see that the distributions of \rbcg{} and \nbcg{} galaxies 
-    on this 2-D plane seem to be offset with each other. 
-    At least at the high mass end, the central galaxies in more and less massive 
-    halos seem to follow \mtot{}-\minn{} relations with similar slopes, but different 
-    normalizations.  
-    Instead of ``arbitrarily'' grouping galaxies into different bins of \mtot{} or 
-    \minn{}, such scaling relation brings us a more generic view of the environmental 
-    dependence of structure, and could help us better investigate the relations among 
-    halo mass, assembly history, and the structure of massive galaxies.
-    On Fig.\ref{fig:scaling_relation} (d), we illustrate the \mtot{}-\minn{} relations 
-    at \logmtot$\geq 11.6$ that are derived using MCMC sampling method.  
+    \update{
+    It is important to show that the \mstar{}-size relation of massive central galaxies 
+    depends on the \mhalo{} or environment, but we want to point out that ``size'' is not 
+    a clearly defined concept for massive galaxies with multiple components, and its 
+    estimation depends on both the quality of the data and the method used in reality. 
+    When it comes to comparison with numerical simulation, it is also difficult to use the
+    exactly same definition.  
+    After some explorations using HSC data, here we propose a different scaling relation 
+    to help us reveal the environmental dependence of massive galaxies, which is the 
+    relation between the \mstar{} within 10 and 100 kpc apertures 
+    (\mtot{}-\minn{} relation). 
+    On the right panel of Fig.\ref{fig:scaling_relation}, it is clear that the 
+    distributions of \rbcg{} and \nbcg{} galaxies are offset with each other. 
+    On average, at fixed \mtot{}, the central galaxy from more massive halo seems to 
+    have lower amount of \mstar{} within the inner 10 kpc comparing to the central of 
+    less massive halo.
+    }
+    We also derive the best-fit \mtot{}-\minn{} relations at \logmtot$\geq 11.6$ using 
+    MCMC sampling method.  
     For \rbcg{} galaxies, the best-fit relation is:
@@
 
-    Fitting this relation in the full \mtot{} range results in even shallower slope for 
-    the \rbcg{} galaxies. 
-    Also, replacing the \minn{} with \mstar{} within 5 or 15 kpc apertures does not 
-    change our conclusions. 
-    In fact, the relation using $M_{\star, 5\ \mathrm{kpc}}$ shows more significant 
-    \mhalo{} dependence at the high-mass end. 
-    Unfortunately, due to the impact of PSF, the $M_{\star, 5\ \mathrm{kpc}}$ values 
-    are less reliable than \minn{}. 
-    \update{
-    Samples at lower redshift, images with higher spatial resolution, and 2-D modeling 
-    analysis can help us push the investigation further into smaller radius, and help 
-    us develop better proxy for the \mstar{} of the ``in-situ'' component.  
-    }
-
-    \update{
-    Limited by our capability to estimate \mhalo{} with better accuracy or individually, 
-    we can not further quantify this \mhalo{}-dependence here.
-    Albeit that the \redm{} richness ($\lambda$) traces \mhalo{} reasonably well, 
-    we do not find any clear correlation with $\lambda$ within the \rbcg{} galaxies.
-    }
-    In the current sample, most of the \rbcg{} galaxies are centrals of clusters with 
-    $30 \leq \lambda \leq 40$, and only a small fraction comes from more massive clusters.  
-    Therefore, the small sample size, the uncertainties of richness from shallow SDSS
-    images, and the intrinsic scatter of the $\lambda$-\mhalo{} relation may conspire to 
-    stop us from extracting more information from this \mhalo{}-dependence.
-
-    \update{
-    The \mhalo{}-dependence of structure in massive central galaxies could be the result 
-    of many different physical processes. 
-    It would be very interesting to compare with progenitors of these massive 
-    galaxies at higher redshift and with the results of numerical simulations (e.g. see 
-    Fig.1 of \citealt{Wellons2016b}) vial the \mtot{}-\minn{} or similar relations.
+    \update{ 
+    Instead of ``arbitrarily'' grouping galaxies into \mtot{} bins, this scaling relation 
+    brings us a more generic view of the environmental dependence of structure.
+    Given that we are using \mtot{} as proxy of total \mstar{}, and \minn{} as the mass of 
+    the in-situ component, this relation essentially reflects the relative contribution of
+    the in-situ (or accreted) component, and its dependence on halo properties.  
+    Since the physical definition of aperture \mstar{} is clear and straightforward, it is 
+    easier to compare with other observations (e.g. massive galaxies at higher redshift) or  
+    theoretical predictions using this relation (e.g. see Fig.1 of \citealt{Wellons2016b}). 
+    We will discuss more about the assumptions on the physical meanings of \mtot{} and 
+    \minn{} later, but replacing the \minn{} with \mstar{} within 5 or 15 kpc aperture 
+    will not change the result; and using \mstar{} in even larger apertures as proxy of 
+    total \mstar{} will make the difference between \rbcg{} and \nbcg{} galaxies more 
+    significant.
+    With the helps of numerical simulations, we may come up with better observational 
+    proxies for the \mstar{} of the in-situ and accreted components to investigate, and 
+    further explore how the distributions of galaxies on the \mtot{}-\minn{} plane depends 
+    on detailed halo properties and evolves with redshift. 
+    In this work, we do not find any clear dependence on the cluster richness ($\lambda$)
+    within the \rbcg{} sample, but it could be just caused by the relative narrow range of 
+    richness, uncertainties of the $\lambda$ estimates, and the intrinsic scatter of the 
+    $\lambda$-\mhalo{} relation.  
     }
@@
 
-\section{Discussions}
+%% ------------------------------------------------------------------------------------ %% 
+\section{Discussion}
     \label{sec:discussion}
 
-    \update{
-    In the past decade, the mass assembly history and structural evolution of massive 
-    ETGs remain an active topic.  
-    More convincing evidence from observations of massive galaxies at high redshift 
-    suggest that the progenitors of massive elliptical galaxies today are quite different 
-    in structural properties (e.g. \citealt{Bezanson2009}, \citealt{vanDokkum2010}).  
-    Collectively, they need to increase their ``size'' ($R_{\mathrm{e}}$) by a factor 
-    of 2 to 4 (e.g. \citealt{Newman2012}, \citealt{vdWel2014}), perhaps decrease the 
-    central stellar velocity dispersion a little (e.g. \citealt{vandeSande2011}, 
-    \citealt{Belli2014}) without changing their inner \mden{} profiles too much 
-    (e.g. \citealt{Szomoru2012}, \citealt{Patel2013}) and  in the last 8-10 Gyrs.  
-    With the help from better simulations, the promising ``two-phase'' formation 
-    scenario seems to be able to deal with these challenges well (e.g. 
-    \citealt{Oser2010}, \citealt{Oser2012}).
-    However, it raises additional questions.
-    As the massive central galaxies in more massive halos should have different mass 
-    assembly history, experience more (minor) mergers than the ones in smaller halos, 
-    we expect to see certain structural properties depend on ``environment''. 
-    Interestingly, although hints of such dependence have been noticed at high redshift 
-    (e.g. \citealt{Papovich2012}, \citealt{Delaye2014}), no clear evidence has been found 
-    at low redshift (e.g. \citealt{Nair2010}, \citealt{HCompany13}). 
     In this work, taking advantage of the deep photometry from the HSC survey, we 
-    detect subtle but robust evidence that suggests the \textbf{structure
-    of massive central galaxies, both the inner and outer parts, depends on the mass of
+    detect subtle but robust evidence that suggests the \textbf{structures
+    of massive central galaxies, at both the inner and outer parts, depend on the mass of
     their host halos at $0.3 < z < 0.5$}. 
@@
     implications.
-    }
-
-    Firstly, the comparisons of the \mden{} profiles suggest that \textbf{\mhalo{} plays
-    a subtle role in shaping the structure of massive central galaxies}.  
-    It appears that massive central galaxies at \logms{}$\geq 11.5$ were shaped by more 
-    or less the same physical processes.  
-    At the fixed \mtot{} and \minn{}, centrals from cluster-level halos do not form a 
-    unique population. 
-    Instead, their individual \mden{} profiles greatly overlap with the ones from smaller 
-    halos.
-    At similar \mtot{}, even their median \mden{} profiles only show very subtle 
-    differences. 
-    For the \rbcg{} sample, this results is similar to \citep{Zhao2015} where these 
-    authors found a considerable fraction of nearby BCGs (34\%) does not fall into 
-    the ``cD'' class.
-    \update{
-    From the smooth distributions of \mden{} profiles on Fig.\ref{fig:prof_1} 
-    and Fig.\ref{fig:prof_4}, it becomes even harder to draw a meaningful line  
-    between ``cD'' galaxy and ``normal elliptical''. 
-    For ETGs above certain \mstar{}, it seems more physical to treat their outer 
-    envelopes as the ``accreted'' components from a series of merging events. 
-    And, the differences in their assembly histories lead to outer \mden{} profiles 
-    with a variety of slopes. 
-    }
+
+%% ------------------------------------------------------------------------------------ %%
+
+\subsection{The ``Two phase'' Formation Scenario of Massive Galaxies and the 
+            Build-Up of Outer Envelopes}
 
@@
 
+%% ------------------------------------------------------------------------------------ %%
+
+\subsection{On the Classification of "cD" Galaxies}
+
+    \alexie{Begin with one sentance about what the cD class is.
+Not sure we have used this terminology before.
+Somthing like " Massive galaxies with extended outer envoloppes are often referred to as "cD" galaxies, but is there actual evidence that these galaxies form a distinct population?
+Somethig like that.
+}
+
+    \alexie{I woudl start this more by saying that we observe a large diversity on the outer component. Large scatter. No evidence that this is however two distinct classes.}
+
+    Firstly, the comparisons of the \mden{} profiles suggest that \textbf{\mhalo{} plays
+    a subtle role in shaping the structure of massive central galaxies}.  
+    It appears that massive central galaxies at \logms{}$\geq 11.5$ were shaped by more 
+    or less the same physical processes \alexie{remove this phrase}.  
+    At the fixed \mtot{} and \minn{}, centrals from cluster-level halos do not form a 
+    unique population. 
+    Instead, their individual \mden{} profiles greatly overlap with the ones from smaller 
+    halos.
+    At similar \mtot{}, even their median \mden{} profiles only show very subtle 
+    differences. 
+    For the \rbcg{} sample, this results is similar to \citep{Zhao2015} where these 
+    authors found a considerable fraction of nearby BCGs (34\%) does not fall into 
+    the ``cD'' class.
+    \update{
+    From the smooth distributions of \mden{} profiles on Fig.\ref{fig:prof_1} 
+    and Fig.\ref{fig:prof_4}, it becomes even harder to draw a meaningful line  
+    between ``cD'' galaxy and ``normal elliptical''. 
+    For ETGs above certain \mstar{}, it seems more physical to treat their outer 
+    envelopes as the ``accreted'' components from a series of merging events. 
+    And, the differences in their assembly histories lead to outer \mden{} profiles 
+    with a variety of slopes. 
+    }
+
+%% ------------------------------------------------------------------------------------ %%
+
+\subsection{Structural Differences in the Cores of Massive Galaxies}
+
     \update{
@@
     further complicate the picture.
-    On Fig.\ref{fig:scaling_relation}, there are a few \rbcg{} galaxies with quite low 
+    On Fig.\ref{fig:m100_m10_A}, there are a few \rbcg{} galaxies with quite low 
     \minn{} at high \mtot{} end. 
@@
     an interesting topic to investigate in the future.
+
+%% ------------------------------------------------------------------------------------ %%
+
+\subsection{What is the "Total Mass" of Massive Galaxies?}
 
@@
 	%\subsection{Future Improvements}
-    %\label{ssec:future}
-    %These results are broadly consistent with the prediction of the ``two-phase''
-    %scenario: the massive central galaxies in more massive halos should experience 
-    %more minor, dry mergers that accumulate more stars in the outskirts. 
     \update{

### 2017-01-23 draft/ms_v3.tex
test
Update

@@
 % Version 2; emulateapj format; Edited by SH and AL
+% Version 3; emulateapj format; Edited AL
 
@@
 
-%\title{The Environment and Structure of Massive Central Galaxies
-%       using the Subaru Hyper Suprime-Cam Survey}
-
-%\title{Environmental Dependence of the Structures of Massive Central 
-%       Galaxies at $0.3 < z < 0.5$}
-
 \title{A Detection of the Environmental Dependence of the Stellar Halos of 
@@
 \end{abstract}
-\keywords{galaxies: elliptical and lenticular, cD --- galaxies: formation --- 
-          galaxies: photometry --- galaxies: structure --- galaxies: surveys}
+\keywords{galaxies: elliptical and lenticular, cD --- 
+          galaxies: formation --- 
+          galaxies: photometry --- 
+          galaxies: structure --- 
+          galaxies: surveys}
 
@@
 
-    \plan{Scientific Background}
-    \begin{itemize}
-        \item \plan{Massive galaxies are important cosmic probe and unique labs to study 
-            galaxy evolution.} 
-        \item \plan{Briefly explain why massive early-type galaxies are important through 
-            the difficulties of stellar-halo mass relation and stellar mass function at 
-            the high-mass end.}
-        \item \plan{Brief summary of the current understanding of their cosmic assembly 
-            history.}
-        \item \plan{Explain why we should care about the environment, and why we expect to 
-            see some environmental dependence in the structure and other properties of
-            massive galaxies.}
-        \item \plan{Brief review of the current observations.  It is still not clear 
-            whether there is a clear environmental dependence.}
-    \end{itemize}
-
-    \plan{Observational difficulties (a.k.a Why we need HSC)}
-    \begin{itemize}
-        \item \plan{Explain why it is important to study the mass distribution of 
-            massive galaxies out to large physical radius; and, given their unique light 
-            profiles, why it is more difficult to study them compared to late-type 
-            galaxies.}
-        \item \plan{Very brief summary of past observational efforts, and why they are not 
-            good enough (Not enough number of really massive galaxy; Shallow images; 
-            Background subtraction issue; and stacking analysis can be dangerous as while)}
-    \end{itemize}
-
-    \update{
-    In the past decade, the mass assembly history and structural evolution of massive 
-    ETGs remain an active topic.  
-    More convincing evidence from observations of massive galaxies at high redshift 
-    suggest that the progenitors of massive elliptical galaxies today are quite different 
+    Massive galaxies are important cosmic probes and unique laboratories to study the 
+    theory of galaxy formation and evolution. 
+    In the nearby universe, massive galaxies are dominated by early-type, quiescent 
+    galaxies (\addref{}). 
+    Under the $\Lambda$-CDM cosmology, they are the end products of the hierarchical
+    structural growth along with their host dark matter halos (\addref{})
+    They should start to form very early on in the highest peaks of density field 
+    (\addref{}), and are very likely the descendants of the extreme star-forming galaxies
+    (e.g. sub-millimeter galaxies, \addref{}) and luminous QSOs (\addref{}) detected at 
+    very high redshift. 
+    Nowadays, the hierarchical growth scenario under the $\Lambda$-CDM cosmology can 
+    already predict important statistical properties of galaxies that are in reasonable
+    consistent with observations, like the stellar mass-halo mass relation 
+    (SMHM, e.g. \addref{}) and the stellar mass function (SMF, e.g. \addref{}) 
+    at different redshift. 
+    However, these statistics still have large uncertainties and potential problems at 
+    the high mass end (e.g. \addref{}) that reflect limitations in both theoretical and 
+    observational sides. 
+    Therefore, it is fundamentally important for us to understand the star formation, mass 
+    assembly, and structural evolution history of these massive galaxies.
+
+    Thanks to the advances in observations at higher redshift and numerical simulation 
+    with more realistic physics, we now realize that these massive, early-type galaxies 
+    must have experienced dramatic structural and dynamical transformation in the last 
+    $\sim$ 10 Gyrs.
+    More and more convincing observations at high redshift point out that the 
+    progenitors of $z=0$ massive elliptical galaxies today are quite different 
     in structural properties (e.g. \citealt{Bezanson2009}, \citealt{vanDokkum2010}).  
@@
     at low redshift (e.g. \citealt{Nair2010}, \citealt{HCompany13}).
-    }
-
-    \plan{Basic idea of this work}
+
+    \plan{Scientific Background}
     \begin{itemize}
-        \item \plan{Here we take advantages of the ambitious Hyper-Suprime camera 
-            survey\ldots}
+        \item \plan{Massive galaxies are important cosmic probe and unique labs to study 
+            galaxy evolution.} 
+        \item \plan{Briefly explain why massive early-type galaxies are important through 
+            the difficulties of stellar-halo mass relation and stellar mass function at 
+            the high-mass end.}
+        \item \plan{Brief summary of the current understanding of their cosmic assembly 
+            history.}
+        \item \plan{Explain why we should care about the environment, and why we expect to 
+            see some environmental dependence in the structure and other properties of
+            massive galaxies.}
+        \item \plan{Brief review of the current observations.  It is still not clear 
+            whether there is a clear environmental dependence.}
     \end{itemize}
 
-    \update{Here, we take advantage of the excellent image quality of the HSC survey, and 
+    \plan{Observational difficulties (a.k.a Why we need HSC)}
+    \begin{itemize}
+        \item \plan{Explain why it is important to study the mass distribution of 
+            massive galaxies out to large physical radius; and, given their unique light 
+            profiles, why it is more difficult to study them compared to late-type 
+            galaxies.}
+        \item \plan{Very brief summary of past observational efforts, and why they are not 
+            good enough (Not enough number of really massive galaxy; Shallow images; 
+            Background subtraction issue; and stacking analysis can be dangerous as while)}
+    \end{itemize}
+
+    Here, we take advantage of the excellent image quality of the HSC survey, and 
     investigate the potential environmental dependence of structure for massive galaxies 
@@
     galaxies in halos that are more or less massive than \logmh{}$\sim 14.0$ at 
-    $0.3 < z < 0.5$ from the available $\sim 100$ square degree of HSC data.}
-
-    \update{Due to the difficulty in appropriately modeling the \mstar{} distributions of 
+    $0.3 < z < 0.5$ from the available $\sim 100$ square degree of HSC data.
+
+    Due to the difficulty in appropriately modeling the \mstar{} distributions of 
     massive galaxies out to their very outskirts, we focus on \mstar{} within two different 
-    physical apertures in this work:}
+    physical apertures in this work:
 
     \begin{itemize}
-        \item \update{\mstar{} within 10 kpc, \minn{}: according to the ``two-phase'' 
+        \item \mstar{} within 10 kpc, \minn{}: according to the ``two-phase'' 
             scenario, the ``in-situ'' star-formation quickly built up the inner, dense 
@@
             We can reliably measure \minn{} without being bothered by smearing effect
-            of seeing.}
-        \item \update{\mstar{} within 100 kpc, \mtot{}: for massive galaxies in this work, 
+            of seeing.
+        \item \mstar{} within 100 kpc, \mtot{}: for massive galaxies in this work, 
             100 kpc aperture reaches to 5-10 $\times R_{\mathrm{e}}$ and very low 
@@
             Although not perfect, \mtot{} is still a much better tracer of total 
-            \mstar{} than the model-dependent ones using shallower images.}
+            \mstar{} than the model-dependent ones using shallower images.
     \end{itemize}
 
-    \update{Massive central galaxies in this work show an intriguing diversity on the 
+    Massive central galaxies in this work show an intriguing diversity on the 
     plane defined by these two metrics.  
@@
     Fig.\ref{fig:m100_m10_color}, we always use elliptical apertures that follow the 
-    average isophotal shape for photometry in this work.}
+    average isophotal shape for photometry in this work.
     And, within our choices of redshift and \mstar{} ranges, we can safely ignore 
@@
     and ${\Omega}_{\lambda}=0.7$.
+
 %% ------------------------------------------------------------------------------------ %%

### 2017-03-14 draft/ms.tex
New draft

--- 2016-02-08 draft/ms.tex
@@
 % Version 0; preprint format; Written by SH
+% Version 1; emulateapj format; Edited by SH and AL
+% Version 2; emulateapj format; Edited by SH and AL
+% Version 3; emulateapj format; Edited AL
+% Version 4; emulateapj format; Edited SH
+% Version 5; MNRAS format; Edited SH
 
-\documentclass[preprint]{aastex}
-\usepackage{emulateapj5}
-\usepackage{apjfonts}
+\documentclass[a4paper,fleqn,usenatbib]{mnras}
+
+% Packages
+%\usepackage{deluxetable}
+%\usepackage{apjfonts}
+\usepackage{newtxtext,newtxmath}
+\usepackage[T1]{fontenc}
+\usepackage{ae,aecompl}
 \usepackage{amssymb, amsmath}
 \usepackage{graphicx}
-\usepackage{CJK}
+\usepackage{natbib}
+\usepackage{hyperref}
+\usepackage{float}
+\usepackage[usenames, dvipsnames]{color}
+
+% Package Settings
+\hypersetup{colorlinks=true,
+            citecolor=cyan,
+            linkcolor=cyan,
+            filecolor=magenta,      
+            urlcolor=cyan}
+\urlstyle{same}
+
+% Figure extention
 \DeclareGraphicsExtensions{.pdf,.png,.jpg}
-\bibliographystyle{apj}
-
-\input psfig.tex
 
@@
 \def\sb{mag~arcsec$^{-2}$}
-\def\solum{$L_\odot$}
-\def\solmass{$M_\odot$}
+\def\lsun{$L_\odot$} 
+\def\msun{$M_\odot$}
 \def\sigs{$\sigma_*$}
@@
 
-%Song Huang's definition 
+\def\etal{{\ et al.~}}
 \def\galfit{{\tt GALFIT}}
 \def\ser{{S\'{e}rsic\ }}
+\def\redm{\texttt{redMaPPer}}
+\def\cmodel{\texttt{cModel}}
+% Samples
+\def\rbcg{\texttt{cenHighMh}}
+\def\nbcg{\texttt{cenLowMh}}
+\def\redbcg{{$\lambda \ge 30$}}
+\def\nonbcg{{$\lambda < 20$}}
+% Mass related 
+\def\mstar{{$M_{\star}$}}
+\def\mhalo{{$M_{\mathrm{halo}}$}}
+\def\logms{{$\log (M_{\star}/M_{\odot})$}}
+\def\logmh{{$\log (M_{\mathrm{Halo}}/M_{\odot})$}}
+
+\def\minn{{$M_{\star,10\mathrm{kpc}}$}}
+\def\meff{{$M_{\star,15\mathrm{kpc}}$}} 
+\def\mtot{{$M_{\star,100\mathrm{kpc}}$}}
+\def\mout{{$M_{\star,150\mathrm{kpc}}$}}
+\def\mmax{{$M_{\star,\mathrm{Max}}$}}
+\def\mgama{{$M_{\star,\mathrm{GAMA}}$}}
+\def\mcmodel{{$M_{\star,\mathrm{cModel}}$}}
+
+\def\logminn{{$\log (M_{\star,10\mathrm{kpc}}/M_{\odot})$}}
+\def\logmtot{{$\log (M_{\star,100\mathrm{kpc}}/M_{\odot})$}}
+\def\logmout{{$\log (M_{\star,150\mathrm{kpc}}/M_{\odot})$}}
+\def\logmmax{{$\log (M_{\star,\mathrm{Max}}/M_{\odot})$}}
+\def\logmgama{{$\log (M_{\star,\mathrm{GAMA}}/M_{\odot})$}}
+\def\logmcmodel{{$\log (M_{\star,\mathrm{cModel}}/M_{\odot})$}}
+
+\def\m2l{{$M_{\star}/L_{\star}$}}
+\def\mden{{$\mu_{\star}$}}
+
+% Commenting:
+\newcommand{\xxx}[1]{\textcolor{red}{\textbf{XXX}}}
+\newcommand{\todo}[1]{\textcolor{red}{\textbf{TODO:~#1}}}
+\newcommand{\plan}[1]{\textcolor{cyan}{#1}}
+\newcommand{\addref}{{\textcolor{red}{REF}}}
+\newcommand{\note}[2]{\textcolor{blue}{\textbf{[Comment (#1): #2]}}}
+\newcommand{\song}[1]{\textcolor{magenta}{\textbf{[Song: #1]}}}
+\newcommand{\alexie}[1]{\textcolor{blue}{\textbf{[Alexie: #1]}}}
+\newcommand{\kevin}[1]{\textcolor{green}{\textbf{[Kevin: #1]}}}
+\newcommand{\update}[1]{\textcolor{Bittersweet}{#1}}
+%\newcommand{\update}[1]{#1}
+
+%%%%%%%%%%%%: Title and Affiliations %%%%%%%%%%%%
+
+\title[Structure and Halo of Massive Galaxies]{A Detection of the Environmental 
+       Dependence of the Stellar Halos of Massive Central Galaxies}
+
+\author[S. Huang et al.]{Song Huang,$^{1,2}$\thanks{E-mail: song.huang@ipmu.jp (SH)}
+        HSC collaboration$^{3}$   
+        \\ \\
+        % List of institutions
+        $^{1}$Kavli-IPMU, The University of Tokyo Institutes for Advanced Study, 
+              the University of Tokyo (Kavli IPMU, WPI), Kashiwa 277--8583, Japan\\
+        $^{2}$Department of Astronomy and Astrophysics, University of California 
+              Santa Cruz, 1156 High St., Santa Cruz, CA 95064, U.S.A\\
+        $^{3}$Another Department, Different Institution, Street Address, City Postal 
+              Code, Country
+        }
+
+\date{Accepted XXX. Received YYY; in original form ZZZ}        
+\pubyear{2017}
+
+%        \author{Song Huang\altaffilmark{1} 
+%        Alexie Leauthaud\altaffilmark{1}, 
+%        Kevin Bundy\altaffilmark{1},
+%        Michael Strauss\altaffilmark{2},
+%        Yen-Ting Lin\altaffilmark{3},
+%        Rachel Mandelbaum\altaffilmark{4}
+%        }
+%\altaffiltext{2}{Princeton University Observatory, 
+%    Peyton Hall, Princeton, NJ 08544, USA}
+%\altaffiltext{3}{Institute of Astronomy and Astrophysics, Academia Sinica, 
+%    P.O.~Box 23--141, Taipei 10617, Taiwan}
+%\altaffiltext{4}{Carnegie-Mellon University \todo{correct affiliation here}}
 
@@
 
-\slugcomment{Draft version 0}
-\shorttitle{ENVIRONMENT DEPENDENCE OF MASS-SIZE RELATION}
-\shortauthors{HUANG ET AL.}
-
 \begin{document}
 
-\begin{CJK*}{UTF8}{gbsn}
+\label{firstpage}
+\pagerange{\pageref{firstpage}--\pageref{lastpage}}
 
-%%%%%%%%%%%%: Title and Affiliations %%%%%%%%%%%%
-
-\title{The Environmental Dependence of Structures for Massive Galaxies
-from the Hyper-Suprime Camera Survey}
-
-\author{Song Huang (黄崧)\altaffilmark{1} Alexie Leauthaud\altaffilmark{1}, 
-Kevin Bundy\altaffilmark{1}, and You}
-\date{}
-
-\altaffiltext{1}{Kavli Institute for the Physics and Mathematics of the
-Universe, Todai Institutes for Advanced Study, the University of Tokyo (Kavli
-IPMU, WPI), Kashiwa 277-8583, Japan}
+\maketitle
 
@@
 
-  Many recent observations and numerical simulations suggest that nearby
-  massive, early-type galaxies are formed through a ``two-phase'' process.  In
-  the proposed second phase, the extended stellar envelope was accumulated
-  through many dry mergers. (XX TODO)
+    The promising hierarchical assembly scenario of massive galaxies suggest the 
+    structure of these galaxies should depend on their environments or halo mass.
+    Yet, at low redshift, observations find no clear evidence for that. 
+    Here, using the deep images from the Subaru Hyper Suprime-Cam (HSC) survey,
+    we map the stellar mass distributions of massive galaxies at $0.3 < z < 0.5$ 
+    out to the very outskirt, and detect subtle, but robust structural differences 
+    that depend on halo mass for central galaxies at high mass end. 
+    With the help of the \redm{} catalog, we separate these massive galaxies 
+    into centrals of halos that are more and less massive than 
+    $M_{200m}\sim 10^{14} M_{\odot}$.
+    For centrals with similar stellar mass within 100 kpc, the ones from 
+    more massive halos on average have slightly more flattened inner profile 
+    within $\sim 10$-$20$ kpc, and more prominent outer envelope.
+    Meanwhile, when matched at the same stellar mass within inner 10 kpc--a 
+    proxy of the mass of the in-situ component, the massive centrals of more  
+    massive halos show much more significant outer stellar envelopes.    
+    We also see that these two samples of massive galaxies follow slightly 
+    different mass-size relation and the relationship between the stellar mass 
+    within 100 and 10 kpc.
+    Such differences in structure are broadly consistent with the expectation that
+    central galaxy from more massive halo should have more complex merging history.
+    These results highlight the importance of deep photometry in the study of 
+    the assembly history of massive galaxies.
 
 \end{abstract}
-\keywords{galaxies: elliptical and lenticular, cD --- galaxies: formation --- 
-          galaxies: photometry --- galaxies: structure --- galaxies: surveys}
 
-\maketitle
+\begin{keywords}
+    galaxies: elliptical and lenticular, cD --
+    galaxies: formation --
+    galaxies: photometry -- 
+    galaxies: structure -- 
+    galaxies: surveys}
+\end{keywords}
 
@@
 
+%% ------------------------------------------------------------------------------------ %% 
+    \begin{figure*}
+        \centering 
+        \includegraphics[width=\textwidth]{fig/redbcg_sdss_compare}
+        \caption{
+            A comparison between the imaging quality of SDSS and HSC Wide for a sample 
+        	of nearby massive elliptical galaxies at $0.2 < z < 0.5$.  
+            These images are generated using $gri$ band images with an arcsinh stretch 
+            \citep{Lupton2004}. 
+            The HSC \texttt{WIDE} layer is $3.0$-$4.0$ magnitudes deeper than SDSS 
+            which is critical to map the outskirts of ETGs out to large radii.
+            }
+        \label{fig:sdss_compare}
+    \end{figure*}
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
+  \begin{figure*}
+      \centering 
+      \includegraphics[width=\textwidth]{fig/redbcg_m100_m10_compare}
+      \caption{
+          Three-color images for a subsample of massive galaxies at $z\sim 0.4$, and 
+          with similar values for their \mstar{} within a 10 kpc aperture 
+          (the dash-line circle on top-left figure indicates the scale of 10 kpc;
+          $11.2<\log (M_{\star,10\ \mathrm{kpc}}/M_{\odot})<11.3$). 
+          Galaxies are rank-ordered from top to bottom and from left to right by 
+          their \mstar{} within 100 kpc aperture which varies from $10^{11.2} M_{\odot}$ 
+          to $10^{11.7} M_{\odot}$. 
+          At fixed "inner" mass ($M_{\star,10}$), massive galaxies display significant
+          diversity in their outer profiles. 
+          Red boxes indicate galaxies in halos more massive than 
+          $\sim 10^{14.0} M_{\odot}$. 
+          }
+      \label{fig:m100_m10_color}
+  \end{figure*}
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
 \section{Introduction}
+    \label{sec:intro}
 
-\section{Sample and Data Reduction}
+    Massive galaxies are unique laboratories to study both cosmology and galaxy 
+    formation. 
+    Although the hierarchical growth scenario under the $\Lambda$-CDM cosmology 
+    is a solid theoretical background (e.g. \citealt{Baugh1996, DeLucia2006}, 
+    plenty important questions regarding the star-formation history, mass assembly 
+    process, and structural evolution of these massive galaxies remain open. 
+    Thanks to the advances in observations and numerical simulations, the newly 
+    developed ``two-phase'' formation scenario (e.g. \citealt{Oser2010, Oser2012}) 
+    becomes the most promising theory that can reasonably explain different 
+    observations of massive galaxies. 
+    Under this picture, the highly dissipative processes at high-$z$ (e.g cold 
+    accretion, gas-rich merger; e.g. \citealt{Hopkins2008, Dekel2009}) induce 
+    intense starburst, and quickly form the massive progenitors of $z\sim 0$ massive 
+    early-type galaxies (ETGs).     
+    Later, certain physical mechanism (e.g. AGN feedback; e.g. \citealt{Sijacki2007,
+    Fabian2012}) 
+    efficiently quenched the on-going star formation so that a large fraction of 
+    these massive progenitors become quiescent at $z>1$ (e.g. \citealt{Bezanson2009,
+    Kriek2016}). 
+    At the same stellar mass (\mstar{}), these so-called ``red nuggets'' 
+    (e.g. \citealt{Damjanov2009}) have smaller effective radius 
+    ($R_{\mathrm{e}}$; \citealt{Trujillo2006, vanDokkum2008, Cimatti2008}), 
+    slightly higher central velocity dispersion and stellar mass density 
+    (\mden{}; e.g. \citealt{vandeSande2011, Belli2014}), more disk-like morphology 
+    (e.g. \citealt{vanderWel2011}) than their local descendants 
+    (e.g. \citealt{Bezanson2009, vanDokkum2010}). 
+    Later, the second phase of evolution is driven by non-dissipative processes 
+    like dry mergers with other galaxies (e.g. \citealt{Naab2006, Khochfar2006}). 
+    According to the ``two-phase'' scenario, minor mergers make dominated 
+    contribution during this period as they help explain the significant increase
+    of $R_{\mathrm{e}}$ (e.g. \citealt{Newman2012, vdWel2014}) and accumulation of 
+    outer stellar halo (e.g.  \citealt{Szomoru2012, Patel2013}).
 
+    Despite the great success, it also raises new questions. 
+    Under the $\Lambda$-CDM cosmology, the formation of galaxy is intrinsically 
+    tied to the growth of the host dark matter halo 
+    (e.g. \citealt{Leauthaud2012, Behroozi2013}).
+    Massive ETGs living in the center of more massive halos should experience 
+    different mass assembly history and undergo different merging events comparing 
+    to the ones from smaller halos. 
+    Therefore, it is reasonable to expect that the structures of massive galaxies
+    depend on the ``environment''\footnote{Although there are different 
+    observational definition of environment, we use the term ``environment'' and 
+    halo mass interchangeably in this work.}.
+
+    As one of the most important structural parameters, the $R_{\mathrm{e}}$ of 
+    massive ETGs follows a tight and steep relation with the \mstar{} 
+    (e.g. \citealt{Shen2003, Guo2009}). 
+    Models based on the ``two-phase'' formation scenario naturally predict that 
+    such mass--size relation should show environmental dependence, and 
+    $R_{\mathrm{e}}$ of massive ETGs in more massive halos should be larger 
+    than the ones in less massive halos at fixed \mstar{} 
+    (e.g. \citealt{Shankar2013, Shankar2014}). 
+    Interestingly, while hints of such dependence have been spotted at high-$z$ 
+    (e.g. \citealt{Papovich2012, Lani2013, Delaye2014}; but also see 
+    \citealt{Rettura2010}), solid evidence of it at low-$z$ is still absence 
+    (e.g. \citealt{Nair2010, HCompany13}; but also see \citealt{Yoon2017}).
+    This confusing result becomes a challenge to the hierarchical growth model 
+    of massive galaxies. 
+    On the observational side, both the depth of the images and the photometric 
+    method contribute to this problem. 
+    The steep inner \mden{} profiles, extremely extended stellar envelopes, 
+    and other structural details make it very difficult to accurately define and 
+    measure the \mstar{} and $R_{\mathrm{e}}$ of massive ETGs 
+    (e.g. \citealt{Bernardi2013, DSouza2014}).
+
+    Here, taking advantage of the excellent image quality of the HSC survey, we 
+    investigate the environmental dependence of structure in massive galaxies 
+    via comparing the \mden{} profiles and structural scaling relations between 
+    massive central galaxies living in more and less massive dark matter halos. 
+    Both the deep imaging depth ($i$-band images are typically 3-4 magnitude deeper 
+    than SDSS ones) and the good seeing condition (median FWHM$\sim 0.6^{\arcsec}$
+    in $i$-band) of the HSC images make them perfect for mapping the \mstar{}
+    distributions of massive galaxies out to very large radius (see 
+    Fig~\ref{fig:sdss_compare}). 
+    With the help of a cluster catalog, we select a large sample of massive central 
+    galaxies in halos that are more or less massive than \logmh{}$\sim 14.0$ at 
+    $0.3 < z < 0.5$ from the available $\sim 100$ square degree of HSC data.
+
+    Motivated by the ``two-phase'' scenario, also due to the difficulty in 
+    appropriately modeling the \mstar{} distributions of massive galaxies out to 
+    their very outskirts, we focus on \mstar{} within two different physical apertures 
+    in this work:
+
+    \begin{itemize}
+        \item \mstar{} within 10 kpc, \minn{}: according to the ``two-phase'' 
+            scenario, the ``in-situ'' star-formation quickly built up the inner, dense 
+            core of massive ETGs.  
+            Based on recent observations and simulations (e.g.~\citealt{vanDokkum2010}; 
+            \citealt{RodriguezGomez2016}), the in-situ 
+            component distributes mostly within the effect radius ($R_{\mathrm{e}}$, 
+            or 5-10 kpc) in massive galaxies.  
+            Here we use \minn{} as a proxy of the \mstar{} formed in the ``in-situ''
+            phase.  Although it is an empirical choice, the detailed comparison of 
+            the stellar mass surface density (\mden{}) profiles later suggests it indeed 
+            helps reveal interesting environmental dependence.  
+            Under the adopted cosmology, $1.0^{\arcsec}$ in radius equals 4.4 and 6.1 kpc 
+            at redshift 0.3 and 0.5.  
+            We can reliably measure \minn{} without being bothered by smearing effect
+            of seeing.
+        \item \mstar{} within 100 kpc, \mtot{}: for massive galaxies in this work, 
+            100 kpc aperture reaches to 5-10 $\times R_{\mathrm{e}}$ and very low 
+            \mden{} region, hence can be treated as proxy of the ``total'' \mstar{}. 
+            Limited by the accuracy of background subtraction, the \mden{} profile 
+            of outer region can not be reliably recovered for massive galaxies across 
+            our redshift range. 
+            Although not perfect, \mtot{} is still a much better tracer of total 
+            \mstar{} than the model-dependent ones using shallower images.
+    \end{itemize}
+
+    Massive central galaxies in this work show an intriguing diversity on the 
+    plane defined by these two metrics.  
+    We preview this using Fig~\ref{fig:m100_m10_color}, which shows a subsample of 
+    massive galaxies at $z\sim 0.4$ that share very similar value of \minn{}, but show 
+    a large range of outer structures. 
+    Assuming galaxies at the same \minn{} have similar amount stars in the in-situ 
+    component, it is of great interest to investigate the relation between their 
+    environments and outer envelopes that are assembled at later time. 
+    It is worth noting that, although a circular aperture is shown on 
+    Fig~\ref{fig:m100_m10_color}, we always use elliptical apertures that follow the 
+    average isophotal shape for photometry in this work.
+    And, within our choices of redshift and \mstar{} ranges, we can safely ignore 
+    significant mass growth and structural evolution 
+    (no star formation, lower merger rate \etal~e.g.\ \citealt{Bellstedt2016},
+    \citealt{Inagaki2015}; but also see \citealt{Bai2014}) 
+    with our redshift and \mstar{} ranges.
+
+    The paper is organized as follows. Section\ref{sec:data} gives a brief overview of 
+    the HSC observation and data reduction, along with the summary of the data selection
+    processes.  
+    Then, we will explain the procedures for extracting 1-D surface brightness profiles 
+    (Section \ref{sec:ellipse}) and estimating stellar mass (Section \ref{sec:mstar}) in
+    details.   
+    We will present the main results in Section \ref{sec:result}, and discuss the several 
+    related technical and scientific issues in Section \ref{sec:discussion}, ending with
+    summary and future plans in Section \ref{sec:summary}.
+
+    All the magnitudes used here are in AB system (\citealt{Oke1983}), and are corrected 
+    for Galactic extinction using calibrations from \citet{Schlafly11}.
+    In this work, we assume $H_0$ = 70~km~s$^{-1}$ Mpc$^{-1}$, ${\Omega}_m=0.3$, 
+    and ${\Omega}_{\lambda}=0.7$.
+
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
+    \begin{figure*}
+        \centering 
+        \includegraphics[width=\textwidth]{fig/redbcg_ellipse_example}
+        \caption{
+            Left: example of the 1-D surface brightness and ellipticity profile 
+            for a massive galaxy at $z=0.23$ in the $i$-band using \texttt{Ellipse}. 
+            In this work, we always show the radial profile using a $R^{1/4}$ scaling 
+            on the x-axis. 
+            By using this scale, the de Vaucouleurs profile will appear as a straight 
+            line on this figure. 
+            The dash-line shows the surface brightness profile after correcting the 
+            background. 
+            We also plot the relative brightness profile of the PSF model normalized 
+            at the central surface brightness of the galaxy to highlight the region 
+            affected by seeing. 
+            The grey shaded region highlights the region most affect by seeing 
+            ($r<3$ kpc).
+            On the top panel, the dash line shows the ellipticity used for the final 
+            isophote. 
+            Right: the masked $i$-band image of this galaxy with the isophotes 
+            extracted by \texttt{Ellipse}. 
+            The thick dotted line highlights the isophote with 
+            $\mu_{i}\sim 28.5$~\sb.
+            }
+        \label{fig:ellipse}
+    \end{figure*}
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
+\section{Data And Sample Selection}
+    \label{sec:data}
+
+\subsection{The Hyper Suprime-Cam Survey}
+    \label{ssec:hsc}
+
+    The Subaru Strategic Program (SSP, \citealt{MiyazakiInPrep}) makes use of the new 
+    prime-focus camera, the Hyper Suprime-Cam (HSC;~\citealt{Miyazaki2012}), on the 
+    8.2-m Subaru telescope at Mauna Kea. 
+    The ambitious multi-layer HSC survey takes advantage of the large field of 
+    view (FoV;~1.5 deg in diameter) of this camera and will cover $\sim 1400$ deg$^2$ 
+    in 5 broad bands (\textit{g r i z Y}) to a limiting depth of $r \sim 26$ mag 
+    in the \texttt{WIDE} layer. 
+    This work is based on the internal data release \texttt{S15B}, which covers 
+    $\sim 100$ deg$^2$ in all 5-band to full \texttt{WIDE} depth.  
+    The regions covered by this release overlap with a number of spectroscopic surveys 
+    (e.g.\ SDSS/BOSS: \citealt{Eisenstein2011}, \citealt{Alam2015}; 
+    GAMA: \citealt{Driver2011}, \citealt{Liske2015}).
+
+    The HSC \texttt{WIDE} survey is about $3.0$-$4.0$ magnitudes deeper in the $i$-band 
+    than SDSS. 
+    Combined with the excellent imaging resolution (the median $i$-band seeing is 0.6"), 
+    and the wide area, the HSC survey represents a tremendous data set to perform a 
+    large statistical study of the surface brightness profiles of ETGs out to large radii.     
+    Fig~\ref{fig:sdss_compare} illustrates the quality of HSC imaging compared to SDSS 
+    for three low redshift ETGs, and shows that HSC survey data are well suited for 
+    mapping the stellar distribution of massive galaxies out to large radii.
+
+	HSC $i$-band images typically have the best seeing compared to other bands because 
+	of strict requirements driven by weak lensing science. 
+    We will therefore use the $i$-band images to measure the stellar distributions of 
+    massive galaxies.
+
+%% ------------------------------------------------------------------------------------ %% 
+\subsection{HSC Data Processing}
+    \label{sec:pipeline}
+
+    The full details of the HSC data processing can be found in \citet{BoschInPrep}
+    and are briefly summarized here. 
+    The HSC SSP data are processed with \texttt{hscPipe 4.0.1}, a derivative of the 
+    Large Synoptic Survey Telescope (LSST) pipeline (e.g.\ \citealt{Juric2015}; 
+    \citealt{Axelrod2010}), modified for HSC. 
+    \texttt{hscPipe} first performs a number of tasks at the single exposure level 
+    (bias subtraction, flat fielding, background modeling, object detection and 
+    measurements). 
+    Astrometric and photometric calibrations are performed at the single exposure level. 
+    \texttt{hscPipe} then warps different exposures on to a common World Coordinate 
+    System (WCS) and combines them into coadded images. 
+    At this stage, \texttt{hscPipe} updates the images with a better astrometric and 
+    photometric calibration using stars that are common among exposures.
+
+    The pixel scale of the combined images is $0.168^{\arcsec}$. 
+    Photometric calibration is based on data from the Panoramic Survey Telescope 
+    and Rapid Response System (Pan-STARRS) 1 imaging survey 
+    (\citealt{Schlafly2012}, \citealt{Tonry2012}, \citealt{Magnier2013}). 
+    To achieve consistent deblending and photometry across all bands, \texttt{hscPipe} 
+    performs multi-band post-processing at the coadd level. 
+    First, \texttt{hscPipe} performs object detection on coadd images in each band 
+    independently and records the flux peak and the above-threshold region 
+    (referred as a ``footprint'') for each source. 
+    Next, ``footprints'' and peaks from different bands are merged together before     
+    performing deblending and measurements. 
+    Finally, \texttt{hscPipe} selects a reference band for each object based on the 
+    $S/N$ in different bands (for most galaxies in this work, the reference band is 
+    the $i$-band). 
+    After fixing the centroids, shape, and other non-amplitude parameters of each 
+    object in this reference catalog, \texttt{hscPipe} perform forced photometry 
+    on the coadd image in each band. 
+    This forced photometry approach is optimized to yield accurate galaxy colors.
+
+    For each galaxy, \texttt{hscPipe} measures a \cmodel{} magnitude using an approach 
+    that is similar to SDSS (\citealt{BoschInPrep}). 
+    However, as opposed to SDSS, the HSC \cmodel{} is based on forced photometry which 
+    means that it can accurately measure both the \textit{fluxes and colors of galaxies}. 
+    The HSC \cmodel{} algorithm fits the flux distribution of each object using a 
+    combination of a de~Vaucouleur and an exponential component and accounts for the PSF. 
+    The performance of this algorithm has been tested using synthetic objects 
+    (\citealt{SynPipeInPrep}), and the results indicate that, generally speaking, 
+    the HSC \cmodel{} photometry is accurate down to $i >25.0$ mag.  
+    However, \cmodel{} currently systematically underestimates the total fluxes of 
+    massive ETGs with extended stellar distributions. 
+    This is caused by an intrinsic limitation of \cmodel{} as it is incapable of
+    modeling profiles with extremely extended outskirts, a problem that is exacerbated 
+    at the depth of the HSC survey. 
+    In addition, at the depth of the HSC survey, accurate deblending in the vicinity of
+    large ETGs where satellites and background galaxies often blend with the low surface 
+    brightness stellar envelope is a challenging problem. 
+    The deblending method implemented by the \texttt{hscPipe} currently tends to 
+    ``over-deblend'' the outskirts of bright galaxies and leads to un 
+    under-estimation of the the total flux of massive ETGs (more discussion in 
+    \citealt{BoschInPrep}).  
+    For these reasons, our results will be based on custom developed code to measure 
+    the luminosities and stellar masses of massive galaxies. 
+    We use the HSC \texttt{hscPipe} photometry for two purposes: 
+    1) to perform a first broad sample selection, and 2) to estimate the average 
+    color of massive galaxies.
+
+%% ------------------------------------------------------------------------------------ %% 
+\subsection{Initial Massive Galaxy Sample}
+    \label{ssec:initial}
+
+    We begin by using a broad luminosity cut to select an initial sample of massive 
+    galaxies at $z < 0.5$ from the HSC photometric catalog. 
+    Based on Leauthaud\etal~(2016), galaxies with \logms{}$\geq 11.5$ mostly have 
+    $i_{\mathrm{SDSS, cModel}} \leq 21.0$ mag. 
+    We therefore select our initial sample to be brighter than 
+    $i_{\mathrm{HSC, cModel}} \leq 21.5$\footnote{We neglect the insignificant 
+    differences between the response curves of SDSS-$i$ and HSC-$i$ filters} 
+    and also limit our sample to regions that have reached the required depth of 
+    the \texttt{WIDE} survey in $i$-band.
+    %% The SQL search is saved as "sample.sql" 
+    %% The master catalog used here is "dr1_wide_galaxy_icmodel_21.5.fits"
+    %%   The original catalogs contain 2275477 objects
+
+    We further select extended objects with no deblending errors, with well defined 
+    centroids, and with \texttt{cModel} magnitudes in all five bands. 
+    After removing objects that have pixels affected by saturation, cosmic-rays, or 
+    other optical artifacts\footnote{each criterion removes less than 8\% of the 
+    entire sample}
+    %% Alexie: Actually, 8 percent is not small if we want to consider the number 
+    %%         densities. Let's re-evaluate the impact of these cuts for the 16B 
+    %%         data with FDFC}. 
+    This sample corresponds to 1760845 galaxies and will be referred as \texttt{hscPho}. 
+    %% Saved as "dr1_wide_galaxy_hscPho.fits"
+
+    Here we limit our study to the very high-\mstar{} end where the majority of galaxies 
+    have either a spectroscopic redshift or a robust red-sequence photo-$z$ from the 
+    \redm{} catalog (see Section \ref{ssec:redmapper}).  
+    We match the \texttt{hscPho} sample with a spec-$z$ catalog compiled by the HSC 
+    team\footnote{It is created by matching HSC objects with all publicly available 
+    spectroscopic redshifts (e.g.\ SDSS/BOSS; GAMA). The spec-z quality flag from 
+    different catalogs are homogenized into a single flag that indicates whether the 
+    redshift is secure (\ref{}). 
+    We only consider the ones with secure spec-$z$s during the match}.  
+    To ensure reasonable \mstar{}-completeness at the high-\mstar{} end we focus on
+    the redshift range $0.3 \leq z \leq 0.5$. 
+    %% This is catalog: "dr1_specz_use.fits"
+
+    For objects without external spec-$z$, we match them with the central galaxies 
+    from the \redm{} catalog using $2.0^{\arcsec}$ radius. 
+    The matched objects with useful red-sequence photo-$z$ ($z_{\lambda}$) are also 
+    included in the final sample of bright galaxies with reliable redshift between 
+    $0.3 \leq z \leq 0.5$. 
+    Comparing with spec-$z$, the accuracy of the red-sequence photo-$z$ is sufficient 
+    (median $|z_{\lambda} - z_{\mathrm{Spec}}| \sim 0.01$ for the ones with spec-$z$) 
+    for the goal of this work.
+    The \redm{} catalog provides additional 133 unique redshifts for massive galaxies 
+    in our sample.
+    %% Estimated from "dr1_redbcg_hsc_sdss_gama_1arcsec.fits"
+
+    In the end, at $0.3 \leq z \leq 0.5$, we gather a sample of 25286 galaxies with 
+    reliable redshift information (will be referred as \texttt{hscZ}).
+    %% Saved as "dr1_wide_galaxy_icmodel_21.5.fits"
+    Among them, the BOSS and SDSS "legacy" LRG samples provide the majority of 
+    spec-$z$. 
+    By comparing with the Stripe 82 Massive Galaxy Catalog
+    (\texttt{S82-MGC}; \citealt{Bundy2015}), \citet{Leauthaud2016} have measured the
+    \mstar{} completeness of the combined BOSS and SDSS samples. 
+    They estimate that the BOSS spec-$z$ is about 80\% complete at \logms{}$\geq 11.6$ 
+    at $0.3 < z < 0.5$. 
+    The GAMA survey, which partially overlaps with the HSC footprints, supplements 
+    our \texttt{hscZ} sample by 14\%. 
+    Based on \citet{Taylor2011} (e.g.\ their Fig~~6), at $z\sim 0.3$, the GAMA 
+    sample is 80\% complete down to $10^{10.8}$\msun; but only 80\% complete to 
+    $10^{12.0}$\msun at $z\sim 0.5$. 
+    We can therefore expect our sample to be roughly \mstar{}-complete above 
+    \logms{}$\geq 11.5$-$11.6$. 
+    This question will be addressed more carefully using the overlap region between 
+    HSC and the \texttt{S82-MGC} in Section\ref{ssec:s82}.
+
+%% ------------------------------------------------------------------------------------ %%  
+\subsection{\redm{}{} cluster catalog}
+    \label{ssec:redmapper}
+
+    Our study focuses on galaxies which are located at the center of their dark matter 
+    halos. 
+    To limit our sample to central galaxies, we use \texttt{v5.10} of the \redm{}{} 
+    cluster catalog\footnote{See: http://risa.stanford.edu/redmapper/} 
+    (e.g.\ \citealt{Rykoff2014}; \citealt{Rozo2015b}). 
+    These authors have developed a well-tested red-sequence cluster finder that has 
+    been run on SDSS DR8 (\citealt{SDSSDR8}) photometric data. 
+    For each cluster, the catalog provides estimates of photometric redshift 
+    ($z_{\lambda}$) and richness ($\lambda$), and identifies the most likely central
+    galaxy (the galaxy with the highest $P_{\mathrm{Cen}}$ value). 
+    The \redm{}{} catalog also provides a list of member galaxies for each cluster 
+    and associated membership probabilities. 
+    Details about the performance of the \redm{}~cluster catalog can be found in 
+    \citet{Rozo2014}, \citet{Rozo2015a}, and \citet{Rozo2015b}. 
+    Several studies have published calibrations between the \redm{}~richness estimate, 
+    $\lambda$, and halo mass (e.g.\ \citealt{Saro2015}; \citealt{Farahi2016}; 
+    \citealt{Simet2016}). 
+    All these studies consistently found that the \redm{} clusters with $\lambda > 20$ 
+    have $\log (M_{200m}/M_{\odot}) \geq 14.0$.
+    The \redm{} catalog therefore helps us group massive central galaxies into samples 
+    with different average \mhalo{}. 
+    The reliable candidates of central galaxies in the \redm{} clusters 
+    ($P_{\mathrm{CEN}} \geq 0.7$) form a nice sample of massive central galaxies 
+    that live in very massive halos.
+
+    Due to the depth and resolution of the SDSS images, the \redm{} catalog 
+    becomes slightly incomplete at lower richness ($\lambda < 40$) at $z > 0.33$. 
+    In addition to that, the typical uncertainty of $\lambda$ estimate ($\sim 5$-10) 
+    can not be ignored. 
+    To ensure the separation in \mhalo{}, here we only focus on the central galaxies of
+    clusters with $\lambda > 30$. 
+    According to \citet{Simet2016}, this $\lambda \geq 30$ sample should have halo mass
+    ($M_{200m}$) more massive than $10^{14.2} M_{\odot}$. 
+    Also, none of the results in this work depend on the choice of the $\lambda$ 
+    limit.
+    For the massive central galaxies that are not in these cluster-level halos, 
+    we unfortunately can not estimate their \mhalo{} individually, but it is safe 
+    to assume they should have $\log (M_{200m}/M_{\odot}) < 14.0$.
+
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
+  \begin{figure*}
+      \centering 
+      \includegraphics[width=\textwidth]{fig/redbcg_smf_new}
+      \caption{
+          \textbf{Left:} Difference between \mcmodel{} and \mtot{} for central
+      	  galaxies in halos less massive than $10^{14} M_{\odot}$ (grey dots) and 
+      	  in halos more massive than $10^{14} M_{\odot}$ (red squares). 
+          On average, \mcmodel{} underestimates the total stellar mass of massive 
+          galaxies by 0.1 dex while the difference can exceed 0.2 dex in some cases.
+          Vertical histograms indicate the mass difference for galaxies with
+          $11.6<$\logmtot{}$<11.9$. 
+          \textbf{Right:}: Impact of using \mcmodel{} on the galaxy stellar mass
+          function. 
+          Dashed lines correspond to the SMF computed using \mcmodel{} as an estimate
+          of the total luminosity whereas solid lines correspond to the SMF computed
+          using the total luminosity from our 1-D profile. 
+          The impact on the SMF can exceed 0.2 dex for massive central galaxies 
+          living in halos larger than $\log (M_{200m}/M_{\odot}) > 14.2$ (red lines).
+          }
+      \label{fig:smf1}
+  \end{figure*}
+
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
+\subsection{Massive Central Galaxies from Low and High Mass Halos}
+    \label{ssec:mass_central}
+
+    Based on recent constraints of $M_{\star}$-$M_{\mathrm{Halo}}$ relation 
+    (e.g.\ \citealt{Leauthaud2012}, \citealt{Behroozi2013}, \citealt{Kravtsov2014}),
+    the massive galaxies in our sample live in halos that span a wide range of 
+    \mhalo{}.
+    With the help of the \redm{} catalog, we can broadly separate our sample into two
+    groups with \logmh{}$<14.0$ and \logmh{}$>14.2$.
+
+    % We match this sample with the central galaxies of \redm{}~catalogs using a 
+    % $1.0^{\arcsec}$ radius, and it results in 704 galaxies.  
+    %% Saved as "dr1_redbcg_hsc_sdss_gama_1arcsec.fits"
+
+    We match the \texttt{hscZ} sample with the massive central galaxies of 
+    \redm{} clusters with $\lambda \geq 30$ and $P_{\mathrm{0.7}} \geq 0.7$,
+    and find 164 matched galaxies at $0.3 \leq z \leq 0.5$.
+    We will refer these \textbf{central galaxies in more massive halos} as the 
+    \rbcg{} sample here.
+    A small fraction of \redm{} centrals within the HSC footprints is missing  
+    due to severe contamination from optical artifacts or bright stars.
+    The median $\lambda$ of these clusters is $\sim 41$, corresponding to 
+    halo mass of $M_{200m}\sim 2.2\times 10^{14} h^{-1} M_{\odot}$.
+    Among them, only 44 of \rbcg{} sample live in clusters with $\lambda \geq 50$
+    ($M_{200m} \sim 3.0\times 10^{14} h^{-1} M_{\odot}$), so the \rbcg{} sample is 
+    not dominated by extremely massive clusters with \mhalo{}$>10^{15} M_{\odot}$. 
+    %% Saved as "dr1_redbcg_use_sed5b.fits"
+
+    To select massive central galaxies in \logmh{}$<14.0$ halos, we identify and 
+    remove all galaxies within a cylinder region around each of the central galaxy of 
+    all \redm{} clusters.
+    We choose to use the $R_{200m}$ as the radius, and twice the uncertainty of the 
+    photometric redshift error as the thickness of the cylinder. 
+    We convert the $\lambda$ into $M_{200m}$ using the calibration in 
+    \citet{Simet2016}, then estimate the $R_{200m}$ with the help of the 
+    mass-concentration relation in \citet{Diemer2015}. 
+    At $0.3 < z < 0.5$, the uncertainty of photo-$z$ is between 0.015 to 0.025, 
+    and is enough to exclude cluster members.
+    After removing galaxies in \redm{} clusters, the rest of the massive galaxies 
+    in our sample should mainly be the central galaxies of halos with \logmh{}$<14.0$,
+    and we will refer these \textbf{central galaxies in less massive halos} as the 
+    \nbcg{} sample.
+    We should note that the \nbcg{} sample at this stage spans a large range in 
+    \mstar{}, and includes contaminations like massive satellites in \logmh{}$< 14.0$ 
+    halos.  
+    Therefore, after we update the total \mstar{} later, we only focus on the 
+    \nbcg{} galaxies at very high-mass end (e.g.~\logms{}$ > 11.5$). 
+    According to recent observation (e.g. \citealt{vanUitert2016}), we can neglect 
+    satellite contamination at such high \mstar{} range. 
+    %% Saved as "dr1_nonbcg_use_sed5b.fits"
+    % TODO: The actual number waits to be updated}
+
+    % \alexie{This is a rather strange procedure, I think we need to change it 
+    % (referee and readers will complain!). What we really want to do is to remove any
+    % galaxies that have $r<R200$ in projection (from the galaxy with the highest value 
+    % of Pcen) and remove galaxies within some deltaz of the cluster redshift. 
+    % The cluster redshift is more well determined than the redshift estimate of any 
+    % cluster member. 
+    % In short, what we are doing here is cutting out a cylinder around the most likely 
+    % BCG. The deltaz value can be motivated by the cluster redshift uncertainty from 
+    % the redmapper papers. The only remaining question is then what radius to use around
+    % clusters. To get that number here is what we need to do. 
+    % 1) Start with Eq 12 and Table 3 in Simet et al. For each cluster, assign a value 
+    % of M200m (halo mass defined as 200 time background) to each cluster. 
+    % 3) we then need to estimate the cluster radius R200m (or R200b, same thing). 
+    % To do this, we need to use a mass-concentration relation. 
+    % I'm pretty sure there is an easy command to do this in Python using the python 
+    % package "colossus" by bendikt diemer. 
+    % Download it and see if you an get it to work. If it doesn't look obvious after
+    % 30 min, I can do it on my end using my own code. But good for you to know how to 
+    % do this. We can simply use the mass-concentration relation from Benedikts work. 
+    % 4) Now for every cluster you have R200m. And you define the low halo mass central
+    % sample as ones that are not within any cylindar around any cluster. 
+    % Sorry, I know this might mean re-doing everything.....let's discuss by Skype if 
+    % this is a major issue.}
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
+\subsection{Summary of Sample Construction}
+    \label{ssec:sample}
+
+    Using $\sim 100$ deg$^2$ of HSC data, we select a large sample of massive central 
+    galaxies with reliable redshift information, and broadly separate them into two 
+    groups with different \mhalo{}. 
+    The following is a summary of our sample construction.
+
+    \begin{itemize}
+        \item \texttt{hscPho} sample: this parent sample consists of bright galaxies 
+            with $i_{\mathrm{cModel}} \leq 21.0$, good quality images and reliable 
+            \texttt{cModel} photometry in all five HSC bands in the \texttt{S15B} 
+            data release. 
+        \item \texttt{hscZ} sample: through matching the \texttt{hscPho} sample with 
+            spectroscopic redshifts from surveys like SDSS/BOSS and GAMA, or accurate 
+            red-sequence photometric redshift in the \redm{} catalog, we come up with 
+            a large sample of bright galaxies with reliable redshift information. 
+        \item \rbcg{} sample: we select a sample of 164 galaxies at 
+            $0.3 \leq z \leq 0.5$ that are reliably identified as the central galaxies 
+            in $\lambda > 30$ \redm{} clusters. 
+            They represent the central galaxies in very massive halos 
+            (\logmh{}$\geq 14.2$). 
+        \item \nbcg{} sample: after excluding all the galaxies that are close to any 
+            \redm{} clusters in both radial and redshift directions from the 
+            \texttt{hscZ} sample, we have 14661 bright galaxies at 
+            $0.3 \leq z \leq 0.5$.
+            With the help of \mstar{} estimates via SED fitting (see Section 
+            \ref{ssec:isedfit}), we consider the massive ones among them as the 
+            central galaxies in halos with \logmh{}$<14.0$.  
+    \end{itemize}
+
+    We now proceed to measure the luminosities and stellar mass profiles for 
+    all galaxies in the \rbcg{} and \nbcg{} samples.
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
+\section{Measurements of 1-D Surface Brightness Profile}
+    \label{sec:ellipse}
+
+    To estimate the total luminosity of massive galaxies, and measure their 
+    one-dimensional stellar mass density (\mden{}) profiles, we perform elliptical 
+    isophotes fitting using the IRAF \texttt{Ellipse} algorithm (Jedrzejewski 1987).  
+    Compared to the popular two-dimensional model fitting method, the isophote fitting
+    approach is insensitive to the choice of model (e.g. de~Vaucouleurs or \ser{} 
+    profile), the number of components, and the initial guesses of free parameters. 
+    It is also less affected by the background subtraction uncertainty, which is 
+    particularly important for the massive ellipticals in our sample.
+    Massive ETGs imaged at the depth of HSC are not well modeled by simple models such 
+    as the de~Vaucouleurs model or a single \ser component model. 
+    These models will fail to simultaneously capture the profile in both the inner and 
+    the outer region and these models also cannot account for any radial variations in 
+    ellipticity and position angle. 
+    In principle, massive galaxies can still be described by more complex 
+    models (e.g \citealt{Huang2013a}; \citealt{Huang2013b}), but they are still 
+    sensitive to background subtraction and initial values of parameters. 
+    For this paper, we opt to for the model-independent 1-D approach and we will only 
+    study galaxies in the radial range where we are not sensitive to either the PSF 
+    ($r<3-5$ kpc) or the background subtraction ($r>100$ kpc).
+
+    We prepare large $i$-band cut-out images for each galaxy in our sample that extend 
+    to at least 750 kpc in radius, along with the bad pixel mask, and the PSF model 
+    reconstructed at the central coordinate. 
+    These cut-outs include all visible light of the galaxy while leaving enough space 
+    to evaluate the background level. 
+    We choose to use $i$-band images because they trace the stellar distributions of 
+    massive galaxies at $0.3 \leq z \leq 0.5$ reasonably well 
+    (the observed i-band corresponds to a rest-frame $g$ or $r$ band), but also 
+    because they have better seeing and much lower background level than the images 
+    in $z$ and Y bands that are supposed to be better tracers of \mden{}.
+
+    For each cut-out, to avoid the ``over-deblending'' issue within the 
+    \texttt{hscPipe}, we use customized procedures to detect and appropriately mask 
+    out all objects around the massive galaxies.
+    Meanwhile, the \texttt{hscPipe} tends to over-subtract background around bright
+    objects, including some of the massive galaxies in our sample. 
+    After aggressively masking out all objects (including the central massive 
+    galaxy), we derive an empirical background correction with the help from 
+    \texttt{SExtractor}.
+    Then, we run \texttt{Ellipse} on the background-corrected, masked cut-outs 
+    following the methodology in \citep{Li2012}. 
+    In short, we start with free centroid and shape (ellipticity and position angle) 
+    for each isophote, then fix the best-estimated centroid and estimate the mean 
+    ellipticity and position angles of all isophotes.  
+    Finally, we extract a 1-D surface brightness profile along the major axis using 
+    the mean ellipticity and position angle. 
+    We correct these surface brightness profiles for Galactic extinction and 
+    cosmological dimming, then integrate them to various radius to get the 
+    luminosity within different physical apertures. 
+    Fig~\ref{fig:ellipse} shows an example of the 1-D surface brightness and 
+    ellipticity profile for a massive galaxy at $z\sim0.2$ together with the 
+    colored image and a subset of isophotes.
+
+    After testing the above procedure with different mask sizes, different 
+    \texttt{Ellipse} parameters, and with or without background correction, 
+    we find that the 1-D surface brightness profile is reliable above 
+    $>28.5$ \sb. 
+    Beyond that, some of the profiles begin to show unphysical behaviors 
+    (truncation or large fluctuations) due to uncertainties from background subtraction. 
+    This conservative choice already enables us to measure the individual surface 
+    brightness profile out to $100$ kpc. 
+    For more details about the technical details of the \texttt{Ellipse} run, please 
+    see Appendix~\ref{app:ellipse}.
+
+    For physical (e.g.\ late-stage major merger) and unphysical (e.g.\ nearby foreground 
+    galaxy or bright star) reasons, we can not extract reliable 1-D profiles for a small 
+    fraction of massive galaxies because they are heavily masked out. 
+    This is an intrinsic limitation of the 1-D method. 
+    It affects $18/164$ of the \rbcg{} galaxies, and a smaller fraction of the \nbcg{} 
+    ones. 
+    It is worth noting that this excludes most major-merging massive galaxies. 
+    We will come back to them in the future using 2-D modeling method.
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
+\section{Stellar Masses and Stellar Mass Density Profiles}
+    \label{sec:mstar}
+
+%% ------------------------------------------------------------------------------------ %% 
+\subsection{Stellar Masses from SED Fitting}
+    \label{ssec:isedfit}
+
+    To convert luminosities into stellar mass, we assume that these massive galaxies 
+    can be well described by an average \m2l{}. 
+    This is a reasonable assumption considering that they are mostly dominated by 
+    old stellar populations and are known to have shallow color gradients. 
+    We will further justify this point by measuring their average color profiles in 
+    Section \ref{ssec:ell_color}.
+
+    We use the broadband Spectral Energy Distributions (SEDs) fitting 
+    (see \citealt{Walcher2011} for a recent review) code 
+    \texttt{iSEDFit}\footnote{http://www.sos.siena.edu/~jmoustakas/isedfit/} 
+    (\citealt{Moustakas13}) to estimate the average \m2l{} and $k$-corrections using
+    5-band HSC \cmodel{} fluxes. 
+    Although \cmodel{} tends to underestimate the total flux for bright, extended 
+    objects, it can still yield accurate \emph{average} color thanks to the 
+    forced-photometry method that takes the PSF convolution into account
+    (e.g. \citealt{SynPipeInPrep}).
+
+    \texttt{iSEDFit} takes a simplified Bayesian approach. 
+    In short, it first generates a large grid of SEDs from synthetic stellar population 
+    models by drawing randomly from the prior distributions of relevant parameters 
+    (e.g.\ age, metallicity, dust extinction, and star formation history).
+    Based on these models, it uses the observed photometry and redshift to compute the 
+    statistical likelihood, and generates the posterior probability distribution 
+    functions (PDF) for each parameter.  
+    To get the best estimate of a given parameter, \texttt{iSEDFit} ``integrates'' the 
+    full PDF over all the other ``nuisance'' parameters.
+    Then, the median value and the 1-$\sigma$ uncertainty are derived based on the 
+    marginalized PDF. 
+    Please refer to \citet{Moustakas13} for technical details.
+
+    In this work, we derive average \m2l{} using the Flexible Stellar Population 
+    Synthesis\footnote{http://scholar.harvard.edu/cconroy/sps-models}
+    (FSPS; \texttt{v2.4}; \citealt{FSPS}, \citealt{Conroy2010}) model based on the MILES
+    \footnote{http://www.iac.es/proyecto/miles/pages/stellar-libraries/miles-library.php}
+    (\citealt{MILES1}, \citealt{MILES2}) stellar library and assuming a
+    \citet{Chabrier2003} IMF between 0.1 to 100 \msun. 
+    The star formation history (SFH) is assumed to follow a delayed-$\tau$ model with 
+    stochastic star bursts (see Appendix~\ref{app:sed}). 
+    This SFH is appropriate for massive galaxies at low redshifts 
+    (e.g.\ \citealt{Kauffmann2003}). 
+    For stellar metallicity, we assume a flat distribution between 0.004 to 0.03 
+    (the highest value allowed by FSPS). 
+    We adopt the \citet{Calzetti2000} extinction law with a order two Gamma distribution 
+    of $A_{V}$ between 0 to 2 magnitude. 
+    A majority of our galaxies are red and quiescent and our results are 
+    not very sensitive to parameters related to the SFH or the internal dust extinction. 
+    To achieve reasonable sampling across these parameters, we generate 250000 models.
+
+    We construct five band SEDs using the forced-photometry \cmodel{} magnitudes 
+    corrected for Galactic extinction. 
+    \cmodel{} only accounts for the statistical error on the flux measurement but does
+    not account for systematic uncertainties in the model-fitting process. 
+    It therefore underestimates the flux errors of bright galaxies. 
+    Based on tests using synthetic objects, we find that the average accuracy of
+    \cmodel{} for bright galaxy is roughly at the 1\% level in the $r$, $i$, $z$ bands, 
+    and slightly worse in the $g$ and Y-band. 
+    Therefore, we supply \texttt{iSEDFit} with simplified flux errors assuming 
+    $S/N = 100$ for the $riz$ bands, and $S/N = 80$ for the $g$Y bands (on average, 
+    images in $gY$ bands are shallower in depth and/or have higher background noise).  
+    The typical uncertainty of \logms{} is around 0.08-0.10 dex at \logms$\sim 11.5$. 
+    Please see Appendix~\ref{app:sed} for more detailed discussions of the SED fitting
+    results.  
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
+  \begin{figure*}
+      \centering 
+      \includegraphics[width=\textwidth]{fig/average_mass_profiles_fsps1_A}
+      \caption{
+          \textbf{Left}: Median \mden{} profiles of galaxies in different \mtot{} bins:
+      	  [11.4, 11.6] (short-dashed line), [11.6, 11.8] (solid line), and 
+      	  [11.8, 12.0] (long-dashed line). 
+      	  Here we combine the \rbcg{} and \nbcg{} samples, and we also show a random 
+      	  subset of individual profiles in the background.
+      	  The shaded region highlights the region that could be affected by PSF.
+          Two vertical lines label the radius of 10 kpc (thin, dotted line) and
+          100 kpc (thick, dash line). ~~~ 
+          \textbf{Right}: comparison between the average \mden{} profiles with the ones 
+          from previous observations and simulations, including: 
+          1) average profile of massive elliptical galaxies at $z\sim 0$ from 
+          \citet[][Cyan, solid]{Huang2013a}; 
+          2) average profile of massive galaxies at $0.25 \leq z < 0.50$ observed by 
+          \textit{HST} from \citet[][Red, long-dashed]{Patel2013} ;
+          3) average radial stellar distributions in massive halos using simulation and 
+          particle tagging method (\citealt{Cooper13}; Purple, short-dashed).
+          }
+      \label{fig:avg_prof}
+  \end{figure*}
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
+  \begin{figure*}
+      \centering 
+      \includegraphics[width=\textwidth]{fig/redbcg_prof_1}
+      \caption{
+          Comparison of the \mden{} profiles for \mtot{}-matched 
+          ($11.6<$\logmtot{}$<11.9$) and \minn{}-matched ($11.2<$\logminn{}$<11.6$) 
+          samples of \rbcg{} (orange to red) and \nbcg{} (grey to black) galaxies.~~
+          \textbf{Left} shows the results for the \mtot{}-matched samples.
+          For details of the matching process, please see Appendix~\ref{app:match}.  
+          On its upper panel, we show the \mden{} profile of each galaxy using very light 
+          color in the background.  
+          We highlight the median profile and its corresponding uncertainties using thick 
+          solid line with darker color and shaded region. 
+          Other formats are the same with Fig~\ref{fig:avg_prof}.
+          Meanwhile, we highlight the difference between the median profiles and its 
+          uncertainty on the bottom panel (brown solid line and shaded region).
+          To test the significance of the differential profile, we perform statistical
+          tests by comparing the median profiles of two random groups that are drawn 
+          from the mixed sample, and have the same sizes with the matched \rbcg{} and
+          \nbcg{} ones.
+          Repeating this process many times, the median of these random differential 
+          profiles (black solid line), the 1-$\sigma$ (dark-grey shaded region) and 
+          3-$\sigma$ (light-grey shaded region) uncertainties are shown on the bottom 
+          panel as well. 
+          A darker vertical dash-line highlights the 100 kpc radius.~~
+          \textbf{Right} shows the results for the \minn{}-matched samples. 
+          The format is exactly the same with the left one, except that the darker 
+          vertical dash-line now highlights the 10 kpc radius.
+          }
+      \label{fig:prof_1} 
+  \end{figure*}
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %%        
+    \subsection{Stellar Mass Completeness}
+    \label{ssec:complete}
+
+    With the help of the \texttt{S82-MGC} sample, we briefly discuss the \mstar{} 
+    completeness of this sample. 
+    The \texttt{S82-MGC} sample matches the deeper SDSS photometric data in the 
+    Stripe 82 region (\citealt{Annis2014}) with the near infrared data from the United 
+    Kingdom Infrared Telescope Infrared Deep Sky Survey (UKIDSS; \citealt{Lawrence2007}). 
+    The deeper photometry and better photo-$z$ make the \texttt{S82-MGC} sample complete 
+    to \logms{}$\geq 11.2$ at $z<0.7$ which makes it sufficient to evaluate the 
+    completeness of this sample.
+    There are 20453 \texttt{S82-MGC} galaxies that are also in the \texttt{hscPho} 
+    sample at $0.3 \leq z_{\mathrm{s82}} \leq 0.5$ (referred as \texttt{s82Pho} sample).   
+    We estimate their \mstar{} using the HSC \texttt{cModel} SED in exactly the 
+    same way\footnote{The \mstar{} using HSC photometry shows tight correlation with the 
+    ones based on the \texttt{S82-MGC} SED which includes NIR data from UKIDSS; 
+    \texttt{S82-MGC} also uses \texttt{iSEDFit} with similar assumptions}.  
+    Then we estimate the volume density distributions of the galaxies in \rbcg{}, 
+    \nbcg{}, and \texttt{s82Pho} samples (right panel of Fig~\ref{fig:smf1}) using 
+    rough estimates of the survey areas they occupied \footnote{We estimate the 
+    uncertainties of these distributions via bootstrap resampling}.
+    By comparing the relative shapes of these distributions, we conclude that 
+    our sample of massive galaxies is reasonably complete down to \logms{}$\sim 11.6$
+    at $0.3 \leq z \leq 0.5$. 
+    While the \rbcg{} sample is less affected by completeness thanks to the reliable
+    photo-$z$ from \redm{}, the completeness of the \nbcg{} sample is still limited 
+    by the spec-$z$ samples.
+    Although there is no apparent reason that the incompleteness can bias our 
+    comparison of structure, we will mainly focus on the \rbcg{} and \nbcg{} galaxies 
+    with $11.6 \le$\logmtot{}$\le 11.9$ where their mass distributions overlap the 
+    most and both have good \mstar{} completeness, and will also match the two samples 
+    carefully in \logms{} and redshift distributions.
+    Please see the next section and Appendix~\ref{app:match} for more details.
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
+\subsection{Stellar Mass Corrected for Total Luminosity}
+    \label{ssec:mtotal}
+
+    Using the best-fit stellar mass from \texttt{iSEDFit} (referred as \mcmodel{}), 
+    we estimate the average \m2l{} in $i$-band, then use that \m2l{} to convert the 
+    1-D luminosity density profiles into stellar mass density profiles; and 
+    also convert the luminosity within 10 and 100 kpc apertures into 
+    corresponding stellar mass estimates (referred as \minn{} and \mtot{}). 
+    From now, we use \mtot{} as the new proxy of ``total'' stellar mass of these 
+    galaxies.  
+    And we also derive the $k$-corrected luminosity and colors from the results.
+    In Appendix~\ref{app:sedasic}, we briefly summarize the basic statistics of 
+    the \rbcg{} and \nbcg{} samples using the newly derived \mtot{} and \minn{}.
+    We can confirm that both samples follow a similar and very tight ``red-sequence''.
+    We also show the outputs from SED fitting process like the average stellar age, 
+    metallicity, and internal dust extinction in Appendix~\ref{app:sed}.
+    Although we do not rely them on scientific analysis, they all behave reasonably for 
+    both samples. 
+    As expected, the integration of 1-D profile out to very large radius help 
+    recover more luminosity (stellar mass) compared to the \cmodel{} results. 
+    We shown in Section \ref{ssec:s82}.
+
+    As mentioned earlier, our assumption of using an average \m2l{} ignores its
+    radial variation.   
+    It is well known that massive ETGs have negative optical color gradient which 
+    indicates a gradient of \m2l{} (e.g.\ \citealt{LaBarbera2012}; 
+    \citealt{DSouza2015}), but the gradient is shallow and smooth out to a few 
+    times of the effective radius (color gradient at the very outskirt is still 
+    not well quantified). 
+    More importantly, for the comparison between the \rbcg{} and \nbcg{} samples, 
+    our results should remain intact as long as there is no significant
+    differences of average color gradient between these two samples.
+    This is confirmed by our initial results on color gradient, and we will 
+    discuss this more in Section \ref{ssec:ell_color}.
+    Therefore the average \m2l{} approach should work reasonably well for our goals.
+
+    This approach to derive total stellar mass is actually quite similar to the 
+    method adopted by the GAMA survey (\citealt{Taylor2011}).
+    They start with \mstar{} estimated using average \m2l{} from SED fitting 
+    results of PSF-matched aperture photometry, and later correct it with better 
+    estimate of total luminosity from single-\ser model fitting
+    (\citealt{Kelvin2012}). 
+    For galaxies in common with the GAMA survey, we also compare their different 
+    estimates of \mstar{} (\mgama{} v.s. \mtot{}) in Appendix~\ref{app:gama},  
+    and notice systematic differences between the two \mstar{} estimates.
+    It is likely that the GAMA models still miss fluxes in the stellar halo that 
+    is beyond the depth of SDSS image. 
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
 \section{Results}
+    \label{sec:result}
 
+%% ------------------------------------------------------------------------------------ %%     
+    \subsection{Impact of Photometry on Stellar Mass and Stellar Mass Function}
+    \label{ssec:s82}
+
+    As mentioned above, different methods lead to different estimates of ``total'' 
+    \mstar{} and impacts important statistics like the stellar mass function 
+    (e.g. \citealt{Bernardi2013, DSouza2014, DSouza2015, Bernardi2016a}).
+    We highlight this in the left panel of Fig~\ref{fig:smf1} by plotting 
+    the \mtot{} from 1-D analysis with the differences between \mtot{} and \mcmodel{}.
+    Apparently, our careful 1-D approach recovers more flux in massive galaxies 
+    than the \texttt{cModel} method. 
+    More importantly, the average difference steadily increases with \mtot{}. 
+    At \logms$>11.5$, the difference is often larger than 0.2 dex.  
+    This difference relates to the intrinsic limitation of the \texttt{cModel} 
+    method and also reflects the fact that more massive ETGs tend to have more 
+    extended stellar mass distributions (e.g. \citealt{Graham2003}).
+
+    Such mass-dependent difference will clearly result in difference of the SMF, 
+    especially at the very high-mass end where the slope is quite uncertain under
+    current constraints (e.g. \citealt{Bernardi2016}).
+    Although the careful evaluation of the SMF is beyond the scope of this work, 
+    we still highlight the impacts of different definitions of ``total \mstar{}''
+    on the volume density distributions of both samples (Fig~\ref{fig:smf1}, 
+    right panel).  
+    Generally speaking, the use of \mtot{} from 1-D analysis instead of the
+    \mcmodel{} shifts the distributions toward the higher-mass end, and slightly 
+    modifies the slope.
+    This impact is more obvious for the \rbcg{} samples.
+    For studies about the SMF or other aspects of galaxy evolution based on 
+    \cmodel{}-like photometry or shallower images, these impacts should be 
+    taken into consideration.
+
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %%
+\subsection{Surface Mass Density Profiles}
+    \label{ssec:sbp_compare}
+
+%% ------------------------------------------------------------------------------------ %%
+\subsubsection{Mass Dependence of \mden{} Profiles}
+    \label{sssec:sbp_inter}
+
+    Comparing to the much discussed scaling relation like the mass-size relation, 
+    the \mden{} profiles contain more structural details that can help us diagnose the 
+    roles of different physical processes, including the environmental effect.  
+    We first mix the \rbcg{} and \nbcg{} together, and show how the average \mden{}
+    profiles of massive galaxies at $0.3 < z < 0.5$ depend on stellar mass using their 
+    median \mden{} profiles\footnote{The median profiles along with their uncertainties 
+    using bootstrap resampling method} in three \mtot{} bins \footnote{Here we ignore a 
+    small population of massive satellite in \redm{} clusters we excluded from our 
+    sample.
+    The sample is clearly not complete in the lowest \mtot{} bin, but its median \mden{}
+    profile is still useful to show the overall trend and to compare with previous 
+    observations}.
+
+    As shown in the left panel of Fig~\ref{fig:avg_prof}, we can comfortably trace 
+    the \mden{} profiles of these massive galaxies out to 100 kpc \textbf{individually}, 
+    which greatly help us study the statistical properties of their outer envelopes. 
+    These median \mden{} profiles have very moderate differences in the inner region, 
+    but show significant differences in the outskirts as more massive galaxies have 
+    much more prominent stellar envelopes.
+    Most of these massive galaxies ($\ge 10^{11.4} M_{\odot}$) are slow-rotating 
+    (e.g.\ \citealt{Cappellari13b}) giant ellipticals with ``boxy'' inner isophotal 
+    shape (e.g.\ \citealt{Kormendy2009}), and slightly flattened \mden{} profile close 
+    to the center (e.g.\ \citealt{Lauer07}).
+    But their structures in the outskirt clearly do \textbf{NOT} response to the 
+    increase of stellar mass in a self-similar way.
+
+    The \mden{} profile of massive galaxy out to such large radius was only available 
+    through image stacking technique (e.g. \citealt{Tal2011, DSouza2015})
+    that suffers from several systematic issues.
+    Although most \mden{} profiles extend beyond 100 kpc, many of them show signs of 
+    unphysical truncation and fluctuation related to inaccurate sky subtraction.  
+    Therefore, we exclude the profiles outside 100 kpc, even though the median \mden{} 
+    profiles for the two more massive bins behave reasonably out to $\sim 200$ kpc.
+
+    In the right panel of Fig~\ref{fig:avg_prof}, we compare these median profiles with 
+    a few past works.  
+    \citep{Huang2013a}, derived the median \mden{} profile for a small sample of very 
+    nearby ellipticals (within 100 Mpc; median \logms{}$\sim 11.3$ based on shallower 
+    images) from the Carnegie-Irvine Galaxy Survey (CGS, \citealt{CGS1}) that are not 
+    affected by seeing until $r < 1$ kpc.
+    This median \mden{} profile qualitatively agrees with the one for the lowest 
+    \mtot{} bin in the inner region, but shows a slightly more prominent outer 
+    envelope at $r > 15$ kpc. 
+    While the small sample size of the CGS sample ($\sim 30$) and differences in the
+    measurements of \mstar{} could explain this difference, it is also interestingly 
+    consistent with mild mass assembly from $z\sim 0.4$ to $z=0$ in the outskirt.   
+    The CGS images are already deeper than SDSS images in $r$-band, but the median 
+    profile still only reaches to $\sim 50$ kpc for $z\sim 0$ massive galaxies.
+    Meanwhile, the deep HSC images can reliably deliver individual \mden{} profiles 
+    for $z\sim 0.4$ galaxy out to at least 100 kpc.
+
+    \citet{Patel2013} extracted the median \mden{} profile of massive ETGs at 
+    $0.25 < z < 0.50$ using the stacked \textit{HST}/ACS images. 
+    These galaxies are selected at a constant cumulative number density that makes them  
+    good candidates of progenitors of $z=0$ massive ETGs.  
+    The median \mstar{} is $\sim 10^{11.2} M_{\odot}$ according to their estimates.  
+    However, once the differences in imaging depth and assumptions in SED fitting method
+    are considered, it is reasonable to assume they are comparable to our galaxies in 
+    the lowest \mtot{} bin, and the comparison of \mden{} profiles does confirm that.
+    Moreover, the superb resolution of the \textit{HST}/ACS image makes the \mden{} 
+    profile unaffected by PSF even within inner 1 kpc.
+    Therefore, the comparison illustrates that the HSC profiles within our redshift
+    range are indeed not bothered by seeing at $r > 3$ kpc, which also ensure the
+    accuracy of the \minn{} estimates.
+
+    We also compare with the predicted average \mden{} profile of central galaxies in 
+    massive halos ($13.5 < \log M_{200,c} < 14.0$) from cosmological simulation
+    (\citealt{Cooper13}) using the particle-tagging technique (\citealt{Cooper10}).
+    Despite the poorer resolution, its \mden{} profile is already quite similar to 
+    the median \mden{} profile for the $11.6 <$\logmtot{}$< 11.8$ bin within 40 kpc. 
+    However, comparing with observation, this simulation predicts stellar envelope that
+    is too prominent at this halo mass.
+    Result like this demonstrates that comparisons between observations and simulations
+    using \mden{} profiles have the potential to not only help us make simulation
+    more realistic, but also help us investigate the physical causes of the observed
+    \mstar{} and environmental dependences of structures.
+
+    We summarize these median profiles in Fig~\ref{fig:avg_prof} in Table.~1,
+    and all the above median profiles are available  
+    \href{https://github.com/dr-guangtou/hsc_cenHighMh/tree/master/profiles}{here}.
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
+\subsubsection{Environmental Dependence of the \mden{} Profiles}
+    \label{sssec:sbp_mtot}
+
+    Finally, we will look into the environmental dependence of structures in massive 
+    galaxies using the \mden{} profiles of the \rbcg{} and \nbcg{} samples that are 
+    carefully matched in \mstar{} and redshift using KDTree algorithm. 
+    We discuss the details and quality of the matching procedure in 
+    Appendix~\ref{app:match} (see Fig~\ref{fig:match}. 
+    The matched redshift distributions within $0.3 < z < 0.5$ ensures the \mden{} 
+    profiles from both samples are impacted by seeing and background at similar level. 
+    As for the \mstar{}, we choose to match using two physically meaning definitions.
+
+    \begin{itemize}
+        \item \mtot{} as the proxy of the ``total'' \mstar{} that include the stellar 
+            envelope.  As mentioned earlier, we match the two samples within 
+            $11.6 < $\logmtot{}$<11.9$ (median \logmtot{}$\sim 11.74$).
+            For the 45 \rbcg{} galaxies, we have 229 unique \nbcg{} galaxies in the 
+            matched sample.
+            Within this \mtot{} range, 100 kpc equals to 5-8 times of the effective 
+            radius, so should enclose most their \mstar{}. 
+            In practice, this choice also reflects the radius range that we can safely 
+            measure \mden{} profile given the depth of the image and the accuracy of 
+            background subtraction.
+
+        \item \minn{} as the proxy of the \mstar{} of the ``in-situ'' component.
+            This is motivated and supported by recent observations and simulations, 
+            and we will discuss more about this assumption in 
+            Section~\ref{sec:discussion}.
+            We match the two samples within $11.2 < $\logminn{}$ < 11.6$ 
+            (median \logminn{}$\sim 11.36$).
+            For 56 galaxies in this \rbcg{} sample, we achieve excellent matches
+            using 375 \nbcg{} galaxies.
+    \end{itemize}
+
+    We show the comparison of the \mtot{}-matched (\minn{}-matched) samples in the 
+    left (right) panel of Fig~\ref{fig:prof_1}.
+
+    For the \mtot{}-matched comparison, it is easy to see that the \mden{}
+    profiles of \rbcg{} and \nbcg{} galaxies \textbf{greatly overlap with each 
+    other over the entire radius range}, which partially explains the difficulties in 
+    confirming any environmental dependence of structure in earlier works.
+    Although the central galaxies from more massive halos do not form a unique 
+    population in term of their structures comparing with the ones in less massive
+    halos at similar \mtot{}, we can still spot interesting differences in their 
+    median profiles: the \rbcg{} galaxy on average has slightly more flattened inner 
+    profile and more significant outer stellar envelope than the \nbcg{} one.
+    We highlight these subtle differences in the bottom panel using the difference 
+    between the two median profiles and its uncertainty. 
+    Given the noticeable uncertainties of \mtot{} and $\lambda$, along with the 
+    small size of the current \rbcg{} sample, we perform statistical test to confirm 
+    the robustness of the result \footnote{We mix the $N_{\mathrm{r}}$ \rbcg{} 
+    galaxies and the $N_{\mathrm{n}}$ \mtot{}-matched \nbcg{} ones together, then 
+    randomly draw $N_{\mathrm{r}}$ galaxies with putting-back, compute the difference 
+    between the median profile of this sample and the \nbcg{} sample. 
+    After repeating this process 2000 times, we can evaluate the possibility that 
+    the systematic differences in median \mden{} profiles can be reproduced by random 
+    selection of massive galaxies.}
+    In both inner and outer regions, we conclude the systematic differences in 
+    median \mden{} profiles are significant and robust.
+    Interestingly, the median profiles for \rbcg{} and \nbcg{} cross each other 
+    at $\sim 15$-20 kpc, quite close to the expected $R_{\mathrm{e}}$ for ETGs 
+    this massive. 
+    In Appendix~\ref{app:robust}, we further prove the robustness of this 
+    interesting result by showing that it is not affected by the range of redshift,
+    range of richness, and the choice of proxy for ``total'' \mstar{} 
+    (see Fig~\ref{fig:prof_3}). 
+    We also explore the possible \mtot{}-dependence of this structural difference 
+    despite the limitation of \mstar{}-completeness and small sample size
+    (see Fig~\ref{fig:prof_2}) in Appendix~\ref{app:robust}.
+    Although the systematic differences are very similar in different \mtot{} bins, 
+    we do find some hints that suggest the environmental dependence becomes more 
+    significant at the more massive end.  
+    This evidence could have intriguing implication in the assembly history of 
+    massive galaxies, and is worth more investigations with larger and more completed 
+    sample later.
+
+    \textbf{All these tests confirm that we robustly detect subtle, but systematic 
+    \mhalo{}-dependence (environmental dependence) of structure in massive, 
+    central galaxies} that seems to be consistent with the expectation of more frequent 
+    (minor) mergers in denser environment. 
+    These minor, non-dissipative mergers do not alter the inner \mden{} profiles 
+    a lot, but are efficient in depositing stellar mass onto the outer envelope
+    (e.g. \citealt{Hilz2013}, \citealt{Oogi2013}).
+
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
+    Meanwhile, the subtlety of this environmental dependence for \mtot{}-matched 
+    samples seems to suggest that environment plays a secondary role in shaping 
+    the structure of galaxies at fixed total stellar mass, and it encourages us to find
+    another interesting angle.  
+    For instance, for massive galaxies that formed similar amount of stars through 
+    intensive star formation at high redshift, how the environments affect their mass 
+    assembly history in the second phase? 
+    We attempt to investigate this question through comparing the \mden{} profiles of 
+    the \minn{}-matched \rbcg{} and \nbcg{} galaxies (right side of 
+    Fig~\ref{fig:prof_1}).
+    Assuming we are now comparing the average structures of massive galaxies that share 
+    similar \mstar{} in the ``in-situ'' component, we start to see the environmental 
+    dependence much more clearly without any statistical test.     
+    The median \mden{} profiles of \rbcg{} and \nbcg{} galaxies are quite similar in 
+    the inner 5-10 kpc, but the \rbcg{} galaxies clearly show much more prominent
+    outer envelope.
+
+    It is also worth noting that \mden{} profiles of massive galaxies have quite uniform
+    slope and small scatter inside 10 kpc.  
+    In contrast, their outer profiles could have a large range of slopes and much 
+    larger scatters than the inner region. 
+    It seems to suggest that the inner and outer parts of massive galaxies are shaped 
+    by distinctive physical processes, and are affected by their environment at 
+    very different level. 
+    Given the highly dissipative nature of the ``in-situ'' phase, the similarity of 
+    inner profiles is consistent with the idea that processes like wet-merger and 
+    star burst often create de~Vaucouleur-like ($n\sim 4$) \mden{} profile
+    (e.g. \citealt{Hopkins2008}).
+    At the same time, the outer envelope of massive galaxies are predicted to be 
+    gradually assembled by non-dissipative mergers, which is a stochastic process and 
+    is more affected by the environment.  
+    Therefore, it is natural to see larger diversity in the outer profiles of 
+    low-$z$ massive galaxies. 
+    On average, massive galaxies in more massive halos show shallower outer \mden{} 
+    profiles, which is in qualitative agreement with recent simulation
+    (e.g. \citealt{Pillepich2014}).
+    We illustrate this interesting diversity in Fig~\ref{fig:m100_m10_color}, where 
+    we show the 3-color images of randomly selected massive central galaxies that 
+    have similar \minn{} ($11.1 \leq \log (M_{\star,\ 10\mathrm{kpc}}/M_{\odot}) < 11.2$)
+    but different \mtot{}.   
+    From the top-left to the bottom-right, the \mtot{} of these galaxies increases
+    from $10^{11.22} M_{\odot}$ to $10^{11.75} M_{\odot}$.
+
+    As with the \mtot{}-matched sample, the results are very robust against 
+    sample details, definition of ``inner'' \mstar{} and the \minn{} bins. 
+    In Appendix~\ref{app:match}, we also show that:
+    1) When we match using both \minn{} and \meff{}, we end up with \rbcg{} and \nbcg{} 
+    samples with perfectly matched inner median \mden{} profiles, while the different 
+    in the outskirt remains the same (see the left figure of Fig~\ref{fig:prof_4}).  
+    2) Also, the results will not change even when only a more \mstar{}-complete sample
+    (\logmtot{}$> 11.5$) is considered (see the right figure of Fig~\ref{fig:prof_4}).
+
+    The median profiles shown in Fig~\ref{fig:prof_1} are available in Table.1.
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
+\subsection{Ellipticity and Color Profiles}
+    \label{ssec:ell_color}
+
+%% ------------------------------------------------------------------------------------ %% 
+  \begin{figure*}
+      \centering 
+      \includegraphics[width=\textwidth]{fig/redbcg_discussion_2}
+      \caption{
+          Comparisons of the radial profiles of ellipticity and optical colors 
+      	  for \mtot{}-matched (\textbf{left figure}) and \minn{}-matched 
+      	  (\textbf{right figure}) of \rbcg{} (orange-red) and \nbcg{} (grey-black) samples. 
+          The formats are very similar to the figure for \mden{} profile 
+          (e.g. right figure of Fig~\ref{fig:prof_1}). 
+          On each side, from top to bottom, we show the elliptical profile, and the 
+          color profile using $g-r$ and $g-i$ color. 
+          Since the individual profile of these properties has very large uncertain in the 
+          outskirt, we block the region at large radii where we think the median profiles 
+          are still unreliable using a dark, shaded box.
+          We also compare these results with previous results based on SDSS images. 
+          They are: 
+          1) Ellipticity profile of the stacked image of a large sample of red galaxies at 
+          $z\sim 0.4$ from \citet{Tal2011} with PSF correction 
+          (solid blue line on top panel); 
+          2) Ellipticity and $g-r$ color profiles from stacking analysis of nearby massive 
+          galaxies with high concentration index ($C>2.6$) in \citet[][blue dash lines 
+          on the top and middle panels]{DSouza2014}; 
+          3) average $g-r$ and $g-i$ color profiles for a large sample of nearby 
+          elliptical galaxies in \citet[][blue, solid lines on the middle and bottom 
+          panels]{LaBarbera2010}.
+          }
+      \label{fig:ell_color}
+  \end{figure*}
+%% ------------------------------------------------------------------------------------ %%
+
+    Besides the 1-D \mden{} profiles, the radial profiles of isophotal shape and colors 
+    are also useful diagnostic tools to study massive galaxies. 
+    Here, we extract the radial profiles of ellipticity and $k$-corrected optical colors
+    of galaxies in both \mtot{}-matched and \minn{}-matched samples (used in 
+    Fig~\ref{fig:prof_1}) using \texttt{Ellipse}, and compare the average profiles between
+    the \rbcg{} and \nbcg{} samples for two main purposes:
+
+    \begin{enumerate}
+        \item To see whether the ellipticity profile strongly depends on environment, 
+            and to see whether 1-D \mden{} profiles using average isophotal shape is 
+            appropriate for the goal of this work.
+
+        \item To verify that the average color gradient does not strongly depend on 
+            the environment, and is not steep enough to invalid the assumption that   
+            it is reasonable to use average \m2l for comparing massive galaxies. 
+            We extract color profiles by applying the isophotes in $i$-band to images 
+            in other bands in ``forced photometry'' manner.  
+    \end{enumerate}
+
+    Since we do not correct the differences in sky subtraction and seeing across 
+    different bands, we simply ignore the ellipticity and color in the inner-most and 
+    very low surface brightness regions (profiles are useful between 5-50 kpc). 
+    We apply Galactic extinction and $k$-correction to both $g-r$ and $g-i$ color 
+    profiles; the $k$-correction values are also from \texttt{iSEDFit} results.
+    We show the average ellipticity, $g-r$, and $g-i$ color profiles for the 
+    \mtot{}-matched (\minn{}-matched) samples of \rbcg{} and \nbcg{} galaxies on the 
+    left (right) side of \ref{fig:ell_color}, and also compare them with previous 
+    estimates that are based on stacking analysis of SDSS galaxies 
+    (e.g. \citealt{LaBarbera2010, Tal2011, DSouza2014}).
+
+    Firstly, the ellipticity of massive galaxies steadily increase with radius 
+    from $e\le 0.2$ around 5-10 kpc to $e\sim 0.3$ at 40-50 kpc, in consistent with 
+    previous 2-D modeling results \citep{Huang2013a}.  
+    For the \mtot{}-matched samples, their ellipticity profiles are very similar 
+    all the way to 50 kpc (2-3$\times R_{\mathrm{e}}$ for their \mstar{}). 
+    Meanwhile, for the \minn{}-matched samples, the \rbcg{} galaxies have higher 
+    ellipticity than the \nbcg{} ones at $r > 10$ kpc, while their inner ellipticity 
+    profiles are very similar.  
+    This further hints that massive central galaxies in different halos but with 
+    similar ``in-situ'' mass could experience different merging history.
+    And, given he relative low ellipticity value and shallow ellipticity profile, 
+    we conclude that average isophote is appropriate for the structural comparisons 
+    we performed.
+    Previously, people often rely on image stacking method to extract ellipticity 
+    profile out to large radius (e.g. \citealt{Tal2011}, \citealt{DSouza2015}).
+    Comparing with the ellipticity profile directly measured on deep HSC image, 
+    we find that the stacked ellipticity profiles tend to underestimate the 
+    ellipticity in the outskirt. 
+    Since the ellipticity profile contains interesting information of the assembly 
+    history, we think it highlights the advantage of the HSC image in studying 
+    massive galaxies again, and it would be very interesting to compare with 
+    numerical simulations on this.
+
+    % \citet{Tal2011} stacked the SDSS images of a large sample of Luminous Red 
+    % Galaxies (LRGs) at $z\sim 0.4$, and extract the ellipticity profile after 
+    % correcting the PSF convolution effect.   
+    % Its slope is much shallower than the average ones using HSC images, despite the 
+    % two samples are at similar redshift and are quite comparable. 
+    % The poorer seeing condition of SDSS image plus the systematics in the stacking 
+    % process can easily explain this. 
+    % \citet{DSouza2015} performed similar stacking analysis for a large sample of very 
+    % nearby ETGs.  
+    % The ellipticity profile is quite consistent with our average ones within 5-10 
+    % kpc, but become much shallower at outer region.  
+    % The lower average \mstar{} of their sample and/or the uncertainties in the 
+    % stacking analysis may explain this.  
+    % This highlights the advantages of the high-resolution, deep HSC images again,
+    % and it would be very interesting to compare with numerical simulations.
+
+    Secondly, we see shallow and negative gradients of average $g-r$ and $g-i$ color 
+    profiles for both \rbcg{} and \nbcg{} galaxies. 
+    For both \mtot{}- and \minn{}-matched samples, we find no significant difference
+    in their median color profiles, which supports the assumption of using single 
+    average \m2l{} value to estimate \mden{} profiles.
+    The median $g-r$ color profiles are quite consistent with the ones based on 
+    stacked SDSS images. 
+    For $g-i$ profiles, the HSC ones are slightly deeper than the SDSS ones, but we 
+    need to remind you the so-called ``red-halo'' effect of extended PSF wing in 
+    SDSS $i$-band (e.g. \citealt{Wu2005}, \citealt{Tal2011}) that could make the 
+    color appears redder.
+    Thank to the thickness of the CCD, the HSC $i$-band image can help provide more 
+    accurate color estimates as it does not suffer from the ``red-halo'' effect.
+
+    These results suggest that multi-band, 2-D information will help us piece together
+    a more complete view of massive galaxy evolution, but also point out limitations 
+    of the 1-D \mden{} profile analysis. 
+    In the near future, we will come back to this point with the help of 2-D modeling
+    method.
+
+    % On the left of Fig~\ref{fig:ell_color}, we see that the \rbcg{} and \nbcg{} 
+    % samples share very similar color profiles from 5-50 kpc. 
+    % This is very good news for using average \m2l{} in the comparisons of \mden{}
+    % profiles: although the \mden{} profiles may not be perfectly accurate, there 
+    % should be no bias when comparing the average profiles of \rbcg{} and \nbcg{} 
+    % samples.
+
+    % On the right side of Fig~\ref{fig:ell_color}, the situation is very similar 
+    % as the slopes of color gradients are basically the same for two samples; 
+    % although there might be some evidence that, when matched at similar \mstar{} 
+    % of the ``in-situ'' component, the \rbcg{} galaxies tend to have slightly redder
+    % envelopes than the \nbcg{} ones. 
+    % This is worth further investigation, especially via multi-band, 2-D 
+    % decomposition method.
+
+    % Although the 1-D analysis is not perfect, these preliminary results already 
+    % point out the importance and benefits of including multiband, 2-D information 
+    % into account. 
+    % Now we know that, for massive central galaxies with similar \mtot{}, the average 
+    % \mden{} profiles show subtle dependence on halo mass, while the color and 
+    % ellipticity profiles are very stable.  
+    % On the other hands, for central galaxies that have the same \mstar{}, ellipticity 
+    % and color profiles within 10 kpc, their outer envelopes appears to be strongly 
+    % depend on environments.
+
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
+\subsection{Environmental Dependence of Scaling Relations}
+    \label{ssec:scaling}
+
+%% ------------------------------------------------------------------------------------ %% 
+  \begin{figure*}
+      \centering 
+      \includegraphics[width=\textwidth]{fig/redbcg_scaling_relation}
+      \caption{
+          \textbf{Left}: The \mstar{}-size relations for \rbcg{} 
+          (orange squares) and \nbcg{} (grey dots) galaxies. 
+          Here we use the \mtot{} as proxy of total \mstar{}, and use the 
+          $R_{\mathrm{50}}$ derived from the 1-D profile as size estimate. 
+          Two vertical lines highlight the $11.6<$\logms{}$<11.9$ mass bin.
+          We visualize the best-fit \mstar{}-$R_{\mathrm{50}}$ relations of \rbcg{} 
+          (red, solid line) and \nbcg{} (grey, dash line) galaxies at high-\mstar{} end.
+          The shaded regions in lighter colors show the 1-$\sigma$ uncertainties
+          from MCMC sampling. 
+          We also compare with the \mstar{}-$R_{\mathrm{50}}$ relation for nearby central 
+          galaxies in massive groups from \citet{HCompany13} (green, long dashed line). 
+          Please refer to the text for more details.~
+          \textbf{Right:} The relations between \mtot{} and \minn{} for the 
+          \rbcg{} and \nbcg{} galaxies, along with the best-fit scaling relations for 
+          both samples.  The format is the same with the left one.
+          }
+      \label{fig:scaling_relation} 
+  \end{figure*}
+%% ------------------------------------------------------------------------------------ %%
+
+\subsubsection{Mass-Size relation}
+    \label{sssec:mass_size}
+
+    Despite being the focus of previous investigations (e.g. \citealt{Shankar2013};
+    \citealt{Leja2013}, \citealt{vdWel2014}), the relation between \mstar{} and 
+    effective radius (or half-light radius; $R_{\mathrm{e}}$ or $R_{\mathrm{50}}$) 
+    has yet to provide clear evidence of environmental dependence of structures of 
+    massive galaxies at low-$z$ (e.g. \citealt{Weinmann2009}, \citealt{Nair2010}, 
+    \citealt{HCompany13}, \citealt{Cerbrian2014}), and sent controversial messages 
+    about the pictures at high-$z$ (e.g. \citealt{MCooper2012}, \citealt{Papovich2012}, 
+    \citealt{Kelkar2015}).
+    Now, according to the previous comparisons of \mden{} profiles, the deep HSC images 
+    also promise evidence of the environmental dependence of mass-size relation 
+    (see the left panel of Fig~\ref{fig:scaling_relation}).
+
+    We use the \mtot{} as the proxy of ``total'' \mstar{}, and the radius that encloses 
+    50\% of luminosity within 100 kpc ($R_{\mathrm{50}}$; derived from $i$-band 
+    curve-of-growth) as the ``size'' to evaluate the relation.
+    This definition of ``effective radius'' is more robust against structural details, 
+    choice of model, and the background subtraction.   
+    Our massive galaxies are also big enough so we do not need to worry about seeing
+    correction.
+
+    On the left of Fig~\ref{fig:scaling_relation}, we see clear \mstar{}-size relations 
+    for both samples.  
+    At fixed \mtot{}, the distributions of $R_{\mathrm{50}}$ for the \rbcg{} and
+    \nbcg{} galaxies greatly overlap, but it seems that the \rbcg{} galaxies do have 
+    systematically higher $R_{\mathrm{50}}$. 
+    % For the \mtot{}-matched samples used in Fig~\ref{fig:prof_1}, the median 
+    % $\log (R_{\mathrm{50}}/\mathrm{kpc})$ values for the \rbcg{} and \nbcg{} are 
+    % $1.22\pm 0.02$ ($\sim 17.4\pm 0.75$ kpc) and $1.09\pm 0.01$ 
+    % ($\sim 12.3\pm0.3$ kpc), which confirm the above observation and is consistent with 
+    % the differences seen in Fig~\ref{fig:prof_1}.  
+    To confirm the differences, we fit the 
+    \logmtot{}-$\log (R_{\mathrm{50}}/\mathrm{kpc})$ relations at 
+    \logmtot{}$\geq 11.6$ using MCMC-sampling method via the ensemble sampler 
+    \texttt{emcee} (\citealt{Emcee})\footnote{Initial guesses are based on maximum 
+    likelihood estimates, and we assume reasonable flat priors for parameters}.
+    The best-fit relation for the massive \rbcg{} galaxies:
+
+    \begin{equation}
+        \begin{aligned}
+        \log (R_{\mathrm{50}}/\mathrm{kpc}) = & (0.73\pm0.13) \times \log (M_{\star, 100\ \mathrm{kpc}}/M_{\odot}) \\ & -(7.49\pm1.56)
+        \end{aligned}
+    \end{equation}
+
+    \noindent And for the massive \nbcg{} galaxies, we have:
+
+    \begin{equation}
+        \begin{aligned}
+        \log (R_{\mathrm{50}}/\mathrm{kpc}) = & (0.68\pm0.06) \times \log (M_{\star, 100\ \mathrm{kpc}}/M_{\odot}) \\ & -(6.88\pm0.75)
+        \end{aligned}
+    \end{equation}
+
+    \noindent As shown in Fig~\ref{fig:scaling_relation}, the two samples follow 
+    relations with similar slope at high-mass end, while have different normalizations.
+    This result is robust against the ranges of \logmtot{}, also the definitions of 
+    ``total'' \mstar{} and  half-light radius (e.g. \mstar{} within different 120 or 150 
+    kpc, and the $R_{\mathrm{50}}$ derived within these apertures).
+
+    We qualitatively compare our results with the one for $z\leq 0.09$ central ETGs in  
+    $14\le$\logmh{}$<15$ halos from \citealt{HCompany13} (HC13; green solid line).
+    HSC13 used the group catalog by \citet{Yang2007} to estimate \logmh{} after
+    empirically convert their \mstar{} from the Kroupa IMF to the Chabrier one 
+    by applying a constant -0.05 shift (see \citealt{Bernardi2016}).
+    They estimated the 2-D $R_{\mathrm{e}}$ using single-\ser{} model fitting to SDSS 
+    images, and derived \mstar{} based on SED fitting using the BC03 (\citealt{BC03}) 
+    synthetic population model.
+    We also increase the \mstar{} in HC13 by $+0.1$dex to account for the systematic 
+    difference between their BC03 and our FSPS model (see Appendix~\ref{app:sed}). 
+    In HC13, the authors found no difference among the mass-size relations for 
+    central galaxies in halos across $12.5\le$\logmh{}$<15.0$. 
+    The mass-size distributions for both \rbcg{} and \nbcg{} galaxies follow the 
+    HC13 relation reasonably well (with slightly shallower slopes) even at 
+    \logmtot{}$< 11.6$ where our samples start to become incomplete.
+
+    In conclusion, we confirm that the massive central galaxies at $0.3 < z < 0.5$
+    follow \mstar{}-size relations that depend on their \mhalo{}. 
+    The central galaxies in denser environment (higher \mhalo{}) have slightly 
+    larger $R_{\mathrm{50}}$ comparing to the ones from smaller haloes at fixed 
+    \mtot{}. 
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
+\subsubsection{Relations between stellar mass within different physical apertures}
+    \label{sssec:m100_m10}
+
+    Now we also want to explore the relationship between \mstar{} within different
+    apertures (\mtot{} v.s. \minn{}) as alternative tool to help us understand the 
+    relationship between \mhalo{} and the assembly history of massive galaxies.   
+    Comparing to the mass-size relation, this relation is not affected by the 
+    ambiguous definition of ``size'', and is much easier to apply to larger samples 
+    and to simulations.
+
+    We show the results in the right panel of Fig \ref{fig:scaling_relation}, and it 
+    is quite easy to notice that the distributions of \rbcg{} and \nbcg{} galaxies 
+    are offset with each other.  
+    Instead of arbitrarily grouping galaxies into different bins of \mtot{} or 
+    \minn{}, this relation brings us a more generic view of the environmental 
+    dependence of structure.
+    On the figure, we also illustrate the \mtot{}-\minn{} relations at 
+    \logmtot$\geq 11.6$ from MCMC sampling method.  
+    For \rbcg{} galaxies, the best-fit relation is:
+
+    \begin{equation}
+        \begin{aligned}
+        \log (M_{\star, 10\ \mathrm{kpc}}/M_{\odot}) = & (0.48\pm0.06) \times \log (M_{\star, 100\ \mathrm{kpc}}/M_{\odot}) \\ & +(5.72\pm0.75).
+        \end{aligned}
+    \end{equation}
+
+    \noindent In the same range of \mtot{}, the best-fit relation for \nbcg{} is:
+
+    \begin{equation}
+        \begin{aligned}
+        \log (M_{\star, 10\ \mathrm{kpc}}/M_{\odot}) = & (0.56\pm0.03) \times \log (M_{\star, 100\ \mathrm{kpc}}/M_{\odot}) \\ & +(4.82\pm0.30).
+        \end{aligned}
+    \end{equation}
+
+    These relations suggest that: (1) At fixed \mtot{}, central galaxy in more 
+    massive halo tend to have lower fraction fraction of \mstar{} stored in the inner
+    region; (2) For massive galaxies with similar \minn{}, the ones in more 
+    massive halos on average have more prominent outer envelopes.  
+    Assuming that the \minn{} traces the \mstar{} of the ``in-situ'' components 
+    reasonably well, this suggests that ``red nuggets'' at high-$z$ with similar 
+    \mstar{} end up following different assembly history that depends on their 
+    environments.
+
+    This result will not change if we replace the \minn{} with \mstar{} within 5 or 
+    15 kpc apertures.
+    Although the $M_{\star, 5\ \mathrm{kpc}}$ values are less reliable than \minn{} 
+    due to the impacts of seeing, the relation using $M_{\star, 5\ \mathrm{kpc}}$ shows 
+    more significant \mhalo{} dependence at the high-mass end.
+    Also, best-fit relation using the full \mtot{} range results in even shallower 
+    slope for the \rbcg{} galaxies.
+
+    % Limited by our capability to estimate \mhalo{} with better accuracy or individually, 
+    % we can not further quantify this \mhalo{}-dependence here.
+    % Albeit that the \redm{} richness ($\lambda$) traces \mhalo{} reasonably well, 
+    % we do not find any clear correlation with $\lambda$ within the \rbcg{} galaxies.
+    % In the current sample, most of the \rbcg{} galaxies are centrals of clusters with 
+    % $30 \leq \lambda \leq 40$, and only a small fraction comes from more massive clusters.  
+    % Therefore, the small sample size, the uncertainties of richness from shallow SDSS
+    % images, and the intrinsic scatter of the $\lambda$-\mhalo{} relation may conspire to 
+    % stop us from extracting more information from this \mhalo{}-dependence.
+
+    This \mhalo{}-dependence can be caused by many different physical processes. 
+    Given the interesting results on the right panel of Fig \ref{fig:scaling_relation},
+    we recommend to apply similar scaling relation to different datasets and 
+    numerical simulations (e.g. see Fig~1 of \citealt{Wellons2016b}) to explore the 
+    physical origins and redshift evolution of this dependence.
+
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
+  \begin{figure}
+      \centering 
+      \includegraphics[width=\columnwidth]{fig/redbcg_discussion_1}
+      \caption{Comparison of the average \mden{} profiles of massive galaxies in the 
+          two lower \mtot{} bins from Fig~\ref{fig:avg_prof} with other observations 
+          and simulations, focusing on the inner region. 
+          The format is similar with the right panel of Fig~\ref{fig:avg_prof}.
+          We include: 
+          1) the average \mden{} profile of inner component from structure 
+          decomposition of massive elliptical galaxies at $z\sim 0$ from 
+          \citet[][Cyan, solid]{Huang2013a}; 
+          2) the average \mden{} profile of massive galaxies at $1.0 < z < 1.5$ 
+          from \textit{HST} observations in \citet[][Red, dashed]{Patel2013}; 
+          3) the average \mden{} profile of the ``in-situ'' stellar components in 
+          simulated massive halos from \citet[][Purple, dot-dashed]{Cooper13};
+          4) the \mden{} profile of the very massive cD galaxy at $z\sim 1.1$ 
+          discovered by \citet[][Yellow, dashed]{Liu2013} in the Hubble 
+          Ultra-Deep Field.}
+      \label{fig:discussion_1}
+  \end{figure}
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
 \section{Discussion}
+    \label{sec:discussion}
 
-\section{Summary}
+    Taking advantage of the deep images from the HSC survey, we show that,
+    \textbf{at $0.3 < z < 0.5$, the structure of massive central galaxy systematically 
+    depends on the mass of their host dark matter halo, at both the inner and outer
+    parts}. 
+    Here, we briefly discuss its physical origin, potential caveats, and more scientific 
+    implications.
 
-%%%%%%%%%%: Acknowledge %%%%%%%%%%
+%% ------------------------------------------------------------------------------------ %%
 
-\acknowledgements
+\subsection{The ``Two phase'' Formation Scenario of Massive Galaxies and the 
+            Build-Up of Outer Envelopes}
 
-  1. Acknowledgements for HSC 
-  2. Acknowledgements for Kevin and Alexie's funding 
-  3. Acknowledgements for the Python libraries
+    Although the photometric data alone can not determine the origin of the 
+    \mhalo{}-dependence we found, \textbf{it does fit the expectations of the 
+    ``two-phase'' scenario at first glance}. 
+    For the massive centrals with similar \mstar{} formed in the ``in-situ'' phase at 
+    high-$z$, it is reasonable to expect that the following mass assembly histories 
+    depend on the environments or halo masses if this second phase of evolution is 
+    indeed dominated by merging with surrounding satellites. 
+    Since the non-dissipative minor mergers mostly accumulate stars onto the 
+    outskirts of the centrals without modifying their central \mden{} much
+    (e.g. \citealt{Oogi2013, Bedorf2013}), the outer stellar envelopes of massive
+    centrals should reflect the environmental dependence of structure better, exactly 
+    as we find from the comparisons of \mden{} profiles and scaling relations.
 
+    State of the art simulations suggest that the slope of the stellar halo becomes 
+    shallower in the central of more massive halos (e.g. \citealt{Pillepich2014}), 
+    this is consistent with the results in Fig \ref{fig:prof_1}. 
+    Meanwhile, these simulation also points out that not only the fraction of 
+    accreted stars increases steeply with total \mstar{}, the ``ex-situ'' component
+    starts to dominate the \mden{} profiles around the $R_{\mathrm{e}}$ for 
+    \logms{}$\geq 11.5$ galaxies.
+    In this work, we do notice that the median \mden{} profiles of \rbcg{} and \nbcg{} 
+    samples start to deviate from each around around 15-20 kpc, which is close to 
+    their $R_{\mathrm{e}}$, and environmental dependence of median \mden{} profiles 
+    become more significant in higher \mtot{} bin (see Fig \ref{fig:prof_4}). 
+    These results all support that the \mhalo{}-dependence of structure in massive 
+    central galaxies is driven by the amount and distribution of accreted stars 
+    in the outskirt.
+
+    In Fig~\ref{fig:discussion_1}, we compare the median \mden{} profiles of the 
+    combined \rbcg{} and \nbcg{} samples in two \mtot{} bins 
+    ($11.4\leq$\logmtot{}$<11.6$ and $11.6\leq$\logmtot{}$<11.8$) with the median 
+    profiles of 
+    (1) massive ETGs at $1.0 < z < 1.5$ that are considered the progenitors of 
+    $\sim 10^{11.5} M_{\odot}$ ETGs at $z=0$ (\citealt{Patel2013}).  
+    After $z\sim 1.5$, the mass assembly of these galaxies should be dominated by 
+    mergers. 
+    (2) the inner components of $\sim 10^{11.4} M_{\odot}$ ellipticals at $z\sim 0$ 
+    from 2-D decomposition (\citealt{Huang2013a}). 
+    \citet{Huang2013b} showed that these components are similar to the compact 
+    ``red nuggets'' at high redshift in structure. 
+    (3) the ``in-situ'' components of simulated galaxies in massive halos from 
+    \citet{Cooper13} using particle-tagging technique (the inner $\sim 5$ kpc is 
+    quite uncertain due to the resolution).  
+    Despite the differences in median \mstar{} and details in \m2l{} 
+    estimates\footnote{We convert the \mden{} profiles to the same Chabrier IMF}, 
+    the comparison confirms that \minn{} should be reasonable proxy of the 
+    ``in-situ'' mass.  
+    More importantly, it shows that the \mden{} profile at $\mathrm{R} > 15$-20 kpc, 
+    where we find clear evidence of environmental dependence, is likely dominated by 
+    stars that are not in the ``in-situ'' component.
+
+    % Most of these literatures that we compare with are not dominated by the extremely 
+    % massive ones in the our sample, so the actual \mden{} median profile of the ``in-situ'' 
+    % components for \rbcg{} and \nbcg{} galaxies could be closer to the median profiles 
+    % shown in Fig~\ref{fig:discussion_1}.
+
+    We also compare with a uniquely massive BCG at high redshift: 
+    a $\sim 10^{11.4} M_{\odot}$ BCG with distinctive ``cD''-like envelope at 
+    $z\sim 1.1$ (\citealt{Liu2013}).  
+    Its \mden{} profile follows the median profile of $11.6\leq$\logmtot{}$<11.8$ 
+    massive galaxies nicely inside 10-15 kpc, but becomes much steeper in the outskirt.  
+    This unique object may present an interesting case where the inner ``core'' of a 
+    massive BCGs is already in pace at $z\sim 1$ when its extended envelope is still
+    under construction.
+    More BCGs like this at $0.5 < z < 1.0$ can shed light on this intriguing 
+    process, and help us confirm whether the environmental dependence of structure 
+    has already emerged within massive galaxies at higher redshift 
+    (e.g. \citealt{Papovich2012})
+
+    At the same time, we also find \rbcg{} galaxy tends to have lower \mstar{} within 
+    inner 5-10 kpc and shallower inner \mden{} profile than the \nbcg{} one at 
+    fixed \mtot{}. 
+    Although the HSC images do not have sufficient resolution to investigate this in 
+    details, it is worth pointing out that this difference could be physically 
+    interesting. 
+    Observations of compact quiescent galaxies at high-$z$ often reveal higher 
+    \mden{} in the central region than their descendants, and certain process need to  
+    be responsible for reducing the central \mden{} (e.g. strong adiabatic expansion 
+    induced by powerful AGN feedback; \citealt{Fan2008}).
+    Coalesce of super-massive black hoes (SMBHs) at the end of major merger, which is 
+    common in the assembly history of massive galaxies, can also flatten the central 
+    \mden{} profile (e.g. \citealt{Milosavljevi2002}).
+    On the right side of Fig \ref{fig:scaling_relation}, we find a few \rbcg{} galaxies 
+    with very low \minn{} at high \mtot{} end that are apparently not bothered by 
+    problematic photometry or exceptionally bad seeing.  
+    They may be similar to the recently discovered massive BCGs with very large core 
+    (a few kpc; e.g. \citealt{Postman2012, LopezCruz2014}) resulting from SMBH mergers.
+    The impacts of these processes, and their dependence on \mhalo{} is an interesting 
+    topic to investigate in the future.
+
+%% ------------------------------------------------------------------------------------ %% 
+  \begin{figure*}
+      \centering 
+      \includegraphics[width=\textwidth]{fig/redbcg_discussion_5}
+      \caption{
+          \textbf{Left}: Relation between \mtot{} and the logarithmic mass difference 
+          between \mmax{} and \mtot{} for both \rbcg{} (red square) and \nbcg{} 
+          (grey dot) galaxies.  The format is very similar to the left figure of 
+          Fig~\ref{fig:smf1}.~~
+          \textbf{Right}: The stellar mass volume-density distributions of massive galaxies 
+          after combining the \rbcg{} and \nbcg{} samples together, using both 
+          \mtot{} (black solid line) and \mmax{} (black dash line). 
+          The uncertainty for distribution using \mtot{} is shown in grey shaded region.  
+          Here, we also compare the distributions with SMF from previous works: 
+          (a): SDSS galaxies at $z\sim 0.1$ from \citet{Bernardi2013}; the \mstar{} is 
+          based on photometry from 2-D \ser{}$+$Exponential model fitting; 
+          (b): SDSS galaxies at $z\sim 0.1$ from \citet{Moustakas13} based on 
+          improved SDSS \texttt{cModel} photometry; 
+          (c): \texttt{S82-MGC} galaxies at $0.15 < z< 0.43$ from 
+          \citet{Leauthaud2016} based on PSF-matched SDSS-UKIDSS photometry.
+          Please see text for more details of the comparison.
+          }
+      \label{fig:discussion_2}
+  \end{figure*}
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %%
+
+\subsection{On the Classification of "cD" Galaxies}
+
+    Among the massive galaxies in our sample (both \rbcg{} and \nbcg{} ones), we find that 
+    the distribution of their outer \mden{} profiles is quite smooth but also with a large
+    scatter (See Fig \ref{fig:avg_prof}) that blurs the boundary between ``normal'' 
+    elliptical galaxy and the so-called ``cD'' galaxies that are surrounded by a large 
+    and diffuse stellar envelope. 
+    Traditionally, the ``cD'' galaxies are often found among BCGs of nearby clusters, 
+    and treated as a distinctive population.
+
+    Now with the help of deep HSC images, we know that the BCGs only show subtle 
+    structural differences comparing to non-BCG galaxies with similar \mtot{}, hence do 
+    not form a unique population in term of structure (see Fig \ref{fig:prof_1}). 
+    The wide and smooth distributions of \mden{} profiles in the outskirt further suggest 
+    that it might not be very physically meaningful to separate these massive galaxies 
+    into two arbitrary morphological classes. 
+    This conclusion is similar to the result of \citep{Zhao2015} where the authors found 
+    a large fraction of nearby BCGs (34\%) does not fall into the ``cD'' class.
+
+    This continuous distribution of \mden{} profiles and its dependence on \mtot{} is 
+    also consistent with results from HST observations of BCGs at $0.3 < z <0.9$ 
+    (\citealt{Bai2014}) and the claimed positive correlation between luminosity and \ser 
+    index (e.g.\ \citealt{Savorgnan13}). 
+    Although single \ser{} model is not appropriate to describe the structure of these 
+    massive galaxies\footnote{Can not explain the diversity of \mden{} profiles; often 
+    fails dramatically at inner region; and can not follow the radial variation of 
+    isophotal shape}, we agree that its time to treat the stellar envelopes of massive 
+    galaxies as the outcomes of a series of merging events, and focus more on how to 
+    extract more information about their assembly histories through a more physical 
+    angle.    
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %%
+
+\subsection{What is the "Total Mass" of Massive Galaxies?}
+
+    Definition of ``total'' \mstar{} is always tricky for massive galaxies even 
+    with deep HSC images.
+    Although our choice of \mtot{} in 1-D has certain advantages over 2-D modeling 
+    method, and should contains most of the stellar contents of the galaxy, there
+    is no evidence that \mden{} profile truncates at 100 kpc. 
+    To illustrate this, we compare the \mtot{} wit the \mstar{} integrated  
+    to the maximum radius allowed by the profile (\mmax{}, Left of Fig 
+    \ref{fig:discussion_2}). 
+    This new definition results in higher value of ``total'' \mstar{}.
+    The difference is small (average: $\sim 0.04$ dex), but apparently depends on 
+    the slope of the stellar envelope. 
+    The \mden{} profiles outside 100 kpc are much less accurate, hence the \mmax{} 
+    is less reliable than \mtot{}. 
+    All the conclusions here also remain intact when replacing \mtot{} with 
+    \minn{}.  
+    However, it is still necessary to remind people again the difficulty of 
+    defining and measuring the \mstar{} of mass galaxies since there are 
+    situations when the scientific results heavily depend on it.
+
+    For instance, the SMF is one of the most important statistics when studying 
+    galaxy evolution. 
+    Yet, even at $z\sim 0$, the normalization and shape of SMF at high-mass end 
+    are still uncertain partly due to the above-mentioned issue 
+    (\citealt{Bernardi2016}) despite that they are critical for understanding the 
+    overall evolution of galaxies. 
+    In Fig~\ref{fig:smf1}, we illustrate how improved \mstar{} measurement can 
+    significantly modify SMF.  
+    On the right side of Fig~\ref{fig:discussion_2}, we further highlight that 
+    the shape of SMF at high-mass end is quite sensitive to even very small 
+    change of \mstar{}.
+    We also compare the volume-density distributions of the combined \rbcg{} and 
+    \nbcg{} samples with published SMFs:
+
+    \begin{itemize}
+        \item SMF for SDSS-\textit{GALEX} sample of $z\sim 0.1$ galaxies from 
+            \citet{Moustakas13}. 
+            The total luminosity is based on SDSS \cmodel{} one; the \m2l{} is 
+            derived via SED fitting using \texttt{iSEDfit} with similar 
+            assumptions.
+        \item SMF for $z\sim 0.1$ SDSS galaxies from \citet{Bernardi2013}. 
+            The total luminosity is based on 2-D \texttt{SerExp} models 
+            (\ser{}$+$ Exponential disk model; integrated to infinity) that 
+            recover much more flux comparing with the \cmodel{} ones at 
+            high-luminosity end. 
+            The \m2l{} is also from SED fitting assuming a Chabrier IMF.
+        \item SMF for $0.15 < z < 0.30$ galaxies from the \texttt{S82-MGC} sample
+            \citep{Leauthaud2016}, where the \mstar{} is derived using 
+            \texttt{iSEDfit} on PSF-corrected aperture photometry from 
+            \texttt{S82}.
+    \end{itemize}
+
+    It is clear that SMFs from different groups show quite different slopes 
+    at high-mass end. 
+    Although we did not carefully separate the impacts from photometry and 
+    assumptions of stellar population models (e.g. \citealt{Bernardi2016}), 
+    we think the main cause of such differences should be photometry alone as 
+    the SED fitting results are based on the same IMF and similar assumptions.  
+    Serious comparison of SMF certainly deserves more careful treatment, 
+    but it is interesting to see that the SMF from \citep{Bernardi2013} has 
+    shallower slope at high-mass end than ours even they still rely on SDSS
+    images. 
+    It is important to look into this by comparing with 2-D models like the 
+    \texttt{SerExp} ones in the near future.
+
+    Finally, we want to point out that we do not separate the potential intra-cluster 
+    light component (ICL; e.g. \citealt{Carlberg1997, Lin2004, Gonzalez2005, 
+    Mihos2005}), but rather treat the stellar distributions 
+    out to 100 kpc as an integrated structure.
+    Reliable isolation of physically meaningful ICL component using photometry 
+    alone is extremely difficult, if not impossible. 
+    At the imaging depth of HSC, we find no evidence for a clearly separated 
+    component in \mden{} and other profiles. 
+    Our \rbcg{} sample contains only a small fraction of extremely massive clusters 
+    where strong evidence of photometric ICL component is often found. 
+    At the typical \mhalo{} of our \rbcg{} clusters, one good nearby example would be 
+    the Virgo cluster, whose ultra-deep images (e.g. \citealt{Mihos2016}) show
+    that the stellar halo of the BCG can smoothly extends beyond 100 kpc, while the 
+    ICL only becomes important outside that radius and is dominated by individual 
+    tidal features. 
+    That being said, we do not ignore the existence of stellar population in the 
+    very outskirt of BCG that are dynamically controlled by the cluster potential 
+    well, and save the discussion about its connection to the assembly of massive 
+    central galaxies to the future.  
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
+\section{Summary and Conclusions}
+    \label{sec:summary}
+
+    In this work, we study the how environment (halo mass) affects the structures and
+    assembly history of massive central galaxies using deep images from the Subaru HSC 
+    survey.
+    With the help of these high-quality data, we map the stellar mass distributions of 
+    large numbers of massive central galaxies at $0.3 < z < 0.5$ out to $>100$ kpc, 
+    and discussing their environmental dependence after grouping them into centrals of 
+    halos more and less massive than \mhalo{}$\sim 10^{14} M_{\odot}$. 
+    The main results here are:
+
+    \begin{enumerate}
+        \item We find that the ``total'' \mstar{} of these massive galaxies could be 
+            significantly underestimated when shallow image (e.g. the SDSS ones) 
+            and/or imperfect model assumption (e.g. the \texttt{cModel}) are used.
+            In different with previous works, this result does not depend on stacking 
+            analysis or any parametric model. 
+            Moreover, the level of such underestimation could also depend on the 
+            stellar mass. 
+            This should be carefully taken into account when discussing important 
+            topics like the stellar mass function and its evolution.
+        \item At fixed \mstar{} within 100 kpc, we find that the massive central 
+            galaxies in more and less massive halos have subtle, but systematic 
+            differences in their \mden{} profiles when their ellipticity and optical 
+            color profiles are very similar. 
+            On average, the ones from denser environments have slightly shallower 
+            inner \mden{} profiles while showing more prominent outer envelope.
+        \item Meanwhile, when matched at the same \mstar{} within inner 10 kpc--a 
+            proxy of the \mstar{} formed in the the ``in-situ'' channel, we find 
+            that the ones in more massive halos possess much more extended stellar 
+            envelope in the outskirts than the ones in smaller halos when the 
+            \mden{}, ellipticity, and optical color profiles inside 10 kpc show 
+            no dependence on environment. 
+        \item The \mstar{}-size relation also reflects the subtle environmental 
+            dependence as the central galaxies from more massive halos have 
+            slightly higher $R_{\mathrm{50}}$ at fixed \mtot{}. 
+            We further suggest that the relation between \mtot{} and 
+            \minn{}\footnote{or any better proxy of total \mstar{} and the mass 
+            formed in the ``in-situ'' phase.} can be useful tool in diagnosing the
+            assembly history of these massive galaxies and its relation to their 
+            dark matter halos.
+    \end{enumerate}
+
+	%\subsection{Future Improvements}
+    These results also highlight the advantages of HSC survey in studying the 
+    evolution of massive galaxies.
+    Upon finishing this work, the HSC survey has already doubled its sky 
+    coverage to $\sim 200$ deg$^2$, and provides a much larger sample of massive 
+    central galaxies. 
+    In the near future, besides using larger samples directly selected using the 
+    HSC photometry and photometric redshift,
+    we will improve the modeling of massive galaxies through careful 2-D method 
+    (e.g.\ \citealt{Huang2013a}) and by including multiband data 
+    (e.g.\ \citealt{Huang2016}).  
+    We will also try to get more physical insights with the help of the HSC weak 
+    lensing analysis and comparisons with cosmological hydro-simulations such as 
+    Illustris (\citealt{Vogelsberger2014}, \citealt{Genel2014}), 
+    EAGLE (\citealt{Schaye2015}, \citealt{Crain2015}), 
+    or \textit{Horizon-AGN} (\citealt{Dubois2014}).
+
+%% ------------------------------------------------------------------------------------ %%
+
+%\acknowledgements
+\section*{Acknowledgements}
+
+  % Personal 
+  SH thanks F.S.Liu for sharing the data from his work.
+
+  % HSC part
+  The Hyper Suprime-Cam (HSC) collaboration includes the astronomical communities of 
+  Japan and Taiwan, and Princeton University.  The HSC instrumentation and software were
+  developed by the National Astronomical Observatory of Japan (NAOJ), the Kavli Institute
+  for the Physics and Mathematics of the Universe (Kavli IPMU), the University of Tokyo,
+  the High Energy Accelerator Research Organization (KEK), the Academia Sinica Institute
+  for Astronomy and Astrophysics in Taiwan (ASIAA), and Princeton University.  
+  Funding was contributed by the FIRST program from Japanese Cabinet Office, the Ministry 
+  of Education, Culture, Sports, Science and Technology (MEXT), the Japan Society for 
+  the Promotion of Science (JSPS), Japan Science and Technology Agency (JST), the
+  Toray Science Foundation, NAOJ, Kavli IPMU, KEK, ASIAA, and Princeton University.
+
+  % SDSS part
   Funding for SDSS-III has been provided by the Alfred P. Sloan Foundation, the
-  Participating Institutions, the National Science Foundation, and the U.S.
-  Department of Energy. The SDSS-III web site is http://www.sdss3.org.  SDSS-III
-  is managed by the Astrophysical Research Consortium for the Participating
-  Institutions of the SDSS-III Collaboration including the University of
-  Arizona, the Brazilian Participation Group, Brookhaven National Laboratory,
-  University of Cambridge, University of Florida, the French Participation
-  Group, the German Participation Group, the Instituto de Astrofisica de
-  Canarias, the Michigan State/Notre Dame/JINA Participation Group, Johns
-  Hopkins University, Lawrence Berkeley National Laboratory, Max Planck
-  Institute for Astrophysics, New Mexico State University, New York University,
-  Ohio State University, Pennsylvania State University, University of
-  Portsmouth, Princeton University, the Spanish Participation Group, University
-  of Tokyo, University of Utah, Vanderbilt University, University of Virginia,
-  University of Washington, and Yale University.
+  Participating Institutions, the National Science Foundation, and the U.S.  Department of
+  Energy. The SDSS-III web site is http://www.sdss3.org.  SDSS-III is managed by the
+  Astrophysical Research Consortium for the Participating Institutions of the SDSS-III
+  Collaboration including the University of Arizona, the Brazilian Participation Group,
+  Brookhaven National Laboratory, University of Cambridge, University of Florida, the
+  French Participation Group, the German Participation Group, the Instituto de Astrofisica
+  de Canarias, the Michigan State/Notre Dame/JINA Participation Group, Johns Hopkins
+  University, Lawrence Berkeley National Laboratory, Max Planck Institute for
+  Astrophysics, New Mexico State University, New York University, Ohio State University,
+  Pennsylvania State University, University of Portsmouth, Princeton University, the
+  Spanish Participation Group, University of Tokyo, University of Utah, Vanderbilt
+  University, University of Virginia, University of Washington, and Yale University.
 
-%%%%%%%%%%: Bibligraphic Section %%%%%%%%%%
+  % Pan-STARRS1 part
+  The Pan-STARRS1 Surveys (PS1) have been made possible through contributions of the 
+  Institute for Astronomy, the University of Hawaii, the Pan-STARRS Project Office, 
+  the Max-Planck Society and its participating institutes, the Max Planck Institute 
+  for Astronomy, Heidelberg and the Max Planck Institute for Extraterrestrial Physics, 
+  Garching, The Johns Hopkins University, Durham University, the University of Edinburgh, 
+  Queen's University Belfast, the Harvard-Smithsonian Center for Astrophysics, the Las 
+  Cumbres Observatory Global Telescope Network Incorporated, the National Central 
+  University of Taiwan, the Space Telescope Science Institute, the National Aeronautics 
+  and Space Administration under Grant No. NNX08AR22G issued through the Planetary 
+  Science Division of the NASA Science Mission Directorate, the National Science 
+  Foundation under Grant No. AST-1238877, the University of Maryland, and Eotvos 
+  Lorand University (ELTE).
 
-%\begin{thebibliography}{}
+  % LSST software
+  This paper makes use of software developed for the Large Synoptic Survey 
+  Telescope. We thank the LSST Project for making their code available as free 
+  software at http://dm.lsstcorp.org.
 
-  %\bibitem[Arnold et al.(2011)]{2011ApJ...736L..26A} Arnold, J.~A., Romanowsky,
-    %A.~J., Brodie, J.~P., et al.\ 2011, \apjl, 736, LL26
+  % Software
+  This research made use of:
+  \href{http://www.stsci.edu/institute/software_hardware/pyraf/stsci\_python}{\texttt{STSCI\_PYTHON}},
+      a general astronomical data analysis infrastructure in Python. 
+      \texttt{STSCI\_PYTHON} is a product of the Space Telescope Science Institute, 
+      which is operated by AURA for NASA;
+  \href{http://www.scipy.org/}{\texttt{SciPy}},
+      an open source scientific tools for Python (\citealt{SciPy});
+  \href{http://www.numpy.org/}{\texttt{NumPy}}, 
+      a fundamental package for scientific computing with Python (\citealt{NumPy});
+  \href{http://matplotlib.org/}{\texttt{Matplotlib}}, 
+      a 2-D plotting library for Python (\citealt{Matplotlib});
+  \href{http://www.astropy.org/}{\texttt{Astropy}}, a community-developed 
+      core Python package for Astronomy (\citealt{AstroPy}); 
+  \href{http://scikit-learn.org/stable/index.html}{\texttt{scikit-learn}},
+      a machine-learning library in Python (\citealt{scikit-learn}); 
+  \href{http://www.astroml.org/}{\texttt{astroML}}, 
+      a machine learning library for astrophysics (\citealt{astroML});
+  \href{https://ipython.org}{\texttt{IPython}}, 
+      an interactive computing system for Python (\citealt{IPython});
+  \href{https://github.com/kbarbary/sep}{\texttt{sep}} 
+      Source Extraction and Photometry in Python (\citealt{PythonSEP});
+  \href{https://jiffyclub.github.io/palettable/}{\texttt{palettable}},
+      color palettes for Python;
+  \href{http://dan.iel.fm/emcee/current/}{\texttt{emcee}}, 
+      Seriously Kick-Ass MCMC in Python;
+  \href{http://bdiemer.bitbucket.org/}{\texttt{Colossus}}, 
+      COsmology, haLO and large-Scale StrUcture toolS (\citealt{Colossus}).
 
-%\end{thebibliography}{}
+%%%%%%%%%%: Bibliographic Section %%%%%%%%%%
 
+\bibliographystyle{mnras}
 \bibliography{redbcg}
@@
 
-\section{A. Atlas of 1-D Profiles}
+%% ------------------------------------------------------------------------------------ %%
 
-%%%%%%%%%%%%: Figures Section %%%%%%%%%%%%
+\section{A. Basic Statistical Properties of the Sample} 
+	\label{app:sedasic}
 
-% Fig. 1
-\clearpage
-\figurenum{1}
+    On the top-left panel of Fig~\ref{fig:sample_stats}, we show the \mtot{}-color 
+    relations using the $k$-corrected $g-r$ color. 
+    Both samples follow the same tight ``red-sequence'' with little contamination 
+    from the ``blue cloud''.
+    At fixed \mtot{}, we see little offset in color distributions of the two 
+    samples, suggesting that both samples consist of quiescent galaxies with 
+    similar average stellar population properties.  
+    This is consistent with previous result that suggests the average stellar 
+    population of massive central galaxy does not depend on \mhalo{} 
+    (e.g.\ \citealt{Park2007}).  
+    In this work, we focus on the \mstar{} range of $11.6 \le$\logmtot{}$\le 11.9$, 
+    where both samples have acceptable completeness, and their \mtot{} distributions 
+    greatly overlap (see the normalized distributions of \mtot{} in the bottom-left 
+    panel of Fig~\ref{fig:sample_stats}). 
+    As for the \minn{} distributions, the two samples overlap the most within 
+    $11.2 \le$\logmtot{}$\le 11.6$, but now they show quite different
+    distributions (bottom-right figure).
+
+    The redshift distributions also show small difference
+    (upper-right panel) even in the high-\mtot{} bin, where the redshift distribution 
+    of the \nbcg{} sample skews toward higher-$z$ end due to the contribution of BOSS 
+    spec-$z$.
+    Since this could bias the comparison of \mden{} profiles and other properties 
+    (please see Appendix\ref{app:redshift} for more details), we address this via matching 
+    the two samples in both mass and redshift distributions carefully
+    (see Appendix~\ref{app:match}).
+
+%% ------------------------------------------------------------------------------------ %% 
+  \begin{figure*}
+      \centering 
+      \includegraphics[width=16.5cm]{fig/redbcg_sample_stats}
+      \caption{
+          \textbf{Top-left}: The \logms{}-$g-r$ color relation of the \rbcg{} 
+          (red circle; detaield format is the same with the right panel of 
+          Fig~\ref{fig:smf1}) and \nbcg{} (grey dots) samples.
+          We apply the $k$-corrections from \texttt{iSEDFit} fitting to the colors.~~          
+          \textbf{Top-right}: the histograms of the redshift for the \rbcg{} and 
+          \nbcg{} galaxies in both \logmtot$>11.2$ and $11.6<$\logmtot{}$<11.9$
+          mass bins.
+          The vertical lines highlights the $0.3\leq z \leq 0.5$ redshift range.~~
+          \textbf{Bottom-left}: the histograms of \mtot{} for the \rbcg{} (orange-red) 
+          and \nbcg{} (grey-black) samples at both $z>0.2$ (step-filled histogram) and 
+          $0.3 \leq z \leq 0.5$ (stepped histogram). 
+          The vertical lines in both top-left and bottom-left figures highlight the 
+          $11.6<$\logmtot{}$<11.9$ mass range that will be used in the comparison of 
+          the \mtot{}-matched samples.~~
+          \textbf{Bottom-right}: the histograms of \minn{} in similar format. 
+          Here the vertical lines highlight the 
+          $11.2<$\logminn{}$<11.6$ mass range that is used for comparison.
+      }
+      \label{fig:sample_stats}
+  \end{figure*}
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
+\section{B. Extraction of 1-D surface brightness profile} 
+    \label{app:ellipse}
+
+    Here we briefly discuss a few technical issues related to the measurements of the 
+    1-D surface brightness profiles around massive galaxies.
+
+    To derive reliable 1-D profile, it is important to mask out all the irrelevant 
+    objects around the target.
+    At the depth of the HSC images, this becomes a quite difficult task, especially 
+    for massive galaxies with extended outer profiles and more satellites. 
+    Right now, the \texttt{hscPipe} tends to ``over-deblend'' around bright object, 
+    we therefore perform \texttt{SExtractor}-like background subtraction and object 
+    detection using the \texttt{SEP} Python library to generate the necessary masks.
+    Combining two different local background models and $S/N$ thresholds, we obtain 
+    the centroid, shape, and radius that enclose 90\% of flux for each object, even 
+    the one that is close to the center of bright galaxy (left panel of 
+    Fig~\ref{fig:ell_tech}), and generate its initial elliptical mask based on these
+    information. 
+    We first create the mask that covers all contaminating objects around the target 
+    after adaptively increasing the sizes of their masks according to their brightness 
+    and distance to the target center. 
+    Generally speaking, we mask out the very bright objects or objects in the 
+    outskirt of the target a little more aggressively as they could impact the 
+    low surface brightness regions more significantly. 
+    We also create masks that are less and more aggressive to test their impacts
+    on the surface brightness profiles.
+
+    Next, we aggressively mask out all objects on the cut-out image and use this mask
+    to evaluate the background level using the distribution of pixel values after 
+    median smoothing the masked image within $6x6$ pixels.
+    This provides us a global estimate of background level along with its uncertainty. 
+    Given the typical RMS of the background pixels, the HSC \texttt{WIDE} images 
+    should reach to $> 29$ \sb surface brightness level in $i$-band.  
+    However, the global background level is often negative around our massive 
+    galaxies, indicating systematic issue in background subtraction.  
+    In current \texttt{hscPipe}, the background on each CCD is modeled with a 
+    Chebyshev-polynomial that is fit to the smoothed image after excluding pixels 
+    with $S/N >5$.
+    This algorithm performs much better than the SDSS version 
+    (e.g.\ see \citealt{Blanton2011}), yet still over-subtracts sky around bright 
+    objects and results in unphysical truncation in the surface brightness profile.
+    We attempt to empirically correct this using the background model generated by 
+    the \texttt{SExtractor} algorithm on the masked image 
+    ($200x200$ pixels background box size, and 6 pixels median filtering size of 
+    sky boxes).
+    This model can account for the slightly over-subtracted background at large scale,
+    and also reduces the impact from the low surface brightness ``wings'' of bright 
+    nearby objects. 
+    After the correction, we can see the improvement from both the remeasured global 
+    background value (closer to 0) and the surface brightness profile (middle panel 
+    of Fig~\ref{app:ellipse}; the negative intensity and the turn-over of the 
+    curve-of-growth in the outskirt of the ``Original'' profile are successfully 
+    corrected). 
+    Such ad hoc correction is not the best way to achieve accurate background 
+    subtraction, but the surface brightness profile within 100 kpc is not very
+    sensitive to the over-subtraction of sky as while.
+
+    The procedure to derive 1-D surface brightness profile from the 
+    background-corrected, contamination-masked images is already described in 
+    Section~\ref{sec:ellipse} briefly. 
+    In practice, the profile at very low surface brightness level is sensitive to 
+    several \texttt{Ellipse} configurations.
+    After some tests, we choose to use 0.1 dex in logarithm as the step in semi-major 
+    axis length between successive ellipses, and we use the median pixel value over the
+    elliptical annulus after rejecting outlying pixels via $3\sigma$-clipping three
+    times.
+    We make the above choices to make the final profile less affected by any nearby
+    object, and also test the differences between the profiles derived using larger
+    step, or mean value on the annulus, or fewer times of $\sigma$-clipping. 
+    Generally speaking, the surface brightness profile is very robust against these
+    changes.  
+    On the right panel of Fig~\ref{fig:ell_tech}, we compare the surface brightness
+    profiles for an example massive galaxy using different masks and \texttt{Ellipse}
+    parameters. 
+    The profile within 100 kpc is very stable, and the only meaningful difference 
+    we can spot is caused by the less aggressive object mask in the very outskirt.
+
+    We should also mention that we run \texttt{Ellipse} allowing for more 
+    sophisticated shapes than a simple ellipse (4th Fourier modes that can make 
+    isophote more ``disky'' or ``boxy'', e.g.\ \citealt{Kormendy2009}) to fit the 
+    isophote better.
+    We also apply the isophotes from $i$-band images to other bands in 
+    ``force-photometry'' mode \texttt{Ellipse} run to get rough estimates of 
+    color profiles.  
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
+    \begin{figure*}
+        \centering 
+        \includegraphics[width=\textwidth]{fig/redbcg_ellipse_tech}
+        \caption{
+            \textbf{Left:} Example of the object-mask built for the \texttt{Ellipse}
+            run for a typical massive galaxy in the sample. 
+            All the shaded regions are masked out. 
+            The three dash lines (red, inner one and two blue ones) around the target 
+            at the center outlines the three radius we defined using the flux radius 
+            of the target.  
+            We increase the mask size for objects detected in different regions 
+            separated by these apertures (which are outlined by solid, elliptical 
+            apertures with different colors) using slightly different criteria.~~
+            \textbf{Middle:}: The flux profile that is zoomed into the near-zero flux 
+            range (top panel), and the curve-of-growth of the magnitude for the example
+            massive galaxy.  
+            To highlight the importance of correcting sky background, we show the profiles 
+            using both images with (red, solid line) and without (black, dash line) 
+            ad-hoc background correction. 
+            On the top panel, besides the horizontal line that highlights the zero flux 
+            level, we also show the uncertainty of the sky background estimate via 
+            grey-shaded region.  
+            On the bottom panel, two horizontal lines indicate the magnitudes 
+            corresponding to total (solid) and half flux (dash) using the 
+            background-corrected profile. ~~
+            \textbf{Right:} compare the 1-D surface brightness profiles for the same 
+            example galaxy extracted using different mask 
+            (smaller masking region: red, dash line; larger masks: blue, dash line), 
+            or different \texttt{Ellipse} settings
+            (more aggressive pixel-clipping: cyan, dash line; 
+             larger step in radius: green, dash line; 
+             using mean flux along the isophote instead of median: purple, dash line)
+            with the one using the default configuration (black, solid line).
+            }
+        \label{fig:ell_tech}
+    \end{figure*}
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
+\section{C. Estimate average {$M_{\star}/L_{\star}$} using \texttt{iSEDFit}} 
+    \label{app:sed}
+
+%% ------------------------------------------------------------------------------------ %% 
+    \begin{figure*}
+        \begin{center}
+        \includegraphics[width=\textwidth]{fig/redbcg_isedfit_example.pdf}
+        \caption{
+            Left: example output figure from \texttt{iSEDFit} that shows the SED 
+        	fitting results. 
+            The open-boxes show the observed fluxes in 5-band, and the solid, blue-dots
+            show the best-fitted results, along with the high-resolution spectrum for
+            this model reconstructed using the synthetic spectra from \texttt{FSPS}. 
+            Top-left corner shows the best-fit stellar population parameters, and 
+            bottom-right corner shows the ID, redshift of this object, and reduced 
+            $\chi^2$ of the best-fit model.~~~
+            Right: the Posterior distributions of a few key parameters.
+            From top-left to bottom right are: 1) stellar mass (\logms{}); 2) age of the 
+            population (mass and star-formation rate weighted) in Gyr; 3) star formation 
+            rate ($\log\ \mathrm{SFR}\ (M_{\odot}/\mathrm{yr})$; instant one and the one 
+            averaged over the previous 100 Myr; 4) stellar metallicity 
+            ($\mathrm{Z}/\mathrm{Z}_{\odot}$); 5) dust extinction ($\mathrm{A}_V$ in mag);
+            6) birthrate parameter ($\log\ b$; averaged over previous 100 and 1000 Myr).
+            }
+        \label{fig:ised}
+        \end{center}
+    \end{figure*}
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
+    \begin{figure*}
+        \begin{center}
+        \includegraphics[width=\textwidth]{fig/redbcg_isedfit_2.pdf}
+        \caption{
+            Relationships between \mstar{} and other stellar population 
+            parameters using the results from \texttt{iSEDfit}. 
+            The \textbf{left} figures are for the \rbcg{} sample, and the 
+            \textbf{righ}t ones are 
+            for the \nbcg{} sample. 
+            They are both color-coded using the redshift of the object, while 
+            their sizes reflect the magnitude differences in $i$-band between 
+            the observed and best-fit value. 
+            The four stellar population properties are: 
+            1) \textbf{Top-left}: mass-weighted stellar age in Gyr; 
+            2) \textbf{Bottom-left}: \m2l{} in $i$-band; 
+            3) \textbf{Top-right}: mass-weighted stellar metallicity in unit of Solar 
+            value;
+            4) \textbf{bottom-right}: dust extinction values in magnitude.
+            }
+        \label{fig:ised_2}
+        \end{center}
+    \end{figure*}
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
+    \begin{figure*}
+        \begin{center}
+        \includegraphics[width=\textwidth]{fig/redbcg_isedfit_3.pdf}
+        \caption{
+            Comparisons of \mstar{} estimated by \texttt{iSEDFit} using different
+            assumptions. 
+            In each figure, we plot the \mstar{} from default model against their 
+            differences with other models. 
+            The top (bottom) row shows the comparisons of the \rbcg{} (\nbcg{}) sample. 
+            The four models involved here are labeled as: 
+            (A): default one; 
+            (B): using the Salpeter IMF instead of the Chabrier one 
+                (\textbf{Left column});
+            (C): using the BC03 synthetic population model instead of the FSPS one
+                (\textbf{Middle column});
+            (D): assume that there is no dust extinction (\textbf{Right column}). 
+            On each figure, the grey shaded region highlights the uncertainty 
+            of the $\log($\logms{}$)$ using typical \mstar{} uncertainties from 
+            both sides. 
+            For each comparison, we highlight the median $\chi^{2}$ value, and the fraction
+            of galaxies with $\chi^{2} > 10.0$ at the top. 
+            We also show the histogram of the \mstar{}-differences on the right panel.
+            }
+        \label{fig:ised_3}
+        \end{center}
+    \end{figure*}
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %%
+
+    In Section~\ref{ssec:isedfit}, we briefly explain the SED fitting procedure and 
+    the priors used.   
+    In Fig~\ref{fig:ised_1}, we show an example of the \texttt{iSEDFit} output by 
+    visualizing the 5-band HSC SED on top of the best-fit model along with the PDF 
+    of the key parameters. 
+    Although we only use the best-fit \m2l{} in this work, it is necessary to make 
+    sure the model is reasonable. 
+    We show the relations between \mstar{} and a few key stellar population parameters 
+    derived by \texttt{iSEDFit} in Fig~\ref{fig:ised_2}. 
+    Although degeneracies among these parameters are almost inevitable using only 
+    five broad-band photometry, most massive galaxies in both \rbcg{} (left) and 
+    \nbcg{} (right) samples have old age, high metallicity ($1.5 \times Z_{\odot}$ is 
+    the highest metallicity allowed by the adopted \texttt{FSPS} SSP models), and low 
+    dust extinction as expected
+
+    Meanwhile, \mstar{} measurement based on SED fitting heavily depends on the 
+    adopted SSP model, the form of IMF, dust extinction law, and details in 
+    the assumption of SFH (e.g.\ \citealt{Bernardi2016b}). 
+    For massive galaxies in this sample, the form of the SFH\footnote{We choose 
+    to use the delayed-$\tau$ model for SFH; we adopt flat distribution between 
+    0.5 to 14.0 Gyrs as the prior for the look-back time when the star formation 
+    turned on. 
+    The exponential delayed time-scale ($\tau$) is allowed to change between 
+    0.1 to 3.0 with equal probability}, the contribution from random star 
+    burst\footnote{The chance of random star burst is set at 0.2 for every 2 Gyrs. 
+    The duration of the star burst is draw from a logarithmic distribution 
+    between 0.03 to 0.3 Gyr; and the mass fraction formed in the burst is from 
+    a logarithmic distribution between 0.01 and 1.0.} do not affect the results. 
+    On the other hand, the choices of SSP model, IMF, and dust extinction do impact
+    the SED fitting results systematically, and we explore it using a few 
+    additional tests (see Fig~\ref{fig:ised_3}):
+
+    \begin{enumerate}
+
+        \item Choosing the \citet{Salpeter1955} IMF results in systematically 
+            higher \mstar{} (on average $+0.25$ dex of \logms{}) for both \rbcg{}
+            and \nbcg{} galaxies (Left panels).
+            Although there are multiple lines of evidence that favor Salpeter 
+            or even more ``bottom-heavy'' IMF in massive galaxies 
+            (e.g.\ \citealt{Conroy2012}; \citealt{Cappellari2012}), we still 
+            present the main results using Chabrier IMF to accommodate galaxies 
+            with lower \mstar{} in the sample, and to be as consistent as possible 
+            with a few previous works.  
+            This choice of IMF does not change the main results qualitatively.
+
+        \item \mstar{} based on the \texttt{BC03} models are systematically lower 
+            than the ones based on \texttt{FSPS+MILES} models (middle panels)
+            The difference shows a large scatter, and can be as large as 0.4 dex,
+            although it does show any \mstar{} dependency. 
+            We notice that the \texttt{BC03} provides better overall ${\chi}^2$. 
+            This could relates to the higher upper limit of stellar metallicity 
+            ($2 \times \mathrm{Z}_{\odot}$) allowed by the \texttt{BC03} model 
+            that help fit the shape of the SED in the red-end better.  
+            However, the \texttt{BC03} model could underestimate the 
+            stellar age for a fraction of massive galaxies ($< 3$--4 Gyrs), and 
+            leads to underestimate of  \m2l{} for them too.
+            It is worth noting that, both \texttt{FSPS} and \texttt{BC03} 
+            models still have difficulties recovering SED at the red-end (between $z$ 
+            and Y-band), and reproducing the optical color-color relations for 
+            red-sequence galaxies (e.g.\ \citealt{MIUSCAT2}).
+            In this work, we decide to keep using the \texttt{FSPS+MILES} model as 
+            the fiducial one.  
+            However, using the results based on \texttt{BC03} model will not 
+            only change the main conclusions here, but also results in more 
+            significant differences in the median \mden{} profiles.
+
+        \item On the right panels of Fig~\ref{fig:ised_3}, we also compare with the
+            SED fitting results without considering the dust extinction. 
+            This choice leads to slightly smaller \mstar{} values as expected. 
+            The impact is very small for the \rbcg{} galaxies, and becomes larger 
+            at the low-\mstar{} end of the \nbcg{} sample. 
+            But it still will not change any of the important results in this work.
+
+    \end{enumerate}
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
+\section{D. Comparison of \mden{} profiles using \mstar{} from the GAMA survey}
+    \label{app:gama}
+
+%% ------------------------------------------------------------------------------------ %% 
+\begin{figure*}
+    \centering
+    \includegraphics[width=\textwidth]{fig/redbcg_prof_gama_new}
+    \caption{
+        \textbf{Left:} comparison of \mstar{} estimated by the GAMA survey and 
+        the \mtot{} using HSC images in this work. 
+        We plot the \logmgama{} against the difference between \logmtot{} and \logmgama{}. 
+        The format is very similar to the left panel of Fig~\ref{fig:smf1}. 
+        The two vertical lines highlight the mass range $11.4 \leq$\logmgama{}$<11.8$ 
+        that is used for the comparison.~~
+        \textbf{Right:} we compare the \mden{} profiles of \rbcg{} (orange-red) and 
+        \nbcg{} (grey-black) galaxies using the samples matched on the 
+        \mgama{}-$z$ plane at $11.4 \leq$\logmgama{}$<11.9$ and $0.28 \leq z < 0.4$. 
+        The format is very similar to the ones in Fig~\ref{fig:prof_1}.}
+    \label{fig:gama}
+\end{figure*}
+%% ------------------------------------------------------------------------------------ %%
+
+    The GAMA survey greatly overlaps with the HSC survey, and it provides carefully 
+    measured \mstar{} for large sample of galaxies (\citealt{Taylor2011}) that help 
+    produce many interesting results (e.g. \citealt{Bauer2013, Ferreras2017}).
+    They use 2-D single-\ser{} model to correct the total luminosity of the galaxy 
+    (\citealt{Kelvin2012}), and derive the \m2l{} through optical-SED fitting 
+    (BC03 model; Chabrier IMF) based on the PSF-matched aperture photometry. 
+    Since the \ser{} model is generally more flexible than the \texttt{cModel} one, 
+    it is therefore interesting to compare with the \rbcg{} and \nbcg{} galaxies 
+    that also have spec-$z$ (at $z < 0.40$) and \mstar{} in GAMA DR2 
+    (\citealt{Liske2015}) and see the impact of deep photometry again.
+
+    We summarize the results in Fig~\ref{fig:gama}.  
+    On the left panel, we compare the differences between \mtot{} and \mgama{}. 
+    HSC survey on average recovers more \mstar{} at high-\mstar{} end, which is 
+    consistent with the expectation from deeper photometry, although the 
+    systematic differences in the estimates of \m2l{} could play a role here. 
+    Meanwhile, it is interesting see that, above \logmtot{}$> 11.8$, \mgama{} 
+    becomes increasingly larger than \mtot{}, and most of these massive 
+    galaxies have very high \ser{} index from the 2-D fitting. 
+    This suggests that the single-\ser{} model is no longer an appropriate one to 
+    describe very massive galaxies as it tends to over-estimate the \mstar{} the 
+    inner and/or outer regions.
+
+    To verify the cause of the difference in \mstar{}, we further select samples 
+    of \rbcg{} and \nbcg{} galaxies with matched \mgama{} and redshift 
+    distributions (at $11.4 <$\logmgama{}$<11.8$; see Appendix \ref{app:match}), 
+    and compare their \mden{} profiles (right panel). 
+    Although these two subsamples are equally massive according to results from 
+    GAMA survey, it is clear that the \rbcg{} galaxy has much more extended 
+    outer envelope, even though its average \mden{} profile is very similar 
+    to the \nbcg{} sample at $< 10$ kpc. 
+    We can reproduce very the same trend with the luminosity density profiles 
+    (with or without $k$-correction), suggesting that the inaccurate \ser{} 
+    model definitely leads to under-estimate of \mstar{}.
+
+%% ------------------------------------------------------------------------------------ %%
+
+\section{E. Comparisons of \mden{} profiles in different redshift bins}
+    \label{app:redshift}
+
+%% ------------------------------------------------------------------------------------ %% 
 \begin{figure}
     \centering 
-    \includegraphics[width=16.5cm]{fig/fig1.png}
+    \includegraphics[width=8.2cm]{fig/redbcg_avg_prof_z}
     \caption{
-   Cartoons that illustrate the basic idea of the proposed method for the
-   estimation of average merger mass ratio.  The style is adopted from Faber\etal (2007).
-   The upper panels show the basic
-   picture of the ``two-phase'' formation scenario. The lower panel describes
-   a general picture for the evolution of massive galaxies on the
-   $M_{\ast}$-color plane.  After massive ETGs were quenched, they quickly
-   moved to the red-sequence, and gradually evolved along it as they are
-   becoming redder due to the aging of stellar population, and more massive due
-   to the accumulation of extended stellar envelope through many minor (dry)
-   mergers.  Since the stellar content of smaller system should have lower
-   metallicity, the outer envelope naturally has a bluer color compared to inner
-   region.  And, such color difference reflects the average mass ratio of all
-   mergers that contribute to the second phase of evolution.  Larger color
-   difference means more stellar material came from smaller galaxies, hence
-   makes minor merger more important.  
+        Comparison of \mden{} profiles of \rbcg{} (orange-red) and \nbcg{} 
+        (grey-black) at $11.6 \le$\logmtot$< 11.9$ in redshift bins of 
+        $0.3\leq z<0.4$ (solid lines) and $0.4\leq z<0.5$ (dash lines). 
+        We show the individual profile in the background using much thinner line, 
+        and highlight the median profiles using thicker line and darker color.
+        Other formats are exactly the same with the left figure of 
+        Fig~\ref{fig:avg_prof}.}
+    \label{fig:avg_prof_z}
+\end{figure}    
+%% ------------------------------------------------------------------------------------ %%
+
+    Given the redshift range for our samples, it is important to evaluate 
+    the impacts from the physical extend of seeing and the imaging depth on the \mden{} 
+    profiles at different redshift. 
+    Under the same seeing, the \mden{} profile of galaxy at higher-$z$ is more 
+    vulnerable to the PSF smearing effect at the center. 
+    It is also harder to reach to the same \mden{} level under the same imaging depth 
+    due to cosmological dimming and background noise.
+
+    In Fig~\ref{fig:avg_prof_z}, we group the \rbcg{} and \nbcg{} galaxies within 
+    $11.6 \le$\logmtot$< 11.9$ into two $z$ bins ($0.3\leq z<0.4$ and $0.4\leq z<0.5$),
+    and compare their \mden{} profiles. 
+    In two redshift bins, the median \mden{} profiles from the same sample follow each 
+    other very well outside 10 kpc, but become visibly different in the central 3-4 kpc,
+    where the effect from seeing kicks in. 
+    Meanwhile, the median \mden{} profiles of \rbcg{} and \nbcg{} in the same $z$ bin 
+    are identical in the central region, which indicates similar average seeing 
+    conditions.       
+    This confirms that \mden{} profile at $> 5$ kpc is safe from the impacts of seeing 
+    and difference in redshift.
+    More importantly, it also suggests that, once the redshift distributions are 
+    carefully matched, the difference of \mden{} profile is likely to be physical 
+    even in the central region.
+
+%% ------------------------------------------------------------------------------------ %%
+
+\section{F. Match the \rbcg{} and \nbcg{} samples in \mstar{} and redshift distributions}
+    \label{app:match}
+
+%% ------------------------------------------------------------------------------------ %% 
+\begin{figure*}
+    \centering 
+    \includegraphics[width=\textwidth]{fig/redbcg_match}
+    \caption{
+        \textbf{Left figure} shows the details of the \mtot{}-matching process, 
+        corresponding to the results shown in the left figure of   
+        On the top panel, we show the overall distributions of \rbcg{} (light orange boxes) 
+        and \nbcg{} (light grey dots) galaxies on the \mtot{}-$z$ plane.  
+        And, we match the two sample in the \mtot{}-$z$ space outlined by the shaded region.
+        We highlight the \rbcg{} galaxies in this region using bigger boxes in red frames, 
+        whose size reflects the $P_{\mathrm{Cen}}$ value.  
+        We also color-code them using the richness ($\lambda$) of the host cluster. 
+        The matched \nbcg{} galaxies are highlighted using darker color and bigger dots. 
+        To further evaluate the matching results, we show the distributions of \mtot{} 
+        (middle panel) and redshift (bottom panel) separately. 
+        On both panesl, we show the histograms along with their kernel density 
+        distributions.  
+        And, on the top of each panel, two sets of short vertical lines highlight the median 
+        value (solid) and the inter-quartile (dash) of each distribution.~~~
+        \textbf{Right figure} shows the similar matching results for the \minn{}-matched
+        samples used for the right figure of Fig~\ref{fig:prof_1}.
+        The format is exactly the same as the left one, except the \minn{} replaces the 
+        \mtot{} in the top and middle panels.}
+    \label{fig:match}
+\end{figure*}
+%% ------------------------------------------------------------------------------------ %%
+
+    As explained earlier, it is important to make sure the two samples have similar 
+    distributions in both \mstar{} and redshift before comparing their average \mden{} 
+    profiles.  
+    Here we briefly describe the procedure used in this work. 
+    Since the \rbcg{} sample is smaller in size, we always match the \nbcg{} sample to 
+    it by searching for the $N$-nearest neighbours on the $M_{\star}$-redshift plane 
+    using the KDTree algorithm in the \texttt{scikit-learn} Python library 
+    (\citealt{scikit-learn}), and evaluate the quality of the match using the 
+    distributions of both parameters (as shown in Fig~\ref{fig:match}).
+
+    As we only keep the unique \nbcg{} galaxies in the matched sample, we manually 
+    adjust the value of $N$ to achieve the best match. 
+    When the redshift distribution of the \rbcg{} sample becomes bi-model, we also try 
+    to split the sample into two redshift bins and match them separately. 
+    Typically $N$ is between 3 to 8.
+    In Fig~\ref{fig:match}, we demonstrate this procedure using the results for 
+    the \mtot{}-matched (Left) and the \minn{}-matched samples in Fig~\ref{fig:prof_1}
+    (Right), and the two samples are well matched in the distributions of \mtot{}
+    (or \minn{}) and redshift.  
+    For all the comparisons of \mden{} profiles in this work, we match the samples 
+    in the same way, and make sure the match has the same quality.
+
+%% ------------------------------------------------------------------------------------ %% 
+\section{G. Robustness of the \mden{} Differences} 
+	\label{app:robust}
+
+    In Fig~\ref{fig:prof_1}, we compare the \mden{} profiles of \mtot{}- and 
+    \minn{}-matched samples of \rbcg{} and \nbcg{} galaxies, and here we test the 
+    robustness of the results using a few extra tests that are illustrated in
+    Fig~\ref{fig:prof_2}, Fig~\ref{fig:prof_3}, and Fig~\ref{fig:prof_4}, and 
+    are briefly described here:
+
+    \begin{enumerate}
+
+        \item In Fig~\ref{fig:prof_2}, we group the samples into two \mtot{} bins. 
+            Given the small sample size, we extend slightly toward lower \mtot{} range 
+            ($11.5 \leq \log (M_{\star,\ 10\mathrm{kpc}}/M_{\odot}) < 11.7$ and 
+             $11.7 \leq \log (M_{\star,\ 10\mathrm{kpc}}/M_{\odot}) < 11.9$). 
+            Although the smaller sample leads to larger statistical uncertainties, 
+            we can still see similar structural differences in both \mtot{} bins, 
+            and the difference becomes more significant in the higher \mtot{} bin.  
+            For the lower \mtot{} bin, the difference in the inner region becomes 
+            quite uncertain, while the difference in the outskirt is still visible. 
+            This potentially suggests that the environmental dependence of structure 
+            also varies with \mstar{}, an important implication deserves more 
+            investigations in the future.
+
+        \item On the left panel of Fig~\ref{fig:prof_3}, we match the \rbcg{} and 
+            \nbcg{} samples in a lower redshift bins ($0.30 < z < 0.42$).
+            Despite the larger uncertainties due to smaller samples, we find the 
+            results are the same.
+
+        \item On the middle panel of Fig~\ref{fig:prof_3}, we includes \rbcg{} 
+            galaxies in poorer clusters ($20 < \lambda < 30$), which should result 
+            in overlapped \mhalo{} distributions with the \nbcg{} samples 
+            considering the typical uncertainty of $\lambda$.
+            This makes the difference in the inner region slightly less significant, 
+            but the overall results are the same.
+
+        \item On the right panel of Fig~\ref{fig:prof_3}, in stead of using \mtot{}, 
+            we use the \mmax{}--the maximum \mstar{} by integrating the \mden{} 
+            profiles to the largest radius allowed.  
+            The \mmax{} values are less reliable than \mtot{} due to the 
+            uncertainty of background subtraction and contamination from nearby 
+            bright objects, but they can serve as different estimates of the ``total''
+            \mstar{} of these galaxies.
+            As shown in Section~\ref{sec:discussion}, they on average increase
+            the \mstar{} by a little bit and affect the \rbcg{} more.
+            The differences in the \mden{} profiles still remain very similar.
+
+    \end{enumerate}
+
+    We also test the robustness of the \mtot{}-matched results using the samples with 
+    only spectroscopic redshift, the samples in the three GAMA fields, and the \rbcg{} 
+    samples without the ones in very massive halos ($\lambda > 40$).  
+    Limited by space, we do not show these results here, but they all verify the 
+    robustness of the results.
+
+    For the results from the \minn{}-matched samples:
+
+    \begin{enumerate}
+
+        \item
+            We match the two samples using both \minn{} and the \mstar{} within 15 kpc 
+            at the same time.  
+            This makes the two median \mden{} profiles very similar inside 10-15 
+            kpc, while the result in the outskirt remains the same (left panel of 
+            Fig~\ref{fig:prof_4}).
+            Use \mstar{} within 5 or 20 kpc leads to the same conclusion.
+
+        \item 
+            To make sure the two samples are comparable in their overall assembly history,
+            we also try to only include the very massive galaxies (\logmtot{}$>11.5$)
+            in both samples. 
+            This excludes the \nbcg{} galaxies that are much less massive and 
+            more ``compact'' in structure. 
+            Yet, the results regarding the structural differences remain the same.
+
+    \end{enumerate}
+
+%% ------------------------------------------------------------------------------------ %% 
+  \begin{figure*}
+      \centering 
+      \includegraphics[width=\textwidth]{fig/redbcg_prof_2}
+      \caption{
+          Comparisons of the \mden{} profiles for \mtot{}-matched \rbcg{} 
+          (orange-red) and \nbcg{} (grey-black) galaxies in lower (left; [11.5,11.70]) 
+          and higher (right; [11.7, 11.9]) \mtot{} bins. 
+          Other formats are in consistent with the right figure of Fig~\ref{fig:prof_1}.
+          The difference in median profiles is more significant in higher \mtot{} bin.
           }
-   \label{figure:1}
-\end{figure}
+      \label{fig:prof_2}
+  \end{figure*}
+%% ------------------------------------------------------------------------------------ %%
 
+%% ------------------------------------------------------------------------------------ %% 
+  \begin{figure*}
+      \centering 
+      \includegraphics[width=\textwidth]{fig/redbcg_prof_3}
+      \caption{
+        Comparisons of the \mden{} profiles for \rbcg{} (orange-red) and \nbcg{} 
+      	(grey-black) galaxies that are matched using proxies of total \mstar{}. 
+        The formats are in consistent with the right figure of Fig~\ref{fig:prof_1}.
+        The differences are, here, the samples are matched in slightly differnt ways. 
+        From left to right: a) using samples at lower redshift ($0.3 < z < 0.4$); 
+        b) using \rbcg{} sample with $\lambda > 20$ instead of 30; 
+        c) using \mstar{} within 150 kpc instead of 100 kpc.
+        The results are broadly consistent with the one in Fig~\ref{fig:prof_1}.
+        }
+      \label{fig:prof_3} 
+  \end{figure*}
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
+  \begin{figure*}
+      \centering 
+      \includegraphics[width=\textwidth]{fig/redbcg_prof_4}
+      \caption{
+          Comparisons of the \mden{} profiles for \rbcg{} (orange-red) and \nbcg{} 
+          (grey-black) galaxies that are matched using the \mstar{} enclosed in the 
+          inner region. 
+          Left panel shows the results after matching the \minn{} and \meff{} together, 
+          and the right panel shows the results when only the \logmtot{}$\ge 11.5$
+          \rbcg{} and \nbcg{} galaxies are included.
+          Other formats are in consistent with the right figure of Fig~\ref{fig:prof_1}.
+          }
+      \label{fig:prof_4} 
+  \end{figure*}
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
+%% Table.1 
+%% ------------------------------------------------------------------------------------ %% 
+%\clearpage
+%\include{table1}
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %%  
+\bsp
+\label{lastpage}
+\end{document}
+%% ------------------------------------------------------------------------------------ %% 
 %%%%%%%%%%%%: End of the File %%%%%%%%%%%%
-
-\end{CJK*}
-
-\clearpage
-
-%%%%%%%%%%%: Possible Tables %%%%%%%%%%%%%
-%\input{table1.tex}
-
-\end{document}
+%% ------------------------------------------------------------------------------------ %%

### 2017-03-14 draft/ms_v2.tex
New draft

@@
 
-    The Subaru Strategic Program (SSP, \addref) makes use of the new prime-focus camera,
-    the Hyper Suprime-Cam (HSC;~\citealt{Miyazaki2012}), on the 8.2-m Subaru telescope at 
-    Mauna Kea. 
+    The Subaru Strategic Program (SSP, \citealt{MiyazakiInPrep}) makes use of the new 
+    prime-focus camera, the Hyper Suprime-Cam (HSC;~\citealt{Miyazaki2012}), on the 
+    8.2-m Subaru telescope at Mauna Kea. 
     The ambitious multi-layer HSC survey takes advantage of the large field of 
@@
 
-The full details of the HSC data processing can be found in \citet{BoschInPrep} and are briefly summarized here. The HSC SSP data are processed with \texttt{hscPipe 4.0.1}, a derivative of the Large 
-    Synoptic Survey Telescope (LSST) pipeline (e.g.\ \citealt{Juric2015}; 
+    The full details of the HSC data processing can be found in \citet{BoschInPrep}
+    and are briefly summarized here. 
+    The HSC SSP data are processed with \texttt{hscPipe 4.0.1}, a derivative of the 
+    Large Synoptic Survey Telescope (LSST) pipeline (e.g.\ \citealt{Juric2015}; 
     \citealt{Axelrod2010}), modified for HSC. 
@@
     (bias subtraction, flat fielding, background modeling, object detection and 
-    measurements). Astrometric and photometric calibration is performed at the single exposure level. \texttt{hscPipe} then warps different exposures on to a common
-    World Coordinate System (WCS) and combines them into coadded images. At this stage, \texttt{hscPipe} updates the images with a better astrometric and 
-    photometric calibration using stars that are common among between exposures.
-
-    The pixel scale of the combined images is $0.168^{\arcsec}$. Photometric calibration is based on data from the Panoramic Survey Telescope 
+    measurements). 
+    Astrometric and photometric calibrations are performed at the single exposure level. 
+    \texttt{hscPipe} then warps different exposures on to a common World Coordinate 
+    System (WCS) and combines them into coadded images. 
+    At this stage, \texttt{hscPipe} updates the images with a better astrometric and 
+    photometric calibration using stars that are common among exposures.
+
+    The pixel scale of the combined images is $0.168^{\arcsec}$. 
+    Photometric calibration is based on data from the Panoramic Survey Telescope 
     and Rapid Response System (Pan-STARRS) 1 imaging survey 
@@
     To achieve consistent deblending and photometry across all bands, \texttt{hscPipe} 
-    performs multi-band post-processing at the coadd level. First, \texttt{hscPipe} performs object detection on coadd images
-    in each band independently and for each source records the flux peak and the above-threshold region (referred as 
-    a ``footprint'').
-Next, ``footprints'' and peaks from different bands are merged together before performing deblending and measurements.
-Finally, \texttt{hscPipe} selects a ``reference band'' for each object based on the
-    $S/N$ in different bands (for most galaxies in this work, the reference band is the $i$-band). 
+    performs multi-band post-processing at the coadd level. 
+    First, \texttt{hscPipe} performs object detection on coadd images in each band 
+    independently and records the flux peak and the above-threshold region 
+    (referred as a ``footprint'') for each source. 
+    Next, ``footprints'' and peaks from different bands are merged together before     
+    performing deblending and measurements. 
+    Finally, \texttt{hscPipe} selects a reference band for each object based on the 
+    $S/N$ in different bands (for most galaxies in this work, the reference band is 
+    the $i$-band). 
     After fixing the centroids, shape, and other non-amplitude parameters of each 
     object in this reference catalog, \texttt{hscPipe} perform forced photometry 
-    on the coadd image in each band. This forced photometry approach is optimized to yield accurate galaxy colors.
-
-    For each galaxy, \texttt{hscPipe} measures a \cmodel{} magnitude using an approach that is similar to SDSS (\ref{}) (Bosch\etal~in prep.~).
-However, as opposed to SDSS, the HSC \cmodel{} is based on forced photometry which means that it can be used to accurately measure both the \textit{fluxes and colors of galaxies}.
-The HSC \cmodel{} algorithm fits the flux distribution of each object using a combination of a de~Vaucouleur and
-    an exponential component and accounts for the PSF. The performance of this algorithm has been testing using synthetic objects (Huang\etal~in prep.~) and 
-    the results indicate that, generally speaking, the HSC \cmodel{} photometry is 
-    accurate down to $i >25.0$ mag.  
-    However, \cmodel{} currently systematically underestimates the total fluxes of massive ETGs with extended stellar distributions.
-This problem indicates an intrinsic limitation of \cmodel{} as it is incapable of
-    modeling profiles with extremely extended outskirts, a problem that is exacerbated at the depth of 
-    the HSC survey.
-In addition, at the depth of the HSC survey, accurate deblending in the vicinity of large ETGs where satellites and background galaxies often blend with the low surface brightness stellar envelope is a challenign problem.
+    on the coadd image in each band. 
+    This forced photometry approach is optimized to yield accurate galaxy colors.
+
+    For each galaxy, \texttt{hscPipe} measures a \cmodel{} magnitude using an approach 
+    that is similar to SDSS (\citealt{BoschInPrep}). 
+    However, as opposed to SDSS, the HSC \cmodel{} is based on forced photometry which 
+    means that it can accurately measure both the \textit{fluxes and colors of galaxies}. 
+    The HSC \cmodel{} algorithm fits the flux distribution of each object using a 
+    combination of a de~Vaucouleur and an exponential component and accounts for the PSF. 
+    The performance of this algorithm has been tested using synthetic objects 
+    (\citealt{SynPipeInPrep}), and the results indicate that, generally speaking, 
+    the HSC \cmodel{} photometry is accurate down to $i >25.0$ mag.  
+    However, \cmodel{} currently systematically underestimates the total fluxes of 
+    massive ETGs with extended stellar distributions. 
+    This is caused by an intrinsic limitation of \cmodel{} as it is incapable of
+    modeling profiles with extremely extended outskirts, a problem that is exacerbated 
+    at the depth of the HSC survey. 
+    In addition, at the depth of the HSC survey, accurate deblending in the vicinity of
+    large ETGs where satellites and background galaxies often blend with the low surface 
+    brightness stellar envelope is a challenging problem. 
     The deblending method implemented by the \texttt{hscPipe} currently tends to 
-    ``over-deblend'' the outskirts of bright galaxies and leads to un under-estimation of the the total flux of massive ETGs (more discussion in 
-    Bosch\etal~in prep.~).
-For these reasons, our results will be based on custom developed code to measure the luminosities and stellar masses of massive galaxies.
-We use the HSC \texttt{hscPipe} photometry for two purposes: 1) to perform a first broad sample selection, and 2) for galaxy colors.
-\alexie{Shouldn't we be using the aperture photometry here ????
-Are we doing teh right thing here??
-Please check.
-Need a simple sanity check to show that the resutls are robust.
-Check using your own color estimates?}.
+    ``over-deblend'' the outskirts of bright galaxies and leads to un 
+    under-estimation of the the total flux of massive ETGs (more discussion in 
+    \citealt{BoschInPrep}).  
+    For these reasons, our results will be based on custom developed code to measure 
+    the luminosities and stellar masses of massive galaxies. 
+    We use the HSC \texttt{hscPipe} photometry for two purposes: 
+    1) to perform a first broad sample selection, and 2) to estimate the average 
+    color of massive galaxies.
 
@@
 
-    \alexie{Try to be more succinct and improve the logical flow in sections 2.3, 2.4, and 2.5. Readers don't care about the process! You should be able to trim these sections.}
-
-    \alexie{We never say anything about Spirals? Are all galaxies in this selection early types? Are there any extra morphology cuts? We need to mention this somewhere.}
-
-    \update{
-    We begin by using a broad luminosity cut to select an initial sample of massive galaxies at $z < 0.5$
-    from the HSC photometric catalog.} Based on Leauthaud\etal~(2016), galaxies with \logms{}$\geq 11.5$ have 
-    $i_{\mathrm{SDSS, cModel}} \leq 21.0$ mag. We therefore select our initla smaple to be brighter than  $i_{\mathrm{HSC, cModel}} \leq 21.5$ 
-    \footnote{We neglect the insignificant differences between the response curves of
-    SDSS-$i$ and HSC-$i$ filters} and also limit our sample to regions that have reached the required depth of the \texttt{WIDE} survey in all 
-    five bands. 
+    We begin by using a broad luminosity cut to select an initial sample of massive 
+    galaxies at $z < 0.5$ from the HSC photometric catalog. 
+    Based on Leauthaud\etal~(2016), galaxies with \logms{}$\geq 11.5$ mostly have 
+    $i_{\mathrm{SDSS, cModel}} \leq 21.0$ mag. 
+    We therefore select our initial sample to be brighter than 
+    $i_{\mathrm{HSC, cModel}} \leq 21.5$\footnote{We neglect the insignificant 
+    differences between the response curves of SDSS-$i$ and HSC-$i$ filters} 
+    and also limit our sample to regions that have reached the required depth of 
+    the \texttt{WIDE} survey in $i$-band.
     %% The SQL search is saved as "sample.sql" 
@@
     After removing objects that have pixels affected by saturation, cosmic-rays, or 
-    other optical artefact \footnote{each criterion removes less than 8\% of the entire
-    sample} \alexie{Actually, 8 percent is not small if we want to condsider the number densities.
-Let's re-evaulate the impact of these cuts for the 16B data with FDFC}.
+    other optical artifacts\footnote{each criterion removes less than 8\% of the 
+    entire sample}
+    %% Alexie: Actually, 8 percent is not small if we want to consider the number 
+    %%         densities. Let's re-evaluate the impact of these cuts for the 16B 
+    %%         data with FDFC}. 
     This sample corresponds to 1760845 galaxies and will be referred as \texttt{hscPho}. 
-
     %% Saved as "dr1_wide_galaxy_hscPho.fits"
 
-    We limit our study to the very high mass end where a majority of galaxies have either a  spectroscopic redshift or a robust 
-    red-sequence photo-$z$ from the \redm{} catalog (see Section \ref{ssec:redmapper}).  
-    We match the \texttt{hscPho} sample with a spec-$z$ catalog 
-    compiled by the HSC team\footnote{It is created by matching HSC objects with all publicly available spectroscopic redshifts (e.g.\ SDSS/BOSS; GAMA).
-The spec-z quality flag from different catalogs
-    are homogenized into a single flag that indicates whether the redshift is secure (\ref{} Cite a paper from the photo team where this is described?).
-Only galaxies with secure spec-$z$s are used in this work \alexie{Ned to be precise here.
-We also use redshifts from redmapper so this statement isn;t quite right}}.
-To ensure reasonable
-    \mstar{}-completeness at the high-\mstar{} end we focus on the redshift range $0.3 \leq z \leq 0.5$. 
+    Here we limit our study to the very high-\mstar{} end where the majority of galaxies 
+    have either a spectroscopic redshift or a robust red-sequence photo-$z$ from the 
+    \redm{} catalog (see Section \ref{ssec:redmapper}).  
+    We match the \texttt{hscPho} sample with a spec-$z$ catalog compiled by the HSC 
+    team\footnote{It is created by matching HSC objects with all publicly available 
+    spectroscopic redshifts (e.g.\ SDSS/BOSS; GAMA). The spec-z quality flag from 
+    different catalogs are homogenized into a single flag that indicates whether the 
+    redshift is secure (\ref{}). 
+    We only consider the ones with secure spec-$z$s during the match}.  
+    To ensure reasonable \mstar{}-completeness at the high-\mstar{} end we focus on
+    the redshift range $0.3 \leq z \leq 0.5$. 
     %% This is catalog: "dr1_specz_use.fits"
 
-        \alexie{Please rewrite the section below.
-It would be better to first say that you further supplements with redmapper redshifts.
-And then simply quote the overall number at the end after making the redshift cut.
-Need to work on logical flow of text!}.
-
-  In addition to the specz-s mentioned above, we also include objects which have a red-sequence photo-$z$ from the \redm{} catalog within the range $0.2 \leq z \leq 0.5$ .........and need to say one sentance about the accuracy of the red sequence redshifts and why this is tolerable for our work
-
-    \rewrite{For objects without external spec-$z$, we match them with the central galaxies 
-    from \redm{} catalog using $2.0^{\arcsec}$ radius. 
+    For objects without external spec-$z$, we match them with the central galaxies 
+    from the \redm{} catalog using $2.0^{\arcsec}$ radius. 
     The matched objects with useful red-sequence photo-$z$ ($z_{\lambda}$) are also 
     included in the final sample of bright galaxies with reliable redshift between 
-    $0.2 \leq z \leq 0.5$
-    (will be referred as \texttt{hscZ}).   From our initial sample, 42696 are at $0.2 \leq z \leq 0.5$.}
+    $0.3 \leq z \leq 0.5$. 
+    Comparing with spec-$z$, the accuracy of the red-sequence photo-$z$ is sufficient 
+    (typical uncertainty $< 0.05$) for the goal of this work.
+    The \redm{} catalog provides additional 133 unique redshifts for massive galaxies 
+    in our sample.
+    %% Estimated from "dr1_redbcg_hsc_sdss_gama_1arcsec.fits"
+
+    In the end, at $0.3 \leq z \leq 0.5$, we gather a sample of 25286 galaxies with 
+    reliable redshift information (will be referred as \texttt{hscZ}).
     %% Saved as "dr1_wide_galaxy_icmodel_21.5.fits"
-
-    The BOSS and SDSS "legacy" LRG samples provide the majority of spec-$z$ for this work. By comparing with the Stripe 82 Massive Galaxy Catalog
-    (\texttt{S82-MGC}; \citealt{Bundy2015}), \citet{Leauthaud2016} have measured the stellar mass completness of the combined BOSS and SDSS samples.
-They estimate that the BOSS spec-$z$ is about 80\% complete at \logms{}$\geq 11.6$ at $0.3 < z < 0.5$.
-The GAMA survey, which partially overlaps with the HSC footprint, supplements our spec-z sample by 14\%.
-\alexie{and redmapper redshifts add another xx percent.} Based on \citet{Taylor2011} (e.g.\ their Fig.~6), at $z\sim 0.3$, the GAMA
+    Among them, the BOSS and SDSS "legacy" LRG samples provide the majority of 
+    spec-$z$. 
+    By comparing with the Stripe 82 Massive Galaxy Catalog
+    (\texttt{S82-MGC}; \citealt{Bundy2015}), \citet{Leauthaud2016} have measured the
+    \mstar{} completeness of the combined BOSS and SDSS samples. 
+    They estimate that the BOSS spec-$z$ is about 80\% complete at \logms{}$\geq 11.6$ 
+    at $0.3 < z < 0.5$. 
+    The GAMA survey, which partially overlaps with the HSC footprints, supplements 
+    our \texttt{hscZ} sample by 14\%. 
+    Based on \citet{Taylor2011} (e.g.\ their Fig.~6), at $z\sim 0.3$, the GAMA 
     sample is 80\% complete down to $10^{10.8}$\msun; but only 80\% complete to 
     $10^{12.0}$\msun at $z\sim 0.5$. 
-We can therfore expect our sample to be roughly stellar-mass complete above \logms{}$\geq 11.5$-$11.6$.
-This question will be addressed more carefully using the overlap region between HSC and the \texttt{S82-MGC} in Section\ref{ssec:s82}.
+    We can therefore expect our sample to be roughly \mstar{}-complete above 
+    \logms{}$\geq 11.5$-$11.6$. 
+    This question will be addressed more carefully using the overlap region between 
+    HSC and the \texttt{S82-MGC} in Section\ref{ssec:s82}.
 
@@
 
-    Our study focuses on galaxies which are located at the center of
-    their dark matter halos. To limit our sample to central galaxies, we use 
-    \texttt{v5.10} of the \redm{}{} cluster 
-    catalog\footnote{See: http://risa.stanford.edu/redmapper/} 
+    Our study focuses on galaxies which are located at the center of their dark matter 
+    halos. 
+    To limit our sample to central galaxies, we use \texttt{v5.10} of the \redm{}{} 
+    cluster catalog\footnote{See: http://risa.stanford.edu/redmapper/} 
     (e.g.\ \citealt{Rykoff2014}; \citealt{Rozo2015b}). 
-    These authors have developed a well-tested red-sequence cluster finder that has been 
-    run on SDSS DR8 (\citealt{SDSSDR8}) photometric data. 
-    For each cluster, the catalog provides a photometric redshift estimate $z_{\lambda}$, 
-    a richness $\lambda$, and identifies the most likely central
-    galaxy (this is the galaxy with the highest central probability value
-    $P_{\mathrm{Cen}}$).
-The \redm{}{} catalog also provides a list of member galaxies for each cluster and associated membership probabilities.
+    These authors have developed a well-tested red-sequence cluster finder that has 
+    been run on SDSS DR8 (\citealt{SDSSDR8}) photometric data. 
+    For each cluster, the catalog provides estimates of photometric redshift 
+    ($z_{\lambda}$) and richness ($\lambda$), and identifies the most likely central
+    galaxy (the galaxy with the highest $P_{\mathrm{Cen}}$ value). 
+    The \redm{}{} catalog also provides a list of member galaxies for each cluster 
+    and associated membership probabilities. 
     Details about the performance of the \redm{}~cluster catalog can be found in 
@@
     \citealt{Simet2016}). 
-    The results of these studies are in good agreement and indicate that clusters 
-    identified by \redm{}~ with $\lambda > 20$ have $\log (M_{200m}/M_{\odot}) \geq 14.0$. 
-    Therefore, the \redm{} catalog helps us group massive central galaxies into samples with different average \mhalo{}.
-\alexie{Here is looks like you are making a cut on pcen.
-But what about galaxies that are not in these clusters?
-You do not have a pcen value!
-So this phrase needs to be rewritten or moved elsewhere.}\rewrite{To select reliable candidates of central galaxies, we only include the ones
-    with high probability of being the central galaxy ($P_{\mathrm{CEN}} \geq 0.7$)}.
-
-    Although the \redm{} catalog provides us a good sample of central galaxies in 
-    massive halos, the typical uncertainty of $\lambda$ estimate is still at the
-    $\sim 5$-10 level.  
-    In addition, due to the depth and resolution of SDSS images, the \redm{} catalog 
+    All these studies consistently found that the \redm{} clusters with $\lambda > 20$ 
+    have $\log (M_{200m}/M_{\odot}) \geq 14.0$.
+    The \redm{} catalog therefore helps us group massive central galaxies into samples 
+    with different average \mhalo{}. 
+    The reliable candidates of central galaxies in the \redm{} clusters 
+    ($P_{\mathrm{CEN}} \geq 0.7$) form a nice sample of massive central galaxies 
+    that live in very massive halos.
+
+    Due to the depth and resolution of the SDSS images, the \redm{} catalog 
     becomes slightly incomplete at lower richness ($\lambda < 40$) at $z > 0.33$. 
-    To reduce the impact of this effect, we will focus on a sample of central galaxies in halos with 
-    $\lambda > 30$. 
-    Based on the calibration of \citet{Simet2016}, the $\lambda \geq 30$ sample should
-    have halo mass ($M_{200m}$) more massive than $10^{14.2} M_{\odot}$. We have checked that none of our results depend on this choice of the $\lambda$ boundary.
+    In addition to that, the typical uncertainty of $\lambda$ estimate ($\sim 5$-10) 
+    can not be ignored. 
+    To ensure the separation in \mhalo{}, here we only focus on the central galaxies of
+    clusters with $\lambda > 30$. 
+    According to \citet{Simet2016}, this $\lambda \geq 30$ sample should have halo mass
+    ($M_{200m}$) more massive than $10^{14.2} M_{\odot}$. 
+    Also, none of the results in this work depend on the choice of the $\lambda$ 
+    limit.
 
@@
 
-%           We compre the \mstar{} volume-density distributions of 
-%      	  \rbcg{} (red) and \nbcg{} (black) galaxies using stellar mass based on 
-%          \mcmodel{} (dash) and \mtot{} (solid) to highlight the increase of \mstar{}
-%          due to different methods.  
-%          Here we also show the volume-density distributions of the \texttt{S82-MGC} 
-%          galaxies (green) to evaluate the \mstar{}-completeness. 
-%          The vertical line highlight \logms{}$=11.6$ before correcting the \mstar{} using
-%          total luminosity from 1-D profile.~~
-
 %% ------------------------------------------------------------------------------------ %%
@@
 
-    \alexie{This section can be synthesized and condensed. Try to be more succinct!}
-
     Based on recent constraints of $M_{\star}$-$M_{\mathrm{Halo}}$ relation 
     (e.g.\ \citealt{Leauthaud2012}, \citealt{Behroozi2013}, \citealt{Kravtsov2014}),
-    the \mhalo{} of \logms{}$ > 11.0$ galaxies has a large scatter at fixed \mstar{}.
-This means that our sample of massive galaxies spans a wide range of halos masses.
-We use the \redm{} catalog to separate our sample into two samples with halos masses above and below \logmh{}$<14.0$ \alexie{14.2 no?}.
+    the massive galaxies in our sample live in halos that span a wide range of 
+    \mhalo{}.
+    With the help of the \redm{} catalog, we can broadly separate our sample into two
+    groups with \logmh{}$<14.0$ and \logmh{}$>14.2$.
 
@@
     We match the \texttt{hscZ} sample with the massive central galaxies of 
-    \redm{} clusters with $\lambda \geq 20$ \alexie{20 or 30... confusing here} and $P_{\mathrm{0.7}} \geq 0.7$ using 
-    $1.0^{\arcsec}$ radius \alexie{mathcing radius not important}.
-
-     \alexie{confusing paragraph.
-The remapper redshift accuracy should be moved to the specz section.
-Why do we care about the number above 0.3?
-I'd remove those kind of details, they just make the reader confused.}
-
-    \rewrite{This step finds 375 matched galaxies at $0.2 \leq z \leq 0.5$ 
-    (among them 282 are at $0.3 \leq z \leq 0.5$).  
-    We will refer these \textbf{central galaxies in more massive halos} as \rbcg{} 
-    sample from now on.
-    A small fraction of \redm{} centrals within the HSC footprints are missing  
+    \redm{} clusters with $\lambda \geq 30$ and $P_{\mathrm{0.7}} \geq 0.7$,
+    and find 164 matched galaxies at $0.3 \leq z \leq 0.5$.
+    We will refer these \textbf{central galaxies in more massive halos} as the 
+    \rbcg{} sample here.
+    A small fraction of \redm{} centrals within the HSC footprints is missing  
     due to severe contamination from optical artifacts or bright stars.
-    Spec-$z$ is not available for 67 (17.9\%) galaxies in the sample, but their 
-    $z_{\lambda}$ should be very accurate (median $|z_{\lambda} - z_{\mathrm{Spec}}|$ is 
-    about 0.01 for the ones with spec-$z$).
-    The median richness ($\lambda$) of these clusters is $\sim 32$, corresponding to 
-    halo mass of $M_{200m}\sim 1.7\times 10^{14} h^{-1} M_{\odot}$. 
-    Among these central galaxies, 222 are in clusters with $\lambda \geq 30$. 
-    When focusing on this subsample, the median richness is $\sim 41$, corresponding 
-    to halos with $M_{200m} \sim 2.2\times 10^{14} h^{-1} M_{\odot}$. 
-    Meanwhile, only 15\% of \rbcg{} sample lives in clusters with $\lambda \geq 50$
-    ($M_{200m} \sim 3.0\times 10^{14} h^{-1} M_{\odot}$).   
-    Therefore, the current \rbcg{} sample is not dominated by very massive clusters 
-    with \mhalo{}$>10^{15} M_{\odot}$.  }
+    The median $\lambda$ of these clusters is $\sim 41$, corresponding to 
+    halo mass of $M_{200m}\sim 2.2\times 10^{14} h^{-1} M_{\odot}$.
+    Among them, only 44 of \rbcg{} sample live in clusters with $\lambda \geq 50$
+    ($M_{200m} \sim 3.0\times 10^{14} h^{-1} M_{\odot}$), so the \rbcg{} sample is 
+    not dominated by extremely massive clusters with \mhalo{}$>10^{15} M_{\odot}$. 
     %% Saved as "dr1_redbcg_use_sed5b.fits"
 
-    \rewrite{Assuming that the \redm{} catalog correctly identifies all halos with 
-    $M_{200m}\sim 1.0\times 10^{14} h^{-1} M_{\odot}$ in the current footprint,
-    the unmatched massive galaxies from the above step should be dominated by central 
-    galaxies of less massive halos and massive satellites galaxies.  
-    \update{
-    To select a purer sample of massive centrals in $M_{200m}<10^{14} h^{-1} M_{\odot}$
-    halos, we identify and remove all galaxies within a cylinder region around the 
-    the central galaxies in \redm{} catalog.
-    We choose to use the $R_{200m}$ as the radius of the cylinder. 
-    For each cluster, we convert the richness estimates into $M_{200m}$ using the 
-    calibration in \citep{Simet2016}, then estimate the $R_{200m}$ using $M_{200m}$
-    and the mass-concentration relation in \citep{Diemer2015}. 
-    For the thickness of the cylinder, we use twice the uncertainty of the photometric 
-    redshift error of each cluster.  
-    At $0.3 < z < 0.5$, such uncertainty is between 0.015 to 0.025, which are more than 
-    enough to exclude cluster member.}}
-    % TODO: The actual number waits to be updated}
-
-    %\alexie{This is a rather strange procedure, I think we need to change it (referee and readers will complain!).
-What we really want to do is to remove any galaxies that have $r<R200$ in projection (from the galaxy with the highest value of Pcen) and remove galaxies within some deltaz of the cluster redshift.
-The cluster redshift is more well determined than the redshift estiamte of any cluster member.
-In short, what we are doing here is cutting out a cylindar arond the most likley BCG.
-The deltaz value can be motivated by the cluster redshift uncertainty from the redmapper papers.
-The only remaining question is then what radius to use around clusters.
-To get that number here is what we need to do.
-1) Start with Eq 12 and Table 3 in Simet et al.
-For each cluster, assign a value of M200m (halo mass defined as 200 time background) to each cluster.
-3) we then need to estimate the cluster radius R200m (or R200b, same thing).
-To do this, we need to use a mass-concentration relation.
-I'm pretty sure there is an easy command to do this in Python using the python package "colossus" by bendikt diemer.
-Download it and see if youc an get it to work.
-If it doens't look obvious after 30 min, I can do it on my end using my own code.
-But good for you to know how to do this.
-We can simply use the mass-concentration realtion from Benedikts work.
-4) Now for every cluster you have R200m.
-And you define the low halo mass central sample as ones that are not within any cylindar around any cluster.
-Sorry, I know this might mean re-doing everything.....let's discuss by Skype if this is a major issue.}
-
-    However, we should note that the \nbcg{} sample at this stage spans a large range
-    in \mstar{}, extending towards \logms{}$<10^{11}$.  
-    Therefore, we should expect contamination from satellites in \logmh{}$< 14.0$ halos
-    at certain degree.  
-    Later, after we update the total \mstar{} of them, we will mainly focus on the 
-    \nbcg{} galaxies at high mass end, especially the ones at \logms{}$ > 11.5$. 
-    Based on observational constraints (e.g. \citealt{vanUitert2016}), we can neglect 
+    To select massive central galaxies in \logmh{}$<14.0$ halos, we identify and 
+    remove all galaxies within a cylinder region around each of the central galaxy of 
+    all \redm{} clusters.
+    We choose to use the $R_{200m}$ as the radius, and twice the uncertainty of the 
+    photometric redshift error as the thickness of the cylinder. 
+    We convert the $\lambda$ into $M_{200m}$ using the calibration in 
+    \citep{Simet2016}, then estimate the $R_{200m}$ with the help of the 
+    mass-concentration relation in \citep{Diemer2015}. 
+    At $0.3 < z < 0.5$, the uncertainty of photo-$z$ is between 0.015 to 0.025, 
+    and is enough to exclude cluster members.
+    After removing galaxies in \redm{} clusters, the rest of the massive galaxies 
+    in our sample should mainly be the central galaxies of halos with \logmh{}$<14.0$,
+    and we will refer these \textbf{central galaxies in less massive halos} as the 
+    \nbcg{} sample.
+    We should note that the \nbcg{} sample at this stage spans a large range in 
+    \mstar{}, and includes contaminations like massive satellites in \logmh{}$< 14.0$ 
+    halos.  
+    Therefore, after we update the total \mstar{} later, we only focus on the 
+    \nbcg{} galaxies at very high-mass end (e.g.~\logms{}$ > 11.5$). 
+    According to recent observation (e.g. \citealt{vanUitert2016}), we can neglect 
     satellite contamination at such high \mstar{} range. 
     %% Saved as "dr1_nonbcg_use_sed5b.fits"
+    % TODO: The actual number waits to be updated}
+
+    % \alexie{This is a rather strange procedure, I think we need to change it 
+    % (referee and readers will complain!). What we really want to do is to remove any
+    % galaxies that have $r<R200$ in projection (from the galaxy with the highest value 
+    % of Pcen) and remove galaxies within some deltaz of the cluster redshift. 
+    % The cluster redshift is more well determined than the redshift estimate of any 
+    % cluster member. 
+    % In short, what we are doing here is cutting out a cylinder around the most likely 
+    % BCG. The deltaz value can be motivated by the cluster redshift uncertainty from 
+    % the redmapper papers. The only remaining question is then what radius to use around
+    % clusters. To get that number here is what we need to do. 
+    % 1) Start with Eq 12 and Table 3 in Simet et al. For each cluster, assign a value 
+    % of M200m (halo mass defined as 200 time background) to each cluster. 
+    % 3) we then need to estimate the cluster radius R200m (or R200b, same thing). 
+    % To do this, we need to use a mass-concentration relation. 
+    % I'm pretty sure there is an easy command to do this in Python using the python 
+    % package "colossus" by bendikt diemer. 
+    % Download it and see if you an get it to work. If it doesn't look obvious after
+    % 30 min, I can do it on my end using my own code. But good for you to know how to 
+    % do this. We can simply use the mass-concentration relation from Benedikts work. 
+    % 4) Now for every cluster you have R200m. And you define the low halo mass central
+    % sample as ones that are not within any cylindar around any cluster. 
+    % Sorry, I know this might mean re-doing everything.....let's discuss by Skype if 
+    % this is a major issue.}
+
+%% ------------------------------------------------------------------------------------ %%
 
@@
 
-    Using $\sim 100$ deg$^2$ of HSC data, we select a large sample
-    of massive central galaxies with reliable redshift information, and broadly separate 
-    them into two groups with different \mhalo{}. The following is a summary of our sample construction.
+    Using $\sim 100$ deg$^2$ of HSC data, we select a large sample of massive central 
+    galaxies with reliable redshift information, and broadly separate them into two 
+    groups with different \mhalo{}. 
+    The following is a summary of our sample construction.
 
@@
             a large sample of bright galaxies with reliable redshift information. 
-        \item \rbcg{} sample: we select a sample of 375 galaxies at $0.2 \leq z \leq 0.5$
-            that are identified as central galaxies in $\lambda > 30$ \redm{} clusters. 
-            The most reliable ones ($P_{\mathrm{Cen}} >0.7$) among 
-            them will represent the central galaxies in very massive halos
-            (\logmh{}$\geq 14.0$). 
+        \item \rbcg{} sample: we select a sample of 164 galaxies at 
+            $0.3 \leq z \leq 0.5$ that are reliably identified as the central galaxies 
+            in $\lambda > 30$ \redm{} clusters. 
+            They represent the central galaxies in very massive halos 
+            (\logmh{}$\geq 14.2$). 
         \item \nbcg{} sample: after excluding all the galaxies that are close to any 
             \redm{} clusters in both radial and redshift directions from the 
-            \texttt{hscZ} sample, we have 29973 bright galaxies at $0.2 \leq z \leq 0.5$.
+            \texttt{hscZ} sample, we have 14661 bright galaxies at 
+            $0.3 \leq z \leq 0.5$.
             With the help of \mstar{} estimates via SED fitting (see Section 
             \ref{ssec:isedfit}), we consider the massive ones among them as the 
-            candidates of central galaxies in halos with \logmh{}$<14.0$.  
+            central galaxies in halos with \logmh{}$<14.0$.  
     \end{itemize}
 
-We now proceed to measure the luminosities and stellar mass profiles for all galaxies in this sample.
-
+    We now proceed to measure the luminosities and stellar mass profiles for 
+    all galaxies in the \rbcg{} and \nbcg{} samples.
 %% ------------------------------------------------------------------------------------ %%
@@
     Compared to the popular two-dimensional model fitting method, the isophote fitting
-    approach is insensitive to the choice of a model (one versus two sersics for example), the number of components, 
-    and the initial guesses of free parameters.
-It is also less affected by uncertainties related to background subtraction.
-This is particularly important for the massive ellipticals in our sample.
-Massive ETGs imaged at the depth of HSC are not well modeled by simple models such as the de~Vaucouleurs model or a single \ser component model.
-These models will fail to simultaneously capture the profile in both the inner and the outter region and these models also cannot account for any radial variations in ellipticity and position angle.
-In principle, massive galaxies can still be described using more complex
-    models (e.g \citealt{Huang2013a}; \citealt{Huang2013b}) but these multi model fits are quite sensitive to the background subtraction.
-For this paper, we opt to for the model independent 1-D approach and we will only study galaxies in the radial range where we are not sensitive to either the PSF ($r<5$ kpc) or the background subtraction ($r>100$ kpc).
-
-    We prepare large $i$-band cut-out images each galaxy in our sample that extend to at least 750 kpc in radius, along with the bad pixel mask, and the 
-    PSF model reconstructed at the central coordinate. These cut-outs include all the visible light of the galaxy while leaving enough space to evaluate the background level. 
-    We choose to use $i$-band images because they have excellent seeing, but also because they trace the stellar distributions of massive 
-    galaxies at $0.3 \leq z \leq 0.5$ reasonably well (the observed i-band corresponds to a rest-frame $g$ or $r$ band), and they suffer less from background uncertainty (because the sky is brighter in z and y).
-The $z$ and Y-bands will be better tracers of \mden{}, but the sky background in these bands
-    is much higher and the seeing is not as good as the i-band.
-
-    For each cut-out, we perform \texttt{SExtractor}-like background estimation and object detection using the \texttt{SEP} Python library.
-Out set up is designed to avoid the ``over-deblending'' problem that exists with \texttt{hscPipe}.
-We use several different backgrounds and $S/N$ thresholds, to identify the footprints of all objects, even those that are very close to the centers of bright galaxies.
+    approach is insensitive to the choice of model (e.g. de~Vaucouleurs or \ser{} 
+    profile), the number of components, and the initial guesses of free parameters. 
+    It is also less affected by the background subtraction uncertainty, which is 
+    particularly important for the massive ellipticals in our sample.
+    Massive ETGs imaged at the depth of HSC are not well modeled by simple models such 
+    as the de~Vaucouleurs model or a single \ser component model. 
+    These models will fail to simultaneously capture the profile in both the inner and 
+    the outer region and these models also cannot account for any radial variations in 
+    ellipticity and position angle. 
+    In principle, massive galaxies can still be described by more complex 
+    models (e.g \citealt{Huang2013a}; \citealt{Huang2013b}), but they are still 
+    sensitive to background subtraction and initial values of parameters. 
+    For this paper, we opt to for the model-independent 1-D approach and we will only 
+    study galaxies in the radial range where we are not sensitive to either the PSF 
+    ($r<3-5$ kpc) or the background subtraction ($r>100$ kpc).
+
+    We prepare large $i$-band cut-out images for each galaxy in our sample that extend 
+    to at least 750 kpc in radius, along with the bad pixel mask, and the PSF model 
+    reconstructed at the central coordinate. 
+    These cut-outs include all visible light of the galaxy while leaving enough space 
+    to evaluate the background level. 
+    We choose to use $i$-band images because they trace the stellar distributions of 
+    massive galaxies at $0.3 \leq z \leq 0.5$ reasonably well 
+    (the observed i-band corresponds to a rest-frame $g$ or $r$ band), but also because 
+    they have better seeing and much lower background level than the images 
+    in $z$ and $Y$ bands that are supposed to be better tracers of \mden{}.
+
+    For each cut-out, we perform \texttt{SExtractor}-like background estimation and 
+    object detection using the \texttt{SEP} Python library. 
+    We design the procedure to avoid the ``over-deblending'' problem that exists in
+    \texttt{hscPipe}. 
+    We use several different backgrounds and $S/N$ thresholds to identify the 
+    footprints of all objects, even those that are very close to the centers of bright 
+    galaxies. 
     We create two masks for the \texttt{Ellipse} procedure. 
-The first mask corresponds to the footprints of neighbouring galaxies.
-At this stage, we create a fiducial mask as well as a more aggresive mask to test for the impact of masking (see Appendix xxxx).
-The second mask is designed to measured the background level and masks out both the central (target) galaxy as well as neighbours.
-After appplying this mask to the cutout, we evalute the background level after smoothing over $6x6$  pixels (see Appendix xxxxx).
-This yields the global sky values over the cutout as well as the uncertainty in the sky.
-Based on the global uncertainty in the sky, at the depth of HSC wide, we should in pinciple be able to measure surface brightness profiles to $\sim 30$ \sb.
-However, in practice, we can only reach $<28.5$ \sb due to the uncertainties in modeling the sky.
+    The first mask corresponds to the footprints of neighboring galaxies. 
+    At this stage, we create a fiducial mask as well as a more aggressive one to test 
+    the impact of masking (see Appendix \ref{app:A}). 
+    The second mask is designed to measured the background level and masks out both 
+    the central (target) galaxy as well as neighbors. 
+    After applying this mask to the cutout, we evaluate the background level after 
+    smoothing the image over $6x6$ pixels (see Appendix \ref{app:A}). 
+    This yields the global sky level as well as the uncertainty in the sky. 
+    Based on the global uncertainty in the sky, at the depth of HSC \texttt{WIDE}, 
+    we should in principle be able to measure surface brightness profiles to $> 29$ \sb
+    in $i$-band.  
+    However, in practice, we can only reach to $<28.5$ \sb due to the often slightly 
+    over-subtracted background around bright objects as indicated by the negative
+    global background value.
+    In \texttt{hscPipe}, the background on each CCD is modeled with a 
+    Chebyshev-polynomial that is fit to the smoothed image after excluding pixels with 
+    $S/N >5$.
+    This algorithm suffers less than the SDSS version (e.g.\ see \citealt{Blanton2011}),
+    but still often creates artifactual truncation or steeper surface brightness profile
+    for low-$z$ massive galaxy. 
+    We attempt to correct the surface brightness profile for this over-subtraction 
+    with the help of a \texttt{SExtractor} background model (see Appendix \ref{app:A}).
 
@@
     %as the average background value around these bright galaxies.
-
-    We find that the global sky values is often slightly negative value indicate that hscpipe typically tends to over-subtract the sky.
-In \texttt{hscPipe}, the background on each CCD is modeled with a
-    Chebyshev-polynomial that is fit to the smoothed image after excluding pixels with $S/N >5$.
-    This algorithm suffer less than the SDSS version (e.g.\ see \citealt{Blanton2011}),
-    but still over-subtract background around very bright object. 
-    For our massive galaxies, such over-subtracted background creates artifactual
-    truncation or steeper surface brightness profile. We attempt to correct for sky for the oversubtraction that results from \texttt{hscPipe} using a method described in Appedix xxx.
 
@@
 
-    Finally, we run \texttt{Ellipse} on the background-corrected cut-out following a similar methodology as \citep{Li2012}.
-In short, we start with a free centroid and shape (ellipticty and position angle) for each isophote.
-We then fix the centroid and then estimate the mean ellipticty and position angles of all isophotes.
-Finally, we extract a 1-D surface brightness profile along the major axis using the mean ellipticy and position angle.
-In practice, we run \texttt{Ellipse} allowing for more sophisticated shapes than a simple ellipse (more ``disky'' or ``boxy'', e.g.\ \citealt{Kormendy2009}).
-Appendix.\ref{app:A} includes more details about the \texttt{Ellipse} procedure.
-We correct these surface brightness profiles for Galactic extinction and
-    cosmological dimming, then integrate them to various radius to get the 
-    luminosity within different physical apertures. Fig.\ref{fig:ellipse} shows an example of the 1-D surface brightness and 
-    ellipticity profile for a massive galaxy at $z\sim0.2$ together with the mask image and a subset of isophotes.
-
     %The 4th Fourier modes are included to fit the isophote better. 
@@
 
-    We find that our 1-D profiles start begin to show unphsical behaviours (truncation or large fluctuations) at surface brightness levels of about $>28.5$ \sb.
+    Finally, we run \texttt{Ellipse} on the background-corrected cut-outs following a 
+    similar methodology as \citep{Li2012}. 
+    In short, we start with free centroid and shape (ellipticity and position angle) for 
+    each isophote, then fix the best-estimated centroid and estimate the mean ellipticity 
+    and position angles of all isophotes.  
+    Finally, we extract a 1-D surface brightness profile along the major axis using the 
+    mean ellipticity and position angle. 
+    In practice, we run \texttt{Ellipse} allowing for more sophisticated shapes than a 
+    simple ellipse (more ``disky'' or ``boxy'', e.g.\ \citealt{Kormendy2009}). 
+    Appendix.\ref{app:A} includes more details about the \texttt{Ellipse} procedure. 
+    We correct these surface brightness profiles for Galactic extinction and cosmological 
+    dimming, then integrate them to various radius to get the luminosity within different 
+    physical apertures. 
+    Fig.\ref{fig:ellipse} shows an example of the 1-D surface brightness and ellipticity 
+    profile for a massive galaxy at $z\sim0.2$ together with the mask image and a subset 
+    of isophotes.
+
+    We find that some of our 1-D profiles begin to show unphysical behaviors (truncation or 
+    large fluctuations) at surface brightness levels of about $>28.5$ \sb. 
     We therefore only consider regions above $<28.5$ \sb. 
-    This conservative choice already allows us to measure light profiles out to $\sim 120$ kpc.
-
-    For physical (e.g.\ late-stage major merger) and unphysical (e.g.\ nearby 
-    foreground galaxy or bright star) reasons, we can not extract reliable 1-D 
-    profiles for small fraction of massive galaxies because their central regions are heavily masked. This is an intrinsic limitation of the 1-D method. 
-    It affects $48/375$ of the\rbcg{} galaxies, and a smaller fraction of \nbcg{} ones. 
-    It is worth noting that this excludes most massive galaxies in major merger 
-    process from the analysis. 
+    This conservative choice already allows us to measure the individual surface 
+    brightness profile out to $100$ kpc.
+
+    For physical (e.g.\ late-stage major merger) and unphysical (e.g.\ nearby foreground 
+    galaxy or bright star) reasons, we can not extract reliable 1-D profiles for a small 
+    fraction of massive galaxies because they are heavily masked out. 
+    This is an intrinsic limitation of the 1-D method. 
+    It affects $18/164$ of the\rbcg{} galaxies, and a smaller fraction of the \nbcg{} 
+    ones. 
+    It is worth noting that this excludes most major-merging massive galaxies. 
     We will come back to them in the future using 2-D modeling method.
-
-%% ------------------------------------------------------------------------------------ %%
-
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
 \section{Stellar Masses and Stellar Mass Density Profiles}
@@
 
-    \alexie{Shold the color gradients stuff go here?? (I don't know.)}
-
+%% ------------------------------------------------------------------------------------ %%         
 \subsection{Mass-to-light ratios from SED Fitting}
@@
 
-    To convert luminosities into stellar mass, we assume that these massive 
-    galaxies can be well described by an average \m2l{}. 
-    This is a reasonable assumption considering that they are ETGs that are dominated by 
+    To convert luminosities into stellar mass, we assume that these massive galaxies 
+    can be well described by an average \m2l{}. 
+    This is a reasonable assumption considering that they are mostly dominated by 
     old stellar populations and are known to have shallow color gradients. 
-    We will further justify this point by measuring their average color profiles in Section xxxxxx
-    \ref{sec:discussion}.
+    We will further justify this point by measuring their average color profiles in 
+    Section \ref{ssec:ell_color}.
 
@@
     Although \cmodel{} tends to underestimate the total flux for bright, extended 
-    objects, it still yields an accurate \emph{average} color 
-    of the galaxy as it is based on forced photomery and also takes the PSF convolution into account
-    (e.g.\ Huang\etal~in prep.~).
+    objects, it can still yield accurate \emph{average} color thanks to the 
+    forced-photometry method that takes the PSF convolution into account
+    (e.g. \citealt{SynPipeInPrep}).
 
@@
     Based on these models, it uses the observed photometry and redshift to compute the 
-    statistical likelihood, and generates the posterior probability distribution (PDF) 
-    functions for each parameter.  
+    statistical likelihood, and generates the posterior probability distribution 
+    functions (PDF) for each parameter.  
     To get the best estimate of a given parameter, \texttt{iSEDFit} ``integrates'' the 
     full PDF over all the other ``nuisance'' parameters.
-    Then, the median value and the 1-$\sigma$ uncertainty are derived based on the marginalized PDF. Please refer to \citet{Moustakas13} for technical details.
-
-%% ------------------------------------------------------------------------------------ %% 
+    Then, the median value and the 1-$\sigma$ uncertainty are derived based on the 
+    marginalized PDF. 
+    Please refer to \citet{Moustakas13} for technical details.
+
     In this work, we derive average \m2l{} using the Flexible Stellar Population 
@@
     \footnote{http://www.iac.es/proyecto/miles/pages/stellar-libraries/miles-library.php}
-    (\citealt{MILES1}, \citealt{MILES2}) stellar library and assuming a \citet{Chabrier2003} 
-    IMF between 0.1 to 100 \msun.
-The star formation history (SFH) is assumed to follow a delayed-$\tau$ model with stochastic star bursts (see Appendix xx).
+    (\citealt{MILES1}, \citealt{MILES2}) stellar library and assuming a 
+    \citet{Chabrier2003} IMF between 0.1 to 100 \msun. 
+    The star formation history (SFH) is assumed to follow a delayed-$\tau$ model with 
+    stochastic star bursts (see Appendix.\ref{app:B}). 
     This SFH is appropriate for massive galaxies at low redshifts 
     (e.g.\ \citealt{Kauffmann2003}). 
-    For stellar metallicity, we assume a flat distribution between 0.004 to 0.03 (the highest value allowed by FSPS). We adopt the \citet{Calzetti2000} extinction law with a order two Gamma 
-    distribution of $A_{V}$ between 0 to 2 magnitude. A majority of our galaxies are red and quiescent and our results are 
+    For stellar metallicity, we assume a flat distribution between 0.004 to 0.03 
+    (the highest value allowed by FSPS). 
+    We adopt the \citet{Calzetti2000} extinction law with a order two Gamma distribution 
+    of $A_{V}$ between 0 to 2 magnitude. 
+    A majority of our galaxies are red and quiescent and our results are 
     not very sensitive to parameters related to the SFH or the internal dust extinction. 
@@
     for Galactic extinction. 
-\cmodel{} only accounts for the statistical error on the flux measurement but does not account for systematic uncertainties in the model-fitting process.
+    \cmodel{} only accounts for the statistical error on the flux measurement but does not 
+    account for systematic uncertainties in the model-fitting process. 
     It therefore underestimates the flux errors of bright galaxies. 
-Based on tests using synthetic objects, we find that the average accuracy of \cmodel{} for bright galaxy is roughly at the 1\% level.
+    Based on tests using synthetic objects, we find that the average accuracy of \cmodel{} 
+    for bright galaxy is roughly at the 1\% level in the $r$, $i$, $z$ bands, and slightly 
+    worse in the $g$ and Y-band. 
     Therefore, we supply \texttt{iSEDFit} with simplified flux errors assuming $S/N = 100$ 
-    for the $riz$ bands, and $S/N = 80$ for the $gY$ bands (on average, images in $gY$ bands are 
-    shallower in depth and/or have higher background noise).  
-    The typical uncertainty of \logms{} is around 0.08-0.10 dex at $M* \sim xxxx$ end. 
+    for the $riz$ bands, and $S/N = 80$ for the $g$Y bands (on average, images in 
+    $gY$ bands are shallower in depth and/or have higher background noise).  
+    The typical uncertainty of \logms{} is around 0.08-0.10 dex at \logms$\sim 11.5$. 
     Please see Appendix.\ref{app:B} for more detailed discussions of the SED fitting
     results.  
-
-    %In Fig.~3, we show an example of SED fitting result. 
-    %\song{Not sure if we need to show one example, but put one here for now.}
-
-%% ------------------------------------------------------------------------------------ %%
-
 %% ------------------------------------------------------------------------------------ %%
@@
       \caption{
-          \update{
           Comparison of the \mden{} profiles for \mtot{}-matched ($11.6<$\logmtot{}$<11.9$) 
@@
           The format is exactly the same with the left one, except that the darker vertical 
-          dash-line now highlights the 10 kpc radius.}
+          dash-line now highlights the 10 kpc radius.
       }
@@
 
+%% ------------------------------------------------------------------------------------ %%        
+    \subsection{Stellar Mass Completeness}
+    \label{ssec:complete}
+
+    With the help of the \texttt{S82-MGC} sample, we briefly discuss the \mstar{} 
+    completeness of this sample. 
+    The \texttt{S82-MGC} sample matches the deeper SDSS photometric data in the 
+    Stripe 82 region (\citealt{Annis2014}) with the near infrared data from the United 
+    Kingdom Infrared Telescope Infrared Deep Sky Survey (UKIDSS; \citealt{Lawrence2007}). 
+    The deeper photometry and better photo-$z$ make the \texttt{S82-MGC} sample complete 
+    to \logms{}$\geq 11.2$ at $z<0.7$ which makes it sufficient to evaluate the 
+    completeness of this sample.
+    There are 20453 \texttt{S82-MGC} galaxies that are also in the \texttt{hscPho} 
+    sample at $0.3 \leq z_{\mathrm{s82}} \leq 0.5$ (referred as \texttt{s82Pho} sample).   
+    We estimate their \mstar{} using the HSC \texttt{cModel} SED in exactly the 
+    same way\footnote{The \mstar{} using HSC photometry shows tight correlation with the 
+    ones based on the \texttt{S82-MGC} SED which includes NIR data from UKIDSS; 
+    \texttt{S82-MGC} also uses \texttt{iSEDFit} with similar assumptions}.  
+    Then we estimate the volume density distributions of the galaxies in \rbcg{}, 
+    \nbcg{}, and \texttt{s82Pho} samples (right panel of Fig.\ref{fig:smf1}) using 
+    rough estimates of the survey areas they occupied \footnote{We estimate the 
+    uncertainties of these distributions via bootstrap resampling}.
+    By comparing the relative shapes of these distributions, we conclude that 
+    our sample of massive galaxies is reasonably complete down to \logms{}$\sim 11.6$
+    at $0.3 \leq z \leq 0.5$. 
+    While the \rbcg{} sample is less affected by completeness thanks to the reliable
+    photo-$z$ from \redm{}, the completeness of the \nbcg{} sample is still limited 
+    by the spec-$z$ samples.
+    Although there is no apparent reason that the incompleteness can bias our 
+    comparison of structure, we will mainly focus on the \rbcg{} and \nbcg{} galaxies 
+    with $11.6 \le$\logmtot{}$\le 11.9$ where their mass distributions overlap the 
+    most and both have good \mstar{} completeness, and will also match the two samples 
+    carefully in \logms{} and redshift distributions.
+    Please see the next section and Appendix.\ref{app:match} for more details.
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
 \subsection{Stellar Mass Density Profiles and Total Stellar Masses}
     \label{ssec:mtotal}
-
-    \alexie{Did not make edits}
 
@@
     And we also derive the $k$-corrected luminosity and colors from the results.
-    In Appendix.\ref{app:B}, we also show the outputs like the average stellar age, 
-    metallicity, and internal dust extinction all behave reasonably for both 
-    samples, but will not use them for further scientific analysis.
-
+    In Appendix.\ref{app:basic}, we briefly summarize the basic statistics of 
+    the \rbcg{} and \nbcg{} samples using the newly derived \mtot{} and \minn{}.
+    We can confirm that both samples follow a similar and very tight ``red-sequence''.
+    We also show the outputs from SED fitting process like the average stellar age, 
+    metallicity, and internal dust extinction in Appendix.\ref{app:B}.
+    Although we do not rely them on scientific analysis, they all behave reasonably for 
+    both samples. 
     As expected, the integration of 1-D profile out to very large radius help 
-    recover more luminosity (stellar mass) compared to the \cmodel{} results. This will shown in Section xx.
+    recover more luminosity (stellar mass) compared to the \cmodel{} results. 
+    We shown in Section \ref{ssec:s82}.
 
@@
     It is well known that massive ETGs have negative optical color gradient which 
-    indicates a gradient of \m2l{} (e.g.\ \citealt{LaBarbera2012}; \citealt{DSouza2015}),
-    but the gradient is smooth and shallow out to a few times of the effective 
-    radius (color gradient at the very outskirt is still not well quantified). 
-    And, for the comparison between the \rbcg{} and \nbcg{} samples, 
-    Our results should remain intact as long as there is no significant
-    differences of color gradient between these two samples.
-    We will discuss this more later, but initial results do suggest a smooth color
-    gradient out to very large radius, and there is no systematic difference in 
-    color gradients of the two samples.  
-    Both suggest that the average \m2l{} approach should work reasonably well for
-    our goals.
-
-    And, we should mention that our approach is in principle very similar to the 
-    one adopted by the GAMA survey (\citealt{Taylor2011}), where they start with 
-    \mstar{} estimated using average \m2l{} from SED fitting results of
-    PSF-matched aperture photometry, and later correct it with better estimate 
-    of total luminosity.  
-    However, the GAMA survey relied on multi-band single-\ser model fitting on 
-    the SDSS images to get total luminosity (\citealt{Kelvin2012}). 
-    It is therefore interesting to compare the \mstar{} (\mgama{} v.s. \mtot{})
-    estimates for galaxies in common, given the differences in data and method. 
-    Please see the Appendix.\ref{app:C} for more details. 
-    In short, we notice systematic differences between the two \mstar{} estimates, 
-    and it is likely that the GAMA models miss fluxes in the stellar halo that 
+    indicates a gradient of \m2l{} (e.g.\ \citealt{LaBarbera2012}; 
+    \citealt{DSouza2015}), but the gradient is shallow and smooth out to a few 
+    times of the effective radius (color gradient at the very outskirt is still 
+    not well quantified). 
+    More importantly, for the comparison between the \rbcg{} and \nbcg{} samples, 
+    our results should remain intact as long as there is no significant
+    differences of average color gradient between these two samples.
+    This is confirmed by our initial results on color gradient, and we will 
+    discuss this more in Section \ref{ssec:ell_color}.
+    Therefore the average \m2l{} approach should work reasonably well for our goals.
+
+    This approach to derive total stellar mass is actually quite similar to the 
+    method adopted by the GAMA survey (\citealt{Taylor2011}).
+    They start with \mstar{} estimated using average \m2l{} from SED fitting 
+    results of PSF-matched aperture photometry, and later correct it with better 
+    estimate of total luminosity from single-\ser model fitting
+    (\citealt{Kelvin2012}). 
+    For galaxies in common with the GAMA survey, we also compare their different 
+    estimates of \mstar{} (\mgama{} v.s. \mtot{}) in Appendix.\ref{app:C},  
+    and notice systematic differences between the two \mstar{} estimates.
+    It is likely that the GAMA models still miss fluxes in the stellar halo that 
     is beyond the depth of SDSS image. 
-
-    \update{In Appendix.\ref{app:basic}, we summarize the basic statistics of 
-    the \rbcg{} and \nbcg{} samples.  In general:}
-
-    %\begin{itemize}
-    %    \item \update{The two samples follow the same, tight ``red-sequence'' 
-    %        defined by $k$-corrected colors.}
-    %    \item \update{The redshift distributions are reasonably similar in 
-    %        $0.3 < z < 0.5$, but the difference can still bias the comparison of
-    %        \mden{} profiles.}
-    %    \item \update{Although their \mtot{} overlaps a lot between 
-    %        $11.6 <$\logmtot{}$< 11.9$, the relative distributions within this 
-    %        bin are still very different.}
-    %    \item \update{The distributions of \minn{} overlaps the most between 
-    %        $11.2 <$\logminn{}$< 11.6$, but the relative distributions also 
-    %        show difference within this \minn{} range.}
-    %\end{itemize}
-
-%% ------------------------------------------------------------------------------------ %%
-
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
 \section{Results}
@@
 
-    \subsection{Stellar Mass Completeness}
-
-    Here we refer to the comparison with Stripe 82 and just say that we are complete to xxx.
-
-    \update{To compare their structural details, we will focus on \rbcg{} and 
-    \nbcg{} galaxies with $11.6 \le$\logmtot{}$\le 11.9$.  
-    Both samples have reasonable completeness in this \mtot{} range
-    (see Fig.\ref{fig:smf1}).
-    In light of the differences in distributions of \mtot{}, \minn{}, and redshift, 
-    we will carefully match these properties between the \rbcg{} and \nbcg{}
-    samples to make sure the comparison is fair and meaningful.  
-    Please see the next section and Appendix.\ref{app:match} for more details.}
-
-    \subsection{Need a title}
+%% ------------------------------------------------------------------------------------ %%     
+    \subsection{Impact of Photometry on Stellar Mass and Stellar Mass Function}
     \label{ssec:s82}
 
-Here we show the luminosty difference and impact on SMF.
-
-We highlight this in the right panel of Fig.\ref{fig:smf1} as we show the 
-    distributions of differences between \mtot{} and \mcmodel{}, and their relations 
-    to the \mtot{}.  
-    For both samples, we see the ``extra mass'' recovered by 1-D photometry 
-    increases with \mtot{}, therefore this improvement impacts the \rbcg{}
-    sample more.  
-    This is basically consistent with the fact that the structure of massive ETGs 
-    depends on its stellar mass in a way that more massive ones tends to be 
-    more extended (e.g.\ \addref).  
-    Apparently, such mass-dependent difference between \mtot{} and \mcmodel{} will 
-    result in difference of the SMF. 
-    \alexie{Discussion!!} As the slope and normalization of SMF at high mass end is very sensitive 
-    to both cosmology and interesting baryonic processes such as AGN feedback
-    (\addref), they are particularly important in constraining the galaxy evolution
-    model, and therefore became the center of some intense arguments (\addref).  
-    Although the jury is still out on this topic, it has become clear that 
-    popular results using SDSS photometry (\addref) underestimate the total 
-    luminosity (stellar mass) of massive ETGs.  
-    However, past works (e.g.\ \addref) often relied on either stacking of 
-    shallow images or the extrapolation of models to investigate this effect. 
-    Using the deep HSC images, we have the potential to answer this question 
-    much better. 
-    Detailed studies of SMF deserves more careful investigations of many 
-    systematic issues (e.g.\ \addref), so we just show the impact of the 
-    ``extra mass'' on the volume density distributions of both samples 
-    (Fig.\ref{fig:smf1}, left panel).  
-    Generally speaking, the stellar mass corrected for total luminosity 
-    shifts the distribution toward the higher mass end, and slightly modify
-    the slope. 
-    People who want to use HSC photometry or other \cmodel{}-like photometry to 
-    study the properties and evolution of SMF should be aware of such effect.
-
-    \rewrite{Given the heterogeneous nature of the redshift resources for these samples, we 
-    further investigate their \mstar{} completeness via comparing with galaxies that are 
-    in common with the \texttt{S82-MGC} sample. 
-    The \texttt{S82-MGC} sample matches the deeper SDSS photometric data in the Stripe 82 
-    region (\citealt{Annis2014}) with the near infrared data from the United Kingdom 
-    Infrared Telescope Infrared Deep Sky Survey (UKIDSS; \citealt{Lawrence2007}). 
-    The deeper photometry and better photo-$z$ make the \texttt{S82-MGC} sample complete 
-    to \logms{}$\geq 11.2$ at $z<0.7$.}
-
-    \rewrite{The match between the \texttt{hscPho} sample and the \texttt{S82-MGC} one results in 
-    20453 galaxies at $0.3 \leq z \leq 0.5$ (referred as \texttt{s82Pho} sample).  
-    We estimate their \mstar{} using \texttt{cModel} SED in exactly the same way. 
-    The \mstar{} using HSC photometry shows tight correlation with ones based on the
-    \texttt{S82-MGC} SED (five optical bands from SDSS and NIR data from UKIDSS; and 
-    \texttt{S82-MGC} also used \texttt{iSEDFit} under slightly different assumptions).  
-    Then we estimate the volume densities distributions of galaxies in \rbcg{}, \nbcg{}, 
-    and \texttt{s82Pho} samples (left panel of Fig.\ref{fig:smf1}) using rough estimates 
-    of the survey areas they occupied (since we only care about the relative shapes of 
-    the density distributions). 
-    And, we estimate the uncertanties of these distributions using a 10000 times 
-    bootstrap resampling. 
-    The distribution of \nbcg{} sample starts to deviates from the \texttt{s82Pho} one 
-    below \logms{}$< 11.6$, indicating that the sample starts to become incomplete within
-    $0.3 \leq z \leq 0.5$. 
-    As for the \rbcg{} sample, their mass completeness should be better thanks to the 
-    reliable \redm{} $z_{\lambda}$. 
-    Its behaviour is quite consistent with the mass function of galaxies in massive 
-    halos with a narrow \mhalo{} distribution (\addref).   
-    Later, we will see that the \cmodel{} photometry on average underestimate the 
-    \mstar{} of galaxies with \logms{}$>11.5$ by $-0.1$ dex.
-    Therefore, we conclude that the \nbcg{} becomes not perfectly complete below 
-    \logms{}$< 11.7$.  
-    This is most likely due to the incompleteness of the BOSS spec-$z$ sample. 
-    Although it is unlikely that the incompleteness will bias the results of our 
-    comparisons, we will bear this in mind, and match the two samples carefully in 
-    \logms{} and redshift space before comparing them}.
-
+    As mentioned above, different methods lead to different estimates of ``total'' 
+    \mstar{} and impacts important statistics like the stellar mass function 
+    (e.g. \addref{}).
+    We highlight this in the left panel of Fig.\ref{fig:smf1} by plotting 
+    the \mtot{} from 1-D analysis with the differences between \mtot{} and \mcmodel{}.
+    Apparently, our careful 1-D approach recovers more flux in massive galaxies 
+    than the \texttt{cModel} method. 
+    More importantly, the average difference steadily increases with \mtot{}. 
+    At \logms$>11.5$, the difference is often larger than 0.2 dex.  
+    This difference relates to the intrinsic limitation of the \texttt{cModel} 
+    method and also reflects the fact that more massive ETGs tend to have more 
+    extended stellar mass distributions (e.g.\ \addref{}).
+
+    Such mass-dependent difference will clearly result in difference of the SMF, 
+    especially at the very high-mass end where the slope is quite uncertain under
+    current constraints (e.g. \ \addref{}).
+    Although the careful evaluation of the SMF is beyond the scope of this work, 
+    we still highlight the impacts of different definitions of ``total \mstar{}''
+    on the volume density distributions of both samples (Fig.\ref{fig:smf1}, 
+    right panel).  
+    Generally speaking, the use of \mtot{} from 1-D analysis instead of the
+    \mcmodel{} shifts the distributions toward the higher-mass end, and slightly 
+    modifies the slope.
+    This impact is more obvious for the \rbcg{} samples.
+    For studies about the SMF or other aspects of galaxy evolution based on 
+    \cmodel{}-like photometry or shallower images, these impacts should be 
+    cautiously taken into consideration.
+
+    % Put to discussion:
+    % As the slope and normalization of SMF at high mass end is very sensitive 
+    % to both cosmology and interesting baryonic processes such as AGN feedback
+    % (\addref), they are particularly important in constraining the galaxy evolution
+    % model, and therefore became the center of some intense arguments (\addref).  
+    % Although the jury is still out on this topic, it has become clear that 
+    % popular results using SDSS photometry (\addref) underestimate the total 
+    % luminosity (stellar mass) of massive ETGs.  
+    % However, past works (e.g.\ \addref) often relied on either stacking of 
+    % shallow images or the extrapolation of models to investigate this effect. 
+    % Using the deep HSC images, we have the potential to answer this question 
+    % much better. 
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %%      
 \subsection{Surface Mass Density Profiles}
@@
 
-\subsubsection{Mass Dependent Profiles}
+%% ------------------------------------------------------------------------------------ %%      
+\subsubsection{Mass Dependence of \mden{} Profiles}
     \label{sssec:sbp_inter}
 
-    As discussed earlier, although the mass-size scaling relation has been intensively 
-    discussed when it comes to the topic of environmental dependence of structure, 
-    it may not be the best tool to investigate this problem.    
-    Compared to the simple scaling relation, the detailed stellar mass density profiles 
-    contain much richer structural details that can help us diagnose the role played by 
-    different physical processes, including the environmental effect.
-
-    \alexie{dont conceptually separate into two samples at this stage,}
-
-    \update{
-    Before dive into more details, we first show the average \mden{} of massive galaxies 
-    at $0.3 < z < 0.5$ in three \mtot{} bins after mixing the \rbcg{} and \nbcg{} 
-    samples together\footnote{Knowing that the two samples have different levels of 
-    completeness, here we simply mean to show the general properties of massive galaxies.
-    In the first two \mtot{} bins, the \nbcg{} galaxies dominate the number; while in
-    the highest \mtot{} bin, the two samples have roughly the same size.}.   
-    For \mden{} profiles in each \mtot{} bin, we derive the median profile along with its 
-    uncertainty using bootstrap resampling method (5000 times). 
-    As one can see in the left panel of Fig.\ref{fig:avg_prof}, we can comfortably trace 
-    the \mstar{} distribution of these massive galaxies out to 100 kpc \alexie{or 120??? Make the same numbers everywhere.}
-    \textbf{individually}, which gives us huge advantage in studying the statistical 
-    properties of their outer envelopes. 
-    We can see that the higher \mtot{} shifts the median \mden{} profile up a little bit 
-    in the inner region, but makes the outskirt significantly more prominent. 
-    Most of these very massive galaxies ($\ge 10^{11.4} M_{\odot}$) should be 
-    slow-rotating (e.g.\ \citealt{Cappellari13b}) giant ellipticals with ``boxy'' inner 
-    isophotal shape (e.g.\ \citealt{Kormendy2009}), and slightly flattened \mden{} profile 
-    around the center (e.g.\ \citealt{Lauer07}).
-    But their structures in the outskirt clearly does \textbf{NOT} response to the 
-    increase of ``total'' stellar mass in a self-similar way.}
-
-    \alexie{Sounds more like Discussion section} In principe, this is consistent with result from HST observations of BCGs at 
-    $0.3 < z <0.9$ (\citealt{Bai2014}) and the claimed positive correlation between 
-    luminosity and \ser index (e.g.\ \citealt{Savorgnan13})\footnote{But it does not mean 
-    such high \ser index model works well for massive ETGs as they fail at the inner-most 
-    region dramatically, and can not explain the radial variation of isophotal shape}; 
-    it is also consistent with the picture that more massive ETGs experienced more recent 
-    (minor) mergers.
-
-    %At the same time, such behaviour should make us very cautious about 
-    %any indication of ``environmental dependence of structure'' as it 
-    %may be degenerate with difference caused by stellar mass when the 
-    %two samples are not perfectly matched in mass.  
-    %This is exactly what we see in the median profiles of \rbcg{}
-    %and \nbcg{} in the same mass bins. 
-    %Although the comparison shows that \rbcg{} shows much more 
-    %extended outer envelope than \nbcg{}, the very similar profile
-    %in the inner $\sim 10$ kpc reveals that this is dominated by the 
-    %different mass distributions in two samples.
+    Comparing to the much discussed scaling relation like the mass-size relation, 
+    the \mden{} profiles contain more structural details that can help us diagnose the 
+    roles of different physical processes, including the environmental effect.  
+    We first mix the \rbcg{} and \nbcg{} together, and show how the average \mden{}
+    profiles of massive galaxies at $0.3 < z < 0.5$ depend on stellar mass using their 
+    median \mden{} profiles\footnote{The median profiles along with their uncertainties 
+    using bootstrap resampling method} in three \mtot{} bins \footnote{Here we ignore a 
+    small population of massive satellite in \redm{} clusters we excluded from our 
+    sample.
+    The sample is clearly not complete in the lowest \mtot{} bin, but its median \mden{}
+    profile is still useful to show the overall trend and to compare with previous 
+    observations}.
+
+    As shown in the left panel of Fig.\ref{fig:avg_prof}, we can comfortably trace 
+    the \mden{} profiles of these massive galaxies out to 100 kpc \textbf{individually}, 
+    which greatly help us study the statistical properties of their outer envelopes. 
+    These median \mden{} profiles have very moderate differences in the inner region, 
+    but show significant differences in the outskirts as more massive galaxies have 
+    much more prominent stellar envelopes.
+    Most of these massive galaxies ($\ge 10^{11.4} M_{\odot}$) are slow-rotating 
+    (e.g.\ \citealt{Cappellari13b}) giant ellipticals with ``boxy'' inner isophotal 
+    shape (e.g.\ \citealt{Kormendy2009}), and slightly flattened \mden{} profile close 
+    to the center (e.g.\ \citealt{Lauer07}).
+    But their structures in the outskirt clearly do \textbf{NOT} response to the 
+    increase of stellar mass in a self-similar way.
+
+    The \mden{} profile of massive galaxy out to such large radius was only available 
+    through image stacking technique (e.g. \citep{Tal2011, DSouza2015}) 
+    that suffers from several systematic issues.
+    Although most \mden{} profiles extend beyond 100 kpc, many of them show signs of 
+    unphysical truncation and fluctuation related to inaccurate sky subtraction.  
+    Therefore, we exclude the profiles outside 100 kpc, even though the median \mden{} 
+    profiles for the two more massive bins behave reasonably out to $\sim 200$ kpc.
+
+    %% Todo: Move to discussion  
+    % In principe, this is consistent with result from HST observations of BCGs at 
+    % $0.3 < z <0.9$ (\citealt{Bai2014}) and the claimed positive correlation between 
+    % luminosity and \ser index (e.g.\ \citealt{Savorgnan13})\footnote{But it does not mean 
+    % such high \ser index model works well for massive ETGs as they fail at the inner-most 
+    % region dramatically, and can not explain the radial variation of isophotal shape}; 
+    % it is also consistent with the picture that more massive ETGs experienced more recent 
+    % (minor) mergers.
 
@@
     a few past works.  
-    \citep{Huang2013a}, derived the median \mden{} profile for a small sample of very nearby 
-    ellipticals from the Carnegie-Irvine Galaxy Survey (CGS, \citealt{CGS1}).
-    Individual profile and total luminosity were derived from three-component 2-D models 
-    that describe both very inner and outer luminosity distributions of these galaxies 
-    accurately. 
-    The average stellar mass of this sample is around $10^{11.3} M_{\odot}$.
-    Due to the proximity of this sample ($< 100$ Mpc), the average profile is unaffected by 
-    seeing within $\sim 1$ kpc.
-    Most galaxies of the CGS sample are not in any cluster.
-    The median profile qualitatively agrees with the median profile in the lowest 
-    \mtot{} bin, especially in the inner region. 
-    Outside the inner 15 kpc, the CGS median profile shows a slightly more prominent 
-    outer envelope.  
-    While this could simply be due to the small size of the CGS sample ($\sim 30$),
-    interestingly, it is also consistent with the expectation if the mild mass growth 
-    from $z\sim 0.4$ to $z=0$ mostly happened in the outskirt.   
-    The CGS images are already slightly deeper than SDSS images in $r$-band,
-    however, the median profile can only reach to $\sim 50$ kpc (with much larger 
-    uncertainty compared to this work) for ETGs within $\sim 100$ Mpc.
-    Such comparison clearly highlights the improvement made by the deep HSC images as 
-    individual profile of $z\sim 0.5$ galaxy is reliable out to at least 100 kpc.
-
-%% ------------------------------------------------------------------------------------ %% 
-  \begin{figure*}[t]
-      \centering 
-      \includegraphics[width=\textwidth]{fig/redbcg_prof_2}
-      \caption{\alexie{Remvoe or move to Appendix} Comparisons of the \mden{} profiles for \mtot{}-matched \rbcg{} 
-          (orange-red) and \nbcg{} (grey-black) galaxies in lower (left; [11.5,11.70]) 
-          and higher (right; [11.7, 11.9]) \mtot{} bins. 
-          Other formats are in consistent with the right figure of Fig.\ref{fig:prof_1}.
-          The difference in median profiles is more significant in higher \mtot{} bin.}
-      \label{fig:prof_2}
-  \end{figure*}
-%% ------------------------------------------------------------------------------------ %%
-
-    \citet{Patel2013} extracted the median \mden{} profile of massive ETGs in a similar 
-    redshift range with this work ($0.25 < z < 0.50$) using the stacked \textit{HST}/ACS
-    images. 
+    \citep{Huang2013a}, derived the median \mden{} profile for a small sample of very 
+    nearby ellipticals (within 100 Mpc; median \logms{}$\sim 11.3$ based on shallower 
+    images) from the Carnegie-Irvine Galaxy Survey (CGS, \citealt{CGS1}) that are not 
+    affected by seeing until $r < 1$ kpc.
+    This median \mden{} profile qualitatively agrees with the one for the lowest 
+    \mtot{} bin in the inner region, but shows a slightly more prominent outer 
+    envelope at $r > 15$ kpc. 
+    While the small sample size of the CGS sample ($\sim 30$) and differences in the
+    measurements of \mstar{} could explain this difference, it is also interestingly 
+    consistent with mild mass assembly from $z\sim 0.4$ to $z=0$ in the outskirt.   
+    The CGS images are already deeper than SDSS images in $r$-band, but the median 
+    profile still only reaches to $\sim 50$ kpc for $z\sim 0$ massive galaxies.
+    Meanwhile, the deep HSC images can reliably deliver individual \mden{} profiles 
+    for $z\sim 0.4$ galaxy out to at least 100 kpc.
+
+    \citet{Patel2013} extracted the median \mden{} profile of massive ETGs at 
+    $0.25 < z < 0.50$ using the stacked \textit{HST}/ACS images. 
     These galaxies are selected at a constant cumulative number density that makes them  
@@
     The median \mstar{} is $\sim 10^{11.2} M_{\odot}$ according to their estimates.  
-    However, given the shallower depth of the ACS images and the usage of the BC03 model 
-    (each could cause -0.1 dex mass offset compared to this work), this sample should be 
-    comparable to the galaxies in the lowest \mtot{} bin, and the comparison of their 
-    median profiles does reflect that.  
+    However, once the differences in imaging depth and assumptions in SED fitting method
+    are considered, it is reasonable to assume they are comparable to our galaxies in 
+    the lowest \mtot{} bin, and the comparison of \mden{} profiles does confirm that.
     Moreover, the superb resolution of the \textit{HST}/ACS image makes the \mden{} 
-    profile unaffected by PSF even within inner 1 kpc, hence the comparison illustrates 
-    that the HSC profiles within our redshift range are indeed not bothered by 
-    seeing outside the shaded region, and \minn{} should be very reliable.
-    In fact, even \mstar{} within 5 kpc should be available for comparison.
-
-    Besides these observations, we also compare with the predicted average \mden{} 
-    profile of central galaxies in very massive halos 
-    ($13.5 < \log M_{200,c} < 14.0$) from cosmological simulation (\citealt{Cooper13}). 
-    This is achieved by combining the detailed assembly information of halos from the 
-    dark-matter-only simulation with semi-analytic model and particle-tagging technique 
-    (\citealt{Cooper10}).
-    Although the physical resolution and detailed baryonic processes are not as 
-    ``realistic'' as state-of-art hydro-simulation, it is very efficient in providing 
-    rough stellar mass distributions in a large sample of massive halos. 
-    Without any adjustment, the profile is already quite similar to the median \mden{}
-    profile of galaxies in the $11.6 <$\logmtot{}$< 11.8$ bin within 30-40 kpc. 
-    But the simulation seems to predict too significant envelope at larger radius for 
-    this average halo mass. 
-    Although we will not dig into the detailed causes of such differences, it already 
-    highlights that the comparison between deep \mden{} profiles from observations 
-    and the predicted ones in simulations can be very interesting, especially in the 
-    outskirt that was rarely discussed using previous data.
-
-    We summarize the median profiles in Fig.\ref{fig:avg_prof} in Table.~1,
+    profile unaffected by PSF even within inner 1 kpc.
+    Therefore, the comparison illustrates that the HSC profiles within our redshift
+    range are indeed not bothered by seeing at $r > 3$ kpc, which also ensure the
+    accuracy of the \minn{} estimates.
+
+    We also compare with the predicted average \mden{} profile of central galaxies in 
+    massive halos ($13.5 < \log M_{200,c} < 14.0$) from cosmological simulation
+    (\citealt{Cooper13}) using the particle-tagging technique (\citealt{Cooper10}).
+    Despite the poorer resolution, its \mden{} profile is already quite similar to 
+    the median \mden{} profile for the $11.6 <$\logmtot{}$< 11.8$ bin within 40 kpc. 
+    However, comparing with observation, this simulation predicts stellar envelope that
+    is too prominent at this halo mass.
+    Result like this demonstrates that comparisons between observations and simulations
+    using \mden{} profiles have the potential to not only help us make simulation
+    more realistic, but also help us investigate the physical causes of the observed
+    \mstar{} and environmental dependences of structures.
+
+    We summarize these median profiles in Fig.\ref{fig:avg_prof} in Table.~1,
     and all the above median profiles are available  
     \href{https://github.com/dr-guangtou/hsc_cenHighMh/tree/master/profiles}{here}.
-
-%% ------------------------------------------------------------------------------------ %%
-
-\subsubsection{Environmental dependence}
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
+\subsubsection{Environmental Dependence of the \mden{} Profiles}
     \label{sssec:sbp_mtot}
 
-\alexie{Merge the two following into ONE section. AND cut it down by half. Sythetisoize.}
-
-    \update{
-    We show the results of the comparison in Fig.\ref{fig:prof_1} after 
-    carefully matching the \nbcg{} sample with larger size to the \rbcg{} samples 
-    within $0.3 < z < 0.5$ and $11.6 < $\logmtot{}$<11.9$ vial searching for the $N$ 
-    nearest neighbours on the $M_{\star}$-redshift plane using the KDTree algorithm. 
-    The details of the procedure and the evaluation of the matching quality can be 
-    found in Appendix.\ref{app:match} (see Fig.\ref{fig:match}.
-    Here, we choose to use the \mstar{} within 100 kpc as a proxy of the ``total''
-    stellar mass.  
-    This choice reflects the radius range of the \mden{} profile that we can safely 
-    measure in a model independent manner given the current depth of the image and 
-    the accuracy of sky background subtraction.
-    For galaxies with $11.6 < $\logmtot{}$<11.9$, 100 kpc equals to 5-8 times of their 
-    effective radius, hence should enclose most their \mstar{}.
-    %Also, for a small fraction of massive \rbcg{} galaxies that are from rich clusters, 
-    %the intra-group/cluster light (IGL/ICL) could contribute a lot to the observed 
-    %\mden{} profile, and complicate the comparison with the \nbcg{} galaxies.  
-    %We will discuss these issues in more details in Section \ref{sec:discussion}.
-    In summary, given the typical uncertainty of stellar mass, the two samples are well 
-    matched in \mtot{}; and their redshift distributions are broadly consistent with 
-    each other, hence we can perform meaning comparison of their average structures at 
-    ``fixed stellar mass'' (median \logmtot{}$\sim 11.74$).    
-    We also check their distributions of $k$-corrected colors ($g-r$), and confirm 
-    that they have similar color distributions as well.
-    }
-
+    Finally, we will look into the environmental dependence of structures in massive 
+    galaxies using the \mden{} profiles of the \rbcg{} and \nbcg{} samples that are 
+    carefully matched in \mstar{} and redshift using KDTree algorithm. 
+    We discuss the details and quality of the matching procedure in 
+    Appendix.\ref{app:match} (see Fig.\ref{fig:match}. 
+    The matched redshift distributions within $0.3 < z < 0.5$ ensures the \mden{} 
+    profiles from both samples are impacted by seeing and background at similar level. 
+    As for the \mstar{}, we choose to match using two physically meaning definitions.
+
+    \begin{itemize}
+        \item \mtot{} as the proxy of the ``total'' \mstar{} that include the stellar 
+            envelope.  As mentioned earlier, we match the two samples within 
+            $11.6 < $\logmtot{}$<11.9$ (median \logmtot{}$\sim 11.74$).
             For the 45 \rbcg{} galaxies, we have 229 unique \nbcg{} galaxies in the 
             matched sample.
-    \update{
-    On the left side of Fig.\ref{fig:prof_1}, we plot the individual \mden{} profile 
-    of \rbcg{} and \nbcg{} galaxies along with the median profiles of both samples.
-    The uncertainties of the median profiles are derived using 5000 times of 
-    bootstrap resampling.
-    The \mden{} profile out to such large radius was only available for large sample of 
-    massive galaxies through image stacking method (e.g. \citep{Tal2011, DSouza2015}) 
-    which suffers from certain systematic issues.}
-    Although the \mden{} profiles of many galaxies extend well beyond the 100 kpc radius, 
-    we notice that some profiles show sign of unphysical truncation that is caused 
-    by inaccurate background subtraction.  
-    Therefore, we will not include profiles outside 100 kpc in the comparison, even 
-    though the median profiles within 200 kpc still behave normally.
-
-    Once we match the distributions of \mtot{}, the \mden{} profiles of massive 
-    galaxies in the \rbcg{} and \nbcg{} samples \textbf{greatly overlap with each 
-    other over the entire radius range}. 
-    At fixed ``total'' stellar mass, massive central galaxies in more massive 
-    halos do not form a unique population comparing to the ones from less massive 
-    halos in term of their radial \mstar{} distributions. 
-    \update{
-    This partially explains why the previous works have trouble finding any clear 
-    environmental dependence of structure.}
-
-    At the same time, thanks to the high-quality individual profile from HSC image, 
-    we can also spot interesting differences in the median profiles of the 
-    \mtot{}-matched \rbcg{} and \nbcg{} samples.  
-    In details, it seems that the central galaxies in more massive halos tend to 
-    have slightly flattened inner \mden{} profiles while also possess more significant 
-    outer stellar envelope.   
-    To highlight such subtle structural features, we show the difference between 
-    the two median profiles and its uncertainty in the bottom panel. 
+            Within this \mtot{} range, 100 kpc equals to 5-8 times of the effective 
+            radius, so should enclose most their \mstar{}. 
+            In practice, this choice also reflects the radius range that we can safely 
+            measure \mden{} profile given the depth of the image and the accuracy of 
+            background subtraction.
+
+        \item \minn{} as the proxy of the \mstar{} of the ``in-situ'' component.
+            This is motivated and supported by recent observations and simulations, 
+            and we will discuss more about this assumption in 
+            Section~\ref{sec:discussion}.
+            We match the two samples within $11.2 < $\logminn{}$ < 11.6$ 
+            (median \logminn{}$\sim 11.36$).
+            For 56 galaxies in this \rbcg{} sample, we achieve excellent matches
+            using 375 \nbcg{} galaxies.
+    \end{itemize}
+
+    We show the comparison of the \mtot{}-matched (\minn{}-matched) samples in the 
+    left (right) panel of Fig.\ref{fig:prof_1}.
+
+    For the \mtot{}-matched comparison, it is easy to see that the \mden{}
+    profiles of \rbcg{} and \nbcg{} galaxies \textbf{greatly overlap with each 
+    other over the entire radius range}, which partially explains the difficulties in 
+    confirming any environmental dependence of structure in earlier works.
+    Although the central galaxies from more massive halos do not form a unique 
+    population in term of their structures comparing with the ones in less massive
+    halos at similar \mtot{}, we can still spot interesting differences in their 
+    median profiles: the \rbcg{} galaxy on average has slightly more flattened inner 
+    profile and more significant outer stellar envelope than the \nbcg{} one.
+    We highlight these subtle differences in the bottom panel using the difference 
+    between the two median profiles and its uncertainty. 
     Given the noticeable uncertainties of \mtot{} and $\lambda$, along with the 
     small size of the current \rbcg{} sample, we perform statistical test to confirm 
-    the robustness of the result: we mix the $N_{\mathrm{r}}$ \rbcg{} galaxies and 
-    the $N_{\mathrm{n}}$ \mtot{}-matched \nbcg{} ones together, then randomly draw 
-    $N_{\mathrm{r}}$ galaxies with putting-back, compute the difference between the 
-    median profile of this sample and the \nbcg{} sample. 
-    \update{
+    the robustness of the result \footnote{We mix the $N_{\mathrm{r}}$ \rbcg{} 
+    galaxies and the $N_{\mathrm{n}}$ \mtot{}-matched \nbcg{} ones together, then 
+    randomly draw $N_{\mathrm{r}}$ galaxies with putting-back, compute the difference 
+    between the median profile of this sample and the \nbcg{} sample. 
     After repeating this process 2000 times, we can evaluate the possibility that 
     the systematic differences in median \mden{} profiles can be reproduced by random 
-    selection of massive galaxies.
-    Comparing with the statistical distributions of the differential profiles from 
-    this test (grey shaded region), we can now conclude that the structural 
-    differences between \rbcg{} and \nbcg{} samples are significant.}
-    Apparently, the ``transition radius'' where the median profiles of \rbcg{} 
-    and \nbcg{} sample have the same \mden{} is $\sim 15$-20 kpc, which is quite 
-    close to the expected $R_{\mathrm{e}}$ of ETGs at this \mtot{} (please see 
-    next section for details).
-
-    To further test the robustness of this interesting result, we apply the above 
-    procedures to \mtot{}-matched samples with slightly different definitions.  
-    The results are shown in Fig.\ref{fig:prof_3} in Appendix.\ref{app:robust}: 
-    (a). At higher redshift, the profile is affected more by the seeing at inner 
-    region, and by the imaging depth in the outskirt.  
-    Therefore, we compare the matched \rbcg{} and \nbcg{} samples within 
-    $0.3 \leq z < 0.4$, and the results are very similar.
-    (b). We also make the comparison using a \rbcg{} sample with lower average 
-    halo mass ($\lambda \geq 20$), the results are still stable (middle panel). 
-    We also check whether the structural differences are driven by small fraction 
-    of \rbcg{} galaxies in very massive clusters.  
-    After removing the \rbcg{} galaxies in clusters with $\lambda \geq 40$, the 
-    differences are as significant as above.  
-    (c). As noted before, the \mtot{} is just a proxy of the total stellar mass. 
-    Given the differences we find, at fixed \mtot{}, \rbcg{} galaxy tends to have 
-    slightly more prominent outer envelope outside 100 kpc than the \nbcg{} one. 
-    Hence their real ``total'' stellar mass could also be slightly larger, and 
-    bias the comparison.  
-    Therefore, we make a similar comparison using the maximum \mstar{} from 
-    the integration of the \mden{} profile instead of the \mtot{}.
-    \update{
-    In this case, the differences between the median profiles become slightly 
-    less significant as expected (a fraction of \rbcg{} galaxies become more 
-    massive, and is not included in the \logmtot{}$< 11.9$ mass bin). 
-    But the systematic trends, especially the differences in the low mass density 
-    outskirt are still very robust. 
-    We will further discuss this in Section \ref{sec:discussion}. 
-    Considering the uncertainty of \mden{} profiles outside 100 kpc, the 
-    feasibility of applying the average \m2l{} to stars in the extreme outskirt, 
-    and the contribution of the diffuse stellar components that trace the halo, 
-    we think that our results are stable.}
+    selection of massive galaxies.}
+    In both inner and outer regions, we conclude the systematic differences in 
+    median \mden{} profiles are significant and robust.
+    Interestingly, the median profiles for \rbcg{} and \nbcg{} cross each other 
+    at $\sim 15$-20 kpc, quite close to the expected $R_{\mathrm{e}}$ for ETGs 
+    this massive. 
+    In Appendix.\ref{app:robust}, we further prove the robustness of this 
+    interesting result by showing that it is not affected by the range of redshift,
+    range of richness, and the choice of proxy for ``total'' \mstar{} 
+    (see Fig.\ref{fig:prof_3}). 
+    We also explore the possible \mtot{}-dependence of this structural difference 
+    despite the limitation of \mstar{}-completeness and small sample size
+    (see Fig.\ref{fig:prof_2}) in Appendix.\ref{app:robust}.
+    Although the systematic differences are very similar in different \mtot{} bins, 
+    we do find some hints that suggest the environmental dependence becomes more 
+    significant at the more massive end.  
+    This evidence could have intriguing implication in the assembly history of 
+    massive galaxies, and is worth more investigations with larger and more completed 
+    sample later.
 
@@
     \mhalo{}-dependence (environmental dependence) of structure in massive, 
-    central galaxies.}
-    \update{
-    Interestingly, the fact the it takes much better data and really cautious 
-    comparison to detect such systematic difference seems to suggest that the role 
-    played by environment in shaping the structure of central galaxies may not be 
-    that crucial in the \mhalo{} and \mstar{} ranges we discussed.}
-
-    At the same time, the systematic differences we find, especially the more 
-    extended stellar envelope of massive central galaxy in more massive halos, 
-    seem to be consistent with the expectation of richer (minor) merging history
-    in denser environment. 
-    \update{
-    Predicted by the ``two-phase'' scenario, the non-dissipative mergers, especially 
-    the minor ones, should mainly deposit stellar mass in the outskirts, help 
-    build the stellar halo while do not change the inner \mden{} profiles very 
-    much (e.g. \citealt{Hilz2013}, \citealt{Oogi2013}).}
-
-    We also explore the possible \mtot{} dependence of such difference.  
-    Limited by the small sample we have, we can only afford to separate the 
-    samples into two \mtot{} bins, and extend to slightly lower \mtot{} bound 
-    ($11.5 \leq \log (M_{\star,\ 10\mathrm{kpc}}/M_{\odot}) < 11.7$ and 
-     $11.7 \leq \log (M_{\star,\ 10\mathrm{kpc}}/M_{\odot}) < 11.9$).  
-    After performing the same procedures of sample matching and comparison, 
-    we show the results in Fig.\ref{fig:prof_2}.   
-    Although the smaller sample leads to larger statistical uncertainties, 
-    it is still interesting to see that the structural differences seem to 
-    be more significant in the higher \mtot{} bin.  
-    For the lower \mtot{} bin, the difference in the inner region becomes quite 
-    uncertain, while there is still evidence of difference in the outskirt.  
-    This result also has interesting implications in the assembly history
-    of massive galaxies, and is worth more investigations with larger samples
-    in the near future.
-
-%% ------------------------------------------------------------------------------------ %%
-
-\subsubsection{Environmental dependence of \mden{} profiles at fixed \minn{}}
-    \label{sssec:sbp_minn}
-
-    \alexie{This is not a seperate section.}
-
-    \update{Here, we compare the median \mden{} profiles of \rbcg{} and \nbcg{} galaxies
-    after matching the two samples using \minn{} ($11.2 <$\logminn{}$ < 11.6$) and 
-    redshift ($0.3 < z < 0.5$).
-    We use the same matching procedure as in the previous section, and also put its 
-    evaluation in Appendix.\ref{app:match}.
-    As mentioned in the beginning, here we use \minn{} as the proxy of the 
-    \mstar{} of the ``in-situ'' component. 
-    We will discuss this assumption more in the Section~\ref{sec:discussion}, but 
-    observations and simulations seem to support this claim in general. 
-    In the previous section, we investigate the environmental dependence of structure 
-    using ``total'' \mstar{}; here, we compare the massive galaxies in low- and 
-    high-mass halos that share similar amount of ``in-situ'' component.}
-
-    \update{
-    As we can see in Fig.\ref{fig:prof_1} and the Appendix.\ref{app:D}, the \minn{} is 
-    not affected by the physical size of PSF out to $z=0.5$.  
-    For the 56 galaxies in this \rbcg{} sample, we achieve excellent matching 
-    result using 375 \nbcg{} galaxies (see Fig.\ref{fig:match}; 
-    median \logminn{}$\sim 11.35$).  
-    Using the same method, we show their individual profiles, and the comparison of 
-    their median \mden{} profiles on the right side of Fig.\ref{fig:prof_1}.}
-
-    Unlike the \mtot{} matched samples, here we see very striking differences that 
-    are already very significant even without any statistical test.     
-    \update{
-    It is easy to see that, when matched at the same \minn{}, the \mden{} profiles of 
-    \rbcg{} and \nbcg{} galaxies are quite similar in the inner 5-10 kpc.
-    However, outside inner 10-15 kpc, the \rbcg{} galaxies show much more prominent
-    stellar envelope.}     
-    Besides the differences in the median profiles, it is also worth discussing 
-    the distributions of individual \mden{} profiles. 
-    \update{
-    Combining the \rbcg{} and \nbcg{} samples together, we should notice that 
-    the slope of the \mden{} profile inside 10 kpc is quite uniform, and the dynamic 
-    range of the \mden{} values is pretty small. 
-    On the other hand, the outer \mden{} profiles of massive central galaxies 
-    can have a larger range of slopes. 
-    The ones from more massive halos on average have shallower outer \mden{} 
-    profiles, which is in qualitative agreement with recent simulation results 
+    central galaxies} that seems to be consistent with the expectation of more frequent 
+    (minor) mergers in denser environment. 
+    These minor, non-dissipative mergers do not alter the inner \mden{} profiles 
+    a lot, but are efficient in depositing stellar mass onto the outer envelope
+    (e.g. \citealt{Hilz2013}, \citealt{Oogi2013}).
+
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
+    Meanwhile, the subtlety of this environmental dependence for \mtot{}-matched 
+    samples seems to suggest that environment plays a secondary role in shaping 
+    the structure of galaxies, and encourage us to look into this issue with a 
+    different angle. 
+    For instance, for massive galaxies that formed similar amount of stars through 
+    intensive star formation at high redshift, how do their host halos (environments) 
+    affect the following mass assembly history? 
+    We attempt to investigate this question through comparing the \mden{} profiles of 
+    the \minn{}-matched \rbcg{} and \nbcg{} galaxies (right side of 
+    Fig.\ref{fig:prof_1}).
+    Assuming we are now comparing the average structures of massive galaxies that share 
+    similar \mstar{} in the ``in-situ'' component, we see striking differences that 
+    are significant without any statistical test.     
+    The median \mden{} profiles of \rbcg{} and \nbcg{} galaxies are quite similar in 
+    the inner 5-10 kpc, but the \rbcg{} galaxies clearly show much more prominent
+    outer envelope.
+
+    It is also worth noting that \mden{} profiles of massive galaxies have quite uniform
+    slope and small scatter inside 10 kpc.  
+    In contrast, their outer profiles could have a large range of slopes and much 
+    larger scatters than the inner region. 
+    It seems to suggest that the inner and outer parts of massive galaxies are shaped 
+    by distinctive physical processes, and are affected by their environment at 
+    very different level. 
+    Given the highly dissipative nature of the ``in-situ'' phase, the similarity of 
+    inner profiles is consistent with the idea that processes like wet-merger and 
+    star burst often create de~Vaucouleur-like ($n\sim 4$) \mden{} profile
+    (e.g. \citealt{Hopkins2008}).
+    At the same time, the outer envelope of massive galaxies are predicted to be 
+    gradually assembled by non-dissipative mergers, which is a stochastic process and 
+    is more affected by the environment.  
+    Therefore, it is natural to see larger diversity in the outer profiles of 
+    low-$z$ massive galaxies. 
+    On average, massive galaxies in more massive halos show shallower outer \mden{} 
+    profiles, which is in qualitative agreement with recent simulation
     (e.g. \citealt{Pillepich2014}).
-    And, for both \rbcg{} and \nbcg{} samples, we find their outer profiles 
-    clearly have much larger dynamic range of \mden{} values at fixed radius.
-    This interesting diversity is also clearly illustrated by 
-    Fig.\ref{fig:m100_m10_color}, where we show the 3-color images of randomly 
-    selected massive central galaxies that have similar \minn{} 
-    ($11.1 \leq \log (M_{\star,\ 10\mathrm{kpc}}/M_{\odot}) < 11.2$)
+    We illustrate this interesting diversity in Fig.\ref{fig:m100_m10_color}, where 
+    we show the 3-color images of randomly selected massive central galaxies that 
+    have similar \minn{} ($11.1 \leq \log (M_{\star,\ 10\mathrm{kpc}}/M_{\odot}) < 11.2$)
     but different \mtot{}.   
     From the top-left to the bottom-right, the \mtot{} of these galaxies increases
-    from $10^{11.22} M_{\odot}$ to $10^{11.75} M_{\odot}$.}
-
-    \update{
-    Putting together, these results indicate that massive central galaxies with 
-    similar \mstar{} in the ``in-situ'' components share very similar radial 
-    \mstar{} distributions in the inner region. 
-    Given the highly dissipative nature of the ``in-situ'' phase, this is consistent
-    with the prediction that dissipative process like intense star-formation or 
-    wet-merger should create de~Vaucouleur-like ($n\sim 4$) \mden{} profile
-    (e.g. \citealt{Hopkins2008}).
-    On the other hand, the outer envelope of massive galaxies should be slowly 
-    assembled through non-dissipative accretion process, where merger history 
-    should play a essential role.  
-    Therefore, it is reasonable to see that the central galaxy of more massive 
-    halo has more significant stellar envelope than the one from lower mass 
-    halo at fixed \mstar{} of their ``in-situ'' components.
-    }
-
-    \update{
-    Despite that the structural contrast is very clear using the median \mden{} 
-    profile, we still perform a serious of tests to verify the robustness of the 
-    results. 
-    Changing the redshift range or the lower $\lambda$ bound of the \rbcg{} sample 
-    has no impact in the significance of the results; 
-    Replacing the \minn{} with the \mstar{} within 5 or 15 kpc will result in 
-    very similar differences; 
-    And, unlike the \mtot{}-matched samples, spitting the samples into two \minn{} 
-    bins (above and below \logminn{}$=11.4$) reveals no apparent \minn{}-dependence 
-    of the structural differences.
-    During the comparison, we notice that there is still tiny structural difference
-    within 10 kpc (right figure of Fig.\ref{fig:prof_1}).
-    When we match the two samples using both \minn{} and \meff{}, we notice that 
-    inner median \mden{} profiles within 10 kpc becomes extremely similar 
-    (see Fig.\ref{fig:match} in Appendix.\ref{app:match}), while the differences 
-    in the outer part remain the same. 
-    Hence, for \rbcg{} and \nbcg{} galaxies that share not only the same inner mass, 
-    but also the same inner \mden{} profiles, we still see significant environmental 
-    dependence in their overall structure.}
-
-    \update{
-    When we match the two samples using \minn{}, the matched samples have 
-    different \mtot{} distributions (median \logmtot{}$\sim 11.78$; 
-    median \logmtot{}$\sim 11.64$).  
-    Although it is still safe to say that they represent very massive central 
-    galaxies, we also notice that the \nbcg{} sample starts to include galaxies with 
-    $11.2 \leq$\logmtot{}$< 11.6$. 
-    For one thing, our samples start to become quite incomplete below 
-    \logmtot{}$\sim 11.5$-11.6; the satellite contamination could also increases
-    toward lower \mtot{} end.  
-    More importantly, when the \mtot{} becomes very different, it is no longer 
-    comfortable to assume that they can share very similar ``in-situ'' components 
-    even at the same \minn{}, as they could be in different phases of evolution.
-    Therefore, we also match the two samples using \minn{} again, but only include the 
-    massive ones with \logmtot{}$\geq 11.5$.  
-    Comparison between these more complete, purer samples of massive central galaxies 
-    shows very similar structural differences again (see the right side of 
-    Fig.\ref{fig:match} in Appendix.\ref{app:match}).
-    In fact, their median profiles become even more similar in the inner region,
-    suggesting that the results are very robust.}
-
-    \update{
-    The median profiles shown in Fig.\ref{fig:prof_1} are available in 
-    Table.1.}
-
-%% ------------------------------------------------------------------------------------ %%
-
-\subsection{Comparisons of ellipticity and optical-color profiles}
+    from $10^{11.22} M_{\odot}$ to $10^{11.75} M_{\odot}$.
+
+    As with the \mtot{}-matched sample, the results are very robust against 
+    sample details, definition of ``inner'' \mstar{} and the \minn{} bins. 
+    In Appendix.\ref{app:match}, we also show that:
+    1) When we match using both \minn{} and \meff{}, we end up with \rbcg{} and \nbcg{} 
+    samples with perfectly matched inner median \mden{} profiles, while the different 
+    in the outskirt remains the same (see the left figure of Fig.\ref{fig:prof_4}).  
+    2) Also, the results will not change even when only a more \mstar{}-complete sample
+    (\logmtot{}$> 11.5$) is considered (see the right figure of Fig.\ref{fig:prof_4}).
+
+    The median profiles shown in Fig.\ref{fig:prof_1} are available in Table.1.
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
+\subsection{Ellipticity and Color Profiles}
     \label{ssec:ell_color}
-
-    \alexie{On the fence about this section. Is it all important???}
 
@@
       \includegraphics[width=\textwidth]{fig/redbcg_discussion_2}
-      \caption{Comparisons of the radial profiles for ellipticity and optical colors 
+      \caption{
+          Comparisons of the radial profiles of ellipticity and optical colors 
       	  for \mtot{}-matched (\textbf{left figure}) and \minn{}-matched 
@@
           elliptical galaxies in \citet[][blue, solid lines on the middle and bottom 
-        panels]{LaBarbera2010}.}
+          panels]{LaBarbera2010}.
+          }
       \label{fig:ell_color}
@@
 
-    \update{
-    In the above section, we focus on the 1-D \mden{} profiles that are based on 
-    $i$-band image along. 
-    Although they already help us reveal interesting structural differences, we 
-    should not forget that the multi-band, 2-D HSC images of massive galaxies 
-    contain more information. 
-    Among them, the shapes and colors of different stellar components are particularly 
-    important to look into.
+    Besides the 1-D \mden{} profiles, the radial profiles of isophotal shape and colors 
+    are also useful diagnostic tools to study massive galaxies. 
     Here, we extract the radial profiles of ellipticity and $k$-corrected optical colors
@@
     Fig.\ref{fig:prof_1}) using \texttt{Ellipse}, and compare the average profiles between
-    the \rbcg{} and \nbcg{} samples for two main purposes:}
+    the \rbcg{} and \nbcg{} samples for two main purposes:
 
     \begin{enumerate}
-        \item \update{Since we derive the \mden{} profiles using average isophotal 
-            shape, if these massive galaxies have steep or complicated elliptical 
-            profiles, or the two samples share very different elliptical profiles, 
-            the comparison of the average \mden{} profiles could be biased.
-            Therefore, we want to verify that photometry using average isophotal 
-            shape is appropriate for these samples. 
-            We extract ellipticity profiles in $i$-band using \texttt{Ellipse} by 
-            setting the geometric parameters free while forcing all isophotes share 
-            the same center.}
-        \item \update{As emphasized earlier, we apply the average \m2l{} to derive 
-            \mstar{} of these massive galaxies knowing that the \m2l{} changes with 
-            radius.  Although this may not be a critical issue when deriving ``total''
-            \mstar{}, it certainly can bias the comparisons of \mden{} profiles when 
-            two samples have very different \m2l{} profiles. 
-            So we want to confirm that the application of average \m2l{} is reasonable
-            using the optical color profiles as tracer of \m2l{}.  
-            After preparing the images in other bands in the same way with $i$-band 
-            ones, we derive color profiles by applying the isophotes from $i$-band 
-            to other images in a ``forced photometry'' mode.}
+        \item To see whether the ellipticity profile strongly depends on environment, 
+            and to see whether 1-D \mden{} profiles using average isophotal shape is 
+            appropriate for the goal of this work.
+
+        \item To verify that the average color gradient does not strongly depend on 
+            the environment, and is not steep enough to invalid the assumption that   
+            it is reasonable to use average \m2l for comparing massive galaxies. 
+            We extract color profiles by applying the isophotes in $i$-band to images 
+            in other bands in ``forced photometry'' manner.  
     \end{enumerate}
 
-    \update{
-    Strictly speaking, we need better background subtraction and 2-D modeling method 
-    to accurately recover these information. 
-    But the straightforward methods applied here are sufficient for these purposes. 
-    We make no correction to the differences in background subtraction and PSF in 
-    different bands, therefore, we will simply ignore the shape and color information 
-    in the inner-most region and very low surface brightness regime. 
-    The profiles between 5-50 kpc should be useful. 
-    Here we only consider $g$ and $r$ band data as the ones in $z$ and Y-band are 
-    often shallower, have worse seeing, and suffer more from background subtraction 
-    issues. 
+    Since we do not correct the differences in sky subtraction and seeing across 
+    different bands, we simply ignore the ellipticity and color in the inner-most and 
+    very low surface brightness regions (profiles are useful between 5-50 kpc). 
     We apply Galactic extinction and $k$-correction to both $g-r$ and $g-i$ color 
@@
     estimates that are based on stacking analysis of SDSS galaxies 
-    (e.g. \citealt{LaBarbera2010, Tal2011, DSouza2014}).}
-
-    \update{
-    Firstly, it is easy to see that massive central galaxies on average have positive 
-    ellipticity profiles. 
-    The ellipticity slowly, but steadily increase with radius from $e\le 0.2$ around 
-    5-10 kpc to $e\sim 0.3$ at 40-50 kpc.  
-    For the \mtot{}-matched samples, their ellipticity profiles trace each other 
-    very well all the way to 50 kpc (2-3$\times R_{\mathrm{e}}$ for their \mstar{}); 
-    there might be hints that the \rbcg{} ones have higher ellipticity at larger 
-    radius, but the isophotal fits with free geometry become very unstable at such 
-    low surface brightness region. 
-    This confirms that the comparisons of \mden{} profiles using average isophotal 
-    shape is reasonable. 
-    On the other hands, when matched using \minn{}, the \rbcg{} galaxies show 
-    systematically higher ellipticity than the \nbcg{} ones at $r > 10$ kpc, despite 
-    the ellipticity profiles at inner region are still very similar. 
-    Since the average ellipticity value is still quite low, and the slope of the 
-    profile is very shallow, the differences in ellipticity profiles will not affect 
-    the significant differences in \mden{} profiles. 
-    And it further hints different assembly histories of the outer envelopes of
-    central galaxies in different environments. 
-    These results are in consistent with the ones from 2-D decomposition in
-    \citep{Huang2013a}: the outer envelopes of massive ETGs have higher ellipticity 
-    than the inner, ``in-situ'' dominated region; and become more elongated with 
-    \mstar{}. 
-    As for the ellipticity profile, although it contains interesting information 
-    regarding the assembly history, it is difficult to estimate them down to very 
-    large radius. 
-    \citet{Tal2011} stacked the SDSS images of a large sample of Luminous Red 
-    Galaxies (LRGs) at $z\sim 0.4$, and extract the ellipticity profile after 
-    correcting the PSF convolution effect.   
-    Its slope is much shallower than the average ones using HSC images, despite the 
-    two samples are at similar redshift and are quite comparable. 
-    The poorer seeing condition of SDSS image plus the systematics in the stacking 
-    process can easily explain this. 
-    \citet{DSouza2015} performed similar stacking analysis for a large sample of very 
-    nearby ETGs.  
-    The ellipticity profile is quite consistent with our average ones within 5-10 
-    kpc, but become much shallower at outer region.  
-    The lower average \mstar{} of their sample and/or the uncertainties in the 
-    stacking analysis may explain this.  
-    This highlights the advantages of the high-resolution, deep HSC images again,
-    and it would be very interesting to compare with numerical simulations. 
-    }
-
-    \update{ 
+    (e.g. \citealt{LaBarbera2010, Tal2011, DSouza2014}).
+
+    Firstly, the ellipticity of massive galaxies steadily increase with radius 
+    from $e\le 0.2$ around 5-10 kpc to $e\sim 0.3$ at 40-50 kpc, in consistent with 
+    previous 2-D modeling results \citep{Huang2013a}.  
+    For the \mtot{}-matched samples, their ellipticity profiles are very similar 
+    all the way to 50 kpc (2-3$\times R_{\mathrm{e}}$ for their \mstar{}). 
+    Meanwhile, for the \minn{}-matched samples, the \rbcg{} galaxies have higher 
+    ellipticity than the \nbcg{} ones at $r > 10$ kpc, while their inner ellipticity 
+    profiles are very similar.  
+    This further hints that massive central galaxies in different halos but with 
+    similar ``in-situ'' mass could experience different merging history.
+    And, given he relative low ellipticity value and shallow ellipticity profile, 
+    we conclude that average isophote is appropriate for the structural comparisons 
+    we performed.
+    Previously, people often rely on image stacking method to extract ellipticity 
+    profile out to large radius (e.g. \citealt{Tal2011}, \citealt{DSouza2015}).
+    Comparing with the ellipticity profile directly measured on deep HSC image, 
+    we find that the stacked ellipticity profiles tend to underestimate the 
+    ellipticity in the outskirt. 
+    Since the ellipticity profile contains interesting information of the assembly 
+    history, we think it highlights the advantage of the HSC image in studying 
+    massive galaxies again, and it would be very interesting to compare with 
+    numerical simulations on this.
+
+    % \citet{Tal2011} stacked the SDSS images of a large sample of Luminous Red 
+    % Galaxies (LRGs) at $z\sim 0.4$, and extract the ellipticity profile after 
+    % correcting the PSF convolution effect.   
+    % Its slope is much shallower than the average ones using HSC images, despite the 
+    % two samples are at similar redshift and are quite comparable. 
+    % The poorer seeing condition of SDSS image plus the systematics in the stacking 
+    % process can easily explain this. 
+    % \citet{DSouza2015} performed similar stacking analysis for a large sample of very 
+    % nearby ETGs.  
+    % The ellipticity profile is quite consistent with our average ones within 5-10 
+    % kpc, but become much shallower at outer region.  
+    % The lower average \mstar{} of their sample and/or the uncertainties in the 
+    % stacking analysis may explain this.  
+    % This highlights the advantages of the high-resolution, deep HSC images again,
+    % and it would be very interesting to compare with numerical simulations.
+
     Secondly, we see shallow and negative gradients of average $g-r$ and $g-i$ color 
-    profiles for both \rbcg{} and \nbcg{} galaxies after excluding the unreliable 
-    regions. 
-    On the left of Fig.\ref{fig:ell_color}, we see that the \rbcg{} and \nbcg{} 
-    samples share very similar color profiles from 5-50 kpc. 
-    This is very good news for using average \m2l{} in the comparisons of \mden{}
-    profiles: although the \mden{} profiles may not be perfectly accurate, there 
-    should be no bias when comparing the average profiles of \rbcg{} and \nbcg{} 
-    samples.
-    On the right side of Fig.\ref{fig:ell_color}, the situation is very similar 
-    as the slopes of color gradients are basically the same for two samples; 
-    although there might be some evidence that, when matched at similar \mstar{} 
-    of the ``in-situ'' component, the \rbcg{} galaxies tend to have slightly redder
-    envelopes than the \nbcg{} ones. 
-    This is worth further investigation, especially vial multi-band, 2-D 
-    decomposition method. 
-    Ignoring the tiny differences between the corresponding HSC and SDSS filters, 
-    we see quite consistent $g-r$ color profiles; but the $g-i$ profiles become 
-    slightly steeper using HSC images. 
-    Although the exact cause of this difference is not clear, it is worth noting that
-    the SDSS $i$-band images suffer from the ``red-halo'' effect of extended PSF 
-    wing (e.g. \citealt{Wu2005}, \citealt{Tal2011}) which could make the color 
-    at larger radius appear redder.
-    Thank to the thickness of the CCD, the HSC $i$-band images do not have this 
-    problem, hence can provide more accurate color estimates.
-    }
-
-    \update{
-    Although the 1-D analysis is not perfect, these preliminary results already 
-    point out the importance and benefits of including multiband, 2-D information 
-    into account. 
-    Now we know that, for massive central galaxies with similar \mtot{}, the average 
-    \mden{} profiles show subtle dependence on halo mass, while the color and 
-    ellipticity profiles are very stable.  
-    On the other hands, for central galaxies that have the same \mstar{}, ellipticity 
-    and color profiles within 10 kpc, their outer envelopes appears to be strongly 
-    depend on environments. 
-    }
-
-%% ------------------------------------------------------------------------------------ %%
-
+    profiles for both \rbcg{} and \nbcg{} galaxies. 
+    For both \mtot{}- and \minn{}-matched samples, we find no significant difference
+    in their median color profiles, which supports the assumption of using single 
+    average \m2l{} value to estimate \mden{} profiles.
+    The median $g-r$ color profiles are quite consistent with the ones based on 
+    stacked SDSS images. 
+    For $g-i$ profiles, the HSC ones are slightly deeper than the SDSS ones, but we 
+    need to remind you the so-called ``red-halo'' effect of extended PSF wing in 
+    SDSS $i$-band (e.g. \citealt{Wu2005}, \citealt{Tal2011}) that could make the 
+    color appears redder.
+    Thank to the thickness of the CCD, the HSC $i$-band image can help provide more 
+    accurate color estimates as it does not suffer from the ``red-halo'' effect.
+
+    These results suggest that multi-band, 2-D information will help us piece together
+    a more complete view of massive galaxy evolution, but also point out limitations 
+    of the 1-D \mden{} profile analysis. 
+    In the near future, we will come back to this point with the help of 2-D modeling
+    method.
+
+    % On the left of Fig.\ref{fig:ell_color}, we see that the \rbcg{} and \nbcg{} 
+    % samples share very similar color profiles from 5-50 kpc. 
+    % This is very good news for using average \m2l{} in the comparisons of \mden{}
+    % profiles: although the \mden{} profiles may not be perfectly accurate, there 
+    % should be no bias when comparing the average profiles of \rbcg{} and \nbcg{} 
+    % samples.
+
+    % On the right side of Fig.\ref{fig:ell_color}, the situation is very similar 
+    % as the slopes of color gradients are basically the same for two samples; 
+    % although there might be some evidence that, when matched at similar \mstar{} 
+    % of the ``in-situ'' component, the \rbcg{} galaxies tend to have slightly redder
+    % envelopes than the \nbcg{} ones. 
+    % This is worth further investigation, especially vial multi-band, 2-D 
+    % decomposition method.
+
+    % Although the 1-D analysis is not perfect, these preliminary results already 
+    % point out the importance and benefits of including multiband, 2-D information 
+    % into account. 
+    % Now we know that, for massive central galaxies with similar \mtot{}, the average 
+    % \mden{} profiles show subtle dependence on halo mass, while the color and 
+    % ellipticity profiles are very stable.  
+    % On the other hands, for central galaxies that have the same \mstar{}, ellipticity 
+    % and color profiles within 10 kpc, their outer envelopes appears to be strongly 
+    % depend on environments.
+
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
 \subsection{Environmental Dependence of Scaling Relations}
@@
       \includegraphics[width=\textwidth]{fig/redbcg_scaling_relation}
-      \caption{\textbf{Left}: The \mstar{}-size relations for \rbcg{} 
+      \caption{
+          \textbf{Left}: The \mstar{}-size relations for \rbcg{} 
           (orange squares) and \nbcg{} (grey dots) galaxies. 
@@
     (e.g. \citealt{MCooper2012}, \citealt{Papovich2012}, \citealt{Kelkar2015}).
-    \update{
     Since comparisons of \mden{} profiles reveal that the structure of massive central 
@@
     Fig.\ref{fig:scaling_relation}).
-    }
 
@@
     the ``size'' to evaluate the relation.
-    \update{
     We derive the $R_{\mathrm{50}}$ using the $i$-band curve-of-growth. 
@@
     subtraction and structural details.
-    }
 
@@
 
-    On the left of Fig.\ref{fig:scaling_relation}, we see clear \mstar{}-size relations for both samples.  
+    On the left of Fig.\ref{fig:scaling_relation}, we see clear \mstar{}-size relations 
+    for both samples.  
     At fixed \mtot{}, the distributions of $R_{\mathrm{50}}$ for the \rbcg{} and
@@
     follow the \mstar{}-size relation for massive ETGs at low-$z$.
-    \update{
     More importantly, we find that the \mstar{}-size relations at high-\mstar{} end 
@@
     ones from smaller haloes at fixed \mtot{}.
-    }
 
@@
     while the sample of HC13 has $z<0.09$.
-    \update{
     Although here we can not study the redshift evolution of \mstar{}-size relation 
@@
     time, we should expect that \mstar{}-size relation shows stronger environmental 
-    dependence at $z\sim 0.0$ using deeper image than SDSS.} 
+    dependence at $z\sim 0.0$ using deeper image than SDSS.
     On the other hand, if the \nbcg{} galaxies could assemble more \mstar{} through
@@
     in the near future.
-
-%% ------------------------------------------------------------------------------------ %%
-
-%%% ------------------------------------------------------------------------------------ %% 
-%  \begin{figure*}[t]
-%      \centering 
-%      \includegraphics[width=\textwidth]{fig/redbcg_m100_m10_new}
-%      \caption{\textbf{(a)}: Distributions of galaxies on the 
-%          \mtot{}-$\Delta (\log M_{\star})_{100\mathrm{kpc}-10\mathrm{kpc}}$ plane. 
-%          All \rbcg{} (open red boxes) and \nbcg{} (light, grey dots) galaxies 
-%          are shown in the background. 
-%          The \mtot{}-matched samples between $11.6<$\logms{}$<11.9$ (between two 
-%          vertical lines) are highlighted (\rbcg{}: solid red boxes; 
-%          \nbcg{}: bigger grey dots). 
-%          We also show the median values (solid triangular and hexagon), and the
-%          distributions of $\Delta (\log M_{\star})_{100\mathrm{kpc}-10\mathrm{kpc}}$
-%          (both histograms and kernel density distributions on the right).
-%          The best scaling relations for \rbcg{} (red, solid) and 
-%          \nbcg{} (grey, dashed) galaxies along with their uncertainties 
-%          are illustrated as well.~~
-%          \textbf{(b)}: Distributions of galaxies on the 
-%          $\Delta (\log M_{\star})_{100\mathrm{kpc}-10\mathrm{kpc}}$-\minn{} plane.~~
-%          \textbf{(c)}: Distributions of galaxies on the 
-%          $\Delta (\log M_{\star})_{100\mathrm{kpc}-10\mathrm{kpc}}$-\mtot{} plane.
-%          But, this time, we highlight the \rbcg{} and \nbcg{} samples that are 
-%          matched using \minn{} instead of \mtot{}.~~
-%          \textbf{(d)}: Relations between \mtot{} and \minn{}. 
-%          Other formats of figure (b), (c), and (d) are very similar with figure (a).}
-%      \label{fig:scaling_relation}
-%  \end{figure*} 
-%%% ------------------------------------------------------------------------------------ %%
-
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
 \subsubsection{Relations between stellar mass within different physical apertures}
@@
     have lower \minn{} than the \nbcg{} sample. 
-    \update{
     When we plot $\Delta \log M$ with \minn{} for the \mtot{}-matched samples in 
@@
     fraction of \mstar{} stored between 10 and 100 kpc than the one from smaller 
-    haloes.}
+    haloes.
 
@@
     Fig.\ref{fig:prof_1}. 
-    \update{
     Their distributions clearly show the impact of the much more prominent outer 
@@
     $\Delta \log M$ of the \minn{}-matched samples.
-    }
 
@@
     are less reliable than \minn{}. 
-    \update{
     Samples at lower redshift, images with higher spatial resolution, and 2-D modeling 
@@
     us develop better proxy for the \mstar{} of the ``in-situ'' component.
-    }
-
-    \update{
+
     Limited by our capability to estimate \mhalo{} with better accuracy or individually, 
@@
     we do not find any clear correlation with $\lambda$ within the \rbcg{} galaxies.
-    }
     In the current sample, most of the \rbcg{} galaxies are centrals of clusters with 
@@
 
-    \update{
     The \mhalo{}-dependence of structure in massive central galaxies could be the result 
@@
     Fig.1 of \citealt{Wellons2016b}) vial the \mtot{}-\minn{} or similar relations.
-    }
-
 %% ------------------------------------------------------------------------------------ %%

### 2017-03-14 draft/ms_v4.tex
New draft

--- 2017-03-14 draft/ms.tex
@@
 % Version 4; emulateapj format; Edited SH
-% Version 5; MNRAS format; Edited SH
-
-\documentclass[a4paper,fleqn,usenatbib]{mnras}
+
+%\documentclass[twocolumn]{aastex6}
+\documentclass{emulateapj}
 
 % Packages
-%\usepackage{deluxetable}
-%\usepackage{apjfonts}
-\usepackage{newtxtext,newtxmath}
-\usepackage[T1]{fontenc}
-\usepackage{ae,aecompl}
+%\usepackage{emulateapj5}
+\usepackage{apjfonts}
 \usepackage{amssymb, amsmath}
 \usepackage{graphicx}
+\usepackage{CJK}
 \usepackage{natbib}
@@
 % Package Settings
+\bibliographystyle{apj}
 \hypersetup{colorlinks=true,
@@
 \DeclareGraphicsExtensions{.pdf,.png,.jpg}
+%\input psFig~tex
 
@@
 \def\logmmax{{$\log (M_{\star,\mathrm{Max}}/M_{\odot})$}}
-\def\logmgama{{$\log (M_{\star,\mathrm{GAMA}}/M_{\odot})$}}
-\def\logmcmodel{{$\log (M_{\star,\mathrm{cModel}}/M_{\odot})$}}
+\def\logmgama{{$\log (M_{\star,mathrm{GAMA}}/M_{\odot})$}}
+\def\logmcmodel{{$\log (M_{\star,mathrm{cModel}}/M_{\odot})$}}
 
@@
 
+%%%%%%%%%%%%: Header and Version %%%%%%%%%%%%
+
+\shorttitle{ENVIRONMENT DEPENDENCE OF MASS-SIZE RELATION}
+\shortauthors{HUANG ET AL.}
+\slugcomment{Draft version 2}
+
+\begin{document}
+
+\begin{CJK*}{UTF8}{gbsn}
+
 %%%%%%%%%%%%: Title and Affiliations %%%%%%%%%%%%
 
-\title[Structure and Halo of Massive Galaxies]{A Detection of the Environmental 
-       Dependence of the Stellar Halos of Massive Central Galaxies}
-
-\author[S. Huang et al.]{Song Huang,$^{1,2}$\thanks{E-mail: song.huang@ipmu.jp (SH)}
-        HSC collaboration$^{3}$   
-        \\ \\
-        % List of institutions
-        $^{1}$Kavli-IPMU, The University of Tokyo Institutes for Advanced Study, 
-              the University of Tokyo (Kavli IPMU, WPI), Kashiwa 277--8583, Japan\\
-        $^{2}$Department of Astronomy and Astrophysics, University of California 
-              Santa Cruz, 1156 High St., Santa Cruz, CA 95064, U.S.A\\
-        $^{3}$Another Department, Different Institution, Street Address, City Postal 
-              Code, Country
-        }
-
-\date{Accepted XXX. Received YYY; in original form ZZZ}        
-\pubyear{2017}
-
-%        \author{Song Huang\altaffilmark{1} 
+\title{A Detection of the Environmental Dependence of the Stellar Halos of 
+       Massive Central Galaxies}
+
+\author{Song Huang (黄崧)\altaffilmark{1}, 
+        HSC collaboration\altaffilmark{1}}   
+%        \author{Song Huang (黄崧)\altaffilmark{1} 
 %        Alexie Leauthaud\altaffilmark{1}, 
@@
 %        }
+
+\email{song.huang@ipmu.jp}
+
+\date{}
+
+\altaffiltext{1}{Kavli Institute for the Physics and Mathematics of the 
+    Universe, The University of Tokyo Institutes for Advanced Study, 
+    the University of Tokyo (Kavli IPMU, WPI), Kashiwa 277--8583, Japan}
 %\altaffiltext{2}{Princeton University Observatory, 
@@
 %\altaffiltext{4}{Carnegie-Mellon University \todo{correct affiliation here}}
-
-%%%%%%%%%%%%: Header and Version %%%%%%%%%%%%
-
-\begin{document}
-
-\label{firstpage}
-\pagerange{\pageref{firstpage}--\pageref{lastpage}}
-
-\maketitle
 
@@
 \end{abstract}
-
-\begin{keywords}
-    galaxies: elliptical and lenticular, cD --
-    galaxies: formation --
-    galaxies: photometry -- 
-    galaxies: structure -- 
+\keywords{galaxies: elliptical and lenticular, cD --- 
+          galaxies: formation --- 
+          galaxies: photometry --- 
+          galaxies: structure --- 
           galaxies: surveys}
-\end{keywords}
+
+\maketitle
 
@@
 %% ------------------------------------------------------------------------------------ %% 
-    \begin{figure*}
+    \begin{figure*}[t!]
         \centering 
@@
 %% ------------------------------------------------------------------------------------ %% 
-  \begin{figure*}
+  \begin{figure*}[t!]
       \centering 
@@
     Although the hierarchical growth scenario under the $\Lambda$-CDM cosmology 
-    is a solid theoretical background (e.g. \citealt{Baugh1996, DeLucia2006}, 
-    plenty important questions regarding the star-formation history, mass assembly 
-    process, and structural evolution of these massive galaxies remain open. 
+    is a solid theoretical background (e.g. \addref{}, plenty important questions 
+    regarding the star-formation history, mass assembly process, and structural 
+    evolution of these massive galaxies remain open. 
     Thanks to the advances in observations and numerical simulations, the newly 
@@
     Under this picture, the highly dissipative processes at high-$z$ (e.g cold 
-    accretion, gas-rich merger; e.g. \citealt{Hopkins2008, Dekel2009}) induce 
-    intense starburst, and quickly form the massive progenitors of $z\sim 0$ massive 
-    early-type galaxies (ETGs).     
-    Later, certain physical mechanism (e.g. AGN feedback; e.g. \citealt{Sijacki2007,
-    Fabian2012}) 
+    accretion, gas-rich merger; e.g. \addref{}) induce intense starburst, and 
+    quickly form the massive progenitors of $z\sim 0$ massive early-type galaxies 
+    (ETGs). 
+    Later, certain physical mechanism (e.g. AGN feedback; e.g. \addref{}) 
     efficiently quenched the on-going star formation so that a large fraction of 
-    these massive progenitors become quiescent at $z>1$ (e.g. \citealt{Bezanson2009,
-    Kriek2016}). 
+    these massive progenitors become quiescent at $z>1$ (e.g. \addref{}). 
     At the same stellar mass (\mstar{}), these so-called ``red nuggets'' 
-    (e.g. \citealt{Damjanov2009}) have smaller effective radius 
-    ($R_{\mathrm{e}}$; \citealt{Trujillo2006, vanDokkum2008, Cimatti2008}), 
+    (e.g. \addref{}) have smaller effective radius ($R_{\mathrm{e}}$; \addref{}), 
     slightly higher central velocity dispersion and stellar mass density 
     (\mden{}; e.g. \citealt{vandeSande2011, Belli2014}), more disk-like morphology 
-    (e.g. \citealt{vanderWel2011}) than their local descendants 
-    (e.g. \citealt{Bezanson2009, vanDokkum2010}). 
+    (e.g. \addref{}) than their local descendants (e.g. \citealt{Bezanson2009,
+    vanDokkum2010}). 
     Later, the second phase of evolution is driven by non-dissipative processes 
-    like dry mergers with other galaxies (e.g. \citealt{Naab2006, Khochfar2006}). 
+    like dry mergers with other galaxies (e.g. \addref{}). 
     According to the ``two-phase'' scenario, minor mergers make dominated 
@@
     Under the $\Lambda$-CDM cosmology, the formation of galaxy is intrinsically 
-    tied to the growth of the host dark matter halo 
-    (e.g. \citealt{Leauthaud2012, Behroozi2013}).
+    tied to the growth of the host dark matter halo (e.g. \addref{}).
     Massive ETGs living in the center of more massive halos should experience 
@@
     massive ETGs follows a tight and steep relation with the \mstar{} 
-    (e.g. \citealt{Shen2003, Guo2009}). 
+    (e.g. \addref{}). 
     Models based on the ``two-phase'' formation scenario naturally predict that 
@@
     $R_{\mathrm{e}}$ of massive ETGs in more massive halos should be larger 
-    than the ones in less massive halos at fixed \mstar{} 
-    (e.g. \citealt{Shankar2013, Shankar2014}). 
+    than the ones in less massive halos at fixed \mstar{} (e.g. \addref{}). 
+    %% Shankar 2013; 2014
     Interestingly, while hints of such dependence have been spotted at high-$z$ 
-    (e.g. \citealt{Papovich2012, Lani2013, Delaye2014}; but also see 
-    \citealt{Rettura2010}), solid evidence of it at low-$z$ is still absence 
-    (e.g. \citealt{Nair2010, HCompany13}; but also see \citealt{Yoon2017}).
+    (e.g. \citealt{Papovich2012, Delaye2014}; but also see \addref{}), solid 
+    evidence of it at low-$z$ is still absence (e.g. \citealt{Nair2010, HCompany13};
+    but also see \addref{}).
     This confusing result becomes a challenge to the hierarchical growth model 
@@
     method contribute to this problem. 
-    The steep inner \mden{} profiles, extremely extended stellar envelopes, 
-    and other structural details make it very difficult to accurately define and 
-    measure the \mstar{} and $R_{\mathrm{e}}$ of massive ETGs 
-    (e.g. \citealt{Bernardi2013, DSouza2014}).
+    The steep inner \mden{} profiles, extremely extended stellar envelopes, and other
+    structural details make it very difficult to accurately define and measure the 
+    \mstar{} and $R_{\mathrm{e}}$ of massive ETGs (e.g. \addref{}).
 
@@
 %% ------------------------------------------------------------------------------------ %% 
-    \begin{figure*}
+    \begin{figure*}[bt]
         \centering 
@@
 %% ------------------------------------------------------------------------------------ %% 
-  \begin{figure*}
+  \begin{figure*}[bt!]
       \centering 
@@
     \mstar{} and impacts important statistics like the stellar mass function 
-    (e.g. \citealt{Bernardi2013, DSouza2014, DSouza2015, Bernardi2016a}).
+    (e.g. \addref{}).
     We highlight this in the left panel of Fig~\ref{fig:smf1} by plotting 
@@
     method and also reflects the fact that more massive ETGs tend to have more 
-    extended stellar mass distributions (e.g. \citealt{Graham2003}).
+    extended stellar mass distributions (e.g.\ \addref{}).
 
@@
     especially at the very high-mass end where the slope is quite uncertain under
-    current constraints (e.g. \citealt{Bernardi2016}).
+    current constraints (e.g. \ \addref{}).
     Although the careful evaluation of the SMF is beyond the scope of this work, 
@@
 %% ------------------------------------------------------------------------------------ %% 
-  \begin{figure}
+  \begin{figure}[bt!]
       \centering 
@@
     outskirts of the centrals without modifying their central \mden{} much
-    (e.g. \citealt{Oogi2013, Bedorf2013}), the outer stellar envelopes of massive
-    centrals should reflect the environmental dependence of structure better, exactly 
-    as we find from the comparisons of \mden{} profiles and scaling relations.
+    (\addref{}), the outer stellar envelopes of massive centrals should reflect the 
+    environmental dependence of structure better, exactly as we find from the 
+    comparisons of \mden{} profiles and scaling relations.
 
     State of the art simulations suggest that the slope of the stellar halo becomes 
-    shallower in the central of more massive halos (e.g. \citealt{Pillepich2014}), 
-    this is consistent with the results in Fig \ref{fig:prof_1}. 
+    shallower in the central of more massive halos (\addref{}), this is consistent 
+    with the results in Fig \ref{fig:prof_1}. 
     Meanwhile, these simulation also points out that not only the fraction of 
@@
     process, and help us confirm whether the environmental dependence of structure 
-    has already emerged within massive galaxies at higher redshift 
-    (e.g. \citealt{Papovich2012})
+    has already emerged within massive galaxies at higher redshift (\addref{})
 
@@
 %% ------------------------------------------------------------------------------------ %% 
-  \begin{figure*}
+  \begin{figure*}[t]
       \centering 
@@
     Yet, even at $z\sim 0$, the normalization and shape of SMF at high-mass end 
-    are still uncertain partly due to the above-mentioned issue 
-    (\citealt{Bernardi2016}) despite that they are critical for understanding the 
-    overall evolution of galaxies. 
+    are still uncertain partly due to the above-mentioned issue (\addref{}) 
+    despite that they are critical for understanding the overall evolution of 
+    galaxies. 
     In Fig~\ref{fig:smf1}, we illustrate how improved \mstar{} measurement can 
@@
     Finally, we want to point out that we do not separate the potential intra-cluster 
-    light component (ICL; e.g. \citealt{Carlberg1997, Lin2004, Gonzalez2005, 
-    Mihos2005}), but rather treat the stellar distributions 
+    light component (ICL; e.g. \addref{}), but rather treat the stellar distributions 
     out to 100 kpc as an integrated structure.
@@
 
-%\acknowledgements
-\section*{Acknowledgements}
+\acknowledgements
 
@@
 
-\bibliographystyle{mnras}
 \bibliography{redbcg}
@@
 %% ------------------------------------------------------------------------------------ %% 
-    \begin{figure*}
+    \begin{figure*}[hbt!]
         \centering 
@@
 %% ------------------------------------------------------------------------------------ %% 
-    \begin{figure*}
+    \begin{figure*}[bt!]
         \begin{center}
@@
 %% ------------------------------------------------------------------------------------ %% 
-    \begin{figure*}
+    \begin{figure*}[hbt!]
         \begin{center}
@@
 %% ------------------------------------------------------------------------------------ %% 
-\begin{figure*}
+\begin{figure*}[bt!]
     \centering
@@
 %% ------------------------------------------------------------------------------------ %% 
-\begin{figure}
+\begin{figure}[tb!]
     \centering 
-    \includegraphics[width=8.2cm]{fig/redbcg_avg_prof_z}
+    \includegraphics[width=13.0cm]{fig/redbcg_avg_prof_z}
     \caption{
@@
 %% ------------------------------------------------------------------------------------ %% 
-\begin{figure*}
+\begin{figure*}[hbt!]
     \centering 
@@
 %% ------------------------------------------------------------------------------------ %% 
-%\clearpage
-%\include{table1}
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %%  
-\bsp
+\clearpage
+\include{table1}
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
+\end{CJK*}
+
+\clearpage
+
 \label{lastpage}
+
 \end{document}

### 2017-03-14 draft/ms_v6.tex
New draft

--- 2017-03-14 draft/ms.tex
@@
 % Packages
-%\usepackage{deluxetable}
-%\usepackage{apjfonts}
+\usepackage{deluxetable}
 \usepackage{newtxtext,newtxmath}
@@
 \def\logms{{$\log (M_{\star}/M_{\odot})$}}
-\def\logmh{{$\log (M_{\mathrm{Halo}}/M_{\odot})$}}
+\def\logmh{{$\log (M_{\mathrm{halo}}/M_{\odot})$}}
 
@@
 
-\author[S. Huang et al.]{Song Huang,$^{1,2}$\thanks{E-mail: song.huang@ipmu.jp (SH)}
+\author[S. Huang et al.]{
+        Song Huang,$^{1,2}$\thanks{E-mail: song.huang@ipmu.jp (SH)}
         HSC collaboration$^{3}$   
@@
     into centrals of halos that are more and less massive than 
-    $M_{200m}\sim 10^{14} M_{\odot}$.
+    $M_{\mathrm{Halo}}\sim 10^{14} M_{\odot}$.
     For centrals with similar stellar mass within 100 kpc, the ones from 
@@
     galaxies: structure -- 
-    galaxies: surveys}
+    galaxies: surveys
 \end{keywords}
@@
         \caption{
-            A comparison between the imaging quality of SDSS and HSC Wide for a sample 
-        	of nearby massive elliptical galaxies at $0.2 < z < 0.5$.  
+            A comparison between the depth and imaging quality of SDSS and the HSC wide 
+            layer for a sample of nearby massive elliptical galaxies at $0.2 < z < 0.5$.  
             These images are generated using $gri$ band images with an arcsinh stretch 
             \citep{Lupton2004}. 
-            The HSC \texttt{WIDE} layer is $3.0$-$4.0$ magnitudes deeper than SDSS 
-            which is critical to map the outskirts of ETGs out to large radii.
+            The HSC \texttt{WIDE} layer is $3.0$-$4.0$ magnitudes deeper than SDSS.
+            This added depth is critical in order map the outskirts of ETGs out to 
+            large radii.
             }
@@
       \caption{
-          Three-color images for a subsample of massive galaxies at $z\sim 0.4$, and 
-          with similar values for their \mstar{} within a 10 kpc aperture 
-          (the dash-line circle on top-left figure indicates the scale of 10 kpc;
-          $11.2<\log (M_{\star,10\ \mathrm{kpc}}/M_{\odot})<11.3$). 
+          Three-color images for a subsample of massive galaxies at $z\sim 0.4$. 
+          All of these galaxies have the same mass within a 10 kpc aperture 
+          ($11.2<\log (M_{\star,10\ \mathrm{kpc}}/M_{\odot})<11.3$). 
+          The dash-line circle at the top-left figure indicates 10 kpc.
           Galaxies are rank-ordered from top to bottom and from left to right by 
-          their \mstar{} within 100 kpc aperture which varies from $10^{11.2} M_{\odot}$ 
+          their \mstar{} within a 100 kpc aperture which varies from $10^{11.2} M_{\odot}$ 
           to $10^{11.7} M_{\odot}$. 
@@
 
-    Massive galaxies are unique laboratories to study both cosmology and galaxy 
+    Massive galaxies are unique laboratories for studying both cosmology and galaxy 
     formation. 
-    Although the hierarchical growth scenario under the $\Lambda$-CDM cosmology 
-    is a solid theoretical background (e.g. \citealt{Baugh1996, DeLucia2006}, 
-    plenty important questions regarding the star-formation history, mass assembly 
-    process, and structural evolution of these massive galaxies remain open. 
-    Thanks to the advances in observations and numerical simulations, the newly 
-    developed ``two-phase'' formation scenario (e.g. \citealt{Oser2010, Oser2012}) 
-    becomes the most promising theory that can reasonably explain different 
-    observations of massive galaxies. 
-    Under this picture, the highly dissipative processes at high-$z$ (e.g cold 
-    accretion, gas-rich merger; e.g. \citealt{Hopkins2008, Dekel2009}) induce 
-    intense starburst, and quickly form the massive progenitors of $z\sim 0$ massive 
-    early-type galaxies (ETGs).     
-    Later, certain physical mechanism (e.g. AGN feedback; e.g. \citealt{Sijacki2007,
-    Fabian2012}) 
-    efficiently quenched the on-going star formation so that a large fraction of 
-    these massive progenitors become quiescent at $z>1$ (e.g. \citealt{Bezanson2009,
-    Kriek2016}). 
-    At the same stellar mass (\mstar{}), these so-called ``red nuggets'' 
-    (e.g. \citealt{Damjanov2009}) have smaller effective radius 
+    Simulations of structure formation within the context of the $\Lambda$-CDM 
+    cosmological model make predictions for the hierarchical growth of dark matter halos 
+    and galaxies (e.g. \citealt{Baugh1996, DeLucia2006}), but there are many open 
+    questions regarding the star-formation history, mass assembly process, and 
+    structural evolution of massive galaxies. 
+    Massive galaxies are thought to grow according to a ``two-phase'' formation scenario 
+    (e.g. \citealt{Oser2010, Oser2012}). 
+    In this scenario, the progenitors of $z\sim 0$ massive early-type galaxies (ETGs) 
+    undergo a rapid growth phase at $z\sim 2$ triggered either by disk instabilities 
+    or gas rich mergers (e.g\citealt{Hopkins2008, Dekel2009}). 
+    Observationally, the progenitors of ETGs are thought to correspond to the so-called 
+    ``red nuggets'' (e.g. \citealt{Damjanov2009}) which have smaller effective radii 
     ($R_{\mathrm{e}}$; \citealt{Trujillo2006, vanDokkum2008, Cimatti2008}), 
     slightly higher central velocity dispersion and stellar mass density 
-    (\mden{}; e.g. \citealt{vandeSande2011, Belli2014}), more disk-like morphology 
+    (\mden{}; e.g. \citealt{vandeSande2011, Belli2014}), more disk-like morphologies 
     (e.g. \citealt{vanderWel2011}) than their local descendants 
     (e.g. \citealt{Bezanson2009, vanDokkum2010}).
-    Later, the second phase of evolution is driven by non-dissipative processes 
-    like dry mergers with other galaxies (e.g. \citealt{Naab2006, Khochfar2006}). 
-    According to the ``two-phase'' scenario, minor mergers make dominated 
-    contribution during this period as they help explain the significant increase
-    of $R_{\mathrm{e}}$ (e.g. \citealt{Newman2012, vdWel2014}) and accumulation of 
-    outer stellar halo (e.g.  \citealt{Szomoru2012, Patel2013}).
-
-    Despite the great success, it also raises new questions. 
-    Under the $\Lambda$-CDM cosmology, the formation of galaxy is intrinsically 
-    tied to the growth of the host dark matter halo 
-    (e.g. \citealt{Leauthaud2012, Behroozi2013}).
-    Massive ETGs living in the center of more massive halos should experience 
-    different mass assembly history and undergo different merging events comparing 
-    to the ones from smaller halos. 
-    Therefore, it is reasonable to expect that the structures of massive galaxies
-    depend on the ``environment''\footnote{Although there are different 
-    observational definition of environment, we use the term ``environment'' and 
-    halo mass interchangeably in this work.}.
-
-    As one of the most important structural parameters, the $R_{\mathrm{e}}$ of 
-    massive ETGs follows a tight and steep relation with the \mstar{} 
-    (e.g. \citealt{Shen2003, Guo2009}). 
-    Models based on the ``two-phase'' formation scenario naturally predict that 
-    such mass--size relation should show environmental dependence, and 
-    $R_{\mathrm{e}}$ of massive ETGs in more massive halos should be larger 
-    than the ones in less massive halos at fixed \mstar{} 
-    (e.g. \citealt{Shankar2013, Shankar2014}). 
-    Interestingly, while hints of such dependence have been spotted at high-$z$ 
-    (e.g. \citealt{Papovich2012, Lani2013, Delaye2014}; but also see 
-    \citealt{Rettura2010}), solid evidence of it at low-$z$ is still absence 
-    (e.g. \citealt{Nair2010, HCompany13}; but also see \citealt{Yoon2017}).
-    This confusing result becomes a challenge to the hierarchical growth model 
-    of massive galaxies. 
-    On the observational side, both the depth of the images and the photometric 
-    method contribute to this problem. 
-    The steep inner \mden{} profiles, extremely extended stellar envelopes, 
-    and other structural details make it very difficult to accurately define and 
-    measure the \mstar{} and $R_{\mathrm{e}}$ of massive ETGs 
-    (e.g. \citealt{Bernardi2013, DSouza2014}).
-
-    Here, taking advantage of the excellent image quality of the HSC survey, we 
-    investigate the environmental dependence of structure in massive galaxies 
-    via comparing the \mden{} profiles and structural scaling relations between 
-    massive central galaxies living in more and less massive dark matter halos. 
-    Both the deep imaging depth ($i$-band images are typically 3-4 magnitude deeper 
-    than SDSS ones) and the good seeing condition (median FWHM$\sim 0.6^{\arcsec}$
-    in $i$-band) of the HSC images make them perfect for mapping the \mstar{}
-    distributions of massive galaxies out to very large radius (see 
-    Fig~\ref{fig:sdss_compare}). 
-    With the help of a cluster catalog, we select a large sample of massive central 
-    galaxies in halos that are more or less massive than \logmh{}$\sim 14.0$ at 
-    $0.3 < z < 0.5$ from the available $\sim 100$ square degree of HSC data.
-
-    Motivated by the ``two-phase'' scenario, also due to the difficulty in 
-    appropriately modeling the \mstar{} distributions of massive galaxies out to 
-    their very outskirts, we focus on \mstar{} within two different physical apertures 
-    in this work:
+
+    Following an initial epoch of early formation, feedback from stars and/or AGN 
+    (e.g. \citealt{Sijacki2007, Fabian2012}) efficiently quench star formation in 
+    massive galaxies and a large fraction of these massive progenitors become quiescent 
+    at $z>1$ (e.g. \citealt{Bezanson2009, Kriek2016}). 
+    The second phase in the ``two-phase'' formation scenario is driven by 
+    non-dissipative processes such as dry mergers with other galaxies 
+    (e.g. \citealt{Naab2006, Khochfar2006}). 
+    According to the ``two-phase'' scenario, minor mergers drive the growth of massive 
+    galaxies at late times and can help explain the significant increase
+    of $R_{\mathrm{e}}$ (e.g. \citealt{Newman2012, vdWel2014}) as well as the build-up 
+    of the outer stellar halos of ETGs (e.g.  \citealt{Szomoru2012, Patel2013}).
+
+    According to this two-phase formation scenario, the late time growth of massive ETGs 
+    is intrinsically tied to the growth of their host dark matter halos 
+    (e.g. \citealt{Leauthaud2012, Behroozi2013, Shankar2013}). 
+    Massive ETGs that live at the center of more massive halos should experience 
+    a different mass assembly history and should be subject to a larger merger rate 
+    compared to ETGs that live in smaller dark matter halos. 
+    A natural prediction of the two-phase formation scenario is therefore that the 
+    structural properties of massive galaxies should depend on their ``environment''
+    \footnote{There are different observational definitions of "environment". 
+    In this paper, we use the term ``environment'' and halo mass interchangeably}.
+
+    Previous work has shown that the half-light radii of massive ETGs is tightly 
+    correlated with \mstar{} (e.g. \citealt{Shen2003, Guo2009}). 
+    Models based on the ``two-phase'' formation scenario naturally predict that this 
+    mass--size relation should exhibit an environmental dependence: the effective radii 
+    of massive ETGs in more massive halos should be larger than those in less massive
+    halos at fixed \mstar{} (e.g. \citealt{Shankar2013, Shankar2014}).
+
+    However, while hints of an environmental dependence in the mass-size relation have 
+    been spotted at high-$z$ (e.g. \citealt{Papovich2012, Lani2013, Delaye2014}; but 
+    also see \citealt{Rettura2010}), there is no solid evidence for this effect at 
+    low-$z$ (e.g. \citealt{Nair2010, HCompany13}; but also see \citealt{Yoon2017}). 
+    The absence of an environmental dependence in the mass-size relation is an 
+    outstanding challenge to the two-phase formation scenario of ETGs.
+
+    From an observational perspective, we hypothesize that the lack of a detection of 
+    this effect may be related a combination of the methodologies employed, as well as 
+    the lack of deep high-quality imaging for large numbers of massive ETGs. 
+    In particular, massive ETGs have very steep inner stellar density profiles, 
+    extremely extended stellar envelopes, and radial-dependent isophotal shapes which 
+    make accurate measurements of \mstar{} and $R_{\mathrm{e}}$ very challenging
+    (e.g. \citealt{Bernardi2013, DSouza2014}), 
+    especially in the presence of shallow imaging data such as the Sloan Digital Sky 
+    Survey (SDSS; e.g. \citealt{SDSSDR7, SDSSDR12}).
+
+    In this paper, we take advantage of new high-resolution (median 
+    FWHM$\sim 0.6^{\arcsec}$ in $i$-band) and deep ($i$-band surface brightness 
+    limit $> 28.5$\sb) imaging from the Hyper-Suprime Cam (HSC) Subaru Strategic 
+    Program (SSP; \citealt{HSCDR1; will be referred as the HSC survey} to revisit the 
+    question of the environmental dependence in the mass-size relation. 
+    The goal of this paper is to compare the \mden{} profiles and structural scaling 
+    relations of massive central galaxies in both low and high mass dark matter halos. 
+    Fig~\ref{fig:sdss_compare} displays a comparison of the imaging quality of massive 
+    ETGs using SDSS versus using the new HSC data. 
+    The deep imaging depth and excellent seeing conditions of HSC images make them 
+    perfect for mapping the \mstar{} distributions of massive galaxies out to very 
+    large radii. 
+    With the help of the \redm{} cluster catalog (e.g.\ \citealt{Rykoff2014}; 
+    \citealt{Rozo2015b}; please see Section~\ref{ssec:redmapper} for details), we 
+    select a large sample ($\sim 15000$) of massive central 
+    galaxies with $0.3 < z < 0.5$ using $\sim 100$ square degree of data from the 
+    HSC wide layer.
+
+    Motivated by the ``two-phase'' scenario, and also due to the difficulty in 
+    providing appropriate model to describe the \mstar{} distribution of massive 
+    galaxy from its center to the very outskirt, we focus on \mstar{} within two 
+    different physical apertures in this work:
 
     \begin{itemize}
-        \item \mstar{} within 10 kpc, \minn{}: according to the ``two-phase'' 
-            scenario, the ``in-situ'' star-formation quickly built up the inner, dense 
-            core of massive ETGs.  
+
+        \item The stellar mass within 10 kpc (hereafter noted \minn{}). 
+            According to the two-phase scenario, the ``in-situ'' star-formation quickly 
+            builds up the inner, dense core of massive ETGs.  
             Based on recent observations and simulations (e.g.~\citealt{vanDokkum2010}; 
-            \citealt{RodriguezGomez2016}), the in-situ 
-            component distributes mostly within the effect radius ($R_{\mathrm{e}}$, 
-            or 5-10 kpc) in massive galaxies.  
-            Here we use \minn{} as a proxy of the \mstar{} formed in the ``in-situ''
-            phase.  Although it is an empirical choice, the detailed comparison of 
-            the stellar mass surface density (\mden{}) profiles later suggests it indeed 
-            helps reveal interesting environmental dependence.  
-            Under the adopted cosmology, $1.0^{\arcsec}$ in radius equals 4.4 and 6.1 kpc 
-            at redshift 0.3 and 0.5.  
-            We can reliably measure \minn{} without being bothered by smearing effect
-            of seeing.
-        \item \mstar{} within 100 kpc, \mtot{}: for massive galaxies in this work, 
-            100 kpc aperture reaches to 5-10 $\times R_{\mathrm{e}}$ and very low 
-            \mden{} region, hence can be treated as proxy of the ``total'' \mstar{}. 
-            Limited by the accuracy of background subtraction, the \mden{} profile 
-            of outer region can not be reliably recovered for massive galaxies across 
-            our redshift range. 
-            Although not perfect, \mtot{} is still a much better tracer of total 
-            \mstar{} than the model-dependent ones using shallower images.
+            \citealt{RodriguezGomez2016}), the in-situ component of massive ETGs is 
+            mostly contained within one effective radius ($R_{\mathrm{e}}$, or 5-10 kpc). 
+            We use \minn{} as a proxy for the mass forged during the ``in-situ''
+            phase. 
+            Given the quality of the HSC data, we can reliably measure \minn{} over our 
+            redshift range ($1.0^{\arcsec}$ in radius equals 4.4 and 6.1 kpc at redshift
+            0.3 and 0.5).
+
+        \item The stellar mass within 100 kpc (hereafter noted \mtot{}). 
+            For our galaxy sample, a 100 kpc aperture corresponds to 5-10 
+            $\times R_{\mathrm{e}}$. 
+            We show in section \ref{ssec:mtotal} that most of the mass for these ETGs 
+            can be captured by a 100 kpc radius and that \mtot{} is a good proxy for the 
+            ``total'' \mstar{}. 
+            Although not perfect, we argue that our measurements of \mtot{} (which are 
+            actually measuring the light directly out to 100 kpc) are a better tracer 
+            of total \mstar{} than model-dependent results from shallower data 
+            (such as SDSS) which rely on extrapolating the light profiles of galaxies 
+            out to large radii.
+
        \end{itemize}
-
-    Massive central galaxies in this work show an intriguing diversity on the 
-    plane defined by these two metrics.  
+%% ------------------------------------------------------------------------------------ %%
+
+    Massive central galaxies in this work show an intriguing diversity on the plane 
+    defined by these two metrics.  
     We preview this using Fig~\ref{fig:m100_m10_color}, which shows a subsample of 
-    massive galaxies at $z\sim 0.4$ that share very similar value of \minn{}, but show 
-    a large range of outer structures. 
-    Assuming galaxies at the same \minn{} have similar amount stars in the in-situ 
-    component, it is of great interest to investigate the relation between their 
-    environments and outer envelopes that are assembled at later time. 
-    It is worth noting that, although a circular aperture is shown on 
-    Fig~\ref{fig:m100_m10_color}, we always use elliptical apertures that follow the 
-    average isophotal shape for photometry in this work.
-    And, within our choices of redshift and \mstar{} ranges, we can safely ignore 
-    significant mass growth and structural evolution 
+    massive galaxies at $z\sim 0.4$ that share very similar value of \minn{}, but 
+    exhibit a large diversity in their outer profiles. 
+    Assuming that galaxies at fixed \minn{} share a similar in-situ formation history, 
+    it is of great interest to investigate the relation between their present day halo 
+    mass and the extend of their outer envelopes. 
+    We note that although a circular aperture is shown on Fig~\ref{fig:m100_m10_color}, 
+    for our mass measurements, we always use elliptical apertures that follow the 
+    average isophotal shape. Finally, given our narrow mass and redshift range, we 
+    can safely ignore significant mass growth and structural evolution in this work
     (no star formation, lower merger rate \etal~e.g.\ \citealt{Bellstedt2016},
-    \citealt{Inagaki2015}; but also see \citealt{Bai2014}) 
-    with our redshift and \mstar{} ranges.
-
-    The paper is organized as follows. Section\ref{sec:data} gives a brief overview of 
-    the HSC observation and data reduction, along with the summary of the data selection
-    processes.  
-    Then, we will explain the procedures for extracting 1-D surface brightness profiles 
-    (Section \ref{sec:ellipse}) and estimating stellar mass (Section \ref{sec:mstar}) in
-    details.   
-    We will present the main results in Section \ref{sec:result}, and discuss the several 
-    related technical and scientific issues in Section \ref{sec:discussion}, ending with
-    summary and future plans in Section \ref{sec:summary}.
-
-    All the magnitudes used here are in AB system (\citealt{Oke1983}), and are corrected 
-    for Galactic extinction using calibrations from \citet{Schlafly11}.
-    In this work, we assume $H_0$ = 70~km~s$^{-1}$ Mpc$^{-1}$, ${\Omega}_m=0.3$, 
-    and ${\Omega}_{\lambda}=0.7$.
+    \citealt{Inagaki2015}; but also see \citealt{Bai2014}).
+
+    This paper is organized as follows. 
+    Section \ref{sec:data} presents our data and our sample selection. 
+    Section \ref{sec:ellipse} describes our procedure for extracting 1-D surface 
+    brightness profiles. 
+    Section \ref{sec:mstar} describes how we estimate stellar mass. 
+    Our main results are presented in Section \ref{sec:result} and discussed in 
+    Section \ref{sec:discussion}. 
+    Section \ref{sec:summary} presents our summary and conclusions.
+
+    Magnitudes use the AB system (\citealt{Oke1983}), and are corrected for Galactic 
+    extinction using calibrations from \citet{Schlafly11}.
+    In this work, we assume $H_0$ = 70~km~s$^{-1}$ Mpc$^{-1}$, ${\Omega}_{\rm m}=0.3$, 
+    and ${\Omega}_{\rm \Lambda}=0.7$.
+    Stellar mass is noted \mstar{} and has been derived using a Chabrier Initial Mass 
+    Function (IMF; \citealt{Chabrier2003}).     
+    $M_{\mathrm{halo}}$ denotes halo mass in general whereas $M_{\rm 200b}$ is 
+    explicitly defined as $M_{\rm 200b}\equiv M(<r_{\rm 200b})=200\bar{\rho} 
+    \frac{4}{3}\pi r_{\rm 200b}^3$ where $r_{\rm 200b}$
+    is the radius at which the mean interior density is equal to 200 times
+    the mean matter density ($\bar{\rho}$).
 
@@
     view (FoV;~1.5 deg in diameter) of this camera and will cover $\sim 1400$ deg$^2$ 
-    in 5 broad bands (\textit{g r i z Y}) to a limiting depth of $r \sim 26$ mag 
+    in 5 broad bands ($grizY$) to a limiting depth of $r \sim 26$ mag 
     in the \texttt{WIDE} layer. 
@@
     The deblending method implemented by the \texttt{hscPipe} currently tends to 
-    ``over-deblend'' the outskirts of bright galaxies and leads to un 
-    under-estimation of the the total flux of massive ETGs (more discussion in 
+    ``over-deblend'' the outskirts of bright galaxies and leads to an 
+    under-estimation of the the total flux of massive ETGs (this is discussed further in 
     \citealt{BoschInPrep}).  
@@
     galaxies at $z < 0.5$ from the HSC photometric catalog. 
-    Based on Leauthaud\etal~(2016), galaxies with \logms{}$\geq 11.5$ mostly have 
+    Based on \citep{Leauthaud2016}, galaxies with \logms{}$\geq 11.5$ mostly have 
     $i_{\mathrm{SDSS, cModel}} \leq 21.0$ mag. 
     We therefore select our initial sample to be brighter than 
-    $i_{\mathrm{HSC, cModel}} \leq 21.5$\footnote{We neglect the insignificant 
-    differences between the response curves of SDSS-$i$ and HSC-$i$ filters} 
+    $i_{\mathrm{HSC, cModel}} \leq 21.5$\footnote{We neglect small differences between 
+    the response curves of SDSS-$i$ and HSC-$i$ filters.} 
     and also limit our sample to regions that have reached the required depth of 
-    the \texttt{WIDE} survey in $i$-band.
+    the \texttt{WIDE} survey in the $i$-band.
     %% The SQL search is saved as "sample.sql" 
@@
     other optical artifacts\footnote{each criterion removes less than 8\% of the 
-    entire sample}
-    %% Alexie: Actually, 8 percent is not small if we want to consider the number 
-    %%         densities. Let's re-evaluate the impact of these cuts for the 16B 
-    %%         data with FDFC}. 
-    This sample corresponds to 1760845 galaxies and will be referred as \texttt{hscPho}. 
+    entire sample.}.This sample corresponds to 1760845 galaxies and will be referred 
+    as \texttt{hscPho}. 
     %% Saved as "dr1_wide_galaxy_hscPho.fits"
 
-    Here we limit our study to the very high-\mstar{} end where the majority of galaxies 
+    Here we limit our study to the very high-mass end where the majority of galaxies 
     have either a spectroscopic redshift or a robust red-sequence photo-$z$ from the 
@@
     spectroscopic redshifts (e.g.\ SDSS/BOSS; GAMA). The spec-z quality flag from 
-    different catalogs are homogenized into a single flag that indicates whether the 
-    redshift is secure (\ref{}). 
-    We only consider the ones with secure spec-$z$s during the match}.  
+    different catalogs are homogenized into a single flag that indicates secure 
+    redshifts.}.  
     To ensure reasonable \mstar{}-completeness at the high-\mstar{} end we focus on
@@
 
-    For objects without external spec-$z$, we match them with the central galaxies 
-    from the \redm{} catalog using $2.0^{\arcsec}$ radius. 
+    For objects without a spectroscopic redshift, we match them with the central 
+    galaxies from the \redm{} catalog using a $2.0^{\arcsec}$ matching radius. 
     The matched objects with useful red-sequence photo-$z$ ($z_{\lambda}$) are also 
     included in the final sample of bright galaxies with reliable redshift between 
-    $0.3 \leq z \leq 0.5$. 
-    Comparing with spec-$z$, the accuracy of the red-sequence photo-$z$ is sufficient 
-    (median $|z_{\lambda} - z_{\mathrm{Spec}}| \sim 0.01$ for the ones with spec-$z$) 
-    for the goal of this work.
-    The \redm{} catalog provides additional 133 unique redshifts for massive galaxies 
-    in our sample.
+    $0.3 \leq z \leq 0.5$. The accuracy of the red-sequence photo-$z$ is sufficient 
+    (median $|z_{\lambda} - z_{\mathrm{Spec}}| \sim 0.01$ for the ones with a 
+    spec-$z$) for the goal of this work.
+    The \redm{} catalog provides an additional 133 unique redshifts for massive 
+    galaxies in our sample.
     %% Estimated from "dr1_redbcg_hsc_sdss_gama_1arcsec.fits"
@@
     \mstar{} completeness of the combined BOSS and SDSS samples. 
-    They estimate that the BOSS spec-$z$ is about 80\% complete at \logms{}$\geq 11.6$ 
-    at $0.3 < z < 0.5$. 
+    They estimate that the BOSS spec-$z$ sample is about 80\% complete at 
+    \logms{}$\geq 11.6$ at $0.3 < z < 0.5$. 
     The GAMA survey, which partially overlaps with the HSC footprints, supplements 
@@
     This question will be addressed more carefully using the overlap region between 
-    HSC and the \texttt{S82-MGC} in Section\ref{ssec:s82}.
-
-%% ------------------------------------------------------------------------------------ %%  
-\subsection{\redm{}{} cluster catalog}
+    HSC and the \texttt{S82-MGC} in Section \ref{ssec:s82}.
+
+%% ------------------------------------------------------------------------------------ %%  
+\subsection{The \redm{}{} cluster catalog}
     \label{ssec:redmapper}
 
-    Our study focuses on galaxies which are located at the center of their dark matter 
-    halos. 
+    Our study focuses on galaxies located at the center of their dark matter halos. 
     To limit our sample to central galaxies, we use \texttt{v5.10} of the \redm{}{} 
@@
     been run on SDSS DR8 (\citealt{SDSSDR8}) photometric data. 
-    For each cluster, the catalog provides estimates of photometric redshift 
-    ($z_{\lambda}$) and richness ($\lambda$), and identifies the most likely central
-    galaxy (the galaxy with the highest $P_{\mathrm{Cen}}$ value). 
-    The \redm{}{} catalog also provides a list of member galaxies for each cluster 
-    and associated membership probabilities. 
+    For each cluster, the catalog provides a photometric redshift ($z_{\lambda}$), a 
+    cluster richness ($\lambda$), and identifies the most likely central galaxy (the 
+    galaxy with the highest $P_{\mathrm{Cen}}$ value). 
+    The \redm{}{} catalog also provides a list of member galaxies for each cluster and 
+    their associated membership probabilities. 
     Details about the performance of the \redm{}~cluster catalog can be found in 
@@
     Several studies have published calibrations between the \redm{}~richness estimate, 
-    $\lambda$, and halo mass (e.g.\ \citealt{Saro2015}; \citealt{Farahi2016}; 
-    \citealt{Simet2016}). 
-    All these studies consistently found that the \redm{} clusters with $\lambda > 20$ 
-    have $\log (M_{200m}/M_{\odot}) \geq 14.0$.
+    $\lambda$, and halo mass (e.g.\ \citealt{Saro2015, Farahi2016, Simet2016, 
+    Melchior2016}). 
+    All these studies consistently find that \redm{} clusters with $\lambda > 20$ 
+    have $\log (M_{\mathrm{halo}}/M_{\odot}) \geq 14.0$. 
     The \redm{} catalog therefore helps us group massive central galaxies into samples 
@@
     ($P_{\mathrm{CEN}} \geq 0.7$) form a nice sample of massive central galaxies 
-    that live in very massive halos.
-
-    Due to the depth and resolution of the SDSS images, the \redm{} catalog 
+    that live in very massive halos \alexie{Let's talk about this phrase.}.
+
+    Due to the depth and resolution of SDSS, the \redm{} catalog 
     becomes slightly incomplete at lower richness ($\lambda < 40$) at $z > 0.33$. 
-    In addition to that, the typical uncertainty of $\lambda$ estimate ($\sim 5$-10) 
-    can not be ignored. 
-    To ensure the separation in \mhalo{}, here we only focus on the central galaxies of
-    clusters with $\lambda > 30$. 
-    According to \citet{Simet2016}, this $\lambda \geq 30$ sample should have halo mass
-    ($M_{200m}$) more massive than $10^{14.2} M_{\odot}$. 
-    Also, none of the results in this work depend on the choice of the $\lambda$ 
-    limit.
-    For the massive central galaxies that are not in these cluster-level halos, 
+    In addition, the typical uncertainty of $\lambda$ estimate ($\sim 5$-10) 
+    can not be ignored \alexie{Let's talk about this}. 
+    To ensure a clean separation in \mhalo{}, here we only focus on the central galaxies 
+    of clusters with $\lambda > 30$. 
+    According to \citet{Simet2016}, this $\lambda \geq 30$ sample should correspond to 
+    $M_{\mathrm{halo}}>10^{14.2} M_{\odot}$. 
+    We have checked that none of the results in this work depend on the choice of this 
+    $\lambda$ limit. 
+    For massive central galaxies that are not in these cluster-level halos, 
     we unfortunately can not estimate their \mhalo{} individually, but it is safe 
-    to assume they should have $\log (M_{200m}/M_{\odot}) < 14.0$.
+    to assume they will have $\log (M_{\mathrm{halo}}/M_{\odot}) < 14.0$.
 
@@
           The impact on the SMF can exceed 0.2 dex for massive central galaxies 
-          living in halos larger than $\log (M_{200m}/M_{\odot}) > 14.2$ (red lines).
+          living in halos larger than $\log (M_{\mathrm{halo}}/M_{\odot}) > 14.2$ (red lines).
           }
@@
     The median $\lambda$ of these clusters is $\sim 41$, corresponding to 
-    halo mass of $M_{200m}\sim 2.2\times 10^{14} h^{-1} M_{\odot}$.
+    halo mass of $M_{\mathrm{halo}}\sim 2.2\times 10^{14} h^{-1} M_{\odot}$.
     Among them, only 44 of \rbcg{} sample live in clusters with $\lambda \geq 50$
-    ($M_{200m} \sim 3.0\times 10^{14} h^{-1} M_{\odot}$), so the \rbcg{} sample is 
+    ($M_{\mathrm{halo}} \sim 3.0\times 10^{14} h^{-1} M_{\odot}$), so the \rbcg{} sample is 
     not dominated by extremely massive clusters with \mhalo{}$>10^{15} M_{\odot}$. 
@@
     all \redm{} clusters.
-    We choose to use the $R_{200m}$ as the radius, and twice the uncertainty of the 
+    We choose to use the $R_{\mathrm{halo}}$ as the radius, and twice the uncertainty of the 
     photometric redshift error as the thickness of the cylinder. 
-    We convert the $\lambda$ into $M_{200m}$ using the calibration in 
-    \citet{Simet2016}, then estimate the $R_{200m}$ with the help of the 
+    We convert the $\lambda$ into $M_{\mathrm{halo}}$ using the calibration in 
+    \citet{Simet2016}, then estimate the $R_{\mathrm{halo}}$ with the help of the 
     mass-concentration relation in \citet{Diemer2015}. 
@@
     % 1) Start with Eq 12 and Table 3 in Simet et al. For each cluster, assign a value 
-    % of M200m (halo mass defined as 200 time background) to each cluster. 
-    % 3) we then need to estimate the cluster radius R200m (or R200b, same thing). 
+    % of M\mathrm{halo} (halo mass defined as 200 time background) to each cluster. 
+    % 3) we then need to estimate the cluster radius R\mathrm{halo} (or R200b, same thing). 
     % To do this, we need to use a mass-concentration relation. 
@@
     % do this. We can simply use the mass-concentration relation from Benedikts work. 
-    % 4) Now for every cluster you have R200m. And you define the low halo mass central
+    % 4) Now for every cluster you have R\mathrm{halo}. And you define the low halo mass central
     % sample as ones that are not within any cylindar around any cluster. 
@@
 %% ------------------------------------------------------------------------------------ %% 
-%\clearpage
-%\include{table1}
+\clearpage
+\include{table1}
+\clearpage
 %% ------------------------------------------------------------------------------------ %%

### 2017-03-24 draft/ms_v10.tex
Close to finishe

--- 2017-03-14 draft/ms_v6.tex
@@
 \usepackage{natbib}
+\usepackage{url}
 \usepackage{hyperref}
@@
 \def\lamb{$\lambda$}
-\def\lax{{$\mathrel{\hbox{\rlap{\hbox{\lower4pt\hbox{$\sim$}}}\hbox{$<$}}}$}}
-\def\gax{{$\mathrel{\hbox{\rlap{\hbox{\lower4pt\hbox{$\sim$}}}\hbox{$>$}}}$}}
-\def\simlt{\lower.5ex\hbox{$\; \buildrel < \over \sim \;$}}
-\def\simgt{\lower.5ex\hbox{$\; \buildrel > \over \sim \;$}}
+\def\lax{{$\mathrel{\hbox{\rlap{\hbox{\lower4pt\hbox{${\sim}$}}}\hbox{$<$}}}$}}
+\def\gax{{$\mathrel{\hbox{\rlap{\hbox{\lower4pt\hbox{${\sim}$}}}\hbox{$>$}}}$}}
+\def\simlt{\lower.5ex\hbox{$\; \buildrel < \over {\sim} \;$}}
+\def\simgt{\lower.5ex\hbox{$\; \buildrel > \over {\sim} \;$}}
 \def\micron{{$\mu$m}}
@@
 
+%% ------------------------------------------------------------------------------------ %% 
 \title[Structure and Halo of Massive Galaxies]{A Detection of the Environmental 
-       Dependence of the Stellar Halos of Massive Central Galaxies}
+       Dependence of the Stellar Profiles and Halos of Massive Central Galaxies}
 
@@
         Song Huang,$^{1,2}$\thanks{E-mail: song.huang@ipmu.jp (SH)}
-        HSC collaboration$^{3}$   
-        \\ \\
-        % List of institutions
+        Alexie Leauthaud,$^{2,1}$
+        Kevin Bundy,$^{3,1}$
+        Jenny Greene,$^{4}$
+        Yen-Ting Lin,$^{5}$
+        \newauthor
+        Rachel Mandelbaum,$^{6}$
+        Michael Strauss,$^{4}$
+        and HSC collaboration$^{7}$   
+        \\
         $^{1}$Kavli-IPMU, The University of Tokyo Institutes for Advanced Study, 
@@
               Santa Cruz, 1156 High St., Santa Cruz, CA 95064, U.S.A\\
-        $^{3}$Another Department, Different Institution, Street Address, City Postal 
+        $^{3}$UCO/Lick Observatory, University of California, Santa Cruz,
+              1156 High Street, Santa Cruz, CA 95064, USA\\
+        $^{4}$Department of Astrophysical Sciences, Peyton Hall,
+              Princeton University, Princeton, NJ 08540, USA \\
+        $^{5}$Academia Sinica Institute of Astronomy and Astrophysics, 
+              P.O. Box 23--141, Taipei 10617, Taiwan\\
+        $^{6}$McWilliams Center for Cosmology, Department of Physics, 
+              Carnegie Mellon University, Pittsburgh, PA 15213, USA\\
+        $^{7}$Another Department, Different Institution, Street Address, City Postal 
               Code, Country
         }   
-
+%% ------------------------------------------------------------------------------------ %% 
 \date{Accepted XXX. Received YYY; in original form ZZZ}        
@@
 
-%        \author{Song Huang\altaffilmark{1} 
-%        Alexie Leauthaud\altaffilmark{1}, 
-%        Kevin Bundy\altaffilmark{1},
-%        Michael Strauss\altaffilmark{2},
-%        Yen-Ting Lin\altaffilmark{3},
-%        Rachel Mandelbaum\altaffilmark{4}
-%        }
-%\altaffiltext{2}{Princeton University Observatory, 
-%    Peyton Hall, Princeton, NJ 08544, USA}
-%\altaffiltext{3}{Institute of Astronomy and Astrophysics, Academia Sinica, 
-%    P.O.~Box 23--141, Taipei 10617, Taiwan}
-%\altaffiltext{4}{Carnegie-Mellon University \todo{correct affiliation here}}
-
 %%%%%%%%%%%%: Header and Version %%%%%%%%%%%%
-
 \begin{document}
@@
 
-    The promising hierarchical assembly scenario of massive galaxies suggest the 
-    structure of these galaxies should depend on their environments or halo mass.
-    Yet, at low redshift, observations find no clear evidence for that. 
-    Here, using the deep images from the Subaru Hyper Suprime-Cam (HSC) survey,
-    we map the stellar mass distributions of massive galaxies at $0.3 < z < 0.5$ 
-    out to the very outskirt, and detect subtle, but robust structural differences 
-    that depend on halo mass for central galaxies at high mass end. 
-    With the help of the \redm{} catalog, we separate these massive galaxies 
-    into centrals of halos that are more and less massive than 
-    $M_{\mathrm{Halo}}\sim 10^{14} M_{\odot}$.
-    For centrals with similar stellar mass within 100 kpc, the ones from 
-    more massive halos on average have slightly more flattened inner profile 
-    within $\sim 10$-$20$ kpc, and more prominent outer envelope.
-    Meanwhile, when matched at the same stellar mass within inner 10 kpc--a 
-    proxy of the mass of the in-situ component, the massive centrals of more  
-    massive halos show much more significant outer stellar envelopes.    
-    We also see that these two samples of massive galaxies follow slightly 
-    different mass-size relation and the relationship between the stellar mass 
-    within 100 and 10 kpc.
-    Such differences in structure are broadly consistent with the expectation that
-    central galaxy from more massive halo should have more complex merging history.
-    These results highlight the importance of deep photometry in the study of 
-    the assembly history of massive galaxies.
+    We use ${\sim}100$ deg$^2$ of deep ($>28.5$ \sb{} in $i$-band), high-quality 
+    (0.6\asec seeing) imaging data from the Hyper Suprime-Cam (HSC) survey 
+    to investigate the halo mass dependence of the surface mass density profiles 
+    and outer stellar envelopes of massive galaxies. 
+    Our sample consists of ${\sim}7000$ massive (\mstar{}$\geq 11.5$) central galaxies 
+    at $0.3 < z < 0.5$. 
+    The depth of the HSC survey reaches ${\sim}4$ magnitudes fainter than SDSS and 
+    enables us to directly trace stellar mass distributions to 100 kpc without 
+    requiring stacking. 
+    For the first time, we conclusively show that at fixed stellar mass, massive central 
+    galaxies display mass density profiles that are not self similar and which 
+    present subtle but systematic differences that correlate with \mhalo{}. 
+    On average, massive central galaxies in more massive halos have shallower inner 
+    stellar mass density profiles (within ${\sim}10$-$20$ kpc) and more prominent outer 
+    envelopes. 
+    These differences translate into a clear environmental dependence of the mass-size 
+    relation: central galaxies in more massive halos have larger $R_{\mathrm{50}}$ 
+    at fixed \mtot{}. 
+    Shallow imaging will miss light at the outskirts of galaxies and this has an 
+    important impact on measurements of the galaxy mass function. 
+    Furthermore, because galaxies in larger halos have more extended envelopes, 
+    the amount of light that is missed will be halo mass dependent. 
+    Finally, at fixed total stellar mass, there is a large (but continuous) diversity 
+    in the amplitude of stellar profiles at 100 kpc. 
+    We argue that ``cD'' galaxies represent the tail end of a distribution and 
+    are not a distinct class of massive galaxies. 
+    Our results are broadly consistent with the two phase formation scenario of 
+    massive galaxies in which outer envelopes are built up at late times from the 
+    accretion of small systems. 
+    Our mass profiles are provided in a convenient tabulated format in order to 
+    facilitate comparisons with predictions from numerical simulations of galaxy 
+    formation.
 
@@
       \caption{
-          Three-color images for a subsample of massive galaxies at $z\sim 0.4$. 
+          Three-color images for a subsample of massive galaxies at $z{\sim}0.4$. 
           All of these galaxies have the same mass within a 10 kpc aperture 
@@
           to $10^{11.7} M_{\odot}$. 
-          At fixed "inner" mass ($M_{\star,10}$), massive galaxies display significant
+          At fixed ``inner'' mass ($M_{\star,10}$), massive galaxies display significant
           diversity in their outer profiles. 
           Red boxes indicate galaxies in halos more massive than 
-          $\sim 10^{14.0} M_{\odot}$. 
+          ${\sim} 10^{14.0} M_{\odot}$. 
           }
@@
     (e.g. \citealt{Oser2010, Oser2012}). 
-    In this scenario, the progenitors of $z\sim 0$ massive early-type galaxies (ETGs) 
-    undergo a rapid growth phase at $z\sim 2$ triggered either by disk instabilities 
-    or gas rich mergers (e.g\citealt{Hopkins2008, Dekel2009}). 
+    In this scenario, the progenitors of $z{\sim} 0$ massive early-type galaxies (ETGs) 
+    undergo a rapid growth phase at $z{\sim} 2$ triggered either by disk instabilities 
+    or gas rich mergers (e.g. \citealt{Hopkins2008, Dekel2009}). 
     Observationally, the progenitors of ETGs are thought to correspond to the so-called 
     ``red nuggets'' (e.g. \citealt{Damjanov2009}) which have smaller effective radii 
-    ($R_{\mathrm{e}}$; \citealt{Trujillo2006, vanDokkum2008, Cimatti2008}), 
+    ($R_{\mathrm{e}}$; e.g. \citealt{Trujillo2006, vanDokkum2008, Cimatti2008}), 
     slightly higher central velocity dispersion and stellar mass density 
@@
     structural properties of massive galaxies should depend on their ``environment''
-    \footnote{There are different observational definitions of "environment". 
+    \footnote{There are different observational definitions of ``environment''. 
     In this paper, we use the term ``environment'' and halo mass interchangeably}.
@@
     In this paper, we take advantage of new high-resolution (median 
-    FWHM$\sim 0.6^{\arcsec}$ in $i$-band) and deep ($i$-band surface brightness 
+    FWHM${\sim} 0.6^{\arcsec}$ in $i$-band) and deep ($i$-band surface brightness 
     limit $> 28.5$\sb) imaging from the Hyper-Suprime Cam (HSC) Subaru Strategic 
-    Program (SSP; \citealt{HSCDR1; will be referred as the HSC survey} to revisit the 
+    Program \citep[SSP,][]{HSCDR1} to revisit the 
     question of the environmental dependence in the mass-size relation. 
@@
     \citealt{Rozo2015b}; please see Section~\ref{ssec:redmapper} for details), we 
-    select a large sample ($\sim 15000$) of massive central 
-    galaxies with $0.3 < z < 0.5$ using $\sim 100$ square degree of data from the 
+    select a large sample (${\sim} 15000$) of massive central 
+    galaxies with $0.3 < z < 0.5$ using ${\sim} 100$ square degree of data from the 
     HSC wide layer.
@@
     We preview this using Fig~\ref{fig:m100_m10_color}, which shows a subsample of 
-    massive galaxies at $z\sim 0.4$ that share very similar value of \minn{}, but 
+    massive galaxies at $z{\sim} 0.4$ that share very similar value of \minn{}, but 
     exhibit a large diversity in their outer profiles. 
@@
             line on this figure. 
-            The dash-line shows the surface brightness profile after correcting the 
-            background. 
             We also plot the relative brightness profile of the PSF model normalized 
@@
             isophote. 
-            Right: the masked $i$-band image of this galaxy with the isophotes 
+            Right: the three color image of this galaxy with isophotes 
             extracted by \texttt{Ellipse}. 
             The thick dotted line highlights the isophote with 
-            $\mu_{i}\sim 28.5$~\sb.
+            $\mu_{i}{\sim} 28.5$~\sb.
             }
@@
     The ambitious multi-layer HSC survey takes advantage of the large field of 
-    view (FoV;~1.5 deg in diameter) of this camera and will cover $\sim 1400$ deg$^2$ 
-    in 5 broad bands ($grizY$) to a limiting depth of $r \sim 26$ mag 
+    view (FoV;~1.5 deg in diameter) of this camera and will cover ${\sim} 1400$ deg$^2$ 
+    in 5 broad bands ($grizY$) to a limiting depth of $r {\sim} 26$ mag 
     in the \texttt{WIDE} layer. 
     This work is based on the internal data release \texttt{S15B}, which covers 
-    $\sim 100$ deg$^2$ in all 5-band to full \texttt{WIDE} depth.  
+    ${\sim} 100$ deg$^2$ in all 5-band to full \texttt{WIDE} depth.  
     The regions covered by this release overlap with a number of spectroscopic surveys 
@@
     than SDSS. 
-    Combined with the excellent imaging resolution (the median $i$-band seeing is 0.6"), 
-    and the wide area, the HSC survey represents a tremendous data set to perform a 
-    large statistical study of the surface brightness profiles of ETGs out to large radii.     
+    Combined with the excellent imaging resolution (the median $i$-band seeing is 
+    0.6\asec), and the wide area, the HSC survey represents a tremendous data set to 
+    perform a large statistical study of the surface brightness profiles of ETGs out to 
+    large radii.     
     Fig~\ref{fig:sdss_compare} illustrates the quality of HSC imaging compared to SDSS 
@@
     $0.3 \leq z \leq 0.5$. The accuracy of the red-sequence photo-$z$ is sufficient 
-    (median $|z_{\lambda} - z_{\mathrm{Spec}}| \sim 0.01$ for the ones with a 
+    (median $|z_{\lambda} - z_{\mathrm{Spec}}| {\sim} 0.01$ for the ones with a 
     spec-$z$) for the goal of this work.
@@
     %% Saved as "dr1_wide_galaxy_icmodel_21.5.fits"
-    Among them, the BOSS and SDSS "legacy" LRG samples provide the majority of 
+    Among them, the BOSS and SDSS ``legacy'' LRG samples provide the majority of 
     spec-$z$. 
@@
     our \texttt{hscZ} sample by 14\%. 
-    Based on \citet{Taylor2011} (e.g.\ their Fig~~6), at $z\sim 0.3$, the GAMA 
+    Based on \citet{Taylor2011} (e.g.\ their Fig~~6), at $z{\sim} 0.3$, the GAMA 
     sample is 80\% complete down to $10^{10.8}$\msun; but only 80\% complete to 
-    $10^{12.0}$\msun at $z\sim 0.5$. 
+    $10^{12.0}$\msun at $z{\sim} 0.5$. 
     We can therefore expect our sample to be roughly \mstar{}-complete above 
@@
     have $\log (M_{\mathrm{halo}}/M_{\odot}) \geq 14.0$. 
-    The \redm{} catalog therefore helps us group massive central galaxies into samples 
-    with different average \mhalo{}. 
-    The reliable candidates of central galaxies in the \redm{} clusters 
-    ($P_{\mathrm{CEN}} \geq 0.7$) form a nice sample of massive central galaxies 
-    that live in very massive halos \alexie{Let's talk about this phrase.}.
-
-    Due to the depth and resolution of SDSS, the \redm{} catalog 
-    becomes slightly incomplete at lower richness ($\lambda < 40$) at $z > 0.33$. 
-    In addition, the typical uncertainty of $\lambda$ estimate ($\sim 5$-10) 
-    can not be ignored \alexie{Let's talk about this}. 
-    To ensure a clean separation in \mhalo{}, here we only focus on the central galaxies 
-    of clusters with $\lambda > 30$. 
+    The \redm{} catalog therefore helps us group massive central galaxies into 
+    samples with different average \mhalo{}. 
+    We will use the central galaxies of \redm{} clusters 
+    ($P_{\mathrm{CEN}} \geq 0.7$) to form a sample of massive central galaxies that 
+    live in massive halos.
+
+    Due to the depth and resolution of SDSS, the \redm{} catalog becomes slightly 
+    incomplete at lower richness ($\lambda < 40$) at $z > 0.33$. 
+    To ensure a clean separation in \mhalo{}, here we only focus on the central 
+    galaxies of clusters with $\lambda > 30$. 
     According to \citet{Simet2016}, this $\lambda \geq 30$ sample should correspond to 
@@
     to assume they will have $\log (M_{\mathrm{halo}}/M_{\odot}) < 14.0$.  
-
 %% ------------------------------------------------------------------------------------ %%
@@
           On average, \mcmodel{} underestimates the total stellar mass of massive 
-          galaxies by 0.1 dex while the difference can exceed 0.2 dex in some cases.
+          galaxies by 0.1 dex while in some cases, the difference can exceed 0.2 dex.
           Vertical histograms indicate the mass difference for galaxies with
@@
           The impact on the SMF can exceed 0.2 dex for massive central galaxies 
-          living in halos larger than $\log (M_{\mathrm{halo}}/M_{\odot}) > 14.2$ (red lines).
+          living in halos larger than $\log (M_{\mathrm{halo}}/M_{\odot}) > 14.2$ 
+          (red lines).
           }
@@
 %% ------------------------------------------------------------------------------------ %% 
-\subsection{Massive Central Galaxies from Low and High Mass Halos}
+\subsection{Massive Central Galaxies in Low and High Mass Halos}
     \label{ssec:mass_central}
@@
     (e.g.\ \citealt{Leauthaud2012}, \citealt{Behroozi2013}, \citealt{Kravtsov2014}), 
-    the massive galaxies in our sample live in halos that span a wide range of 
-    \mhalo{}.
+    even though our sample selects very massive galaxies (\logms{}$\geq 11.5$), they 
+    live in a fairly broad range of halos masses.
     With the help of the \redm{} catalog, we can broadly separate our sample into two
@@
 
-    We match the \texttt{hscZ} sample with the massive central galaxies of 
-    \redm{} clusters with $\lambda \geq 30$ and $P_{\mathrm{0.7}} \geq 0.7$,
-    and find 164 matched galaxies at $0.3 \leq z \leq 0.5$.
-    We will refer these \textbf{central galaxies in more massive halos} as the 
-    \rbcg{} sample here.
-    A small fraction of \redm{} centrals within the HSC footprints is missing  
-    due to severe contamination from optical artifacts or bright stars.
-    The median $\lambda$ of these clusters is $\sim 41$, corresponding to 
-    halo mass of $M_{\mathrm{halo}}\sim 2.2\times 10^{14} h^{-1} M_{\odot}$.
-    Among them, only 44 of \rbcg{} sample live in clusters with $\lambda \geq 50$
-    ($M_{\mathrm{halo}} \sim 3.0\times 10^{14} h^{-1} M_{\odot}$), so the \rbcg{} sample is 
-    not dominated by extremely massive clusters with \mhalo{}$>10^{15} M_{\odot}$. 
+    We match the \texttt{hscZ} sample with the central galaxies of \redm{} clusters 
+    with $\lambda \geq 30$ and $P_{\mathrm{0.7}} \geq 0.7$, and find 164 matched 
+    galaxies at $0.3 \leq z \leq 0.5$.
+    Our sample of \textbf{central galaxies in more massive halos} will be referred to 
+    as the \rbcg{} sample. 
+    The median $\lambda$ of the clusters associated with the \rbcg{} sample is 
+    ${\sim} 41$, corresponding to halo mass of 
+    $M_{\mathrm{halo}}{\sim} 2.2\times 10^{14}$ $h^{-1}$ $M_{\odot}$.
+    Only 44 centrals from the \rbcg{} sample live in clusters with $\lambda \geq 50$
+    ($M_{\mathrm{halo}} {\sim} 3.0\times 10^{14}$ $h^{-1} M_{\odot}$). 
+    Our \rbcg{} sample therefore corresponds to galaxies in moderate mass halos.
     %% Saved as "dr1_redbcg_use_sed5b.fits"
 
-    To select massive central galaxies in \logmh{}$<14.0$ halos, we identify and 
-    remove all galaxies within a cylinder region around each of the central galaxy of 
-    all \redm{} clusters.
-    We choose to use the $R_{\mathrm{halo}}$ as the radius, and twice the uncertainty of the 
-    photometric redshift error as the thickness of the cylinder. 
-    We convert the $\lambda$ into $M_{\mathrm{halo}}$ using the calibration in 
-    \citet{Simet2016}, then estimate the $R_{\mathrm{halo}}$ with the help of the 
-    mass-concentration relation in \citet{Diemer2015}. 
-    At $0.3 < z < 0.5$, the uncertainty of photo-$z$ is between 0.015 to 0.025, 
-    and is enough to exclude cluster members.
-    After removing galaxies in \redm{} clusters, the rest of the massive galaxies 
-    in our sample should mainly be the central galaxies of halos with \logmh{}$<14.0$,
-    and we will refer these \textbf{central galaxies in less massive halos} as the 
-    \nbcg{} sample.
-    We should note that the \nbcg{} sample at this stage spans a large range in 
-    \mstar{}, and includes contaminations like massive satellites in \logmh{}$< 14.0$ 
-    halos.  
-    Therefore, after we update the total \mstar{} later, we only focus on the 
-    \nbcg{} galaxies at very high-mass end (e.g.~\logms{}$ > 11.5$). 
-    According to recent observation (e.g. \citealt{vanUitert2016}), we can neglect 
-    satellite contamination at such high \mstar{} range. 
+    Out next goal is to construct a sample of central galaxies living in halos with 
+    \logmh{}$<14.0$. 
+    We first identify and remove all galaxies within a cylindrical region around all 
+    \redm{} clusters. 
+    We use a radius equal to $R_{\mathrm{200b}}$ and the thickness of the cylinder is 
+    set to twice the uncertainty of the photometric redshift error. 
+    We convert $\lambda$ to $M_{\mathrm{halo}}$ using the calibration of 
+    \citet{Simet2016} and we use the mass-concentration relation from 
+    \citet{Diemer2015} to compute $R_{\mathrm{200b}}$. At $0.3 < z < 0.5$, the 
+    uncertainty of photo-$z$ is between 0.015 to 0.025, and is enough to exclude 
+    cluster members.
+    After removing galaxies associated with \redm{} clusters, the remaining galaxies 
+    in our sample will be dominated by central galaxies living in halos with 
+    \logmh{}$\leq 14.0$. 
+    We will refer to this sample of \textbf{central galaxies in less massive halos}
+    as the \nbcg{} sample.
+
+    We note that at this stage, our \nbcg{} sample still contains galaxies with a 
+    wide range of \mstar{} values. 
+    Later on, once we have more accurate \mstar{} estimates, we will further limit this 
+    sample to \logms{}$ > 11.5$. 
+    At this very high mass end, and given that we have rejected satellites in \redm{} 
+    clusters, any further satellite contamination can be safely neglected 
+    (e.g. \citealt{Reid2014, Hoshino2015, Saito2016, vanUitert2016}).
     %% Saved as "dr1_nonbcg_use_sed5b.fits"
@@
 
-    % \alexie{This is a rather strange procedure, I think we need to change it 
-    % (referee and readers will complain!). What we really want to do is to remove any
-    % galaxies that have $r<R200$ in projection (from the galaxy with the highest value 
-    % of Pcen) and remove galaxies within some deltaz of the cluster redshift. 
-    % The cluster redshift is more well determined than the redshift estimate of any 
-    % cluster member. 
-    % In short, what we are doing here is cutting out a cylinder around the most likely 
-    % BCG. The deltaz value can be motivated by the cluster redshift uncertainty from 
-    % the redmapper papers. The only remaining question is then what radius to use around
-    % clusters. To get that number here is what we need to do. 
-    % 1) Start with Eq 12 and Table 3 in Simet et al. For each cluster, assign a value 
-    % of M\mathrm{halo} (halo mass defined as 200 time background) to each cluster. 
-    % 3) we then need to estimate the cluster radius R\mathrm{halo} (or R200b, same thing). 
-    % To do this, we need to use a mass-concentration relation. 
-    % I'm pretty sure there is an easy command to do this in Python using the python 
-    % package "colossus" by bendikt diemer. 
-    % Download it and see if you an get it to work. If it doesn't look obvious after
-    % 30 min, I can do it on my end using my own code. But good for you to know how to 
-    % do this. We can simply use the mass-concentration relation from Benedikts work. 
-    % 4) Now for every cluster you have R\mathrm{halo}. And you define the low halo mass central
-    % sample as ones that are not within any cylindar around any cluster. 
-    % Sorry, I know this might mean re-doing everything.....let's discuss by Skype if 
-    % this is a major issue.}
 %% ------------------------------------------------------------------------------------ %%
@@
 
-    Using $\sim 100$ deg$^2$ of HSC data, we select a large sample of massive central 
-    galaxies with reliable redshift information, and broadly separate them into two 
-    groups with different \mhalo{}. 
+    Using ${\sim} 100$ deg$^2$ of HSC data, we select a large sample of massive central 
+    galaxies with reliable redshift information, and broadly separate them two 
+    categories based on $M_{\mathrm{halo}}$.
+
     The following is a summary of our sample construction.
@@
         \item \texttt{hscPho} sample: this parent sample consists of bright galaxies 
-            with $i_{\mathrm{cModel}} \leq 21.0$, good quality images and reliable 
+            with $i_{\mathrm{cModel}} \leq 21.0$, good quality imaging, and reliable 
             \texttt{cModel} photometry in all five HSC bands in the \texttt{S15B} 
             data release. 
-        \item \texttt{hscZ} sample: through matching the \texttt{hscPho} sample with 
-            spectroscopic redshifts from surveys like SDSS/BOSS and GAMA, or accurate 
-            red-sequence photometric redshift in the \redm{} catalog, we come up with 
-            a large sample of bright galaxies with reliable redshift information. 
+        \item \texttt{hscZ} sample: we limit the \texttt{hscPho} sample to galaxies 
+            with reliable redshift information. 
         \item \rbcg{} sample: we select a sample of 164 galaxies at 
-            $0.3 \leq z \leq 0.5$ that are reliably identified as the central galaxies 
+            $0.3 \leq z \leq 0.5$ that are the central galaxies 
             in $\lambda > 30$ \redm{} clusters. 
@@
             (\logmh{}$\geq 14.2$). 
-        \item \nbcg{} sample: after excluding all the galaxies that are close to any 
-            \redm{} clusters in both radial and redshift directions from the 
+        \item \nbcg{} sample: after excluding all cluster members from the 
             \texttt{hscZ} sample, we have 14661 bright galaxies at 
             $0.3 \leq z \leq 0.5$. 
-            With the help of \mstar{} estimates via SED fitting (see Section 
-            \ref{ssec:isedfit}), we consider the massive ones among them as the 
-            central galaxies in halos with \logmh{}$<14.0$.  
+            After applying an additional \mstar{} cut (see Section 
+            \ref{ssec:isedfit}), this sample corresponds to central galaxies in 
+            halos with \logmh{}$<14.0$.  
     \end{itemize}
@@
 %% ------------------------------------------------------------------------------------ %% 
-\section{Measurements of 1-D Surface Brightness Profile}
+\section{Measurements of 1-D Surface Brightness Profiles}
     \label{sec:ellipse}
 
-    To estimate the total luminosity of massive galaxies, and measure their 
-    one-dimensional stellar mass density (\mden{}) profiles, we perform elliptical 
-    isophotes fitting using the IRAF \texttt{Ellipse} algorithm (Jedrzejewski 1987).  
-    Compared to the popular two-dimensional model fitting method, the isophote fitting
-    approach is insensitive to the choice of model (e.g. de~Vaucouleurs or \ser{} 
-    profile), the number of components, and the initial guesses of free parameters. 
-    It is also less affected by the background subtraction uncertainty, which is 
-    particularly important for the massive ellipticals in our sample.
     Massive ETGs imaged at the depth of HSC are not well modeled by simple models such 
@@
     In principle, massive galaxies can still be described by more complex 
-    models (e.g \citealt{Huang2013a}; \citealt{Huang2013b}), but they are still 
-    sensitive to background subtraction and initial values of parameters. 
-    For this paper, we opt to for the model-independent 1-D approach and we will only 
-    study galaxies in the radial range where we are not sensitive to either the PSF 
-    ($r<3-5$ kpc) or the background subtraction ($r>100$ kpc).
-
-    We prepare large $i$-band cut-out images for each galaxy in our sample that extend 
-    to at least 750 kpc in radius, along with the bad pixel mask, and the PSF model 
-    reconstructed at the central coordinate. 
-    These cut-outs include all visible light of the galaxy while leaving enough space 
-    to evaluate the background level. 
+    models (e.g \citealt{Huang2013a, Huang2013b, Oh2017}), but they are still 
+    sensitive to the choices of models (e.g. de~Vaucouleurs or \ser{} profile), 
+    the number of components, initial guesses of parameters, and the internal 
+    degeneracies among different parameters. 
+    Background subtraction uncertainty can affect the 2-D model fitting dramatically, 
+    especially for massive ETGs in our sample. 
+    We therefore perform elliptical isophote fitting using the IRAF \texttt{Ellipse} 
+    algorithm (Jedrzejewski 1987) to estimate the total luminosities of massive 
+    galaxies and measure their one-dimensional profiles of stellar mass surface 
+    density (\mden{}). 
+    This 1-D method we adopt is less affected by the issues mentioned above. 
+    Also, we will only study galaxies in the radial range where we are not sensitive 
+    to either the PSF ($r<3-5$ kpc) or the background subtraction ($r>100$ kpc).
+
+    We prepare large $i$-band cut-outs for each galaxy that extend to 750 kpc in 
+    radius, along with a bad pixel mask, and the PSF model. 
+    These cut-outs include all of the light of the galaxy and are large enough to 
+    also evaluate the background level. 
     We choose to use $i$-band images because they trace the stellar distributions of 
@@
     (the observed i-band corresponds to a rest-frame $g$ or $r$ band), but also 
-    because they have better seeing and much lower background level than the images 
-    in $z$ and Y bands that are supposed to be better tracers of \mden{}.
-
-    For each cut-out, to avoid the ``over-deblending'' issue within the 
-    \texttt{hscPipe}, we use customized procedures to detect and appropriately mask 
-    out all objects around the massive galaxies.
-    Meanwhile, the \texttt{hscPipe} tends to over-subtract background around bright
-    objects, including some of the massive galaxies in our sample. 
-    After aggressively masking out all objects (including the central massive 
-    galaxy), we derive an empirical background correction with the help from 
-    \texttt{SExtractor}.
+    because they have better seeing and much lower background levels than the $z$ 
+    and Y band images (although these in principle may be better tracers of \mden{}).
+
+    For each cut-out, to overcome the \texttt{hscPipe} ``over-deblending'' issue, we 
+    use a customized procedure to detect and appropriately mask out neighbouring 
+    objects. 
+    Furthermore, \texttt{hscPipe} tends to over-subtract the background around 
+    bright objects. 
+    To correct for this over-subtraction, we first aggressively mask all objects 
+    (including the central massive galaxy), and derive an empirical background 
+    correction using \texttt{SExtractor}.
     Then, we run \texttt{Ellipse} on the background-corrected, masked cut-outs 
-    following the methodology in \citep{Li2012}. 
-    In short, we start with free centroid and shape (ellipticity and position angle) 
-    for each isophote, then fix the best-estimated centroid and estimate the mean 
-    ellipticity and position angles of all isophotes.  
+    following the methodology of \citet{Li2012}. 
+    In short, we first fit each isophote using a free centroid and shape 
+    (ellipticity and position angle). 
+    We then fix the centroid (using the mean flux-weighted centroid) and estimate
+    the mean ellipticity and position angles of all isophotes. 
     Finally, we extract a 1-D surface brightness profile along the major axis using 
@@
     We correct these surface brightness profiles for Galactic extinction and 
-    cosmological dimming, then integrate them to various radius to get the 
-    luminosity within different physical apertures. 
+    cosmological dimming, and integrate them to various radii to get the luminosity 
+    within different physical (elliptical) apertures. 
     Fig~\ref{fig:ellipse} shows an example of the 1-D surface brightness and 
-    ellipticity profile for a massive galaxy at $z\sim0.2$ together with the 
-    colored image and a subset of isophotes.
-
-    After testing the above procedure with different mask sizes, different 
-    \texttt{Ellipse} parameters, and with or without background correction, 
-    we find that the 1-D surface brightness profile is reliable above 
-    $>28.5$ \sb. 
-    Beyond that, some of the profiles begin to show unphysical behaviors 
-    (truncation or large fluctuations) due to uncertainties from background subtraction. 
-    This conservative choice already enables us to measure the individual surface 
-    brightness profile out to $100$ kpc. 
-    For more details about the technical details of the \texttt{Ellipse} run, please 
-    see Appendix~\ref{app:ellipse}.
+    ellipticity profile for a massive galaxy at $z{\sim}0.2$ and also highlights 
+    a few isophotes.
+
+    We test our procedure using different mask sizes, different \texttt{Ellipse} 
+    parameters, and with or without our background correction. 
+    Based on these tests, we find that our 1-D surface brightness profiles are reliable 
+    up to surfaces brightness levels of $>28.5$ \sb. 
+    Beyond that, some of our profiles shows signs of truncation and/or large 
+    fluctuations which are due to the uncertainty in the background subtraction. 
+    We choose to limit our study to surface brightness levels up to ${\sim} 28.5$ \sb. 
+    This is a conservative choice but already enables us to measure light profiles 
+    out to $100$ kpc on a galaxy-by-galaxy basis (no stacking). 
+    For more details about the technical details of how we use \texttt{Ellipse}, 
+    please see Appendix~\ref{app:ellipse}.
 
@@
     This is an intrinsic limitation of the 1-D method. 
-    It affects $18/164$ of the \rbcg{} galaxies, and a smaller fraction of the \nbcg{} 
-    ones. 
+    It affects $18/164$ of the \rbcg{} sample, and a smaller fraction of the 
+    \nbcg{} sample. 
     It is worth noting that this excludes most major-merging massive galaxies. 
-    We will come back to them in the future using 2-D modeling method.
 %% ------------------------------------------------------------------------------------ %%
@@
     old stellar populations and are known to have shallow color gradients. 
-    We will further justify this point by measuring their average color profiles in 
+    We will further justify this point by measuring their median color profiles in 
     Section \ref{ssec:ell_color}.
@@
     Although \cmodel{} tends to underestimate the total flux for bright, extended 
-    objects, it can still yield accurate \emph{average} color thanks to the 
+    objects, it can still yield accurate \emph{average} colors thanks to the 
     forced-photometry method that takes the PSF convolution into account
@@
     models by drawing randomly from the prior distributions of relevant parameters 
-    (e.g.\ age, metallicity, dust extinction, and star formation history).
+    (e.g. age, metallicity, dust extinction, and star formation history).
     Based on these models, it uses the observed photometry and redshift to compute the 
@@
     functions (PDF) for each parameter.  
-    To get the best estimate of a given parameter, \texttt{iSEDFit} ``integrates'' the 
-    full PDF over all the other ``nuisance'' parameters.
+    To get the best estimate of a given parameter, \texttt{iSEDFit} integrates the 
+    full PDF over all the other nuisance parameters.
     Then, the median value and the 1-$\sigma$ uncertainty are derived based on the 
@@
     (the highest value allowed by FSPS). 
-    We adopt the \citet{Calzetti2000} extinction law with a order two Gamma distribution 
-    of $A_{V}$ between 0 to 2 magnitude. 
+    We adopt the \citet{Calzetti2000} extinction law with a order two Gamma 
+    distribution of $A_{V}$ between 0 to 2 magnitude. 
     A majority of our galaxies are red and quiescent and our results are 
@@
     images in $gY$ bands are shallower in depth and/or have higher background noise).  
-    The typical uncertainty of \logms{} is around 0.08-0.10 dex at \logms$\sim 11.5$. 
-    Please see Appendix~\ref{app:sed} for more detailed discussions of the SED fitting
-    results.  
+    The typical uncertainty of \logms{} is around 0.08-0.10 dex at \logms${\sim} 11.5$. 
+    Please see Appendix~\ref{app:sed} for further details.
+
 %% ------------------------------------------------------------------------------------ %%
@@
       \caption{
-          \textbf{Left}: Median \mden{} profiles of galaxies in different \mtot{} bins:
-      	  [11.4, 11.6] (short-dashed line), [11.6, 11.8] (solid line), and 
-      	  [11.8, 12.0] (long-dashed line). 
-      	  Here we combine the \rbcg{} and \nbcg{} samples, and we also show a random 
-      	  subset of individual profiles in the background.
-      	  The shaded region highlights the region that could be affected by PSF.
-          Two vertical lines label the radius of 10 kpc (thin, dotted line) and
+          \textbf{Left}: Median \mden{} profiles in three total stellar mass bins. 
+              Here we combine the two \rbcg{} and \nbcg{} samples together -- 
+              the halo mass dependence of these profiles will be explored in subsequent 
+              figures. 
+              Thin grey lines show a random subset of individual profiles. 
+              The shaded region highlights the region that could be affected by the PSF. 
+              Two vertical lines indicate 10 kpc (thin, dotted line) and
               100 kpc (thick, dash line). ~~~ 
-          \textbf{Right}: comparison between the average \mden{} profiles with the ones 
-          from previous observations and simulations, including: 
-          1) average profile of massive elliptical galaxies at $z\sim 0$ from 
-          \citet[][Cyan, solid]{Huang2013a}; 
-          2) average profile of massive galaxies at $0.25 \leq z < 0.50$ observed by 
-          \textit{HST} from \citet[][Red, long-dashed]{Patel2013} ;
-          3) average radial stellar distributions in massive halos using simulation and 
-          particle tagging method (\citealt{Cooper13}; Purple, short-dashed).
-          }
+          \textbf{Right}: comparison between our \mden{} profiles, previous observations, 
+              and simulations. 
+              The solid cyan line shows the median profile of massive elliptical 
+              galaxies at $z{\sim} 0$ from \citet[][]{Huang2013a}. 
+              The red long-dashed line shows the median profile of massive galaxies at 
+              $0.25 \leq z < 0.50$ observed by \textit{HST} from \citet[][]{Patel2013}. 
+              The purple short-dashed line shows the median radial stellar distributions 
+              in massive halos from simulation using the particle tagging method
+              (\citealt{Cooper13}).}
       \label{fig:avg_prof}
@@
       \caption{
-          Comparison of the \mden{} profiles for \mtot{}-matched 
-          ($11.6<$\logmtot{}$<11.9$) and \minn{}-matched ($11.2<$\logminn{}$<11.6$) 
-          samples of \rbcg{} (orange to red) and \nbcg{} (grey to black) galaxies.~~
-          \textbf{Left} shows the results for the \mtot{}-matched samples.
-          For details of the matching process, please see Appendix~\ref{app:match}.  
-          On its upper panel, we show the \mden{} profile of each galaxy using very light 
-          color in the background.  
-          We highlight the median profile and its corresponding uncertainties using thick 
-          solid line with darker color and shaded region. 
-          Other formats are the same with Fig~\ref{fig:avg_prof}.
-          Meanwhile, we highlight the difference between the median profiles and its 
-          uncertainty on the bottom panel (brown solid line and shaded region).
-          To test the significance of the differential profile, we perform statistical
-          tests by comparing the median profiles of two random groups that are drawn 
-          from the mixed sample, and have the same sizes with the matched \rbcg{} and
-          \nbcg{} ones.
-          Repeating this process many times, the median of these random differential 
-          profiles (black solid line), the 1-$\sigma$ (dark-grey shaded region) and 
-          3-$\sigma$ (light-grey shaded region) uncertainties are shown on the bottom 
-          panel as well. 
-          A darker vertical dash-line highlights the 100 kpc radius.~~
-          \textbf{Right} shows the results for the \minn{}-matched samples. 
-          The format is exactly the same with the left one, except that the darker 
-          vertical dash-line now highlights the 10 kpc radius.
+          The environmental dependence of the stellar mass profiles of massive central 
+          galaxies. 
+          The left panel corresponds to samples matched by ``total'' stellar mass 
+          (\mtot{}). 
+          The right panel corresponds to samples matched by ``core-mass'' (\minn{}). 
+          Orange and red lines correspond to central galaxies living in halos with 
+          \logmh{} $\geq 14.2$. 
+          Black and grey correspond to central galaxies living in halos with 
+          \logmh{} $\leq 14.0$. 
+          Thin lines show the profiles of individual galaxies while thick lines show 
+          the median profile. 
+          The uncertainty on the median profile is given by the shaded region and is 
+          computed via bootstrap resampling. 
+          The brown line in the bottom panels show the relative difference between 
+          two median profiles 
+          ($\Delta = \log(\mu_{\star, \mathrm{cenHighMh}}) - 
+          \log(\mu_{\star, \mathrm{cenLowMh}})$). 
+          Errors on the difference between the two profiles is computed via bootstrap 
+          too. 
+          The grey shaded regions show a Monte Carlo test to asses how likely is it to 
+          obtain $\Delta$ from random sub-samples of the data. 
+          To compute the grey shaded regions, we first mix the two samples 
+          (\rbcg{} and \nbcg{}), then draw sub-samples of galaxies from the mixed 
+          population and compute $\Delta$ in the same fashion as for our fiducial signal. 
+          We repeat this process 5000 times.  
+          The dark-grey shaded region (light-grey shaded region) shows the 1-$\sigma$ 
+          (3-$\sigma$) fluctuations in $\Delta$ from these 5000 draws.
           }
@@
 
-    With the help of the \texttt{S82-MGC} sample, we briefly discuss the \mstar{} 
-    completeness of this sample. 
+    With the help of the \texttt{S82-MGC} (\citealt{Bundy2015}), we investigate the 
+    \mstar{} completeness of our samples. 
     The \texttt{S82-MGC} sample matches the deeper SDSS photometric data in the 
@@
     Kingdom Infrared Telescope Infrared Deep Sky Survey (UKIDSS; \citealt{Lawrence2007}). 
-    The deeper photometry and better photo-$z$ make the \texttt{S82-MGC} sample complete 
+    The deeper photometry and better photo-$z$s make the \texttt{S82-MGC} sample complete 
     to \logms{}$\geq 11.2$ at $z<0.7$ which makes it sufficient to evaluate the 
-    completeness of this sample.
+    completeness of our HSC samples.
+
     There are 20453 \texttt{S82-MGC} galaxies that are also in the \texttt{hscPho} 
-    sample at $0.3 \leq z_{\mathrm{s82}} \leq 0.5$ (referred as \texttt{s82Pho} sample).   
-    We estimate their \mstar{} using the HSC \texttt{cModel} SED in exactly the 
-    same way\footnote{The \mstar{} using HSC photometry shows tight correlation with the 
-    ones based on the \texttt{S82-MGC} SED which includes NIR data from UKIDSS; 
-    \texttt{S82-MGC} also uses \texttt{iSEDFit} with similar assumptions}.  
-    Then we estimate the volume density distributions of the galaxies in \rbcg{}, 
-    \nbcg{}, and \texttt{s82Pho} samples (right panel of Fig~\ref{fig:smf1}) using 
-    rough estimates of the survey areas they occupied \footnote{We estimate the 
-    uncertainties of these distributions via bootstrap resampling}.
-    By comparing the relative shapes of these distributions, we conclude that 
-    our sample of massive galaxies is reasonably complete down to \logms{}$\sim 11.6$
-    at $0.3 \leq z \leq 0.5$. 
-    While the \rbcg{} sample is less affected by completeness thanks to the reliable
-    photo-$z$ from \redm{}, the completeness of the \nbcg{} sample is still limited 
-    by the spec-$z$ samples.
-    Although there is no apparent reason that the incompleteness can bias our 
-    comparison of structure, we will mainly focus on the \rbcg{} and \nbcg{} galaxies 
-    with $11.6 \le$\logmtot{}$\le 11.9$ where their mass distributions overlap the 
-    most and both have good \mstar{} completeness, and will also match the two samples 
-    carefully in \logms{} and redshift distributions.
+    sample at $0.3 \leq z_{\mathrm{s82}} \leq 0.5$. 
+    We compute \mstar{} values for these galaxies using our fiducial 
+    procedure\footnote{The \mstar{} using HSC photometry is in excellent with the 
+    values derived from the \texttt{S82-MGC} which includes NIR data from UKIDSS; 
+    \texttt{S82-MGC} also uses \texttt{iSEDFit} with similar assumptions.}. 
+    The right side of Fig~\ref{fig:smf1} compares the SMFs of galaxies from 
+    \texttt{S82-MGC} with the SMFs of galaxies from our two 
+    samples\footnote{Errors on the SMFs are estimated via bootstrap resampling}. 
+    Based on Fig~\ref{fig:smf1}, we conclude that our sample of massive galaxies is 
+    reasonably complete down to \logms{}${\sim} 11.6$ at $0.3 \leq z \leq 0.5$. 
+    The \rbcg{} sample is less affected by completeness because we can utilize 
+    photo-$z$s from \redm{}. 
+    However, the completeness of the \nbcg{} sample is still limited by the 
+    availability of spec-$z$s from BOSS.
+
+    In this work, we will focus on the range $11.6 \le$ \logmtot{}$ \le 11.9$ 
+    where our two samples are complete. 
+    When comparing \nbcg{} and \rbcg{} we will also always make sure that the two 
+    samples are well matched both in terms of \mstar{} as well as in terms of redshift. 
     Please see the next section and Appendix~\ref{app:match} for more details.
@@
 
-    Using the best-fit stellar mass from \texttt{iSEDFit} (referred as \mcmodel{}), 
-    we estimate the average \m2l{} in $i$-band, then use that \m2l{} to convert the 
-    1-D luminosity density profiles into stellar mass density profiles; and 
-    also convert the luminosity within 10 and 100 kpc apertures into 
-    corresponding stellar mass estimates (referred as \minn{} and \mtot{}). 
-    From now, we use \mtot{} as the new proxy of ``total'' stellar mass of these 
-    galaxies.  
-    And we also derive the $k$-corrected luminosity and colors from the results.
+    Using the best-fit stellar mass from \texttt{iSEDFit} (noted as as \mcmodel{}), 
+    we estimate the average \m2l{} in the $i$-band, then use that \m2l{} to convert our 
+    1-D luminosity density profiles into stellar mass density profiles. 
+    We also convert our 10 and 100 kpc aperture luminosities into corresponding stellar 
+    mass estimates (noted as \minn{} and \mtot{}).
+
+    For the remainder of this paper, we will use \mtot{} as a proxy of ``total'' 
+    stellar mass. 
     In Appendix~\ref{app:sedasic}, we briefly summarize the basic statistics of 
-    the \rbcg{} and \nbcg{} samples using the newly derived \mtot{} and \minn{}.
-    We can confirm that both samples follow a similar and very tight ``red-sequence''.
-    We also show the outputs from SED fitting process like the average stellar age, 
-    metallicity, and internal dust extinction in Appendix~\ref{app:sed}.
-    Although we do not rely them on scientific analysis, they all behave reasonably for 
-    both samples. 
-    As expected, the integration of 1-D profile out to very large radius help 
-    recover more luminosity (stellar mass) compared to the \cmodel{} results. 
-    We shown in Section \ref{ssec:s82}.
-
-    As mentioned earlier, our assumption of using an average \m2l{} ignores its
-    radial variation.   
-    It is well known that massive ETGs have negative optical color gradient which 
-    indicates a gradient of \m2l{} (e.g.\ \citealt{LaBarbera2012}; 
-    \citealt{DSouza2015}), but the gradient is shallow and smooth out to a few 
-    times of the effective radius (color gradient at the very outskirt is still 
-    not well quantified). 
+    the \rbcg{} and \nbcg{} samples using our estimates of \mtot{} and \minn{}.
+    We confirm that both samples follow a similar and very tight ``red-sequence''. 
+    Appendix~\ref{app:sed} describes the outputs from our SED fitting process 
+    (average stellar age, metallicity, and internal dust extinction). 
+    We do not utilize these quantities in this paper, but we have checked that they all 
+    behave reasonably for both samples. 
+    As expected, the integration of the 1-D profile out to very large radius recovers 
+    more luminosity (stellar mass) compared to the \cmodel{}-based estimates. 
+    This will be shown in Section \ref{ssec:s82}.
+
+    Our methodology ignores any radial variations in \m2l{}. 
+    It is well known that massive ETGs have negative optical color gradients indicating 
+    gradients in \m2l{} (e.g.\ \citealt{LaBarbera2012}; 
+    \citealt{DSouza2015}). 
+    These color gradients are shallow and smooth out to a few times of the effective 
+    radius and color gradients at the outskirts are not yet well quantified. 
     More importantly, for the comparison between the \rbcg{} and \nbcg{} samples, 
-    our results should remain intact as long as there is no significant
-    differences of average color gradient between these two samples.
-    This is confirmed by our initial results on color gradient, and we will 
-    discuss this more in Section \ref{ssec:ell_color}.
-    Therefore the average \m2l{} approach should work reasonably well for our goals.
-
-    This approach to derive total stellar mass is actually quite similar to the 
-    method adopted by the GAMA survey (\citealt{Taylor2011}).
-    They start with \mstar{} estimated using average \m2l{} from SED fitting 
-    results of PSF-matched aperture photometry, and later correct it with better 
-    estimate of total luminosity from single-\ser model fitting
-    (\citealt{Kelvin2012}). 
-    For galaxies in common with the GAMA survey, we also compare their different 
-    estimates of \mstar{} (\mgama{} v.s. \mtot{}) in Appendix~\ref{app:gama},  
-    and notice systematic differences between the two \mstar{} estimates.
-    It is likely that the GAMA models still miss fluxes in the stellar halo that 
-    is beyond the depth of SDSS image. 
+    our results will be robust as long as there is \emph{no significant difference in 
+    the average color gradient between the two samples}. 
+    We have confirmed that this is indeed the case and this will be discussed in 
+    Section~\ref{ssec:ell_color}.
+
+    Our method for deriving total stellar masses is similar to the 
+    method adopted by the GAMA survey (\citealt{Taylor2011, Kelvin2012}). 
+    We have compared our \mstar{} values with those from GAMA and the results are given 
+    in Appendix~\ref{app:gama}. 
+    We find a systematic differences between the two \mstar{} estimates.
+    It is likely that the GAMA models fail to capture the flux associated with the 
+    outskirts of galaxies due to the limited depth of SDSS.     
 %% ------------------------------------------------------------------------------------ %%
@@
 %% ------------------------------------------------------------------------------------ %%     
-    \subsection{Impact of Photometry on Stellar Mass and Stellar Mass Function}
+    \subsection{Impact of Missing Light on the Galaxy Stellar Mass Function}
     \label{ssec:s82}
 
-    As mentioned above, different methods lead to different estimates of ``total'' 
-    \mstar{} and impacts important statistics like the stellar mass function 
-    (e.g. \citealt{Bernardi2013, DSouza2014, DSouza2015, Bernardi2016a}).
-    We highlight this in the left panel of Fig~\ref{fig:smf1} by plotting 
-    the \mtot{} from 1-D analysis with the differences between \mtot{} and \mcmodel{}.
-    Apparently, our careful 1-D approach recovers more flux in massive galaxies 
-    than the \texttt{cModel} method. 
-    More importantly, the average difference steadily increases with \mtot{}. 
-    At \logms$>11.5$, the difference is often larger than 0.2 dex.  
-    This difference relates to the intrinsic limitation of the \texttt{cModel} 
-    method and also reflects the fact that more massive ETGs tend to have more 
-    extended stellar mass distributions (e.g. \citealt{Graham2003}).
-
-    Such mass-dependent difference will clearly result in difference of the SMF, 
-    especially at the very high-mass end where the slope is quite uncertain under
-    current constraints (e.g. \citealt{Bernardi2016}).
-    Although the careful evaluation of the SMF is beyond the scope of this work, 
-    we still highlight the impacts of different definitions of ``total \mstar{}''
-    on the volume density distributions of both samples (Fig~\ref{fig:smf1}, 
-    right panel).  
-    Generally speaking, the use of \mtot{} from 1-D analysis instead of the
-    \mcmodel{} shifts the distributions toward the higher-mass end, and slightly 
-    modifies the slope.
-    This impact is more obvious for the \rbcg{} samples.
+    Different methods for estimating the ``total'' \mstar{} can have a large impact on 
+    the high mass end of the galaxy stellar mass function (e.g. \citealt{Bernardi2013, 
+    DSouza2014, DSouza2015, Bernardi2016a}). 
+    Fig~\ref{fig:smf1} shows the SMF computed using both \mtot{} and \mcmodel{}. 
+    As one can be seen from this figure, our careful 1-D approach recovers more flux 
+    in massive galaxies than \texttt{cModel}. 
+    More importantly, the average difference steadily increases with \mtot{} and also 
+    has a dependence on \mhalo{}. 
+    At \logms{} $>11.5$, the difference can be larger than 0.2 dex. 
+    This difference relates to the intrinsic limitation of the \texttt{cModel} method 
+    and also reflects the fact that more massive ETGs tend to have more extended 
+    stellar mass distributions (e.g. \citealt{Graham2003}). 
+    Generally speaking, the use of \mtot{} instead of the \mcmodel{} shifts the SMF 
+    towards the higher-mass end and slightly modifies the high-mass slope. 
+    The impact of missing flux is most prominent for the \rbcg{} sample.
     For studies about the SMF or other aspects of galaxy evolution based on 
-    \cmodel{}-like photometry or shallower images, these impacts should be 
-    taken into consideration.
-
+    \cmodel{}-like photometry or shallower images, these effects can not be neglected.
 %% ------------------------------------------------------------------------------------ %%
@@
 %% ------------------------------------------------------------------------------------ %%
-\subsubsection{Mass Dependence of \mden{} Profiles}
+\subsubsection{General Trends and Comparison with Previous Work}
     \label{sssec:sbp_inter}
 
-    Comparing to the much discussed scaling relation like the mass-size relation, 
-    the \mden{} profiles contain more structural details that can help us diagnose the 
-    roles of different physical processes, including the environmental effect.  
-    We first mix the \rbcg{} and \nbcg{} together, and show how the average \mden{}
-    profiles of massive galaxies at $0.3 < z < 0.5$ depend on stellar mass using their 
-    median \mden{} profiles\footnote{The median profiles along with their uncertainties 
-    using bootstrap resampling method} in three \mtot{} bins \footnote{Here we ignore a 
-    small population of massive satellite in \redm{} clusters we excluded from our 
-    sample.
-    The sample is clearly not complete in the lowest \mtot{} bin, but its median \mden{}
-    profile is still useful to show the overall trend and to compare with previous 
-    observations}.
-
+    Compared to the much discussed ``mass-size'' relation, the \mden{} profiles that 
+    we have derived capture the full information about the structural properties of 
+    massive galaxies. 
+    We argue that by studying the shapes of these galaxy profiles directly, we can 
+    by-pass outstanding questions about how to accurately define and measure the 
+    ``sizes'' and ``masses'' of these massive galaxies. 
+    Fig~\ref{fig:avg_prof} shows the median \mden{} profiles\footnote{The median 
+    profiles along with their uncertainties are derived using bootstrap resampling 
+    method} of massive central galaxies at $0.3 < z < 0.5$ in three \mtot{} 
+    bins\footnote{The sample is clearly not complete in the lowest \mtot{} bin, 
+    but its median \mden{} profile is still useful to show the overall trend and to 
+    compare with previous work}. 
     As shown in the left panel of Fig~\ref{fig:avg_prof}, we can comfortably trace
-    the \mden{} profiles of these massive galaxies out to 100 kpc \textbf{individually}, 
-    which greatly help us study the statistical properties of their outer envelopes. 
-    These median \mden{} profiles have very moderate differences in the inner region, 
-    but show significant differences in the outskirts as more massive galaxies have 
-    much more prominent stellar envelopes.
-    Most of these massive galaxies ($\ge 10^{11.4} M_{\odot}$) are slow-rotating 
+    the \mden{} profiles of these massive galaxies out to 100 kpc 
+    \textbf{individually}. 
+    These median \mden{} profiles have moderate differences in the inner region, 
+    but show significant differences in the outskirts with more massive galaxies 
+    showing more prominent stellar envelopes. 
+    Most of these massive galaxies ($\ge 10^{11.4} M_{\odot}$) are slowly-rotating 
     (e.g.\ \citealt{Cappellari13b}) giant ellipticals with ``boxy'' inner isophotal 
-    shape (e.g.\ \citealt{Kormendy2009}), and slightly flattened \mden{} profile close 
-    to the center (e.g.\ \citealt{Lauer07}).
-    But their structures in the outskirt clearly do \textbf{NOT} response to the 
-    increase of stellar mass in a self-similar way.
-
-    The \mden{} profile of massive galaxy out to such large radius was only available 
-    through image stacking technique (e.g. \citealt{Tal2011, DSouza2015})
-    that suffers from several systematic issues.
-    Although most \mden{} profiles extend beyond 100 kpc, many of them show signs of 
-    unphysical truncation and fluctuation related to inaccurate sky subtraction.  
-    Therefore, we exclude the profiles outside 100 kpc, even though the median \mden{} 
-    profiles for the two more massive bins behave reasonably out to $\sim 200$ kpc.
-
-    In the right panel of Fig~\ref{fig:avg_prof}, we compare these median profiles with 
-    a few past works.  
-    \citep{Huang2013a}, derived the median \mden{} profile for a small sample of very 
-    nearby ellipticals (within 100 Mpc; median \logms{}$\sim 11.3$ based on shallower 
-    images) from the Carnegie-Irvine Galaxy Survey (CGS, \citealt{CGS1}) that are not 
-    affected by seeing until $r < 1$ kpc.
-    This median \mden{} profile qualitatively agrees with the one for the lowest 
-    \mtot{} bin in the inner region, but shows a slightly more prominent outer 
-    envelope at $r > 15$ kpc. 
-    While the small sample size of the CGS sample ($\sim 30$) and differences in the
-    measurements of \mstar{} could explain this difference, it is also interestingly 
-    consistent with mild mass assembly from $z\sim 0.4$ to $z=0$ in the outskirt.   
-    The CGS images are already deeper than SDSS images in $r$-band, but the median 
-    profile still only reaches to $\sim 50$ kpc for $z\sim 0$ massive galaxies.
-    Meanwhile, the deep HSC images can reliably deliver individual \mden{} profiles 
-    for $z\sim 0.4$ galaxy out to at least 100 kpc.
-
-    \citet{Patel2013} extracted the median \mden{} profile of massive ETGs at 
-    $0.25 < z < 0.50$ using the stacked \textit{HST}/ACS images. 
-    These galaxies are selected at a constant cumulative number density that makes them  
-    good candidates of progenitors of $z=0$ massive ETGs.  
-    The median \mstar{} is $\sim 10^{11.2} M_{\odot}$ according to their estimates.  
-    However, once the differences in imaging depth and assumptions in SED fitting method
-    are considered, it is reasonable to assume they are comparable to our galaxies in 
-    the lowest \mtot{} bin, and the comparison of \mden{} profiles does confirm that.
-    Moreover, the superb resolution of the \textit{HST}/ACS image makes the \mden{} 
-    profile unaffected by PSF even within inner 1 kpc.
-    Therefore, the comparison illustrates that the HSC profiles within our redshift
-    range are indeed not bothered by seeing at $r > 3$ kpc, which also ensure the
-    accuracy of the \minn{} estimates.
-
-    We also compare with the predicted average \mden{} profile of central galaxies in 
-    massive halos ($13.5 < \log M_{200,c} < 14.0$) from cosmological simulation
-    (\citealt{Cooper13}) using the particle-tagging technique (\citealt{Cooper10}).
-    Despite the poorer resolution, its \mden{} profile is already quite similar to 
-    the median \mden{} profile for the $11.6 <$\logmtot{}$< 11.8$ bin within 40 kpc. 
-    However, comparing with observation, this simulation predicts stellar envelope that
-    is too prominent at this halo mass.
-    Result like this demonstrates that comparisons between observations and simulations
-    using \mden{} profiles have the potential to not only help us make simulation
-    more realistic, but also help us investigate the physical causes of the observed
-    \mstar{} and environmental dependences of structures.
-
-    We summarize these median profiles in Fig~\ref{fig:avg_prof} in Table.~1,
-    and all the above median profiles are available  
-    \href{https://github.com/dr-guangtou/hsc_cenHighMh/tree/master/profiles}{here}.
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %% 
-\subsubsection{Environmental Dependence of the \mden{} Profiles}
+    shapes (e.g.\ \citealt{Kormendy2009}), and slightly flattened inner \mden{} 
+    profiles (e.g.\ \citealt{Lauer07}). 
+    But in the outskirts, the structure of these galaxies is 
+    \emph{clearly not self-similar}. 
+    Some of our \mden{} profiles show signs of unphysical truncation and fluctuation 
+    related to inaccurate sky subtraction. 
+    In this paper, we do not use profiles beyond 100 kpc, even though the median 
+    \mden{} profiles for the two most massive bins behave reasonably out to 
+    ${\sim} 200$ kpc.
+
+    Fig~\ref{fig:avg_prof} compares our results with previous work. 
+    Most previous studies have relied on stacking techniques to measure surface 
+    brightness profiles out to large radii.
+    So far, the surface brightness profiles of massive galaxies out to such large 
+    radii was mostly derived via image stacking technique that suffers from several 
+    systematic issues (e.g. \citealt{Tal2011, DSouza2015}; but also see:
+    \citealt{Capaccioli2015}); and the \mden{} profiles are even more rarely 
+    available.
+
+    \citet{Huang2013a} derived \mden{} profiles for a small sample of very nearby 
+    ellipticals (within 100 Mpc; median \logms{} ${\sim} 11.3$ based on shallower 
+    images) from the Carnegie-Irvine Galaxy Survey (CGS, \citealt{CGS1}). 
+    Because this is a very low redshift sample, these profiles are robust to $r=1$ kpc. 
+    The \citet{Huang2013a} profiles show good agreement with ours in the region of 
+    overlap and out to 50 kpc. 
+    CGS images are deeper than SDSS images in the $r$-band, but the median 
+    profile from \citet{Huang2013a} still only reaches ${\sim} 50$ kpc for $z{\sim} 0$ 
+    massive galaxies.
+    Meanwhile, our deep HSC images can reliably deliver individual \mden{} profiles 
+    for $z{\sim} 0.4$ galaxies out to at least 100 kpc.
+
+    \citet{Patel2013} extracted a median \mden{} profile of massive ETGs at 
+    $0.25 < z < 0.50$ using stacked \textit{HST}/ACS images. 
+    These galaxies are selected at a constant cumulative number density and are 
+    thought to be the progenitors of $z=0$ massive ETGs (e.g. \citealt{Leja2013}).  
+    The median \mstar{} of the \citet{Patel2013} sample is ${\sim} 10^{11.2} M_{\odot}$ 
+    which is lower than our lowest mass bin. 
+    However, \citep{Patel2013} use the BC03 SSP model which are roughly 0.1 dex 
+    lower than our FSPS masses (Appendix~\ref{app:sed}). 
+    Furthermore, the \citep{Patel2013} images are shallower than ours meaning 
+    that there masses will be lower than ours because of missing light in the 
+    outskirts. 
+    Given these two considerations, it is reasonable to roughly compare the 
+    \citet{Patel2013} profile with the one in our lowest stellar mass bin. 
+    The superb resolution of the \textit{HST}/ACS image means that the profile in
+    \citet{Patel2013} is unaffected by the seeing even down to 1 kpc. 
+    The good agreement between our profile and the one derived from HST image 
+    shows that our profiles are robust at $r > 3$ kpc and that we can accurately 
+    measure \minn{}.
+
+    Finally, we also compare with the predicted median \mden{} profile of central 
+    galaxies in massive halos ($13.5 < \log M_{200,c} < 14.0$) from cosmological 
+    simulation where the \mden{} profiles of galaxies are calculated using the 
+    particle-tagging technique (e.g. \citealt{Cooper10}).
+
+    The simulated \mden{} profile is also affected by limited resolution in the 
+    center, but it is already quite similar to the median \mden{} profile for 
+    the $11.6 <$ \logmtot{} $< 11.8$ bin within 40 kpc. 
+    However, compared with our data, this simulation predicts stellar envelope that
+    are too prominent at this halo mass. 
+    This types of comparisons between our HSC data and predictions from simulations 
+    will help to fine-tune simulations and to also investigate the main physical 
+    mechanisms that drive the assembly of massive galaxies and the build up of 
+    stellar envelopes.
+
+    Table~1 provides tabulated values for the median profiles that are 
+    displayed in Fig~\ref{fig:avg_prof}. 
+    These profiles are also available  
+    \href{https://github.com/dr-guangtou/hsc_redbcg/tree/master/profiles}{here}:
+    {\url{https://github.com/dr_guangtou/hsc_redbcg/tree/master/profiles/}}.
+
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
+\subsubsection{Environmental Dependence of the Profiles of Massive Galaxies}
     \label{sssec:sbp_mtot}
 
-    Finally, we will look into the environmental dependence of structures in massive 
-    galaxies using the \mden{} profiles of the \rbcg{} and \nbcg{} samples that are 
-    carefully matched in \mstar{} and redshift using KDTree algorithm. 
-    We discuss the details and quality of the matching procedure in 
-    Appendix~\ref{app:match} (see Fig~\ref{fig:match}. 
-    The matched redshift distributions within $0.3 < z < 0.5$ ensures the \mden{} 
-    profiles from both samples are impacted by seeing and background at similar level. 
-    As for the \mstar{}, we choose to match using two physically meaning definitions.
+    We now ask whether or not galaxies from our sample have \mden{} profiles that 
+    depend on \mhalo{} (at fixed \mstar{}). 
+    For this, we will build matched samples drawing from \rbcg{} and \nbcg{} that are 
+    carefully matched in \mstar{} and redshift using a KDTree algorithm 
+    (see Appendix~\ref{app:match} and Fig~\ref{fig:match} for details). 
+    By matching the redshift distributions within $0.3 < z < 0.5$, we ensure that the 
+    \mden{} profiles from both samples are impacted by seeing and background subtraction 
+    at similar levels. 
+    To match the two samples by stellar mass, we will use two different methods:
 
     \begin{itemize}
-        \item \mtot{} as the proxy of the ``total'' \mstar{} that include the stellar 
-            envelope.  As mentioned earlier, we match the two samples within 
-            $11.6 < $\logmtot{}$<11.9$ (median \logmtot{}$\sim 11.74$).
-            For the 45 \rbcg{} galaxies, we have 229 unique \nbcg{} galaxies in the 
-            matched sample.
-            Within this \mtot{} range, 100 kpc equals to 5-8 times of the effective 
-            radius, so should enclose most their \mstar{}. 
-            In practice, this choice also reflects the radius range that we can safely 
-            measure \mden{} profile given the depth of the image and the accuracy of 
-            background subtraction.
-
-        \item \minn{} as the proxy of the \mstar{} of the ``in-situ'' component.
-            This is motivated and supported by recent observations and simulations, 
-            and we will discuss more about this assumption in 
+
+        \item We match the two samples according to \mtot{}. 
+            We select galaxies from \rbcg{} with $11.6 < $\logmtot{} $<11.9$ 
+            (median \logmtot{} ${\sim} 11.74$). 
+            There are 45 \rbcg{} galaxies in this range. 
+            We then match this distribution by drawing galaxies from \nbcg{}. 
+            There are 229 unique \nbcg{} galaxies in the matched sample. 
+            In this \mtot{} range, 100 kpc corresponds to 5-8 times the effective radius 
+            and \mtot{} is a good proxy of total stellar mass.
+
+       \item We match the two samples according to \minn{}. 
+           We select galaxies from \rbcg{} with $11.2 < $\logminn{}$ < 11.6$ 
+            (median \logminn{}${\sim} 11.36$).
+            For the 56 galaxies from the \rbcg{} sample, we achieve excellent matches
+            in \minn{} and redshift using 375 \nbcg{} galaxies.
+            Motivated by recent observations and simulations, we use \minn{} as the 
+            proxy of the \mstar{} of the ``in-situ'' component.
+            We will discuss more about this assumption in 
             Section~\ref{sec:discussion}.
-            We match the two samples within $11.2 < $\logminn{}$ < 11.6$ 
-            (median \logminn{}$\sim 11.36$).
-            For 56 galaxies in this \rbcg{} sample, we achieve excellent matches
-            using 375 \nbcg{} galaxies.
+
     \end{itemize}
 
-    We show the comparison of the \mtot{}-matched (\minn{}-matched) samples in the 
-    left (right) panel of Fig~\ref{fig:prof_1}.
-
-    For the \mtot{}-matched comparison, it is easy to see that the \mden{}
-    profiles of \rbcg{} and \nbcg{} galaxies \textbf{greatly overlap with each 
-    other over the entire radius range}, which partially explains the difficulties in 
-    confirming any environmental dependence of structure in earlier works.
-    Although the central galaxies from more massive halos do not form a unique 
-    population in term of their structures comparing with the ones in less massive
-    halos at similar \mtot{}, we can still spot interesting differences in their 
-    median profiles: the \rbcg{} galaxy on average has slightly more flattened inner 
-    profile and more significant outer stellar envelope than the \nbcg{} one.
-    We highlight these subtle differences in the bottom panel using the difference 
-    between the two median profiles and its uncertainty. 
-    Given the noticeable uncertainties of \mtot{} and $\lambda$, along with the 
-    small size of the current \rbcg{} sample, we perform statistical test to confirm 
-    the robustness of the result \footnote{We mix the $N_{\mathrm{r}}$ \rbcg{} 
-    galaxies and the $N_{\mathrm{n}}$ \mtot{}-matched \nbcg{} ones together, then 
-    randomly draw $N_{\mathrm{r}}$ galaxies with putting-back, compute the difference 
-    between the median profile of this sample and the \nbcg{} sample. 
-    After repeating this process 2000 times, we can evaluate the possibility that 
-    the systematic differences in median \mden{} profiles can be reproduced by random 
-    selection of massive galaxies.}
-    In both inner and outer regions, we conclude the systematic differences in 
-    median \mden{} profiles are significant and robust.
-    Interestingly, the median profiles for \rbcg{} and \nbcg{} cross each other 
-    at $\sim 15$-20 kpc, quite close to the expected $R_{\mathrm{e}}$ for ETGs 
-    this massive. 
-    In Appendix~\ref{app:robust}, we further prove the robustness of this 
-    interesting result by showing that it is not affected by the range of redshift,
-    range of richness, and the choice of proxy for ``total'' \mstar{} 
-    (see Fig~\ref{fig:prof_3}). 
-    We also explore the possible \mtot{}-dependence of this structural difference 
-    despite the limitation of \mstar{}-completeness and small sample size
-    (see Fig~\ref{fig:prof_2}) in Appendix~\ref{app:robust}.
-    Although the systematic differences are very similar in different \mtot{} bins, 
-    we do find some hints that suggest the environmental dependence becomes more 
-    significant at the more massive end.  
-    This evidence could have intriguing implication in the assembly history of 
-    massive galaxies, and is worth more investigations with larger and more completed 
-    sample later.
-
-    \textbf{All these tests confirm that we robustly detect subtle, but systematic 
-    \mhalo{}-dependence (environmental dependence) of structure in massive, 
-    central galaxies} that seems to be consistent with the expectation of more frequent 
-    (minor) mergers in denser environment. 
-    These minor, non-dissipative mergers do not alter the inner \mden{} profiles 
-    a lot, but are efficient in depositing stellar mass onto the outer envelope
-    (e.g. \citealt{Hilz2013}, \citealt{Oogi2013}).
-
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %% 
-    Meanwhile, the subtlety of this environmental dependence for \mtot{}-matched 
-    samples seems to suggest that environment plays a secondary role in shaping 
-    the structure of galaxies at fixed total stellar mass, and it encourages us to find
-    another interesting angle.  
-    For instance, for massive galaxies that formed similar amount of stars through 
-    intensive star formation at high redshift, how the environments affect their mass 
-    assembly history in the second phase? 
-    We attempt to investigate this question through comparing the \mden{} profiles of 
-    the \minn{}-matched \rbcg{} and \nbcg{} galaxies (right side of 
-    Fig~\ref{fig:prof_1}).
-    Assuming we are now comparing the average structures of massive galaxies that share 
-    similar \mstar{} in the ``in-situ'' component, we start to see the environmental 
-    dependence much more clearly without any statistical test.     
-    The median \mden{} profiles of \rbcg{} and \nbcg{} galaxies are quite similar in 
-    the inner 5-10 kpc, but the \rbcg{} galaxies clearly show much more prominent
-    outer envelope.
-
-    It is also worth noting that \mden{} profiles of massive galaxies have quite uniform
-    slope and small scatter inside 10 kpc.  
-    In contrast, their outer profiles could have a large range of slopes and much 
-    larger scatters than the inner region. 
-    It seems to suggest that the inner and outer parts of massive galaxies are shaped 
-    by distinctive physical processes, and are affected by their environment at 
-    very different level. 
-    Given the highly dissipative nature of the ``in-situ'' phase, the similarity of 
-    inner profiles is consistent with the idea that processes like wet-merger and 
-    star burst often create de~Vaucouleur-like ($n\sim 4$) \mden{} profile
-    (e.g. \citealt{Hopkins2008}).
-    At the same time, the outer envelope of massive galaxies are predicted to be 
-    gradually assembled by non-dissipative mergers, which is a stochastic process and 
-    is more affected by the environment.  
-    Therefore, it is natural to see larger diversity in the outer profiles of 
-    low-$z$ massive galaxies. 
-    On average, massive galaxies in more massive halos show shallower outer \mden{} 
-    profiles, which is in qualitative agreement with recent simulation
-    (e.g. \citealt{Pillepich2014}).
+%% ------------------------------------------------------------------------------------ %%     
+    Fig~\ref{fig:prof_1} compares the profiles of galaxies at fixed \mtot{} and at fixed 
+    \minn{} for our two matched samples, and shows the main results of this paper which 
+    is that we find a clear halo mass dependence in the \mden{} profiles of massive 
+    galaxies. 
+    The bottom panel of Fig~\ref{fig:prof_1} shows the difference between the two 
+    profiles, $\Delta = \log(\mu_{\star, \mathrm{cenHighMh}}) - 
+    \log(\mu_{\star, \mathrm{cenLowMh}})$, 
+    with errors computed via bootstrap resampling. 
+    In Appendix~\ref{app:robust}, we present a variety of tests that verify the 
+    robustness of these results against different uncertainties.
+
+    There are several important points to be noticed in Fig~\ref{fig:prof_1}. 
+    First, when galaxies are matched by \mtot{}, although we detect a robust 
+    environmental dependence, it mainly only becomes prominent in the outskirts 
+    at $R>50$ kpc. 
+    This partially explains the difficulties for previous works to detect this effect
+    on shallower images. 
+    Second, we find that central galaxies in more massive dark mater halos display 
+    more flattened inner profile and more significant outer stellar envelope than 
+    the ones living in less massive halos. 
+    Third, the median \mden{} profiles of \rbcg{} and \nbcg{} cross each other 
+    at ${\sim} 15$-20 kpc, the expected $R_{\mathrm{e}}$ for ETGs at this \mtot{}. 
+    Finally, such systematic difference in structure may become more significant 
+    at very high-mass end. 
+    We see evidence of this effect when we compare the $Delta$ profiles in two \mtot{} 
+    bins (see Fig~\ref{fig:prof_2} and discussion in 
+    Appendix~\ref{app:robust})\footnote{Though the lower \mtot{} bin becomes somewhat
+    incomplete} and when we discuss the relation between \mtot{} and \minn{} for 
+    these two samples (see Fig~\ref{fig:scaling_relation}). 
+    This potential interesting result and its implication is worth more investigations 
+    later.
+
+    Meanwhile, the subtle environmental dependence of \mden{} profiles for the 
+    \mtot{}-matched samples suggests that environment does not play the major role in 
+    shaping massive galaxies \textbf{at fixed total stellar mass}.
+    Therefore it is interesting to ask, for massive galaxies that \textbf{contain 
+    similar \mstar{} in the in-situ component}, how does environment affect their 
+    subsequent mass assembly?
+    Assuming that the \minn{} is reasonable proxy of in-situ mass, we look into this 
+    question by comparing the \mden{} profiles of the \minn{}-matched samples ( 
+    Fig~\ref{fig:prof_1}, right).  
+    Although the median \mden{} profiles are similar at $r \leq 10$ kpc, the
+    central galaxies in more massive halos clearly possess much more prominent outer
+    envelope. 
+    This result is robust in a series of statistical and systematical tests 
+    (see Appendix~\ref{app:robust}.
+
+    At the same time, the uniform slope of the \mden{} profiles within 
+    10 kpc is in sharp contrast with the large scatter of the outskirts. 
+    It hints that these two regions are shaped by distinctive processes, and may 
+    explain their differences in environmental dependency. 
+    In simulations, intensive dissipative process helps create 
+    self-similar de~Vaucouleur-like ($n{\sim} 4$) \mden{} profile in the inner part 
+    of massive galaxy (e.g. \citealt{Hopkins2008}), and the \mhalo{}-dependent
+    merging history leads to shallower stellar halo profile for central galaxy 
+    of more massive halo (e.g. \citealt{Pillepich2014}). 
+    The stochastic nature of the merging process also helps explain the 
+    large scatter in the distributions of outer \mden{} profiles. 
     We illustrate this interesting diversity in Fig~\ref{fig:m100_m10_color}, where 
     we show the 3-color images of randomly selected massive central galaxies that 
-    have similar \minn{} ($11.1 \leq \log (M_{\star,\ 10\mathrm{kpc}}/M_{\odot}) < 11.2$)
+    have similar \minn{} 
+    ($11.1 \leq \log (M_{\star,\ 10\mathrm{kpc}}/M_{\odot}) < 11.2$)
     but different \mtot{}.   
@@
 
-    As with the \mtot{}-matched sample, the results are very robust against 
-    sample details, definition of ``inner'' \mstar{} and the \minn{} bins. 
-    In Appendix~\ref{app:match}, we also show that:
-    1) When we match using both \minn{} and \meff{}, we end up with \rbcg{} and \nbcg{} 
-    samples with perfectly matched inner median \mden{} profiles, while the different 
-    in the outskirt remains the same (see the left figure of Fig~\ref{fig:prof_4}).  
-    2) Also, the results will not change even when only a more \mstar{}-complete sample
-    (\logmtot{}$> 11.5$) is considered (see the right figure of Fig~\ref{fig:prof_4}).
-
-    The median profiles shown in Fig~\ref{fig:prof_1} are available in Table.1.
+    \textbf{In summary, we reliably detect subtle, but systematic \mhalo{}-dependence 
+    (environmental dependence) of structure in massive central galaxies}, which seems 
+    to be consistent with the expectation of more frequent (minor) mergers in denser 
+    environment. 
+    These minor, non-dissipative mergers do not alter the inner \mden{} profiles 
+    a lot, but are efficient in depositing stars to the outer envelope
+    (e.g. \citealt{Hilz2013}, \citealt{Oogi2013})
+
+    The median profiles shown in Fig~\ref{fig:prof_1} are available in Table~1.
 %% ------------------------------------------------------------------------------------ %%
@@
       \caption{
-          Comparisons of the radial profiles of ellipticity and optical colors 
-      	  for \mtot{}-matched (\textbf{left figure}) and \minn{}-matched 
-      	  (\textbf{right figure}) of \rbcg{} (orange-red) and \nbcg{} (grey-black) samples. 
-          The formats are very similar to the figure for \mden{} profile 
-          (e.g. right figure of Fig~\ref{fig:prof_1}). 
-          On each side, from top to bottom, we show the elliptical profile, and the 
-          color profile using $g-r$ and $g-i$ color. 
-          Since the individual profile of these properties has very large uncertain in the 
-          outskirt, we block the region at large radii where we think the median profiles 
-          are still unreliable using a dark, shaded box.
-          We also compare these results with previous results based on SDSS images. 
-          They are: 
-          1) Ellipticity profile of the stacked image of a large sample of red galaxies at 
-          $z\sim 0.4$ from \citet{Tal2011} with PSF correction 
-          (solid blue line on top panel); 
-          2) Ellipticity and $g-r$ color profiles from stacking analysis of nearby massive 
-          galaxies with high concentration index ($C>2.6$) in \citet[][blue dash lines 
-          on the top and middle panels]{DSouza2014}; 
-          3) average $g-r$ and $g-i$ color profiles for a large sample of nearby 
-          elliptical galaxies in \citet[][blue, solid lines on the middle and bottom 
-          panels]{LaBarbera2010}.
+          Radial variations in ellipticity and optical colors for massive galaxies. 
+          The format of this figure is similar to the right hand side of 
+          Fig~\ref{fig:prof_1}. 
+          Top panels show the ellipticity profile, middle panels show $g-r$, and lower 
+          panels show $g-i$. 
+          We compare our results with those from \citet{Tal2011} based on stacking 
+          large samples of luminous red galaxies in SDSS at $z{\sim} 0.4$ 
+          (solid blue line on top panel). 
+          We also compare with the results from a stacking analysis of nearby massive 
+          galaxies with high concentration index ($C>2.6$) in 
+          \citet[][blue dash lines on the top and middle panels]{DSouza2014}. 
+          Finally, we also compare with the average $g-r$ and $g-i$ color profiles 
+          from a large sample of nearby elliptical galaxies in \citet[][blue, solid 
+          lines on the middle and bottom panels]{LaBarbera2010}.
           }
@@
 
-    Besides the 1-D \mden{} profiles, the radial profiles of isophotal shape and colors 
-    are also useful diagnostic tools to study massive galaxies. 
-    Here, we extract the radial profiles of ellipticity and $k$-corrected optical colors
-    of galaxies in both \mtot{}-matched and \minn{}-matched samples (used in 
-    Fig~\ref{fig:prof_1}) using \texttt{Ellipse}, and compare the average profiles between
-    the \rbcg{} and \nbcg{} samples for two main purposes:
+%% ------------------------------------------------------------------------------------ %% 
+    We now study how the ellipticities (computed via \texttt{Ellipse}) and $k$-corrected 
+    optical colors of massive galaxies vary with radius. 
+    We also study whether or these radial trends differ between our various samples. 
+    These quantities contain interesting information about the physical processes that 
+    shape galaxies, but here we study them mainly with two goals in mind:
 
     \begin{enumerate}
-        \item To see whether the ellipticity profile strongly depends on environment, 
-            and to see whether 1-D \mden{} profiles using average isophotal shape is 
-            appropriate for the goal of this work.
-
-        \item To verify that the average color gradient does not strongly depend on 
-            the environment, and is not steep enough to invalid the assumption that   
-            it is reasonable to use average \m2l for comparing massive galaxies. 
+
+        \item To see whether the ellipticity profile depends strongly on environment, 
+            and to see whether or not the fact that we use an using average isophotal 
+            shape for our our 1-D \mden{} profiles has any impact on our results.
+
+        \item To verify that the average color gradient does not depend strongly on 
+            the environment and that is not steep enough to cause a problem with our 
+            choice the assumption that it is reasonable to use average \m2l for 
+            comparing massive galaxies. 
             We extract color profiles by applying the isophotes in $i$-band to images 
             in other bands in ``forced photometry'' manner.
+
     \end{enumerate}
 
-    Since we do not correct the differences in sky subtraction and seeing across 
-    different bands, we simply ignore the ellipticity and color in the inner-most and 
-    very low surface brightness regions (profiles are useful between 5-50 kpc). 
+    We compute ellipticities and color profiles in the radial range of 5-50 kpc 
+    (this is the range where we can safely ignore differences in sky subtraction and 
+    seeing across different bands). 
     We apply Galactic extinction and $k$-correction to both $g-r$ and $g-i$ color 
@@
     \mtot{}-matched (\minn{}-matched) samples of \rbcg{} and \nbcg{} galaxies on the 
-    left (right) side of \ref{fig:ell_color}, and also compare them with previous 
-    estimates that are based on stacking analysis of SDSS galaxies 
+    left (right) side of \ref{fig:ell_color}. 
+    We also compare our results with previous work based on stacking SDSS galaxies 
     (e.g. \citealt{LaBarbera2010, Tal2011, DSouza2014}).
 
-    Firstly, the ellipticity of massive galaxies steadily increase with radius 
-    from $e\le 0.2$ around 5-10 kpc to $e\sim 0.3$ at 40-50 kpc, in consistent with 
-    previous 2-D modeling results \citep{Huang2013a}.  
-    For the \mtot{}-matched samples, their ellipticity profiles are very similar 
-    all the way to 50 kpc (2-3$\times R_{\mathrm{e}}$ for their \mstar{}). 
-    Meanwhile, for the \minn{}-matched samples, the \rbcg{} galaxies have higher 
+    We find that in general, the ellipticities of massive galaxies increases with 
+    radius from $e\le 0.2$ around 5-10 kpc to $e{\sim} 0.3$ at 40-50 kpc. 
+    This is consistent with previous 2-D modeling results from \citet{Huang2013a}. 
+    The ellipticity profiles of the \mtot{}-matched samples are very similar at 
+    $r<50$ kpc (2-3$\times R_{\mathrm{e}}$ for their \mstar{}). 
+    However, for the \minn{}-matched samples, the \rbcg{} galaxies have higher 
     ellipticity than the \nbcg{} ones at $r > 10$ kpc, while their inner ellipticity 
@@
     This further hints that massive central galaxies in different halos but with 
-    similar ``in-situ'' mass could experience different merging history.
-    And, given he relative low ellipticity value and shallow ellipticity profile, 
-    we conclude that average isophote is appropriate for the structural comparisons 
-    we performed.
-    Previously, people often rely on image stacking method to extract ellipticity 
-    profile out to large radius (e.g. \citealt{Tal2011}, \citealt{DSouza2015}).
-    Comparing with the ellipticity profile directly measured on deep HSC image, 
-    we find that the stacked ellipticity profiles tend to underestimate the 
-    ellipticity in the outskirt. 
-    Since the ellipticity profile contains interesting information of the assembly 
-    history, we think it highlights the advantage of the HSC image in studying 
-    massive galaxies again, and it would be very interesting to compare with 
-    numerical simulations on this.
-
-    % \citet{Tal2011} stacked the SDSS images of a large sample of Luminous Red 
-    % Galaxies (LRGs) at $z\sim 0.4$, and extract the ellipticity profile after 
-    % correcting the PSF convolution effect.   
-    % Its slope is much shallower than the average ones using HSC images, despite the 
-    % two samples are at similar redshift and are quite comparable. 
-    % The poorer seeing condition of SDSS image plus the systematics in the stacking 
-    % process can easily explain this. 
-    % \citet{DSouza2015} performed similar stacking analysis for a large sample of very 
-    % nearby ETGs.  
-    % The ellipticity profile is quite consistent with our average ones within 5-10 
-    % kpc, but become much shallower at outer region.  
-    % The lower average \mstar{} of their sample and/or the uncertainties in the 
-    % stacking analysis may explain this.  
-    % This highlights the advantages of the high-resolution, deep HSC images again,
-    % and it would be very interesting to compare with numerical simulations.
-
-    Secondly, we see shallow and negative gradients of average $g-r$ and $g-i$ color 
-    profiles for both \rbcg{} and \nbcg{} galaxies. 
+    similar ``in-situ'' mass may experience different late-time merging histories. 
+    Overall, the relative low ellipticity value and the fact that the ellipticity 
+    gradients are shallow lead us to conclude that the use of an average 
+    isophotal ellipticity is fine for this present study.
+
+    Previous attempts to constrain ellipticity gradients have relied on image 
+    stacking techniques (e.g. \citealt{Tal2011}, \citealt{DSouza2015}). 
+    Compared to our measurements, we find that stacked ellipticity profiles tend to 
+    underestimate the ellipticity in the outskirt. 
+    Ellipticity profiles contain additional information about the assembly histories 
+    and in future work, it would be of interest to compare our ellipticity profiles 
+    with predictions from hydrodynamic simulations such as Illustris 
+    (\citealt{Vogelsberger2014}, \citealt{Genel2014}) or \textit{Horizon-AGN} 
+    (\citealt{Dubois2014}).
+
+    In terms of color gradients, we find shallow and negative gradients of median 
+    $g-r$ and $g-i$ color profiles for both \rbcg{} and \nbcg{} galaxies. 
     For both \mtot{}- and \minn{}-matched samples, we find no significant difference
@@
     average \m2l{} value to estimate \mden{} profiles.
-    The median $g-r$ color profiles are quite consistent with the ones based on 
+    The median $g-r$ color profiles are quite consistent with those based on 
     stacked SDSS images. 
-    For $g-i$ profiles, the HSC ones are slightly deeper than the SDSS ones, but we 
-    need to remind you the so-called ``red-halo'' effect of extended PSF wing in 
-    SDSS $i$-band (e.g. \citealt{Wu2005}, \citealt{Tal2011}) that could make the 
-    color appears redder.
-    Thank to the thickness of the CCD, the HSC $i$-band image can help provide more 
-    accurate color estimates as it does not suffer from the ``red-halo'' effect.
-
-    These results suggest that multi-band, 2-D information will help us piece together
-    a more complete view of massive galaxy evolution, but also point out limitations 
-    of the 1-D \mden{} profile analysis. 
-    In the near future, we will come back to this point with the help of 2-D modeling
-    method.
-
-    % On the left of Fig~\ref{fig:ell_color}, we see that the \rbcg{} and \nbcg{} 
-    % samples share very similar color profiles from 5-50 kpc. 
-    % This is very good news for using average \m2l{} in the comparisons of \mden{}
-    % profiles: although the \mden{} profiles may not be perfectly accurate, there 
-    % should be no bias when comparing the average profiles of \rbcg{} and \nbcg{} 
-    % samples.
-
-    % On the right side of Fig~\ref{fig:ell_color}, the situation is very similar 
-    % as the slopes of color gradients are basically the same for two samples; 
-    % although there might be some evidence that, when matched at similar \mstar{} 
-    % of the ``in-situ'' component, the \rbcg{} galaxies tend to have slightly redder
-    % envelopes than the \nbcg{} ones. 
-    % This is worth further investigation, especially via multi-band, 2-D 
-    % decomposition method.
-
-    % Although the 1-D analysis is not perfect, these preliminary results already 
-    % point out the importance and benefits of including multiband, 2-D information 
-    % into account. 
-    % Now we know that, for massive central galaxies with similar \mtot{}, the average 
-    % \mden{} profiles show subtle dependence on halo mass, while the color and 
-    % ellipticity profiles are very stable.  
-    % On the other hands, for central galaxies that have the same \mstar{}, ellipticity 
-    % and color profiles within 10 kpc, their outer envelopes appears to be strongly 
-    % depend on environments.
-
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %% 
-\subsection{Environmental Dependence of Scaling Relations}
+    For the $g-i$ profiles, the HSC ones show steeper gradients than the SDSS ones, 
+    however, it is important to point out that the SDSS $i$-band suffers from the 
+    so-called ``red-halo'' effect of (e.g. \citealt{Wu2005}, \citealt{Tal2011}) that 
+    could make the SDSS color appears redder. 
+    In contrast, HSC $i$-band image do not suffer from this effect (thanks to thick 
+    CCDs), therefore can help provide more accurate color estimates.
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
+\subsection{The Environmental Dependence of Scaling Relations}
     \label{ssec:scaling}
@@
       \caption{
-          \textbf{Left}: The \mstar{}-size relations for \rbcg{} 
-          (orange squares) and \nbcg{} (grey dots) galaxies. 
-          Here we use the \mtot{} as proxy of total \mstar{}, and use the 
-          $R_{\mathrm{50}}$ derived from the 1-D profile as size estimate. 
-          Two vertical lines highlight the $11.6<$\logms{}$<11.9$ mass bin.
-          We visualize the best-fit \mstar{}-$R_{\mathrm{50}}$ relations of \rbcg{} 
-          (red, solid line) and \nbcg{} (grey, dash line) galaxies at high-\mstar{} end.
-          The shaded regions in lighter colors show the 1-$\sigma$ uncertainties
+          \textbf{Left}: The mass-size relations for \rbcg{} (orange squares) and 
+          \nbcg{} (grey dots) galaxies. 
+          Two vertical lines highlight our $11.6<$ \logms{} $<11.9$ mass bin. 
+          The red solid line shows the best fit mass-size relation for \rbcg{} and the 
+          grey dashed line shows the best fit relation for \nbcg{}. 
+          Shaded regions in lighter colors show the 1-$\sigma$ uncertainties
           from MCMC sampling.  
-          We also compare with the \mstar{}-$R_{\mathrm{50}}$ relation for nearby central 
-          galaxies in massive groups from \citet{HCompany13} (green, long dashed line). 
-          Please refer to the text for more details.~
+          The green dashed line shows the mass-size relation for nearby central 
+          galaxies in massive groups from \citet{HCompany13}. 
           \textbf{Right:} The relations between \mtot{} and \minn{} for the 
           \rbcg{} and \nbcg{} galaxies, along with the best-fit scaling relations for 
-          both samples.  The format is the same with the left one.
+          both samples.
           }
@@
 
-\subsubsection{Mass-Size relation}
+\subsubsection{Mass-Size Relation}
     \label{sssec:mass_size}
 
-    Despite being the focus of previous investigations (e.g. \citealt{Shankar2013};
-    \citealt{Leja2013}, \citealt{vdWel2014}), the relation between \mstar{} and 
-    effective radius (or half-light radius; $R_{\mathrm{e}}$ or $R_{\mathrm{50}}$) 
-    has yet to provide clear evidence of environmental dependence of structures of 
-    massive galaxies at low-$z$ (e.g. \citealt{Weinmann2009}, \citealt{Nair2010}, 
-    \citealt{HCompany13}, \citealt{Cerbrian2014}), and sent controversial messages 
-    about the pictures at high-$z$ (e.g. \citealt{MCooper2012}, \citealt{Papovich2012}, 
-    \citealt{Kelkar2015}).
-    Now, according to the previous comparisons of \mden{} profiles, the deep HSC images 
-    also promise evidence of the environmental dependence of mass-size relation 
-    (see the left panel of Fig~\ref{fig:scaling_relation}).
-
-    We use the \mtot{} as the proxy of ``total'' \mstar{}, and the radius that encloses 
-    50\% of luminosity within 100 kpc ($R_{\mathrm{50}}$; derived from $i$-band 
-    curve-of-growth) as the ``size'' to evaluate the relation.
+    Despite numerous attempts, previous studies have failed to clearly 
+    demonstrate the existence of an environmental dependence of mass-size relation
+    at low-$z$ (e.g. \citealt{Weinmann2009, Nair2010, HCompany13, Cerbrian2014})
+
+    %Despite being the focus of previous investigations (e.g. \citealt{Shankar2013};
+    %\citealt{Leja2013}, \citealt{vdWel2014}), the relation between \mstar{} and 
+    %effective radius (or half-light radius; $R_{\mathrm{e}}$ or $R_{\mathrm{50}}$) 
+    %has yet to provide clear evidence of environmental dependence of structures of 
+    %massive galaxies at low-$z$ (e.g. \citealt{Weinmann2009}, \citealt{Nair2010}, 
+    %\citealt{HCompany13}, \citealt{Cerbrian2014}), and sent controversial messages 
+    %about the pictures at high-$z$ (e.g. \citealt{MCooper2012}, \citealt{Papovich2012}, 
+    %\citealt{Kelkar2015}).
+
+    By using deep HSC images, and by comparing\mden{} profiles directly, 
+    we have shown that the structures of massive galaxies do depend on the masses of 
+    their host halos (see the left panel of Fig~\ref{fig:scaling_relation}). 
+    We now present our results in terms of the more traditional ``mass-size'' relation. 
+    For this purpose, we will use \mtot{} as our ``total'' \mstar{} and the radius 
+    enclosing 50\% of luminosity within 100 kpc ($R_{\mathrm{50}}$; derived from the 
+    $i$-band curve-of-growth) as our ``size''. 
     This definition of ``effective radius'' is more robust against structural details, 
     choice of model, and the background subtraction. 
-    Our massive galaxies are also big enough so we do not need to worry about seeing
-    correction.
-
-    On the left of Fig~\ref{fig:scaling_relation}, we see clear \mstar{}-size relations 
-    for both samples.  
-    At fixed \mtot{}, the distributions of $R_{\mathrm{50}}$ for the \rbcg{} and
-    \nbcg{} galaxies greatly overlap, but it seems that the \rbcg{} galaxies do have 
-    systematically higher $R_{\mathrm{50}}$. 
-    % For the \mtot{}-matched samples used in Fig~\ref{fig:prof_1}, the median 
-    % $\log (R_{\mathrm{50}}/\mathrm{kpc})$ values for the \rbcg{} and \nbcg{} are 
-    % $1.22\pm 0.02$ ($\sim 17.4\pm 0.75$ kpc) and $1.09\pm 0.01$ 
-    % ($\sim 12.3\pm0.3$ kpc), which confirm the above observation and is consistent with 
-    % the differences seen in Fig~\ref{fig:prof_1}.  
-    To confirm the differences, we fit the 
-    \logmtot{}-$\log (R_{\mathrm{50}}/\mathrm{kpc})$ relations at 
-    \logmtot{}$\geq 11.6$ using MCMC-sampling method via the ensemble sampler 
-    \texttt{emcee} (\citealt{Emcee})\footnote{Initial guesses are based on maximum 
-    likelihood estimates, and we assume reasonable flat priors for parameters}.
-    The best-fit relation for the massive \rbcg{} galaxies:
+    Our massive galaxies are large enough that we do not need to worry about the 
+    effects of seeing.
+
+    Fig~\ref{fig:scaling_relation} shows the \mstar{}-size relations for both samples. 
+    We fit the \logmtot{}-$\log (R_{\mathrm{50}}/\mathrm{kpc})$ relations at 
+    \logmtot{}$\geq 11.6$\footnote{We use MCMC and the ensemble sampler 
+    \texttt{emcee} (\citealt{Emcee}) with initial guesses are based on maximum 
+    likelihood estimates, and we assume reasonable flat priors for parameters.}.
+    The best-fit relation for \rbcg{} is:
 
@@
 
-    \noindent And for the massive \nbcg{} galaxies, we have:
+    \noindent And for \nbcg{}, we find:
 
@@
 
-    \noindent As shown in Fig~\ref{fig:scaling_relation}, the two samples follow 
-    relations with similar slope at high-mass end, while have different normalizations.
-    This result is robust against the ranges of \logmtot{}, also the definitions of 
-    ``total'' \mstar{} and  half-light radius (e.g. \mstar{} within different 120 or 150 
-    kpc, and the $R_{\mathrm{50}}$ derived within these apertures).
-
-    We qualitatively compare our results with the one for $z\leq 0.09$ central ETGs in  
-    $14\le$\logmh{}$<15$ halos from \citealt{HCompany13} (HC13; green solid line).
-    HSC13 used the group catalog by \citet{Yang2007} to estimate \logmh{} after
-    empirically convert their \mstar{} from the Kroupa IMF to the Chabrier one 
-    by applying a constant -0.05 shift (see \citealt{Bernardi2016}).
+    \noindent As shown in Fig~\ref{fig:scaling_relation}, the slopes of the \mtot{}-size 
+    relations are similar between the two samples, but the normalization of the 
+    \mtot{}-size relation is different for \rbcg{} compared to \nbcg{}. 
+    This result is robust against the ranges of \mstar{}, also the definitions of 
+    ``total'' \mstar{} and  half-light radius\footnote{Using \mstar{} within 120 or 150 
+    kpc, or using the $R_{\mathrm{50}}$ derived within these apertures will not change 
+    the results.}.
+
+    We qualitatively compare our results with \citealt{HCompany13} (HC13; green solid line) 
+    who studied $z\leq 0.09$ central ETGs in  $14\le$ \logmh{} $<15$ halos. 
+    HC13 used the group catalog by \citet{Yang2007} to estimate \mhalo{} after empirically 
+    convert their \mstar{} from a Kroupa IMF to a Chabrier IMF by applying a constant 
+    -0.05 shift (see \citealt{Bernardi2016}).
     They estimated the 2-D $R_{\mathrm{e}}$ using single-\ser{} model fitting to SDSS 
@@
     synthetic population model. 
-    We also increase the \mstar{} in HC13 by $+0.1$dex to account for the systematic 
+    We add $+0.1$dex to the HSC13 results to account for the systematic 
     difference between their BC03 and our FSPS model (see Appendix~\ref{app:sed}). 
-    In HC13, the authors found no difference among the mass-size relations for 
-    central galaxies in halos across $12.5\le$\logmh{}$<15.0$. 
     The mass-size distributions for both \rbcg{} and \nbcg{} galaxies follow the 
@@
     \logmtot{}$< 11.6$ where our samples start to become incomplete. 
-
-    In conclusion, we confirm that the massive central galaxies at $0.3 < z < 0.5$
-    follow \mstar{}-size relations that depend on their \mhalo{}. 
-    The central galaxies in denser environment (higher \mhalo{}) have slightly 
-    larger $R_{\mathrm{50}}$ comparing to the ones from smaller haloes at fixed 
+    In contrast to the present study, HC13 finds no halo mass dependence in the 
+    mass-size relation for $12.5\le$ \logmh{} $<15.0$ halos.
+    A possible explanation for this difference is that the region that strongly depends 
+    on halo mass is the low surface brightness outer envelope where the stars are 
+    mostly assembled through multiple mergers. 
+    This region is difficult to detect on shallow SDSS images, but the much deeper 
+    HSC images can provide accurate measurements of total \mstar{} and size.
+
+    In conclusion, we confirm that massive central galaxies at $0.3 < z < 0.5$
+    follow \mstar{}-size relations that depend on the masses of their host halos. 
+    Central galaxies in denser environment (higher \mhalo{}) have slightly 
+    larger $R_{\mathrm{50}}$ comparing to ones in smaller haloes at fixed 
     \mtot{}. 
@@
 %% ------------------------------------------------------------------------------------ %% 
-\subsubsection{Relations between stellar mass within different physical apertures}
+\subsubsection{\mtot{} - \minn{} Relation}
     \label{sssec:m100_m10}
 
-    Now we also want to explore the relationship between \mstar{} within different
-    apertures (\mtot{} v.s. \minn{}) as alternative tool to help us understand the 
-    relationship between \mhalo{} and the assembly history of massive galaxies.   
+    We also investigate the relationship between \mstar{} for two different
+    fixed physical apertures (\mtot{} v.s. \minn{}) as alternative tool to help us 
+    understand the relationship between \mhalo{} and the assembly history of massive
+    galaxies.   
     Comparing to the mass-size relation, this relation is not affected by the 
@@
 
-    We show the results in the right panel of Fig \ref{fig:scaling_relation}, and it 
-    is quite easy to notice that the distributions of \rbcg{} and \nbcg{} galaxies 
-    are offset with each other.  
-    Instead of arbitrarily grouping galaxies into different bins of \mtot{} or 
-    \minn{}, this relation brings us a more generic view of the environmental 
-    dependence of structure.
-    On the figure, we also illustrate the \mtot{}-\minn{} relations at 
-    \logmtot$\geq 11.6$ from MCMC sampling method.  
-    For \rbcg{} galaxies, the best-fit relation is:
+    The right panel of Fig \ref{fig:scaling_relation} compares \mtot{} and \minn{}. 
+    We find that our \rbcg{} and \nbcg{} occupy different locations within this plane,
+    and follow different best-fit \mtot{} - \minn{} relations. 
+    For \rbcg{} galaxies we find:
 
@@
 
-    These relations suggest that: (1) At fixed \mtot{}, central galaxy in more 
-    massive halo tend to have lower fraction fraction of \mstar{} stored in the inner
-    region; (2) For massive galaxies with similar \minn{}, the ones in more 
-    massive halos on average have more prominent outer envelopes.  
-    Assuming that the \minn{} traces the \mstar{} of the ``in-situ'' components 
-    reasonably well, this suggests that ``red nuggets'' at high-$z$ with similar 
-    \mstar{} end up following different assembly history that depends on their 
-    environments.
-
-    This result will not change if we replace the \minn{} with \mstar{} within 5 or 
-    15 kpc apertures.
+    We have checked that our results are unchanged if we replace the \minn{} with 
+    \mstar{} within 5 or 15 kpc apertures. 
     Although the $M_{\star, 5\ \mathrm{kpc}}$ values are less reliable than \minn{} 
@@
 
-    % Limited by our capability to estimate \mhalo{} with better accuracy or individually, 
-    % we can not further quantify this \mhalo{}-dependence here.
-    % Albeit that the \redm{} richness ($\lambda$) traces \mhalo{} reasonably well, 
-    % we do not find any clear correlation with $\lambda$ within the \rbcg{} galaxies.
-    % In the current sample, most of the \rbcg{} galaxies are centrals of clusters with 
-    % $30 \leq \lambda \leq 40$, and only a small fraction comes from more massive clusters.  
-    % Therefore, the small sample size, the uncertainties of richness from shallow SDSS
-    % images, and the intrinsic scatter of the $\lambda$-\mhalo{} relation may conspire to 
-    % stop us from extracting more information from this \mhalo{}-dependence.
-
-    This \mhalo{}-dependence can be caused by many different physical processes. 
-    Given the interesting results on the right panel of Fig \ref{fig:scaling_relation},
-    we recommend to apply similar scaling relation to different datasets and 
-    numerical simulations (e.g. see Fig~1 of \citealt{Wellons2016b}) to explore the 
-    physical origins and redshift evolution of this dependence.
-
+    Our results suggest that: 
+    (1) At fixed \mtot{}, central galaxies in more massive halos tend to have 
+    lower fractions of \mstar{} stored in the inner region; 
+    (2) For massive galaxies with similar \minn{}, the ones in more massive halos on 
+    average have more prominent outer envelopes. 
+    The scientific implication of this result is briefly discussed in 
+    Section~\ref{sec:discussion}.
 %% ------------------------------------------------------------------------------------ %%
@@
       \includegraphics[width=\columnwidth]{fig/redbcg_discussion_1}
-      \caption{Comparison of the average \mden{} profiles of massive galaxies in the 
+      \caption{Comparison of the median \mden{} profiles of massive galaxies in the 
           two lower \mtot{} bins from Fig~\ref{fig:avg_prof} with other observations 
@@
           We include: 
-          1) the average \mden{} profile of inner component from structure 
-          decomposition of massive elliptical galaxies at $z\sim 0$ from 
+          1) the median \mden{} profile of inner component from structure 
+          decomposition of massive elliptical galaxies at $z{\sim} 0$ from 
           \citet[][Cyan, solid]{Huang2013a}; 
-          2) the average \mden{} profile of massive galaxies at $1.0 < z < 1.5$ 
+          2) the median \mden{} profile of massive galaxies at $1.0 < z < 1.5$ 
           from \textit{HST} observations in \citet[][Red, dashed]{Patel2013}; 
-          3) the average \mden{} profile of the ``in-situ'' stellar components in 
+          3) the median \mden{} profile of the ``in-situ'' stellar components in 
           simulated massive halos from \citet[][Purple, dot-dashed]{Cooper13};
-          4) the \mden{} profile of the very massive cD galaxy at $z\sim 1.1$ 
+          4) the \mden{} profile of the very massive cD galaxy at $z{\sim} 1.1$ 
           discovered by \citet[][Yellow, dashed]{Liu2013} in the Hubble 
@@
 
-    Taking advantage of the deep images from the HSC survey, we show that,
-    \textbf{at $0.3 < z < 0.5$, the structure of massive central galaxy systematically 
-    depends on the mass of their host dark matter halo, at both the inner and outer
-    parts}. 
-    Here, we briefly discuss its physical origin, potential caveats, and more scientific 
-    implications.
+    By using deep imaging from the HSC survey we have shown that the stellar mass 
+    density profiles of massive central galaxies depend systematically on the mass 
+    of their host dark matter halos. 
+    Here we discuss the physical origin, scientific implications, and potential 
+    caveats of this result.
 
@@
 
-    Although the photometric data alone can not determine the origin of the 
-    \mhalo{}-dependence we found, \textbf{it does fit the expectations of the 
-    ``two-phase'' scenario at first glance}. 
-    For the massive centrals with similar \mstar{} formed in the ``in-situ'' phase at 
-    high-$z$, it is reasonable to expect that the following mass assembly histories 
-    depend on the environments or halo masses if this second phase of evolution is 
-    indeed dominated by merging with surrounding satellites. 
-    Since the non-dissipative minor mergers mostly accumulate stars onto the 
-    outskirts of the centrals without modifying their central \mden{} much
-    (e.g. \citealt{Oogi2013, Bedorf2013}), the outer stellar envelopes of massive
-    centrals should reflect the environmental dependence of structure better, exactly 
-    as we find from the comparisons of \mden{} profiles and scaling relations.
-
-    State of the art simulations suggest that the slope of the stellar halo becomes 
-    shallower in the central of more massive halos (e.g. \citealt{Pillepich2014}), 
-    this is consistent with the results in Fig \ref{fig:prof_1}. 
-    Meanwhile, these simulation also points out that not only the fraction of 
-    accreted stars increases steeply with total \mstar{}, the ``ex-situ'' component
-    starts to dominate the \mden{} profiles around the $R_{\mathrm{e}}$ for 
+    Our results are consistent with the picture that massive central galaxies form via 
+    a ``two-phase'' scenario. 
+    According to this theory, the cores of massive galaxies were formed at $z{\sim} 2$ 
+    during an intense period of in-situ star formation. 
+    The outskirts of massive galaxies are then built up via a more gradual second 
+    phase of evolution (the ``ex-situ'' phase) which is dominated by mass growth via 
+    the accretion of satellite systems. 
+    Non-dissipative minor mergers mostly deposit stars on the outskirts of the 
+    centrals and do not have large impact on the central \mden{} profile 
+    (e.g. \citealt{Oogi2013, Bedorf2013}). 
+    Hence, according to this picture, the outer stellar envelopes of massive centrals 
+    should correlate with the masses of their host halos, in qualitative agreement with
+    our findings.
+
+    State of the art hydrodynamic simulations suggest that massive dark matter halos 
+    have central galaxies that have outer stellar envelopes with shallow slopes 
+    (e.g. \citealt{Pillepich2014}). 
+    This is consistent with the results in Fig \ref{fig:prof_1}.
+
+    Meanwhile, these simulation also point out that the fraction of accreted stars 
+    increases steeply with total \mstar{} and that the ``ex-situ'' component
+    starts to dominate the \mden{} profiles around $R_{\mathrm{e}}$ for 
     \logms{}$\geq 11.5$ galaxies. 
-    In this work, we do notice that the median \mden{} profiles of \rbcg{} and \nbcg{} 
-    samples start to deviate from each around around 15-20 kpc, which is close to 
-    their $R_{\mathrm{e}}$, and environmental dependence of median \mden{} profiles 
-    become more significant in higher \mtot{} bin (see Fig \ref{fig:prof_4}). 
-    These results all support that the \mhalo{}-dependence of structure in massive 
-    central galaxies is driven by the amount and distribution of accreted stars 
-    in the outskirt.
-
-    In Fig~\ref{fig:discussion_1}, we compare the median \mden{} profiles of the 
+    In this work, we find that the median \mden{} profiles of \rbcg{} and \nbcg{} 
+    samples start to show differences around 15-20 kpc, which is close to 
+    their $R_{\mathrm{e}}$. 
+    Furthermore, the environmental dependence of our median \mden{} profiles 
+    becomes more significant in our highest \mtot{} bin (see Fig \ref{fig:prof_4}). 
+    These results all align with the picture that the \mhalo{}-dependence of the 
+    \mden{} profiles of massive galaxies is driven by the variations in the 
+    ``ex-situ'' component at large radii.
+
+    We now investigate to what degree our assumption that the inner 10 kpc \mstar{}
+    corresponds to an in-situ mass.    
+    Fig \ref{fig:discussion_1} compares the median \mden{} profiles of the 
     combined \rbcg{} and \nbcg{} samples in two \mtot{} bins 
-    ($11.4\leq$\logmtot{}$<11.6$ and $11.6\leq$\logmtot{}$<11.8$) with the median 
-    profiles of 
-    (1) massive ETGs at $1.0 < z < 1.5$ that are considered the progenitors of 
-    $\sim 10^{11.5} M_{\odot}$ ETGs at $z=0$ (\citealt{Patel2013}).  
-    After $z\sim 1.5$, the mass assembly of these galaxies should be dominated by 
-    mergers. 
-    (2) the inner components of $\sim 10^{11.4} M_{\odot}$ ellipticals at $z\sim 0$ 
-    from 2-D decomposition (\citealt{Huang2013a}). 
-    \citet{Huang2013b} showed that these components are similar to the compact 
-    ``red nuggets'' at high redshift in structure. 
-    (3) the ``in-situ'' components of simulated galaxies in massive halos from 
-    \citet{Cooper13} using particle-tagging technique (the inner $\sim 5$ kpc is 
-    quite uncertain due to the resolution).  
-    Despite the differences in median \mstar{} and details in \m2l{} 
-    estimates\footnote{We convert the \mden{} profiles to the same Chabrier IMF}, 
-    the comparison confirms that \minn{} should be reasonable proxy of the 
-    ``in-situ'' mass.  
-    More importantly, it shows that the \mden{} profile at $\mathrm{R} > 15$-20 kpc, 
-    where we find clear evidence of environmental dependence, is likely dominated by 
-    stars that are not in the ``in-situ'' component.
-
-    % Most of these literatures that we compare with are not dominated by the extremely 
-    % massive ones in the our sample, so the actual \mden{} median profile of the ``in-situ'' 
-    % components for \rbcg{} and \nbcg{} galaxies could be closer to the median profiles 
-    % shown in Fig~\ref{fig:discussion_1}.
+    ($11.4\leq$\logmtot{}$<11.6$ and $11.6\leq$\logmtot{}$<11.8$) with 
+    (1) the median \mden{} profiles of massive ETGs at $1.0 < z < 1.5$ in
+    \citealt{Patel2013} since they are considered as the progenitors of 
+    ${\sim} 10^{11.5} M_{\odot}$ ETGs at $z=0$.    
+    (2) the inner components of $z{\sim} 0$ ellipticals from 2-D decomposition 
+    (\citealt{Huang2013a}).
+    As proxy of the in-situ components, \citet{Huang2013b} showed they are 
+    structurally similar to the compact ``red nuggets'' at high-$z$. 
+    (3) the ``in-situ'' components of simulated central galaxies in massive halos 
+    from \citet{Cooper13} (the inner ${\sim} 5$ kpc is quite uncertain due to the 
+    resolution).  
+    The comparison confirms that \minn{} should be reasonable proxy of the 
+    ``in-situ'' mass\footnote{We convert these \mden{} profiles to the same 
+    Chabrier IMF; but there are still differences in median \mstar{} and 
+    details in the \m2l{} estimates}.  
+    More importantly, it shows that the \mden{} profile at 
+    $\mathrm{R} > 15$-20 kpc is likely dominated by stars that are not related 
+    to the ``in-situ'' processes.
 
     We also compare with a uniquely massive BCG at high redshift: 
-    a $\sim 10^{11.4} M_{\odot}$ BCG with distinctive ``cD''-like envelope at 
-    $z\sim 1.1$ (\citealt{Liu2013}).  
+    a ${\sim} 10^{11.4} M_{\odot}$ BCG with distinctive ``cD''-like envelope at 
+    $z{\sim} 1.1$ (\citealt{Liu2013}).  
     Its \mden{} profile follows the median profile of $11.6\leq$\logmtot{}$<11.8$ 
@@
     This unique object may present an interesting case where the inner ``core'' of a 
-    massive BCGs is already in pace at $z\sim 1$ when its extended envelope is still
+    massive BCGs is already in pace at $z{\sim} 1$ when its extended envelope is still
     under construction.
@@
     topic to investigate in the future.
+%% ------------------------------------------------------------------------------------ %%
 
@@
           Fig~\ref{fig:smf1}.~~
-          \textbf{Right}: The stellar mass volume-density distributions of massive galaxies 
-          after combining the \rbcg{} and \nbcg{} samples together, using both 
-          \mtot{} (black solid line) and \mmax{} (black dash line). 
+          \textbf{Right}: The stellar mass volume-density distributions of massive 
+          galaxies after combining the \rbcg{} and \nbcg{} samples together, using 
+          both \mtot{} (black solid line) and \mmax{} (black dash line). 
           The uncertainty for distribution using \mtot{} is shown in grey shaded region.  
           Here, we also compare the distributions with SMF from previous works: 
-          (a): SDSS galaxies at $z\sim 0.1$ from \citet{Bernardi2013}; the \mstar{} is 
-          based on photometry from 2-D \ser{}$+$Exponential model fitting; 
-          (b): SDSS galaxies at $z\sim 0.1$ from \citet{Moustakas13} based on 
+          (a): SDSS galaxies at $z{\sim} 0.1$ from \citet{Bernardi2013}; the \mstar{} 
+          is based on photometry from 2-D \ser{}$+$Exponential model fitting; 
+          (b): SDSS galaxies at $z{\sim} 0.1$ from \citet{Moustakas13} based on 
           improved SDSS \texttt{cModel} photometry; 
@@
 
-\subsection{On the Classification of "cD" Galaxies}
-
-    Among the massive galaxies in our sample (both \rbcg{} and \nbcg{} ones), we find that 
-    the distribution of their outer \mden{} profiles is quite smooth but also with a large
-    scatter (See Fig \ref{fig:avg_prof}) that blurs the boundary between ``normal'' 
-    elliptical galaxy and the so-called ``cD'' galaxies that are surrounded by a large 
-    and diffuse stellar envelope. 
-    Traditionally, the ``cD'' galaxies are often found among BCGs of nearby clusters, 
-    and treated as a distinctive population.
-
-    Now with the help of deep HSC images, we know that the BCGs only show subtle 
-    structural differences comparing to non-BCG galaxies with similar \mtot{}, hence do 
-    not form a unique population in term of structure (see Fig \ref{fig:prof_1}). 
-    The wide and smooth distributions of \mden{} profiles in the outskirt further suggest 
-    that it might not be very physically meaningful to separate these massive galaxies 
-    into two arbitrary morphological classes. 
-    This conclusion is similar to the result of \citep{Zhao2015} where the authors found 
-    a large fraction of nearby BCGs (34\%) does not fall into the ``cD'' class.
-
-    This continuous distribution of \mden{} profiles and its dependence on \mtot{} is 
-    also consistent with results from HST observations of BCGs at $0.3 < z <0.9$ 
-    (\citealt{Bai2014}) and the claimed positive correlation between luminosity and \ser 
-    index (e.g.\ \citealt{Savorgnan13}). 
-    Although single \ser{} model is not appropriate to describe the structure of these 
-    massive galaxies\footnote{Can not explain the diversity of \mden{} profiles; often 
-    fails dramatically at inner region; and can not follow the radial variation of 
-    isophotal shape}, we agree that its time to treat the stellar envelopes of massive 
-    galaxies as the outcomes of a series of merging events, and focus more on how to 
-    extract more information about their assembly histories through a more physical 
-    angle.    
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %%
-
-\subsection{What is the "Total Mass" of Massive Galaxies?}
-
-    Definition of ``total'' \mstar{} is always tricky for massive galaxies even 
-    with deep HSC images.
-    Although our choice of \mtot{} in 1-D has certain advantages over 2-D modeling 
-    method, and should contains most of the stellar contents of the galaxy, there
-    is no evidence that \mden{} profile truncates at 100 kpc. 
-    To illustrate this, we compare the \mtot{} wit the \mstar{} integrated  
-    to the maximum radius allowed by the profile (\mmax{}, Left of Fig 
-    \ref{fig:discussion_2}). 
-    This new definition results in higher value of ``total'' \mstar{}.
-    The difference is small (average: $\sim 0.04$ dex), but apparently depends on 
-    the slope of the stellar envelope. 
-    The \mden{} profiles outside 100 kpc are much less accurate, hence the \mmax{} 
-    is less reliable than \mtot{}. 
-    All the conclusions here also remain intact when replacing \mtot{} with 
-    \minn{}.  
-    However, it is still necessary to remind people again the difficulty of 
-    defining and measuring the \mstar{} of mass galaxies since there are 
-    situations when the scientific results heavily depend on it.
-
-    For instance, the SMF is one of the most important statistics when studying 
-    galaxy evolution. 
-    Yet, even at $z\sim 0$, the normalization and shape of SMF at high-mass end 
-    are still uncertain partly due to the above-mentioned issue 
-    (\citealt{Bernardi2016}) despite that they are critical for understanding the 
-    overall evolution of galaxies. 
-    In Fig~\ref{fig:smf1}, we illustrate how improved \mstar{} measurement can 
-    significantly modify SMF.  
-    On the right side of Fig~\ref{fig:discussion_2}, we further highlight that 
+\subsection{Scatter in Outer Stellar Enveloppes and ``cD'' Galaxies}
+
+   The thin lines in Figure \ref{fig:prof_1} show the \mden{} density profiles of 
+   individual galaxies. 
+   In general, we find that any given galaxy has a relatively smooth profile, even out 
+   to large radii, however, on a galax-by-galaxy basis there is a large (but continuous) 
+   variation in the amplitude of \mden{} at large scales. 
+   Traditionally, the so-called ``cD'' galaxies are defined to have large stellar 
+   envelopes and are found at the hearts of massive clusters (\citealt{Matthews1964, 
+   Schombert1988}). 
+   However, until present, it has not been clear whether ``cD'' galaxies are a distinct 
+   and special population, or if they are simply the continum of a smoothly varying 
+   population. 
+   Fig \ref{fig:prof_1} shows that with the help of our deep HSC images, we can directly 
+   map out the variations in \mden{} profiles at large scales. 
+   Instead of a bi-model distribution, we find that the outskirts of massive galaxies 
+   display a smooth but continuous variation. 
+   We can hence conclude that ``cD'' galaxies are simply the extremes of a continuous 
+   population but that do not necessarily form a unique a special class of galaxies. 
+   This suggests that it might not be very physically meaningful to separate these 
+   massive galaxies into two arbitrary morphological classes (``cD'' versus non-``cD''). 
+   This conclusion is similar to those of \citep{Zhao2015} who found that a large 
+   fraction of nearby BCGs (34\%) does not fall into the ``cD'' class. 
+   Our finding that massive galaxies display a diverse range of outer stellar 
+   envelope is also supported by HST observations of BCGs at $0.3 < z <0.9$ 
+   by \citealt{Bai2014}.
+
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
+\subsection{What is the ``Total Mass'' of Massive Galaxies?}
+
+    Even with deep HSC images, it is non trivial to clearly define and measure the
+    ``total'' \mstar{} for these massive systems. 
+    As discussed in Section~\ref{ssec:mtotal}, our 1-D approach has certain advantages 
+    over the 2-D modeling method and in principle, should capture a the majority of 
+    the stellar mass. 
+    However, even though we extend to 100 kpc, there is no evidence that the profile 
+    drops to zero on these scales. 
+    We now estimate how much extra mass is ``hidden'' beyond the 100 kpc radius. 
+    For this, we integrate the \mden{} profiles out to the detection limit in 
+    surface brightness profile that is defined by the background noise.
+    We will call this the ``maximum mass'' of the galaxy (\mmax{}). 
+    For obvious reasons, we find that \mmax{} is larger than \mtot{} with an average 
+    difference of about ${\sim}0.04$ dex. 
+    The left hand side of Fig \ref{fig:discussion_2} shows differences between \mtot{}
+    and \mmax{}. 
+    On a galaxy-by-galaxy basis, the difference \mmax{}-\mtot{} depends on the slope 
+    of the stellar envelope. 
+    In this work, we have opted to in general use \mtot{} rather than \mmax{} as the 
+    uncertainty on \mmax{} is larger. 
+    However, we have checked that none of our results are changed by replacing \mtot{} 
+    via \mmax{}.
+
+    How to define and measure the ``total'' mass of a galaxy becomes a critical 
+    question when studying the high-mass end of the galaxy SMF. 
+    The issues discussed above are currently one of the primary limitations in 
+    determinations of the high-mass end of the SMF (\citealt{Bernardi2016}). 
+    Fig~\ref{fig:smf1} illustrated how improved \mstar{} measurement can 
+    significantly modifies the SMF. 
+    On the right hand side of Fig~\ref{fig:discussion_2}, we further highlight that 
     the shape of SMF at high-mass end is quite sensitive to even very small 
     change of \mstar{}. 
-    We also compare the volume-density distributions of the combined \rbcg{} and 
-    \nbcg{} samples with published SMFs:
+    We also compare the SMFs of our HSC samples with the following previous studies:
 
     \begin{itemize}
-        \item SMF for SDSS-\textit{GALEX} sample of $z\sim 0.1$ galaxies from 
-            \citet{Moustakas13}. 
-            The total luminosity is based on SDSS \cmodel{} one; the \m2l{} is 
-            derived via SED fitting using \texttt{iSEDfit} with similar 
-            assumptions.
-        \item SMF for $z\sim 0.1$ SDSS galaxies from \citet{Bernardi2013}. 
+
+        \item The SMF derived from a SDSS-\textit{GALEX} sample of $z{\sim} 0.1$ 
+            galaxies from \citet{Moustakas13}. 
+            Here, the total luminosity is based on the SDSS \cmodel{} magnitude. 
+            The \m2l{} is derived via SED fitting using \texttt{iSEDfit} with similar 
+            assumptions as in our work.
+
+        \item The SMF for $z{\sim} 0.1$ SDSS galaxies from \citet{Bernardi2013}. 
             The total luminosity is based on 2-D \texttt{SerExp} models 
             (\ser{}$+$ Exponential disk model; integrated to infinity) that 
-            recover much more flux comparing with the \cmodel{} ones at 
-            high-luminosity end. 
+            recovers much more flux compared to SDSS \cmodel{} magnitudes. 
             The \m2l{} is also from SED fitting assuming a Chabrier IMF.
-        \item SMF for $0.15 < z < 0.30$ galaxies from the \texttt{S82-MGC} sample
-            \citep{Leauthaud2016}, where the \mstar{} is derived using 
+
+        \item The SMF for $0.15 < z < 0.30$ galaxies from the \texttt{S82-MGC} sample
+            \citep{Leauthaud2016} where the \mstar{} is derived using 
             \texttt{iSEDfit} on PSF-corrected aperture photometry from 
             \texttt{S82}.
+
     \end{itemize}
 
-    It is clear that SMFs from different groups show quite different slopes 
-    at high-mass end. 
-    Although we did not carefully separate the impacts from photometry and 
-    assumptions of stellar population models (e.g. \citealt{Bernardi2016}), 
-    we think the main cause of such differences should be photometry alone as 
-    the SED fitting results are based on the same IMF and similar assumptions.  
-    Serious comparison of SMF certainly deserves more careful treatment, 
-    but it is interesting to see that the SMF from \citep{Bernardi2013} has 
-    shallower slope at high-mass end than ours even they still rely on SDSS
-    images. 
-    It is important to look into this by comparing with 2-D models like the 
-    \texttt{SerExp} ones in the near future.
-
-    Finally, we want to point out that we do not separate the potential intra-cluster 
+%% ------------------------------------------------------------------------------------ %% 
+    It is clear that different analyses lead to very different slopes at high-mass end. 
+    Here, we do not try to evaluate whether the differences displayed in 
+    Fig~\ref{fig:discussion_2} are dominated by differences in photometry versus 
+    assumptions about stellar population models (e.g. \citealt{Bernardi2016}). 
+    However, given that the results that we are comparing assume the same IMF and adopt 
+    similar assumptions about stellar population models, we hypothesize that the 
+    differences in Fig~\ref{fig:discussion_2} are dominated by differences in photometry. 
+    The goal of our of present paper is not to present and discuss a careful evaluation
+    of the high-mass end of the SMF -- this will be presented in a forthcoming paper 
+    once the HSC survey has accumulated more data. 
+    However, this is clearly a topic that warrants further investigation, and careful 
+    photometry measurements from HSC data will shed further light on these questions.
+
+    Finally, we emphasize that in this present study we do not attempt to separate the 
+    light of the galaxy with a potential (and distinct) ``intra-cluster''
     light component (ICL; e.g. \citealt{Carlberg1997, Lin2004, Gonzalez2005, 
-    Mihos2005}), but rather treat the stellar distributions 
-    out to 100 kpc as an integrated structure.
-    Reliable isolation of physically meaningful ICL component using photometry 
+    Mihos2005}). 
+    Instead, we adopt the view that the light of the main galaxy and the 
+    ``intra-cluster''component are a smooth and continuous distribution. 
+    A reliable isolation of a physically meaningful ICL component using photometry 
     alone is extremely difficult, if not impossible. 
-    At the imaging depth of HSC, we find no evidence for a clearly separated 
-    component in \mden{} and other profiles. 
-    Our \rbcg{} sample contains only a small fraction of extremely massive clusters 
-    where strong evidence of photometric ICL component is often found. 
+    At the imaging depth of HSC, we find no evidence for a clearly distinction between 
+    an ``inner component'' and an ``intra-cluster'' component. 
+    Instead, most of our profiles are smoothly varying out to 100 kpc with little 
+    evidence for a distinct secondary component. 
+    We do note however, that our \rbcg{} sample contains only a small fraction of 
+    extremely massive clusters where strong evidence of photometric ICL component is 
+    often found (\mhalo{}$\simgt 10^{15}M_{\star}$). 
     At the typical \mhalo{} of our \rbcg{} clusters, one good nearby example would be 
@@
     tidal features.
-    That being said, we do not ignore the existence of stellar population in the 
-    very outskirt of BCG that are dynamically controlled by the cluster potential 
-    well, and save the discussion about its connection to the assembly of massive 
-    central galaxies to the future.  
+
 %% ------------------------------------------------------------------------------------ %%
@@
 
-    In this work, we study the how environment (halo mass) affects the structures and
-    assembly history of massive central galaxies using deep images from the Subaru HSC 
+    In this work, we study how environment (halo mass) affects the stellar mass density 
+    profiles of massive central galaxies using deep images from the Subaru HSC 
     survey. 
-    With the help of these high-quality data, we map the stellar mass distributions of 
-    large numbers of massive central galaxies at $0.3 < z < 0.5$ out to $>100$ kpc, 
-    and discussing their environmental dependence after grouping them into centrals of 
-    halos more and less massive than \mhalo{}$\sim 10^{14} M_{\odot}$. 
-    The main results here are:
+    With the help of this high-quality and wide area data set, we directly map the 
+    stellar mass distributions of ${\sim}7000$ massive central galaxies at 
+    $0.3 < z < 0.5$ out to $>100$ kpc without resorting to stacking techniques. 
+    We group massive central galaxies into two categories based on their host halo 
+    mass (\mhalo{}$\simgt 10^{14.2} M_{\odot}$ and \mhalo{}$\simlt 10^{14} M_{\odot}$). 
+    Our main results are:
 
     \begin{enumerate}
-        \item We find that the ``total'' \mstar{} of these massive galaxies could be 
-            significantly underestimated when shallow image (e.g. the SDSS ones) 
-            and/or imperfect model assumption (e.g. the \texttt{cModel}) are used.
-            In different with previous works, this result does not depend on stacking 
-            analysis or any parametric model. 
+        \item We find that the ``total'' \mstar{} of these massive galaxies can be 
+            significantly underestimated with shallow imaging data such as SDSS and/or 
+            imperfect model assumption (e.g. the \texttt{cModel} or single-\ser{}) 
+            are used. 
+            In contrast to previous work, our results do not depend on stacking or any 
+            parametric models. 
             Moreover, the level of such underestimation could also depend on the 
-            stellar mass. 
-            This should be carefully taken into account when discussing important 
-            topics like the stellar mass function and its evolution.
-        \item At fixed \mstar{} within 100 kpc, we find that the massive central 
-            galaxies in more and less massive halos have subtle, but systematic 
-            differences in their \mden{} profiles when their ellipticity and optical 
-            color profiles are very similar. 
-            On average, the ones from denser environments have slightly shallower 
-            inner \mden{} profiles while showing more prominent outer envelope.
-        \item Meanwhile, when matched at the same \mstar{} within inner 10 kpc--a 
-            proxy of the \mstar{} formed in the the ``in-situ'' channel, we find 
-            that the ones in more massive halos possess much more extended stellar 
-            envelope in the outskirts than the ones in smaller halos when the 
-            \mden{}, ellipticity, and optical color profiles inside 10 kpc show 
-            no dependence on environment. 
-        \item The \mstar{}-size relation also reflects the subtle environmental 
-            dependence as the central galaxies from more massive halos have 
-            slightly higher $R_{\mathrm{50}}$ at fixed \mtot{}. 
-            We further suggest that the relation between \mtot{} and 
-            \minn{}\footnote{or any better proxy of total \mstar{} and the mass 
-            formed in the ``in-situ'' phase.} can be useful tool in diagnosing the
-            assembly history of these massive galaxies and its relation to their 
-            dark matter halos.
+            stellar mass and on halo mass. 
+            This should be carefully taken into account when discussing topics such 
+            as the evolution of the galaxy SMF.
+
+        \item We show that the \mden{} profiles of massive galaxies are generally quite 
+            smooth out to 10 kpc but that there is a large but continuous scatter in the 
+            amount of light in their outskirts. 
+            We argue that ``cD'' galaxies simply represent the tail end of a 
+            distribution but that they are not a distinct class of massive galaxies.
+
+        \item At fixed \mstar{} evaluate within 100 kpc, we find that massive central 
+            galaxies display \mden{} profiles that are not self-similar and which 
+            present subtle but systematic differences that correlate with \mhalo{}.
+            On average, massive central galaxies in more massive halos have slightly 
+            shallower inner \mden{} profiles and more prominent outer envelope.
+
+        \item We also study how the \mden{} profiles vary with \mhalo{} at fixed 
+            ``in-situ'' mass where it is approximated by the \mstar{} within 10 kpc. 
+            At fixed \minn{} we find that central galaxies in more massive halos 
+            possess much more extended stellar envelope in the outskirts than the ones 
+            in smaller halos. 
+            At the same time the ellipticity, and optical color profiles inside 10 kpc 
+            show little to no dependence on environment.
+
+        \item The \mstar{}-size relation also exhibits a clear environmental 
+            dependence and central galaxies in more massive halos have larger 
+            $R_{\mathrm{50}}$ at fixed \mtot{}. 
+            We suggest that the relation between \mtot{} and \minn{}\footnote{or any 
+            better proxy of total \mstar{} and the mass formed in the ``in-situ'' phase.} 
+            can be a useful tool in diagnosing the assembly history of these massive 
+            galaxies and the connection with the assembly of their dark matter halos.
+
     \end{enumerate}
 
-	%\subsection{Future Improvements}
-    These results also highlight the advantages of HSC survey in studying the 
-    evolution of massive galaxies.
-    Upon finishing this work, the HSC survey has already doubled its sky 
-    coverage to $\sim 200$ deg$^2$, and provides a much larger sample of massive 
-    central galaxies. 
-    In the near future, besides using larger samples directly selected using the 
-    HSC photometry and photometric redshift,
-    we will improve the modeling of massive galaxies through careful 2-D method 
-    (e.g.\ \citealt{Huang2013a}) and by including multiband data 
-    (e.g.\ \citealt{Huang2016}).  
-    We will also try to get more physical insights with the help of the HSC weak 
-    lensing analysis and comparisons with cosmological hydro-simulations such as 
-    Illustris (\citealt{Vogelsberger2014}, \citealt{Genel2014}), 
-    EAGLE (\citealt{Schaye2015}, \citealt{Crain2015}), 
-    or \textit{Horizon-AGN} (\citealt{Dubois2014}).
+    These results highlight the advantages of wide area, deep, and high-quality imaging 
+    for studying the evolution of massive galaxies. 
+    Upon finishing this work, the HSC survey has already doubled its sky coverage to 
+    ${\sim} 200$ deg$^2$, and provides a much larger sample of massive central galaxies. 
+    In the near future, we will extend this work to lower \mtot{} by using photometric 
+    redshifts, and we will also apply 2-D photometry method (e.g.\ \citealt{Huang2013a}) 
+    to take advantages of the multi-wavelength nature of the HSC survey 
+    (e.g. \citealt{Huang2016}). 
+    Our current work can also be combined with weak lensing measurements of the dark 
+    matter halos of massive galaxies and physical insights into the assembly histories 
+    of these galaxies can be gained by comparing with cosmological hydro-simulations 
+    such as Illustris (\citealt{Vogelsberger2014}, \citealt{Genel2014}), 
+    EAGLE (\citealt{Schaye2015}, \citealt{Crain2015}), or \textit{Horizon-AGN} 
+    (\citealt{Dubois2014}).
 
@@
     GAMA survey, it is clear that the \rbcg{} galaxy has much more extended 
-    outer envelope, even though its average \mden{} profile is very similar 
+    outer envelope, even though its median \mden{} profile is very similar 
     to the \nbcg{} sample at $< 10$ kpc. 
@@
     As explained earlier, it is important to make sure the two samples have similar 
-    distributions in both \mstar{} and redshift before comparing their average \mden{} 
+    distributions in both \mstar{} and redshift before comparing their median \mden{} 
     profiles.  

### 2017-03-24 draft/ms_v7.tex
Close to finishe

--- 2017-03-14 draft/ms_v6.tex
@@
             isophote. 
-            Right: the masked $i$-band image of this galaxy with the isophotes 
+            Right: the three color image of this galaxy with isophotes 
             extracted by \texttt{Ellipse}. 
@@
 
-    We match the \texttt{hscZ} sample with the massive central galaxies of 
-    \redm{} clusters with $\lambda \geq 30$ and $P_{\mathrm{0.7}} \geq 0.7$,
-    and find 164 matched galaxies at $0.3 \leq z \leq 0.5$.
-    We will refer these \textbf{central galaxies in more massive halos} as the 
-    \rbcg{} sample here.
-    A small fraction of \redm{} centrals within the HSC footprints is missing  
-    due to severe contamination from optical artifacts or bright stars.
-    The median $\lambda$ of these clusters is $\sim 41$, corresponding to 
-    halo mass of $M_{\mathrm{halo}}\sim 2.2\times 10^{14} h^{-1} M_{\odot}$.
-    Among them, only 44 of \rbcg{} sample live in clusters with $\lambda \geq 50$
-    ($M_{\mathrm{halo}} \sim 3.0\times 10^{14} h^{-1} M_{\odot}$), so the \rbcg{} sample is 
-    not dominated by extremely massive clusters with \mhalo{}$>10^{15} M_{\odot}$. 
+    We match the \texttt{hscZ} sample with the central galaxies of \redm{} clusters 
+    with $\lambda \geq 30$ and $P_{\mathrm{0.7}} \geq 0.7$, and find 164 matched 
+    galaxies at $0.3 \leq z \leq 0.5$.
+    Our sample of \textbf{central galaxies in more massive halos} will be referred to 
+    as the \rbcg{} sample. 
+    The median $\lambda$ of the clusters associated with the \rbcg{} sample is 
+    $\sim 41$, corresponding to halo mass of 
+    $M_{\mathrm{halo}}\sim 2.2\times 10^{14}$ $h^{-1}$ $M_{\odot}$.
+    Only 44 centrals from the \rbcg{} sample live in clusters with $\lambda \geq 50$
+    ($M_{\mathrm{halo}} \sim 3.0\times 10^{14}$ $h^{-1} M_{\odot}$). 
+    Our \rbcg{} sample therefore corresponds to galaxies in moderate mass halos.
     %% Saved as "dr1_redbcg_use_sed5b.fits"
 
-    To select massive central galaxies in \logmh{}$<14.0$ halos, we identify and 
-    remove all galaxies within a cylinder region around each of the central galaxy of 
-    all \redm{} clusters.
-    We choose to use the $R_{\mathrm{halo}}$ as the radius, and twice the uncertainty of the 
-    photometric redshift error as the thickness of the cylinder. 
-    We convert the $\lambda$ into $M_{\mathrm{halo}}$ using the calibration in 
-    \citet{Simet2016}, then estimate the $R_{\mathrm{halo}}$ with the help of the 
-    mass-concentration relation in \citet{Diemer2015}. 
-    At $0.3 < z < 0.5$, the uncertainty of photo-$z$ is between 0.015 to 0.025, 
-    and is enough to exclude cluster members.
-    After removing galaxies in \redm{} clusters, the rest of the massive galaxies 
-    in our sample should mainly be the central galaxies of halos with \logmh{}$<14.0$,
-    and we will refer these \textbf{central galaxies in less massive halos} as the 
-    \nbcg{} sample.
-    We should note that the \nbcg{} sample at this stage spans a large range in 
-    \mstar{}, and includes contaminations like massive satellites in \logmh{}$< 14.0$ 
-    halos.  
-    Therefore, after we update the total \mstar{} later, we only focus on the 
-    \nbcg{} galaxies at very high-mass end (e.g.~\logms{}$ > 11.5$). 
-    According to recent observation (e.g. \citealt{vanUitert2016}), we can neglect 
-    satellite contamination at such high \mstar{} range. 
+    Out next goal is to construct a sample of central galaxies living in halos with 
+    \logmh{}$<14.0$. 
+    We first identify and remove all galaxies within a cylindrical region around all 
+    \redm{} clusters. 
+    We use a radius equal to $R_{\mathrm{200b}}$ and the thickness of the cylinder is 
+    set to twice the uncertainty of the photometric redshift error. 
+    We convert $\lambda$ to $M_{\mathrm{halo}}$ using the calibration of 
+    \citet{Simet2016} and we use the mass-concentration relation from 
+    \citet{Diemer2015} to compute $R_{\mathrm{200b}}$. At $0.3 < z < 0.5$, the 
+    uncertainty of photo-$z$ is between 0.015 to 0.025, and is enough to exclude 
+    cluster members.
+    After removing galaxies associated with \redm{} clusters, the remaining galaxies 
+    in our sample will be dominated by central galaxies living in halos with 
+    \logmh{}$\leq 14.0$. 
+    We will refer to this sample of \textbf{central galaxies in less massive halos}
+    as the \nbcg{} sample.
+
+    We note that at this stage, our \nbcg{} sample still contains galaxies with a 
+    wide range of \mstar{} values. 
+    Later on, once we have more accurate \mstar{} estimates, we will further limit this 
+    sample to \logms{}$ > 11.5$. 
+    At this very high mass end, and given that we have rejected satellites in \redm{} 
+    clusters, any further satellite contamination can be safely neglected 
+    (e.g. \citealt{Reid2014, Hoshino2015, Saito2016, vanUitert2016}).
     %% Saved as "dr1_nonbcg_use_sed5b.fits"
@@
     Using $\sim 100$ deg$^2$ of HSC data, we select a large sample of massive central 
-    galaxies with reliable redshift information, and broadly separate them into two 
-    groups with different \mhalo{}. 
+    galaxies with reliable redshift information, and broadly separate them two 
+    categories based on $M_{\mathrm{halo}}$.
+
     The following is a summary of our sample construction.
@@
     (the observed i-band corresponds to a rest-frame $g$ or $r$ band), but also 
-    because they have better seeing and much lower background level than the images 
-    in $z$ and Y bands that are supposed to be better tracers of \mden{}.
-
-    For each cut-out, to avoid the ``over-deblending'' issue within the 
-    \texttt{hscPipe}, we use customized procedures to detect and appropriately mask 
-    out all objects around the massive galaxies.
-    Meanwhile, the \texttt{hscPipe} tends to over-subtract background around bright
-    objects, including some of the massive galaxies in our sample. 
-    After aggressively masking out all objects (including the central massive 
-    galaxy), we derive an empirical background correction with the help from 
-    \texttt{SExtractor}.
+    because they have better seeing and much lower background levels than the $z$ 
+    and Y band images (although these in principle may be better tracers of \mden{}).
+
+    For each cut-out, to overcome the \texttt{hscPipe} ``over-deblending'' issue, we 
+    use a customized procedure to detect and appropriately mask out neighbouring 
+    objects. 
+    Furthermore, \texttt{hscPipe} tends to over-subtract the background around 
+    bright objects. 
+    To correct for this over-subtraction, we first aggressively mask all objects 
+    (including the central massive galaxy), and derive an empirical background 
+    correction using \texttt{SExtractor}.
     Then, we run \texttt{Ellipse} on the background-corrected, masked cut-outs 
-    following the methodology in \citep{Li2012}. 
-    In short, we start with free centroid and shape (ellipticity and position angle) 
-    for each isophote, then fix the best-estimated centroid and estimate the mean 
-    ellipticity and position angles of all isophotes.  
+    following the methodology of \citep{Li2012}. 
+    In short, we first fit each isophote using a free centroid and shape 
+    (ellipticity and position angle). 
+    We then fix the centroid (using the mean flux-weighted centroid) and estimate
+    the mean ellipticity and position angles of all isophotes. 
     Finally, we extract a 1-D surface brightness profile along the major axis using 
@@
     We correct these surface brightness profiles for Galactic extinction and 
-    cosmological dimming, then integrate them to various radius to get the 
-    luminosity within different physical apertures. 
+    cosmological dimming, and integrate them to various radii to get the luminosity 
+    within different physical (elliptical) apertures. 
     Fig~\ref{fig:ellipse} shows an example of the 1-D surface brightness and 
-    ellipticity profile for a massive galaxy at $z\sim0.2$ together with the 
-    colored image and a subset of isophotes.
-
-    After testing the above procedure with different mask sizes, different 
-    \texttt{Ellipse} parameters, and with or without background correction, 
-    we find that the 1-D surface brightness profile is reliable above 
-    $>28.5$ \sb. 
-    Beyond that, some of the profiles begin to show unphysical behaviors 
-    (truncation or large fluctuations) due to uncertainties from background subtraction. 
-    This conservative choice already enables us to measure the individual surface 
-    brightness profile out to $100$ kpc. 
-    For more details about the technical details of the \texttt{Ellipse} run, please 
-    see Appendix~\ref{app:ellipse}.
+    ellipticity profile for a massive galaxy at $z\sim0.2$ and also highlights 
+    a few isophotes.
+
+    We test our procedure using different mask sizes, different \texttt{Ellipse} 
+    parameters, and with or without our background correction. 
+    Based on these tests, we find that our 1-D surface brightness profiles are reliable 
+    up to surfaces brightness levels of $>28.5$ \sb. 
+    Beyond that, some of our profiles shows signs of truncation and/or large 
+    fluctuations which are due to the uncertainty in the background subtraction. 
+    We choose to limit our study to surface brightness levels up to $\sim 28.5$ \sb. 
+    This is a conservative choice but already enables us to measure light profiles 
+    out to $100$ kpc on a galaxy-by-galaxy basis (no stacking). 
+    For more details about the technical details of how we use \texttt{Ellipse}, 
+    please see Appendix~\ref{app:ellipse}.
 
@@
     The typical uncertainty of \logms{} is around 0.08-0.10 dex at \logms$\sim 11.5$. 
-    Please see Appendix~\ref{app:sed} for more detailed discussions of the SED fitting
-    results.  
+    Please see Appendix~\ref{app:sed} for further details.
+
 %% ------------------------------------------------------------------------------------ %%
@@
       \caption{
-          \textbf{Left}: Median \mden{} profiles of galaxies in different \mtot{} bins:
-      	  [11.4, 11.6] (short-dashed line), [11.6, 11.8] (solid line), and 
-      	  [11.8, 12.0] (long-dashed line). 
-      	  Here we combine the \rbcg{} and \nbcg{} samples, and we also show a random 
-      	  subset of individual profiles in the background.
-      	  The shaded region highlights the region that could be affected by PSF.
-          Two vertical lines label the radius of 10 kpc (thin, dotted line) and
+          \textbf{Left}: Median \mden{} profiles in three total stellar mass bins. 
+              Here we combine the two \rbcg{} and \nbcg{} samples together -- 
+              the halo mass dependence of these profiles will be explored in subsequent 
+              figures. 
+              Thin grey lines show a random subset of individual profiles. 
+              The shaded region highlights the region that could be affected by the PSF. 
+              Two vertical lines indicate 10 kpc (thin, dotted line) and
               100 kpc (thick, dash line). ~~~ 
-          \textbf{Right}: comparison between the average \mden{} profiles with the ones 
-          from previous observations and simulations, including: 
-          1) average profile of massive elliptical galaxies at $z\sim 0$ from 
-          \citet[][Cyan, solid]{Huang2013a}; 
-          2) average profile of massive galaxies at $0.25 \leq z < 0.50$ observed by 
-          \textit{HST} from \citet[][Red, long-dashed]{Patel2013} ;
-          3) average radial stellar distributions in massive halos using simulation and 
-          particle tagging method (\citealt{Cooper13}; Purple, short-dashed).
-          }
+          \textbf{Right}: comparison between our \mden{} profiles, previous observations, 
+              and simulations. 
+              The solid cyan line shows the median profile of massive elliptical 
+              galaxies at $z\sim 0$ from \citet[][]{Huang2013a}. 
+              The red long-dashed line shows the median profile of massive galaxies at 
+              $0.25 \leq z < 0.50$ observed by \textit{HST} from \citet[][]{Patel2013}. 
+              The purple short-dashed line shows the median radial stellar distributions 
+              in massive halos from simulation using the particle tagging method
+              (\citealt{Cooper13}).}
       \label{fig:avg_prof}
@@
       \caption{
-          Comparison of the \mden{} profiles for \mtot{}-matched 
-          ($11.6<$\logmtot{}$<11.9$) and \minn{}-matched ($11.2<$\logminn{}$<11.6$) 
-          samples of \rbcg{} (orange to red) and \nbcg{} (grey to black) galaxies.~~
-          \textbf{Left} shows the results for the \mtot{}-matched samples.
-          For details of the matching process, please see Appendix~\ref{app:match}.  
-          On its upper panel, we show the \mden{} profile of each galaxy using very light 
-          color in the background.  
-          We highlight the median profile and its corresponding uncertainties using thick 
-          solid line with darker color and shaded region. 
-          Other formats are the same with Fig~\ref{fig:avg_prof}.
-          Meanwhile, we highlight the difference between the median profiles and its 
-          uncertainty on the bottom panel (brown solid line and shaded region).
+          \mden{} profiles for \mtot{}-matched ($11.6<$\logmtot{}$<11.9$) and 
+          \minn{}-matched ($11.2<$\logminn{}$<11.6$) samples. 
+          Orange and red correspond to \rbcg{} and grey and black correspond to \nbcg{}. 
+          The \mtot{}-matched samples are shown on the left and the \minn{}-matched 
+          samples are shown on the right. 
+          Thin lines show the \mden{} profile for individual galaxies. 
+          Thick lines with shaded regions show the median profile for each sample with 
+          uncertainties given by the shaded region. 
+          The bottom panel highlights the differences between the two median profiles 
+          (brown solid line and shaded region). 
           To test the significance of the differential profile, we perform statistical
@@
           \nbcg{} ones. 
-          Repeating this process many times, the median of these random differential 
-          profiles (black solid line), the 1-$\sigma$ (dark-grey shaded region) and 
-          3-$\sigma$ (light-grey shaded region) uncertainties are shown on the bottom 
-          panel as well. 
-          A darker vertical dash-line highlights the 100 kpc radius.~~
-          \textbf{Right} shows the results for the \minn{}-matched samples. 
-          The format is exactly the same with the left one, except that the darker 
-          vertical dash-line now highlights the 10 kpc radius.
-          }
+          Repeating this process 5000 times, the median (black solid line), 1-$\sigma$ 
+          (dark-grey shaded region) and 3-$\sigma$ (light-grey shaded region) ranges
+          of these random differential profiles are shown on the bottom panel.}
       \label{fig:prof_1} 
@@
     Kingdom Infrared Telescope Infrared Deep Sky Survey (UKIDSS; \citealt{Lawrence2007}). 
-    The deeper photometry and better photo-$z$ make the \texttt{S82-MGC} sample complete 
+    The deeper photometry and better photo-$z$s make the \texttt{S82-MGC} sample complete 
     to \logms{}$\geq 11.2$ at $z<0.7$ which makes it sufficient to evaluate the 
-    completeness of this sample.
+    completeness of our HSC samples.
+
     There are 20453 \texttt{S82-MGC} galaxies that are also in the \texttt{hscPho} 
-    sample at $0.3 \leq z_{\mathrm{s82}} \leq 0.5$ (referred as \texttt{s82Pho} sample).   
-    We estimate their \mstar{} using the HSC \texttt{cModel} SED in exactly the 
-    same way\footnote{The \mstar{} using HSC photometry shows tight correlation with the 
-    ones based on the \texttt{S82-MGC} SED which includes NIR data from UKIDSS; 
-    \texttt{S82-MGC} also uses \texttt{iSEDFit} with similar assumptions}.  
-    Then we estimate the volume density distributions of the galaxies in \rbcg{}, 
-    \nbcg{}, and \texttt{s82Pho} samples (right panel of Fig~\ref{fig:smf1}) using 
-    rough estimates of the survey areas they occupied \footnote{We estimate the 
-    uncertainties of these distributions via bootstrap resampling}.
-    By comparing the relative shapes of these distributions, we conclude that 
-    our sample of massive galaxies is reasonably complete down to \logms{}$\sim 11.6$
-    at $0.3 \leq z \leq 0.5$. 
-    While the \rbcg{} sample is less affected by completeness thanks to the reliable
-    photo-$z$ from \redm{}, the completeness of the \nbcg{} sample is still limited 
-    by the spec-$z$ samples.
-    Although there is no apparent reason that the incompleteness can bias our 
-    comparison of structure, we will mainly focus on the \rbcg{} and \nbcg{} galaxies 
-    with $11.6 \le$\logmtot{}$\le 11.9$ where their mass distributions overlap the 
-    most and both have good \mstar{} completeness, and will also match the two samples 
-    carefully in \logms{} and redshift distributions.
+    sample at $0.3 \leq z_{\mathrm{s82}} \leq 0.5$. 
+    We compute \mstar{} values for these galaxies using our fiducial 
+    procedure\footnote{The \mstar{} using HSC photometry is in excellent with the 
+    values derived from the \texttt{S82-MGC} which includes NIR data from UKIDSS; 
+    \texttt{S82-MGC} also uses \texttt{iSEDFit} with similar assumptions.}. 
+    The right side of Fig~\ref{fig:smf1} compares the SMFs of galaxies from 
+    \texttt{S82-MGC} with the SMFs of galaxies from our two 
+    samples\footnote{Errors on the SMFs are estimated via bootstrap resampling}. 
+    Based on Fig~\ref{fig:smf1}, we conclude that our sample of massive galaxies is 
+    reasonably complete down to \logms{}$\sim 11.6$ at $0.3 \leq z \leq 0.5$. 
+    The \rbcg{} sample is less affected by completeness because we can utilize 
+    photo-$z$s from \redm{}. 
+    However, the completeness of the \nbcg{} sample is still limited by the 
+    availability of spec-$z$s from BOSS.
+
+    In this work, we will focus on the range $11.6 \le$ \logmtot{}$ \le 11.9$ 
+    where our two samples are complete. 
+    When comparing \nbcg{} and \rbcg{} we will also always make sure that the two 
+    samples are well matched both in terms of \mstar{} as well as in terms of redshift. 
     Please see the next section and Appendix~\ref{app:match} for more details.
@@
 
-    Using the best-fit stellar mass from \texttt{iSEDFit} (referred as \mcmodel{}), 
-    we estimate the average \m2l{} in $i$-band, then use that \m2l{} to convert the 
-    1-D luminosity density profiles into stellar mass density profiles; and 
-    also convert the luminosity within 10 and 100 kpc apertures into 
-    corresponding stellar mass estimates (referred as \minn{} and \mtot{}). 
-    From now, we use \mtot{} as the new proxy of ``total'' stellar mass of these 
-    galaxies.  
-    And we also derive the $k$-corrected luminosity and colors from the results.
+    Using the best-fit stellar mass from \texttt{iSEDFit} (noted as as \mcmodel{}), 
+    we estimate the average \m2l{} in the $i$-band, then use that \m2l{} to convert our 
+    1-D luminosity density profiles into stellar mass density profiles. 
+    We also convert our 10 and 100 kpc aperture luminosities into corresponding stellar 
+    mass estimates (noted as \minn{} and \mtot{}).
+
+    For the remainder of this paper, we will use \mtot{} as a proxy of ``total'' 
+    stellar mass. 
     In Appendix~\ref{app:sedasic}, we briefly summarize the basic statistics of 
-    the \rbcg{} and \nbcg{} samples using the newly derived \mtot{} and \minn{}.
-    We can confirm that both samples follow a similar and very tight ``red-sequence''.
-    We also show the outputs from SED fitting process like the average stellar age, 
-    metallicity, and internal dust extinction in Appendix~\ref{app:sed}.
-    Although we do not rely them on scientific analysis, they all behave reasonably for 
-    both samples. 
-    As expected, the integration of 1-D profile out to very large radius help 
-    recover more luminosity (stellar mass) compared to the \cmodel{} results. 
-    We shown in Section \ref{ssec:s82}.
-
-    As mentioned earlier, our assumption of using an average \m2l{} ignores its
-    radial variation.   
-    It is well known that massive ETGs have negative optical color gradient which 
-    indicates a gradient of \m2l{} (e.g.\ \citealt{LaBarbera2012}; 
-    \citealt{DSouza2015}), but the gradient is shallow and smooth out to a few 
-    times of the effective radius (color gradient at the very outskirt is still 
-    not well quantified). 
+    the \rbcg{} and \nbcg{} samples using our estimates of \mtot{} and \minn{}.
+    We confirm that both samples follow a similar and very tight ``red-sequence''. 
+    Appendix~\ref{app:sed} describes the outputs from our SED fitting process 
+    (average stellar age, metallicity, and internal dust extinction). 
+    We do not utilize these quantities in this paper, but we have checked that they all 
+    behave reasonably for both samples. 
+    As expected, the integration of the 1-D profile out to very large radius recovers 
+    more luminosity (stellar mass) compared to the \cmodel{}-based estimates. 
+    This will be shown in Section \ref{ssec:s82}.
+
+    Our methodology ignores any radial variations in \m2l{}. 
+    It is well known that massive ETGs have negative optical color gradients indicating 
+    gradients in \m2l{} \alexie{xxx} (e.g.\ \citealt{LaBarbera2012}; 
+    \citealt{DSouza2015}). 
+    These color gradients are shallow and smooth out to a few times of the effective 
+    radius and color gradients at the outskirts are not yet well quantified. 
     More importantly, for the comparison between the \rbcg{} and \nbcg{} samples, 
-    our results should remain intact as long as there is no significant
-    differences of average color gradient between these two samples.
-    This is confirmed by our initial results on color gradient, and we will 
-    discuss this more in Section \ref{ssec:ell_color}.
-    Therefore the average \m2l{} approach should work reasonably well for our goals.
-
-    This approach to derive total stellar mass is actually quite similar to the 
-    method adopted by the GAMA survey (\citealt{Taylor2011}).
-    They start with \mstar{} estimated using average \m2l{} from SED fitting 
-    results of PSF-matched aperture photometry, and later correct it with better 
-    estimate of total luminosity from single-\ser model fitting
-    (\citealt{Kelvin2012}). 
-    For galaxies in common with the GAMA survey, we also compare their different 
-    estimates of \mstar{} (\mgama{} v.s. \mtot{}) in Appendix~\ref{app:gama},  
-    and notice systematic differences between the two \mstar{} estimates.
-    It is likely that the GAMA models still miss fluxes in the stellar halo that 
-    is beyond the depth of SDSS image. 
+    our results will be robust as long as there is \emph{no significant difference in the 
+    average color gradient between the two samples}. 
+    We have confirmed that this is indeed the case and this will be discussed in Section 
+    \ref{ssec:ell_color}.
+
+    Our method for deriving total stellar masses is similar to the 
+    method adopted by the GAMA survey (\citealt{Taylor2011, Kelvin2012}). 
+    We have compared our \mstar{} values with those from GAMA and the results are given 
+    in Appendix~\ref{app:gama}. 
+    We find a systematic differences between the two \mstar{} estimates.
+    It is likely that the GAMA models fail to capture the flux associated with the 
+    outskirts of galaxies due to the limited depth of SDSS.     
 %% ------------------------------------------------------------------------------------ %%
@@
 %% ------------------------------------------------------------------------------------ %%
-\subsubsection{Mass Dependence of \mden{} Profiles}
+\subsubsection{General Trends and Comparison with Previous Work}
     \label{sssec:sbp_inter}
 
-    Comparing to the much discussed scaling relation like the mass-size relation, 
-    the \mden{} profiles contain more structural details that can help us diagnose the 
-    roles of different physical processes, including the environmental effect.  
-    We first mix the \rbcg{} and \nbcg{} together, and show how the average \mden{}
-    profiles of massive galaxies at $0.3 < z < 0.5$ depend on stellar mass using their 
-    median \mden{} profiles\footnote{The median profiles along with their uncertainties 
-    using bootstrap resampling method} in three \mtot{} bins \footnote{Here we ignore a 
-    small population of massive satellite in \redm{} clusters we excluded from our 
-    sample.
+    Compared to the much discussed "mass-size" relation, the \mden{} profiles that we 
+    have derived capture the full information about the structural properties of 
+    massive galaxies. 
+    We argue that by studying the shapes of these galaxy profiles directly, we can 
+    by-pass outstanding questions about how to accurately define and measure the 
+    "sizes" and "masses" of these massive galaxies. 
+    Fig~\ref{fig:avg_prof} shows the median \mden{} profiles\footnote{The median 
+    profiles along with their uncertainties are derived using bootstrap resampling 
+    method} of massive galaxies at $0.3 < z < 0.5$ in three \mtot{} bins\footnote{Here 
+    we ignore a small population of massive satellites \alexie{xxxx} in \redm{} clusters 
+    we excluded from our sample. 
     The sample is clearly not complete in the lowest \mtot{} bin, but its median \mden{}
@@
     observations}. 
-
     As shown in the left panel of Fig~\ref{fig:avg_prof}, we can comfortably trace
-    the \mden{} profiles of these massive galaxies out to 100 kpc \textbf{individually}, 
-    which greatly help us study the statistical properties of their outer envelopes. 
-    These median \mden{} profiles have very moderate differences in the inner region, 
-    but show significant differences in the outskirts as more massive galaxies have 
-    much more prominent stellar envelopes.
-    Most of these massive galaxies ($\ge 10^{11.4} M_{\odot}$) are slow-rotating 
+    the \mden{} profiles of these massive galaxies out to 100 kpc 
+    \textbf{individually}. 
+    These median \mden{} profiles have moderate differences in the inner region, 
+    but show significant differences in the outskirts with more massive galaxies 
+    showing more prominent stellar envelopes. 
+    Most of these massive galaxies ($\ge 10^{11.4} M_{\odot}$) are slowly-rotating 
     (e.g.\ \citealt{Cappellari13b}) giant ellipticals with ``boxy'' inner isophotal 
-    shape (e.g.\ \citealt{Kormendy2009}), and slightly flattened \mden{} profile close 
-    to the center (e.g.\ \citealt{Lauer07}).
-    But their structures in the outskirt clearly do \textbf{NOT} response to the 
-    increase of stellar mass in a self-similar way.
-
-    The \mden{} profile of massive galaxy out to such large radius was only available 
-    through image stacking technique (e.g. \citealt{Tal2011, DSouza2015})
-    that suffers from several systematic issues.
-    Although most \mden{} profiles extend beyond 100 kpc, many of them show signs of 
-    unphysical truncation and fluctuation related to inaccurate sky subtraction.  
-    Therefore, we exclude the profiles outside 100 kpc, even though the median \mden{} 
+    shapes (e.g.\ \citealt{Kormendy2009}), and slightly flattened inner \mden{} 
+    profiles (e.g.\ \citealt{Lauer07}). 
+    But in the outskirts, the structure of these galaxies clearly does \textbf{NOT} 
+    response to the increase of stellar mass in a self-similar way.
+    As mentioned earlier, some of the \mden{} profiles show signs of unphysical 
+    truncation and fluctuation related to inaccurate sky subtraction.  
+    We exclude the profiles outside 100 kpc, even though the median \mden{} 
     profiles for the two more massive bins behave reasonably out to $\sim 200$ kpc.
 
-    In the right panel of Fig~\ref{fig:avg_prof}, we compare these median profiles with 
-    a few past works.  
-    \citep{Huang2013a}, derived the median \mden{} profile for a small sample of very 
+    The right panel of Fig~\ref{fig:avg_prof} compares our median profiles with a few
+    past works.
+    So far, the surface brightness profiles of massive galaxies out to such large 
+    radii was mostly derived via image stacking technique that suffers from several 
+    systematic issues (e.g. \citealt{Tal2011, DSouza2015}; but also see:
+    \citealt{Capaccioli2015}); and the \mden{} profiles are even more rarely 
+    available.
+    \citep{Huang2013a} derived \mden{} profiles for a small sample of very 
     nearby ellipticals (within 100 Mpc; median \logms{}$\sim 11.3$ based on shallower 
-    images) from the Carnegie-Irvine Galaxy Survey (CGS, \citealt{CGS1}) that are not 
-    affected by seeing until $r < 1$ kpc.
+    images) from the Carnegie-Irvine Galaxy Survey (CGS, \citealt{CGS1}) that are 
+    only affected by seeing within $r < 1$ kpc. 
     This median \mden{} profile qualitatively agrees with the one for the lowest 
@@
     envelope at $r > 15$ kpc. 
-    While the small sample size of the CGS sample ($\sim 30$) and differences in the
-    measurements of \mstar{} could explain this difference, it is also interestingly 
-    consistent with mild mass assembly from $z\sim 0.4$ to $z=0$ in the outskirt.   
-    The CGS images are already deeper than SDSS images in $r$-band, but the median 
-    profile still only reaches to $\sim 50$ kpc for $z\sim 0$ massive galaxies.
-    Meanwhile, the deep HSC images can reliably deliver individual \mden{} profiles 
-    for $z\sim 0.4$ galaxy out to at least 100 kpc.
-
-    \citet{Patel2013} extracted the median \mden{} profile of massive ETGs at 
-    $0.25 < z < 0.50$ using the stacked \textit{HST}/ACS images. 
-    These galaxies are selected at a constant cumulative number density that makes them  
-    good candidates of progenitors of $z=0$ massive ETGs.  
-    The median \mstar{} is $\sim 10^{11.2} M_{\odot}$ according to their estimates.  
-    However, once the differences in imaging depth and assumptions in SED fitting method
-    are considered, it is reasonable to assume they are comparable to our galaxies in 
-    the lowest \mtot{} bin, and the comparison of \mden{} profiles does confirm that.
-    Moreover, the superb resolution of the \textit{HST}/ACS image makes the \mden{} 
-    profile unaffected by PSF even within inner 1 kpc.
-    Therefore, the comparison illustrates that the HSC profiles within our redshift
-    range are indeed not bothered by seeing at $r > 3$ kpc, which also ensure the
-    accuracy of the \minn{} estimates.
-
-    We also compare with the predicted average \mden{} profile of central galaxies in 
-    massive halos ($13.5 < \log M_{200,c} < 14.0$) from cosmological simulation
-    (\citealt{Cooper13}) using the particle-tagging technique (\citealt{Cooper10}).
-    Despite the poorer resolution, its \mden{} profile is already quite similar to 
-    the median \mden{} profile for the $11.6 <$\logmtot{}$< 11.8$ bin within 40 kpc. 
-    However, comparing with observation, this simulation predicts stellar envelope that
-    is too prominent at this halo mass.
-    Result like this demonstrates that comparisons between observations and simulations
-    using \mden{} profiles have the potential to not only help us make simulation
-    more realistic, but also help us investigate the physical causes of the observed
-    \mstar{} and environmental dependences of structures.
-
-    We summarize these median profiles in Fig~\ref{fig:avg_prof} in Table.~1,
-    and all the above median profiles are available  
-    \href{https://github.com/dr-guangtou/hsc_cenHighMh/tree/master/profiles}{here}.
+    While the small size of the CGS sample ($\sim 30$) and differences in the
+    measurements of \mstar{} could explain this difference, it may also correspond 
+    to evidence for build-up in the outskirts of massive galaxies from $z\sim 0.4$ 
+    to $z=0$. 
+    CGS images are deeper than SDSS images in the $r$-band, but the median 
+    profile from \citep{Huang2013a} still only reaches $\sim 50$ kpc for $z\sim 0$ 
+    massive galaxies.
+    Meanwhile, our deep HSC images can reliably deliver individual \mden{} profiles 
+    for $z\sim 0.4$ galaxies out to at least 100 kpc.
+
+    \citet{Patel2013} extracted a median \mden{} profile of massive ETGs at 
+    $0.25 < z < 0.50$ using stacked \textit{HST}/ACS images. 
+    These galaxies are selected at a constant cumulative number density and are 
+    thought to be the progenitors of $z=0$ massive ETGs (e.g. \citealt{Leja2013}).  
+    The median \mstar{} of the \citet{Patel2013} sample is $\sim 10^{11.2} M_{\odot}$, 
+    but the shallower imaging depth and the differences in SED fitting 
+    assumptions\footnote{\citep{Patel2013} uses the BC03 SSP model, which show an 
+    average -0.1 dex difference with the FSPS one based on our tests.}
+    can make them comparable to our galaxies in the lowest \mtot{} bin, and the 
+    comparison of \mden{} profiles does confirm that. 
+    The superb resolution of the \textit{HST}/ACS image means that the profile in
+    \citet{Patel2013} is unaffected by the seeing even down to 1 kpc. 
+    The good agreement between our profile and the one derived from HST image 
+    shows that our profiles are robust at $r > 3$ kpc and that we can accurately 
+    measure \minn{}.
+
+    Finally, we also compare with the predicted median \mden{} profile of central 
+    galaxies in massive halos ($13.5 < \log M_{200,c} < 14.0$) from cosmological 
+    simulation where the \mden{} profiles of galaxies are calculated using the 
+    particle-tagging technique (\citealt{Cooper10}). 
+    Despite the poorer resolution, the simulated \mden{} profile is already quite 
+    similar to the median \mden{} profile for the $11.6 <$ \logmtot{} $< 11.8$ bin 
+    within 40 kpc. 
+    However, compared with our data, this simulation predicts stellar envelope that
+    are too prominent at this halo mass. 
+    This types of comparisons between our HSC data and predictions from simulations 
+    will help to fine-tune simulations and to also investigate the main physical 
+    mechanisms that drive the assembly of massive galaxies and the build up of 
+    stellar envelopes.
+
+    Table 1 provides tabulated values for the median profiles that are displayed 
+    in Fig~\ref{fig:avg_prof}. 
+    These profiles are also available  
+    \href{https://github.com/dr-guangtou/hsc_redbcg/tree/master/profiles}{here}:
+    {\url{https://github.com/dr_guangtou/hsc_redbcg/tree/master/profiles/}}.
+
 %% ------------------------------------------------------------------------------------ %%
@@
     of galaxies in both \mtot{}-matched and \minn{}-matched samples (used in 
-    Fig~\ref{fig:prof_1}) using \texttt{Ellipse}, and compare the average profiles between
+    Fig~\ref{fig:prof_1}) using \texttt{Ellipse}, and compare the median profiles between
     the \rbcg{} and \nbcg{} samples for two main purposes:
@@
 
-    Secondly, we see shallow and negative gradients of average $g-r$ and $g-i$ color 
+    Secondly, we see shallow and negative gradients of median $g-r$ and $g-i$ color 
     profiles for both \rbcg{} and \nbcg{} galaxies. 
@@
           We include: 
-          1) the average \mden{} profile of inner component from structure 
+          1) the median \mden{} profile of inner component from structure 
           decomposition of massive elliptical galaxies at $z\sim 0$ from 
           \citet[][Cyan, solid]{Huang2013a}; 
-          2) the average \mden{} profile of massive galaxies at $1.0 < z < 1.5$ 
+          2) the median \mden{} profile of massive galaxies at $1.0 < z < 1.5$ 
           from \textit{HST} observations in \citet[][Red, dashed]{Patel2013}; 
-          3) the average \mden{} profile of the ``in-situ'' stellar components in 
+          3) the median \mden{} profile of the ``in-situ'' stellar components in 
           simulated massive halos from \citet[][Purple, dot-dashed]{Cooper13};

### 2017-03-24 draft/ms_v8.tex
Close to finishe

--- 2017-03-24 draft/ms_v7.tex
@@
     limit $> 28.5$\sb) imaging from the Hyper-Suprime Cam (HSC) Subaru Strategic 
-    Program (SSP; \citealt{HSCDR1; will be referred as the HSC survey} to revisit the 
+    Program \citep[SSP,][]{HSCDR1} to revisit the 
     question of the environmental dependence in the mass-size relation. 
@@
       \caption{
-          \mden{} profiles for \mtot{}-matched ($11.6<$\logmtot{}$<11.9$) and 
-          \minn{}-matched ($11.2<$\logminn{}$<11.6$) samples. 
-          Orange and red correspond to \rbcg{} and grey and black correspond to \nbcg{}. 
-          The \mtot{}-matched samples are shown on the left and the \minn{}-matched 
-          samples are shown on the right. 
-          Thin lines show the \mden{} profile for individual galaxies. 
-          Thick lines with shaded regions show the median profile for each sample with 
-          uncertainties given by the shaded region. 
-          The bottom panel highlights the differences between the two median profiles 
-          (brown solid line and shaded region). 
-          To test the significance of the differential profile, we perform statistical
-          tests by comparing the median profiles of two random groups that are drawn 
-          from the mixed sample, and have the same sizes with the matched \rbcg{} and
-          \nbcg{} ones. 
-          Repeating this process 5000 times, the median (black solid line), 1-$\sigma$ 
-          (dark-grey shaded region) and 3-$\sigma$ (light-grey shaded region) ranges
-          of these random differential profiles are shown on the bottom panel.}
+          The environmental dependence of the stellar mass profiles of massive central 
+          galaxies. 
+          The left panel corresponds to samples matched by "total" stellar mass 
+          (\mtot{}). 
+          The right panel corresponds to samples matched by "core-mass" (\minn{}). 
+          Orange and red lines correspond to central galaxies living in halos with 
+          \logmh{} $\geq 14.2$. 
+          Black and grey correspond to central galaxies living in halos with 
+          \logmh{} $\leq 14.0$. 
+          Thin lines show the profiles of individual galaxies while thick lines show 
+          the median profile. 
+          The uncertainty on the median profile is given by the shaded region and is 
+          computed via bootstrap resampling. 
+          The brown line in the bottom panels show the relative difference between 
+          two median profiles 
+          ($\Delta = \log(\mu_{\star, \mathrm{cenHighMh}}) - 
+          \log(\mu_{\star, \mathrm{cenLowMh}})$). 
+          Errors on the difference between the two profiles is computed via bootstrap 
+          too. 
+          The grey shaded regions show a Monte Carlo test to asses how likely is it to 
+          obtain $\Delta$ from random sub-samples of the data. 
+          To compute the grey shaded regions, we first mix the two samples 
+          (\rbcg{} and \nbcg{}), then draw sub-samples of galaxies from the mixed 
+          population and compute $\Delta$ in the same fashion as for our fiducial signal. 
+          We repeat this process 5000 times.  
+          The dark-grey shaded region (light-grey shaded region) shows the 1-$\sigma$ 
+          (3-$\sigma$) fluctuations in $\Delta$ from these 5000 draws.
+          }
       \label{fig:prof_1} 
@@
     It is well known that massive ETGs have negative optical color gradients indicating 
-    gradients in \m2l{} \alexie{xxx} (e.g.\ \citealt{LaBarbera2012}; 
+    gradients in \m2l{} (e.g.\ \citealt{LaBarbera2012}; 
     \citealt{DSouza2015}). 
@@
     More importantly, for the comparison between the \rbcg{} and \nbcg{} samples, 
-    our results will be robust as long as there is \emph{no significant difference in the 
-    average color gradient between the two samples}. 
-    We have confirmed that this is indeed the case and this will be discussed in Section 
-    \ref{ssec:ell_color}.
+    our results will be robust as long as there is \emph{no significant difference in 
+    the average color gradient between the two samples}. 
+    We have confirmed that this is indeed the case and this will be discussed in 
+    Section~\ref{ssec:ell_color}.
 
@@
     profiles along with their uncertainties are derived using bootstrap resampling 
-    method} of massive galaxies at $0.3 < z < 0.5$ in three \mtot{} bins\footnote{Here 
-    we ignore a small population of massive satellites \alexie{xxxx} in \redm{} clusters 
-    we excluded from our sample. 
-    The sample is clearly not complete in the lowest \mtot{} bin, but its median \mden{}
-    profile is still useful to show the overall trend and to compare with previous 
-    observations}. 
+    method} of massive central galaxies at $0.3 < z < 0.5$ in three \mtot{} 
+    bins\footnote{The sample is clearly not complete in the lowest \mtot{} bin, 
+    but its median \mden{} profile is still useful to show the overall trend and to 
+    compare with previous work}. 
     As shown in the left panel of Fig~\ref{fig:avg_prof}, we can comfortably trace
@@
     profiles (e.g.\ \citealt{Lauer07}). 
-    But in the outskirts, the structure of these galaxies clearly does \textbf{NOT} 
-    response to the increase of stellar mass in a self-similar way.
-    As mentioned earlier, some of the \mden{} profiles show signs of unphysical 
-    truncation and fluctuation related to inaccurate sky subtraction.  
-    We exclude the profiles outside 100 kpc, even though the median \mden{} 
-    profiles for the two more massive bins behave reasonably out to $\sim 200$ kpc.
-
-    The right panel of Fig~\ref{fig:avg_prof} compares our median profiles with a few
-    past works.
+    But in the outskirts, the structure of these galaxies is 
+    \emph{clearly not self-similar}. 
+    Some of our \mden{} profiles show signs of unphysical truncation and fluctuation 
+    related to inaccurate sky subtraction. 
+    In this paper, we do not use profiles beyond 100 kpc, even though the median 
+    \mden{} profiles for the two most massive bins behave reasonably out to 
+    $\sim 200$ kpc.
+
+    Fig~\ref{fig:avg_prof} compares our results with previous work. 
+    Most previous studies have relied on stacking techniques to measure surface 
+    brightness profiles out to large radii.
     So far, the surface brightness profiles of massive galaxies out to such large 
@@
     available.
-    \citep{Huang2013a} derived \mden{} profiles for a small sample of very 
-    nearby ellipticals (within 100 Mpc; median \logms{}$\sim 11.3$ based on shallower 
-    images) from the Carnegie-Irvine Galaxy Survey (CGS, \citealt{CGS1}) that are 
-    only affected by seeing within $r < 1$ kpc. 
-    This median \mden{} profile qualitatively agrees with the one for the lowest 
-    \mtot{} bin in the inner region, but shows a slightly more prominent outer 
-    envelope at $r > 15$ kpc. 
-    While the small size of the CGS sample ($\sim 30$) and differences in the
-    measurements of \mstar{} could explain this difference, it may also correspond 
-    to evidence for build-up in the outskirts of massive galaxies from $z\sim 0.4$ 
-    to $z=0$. 
+
+    \citep{Huang2013a} derived \mden{} profiles for a small sample of very nearby 
+    ellipticals (within 100 Mpc; median \logms{} $\sim 11.3$ based on shallower 
+    images) from the Carnegie-Irvine Galaxy Survey (CGS, \citealt{CGS1}). 
+    Because this is a very low redshift sample, these profiles are robust to $r=1$ kpc. 
+    The \citep{Huang2013a} profiles show good agreement with ours in the region of 
+    overlap and out to 50 kpc. 
     CGS images are deeper than SDSS images in the $r$-band, but the median 
@@
     thought to be the progenitors of $z=0$ massive ETGs (e.g. \citealt{Leja2013}).  
-    The median \mstar{} of the \citet{Patel2013} sample is $\sim 10^{11.2} M_{\odot}$, 
-    but the shallower imaging depth and the differences in SED fitting 
-    assumptions\footnote{\citep{Patel2013} uses the BC03 SSP model, which show an 
-    average -0.1 dex difference with the FSPS one based on our tests.}
-    can make them comparable to our galaxies in the lowest \mtot{} bin, and the 
-    comparison of \mden{} profiles does confirm that. 
+    The median \mstar{} of the \citet{Patel2013} sample is $\sim 10^{11.2} M_{\odot}$ 
+    which is lower than our lowest mass bin. 
+    However, \citep{Patel2013} use the BC03 SSP model which are roughly 0.1 dex 
+    lower than our FSPS masses (Appendix~\ref{app:sed}). 
+    Furthermore, the \citep{Patel2013} images are shallower than ours meaning 
+    that there masses will be lower than ours because of missing light in the 
+    outskirts. 
+    Given these two considerations, it is reasonable to roughly compare the 
+    \citep{Patel2013} profile with the one in our lowest stellar mass bin. 
     The superb resolution of the \textit{HST}/ACS image means that the profile in
@@
     particle-tagging technique (\citealt{Cooper10}).
-    Despite the poorer resolution, the simulated \mden{} profile is already quite 
-    similar to the median \mden{} profile for the $11.6 <$ \logmtot{} $< 11.8$ bin 
-    within 40 kpc. 
+
+    The simulated \mden{} profile is also affected by limited resolution in the 
+    center, but it is already quite similar to the median \mden{} profile for 
+    the $11.6 <$ \logmtot{} $< 11.8$ bin within 40 kpc. 
     However, compared with our data, this simulation predicts stellar envelope that
@@
 
-    Table 1 provides tabulated values for the median profiles that are displayed 
-    in Fig~\ref{fig:avg_prof}. 
+    Table~1 provides tabulated values for the median profiles that are 
+    displayed in Fig~\ref{fig:avg_prof}. 
     These profiles are also available  
@@
 %% ------------------------------------------------------------------------------------ %% 
-\subsubsection{Environmental Dependence of the \mden{} Profiles}
+\subsubsection{Environmental Dependence of the Profiles of Massive Galaxies}
     \label{sssec:sbp_mtot}
 
-    Finally, we will look into the environmental dependence of structures in massive 
-    galaxies using the \mden{} profiles of the \rbcg{} and \nbcg{} samples that are 
-    carefully matched in \mstar{} and redshift using KDTree algorithm. 
-    We discuss the details and quality of the matching procedure in 
-    Appendix~\ref{app:match} (see Fig~\ref{fig:match}. 
-    The matched redshift distributions within $0.3 < z < 0.5$ ensures the \mden{} 
-    profiles from both samples are impacted by seeing and background at similar level. 
-    As for the \mstar{}, we choose to match using two physically meaning definitions.
+    We now ask whether or not galaxies from our sample have \mden{} profiles that 
+    depend on \mhalo{} (at fixed \mstar{}). 
+    For this, we will build matched samples drawing from \rbcg{} and \nbcg{} that are 
+    carefully matched in \mstar{} and redshift using a KDTree algorithm 
+    (see Appendix~\ref{app:match} and Fig~\ref{fig:match} for details). 
+    By matching the redshift distributions within $0.3 < z < 0.5$, we ensure that the 
+    \mden{} profiles from both samples are impacted by seeing and background subtraction 
+    at similar levels. 
+    To match the two samples by stellar mass, we will use two different methods:
 
     \begin{itemize}
-        \item \mtot{} as the proxy of the ``total'' \mstar{} that include the stellar 
-            envelope.  As mentioned earlier, we match the two samples within 
-            $11.6 < $\logmtot{}$<11.9$ (median \logmtot{}$\sim 11.74$).
-            For the 45 \rbcg{} galaxies, we have 229 unique \nbcg{} galaxies in the 
-            matched sample.
-            Within this \mtot{} range, 100 kpc equals to 5-8 times of the effective 
-            radius, so should enclose most their \mstar{}. 
-            In practice, this choice also reflects the radius range that we can safely 
-            measure \mden{} profile given the depth of the image and the accuracy of 
-            background subtraction.
-
-        \item \minn{} as the proxy of the \mstar{} of the ``in-situ'' component.
-            This is motivated and supported by recent observations and simulations, 
-            and we will discuss more about this assumption in 
+
+        \item We match the two samples according to \mtot{}. 
+            We select galaxies from \rbcg{} with $11.6 < $\logmtot{} $<11.9$ 
+            (median \logmtot{} $\sim 11.74$). 
+            There are 45 \rbcg{} galaxies in this range. 
+            We then match this distribution by drawing galaxies from \nbcg{}. 
+            There are 229 unique \nbcg{} galaxies in the matched sample. 
+            In this \mtot{} range, 100 kpc corresponds to 5-8 times the effective radius 
+            and \mtot{} is a good proxy of total stellar mass.
+
+       \item We match the two samples according to \minn{}. 
+           We select galaxies from \rbcg{} with $11.2 < $\logminn{}$ < 11.6$ 
+            (median \logminn{}$\sim 11.36$).
+            For the 56 galaxies from the \rbcg{} sample, we achieve excellent matches
+            in \minn{} and redshift using 375 \nbcg{} galaxies.
+            Motivated by recent observations and simulations, we use \minn{} as the 
+            proxy of the \mstar{} of the ``in-situ'' component.
+            We will discuss more about this assumption in 
             Section~\ref{sec:discussion}.
-            We match the two samples within $11.2 < $\logminn{}$ < 11.6$ 
-            (median \logminn{}$\sim 11.36$).
-            For 56 galaxies in this \rbcg{} sample, we achieve excellent matches
-            using 375 \nbcg{} galaxies.
+
     \end{itemize}
 
-    We show the comparison of the \mtot{}-matched (\minn{}-matched) samples in the 
-    left (right) panel of Fig~\ref{fig:prof_1}.
-
-    For the \mtot{}-matched comparison, it is easy to see that the \mden{}
-    profiles of \rbcg{} and \nbcg{} galaxies \textbf{greatly overlap with each 
-    other over the entire radius range}, which partially explains the difficulties in 
-    confirming any environmental dependence of structure in earlier works.
-    Although the central galaxies from more massive halos do not form a unique 
-    population in term of their structures comparing with the ones in less massive
-    halos at similar \mtot{}, we can still spot interesting differences in their 
-    median profiles: the \rbcg{} galaxy on average has slightly more flattened inner 
-    profile and more significant outer stellar envelope than the \nbcg{} one.
-    We highlight these subtle differences in the bottom panel using the difference 
-    between the two median profiles and its uncertainty. 
-    Given the noticeable uncertainties of \mtot{} and $\lambda$, along with the 
-    small size of the current \rbcg{} sample, we perform statistical test to confirm 
-    the robustness of the result \footnote{We mix the $N_{\mathrm{r}}$ \rbcg{} 
-    galaxies and the $N_{\mathrm{n}}$ \mtot{}-matched \nbcg{} ones together, then 
-    randomly draw $N_{\mathrm{r}}$ galaxies with putting-back, compute the difference 
-    between the median profile of this sample and the \nbcg{} sample. 
-    After repeating this process 2000 times, we can evaluate the possibility that 
-    the systematic differences in median \mden{} profiles can be reproduced by random 
-    selection of massive galaxies.}
-    In both inner and outer regions, we conclude the systematic differences in 
-    median \mden{} profiles are significant and robust.
-    Interestingly, the median profiles for \rbcg{} and \nbcg{} cross each other 
-    at $\sim 15$-20 kpc, quite close to the expected $R_{\mathrm{e}}$ for ETGs 
-    this massive. 
-    In Appendix~\ref{app:robust}, we further prove the robustness of this 
-    interesting result by showing that it is not affected by the range of redshift,
-    range of richness, and the choice of proxy for ``total'' \mstar{} 
-    (see Fig~\ref{fig:prof_3}). 
-    We also explore the possible \mtot{}-dependence of this structural difference 
-    despite the limitation of \mstar{}-completeness and small sample size
-    (see Fig~\ref{fig:prof_2}) in Appendix~\ref{app:robust}.
-    Although the systematic differences are very similar in different \mtot{} bins, 
-    we do find some hints that suggest the environmental dependence becomes more 
-    significant at the more massive end.  
-    This evidence could have intriguing implication in the assembly history of 
-    massive galaxies, and is worth more investigations with larger and more completed 
-    sample later.
-
-    \textbf{All these tests confirm that we robustly detect subtle, but systematic 
-    \mhalo{}-dependence (environmental dependence) of structure in massive, 
-    central galaxies} that seems to be consistent with the expectation of more frequent 
-    (minor) mergers in denser environment. 
-    These minor, non-dissipative mergers do not alter the inner \mden{} profiles 
-    a lot, but are efficient in depositing stellar mass onto the outer envelope
-    (e.g. \citealt{Hilz2013}, \citealt{Oogi2013}).
-
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %% 
-    Meanwhile, the subtlety of this environmental dependence for \mtot{}-matched 
-    samples seems to suggest that environment plays a secondary role in shaping 
-    the structure of galaxies at fixed total stellar mass, and it encourages us to find
-    another interesting angle.  
-    For instance, for massive galaxies that formed similar amount of stars through 
-    intensive star formation at high redshift, how the environments affect their mass 
-    assembly history in the second phase? 
-    We attempt to investigate this question through comparing the \mden{} profiles of 
-    the \minn{}-matched \rbcg{} and \nbcg{} galaxies (right side of 
-    Fig~\ref{fig:prof_1}).
-    Assuming we are now comparing the average structures of massive galaxies that share 
-    similar \mstar{} in the ``in-situ'' component, we start to see the environmental 
-    dependence much more clearly without any statistical test.     
-    The median \mden{} profiles of \rbcg{} and \nbcg{} galaxies are quite similar in 
-    the inner 5-10 kpc, but the \rbcg{} galaxies clearly show much more prominent
-    outer envelope.
-
-    It is also worth noting that \mden{} profiles of massive galaxies have quite uniform
-    slope and small scatter inside 10 kpc.  
-    In contrast, their outer profiles could have a large range of slopes and much 
-    larger scatters than the inner region. 
-    It seems to suggest that the inner and outer parts of massive galaxies are shaped 
-    by distinctive physical processes, and are affected by their environment at 
-    very different level. 
-    Given the highly dissipative nature of the ``in-situ'' phase, the similarity of 
-    inner profiles is consistent with the idea that processes like wet-merger and 
-    star burst often create de~Vaucouleur-like ($n\sim 4$) \mden{} profile
-    (e.g. \citealt{Hopkins2008}).
-    At the same time, the outer envelope of massive galaxies are predicted to be 
-    gradually assembled by non-dissipative mergers, which is a stochastic process and 
-    is more affected by the environment.  
-    Therefore, it is natural to see larger diversity in the outer profiles of 
-    low-$z$ massive galaxies. 
-    On average, massive galaxies in more massive halos show shallower outer \mden{} 
-    profiles, which is in qualitative agreement with recent simulation
-    (e.g. \citealt{Pillepich2014}).
+%% ------------------------------------------------------------------------------------ %%     
+    Fig~\ref{fig:prof_1} compares the profiles of galaxies at fixed \mtot{} and at fixed 
+    \minn{} for our two matched samples, and shows the main results of this paper which 
+    is that we find a clear halo mass dependence in the \mden{} profiles of massive 
+    galaxies. 
+    The bottom panel of Fig~\ref{fig:prof_1} shows the difference between the two 
+    profiles, $\Delta = \log(\mu_{\star, \mathrm{cenHighMh}}) - 
+    \log(\mu_{\star, \mathrm{cenLowMh}})$, 
+    with errors computed via bootstrap resampling. 
+    In Appendix~\ref{app:robust}, we present a variety of tests that verify the 
+    robustness of these results against different uncertainties.
+
+    There are several important points to be noticed in Fig~\ref{fig:prof_1}. 
+    First, when galaxies are matched by \mtot{}, although we detect a robust 
+    environmental dependence, it mainly only becomes prominent in the outskirts 
+    at $R>50$ kpc. 
+    This partially explains the difficulties for previous works to detect this effect
+    on shallower images. 
+    Second, we find that central galaxies in more massive dark mater halos display 
+    more flattened inner profile and more significant outer stellar envelope than 
+    the ones living in less massive halos. 
+    Third, the median \mden{} profiles of \rbcg{} and \nbcg{} cross each other 
+    at $\sim 15$-20 kpc, the expected $R_{\mathrm{e}}$ for ETGs at this \mtot{}. 
+    Finally, such systematic difference in structure may become more significant 
+    at very high-mass end. 
+    We see evidence of this effect when we compare the $Delta$ profiles in two \mtot{} 
+    bins (see Fig~\ref{fig:prof_2} and discussion in 
+    Appendix~\ref{app:robust})\footnote{Though the lower \mtot{} bin becomes somewhat
+    incomplete} and when we discuss the relation between \mtot{} and \minn{} for 
+    these two samples (see Fig~\ref{fig:scaling_relation}). 
+    This potential interesting result and its implication is worth more investigations 
+    later.
+
+    Meanwhile, the subtle environmental dependence of \mden{} profiles for the 
+    \mtot{}-matched samples suggests that environment does not play the major role in 
+    shaping massive galaxies \textbf{at fixed total stellar mass}.
+    Therefore it is interesting to ask, for massive galaxies that \textbf{contain 
+    similar \mstar{} in the in-situ component}, how does environment affect their 
+    subsequent mass assembly?
+    Assuming that the \minn{} is reasonable proxy of in-situ mass, we look into this 
+    question by comparing the \mden{} profiles of the \minn{}-matched samples ( 
+    Fig~\ref{fig:prof_1}, right).  
+    Although the median \mden{} profiles are similar at $r \leq 10$ kpc, the
+    central galaxies in more massive halos clearly possess much more prominent outer
+    envelope. 
+    This result is robust in a series of statistical and systematical tests 
+    (see Appendix~\ref{app:robust}.
+
+    At the same time, the uniform slope of the \mden{} profiles within 
+    10 kpc is in sharp contrast with the large scatter of the outskirts. 
+    It hints that these two regions are shaped by distinctive processes, and may 
+    explain their differences in environmental dependency. 
+    In simulations, intensive dissipative process helps create 
+    self-similar de~Vaucouleur-like ($n\sim 4$) \mden{} profile in the inner part 
+    of massive galaxy (e.g. \citealt{Hopkins2008}), and the \mhalo{}-dependent
+    merging history leads to shallower stellar halo profile for central galaxy 
+    of more massive halo (e.g. \citealt{Pillepich2014}). 
+    The stochastic nature of the merging process also helps explain the 
+    large scatter in the distributions of outer \mden{} profiles. 
     We illustrate this interesting diversity in Fig~\ref{fig:m100_m10_color}, where 
     we show the 3-color images of randomly selected massive central galaxies that 
-    have similar \minn{} ($11.1 \leq \log (M_{\star,\ 10\mathrm{kpc}}/M_{\odot}) < 11.2$)
+    have similar \minn{} 
+    ($11.1 \leq \log (M_{\star,\ 10\mathrm{kpc}}/M_{\odot}) < 11.2$)
     but different \mtot{}.   
@@
       \caption{
-          Comparisons of the radial profiles of ellipticity and optical colors 
-      	  for \mtot{}-matched (\textbf{left figure}) and \minn{}-matched 
-      	  (\textbf{right figure}) of \rbcg{} (orange-red) and \nbcg{} (grey-black) samples. 
-          The formats are very similar to the figure for \mden{} profile 
-          (e.g. right figure of Fig~\ref{fig:prof_1}). 
-          On each side, from top to bottom, we show the elliptical profile, and the 
-          color profile using $g-r$ and $g-i$ color. 
-          Since the individual profile of these properties has very large uncertain in the 
-          outskirt, we block the region at large radii where we think the median profiles 
-          are still unreliable using a dark, shaded box.
-          We also compare these results with previous results based on SDSS images. 
-          They are: 
-          1) Ellipticity profile of the stacked image of a large sample of red galaxies at 
-          $z\sim 0.4$ from \citet{Tal2011} with PSF correction 
-          (solid blue line on top panel); 
-          2) Ellipticity and $g-r$ color profiles from stacking analysis of nearby massive 
-          galaxies with high concentration index ($C>2.6$) in \citet[][blue dash lines 
-          on the top and middle panels]{DSouza2014}; 
-          3) average $g-r$ and $g-i$ color profiles for a large sample of nearby 
-          elliptical galaxies in \citet[][blue, solid lines on the middle and bottom 
-          panels]{LaBarbera2010}.
+          Radial variations in ellipticity and optical colors for massive galaxies. 
+          The format of this figure is similar to the right hand side of 
+          Fig~\ref{fig:prof_1}. 
+          Top panels show the ellipticity profile, middle panels show $g-r$, and lower 
+          panels show $g-i$. 
+          We compare our results with those from \citet{Tal2011} based on stacking 
+          large samples of luminous red galaxies in SDSS at $z\sim 0.4$ 
+          (solid blue line on top panel). 
+          We also compare with the results from a stacking analysis of nearby massive 
+          galaxies with high concentration index ($C>2.6$) in 
+          \citet[][blue dash lines on the top and middle panels]{DSouza2014}. 
+          Finally, we also compare with the average $g-r$ and $g-i$ color profiles 
+          from a large sample of nearby elliptical galaxies in \citet[][blue, solid 
+          lines on the middle and bottom panels]{LaBarbera2010}.
           }
@@
 
-    Besides the 1-D \mden{} profiles, the radial profiles of isophotal shape and colors 
-    are also useful diagnostic tools to study massive galaxies. 
-    Here, we extract the radial profiles of ellipticity and $k$-corrected optical colors
-    of galaxies in both \mtot{}-matched and \minn{}-matched samples (used in 
-    Fig~\ref{fig:prof_1}) using \texttt{Ellipse}, and compare the median profiles between
-    the \rbcg{} and \nbcg{} samples for two main purposes:
+%% ------------------------------------------------------------------------------------ %% 
+    We now study how the ellipticities (computed via \texttt{Ellipse}) and $k$-corrected 
+    optical colors of massive galaxies vary with radius. 
+    We also study whether or these radial trends differ between our various samples. 
+    These quantities contain interesting information about the physical processes that 
+    shape galaxies, but here we study them mainly with two goals in mind:
 
     \begin{enumerate}
-        \item To see whether the ellipticity profile strongly depends on environment, 
-            and to see whether 1-D \mden{} profiles using average isophotal shape is 
-            appropriate for the goal of this work.
-
-        \item To verify that the average color gradient does not strongly depend on 
-            the environment, and is not steep enough to invalid the assumption that   
-            it is reasonable to use average \m2l for comparing massive galaxies. 
+
+        \item To see whether the ellipticity profile depends strongly on environment, 
+            and to see whether or not the fact that we use an using average isophotal 
+            shape for our our 1-D \mden{} profiles has any impact on our results.
+
+        \item To verify that the average color gradient does not depend strongly on 
+            the environment and that is not steep enough to cause a problem with our 
+            choice the assumption that it is reasonable to use average \m2l for 
+            comparing massive galaxies. 
             We extract color profiles by applying the isophotes in $i$-band to images 
             in other bands in ``forced photometry'' manner.
+
     \end{enumerate}
 
-    Since we do not correct the differences in sky subtraction and seeing across 
-    different bands, we simply ignore the ellipticity and color in the inner-most and 
-    very low surface brightness regions (profiles are useful between 5-50 kpc). 
+    We compute ellipticities and color profiles in the radial range of 5-50 kpc 
+    (this is the range where we can safely ignore differences in sky subtraction and 
+    seeing across different bands). 
     We apply Galactic extinction and $k$-correction to both $g-r$ and $g-i$ color 
@@
     \mtot{}-matched (\minn{}-matched) samples of \rbcg{} and \nbcg{} galaxies on the 
-    left (right) side of \ref{fig:ell_color}, and also compare them with previous 
-    estimates that are based on stacking analysis of SDSS galaxies 
+    left (right) side of \ref{fig:ell_color}. 
+    We also compare our results with previous work based on stacking SDSS galaxies 
     (e.g. \citealt{LaBarbera2010, Tal2011, DSouza2014}).
 
-    Firstly, the ellipticity of massive galaxies steadily increase with radius 
-    from $e\le 0.2$ around 5-10 kpc to $e\sim 0.3$ at 40-50 kpc, in consistent with 
-    previous 2-D modeling results \citep{Huang2013a}.  
-    For the \mtot{}-matched samples, their ellipticity profiles are very similar 
-    all the way to 50 kpc (2-3$\times R_{\mathrm{e}}$ for their \mstar{}). 
-    Meanwhile, for the \minn{}-matched samples, the \rbcg{} galaxies have higher 
+    We find that in general, the ellipticities of massive galaxies increases with 
+    radius from $e\le 0.2$ around 5-10 kpc to $e\sim 0.3$ at 40-50 kpc. 
+    This is consistent with previous 2-D modeling results from \citep{Huang2013a}. 
+    The ellipticity profiles of the \mtot{}-matched samples are very similar at 
+    $r<50$ kpc (2-3$\times R_{\mathrm{e}}$ for their \mstar{}). 
+    However, for the \minn{}-matched samples, the \rbcg{} galaxies have higher 
     ellipticity than the \nbcg{} ones at $r > 10$ kpc, while their inner ellipticity 
@@
     This further hints that massive central galaxies in different halos but with 
-    similar ``in-situ'' mass could experience different merging history.
-    And, given he relative low ellipticity value and shallow ellipticity profile, 
-    we conclude that average isophote is appropriate for the structural comparisons 
-    we performed.
-    Previously, people often rely on image stacking method to extract ellipticity 
-    profile out to large radius (e.g. \citealt{Tal2011}, \citealt{DSouza2015}).
-    Comparing with the ellipticity profile directly measured on deep HSC image, 
-    we find that the stacked ellipticity profiles tend to underestimate the 
-    ellipticity in the outskirt. 
-    Since the ellipticity profile contains interesting information of the assembly 
-    history, we think it highlights the advantage of the HSC image in studying 
-    massive galaxies again, and it would be very interesting to compare with 
-    numerical simulations on this.
-
-    % \citet{Tal2011} stacked the SDSS images of a large sample of Luminous Red 
-    % Galaxies (LRGs) at $z\sim 0.4$, and extract the ellipticity profile after 
-    % correcting the PSF convolution effect.   
-    % Its slope is much shallower than the average ones using HSC images, despite the 
-    % two samples are at similar redshift and are quite comparable. 
-    % The poorer seeing condition of SDSS image plus the systematics in the stacking 
-    % process can easily explain this. 
-    % \citet{DSouza2015} performed similar stacking analysis for a large sample of very 
-    % nearby ETGs.  
-    % The ellipticity profile is quite consistent with our average ones within 5-10 
-    % kpc, but become much shallower at outer region.  
-    % The lower average \mstar{} of their sample and/or the uncertainties in the 
-    % stacking analysis may explain this.  
-    % This highlights the advantages of the high-resolution, deep HSC images again,
-    % and it would be very interesting to compare with numerical simulations.
-
-    Secondly, we see shallow and negative gradients of median $g-r$ and $g-i$ color 
-    profiles for both \rbcg{} and \nbcg{} galaxies. 
+    similar ``in-situ'' mass may experience different late-time merging histories. 
+    Overall, the relative low ellipticity value and the fact that the ellipticity 
+    gradients are shallow lead us to conclude that the use of an average 
+    isophotal ellipticity is fine for this present study.
+
+    Previous attempts to constrain ellipticity gradients have relied on image 
+    stacking techniques (e.g. \citealt{Tal2011}, \citealt{DSouza2015}). 
+    Compared to our measurements, we find that stacked ellipticity profiles tend to 
+    underestimate the ellipticity in the outskirt. 
+    Ellipticity profiles contain additional information about the assembly histories 
+    and in future work, it would be of interest to compare our ellipticity profiles 
+    with predictions from hydrodynamic simulations such as Illustris 
+    (\citealt{Vogelsberger2014}, \citealt{Genel2014}) or \textit{Horizon-AGN} 
+    (\citealt{Dubois2014}).
+
+    In terms of color gradients, we find shallow and negative gradients of median 
+    $g-r$ and $g-i$ color profiles for both \rbcg{} and \nbcg{} galaxies. 
     For both \mtot{}- and \minn{}-matched samples, we find no significant difference
@@
 
-\subsubsection{Mass-Size relation}
+\subsubsection{Mass-Size Relation}
     \label{sssec:mass_size}
 
-    Despite being the focus of previous investigations (e.g. \citealt{Shankar2013};
-    \citealt{Leja2013}, \citealt{vdWel2014}), the relation between \mstar{} and 
-    effective radius (or half-light radius; $R_{\mathrm{e}}$ or $R_{\mathrm{50}}$) 
-    has yet to provide clear evidence of environmental dependence of structures of 
-    massive galaxies at low-$z$ (e.g. \citealt{Weinmann2009}, \citealt{Nair2010}, 
-    \citealt{HCompany13}, \citealt{Cerbrian2014}), and sent controversial messages 
-    about the pictures at high-$z$ (e.g. \citealt{MCooper2012}, \citealt{Papovich2012}, 
-    \citealt{Kelkar2015}).
-    Now, according to the previous comparisons of \mden{} profiles, the deep HSC images 
-    also promise evidence of the environmental dependence of mass-size relation 
-    (see the left panel of Fig~\ref{fig:scaling_relation}).
-
-    We use the \mtot{} as the proxy of ``total'' \mstar{}, and the radius that encloses 
-    50\% of luminosity within 100 kpc ($R_{\mathrm{50}}$; derived from $i$-band 
-    curve-of-growth) as the ``size'' to evaluate the relation.
+    Despite numerous previous attempts, previous works have failed to clearly 
+    demonstrate the existence of an environmental dependence of mass-size relation
+    at low-$z$ (e.g. \citealt{Weinmann2009, Nair2010, HCompany13, Cerbrian2014})
+
+    %Despite being the focus of previous investigations (e.g. \citealt{Shankar2013};
+    %\citealt{Leja2013}, \citealt{vdWel2014}), the relation between \mstar{} and 
+    %effective radius (or half-light radius; $R_{\mathrm{e}}$ or $R_{\mathrm{50}}$) 
+    %has yet to provide clear evidence of environmental dependence of structures of 
+    %massive galaxies at low-$z$ (e.g. \citealt{Weinmann2009}, \citealt{Nair2010}, 
+    %\citealt{HCompany13}, \citealt{Cerbrian2014}), and sent controversial messages 
+    %about the pictures at high-$z$ (e.g. \citealt{MCooper2012}, \citealt{Papovich2012}, 
+    %\citealt{Kelkar2015}).
+
+    By using the deep HSC images, and by comparing the \mden{} profiles directly, 
+    we have shown that the structures of massive galaxies do depends on the masses of 
+    their host halos (see the left panel of Fig~\ref{fig:scaling_relation}). 
+    We now couch our results in terms of the more traditional "mass-size" relation. 
+    For this purpose, we will use \mtot{} as our ``total'' \mstar{} and the radius 
+    enclosing 50\% of luminosity within 100 kpc ($R_{\mathrm{50}}$; derived from $i$-band 
+    curve-of-growth) as our ``size''. 
     This definition of ``effective radius'' is more robust against structural details, 
     choice of model, and the background subtraction. 
-    Our massive galaxies are also big enough so we do not need to worry about seeing
-    correction.
-
-    On the left of Fig~\ref{fig:scaling_relation}, we see clear \mstar{}-size relations 
-    for both samples.  
-    At fixed \mtot{}, the distributions of $R_{\mathrm{50}}$ for the \rbcg{} and
-    \nbcg{} galaxies greatly overlap, but it seems that the \rbcg{} galaxies do have 
-    systematically higher $R_{\mathrm{50}}$. 
-    % For the \mtot{}-matched samples used in Fig~\ref{fig:prof_1}, the median 
-    % $\log (R_{\mathrm{50}}/\mathrm{kpc})$ values for the \rbcg{} and \nbcg{} are 
-    % $1.22\pm 0.02$ ($\sim 17.4\pm 0.75$ kpc) and $1.09\pm 0.01$ 
-    % ($\sim 12.3\pm0.3$ kpc), which confirm the above observation and is consistent with 
-    % the differences seen in Fig~\ref{fig:prof_1}.  
-    To confirm the differences, we fit the 
-    \logmtot{}-$\log (R_{\mathrm{50}}/\mathrm{kpc})$ relations at 
-    \logmtot{}$\geq 11.6$ using MCMC-sampling method via the ensemble sampler 
-    \texttt{emcee} (\citealt{Emcee})\footnote{Initial guesses are based on maximum 
-    likelihood estimates, and we assume reasonable flat priors for parameters}.
-    The best-fit relation for the massive \rbcg{} galaxies:
+    Our massive galaxies are large enough so we do not need to worry about the 
+    effects of seeing.
+
+    Fig~\ref{fig:scaling_relation} shows the \mstar{}-size relations for both samples. 
+    We fit the \logmtot{}-$\log (R_{\mathrm{50}}/\mathrm{kpc})$ relations at 
+    \logmtot{}$\geq 11.6$\footnote{We use MCMC and the ensemble sampler 
+    \texttt{emcee} (\citealt{Emcee}) with initial guesses are based on maximum 
+    likelihood estimates, and we assume reasonable flat priors for parameters.}.
+    The best-fit relation for \rbcg{} is:
 
@@
             Build-Up of Outer Envelopes}
+
+    %Assuming that the \minn{} traces the \mstar{} of the ``in-situ'' components 
+    %reasonably well, this suggests that ``red nuggets'' at high-$z$ with similar 
+    %\mstar{} end up following different assembly history that depends on their 
+    %environments. The \mhalo{}-dependence that wecan be caused by many different physical processes. 
+    %Given the interesting results on the right panel of Fig \ref{fig:scaling_relation},
+    %we recommend to apply similar scaling relation to different datasets and 
+    %numerical simulations (e.g. see Fig~1 of \citealt{Wellons2016b}) to explore the 
+    %physical origins and redshift evolution of this dependence.
 

### 2017-03-24 draft/ms_v9.tex
Close to finishe

--- 2017-03-24 draft/ms_v10.tex
@@
 
+%        \author{Song Huang\altaffilmark{1} 
+%        Alexie Leauthaud\altaffilmark{1}, 
+%        Kevin Bundy\altaffilmark{1},
+%        Michael Strauss\altaffilmark{2},
+%        Yen-Ting Lin\altaffilmark{3},
+%        Rachel Mandelbaum\altaffilmark{4}
+%        }
+%\altaffiltext{2}{Princeton University Observatory, 
+%    Peyton Hall, Princeton, NJ 08544, USA}
+%\altaffiltext{3}{Institute of Astronomy and Astrophysics, Academia Sinica, 
+%    P.O.~Box 23--141, Taipei 10617, Taiwan}
+%\altaffiltext{4}{Carnegie-Mellon University \todo{correct affiliation here}}
+
 %%%%%%%%%%%%: Header and Version %%%%%%%%%%%%
+
 \begin{document}
@@
 
-    We use ${\sim}100$ deg$^2$ of deep ($>28.5$ \sb{} in $i$-band), high-quality 
-    (0.6\asec seeing) imaging data from the Hyper Suprime-Cam (HSC) survey 
+    We use ${\sim}100$ deg$^2$ of deep ($>28.5$\sb{} in $i$-band), high-quality 
+    (median 0.6\asec seeing) imaging data from the Hyper Suprime-Cam (HSC) survey 
     to investigate the halo mass dependence of the surface mass density profiles 
     and outer stellar envelopes of massive galaxies. 
-    Our sample consists of ${\sim}7000$ massive (\mstar{}$\geq 11.5$) central galaxies 
+    Our sample consists of ${\sim}7000$ massive (\mstar{}$\leq 11.5$) central galaxies 
     at $0.3 < z < 0.5$. 

### 2017-03-31 draft/paper1.tex
Paper split

--- 2017-03-24 draft/ms_v10.tex
@@
 \newcommand{\alexie}[1]{\textcolor{blue}{\textbf{[Alexie: #1]}}}
+\newcommand{\jenny}[1]{\textcolor{Bittersweet}{\textbf{[Jenny: #1]}}}
 \newcommand{\kevin}[1]{\textcolor{green}{\textbf{[Kevin: #1]}}}
@@
 %% ------------------------------------------------------------------------------------ %% 
-\title[Structure and Halo of Massive Galaxies]{A Detection of the Environmental 
-       Dependence of the Stellar Profiles and Halos of Massive Central Galaxies}
+\title[Structure and Halo of Massive Galaxies]{Tracing the Stellar Halo of Massive 
+       Galaxies to 100 kpc at $0.3<z<0.5$ using the Hyper Suprime-Cam}
 
@@
         Alexie Leauthaud,$^{2,1}$
+        Jenny Greene,$^{4}$
         Kevin Bundy,$^{3,1}$
-        Jenny Greene,$^{4}$
         Yen-Ting Lin,$^{5}$
         \newauthor
-        Rachel Mandelbaum,$^{6}$
-        Michael Strauss,$^{4}$
-        and HSC collaboration$^{7}$   
+        Masayuki Tanaka,$^{6}$
+        Rachel Mandelbaum,$^{7}$
+        Satoshi Miyazaki,$^{5,8}$
+        HSC collaboration 
         \\
@@
               Princeton University, Princeton, NJ 08540, USA \\
-        $^{5}$Academia Sinica Institute of Astronomy and Astrophysics, 
+        $^{5}$National Astronomical Observatory of Japan, 2--21--1 Osawa, Mitaka, 
+              Tokyo 181--8588, Japan\\
+        $^{6}$Academia Sinica Institute of Astronomy and Astrophysics, 
               P.O. Box 23--141, Taipei 10617, Taiwan\\
-        $^{6}$McWilliams Center for Cosmology, Department of Physics, 
+        $^{7}$McWilliams Center for Cosmology, Department of Physics, 
               Carnegie Mellon University, Pittsburgh, PA 15213, USA\\
-        $^{7}$Another Department, Different Institution, Street Address, City Postal 
-              Code, Country
+        $^{8}$SOKENDAI (The Graduate University for Advanced Studies), Mitaka,
+              Tokyo, 181--8588, Japan
         }   
@@
     requiring stacking. 
-    For the first time, we conclusively show that at fixed stellar mass, massive central 
-    galaxies display mass density profiles that are not self similar and which 
-    present subtle but systematic differences that correlate with \mhalo{}. 
-    On average, massive central galaxies in more massive halos have shallower inner 
-    stellar mass density profiles (within ${\sim}10$-$20$ kpc) and more prominent outer 
-    envelopes. 
-    These differences translate into a clear environmental dependence of the mass-size 
-    relation: central galaxies in more massive halos have larger $R_{\mathrm{50}}$ 
-    at fixed \mtot{}. 
     Shallow imaging will miss light at the outskirts of galaxies and this has an 
     important impact on measurements of the galaxy mass function. 
-    Furthermore, because galaxies in larger halos have more extended envelopes, 
-    the amount of light that is missed will be halo mass dependent. 
-    Finally, at fixed total stellar mass, there is a large (but continuous) diversity 
-    in the amplitude of stellar profiles at 100 kpc. 
-    We argue that ``cD'' galaxies represent the tail end of a distribution and 
-    are not a distinct class of massive galaxies. 
+    With these deeper data, we show definitively that at fixed stellar mass,
+    massive central galaxies display mass density profiles that are not self similar, 
+    with the accreted fraction increasing towards unity for galaxies in our highest 
+    stellar mass bin. 
     Our results are broadly consistent with the two phase formation scenario of 
@@
         \label{fig:sdss_compare}
-    \end{figure*}
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %% 
-  \begin{figure*}
-      \centering 
-      \includegraphics[width=\textwidth]{fig/redbcg_m100_m10_compare}
-      \caption{
-          Three-color images for a subsample of massive galaxies at $z{\sim}0.4$. 
-          All of these galaxies have the same mass within a 10 kpc aperture 
-          ($11.2<\log (M_{\star,10\ \mathrm{kpc}}/M_{\odot})<11.3$). 
-          The dash-line circle at the top-left figure indicates 10 kpc.
-          Galaxies are rank-ordered from top to bottom and from left to right by 
-          their \mstar{} within a 100 kpc aperture which varies from $10^{11.2} M_{\odot}$ 
-          to $10^{11.7} M_{\odot}$. 
-          At fixed ``inner'' mass ($M_{\star,10}$), massive galaxies display significant
-          diversity in their outer profiles. 
-          Red boxes indicate galaxies in halos more massive than 
-          ${\sim} 10^{14.0} M_{\odot}$. 
-          }
-      \label{fig:m100_m10_color}
     \end{figure*}
@@
 
-    According to this two-phase formation scenario, the late time growth of massive ETGs 
+    {\bf PP here about mass dependence: in the simulations, a larger fraction of the mass 
+    is ex-situ at increasingly higher mass. Can we see evidence for that observationally by 
+    looking at light profiles?}
+
+    In addition, according to this two-phase formation scenario, the late time growth of massive ETGs 
     is intrinsically tied to the growth of their host dark matter halos 
@@
     structural properties of massive galaxies should depend on their ``environment''
-    \footnote{There are different observational definitions of ``environment''. 
-    In this paper, we use the term ``environment'' and halo mass interchangeably}.
-
-    Previous work has shown that the half-light radii of massive ETGs is tightly 
-    correlated with \mstar{} (e.g. \citealt{Shen2003, Guo2009}). 
-    Models based on the ``two-phase'' formation scenario naturally predict that this 
-    mass--size relation should exhibit an environmental dependence: the effective radii 
-    of massive ETGs in more massive halos should be larger than those in less massive
-    halos at fixed \mstar{} (e.g. \citealt{Shankar2013, Shankar2014}).
-
-    However, while hints of an environmental dependence in the mass-size relation have 
-    been spotted at high-$z$ (e.g. \citealt{Papovich2012, Lani2013, Delaye2014}; but 
-    also see \citealt{Rettura2010}), there is no solid evidence for this effect at 
-    low-$z$ (e.g. \citealt{Nair2010, HCompany13}; but also see \citealt{Yoon2017}). 
-    The absence of an environmental dependence in the mass-size relation is an 
-    outstanding challenge to the two-phase formation scenario of ETGs.
-
-    From an observational perspective, we hypothesize that the lack of a detection of 
-    this effect may be related a combination of the methodologies employed, as well as 
-    the lack of deep high-quality imaging for large numbers of massive ETGs. 
-    In particular, massive ETGs have very steep inner stellar density profiles, 
+
+    In order to truly understand the build-up of the outer parts of massive galaxies, very 
+    deep data are needed. Massive ETGs have very steep inner stellar density profiles, 
     extremely extended stellar envelopes, and radial-dependent isophotal shapes which 
@@
     limit $> 28.5$\sb) imaging from the Hyper-Suprime Cam (HSC) Subaru Strategic 
-    Program \citep[SSP,][]{HSCDR1} to revisit the 
-    question of the environmental dependence in the mass-size relation. 
-    The goal of this paper is to compare the \mden{} profiles and structural scaling 
-    relations of massive central galaxies in both low and high mass dark matter halos. 
-    Fig~\ref{fig:sdss_compare} displays a comparison of the imaging quality of massive 
-    ETGs using SDSS versus using the new HSC data. 
+    Program \citep[SSP,][]{HSCDR1} to characterize the outer parts of massive galaxies 
+    as a function of their properties. Here we will focus on (a) showing that we can 
+    measure profiles for galaxies out to 100 kpc reliably with the HSC data and (b) looking at 
+    trends in stellar mass and outer envelope properties. In a second paper in this series, we 
+    will directly show the environmental dependence of the outer envelope mass.
+    %The goal of this paper is to compare the \mden{} profiles and structural scaling 
+    %relations of massive central galaxies in both low and high mass dark matter halos. 
+    %Fig~\ref{fig:sdss_compare} displays a comparison of the imaging quality of massive 
+    %ETGs using SDSS versus using the new HSC data. 
     The deep imaging depth and excellent seeing conditions of HSC images make them 
@@
 
-    Massive central galaxies in this work show an intriguing diversity on the plane 
-    defined by these two metrics.  
-    We preview this using Fig~\ref{fig:m100_m10_color}, which shows a subsample of 
-    massive galaxies at $z{\sim} 0.4$ that share very similar value of \minn{}, but 
-    exhibit a large diversity in their outer profiles. 
-    Assuming that galaxies at fixed \minn{} share a similar in-situ formation history, 
-    it is of great interest to investigate the relation between their present day halo 
-    mass and the extend of their outer envelopes. 
-    We note that although a circular aperture is shown on Fig~\ref{fig:m100_m10_color}, 
-    for our mass measurements, we always use elliptical apertures that follow the 
-    average isophotal shape. Finally, given our narrow mass and redshift range, we 
-    can safely ignore significant mass growth and structural evolution in this work
-    (no star formation, lower merger rate \etal~e.g.\ \citealt{Bellstedt2016},
-    \citealt{Inagaki2015}; but also see \citealt{Bai2014}).
+    {\bf We will show the implications for the stellar mass function of including most of 
+    the stellar light, a task that has been complicated before now due to shallower data. 
+    We will also investigate the idea that the accreted fraction is a function of stellar mass.}
 
@@
     HSC and the \texttt{S82-MGC} in Section \ref{ssec:s82}.
+    {\bf Seems to have the section wrong? Plus, can we consolidate these discussions?}
 
@@
 
-    Our study focuses on galaxies located at the center of their dark matter halos. 
+    For now, we wish to focus on galaxies located at the center of their dark matter halos. 
     To limit our sample to central galaxies, we use \texttt{v5.10} of the \redm{}{} 
@@
     live in massive halos.
-
-    Due to the depth and resolution of SDSS, the \redm{} catalog becomes slightly 
-    incomplete at lower richness ($\lambda < 40$) at $z > 0.33$. 
-    To ensure a clean separation in \mhalo{}, here we only focus on the central 
-    galaxies of clusters with $\lambda > 30$. 
-    According to \citet{Simet2016}, this $\lambda \geq 30$ sample should correspond to 
-    $M_{\mathrm{halo}}>10^{14.2} M_{\odot}$. 
-    We have checked that none of the results in this work depend on the choice of this 
-    $\lambda$ limit. 
-    For massive central galaxies that are not in these cluster-level halos, 
-    we unfortunately can not estimate their \mhalo{} individually, but it is safe 
-    to assume they will have $\log (M_{\mathrm{halo}}/M_{\odot}) < 14.0$.  
 %% ------------------------------------------------------------------------------------ %%
@@
 
-    Based on recent constraints of $M_{\star}$-$M_{\mathrm{Halo}}$ relation 
+    One of the goals of our work is to investigate the halo dependence of the outer 
+    envelope. Although there is a correlation between $M_{\star}$ and $M_{\mathrm{Halo}}$,
+    based on recent constraints of $M_{\star}$-$M_{\mathrm{Halo}}$ relation 
     (e.g.\ \citealt{Leauthaud2012}, \citealt{Behroozi2013}, \citealt{Kravtsov2014}), 
     even though our sample selects very massive galaxies (\logms{}$\geq 11.5$), they 
-    live in a fairly broad range of halos masses.
     With the help of the \redm{} catalog, we can broadly separate our sample into two
     groups with \logmh{}$<14.0$ and \logmh{}$>14.2$.
+    live in a fairly broad range of halos masses.
 
@@
 
+    Due to the depth and resolution of SDSS, the \redm{} catalog becomes slightly 
+    incomplete at lower richness ($\lambda < 40$) at $z > 0.33$. 
+    To ensure a clean separation in \mhalo{}, here we only focus on the central 
+    galaxies of clusters with $\lambda > 30$. 
+    According to \citet{Simet2016}, this $\lambda \geq 30$ sample should correspond to 
+    $M_{\mathrm{halo}}>10^{14.2} M_{\odot}$. 
+    We have checked that none of the results in this work depend on the choice of this 
+    $\lambda$ limit. 
+    For massive central galaxies that are not in these cluster-level halos, 
+    we unfortunately can not estimate their \mhalo{} individually, but it is safe 
+    to assume they will have $\log (M_{\mathrm{halo}}/M_{\odot}) < 14.0$.  
+    {\bf I am still a bit confused why stellar mass completeness depends on Mh??}
+
     We note that at this stage, our \nbcg{} sample still contains galaxies with a 
@@
             with reliable redshift information. 
-        \item \rbcg{} sample: we select a sample of 164 galaxies at 
-            $0.3 \leq z \leq 0.5$ that are the central galaxies 
-            in $\lambda > 30$ \redm{} clusters. 
-            They represent the central galaxies in very massive halos 
-            (\logmh{}$\geq 14.2$). 
-        \item \nbcg{} sample: after excluding all cluster members from the 
-            \texttt{hscZ} sample, we have 14661 bright galaxies at 
-            $0.3 \leq z \leq 0.5$. 
-            After applying an additional \mstar{} cut (see Section 
-            \ref{ssec:isedfit}), this sample corresponds to central galaxies in 
-            halos with \logmh{}$<14.0$.  
+        \item {\bf Select only central galaxies using RedMapper: total number in full 
+        sample?}
+        \item We further divide the sample into an \rbcg{} sample and a \nbcg{} sample, 
+          with the former roughly having \logmh{}$\geq 14.2$ and the latter having 
+           \logmh{}$<14.0$.
+
+%          : we select a sample of 164 galaxies at 
+%            $0.3 \leq z \leq 0.5$ that are the central galaxies 
+%            in $\lambda > 30$ \redm{} clusters. 
+%            They represent the central galaxies in very massive halos 
+%            (\logmh{}$\geq 14.2$). 
+%        \item \nbcg{} sample: after excluding all cluster members from the 
+%            \texttt{hscZ} sample, we have 14661 bright galaxies at 
+%            $0.3 \leq z \leq 0.5$. 
+%            After applying an additional \mstar{} cut (see Section 
+%            \ref{ssec:isedfit}), this sample corresponds to central galaxies in 
+%            halos with \logmh{}$<14.0$.  
     \end{itemize}
@@
 %% ------------------------------------------------------------------------------------ %%        
-  \begin{figure*}
-      \centering 
-      \includegraphics[width=\textwidth]{fig/redbcg_prof_1}
-      \caption{
-          The environmental dependence of the stellar mass profiles of massive central 
-          galaxies. 
-          The left panel corresponds to samples matched by ``total'' stellar mass 
-          (\mtot{}). 
-          The right panel corresponds to samples matched by ``core-mass'' (\minn{}). 
-          Orange and red lines correspond to central galaxies living in halos with 
-          \logmh{} $\geq 14.2$. 
-          Black and grey correspond to central galaxies living in halos with 
-          \logmh{} $\leq 14.0$. 
-          Thin lines show the profiles of individual galaxies while thick lines show 
-          the median profile. 
-          The uncertainty on the median profile is given by the shaded region and is 
-          computed via bootstrap resampling. 
-          The brown line in the bottom panels show the relative difference between 
-          two median profiles 
-          ($\Delta = \log(\mu_{\star, \mathrm{cenHighMh}}) - 
-          \log(\mu_{\star, \mathrm{cenLowMh}})$). 
-          Errors on the difference between the two profiles is computed via bootstrap 
-          too. 
-          The grey shaded regions show a Monte Carlo test to asses how likely is it to 
-          obtain $\Delta$ from random sub-samples of the data. 
-          To compute the grey shaded regions, we first mix the two samples 
-          (\rbcg{} and \nbcg{}), then draw sub-samples of galaxies from the mixed 
-          population and compute $\Delta$ in the same fashion as for our fiducial signal. 
-          We repeat this process 5000 times.  
-          The dark-grey shaded region (light-grey shaded region) shows the 1-$\sigma$ 
-          (3-$\sigma$) fluctuations in $\Delta$ from these 5000 draws.
-          }
-      \label{fig:prof_1} 
-  \end{figure*}
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %%        
     \subsection{Stellar Mass Completeness}
@@
 
+    {\bf Still worth thinking about where this belongs and if it can be consolidated with the 
+    previous discussion somehow. Maybe better in results?}
     With the help of the \texttt{S82-MGC} (\citealt{Bundy2015}), we investigate the 
@@
     reasonably complete down to \logms{}${\sim} 11.6$ at $0.3 \leq z \leq 0.5$. 
-    The \rbcg{} sample is less affected by completeness because we can utilize 
-    photo-$z$s from \redm{}. 
-    However, the completeness of the \nbcg{} sample is still limited by the 
-    availability of spec-$z$s from BOSS.
-
+    %The \rbcg{} sample is less affected by completeness because we can utilize 
+    %photo-$z$s from \redm{}. 
+    %However, the completeness of the \nbcg{} sample is still limited by the 
+    %availability of spec-$z$s from BOSS.    
     In this work, we will focus on the range $11.6 \le$ \logmtot{}$ \le 11.9$ 
     where our two samples are complete. 
-    When comparing \nbcg{} and \rbcg{} we will also always make sure that the two 
-    samples are well matched both in terms of \mstar{} as well as in terms of redshift. 
-    Please see the next section and Appendix~\ref{app:match} for more details.
+    %When comparing \nbcg{} and \rbcg{} we will also always make sure that the two 
+    %samples are well matched both in terms of \mstar{} as well as in terms of redshift. 
+    %Please see the next section and Appendix~\ref{app:match} for more details.
 %% ------------------------------------------------------------------------------------ %%
@@
     radius and color gradients at the outskirts are not yet well quantified.
-    More importantly, for the comparison between the \rbcg{} and \nbcg{} samples, 
-    our results will be robust as long as there is \emph{no significant difference in 
-    the average color gradient between the two samples}. 
+    Our results looking at the outer envelopes as a function of mass and environment 
+    will be robust as long as there is \emph{no significant difference in 
+    the average color gradient between sub-samples}.
+    %More importantly, for the comparison between the \rbcg{} and \nbcg{} samples, 
+    %our results will be robust as long as there is \emph{no significant difference in 
+    %the average color gradient between the two samples}. 
     We have confirmed that this is indeed the case and this will be discussed in 
@@
     towards the higher-mass end and slightly modifies the high-mass slope. 
-    The impact of missing flux is most prominent for the \rbcg{} sample.
+    %The impact of missing flux is most prominent for the \rbcg{} sample.
     For studies about the SMF or other aspects of galaxy evolution based on 
@@
 %% ------------------------------------------------------------------------------------ %% 
-\subsubsection{Environmental Dependence of the Profiles of Massive Galaxies}
-    \label{sssec:sbp_mtot}
-
-    We now ask whether or not galaxies from our sample have \mden{} profiles that 
-    depend on \mhalo{} (at fixed \mstar{}). 
-    For this, we will build matched samples drawing from \rbcg{} and \nbcg{} that are 
-    carefully matched in \mstar{} and redshift using a KDTree algorithm 
-    (see Appendix~\ref{app:match} and Fig~\ref{fig:match} for details). 
-    By matching the redshift distributions within $0.3 < z < 0.5$, we ensure that the 
-    \mden{} profiles from both samples are impacted by seeing and background subtraction 
-    at similar levels. 
-    To match the two samples by stellar mass, we will use two different methods:
-
-    \begin{itemize}
-
-        \item We match the two samples according to \mtot{}. 
-            We select galaxies from \rbcg{} with $11.6 < $\logmtot{} $<11.9$ 
-            (median \logmtot{} ${\sim} 11.74$). 
-            There are 45 \rbcg{} galaxies in this range. 
-            We then match this distribution by drawing galaxies from \nbcg{}. 
-            There are 229 unique \nbcg{} galaxies in the matched sample. 
-            In this \mtot{} range, 100 kpc corresponds to 5-8 times the effective radius 
-            and \mtot{} is a good proxy of total stellar mass.
-
-       \item We match the two samples according to \minn{}. 
-           We select galaxies from \rbcg{} with $11.2 < $\logminn{}$ < 11.6$ 
-            (median \logminn{}${\sim} 11.36$).
-            For the 56 galaxies from the \rbcg{} sample, we achieve excellent matches
-            in \minn{} and redshift using 375 \nbcg{} galaxies.
-            Motivated by recent observations and simulations, we use \minn{} as the 
-            proxy of the \mstar{} of the ``in-situ'' component.
-            We will discuss more about this assumption in 
-            Section~\ref{sec:discussion}.
-
-    \end{itemize}
-
-%% ------------------------------------------------------------------------------------ %%     
-    Fig~\ref{fig:prof_1} compares the profiles of galaxies at fixed \mtot{} and at fixed 
-    \minn{} for our two matched samples, and shows the main results of this paper which 
-    is that we find a clear halo mass dependence in the \mden{} profiles of massive 
-    galaxies. 
-    The bottom panel of Fig~\ref{fig:prof_1} shows the difference between the two 
-    profiles, $\Delta = \log(\mu_{\star, \mathrm{cenHighMh}}) - 
-    \log(\mu_{\star, \mathrm{cenLowMh}})$, 
-    with errors computed via bootstrap resampling. 
-    In Appendix~\ref{app:robust}, we present a variety of tests that verify the 
-    robustness of these results against different uncertainties.
-
-    There are several important points to be noticed in Fig~\ref{fig:prof_1}. 
-    First, when galaxies are matched by \mtot{}, although we detect a robust 
-    environmental dependence, it mainly only becomes prominent in the outskirts 
-    at $R>50$ kpc. 
-    This partially explains the difficulties for previous works to detect this effect
-    on shallower images. 
-    Second, we find that central galaxies in more massive dark mater halos display 
-    more flattened inner profile and more significant outer stellar envelope than 
-    the ones living in less massive halos. 
-    Third, the median \mden{} profiles of \rbcg{} and \nbcg{} cross each other 
-    at ${\sim} 15$-20 kpc, the expected $R_{\mathrm{e}}$ for ETGs at this \mtot{}. 
-    Finally, such systematic difference in structure may become more significant 
-    at very high-mass end. 
-    We see evidence of this effect when we compare the $Delta$ profiles in two \mtot{} 
-    bins (see Fig~\ref{fig:prof_2} and discussion in 
-    Appendix~\ref{app:robust})\footnote{Though the lower \mtot{} bin becomes somewhat
-    incomplete} and when we discuss the relation between \mtot{} and \minn{} for 
-    these two samples (see Fig~\ref{fig:scaling_relation}). 
-    This potential interesting result and its implication is worth more investigations 
-    later.
-
-    Meanwhile, the subtle environmental dependence of \mden{} profiles for the 
-    \mtot{}-matched samples suggests that environment does not play the major role in 
-    shaping massive galaxies \textbf{at fixed total stellar mass}.
-    Therefore it is interesting to ask, for massive galaxies that \textbf{contain 
-    similar \mstar{} in the in-situ component}, how does environment affect their 
-    subsequent mass assembly?
-    Assuming that the \minn{} is reasonable proxy of in-situ mass, we look into this 
-    question by comparing the \mden{} profiles of the \minn{}-matched samples ( 
-    Fig~\ref{fig:prof_1}, right).  
-    Although the median \mden{} profiles are similar at $r \leq 10$ kpc, the
-    central galaxies in more massive halos clearly possess much more prominent outer
-    envelope. 
-    This result is robust in a series of statistical and systematical tests 
-    (see Appendix~\ref{app:robust}.
-
-    At the same time, the uniform slope of the \mden{} profiles within 
-    10 kpc is in sharp contrast with the large scatter of the outskirts. 
-    It hints that these two regions are shaped by distinctive processes, and may 
-    explain their differences in environmental dependency. 
-    In simulations, intensive dissipative process helps create 
-    self-similar de~Vaucouleur-like ($n{\sim} 4$) \mden{} profile in the inner part 
-    of massive galaxy (e.g. \citealt{Hopkins2008}), and the \mhalo{}-dependent
-    merging history leads to shallower stellar halo profile for central galaxy 
-    of more massive halo (e.g. \citealt{Pillepich2014}). 
-    The stochastic nature of the merging process also helps explain the 
-    large scatter in the distributions of outer \mden{} profiles. 
-    We illustrate this interesting diversity in Fig~\ref{fig:m100_m10_color}, where 
-    we show the 3-color images of randomly selected massive central galaxies that 
-    have similar \minn{} 
-    ($11.1 \leq \log (M_{\star,\ 10\mathrm{kpc}}/M_{\odot}) < 11.2$)
-    but different \mtot{}.   
-    From the top-left to the bottom-right, the \mtot{} of these galaxies increases
-    from $10^{11.22} M_{\odot}$ to $10^{11.75} M_{\odot}$.
-
-    \textbf{In summary, we reliably detect subtle, but systematic \mhalo{}-dependence 
-    (environmental dependence) of structure in massive central galaxies}, which seems 
-    to be consistent with the expectation of more frequent (minor) mergers in denser 
-    environment. 
-    These minor, non-dissipative mergers do not alter the inner \mden{} profiles 
-    a lot, but are efficient in depositing stars to the outer envelope
-    (e.g. \citealt{Hilz2013}, \citealt{Oogi2013})
-
-    The median profiles shown in Fig~\ref{fig:prof_1} are available in Table~1.
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %% 
 \subsection{Ellipticity and Color Profiles}
@@
     profiles are very similar.  
+    {\bf I suggest we keep this}
     This further hints that massive central galaxies in different halos but with 
@@
     $g-r$ and $g-i$ color profiles for both \rbcg{} and \nbcg{} galaxies. 
+    {\bf Can we also look as a function of stellar mass?}
     For both \mtot{}- and \minn{}-matched samples, we find no significant difference
@@
     CCDs), therefore can help provide more accurate color estimates.
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %% 
-\subsection{The Environmental Dependence of Scaling Relations}
-    \label{ssec:scaling}
-
-%% ------------------------------------------------------------------------------------ %% 
-  \begin{figure*}
-      \centering 
-      \includegraphics[width=\textwidth]{fig/redbcg_scaling_relation}
-      \caption{
-          \textbf{Left}: The mass-size relations for \rbcg{} (orange squares) and 
-          \nbcg{} (grey dots) galaxies. 
-          Two vertical lines highlight our $11.6<$ \logms{} $<11.9$ mass bin. 
-          The red solid line shows the best fit mass-size relation for \rbcg{} and the 
-          grey dashed line shows the best fit relation for \nbcg{}. 
-          Shaded regions in lighter colors show the 1-$\sigma$ uncertainties
-          from MCMC sampling.  
-          The green dashed line shows the mass-size relation for nearby central 
-          galaxies in massive groups from \citet{HCompany13}. 
-          \textbf{Right:} The relations between \mtot{} and \minn{} for the 
-          \rbcg{} and \nbcg{} galaxies, along with the best-fit scaling relations for 
-          both samples.
-          }
-      \label{fig:scaling_relation} 
-  \end{figure*}
-%% ------------------------------------------------------------------------------------ %%
-
-\subsubsection{Mass-Size Relation}
-    \label{sssec:mass_size}
-
-    Despite numerous attempts, previous studies have failed to clearly 
-    demonstrate the existence of an environmental dependence of mass-size relation
-    at low-$z$ (e.g. \citealt{Weinmann2009, Nair2010, HCompany13, Cerbrian2014})
-
-    %Despite being the focus of previous investigations (e.g. \citealt{Shankar2013};
-    %\citealt{Leja2013}, \citealt{vdWel2014}), the relation between \mstar{} and 
-    %effective radius (or half-light radius; $R_{\mathrm{e}}$ or $R_{\mathrm{50}}$) 
-    %has yet to provide clear evidence of environmental dependence of structures of 
-    %massive galaxies at low-$z$ (e.g. \citealt{Weinmann2009}, \citealt{Nair2010}, 
-    %\citealt{HCompany13}, \citealt{Cerbrian2014}), and sent controversial messages 
-    %about the pictures at high-$z$ (e.g. \citealt{MCooper2012}, \citealt{Papovich2012}, 
-    %\citealt{Kelkar2015}).
-
-    By using deep HSC images, and by comparing\mden{} profiles directly, 
-    we have shown that the structures of massive galaxies do depend on the masses of 
-    their host halos (see the left panel of Fig~\ref{fig:scaling_relation}). 
-    We now present our results in terms of the more traditional ``mass-size'' relation. 
-    For this purpose, we will use \mtot{} as our ``total'' \mstar{} and the radius 
-    enclosing 50\% of luminosity within 100 kpc ($R_{\mathrm{50}}$; derived from the 
-    $i$-band curve-of-growth) as our ``size''. 
-    This definition of ``effective radius'' is more robust against structural details, 
-    choice of model, and the background subtraction. 
-    Our massive galaxies are large enough that we do not need to worry about the 
-    effects of seeing.
-
-    Fig~\ref{fig:scaling_relation} shows the \mstar{}-size relations for both samples. 
-    We fit the \logmtot{}-$\log (R_{\mathrm{50}}/\mathrm{kpc})$ relations at 
-    \logmtot{}$\geq 11.6$\footnote{We use MCMC and the ensemble sampler 
-    \texttt{emcee} (\citealt{Emcee}) with initial guesses are based on maximum 
-    likelihood estimates, and we assume reasonable flat priors for parameters.}.
-    The best-fit relation for \rbcg{} is:
-
-    \begin{equation}
-        \begin{aligned}
-        \log (R_{\mathrm{50}}/\mathrm{kpc}) = & (0.73\pm0.13) \times \log (M_{\star, 100\ \mathrm{kpc}}/M_{\odot}) \\ & -(7.49\pm1.56)
-        \end{aligned}
-    \end{equation}
-
-    \noindent And for \nbcg{}, we find:
-
-    \begin{equation}
-        \begin{aligned}
-        \log (R_{\mathrm{50}}/\mathrm{kpc}) = & (0.68\pm0.06) \times \log (M_{\star, 100\ \mathrm{kpc}}/M_{\odot}) \\ & -(6.88\pm0.75)
-        \end{aligned}
-    \end{equation}
-
-    \noindent As shown in Fig~\ref{fig:scaling_relation}, the slopes of the \mtot{}-size 
-    relations are similar between the two samples, but the normalization of the 
-    \mtot{}-size relation is different for \rbcg{} compared to \nbcg{}. 
-    This result is robust against the ranges of \mstar{}, also the definitions of 
-    ``total'' \mstar{} and  half-light radius\footnote{Using \mstar{} within 120 or 150 
-    kpc, or using the $R_{\mathrm{50}}$ derived within these apertures will not change 
-    the results.}.
-
-    We qualitatively compare our results with \citealt{HCompany13} (HC13; green solid line) 
-    who studied $z\leq 0.09$ central ETGs in  $14\le$ \logmh{} $<15$ halos. 
-    HC13 used the group catalog by \citet{Yang2007} to estimate \mhalo{} after empirically 
-    convert their \mstar{} from a Kroupa IMF to a Chabrier IMF by applying a constant 
-    -0.05 shift (see \citealt{Bernardi2016}).
-    They estimated the 2-D $R_{\mathrm{e}}$ using single-\ser{} model fitting to SDSS 
-    images, and derived \mstar{} based on SED fitting using the BC03 (\citealt{BC03}) 
-    synthetic population model. 
-    We add $+0.1$dex to the HSC13 results to account for the systematic 
-    difference between their BC03 and our FSPS model (see Appendix~\ref{app:sed}). 
-    The mass-size distributions for both \rbcg{} and \nbcg{} galaxies follow the 
-    HC13 relation reasonably well (with slightly shallower slopes) even at 
-    \logmtot{}$< 11.6$ where our samples start to become incomplete. 
-    In contrast to the present study, HC13 finds no halo mass dependence in the 
-    mass-size relation for $12.5\le$ \logmh{} $<15.0$ halos.
-    A possible explanation for this difference is that the region that strongly depends 
-    on halo mass is the low surface brightness outer envelope where the stars are 
-    mostly assembled through multiple mergers. 
-    This region is difficult to detect on shallow SDSS images, but the much deeper 
-    HSC images can provide accurate measurements of total \mstar{} and size.
-
-    In conclusion, we confirm that massive central galaxies at $0.3 < z < 0.5$
-    follow \mstar{}-size relations that depend on the masses of their host halos. 
-    Central galaxies in denser environment (higher \mhalo{}) have slightly 
-    larger $R_{\mathrm{50}}$ comparing to ones in smaller haloes at fixed 
-    \mtot{}. 
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %% 
-\subsubsection{\mtot{} - \minn{} Relation}
-    \label{sssec:m100_m10}
-
-    We also investigate the relationship between \mstar{} for two different
-    fixed physical apertures (\mtot{} v.s. \minn{}) as alternative tool to help us 
-    understand the relationship between \mhalo{} and the assembly history of massive
-    galaxies.   
-    Comparing to the mass-size relation, this relation is not affected by the 
-    ambiguous definition of ``size'', and is much easier to apply to larger samples 
-    and to simulations.
-
-    The right panel of Fig \ref{fig:scaling_relation} compares \mtot{} and \minn{}. 
-    We find that our \rbcg{} and \nbcg{} occupy different locations within this plane,
-    and follow different best-fit \mtot{} - \minn{} relations. 
-    For \rbcg{} galaxies we find:
-
-    \begin{equation}
-        \begin{aligned}
-        \log (M_{\star, 10\ \mathrm{kpc}}/M_{\odot}) = & (0.48\pm0.06) \times \log (M_{\star, 100\ \mathrm{kpc}}/M_{\odot}) \\ & +(5.72\pm0.75).
-        \end{aligned}
-    \end{equation}
-
-    \noindent In the same range of \mtot{}, the best-fit relation for \nbcg{} is:
-
-    \begin{equation}
-        \begin{aligned}
-        \log (M_{\star, 10\ \mathrm{kpc}}/M_{\odot}) = & (0.56\pm0.03) \times \log (M_{\star, 100\ \mathrm{kpc}}/M_{\odot}) \\ & +(4.82\pm0.30).
-        \end{aligned}
-    \end{equation}
-
-    We have checked that our results are unchanged if we replace the \minn{} with 
-    \mstar{} within 5 or 15 kpc apertures. 
-    Although the $M_{\star, 5\ \mathrm{kpc}}$ values are less reliable than \minn{} 
-    due to the impacts of seeing, the relation using $M_{\star, 5\ \mathrm{kpc}}$ shows 
-    more significant \mhalo{} dependence at the high-mass end.
-    Also, best-fit relation using the full \mtot{} range results in even shallower 
-    slope for the \rbcg{} galaxies.
-
-    Our results suggest that: 
-    (1) At fixed \mtot{}, central galaxies in more massive halos tend to have 
-    lower fractions of \mstar{} stored in the inner region; 
-    (2) For massive galaxies with similar \minn{}, the ones in more massive halos on 
-    average have more prominent outer envelopes. 
-    The scientific implication of this result is briefly discussed in 
-    Section~\ref{sec:discussion}.
 %% ------------------------------------------------------------------------------------ %%
@@
 
+    {\bf Do we need two different sections and two different radial profile figures?}
+
     Our results are consistent with the picture that massive central galaxies form via 
@@
     Fig \ref{fig:discussion_1} compares the median \mden{} profiles of the 
-    combined \rbcg{} and \nbcg{} samples in two \mtot{} bins 
+    galaxies in two \mtot{} bins 
     ($11.4\leq$\logmtot{}$<11.6$ and $11.6\leq$\logmtot{}$<11.8$) with 
@@
 
-    At the same time, we also find \rbcg{} galaxy tends to have lower \mstar{} within 
-    inner 5-10 kpc and shallower inner \mden{} profile than the \nbcg{} one at 
-    fixed \mtot{}. 
-    Although the HSC images do not have sufficient resolution to investigate this in 
-    details, it is worth pointing out that this difference could be physically 
-    interesting. 
-    Observations of compact quiescent galaxies at high-$z$ often reveal higher 
-    \mden{} in the central region than their descendants, and certain process need to  
-    be responsible for reducing the central \mden{} (e.g. strong adiabatic expansion 
-    induced by powerful AGN feedback; \citealt{Fan2008}).
-    Coalesce of super-massive black hoes (SMBHs) at the end of major merger, which is 
-    common in the assembly history of massive galaxies, can also flatten the central 
-    \mden{} profile (e.g. \citealt{Milosavljevi2002}).
-    On the right side of Fig \ref{fig:scaling_relation}, we find a few \rbcg{} galaxies 
-    with very low \minn{} at high \mtot{} end that are apparently not bothered by 
-    problematic photometry or exceptionally bad seeing.  
-    They may be similar to the recently discovered massive BCGs with very large core 
-    (a few kpc; e.g. \citealt{Postman2012, LopezCruz2014}) resulting from SMBH mergers.
-    The impacts of these processes, and their dependence on \mhalo{} is an interesting 
-    topic to investigate in the future.
+    {\bf Have we looked at delta M as a function of Mtot?  I think that would be useful 
+    for comparison with the Oser papers, for instance. }
+
 %% ------------------------------------------------------------------------------------ %%
@@
 %% ------------------------------------------------------------------------------------ %% 
-
-\subsection{Scatter in Outer Stellar Enveloppes and ``cD'' Galaxies}
-
-   The thin lines in Figure \ref{fig:prof_1} show the \mden{} density profiles of 
-   individual galaxies. 
-   In general, we find that any given galaxy has a relatively smooth profile, even out 
-   to large radii, however, on a galax-by-galaxy basis there is a large (but continuous) 
-   variation in the amplitude of \mden{} at large scales. 
-   Traditionally, the so-called ``cD'' galaxies are defined to have large stellar 
-   envelopes and are found at the hearts of massive clusters (\citealt{Matthews1964, 
-   Schombert1988}). 
-   However, until present, it has not been clear whether ``cD'' galaxies are a distinct 
-   and special population, or if they are simply the continum of a smoothly varying 
-   population. 
-   Fig \ref{fig:prof_1} shows that with the help of our deep HSC images, we can directly 
-   map out the variations in \mden{} profiles at large scales. 
-   Instead of a bi-model distribution, we find that the outskirts of massive galaxies 
-   display a smooth but continuous variation. 
-   We can hence conclude that ``cD'' galaxies are simply the extremes of a continuous 
-   population but that do not necessarily form a unique a special class of galaxies. 
-   This suggests that it might not be very physically meaningful to separate these 
-   massive galaxies into two arbitrary morphological classes (``cD'' versus non-``cD''). 
-   This conclusion is similar to those of \citep{Zhao2015} who found that a large 
-   fraction of nearby BCGs (34\%) does not fall into the ``cD'' class. 
-   Our finding that massive galaxies display a diverse range of outer stellar 
-   envelope is also supported by HST observations of BCGs at $0.3 < z <0.9$ 
-   by \citealt{Bai2014}.
-
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %% 
 \subsection{What is the ``Total Mass'' of Massive Galaxies?}
@@
     ICL only becomes important outside that radius and is dominated by individual 
-    tidal features.
+    tidal features. {\bf I continue to think you are saying all gals have some ICL, rather 
+    that no galaxies have ICL...}
 
@@
             amount of light in their outskirts. 
-            We argue that ``cD'' galaxies simply represent the tail end of a 
-            distribution but that they are not a distinct class of massive galaxies.
-
-        \item At fixed \mstar{} evaluate within 100 kpc, we find that massive central 
-            galaxies display \mden{} profiles that are not self-similar and which 
-            present subtle but systematic differences that correlate with \mhalo{}.
-            On average, massive central galaxies in more massive halos have slightly 
-            shallower inner \mden{} profiles and more prominent outer envelope.
-
-        \item We also study how the \mden{} profiles vary with \mhalo{} at fixed 
-            ``in-situ'' mass where it is approximated by the \mstar{} within 10 kpc. 
-            At fixed \minn{} we find that central galaxies in more massive halos 
-            possess much more extended stellar envelope in the outskirts than the ones 
-            in smaller halos. 
-            At the same time the ellipticity, and optical color profiles inside 10 kpc 
-            show little to no dependence on environment.
-
-        \item The \mstar{}-size relation also exhibits a clear environmental 
-            dependence and central galaxies in more massive halos have larger 
-            $R_{\mathrm{50}}$ at fixed \mtot{}. 
-            We suggest that the relation between \mtot{} and \minn{}\footnote{or any 
-            better proxy of total \mstar{} and the mass formed in the ``in-situ'' phase.} 
-            can be a useful tool in diagnosing the assembly history of these massive 
-            galaxies and the connection with the assembly of their dark matter halos.
+            {\bf KEEP? We argue that ``cD'' galaxies simply represent the tail end of a 
+            distribution but that they are not a distinct class of massive galaxies.}
+
+        \item {\bf How do profiles depend on Mstar?}
 
@@
 
-%\acknowledgements
 \section*{Acknowledgements}
@@
 
+\song{A few appendix need to be moved to Paper II}
 %% ------------------------------------------------------------------------------------ %%

### 2017-03-31 draft/paper2.tex
Paper split

--- 2017-03-24 draft/ms_v10.tex
@@
-% Version 0; preprint format; Written by SH
-% Version 1; emulateapj format; Edited by SH and AL
-% Version 2; emulateapj format; Edited by SH and AL
-% Version 3; emulateapj format; Edited AL
-% Version 4; emulateapj format; Edited SH
-% Version 5; MNRAS format; Edited SH
+% Version 0; preprint format; Outline of paper II by Song Huang
 
@@
     formation. 
+    \song{This is the abstract of old draft, need some works}
 
@@
 %%%%%%%%%%%%: Main Text %%%%%%%%%%%%
-
-%% ------------------------------------------------------------------------------------ %% 
-    \begin{figure*}
-        \centering 
-        \includegraphics[width=\textwidth]{fig/redbcg_sdss_compare}
-        \caption{
-            A comparison between the depth and imaging quality of SDSS and the HSC wide 
-            layer for a sample of nearby massive elliptical galaxies at $0.2 < z < 0.5$.  
-            These images are generated using $gri$ band images with an arcsinh stretch 
-            \citep{Lupton2004}. 
-            The HSC \texttt{WIDE} layer is $3.0$-$4.0$ magnitudes deeper than SDSS.
-            This added depth is critical in order map the outskirts of ETGs out to 
-            large radii.
-            }
-        \label{fig:sdss_compare}
-    \end{figure*}
-%% ------------------------------------------------------------------------------------ %%
 
@@
 
+    \song{This is the old version, need works}
     Massive galaxies are unique laboratories for studying both cosmology and galaxy 
@@
 
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %% 
-    \begin{figure*}
-        \centering 
-        \includegraphics[width=\textwidth]{fig/redbcg_ellipse_example}
-        \caption{
-            Left: example of the 1-D surface brightness and ellipticity profile 
-            for a massive galaxy at $z=0.23$ in the $i$-band using \texttt{Ellipse}. 
-            In this work, we always show the radial profile using a $R^{1/4}$ scaling 
-            on the x-axis. 
-            By using this scale, the de Vaucouleurs profile will appear as a straight 
-            line on this figure. 
-            We also plot the relative brightness profile of the PSF model normalized 
-            at the central surface brightness of the galaxy to highlight the region 
-            affected by seeing. 
-            The grey shaded region highlights the region most affect by seeing 
-            ($r<3$ kpc).
-            On the top panel, the dash line shows the ellipticity used for the final 
-            isophote. 
-            Right: the three color image of this galaxy with isophotes 
-            extracted by \texttt{Ellipse}. 
-            The thick dotted line highlights the isophote with 
-            $\mu_{i}{\sim} 28.5$~\sb.
-            }
-        \label{fig:ellipse}
-    \end{figure*}
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %% 
-\section{Data And Sample Selection}
-    \label{sec:data}
-
-\subsection{The Hyper Suprime-Cam Survey}
-    \label{ssec:hsc}
-
-    The Subaru Strategic Program (SSP, \citealt{MiyazakiInPrep}) makes use of the new 
-    prime-focus camera, the Hyper Suprime-Cam (HSC;~\citealt{Miyazaki2012}), on the 
-    8.2-m Subaru telescope at Mauna Kea. 
-    The ambitious multi-layer HSC survey takes advantage of the large field of 
-    view (FoV;~1.5 deg in diameter) of this camera and will cover ${\sim} 1400$ deg$^2$ 
-    in 5 broad bands ($grizY$) to a limiting depth of $r {\sim} 26$ mag 
-    in the \texttt{WIDE} layer. 
-    This work is based on the internal data release \texttt{S15B}, which covers 
-    ${\sim} 100$ deg$^2$ in all 5-band to full \texttt{WIDE} depth.  
-    The regions covered by this release overlap with a number of spectroscopic surveys 
-    (e.g.\ SDSS/BOSS: \citealt{Eisenstein2011}, \citealt{Alam2015}; 
-    GAMA: \citealt{Driver2011}, \citealt{Liske2015}).
-
-    The HSC \texttt{WIDE} survey is about $3.0$-$4.0$ magnitudes deeper in the $i$-band 
-    than SDSS. 
-    Combined with the excellent imaging resolution (the median $i$-band seeing is 
-    0.6\asec), and the wide area, the HSC survey represents a tremendous data set to 
-    perform a large statistical study of the surface brightness profiles of ETGs out to 
-    large radii.     
-    Fig~\ref{fig:sdss_compare} illustrates the quality of HSC imaging compared to SDSS 
-    for three low redshift ETGs, and shows that HSC survey data are well suited for 
-    mapping the stellar distribution of massive galaxies out to large radii.
-
-	HSC $i$-band images typically have the best seeing compared to other bands because 
-	of strict requirements driven by weak lensing science. 
-    We will therefore use the $i$-band images to measure the stellar distributions of 
-    massive galaxies.
-
-%% ------------------------------------------------------------------------------------ %% 
-\subsection{HSC Data Processing}
-    \label{sec:pipeline}
-
-    The full details of the HSC data processing can be found in \citet{BoschInPrep}
-    and are briefly summarized here. 
-    The HSC SSP data are processed with \texttt{hscPipe 4.0.1}, a derivative of the 
-    Large Synoptic Survey Telescope (LSST) pipeline (e.g.\ \citealt{Juric2015}; 
-    \citealt{Axelrod2010}), modified for HSC. 
-    \texttt{hscPipe} first performs a number of tasks at the single exposure level 
-    (bias subtraction, flat fielding, background modeling, object detection and 
-    measurements). 
-    Astrometric and photometric calibrations are performed at the single exposure level. 
-    \texttt{hscPipe} then warps different exposures on to a common World Coordinate 
-    System (WCS) and combines them into coadded images. 
-    At this stage, \texttt{hscPipe} updates the images with a better astrometric and 
-    photometric calibration using stars that are common among exposures.
-
-    The pixel scale of the combined images is $0.168^{\arcsec}$. 
-    Photometric calibration is based on data from the Panoramic Survey Telescope 
-    and Rapid Response System (Pan-STARRS) 1 imaging survey 
-    (\citealt{Schlafly2012}, \citealt{Tonry2012}, \citealt{Magnier2013}). 
-    To achieve consistent deblending and photometry across all bands, \texttt{hscPipe} 
-    performs multi-band post-processing at the coadd level. 
-    First, \texttt{hscPipe} performs object detection on coadd images in each band 
-    independently and records the flux peak and the above-threshold region 
-    (referred as a ``footprint'') for each source. 
-    Next, ``footprints'' and peaks from different bands are merged together before     
-    performing deblending and measurements. 
-    Finally, \texttt{hscPipe} selects a reference band for each object based on the 
-    $S/N$ in different bands (for most galaxies in this work, the reference band is 
-    the $i$-band). 
-    After fixing the centroids, shape, and other non-amplitude parameters of each 
-    object in this reference catalog, \texttt{hscPipe} perform forced photometry 
-    on the coadd image in each band. 
-    This forced photometry approach is optimized to yield accurate galaxy colors.
-
-    For each galaxy, \texttt{hscPipe} measures a \cmodel{} magnitude using an approach 
-    that is similar to SDSS (\citealt{BoschInPrep}). 
-    However, as opposed to SDSS, the HSC \cmodel{} is based on forced photometry which 
-    means that it can accurately measure both the \textit{fluxes and colors of galaxies}. 
-    The HSC \cmodel{} algorithm fits the flux distribution of each object using a 
-    combination of a de~Vaucouleur and an exponential component and accounts for the PSF. 
-    The performance of this algorithm has been tested using synthetic objects 
-    (\citealt{SynPipeInPrep}), and the results indicate that, generally speaking, 
-    the HSC \cmodel{} photometry is accurate down to $i >25.0$ mag.  
-    However, \cmodel{} currently systematically underestimates the total fluxes of 
-    massive ETGs with extended stellar distributions. 
-    This is caused by an intrinsic limitation of \cmodel{} as it is incapable of
-    modeling profiles with extremely extended outskirts, a problem that is exacerbated 
-    at the depth of the HSC survey. 
-    In addition, at the depth of the HSC survey, accurate deblending in the vicinity of
-    large ETGs where satellites and background galaxies often blend with the low surface 
-    brightness stellar envelope is a challenging problem. 
-    The deblending method implemented by the \texttt{hscPipe} currently tends to 
-    ``over-deblend'' the outskirts of bright galaxies and leads to an 
-    under-estimation of the the total flux of massive ETGs (this is discussed further in 
-    \citealt{BoschInPrep}).  
-    For these reasons, our results will be based on custom developed code to measure 
-    the luminosities and stellar masses of massive galaxies. 
-    We use the HSC \texttt{hscPipe} photometry for two purposes: 
-    1) to perform a first broad sample selection, and 2) to estimate the average 
-    color of massive galaxies.
-
-%% ------------------------------------------------------------------------------------ %% 
-\subsection{Initial Massive Galaxy Sample}
-    \label{ssec:initial}
-
-    We begin by using a broad luminosity cut to select an initial sample of massive 
-    galaxies at $z < 0.5$ from the HSC photometric catalog. 
-    Based on \citep{Leauthaud2016}, galaxies with \logms{}$\geq 11.5$ mostly have 
-    $i_{\mathrm{SDSS, cModel}} \leq 21.0$ mag. 
-    We therefore select our initial sample to be brighter than 
-    $i_{\mathrm{HSC, cModel}} \leq 21.5$\footnote{We neglect small differences between 
-    the response curves of SDSS-$i$ and HSC-$i$ filters.}
-    and also limit our sample to regions that have reached the required depth of 
-    the \texttt{WIDE} survey in the $i$-band.
-    %% The SQL search is saved as "sample.sql" 
-    %% The master catalog used here is "dr1_wide_galaxy_icmodel_21.5.fits"
-    %%   The original catalogs contain 2275477 objects
-
-    We further select extended objects with no deblending errors, with well defined 
-    centroids, and with \texttt{cModel} magnitudes in all five bands. 
-    After removing objects that have pixels affected by saturation, cosmic-rays, or 
-    other optical artifacts\footnote{each criterion removes less than 8\% of the 
-    entire sample.}.This sample corresponds to 1760845 galaxies and will be referred 
-    as \texttt{hscPho}. 
-    %% Saved as "dr1_wide_galaxy_hscPho.fits"
-
-    Here we limit our study to the very high-mass end where the majority of galaxies 
-    have either a spectroscopic redshift or a robust red-sequence photo-$z$ from the 
-    \redm{} catalog (see Section \ref{ssec:redmapper}).  
-    We match the \texttt{hscPho} sample with a spec-$z$ catalog compiled by the HSC 
-    team\footnote{It is created by matching HSC objects with all publicly available 
-    spectroscopic redshifts (e.g.\ SDSS/BOSS; GAMA). The spec-z quality flag from 
-    different catalogs are homogenized into a single flag that indicates secure 
-    redshifts.}.  
-    To ensure reasonable \mstar{}-completeness at the high-\mstar{} end we focus on
-    the redshift range $0.3 \leq z \leq 0.5$. 
-    %% This is catalog: "dr1_specz_use.fits"
-
-    For objects without a spectroscopic redshift, we match them with the central 
-    galaxies from the \redm{} catalog using a $2.0^{\arcsec}$ matching radius. 
-    The matched objects with useful red-sequence photo-$z$ ($z_{\lambda}$) are also 
-    included in the final sample of bright galaxies with reliable redshift between 
-    $0.3 \leq z \leq 0.5$. The accuracy of the red-sequence photo-$z$ is sufficient 
-    (median $|z_{\lambda} - z_{\mathrm{Spec}}| {\sim} 0.01$ for the ones with a 
-    spec-$z$) for the goal of this work.
-    The \redm{} catalog provides an additional 133 unique redshifts for massive 
-    galaxies in our sample.
-    %% Estimated from "dr1_redbcg_hsc_sdss_gama_1arcsec.fits"
-
-    In the end, at $0.3 \leq z \leq 0.5$, we gather a sample of 25286 galaxies with 
-    reliable redshift information (will be referred as \texttt{hscZ}).
-    %% Saved as "dr1_wide_galaxy_icmodel_21.5.fits"
-    Among them, the BOSS and SDSS ``legacy'' LRG samples provide the majority of 
-    spec-$z$. 
-    By comparing with the Stripe 82 Massive Galaxy Catalog
-    (\texttt{S82-MGC}; \citealt{Bundy2015}), \citet{Leauthaud2016} have measured the
-    \mstar{} completeness of the combined BOSS and SDSS samples. 
-    They estimate that the BOSS spec-$z$ sample is about 80\% complete at 
-    \logms{}$\geq 11.6$ at $0.3 < z < 0.5$. 
-    The GAMA survey, which partially overlaps with the HSC footprints, supplements 
-    our \texttt{hscZ} sample by 14\%. 
-    Based on \citet{Taylor2011} (e.g.\ their Fig~~6), at $z{\sim} 0.3$, the GAMA 
-    sample is 80\% complete down to $10^{10.8}$\msun; but only 80\% complete to 
-    $10^{12.0}$\msun at $z{\sim} 0.5$. 
-    We can therefore expect our sample to be roughly \mstar{}-complete above 
-    \logms{}$\geq 11.5$-$11.6$. 
-    This question will be addressed more carefully using the overlap region between 
-    HSC and the \texttt{S82-MGC} in Section \ref{ssec:s82}.
-
-%% ------------------------------------------------------------------------------------ %%  
-\subsection{The \redm{}{} cluster catalog}
-    \label{ssec:redmapper}
-
-    Our study focuses on galaxies located at the center of their dark matter halos. 
-    To limit our sample to central galaxies, we use \texttt{v5.10} of the \redm{}{} 
-    cluster catalog\footnote{See: http://risa.stanford.edu/redmapper/} 
-    (e.g.\ \citealt{Rykoff2014}; \citealt{Rozo2015b}). 
-    These authors have developed a well-tested red-sequence cluster finder that has 
-    been run on SDSS DR8 (\citealt{SDSSDR8}) photometric data. 
-    For each cluster, the catalog provides a photometric redshift ($z_{\lambda}$), a 
-    cluster richness ($\lambda$), and identifies the most likely central galaxy (the 
-    galaxy with the highest $P_{\mathrm{Cen}}$ value). 
-    The \redm{}{} catalog also provides a list of member galaxies for each cluster and 
-    their associated membership probabilities. 
-    Details about the performance of the \redm{}~cluster catalog can be found in 
-    \citet{Rozo2014}, \citet{Rozo2015a}, and \citet{Rozo2015b}. 
-    Several studies have published calibrations between the \redm{}~richness estimate, 
-    $\lambda$, and halo mass (e.g.\ \citealt{Saro2015, Farahi2016, Simet2016, 
-    Melchior2016}). 
-    All these studies consistently find that \redm{} clusters with $\lambda > 20$ 
-    have $\log (M_{\mathrm{halo}}/M_{\odot}) \geq 14.0$. 
-    The \redm{} catalog therefore helps us group massive central galaxies into 
-    samples with different average \mhalo{}. 
-    We will use the central galaxies of \redm{} clusters 
-    ($P_{\mathrm{CEN}} \geq 0.7$) to form a sample of massive central galaxies that 
-    live in massive halos.
-
-    Due to the depth and resolution of SDSS, the \redm{} catalog becomes slightly 
-    incomplete at lower richness ($\lambda < 40$) at $z > 0.33$. 
-    To ensure a clean separation in \mhalo{}, here we only focus on the central 
-    galaxies of clusters with $\lambda > 30$. 
-    According to \citet{Simet2016}, this $\lambda \geq 30$ sample should correspond to 
-    $M_{\mathrm{halo}}>10^{14.2} M_{\odot}$. 
-    We have checked that none of the results in this work depend on the choice of this 
-    $\lambda$ limit. 
-    For massive central galaxies that are not in these cluster-level halos, 
-    we unfortunately can not estimate their \mhalo{} individually, but it is safe 
-    to assume they will have $\log (M_{\mathrm{halo}}/M_{\odot}) < 14.0$.  
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %% 
-  \begin{figure*}
-      \centering 
-      \includegraphics[width=\textwidth]{fig/redbcg_smf_new}
-      \caption{
-          \textbf{Left:} Difference between \mcmodel{} and \mtot{} for central
-      	  galaxies in halos less massive than $10^{14} M_{\odot}$ (grey dots) and 
-      	  in halos more massive than $10^{14} M_{\odot}$ (red squares). 
-          On average, \mcmodel{} underestimates the total stellar mass of massive 
-          galaxies by 0.1 dex while in some cases, the difference can exceed 0.2 dex.
-          Vertical histograms indicate the mass difference for galaxies with
-          $11.6<$\logmtot{}$<11.9$. 
-          \textbf{Right:}: Impact of using \mcmodel{} on the galaxy stellar mass
-          function. 
-          Dashed lines correspond to the SMF computed using \mcmodel{} as an estimate
-          of the total luminosity whereas solid lines correspond to the SMF computed
-          using the total luminosity from our 1-D profile. 
-          The impact on the SMF can exceed 0.2 dex for massive central galaxies 
-          living in halos larger than $\log (M_{\mathrm{halo}}/M_{\odot}) > 14.2$ 
-          (red lines).
-          }
-      \label{fig:smf1}
-  \end{figure*}
-
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %% 
-\subsection{Massive Central Galaxies in Low and High Mass Halos}
-    \label{ssec:mass_central}
-
-    Based on recent constraints of $M_{\star}$-$M_{\mathrm{Halo}}$ relation 
-    (e.g.\ \citealt{Leauthaud2012}, \citealt{Behroozi2013}, \citealt{Kravtsov2014}), 
-    even though our sample selects very massive galaxies (\logms{}$\geq 11.5$), they 
-    live in a fairly broad range of halos masses.
-    With the help of the \redm{} catalog, we can broadly separate our sample into two
-    groups with \logmh{}$<14.0$ and \logmh{}$>14.2$.
-
-    % We match this sample with the central galaxies of \redm{}~catalogs using a 
-    % $1.0^{\arcsec}$ radius, and it results in 704 galaxies.  
-    %% Saved as "dr1_redbcg_hsc_sdss_gama_1arcsec.fits"
-
-    We match the \texttt{hscZ} sample with the central galaxies of \redm{} clusters 
-    with $\lambda \geq 30$ and $P_{\mathrm{0.7}} \geq 0.7$, and find 164 matched 
-    galaxies at $0.3 \leq z \leq 0.5$.
-    Our sample of \textbf{central galaxies in more massive halos} will be referred to 
-    as the \rbcg{} sample. 
-    The median $\lambda$ of the clusters associated with the \rbcg{} sample is 
-    ${\sim} 41$, corresponding to halo mass of 
-    $M_{\mathrm{halo}}{\sim} 2.2\times 10^{14}$ $h^{-1}$ $M_{\odot}$.
-    Only 44 centrals from the \rbcg{} sample live in clusters with $\lambda \geq 50$
-    ($M_{\mathrm{halo}} {\sim} 3.0\times 10^{14}$ $h^{-1} M_{\odot}$). 
-    Our \rbcg{} sample therefore corresponds to galaxies in moderate mass halos.
-    %% Saved as "dr1_redbcg_use_sed5b.fits"
-
-    Out next goal is to construct a sample of central galaxies living in halos with 
-    \logmh{}$<14.0$. 
-    We first identify and remove all galaxies within a cylindrical region around all 
-    \redm{} clusters. 
-    We use a radius equal to $R_{\mathrm{200b}}$ and the thickness of the cylinder is 
-    set to twice the uncertainty of the photometric redshift error. 
-    We convert $\lambda$ to $M_{\mathrm{halo}}$ using the calibration of 
-    \citet{Simet2016} and we use the mass-concentration relation from 
-    \citet{Diemer2015} to compute $R_{\mathrm{200b}}$. At $0.3 < z < 0.5$, the 
-    uncertainty of photo-$z$ is between 0.015 to 0.025, and is enough to exclude 
-    cluster members.
-    After removing galaxies associated with \redm{} clusters, the remaining galaxies 
-    in our sample will be dominated by central galaxies living in halos with 
-    \logmh{}$\leq 14.0$. 
-    We will refer to this sample of \textbf{central galaxies in less massive halos}
-    as the \nbcg{} sample.
-
-    We note that at this stage, our \nbcg{} sample still contains galaxies with a 
-    wide range of \mstar{} values. 
-    Later on, once we have more accurate \mstar{} estimates, we will further limit this 
-    sample to \logms{}$ > 11.5$. 
-    At this very high mass end, and given that we have rejected satellites in \redm{} 
-    clusters, any further satellite contamination can be safely neglected 
-    (e.g. \citealt{Reid2014, Hoshino2015, Saito2016, vanUitert2016}).
-    %% Saved as "dr1_nonbcg_use_sed5b.fits"
-    % TODO: The actual number waits to be updated}
-
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %% 
-\subsection{Summary of Sample Construction}
-    \label{ssec:sample}
-
-    Using ${\sim} 100$ deg$^2$ of HSC data, we select a large sample of massive central 
-    galaxies with reliable redshift information, and broadly separate them two 
-    categories based on $M_{\mathrm{halo}}$.
-
-    The following is a summary of our sample construction.
-
-    \begin{itemize}
-        \item \texttt{hscPho} sample: this parent sample consists of bright galaxies 
-            with $i_{\mathrm{cModel}} \leq 21.0$, good quality imaging, and reliable 
-            \texttt{cModel} photometry in all five HSC bands in the \texttt{S15B} 
-            data release. 
-        \item \texttt{hscZ} sample: we limit the \texttt{hscPho} sample to galaxies 
-            with reliable redshift information. 
-        \item \rbcg{} sample: we select a sample of 164 galaxies at 
-            $0.3 \leq z \leq 0.5$ that are the central galaxies 
-            in $\lambda > 30$ \redm{} clusters. 
-            They represent the central galaxies in very massive halos 
-            (\logmh{}$\geq 14.2$). 
-        \item \nbcg{} sample: after excluding all cluster members from the 
-            \texttt{hscZ} sample, we have 14661 bright galaxies at 
-            $0.3 \leq z \leq 0.5$. 
-            After applying an additional \mstar{} cut (see Section 
-            \ref{ssec:isedfit}), this sample corresponds to central galaxies in 
-            halos with \logmh{}$<14.0$.  
-    \end{itemize}
-
-    We now proceed to measure the luminosities and stellar mass profiles for 
-    all galaxies in the \rbcg{} and \nbcg{} samples.
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %% 
-\section{Measurements of 1-D Surface Brightness Profiles}
-    \label{sec:ellipse}
-
-    Massive ETGs imaged at the depth of HSC are not well modeled by simple models such 
-    as the de~Vaucouleurs model or a single \ser component model. 
-    These models will fail to simultaneously capture the profile in both the inner and 
-    the outer region and these models also cannot account for any radial variations in 
-    ellipticity and position angle. 
-    In principle, massive galaxies can still be described by more complex 
-    models (e.g \citealt{Huang2013a, Huang2013b, Oh2017}), but they are still 
-    sensitive to the choices of models (e.g. de~Vaucouleurs or \ser{} profile), 
-    the number of components, initial guesses of parameters, and the internal 
-    degeneracies among different parameters. 
-    Background subtraction uncertainty can affect the 2-D model fitting dramatically, 
-    especially for massive ETGs in our sample. 
-    We therefore perform elliptical isophote fitting using the IRAF \texttt{Ellipse} 
-    algorithm (Jedrzejewski 1987) to estimate the total luminosities of massive 
-    galaxies and measure their one-dimensional profiles of stellar mass surface 
-    density (\mden{}). 
-    This 1-D method we adopt is less affected by the issues mentioned above. 
-    Also, we will only study galaxies in the radial range where we are not sensitive 
-    to either the PSF ($r<3-5$ kpc) or the background subtraction ($r>100$ kpc).
-
-    We prepare large $i$-band cut-outs for each galaxy that extend to 750 kpc in 
-    radius, along with a bad pixel mask, and the PSF model. 
-    These cut-outs include all of the light of the galaxy and are large enough to 
-    also evaluate the background level. 
-    We choose to use $i$-band images because they trace the stellar distributions of 
-    massive galaxies at $0.3 \leq z \leq 0.5$ reasonably well 
-    (the observed i-band corresponds to a rest-frame $g$ or $r$ band), but also 
-    because they have better seeing and much lower background levels than the $z$ 
-    and Y band images (although these in principle may be better tracers of \mden{}).
-
-    For each cut-out, to overcome the \texttt{hscPipe} ``over-deblending'' issue, we 
-    use a customized procedure to detect and appropriately mask out neighbouring 
-    objects. 
-    Furthermore, \texttt{hscPipe} tends to over-subtract the background around 
-    bright objects. 
-    To correct for this over-subtraction, we first aggressively mask all objects 
-    (including the central massive galaxy), and derive an empirical background 
-    correction using \texttt{SExtractor}.
-    Then, we run \texttt{Ellipse} on the background-corrected, masked cut-outs 
-    following the methodology of \citet{Li2012}. 
-    In short, we first fit each isophote using a free centroid and shape 
-    (ellipticity and position angle). 
-    We then fix the centroid (using the mean flux-weighted centroid) and estimate
-    the mean ellipticity and position angles of all isophotes. 
-    Finally, we extract a 1-D surface brightness profile along the major axis using 
-    the mean ellipticity and position angle. 
-    We correct these surface brightness profiles for Galactic extinction and 
-    cosmological dimming, and integrate them to various radii to get the luminosity 
-    within different physical (elliptical) apertures. 
-    Fig~\ref{fig:ellipse} shows an example of the 1-D surface brightness and 
-    ellipticity profile for a massive galaxy at $z{\sim}0.2$ and also highlights 
-    a few isophotes.
-
-    We test our procedure using different mask sizes, different \texttt{Ellipse} 
-    parameters, and with or without our background correction. 
-    Based on these tests, we find that our 1-D surface brightness profiles are reliable 
-    up to surfaces brightness levels of $>28.5$ \sb. 
-    Beyond that, some of our profiles shows signs of truncation and/or large 
-    fluctuations which are due to the uncertainty in the background subtraction. 
-    We choose to limit our study to surface brightness levels up to ${\sim} 28.5$ \sb. 
-    This is a conservative choice but already enables us to measure light profiles 
-    out to $100$ kpc on a galaxy-by-galaxy basis (no stacking). 
-    For more details about the technical details of how we use \texttt{Ellipse}, 
-    please see Appendix~\ref{app:ellipse}.
-
-    For physical (e.g.\ late-stage major merger) and unphysical (e.g.\ nearby foreground 
-    galaxy or bright star) reasons, we can not extract reliable 1-D profiles for a small 
-    fraction of massive galaxies because they are heavily masked out. 
-    This is an intrinsic limitation of the 1-D method. 
-    It affects $18/164$ of the \rbcg{} sample, and a smaller fraction of the 
-    \nbcg{} sample. 
-    It is worth noting that this excludes most major-merging massive galaxies. 
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %% 
-\section{Stellar Masses and Stellar Mass Density Profiles}
-    \label{sec:mstar}
-
-%% ------------------------------------------------------------------------------------ %% 
-\subsection{Stellar Masses from SED Fitting}
-    \label{ssec:isedfit}
-
-    To convert luminosities into stellar mass, we assume that these massive galaxies 
-    can be well described by an average \m2l{}. 
-    This is a reasonable assumption considering that they are mostly dominated by 
-    old stellar populations and are known to have shallow color gradients. 
-    We will further justify this point by measuring their median color profiles in 
-    Section \ref{ssec:ell_color}.
-
-    We use the broadband Spectral Energy Distributions (SEDs) fitting 
-    (see \citealt{Walcher2011} for a recent review) code 
-    \texttt{iSEDFit}\footnote{http://www.sos.siena.edu/~jmoustakas/isedfit/} 
-    (\citealt{Moustakas13}) to estimate the average \m2l{} and $k$-corrections using
-    5-band HSC \cmodel{} fluxes.
-    Although \cmodel{} tends to underestimate the total flux for bright, extended 
-    objects, it can still yield accurate \emph{average} colors thanks to the 
-    forced-photometry method that takes the PSF convolution into account
-    (e.g. \citealt{SynPipeInPrep}).
-
-    \texttt{iSEDFit} takes a simplified Bayesian approach. 
-    In short, it first generates a large grid of SEDs from synthetic stellar population 
-    models by drawing randomly from the prior distributions of relevant parameters 
-    (e.g. age, metallicity, dust extinction, and star formation history).
-    Based on these models, it uses the observed photometry and redshift to compute the 
-    statistical likelihood, and generates the posterior probability distribution 
-    functions (PDF) for each parameter.  
-    To get the best estimate of a given parameter, \texttt{iSEDFit} integrates the 
-    full PDF over all the other nuisance parameters.
-    Then, the median value and the 1-$\sigma$ uncertainty are derived based on the 
-    marginalized PDF. 
-    Please refer to \citet{Moustakas13} for technical details.
-
-    In this work, we derive average \m2l{} using the Flexible Stellar Population 
-    Synthesis\footnote{http://scholar.harvard.edu/cconroy/sps-models}
-    (FSPS; \texttt{v2.4}; \citealt{FSPS}, \citealt{Conroy2010}) model based on the MILES
-    \footnote{http://www.iac.es/proyecto/miles/pages/stellar-libraries/miles-library.php}
-    (\citealt{MILES1}, \citealt{MILES2}) stellar library and assuming a
-    \citet{Chabrier2003} IMF between 0.1 to 100 \msun. 
-    The star formation history (SFH) is assumed to follow a delayed-$\tau$ model with 
-    stochastic star bursts (see Appendix~\ref{app:sed}). 
-    This SFH is appropriate for massive galaxies at low redshifts 
-    (e.g.\ \citealt{Kauffmann2003}). 
-    For stellar metallicity, we assume a flat distribution between 0.004 to 0.03 
-    (the highest value allowed by FSPS). 
-    We adopt the \citet{Calzetti2000} extinction law with a order two Gamma 
-    distribution of $A_{V}$ between 0 to 2 magnitude. 
-    A majority of our galaxies are red and quiescent and our results are 
-    not very sensitive to parameters related to the SFH or the internal dust extinction. 
-    To achieve reasonable sampling across these parameters, we generate 250000 models.
-
-    We construct five band SEDs using the forced-photometry \cmodel{} magnitudes 
-    corrected for Galactic extinction. 
-    \cmodel{} only accounts for the statistical error on the flux measurement but does
-    not account for systematic uncertainties in the model-fitting process. 
-    It therefore underestimates the flux errors of bright galaxies. 
-    Based on tests using synthetic objects, we find that the average accuracy of
-    \cmodel{} for bright galaxy is roughly at the 1\% level in the $r$, $i$, $z$ bands, 
-    and slightly worse in the $g$ and Y-band. 
-    Therefore, we supply \texttt{iSEDFit} with simplified flux errors assuming 
-    $S/N = 100$ for the $riz$ bands, and $S/N = 80$ for the $g$Y bands (on average, 
-    images in $gY$ bands are shallower in depth and/or have higher background noise).  
-    The typical uncertainty of \logms{} is around 0.08-0.10 dex at \logms${\sim} 11.5$. 
-    Please see Appendix~\ref{app:sed} for further details.
-
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %% 
-  \begin{figure*}
-      \centering 
-      \includegraphics[width=\textwidth]{fig/average_mass_profiles_fsps1_A}
-      \caption{
-          \textbf{Left}: Median \mden{} profiles in three total stellar mass bins. 
-              Here we combine the two \rbcg{} and \nbcg{} samples together -- 
-              the halo mass dependence of these profiles will be explored in subsequent 
-              figures. 
-              Thin grey lines show a random subset of individual profiles. 
-              The shaded region highlights the region that could be affected by the PSF. 
-              Two vertical lines indicate 10 kpc (thin, dotted line) and
-              100 kpc (thick, dash line). ~~~ 
-          \textbf{Right}: comparison between our \mden{} profiles, previous observations, 
-              and simulations. 
-              The solid cyan line shows the median profile of massive elliptical 
-              galaxies at $z{\sim} 0$ from \citet[][]{Huang2013a}. 
-              The red long-dashed line shows the median profile of massive galaxies at 
-              $0.25 \leq z < 0.50$ observed by \textit{HST} from \citet[][]{Patel2013}. 
-              The purple short-dashed line shows the median radial stellar distributions 
-              in massive halos from simulation using the particle tagging method
-              (\citealt{Cooper13}).}
-      \label{fig:avg_prof}
-  \end{figure*}
 %% ------------------------------------------------------------------------------------ %%
@@
 %% ------------------------------------------------------------------------------------ %% 
-    \subsection{Stellar Mass Completeness}
-    \label{ssec:complete}
-
-    With the help of the \texttt{S82-MGC} (\citealt{Bundy2015}), we investigate the 
-    \mstar{} completeness of our samples. 
-    The \texttt{S82-MGC} sample matches the deeper SDSS photometric data in the 
-    Stripe 82 region (\citealt{Annis2014}) with the near infrared data from the United 
-    Kingdom Infrared Telescope Infrared Deep Sky Survey (UKIDSS; \citealt{Lawrence2007}). 
-    The deeper photometry and better photo-$z$s make the \texttt{S82-MGC} sample complete 
-    to \logms{}$\geq 11.2$ at $z<0.7$ which makes it sufficient to evaluate the 
-    completeness of our HSC samples.
-
-    There are 20453 \texttt{S82-MGC} galaxies that are also in the \texttt{hscPho} 
-    sample at $0.3 \leq z_{\mathrm{s82}} \leq 0.5$. 
-    We compute \mstar{} values for these galaxies using our fiducial 
-    procedure\footnote{The \mstar{} using HSC photometry is in excellent with the 
-    values derived from the \texttt{S82-MGC} which includes NIR data from UKIDSS; 
-    \texttt{S82-MGC} also uses \texttt{iSEDFit} with similar assumptions.}. 
-    The right side of Fig~\ref{fig:smf1} compares the SMFs of galaxies from 
-    \texttt{S82-MGC} with the SMFs of galaxies from our two 
-    samples\footnote{Errors on the SMFs are estimated via bootstrap resampling}. 
-    Based on Fig~\ref{fig:smf1}, we conclude that our sample of massive galaxies is 
-    reasonably complete down to \logms{}${\sim} 11.6$ at $0.3 \leq z \leq 0.5$. 
+  \begin{figure*}
+      \centering 
+      \includegraphics[width=\textwidth]{fig/redbcg_scaling_relation}
+      \caption{
+          \textbf{Left}: The mass-size relations for \rbcg{} (orange squares) and 
+          \nbcg{} (grey dots) galaxies. 
+          Two vertical lines highlight our $11.6<$ \logms{} $<11.9$ mass bin. 
+          The red solid line shows the best fit mass-size relation for \rbcg{} and the 
+          grey dashed line shows the best fit relation for \nbcg{}. 
+          Shaded regions in lighter colors show the 1-$\sigma$ uncertainties
+          from MCMC sampling.  
+          The green dashed line shows the mass-size relation for nearby central 
+          galaxies in massive groups from \citet{HCompany13}. 
+          \textbf{Right:} The relations between \mtot{} and \minn{} for the 
+          \rbcg{} and \nbcg{} galaxies, along with the best-fit scaling relations for 
+          both samples.
+          }
+      \label{fig:scaling_relation} 
+  \end{figure*}
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
+\section{Data And Sample Selection}
+    \label{sec:data}
+
+    \song{Need a much shorter version of this}
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
+\section{Results}
+    \label{sec:results}
+
+    %\footnote{There are different observational definitions of ``environment''. 
+    %In this paper, we use the term ``environment'' and halo mass interchangeably}.
+
+    %Previous work has shown that the half-light radii of massive ETGs is tightly 
+    %correlated with \mstar{} (e.g. \citealt{Shen2003, Guo2009}). 
+    %Models based on the ``two-phase'' formation scenario naturally predict that this 
+    %mass--size relation should exhibit an environmental dependence: the effective radii 
+    %of massive ETGs in more massive halos should be larger than those in less massive
+    %halos at fixed \mstar{} (e.g. \citealt{Shankar2013, Shankar2014}).
+
+    %However, while hints of an environmental dependence in the mass-size relation have 
+    %been spotted at high-$z$ (e.g. \citealt{Papovich2012, Lani2013, Delaye2014}; but 
+    %also see \citealt{Rettura2010}), there is no solid evidence for this effect at 
+    %low-$z$ (e.g. \citealt{Nair2010, HCompany13}; but also see \citealt{Yoon2017}). 
+    %The absence of an environmental dependence in the mass-size relation is an 
+    %outstanding challenge to the two-phase formation scenario of ETGs.
+
+    \song{These paragraphs are from Jenny's txt file, need organization.}
+    Massive central galaxies in this work show an intriguing diversity on the plane 
+    defined by these two metrics.  
+    We preview this using Fig~\ref{fig:m100_m10_color}, which shows a subsample of 
+    massive galaxies at $z{\sim} 0.4$ that share very similar value of \minn{}, but 
+    exhibit a large diversity in their outer profiles. 
+    Assuming that galaxies at fixed \minn{} share a similar in-situ formation history, 
+    it is of great interest to investigate the relation between their present day halo 
+    mass and the extend of their outer envelopes. 
+    We note that although a circular aperture is shown on Fig~\ref{fig:m100_m10_color}, 
+    for our mass measurements, we always use elliptical apertures that follow the 
+    average isophotal shape. Finally, given our narrow mass and redshift range, we 
+    can safely ignore significant mass growth and structural evolution in this work
+    (no star formation, lower merger rate \etal~e.g.\ \citealt{Bellstedt2016},
+    \citealt{Inagaki2015}; but also see \citealt{Bai2014}).
+
+    \textbf{Completeness that depends on halo mass:}
+
     The \rbcg{} sample is less affected by completeness because we can utilize 
@@
 
-    In this work, we will focus on the range $11.6 \le$ \logmtot{}$ \le 11.9$ 
-    where our two samples are complete. 
     When comparing \nbcg{} and \rbcg{} we will also always make sure that the two 
@@
     Please see the next section and Appendix~\ref{app:match} for more details.
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %% 
-\subsection{Stellar Mass Corrected for Total Luminosity}
-    \label{ssec:mtotal}
-
-    Using the best-fit stellar mass from \texttt{iSEDFit} (noted as as \mcmodel{}), 
-    we estimate the average \m2l{} in the $i$-band, then use that \m2l{} to convert our 
-    1-D luminosity density profiles into stellar mass density profiles. 
-    We also convert our 10 and 100 kpc aperture luminosities into corresponding stellar 
-    mass estimates (noted as \minn{} and \mtot{}).
-
-    For the remainder of this paper, we will use \mtot{} as a proxy of ``total'' 
-    stellar mass. 
-    In Appendix~\ref{app:sedasic}, we briefly summarize the basic statistics of 
-    the \rbcg{} and \nbcg{} samples using our estimates of \mtot{} and \minn{}.
-    We confirm that both samples follow a similar and very tight ``red-sequence''. 
-    Appendix~\ref{app:sed} describes the outputs from our SED fitting process 
-    (average stellar age, metallicity, and internal dust extinction). 
-    We do not utilize these quantities in this paper, but we have checked that they all 
-    behave reasonably for both samples. 
-    As expected, the integration of the 1-D profile out to very large radius recovers 
-    more luminosity (stellar mass) compared to the \cmodel{}-based estimates. 
-    This will be shown in Section \ref{ssec:s82}.
-
-    Our methodology ignores any radial variations in \m2l{}. 
-    It is well known that massive ETGs have negative optical color gradients indicating 
-    gradients in \m2l{} (e.g.\ \citealt{LaBarbera2012}; 
-    \citealt{DSouza2015}). 
-    These color gradients are shallow and smooth out to a few times of the effective 
-    radius and color gradients at the outskirts are not yet well quantified. 
-    More importantly, for the comparison between the \rbcg{} and \nbcg{} samples, 
-    our results will be robust as long as there is \emph{no significant difference in 
-    the average color gradient between the two samples}. 
-    We have confirmed that this is indeed the case and this will be discussed in 
-    Section~\ref{ssec:ell_color}.
-
-    Our method for deriving total stellar masses is similar to the 
-    method adopted by the GAMA survey (\citealt{Taylor2011, Kelvin2012}). 
-    We have compared our \mstar{} values with those from GAMA and the results are given 
-    in Appendix~\ref{app:gama}. 
-    We find a systematic differences between the two \mstar{} estimates.
-    It is likely that the GAMA models fail to capture the flux associated with the 
-    outskirts of galaxies due to the limited depth of SDSS.     
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %% 
-\section{Results}
-    \label{sec:result}
-
-%% ------------------------------------------------------------------------------------ %%     
-    \subsection{Impact of Missing Light on the Galaxy Stellar Mass Function}
-    \label{ssec:s82}
-
-    Different methods for estimating the ``total'' \mstar{} can have a large impact on 
-    the high mass end of the galaxy stellar mass function (e.g. \citealt{Bernardi2013, 
-    DSouza2014, DSouza2015, Bernardi2016a}). 
-    Fig~\ref{fig:smf1} shows the SMF computed using both \mtot{} and \mcmodel{}. 
-    As one can be seen from this figure, our careful 1-D approach recovers more flux 
-    in massive galaxies than \texttt{cModel}. 
-    More importantly, the average difference steadily increases with \mtot{} and also 
-    has a dependence on \mhalo{}. 
-    At \logms{} $>11.5$, the difference can be larger than 0.2 dex. 
-    This difference relates to the intrinsic limitation of the \texttt{cModel} method 
-    and also reflects the fact that more massive ETGs tend to have more extended 
-    stellar mass distributions (e.g. \citealt{Graham2003}). 
-    Generally speaking, the use of \mtot{} instead of the \mcmodel{} shifts the SMF 
-    towards the higher-mass end and slightly modifies the high-mass slope. 
-    The impact of missing flux is most prominent for the \rbcg{} sample.
-    For studies about the SMF or other aspects of galaxy evolution based on 
-    \cmodel{}-like photometry or shallower images, these effects can not be neglected.
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %%
-\subsection{Surface Mass Density Profiles}
-    \label{ssec:sbp_compare}
-
-%% ------------------------------------------------------------------------------------ %%
-\subsubsection{General Trends and Comparison with Previous Work}
-    \label{sssec:sbp_inter}
-
-    Compared to the much discussed ``mass-size'' relation, the \mden{} profiles that 
-    we have derived capture the full information about the structural properties of 
-    massive galaxies. 
-    We argue that by studying the shapes of these galaxy profiles directly, we can 
-    by-pass outstanding questions about how to accurately define and measure the 
-    ``sizes'' and ``masses'' of these massive galaxies. 
-    Fig~\ref{fig:avg_prof} shows the median \mden{} profiles\footnote{The median 
-    profiles along with their uncertainties are derived using bootstrap resampling 
-    method} of massive central galaxies at $0.3 < z < 0.5$ in three \mtot{} 
-    bins\footnote{The sample is clearly not complete in the lowest \mtot{} bin, 
-    but its median \mden{} profile is still useful to show the overall trend and to 
-    compare with previous work}. 
-    As shown in the left panel of Fig~\ref{fig:avg_prof}, we can comfortably trace
-    the \mden{} profiles of these massive galaxies out to 100 kpc 
-    \textbf{individually}. 
-    These median \mden{} profiles have moderate differences in the inner region, 
-    but show significant differences in the outskirts with more massive galaxies 
-    showing more prominent stellar envelopes. 
-    Most of these massive galaxies ($\ge 10^{11.4} M_{\odot}$) are slowly-rotating 
-    (e.g.\ \citealt{Cappellari13b}) giant ellipticals with ``boxy'' inner isophotal 
-    shapes (e.g.\ \citealt{Kormendy2009}), and slightly flattened inner \mden{} 
-    profiles (e.g.\ \citealt{Lauer07}). 
-    But in the outskirts, the structure of these galaxies is 
-    \emph{clearly not self-similar}. 
-    Some of our \mden{} profiles show signs of unphysical truncation and fluctuation 
-    related to inaccurate sky subtraction. 
-    In this paper, we do not use profiles beyond 100 kpc, even though the median 
-    \mden{} profiles for the two most massive bins behave reasonably out to 
-    ${\sim} 200$ kpc.
-
-    Fig~\ref{fig:avg_prof} compares our results with previous work. 
-    Most previous studies have relied on stacking techniques to measure surface 
-    brightness profiles out to large radii.
-    So far, the surface brightness profiles of massive galaxies out to such large 
-    radii was mostly derived via image stacking technique that suffers from several 
-    systematic issues (e.g. \citealt{Tal2011, DSouza2015}; but also see:
-    \citealt{Capaccioli2015}); and the \mden{} profiles are even more rarely 
-    available.
-
-    \citet{Huang2013a} derived \mden{} profiles for a small sample of very nearby 
-    ellipticals (within 100 Mpc; median \logms{} ${\sim} 11.3$ based on shallower 
-    images) from the Carnegie-Irvine Galaxy Survey (CGS, \citealt{CGS1}). 
-    Because this is a very low redshift sample, these profiles are robust to $r=1$ kpc. 
-    The \citet{Huang2013a} profiles show good agreement with ours in the region of 
-    overlap and out to 50 kpc. 
-    CGS images are deeper than SDSS images in the $r$-band, but the median 
-    profile from \citet{Huang2013a} still only reaches ${\sim} 50$ kpc for $z{\sim} 0$ 
-    massive galaxies.
-    Meanwhile, our deep HSC images can reliably deliver individual \mden{} profiles 
-    for $z{\sim} 0.4$ galaxies out to at least 100 kpc.
-
-    \citet{Patel2013} extracted a median \mden{} profile of massive ETGs at 
-    $0.25 < z < 0.50$ using stacked \textit{HST}/ACS images. 
-    These galaxies are selected at a constant cumulative number density and are 
-    thought to be the progenitors of $z=0$ massive ETGs (e.g. \citealt{Leja2013}).  
-    The median \mstar{} of the \citet{Patel2013} sample is ${\sim} 10^{11.2} M_{\odot}$ 
-    which is lower than our lowest mass bin. 
-    However, \citep{Patel2013} use the BC03 SSP model which are roughly 0.1 dex 
-    lower than our FSPS masses (Appendix~\ref{app:sed}). 
-    Furthermore, the \citep{Patel2013} images are shallower than ours meaning 
-    that there masses will be lower than ours because of missing light in the 
-    outskirts. 
-    Given these two considerations, it is reasonable to roughly compare the 
-    \citet{Patel2013} profile with the one in our lowest stellar mass bin. 
-    The superb resolution of the \textit{HST}/ACS image means that the profile in
-    \citet{Patel2013} is unaffected by the seeing even down to 1 kpc. 
-    The good agreement between our profile and the one derived from HST image 
-    shows that our profiles are robust at $r > 3$ kpc and that we can accurately 
-    measure \minn{}.
-
-    Finally, we also compare with the predicted median \mden{} profile of central 
-    galaxies in massive halos ($13.5 < \log M_{200,c} < 14.0$) from cosmological 
-    simulation where the \mden{} profiles of galaxies are calculated using the 
-    particle-tagging technique (e.g. \citealt{Cooper10}).
-
-    The simulated \mden{} profile is also affected by limited resolution in the 
-    center, but it is already quite similar to the median \mden{} profile for 
-    the $11.6 <$ \logmtot{} $< 11.8$ bin within 40 kpc. 
-    However, compared with our data, this simulation predicts stellar envelope that
-    are too prominent at this halo mass. 
-    This types of comparisons between our HSC data and predictions from simulations 
-    will help to fine-tune simulations and to also investigate the main physical 
-    mechanisms that drive the assembly of massive galaxies and the build up of 
-    stellar envelopes.
-
-    Table~1 provides tabulated values for the median profiles that are 
-    displayed in Fig~\ref{fig:avg_prof}. 
-    These profiles are also available  
-    \href{https://github.com/dr-guangtou/hsc_redbcg/tree/master/profiles}{here}:
-    {\url{https://github.com/dr_guangtou/hsc_redbcg/tree/master/profiles/}}.
-
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %% 
-\subsubsection{Environmental Dependence of the Profiles of Massive Galaxies}
-    \label{sssec:sbp_mtot}
+
+%% ------------------------------------------------------------------------------------ %% 
+\subsection{Environmental Dependence of the Profiles of Massive Galaxies}
+    \label{ssec:sbp_mtot}
 
@@
 %% ------------------------------------------------------------------------------------ %% 
-\subsection{Ellipticity and Color Profiles}
-    \label{ssec:ell_color}
-
-%% ------------------------------------------------------------------------------------ %% 
-  \begin{figure*}
-      \centering 
-      \includegraphics[width=\textwidth]{fig/redbcg_discussion_2}
-      \caption{
-          Radial variations in ellipticity and optical colors for massive galaxies. 
-          The format of this figure is similar to the right hand side of 
-          Fig~\ref{fig:prof_1}. 
-          Top panels show the ellipticity profile, middle panels show $g-r$, and lower 
-          panels show $g-i$. 
-          We compare our results with those from \citet{Tal2011} based on stacking 
-          large samples of luminous red galaxies in SDSS at $z{\sim} 0.4$ 
-          (solid blue line on top panel). 
-          We also compare with the results from a stacking analysis of nearby massive 
-          galaxies with high concentration index ($C>2.6$) in 
-          \citet[][blue dash lines on the top and middle panels]{DSouza2014}. 
-          Finally, we also compare with the average $g-r$ and $g-i$ color profiles 
-          from a large sample of nearby elliptical galaxies in \citet[][blue, solid 
-          lines on the middle and bottom panels]{LaBarbera2010}.
-          }
-      \label{fig:ell_color}
-  \end{figure*}
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %% 
-    We now study how the ellipticities (computed via \texttt{Ellipse}) and $k$-corrected 
-    optical colors of massive galaxies vary with radius. 
-    We also study whether or these radial trends differ between our various samples. 
-    These quantities contain interesting information about the physical processes that 
-    shape galaxies, but here we study them mainly with two goals in mind:
-
-    \begin{enumerate}
-
-        \item To see whether the ellipticity profile depends strongly on environment, 
-            and to see whether or not the fact that we use an using average isophotal 
-            shape for our our 1-D \mden{} profiles has any impact on our results.
-
-        \item To verify that the average color gradient does not depend strongly on 
-            the environment and that is not steep enough to cause a problem with our 
-            choice the assumption that it is reasonable to use average \m2l for 
-            comparing massive galaxies. 
-            We extract color profiles by applying the isophotes in $i$-band to images 
-            in other bands in ``forced photometry'' manner.
-
-    \end{enumerate}
-
-    We compute ellipticities and color profiles in the radial range of 5-50 kpc 
-    (this is the range where we can safely ignore differences in sky subtraction and 
-    seeing across different bands). 
-    We apply Galactic extinction and $k$-correction to both $g-r$ and $g-i$ color 
-    profiles; the $k$-correction values are also from \texttt{iSEDFit} results.
-    We show the average ellipticity, $g-r$, and $g-i$ color profiles for the 
-    \mtot{}-matched (\minn{}-matched) samples of \rbcg{} and \nbcg{} galaxies on the 
-    left (right) side of \ref{fig:ell_color}. 
-    We also compare our results with previous work based on stacking SDSS galaxies 
-    (e.g. \citealt{LaBarbera2010, Tal2011, DSouza2014}).
-
-    We find that in general, the ellipticities of massive galaxies increases with 
-    radius from $e\le 0.2$ around 5-10 kpc to $e{\sim} 0.3$ at 40-50 kpc. 
-    This is consistent with previous 2-D modeling results from \citet{Huang2013a}. 
-    The ellipticity profiles of the \mtot{}-matched samples are very similar at 
-    $r<50$ kpc (2-3$\times R_{\mathrm{e}}$ for their \mstar{}). 
-    However, for the \minn{}-matched samples, the \rbcg{} galaxies have higher 
-    ellipticity than the \nbcg{} ones at $r > 10$ kpc, while their inner ellipticity 
-    profiles are very similar.  
-    This further hints that massive central galaxies in different halos but with 
-    similar ``in-situ'' mass may experience different late-time merging histories. 
-    Overall, the relative low ellipticity value and the fact that the ellipticity 
-    gradients are shallow lead us to conclude that the use of an average 
-    isophotal ellipticity is fine for this present study.
-
-    Previous attempts to constrain ellipticity gradients have relied on image 
-    stacking techniques (e.g. \citealt{Tal2011}, \citealt{DSouza2015}). 
-    Compared to our measurements, we find that stacked ellipticity profiles tend to 
-    underestimate the ellipticity in the outskirt. 
-    Ellipticity profiles contain additional information about the assembly histories 
-    and in future work, it would be of interest to compare our ellipticity profiles 
-    with predictions from hydrodynamic simulations such as Illustris 
-    (\citealt{Vogelsberger2014}, \citealt{Genel2014}) or \textit{Horizon-AGN} 
-    (\citealt{Dubois2014}).
-
-    In terms of color gradients, we find shallow and negative gradients of median 
-    $g-r$ and $g-i$ color profiles for both \rbcg{} and \nbcg{} galaxies. 
-    For both \mtot{}- and \minn{}-matched samples, we find no significant difference
-    in their median color profiles, which supports the assumption of using single 
-    average \m2l{} value to estimate \mden{} profiles.
-    The median $g-r$ color profiles are quite consistent with those based on 
-    stacked SDSS images. 
-    For the $g-i$ profiles, the HSC ones show steeper gradients than the SDSS ones, 
-    however, it is important to point out that the SDSS $i$-band suffers from the 
-    so-called ``red-halo'' effect of (e.g. \citealt{Wu2005}, \citealt{Tal2011}) that 
-    could make the SDSS color appears redder. 
-    In contrast, HSC $i$-band image do not suffer from this effect (thanks to thick 
-    CCDs), therefore can help provide more accurate color estimates.
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %% 
 \subsection{The Environmental Dependence of Scaling Relations}
     \label{ssec:scaling}
-
-%% ------------------------------------------------------------------------------------ %% 
-  \begin{figure*}
-      \centering 
-      \includegraphics[width=\textwidth]{fig/redbcg_scaling_relation}
-      \caption{
-          \textbf{Left}: The mass-size relations for \rbcg{} (orange squares) and 
-          \nbcg{} (grey dots) galaxies. 
-          Two vertical lines highlight our $11.6<$ \logms{} $<11.9$ mass bin. 
-          The red solid line shows the best fit mass-size relation for \rbcg{} and the 
-          grey dashed line shows the best fit relation for \nbcg{}. 
-          Shaded regions in lighter colors show the 1-$\sigma$ uncertainties
-          from MCMC sampling.  
-          The green dashed line shows the mass-size relation for nearby central 
-          galaxies in massive groups from \citet{HCompany13}. 
-          \textbf{Right:} The relations between \mtot{} and \minn{} for the 
-          \rbcg{} and \nbcg{} galaxies, along with the best-fit scaling relations for 
-          both samples.
-          }
-      \label{fig:scaling_relation} 
-  \end{figure*}
-%% ------------------------------------------------------------------------------------ %%
 
@@
 
-%% ------------------------------------------------------------------------------------ %% 
-  \begin{figure}
-      \centering 
-      \includegraphics[width=\columnwidth]{fig/redbcg_discussion_1}
-      \caption{Comparison of the median \mden{} profiles of massive galaxies in the 
-          two lower \mtot{} bins from Fig~\ref{fig:avg_prof} with other observations 
-          and simulations, focusing on the inner region. 
-          The format is similar with the right panel of Fig~\ref{fig:avg_prof}.
-          We include: 
-          1) the median \mden{} profile of inner component from structure 
-          decomposition of massive elliptical galaxies at $z{\sim} 0$ from 
-          \citet[][Cyan, solid]{Huang2013a}; 
-          2) the median \mden{} profile of massive galaxies at $1.0 < z < 1.5$ 
-          from \textit{HST} observations in \citet[][Red, dashed]{Patel2013}; 
-          3) the median \mden{} profile of the ``in-situ'' stellar components in 
-          simulated massive halos from \citet[][Purple, dot-dashed]{Cooper13};
-          4) the \mden{} profile of the very massive cD galaxy at $z{\sim} 1.1$ 
-          discovered by \citet[][Yellow, dashed]{Liu2013} in the Hubble 
-          Ultra-Deep Field.}
-      \label{fig:discussion_1}
-  \end{figure}
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %% 
-\section{Discussion}
-    \label{sec:discussion}
-
-    By using deep imaging from the HSC survey we have shown that the stellar mass 
-    density profiles of massive central galaxies depend systematically on the mass 
-    of their host dark matter halos. 
-    Here we discuss the physical origin, scientific implications, and potential 
-    caveats of this result.
-
-%% ------------------------------------------------------------------------------------ %%
-
-\subsection{The ``Two phase'' Formation Scenario of Massive Galaxies and the 
-            Build-Up of Outer Envelopes}
-
-    Our results are consistent with the picture that massive central galaxies form via 
-    a ``two-phase'' scenario. 
-    According to this theory, the cores of massive galaxies were formed at $z{\sim} 2$ 
-    during an intense period of in-situ star formation. 
-    The outskirts of massive galaxies are then built up via a more gradual second 
-    phase of evolution (the ``ex-situ'' phase) which is dominated by mass growth via 
-    the accretion of satellite systems. 
-    Non-dissipative minor mergers mostly deposit stars on the outskirts of the 
-    centrals and do not have large impact on the central \mden{} profile 
-    (e.g. \citealt{Oogi2013, Bedorf2013}). 
-    Hence, according to this picture, the outer stellar envelopes of massive centrals 
-    should correlate with the masses of their host halos, in qualitative agreement with
-    our findings.
-
-    State of the art hydrodynamic simulations suggest that massive dark matter halos 
-    have central galaxies that have outer stellar envelopes with shallow slopes 
-    (e.g. \citealt{Pillepich2014}). 
-    This is consistent with the results in Fig \ref{fig:prof_1}.
-
-    Meanwhile, these simulation also point out that the fraction of accreted stars 
-    increases steeply with total \mstar{} and that the ``ex-situ'' component
-    starts to dominate the \mden{} profiles around $R_{\mathrm{e}}$ for 
-    \logms{}$\geq 11.5$ galaxies. 
-    In this work, we find that the median \mden{} profiles of \rbcg{} and \nbcg{} 
-    samples start to show differences around 15-20 kpc, which is close to 
-    their $R_{\mathrm{e}}$. 
-    Furthermore, the environmental dependence of our median \mden{} profiles 
-    becomes more significant in our highest \mtot{} bin (see Fig \ref{fig:prof_4}). 
-    These results all align with the picture that the \mhalo{}-dependence of the 
-    \mden{} profiles of massive galaxies is driven by the variations in the 
-    ``ex-situ'' component at large radii.
-
-    We now investigate to what degree our assumption that the inner 10 kpc \mstar{}
-    corresponds to an in-situ mass.    
-    Fig \ref{fig:discussion_1} compares the median \mden{} profiles of the 
-    combined \rbcg{} and \nbcg{} samples in two \mtot{} bins 
-    ($11.4\leq$\logmtot{}$<11.6$ and $11.6\leq$\logmtot{}$<11.8$) with 
-    (1) the median \mden{} profiles of massive ETGs at $1.0 < z < 1.5$ in
-    \citealt{Patel2013} since they are considered as the progenitors of 
-    ${\sim} 10^{11.5} M_{\odot}$ ETGs at $z=0$.    
-    (2) the inner components of $z{\sim} 0$ ellipticals from 2-D decomposition 
-    (\citealt{Huang2013a}).
-    As proxy of the in-situ components, \citet{Huang2013b} showed they are 
-    structurally similar to the compact ``red nuggets'' at high-$z$. 
-    (3) the ``in-situ'' components of simulated central galaxies in massive halos 
-    from \citet{Cooper13} (the inner ${\sim} 5$ kpc is quite uncertain due to the 
-    resolution).  
-    The comparison confirms that \minn{} should be reasonable proxy of the 
-    ``in-situ'' mass\footnote{We convert these \mden{} profiles to the same 
-    Chabrier IMF; but there are still differences in median \mstar{} and 
-    details in the \m2l{} estimates}.  
-    More importantly, it shows that the \mden{} profile at 
-    $\mathrm{R} > 15$-20 kpc is likely dominated by stars that are not related 
-    to the ``in-situ'' processes.
-
-    We also compare with a uniquely massive BCG at high redshift: 
-    a ${\sim} 10^{11.4} M_{\odot}$ BCG with distinctive ``cD''-like envelope at 
-    $z{\sim} 1.1$ (\citealt{Liu2013}).  
-    Its \mden{} profile follows the median profile of $11.6\leq$\logmtot{}$<11.8$ 
-    massive galaxies nicely inside 10-15 kpc, but becomes much steeper in the outskirt.  
-    This unique object may present an interesting case where the inner ``core'' of a 
-    massive BCGs is already in pace at $z{\sim} 1$ when its extended envelope is still
-    under construction.
-    More BCGs like this at $0.5 < z < 1.0$ can shed light on this intriguing 
-    process, and help us confirm whether the environmental dependence of structure 
-    has already emerged within massive galaxies at higher redshift 
-    (e.g. \citealt{Papovich2012})
-
     At the same time, we also find \rbcg{} galaxy tends to have lower \mstar{} within 
@@
     topic to investigate in the future.
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %% 
-  \begin{figure*}
-      \centering 
-      \includegraphics[width=\textwidth]{fig/redbcg_discussion_5}
-      \caption{
-          \textbf{Left}: Relation between \mtot{} and the logarithmic mass difference 
-          between \mmax{} and \mtot{} for both \rbcg{} (red square) and \nbcg{} 
-          (grey dot) galaxies.  The format is very similar to the left figure of 
-          Fig~\ref{fig:smf1}.~~
-          \textbf{Right}: The stellar mass volume-density distributions of massive 
-          galaxies after combining the \rbcg{} and \nbcg{} samples together, using 
-          both \mtot{} (black solid line) and \mmax{} (black dash line). 
-          The uncertainty for distribution using \mtot{} is shown in grey shaded region.  
-          Here, we also compare the distributions with SMF from previous works: 
-          (a): SDSS galaxies at $z{\sim} 0.1$ from \citet{Bernardi2013}; the \mstar{} 
-          is based on photometry from 2-D \ser{}$+$Exponential model fitting; 
-          (b): SDSS galaxies at $z{\sim} 0.1$ from \citet{Moustakas13} based on 
-          improved SDSS \texttt{cModel} photometry; 
-          (c): \texttt{S82-MGC} galaxies at $0.15 < z< 0.43$ from 
-          \citet{Leauthaud2016} based on PSF-matched SDSS-UKIDSS photometry.
-          Please see text for more details of the comparison.
-          }
-      \label{fig:discussion_2}
-  \end{figure*}
-%% ------------------------------------------------------------------------------------ %%
 
@@
 %% ------------------------------------------------------------------------------------ %%
-\subsection{What is the ``Total Mass'' of Massive Galaxies?}
-
-    Even with deep HSC images, it is non trivial to clearly define and measure the
-    ``total'' \mstar{} for these massive systems. 
-    As discussed in Section~\ref{ssec:mtotal}, our 1-D approach has certain advantages 
-    over the 2-D modeling method and in principle, should capture a the majority of 
-    the stellar mass. 
-    However, even though we extend to 100 kpc, there is no evidence that the profile 
-    drops to zero on these scales. 
-    We now estimate how much extra mass is ``hidden'' beyond the 100 kpc radius. 
-    For this, we integrate the \mden{} profiles out to the detection limit in 
-    surface brightness profile that is defined by the background noise.
-    We will call this the ``maximum mass'' of the galaxy (\mmax{}). 
-    For obvious reasons, we find that \mmax{} is larger than \mtot{} with an average 
-    difference of about ${\sim}0.04$ dex. 
-    The left hand side of Fig \ref{fig:discussion_2} shows differences between \mtot{}
-    and \mmax{}. 
-    On a galaxy-by-galaxy basis, the difference \mmax{}-\mtot{} depends on the slope 
-    of the stellar envelope. 
-    In this work, we have opted to in general use \mtot{} rather than \mmax{} as the 
-    uncertainty on \mmax{} is larger. 
-    However, we have checked that none of our results are changed by replacing \mtot{} 
-    via \mmax{}.
-
-    How to define and measure the ``total'' mass of a galaxy becomes a critical 
-    question when studying the high-mass end of the galaxy SMF. 
-    The issues discussed above are currently one of the primary limitations in 
-    determinations of the high-mass end of the SMF (\citealt{Bernardi2016}). 
-    Fig~\ref{fig:smf1} illustrated how improved \mstar{} measurement can 
-    significantly modifies the SMF. 
-    On the right hand side of Fig~\ref{fig:discussion_2}, we further highlight that 
-    the shape of SMF at high-mass end is quite sensitive to even very small 
-    change of \mstar{}. 
-    We also compare the SMFs of our HSC samples with the following previous studies:
-
+   \song{This part is directly copied from Jenny's txt file, not the right place.}    
    \begin{itemize}
 
-        \item The SMF derived from a SDSS-\textit{GALEX} sample of $z{\sim} 0.1$ 
-            galaxies from \citet{Moustakas13}. 
-            Here, the total luminosity is based on the SDSS \cmodel{} magnitude. 
-            The \m2l{} is derived via SED fitting using \texttt{iSEDfit} with similar 
-            assumptions as in our work.
-
-        \item The SMF for $z{\sim} 0.1$ SDSS galaxies from \citet{Bernardi2013}. 
-            The total luminosity is based on 2-D \texttt{SerExp} models 
-            (\ser{}$+$ Exponential disk model; integrated to infinity) that 
-            recovers much more flux compared to SDSS \cmodel{} magnitudes. 
-            The \m2l{} is also from SED fitting assuming a Chabrier IMF.
-
-        \item The SMF for $0.15 < z < 0.30$ galaxies from the \texttt{S82-MGC} sample
-            \citep{Leauthaud2016} where the \mstar{} is derived using 
-            \texttt{iSEDfit} on PSF-corrected aperture photometry from 
-            \texttt{S82}.
+         \item At fixed \mstar{} evaluate within 100 kpc, we find that massive central 
+            galaxies display \mden{} profiles that are not self-similar and which 
+            present subtle but systematic differences that correlate with \mhalo{}.
+            On average, massive central galaxies in more massive halos have slightly 
+            shallower inner \mden{} profiles and more prominent outer envelope.
+
+        \item We also study how the \mden{} profiles vary with \mhalo{} at fixed 
+            ``in-situ'' mass where it is approximated by the \mstar{} within 10 kpc. 
+            At fixed \minn{} we find that central galaxies in more massive halos 
+            possess much more extended stellar envelope in the outskirts than the ones 
+            in smaller halos. 
+            At the same time the ellipticity, and optical color profiles inside 10 kpc 
+            show little to no dependence on environment.
+
+        \item The \mstar{}-size relation also exhibits a clear environmental 
+            dependence and central galaxies in more massive halos have larger 
+            $R_{\mathrm{50}}$ at fixed \mtot{}. 
+            We suggest that the relation between \mtot{} and \minn{}\footnote{or any 
+            better proxy of total \mstar{} and the mass formed in the ``in-situ'' phase.} 
+            can be a useful tool in diagnosing the assembly history of these massive 
+            galaxies and the connection with the assembly of their dark matter halos.
 
    \end{itemize}
-
-%% ------------------------------------------------------------------------------------ %% 
-    It is clear that different analyses lead to very different slopes at high-mass end. 
-    Here, we do not try to evaluate whether the differences displayed in 
-    Fig~\ref{fig:discussion_2} are dominated by differences in photometry versus 
-    assumptions about stellar population models (e.g. \citealt{Bernardi2016}). 
-    However, given that the results that we are comparing assume the same IMF and adopt 
-    similar assumptions about stellar population models, we hypothesize that the 
-    differences in Fig~\ref{fig:discussion_2} are dominated by differences in photometry. 
-    The goal of our of present paper is not to present and discuss a careful evaluation
-    of the high-mass end of the SMF -- this will be presented in a forthcoming paper 
-    once the HSC survey has accumulated more data. 
-    However, this is clearly a topic that warrants further investigation, and careful 
-    photometry measurements from HSC data will shed further light on these questions.
-
-    Finally, we emphasize that in this present study we do not attempt to separate the 
-    light of the galaxy with a potential (and distinct) ``intra-cluster''
-    light component (ICL; e.g. \citealt{Carlberg1997, Lin2004, Gonzalez2005, 
-    Mihos2005}). 
-    Instead, we adopt the view that the light of the main galaxy and the 
-    ``intra-cluster''component are a smooth and continuous distribution. 
-    A reliable isolation of a physically meaningful ICL component using photometry 
-    alone is extremely difficult, if not impossible. 
-    At the imaging depth of HSC, we find no evidence for a clearly distinction between 
-    an ``inner component'' and an ``intra-cluster'' component. 
-    Instead, most of our profiles are smoothly varying out to 100 kpc with little 
-    evidence for a distinct secondary component. 
-    We do note however, that our \rbcg{} sample contains only a small fraction of 
-    extremely massive clusters where strong evidence of photometric ICL component is 
-    often found (\mhalo{}$\simgt 10^{15}M_{\star}$). 
-    At the typical \mhalo{} of our \rbcg{} clusters, one good nearby example would be 
-    the Virgo cluster, whose ultra-deep images (e.g. \citealt{Mihos2016}) show
-    that the stellar halo of the BCG can smoothly extends beyond 100 kpc, while the 
-    ICL only becomes important outside that radius and is dominated by individual 
-    tidal features.
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
+\section{Discussion}
+    \label{sec:discussion}
+
+    \song{Keep the relevant session from previous draft, need some works.}
+    By using deep imaging from the HSC survey we have shown that the stellar mass 
+    density profiles of massive central galaxies depend systematically on the mass 
+    of their host dark matter halos. 
+    Here we discuss the physical origin, scientific implications, and potential 
+    caveats of this result.
+
+%% ------------------------------------------------------------------------------------ %%
+
+\subsection{The ``Two phase'' Formation Scenario of Massive Galaxies and the 
+            Build-Up of Outer Envelopes}
+
+    Our results are consistent with the picture that massive central galaxies form via 
+    a ``two-phase'' scenario. 
+    According to this theory, the cores of massive galaxies were formed at $z{\sim} 2$ 
+    during an intense period of in-situ star formation. 
+    The outskirts of massive galaxies are then built up via a more gradual second 
+    phase of evolution (the ``ex-situ'' phase) which is dominated by mass growth via 
+    the accretion of satellite systems. 
+    Non-dissipative minor mergers mostly deposit stars on the outskirts of the 
+    centrals and do not have large impact on the central \mden{} profile 
+    (e.g. \citealt{Oogi2013, Bedorf2013}). 
+    Hence, according to this picture, the outer stellar envelopes of massive centrals 
+    should correlate with the masses of their host halos, in qualitative agreement with
+    our findings.
+
+    State of the art hydrodynamic simulations suggest that massive dark matter halos 
+    have central galaxies that have outer stellar envelopes with shallow slopes 
+    (e.g. \citealt{Pillepich2014}). 
+    This is consistent with the results in Fig \ref{fig:prof_1}.
+
+    Meanwhile, these simulation also point out that the fraction of accreted stars 
+    increases steeply with total \mstar{} and that the ``ex-situ'' component
+    starts to dominate the \mden{} profiles around $R_{\mathrm{e}}$ for 
+    \logms{}$\geq 11.5$ galaxies. 
+    In this work, we find that the median \mden{} profiles of \rbcg{} and \nbcg{} 
+    samples start to show differences around 15-20 kpc, which is close to 
+    their $R_{\mathrm{e}}$. 
+    Furthermore, the environmental dependence of our median \mden{} profiles 
+    becomes more significant in our highest \mtot{} bin (see Fig \ref{fig:prof_4}). 
+    These results all align with the picture that the \mhalo{}-dependence of the 
+    \mden{} profiles of massive galaxies is driven by the variations in the 
+    ``ex-situ'' component at large radii.
+
+    We now investigate to what degree our assumption that the inner 10 kpc \mstar{}
+    corresponds to an in-situ mass.    
+    Fig \ref{fig:discussion_1} compares the median \mden{} profiles of the 
+    galaxies in two \mtot{} bins 
+    ($11.4\leq$\logmtot{}$<11.6$ and $11.6\leq$\logmtot{}$<11.8$) with 
+    (1) the median \mden{} profiles of massive ETGs at $1.0 < z < 1.5$ in
+    \citealt{Patel2013} since they are considered as the progenitors of 
+    ${\sim} 10^{11.5} M_{\odot}$ ETGs at $z=0$.    
+    (2) the inner components of $z{\sim} 0$ ellipticals from 2-D decomposition 
+    (\citealt{Huang2013a}).
+    As proxy of the in-situ components, \citet{Huang2013b} showed they are 
+    structurally similar to the compact ``red nuggets'' at high-$z$. 
+    (3) the ``in-situ'' components of simulated central galaxies in massive halos 
+    from \citet{Cooper13} (the inner ${\sim} 5$ kpc is quite uncertain due to the 
+    resolution).  
+    The comparison confirms that \minn{} should be reasonable proxy of the 
+    ``in-situ'' mass\footnote{We convert these \mden{} profiles to the same 
+    Chabrier IMF; but there are still differences in median \mstar{} and 
+    details in the \m2l{} estimates}.  
+    More importantly, it shows that the \mden{} profile at 
+    $\mathrm{R} > 15$-20 kpc is likely dominated by stars that are not related 
+    to the ``in-situ'' processes.
+
+    We also compare with a uniquely massive BCG at high redshift: 
+    a ${\sim} 10^{11.4} M_{\odot}$ BCG with distinctive ``cD''-like envelope at 
+    $z{\sim} 1.1$ (\citealt{Liu2013}).  
+    Its \mden{} profile follows the median profile of $11.6\leq$\logmtot{}$<11.8$ 
+    massive galaxies nicely inside 10-15 kpc, but becomes much steeper in the outskirt.  
+    This unique object may present an interesting case where the inner ``core'' of a 
+    massive BCGs is already in pace at $z{\sim} 1$ when its extended envelope is still
+    under construction.
+    More BCGs like this at $0.5 < z < 1.0$ can shed light on this intriguing 
+    process, and help us confirm whether the environmental dependence of structure 
+    has already emerged within massive galaxies at higher redshift 
+    (e.g. \citealt{Papovich2012})
+%% ------------------------------------------------------------------------------------ %%
 
@@
     \label{sec:summary}
+
+    \song{From old draft, need some works}
 
@@
 \section*{Acknowledgements}
-
-  % Personal 
-  SH thanks F.S.Liu for sharing the data from his work.
 
@@
 
+%% ------------------------------------------------------------------------------------ %% 
+%% Table.1 
+%% ------------------------------------------------------------------------------------ %% 
+\clearpage
+\include{table1}
+\clearpage
+%% ------------------------------------------------------------------------------------ %%
+
 %%%%%%%%%%: Appendix Section %%%%%%%%%%%%
@@
 
-%% ------------------------------------------------------------------------------------ %%
-
-\section{A. Basic Statistical Properties of the Sample} 
-	\label{app:sedasic}
-
-    On the top-left panel of Fig~\ref{fig:sample_stats}, we show the \mtot{}-color 
-    relations using the $k$-corrected $g-r$ color. 
-    Both samples follow the same tight ``red-sequence'' with little contamination 
-    from the ``blue cloud''.
-    At fixed \mtot{}, we see little offset in color distributions of the two 
-    samples, suggesting that both samples consist of quiescent galaxies with 
-    similar average stellar population properties.  
-    This is consistent with previous result that suggests the average stellar 
-    population of massive central galaxy does not depend on \mhalo{} 
-    (e.g.\ \citealt{Park2007}).  
-    In this work, we focus on the \mstar{} range of $11.6 \le$\logmtot{}$\le 11.9$, 
-    where both samples have acceptable completeness, and their \mtot{} distributions 
-    greatly overlap (see the normalized distributions of \mtot{} in the bottom-left 
-    panel of Fig~\ref{fig:sample_stats}). 
-    As for the \minn{} distributions, the two samples overlap the most within 
-    $11.2 \le$\logmtot{}$\le 11.6$, but now they show quite different
-    distributions (bottom-right figure).
-
-    The redshift distributions also show small difference
-    (upper-right panel) even in the high-\mtot{} bin, where the redshift distribution 
-    of the \nbcg{} sample skews toward higher-$z$ end due to the contribution of BOSS 
-    spec-$z$.
-    Since this could bias the comparison of \mden{} profiles and other properties 
-    (please see Appendix\ref{app:redshift} for more details), we address this via matching 
-    the two samples in both mass and redshift distributions carefully
-    (see Appendix~\ref{app:match}).
-
-%% ------------------------------------------------------------------------------------ %% 
-  \begin{figure*}
-      \centering 
-      \includegraphics[width=16.5cm]{fig/redbcg_sample_stats}
-      \caption{
-          \textbf{Top-left}: The \logms{}-$g-r$ color relation of the \rbcg{} 
-          (red circle; detaield format is the same with the right panel of 
-          Fig~\ref{fig:smf1}) and \nbcg{} (grey dots) samples.
-          We apply the $k$-corrections from \texttt{iSEDFit} fitting to the colors.~~          
-          \textbf{Top-right}: the histograms of the redshift for the \rbcg{} and 
-          \nbcg{} galaxies in both \logmtot$>11.2$ and $11.6<$\logmtot{}$<11.9$
-          mass bins.
-          The vertical lines highlights the $0.3\leq z \leq 0.5$ redshift range.~~
-          \textbf{Bottom-left}: the histograms of \mtot{} for the \rbcg{} (orange-red) 
-          and \nbcg{} (grey-black) samples at both $z>0.2$ (step-filled histogram) and 
-          $0.3 \leq z \leq 0.5$ (stepped histogram). 
-          The vertical lines in both top-left and bottom-left figures highlight the 
-          $11.6<$\logmtot{}$<11.9$ mass range that will be used in the comparison of 
-          the \mtot{}-matched samples.~~
-          \textbf{Bottom-right}: the histograms of \minn{} in similar format. 
-          Here the vertical lines highlight the 
-          $11.2<$\logminn{}$<11.6$ mass range that is used for comparison.
-      }
-      \label{fig:sample_stats}
-  \end{figure*}
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %% 
-\section{B. Extraction of 1-D surface brightness profile} 
-    \label{app:ellipse}
-
-    Here we briefly discuss a few technical issues related to the measurements of the 
-    1-D surface brightness profiles around massive galaxies.
-
-    To derive reliable 1-D profile, it is important to mask out all the irrelevant 
-    objects around the target.
-    At the depth of the HSC images, this becomes a quite difficult task, especially 
-    for massive galaxies with extended outer profiles and more satellites. 
-    Right now, the \texttt{hscPipe} tends to ``over-deblend'' around bright object, 
-    we therefore perform \texttt{SExtractor}-like background subtraction and object 
-    detection using the \texttt{SEP} Python library to generate the necessary masks.
-    Combining two different local background models and $S/N$ thresholds, we obtain 
-    the centroid, shape, and radius that enclose 90\% of flux for each object, even 
-    the one that is close to the center of bright galaxy (left panel of 
-    Fig~\ref{fig:ell_tech}), and generate its initial elliptical mask based on these
-    information. 
-    We first create the mask that covers all contaminating objects around the target 
-    after adaptively increasing the sizes of their masks according to their brightness 
-    and distance to the target center. 
-    Generally speaking, we mask out the very bright objects or objects in the 
-    outskirt of the target a little more aggressively as they could impact the 
-    low surface brightness regions more significantly. 
-    We also create masks that are less and more aggressive to test their impacts
-    on the surface brightness profiles.
-
-    Next, we aggressively mask out all objects on the cut-out image and use this mask
-    to evaluate the background level using the distribution of pixel values after 
-    median smoothing the masked image within $6x6$ pixels.
-    This provides us a global estimate of background level along with its uncertainty. 
-    Given the typical RMS of the background pixels, the HSC \texttt{WIDE} images 
-    should reach to $> 29$ \sb surface brightness level in $i$-band.  
-    However, the global background level is often negative around our massive 
-    galaxies, indicating systematic issue in background subtraction.  
-    In current \texttt{hscPipe}, the background on each CCD is modeled with a 
-    Chebyshev-polynomial that is fit to the smoothed image after excluding pixels 
-    with $S/N >5$.
-    This algorithm performs much better than the SDSS version 
-    (e.g.\ see \citealt{Blanton2011}), yet still over-subtracts sky around bright 
-    objects and results in unphysical truncation in the surface brightness profile.
-    We attempt to empirically correct this using the background model generated by 
-    the \texttt{SExtractor} algorithm on the masked image 
-    ($200x200$ pixels background box size, and 6 pixels median filtering size of 
-    sky boxes).
-    This model can account for the slightly over-subtracted background at large scale,
-    and also reduces the impact from the low surface brightness ``wings'' of bright 
-    nearby objects. 
-    After the correction, we can see the improvement from both the remeasured global 
-    background value (closer to 0) and the surface brightness profile (middle panel 
-    of Fig~\ref{app:ellipse}; the negative intensity and the turn-over of the 
-    curve-of-growth in the outskirt of the ``Original'' profile are successfully 
-    corrected). 
-    Such ad hoc correction is not the best way to achieve accurate background 
-    subtraction, but the surface brightness profile within 100 kpc is not very
-    sensitive to the over-subtraction of sky as while.
-
-    The procedure to derive 1-D surface brightness profile from the 
-    background-corrected, contamination-masked images is already described in 
-    Section~\ref{sec:ellipse} briefly. 
-    In practice, the profile at very low surface brightness level is sensitive to 
-    several \texttt{Ellipse} configurations.
-    After some tests, we choose to use 0.1 dex in logarithm as the step in semi-major 
-    axis length between successive ellipses, and we use the median pixel value over the
-    elliptical annulus after rejecting outlying pixels via $3\sigma$-clipping three
-    times.
-    We make the above choices to make the final profile less affected by any nearby
-    object, and also test the differences between the profiles derived using larger
-    step, or mean value on the annulus, or fewer times of $\sigma$-clipping. 
-    Generally speaking, the surface brightness profile is very robust against these
-    changes.  
-    On the right panel of Fig~\ref{fig:ell_tech}, we compare the surface brightness
-    profiles for an example massive galaxy using different masks and \texttt{Ellipse}
-    parameters. 
-    The profile within 100 kpc is very stable, and the only meaningful difference 
-    we can spot is caused by the less aggressive object mask in the very outskirt.
-
-    We should also mention that we run \texttt{Ellipse} allowing for more 
-    sophisticated shapes than a simple ellipse (4th Fourier modes that can make 
-    isophote more ``disky'' or ``boxy'', e.g.\ \citealt{Kormendy2009}) to fit the 
-    isophote better.
-    We also apply the isophotes from $i$-band images to other bands in 
-    ``force-photometry'' mode \texttt{Ellipse} run to get rough estimates of 
-    color profiles.  
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %% 
-    \begin{figure*}
-        \centering 
-        \includegraphics[width=\textwidth]{fig/redbcg_ellipse_tech}
-        \caption{
-            \textbf{Left:} Example of the object-mask built for the \texttt{Ellipse}
-            run for a typical massive galaxy in the sample. 
-            All the shaded regions are masked out. 
-            The three dash lines (red, inner one and two blue ones) around the target 
-            at the center outlines the three radius we defined using the flux radius 
-            of the target.  
-            We increase the mask size for objects detected in different regions 
-            separated by these apertures (which are outlined by solid, elliptical 
-            apertures with different colors) using slightly different criteria.~~
-            \textbf{Middle:}: The flux profile that is zoomed into the near-zero flux 
-            range (top panel), and the curve-of-growth of the magnitude for the example
-            massive galaxy.  
-            To highlight the importance of correcting sky background, we show the profiles 
-            using both images with (red, solid line) and without (black, dash line) 
-            ad-hoc background correction. 
-            On the top panel, besides the horizontal line that highlights the zero flux 
-            level, we also show the uncertainty of the sky background estimate via 
-            grey-shaded region.  
-            On the bottom panel, two horizontal lines indicate the magnitudes 
-            corresponding to total (solid) and half flux (dash) using the 
-            background-corrected profile. ~~
-            \textbf{Right:} compare the 1-D surface brightness profiles for the same 
-            example galaxy extracted using different mask 
-            (smaller masking region: red, dash line; larger masks: blue, dash line), 
-            or different \texttt{Ellipse} settings
-            (more aggressive pixel-clipping: cyan, dash line; 
-             larger step in radius: green, dash line; 
-             using mean flux along the isophote instead of median: purple, dash line)
-            with the one using the default configuration (black, solid line).
-            }
-        \label{fig:ell_tech}
-    \end{figure*}
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %% 
-\section{C. Estimate average {$M_{\star}/L_{\star}$} using \texttt{iSEDFit}} 
-    \label{app:sed}
-
-%% ------------------------------------------------------------------------------------ %% 
-    \begin{figure*}
-        \begin{center}
-        \includegraphics[width=\textwidth]{fig/redbcg_isedfit_example.pdf}
-        \caption{
-            Left: example output figure from \texttt{iSEDFit} that shows the SED 
-        	fitting results. 
-            The open-boxes show the observed fluxes in 5-band, and the solid, blue-dots
-            show the best-fitted results, along with the high-resolution spectrum for
-            this model reconstructed using the synthetic spectra from \texttt{FSPS}. 
-            Top-left corner shows the best-fit stellar population parameters, and 
-            bottom-right corner shows the ID, redshift of this object, and reduced 
-            $\chi^2$ of the best-fit model.~~~
-            Right: the Posterior distributions of a few key parameters.
-            From top-left to bottom right are: 1) stellar mass (\logms{}); 2) age of the 
-            population (mass and star-formation rate weighted) in Gyr; 3) star formation 
-            rate ($\log\ \mathrm{SFR}\ (M_{\odot}/\mathrm{yr})$; instant one and the one 
-            averaged over the previous 100 Myr; 4) stellar metallicity 
-            ($\mathrm{Z}/\mathrm{Z}_{\odot}$); 5) dust extinction ($\mathrm{A}_V$ in mag);
-            6) birthrate parameter ($\log\ b$; averaged over previous 100 and 1000 Myr).
-            }
-        \label{fig:ised}
-        \end{center}
-    \end{figure*}
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %% 
-    \begin{figure*}
-        \begin{center}
-        \includegraphics[width=\textwidth]{fig/redbcg_isedfit_2.pdf}
-        \caption{
-            Relationships between \mstar{} and other stellar population 
-            parameters using the results from \texttt{iSEDfit}. 
-            The \textbf{left} figures are for the \rbcg{} sample, and the 
-            \textbf{righ}t ones are 
-            for the \nbcg{} sample. 
-            They are both color-coded using the redshift of the object, while 
-            their sizes reflect the magnitude differences in $i$-band between 
-            the observed and best-fit value. 
-            The four stellar population properties are: 
-            1) \textbf{Top-left}: mass-weighted stellar age in Gyr; 
-            2) \textbf{Bottom-left}: \m2l{} in $i$-band; 
-            3) \textbf{Top-right}: mass-weighted stellar metallicity in unit of Solar 
-            value;
-            4) \textbf{bottom-right}: dust extinction values in magnitude.
-            }
-        \label{fig:ised_2}
-        \end{center}
-    \end{figure*}
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %% 
-    \begin{figure*}
-        \begin{center}
-        \includegraphics[width=\textwidth]{fig/redbcg_isedfit_3.pdf}
-        \caption{
-            Comparisons of \mstar{} estimated by \texttt{iSEDFit} using different
-            assumptions. 
-            In each figure, we plot the \mstar{} from default model against their 
-            differences with other models. 
-            The top (bottom) row shows the comparisons of the \rbcg{} (\nbcg{}) sample. 
-            The four models involved here are labeled as: 
-            (A): default one; 
-            (B): using the Salpeter IMF instead of the Chabrier one 
-                (\textbf{Left column});
-            (C): using the BC03 synthetic population model instead of the FSPS one
-                (\textbf{Middle column});
-            (D): assume that there is no dust extinction (\textbf{Right column}). 
-            On each figure, the grey shaded region highlights the uncertainty 
-            of the $\log($\logms{}$)$ using typical \mstar{} uncertainties from 
-            both sides. 
-            For each comparison, we highlight the median $\chi^{2}$ value, and the fraction
-            of galaxies with $\chi^{2} > 10.0$ at the top. 
-            We also show the histogram of the \mstar{}-differences on the right panel.
-            }
-        \label{fig:ised_3}
-        \end{center}
-    \end{figure*}
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %%
-
-    In Section~\ref{ssec:isedfit}, we briefly explain the SED fitting procedure and 
-    the priors used.   
-    In Fig~\ref{fig:ised_1}, we show an example of the \texttt{iSEDFit} output by 
-    visualizing the 5-band HSC SED on top of the best-fit model along with the PDF 
-    of the key parameters. 
-    Although we only use the best-fit \m2l{} in this work, it is necessary to make 
-    sure the model is reasonable. 
-    We show the relations between \mstar{} and a few key stellar population parameters 
-    derived by \texttt{iSEDFit} in Fig~\ref{fig:ised_2}. 
-    Although degeneracies among these parameters are almost inevitable using only 
-    five broad-band photometry, most massive galaxies in both \rbcg{} (left) and 
-    \nbcg{} (right) samples have old age, high metallicity ($1.5 \times Z_{\odot}$ is 
-    the highest metallicity allowed by the adopted \texttt{FSPS} SSP models), and low 
-    dust extinction as expected
-
-    Meanwhile, \mstar{} measurement based on SED fitting heavily depends on the 
-    adopted SSP model, the form of IMF, dust extinction law, and details in 
-    the assumption of SFH (e.g.\ \citealt{Bernardi2016b}). 
-    For massive galaxies in this sample, the form of the SFH\footnote{We choose 
-    to use the delayed-$\tau$ model for SFH; we adopt flat distribution between 
-    0.5 to 14.0 Gyrs as the prior for the look-back time when the star formation 
-    turned on. 
-    The exponential delayed time-scale ($\tau$) is allowed to change between 
-    0.1 to 3.0 with equal probability}, the contribution from random star 
-    burst\footnote{The chance of random star burst is set at 0.2 for every 2 Gyrs. 
-    The duration of the star burst is draw from a logarithmic distribution 
-    between 0.03 to 0.3 Gyr; and the mass fraction formed in the burst is from 
-    a logarithmic distribution between 0.01 and 1.0.} do not affect the results. 
-    On the other hand, the choices of SSP model, IMF, and dust extinction do impact
-    the SED fitting results systematically, and we explore it using a few 
-    additional tests (see Fig~\ref{fig:ised_3}):
-
-    \begin{enumerate}
-
-        \item Choosing the \citet{Salpeter1955} IMF results in systematically 
-            higher \mstar{} (on average $+0.25$ dex of \logms{}) for both \rbcg{}
-            and \nbcg{} galaxies (Left panels).
-            Although there are multiple lines of evidence that favor Salpeter 
-            or even more ``bottom-heavy'' IMF in massive galaxies 
-            (e.g.\ \citealt{Conroy2012}; \citealt{Cappellari2012}), we still 
-            present the main results using Chabrier IMF to accommodate galaxies 
-            with lower \mstar{} in the sample, and to be as consistent as possible 
-            with a few previous works.  
-            This choice of IMF does not change the main results qualitatively.
-
-        \item \mstar{} based on the \texttt{BC03} models are systematically lower 
-            than the ones based on \texttt{FSPS+MILES} models (middle panels)
-            The difference shows a large scatter, and can be as large as 0.4 dex,
-            although it does show any \mstar{} dependency. 
-            We notice that the \texttt{BC03} provides better overall ${\chi}^2$. 
-            This could relates to the higher upper limit of stellar metallicity 
-            ($2 \times \mathrm{Z}_{\odot}$) allowed by the \texttt{BC03} model 
-            that help fit the shape of the SED in the red-end better.  
-            However, the \texttt{BC03} model could underestimate the 
-            stellar age for a fraction of massive galaxies ($< 3$--4 Gyrs), and 
-            leads to underestimate of  \m2l{} for them too.
-            It is worth noting that, both \texttt{FSPS} and \texttt{BC03} 
-            models still have difficulties recovering SED at the red-end (between $z$ 
-            and Y-band), and reproducing the optical color-color relations for 
-            red-sequence galaxies (e.g.\ \citealt{MIUSCAT2}).
-            In this work, we decide to keep using the \texttt{FSPS+MILES} model as 
-            the fiducial one.  
-            However, using the results based on \texttt{BC03} model will not 
-            only change the main conclusions here, but also results in more 
-            significant differences in the median \mden{} profiles.
-
-        \item On the right panels of Fig~\ref{fig:ised_3}, we also compare with the
-            SED fitting results without considering the dust extinction. 
-            This choice leads to slightly smaller \mstar{} values as expected. 
-            The impact is very small for the \rbcg{} galaxies, and becomes larger 
-            at the low-\mstar{} end of the \nbcg{} sample. 
-            But it still will not change any of the important results in this work.
-
-    \end{enumerate}
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %% 
-\section{D. Comparison of \mden{} profiles using \mstar{} from the GAMA survey}
+\song{Just copied a couple of relevant sections here; need some works}
+%% ------------------------------------------------------------------------------------ %% 
+\section{A. Comparison of \mden{} profiles using \mstar{} from the GAMA survey}
     \label{app:gama}
@@
 
-\section{E. Comparisons of \mden{} profiles in different redshift bins}
+\section{B. Comparisons of \mden{} profiles in different redshift bins}
     \label{app:redshift}
@@
 
-\section{F. Match the \rbcg{} and \nbcg{} samples in \mstar{} and redshift distributions}
+\section{C. Match the \rbcg{} and \nbcg{} samples in \mstar{} and redshift distributions}
     \label{app:match}
@@
 %% ------------------------------------------------------------------------------------ %% 
-\section{G. Robustness of the \mden{} Differences} 
+\section{D. Robustness of the \mden{} Differences} 
 	\label{app:robust}
@@
 %% ------------------------------------------------------------------------------------ %%  
-%% Table.1 
-%% ------------------------------------------------------------------------------------ %% 
-\clearpage
-\include{table1}
-\clearpage
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %%  
 \bsp

### 2017-03-31 draft/paper1.tex
Change short title

@@
 %% ------------------------------------------------------------------------------------ %% 
-\title[Structure and Halo of Massive Galaxies]{Tracing the Stellar Halo of Massive 
-       Galaxies to 100 kpc at $0.3<z<0.5$ using the Hyper Suprime-Cam}
+\title[Mass Dependent Stellar Halo in Massive Galaxies]{Tracing the Stellar Halo of 
+	   Massive Galaxies to 100 kpc at $0.3<z<0.5$ using the Hyper Suprime-Cam}
 

### 2017-03-31 draft/paper2.tex
Change short title

@@
 %% ------------------------------------------------------------------------------------ %% 
-\title[Structure and Halo of Massive Galaxies]{A Detection of the Environmental 
+\title[Structure and Environment of Massive Galaxies]{A Detection of the Environmental 
        Dependence of the Stellar Profiles and Halos of Massive Central Galaxies}

### 2017-04-07 draft/paper1.tex
New figures to Paper I

@@
     formation.
+    \song{First trial by Jenny; need more works}
 
@@
 %% ------------------------------------------------------------------------------------ %% 
-  \begin{figure*}
+  \begin{figure}
       \centering 
-      \includegraphics[width=\textwidth]{fig/redbcg_smf_new}
+      \includegraphics[width=\columnwidth]{fig/redbcg_completeness}
       \caption{
@@
           (red lines).
+          \song{New figure for completeness; Need to update the caption}
           }
-      \label{fig:smf1}
-  \end{figure*}
+      \label{fig:mass_complete}
+  \end{figure}
+
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
+  \begin{figure}
+      \centering 
+      \includegraphics[width=\columnwidth]{fig/redbcg_mass_diff}
+      \caption{
+          \song{New figures to show how \mstar{} changes with different definitions; 
+                Need to update the caption.}
+          \textbf{Left:} Difference between \mcmodel{} and \mtot{} for central
+      	  galaxies in halos less massive than $10^{14} M_{\odot}$ (grey dots) and 
+      	  in halos more massive than $10^{14} M_{\odot}$ (red squares). 
+          On average, \mcmodel{} underestimates the total stellar mass of massive 
+          galaxies by 0.1 dex while in some cases, the difference can exceed 0.2 dex.
+          Vertical histograms indicate the mass difference for galaxies with
+          $11.6<$\logmtot{}$<11.9$. 
+          \textbf{Right:}: Impact of using \mcmodel{} on the galaxy stellar mass
+          function. 
+          Dashed lines correspond to the SMF computed using \mcmodel{} as an estimate
+          of the total luminosity whereas solid lines correspond to the SMF computed
+          using the total luminosity from our 1-D profile. 
+          The impact on the SMF can exceed 0.2 dex for massive central galaxies 
+          living in halos larger than $\log (M_{\mathrm{halo}}/M_{\odot}) > 14.2$ 
+          (red lines).
+          }
+      \label{fig:mass_diff}
+  \end{figure}
 
@@
     \texttt{S82-MGC} also uses \texttt{iSEDFit} with similar assumptions.}. 
-    The right side of Fig~\ref{fig:smf1} compares the SMFs of galaxies from 
+    The right side of Fig~\ref{fig:mass_complete} compares the SMFs of galaxies from 
     \texttt{S82-MGC} with the SMFs of galaxies from our two 
     samples\footnote{Errors on the SMFs are estimated via bootstrap resampling}. 
-    Based on Fig~\ref{fig:smf1}, we conclude that our sample of massive galaxies is 
+    Based on Fig~\ref{fig:mass_complete}, we conclude that our sample of massive galaxies is 
     reasonably complete down to \logms{}${\sim} 11.6$ at $0.3 \leq z \leq 0.5$. 
@@
     DSouza2014, DSouza2015, Bernardi2016a}). 
-    Fig~\ref{fig:smf1} shows the SMF computed using both \mtot{} and \mcmodel{}. 
+    Fig~\ref{fig:mass_complete} shows the SMF computed using both \mtot{} and \mcmodel{}. 
     As one can be seen from this figure, our careful 1-D approach recovers more flux 
@@
 %% ------------------------------------------------------------------------------------ %% 
-  \begin{figure}
+  \begin{figure*}
       \centering 
-      \includegraphics[width=\columnwidth]{fig/redbcg_discussion_1}
-      \caption{Comparison of the median \mden{} profiles of massive galaxies in the 
+      \includegraphics[width=\textwidth]{fig/redbcg_insitu_accretion}
+      \caption{
+          \song{New figures to illustrate the assumption of in-situ and accreted mass;
+                Need to update the caption.}
+          Comparison of the median \mden{} profiles of massive galaxies in the 
           two lower \mtot{} bins from Fig~\ref{fig:avg_prof} with other observations 
@@
       \label{fig:discussion_1}
-  \end{figure}
+  \end{figure*}
 %% ------------------------------------------------------------------------------------ %%
@@
       \centering 
-      \includegraphics[width=\textwidth]{fig/redbcg_discussion_5}
+      \includegraphics[width=\textwidth]{fig/redbcg_mass_smf}
       \caption{
+          \song{New figures to show the impact of mass definition on SMF. 
+                Need to update the caption.}
           \textbf{Left}: Relation between \mtot{} and the logarithmic mass difference 
@@
           (grey dot) galaxies.  The format is very similar to the left figure of 
-          Fig~\ref{fig:smf1}.~~
+          Fig~\ref{fig:mass_complete}.~~
           \textbf{Right}: The stellar mass volume-density distributions of massive 
@@
     determinations of the high-mass end of the SMF (\citealt{Bernardi2016}). 
-    Fig~\ref{fig:smf1} illustrated how improved \mstar{} measurement can 
+    Fig~\ref{fig:mass_complete} illustrated how improved \mstar{} measurement can 
     significantly modifies the SMF. 
@@
           (red circle; detaield format is the same with the right panel of 
-          Fig~\ref{fig:smf1}) and \nbcg{} (grey dots) samples.
+          Fig~\ref{fig:mass_complete}) and \nbcg{} (grey dots) samples.
           We apply the $k$-corrections from \texttt{iSEDFit} fitting to the colors.~~          
@@
         We plot the \logmgama{} against the difference between \logmtot{} and \logmgama{}. 
-        The format is very similar to the left panel of Fig~\ref{fig:smf1}. 
+        The format is very similar to the left panel of Fig~\ref{fig:mass_complete}. 
         The two vertical lines highlight the mass range $11.4 \leq$\logmgama{}$<11.8$ 

### 2017-04-14 draft/paper1.tex
Add Komiyama-san to author list

@@
 % Version 5; MNRAS format; Edited SH
+% Version 6; MNRAS format; Paper I edited by JG
 
@@
         Alexie Leauthaud,$^{2,1}$
-        Jenny Greene,$^{4}$
+        Jenny E. Greene,$^{4}$
         Kevin Bundy,$^{3,1}$
@@
         Satoshi Miyazaki,$^{5,8}$
+        Yutaka Komiyama,$^{5,8}$
         HSC collaboration 
@@
 
-    Following an initial epoch of early formation, feedback from stars and/or AGN 
+    Following this initial epoch of early formation, feedback from stars and/or AGN 
     (e.g. \citealt{Sijacki2007, Fabian2012}) efficiently quench star formation in 
@@
     of the outer stellar halos of ETGs (e.g.  \citealt{Szomoru2012, Patel2013}).        
-
-    {\bf PP here about mass dependence: in the simulations, a larger fraction of the mass 
-    is ex-situ at increasingly higher mass. Can we see evidence for that observationally by 
-    looking at light profiles?}
+    {\bf Words here about mass dependence: in the simulations, a larger fraction of the mass 
+    is ex-situ at increasingly higher mass. Seen in early work by Naab, Oser, etc, and in the 
+    Illustris papers. First prediction to compare with is that the accreted/ex-situ fraction is 
+    a function of mass.}
 
@@
     compared to ETGs that live in smaller dark matter halos. 
-    A natural prediction of the two-phase formation scenario is therefore that the 
+    A second prediction of the two-phase formation scenario is therefore that the 
     structural properties of massive galaxies should depend on their ``environment''
@@
     Program \citep[SSP,][]{HSCDR1} to characterize the outer parts of massive galaxies 
-    as a function of their properties. Here we will focus on (a) showing that we can 
-    measure profiles for galaxies out to 100 kpc reliably with the HSC data and (b) looking at 
-    trends in stellar mass and outer envelope properties. In a second paper in this series, we 
-    will directly show the environmental dependence of the outer envelope mass.
-    %The goal of this paper is to compare the \mden{} profiles and structural scaling 
-    %relations of massive central galaxies in both low and high mass dark matter halos. 
-    %Fig~\ref{fig:sdss_compare} displays a comparison of the imaging quality of massive 
-    %ETGs using SDSS versus using the new HSC data. 
+    as a function of their properties. 
     The deep imaging depth and excellent seeing conditions of HSC images make them 
@@
     galaxies with $0.3 < z < 0.5$ using ${\sim} 100$ square degree of data from the 
-    HSC wide layer.
-
+    HSC wide layer. In this paper, we use this sample to (a)  
+    measure profiles for galaxies out to 100 kpc reliably with the HSC data and (b) examine the implications 
+    for the stellar mass function when the outer parts of galaxies are accounted for (c) look at 
+    trends in outer envelope properties as a function of stellar mass. In a second paper in this series, we 
+    will directly show the environmental dependence of the outer envelope mass.
+    %The goal of this paper is to compare the \mden{} profiles and structural scaling 
+    %relations of massive central galaxies in both low and high mass dark matter halos. 
+    %Fig~\ref{fig:sdss_compare} displays a comparison of the imaging quality of massive 
+    %ETGs using SDSS versus using the new HSC data.
+
+    \jenny{I suggest removing this here. I do not think it belongs in the Intro:
     Motivated by the ``two-phase'' scenario, and also due to the difficulty in 
@@
     galaxy from its center to the very outskirt, we focus on \mstar{} within two 
-    different physical apertures in this work:
-
-    \begin{itemize}
-
-        \item The stellar mass within 10 kpc (hereafter noted \minn{}). 
-            According to the two-phase scenario, the ``in-situ'' star-formation quickly 
-            builds up the inner, dense core of massive ETGs.  
-            Based on recent observations and simulations (e.g.~\citealt{vanDokkum2010}; 
-            \citealt{RodriguezGomez2016}), the in-situ component of massive ETGs is 
-            mostly contained within one effective radius ($R_{\mathrm{e}}$, or 5-10 kpc). 
-            We use \minn{} as a proxy for the mass forged during the ``in-situ''
-            phase. 
-            Given the quality of the HSC data, we can reliably measure \minn{} over our 
-            redshift range ($1.0^{\arcsec}$ in radius equals 4.4 and 6.1 kpc at redshift
-            0.3 and 0.5).
-
-        \item The stellar mass within 100 kpc (hereafter noted \mtot{}). 
-            For our galaxy sample, a 100 kpc aperture corresponds to 5-10 
-            $\times R_{\mathrm{e}}$. 
-            We show in section \ref{ssec:mtotal} that most of the mass for these ETGs 
-            can be captured by a 100 kpc radius and that \mtot{} is a good proxy for the 
-            ``total'' \mstar{}. 
-            Although not perfect, we argue that our measurements of \mtot{} (which are 
-            actually measuring the light directly out to 100 kpc) are a better tracer 
-            of total \mstar{} than model-dependent results from shallower data 
-            (such as SDSS) which rely on extrapolating the light profiles of galaxies 
-            out to large radii.
-
-       \end{itemize}
-%% ------------------------------------------------------------------------------------ %%
-
-    {\bf We will show the implications for the stellar mass function of including most of 
-    the stellar light, a task that has been complicated before now due to shallower data. 
-    We will also investigate the idea that the accreted fraction is a function of stellar mass.}
+    different physical apertures in this work:}
+
+%    \begin{itemize}
+%    
+%        \item The stellar mass within 10 kpc (hereafter noted \minn{}). 
+%            According to the two-phase scenario, the ``in-situ'' star-formation quickly 
+%            builds up the inner, dense core of massive ETGs.  
+%            Based on recent observations and simulations (e.g.~\citealt{vanDokkum2010}; 
+%            \citealt{RodriguezGomez2016}), the in-situ component of massive ETGs is 
+%            mostly contained within one effective radius ($R_{\mathrm{e}}$, or 5-10 kpc). 
+%            We use \minn{} as a proxy for the mass forged during the ``in-situ''
+%            phase. 
+%            Given the quality of the HSC data, we can reliably measure \minn{} over our 
+%            redshift range ($1.0^{\arcsec}$ in radius equals 4.4 and 6.1 kpc at redshift
+%            0.3 and 0.5).  
+%            
+%        \item The stellar mass within 100 kpc (hereafter noted \mtot{}). 
+%            For our galaxy sample, a 100 kpc aperture corresponds to 5-10 
+%            $\times R_{\mathrm{e}}$. 
+%            We show in section \ref{ssec:mtotal} that most of the mass for these ETGs 
+%            can be captured by a 100 kpc radius and that \mtot{} is a good proxy for the 
+%            ``total'' \mstar{}. 
+%            Although not perfect, we argue that our measurements of \mtot{} (which are 
+%            actually measuring the light directly out to 100 kpc) are a better tracer 
+%            of total \mstar{} than model-dependent results from shallower data 
+%            (such as SDSS) which rely on extrapolating the light profiles of galaxies 
+%            out to large radii.
+%            
+%       \end{itemize}}
+%% ------------------------------------------------------------------------------------ %%
 
@@
     galaxies at $z < 0.5$ from the HSC photometric catalog. 
-    Based on \citep{Leauthaud2016}, galaxies with \logms{}$\geq 11.5$ mostly have 
+    Based on \citet{Leauthaud2016}, galaxies with \logms{}$\geq 11.5$ mostly have 
     $i_{\mathrm{SDSS, cModel}} \leq 21.0$ mag. 
@@
     other optical artifacts\footnote{each criterion removes less than 8\% of the 
-    entire sample.}.This sample corresponds to 1760845 galaxies and will be referred 
+    entire sample.}. This sample corresponds to 1760845 galaxies and will be referred 
     as \texttt{hscPho}. 
@@
     In the end, at $0.3 \leq z \leq 0.5$, we gather a sample of 25286 galaxies with 
-    reliable redshift information (will be referred as \texttt{hscZ}).
+    reliable redshift information (referred as \texttt{hscZ}).
     %% Saved as "dr1_wide_galaxy_icmodel_21.5.fits"
     Among them, the BOSS and SDSS ``legacy'' LRG samples provide the majority of 
-    spec-$z$. 
-    By comparing with the Stripe 82 Massive Galaxy Catalog
-    (\texttt{S82-MGC}; \citealt{Bundy2015}), \citet{Leauthaud2016} have measured the
-    \mstar{} completeness of the combined BOSS and SDSS samples. 
-    They estimate that the BOSS spec-$z$ sample is about 80\% complete at 
-    \logms{}$\geq 11.6$ at $0.3 < z < 0.5$. 
-    The GAMA survey, which partially overlaps with the HSC footprints, supplements 
-    our \texttt{hscZ} sample by 14\%. 
-    Based on \citet{Taylor2011} (e.g.\ their Fig~~6), at $z{\sim} 0.3$, the GAMA 
-    sample is 80\% complete down to $10^{10.8}$\msun; but only 80\% complete to 
-    $10^{12.0}$\msun at $z{\sim} 0.5$. 
-    We can therefore expect our sample to be roughly \mstar{}-complete above 
-    \logms{}$\geq 11.5$-$11.6$. 
-    This question will be addressed more carefully using the overlap region between 
-    HSC and the \texttt{S82-MGC} in Section \ref{ssec:s82}.
-    {\bf Seems to have the section wrong? Plus, can we consolidate these discussions?}
-
-%% ------------------------------------------------------------------------------------ %%  
-\subsection{The \redm{}{} cluster catalog}
-    \label{ssec:redmapper}
-
-    For now, we wish to focus on galaxies located at the center of their dark matter halos. 
-    To limit our sample to central galaxies, we use \texttt{v5.10} of the \redm{}{} 
-    cluster catalog\footnote{See: http://risa.stanford.edu/redmapper/} 
-    (e.g.\ \citealt{Rykoff2014}; \citealt{Rozo2015b}). 
-    These authors have developed a well-tested red-sequence cluster finder that has 
-    been run on SDSS DR8 (\citealt{SDSSDR8}) photometric data. 
-    For each cluster, the catalog provides a photometric redshift ($z_{\lambda}$), a 
-    cluster richness ($\lambda$), and identifies the most likely central galaxy (the 
-    galaxy with the highest $P_{\mathrm{Cen}}$ value). 
-    The \redm{}{} catalog also provides a list of member galaxies for each cluster and 
-    their associated membership probabilities. 
-    Details about the performance of the \redm{}~cluster catalog can be found in 
-    \citet{Rozo2014}, \citet{Rozo2015a}, and \citet{Rozo2015b}. 
-    Several studies have published calibrations between the \redm{}~richness estimate, 
-    $\lambda$, and halo mass (e.g.\ \citealt{Saro2015, Farahi2016, Simet2016, 
-    Melchior2016}). 
-    All these studies consistently find that \redm{} clusters with $\lambda > 20$ 
-    have $\log (M_{\mathrm{halo}}/M_{\odot}) \geq 14.0$. 
-    The \redm{} catalog therefore helps us group massive central galaxies into 
-    samples with different average \mhalo{}. 
-    We will use the central galaxies of \redm{} clusters 
-    ($P_{\mathrm{CEN}} \geq 0.7$) to form a sample of massive central galaxies that 
-    live in massive halos.
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %% 
-  \begin{figure}
-      \centering 
-      \includegraphics[width=\columnwidth]{fig/redbcg_completeness}
-      \caption{
-          \textbf{Left:} Difference between \mcmodel{} and \mtot{} for central
-      	  galaxies in halos less massive than $10^{14} M_{\odot}$ (grey dots) and 
-      	  in halos more massive than $10^{14} M_{\odot}$ (red squares). 
-          On average, \mcmodel{} underestimates the total stellar mass of massive 
-          galaxies by 0.1 dex while in some cases, the difference can exceed 0.2 dex.
-          Vertical histograms indicate the mass difference for galaxies with
-          $11.6<$\logmtot{}$<11.9$. 
-          \textbf{Right:}: Impact of using \mcmodel{} on the galaxy stellar mass
-          function. 
-          Dashed lines correspond to the SMF computed using \mcmodel{} as an estimate
-          of the total luminosity whereas solid lines correspond to the SMF computed
-          using the total luminosity from our 1-D profile. 
-          The impact on the SMF can exceed 0.2 dex for massive central galaxies 
-          living in halos larger than $\log (M_{\mathrm{halo}}/M_{\odot}) > 14.2$ 
-          (red lines).
-          \song{New figure for completeness; Need to update the caption}
-          }
-      \label{fig:mass_complete}
-  \end{figure}
+    spec-$z$. Before we can define our mass-complete sample of central galaxies required for 
+    our analysis, we describe our one-dimensional photometric analysis (\S \ref{sec:ellipse}) 
+    and stellar mass estimations (\S \ref{sec:mstar}). We then define the final sample in \S \ref{sec:final}.
+%    By comparing with the Stripe 82 Massive Galaxy Catalog
+%    (\texttt{S82-MGC}; \citealt{Bundy2015}), \citet{Leauthaud2016} have measured the
+%    \mstar{} completeness of the combined BOSS and SDSS samples. 
+%    They estimate that the BOSS spec-$z$ sample is about 80\% complete at 
+%    \logms{}$\geq 11.6$ at $0.3 < z < 0.5$. 
+%    The GAMA survey, which partially overlaps with the HSC footprints, supplements 
+%    our \texttt{hscZ} sample by 14\%. 
+%    Based on \citet{Taylor2011} (e.g.\ their Fig~~6), at $z{\sim} 0.3$, the GAMA 
+%    sample is 80\% complete down to $10^{10.8}$\msun; but only 80\% complete to 
+%    $10^{12.0}$\msun at $z{\sim} 0.5$. 
+%    We can therefore expect our sample to be roughly \mstar{}-complete above 
+%    \logms{}$\geq 11.5$-$11.6$. 
+%    This question will be addressed more carefully using the overlap region between 
+%    HSC and the \texttt{S82-MGC} in Section \ref{ssec:s82}.
+
+%% ------------------------------------------------------------------------------------ %%  
+%\subsection{The \redm{}{} cluster catalog}
+%    \label{ssec:redmapper}
+%    
+%    For now, we wish to focus on galaxies located at the center of their dark matter halos. 
+%    To limit our sample to central galaxies, we use \texttt{v5.10} of the \redm{}{} 
+%    cluster catalog\footnote{See: http://risa.stanford.edu/redmapper/} 
+%    (e.g.\ \citealt{Rykoff2014}; \citealt{Rozo2015b}). 
+%    These authors have developed a well-tested red-sequence cluster finder that has 
+%    been run on SDSS DR8 (\citealt{SDSSDR8}) photometric data. 
+%    For each cluster, the catalog provides a photometric redshift ($z_{\lambda}$), a 
+%    cluster richness ($\lambda$), and identifies the most likely central galaxy (the 
+%    galaxy with the highest $P_{\mathrm{Cen}}$ value). 
+%    The \redm{}{} catalog also provides a list of member galaxies for each cluster and 
+%    their associated membership probabilities. 
+%    Details about the performance of the \redm{}~cluster catalog can be found in 
+%    \citet{Rozo2014}, \citet{Rozo2015a}, and \citet{Rozo2015b}. 
+%    Several studies have published calibrations between the \redm{}~richness estimate, 
+%    $\lambda$, and halo mass (e.g.\ \citealt{Saro2015, Farahi2016, Simet2016, 
+%    Melchior2016}). 
+%    All these studies consistently find that \redm{} clusters with $\lambda > 20$ 
+%    have $\log (M_{\mathrm{halo}}/M_{\odot}) \geq 14.0$. 
+%    The \redm{} catalog therefore helps us group massive central galaxies into 
+%    samples with different average \mhalo{}. 
+%    We will use the central galaxies of \redm{} clusters 
+%    ($P_{\mathrm{CEN}} \geq 0.7$) to form a sample of massive central galaxies that 
+%    live in massive halos.
+%% ------------------------------------------------------------------------------------ %% 
+%
+%% ------------------------------------------------------------------------------------ %% 
+%  \begin{figure}
+%      \centering 
+%      \includegraphics[width=\columnwidth]{fig/redbcg_completeness}
+%      \caption{
+%          \textbf{Left:} Difference between \mcmodel{} and \mtot{} for central
+%      	  galaxies in halos less massive than $10^{14} M_{\odot}$ (grey dots) and 
+%      	  in halos more massive than $10^{14} M_{\odot}$ (red squares). 
+%          On average, \mcmodel{} underestimates the total stellar mass of massive 
+%          galaxies by 0.1 dex while in some cases, the difference can exceed 0.2 dex.
+%          Vertical histograms indicate the mass difference for galaxies with
+%          $11.6<$\logmtot{}$<11.9$. 
+%          \textbf{Right:}: Impact of using \mcmodel{} on the galaxy stellar mass
+%          function. 
+%          Dashed lines correspond to the SMF computed using \mcmodel{} as an estimate
+%          of the total luminosity whereas solid lines correspond to the SMF computed
+%          using the total luminosity from our 1-D profile. 
+%          The impact on the SMF can exceed 0.2 dex for massive central galaxies 
+%          living in halos larger than $\log (M_{\mathrm{halo}}/M_{\odot}) > 14.2$ 
+%          (red lines).
+%          \song{New figure for completeness; Need to update the caption}
+%          }
+%      \label{fig:mass_complete}
+%  \end{figure}
 
@@
 %% ------------------------------------------------------------------------------------ %% 
-\subsection{Massive Central Galaxies in Low and High Mass Halos}
-    \label{ssec:mass_central}
-
-    One of the goals of our work is to investigate the halo dependence of the outer 
-    envelope. Although there is a correlation between $M_{\star}$ and $M_{\mathrm{Halo}}$,
-    based on recent constraints of $M_{\star}$-$M_{\mathrm{Halo}}$ relation 
-    (e.g.\ \citealt{Leauthaud2012}, \citealt{Behroozi2013}, \citealt{Kravtsov2014}), 
-    even though our sample selects very massive galaxies (\logms{}$\geq 11.5$), they 
-    With the help of the \redm{} catalog, we can broadly separate our sample into two
-    groups with \logmh{}$<14.0$ and \logmh{}$>14.2$.
-    live in a fairly broad range of halos masses.
-
-    % We match this sample with the central galaxies of \redm{}~catalogs using a 
-    % $1.0^{\arcsec}$ radius, and it results in 704 galaxies.  
-    %% Saved as "dr1_redbcg_hsc_sdss_gama_1arcsec.fits"
-
-    We match the \texttt{hscZ} sample with the central galaxies of \redm{} clusters 
-    with $\lambda \geq 30$ and $P_{\mathrm{0.7}} \geq 0.7$, and find 164 matched 
-    galaxies at $0.3 \leq z \leq 0.5$.
-    Our sample of \textbf{central galaxies in more massive halos} will be referred to 
-    as the \rbcg{} sample. 
-    The median $\lambda$ of the clusters associated with the \rbcg{} sample is 
-    ${\sim} 41$, corresponding to halo mass of 
-    $M_{\mathrm{halo}}{\sim} 2.2\times 10^{14}$ $h^{-1}$ $M_{\odot}$.
-    Only 44 centrals from the \rbcg{} sample live in clusters with $\lambda \geq 50$
-    ($M_{\mathrm{halo}} {\sim} 3.0\times 10^{14}$ $h^{-1} M_{\odot}$). 
-    Our \rbcg{} sample therefore corresponds to galaxies in moderate mass halos.
-    %% Saved as "dr1_redbcg_use_sed5b.fits"
-
-    Out next goal is to construct a sample of central galaxies living in halos with 
-    \logmh{}$<14.0$. 
-    We first identify and remove all galaxies within a cylindrical region around all 
-    \redm{} clusters. 
-    We use a radius equal to $R_{\mathrm{200b}}$ and the thickness of the cylinder is 
-    set to twice the uncertainty of the photometric redshift error. 
-    We convert $\lambda$ to $M_{\mathrm{halo}}$ using the calibration of 
-    \citet{Simet2016} and we use the mass-concentration relation from 
-    \citet{Diemer2015} to compute $R_{\mathrm{200b}}$. At $0.3 < z < 0.5$, the 
-    uncertainty of photo-$z$ is between 0.015 to 0.025, and is enough to exclude 
-    cluster members.
-    After removing galaxies associated with \redm{} clusters, the remaining galaxies 
-    in our sample will be dominated by central galaxies living in halos with 
-    \logmh{}$\leq 14.0$. 
-    We will refer to this sample of \textbf{central galaxies in less massive halos}
-    as the \nbcg{} sample.
-
-    Due to the depth and resolution of SDSS, the \redm{} catalog becomes slightly 
-    incomplete at lower richness ($\lambda < 40$) at $z > 0.33$. 
-    To ensure a clean separation in \mhalo{}, here we only focus on the central 
-    galaxies of clusters with $\lambda > 30$. 
-    According to \citet{Simet2016}, this $\lambda \geq 30$ sample should correspond to 
-    $M_{\mathrm{halo}}>10^{14.2} M_{\odot}$. 
-    We have checked that none of the results in this work depend on the choice of this 
-    $\lambda$ limit. 
-    For massive central galaxies that are not in these cluster-level halos, 
-    we unfortunately can not estimate their \mhalo{} individually, but it is safe 
-    to assume they will have $\log (M_{\mathrm{halo}}/M_{\odot}) < 14.0$.  
-    {\bf I am still a bit confused why stellar mass completeness depends on Mh??}
-
-    We note that at this stage, our \nbcg{} sample still contains galaxies with a 
-    wide range of \mstar{} values. 
-    Later on, once we have more accurate \mstar{} estimates, we will further limit this 
-    sample to \logms{}$ > 11.5$. 
-    At this very high mass end, and given that we have rejected satellites in \redm{} 
-    clusters, any further satellite contamination can be safely neglected 
-    (e.g. \citealt{Reid2014, Hoshino2015, Saito2016, vanUitert2016}).
-    %% Saved as "dr1_nonbcg_use_sed5b.fits"
-    % TODO: The actual number waits to be updated}
-
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %% 
-\subsection{Summary of Sample Construction}
-    \label{ssec:sample}
-
-    Using ${\sim} 100$ deg$^2$ of HSC data, we select a large sample of massive central 
-    galaxies with reliable redshift information, and broadly separate them two 
-    categories based on $M_{\mathrm{halo}}$.
-
-    The following is a summary of our sample construction.
-
-    \begin{itemize}
-        \item \texttt{hscPho} sample: this parent sample consists of bright galaxies 
-            with $i_{\mathrm{cModel}} \leq 21.0$, good quality imaging, and reliable 
-            \texttt{cModel} photometry in all five HSC bands in the \texttt{S15B} 
-            data release. 
-        \item \texttt{hscZ} sample: we limit the \texttt{hscPho} sample to galaxies 
-            with reliable redshift information. 
-        \item {\bf Select only central galaxies using RedMapper: total number in full 
-        sample?}
-        \item We further divide the sample into an \rbcg{} sample and a \nbcg{} sample, 
-          with the former roughly having \logmh{}$\geq 14.2$ and the latter having 
-           \logmh{}$<14.0$.
-
+%\subsection{Massive Central Galaxies in Low and High Mass Halos}
+%    \label{ssec:mass_central}
+%
+%    One of the goals of our work is to investigate the halo dependence of the outer 
+%    envelope. Although there is a correlation between $M_{\star}$ and $M_{\mathrm{Halo}}$,
+%    based on recent constraints of $M_{\star}$-$M_{\mathrm{Halo}}$ relation 
+%    (e.g.\ \citealt{Leauthaud2012}, \citealt{Behroozi2013}, \citealt{Kravtsov2014}), 
+%    even though our sample selects very massive galaxies (\logms{}$\geq 11.5$), they 
+%    With the help of the \redm{} catalog, we can broadly separate our sample into two
+%    groups with \logmh{}$<14.0$ and \logmh{}$>14.2$.
+%    live in a fairly broad range of halos masses.
+%    
+%    % We match this sample with the central galaxies of \redm{}~catalogs using a 
+%    % $1.0^{\arcsec}$ radius, and it results in 704 galaxies.  
+%    %% Saved as "dr1_redbcg_hsc_sdss_gama_1arcsec.fits"
+%    
+%    We match the \texttt{hscZ} sample with the central galaxies of \redm{} clusters 
+%    with $\lambda \geq 30$ and $P_{\mathrm{0.7}} \geq 0.7$, and find 164 matched 
+%    galaxies at $0.3 \leq z \leq 0.5$.
+%    Our sample of \textbf{central galaxies in more massive halos} will be referred to 
+%    as the \rbcg{} sample. 
+%    The median $\lambda$ of the clusters associated with the \rbcg{} sample is 
+%    ${\sim} 41$, corresponding to halo mass of 
+%    $M_{\mathrm{halo}}{\sim} 2.2\times 10^{14}$ $h^{-1}$ $M_{\odot}$.
+%    Only 44 centrals from the \rbcg{} sample live in clusters with $\lambda \geq 50$
+%    ($M_{\mathrm{halo}} {\sim} 3.0\times 10^{14}$ $h^{-1} M_{\odot}$). 
+%    Our \rbcg{} sample therefore corresponds to galaxies in moderate mass halos.
+%    %% Saved as "dr1_redbcg_use_sed5b.fits"
+%    
+%    Out next goal is to construct a sample of central galaxies living in halos with 
+%    \logmh{}$<14.0$. 
+%    We first identify and remove all galaxies within a cylindrical region around all 
+%    \redm{} clusters. 
+%    We use a radius equal to $R_{\mathrm{200b}}$ and the thickness of the cylinder is 
+%    set to twice the uncertainty of the photometric redshift error. 
+%    We convert $\lambda$ to $M_{\mathrm{halo}}$ using the calibration of 
+%    \citet{Simet2016} and we use the mass-concentration relation from 
+%    \citet{Diemer2015} to compute $R_{\mathrm{200b}}$. At $0.3 < z < 0.5$, the 
+%    uncertainty of photo-$z$ is between 0.015 to 0.025, and is enough to exclude 
+%    cluster members.
+%    After removing galaxies associated with \redm{} clusters, the remaining galaxies 
+%    in our sample will be dominated by central galaxies living in halos with 
+%    \logmh{}$\leq 14.0$. 
+%    We will refer to this sample of \textbf{central galaxies in less massive halos}
+%    as the \nbcg{} sample.
+%   
+%    Due to the depth and resolution of SDSS, the \redm{} catalog becomes slightly 
+%    incomplete at lower richness ($\lambda < 40$) at $z > 0.33$. 
+%    To ensure a clean separation in \mhalo{}, here we only focus on the central 
+%    galaxies of clusters with $\lambda > 30$. 
+%    According to \citet{Simet2016}, this $\lambda \geq 30$ sample should correspond to 
+%    $M_{\mathrm{halo}}>10^{14.2} M_{\odot}$. 
+%    We have checked that none of the results in this work depend on the choice of this 
+%    $\lambda$ limit. 
+%    For massive central galaxies that are not in these cluster-level halos, 
+%    we unfortunately can not estimate their \mhalo{} individually, but it is safe 
+%    to assume they will have $\log (M_{\mathrm{halo}}/M_{\odot}) < 14.0$.  
+%    {\bf I am still a bit confused why stellar mass completeness depends on Mh??}
+%
+%    We note that at this stage, our \nbcg{} sample still contains galaxies with a 
+%    wide range of \mstar{} values. 
+%    Later on, once we have more accurate \mstar{} estimates, we will further limit this 
+%    sample to \logms{}$ > 11.5$. 
+%    At this very high mass end, and given that we have rejected satellites in \redm{} 
+%    clusters, any further satellite contamination can be safely neglected 
+%    (e.g. \citealt{Reid2014, Hoshino2015, Saito2016, vanUitert2016}).
+%    %% Saved as "dr1_nonbcg_use_sed5b.fits"
+%    % TODO: The actual number waits to be updated}
+%    
+% 
+%%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
+%\subsection{Summary of Sample Construction}
+%    \label{ssec:sample}
+%
+%    Using ${\sim} 100$ deg$^2$ of HSC data, we select a large sample of massive central 
+%    galaxies with reliable redshift information, and broadly separate them two 
+%    categories based on $M_{\mathrm{halo}}$.
+%    
+%    The following is a summary of our sample construction.
+%    
+%    \begin{itemize}
+%        \item \texttt{hscPho} sample: this parent sample consists of bright galaxies 
+%            with $i_{\mathrm{cModel}} \leq 21.0$, good quality imaging, and reliable 
+%            \texttt{cModel} photometry in all five HSC bands in the \texttt{S15B} 
+%            data release. 
+%        \item \texttt{hscZ} sample: we limit the \texttt{hscPho} sample to galaxies 
+%            with reliable redshift information. 
+%        \item {\bf Select only central galaxies using RedMapper: total number in full 
+%        sample?}
+%        \item We further divide the sample into an \rbcg{} sample and a \nbcg{} sample, 
+%          with the former roughly having \logmh{}$\geq 14.2$ and the latter having 
+%           \logmh{}$<14.0$.
+%
 %          : we select a sample of 164 galaxies at 
@@
 %            halos with \logmh{}$<14.0$.  
-    \end{itemize}
-
-    We now proceed to measure the luminosities and stellar mass profiles for 
-    all galaxies in the \rbcg{} and \nbcg{} samples.
+%    \end{itemize}
+%    
+%    We now proceed to measure the luminosities and stellar mass profiles for 
+%    all galaxies in the \rbcg{} and \nbcg{} samples.
 %% ------------------------------------------------------------------------------------ %%
@@
     This is an intrinsic limitation of the 1-D method. 
-    It affects $18/164$ of the \rbcg{} sample, and a smaller fraction of the 
-    \nbcg{} sample. 
+    \jenny{This cut removes roughly 10\% of the sample.}
+    %It affects $18/164$ of the \rbcg{} sample, and a smaller fraction of the 
+    %\nbcg{} sample. 
     It is worth noting that this excludes most major-merging massive galaxies.
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %% 
-\section{Stellar Masses and Stellar Mass Density Profiles}
+
+    \jenny{Describe the two apertures here I think?}
+    Given our exquisite profiles out to 100 kpc, the meaning of ``total'' magnitude can take on different meanings. 
+    Throughout this work, we consider two benchmark physical apertures:
+        \begin{itemize}    
+        \item The stellar mass within 10 kpc (hereafter noted \minn{}). 
+            According to the two-phase scenario, the ``in-situ'' star-formation quickly 
+            builds up the inner, dense core of massive ETGs.  
+            Based on recent observations and simulations (e.g.~\citealt{vanDokkum2010}; 
+            \citealt{RodriguezGomez2016}), the in-situ component of massive ETGs is 
+            mostly contained within one effective radius ($R_{\mathrm{e}}$, or 5-10 kpc). 
+            We use \minn{} as a proxy for the mass forged during the ``in-situ''
+            phase. 
+            Given the quality of the HSC data, we can reliably measure \minn{} over our 
+            redshift range ($1.0^{\arcsec}$ in radius equals 4.4 and 6.1 kpc at redshift
+            0.3 and 0.5).
+
+        \item The stellar mass within 100 kpc (hereafter noted \mtot{}). 
+            For our galaxy sample, a 100 kpc aperture corresponds to 5-10 
+            $\times R_{\mathrm{e}}$. 
+            We show in section \ref{ssec:mtotal} that most of the mass for these ETGs 
+            can be captured by a 100 kpc radius and that \mtot{} is a good proxy for the 
+            ``total'' \mstar{}. 
+            Although not perfect, we argue that our measurements of \mtot{} (which are 
+            actually measuring the light directly out to 100 kpc) are a better tracer 
+            of total \mstar{} than model-dependent results from shallower data 
+            (such as SDSS) which rely on extrapolating the light profiles of galaxies 
+            out to large radii.
+
+       \end{itemize}
+
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
+\section{Stellar Masses and Mass Density Profiles}
     \label{sec:mstar}
@@
     For stellar metallicity, we assume a flat distribution between 0.004 to 0.03 
-    (the highest value allowed by FSPS). 
+    (the highest value allowed by FSPS) \jenny{define metallicity here, means different things sometimes}. 
     We adopt the \citet{Calzetti2000} extinction law with a order two Gamma 
@@
     Based on tests using synthetic objects, we find that the average accuracy of
-    \cmodel{} for bright galaxy is roughly at the 1\% level in the $r$, $i$, $z$ bands, 
+    \cmodel{} for a bright galaxy is $\sim 1$\% in the $r$, $i$, $z$ bands, 
     and slightly worse in the $g$ and Y-band. 
@@
 %% ------------------------------------------------------------------------------------ %% 
+\subsection{``Total'' Stellar Masses}
+    \label{ssec:mtotal}
+
+    Using the best-fit stellar mass from \texttt{iSEDFit} (noted as as \mcmodel{}), 
+    we estimate the average \m2l{} in the $i$-band, then use that \m2l{} to convert our 
+    1-D luminosity density profiles into stellar mass density profiles. 
+    We also convert our 10 and 100 kpc aperture luminosities into corresponding stellar 
+    mass estimates (noted as \minn{} and \mtot{}).
+
+    For the remainder of this paper, we will use \mtot{} as a proxy of ``total'' 
+    stellar mass. \jenny{Here is where we need discussion of Figure \ref{fig:mass_diff} I think? When do 
+    we discuss cModel magnitudes?}
+	\jenny{Check me here!}
+    In Appendix~\ref{app:sedasic}, we briefly summarize the basic statistics of 
+    the sample using our estimates of \mtot{} and \minn{}.
+    We confirm that the sample follows a very tight ``red-sequence'' that does not appear to depend on 
+    environment (see \S XX). 
+    Appendix~\ref{app:sed} describes the outputs from our SED fitting process 
+    (average stellar age, metallicity, and internal dust extinction). 
+    We do not utilize these quantities in this paper, but we have checked that they all 
+    behave reasonably for both samples. 
+    As expected, the integration of the 1-D profile out to very large radius recovers 
+    more luminosity (stellar mass) compared to the \cmodel{}-based estimates. 
+    This will be shown in Section \ref{ssec:s82}.
+
+    Our methodology ignores any radial variations in \m2l{}. 
+    It is well known that massive ETGs have negative optical color gradients indicating 
+    gradients in \m2l{} (e.g.\ \citealt{LaBarbera2012}; 
+    \citealt{DSouza2015}). \jenny{earlier reference here?}
+    These color gradients are shallow and smooth out to a few times the effective 
+    radius and color gradients at the outskirts are not yet well quantified.
+    Our results looking at the outer envelopes as a function of mass and environment 
+    will be robust as long as there is \emph{no significant difference in 
+    the average color gradient between sub-samples}.
+    %More importantly, for the comparison between the \rbcg{} and \nbcg{} samples, 
+    %our results will be robust as long as there is \emph{no significant difference in 
+    %the average color gradient between the two samples}. 
+    We have confirmed that this is indeed the case (see Section~\ref{ssec:ell_color}).
+
+    Our method for deriving total stellar masses is similar to the 
+    method adopted by the GAMA survey (\citealt{Taylor2011, Kelvin2012}). 
+    We have compared our \mstar{} values with those from GAMA and the results are given 
+    in Appendix~\ref{app:gama}. 
+    We find a systematic differences between the two \mstar{} estimates.
+    It is likely that the GAMA models fail to capture the flux associated with the 
+    outskirts of galaxies due to the limited depth of SDSS.     
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %%        
+    \subsection{Stellar Mass Completeness}
+    \label{ssec:complete}
+
+    With the help of the \texttt{S82-MGC} (\citealt{Bundy2015}), we investigate the 
+    \mstar{} completeness of our samples. 
+    The \texttt{S82-MGC} sample matches the deeper SDSS photometric data in the 
+    Stripe 82 region (\citealt{Annis2014}) with the near infrared data from the United 
+    Kingdom Infrared Telescope Infrared Deep Sky Survey (UKIDSS; \citealt{Lawrence2007}). 
+    The deeper photometry and better photo-$z$s make the \texttt{S82-MGC} sample complete 
+    to \logms{}$\geq 11.2$ at $z<0.7$ which makes it sufficient to evaluate the 
+    completeness of our HSC samples.
+
+    There are 20453 \texttt{S82-MGC} galaxies that are also in the \texttt{hscPho} 
+    sample at $0.3 \leq z_{\mathrm{s82}} \leq 0.5$. 
+    We compute \mstar{} values for these galaxies using our fiducial 
+    procedure\footnote{The \mstar{} using HSC photometry is in excellent with the 
+    values derived from the \texttt{S82-MGC} which includes NIR data from UKIDSS; 
+    \texttt{S82-MGC} also uses \texttt{iSEDFit} with similar assumptions.}. 
+    Figure~\ref{fig:mass_complete} compares the SMFs of galaxies from 
+    \texttt{S82-MGC} with the SMFs of galaxies from our 
+    sample\footnote{Errors on the SMFs are estimated via bootstrap resampling}. 
+    Based on Fig~\ref{fig:mass_complete}, we conclude that our sample of massive galaxies is 
+    reasonably complete down to \logms{}${\sim} 11.6$ at $0.3 \leq z \leq 0.5$. 
+    %The \rbcg{} sample is less affected by completeness because we can utilize 
+    %photo-$z$s from \redm{}. 
+    %However, the completeness of the \nbcg{} sample is still limited by the 
+    %availability of spec-$z$s from BOSS.    
+    In this work, we will focus on the range $11.6 \le$ \logmtot{}$ \le 11.9$ 
+    where our two samples are complete. 
+    %When comparing \nbcg{} and \rbcg{} we will also always make sure that the two 
+    %samples are well matched both in terms of \mstar{} as well as in terms of redshift. 
+    %Please see the next section and Appendix~\ref{app:match} for more details.
+
+	\jenny{Anything else we need to keep from here?}
+	By comparing with the Stripe 82 Massive Galaxy Catalog
+    (\texttt{S82-MGC}; \citealt{Bundy2015}), \citet{Leauthaud2016} have measured the
+    \mstar{} completeness of the combined BOSS and SDSS samples. 
+    They estimate that the BOSS spec-$z$ sample is about 80\% complete at 
+    \logms{}$\geq 11.6$ at $0.3 < z < 0.5$. 
+    The GAMA survey, which partially overlaps with the HSC footprints, supplements 
+    our \texttt{hscZ} sample by 14\%. 
+    Based on \citet{Taylor2011} (e.g.\ their Fig~~6), at $z{\sim} 0.3$, the GAMA 
+    sample is 80\% complete down to $10^{10.8}$\msun; but only 80\% complete to 
+    $10^{12.0}$\msun at $z{\sim} 0.5$. 
+    We can therefore expect our sample to be roughly \mstar{}-complete above 
+    \logms{}$\geq 11.5$-$11.6$. 
+    This question will be addressed more carefully using the overlap region between 
+    HSC and the \texttt{S82-MGC} in Section \ref{ssec:s82}.
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %%  
+\section{The Final Sample}
+    \label{sec:final}
+
+	With stellar masses in hand, we now use the redMapper cluster catalog to identify a sample of 
+    central galaxies.
+
+	\subsection{Indentifying central galaxies using the \redm{}{} cluster catalog}
+    \label{ssec:redmapper}
+
+    We wish to focus on galaxies located at the center of their dark matter halos. 
+    To limit our sample to central galaxies, we use \texttt{v5.10} of the \redm{}{} 
+    cluster catalog\footnote{See: http://risa.stanford.edu/redmapper/} 
+    (e.g.\ \citealt{Rykoff2014}; \citealt{Rozo2015b}). 
+    These authors have developed a well-tested red-sequence cluster finder that has 
+    been run on SDSS DR8 (\citealt{SDSSDR8}) photometric data. 
+    For each cluster, the catalog provides a photometric redshift ($z_{\lambda}$), a 
+    cluster richness ($\lambda$), and identifies the most likely central galaxy (the 
+    galaxy with the highest $P_{\mathrm{Cen}}$ value). 
+    The \redm{}{} catalog also provides a list of member galaxies for each cluster and 
+    their associated membership probabilities. 
+    Details about the performance of the \redm{}~cluster catalog can be found in 
+    \citet{Rozo2014}, \citet{Rozo2015a}, and \citet{Rozo2015b}.
+
+    Several studies have published calibrations between the \redm{}~richness estimate, 
+    $\lambda$, and halo mass (e.g.\ \citealt{Saro2015, Farahi2016, Simet2016, 
+    Melchior2016}). 
+    All these studies consistently find that \redm{} clusters with $\lambda > 20$ 
+    have $\log (M_{\mathrm{halo}}/M_{\odot}) \geq 14.0$. 
+    The \redm{} catalog therefore helps us group massive central galaxies into 
+    samples with different average \mhalo{}. 
+    We will use the central galaxies of \redm{} clusters 
+    ($P_{\mathrm{CEN}} \geq 0.7$) to form a sample of massive central galaxies that 
+    live in massive halos as described below. In addition to identifying central galaxies, 
+    we are also able to link each galaxy with a halo mass using the redMaPPer catalog, and 
+    this information is also very useful in studying the 
+    relationship between galaxy structure and environment.
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
+  \begin{figure}
+      \centering 
+      \includegraphics[width=\columnwidth]{fig/redbcg_completeness}
+      \caption{
+          \textbf{Left:} Difference between \mcmodel{} and \mtot{} for central
+      	  galaxies in halos less massive than $10^{14} M_{\odot}$ (grey dots) and 
+      	  in halos more massive than $10^{14} M_{\odot}$ (red squares). 
+          On average, \mcmodel{} underestimates the total stellar mass of massive 
+          galaxies by 0.1 dex while in some cases, the difference can exceed 0.2 dex.
+          Vertical histograms indicate the mass difference for galaxies with
+          $11.6<$\logmtot{}$<11.9$. 
+          \textbf{Right:}: Impact of using \mcmodel{} on the galaxy stellar mass
+          function. 
+          Dashed lines correspond to the SMF computed using \mcmodel{} as an estimate
+          of the total luminosity whereas solid lines correspond to the SMF computed
+          using the total luminosity from our 1-D profile. 
+          The impact on the SMF can exceed 0.2 dex for massive central galaxies 
+          living in halos larger than $\log (M_{\mathrm{halo}}/M_{\odot}) > 14.2$ 
+          (red lines).
+          \song{New figure for completeness; Need to update the caption}
+          }
+      \label{fig:mass_complete}
+  \end{figure}
+
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
+%\subsection{Massive Central Galaxies in Low and High Mass Halos}
+%    \label{ssec:mass_central}
+
+    %One of the goals of our work is to investigate the halo dependence of the outer 
+    %envelope. Although there is a correlation between $M_{\star}$ and $M_{\mathrm{Halo}}$,
+    %based on recent constraints of $M_{\star}$-$M_{\mathrm{Halo}}$ relation 
+    %(e.g.\ \citealt{Leauthaud2012}, \citealt{Behroozi2013}, \citealt{Kravtsov2014}), 
+    %even though our sample selects very massive galaxies (\logms{}$\geq 11.5$), they 
+    %With the help of the \redm{} catalog, we can broadly separate our sample into two
+    %groups with \logmh{}$<14.0$ and \logmh{}$>14.2$.
+    %live in a fairly broad range of halos masses.
+
+    % We match this sample with the central galaxies of \redm{}~catalogs using a 
+    % $1.0^{\arcsec}$ radius, and it results in 704 galaxies.  
+    %% Saved as "dr1_redbcg_hsc_sdss_gama_1arcsec.fits"
+
+    Due to the depth and resolution of SDSS, the \redm{} catalog becomes slightly 
+    incomplete at lower richness ($\lambda < 40$) at $z > 0.33$. 
+    To ensure a clean separation in \mhalo{}, here we only focus on the central 
+    galaxies of clusters with $\lambda > 30$. 
+    According to \citet{Simet2016}, this $\lambda \geq 30$ sample should correspond to 
+    $M_{\mathrm{halo}}>10^{14.2} M_{\odot}$. 
+    We have checked that none of the results in this work depend on the choice of this 
+    $\lambda$ limit.
+
+    We therefore match the \texttt{hscZ} sample with the central galaxies of \redm{} clusters 
+    with $\lambda \geq 30$ and $P_{\mathrm{0.7}} \geq 0.7$, and find 164 matched 
+    galaxies at $0.3 \leq z \leq 0.5$.
+    Our sample of \textbf{central galaxies in more massive halos} will be referred to 
+    as the \rbcg{} sample. 
+    The median $\lambda$ of the clusters associated with the \rbcg{} sample is 
+    ${\sim} 41$, corresponding to halo mass of 
+    $M_{\mathrm{halo}}{\sim} 2.2\times 10^{14}$ $h^{-1}$ $M_{\odot}$.
+    Only 44 centrals from the \rbcg{} sample live in clusters with $\lambda \geq 50$
+    ($M_{\mathrm{halo}} {\sim} 3.0\times 10^{14}$ $h^{-1} M_{\odot}$). 
+    Our \rbcg{} sample therefore corresponds to galaxies in moderate mass halos.
+    %% Saved as "dr1_redbcg_use_sed5b.fits"
+
+    Out next goal is to construct a sample of central galaxies living in halos with 
+    \logmh{}$<14.0$. 
+    We first identify and remove all galaxies within a cylindrical region around all 
+    \redm{} clusters. 
+    We use a radius equal to $R_{\mathrm{200b}}$ and the thickness of the cylinder is 
+    set to twice the uncertainty of the photometric redshift error. 
+    We convert $\lambda$ to $M_{\mathrm{halo}}$ using the calibration of 
+    \citet{Simet2016} and we use the mass-concentration relation from 
+    \citet{Diemer2015} to compute $R_{\mathrm{200b}}$. At $0.3 < z < 0.5$, the 
+    uncertainty of photo-$z$ is between 0.015 to 0.025, and is enough to exclude 
+    cluster members.
+    After removing galaxies associated with \redm{} clusters, the remaining galaxies 
+    in our sample will be dominated by central galaxies living in halos with 
+    \logmh{}$\leq 14.0$. 
+    We will refer to this sample of \textbf{central galaxies in less massive halos}
+    as the \nbcg{} sample. For massive central galaxies that are not in these cluster-level halos, 
+    we unfortunately can not estimate their \mhalo{} individually, but it is safe 
+    to assume they will have $\log (M_{\mathrm{halo}}/M_{\odot}) < 14.0$.  
+    At this very high mass end, and given that we have rejected satellites in \redm{} 
+    clusters, any further satellite contamination can be safely neglected 
+    (e.g. \citealt{Reid2014, Hoshino2015, Saito2016, vanUitert2016}).
+    %% Saved as "dr1_nonbcg_use_sed5b.fits"
+    % TODO: The actual number waits to be updated}
+
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
+\subsection{Summary of Sample Construction}
+    \label{ssec:sample}
+
+    Using ${\sim} 100$ deg$^2$ of HSC data, we select a large sample of massive central 
+    galaxies with reliable redshift information, and broadly separate them two 
+    categories based on $M_{\mathrm{halo}}$.
+
+    The following is a summary of our sample construction.
+
+    \begin{itemize}
+        \item \texttt{hscPho} sample: this parent sample consists of bright galaxies 
+            with $i_{\mathrm{cModel}} \leq 21.0$, good quality imaging, and reliable 
+            \texttt{cModel} photometry in all five HSC bands in the \texttt{S15B} 
+            data release. 
+        \item \texttt{hscZ} sample: we limit the \texttt{hscPho} sample to galaxies 
+            with reliable redshift information. 
+        \item We further divide the sample into an \rbcg{} sample and a \nbcg{} sample, 
+          with the former roughly having \logmh{}$\geq 14.2$ and the latter having 
+           \logmh{}$<14.0$.
+
+%          : we select a sample of 164 galaxies at 
+%            $0.3 \leq z \leq 0.5$ that are the central galaxies 
+%            in $\lambda > 30$ \redm{} clusters. 
+%            They represent the central galaxies in very massive halos 
+%            (\logmh{}$\geq 14.2$). 
+%        \item \nbcg{} sample: after excluding all cluster members from the 
+%            \texttt{hscZ} sample, we have 14661 bright galaxies at 
+%            $0.3 \leq z \leq 0.5$. 
+%            After applying an additional \mstar{} cut (see Section 
+%            \ref{ssec:isedfit}), this sample corresponds to central galaxies in 
+%            halos with \logmh{}$<14.0$.  
+    \end{itemize}
+
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
+\section{Results}
+    \label{sec:result}
+
+%% ------------------------------------------------------------------------------------ %%     
+    \subsection{Impact of Missing Light on the Galaxy Stellar Mass Function}
+    \label{ssec:s82}
+
+    Different methods for estimating the ``total'' \mstar{} can have a large impact on 
+    the high mass end of the galaxy stellar mass function (e.g. \citealt{Bernardi2013, 
+    DSouza2014, DSouza2015, Bernardi2016a}). 
+    Fig~\ref{fig:mass_complete} shows the SMF computed using both \mtot{} and \mcmodel{}. 
+    As can be seen from this figure, our careful 1-D approach recovers more flux 
+    in massive galaxies than \texttt{cModel}. 
+    More importantly, the average difference steadily increases with \mtot{}. 
+    At \logms{} $>11.5$, the difference can be larger than 0.2 dex. 
+    This difference relates to the intrinsic limitation of the \texttt{cModel} method 
+    and also reflects the fact that more massive ETGs tend to have more extended 
+    stellar mass distributions (e.g. \citealt{Graham2003}). 
+    Generally speaking, the use of \mtot{} instead of the \mcmodel{} shifts the SMF 
+    towards the higher-mass end and slightly modifies the high-mass slope. 
+    %The impact of missing flux is most prominent for the \rbcg{} sample.
+    For studies about the SMF or other aspects of galaxy evolution based on 
+    \cmodel{}-like photometry or shallower images, these effects can not be neglected.
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %%
+\subsection{Surface Mass Density Profiles}
+    \label{ssec:sbp_compare}
+
+%% ------------------------------------------------------------------------------------ %% 
   \begin{figure*}
@@
           \textbf{Left}: Median \mden{} profiles in three total stellar mass bins. 
-              Here we combine the two \rbcg{} and \nbcg{} samples together -- 
-              the halo mass dependence of these profiles will be explored in subsequent 
-              figures. 
               Thin grey lines show a random subset of individual profiles. 
@@
 %% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %%        
-    \subsection{Stellar Mass Completeness}
-    \label{ssec:complete}
-
-    {\bf Still worth thinking about where this belongs and if it can be consolidated with the 
-    previous discussion somehow. Maybe better in results?}
-    With the help of the \texttt{S82-MGC} (\citealt{Bundy2015}), we investigate the 
-    \mstar{} completeness of our samples. 
-    The \texttt{S82-MGC} sample matches the deeper SDSS photometric data in the 
-    Stripe 82 region (\citealt{Annis2014}) with the near infrared data from the United 
-    Kingdom Infrared Telescope Infrared Deep Sky Survey (UKIDSS; \citealt{Lawrence2007}). 
-    The deeper photometry and better photo-$z$s make the \texttt{S82-MGC} sample complete 
-    to \logms{}$\geq 11.2$ at $z<0.7$ which makes it sufficient to evaluate the 
-    completeness of our HSC samples.
-
-    There are 20453 \texttt{S82-MGC} galaxies that are also in the \texttt{hscPho} 
-    sample at $0.3 \leq z_{\mathrm{s82}} \leq 0.5$. 
-    We compute \mstar{} values for these galaxies using our fiducial 
-    procedure\footnote{The \mstar{} using HSC photometry is in excellent with the 
-    values derived from the \texttt{S82-MGC} which includes NIR data from UKIDSS; 
-    \texttt{S82-MGC} also uses \texttt{iSEDFit} with similar assumptions.}. 
-    The right side of Fig~\ref{fig:mass_complete} compares the SMFs of galaxies from 
-    \texttt{S82-MGC} with the SMFs of galaxies from our two 
-    samples\footnote{Errors on the SMFs are estimated via bootstrap resampling}. 
-    Based on Fig~\ref{fig:mass_complete}, we conclude that our sample of massive galaxies is 
-    reasonably complete down to \logms{}${\sim} 11.6$ at $0.3 \leq z \leq 0.5$. 
-    %The \rbcg{} sample is less affected by completeness because we can utilize 
-    %photo-$z$s from \redm{}. 
-    %However, the completeness of the \nbcg{} sample is still limited by the 
-    %availability of spec-$z$s from BOSS.    
-    In this work, we will focus on the range $11.6 \le$ \logmtot{}$ \le 11.9$ 
-    where our two samples are complete. 
-    %When comparing \nbcg{} and \rbcg{} we will also always make sure that the two 
-    %samples are well matched both in terms of \mstar{} as well as in terms of redshift. 
-    %Please see the next section and Appendix~\ref{app:match} for more details.
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %% 
-\subsection{Stellar Mass Corrected for Total Luminosity}
-    \label{ssec:mtotal}
-
-    Using the best-fit stellar mass from \texttt{iSEDFit} (noted as as \mcmodel{}), 
-    we estimate the average \m2l{} in the $i$-band, then use that \m2l{} to convert our 
-    1-D luminosity density profiles into stellar mass density profiles. 
-    We also convert our 10 and 100 kpc aperture luminosities into corresponding stellar 
-    mass estimates (noted as \minn{} and \mtot{}).
-
-    For the remainder of this paper, we will use \mtot{} as a proxy of ``total'' 
-    stellar mass. 
-    In Appendix~\ref{app:sedasic}, we briefly summarize the basic statistics of 
-    the \rbcg{} and \nbcg{} samples using our estimates of \mtot{} and \minn{}.
-    We confirm that both samples follow a similar and very tight ``red-sequence''. 
-    Appendix~\ref{app:sed} describes the outputs from our SED fitting process 
-    (average stellar age, metallicity, and internal dust extinction). 
-    We do not utilize these quantities in this paper, but we have checked that they all 
-    behave reasonably for both samples. 
-    As expected, the integration of the 1-D profile out to very large radius recovers 
-    more luminosity (stellar mass) compared to the \cmodel{}-based estimates. 
-    This will be shown in Section \ref{ssec:s82}.
-
-    Our methodology ignores any radial variations in \m2l{}. 
-    It is well known that massive ETGs have negative optical color gradients indicating 
-    gradients in \m2l{} (e.g.\ \citealt{LaBarbera2012}; 
-    \citealt{DSouza2015}). 
-    These color gradients are shallow and smooth out to a few times of the effective 
-    radius and color gradients at the outskirts are not yet well quantified.
-    Our results looking at the outer envelopes as a function of mass and environment 
-    will be robust as long as there is \emph{no significant difference in 
-    the average color gradient between sub-samples}.
-    %More importantly, for the comparison between the \rbcg{} and \nbcg{} samples, 
-    %our results will be robust as long as there is \emph{no significant difference in 
-    %the average color gradient between the two samples}. 
-    We have confirmed that this is indeed the case and this will be discussed in 
-    Section~\ref{ssec:ell_color}.
-
-    Our method for deriving total stellar masses is similar to the 
-    method adopted by the GAMA survey (\citealt{Taylor2011, Kelvin2012}). 
-    We have compared our \mstar{} values with those from GAMA and the results are given 
-    in Appendix~\ref{app:gama}. 
-    We find a systematic differences between the two \mstar{} estimates.
-    It is likely that the GAMA models fail to capture the flux associated with the 
-    outskirts of galaxies due to the limited depth of SDSS.     
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %% 
-\section{Results}
-    \label{sec:result}
-
-%% ------------------------------------------------------------------------------------ %%     
-    \subsection{Impact of Missing Light on the Galaxy Stellar Mass Function}
-    \label{ssec:s82}
-
-    Different methods for estimating the ``total'' \mstar{} can have a large impact on 
-    the high mass end of the galaxy stellar mass function (e.g. \citealt{Bernardi2013, 
-    DSouza2014, DSouza2015, Bernardi2016a}). 
-    Fig~\ref{fig:mass_complete} shows the SMF computed using both \mtot{} and \mcmodel{}. 
-    As one can be seen from this figure, our careful 1-D approach recovers more flux 
-    in massive galaxies than \texttt{cModel}. 
-    More importantly, the average difference steadily increases with \mtot{} and also 
-    has a dependence on \mhalo{}. 
-    At \logms{} $>11.5$, the difference can be larger than 0.2 dex. 
-    This difference relates to the intrinsic limitation of the \texttt{cModel} method 
-    and also reflects the fact that more massive ETGs tend to have more extended 
-    stellar mass distributions (e.g. \citealt{Graham2003}). 
-    Generally speaking, the use of \mtot{} instead of the \mcmodel{} shifts the SMF 
-    towards the higher-mass end and slightly modifies the high-mass slope. 
-    %The impact of missing flux is most prominent for the \rbcg{} sample.
-    For studies about the SMF or other aspects of galaxy evolution based on 
-    \cmodel{}-like photometry or shallower images, these effects can not be neglected.
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %%
-\subsection{Surface Mass Density Profiles}
-    \label{ssec:sbp_compare}
 
@@
     showing more prominent stellar envelopes. 
-    Most of these massive galaxies ($\ge 10^{11.4} M_{\odot}$) are slowly-rotating 
+    \jenny{This seems out of place here:Most of these massive galaxies ($\ge 10^{11.4} M_{\odot}$) are slowly-rotating 
     (e.g.\ \citealt{Cappellari13b}) giant ellipticals with ``boxy'' inner isophotal 
     shapes (e.g.\ \citealt{Kormendy2009}), and slightly flattened inner \mden{} 
-    profiles (e.g.\ \citealt{Lauer07}). 
+    profiles (e.g.\ \citealt{Lauer07})}. 
     But in the outskirts, the structure of these galaxies is 
@@
     images) from the Carnegie-Irvine Galaxy Survey (CGS, \citealt{CGS1}). 
-    Because this is a very low redshift sample, these profiles are robust to $r=1$ kpc. 
+    Because this is a very low redshift sample, these profiles are robust to smaller scales, $r=1$ kpc. 
     The \citet{Huang2013a} profiles show good agreement with ours in the region of 
@@
     which is lower than our lowest mass bin. 
-    However, \citep{Patel2013} use the BC03 SSP model which are roughly 0.1 dex 
+    However, \citet{Patel2013} use the BC03 SSP model which are roughly 0.1 dex 
     lower than our FSPS masses (Appendix~\ref{app:sed}). 
-    Furthermore, the \citep{Patel2013} images are shallower than ours meaning 
+    Furthermore, the \citet{Patel2013} images are shallower than ours meaning 
     that there masses will be lower than ours because of missing light in the 
@@
 %% ------------------------------------------------------------------------------------ %% 
-    We now study how the ellipticities (computed via \texttt{Ellipse}) and $k$-corrected 
-    optical colors of massive galaxies vary with radius. 
-    We also study whether or these radial trends differ between our various samples. 
+	In addition to the shape of the light profile, we can also 
+    study the $k$-corrected color profiles and ellipticity profiles 
+    (computed via \texttt{Ellipse}) of these galaxies, and how 
+    they depend on mass and environment.
     These quantities contain interesting information about the physical processes that 
-    shape galaxies, but here we study them mainly with two goals in mind:
-
-    \begin{enumerate}
-
-        \item To see whether the ellipticity profile depends strongly on environment, 
-            and to see whether or not the fact that we use an using average isophotal 
-            shape for our our 1-D \mden{} profiles has any impact on our results.
-
-        \item To verify that the average color gradient does not depend strongly on 
-            the environment and that is not steep enough to cause a problem with our 
-            choice the assumption that it is reasonable to use average \m2l for 
-            comparing massive galaxies. 
-            We extract color profiles by applying the isophotes in $i$-band to images 
-            in other bands in ``forced photometry'' manner.
-
-    \end{enumerate}
+    shape galaxies. We also want to be sure that we do not introduce any systematic bias in 
+    our mass determinations because of systematic changes in color profile with stellar or 
+    halo mass.
+
+    \jenny{Could we add a panel to the plot showing the mass bins as above with the ellipticity profiles?}
+
+    %\begin{enumerate}
+    %    
+    %    \item To see whether the ellipticity profile depends strongly on environment, 
+    %        and to see whether or not the fact that we use an using average isophotal 
+    %        shape for our our 1-D \mden{} profiles has any impact on our results.
+    %    
+    %    \item To verify that the average color gradient does not depend strongly on 
+    %        the environment and that is not steep enough to cause a problem with our 
+    %        choice the assumption that it is reasonable to use average \m2l for 
+    %        comparing massive galaxies. 
+    %        We extract color profiles by applying the isophotes in $i$-band to images 
+    %        in other bands in ``forced photometry'' manner.  
+    %        
+    %\end{enumerate}
 
@@
     profiles are very similar.  
-    {\bf I suggest we keep this}
     This further hints that massive central galaxies in different halos but with 

### 2017-04-17 draft/paper1.tex
Intro: accreted fraction

@@
     Simulations of structure formation within the context of the $\Lambda$-CDM 
-    cosmological model make predictions for the hierarchical growth of dark matter halos 
-    and galaxies (e.g. \citealt{Baugh1996, DeLucia2006}), but there are many open 
-    questions regarding the star-formation history, mass assembly process, and 
+    cosmological model make predictions for the hierarchical growth of dark matter 
+    halos and galaxies (e.g. \citealt{Baugh1996, DeLucia2006}), but there are many 
+    open questions regarding the star-formation history, mass assembly process, and 
     structural evolution of massive galaxies. 
-    Massive galaxies are thought to grow according to a ``two-phase'' formation scenario 
-    (e.g. \citealt{Oser2010, Oser2012}). 
-    In this scenario, the progenitors of $z{\sim} 0$ massive early-type galaxies (ETGs) 
-    undergo a rapid growth phase at $z{\sim} 2$ triggered either by disk instabilities 
-    or gas rich mergers (e.g. \citealt{Hopkins2008, Dekel2009}). 
-    Observationally, the progenitors of ETGs are thought to correspond to the so-called 
-    ``red nuggets'' (e.g. \citealt{Damjanov2009}) which have smaller effective radii 
-    ($R_{\mathrm{e}}$; e.g. \citealt{Trujillo2006, vanDokkum2008, Cimatti2008}), 
-    slightly higher central velocity dispersion and stellar mass density 
-    (\mden{}; e.g. \citealt{vandeSande2011, Belli2014}), more disk-like morphologies 
-    (e.g. \citealt{vanderWel2011}) than their local descendants 
+    Massive galaxies are thought to grow according to a ``two-phase'' formation 
+    scenario (e.g. \citealt{Oser2010, Oser2012}). 
+    In this scenario, the progenitors of $z{\sim} 0$ massive early-type galaxies 
+    (ETGs) undergo a rapid growth phase at $z{\sim} 2$ triggered either by disk 
+    instabilities or gas rich mergers (e.g. \citealt{Hopkins2008, Dekel2009}). 
+    Observationally, the progenitors of ETGs are thought to correspond to the 
+    so-called ``red nuggets'' (e.g. \citealt{Damjanov2009}) which have smaller 
+    effective radii ($R_{\mathrm{e}}$; e.g. \citealt{Trujillo2006, vanDokkum2008, 
+    Cimatti2008}), slightly higher central velocity dispersion and stellar mass 
+    density (\mden{}; e.g. \citealt{vandeSande2011, Belli2014}), more disk-like 
+    morphologies (e.g. \citealt{vanderWel2011}) than their local descendants 
     (e.g. \citealt{Bezanson2009, vanDokkum2010}).
@@
     (e.g. \citealt{Sijacki2007, Fabian2012}) efficiently quench star formation in 
-    massive galaxies and a large fraction of these massive progenitors become quiescent 
-    at $z>1$ (e.g. \citealt{Bezanson2009, Kriek2016}). 
+    massive galaxies and a large fraction of these massive progenitors become 
+    quiescent at $z>1$ (e.g. \citealt{Bezanson2009, Kriek2016}). 
     The second phase in the ``two-phase'' formation scenario is driven by 
@@
     (e.g. \citealt{Naab2006, Khochfar2006}). 
-    According to the ``two-phase'' scenario, minor mergers drive the growth of massive 
-    galaxies at late times and can help explain the significant increase
-    of $R_{\mathrm{e}}$ (e.g. \citealt{Newman2012, vdWel2014}) as well as the build-up 
-    of the outer stellar halos of ETGs (e.g.  \citealt{Szomoru2012, Patel2013}).        
-    {\bf Words here about mass dependence: in the simulations, a larger fraction of the mass 
-    is ex-situ at increasingly higher mass. Seen in early work by Naab, Oser, etc, and in the 
-    Illustris papers. First prediction to compare with is that the accreted/ex-situ fraction is 
-    a function of mass.}
-
-    In addition, according to this two-phase formation scenario, the late time growth of massive ETGs 
-    is intrinsically tied to the growth of their host dark matter halos 
-    (e.g. \citealt{Leauthaud2012, Behroozi2013, Shankar2013}). 
+    According to the ``two-phase'' scenario, minor mergers drive the growth of 
+    massive galaxies at late times and can help explain the significant increase
+    of $R_{\mathrm{e}}$ (e.g. \citealt{Newman2012, vdWel2014}) as well as the 
+    build-up of the outer stellar halos of ETGs (e.g.  \citealt{Szomoru2012, 
+    Patel2013}).        
+    \update{
+    More importantly, both numerical simulation (e.g. \citealt{Oser2010}) and 
+    semi-analytic model (SAM; e.g. \citealt{LeeYi2013, LeeYi2017}) agree that the 
+    mass fraction of the accreted component should increase with total stellar mass, 
+    although different models still predict somewhat different values at fixed 
+    stellar mass (e.g. \citealt{Lackner2012, Cooper13, Qu2017}).
+    According to the recent results from Illustris \footnote{
+    \texttt{http://www.illustris-project.org/}} simulation (\citealt{Vogelsberger2014},
+    \citealt{Genel2014}), the fraction of the accreted mass increases significantly
+    with total stellar mass at \logms{}$>11.0$, and the accreted component starts 
+    to dominate the stellar mass budget ($f_{\mathrm{accreted}}>0.5$) at 
+    \logms{}$>11.5$ (\citealt{RodriguezGomez2016}).
+    }
+
+    \update{
+    These predictions
+
+    }
+    \song{The following section focuses on the environmental dependence, should move 
+    to Paper II, I will replace it with introduction that focus on the mass
+    dependence and outskirt profile.}
+
+    In addition, according to this two-phase formation scenario, the late time growth 
+    of massive ETGs is intrinsically tied to the growth of their host dark matter 
+    halos (e.g. \citealt{Leauthaud2012, Behroozi2013, Shankar2013}). 
     Massive ETGs that live at the center of more massive halos should experience 

### 2017-04-17 draft/paper1.tex
Intro: 1-D profile

--- 2017-04-14 draft/paper1.tex
@@
     (e.g. \citealt{Naab2006, Khochfar2006}). 
-    According to the ``two-phase'' scenario, minor mergers drive the growth of massive 
-    galaxies at late times and can help explain the significant increase
-    of $R_{\mathrm{e}}$ (e.g. \citealt{Newman2012, vdWel2014}) as well as the build-up 
-    of the outer stellar halos of ETGs (e.g.  \citealt{Szomoru2012, Patel2013}).        
-    {\bf Words here about mass dependence: in the simulations, a larger fraction of the mass 
-    is ex-situ at increasingly higher mass. Seen in early work by Naab, Oser, etc, and in the 
-    Illustris papers. First prediction to compare with is that the accreted/ex-situ fraction is 
-    a function of mass.}
-
-    In addition, according to this two-phase formation scenario, the late time growth of massive ETGs 
-    is intrinsically tied to the growth of their host dark matter halos 
-    (e.g. \citealt{Leauthaud2012, Behroozi2013, Shankar2013}). 
-    Massive ETGs that live at the center of more massive halos should experience 
-    a different mass assembly history and should be subject to a larger merger rate 
-    compared to ETGs that live in smaller dark matter halos. 
-    A second prediction of the two-phase formation scenario is therefore that the 
-    structural properties of massive galaxies should depend on their ``environment''
-
-    In order to truly understand the build-up of the outer parts of massive galaxies, very 
-    deep data are needed. Massive ETGs have very steep inner stellar density profiles, 
-    extremely extended stellar envelopes, and radial-dependent isophotal shapes which 
-    make accurate measurements of \mstar{} and $R_{\mathrm{e}}$ very challenging
-    (e.g. \citealt{Bernardi2013, DSouza2014}), 
-    especially in the presence of shallow imaging data such as the Sloan Digital Sky 
-    Survey (SDSS; e.g. \citealt{SDSSDR7, SDSSDR12}).
+    \update{
+    To explain the observed significant increase of $R_{\mathrm{e}}$ (e.g. 
+    \citealt{Newman2012, vdWel2014}) as well as the build-up of the outer stellar 
+    halos of ETGs (e.g. \citealt{Szomoru2012, Patel2013}), the ``two-phase'' 
+    scenario suggests that minor mergers should dominate the mass assembly during 
+    the second phase (e.g. \citealt{Hilz2012, Hilz2013, Oogi2013, Bedorf2013, 
+    Laporte2013}).
+    More importantly, both numerical simulation (e.g. \citealt{Oser2010}) and 
+    semi-analytic model (SAM; e.g. \citealt{LeeYi2013, LeeYi2017}) agree that the 
+    mass fraction of the accreted component should increase with total stellar mass, 
+    although different models still predict somewhat different values at fixed 
+    stellar mass (e.g. \citealt{Lackner2012, Cooper2013, Qu2017}).
+    According to the recent results from Illustris \footnote{
+    \texttt{http://www.illustris-project.org/}} simulation 
+    (\citealt{Vogelsberger2014}, \citealt{Genel2014}), the fraction of the 
+    accreted mass increases significantly with total stellar mass at \logms{}$>11.0$, 
+    and the accreted component starts to dominate the stellar mass budget 
+    ($f_{\mathrm{accreted}}>0.5$) at \logms{}$>11.5$ (\citealt{RodriguezGomez2016}).
+    }
+%% ------------------------------------------------------------------------------------ %%
+
+    \update{
+    At the same time, some of these ``two-phase'' scenario's predictions still have 
+    little observational constraint. 
+    One-dimensional analysis used to conclude that \ser{} law can reasonably describe  
+    the surface brightness (or stellar mass density) profiles of nearby massive 
+    elliptical galaxies (e.g. \citealt{Kormendy2009}; except for the most central 
+    region), and the \ser{} index seems to increase with total luminosity (or stellar 
+    mass; e.g. \citealt{Graham2013}). 
+    There was also suggestion that elliptical galaxies can be divided into two groups
+    based on how well their 1-D surface brightness profiles can be described by \ser{}
+    law (e.g. \citealt{Schombert2015}). 
+    Meanwhile, recent two-dimensional analysis points out that the stellar distributions 
+    of massive ETGs are better fit by multiple-component models 
+    (e.g. \citealt{Huang2013a, Oh2017}). 
+    However, it is still not clear whether these 1-D or 2-D results are consistent with 
+    the ``two-phase'' scenario. 
+    One of the main limitation here is that one needs very deep observations for large 
+    sample of massive ETGs to correctly estimate their total stellar mass 
+    (e.g. \citealt{Bernardi2013, DSouza2014}) and study the assembly history via 
+    their accreted halos (e.g. \citealt{Capaccioli2015, Iodice2016, Iodice2017}).
+    Currently, such works are often limited by the shallow images such as the ones from
+    the Sloan Digital Sky Survey (SDSS; e.g. \citealt{SDSSDR7, SDSSDR12}) or the small 
+    sample size. 
+    }
 
@@
     large radii. 
-    With the help of the \redm{} cluster catalog (e.g.\ \citealt{Rykoff2014}; 
-    \citealt{Rozo2015b}; please see Section~\ref{ssec:redmapper} for details), we 
-    select a large sample (${\sim} 15000$) of massive central 
-    galaxies with $0.3 < z < 0.5$ using ${\sim} 100$ square degree of data from the 
-    HSC wide layer. In this paper, we use this sample to (a)  
-    measure profiles for galaxies out to 100 kpc reliably with the HSC data and (b) examine the implications 
-    for the stellar mass function when the outer parts of galaxies are accounted for (c) look at 
-    trends in outer envelope properties as a function of stellar mass. In a second paper in this series, we 
-    will directly show the environmental dependence of the outer envelope mass.
-    %The goal of this paper is to compare the \mden{} profiles and structural scaling 
-    %relations of massive central galaxies in both low and high mass dark matter halos. 
-    %Fig~\ref{fig:sdss_compare} displays a comparison of the imaging quality of massive 
-    %ETGs using SDSS versus using the new HSC data.
+    \update{
+    With the help of reliable spectroscopic and photometric redshift 
+    (e.g. the ones for \redm{} clusters, \citealt{Rykoff2014}; \citealt{Rozo2015b}),
+    we select a large sample (${\sim} 7000$) of massive central galaxies at 
+    $0.3 < z < 0.5$ using ${\sim} 100$ square degree of data from the 
+    HSC wide layer. 
+    In this paper, we use this sample to 
+    (a) measure individual \mden{} profiles for galaxies out to 100 kpc reliably with 
+    the HSC data, 
+    (b) examine the implications for the stellar mass function when the outer parts 
+    of galaxies are accounted for, and
+    (c) look at trends in outer envelope properties as a function of stellar mass. 
+    In a second paper in this series, we will directly show the environmental dependence
+    of the outer envelope mass (Huang\etal. in prep.)
+    }
 
@@
     different physical apertures in this work:}
+    \song{Since the original paper is quite long and complicated, we decide to define
+    the two aperture masses in the beginning, and explain why they are important.
+    For the new draft, I think it is Ok to do this later, but more comments on this 
+    are welcomed!}
 
@@
               in massive halos from simulation using the particle tagging method
-              (\citealt{Cooper13}).}
+              (\citealt{Cooper2013}).}
       \label{fig:avg_prof}
@@
     simulation where the \mden{} profiles of galaxies are calculated using the 
-    particle-tagging technique (e.g. \citealt{Cooper10}).
+    particle-tagging technique (e.g. \citealt{Cooper2010}).
 
@@
           3) the median \mden{} profile of the ``in-situ'' stellar components in 
-          simulated massive halos from \citet[][Purple, dot-dashed]{Cooper13};
+          simulated massive halos from \citet[][Purple, dot-dashed]{Cooper2013};
           4) the \mden{} profile of the very massive cD galaxy at $z{\sim} 1.1$ 
@@
     (3) the ``in-situ'' components of simulated central galaxies in massive halos 
-    from \citet{Cooper13} (the inner ${\sim} 5$ kpc is quite uncertain due to the 
+    from \citet{Cooper2013} (the inner ${\sim} 5$ kpc is quite uncertain due to the 
     resolution).  

### 2017-04-17 draft/paper1.tex
Intro: goals

@@
     the HSC data, 
-    (b) examine the implications for the stellar mass function when the outer parts 
-    of galaxies are accounted for, and
-    (c) look at trends in outer envelope properties as a function of stellar mass. 
-    In a second paper in this series, we will directly show the environmental dependence
-    of the outer envelope mass (Huang\etal. in prep.)
+    (b) examine the implications for the stellar mass function (SMF) when the outer 
+    parts of galaxies are accounted for, and
+    (c) investigate the dependence of their outer envelopes on stellar mass.    
+    In a second paper in this series, we will further look into the potential 
+    environmental dependence of structures in massive ETGs (Huang\etal in prep.).
     }
 
-    \jenny{I suggest removing this here. I do not think it belongs in the Intro:
-    Motivated by the ``two-phase'' scenario, and also due to the difficulty in 
-    providing appropriate model to describe the \mstar{} distribution of massive 
-    galaxy from its center to the very outskirt, we focus on \mstar{} within two 
-    different physical apertures in this work:}
-    \song{Since the original paper is quite long and complicated, we decide to define
-    the two aperture masses in the beginning, and explain why they are important.
-    For the new draft, I think it is Ok to do this later, but more comments on this 
-    are welcomed!}
+    %\jenny{I suggest removing this here. I do not think it belongs in the Intro:
+    %Motivated by the ``two-phase'' scenario, and also due to the difficulty in 
+    %providing appropriate model to describe the \mstar{} distribution of massive 
+    %galaxy from its center to the very outskirt, we focus on \mstar{} within two 
+    %different physical apertures in this work:}
+    %\song{Since the original paper is quite long and complicated, we decide to define
+    %the two aperture masses in the beginning, and explain why they are important.
+    %For the new draft, I think it is Ok to do this later, but more comments on this 
+    %are welcomed!}
 

### 2017-04-17 draft/paper1.tex
Method: 1-D profile

@@
     Combined with the excellent imaging resolution (the median $i$-band seeing is 
-    0.6\asec), and the wide area, the HSC survey represents a tremendous data set to 
-    perform a large statistical study of the surface brightness profiles of ETGs out to 
+    0.6\asec), and the wide area, the HSC survey represents a tremendous dataset to 
+    perform large statistical study of the surface brightness profiles of ETGs out to 
     large radii.     
@@
     and are briefly summarized here. 
-    The HSC SSP data are processed with \texttt{hscPipe 4.0.1}, a derivative of the 
+    The HSC SSP data are processed with \texttt{hscPipe 4.0.2}, a derivative of the 
     Large Synoptic Survey Telescope (LSST) pipeline (e.g.\ \citealt{Juric2015}; 
@@
     measurements). 
-    Astrometric and photometric calibrations are performed at the single exposure level. 
+    Astrometric and photometric calibrations are performed at the single exposure 
+    level. 
     \texttt{hscPipe} then warps different exposures on to a common World Coordinate 
@@
 
-    The pixel scale of the combined images is $0.168^{\arcsec}$. 
+    The pixel scale of the combined images is $0.168$\asec{}. 
     Photometric calibration is based on data from the Panoramic Survey Telescope 
@@
     To achieve consistent deblending and photometry across all bands, \texttt{hscPipe} 
-    performs multi-band post-processing at the coadd level. 
-    First, \texttt{hscPipe} performs object detection on coadd images in each band 
-    independently and records the flux peak and the above-threshold region 
-    (referred as a ``footprint'') for each source. 
-    Next, ``footprints'' and peaks from different bands are merged together before     
+    performs multi-band post-processing at the \texttt{coadd} level. 
+    First, \texttt{hscPipe} performs object detection on \texttt{coadd} images in 
+    each band independently and records the flux peak and the above-threshold region 
+    (referred as a \texttt{footprint}) for each source. 
+    Next, \texttt{footprints} and peaks from different bands are merged together before     
     performing deblending and measurements. 
@@
     object in this reference catalog, \texttt{hscPipe} perform forced photometry 
-    on the coadd image in each band. 
+    on the \texttt{coadd} image in each band. 
     This forced photometry approach is optimized to yield accurate galaxy colors.
@@
     galaxies at $z < 0.5$ from the HSC photometric catalog. 
-    Based on \citet{Leauthaud2016}, galaxies with \logms{}$\geq 11.5$ mostly have 
-    $i_{\mathrm{SDSS, cModel}} \leq 21.0$ mag. 
+    Based on \citet{Leauthaud2016}, $i_{\mathrm{SDSS, cModel}} \leq 21.0$ mag can 
+    define a sample that includes almost all \logms{}$\geq 11.5$ galaxies.    
     We therefore select our initial sample to be brighter than 
@@
     We further select extended objects with no deblending errors, with well defined 
-    centroids, and with \texttt{cModel} magnitudes in all five bands. 
+    centroids, and with useful \texttt{cModel} magnitudes in all five bands. 
     After removing objects that have pixels affected by saturation, cosmic-rays, or 
@@
     have either a spectroscopic redshift or a robust red-sequence photo-$z$ from the 
-    \redm{} catalog (see Section \ref{ssec:redmapper}).  
+    \redm{} galaxy cluster catalog\footnote{See: http://risa.stanford.edu/redmapper/} 
+    (e.g.\ \citealt{Rykoff2014}; \citealt{Rozo2015b}).  
     We match the \texttt{hscPho} sample with a spec-$z$ catalog compiled by the HSC 
     team\footnote{It is created by matching HSC objects with all publicly available 
-    spectroscopic redshifts (e.g.\ SDSS/BOSS; GAMA). The spec-z quality flag from 
-    different catalogs are homogenized into a single flag that indicates secure 
-    redshifts.}.  
+    spectroscopic redshifts (e.g.\ SDSS/BOSS; GAMA). 
+    The spec-z quality flag from different catalogs are homogenized into a single 
+    flag that indicates secure redshifts.}.  
     To ensure reasonable \mstar{}-completeness at the high-\mstar{} end we focus on
@@
 
+    \update{
     For objects without a spectroscopic redshift, we match them with the central 
-    galaxies from the \redm{} catalog using a $2.0^{\arcsec}$ matching radius. 
-    The matched objects with useful red-sequence photo-$z$ ($z_{\lambda}$) are also 
-    included in the final sample of bright galaxies with reliable redshift between 
-    $0.3 \leq z \leq 0.5$. The accuracy of the red-sequence photo-$z$ is sufficient 
-    (median $|z_{\lambda} - z_{\mathrm{Spec}}| {\sim} 0.01$ for the ones with a 
-    spec-$z$) for the goal of this work.
+    galaxies from the \redm{} catalog using a $2.0^{\arcsec}$ matching radius, 
+    and keep the matched objects with useful red-sequence photo-$z$ 
+    ($0.3 \leq z_{\lambda} < 0.5$) in the final sample. 
+    These galaxies are the best candidates for BCGs in clusters selected from 
+    SDSS DR8 data (\citealt{SDSSDR8}) via a well-tested red-sequence method. 
+    The accuracy of the red-sequence photo-$z$ is sufficient (median 
+    $|z_{\lambda} - z_{\mathrm{Spec}}| {\sim} 0.01$ for the ones with spec-$z$) 
+    for the goal of this work.
+    }
     The \redm{} catalog provides an additional 133 unique redshifts for massive 
@@
     Among them, the BOSS and SDSS ``legacy'' LRG samples provide the majority of 
-    spec-$z$. Before we can define our mass-complete sample of central galaxies required for 
-    our analysis, we describe our one-dimensional photometric analysis (\S \ref{sec:ellipse}) 
-    and stellar mass estimations (\S \ref{sec:mstar}). We then define the final sample in \S \ref{sec:final}.
+    spec-$z$. 
+    Before we can define our mass-complete sample of central galaxies required for 
+    our analysis, we describe our one-dimensional photometric analysis 
+    (\S \ref{sec:ellipse}) and stellar mass estimations (\S \ref{sec:mstar}). 
+    We then define the final sample in \S \ref{sec:final}.
+
 %    By comparing with the Stripe 82 Massive Galaxy Catalog
@@
 
-    Massive ETGs imaged at the depth of HSC are not well modeled by simple models such 
-    as the de~Vaucouleurs model or a single \ser component model. 
-    These models will fail to simultaneously capture the profile in both the inner and 
-    the outer region and these models also cannot account for any radial variations in 
-    ellipticity and position angle. 
+    Massive ETGs imaged at the depth of HSC are not well modeled by the de~Vaucouleurs
+    or \ser law. 
+    These models will fail to simultaneously describe the profile in both the inner and 
+    the outer regions and also cannot account for any radial variations in ellipticity 
+    and position angle. 
     In principle, massive galaxies can still be described by more complex 
@@
     degeneracies among different parameters. 
-    Background subtraction uncertainty can affect the 2-D model fitting dramatically, 
+    Background subtraction uncertainty also affects the 2-D model fitting dramatically, 
     especially for massive ETGs in our sample. 
@@
     Based on these tests, we find that our 1-D surface brightness profiles are reliable 
-    up to surfaces brightness levels of $>28.5$ \sb. 
+    up to surfaces brightness levels of $i{\sim}28.5$ \sb. 
     Beyond that, some of our profiles shows signs of truncation and/or large 
@@
     out to $100$ kpc on a galaxy-by-galaxy basis (no stacking). 
-    For more details about the technical details of how we use \texttt{Ellipse}, 
-    please see Appendix~\ref{app:ellipse}.
+    For more technical details of the \texttt{Ellipse} procedure, please see 
+    Appendix~\ref{app:ellipse}.
+
+%% ------------------------------------------------------------------------------------ %%
 
@@
     fraction of massive galaxies because they are heavily masked out. 
-    This is an intrinsic limitation of the 1-D method. 
-    \jenny{This cut removes roughly 10\% of the sample.}
+    \update{
+    This is an intrinsic limitation of the 1-D method, and it removes ${\sim}10$\% of 
+    the sample.
+    }
     %It affects $18/164$ of the \rbcg{} sample, and a smaller fraction of the 
@@
 
-    \jenny{Describe the two apertures here I think?}
-    Given our exquisite profiles out to 100 kpc, the meaning of ``total'' magnitude can take on different meanings. 
-    Throughout this work, we consider two benchmark physical apertures:
+    \update{
+    Given our exquisite profiles out to 100 kpc, the definition and meaning of ``total'' 
+    magnitude (and stellar mass) becomes more interesting.
+    With the help of the \m2l{} estimated in the next section (\S \ref{sec:mstar}), 
+    we can integrate the profile out to certain radii, and estimate the stellar mass 
+    within.  
+    Motivated by the ``two-phase'' scenario, we will consider two benchmark physical 
+    apertures throughout this work:
+    }
+
     \begin{itemize}
-        \item The stellar mass within 10 kpc (hereafter noted \minn{}). 
+
+        \item \textbf{The \mstar{} within the inner 10 kpc} (hereafter noted \minn{}). 
             According to the two-phase scenario, the ``in-situ'' star-formation quickly 
             builds up the inner, dense core of massive ETGs.  
-            Based on recent observations and simulations (e.g.~\citealt{vanDokkum2010}; 
-            \citealt{RodriguezGomez2016}), the in-situ component of massive ETGs is 
-            mostly contained within one effective radius ($R_{\mathrm{e}}$, or 5-10 kpc). 
-            We use \minn{} as a proxy for the mass forged during the ``in-situ''
+            Based on recent observation (e.g.~\citealt{vanDokkum2010}) and simulations 
+            (e.g. \citealt{RodriguezGomez2016}), the in-situ component dominates the 
+            \mstar{} within one effective radius ($R_{\mathrm{e}}$, or 5-10 kpc) of 
+            $z{\sim}0$ massive ETGs.
+            We therefore use \minn{} as proxy for the mass forged during the ``in-situ''
             phase. 
@@
 
-        \item The stellar mass within 100 kpc (hereafter noted \mtot{}). 
+        \item \textbf{The stellar mass within 100 kpc} (hereafter noted \mtot{}). 
             For our galaxy sample, a 100 kpc aperture corresponds to 5-10 
             $\times R_{\mathrm{e}}$. 
-            We show in section \ref{ssec:mtotal} that most of the mass for these ETGs 
-            can be captured by a 100 kpc radius and that \mtot{} is a good proxy for the 
-            ``total'' \mstar{}. 
+            We show in section \ref{ssec:mtotal} that most of the \mstar{} for these 
+            ETGs can be captured by a 100 kpc radius and that \mtot{} is a good proxy 
+            for the ``total'' \mstar{}. 
             Although not perfect, we argue that our measurements of \mtot{} (which are 

### 2017-04-17 draft/paper1.tex
Method: SED fitting

@@
 \newcommand{\kevin}[1]{\textcolor{green}{\textbf{[Kevin: #1]}}}
-\newcommand{\update}[1]{\textcolor{Bittersweet}{#1}}
+\newcommand{\update}[1]{\textcolor{OliveGreen}{#1}}
 %\newcommand{\update}[1]{#1}
@@
     Function (IMF; \citealt{Chabrier2003}).
-    $M_{\mathrm{halo}}$ denotes halo mass in general whereas $M_{\rm 200b}$ is 
-    explicitly defined as $M_{\rm 200b}\equiv M(<r_{\rm 200b})=200\bar{\rho} 
-    \frac{4}{3}\pi r_{\rm 200b}^3$ where $r_{\rm 200b}$
-    is the radius at which the mean interior density is equal to 200 times
-    the mean matter density ($\bar{\rho}$).
+
+    %$M_{\mathrm{halo}}$ denotes halo mass in general whereas $M_{\rm 200b}$ is 
+    %explicitly defined as $M_{\rm 200b}\equiv M(<r_{\rm 200b})=200\bar{\rho} 
+    %\frac{4}{3}\pi r_{\rm 200b}^3$ where $r_{\rm 200b}$
+    %is the radius at which the mean interior density is equal to 200 times
+    %the mean matter density ($\bar{\rho}$).
 
@@
     (e.g. age, metallicity, dust extinction, and star formation history).
-    Based on these models, it uses the observed photometry and redshift to compute the 
-    statistical likelihood, and generates the posterior probability distribution 
+    Based on these models, it uses the observed photometry and redshift to compute 
+    the statistical likelihood, and generates the posterior probability distribution 
     functions (PDF) for each parameter.  
@@
     Synthesis\footnote{http://scholar.harvard.edu/cconroy/sps-models}
-    (FSPS; \texttt{v2.4}; \citealt{FSPS}, \citealt{Conroy2010}) model based on the MILES
-    \footnote{http://www.iac.es/proyecto/miles/pages/stellar-libraries/miles-library.php}
+    (FSPS; \texttt{v2.4}; \citealt{FSPS}, \citealt{Conroy2010}) model based on the 
+    MILES\footnote{http://www.iac.es/proyecto/miles/pages/stellar-libraries}
     (\citealt{MILES1}, \citealt{MILES2}) stellar library and assuming a
@@
     (e.g.\ \citealt{Kauffmann2003}). 
-    For stellar metallicity, we assume a flat distribution between 0.004 to 0.03 
-    (the highest value allowed by FSPS) \jenny{define metallicity here, means different things sometimes}. 
+    \update{
+    For stellar metallicity 
+    ($[\mathrm{M}/\mathrm{H}]=\log\ \mathrm{Z}/\mathrm{Z}_{\odot}$), we assume a flat 
+    distribution between 0.004 to 0.03 (the highest value allowed by FSPS).
+    } 
     We adopt the \citet{Calzetti2000} extinction law with a order two Gamma 
@@
     It therefore underestimates the flux errors of bright galaxies. 
-    Based on tests using synthetic objects, we find that the average accuracy of
-    \cmodel{} for a bright galaxy is $\sim 1$\% in the $r$, $i$, $z$ bands, 
-    and slightly worse in the $g$ and Y-band. 
-    Therefore, we supply \texttt{iSEDFit} with simplified flux errors assuming 
-    $S/N = 100$ for the $riz$ bands, and $S/N = 80$ for the $g$Y bands (on average, 
-    images in $gY$ bands are shallower in depth and/or have higher background noise).  
-    The typical uncertainty of \logms{} is around 0.08-0.10 dex at \logms${\sim} 11.5$. 
+    For this work, we supply \texttt{iSEDFit} with simplified flux errors assuming 
+    $S/N = 100$ for the $riz$ bands, and $S/N = 80$ for the $g$- and $y$-band 
+    (on average, images in $gy$ bands are shallower in depth and/or have higher 
+    background noise).  
+    Although thse are still conservative estimates of the systematic uncertainties 
+    involved in the model-fitting, tests using synthetic galaxies show that \cmodel{}
+    provides excellent measurements of five-band colors, which are crucial for reliable
+    \m2l{} estimates.
+    The typical uncertainty of \logms{} is around 0.06-0.08 dex at \logms${\sim} 11.5$. 
     Please see Appendix~\ref{app:sed} for further details.
@@
     Using the best-fit stellar mass from \texttt{iSEDFit} (noted as as \mcmodel{}), 
-    we estimate the average \m2l{} in the $i$-band, then use that \m2l{} to convert our 
-    1-D luminosity density profiles into stellar mass density profiles. 
+    we estimate the average \m2l{} in the $i$-band, then use that \m2l{} to convert 
+    our 1-D luminosity density profiles into stellar mass density (\mden{}) profiles. 
     We also convert our 10 and 100 kpc aperture luminosities into corresponding stellar 
@@
     For the remainder of this paper, we will use \mtot{} as a proxy of ``total'' 
-    stellar mass. \jenny{Here is where we need discussion of Figure \ref{fig:mass_diff} I think? When do 
-    we discuss cModel magnitudes?}
-	\jenny{Check me here!}
+    stellar mass.
+
     In Appendix~\ref{app:sedasic}, we briefly summarize the basic statistics of 

### 2017-04-18 draft/paper1.tex
Minor changes; new references

@@
 \hypersetup{colorlinks=true,
-            citecolor=cyan,
-            linkcolor=cyan,
+            citecolor=MidnightBlue,
+            linkcolor=MidnightBlue,
             filecolor=magenta,      
@@
 \newcommand{\kevin}[1]{\textcolor{green}{\textbf{[Kevin: #1]}}}
-\newcommand{\update}[1]{\textcolor{OliveGreen}{#1}}
+\newcommand{\update}[1]{\textcolor{PineGreen}{#1}}
 %\newcommand{\update}[1]{#1}
@@
     stellar mass. 
-
-    In Appendix~\ref{app:sedasic}, we briefly summarize the basic statistics of 
+    \update{
+    As expected, the integration of the 1-D profile out to very large radius recovers 
+    more luminosity (stellar mass) compared to the \cmodel{}-based estimates 
+    (Fig \ref{fig:mass_diff}).
+    }
+    \song{Work in progress.}
+
+    In Appendix~\ref{app:sed}, we briefly summarize the basic statistics of 
     the sample using our estimates of \mtot{} and \minn{}.
@@
     behave reasonably for both samples.
-    As expected, the integration of the 1-D profile out to very large radius recovers 
-    more luminosity (stellar mass) compared to the \cmodel{}-based estimates. 
-    This will be shown in Section \ref{ssec:s82}.
-
+
+    \song{The color gradients and ellipticity profiles will be updated}
     Our methodology ignores any radial variations in \m2l{}. 

### 2017-04-20 draft/paper1.tex
Update the sample stats. figure
Update the SED related figures

@@
           $11.2<$\logminn{}$<11.6$ mass range that is used for comparison.
+          \song{Update the caption}
       }
@@
         \begin{center}
-        \includegraphics[width=\textwidth]{fig/redbcg_isedfit_2.pdf}
+        \includegraphics[width=12cm]{fig/redbcg_isedfit_2.pdf}
         \caption{
+            \song{Update the caption.}
             Relationships between \mstar{} and other stellar population 
@@
 %% ------------------------------------------------------------------------------------ %% 
-    \begin{figure*}
+    \begin{figure}
         \begin{center}
-        \includegraphics[width=\textwidth]{fig/redbcg_isedfit_3.pdf}
+        \includegraphics[width=\columnwidth]{fig/redbcg_isedfit_3.pdf}
         \caption{
+            \song{Update the caption.}
             Comparisons of \mstar{} estimated by \texttt{iSEDFit} using different
@@
         \end{center}
-    \end{figure*}
+    \end{figure}
 %% ------------------------------------------------------------------------------------ %%

### 2017-04-23 draft/paper1_jenny.tex
more edits from Jenny

--- 2017-04-20 draft/paper1.tex
@@
     (ETGs) undergo a rapid growth phase at $z{\sim} 2$ triggered either by disk 
-    instabilities or gas rich mergers (e.g. \citealt{Hopkins2008, Dekel2009}). 
+    instabilities or gas-rich mergers (e.g. \citealt{Hopkins2008, Dekel2009}). 
     Observationally, the progenitors of ETGs are thought to correspond to the 
@@
     Cimatti2008}), slightly higher central velocity dispersion and stellar mass 
-    density (\mden{}; e.g. \citealt{vandeSande2011, Belli2014}), more disk-like 
+    density (\mden{}; e.g. \citealt{vandeSande2011, Belli2014}), and more disk-like 
     morphologies (e.g. \citealt{vanderWel2011}) than their local descendants 
@@
     Laporte2013}).
-    More importantly, both numerical simulation (e.g. \citealt{Oser2010}) and 
-    semi-analytic model (SAM; e.g. \citealt{LeeYi2013, LeeYi2017}) agree that the 
-    mass fraction of the accreted component should increase with total stellar mass, 
-    although different models still predict somewhat different values at fixed 
-    stellar mass (e.g. \citealt{Lackner2012, Cooper2013, Qu2017}).
-    According to the recent results from Illustris \footnote{
+    Both numerical simulation (e.g. \citealt{Oser2010}) and 
+    semi-analytic modeling (SAM; e.g. \citealt{LeeYi2013, LeeYi2017}) agree that the 
+    mass fraction in the accreted component should increase with total stellar mass, 
+    although details still differ between models (e.g. \citealt{Lackner2012, Cooper2013, Qu2017}).
+    According to recent results from the Illustris \footnote{
     \texttt{http://www.illustris-project.org/}} simulation 
-    (\citealt{Vogelsberger2014}, \citealt{Genel2014}), the fraction of the 
+    (\citealt{Vogelsberger2014}, \citealt{Genel2014}), the fraction of  
     accreted mass increases significantly with total stellar mass at \logms{}$>11.0$, 
@@
     \update{
-    At the same time, some of these ``two-phase'' scenario's predictions still have 
-    little observational constraint. 
-    One-dimensional analysis used to conclude that \ser{} law can reasonably describe  
-    the surface brightness (or stellar mass density) profiles of nearby massive 
+    Given the success of this two-phase scenario in explaining trends like overall size growth, it is 
+    time to confront their predictions with additional observations using local galaxy mass profiles. Some 
+    progress has been made. One-dimensional analysis has shown that a \ser{} law well-describes 
+    the surface brightness (or stellar mass density) profiles of most nearby massive 
     elliptical galaxies (e.g. \citealt{Kormendy2009}; except for the most central 
-    region), and the \ser{} index seems to increase with total luminosity (or stellar 
-    mass; e.g. \citealt{Graham2013}). 
-    There was also suggestion that elliptical galaxies can be divided into two groups
-    based on how well their 1-D surface brightness profiles can be described by \ser{}
-    law (e.g. \citealt{Schombert2015}). 
-    Meanwhile, recent two-dimensional analysis points out that the stellar distributions 
+    region), with the \ser{} index increasing with total luminosity (e.g. \citealt{Graham2013}).
+	But, the situation may be more complicated, with a suggestion from \citet{Schombert2015} that there are actually 
+    two families of light profiles. Two-dimensional analysis, meanwhile, finds that the stellar distributions 
     of massive ETGs are better fit by multiple-component models 
     (e.g. \citealt{Huang2013a, Oh2017}). 
-    However, it is still not clear whether these 1-D or 2-D results are consistent with 
-    the ``two-phase'' scenario. 
-    One of the main limitation here is that one needs very deep observations for large 
-    sample of massive ETGs to correctly estimate their total stellar mass 
-    (e.g. \citealt{Bernardi2013, DSouza2014}) and study the assembly history via 
+    To really confront the two-phase model requires very deep observations for large 
+    samples of massive ETGs to correctly estimate their total stellar mass 
+    (e.g. \citealt{Bernardi2013, DSouza2014}) and study their assembly history via 
     their accreted halos (e.g. \citealt{Capaccioli2015, Iodice2016, Iodice2017}).
-    Currently, such works are often limited by the shallow images such as the ones from
-    the Sloan Digital Sky Survey (SDSS; e.g. \citealt{SDSSDR7, SDSSDR12}) or the small 
-    sample size. 
+    Currently, such work is limited by the depth of imaging from large-area surveys such as the 
+    Sloan Digital Sky Survey (SDSS; e.g. \citealt{SDSSDR7, SDSSDR12}) or the small 
+    area of deeper imaging. 
     }
@@
     \update{
-    For objects without a spectroscopic redshift, we match them with the central 
-    galaxies from the \redm{} catalog using a $2.0^{\arcsec}$ matching radius, 
-    and keep the matched objects with useful red-sequence photo-$z$ 
+    Objects without a spectroscopic redshift are matched with the central 
+    galaxies from the \redm{} catalog using a $2.0^{\arcsec}$ matching radius. 
+    We keep the matched objects with useful red-sequence photo-$z$ 
     ($0.3 \leq z_{\lambda} < 0.5$) in the final sample. 
-    These galaxies are the best candidates for BCGs in clusters selected from 
+    These galaxies are the best candidates for centrals in clusters selected from 
     SDSS DR8 data (\citealt{SDSSDR8}) via a well-tested red-sequence method. 
@@
 
-    For physical (e.g.\ late-stage major merger) and unphysical (e.g.\ nearby foreground 
-    galaxy or bright star) reasons, we can not extract reliable 1-D profiles for a small 
+    For physical (e.g.\ late-stage major merger) and nuisance (e.g.\ nearby foreground 
+    galaxy or bright star) reasons, we cannot extract reliable 1-D profiles for a small 
     fraction of massive galaxies because they are heavily masked out. 
@@
     \update{
-    Given our exquisite profiles out to 100 kpc, the definition and meaning of ``total'' 
-    magnitude (and stellar mass) becomes more interesting.
+    Given our exquisite profiles that extend to 100 kpc, the definition and meaning of ``total'' 
+    magnitude (and stellar mass) becomes more nuanced.
     With the help of the \m2l{} estimated in the next section (\S \ref{sec:mstar}), 
-    we can integrate the profile out to certain radii, and estimate the stellar mass 
-    within.  
-    Motivated by the ``two-phase'' scenario, we will consider two benchmark physical 
+    we integrate the profile to a range of radii, and estimate the stellar mass 
+    within these different apertures.  
+    Motivated by the two-phase scenario, we will consider two benchmark physical 
     apertures throughout this work:
@@
 %% ------------------------------------------------------------------------------------ %% 
-  \begin{figure*}
+  \begin{figure}
       \centering 
-      \includegraphics[width=\textwidth]{fig/redbcg_discussion_2}
+      \includegraphics[width=\columnwidth]{fig/redbcg_discussion_2}
       \caption{
+          \song{Update caption.}
           Radial variations in ellipticity and optical colors for massive galaxies. 
@@
       \label{fig:ell_color}
-  \end{figure*}
+  \end{figure}
 %% ------------------------------------------------------------------------------------ %%

### 2017-05-25 draft/paper1_jenny.tex
New ellipticity and color gradient plot

@@
         Kevin Bundy,$^{3,1}$
+        \newauthor
         Yen-Ting Lin,$^{5}$
-        \newauthor
-        Masayuki Tanaka,$^{6}$
+        Masayuki Tanaka,$^{5}$
         Rachel Mandelbaum,$^{7}$
         Satoshi Miyazaki,$^{5,8}$
+        \newauthor
         Yutaka Komiyama,$^{5,8}$
@@
     \update{
-    Given the success of this two-phase scenario in explaining trends like overall size growth, it is 
-    time to confront their predictions with additional observations using local galaxy mass profiles. Some 
-    progress has been made. One-dimensional analysis has shown that a \ser{} law well-describes 
-    the surface brightness (or stellar mass density) profiles of most nearby massive 
-    elliptical galaxies (e.g. \citealt{Kormendy2009}; except for the most central 
-    region), with the \ser{} index increasing with total luminosity (e.g. \citealt{Graham2013}).
-	But, the situation may be more complicated, with a suggestion from \citet{Schombert2015} that there are actually 
-    two families of light profiles. Two-dimensional analysis, meanwhile, finds that the stellar distributions 
+    Given the success of this two-phase scenario in explaining trends like overall size 
+    growth, it is time to confront their predictions with additional observations using 
+    local galaxy mass profiles. 
+    Some progress has been made. 
+    One-dimensional analysis has shown that a \ser{} law well-describes the surface 
+    brightness (or stellar mass density) profiles of most nearby massive elliptical 
+    galaxies (e.g. \citealt{Kormendy2009}; except for the most central region), with 
+    the \ser{} index increasing with total luminosity (e.g. \citealt{Graham2013}).
+	But, the situation may be more complicated, with a suggestion from 
+	\citet{Schombert2015} that there are actually two families of light profiles. 
+	Two-dimensional analysis, meanwhile, finds that the stellar distributions 
     of massive ETGs are better fit by multiple-component models 
@@
     their accreted halos (e.g. \citealt{Capaccioli2015, Iodice2016, Iodice2017}).
-    Currently, such work is limited by the depth of imaging from large-area surveys such as the 
-    Sloan Digital Sky Survey (SDSS; e.g. \citealt{SDSSDR7, SDSSDR12}) or the small 
-    area of deeper imaging. 
+    Currently, such work is limited by the depth of imaging from large-area surveys 
+    such as the Sloan Digital Sky Survey (SDSS; e.g. \citealt{SDSSDR7, SDSSDR12}) or
+    the small area of deeper imaging. 
     }
@@
 %% ------------------------------------------------------------------------------------ %% 
-  \begin{figure}
+  \begin{figure*}
       \centering 
-      \includegraphics[width=\columnwidth]{fig/redbcg_discussion_2}
+      \includegraphics[width=\textwidth]{fig/redbcg_ell_color.pdf}
       \caption{
@@
       \label{fig:ell_color}
-  \end{figure}
+  \end{figure*}
 %% ------------------------------------------------------------------------------------ %%

### 2017-05-25 draft/paper1_jenny.tex
Abstract

@@
 
-    We use ${\sim}100$ deg$^2$ of deep ($>28.5$ \sb{} in $i$-band), high-quality 
-    (0.6\asec seeing) imaging data from the Hyper Suprime-Cam (HSC) survey 
-    to investigate the halo mass dependence of the surface mass density profiles 
-    and outer stellar envelopes of massive galaxies. 
+    \update{
+    Massive galaxies are important to our understanding of galaxy formation, and 
+    their extended stellar halos contain crucial fossil records of their assembly 
+    history. 
+    In this work, we use ${\sim}100$ deg$^2$ of deep ($>28.5$ \sb{} in $i$-band), 
+    high-quality (0.6\asec seeing) imaging data from the Hyper Suprime-Cam (HSC) 
+    survey to investigate the surface mass density profiles and outer stellar halos 
+    of massive galaxies. 
     Our sample consists of ${\sim}7000$ massive (\mstar{}$\geq 11.5$) central galaxies 
@@
     requiring stacking. 
-    Shallow imaging will miss light at the outskirts of galaxies and this has an 
-    important impact on measurements of the galaxy mass function. 
-    With these deeper data, we show definitively that at fixed stellar mass,
-    massive central galaxies display mass density profiles that are not self similar, 
-    with the accreted fraction increasing towards unity for galaxies in our highest 
-    stellar mass bin. 
+    Shallow images and/or over-simplified models like the \texttt{CModel} tend to 
+    miss the extended stellar halo and result in underestimated stellar mass in a 
+    mass-dependent way.  
+    It will impact important applications like the measurements of the stellar mass 
+    function. 
+    With these deeper data, we explicitly show that at fixed stellar mass,
+    massive central galaxies display surface mass density profiles that are not 
+    self-similar, with the outer-slope becoming shallower and the fraction of mass 
+    in the outskirt increasing with total stellar mass.
+    We also show that the ellipticity of the stellar halo increases with stellar
+    mass, while the optical color gradients do not strongly depend on stellar mass.
     Our results are broadly consistent with the two phase formation scenario of 
     massive galaxies in which outer envelopes are built up at late times from the 
-    accretion of small systems. 
-    Our mass profiles are provided in a convenient tabulated format in order to 
-    facilitate comparisons with predictions from numerical simulations of galaxy 
-    formation.
-    \song{First trial by Jenny; need more works}
+    accretions of small systems. 
+    The surface mass density profiles are provided in a convenient tabulated format 
+    in order to facilitate comparisons with predictions from numerical simulations 
+    of galaxy formation.
+    }
 

### 2017-05-25 draft/paper1_jenny.tex
Fig 3: Caption

@@
 % Version 6; MNRAS format; Paper I edited by JG
+% Version 7; MNRAS format; Edited by SH
 
@@
 %% ------------------------------------------------------------------------------------ %%
-%
-%% ------------------------------------------------------------------------------------ %% 
-%  \begin{figure}
-%      \centering 
-%      \includegraphics[width=\columnwidth]{fig/redbcg_completeness}
-%      \caption{
-%          \textbf{Left:} Difference between \mcmodel{} and \mtot{} for central
-%      	  galaxies in halos less massive than $10^{14} M_{\odot}$ (grey dots) and 
-%      	  in halos more massive than $10^{14} M_{\odot}$ (red squares). 
-%          On average, \mcmodel{} underestimates the total stellar mass of massive 
-%          galaxies by 0.1 dex while in some cases, the difference can exceed 0.2 dex.
-%          Vertical histograms indicate the mass difference for galaxies with
-%          $11.6<$\logmtot{}$<11.9$. 
-%          \textbf{Right:}: Impact of using \mcmodel{} on the galaxy stellar mass
-%          function. 
-%          Dashed lines correspond to the SMF computed using \mcmodel{} as an estimate
-%          of the total luminosity whereas solid lines correspond to the SMF computed
-%          using the total luminosity from our 1-D profile. 
-%          The impact on the SMF can exceed 0.2 dex for massive central galaxies 
-%          living in halos larger than $\log (M_{\mathrm{halo}}/M_{\odot}) > 14.2$ 
-%          (red lines).
-%          \song{New figure for completeness; Need to update the caption}
-%          }
-%      \label{fig:mass_complete}
-%  \end{figure}
-
-%% ------------------------------------------------------------------------------------ %%
 
@@
       \caption{              
-          \song{New figures to show how \mstar{} changes with different definitions; 
-                Need to update the caption.}
-          \textbf{Left:} Difference between \mcmodel{} and \mtot{} for central
-      	  galaxies in halos less massive than $10^{14} M_{\odot}$ (grey dots) and 
-      	  in halos more massive than $10^{14} M_{\odot}$ (red squares). 
+          \textbf{Top:} Difference between \mcmodel{} and \mtot{} for massive
+      	  galaxies (grey dots).
+      	  The running-median of the mass differences along with the standard deviations
+      	  in a series of mass bins are shown in large red, hexagons with error bars. 
           On average, \mcmodel{} underestimates the total stellar mass of massive 
           galaxies by 0.1 dex while in some cases, the difference can exceed 0.2 dex.
-          Vertical histograms indicate the mass difference for galaxies with
-          $11.6<$\logmtot{}$<11.9$. 
-          \textbf{Right:}: Impact of using \mcmodel{} on the galaxy stellar mass
-          function. 
-          Dashed lines correspond to the SMF computed using \mcmodel{} as an estimate
-          of the total luminosity whereas solid lines correspond to the SMF computed
-          using the total luminosity from our 1-D profile. 
-          The impact on the SMF can exceed 0.2 dex for massive central galaxies 
-          living in halos larger than $\log (M_{\mathrm{halo}}/M_{\odot}) > 14.2$ 
-          (red lines).
+          Vertical histograms indicate the mass difference for all galaxies (shaded 
+          histogram) and for the ones with \logmtot{}$>11.6$ (empty histogram).
+          \textbf{Middle:} Difference between \mmax{} and \mtot{} in the same format. 
+          The average difference is small (0.02 dex) and does not show 
+          clear mass--dependence. 
+          \textbf{Bottom:} Difference between the \mtot{} and \mgama{} in the same
+          format.  
+          Here \mgama{} is based on single-\ser{} model derived from SDSS images. 
           }

### 2017-05-25 draft/paper1_jenny.tex
Fig 4: Caption

@@
       \caption{
-          \textbf{Left:} Difference between \mcmodel{} and \mtot{} for central
-      	  galaxies in halos less massive than $10^{14} M_{\odot}$ (grey dots) and 
-      	  in halos more massive than $10^{14} M_{\odot}$ (red squares). 
-          On average, \mcmodel{} underestimates the total stellar mass of massive 
-          galaxies by 0.1 dex while in some cases, the difference can exceed 0.2 dex.
-          Vertical histograms indicate the mass difference for galaxies with
-          $11.6<$\logmtot{}$<11.9$. 
-          \textbf{Right:}: Impact of using \mcmodel{} on the galaxy stellar mass
-          function. 
-          Dashed lines correspond to the SMF computed using \mcmodel{} as an estimate
-          of the total luminosity whereas solid lines correspond to the SMF computed
-          using the total luminosity from our 1-D profile. 
-          The impact on the SMF can exceed 0.2 dex for massive central galaxies 
-          living in halos larger than $\log (M_{\mathrm{halo}}/M_{\odot}) > 14.2$ 
-          (red lines).
-          \song{New figure for completeness; Need to update the caption}
+          Evaluation of the \mstar{} completeness of the HSC massive galaxy sample.
+          We compare the volume number density function of the massive galaxies 
+          for this work (black line) with the one of a much more complete sample
+          from the S82-MGC catalog (green line).  
+          The associated uncertainties derived from bootstrap resampling are shown in 
+          shaded regions. 
+          The vertical grey line highlight the \logms{}$=11.6$ limit.  
+          Below it, the HSC massive galaxy sample becomes significantly incomplete in 
+          stellar mass. 
           }

### 2017-05-25 draft/paper1_jenny.tex
Fig 6: Caption

@@
   \end{figure}     
-
 %% ------------------------------------------------------------------------------------ %%
@@
       \caption{
-          \song{Update caption.}
           Radial variations in ellipticity and optical colors for massive galaxies. 
-          The format of this figure is similar to the right hand side of 
-          Fig~\ref{fig:prof_1}. 
-          Top panels show the ellipticity profile, middle panels show $g-r$, and lower 
-          panels show $g-i$. 
+          The format of this figure is similar to Fig~\ref{fig:avg_prof}. 
+          \textbf{Left panel} shows the ellipticity profiles, 
+          \textbf{Upper-right panel} shows the $g-r$ color profiles, and 
+          \textbf{Lower-right panel} is for $g-i$ color profiles. 
           We compare our results with those from \citet{Tal2011} based on stacking 
           large samples of luminous red galaxies in SDSS at $z{\sim} 0.4$ 
-          (solid blue line on top panel). 
+          (solid red line on left panel). 
           We also compare with the results from a stacking analysis of nearby massive 
           galaxies with high concentration index ($C>2.6$) in 
-          \citet[][blue dash lines on the top and middle panels]{DSouza2014}. 
+          \citet[][blue dash lines on the left and upper-right panels]{DSouza2014}. 
           Finally, we also compare with the average $g-r$ and $g-i$ color profiles 
           from a large sample of nearby elliptical galaxies in \citet[][blue, solid 
-          lines on the middle and bottom panels]{LaBarbera2010}.
+          lines on both right panels]{LaBarbera2010}.
           }
@@
     halo mass.
-
-    \jenny{Could we add a panel to the plot showing the mass bins as above with the ellipticity profiles?}
 

### 2017-05-25 draft/paper1_jenny.tex
Fig 7: Caption

@@
       \caption{
-          \song{New figures to illustrate the assumption of in-situ and accreted mass;
-                Need to update the caption.}
+          \textbf{Left:}
           Comparison of the median \mden{} profiles of massive galaxies in the 
@@
           discovered by \citet[][Yellow, dashed]{Liu2013} in the Hubble 
-          Ultra-Deep Field.}
+          Ultra-Deep Field.
+          \textbf{Right:}
+          Relation between \mtot{} and the fraction of \mstar{} within 10 to 100 kpc, 
+          which is used here as proxy of the fraction of accreted stars. 
+          The typical uncertainties of \mtot{} and the mass fraction are shown in 
+          upper-left corner. 
+          This relation is compared with the relation between \mstar{} and the fraction
+          of accreted stars derived from the Illustris simulation at $z=0$ 
+          (Fig 4 in \citealt{RodriguezGomez2016}; grey solid and dashed lines). 
+          }
       \label{fig:discussion_1}
@@
       \caption{
-          \song{New figures to show the impact of mass definition on SMF. 
-                Need to update the caption.}
-          \textbf{Left}: Relation between \mtot{} and the logarithmic mass difference 
-          between \mmax{} and \mtot{} for both \rbcg{} (red square) and \nbcg{} 
-          (grey dot) galaxies.  The format is very similar to the left figure of 
-          Fig~\ref{fig:mass_complete}.~~
-          \textbf{Right}: The stellar mass volume-density distributions of massive 
+          \textbf{Left}: The stellar mass volume-density distributions of massive 
           galaxies after combining the \rbcg{} and \nbcg{} samples together, using 

### 2017-05-25 draft/paper1_jenny.tex
Fig 8: Caption

@@
       \caption{
-          \textbf{Left}: The stellar mass volume-density distributions of massive 
-          galaxies after combining the \rbcg{} and \nbcg{} samples together, using 
-          both \mtot{} (black solid line) and \mmax{} (black dash line). 
-          The uncertainty for distribution using \mtot{} is shown in grey shaded region.  
+          \textbf{Left:} Impact of using \mtot{} on the galaxy stellar mass function. 
+          Dashed lines correspond to the SMF computed using \mcmodel{} whereas solid 
+          lines correspond to the SMF computed using \mtot{}. 
+          Here we separate the HSC massive galaxies into the central galaxies living 
+          in halos more massive than \logmh{}$\sim14.2$ (red lines) and the ones in 
+          halos with \logmh{}$<14.0$ (black lines).
+          The impact on the SMF can exceed 0.2 dex for massive central galaxies in 
+          very massive halos.
+          \textbf{Right}: The stellar mass volume density distributions of massive 
+          HSC galaxies, using both \mtot{} (black solid line) and \mmax{} (black dotted 
+          line). 
+          The uncertainty of distribution using \mtot{} is shown in grey shaded 
+          region.  
           Here, we also compare the distributions with SMF from previous works: 
           (a): SDSS galaxies at $z{\sim} 0.1$ from \citet{Bernardi2013}; the \mstar{} 
-          is based on photometry from 2-D \ser{}$+$Exponential model fitting; 
+          is based on photometry from 2-D \ser{}$+$Exponential model fitting 
+          (purple); 
           (b): SDSS galaxies at $z{\sim} 0.1$ from \citet{Moustakas13} based on 
-          improved SDSS \texttt{cModel} photometry; 
+          improved SDSS \texttt{cModel} photometry (blue); 
           (c): \texttt{S82-MGC} galaxies at $0.15 < z< 0.43$ from 
-          \citet{Leauthaud2016} based on PSF-matched SDSS-UKIDSS photometry.
+          \citet{Leauthaud2016} based on PSF-matched SDSS-UKIDSS photometry (green).
           Please see text for more details of the comparison.

### 2017-05-25 draft/paper1_jenny.tex
Remove old Appendix A

@@
 
-\song{A few appendix need to be moved to Paper II}
-%% ------------------------------------------------------------------------------------ %%
-
-\section{A. Basic Statistical Properties of the Sample} 
-	\label{app:sedasic}
-
-    On the top-left panel of Fig~\ref{fig:sample_stats}, we show the \mtot{}-color 
-    relations using the $k$-corrected $g-r$ color. 
-    Both samples follow the same tight ``red-sequence'' with little contamination 
-    from the ``blue cloud''.
-    At fixed \mtot{}, we see little offset in color distributions of the two 
-    samples, suggesting that both samples consist of quiescent galaxies with 
-    similar average stellar population properties.  
-    This is consistent with previous result that suggests the average stellar 
-    population of massive central galaxy does not depend on \mhalo{} 
-    (e.g.\ \citealt{Park2007}).  
-    In this work, we focus on the \mstar{} range of $11.6 \le$\logmtot{}$\le 11.9$, 
-    where both samples have acceptable completeness, and their \mtot{} distributions 
-    greatly overlap (see the normalized distributions of \mtot{} in the bottom-left 
-    panel of Fig~\ref{fig:sample_stats}). 
-    As for the \minn{} distributions, the two samples overlap the most within 
-    $11.2 \le$\logmtot{}$\le 11.6$, but now they show quite different
-    distributions (bottom-right figure).
-
-    The redshift distributions also show small difference
-    (upper-right panel) even in the high-\mtot{} bin, where the redshift distribution 
-    of the \nbcg{} sample skews toward higher-$z$ end due to the contribution of BOSS 
-    spec-$z$.
-    Since this could bias the comparison of \mden{} profiles and other properties 
-    (please see Appendix\ref{app:redshift} for more details), we address this via matching 
-    the two samples in both mass and redshift distributions carefully
-    (see Appendix~\ref{app:match}).
-
-%% ------------------------------------------------------------------------------------ %% 
-  \begin{figure*}
-      \centering 
-      \includegraphics[width=16.5cm]{fig/redbcg_sample_stats}
-      \caption{
-          \textbf{Top-left}: The \logms{}-$g-r$ color relation of the \rbcg{} 
-          (red circle; detaield format is the same with the right panel of 
-          Fig~\ref{fig:mass_complete}) and \nbcg{} (grey dots) samples.
-          We apply the $k$-corrections from \texttt{iSEDFit} fitting to the colors.~~          
-          \textbf{Top-right}: the histograms of the redshift for the \rbcg{} and 
-          \nbcg{} galaxies in both \logmtot$>11.2$ and $11.6<$\logmtot{}$<11.9$
-          mass bins.
-          The vertical lines highlights the $0.3\leq z \leq 0.5$ redshift range.~~
-          \textbf{Bottom-left}: the histograms of \mtot{} for the \rbcg{} (orange-red) 
-          and \nbcg{} (grey-black) samples at both $z>0.2$ (step-filled histogram) and 
-          $0.3 \leq z \leq 0.5$ (stepped histogram). 
-          The vertical lines in both top-left and bottom-left figures highlight the 
-          $11.6<$\logmtot{}$<11.9$ mass range that will be used in the comparison of 
-          the \mtot{}-matched samples.~~
-          \textbf{Bottom-right}: the histograms of \minn{} in similar format. 
-          Here the vertical lines highlight the 
-          $11.2<$\logminn{}$<11.6$ mass range that is used for comparison.
-          \song{Update the caption}
-      }
-      \label{fig:sample_stats}
-  \end{figure*}
-%% ------------------------------------------------------------------------------------ %%
-
 %% ------------------------------------------------------------------------------------ %% 

### 2017-05-25 draft/paper1_jenny.tex
Remove irrelevant Appendix

@@
 %% ------------------------------------------------------------------------------------ %% 
-\section{B. Extraction of 1-D surface brightness profile} 
+\section{A. Extraction of 1-D surface brightness profile} 
     \label{app:ellipse}
@@
     objects around the target.
-    At the depth of the HSC images, this becomes a quite difficult task, especially 
-    for massive galaxies with extended outer profiles and more satellites. 
+    At the depth of the HSC images, this becomes a challenging task, especially 
+    for massive galaxies with extended outer profiles and many satellites. 
     Right now, the \texttt{hscPipe} tends to ``over-deblend'' around bright object, 
@@
 %% ------------------------------------------------------------------------------------ %% 
-\section{C. Estimate average {$M_{\star}/L_{\star}$} using \texttt{iSEDFit}} 
+\section{B. Estimate average {$M_{\star}/L_{\star}$} using \texttt{iSEDFit}} 
     \label{app:sed}
@@
 %% ------------------------------------------------------------------------------------ %% 
-\section{D. Comparison of \mden{} profiles using \mstar{} from the GAMA survey}
-    \label{app:gama}
-
-%% ------------------------------------------------------------------------------------ %% 
-\begin{figure*}
-    \centering
-    \includegraphics[width=\textwidth]{fig/redbcg_prof_gama_new}
-    \caption{
-        \textbf{Left:} comparison of \mstar{} estimated by the GAMA survey and 
-        the \mtot{} using HSC images in this work. 
-        We plot the \logmgama{} against the difference between \logmtot{} and \logmgama{}. 
-        The format is very similar to the left panel of Fig~\ref{fig:mass_complete}. 
-        The two vertical lines highlight the mass range $11.4 \leq$\logmgama{}$<11.8$ 
-        that is used for the comparison.~~
-        \textbf{Right:} we compare the \mden{} profiles of \rbcg{} (orange-red) and 
-        \nbcg{} (grey-black) galaxies using the samples matched on the 
-        \mgama{}-$z$ plane at $11.4 \leq$\logmgama{}$<11.9$ and $0.28 \leq z < 0.4$. 
-        The format is very similar to the ones in Fig~\ref{fig:prof_1}.}
-    \label{fig:gama}
-\end{figure*}
-%% ------------------------------------------------------------------------------------ %%
-
-    The GAMA survey greatly overlaps with the HSC survey, and it provides carefully 
-    measured \mstar{} for large sample of galaxies (\citealt{Taylor2011}) that help 
-    produce many interesting results (e.g. \citealt{Bauer2013, Ferreras2017}).
-    They use 2-D single-\ser{} model to correct the total luminosity of the galaxy 
-    (\citealt{Kelvin2012}), and derive the \m2l{} through optical-SED fitting 
-    (BC03 model; Chabrier IMF) based on the PSF-matched aperture photometry. 
-    Since the \ser{} model is generally more flexible than the \texttt{cModel} one, 
-    it is therefore interesting to compare with the \rbcg{} and \nbcg{} galaxies 
-    that also have spec-$z$ (at $z < 0.40$) and \mstar{} in GAMA DR2 
-    (\citealt{Liske2015}) and see the impact of deep photometry again.
-
-    We summarize the results in Fig~\ref{fig:gama}.  
-    On the left panel, we compare the differences between \mtot{} and \mgama{}. 
-    HSC survey on average recovers more \mstar{} at high-\mstar{} end, which is 
-    consistent with the expectation from deeper photometry, although the 
-    systematic differences in the estimates of \m2l{} could play a role here. 
-    Meanwhile, it is interesting see that, above \logmtot{}$> 11.8$, \mgama{} 
-    becomes increasingly larger than \mtot{}, and most of these massive 
-    galaxies have very high \ser{} index from the 2-D fitting. 
-    This suggests that the single-\ser{} model is no longer an appropriate one to 
-    describe very massive galaxies as it tends to over-estimate the \mstar{} the 
-    inner and/or outer regions.
-
-    To verify the cause of the difference in \mstar{}, we further select samples 
-    of \rbcg{} and \nbcg{} galaxies with matched \mgama{} and redshift 
-    distributions (at $11.4 <$\logmgama{}$<11.8$; see Appendix \ref{app:match}), 
-    and compare their \mden{} profiles (right panel). 
-    Although these two subsamples are equally massive according to results from 
-    GAMA survey, it is clear that the \rbcg{} galaxy has much more extended 
-    outer envelope, even though its median \mden{} profile is very similar 
-    to the \nbcg{} sample at $< 10$ kpc. 
-    We can reproduce very the same trend with the luminosity density profiles 
-    (with or without $k$-correction), suggesting that the inaccurate \ser{} 
-    model definitely leads to under-estimate of \mstar{}.
-
-%% ------------------------------------------------------------------------------------ %%
-
-\section{E. Comparisons of \mden{} profiles in different redshift bins}
-    \label{app:redshift}
-
-%% ------------------------------------------------------------------------------------ %% 
-\begin{figure}
-    \centering 
-    \includegraphics[width=8.2cm]{fig/redbcg_avg_prof_z}
-    \caption{
-        Comparison of \mden{} profiles of \rbcg{} (orange-red) and \nbcg{} 
-        (grey-black) at $11.6 \le$\logmtot$< 11.9$ in redshift bins of 
-        $0.3\leq z<0.4$ (solid lines) and $0.4\leq z<0.5$ (dash lines). 
-        We show the individual profile in the background using much thinner line, 
-        and highlight the median profiles using thicker line and darker color.
-        Other formats are exactly the same with the left figure of 
-        Fig~\ref{fig:avg_prof}.}
-    \label{fig:avg_prof_z}
-\end{figure}    
-%% ------------------------------------------------------------------------------------ %%
-
-    Given the redshift range for our samples, it is important to evaluate 
-    the impacts from the physical extend of seeing and the imaging depth on the \mden{} 
-    profiles at different redshift. 
-    Under the same seeing, the \mden{} profile of galaxy at higher-$z$ is more 
-    vulnerable to the PSF smearing effect at the center. 
-    It is also harder to reach to the same \mden{} level under the same imaging depth 
-    due to cosmological dimming and background noise.
-
-    In Fig~\ref{fig:avg_prof_z}, we group the \rbcg{} and \nbcg{} galaxies within 
-    $11.6 \le$\logmtot$< 11.9$ into two $z$ bins ($0.3\leq z<0.4$ and $0.4\leq z<0.5$),
-    and compare their \mden{} profiles. 
-    In two redshift bins, the median \mden{} profiles from the same sample follow each 
-    other very well outside 10 kpc, but become visibly different in the central 3-4 kpc,
-    where the effect from seeing kicks in. 
-    Meanwhile, the median \mden{} profiles of \rbcg{} and \nbcg{} in the same $z$ bin 
-    are identical in the central region, which indicates similar average seeing 
-    conditions.       
-    This confirms that \mden{} profile at $> 5$ kpc is safe from the impacts of seeing 
-    and difference in redshift.
-    More importantly, it also suggests that, once the redshift distributions are 
-    carefully matched, the difference of \mden{} profile is likely to be physical 
-    even in the central region.
-
-%% ------------------------------------------------------------------------------------ %%
-
-\section{F. Match the \rbcg{} and \nbcg{} samples in \mstar{} and redshift distributions}
-    \label{app:match}
-
-%% ------------------------------------------------------------------------------------ %% 
-\begin{figure*}
-    \centering 
-    \includegraphics[width=\textwidth]{fig/redbcg_match}
-    \caption{
-        \textbf{Left figure} shows the details of the \mtot{}-matching process, 
-        corresponding to the results shown in the left figure of   
-        On the top panel, we show the overall distributions of \rbcg{} (light orange boxes) 
-        and \nbcg{} (light grey dots) galaxies on the \mtot{}-$z$ plane.  
-        And, we match the two sample in the \mtot{}-$z$ space outlined by the shaded region.
-        We highlight the \rbcg{} galaxies in this region using bigger boxes in red frames, 
-        whose size reflects the $P_{\mathrm{Cen}}$ value.  
-        We also color-code them using the richness ($\lambda$) of the host cluster. 
-        The matched \nbcg{} galaxies are highlighted using darker color and bigger dots. 
-        To further evaluate the matching results, we show the distributions of \mtot{} 
-        (middle panel) and redshift (bottom panel) separately. 
-        On both panesl, we show the histograms along with their kernel density 
-        distributions.  
-        And, on the top of each panel, two sets of short vertical lines highlight the median 
-        value (solid) and the inter-quartile (dash) of each distribution.~~~
-        \textbf{Right figure} shows the similar matching results for the \minn{}-matched
-        samples used for the right figure of Fig~\ref{fig:prof_1}.
-        The format is exactly the same as the left one, except the \minn{} replaces the 
-        \mtot{} in the top and middle panels.}
-    \label{fig:match}
-\end{figure*}
-%% ------------------------------------------------------------------------------------ %%
-
-    As explained earlier, it is important to make sure the two samples have similar 
-    distributions in both \mstar{} and redshift before comparing their median \mden{} 
-    profiles.  
-    Here we briefly describe the procedure used in this work. 
-    Since the \rbcg{} sample is smaller in size, we always match the \nbcg{} sample to 
-    it by searching for the $N$-nearest neighbours on the $M_{\star}$-redshift plane 
-    using the KDTree algorithm in the \texttt{scikit-learn} Python library 
-    (\citealt{scikit-learn}), and evaluate the quality of the match using the 
-    distributions of both parameters (as shown in Fig~\ref{fig:match}).
-
-    As we only keep the unique \nbcg{} galaxies in the matched sample, we manually 
-    adjust the value of $N$ to achieve the best match. 
-    When the redshift distribution of the \rbcg{} sample becomes bi-model, we also try 
-    to split the sample into two redshift bins and match them separately. 
-    Typically $N$ is between 3 to 8.
-    In Fig~\ref{fig:match}, we demonstrate this procedure using the results for 
-    the \mtot{}-matched (Left) and the \minn{}-matched samples in Fig~\ref{fig:prof_1}
-    (Right), and the two samples are well matched in the distributions of \mtot{}
-    (or \minn{}) and redshift.  
-    For all the comparisons of \mden{} profiles in this work, we match the samples 
-    in the same way, and make sure the match has the same quality.
-
-%% ------------------------------------------------------------------------------------ %% 
-\section{G. Robustness of the \mden{} Differences} 
-	\label{app:robust}
-
-    In Fig~\ref{fig:prof_1}, we compare the \mden{} profiles of \mtot{}- and 
-    \minn{}-matched samples of \rbcg{} and \nbcg{} galaxies, and here we test the 
-    robustness of the results using a few extra tests that are illustrated in
-    Fig~\ref{fig:prof_2}, Fig~\ref{fig:prof_3}, and Fig~\ref{fig:prof_4}, and 
-    are briefly described here:
-
-    \begin{enumerate}
-
-        \item In Fig~\ref{fig:prof_2}, we group the samples into two \mtot{} bins. 
-            Given the small sample size, we extend slightly toward lower \mtot{} range 
-            ($11.5 \leq \log (M_{\star,\ 10\mathrm{kpc}}/M_{\odot}) < 11.7$ and 
-             $11.7 \leq \log (M_{\star,\ 10\mathrm{kpc}}/M_{\odot}) < 11.9$). 
-            Although the smaller sample leads to larger statistical uncertainties, 
-            we can still see similar structural differences in both \mtot{} bins, 
-            and the difference becomes more significant in the higher \mtot{} bin.  
-            For the lower \mtot{} bin, the difference in the inner region becomes 
-            quite uncertain, while the difference in the outskirt is still visible. 
-            This potentially suggests that the environmental dependence of structure 
-            also varies with \mstar{}, an important implication deserves more 
-            investigations in the future.
-
-        \item On the left panel of Fig~\ref{fig:prof_3}, we match the \rbcg{} and 
-            \nbcg{} samples in a lower redshift bins ($0.30 < z < 0.42$).
-            Despite the larger uncertainties due to smaller samples, we find the 
-            results are the same.
-
-        \item On the middle panel of Fig~\ref{fig:prof_3}, we includes \rbcg{} 
-            galaxies in poorer clusters ($20 < \lambda < 30$), which should result 
-            in overlapped \mhalo{} distributions with the \nbcg{} samples 
-            considering the typical uncertainty of $\lambda$.
-            This makes the difference in the inner region slightly less significant, 
-            but the overall results are the same.
-
-        \item On the right panel of Fig~\ref{fig:prof_3}, in stead of using \mtot{}, 
-            we use the \mmax{}--the maximum \mstar{} by integrating the \mden{} 
-            profiles to the largest radius allowed.  
-            The \mmax{} values are less reliable than \mtot{} due to the 
-            uncertainty of background subtraction and contamination from nearby 
-            bright objects, but they can serve as different estimates of the ``total''
-            \mstar{} of these galaxies.
-            As shown in Section~\ref{sec:discussion}, they on average increase
-            the \mstar{} by a little bit and affect the \rbcg{} more.
-            The differences in the \mden{} profiles still remain very similar.
-
-    \end{enumerate}
-
-    We also test the robustness of the \mtot{}-matched results using the samples with 
-    only spectroscopic redshift, the samples in the three GAMA fields, and the \rbcg{} 
-    samples without the ones in very massive halos ($\lambda > 40$).  
-    Limited by space, we do not show these results here, but they all verify the 
-    robustness of the results.
-
-    For the results from the \minn{}-matched samples:
-
-    \begin{enumerate}
-
-        \item
-            We match the two samples using both \minn{} and the \mstar{} within 15 kpc 
-            at the same time.  
-            This makes the two median \mden{} profiles very similar inside 10-15 
-            kpc, while the result in the outskirt remains the same (left panel of 
-            Fig~\ref{fig:prof_4}).
-            Use \mstar{} within 5 or 20 kpc leads to the same conclusion.
-
-        \item 
-            To make sure the two samples are comparable in their overall assembly history,
-            we also try to only include the very massive galaxies (\logmtot{}$>11.5$)
-            in both samples. 
-            This excludes the \nbcg{} galaxies that are much less massive and 
-            more ``compact'' in structure. 
-            Yet, the results regarding the structural differences remain the same.
-
-    \end{enumerate}
-
-%% ------------------------------------------------------------------------------------ %% 
-  \begin{figure*}
-      \centering 
-      \includegraphics[width=\textwidth]{fig/redbcg_prof_2}
-      \caption{
-          Comparisons of the \mden{} profiles for \mtot{}-matched \rbcg{} 
-          (orange-red) and \nbcg{} (grey-black) galaxies in lower (left; [11.5,11.70]) 
-          and higher (right; [11.7, 11.9]) \mtot{} bins. 
-          Other formats are in consistent with the right figure of Fig~\ref{fig:prof_1}.
-          The difference in median profiles is more significant in higher \mtot{} bin.
-          }
-      \label{fig:prof_2}
-  \end{figure*}
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %% 
-  \begin{figure*}
-      \centering 
-      \includegraphics[width=\textwidth]{fig/redbcg_prof_3}
-      \caption{
-        Comparisons of the \mden{} profiles for \rbcg{} (orange-red) and \nbcg{} 
-      	(grey-black) galaxies that are matched using proxies of total \mstar{}. 
-        The formats are in consistent with the right figure of Fig~\ref{fig:prof_1}.
-        The differences are, here, the samples are matched in slightly differnt ways. 
-        From left to right: a) using samples at lower redshift ($0.3 < z < 0.4$); 
-        b) using \rbcg{} sample with $\lambda > 20$ instead of 30; 
-        c) using \mstar{} within 150 kpc instead of 100 kpc.
-        The results are broadly consistent with the one in Fig~\ref{fig:prof_1}.
-        }
-      \label{fig:prof_3} 
-  \end{figure*}
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %% 
-  \begin{figure*}
-      \centering 
-      \includegraphics[width=\textwidth]{fig/redbcg_prof_4}
-      \caption{
-          Comparisons of the \mden{} profiles for \rbcg{} (orange-red) and \nbcg{} 
-          (grey-black) galaxies that are matched using the \mstar{} enclosed in the 
-          inner region. 
-          Left panel shows the results after matching the \minn{} and \meff{} together, 
-          and the right panel shows the results when only the \logmtot{}$\ge 11.5$
-          \rbcg{} and \nbcg{} galaxies are included.
-          Other formats are in consistent with the right figure of Fig~\ref{fig:prof_1}.
-          }
-      \label{fig:prof_4} 
-  \end{figure*}
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %% 
 %% Table.1 

### 2017-05-25 draft/paper1_jenny.tex
Edit Appendix A

@@
     for massive galaxies with extended outer profiles and many satellites. 
-    Right now, the \texttt{hscPipe} tends to ``over-deblend'' around bright object, 
-    we therefore perform \texttt{SExtractor}-like background subtraction and object 
-    detection using the \texttt{SEP} Python library to generate the necessary masks.
+    At this point, the \texttt{hscPipe} tends to over-subtract the background around 
+    bright objects.  
+    The performance of its deblending process is also not optimized for extended
+    objects. 
+    For these reasons, we perform \texttt{SExtractor}-like background subtraction and 
+    object detection using the \texttt{SEP} Python library to generate the necessary 
+    masks.
     Combining two different local background models and $S/N$ thresholds, we obtain 
-    the centroid, shape, and radius that enclose 90\% of flux for each object, even 
-    the one that is close to the center of bright galaxy (left panel of 
-    Fig~\ref{fig:ell_tech}), and generate its initial elliptical mask based on these
-    information. 
-    We first create the mask that covers all contaminating objects around the target 
-    after adaptively increasing the sizes of their masks according to their brightness 
-    and distance to the target center. 
-    Generally speaking, we mask out the very bright objects or objects in the 
-    outskirt of the target a little more aggressively as they could impact the 
-    low surface brightness regions more significantly. 
-    We also create masks that are less and more aggressive to test their impacts
-    on the surface brightness profiles.
-
-    Next, we aggressively mask out all objects on the cut-out image and use this mask
-    to evaluate the background level using the distribution of pixel values after 
-    median smoothing the masked image within $6x6$ pixels.
-    This provides us a global estimate of background level along with its uncertainty. 
-    Given the typical RMS of the background pixels, the HSC \texttt{WIDE} images 
-    should reach to $> 29$ \sb surface brightness level in $i$-band.  
-    However, the global background level is often negative around our massive 
-    galaxies, indicating systematic issue in background subtraction.  
-    In current \texttt{hscPipe}, the background on each CCD is modeled with a 
+    the centroid, shape, and radius that enclose 90\% of flux for each object, 
+    including the one that is very close to the center of bright galaxy (left panel of 
+    Fig~\ref{fig:ell_tech}). 
+    Based on these information, we then create the mask that covers all contaminating 
+    objects around the target after adaptively increasing the sizes of their masks 
+    according to their brightness and distance to the central target. 
+    Generally speaking, we mask out bright objects or objects in the outskirt of the 
+    image more aggressively to reduce their impact on the surface brightness profiles 
+    in the outskirt. 
+    We also create masks that are less and more aggressive than the default one to 
+    test their impacts on the surface brightness profiles.
+
+    Next, we aggressively mask out all objects on the cut-out image.  
+    We then evaluate the background level using the unmasked pixels after median 
+    smoothing the masked image using box of $6x6$ pixels.
+    This provides estimate of global background level along with its uncertainty. 
+    Given the typical background uncertainty, the HSC \texttt{WIDE} image should be 
+    able to reach down to $> 29$ \sb surface brightness level in the $i$-band.  
+    However, as mentioned, we often find evidence of slightly over-subtracted 
+    background for massive galaxies in our sample. 
+    In the current \texttt{hscPipe}, the background on each CCD is modeled with a 
     Chebyshev-polynomial that is fit to the smoothed image after excluding pixels 
@@
     This algorithm performs much better than the SDSS version 
-    (e.g.\ see \citealt{Blanton2011}), yet still over-subtracts sky around bright 
-    objects and results in unphysical truncation in the surface brightness profile.
-    We attempt to empirically correct this using the background model generated by 
+    (e.g.\ see \citealt{Blanton2011}), yet still over-subtracts background around 
+    bright objects and results in unphysical truncation in their surface brightness 
+    profiles.
+    We empirically correct this issue using the background model generated by 
     the \texttt{SExtractor} algorithm on the masked image 
@@
     This model can account for the slightly over-subtracted background at large scale,
-    and also reduces the impact from the low surface brightness ``wings'' of bright 
-    nearby objects. 
-    After the correction, we can see the improvement from both the remeasured global 
-    background value (closer to 0) and the surface brightness profile (middle panel 
-    of Fig~\ref{app:ellipse}; the negative intensity and the turn-over of the 
-    curve-of-growth in the outskirt of the ``Original'' profile are successfully 
-    corrected). 
-    Such ad hoc correction is not the best way to achieve accurate background 
-    subtraction, but the surface brightness profile within 100 kpc is not very
-    sensitive to the over-subtraction of sky as while.
-
-    The procedure to derive 1-D surface brightness profile from the 
+    and reduce the impact from the low surface brightness ``wings'' of bright 
+    neighbors. 
+    We clearly see improvement in both the distributions of background pixels 
+    (more symmetric distribution; median value is closer to 0) and the surface 
+    brightness profile (middle panel of Fig~\ref{app:ellipse}; the negative intensity 
+    and the turn-over of the curve-of-growth in the outskirt of the ``Original'' 
+    profile are successfully corrected) after this correction.
+    Also, it is worth mentioning that such correction does not often affect the 
+    surface brightness profile within 100 kpc.
+
+    The procedure used to derive 1-D surface brightness profile from the 
     background-corrected, contamination-masked images is already described in 
@@
     Generally speaking, the surface brightness profile is very robust against these
-    changes.  
+    changes, especially within 100 kpc. 
     On the right panel of Fig~\ref{fig:ell_tech}, we compare the surface brightness
@@
     parameters. 
-    The profile within 100 kpc is very stable, and the only meaningful difference 
-    we can spot is caused by the less aggressive object mask in the very outskirt.
+    The profile within 100 kpc is very stable, and the only noticable difference 
+    is caused by the less aggressive object-mask in the very outskirt.
 
     We should also mention that we run \texttt{Ellipse} allowing for more 
-    sophisticated shapes than a simple ellipse (4th Fourier modes that can make 
+    sophisticated shapes than simple ellipse (4th Fourier modes that can make 
     isophote more ``disky'' or ``boxy'', e.g.\ \citealt{Kormendy2009}) to fit the 
@@
     We also apply the isophotes from $i$-band images to other bands in 
-    ``force-photometry'' mode \texttt{Ellipse} run to get rough estimates of 
+    ``force-photometry'' mode \texttt{Ellipse} run to get initial estimates of 
     color profiles.  

### 2017-05-25 draft/paper1_jenny.tex
Fig A1: Caption

@@
             apertures with different colors) using slightly different criteria.~~
-            \textbf{Middle:}: The flux profile that is zoomed into the near-zero flux 
-            range (top panel), and the curve-of-growth of the magnitude for the example
-            massive galaxy.  
-            To highlight the importance of correcting sky background, we show the profiles 
-            using both images with (red, solid line) and without (black, dash line) 
-            ad-hoc background correction. 
+            \textbf{Middle:}: The zoom-in intensity profile around very low intensity 
+            value (top panel), and the curve-of-growth of the enclosed magnitude 
+            (bottom panel) of the example galaxy.  
+            To highlight the importance of background correction, we show the profiles 
+            using both images with (red, solid line) and without (black, dotted line) 
+            background correction. 
             On the top panel, besides the horizontal line that highlights the zero flux 
-            level, we also show the uncertainty of the sky background estimate via 
-            grey-shaded region.  
+            level, we also show the uncertainty of the sky background estimate using 
+            the grey-shaded region.  
             On the bottom panel, two horizontal lines indicate the magnitudes 
-            corresponding to total (solid) and half flux (dash) using the 
-            background-corrected profile. ~~
-            \textbf{Right:} compare the 1-D surface brightness profiles for the same 
-            example galaxy extracted using different mask 
+            corresponding to total flux (solid) and flux within 100 kpc (dash).~~
+            \textbf{Right:} compares the 1-D surface brightness profiles for the same 
+            example galaxy using different masks 
             (smaller masking region: red, dash line; larger masks: blue, dash line), 
-            or different \texttt{Ellipse} settings
+            or different \texttt{Ellipse} configurations
             (more aggressive pixel-clipping: cyan, dash line; 
@@
              using mean flux along the isophote instead of median: purple, dash line)
-            with the one using the default configuration (black, solid line).
+            with the default one (black, solid line).
             }

### 2017-05-25 draft/paper1_jenny.tex
Fig B1-3: Caption

@@
         \caption{
-            Left: example output figure from \texttt{iSEDFit} that shows the SED 
-        	fitting results. 
+            \textbf{Left:} Example of output figure from \texttt{iSEDFit} that shows 
+            the SED fitting results. 
             The open-boxes show the observed fluxes in 5-band, and the solid, blue-dots
@@
             $\chi^2$ of the best-fit model.~~~
-            Right: the Posterior distributions of a few key parameters.
-            From top-left to bottom right are: 1) stellar mass (\logms{}); 2) age of the 
-            population (mass and star-formation rate weighted) in Gyr; 3) star formation 
-            rate ($\log\ \mathrm{SFR}\ (M_{\odot}/\mathrm{yr})$; instant one and the one 
-            averaged over the previous 100 Myr; 4) stellar metallicity 
-            ($\mathrm{Z}/\mathrm{Z}_{\odot}$); 5) dust extinction ($\mathrm{A}_V$ in mag);
+            \textbf{Right:} the Posterior distributions of a few key parameters.
+            From top-left to bottom right are: 
+            1) stellar mass (\logms{}); 
+            2) age of the population (mass and star-formation rate weighted) in Gyr; 
+            3) star formation rate ($\log\ \mathrm{SFR}\ (M_{\odot}/\mathrm{yr})$; 
+            instant one and the one averaged over the previous 100 Myr; 
+            4) stellar metallicity ($\mathrm{Z}/\mathrm{Z}_{\odot}$); 
+            5) dust extinction ($\mathrm{A}_V$ in mag);
             6) birthrate parameter ($\log\ b$; averaged over previous 100 and 1000 Myr).
@@
         \caption{
-            \song{Update the caption.}
-            Relationships between \mstar{} and other stellar population 
-            parameters using the results from \texttt{iSEDfit}. 
-            The \textbf{left} figures are for the \rbcg{} sample, and the 
-            \textbf{righ}t ones are 
-            for the \nbcg{} sample. 
-            They are both color-coded using the redshift of the object, while 
-            their sizes reflect the magnitude differences in $i$-band between 
-            the observed and best-fit value. 
+            Relationships between \mstar{} and key stellar population parameters from 
+            \texttt{iSEDfit}. 
             The four stellar population properties are: 
-            1) \textbf{Top-left}: mass-weighted stellar age in Gyr; 
-            2) \textbf{Bottom-left}: \m2l{} in $i$-band; 
-            3) \textbf{Top-right}: mass-weighted stellar metallicity in unit of Solar 
-            value;
-            4) \textbf{bottom-right}: dust extinction values in magnitude.
+            1) \textbf{Top-left}: \mstar{}-weighted stellar population age in Gyr; 
+            2) \textbf{Bottom-left}: SFR-weighted age in Gyr; 
+            3) \textbf{Top-right}: \mstar{}-weighted stellar metallicity in unit of 
+            Solar value;
+            4) \textbf{bottom-right}: dust extinction value in $V$-band.
+            As expected, most of the HSC massive galaxies are old, metal-rich, and 
+            dust-free. 
             }
@@
         \caption{
-            \song{Update the caption.}
             Comparisons of \mstar{} estimated by \texttt{iSEDFit} using different
-            assumptions. 
-            In each figure, we plot the \mstar{} from default model against their 
+            model assumptions. 
+            In each figure, we plot the \mstar{} from the default model against the
             differences with other models. 
-            The top (bottom) row shows the comparisons of the \rbcg{} (\nbcg{}) sample. 
-            The four models involved here are labeled as: 
-            (A): default one; 
-            (B): using the Salpeter IMF instead of the Chabrier one 
-                (\textbf{Left column});
-            (C): using the BC03 synthetic population model instead of the FSPS one
-                (\textbf{Middle column});
-            (D): assume that there is no dust extinction (\textbf{Right column}). 
-            On each figure, the grey shaded region highlights the uncertainty 
-            of the $\log($\logms{}$)$ using typical \mstar{} uncertainties from 
-            both sides. 
-            For each comparison, we highlight the median $\chi^{2}$ value, and the fraction
-            of galaxies with $\chi^{2} > 10.0$ at the top. 
-            We also show the histogram of the \mstar{}-differences on the right panel.
+            The four models involved are labeled as: 
+            (A): Default model; 
+            (B): Using the Salpeter IMF instead of the Chabrier one 
+                (\textbf{Top panel});
+            (C): Using the BC03 synthetic population model instead of the FSPS one
+                (\textbf{Middle panel});
+            (D): No dust extinction (\textbf{Bottom panel}). 
+            On each panel, the grey shaded region highlights the typical uncertainty 
+            of the $\log($\logms{}$)$.            
+            For each pair of models, we highlight their median $\chi^{2}$ values and 
+            the fraction of galaxies with $\chi^{2} > 10.0$ at the top. 
+            On each panel, we also show the histograms of the \mstar{}-differences on 
+            the right side.
             }

### 2017-05-25 draft/paper1_jenny.tex
Edit Appendix B

@@
     of the key parameters.
+
     Although we only use the best-fit \m2l{} in this work, it is necessary to make 
@@
     derived by \texttt{iSEDFit} in Fig~\ref{fig:ised_2}. 
-    Although degeneracies among these parameters are almost inevitable using only 
-    five broad-band photometry, most massive galaxies in both \rbcg{} (left) and 
-    \nbcg{} (right) samples have old age, high metallicity ($1.5 \times Z_{\odot}$ is 
-    the highest metallicity allowed by the adopted \texttt{FSPS} SSP models), and low 
-    dust extinction as expected
+    Degeneracies among these parameters are inevitable based on only five broad-band
+    photometry, but as expected, most massive galaxies show old stellar age, high
+    stellar metallicity ($1.5 \times Z_{\odot}$ is the highest metallicity allowed by 
+    the adopted \texttt{FSPS} SSP models), and low dust extinction.
 
@@
     between 0.03 to 0.3 Gyr; and the mass fraction formed in the burst is from 
-    a logarithmic distribution between 0.01 and 1.0.} do not affect the results. 
-    On the other hand, the choices of SSP model, IMF, and dust extinction do impact
-    the SED fitting results systematically, and we explore it using a few 
+    a logarithmic distribution between 0.01 and 1.0.} rarely affect the \mstar{}. 
+    But he choices of SSP model, IMF, and dust extinction do systematically impact
+    the estimates of \mstar{}, and therefore we look into this with a few 
     additional tests (see Fig~\ref{fig:ised_3}):
@@
         \item Choosing the \citet{Salpeter1955} IMF results in systematically 
-            higher \mstar{} (on average $+0.25$ dex of \logms{}) for both \rbcg{}
-            and \nbcg{} galaxies (Left panels).
+            higher \mstar{} (on average $+0.25$ dex of \logms{}) for these massive 
+            galaxies (top panel).
             Although there are multiple lines of evidence that favor Salpeter 
@@
             with lower \mstar{} in the sample, and to be as consistent as possible 
-            with a few previous works.  
+            with previous works.  
             This choice of IMF does not change the main results qualitatively.
@@
         \item \mstar{} based on the \texttt{BC03} models are systematically lower 
-            than the ones based on \texttt{FSPS+MILES} models (middle panels)
+            than the ones based on \texttt{FSPS+MILES} models (middle panel)
             The difference shows a large scatter, and can be as large as 0.4 dex,
-            although it does show any \mstar{} dependency. 
-            We notice that the \texttt{BC03} provides better overall ${\chi}^2$. 
-            This could relates to the higher upper limit of stellar metallicity 
-            ($2 \times \mathrm{Z}_{\odot}$) allowed by the \texttt{BC03} model 
-            that help fit the shape of the SED in the red-end better.  
-            However, the \texttt{BC03} model could underestimate the 
-            stellar age for a fraction of massive galaxies ($< 3$--4 Gyrs), and 
-            leads to underestimate of  \m2l{} for them too.
+            although it is not \mstar{}-dependent. 
+            The \texttt{BC03} results show better average ${\chi}^2$ than the 
+            \texttt{FSPS} ones. 
+            This relates to the higher upper-limit of stellar metallicity 
+            ($2 \times \mathrm{Z}_{\odot}$) allowed by the \texttt{BC03} model, 
+            which help fits the shape of the SED in the red-end slightly better.  
+            However, the \texttt{BC03} results also show puzzlingly low stellar 
+            ages ($< 3$--4 Gyrs) for these massive, red galaxies. 
+            This could also lead to underestimated \m2l{} values.
             It is worth noting that, both \texttt{FSPS} and \texttt{BC03} 
-            models still have difficulties recovering SED at the red-end (between $z$ 
-            and Y-band), and reproducing the optical color-color relations for 
-            red-sequence galaxies (e.g.\ \citealt{MIUSCAT2}).
+            models still have difficulties recovering SED at the very red-end 
+            (between $z$ and $y$-band), and reproducing the optical color-color 
+            relations for red-sequence galaxies (e.g.\ \citealt{MIUSCAT2}).
             In this work, we decide to keep using the \texttt{FSPS+MILES} model as 
             the fiducial one.  
-            However, using the results based on \texttt{BC03} model will not 
-            only change the main conclusions here, but also results in more 
-            significant differences in the median \mden{} profiles.
-
-        \item On the right panels of Fig~\ref{fig:ised_3}, we also compare with the
+            Using results based on \texttt{BC03} model will not change any of our 
+            conclusions here.
+
+        \item On the bottom panel of Fig~\ref{fig:ised_3}, we compare with the
             SED fitting results without considering the dust extinction. 
             This choice leads to slightly smaller \mstar{} values as expected. 
-            The impact is very small for the \rbcg{} galaxies, and becomes larger 
-            at the low-\mstar{} end of the \nbcg{} sample. 
-            But it still will not change any of the important results in this work.
+            Its impact becomes slightly larger at lower \mstar{} end. 
+            It will not change any of our conclusions here.
 

### 2017-05-25 draft/paper1_jenny.tex
Edit Introduction

@@
 
-    \update{
     Massive galaxies are important to our understanding of galaxy formation, and 
@@
     of galaxy formation.
-    }
 
@@
 
-    Massive galaxies are unique laboratories for studying both cosmology and galaxy 
-    formation. 
+    Massive galaxies are fascinating objects that have experienced complex assembly 
+    process and dramatic evolution.  
+    They are crucial for both cosmology and the study of galaxy formation. 
     Simulations of structure formation within the context of the $\Lambda$-CDM 
@@
     Observationally, the progenitors of ETGs are thought to correspond to the 
-    so-called ``red nuggets'' (e.g. \citealt{Damjanov2009}) which have smaller 
-    effective radii ($R_{\mathrm{e}}$; e.g. \citealt{Trujillo2006, vanDokkum2008, 
-    Cimatti2008}), slightly higher central velocity dispersion and stellar mass 
-    density (\mden{}; e.g. \citealt{vandeSande2011, Belli2014}), and more disk-like 
-    morphologies (e.g. \citealt{vanderWel2011}) than their local descendants 
-    (e.g. \citealt{Bezanson2009, vanDokkum2010}).
+    population of massive quiescent galaxies at high redshift that have smaller 
+    average effective radii ($R_{\mathrm{e}}$; e.g. \citealt{Trujillo2006, 
+    vanDokkum2008, Cimatti2008}), slightly higher central velocity dispersion and 
+    stellar mass density (\mden{}; e.g. \citealt{vandeSande2011, Belli2014}), and 
+    more disk-like morphologies (e.g. \citealt{vanderWel2011}) than their local 
+    descendants (e.g. \citealt{Bezanson2009, vanDokkum2010}) with similar stellar 
+    mass.
 
@@
     (e.g. \citealt{Sijacki2007, Fabian2012}) efficiently quench star formation in 
-    massive galaxies and a large fraction of these massive progenitors become 
-    quiescent at $z>1$ (e.g. \citealt{Bezanson2009, Kriek2016}). 
-    The second phase in the ``two-phase'' formation scenario is driven by 
-    non-dissipative processes such as dry mergers with other galaxies 
-    (e.g. \citealt{Naab2006, Khochfar2006}). 
-    \update{
-    To explain the observed significant increase of $R_{\mathrm{e}}$ (e.g. 
+    massive galaxies. 
+    A large fraction of these massive progenitors became quiescent at $z>1$ 
+    (e.g. \citealt{Bezanson2009, Kriek2016}). 
+    The second phase of their assembly is driven by non-dissipative processes such 
+    as dry mergers with other galaxies (e.g. \citealt{Naab2006, Khochfar2006}). 
+    To explain the observed increase of $R_{\mathrm{e}}$ (e.g. 
     \citealt{Newman2012, vdWel2014}) as well as the build-up of the outer stellar 
@@
     Laporte2013}).
-    Both numerical simulation (e.g. \citealt{Oser2010}) and 
-    semi-analytic modeling (SAM; e.g. \citealt{LeeYi2013, LeeYi2017}) agree that the 
+    Both numerical simulations (e.g. \citealt{Oser2010}) and 
+    semi-analytic models (SAM; e.g. \citealt{LeeYi2013, LeeYi2017}) agree that the 
     mass fraction in the accreted component should increase with total stellar mass, 
-    although details still differ between models (e.g. \citealt{Lackner2012, Cooper2013, Qu2017}).
-    According to recent results from the Illustris \footnote{
+    despite their technical differences (e.g. \citealt{Lackner2012, Cooper2013, 
+    Qu2017}).
+    For instance, recent result from the Illustris \footnote{
     \texttt{http://www.illustris-project.org/}} simulation 
-    (\citealt{Vogelsberger2014}, \citealt{Genel2014}), the fraction of  
-    accreted mass increases significantly with total stellar mass at \logms{}$>11.0$, 
+    (\citealt{Vogelsberger2014}, \citealt{Genel2014}) predicts that the fraction of  
+    accreted stars increases significantly with total stellar mass at \logms{}$>11.0$, 
     and the accreted component starts to dominate the stellar mass budget 
     ($f_{\mathrm{accreted}}>0.5$) at \logms{}$>11.5$ (\citealt{RodriguezGomez2016}).
-    }
-%% ------------------------------------------------------------------------------------ %%
-
-    \update{
+%% ------------------------------------------------------------------------------------ %%
+
     Given the success of this two-phase scenario in explaining trends like overall size 
-    growth, it is time to confront their predictions with additional observations using 
-    local galaxy mass profiles. 
-    Some progress has been made. 
-    One-dimensional analysis has shown that a \ser{} law well-describes the surface 
-    brightness (or stellar mass density) profiles of most nearby massive elliptical 
-    galaxies (e.g. \citealt{Kormendy2009}; except for the most central region), with 
-    the \ser{} index increasing with total luminosity (e.g. \citealt{Graham2013}).
-	But, the situation may be more complicated, with a suggestion from 
-	\citet{Schombert2015} that there are actually two families of light profiles. 
+    growth, it is time to confront their predictions with additional observations, 
+    especially the detailed profiles of surface mass density and shape for low redshift 
+    massive galaxies.  
+    Early one-dimensional analysis of nearby massive ETGs suggest that the 
+    single-\ser{} profile can describe their surface brightness (or surface mass 
+    density) profiles reasonably well (e.g. \citealt{Kormendy2009}; except for the
+    most central region), with the \ser{} index increasing with total luminosity 
+    (e.g. \citealt{Graham2013}).
+	However, the situation is in fact more complicated, with a suggestion from 
+	\citet{Schombert2015} that there are actually two families of light profiles:
+	the ones that follow single-\ser{} law well and the ones show significant 
+	deviation.
 	Two-dimensional analysis, meanwhile, finds that the stellar distributions 
-    of massive ETGs are better fit by multiple-component models 
+    of massive ETGs are often better fit by multiple-component models 
     (e.g. \citealt{Huang2013a, Oh2017}). 
-    To really confront the two-phase model requires very deep observations for large 
-    samples of massive ETGs to correctly estimate their total stellar mass 
-    (e.g. \citealt{Bernardi2013, DSouza2014}) and study their assembly history via 
-    their accreted halos (e.g. \citealt{Capaccioli2015, Iodice2016, Iodice2017}).
+    \citet{Huang2013b} further suggests a connection between the multi-component 
+    nature of massive galaxies and their two-phase assembly history. 
+    To further confront the two-phase scenario requires very deep observations of 
+    large samples of massive ETGs to correctly estimate their total stellar mass 
+    (e.g. \citealt{Bernardi2013, DSouza2014}) and explore their assembly history via 
+    their extended, accreted halos (e.g. \citealt{Capaccioli2015, Iodice2016, 
+    Iodice2017}).
     Currently, such work is limited by the depth of imaging from large-area surveys 
     such as the Sloan Digital Sky Survey (SDSS; e.g. \citealt{SDSSDR7, SDSSDR12}) or
-    the small area of deeper imaging. 
-    }
-
-    In this paper, we take advantage of new high-resolution (median 
+    the small sample size of massive galaxies with deep images.
+
+    In this paper, we take advantage of new high-quality (median 
     FWHM${\sim} 0.6^{\arcsec}$ in $i$-band) and deep ($i$-band surface brightness 
-    limit $> 28.5$\sb) imaging from the Hyper-Suprime Cam (HSC) Subaru Strategic 
+    limit $> 28.5$\sb) images from the Hyper Suprime-Cam (HSC) Subaru Strategic 
     Program \citep[SSP,][]{HSCDR1} to characterize the outer parts of massive galaxies 
@@
     large radii. 
-    \update{
     With the help of reliable spectroscopic and photometric redshift 
@@
     we select a large sample (${\sim} 7000$) of massive central galaxies at 
-    $0.3 < z < 0.5$ using ${\sim} 100$ square degree of data from the 
-    HSC wide layer. 
+    $0.3 < z < 0.5$ using ${\sim} 100$ deg$^2$ of data from the HSC wide layer. 
     In this paper, we use this sample to 
-    (a) measure individual \mden{} profiles for galaxies out to 100 kpc reliably with 
-    the HSC data, 
-    (b) examine the implications for the stellar mass function (SMF) when the outer 
-    parts of galaxies are accounted for, and
-    (c) investigate the dependence of their outer envelopes on stellar mass.    
+    (a) reliably measure individual surface mass density (\mden{}) profile of 
+    massive galaxy out to 100 kpc, 
+    (b) investigate the dependence of their outer stellar halos on total stellar 
+    mass, and 
+    (c) examine the implications for the stellar mass function (SMF) when the outer 
+    halos of massive galaxies are accounted for.   
     In a second paper in this series, we will further look into the potential 
     environmental dependence of structures in massive ETGs (Huang\etal in prep.).
-    }
-
-    %\jenny{I suggest removing this here. I do not think it belongs in the Intro:
-    %Motivated by the ``two-phase'' scenario, and also due to the difficulty in 
-    %providing appropriate model to describe the \mstar{} distribution of massive 
-    %galaxy from its center to the very outskirt, we focus on \mstar{} within two 
-    %different physical apertures in this work:}
-    %\song{Since the original paper is quite long and complicated, we decide to define
-    %the two aperture masses in the beginning, and explain why they are important.
-    %For the new draft, I think it is Ok to do this later, but more comments on this 
-    %are welcomed!}
-
-%    \begin{itemize}
-%    
-%        \item The stellar mass within 10 kpc (hereafter noted \minn{}). 
-%            According to the two-phase scenario, the ``in-situ'' star-formation quickly 
-%            builds up the inner, dense core of massive ETGs.  
-%            Based on recent observations and simulations (e.g.~\citealt{vanDokkum2010}; 
-%            \citealt{RodriguezGomez2016}), the in-situ component of massive ETGs is 
-%            mostly contained within one effective radius ($R_{\mathrm{e}}$, or 5-10 kpc). 
-%            We use \minn{} as a proxy for the mass forged during the ``in-situ''
-%            phase. 
-%            Given the quality of the HSC data, we can reliably measure \minn{} over our 
-%            redshift range ($1.0^{\arcsec}$ in radius equals 4.4 and 6.1 kpc at redshift
-%            0.3 and 0.5).  
-%            
-%        \item The stellar mass within 100 kpc (hereafter noted \mtot{}). 
-%            For our galaxy sample, a 100 kpc aperture corresponds to 5-10 
-%            $\times R_{\mathrm{e}}$. 
-%            We show in section \ref{ssec:mtotal} that most of the mass for these ETGs 
-%            can be captured by a 100 kpc radius and that \mtot{} is a good proxy for the 
-%            ``total'' \mstar{}. 
-%            Although not perfect, we argue that our measurements of \mtot{} (which are 
-%            actually measuring the light directly out to 100 kpc) are a better tracer 
-%            of total \mstar{} than model-dependent results from shallower data 
-%            (such as SDSS) which rely on extrapolating the light profiles of galaxies 
-%            out to large radii.
-%            
-%       \end{itemize}}
-%% ------------------------------------------------------------------------------------ %%
 
@@
 
-    %$M_{\mathrm{halo}}$ denotes halo mass in general whereas $M_{\rm 200b}$ is 
-    %explicitly defined as $M_{\rm 200b}\equiv M(<r_{\rm 200b})=200\bar{\rho} 
-    %\frac{4}{3}\pi r_{\rm 200b}^3$ where $r_{\rm 200b}$
-    %is the radius at which the mean interior density is equal to 200 times
-    %the mean matter density ($\bar{\rho}$).
+    $M_{\mathrm{halo}}$ denotes halo mass in general whereas $M_{\rm 200b}$ is 
+    explicitly defined as $M_{\rm 200b}\equiv M(<r_{\rm 200b})=200\bar{\rho} 
+    \frac{4}{3}\pi r_{\rm 200b}^3$ where $r_{\rm 200b}$
+    is the radius at which the mean interior density is equal to 200 times
+    the mean matter density ($\bar{\rho}$).
 

### 2017-05-25 draft/paper1_jenny.tex
Edit HSC camera subsection

@@
     The ambitious multi-layer HSC survey takes advantage of the large field of 
-    view (FoV;~1.5 deg in diameter) of this camera and will cover ${\sim} 1400$ deg$^2$ 
-    in 5 broad bands ($grizY$) to a limiting depth of $r {\sim} 26$ mag 
+    view (FoV;~1.5 deg in diameter) of this camera and will cover $>1000$ deg$^2$ 
+    of sky in 5 broad bands ($grizy$) to a limiting depth of $r {\sim} 26$ mag 
     in the \texttt{WIDE} layer. 
@@
 
-    The HSC \texttt{WIDE} survey is about $3.0$-$4.0$ magnitudes deeper in the $i$-band 
-    than SDSS. 
+    The HSC \texttt{WIDE} survey is about $3.0$-$4.0$ magnitudes deeper in the 
+    $i$-band surface brightness limit than SDSS. 
     Combined with the excellent imaging resolution (the median $i$-band seeing is 
-    0.6\asec), and the wide area, the HSC survey represents a tremendous dataset to 
-    perform large statistical study of the surface brightness profiles of ETGs out to 
-    large radii.     
+    0.6\asec) and the wide area, the HSC survey represents a tremendous dataset to 
+    perform large statistical study of the surface brightness profiles of massive
+    galaxies out to their very outskirts.     
     Fig~\ref{fig:sdss_compare} illustrates the quality of HSC imaging compared to SDSS 

### 2017-05-26 draft/paper1_jenny.tex
New figure 3

@@
 %% ------------------------------------------------------------------------------------ %% 
+  \begin{figure*}
+      \centering 
+      \includegraphics[width=\textwidth]{fig/redbcg_mass_diff_new}
+      \caption{              
+          \textbf{Left:} Difference between \mcmodel{} and \mtot{} for massive
+      	  galaxies (grey dots).
+      	  The running-median of the mass differences along with the standard deviations
+      	  in a series of mass bins are shown in large red, hexagons with error bars. 
+          On average, \mcmodel{} underestimates the total stellar mass of massive 
+          galaxies by 0.1 dex while in some cases, the difference can exceed 0.2 dex.
+          Vertical histograms indicate the mass difference for all galaxies (shaded 
+          histogram) and for the ones with \logmtot{}$>11.6$ (empty histogram).
+          \textbf{Right:} Difference between \mmax{} and \mtot{} in the same format. 
+          The average difference is small (0.02 dex) and does not show 
+          clear mass--dependence. 
+          }
+      \label{fig:mass_diff}
+  \end{figure*}
+
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
 \subsection{Initial Massive Galaxy Sample}
@@
 %    live in massive halos.
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %% 
-  \begin{figure}
-      \centering 
-      \includegraphics[width=\columnwidth]{fig/redbcg_mass_diff}
-      \caption{              
-          \textbf{Top:} Difference between \mcmodel{} and \mtot{} for massive
-      	  galaxies (grey dots).
-      	  The running-median of the mass differences along with the standard deviations
-      	  in a series of mass bins are shown in large red, hexagons with error bars. 
-          On average, \mcmodel{} underestimates the total stellar mass of massive 
-          galaxies by 0.1 dex while in some cases, the difference can exceed 0.2 dex.
-          Vertical histograms indicate the mass difference for all galaxies (shaded 
-          histogram) and for the ones with \logmtot{}$>11.6$ (empty histogram).
-          \textbf{Middle:} Difference between \mmax{} and \mtot{} in the same format. 
-          The average difference is small (0.02 dex) and does not show 
-          clear mass--dependence. 
-          \textbf{Bottom:} Difference between the \mtot{} and \mgama{} in the same
-          format.  
-          Here \mgama{} is based on single-\ser{} model derived from SDSS images. 
-          }
-      \label{fig:mass_diff}
-  \end{figure}
-
 %% ------------------------------------------------------------------------------------ %%

### 2017-05-29 draft/paper1_jenny.tex
Edit basic data reduction

@@
 
-    The Subaru Strategic Program (SSP, \citealt{MiyazakiInPrep}) makes use of the new 
-    prime-focus camera, the Hyper Suprime-Cam (HSC;~\citealt{Miyazaki2012}), on the 
+    The Subaru Strategic Program (SSP, \citealt{HSC_SSP, HSC_DR1}) makes use of the 
+    new prime-focus camera, the Hyper Suprime-Cam (HSC;~\citealt{Miyazaki2012}), on the 
     8.2-m Subaru telescope at Mauna Kea. 
@@
 
-    The full details of the HSC data processing can be found in \citet{BoschInPrep}
+    The full details of the HSC data processing can be found in \citet{Bosch2017}
     and are briefly summarized here. 
@@
     For each galaxy, \texttt{hscPipe} measures a \cmodel{} magnitude using an approach 
-    that is similar to SDSS (\citealt{BoschInPrep}). 
+    that is similar to SDSS (\citealt{Bosch2017}). 
     However, as opposed to SDSS, the HSC \cmodel{} is based on forced photometry which 
@@
     The performance of this algorithm has been tested using synthetic objects 
-    (\citealt{SynPipeInPrep}), and the results indicate that, generally speaking, 
+    (\citealt{SynPipe}), and the results indicate that, generally speaking, 
     the HSC \cmodel{} photometry is accurate down to $i >25.0$ mag.  
@@
     under-estimation of the the total flux of massive ETGs (this is discussed further in 
-    \citealt{BoschInPrep}).  
+    \citealt{Bosch2017}).  
     For these reasons, our results will be based on custom developed code to measure 
@@
     define a sample that includes almost all \logms{}$\geq 11.5$ galaxies.    
-    We therefore select our initial sample to be brighter than 
-    $i_{\mathrm{HSC, cModel}} \leq 21.5$\footnote{We neglect small differences between 
-    the response curves of SDSS-$i$ and HSC-$i$ filters.}
+    We therefore made a conservative selection of initial sample of massive galaxies
+    with $i_{\mathrm{HSC, cModel}} \leq 21.5$\footnote{We neglect small differences
+    between the response curves of SDSS-$i$ and HSC-$i$ filters.}
     and also limit our sample to regions that have reached the required depth of 
@@
     spectroscopic redshifts (e.g.\ SDSS/BOSS; GAMA). 
-    The spec-z quality flag from different catalogs are homogenized into a single 
+    The spec-$z$ quality flag from different catalogs are homogenized into a single 
     flag that indicates secure redshifts.}.  
@@
 
-    \update{
     Objects without a spectroscopic redshift are matched with the central 
@@
     for the goal of this work.
-    }
     The \redm{} catalog provides an additional 133 unique redshifts for massive 
@@
     Among them, the BOSS and SDSS ``legacy'' LRG samples provide the majority of 
-    spec-$z$. 
-    Before we can define our mass-complete sample of central galaxies required for 
+    spec-$z$. and the GAMA survey provides additional $14$\% of spec-$z$.
+    We choose the redshift range of $0.3 \leq z \leq 0.5$ to make sure that 
+    (1) The inner region of massive galaxies can be resolved, and \mstar{} within 
+    10 kpc can be reliably measured; 
+    (2) The background noise and cosmological dimming are not major issues and the 
+    \mden{} profile can be measured out to $>100$ kpc; 
+    (3) Evolution in structure and stellar population properties can be largely 
+    ignored.  
+    At both lower and higher redshift, the completeness of spec-$z$ sample starts 
+    to decline.  
+    Also for bright galaxies at lower redshift, the over-subtraction of background 
+    becomes a more serious issue. 
+    Before we can define our mass-complete sample of massive galaxies required for 
     our analysis, we describe our one-dimensional photometric analysis 
@@
     forced-photometry method that takes the PSF convolution into account
-    (e.g. \citealt{SynPipeInPrep}).
+    (e.g. \citealt{SynPipe}).
 

### 2017-05-29 draft/paper1_jenny.tex
Edit 1-D profile

@@
 %    %% Saved as "dr1_nonbcg_use_sed5b.fits"
-%    % TODO: The actual number waits to be updated}
 %    
@@
 
-    Massive ETGs imaged at the depth of HSC are not well modeled by the de~Vaucouleurs
-    or \ser law. 
-    These models will fail to simultaneously describe the profile in both the inner and 
-    the outer regions and also cannot account for any radial variations in ellipticity 
-    and position angle. 
+    The surface brightness profile of massive ETG can not be well modeled by the 
+    de~Vaucouleurs or single-\ser law, especially at the imaging depth of HSC.
+    These models will fail to simultaneously describe the profile in both the inner 
+    and the outer regions and also cannot account for any radial variations in 
+    ellipticity and position angle. 
     In principle, massive galaxies can still be described by more complex 
@@
     degeneracies among different parameters. 
-    Background subtraction uncertainty also affects the 2-D model fitting dramatically, 
-    especially for massive ETGs in our sample. 
+    Background subtraction uncertainty also affects the 2-D model fitting 
+    dramatically, especially for massive ETGs in our sample. 
     We therefore perform elliptical isophote fitting using the IRAF \texttt{Ellipse} 
@@
     This 1-D method we adopt is less affected by the issues mentioned above. 
-    Also, we will only study galaxies in the radial range where we are not sensitive 
-    to either the PSF ($r<3-5$ kpc) or the background subtraction ($r>100$ kpc).
+    Also, we will only study galaxies in the radial range where we are not 
+    sensitive to either the PSF ($r<3-5$ kpc) or the background subtraction 
+    ($r>100$ kpc).
 
     We prepare large $i$-band cut-outs for each galaxy that extend to 750 kpc in 
-    radius, along with a bad pixel mask, and the PSF model. 
+    radius, along with a bad pixel mask and the PSF model. 
     These cut-outs include all of the light of the galaxy and are large enough to 
@@
     because they have better seeing and much lower background levels than the $z$ 
-    and Y band images (although these in principle may be better tracers of \mden{}).
-
-    For each cut-out, to overcome the \texttt{hscPipe} ``over-deblending'' issue, we 
-    use a customized procedure to detect and appropriately mask out neighbouring 
-    objects. 
+    and $y$ band images (although these in principle may be better tracers of 
+    \mden{}).
+
+    For each cut-out, to overcome the \texttt{hscPipe} ``over-deblending'' issue, 
+    we use a customized procedure to detect and aggressively mask out
+    neighbouring objects. 
     Furthermore, \texttt{hscPipe} tends to over-subtract the background around 
     bright objects. 
-    To correct for this over-subtraction, we first aggressively mask all objects 
-    (including the central massive galaxy), and derive an empirical background 
-    correction using \texttt{SExtractor}.
+    To improve the background subtraction, we first aggressively mask 
+    out all objects (including the central massive galaxy), and derive an 
+    empirical background correction using \texttt{SExtractor}.
     Then, we run \texttt{Ellipse} on the background-corrected, masked cut-outs 
@@
     Beyond that, some of our profiles shows signs of truncation and/or large 
-    fluctuations which are due to the uncertainty in the background subtraction. 
+    fluctuations which are due to either the uncertainty in the background 
+    subtraction or the unmasked flux from other objects.
     We choose to limit our study to surface brightness levels up to ${\sim} 28.5$ \sb. 
@@
     fraction of massive galaxies because they are heavily masked out. 
-    \update{
     This is an intrinsic limitation of the 1-D method, and it removes ${\sim}10$\% of 
     the sample.
-    }
     %It affects $18/164$ of the \rbcg{} sample, and a smaller fraction of the 
@@
 
-    \update{
-    Given our exquisite profiles that extend to 100 kpc, the definition and meaning of ``total'' 
-    magnitude (and stellar mass) becomes more nuanced.
+    Given our exquisite profiles that extend to 100 kpc, the definition and meaning 
+    of ``total'' magnitude (and stellar mass) becomes more nuanced.
     With the help of the \m2l{} estimated in the next section (\S \ref{sec:mstar}), 
@@
     apertures throughout this work:
-    }
 
@@
 
-        \item \textbf{The \mstar{} within the inner 10 kpc} (hereafter noted \minn{}). 
-            According to the two-phase scenario, the ``in-situ'' star-formation quickly 
-            builds up the inner, dense core of massive ETGs.  
-            Based on recent observation (e.g.~\citealt{vanDokkum2010}) and simulations 
-            (e.g. \citealt{RodriguezGomez2016}), the in-situ component dominates the 
-            \mstar{} within one effective radius ($R_{\mathrm{e}}$, or 5-10 kpc) of 
-            $z{\sim}0$ massive ETGs.
-            We therefore use \minn{} as proxy for the mass forged during the ``in-situ''
-            phase. 
-            Given the quality of the HSC data, we can reliably measure \minn{} over our 
-            redshift range ($1.0^{\arcsec}$ in radius equals 4.4 and 6.1 kpc at redshift
-            0.3 and 0.5).
-
-        \item \textbf{The stellar mass within 100 kpc} (hereafter noted \mtot{}). 
+        \item \textbf{The \mstar{} within the inner 10 kpc} 
+            (hereafter noted \minn{}). 
+            According to the two-phase scenario, the ``in-situ'' star-formation 
+            quickly builds up the inner, dense core of massive ETGs.  
+            Based on recent observation (e.g.~\citealt{vanDokkum2010}) and 
+            simulations (e.g. \citealt{RodriguezGomez2016}), the in-situ component
+            dominates the \mstar{} within one effective radius ($R_{\mathrm{e}}$, 
+            or 5-10 kpc) of $z{\sim}0$ massive ETGs.
+            We therefore use \minn{} as proxy for the mass forged during the 
+            ``in-situ'' phase. 
+            Given the quality of the HSC data, we can reliably measure \minn{} over 
+            our redshift range ($1.0^{\arcsec}$ in radius equals 4.4 and 6.1 kpc 
+            at redshift 0.3 and 0.5).  
+            It is worth noting that, at very high-\mstar{} end, there can be 
+            significant contribution of accreted stars within 10 kpc 
+            (e.g. \citealt{RodriguezGomez2016). 
+            We will further discuss the justification of this assumption in 
+            \ref{ssec:twophase}.
+
+        \item \textbf{The stellar mass within 100 kpc} 
+            (hereafter noted \mtot{}). 
             For our galaxy sample, a 100 kpc aperture corresponds to 5-10 
             $\times R_{\mathrm{e}}$. 
-            We show in section \ref{ssec:mtotal} that most of the \mstar{} for these 
-            ETGs can be captured by a 100 kpc radius and that \mtot{} is a good proxy 
-            for the ``total'' \mstar{}. 
+            We show in section \ref{ssec:mtotal} that most of the \mstar{} for 
+            these ETGs can be captured by a 100 kpc radius and that \mtot{} is 
+            a good proxy for the ``total'' \mstar{}. 
             Although not perfect, we argue that our measurements of \mtot{} (which are 
@@
             Build-Up of Outer Envelopes}
+    \label{ssec:twophase}
 

### 2017-05-29 draft/paper1_jenny.tex
Edit M/L measurement

@@
             significant contribution of accreted stars within 10 kpc 
-            (e.g. \citealt{RodriguezGomez2016). 
+            (e.g. \citealt{RodriguezGomez2016}). 
             We will further discuss the justification of this assumption in 
@@
 
-    To convert luminosities into stellar mass, we assume that these massive galaxies 
+    To convert luminosities into \mstar{}, we assume that these massive galaxies 
     can be well described by an average \m2l{}. 
     This is a reasonable assumption considering that they are mostly dominated by 
-    old stellar populations and are known to have shallow color gradients. 
+    old stellar populations and are known to have only shallow color gradients. 
     We will further justify this point by measuring their median color profiles in 
@@
     \texttt{iSEDFit} takes a simplified Bayesian approach. 
-    In short, it first generates a large grid of SEDs from synthetic stellar population 
-    models by drawing randomly from the prior distributions of relevant parameters 
-    (e.g. age, metallicity, dust extinction, and star formation history).
+    In short, it first generates a large grid of SEDs from synthetic stellar 
+    population models by drawing randomly from the prior distributions of relevant
+    parameters (e.g. age, metallicity, dust extinction, and star formation history).
     Based on these models, it uses the observed photometry and redshift to compute 
@@
     (e.g.\ \citealt{Kauffmann2003}). 
-    \update{
     For stellar metallicity 
@@
     distribution between 0.004 to 0.03 (the highest value allowed by FSPS).
-    } 
     We adopt the \citet{Calzetti2000} extinction law with a order two Gamma 
     distribution of $A_{V}$ between 0 to 2 magnitude. 
-    A majority of our galaxies are red and quiescent and our results are 
-    not very sensitive to parameters related to the SFH or the internal dust extinction. 
+    The majority of our galaxies are red and quiescent ones so the results are not 
+    very sensitive to parameters related to the SFH or the internal dust extinction. 
     To achieve reasonable sampling across these parameters, we generate 250000 models.
@@
     corrected for Galactic extinction. 
-    \cmodel{} only accounts for the statistical error on the flux measurement but does
-    not account for systematic uncertainties in the model-fitting process. 
+    \cmodel{} only accounts for the statistical error on the flux measurement but 
+    does not account for systematic uncertainties in the model-fitting process. 
     It therefore underestimates the flux errors of bright galaxies. 
     For this work, we supply \texttt{iSEDFit} with simplified flux errors assuming 
-    $S/N = 100$ for the $riz$ bands, and $S/N = 80$ for the $g$- and $y$-band 
+    $S/N = 100$ for the $riz$ bands, and $S/N = 80$ for the $g$ and $y$ band 
     (on average, images in $gy$ bands are shallower in depth and/or have higher 
     background noise).  
-    Although thse are still conservative estimates of the systematic uncertainties 
+    Although these are still conservative estimates of the systematic uncertainties 
     involved in the model-fitting, tests using synthetic galaxies show that \cmodel{}
-    provides excellent measurements of five-band colors, which are crucial for reliable
-    \m2l{} estimates.
+    provides excellent measurements of five-band colors, which are crucial for 
+    reliable \m2l{} estimates.
     The typical uncertainty of \logms{} is around 0.06-0.08 dex at \logms${\sim} 11.5$. 

### 2017-05-29 draft/paper1_jenny.tex
Edit Mtotal

@@
     The typical uncertainty of \logms{} is around 0.06-0.08 dex at \logms${\sim} 11.5$.
+
+    In Appendix~\ref{app:sed}, we briefly summarize the basic statistics of 
+    the sample, including average stellar age, metallicity, and internal dust 
+    extinction along with their relation with \mtot{}. 
+    All these properties behave reasonably for massive galaxies in this sample despite 
+    that we do not utilize them in this paper. 
+    Using the $k$-corrected optical color, we can also confirm that the sample follows 
+    a tight ``red-sequence''.  
     Please see Appendix~\ref{app:sed} for further details.
@@
 
-    Using the best-fit stellar mass from \texttt{iSEDFit} (noted as as \mcmodel{}), 
+    Using the best-fit \mstar{} from \texttt{iSEDFit} (noted as as \mcmodel{}), 
     we estimate the average \m2l{} in the $i$-band, then use that \m2l{} to convert 
@@
     stellar mass. 
-    \update{
     As expected, the integration of the 1-D profile out to very large radius recovers 
@@
     (Fig \ref{fig:mass_diff}).
-    }
-    \song{Work in progress.}
-
-    In Appendix~\ref{app:sed}, we briefly summarize the basic statistics of 
-    the sample using our estimates of \mtot{} and \minn{}.
-    We confirm that the sample follows a very tight ``red-sequence'' that does not appear to depend on 
-    environment (see \S XX). 
-    Appendix~\ref{app:sed} describes the outputs from our SED fitting process 
-    (average stellar age, metallicity, and internal dust extinction). 
-    We do not utilize these quantities in this paper, but we have checked that they all 
-    behave reasonably for both samples.
-
-    \song{The color gradients and ellipticity profiles will be updated}
+    At high-\mstar{} end (e.g. \logmtot{}$>11.6$), the average difference is larger 
+    than 0.1 dex and can be as large as 0.2--0.3 dex.  
+    More importantly, the differences between \mtot{} and \mcmodel{} clearly show 
+    dependence on total stellar mass as \mcmodel{} tends to misse more light in 
+    more massive galaxies.  
+    In the next section, we will show that this
+
     Our methodology ignores any radial variations in \m2l{}. 
-    It is well known that massive ETGs have negative optical color gradients indicating 
-    gradients in \m2l{} (e.g.\ \citealt{LaBarbera2012}; 
+    It is well known that massive ETGs have negative optical color gradients 
+    indicating gradients in \m2l{} (e.g.\ \citealt{LaBarbera2012}; 
     \citealt{DSouza2015}). \jenny{earlier reference here?}

### 2017-05-30 draft/paper1_jenny.tex
Edit total stellar mass

@@
     More importantly, the differences between \mtot{} and \mcmodel{} clearly show 
-    dependence on total stellar mass as \mcmodel{} tends to misse more light in 
+    dependence on total stellar mass as \mcmodel{} tends to miss more light in 
     more massive galaxies.  
-    In the next section, we will show that this
+    This relates to the mass-dependence nature of the stellar halos in massive 
+    galaxies and the intrinsic limitation of \cmodel{} method, which we will discuss
+    more in the next section.
+    Such differences also have important implications in the estimation of stellar 
+    mass function or in the study of environment-dependence of galaxy structure.  
+    We will also discuss these topics in Section \ref{sec:discussion}.
+
+    Although 100 kpc is already a very large radius that should enclose the majority 
+    of stars that belong to these massive galaxies, we know that their \mden{} 
+    profiles extend beyond 100 kpc without showing sign of truncation. 
+    Therefore, for massive galaxies, even \mtot{} should be only considered a lower
+    limit of the ``total'' \mstar{}. 
+    In Fig \ref{fig:mass_diff}, we also integrate the \mden{} of each galaxy to the 
+    outermost radii as \mmax{} and compare their differences with \mtot{} 
+    (right panel).  
+    Although \mmax{} is much more uncertain than \mtot{} due to background subtraction
+    and impacts from nearby objects, we see they do return more \mstar{} than \mtot{}. 
+    However, the mass differences are on average very small ($\sim0.02-0.03$ dex) and 
+    do not show strong mass dependence.  
+    This confirms that, at the current depth of HSC images, \mtot{} can be used as 
+    good proxy of ``total'' stellar mass.
 
@@
     It is well known that massive ETGs have negative optical color gradients 
-    indicating gradients in \m2l{} (e.g.\ \citealt{LaBarbera2012}; 
-    \citealt{DSouza2015}). \jenny{earlier reference here?}
+    indicating gradients in \m2l{} (e.g.\ \citealt{Carollo1993, Davies1993, 
+    LaBarbera2012, DSouza2015}).
     These color gradients are shallow and smooth out to a few times the effective 
     radius and color gradients at the outskirts are not yet well quantified.
-    Our results looking at the outer envelopes as a function of mass and environment 
-    will be robust as long as there is \emph{no significant difference in 
-    the average color gradient between sub-samples}.
-    %More importantly, for the comparison between the \rbcg{} and \nbcg{} samples, 
-    %our results will be robust as long as there is \emph{no significant difference in 
-    %the average color gradient between the two samples}. 
-    We have confirmed that this is indeed the case (see Section~\ref{ssec:ell_color}).
-
-    Our method for deriving total stellar masses is similar to the 
-    method adopted by the GAMA survey (\citealt{Taylor2011, Kelvin2012}). 
-    We have compared our \mstar{} values with those from GAMA and the results are given 
-    in Appendix~\ref{app:gama}. 
-    We find a systematic differences between the two \mstar{} estimates.
+    Therefore, using average \m2l{} is unlikely to bias the results on \mstar{}
+    measurements.  
+    We will discuss color gradients more in Section~\ref{ssec:ell_color}. 
+    In summary, we do not find optical color gradient shows dependence on stellar
+    mass, hence the results about the mass-dependence of the \mden{} profiles will 
+    not be affected by it.
+
+    %Our results looking at the outer envelopes as a function of mass and environment 
+    %will be robust as long as there is \emph{no significant difference in 
+    %the average color gradient between sub-samples}.
+    %We have confirmed that this is indeed the case (see Section~\ref{ssec:ell_color}).
+
+    Our method for deriving total \mstar{} is similar to the method adopted by the 
+    GAMA survey (\citealt{Taylor2011, Kelvin2012}), where the average \m2l{} is from 
+    SED fitting of PSF-matched aperture photometry and the total luminosity comes from 
+    sing-\ser{} modeling of the SDSS images. 
+    To avoid the differences in stellar population assumptions, we directly compare the 
+    total luminosity within 100 kpc and the GAMA single-\ser{} luminosity for the same
+    galaxies. 
+    At high-\mstar{} end, the HSC 1-D profiles still recover more light than the 
+    single-\ser{} model on average.
     It is likely that the GAMA models fail to capture the flux associated with the 
     outskirts of galaxies due to the limited depth of SDSS.  
+    Meanwhile, there are also many cases where the high-\ser{} index of GAMA model leads 
+    to over-estimated total luminosity. 
+    We will discuss more of this comparison in the next paper of this series 
+    (Huang\etal in prep.).
+
+    %We have compared our \mstar{} values with those from GAMA and the results are given 
+    %in Appendix~\ref{app:gama}.
+
 %% ------------------------------------------------------------------------------------ %%

### 2017-05-30 draft/paper1_jenny.tex
Edit final sample

@@
     Stripe 82 region (\citealt{Annis2014}) with the near infrared data from the United 
-    Kingdom Infrared Telescope Infrared Deep Sky Survey (UKIDSS; \citealt{Lawrence2007}). 
-    The deeper photometry and better photo-$z$s make the \texttt{S82-MGC} sample complete 
-    to \logms{}$\geq 11.2$ at $z<0.7$ which makes it sufficient to evaluate the 
-    completeness of our HSC samples.
+    Kingdom Infrared Telescope Infrared Deep Sky Survey (UKIDSS; 
+    \citealt{Lawrence2007}). 
+    The deeper photometry and better photo-$z$s make the \texttt{S82-MGC} sample 
+    complete to \logms{}$\geq 11.2$ at $z<0.7$ which makes it sufficient to evaluate 
+    the completeness of our HSC sample.   
+	By comparing with the Stripe 82 Massive Galaxy Catalog
+    (\texttt{S82-MGC}; \citealt{Bundy2015}), \citet{Leauthaud2016} have measured the
+    \mstar{} completeness of the combined BOSS and SDSS samples. 
+    They estimate that the BOSS spec-$z$ sample, which is the main contributor of 
+    spec-$z$ in our massive galaxy sample, is about 80\% complete at 
+    \logms{}$\geq 11.6$ at $0.3 < z < 0.5$. 
+    As the secondary contributor, the GAMA survey is 80\% complete down to 
+    $10^{10.8}$\msun at $z{\sim} 0.3$, but is only 80\% complete to 
+    $10^{12.0}$\msun{} at $z{\sim} 0.5$ according to \citet{Taylor2011} (e.g.\ 
+    their Fig~~6).
 
@@
     sample at $0.3 \leq z_{\mathrm{s82}} \leq 0.5$. 
-    We compute \mstar{} values for these galaxies using our fiducial 
+    We estimate \mcmodel{} values of these galaxies using our fiducial 
     procedure\footnote{The \mstar{} using HSC photometry is in excellent with the 
@@
     \texttt{S82-MGC} also uses \texttt{iSEDFit} with similar assumptions.}. 
-    Figure~\ref{fig:mass_complete} compares the SMFs of galaxies from 
-    \texttt{S82-MGC} with the SMFs of galaxies from our 
-    sample\footnote{Errors on the SMFs are estimated via bootstrap resampling}. 
-    Based on Fig~\ref{fig:mass_complete}, we conclude that our sample of massive galaxies is 
-    reasonably complete down to \logms{}${\sim} 11.6$ at $0.3 \leq z \leq 0.5$. 
+    Figure~\ref{fig:mass_complete} compares the volume number density distributions 
+    of galaxies from \texttt{S82-MGC} with the one for galaxies in our 
+    sample\footnote{Since we do not apply any statistical correction on the 
+    completeness, we do not use the term ``stellar mass function'' to avoid confusion;
+    Errors on the distributions are estimated via bootstrap resampling}. 
+    Based on Fig~\ref{fig:mass_complete}, we conclude that our sample of massive 
+    galaxies is reasonably complete down to \logmcmodel{}${\sim} 11.5$ at 
+    $0.3 \leq z \leq 0.5$. 
     %The \rbcg{} sample is less affected by completeness because we can utilize 
@@
     %availability of spec-$z$s from BOSS.    
-    In this work, we will focus on the range $11.6 \le$ \logmtot{}$ \le 11.9$ 
-    where our two samples are complete. 
+    Given the average difference between \mtot{} and \mcmodel{}, we will focus on 
+    the galaxies with \logmtot{}$> 11.6$ where our sample shows good completeness.
+    The massive galaxies with $11.4 \le$\logmtot{}$<11.6$ are also included in the 
+    discussion since there is no obvious reason to worry about the impact of
+    completeness on the main results of this work.
+
     %When comparing \nbcg{} and \rbcg{} we will also always make sure that the two 
@@
 
-	\jenny{Anything else we need to keep from here?}
-	By comparing with the Stripe 82 Massive Galaxy Catalog
-    (\texttt{S82-MGC}; \citealt{Bundy2015}), \citet{Leauthaud2016} have measured the
-    \mstar{} completeness of the combined BOSS and SDSS samples. 
-    They estimate that the BOSS spec-$z$ sample is about 80\% complete at 
-    \logms{}$\geq 11.6$ at $0.3 < z < 0.5$. 
-    The GAMA survey, which partially overlaps with the HSC footprints, supplements 
-    our \texttt{hscZ} sample by 14\%. 
-    Based on \citet{Taylor2011} (e.g.\ their Fig~~6), at $z{\sim} 0.3$, the GAMA 
-    sample is 80\% complete down to $10^{10.8}$\msun; but only 80\% complete to 
-    $10^{12.0}$\msun at $z{\sim} 0.5$. 
-    We can therefore expect our sample to be roughly \mstar{}-complete above 
-    \logms{}$\geq 11.5$-$11.6$. 
-    This question will be addressed more carefully using the overlap region between 
-    HSC and the \texttt{S82-MGC} in Section \ref{ssec:s82}.
 %% ------------------------------------------------------------------------------------ %%
@@
 
-	With stellar masses in hand, we now use the redMapper cluster catalog to identify a sample of 
-    central galaxies.
-
-	\subsection{Indentifying central galaxies using the \redm{}{} cluster catalog}
+	With the different estimates of \mstar{} and the \mden{} profiles in hand, we now 
+	proceed to identify a sample of massive central galaxies with the help from the 
+	\redm{} galaxy cluster catalog. 
+	The ``central'' galaxy can be roughly defined as the galaxy that live in the 
+	center of its own dark matter halo.  
+	In contrast, galaxy in a sub-halo who is orbiting within the virial radius of a 
+	more massive halo is referred to as ``satellite''. 
+	Central galaxy has its unique importance in the study of galaxy evolution and 
+	galaxy-halo coevolution.
+	Therefore, to better understand the connection between the structure of massive 
+	galaxies and the assembly history of stars and halos, we wish to focus on central 
+	galaxies in this work.
+
+\subsection{Candidates of massive central galaxies}
     \label{ssec:redmapper}
 
-    We wish to focus on galaxies located at the center of their dark matter halos. 
-    To limit our sample to central galaxies, we use \texttt{v5.10} of the \redm{}{} 
-    cluster catalog\footnote{See: http://risa.stanford.edu/redmapper/} 
+    Identification of central galaxy is not an easy task (e.g. \citealt{Yang2007}).
+    For this purpose, we first use the \redm{} catalog to help us isolate the central 
+    galaxies in massive halos and also exclude the massive satellite galaxies in these
+    haloes.  
+    Assuming the completeness of the \redm{} catalog, we treat the rest of sample as 
+    galaxies from less massive halos.  
+    Given the smaller fraction of satellite galaxies at high-\mstar{} end (e.g. 
+    \citealt{Reid2014, Hoshino2015, Saito2016}), 
+    we further assume that the massive ones (\logmtot{}$>11.4$) among them are likely 
+    to be the central galaxies of these smaller halos.
+
+    In the first step, we make use of the \texttt{v5.10} of the \redm{} cluster 
+    \footnote{See: http://risa.stanford.edu/redmapper/} 
     (e.g.\ \citealt{Rykoff2014}; \citealt{Rozo2015b}). 
@@
     have $\log (M_{\mathrm{halo}}/M_{\odot}) \geq 14.0$. 
-    The \redm{} catalog therefore helps us group massive central galaxies into 
-    samples with different average \mhalo{}. 
-    We will use the central galaxies of \redm{} clusters 
-    ($P_{\mathrm{CEN}} \geq 0.7$) to form a sample of massive central galaxies that 
-    live in massive halos as described below. In addition to identifying central galaxies, 
-    we are also able to link each galaxy with a halo mass using the redMaPPer catalog, and 
-    this information is also very useful in studying the 
-    relationship between galaxy structure and environment.
+    Therefore the central galaxies of these \redm{} clusters\footnote{We only use the 
+    central galaxies with $P_{\mathrm{CEN}} \geq 0.7$} form a sample of massive central 
+    galaxies that live in massive halos as described above.
+    Besides the selection of central galaxies, we are also able to link each galaxy
+    with a \mhalo{} using the \redm{} catalog. 
+    Such information is also very useful in studying the relationship between galaxy
+    structure and environment (Huang\etal in prep.).
 %% ------------------------------------------------------------------------------------ %%
@@
 
+    % TODO: Move this to Paper II
+    %To ensure a clean separation in \mhalo{}, here we only focus on the central 
+    %galaxies of clusters with $\lambda > 30$. 
+    %According to \citet{Simet2016}, this $\lambda \geq 30$ sample should correspond to 
+    %$M_{\mathrm{halo}}>10^{14.2} M_{\odot}$. 
+    %We have checked that none of the results in this work depend on the choice of this 
+    %$\lambda$ limit.
+
+    %The median $\lambda$ of the clusters associated with the \rbcg{} sample is 
+    %${\sim} 41$, corresponding to halo mass of 
+    %$M_{\mathrm{halo}}{\sim} 2.2\times 10^{14}$ $h^{-1}$ $M_{\odot}$.
+    %Only 44 centrals from the \rbcg{} sample live in clusters with $\lambda \geq 50$
+    %($M_{\mathrm{halo}} {\sim} 3.0\times 10^{14}$ $h^{-1} M_{\odot}$). 
+    %Our \rbcg{} sample therefore corresponds to galaxies in moderate mass halos.
+
+    After matching the \texttt{hscZ} sample with the central galaxies of \redm{} 
+    clusters with $\lambda \geq 20$ and $P_{\mathrm{0.7}} \geq 0.7$, we find 164 
+    matched galaxies at $0.3 \leq z \leq 0.5$.
+    This sample of \textbf{central galaxies in more massive halos} will be referred to 
+    as the \rbcg{} sample. 
     Due to the depth and resolution of SDSS, the \redm{} catalog becomes slightly 
-    incomplete at lower richness ($\lambda < 40$) at $z > 0.33$. 
-    To ensure a clean separation in \mhalo{}, here we only focus on the central 
-    galaxies of clusters with $\lambda > 30$. 
-    According to \citet{Simet2016}, this $\lambda \geq 30$ sample should correspond to 
-    $M_{\mathrm{halo}}>10^{14.2} M_{\odot}$. 
-    We have checked that none of the results in this work depend on the choice of this 
-    $\lambda$ limit.
-
-    We therefore match the \texttt{hscZ} sample with the central galaxies of \redm{} clusters 
-    with $\lambda \geq 30$ and $P_{\mathrm{0.7}} \geq 0.7$, and find 164 matched 
-    galaxies at $0.3 \leq z \leq 0.5$.
-    Our sample of \textbf{central galaxies in more massive halos} will be referred to 
-    as the \rbcg{} sample. 
-    The median $\lambda$ of the clusters associated with the \rbcg{} sample is 
-    ${\sim} 41$, corresponding to halo mass of 
-    $M_{\mathrm{halo}}{\sim} 2.2\times 10^{14}$ $h^{-1}$ $M_{\odot}$.
-    Only 44 centrals from the \rbcg{} sample live in clusters with $\lambda \geq 50$
-    ($M_{\mathrm{halo}} {\sim} 3.0\times 10^{14}$ $h^{-1} M_{\odot}$). 
-    Our \rbcg{} sample therefore corresponds to galaxies in moderate mass halos.
+    incomplete at lower richness ($\lambda < 40$) at $z > 0.33$, but the main results 
+    of this work are not affected by this.
     %% Saved as "dr1_redbcg_use_sed5b.fits"
 
-    Out next goal is to construct a sample of central galaxies living in halos with 
-    \logmh{}$<14.0$. 
-    We first identify and remove all galaxies within a cylindrical region around all 
-    \redm{} clusters. 
+    As the next step, we want to construct a sample of central galaxies living in halos 
+    with \logmh{}$<14.0$. 
+    To achieve this, we identify and remove all galaxies within a cylindrical region 
+    around all \redm{} clusters. 
     We use a radius equal to $R_{\mathrm{200b}}$ and the thickness of the cylinder is 
-    set to twice the uncertainty of the photometric redshift error. 
-    We convert $\lambda$ to $M_{\mathrm{halo}}$ using the calibration of 
-    \citet{Simet2016} and we use the mass-concentration relation from 
-    \citet{Diemer2015} to compute $R_{\mathrm{200b}}$. At $0.3 < z < 0.5$, the 
-    uncertainty of photo-$z$ is between 0.015 to 0.025, and is enough to exclude 
-    cluster members.
+    set to twice the uncertainty of the photometric redshift error of the cluster. 
+    We convert $\lambda$ of each cluster to $M_{\mathrm{halo}}$ using the calibration 
+    of \citet{Simet2016} and we use the mass-concentration relation from 
+    \citet{Diemer2015} to compute $R_{\mathrm{200b}}$. 
+    At $0.3 < z < 0.5$, the uncertainty of photo-$z$ is between 0.015 to 0.025, and 
+    is enough to exclude cluster members.
+
     After removing galaxies associated with \redm{} clusters, the remaining galaxies 
     in our sample will be dominated by central galaxies living in halos with 
-    \logmh{}$\leq 14.0$. 
-    We will refer to this sample of \textbf{central galaxies in less massive halos}
-    as the \nbcg{} sample. For massive central galaxies that are not in these cluster-level halos, 
-    we unfortunately can not estimate their \mhalo{} individually, but it is safe 
-    to assume they will have $\log (M_{\mathrm{halo}}/M_{\odot}) < 14.0$.  
-    At this very high mass end, and given that we have rejected satellites in \redm{} 
-    clusters, any further satellite contamination can be safely neglected 
-    (e.g. \citealt{Reid2014, Hoshino2015, Saito2016, vanUitert2016}).
+    \logmh{}$< 14.0$. 
+    We will refer to this sample of \textbf{potential central galaxies in less 
+    massive halos} as the \nbcg{} sample. 
+    Since we have rejected satellites in \redm{} cluster and the satellite 
+    contamination steadily decreases with stellar mass (e.g. \citealt{Reid2014, 
+    Hoshino2015, Saito2016, vanUitert2016}), the massive galaxies in the \nbcg{} 
+    sample are very likely to be the central galaxies of
+
+     very high mass end, and given that we have rejected satellites in \redm{} 
+    clusters, any further satellite contamination can be neglected for the purpose of 
+    this work
+    .
     %% Saved as "dr1_nonbcg_use_sed5b.fits"
-    % TODO: The actual number waits to be updated}
-
 %% ------------------------------------------------------------------------------------ %%

### 2017-05-30 draft/paper1_jenny.tex
Edit final sample

@@
     Hoshino2015, Saito2016, vanUitert2016}), the massive galaxies in the \nbcg{} 
-    sample are very likely to be the central galaxies of
-
-     very high mass end, and given that we have rejected satellites in \redm{} 
-    clusters, any further satellite contamination can be neglected for the purpose of 
-    this work
-    .
+    sample are very likely to be the central galaxies of their own dark matter halos.
     %% Saved as "dr1_nonbcg_use_sed5b.fits"
@@
             with reliable redshift information. 
-        \item We further divide the sample into an \rbcg{} sample and a \nbcg{} sample, 
-          with the former roughly having \logmh{}$\geq 14.2$ and the latter having 
-           \logmh{}$<14.0$.
-
-%          : we select a sample of 164 galaxies at 
-%            $0.3 \leq z \leq 0.5$ that are the central galaxies 
-%            in $\lambda > 30$ \redm{} clusters. 
-%            They represent the central galaxies in very massive halos 
-%            (\logmh{}$\geq 14.2$). 
-%        \item \nbcg{} sample: after excluding all cluster members from the 
-%            \texttt{hscZ} sample, we have 14661 bright galaxies at 
-%            $0.3 \leq z \leq 0.5$. 
-%            After applying an additional \mstar{} cut (see Section 
-%            \ref{ssec:isedfit}), this sample corresponds to central galaxies in 
-%            halos with \logmh{}$<14.0$.  
+        \item With the help of the \redm{} cluster catalog, we further select 
+            candidates of massive central galaxies in a range of \mhalo{}
+            We broadly divide the sample into the central galaxies living in halos
+            with \logmh{}$\geq 14.0$ (\rbcg{}) and \logmh{}$<14.0$ (\nbcg{}). 
     \end{itemize}
 
+    To discuss the mass-dependence of galaxy structure, we will combine the \rbcg{}
+    and \nbcg{} samples and group them into three bins of \mtot{}.  
+    In this work, we will only separately discuss the \rbcg{} and \nbcg{} samples 
+    when we look into the impact of \mstar{} definition on the SMF in Section 
+    \ref{ssec:smf}. 
+    We will carefully look into the structural differences between the central galaxies 
+    from these two samples later (Huang\etal~in prep.).  
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
+  \begin{figure*}
+      \centering 
+      \includegraphics[width=\textwidth]{fig/redbcg_mass_smf}
+      \caption{
+          \textbf{Left:} Impact of using \mtot{} on the galaxy stellar mass function. 
+          Dashed lines correspond to the SMF computed using \mcmodel{} whereas solid 
+          lines correspond to the SMF computed using \mtot{}. 
+          Here we separate the HSC massive galaxies into the central galaxies living 
+          in halos more massive than \logmh{}$\sim14.2$ (red lines) and the ones in 
+          halos with \logmh{}$<14.0$ (black lines).
+          The impact on the SMF can exceed 0.2 dex for massive central galaxies in 
+          very massive halos.
+          \textbf{Right}: The stellar mass volume density distributions of massive 
+          HSC galaxies, using both \mtot{} (black solid line) and \mmax{} (black dotted 
+          line). 
+          The uncertainty of distribution using \mtot{} is shown in grey shaded 
+          region.  
+          Here, we also compare the distributions with SMF from previous works: 
+          (a): SDSS galaxies at $z{\sim} 0.1$ from \citet{Bernardi2013}; the \mstar{} 
+          is based on photometry from 2-D \ser{}$+$Exponential model fitting 
+          (purple); 
+          (b): SDSS galaxies at $z{\sim} 0.1$ from \citet{Moustakas13} based on 
+          improved SDSS \texttt{cModel} photometry (blue); 
+          (c): \texttt{S82-MGC} galaxies at $0.15 < z< 0.43$ from 
+          \citet{Leauthaud2016} based on PSF-matched SDSS-UKIDSS photometry (green).
+          Please see text for more details of the comparison.
+          }
+      \label{fig:smf}
+  \end{figure*}
 %% ------------------------------------------------------------------------------------ %%
@@
     \subsection{Impact of Missing Light on the Galaxy Stellar Mass Function}
-    \label{ssec:s82}
+    \label{ssec:smf}
+
+    In Section \ref{ssec:mtotal}, we demonstrate that different methods for estimating
+    ``total'' stellar mass.
 
@@
     \cmodel{}-like photometry or shallower images, these effects can not be neglected.
+
+        Even with deep HSC images, it is non trivial to clearly define and measure the
+    ``total'' \mstar{} for these massive systems. 
+    As discussed in Section~\ref{ssec:mtotal}, our 1-D approach has certain advantages 
+    over the 2-D modeling method and in principle, should capture a the majority of 
+    the stellar mass. 
+    However, even though we extend to 100 kpc, there is no evidence that the profile 
+    drops to zero on these scales. 
+    We now estimate how much extra mass is ``hidden'' beyond the 100 kpc radius. 
+    For this, we integrate the \mden{} profiles out to the detection limit in 
+    surface brightness profile that is defined by the background noise.
+    We will call this the ``maximum mass'' of the galaxy (\mmax{}). 
+    For obvious reasons, we find that \mmax{} is larger than \mtot{} with an average 
+    difference of about ${\sim}0.04$ dex. 
+    The left hand side of Fig \ref{fig:smf} shows differences between \mtot{}
+    and \mmax{}. 
+    On a galaxy-by-galaxy basis, the difference \mmax{}-\mtot{} depends on the slope 
+    of the stellar envelope. 
+    In this work, we have opted to in general use \mtot{} rather than \mmax{} as the 
+    uncertainty on \mmax{} is larger. 
+    However, we have checked that none of our results are changed by replacing \mtot{} 
+    via \mmax{}.
+
+    How to define and measure the ``total'' mass of a galaxy becomes a critical 
+    question when studying the high-mass end of the galaxy SMF. 
+    The issues discussed above are currently one of the primary limitations in 
+    determinations of the high-mass end of the SMF (\citealt{Bernardi2016}). 
+    Fig~\ref{fig:mass_complete} illustrated how improved \mstar{} measurement can 
+    significantly modifies the SMF. 
+    On the right hand side of Fig~\ref{fig:smf}, we further highlight that 
+    the shape of SMF at high-mass end is quite sensitive to even very small 
+    change of \mstar{}. 
+    We also compare the SMFs of our HSC samples with the following previous studies:
+
+    \begin{itemize}
+
+        \item The SMF derived from a SDSS-\textit{GALEX} sample of $z{\sim} 0.1$ 
+            galaxies from \citet{Moustakas13}. 
+            Here, the total luminosity is based on the SDSS \cmodel{} magnitude. 
+            The \m2l{} is derived via SED fitting using \texttt{iSEDfit} with similar 
+            assumptions as in our work.
+
+        \item The SMF for $z{\sim} 0.1$ SDSS galaxies from \citet{Bernardi2013}. 
+            The total luminosity is based on 2-D \texttt{SerExp} models 
+            (\ser{}$+$ Exponential disk model; integrated to infinity) that 
+            recovers much more flux compared to SDSS \cmodel{} magnitudes. 
+            The \m2l{} is also from SED fitting assuming a Chabrier IMF.
+
+        \item The SMF for $0.15 < z < 0.30$ galaxies from the \texttt{S82-MGC} sample
+            \citep{Leauthaud2016} where the \mstar{} is derived using 
+            \texttt{iSEDfit} on PSF-corrected aperture photometry from 
+            \texttt{S82}.
+
+    \end{itemize}
+
+%% ------------------------------------------------------------------------------------ %% 
+    It is clear that different analyses lead to very different slopes at high-mass end. 
+    Here, we do not try to evaluate whether the differences displayed in 
+    Fig~\ref{fig:smf} are dominated by differences in photometry versus 
+    assumptions about stellar population models (e.g. \citealt{Bernardi2016}). 
+    However, given that the results that we are comparing assume the same IMF and adopt 
+    similar assumptions about stellar population models, we hypothesize that the 
+    differences in Fig~\ref{fig:smf} are dominated by differences in photometry. 
+    The goal of our of present paper is not to present and discuss a careful evaluation
+    of the high-mass end of the SMF -- this will be presented in a forthcoming paper 
+    once the HSC survey has accumulated more data. 
+    However, this is clearly a topic that warrants further investigation, and careful 
+    photometry measurements from HSC data will shed further light on these questions.
+
 %% ------------------------------------------------------------------------------------ %%
@@
 %% ------------------------------------------------------------------------------------ %% 
-  \begin{figure*}
-      \centering 
-      \includegraphics[width=\textwidth]{fig/redbcg_mass_smf}
-      \caption{
-          \textbf{Left:} Impact of using \mtot{} on the galaxy stellar mass function. 
-          Dashed lines correspond to the SMF computed using \mcmodel{} whereas solid 
-          lines correspond to the SMF computed using \mtot{}. 
-          Here we separate the HSC massive galaxies into the central galaxies living 
-          in halos more massive than \logmh{}$\sim14.2$ (red lines) and the ones in 
-          halos with \logmh{}$<14.0$ (black lines).
-          The impact on the SMF can exceed 0.2 dex for massive central galaxies in 
-          very massive halos.
-          \textbf{Right}: The stellar mass volume density distributions of massive 
-          HSC galaxies, using both \mtot{} (black solid line) and \mmax{} (black dotted 
-          line). 
-          The uncertainty of distribution using \mtot{} is shown in grey shaded 
-          region.  
-          Here, we also compare the distributions with SMF from previous works: 
-          (a): SDSS galaxies at $z{\sim} 0.1$ from \citet{Bernardi2013}; the \mstar{} 
-          is based on photometry from 2-D \ser{}$+$Exponential model fitting 
-          (purple); 
-          (b): SDSS galaxies at $z{\sim} 0.1$ from \citet{Moustakas13} based on 
-          improved SDSS \texttt{cModel} photometry (blue); 
-          (c): \texttt{S82-MGC} galaxies at $0.15 < z< 0.43$ from 
-          \citet{Leauthaud2016} based on PSF-matched SDSS-UKIDSS photometry (green).
-          Please see text for more details of the comparison.
-          }
-      \label{fig:discussion_2}
-  \end{figure*}
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %% 
 \subsection{What is the ``Total Mass'' of Massive Galaxies?}
@@
     difference of about ${\sim}0.04$ dex. 
-    The left hand side of Fig \ref{fig:discussion_2} shows differences between \mtot{}
+    The left hand side of Fig \ref{fig:smf} shows differences between \mtot{}
     and \mmax{}. 
@@
     significantly modifies the SMF. 
-    On the right hand side of Fig~\ref{fig:discussion_2}, we further highlight that 
+    On the right hand side of Fig~\ref{fig:smf}, we further highlight that 
     the shape of SMF at high-mass end is quite sensitive to even very small 
@@
     Here, we do not try to evaluate whether the differences displayed in 
-    Fig~\ref{fig:discussion_2} are dominated by differences in photometry versus 
+    Fig~\ref{fig:smf} are dominated by differences in photometry versus 
     assumptions about stellar population models (e.g. \citealt{Bernardi2016}). 
@@
     similar assumptions about stellar population models, we hypothesize that the 
-    differences in Fig~\ref{fig:discussion_2} are dominated by differences in photometry. 
+    differences in Fig~\ref{fig:smf} are dominated by differences in photometry. 
     The goal of our of present paper is not to present and discuss a careful evaluation

### 2017-05-30 draft/paper1_jenny.tex
Edit 1-D profile

@@
           Here, we also compare the distributions with SMF from previous works: 
-          (a): SDSS galaxies at $z{\sim} 0.1$ from \citet{Bernardi2013}; the \mstar{} 
+          (a): SDSS galaxies at $z{\sim} 0.1$ from \citet{Bernardi2017}; the \mstar{} 
           is based on photometry from 2-D \ser{}$+$Exponential model fitting 
@@
     In Section \ref{ssec:mtotal}, we demonstrate that different methods for estimating
-    ``total'' stellar mass.
+    ``total'' \mstar{} can have a large impact at the high-mass end.
 
@@
 
-    Compared to the much discussed ``mass-size'' relation, the \mden{} profiles that 
-    we have derived capture the full information about the structural properties of 
+    Previous discussions about the structural evolution of massive galaxies or the 
+    environmental dependence of their structures often focus on scaling relations,  
+    like the ``\mstar{}-size'' relation. 
+    In this work, we argue that, compared to these scaling relations, the \mden{} 
+    profiles that we have derived capture the full structural information of these 
     massive galaxies.
-    We argue that by studying the shapes of these galaxy profiles directly, we can 
-    by-pass outstanding questions about how to accurately define and measure the 
-    ``sizes'' and ``masses'' of these massive galaxies. 
+    By studying these \mden{} profiles directly, we can by-pass difficult questions 
+    about how to accurately define and measure the ``sizes'' and ``masses'' of these 
+    massive galaxies.
+
     Fig~\ref{fig:avg_prof} shows the median \mden{} profiles\footnote{The median 
@@
     \textbf{individually}. 
-    These median \mden{} profiles have moderate differences in the inner region, 
-    but show significant differences in the outskirts with more massive galaxies 
-    showing more prominent stellar envelopes. 
-    \jenny{This seems out of place here:Most of these massive galaxies ($\ge 10^{11.4} M_{\odot}$) are slowly-rotating 
-    (e.g.\ \citealt{Cappellari13b}) giant ellipticals with ``boxy'' inner isophotal 
-    shapes (e.g.\ \citealt{Kormendy2009}), and slightly flattened inner \mden{} 
-    profiles (e.g.\ \citealt{Lauer07})}. 
-    But in the outskirts, the structure of these galaxies is 
-    \emph{clearly not self-similar}. 
+    These median \mden{} profiles have moderate differences in the inner region. 
+    Within inner 10 kpc, the median \mden{} profile of more massive galaxies 
+    shows slightly higher \mden{} value but similar slope. 
+    These massive galaxies ($\ge 10^{11.4} M_{\odot}$) are known to have quite 
+    uniform properties in the inner region. 
+    At these masses, most of them should be ``slow-rotating'' 
+    (e.g.\ \citealt{Cappellari13b})``core''--elliptical galaxies 
+    (e.g.\ \citealt{Lauer07}) that have ``boxy'' inner isophotal shapes and similar 
+    slopes of the inner surface brightness profiles (e.g.\ \citealt{Kormendy2009,
+    Schombert2015}).
+
+    Meanwhile, in the outskirts, we can notice significant differences where more 
+    massive galaxies have gradually more flattened \mden{} profiles and show more 
+    prominent stellar halos.
+    It is also interesting to see that the distributions of \mden{} profiles show 
+    considerably large scatter at large radius. 
+    Given the \s2n{} of the HSC image at these surface brightness levels, these 
+    scatters should reflect the \textbf{intrinsic scatter of the structures of 
+    massive galaxies in their stellar halos}.
+    Overall, the structures of massive galaxies are \emph{clearly not self-similar}
+    out to 100 kpc. 
     Some of our \mden{} profiles show signs of unphysical truncation and fluctuation 
@@
 
-    Fig~\ref{fig:avg_prof} compares our results with previous work. 
+    The right panel of Fig~\ref{fig:avg_prof} compares our results with previous 
+    works. 
     Most previous studies have relied on stacking techniques to measure surface 

### 2017-05-30 draft/paper1_jenny.tex
Edit 1-D profile

@@
 \def\m2l{{$M_{\star}/L_{\star}$}}
+\def\s2n{{$\mathrm{S}/\mathrm{N}$}}
 \def\mden{{$\mu_{\star}$}}
@@
     massive galaxies in their stellar halos}.
-    Overall, the structures of massive galaxies are \emph{clearly not self-similar}
-    out to 100 kpc. 
+    Overall, the structures of massive galaxies are \textbf{clearly not 
+    self-similar} out to 100 kpc. 
     Some of our \mden{} profiles show signs of unphysical truncation and fluctuation 
@@
 
-    The right panel of Fig~\ref{fig:avg_prof} compares our results with previous 
-    works. 
+    The right panel of Fig~\ref{fig:avg_prof} compares our results with several 
+    previous works. 
+    So far, deep \mden{} profiles of massive galaxies are rarely available. 
+    Even in the nearby universe, it is still not easy to reach to the very outskirt
+    of massive galaxy due to several technical issues (e.g. 
+    \citealt{Capaccioli2015, Iodice2016, Iodice2017, Spavone2017, Mihos2017})
+
+    Although it is relative easier to reach to the very outskirt of massive galaxy 
+    in the nearby universe, the small volume limits the number of available 
+    galaxies at high-mass end. 
+    Most previous studies often focus more on the surface brightness profiles, 
+    and they also depend on stacking techniques or model-dependent method to 
+    study the structure of massive galaxies in their outskirts.
+
     Most previous studies have relied on stacking techniques to measure surface 
@@
     images) from the Carnegie-Irvine Galaxy Survey (CGS, \citealt{CGS1}). 
-    Because this is a very low redshift sample, these profiles are robust to smaller scales, $r=1$ kpc. 
+    Because this is a very low redshift sample, these profiles are accurate to 
+    smaller scales, $r=1$ kpc. 
     The \citet{Huang2013a} profiles show good agreement with ours in the region of 

### 2017-05-30 draft/paper1_jenny.tex
Edit 1-D profile

@@
     Even in the nearby universe, it is still not easy to reach to the very outskirt
-    of massive galaxy due to several technical issues (e.g. 
+    of massive galaxy due to technical difficulties (e.g. 
     \citealt{Capaccioli2015, Iodice2016, Iodice2017, Spavone2017, Mihos2017})
-
-    Although it is relative easier to reach to the very outskirt of massive galaxy 
-    in the nearby universe, the small volume limits the number of available 
+    The small volume of local universe also limits the number of available 
     galaxies at high-mass end.
@@
     and they also depend on stacking techniques or model-dependent method to 
-    study the structure of massive galaxies in their outskirts.
-
-    Most previous studies have relied on stacking techniques to measure surface 
-    brightness profiles out to large radii.
-    So far, the surface brightness profiles of massive galaxies out to such large 
-    radii was mostly derived via image stacking technique that suffers from several 
-    systematic issues (e.g. \citealt{Tal2011, DSouza2015}; but also see:
-    \citealt{Capaccioli2015}); and the \mden{} profiles are even more rarely 
-    available.
+    study the structure of massive galaxies in their outskirts (e.g. 
+    \citealt{Tal2011, DSouza2015}), both of which suffer from several systematic 
+    issues.
 
@@
     smaller scales, $r=1$ kpc. 
-    The \citet{Huang2013a} profiles show good agreement with ours in the region of 
-    overlap and out to 50 kpc. 
+    The \citet{Huang2013a} \mden{} profiles show good agreement with ours in the 
+    region of overlap and out to 50 kpc although their \m2l{} are derived in 
+    slightly different ways.
     CGS images are deeper than SDSS images in the $r$-band, but the median 
@@
     thought to be the progenitors of $z=0$ massive ETGs (e.g. \citealt{Leja2013}).  
-    The median \mstar{} of the \citet{Patel2013} sample is ${\sim} 10^{11.2} M_{\odot}$ 
-    which is lower than our lowest mass bin. 
+    The median \mstar{} of the \citet{Patel2013} sample is 
+    ${\sim} 10^{11.2} M_{\odot}$ which is lower than our lowest mass bin. 
     However, \citet{Patel2013} use the BC03 SSP model which are roughly 0.1 dex 
@@
     particle-tagging technique (e.g. \citealt{Cooper2010}). 
-
     The simulated \mden{} profile is also affected by limited resolution in the 
@@
     the $11.6 <$ \logmtot{} $< 11.8$ bin within 40 kpc. 
-    However, compared with our data, this simulation predicts stellar envelope that
-    are too prominent at this halo mass. 
-    This types of comparisons between our HSC data and predictions from simulations 
-    will help to fine-tune simulations and to also investigate the main physical 
-    mechanisms that drive the assembly of massive galaxies and the build up of 
-    stellar envelopes.
+    However, outside 40 kpc, the particle tagging method seems to predict a too 
+    prominent stellar halo that has much shallower slope compared to our data.
+
+    Although the particle tagging method is not considered the best way to simulate
+    the stellar mass distributions of massive galaxies, this comparison can already 
+    demonstrate the advantages of our \mden{} profiles. 
+    Such comparisons between our HSC data and predictions from more advanced 
+    hydrodynamic simulations will help fine-tune simulations and also investigate 
+    the physical mechanisms that drive the assembly of massive galaxies and the 
+    build up of stellar halos.
 

### 2017-05-31 draft/paper1_jenny.tex
Edit SMF

@@
 
+    As one of the most fundamental statistics of galaxy population, the Stellar 
+    Mass Function (SMF) and its evolution are critical to our understanding of 
+    galaxy evolution.  
     In Section \ref{ssec:mtotal}, we demonstrate that different methods for estimating
-    ``total'' \mstar{} can have a large impact at the high-mass end.
-
-    Different methods for estimating the ``total'' \mstar{} can have a large impact on 
-    the high mass end of the galaxy stellar mass function (e.g. \citealt{Bernardi2013, 
-    DSouza2014, DSouza2015, Bernardi2016a}). 
-    Fig~\ref{fig:mass_complete} shows the SMF computed using both \mtot{} and \mcmodel{}. 
-    As can be seen from this figure, our careful 1-D approach recovers more flux 
-    in massive galaxies than \texttt{cModel}. 
+    ``total'' \mstar{} can lead to quite different results, hence have a large impact 
+    on the high mass end of the galaxy stellar mass function (e.g. 
+    \citealt{Bernardi2013, DSouza2014, DSouza2015, Bernardi2017}).
+    On average, integration of our carefully derived non-parametric \mden{} profile 
+    to 100 kpc (\mtot{}) recovers more light (hence mass) than the \texttt{cModel}
+    method. 
+    At \logmtot{} $>11.6$, the difference sometimes can be larger than 0.2 dex. 
     More importantly, the average difference steadily increases with \mtot{}. 
-    At \logms{} $>11.5$, the difference can be larger than 0.2 dex. 
-    This difference relates to the intrinsic limitation of the \texttt{cModel} method 
-    and also reflects the fact that more massive ETGs tend to have more extended 
-    stellar mass distributions (e.g. \citealt{Graham2003}). 
+    These differences relates to the intrinsic limitation of the \texttt{cModel} 
+    method and also reflects the fact that more massive ETGs tend to have more 
+    extended stellar mass distributions (e.g. higher-\ser{} index, 
+    \citealt{Graham2003}).
+
+    Although we do not attempt to measure SMF, we use Fig \ref{fig:smf}
+    to demonstrate the impacts from missing light and different definitions of 
+    \mstar{}.
+    The left panel of Fig \ref{fig:smf} shows the SMF\footnote{There are actually
+    the volume density distributions, we refer to them as SMFs for convenience 
+    although the incompleteness and other systematics have not been corrected}
+    computed using \mcmodel{} and \mtot{} for both the \rbcg{} and \nbcg{} samples.
+
     Generally speaking, the use of \mtot{} instead of the \mcmodel{} shifts the SMF 
-    towards the higher-mass end and slightly modifies the high-mass slope. 
-    %The impact of missing flux is most prominent for the \rbcg{} sample.
-    For studies about the SMF or other aspects of galaxy evolution based on 
-    \cmodel{}-like photometry or shallower images, these effects can not be neglected.
-
-        Even with deep HSC images, it is non trivial to clearly define and measure the
-    ``total'' \mstar{} for these massive systems. 
-    As discussed in Section~\ref{ssec:mtotal}, our 1-D approach has certain advantages 
-    over the 2-D modeling method and in principle, should capture a the majority of 
-    the stellar mass. 
-    However, even though we extend to 100 kpc, there is no evidence that the profile 
-    drops to zero on these scales. 
-    We now estimate how much extra mass is ``hidden'' beyond the 100 kpc radius. 
-    For this, we integrate the \mden{} profiles out to the detection limit in 
-    surface brightness profile that is defined by the background noise.
-    We will call this the ``maximum mass'' of the galaxy (\mmax{}). 
-    For obvious reasons, we find that \mmax{} is larger than \mtot{} with an average 
-    difference of about ${\sim}0.04$ dex. 
-    The left hand side of Fig \ref{fig:smf} shows differences between \mtot{}
-    and \mmax{}. 
-    On a galaxy-by-galaxy basis, the difference \mmax{}-\mtot{} depends on the slope 
-    of the stellar envelope. 
-    In this work, we have opted to in general use \mtot{} rather than \mmax{} as the 
-    uncertainty on \mmax{} is larger. 
-    However, we have checked that none of our results are changed by replacing \mtot{} 
-    via \mmax{}.
+    towards the higher-mass end without significantly modifying the slope at 
+    high-mass end.
+    Interestingly, the impact of missing flux is more prominent for the \rbcg{} 
+    galaxies whose contribution to the very high-mass end is substantial. 
+    This difference between the \rbcg{} and \nbcg{} samples here may hint that 
+    the \rbcg{} galaxies suffer more from missing light. 
+    We will look into this in details in the following work (Huang\etal in prep.).
+
+    As discussed in Section~\ref{ssec:mtotal}, even with much deeper images from HSC,
+    it is non-trivial to clearly define and measure the ``total'' \mstar{} for 
+    these massive systems, and the \mden{} profiles of these galaxies often extend 
+    well beyond 100 kpc. 
+    We measure \mmax{} by integrating the \mden{} profiles out to the detection 
+    limit that is defined by the background noise.
+    Although the \mden{} profile becomes more uncertain at $>100$ kpc, \mmax{} can
+    provide us certain clue about how much extra mass is ``hidden'' there. 
+    Although the average difference we find is small even at high-mass end 
+    (${\sim}0.03$ dex), on the right panel of Fig \ref{fig:smf}, we can still its 
+    influence on the SMF at high-mass end, where the slope becomes slightly 
+    shallower.
+
+    % TODO: Move this to Paper II
+    %In this work, we have opted to in general use \mtot{} rather than \mmax{} as the 
+    %uncertainty on \mmax{} is larger. 
+    %However, we have checked that none of our results are changed by replacing \mtot{} 
+    %via \mmax{}.
 
@@
     The issues discussed above are currently one of the primary limitations in 
-    determinations of the high-mass end of the SMF (\citealt{Bernardi2016}). 
+    determinations of the high-mass end of the SMF (\citealt{Bernardi2017}). 
     Fig~\ref{fig:mass_complete} illustrated how improved \mstar{} measurement can 
@@
 
+    Overall, this illustrates again that our 1-D approach has certain advantages 
+    over the 2-D modeling method and in principle, should capture the majority of 
+    the total \mstar{}.
+
+    For studies about the SMF or other aspects of galaxy evolution based on 
+    \cmodel{}-like photometry or shallower images, these effects can not be neglected.
 %% ------------------------------------------------------------------------------------ %% 
@@
     Fig~\ref{fig:smf} are dominated by differences in photometry versus 
-    assumptions about stellar population models (e.g. \citealt{Bernardi2016}). 
+    assumptions about stellar population models (e.g. \citealt{Bernardi2017}). 
     However, given that the results that we are comparing assume the same IMF and adopt 
@@
 %% ------------------------------------------------------------------------------------ %% 
+	The 1-D \mden{} profiles are extracted using single band image and the flux-weighted 
+	shape of the isophote.  
+	From the HSC images of these massive
+
 	In addition to the shape of the light profile, we can also 

### 2017-05-31 draft/paper1_jenny.tex
Edit SMF

@@
 
-    How to define and measure the ``total'' mass of a galaxy becomes a critical 
-    question when studying the high-mass end of the galaxy SMF. 
-    The issues discussed above are currently one of the primary limitations in 
-    determinations of the high-mass end of the SMF (\citealt{Bernardi2017}). 
-    Fig~\ref{fig:mass_complete} illustrated how improved \mstar{} measurement can 
-    significantly modifies the SMF. 
-    On the right hand side of Fig~\ref{fig:smf}, we further highlight that 
-    the shape of SMF at high-mass end is quite sensitive to even very small 
-    change of \mstar{}. 
-    We also compare the SMFs of our HSC samples with the following previous studies:
+    On the same figure, we also compare the HSC results with the ones from following 
+    works:
 
     \begin{itemize}
+
+        \item The SMF for $0.15 < z < 0.30$ galaxies from the \texttt{S82-MGC} sample
+            \citep{Leauthaud2016} where the \mstar{} is derived using 
+            \texttt{iSEDfit} on PSF-corrected aperture photometry from 
+            \texttt{S82}.
+            The stellar population model and star-formation history assumptions are 
+            very similar to the ones in this work, except that it uses the 
+            \texttt{BC03} model. 
+            Based on the test results from Appendix \ref{app:sed}, we simply shifts 
+            the SMF to higher \mstar{} by 0.08 dex.
 
@@
 
-        \item The SMF for $z{\sim} 0.1$ SDSS galaxies from \citet{Bernardi2013}. 
+        \item The observed SMF for $z{\sim} 0.1$ SDSS galaxies from 
+            \citet{Bernardi2017}. 
             The total luminosity is based on 2-D \texttt{SerExp} models 
             (\ser{}$+$ Exponential disk model; integrated to infinity) that 
-            recovers much more flux compared to SDSS \cmodel{} magnitudes. 
-            The \m2l{} is also from SED fitting assuming a Chabrier IMF.
-
-        \item The SMF for $0.15 < z < 0.30$ galaxies from the \texttt{S82-MGC} sample
-            \citep{Leauthaud2016} where the \mstar{} is derived using 
-            \texttt{iSEDfit} on PSF-corrected aperture photometry from 
-            \texttt{S82}.
+            recovers much more flux compared to SDSS \cmodel{} magnitudes 
+            (\citealt{Bernardi2013, Meert2015}). 
+            The \m2l{} is adopted from the SED fitting results from the ``dusty'' 
+            model in \citet{Mendel2014} which share similar assumptions of stellar 
+            population models with this work.
 
@@
 
-    Overall, this illustrates again that our 1-D approach has certain advantages 
-    over the 2-D modeling method and in principle, should capture the majority of 
-    the total \mstar{}.
-
+    To appropriately compare SMFs from different works, one needs to carefully 
+    separate the differences in the measurements of luminosity and \m2l{}, and 
+    takes the uncertainties of \mstar{} measurements into account\footnote{
+    Fixed uncertainty of \logms{} can lead to increasingly over-estimated 
+    volume density with \mstar{} due to the very steep slope of SMF at high-mass end.} 
+    (\citealt{Bernardi2010, Bernardi2017}), which is beyond the scope of this work.  
+    Here, we primarily want to visualize the importance of \mstar{} measurements 
+    to the SMF at high-mass end. 
+    All SMFs share similar volume density around \logms{}${\sim}11.0$, but the ones
+    that are based on \texttt{cModel} and small aperture photometry show much 
+    steeper slopes than the HSC \mtot{} one. 
+    The SMF based on single-\ser{} model seems to face the same issue. 
+    We also compare with the $z{\sim}0.1$ SMF from the GAMA survey 
+    (\citealt{Wright2017}) whose luminosity is scaled with the single-\ser{} model
+    from \citet{Kelvin2012}, and its high-mass end behavior is very similar to 
+    the \citet{Leauthaud2016} and the \citet{Moustakas13} ones. 
+    And, once the \m2l{} measurements based on similar assumptions are adopted, 
+    the SDSS SMF using the \texttt{SerExp} models from \citet{Bernardi2017} becomes 
+    surprisingly similar to the HSC \mtot{} one that is not model dependent.
+    Both SMFs highlight the importance of ``missing light'' from different angles. 
+    Right now, the \citet{Bernardi2017} sample and our HSC one have almost no 
+    galaxy in common due to the differences in redshift range, hence it is not 
+    clear whether the \texttt{SerExp} model can indeed describe the flux 
+    distributions of these massive galaxies out to $>100$ kpc. 
+    It would be interesting to look into the application of multi-component 
+    2-D models using HSC images.
+
+    In summary, the result highlights that the SMF at high-mass end is sensitive to 
+    even moderate change of \mstar{}, and illustrates the advantages of deep HSC image
+    and careful 1-D approach in estimating total \mstar{} of massive galaxies.
     For studies about the SMF or other aspects of galaxy evolution based on 
-    \cmodel{}-like photometry or shallower images, these effects can not be neglected.
-%% ------------------------------------------------------------------------------------ %% 
-    It is clear that different analyses lead to very different slopes at high-mass end. 
-    Here, we do not try to evaluate whether the differences displayed in 
-    Fig~\ref{fig:smf} are dominated by differences in photometry versus 
-    assumptions about stellar population models (e.g. \citealt{Bernardi2017}). 
-    However, given that the results that we are comparing assume the same IMF and adopt 
-    similar assumptions about stellar population models, we hypothesize that the 
-    differences in Fig~\ref{fig:smf} are dominated by differences in photometry. 
-    The goal of our of present paper is not to present and discuss a careful evaluation
-    of the high-mass end of the SMF -- this will be presented in a forthcoming paper 
-    once the HSC survey has accumulated more data. 
-    However, this is clearly a topic that warrants further investigation, and careful 
-    photometry measurements from HSC data will shed further light on these questions.
-
+    shallow image or simplified model, these effects can not be neglected.
+    Although we only discuss the high-mass end, this \mstar{} range is crucial for 
+    tracing the evolution of massive galaxies and calibrating numerical simulation 
+    and semi-analytic model as it is very sensitive to the AGN-feedback recipe.   
 %% ------------------------------------------------------------------------------------ %%
@@
     adopted SSP model, the form of IMF, dust extinction law, and details in 
-    the assumption of SFH (e.g.\ \citealt{Bernardi2016b}). 
+    the assumption of SFH (e.g.\ \citealt{Bernardi2017}). 
     For massive galaxies in this sample, the form of the SFH\footnote{We choose 

### 2017-05-31 draft/paper1_jenny.tex
Edit color_ell 1

@@
 %% ------------------------------------------------------------------------------------ %% 
-	The 1-D \mden{} profiles are extracted using single band image and the flux-weighted 
-	shape of the isophote.  
-	From the HSC images of these massive
-
-	In addition to the shape of the light profile, we can also 
-    study the $k$-corrected color profiles and ellipticity profiles 
-    (computed via \texttt{Ellipse}) of these galaxies, and how 
-    they depend on mass and environment.
+	Aforementioned results only use the 1-D \mden{} profiles that are baed on single 
+	band image and the flux-weighted isophotal shape, while more useful information 
+	can be gathered from the HSC images of these massive galaxies.
+	The ellipticity and $k$-corrected optical color profiles are particularly 
+	interesting.
+	We extract ellipticity profile using \texttt{Ellipse} by setting the shape of each 
+	isophote free. 
+	And by applying the $i$-band isophotes to images of other bands in the 
+	forced-photometry way, we can also measure the color profiles too. 
+	We apply Galactic extinction correction and \texttt{iSEDFit} $k$-correction to 
+	both the $g-r$ and $g-i$ color profiles.
+	The PSF smearing effect will make the central isophotal shape rounder than the 
+	real value, while the seeing differences between filters will bias the central 
+	color\footnote{Since the HSC $i$-band always has better seeing, the central color 
+	will become redder when the seeing effect is not corrected.}. 
+	At the same time, it is more difficult to extract reliable ellipticity and 
+	color profiles out to 100 kpc: at low surface brightness region, isophotal shape 
+	becomes unstable and easily affected by any contamination; the color profile in
+	the outskirt also becomes very sensitive to background level and noise level in 
+	either band. 
+	In this work, we will only
+
    These quantities contain interesting information about the physical processes that 
@@
     seeing across different bands).
-    We apply Galactic extinction and $k$-correction to both $g-r$ and $g-i$ color 
-    profiles; the $k$-correction values are also from \texttt{iSEDFit} results.
+
     We show the average ellipticity, $g-r$, and $g-i$ color profiles for the 

### 2017-05-31 draft/paper1_jenny.tex
Edit color_ell 2

@@
 	either band. 
-	In this work, we will only
-
-   These quantities contain interesting information about the physical processes that 
-    shape galaxies. We also want to be sure that we do not introduce any systematic bias in 
-    our mass determinations because of systematic changes in color profile with stellar or 
-    halo mass.
-
-    %\begin{enumerate}
-    %    
-    %    \item To see whether the ellipticity profile depends strongly on environment, 
-    %        and to see whether or not the fact that we use an using average isophotal 
-    %        shape for our our 1-D \mden{} profiles has any impact on our results.
-    %    
-    %    \item To verify that the average color gradient does not depend strongly on 
-    %        the environment and that is not steep enough to cause a problem with our 
-    %        choice the assumption that it is reasonable to use average \m2l for 
-    %        comparing massive galaxies. 
-    %        We extract color profiles by applying the isophotes in $i$-band to images 
-    %        in other bands in ``forced photometry'' manner.  
-    %        
-    %\end{enumerate}
-
-    We compute ellipticities and color profiles in the radial range of 5-50 kpc 
-    (this is the range where we can safely ignore differences in sky subtraction and 
-    seeing across different bands).
+	In this work, we will focus on the median ellipticity and color profiles between 
+	8--60 kpc where we can safely ignore the above issues.
+
+	The ellipticity of the isophote contains information about the 3-D geometry 
+	(e.g. \citealt{Chang2013, Mitsuda2017}) and kinematic (e.g. 
+	\citealt{Cappellari2012, Weijmans2014}) of stars in massive galaxies.  
+	Left of Fig \ref{fig:ell_color} shows the ellipticity profiles of HSC massive 
+	galaxies and highlight the median profiles for the same three \mtot{} bins used 
+	in Fig \ref{fig:avg_prof}. 
+	In general, the ellipticity of massive galaxy slowly increases with radius.
+	One can even notice this trend by directly comparing the shape of galaxy between 
+	SDSS and HSC images (e.g. Fig \ref{fig:sdss_compare}).  
+	More interestingly, the ellipticity profiles clear depend on \mtot{}: 
+	at ${\sim} 10$ kpc, median ellipticities from all three bins are low and similar 
+	($< 0.2$); but more massive galaxies become increasingly more elongated in their
+	stellar halo. 	
+	For the \logms{}$>11.8$ galaxy, its median ellipticity profile becomes steeper 
+	at $>10$ kpc, and the ellipticity steadily increases from $e\le 0.2$ to 
+	$e{\sim} 0.4$ at 50-60 kpc.
+	This is consistent with previous 2-D modeling results from \citet{Huang2013a}.
+	If accreted stars dominate the stellar halos of massive galaxies, this 
+	mass-dependent ellipticity profile may lead us to some insights about the 
+	differences in their assembly history (e.g. average time since last merger, 
+	average merger mass ratio).
+	We also compare our ellipticity profiles with previous ones that are based on 
+	image stacking techniques (the PSF-removed $i$-band from \citealt{Tal2011}, 
+	the concentration galaxies with $11.0<$\logms{}$<11.4$ from 
+	\citealt{DSouza2015}), 
+	We notice that the stacked image sometimes fails to recover the ellipticity 
+	profile, probably due to the uncertainties in aligning galaxies before the 
+	stacking process.
 
@@
 
-    We find that in general, the ellipticities of massive galaxies increases with 
-    radius from $e\le 0.2$ around 5-10 kpc to $e{\sim} 0.3$ at 40-50 kpc. 
-    This is consistent with previous 2-D modeling results from \citet{Huang2013a}. 
-    The ellipticity profiles of the \mtot{}-matched samples are very similar at 
-    $r<50$ kpc (2-3$\times R_{\mathrm{e}}$ for their \mstar{}). 
-    However, for the \minn{}-matched samples, the \rbcg{} galaxies have higher 
-    ellipticity than the \nbcg{} ones at $r > 10$ kpc, while their inner ellipticity 
-    profiles are very similar.  
-    This further hints that massive central galaxies in different halos but with 
-    similar ``in-situ'' mass may experience different late-time merging histories. 
-    Overall, the relative low ellipticity value and the fact that the ellipticity 
-    gradients are shallow lead us to conclude that the use of an average 
-    isophotal ellipticity is fine for this present study.
-
-    Previous attempts to constrain ellipticity gradients have relied on image 
-    stacking techniques (e.g. \citealt{Tal2011}, \citealt{DSouza2015}). 
-    Compared to our measurements, we find that stacked ellipticity profiles tend to 
-    underestimate the ellipticity in the outskirt. 
+    % TODO: Move this to Paper II 
+    %The ellipticity profiles of the \mtot{}-matched samples are very similar at 
+    %$r<50$ kpc (2-3$\times R_{\mathrm{e}}$ for their \mstar{}). 
+    %However, for the \minn{}-matched samples, the \rbcg{} galaxies have higher 
+    %ellipticity than the \nbcg{} ones at $r > 10$ kpc, while their inner ellipticity 
+    %profiles are very similar.  
+    %This further hints that massive central galaxies in different halos but with 
+    %similar ``in-situ'' mass may experience different late-time merging histories. 
+    %Overall, the relative low ellipticity value and the fact that the ellipticity 
+    %gradients are shallow lead us to conclude that the use of an average 
+    %isophotal ellipticity is fine for this present study.
+
     Ellipticity profiles contain additional information about the assembly histories 

### 2017-06-01 draft/paper1_jenny.tex
Edit ell_color 3

@@
 	\citealt{Cappellari2012, Weijmans2014}) of stars in massive galaxies.  
-	Left of Fig \ref{fig:ell_color} shows the ellipticity profiles of HSC massive 
-	galaxies and highlight the median profiles for the same three \mtot{} bins used 
-	in Fig \ref{fig:avg_prof}. 
+	The left panel of Fig \ref{fig:ell_color} shows the ellipticity profiles of HSC 
+	massive galaxies and highlight the median profiles for the same three \mtot{} 
+	bins used in Fig \ref{fig:avg_prof}. 
 	In general, the ellipticity of massive galaxy slowly increases with radius.
@@
 
-    We show the average ellipticity, $g-r$, and $g-i$ color profiles for the 
-    \mtot{}-matched (\minn{}-matched) samples of \rbcg{} and \nbcg{} galaxies on the 
-    left (right) side of \ref{fig:ell_color}. 
-    We also compare our results with previous work based on stacking SDSS galaxies 
-    (e.g. \citealt{LaBarbera2010, Tal2011, DSouza2014}).
+    As for the color profiles, it is well known that massive elliptical galaxies 
+    have shallow and negative color gradient that reflects radial variation of 
+    stellar population (e.g.\ \citealt{Carollo1993, LaBarbera2012}) and contains 
+    information about the assembly history of stellar halos (e.g. 
+    \citealt{Hirschmann2015}). 
+    The right panels of Fig \ref{fig:ell_color} show the $k$-corrected $g-r$ and 
+    $g-i$ color profiles and the median profiles in three \mtot{} bins. 
+    As expected, all median color profiles show smooth and shallow negative 
+    gradients, but we do not find evidence for mass-dependence here. 
+    We also compare our results with the stacked color profiles from  
+    \citealt{LaBarbera2010}\footnote{Use the median color profiles of high-mass 
+    ETGs; the original profile is in unit of $R_{\mathrm{e}}$, we use a typical 
+    $R_{\mathrm{e}}=8.0$ kpc to convert it into kpc unit.} and 
+    \citealt{DSouza2014}.
+    The median color profiles from HSC images are systematically steeper than the 
+    stacked SDSS ones. 
+    Considering the differences in response curves of HSC and SDSS filters, and 
+    the uncertainties of color measurements, the HSC $g-r$ color profiles are 
+    consistent with those based on SDSS images. 
+    For the $g-i$ profiles, the HSC ones still show steeper gradients. 
+    The SDSS $i$-band suffers from the so-called ``red-halo'' effect of 
+    (e.g. \citealt{Wu2005}, \citealt{Tal2011}) that could lead to redder color in 
+    the low surface brightness outskirt of galaxy.
+    HSC $i$-band image do not suffer from this effect (thanks to thick CCDs), 
+    therefore can help provide more accurate color estimates.
+    For the ones from \citet{LaBarbera2010}, uncertainty of $R_{\mathrm{e}}$ 
+    measurements could also ``smooth'' the color gradients.
+    The relative steeper color profiles have been observed in very nearby massive 
+    ETGs individually.  
+    On Fig \ref{fig:ell_color}, we also compare with the $g-r$ color profiles of 
+    NGC 4472 (\citealt{Mihos2013}) and NGC 4365 (\citealt{Mihos2017})\footnote{
+    Both are converted from $B-V$ colors}, and the $g-i$ profile of NGC 1399 
+    (\citealt{Iodice2016}). 
+    These individual profiles show similar color gradients with the HSC median ones.
+
+    % TODO: Move to discussion
+    %Ellipticity profiles contain additional information about the assembly histories 
+    %and in future work, it would be of interest to compare our ellipticity profiles 
+    %with predictions from hydrodynamic simulations such as Illustris 
+    %\citealt{Vogelsberger2014}, \citealt{Genel2014}) or \textit{Horizon-AGN} 
+    %(\citealt{Dubois2014}).
 
@@
     %isophotal ellipticity is fine for this present study.
-
-    Ellipticity profiles contain additional information about the assembly histories 
-    and in future work, it would be of interest to compare our ellipticity profiles 
-    with predictions from hydrodynamic simulations such as Illustris 
-    (\citealt{Vogelsberger2014}, \citealt{Genel2014}) or \textit{Horizon-AGN} 
-    (\citealt{Dubois2014}).
-
-    In terms of color gradients, we find shallow and negative gradients of median 
-    $g-r$ and $g-i$ color profiles for both \rbcg{} and \nbcg{} galaxies. 
-    {\bf Can we also look as a function of stellar mass?}
-    For both \mtot{}- and \minn{}-matched samples, we find no significant difference
-    in their median color profiles, which supports the assumption of using single 
-    average \m2l{} value to estimate \mden{} profiles.
-    The median $g-r$ color profiles are quite consistent with those based on 
-    stacked SDSS images. 
-    For the $g-i$ profiles, the HSC ones show steeper gradients than the SDSS ones, 
-    however, it is important to point out that the SDSS $i$-band suffers from the 
-    so-called ``red-halo'' effect of (e.g. \citealt{Wu2005}, \citealt{Tal2011}) that 
-    could make the SDSS color appears redder. 
-    In contrast, HSC $i$-band image do not suffer from this effect (thanks to thick 
-    CCDs), therefore can help provide more accurate color estimates.
+    %We show the average ellipticity, $g-r$, and $g-i$ color profiles for the 
+    %\mtot{}-matched (\minn{}-matched) samples of \rbcg{} and \nbcg{} galaxies on the 
+    %left (right) side of \ref{fig:ell_color}. 
+    %We also compare our results with previous work based on stacking SDSS galaxies 
+    %(e.g. \citealt{LaBarbera2010, Tal2011, DSouza2014}).
+
+    %In terms of color gradients, we find shallow and negative gradients of median 
+    %$g-r$ and $g-i$ color profiles for both \rbcg{} and \nbcg{} galaxies. 
+    %For both \mtot{}- and \minn{}-matched samples, we find no significant difference
+    %in their median color profiles, which supports the assumption of using single 
+    %average \m2l{} value to estimate \mden{} profiles.
 %% ------------------------------------------------------------------------------------ %%

### 2017-06-01 draft/paper1_jenny.tex
Edit summary 1

@@
 
-    In this work, we study how environment (halo mass) affects the stellar mass density 
-    profiles of massive central galaxies using deep images from the Subaru HSC 
-    survey. 
+    In this work, we study how the stellar mass density profiles and other structural
+    properties of massive central galaxies depend on their total stellar mass using 
+    deep images from the Subaru HSC survey. 
     With the help of this high-quality and wide area data set, we directly map the 
@@
     We group massive central galaxies into two categories based on their host halo 
-    mass (\mhalo{}$\simgt 10^{14.2} M_{\odot}$ and \mhalo{}$\simlt 10^{14} M_{\odot}$). 
+    mass (\mhalo{}$\simgt 10^{14.0} M_{\odot}$ and \mhalo{}$\simlt 10^{14} M_{\odot}$)
+    and three bins of \mtot{}.  
     Our main results are:
@@
             significantly underestimated with shallow imaging data such as SDSS and/or 
-            imperfect model assumption (e.g. the \texttt{cModel} or single-\ser{}) 
-            are used. 
+            oversimplified model assumption (e.g. the \texttt{cModel} or single-\ser{}). 
             In contrast to previous work, our results do not depend on stacking or any 
             parametric models. 
-            Moreover, the level of such underestimation could also depend on the 
-            stellar mass and on halo mass. 
+            Moreover, the level of such underestimation also depends on their \mtot{}.
+            More massive galaxies tend to have larger amount of light missing in the 
+            outskirt.  
+            The level of underestimation also shows evidence of \mhalo{}-dependence. 
+            The central galaxies of \mhalo{}$\simgt 10^{14.0} M_{\odot}$ halos suffer
+            more from this issue. 
             This should be carefully taken into account when discussing topics such 

### 2017-06-01 draft/paper1_jenny.tex
Edit summary

@@
 
-    By using deep imaging from the HSC survey we have shown that the stellar mass 
-    density profiles of massive central galaxies depend systematically on the mass 
-    of their host dark matter halos. 
-    Here we discuss the physical origin, scientific implications, and potential 
-    caveats of this result.
-
-%% ------------------------------------------------------------------------------------ %%
-
+    With the help of deep HSC images, we trace the stellar mass distributions of 
+    $0.3 < z < 0.5$ massive galaxies out to $>100$ kpc, and reveal the mass-dependent 
+    nature of their stellar halos.
+    Here we briefly discuss the physical origin, scientific implications, and potential 
+    caveats of these results.
+
+    % TODO: Move to Paper II
+    %By using deep imaging from the HSC survey we have shown that the stellar mass 
+    %density profiles of massive central galaxies depend systematically on the mass 
+    %of their host dark matter halos.
+
+%% ------------------------------------------------------------------------------------ %% 
 \subsection{The ``Two phase'' Formation Scenario of Massive Galaxies and the 
@@
 
-    {\bf Do we need two different sections and two different radial profile figures?}
-
-    Our results are consistent with the picture that massive central galaxies form via 
-    a ``two-phase'' scenario. 
-    According to this theory, the cores of massive galaxies were formed at $z{\sim} 2$ 
-    during an intense period of in-situ star formation. 
-    The outskirts of massive galaxies are then built up via a more gradual second 
-    phase of evolution (the ``ex-situ'' phase) which is dominated by mass growth via 
-    the accretion of satellite systems. 
-    Non-dissipative minor mergers mostly deposit stars on the outskirts of the 
-    centrals and do not have large impact on the central \mden{} profile 
-    (e.g. \citealt{Oogi2013, Bedorf2013}). 
-    Hence, according to this picture, the outer stellar envelopes of massive centrals 
-    should correlate with the masses of their host halos, in qualitative agreement with
-    our findings.
-
-    State of the art hydrodynamic simulations suggest that massive dark matter halos 
-    have central galaxies that have outer stellar envelopes with shallow slopes 
-    (e.g. \citealt{Pillepich2014}). 
-    This is consistent with the results in Fig \ref{fig:prof_1}.
+    The mass-dependent nature we find in the \mden{} and ellipticity profiles of 
+    massive galaxies are consistent with the two-phase formation scenario. 
+    According to this theory, the ``cores'' of massive central galaxies are formed 
+    at $z{\sim} 2$ during an intense period of in-situ star formation. 
+    The outskirts of massive galaxies are then built up through a more gradual second 
+    phase of evolution (the ``ex-situ'' phase) that is dominated by mass assembly via 
+    accretion and merger.
+    Non-dissipative mergers, especially the minor ones, mostly deposit stars in the 
+    outskirts of the centrals and do not have large impact on the central \mden{} 
+    profile (e.g. \citealt{Oogi2013, Bedorf2013}).
+    Given the stochastic nature of the merging process, it is easy to understand why 
+    the \mden{} profiles of massive galaxies are similar in the inner region but show
+    large and continuous scatter in the outskirt.
+
+    State of the art hydrodynamic simulations of massive galaxy formation predict 
+    that the fraction of accreted stars should strongly depend on their stellar mass 
+    (e.g. \citealt{RodriguezGomez2016} \addref{}). 
+    The increasingly more prominent stellar halos in more massive galaxies could 
+    reflect this point, assuming the stars in the outskirts are dominated by accreted 
+    ones.  
+    The negative color gradients we see in these massive galaxies may support this 
+    assumption. 
+    The slightly bluer color in their outskirts are consistent with the picture that 
+    the stars there are from less massive galaxies on the ``red-squence''.
+
+    % Ellipticity of accreted stars.
+
+    It would be interesting to make detailed comparison with these simulations to see
+    if they can reproduce the observed
+
+    % TODO: Move to paper II     
+    %State of the art hydrodynamic simulations suggest that massive dark matter halos 
+    %have central galaxies that have outer stellar envelopes with shallow slopes 
+    %(e.g. \citealt{Pillepich2014}). 
+    %This is consistent with the results in Fig \ref{fig:prof_1}.
+
+    %Hence, according to this picture, the outer stellar envelopes of massive centrals 
+    %should correlate with the masses of their host halos, in qualitative agreement with
+    %our findings.
+
+%% ------------------------------------------------------------------------------------ %% 
+\subsection{Aperture Masses as Proxies of In-Situ and Accreted Stars}
+    \label{ssec:insitu}
 
@@
 
-    {\bf Have we looked at delta M as a function of Mtot?  I think that would be useful 
-    for comparison with the Oser papers, for instance. }
+    % TODO: Comparison with Illustris.
 
@@
 
-        \item We show that the \mden{} profiles of massive galaxies are generally quite 
-            smooth out to 10 kpc but that there is a large but continuous scatter in the 
-            amount of light in their outskirts. 
-            {\bf KEEP? We argue that ``cD'' galaxies simply represent the tail end of a 
-            distribution but that they are not a distinct class of massive galaxies.}
-
-        \item {\bf How do profiles depend on Mstar?}
+        \item We show that the \mden{} profiles of massive galaxies within inner 
+            10-20 kpc generally show similar slopes and have relative small scatter. 
+            Meanwhile, there is a large but continuous scatter in the outskirts of 
+            \mden{} profiles that suggests the stellar halos of these massive galaxies 
+            are not self-similar. 
+            Galaxies with higher \mtot{} show more prominent stellar halos and have 
+            shallower outer \mden{} slopes than the less massive ones. 
+            Assuming the stellar halos are dominated by accreted stars, the result is 
+            in consistent with the two-phase formation picture of massive galaxies.
+
+        \item We show that, on average, massive galaxies have positive ellipticity 
+            gradient out to at least 60 kpc. 
+            The average ellipticity profiles also depend on \mtot{}: more massive 
+            galaxies tend to have steeper ellipticity gradients and become more 
+            elongated in the accreted stellar halo. 
+            On the other hand, the average $g-r$ and $g-i$ color gradients do not 
+            show clear dependence on \mtot{} within 10-60 kpc.
 

### 2017-06-01 draft/paper1_jenny.tex
Edit summary

@@
 	$e{\sim} 0.4$ at 50-60 kpc.
-	This is consistent with previous 2-D modeling results from \citet{Huang2013a}.
+	This is consistent with studies of nearby massive galaxies, both from 1-D 
+	ellipticity profiles and 2-D modeling results \citep{Gonzalez2005, 
+	Huang2013a, Spavone2017}.
+	Although this phenomenon was well-documented, clear evidence of mass-dependent
+	ellipticity profiles and the potentially anti-correlated slopes of \mden{} and 
+	ellipticity profiles has not been identified.
 	If accreted stars dominate the stellar halos of massive galaxies, this 
@@
 	average merger mass ratio).
+	Previous simulations often focused on reproducing the rounder average shape 
+	and slow-rotating nature of massive ETGs (e.g. \citealt{Wu2014}), the projected 
+	ellipticity profiles and their correlations with the kinematic of stars and 
+	merging history have not been well explored. 
 	We also compare our ellipticity profiles with previous ones that are based on 
@@
 \subsection{The ``Two phase'' Formation Scenario of Massive Galaxies and the 
-            Build-Up of Outer Envelopes}
+            Build-Up of Outer Halos}
     \label{ssec:twophase}
@@
     State of the art hydrodynamic simulations of massive galaxy formation predict 
-    that the fraction of accreted stars should strongly depend on their stellar mass 
-    (e.g. \citealt{RodriguezGomez2016} \addref{}). 
-    The increasingly more prominent stellar halos in more massive galaxies could 
-    reflect this point, assuming the stars in the outskirts are dominated by accreted 
-    ones.  
-    The negative color gradients we see in these massive galaxies may support this 
-    assumption. 
+    that the fraction of accreted stars should strongly increase with their stellar 
+    mass and the ``ex-situ'' component dominate the stellar halo (e.g.
+    \citealt{RodriguezGomez2016} \addref{}). 
+    This picture is supported by the increasingly more prominent stellar halos in 
+    more massive galaxies and the negative color gradients we see in these massive 
+    galaxies. 
     The slightly bluer color in their outskirts are consistent with the picture that 
     the stars there are from less massive galaxies on the ``red-squence''.
+
+    Also under this picture, the shape of the stellar halo should keep fossil record
+
+    As for the shape of the stellar halo,
+
+    Tidal shocking and stripping during merger with the cD galaxy: the massive galaxies in the substructure generally interact with the cluster centre and the cD galaxy on near-radial orbits
 

### 2017-06-01 draft/paper1_jenny.tex
Edit Discussion 1

@@
 %% ------------------------------------------------------------------------------------ %% 
-\subsection{The ``Two phase'' Formation Scenario of Massive Galaxies and the 
-            Build-Up of Outer Halos}
+\subsection{The Formation of Massive Galaxies and the Assembly of Outer Halos}
     \label{ssec:twophase}
@@
     mass and the ``ex-situ'' component dominate the stellar halo (e.g.
-    \citealt{RodriguezGomez2016} \addref{}). 
+    \citealt{Oser2010, Cooper2013, Dubois2013, LeeYi2013, Hirschmann2015,
+    RodriguezGomez2016}). 
     This picture is supported by the increasingly more prominent stellar halos in 
@@
 
-    Also under this picture, the shape of the stellar halo should keep fossil record
-
-    As for the shape of the stellar halo,
-
-    Tidal shocking and stripping during merger with the cD galaxy: the massive galaxies in the substructure generally interact with the cluster centre and the cD galaxy on near-radial orbits
-
-    % Ellipticity of accreted stars.
-
-    It would be interesting to make detailed comparison with these simulations to see
-    if they can reproduce the observed
+    Also under this picture, the shape of the stellar halo should preserve information
+    about the merging history and even the dark matter halos. 
+    Simulations show that, for slow-rotating massive ETGs experienced multiple 
+    minor-mergers, the shape of the stellar and dark matter halos are closely 
+    correlated (e.g. \citealt{Wu2014}). 
+    However, simulation like the one in \citet{Wu2014} predicts that more massive 
+    galaxies should be rounder in the outskirt.
+    This difference deserves more investigations using stellar kinematics and 
+    simulations. 
+    It may reflect the importance of major merger in shaping the most massive 
+    galaxies. 
+    Major merger with central galaxy of massive halo often happens on near-radial 
+    orbits, hence leads to (e.g. \citealt{Murante2007}) radially biassed stellar 
+    orbits and more elongated halo.
+
+    At a larger scale, the distribution of satellites in massive halo is known to 
+    intrinsically align with the central galaxy (e.g. \citealt{Brainerd2005, 
+    Yang2006b, NiedersteOstholt2010, HuangMandelbaum2016}), and the alignment signal
+    is stronger for more massive galaxies (e.g. \citealt{Hirata2007}).
+    The fact that more massive central galaxies have steeper ellipticity profiles 
+    and become increasingly more elongated in the outskirt may help understand 
+    the physical causes of the intrinsic alignment. 
+    Moreover, the shape of the dark matter halo can now be estimated using both 
+    satellite distributions and weak lensing analysis (\citealt{ClampittJain2016}). 
+    It is interesting to point out that the most recent measurement by 
+    \citet{Shin2017} around SDSS clusters show a halo axis-ratio of ${\sim}0.55$, 
+    which is only slightly more elongated than the stellar halo of galaxies in our 
+    highest \mtot{} bin.
 
@@
 
-    Meanwhile, these simulation also point out that the fraction of accreted stars 
-    increases steeply with total \mstar{} and that the ``ex-situ'' component
-    starts to dominate the \mden{} profiles around $R_{\mathrm{e}}$ for 
-    \logms{}$\geq 11.5$ galaxies. 
-    In this work, we find that the median \mden{} profiles of \rbcg{} and \nbcg{} 
-    samples start to show differences around 15-20 kpc, which is close to 
-    their $R_{\mathrm{e}}$. 
-    Furthermore, the environmental dependence of our median \mden{} profiles 
-    becomes more significant in our highest \mtot{} bin (see Fig \ref{fig:prof_4}). 
-    These results all align with the picture that the \mhalo{}-dependence of the 
-    \mden{} profiles of massive galaxies is driven by the variations in the 
-    ``ex-situ'' component at large radii.
+    Recent hydrodynamic simulations of galaxy formation often separate the stars in 
+    galaxy into the \textit{in-situ} and accreted components. 
+    In simulation, the \textit{in-situ} component is often defined as the stars formed 
+    in the halo of the ``main progenitor''.  
+    The spatial distribution, kinematic, and stellar population properties of both 
+    components become important theoretical predictions to be examined. 
+    Among them, the fraction of the accreted component and its relation with stellar 
+    mass is the most fundamental one. 
+    However, on the observational side, separation of these two physical components 
+    is extremely difficult. 
+    So far, we have
+
+    % TODO: Move to Paper II
+    %Meanwhile, these simulation also point out that the fraction of accreted stars 
+    %increases steeply with total \mstar{} and that the ``ex-situ'' component
+    %starts to dominate the \mden{} profiles around $R_{\mathrm{e}}$ for 
+    %\logms{}$\geq 11.5$ galaxies. 
+    %In this work, we find that the median \mden{} profiles of \rbcg{} and \nbcg{} 
+    %samples start to show differences around 15-20 kpc, which is close to 
+    %their $R_{\mathrm{e}}$. 
+    %Furthermore, the environmental dependence of our median \mden{} profiles 
+    %becomes more significant in our highest \mtot{} bin (see Fig \ref{fig:prof_4}). 
+    %These results all align with the picture that the \mhalo{}-dependence of the 
+    %\mden{} profiles of massive galaxies is driven by the variations in the 
+    %``ex-situ'' component at large radii.
 

### 2017-06-01 draft/paper1_jenny.tex
Edit Discussion 2

@@
           \textbf{Lower-right panel} is for $g-i$ color profiles. 
-          We compare our results with those from \citet{Tal2011} based on stacking 
+          We compare our results with those from (1) \citet{Tal2011} based on stacking 
           large samples of luminous red galaxies in SDSS at $z{\sim} 0.4$ 
-          (solid red line on left panel). 
-          We also compare with the results from a stacking analysis of nearby massive 
+          (solid red line on left panel), 
+          (2) the results from a stacking analysis of nearby massive 
           galaxies with high concentration index ($C>2.6$) in 
-          \citet[][blue dash lines on the left and upper-right panels]{DSouza2014}. 
-          Finally, we also compare with the average $g-r$ and $g-i$ color profiles 
+          \citet[][blue dash lines on the left and upper-right panels]{DSouza2014}, 
+          (3) and the average $g-r$ and $g-i$ color profiles 
           from a large sample of nearby elliptical galaxies in \citet[][blue, solid 
           lines on both right panels]{LaBarbera2010}.
+          For color profiles, we also compare with deep observations of a few nearby 
+          massive ETGs: the $g-r$ color profiles of NGC 4472 (\citealt{Mihos2013}) 
+          and NGC 4365 (\citealt{Mihos2017}), and the $g-i$ profile of NGC 1399 
+          (\citealt{Iodice2016})
           }
@@
           \textbf{Left:}
+          Relation between \mtot{} and the fraction of \mstar{} within 10 to 100 kpc, 
+          which is used here as proxy of the fraction of accreted stars. 
+          The typical uncertainties of \mtot{} and the mass fraction are shown in 
+          upper-left corner. 
+          This relation is compared with the relation between \mstar{} and the fraction
+          of accreted stars derived from the Illustris simulation at $z=0$ 
+          (Fig 4 in \citealt{RodriguezGomez2016}; grey solid and dashed lines). 
+          \textbf{Right:}
           Comparison of the median \mden{} profiles of massive galaxies in the 
@@
           Ultra-Deep Field.
-          \textbf{Right:}
-          Relation between \mtot{} and the fraction of \mstar{} within 10 to 100 kpc, 
-          which is used here as proxy of the fraction of accreted stars. 
-          The typical uncertainties of \mtot{} and the mass fraction are shown in 
-          upper-left corner. 
-          This relation is compared with the relation between \mstar{} and the fraction
-          of accreted stars derived from the Illustris simulation at $z=0$ 
-          (Fig 4 in \citealt{RodriguezGomez2016}; grey solid and dashed lines). 
           }
@@
 %% ------------------------------------------------------------------------------------ %% 
-\subsection{Aperture Masses as Proxies of In-Situ and Accreted Stars}
+\subsection{Aperture Masses as Proxies of the \textit{In-situ} and Accreted Stars}
     \label{ssec:insitu}
@@
     is extremely difficult. 
-    So far, we have
+    Recently, deep surveys of nearby disk galaxies start to provide constraints of 
+    their accreted fraction using the distinctive halo components. 
+    For more massive ETGs, efforts so far all depend on multi-component model fitting
+    and image stacking analysis (e.g. \citealt{Huang2013a, dSouza2014, Spavone2017}).
+    In this work, we propose that \mstar{} within different physical apertures could 
+    be explored as potential proxies of masses in \textit{in-situ} and accreted 
+    components.  
+    Given the behaviours of the \mden{} profiles shown in Fig \ref{fig:avg_prof}, 
+    we propose to use mass within 10 kpc (\minn{}) and 100 kpc (\mtot{}) as proxies 
+    of the \textit{in-situ} and total \mstar{}.
+
+    On the left panel of Fig \ref{fig:discussion_1}, we plot the relation between 
+    \mtot{} and the fraction of mass between 10 and 100 kpc (as proxy of the mass of 
+    the accreted component), and compare with the relation between \mstar{} and 
+    accreted fraction derived from the Illustris simulation 
+    (\citealt{RodriguezGomez2016}). 
+    It is intriguing to see that, our proxy of accreted mass not only strongly 
+    correlates with \mtot{}, the relation is surprisingly consistent with the 
+    prediction from \citet{RodriguezGomez2016}. 
+    Given the different definition of total stellar mass,
 
@@
 
-    We now investigate to what degree our assumption that the inner 10 kpc \mstar{}
-    corresponds to an in-situ mass.    
-    Fig \ref{fig:discussion_1} compares the median \mden{} profiles of the 
-    galaxies in two \mtot{} bins 
-    ($11.4\leq$\logmtot{}$<11.6$ and $11.6\leq$\logmtot{}$<11.8$) with 
-    (1) the median \mden{} profiles of massive ETGs at $1.0 < z < 1.5$ in
+    To see whether \minn{} can reasonably represent the \textit{in-situ} mass, we 
+    compare the average \mden{} profiles of HSC massive galaxies in two \mtot{} 
+    bins (Left panel of Fig \ref{fig:discussion_1}, 
+    $11.4\leq$\logmtot{}$<11.6$ and $11.6\leq$\logmtot{}$<11.8$) with:
+
+    \begin{enumerate}
+
+        \item The median \mden{} profiles of massive ETGs at $1.0 < z < 1.5$ in
             \citealt{Patel2013} since they are considered as the progenitors of 
-    ${\sim} 10^{11.5} M_{\odot}$ ETGs at $z=0$.    
-    (2) the inner components of $z{\sim} 0$ ellipticals from 2-D decomposition 
-    (\citealt{Huang2013a}).
-    As proxy of the in-situ components, \citet{Huang2013b} showed they are 
-    structurally similar to the compact ``red nuggets'' at high-$z$. 
-    (3) the ``in-situ'' components of simulated central galaxies in massive halos 
-    from \citet{Cooper2013} (the inner ${\sim} 5$ kpc is quite uncertain due to the 
-    resolution).  
+            ${\sim} 10^{11.5} M_{\odot}$ ETGs at $z=0$ and their inner region 
+            should be dominated by \textit{in-situ} stars.
+
+        \item The inner components of $z{\sim} 0$ ellipticals from 2-D 
+            decomposition (\citealt{Huang2013a}).
+            As proxy of the \textit{in-situ} component, \citet{Huang2013b} showed 
+            that they are structurally similar to the compact ``red nuggets'' at 
+            high-$z$.
+
+        \item The \textit{in-situ} components of simulated central galaxies in 
+            massive halos from \citet{Cooper2013} (the inner ${\sim} 5$ kpc is 
+            quite uncertain due to the resolution).  
+            These \mden{} profiles are generated using the particle tagging 
+            method (see \citealt{Cooper2010})
+
+    \end{enumerate}
+
     The comparison confirms that \minn{} should be reasonable proxy of the 

### 2017-06-01 draft/paper1_jenny.tex
Edit Discussion 3

@@
     prediction from \citet{RodriguezGomez2016}. 
-    Given the different definition of total stellar mass,
+    Given the limitations of the Illustris simulation and the different definitions
+    of total stellar mass, the almost perfect consistency may well be a coincidence. 
+    However, it is encouraging to see that our arbitrary choices of aperture masses 
+    can already reproduce similar slope and scatter of this relation. 
+    Right now, there are other hydrodynamic simulations that predict significantly 
+    different mass fraction of accreted stars at fixed \mstar{} (e.g. 
+    \citealt{Lackner2012, Qu2017}). 
+    Therefore, it will be very useful to perform more detailed comparisons with 
+    these simulations and explore the possibilities of using certain aperture mass 
+    to trace the \textit{in-situ} component.
 
@@
 
-    To see whether \minn{} can reasonably represent the \textit{in-situ} mass, we 
-    compare the average \mden{} profiles of HSC massive galaxies in two \mtot{} 
-    bins (Left panel of Fig \ref{fig:discussion_1}, 
+    To further check whether \minn{} can reasonably represent the \textit{in-situ} 
+    mass, we compare the average \mden{} profiles of HSC massive galaxies in two 
+    \mtot{} bins (Left panel of Fig \ref{fig:discussion_1}, 
     $11.4\leq$\logmtot{}$<11.6$ and $11.6\leq$\logmtot{}$<11.8$) with:

### 2017-06-01 draft/paper1_jenny.tex
Edit Discussion 4

@@
 
-    The comparison confirms that \minn{} should be reasonable proxy of the 
-    ``in-situ'' mass\footnote{We convert these \mden{} profiles to the same 
-    Chabrier IMF; but there are still differences in median \mstar{} and 
-    details in the \m2l{} estimates}.  
-    More importantly, it shows that the \mden{} profile at 
-    $\mathrm{R} > 15$-20 kpc is likely dominated by stars that are not related 
-    to the ``in-situ'' processes.
-
     We also compare with a uniquely massive BCG at high redshift: 
@@
     Its \mden{} profile follows the median profile of $11.6\leq$\logmtot{}$<11.8$ 
-    massive galaxies nicely inside 10-15 kpc, but becomes much steeper in the outskirt.  
-    This unique object may present an interesting case where the inner ``core'' of a 
-    massive BCGs is already in pace at $z{\sim} 1$ when its extended envelope is still
-    under construction.
-    More BCGs like this at $0.5 < z < 1.0$ can shed light on this intriguing 
-    process, and help us confirm whether the environmental dependence of structure 
-    has already emerged within massive galaxies at higher redshift 
-    (e.g. \citealt{Papovich2012})
-
-    % TODO: Comparison with Illustris.
-
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %% 
-\subsection{What is the ``Total Mass'' of Massive Galaxies?}
-
-    Even with deep HSC images, it is non trivial to clearly define and measure the
-    ``total'' \mstar{} for these massive systems. 
-    As discussed in Section~\ref{ssec:mtotal}, our 1-D approach has certain advantages 
-    over the 2-D modeling method and in principle, should capture a the majority of 
-    the stellar mass. 
-    However, even though we extend to 100 kpc, there is no evidence that the profile 
-    drops to zero on these scales. 
-    We now estimate how much extra mass is ``hidden'' beyond the 100 kpc radius. 
-    For this, we integrate the \mden{} profiles out to the detection limit in 
-    surface brightness profile that is defined by the background noise.
-    We will call this the ``maximum mass'' of the galaxy (\mmax{}). 
-    For obvious reasons, we find that \mmax{} is larger than \mtot{} with an average 
-    difference of about ${\sim}0.04$ dex. 
-    The left hand side of Fig \ref{fig:smf} shows differences between \mtot{}
-    and \mmax{}. 
-    On a galaxy-by-galaxy basis, the difference \mmax{}-\mtot{} depends on the slope 
-    of the stellar envelope. 
-    In this work, we have opted to in general use \mtot{} rather than \mmax{} as the 
-    uncertainty on \mmax{} is larger. 
-    However, we have checked that none of our results are changed by replacing \mtot{} 
-    via \mmax{}.
-
-    How to define and measure the ``total'' mass of a galaxy becomes a critical 
-    question when studying the high-mass end of the galaxy SMF. 
-    The issues discussed above are currently one of the primary limitations in 
-    determinations of the high-mass end of the SMF (\citealt{Bernardi2017}). 
-    Fig~\ref{fig:mass_complete} illustrated how improved \mstar{} measurement can 
-    significantly modifies the SMF. 
-    On the right hand side of Fig~\ref{fig:smf}, we further highlight that 
-    the shape of SMF at high-mass end is quite sensitive to even very small 
-    change of \mstar{}. 
-    We also compare the SMFs of our HSC samples with the following previous studies:
-
-    \begin{itemize}
-
-        \item The SMF derived from a SDSS-\textit{GALEX} sample of $z{\sim} 0.1$ 
-            galaxies from \citet{Moustakas13}. 
-            Here, the total luminosity is based on the SDSS \cmodel{} magnitude. 
-            The \m2l{} is derived via SED fitting using \texttt{iSEDfit} with similar 
-            assumptions as in our work.
-
-        \item The SMF for $z{\sim} 0.1$ SDSS galaxies from \citet{Bernardi2013}. 
-            The total luminosity is based on 2-D \texttt{SerExp} models 
-            (\ser{}$+$ Exponential disk model; integrated to infinity) that 
-            recovers much more flux compared to SDSS \cmodel{} magnitudes. 
-            The \m2l{} is also from SED fitting assuming a Chabrier IMF.
-
-        \item The SMF for $0.15 < z < 0.30$ galaxies from the \texttt{S82-MGC} sample
-            \citep{Leauthaud2016} where the \mstar{} is derived using 
-            \texttt{iSEDfit} on PSF-corrected aperture photometry from 
-            \texttt{S82}.
-
-    \end{itemize}
-
-%% ------------------------------------------------------------------------------------ %% 
-    It is clear that different analyses lead to very different slopes at high-mass end. 
-    Here, we do not try to evaluate whether the differences displayed in 
-    Fig~\ref{fig:smf} are dominated by differences in photometry versus 
-    assumptions about stellar population models (e.g. \citealt{Bernardi2017}). 
-    However, given that the results that we are comparing assume the same IMF and adopt 
-    similar assumptions about stellar population models, we hypothesize that the 
-    differences in Fig~\ref{fig:smf} are dominated by differences in photometry. 
-    The goal of our of present paper is not to present and discuss a careful evaluation
-    of the high-mass end of the SMF -- this will be presented in a forthcoming paper 
-    once the HSC survey has accumulated more data. 
-    However, this is clearly a topic that warrants further investigation, and careful 
-    photometry measurements from HSC data will shed further light on these questions.
-
-    Finally, we emphasize that in this present study we do not attempt to separate the 
-    light of the galaxy with a potential (and distinct) ``intra-cluster''
-    light component (ICL; e.g. \citealt{Carlberg1997, Lin2004, Gonzalez2005, 
-    Mihos2005}). 
+    massive galaxies nicely inside 10-15 kpc, but becomes steeper in the outskirt.
+    It represents an interesting phase where the inner ``core'' of massive BCG is 
+    already in pace at $z{\sim} 1$ while the outer halo is still being assembled.
+
+    These comparisons certainly support the idea that \minn{} mainly consists of 
+    \textit{in-situ} stars and mass at $\mathrm{R} > 15$-20 kpc is dominated by accreted 
+    component.     
+    Meanwhile, they also show that the \texttt{in-situ} component 
+    could have steeper \mden{} slope and mass distribution much more extended than 
+    10 kpc\footnote{We convert these \mden{} profiles to the same 
+    Chabrier IMF; but there are still differences in median \mstar{} and 
+    details in the \m2l{} estimates}. 
+    More comparisons with massive galaxies at high redshift and simulated 
+    \textit{in-situ} components will help shed light on this.
+
+    In line with the prediction from Illustris, this comparison also 
+    suggests that, at very high-mass end, the accreted component can make significant 
+    contribution even within the inner 10--20 kpc. 
+    The nature of these ``accreted'' stars in the center of massive galaxies deserve 
+    more attention. 
+    It is possible that they mainly come from major merger and used to be the 
+    \texttt{in-situ} component of another massive galaxy. 
+    It would be interesting see whether there is an alternative, but also physically 
+    motivated definition of \textit{in-situ} component that can be more easily examined 
+    by observation.
+
+    % TODO: Move to Paper II
+    %More BCGs like this at $0.5 < z < 1.0$ can shed light on this intriguing 
+    %process, and help us confirm whether the environmental dependence of structure 
+    %has already emerged within massive galaxies at higher redshift 
+    %(e.g. \citealt{Papovich2012})
+
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
+\subsection{Stellar Halo or Intra-cluster Light?}
+
+    Finally, we emphasize that in this work we do not attempt to separate the 
+    potential (and distinct) ``intra-cluster'' light component (ICL; e.g. 
+    \citealt{Carlberg1997, Lin2004, Gonzalez2005, Mihos2005}) from the massive 
+    galaxies. 
     Instead, we adopt the view that the light of the main galaxy and the 
-    ``intra-cluster''component are a smooth and continuous distribution. 
-    A reliable isolation of a physically meaningful ICL component using photometry 
-    alone is extremely difficult, if not impossible. 
+    ``intra-cluster''component share a smooth and continuous distribution.
+
+    The majority of massive galaxies in our samples are not considered as BCGs
     At the imaging depth of HSC, we find no evidence for a clearly distinction between 
@@
     ICL only becomes important outside that radius and is dominated by individual 
-    tidal features. {\bf I continue to think you are saying all gals have some ICL, rather 
-    that no galaxies have ICL...}
+    tidal features.
+Reliable isolation of a physically meaningful ICL component using photometry 
+    alone is extremely difficult, if not impossible.
 

### 2017-06-02 draft/paper1_jenny.tex
Edit Discussion 5

@@
 %% ------------------------------------------------------------------------------------ %% 
-\subsection{Stellar Halo or Intra-cluster Light?}
+\subsection{Stellar Halo and Intra-cluster Light}
 
@@
 
-    The majority of massive galaxies in our samples are not considered as BCGs
-    At the imaging depth of HSC, we find no evidence for a clearly distinction between 
-    an ``inner component'' and an ``intra-cluster'' component. 
-    Instead, most of our profiles are smoothly varying out to 100 kpc with little 
-    evidence for a distinct secondary component. 
-    We do note however, that our \rbcg{} sample contains only a small fraction of 
-    extremely massive clusters where strong evidence of photometric ICL component is 
-    often found (\mhalo{}$\simgt 10^{15}M_{\star}$). 
-    At the typical \mhalo{} of our \rbcg{} clusters, one good nearby example would be 
-    the Virgo cluster, whose ultra-deep images (e.g. \citealt{Mihos2016}) show
-    that the stellar halo of the BCG can smoothly extends beyond 100 kpc, while the 
-    ICL only becomes important outside that radius and is dominated by individual 
-    tidal features.
-Reliable isolation of a physically meaningful ICL component using photometry 
-    alone is extremely difficult, if not impossible.
+    In practice, reliable isolation of a physically meaningful ICL component using 
+    photometry alone is extremely difficult, if not impossible. 
+    More importantly, he majority of massive galaxies in our samples are not considered 
+    as the BCG of a cluster (\mhalo{}$\simgt 10^{14}M_{\star}$). 
+    Even for BCGs in the \rbcg{} samples, only small fraction of them belong to very 
+    massive clusters where strong evidence of photometric ICL component is 
+    often found (\mhalo{}$\simgt 10^{15}M_{\star}$, e.g. \citealt{Presotto2014, 
+    Burke2015}).
+    For typical \rbcg{} cluster in our sample, the Virgo cluster is a good nearby 
+    example.  
+    Ultra-deep images show that the stellar halo of the BCG smoothly extends beyond 
+    100 kpc, while the ICL only becomes important outside that radius and is dominated 
+    by many individual tidal features (e.g. \citealt{Mihos2016}).
+    Therefore, it is highly unlikely the main results are driven by the ICL component.
+
+    At the imaging depth of HSC and out to 100 kpc, the \mden{} profiles of massive 
+    galaxies vary smoothly and we find no evidence for a distinctive ICL component. 
+    Although the rising stellar velocity dispersion in the outskirt of massive BCG
+    has been used as evidence of a kinematically separated ICL component (e.g. 
+    \citealt{Dressler1979, Carter1999, Kelson2002, Bender2015, Longobardi2015}), 
+    we think it is reasonable to treat the stellar halo of BCG and potential ICL as 
+    an integrate component. 
+    They both carry important information regarding the assembly of central galaxy 
+    and its dark matter halo.
 

### 2017-06-02 draft/paper1.tex
Update the ellipticity and color gradient figure
New paper1

@@
 
-    We use ${\sim}100$ deg$^2$ of deep ($>28.5$ \sb{} in $i$-band), high-quality 
-    (0.6\asec seeing) imaging data from the Hyper Suprime-Cam (HSC) survey 
-    to investigate the halo mass dependence of the surface mass density profiles 
-    and outer stellar envelopes of massive galaxies. 
+    Massive galaxies are important to our understanding of galaxy formation, and 
+    their extended stellar halos contain crucial fossil records of their assembly 
+    history. 
+    In this work, we use ${\sim}100$ deg$^2$ of deep ($>28.5$ \sb{} in $i$-band), 
+    high-quality (0.6\asec seeing) imaging data from the Hyper Suprime-Cam (HSC) 
+    survey to investigate the surface mass density profiles and outer stellar halos 
+    of massive galaxies. 
     Our sample consists of ${\sim}7000$ massive (\mstar{}$\geq 11.5$) central galaxies 
@@
     requiring stacking. 
-    Shallow imaging will miss light at the outskirts of galaxies and this has an 
-    important impact on measurements of the galaxy mass function. 
-    With these deeper data, we show definitively that at fixed stellar mass,
-    massive central galaxies display mass density profiles that are not self similar, 
-    with the accreted fraction increasing towards unity for galaxies in our highest 
-    stellar mass bin. 
+    Shallow images and/or over-simplified models like the \texttt{CModel} tend to 
+    miss the extended stellar halo and result in underestimated stellar mass in a 
+    mass-dependent way.  
+    It will impact important applications like the measurements of the stellar mass 
+    function. 
+    With these deeper data, we explicitly show that at fixed stellar mass,
+    massive central galaxies display surface mass density profiles that are not 
+    self-similar, with the outer-slope becoming shallower and the fraction of mass 
+    in the outskirt increasing with total stellar mass.
+    We also show that the ellipticity of the stellar halo increases with stellar
+    mass, while the optical color gradients do not strongly depend on stellar mass.
     Our results are broadly consistent with the two phase formation scenario of 
     massive galaxies in which outer envelopes are built up at late times from the 
-    accretion of small systems. 
-    Our mass profiles are provided in a convenient tabulated format in order to 
-    facilitate comparisons with predictions from numerical simulations of galaxy 
-    formation.
-    \song{First trial by Jenny; need more works}
+    accretions of small systems. 
+    The surface mass density profiles are provided in a convenient tabulated format 
+    in order to facilitate comparisons with predictions from numerical simulations 
+    of galaxy formation.
 
@@
     (ETGs) undergo a rapid growth phase at $z{\sim} 2$ triggered either by disk 
-    instabilities or gas rich mergers (e.g. \citealt{Hopkins2008, Dekel2009}). 
+    instabilities or gas-rich mergers (e.g. \citealt{Hopkins2008, Dekel2009}). 
     Observationally, the progenitors of ETGs are thought to correspond to the 
-    so-called ``red nuggets'' (e.g. \citealt{Damjanov2009}) which have smaller 
-    effective radii ($R_{\mathrm{e}}$; e.g. \citealt{Trujillo2006, vanDokkum2008, 
-    Cimatti2008}), slightly higher central velocity dispersion and stellar mass 
-    density (\mden{}; e.g. \citealt{vandeSande2011, Belli2014}), more disk-like 
-    morphologies (e.g. \citealt{vanderWel2011}) than their local descendants 
-    (e.g. \citealt{Bezanson2009, vanDokkum2010}).
+    population of massive quiescent galaxies at high redshift that have smaller 
+    average effective radii ($R_{\mathrm{e}}$; e.g. \citealt{Trujillo2006, 
+    vanDokkum2008, Cimatti2008}), slightly higher central velocity dispersion and 
+    stellar mass density (\mden{}; e.g. \citealt{vandeSande2011, Belli2014}), and 
+    more disk-like morphologies (e.g. \citealt{vanderWel2011}) than their local 
+    descendants (e.g. \citealt{Bezanson2009, vanDokkum2010}) with similar stellar 
+    mass.
 
@@
     Laporte2013}).
-    More importantly, both numerical simulation (e.g. \citealt{Oser2010}) and 
-    semi-analytic model (SAM; e.g. \citealt{LeeYi2013, LeeYi2017}) agree that the 
-    mass fraction of the accreted component should increase with total stellar mass, 
-    although different models still predict somewhat different values at fixed 
-    stellar mass (e.g. \citealt{Lackner2012, Cooper2013, Qu2017}).
-    According to the recent results from Illustris \footnote{
+    Both numerical simulations (e.g. \citealt{Oser2010}) and 
+    semi-analytic models (SAM; e.g. \citealt{LeeYi2013, LeeYi2017}) agree that the 
+    mass fraction in the accreted component should increase with total stellar mass, 
+    despite their technical differences (e.g. \citealt{Lackner2012, Cooper2013, 
+    Qu2017}).
+    For instance, recent result from the Illustris \footnote{
     \texttt{http://www.illustris-project.org/}} simulation 
-    (\citealt{Vogelsberger2014}, \citealt{Genel2014}), the fraction of the 
-    accreted mass increases significantly with total stellar mass at \logms{}$>11.0$, 
+    (\citealt{Vogelsberger2014}, \citealt{Genel2014}) predicts that the fraction of  
+    accreted stars increases significantly with total stellar mass at \logms{}$>11.0$, 
     and the accreted component starts to dominate the stellar mass budget 
     ($f_{\mathrm{accreted}}>0.5$) at \logms{}$>11.5$ (\citealt{RodriguezGomez2016}).
-    }
-%% ------------------------------------------------------------------------------------ %%
-
-    \update{
-    At the same time, some of these ``two-phase'' scenario's predictions still have 
-    little observational constraint. 
-    One-dimensional analysis used to conclude that \ser{} law can reasonably describe  
-    the surface brightness (or stellar mass density) profiles of nearby massive 
-    elliptical galaxies (e.g. \citealt{Kormendy2009}; except for the most central 
-    region), and the \ser{} index seems to increase with total luminosity (or stellar 
-    mass; e.g. \citealt{Graham2013}). 
-    There was also suggestion that elliptical galaxies can be divided into two groups
-    based on how well their 1-D surface brightness profiles can be described by \ser{}
-    law (e.g. \citealt{Schombert2015}). 
-    Meanwhile, recent two-dimensional analysis points out that the stellar distributions 
-    of massive ETGs are better fit by multiple-component models 
+%% ------------------------------------------------------------------------------------ %%
+
+    Given the success of this two-phase scenario in explaining trends like overall size 
+    growth, it is time to confront their predictions with additional observations, 
+    especially the detailed profiles of surface mass density and shape for low redshift 
+    massive galaxies.  
+    Early one-dimensional analysis of nearby massive ETGs suggest that the 
+    single-\ser{} profile can describe their surface brightness (or surface mass 
+    density) profiles reasonably well (e.g. \citealt{Kormendy2009}; except for the
+    most central region), with the \ser{} index increasing with total luminosity 
+    (e.g. \citealt{Graham2013}).
+	However, the situation is in fact more complicated, with a suggestion from 
+	\citet{Schombert2015} that there are actually two families of light profiles:
+	the ones that follow single-\ser{} law well and the ones show significant 
+	deviation.
+	Two-dimensional analysis, meanwhile, finds that the stellar distributions 
+    of massive ETGs are often better fit by multiple-component models 
     (e.g. \citealt{Huang2013a, Oh2017}). 
-    However, it is still not clear whether these 1-D or 2-D results are consistent with 
-    the ``two-phase'' scenario. 
-    One of the main limitation here is that one needs very deep observations for large 
-    sample of massive ETGs to correctly estimate their total stellar mass 
-    (e.g. \citealt{Bernardi2013, DSouza2014}) and study the assembly history via 
-    their accreted halos (e.g. \citealt{Capaccioli2015, Iodice2016, Iodice2017}).
-    Currently, such works are often limited by the shallow images such as the ones from
-    the Sloan Digital Sky Survey (SDSS; e.g. \citealt{SDSSDR7, SDSSDR12}) or the small 
-    sample size. 
-    }
-
-    In this paper, we take advantage of new high-resolution (median 
+    \citet{Huang2013b} further suggests a connection between the multi-component 
+    nature of massive galaxies and their two-phase assembly history. 
+    To further confront the two-phase scenario requires very deep observations of 
+    large samples of massive ETGs to correctly estimate their total stellar mass 
+    (e.g. \citealt{Bernardi2013, DSouza2014}) and explore their assembly history via 
+    their extended, accreted halos (e.g. \citealt{Capaccioli2015, Iodice2016, 
+    Iodice2017}).
+    Currently, such work is limited by the depth of imaging from large-area surveys 
+    such as the Sloan Digital Sky Survey (SDSS; e.g. \citealt{SDSSDR7, SDSSDR12}) or
+    the small sample size of massive galaxies with deep images.
+
+    In this paper, we take advantage of new high-quality (median 
     FWHM${\sim} 0.6^{\arcsec}$ in $i$-band) and deep ($i$-band surface brightness 
-    limit $> 28.5$\sb) imaging from the Hyper-Suprime Cam (HSC) Subaru Strategic 
+    limit $> 28.5$\sb) images from the Hyper Suprime-Cam (HSC) Subaru Strategic 
     Program \citep[SSP,][]{HSCDR1} to characterize the outer parts of massive galaxies 
@@
 
-    The Subaru Strategic Program (SSP, \citealt{MiyazakiInPrep}) makes use of the new 
-    prime-focus camera, the Hyper Suprime-Cam (HSC;~\citealt{Miyazaki2012}), on the 
+    The Subaru Strategic Program (SSP, \citealt{HSC_SSP, HSC_DR1}) makes use of the 
+    new prime-focus camera, the Hyper Suprime-Cam (HSC;~\citealt{Miyazaki2012}), on the 
     8.2-m Subaru telescope at Mauna Kea. 
     The ambitious multi-layer HSC survey takes advantage of the large field of 
-    view (FoV;~1.5 deg in diameter) of this camera and will cover ${\sim} 1400$ deg$^2$ 
-    in 5 broad bands ($grizY$) to a limiting depth of $r {\sim} 26$ mag 
+    view (FoV;~1.5 deg in diameter) of this camera and will cover $>1000$ deg$^2$ 
+    of sky in 5 broad bands ($grizy$) to a limiting depth of $r {\sim} 26$ mag 
     in the \texttt{WIDE} layer. 
@@
 
-    \update{
-    For objects without a spectroscopic redshift, we match them with the central 
-    galaxies from the \redm{} catalog using a $2.0^{\arcsec}$ matching radius, 
-    and keep the matched objects with useful red-sequence photo-$z$ 
+    Objects without a spectroscopic redshift are matched with the central 
+    galaxies from the \redm{} catalog using a $2.0^{\arcsec}$ matching radius. 
+    We keep the matched objects with useful red-sequence photo-$z$ 
     ($0.3 \leq z_{\lambda} < 0.5$) in the final sample. 
-    These galaxies are the best candidates for BCGs in clusters selected from 
+    These galaxies are the best candidates for centrals in clusters selected from 
     SDSS DR8 data (\citealt{SDSSDR8}) via a well-tested red-sequence method. 
@@
 %    live in massive halos.
-%% ------------------------------------------------------------------------------------ %% 
-%
-%% ------------------------------------------------------------------------------------ %% 
-%  \begin{figure}
-%      \centering 
-%      \includegraphics[width=\columnwidth]{fig/redbcg_completeness}
-%      \caption{
-%          \textbf{Left:} Difference between \mcmodel{} and \mtot{} for central
-%      	  galaxies in halos less massive than $10^{14} M_{\odot}$ (grey dots) and 
-%      	  in halos more massive than $10^{14} M_{\odot}$ (red squares). 
-%          On average, \mcmodel{} underestimates the total stellar mass of massive 
-%          galaxies by 0.1 dex while in some cases, the difference can exceed 0.2 dex.
-%          Vertical histograms indicate the mass difference for galaxies with
-%          $11.6<$\logmtot{}$<11.9$. 
-%          \textbf{Right:}: Impact of using \mcmodel{} on the galaxy stellar mass
-%          function. 
-%          Dashed lines correspond to the SMF computed using \mcmodel{} as an estimate
-%          of the total luminosity whereas solid lines correspond to the SMF computed
-%          using the total luminosity from our 1-D profile. 
-%          The impact on the SMF can exceed 0.2 dex for massive central galaxies 
-%          living in halos larger than $\log (M_{\mathrm{halo}}/M_{\odot}) > 14.2$ 
-%          (red lines).
-%          \song{New figure for completeness; Need to update the caption}
-%          }
-%      \label{fig:mass_complete}
-%  \end{figure}
-
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %% 
-  \begin{figure}
-      \centering 
-      \includegraphics[width=\columnwidth]{fig/redbcg_mass_diff}
-      \caption{
-          \song{New figures to show how \mstar{} changes with different definitions; 
-                Need to update the caption.}
-          \textbf{Left:} Difference between \mcmodel{} and \mtot{} for central
-      	  galaxies in halos less massive than $10^{14} M_{\odot}$ (grey dots) and 
-      	  in halos more massive than $10^{14} M_{\odot}$ (red squares). 
-          On average, \mcmodel{} underestimates the total stellar mass of massive 
-          galaxies by 0.1 dex while in some cases, the difference can exceed 0.2 dex.
-          Vertical histograms indicate the mass difference for galaxies with
-          $11.6<$\logmtot{}$<11.9$. 
-          \textbf{Right:}: Impact of using \mcmodel{} on the galaxy stellar mass
-          function. 
-          Dashed lines correspond to the SMF computed using \mcmodel{} as an estimate
-          of the total luminosity whereas solid lines correspond to the SMF computed
-          using the total luminosity from our 1-D profile. 
-          The impact on the SMF can exceed 0.2 dex for massive central galaxies 
-          living in halos larger than $\log (M_{\mathrm{halo}}/M_{\odot}) > 14.2$ 
-          (red lines).
-          }
-      \label{fig:mass_diff}
-  \end{figure}
-
 %% ------------------------------------------------------------------------------------ %%
@@
 
-    For physical (e.g.\ late-stage major merger) and unphysical (e.g.\ nearby foreground 
-    galaxy or bright star) reasons, we can not extract reliable 1-D profiles for a small 
+    For physical (e.g.\ late-stage major merger) and nuisance (e.g.\ nearby foreground 
+    galaxy or bright star) reasons, we cannot extract reliable 1-D profiles for a small 
     fraction of massive galaxies because they are heavily masked out. 
-    \update{
     This is an intrinsic limitation of the 1-D method, and it removes ${\sim}10$\% of 
     the sample.
-    }
     %It affects $18/164$ of the \rbcg{} sample, and a smaller fraction of the 
@@
 
-    \update{
-    Given our exquisite profiles out to 100 kpc, the definition and meaning of ``total'' 
-    magnitude (and stellar mass) becomes more interesting.
+    Given our exquisite profiles that extend to 100 kpc, the definition and meaning 
+    of ``total'' magnitude (and stellar mass) becomes more nuanced.
     With the help of the \m2l{} estimated in the next section (\S \ref{sec:mstar}), 
-    we can integrate the profile out to certain radii, and estimate the stellar mass 
-    within.  
-    Motivated by the ``two-phase'' scenario, we will consider two benchmark physical 
+    we integrate the profile to a range of radii, and estimate the stellar mass 
+    within these different apertures.  
+    Motivated by the two-phase scenario, we will consider two benchmark physical 
     apertures throughout this work:
-    }
 
@@
 
-        \item \textbf{The \mstar{} within the inner 10 kpc} (hereafter noted \minn{}). 
-            According to the two-phase scenario, the ``in-situ'' star-formation quickly 
-            builds up the inner, dense core of massive ETGs.  
-            Based on recent observation (e.g.~\citealt{vanDokkum2010}) and simulations 
-            (e.g. \citealt{RodriguezGomez2016}), the in-situ component dominates the 
-            \mstar{} within one effective radius ($R_{\mathrm{e}}$, or 5-10 kpc) of 
-            $z{\sim}0$ massive ETGs.
-            We therefore use \minn{} as proxy for the mass forged during the ``in-situ''
-            phase. 
-            Given the quality of the HSC data, we can reliably measure \minn{} over our 
-            redshift range ($1.0^{\arcsec}$ in radius equals 4.4 and 6.1 kpc at redshift
-            0.3 and 0.5).
-
-        \item \textbf{The stellar mass within 100 kpc} (hereafter noted \mtot{}). 
+        \item \textbf{The \mstar{} within the inner 10 kpc} 
+            (hereafter noted \minn{}). 
+            According to the two-phase scenario, the \textit{in situ} star-formation 
+            quickly builds up the inner, dense core of massive ETGs.  
+            Based on recent observation (e.g.~\citealt{vanDokkum2010}) and 
+            simulations (e.g. \citealt{RodriguezGomez2016}), the \textit{in situ} 
+            component dominates the \mstar{} within one effective radius 
+            ($R_{\mathrm{e}}$, or 5-10 kpc) of $z{\sim}0$ massive ETGs.
+            We therefore use \minn{} as proxy for the mass forged during the 
+            \textit{in situ} phase. 
+            Given the quality of the HSC data, we can reliably measure \minn{} over 
+            our redshift range ($1.0^{\arcsec}$ in radius equals 4.4 and 6.1 kpc 
+            at redshift 0.3 and 0.5).  
+            It is worth noting that, at very high-\mstar{} end, there can be 
+            significant contribution of accreted stars within 10 kpc 
+            (e.g. \citealt{RodriguezGomez2016}). 
+            We will further discuss the justification of this assumption in 
+            \ref{ssec:twophase}.
+
+        \item \textbf{The stellar mass within 100 kpc} 
+            (hereafter noted \mtot{}). 
             For our galaxy sample, a 100 kpc aperture corresponds to 5-10 
             $\times R_{\mathrm{e}}$. 
-            We show in section \ref{ssec:mtotal} that most of the \mstar{} for these 
-            ETGs can be captured by a 100 kpc radius and that \mtot{} is a good proxy 
-            for the ``total'' \mstar{}. 
+            We show in section \ref{ssec:mtotal} that most of the \mstar{} for 
+            these ETGs can be captured by a 100 kpc radius and that \mtot{} is 
+            a good proxy for the ``total'' \mstar{}. 
             Although not perfect, we argue that our measurements of \mtot{} (which are 
@@
     forced-photometry method that takes the PSF convolution into account
-    (e.g. \citealt{SynPipeInPrep}).
+    (e.g. \citealt{SynPipe}).
 
     \texttt{iSEDFit} takes a simplified Bayesian approach. 
-    In short, it first generates a large grid of SEDs from synthetic stellar population 
-    models by drawing randomly from the prior distributions of relevant parameters 
-    (e.g. age, metallicity, dust extinction, and star formation history).
+    In short, it first generates a large grid of SEDs from synthetic stellar 
+    population models by drawing randomly from the prior distributions of relevant
+    parameters (e.g. age, metallicity, dust extinction, and star formation history).
     Based on these models, it uses the observed photometry and redshift to compute 
@@
     corrected for Galactic extinction. 
-    \cmodel{} only accounts for the statistical error on the flux measurement but does
-    not account for systematic uncertainties in the model-fitting process. 
+    \cmodel{} only accounts for the statistical error on the flux measurement but 
+    does not account for systematic uncertainties in the model-fitting process. 
     It therefore underestimates the flux errors of bright galaxies. 
     For this work, we supply \texttt{iSEDFit} with simplified flux errors assuming 
-    $S/N = 100$ for the $riz$ bands, and $S/N = 80$ for the $g$- and $y$-band 
+    $S/N = 100$ for the $riz$ bands, and $S/N = 80$ for the $g$ and $y$ band 
     (on average, images in $gy$ bands are shallower in depth and/or have higher 
     background noise).  
-    Although thse are still conservative estimates of the systematic uncertainties 
+    Although these are still conservative estimates of the systematic uncertainties 
     involved in the model-fitting, tests using synthetic galaxies show that \cmodel{}
-    provides excellent measurements of five-band colors, which are crucial for reliable
-    \m2l{} estimates.
+    provides excellent measurements of five-band colors, which are crucial for 
+    reliable \m2l{} estimates.
     The typical uncertainty of \logms{} is around 0.06-0.08 dex at \logms${\sim} 11.5$.
+
+    In Appendix~\ref{app:sed}, we briefly summarize the basic statistics of 
+    the sample, including average stellar age, metallicity, and internal dust 
+    extinction along with their relation with \mtot{}. 
+    All these properties behave reasonably for massive galaxies in this sample despite 
+    that we do not utilize them in this paper. 
+    Using the $k$-corrected optical color, we can also confirm that the sample follows 
+    a tight ``red-sequence''.  
     Please see Appendix~\ref{app:sed} for further details.
@@
     (Fig \ref{fig:mass_diff}).
-    }
-    \song{Work in progress.}
-
-    In Appendix~\ref{app:sed}, we briefly summarize the basic statistics of 
-    the sample using our estimates of \mtot{} and \minn{}.
-    We confirm that the sample follows a very tight ``red-sequence'' that does not appear to depend on 
-    environment (see \S XX). 
-    Appendix~\ref{app:sed} describes the outputs from our SED fitting process 
-    (average stellar age, metallicity, and internal dust extinction). 
-    We do not utilize these quantities in this paper, but we have checked that they all 
-    behave reasonably for both samples.
-
-    \song{The color gradients and ellipticity profiles will be updated}
+    At high-\mstar{} end (e.g. \logmtot{}$>11.6$), the average difference is larger 
+    than 0.1 dex and can be as large as 0.2--0.3 dex.  
+    More importantly, the differences between \mtot{} and \mcmodel{} clearly show 
+    dependence on total stellar mass as \mcmodel{} tends to miss more light in 
+    more massive galaxies.  
+    This relates to the mass-dependence nature of the stellar halos in massive 
+    galaxies and the intrinsic limitation of \cmodel{} method, which we will discuss
+    more in the next section.
+    Such differences also have important implications in the estimation of stellar 
+    mass function or in the study of environment-dependence of galaxy structure.  
+    We will also discuss these topics in Section \ref{sec:discussion}.
+
+    Although 100 kpc is already a very large radius that should enclose the majority 
+    of stars that belong to these massive galaxies, we know that their \mden{} 
+    profiles extend beyond 100 kpc without showing sign of truncation. 
+    Therefore, for massive galaxies, even \mtot{} should be only considered a lower
+    limit of the ``total'' \mstar{}. 
+    In Fig \ref{fig:mass_diff}, we also integrate the \mden{} of each galaxy to the 
+    outermost radii as \mmax{} and compare their differences with \mtot{} 
+    (right panel).  
+    Although \mmax{} is much more uncertain than \mtot{} due to background subtraction
+    and impacts from nearby objects, we see they do return more \mstar{} than \mtot{}. 
+    However, the mass differences are on average very small ($\sim0.02-0.03$ dex) and 
+    do not show strong mass dependence.  
+    This confirms that, at the current depth of HSC images, \mtot{} can be used as 
+    good proxy of ``total'' stellar mass.
+
     Our methodology ignores any radial variations in \m2l{}. 
-    It is well known that massive ETGs have negative optical color gradients indicating 
-    gradients in \m2l{} (e.g.\ \citealt{LaBarbera2012}; 
-    \citealt{DSouza2015}). \jenny{earlier reference here?}
+    It is well known that massive ETGs have negative optical color gradients 
+    indicating gradients in \m2l{} (e.g.\ \citealt{Carollo1993, Davies1993, 
+    LaBarbera2012, DSouza2015}).
     These color gradients are shallow and smooth out to a few times the effective 
     radius and color gradients at the outskirts are not yet well quantified.
-    Our results looking at the outer envelopes as a function of mass and environment 
-    will be robust as long as there is \emph{no significant difference in 
-    the average color gradient between sub-samples}.
-    %More importantly, for the comparison between the \rbcg{} and \nbcg{} samples, 
-    %our results will be robust as long as there is \emph{no significant difference in 
-    %the average color gradient between the two samples}. 
-    We have confirmed that this is indeed the case (see Section~\ref{ssec:ell_color}).
-
-    Our method for deriving total stellar masses is similar to the 
-    method adopted by the GAMA survey (\citealt{Taylor2011, Kelvin2012}). 
-    We have compared our \mstar{} values with those from GAMA and the results are given 
-    in Appendix~\ref{app:gama}. 
-    We find a systematic differences between the two \mstar{} estimates.
+    Therefore, using average \m2l{} is unlikely to bias the results on \mstar{}
+    measurements.  
+    We will discuss color gradients more in Section~\ref{ssec:ell_color}. 
+    In summary, we do not find optical color gradient shows dependence on stellar
+    mass, hence the results about the mass-dependence of the \mden{} profiles will 
+    not be affected by it.
+
+    %Our results looking at the outer envelopes as a function of mass and environment 
+    %will be robust as long as there is \emph{no significant difference in 
+    %the average color gradient between sub-samples}.
+    %We have confirmed that this is indeed the case (see Section~\ref{ssec:ell_color}).
+
+    Our method for deriving total \mstar{} is similar to the method adopted by the 
+    GAMA survey (\citealt{Taylor2011, Kelvin2012}), where the average \m2l{} is from 
+    SED fitting of PSF-matched aperture photometry and the total luminosity comes from 
+    sing-\ser{} modeling of the SDSS images. 
+    To avoid the differences in stellar population assumptions, we directly compare the 
+    total luminosity within 100 kpc and the GAMA single-\ser{} luminosity for the same
+    galaxies. 
+    At high-\mstar{} end, the HSC 1-D profiles still recover more light than the 
+    single-\ser{} model on average.
     It is likely that the GAMA models fail to capture the flux associated with the 
     outskirts of galaxies due to the limited depth of SDSS.  
+    Meanwhile, there are also many cases where the high-\ser{} index of GAMA model leads 
+    to over-estimated total luminosity. 
+    We will discuss more of this comparison in the next paper of this series 
+    (Huang\etal in prep.).
+
+    %We have compared our \mstar{} values with those from GAMA and the results are given 
+    %in Appendix~\ref{app:gama}.
+
 %% ------------------------------------------------------------------------------------ %%
@@
 
+    % TODO: Move this to Paper II
+    %To ensure a clean separation in \mhalo{}, here we only focus on the central 
+    %galaxies of clusters with $\lambda > 30$. 
+    %According to \citet{Simet2016}, this $\lambda \geq 30$ sample should correspond to 
+    %$M_{\mathrm{halo}}>10^{14.2} M_{\odot}$. 
+    %We have checked that none of the results in this work depend on the choice of this 
+    %$\lambda$ limit.
+
+    %The median $\lambda$ of the clusters associated with the \rbcg{} sample is 
+    %${\sim} 41$, corresponding to halo mass of 
+    %$M_{\mathrm{halo}}{\sim} 2.2\times 10^{14}$ $h^{-1}$ $M_{\odot}$.
+    %Only 44 centrals from the \rbcg{} sample live in clusters with $\lambda \geq 50$
+    %($M_{\mathrm{halo}} {\sim} 3.0\times 10^{14}$ $h^{-1} M_{\odot}$). 
+    %Our \rbcg{} sample therefore corresponds to galaxies in moderate mass halos.
+
+    After matching the \texttt{hscZ} sample with the central galaxies of \redm{} 
+    clusters with $\lambda \geq 20$ and $P_{\mathrm{0.7}} \geq 0.7$, we find 164 
+    matched galaxies at $0.3 \leq z \leq 0.5$.
+    This sample of \textbf{central galaxies in more massive halos} will be referred to 
+    as the \rbcg{} sample. 
     Due to the depth and resolution of SDSS, the \redm{} catalog becomes slightly 
-    incomplete at lower richness ($\lambda < 40$) at $z > 0.33$. 
-    To ensure a clean separation in \mhalo{}, here we only focus on the central 
-    galaxies of clusters with $\lambda > 30$. 
-    According to \citet{Simet2016}, this $\lambda \geq 30$ sample should correspond to 
-    $M_{\mathrm{halo}}>10^{14.2} M_{\odot}$. 
-    We have checked that none of the results in this work depend on the choice of this 
-    $\lambda$ limit.
-
-    We therefore match the \texttt{hscZ} sample with the central galaxies of \redm{} clusters 
-    with $\lambda \geq 30$ and $P_{\mathrm{0.7}} \geq 0.7$, and find 164 matched 
-    galaxies at $0.3 \leq z \leq 0.5$.
-    Our sample of \textbf{central galaxies in more massive halos} will be referred to 
-    as the \rbcg{} sample. 
-    The median $\lambda$ of the clusters associated with the \rbcg{} sample is 
-    ${\sim} 41$, corresponding to halo mass of 
-    $M_{\mathrm{halo}}{\sim} 2.2\times 10^{14}$ $h^{-1}$ $M_{\odot}$.
-    Only 44 centrals from the \rbcg{} sample live in clusters with $\lambda \geq 50$
-    ($M_{\mathrm{halo}} {\sim} 3.0\times 10^{14}$ $h^{-1} M_{\odot}$). 
-    Our \rbcg{} sample therefore corresponds to galaxies in moderate mass halos.
+    incomplete at lower richness ($\lambda < 40$) at $z > 0.33$, but the main results 
+    of this work are not affected by this.
     %% Saved as "dr1_redbcg_use_sed5b.fits"
 
-    Out next goal is to construct a sample of central galaxies living in halos with 
-    \logmh{}$<14.0$. 
-    We first identify and remove all galaxies within a cylindrical region around all 
-    \redm{} clusters. 
+    As the next step, we want to construct a sample of central galaxies living in halos 
+    with \logmh{}$<14.0$. 
+    To achieve this, we identify and remove all galaxies within a cylindrical region 
+    around all \redm{} clusters. 
     We use a radius equal to $R_{\mathrm{200b}}$ and the thickness of the cylinder is 
-    set to twice the uncertainty of the photometric redshift error. 
-    We convert $\lambda$ to $M_{\mathrm{halo}}$ using the calibration of 
-    \citet{Simet2016} and we use the mass-concentration relation from 
-    \citet{Diemer2015} to compute $R_{\mathrm{200b}}$. At $0.3 < z < 0.5$, the 
-    uncertainty of photo-$z$ is between 0.015 to 0.025, and is enough to exclude 
-    cluster members.
+    set to twice the uncertainty of the photometric redshift error of the cluster. 
+    We convert $\lambda$ of each cluster to $M_{\mathrm{halo}}$ using the calibration 
+    of \citet{Simet2016} and we use the mass-concentration relation from 
+    \citet{Diemer2015} to compute $R_{\mathrm{200b}}$. 
+    At $0.3 < z < 0.5$, the uncertainty of photo-$z$ is between 0.015 to 0.025, and 
+    is enough to exclude cluster members.
+
     After removing galaxies associated with \redm{} clusters, the remaining galaxies 
     in our sample will be dominated by central galaxies living in halos with 
-    \logmh{}$\leq 14.0$. 
-    We will refer to this sample of \textbf{central galaxies in less massive halos}
-    as the \nbcg{} sample. For massive central galaxies that are not in these cluster-level halos, 
-    we unfortunately can not estimate their \mhalo{} individually, but it is safe 
-    to assume they will have $\log (M_{\mathrm{halo}}/M_{\odot}) < 14.0$.  
-    At this very high mass end, and given that we have rejected satellites in \redm{} 
-    clusters, any further satellite contamination can be safely neglected 
-    (e.g. \citealt{Reid2014, Hoshino2015, Saito2016, vanUitert2016}).
+    \logmh{}$< 14.0$. 
+    We will refer to this sample of \textbf{potential central galaxies in less 
+    massive halos} as the \nbcg{} sample. 
+    Since we have rejected satellites in \redm{} cluster and the satellite 
+    contamination steadily decreases with stellar mass (e.g. \citealt{Reid2014, 
+    Hoshino2015, Saito2016, vanUitert2016}), the massive galaxies in the \nbcg{} 
+    sample are very likely to be the central galaxies of their own dark matter halos.
     %% Saved as "dr1_nonbcg_use_sed5b.fits"
-    % TODO: The actual number waits to be updated}
-
 %% ------------------------------------------------------------------------------------ %%
@@
             with reliable redshift information. 
-        \item We further divide the sample into an \rbcg{} sample and a \nbcg{} sample, 
-          with the former roughly having \logmh{}$\geq 14.2$ and the latter having 
-           \logmh{}$<14.0$.
-
-%          : we select a sample of 164 galaxies at 
-%            $0.3 \leq z \leq 0.5$ that are the central galaxies 
-%            in $\lambda > 30$ \redm{} clusters. 
-%            They represent the central galaxies in very massive halos 
-%            (\logmh{}$\geq 14.2$). 
-%        \item \nbcg{} sample: after excluding all cluster members from the 
-%            \texttt{hscZ} sample, we have 14661 bright galaxies at 
-%            $0.3 \leq z \leq 0.5$. 
-%            After applying an additional \mstar{} cut (see Section 
-%            \ref{ssec:isedfit}), this sample corresponds to central galaxies in 
-%            halos with \logmh{}$<14.0$.  
+        \item With the help of the \redm{} cluster catalog, we further select 
+            candidates of massive central galaxies in a range of \mhalo{}
+            We broadly divide the sample into the central galaxies living in halos
+            with \logmh{}$\geq 14.0$ (\rbcg{}) and \logmh{}$<14.0$ (\nbcg{}). 
     \end{itemize}
 
+    To discuss the mass-dependence of galaxy structure, we will combine the \rbcg{}
+    and \nbcg{} samples and group them into three bins of \mtot{}.  
+    In this work, we will only separately discuss the \rbcg{} and \nbcg{} samples 
+    when we look into the impact of \mstar{} definition on the SMF in Section 
+    \ref{ssec:smf}. 
+    We will carefully look into the structural differences between the central galaxies 
+    from these two samples later (Huang\etal~in prep.).  
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
+  \begin{figure*}
+      \centering 
+      \includegraphics[width=\textwidth]{fig/redbcg_mass_smf}
+      \caption{
+          \textbf{Left:} Impact of using \mtot{} on the galaxy stellar mass function. 
+          Dashed lines correspond to the SMF computed using \mcmodel{} whereas solid 
+          lines correspond to the SMF computed using \mtot{}. 
+          Here we separate the HSC massive galaxies into the central galaxies living 
+          in halos more massive than \logmh{}$\sim14.2$ (red lines) and the ones in 
+          halos with \logmh{}$<14.0$ (black lines).
+          The impact on the SMF can exceed 0.2 dex for massive central galaxies in 
+          very massive halos.
+          \textbf{Right}: The stellar mass volume density distributions of massive 
+          HSC galaxies, using both \mtot{} (black solid line) and \mmax{} (black dotted 
+          line). 
+          The uncertainty of distribution using \mtot{} is shown in grey shaded 
+          region.  
+          Here, we also compare the distributions with SMF from previous works: 
+          (a): SDSS galaxies at $z{\sim} 0.1$ from \citet{Bernardi2017}; the \mstar{} 
+          is based on photometry from 2-D \ser{}$+$Exponential model fitting 
+          (purple); 
+          (b): SDSS galaxies at $z{\sim} 0.1$ from \citet{Moustakas13} based on 
+          improved SDSS \texttt{cModel} photometry (blue); 
+          (c): \texttt{S82-MGC} galaxies at $0.15 < z< 0.43$ from 
+          \citet{Leauthaud2016} based on PSF-matched SDSS-UKIDSS photometry (green).
+          Please see text for more details of the comparison.
+          }
+      \label{fig:smf}
+  \end{figure*}
 %% ------------------------------------------------------------------------------------ %%
@@
 \subsection{Impact of Missing Light on the Galaxy Stellar Mass Function}
-    \label{ssec:s82}
-
-    Different methods for estimating the ``total'' \mstar{} can have a large impact on 
-    the high mass end of the galaxy stellar mass function (e.g. \citealt{Bernardi2013, 
-    DSouza2014, DSouza2015, Bernardi2016a}). 
-    Fig~\ref{fig:mass_complete} shows the SMF computed using both \mtot{} and \mcmodel{}. 
-    As can be seen from this figure, our careful 1-D approach recovers more flux 
-    in massive galaxies than \texttt{cModel}. 
+    \label{ssec:smf}
+
+    As one of the most fundamental statistics of galaxy population, the Stellar 
+    Mass Function (SMF) and its evolution are critical to our understanding of 
+    galaxy evolution.  
+    In Section \ref{ssec:mtotal}, we demonstrate that different methods for estimating
+    ``total'' \mstar{} can lead to quite different results, hence have a large impact 
+    on the high mass end of the galaxy stellar mass function (e.g. 
+    \citealt{Bernardi2013, DSouza2014, DSouza2015, Bernardi2017}).
+    On average, integration of our carefully derived non-parametric \mden{} profile 
+    to 100 kpc (\mtot{}) recovers more light (hence mass) than the \texttt{cModel}
+    method. 
+    At \logmtot{} $>11.6$, the difference sometimes can be larger than 0.2 dex. 
     More importantly, the average difference steadily increases with \mtot{}. 
-    At \logms{} $>11.5$, the difference can be larger than 0.2 dex. 
-    This difference relates to the intrinsic limitation of the \texttt{cModel} method 
-    and also reflects the fact that more massive ETGs tend to have more extended 
-    stellar mass distributions (e.g. \citealt{Graham2003}). 
+    These differences relates to the intrinsic limitation of the \texttt{cModel} 
+    method and also reflects the fact that more massive ETGs tend to have more 
+    extended stellar mass distributions (e.g. higher-\ser{} index, 
+    \citealt{Graham2003}).
+
+    Although we do not attempt to measure SMF, we use Fig \ref{fig:smf}
+    to demonstrate the impacts from missing light and different definitions of 
+    \mstar{}.
+    The left panel of Fig \ref{fig:smf} shows the SMF\footnote{There are actually
+    the volume density distributions, we refer to them as SMFs for convenience 
+    although the incompleteness and other systematics have not been corrected}
+    computed using \mcmodel{} and \mtot{} for both the \rbcg{} and \nbcg{} samples.
+
     Generally speaking, the use of \mtot{} instead of the \mcmodel{} shifts the SMF 
-    towards the higher-mass end and slightly modifies the high-mass slope. 
-    %The impact of missing flux is most prominent for the \rbcg{} sample.
+    towards the higher-mass end without significantly modifying the slope at 
+    high-mass end.
+    Interestingly, the impact of missing flux is more prominent for the \rbcg{} 
+    galaxies whose contribution to the very high-mass end is substantial. 
+    This difference between the \rbcg{} and \nbcg{} samples here may hint that 
+    the \rbcg{} galaxies suffer more from missing light. 
+    We will look into this in details in the following work (Huang\etal in prep.).
+
+    As discussed in Section~\ref{ssec:mtotal}, even with much deeper images from HSC,
+    it is non-trivial to clearly define and measure the ``total'' \mstar{} for 
+    these massive systems, and the \mden{} profiles of these galaxies often extend 
+    well beyond 100 kpc. 
+    We measure \mmax{} by integrating the \mden{} profiles out to the detection 
+    limit that is defined by the background noise.
+    Although the \mden{} profile becomes more uncertain at $>100$ kpc, \mmax{} can
+    provide us certain clue about how much extra mass is ``hidden'' there. 
+    Although the average difference we find is small even at high-mass end 
+    (${\sim}0.03$ dex), on the right panel of Fig \ref{fig:smf}, we can still its 
+    influence on the SMF at high-mass end, where the slope becomes slightly 
+    shallower.
+
+    % TODO: Move this to Paper II
+    %In this work, we have opted to in general use \mtot{} rather than \mmax{} as the 
+    %uncertainty on \mmax{} is larger. 
+    %However, we have checked that none of our results are changed by replacing \mtot{} 
+    %via \mmax{}.
+
+    On the same figure, we also compare the HSC results with the ones from following 
+    works:
+
+    \begin{itemize}
+
+        \item The SMF for $0.15 < z < 0.30$ galaxies from the \texttt{S82-MGC} sample
+            \citep{Leauthaud2016} where the \mstar{} is derived using 
+            \texttt{iSEDfit} on PSF-corrected aperture photometry from 
+            \texttt{S82}.
+            The stellar population model and star-formation history assumptions are 
+            very similar to the ones in this work, except that it uses the 
+            \texttt{BC03} model. 
+            Based on the test results from Appendix \ref{app:sed}, we simply shifts 
+            the SMF to higher \mstar{} by 0.08 dex.
+
+        \item The SMF derived from a SDSS-\textit{GALEX} sample of $z{\sim} 0.1$ 
+            galaxies from \citet{Moustakas13}. 
+            Here, the total luminosity is based on the SDSS \cmodel{} magnitude. 
+            The \m2l{} is derived via SED fitting using \texttt{iSEDfit} with similar 
+            assumptions as in our work.
+
+        \item The observed SMF for $z{\sim} 0.1$ SDSS galaxies from 
+            \citet{Bernardi2017}. 
+            The total luminosity is based on 2-D \texttt{SerExp} models 
+            (\ser{}$+$ Exponential disk model; integrated to infinity) that 
+            recovers much more flux compared to SDSS \cmodel{} magnitudes 
+            (\citealt{Bernardi2013, Meert2015}). 
+            The \m2l{} is adopted from the SED fitting results from the ``dusty'' 
+            model in \citet{Mendel2014} which share similar assumptions of stellar 
+            population models with this work.
+
+    \end{itemize}
+
+    To appropriately compare SMFs from different works, one needs to carefully 
+    separate the differences in the measurements of luminosity and \m2l{}, and 
+    takes the uncertainties of \mstar{} measurements into account\footnote{
+    Fixed uncertainty of \logms{} can lead to increasingly over-estimated 
+    volume density with \mstar{} due to the very steep slope of SMF at high-mass end.} 
+    (\citealt{Bernardi2010, Bernardi2017}), which is beyond the scope of this work.  
+    Here, we primarily want to visualize the importance of \mstar{} measurements 
+    to the SMF at high-mass end. 
+    All SMFs share similar volume density around \logms{}${\sim}11.0$, but the ones
+    that are based on \texttt{cModel} and small aperture photometry show much 
+    steeper slopes than the HSC \mtot{} one. 
+    The SMF based on single-\ser{} model seems to face the same issue. 
+    We also compare with the $z{\sim}0.1$ SMF from the GAMA survey 
+    (\citealt{Wright2017}) whose luminosity is scaled with the single-\ser{} model
+    from \citet{Kelvin2012}, and its high-mass end behavior is very similar to 
+    the \citet{Leauthaud2016} and the \citet{Moustakas13} ones. 
+    And, once the \m2l{} measurements based on similar assumptions are adopted, 
+    the SDSS SMF using the \texttt{SerExp} models from \citet{Bernardi2017} becomes 
+    surprisingly similar to the HSC \mtot{} one that is not model dependent.
+    Both SMFs highlight the importance of ``missing light'' from different angles. 
+    Right now, the \citet{Bernardi2017} sample and our HSC one have almost no 
+    galaxy in common due to the differences in redshift range, hence it is not 
+    clear whether the \texttt{SerExp} model can indeed describe the flux 
+    distributions of these massive galaxies out to $>100$ kpc. 
+    It would be interesting to look into the application of multi-component 
+    2-D models using HSC images.
+
+    In summary, the result highlights that the SMF at high-mass end is sensitive to 
+    even moderate change of \mstar{}, and illustrates the advantages of deep HSC image
+    and careful 1-D approach in estimating total \mstar{} of massive galaxies.
     For studies about the SMF or other aspects of galaxy evolution based on 
-    \cmodel{}-like photometry or shallower images, these effects can not be neglected.
+    shallow image or simplified model, these effects can not be neglected.
+    Although we only discuss the high-mass end, this \mstar{} range is crucial for 
+    tracing the evolution of massive galaxies and calibrating numerical simulation 
+    and semi-analytic model as it is very sensitive to the AGN-feedback recipe.   
 %% ------------------------------------------------------------------------------------ %%
@@
     \textbf{individually}. 
-    These median \mden{} profiles have moderate differences in the inner region, 
-    but show significant differences in the outskirts with more massive galaxies 
-    showing more prominent stellar envelopes. 
-    \jenny{This seems out of place here:Most of these massive galaxies ($\ge 10^{11.4} M_{\odot}$) are slowly-rotating 
-    (e.g.\ \citealt{Cappellari13b}) giant ellipticals with ``boxy'' inner isophotal 
-    shapes (e.g.\ \citealt{Kormendy2009}), and slightly flattened inner \mden{} 
-    profiles (e.g.\ \citealt{Lauer07})}. 
-    But in the outskirts, the structure of these galaxies is 
-    \emph{clearly not self-similar}. 
+    These median \mden{} profiles have moderate differences in the inner region. 
+    Within inner 10 kpc, the median \mden{} profile of more massive galaxies 
+    shows slightly higher \mden{} value but similar slope. 
+    These massive galaxies ($\ge 10^{11.4} M_{\odot}$) are known to have quite 
+    uniform properties in the inner region. 
+    At these masses, most of them should be ``slow-rotating'' 
+    (e.g.\ \citealt{Cappellari13b})``core''--elliptical galaxies 
+    (e.g.\ \citealt{Lauer07}) that have ``boxy'' inner isophotal shapes and similar 
+    slopes of the inner surface brightness profiles (e.g.\ \citealt{Kormendy2009,
+    Schombert2015}).
+
+    Meanwhile, in the outskirts, we can notice significant differences where more 
+    massive galaxies have gradually more flattened \mden{} profiles and show more 
+    prominent stellar halos.
+    It is also interesting to see that the distributions of \mden{} profiles show 
+    considerably large scatter at large radius. 
+    Given the \s2n{} of the HSC image at these surface brightness levels, these 
+    scatters should reflect the \textbf{intrinsic scatter of the structures of 
+    massive galaxies in their stellar halos}.
+    Overall, the structures of massive galaxies are \textbf{clearly not 
+    self-similar} out to 100 kpc. 
     Some of our \mden{} profiles show signs of unphysical truncation and fluctuation 
@@
 
-    Fig~\ref{fig:avg_prof} compares our results with previous work. 
-    Most previous studies have relied on stacking techniques to measure surface 
-    brightness profiles out to large radii.
-    So far, the surface brightness profiles of massive galaxies out to such large 
-    radii was mostly derived via image stacking technique that suffers from several 
-    systematic issues (e.g. \citealt{Tal2011, DSouza2015}; but also see:
-    \citealt{Capaccioli2015}); and the \mden{} profiles are even more rarely 
-    available.
+    The right panel of Fig~\ref{fig:avg_prof} compares our results with several 
+    previous works. 
+    So far, deep \mden{} profiles of massive galaxies are rarely available. 
+    Even in the nearby universe, it is still not easy to reach to the very outskirt
+    of massive galaxy due to technical difficulties (e.g. 
+    \citealt{Capaccioli2015, Iodice2016, Iodice2017, Spavone2017, Mihos2017})
+    The small volume of local universe also limits the number of available 
+    galaxies at high-mass end.
+    Most previous studies often focus more on the surface brightness profiles, 
+    and they also depend on stacking techniques or model-dependent method to 
+    study the structure of massive galaxies in their outskirts (e.g. 
+    \citealt{Tal2011, DSouza2015}), both of which suffer from several systematic 
+    issues.
 
@@
     images) from the Carnegie-Irvine Galaxy Survey (CGS, \citealt{CGS1}). 
-    Because this is a very low redshift sample, these profiles are robust to smaller scales, $r=1$ kpc. 
-    The \citet{Huang2013a} profiles show good agreement with ours in the region of 
-    overlap and out to 50 kpc. 
+    Because this is a very low redshift sample, these profiles are accurate to 
+    smaller scales, $r=1$ kpc. 
+    The \citet{Huang2013a} \mden{} profiles show good agreement with ours in the 
+    region of overlap and out to 50 kpc although their \m2l{} are derived in 
+    slightly different ways.
     CGS images are deeper than SDSS images in the $r$-band, but the median 
@@
       \centering 
-      \includegraphics[width=\textwidth]{fig/redbcg_discussion_2}
+      \includegraphics[width=\textwidth]{fig/redbcg_ell_color.pdf}
       \caption{
           Radial variations in ellipticity and optical colors for massive galaxies. 
-          The format of this figure is similar to the right hand side of 
-          Fig~\ref{fig:prof_1}. 
-          Top panels show the ellipticity profile, middle panels show $g-r$, and lower 
-          panels show $g-i$. 
-          We compare our results with those from \citet{Tal2011} based on stacking 
+          The format of this figure is similar to Fig~\ref{fig:avg_prof}. 
+          \textbf{Left panel} shows the ellipticity profiles, 
+          \textbf{Upper-right panel} shows the $g-r$ color profiles, and 
+          \textbf{Lower-right panel} is for $g-i$ color profiles. 
+          We compare our results with those from (1) \citet{Tal2011} based on stacking 
           large samples of luminous red galaxies in SDSS at $z{\sim} 0.4$ 
-          (solid blue line on top panel). 
-          We also compare with the results from a stacking analysis of nearby massive 
+          (solid red line on left panel), 
+          (2) the results from a stacking analysis of nearby massive 
           galaxies with high concentration index ($C>2.6$) in 
-          \citet[][blue dash lines on the top and middle panels]{DSouza2014}. 
-          Finally, we also compare with the average $g-r$ and $g-i$ color profiles 
+          \citet[][blue dash lines on the left and upper-right panels]{DSouza2014}, 
+          (3) and the average $g-r$ and $g-i$ color profiles 
           from a large sample of nearby elliptical galaxies in \citet[][blue, solid 
-          lines on the middle and bottom panels]{LaBarbera2010}.
+          lines on both right panels]{LaBarbera2010}.
+          For color profiles, we also compare with deep observations of a few nearby 
+          massive ETGs: the $g-r$ color profiles of NGC 4472 (\citealt{Mihos2013}) 
+          and NGC 4365 (\citealt{Mihos2017}), and the $g-i$ profile of NGC 1399 
+          (\citealt{Iodice2016})
           }
@@
 %% ------------------------------------------------------------------------------------ %% 
-	In addition to the shape of the light profile, we can also 
-    study the $k$-corrected color profiles and ellipticity profiles 
-    (computed via \texttt{Ellipse}) of these galaxies, and how 
-    they depend on mass and environment.
-    These quantities contain interesting information about the physical processes that 
-    shape galaxies. We also want to be sure that we do not introduce any systematic bias in 
-    our mass determinations because of systematic changes in color profile with stellar or 
-    halo mass.
-
-    \jenny{Could we add a panel to the plot showing the mass bins as above with the ellipticity profiles?}
-
-    %\begin{enumerate}
-    %    
-    %    \item To see whether the ellipticity profile depends strongly on environment, 
-    %        and to see whether or not the fact that we use an using average isophotal 
-    %        shape for our our 1-D \mden{} profiles has any impact on our results.
-    %    
-    %    \item To verify that the average color gradient does not depend strongly on 
-    %        the environment and that is not steep enough to cause a problem with our 
-    %        choice the assumption that it is reasonable to use average \m2l for 
-    %        comparing massive galaxies. 
-    %        We extract color profiles by applying the isophotes in $i$-band to images 
-    %        in other bands in ``forced photometry'' manner.  
-    %        
-    %\end{enumerate}
-
-    We compute ellipticities and color profiles in the radial range of 5-50 kpc 
-    (this is the range where we can safely ignore differences in sky subtraction and 
-    seeing across different bands). 
-    We apply Galactic extinction and $k$-correction to both $g-r$ and $g-i$ color 
-    profiles; the $k$-correction values are also from \texttt{iSEDFit} results.
-    We show the average ellipticity, $g-r$, and $g-i$ color profiles for the 
-    \mtot{}-matched (\minn{}-matched) samples of \rbcg{} and \nbcg{} galaxies on the 
-    left (right) side of \ref{fig:ell_color}. 
-    We also compare our results with previous work based on stacking SDSS galaxies 
-    (e.g. \citealt{LaBarbera2010, Tal2011, DSouza2014}).
-
-    We find that in general, the ellipticities of massive galaxies increases with 
-    radius from $e\le 0.2$ around 5-10 kpc to $e{\sim} 0.3$ at 40-50 kpc. 
-    This is consistent with previous 2-D modeling results from \citet{Huang2013a}. 
-    The ellipticity profiles of the \mtot{}-matched samples are very similar at 
-    $r<50$ kpc (2-3$\times R_{\mathrm{e}}$ for their \mstar{}). 
-    However, for the \minn{}-matched samples, the \rbcg{} galaxies have higher 
-    ellipticity than the \nbcg{} ones at $r > 10$ kpc, while their inner ellipticity 
-    profiles are very similar.  
-    This further hints that massive central galaxies in different halos but with 
-    similar ``in-situ'' mass may experience different late-time merging histories. 
-    Overall, the relative low ellipticity value and the fact that the ellipticity 
-    gradients are shallow lead us to conclude that the use of an average 
-    isophotal ellipticity is fine for this present study.
-
-    Previous attempts to constrain ellipticity gradients have relied on image 
-    stacking techniques (e.g. \citealt{Tal2011}, \citealt{DSouza2015}). 
-    Compared to our measurements, we find that stacked ellipticity profiles tend to 
-    underestimate the ellipticity in the outskirt. 
-    Ellipticity profiles contain additional information about the assembly histories 
-    and in future work, it would be of interest to compare our ellipticity profiles 
-    with predictions from hydrodynamic simulations such as Illustris 
-    (\citealt{Vogelsberger2014}, \citealt{Genel2014}) or \textit{Horizon-AGN} 
-    (\citealt{Dubois2014}).
-
-    In terms of color gradients, we find shallow and negative gradients of median 
-    $g-r$ and $g-i$ color profiles for both \rbcg{} and \nbcg{} galaxies. 
-    {\bf Can we also look as a function of stellar mass?}
-    For both \mtot{}- and \minn{}-matched samples, we find no significant difference
-    in their median color profiles, which supports the assumption of using single 
-    average \m2l{} value to estimate \mden{} profiles.
-    The median $g-r$ color profiles are quite consistent with those based on 
-    stacked SDSS images. 
-    For the $g-i$ profiles, the HSC ones show steeper gradients than the SDSS ones, 
-    however, it is important to point out that the SDSS $i$-band suffers from the 
-    so-called ``red-halo'' effect of (e.g. \citealt{Wu2005}, \citealt{Tal2011}) that 
-    could make the SDSS color appears redder. 
-    In contrast, HSC $i$-band image do not suffer from this effect (thanks to thick 
-    CCDs), therefore can help provide more accurate color estimates.
+	Aforementioned results only use the 1-D \mden{} profiles that are baed on single 
+	band image and the flux-weighted isophotal shape, while more useful information 
+	can be gathered from the HSC images of these massive galaxies.
+	The ellipticity and $k$-corrected optical color profiles are particularly 
+	interesting.
+	We extract ellipticity profile using \texttt{Ellipse} by setting the shape of each 
+	isophote free. 
+	And by applying the $i$-band isophotes to images of other bands in the 
+	forced-photometry way, we can also measure the color profiles too. 
+	We apply Galactic extinction correction and \texttt{iSEDFit} $k$-correction to 
+	both the $g-r$ and $g-i$ color profiles.
+	The PSF smearing effect will make the central isophotal shape rounder than the 
+	real value, while the seeing differences between filters will bias the central 
+	color\footnote{Since the HSC $i$-band always has better seeing, the central color 
+	will become redder when the seeing effect is not corrected.}. 
+	At the same time, it is more difficult to extract reliable ellipticity and 
+	color profiles out to 100 kpc: at low surface brightness region, isophotal shape 
+	becomes unstable and easily affected by any contamination; the color profile in
+	the outskirt also becomes very sensitive to background level and noise level in 
+	either band. 
+	In this work, we will focus on the median ellipticity and color profiles between 
+	8--60 kpc where we can safely ignore the above issues.
+
+	The ellipticity of the isophote contains information about the 3-D geometry 
+	(e.g. \citealt{Chang2013, Mitsuda2017}) and kinematic (e.g. 
+	\citealt{Cappellari2012, Weijmans2014}) of stars in massive galaxies.  
+	The left panel of Fig \ref{fig:ell_color} shows the ellipticity profiles of HSC 
+	massive galaxies and highlight the median profiles for the same three \mtot{} 
+	bins used in Fig \ref{fig:avg_prof}. 
+	In general, the ellipticity of massive galaxy slowly increases with radius.
+	One can even notice this trend by directly comparing the shape of galaxy between 
+	SDSS and HSC images (e.g. Fig \ref{fig:sdss_compare}).  
+	More interestingly, the ellipticity profiles clear depend on \mtot{}: 
+	at ${\sim} 10$ kpc, median ellipticities from all three bins are low and similar 
+	($< 0.2$); but more massive galaxies become increasingly more elongated in their
+	stellar halo. 	
+	For the \logms{}$>11.8$ galaxy, its median ellipticity profile becomes steeper 
+	at $>10$ kpc, and the ellipticity steadily increases from $e\le 0.2$ to 
+	$e{\sim} 0.4$ at 50-60 kpc.
+	This is consistent with studies of nearby massive galaxies, both from 1-D 
+	ellipticity profiles and 2-D modeling results \citep{Gonzalez2005, 
+	Huang2013a, Spavone2017}.
+	Although this phenomenon was well-documented, clear evidence of mass-dependent
+	ellipticity profiles and the potentially anti-correlated slopes of \mden{} and 
+	ellipticity profiles has not been identified.
+	If accreted stars dominate the stellar halos of massive galaxies, this 
+	mass-dependent ellipticity profile may lead us to some insights about the 
+	differences in their assembly history (e.g. average time since last merger, 
+	average merger mass ratio).
+	Previous simulations often focused on reproducing the rounder average shape 
+	and slow-rotating nature of massive ETGs (e.g. \citealt{Wu2014}), the projected 
+	ellipticity profiles and their correlations with the kinematic of stars and 
+	merging history have not been well explored. 
+	We also compare our ellipticity profiles with previous ones that are based on 
+	image stacking techniques (the PSF-removed $i$-band from \citealt{Tal2011}, 
+	the concentration galaxies with $11.0<$\logms{}$<11.4$ from 
+	\citealt{DSouza2015}), 
+	We notice that the stacked image sometimes fails to recover the ellipticity 
+	profile, probably due to the uncertainties in aligning galaxies before the 
+	stacking process.
+
+    As for the color profiles, it is well known that massive elliptical galaxies 
+    have shallow and negative color gradient that reflects radial variation of 
+    stellar population (e.g.\ \citealt{Carollo1993, LaBarbera2012}) and contains 
+    information about the assembly history of stellar halos (e.g. 
+    \citealt{Hirschmann2015}). 
+    The right panels of Fig \ref{fig:ell_color} show the $k$-corrected $g-r$ and 
+    $g-i$ color profiles and the median profiles in three \mtot{} bins. 
+    As expected, all median color profiles show smooth and shallow negative 
+    gradients, but we do not find evidence for mass-dependence here. 
+    We also compare our results with the stacked color profiles from  
+    \citealt{LaBarbera2010}\footnote{Use the median color profiles of high-mass 
+    ETGs; the original profile is in unit of $R_{\mathrm{e}}$, we use a typical 
+    $R_{\mathrm{e}}=8.0$ kpc to convert it into kpc unit.} and 
+    \citealt{DSouza2014}.
+    The median color profiles from HSC images are systematically steeper than the 
+    stacked SDSS ones. 
+    Considering the differences in response curves of HSC and SDSS filters, and 
+    the uncertainties of color measurements, the HSC $g-r$ color profiles are 
+    consistent with those based on SDSS images. 
+    For the $g-i$ profiles, the HSC ones still show steeper gradients. 
+    The SDSS $i$-band suffers from the so-called ``red-halo'' effect of 
+    (e.g. \citealt{Wu2005}, \citealt{Tal2011}) that could lead to redder color in 
+    the low surface brightness outskirt of galaxy.
+    HSC $i$-band image do not suffer from this effect (thanks to thick CCDs), 
+    therefore can help provide more accurate color estimates.
+    For the ones from \citet{LaBarbera2010}, uncertainty of $R_{\mathrm{e}}$ 
+    measurements could also ``smooth'' the color gradients.
+    The relative steeper color profiles have been observed in very nearby massive 
+    ETGs individually.  
+    On Fig \ref{fig:ell_color}, we also compare with the $g-r$ color profiles of 
+    NGC 4472 (\citealt{Mihos2013}) and NGC 4365 (\citealt{Mihos2017})\footnote{
+    Both are converted from $B-V$ colors}, and the $g-i$ profile of NGC 1399 
+    (\citealt{Iodice2016}). 
+    These individual profiles show similar color gradients with the HSC median ones.
+
+    % TODO: Move to discussion
+    %Ellipticity profiles contain additional information about the assembly histories 
+    %and in future work, it would be of interest to compare our ellipticity profiles 
+    %with predictions from hydrodynamic simulations such as Illustris 
+    %\citealt{Vogelsberger2014}, \citealt{Genel2014}) or \textit{Horizon-AGN} 
+    %(\citealt{Dubois2014}).
+
+    % TODO: Move this to Paper II 
+    %The ellipticity profiles of the \mtot{}-matched samples are very similar at 
+    %$r<50$ kpc (2-3$\times R_{\mathrm{e}}$ for their \mstar{}). 
+    %However, for the \minn{}-matched samples, the \rbcg{} galaxies have higher 
+    %ellipticity than the \nbcg{} ones at $r > 10$ kpc, while their inner ellipticity 
+    %profiles are very similar.  
+    %This further hints that massive central galaxies in different halos but with 
+    %similar ``in situ'' mass may experience different late-time merging histories. 
+    %Overall, the relative low ellipticity value and the fact that the ellipticity 
+    %gradients are shallow lead us to conclude that the use of an average 
+    %isophotal ellipticity is fine for this present study.
+    %We show the average ellipticity, $g-r$, and $g-i$ color profiles for the 
+    %\mtot{}-matched (\minn{}-matched) samples of \rbcg{} and \nbcg{} galaxies on the 
+    %left (right) side of \ref{fig:ell_color}. 
+    %We also compare our results with previous work based on stacking SDSS galaxies 
+    %(e.g. \citealt{LaBarbera2010, Tal2011, DSouza2014}).
+
+    %In terms of color gradients, we find shallow and negative gradients of median 
+    %$g-r$ and $g-i$ color profiles for both \rbcg{} and \nbcg{} galaxies. 
+    %For both \mtot{}- and \minn{}-matched samples, we find no significant difference
+    %in their median color profiles, which supports the assumption of using single 
+    %average \m2l{} value to estimate \mden{} profiles.
 %% ------------------------------------------------------------------------------------ %%
@@
       \caption{
-          \song{New figures to illustrate the assumption of in-situ and accreted mass;
-                Need to update the caption.}
+          \textbf{Left:}
+          Relation between \mtot{} and the fraction of \mstar{} within 10 to 100 kpc, 
+          which is used here as proxy of the fraction of accreted stars. 
+          The typical uncertainties of \mtot{} and the mass fraction are shown in 
+          upper-left corner. 
+          This relation is compared with the relation between \mstar{} and the fraction
+          of accreted stars derived from the Illustris simulation at $z=0$ 
+          (Fig 4 in \citealt{RodriguezGomez2016}; grey solid and dashed lines). 
+          \textbf{Right:}
           Comparison of the median \mden{} profiles of massive galaxies in the 
@@
           from \textit{HST} observations in \citet[][Red, dashed]{Patel2013}; 
-          3) the median \mden{} profile of the ``in-situ'' stellar components in 
+          3) the median \mden{} profile of the \textit{in situ} stellar components in 
           simulated massive halos from \citet[][Purple, dot-dashed]{Cooper2013};
@@
           discovered by \citet[][Yellow, dashed]{Liu2013} in the Hubble 
-          Ultra-Deep Field.}
+          Ultra-Deep Field.
+          }
       \label{fig:discussion_1}
@@
 
-    By using deep imaging from the HSC survey we have shown that the stellar mass 
-    density profiles of massive central galaxies depend systematically on the mass 
-    of their host dark matter halos. 
-    Here we discuss the physical origin, scientific implications, and potential 
-    caveats of this result.
-
-%% ------------------------------------------------------------------------------------ %%
-
-\subsection{The ``Two phase'' Formation Scenario of Massive Galaxies and the 
-            Build-Up of Outer Envelopes}
-
-    {\bf Do we need two different sections and two different radial profile figures?}
-
-    Our results are consistent with the picture that massive central galaxies form via 
-    a ``two-phase'' scenario. 
-    According to this theory, the cores of massive galaxies were formed at $z{\sim} 2$ 
-    during an intense period of in-situ star formation. 
-    The outskirts of massive galaxies are then built up via a more gradual second 
-    phase of evolution (the ``ex-situ'' phase) which is dominated by mass growth via 
-    the accretion of satellite systems. 
-    Non-dissipative minor mergers mostly deposit stars on the outskirts of the 
-    centrals and do not have large impact on the central \mden{} profile 
-    (e.g. \citealt{Oogi2013, Bedorf2013}). 
-    Hence, according to this picture, the outer stellar envelopes of massive centrals 
-    should correlate with the masses of their host halos, in qualitative agreement with
-    our findings.
-
-    State of the art hydrodynamic simulations suggest that massive dark matter halos 
-    have central galaxies that have outer stellar envelopes with shallow slopes 
-    (e.g. \citealt{Pillepich2014}). 
-    This is consistent with the results in Fig \ref{fig:prof_1}.
-
-    Meanwhile, these simulation also point out that the fraction of accreted stars 
-    increases steeply with total \mstar{} and that the ``ex-situ'' component
-    starts to dominate the \mden{} profiles around $R_{\mathrm{e}}$ for 
-    \logms{}$\geq 11.5$ galaxies. 
-    In this work, we find that the median \mden{} profiles of \rbcg{} and \nbcg{} 
-    samples start to show differences around 15-20 kpc, which is close to 
-    their $R_{\mathrm{e}}$. 
-    Furthermore, the environmental dependence of our median \mden{} profiles 
-    becomes more significant in our highest \mtot{} bin (see Fig \ref{fig:prof_4}). 
-    These results all align with the picture that the \mhalo{}-dependence of the 
-    \mden{} profiles of massive galaxies is driven by the variations in the 
-    ``ex-situ'' component at large radii.
-
-    We now investigate to what degree our assumption that the inner 10 kpc \mstar{}
-    corresponds to an in-situ mass.    
-    Fig \ref{fig:discussion_1} compares the median \mden{} profiles of the 
-    galaxies in two \mtot{} bins 
-    ($11.4\leq$\logmtot{}$<11.6$ and $11.6\leq$\logmtot{}$<11.8$) with 
-    (1) the median \mden{} profiles of massive ETGs at $1.0 < z < 1.5$ in
+    With the help of deep HSC images, we trace the stellar mass distributions of 
+    $0.3 < z < 0.5$ massive galaxies out to $>100$ kpc, and reveal the mass-dependent 
+    nature of their stellar halos.
+    Here we briefly discuss the physical origin, scientific implications, and potential 
+    caveats of these results.
+
+    % TODO: Move to Paper II
+    %By using deep imaging from the HSC survey we have shown that the stellar mass 
+    %density profiles of massive central galaxies depend systematically on the mass 
+    %of their host dark matter halos.
+
+%% ------------------------------------------------------------------------------------ %% 
+\subsection{The Formation of Massive Galaxies and the Assembly of Outer Halos}
+    \label{ssec:twophase}
+
+    The mass-dependent nature we find in the \mden{} and ellipticity profiles of 
+    massive galaxies are consistent with the two-phase formation scenario. 
+    According to this theory, the ``cores'' of massive central galaxies are formed 
+    at $z{\sim} 2$ during an intense period of \textit{in situ} star formation. 
+    The outskirts of massive galaxies are then built up through a more gradual second 
+    phase of evolution (the \textit{ex situ} phase) that is dominated by mass assembly via 
+    accretion and merger.
+    Non-dissipative mergers, especially the minor ones, mostly deposit stars in the 
+    outskirts of the centrals and do not have large impact on the central \mden{} 
+    profile (e.g. \citealt{Oogi2013, Bedorf2013}).
+    Given the stochastic nature of the merging process, it is easy to understand why 
+    the \mden{} profiles of massive galaxies are similar in the inner region but show
+    large and continuous scatter in the outskirt.
+
+    State of the art hydrodynamic simulations of massive galaxy formation predict 
+    that the fraction of accreted stars should strongly increase with their stellar 
+    mass and the ``ex-situ'' component dominate the stellar halo (e.g.
+    \citealt{Oser2010, Cooper2013, Dubois2013, LeeYi2013, Hirschmann2015,
+    RodriguezGomez2016}). 
+    This picture is supported by the increasingly more prominent stellar halos in 
+    more massive galaxies and the negative color gradients we see in these massive 
+    galaxies. 
+    The slightly bluer color in their outskirts are consistent with the picture that 
+    the stars there are from less massive galaxies on the ``red-squence''.
+
+    Also under this picture, the shape of the stellar halo should preserve information
+    about the merging history and even the dark matter halos. 
+    Simulations show that, for slow-rotating massive ETGs experienced multiple 
+    minor-mergers, the shape of the stellar and dark matter halos are closely 
+    correlated (e.g. \citealt{Wu2014}). 
+    However, simulation like the one in \citet{Wu2014} predicts that more massive 
+    galaxies should be rounder in the outskirt.
+    This difference deserves more investigations using stellar kinematics and 
+    simulations. 
+    It may reflect the importance of major merger in shaping the most massive 
+    galaxies. 
+    Major merger with central galaxy of massive halo often happens on near-radial 
+    orbits, hence leads to (e.g. \citealt{Murante2007}) radially biassed stellar 
+    orbits and more elongated halo.
+
+    At a larger scale, the distribution of satellites in massive halo is known to 
+    intrinsically align with the central galaxy (e.g. \citealt{Brainerd2005, 
+    Yang2006b, NiedersteOstholt2010, HuangMandelbaum2016}), and the alignment signal
+    is stronger for more massive galaxies (e.g. \citealt{Hirata2007}).
+    The fact that more massive central galaxies have steeper ellipticity profiles 
+    and become increasingly more elongated in the outskirt may help understand 
+    the physical causes of the intrinsic alignment. 
+    Moreover, the shape of the dark matter halo can now be estimated using both 
+    satellite distributions and weak lensing analysis (\citealt{ClampittJain2016}). 
+    It is interesting to point out that the most recent measurement by 
+    \citet{Shin2017} around SDSS clusters show a halo axis-ratio of ${\sim}0.55$, 
+    which is only slightly more elongated than the stellar halo of galaxies in our 
+    highest \mtot{} bin.
+
+    % TODO: Move to paper II     
+    %State of the art hydrodynamic simulations suggest that massive dark matter halos 
+    %have central galaxies that have outer stellar envelopes with shallow slopes 
+    %(e.g. \citealt{Pillepich2014}). 
+    %This is consistent with the results in Fig \ref{fig:prof_1}.
+
+    %Hence, according to this picture, the outer stellar envelopes of massive centrals 
+    %should correlate with the masses of their host halos, in qualitative agreement with
+    %our findings.
+
+%% ------------------------------------------------------------------------------------ %% 
+\subsection{Aperture Masses as Proxies of the \textit{In situ} and Accreted Stars}
+    \label{ssec:insitu}
+
+    Recent hydrodynamic simulations of galaxy formation often separate the stars in 
+    galaxy into the \textit{in situ} and accreted components. 
+    In simulation, the \textit{in situ} component is often defined as the stars formed 
+    in the halo of the ``main progenitor''.  
+    The spatial distribution, kinematic, and stellar population properties of both 
+    components become important theoretical predictions to be examined. 
+    Among them, the fraction of the accreted component and its relation with stellar 
+    mass is the most fundamental one. 
+    However, on the observational side, separation of these two physical components 
+    is extremely difficult. 
+    Recently, deep surveys of nearby disk galaxies start to provide constraints of 
+    their accreted fraction using the distinctive halo components. 
+    For more massive ETGs, efforts so far all depend on multi-component model fitting
+    and image stacking analysis (e.g. \citealt{Huang2013a, dSouza2014, Spavone2017}).
+    In this work, we propose that \mstar{} within different physical apertures could 
+    be explored as potential proxies of masses in \textit{in situ} and accreted 
+    components.  
+    Given the behaviours of the \mden{} profiles shown in Fig \ref{fig:avg_prof}, 
+    we propose to use mass within 10 kpc (\minn{}) and 100 kpc (\mtot{}) as proxies 
+    of the \textit{in situ} and total \mstar{}.
+
+    On the left panel of Fig \ref{fig:discussion_1}, we plot the relation between 
+    \mtot{} and the fraction of mass between 10 and 100 kpc (as proxy of the mass of 
+    the accreted component), and compare with the relation between \mstar{} and 
+    accreted fraction derived from the Illustris simulation 
+    (\citealt{RodriguezGomez2016}). 
+    It is intriguing to see that, our proxy of accreted mass not only strongly 
+    correlates with \mtot{}, the relation is surprisingly consistent with the 
+    prediction from \citet{RodriguezGomez2016}. 
+    Given the limitations of the Illustris simulation and the different definitions
+    of total stellar mass, the almost perfect consistency may well be a coincidence. 
+    However, it is encouraging to see that our arbitrary choices of aperture masses 
+    can already reproduce similar slope and scatter of this relation. 
+    Right now, there are other hydrodynamic simulations that predict significantly 
+    different mass fraction of accreted stars at fixed \mstar{} (e.g. 
+    \citealt{Lackner2012, Qu2017}). 
+    Therefore, it will be very useful to perform more detailed comparisons with 
+    these simulations and explore the possibilities of using certain aperture mass 
+    to trace the \textit{in situ} component.
+
+    % TODO: Move to Paper II
+    %Meanwhile, these simulation also point out that the fraction of accreted stars 
+    %increases steeply with total \mstar{} and that the ``ex-situ'' component
+    %starts to dominate the \mden{} profiles around $R_{\mathrm{e}}$ for 
+    %\logms{}$\geq 11.5$ galaxies. 
+    %In this work, we find that the median \mden{} profiles of \rbcg{} and \nbcg{} 
+    %samples start to show differences around 15-20 kpc, which is close to 
+    %their $R_{\mathrm{e}}$. 
+    %Furthermore, the environmental dependence of our median \mden{} profiles 
+    %becomes more significant in our highest \mtot{} bin (see Fig \ref{fig:prof_4}). 
+    %These results all align with the picture that the \mhalo{}-dependence of the 
+    %\mden{} profiles of massive galaxies is driven by the variations in the 
+    %``ex-situ'' component at large radii.
+
+    To further check whether \minn{} can reasonably represent the \textit{in situ} 
+    mass, we compare the average \mden{} profiles of HSC massive galaxies in two 
+    \mtot{} bins (Left panel of Fig \ref{fig:discussion_1}, 
+    $11.4\leq$\logmtot{}$<11.6$ and $11.6\leq$\logmtot{}$<11.8$) with:
+
+    \begin{enumerate}
+
+        \item The median \mden{} profiles of massive ETGs at $1.0 < z < 1.5$ in
             \citealt{Patel2013} since they are considered as the progenitors of 
-    ${\sim} 10^{11.5} M_{\odot}$ ETGs at $z=0$.    
-    (2) the inner components of $z{\sim} 0$ ellipticals from 2-D decomposition 
-    (\citealt{Huang2013a}).
-    As proxy of the in-situ components, \citet{Huang2013b} showed they are 
-    structurally similar to the compact ``red nuggets'' at high-$z$. 
-    (3) the ``in-situ'' components of simulated central galaxies in massive halos 
-    from \citet{Cooper2013} (the inner ${\sim} 5$ kpc is quite uncertain due to the 
-    resolution).  
-    The comparison confirms that \minn{} should be reasonable proxy of the 
-    ``in-situ'' mass\footnote{We convert these \mden{} profiles to the same 
-    Chabrier IMF; but there are still differences in median \mstar{} and 
-    details in the \m2l{} estimates}.  
-    More importantly, it shows that the \mden{} profile at 
-    $\mathrm{R} > 15$-20 kpc is likely dominated by stars that are not related 
-    to the ``in-situ'' processes.
+            ${\sim} 10^{11.5} M_{\odot}$ ETGs at $z=0$ and their inner region 
+            should be dominated by \textit{in situ} stars.
+
+        \item The inner components of $z{\sim} 0$ ellipticals from 2-D 
+            decomposition (\citealt{Huang2013a}).
+            As proxy of the \textit{in situ} component, \citet{Huang2013b} showed 
+            that they are structurally similar to the compact ``red nuggets'' at 
+            high-$z$.
+
+        \item The \textit{in situ} components of simulated central galaxies in 
+            massive halos from \citet{Cooper2013} (the inner ${\sim} 5$ kpc is 
+            quite uncertain due to the resolution).  
+            These \mden{} profiles are generated using the particle tagging 
+            method (see \citealt{Cooper2010})
+
+    \end{enumerate}
 
@@
     Its \mden{} profile follows the median profile of $11.6\leq$\logmtot{}$<11.8$ 
-    massive galaxies nicely inside 10-15 kpc, but becomes much steeper in the outskirt.  
-    This unique object may present an interesting case where the inner ``core'' of a 
-    massive BCGs is already in pace at $z{\sim} 1$ when its extended envelope is still
-    under construction.
-    More BCGs like this at $0.5 < z < 1.0$ can shed light on this intriguing 
-    process, and help us confirm whether the environmental dependence of structure 
-    has already emerged within massive galaxies at higher redshift 
-    (e.g. \citealt{Papovich2012})
-
-    {\bf Have we looked at delta M as a function of Mtot?  I think that would be useful 
-    for comparison with the Oser papers, for instance. }
-
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %% 
-  \begin{figure*}
-      \centering 
-      \includegraphics[width=\textwidth]{fig/redbcg_mass_smf}
-      \caption{
-          \song{New figures to show the impact of mass definition on SMF. 
-                Need to update the caption.}
-          \textbf{Left}: Relation between \mtot{} and the logarithmic mass difference 
-          between \mmax{} and \mtot{} for both \rbcg{} (red square) and \nbcg{} 
-          (grey dot) galaxies.  The format is very similar to the left figure of 
-          Fig~\ref{fig:mass_complete}.~~
-          \textbf{Right}: The stellar mass volume-density distributions of massive 
-          galaxies after combining the \rbcg{} and \nbcg{} samples together, using 
-          both \mtot{} (black solid line) and \mmax{} (black dash line). 
-          The uncertainty for distribution using \mtot{} is shown in grey shaded region.  
-          Here, we also compare the distributions with SMF from previous works: 
-          (a): SDSS galaxies at $z{\sim} 0.1$ from \citet{Bernardi2013}; the \mstar{} 
-          is based on photometry from 2-D \ser{}$+$Exponential model fitting; 
-          (b): SDSS galaxies at $z{\sim} 0.1$ from \citet{Moustakas13} based on 
-          improved SDSS \texttt{cModel} photometry; 
-          (c): \texttt{S82-MGC} galaxies at $0.15 < z< 0.43$ from 
-          \citet{Leauthaud2016} based on PSF-matched SDSS-UKIDSS photometry.
-          Please see text for more details of the comparison.
-          }
-      \label{fig:discussion_2}
-  \end{figure*}
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %% 
-\subsection{What is the ``Total Mass'' of Massive Galaxies?}
-
-    Even with deep HSC images, it is non trivial to clearly define and measure the
-    ``total'' \mstar{} for these massive systems. 
-    As discussed in Section~\ref{ssec:mtotal}, our 1-D approach has certain advantages 
-    over the 2-D modeling method and in principle, should capture a the majority of 
-    the stellar mass. 
-    However, even though we extend to 100 kpc, there is no evidence that the profile 
-    drops to zero on these scales. 
-    We now estimate how much extra mass is ``hidden'' beyond the 100 kpc radius. 
-    For this, we integrate the \mden{} profiles out to the detection limit in 
-    surface brightness profile that is defined by the background noise.
-    We will call this the ``maximum mass'' of the galaxy (\mmax{}). 
-    For obvious reasons, we find that \mmax{} is larger than \mtot{} with an average 
-    difference of about ${\sim}0.04$ dex. 
-    The left hand side of Fig \ref{fig:discussion_2} shows differences between \mtot{}
-    and \mmax{}. 
-    On a galaxy-by-galaxy basis, the difference \mmax{}-\mtot{} depends on the slope 
-    of the stellar envelope. 
-    In this work, we have opted to in general use \mtot{} rather than \mmax{} as the 
-    uncertainty on \mmax{} is larger. 
-    However, we have checked that none of our results are changed by replacing \mtot{} 
-    via \mmax{}.
-
-    How to define and measure the ``total'' mass of a galaxy becomes a critical 
-    question when studying the high-mass end of the galaxy SMF. 
-    The issues discussed above are currently one of the primary limitations in 
-    determinations of the high-mass end of the SMF (\citealt{Bernardi2016}). 
-    Fig~\ref{fig:mass_complete} illustrated how improved \mstar{} measurement can 
-    significantly modifies the SMF. 
-    On the right hand side of Fig~\ref{fig:discussion_2}, we further highlight that 
-    the shape of SMF at high-mass end is quite sensitive to even very small 
-    change of \mstar{}. 
-    We also compare the SMFs of our HSC samples with the following previous studies:
-
-    \begin{itemize}
-
-        \item The SMF derived from a SDSS-\textit{GALEX} sample of $z{\sim} 0.1$ 
-            galaxies from \citet{Moustakas13}. 
-            Here, the total luminosity is based on the SDSS \cmodel{} magnitude. 
-            The \m2l{} is derived via SED fitting using \texttt{iSEDfit} with similar 
-            assumptions as in our work.
-
-        \item The SMF for $z{\sim} 0.1$ SDSS galaxies from \citet{Bernardi2013}. 
-            The total luminosity is based on 2-D \texttt{SerExp} models 
-            (\ser{}$+$ Exponential disk model; integrated to infinity) that 
-            recovers much more flux compared to SDSS \cmodel{} magnitudes. 
-            The \m2l{} is also from SED fitting assuming a Chabrier IMF.
-
-        \item The SMF for $0.15 < z < 0.30$ galaxies from the \texttt{S82-MGC} sample
-            \citep{Leauthaud2016} where the \mstar{} is derived using 
-            \texttt{iSEDfit} on PSF-corrected aperture photometry from 
-            \texttt{S82}.
-
-    \end{itemize}
-
-%% ------------------------------------------------------------------------------------ %% 
-    It is clear that different analyses lead to very different slopes at high-mass end. 
-    Here, we do not try to evaluate whether the differences displayed in 
-    Fig~\ref{fig:discussion_2} are dominated by differences in photometry versus 
-    assumptions about stellar population models (e.g. \citealt{Bernardi2016}). 
-    However, given that the results that we are comparing assume the same IMF and adopt 
-    similar assumptions about stellar population models, we hypothesize that the 
-    differences in Fig~\ref{fig:discussion_2} are dominated by differences in photometry. 
-    The goal of our of present paper is not to present and discuss a careful evaluation
-    of the high-mass end of the SMF -- this will be presented in a forthcoming paper 
-    once the HSC survey has accumulated more data. 
-    However, this is clearly a topic that warrants further investigation, and careful 
-    photometry measurements from HSC data will shed further light on these questions.
-
-    Finally, we emphasize that in this present study we do not attempt to separate the 
-    light of the galaxy with a potential (and distinct) ``intra-cluster''
-    light component (ICL; e.g. \citealt{Carlberg1997, Lin2004, Gonzalez2005, 
-    Mihos2005}). 
+    massive galaxies nicely inside 10-15 kpc, but becomes steeper in the outskirt.
+    It represents an interesting phase where the inner ``core'' of massive BCG is 
+    already in pace at $z{\sim} 1$ while the outer halo is still being assembled.
+
+    These comparisons certainly support the idea that \minn{} mainly consists of 
+    \textit{in situ} stars and mass at $\mathrm{R} > 15$-20 kpc is dominated by accreted 
+    component.     
+    Meanwhile, they also show that the \texttt{in situ} component 
+    could have steeper \mden{} slope and mass distribution much more extended than 
+    10 kpc\footnote{We convert these \mden{} profiles to the same 
+    Chabrier IMF; but there are still differences in median \mstar{} and 
+    details in the \m2l{} estimates}. 
+    More comparisons with massive galaxies at high redshift and simulated 
+    \textit{in situ} components will help shed light on this.
+
+    In line with the prediction from Illustris, this comparison also 
+    suggests that, at very high-mass end, the accreted component can make significant 
+    contribution even within the inner 10--20 kpc. 
+    The nature of these ``accreted'' stars in the center of massive galaxies deserve 
+    more attention. 
+    It is possible that they mainly come from major merger and used to be the 
+    \texttt{in situ} component of another massive galaxy. 
+    It would be interesting see whether there is an alternative, but also physically 
+    motivated definition of \textit{in situ} component that can be more easily examined 
+    by observation.
+
+    % TODO: Move to Paper II
+    %More BCGs like this at $0.5 < z < 1.0$ can shed light on this intriguing 
+    %process, and help us confirm whether the environmental dependence of structure 
+    %has already emerged within massive galaxies at higher redshift 
+    %(e.g. \citealt{Papovich2012})
+
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
+\subsection{Stellar Halo and Intra-cluster Light}
+
+    Finally, we emphasize that in this work we do not attempt to separate the 
+    potential (and distinct) ``intra-cluster'' light component (ICL; e.g. 
+    \citealt{Carlberg1997, Lin2004, Gonzalez2005, Mihos2005}) from the massive 
+    galaxies. 
     Instead, we adopt the view that the light of the main galaxy and the 
-    ``intra-cluster''component are a smooth and continuous distribution. 
-    A reliable isolation of a physically meaningful ICL component using photometry 
-    alone is extremely difficult, if not impossible. 
-    At the imaging depth of HSC, we find no evidence for a clearly distinction between 
-    an ``inner component'' and an ``intra-cluster'' component. 
-    Instead, most of our profiles are smoothly varying out to 100 kpc with little 
-    evidence for a distinct secondary component. 
-    We do note however, that our \rbcg{} sample contains only a small fraction of 
-    extremely massive clusters where strong evidence of photometric ICL component is 
-    often found (\mhalo{}$\simgt 10^{15}M_{\star}$). 
-    At the typical \mhalo{} of our \rbcg{} clusters, one good nearby example would be 
-    the Virgo cluster, whose ultra-deep images (e.g. \citealt{Mihos2016}) show
-    that the stellar halo of the BCG can smoothly extends beyond 100 kpc, while the 
-    ICL only becomes important outside that radius and is dominated by individual 
-    tidal features. {\bf I continue to think you are saying all gals have some ICL, rather 
-    that no galaxies have ICL...}
+    ``intra-cluster''component share a smooth and continuous distribution.
+
+    In practice, reliable isolation of a physically meaningful ICL component using 
+    photometry alone is extremely difficult, if not impossible. 
+    More importantly, he majority of massive galaxies in our samples are not considered 
+    as the BCG of a cluster (\mhalo{}$\simgt 10^{14}M_{\star}$). 
+    Even for BCGs in the \rbcg{} samples, only small fraction of them belong to very 
+    massive clusters where strong evidence of photometric ICL component is 
+    often found (\mhalo{}$\simgt 10^{15}M_{\star}$, e.g. \citealt{Presotto2014, 
+    Burke2015}).
+    For typical \rbcg{} cluster in our sample, the Virgo cluster is a good nearby 
+    example.  
+    Ultra-deep images show that the stellar halo of the BCG smoothly extends beyond 
+    100 kpc, while the ICL only becomes important outside that radius and is dominated 
+    by many individual tidal features (e.g. \citealt{Mihos2016}).
+    Therefore, it is highly unlikely the main results are driven by the ICL component.
+
+    At the imaging depth of HSC and out to 100 kpc, the \mden{} profiles of massive 
+    galaxies vary smoothly and we find no evidence for a distinctive ICL component. 
+    Although the rising stellar velocity dispersion in the outskirt of massive BCG
+    has been used as evidence of a kinematically separated ICL component (e.g. 
+    \citealt{Dressler1979, Carter1999, Kelson2002, Bender2015, Longobardi2015}), 
+    we think it is reasonable to treat the stellar halo of BCG and potential ICL as 
+    an integrate component. 
+    They both carry important information regarding the assembly of central galaxy 
+    and its dark matter halo.
 
@@
 
-\song{A few appendix need to be moved to Paper II}
-%% ------------------------------------------------------------------------------------ %%
-
-\section{A. Basic Statistical Properties of the Sample} 
-	\label{app:sedasic}
-
-    On the top-left panel of Fig~\ref{fig:sample_stats}, we show the \mtot{}-color 
-    relations using the $k$-corrected $g-r$ color. 
-    Both samples follow the same tight ``red-sequence'' with little contamination 
-    from the ``blue cloud''.
-    At fixed \mtot{}, we see little offset in color distributions of the two 
-    samples, suggesting that both samples consist of quiescent galaxies with 
-    similar average stellar population properties.  
-    This is consistent with previous result that suggests the average stellar 
-    population of massive central galaxy does not depend on \mhalo{} 
-    (e.g.\ \citealt{Park2007}).  
-    In this work, we focus on the \mstar{} range of $11.6 \le$\logmtot{}$\le 11.9$, 
-    where both samples have acceptable completeness, and their \mtot{} distributions 
-    greatly overlap (see the normalized distributions of \mtot{} in the bottom-left 
-    panel of Fig~\ref{fig:sample_stats}). 
-    As for the \minn{} distributions, the two samples overlap the most within 
-    $11.2 \le$\logmtot{}$\le 11.6$, but now they show quite different
-    distributions (bottom-right figure).
-
-    The redshift distributions also show small difference
-    (upper-right panel) even in the high-\mtot{} bin, where the redshift distribution 
-    of the \nbcg{} sample skews toward higher-$z$ end due to the contribution of BOSS 
-    spec-$z$.
-    Since this could bias the comparison of \mden{} profiles and other properties 
-    (please see Appendix\ref{app:redshift} for more details), we address this via matching 
-    the two samples in both mass and redshift distributions carefully
-    (see Appendix~\ref{app:match}).
-
-%% ------------------------------------------------------------------------------------ %% 
-  \begin{figure*}
-      \centering 
-      \includegraphics[width=16.5cm]{fig/redbcg_sample_stats}
-      \caption{
-          \textbf{Top-left}: The \logms{}-$g-r$ color relation of the \rbcg{} 
-          (red circle; detaield format is the same with the right panel of 
-          Fig~\ref{fig:mass_complete}) and \nbcg{} (grey dots) samples.
-          We apply the $k$-corrections from \texttt{iSEDFit} fitting to the colors.~~          
-          \textbf{Top-right}: the histograms of the redshift for the \rbcg{} and 
-          \nbcg{} galaxies in both \logmtot$>11.2$ and $11.6<$\logmtot{}$<11.9$
-          mass bins.
-          The vertical lines highlights the $0.3\leq z \leq 0.5$ redshift range.~~
-          \textbf{Bottom-left}: the histograms of \mtot{} for the \rbcg{} (orange-red) 
-          and \nbcg{} (grey-black) samples at both $z>0.2$ (step-filled histogram) and 
-          $0.3 \leq z \leq 0.5$ (stepped histogram). 
-          The vertical lines in both top-left and bottom-left figures highlight the 
-          $11.6<$\logmtot{}$<11.9$ mass range that will be used in the comparison of 
-          the \mtot{}-matched samples.~~
-          \textbf{Bottom-right}: the histograms of \minn{} in similar format. 
-          Here the vertical lines highlight the 
-          $11.2<$\logminn{}$<11.6$ mass range that is used for comparison.
-          \song{Update the caption}
-      }
-      \label{fig:sample_stats}
-  \end{figure*}
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %% 
-\section{B. Extraction of 1-D surface brightness profile} 
+%% ------------------------------------------------------------------------------------ %% 
+\section{A. Extraction of 1-D surface brightness profile} 
     \label{app:ellipse}
@@
     objects around the target.
-    At the depth of the HSC images, this becomes a quite difficult task, especially 
-    for massive galaxies with extended outer profiles and more satellites. 
-    Right now, the \texttt{hscPipe} tends to ``over-deblend'' around bright object, 
-    we therefore perform \texttt{SExtractor}-like background subtraction and object 
-    detection using the \texttt{SEP} Python library to generate the necessary masks.
+    At the depth of the HSC images, this becomes a challenging task, especially 
+    for massive galaxies with extended outer profiles and many satellites. 
+    At this point, the \texttt{hscPipe} tends to over-subtract the background around 
+    bright objects.  
+    The performance of its deblending process is also not optimized for extended
+    objects. 
+    For these reasons, we perform \texttt{SExtractor}-like background subtraction and 
+    object detection using the \texttt{SEP} Python library to generate the necessary 
+    masks.
     Combining two different local background models and $S/N$ thresholds, we obtain 
-    the centroid, shape, and radius that enclose 90\% of flux for each object, even 
-    the one that is close to the center of bright galaxy (left panel of 
-    Fig~\ref{fig:ell_tech}), and generate its initial elliptical mask based on these
-    information. 
-    We first create the mask that covers all contaminating objects around the target 
-    after adaptively increasing the sizes of their masks according to their brightness 
-    and distance to the target center. 
-    Generally speaking, we mask out the very bright objects or objects in the 
-    outskirt of the target a little more aggressively as they could impact the 
-    low surface brightness regions more significantly. 
-    We also create masks that are less and more aggressive to test their impacts
-    on the surface brightness profiles.
-
-    Next, we aggressively mask out all objects on the cut-out image and use this mask
-    to evaluate the background level using the distribution of pixel values after 
-    median smoothing the masked image within $6x6$ pixels.
-    This provides us a global estimate of background level along with its uncertainty. 
-    Given the typical RMS of the background pixels, the HSC \texttt{WIDE} images 
-    should reach to $> 29$ \sb surface brightness level in $i$-band.  
-    However, the global background level is often negative around our massive 
-    galaxies, indicating systematic issue in background subtraction.  
-    In current \texttt{hscPipe}, the background on each CCD is modeled with a 
+    the centroid, shape, and radius that enclose 90\% of flux for each object, 
+    including the one that is very close to the center of bright galaxy (left panel of 
+    Fig~\ref{fig:ell_tech}). 
+    Based on these information, we then create the mask that covers all contaminating 
+    objects around the target after adaptively increasing the sizes of their masks 
+    according to their brightness and distance to the central target. 
+    Generally speaking, we mask out bright objects or objects in the outskirt of the 
+    image more aggressively to reduce their impact on the surface brightness profiles 
+    in the outskirt. 
+    We also create masks that are less and more aggressive than the default one to 
+    test their impacts on the surface brightness profiles.
+
+    Next, we aggressively mask out all objects on the cut-out image.  
+    We then evaluate the background level using the unmasked pixels after median 
+    smoothing the masked image using box of $6x6$ pixels.
+    This provides estimate of global background level along with its uncertainty. 
+    Given the typical background uncertainty, the HSC \texttt{WIDE} image should be 
+    able to reach down to $> 29$ \sb surface brightness level in the $i$-band.  
+    However, as mentioned, we often find evidence of slightly over-subtracted 
+    background for massive galaxies in our sample. 
+    In the current \texttt{hscPipe}, the background on each CCD is modeled with a 
     Chebyshev-polynomial that is fit to the smoothed image after excluding pixels 
@@
         \item \mstar{} based on the \texttt{BC03} models are systematically lower 
-            than the ones based on \texttt{FSPS+MILES} models (middle panels)
+            than the ones based on \texttt{FSPS+MILES} models (middle panel)
             The difference shows a large scatter, and can be as large as 0.4 dex,
-            although it does show any \mstar{} dependency. 
-            We notice that the \texttt{BC03} provides better overall ${\chi}^2$. 
-            This could relates to the higher upper limit of stellar metallicity 
-            ($2 \times \mathrm{Z}_{\odot}$) allowed by the \texttt{BC03} model 
-            that help fit the shape of the SED in the red-end better.  
-            However, the \texttt{BC03} model could underestimate the 
-            stellar age for a fraction of massive galaxies ($< 3$--4 Gyrs), and 
-            leads to underestimate of  \m2l{} for them too.
+            although it is not \mstar{}-dependent. 
+            The \texttt{BC03} results show better average ${\chi}^2$ than the 
+            \texttt{FSPS} ones. 
+            This relates to the higher upper-limit of stellar metallicity 
+            ($2 \times \mathrm{Z}_{\odot}$) allowed by the \texttt{BC03} model, 
+            which help fits the shape of the SED in the red-end slightly better.  
+            However, the \texttt{BC03} results also show puzzlingly low stellar 
+            ages ($< 3$--4 Gyrs) for these massive, red galaxies. 
+            This could also lead to underestimated \m2l{} values.
             It is worth noting that, both \texttt{FSPS} and \texttt{BC03} 
-            models still have difficulties recovering SED at the red-end (between $z$ 
-            and Y-band), and reproducing the optical color-color relations for 
-            red-sequence galaxies (e.g.\ \citealt{MIUSCAT2}).
+            models still have difficulties recovering SED at the very red-end 
+            (between $z$ and $y$-band), and reproducing the optical color-color 
+            relations for red-sequence galaxies (e.g.\ \citealt{MIUSCAT2}).
             In this work, we decide to keep using the \texttt{FSPS+MILES} model as 
             the fiducial one.  
-            However, using the results based on \texttt{BC03} model will not 
-            only change the main conclusions here, but also results in more 
-            significant differences in the median \mden{} profiles.
-
-        \item On the right panels of Fig~\ref{fig:ised_3}, we also compare with the
+            Using results based on \texttt{BC03} model will not change any of our 
+            conclusions here.
+
+        \item On the bottom panel of Fig~\ref{fig:ised_3}, we compare with the
             SED fitting results without considering the dust extinction. 
             This choice leads to slightly smaller \mstar{} values as expected. 
-            The impact is very small for the \rbcg{} galaxies, and becomes larger 
-            at the low-\mstar{} end of the \nbcg{} sample. 
-            But it still will not change any of the important results in this work.
+            Its impact becomes slightly larger at lower \mstar{} end. 
+            It will not change any of our conclusions here.
 
     \end{enumerate}
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %% 
-\section{D. Comparison of \mden{} profiles using \mstar{} from the GAMA survey}
-    \label{app:gama}
-
-%% ------------------------------------------------------------------------------------ %% 
-\begin{figure*}
-    \centering
-    \includegraphics[width=\textwidth]{fig/redbcg_prof_gama_new}
-    \caption{
-        \textbf{Left:} comparison of \mstar{} estimated by the GAMA survey and 
-        the \mtot{} using HSC images in this work. 
-        We plot the \logmgama{} against the difference between \logmtot{} and \logmgama{}. 
-        The format is very similar to the left panel of Fig~\ref{fig:mass_complete}. 
-        The two vertical lines highlight the mass range $11.4 \leq$\logmgama{}$<11.8$ 
-        that is used for the comparison.~~
-        \textbf{Right:} we compare the \mden{} profiles of \rbcg{} (orange-red) and 
-        \nbcg{} (grey-black) galaxies using the samples matched on the 
-        \mgama{}-$z$ plane at $11.4 \leq$\logmgama{}$<11.9$ and $0.28 \leq z < 0.4$. 
-        The format is very similar to the ones in Fig~\ref{fig:prof_1}.}
-    \label{fig:gama}
-\end{figure*}
-%% ------------------------------------------------------------------------------------ %%
-
-    The GAMA survey greatly overlaps with the HSC survey, and it provides carefully 
-    measured \mstar{} for large sample of galaxies (\citealt{Taylor2011}) that help 
-    produce many interesting results (e.g. \citealt{Bauer2013, Ferreras2017}).
-    They use 2-D single-\ser{} model to correct the total luminosity of the galaxy 
-    (\citealt{Kelvin2012}), and derive the \m2l{} through optical-SED fitting 
-    (BC03 model; Chabrier IMF) based on the PSF-matched aperture photometry. 
-    Since the \ser{} model is generally more flexible than the \texttt{cModel} one, 
-    it is therefore interesting to compare with the \rbcg{} and \nbcg{} galaxies 
-    that also have spec-$z$ (at $z < 0.40$) and \mstar{} in GAMA DR2 
-    (\citealt{Liske2015}) and see the impact of deep photometry again.
-
-    We summarize the results in Fig~\ref{fig:gama}.  
-    On the left panel, we compare the differences between \mtot{} and \mgama{}. 
-    HSC survey on average recovers more \mstar{} at high-\mstar{} end, which is 
-    consistent with the expectation from deeper photometry, although the 
-    systematic differences in the estimates of \m2l{} could play a role here. 
-    Meanwhile, it is interesting see that, above \logmtot{}$> 11.8$, \mgama{} 
-    becomes increasingly larger than \mtot{}, and most of these massive 
-    galaxies have very high \ser{} index from the 2-D fitting. 
-    This suggests that the single-\ser{} model is no longer an appropriate one to 
-    describe very massive galaxies as it tends to over-estimate the \mstar{} the 
-    inner and/or outer regions.
-
-    To verify the cause of the difference in \mstar{}, we further select samples 
-    of \rbcg{} and \nbcg{} galaxies with matched \mgama{} and redshift 
-    distributions (at $11.4 <$\logmgama{}$<11.8$; see Appendix \ref{app:match}), 
-    and compare their \mden{} profiles (right panel). 
-    Although these two subsamples are equally massive according to results from 
-    GAMA survey, it is clear that the \rbcg{} galaxy has much more extended 
-    outer envelope, even though its median \mden{} profile is very similar 
-    to the \nbcg{} sample at $< 10$ kpc. 
-    We can reproduce very the same trend with the luminosity density profiles 
-    (with or without $k$-correction), suggesting that the inaccurate \ser{} 
-    model definitely leads to under-estimate of \mstar{}.
-
-%% ------------------------------------------------------------------------------------ %%
-
-\section{E. Comparisons of \mden{} profiles in different redshift bins}
-    \label{app:redshift}
-
-%% ------------------------------------------------------------------------------------ %% 
-\begin{figure}
-    \centering 
-    \includegraphics[width=8.2cm]{fig/redbcg_avg_prof_z}
-    \caption{
-        Comparison of \mden{} profiles of \rbcg{} (orange-red) and \nbcg{} 
-        (grey-black) at $11.6 \le$\logmtot$< 11.9$ in redshift bins of 
-        $0.3\leq z<0.4$ (solid lines) and $0.4\leq z<0.5$ (dash lines). 
-        We show the individual profile in the background using much thinner line, 
-        and highlight the median profiles using thicker line and darker color.
-        Other formats are exactly the same with the left figure of 
-        Fig~\ref{fig:avg_prof}.}
-    \label{fig:avg_prof_z}
-\end{figure}    
-%% ------------------------------------------------------------------------------------ %%
-
-    Given the redshift range for our samples, it is important to evaluate 
-    the impacts from the physical extend of seeing and the imaging depth on the \mden{} 
-    profiles at different redshift. 
-    Under the same seeing, the \mden{} profile of galaxy at higher-$z$ is more 
-    vulnerable to the PSF smearing effect at the center. 
-    It is also harder to reach to the same \mden{} level under the same imaging depth 
-    due to cosmological dimming and background noise.
-
-    In Fig~\ref{fig:avg_prof_z}, we group the \rbcg{} and \nbcg{} galaxies within 
-    $11.6 \le$\logmtot$< 11.9$ into two $z$ bins ($0.3\leq z<0.4$ and $0.4\leq z<0.5$),
-    and compare their \mden{} profiles. 
-    In two redshift bins, the median \mden{} profiles from the same sample follow each 
-    other very well outside 10 kpc, but become visibly different in the central 3-4 kpc,
-    where the effect from seeing kicks in. 
-    Meanwhile, the median \mden{} profiles of \rbcg{} and \nbcg{} in the same $z$ bin 
-    are identical in the central region, which indicates similar average seeing 
-    conditions.       
-    This confirms that \mden{} profile at $> 5$ kpc is safe from the impacts of seeing 
-    and difference in redshift.
-    More importantly, it also suggests that, once the redshift distributions are 
-    carefully matched, the difference of \mden{} profile is likely to be physical 
-    even in the central region.
-
-%% ------------------------------------------------------------------------------------ %%
-
-\section{F. Match the \rbcg{} and \nbcg{} samples in \mstar{} and redshift distributions}
-    \label{app:match}
-
-%% ------------------------------------------------------------------------------------ %% 
-\begin{figure*}
-    \centering 
-    \includegraphics[width=\textwidth]{fig/redbcg_match}
-    \caption{
-        \textbf{Left figure} shows the details of the \mtot{}-matching process, 
-        corresponding to the results shown in the left figure of   
-        On the top panel, we show the overall distributions of \rbcg{} (light orange boxes) 
-        and \nbcg{} (light grey dots) galaxies on the \mtot{}-$z$ plane.  
-        And, we match the two sample in the \mtot{}-$z$ space outlined by the shaded region.
-        We highlight the \rbcg{} galaxies in this region using bigger boxes in red frames, 
-        whose size reflects the $P_{\mathrm{Cen}}$ value.  
-        We also color-code them using the richness ($\lambda$) of the host cluster. 
-        The matched \nbcg{} galaxies are highlighted using darker color and bigger dots. 
-        To further evaluate the matching results, we show the distributions of \mtot{} 
-        (middle panel) and redshift (bottom panel) separately. 
-        On both panesl, we show the histograms along with their kernel density 
-        distributions.  
-        And, on the top of each panel, two sets of short vertical lines highlight the median 
-        value (solid) and the inter-quartile (dash) of each distribution.~~~
-        \textbf{Right figure} shows the similar matching results for the \minn{}-matched
-        samples used for the right figure of Fig~\ref{fig:prof_1}.
-        The format is exactly the same as the left one, except the \minn{} replaces the 
-        \mtot{} in the top and middle panels.}
-    \label{fig:match}
-\end{figure*}
-%% ------------------------------------------------------------------------------------ %%
-
-    As explained earlier, it is important to make sure the two samples have similar 
-    distributions in both \mstar{} and redshift before comparing their median \mden{} 
-    profiles.  
-    Here we briefly describe the procedure used in this work. 
-    Since the \rbcg{} sample is smaller in size, we always match the \nbcg{} sample to 
-    it by searching for the $N$-nearest neighbours on the $M_{\star}$-redshift plane 
-    using the KDTree algorithm in the \texttt{scikit-learn} Python library 
-    (\citealt{scikit-learn}), and evaluate the quality of the match using the 
-    distributions of both parameters (as shown in Fig~\ref{fig:match}).
-
-    As we only keep the unique \nbcg{} galaxies in the matched sample, we manually 
-    adjust the value of $N$ to achieve the best match. 
-    When the redshift distribution of the \rbcg{} sample becomes bi-model, we also try 
-    to split the sample into two redshift bins and match them separately. 
-    Typically $N$ is between 3 to 8.
-    In Fig~\ref{fig:match}, we demonstrate this procedure using the results for 
-    the \mtot{}-matched (Left) and the \minn{}-matched samples in Fig~\ref{fig:prof_1}
-    (Right), and the two samples are well matched in the distributions of \mtot{}
-    (or \minn{}) and redshift.  
-    For all the comparisons of \mden{} profiles in this work, we match the samples 
-    in the same way, and make sure the match has the same quality.
-
-%% ------------------------------------------------------------------------------------ %% 
-\section{G. Robustness of the \mden{} Differences} 
-	\label{app:robust}
-
-    In Fig~\ref{fig:prof_1}, we compare the \mden{} profiles of \mtot{}- and 
-    \minn{}-matched samples of \rbcg{} and \nbcg{} galaxies, and here we test the 
-    robustness of the results using a few extra tests that are illustrated in
-    Fig~\ref{fig:prof_2}, Fig~\ref{fig:prof_3}, and Fig~\ref{fig:prof_4}, and 
-    are briefly described here:
-
-    \begin{enumerate}
-
-        \item In Fig~\ref{fig:prof_2}, we group the samples into two \mtot{} bins. 
-            Given the small sample size, we extend slightly toward lower \mtot{} range 
-            ($11.5 \leq \log (M_{\star,\ 10\mathrm{kpc}}/M_{\odot}) < 11.7$ and 
-             $11.7 \leq \log (M_{\star,\ 10\mathrm{kpc}}/M_{\odot}) < 11.9$). 
-            Although the smaller sample leads to larger statistical uncertainties, 
-            we can still see similar structural differences in both \mtot{} bins, 
-            and the difference becomes more significant in the higher \mtot{} bin.  
-            For the lower \mtot{} bin, the difference in the inner region becomes 
-            quite uncertain, while the difference in the outskirt is still visible. 
-            This potentially suggests that the environmental dependence of structure 
-            also varies with \mstar{}, an important implication deserves more 
-            investigations in the future.
-
-        \item On the left panel of Fig~\ref{fig:prof_3}, we match the \rbcg{} and 
-            \nbcg{} samples in a lower redshift bins ($0.30 < z < 0.42$).
-            Despite the larger uncertainties due to smaller samples, we find the 
-            results are the same.
-
-        \item On the middle panel of Fig~\ref{fig:prof_3}, we includes \rbcg{} 
-            galaxies in poorer clusters ($20 < \lambda < 30$), which should result 
-            in overlapped \mhalo{} distributions with the \nbcg{} samples 
-            considering the typical uncertainty of $\lambda$.
-            This makes the difference in the inner region slightly less significant, 
-            but the overall results are the same.
-
-        \item On the right panel of Fig~\ref{fig:prof_3}, in stead of using \mtot{}, 
-            we use the \mmax{}--the maximum \mstar{} by integrating the \mden{} 
-            profiles to the largest radius allowed.  
-            The \mmax{} values are less reliable than \mtot{} due to the 
-            uncertainty of background subtraction and contamination from nearby 
-            bright objects, but they can serve as different estimates of the ``total''
-            \mstar{} of these galaxies.
-            As shown in Section~\ref{sec:discussion}, they on average increase
-            the \mstar{} by a little bit and affect the \rbcg{} more.
-            The differences in the \mden{} profiles still remain very similar.
-
-    \end{enumerate}
-
-    We also test the robustness of the \mtot{}-matched results using the samples with 
-    only spectroscopic redshift, the samples in the three GAMA fields, and the \rbcg{} 
-    samples without the ones in very massive halos ($\lambda > 40$).  
-    Limited by space, we do not show these results here, but they all verify the 
-    robustness of the results.
-
-    For the results from the \minn{}-matched samples:
-
-    \begin{enumerate}
-
-        \item
-            We match the two samples using both \minn{} and the \mstar{} within 15 kpc 
-            at the same time.  
-            This makes the two median \mden{} profiles very similar inside 10-15 
-            kpc, while the result in the outskirt remains the same (left panel of 
-            Fig~\ref{fig:prof_4}).
-            Use \mstar{} within 5 or 20 kpc leads to the same conclusion.
-
-        \item 
-            To make sure the two samples are comparable in their overall assembly history,
-            we also try to only include the very massive galaxies (\logmtot{}$>11.5$)
-            in both samples. 
-            This excludes the \nbcg{} galaxies that are much less massive and 
-            more ``compact'' in structure. 
-            Yet, the results regarding the structural differences remain the same.
-
-    \end{enumerate}
-
-%% ------------------------------------------------------------------------------------ %% 
-  \begin{figure*}
-      \centering 
-      \includegraphics[width=\textwidth]{fig/redbcg_prof_2}
-      \caption{
-          Comparisons of the \mden{} profiles for \mtot{}-matched \rbcg{} 
-          (orange-red) and \nbcg{} (grey-black) galaxies in lower (left; [11.5,11.70]) 
-          and higher (right; [11.7, 11.9]) \mtot{} bins. 
-          Other formats are in consistent with the right figure of Fig~\ref{fig:prof_1}.
-          The difference in median profiles is more significant in higher \mtot{} bin.
-          }
-      \label{fig:prof_2}
-  \end{figure*}
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %% 
-  \begin{figure*}
-      \centering 
-      \includegraphics[width=\textwidth]{fig/redbcg_prof_3}
-      \caption{
-        Comparisons of the \mden{} profiles for \rbcg{} (orange-red) and \nbcg{} 
-      	(grey-black) galaxies that are matched using proxies of total \mstar{}. 
-        The formats are in consistent with the right figure of Fig~\ref{fig:prof_1}.
-        The differences are, here, the samples are matched in slightly differnt ways. 
-        From left to right: a) using samples at lower redshift ($0.3 < z < 0.4$); 
-        b) using \rbcg{} sample with $\lambda > 20$ instead of 30; 
-        c) using \mstar{} within 150 kpc instead of 100 kpc.
-        The results are broadly consistent with the one in Fig~\ref{fig:prof_1}.
-        }
-      \label{fig:prof_3} 
-  \end{figure*}
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %% 
-  \begin{figure*}
-      \centering 
-      \includegraphics[width=\textwidth]{fig/redbcg_prof_4}
-      \caption{
-          Comparisons of the \mden{} profiles for \rbcg{} (orange-red) and \nbcg{} 
-          (grey-black) galaxies that are matched using the \mstar{} enclosed in the 
-          inner region. 
-          Left panel shows the results after matching the \minn{} and \meff{} together, 
-          and the right panel shows the results when only the \logmtot{}$\ge 11.5$
-          \rbcg{} and \nbcg{} galaxies are included.
-          Other formats are in consistent with the right figure of Fig~\ref{fig:prof_1}.
-          }
-      \label{fig:prof_4} 
-  \end{figure*}
 %% ------------------------------------------------------------------------------------ %%

### 2017-06-02 draft/paper2.tex
Add Komiyama-san to author list
Starts from Jenny's edit

@@
 
-    \song{This is the old version, need works}
+    \jenny{Here is a suggested shorter introduction.}   
+    One of the most intriguing observations of high-redshift galaxies from the last decade has 
+    been the dramatic size growth in massive quiescent galaxies 
+    \citep{Trujillo2006,vanDokkum2008,Damjanov2009,Cimatti2008} of factors of $2-4$ from $z \approx 2$ to the present. 
+    These observations have led to a two-phase picture of galaxy growth,
+    in which galaxies dissipatively form a central compact region and then their envelope grows around 
+    them via dry merging \citep[e.g,][]{Naab2006, Khochfar2006,Oser2010, Oser2012}, which allows for 
+    dramatic growth at late times. 
+    There is likely also a contribution from progenitor bias, in which larger galaxies become quiescent 
+    later \citep[e.g.,][]{Newman2012,XX}.
+
+	There have been a number of papers testing the two-phase picture observationally at low redshift, 
+    looking at the light profiles \citep{Huang2013a,Huang2013b,Oh2017}, color gradients (), 
+    and stellar population gradients \citep[e.g.,][]{}. The observations are generically consistent with the 
+    two-phase model. However, to really test this picture requires highly sensitive observations extending 
+    beyond 10 kpc to truly probe the material accreted at late times \citep[Illustris paper here?][]{}. The surface 
+    brightness falls rapidly in the outer parts of elliptical galaxies, making such observations very challenging. In 
+    \citet[][; Paper I hereafter]{Huanetal2017}, we showed that the Hyper-Suprime Camera Survey {\bf CITE} allows us 
+    to derive robust surface brightness profiles for {\it individual} galaxies out to 100 kpc.
+
+    In Paper I, we exploited this sensitivity to verify that the fraction of accreted mass residing in an extended
+    envelope is a function of the mass of the galaxy. Another unexplored issue is the extent to which, at fixed stellar 
+    mass, the accreted fraction depends on the surrounding halo mass. According to this two-phase formation 
+    scenario, the late time growth of massive ETGs is intrinsically tied to the growth of their host dark matter halos 
+    (e.g. \citealt{Leauthaud2012, Behroozi2013, Shankar2013}). 
+    Massive ETGs that live at the center of more massive halos should experience 
+    a different mass assembly history and should be subject to a larger merger rate 
+    compared to ETGs that live in smaller dark matter halos. 
+    A natural prediction of the two-phase formation scenario is therefore that the 
+    structural properties of massive galaxies should depend on their ``environment''. In this paper, we use our 
+    large sample of early-type galaxies, along with halo masses from RedMapper \citep{}, to explore how the mass in
+    extended stellar envelopes depends on halo mass. 
+    Paper proceeds as follows: XXX.
+
+    \song{This is the old version, needs work}
     Massive galaxies are unique laboratories for studying both cosmology and galaxy 
@@
 
-    \song{Need a much shorter version of this}
+    \song{Need a much shorter version of HSC data summar here.}
+
+    %    The \rbcg{} sample is less affected by completeness because we can utilize 
+    %photo-$z$s from \redm{}. 
+    %However, the completeness of the \nbcg{} sample is still limited by the 
+    %availability of spec-$z$s from BOSS.\alexie{Not sure this is important here.}
+
+    \jenny{Here is an attempt to include all the things we really need here.}
+    Our sample selection is described in detail in Paper I. Here we include a short summary for completeness. 
+    We focus on early-type galaxies with $0.3<z<0.5$ and stellar mass $M_*>10^{11.5}$~\msun. 
+    The redshift range includes a large enough volume to have good statistics at the high-mass end, while 
+    the stellar mass limit is set by our photometric incompleteness. HSC-identified objects are cross-matched 
+    with the spectroscopic and photometric samples from redMapper \citep{Rykoff2014}. Stellar masses are estimated 
+    using stellar population synthesis modeling of the broad-band photometry, and then the mass limit is 
+    imposed. Using comparisons with published mass functions, we demonstrate that we are complete 
+    to $M_*>10^{11.5}$~\msun\ over the full redshift range.
+
+    Finally, here we wish to focus on galaxies that live at the centers of their dark matter halos. 
+    We utilize the group information 
+    in redMapper v5.10 \citep{Rykoff2014,Rozo2015b} to identify central galaxies. We use the 
+    relation between richness $\lambda$ and stellar mass to select groups with 
+    $\lambda>30$ or $M_{\rm halo}>10^{14.2}$~\msun\ \citep[e.g.,][]{simetetal2016}. This limit is chosen 
+    to mitigate incompleteness at the high end of our redshift window. We then identify the 
+    central galaxy to have $P_{\rm CEN}>0.7$. We will refer to this sample of 164 central galaxies as \rbcg{}. The median 
+    richness of the sample is $\lambda \approx 41$ ($M_* \approx 2.2 \times 10^{14}$~\msun), and there are 
+    only 44 central galaxies in clusters with $\lambda>0.5$ ($M_* > 10^{15}$~\msun). We build a complementary 
+    sample of central galaxies in lower-mass halos by calculating the radius of each group with 
+    $\lambda>20$ \citep{Diemer2015} and 
+    then excluding galaxies within a cylinder around each group, with the thickness of the cylinder broadened to include 
+    photo-z uncertainty. The sample of {\bf XX} central galaxies living in halos with $M_* < 10^{14}$~\msun\ will 
+    be called \nbcg{}.
+
 %% ------------------------------------------------------------------------------------ %%
@@
 
-    The \rbcg{} sample is less affected by completeness because we can utilize 
-    photo-$z$s from \redm{}. 
-    However, the completeness of the \nbcg{} sample is still limited by the 
-    availability of spec-$z$s from BOSS.
-
     When comparing \nbcg{} and \rbcg{} we will also always make sure that the two 
@@
     To match the two samples by stellar mass, we will use two different methods:
-
-    \begin{itemize}
-
-        \item We match the two samples according to \mtot{}. 
-            We select galaxies from \rbcg{} with $11.6 < $\logmtot{} $<11.9$ 
-            (median \logmtot{} ${\sim} 11.74$). 
-            There are 45 \rbcg{} galaxies in this range. 
-            We then match this distribution by drawing galaxies from \nbcg{}. 
-            There are 229 unique \nbcg{} galaxies in the matched sample. 
-            In this \mtot{} range, 100 kpc corresponds to 5-8 times the effective radius 
-            and \mtot{} is a good proxy of total stellar mass.
-
-       \item We match the two samples according to \minn{}. 
-           We select galaxies from \rbcg{} with $11.2 < $\logminn{}$ < 11.6$ 
-            (median \logminn{}${\sim} 11.36$).
-            For the 56 galaxies from the \rbcg{} sample, we achieve excellent matches
-            in \minn{} and redshift using 375 \nbcg{} galaxies.
-            Motivated by recent observations and simulations, we use \minn{} as the 
-            proxy of the \mstar{} of the ``in-situ'' component.
-            We will discuss more about this assumption in 
-            Section~\ref{sec:discussion}.
-
-    \end{itemize}
 

### 2017-06-02 draft/paper2.tex
Preparation

@@
 % Version 0; preprint format; Outline of paper II by Song Huang
+% Version 1; preprint format; Edited by Jenny Greene
+% Version 2; preprint format; Edited by Song Huang
 
@@
 \def\m2l{{$M_{\star}/L_{\star}$}}
+\def\s2n{{$\mathrm{S}/\mathrm{N}$}}
 \def\mden{{$\mu_{\star}$}}
+
+\def\insitu{{\textit{in situ}}}
+\def\exsitu{{\textit{ex situ}}}
 
@@
 \newcommand{\kevin}[1]{\textcolor{green}{\textbf{[Kevin: #1]}}}
-\newcommand{\update}[1]{\textcolor{Bittersweet}{#1}}
-%\newcommand{\update}[1]{#1}
+\newcommand{\update}[1]{\textcolor{PineGreen}{#1}}
 
@@
         Kevin Bundy,$^{3,1}$
+        \newauthor
         Yen-Ting Lin,$^{5}$
-        \newauthor
         Masayuki Tanaka,$^{6}$
@@
         Satoshi Miyazaki,$^{5,8}$
+        \newauthor
         HSC collaboration 

### 2017-06-06 draft/paper1_v11.tex
Jenny's comment: 1

--- 2017-06-02 draft/paper1.tex
@@
 % Version 7; MNRAS format; Edited by SH
+% Version 10; MNRAS format; Edited by AL and JG
+% Version 11; MNRAS format; Edited by SH
 
@@
 %% ------------------------------------------------------------------------------------ %% 
-\title[Mass Dependent Stellar Halo in Massive Galaxies]{Tracing the Stellar Halo of 
-	   Massive Galaxies to 100 kpc at $0.3<z<0.5$ using the Hyper Suprime-Cam}
+\title[Mass Dependent Stellar Halo in Massive Galaxies]{Tracing the Stellar Halos of 
+	   Massive Galaxies to 100 kpc at $0.3<z<0.5$ using Hyper Suprime-Cam}
 
@@
 
-\begin{abstract}
-
-    Massive galaxies are important to our understanding of galaxy formation, and 
-    their extended stellar halos contain crucial fossil records of their assembly 
-    history. 
-    In this work, we use ${\sim}100$ deg$^2$ of deep ($>28.5$ \sb{} in $i$-band), 
-    high-quality (0.6\asec seeing) imaging data from the Hyper Suprime-Cam (HSC) 
-    survey to investigate the surface mass density profiles and outer stellar halos 
-    of massive galaxies. 
-    Our sample consists of ${\sim}7000$ massive (\mstar{}$\geq 11.5$) central galaxies 
-    at $0.3 < z < 0.5$. 
-    The depth of the HSC survey reaches ${\sim}4$ magnitudes fainter than SDSS and 
-    enables us to directly trace stellar mass distributions to 100 kpc without 
-    requiring stacking. 
-    Shallow images and/or over-simplified models like the \texttt{CModel} tend to 
-    miss the extended stellar halo and result in underestimated stellar mass in a 
-    mass-dependent way.  
-    It will impact important applications like the measurements of the stellar mass 
-    function. 
-    With these deeper data, we explicitly show that at fixed stellar mass,
-    massive central galaxies display surface mass density profiles that are not 
-    self-similar, with the outer-slope becoming shallower and the fraction of mass 
-    in the outskirt increasing with total stellar mass.
-    We also show that the ellipticity of the stellar halo increases with stellar
-    mass, while the optical color gradients do not strongly depend on stellar mass.
-    Our results are broadly consistent with the two phase formation scenario of 
-    massive galaxies in which outer envelopes are built up at late times from the 
-    accretions of small systems. 
-    The surface mass density profiles are provided in a convenient tabulated format 
-    in order to facilitate comparisons with predictions from numerical simulations 
-    of galaxy formation.
-
-\end{abstract}
+\begin{abstract} Massive galaxies display extended light profiles that can reach out to several hundreds of kiloparsecs.
+These extended stellar halos are key fossil records of the assembly history of massive galaxies.
+Using data that is both wide (${\sim}100$ deg$^2$) and deep ($>28.5$ \sb{} in the $i$-band), we  present a systematic study of the stellar halos of the most massive galaxies (\mstar{}$\geq 11.5$) using a statistically significant sample of more than $7000$ galaxies at $0.3 < z < 0.5$.
+Our  study is based on high-quality (0.6\asec seeing) imaging data from the Hyper Suprime-Cam (HSC) survey which reaches ${\sim}4$ magnitudes fainter than SDSS and  enables us to directly trace mass profiles to 100 kpc without resorting to stacking.
+Shallow images and/or over-simplified models like \texttt{CModel} cannot capture the extended stellar halo and result in underestimated stellar masses.
+We show that this has a signifcant impact on  the high mass end of the galaxy mass function.
+The surface mass density profiles of massive galaxies are not self-similar; at fixed "core mass" they display a diverse  range of outer profiles.
+Galaxies in our sample have optical color gradients that are independent of galaxy mass but stellar halo ellipticites that increases with galaxy mass.
+Our results are broadly consistent with the two phase formation scenario of massive galaxies in which outer envelopes are built up at late times from minor merging.
+We provide surface mass surface mass density profiles in a convenient tabulated format to facilitate comparisons with predictions from numerical simulations of galaxy formation.\end{abstract}
+
+%massive central galaxies display surface mass density profiles that are not 
+%    self-similar, with the outer-slope becoming shallower and the fraction of mass 
+%    in the outskirt increasing with total stellar mass (xxxxxxxxx).
 
@@
 
-    Massive galaxies are fascinating objects that have experienced complex assembly 
-    process and dramatic evolution.  
-    They are crucial for both cosmology and the study of galaxy formation. 
     Simulations of structure formation within the context of the $\Lambda$-CDM 
@@
     average effective radii ($R_{\mathrm{e}}$; e.g. \citealt{Trujillo2006, 
-    vanDokkum2008, Cimatti2008}), slightly higher central velocity dispersion and 
-    stellar mass density (\mden{}; e.g. \citealt{vandeSande2011, Belli2014}), and 
-    more disk-like morphologies (e.g. \citealt{vanderWel2011}) than their local 
-    descendants (e.g. \citealt{Bezanson2009, vanDokkum2010}) with similar stellar 
+    vanDokkum2008, Cimatti2008}).
+These high redshift galaxies also have slightly higher central velocity dispersions and stellar mass densities (\mden{}; e.g.
+\citealt{vandeSande2011, Belli2014}), and
+    more disk-like morphologies (e.g. \citealt{vanderWel2011}) than low redshift galaxies (e.g. \citealt{Bezanson2009, vanDokkum2010}) with similar stellar 
     mass.
@@
     Following this initial epoch of early formation, feedback from stars and/or AGN 
-    (e.g. \citealt{Sijacki2007, Fabian2012}) efficiently quench star formation in 
+    (e.g. \citealt{Sijacki2007, Fabian2012}) efficiently quenches star formation in 
     massive galaxies. 
-    A large fraction of these massive progenitors became quiescent at $z>1$ 
+    A large fraction of these massive progenitors are already quiescent by $z=1$ 
     (e.g. \citealt{Bezanson2009, Kriek2016}). 
     The second phase of their assembly is driven by non-dissipative processes such 
-    as dry mergers with other galaxies (e.g. \citealt{Naab2006, Khochfar2006}). 
-    To explain the observed increase of $R_{\mathrm{e}}$ (e.g. 
-    \citealt{Newman2012, vdWel2014}) as well as the build-up of the outer stellar 
-    halos of ETGs (e.g. \citealt{Szomoru2012, Patel2013}), the ``two-phase'' 
-    scenario suggests that minor mergers should dominate the mass assembly during 
-    the second phase (e.g. \citealt{Hilz2012, Hilz2013, Oogi2013, Bedorf2013, 
-    Laporte2013}).
+    as dry mergers with other galaxies (e.g.
+\citealt{Naab2006, Khochfar2006}).
+The ``two-phase'' formation of massive galaxies is  designed to both explain the observed increase in the effective radii ($R_{\mathrm{e}}$) of massive galaxies (e.g.
+    \citealt{Newman2012, vdWel2014}) and the build-up of stellar 
+    halos  (e.g.
+\citealt{Szomoru2012, Patel2013}).
+According to this formation mecanisms, minor mergers dominate the mass assembly of massive galaxies at late times (e.g.
+\citealt{Hilz2012, Hilz2013, Oogi2013, Bedorf2013, Laporte2013}).
+
     Both numerical simulations (e.g. \citealt{Oser2010}) and 
     semi-analytic models (SAM; e.g. \citealt{LeeYi2013, LeeYi2017}) agree that the 
-    mass fraction in the accreted component should increase with total stellar mass, 
-    despite their technical differences (e.g. \citealt{Lackner2012, Cooper2013, 
-    Qu2017}).
-    For instance, recent result from the Illustris \footnote{
+    mass fraction in the accreted component should increase with total galaxy stellar mass (e.g. \citealt{Lackner2012, Cooper2013, 
+    Qu2017}). For instance, recent results from the Illustris \footnote{
     \texttt{http://www.illustris-project.org/}} simulation 
     (\citealt{Vogelsberger2014}, \citealt{Genel2014}) predicts that the fraction of  
-    accreted stars increases significantly with total stellar mass at \logms{}$>11.0$, 
-    and the accreted component starts to dominate the stellar mass budget 
-    ($f_{\mathrm{accreted}}>0.5$) at \logms{}$>11.5$ (\citealt{RodriguezGomez2016}).
+    accreted stars increases significantly and reaches $f_{\mathrm{accreted}}>0.5$ at \logms{}$>11.5$ (\citealt{RodriguezGomez2016}).
 %% ------------------------------------------------------------------------------------ %%
@@
     Given the success of this two-phase scenario in explaining trends like overall size 
-    growth, it is time to confront their predictions with additional observations, 
-    especially the detailed profiles of surface mass density and shape for low redshift 
-    massive galaxies.  
-    Early one-dimensional analysis of nearby massive ETGs suggest that the 
-    single-\ser{} profile can describe their surface brightness (or surface mass 
-    density) profiles reasonably well (e.g. \citealt{Kormendy2009}; except for the
-    most central region), with the \ser{} index increasing with total luminosity 
-    (e.g. \citealt{Graham2013}).
-	However, the situation is in fact more complicated, with a suggestion from 
-	\citet{Schombert2015} that there are actually two families of light profiles:
-	the ones that follow single-\ser{} law well and the ones show significant 
-	deviation.
-	Two-dimensional analysis, meanwhile, finds that the stellar distributions 
-    of massive ETGs are often better fit by multiple-component models 
-    (e.g. \citealt{Huang2013a, Oh2017}). 
-    \citet{Huang2013b} further suggests a connection between the multi-component 
+    growth, it is time to confront this model with additional observations,  in particular, the detailed surface mass density profiles of low redshift massive galaxies.
+Early studies based on one-dimenstional light profiles, suggested that the profiles of nearby ETGs are well described by single-\ser{} profiles (e.g.
+\citealt{Kormendy2009}; except for the
+    most central region) and that the \ser{} index increases with total luminosity 
+    (e.g.
+\citealt{Graham2013}).
+However,  later work revealed a more complicated  situation  showing  that  ETGs  belong to two famillies, those that follow single-\ser{} law, versus those that significant deviation from the single-\ser{} profile \citep{Schombert2015}.
+Two-dimensional analyses have found that the stellar distributions of massive ETGs are often better fit by multiple-component models
+    (e.g. \citealt{Huang2013a, Oh2017}).  \citet{Huang2013b} further suggest a connection between the multi-component 
     nature of massive galaxies and their two-phase assembly history. 
     To further confront the two-phase scenario requires very deep observations of 
-    large samples of massive ETGs to correctly estimate their total stellar mass 
-    (e.g. \citealt{Bernardi2013, DSouza2014}) and explore their assembly history via 
-    their extended, accreted halos (e.g. \citealt{Capaccioli2015, Iodice2016, 
+    large samples of massive ETGs to correctly estimate their total stellar masses
+    (e.g. \citealt{Bernardi2013, DSouza2014}) as well as to quantify the amplitude and scatter among outer enveloppes (e.g. \citealt{Capaccioli2015, Iodice2016, 
     Iodice2017}).
-    Currently, such work is limited by the depth of imaging from large-area surveys 
-    such as the Sloan Digital Sky Survey (SDSS; e.g. \citealt{SDSSDR7, SDSSDR12}) or
-    the small sample size of massive galaxies with deep images.
-
-    In this paper, we take advantage of new high-quality (median 
-    FWHM${\sim} 0.6^{\arcsec}$ in $i$-band) and deep ($i$-band surface brightness 
+
+    To-date,  studies of the profiles of massive galaxies have been  either  been conducted  using large samples but with shallow imaging, for example the Sloan Digital Sky Survey (SDSS; e.g.
+\citealt{SDSSDR7, SDSSDR12}), or with deeper imaging  but smaller samples sizes (e.g cite CLASH AND FRONTIER FIELDS??).
+In this paper, we take advantage of new high-quality (median  seeing of
+    FWHM${\sim} 0.6^{\arcsec}$ in the $i$-band) and deep ($i$-band surface brightness 
     limit $> 28.5$\sb) images from the Hyper Suprime-Cam (HSC) Subaru Strategic 
-    Program \citep[SSP,][]{HSCDR1} to characterize the outer parts of massive galaxies 
-    as a function of their properties. 
-    The deep imaging depth and excellent seeing conditions of HSC images make them 
+    Program \citep[SSP,][]{HSCDR1} to characterize the light profiles of massive galaxies out to 100 kpc. The deep imaging depth and excellent seeing conditions of HSC images make them 
     perfect for mapping the \mstar{} distributions of massive galaxies out to very 
-    large radii. 
-    With the help of reliable spectroscopic and photometric redshift 
-    (e.g. the ones for \redm{} clusters, \citealt{Rykoff2014}; \citealt{Rozo2015b}),
-    we select a large sample (${\sim} 7000$) of massive central galaxies at 
-    $0.3 < z < 0.5$ using ${\sim} 100$ deg$^2$ of data from the HSC wide layer. 
+    large radii. We select a large sample (${\sim} 7000$) of massive central galaxies at $0.3 < z < 0.5$ using ${\sim} 100$ deg$^2$ of data from the HSC wide layer.
+
+ %       With the help of reliable spectroscopic and photometric redshift 
+ %   (e.g. the ones for \redm{} clusters, \citealt{Rykoff2014}; \citealt{Rozo2015b}),
+ %   we select a large sample (${\sim} 7000$) of massive central galaxies at 
+ %   $0.3 < z < 0.5$ using ${\sim} 100$ deg$^2$ of data from the HSC wide layer.
+
     In this paper, we use this sample to 
-    (a) reliably measure individual surface mass density (\mden{}) profile of 
+    (a) reliably measure individual surface mass density (\mden{}) profiles of 
     massive galaxy out to 100 kpc, 
@@
     mass, and 
-    (c) examine the implications for the stellar mass function (SMF) when the outer 
-    halos of massive galaxies are accounted for.   
-    In a second paper in this series, we will further look into the potential 
-    environmental dependence of structures in massive ETGs (Huang\etal in prep.).
+    (c) examine the implications in terms of  evaluating the high mass end of the galaxy stellar mass function (SMF).
+In a second paper in this series, we will investigate the environmental (dark matter halo mass) dependence of the sizes of massive ETGs (Huang\etal in prep.).
 
     This paper is organized as follows. 
-    Section \ref{sec:data} presents our data and our sample selection. 
+    Section \ref{sec:data} presents our data and sample selection. 
     Section \ref{sec:ellipse} describes our procedure for extracting 1-D surface 
@@
 
-    The HSC \texttt{WIDE} survey is about $3.0$-$4.0$ magnitudes deeper in the 
-    $i$-band surface brightness limit than SDSS. 
+    The HSC \texttt{WIDE} survey is about $3.0$-$4.0$ magnitudes deeper in terms of the $i$-band surface brightness limit than SDSS.
 Combined with the excellent imaging resolution (the median $i$-band seeing is
     0.6\asec) and the wide area, the HSC survey represents a tremendous dataset to 
-    perform large statistical study of the surface brightness profiles of massive
+    perform large statistical studies of the surface brightness profiles of massive
     galaxies out to their very outskirts.     
@@
 	of strict requirements driven by weak lensing science. 
-    We will therefore use the $i$-band images to measure the stellar distributions of 
+    We will therefore use $i$-band images to measure the stellar distributions of 
     massive galaxies.
@@
       	  galaxies (grey dots).
-      	  The running-median of the mass differences along with the standard deviations
-      	  in a series of mass bins are shown in large red, hexagons with error bars. 
-          On average, \mcmodel{} underestimates the total stellar mass of massive 
+      	  The running-median of the mass difference is shown by large red hexagons. On average, \mcmodel{} underestimates the total stellar mass of massive 
           galaxies by 0.1 dex while in some cases, the difference can exceed 0.2 dex.
@@
           \textbf{Right:} Difference between \mmax{} and \mtot{} in the same format. 
-          The average difference is small (0.02 dex) and does not show 
-          clear mass--dependence. 
-          }
+          The average difference is small (0.02 dex) and with no clear mass--dependence. }
       \label{fig:mass_diff}
@@
     define a sample that includes almost all \logms{}$\geq 11.5$ galaxies.    
-    We therefore made a conservative selection of initial sample of massive galaxies
+    We therefore perform an initial conservative selection of massive galaxies
     with $i_{\mathrm{HSC, cModel}} \leq 21.5$\footnote{We neglect small differences
-    between the response curves of SDSS-$i$ and HSC-$i$ filters.}
-    and also limit our sample to regions that have reached the required depth of 
+    between the response curves of the SDSS-$i$ and HSC-$i$ filters.}. We also limit our sample to regions that have reached the required depth of 
     the \texttt{WIDE} survey in the $i$-band.
@@
     other optical artifacts\footnote{each criterion removes less than 8\% of the 
-    entire sample.}. This sample corresponds to 1760845 galaxies and will be referred 
+    entire sample.}, this sample corresponds to 1760845 galaxies and will be referred 
     as \texttt{hscPho}. 
@@
 
-    Objects without a spectroscopic redshift are matched with the central 
-    galaxies from the \redm{} catalog using a $2.0^{\arcsec}$ matching radius. 
-    We keep the matched objects with useful red-sequence photo-$z$ 
-    ($0.3 \leq z_{\lambda} < 0.5$) in the final sample. 
-    These galaxies are the best candidates for centrals in clusters selected from 
-    SDSS DR8 data (\citealt{SDSSDR8}) via a well-tested red-sequence method. 
+    Objects without a spectroscopic redshift are matched with central 
+    galaxies from the \redm{} SDSS DR8 (\citealt{SDSSDR8}) catalog using a $2.0^{\arcsec}$ matching radius.
+Matched objects with a red-sequence photo-$z$ ($0.3 \leq z_{\lambda} < 0.5$) are included in our sample.
 The accuracy of the red-sequence photo-$z$ is sufficient (median
@@
 
-    In the end, at $0.3 \leq z \leq 0.5$, we gather a sample of 25286 galaxies with 
+    In total, at $0.3 \leq z \leq 0.5$, our sample consists of 25286 galaxies with 
     reliable redshift information (referred as \texttt{hscZ}).
     %% Saved as "dr1_wide_galaxy_icmodel_21.5.fits"
-    Among them, the BOSS and SDSS ``legacy'' LRG samples provide the majority of 
-    spec-$z$. and the GAMA survey provides additional $14$\% of spec-$z$.
+    The majority of our redshifts come from the BOSS and SDSS ``legacy'' LRG samples. The GAMA survey provides an additional $14$\% of spec-$z$.
     We choose the redshift range of $0.3 \leq z \leq 0.5$ to make sure that 
@@
     \mden{} profile can be measured out to $>100$ kpc; 
-    (3) Evolution in structure and stellar population properties can be largely 
+    (3) Redshift evolution in the stellar population properties can be largely 
     ignored.  
-    At both lower and higher redshift, the completeness of spec-$z$ sample starts 
-    to decline.  
-    Also for bright galaxies at lower redshift, the over-subtraction of background 
-    becomes a more serious issue. 
-    Before we can define our mass-complete sample of massive galaxies required for 
-    our analysis, we describe our one-dimensional photometric analysis 
-    (\S \ref{sec:ellipse}) and stellar mass estimations (\S \ref{sec:mstar}). 
-    We then define the final sample in \S \ref{sec:final}.
+    Also at higher redshift, the completeness of the spec-$z$ sample starts to decline.
+And finally, the over-subtraction of the background level becomes a more serious issue at lower redshifts.
+We will now describe our one-dimensional photometric analysis  (\S \ref{sec:ellipse}) and our stellar mass estimates (\S \ref{sec:mstar}).
+We will then define the final sample in \S \ref{sec:final}.
 
@@
 
-    The surface brightness profile of massive ETG can not be well modeled by the 
+    The surface brightness profiles of massive ETG are not well modeled by the 
     de~Vaucouleurs or single-\ser law, especially at the imaging depth of HSC.
@@
     models (e.g \citealt{Huang2013a, Huang2013b, Oh2017}), but they are still 
-    sensitive to the choices of models (e.g. de~Vaucouleurs or \ser{} profile), 
-    the number of components, initial guesses of parameters, and the internal 
+    sensitive to the choice of a particular model (e.g. de~Vaucouleurs or \ser{} profile), 
+    the number of components, initial guesses of parameters, and internal 
     degeneracies among different parameters. 
-    Background subtraction uncertainty also affects the 2-D model fitting 
-    dramatically, especially for massive ETGs in our sample. 
+    Background subtraction uncertainties can also affect the 2-D model fitting method, especially for the massive ETGs that make up our sample.
+
     We therefore perform elliptical isophote fitting using the IRAF \texttt{Ellipse} 
     algorithm (Jedrzejewski 1987) to estimate the total luminosities of massive 
-    galaxies and measure their one-dimensional profiles of stellar mass surface 
-    density (\mden{}). 
-    This 1-D method we adopt is less affected by the issues mentioned above. 
+    galaxies and to measure their one-dimensional stellar mass surface 
+    density profiles (\mden{}). 
+    This 1-D method is less affected by the issues mentioned above. 
     Also, we will only study galaxies in the radial range where we are not 
@@
 
-    We prepare large $i$-band cut-outs for each galaxy that extend to 750 kpc in 
+    We prepare large $i$-band postage-stamkps for each galaxy that extend to 750 kpc in 
     radius, along with a bad pixel mask and the PSF model. 
-    These cut-outs include all of the light of the galaxy and are large enough to 
+    These postage-stamlps include all of the light of the galaxy and are large enough to 
     also evaluate the background level. 
@@
     %\nbcg{} sample. 
-    It is worth noting that this excludes most major-merging massive galaxies.
+    It is worth noting that this excludes most massive galaxies undergoing major mergers.
 
     Given our exquisite profiles that extend to 100 kpc, the definition and meaning 
-    of ``total'' magnitude (and stellar mass) becomes more nuanced.
+    of ``total'' magnitude (and stellar mass) becomes nuanced.
     With the help of the \m2l{} estimated in the next section (\S \ref{sec:mstar}), 
@@
             (hereafter noted \minn{}). 
-            According to the two-phase scenario, the \textit{in situ} star-formation 
-            quickly builds up the inner, dense core of massive ETGs.  
+            According to the two-phase scenario, the \textit{in situ} star-formation phase quickly builds up the inner, dense core of massive ETGs.  
             Based on recent observation (e.g.~\citealt{vanDokkum2010}) and 
@@
             our redshift range ($1.0^{\arcsec}$ in radius equals 4.4 and 6.1 kpc 
-            at redshift 0.3 and 0.5).  
-            It is worth noting that, at very high-\mstar{} end, there can be 
-            significant contribution of accreted stars within 10 kpc 
-            (e.g. \citealt{RodriguezGomez2016}). 
-            We will further discuss the justification of this assumption in 
+            at redshifts 0.3 and 0.5 respectively).  
+            It is worth noting that, at the very high-\mstar{} end, accreted stars may make a significant contribution to the mass within 10 kpc 
+            (e.g. \citealt{RodriguezGomez2016}). We will further discuss the justification of this assumption in 
             \ref{ssec:twophase}.
@@
     extinction along with their relation with \mtot{}. 
-    All these properties behave reasonably for massive galaxies in this sample despite 
-    that we do not utilize them in this paper. 
+    All these properties behave reasonably for massive galaxies in this sample. 
     Using the $k$-corrected optical color, we can also confirm that the sample follows 
@@
     (Fig \ref{fig:mass_diff}).
-    At high-\mstar{} end (e.g. \logmtot{}$>11.6$), the average difference is larger 
+    At the high-\mstar{} end (e.g. \logmtot{}$>11.6$), the average difference is larger 
     than 0.1 dex and can be as large as 0.2--0.3 dex.  
-    More importantly, the differences between \mtot{} and \mcmodel{} clearly show 
+    More importantly, the differences between \mtot{} and \mcmodel{} clearly show a 
     dependence on total stellar mass as \mcmodel{} tends to miss more light in 
     more massive galaxies.  
-    This relates to the mass-dependence nature of the stellar halos in massive 
+    This relates to the mass-dependent nature of the stellar halos of massive 
     galaxies and the intrinsic limitation of \cmodel{} method, which we will discuss
     more in the next section.
-    Such differences also have important implications in the estimation of stellar 
-    mass function or in the study of environment-dependence of galaxy structure.  
-    We will also discuss these topics in Section \ref{sec:discussion}.
+    Such differences also have important implications for estimates of the stellar 
+    mass function and for studies of the environment-dependence of galaxy structure. These topics will be discussed in Section \ref{sec:discussion}.
 
@@
     of stars that belong to these massive galaxies, we know that their \mden{} 
-    profiles extend beyond 100 kpc without showing sign of truncation. 
+    profiles extend beyond 100 kpc without showing any signs of truncation. 
     Therefore, for massive galaxies, even \mtot{} should be only considered a lower
-    limit of the ``total'' \mstar{}. 
-    In Fig \ref{fig:mass_diff}, we also integrate the \mden{} of each galaxy to the 
-    outermost radii as \mmax{} and compare their differences with \mtot{} 
-    (right panel).  
-    Although \mmax{} is much more uncertain than \mtot{} due to background subtraction
-    and impacts from nearby objects, we see they do return more \mstar{} than \mtot{}. 
+    limit on the ``total'' \mstar{}. 
+    In Fig \ref{fig:mass_diff}, we integrate the \mden{} of each galaxy to the  edge of the postage-stamp and call this mass \mmax{}.
+The right panel of Fig \ref{fig:mass_diff} compares \mmax{} and \mtot{}.
+Uncertainties in the background subtraction , and the impact of neighbouring objects, means that \mmax{} is much more uncertain than \mtot{}.
+Nontheless, we do see that \mmax{} is larger than than \mtot{}.
 However, the mass differences are on average very small ($\sim0.02-0.03$ dex) and
-    do not show strong mass dependence.  
+    do not show a strong mass dependence.  
     This confirms that, at the current depth of HSC images, \mtot{} can be used as 
@@
     indicating gradients in \m2l{} (e.g.\ \citealt{Carollo1993, Davies1993, 
-    LaBarbera2012, DSouza2015}).
-    These color gradients are shallow and smooth out to a few times the effective 
-    radius and color gradients at the outskirts are not yet well quantified.
-    Therefore, using average \m2l{} is unlikely to bias the results on \mstar{}
-    measurements.  
-    We will discuss color gradients more in Section~\ref{ssec:ell_color}. 
-    In summary, we do not find optical color gradient shows dependence on stellar
-    mass, hence the results about the mass-dependence of the \mden{} profiles will 
-    not be affected by it.
+    LaBarbera2012, DSouza2015}). However, these color gradients are shallow and smooth out to a few times the effective 
+    radius (color gradients are larger radii are not yet well quantified). Because the gradients are shallow, using an average \m2l{} is unlikely to bias our results on \mstar{}
+    measurements. Color gradients will be discussed more in Section~\ref{ssec:ell_color}. 
+    In summary, our results about the mass-dependence of \mden{} profiles should not be affected by the asumption of a constant  \m2l{} ratio because optical color gradients in our sample do not show a dependence on  stellar mass.
 
@@
 
-    Our method for deriving total \mstar{} is similar to the method adopted by the 
-    GAMA survey (\citealt{Taylor2011, Kelvin2012}), where the average \m2l{} is from 
-    SED fitting of PSF-matched aperture photometry and the total luminosity comes from 
-    sing-\ser{} modeling of the SDSS images. 
-    To avoid the differences in stellar population assumptions, we directly compare the 
-    total luminosity within 100 kpc and the GAMA single-\ser{} luminosity for the same
-    galaxies. 
-    At high-\mstar{} end, the HSC 1-D profiles still recover more light than the 
-    single-\ser{} model on average.
-    It is likely that the GAMA models fail to capture the flux associated with the 
-    outskirts of galaxies due to the limited depth of SDSS.  
-    Meanwhile, there are also many cases where the high-\ser{} index of GAMA model leads 
-    to over-estimated total luminosity. 
-    We will discuss more of this comparison in the next paper of this series 
-    (Huang\etal in prep.).
+    %We now compare our masses with those from the GAMA survey. Our method for deriving total \mstar{} is similar to the method adopted by the 
+    %GAMA survey (\citealt{Taylor2011, Kelvin2012}), where the average \m2l{} is from 
+    %SED fitting of PSF-matched aperture photometry and the total luminosity comes from 
+    %sing-\ser{} fits to SDSS images.  
+    %To avoid differences in stellar population assumptions, we directly compare the 
+    %total luminosity within 100 kpc and the GAMA single-\ser{} luminosity for the same
+    %galaxies.
+
+    %At high-\mstar{} end, the HSC 1-D profiles still recover more light than the 
+    %single-\ser{} model on average.
+    %It is likely that the GAMA models fail to capture the flux associated with the 
+    %outskirts of galaxies due to the limited depth of SDSS.  
+    %Meanwhile, there are also many cases where the high-\ser{} index of GAMA model leads 
+    %to over-estimated total luminosity. 
+    %We will discuss more of this comparison in the next paper of this series 
+    %(Huang\etal in prep.).
 
@@
     \mstar{} completeness of the combined BOSS and SDSS samples. 
-    They estimate that the BOSS spec-$z$ sample, which is the main contributor of 
-    spec-$z$ in our massive galaxy sample, is about 80\% complete at 
-    \logms{}$\geq 11.6$ at $0.3 < z < 0.5$. 
-    As the secondary contributor, the GAMA survey is 80\% complete down to 
+    They estimate that the BOSS spec-$z$ sample, which is the main source of redshifts for our sample, is about 80\% complete at 
+    \logms{}$\geq 11.6$ at $0.3 < z < 0.5$. The GAMA survey is 80\% complete down to 
     $10^{10.8}$\msun at $z{\sim} 0.3$, but is only 80\% complete to 
@@
     sample at $0.3 \leq z_{\mathrm{s82}} \leq 0.5$.
-    We estimate \mcmodel{} values of these galaxies using our fiducial 
-    procedure\footnote{The \mstar{} using HSC photometry is in excellent with the 
-    values derived from the \texttt{S82-MGC} which includes NIR data from UKIDSS; 
-    \texttt{S82-MGC} also uses \texttt{iSEDFit} with similar assumptions.}. 
-    Figure~\ref{fig:mass_complete} compares the volume number density distributions 
-    of galaxies from \texttt{S82-MGC} with the one for galaxies in our 
-    sample\footnote{Since we do not apply any statistical correction on the 
-    completeness, we do not use the term ``stellar mass function'' to avoid confusion;
+Because the \texttt{S82-MGC} uses  cmodel  magnitudes,  in this section we use  \mcmodel{} for consistency with the  \texttt{S82-MGC} catalog.
+The \texttt{S82-MGC} also uses \texttt{iSEDFit} with similar assumptions as used in this work and we find excellent agreement between HSC  \mcmodel{} and the mass derived in  the \texttt{S82-MGC} which includes NIR data from UKIDSS;
+
+    Figure~\ref{fig:mass_complete} compares the number density distributions of galaxies from \texttt{S82-MGC} with those from our sample\footnote{We do not apply any statistical corrections forcompleteness and hence we do not use the term ``stellar mass function'' to avoid confusion;
     Errors on the distributions are estimated via bootstrap resampling}. 
@@
     %availability of spec-$z$s from BOSS.    
-    Given the average difference between \mtot{} and \mcmodel{}, we will focus on 
-    the galaxies with \logmtot{}$> 11.6$ where our sample shows good completeness.
-    The massive galaxies with $11.4 \le$\logmtot{}$<11.6$ are also included in the 
-    discussion since there is no obvious reason to worry about the impact of
-    completeness on the main results of this work.
+    Given the average difference between \mtot{} and \mcmodel{}, we will focus on galaxies with \logmtot{}$> 11.6$ where our sample shows good completeness.
+In our discussion section, we will also show results formassive galaxies with $11.4 \le$\logmtot{}$<11.6$ but we caution that our sample is incomplete in this  lower mass bin.
 
@@
 
-	With the different estimates of \mstar{} and the \mden{} profiles in hand, we now 
-	proceed to identify a sample of massive central galaxies with the help from the 
-	\redm{} galaxy cluster catalog. 
-	The ``central'' galaxy can be roughly defined as the galaxy that live in the 
+	With  \mstar{} estimates in hand, we now use the \redm{} galaxy cluster catalog to  create a sample of massive central galaxies. The ``central'' galaxy is defined as the galaxy that lives in the 
 	center of its own dark matter halo.  
-	In contrast, galaxy in a sub-halo who is orbiting within the virial radius of a 
-	more massive halo is referred to as ``satellite''. 
-	Central galaxy has its unique importance in the study of galaxy evolution and 
-	galaxy-halo coevolution.
-	Therefore, to better understand the connection between the structure of massive 
-	galaxies and the assembly history of stars and halos, we wish to focus on central 
+	In contrast, a galaxy in a sub-halo that is orbiting within the virial radius of a 
+	more massive halo is referred to as a ``satellite''. 
+	%The central galaxy has its unique importance in the study of galaxy evolution and 
+	%galaxy-halo coevolution.
+	To better understand the connection between the structures of massive 
+	galaxies and the assembly history of both their stars and dark matter halos, we wish to focus on central 
 	galaxies in this work.
 
-\subsection{Candidates of massive central galaxies}
+\subsection{Candidate massive central galaxies}
     \label{ssec:redmapper}
 
-    Identification of central galaxy is not an easy task (e.g. \citealt{Yang2007}).
-    For this purpose, we first use the \redm{} catalog to help us isolate the central 
-    galaxies in massive halos and also exclude the massive satellite galaxies in these
-    haloes.  
-    Assuming the completeness of the \redm{} catalog, we treat the rest of sample as 
-    galaxies from less massive halos.  
-    Given the smaller fraction of satellite galaxies at high-\mstar{} end (e.g. 
-    \citealt{Reid2014, Hoshino2015, Saito2016}), 
-    we further assume that the massive ones (\logmtot{}$>11.4$) among them are likely 
-    to be the central galaxies of these smaller halos.
-
-    In the first step, we make use of the \texttt{v5.10} of the \redm{} cluster 
+    The robust identification of the central galaxy is not an easy task (e.g.
+\citealt{Yang2007}).
+In this paper, we use the \redm{} catalog create a sample of massive central galaxies with minimal contamination from satellite galaxies.
+
+%    Given the smaller fraction of satellite galaxies at high-\mstar{} end (e.g. 
+%    \citealt{Reid2014, Hoshino2015, Saito2016}), 
+%    we further assume that the massive ones (\logmtot{}$>11.4$) among them are likely 
+%    to be the central galaxies of these smaller halos.
+
+    We use \texttt{v5.10} of the \redm{} cluster  catalog
     \footnote{See: http://risa.stanford.edu/redmapper/} 
@@
     We use a radius equal to $R_{\mathrm{200b}}$ and the thickness of the cylinder is 
-    set to twice the uncertainty of the photometric redshift error of the cluster. 
+    set to twice the value of the photometric redshift uncertainty of each cluster ().
+
     We convert $\lambda$ of each cluster to $M_{\mathrm{halo}}$ using the calibration 
@@
     \logmh{}$< 14.0$. 
-    We will refer to this sample of \textbf{potential central galaxies in less 
+    We will refer to this sample of \textbf{galaxies in less 
     massive halos} as the \nbcg{} sample.
-    Since we have rejected satellites in \redm{} cluster and the satellite 
-    contamination steadily decreases with stellar mass (e.g. \citealt{Reid2014, 
-    Hoshino2015, Saito2016, vanUitert2016}), the massive galaxies in the \nbcg{} 
-    sample are very likely to be the central galaxies of their own dark matter halos.
+Because we have rejected satellites in \redm{} clusters, and because above our galaxy mass cut most satellite reside in halos with $log(M_{halo})>14$ (e.g.
+\citealt{Reid2014,
+    Hoshino2015, Saito2016, vanUitert2016}),galaxies in the \nbcg{} sample should  be dominated by central galaxies.
+
     %% Saved as "dr1_nonbcg_use_sed5b.fits"
@@
     Using ${\sim} 100$ deg$^2$ of HSC data, we select a large sample of massive central 
-    galaxies with reliable redshift information, and broadly separate them two 
+    galaxies with reliable redshift information, and broadly separate them into two 
     categories based on $M_{\mathrm{halo}}$.
@@
         \item With the help of the \redm{} cluster catalog, we further select 
-            candidates of massive central galaxies in a range of \mhalo{}
-            We broadly divide the sample into the central galaxies living in halos
+            candidates of massive central galaxies in a range of \mhalo{}.
+            We broadly divide the sample into central galaxies living in halos
             with \logmh{}$\geq 14.0$ (\rbcg{}) and \logmh{}$<14.0$ (\nbcg{}). 
@@
 
-    To discuss the mass-dependence of galaxy structure, we will combine the \rbcg{}
-    and \nbcg{} samples and group them into three bins of \mtot{}.  
-    In this work, we will only separately discuss the \rbcg{} and \nbcg{} samples 
-    when we look into the impact of \mstar{} definition on the SMF in Section 
-    \ref{ssec:smf}. 
-    We will carefully look into the structural differences between the central galaxies 
-    from these two samples later (Huang\etal~in prep.).  
+    The  division of our sample into two halo mass bins is mainly relevent for Paper II.
+For this paper, we only consider the halo mass dependence on our sample when we evaluate impact of  mass estimates on the SMF in Section \ref{ssec:smf}.
+
 %% ------------------------------------------------------------------------------------ %%
@@
           lines correspond to the SMF computed using \mtot{}. 
-          Here we separate the HSC massive galaxies into the central galaxies living 
-          in halos more massive than \logmh{}$\sim14.2$ (red lines) and the ones in 
+          Here we separate our HSC sample into  centrals in halos more massive than \logmh{}$\sim14.2$ (red lines) and centrals in 
           halos with \logmh{}$<14.0$ (black lines).
@@
           line).
-          The uncertainty of distribution using \mtot{} is shown in grey shaded 
-          region.  
-          Here, we also compare the distributions with SMF from previous works: 
-          (a): SDSS galaxies at $z{\sim} 0.1$ from \citet{Bernardi2017}; the \mstar{} 
-          is based on photometry from 2-D \ser{}$+$Exponential model fitting 
+The grey  shaded region shows the resampling error on the HSC SMF.
+We  compaer our results with previous studies: (a): SDSS galaxies at $z{\sim} 0.1$ from \citet{Bernardi2017} with \mstar{} values based on photometry from 2-D \ser{}$+$Exponential model fitting
           (purple); 
@@
 
-    As one of the most fundamental statistics of galaxy population, the Stellar 
-    Mass Function (SMF) and its evolution are critical to our understanding of 
-    galaxy evolution.  
-    In Section \ref{ssec:mtotal}, we demonstrate that different methods for estimating
-    ``total'' \mstar{} can lead to quite different results, hence have a large impact 
+    The Stellar Mass Function (SMF) and its evolution are critical to our understanding of galaxy evolution. In Section \ref{ssec:mtotal}, we demonstrate that different methods for estimating
+    ``total'' \mstar{} can lead to quite different results, and hence have a large impact 
     on the high mass end of the galaxy stellar mass function (e.g. 
     \citealt{Bernardi2013, DSouza2014, DSouza2015, Bernardi2017}).
-    On average, integration of our carefully derived non-parametric \mden{} profile 
+    On average, the integration of our carefully derived non-parametric \mden{} profile 
     to 100 kpc (\mtot{}) recovers more light (hence mass) than the \texttt{cModel}
     method. 
-    At \logmtot{} $>11.6$, the difference sometimes can be larger than 0.2 dex. 
+    At \logmtot{} $>11.6$, the difference can sometimes be larger than 0.2 dex. 
     More importantly, the average difference steadily increases with \mtot{}. 
-    These differences relates to the intrinsic limitation of the \texttt{cModel} 
+    These differences relate to the intrinsic limitation of the \texttt{cModel} 
     method and also reflects the fact that more massive ETGs tend to have more 
@@
 
-    Although we do not attempt to measure SMF, we use Fig \ref{fig:smf}
-    to demonstrate the impacts from missing light and different definitions of 
-    \mstar{}.
-    The left panel of Fig \ref{fig:smf} shows the SMF\footnote{There are actually
-    the volume density distributions, we refer to them as SMFs for convenience 
-    although the incompleteness and other systematics have not been corrected}
-    computed using \mcmodel{} and \mtot{} for both the \rbcg{} and \nbcg{} samples.
-
-    Generally speaking, the use of \mtot{} instead of the \mcmodel{} shifts the SMF 
-    towards the higher-mass end without significantly modifying the slope at 
-    high-mass end.
-    Interestingly, the impact of missing flux is more prominent for the \rbcg{} 
-    galaxies whose contribution to the very high-mass end is substantial. 
-    This difference between the \rbcg{} and \nbcg{} samples here may hint that 
-    the \rbcg{} galaxies suffer more from missing light. 
-    We will look into this in details in the following work (Huang\etal in prep.).
+     Figure \ref{fig:smf} displays the impact of missing light and of different definitions of \mstar{}.
+The left panel of Fig \ref{fig:smf} shows the SMF\footnote{These are actually volume density distributions, but we refer to them as SMFs for convenience although we have not applied any completeness corrections at the low mass end} computed using \mcmodel{} and \mtot{} for both the \rbcg{} and \nbcg{} samples.
+Generally speaking, the use of \mtot{} instead of \mcmodel{} shifts the SMF
+    towards the high-mass end without significantly modifying the slope.
+    Interestingly, the impact of missing flux is more prominent for  galaxies in high mass halos (the \rbcg{} sample).
+In Paper II it will be demonstrated that this occurs because  galaxies in more massive halos have larger extended  wings than those  in low mass halos (Huang\etal in prep.).
 
@@
     limit that is defined by the background noise.
-    Although the \mden{} profile becomes more uncertain at $>100$ kpc, \mmax{} can
-    provide us certain clue about how much extra mass is ``hidden'' there. 
-    Although the average difference we find is small even at high-mass end 
-    (${\sim}0.03$ dex), on the right panel of Fig \ref{fig:smf}, we can still its 
-    influence on the SMF at high-mass end, where the slope becomes slightly 
-    shallower.
+    Although the \mden{} profiles become more uncertain at $>100$ kpc, \mmax{} helps us quantify how much extra mass may be contained at radii greater than 100 kpc.
+We find that  a 100 kpc radius captures a majority of the galaxy mass and that the impact of going from \mtot{} to \mmax{} is relatively small
 
@@
 
-    On the same figure, we also compare the HSC results with the ones from following 
-    works:
+    In Figure \ref{fig:smf} we also compare our results  with the following previous studies:
 
@@
         \item The SMF for $0.15 < z < 0.30$ galaxies from the \texttt{S82-MGC} sample
-            \citep{Leauthaud2016} where the \mstar{} is derived using 
+            \citep{Leauthaud2016} where \mstar{} is derived using 
             \texttt{iSEDfit} on PSF-corrected aperture photometry from 
             \texttt{S82}.
-            The stellar population model and star-formation history assumptions are 
-            very similar to the ones in this work, except that it uses the 
-            \texttt{BC03} model. 
-            Based on the test results from Appendix \ref{app:sed}, we simply shifts 
-            the SMF to higher \mstar{} by 0.08 dex.
-
+            The stellar population model and star-formation history that are assumed are similar to those assumed in this paper, except that the \citep{Leauthaud2016} masses use the \texttt{BC03} model \alexie{Question}.
+            Based on the test results from Appendix \ref{app:sed}, we shift the \citep{Leauthaud2016} SMF by 0.08 dex to add their data to \ref{fig:smf}. 
         \item The SMF derived from a SDSS-\textit{GALEX} sample of $z{\sim} 0.1$ 
-            galaxies from \citet{Moustakas13}. 
-            Here, the total luminosity is based on the SDSS \cmodel{} magnitude. 
-            The \m2l{} is derived via SED fitting using \texttt{iSEDfit} with similar 
-            assumptions as in our work.
+            galaxies from \citet{Moustakas13}.  Total luminosities from \citet{Moustakas13} are based on SDSS \cmodel{} magnitude. 
+            They use a \m2l{} that is derived via SED fitting using \texttt{iSEDfit} with similar 
+            assumptions as here.
 
         \item The observed SMF for $z{\sim} 0.1$ SDSS galaxies from 
-            \citet{Bernardi2017}. 
-            The total luminosity is based on 2-D \texttt{SerExp} models 
+            \citet{Bernardi2017}.  Total luminosities in  \citet{Bernardi2017} are based on 2-D \texttt{SerExp} models 
             (\ser{}$+$ Exponential disk model; integrated to infinity) that 
-            recovers much more flux compared to SDSS \cmodel{} magnitudes 
+            recover more flux compared to SDSS \cmodel{} magnitudes 
             (\citealt{Bernardi2013, Meert2015}). 
-            The \m2l{} is adopted from the SED fitting results from the ``dusty'' 
+            They use a  \m2l{} that is adopted from the SED fitting results from the ``dusty'' 
             model in \citet{Mendel2014} which share similar assumptions of stellar 
-            population models with this work.
-
+            population models with this work. \alexie{Question}.   
     \end{itemize}
 
-    To appropriately compare SMFs from different works, one needs to carefully 
+    In this work, we do not attempt to detailed comparison between different SMFs
+    \citep[e.g.,][]{Bernardi2013, Bernardi2017} \footnote{To do that, one needs to 
     separate the differences in the measurements of luminosity and \m2l{}, and 
-    takes the uncertainties of \mstar{} measurements into account\footnote{
-    Fixed uncertainty of \logms{} can lead to increasingly over-estimated 
-    volume density with \mstar{} due to the very steep slope of SMF at high-mass end.} 
-    (\citealt{Bernardi2010, Bernardi2017}), which is beyond the scope of this work.  
-    Here, we primarily want to visualize the importance of \mstar{} measurements 
-    to the SMF at high-mass end. 
-    All SMFs share similar volume density around \logms{}${\sim}11.0$, but the ones
-    that are based on \texttt{cModel} and small aperture photometry show much 
-    steeper slopes than the HSC \mtot{} one. 
-    The SMF based on single-\ser{} model seems to face the same issue. 
-    We also compare with the $z{\sim}0.1$ SMF from the GAMA survey 
-    (\citealt{Wright2017}) whose luminosity is scaled with the single-\ser{} model
-    from \citet{Kelvin2012}, and its high-mass end behavior is very similar to 
-    the \citet{Leauthaud2016} and the \citet{Moustakas13} ones. 
-    And, once the \m2l{} measurements based on similar assumptions are adopted, 
-    the SDSS SMF using the \texttt{SerExp} models from \citet{Bernardi2017} becomes 
-    surprisingly similar to the HSC \mtot{} one that is not model dependent.
-    Both SMFs highlight the importance of ``missing light'' from different angles. 
-    Right now, the \citet{Bernardi2017} sample and our HSC one have almost no 
-    galaxy in common due to the differences in redshift range, hence it is not 
-    clear whether the \texttt{SerExp} model can indeed describe the flux 
-    distributions of these massive galaxies out to $>100$ kpc. 
-    It would be interesting to look into the application of multi-component 
-    2-D models using HSC images.
-
-    In summary, the result highlights that the SMF at high-mass end is sensitive to 
-    even moderate change of \mstar{}, and illustrates the advantages of deep HSC image
-    and careful 1-D approach in estimating total \mstar{} of massive galaxies.
-    For studies about the SMF or other aspects of galaxy evolution based on 
-    shallow image or simplified model, these effects can not be neglected.
-    Although we only discuss the high-mass end, this \mstar{} range is crucial for 
-    tracing the evolution of massive galaxies and calibrating numerical simulation 
-    and semi-analytic model as it is very sensitive to the AGN-feedback recipe.   
+    take the uncertainties of \mstar{} measurements into account}.
+    Instead, we primarily aim to visualize the importance of \mstar{} measurements 
+    to the SMF at the high-mass end.
+    Despite the differences in these SMF, we can see that the ones using 
+    \texttt{cModel} or small aperture photometry can not appropriately account for 
+    the high-mass end due to the missing light in the outskirt. 
+    The $z{\sim}0.1$ GAMA SMF based on single-\ser{} model from \citet{Kelvin2012} 
+    appears to have the same issue (\citealt{Wright2017}), although the \ser{} model
+    also can overestimate the luminosity at high-mass end\footnote{Due to 
+    overestimated \ser{} index and/or effective radius.}.
+
+    And, interestingly, the \texttt{SerExp} models from \citet{Bernardi2017} (at 
+    $z{\sim}0.1$) suggest a SMF that is very close to the HSC \mtot{} one 
+    (at $z{\sim}0.4$) once the \m2l{} is derived under similar assumptions.
+    Apparently, the missing light problem is at least partially overcome by these 
+    two-component 2-D models. 
+    These two samples have different average redshifts, so it would be interesting
+    to exam whether \texttt{SerExp} is good model for massive galaxies out to 
+    $>100$ kpc using the same HSC galaxies.
+
+    The high-mass end of SMF is crucial for tracing the evolution of massive 
+    galaxies.  
+    And due to its sensitivity to physical process like the AGN-feedback, it is also 
+    important in calibrating simulation and semi-analytic model.
+    Here, using individual \mden{} profiles, we confirm that shallow images and/or
+    simplified models often lead to underestimated \mstar{} at high-mass end that 
+    can not be ignored.
 %% ------------------------------------------------------------------------------------ %%
@@
     These massive galaxies ($\ge 10^{11.4} M_{\odot}$) are known to have quite 
-    uniform properties in the inner region. 
+    uniform properties in the inner region. \jenny{if we introduce this jargon we need
+    to define it at the 1-3 sentence level. Do we need it? we are not resolving cores, right?}
     At these masses, most of them should be ``slow-rotating'' 
@@
     previous works. 
-    So far, deep \mden{} profiles of massive galaxies are rarely available. 
+    Deep \mden{} profiles of massive galaxies are rarely available. 
     Even in the nearby universe, it is still not easy to reach to the very outskirt
@@
     CGS images are deeper than SDSS images in the $r$-band, but the median 
-    profile from \citet{Huang2013a} still only reaches ${\sim} 50$ kpc for $z{\sim} 0$ 
+    profile from \citet{Huang2013a} still only reaches to ${\sim} 50$ kpc for $z{\sim} 0$ 
     massive galaxies.
@@
 %% ------------------------------------------------------------------------------------ %% 
-	Aforementioned results only use the 1-D \mden{} profiles that are baed on single 
-	band image and the flux-weighted isophotal shape, while more useful information 
-	can be gathered from the HSC images of these massive galaxies.
-	The ellipticity and $k$-corrected optical color profiles are particularly 
-	interesting.
+	%Aforementioned results only use the 1-D \mden{} profiles that are baed on single 
+	%band image and the flux-weighted isophotal shape, while more useful information 
+	%can be gathered from the HSC images of these massive galaxies.
+    So far, we have focused only on the 1-D \mden{} profiles from a single band.
+	Here we turn to the ellipticity and $k$-corrected optical color profiles.
 	We extract ellipticity profile using \texttt{Ellipse} by setting the shape of each 
 	isophote free. 
-	And by applying the $i$-band isophotes to images of other bands in the 
-	forced-photometry way, we can also measure the color profiles too. 
+	By applying the $i$-band isophotes to images of other bands in the 
+	forced-photometry way \jenny{not sure what this means?}, we can also measure the color profiles too. 
 	We apply Galactic extinction correction and \texttt{iSEDFit} $k$-correction to 
@@
 	The ellipticity of the isophote contains information about the 3-D geometry 
-	(e.g. \citealt{Chang2013, Mitsuda2017}) and kinematic (e.g. 
+	(e.g. \citealt{Chang2013, Mitsuda2017}) and kinematics (e.g. 
 	\citealt{Cappellari2012, Weijmans2014}) of stars in massive galaxies.  
 	The left panel of Fig \ref{fig:ell_color} shows the ellipticity profiles of HSC 
-	massive galaxies and highlight the median profiles for the same three \mtot{} 
+	massive galaxies and highlights the median profiles for the same three \mtot{} 
 	bins used in Fig \ref{fig:avg_prof}. 
@@
 	Previous simulations often focused on reproducing the rounder average shape 
-	and slow-rotating nature of massive ETGs (e.g. \citealt{Wu2014}), the projected 
+	and slow-rotating nature of massive ETGs (e.g. \citealt{Wu2014}), so the projected 
 	ellipticity profiles and their correlations with the kinematic of stars and 
 	merging history have not been well explored. 
+    \jenny{these sentences seem like an afterthought, maybe more natural before the main
+    results of the paragraph?}
 	We also compare our ellipticity profiles with previous ones that are based on 
@@
     the low surface brightness outskirt of galaxy.
+    \jenny{explain what the red-halo effect is}
     HSC $i$-band image do not suffer from this effect (thanks to thick CCDs), 
@@
     With the help of deep HSC images, we trace the stellar mass distributions of 
-    $0.3 < z < 0.5$ massive galaxies out to $>100$ kpc, and reveal the mass-dependent 
-    nature of their stellar halos.
+    $0.3 < z < 0.5$ massive galaxies out to $>100$ kpc and reveal the mass-dependent nature 
+    of their stellar halos.
     Here we briefly discuss the physical origin, scientific implications, and potential 
@@
 
-    The mass-dependent nature we find in the \mden{} and ellipticity profiles of 
-    massive galaxies are consistent with the two-phase formation scenario. 
-    According to this theory, the ``cores'' of massive central galaxies are formed 
+    %The mass-dependent nature we find in the \mden{} and ellipticity profiles of 
+    %massive galaxies are consistent with the two-phase formation scenario. 
+    \jenny{We find that the outer halos of massive elliptical galaxies grow more prominent and 
+    more elliptical with increasing stellar mass.}
+    According to this theory, the ``cores'' \jenny{specify 5-10 kpc is meant?} of massive central galaxies are formed 
     at $z{\sim} 2$ during an intense period of \textit{in situ} star formation. 
@@
     Non-dissipative mergers, especially the minor ones, mostly deposit stars in the 
-    outskirts of the centrals and do not have large impact on the central \mden{} 
-    profile (e.g. \citealt{Oogi2013, Bedorf2013}).
+    outskirts of the centrals and do not have a large impact on the central \mden{} 
+    profile (e.g. \citealt{Oogi2013, Bedorf2013}). \jenny{Mike BK \& Ma paper too.}
     Given the stochastic nature of the merging process, it is easy to understand why 
     the \mden{} profiles of massive galaxies are similar in the inner region but show
-    large and continuous scatter in the outskirt.
+    large and continuous scatter in the outskirt. \jenny{do not understand what continuous 
+    scatter means?}
 
@@
     about the merging history and even the dark matter halos. 
-    Simulations show that, for slow-rotating massive ETGs experienced multiple 
+    Simulations show that, slowly-rotating massive ETGs that experienced multiple 
     minor-mergers, the shape of the stellar and dark matter halos are closely 
@@
     Major merger with central galaxy of massive halo often happens on near-radial 
-    orbits, hence leads to (e.g. \citealt{Murante2007}) radially biassed stellar 
-    orbits and more elongated halo.
+    orbits (e.g. \citealt{Murante2007}), hence leading to radially biassed stellar 
+    orbits and more elongated halo. \jenny{Semyeongs paper may have some interesting relevant 
+    citations about cluster-scale simulations, that also show ICL to grow more elliptical at 
+    large radius.}
 
@@
     photometry alone is extremely difficult, if not impossible. 
-    More importantly, he majority of massive galaxies in our samples are not considered 
+    More importantly, the majority of massive galaxies in our samples are not considered 
     as the BCG of a cluster (\mhalo{}$\simgt 10^{14}M_{\star}$). 
-    Even for BCGs in the \rbcg{} samples, only small fraction of them belong to very 
-    massive clusters where strong evidence of photometric ICL component is 
+    Only a small fraction of the BCGs in the \rbcg{} sample belong to very 
+    massive clusters where the strongest photometric evidence of an ICL component is 
     often found (\mhalo{}$\simgt 10^{15}M_{\star}$, e.g. \citealt{Presotto2014, 
@@
     by many individual tidal features (e.g. \citealt{Mihos2016}).
-    Therefore, it is highly unlikely the main results are driven by the ICL component.
+    Therefore, it is highly unlikely that out main results are driven by the ICL component.
 
@@
     we think it is reasonable to treat the stellar halo of BCG and potential ICL as 
-    an integrate component. 
+    an integrated component. 
     They both carry important information regarding the assembly of central galaxy 
@@
             significantly underestimated with shallow imaging data such as SDSS and/or 
-            oversimplified model assumption (e.g. the \texttt{cModel} or single-\ser{}). 
+            oversimplified model assumptions (e.g. the \texttt{cModel} or single-\ser{}). 
             In contrast to previous work, our results do not depend on stacking or any 
@@
 
-        \item We show that the \mden{} profiles of massive galaxies within inner 
+        \item We show that the \mden{} profiles of massive galaxies within the inner 
             10-20 kpc generally show similar slopes and have relative small scatter. 
@@
         \item We show that, on average, massive galaxies have positive ellipticity 
-            gradient out to at least 60 kpc. 
+            gradients out to at least 60 kpc. 
             The average ellipticity profiles also depend on \mtot{}: more massive 
@@
     for studying the evolution of massive galaxies. 
-    Upon finishing this work, the HSC survey has already doubled its sky coverage to 
+    At present, the HSC survey has already doubled its sky coverage to 
     ${\sim} 200$ deg$^2$, and provides a much larger sample of massive central galaxies. 
     In the near future, we will extend this work to lower \mtot{} by using photometric 
-    redshifts, and we will also apply 2-D photometry method (e.g.\ \citealt{Huang2013a}) 
+    redshifts, and we will also apply 2-D photometric methods (e.g.\ \citealt{Huang2013a}) 
     to take advantages of the multi-wavelength nature of the HSC survey 

### 2017-06-06 draft/paper1_v11.tex
Jenny's comment: 2

@@
     These massive galaxies ($\ge 10^{11.4} M_{\odot}$) are known to have quite 
-    uniform properties in the inner region. \jenny{if we introduce this jargon we need
-    to define it at the 1-3 sentence level. Do we need it? we are not resolving cores, right?}
-    At these masses, most of them should be ``slow-rotating'' 
-    (e.g.\ \citealt{Cappellari13b})``core''--elliptical galaxies 
-    (e.g.\ \citealt{Lauer07}) that have ``boxy'' inner isophotal shapes and similar 
-    slopes of the inner surface brightness profiles (e.g.\ \citealt{Kormendy2009,
-    Schombert2015}).
+    uniform properties in the inner region. 
+    At these high \mstar{}, these massive elliptical galaxies are known to have 
+    quite uniform structural (e.g. \mden{} profile, isophotal shape, 
+    \citealt{Lauer07, Kormendy2009, Schombert2015} and kinematic (e.g. 
+    \citealt{Cappellari13b}) properties.
 

### 2017-06-06 draft/paper1_v11.tex
Jenny's comment: 3

@@
 	isophote free. 
-	By applying the $i$-band isophotes to images of other bands in the 
-	forced-photometry way \jenny{not sure what this means?}, we can also measure the color profiles too. 
-	We apply Galactic extinction correction and \texttt{iSEDFit} $k$-correction to 
-	both the $g-r$ and $g-i$ color profiles.
+	We also apply the isophotal information derived in $i$-band directly to other 
+	filters and extract 1-D $g-r$ and $g-i$ color profiles.
+	Both Galactic extinction correction and \texttt{iSEDFit} $k$-correction are applied 
+	to them.
 	The PSF smearing effect will make the central isophotal shape rounder than the 

### 2017-06-06 draft/paper1_v11.tex
Jenny's comment: 4

@@
 	bins used in Fig \ref{fig:avg_prof}. 
+    We also compare our ellipticity profiles with previous ones that are based on 
+	image stacking techniques (the PSF-removed $i$-band from \citealt{Tal2011}, 
+	the concentration galaxies with $11.0<$\logms{}$<11.4$ from \citealt{DSouza2015}).
+	As expected, the ellipticity profile from image stacking method tends to be 
+	shallower than the HSC one.  
+	Uncertainties in aligning galaxies before stacking and the intrinsic isophotal 
+	twist can lead to this effect.
+
 	In general, the ellipticity of massive galaxy slowly increases with radius.
@@
 	Previous simulations often focused on reproducing the rounder average shape 
-	and slow-rotating nature of massive ETGs (e.g. \citealt{Wu2014}), so the projected 
-	ellipticity profiles and their correlations with the kinematic of stars and 
-	merging history have not been well explored. 
-    \jenny{these sentences seem like an afterthought, maybe more natural before the main
-    results of the paragraph?}
-	We also compare our ellipticity profiles with previous ones that are based on 
-	image stacking techniques (the PSF-removed $i$-band from \citealt{Tal2011}, 
-	the concentration galaxies with $11.0<$\logms{}$<11.4$ from 
-	\citealt{DSouza2015}), 
-	We notice that the stacked image sometimes fails to recover the ellipticity 
-	profile, probably due to the uncertainties in aligning galaxies before the 
-	stacking process.
+	and slow-rotating nature of massive ETGs (e.g. \citealt{Wu2014}), so the 
+	projected ellipticity profiles and their correlations with the kinematic of 
+	stars and merging history have not been well explored.
 

### 2017-06-06 draft/paper1_v11.tex
Jenny's comment: 5

@@
     For the $g-i$ profiles, the HSC ones still show steeper gradients. 
-    The SDSS $i$-band suffers from the so-called ``red-halo'' effect of 
-    (e.g. \citealt{Wu2005}, \citealt{Tal2011}) that could lead to redder color in 
+    The SDSS $i$-band suffers from the so-called ``red-halo'' effect
+    (e.g. \citealt{Wu2005}, \citealt{Tal2011}). 
+    The $i$-band PSF has more prominent wing than the other bands that 
+    artificially distributes more flux to the outskirt, and lead to redder color in 
     the low surface brightness outskirt of galaxy.
-    \jenny{explain what the red-halo effect is}
     HSC $i$-band image do not suffer from this effect (thanks to thick CCDs), 

### 2017-06-06 draft/paper1_v11.tex
Jenny's comment: 6

@@
     %massive galaxies are consistent with the two-phase formation scenario. 
-    \jenny{We find that the outer halos of massive elliptical galaxies grow more prominent and 
-    more elliptical with increasing stellar mass.}
-    According to this theory, the ``cores'' \jenny{specify 5-10 kpc is meant?} of massive central galaxies are formed 
-    at $z{\sim} 2$ during an intense period of \textit{in situ} star formation. 
+    We find that the outer halos of massive elliptical galaxies grow more prominent and 
+    more elliptical with increasing stellar mass.
+    According to the two-phase formation scenario, the inner 5--10 kpc of these 
+    massive central galaxies are formed at $z>1$ during an intense period of 
+    \textit{in situ} star formation. 
     The outskirts of massive galaxies are then built up through a more gradual second 
@@
     the \mden{} profiles of massive galaxies are similar in the inner region but show
-    large and continuous scatter in the outskirt. \jenny{do not understand what continuous 
-    scatter means?}
+    large and continuous scatter in the outskirt.
 

### 2017-06-07 draft/paper1_v11.tex
Jenny's comment: 7; and more references

@@
 	The ellipticity of the isophote contains information about the 3-D geometry 
-	(e.g. \citealt{Chang2013, Mitsuda2017}) and kinematics (e.g. 
-	\citealt{Cappellari2012, Weijmans2014}) of stars in massive galaxies.  
+	(e.g. \citealt{Tremblay1995, Tremblay1996, Chang2013, RodriguezPadilla2013, 
+	Mitsuda2017}) and kinematics (e.g. \citealt{Cappellari2012, Weijmans2014}) of 
+	stars in massive galaxies.  
 	The left panel of Fig \ref{fig:ell_color} shows the ellipticity profiles of HSC 
@@
 	This is consistent with studies of nearby massive galaxies, both from 1-D 
-	ellipticity profiles and 2-D modeling results \citep{Gonzalez2005, 
-	Huang2013a, Spavone2017}.
+	ellipticity profiles and 2-D modeling results \citep{Porter1991, Gonzalez2005, 
+	Zibetti2005, Spavone2017; Huang2013a, Oh2017}.
 	Although this phenomenon was well-documented, clear evidence of mass-dependent
@@
     outskirts of the centrals and do not have a large impact on the central \mden{} 
-    profile (e.g. \citealt{Oogi2013, Bedorf2013}). \jenny{Mike BK \& Ma paper too.}
+    profile (e.g. \citealt{BoylanKolchin2008, Oogi2013, Bedorf2013}).
     Given the stochastic nature of the merging process, it is easy to understand why 
     the \mden{} profiles of massive galaxies are similar in the inner region but show
-    large and continuous scatter in the outskirt.
+    larger scatter in the outskirt.
 
@@
     correlated (e.g. \citealt{Wu2014}). 
+    The more elongated outer halo and the trend between ellipticity profile and 
+    stellar mass may reflect that the orbital properties of infalling satellite are 
+    not random. 
+    In simulations, satellite orbit becomes more radial when it falls into more 
+    massive halos and when the satellite-central mass ratio is high (e.g. 
+    \citealt{Murante2007, Wetzel2011, Jiang2015}.
+    In principle, these results help explain the observed trend, and emphasize the 
+    importance of major merger in shaping the halo of massive galaxies. 
     However, simulation like the one in \citet{Wu2014} predicts that more massive 
@@
     simulations.
-    It may reflect the importance of major merger in shaping the most massive 
-    galaxies. 
-    Major merger with central galaxy of massive halo often happens on near-radial 
-    orbits (e.g. \citealt{Murante2007}), hence leading to radially biassed stellar 
-    orbits and more elongated halo. \jenny{Semyeongs paper may have some interesting relevant 
-    citations about cluster-scale simulations, that also show ICL to grow more elliptical at 
-    large radius.}
 

### 2017-06-07 draft/paper1_v11.tex
Alexie's comment: Uncertainties on SMF

@@
           lines correspond to the SMF computed using \mtot{}. 
-          Here we separate our HSC sample into  centrals in halos more massive than \logmh{}$\sim14.2$ (red lines) and centrals in 
-          halos with \logmh{}$<14.0$ (black lines).
+          Here we separate our HSC sample into  centrals in halos more massive than
+          \logmh{}$\sim14.2$ (red lines) and centrals in halos with \logmh{}$<14.0$ 
+          (black lines).
           The impact on the SMF can exceed 0.2 dex for massive central galaxies in 
@@
           line).  
-The grey  shaded region shows the resampling error on the HSC SMF.
-We  compaer our results with previous studies: (a): SDSS galaxies at $z{\sim} 0.1$ from \citet{Bernardi2017} with \mstar{} values based on photometry from 2-D \ser{}$+$Exponential model fitting
+          The grey shaded region shows the resampling error on the HSC SMF plus a 20\%
+          uncertainties to account for other issues in our sample. 
+          We compare our results with previous studies: 
+          (a): SDSS galaxies at $z{\sim} 0.1$ from \citet{Bernardi2017} with \mstar{} 
+          values based on photometry from 2-D \ser{}$+$Exponential model fitting 
           (purple); 
@@
     to the SMF at the high-mass end.
+    We do not include satellite galaxy in our sample (could affect ${\sim}10$\% of 
+    galaxies at this very high-mass end) and can not extract 1-D \mden{} profile 
+    for a small fraction of galaxies due to severe contamination of nearby object. 
+    Therefore, we should expect at least ${\sim}20$\% uncertainties in the current 
+    volume density distributions (shown as the shaded region on Fig \ref{fig:smf}).
     Despite the differences in these SMF, we can see that the ones using 

### 2017-06-07 draft/paper1_v11.tex
Simulations of ICL

@@
     and its dark matter halo. 
+    In recent years, we can start to investigate the origin and evolution of ICL using 
+    simulations where physical separation of ICL is possible
+    (e.g. \citealt{SommerLarsen2005, Murante2007, Martel2012, Cui2014, Cooper2015, 
+    Harris2017}). 
+    It will be interesting to perform detailed comparisons between these simulations 
+    and deep HSC observations to look into the contributions from different stellar 
+    components to the halo of massive galaxy.
 

### 2017-06-07 draft/paper1_v11.tex
Updated abstract

@@
 
-\begin{abstract} Massive galaxies display extended light profiles that can reach out to several hundreds of kiloparsecs.
-These extended stellar halos are key fossil records of the assembly history of massive galaxies.
-Using data that is both wide (${\sim}100$ deg$^2$) and deep ($>28.5$ \sb{} in the $i$-band), we  present a systematic study of the stellar halos of the most massive galaxies (\mstar{}$\geq 11.5$) using a statistically significant sample of more than $7000$ galaxies at $0.3 < z < 0.5$.
-Our  study is based on high-quality (0.6\asec seeing) imaging data from the Hyper Suprime-Cam (HSC) survey which reaches ${\sim}4$ magnitudes fainter than SDSS and  enables us to directly trace mass profiles to 100 kpc without resorting to stacking.
-Shallow images and/or over-simplified models like \texttt{CModel} cannot capture the extended stellar halo and result in underestimated stellar masses.
-We show that this has a signifcant impact on  the high mass end of the galaxy mass function.
-The surface mass density profiles of massive galaxies are not self-similar; at fixed "core mass" they display a diverse  range of outer profiles.
-Galaxies in our sample have optical color gradients that are independent of galaxy mass but stellar halo ellipticites that increases with galaxy mass.
-Our results are broadly consistent with the two phase formation scenario of massive galaxies in which outer envelopes are built up at late times from minor merging.
-We provide surface mass surface mass density profiles in a convenient tabulated format to facilitate comparisons with predictions from numerical simulations of galaxy formation.\end{abstract}
+\begin{abstract}
+
+    Massive galaxies display extended light profiles that can reach out to several 
+    hundreds of kilo parsecs. 
+    These extended stellar halos are key fossil records of the assembly history of 
+    massive galaxies.  
+    Using data that is both wide (${\sim}100$ deg$^2$) and deep ($>28.5$ \sb{} in 
+    the $i$-band), we present a systematic study of the stellar halos of the most 
+    massive galaxies (\mstar{}$\geq 11.5$) using a statistically significant sample 
+    of more than $7000$ galaxies at $0.3 < z < 0.5$. 
+    Our study is based on high-quality (0.6\asec seeing) imaging data from the Hyper 
+    Suprime-Cam (HSC) survey which reaches ${\sim}4$ magnitudes fainter than SDSS in 
+    surface brightness and enables us to directly trace mass profiles to 100 kpc 
+    without resorting to stacking. 
+    Shallow images and/or over-simplified models like \texttt{CModel} cannot capture 
+    the extended stellar halo and result in underestimated stellar masses. 
+    Our extended profiles reveal a number of mass-dependent trends. 
+    We find that the halos of massive galaxies have higher ellipticity, and that the 
+    outer ellipticity increases with stellar mass, but we find no evidence for trend 
+    between stellar mass and color gradients. 
+    As in previous work, we see a clear trend towards more extended outer profiles in 
+    more massive galaxies. 
+    Thus, when this extended light is not properly accounted for, the stellar mass 
+    function is systematically underestimated at the highest masses. 
+    Our results are broadly consistent with the two-phase formation scenario of 
+    massive galaxies in which outer envelopes are built up at late times from series
+    of mergers. 
+    We provide surface mass density profiles in a convenient tabulated format to 
+    facilitate comparisons with predictions from numerical simulations of galaxy 
+    formation.
+
+\end{abstract}
 

### 2017-06-13 draft/paper1_rachel.tex
Comments from Rachel

--- 2017-06-07 draft/paper1_v11.tex
@@
 \newcommand{\kevin}[1]{\textcolor{green}{\textbf{[Kevin: #1]}}}
+\newcommand{\rachel}[1]{\textcolor{cyan}{\textbf{[Rachel: #1]}}}
 \newcommand{\update}[1]{\textcolor{PineGreen}{#1}}
@@
 
-\begin{abstract} Massive galaxies display extended light profiles that can reach out to several hundreds of kiloparsecs.
-These extended stellar halos are key fossil records of the assembly history of massive galaxies.
-Using data that is both wide (${\sim}100$ deg$^2$) and deep ($>28.5$ \sb{} in the $i$-band), we  present a systematic study of the stellar halos of the most massive galaxies (\mstar{}$\geq 11.5$) using a statistically significant sample of more than $7000$ galaxies at $0.3 < z < 0.5$.
-Our  study is based on high-quality (0.6\asec seeing) imaging data from the Hyper Suprime-Cam (HSC) survey which reaches ${\sim}4$ magnitudes fainter than SDSS and  enables us to directly trace mass profiles to 100 kpc without resorting to stacking.
-Shallow images and/or over-simplified models like \texttt{CModel} cannot capture the extended stellar halo and result in underestimated stellar masses.
-We show that this has a signifcant impact on  the high mass end of the galaxy mass function.
-The surface mass density profiles of massive galaxies are not self-similar; at fixed "core mass" they display a diverse  range of outer profiles.
-Galaxies in our sample have optical color gradients that are independent of galaxy mass but stellar halo ellipticites that increases with galaxy mass.
+\begin{abstract} 
+    Massive galaxies display extended light profiles that can reach out to several 
+    hundreds of kilo parsecs. 
+    These stellar halos are a key fossil record of galaxy assembly history. Using data that is both wide (${\sim}100$ deg$^2$) and deep ($>28.5$ \sb{} in 
+    the $i$-band), we present a systematic study of the stellar halos of  a sample of more than $7000$ galaxies at $0.3 < z < 0.5$. 
+Our study is based on high-quality (0.6\asec\ seeing) imaging data from the Hyper 
+    Suprime-Cam (HSC) survey, which reaches ${\sim}4$ magnitudes fainter than SDSS and enables us to directly trace mass profiles to 100 kpc 
+    without resorting to stacking. Shallow images and/or over-simplified parametric models cannot capture the extended stellar halo and result in underestimated stellar masses.
+    Our extended profiles reveal a number of mass-dependent trends.
+The outer parts of our galaxies have higher ellipticity, and this ellipticity increases with stellar mass, but we find no difference in color gradients with mass.
+As in previous work, we see a clear trend towards more extended outer profiles in more massive galaxies.
+Thus, when this extended light is not properly accounted for, the stellar mass function is systematically underestimated at the highest masses.
 Our results are broadly consistent with the two phase formation scenario of massive galaxies in which outer envelopes are built up at late times from minor merging.
@@
             large radii.
+\rachel{Should replace the quote marks with arcsec symbols in the scale on these plots.}
 }
@@
 \citealt{Szomoru2012, Patel2013}).
-According to this formation mecanisms, minor mergers dominate the mass assembly of massive galaxies at late times (e.g.
+According to this formation mechanism, minor mergers dominate the mass assembly of massive galaxies at late times (e.g.
 \citealt{Hilz2012, Hilz2013, Oogi2013, Bedorf2013, Laporte2013}).
@@
     mass fraction in the accreted component should increase with total galaxy stellar mass (e.g. \citealt{Lackner2012, Cooper2013, 
-    Qu2017}). For instance, recent results from the Illustris \footnote{
+    Qu2017}). For instance, recent results from the Illustris\footnote{
     \texttt{http://www.illustris-project.org/}} simulation 
@@
     accreted stars increases significantly and reaches $f_{\mathrm{accreted}}>0.5$ at \logms{}$>11.5$ (\citealt{RodriguezGomez2016}).
+\rachel{Given that Illustris gets the SMF totally wrong at high stellar mass, is there a reason we should be quoting their results?
+Perhaps better to wait for Illustris-TNG?
+Or give some caveat here that it's not clear that the physics that shapes the most massive galaxies is a realistic implementation?}
 %% ------------------------------------------------------------------------------------ %%
@@
     growth, it is time to confront this model with additional observations,  in particular, the detailed surface mass density profiles of low redshift massive galaxies.
-Early studies based on one-dimenstional light profiles, suggested that the profiles of nearby ETGs are well described by single-\ser{} profiles (e.g.
+Early studies based on one-dimensional light profiles suggested that the profiles of nearby ETGs are well described by single-\ser{} profiles (e.g.
 \citealt{Kormendy2009}; except for the
@@
 However,  later work revealed a more complicated  situation  showing  that  ETGs  belong to two famillies, those that follow single-\ser{} law, versus those that significant deviation from the single-\ser{} profile \citep{Schombert2015}.
-Two-dimensional analyses have found that the stellar distributions of massive ETGs are often better fit by multiple-component models
+\rachel{You should say what differed in these later studies; e.g., use of deeper/better data?} Two-dimensional analyses have found that the stellar distributions of massive ETGs are often better fit by multiple-component models
     (e.g. \citealt{Huang2013a, Oh2017}).  \citet{Huang2013b} further suggest a connection between the multi-component 
@@
     large samples of massive ETGs to correctly estimate their total stellar masses
-    (e.g. \citealt{Bernardi2013, DSouza2014}) as well as to quantify the amplitude and scatter among outer enveloppes (e.g. \citealt{Capaccioli2015, Iodice2016, 
+    (e.g. \citealt{Bernardi2013, DSouza2014}) as well as to quantify the amplitude and scatter among outer envelopes (e.g. \citealt{Capaccioli2015, Iodice2016, 
     Iodice2017}).
 
-    To-date,  studies of the profiles of massive galaxies have been  either  been conducted  using large samples but with shallow imaging, for example the Sloan Digital Sky Survey (SDSS; e.g.
-\citealt{SDSSDR7, SDSSDR12}), or with deeper imaging  but smaller samples sizes (e.g cite CLASH AND FRONTIER FIELDS??).
+    Until now,  studies of the profiles of massive galaxies have been  either  been conducted  using large samples but with shallow imaging, for example the Sloan Digital Sky Survey (SDSS; e.g.
+\citealt{SDSSDR7, SDSSDR12}), or with deeper imaging  but smaller sample sizes (e.g cite CLASH AND FRONTIER FIELDS??).
 In this paper, we take advantage of new high-quality (median  seeing of
     FWHM${\sim} 0.6^{\arcsec}$ in the $i$-band) and deep ($i$-band surface brightness 
-    limit $> 28.5$\sb) images from the Hyper Suprime-Cam (HSC) Subaru Strategic 
+    limit $> 28.5$~\sb) images from the Hyper Suprime-Cam (HSC) Subaru Strategic 
     Program \citep[SSP,][]{HSCDR1} to characterize the light profiles of massive galaxies out to 100 kpc. The deep imaging depth and excellent seeing conditions of HSC images make them 
@@
     (a) reliably measure individual surface mass density (\mden{}) profiles of 
-    massive galaxy out to 100 kpc, 
+    massive galaxies out to 100 kpc, 
     (b) investigate the dependence of their outer stellar halos on total stellar 
@@
     Section \ref{sec:discussion}. 
-    Section \ref{sec:summary} presents our summary and conclusions.
+    Section \ref{sec:summary} presents our summary and conclusions. \rachel{Outline does not mention section 5.}
 
@@
     and ${\Omega}_{\rm \Lambda}=0.7$.
-    Stellar mass is noted \mstar{} and has been derived using a Chabrier Initial Mass 
+    Stellar mass is denoted \mstar{} and has been derived using a Chabrier Initial Mass 
     Function (IMF; \citealt{Chabrier2003}).
@@
             In this work, we always show the radial profile using a $R^{1/4}$ scaling 
-            on the x-axis. 
+            on the x-axis. \rachel{So should the units be kpc$^{1/4}$?}
             By using this scale, the de Vaucouleurs profile will appear as a straight 
@@
             affected by seeing.
+\rachel{`most strongly affected by seeing'?
+It's not the case that the seeing is totally irrelevant outside this region.
+The `most affect' in the sentence below does not quite make sense either.}
             The grey shaded region highlights the region most affect by seeing 
             ($r<3$ kpc).
-            On the top panel, the dash line shows the ellipticity used for the final 
+            On the top panel, the dashed line shows the ellipticity used for the final 
             isophote. 
@@
     8.2-m Subaru telescope at Mauna Kea. 
+\rachel{Need to cite the HSC survey camera paper, Miyazaki et al in prep.}
 The ambitious multi-layer HSC survey takes advantage of the large field of 
@@
     ${\sim} 100$ deg$^2$ in all 5-band to full \texttt{WIDE} depth.  
+\rachel{Need to say how this relates to the release that is available to the public and described in the HSC DR1 paper, for the sake of reproducibility.}
 The regions covered by this release overlap with a number of spectroscopic surveys 
@@
     perform large statistical studies of the surface brightness profiles of massive
-    galaxies out to their very outskirts.     
+    galaxies out to their very outskirts.  \rachel{This language seems a bit too informal for a journal article.  Perhaps `\dots represents an ideal dataset to perform statistical studies\dots'?}   
     Fig~\ref{fig:sdss_compare} illustrates the quality of HSC imaging compared to SDSS 
@@
     brightness stellar envelope is a challenging problem. 
-    The deblending method implemented by the \texttt{hscPipe} currently tends to 
+    The deblending method currently implemented in \texttt{hscPipe} tends to 
     ``over-deblend'' the outskirts of bright galaxies and leads to an 
@@
     \citealt{Bosch2017}).  
-    For these reasons, our results will be based on custom developed code to measure 
+    For these reasons, our results will be based on custom-developed code to measure 
     the luminosities and stellar masses of massive galaxies. 
@@
           \textbf{Right:} Difference between \mmax{} and \mtot{} in the same format. 
-          The average difference is small (0.02 dex) and with no clear mass--dependence. }
+          The average difference is small (0.02 dex) and with no clear mass--dependence.
+\rachel{It might be worth explicitly noting the different vertical axis scales in the caption.
+I did not notice at first, and if you do not notice then you might draw the wrong conclusion.}}
       \label{fig:mass_diff}
@@
     galaxies at $z < 0.5$ from the HSC photometric catalog. 
+\rachel{You do not seem to explicitly calculate luminosities, but rather to make a flux (not luminosity) cut.  So should we call it a `broad flux cut'?}
 Based on \citet{Leauthaud2016}, $i_{\mathrm{SDSS, cModel}} \leq 21.0$ mag can 
@@
     between the response curves of the SDSS-$i$ and HSC-$i$ filters.}. We also limit our sample to regions that have reached the required depth of 
-    the \texttt{WIDE} survey in the $i$-band.
+    the \texttt{WIDE} survey in the $i$-band. \rachel{As defined in DR1 paper?}
     %% The SQL search is saved as "sample.sql" 
@@
     (e.g.\ \citealt{Rykoff2014}; \citealt{Rozo2015b}).  
+\rachel{You require it to be a redmapper cluster member?  Or do you mean it must be part of the redmagic galaxy sample?  I do not fully understand the logic in using redmapper rather than redmagic.}
 We match the \texttt{hscPho} sample with a spec-$z$ catalog compiled by the HSC 
@@
     The spec-$z$ quality flag from different catalogs are homogenized into a single 
-    flag that indicates secure redshifts.}.  
+    flag that indicates secure redshifts. \rachel{Is there a paper or a note at the data release page that we could reference so readers can check out how this was defined?}}.  
     To ensure reasonable \mstar{}-completeness at the high-\mstar{} end we focus on
@@
     The majority of our redshifts come from the BOSS and SDSS ``legacy'' LRG samples. The GAMA survey provides an additional $14$\% of spec-$z$.
+\rachel{This is only of order 1\% of the original sample.
+Do we understand why?
+Of particular concern are cuts that affect survey homogeneity; e.g., in the area covered by GAMA vs.\ the area not covered by GAMA, might the sample look different?
+What will that do to this study?}
 We choose the redshift range of $0.3 \leq z \leq 0.5$ to make sure that 
@@
     ($r>100$ kpc).
-
-    We prepare large $i$-band postage-stamkps for each galaxy that extend to 750 kpc in 
+\rachel{Here too I think we have to be careful about how we say this.
+The PSF is not irrelevant outside of the inner part of the profile.
+It's just less important.
+Perhaps say `\dots where we are less sensitive to the PSF or the background subtraction\dots'}
+
+    We prepare large $i$-band postage-stamps for each galaxy that extend to 750 kpc in 
     radius, along with a bad pixel mask and the PSF model. 
-    These postage-stamlps include all of the light of the galaxy and are large enough to 
-    also evaluate the background level. 
-    We choose to use $i$-band images because they trace the stellar distributions of 
+    These postage-stamps include all of the light of the galaxy and are large enough to 
+    also evaluate the background level. We choose to use $i$-band images because they trace the stellar distributions of 
     massive galaxies at $0.3 \leq z \leq 0.5$ reasonably well 
-    (the observed i-band corresponds to a rest-frame $g$ or $r$ band), but also 
+    (the observed $i$-band corresponds to a rest-frame $g$ or $r$ band), but also 
     because they have better seeing and much lower background levels than the $z$ 
@@
     empirical background correction using \texttt{SExtractor}.
+\rachel{Need to describe what settings were used and, more importantly, how these were validated.
+Otherwise there is no reason to trust them over the \texttt{hscPipe} results!
+You state below that you've tested this procedure, but without enough information for readers to judge.
+Perhaps a key plot or two could go in the appendix?}
 Then, we run \texttt{Ellipse} on the background-corrected, masked cut-outs 
@@
     within these different apertures.
+\rachel{You should at least clarify whether it's a radius-dependent \m2l{} here or not, so readers know whether both luminosity and \m2l{} depend on radius, or just luminosity.}
     Motivated by the two-phase scenario, we will consider two benchmark physical 
@@
             at redshifts 0.3 and 0.5 respectively).  
+\rachel{Earlier you said you do not measure the profiles on the very smallest scales, below 3-5 kpc, so how are scales in that range handled when measuring \mstar{} within 10 kpc?}
 It is worth noting that, at the very high-\mstar{} end, accreted stars may make a significant contribution to the mass within 10 kpc 
@@
     reliable \m2l{} estimates.
+\rachel{I'm a little surprised at the statement that 1\% error is a conservative estimate of systematic uncertainties.
+It definitely seems like a conservative estimate of {\em statistical} error.
+Can you justify that all systematics are really below 1\%?}
 The typical uncertainty of \logms{} is around 0.06-0.08 dex at \logms${\sim} 11.5$.
@@
     profiles extend beyond 100 kpc without showing any signs of truncation. 
+\rachel{This bold assertion is practically begging for justification.  Is this based on past work we can reference, or a part of this paper that we can forward reference?}
 Therefore, for massive galaxies, even \mtot{} should be only considered a lower
@@
 The right panel of Fig \ref{fig:mass_diff} compares \mmax{} and \mtot{}.
-Uncertainties in the background subtraction , and the impact of neighbouring objects, means that \mmax{} is much more uncertain than \mtot{}.
+Uncertainties in the background subtraction, and the impact of neighbouring objects, means that \mmax{} is much more uncertain than \mtot{}.
 Nontheless, we do see that \mmax{} is larger than than \mtot{}.
@@
     LaBarbera2012, DSouza2015}). However, these color gradients are shallow and smooth out to a few times the effective 
-    radius (color gradients are larger radii are not yet well quantified). Because the gradients are shallow, using an average \m2l{} is unlikely to bias our results on \mstar{}
-    measurements. Color gradients will be discussed more in Section~\ref{ssec:ell_color}. 
+    radius (color gradients at larger radii are not yet well quantified). Because the gradients are shallow, using an average \m2l{} is unlikely to bias our results on \mstar{}
+    measurements.
+\rachel{I can see why this statement might be true for the total stellar mass estimates, but might the stellar mass within 10 kpc be biased?
+Can we at least say the typical sign of this bias or a rough magnitude?} Color gradients will be discussed more in Section~\ref{ssec:ell_color}.
     In summary, our results about the mass-dependence of \mden{} profiles should not be affected by the asumption of a constant  \m2l{} ratio because optical color gradients in our sample do not show a dependence on  stellar mass.
@@
     \citealt{Lawrence2007}). 
-    The deeper photometry and better photo-$z$s make the \texttt{S82-MGC} sample 
+    The deeper photometry and better photo-$z$s \rachel{Are `deeper' and `brighter' here compared to SDSS?
+It isn't deeper than HSC, is it?
+Should be clear what we are comparing here.} make the \texttt{S82-MGC} sample
     complete to \logms{}$\geq 11.2$ at $z<0.7$ which makes it sufficient to evaluate 
@@
     $10^{12.0}$\msun{} at $z{\sim} 0.5$ according to \citet{Taylor2011} (e.g.\ 
-    their Fig~~6).
+    their Fig.~6).
 
@@
 
-    Figure~\ref{fig:mass_complete} compares the number density distributions of galaxies from \texttt{S82-MGC} with those from our sample\footnote{We do not apply any statistical corrections forcompleteness and hence we do not use the term ``stellar mass function'' to avoid confusion;
-    Errors on the distributions are estimated via bootstrap resampling}. 
-    Based on Fig~\ref{fig:mass_complete}, we conclude that our sample of massive 
+    Figure~\ref{fig:mass_complete} compares the number density distributions of galaxies from \texttt{S82-MGC} with those from our sample\footnote{We do not apply any statistical corrections for completeness and hence we do not use the term ``stellar mass function'' to avoid confusion;
+    Errors on the distributions are estimated via bootstrap resampling.}. 
+    Based on Fig.~\ref{fig:mass_complete}, we conclude that our sample of massive 
     galaxies is reasonably complete down to \logmcmodel{}${\sim} 11.5$ at 
@@
     Given the average difference between \mtot{} and \mcmodel{}, we will focus on galaxies with \logmtot{}$> 11.6$ where our sample shows good completeness.
-In our discussion section, we will also show results formassive galaxies with $11.4 \le$\logmtot{}$<11.6$ but we caution that our sample is incomplete in this  lower mass bin.
+In our discussion section, we will also show results for massive galaxies with $11.4 \le$\logmtot{}$<11.6$ but we caution that our sample is incomplete in this  lower mass bin.
+\rachel{I am a bit lost as to the primary source of this incompleteness.
+Is it due to limitations inherited from CMASS, or something inherent to the data (no NIR) or procedure used to select the galaxies in this work?}
 
@@
 In this paper, we use the \redm{} catalog create a sample of massive central galaxies with minimal contamination from satellite galaxies.
+\rachel{What about those that are centrals in massive groups?
+Also, the \redm{} catalog is not volume-limited to $z=0.5$, so what are the implications for this work?
+It wasn't clear to me if that was part of the incompleteness shown in figure 4 since I was not sure if that was after the final selection or not.}
 
@@
 
-    We use \texttt{v5.10} of the \redm{} cluster  catalog
-    \footnote{See: http://risa.stanford.edu/redmapper/} 
+    We use \texttt{v5.10} of the \redm{} cluster  catalog\footnote{See: http://risa.stanford.edu/redmapper/} 
     (e.g.\ \citealt{Rykoff2014}; \citealt{Rozo2015b}). 
@@
     galaxies that live in massive halos as described above.
-    Besides the selection of central galaxies, we are also able to link each galaxy
-    with a \mhalo{} using the \redm{} catalog. 
+\rachel{Intrinsic scatter in \mhalo{} at fixed $\lambda$ is pretty big, though, so we should be careful about this assertion.}
 Such information is also very useful in studying the relationship between galaxy
@@
           stellar mass. 
+\rachel{Is this figure before or after the final cuts in section 5?  The figure is referenced in section 4, so I wasn't sure.}
 }
@@
     After matching the \texttt{hscZ} sample with the central galaxies of \redm{} 
-    clusters with $\lambda \geq 20$ and $P_{\mathrm{0.7}} \geq 0.7$, we find 164 
+    clusters with $\lambda \geq 20$ and $P_{\mathrm{0.7}} \geq 0.7$ \rachel{What is $P_{\mathrm{0.7}}$?  Does not seem to have been defined.}, we find 164 
     matched galaxies at $0.3 \leq z \leq 0.5$.
@@
     set to twice the value of the photometric redshift uncertainty of each cluster ().
+\rachel{Need to fill in empty parenthesis in previous sentence.}
 
@@
     massive halos} as the \nbcg{} sample.
-Because we have rejected satellites in \redm{} clusters, and because above our galaxy mass cut most satellite reside in halos with $log(M_{halo})>14$ (e.g.
+Because we have rejected satellites in \redm{} clusters, and because above our galaxy mass cut most satellites reside in halos with $\log{(M_{halo})}>14$ (e.g.
 \citealt{Reid2014,
-    Hoshino2015, Saito2016, vanUitert2016}),galaxies in the \nbcg{} sample should  be dominated by central galaxies.
+    Hoshino2015, Saito2016, vanUitert2016}), galaxies in the \nbcg{} sample should  be dominated by central galaxies.
+    \rachel{There is a statistical distribution of halo masses that satellites at this stellar mass live in, based on the papers you cited; can you say more quantitatively what fraction you expect to be satellites in less massive halos?
+Right now it all sounds kind of hand-wavey.}
 
@@
 
-    The following is a summary of our sample construction.
+    The following is a summary of our sample construction. \rachel{Would be valuable to remind the reader in what sections these samples were defined, and how many galaxies are in each one.}
 
@@
 For this paper, we only consider the halo mass dependence on our sample when we evaluate impact of  mass estimates on the SMF in Section \ref{ssec:smf}.
+
+\rachel{Could we show the redshift distribution of the second and third of these samples?}
 
@@
           line).  
-          The grey shaded region shows the resampling error on the HSC SMF plus a 20\%
-          uncertainties to account for other issues in our sample. 
+          The grey shaded region shows the resampling error on the HSC SMF plus an additional 20\%
+          uncertainty to account for the fact that  we do not include satellite galaxies and that we fail to extract a 1-D profile for xxx\% of our galaxies.
+These issues will be adressed in forthcoming work.
 We compare our results with previous studies:
@@
           \citet{Leauthaud2016} based on PSF-matched SDSS-UKIDSS photometry (green).
-          Please see text for more details of the comparison.
-          }
+          \rachel{Need to state explicitly what the vertical line is.
+I assume this is the stellar mass below which the sample is presumed to be too incomplete for proper derivation of the SMF.
+If that's true, should we even be showing masses below that?
+Or perhaps the entire left side can be shaded, instead of just having a line there?
+Also, are any completeness corrections applied at any value of stellar mass?}}
       \label{fig:smf}
@@
 
-    The Stellar Mass Function (SMF) and its evolution are critical to our understanding of galaxy evolution. In Section \ref{ssec:mtotal}, we demonstrate that different methods for estimating
-    ``total'' \mstar{} can lead to quite different results, and hence have a large impact 
-    on the high mass end of the galaxy stellar mass function (e.g. 
-    \citealt{Bernardi2013, DSouza2014, DSouza2015, Bernardi2017}).
-    On average, the integration of our carefully derived non-parametric \mden{} profile 
-    to 100 kpc (\mtot{}) recovers more light (hence mass) than the \texttt{cModel}
-    method. 
+    The Stellar Mass Function (SMF) and its evolution are critical to our understanding of galaxy evolution. On average, the integration of our carefully derived non-parametric \mden{} profile 
+    to 100 kpc (\mtot{}) recovers more light (hence mass) than the \texttt{cModel} method. 
     At \logmtot{} $>11.6$, the difference can sometimes be larger than 0.2 dex. 
@@
     extended stellar mass distributions (e.g. higher-\ser{} index, 
-    \citealt{Graham2003}).
-
-     Figure \ref{fig:smf} displays the impact of missing light and of different definitions of \mstar{}.
-The left panel of Fig \ref{fig:smf} shows the SMF\footnote{These are actually volume density distributions, but we refer to them as SMFs for convenience although we have not applied any completeness corrections at the low mass end} computed using \mcmodel{} and \mtot{} for both the \rbcg{} and \nbcg{} samples.
-Generally speaking, the use of \mtot{} instead of \mcmodel{} shifts the SMF
-    towards the high-mass end without significantly modifying the slope.
-    Interestingly, the impact of missing flux is more prominent for  galaxies in high mass halos (the \rbcg{} sample).
+    \citealt{Graham2003}). Hence,  the determination of the ``total luminosities'' of massive galaxies can result in  a significant impact 
+    on the high mass end of the galaxy stellar mass function (e.g. 
+    \citealt{Bernardi2013, DSouza2014, DSouza2015, Bernardi2017}).
+
+%    \footnote{To do that, one needs to 
+%    separate the differences in the measurements of luminosity and \m2l{}, and 
+%    take the uncertainties of \mstar{} measurements into account}
+
+In this paper, we have only measured light profiles for central galaxies.
+Also,  we cannot extract  a 1-D profile for xxxxxx\% of galaxies (because contamination from neighbouring galaxies is too severe).
+These two effects will lead to a ${\sim}20$\% uncertainty in  the amplitude of our SMF.
+\rachel{Mass-dependent, or really 20\% at all masses?} These are limitations that we are currently working to address and a forthcoming paper will  address them.
+Our goal in this paper is therefore not  to  attempt a detailed comparison between different SMFs
+    \citep[e.g.,][]{Bernardi2013, Bernardi2017}. Instead, our goal in this section is more simply to characterize the  impact of various \mstar{} measurements  on the high-mass end of the SMF.
+
+     Figure \ref{fig:smf} displays the impact of missing light and of different definitions of \mstar{} on the SMF.
+The left panel of Fig.~\ref{fig:smf} shows the SMF\footnote{Our SMFs turn over at the low mass end as we have not applied any completeness corrections here.
+\rachel{Why is this a footnote?
+It's a major feature of the plot, not a minor detail.}} computed using \mcmodel{} and \mtot{} for galaxies that live in low and high mass halos.
+Figure \ref{fig:smf} shows that the impact of missing flux is more severe for  galaxies in high mass halos.
 In Paper II it will be demonstrated that this occurs because  galaxies in more massive halos have larger extended  wings than those in low mass halos (Huang\etal in prep.).
-
-    As discussed in Section~\ref{ssec:mtotal}, even with much deeper images from HSC,
+Figure \ref{fig:smf} also shows that  the use of the HSC \texttt{cModel} magnitude leads to a severe underestimation of the  high mass end of the SMF.
+\rachel{It would be useful if we can say whether this is primarily because of the adoption of simple parametric profiles, or due to background subtraction failures.
+For example, if the adoption of simple parametric profiles is the primary cause of this difference, then that is a statement that might be more widely applicable than just the HSC pipeline.
+If it's really just because our background subtraction algorithm is bad, then the implications are more limited.
+Do we have the information that would allow us to make a statement about this?
+If not, we should at minimum reiterate here the possible causes of this discrepancy.}
+
+     %According to \citet{Wright2017}, the $z{\sim}0.1$ GAMA SMF based on a single-\ser{} model from \citet{Kelvin2012} suffers from similar issues.
+    %appears to have the same issue (\citealt{Wright2017}),
+    %    although the \ser{} model
+    %also can overestimate the luminosity at high-mass end\footnote{Due to 
+    %overestimated \ser{} index and/or effective radius.}.
+
+        As discussed in Section~\ref{ssec:mtotal}, even with our deep HSC images,
     it is non-trivial to clearly define and measure the ``total'' \mstar{} for 
@@
     well beyond 100 kpc.
-    We measure \mmax{} by integrating the \mden{} profiles out to the detection 
+Is our fiducial 100 kpc radius sufficient in order to capture  most of the flux associated with these galaxies, or does one need to integrate out to even larger radii?
+To answer this question,  we attempt to capture more flux by integrating our \mden{} profiles out to the detection
     limit that is defined by the background noise.
+We will refer to this mass as \mmax{}.
 Although the \mden{} profiles become more uncertain at $>100$ kpc, \mmax{} helps us quantify how much extra mass may be contained at radii greater than 100 kpc.
+The right hand side of Figure \ref{fig:smf} shows the impact of using \mmax{} instead of  \mtot{} on the SMF.
 We find that  a 100 kpc radius captures a majority of the galaxy mass and that the impact of going from \mtot{} to \mmax{} is relatively small
-
-    % TODO: Move this to Paper II
-    %In this work, we have opted to in general use \mtot{} rather than \mmax{} as the 
-    %uncertainty on \mmax{} is larger. 
-    %However, we have checked that none of our results are changed by replacing \mtot{} 
-    %via \mmax{}.
 
@@
             \texttt{S82}.
-            The stellar population model and star-formation history that are assumed are similar to those assumed in this paper, except that the \citep{Leauthaud2016} masses use the \texttt{BC03} model \alexie{Question}.
-            Based on the test results from Appendix \ref{app:sed}, we shift the \citep{Leauthaud2016} SMF by 0.08 dex to add their data to \ref{fig:smf}. 
+They adopt the same IMF, dust model, and star-formation model as we do, but use the \texttt{BC03} model.
+Based on the test results from Appendix \ref{app:sed}, we shift the \citet{Leauthaud2016} SMF by 0.08 dex to add their data to Figure~\ref{fig:smf}.
         \item The SMF derived from a SDSS-\textit{GALEX} sample of $z{\sim} 0.1$ 
@@
             assumptions as here.
-
         \item The observed SMF for $z{\sim} 0.1$ SDSS galaxies from 
@@
             They use a  \m2l{} that is adopted from the SED fitting results from the ``dusty'' 
-            model in \citet{Mendel2014} which share similar assumptions of stellar 
-            population models with this work. \alexie{Question}.   
+            model in \citet{Mendel2014}.  \alexie{CLARIFY HERE SSp model}.   
     \end{itemize}
 
-    In this work, we do not attempt to detailed comparison between different SMFs
-    \citep[e.g.,][]{Bernardi2013, Bernardi2017} \footnote{To do that, one needs to 
-    separate the differences in the measurements of luminosity and \m2l{}, and 
-    take the uncertainties of \mstar{} measurements into account}.
-    Instead, we primarily aim to visualize the importance of \mstar{} measurements 
-    to the SMF at the high-mass end.
-    We do not include satellite galaxy in our sample (could affect ${\sim}10$\% of 
-    galaxies at this very high-mass end) and can not extract 1-D \mden{} profile 
-    for a small fraction of galaxies due to severe contamination of nearby object. 
-    Therefore, we should expect at least ${\sim}20$\% uncertainties in the current 
-    volume density distributions (shown as the shaded region on Fig \ref{fig:smf}).
-    Despite the differences in these SMF, we can see that the ones using 
-    \texttt{cModel} or small aperture photometry can not appropriately account for 
-    the high-mass end due to the missing light in the outskirt. 
-    The $z{\sim}0.1$ GAMA SMF based on single-\ser{} model from \citet{Kelvin2012} 
-    appears to have the same issue (\citealt{Wright2017}), although the \ser{} model
-    also can overestimate the luminosity at high-mass end\footnote{Due to 
-    overestimated \ser{} index and/or effective radius.}.
-
-    And, interestingly, the \texttt{SerExp} models from \citet{Bernardi2017} (at 
-    $z{\sim}0.1$) suggest a SMF that is very close to the HSC \mtot{} one 
-    (at $z{\sim}0.4$) once the \m2l{} is derived under similar assumptions.
-    Apparently, the missing light problem is at least partially overcome by these 
-    two-component 2-D models. 
-    These two samples have different average redshifts, so it would be interesting
-    to exam whether \texttt{SerExp} is good model for massive galaxies out to 
-    $>100$ kpc using the same HSC galaxies.
-
-    The high-mass end of SMF is crucial for tracing the evolution of massive 
-    galaxies.  
-    And due to its sensitivity to physical process like the AGN-feedback, it is also 
-    important in calibrating simulation and semi-analytic model.
-    Here, using individual \mden{} profiles, we confirm that shallow images and/or
-    simplified models often lead to underestimated \mstar{} at high-mass end that 
-    can not be ignored.
+    As mentioned above, our current SMF is subject to an additional 20\% uncertainty that will be addressed in forthcoming work.
+Hence,  we do not attempt a detailed comparison  with respect to previous work on the galaxy SMF, reserving this  for  a future study.
+Here, we simply note that the  HSC SMF derived using \mtot{} is close to the one derived by \citet{Bernardi2017} using SDSS data at $z{\sim}0.1$ and assuming \texttt{SerExp} models.
+Our  sample and the \citet{Bernardi2017} sample have different redshifts.
+Without a more in-depth study, we cannot ascertain wheter or not  the apparent agreement between the HSC SMF and the  \citet{Bernardi2017} SMF indicates a global lack of evolution in the galaxy SMF, or  that other effects are at play (difference between \mtot{} masses and \texttt{SerExp} masses) that have cancelled redshift evolution.
+In future work, it will be interesting to perform a more consistent analysis to search for redshift evolution in the galaxy SMF and to study whether  or not massive galaxies in HSC are well described by \texttt{SerExp} models.
+
+    % TODO: Move this to Paper II
+    %In this work, we have opted to in general use \mtot{} rather than \mmax{} as the 
+    %uncertainty on \mmax{} is larger. 
+    %However, we have checked that none of our results are changed by replacing \mtot{} 
+    %via \mmax{}.
+
+%    The high-mass end of SMF is crucial for tracing the evolution of massive galaxies.  It is also  very sensitive to
+
+%    And due to its sensitivity to physical process like the AGN-feedback, it is also 
+%    important in calibrating simulation and semi-analytic model.
+
+%    Here, using individual \mden{} profiles, we confirm that shallow images and/or
+%    simplified models often lead to underestimated \mstar{} at high-mass end that 
+%    can not be ignored.
+
 %% ------------------------------------------------------------------------------------ %%
@@
               Thin grey lines show a random subset of individual profiles.
+The scatter between the thin grey lines reflects the true scatter in the profiles of massive galaxies (not measurement error).
 The shaded region highlights the region that could be affected by the PSF.
+\rachel{`most strongly' affected?}
               Two vertical lines indicate 10 kpc (thin, dotted line) and
-              100 kpc (thick, dash line). ~~~ 
+              100 kpc (thick, dashed line). ~~~ 
           \textbf{Right}: comparison between our \mden{} profiles, previous observations, 
@@
 
-    Previous discussions about the structural evolution of massive galaxies or the 
-    environmental dependence of their structures often focus on scaling relations,  
-    like the ``\mstar{}-size'' relation. 
-    In this work, we argue that, compared to these scaling relations, the \mden{} 
-    profiles that we have derived capture the full structural information of these 
-    massive galaxies.
-    By studying these \mden{} profiles directly, we can by-pass difficult questions 
-    about how to accurately define and measure the ``sizes'' and ``masses'' of these 
-    massive galaxies.
-
-    Fig~\ref{fig:avg_prof} shows the median \mden{} profiles\footnote{The median 
-    profiles along with their uncertainties are derived using bootstrap resampling 
-    method} of massive central galaxies at $0.3 < z < 0.5$ in three \mtot{} 
-    bins\footnote{The sample is clearly not complete in the lowest \mtot{} bin, 
-    but its median \mden{} profile is still useful to show the overall trend and to 
-    compare with previous work}. 
+    Previous work on the structural evolution of massive galaxies has often focused on scaling relations such as the ``\mstar{}-size'' relation.  We argue that  comparing \mden{} 
+    profiles  directly  captures more information than the \mstar{}-size relation and  has the advantage that it bypasses difficult questions 
+    about how to accurately define and measure galaxy ``sizes'' and ``masses''.
+
+    Fig.~\ref{fig:avg_prof} shows the median \mden{} profiles\footnote{The median 
+    profiles along with their uncertainties are derived using bootstrap resampling.
+\rachel{Why is this a footnote?
+It's a major feature of the plot, not a minor detail.
+Same comment applies to footnote below this.}} of massive central galaxies at $0.3 < z < 0.5$ in three \mtot{}
+    bins\footnote{Note that our sample is not complete in our lowest \mtot{} bin.}. 
     As shown in the left panel of Fig~\ref{fig:avg_prof}, we can comfortably trace
     the \mden{} profiles of these massive galaxies out to 100 kpc 
-    \textbf{individually}. 
-    These median \mden{} profiles have moderate differences in the inner region. 
-    Within inner 10 kpc, the median \mden{} profile of more massive galaxies 
-    shows slightly higher \mden{} value but similar slope. 
-    These massive galaxies ($\ge 10^{11.4} M_{\odot}$) are known to have quite 
-    uniform properties in the inner region. 
-    At these high \mstar{}, these massive elliptical galaxies are known to have 
-    quite uniform structural (e.g. \mden{} profile, isophotal shape, 
+    \textbf{individually}.  At large scales, some of our \mden{} profiles show signs of unphysical truncation and fluctuation 
+    related to inaccurate sky subtraction. In this paper, we do not use profiles beyond 100 kpc, even though the median 
+    \mden{} profiles for the two most massive bins behave reasonably out to 
+    ${\sim} 200$ kpc.
+
+       From Figure~\ref{fig:avg_prof} we can see  the galaxies in our sample have homogeneous profiles on small radial scales.
+The amplitude of \mden{} increases with galaxy mass on 10 kpc scales but the slope of  \mden{} remains similar.
+From previous work on this topic, we already know that the inner regions of massive elliptical galaxies display relatively uniform structural (e.g.
+\mden{} profile, isophotal shape,
     \citealt{Lauer07, Kormendy2009, Schombert2015} and kinematic (e.g. 
     \citealt{Cappellari13b}) properties.
-
-    Meanwhile, in the outskirts, we can notice significant differences where more 
-    massive galaxies have gradually more flattened \mden{} profiles and show more 
-    prominent stellar halos.
-    It is also interesting to see that the distributions of \mden{} profiles show 
-    considerably large scatter at large radius. 
-    Given the \s2n{} of the HSC image at these surface brightness levels, these 
-    scatters should reflect the \textbf{intrinsic scatter of the structures of 
-    massive galaxies in their stellar halos}.
-    Overall, the structures of massive galaxies are \textbf{clearly not 
+However,  Figure~\ref{fig:avg_prof} reveals  a significant diversity in the outer envelopes of massive galaxies.
+Given the \s2n{} of HSC images at these surface brightness levels, the scatter shown in Figure~\ref{fig:avg_prof} corresponds to \textbf{intrinsic scatter in the stellar envelopes of massive galaxies.}.
+Importantly, Figure~\ref{fig:avg_prof} shows that the global mass profiles of galaxies at these masses are  \textbf{clearly not
     self-similar} out to 100 kpc.
-    Some of our \mden{} profiles show signs of unphysical truncation and fluctuation 
-    related to inaccurate sky subtraction. 
-    In this paper, we do not use profiles beyond 100 kpc, even though the median 
-    \mden{} profiles for the two most massive bins behave reasonably out to 
-    ${\sim} 200$ kpc.
-
-    The right panel of Fig~\ref{fig:avg_prof} compares our results with several 
-    previous works. 
+
+In the right-hand side of Fig.~\ref{fig:avg_prof}, we compare our 
+\mden{} profiles with results from previous  work.
 Deep \mden{} profiles of massive galaxies are rarely available.
-    Even in the nearby universe, it is still not easy to reach to the very outskirt
-    of massive galaxy due to technical difficulties (e.g. 
-    \citealt{Capaccioli2015, Iodice2016, Iodice2017, Spavone2017, Mihos2017})
-    The small volume of local universe also limits the number of available 
-    galaxies at high-mass end.
-    Most previous studies often focus more on the surface brightness profiles, 
-    and they also depend on stacking techniques or model-dependent method to 
-    study the structure of massive galaxies in their outskirts (e.g. 
-    \citealt{Tal2011, DSouza2015}), both of which suffer from several systematic 
-    issues.
-
+Even in the nearby universe, it is not trivial to map the low surface brightness  outskirts of massive galaxies (e.g.,
+    \citealt{Capaccioli2015, Iodice2016, Iodice2017, Spavone2017, Mihos2017}).
+There are also not many galaxies that are this massive in the local universe.
+For example, the central galaxy of the COMA cluster, NCG xxx has a galaxy mass of xxxx and is smaller than any of the galaxies considered in this sample.
+
+Most previous studies have often focused on surface brightness profiles instead of mass density profiles.
+Results can also depend on the stacking technique or the model  used to extract the profile (e.g., \citealt{Tal2011, DSouza2015}).
 \citet{Huang2013a} derived \mden{} profiles for a small sample of very nearby
-    ellipticals (within 100 Mpc; median \logms{} ${\sim} 11.3$ based on shallower 
-    images) from the Carnegie-Irvine Galaxy Survey (CGS, \citealt{CGS1}). 
-    Because this is a very low redshift sample, these profiles are accurate to 
-    smaller scales, $r=1$ kpc. 
-    The \citet{Huang2013a} \mden{} profiles show good agreement with ours in the 
-    region of overlap and out to 50 kpc although their \m2l{} are derived in 
-    slightly different ways.
+    ellipticals (within 100 Mpc; median \logms{} ${\sim} 11.3$) based on relatively shallow 
+    images from the Carnegie-Irvine Galaxy Survey (CGS, \citealt{CGS1}).
+This sample is a very low redshift ($z=xxx$), and so the \citet{Huang2013a} galaxies are accurate to  smaller scales (down to $r=1$ kpc) than our HSC sample.
+Our \mden{} profiles show good agreement with the \citet{Huang2013a} sample in the radial range of overlap (out to 50 kpc).
 CGS images are deeper than SDSS images in the $r$-band, but the median
-    profile from \citet{Huang2013a} still only reaches to ${\sim} 50$ kpc for $z{\sim} 0$ 
+    profiles from \citet{Huang2013a} still only reach to ${\sim} 50$ kpc for $z{\sim} 0$ (PUT THE EXACT REDSHIFTS HERE)
     massive galaxies.
@@
 
-    \citet{Patel2013} extracted a median \mden{} profile of massive ETGs at 
+    \citet{Patel2013} extracted a median \mden{} profile for massive ETGs at 
     $0.25 < z < 0.50$ using stacked \textit{HST}/ACS images. 
@@
     ${\sim} 10^{11.2} M_{\odot}$ which is lower than our lowest mass bin. 
-    However, \citet{Patel2013} use the BC03 SSP model which are roughly 0.1 dex 
+    However, \citet{Patel2013} use the BC03 SSP model which provides masses that are roughly 0.1 dex 
     lower than our FSPS masses (Appendix~\ref{app:sed}). 
     Furthermore, the \citet{Patel2013} images are shallower than ours meaning 
-    that there masses will be lower than ours because of missing light in the 
+    that their masses will be lower than ours because of missing light in the 
     outskirts. 
@@
     \citet{Patel2013} profile with the one in our lowest stellar mass bin. 
-    The superb resolution of the \textit{HST}/ACS image means that the profile in
-    \citet{Patel2013} is unaffected by the seeing even down to 1 kpc. 
-    The good agreement between our profile and the one derived from HST image 
-    shows that our profiles are robust at $r > 3$ kpc and that we can accurately 
+    The superb resolution of the \textit{HST}/ACS image means that the profiles in
+    \citet{Patel2013} can be measured down to 1 kpc. 
+    The good agreement between our profiles and the ones derived from HST imaging demonstrates that our profiles are robust at $r > 3$ kpc and that we can accurately 
     measure \minn{}.
@@
     Finally, we also compare with the predicted median \mden{} profile of central 
-    galaxies in massive halos ($13.5 < \log M_{200,c} < 14.0$) from cosmological 
+    galaxies in massive halos ($13.5 < \log M_{200,c} < 14.0$) from a cosmological 
     simulation where the \mden{} profiles of galaxies are calculated using the 
-    particle-tagging technique (e.g. \citealt{Cooper2010}). 
-    The simulated \mden{} profile is also affected by limited resolution in the 
-    center, but it is already quite similar to the median \mden{} profile for 
+    particle-tagging technique (e.g., \citealt{Cooper2010}). 
+    The simulated \mden{} profile is affected by the resolution limit of the simulation in the inner region, but  is in good agreement with our median \mden{} profile for 
     the $11.6 <$ \logmtot{} $< 11.8$ bin within 40 kpc. 
     However, outside 40 kpc, the particle tagging method seems to predict a too 
-    prominent stellar halo that has much shallower slope compared to our data.
-
-    Although the particle tagging method is not considered the best way to simulate
-    the stellar mass distributions of massive galaxies, this comparison can already 
-    demonstrate the advantages of our \mden{} profiles. 
-    Such comparisons between our HSC data and predictions from more advanced 
-    hydrodynamic simulations will help fine-tune simulations and also investigate 
-    the physical mechanisms that drive the assembly of massive galaxies and the 
+    prominent stellar halo and has much shallower outer slope compared to our data. In future work, we will compare  our HSC profiles with  predictions from more advanced 
+    hydrodynamic simulations such as XXX AND XXXXX. These data will help fine-tune simulations and to understand the physical mechanisms that drive the assembly of massive galaxies and the 
     build up of stellar halos.
@@
     Table~1 provides tabulated values for the median profiles that are 
-    displayed in Fig~\ref{fig:avg_prof}. 
+    displayed in Fig.~\ref{fig:avg_prof}. 
     These profiles are also available  
@@
       \includegraphics[width=\textwidth]{fig/redbcg_ell_color.pdf}
-      \caption{
-          Radial variations in ellipticity and optical colors for massive galaxies. 
-          The format of this figure is similar to Fig~\ref{fig:avg_prof}. 
-          \textbf{Left panel} shows the ellipticity profiles, 
-          \textbf{Upper-right panel} shows the $g-r$ color profiles, and 
-          \textbf{Lower-right panel} is for $g-i$ color profiles. 
+      \caption{\alexie{Remake the light grey lines in this figure.
+Pick a smaller number.
+Say 100.
+And make the thin grey lines a little darker.
+Right now it is really hard to get anything useful from the think grey lines.}
+          Radial profiles of the ellipticty and optical colors of massive galaxies in our sample. The general format of this figure is similar to Fig~\ref{fig:avg_prof}.  The
+          \textbf{left panel} displays ellipticity profiles, 
+          the \textbf{Upper-right panel} shows $g-r$ color profiles, and  the
+          \textbf{lower-right panel} is for $g-i$ color profiles. 
           We compare our results with those from (1) \citet{Tal2011} based on stacking 
           large samples of luminous red galaxies in SDSS at $z{\sim} 0.4$ 
-          (solid red line on left panel), 
+          (solid red line on the left panel), 
           (2) the results from a stacking analysis of nearby massive 
@@
           and NGC 4365 (\citealt{Mihos2017}), and the $g-i$ profile of NGC 1399 
-          (\citealt{Iodice2016})
+          (\citealt{Iodice2016}). \rachel{State explicitly that these are rest-frame colors.}
           }
@@
 	%can be gathered from the HSC images of these massive galaxies.
-    So far, we have focused only on the 1-D \mden{} profiles from a single band.
-	Here we turn to the ellipticity and $k$-corrected optical color profiles.
-	We extract ellipticity profile using \texttt{Ellipse} by setting the shape of each 
-	isophote free. 
-	We also apply the isophotal information derived in $i$-band directly to other 
+    So far, we have focused only on 1-D \mden{} profiles. We now consider ellipticity and $k$-corrected optical color profiles.
+	We extract ellipticity profiles using \texttt{Ellipse} by leaving the shape of each isophote as a free parameter. We also apply the isophotal information derived in the $i$-band directly to other 
 	filters and extract 1-D $g-r$ and $g-i$ color profiles.
-	Both Galactic extinction correction and \texttt{iSEDFit} $k$-correction are applied 
-	to them.
-	The PSF smearing effect will make the central isophotal shape rounder than the 
-	real value, while the seeing differences between filters will bias the central 
+We apply the Galactic extinction correction and the \texttt{iSEDFit} $k$-correction  to the color profiles.
+Smearing by the PSF wil l make the central isophotal shape rounder than the
+	real value, while seeing differences between filters will bias the central 
 	color\footnote{Since the HSC $i$-band always has better seeing, the central color 
-	will become redder when the seeing effect is not corrected.}. 
-	At the same time, it is more difficult to extract reliable ellipticity and 
-	color profiles out to 100 kpc: at low surface brightness region, isophotal shape 
-	becomes unstable and easily affected by any contamination; the color profile in
-	the outskirt also becomes very sensitive to background level and noise level in 
-	either band. 
-	In this work, we will focus on the median ellipticity and color profiles between 
-	8--60 kpc where we can safely ignore the above issues.
-
-	The ellipticity of the isophote contains information about the 3-D geometry 
+	will become redder is seeing effects are not accounted for}. On large scales, it is more difficult to extract reliable ellipticity and 
+	color profiles out to 100 kpc: at low surface brightness levels, the isophotal shape 
+	becomes unstable and is easily affected by contamination.
+Color profiles are also more difficult to extract out to large radial scales because  getting the color accurately depends on the background subtraction and the noise levels in both bands.
+In this paper, we will focus on the median ellipticity and color profiles between
+	8--60 kpc where we can safely ignore the issues described above.
+
+	The ellipticity of the isophotes contains information about the 3-D geometry 
 	(e.g. \citealt{Tremblay1995, Tremblay1996, Chang2013, RodriguezPadilla2013, 
@@
 	massive galaxies and highlights the median profiles for the same three \mtot{} 
-	bins used in Fig \ref{fig:avg_prof}. 
-    We also compare our ellipticity profiles with previous ones that are based on 
-	image stacking techniques (the PSF-removed $i$-band from \citealt{Tal2011}, 
-	the concentration galaxies with $11.0<$\logms{}$<11.4$ from \citealt{DSouza2015}).
-	As expected, the ellipticity profile from image stacking method tends to be 
-	shallower than the HSC one.  
-	Uncertainties in aligning galaxies before stacking and the intrinsic isophotal 
-	twist can lead to this effect.
-
-	In general, the ellipticity of massive galaxy slowly increases with radius.
-	One can even notice this trend by directly comparing the shape of galaxy between 
-	SDSS and HSC images (e.g. Fig \ref{fig:sdss_compare}).  
-	More interestingly, the ellipticity profiles clear depend on \mtot{}: 
-	at ${\sim} 10$ kpc, median ellipticities from all three bins are low and similar 
-	($< 0.2$); but more massive galaxies become increasingly more elongated in their
-	stellar halo. 	
-	For the \logms{}$>11.8$ galaxy, its median ellipticity profile becomes steeper 
-	at $>10$ kpc, and the ellipticity steadily increases from $e\le 0.2$ to 
-	$e{\sim} 0.4$ at 50-60 kpc.
+	bins used in Fig \ref{fig:avg_prof}.  Our results are also compared with previous work based on image stacking techniques (the PSF-removed $i$-band results from \citealt{Tal2011},  and
+concentrated galaxies with $11.0<$\logms{}$<11.4$ from \citealt{DSouza2015}).
+	As expected, ellipticity profiles from image stacking methods yield results that are more shallow than when  ellipticities can be measured on a galaxy-by-galaxy basis.
+Uncertainties in how to align galaxies, and the intrinsic isophotal twist can lead to this effect.
+
+	In general, we find that the ellipticities of massive galaxies slowly increase with radius.
+This trend can even be seen directly "by eye" in HSC images (e.g.
+Fig \ref{fig:sdss_compare}).
+More interestingly, the ellipticity profiles vary with  \mtot{}:
+	at ${\sim} 10$ kpc, the median ellipticity ($< 0.2$) is similar for all three redshift bins,  but the ellipticity of the outer stellar halo increases with galaxy mass.
+Galaxies with  \logms{}$>11.8$ have median ellipticity profiles that become steeper at $>10$ kpc.
+The ellipticity of the outer profiles steadily increases from $e\le 0.2$ to $e{\sim} 0.4$ at 50-60 kpc.
+
 	This is consistent with studies of nearby massive galaxies, both from 1-D 
@@
 	Zibetti2005, Spavone2017; Huang2013a, Oh2017}.
-	Although this phenomenon was well-documented, clear evidence of mass-dependent
-	ellipticity profiles and the potentially anti-correlated slopes of \mden{} and 
-	ellipticity profiles has not been identified.
+However,  to the best of our knowledge, our HSC results are the first to show  clear evidence that:  a) the ellipticities of the stellar halo  depend strong ly on galaxy mass, and b)  the ellipticity of the stellar halo is anti-correlated with the slope of \mden{}.
+
 	If accreted stars dominate the stellar halos of massive galaxies, this 
-	mass-dependent ellipticity profile may lead us to some insights about the 
-	differences in their assembly history (e.g. average time since last merger, 
+	mass-dependent ellipticity profile may contain clues about the assembly history of massive galaxies (e.g. average time since last merger, 
 	average merger mass ratio).
 	Previous simulations often focused on reproducing the rounder average shape 
-	and slow-rotating nature of massive ETGs (e.g. \citealt{Wu2014}), so the 
+	and slow-rotating nature of massive ETGs (e.g. \citealt{Wu2014}), and the 
 	projected ellipticity profiles and their correlations with the kinematic of 
@@
 
-    As for the color profiles, it is well known that massive elliptical galaxies 
-    have shallow and negative color gradient that reflects radial variation of 
-    stellar population (e.g.\ \citealt{Carollo1993, LaBarbera2012}) and contains 
-    information about the assembly history of stellar halos (e.g. 
+    Regarding the color profiles, it is well known that massive elliptical galaxies 
+    have shallow and negative color gradients that reflect radial variations in their  
+    stellar populations (e.g.\ \citealt{Carollo1993, LaBarbera2012}) and hence contain
+    information about the assembly history of their stellar halos (e.g. 
     \citealt{Hirschmann2015}). 
     The right panels of Fig \ref{fig:ell_color} show the $k$-corrected $g-r$ and 
-    $g-i$ color profiles and the median profiles in three \mtot{} bins. 
-    As expected, all median color profiles show smooth and shallow negative 
-    gradients, but we do not find evidence for mass-dependence here. 
-    We also compare our results with the stacked color profiles from  
-    \citealt{LaBarbera2010}\footnote{Use the median color profiles of high-mass 
-    ETGs; the original profile is in unit of $R_{\mathrm{e}}$, we use a typical 
-    $R_{\mathrm{e}}=8.0$ kpc to convert it into kpc unit.} and 
+    $g-i$ color profiles for all galaxies in our sample, together with the median profiles in three \mtot{} bins.
+We find the the  median $g-r$ and $g-i$ color  decreases  at larger radii, but there does not appear to be an significant mass dependence in the  gradient of the color profiles.
+We also compare our results with the stacked color profiles from  \citealt{LaBarbera2010}\footnote{We use the median color profiles of high-mass
+    ETGs; the original profile is in units of $R_{\mathrm{e}}$, we use a typical 
+    $R_{\mathrm{e}}=8.0$ kpc to convert it into physical kpc} and 
     \citealt{DSouza2014}.
@@
     stacked SDSS ones. 
-    Considering the differences in response curves of HSC and SDSS filters, and 
-    the uncertainties of color measurements, the HSC $g-r$ color profiles are 
-    consistent with those based on SDSS images. 
-    For the $g-i$ profiles, the HSC ones still show steeper gradients. 
+    Considering differences in the response curves between HSC and SDSS filters, together with the uncertainties of color measurements, the HSC $g-r$ color profiles are  in failry good agreement with  those from SDSS.
+However, the $g-i$ profiles of HSC galaxies are steeper compared to SDSS.
 The SDSS $i$-band suffers from the so-called ``red-halo'' effect
-    (e.g. \citealt{Wu2005}, \citealt{Tal2011}). 
-    The $i$-band PSF has more prominent wing than the other bands that 
-    artificially distributes more flux to the outskirt, and lead to redder color in 
-    the low surface brightness outskirt of galaxy.
-    HSC $i$-band image do not suffer from this effect (thanks to thick CCDs), 
-    therefore can help provide more accurate color estimates.
-    For the ones from \citet{LaBarbera2010}, uncertainty of $R_{\mathrm{e}}$ 
-    measurements could also ``smooth'' the color gradients.
-    The relative steeper color profiles have been observed in very nearby massive 
-    ETGs individually.  
-    On Fig \ref{fig:ell_color}, we also compare with the $g-r$ color profiles of 
+    (e.g.
+\citealt{Wu2005}, \citealt{Tal2011}).
+This is due to  the fact that the SDSS $i$-band PSF has more prominent wing than other bands.
+Because the PSF model does not capture these wings, this artificially distributes more flux to the outskirts, and leads to apparently redder colors in
+    the low surface brightness outskirts of galaxies. Because HSC uses thick CCDs, HSC $i$-band images do not suffer from this effect and can be used to determine galaxy colors with higher accuracy.
+
+%    For the ones from \citet{LaBarbera2010}, uncertainty of $R_{\mathrm{e}}$ 
+%    measurements could also ``smooth'' the color gradients.
+
+    Fairly steep color profiles have been observed in several very nearby massive 
+    ETGs.  Fig \ref{fig:ell_color} shows the $g-r$ color profiles of 
     NGC 4472 (\citealt{Mihos2013}) and NGC 4365 (\citealt{Mihos2017})\footnote{
     Both are converted from $B-V$ colors}, and the $g-i$ profile of NGC 1399 
-    (\citealt{Iodice2016}). 
-    These individual profiles show similar color gradients with the HSC median ones.
+    (\citealt{Iodice2016}). These individual profiles  display  similar color gradients as our HSC sample.
 
@@
       \caption{
-          \textbf{Left:}
-          Relation between \mtot{} and the fraction of \mstar{} within 10 to 100 kpc, 
-          which is used here as proxy of the fraction of accreted stars. 
-          The typical uncertainties of \mtot{} and the mass fraction are shown in 
-          upper-left corner. 
-          This relation is compared with the relation between \mstar{} and the fraction
-          of accreted stars derived from the Illustris simulation at $z=0$ 
-          (Fig 4 in \citealt{RodriguezGomez2016}; grey solid and dashed lines). 
-          \textbf{Right:}
-          Comparison of the median \mden{} profiles of massive galaxies in the 
-          two lower \mtot{} bins from Fig~\ref{fig:avg_prof} with other observations 
-          and simulations, focusing on the inner region. 
-          The format is similar with the right panel of Fig~\ref{fig:avg_prof}.
-          We include: 
-          1) the median \mden{} profile of inner component from structure 
-          decomposition of massive elliptical galaxies at $z{\sim} 0$ from 
-          \citet[][Cyan, solid]{Huang2013a}; 
-          2) the median \mden{} profile of massive galaxies at $1.0 < z < 1.5$ 
-          from \textit{HST} observations in \citet[][Red, dashed]{Patel2013}; 
-          3) the median \mden{} profile of the \textit{in situ} stellar components in 
-          simulated massive halos from \citet[][Purple, dot-dashed]{Cooper2013};
-          4) the \mden{} profile of the very massive cD galaxy at $z{\sim} 1.1$ 
-          discovered by \citet[][Yellow, dashed]{Liu2013} in the Hubble 
-          Ultra-Deep Field.
-          }
+          \textbf{Left:} Ratio of the fraction of stars between 10 to 100 kpc to the total galaxy mass \mtot{}.
+We adopt this ratio as a proxy for the fraction of ex-situ stars in our sample.
+Typical observational uncertainties are shown in the upper left hand corner.
+The solid grey line shows the predicted relation  derived from the Illustris simulation at $z=0$
+          (Fig 4 in \citealt{RodriguezGomez2016}).
+Grey dashed lines correspond to the predicted 68 percentile of the distribution \alexie{CHECK}.
+\textbf{Right:} comparison between our median \mden{} profiles with the inner component of the structural decomposition of massive elliptical galaxies at $z{\sim} 0$ from \citet[][Cyan, solid]{Huang2013a}.
+\alexie{A phrase about what we learn here}.
+At high redshifts,  the profiles of massive galaxies  should be dominated by  the in-situ component.
+We compare our profiles with the median \mden{} profile of massive galaxies at $1.0 < z < 1.5$ from \textit{HST} observations \citet[][Red, dashed]{Patel2013} and the \mden{} profile of a very massive cD galaxy at $z{\sim} 1.1$ discovered by \citet[][Yellow, dashed]{Liu2013} in the Hubble Ultra-Deep Field.
+\alexie{Always finish with a phrase saying what we learn from this figure.
+Are we going to say something about redshift evolution?
+What is the goal?}.}
       \label{fig:discussion_1}
@@
 
-    With the help of deep HSC images, we trace the stellar mass distributions of 
-    $0.3 < z < 0.5$ massive galaxies out to $>100$ kpc and reveal the mass-dependent nature 
+    In this paper, we have used  data from the HSC survey that is both simultaneously deep and wide to trace the stellar mass distributions of 
+    $0.3 < z < 0.5$ massive galaxies out to $>100$ kpc and to reveal the mass-dependent nature 
     of their stellar halos.
-    Here we briefly discuss the physical origin, scientific implications, and potential 
-    caveats of these results.
+    Here we briefly discuss the scientific implications of our results .
 
@@
 %% ------------------------------------------------------------------------------------ %% 
-\subsection{The Formation of Massive Galaxies and the Assembly of Outer Halos}
+\subsection{The Formation of Massive Galaxies and the Assembly of Their Outer Halos}
     \label{ssec:twophase}
@@
     phase of evolution (the \textit{ex situ} phase) that is dominated by mass assembly via 
-    accretion and merger.
+    accretion via mergers.
     Non-dissipative mergers, especially the minor ones, mostly deposit stars in the 
-    outskirts of the centrals and do not have a large impact on the central \mden{} 
+    outskirts of centrals and do not have a large impact on the central \mden{} 
     profile (e.g. \citealt{BoylanKolchin2008, Oogi2013, Bedorf2013}).
@@
     State of the art hydrodynamic simulations of massive galaxy formation predict 
-    that the fraction of accreted stars should strongly increase with their stellar 
-    mass and the ``ex-situ'' component dominate the stellar halo (e.g.
+    that the fraction of accreted stars should strongly increase with stellar 
+    mass and that for very massive galaxies, the  ``ex-situ'' may reach up to xxxxxxx \% of the total galaxy mass (e.g.
     \citealt{Oser2010, Cooper2013, Dubois2013, LeeYi2013, Hirschmann2015,
     RodriguezGomez2016}).
-    This picture is supported by the increasingly more prominent stellar halos in 
-    more massive galaxies and the negative color gradients we see in these massive 
-    galaxies. 
-    The slightly bluer color in their outskirts are consistent with the picture that 
-    the stars there are from less massive galaxies on the ``red-squence''.
-
-    Also under this picture, the shape of the stellar halo should preserve information
-    about the merging history and even the dark matter halos. 
-    Simulations show that, slowly-rotating massive ETGs that experienced multiple 
-    minor-mergers, the shape of the stellar and dark matter halos are closely 
-    correlated (e.g. \citealt{Wu2014}). 
-    The more elongated outer halo and the trend between ellipticity profile and 
-    stellar mass may reflect that the orbital properties of infalling satellite are 
-    not random. 
-    In simulations, satellite orbit becomes more radial when it falls into more 
-    massive halos and when the satellite-central mass ratio is high (e.g. 
+
+    This picture is supported by our observations that massive galaxies display more prominent stellar halos as well as by their  negative color gradients.
+The fact that the outskirts of these galaxies are slighly bluer than  the inner regions, is  consistent with the picture that  stellar halos are built up from  less massive galaxies \alexie{justify here.
+Why bluer?}.
+
+    Also according to this picture, the shape of the stellar halo should preserve information
+    about the merging history and possibly even about the shape of the dark matter halo. 
+    Simulations show the shape of the stellar and dark matter halos are closely correlated (e.g. \citealt{Wu2014}) for slowly-rotating massive ETGs having undergone multiple 
+    minor-mergers. The more elongated outer halo and the trend between the ellipticity profile and 
+    stellar mass may reflect the orbital properties of infalling satellite. 
+    In simulations, satellite orbits become more radial for more massive halos (e.g.
 \citealt{Murante2007, Wetzel2011, Jiang2015}.
-    In principle, these results help explain the observed trend, and emphasize the 
-    importance of major merger in shaping the halo of massive galaxies. 
-    However, simulation like the one in \citet{Wu2014} predicts that more massive 
-    galaxies should be rounder in the outskirt.
-    This difference deserves more investigations using stellar kinematics and 
-    simulations.
-
-    At a larger scale, the distribution of satellites in massive halo is known to 
-    intrinsically align with the central galaxy (e.g. \citealt{Brainerd2005, 
-    Yang2006b, NiedersteOstholt2010, HuangMandelbaum2016}), and the alignment signal
-    is stronger for more massive galaxies (e.g. \citealt{Hirata2007}).
+Satellites infalling along radial orbits may  help to form elongated  stellar halos.
+Hence, in principle, these results help explain the trend that we see.
+However, on contrast, simulation from \citet{Wu2014} predict that more massive
+    galaxies should have \emph{rounder} outskirts which is the opposite trend compared to HSC. This difference warrants further investigation.
+
+    At larger scales, the distribution of satellites galaxies in massive halos is found to  be aligned with the major axis of the central galaxy \alexie{CHECK} (e.g. \citealt{Brainerd2005, 
+    Yang2006b, NiedersteOstholt2010, HuangMandelbaum2016}). This alignement signal is found to be stronger for more massive \alexie{satellites???} galaxies (e.g. \citealt{Hirata2007}).
     The fact that more massive central galaxies have steeper ellipticity profiles 
-    and become increasingly more elongated in the outskirt may help understand 
-    the physical causes of the intrinsic alignment. 
-    Moreover, the shape of the dark matter halo can now be estimated using both 
-    satellite distributions and weak lensing analysis (\citealt{ClampittJain2016}). 
+    and become increasingly more elongated in the outskirt may arise because of such alignements.
+Moreover, the shape of the dark matter halo can be estimated by analyzing satellite distributions and weak lensing profiles (\citealt{ClampittJain2016}).
     It is interesting to point out that the most recent measurement by 
@@
 
-    Recent hydrodynamic simulations of galaxy formation often separate the stars in 
-    galaxy into the \textit{in situ} and accreted components. 
-    In simulation, the \textit{in situ} component is often defined as the stars formed 
+    Recent hydrodynamic simulations of galaxy formation often separate stars in 
+    galaxies into \textit{in situ} and \textit{ex situ} components. 
+    In simulations, the \textit{in situ} component is often defined as the stars formed 
     in the halo of the ``main progenitor''.  
     The spatial distribution, kinematic, and stellar population properties of both 
-    components become important theoretical predictions to be examined. 
-    Among them, the fraction of the accreted component and its relation with stellar 
-    mass is the most fundamental one. 
-    However, on the observational side, separation of these two physical components 
-    is extremely difficult. 
-    Recently, deep surveys of nearby disk galaxies start to provide constraints of 
-    their accreted fraction using the distinctive halo components. 
-    For more massive ETGs, efforts so far all depend on multi-component model fitting
-    and image stacking analysis (e.g. \citealt{Huang2013a, dSouza2014, Spavone2017}).
-    In this work, we propose that \mstar{} within different physical apertures could 
-    be explored as potential proxies of masses in \textit{in situ} and accreted 
-    components.  
-    Given the behaviours of the \mden{} profiles shown in Fig \ref{fig:avg_prof}, 
-    we propose to use mass within 10 kpc (\minn{}) and 100 kpc (\mtot{}) as proxies 
-    of the \textit{in situ} and total \mstar{}.
-
-    On the left panel of Fig \ref{fig:discussion_1}, we plot the relation between 
-    \mtot{} and the fraction of mass between 10 and 100 kpc (as proxy of the mass of 
-    the accreted component), and compare with the relation between \mstar{} and 
-    accreted fraction derived from the Illustris simulation 
+    components are important theoretical predictions.
+Among various predictions,  the faction of  \textit{ex situ} stars and the scaling of the  ex situ fraction with galaxy mass is perhaps the  first aspect to test.
+However, on the observational side, there is no strightforward way to actually disentangle these two components for massive galaxies.
+Disk galaxies  are more easily decomposed into multiple components and recently, deep surveys of nearby disk galaxies have started to provide constraints on their stellar halos \alexie{NEED REFERENCE HERE}.
+
+    For more massive ETGs,  results so far mainly depend on multi-component model fitting
+    and image stacking analyses (e.g. \citealt{Huang2013a, dSouza2014, Spavone2017}).
+    In this work, we propose that \mstar{} computed within different fixed physical apertures are worth exploring as  proxies of the  ex situ fraction.
+We propose to use the mass within 10 kpc (\minn{}) and 100 kpc (\mtot{}) as proxies for the \textit{in situ} componnt and for the total \mstar{}.
+
+    On the left panel of Fig \ref{fig:discussion_1} we show the relation between \mtot{} and the fraction of mass between 10 and 100 kpc (as a proxy of the mass of the accreted component).
+We compare this with the  fraction of ex-situ stars predicted by the Illustris simulation
     (\citealt{RodriguezGomez2016}).
-    It is intriguing to see that, our proxy of accreted mass not only strongly 
-    correlates with \mtot{}, the relation is surprisingly consistent with the 
-    prediction from \citet{RodriguezGomez2016}. 
-    Given the limitations of the Illustris simulation and the different definitions
-    of total stellar mass, the almost perfect consistency may well be a coincidence. 
-    However, it is encouraging to see that our arbitrary choices of aperture masses 
-    can already reproduce similar slope and scatter of this relation. 
-    Right now, there are other hydrodynamic simulations that predict significantly 
-    different mass fraction of accreted stars at fixed \mstar{} (e.g. 
+We find that  our proxy for the accreted mass component correlates strongly with  \mtot{} and that this relation is surprisingly consistent with predictions from \citet{RodriguezGomez2016}.
+Given the limitations of the Illustris simulation, and the impperfect nature of our proxy for the ex sity fraction proxy, the almost perfect agreeement seen in Figure \ref{fig:discussion_1} may well be a coincidence.
+However, it is encouraging to see that our simple proxy for the fraction of ex sity stars seems to match both the slope and the scatter of the predicted relation.
+There exist other  hydrodynamic simulations that predict significantly different ex situ fractions compared to Illustris (e.g.
     \citealt{Lackner2012, Qu2017}).
-    Therefore, it will be very useful to perform more detailed comparisons with 
-    these simulations and explore the possibilities of using certain aperture mass 
-    to trace the \textit{in situ} component.
+In future work, we will explore more detailed comparisons between our data and predictions from hydrodynamic simulations and we will  investigate to what degree simple aperture masses may be used to  trace \textit{ex situ} fractions.
 
@@
 
-    To further check whether \minn{} can reasonably represent the \textit{in situ} 
-    mass, we compare the average \mden{} profiles of HSC massive galaxies in two 
-    \mtot{} bins (Left panel of Fig \ref{fig:discussion_1}, 
-    $11.4\leq$\logmtot{}$<11.6$ and $11.6\leq$\logmtot{}$<11.8$) with:
+   How well justified is our choice of  \minn{} as a proxy of the  in-situ component?
+A full investigation is beyond the scope of this paper.
+Here we simply present a comparison  between our profiles and  a)  several estimates of the in-situ component and b) observations of high redshift massive galaxies that should be dominated by the  \textit{in situ} component.
+In particular, we compare with:
 
@@
 
-        \item The median \mden{} profiles of massive ETGs at $1.0 < z < 1.5$ in
-            \citealt{Patel2013} since they are considered as the progenitors of 
+        \item The median \mden{} profiles of massive ETGs at $1.0 < z < 1.5$ from
+            \citealt{Patel2013}. These are considered to be the progenitors of 
             ${\sim} 10^{11.5} M_{\odot}$ ETGs at $z=0$ and their inner region 
@@
 
-        \item The inner components of $z{\sim} 0$ ellipticals from 2-D 
-            decomposition (\citealt{Huang2013a}).
-            As proxy of the \textit{in situ} component, \citet{Huang2013b} showed 
-            that they are structurally similar to the compact ``red nuggets'' at 
-            high-$z$.
-
+        \item The inner component of $z{\sim} 0$ ellipticals from the 2-D 
+            decomposition of \citet{Huang2013a}. \citet{Huang2013b} showed 
+            that this inner component is structurally similar to the compact ``red nuggets'' at  high-$z$. 
         \item The \textit{in situ} components of simulated central galaxies in 
@@
     We also compare with a uniquely massive BCG at high redshift: 
-    a ${\sim} 10^{11.4} M_{\odot}$ BCG with distinctive ``cD''-like envelope at 
+    a ${\sim} 10^{11.4} M_{\odot}$ BCG with a distinctive ``cD''-like envelope at 
     $z{\sim} 1.1$ (\citealt{Liu2013}).
-    Its \mden{} profile follows the median profile of $11.6\leq$\logmtot{}$<11.8$ 
-    massive galaxies nicely inside 10-15 kpc, but becomes steeper in the outskirt.
-    It represents an interesting phase where the inner ``core'' of massive BCG is 
-    already in pace at $z{\sim} 1$ while the outer halo is still being assembled.
-
-    These comparisons certainly support the idea that \minn{} mainly consists of 
-    \textit{in situ} stars and mass at $\mathrm{R} > 15$-20 kpc is dominated by accreted 
-    component.     
-    Meanwhile, they also show that the \texttt{in situ} component 
-    could have steeper \mden{} slope and mass distribution much more extended than 
-    10 kpc\footnote{We convert these \mden{} profiles to the same 
+This high redshift galaxy has a \mden{} profile that follows the median profile of our $11.6\leq$\logmtot{}$<11.8$ sample nicely inside 10-15 kpc, but becomes steeper in the outskirt.
+This suggest that the  inner ``core'' of massive BCGs are already in pace at $z{\sim} 1$ while the outer halo is still being assembled.
+
+    These simple comparisons certainly support the idea that \minn{} mainly consists of 
+    \textit{in situ} stars whereas mass at $\mathrm{R} > 15$-20 kpc is dominated by accreted 
+    component.   Meanwhile, this comparison also shows that the \texttt{in situ} component may extend beyond 10 kpc\footnote{We convert these \mden{} profiles to the same 
     Chabrier IMF; but there are still differences in median \mstar{} and 
     details in the \m2l{} estimates}.
-    More comparisons with massive galaxies at high redshift and simulated 
-    \textit{in situ} components will help shed light on this.
-
-    In line with the prediction from Illustris, this comparison also 
-    suggests that, at very high-mass end, the accreted component can make significant 
-    contribution even within the inner 10--20 kpc. 
-    The nature of these ``accreted'' stars in the center of massive galaxies deserve 
-    more attention. 
-    It is possible that they mainly come from major merger and used to be the 
-    \texttt{in situ} component of another massive galaxy. 
-    It would be interesting see whether there is an alternative, but also physically 
-    motivated definition of \textit{in situ} component that can be more easily examined 
-    by observation.
+Further comparisons with massive galaxies at high redshift and with hydrodynamicl simulations wil help understand which radius is optimal for probing the in situ mass.
+
+%    In line with the prediction from Illustris, this comparison also 
+%    suggests that, at very high-mass end, the accreted component can make significant 
+%    contribution even within the inner 10--20 kpc. 
+%    The nature of these ``accreted'' stars in the center of massive galaxies deserve 
+%    more attention. 
+%    It is possible that they mainly come from major merger and used to be the 
+%    \texttt{in situ} component of another massive galaxy. 
+%    It would be interesting see whether there is an alternative, but also physically 
+%    motivated definition of \textit{in situ} component that can be more easily examined 
+%    by observation.
 
@@
 
-    Finally, we emphasize that in this work we do not attempt to separate the 
-    potential (and distinct) ``intra-cluster'' light component (ICL; e.g. 
-    \citealt{Carlberg1997, Lin2004, Gonzalez2005, Mihos2005}) from the massive 
-    galaxies. 
-    Instead, we adopt the view that the light of the main galaxy and the 
+    Finally, we emphasize that in this work, we do not attempt  to  disentangle the galaxy light from any ``intra-cluster'' light component (ICL; e.g. 
+    \citealt{Carlberg1997, Lin2004, Gonzalez2005, Mihos2005}). Instead, we adopt the view that the light of the main galaxy and the 
     ``intra-cluster''component share a smooth and continuous distribution.
@@
     More importantly, the majority of massive galaxies in our samples are not considered 
-    as the BCG of a cluster (\mhalo{}$\simgt 10^{14}M_{\star}$). 
+    as the BCG of a cluster (\mhalo{}$\simgt 10^{14}M_{\star}$) \alexie{CHECK}. 
     Only a small fraction of the BCGs in the \rbcg{} sample belong to very 
@@
     often found (\mhalo{}$\simgt 10^{15}M_{\star}$, e.g. \citealt{Presotto2014, 
-    Burke2015}).
-    For typical \rbcg{} cluster in our sample, the Virgo cluster is a good nearby 
-    example.  
+    Burke2015}). The virgo cluster is a good  local analog of the typical galaxy in our sample.
+
     Ultra-deep images show that the stellar halo of the BCG smoothly extends beyond 
@@
     by many individual tidal features (e.g. \citealt{Mihos2016}).
-    Therefore, it is highly unlikely that out main results are driven by the ICL component.
+    Therefore, it is highly unlikely that out main results are driven by the ICL component. \alexie{I'm not sure I agree with these statements. What is the ICL anyway?}
 
@@
             parametric models. 
-            Moreover, the level of such underestimation also depends on their \mtot{}.
-            More massive galaxies tend to have larger amount of light missing in the 
-            outskirt.  
-            The level of underestimation also shows evidence of \mhalo{}-dependence. 
-            The central galaxies of \mhalo{}$\simgt 10^{14.0} M_{\odot}$ halos suffer
-            more from this issue. 
-            This should be carefully taken into account when discussing topics such 
-            as the evolution of the galaxy SMF.
-
-        \item We show that the \mden{} profiles of massive galaxies within the inner 
-            10-20 kpc generally show similar slopes and have relative small scatter. 
-            Meanwhile, there is a large but continuous scatter in the outskirts of 
-            \mden{} profiles that suggests the stellar halos of these massive galaxies 
-            are not self-similar. 
+            Moreover, the degree to which mass is underestimated depends on \mtot{}.
+Simple model miss more light for massive galaxies because they have more extended enveloppes.
+There is also a \mhalo{}-dependence of this effect and naive luminosity estimates will  miss more light for BCGs is massive halos compared to centrals in less massive halos.
+These effects need to be carefully taken into account when discussing topics such as the evolution of the galaxy SMF.
+        \item We show that the \mden{} profiles of massive galaxies are relatively homogenous  within 10-20 kpc.
+However, there is a large but continuous scatter in outer profiles of massive galaxies.
 Galaxies with higher \mtot{} show more prominent stellar halos and have
-            shallower outer \mden{} slopes than the less massive ones. 
-            Assuming the stellar halos are dominated by accreted stars, the result is 
-            in consistent with the two-phase formation picture of massive galaxies.
-
+            shallower outer \mden{} slopes. 
+            Assuming that stellar halos are dominated by accreted stars, this result is consistent with the two-phase formation picture of massive galaxies. 
         \item We show that, on average, massive galaxies have positive ellipticity 
             gradients out to at least 60 kpc. 
-            The average ellipticity profiles also depend on \mtot{}: more massive 
+            The average ellipticity profile also depend on \mtot{}: more massive 
             galaxies tend to have steeper ellipticity gradients and become more 
@@
             show clear dependence on \mtot{} within 10-60 kpc.      
-
     \end{enumerate}
@@
     redshifts, and we will also apply 2-D photometric methods (e.g.\ \citealt{Huang2013a}) 
-    to take advantages of the multi-wavelength nature of the HSC survey 
+    to take advantage of the multi-wavelength nature of the HSC survey 
     (e.g. \citealt{Huang2016}). 

### 2017-06-29 draft/paper1_rachel.tex
Abstract, Figure 1

@@
     hundreds of kilo parsecs. 
-    These stellar halos are a key fossil record of galaxy assembly history. Using data that is both wide (${\sim}100$ deg$^2$) and deep ($>28.5$ \sb{} in 
-    the $i$-band), we present a systematic study of the stellar halos of  a sample of more than $7000$ galaxies at $0.3 < z < 0.5$. 
+    These stellar halos are a key fossil record of galaxy assembly history. 
+    Using data that is both wide (${\sim}100$ deg$^2$) and deep ($>28.5$ \sb{} in 
+    $i$-band), we present a systematic study of the stellar halos of a sample of more 
+    than $7000$ galaxies at $0.3 < z < 0.5$. 
     Our study is based on high-quality (0.6\asec\ seeing) imaging data from the Hyper 
-    Suprime-Cam (HSC) survey, which reaches ${\sim}4$ magnitudes fainter than SDSS and enables us to directly trace mass profiles to 100 kpc 
-    without resorting to stacking. Shallow images and/or over-simplified parametric models cannot capture the extended stellar halo and result in underestimated stellar masses.
+    Suprime-Cam (HSC) Subaru Strategic Program (SSP), which reaches ${\sim}4$ magnitudes 
+    fainter than SDSS and enables us to directly trace mass profiles to 100 kpc 
+    without resorting to stacking. 
+    Shallow images and/or over-simplified parametric models cannot capture the extended 
+    stellar halo and result in underestimated stellar masses.
     Our extended profiles reveal a number of mass-dependent trends. 
-The outer parts of our galaxies have higher ellipticity, and this ellipticity increases with stellar mass, but we find no difference in color gradients with mass.
-As in previous work, we see a clear trend towards more extended outer profiles in more massive galaxies.
-Thus, when this extended light is not properly accounted for, the stellar mass function is systematically underestimated at the highest masses.
-Our results are broadly consistent with the two phase formation scenario of massive galaxies in which outer envelopes are built up at late times from minor merging.
-We provide surface mass surface mass density profiles in a convenient tabulated format to facilitate comparisons with predictions from numerical simulations of galaxy formation.\end{abstract}
-
-%massive central galaxies display surface mass density profiles that are not 
-%    self-similar, with the outer-slope becoming shallower and the fraction of mass 
-%    in the outskirt increasing with total stellar mass (xxxxxxxxx).
+    The outer parts of our galaxies have higher ellipticity, and this ellipticity increases 
+    with stellar mass, but we find no difference in color gradients with mass. 
+    As in previous work, we see a clear trend towards more extended outer profiles 
+    in more massive galaxies. 
+    Thus, when this extended light is not properly accounted for, the stellar mass 
+    function is systematically underestimated at the highest masses.
+    Our results are broadly consistent with the two phase formation scenario of massive 
+    galaxies in which outer envelopes are built up at late times from minor merging. 
+    We provide surface mass surface mass density profiles in a convenient tabulated format 
+    to facilitate comparisons with predictions from numerical simulations of 
+    galaxy formation.
+\end{abstract}
 
@@
             large radii.
-\rachel{Should replace the quote marks with arcsec symbols in the scale on these plots.}
             }
@@
   % Personal 
+  The authors thank Frank van~den~Bosch for insightful discussions.
   SH thanks F.S.Liu for sharing the data from his work.
@@
   software at http://dm.lsstcorp.org.
+
+  % KITP
+  This research was supported in part by the National Science Foundation under Grant 
+  No. NSF PHY11-25915.
 

### 2017-06-29 draft/paper1_rachel.tex
Edit Introduction

@@
 \begin{abstract}
+
     Massive galaxies display extended light profiles that can reach out to several 
@@
     Our results are broadly consistent with the two phase formation scenario of massive 
-    galaxies in which outer envelopes are built up at late times from minor merging. 
+    galaxies in which outer envelopes are built up at late times from series of merging
+    events. 
     We provide surface mass surface mass density profiles in a convenient tabulated format 
@@
     galaxy formation.
+
 \end{abstract}
@@
     vanDokkum2008, Cimatti2008}).  
-These high redshift galaxies also have slightly higher central velocity dispersions and stellar mass densities (\mden{}; e.g.
-\citealt{vandeSande2011, Belli2014}), and
-    more disk-like morphologies (e.g. \citealt{vanderWel2011}) than low redshift galaxies (e.g. \citealt{Bezanson2009, vanDokkum2010}) with similar stellar 
-    mass.
+    These high redshift galaxies also have slightly higher central velocity dispersions 
+    and stellar mass densities (\mden{}; e.g. \citealt{vandeSande2011, Belli2014}), 
+    and more disk-like morphologies (e.g. \citealt{vanderWel2011}) than low redshift 
+    galaxies (e.g. \citealt{Bezanson2009, vanDokkum2010}) with similar stellar mass.
 
@@
     The second phase of their assembly is driven by non-dissipative processes such 
-    as dry mergers with other galaxies (e.g.
-\citealt{Naab2006, Khochfar2006}).
-The ``two-phase'' formation of massive galaxies is  designed to both explain the observed increase in the effective radii ($R_{\mathrm{e}}$) of massive galaxies (e.g.
-    \citealt{Newman2012, vdWel2014}) and the build-up of stellar 
-    halos  (e.g.
-\citealt{Szomoru2012, Patel2013}).
-According to this formation mechanism, minor mergers dominate the mass assembly of massive galaxies at late times (e.g.
-\citealt{Hilz2012, Hilz2013, Oogi2013, Bedorf2013, Laporte2013}).
+    as dry mergers with other galaxies (e.g. \citealt{Naab2006, Khochfar2006}). 
+    The ``two-phase'' formation of massive galaxies is designed to both explain the 
+    observed increase in the effective radii ($R_{\mathrm{e}}$) of massive galaxies 
+    (e.g. \citealt{Newman2012, vdWel2014}) and the build-up of stellar 
+    halos  (e.g. \citealt{Szomoru2012, Patel2013}). 
+    According to this formation mechanism, minor mergers dominate the mass assembly 
+    of massive galaxies at late times 
+    (e.g. \citealt{Hilz2012, Hilz2013, Oogi2013, Bedorf2013, Laporte2013}).
 
@@
     semi-analytic models (SAM; e.g. \citealt{LeeYi2013, LeeYi2017}) agree that the 
-    mass fraction in the accreted component should increase with total galaxy stellar mass (e.g. \citealt{Lackner2012, Cooper2013, 
-    Qu2017}). For instance, recent results from the Illustris\footnote{
-    \texttt{http://www.illustris-project.org/}} simulation 
-    (\citealt{Vogelsberger2014}, \citealt{Genel2014}) predicts that the fraction of  
-    accreted stars increases significantly and reaches $f_{\mathrm{accreted}}>0.5$ at \logms{}$>11.5$ (\citealt{RodriguezGomez2016}).
-\rachel{Given that Illustris gets the SMF totally wrong at high stellar mass, is there a reason we should be quoting their results?
-Perhaps better to wait for Illustris-TNG?
-Or give some caveat here that it's not clear that the physics that shapes the most massive galaxies is a realistic implementation?}
+    mass fraction in the accreted component should increase with total galaxy stellar 
+    mass (e.g. \citealt{Lackner2012, Cooper2013, Qu2017}).
+    For instance, recent results from the 
+    Illustris\footnote{\texttt{http://www.illustris-project.org/}} simulation 
+    (\citealt{Vogelsberger2014}, \citealt{Genel2014}) predict that the fraction of  
+    accreted stars increases significantly and reaches $f_{\mathrm{accreted}}>0.5$ at 
+    \logms{}$>11.5$ (\citealt{RodriguezGomez2016})\footnote{The Illustris simulation
+    does not reproduce the observed stellar mass function at high \mstar{} end.}. 
 %% ------------------------------------------------------------------------------------ %%
@@
     Given the success of this two-phase scenario in explaining trends like overall size 
-    growth, it is time to confront this model with additional observations,  in particular, the detailed surface mass density profiles of low redshift massive galaxies.
-Early studies based on one-dimensional light profiles suggested that the profiles of nearby ETGs are well described by single-\ser{} profiles (e.g.
-\citealt{Kormendy2009}; except for the
-    most central region) and that the \ser{} index increases with total luminosity 
-    (e.g.
-\citealt{Graham2013}).
-However,  later work revealed a more complicated  situation  showing  that  ETGs  belong to two famillies, those that follow single-\ser{} law, versus those that significant deviation from the single-\ser{} profile \citep{Schombert2015}.
-\rachel{You should say what differed in these later studies; e.g., use of deeper/better data?} Two-dimensional analyses have found that the stellar distributions of massive ETGs are often better fit by multiple-component models
-    (e.g. \citealt{Huang2013a, Oh2017}).  \citet{Huang2013b} further suggest a connection between the multi-component 
+    growth, it is time to confront this model with additional observations, 
+    in particular, the detailed surface mass density profiles of low redshift massive 
+    galaxies. 
+    Early studies based on one-dimensional light profiles suggested that the surface 
+    mass density profiles of nearby ETGs are well described by single-\ser{} profiles 
+    (e.g. \citealt{Kormendy2009}; except for the most central region) and that the 
+    \ser{} index increases with total luminosity 
+    (e.g. \citealt{Graham2013}). 
+    However, recently, detailed empirical comparison of surface brightness profiles 
+    revealed a more complicated situation showing that ETGs belong to two famillies, 
+    those that follow single-\ser{} law, versus those that significantly deviate from 
+    the single-\ser{} profile \citep{Schombert2015}.  
+    Two-dimensional analyses have also found that the stellar distributions of massive 
+    ETGs are often better fit by multiple-component models 
+    (e.g. \citealt{Huang2013a, Oh2017}).  
+    \citet{Huang2013b} further suggest a connection between the multi-component 
     nature of massive galaxies and their two-phase assembly history. 
@@
     large samples of massive ETGs to correctly estimate their total stellar masses
-    (e.g. \citealt{Bernardi2013, DSouza2014}) as well as to quantify the amplitude and scatter among outer envelopes (e.g. \citealt{Capaccioli2015, Iodice2016, 
+    (e.g. \citealt{Bernardi2013, DSouza2014}) as well as to quantify the amplitude and 
+    scatter among outer envelopes (e.g. \citealt{Capaccioli2015, Iodice2016, 
     Iodice2017}).
 
-    Until now,  studies of the profiles of massive galaxies have been  either  been conducted  using large samples but with shallow imaging, for example the Sloan Digital Sky Survey (SDSS; e.g.
-\citealt{SDSSDR7, SDSSDR12}), or with deeper imaging  but smaller sample sizes (e.g cite CLASH AND FRONTIER FIELDS??).
+    Until now, studies of the surface brightness or mass density profiles of massive 
+    galaxies have been either conducted using large samples but with shallow imaging, 
+    for example the Sloan Digital Sky Survey (SDSS; e.g. \citealt{SDSSDR7, SDSSDR12}), 
+    or with deeper imaging but much smaller sample sizes (e.g \citealt{Gonzalez2005, 
+    Capaccioli2015}). 
     In this paper, we take advantage of new high-quality (median seeing of
-    FWHM${\sim} 0.6^{\arcsec}$ in the $i$-band) and deep ($i$-band surface brightness 
+    FWHM${\sim} 0.6^{\arcsec}$ in $i$-band) and deep ($i$-band surface brightness 
     limit $> 28.5$~\sb) images from the Hyper Suprime-Cam (HSC) Subaru Strategic 
-    Program \citep[SSP,][]{HSCDR1} to characterize the light profiles of massive galaxies out to 100 kpc. The deep imaging depth and excellent seeing conditions of HSC images make them 
+    Program \citep[SSP,][]{HSCDR1} to characterize the light profiles of massive 
+    galaxies out to 100 kpc. 
+    The deep imaging depth and excellent seeing conditions of HSC images make them 
     perfect for mapping the \mstar{} distributions of massive galaxies out to very 
-    large radii. We select a large sample (${\sim} 7000$) of massive central galaxies at $0.3 < z < 0.5$ using ${\sim} 100$ deg$^2$ of data from the HSC wide layer.
+    large radii. 
+    We select a large sample (${\sim} 7000$) of massive central galaxies 
+    at $0.3 < z < 0.5$ using ${\sim} 100$ deg$^2$ of data from the HSC wide layer.
 
@@
     mass, and 
-    (c) examine the implications in terms of  evaluating the high mass end of the galaxy stellar mass function (SMF).
-In a second paper in this series, we will investigate the environmental (dark matter halo mass) dependence of the sizes of massive ETGs (Huang\etal in prep.).
+    (c) examine the implications in terms of evaluating the high mass end of the 
+    galaxy stellar mass function (SMF). 
+    In a second paper in this series, we will investigate the environmental 
+    (dark matter halo mass) dependence of the sizes of massive ETGs 
+    (Huang\etal in prep.).
 
     This paper is organized as follows. 
-    Section \ref{sec:data} presents our data and sample selection. 
+    Section \ref{sec:data} presents our data and initial sample selection. 
     Section \ref{sec:ellipse} describes our procedure for extracting 1-D surface 
@@
     Section \ref{sec:mstar} describes how we estimate stellar mass.
+    Section \ref{sec:final} summaries the final sample selection procedure. 
     Our main results are presented in Section \ref{sec:result} and discussed in 
     Section \ref{sec:discussion}. 
-    Section \ref{sec:summary} presents our summary and conclusions. \rachel{Outline does not mention section 5.}
+    Section \ref{sec:summary} presents our summary and conclusions.
 

### 2017-06-29 draft/paper1_rachel.tex
Edit sample selection 1

@@
     galaxies. 
-    Early studies based on one-dimensional light profiles suggested that the surface 
+    Early studies based on one-dimensional light profiles found that the surface 
     mass density profiles of nearby ETGs are well described by single-\ser{} profiles 
@@
             at the central surface brightness of the galaxy to highlight the region 
-            affected by seeing.
-\rachel{`most strongly affected by seeing'?
-It's not the case that the seeing is totally irrelevant outside this region.
-The `most affect' in the sentence below does not quite make sense either.}
-            The grey shaded region highlights the region most affect by seeing 
-            ($r<3$ kpc).
+            most strongly affected by seeing.
+            The grey shaded region highlights the region ($r<6$ kpc) that is equivalent 
+            to twice the size of the half-width of a 1\asec{} seeing at $z\sim 0.5$.
+            It is a very conservative estimate of the region that we can not reliable 
+            extract 1-D profile due to the smearing effect of seeing.
             On the top panel, the dashed line shows the ellipticity used for the final 
@@
     The Subaru Strategic Program (SSP, \citealt{HSC_SSP, HSC_DR1}) makes use of the 
-    new prime-focus camera, the Hyper Suprime-Cam (HSC;~\citealt{Miyazaki2012}), on the 
+    new prime-focus camera, the Hyper Suprime-Cam (HSC;~\citealt{Miyazaki2012}, 
+    Miyazaki in~prep.), on the 
     8.2-m Subaru telescope at Mauna Kea. 
-\rachel{Need to cite the HSC survey camera paper, Miyazaki et al in prep.}
     The ambitious multi-layer HSC survey takes advantage of the large field of 
@@
     This work is based on the internal data release \texttt{S15B}, which covers 
-    ${\sim} 100$ deg$^2$ in all 5-band to full \texttt{WIDE} depth.  
-\rachel{Need to say how this relates to the release that is available to the public and described in the HSC DR1 paper, for the sake of reproducibility.}
+    ${\sim} 110$ deg$^2$ in all 5-band to full \texttt{WIDE} depth.  
     The regions covered by this release overlap with a number of spectroscopic surveys 
@@
     GAMA: \citealt{Driver2011}, \citealt{Liske2015}).
-
-    The HSC \texttt{WIDE} survey is about $3.0$-$4.0$ magnitudes deeper in terms of the $i$-band surface brightness limit than SDSS.
+    \texttt{S15B} release has similar sky coverage with the Public Data Release 1
+    (Please see Table 3 in \citealt{HSC_DR1} for detailed comparison).
+
+    The HSC \texttt{WIDE} survey is about $3.0$-$4.0$ magnitudes deeper in terms of 
+    the $i$-band surface brightness limit than SDSS. 
     Combined with the excellent imaging resolution (the median $i$-band seeing is 
-    0.6\asec) and the wide area, the HSC survey represents a tremendous dataset to 
-    perform large statistical studies of the surface brightness profiles of massive
-    galaxies out to their very outskirts.  \rachel{This language seems a bit too informal for a journal article.  Perhaps `\dots represents an ideal dataset to perform statistical studies\dots'?}   
+    0.6\asec) and the wide area, the HSC survey represents an ideal dataset to perform 
+    statistical studies of the surface brightness profiles of massive galaxies out to 
+    their very outskirts.  
     Fig~\ref{fig:sdss_compare} illustrates the quality of HSC imaging compared to SDSS 
@@
 
-    We begin by using a broad luminosity cut to select an initial sample of massive 
+    We begin by using a broad flux cut to select an initial sample of massive 
     galaxies at $z < 0.5$ from the HSC photometric catalog. 
-\rachel{You do not seem to explicitly calculate luminosities, but rather to make a flux (not luminosity) cut.  So should we call it a `broad flux cut'?}
     Based on \citet{Leauthaud2016}, $i_{\mathrm{SDSS, cModel}} \leq 21.0$ mag can 
@@
     with $i_{\mathrm{HSC, cModel}} \leq 21.5$\footnote{We neglect small differences
-    between the response curves of the SDSS-$i$ and HSC-$i$ filters.}. We also limit our sample to regions that have reached the required depth of 
-    the \texttt{WIDE} survey in the $i$-band. \rachel{As defined in DR1 paper?}
+    between the response curves of the SDSS-$i$ and HSC-$i$ filters.}. 
+    We also limit our sample to regions that have reached the required depth of 
+    the \texttt{WIDE} survey in $i$-band as defined in \citet{HSC_DR1}.
     %% The SQL search is saved as "sample.sql" 

### 2017-06-29 draft/paper1_rachel.tex
Edit sample selection 2

@@
 
-    $M_{\mathrm{halo}}$ denotes halo mass in general whereas $M_{\rm 200b}$ is 
-    explicitly defined as $M_{\rm 200b}\equiv M(<r_{\rm 200b})=200\bar{\rho} 
+    Halo mass is defined as $M_{\rm 200b}$ as 
+    $M_{\rm 200b}\equiv M(<r_{\rm 200b})=200\bar{\rho} 
     \frac{4}{3}\pi r_{\rm 200b}^3$ where $r_{\rm 200b}$
@@
     (e.g.\ \citealt{Rykoff2014}; \citealt{Rozo2015b}).
-\rachel{You require it to be a redmapper cluster member?  Or do you mean it must be part of the redmagic galaxy sample?  I do not fully understand the logic in using redmapper rather than redmagic.}
+
     We match the \texttt{hscPho} sample with a spec-$z$ catalog compiled by the HSC 
-    team\footnote{It is created by matching HSC objects with all publicly available 
-    spectroscopic redshifts (e.g.\ SDSS/BOSS; GAMA). 
+    team.
+    It is created by matching HSC objects with a series of publicly available 
+    spectroscopic redshifts (e.g.\ SDSS DR12 \citealt{SDSSDR12}; 
+    GAMA DR2 \citealt{Liske2015}). 
     The spec-$z$ quality flag from different catalogs are homogenized into a single 
-    flag that indicates secure redshifts. \rachel{Is there a paper or a note at the data release page that we could reference so readers can check out how this was defined?}}.  
+    flag that indicates secure redshifts.
+    Please see Section 4.4.2 of \citet{HSC_DR1} for details of this catalog.  
     To ensure reasonable \mstar{}-completeness at the high-\mstar{} end we focus on
@@
     Objects without a spectroscopic redshift are matched with central 
-    galaxies from the \redm{} SDSS DR8 (\citealt{SDSSDR8}) catalog using a $2.0^{\arcsec}$ matching radius.
-Matched objects with a red-sequence photo-$z$ ($0.3 \leq z_{\lambda} < 0.5$) are included in our sample.
+    galaxies from the \redm{} SDSS DR8 (\citealt{Rykoff2014}) catalog using a 
+    $2.0^{\arcsec}$ matching radius. 
+    Matched objects with a red-sequence photo-$z$ ($0.3 \leq z_{\lambda} < 0.5$) are 
+    included in our sample. 
     The accuracy of the red-sequence photo-$z$ is sufficient (median 
@@
     %% Saved as "dr1_wide_galaxy_icmodel_21.5.fits"
-    The majority of our redshifts come from the BOSS and SDSS ``legacy'' LRG samples. The GAMA survey provides an additional $14$\% of spec-$z$.
-\rachel{This is only of order 1\% of the original sample.
-Do we understand why?
-Of particular concern are cuts that affect survey homogeneity; e.g., in the area covered by GAMA vs.\ the area not covered by GAMA, might the sample look different?
-What will that do to this study?}
+    The majority of our redshifts comes from the BOSS and SDSS ``legacy'' LRG samples. 
+    The GAMA survey provides an additional $14$\% of spec-$z$.
+    Although the GAMA survey only covers parts of the \texttt{S15B} data release, hence affects 
+    the homogeneity of our sample, it will not affect the results of this work.
+    We will discuss this more in \S \ref{sec:final}.
+
     We choose the redshift range of $0.3 \leq z \leq 0.5$ to make sure that 
@@
     Also at higher redshift, the completeness of the spec-$z$ sample starts to decline. 
-And finally, the over-subtraction of the background level becomes a more serious issue at lower redshifts.
-We will now describe our one-dimensional photometric analysis  (\S \ref{sec:ellipse}) and our stellar mass estimates (\S \ref{sec:mstar}).
+    And finally, the over-subtraction of the background level becomes a more serious 
+    issue at lower redshifts.  
+    We will now describe our one-dimensional photometric analysis (\S \ref{sec:ellipse}) 
+    and our stellar mass estimates (\S \ref{sec:mstar}). 
     We will then define the final sample in \S \ref{sec:final}.
@@
     degeneracies among different parameters. 
-    Background subtraction uncertainties can also affect the 2-D model fitting method, especially for the massive ETGs that make up our sample.
+    Background subtraction uncertainties can also affect the 2-D model fitting method, 
+    especially for the massive ETGs that make up our sample.
 
@@
     This 1-D method is less affected by the issues mentioned above. 
-    Also, we will only study galaxies in the radial range where we are not 
-    sensitive to either the PSF ($r<3-5$ kpc) or the background subtraction 
+    Also, we will only study galaxies in the radial range where we are less 
+    sensitive to either the PSF ($r<5-6$ kpc) or the background subtraction 
     ($r>100$ kpc).
-\rachel{Here too I think we have to be careful about how we say this.
-The PSF is not irrelevant outside of the inner part of the profile.
-It's just less important.
-Perhaps say `\dots where we are less sensitive to the PSF or the background subtraction\dots'}
+    The region 
+    It is worth noting that the PSF
 

### 2017-06-29 draft/paper1_rachel.tex
Edit sample selection 3

@@
       	  galaxies (grey dots).
-      	  The running-median of the mass difference is shown by large red hexagons. On average, \mcmodel{} underestimates the total stellar mass of massive 
+      	  The running-median of the mass difference is shown by large red hexagons. 
+      	  On average, \mcmodel{} underestimates the total stellar mass of massive 
           galaxies by 0.1 dex while in some cases, the difference can exceed 0.2 dex.
@@
           The average difference is small (0.02 dex) and with no clear mass--dependence. 
-\rachel{It might be worth explicitly noting the different vertical axis scales in the caption.
-I did not notice at first, and if you do not notice then you might draw the wrong conclusion.}}
+          \textbf{Please note that the scales of the vertical axes are different 
+            for these two figures.}
+          }
       \label{fig:mass_diff}
@@
     The GAMA survey provides an additional $14$\% of spec-$z$.
-    Although the GAMA survey only covers parts of the \texttt{S15B} data release, hence affects 
-    the homogeneity of our sample, it will not affect the results of this work.
+    Although the GAMA survey only covers parts of the \texttt{S15B} data release, 
+    hence affects the homogeneity of our sample, it will not affect the results of 
+    this work.
     We will discuss this more in \S \ref{sec:final}.
@@
     models (e.g \citealt{Huang2013a, Huang2013b, Oh2017}), but they are still 
-    sensitive to the choice of a particular model (e.g. de~Vaucouleurs or \ser{} profile), 
-    the number of components, initial guesses of parameters, and internal 
+    sensitive to the choice of a particular model (e.g. de~Vaucouleurs or \ser{} 
+    profile), the number of components, initial guesses of parameters, and internal 
     degeneracies among different parameters. 
@@
     Also, we will only study galaxies in the radial range where we are less 
-    sensitive to either the PSF ($r<5-6$ kpc) or the background subtraction 
-    ($r>100$ kpc).
-    The region 
-    It is worth noting that the PSF
-
-    We prepare large $i$-band postage-stamps for each galaxy that extend to 750 kpc in 
-    radius, along with a bad pixel mask and the PSF model. 
-    These postage-stamps include all of the light of the galaxy and are large enough to 
-    also evaluate the background level. We choose to use $i$-band images because they trace the stellar distributions of 
-    massive galaxies at $0.3 \leq z \leq 0.5$ reasonably well 
+    sensitive to either the PSF or the background subtraction.
+    We ignore the inner 6.11 kpc, which is twice the size of 1\asec{} seeing at 
+    $z=0.5$.
+    Using this conservative choice, we can safely ignore the smearing effect of 
+    seeing outside this radius.
+    As we will show later, we confirm this by comparing our HSC profiles with 
+    observations with higher spatial resolution. 
+    As for the impact from background subtraction, we will focus on the profiles 
+    within 100 kpc.
+
+    We prepare large $i$-band postage-stamps for each galaxy that extend to 750 kpc 
+    in radius, along with a bad pixel mask and the PSF model. 
+    These postage-stamps include all of the light of the galaxy and are large enough 
+    to also evaluate the background level. We choose to use $i$-band images because 
+    they trace the stellar mass distributions of massive galaxies at 
+    $0.3 \leq z \leq 0.5$ reasonably well 
     (the observed $i$-band corresponds to a rest-frame $g$ or $r$ band), but also 

### 2017-06-29 draft/paper1_rachel.tex
Edit 1-D profile selection 1

@@
     empirical background correction using \texttt{SExtractor}.
-\rachel{Need to describe what settings were used and, more importantly, how these were validated.
-Otherwise there is no reason to trust them over the \texttt{hscPipe} results!
-You state below that you've tested this procedure, but without enough information for readers to judge.
-Perhaps a key plot or two could go in the appendix?}
+    These procedures are described in details in Appendix~\ref{app:ellipse}. 
+    We should point out that we are not using the photometric results from our 
+    customized process, but simply rely on them for improved local background model
+    and appropriate object mask.
+
     Then, we run \texttt{Ellipse} on the background-corrected, masked cut-outs 

### 2017-06-29 draft/paper1_rachel.tex
Edit 1-D profile selection 2

@@
             In this work, we always show the radial profile using a $R^{1/4}$ scaling 
-            on the x-axis. \rachel{So should the units be kpc$^{1/4}$?}
+            on the x-axis.
             By using this scale, the de Vaucouleurs profile will appear as a straight 
@@
     We choose to limit our study to surface brightness levels up to ${\sim} 28.5$ \sb. 
-    This is a conservative choice but already enables us to measure light profiles 
+    This is a conservative choice but already åenables us to measure light profiles 
     out to $100$ kpc on a galaxy-by-galaxy basis (no stacking). 
@@
     %\nbcg{} sample. 
-    It is worth noting that this excludes most massive galaxies undergoing major mergers.
+    We visually examine the 3-color images of randomly selected galaxies with failed 
+    1-D profile.  
+    Most of them are relative small galaxies that are severly contaminated by nearby 
+    objects, and will not affect the results of this work.  
+    Meanwhile, tt is worth noting that this does exclude most major merging systems 
+    among massive galaxies.
 
@@
     of ``total'' magnitude (and stellar mass) becomes nuanced.
-    With the help of the \m2l{} estimated in the next section (\S \ref{sec:mstar}), 
-    we integrate the profile to a range of radii, and estimate the stellar mass 
-    within these different apertures.
-\rachel{You should at least clarify whether it's a radius-dependent \m2l{} here or not, so readers know whether both luminosity and \m2l{} depend on radius, or just luminosity.}
+    With the help of the average \m2l{} estimated in the next section 
+    (\S \ref{sec:mstar}), we integrate the profile to a range of radii, and estimate 
+    the stellar mass within these different apertures.  
     Motivated by the two-phase scenario, we will consider two benchmark physical 
@@
             (hereafter noted \minn{}). 
-            According to the two-phase scenario, the \textit{in situ} star-formation phase quickly builds up the inner, dense core of massive ETGs.  
+            According to the two-phase scenario, the \textit{in situ} star-formation 
+            phase quickly builds up the inner, dense core of massive ETGs.  
             Based on recent observation (e.g.~\citealt{vanDokkum2010}) and 
@@
             at redshifts 0.3 and 0.5 respectively).  
-\rachel{Earlier you said you do not measure the profiles on the very smallest scales, below 3-5 kpc, so how are scales in that range handled when measuring \mstar{} within 10 kpc?}
-It is worth noting that, at the very high-\mstar{} end, accreted stars may make a significant contribution to the mass within 10 kpc 
-            (e.g. \citealt{RodriguezGomez2016}). We will further discuss the justification of this assumption in 
+            It is worth noting that, at the very high-\mstar{} end, accreted stars 
+            may make a significant contribution to the mass within 10 kpc 
+            (e.g. \citealt{RodriguezGomez2016}). 
+            We will further discuss the justification of this assumption in 
             \ref{ssec:twophase}.
@@
             $\times R_{\mathrm{e}}$. 
-            We show in section \ref{ssec:mtotal} that most of the \mstar{} for 
+            We show in Section \ref{ssec:mtotal} that most of the \mstar{} for 
             these ETGs can be captured by a 100 kpc radius and that \mtot{} is 

### 2017-06-29 draft/paper1_rachel.tex
Edit stellar mass measurement 1

@@
             Left: example of the 1-D surface brightness and ellipticity profile 
-            for a massive galaxy at $z=0.23$ in the $i$-band using \texttt{Ellipse}. 
+            of a massive galaxy at $z=0.23$ in the $i$-band extracted using 
+            \texttt{Ellipse}. 
             In this work, we always show the radial profile using a $R^{1/4}$ scaling 
@@
             extract 1-D profile due to the smearing effect of seeing.
-            On the top panel, the dashed line shows the ellipticity used for the final 
-            isophote. 
+            On the top panel, the dashed line shows the mean ellipticity used for the 
+            final isophote. 
             Right: the three color image of this galaxy with isophotes 
@@
     ``over-deblend'' the outskirts of bright galaxies and leads to an 
-    under-estimation of the the total flux of massive ETGs (this is discussed further in 
+    under-estimation of the total flux of massive ETGs (this is discussed further in 
     \citealt{Bosch2017}).  
@@
     The accuracy of the red-sequence photo-$z$ is sufficient (median 
-    $|z_{\lambda} - z_{\mathrm{Spec}}| {\sim} 0.01$ for the ones with spec-$z$) 
-    for the goal of this work.
+    $|z_{\lambda} - z_{\mathrm{Spec}}| {\sim} 0.01$) for our goal.
     The \redm{} catalog provides an additional 133 unique redshifts for massive 
@@
     The majority of our redshifts comes from the BOSS and SDSS ``legacy'' LRG samples. 
-    The GAMA survey provides an additional $14$\% of spec-$z$.
+    The GAMA survey provides an additional $14$\% of all spectroscopic redshifts.
     Although the GAMA survey only covers parts of the \texttt{S15B} data release, 
@@
 
-    We choose the redshift range of $0.3 \leq z \leq 0.5$ to make sure that 
+    We choose the redshift range $0.3 \leq z \leq 0.5$ to make sure that: 
     (1) The inner region of massive galaxies can be resolved, and \mstar{} within 
     10 kpc can be reliably measured; 
-    (2) The background noise and cosmological dimming are not major issues and the 
+    (2) The background noise and cosmological dimming are not major issues so that the 
     \mden{} profile can be measured out to $>100$ kpc; 
@@
     issue at lower redshifts.
+
     We will now describe our one-dimensional photometric analysis (\S \ref{sec:ellipse}) 
@@
     in radius, along with a bad pixel mask and the PSF model. 
-    These postage-stamps include all of the light of the galaxy and are large enough 
-    to also evaluate the background level. We choose to use $i$-band images because 
-    they trace the stellar mass distributions of massive galaxies at 
+    These postage-stamps include all of the light of the galaxy and are also large 
+    enough to also evaluate the background level. We choose to use $i$-band images 
+    because they trace the stellar mass distributions of massive galaxies at 
     $0.3 \leq z \leq 0.5$ reasonably well 
@@
 
+    We should point out that both \minn{} and \mtot{} are measured within the same 
+    elliptical aperture. 
+    The 10 kpc and 100 kpc here refer to the radius along the major aixs of the 
+    elliptical isophote.
+
 %% ------------------------------------------------------------------------------------ %%
@@
     5-band HSC \cmodel{} fluxes.
-    Although \cmodel{} tends to underestimate the total flux for bright, extended 
+    Although \cmodel{} tends to underestimate the total fluxes of bright, extended 
     objects, it can still yield accurate \emph{average} colors thanks to the 

### 2017-06-30 draft/paper1_rachel.tex
Edit stellar mass measurement 2

@@
     For stellar metallicity 
-    ($[\mathrm{M}/\mathrm{H}]=\log\ \mathrm{Z}/\mathrm{Z}_{\odot}$), we assume a flat 
-    distribution between 0.004 to 0.03 (the highest value allowed by FSPS).
+    ($[\mathrm{M}/\mathrm{H}]=\log\ (\mathrm{Z}/\mathrm{Z}_{\odot})$), we assume a 
+    flat distribution between 0.004 to 0.03 (the highest value allowed by FSPS).
     We adopt the \citet{Calzetti2000} extinction law with a order two Gamma 
@@
     very sensitive to parameters related to the SFH or the internal dust extinction. 
-    To achieve reasonable sampling across these parameters, we generate 250000 models.
+    To achieve reasonable sampling across these parameters, we generate 250000 
+    models.
 
@@
     corrected for Galactic extinction. 
-    \cmodel{} only accounts for the statistical error on the flux measurement but 
-    does not account for systematic uncertainties in the model-fitting process. 
-    It therefore underestimates the flux errors of bright galaxies. 
+    Right now, \cmodel{} only accounts for the statistical error on the flux 
+    measurement and it certaintly underestimates the true flux errors of bright 
+    galaxies.  
     For this work, we supply \texttt{iSEDFit} with simplified flux errors assuming 
@@
     background noise).  
-    Although these are still conservative estimates of the systematic uncertainties 
-    involved in the model-fitting, tests using synthetic galaxies show that \cmodel{}
-    provides excellent measurements of five-band colors, which are crucial for 
-    reliable \m2l{} estimates.
-\rachel{I'm a little surprised at the statement that 1\% error is a conservative estimate of systematic uncertainties.
-It definitely seems like a conservative estimate of {\em statistical} error.
-Can you justify that all systematics are really below 1\%?}
+    These empirical \s2n{} choices still only provide lower-limits of the true 
+    systematic uncertainties from the model-fitting process. 
+    In \citealt{SynPipe}, we evaluate the accuracy of HSC \cmodel{} photometry 
+    using synthetic galaxies, and show that \cmodel{} provides excellent measurements 
+    of five-band colors, which are crucial for reliable \m2l{} estimates.
     The typical uncertainty of \logms{} is around 0.06-0.08 dex at \logms${\sim} 11.5$.

### 2017-06-30 draft/paper1_rachel.tex
Edit stellar mass measurement 3

@@
     However, recently, detailed empirical comparison of surface brightness profiles 
-    revealed a more complicated situation showing that ETGs belong to two famillies, 
+    revealed a more complicated situation showing that ETGs belong to two families, 
     those that follow single-\ser{} law, versus those that significantly deviate from 
@@
     We choose to limit our study to surface brightness levels up to ${\sim} 28.5$ \sb. 
-    This is a conservative choice but already åenables us to measure light profiles 
+    This is a conservative choice but already enables us to measure light profiles 
     out to $100$ kpc on a galaxy-by-galaxy basis (no stacking). 
@@
     1-D profile.  
-    Most of them are relative small galaxies that are severly contaminated by nearby 
+    Most of them are relative small galaxies that are severely contaminated by nearby 
     objects, and will not affect the results of this work.  
-    Meanwhile, tt is worth noting that this does exclude most major merging systems 
+    Meanwhile, it is worth noting that this does exclude most major merging systems 
     among massive galaxies.
@@
     elliptical aperture. 
-    The 10 kpc and 100 kpc here refer to the radius along the major aixs of the 
+    The 10 kpc and 100 kpc here refer to the radius along the major axis of the 
     elliptical isophote.
@@
     We adopt the \citet{Calzetti2000} extinction law with a order two Gamma 
-    distribution of $A_{V}$ between 0 to 2 magnitude. 
-    The majority of our galaxies are red and quiescent ones so the results are not 
+    distribution of $A_{V}$ between 0 to 2 magnitudes. 
+    The majority of our galaxies are red and quiescent so the results are not 
     very sensitive to parameters related to the SFH or the internal dust extinction. 
@@
     Right now, \cmodel{} only accounts for the statistical error on the flux 
-    measurement and it certaintly underestimates the true flux errors of bright 
+    measurement and it certainly underestimates the true flux errors of bright 
     galaxies.  
@@
     In Appendix~\ref{app:sed}, we briefly summarize the basic statistics of 
-    the sample, including average stellar age, metallicity, and internal dust 
-    extinction along with their relation with \mtot{}. 
+    the sample by showing the relationships between \mtot{} and stellar age, 
+    metallicity, and internal dust extinction. 
     All these properties behave reasonably for massive galaxies in this sample. 
@@
 
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
+  \begin{figure}
+      \centering 
+      \includegraphics[width=\columnwidth]{fig/redbcg_completeness}
+      \caption{
+          Evaluation of the \mstar{} completeness of the HSC massive galaxy sample.
+          We compare the volume number density function of the massive galaxies 
+          for this work (black line) with the one of a much more complete sample
+          from the S82-MGC catalog (green line).  
+          The associated uncertainties derived from bootstrap resampling are shown in 
+          shaded regions. 
+          The vertical grey line highlight the \logms{}$=11.6$ limit.  
+          Below it, the HSC massive galaxy sample becomes significantly incomplete in 
+          stellar mass. 
+          }
+      \label{fig:mass_complete}
+  \end{figure}     
 %% ------------------------------------------------------------------------------------ %%
@@
     Such differences also have important implications for estimates of the stellar 
-    mass function and for studies of the environment-dependence of galaxy structure. These topics will be discussed in Section \ref{sec:discussion}.
+    mass function and for studies of the environment-dependence of galaxy structure. 
+    These topics will be discussed in Section \ref{sec:discussion}.
 
@@
     of stars that belong to these massive galaxies, we know that their \mden{} 
-    profiles extend beyond 100 kpc without showing any signs of truncation. 
-\rachel{This bold assertion is practically begging for justification.  Is this based on past work we can reference, or a part of this paper that we can forward reference?}
+    profiles extend beyond 100 kpc without showing any signs of truncation
+    (e.g. \citealt{Gonzalez2005, Tal2011, DSouza2014}).
     Therefore, for massive galaxies, even \mtot{} should be only considered a lower
     limit on the ``total'' \mstar{}. 
-    In Fig \ref{fig:mass_diff}, we integrate the \mden{} of each galaxy to the  edge of the postage-stamp and call this mass \mmax{}.
+    In Fig \ref{fig:mass_diff}, we integrate the \mden{} of each galaxy to the edge of 
+    the postage-stamp and call this mass \mmax{}. 
     The right panel of Fig \ref{fig:mass_diff} compares \mmax{} and \mtot{}.  
-Uncertainties in the background subtraction, and the impact of neighbouring objects, means that \mmax{} is much more uncertain than \mtot{}.
-Nontheless, we do see that \mmax{} is larger than than \mtot{}.
+    Uncertainties in the background subtraction, and the impact of neighbouring objects,
+    means that \mmax{} is much more uncertain than \mtot{}. 
+    Nonetheless, we do see that \mmax{} is larger than than \mtot{}. 
     However, the mass differences are on average very small ($\sim0.02-0.03$ dex) and 
@@
 
-    Our methodology ignores any radial variations in \m2l{}. 
+    Our methodology ignores radial variations in \m2l{}. 
     It is well known that massive ETGs have negative optical color gradients 
     indicating gradients in \m2l{} (e.g.\ \citealt{Carollo1993, Davies1993, 
-    LaBarbera2012, DSouza2015}). However, these color gradients are shallow and smooth out to a few times the effective 
-    radius (color gradients at larger radii are not yet well quantified). Because the gradients are shallow, using an average \m2l{} is unlikely to bias our results on \mstar{}
-    measurements.
-\rachel{I can see why this statement might be true for the total stellar mass estimates, but might the stellar mass within 10 kpc be biased?
-Can we at least say the typical sign of this bias or a rough magnitude?} Color gradients will be discussed more in Section~\ref{ssec:ell_color}.
-    In summary, our results about the mass-dependence of \mden{} profiles should not be affected by the asumption of a constant  \m2l{} ratio because optical color gradients in our sample do not show a dependence on  stellar mass.
+    LaBarbera2012, DSouza2015}). 
+    Assuming all massive galaxies in our sample have negative color gradients, and 
+    there is a simple monotonic relation between optical color and \m2l{}, the
+    average \m2l{} we used should in principle underestimate the \mstar{} in the 
+    center while overestimate the \mstar{} in the outskirt.
+    However, these color gradients are shallow and smooth out to a few times the 
+    effective radius (e.g. \citealt{LaBarbera2010, Tal2011, DSouza2014}, 
+    color gradients at larger radii are not yet well quantified). 
+    Because the gradients are shallow, using an average \m2l{} is unlikely to bias our
+    results on \mstar{} measurements.  
+    In \citet{Huang2016}, the authors conduct multi-band decomposition for a sample 
+    of very nearby elliptical galaxies, and estimate the \m2l{} of each component 
+    separately. 
+    The sum of all components suggest a slightly higher \mstar{} ($0.05-0.10$ dex when
+    typical uncertainty of \mstar{} is 0.12-0.15 dex) and the mass differences show
+    no dependence on \mstar{}.
+
+    Color gradients will be discussed more in Section~\ref{ssec:ell_color}. 
+    In summary, our results about the mass-dependence of \mden{} profiles should not 
+    be affected by the assumption of a constant \m2l{} ratio because optical color 
+    gradients in our sample do not show a dependence on stellar mass.
 
@@
 %% ------------------------------------------------------------------------------------ %% 
-  \begin{figure}
-      \centering 
-      \includegraphics[width=\columnwidth]{fig/redbcg_completeness}
-      \caption{
-          Evaluation of the \mstar{} completeness of the HSC massive galaxy sample.
-          We compare the volume number density function of the massive galaxies 
-          for this work (black line) with the one of a much more complete sample
-          from the S82-MGC catalog (green line).  
-          The associated uncertainties derived from bootstrap resampling are shown in 
-          shaded regions. 
-          The vertical grey line highlight the \logms{}$=11.6$ limit.  
-          Below it, the HSC massive galaxy sample becomes significantly incomplete in 
-          stellar mass. 
-\rachel{Is this figure before or after the final cuts in section 5?  The figure is referenced in section 4, so I wasn't sure.}
-}
-      \label{fig:mass_complete}
-  \end{figure}     
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %% 
 %\subsection{Massive Central Galaxies in Low and High Mass Halos}
@@
     After matching the \texttt{hscZ} sample with the central galaxies of \redm{} 
-    clusters with $\lambda \geq 20$ and $P_{\mathrm{0.7}} \geq 0.7$ \rachel{What is $P_{\mathrm{0.7}}$?  Does not seem to have been defined.}, we find 164 
+    clusters with $\lambda \geq 20$ and $P_{\mathrm{Cen}} \geq 0.7$, we find 164 
     matched galaxies at $0.3 \leq z \leq 0.5$.

### 2017-06-30 draft/paper1_rachel.tex
Edit stellar mass measurement 4

@@
     \citealt{Lawrence2007}). 
-    The deeper photometry and better photo-$z$s \rachel{Are `deeper' and `brighter' here compared to SDSS?
-It isn't deeper than HSC, is it?
-Should be clear what we are comparing here.} make the \texttt{S82-MGC} sample
-    complete to \logms{}$\geq 11.2$ at $z<0.7$ which makes it sufficient to evaluate 
-    the completeness of our HSC sample.   
+    Comparing to normal SDSS images, the deeper photometry and better photo-$z$s 
+    from \texttt{S82-MGC} make this sample complete to \logms{}$\geq 11.2$ at $z<0.7$ 
+    which makes it sufficient to evaluate the completeness of our HSC sample.   
 	By comparing with the Stripe 82 Massive Galaxy Catalog
@@
     \mstar{} completeness of the combined BOSS and SDSS samples. 
-    They estimate that the BOSS spec-$z$ sample, which is the main source of redshifts for our sample, is about 80\% complete at 
+    They estimate that the BOSS spec-$z$ sample, which is the main source of redshifts 
+    for our sample, is about 80\% complete at 
     \logms{}$\geq 11.6$ at $0.3 < z < 0.5$. The GAMA survey is 80\% complete down to 
@@
     sample at $0.3 \leq z_{\mathrm{s82}} \leq 0.5$.  
-Because the \texttt{S82-MGC} uses  cmodel  magnitudes,  in this section we use  \mcmodel{} for consistency with the  \texttt{S82-MGC} catalog.
-The \texttt{S82-MGC} also uses \texttt{iSEDFit} with similar assumptions as used in this work and we find excellent agreement between HSC  \mcmodel{} and the mass derived in  the \texttt{S82-MGC} which includes NIR data from UKIDSS;
-
-    Figure~\ref{fig:mass_complete} compares the number density distributions of galaxies from \texttt{S82-MGC} with those from our sample\footnote{We do not apply any statistical corrections for completeness and hence we do not use the term ``stellar mass function'' to avoid confusion;
+    Because the \texttt{S82-MGC} uses \cmodel{} magnitudes, in this section we use  
+    \mcmodel{} for consistency with the \texttt{S82-MGC} catalog.  
+    The \texttt{S82-MGC} also uses \texttt{iSEDFit} with similar assumptions as 
+    used in this work and we find excellent agreement between HSC \mcmodel{} and 
+    the mass derived by \texttt{S82-MGC} which includes NIR data from UKIDSS;
+
+    Figure~\ref{fig:mass_complete} compares the number density distributions of 
+    galaxies from \texttt{S82-MGC} with those from our sample\footnote{We do not 
+    apply any statistical corrections for completeness and hence we do not use the 
+    term ``stellar mass function'' to avoid confusion;
     Errors on the distributions are estimated via bootstrap resampling.}. 
@@
     %availability of spec-$z$s from BOSS.    
-    Given the average difference between \mtot{} and \mcmodel{}, we will focus on galaxies with \logmtot{}$> 11.6$ where our sample shows good completeness.
-In our discussion section, we will also show results for massive galaxies with $11.4 \le$\logmtot{}$<11.6$ but we caution that our sample is incomplete in this  lower mass bin.
-\rachel{I am a bit lost as to the primary source of this incompleteness.
-Is it due to limitations inherited from CMASS, or something inherent to the data (no NIR) or procedure used to select the galaxies in this work?}
+    Given the average difference between \mtot{} and \mcmodel{}, we will focus on 
+    galaxies with \logmtot{}$> 11.6$ where our sample shows good completeness. 
+    In our discussion section, we will also show results for massive galaxies 
+    with $11.4 \le$\logmtot{}$<11.6$ but we caution that our sample is incomplete 
+    in this lower mass bin mainly due to the intrinsic incompleteness of the 
+    SDSS/BOSS spec-$z$ (see \citealt{Leauthaud2016}).
 

### 2017-06-30 draft/paper1_rachel.tex
Edit final sample 1

@@
 
-    With the help of the \texttt{S82-MGC} (\citealt{Bundy2015}), we investigate the 
-    \mstar{} completeness of our samples. 
+    With the help of the Stripe82 Massive Galaxy Catalog (\texttt{S82-MGC},
+    \citealt{Bundy2015}
+    )\footnote{http://www.ucolick.org/$~$kbundy/massivegalaxies/s82-mgc.html}, 
+    we investigate the \mstar{} completeness of our samples. 
     The \texttt{S82-MGC} sample matches the deeper SDSS photometric data in the 
@@
     which makes it sufficient to evaluate the completeness of our HSC sample.   
-	By comparing with the Stripe 82 Massive Galaxy Catalog
-    (\texttt{S82-MGC}; \citealt{Bundy2015}), \citet{Leauthaud2016} have measured the
-    \mstar{} completeness of the combined BOSS and SDSS samples. 
+	By comparing with the \texttt{S82-MGC} sample (\citealt{Bundy2015}), 
+	\citet{Leauthaud2016} have measured the \mstar{} completeness of the combined BOSS 
+	and SDSS samples. 
     They estimate that the BOSS spec-$z$ sample, which is the main source of redshifts 
@@
     \logms{}$\geq 11.6$ at $0.3 < z < 0.5$. The GAMA survey is 80\% complete down to 
-    $10^{10.8}$\msun at $z{\sim} 0.3$, but is only 80\% complete to 
+    $10^{10.8}$\msun{} at $z{\sim} 0.3$, but is only 80\% complete to 
     $10^{12.0}$\msun{} at $z{\sim} 0.5$ according to \citet{Taylor2011} (e.g.\ 
@@
     used in this work and we find excellent agreement between HSC \mcmodel{} and 
-    the mass derived by \texttt{S82-MGC} which includes NIR data from UKIDSS;
+    the mass derived by \texttt{S82-MGC} which includes NIR data from UKIDSS.
 
@@
 
-	With  \mstar{} estimates in hand, we now use the \redm{} galaxy cluster catalog to  create a sample of massive central galaxies. The ``central'' galaxy is defined as the galaxy that lives in the 
+	With \mstar{} estimates in hand, we now use the \redm{} galaxy cluster catalog to  
+	create a sample of massive central galaxies. 
+	The ``central'' galaxy is defined as the galaxy that lives in the 
 	center of its own dark matter halo.  
@@
 	more massive halo is referred to as a ``satellite''. 
-	%The central galaxy has its unique importance in the study of galaxy evolution and 
-	%galaxy-halo coevolution.
 	To better understand the connection between the structures of massive 
-	galaxies and the assembly history of both their stars and dark matter halos, we wish to focus on central 
-	galaxies in this work.
+	galaxies and the assembly history of both their stars and dark matter halos, we 
+	wish to focus on central galaxies in this work.
 
@@
     \citealt{Yang2007}). 
-In this paper, we use the \redm{} catalog create a sample of massive central galaxies with minimal contamination from satellite galaxies.
-\rachel{What about those that are centrals in massive groups?
-Also, the \redm{} catalog is not volume-limited to $z=0.5$, so what are the implications for this work?
-It wasn't clear to me if that was part of the incompleteness shown in figure 4 since I was not sure if that was after the final selection or not.}
+    In this paper, we use the \redm{} catalog create a sample of massive central 
+    galaxies with minimal contamination from satellite galaxies.
 
@@
 
-    We use \texttt{v5.10} of the \redm{} cluster  catalog\footnote{See: http://risa.stanford.edu/redmapper/} 
+    We use \texttt{v5.10} of the \redm{} cluster  catalog
     (e.g.\ \citealt{Rykoff2014}; \citealt{Rozo2015b}). 

### 2017-06-30 draft/paper1_rachel.tex
Edit final sample 2

@@
 \def\mstar{{$M_{\star}$}}
-\def\mhalo{{$M_{\mathrm{halo}}$}}
+\def\mhalo{{$M_{\mathrm{200b}}$}}
 \def\logms{{$\log (M_{\star}/M_{\odot})$}}
-\def\logmh{{$\log (M_{\mathrm{halo}}/M_{\odot})$}}
+\def\logmh{{$\log (M_{\mathrm{200b}}/M_{\odot})$}}
 
@@
     \citealt{Bundy2015}
-    )\footnote{http://www.ucolick.org/$~$kbundy/massivegalaxies/s82-mgc.html}, 
+    )\footnote{http://www.ucolick.org/\~{}kbundy/massivegalaxies/s82-mgc.html}, 
     we investigate the \mstar{} completeness of our samples. 
@@
     These authors have developed a well-tested red-sequence cluster finder that has 
-    been run on SDSS DR8 (\citealt{SDSSDR8}) photometric data. 
+    been run on SDSS DR8 (\citealt{SDSSDR8}) images. 
     For each cluster, the catalog provides a photometric redshift ($z_{\lambda}$), a 
@@
     have $\log (M_{\mathrm{halo}}/M_{\odot}) \geq 14.0$. 
-    Therefore the central galaxies of these \redm{} clusters\footnote{We only use the 
+    Therefore the central galaxies of these \redm{} clusters\footnote{We only use 
     central galaxies with $P_{\mathrm{CEN}} \geq 0.7$} form a sample of massive central 
@@
     We use a radius equal to $R_{\mathrm{200b}}$ and the thickness of the cylinder is 
-    set to twice the value of the photometric redshift uncertainty of each cluster ().
-\rachel{Need to fill in empty parenthesis in previous sentence.}
-
-    We convert $\lambda$ of each cluster to $M_{\mathrm{halo}}$ using the calibration 
+    set to twice the value of the photometric redshift uncertainty of each cluster.
+
+    We convert $\lambda$ of each cluster to $M_{\mathrm{200b}}$ using the calibration 
     of \citet{Simet2016} and we use the mass-concentration relation from 
@@
     massive halos} as the \nbcg{} sample.
-Because we have rejected satellites in \redm{} clusters, and because above our galaxy mass cut most satellites reside in halos with $\log{(M_{halo})}>14$ (e.g.
+Because we have rejected satellites in \redm{} clusters, and because above our galaxy mass cut most satellites reside in halos with \logmh$>14.0$ (e.g.
 \citealt{Reid2014,
@@
 In this paper, we have only measured light profiles for central galaxies.
-Also,  we cannot extract  a 1-D profile for xxxxxx\% of galaxies (because contamination from neighbouring galaxies is too severe).
+Also,  we cannot extract  a 1-D profile for $\sim 11$\% of galaxies (because contamination from neighbouring galaxies is too severe).
 These two effects will lead to a ${\sim}20$\% uncertainty in  the amplitude of our SMF.
@@
             They use a \m2l{} that is adopted from the SED fitting results from the ``dusty'' 
-            model in \citet{Mendel2014}.  \alexie{CLARIFY HERE SSp model}.   
+            model in \citet{Mendel2014}. 
+            This model also uses the \texttt{FSPS} stellar population model 
+            \citep{FSPS} and assumes a \citet{Chabrier2003} IMF. 
     \end{itemize}
@@
     prominent stellar halo and has much shallower outer slope compared to our data. In future work, we will compare  our HSC profiles with  predictions from more advanced 
-    hydrodynamic simulations such as XXX AND XXXXX. These data will help fine-tune simulations and to understand the physical mechanisms that drive the assembly of massive galaxies and the 
+    hydrodynamic simulations such as Horizon-AGN () and MassiveBlackII ().
+These data will help fine-tune simulations and to understand the physical mechanisms that drive the assembly of massive galaxies and the
     build up of stellar halos.
@@
       \includegraphics[width=\textwidth]{fig/redbcg_ell_color.pdf}
-      \caption{\alexie{Remake the light grey lines in this figure.
-Pick a smaller number.
-Say 100.
-And make the thin grey lines a little darker.
-Right now it is really hard to get anything useful from the think grey lines.}
-          Radial profiles of the ellipticty and optical colors of massive galaxies in our sample. The general format of this figure is similar to Fig~\ref{fig:avg_prof}.  The
-          \textbf{left panel} displays ellipticity profiles, 
+      \caption{
+          Radial profiles of the ellipticty and $k$-corrected rest-frame optical colors 
+          of massive galaxies in our sample. 
+          The general format of this figure is similar to Fig~\ref{fig:avg_prof}.  
+          The \textbf{left panel} displays ellipticity profiles, 
           the \textbf{Upper-right panel} shows $g-r$ color profiles, and  the
@@
           and NGC 4365 (\citealt{Mihos2017}), and the $g-i$ profile of NGC 1399 
-          (\citealt{Iodice2016}). \rachel{State explicitly that these are rest-frame colors.}
+          (\citealt{Iodice2016}).
           }
@@
 	ellipticity profiles and 2-D modeling results \citep{Porter1991, Gonzalez2005, 
-	Zibetti2005, Spavone2017; Huang2013a, Oh2017}.
-However,  to the best of our knowledge, our HSC results are the first to show  clear evidence that:  a) the ellipticities of the stellar halo  depend strong ly on galaxy mass, and b)  the ellipticity of the stellar halo is anti-correlated with the slope of \mden{}.
+	Zibetti2005, Spavone2017, Huang2013a, Oh2017}.
+However,  to the best of our knowledge, our HSC results are the first to show  clear evidence that:  a) the ellipticities of the stellar halo  depend strongly on galaxy mass, and b)  the ellipticity of the stellar halo is anti-correlated with the slope of \mden{}.
 
@@
     ETGs; the original profile is in units of $R_{\mathrm{e}}$, we use a typical 
-    $R_{\mathrm{e}}=8.0$ kpc to convert it into physical kpc} and 
+    $R_{\mathrm{e}}=8.0$ kpc to convert it into physical kpc.} and 
     \citealt{DSouza2014}.
@@
     stacked SDSS ones. 
-    Considering differences in the response curves between HSC and SDSS filters, together with the uncertainties of color measurements, the HSC $g-r$ color profiles are  in failry good agreement with  those from SDSS.
-However, the $g-i$ profiles of HSC galaxies are steeper compared to SDSS.
+    Considering differences in the response curves between HSC and SDSS filters, together with the uncertainties of color measurements, the HSC $(g-r)$ color profiles are  in fairly good agreement with  those from SDSS.
+However, the $(g-i)$ profiles of HSC galaxies are steeper compared to SDSS.
 The SDSS $i$-band suffers from the so-called ``red-halo'' effect
@@
     NGC 4472 (\citealt{Mihos2013}) and NGC 4365 (\citealt{Mihos2017})\footnote{
-    Both are converted from $B-V$ colors}, and the $g-i$ profile of NGC 1399 
+    Both are converted from ($B-V$) colors.}, and the $g-i$ profile of NGC 1399 
     (\citealt{Iodice2016}). These individual profiles  display  similar color gradients as our HSC sample.
@@
     that the fraction of accreted stars should strongly increase with stellar 
-    mass and that for very massive galaxies, the  ``ex-situ'' may reach up to xxxxxxx \% of the total galaxy mass (e.g.
+    mass and that for very massive galaxies, the \textit{ex-situ} may reach up to 
+    50-90\% of the total galaxy mass (e.g.
     \citealt{Oser2010, Cooper2013, Dubois2013, LeeYi2013, Hirschmann2015,
@@
 
-    This picture is supported by our observations that massive galaxies display more prominent stellar halos as well as by their  negative color gradients.
-The fact that the outskirts of these galaxies are slighly bluer than  the inner regions, is  consistent with the picture that  stellar halos are built up from  less massive galaxies \alexie{justify here.
-Why bluer?}.
+    This picture is supported by our observations that massive galaxies display more 
+    prominent stellar halos as well as by their  negative color gradients. 
+    The fact that the outskirts of these galaxies are slightly bluer than the inner
+    regions, is consistent with the picture that stellar halos are built up by 
+    series of minor mergers (average merger mass-ratio between 1:3-1:10; e.g. 
+    \citealt{Huang2016}) as less massive ETGs are typically bluer.
 
@@
     For more massive ETGs,  results so far mainly depend on multi-component model fitting
-    and image stacking analyses (e.g. \citealt{Huang2013a, dSouza2014, Spavone2017}).
+    and image stacking analyses (e.g. \citealt{Huang2013a, DSouza2014, Spavone2017}).
     In this work, we propose that \mstar{} computed within different fixed physical apertures are worth exploring as  proxies of the  ex situ fraction.
-We propose to use the mass within 10 kpc (\minn{}) and 100 kpc (\mtot{}) as proxies for the \textit{in situ} componnt and for the total \mstar{}.
+We propose to use the mass within 10 kpc (\minn{}) and 100 kpc (\mtot{}) as proxies for the \textit{in situ} component and for the total \mstar{}.
 
@@
 We find that  our proxy for the accreted mass component correlates strongly with  \mtot{} and that this relation is surprisingly consistent with predictions from \citet{RodriguezGomez2016}.
-Given the limitations of the Illustris simulation, and the impperfect nature of our proxy for the ex sity fraction proxy, the almost perfect agreeement seen in Figure \ref{fig:discussion_1} may well be a coincidence.
-However, it is encouraging to see that our simple proxy for the fraction of ex sity stars seems to match both the slope and the scatter of the predicted relation.
+Given the limitations of the Illustris simulation, and the imperfect nature of our proxy for the ex situ fraction proxy, the almost perfect agreement seen in Figure \ref{fig:discussion_1} may well be a coincidence.
+However, it is encouraging to see that our simple proxy for the fraction of ex situ stars seems to match both the slope and the scatter of the predicted relation.
 There exist other  hydrodynamic simulations that predict significantly different ex situ fractions compared to Illustris (e.g.
@@
 %% ------------------------------------------------------------------------------------ %%  
-\section{A. Extraction of 1-D surface brightness profile} 
+\section{A. Basic Statistical Properties of the Sample} 
+	\label{app:basic}
+
+    On the top-left panel of Fig~\ref{fig:sample_stats}, we show the \mtot{}-color 
+    relations using the $k$-corrected $g-r$ color. 
+    Both samples follow the same tight ``red-sequence'' with little contamination 
+    from the ``blue cloud''.
+    At fixed \mtot{}, we see little offset in color distributions of the two 
+    samples, suggesting that both samples consist of quiescent galaxies with 
+    similar average stellar population properties.  
+    This is consistent with previous result that suggests the average stellar 
+    population of massive central galaxy does not depend on \mhalo{} 
+    (e.g.\ \citealt{Park2007}).  
+    In this work, we focus on the \mstar{} range of $11.6 \le$\logmtot{}$\le 11.9$, 
+    where both samples have acceptable completeness, and their \mtot{} distributions 
+    greatly overlap (see the normalized distributions of \mtot{} in the bottom-left 
+    panel of Fig~\ref{fig:sample_stats}). 
+    As for the \minn{} distributions, the two samples overlap the most within 
+    $11.2 \le$\logmtot{}$\le 11.6$, but now they show quite different
+    distributions (bottom-right figure).
+
+    The redshift distributions also show small difference
+    (upper-right panel) even in the high-\mtot{} bin, where the redshift distribution 
+    of the \nbcg{} sample skews toward higher-$z$ end due to the contribution of BOSS 
+    spec-$z$.
+
+%% ------------------------------------------------------------------------------------ %% 
+  \begin{figure}
+      \centering 
+      \includegraphics[width=\columnwidth]{fig/redbcg_sample_stats}
+      \caption{
+          \textbf{Top-left}: The \logms{}-$g-r$ color relation of the \rbcg{} 
+          (red circle; detaield format is the same with the right panel of 
+          Fig~\ref{fig:smf1}) and \nbcg{} (grey dots) samples.
+          We apply the $k$-corrections from \texttt{iSEDFit} fitting to the colors.~~          
+          \textbf{Top-right}: the histograms of the redshift for the \rbcg{} and 
+          \nbcg{} galaxies in both \logmtot$>11.2$ and $11.6<$\logmtot{}$<11.9$
+          mass bins.
+          The vertical lines highlights the $0.3\leq z \leq 0.5$ redshift range.~~
+          \textbf{Bottom-left}: the histograms of \mtot{} for the \rbcg{} (orange-red) 
+          and \nbcg{} (grey-black) samples at both $z>0.2$ (step-filled histogram) and 
+          $0.3 \leq z \leq 0.5$ (stepped histogram). 
+          The vertical lines in both top-left and bottom-left figures highlight the 
+          $11.6<$\logmtot{}$<11.9$ mass range that will be used in the comparison of 
+          the \mtot{}-matched samples.~~
+          \textbf{Bottom-right}: the histograms of \minn{} in similar format. 
+          Here the vertical lines highlight the 
+          $11.2<$\logminn{}$<11.6$ mass range that is used for comparison.
+      }
+      \label{fig:sample_stats}
+  \end{figure}
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
+\section{B. Extraction of 1-D surface brightness profile} 
     \label{app:ellipse}
@@
 %% ------------------------------------------------------------------------------------ %% 
-\section{B. Estimate average {$M_{\star}/L_{\star}$} using \texttt{iSEDFit}} 
+\section{C. Estimate average {$M_{\star}/L_{\star}$} using \texttt{iSEDFit}} 
     \label{app:sed}

### 2017-06-30 draft/paper1_rachel.tex
Edit final sample and result 1

@@
           from the S82-MGC catalog (green line). 
+          The grey dashed line shows the number density function of HSC massive 
+          galaxies in the three GAMA fields for comparison.
           The associated uncertainties derived from bootstrap resampling are shown in 
@@
     limit on the ``total'' \mstar{}. 
-    In Fig \ref{fig:mass_diff}, we integrate the \mden{} of each galaxy to the edge of 
-    the postage-stamp and call this mass \mmax{}. 
+    In Fig \ref{fig:mass_diff}, we integrate the \mden{} of each galaxy to the 
+    edge of the postage-stamp, and pick the isophote that gives us the highest  
+    luminosity to estimate the \mstar{} within and call this one \mmax{}. 
     The right panel of Fig \ref{fig:mass_diff} compares \mmax{} and \mtot{}.  
@@
 
-    The robust identification of the central galaxy is not an easy task (e.g.
-    \citealt{Yang2007}). 
-    In this paper, we use the \redm{} catalog create a sample of massive central 
-    galaxies with minimal contamination from satellite galaxies.
-
-%    Given the smaller fraction of satellite galaxies at high-\mstar{} end (e.g. 
-%    \citealt{Reid2014, Hoshino2015, Saito2016}), 
-%    we further assume that the massive ones (\logmtot{}$>11.4$) among them are likely 
-%    to be the central galaxies of these smaller halos.
+    Although the central galaxies of dark matter halos have unique importance is 
+    studying galaxy-halo connection, robust identification of central galaxy is 
+    not easy(e.g.\citealt{Yang2007}) in observation.
+    First, based on previous results (\citealt{Reid2014, Hoshino2015, Saito2016}),
+    the satellite fraction at \logmtot{}$> 11.6$ should become quite low 
+    ($\sim 10$\% level). 
+    And, we can further use the \redm{} catalog to identify and exclude massive 
+    satellites in cluster-level dark matter halos--to further reduce contamination
+    from satellite galaxies.
 
@@
     All these studies consistently find that \redm{} clusters with $\lambda > 20$ 
-    have $\log (M_{\mathrm{halo}}/M_{\odot}) \geq 14.0$. 
+    generally have $\log (M_{\mathrm{halo}}/M_{\odot}) \geq 14.0$, although the scatter 
+    of \mhalo{} at fixed $\lambda$ can not be ignored.
     Therefore the central galaxies of these \redm{} clusters\footnote{We only use 
@@
     galaxies that live in massive halos as described above.
-\rachel{Intrinsic scatter in \mhalo{} at fixed $\lambda$ is pretty big, though, so we should be careful about this assertion.}
     Such information is also very useful in studying the relationship between galaxy
     structure and environment (Huang\etal in prep.).
+
 %% ------------------------------------------------------------------------------------ %%
@@
     as the \rbcg{} sample. 
-    Due to the depth and resolution of SDSS, the \redm{} catalog becomes slightly 
-    incomplete at lower richness ($\lambda < 40$) at $z > 0.33$, but the main results 
-    of this work are not affected by this.
+    It is also worth pointing out that, due to the depth and resolution of SDSS 
+    images, this \redm{} catalog is not complete down to $\lambda=20$ at 
+    $0.3 < z < 0.5$. 
+    At $z\geq0.33$, it starts to miss a small fraction of clusters with $\lambda < 30$, 
+    but the main results of this work will not be affected by this.
     %% Saved as "dr1_redbcg_use_sed5b.fits"
@@
     \logmh{}$< 14.0$. 
-    We will refer to this sample of \textbf{galaxies in less 
-    massive halos} as the \nbcg{} sample.
-Because we have rejected satellites in \redm{} clusters, and because above our galaxy mass cut most satellites reside in halos with \logmh$>14.0$ (e.g.
-\citealt{Reid2014,
-    Hoshino2015, Saito2016, vanUitert2016}), galaxies in the \nbcg{} sample should  be dominated by central galaxies.
-    \rachel{There is a statistical distribution of halo masses that satellites at this stellar mass live in, based on the papers you cited; can you say more quantitatively what fraction you expect to be satellites in less massive halos?
-Right now it all sounds kind of hand-wavey.}
-
+    We will refer to this sample of \textbf{galaxies in less massive halos} as the 
+    \nbcg{} sample. 
+    Because we have rejected satellites in \redm{} clusters, and because above our 
+    galaxy mass cut most satellites reside in halos with 
+    \logmh$>14.0$ (e.g. \citealt{Reid2014, Hoshino2015, Saito2016, vanUitert2016}), 
+    galaxies in the \nbcg{} sample should  be dominated by central galaxies.
+    Using the model presented in \citet{Saito2016}, we estimate that in dark matter 
+    halos with \logmh$<11.4$, $\sim 7$\% of galaxies with \logmcmodel{}$>11.5$ are 
+    satellites.
+    This confirms that our sample should have low enough satellite contamination 
+    so that it can be taken as a sample of massive central galaxy.     
     %% Saved as "dr1_nonbcg_use_sed5b.fits"
@@
 
-    The following is a summary of our sample construction. \rachel{Would be valuable to remind the reader in what sections these samples were defined, and how many galaxies are in each one.}
+    The following is a summary of our sample construction.
 
@@
             data release. 
+            This sample is described in \S \ref{ssec:initial}, and it contains 
+            1760845 galaxies. 
         \item \texttt{hscZ} sample: we limit the \texttt{hscPho} sample to galaxies 
             with reliable redshift information. 
+            More details of this sample can also be found in \S \ref{ssec:initial}. 
+            It provides us 25286 useful galaxies at $0.3<z<0.5$.
         \item With the help of the \redm{} cluster catalog, we further select 
-            candidates of massive central galaxies in a range of \mhalo{}.
+            candidates of massive central galaxies.
             We broadly divide the sample into central galaxies living in halos
             with \logmh{}$\geq 14.0$ (\rbcg{}) and \logmh{}$<14.0$ (\nbcg{}).
+            To ensure the sample is \mstar{}-complete and has minimal satellite 
+            contamination, we will further focus on the 950 massive galaxies with 
+            \logmtot{}$>11.6$ in this work\footnote{As reference, there are 
+            2613 massive galaxies with \logmtot{}$>11.5$ in our sample.}.
+
     \end{itemize}
 
-    The  division of our sample into two halo mass bins is mainly relevent for Paper II.
-For this paper, we only consider the halo mass dependence on our sample when we evaluate impact of  mass estimates on the SMF in Section \ref{ssec:smf}.
-
-\rachel{Could we show the redshift distribution of the second and third of these samples?}
+    The division of our sample into two halo mass bins is mainly relevant for Paper II
+    (Huang \etal in prep.).  
+    For this paper, we only consider the halo mass dependence on our sample when we 
+    evaluate impact of mass estimates on the SMF in \S \ref{ssec:smf}. 
+    We show the distributions of redshift, \mtot{} and \minn{} of the massive galaxy 
+    sample in Appendix \ref{app:basic}, along with its \mtot{}-$(g-r)$ rest-frame 
+    color relation.
 
@@
           \textbf{Left:} Impact of using \mtot{} on the galaxy stellar mass function. 
-          Dashed lines correspond to the SMF computed using \mcmodel{} whereas solid 
-          lines correspond to the SMF computed using \mtot{}. 
+          Dashed lines correspond to the observed volume density distribution 
+          computed using \mcmodel{} whereas solid lines correspond to the distribution
+          computed using \mtot{}. 
+          We do not apply any completeness correction to the distributions here.
           Here we separate our HSC sample into centrals in halos more massive than
@@
           very massive halos.
-          \textbf{Right}: The stellar mass volume density distributions of massive 
+          \textbf{Right}: The \mstar{} volume density distributions of massive 
           HSC galaxies, using both \mtot{} (black solid line) and \mmax{} (black dotted 
           line).  
-          The grey shaded region shows the resampling error on the HSC SMF plus an additional 20\%
-          uncertainty to account for the fact that  we do not include satellite galaxies and that we fail to extract a 1-D profile for xxx\% of our galaxies.
-These issues will be adressed in forthcoming work.
+          Vertical lines on both plots highlight the \logmtot{}$=11.6$ mass limit. 
+          The grey shaded region shows the resampling error on the HSC SMF plus an
+          additional 20\% uncertainty to account for the fact that we do not include 
+          satellite galaxies and that we fail to extract a 1-D profile for $\sim 10$\% 
+          of our galaxies. 
+          These issues will be addressed in forthcoming work. 
           We compare our results with previous studies: 
@@
           \citet{Leauthaud2016} based on PSF-matched SDSS-UKIDSS photometry (green).
-          \rachel{Need to state explicitly what the vertical line is.
-I assume this is the stellar mass below which the sample is presumed to be too incomplete for proper derivation of the SMF.
-If that's true, should we even be showing masses below that?
-Or perhaps the entire left side can be shaded, instead of just having a line there?
-Also, are any completeness corrections applied at any value of stellar mass?}}
+          }
       \label{fig:smf}
@@
 
-    The Stellar Mass Function (SMF) and its evolution are critical to our understanding of galaxy evolution. On average, the integration of our carefully derived non-parametric \mden{} profile 
+    The Stellar Mass Function (SMF) and its evolution are critical to our understanding 
+    of galaxy evolution. 
+    On average, the integration of our carefully derived non-parametric \mden{} profiles 
     to 100 kpc (\mtot{}) recovers more light (hence mass) than the \texttt{cModel} method. 
@@
     These differences relate to the intrinsic limitation of the \texttt{cModel} 
-    method and also reflects the fact that more massive ETGs tend to have more 
+    method and also reflect the fact that more massive ETGs tend to have more 
     extended stellar mass distributions (e.g. higher-\ser{} index, 
-    \citealt{Graham2003}). Hence,  the determination of the ``total luminosities'' of massive galaxies can result in  a significant impact 
-    on the high mass end of the galaxy stellar mass function (e.g. 
-    \citealt{Bernardi2013, DSouza2014, DSouza2015, Bernardi2017}).
+    \citealt{Graham2003}). Hence, the determination of the ``total luminosities'' of 
+    massive galaxies can result in a significant impact on the high mass end of the 
+    galaxy stellar mass function (e.g. \citealt{Bernardi2013, DSouza2014, DSouza2015,
+    Bernardi2017}).
 
@@
     In this paper, we have only measured light profiles for central galaxies. 
-Also,  we cannot extract  a 1-D profile for $\sim 11$\% of galaxies (because contamination from neighbouring galaxies is too severe).
-These two effects will lead to a ${\sim}20$\% uncertainty in  the amplitude of our SMF.
-\rachel{Mass-dependent, or really 20\% at all masses?} These are limitations that we are currently working to address and a forthcoming paper will  address them.
-Our goal in this paper is therefore not  to  attempt a detailed comparison between different SMFs
-    \citep[e.g.,][]{Bernardi2013, Bernardi2017}. Instead, our goal in this section is more simply to characterize the  impact of various \mstar{} measurements  on the high-mass end of the SMF.
-
-     Figure \ref{fig:smf} displays the impact of missing light and of different definitions of \mstar{} on the SMF.
-The left panel of Fig.~\ref{fig:smf} shows the SMF\footnote{Our SMFs turn over at the low mass end as we have not applied any completeness corrections here.
-\rachel{Why is this a footnote?
-It's a major feature of the plot, not a minor detail.}} computed using \mcmodel{} and \mtot{} for galaxies that live in low and high mass halos.
-Figure \ref{fig:smf} shows that the impact of missing flux is more severe for  galaxies in high mass halos.
-In Paper II it will be demonstrated that this occurs because  galaxies in more massive halos have larger extended  wings than those in low mass halos (Huang\etal in prep.).
-Figure \ref{fig:smf} also shows that  the use of the HSC \texttt{cModel} magnitude leads to a severe underestimation of the  high mass end of the SMF.
-\rachel{It would be useful if we can say whether this is primarily because of the adoption of simple parametric profiles, or due to background subtraction failures.
-For example, if the adoption of simple parametric profiles is the primary cause of this difference, then that is a statement that might be more widely applicable than just the HSC pipeline.
-If it's really just because our background subtraction algorithm is bad, then the implications are more limited.
-Do we have the information that would allow us to make a statement about this?
-If not, we should at minimum reiterate here the possible causes of this discrepancy.}
+    Also, we cannot extract 1-D profiles for $\sim 11$\% of galaxies (because 
+    contamination from nearby bright object is too severe; or the its in a late-stage
+    on-going merger system). 
+    These two effects will lead to a ${\sim}20$\% uncertainty in the amplitude of 
+    our volume number density distributions. 
+    Both of these effects show dependence on \mtot{} whereas more massive galaxies 
+    suffer slightly less from them.
+    We are currently working to address these limitations in a forthcoming paper. 
+    Our goal in this paper is therefore not to attempt a detailed comparison between 
+    different SMFs \citep[e.g.,][]{Bernardi2013, Bernardi2017}. 
+    Instead, our goal in this section is simply to characterize the impact of various 
+    \mstar{} measurements on the high-mass end of the SMF.   
+    Our volume density distributions (will be referred to as SMF for simplicity) 
+    turn over at low-mass end where the sample becomes incomplete, and we do not attempt
+    to apply any completeness correction here.
+
+     Figure \ref{fig:smf} displays the impact of missing light and of different 
+     definitions of \mstar{} on the SMF. 
+     The left panel of Fig.~\ref{fig:smf} shows the SMF computed using \mcmodel{} 
+     and \mtot{} for galaxies that live in low and high mass halos.  
+     Figure \ref{fig:smf} shows that the impact of missing flux is more severe for  
+     galaxies in high mass halos. 
+     In Paper II of this series (Huang\etal in prep.), it will be demonstrated that 
+     this occurs because galaxies in more massive halos have more extended stellar 
+     envelopes than those in lower mass halos at fixed \mtot{}. 
+     Figure \ref{fig:smf} also shows that the use of the HSC \texttt{cModel} 
+     magnitude leads to a severe underestimation of \mstar{} at the high mass end 
+     of SMF. 
+     From the current \texttt{hscPipe}, this problem could relate to the intrinsic 
+     limitation of simply model like \cmodel{} and the issue of over-subtracted 
+     background. 
+     Based on the 1-D surface brightness profiles in $i$-band, background subtraction
+     does not seem to be the most serious problem for these $z>0.3$ galaxies 
+     (at least not within 100 kpc). 
+     And, in the next section, we will show that a significant fraction of these 
+     1-D profiles are more extended in the outskirt than the de~Vaucouleurs profile, 
+     therefore it is not surprising that \cmodel{} will systematically underestimate 
+     their total flux.
 
@@
 
-        As discussed in Section~\ref{ssec:mtotal}, even with our deep HSC images,
-    it is non-trivial to clearly define and measure the ``total'' \mstar{} for 
+    As discussed in \S~\ref{ssec:mtotal}, even with deep HSC images,
+    it is not trivial to clearly define and measure the ``total'' \mstar{} for 
     these massive systems, and the \mden{} profiles of these galaxies often extend 
     well beyond 100 kpc. 
-Is our fiducial 100 kpc radius sufficient in order to capture  most of the flux associated with these galaxies, or does one need to integrate out to even larger radii?
-To answer this question,  we attempt to capture more flux by integrating our \mden{} profiles out to the detection
-    limit that is defined by the background noise.
-We will refer to this mass as \mmax{}.
-Although the \mden{} profiles become more uncertain at $>100$ kpc, \mmax{} helps us quantify how much extra mass may be contained at radii greater than 100 kpc.
-The right hand side of Figure \ref{fig:smf} shows the impact of using \mmax{} instead of  \mtot{} on the SMF.
-We find that  a 100 kpc radius captures a majority of the galaxy mass and that the impact of going from \mtot{} to \mmax{} is relatively small
-
-    In Figure \ref{fig:smf} we also compare our results  with the following previous studies:
+    Is our fiducial 100 kpc radius sufficient to capture most of the flux associated 
+    with these galaxies, or does one need to integrate out to even larger radii? 
+    To answer this question, we attempt to capture more flux by integrating our 
+    \mden{} profiles out to the edge of the image and use the highest \mstar{} 
+    achieved during this process as \mmax{}.
+    Although the \mden{} profiles become more uncertain at $>100$ kpc, \mmax{} helps 
+    us quantify how much extra \mstar{} may be contained at radii greater than 100 kpc.  
+    The right hand side of Figure \ref{fig:smf} shows the impact of using \mmax{} 
+    instead of  \mtot{} on the SMF.  
+    We find that a 100 kpc radius captures a majority of the galaxy mass and that the 
+    impact of going from \mtot{} to \mmax{} is relatively small.
+
+    In Figure \ref{fig:smf} we also compare our results with the following previous 
+    studies:
 
@@
             \citep{Leauthaud2016} where \mstar{} is derived using 
-            \texttt{iSEDfit} on PSF-corrected aperture photometry from 
-            \texttt{S82}.
-They adopt the same IMF, dust model, and star-formation model as we do, but use the \texttt{BC03} model.
-Based on the test results from Appendix \ref{app:sed}, we shift the \citet{Leauthaud2016} SMF by 0.08 dex to add their data to Figure~\ref{fig:smf}.
+            \texttt{iSEDfit} on PSF-corrected aperture photometry from \texttt{S82}. 
+            They adopt the same IMF, dust model, and star-formation model as we do, 
+            but use the \texttt{BC03} model instead. 
+            Based on the test results in Appendix \ref{app:sed}, we shift this SMF by 
+            0.08 dex to add their data to Figure~\ref{fig:smf}.
+
         \item The SMF derived from a SDSS-\textit{GALEX} sample of $z{\sim} 0.1$ 
-            galaxies from \citet{Moustakas13}.  Total luminosities from \citet{Moustakas13} are based on SDSS \cmodel{} magnitude. 
-            They use a \m2l{} that is derived via SED fitting using \texttt{iSEDfit} with similar 
-            assumptions as here.
-        \item The observed SMF for $z{\sim} 0.1$ SDSS galaxies from 
-            \citet{Bernardi2017}.  Total luminosities in  \citet{Bernardi2017} are based on 2-D \texttt{SerExp} models 
-            (\ser{}$+$ Exponential disk model; integrated to infinity) that 
+            galaxies by \citet{Moustakas13}. 
+            Total luminosities in \citet{Moustakas13} are based on SDSS \cmodel{} 
+            magnitudes. 
+            They use a \m2l{} that is derived via SED fitting using \texttt{iSEDfit} 
+            with similar assumptions as the ones adopted here.
+
+        \item The observed SMF for $z{\sim} 0.1$ SDSS galaxies from \citet{Bernardi2017}.          
+            Total luminosities in \citet{Bernardi2017} are based on 2-D \texttt{SerExp} 
+            models (\ser{}$+$ Exponential disk model; integrated to infinity) that 
             recover more flux compared to SDSS \cmodel{} magnitudes 
             (\citealt{Bernardi2013, Meert2015}). 
-            They use a \m2l{} that is adopted from the SED fitting results from the ``dusty'' 
-            model in \citet{Mendel2014}. 
+            They use a \m2l{} that is adopted from the SED fitting results in
+            \citet{Mendel2014}. 
             This model also uses the \texttt{FSPS} stellar population model 
-            \citep{FSPS} and assumes a \citet{Chabrier2003} IMF. 
+            \citep{FSPS}, assumes a \citet{Chabrier2003} IMF, and considers dust 
+            extinction using the \citet{Calzetti2000} extinction law (the 
+            ``dusty'' model).
+
     \end{itemize}
 
-    As mentioned above, our current SMF is subject to an additional 20\% uncertainty that will be addressed in forthcoming work.
-Hence,  we do not attempt a detailed comparison  with respect to previous work on the galaxy SMF, reserving this  for  a future study.
-Here, we simply note that the  HSC SMF derived using \mtot{} is close to the one derived by \citet{Bernardi2017} using SDSS data at $z{\sim}0.1$ and assuming \texttt{SerExp} models.
+    As mentioned above, our current SMF is subject to an additional 20\% uncertainty 
+    that will be addressed in forthcoming work. 
+    Hence, we do not attempt a detailed comparison with respect to previous works on 
+    the SMF, reserving this for a future study. 
+    Here, we simply note that the HSC SMF derived using \mtot{} is close to the one 
+    derived by \citet{Bernardi2017} using SDSS data at $z{\sim}0.1$ and assuming 
+    the \texttt{SerExp} models.  
     Our sample and the \citet{Bernardi2017} sample have different redshifts. 
-Without a more in-depth study, we cannot ascertain wheter or not  the apparent agreement between the HSC SMF and the  \citet{Bernardi2017} SMF indicates a global lack of evolution in the galaxy SMF, or  that other effects are at play (difference between \mtot{} masses and \texttt{SerExp} masses) that have cancelled redshift evolution.
-In future work, it will be interesting to perform a more consistent analysis to search for redshift evolution in the galaxy SMF and to study whether  or not massive galaxies in HSC are well described by \texttt{SerExp} models.
+    Without a more in-depth study, we cannot ascertain whether or not the apparent 
+    agreement between the HSC SMF and the \citet{Bernardi2017} SMF indicates a global 
+    lack of evolution in the galaxy SMF, or that other effects are at play 
+    (difference between \mtot{} masses and \texttt{SerExp} masses) that have cancelled
+    redshift evolution.  
+    In future work, it will be interesting to perform a more consistent analysis to 
+    search for redshift evolution in the galaxy SMF and to study whether or not 
+    massive galaxies in HSC are well described by \texttt{SerExp} models.
 

### 2017-06-30 draft/paper1_rachel.tex
Edit final sample and result 1

@@
         \newauthor
-        Yutaka Komiyama,$^{5,8}$
-        HSC collaboration 
+        Yutaka Komiyama$^{5,8}$
         \\
@@
               Thin grey lines show a random subset of individual profiles.  
-The scatter between the thin grey lines reflects the true scatter in the profiles of massive galaxies (not measurement error).
-The shaded region highlights the region that could be affected by the PSF.
-\rachel{`most strongly' affected?}
+              The scatter between the thin grey lines reflects the true scatter in 
+              the profiles of massive galaxies (not measurement error). 
+              The shaded region highlights the region that is most strongly affected 
+              by the seeing. 
               Two vertical lines indicate 10 kpc (thin, dotted line) and
@@
 
-    Previous work on the structural evolution of massive galaxies has often focused on scaling relations such as the ``\mstar{}-size'' relation.  We argue that  comparing \mden{} 
-    profiles  directly  captures more information than the \mstar{}-size relation and  has the advantage that it bypasses difficult questions 
-    about how to accurately define and measure galaxy ``sizes'' and ``masses''.
-
-    Fig.~\ref{fig:avg_prof} shows the median \mden{} profiles\footnote{The median 
-    profiles along with their uncertainties are derived using bootstrap resampling.
-\rachel{Why is this a footnote?
-It's a major feature of the plot, not a minor detail.
-Same comment applies to footnote below this.}} of massive central galaxies at $0.3 < z < 0.5$ in three \mtot{}
-    bins\footnote{Note that our sample is not complete in our lowest \mtot{} bin.}. 
+    Previous work on the structural evolution of massive galaxies has often focused on 
+    scaling relations such as the ``\mstar{}-size'' relation.  
+    We argue that  comparing \mden{} profiles directly captures more information than
+    the \mstar{}-size relation and has the advantage that it bypasses difficult 
+    questions about how to accurately define and measure galaxy ``sizes'' and 
+    ``masses''.
+
+    Fig.~\ref{fig:avg_prof} shows the median \mden{} profiles of massive central 
+    galaxies at $0.3 < z < 0.5$ in three \mtot{} bins.
+    These median profiles along with their uncertainties are derived using bootstrap
+    resampling method. 
+    And it is worth pointing out again that our sample is not complete in the lowest 
+    \mtot{} bin, although there is no reason to believe the median \mden{} profile
+    will be significantly affected. 
     As shown in the left panel of Fig~\ref{fig:avg_prof}, we can comfortably trace
-    the \mden{} profiles of these massive galaxies out to 100 kpc 
-    \textbf{individually}.  At large scales, some of our \mden{} profiles show signs of unphysical truncation and fluctuation 
-    related to inaccurate sky subtraction. In this paper, we do not use profiles beyond 100 kpc, even though the median 
+    the \mden{} profiles of these massive galaxies out to 100 kpc \textbf{individually}.  
+    At large scales, some of our \mden{} profiles show signs of unphysical truncation and
+    fluctuation related to inaccurate sky subtraction. 
+    In this paper, we do not use profiles beyond 100 kpc, even though the median 
     \mden{} profiles for the two most massive bins behave reasonably out to 
@@
     particle-tagging technique (e.g., \citealt{Cooper2010}). 
-    The simulated \mden{} profile is affected by the resolution limit of the simulation in the inner region, but  is in good agreement with our median \mden{} profile for 
+    The simulated \mden{} profile is affected by the resolution limit of the simulation 
+    in the inner region, but is in good agreement with our median \mden{} profile for 
     the $11.6 <$ \logmtot{} $< 11.8$ bin within 40 kpc. 
     However, outside 40 kpc, the particle tagging method seems to predict a too 
-    prominent stellar halo and has much shallower outer slope compared to our data. In future work, we will compare  our HSC profiles with  predictions from more advanced 
-    hydrodynamic simulations such as Horizon-AGN () and MassiveBlackII ().
-These data will help fine-tune simulations and to understand the physical mechanisms that drive the assembly of massive galaxies and the
-    build up of stellar halos.
+    prominent stellar halo and has much shallower outer slope compared to our data. 
+    In future work, we will compare our HSC profiles with predictions from more 
+    advanced hydrodynamic simulations such as \textit{Horizon-AGN} (\citealt{Dubois2014}) 
+    and MassiveBlackII (\citealt{Khandai2015}). 
+    These data will help fine-tune simulations and to understand the physical mechanisms 
+    that drive the assembly of massive galaxies and the build up of stellar halos.
 
@@
   % Personal 
-  The authors thank Frank van~den~Bosch for insightful discussions.
-  SH thanks F.S.Liu for sharing the data from his work.
+  The authors thank Frank van~den~Bosch for insightful discussions and thank 
+  Shun Saito for helping us estimate the fraction of satellite galaxies in our sample.
+  SH thanks Feng-Shan Liu for sharing the \mden{} profile of the $z\sim1$ BCG from 
+  his work.
 

### 2017-06-30 draft/paper1_rachel.tex
Edit mden profile result 1

@@
     lack of evolution in the galaxy SMF, or that other effects are at play 
-    (difference between \mtot{} masses and \texttt{SerExp} masses) that have cancelled
-    redshift evolution.  
+    (for example, the difference between \mtot{} masses and \texttt{SerExp} masses) 
+    that have cancelled redshift evolution.  
     In future work, it will be interesting to perform a more consistent analysis to 
@@
 
-       From Figure~\ref{fig:avg_prof} we can see  the galaxies in our sample have homogeneous profiles on small radial scales.
-The amplitude of \mden{} increases with galaxy mass on 10 kpc scales but the slope of  \mden{} remains similar.
-From previous work on this topic, we already know that the inner regions of massive elliptical galaxies display relatively uniform structural (e.g.
-\mden{} profile, isophotal shape,
-    \citealt{Lauer07, Kormendy2009, Schombert2015} and kinematic (e.g. 
-    \citealt{Cappellari13b}) properties.
-However,  Figure~\ref{fig:avg_prof} reveals  a significant diversity in the outer envelopes of massive galaxies.
-Given the \s2n{} of HSC images at these surface brightness levels, the scatter shown in Figure~\ref{fig:avg_prof} corresponds to \textbf{intrinsic scatter in the stellar envelopes of massive galaxies.}.
-Importantly, Figure~\ref{fig:avg_prof} shows that the global mass profiles of galaxies at these masses are  \textbf{clearly not
-    self-similar} out to 100 kpc.
-
-In the right-hand side of Fig.~\ref{fig:avg_prof}, we compare our 
-\mden{} profiles with results from previous  work.
+    From Figure~\ref{fig:avg_prof} we can see the galaxies in our sample have 
+    homogeneous profiles on small radial scales. 
+    The amplitude of \mden{} increases with galaxy mass on 10 kpc scales but the slope 
+    of \mden{} remains similar.  
+    From previous work on this topic, we already know that the inner regions of 
+    massive elliptical galaxies display relatively uniform structural (e.g.
+    \mden{} profile, isophotal shape: e.g. \citealt{Lauer07, Kormendy2009, 
+    Schombert2015}; and kinematic: e.g. \citealt{Cappellari13b}) properties.  
+    However, Figure~\ref{fig:avg_prof} reveals a significant diversity in the outer 
+    envelopes of massive galaxies.  
+    Given the \s2n{} of HSC images at these surface brightness levels, the scatter 
+    shown in Figure~\ref{fig:avg_prof} corresponds to \textbf{intrinsic scatter in 
+    the stellar envelopes of massive galaxies}. 
+    Importantly, Figure~\ref{fig:avg_prof} shows that the global \mden{} profiles 
+    of galaxies at these masses are \textbf{clearly not self-similar} out to 100 
+    kpc and have outskirts with larger scatter.
+
+    In the right-hand side of Fig.~\ref{fig:avg_prof}, we compare our \mden{} 
+    profiles with results from previous work. 
     Deep \mden{} profiles of massive galaxies are rarely available. 
-Even in the nearby universe, it is not trivial to map the low surface brightness  outskirts of massive galaxies (e.g.,
+    Even in the nearby universe, it is not trivial to map the low surface
+    brightness outskirts of massive galaxies (e.g., 
     \citealt{Capaccioli2015, Iodice2016, Iodice2017, Spavone2017, Mihos2017}). 
-There are also not many galaxies that are this massive in the local universe.
-For example, the central galaxy of the COMA cluster, NCG xxx has a galaxy mass of xxxx and is smaller than any of the galaxies considered in this sample.
-
-Most previous studies have often focused on surface brightness profiles instead of mass density profiles.
-Results can also depend on the stacking technique or the model  used to extract the profile (e.g., \citealt{Tal2011, DSouza2015}).
+    The number of very massive galaxies is also very limited in the local universe.
+    For example, according to the \texttt{MASSIVE} survey (\citealt{Ma2014}), there
+    are only $\sim 60$-70 massive galaxies with \logms$> 11.6$ (based on K-band 
+    luminosity) within 108 Mpc.
+
+    Most previous studies have often focused on surface brightness profiles instead 
+    of mass density profiles.  
+    Results can also depend on the stacking technique or the model used to extract 
+    the profile (e.g., \citealt{Tal2011, DSouza2015}). 
     \citet{Huang2013a} derived \mden{} profiles for a small sample of very nearby 
-    ellipticals (within 100 Mpc; median \logms{} ${\sim} 11.3$) based on relatively shallow 
-    images from the Carnegie-Irvine Galaxy Survey (CGS, \citealt{CGS1}).
-This sample is a very low redshift ($z=xxx$), and so the \citet{Huang2013a} galaxies are accurate to  smaller scales (down to $r=1$ kpc) than our HSC sample.
-Our \mden{} profiles show good agreement with the \citet{Huang2013a} sample in the radial range of overlap (out to 50 kpc).
-CGS images are deeper than SDSS images in the $r$-band, but the median
+    ellipticals (within 100 Mpc; median \logms{} ${\sim} 11.3$) based on relatively 
+    shallow images from the Carnegie-Irvine Galaxy Survey (CGS, \citealt{CGS1}).  
+    This sample is at very low redshift ($z<0.02$), and so the \mden{} profiles from 
+    \citet{Huang2013a} galaxies are accurate to smaller scales (down to $r=1$ kpc) 
+    than our HSC ones.  
+    Our \mden{} profiles show good agreement with the \citet{Huang2013a} sample in the radial range of overlap (out to 50 kpc). CGS images are deeper than SDSS images in the $r$-band, but the median 
     profiles from \citet{Huang2013a} still only reach to ${\sim} 50$ kpc for $z{\sim} 0$ (PUT THE EXACT REDSHIFTS HERE)

### 2017-06-30 draft/paper1_rachel.tex
Edit mden profile result 2

@@
     ellipticals (within 100 Mpc; median \logms{} ${\sim} 11.3$) based on relatively 
-    shallow images from the Carnegie-Irvine Galaxy Survey (CGS, \citealt{CGS1}).  
+    shallow images from the Carnegie-Irvine Galaxy Survey 
+    (CGS, \citealt{CGS1})\footnote{https://cgs.obs.carnegiescience.edu/CGS/Home.html}.  
     This sample is at very low redshift ($z<0.02$), and so the \mden{} profiles from 
@@
     than our HSC ones.  
-    Our \mden{} profiles show good agreement with the \citet{Huang2013a} sample in the radial range of overlap (out to 50 kpc). CGS images are deeper than SDSS images in the $r$-band, but the median 
-    profiles from \citet{Huang2013a} still only reach to ${\sim} 50$ kpc for $z{\sim} 0$ (PUT THE EXACT REDSHIFTS HERE)
-    massive galaxies.
+    Our \mden{} profiles show good agreement with the \citet{Huang2013a} sample in 
+    the radial range of overlap (out to 50 kpc). 
+    CGS images are deeper than SDSS images in the $r$-band, but the median 
+    profiles from \citet{Huang2013a} still only reach to ${\sim} 50$ kpc for 
+    $z<0.02$ massive galaxies.
     Meanwhile, our deep HSC images can reliably deliver individual \mden{} profiles 
@@
     ${\sim} 10^{11.2} M_{\odot}$ which is lower than our lowest mass bin. 
-    However, \citet{Patel2013} use the BC03 SSP model which provides masses that are roughly 0.1 dex 
-    lower than our FSPS masses (Appendix~\ref{app:sed}). 
-    Furthermore, the \citet{Patel2013} images are shallower than ours meaning 
-    that their masses will be lower than ours because of missing light in the 
+    However, \citet{Patel2013} uses the BC03 stellar population model which leads to 
+    \mstar{} that are roughly 0.1 dex lower than our FSPS estimates 
+    (see Appendix~\ref{app:sed}). 
+    Furthermore, the \citet{Patel2013} images are shallower than ours which means 
+    that their \mstar{} could still be underestimated due to missing light in the 
     outskirts. 
     Given these two considerations, it is reasonable to roughly compare the 
-    \citet{Patel2013} profile with the one in our lowest stellar mass bin. 
-    The superb resolution of the \textit{HST}/ACS image means that the profiles in
-    \citet{Patel2013} can be measured down to 1 kpc. 
-    The good agreement between our profiles and the ones derived from HST imaging demonstrates that our profiles are robust at $r > 3$ kpc and that we can accurately 
-    measure \minn{}.
+    \citet{Patel2013} profile with the one in our lowest \mtot{} bin. 
+    The superb resolution of the \textit{HST}/ACS image allows \citet{Patel2013} to 
+    accurately measure \mden{} profile down to 1 kpc without worrying the smearing 
+    effect of seeing. 
+    The good agreement between our profiles and the ones derived from HST imaging 
+    demonstrates that our profiles are robust at $r\geq 3$ kpc so that we can 
+    accurately measure \minn{}.
 
@@
 	%can be gathered from the HSC images of these massive galaxies.
-    So far, we have focused only on 1-D \mden{} profiles. We now consider ellipticity and $k$-corrected optical color profiles.
-	We extract ellipticity profiles using \texttt{Ellipse} by leaving the shape of each isophote as a free parameter. We also apply the isophotal information derived in the $i$-band directly to other 
+    So far, we have focused only on 1-D \mden{} profiles. 
+    We now consider ellipticity and $k$-corrected optical color profiles.
+	We extract ellipticity profiles using \texttt{Ellipse} by leaving the shape of 
+	each isophote as a free parameter. 
+	We also apply the isophotal information derived in the $i$-band directly to other 
 	filters and extract 1-D $g-r$ and $g-i$ color profiles.
-We apply the Galactic extinction correction and the \texttt{iSEDFit} $k$-correction  to the color profiles.
-Smearing by the PSF wil l make the central isophotal shape rounder than the
+	We apply the Galactic extinction correction and the \texttt{iSEDFit} $k$-correction 
+	to the color profiles. 
+	Smearing effect of seeing will make the central isophotal shape rounder than the 
 	real value, while seeing differences between filters will bias the central 
 	color\footnote{Since the HSC $i$-band always has better seeing, the central color 
-	will become redder is seeing effects are not accounted for}. On large scales, it is more difficult to extract reliable ellipticity and 
-	color profiles out to 100 kpc: at low surface brightness levels, the isophotal shape 
-	becomes unstable and is easily affected by contamination.
-Color profiles are also more difficult to extract out to large radial scales because  getting the color accurately depends on the background subtraction and the noise levels in both bands.
+	will become redder is seeing effects are not accounted for}. 
+	On large scales, it is more difficult to extract reliable ellipticity and 
+	color profiles out to 100 kpc: at low surface brightness levels, the isophotal 
+	shape becomes unstable and is easily affected by contamination. 
+	Color profiles are also more difficult to extract out to large radial scales
+	because  getting the color accurately depends on the background subtraction and 
+	the noise levels in both bands. 
 	In this paper, we will focus on the median ellipticity and color profiles between 
@@
 	stars in massive galaxies.  
-	The left panel of Fig \ref{fig:ell_color} shows the ellipticity profiles of HSC 
+	The left panel of Fig \ref{fig:ell_color} shows the ellipticity profiles of 
 	massive galaxies and highlights the median profiles for the same three \mtot{} 
-	bins used in Fig \ref{fig:avg_prof}.  Our results are also compared with previous work based on image stacking techniques (the PSF-removed $i$-band results from \citealt{Tal2011},  and
+	bins as used in Fig \ref{fig:avg_prof}.  
+	Our results are also compared with previous work based on image stacking techniques 
+	(the PSF-removed $i$-band results from \citealt{Tal2011}, and
     concentrated galaxies with $11.0<$\logms{}$<11.4$ from \citealt{DSouza2015}).
-	As expected, ellipticity profiles from image stacking methods yield results that are more shallow than when  ellipticities can be measured on a galaxy-by-galaxy basis.
-Uncertainties in how to align galaxies, and the intrinsic isophotal twist can lead to this effect.
-
-	In general, we find that the ellipticities of massive galaxies slowly increase with radius.
+	As expected, ellipticity profiles from image stacking methods yield results that 
+	are more shallow than when ellipticity can be measured on a galaxy-by-galaxy basis.     
+	Uncertainties in how to align galaxies, and the intrinsic isophotal twist can 
+	lead to this effect.
+
+	In general, we find that the ellipticities of massive galaxies slowly increase 
+	with radius. 
 	This trend can even be seen directly "by eye" in HSC images (e.g. 
@@
 	More interestingly, the ellipticity profiles vary with \mtot{}: 
-	at ${\sim} 10$ kpc, the median ellipticity ($< 0.2$) is similar for all three redshift bins,  but the ellipticity of the outer stellar halo increases with galaxy mass.
-Galaxies with  \logms{}$>11.8$ have median ellipticity profiles that become steeper at $>10$ kpc.
-The ellipticity of the outer profiles steadily increases from $e\le 0.2$ to $e{\sim} 0.4$ at 50-60 kpc.
+	at ${\sim} 10$ kpc, the median ellipticity ($< 0.2$) is similar for all three 
+	redshift bins, but the ellipticity of the outer stellar halo increases with 
+	\mtot{}. 
+	Galaxies with \logmtot{}$>11.8$ have median ellipticity profiles that become 
+	steeper at $>10$ kpc. 
+	The ellipticity of the outer profile steadily increases from 
+	$e\le 0.2$ to $e{\sim} 0.4$ at 50-60 kpc.
 
@@
 	Zibetti2005, Spavone2017, Huang2013a, Oh2017}. 
-However,  to the best of our knowledge, our HSC results are the first to show  clear evidence that:  a) the ellipticities of the stellar halo  depend strongly on galaxy mass, and b)  the ellipticity of the stellar halo is anti-correlated with the slope of \mden{}.
+	However, to the best of our knowledge, our HSC results are the first to show 
+	clear evidence that:  
+	a) the ellipticity of stellar halo in massive ETGs depends strongly on 
+	\mstar{}, and 
+	b) the ellipticity of the stellar halo is anti-correlated with the slope of 
+	\mden{}.
 
 	If accreted stars dominate the stellar halos of massive galaxies, this 
-	mass-dependent ellipticity profile may contain clues about the assembly history of massive galaxies (e.g. average time since last merger, 
-	average merger mass ratio).
+	mass-dependent ellipticity profile may contain clues about the assembly history 
+	of massive galaxies (e.g. average time since last merger, average merger 
+	mass ratio).
 	Previous simulations often focused on reproducing the rounder average shape 
@@
 	projected ellipticity profiles and their correlations with the kinematic of 
-	stars and merging history have not been well explored.
+	stars and merging history have not been carefully explored.
 
@@
     \citealt{Hirschmann2015}). 
-    The right panels of Fig \ref{fig:ell_color} show the $k$-corrected $g-r$ and 
-    $g-i$ color profiles for all galaxies in our sample, together with the median profiles in three \mtot{} bins.
-We find the the  median $g-r$ and $g-i$ color  decreases  at larger radii, but there does not appear to be an significant mass dependence in the  gradient of the color profiles.
-We also compare our results with the stacked color profiles from  \citealt{LaBarbera2010}\footnote{We use the median color profiles of high-mass
+    The right panels of Fig \ref{fig:ell_color} show the $k$-corrected $(g-r)$ and 
+    $(g-i)$ color profiles for all galaxies in our sample, together with the median 
+    profiles in three \mtot{} bins. 
+    We find the the median rest-frame $(g-r)$ and $(g-i)$ color decreases at 
+    larger radii, but there does not appear to be an significant \mstar{} dependence 
+    in the gradient of rest-frame optical colors. 
+    We also compare our results with the stacked color profiles from  
+    \citealt{LaBarbera2010}\footnote{We use the median color profiles of high-mass 
     ETGs; the original profile is in units of $R_{\mathrm{e}}$, we use a typical 
@@
     stacked SDSS ones. 
-    Considering differences in the response curves between HSC and SDSS filters, together with the uncertainties of color measurements, the HSC $(g-r)$ color profiles are  in fairly good agreement with  those from SDSS.
+    Considering differences in the response curves between HSC and SDSS filters, 
+    together with the uncertainties of color measurements, the HSC $(g-r)$ color 
+    profiles are in fairly good agreement with those from SDSS. 
     However, the $(g-i)$ profiles of HSC galaxies are steeper compared to SDSS. 
     The SDSS $i$-band suffers from the so-called ``red-halo'' effect
-    (e.g.
-\citealt{Wu2005}, \citealt{Tal2011}).
-This is due to  the fact that the SDSS $i$-band PSF has more prominent wing than other bands.
-Because the PSF model does not capture these wings, this artificially distributes more flux to the outskirts, and leads to apparently redder colors in
-    the low surface brightness outskirts of galaxies. Because HSC uses thick CCDs, HSC $i$-band images do not suffer from this effect and can be used to determine galaxy colors with higher accuracy.
+    (e.g. \citealt{Wu2005}, \citealt{Tal2011}).  
+    This is due to the fact that the SDSS $i$-band PSF has more prominent wing 
+    than other bands. 
+    Because the PSF model does not capture these wings, this artificially distributes 
+    more flux to the outskirts, and leads to apparently redder colors in the low 
+    surface brightness outskirts of galaxies. 
+    Because HSC uses thick CCDs, HSC $i$-band images do not suffer from this effect 
+    and can be used to determine galaxy colors with higher accuracy.
 
@@
     Fairly steep color profiles have been observed in several very nearby massive 
-    ETGs.  Fig \ref{fig:ell_color} shows the $g-r$ color profiles of 
-    NGC 4472 (\citealt{Mihos2013}) and NGC 4365 (\citealt{Mihos2017})\footnote{
+    ETGs.  
+    Fig \ref{fig:ell_color} shows the $g-r$ color profiles of NGC 4472 
+    (\citealt{Mihos2013}) and NGC 4365 (\citealt{Mihos2017})\footnote{
     Both are converted from ($B-V$) colors.}, and the $g-i$ profile of NGC 1399 
-    (\citealt{Iodice2016}). These individual profiles  display  similar color gradients as our HSC sample.
+    (\citealt{Iodice2016}). 
+    These individual profiles display similar color gradients as our HSC sample.
 
@@
 
-    In this paper, we have used  data from the HSC survey that is both simultaneously deep and wide to trace the stellar mass distributions of 
-    $0.3 < z < 0.5$ massive galaxies out to $>100$ kpc and to reveal the mass-dependent nature 
-    of their stellar halos.
-    Here we briefly discuss the scientific implications of our results .
+    In this paper, we have used data from the HSC survey that is both simultaneously 
+    deep and wide to trace the stellar mass distributions of $0.3 < z < 0.5$ massive 
+    galaxies out to $>100$ kpc and to reveal the mass-dependent nature of their 
+    stellar halos.
+    Here we briefly discuss the scientific implications of our results.
 

### 2017-06-30 draft/paper1_rachel.tex
Edit summary

@@
       \caption{
-          \textbf{Left:} Ratio of the fraction of stars between 10 to 100 kpc to the total galaxy mass \mtot{}.
-We adopt this ratio as a proxy for the fraction of ex-situ stars in our sample.
+          \textbf{Left:} Ratio of the fraction of stars between 10 to 100 kpc to the 
+          total galaxy mass \mtot{}. 
+          We adopt this ratio as a proxy for the fraction of ex-situ stars in our 
+          sample. 
           Typical observational uncertainties are shown in the upper left hand corner. 
-The solid grey line shows the predicted relation  derived from the Illustris simulation at $z=0$
-          (Fig 4 in \citealt{RodriguezGomez2016}).
-Grey dashed lines correspond to the predicted 68 percentile of the distribution \alexie{CHECK}.
-\textbf{Right:} comparison between our median \mden{} profiles with the inner component of the structural decomposition of massive elliptical galaxies at $z{\sim} 0$ from \citet[][Cyan, solid]{Huang2013a}.
-\alexie{A phrase about what we learn here}.
-At high redshifts,  the profiles of massive galaxies  should be dominated by  the in-situ component.
-We compare our profiles with the median \mden{} profile of massive galaxies at $1.0 < z < 1.5$ from \textit{HST} observations \citet[][Red, dashed]{Patel2013} and the \mden{} profile of a very massive cD galaxy at $z{\sim} 1.1$ discovered by \citet[][Yellow, dashed]{Liu2013} in the Hubble Ultra-Deep Field.
-\alexie{Always finish with a phrase saying what we learn from this figure.
-Are we going to say something about redshift evolution?
-What is the goal?}.}
+          The solid grey line shows the predicted relation  derived from the Illustris
+          simulation at $z=0$ (Fig 4 in \citealt{RodriguezGomez2016}). 
+          Regions between the grey dashed lines correspond to the range between the 
+          16 and 84 percentile of the distribution. 
+          \textbf{Right:} comparison between our median \mden{} profiles with the 
+          inner component of the structural decomposition of massive elliptical 
+          galaxies at $z<0.02$ from \citet[][Cyan, solid]{Huang2013a}.
+          At higher redshifts, the \mden{} profiles of massive galaxies should be 
+          dominated by the in-situ component. 
+          We compare our profiles with the median \mden{} profile of massive galaxies 
+          at $1.0 < z < 1.5$ from \textit{HST} observations 
+          \citet[][Red, dashed]{Patel2013}. 
+          Both these comparisons suggest that the \mden{} profile within 10 kpc is 
+          dominated by \textit{in situ} stars, but there are already contributions
+          from the accreted stars at very high \mstar{} end. 
+          We also compare with the \mden{} profile of a very massive cD galaxy at
+          $z{\sim} 1.1$ discovered by \citet[][Yellow, dashed]{Liu2013} in the Hubble 
+          Ultra-Deep Field. 
+          It is likely that this object will grow into one of the very massive central
+          galaxy in our sample.
+          It is interesting to see that its \mden{} profile is very similar to the 
+          HSC one of the most massive \mtot{} bin in the inner $\sim 20$ kpc, so the 
+          following growth should mostly happen in the outskirt. 
+          }
       \label{fig:discussion_1}
@@
     \begin{enumerate}
+
         \item We find that the ``total'' \mstar{} of these massive galaxies can be 
@@
             parametric models. 
-            Moreover, the degree to which mass is underestimated depends on \mtot{}.
-Simple model miss more light for massive galaxies because they have more extended enveloppes.
-There is also a \mhalo{}-dependence of this effect and naive luminosity estimates will  miss more light for BCGs is massive halos compared to centrals in less massive halos.
-These effects need to be carefully taken into account when discussing topics such as the evolution of the galaxy SMF.
-        \item We show that the \mden{} profiles of massive galaxies are relatively homogenous  within 10-20 kpc.
-However, there is a large but continuous scatter in outer profiles of massive galaxies.
+            Moreover, the degree to which stellar mass is underestimated depends on 
+            \mtot{}. 
+            Simple model misses more light for massive galaxies because they have 
+            more extended envelopes. 
+            There is also a \mhalo{}-dependence of this effect and naive luminosity
+            estimates will miss more light for BCGs in more massive halos compared 
+            to centrals in less massive halos.
+            These effects need to be carefully taken into account when discussing 
+            topics such as the evolution of the galaxy stellar mass function.
+
+        \item We show that the \mden{} profiles of massive galaxies are relatively
+            homogenous within 10-20 kpc. 
+            However, there is a large but continuous scatter in outer profiles of 
+            massive galaxies. 
             Galaxies with higher \mtot{} show more prominent stellar halos and have 
             shallower outer \mden{} slopes. 
-            Assuming that stellar halos are dominated by accreted stars, this result is consistent with the two-phase formation picture of massive galaxies. 
+            Assuming that stellar halos are dominated by accreted stars, this result 
+            is consistent with the two-phase formation picture of massive galaxies.
+
         \item We show that, on average, massive galaxies have positive ellipticity 
@@
             elongated in the accreted stellar halo. 
-            On the other hand, the average $g-r$ and $g-i$ color gradients do not 
-            show clear dependence on \mtot{} within 10-60 kpc.      
+            On the other hand, the average $(g-r)$ and $(g-i)$ color gradients do 
+            not show clear dependence on \mtot{} within 10-60 kpc.
+
     \end{enumerate}

### 2017-06-30 draft/paper1_rachel.tex
Section sign

@@
     This paper is organized as follows. 
-    Section \ref{sec:data} presents our data and initial sample selection. 
-    Section \ref{sec:ellipse} describes our procedure for extracting 1-D surface 
+    \S~\ref{sec:data} presents our data and initial sample selection. 
+    \S~\ref{sec:ellipse} describes our procedure for extracting 1-D surface 
     brightness profiles. 
-    Section \ref{sec:mstar} describes how we estimate stellar mass.
-    Section \ref{sec:final} summaries the final sample selection procedure. 
-    Our main results are presented in Section \ref{sec:result} and discussed in 
-    Section \ref{sec:discussion}. 
-    Section \ref{sec:summary} presents our summary and conclusions.
+    \S~\ref{sec:mstar} describes how we estimate stellar mass.
+    \S~\ref{sec:final} summaries the final sample selection procedure. 
+    Our main results are presented in \S~\ref{sec:result} and discussed in 
+    \S~\ref{sec:discussion}. 
+    \S~\ref{sec:summary} presents our summary and conclusions.
 
@@
     flag that indicates secure redshifts.
-    Please see Section 4.4.2 of \citet{HSC_DR1} for details of this catalog.  
+    Please see \S~4.4.2 of \citet{HSC_DR1} for details of this catalog.  
     To ensure reasonable \mstar{}-completeness at the high-\mstar{} end we focus on
@@
             $\times R_{\mathrm{e}}$. 
-            We show in Section \ref{ssec:mtotal} that most of the \mstar{} for 
+            We show in \S~\ref{ssec:mtotal} that most of the \mstar{} for 
             these ETGs can be captured by a 100 kpc radius and that \mtot{} is 
@@
     We will further justify this point by measuring their median color profiles in 
-    Section \ref{ssec:ell_color}.
+    \S~\ref{ssec:ell_color}.
 
@@
     mass function and for studies of the environment-dependence of galaxy structure. 
-    These topics will be discussed in Section \ref{sec:discussion}.
+    These topics will be discussed in \S~\ref{sec:discussion}.
 
@@
 
-    Color gradients will be discussed more in Section~\ref{ssec:ell_color}. 
+    Color gradients will be discussed more in \S~\ref{ssec:ell_color}. 
     In summary, our results about the mass-dependence of \mden{} profiles should not 
@@
     %massive galaxies are consistent with the two-phase formation scenario. 
-    We find that the outer halos of massive elliptical galaxies grow more prominent and 
-    more elliptical with increasing stellar mass.
+    We find that the outer halos of massive elliptical galaxies grow more prominent 
+    and more elliptical with increasing stellar mass.
     According to the two-phase formation scenario, the inner 5--10 kpc of these 
@@
 
-    Also according to this picture, the shape of the stellar halo should preserve information
-    about the merging history and possibly even about the shape of the dark matter halo. 
+    Also according to this picture, the shape of the stellar halo should preserve
+    information about the merging history and possibly even about the shape of the 
+    dark matter halo. 
     Simulations show the shape of the stellar and dark matter halos are closely correlated (e.g. \citealt{Wu2014}) for slowly-rotating massive ETGs having undergone multiple 
@@
     background-corrected, contamination-masked images is already described in 
-    Section~\ref{sec:ellipse} briefly. 
+    \S~\ref{sec:ellipse} briefly. 
     In practice, the profile at very low surface brightness level is sensitive to 
@@
 
-    In Section~\ref{ssec:isedfit}, we briefly explain the SED fitting procedure and 
+    In \S~\ref{ssec:isedfit}, we briefly explain the SED fitting procedure and 
     the priors used.   

### 2017-06-30 draft/paper1_rachel.tex
Section discussion

@@
     dark matter halo. 
-    Simulations show the shape of the stellar and dark matter halos are closely correlated (e.g. \citealt{Wu2014}) for slowly-rotating massive ETGs having undergone multiple 
-    minor-mergers. The more elongated outer halo and the trend between the ellipticity profile and 
-    stellar mass may reflect the orbital properties of infalling satellite. 
-    In simulations, satellite orbits become more radial for more massive halos (e.g.
-\citealt{Murante2007, Wetzel2011, Jiang2015}.
-Satellites infalling along radial orbits may  help to form elongated  stellar halos.
+    Simulations show the shape of the stellar and dark matter halos are closely 
+    correlated (e.g. \citealt{Wu2014}) for slowly-rotating massive ETGs having 
+    undergone multiple minor-mergers.
+    The more elongated outer halo and the trend between the ellipticity profile and 
+    stellar mass may reflect the orbital properties of accreted satellite. 
+    In simulations, satellite orbits become more radial for more massive halos 
+    (e.g. \citealt{Murante2007, Wetzel2011, Jiang2015}. 
+    Satellites infalling along radial orbits may help to form elongated stellar 
+    halos. 
     Hence, in principle, these results help explain the trend that we see. 
-However, on contrast, simulation from \citet{Wu2014} predict that more massive
-    galaxies should have \emph{rounder} outskirts which is the opposite trend compared to HSC. This difference warrants further investigation.
-
-    At larger scales, the distribution of satellites galaxies in massive halos is found to  be aligned with the major axis of the central galaxy \alexie{CHECK} (e.g. \citealt{Brainerd2005, 
-    Yang2006b, NiedersteOstholt2010, HuangMandelbaum2016}). This alignement signal is found to be stronger for more massive \alexie{satellites???} galaxies (e.g. \citealt{Hirata2007}).
+    However, in contrast, simulation from \citet{Wu2014} predict that more massive 
+    galaxies should have \emph{rounder} outskirts which is the opposite trend 
+    compared to HSC. 
+    This difference warrants further investigation.
+
+    At larger scales, the distribution of satellites galaxies in massive halos is 
+    found to be aligned with the major axis of the central galaxy 
+    (e.g. \citealt{Brainerd2005, Yang2006b, NiedersteOstholt2010, 
+    HuangMandelbaum2016}). 
+    This alignment signal is found to be stronger for more massive galaxies 
+    (e.g. \citealt{Hirata2007}).
     The fact that more massive central galaxies have steeper ellipticity profiles 
-    and become increasingly more elongated in the outskirt may arise because of such alignements.
-Moreover, the shape of the dark matter halo can be estimated by analyzing satellite distributions and weak lensing profiles (\citealt{ClampittJain2016}).
+    and become increasingly more elongated in the outskirt may arise because of 
+    such alignment. 
+    Moreover, the shape of the dark matter halo can be estimated by analyzing 
+    satellite distributions and weak lensing profiles (\citealt{ClampittJain2016}). 
     It is interesting to point out that the most recent measurement by 
@@
     galaxies into \textit{in situ} and \textit{ex situ} components. 
-    In simulations, the \textit{in situ} component is often defined as the stars formed 
-    in the halo of the ``main progenitor''.  
+    In simulations, the \textit{in situ} component is often defined as the stars 
+    formed in the halo of the ``main progenitor''.  
     The spatial distribution, kinematic, and stellar population properties of both 
     components are important theoretical predictions. 
-Among various predictions,  the faction of  \textit{ex situ} stars and the scaling of the  ex situ fraction with galaxy mass is perhaps the  first aspect to test.
-However, on the observational side, there is no strightforward way to actually disentangle these two components for massive galaxies.
-Disk galaxies  are more easily decomposed into multiple components and recently, deep surveys of nearby disk galaxies have started to provide constraints on their stellar halos \alexie{NEED REFERENCE HERE}.
-
-    For more massive ETGs,  results so far mainly depend on multi-component model fitting
-    and image stacking analyses (e.g. \citealt{Huang2013a, DSouza2014, Spavone2017}).
-    In this work, we propose that \mstar{} computed within different fixed physical apertures are worth exploring as  proxies of the  ex situ fraction.
-We propose to use the mass within 10 kpc (\minn{}) and 100 kpc (\mtot{}) as proxies for the \textit{in situ} component and for the total \mstar{}.
-
-    On the left panel of Fig \ref{fig:discussion_1} we show the relation between \mtot{} and the fraction of mass between 10 and 100 kpc (as a proxy of the mass of the accreted component).
-We compare this with the  fraction of ex-situ stars predicted by the Illustris simulation
-    (\citealt{RodriguezGomez2016}).
-We find that  our proxy for the accreted mass component correlates strongly with  \mtot{} and that this relation is surprisingly consistent with predictions from \citet{RodriguezGomez2016}.
-Given the limitations of the Illustris simulation, and the imperfect nature of our proxy for the ex situ fraction proxy, the almost perfect agreement seen in Figure \ref{fig:discussion_1} may well be a coincidence.
-However, it is encouraging to see that our simple proxy for the fraction of ex situ stars seems to match both the slope and the scatter of the predicted relation.
-There exist other  hydrodynamic simulations that predict significantly different ex situ fractions compared to Illustris (e.g.
-    \citealt{Lackner2012, Qu2017}).
-In future work, we will explore more detailed comparisons between our data and predictions from hydrodynamic simulations and we will  investigate to what degree simple aperture masses may be used to trace \textit{ex situ} fractions.
+    Among various predictions, the faction of \textit{ex situ} stars and the scaling 
+    of the \textit{ex situ} fraction with stellar mass is perhaps the first aspect to 
+    test. 
+    However, on the observational side, there is no straightforward way to actually
+    disentangle these two components for massive galaxies. 
+    Disk galaxies are more easily decomposed into multiple components and recently, 
+    deep surveys of nearby disk galaxies have started to provide constraints on 
+    their stellar halos (e.g. \citealt{Courteau2011, Merritt2016, 
+    Harmsen2017})\footnote{Although it is still not certain that all stellar halos
+    around disk galaxies are made out of \textit{ex situ} stars.}.
+
+    For more massive ETGs, results so far mainly depend on multi-component model 
+    fitting and image stacking analyses (e.g. \citealt{Huang2013a, DSouza2014,
+    Spavone2017}).
+    In this work, we propose that \mstar{} computed within different fixed physical
+    apertures are worth exploring as proxies of the \textit{ex situ} fraction. 
+    We propose to use the mass within 10 kpc (\minn{}) and 100 kpc (\mtot{}) as 
+    proxies for the \textit{in situ} component and for the total \mstar{}.
+
+    On the left panel of Fig \ref{fig:discussion_1} we show the relation between 
+    \mtot{} and the fraction of mass between 10 and 100 kpc (as a proxy of the mass of 
+    the accreted component).
+    We compare this with the fraction of \textit{ex-situ} stars predicted by the 
+    Illustris simulation (\citealt{RodriguezGomez2016}).  
+    We find that our proxy for the accreted mass component correlates strongly with  
+    \mtot{} and that this relation is surprisingly consistent with predictions from
+    \citet{RodriguezGomez2016}.  
+    Given the limitations of the Illustris simulation, and the imperfect nature of 
+    our \textit{ex situ} fraction proxy, the almost perfect agreement seen in 
+    Figure \ref{fig:discussion_1} may well be a coincidence.  
+    However, it is encouraging to see that our simple proxy for the fraction of 
+    \textit{ex situ} stars seems to match both the slope and the scatter of the 
+    predicted relation.  
+    There exists other hydrodynamic simulations that predict significantly different 
+    \textit{ex situ} fractions compared to Illustris (e.g. \citealt{Lackner2012, 
+    Qu2017}). 
+    In future work, we will explore more detailed comparisons between our data and
+    predictions from hydrodynamic simulations and we will investigate to what degree 
+    simple aperture masses may be used to trace \textit{ex situ} fractions.
 
@@
 
-   How well justified is our choice of  \minn{} as a proxy of the  in-situ component?
+   How well justified is our choice of \minn{} as a proxy of the \textit{in-situ} 
+   component?  
    A full investigation is beyond the scope of this paper. 
-Here we simply present a comparison  between our profiles and  a)  several estimates of the in-situ component and b) observations of high redshift massive galaxies that should be dominated by the  \textit{in situ} component.
+   Here we simply present comparisons between our profiles and  
+   a) several estimates of the \textit{in-situ} component and 
+   b) observations of high redshift massive galaxies that should be dominated by 
+   the \textit{in situ} component.  
    In particular, we compare with:
@@
         \item The median \mden{} profiles of massive ETGs at $1.0 < z < 1.5$ from
-            \citealt{Patel2013}. These are considered to be the progenitors of 
+            \citealt{Patel2013}.
+            These are considered to be the progenitors of 
             ${\sim} 10^{11.5} M_{\odot}$ ETGs at $z=0$ and their inner region 
@@
         \item The inner component of $z{\sim} 0$ ellipticals from the 2-D 
-            decomposition of \citet{Huang2013a}. \citet{Huang2013b} showed 
-            that this inner component is structurally similar to the compact ``red nuggets'' at  high-$z$. 
+            decomposition of \citet{Huang2013a}. 
+            \citet{Huang2013b} showed that this inner component is structurally 
+            similar to the compact ``red nuggets'' at high-$z$.
+
         \item The \textit{in situ} components of simulated central galaxies in 
@@
     $z{\sim} 1.1$ (\citealt{Liu2013}).  
-This high redshift galaxy has a \mden{} profile that follows the median profile of our $11.6\leq$\logmtot{}$<11.8$ sample nicely inside 10-15 kpc, but becomes steeper in the outskirt.
-This suggest that the  inner ``core'' of massive BCGs are already in pace at $z{\sim} 1$ while the outer halo is still being assembled.
-
-    These simple comparisons certainly support the idea that \minn{} mainly consists of 
-    \textit{in situ} stars whereas mass at $\mathrm{R} > 15$-20 kpc is dominated by accreted 
-    component.   Meanwhile, this comparison also shows that the \texttt{in situ} component may extend beyond 10 kpc\footnote{We convert these \mden{} profiles to the same 
-    Chabrier IMF; but there are still differences in median \mstar{} and 
-    details in the \m2l{} estimates}.
-Further comparisons with massive galaxies at high redshift and with hydrodynamicl simulations wil help understand which radius is optimal for probing the in situ mass.
+    This high redshift galaxy has a \mden{} profile that follows the median \mden{} 
+    profile of our $11.6\leq$\logmtot{}$<11.8$ sample nicely at $\mathrm{R} < 20$ 
+    kpc, but the profile becomes much steeper in the outskirt. 
+    This suggests that the inner ``core'' of massive BCGs are already in pace at 
+    $z{\sim} 1$ while the outer halo is still being assembled.
+
+    These simple comparisons certainly support the idea that \minn{} mainly consists 
+    of \textit{in situ} stars whereas mass at $\mathrm{R} > 15$-20 kpc is dominated 
+    by \textit{ex situ} component.  
+    Meanwhile, this comparison also shows that the \texttt{in situ} component may 
+    extend beyond 10 kpc\footnote{We convert these \mden{} profiles to the same 
+    \citealt{Chabrier2003} IMF; but there are still differences in median \mstar{} 
+    and details in the \m2l{} estimates}. 
+    Further comparisons with massive galaxies at high redshift and with 
+    hydrodynamical simulations will help understand which radius is optimal for 
+    probing the \textit{in situ} mass.
 

### 2017-06-30 draft/paper1_rachel.tex
ICL disucssion

@@
     the mean matter density ($\bar{\rho}$).
+
+    Finally, we emphasize that in this work, we do not attempt to disentangle the 
+    galaxy light from any ``intra-cluster'' light component (ICL; e.g. 
+    \citealt{Carlberg1997, Lin2004, Gonzalez2005, Mihos2005}). 
+    Although the rising stellar velocity dispersion in the outskirt of massive BCG
+    hints a kinematically separated ICL component (e.g. 
+    \citealt{Dressler1979, Carter1999, Kelson2002, Bender2015, Longobardi2015}),
+    it is extremely difficult to reliably isolate them photometrically.
+    Moreover, both the stellar halo of main galaxy and the ICL component carry 
+    important information regarding the assembly history of central galaxy and its 
+    dark matter halo. 
+    Therefore, we adopt the view that the light of the main galaxy and the 
+    ICL component share a smooth and continuous distribution.
+
+    % In practice, reliable isolation of a physically meaningful ICL component using 
+    % photometry alone is extremely difficult, if not impossible. 
+    % More importantly, the majority of massive galaxies in our samples are not considered 
+    % as the BCG of a cluster (\mhalo{}$\simgt 10^{14}M_{\star}$) \alexie{CHECK}. 
+    % Only a small fraction of the BCGs in the \rbcg{} sample belong to very 
+    % massive clusters where the strongest photometric evidence of an ICL component is 
+    % often found (\mhalo{}$\simgt 10^{15}M_{\star}$, e.g. \citealt{Presotto2014, 
+    % Burke2015}). 
+    % The virgo cluster is a good  local analog of the typical galaxy in our sample.
+
+    % Ultra-deep images show that the stellar halo of the BCG smoothly extends beyond 
+    % 100 kpc, while the ICL only becomes important outside that radius and is dominated 
+    % by many individual tidal features (e.g. \citealt{Mihos2016}).
+    % Therefore, it is highly unlikely that out main results are driven by the ICL 
+    % component.
+
+    % At the imaging depth of HSC and out to 100 kpc, the \mden{} profiles of massive 
+    % galaxies vary smoothly and we find no evidence for a distinctive ICL component. 
+    % Although the rising stellar velocity dispersion in the outskirt of massive BCG
+    % has been used as evidence of a kinematically separated ICL component (e.g. 
+    % \citealt{Dressler1979, Carter1999, Kelson2002, Bender2015, Longobardi2015}), 
+    % we think it is reasonable to treat the stellar halo of BCG and potential ICL as 
+    % an integrated component. 
+    % They both carry important information regarding the assembly of central galaxy 
+    % and its dark matter halo. 
+    % In recent years, we can start to investigate the origin and evolution of ICL using 
+    % simulations where physical separation of ICL is possible
+    % (e.g. \citealt{SommerLarsen2005, Murante2007, Martel2012, Cui2014, Cooper2015, 
+    % Harris2017}). 
+    % It will be interesting to perform detailed comparisons between these simulations 
+    % and deep HSC observations to look into the contributions from different stellar 
+    % components to the halo of massive galaxy.
 
@@
 %% ------------------------------------------------------------------------------------ %% 
-\subsection{Stellar Halo and Intra-cluster Light}
-
-    Finally, we emphasize that in this work, we do not attempt  to  disentangle the galaxy light from any ``intra-cluster'' light component (ICL; e.g. 
-    \citealt{Carlberg1997, Lin2004, Gonzalez2005, Mihos2005}). Instead, we adopt the view that the light of the main galaxy and the 
-    ``intra-cluster''component share a smooth and continuous distribution.
-
-    In practice, reliable isolation of a physically meaningful ICL component using 
-    photometry alone is extremely difficult, if not impossible. 
-    More importantly, the majority of massive galaxies in our samples are not considered 
-    as the BCG of a cluster (\mhalo{}$\simgt 10^{14}M_{\star}$) \alexie{CHECK}. 
-    Only a small fraction of the BCGs in the \rbcg{} sample belong to very 
-    massive clusters where the strongest photometric evidence of an ICL component is 
-    often found (\mhalo{}$\simgt 10^{15}M_{\star}$, e.g. \citealt{Presotto2014, 
-    Burke2015}). The virgo cluster is a good  local analog of the typical galaxy in our sample.
-
-    Ultra-deep images show that the stellar halo of the BCG smoothly extends beyond 
-    100 kpc, while the ICL only becomes important outside that radius and is dominated 
-    by many individual tidal features (e.g. \citealt{Mihos2016}).
-    Therefore, it is highly unlikely that out main results are driven by the ICL component. \alexie{I'm not sure I agree with these statements. What is the ICL anyway?}
-
-    At the imaging depth of HSC and out to 100 kpc, the \mden{} profiles of massive 
-    galaxies vary smoothly and we find no evidence for a distinctive ICL component. 
-    Although the rising stellar velocity dispersion in the outskirt of massive BCG
-    has been used as evidence of a kinematically separated ICL component (e.g. 
-    \citealt{Dressler1979, Carter1999, Kelson2002, Bender2015, Longobardi2015}), 
-    we think it is reasonable to treat the stellar halo of BCG and potential ICL as 
-    an integrated component. 
-    They both carry important information regarding the assembly of central galaxy 
-    and its dark matter halo. 
-    In recent years, we can start to investigate the origin and evolution of ICL using 
-    simulations where physical separation of ICL is possible
-    (e.g. \citealt{SommerLarsen2005, Murante2007, Martel2012, Cui2014, Cooper2015, 
-    Harris2017}). 
-    It will be interesting to perform detailed comparisons between these simulations 
-    and deep HSC observations to look into the contributions from different stellar 
-    components to the halo of massive galaxy.
-
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %% 
 \section{Summary and Conclusions}

### 2017-06-30 draft/paper1_v12.tex
New draft version

--- 2017-06-30 draft/paper1_rachel.tex
@@
 
-    We will now describe our one-dimensional photometric analysis (\S \ref{sec:ellipse}) 
-    and our stellar mass estimates (\S \ref{sec:mstar}). 
+    We will now describe our one-dimensional photometric analysis 
+    (\S \ref{sec:ellipse}) and our stellar mass estimates (\S \ref{sec:mstar}). 
     We will then define the final sample in \S \ref{sec:final}.
@@
     The right panel of Fig \ref{fig:mass_diff} compares \mmax{} and \mtot{}.  
-    Uncertainties in the background subtraction, and the impact of neighbouring objects,
-    means that \mmax{} is much more uncertain than \mtot{}. 
+    Uncertainties in the background subtraction, and the impact of neighbouring 
+    objects, means that \mmax{} is much more uncertain than \mtot{}. 
     Nonetheless, we do see that \mmax{} is larger than than \mtot{}. 
@@
     color gradients at larger radii are not yet well quantified). 
-    Because the gradients are shallow, using an average \m2l{} is unlikely to bias our
-    results on \mstar{} measurements.  
+    Because the gradients are shallow, using an average \m2l{} is unlikely to bias 
+    our results on \mstar{} measurements.  
     In \citet{Huang2016}, the authors conduct multi-band decomposition for a sample 
@@
     separately. 
-    The sum of all components suggest a slightly higher \mstar{} ($0.05-0.10$ dex when
-    typical uncertainty of \mstar{} is 0.12-0.15 dex) and the mass differences show
-    no dependence on \mstar{}.
+    The sum of all components suggest a slightly higher \mstar{} ($0.05-0.10$ dex 
+    when typical uncertainty of \mstar{} is 0.12-0.15 dex) and the mass differences 
+    show no dependence on \mstar{}.
 
@@
 %% ------------------------------------------------------------------------------------ %% 
-\section{A. Basic Statistical Properties of the Sample} 
-	\label{app:basic}
-
-    On the top-left panel of Fig~\ref{fig:sample_stats}, we show the \mtot{}-color 
-    relations using the $k$-corrected $g-r$ color. 
-    Both samples follow the same tight ``red-sequence'' with little contamination 
-    from the ``blue cloud''.
-    At fixed \mtot{}, we see little offset in color distributions of the two 
-    samples, suggesting that both samples consist of quiescent galaxies with 
-    similar average stellar population properties.  
-    This is consistent with previous result that suggests the average stellar 
-    population of massive central galaxy does not depend on \mhalo{} 
-    (e.g.\ \citealt{Park2007}).  
-    In this work, we focus on the \mstar{} range of $11.6 \le$\logmtot{}$\le 11.9$, 
-    where both samples have acceptable completeness, and their \mtot{} distributions 
-    greatly overlap (see the normalized distributions of \mtot{} in the bottom-left 
-    panel of Fig~\ref{fig:sample_stats}). 
-    As for the \minn{} distributions, the two samples overlap the most within 
-    $11.2 \le$\logmtot{}$\le 11.6$, but now they show quite different
-    distributions (bottom-right figure).
-
-    The redshift distributions also show small difference
-    (upper-right panel) even in the high-\mtot{} bin, where the redshift distribution 
-    of the \nbcg{} sample skews toward higher-$z$ end due to the contribution of BOSS 
-    spec-$z$.
-
-%% ------------------------------------------------------------------------------------ %% 
   \begin{figure}
@@
       \caption{
-          \textbf{Top-left}: The \logms{}-$g-r$ color relation of the \rbcg{} 
-          (red circle; detaield format is the same with the right panel of 
-          Fig~\ref{fig:smf1}) and \nbcg{} (grey dots) samples.
-          We apply the $k$-corrections from \texttt{iSEDFit} fitting to the colors.~~          
-          \textbf{Top-right}: the histograms of the redshift for the \rbcg{} and 
-          \nbcg{} galaxies in both \logmtot$>11.2$ and $11.6<$\logmtot{}$<11.9$
-          mass bins.
+          \textbf{Top-left}: The \logmtot{}-$(g-r)$ rest-frame color relation for the 
+          HSC massive galaxies.
+          We $k$-correct the color using the \texttt{iSEDFit} fitting results.
+          Massive galaxies form a ``red-sequence'' on this figure, and there is 
+          little contamination from blue object at high-mass end.~~          
+          \textbf{Top-right}: the redshift distribution of the massive galaxies. 
+          The filled and empty histograms are for the \logmtot{}$>11.6$ and 
+          \logmtot{}$>11.2$ galaxies.
           The vertical lines highlights the $0.3\leq z \leq 0.5$ redshift range.~~
-          \textbf{Bottom-left}: the histograms of \mtot{} for the \rbcg{} (orange-red) 
-          and \nbcg{} (grey-black) samples at both $z>0.2$ (step-filled histogram) and 
-          $0.3 \leq z \leq 0.5$ (stepped histogram). 
-          The vertical lines in both top-left and bottom-left figures highlight the 
-          $11.6<$\logmtot{}$<11.9$ mass range that will be used in the comparison of 
-          the \mtot{}-matched samples.~~
-          \textbf{Bottom-right}: the histograms of \minn{} in similar format. 
-          Here the vertical lines highlight the 
-          $11.2<$\logminn{}$<11.6$ mass range that is used for comparison.
+          \textbf{Bottom-left}: the distributions of \mtot{} of massive galaxies in 
+          this sample. 
+          Filled histogram shows the distribution for $0.3 < z < 0.5$ galaxies 
+          used in this work. 
+          And the empty histogram shows the distribution for the whole $z>0.2$ sample
+          as comparison.~~
+          \textbf{Bottom-right}: the distributions of \minn{} in similar format. 
       }
@@
 %% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %%  
+\section{A. Basic Statistical Properties of the Sample} 
+	\label{app:basic}
+
+    Here we show the basic statistics of the massive galaxies used in this work.
+    On the top-left panel of Fig~\ref{fig:sample_stats}, we show the \mtot{}-color 
+    relation using the $k$-corrected rest-frame $(g-r)$ color. 
+    These massive galaxies form a clear ``red-sequence'' with little contamination 
+    from the ``blue cloud'' at the very high-mass end.
+
+    In the rest of Fig~\ref{fig:sample_stats}, we also show the distributions of 
+    redshift, \mtot{}, and \minn{}.
+    In this work, we focus on the massive galaxies with \logmtot{}$>11.6$ at 
+    $0.3 < z < 0.5$ where the sample is fairly complete in \mtot{}.
+
+    % TODO: Move to Paper II
+    % At fixed \mtot{}, we see little offset in color distributions of the two 
+    % samples, suggesting that both samples consist of quiescent galaxies with 
+    % similar average stellar population properties.  
+    % This is consistent with previous result that suggests the average stellar 
+    % population of massive central galaxy does not depend on \mhalo{} 
+    % (e.g.\ \citealt{Park2007}).  
+    % In this work, we focus on the \mstar{} range of $11.6 \le$\logmtot{}$\le 11.9$, 
+    % where both samples have acceptable completeness, and their \mtot{} distributions 
+    % greatly overlap (see the normalized distributions of \mtot{} in the bottom-left 
+    % panel of Fig~\ref{fig:sample_stats}). 
+    % As for the \minn{} distributions, the two samples overlap the most within 
+    % $11.2 \le$\logmtot{}$\le 11.6$, but now they show quite different
+    % distributions (bottom-right figure).
+
+    % The redshift distributions also show small difference
+    % (upper-right panel) even in the high-\mtot{} bin, where the redshift distribution 
+    % of the \nbcg{} sample skews toward higher-$z$ end due to the contribution of BOSS 
+    % spec-$z$.
 

### 2017-07-01 draft/paper1_v12.tex
Check Hirata2007
Small edits

@@
 % Version 11; MNRAS format; Edited by SH
+% Version 12; MNRAS format; Edited by SH
 
@@
     phase of evolution (the \textit{ex situ} phase) that is dominated by mass assembly via 
-    accretion via mergers.
-    Non-dissipative mergers, especially the minor ones, mostly deposit stars in the 
-    outskirts of centrals and do not have a large impact on the central \mden{} 
+    accretions.
+    Non-dissipative mergers, especially minor mergers\footnote{Normally minor merger
+    means the one with stellar mass ratio smaller than 1:3 or 1:4}, mostly deposit stars
+    in the outskirts of centrals and do not have a large impact on the central \mden{} 
     profile (e.g. \citealt{BoylanKolchin2008, Oogi2013, Bedorf2013}).
@@
     the \mden{} profiles of massive galaxies are similar in the inner region but show
-    larger scatter in the outskirt.
+    a large scatter in the outer region.
 
@@
     halos. 
-    Hence, in principle, these results help explain the trend that we see. 
+    In principle, these results may explain the trend that we see. 
     However, in contrast, simulation from \citet{Wu2014} predict that more massive 
@@
     HuangMandelbaum2016}). 
-    This alignment signal is found to be stronger for more massive galaxies 
-    (e.g. \citealt{Hirata2007}).
+    This alignment signal is found to be stronger for more luminous galaxies 
+    living in more massive halos (e.g. \citealt{Hirata2007}).
     The fact that more massive central galaxies have steeper ellipticity profiles 
@@
     In this work, we propose that \mstar{} computed within different fixed physical
-    apertures are worth exploring as proxies of the \textit{ex situ} fraction. 
+    elliptical apertures are worth exploring as proxies of the \textit{ex situ} 
+    fraction. 
     We propose to use the mass within 10 kpc (\minn{}) and 100 kpc (\mtot{}) as 
@@
     predictions from hydrodynamic simulations and we will investigate to what degree 
-    simple aperture masses may be used to trace \textit{ex situ} fractions.
+    simple elliptical aperture masses may be used to trace \textit{ex situ} fractions.
 
@@
     We also compare with a uniquely massive BCG at high redshift: 
-    a ${\sim} 10^{11.4} M_{\odot}$ BCG with a distinctive ``cD''-like envelope at 
-    $z{\sim} 1.1$ (\citealt{Liu2013}).  
+    a \logms{}${\sim} 10^{11.4} M_{\odot}$ BCG with a distinctive ``cD''-like envelope 
+    at $z{\sim} 1.1$ (\citealt{Liu2013}).  
     This high redshift galaxy has a \mden{} profile that follows the median \mden{} 
@@
             significantly underestimated with shallow imaging data such as SDSS and/or 
-            oversimplified model assumptions (e.g. the \texttt{cModel} or single-\ser{}). 
+            oversimplified model assumptions (e.g. the \texttt{cModel} or single-\ser). 
             In contrast to previous work, our results do not depend on stacking or any 
@@
             galaxies tend to have steeper ellipticity gradients and become more 
-            elongated in the accreted stellar halo. 
+            elongated in stellar halos. 
             On the other hand, the average $(g-r)$ and $(g-i)$ color gradients do 

### 2017-07-01 draft/paper1_v12.tex
Small edits

@@
     \citealt{Carlberg1997, Lin2004, Gonzalez2005, Mihos2005}). 
-    Although the rising stellar velocity dispersion in the outskirt of massive BCG
+    Although the rising stellar velocity dispersion in the outskirt of massive 
+    brightest cluster galaxy (BCG)
     hints a kinematically separated ICL component (e.g. 
@@
     \citet{Patel2013} profile with the one in our lowest \mtot{} bin. 
-    The superb resolution of the \textit{HST}/ACS image allows \citet{Patel2013} to 
+    The superb resolution of the \textit{HST}/ACS images allows \citet{Patel2013} to 
     accurately measure \mden{} profile down to 1 kpc without worrying the smearing 
@@
             decomposition of \citet{Huang2013a}. 
-            \citet{Huang2013b} showed that this inner component is structurally 
+            \citet{Huang2013b} show that this inner component is structurally 
             similar to the compact ``red nuggets'' at high-$z$.
@@
 
-    In this work, we study how the stellar mass density profiles and other structural
-    properties of massive central galaxies depend on their total stellar mass using 
-    deep images from the Subaru HSC survey. 
+    In this work, we study how the projected stellar mass density profiles and other 
+    structural properties of massive central galaxies depend on their total stellar 
+    mass using deep images from the Subaru HSC survey. 
     With the help of this high-quality and wide area data set, we directly map the 

### 2017-07-01 draft/paper2.tex
Author and Acknowledgement

@@
         \newauthor
-        HSC collaboration 
+        Yutaka Komiyama$^{5,8}$
         \\
@@
 
+  % Personal 
+  The authors thank Frank van~den~Bosch for insightful discussions and thank 
+  Shun Saito for helping us estimate the fraction of satellite galaxies in our sample.
+  SH thanks Feng-Shan Liu for sharing the \mden{} profile of the $z\sim1$ BCG from 
+  his work.
+
   % HSC part

### 2017-07-02 draft/paper1_v13.tex
New draft edited by Kevin

--- 2017-07-01 draft/paper1_v12.tex
@@
 % Version 12; MNRAS format; Edited by SH
+% Version 13; MNRAS format; Edited by KB
 
@@
 %% ------------------------------------------------------------------------------------ %% 
-\title[Mass Dependent Stellar Halo in Massive Galaxies]{Tracing the Stellar Halos of 
-	   Massive Galaxies to 100 kpc at $0.3<z<0.5$ using Hyper Suprime-Cam}
+\title[Mass Dependent Stellar Halos in Massive Galaxies]{Individual Stellar Halos of 
+	   Massive Galaxies Measured to 100 kpc at $0.3<z<0.5$ using Hyper Suprime-Cam}
+% \title[Mass Dependent Stellar Halo in Massive Galaxies]{Tracing the Stellar Halos of 
+% 	   Massive Galaxies to 100 kpc at $0.3<z<0.5$ using Hyper Suprime-Cam}
 
@@
 
-    Massive galaxies display extended light profiles that can reach out to several 
+    Massive galaxies display extended light profiles that can reach several 
     hundreds of kilo parsecs. 
-    These stellar halos are a key fossil record of galaxy assembly history. 
+    These stellar halos provide a fossil record of galaxy assembly histories. 
     Using data that is both wide (${\sim}100$ deg$^2$) and deep ($>28.5$ \sb{} in 
     $i$-band), we present a systematic study of the stellar halos of a sample of more 
-    than $7000$ galaxies at $0.3 < z < 0.5$. 
+    than $7000$ galaxies at $0.3 < z < 0.5$ with $log M_{\star}/M_{\odot} > 11.4$. 
     Our study is based on high-quality (0.6\asec\ seeing) imaging data from the Hyper 
-    Suprime-Cam (HSC) Subaru Strategic Program (SSP), which reaches ${\sim}4$ magnitudes 
-    fainter than SDSS and enables us to directly trace mass profiles to 100 kpc 
-    without resorting to stacking. 
-    Shallow images and/or over-simplified parametric models cannot capture the extended 
-    stellar halo and result in underestimated stellar masses.
-    Our extended profiles reveal a number of mass-dependent trends. 
-    The outer parts of our galaxies have higher ellipticity, and this ellipticity increases 
-    with stellar mass, but we find no difference in color gradients with mass. 
-    As in previous work, we see a clear trend towards more extended outer profiles 
-    in more massive galaxies. 
-    Thus, when this extended light is not properly accounted for, the stellar mass 
-    function is systematically underestimated at the highest masses.
-    Our results are broadly consistent with the two phase formation scenario of massive 
-    galaxies in which outer envelopes are built up at late times from series of merging
-    events. 
+    Suprime-Cam (HSC) Subaru Strategic Program (SSP), which enables us to individually 
+    estimate surface mass density profiles to 100 kpc without stacking. 
+    As in previous work, we find that more massive galaxies exhibit more extended outer 
+    profiles.  
+    When this extended light is not properly accounted for as a result of shallow imaging 
+    or inadequate profile modeling, the derived stellar mass function can be 
+    significantly underestimated at the highest masses.  
+    Across our sample, the ellipticity of outer light profiles increases substantially 
+    as we probe larger radii.  
+    We show for the first time that these ellipticity gradients steepen dramatically as 
+    a function of galaxy mass, but we detect no mass-dependence in outer color gradients. 
+    Our results support the two-phase formation scenario for massive galaxies in which 
+    outer envelopes are built up at late times from a series of merging events. 
     We provide surface mass surface mass density profiles in a convenient tabulated format 

### 2017-07-03 draft/paper1_v13.tex
Final edits

@@
         Masayuki Tanaka,$^{5}$
-        Rachel Mandelbaum,$^{7}$
-        Satoshi Miyazaki,$^{5,8}$
+        Satoshi Miyazaki,$^{5,7}$
         \newauthor
-        Yutaka Komiyama$^{5,8}$
+        Yutaka Komiyama$^{5,7}$
         \\
         $^{1}$Kavli-IPMU, The University of Tokyo Institutes for Advanced Study, 
-              the University of Tokyo (Kavli IPMU, WPI), Kashiwa 277--8583, Japan\\
+              the University of Tokyo, Kashiwa 277--8583, Japan\\
         $^{2}$Department of Astronomy and Astrophysics, University of California 
@@
               P.O. Box 23--141, Taipei 10617, Taiwan\\
-        $^{7}$McWilliams Center for Cosmology, Department of Physics, 
-              Carnegie Mellon University, Pittsburgh, PA 15213, USA\\
-        $^{8}$SOKENDAI (The Graduate University for Advanced Studies), Mitaka,
+        $^{7}$SOKENDAI (The Graduate University for Advanced Studies), Mitaka,
               Tokyo, 181--8588, Japan
@@
 
-    Following this initial epoch of early formation, feedback from stars and/or AGN 
+    Following the initial phase of growth, feedback from stars and/or AGN 
     (e.g. \citealt{Sijacki2007, Fabian2012}) efficiently quenches star formation in 
@@
     as dry mergers with other galaxies (e.g. \citealt{Naab2006, Khochfar2006}). 
-    The ``two-phase'' formation of massive galaxies is designed to both explain the 
+    The ``two-phase'' formation of massive galaxies help explain both the 
     observed increase in the effective radii ($R_{\mathrm{e}}$) of massive galaxies 
@@
     halos  (e.g. \citealt{Szomoru2012, Patel2013}). 
-    According to this formation mechanism, minor mergers dominate the mass assembly 
+    It also posits that minor mergers dominate the mass assembly 
     of massive galaxies at late times 
@@
     The deep imaging depth and excellent seeing conditions of HSC images make them 
-    perfect for mapping the \mstar{} distributions of massive galaxies out to very 
+    ideal for mapping the \mstar{} distributions of massive galaxies out to very 
     large radii. 
@@
     In this paper, we use this sample to 
-    (a) reliably measure individual surface mass density (\mden{}) profiles of 
+    (a) reliably estimate individual surface mass density (\mden{}) profiles of 
     massive galaxies out to 100 kpc, 
@@
     \citealt{Carlberg1997, Lin2004, Gonzalez2005, Mihos2005}). 
-    Although the rising stellar velocity dispersion in the outskirt of massive 
+    Although the rising stellar velocity dispersion in the outskirts of massive 
     brightest cluster galaxy (BCG)
-    hints a kinematically separated ICL component (e.g. 
+    hints at a kinematically separated ICL component (e.g. 
     \citealt{Dressler1979, Carter1999, Kelson2002, Bender2015, Longobardi2015}),
@@
     Therefore, we adopt the view that the light of the main galaxy and the 
-    ICL component share a smooth and continuous distribution.
+    ICL component trace different scales of a single, smooth, and continuous 
+    distribution.
 
@@
     statistical studies of the surface brightness profiles of massive galaxies out to 
-    their very outskirts.  
+    their distant outskirts.  
     Fig~\ref{fig:sdss_compare} illustrates the quality of HSC imaging compared to SDSS 
@@
     After fixing the centroids, shape, and other non-amplitude parameters of each 
-    object in this reference catalog, \texttt{hscPipe} perform forced photometry 
+    object in this reference catalog, \texttt{hscPipe} performs forced photometry 
     on the \texttt{coadd} image in each band. 
-    This forced photometry approach is optimized to yield accurate galaxy colors.
+    This forced photometry approach is optimized to yield accurate galaxy colors
+    at $i_{\mathrm{CModel}\leq25.0}$ mag (see \citealt{SynPipe}).
 
@@
     that is similar to SDSS (\citealt{Bosch2017}). 
-    However, as opposed to SDSS, the HSC \cmodel{} is based on forced photometry which 
-    means that it can accurately measure both the \textit{fluxes and colors of galaxies}. 
+    However, as opposed to SDSS, the HSC \cmodel{} is based on forced multi-band 
+    photometry which means that it can accurately measure both the 
+    \textit{fluxes and colors of galaxies}. 
     The HSC \cmodel{} algorithm fits the flux distribution of each object using a 
@@
     GAMA DR2 \citealt{Liske2015}). 
-    The spec-$z$ quality flag from different catalogs are homogenized into a single 
+    The spec-$z$ quality flags from different catalogs are homogenized into a single 
     flag that indicates secure redshifts.
@@
     The accuracy of the red-sequence photo-$z$ is sufficient (median 
-    $|z_{\lambda} - z_{\mathrm{Spec}}| {\sim} 0.01$) for our goal.
+    $|z_{\lambda} - z_{\mathrm{Spec}}| {\sim} 0.01$) for our purpose.
     The \redm{} catalog provides an additional 133 unique redshifts for massive 
@@
     In principle, massive galaxies can still be described by more complex 
-    models (e.g \citealt{Huang2013a, Huang2013b, Oh2017}), but they are still 
+    models (e.g \citealt{Huang2013a, Huang2013b, Oh2017}), but the results are still 
     sensitive to the choice of a particular model (e.g. de~Vaucouleurs or \ser{} 
@@
     sensitive to either the PSF or the background subtraction.
-    We ignore the inner 6.11 kpc, which is twice the size of 1\asec{} seeing at 
+    We ignore the inner $\sim6$ kpc, which is twice the size of 1\asec{} seeing at 
     $z=0.5$.
@@
     within 100 kpc. 
+    This is an empirical, but also conservative choice based on the tests we 
+    conducted on background-corrected postage-stamps. 
+    Once the surrounding objects are appropriately masked out, the extracted 1-D 
+    surface brightness profiles rarely see unphysical truncation or fluctuation 
+    within 100 kpc, especially for the \logmtot{}$>11.6$ galaxies. 
+    Please see Appendix~\ref{app:ellipse} for more details on these tests.
 
@@
     These postage-stamps include all of the light of the galaxy and are also large 
-    enough to also evaluate the background level. We choose to use $i$-band images 
+    enough to evaluate the background level. We choose to use $i$-band images 
     because they trace the stellar mass distributions of massive galaxies at 
@@
     empirical background correction using \texttt{SExtractor}.
-    These procedures are described in details in Appendix~\ref{app:ellipse}. 
+    These procedures are described in detail in Appendix~\ref{app:ellipse}. 
     We should point out that we are not using the photometric results from our 
@@
 
-    For physical (e.g.\ late-stage major merger) and nuisance (e.g.\ nearby foreground 
-    galaxy or bright star) reasons, we cannot extract reliable 1-D profiles for a small 
-    fraction of massive galaxies because they are heavily masked out. 
+    We cannot extract reliable 1-D profiles for a small fraction of massive galaxies 
+    because they are heavily masked out for either physical 
+    (e.g.\ late-stage major merger) or nuisance (e.g.\ nearby foreground 
+    galaxy or bright star) reasons. 
     This is an intrinsic limitation of the 1-D method, and it removes ${\sim}10$\% of 
@@
     We visually examine the 3-color images of randomly selected galaxies with failed 
-    1-D profile.  
+    1-D profiles.  
     Most of them are relative small galaxies that are severely contaminated by nearby 
@@
 
-    Given our exquisite profiles that extend to 100 kpc, the definition and meaning 
+    Given exquisite profiles extending to 100 kpc, the definition and meaning 
     of ``total'' magnitude (and stellar mass) becomes nuanced.
@@
     (\S \ref{sec:mstar}), we integrate the profile to a range of radii, and estimate 
-    the stellar mass within these different apertures.  
+    the stellar mass within these different projected 2-D apertures.  
     Motivated by the two-phase scenario, we will consider two benchmark physical 
@@
             ($R_{\mathrm{e}}$, or 5-10 kpc) of $z{\sim}0$ massive ETGs.
-            We therefore use \minn{} as proxy for the mass forged during the 
+            We therefore use \minn{} as a proxy for the mass formed during the 
             \textit{in situ} phase. 
@@
             $\times R_{\mathrm{e}}$. 
-            We show in \S~\ref{ssec:mtotal} that most of the \mstar{} for 
-            these ETGs can be captured by a 100 kpc radius and that \mtot{} is 
+            We show in \S~\ref{ssec:mtotal} that most of the total \mstar{} for 
+            these ETGs lies within a 100 kpc radius and that \mtot{} is 
             a good proxy for the ``total'' \mstar{}. 
@@
 
-    We should point out that both \minn{} and \mtot{} are measured within the same 
-    elliptical aperture. 
+    We should point out that both \minn{} and \mtot{} are measured after adopting a 
+    isophote with fixed ellipticity and position angle. 
     The 10 kpc and 100 kpc here refer to the radius along the major axis of the 
@@
 
-    We construct five band SEDs using the forced-photometry \cmodel{} magnitudes 
+    We construct five-band SEDs using the forced-photometry \cmodel{} magnitudes 
     corrected for Galactic extinction. 
-    Right now, \cmodel{} only accounts for the statistical error on the flux 
+    Presently, \cmodel{} only accounts for the statistical error on the flux 
     measurement and it certainly underestimates the true flux errors of bright 
@@
     This confirms that, at the current depth of HSC images, \mtot{} can be used as 
-    good proxy of ``total'' stellar mass.
+    a good proxy of ``total'' stellar mass.
 
@@
     Color gradients will be discussed more in \S~\ref{ssec:ell_color}. 
-    In summary, our results about the mass-dependence of \mden{} profiles should not 
+    In summary, our results about the mass dependence of \mden{} profiles should not 
     be affected by the assumption of a constant \m2l{} ratio because optical color 
@@
     generally have $\log (M_{\mathrm{halo}}/M_{\odot}) \geq 14.0$, although the scatter 
-    of \mhalo{} at fixed $\lambda$ can not be ignored.
+    of \mhalo{} at fixed $\lambda$ cannot be ignored.
     Therefore the central galaxies of these \redm{} clusters\footnote{We only use 
@@
 
-    As the next step, we want to construct a sample of central galaxies living in halos 
+    As a next step, we want to construct a sample of central galaxies living in halos 
     with \logmh{}$<14.0$. 
@@
     around all \redm{} clusters. 
-    We use a radius equal to $R_{\mathrm{200b}}$ and the thickness of the cylinder is 
+    We use a radius equal to $R_{\mathrm{200b}}$ and the length of the cylinder is 
     set to twice the value of the photometric redshift uncertainty of each cluster.
@@
     This confirms that our sample should have low enough satellite contamination 
-    so that it can be taken as a sample of massive central galaxy.     
+    so that it can be taken as representative massive central galaxies.     
     %% Saved as "dr1_nonbcg_use_sed5b.fits"
@@
     (Huang \etal in prep.).  
-    For this paper, we only consider the halo mass dependence on our sample when we 
-    evaluate impact of mass estimates on the SMF in \S \ref{ssec:smf}. 
+    For the present paper, we only consider the halo mass dependence on our sample when 
+    we evaluate impact of mass estimates on the SMF in \S \ref{ssec:smf}. 
     We show the distributions of redshift, \mtot{} and \minn{} of the massive galaxy 
@@
     Our volume density distributions (will be referred to as SMF for simplicity) 
-    turn over at low-mass end where the sample becomes incomplete, and we do not attempt
-    to apply any completeness correction here.
+    turn over at the low-mass end where the sample becomes incomplete, and we do not 
+    attempt to apply any completeness correction here.
 
@@
     resampling method. 
-    And it is worth pointing out again that our sample is not complete in the lowest 
-    \mtot{} bin, although there is no reason to believe the median \mden{} profile
-    will be significantly affected. 
+    Note that our sample is not complete in the lowest \mtot{} bin, althaough the 
+    median \mden{} profile may not be significantly affected. 
     As shown in the left panel of Fig~\ref{fig:avg_prof}, we can comfortably trace
@@
 
-    Most previous studies have often focused on surface brightness profiles instead 
+    Most previous studies have focused on surface brightness profiles instead 
     of mass density profiles.  
@@
     These profiles are also available  
-    \href{https://github.com/dr-guangtou/hsc_redbcg/tree/master/profiles}{here}:
-    {\url{https://github.com/dr_guangtou/hsc_redbcg/tree/master/profiles/}}.
+    \href{http://www.ucolick.org/\~kbundy/massivegalaxies}{here}:
+    {\url{http://www.ucolick.org/\~kbundy/massivegalaxies}}. (The files will be made 
+    available after the paper is accepted)
 
@@
 	%can be gathered from the HSC images of these massive galaxies.
-    So far, we have focused only on 1-D \mden{} profiles. 
+    So far, we have focused on 1-D \mden{} profiles. 
     We now consider ellipticity and $k$-corrected optical color profiles.
@@
 	a) the ellipticity of stellar halo in massive ETGs depends strongly on 
-	\mstar{}, and 
-	b) the ellipticity of the stellar halo is anti-correlated with the slope of 
-	\mden{}.
+	\mtot{}, and 
+	b) the ellipticity of stellar halo also relates to the slope of the \mden{}
+	profile (see Fig~\ref{fig:avg_prof} and Fig~\ref{fig:ell_color}; 
+	we will discuss this more in Paper II).
 
@@
     We find the the median rest-frame $(g-r)$ and $(g-i)$ color decreases at 
-    larger radii, but there does not appear to be an significant \mstar{} dependence 
+    larger radii, but there does not appear to be a significant \mstar{} dependence 
     in the gradient of rest-frame optical colors. 
@@
             homogenous within 10-20 kpc. 
-            However, there is a large but continuous scatter in outer profiles of 
-            massive galaxies. 
+            However, there is large scatter in outer profiles of massive galaxies. 
             Galaxies with higher \mtot{} show more prominent stellar halos and have 
@@
   % Personal 
-  The authors thank Frank van~den~Bosch for insightful discussions and thank 
-  Shun Saito for helping us estimate the fraction of satellite galaxies in our sample.
-  SH thanks Feng-Shan Liu for sharing the \mden{} profile of the $z\sim1$ BCG from 
+  The authors thank Rachel Mandelbaum and Frank van~den~Bosch for insightful 
+  discussions and comments; 
+  thank Shun Saito for helping us estimate the fraction of satellite 
+  galaxies in our sample;
+  thank Feng-Shan Liu for sharing the \mden{} profile of the $z\sim1$ BCG from 
   his work.

### 2017-07-10 draft/paper2.tex
Figure 1

@@
 
-%%%%%%%%%%%%: Title and Affiliations %%%%%%%%%%%%
-
-%% ------------------------------------------------------------------------------------ %% 
-\title[Structure and Environment of Massive Galaxies]{A Detection of the Environmental 
-       Dependence of the Stellar Profiles and Halos of Massive Central Galaxies}
+%% ------------------------------------------------------------------------------------ %% 
+%% Title and Affiliations 
+%% ------------------------------------------------------------------------------------ %%
+
+\title[Structure and Environment of Massive Galaxies]{
+       A Detection of the Environmental Dependence of the Stellar Profiles and Halos
+       of Massive Central Galaxies}
 
@@
 
-%%%%%%%%%%%%: Header and Version %%%%%%%%%%%%
+%% ------------------------------------------------------------------------------------ %% 
+%% Header and Version 
+%% ------------------------------------------------------------------------------------ %%
+
 \begin{document}
@@
 
-%%%%%%%%%%%%: Abstract and Keywords %%%%%%%%%%%%
+%% ------------------------------------------------------------------------------------ %% 
+%% Abstract and Keywords 
+%% ------------------------------------------------------------------------------------ %%
 
@@
 
-%%%%%%%%%%%%: Main Text %%%%%%%%%%%%
+%% ------------------------------------------------------------------------------------ %% 
+%% Main Text
+%% ------------------------------------------------------------------------------------ %%
 
@@
           Three-color images for a subsample of massive galaxies at $z{\sim}0.4$. 
-          All of these galaxies have the same mass within a 10 kpc aperture 
+          All of these massive galaxies have very similar \mstar{} within a 10 kpc 
+          elliptical aperture 
           ($11.2<\log (M_{\star,10\ \mathrm{kpc}}/M_{\odot})<11.3$). 
-          The dash-line circle at the top-left figure indicates 10 kpc.
-          Galaxies are rank-ordered from top to bottom and from left to right by 
-          their \mstar{} within a 100 kpc aperture which varies from $10^{11.2} M_{\odot}$ 
-          to $10^{11.7} M_{\odot}$. 
-          At fixed ``inner'' mass ($M_{\star,10}$), massive galaxies display significant
+          The dash-line circle at the top-left figure indicates $R=$10 kpc.
+          These galaxies are rank-ordered from top to bottom and from left to right 
+          by their \mstar{} within a 100 kpc elliptical aperture which varies 
+          from $10^{11.2} M_{\odot}$ to $10^{11.7} M_{\odot}$. 
+          At fixed ``inner'' mass (\minn{}), massive galaxies display significant
           diversity in their outer profiles. 
-          Red boxes indicate galaxies in halos more massive than 
-          ${\sim} 10^{14.0} M_{\odot}$. 
+          Red boxes indicate galaxies from dark matter haloes that are more massive 
+          than ${\sim} 10^{14.0} M_{\odot}$. 
           }
@@
 %% ------------------------------------------------------------------------------------ %% 
+%% Introduction 
+%% ------------------------------------------------------------------------------------ %%
+
 \section{Introduction}

### 2017-07-10 draft/paper2.tex
Introduction edits I

@@
 
-    \jenny{Here is a suggested shorter introduction.}   
-    One of the most intriguing observations of high-redshift galaxies from the last decade has 
-    been the dramatic size growth in massive quiescent galaxies 
-    \citep{Trujillo2006,vanDokkum2008,Damjanov2009,Cimatti2008} of factors of $2-4$ from $z \approx 2$ to the present. 
-    These observations have led to a two-phase picture of galaxy growth,
-    in which galaxies dissipatively form a central compact region and then their envelope grows around 
-    them via dry merging \citep[e.g,][]{Naab2006, Khochfar2006,Oser2010, Oser2012}, which allows for 
-    dramatic growth at late times. 
-    There is likely also a contribution from progenitor bias, in which larger galaxies become quiescent 
-    later \citep[e.g.,][]{Newman2012,XX}.
-
-	There have been a number of papers testing the two-phase picture observationally at low redshift, 
-    looking at the light profiles \citep{Huang2013a,Huang2013b,Oh2017}, color gradients (), 
-    and stellar population gradients \citep[e.g.,][]{}. The observations are generically consistent with the 
-    two-phase model. However, to really test this picture requires highly sensitive observations extending 
-    beyond 10 kpc to truly probe the material accreted at late times \citep[Illustris paper here?][]{}. The surface 
-    brightness falls rapidly in the outer parts of elliptical galaxies, making such observations very challenging. In 
-    \citet[][; Paper I hereafter]{Huanetal2017}, we showed that the Hyper-Suprime Camera Survey {\bf CITE} allows us 
-    to derive robust surface brightness profiles for {\it individual} galaxies out to 100 kpc.
-
-    In Paper I, we exploited this sensitivity to verify that the fraction of accreted mass residing in an extended
-    envelope is a function of the mass of the galaxy. Another unexplored issue is the extent to which, at fixed stellar 
-    mass, the accreted fraction depends on the surrounding halo mass. According to this two-phase formation 
-    scenario, the late time growth of massive ETGs is intrinsically tied to the growth of their host dark matter halos 
+    One of the most intriguing observations of high-redshift galaxies from the last 
+    decade has been the dramatic structural transformation in massive quiescent 
+    galaxies \citep[e.g.][]{Trujillo2006, vanDokkum2008, Cimatti2008, Damjanov2009, 
+    vanderWel2011, Szomoru2012, Patel2013} from $z \approx 2$ to the present. 
+    These observations suggest that the progenitors of $z{\sim} 0$ massive early-type 
+    galaxies (ETGs) need to increase their effective radius ($R_{\rm e}$) by factor 
+    of 2--4 in the last 10 Gyrs (e.g. \citealt{Newman2012, vdWel2014}).
+    They have led to a ``two-phase'' scenario for the formation of massive ETGs 
+    (e.g. \citealt{Oser2010, Oser2012}),
+    in which galaxies form a compact central region through highly dissipative 
+    processes (e.g. gas-rich merger or cold gas-accretion; 
+    \citealt{Hopkins2008, Dekel2009}) and then assemble their extended stellar 
+    haloes via dry mergers 
+    \citep[e.g,][]{Naab2006, Khochfar2006, Oser2010, Oser2012}, which allows for 
+    significant growth at late times. 
+    Meanwhile, progenitor bias, which proposes that larger ETGs were quenched more 
+    recently, could also contribute to the apparent size growth, although its 
+    important is under argument (e.g. \citealt{Newman2012, Carollo2013, 
+    Poggianti2013, Belli2015, Keating2015, Fagioli2016}).
+
+    Several previous works have tested the two-phase formation scenario 
+    observationally using galaxies at low redshift, looking at their surface 
+    brightness of mass density profiles (e.g. \citealt{Huang2013a, Huang2013b, 
+    Oh2017}, optical color gradients (e.g. \citealt{LaBarbera2010, LaBarbera2012}), 
+    and stellar population gradients \citep[e.g.,][]{Coccato2010, Coccato2011, 
+    Greene2015, Barbosa2016}. 
+    These observations are generally consistent with the two-phase scenario, 
+    but this picture still face many challenges.
+    One of the most outstanding issues is the extent to which, at fixed stellar mass, 
+    the accreted fraction depends on the surrounding dark matter halo mass.
+
+    According to this two-phase formation scenario, the late time growth of massive 
+    ETGs is intrinsically tied to the growth of their host dark matter halos 
     (e.g. \citealt{Leauthaud2012, Behroozi2013, Shankar2013}). 
     Massive ETGs that live at the center of more massive halos should experience 
-    a different mass assembly history and should be subject to a larger merger rate 
-    compared to ETGs that live in smaller dark matter halos. 
-    A natural prediction of the two-phase formation scenario is therefore that the 
-    structural properties of massive galaxies should depend on their ``environment''. In this paper, we use our 
-    large sample of early-type galaxies, along with halo masses from RedMapper \citep{}, to explore how the mass in
-    extended stellar envelopes depends on halo mass. 
-    Paper proceeds as follows: XXX.
-
-    \song{This is the old version, needs work}
-    Massive galaxies are unique laboratories for studying both cosmology and galaxy 
-    formation. 
-    Simulations of structure formation within the context of the $\Lambda$-CDM 
-    cosmological model make predictions for the hierarchical growth of dark matter halos 
-    and galaxies (e.g. \citealt{Baugh1996, DeLucia2006}), but there are many open 
-    questions regarding the star-formation history, mass assembly process, and 
-    structural evolution of massive galaxies. 
-    Massive galaxies are thought to grow according to a ``two-phase'' formation scenario 
-    (e.g. \citealt{Oser2010, Oser2012}). 
-    In this scenario, the progenitors of $z{\sim} 0$ massive early-type galaxies (ETGs) 
-    undergo a rapid growth phase at $z{\sim} 2$ triggered either by disk instabilities 
-    or gas rich mergers (e.g. \citealt{Hopkins2008, Dekel2009}). 
-    Observationally, the progenitors of ETGs are thought to correspond to the so-called 
-    ``red nuggets'' (e.g. \citealt{Damjanov2009}) which have smaller effective radii 
-    ($R_{\mathrm{e}}$; e.g. \citealt{Trujillo2006, vanDokkum2008, Cimatti2008}), 
-    slightly higher central velocity dispersion and stellar mass density 
-    (\mden{}; e.g. \citealt{vandeSande2011, Belli2014}), more disk-like morphologies 
-    (e.g. \citealt{vanderWel2011}) than their local descendants 
-    (e.g. \citealt{Bezanson2009, vanDokkum2010}).
-
-    Following an initial epoch of early formation, feedback from stars and/or AGN 
-    (e.g. \citealt{Sijacki2007, Fabian2012}) efficiently quench star formation in 
-    massive galaxies and a large fraction of these massive progenitors become quiescent 
-    at $z>1$ (e.g. \citealt{Bezanson2009, Kriek2016}). 
-    The second phase in the ``two-phase'' formation scenario is driven by 
-    non-dissipative processes such as dry mergers with other galaxies 
-    (e.g. \citealt{Naab2006, Khochfar2006}). 
-    According to the ``two-phase'' scenario, minor mergers drive the growth of massive 
-    galaxies at late times and can help explain the significant increase
-    of $R_{\mathrm{e}}$ (e.g. \citealt{Newman2012, vdWel2014}) as well as the build-up 
-    of the outer stellar halos of ETGs (e.g.  \citealt{Szomoru2012, Patel2013}).
-
-    {\bf PP here about mass dependence: in the simulations, a larger fraction of the mass 
-    is ex-situ at increasingly higher mass. Can we see evidence for that observationally by 
-    looking at light profiles?}
-
-    In addition, according to this two-phase formation scenario, the late time growth of massive ETGs 
-    is intrinsically tied to the growth of their host dark matter halos 
-    (e.g. \citealt{Leauthaud2012, Behroozi2013, Shankar2013}). 
-    Massive ETGs that live at the center of more massive halos should experience 
-    a different mass assembly history and should be subject to a larger merger rate 
-    compared to ETGs that live in smaller dark matter halos. 
-    A natural prediction of the two-phase formation scenario is therefore that the 
-    structural properties of massive galaxies should depend on their ``environment''
-
-    In order to truly understand the build-up of the outer parts of massive galaxies, very 
-    deep data are needed. Massive ETGs have very steep inner stellar density profiles, 
-    extremely extended stellar envelopes, and radial-dependent isophotal shapes which 
-    make accurate measurements of \mstar{} and $R_{\mathrm{e}}$ very challenging
-    (e.g. \citealt{Bernardi2013, DSouza2014}), 
-    especially in the presence of shallow imaging data such as the Sloan Digital Sky 
-    Survey (SDSS; e.g. \citealt{SDSSDR7, SDSSDR12}).
-
-    In this paper, we take advantage of new high-resolution (median 
-    FWHM${\sim} 0.6^{\arcsec}$ in $i$-band) and deep ($i$-band surface brightness 
-    limit $> 28.5$\sb) imaging from the Hyper-Suprime Cam (HSC) Subaru Strategic 
-    Program \citep[SSP,][]{HSCDR1} to characterize the outer parts of massive galaxies 
-    as a function of their properties. Here we will focus on (a) showing that we can 
-    measure profiles for galaxies out to 100 kpc reliably with the HSC data and (b) looking at 
-    trends in stellar mass and outer envelope properties. In a second paper in this series, we 
-    will directly show the environmental dependence of the outer envelope mass.
-    %The goal of this paper is to compare the \mden{} profiles and structural scaling 
-    %relations of massive central galaxies in both low and high mass dark matter halos. 
-    %Fig~\ref{fig:sdss_compare} displays a comparison of the imaging quality of massive 
-    %ETGs using SDSS versus using the new HSC data. 
-    The deep imaging depth and excellent seeing conditions of HSC images make them 
-    perfect for mapping the \mstar{} distributions of massive galaxies out to very 
-    large radii. 
-    With the help of the \redm{} cluster catalog (e.g.\ \citealt{Rykoff2014}; 
-    \citealt{Rozo2015b}; please see Section~\ref{ssec:redmapper} for details), we 
-    select a large sample (${\sim} 15000$) of massive central 
-    galaxies with $0.3 < z < 0.5$ using ${\sim} 100$ square degree of data from the 
-    HSC wide layer.
+    different assembly and should be subject to higher merger rate compared to 
+    ETGs with similar \mstar{} that live in less massive dark matter halos. 
+    A natural prediction of this picture is therefore that the structures of 
+    massive ETGs should depend on their ``environment''\footnote{There are 
+    different definitions of ``environment'' in the literature.  
+    In this work, we use ``environment'' and halo mass interchangeably.}.
+    For instance, models based on two-phase scenario predict that the well-know 
+    stellar mass--effective radius relation for ETGs (\mstar{}--$R_{\rm e}$ relation; 
+    e.g., \citealt{Shen2003, Guo2009}) should show environmental dependence: the 
+    $R_{\rm e}$ of massive ETGs in more massive halos should be larger than those 
+    in less massive halos at fixed \mstar{} 
+    (e.g. \citealt{Shankar2013, Shankar2014}).
+    Yet, solid evidence of this effect at low redshift is still missing 
+    (e.g. \citealt{Nair2010, HCompany13}; but also see \citealt{Yoon2017}).
+
+    %However, while hints of an environmental dependence in the mass-size relation have 
+    %been spotted at high-$z$ (e.g. \citealt{Papovich2012, Lani2013, Delaye2014}; but 
+    %also see \citealt{Rettura2010}).
+
+	% Song: Actually the Illustris paper suggests that, for massive galaxies, 
+	%       even the inner region is dominated by accreted stars.
+
+    To seriously test the environmental dependence of structure in massive ETGs 
+    requires highly sensitive observations extending beyond the inner region of these 
+    galaxies to truly probe the material accreted at late times. 
+    This is very challenging observation as the surface brightness drops rapidly 
+    with radius in massive ETGs.
+
+    In \citet[][; Paper I hereafter]{hscMassiveI}, we showed that the deep, 
+    multi-band images from the Subaru Strategic Program (SSP; \citealt{HSC_SSP,
+    HSC_DR1}) using Hyper Suprime-Cam (HSC; \citealt{Miyazaki2012}, 
+    Miyazaki in~prep.) allows us to extract robust surface stellar
+    mass density (\mden{}) profiles for {\it individual} massive galaxies 
+    at $0.3 < z < 0.5$ out to 100 kpc. 
+    In Paper I, we exploited this sensitivity to show that the \mden{} profiles 
+    and the shapes of the stellar halos of massive ETGs has a clear \mstar{} 
+    dependence. 
+    And the fraction of accreted stars residing in the extended envelope increases
+    with the total \mstar{} of the galaxy.
+
+    In this paper, we explore how the extended stellar halo in massive central galaxies
+    depends on dark matter halo mass with the help of HSC images of a large sample 
+    of massive ETGs and the \redm{} cluster catalog (e.g.\ \citealt{Rykoff2014}; 
+    \citealt{Rozo2015b}; please see Section~\ref{ssec:redmapper} for details)
+
+%% ------------------------------------------------------------------------------------ %%
 
@@
     and ${\Omega}_{\rm \Lambda}=0.7$.
-    Stellar mass is noted \mstar{} and has been derived using a Chabrier Initial Mass 
+    Stellar mass is denoted \mstar{} and has been derived using a Chabrier Initial Mass 
     Function (IMF; \citealt{Chabrier2003}).
-    $M_{\mathrm{halo}}$ denotes halo mass in general whereas $M_{\rm 200b}$ is 
-    explicitly defined as $M_{\rm 200b}\equiv M(<r_{\rm 200b})=200\bar{\rho} 
+
+    Halo mass is defined as $M_{\rm 200b}$ as 
+    $M_{\rm 200b}\equiv M(<r_{\rm 200b})=200\bar{\rho} 
     \frac{4}{3}\pi r_{\rm 200b}^3$ where $r_{\rm 200b}$
@@
 
-    %Previous work has shown that the half-light radii of massive ETGs is tightly 
-    %correlated with \mstar{} (e.g. \citealt{Shen2003, Guo2009}). 
-    %Models based on the ``two-phase'' formation scenario naturally predict that this 
-    %mass--size relation should exhibit an environmental dependence: the effective radii 
-    %of massive ETGs in more massive halos should be larger than those in less massive
-    %halos at fixed \mstar{} (e.g. \citealt{Shankar2013, Shankar2014}).
-
-    %However, while hints of an environmental dependence in the mass-size relation have 
-    %been spotted at high-$z$ (e.g. \citealt{Papovich2012, Lani2013, Delaye2014}; but 
-    %also see \citealt{Rettura2010}), there is no solid evidence for this effect at 
-    %low-$z$ (e.g. \citealt{Nair2010, HCompany13}; but also see \citealt{Yoon2017}). 
-    %The absence of an environmental dependence in the mass-size relation is an 
-    %outstanding challenge to the two-phase formation scenario of ETGs.
-
     \song{These paragraphs are from Jenny's txt file, need organization.}

### 2017-07-10 draft/paper2.tex
Introduction edits 2

@@
 %% ------------------------------------------------------------------------------------ %% 
+%% Introduction 
+%% ------------------------------------------------------------------------------------ %%
+
+\section{Introduction}
+    \label{sec:intro}
+
+    One of the most intriguing observations of high-redshift galaxies from the last 
+    decade has been the dramatic structural transformation in massive quiescent 
+    galaxies \citep[e.g.][]{Trujillo2006, vanDokkum2008, Cimatti2008, Damjanov2009, 
+    vanderWel2011, Szomoru2012, Patel2013} from $z \approx 2$ to the present. 
+    These observations suggest that the progenitors of $z{\sim} 0$ massive early-type 
+    galaxies (ETGs) need to increase their effective radius ($R_{\rm e}$) by factor 
+    of 2--4 in the last 10 Gyrs (e.g. \citealt{Newman2012, vdWel2014}).
+    They have led to a ``two-phase'' scenario for the formation of massive ETGs 
+    (e.g. \citealt{Oser2010, Oser2012}),
+    in which galaxies form a compact central region through highly dissipative 
+    processes (e.g. gas-rich merger or cold gas-accretion; 
+    \citealt{Hopkins2008, Dekel2009}) and then assemble their extended stellar 
+    haloes via dry mergers 
+    \citep[e.g,][]{Naab2006, Khochfar2006, Oser2010, Oser2012}, which allows for 
+    significant growth at late times. 
+    Meanwhile, progenitor bias, which proposes that larger ETGs were quenched more 
+    recently, could also contribute to the apparent size growth, although its 
+    important is under argument (e.g. \citealt{Newman2012, Carollo2013, 
+    Poggianti2013, Belli2015, Keating2015, Fagioli2016}).
+
+    Several previous works have tested the two-phase formation scenario 
+    observationally using galaxies at low redshift, looking at their surface 
+    brightness of mass density profiles (e.g. \citealt{Huang2013a, Huang2013b, 
+    Oh2017}, optical color gradients (e.g. \citealt{LaBarbera2010, LaBarbera2012}), 
+    and stellar population gradients \citep[e.g.,][]{Coccato2010, Coccato2011, 
+    Greene2015, Barbosa2016}. 
+    These observations are generally consistent with the two-phase scenario, 
+    but this picture still face many challenges.
+    One of the most outstanding issues is the extent to which, at fixed stellar mass, 
+    the accreted fraction depends on the surrounding dark matter halo mass.
+
+    According to this two-phase formation scenario, the late time growth of massive 
+    ETGs is intrinsically tied to the growth of their host dark matter halos 
+    (e.g. \citealt{Leauthaud2012, Behroozi2013, Shankar2013}). 
+    Massive ETGs that live at the center of more massive halos should experience 
+    different assembly and should be subject to higher merger rate compared to 
+    ETGs with similar \mstar{} that live in less massive dark matter halos. 
+    A natural prediction of this picture is therefore that the structures of 
+    massive ETGs should depend on their ``environment''\footnote{There are 
+    different definitions of ``environment'' in the literature.  
+    In this work, we use ``environment'' and halo mass interchangeably.}.
+    For instance, models based on two-phase scenario predict that the well-know 
+    stellar mass--effective radius relation for ETGs (\mstar{}--$R_{\rm e}$ relation; 
+    e.g., \citealt{Shen2003, Guo2009}) should show environmental dependence: the 
+    $R_{\rm e}$ of massive ETGs in more massive halos should be larger than those 
+    in less massive halos at fixed \mstar{} 
+    (e.g. \citealt{Shankar2013, Shankar2014}).
+    Yet, solid evidence of this effect at low redshift is still missing 
+    (e.g. \citealt{Nair2010, HCompany13}; but also see \citealt{Yoon2017}).
+
+    %However, while hints of an environmental dependence in the mass-size relation have 
+    %been spotted at high-$z$ (e.g. \citealt{Papovich2012, Lani2013, Delaye2014}; but 
+    %also see \citealt{Rettura2010}).
+
+	% Song: Actually the Illustris paper suggests that, for massive galaxies, 
+	%       even the inner region is dominated by accreted stars.
+
+    To seriously test the environmental dependence of structure in massive ETGs 
+    requires highly sensitive observations extending beyond the inner region of these 
+    galaxies to truly probe the material accreted at late times. 
+    This is very challenging observation as the surface brightness drops rapidly 
+    with radius in massive ETGs.
+
+    In \citet[][Paper I hereafter]{hscMassiveI}, we showed that the deep, 
+    multi-band images from the Subaru Strategic Program (SSP; \citealt{HSC-SSP,
+    HSC-DR1}) using Hyper Suprime-Cam (HSC; \citealt{Miyazaki2012}, 
+    Miyazaki in~prep.) allows us to extract robust surface stellar
+    mass density (\mden{}) profiles for {\it individual} massive galaxies 
+    at $0.3 < z < 0.5$ out to 100 kpc. 
+    In Paper I, we exploited this sensitivity to show that the \mden{} profiles 
+    and the shapes of the stellar halos of massive ETGs has a clear \mstar{} 
+    dependence. 
+    And the fraction of accreted stars residing in the extended envelope increases
+    with the total \mstar{} of the galaxy.
+
+    In this paper, we explore how the extended stellar halo in massive central galaxies
+    depends on dark matter halo mass with the help of HSC images of a large sample 
+    of massive ETGs and the \redm{} cluster catalog (e.g.\ \citealt{Rykoff2014}; 
+    \citealt{Rozo2015b}; please see \S \ref{sec:data} for details)
+
+    This paper is organized as follows. 
+    \S \ref{sec:data} briefly introduce the sample selection and data reduction 
+    processes.  
+    Please refer to \citet{hscMassiveI} for more technical details.
+    Our main results are presented in \S \ref{sec:result} and discussed in 
+    \S \ref{sec:discussion}. 
+    \S \ref{sec:summary} presents our summary and conclusions.
+
+    Magnitudes use the AB system (\citealt{Oke1983}), and are corrected for Galactic 
+    extinction using calibrations from \citet{Schlafly11}.
+    In this work, we assume $H_0$ = 70~km~s$^{-1}$ Mpc$^{-1}$, ${\Omega}_{\rm m}=0.3$, 
+    and ${\Omega}_{\rm \Lambda}=0.7$.
+    Stellar mass is denoted \mstar{} and has been derived using a Chabrier Initial Mass 
+    Function (IMF; \citealt{Chabrier2003}).
+
+    Halo mass is defined as $M_{\rm 200b}$ as 
+    $M_{\rm 200b}\equiv M(<r_{\rm 200b})=200\bar{\rho} 
+    \frac{4}{3}\pi r_{\rm 200b}^3$ where $r_{\rm 200b}$
+    is the radius at which the mean interior density is equal to 200 times
+    the mean matter density ($\bar{\rho}$).
+
+    As in \citet{hscMassiveI}, we do not try to separate any potential ``intra-cluster''
+    component (ICL; e.g. \citealt{Carlberg1997, Lin2004, Gonzalez2005, Mihos2005}) from 
+    massive galaxies in our sample for both technical and scientific reasons.  
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
   \begin{figure*}
@@
   \end{figure*}
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %% 
-%% Introduction 
-%% ------------------------------------------------------------------------------------ %%
-
-\section{Introduction}
-    \label{sec:intro}
-
-    One of the most intriguing observations of high-redshift galaxies from the last 
-    decade has been the dramatic structural transformation in massive quiescent 
-    galaxies \citep[e.g.][]{Trujillo2006, vanDokkum2008, Cimatti2008, Damjanov2009, 
-    vanderWel2011, Szomoru2012, Patel2013} from $z \approx 2$ to the present. 
-    These observations suggest that the progenitors of $z{\sim} 0$ massive early-type 
-    galaxies (ETGs) need to increase their effective radius ($R_{\rm e}$) by factor 
-    of 2--4 in the last 10 Gyrs (e.g. \citealt{Newman2012, vdWel2014}).
-    They have led to a ``two-phase'' scenario for the formation of massive ETGs 
-    (e.g. \citealt{Oser2010, Oser2012}),
-    in which galaxies form a compact central region through highly dissipative 
-    processes (e.g. gas-rich merger or cold gas-accretion; 
-    \citealt{Hopkins2008, Dekel2009}) and then assemble their extended stellar 
-    haloes via dry mergers 
-    \citep[e.g,][]{Naab2006, Khochfar2006, Oser2010, Oser2012}, which allows for 
-    significant growth at late times. 
-    Meanwhile, progenitor bias, which proposes that larger ETGs were quenched more 
-    recently, could also contribute to the apparent size growth, although its 
-    important is under argument (e.g. \citealt{Newman2012, Carollo2013, 
-    Poggianti2013, Belli2015, Keating2015, Fagioli2016}).
-
-    Several previous works have tested the two-phase formation scenario 
-    observationally using galaxies at low redshift, looking at their surface 
-    brightness of mass density profiles (e.g. \citealt{Huang2013a, Huang2013b, 
-    Oh2017}, optical color gradients (e.g. \citealt{LaBarbera2010, LaBarbera2012}), 
-    and stellar population gradients \citep[e.g.,][]{Coccato2010, Coccato2011, 
-    Greene2015, Barbosa2016}. 
-    These observations are generally consistent with the two-phase scenario, 
-    but this picture still face many challenges.
-    One of the most outstanding issues is the extent to which, at fixed stellar mass, 
-    the accreted fraction depends on the surrounding dark matter halo mass.
-
-    According to this two-phase formation scenario, the late time growth of massive 
-    ETGs is intrinsically tied to the growth of their host dark matter halos 
-    (e.g. \citealt{Leauthaud2012, Behroozi2013, Shankar2013}). 
-    Massive ETGs that live at the center of more massive halos should experience 
-    different assembly and should be subject to higher merger rate compared to 
-    ETGs with similar \mstar{} that live in less massive dark matter halos. 
-    A natural prediction of this picture is therefore that the structures of 
-    massive ETGs should depend on their ``environment''\footnote{There are 
-    different definitions of ``environment'' in the literature.  
-    In this work, we use ``environment'' and halo mass interchangeably.}.
-    For instance, models based on two-phase scenario predict that the well-know 
-    stellar mass--effective radius relation for ETGs (\mstar{}--$R_{\rm e}$ relation; 
-    e.g., \citealt{Shen2003, Guo2009}) should show environmental dependence: the 
-    $R_{\rm e}$ of massive ETGs in more massive halos should be larger than those 
-    in less massive halos at fixed \mstar{} 
-    (e.g. \citealt{Shankar2013, Shankar2014}).
-    Yet, solid evidence of this effect at low redshift is still missing 
-    (e.g. \citealt{Nair2010, HCompany13}; but also see \citealt{Yoon2017}).
-
-    %However, while hints of an environmental dependence in the mass-size relation have 
-    %been spotted at high-$z$ (e.g. \citealt{Papovich2012, Lani2013, Delaye2014}; but 
-    %also see \citealt{Rettura2010}).
-
-	% Song: Actually the Illustris paper suggests that, for massive galaxies, 
-	%       even the inner region is dominated by accreted stars.
-
-    To seriously test the environmental dependence of structure in massive ETGs 
-    requires highly sensitive observations extending beyond the inner region of these 
-    galaxies to truly probe the material accreted at late times. 
-    This is very challenging observation as the surface brightness drops rapidly 
-    with radius in massive ETGs.
-
-    In \citet[][; Paper I hereafter]{hscMassiveI}, we showed that the deep, 
-    multi-band images from the Subaru Strategic Program (SSP; \citealt{HSC_SSP,
-    HSC_DR1}) using Hyper Suprime-Cam (HSC; \citealt{Miyazaki2012}, 
-    Miyazaki in~prep.) allows us to extract robust surface stellar
-    mass density (\mden{}) profiles for {\it individual} massive galaxies 
-    at $0.3 < z < 0.5$ out to 100 kpc. 
-    In Paper I, we exploited this sensitivity to show that the \mden{} profiles 
-    and the shapes of the stellar halos of massive ETGs has a clear \mstar{} 
-    dependence. 
-    And the fraction of accreted stars residing in the extended envelope increases
-    with the total \mstar{} of the galaxy.
-
-    In this paper, we explore how the extended stellar halo in massive central galaxies
-    depends on dark matter halo mass with the help of HSC images of a large sample 
-    of massive ETGs and the \redm{} cluster catalog (e.g.\ \citealt{Rykoff2014}; 
-    \citealt{Rozo2015b}; please see Section~\ref{ssec:redmapper} for details)
-
-%% ------------------------------------------------------------------------------------ %%
-
-    Motivated by the ``two-phase'' scenario, and also due to the difficulty in 
-    providing appropriate model to describe the \mstar{} distribution of massive 
-    galaxy from its center to the very outskirt, we focus on \mstar{} within two 
-    different physical apertures in this work:
-
-    \begin{itemize}
-
-        \item The stellar mass within 10 kpc (hereafter noted \minn{}). 
-            According to the two-phase scenario, the ``in-situ'' star-formation quickly 
-            builds up the inner, dense core of massive ETGs.  
-            Based on recent observations and simulations (e.g.~\citealt{vanDokkum2010}; 
-            \citealt{RodriguezGomez2016}), the in-situ component of massive ETGs is 
-            mostly contained within one effective radius ($R_{\mathrm{e}}$, or 5-10 kpc). 
-            We use \minn{} as a proxy for the mass forged during the ``in-situ''
-            phase. 
-            Given the quality of the HSC data, we can reliably measure \minn{} over our 
-            redshift range ($1.0^{\arcsec}$ in radius equals 4.4 and 6.1 kpc at redshift
-            0.3 and 0.5).
-
-        \item The stellar mass within 100 kpc (hereafter noted \mtot{}). 
-            For our galaxy sample, a 100 kpc aperture corresponds to 5-10 
-            $\times R_{\mathrm{e}}$. 
-            We show in section \ref{ssec:mtotal} that most of the mass for these ETGs 
-            can be captured by a 100 kpc radius and that \mtot{} is a good proxy for the 
-            ``total'' \mstar{}. 
-            Although not perfect, we argue that our measurements of \mtot{} (which are 
-            actually measuring the light directly out to 100 kpc) are a better tracer 
-            of total \mstar{} than model-dependent results from shallower data 
-            (such as SDSS) which rely on extrapolating the light profiles of galaxies 
-            out to large radii.
-
-   \end{itemize}
-%% ------------------------------------------------------------------------------------ %%
-
-    {\bf We will show the implications for the stellar mass function of including most of 
-    the stellar light, a task that has been complicated before now due to shallower data. 
-    We will also investigate the idea that the accreted fraction is a function of stellar mass.}
-
-    This paper is organized as follows. 
-    Section \ref{sec:data} presents our data and our sample selection. 
-    Section \ref{sec:ellipse} describes our procedure for extracting 1-D surface 
-    brightness profiles. 
-    Section \ref{sec:mstar} describes how we estimate stellar mass. 
-    Our main results are presented in Section \ref{sec:result} and discussed in 
-    Section \ref{sec:discussion}. 
-    Section \ref{sec:summary} presents our summary and conclusions.
-
-    Magnitudes use the AB system (\citealt{Oke1983}), and are corrected for Galactic 
-    extinction using calibrations from \citet{Schlafly11}.
-    In this work, we assume $H_0$ = 70~km~s$^{-1}$ Mpc$^{-1}$, ${\Omega}_{\rm m}=0.3$, 
-    and ${\Omega}_{\rm \Lambda}=0.7$.
-    Stellar mass is denoted \mstar{} and has been derived using a Chabrier Initial Mass 
-    Function (IMF; \citealt{Chabrier2003}).
-
-    Halo mass is defined as $M_{\rm 200b}$ as 
-    $M_{\rm 200b}\equiv M(<r_{\rm 200b})=200\bar{\rho} 
-    \frac{4}{3}\pi r_{\rm 200b}^3$ where $r_{\rm 200b}$
-    is the radius at which the mean interior density is equal to 200 times
-    the mean matter density ($\bar{\rho}$).
-
 %% ------------------------------------------------------------------------------------ %%
@@
 %% ------------------------------------------------------------------------------------ %% 
-\section{Data And Sample Selection}
+%% Sample Selection and Data Reduction
+%% ------------------------------------------------------------------------------------ %% 
+\section{Sample Selection and Data Reduction}
     \label{sec:data}
@@
 %% ------------------------------------------------------------------------------------ %% 
-
+    Motivated by the two-phase formation scenario, we focus on \mstar{} within two 
+    different physical apertures in this work:
+
+    \begin{itemize}
+
+        \item The stellar mass within 10 kpc (hereafter noted \minn{}). 
+            According to the two-phase scenario, the ``in-situ'' star-formation quickly 
+            builds up the inner, dense core of massive ETGs.  
+            Based on recent observations and simulations (e.g.~\citealt{vanDokkum2010}; 
+            \citealt{RodriguezGomez2016}), the in-situ component of massive ETGs is 
+            mostly contained within one effective radius ($R_{\mathrm{e}}$, or 5-10 kpc). 
+            We use \minn{} as a proxy for the mass forged during the ``in-situ''
+            phase. 
+            Given the quality of the HSC data, we can reliably measure \minn{} over our 
+            redshift range ($1.0^{\arcsec}$ in radius equals 4.4 and 6.1 kpc at redshift
+            0.3 and 0.5).
+
+        \item The stellar mass within 100 kpc (hereafter noted \mtot{}). 
+            For our galaxy sample, a 100 kpc aperture corresponds to 5-10 
+            $\times R_{\mathrm{e}}$. 
+            We show in section \ref{ssec:mtotal} that most of the mass for these ETGs 
+            can be captured by a 100 kpc radius and that \mtot{} is a good proxy for the 
+            ``total'' \mstar{}. 
+            Although not perfect, we argue that our measurements of \mtot{} (which are 
+            actually measuring the light directly out to 100 kpc) are a better tracer 
+            of total \mstar{} than model-dependent results from shallower data 
+            (such as SDSS) which rely on extrapolating the light profiles of galaxies 
+            out to large radii.
+
+   \end{itemize}
+%% ------------------------------------------------------------------------------------ %%
+
+    {\bf We will show the implications for the stellar mass function of including most of 
+    the stellar light, a task that has been complicated before now due to shallower data. 
+    We will also investigate the idea that the accreted fraction is a function of stellar mass.}
+
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
+%% Results 
 %% ------------------------------------------------------------------------------------ %% 
 \section{Results}
-    \label{sec:results}
+    \label{sec:result}
 

### 2017-07-10 draft/paper2.tex
Data Reduction 1

@@
 
-    \song{Need a much shorter version of HSC data summar here.}
+    The sample selection and data reduction processes are described in detail in 
+    Paper I. 
+    Here we include a short summary for completeness.
+
+    This work makes use of the imaging data from the internal data release 
+    \texttt{S15B}, which is very similar to the Public Data Release 1 
+    (\citealt{HSC-DR1} and covers ${\sim} 110$ deg$^2$ in all five-band ($grizy$) to 
+    the required depth. 
+    These images are reduced by \texttt{hscPipe 4.0.2}, a derivative of the 
+    Large Synoptic Survey Telescope (LSST) pipeline (e.g.\ \citealt{Juric2015}; 
+    \citealt{Axelrod2010}), modified for HSC (\citealt{HSC-PIPE}).
+    The pixel scale of the reduced image is $0.168$\asec{}.
+    We use the $i$-band image for extracting surface brightness profiles.    
+    The HSC $i$-band image is typically 3--4 mag deeper than the SDSS one in surface 
+    brightness limit and has superb seeing condition (mean FWHM$=0.6$\asec{}).
+
+    In Paper~I, we select large sample of massive galaxies with either spectroscopic 
+    redshift or reliable ``red-sequence'' photometric redshift at $0.3<z<0.5$. 
+    Within this redshift range, we have large enough volume to achieve reasonable 
+    statistics at very high \mstar{} end, can spatially resolve the inner $\sim 5$ 
+    kpc of massive galaxies, and can safely ignore any structural evolution. 
+    We derive $i$-band surface brightness profiles out to 100 kpc after carefully 
+    masking out any surrounding contaminations and correcting the background 
+    subtraction. 
+    We measure the average \m2l{} of these galaxies 
+    Using the five-band forced \cmodel{} magnitudes from \texttt{hscPipe}, we 
+    measure  of the galaxy via SED fitting.
 
@@
     \jenny{Here is an attempt to include all the things we really need here.}
-    Our sample selection is described in detail in Paper I. Here we include a short summary for completeness. 
-    We focus on early-type galaxies with $0.3<z<0.5$ and stellar mass $M_*>10^{11.5}$~\msun. 
+
+    We focus on early-type galaxies with  and stellar mass $M_*>10^{11.5}$~\msun. 
     The redshift range includes a large enough volume to have good statistics at the high-mass end, while 

### 2017-07-10 draft/paper2.tex
Data Reduction 2

@@
     In Paper~I, we select large sample of massive galaxies with either spectroscopic 
-    redshift or reliable ``red-sequence'' photometric redshift at $0.3<z<0.5$. 
+    redshift or reliable ``red-sequence'' photometric redshift (\citealt{Rykoff2014}) 
+    at $0.3<z<0.5$. 
     Within this redshift range, we have large enough volume to achieve reasonable 
     statistics at very high \mstar{} end, can spatially resolve the inner $\sim 5$ 
-    kpc of massive galaxies, and can safely ignore any structural evolution. 
+    kpc of massive galaxies ($1.0^{\arcsec}$ corresponds to 4.4 and 6.1 kpc at 
+    $z=0.3$ and 0.5), and can safely ignore any structural evolution. 
     We derive $i$-band surface brightness profiles out to 100 kpc after carefully 
@@
     subtraction. 
-    We measure the average \m2l{} of these galaxies 
-    Using the five-band forced \cmodel{} magnitudes from \texttt{hscPipe}, we 
-    measure  of the galaxy via SED fitting.
+    We use the broadband spectral energy distributions (SED) fitting code 
+    \texttt{iSEDFit}\footnote{http://www.sos.siena.edu/~jmoustakas/isedfit/} 
+    (\citealt{Moustakas13}) to measure the average \m2l{} and $k$--correction of 
+    these galaxies using five-band forced \cmodel{} magnitudes from \texttt{hscPipe}.
+    \citet{Chabrier2003} IMF, Flexible Stellar Population 
+    Synthesis\footnote{http://scholar.harvard.edu/cconroy/sps-models}
+    (FSPS; \texttt{v2.4}; \citealt{FSPS}, \citealt{Conroy2010}) model, 
+    \citet{Calzetti2000} extinction law, simple delayed-$\tau$ model for star 
+    formation history (SFH) are assumed here. 
+    Using these information, we obtain reliable \mden{} profiles of these 
+    galaxies out to $> 100$ kpc and \mstar{} integrated to different physical 
+    radius using elliptical apertures.
+
+    As explained in Paper I, here we focus on \mstar{} within
+
+    \begin{itemize}
+
+        \item a 10 kpc radii (hereafter noted \minn{}) as proxy of the ``in-situ'' 
+            stellar component. 
+            This is motivated by recent observations and simulations 
+            (e.g.~\citealt{vanDokkum2010}, \citealt{RodriguezGomez2016}).
+
+        \item a 100 kpc radii (hereafter noted \mtot{}), which is shown to recover 
+            more \mstar{} than the ones based on \cmodel{} photometry, as proxy of the 
+            total \mstar{} of the galaxy.
+
+   \end{itemize}
+
+   Although these radius are empirically selected, they help recover the 
+   \mstar{}-dependence of the fraction of accreted stars, and reveal the diversity of 
+   stellar envelopes among massive galaxies. 
+   In Figure \ref{fig:m100_m10_color}, we demonstrate such diversity by showing 
+   a random subsample of massive galaxies with very similar \minn{} that have large 
+   range of \mtot{}. 
+   We will use these two
+
+%% ------------------------------------------------------------------------------------ %%    
+\subsection{Massive Central Galaxies from Different Environment}
+    \label{ssec:cen}
 
@@
     be called \nbcg{}.
-
-%% ------------------------------------------------------------------------------------ %% 
-    Motivated by the two-phase formation scenario, we focus on \mstar{} within two 
-    different physical apertures in this work:
-
-    \begin{itemize}
-
-        \item The stellar mass within 10 kpc (hereafter noted \minn{}). 
-            According to the two-phase scenario, the ``in-situ'' star-formation quickly 
-            builds up the inner, dense core of massive ETGs.  
-            Based on recent observations and simulations (e.g.~\citealt{vanDokkum2010}; 
-            \citealt{RodriguezGomez2016}), the in-situ component of massive ETGs is 
-            mostly contained within one effective radius ($R_{\mathrm{e}}$, or 5-10 kpc). 
-            We use \minn{} as a proxy for the mass forged during the ``in-situ''
-            phase. 
-            Given the quality of the HSC data, we can reliably measure \minn{} over our 
-            redshift range ($1.0^{\arcsec}$ in radius equals 4.4 and 6.1 kpc at redshift
-            0.3 and 0.5).
-
-        \item The stellar mass within 100 kpc (hereafter noted \mtot{}). 
-            For our galaxy sample, a 100 kpc aperture corresponds to 5-10 
-            $\times R_{\mathrm{e}}$. 
-            We show in section \ref{ssec:mtotal} that most of the mass for these ETGs 
-            can be captured by a 100 kpc radius and that \mtot{} is a good proxy for the 
-            ``total'' \mstar{}. 
-            Although not perfect, we argue that our measurements of \mtot{} (which are 
-            actually measuring the light directly out to 100 kpc) are a better tracer 
-            of total \mstar{} than model-dependent results from shallower data 
-            (such as SDSS) which rely on extrapolating the light profiles of galaxies 
-            out to large radii.
-
-   \end{itemize}
-%% ------------------------------------------------------------------------------------ %%
-
-    {\bf We will show the implications for the stellar mass function of including most of 
-    the stellar light, a task that has been complicated before now due to shallower data. 
-    We will also investigate the idea that the accreted fraction is a function of stellar mass.}
 

### 2017-07-12 draft/paper2.tex
Data and sample: edit 2

@@
    range of \mtot{}. 
-   We will use these two
-
-%% ------------------------------------------------------------------------------------ %%    
-\subsection{Massive Central Galaxies from Different Environment}
+   We will use these two apertures\mstar{} to guide the comparisons of massive galaxies 
+   from different environments.
+
+%% ------------------------------------------------------------------------------------ %%    
+\subsection{Massive Central Galaxies from Different Environments}
     \label{ssec:cen}
 
-    %    The \rbcg{} sample is less affected by completeness because we can utilize 
-    %photo-$z$s from \redm{}. 
-    %However, the completeness of the \nbcg{} sample is still limited by the 
-    %availability of spec-$z$s from BOSS.\alexie{Not sure this is important here.}
-
-    \jenny{Here is an attempt to include all the things we really need here.}
-
-    We focus on early-type galaxies with  and stellar mass $M_*>10^{11.5}$~\msun. 
-    The redshift range includes a large enough volume to have good statistics at the high-mass end, while 
-    the stellar mass limit is set by our photometric incompleteness. HSC-identified objects are cross-matched 
-    with the spectroscopic and photometric samples from redMapper \citep{Rykoff2014}. Stellar masses are estimated 
-    using stellar population synthesis modeling of the broad-band photometry, and then the mass limit is 
-    imposed. Using comparisons with published mass functions, we demonstrate that we are complete 
-    to $M_*>10^{11.5}$~\msun\ over the full redshift range.
-
-    Finally, here we wish to focus on galaxies that live at the centers of their dark matter halos. 
-    We utilize the group information 
-    in redMapper v5.10 \citep{Rykoff2014,Rozo2015b} to identify central galaxies. We use the 
-    relation between richness $\lambda$ and stellar mass to select groups with 
-    $\lambda>30$ or $M_{\rm halo}>10^{14.2}$~\msun\ \citep[e.g.,][]{simetetal2016}. This limit is chosen 
-    to mitigate incompleteness at the high end of our redshift window. We then identify the 
-    central galaxy to have $P_{\rm CEN}>0.7$. We will refer to this sample of 164 central galaxies as \rbcg{}. The median 
-    richness of the sample is $\lambda \approx 41$ ($M_* \approx 2.2 \times 10^{14}$~\msun), and there are 
-    only 44 central galaxies in clusters with $\lambda>0.5$ ($M_* > 10^{15}$~\msun). We build a complementary 
-    sample of central galaxies in lower-mass halos by calculating the radius of each group with 
-    $\lambda>20$ \citep{Diemer2015} and 
-    then excluding galaxies within a cylinder around each group, with the thickness of the cylinder broadened to include 
-    photo-z uncertainty. The sample of {\bf XX} central galaxies living in halos with $M_* < 10^{14}$~\msun\ will 
-    be called \nbcg{}.
+    In this work, we focus on massive galaxies with \mtot{} $>10^{11.6}$~\msun{}. 
+    In Paper~I, we demonstrate that the \mstar{} completeness above this threshold is 
+    good over the full redshift range using comparisons with stellar mass functions 
+    from more complete samples.
+
+    We also wish to focus on massive galaxies that live at the centers of their own 
+    dark matter halos-- so-called ``central'' galaxies.  
+    They are uniquely important to the study of galaxy-halo connection and are known 
+    to follow stellar mass--halo mass relation (SHMR; e.g. \citealt{Leauthaud2012, 
+    Behroozi2013, Kravtsov2014, Tinker2017}) at high-\mstar{} end with small scatter.
+    We utilize the \redm{} \texttt{v5.10} \citep{Rykoff2014, Rozo2015b} cluster catalog 
+    to identify central galaxies.
+
+    Firstly, we select 68 massive central galaxies from the \redm{} clusters 
+    with $\lambda \geq 30$, $P_{\mathrm{Cen}} \geq 0.7$, and \logmtot{}$>11.5$ 
+    at $0.3 < z < 0.5$ (63/69 have \logmtot{}$>11.6$). 
+    This $\lambda$ limit is chosen to mitigate incompleteness of low richness clusters
+    at the high end of our redshift window, and the $P_{\mathrm{Cen}}$ limit is 
+    selected to exclude low probability candidate of central galaxy. 
+    Based on the \mhalo{}-$\lambda$ relation calibrated by \citet{Simet2016}, these 
+    galaxies are the brightest cluster galaxies (BCGs) of clusters with 
+    \mhalo{}$>10^{14.2}$~\msun{}.
+    This calibration is consistent with other works (e.g. \citealt{Saro2015, Farahi2016, 
+    Melchior2016, Murata2017}). 
+    The median richness of the sample is $\lambda \approx 41$ 
+    (\mhalo{}$\approx 2.2 \times 10^{14}$~\msun{}), and there are 
+    only 44 central galaxies in clusters with $\lambda>50$ 
+    (\mhalo{}$\approx 3.0 \times 10^{14}$~\msun{}).
+    We will refer to this sample of \textbf{central galaxies in more massive halos} as 
+    the \rbcg{} sample.
+
+    Secondly, we build a complementary sample of central galaxies in lower-mass haloes
+    by excluding all galaxies that are in any \redm{} cluster with $\lambda > 20$.
+    We convert their $\lambda$ into $M_{\mathrm{200b}}$ using calibration by 
+    \citet{Simet2016}. 
+    Then we estimate the $R_{\mathrm{200b}}$ of each cluster using the method in 
+    \citet{Diemer2015}. 
+    And we exclude all galaxies within a cylinder around each cluster, with the radius
+    equal to $R_{\mathrm{200b}}$ and length equal to twice the value of the photometric 
+    redshift uncertainty (typically around 0.015 to 0.025). 
+    We generally consider this sample as the central galaxies living in halos with
+    $M_{\mathrm{200b}} < 10^{14}$~\msun{}, and will refer to this sample as \nbcg{}.
+    Initially, we select 3453 galaxies this way with \logmtot{}$> 11.2$ at 
+    $0.3 < z < 0.5$. 
+    Among them, 1564 (833) have \logmtot{}$> 11.5$ (11.6). 
+    Satellite contamination should be relative low at the high-\mtot{} end
+    (e.g. \citealt{Reid2014, Hoshino2015, Saito2016, vanUitert2016}). 
+    For instance, the model from \citet{Saito2016} predicts a $\sim 7$\% 
+    contamination in the \logmtot{}$>11.6$ sample from satellites from 
+    \logmh$<11.4$ haloes.
+
+    It is worth noting that we failed to extract 1-D profiles for $\sim10$\% of 
+    \rbcg{} and \nbcg{} galaxies due to physical (e.g. on-going major merger) or 
+    nuisance (e.g.\ nearby foreground galaxy or bright star) reasons. 
+    These situations happen more frequently for lower-\mtot{} galaxies, and should not 
+    affect the results of this work.
 
@@
 
-    %\footnote{There are different observational definitions of ``environment''. 
-    %In this paper, we use the term ``environment'' and halo mass interchangeably}.
-
-    \song{These paragraphs are from Jenny's txt file, need organization.}
     Massive central galaxies in this work show an intriguing diversity on the plane 
@@
     \citealt{Inagaki2015}; but also see \citealt{Bai2014}).
-
-    \textbf{Completeness that depends on halo mass:}
 
@@
 
-%%%%%%%%%%: Appendix Section %%%%%%%%%%%%
+%% ------------------------------------------------------------------------------------ %% 
+%% Appendix Section
+%% ------------------------------------------------------------------------------------ %%
 
@@
 
-\song{Just copied a couple of relevant sections here; need some works}
-%% ------------------------------------------------------------------------------------ %% 
-\section{A. Comparison of \mden{} profiles using \mstar{} from the GAMA survey}
+%% ------------------------------------------------------------------------------------ %% 
+\section{A. Basic Statistical Properties of the Sample} 
+	\label{app:sedasic}
+
+    On the top-left panel of Fig~\ref{fig:sample_stats}, we show the \mtot{}-color 
+    relations using the $k$-corrected $g-r$ color. 
+    Both samples follow the same tight ``red-sequence'' with little contamination 
+    from the ``blue cloud''.
+    At fixed \mtot{}, we see little offset in color distributions of the two 
+    samples, suggesting that both samples consist of quiescent galaxies with 
+    similar average stellar population properties.  
+    This is consistent with previous result that suggests the average stellar 
+    population of massive central galaxy does not depend on \mhalo{} 
+    (e.g.\ \citealt{Park2007}).  
+    In this work, we focus on the \mstar{} range of $11.6 \le$\logmtot{}$\le 11.9$, 
+    where both samples have acceptable completeness, and their \mtot{} distributions 
+    greatly overlap (see the normalized distributions of \mtot{} in the bottom-left 
+    panel of Fig~\ref{fig:sample_stats}). 
+    As for the \minn{} distributions, the two samples overlap the most within 
+    $11.2 \le$\logmtot{}$\le 11.6$, but now they show quite different
+    distributions (bottom-right figure).
+
+    The redshift distributions also show small difference
+    (upper-right panel) even in the high-\mtot{} bin, where the redshift distribution 
+    of the \nbcg{} sample skews toward higher-$z$ end due to the contribution of BOSS 
+    spec-$z$.
+    Since this could bias the comparison of \mden{} profiles and other properties 
+    (please see Appendix\ref{app:redshift} for more details), we address this via matching 
+    the two samples in both mass and redshift distributions carefully
+    (see Appendix~\ref{app:match}).
+
+%% ------------------------------------------------------------------------------------ %% 
+  \begin{figure*}
+      \centering 
+      \includegraphics[width=16.5cm]{fig/redbcg_sample_stats}
+      \caption{
+          \textbf{Top-left}: The \logms{}-$g-r$ color relation of the \rbcg{} 
+          (red circle; detaield format is the same with the right panel of 
+          Fig~\ref{fig:smf1}) and \nbcg{} (grey dots) samples.
+          We apply the $k$-corrections from \texttt{iSEDFit} fitting to the colors.~~          
+          \textbf{Top-right}: the histograms of the redshift for the \rbcg{} and 
+          \nbcg{} galaxies in both \logmtot$>11.2$ and $11.6<$\logmtot{}$<11.9$
+          mass bins.
+          The vertical lines highlights the $0.3\leq z \leq 0.5$ redshift range.~~
+          \textbf{Bottom-left}: the histograms of \mtot{} for the \rbcg{} (orange-red) 
+          and \nbcg{} (grey-black) samples at both $z>0.2$ (step-filled histogram) and 
+          $0.3 \leq z \leq 0.5$ (stepped histogram). 
+          The vertical lines in both top-left and bottom-left figures highlight the 
+          $11.6<$\logmtot{}$<11.9$ mass range that will be used in the comparison of 
+          the \mtot{}-matched samples.~~
+          \textbf{Bottom-right}: the histograms of \minn{} in similar format. 
+          Here the vertical lines highlight the 
+          $11.2<$\logminn{}$<11.6$ mass range that is used for comparison.
+      }
+      \label{fig:sample_stats}
+  \end{figure*}
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
+\section{B. Comparison of \mden{} profiles using \mstar{} from the GAMA survey}
     \label{app:gama}
@@
 
-\section{B. Comparisons of \mden{} profiles in different redshift bins}
+\section{C. Comparisons of \mden{} profiles in different redshift bins}
     \label{app:redshift}
@@
 
-\section{C. Match the \rbcg{} and \nbcg{} samples in \mstar{} and redshift distributions}
+\section{D. Match the \rbcg{} and \nbcg{} samples in \mstar{} and redshift distributions}
     \label{app:match}
@@
 %% ------------------------------------------------------------------------------------ %% 
-\section{D. Robustness of the \mden{} Differences} 
+\section{E. Robustness of the \mden{} Differences} 
 	\label{app:robust}

### 2017-07-12 draft/paper2.tex
Data and sample: edit 3
Edit results 1

@@
 
+    In Appendix~\ref{app:basic}, we show the distributions of redshift, \mtot{}, and 
+    \minn{} for \rbcg{} and \nbcg{} samples. 
+    We also compare these two samples on the \mtot{} - rest-frame $g-r$ color plane. 
+    Both of them follow the same ``red-sequence'' without much contamination from the 
+    ``blue clouds''.
+
     It is worth noting that we failed to extract 1-D profiles for $\sim10$\% of 
@@
 
-    Massive central galaxies in this work show an intriguing diversity on the plane 
-    defined by these two metrics.  
-    We preview this using Fig~\ref{fig:m100_m10_color}, which shows a subsample of 
-    massive galaxies at $z{\sim} 0.4$ that share very similar value of \minn{}, but 
-    exhibit a large diversity in their outer profiles. 
-    Assuming that galaxies at fixed \minn{} share a similar in-situ formation history, 
-    it is of great interest to investigate the relation between their present day halo 
-    mass and the extend of their outer envelopes. 
-    We note that although a circular aperture is shown on Fig~\ref{fig:m100_m10_color}, 
-    for our mass measurements, we always use elliptical apertures that follow the 
-    average isophotal shape. Finally, given our narrow mass and redshift range, we 
-    can safely ignore significant mass growth and structural evolution in this work
+    As shown in Figure~\ref{fig:m100_m10_color}, massive central galaxies show 
+    intriguing diversity on the \mtot{}-\minn{} plane and in their \mden{} profiles 
+    in the outer haloes.  
+    In Paper~1, we explore the \mstar{}-dependence of the stellar halos in massive 
+    galaxies, and conclude that the general trends are consistent with the 
+    predictions of two-phase formation scenario. 
+    In the following sections, we will investigate the relation between their 
+    present day halo mass and their stellar haloes using the \mden{} profiles and 
+    scaling relations for massive central galaxies with different $M_{\mathrm{200b}}$ 
+    (\rbcg{} and \nbcg{}).
+
+    We should emphasize again that although a circular aperture is shown on 
+    Fig~\ref{fig:m100_m10_color}, we extract 1-D \mden{} profiles, estimate 
+    \mtot{} and \minn{} using elliptical apertures defined by fluxed-weighted average 
+    isophotal shape. 
+    And, given the narrow \mstar{} and redshift range, we ignore \mstar{} growth 
+    and structural evolution here
     (no star formation, lower merger rate \etal~e.g.\ \citealt{Bellstedt2016},
@@
 \section{A. Basic Statistical Properties of the Sample} 
-	\label{app:sedasic}
+	\label{app:basic}
 
@@
       \centering 
-      \includegraphics[width=16.5cm]{fig/redbcg_sample_stats}
+      \includegraphics[width=16.5cm]{fig/redbcg_sample_stats_old}
       \caption{

### 2017-07-12 draft/paper2.tex
Edit results 2

@@
 
-    When comparing \nbcg{} and \rbcg{} we will also always make sure that the two 
-    samples are well matched both in terms of \mstar{} as well as in terms of redshift. 
-    Please see the next section and Appendix~\ref{app:match} for more details.
-
 %% ------------------------------------------------------------------------------------ %% 
@@
 
-    We now ask whether or not galaxies from our sample have \mden{} profiles that 
-    depend on \mhalo{} (at fixed \mstar{}). 
-    For this, we will build matched samples drawing from \rbcg{} and \nbcg{} that are 
-    carefully matched in \mstar{} and redshift using a KDTree algorithm 
-    (see Appendix~\ref{app:match} and Fig~\ref{fig:match} for details). 
-    By matching the redshift distributions within $0.3 < z < 0.5$, we ensure that the 
-    \mden{} profiles from both samples are impacted by seeing and background subtraction 
-    at similar levels. 
-    To match the two samples by stellar mass, we will use two different methods:
-
-%% ------------------------------------------------------------------------------------ %%     
-    Fig~\ref{fig:prof_1} compares the profiles of galaxies at fixed \mtot{} and at fixed 
-    \minn{} for our two matched samples, and shows the main results of this paper which 
-    is that we find a clear halo mass dependence in the \mden{} profiles of massive 
+    First, we ask whether the \mden{} profiles of massive central galaxies show 
+    \mhalo{}-dependence within 100 kpc at fixed \mstar{}. 
+    To perform meaning comparison, we build matched samples drawing from \rbcg{} and 
+    \nbcg{} that are carefully matched in \mstar{} and redshift using KDTree algorithm 
+    (please see Appendix~\ref{app:match} and Fig~\ref{fig:match} for details). 
+    The similar distributions of redshift of the matched samples ensure that the 
+    median \mden{} profiles from both samples are affected by seeing and background 
+    subtraction to the same extend. 
+    We address this issue more in Appendix~\ref{app:redshift}.
+
+    We match the \rbcg{} and \nbcg{} samples using both \mtot{} and \minn{} in this
+    work. 
+    As explained in Paper~1, we use \mtot{} as proxy of the ``total'' \mstar{}
+    of massive galaxies while treat \minn{} as a rough indicator of the mass of the 
+    \textit{in-situ} component.
+
+%% ------------------------------------------------------------------------------------ %%     
+    Fig~\ref{fig:prof_1} compares the \mden{} profiles of massive central galaxies 
+    in \rbcg{} (orange-red color) and \nbcg{} (grey-black color) at fixed \mtot{} 
+    (left panel) and at fixed \minn{} (right panel). 
+    The top panels show the individual \mden{} profiles along with the median profiles 
+    for both samples. 
+    The bottom panel of Fig~\ref{fig:prof_1} shows the difference between the median 
+    \mden{} profile of \rbcg{} and \nbcg{} samples, with errors computed via bootstrap 
+    resampling.
+    $\Delta = \log(\mu_{\star, \mathrm{cenHighMh}}) - 
+    \log(\mu_{\star, \mathrm{cenLowMh}})$. 
+    This figure presents the main results of this work: \textbf{The \mden{} profiles of 
+    massive central galaxies show \mhalo{}-dependence at both fixed \mtot{} and 
+    \minn{}.}
+    For both \mtot{}-- and \minn{}--matched samples, we see systematic differences
+    between the median \mden{} profile of \rbcg{} galaxies and the one for \nbcg{}
     galaxies.
-    The bottom panel of Fig~\ref{fig:prof_1} shows the difference between the two 
-    profiles, $\Delta = \log(\mu_{\star, \mathrm{cenHighMh}}) - 
-    \log(\mu_{\star, \mathrm{cenLowMh}})$, 
-    with errors computed via bootstrap resampling. 
-    In Appendix~\ref{app:robust}, we present a variety of tests that verify the 
-    robustness of these results against different uncertainties.
-
-    There are several important points to be noticed in Fig~\ref{fig:prof_1}. 
-    First, when galaxies are matched by \mtot{}, although we detect a robust 
-    environmental dependence, it mainly only becomes prominent in the outskirts 
-    at $R>50$ kpc. 
-    This partially explains the difficulties for previous works to detect this effect
-    on shallower images. 
-    Second, we find that central galaxies in more massive dark mater halos display 
-    more flattened inner profile and more significant outer stellar envelope than 
-    the ones living in less massive halos. 
-    Third, the median \mden{} profiles of \rbcg{} and \nbcg{} cross each other 
-    at ${\sim} 15$-20 kpc, the expected $R_{\mathrm{e}}$ for ETGs at this \mtot{}. 
-    Finally, such systematic difference in structure may become more significant 
-    at very high-mass end. 
-    We see evidence of this effect when we compare the $Delta$ profiles in two \mtot{} 
+
+    We perform statistical tests to show that the differences we see in the median 
+    \mden{} profiles are significant. 
+    We also conduct a variety of tests that verify the robustness of these results 
+    against choices of \mtot{} bins, $\lambda$ cut, and redshift range. 
+    Please see Appendix~\ref{app:robust} for more details about these tests.
+
+    There are several important points to be noticed on the left panel of 
+    Fig~\ref{fig:prof_1}.
+
+    \begin{itemize}
+
+        \item First, for the \mtot{} matched sample, although the difference in 
+            median \mden{} profiles is systematical and robust, the overall difference 
+            is very subtle and only becomes clear in the outskirts at $R>50$ kpc, 
+            which explains why such environment dependence is extremely difficult 
+            for previous works to detect using shallower images.
+
+        \item Second, we find that, at fixed \mtot{}, massive central galaxies in 
+            more massive dark mater halos display shallower \mden{} profiles that the 
+            ones living in less massive haloes. 
+            This can be seen from the more flattened inner \mden{} profile and more 
+            significant outer stellar halos.
+
+        \item Third, the median \mden{} profiles of \rbcg{} and \nbcg{} cross each 
+            other at ${\sim} 15$-20 kpc, the expected $R_{\mathrm{e}}$ for massive 
+            ETGs around this \mtot{}.
+
+        \item Finally, such systematic difference in \mden{} profiles may become more 
+            significant at higher \mtot{}.
+            We see evidence of this using the $Delta$ profiles of two \mtot{} 
             bins (see Fig~\ref{fig:prof_2} and discussion in 
-    Appendix~\ref{app:robust})\footnote{Though the lower \mtot{} bin becomes somewhat
-    incomplete} and when we discuss the relation between \mtot{} and \minn{} for 
-    these two samples (see Fig~\ref{fig:scaling_relation}). 
-    This potential interesting result and its implication is worth more investigations 
-    later.
-
-    Meanwhile, the subtle environmental dependence of \mden{} profiles for the 
-    \mtot{}-matched samples suggests that environment does not play the major role in 
-    shaping massive galaxies \textbf{at fixed total stellar mass}.
+            Appendix~\ref{app:robust})\footnote{Though the lower \mtot{} bin becomes 
+            somewhat incomplete} and when we discuss the relation between \mtot{} and 
+            \minn{} (see Fig~\ref{fig:scaling_relation}). 
+            This trend has potentially interesting implication that is worth more 
+            investigations later.
+
+    \end{itemize}
+
+    Generally speaking, such subtle environmental dependence of \mden{} profiles in 
+    the \mtot{}-matched samples suggests that environment does not play a major role 
+    in shaping massive galaxies \textbf{at fixed ``total'' stellar mass}.
     Therefore it is interesting to ask, for massive galaxies that \textbf{contain 
-    similar \mstar{} in the in-situ component}, how does environment affect their 
-    subsequent mass assembly?
-    Assuming that the \minn{} is reasonable proxy of in-situ mass, we look into this 
-    question by comparing the \mden{} profiles of the \minn{}-matched samples ( 
-    Fig~\ref{fig:prof_1}, right).  
-    Although the median \mden{} profiles are similar at $r \leq 10$ kpc, the
-    central galaxies in more massive halos clearly possess much more prominent outer
-    envelope. 
-    This result is robust in a series of statistical and systematical tests 
-    (see Appendix~\ref{app:robust}.
-
-    At the same time, the uniform slope of the \mden{} profiles within 
-    10 kpc is in sharp contrast with the large scatter of the outskirts. 
+    similar \mstar{} in the \textit{in-situ} component}, how does environment affect 
+    their subsequent mass assembly?
+    Assuming \minn{} is reasonable tracer of the ``in-situ'' mass, we compare the 
+    \mden{} profiles of \minn{}-matched samples (right panel of Fig~\ref{fig:prof_1}).  
+    Although the median \mden{} profiles are very similar at $R \leq 10$ kpc, the
+    massive central galaxies in more massive halos host much more prominent outer 
+    stellar halo.
+
+    Meanwhile, the uniform slope of the \mden{} profile within 10 kpc is in sharp 
+    contrast with the large \textit{intrinsic} scatter in the outskirts. 
     It hints that these two regions are shaped by distinctive processes, and may 
-    explain their differences in environmental dependency. 
+    explain why they depend on environment at different levels.  
     In simulations, intensive dissipative process helps create 

### 2017-07-13 draft/paper2.tex
Edit results 3

@@
 \title[Structure and Environment of Massive Galaxies]{
-       A Detection of the Environmental Dependence of the Stellar Profiles and Halos
+       A Detection of the Environmental Dependence of the Stellar Profiles and haloes
        of Massive Central Galaxies}
@@
     present subtle but systematic differences that correlate with \mhalo{}. 
-    On average, massive central galaxies in more massive halos have shallower inner 
+    On average, massive central galaxies in more massive haloes have shallower inner 
     stellar mass density profiles (within ${\sim}10$-$20$ kpc) and more prominent outer 
@@
     These differences translate into a clear environmental dependence of the mass-size 
-    relation: central galaxies in more massive halos have larger $R_{\mathrm{50}}$ 
+    relation: central galaxies in more massive haloes have larger $R_{\mathrm{50}}$ 
     at fixed \mtot{}. 
@@
     important impact on measurements of the galaxy mass function. 
-    Furthermore, because galaxies in larger halos have more extended envelopes, 
+    Furthermore, because galaxies in larger haloes have more extended envelopes, 
     the amount of light that is missed will be halo mass dependent. 
@@
     According to this two-phase formation scenario, the late time growth of massive 
-    ETGs is intrinsically tied to the growth of their host dark matter halos 
+    ETGs is intrinsically tied to the growth of their host dark matter haloes 
     (e.g. \citealt{Leauthaud2012, Behroozi2013, Shankar2013}). 
-    Massive ETGs that live at the center of more massive halos should experience 
+    Massive ETGs that live at the center of more massive haloes should experience 
     different assembly and should be subject to higher merger rate compared to 
-    ETGs with similar \mstar{} that live in less massive dark matter halos. 
+    ETGs with similar \mstar{} that live in less massive dark matter haloes. 
     A natural prediction of this picture is therefore that the structures of 
@@
     e.g., \citealt{Shen2003, Guo2009}) should show environmental dependence: the 
-    $R_{\rm e}$ of massive ETGs in more massive halos should be larger than those 
-    in less massive halos at fixed \mstar{} 
+    $R_{\rm e}$ of massive ETGs in more massive haloes should be larger than those 
+    in less massive haloes at fixed \mstar{} 
     (e.g. \citealt{Shankar2013, Shankar2014}).
@@
     In Paper I, we exploited this sensitivity to show that the \mden{} profiles 
-    and the shapes of the stellar halos of massive ETGs has a clear \mstar{} 
+    and the shapes of the stellar haloes of massive ETGs has a clear \mstar{} 
     dependence. 
@@
           The right panel corresponds to samples matched by ``core-mass'' (\minn{}). 
-          Orange and red lines correspond to central galaxies living in halos with 
+          Orange and red lines correspond to central galaxies living in haloes with 
           \logmh{} $\geq 14.2$. 
-          Black and grey correspond to central galaxies living in halos with 
+          Black and grey correspond to central galaxies living in haloes with 
           \logmh{} $\leq 14.0$. 
@@
     We also wish to focus on massive galaxies that live at the centers of their own 
-    dark matter halos-- so-called ``central'' galaxies.  
+    dark matter haloes-- so-called ``central'' galaxies.  
     They are uniquely important to the study of galaxy-halo connection and are known 
@@
     (\mhalo{}$\approx 3.0 \times 10^{14}$~\msun{}).
-    We will refer to this sample of \textbf{central galaxies in more massive halos} as 
+    We will refer to this sample of \textbf{central galaxies in more massive haloes} as 
     the \rbcg{} sample.
@@
     redshift uncertainty (typically around 0.015 to 0.025). 
-    We generally consider this sample as the central galaxies living in halos with
+    We generally consider this sample as the central galaxies living in haloes with
     $M_{\mathrm{200b}} < 10^{14}$~\msun{}, and will refer to this sample as \nbcg{}.
@@
     in the outer haloes.  
-    In Paper~1, we explore the \mstar{}-dependence of the stellar halos in massive 
+    In Paper~1, we explore the \mstar{}-dependence of the stellar haloes in massive 
     galaxies, and conclude that the general trends are consistent with the 
@@
     We also conduct a variety of tests that verify the robustness of these results 
-    against choices of \mtot{} bins, $\lambda$ cut, and redshift range. 
+    against choices of \mtot{} bins, $\lambda$ cut, redshift range, and the proxy
+    of ``total'' or \textit{in situ} stellar mass. 
     Please see Appendix~\ref{app:robust} for more details about these tests.
@@
         \item Second, we find that, at fixed \mtot{}, massive central galaxies in 
-            more massive dark mater halos display shallower \mden{} profiles that the 
+            more massive dark mater haloes display shallower \mden{} profiles that the 
             ones living in less massive haloes. 
             This can be seen from the more flattened inner \mden{} profile and more 
-            significant outer stellar halos.
+            significant outer stellar haloes.
 
@@
     Although the median \mden{} profiles are very similar at $R \leq 10$ kpc, the
-    massive central galaxies in more massive halos host much more prominent outer 
+    massive central galaxies in more massive haloes host much more prominent outer 
     stellar halo.
@@
     of more massive halo (e.g. \citealt{Pillepich2014}). 
-    The stochastic nature of the merging process also helps explain the 
-    large scatter in the distributions of outer \mden{} profiles. 
-    We illustrate this interesting diversity in Fig~\ref{fig:m100_m10_color}, where 
-    we show the 3-color images of randomly selected massive central galaxies that 
-    have similar \minn{} 
-    ($11.1 \leq \log (M_{\star,\ 10\mathrm{kpc}}/M_{\odot}) < 11.2$)
-    but different \mtot{}.   
-    From the top-left to the bottom-right, the \mtot{} of these galaxies increases
-    from $10^{11.22} M_{\odot}$ to $10^{11.75} M_{\odot}$.
+    The scatter of halo assembly process at fixed halo mass and the stochastic 
+    nature of the galaxy--galaxy mergers also explain the large \textit{intrinsic} 
+    scatter in the outer \mden{} profiles and the diversity seen on the 
+    \mtot{}--\minn{} plane (Fig~\ref{fig:m100_m10_color}).
 
     \textbf{In summary, we reliably detect subtle, but systematic \mhalo{}-dependence 
-    (environmental dependence) of structure in massive central galaxies}, which seems 
-    to be consistent with the expectation of more frequent (minor) mergers in denser 
-    environment. 
-    These minor, non-dissipative mergers do not alter the inner \mden{} profiles 
-    a lot, but are efficient in depositing stars to the outer envelope
-    (e.g. \citealt{Hilz2013}, \citealt{Oogi2013})
-
-    The median profiles shown in Fig~\ref{fig:prof_1} are available in Table~1.
+    (environmental dependence) of \mden{} profiles within 100 kpc in massive central 
+    galaxies}. 
+    Such dependence seems to be consistent with the expectation of more (minor) 
+    mergers in more massive dark matter haloes. 
+    Non-dissipative (minor) mergers should not strongly alter the inner \mden{} 
+    profiles, but can build up the outer halo efficiently
+    (e.g. \citealt{Hilz2013}, \citealt{Oogi2013}).
+
 %% ------------------------------------------------------------------------------------ %%
@@
 
+    Although the comparisons of \mden{} profiles can reveal the environment dependence 
+    directly, it is not straightforward to compare with other observations, model 
+    predictions or numerical simulations. 
+    In this section, we compare the \rbcg{} and \nbcg{} galaxies on 
+    1) the well-know \mstar{}--$R_{\mathrm{e}}$ relation; 
+    2) the \mtot{}--\minn{} plane.
+
+%% ------------------------------------------------------------------------------------ %% 
 \subsubsection{Mass-Size Relation}
@@
 
-    Despite numerous attempts, previous studies have failed to clearly 
-    demonstrate the existence of an environmental dependence of mass-size relation
-    at low-$z$ (e.g. \citealt{Weinmann2009, Nair2010, HCompany13, Cerbrian2014})
-
-    %Despite being the focus of previous investigations (e.g. \citealt{Shankar2013};
-    %\citealt{Leja2013}, \citealt{vdWel2014}), the relation between \mstar{} and 
-    %effective radius (or half-light radius; $R_{\mathrm{e}}$ or $R_{\mathrm{50}}$) 
-    %has yet to provide clear evidence of environmental dependence of structures of 
-    %massive galaxies at low-$z$ (e.g. \citealt{Weinmann2009}, \citealt{Nair2010}, 
-    %\citealt{HCompany13}, \citealt{Cerbrian2014}), and sent controversial messages 
-    %about the pictures at high-$z$ (e.g. \citealt{MCooper2012}, \citealt{Papovich2012}, 
-    %\citealt{Kelkar2015}).
-
-    By using deep HSC images, and by comparing\mden{} profiles directly, 
-    we have shown that the structures of massive galaxies do depend on the masses of 
-    their host halos (see the left panel of Fig~\ref{fig:scaling_relation}). 
-    We now present our results in terms of the more traditional ``mass-size'' relation. 
-    For this purpose, we will use \mtot{} as our ``total'' \mstar{} and the radius 
-    enclosing 50\% of luminosity within 100 kpc ($R_{\mathrm{50}}$; derived from the 
-    $i$-band curve-of-growth) as our ``size''. 
+    The tight relation between \mstar{} and effective radius (or half-light radius; 
+    $R_{\mathrm{e}}$ or $R_{\mathrm{50}}$; e.g. \citealt{Shankar2013, Leja2013, 
+    vdWel2014}) is one of the most important scaling relation for ETGs. 
+    Despite numerous attempts, previous works failed to demonstrate the impact of 
+    environment to the \mstar{}--$R_{\mathrm{e}}$ relation at low-$z$ 
+    (e.g. \citealt{Weinmann2009, Nair2010, HCompany13, Cerbrian2014}; 
+    but see \citealt{Yoon2017}).
+
+    In the last section, we show that the median \mden{} profiles of massive central 
+    galaxies depend on environment. 
+    Therefore, we expect to also see difference in the \mstar{}--$R_{\mathrm{e}}$ 
+    relations of the \rbcg{} and \nbcg{} samples. 
+    For this purpose, we still use \mtot{} as proxy of ``total'' \mstar{}, and adopt 
+    the radius enclosing 50\% of luminosity within 100 kpc ($R_{\mathrm{50}}$; derived 
+    from the $i$-band curve-of-growth) as ``size''. 
     This definition of ``effective radius'' is more robust against structural details, 
     choice of model, and the background subtraction. 
-    Our massive galaxies are large enough that we do not need to worry about the 
-    effects of seeing.
-
-    Fig~\ref{fig:scaling_relation} shows the \mstar{}-size relations for both samples. 
+    Massive galaxies from this sample are large enough so we do not need to worry 
+    about the effects of seeing.
+
+    Left panel of Fig~\ref{fig:scaling_relation} shows the \mtot{}--$R_{\mathrm{50}}$
+    relations for both \rbcg{} (orange--red color) and \nbcg{} (grey--black color). 
     We fit the \logmtot{}-$\log (R_{\mathrm{50}}/\mathrm{kpc})$ relations at 
-    \logmtot{}$\geq 11.6$\footnote{We use MCMC and the ensemble sampler 
-    \texttt{emcee} (\citealt{Emcee}) with initial guesses are based on maximum 
+    \logmtot{}$\geq 11.6$ using MCMC method with the help from ensemble sampler 
+    \texttt{emcee} (\citealt{Emcee})\footnote{The initial guesses are based on maximum 
     likelihood estimates, and we assume reasonable flat priors for parameters.}.
@@
 
-    \noindent As shown in Fig~\ref{fig:scaling_relation}, the slopes of the \mtot{}-size 
-    relations are similar between the two samples, but the normalization of the 
-    \mtot{}-size relation is different for \rbcg{} compared to \nbcg{}. 
-    This result is robust against the ranges of \mstar{}, also the definitions of 
-    ``total'' \mstar{} and  half-light radius\footnote{Using \mstar{} within 120 or 150 
-    kpc, or using the $R_{\mathrm{50}}$ derived within these apertures will not change 
-    the results.}.
+    \noindent As shown in the left panel of Fig~\ref{fig:scaling_relation}, the slopes 
+    of the \mtot{}--$R_{\mathrm{50}}$ relations are similar, but their normalizations 
+    show difference between the \rbcg{} and \nbcg{} galaxies. 
+    This result is robust against the ranges of \mstar{}, also against the definitions 
+    of  ``total'' \mstar{} and half-light radius\footnote{Using \mstar{} within 120 or 
+    150 kpc, or using the $R_{\mathrm{50}}$ derived within these apertures will not 
+    change the results.}.
 
     We qualitatively compare our results with \citealt{HCompany13} (HC13; green solid line) 
-    who studied $z\leq 0.09$ central ETGs in  $14\le$ \logmh{} $<15$ halos. 
-    HC13 used the group catalog by \citet{Yang2007} to estimate \mhalo{} after empirically 
-    convert their \mstar{} from a Kroupa IMF to a Chabrier IMF by applying a constant 
-    -0.05 shift (see \citealt{Bernardi2016}).
-    They estimated the 2-D $R_{\mathrm{e}}$ using single-\ser{} model fitting to SDSS 
+    who studied $z\leq 0.09$ central ETGs in $12.5 \le$ \logmh{} $< 15$ haloes. 
+    HC13 uses the group catalog by \citet{Yang2007} to estimate \mhalo{} and  
+    empirically convert the \mstar{} from a Kroupa IMF to a Chabrier IMF by applying 
+    a constant -0.05 shift (see \citealt{Bernardi2016}).
+    They estimate the 2-D $R_{\mathrm{e}}$ using single-\ser{} model fitting to SDSS 
     images, and derived \mstar{} based on SED fitting using the BC03 (\citealt{BC03}) 
     synthetic population model. 
-    We add $+0.1$dex to the HSC13 results to account for the systematic 
+    We add $+0.1$dex to the HSC13 \mstar{} to account for the systematic 
     difference between their BC03 and our FSPS model (see Appendix~\ref{app:sed}). 
-    The mass-size distributions for both \rbcg{} and \nbcg{} galaxies follow the 
-    HC13 relation reasonably well (with slightly shallower slopes) even at 
-    \logmtot{}$< 11.6$ where our samples start to become incomplete. 
-    In contrast to the present study, HC13 finds no halo mass dependence in the 
-    mass-size relation for $12.5\le$ \logmh{} $<15.0$ halos.
+    The distributions of both \rbcg{} and \nbcg{} galaxies on the 
+    \mtot{}--$R_{\mathrm{50}}$ plane follow the HC13 relation reasonably well 
+    (with slightly shallower slopes) even at \logmtot{}$< 11.6$ where our samples 
+    start to become incomplete. 
+    In contrast to the present study, HC13 finds no environment dependence in the 
+    mass--size relation for central galaxies from $12.5\le$ \logmh{} $<15.0$ haloes.
     A possible explanation for this difference is that the region that strongly depends 
@@
     In conclusion, we confirm that massive central galaxies at $0.3 < z < 0.5$
-    follow \mstar{}-size relations that depend on the masses of their host halos. 
-    Central galaxies in denser environment (higher \mhalo{}) have slightly 
-    larger $R_{\mathrm{50}}$ comparing to ones in smaller haloes at fixed 
+    follow \mtot{}--$R_{\mathrm{50}}$ relations that show halo mass dependence. 
+    At fixed \mtot{}, massive central galaxies in denser environment (higher \mhalo{}) 
+    have slightly larger $R_{\mathrm{50}}$ comparing to ones in smaller haloes at fixed 
     \mtot{}. 
@@
     Our results suggest that: 
-    (1) At fixed \mtot{}, central galaxies in more massive halos tend to have 
+    (1) At fixed \mtot{}, central galaxies in more massive haloes tend to have 
     lower fractions of \mstar{} stored in the inner region; 
-    (2) For massive galaxies with similar \minn{}, the ones in more massive halos on 
+    (2) For massive galaxies with similar \minn{}, the ones in more massive haloes on 
     average have more prominent outer envelopes. 
@@
             present subtle but systematic differences that correlate with \mhalo{}.
-            On average, massive central galaxies in more massive halos have slightly 
+            On average, massive central galaxies in more massive haloes have slightly 
             shallower inner \mden{} profiles and more prominent outer envelope.
@@
             ``in-situ'' mass where it is approximated by the \mstar{} within 10 kpc. 
-            At fixed \minn{} we find that central galaxies in more massive halos 
+            At fixed \minn{} we find that central galaxies in more massive haloes 
             possess much more extended stellar envelope in the outskirts than the ones 
-            in smaller halos. 
+            in smaller haloes. 
             At the same time the ellipticity, and optical color profiles inside 10 kpc 
@@
         \item The \mstar{}-size relation also exhibits a clear environmental 
-            dependence and central galaxies in more massive halos have larger 
+            dependence and central galaxies in more massive haloes have larger 
             $R_{\mathrm{50}}$ at fixed \mtot{}. 
@@
             can be a useful tool in diagnosing the assembly history of these massive 
-            galaxies and the connection with the assembly of their dark matter halos.
+            galaxies and the connection with the assembly of their dark matter haloes.
 
@@
     density profiles of massive central galaxies depend systematically on the mass 
-    of their host dark matter halos. 
+    of their host dark matter haloes. 
     Here we discuss the physical origin, scientific implications, and potential 
@@
     Hence, according to this picture, the outer stellar envelopes of massive centrals 
-    should correlate with the masses of their host halos, in qualitative agreement with
+    should correlate with the masses of their host haloes, in qualitative agreement with
     our findings.
 
-    State of the art hydrodynamic simulations suggest that massive dark matter halos 
+    State of the art hydrodynamic simulations suggest that massive dark matter haloes 
     have central galaxies that have outer stellar envelopes with shallow slopes 
@@
     structurally similar to the compact ``red nuggets'' at high-$z$. 
-    (3) the ``in-situ'' components of simulated central galaxies in massive halos 
+    (3) the ``in-situ'' components of simulated central galaxies in massive haloes 
     from \citet{Cooper13} (the inner ${\sim} 5$ kpc is quite uncertain due to the 
@@
     Our current work can also be combined with weak lensing measurements of the dark 
-    matter halos of massive galaxies and physical insights into the assembly histories 
+    matter haloes of massive galaxies and physical insights into the assembly histories 
     of these galaxies can be gained by comparing with cosmological hydro-simulations 
@@
     only spectroscopic redshift, the samples in the three GAMA fields, and the \rbcg{} 
-    samples without the ones in very massive halos ($\lambda > 40$).  
+    samples without the ones in very massive haloes ($\lambda > 40$).  
     Limited by space, we do not show these results here, but they all verify the 

### 2017-07-13 draft/paper2.tex
Edit results 4

@@
     Section~\ref{sec:discussion}.
-%% ------------------------------------------------------------------------------------ %%
 
@@
     topic to investigate in the future.
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
+  \begin{figure*}
+      \centering 
+      \includegraphics[width=\textwidth]{fig/redbcg_ell_color_environ}
+      \caption{
+          Radial variations in ellipticity and optical colors for massive galaxies. 
+          The format of this figure is similar to the right hand side of 
+          Fig~\ref{fig:prof_1}. 
+          Top panels show the ellipticity profile, middle panels show $g-r$, and lower 
+          panels show $g-i$. 
+          We compare our results with those from \citet{Tal2011} based on stacking 
+          large samples of luminous red galaxies in SDSS at $z{\sim} 0.4$ 
+          (solid blue line on top panel). 
+          We also compare with the results from a stacking analysis of nearby massive 
+          galaxies with high concentration index ($C>2.6$) in 
+          \citet[][blue dash lines on the top and middle panels]{DSouza2014}. 
+          Finally, we also compare with the average $g-r$ and $g-i$ color profiles 
+          from a large sample of nearby elliptical galaxies in \citet[][blue, solid 
+          lines on the middle and bottom panels]{LaBarbera2010}.
+          }
+      \label{fig:ell_color}
+  \end{figure*}
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
+\subsection{Ellipticity and Color Profiles}
+    \label{ssec:ell_color}
+
+    We now study how the ellipticities (computed via \texttt{Ellipse}) and $k$-corrected 
+    optical colors of massive galaxies vary with radius. 
+    We also study whether or these radial trends differ between our various samples. 
+    These quantities contain interesting information about the physical processes that 
+    shape galaxies, but here we study them mainly with two goals in mind:
+
+    \begin{enumerate}
+
+        \item To see whether the ellipticity profile depends strongly on environment, 
+            and to see whether or not the fact that we use an using average isophotal 
+            shape for our our 1-D \mden{} profiles has any impact on our results.
+
+        \item To verify that the average color gradient does not depend strongly on 
+            the environment and that is not steep enough to cause a problem with our 
+            choice the assumption that it is reasonable to use average \m2l for 
+            comparing massive galaxies. 
+            We extract color profiles by applying the isophotes in $i$-band to images 
+            in other bands in ``forced photometry'' manner.
+
+    \end{enumerate}
+
+    We compute ellipticities and color profiles in the radial range of 5-50 kpc 
+    (this is the range where we can safely ignore differences in sky subtraction and 
+    seeing across different bands). 
+    We apply Galactic extinction and $k$-correction to both $g-r$ and $g-i$ color 
+    profiles; the $k$-correction values are also from \texttt{iSEDFit} results.
+    We show the average ellipticity, $g-r$, and $g-i$ color profiles for the 
+    \mtot{}-matched (\minn{}-matched) samples of \rbcg{} and \nbcg{} galaxies on the 
+    left (right) side of \ref{fig:ell_color}. 
+    We also compare our results with previous work based on stacking SDSS galaxies 
+    (e.g. \citealt{LaBarbera2010, Tal2011, DSouza2014}).
+
+    We find that in general, the ellipticities of massive galaxies increases with 
+    radius from $e\le 0.2$ around 5-10 kpc to $e{\sim} 0.3$ at 40-50 kpc. 
+    This is consistent with previous 2-D modeling results from \citet{Huang2013a}. 
+    The ellipticity profiles of the \mtot{}-matched samples are very similar at 
+    $r<50$ kpc (2-3$\times R_{\mathrm{e}}$ for their \mstar{}). 
+    However, for the \minn{}-matched samples, the \rbcg{} galaxies have higher 
+    ellipticity than the \nbcg{} ones at $r > 10$ kpc, while their inner ellipticity 
+    profiles are very similar.  
+    This further hints that massive central galaxies in different halos but with 
+    similar ``in-situ'' mass may experience different late-time merging histories. 
+    Overall, the relative low ellipticity value and the fact that the ellipticity 
+    gradients are shallow lead us to conclude that the use of an average 
+    isophotal ellipticity is fine for this present study.
+
+    Previous attempts to constrain ellipticity gradients have relied on image 
+    stacking techniques (e.g. \citealt{Tal2011}, \citealt{DSouza2015}). 
+    Compared to our measurements, we find that stacked ellipticity profiles tend to 
+    underestimate the ellipticity in the outskirt. 
+    Ellipticity profiles contain additional information about the assembly histories 
+    and in future work, it would be of interest to compare our ellipticity profiles 
+    with predictions from hydrodynamic simulations such as Illustris 
+    (\citealt{Vogelsberger2014}, \citealt{Genel2014}) or \textit{Horizon-AGN} 
+    (\citealt{Dubois2014}).
+
+    In terms of color gradients, we find shallow and negative gradients of median 
+    $g-r$ and $g-i$ color profiles for both \rbcg{} and \nbcg{} galaxies. 
+    For both \mtot{}- and \minn{}-matched samples, we find no significant difference
+    in their median color profiles, which supports the assumption of using single 
+    average \m2l{} value to estimate \mden{} profiles.
+    The median $g-r$ color profiles are quite consistent with those based on 
+    stacked SDSS images. 
+    For the $g-i$ profiles, the HSC ones show steeper gradients than the SDSS ones, 
+    however, it is important to point out that the SDSS $i$-band suffers from the 
+    so-called ``red-halo'' effect of (e.g. \citealt{Wu2005}, \citealt{Tal2011}) that 
+    could make the SDSS color appears redder. 
+    In contrast, HSC $i$-band image do not suffer from this effect (thanks to thick 
+    CCDs), therefore can help provide more accurate color estimates.
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
+\section{Discussion}
+    \label{sec:discussion}
+
+    \song{Keep the relevant session from previous draft, need some works.}
+    By using deep imaging from the HSC survey we have shown that the stellar mass 
+    density profiles of massive central galaxies depend systematically on the mass 
+    of their host dark matter haloes. 
+    Here we discuss the physical origin, scientific implications, and potential 
+    caveats of this result.
+
+%% ------------------------------------------------------------------------------------ %%
+
+\subsection{The ``Two phase'' Formation Scenario of Massive Galaxies and the 
+            Build-Up of Outer Envelopes}
+
+    Our results are consistent with the picture that massive central galaxies form via 
+    a ``two-phase'' scenario. 
+    According to this theory, the cores of massive galaxies were formed at $z{\sim} 2$ 
+    during an intense period of in-situ star formation. 
+    The outskirts of massive galaxies are then built up via a more gradual second 
+    phase of evolution (the ``ex-situ'' phase) which is dominated by mass growth via 
+    the accretion of satellite systems. 
+    Non-dissipative minor mergers mostly deposit stars on the outskirts of the 
+    centrals and do not have large impact on the central \mden{} profile 
+    (e.g. \citealt{Oogi2013, Bedorf2013}). 
+    Hence, according to this picture, the outer stellar envelopes of massive centrals 
+    should correlate with the masses of their host haloes, in qualitative agreement with
+    our findings.
+
+    State of the art hydrodynamic simulations suggest that massive dark matter haloes 
+    have central galaxies that have outer stellar envelopes with shallow slopes 
+    (e.g. \citealt{Pillepich2014}). 
+    This is consistent with the results in Fig \ref{fig:prof_1}.
+
+    Meanwhile, these simulation also point out that the fraction of accreted stars 
+    increases steeply with total \mstar{} and that the ``ex-situ'' component
+    starts to dominate the \mden{} profiles around $R_{\mathrm{e}}$ for 
+    \logms{}$\geq 11.5$ galaxies. 
+    In this work, we find that the median \mden{} profiles of \rbcg{} and \nbcg{} 
+    samples start to show differences around 15-20 kpc, which is close to 
+    their $R_{\mathrm{e}}$. 
+    Furthermore, the environmental dependence of our median \mden{} profiles 
+    becomes more significant in our highest \mtot{} bin (see Fig \ref{fig:prof_4}). 
+    These results all align with the picture that the \mhalo{}-dependence of the 
+    \mden{} profiles of massive galaxies is driven by the variations in the 
+    ``ex-situ'' component at large radii.
+
+    We now investigate to what degree our assumption that the inner 10 kpc \mstar{}
+    corresponds to an in-situ mass.    
+    Fig \ref{fig:discussion_1} compares the median \mden{} profiles of the 
+    galaxies in two \mtot{} bins 
+    ($11.4\leq$\logmtot{}$<11.6$ and $11.6\leq$\logmtot{}$<11.8$) with 
+    (1) the median \mden{} profiles of massive ETGs at $1.0 < z < 1.5$ in
+    \citealt{Patel2013} since they are considered as the progenitors of 
+    ${\sim} 10^{11.5} M_{\odot}$ ETGs at $z=0$.    
+    (2) the inner components of $z{\sim} 0$ ellipticals from 2-D decomposition 
+    (\citealt{Huang2013a}).
+    As proxy of the in-situ components, \citet{Huang2013b} showed they are 
+    structurally similar to the compact ``red nuggets'' at high-$z$. 
+    (3) the ``in-situ'' components of simulated central galaxies in massive haloes 
+    from \citet{Cooper13} (the inner ${\sim} 5$ kpc is quite uncertain due to the 
+    resolution).  
+    The comparison confirms that \minn{} should be reasonable proxy of the 
+    ``in-situ'' mass\footnote{We convert these \mden{} profiles to the same 
+    Chabrier IMF; but there are still differences in median \mstar{} and 
+    details in the \m2l{} estimates}.  
+    More importantly, it shows that the \mden{} profile at 
+    $\mathrm{R} > 15$-20 kpc is likely dominated by stars that are not related 
+    to the ``in-situ'' processes.
+
+    We also compare with a uniquely massive BCG at high redshift: 
+    a ${\sim} 10^{11.4} M_{\odot}$ BCG with distinctive ``cD''-like envelope at 
+    $z{\sim} 1.1$ (\citealt{Liu2013}).  
+    Its \mden{} profile follows the median profile of $11.6\leq$\logmtot{}$<11.8$ 
+    massive galaxies nicely inside 10-15 kpc, but becomes much steeper in the outskirt.  
+    This unique object may present an interesting case where the inner ``core'' of a 
+    massive BCGs is already in pace at $z{\sim} 1$ when its extended envelope is still
+    under construction.
+    More BCGs like this at $0.5 < z < 1.0$ can shed light on this intriguing 
+    process, and help us confirm whether the environmental dependence of structure 
+    has already emerged within massive galaxies at higher redshift 
+    (e.g. \citealt{Papovich2012})
+%% ------------------------------------------------------------------------------------ %%
 
@@
    \end{itemize}
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %% 
-\section{Discussion}
-    \label{sec:discussion}
-
-    \song{Keep the relevant session from previous draft, need some works.}
-    By using deep imaging from the HSC survey we have shown that the stellar mass 
-    density profiles of massive central galaxies depend systematically on the mass 
-    of their host dark matter haloes. 
-    Here we discuss the physical origin, scientific implications, and potential 
-    caveats of this result.
-
-%% ------------------------------------------------------------------------------------ %%
-
-\subsection{The ``Two phase'' Formation Scenario of Massive Galaxies and the 
-            Build-Up of Outer Envelopes}
-
-    Our results are consistent with the picture that massive central galaxies form via 
-    a ``two-phase'' scenario. 
-    According to this theory, the cores of massive galaxies were formed at $z{\sim} 2$ 
-    during an intense period of in-situ star formation. 
-    The outskirts of massive galaxies are then built up via a more gradual second 
-    phase of evolution (the ``ex-situ'' phase) which is dominated by mass growth via 
-    the accretion of satellite systems. 
-    Non-dissipative minor mergers mostly deposit stars on the outskirts of the 
-    centrals and do not have large impact on the central \mden{} profile 
-    (e.g. \citealt{Oogi2013, Bedorf2013}). 
-    Hence, according to this picture, the outer stellar envelopes of massive centrals 
-    should correlate with the masses of their host haloes, in qualitative agreement with
-    our findings.
-
-    State of the art hydrodynamic simulations suggest that massive dark matter haloes 
-    have central galaxies that have outer stellar envelopes with shallow slopes 
-    (e.g. \citealt{Pillepich2014}). 
-    This is consistent with the results in Fig \ref{fig:prof_1}.
-
-    Meanwhile, these simulation also point out that the fraction of accreted stars 
-    increases steeply with total \mstar{} and that the ``ex-situ'' component
-    starts to dominate the \mden{} profiles around $R_{\mathrm{e}}$ for 
-    \logms{}$\geq 11.5$ galaxies. 
-    In this work, we find that the median \mden{} profiles of \rbcg{} and \nbcg{} 
-    samples start to show differences around 15-20 kpc, which is close to 
-    their $R_{\mathrm{e}}$. 
-    Furthermore, the environmental dependence of our median \mden{} profiles 
-    becomes more significant in our highest \mtot{} bin (see Fig \ref{fig:prof_4}). 
-    These results all align with the picture that the \mhalo{}-dependence of the 
-    \mden{} profiles of massive galaxies is driven by the variations in the 
-    ``ex-situ'' component at large radii.
-
-    We now investigate to what degree our assumption that the inner 10 kpc \mstar{}
-    corresponds to an in-situ mass.    
-    Fig \ref{fig:discussion_1} compares the median \mden{} profiles of the 
-    galaxies in two \mtot{} bins 
-    ($11.4\leq$\logmtot{}$<11.6$ and $11.6\leq$\logmtot{}$<11.8$) with 
-    (1) the median \mden{} profiles of massive ETGs at $1.0 < z < 1.5$ in
-    \citealt{Patel2013} since they are considered as the progenitors of 
-    ${\sim} 10^{11.5} M_{\odot}$ ETGs at $z=0$.    
-    (2) the inner components of $z{\sim} 0$ ellipticals from 2-D decomposition 
-    (\citealt{Huang2013a}).
-    As proxy of the in-situ components, \citet{Huang2013b} showed they are 
-    structurally similar to the compact ``red nuggets'' at high-$z$. 
-    (3) the ``in-situ'' components of simulated central galaxies in massive haloes 
-    from \citet{Cooper13} (the inner ${\sim} 5$ kpc is quite uncertain due to the 
-    resolution).  
-    The comparison confirms that \minn{} should be reasonable proxy of the 
-    ``in-situ'' mass\footnote{We convert these \mden{} profiles to the same 
-    Chabrier IMF; but there are still differences in median \mstar{} and 
-    details in the \m2l{} estimates}.  
-    More importantly, it shows that the \mden{} profile at 
-    $\mathrm{R} > 15$-20 kpc is likely dominated by stars that are not related 
-    to the ``in-situ'' processes.
-
-    We also compare with a uniquely massive BCG at high redshift: 
-    a ${\sim} 10^{11.4} M_{\odot}$ BCG with distinctive ``cD''-like envelope at 
-    $z{\sim} 1.1$ (\citealt{Liu2013}).  
-    Its \mden{} profile follows the median profile of $11.6\leq$\logmtot{}$<11.8$ 
-    massive galaxies nicely inside 10-15 kpc, but becomes much steeper in the outskirt.  
-    This unique object may present an interesting case where the inner ``core'' of a 
-    massive BCGs is already in pace at $z{\sim} 1$ when its extended envelope is still
-    under construction.
-    More BCGs like this at $0.5 < z < 1.0$ can shed light on this intriguing 
-    process, and help us confirm whether the environmental dependence of structure 
-    has already emerged within massive galaxies at higher redshift 
-    (e.g. \citealt{Papovich2012})
 %% ------------------------------------------------------------------------------------ %%

### 2017-07-13 draft/paper2.tex
Edit result 4

@@
     galaxies depend on environment. 
-    Therefore, we expect to also see difference in the \mstar{}--$R_{\mathrm{e}}$ 
+    We therefore expect to also see difference in the \mstar{}--$R_{\mathrm{e}}$ 
     relations of the \rbcg{} and \nbcg{} samples. 
@@
 
-    We qualitatively compare our results with \citealt{HCompany13} (HC13; green solid line) 
-    who studied $z\leq 0.09$ central ETGs in $12.5 \le$ \logmh{} $< 15$ haloes. 
-    HC13 uses the group catalog by \citet{Yang2007} to estimate \mhalo{} and  
-    empirically convert the \mstar{} from a Kroupa IMF to a Chabrier IMF by applying 
-    a constant -0.05 shift (see \citealt{Bernardi2016}).
+    We qualitatively compare our results with \citealt{HCompany13} (HC13; 
+    green solid line) who studied $z\leq 0.09$ central ETGs in 
+    $12.5 \le$ \logmh{} $< 15$ haloes. 
+    HC13 uses the group catalog by \citet{Yang2007} to estimate \mhalo{}. 
     They estimate the 2-D $R_{\mathrm{e}}$ using single-\ser{} model fitting to SDSS 
@@
     synthetic population model. 
+    The \mstar{} estimates are empirically converted from a Kroupa IMF to a Chabrier 
+    IMF by applying a constant -0.05 shift (see \citealt{Bernardi2016}).
     We add $+0.1$dex to the HSC13 \mstar{} to account for the systematic 
@@
     \mtot{}--$R_{\mathrm{50}}$ plane follow the HC13 relation reasonably well 
-    (with slightly shallower slopes) even at \logmtot{}$< 11.6$ where our samples 
+    (with slightly shallower slopes), even at \logmtot{}$< 11.6$ where our samples 
     start to become incomplete. 
@@
     mass--size relation for central galaxies from $12.5\le$ \logmh{} $<15.0$ haloes.
-    A possible explanation for this difference is that the region that strongly depends 
-    on halo mass is the low surface brightness outer envelope where the stars are 
-    mostly assembled through multiple mergers. 
-    This region is difficult to detect on shallow SDSS images, but the much deeper 
-    HSC images can provide accurate measurements of total \mstar{} and size.
-
-    In conclusion, we confirm that massive central galaxies at $0.3 < z < 0.5$
-    follow \mtot{}--$R_{\mathrm{50}}$ relations that show halo mass dependence. 
+    The \mstar{} and $R_{\mathrm{e}}$ in HC13 are based on much shallower SDSS images
+    that can not constrain the environment-sensitive outer stellar halos well. 
+    Detailed analysis on this topic is beyond the scope of this work, but we briefly 
+    demonstrate this using the \rbcg{} and \nbcg{} galaxies that overlap with the GAMA
+    survey (please see Appendix~\ref{app:gama} for details). 
+    We matched the two samples using the \mstar{} measured using single-\ser{} 2-D
+    model by the GAMA team (\citealt{Kelvin2012}). 
+    At fixed \mgama{}, the \rbcg{} galaxies display much more significant stellar 
+    halo despite they have very similar inner \mden{} profiles.  
+    This shows again that the deeper HSC images has unique advantage in studying the
+    connection between the assembly of massive galaxies and their dark matter haloes.
+
+    In conclusion, we confirm that the \mtot{}--$R_{\mathrm{50}}$ relation of massive
+    central galaxies at $0.3 < z < 0.5$ depends on halo mass. 
     At fixed \mtot{}, massive central galaxies in denser environment (higher \mhalo{}) 
@@
 
-    We also investigate the relationship between \mstar{} for two different
-    fixed physical apertures (\mtot{} v.s. \minn{}) as alternative tool to help us 
-    understand the relationship between \mhalo{} and the assembly history of massive
-    galaxies.   
-    Comparing to the mass-size relation, this relation is not affected by the 
-    ambiguous definition of ``size'', and is much easier to apply to larger samples 
-    and to simulations.
-
-    The right panel of Fig \ref{fig:scaling_relation} compares \mtot{} and \minn{}. 
-    We find that our \rbcg{} and \nbcg{} occupy different locations within this plane,
-    and follow different best-fit \mtot{} - \minn{} relations. 
-    For \rbcg{} galaxies we find:
+    Now we investigate the relationship between \mstar{} within two elliptical 
+    apertures (\mtot{} v.s. \minn{}) as alternative tool to help us explore the 
+    structure and assembly of massive galaxies.
+    Comparing to the mass--size relation, this relation is not affected by the 
+    ambiguous definition of ``size'', and it is easier to apply it to larger 
+    samples or numerical simulations.
+
+    The right panel of Fig \ref{fig:scaling_relation} compares the \rbcg{} and \nbcg{}
+    galaxies on the \mtot{}--\minn{} plane.
+    We show that these two samples occupy slightly different locations on this plane,
+    and follow different best--fit \mtot{}--\minn{} relations. 
+    For \rbcg{} galaxies with \logmtot{}$>11.6$ we find:
 
@@
 
-    We have checked that our results are unchanged if we replace the \minn{} with 
-    \mstar{} within 5 or 15 kpc apertures. 
-    Although the $M_{\star, 5\ \mathrm{kpc}}$ values are less reliable than \minn{} 
-    due to the impacts of seeing, the relation using $M_{\star, 5\ \mathrm{kpc}}$ shows 
-    more significant \mhalo{} dependence at the high-mass end.
-    Also, best-fit relation using the full \mtot{} range results in even shallower 
-    slope for the \rbcg{} galaxies.
-
-    Our results suggest that: 
+    These results are robust against the \mtot{} range for fitting, and they will not 
+    be affected if we replace the \minn{} with \mstar{} within 5 or 15 kpc apertures
+    or replace the \mtot{} with \mstar{} within 120 or 150 kpc apertures.  
+    The \mtot{}--$M_{\star, 5\ \mathrm{kpc}}$ relation actually suggests clearer 
+    \mhalo{}-dependence at high-\mtot{} end, but the $M_{\star, 5\ \mathrm{kpc}}$ 
+    are more vulnerable to the impact from seeing than \minn{}.
+
+    We conclude that: 
     (1) At fixed \mtot{}, central galaxies in more massive haloes tend to have 
@@
 
-    At the same time, we also find \rbcg{} galaxy tends to have lower \mstar{} within 
-    inner 5-10 kpc and shallower inner \mden{} profile than the \nbcg{} one at 
-    fixed \mtot{}. 
-    Although the HSC images do not have sufficient resolution to investigate this in 
-    details, it is worth pointing out that this difference could be physically 
-    interesting. 
-    Observations of compact quiescent galaxies at high-$z$ often reveal higher 
-    \mden{} in the central region than their descendants, and certain process need to  
-    be responsible for reducing the central \mden{} (e.g. strong adiabatic expansion 
-    induced by powerful AGN feedback; \citealt{Fan2008}).
+    Meanwhile, we find \rbcg{} galaxy tends to have lower \mstar{} within 10--15 kpc 
+    and shallower inner \mden{} profile than the \nbcg{} one at fixed \mtot{}. 
+    Although the HSC can not resolve the central region of these massive galaxies, 
+    such difference could have interesting physical implications. 
+    Observations of compact quiescent galaxies at high-$z$ tend to suggest higher 
+    \mden{} in the central region than their descendants, hence it is necessary to 
+    have certain process to reduce the central \mden{} (e.g. strong adiabatic expansion 
+    induced by powerful AGN feedback; \citealt{Fan2008}) to match the inner \mden{} 
+    profiles of massive central galaxies at low-$z$.
     Coalesce of super-massive black hoes (SMBHs) at the end of major merger, which is 
     common in the assembly history of massive galaxies, can also flatten the central 
-    \mden{} profile (e.g. \citealt{Milosavljevi2002}).
+    \mden{} profile via efficient scattering effect (e.g. \citealt{Milosavljevi2002}).
     On the right side of Fig \ref{fig:scaling_relation}, we find a few \rbcg{} galaxies 

### 2017-07-13 draft/paper2.tex
Edit result 5

@@
 
-    We now study how the ellipticities (computed via \texttt{Ellipse}) and $k$-corrected 
-    optical colors of massive galaxies vary with radius. 
-    We also study whether or these radial trends differ between our various samples. 
-    These quantities contain interesting information about the physical processes that 
-    shape galaxies, but here we study them mainly with two goals in mind:
-
-    \begin{enumerate}
-
-        \item To see whether the ellipticity profile depends strongly on environment, 
-            and to see whether or not the fact that we use an using average isophotal 
-            shape for our our 1-D \mden{} profiles has any impact on our results.
-
-        \item To verify that the average color gradient does not depend strongly on 
-            the environment and that is not steep enough to cause a problem with our 
-            choice the assumption that it is reasonable to use average \m2l for 
-            comparing massive galaxies. 
-            We extract color profiles by applying the isophotes in $i$-band to images 
-            in other bands in ``forced photometry'' manner.
-
-    \end{enumerate}
-
-    We compute ellipticities and color profiles in the radial range of 5-50 kpc 
-    (this is the range where we can safely ignore differences in sky subtraction and 
-    seeing across different bands). 
-    We apply Galactic extinction and $k$-correction to both $g-r$ and $g-i$ color 
-    profiles; the $k$-correction values are also from \texttt{iSEDFit} results.
+    In Paper~1, we show that the ellipticity of outer stellar halo in massive galaxy 
+    steadily increases with \mtot{}, while the rest--frame color gradients do not show 
+    clear \mtot{}-dependence. 
+    Both these results provide us more insights about the assembly of massive galaxies. 
+    Here we quickly look into the environment dependence of ellipticity and 
+    rest--frame color profiles (Figure~\ref{fig:ell_color}).
+
+    We focus on ellipticity and color profiles within 5--60 kpc where we can safely 
+    ignore differences in sky subtraction and seeing across different bands. 
+    We apply Galactic extinction and $k$-correction to both $(g-r)$ and $(g-i)$ color 
+    profiles.
     We show the average ellipticity, $g-r$, and $g-i$ color profiles for the 
     \mtot{}-matched (\minn{}-matched) samples of \rbcg{} and \nbcg{} galaxies on the 
-    left (right) side of \ref{fig:ell_color}. 
-    We also compare our results with previous work based on stacking SDSS galaxies 
+    left (right) side of \ref{fig:ell_color} along with comparisons with previous 
+    works based on stacked SDSS galaxies 
     (e.g. \citealt{LaBarbera2010, Tal2011, DSouza2014}).
 
-    We find that in general, the ellipticities of massive galaxies increases with 
-    radius from $e\le 0.2$ around 5-10 kpc to $e{\sim} 0.3$ at 40-50 kpc. 
-    This is consistent with previous 2-D modeling results from \citet{Huang2013a}. 
-    The ellipticity profiles of the \mtot{}-matched samples are very similar at 
-    $r<50$ kpc (2-3$\times R_{\mathrm{e}}$ for their \mstar{}). 
-    However, for the \minn{}-matched samples, the \rbcg{} galaxies have higher 
-    ellipticity than the \nbcg{} ones at $r > 10$ kpc, while their inner ellipticity 
-    profiles are very similar.  
-    This further hints that massive central galaxies in different halos but with 
-    similar ``in-situ'' mass may experience different late-time merging histories. 
-    Overall, the relative low ellipticity value and the fact that the ellipticity 
-    gradients are shallow lead us to conclude that the use of an average 
-    isophotal ellipticity is fine for this present study.
-
-    Previous attempts to constrain ellipticity gradients have relied on image 
-    stacking techniques (e.g. \citealt{Tal2011}, \citealt{DSouza2015}). 
-    Compared to our measurements, we find that stacked ellipticity profiles tend to 
-    underestimate the ellipticity in the outskirt. 
-    Ellipticity profiles contain additional information about the assembly histories 
-    and in future work, it would be of interest to compare our ellipticity profiles 
-    with predictions from hydrodynamic simulations such as Illustris 
-    (\citealt{Vogelsberger2014}, \citealt{Genel2014}) or \textit{Horizon-AGN} 
-    (\citealt{Dubois2014}).
-
-    In terms of color gradients, we find shallow and negative gradients of median 
-    $g-r$ and $g-i$ color profiles for both \rbcg{} and \nbcg{} galaxies. 
-    For both \mtot{}- and \minn{}-matched samples, we find no significant difference
-    in their median color profiles, which supports the assumption of using single 
-    average \m2l{} value to estimate \mden{} profiles.
-    The median $g-r$ color profiles are quite consistent with those based on 
-    stacked SDSS images. 
-    For the $g-i$ profiles, the HSC ones show steeper gradients than the SDSS ones, 
-    however, it is important to point out that the SDSS $i$-band suffers from the 
-    so-called ``red-halo'' effect of (e.g. \citealt{Wu2005}, \citealt{Tal2011}) that 
-    could make the SDSS color appears redder. 
-    In contrast, HSC $i$-band image do not suffer from this effect (thanks to thick 
-    CCDs), therefore can help provide more accurate color estimates.
-%% ------------------------------------------------------------------------------------ %%
-
+    These results show:
+
+    \begin{itemize}
+
+        \item Once matched at fixed \mtot{}, the \rbcg{} and \nbcg{} galaxies 
+            show similar average ellipticity profiles. 
+            There is hint that suggests the central galaxies from more massive 
+            haloes become slightly more elongated at $R>50$ kpc than the ones 
+            in less massive halos with similar \mtot{}. 
+            However, the uncertainties in the current profiles make it not 
+            conclusive.
+
+        \item For the \minn{}-matched samples, the \rbcg{} galaxies show higher
+            average ellipticity than the \nbcg{} ones at $R > 10$ kpc. 
+            The average ellipticities in the inner region are very similar. 
+            This further suggests that the more elongated outer stellar haloes 
+            of massive halos relate to the accreted stars.
+
+        \item For the rest--frame color gradients, we find shallow and negative 
+            gradients for both \rbcg{} and \nbcg{} galaxies using both colors.
+            We find no significant difference for both the \mtot{}- and 
+            \minn{}--matched samples within 60 kpc.
+
+    \end{itemize}
+
+    Besides these conclusions, these comparisons also suggest:
+
+    \begin{itemize}
+
+        \item The smooth ellipticity profile and its shallow gradient supports 
+            the idea of using the flux-weighted average isophotal shape to 
+            extract 1-D profiles of massive galaxies.
+
+        \item The similarity of average rest-frame color profiles between the 
+            \rbcg{} and \nbcg{} samples suggests that \mden{} profiles based on 
+            single average \m2l{} will not bias our comparisons.
+
+    \end{itemize}
 %% ------------------------------------------------------------------------------------ %%

### 2017-07-13 draft/paper2.tex
Edit summary

@@
 
-        \item a 10 kpc radii (hereafter noted \minn{}) as proxy of the ``in-situ'' 
+        \item a 10 kpc radii (hereafter noted \minn{}) as proxy of the ``in situ'' 
             stellar component. 
@@
     of massive galaxies while treat \minn{} as a rough indicator of the mass of the 
-    \textit{in-situ} component.
+    \textit{in situ} component.
 
@@
     Therefore it is interesting to ask, for massive galaxies that \textbf{contain 
-    similar \mstar{} in the \textit{in-situ} component}, how does environment affect 
+    similar \mstar{} in the \textit{in situ} component}, how does environment affect 
     their subsequent mass assembly?
-    Assuming \minn{} is reasonable tracer of the ``in-situ'' mass, we compare the 
+    Assuming \minn{} is reasonable tracer of the ``in situ'' mass, we compare the 
     \mden{} profiles of \minn{}-matched samples (right panel of Fig~\ref{fig:prof_1}).  
@@
     The \mstar{} and $R_{\mathrm{e}}$ in HC13 are based on much shallower SDSS images
-    that can not constrain the environment-sensitive outer stellar halos well. 
+    that can not constrain the environment-sensitive outer stellar haloes well. 
     Detailed analysis on this topic is beyond the scope of this work, but we briefly 
@@
             haloes become slightly more elongated at $R>50$ kpc than the ones 
-            in less massive halos with similar \mtot{}. 
+            in less massive haloes with similar \mtot{}. 
             However, the uncertainties in the current profiles make it not 
@@
             This further suggests that the more elongated outer stellar haloes 
-            of massive halos relate to the accreted stars.
+            of massive haloes relate to the accreted stars.
 
@@
     According to this theory, the cores of massive galaxies were formed at $z{\sim} 2$ 
-    during an intense period of in-situ star formation. 
+    during an intense period of in situ star formation. 
     The outskirts of massive galaxies are then built up via a more gradual second 
@@
     We now investigate to what degree our assumption that the inner 10 kpc \mstar{}
-    corresponds to an in-situ mass.    
+    corresponds to an in situ mass.    
     Fig \ref{fig:discussion_1} compares the median \mden{} profiles of the 
@@
     (\citealt{Huang2013a}).
-    As proxy of the in-situ components, \citet{Huang2013b} showed they are 
+    As proxy of the in situ components, \citet{Huang2013b} showed they are 
     structurally similar to the compact ``red nuggets'' at high-$z$. 
-    (3) the ``in-situ'' components of simulated central galaxies in massive haloes 
+    (3) the ``in situ'' components of simulated central galaxies in massive haloes 
     from \citet{Cooper13} (the inner ${\sim} 5$ kpc is quite uncertain due to the 
@@
     The comparison confirms that \minn{} should be reasonable proxy of the 
-    ``in-situ'' mass\footnote{We convert these \mden{} profiles to the same 
+    ``in situ'' mass\footnote{We convert these \mden{} profiles to the same 
     Chabrier IMF; but there are still differences in median \mstar{} and 
@@
     $\mathrm{R} > 15$-20 kpc is likely dominated by stars that are not related 
-    to the ``in-situ'' processes.
+    to the ``in situ'' processes.
 
@@
 %% ------------------------------------------------------------------------------------ %% 
-   \song{This part is directly copied from Jenny's txt file, not the right place.}    
-   \begin{itemize}
-
-         \item At fixed \mstar{} evaluate within 100 kpc, we find that massive central 
-            galaxies display \mden{} profiles that are not self-similar and which 
-            present subtle but systematic differences that correlate with \mhalo{}.
-            On average, massive central galaxies in more massive haloes have slightly 
-            shallower inner \mden{} profiles and more prominent outer envelope.
-
-        \item We also study how the \mden{} profiles vary with \mhalo{} at fixed 
-            ``in-situ'' mass where it is approximated by the \mstar{} within 10 kpc. 
-            At fixed \minn{} we find that central galaxies in more massive haloes 
-            possess much more extended stellar envelope in the outskirts than the ones 
-            in smaller haloes. 
-            At the same time the ellipticity, and optical color profiles inside 10 kpc 
-            show little to no dependence on environment.
-
-        \item The \mstar{}-size relation also exhibits a clear environmental 
-            dependence and central galaxies in more massive haloes have larger 
-            $R_{\mathrm{50}}$ at fixed \mtot{}. 
-            We suggest that the relation between \mtot{} and \minn{}\footnote{or any 
-            better proxy of total \mstar{} and the mass formed in the ``in-situ'' phase.} 
-            can be a useful tool in diagnosing the assembly history of these massive 
-            galaxies and the connection with the assembly of their dark matter haloes.
-
-   \end{itemize}
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %% 
 \section{Summary and Conclusions}
@@
 
-    \song{From old draft, need some works}
-
-    In this work, we study how environment (halo mass) affects the stellar mass density 
-    profiles of massive central galaxies using deep images from the Subaru HSC 
-    survey. 
-    With the help of this high-quality and wide area data set, we directly map the 
-    stellar mass distributions of ${\sim}7000$ massive central galaxies at 
-    $0.3 < z < 0.5$ out to $>100$ kpc without resorting to stacking techniques. 
-    We group massive central galaxies into two categories based on their host halo 
-    mass (\mhalo{}$\simgt 10^{14.2} M_{\odot}$ and \mhalo{}$\simlt 10^{14} M_{\odot}$). 
-    Our main results are:
+    Using the high-quality images from the first $\sim100$ deg$^2$ data of the 
+    Hyper Suprime-Cam Subaru Strategic Program, we group a large sample of massive 
+    central galaxies at $0.3 < z < 0.5$ into two categories based on their dark matter
+    halo mass (\mhalo{}$\simgt 10^{14.2} M_{\odot}$ and 
+    \mhalo{}$\simlt 10^{14} M_{\odot}$), and study how their stellar mass distributions 
+    out to 100 kpc depend on their environments (or \mhalo{}). 
+    The main results are:
 
     \begin{enumerate}
-        \item We find that the ``total'' \mstar{} of these massive galaxies can be 
-            significantly underestimated with shallow imaging data such as SDSS and/or 
-            imperfect model assumption (e.g. the \texttt{cModel} or single-\ser{}) 
-            are used. 
-            In contrast to previous work, our results do not depend on stacking or any 
-            parametric models. 
-            Moreover, the level of such underestimation could also depend on the 
-            stellar mass and on halo mass. 
-            This should be carefully taken into account when discussing topics such 
-            as the evolution of the galaxy SMF.
-
-        \item We show that the \mden{} profiles of massive galaxies are generally quite 
-            smooth out to 10 kpc but that there is a large but continuous scatter in the 
-            amount of light in their outskirts. 
-            {\bf KEEP? We argue that ``cD'' galaxies simply represent the tail end of a 
-            distribution but that they are not a distinct class of massive galaxies.}
-
-        \item {\bf How do profiles depend on Mstar?}
+
+        \item At fixed \mtot{}, we find that massive central galaxies display \mden{} 
+            profiles that have large intrinsic scatter in the outer stellar haloes and 
+            present subtle but systematic trend with \mhalo{}.
+            On average, massive central galaxies in more massive haloes have slightly 
+            shallower inner \mden{} profiles and more prominent outer haloes. 
+            This suggests that the environment affects the assembly of massive central
+            galaxies at fixed ``total'' stellar mass.
+
+        \item At fixed \minn{}, massive central galaxies in more massive haloes 
+            possess much more extended stellar haloes than the ones in smaller haloes, 
+            despite their median \mden{} profiles at $R < 15$ kpc are very similar. 
+            Assuming that \minn{} traces the amount of ``in situ'' stars in massive
+            galaxies, this results is consistent with the picture that more massive 
+            haloes favor the growth of extended stellar haloes in their central 
+            galaxies through more frequent mergers.
+
+        \item The \mtot{}-$R_{\mathrm{50}}$ relation for massive central galaxies 
+            also exhibits environmental dependence. 
+            Central galaxies in more massive haloes have slightly larger
+            $R_{\mathrm{50}}$ than the ones from less massive haloes at fixed \mtot{}.
+
+        \item We also find that massive central galaxies in different environments
+            follow different relations between their \mtot{} and \minn{}. 
+            Assuming that \mtot{} is a reasonable proxy of ``total'' stellar mass and 
+            \minn{} reflects the amount of \textit{in situ} stars, we propose that 
+            this relation can help diagnose the assembly of massive central galaxies 
+            without using ``size'' with ambiguous definition.
+
+        \item At fixed \mtot{}, the ellipticity profiles of massive central galaxies 
+            do not display strong environment dependence at $R < 60$ kpc. 
+            At fixed \minn{}, the more extended stellar haloes presented in the \rbcg{}
+            galaxies also show higher ellipticity than the \nbcg{} galaxies.
+
+        \item We do not find evidence that suggests the rest-frame color profiles 
+            within 60 kpc depend on environment for neither \mtot{}- nor 
+            \minn{}--matched samples.
 
@@
 
-    These results highlight the advantages of wide area, deep, and high-quality imaging 
-    for studying the evolution of massive galaxies. 
-    Upon finishing this work, the HSC survey has already doubled its sky coverage to 
-    ${\sim} 200$ deg$^2$, and provides a much larger sample of massive central galaxies. 
-    In the near future, we will extend this work to lower \mtot{} by using photometric 
-    redshifts, and we will also apply 2-D photometry method (e.g.\ \citealt{Huang2013a}) 
-    to take advantages of the multi-wavelength nature of the HSC survey 
-    (e.g. \citealt{Huang2016}). 
-    Our current work can also be combined with weak lensing measurements of the dark 
-    matter haloes of massive galaxies and physical insights into the assembly histories 
-    of these galaxies can be gained by comparing with cosmological hydro-simulations 
-    such as Illustris (\citealt{Vogelsberger2014}, \citealt{Genel2014}), 
-    EAGLE (\citealt{Schaye2015}, \citealt{Crain2015}), or \textit{Horizon-AGN} 
-    (\citealt{Dubois2014}).
+    These results highlight the importance of deep, high-quality images for studying 
+    the assembly of massive haloes and their central galaxies. 
+    We are currently working on combining the current results with weak lensing 
+    measurements of dark matter haloes around these massive galaxies to gain more physical 
+    insights. 
+    We will also compare our results with cosmological hydro-simulations 
+    such as 
+    \textit{Illustris-TNG} (\citealt{Pillepich2017a, Pillepich2017b, Weinberger2017}, 
+    \textit{Horizon-AGN} (\citealt{Dubois2014}), or 
+    \textit{MassiveBlackII} (\citealt{Khandai2015}).
 

### 2017-07-13 draft/paper2.tex
Organzie appendix

@@
 %% ------------------------------------------------------------------------------------ %% 
-\section{A. Basic Statistical Properties of the Sample} 
-	\label{app:basic}
-
-    On the top-left panel of Fig~\ref{fig:sample_stats}, we show the \mtot{}-color 
-    relations using the $k$-corrected $g-r$ color. 
-    Both samples follow the same tight ``red-sequence'' with little contamination 
-    from the ``blue cloud''.
-    At fixed \mtot{}, we see little offset in color distributions of the two 
-    samples, suggesting that both samples consist of quiescent galaxies with 
-    similar average stellar population properties.  
-    This is consistent with previous result that suggests the average stellar 
-    population of massive central galaxy does not depend on \mhalo{} 
-    (e.g.\ \citealt{Park2007}).  
-    In this work, we focus on the \mstar{} range of $11.6 \le$\logmtot{}$\le 11.9$, 
-    where both samples have acceptable completeness, and their \mtot{} distributions 
-    greatly overlap (see the normalized distributions of \mtot{} in the bottom-left 
-    panel of Fig~\ref{fig:sample_stats}). 
-    As for the \minn{} distributions, the two samples overlap the most within 
-    $11.2 \le$\logmtot{}$\le 11.6$, but now they show quite different
-    distributions (bottom-right figure).
-
-    The redshift distributions also show small difference
-    (upper-right panel) even in the high-\mtot{} bin, where the redshift distribution 
-    of the \nbcg{} sample skews toward higher-$z$ end due to the contribution of BOSS 
-    spec-$z$.
-    Since this could bias the comparison of \mden{} profiles and other properties 
-    (please see Appendix\ref{app:redshift} for more details), we address this via matching 
-    the two samples in both mass and redshift distributions carefully
-    (see Appendix~\ref{app:match}).
-
-%% ------------------------------------------------------------------------------------ %% 
-  \begin{figure*}
+  \begin{figure}
       \centering 
-      \includegraphics[width=16.5cm]{fig/redbcg_sample_stats_old}
+      \includegraphics[width=8.5cm]{fig/redbcg_sample_stats_old}
       \caption{
@@
       \label{fig:sample_stats}
-  \end{figure*}
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %% 
-\section{B. Comparison of \mden{} profiles using \mstar{} from the GAMA survey}
-    \label{app:gama}
-
-%% ------------------------------------------------------------------------------------ %% 
-\begin{figure*}
-    \centering
-    \includegraphics[width=\textwidth]{fig/redbcg_prof_gama_new}
-    \caption{
-        \textbf{Left:} comparison of \mstar{} estimated by the GAMA survey and 
-        the \mtot{} using HSC images in this work. 
-        We plot the \logmgama{} against the difference between \logmtot{} and \logmgama{}. 
-        The format is very similar to the left panel of Fig~\ref{fig:smf1}. 
-        The two vertical lines highlight the mass range $11.4 \leq$\logmgama{}$<11.8$ 
-        that is used for the comparison.~~
-        \textbf{Right:} we compare the \mden{} profiles of \rbcg{} (orange-red) and 
-        \nbcg{} (grey-black) galaxies using the samples matched on the 
-        \mgama{}-$z$ plane at $11.4 \leq$\logmgama{}$<11.9$ and $0.28 \leq z < 0.4$. 
-        The format is very similar to the ones in Fig~\ref{fig:prof_1}.}
-    \label{fig:gama}
-\end{figure*}
-%% ------------------------------------------------------------------------------------ %%
-
-    The GAMA survey greatly overlaps with the HSC survey, and it provides carefully 
-    measured \mstar{} for large sample of galaxies (\citealt{Taylor2011}) that help 
-    produce many interesting results (e.g. \citealt{Bauer2013, Ferreras2017}).
-    They use 2-D single-\ser{} model to correct the total luminosity of the galaxy 
-    (\citealt{Kelvin2012}), and derive the \m2l{} through optical-SED fitting 
-    (BC03 model; Chabrier IMF) based on the PSF-matched aperture photometry. 
-    Since the \ser{} model is generally more flexible than the \texttt{cModel} one, 
-    it is therefore interesting to compare with the \rbcg{} and \nbcg{} galaxies 
-    that also have spec-$z$ (at $z < 0.40$) and \mstar{} in GAMA DR2 
-    (\citealt{Liske2015}) and see the impact of deep photometry again.
-
-    We summarize the results in Fig~\ref{fig:gama}.  
-    On the left panel, we compare the differences between \mtot{} and \mgama{}. 
-    HSC survey on average recovers more \mstar{} at high-\mstar{} end, which is 
-    consistent with the expectation from deeper photometry, although the 
-    systematic differences in the estimates of \m2l{} could play a role here. 
-    Meanwhile, it is interesting see that, above \logmtot{}$> 11.8$, \mgama{} 
-    becomes increasingly larger than \mtot{}, and most of these massive 
-    galaxies have very high \ser{} index from the 2-D fitting. 
-    This suggests that the single-\ser{} model is no longer an appropriate one to 
-    describe very massive galaxies as it tends to over-estimate the \mstar{} the 
-    inner and/or outer regions.
-
-    To verify the cause of the difference in \mstar{}, we further select samples 
-    of \rbcg{} and \nbcg{} galaxies with matched \mgama{} and redshift 
-    distributions (at $11.4 <$\logmgama{}$<11.8$; see Appendix \ref{app:match}), 
-    and compare their \mden{} profiles (right panel). 
-    Although these two subsamples are equally massive according to results from 
-    GAMA survey, it is clear that the \rbcg{} galaxy has much more extended 
-    outer envelope, even though its median \mden{} profile is very similar 
-    to the \nbcg{} sample at $< 10$ kpc. 
-    We can reproduce very the same trend with the luminosity density profiles 
-    (with or without $k$-correction), suggesting that the inaccurate \ser{} 
-    model definitely leads to under-estimate of \mstar{}.
-
-%% ------------------------------------------------------------------------------------ %%
-
-\section{C. Comparisons of \mden{} profiles in different redshift bins}
-    \label{app:redshift}
+  \end{figure}
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
+\section{A. Basic Statistical Properties of the Sample} 
+	\label{app:basic}
+
+    On the top-left panel of Fig~\ref{fig:sample_stats}, we show the \mtot{}-color 
+    relations using the $k$-corrected $g-r$ color. 
+    Both samples follow the same tight ``red-sequence'' with little contamination 
+    from the ``blue cloud''.
+    At fixed \mtot{}, we see little offset in color distributions of the two 
+    samples, suggesting that both samples consist of quiescent galaxies with 
+    similar average stellar population properties.  
+    This is consistent with previous result that suggests the average stellar 
+    population of massive central galaxy does not depend on \mhalo{} 
+    (e.g.\ \citealt{Park2007}).  
+    In this work, we focus on the \mstar{} range of $11.6 \le$\logmtot{}$\le 11.9$, 
+    where both samples have acceptable completeness, and their \mtot{} distributions 
+    greatly overlap (see the normalized distributions of \mtot{} in the bottom-left 
+    panel of Fig~\ref{fig:sample_stats}). 
+    As for the \minn{} distributions, the two samples overlap the most within 
+    $11.2 \le$\logmtot{}$\le 11.6$, but now they show quite different
+    distributions (bottom-right figure).
+
+    The redshift distributions also show small difference
+    (upper-right panel) even in the high-\mtot{} bin, where the redshift distribution 
+    of the \nbcg{} sample skews toward higher-$z$ end due to the contribution of BOSS 
+    spec-$z$.
+    Since this could bias the comparison of \mden{} profiles and other properties 
+    (please see Appendix\ref{app:redshift} for more details), we address this via matching 
+    the two samples in both mass and redshift distributions carefully
+    (see Appendix~\ref{app:match}).
 
@@
         and highlight the median profiles using thicker line and darker color.
-        Other formats are exactly the same with the left figure of 
-        Fig~\ref{fig:avg_prof}.}
+        }
     \label{fig:avg_prof_z}
@@
 %% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
+\section{B. Comparisons of \mden{} profiles in different redshift bins}
+    \label{app:redshift}
 
@@
     even in the central region.  
-
-%% ------------------------------------------------------------------------------------ %%
-
-\section{D. Match the \rbcg{} and \nbcg{} samples in \mstar{} and redshift distributions}
-    \label{app:match}
+%% ------------------------------------------------------------------------------------ %%
 
@@
     \centering 
-    \includegraphics[width=\textwidth]{fig/redbcg_match}
+    \includegraphics[width=16cm]{fig/redbcg_match}
     \caption{
@@
 
-    As explained earlier, it is important to make sure the two samples have similar 
-    distributions in both \mstar{} and redshift before comparing their median \mden{} 
-    profiles.  
-    Here we briefly describe the procedure used in this work. 
-    Since the \rbcg{} sample is smaller in size, we always match the \nbcg{} sample to 
-    it by searching for the $N$-nearest neighbours on the $M_{\star}$-redshift plane 
-    using the KDTree algorithm in the \texttt{scikit-learn} Python library 
-    (\citealt{scikit-learn}), and evaluate the quality of the match using the 
-    distributions of both parameters (as shown in Fig~\ref{fig:match}).
-
-    As we only keep the unique \nbcg{} galaxies in the matched sample, we manually 
-    adjust the value of $N$ to achieve the best match. 
-    When the redshift distribution of the \rbcg{} sample becomes bi-model, we also try 
-    to split the sample into two redshift bins and match them separately. 
-    Typically $N$ is between 3 to 8.
-    In Fig~\ref{fig:match}, we demonstrate this procedure using the results for 
-    the \mtot{}-matched (Left) and the \minn{}-matched samples in Fig~\ref{fig:prof_1}
-    (Right), and the two samples are well matched in the distributions of \mtot{}
-    (or \minn{}) and redshift.  
-    For all the comparisons of \mden{} profiles in this work, we match the samples 
-    in the same way, and make sure the match has the same quality.
-
-%% ------------------------------------------------------------------------------------ %% 
-\section{E. Robustness of the \mden{} Differences} 
-	\label{app:robust}
-
-    In Fig~\ref{fig:prof_1}, we compare the \mden{} profiles of \mtot{}- and 
-    \minn{}-matched samples of \rbcg{} and \nbcg{} galaxies, and here we test the 
-    robustness of the results using a few extra tests that are illustrated in
-    Fig~\ref{fig:prof_2}, Fig~\ref{fig:prof_3}, and Fig~\ref{fig:prof_4}, and 
-    are briefly described here:
-
-    \begin{enumerate}
-
-        \item In Fig~\ref{fig:prof_2}, we group the samples into two \mtot{} bins. 
-            Given the small sample size, we extend slightly toward lower \mtot{} range 
-            ($11.5 \leq \log (M_{\star,\ 10\mathrm{kpc}}/M_{\odot}) < 11.7$ and 
-             $11.7 \leq \log (M_{\star,\ 10\mathrm{kpc}}/M_{\odot}) < 11.9$). 
-            Although the smaller sample leads to larger statistical uncertainties, 
-            we can still see similar structural differences in both \mtot{} bins, 
-            and the difference becomes more significant in the higher \mtot{} bin.  
-            For the lower \mtot{} bin, the difference in the inner region becomes 
-            quite uncertain, while the difference in the outskirt is still visible. 
-            This potentially suggests that the environmental dependence of structure 
-            also varies with \mstar{}, an important implication deserves more 
-            investigations in the future.
-
-        \item On the left panel of Fig~\ref{fig:prof_3}, we match the \rbcg{} and 
-            \nbcg{} samples in a lower redshift bins ($0.30 < z < 0.42$).
-            Despite the larger uncertainties due to smaller samples, we find the 
-            results are the same.
-
-        \item On the middle panel of Fig~\ref{fig:prof_3}, we includes \rbcg{} 
-            galaxies in poorer clusters ($20 < \lambda < 30$), which should result 
-            in overlapped \mhalo{} distributions with the \nbcg{} samples 
-            considering the typical uncertainty of $\lambda$.
-            This makes the difference in the inner region slightly less significant, 
-            but the overall results are the same.
-
-        \item On the right panel of Fig~\ref{fig:prof_3}, in stead of using \mtot{}, 
-            we use the \mmax{}--the maximum \mstar{} by integrating the \mden{} 
-            profiles to the largest radius allowed.  
-            The \mmax{} values are less reliable than \mtot{} due to the 
-            uncertainty of background subtraction and contamination from nearby 
-            bright objects, but they can serve as different estimates of the ``total''
-            \mstar{} of these galaxies.
-            As shown in Section~\ref{sec:discussion}, they on average increase
-            the \mstar{} by a little bit and affect the \rbcg{} more.
-            The differences in the \mden{} profiles still remain very similar.
-
-    \end{enumerate}
-
-    We also test the robustness of the \mtot{}-matched results using the samples with 
-    only spectroscopic redshift, the samples in the three GAMA fields, and the \rbcg{} 
-    samples without the ones in very massive haloes ($\lambda > 40$).  
-    Limited by space, we do not show these results here, but they all verify the 
-    robustness of the results.
-
-    For the results from the \minn{}-matched samples:
-
-    \begin{enumerate}
-
-        \item
-            We match the two samples using both \minn{} and the \mstar{} within 15 kpc 
-            at the same time.  
-            This makes the two median \mden{} profiles very similar inside 10-15 
-            kpc, while the result in the outskirt remains the same (left panel of 
-            Fig~\ref{fig:prof_4}).
-            Use \mstar{} within 5 or 20 kpc leads to the same conclusion.
-
-        \item 
-            To make sure the two samples are comparable in their overall assembly history,
-            we also try to only include the very massive galaxies (\logmtot{}$>11.5$)
-            in both samples. 
-            This excludes the \nbcg{} galaxies that are much less massive and 
-            more ``compact'' in structure. 
-            Yet, the results regarding the structural differences remain the same.
-
-    \end{enumerate}
-
 %% ------------------------------------------------------------------------------------ %% 
@@
       \centering 
-      \includegraphics[width=\textwidth]{fig/redbcg_prof_2}
+      \includegraphics[width=15.5cm]{fig/redbcg_prof_2}
       \caption{
@@
       \centering 
-      \includegraphics[width=\textwidth]{fig/redbcg_prof_4}
+      \includegraphics[width=15.5cm]{fig/redbcg_prof_4}
       \caption{
@@
 %% ------------------------------------------------------------------------------------ %% 
+\begin{figure*}
+    \centering
+    \includegraphics[width=16cm]{fig/redbcg_prof_gama_new}
+    \caption{
+        \textbf{Left:} comparison of \mstar{} estimated by the GAMA survey and 
+        the \mtot{} using HSC images in this work. 
+        We plot the \logmgama{} against the difference between \logmtot{} and \logmgama{}. 
+        The format is very similar to the left panel of Fig~\ref{fig:smf1}. 
+        The two vertical lines highlight the mass range $11.4 \leq$\logmgama{}$<11.8$ 
+        that is used for the comparison.~~
+        \textbf{Right:} we compare the \mden{} profiles of \rbcg{} (orange-red) and 
+        \nbcg{} (grey-black) galaxies using the samples matched on the 
+        \mgama{}-$z$ plane at $11.4 \leq$\logmgama{}$<11.9$ and $0.28 \leq z < 0.4$. 
+        The format is very similar to the ones in Fig~\ref{fig:prof_1}.}
+    \label{fig:gama}
+\end{figure*}
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
+\section{C. Match the \rbcg{} and \nbcg{} samples in \mstar{} and redshift distributions}
+    \label{app:match}
+
+    As explained earlier, it is important to make sure the two samples have similar 
+    distributions in both \mstar{} and redshift before comparing their median \mden{} 
+    profiles.  
+    Here we briefly describe the procedure used in this work. 
+    Since the \rbcg{} sample is smaller in size, we always match the \nbcg{} sample to 
+    it by searching for the $N$-nearest neighbours on the $M_{\star}$-redshift plane 
+    using the KDTree algorithm in the \texttt{scikit-learn} Python library 
+    (\citealt{scikit-learn}), and evaluate the quality of the match using the 
+    distributions of both parameters (as shown in Fig~\ref{fig:match}).
+
+    As we only keep the unique \nbcg{} galaxies in the matched sample, we manually 
+    adjust the value of $N$ to achieve the best match. 
+    When the redshift distribution of the \rbcg{} sample becomes bi-model, we also try 
+    to split the sample into two redshift bins and match them separately. 
+    Typically $N$ is between 3 to 8.
+    In Fig~\ref{fig:match}, we demonstrate this procedure using the results for 
+    the \mtot{}-matched (Left) and the \minn{}-matched samples in Fig~\ref{fig:prof_1}
+    (Right), and the two samples are well matched in the distributions of \mtot{}
+    (or \minn{}) and redshift.  
+    For all the comparisons of \mden{} profiles in this work, we match the samples 
+    in the same way, and make sure the match has the same quality. 
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
+\section{D. Robustness of the \mden{} Differences} 
+	\label{app:robust}
+
+    In Fig~\ref{fig:prof_1}, we compare the \mden{} profiles of \mtot{}- and 
+    \minn{}-matched samples of \rbcg{} and \nbcg{} galaxies, and here we test the 
+    robustness of the results using a few extra tests that are illustrated in
+    Fig~\ref{fig:prof_2}, Fig~\ref{fig:prof_3}, and Fig~\ref{fig:prof_4}, and 
+    are briefly described here:
+
+    \begin{enumerate}
+
+        \item In Fig~\ref{fig:prof_2}, we group the samples into two \mtot{} bins. 
+            Given the small sample size, we extend slightly toward lower \mtot{} range 
+            ($11.5 \leq \log (M_{\star,\ 10\mathrm{kpc}}/M_{\odot}) < 11.7$ and 
+             $11.7 \leq \log (M_{\star,\ 10\mathrm{kpc}}/M_{\odot}) < 11.9$). 
+            Although the smaller sample leads to larger statistical uncertainties, 
+            we can still see similar structural differences in both \mtot{} bins, 
+            and the difference becomes more significant in the higher \mtot{} bin.  
+            For the lower \mtot{} bin, the difference in the inner region becomes 
+            quite uncertain, while the difference in the outskirt is still visible. 
+            This potentially suggests that the environmental dependence of structure 
+            also varies with \mstar{}, an important implication deserves more 
+            investigations in the future.
+
+        \item On the left panel of Fig~\ref{fig:prof_3}, we match the \rbcg{} and 
+            \nbcg{} samples in a lower redshift bins ($0.30 < z < 0.42$).
+            Despite the larger uncertainties due to smaller samples, we find the 
+            results are the same.
+
+        \item On the middle panel of Fig~\ref{fig:prof_3}, we includes \rbcg{} 
+            galaxies in poorer clusters ($20 < \lambda < 30$), which should result 
+            in overlapped \mhalo{} distributions with the \nbcg{} samples 
+            considering the typical uncertainty of $\lambda$.
+            This makes the difference in the inner region slightly less significant, 
+            but the overall results are the same.
+
+        \item On the right panel of Fig~\ref{fig:prof_3}, in stead of using \mtot{}, 
+            we use the \mmax{}--the maximum \mstar{} by integrating the \mden{} 
+            profiles to the largest radius allowed.  
+            The \mmax{} values are less reliable than \mtot{} due to the 
+            uncertainty of background subtraction and contamination from nearby 
+            bright objects, but they can serve as different estimates of the ``total''
+            \mstar{} of these galaxies.
+            As shown in Section~\ref{sec:discussion}, they on average increase
+            the \mstar{} by a little bit and affect the \rbcg{} more.
+            The differences in the \mden{} profiles still remain very similar.
+
+    \end{enumerate}
+
+    We also test the robustness of the \mtot{}-matched results using the samples with 
+    only spectroscopic redshift, the samples in the three GAMA fields, and the \rbcg{} 
+    samples without the ones in very massive haloes ($\lambda > 40$).  
+    Limited by space, we do not show these results here, but they all verify the 
+    robustness of the results.
+
+    For the results from the \minn{}-matched samples:
+
+    \begin{enumerate}
+
+        \item
+            We match the two samples using both \minn{} and the \mstar{} within 15 kpc 
+            at the same time.  
+            This makes the two median \mden{} profiles very similar inside 10-15 
+            kpc, while the result in the outskirt remains the same (left panel of 
+            Fig~\ref{fig:prof_4}).
+            Use \mstar{} within 5 or 20 kpc leads to the same conclusion.
+
+        \item 
+            To make sure the two samples are comparable in their overall assembly history,
+            we also try to only include the very massive galaxies (\logmtot{}$>11.5$)
+            in both samples. 
+            This excludes the \nbcg{} galaxies that are much less massive and 
+            more ``compact'' in structure. 
+            Yet, the results regarding the structural differences remain the same.
+
+    \end{enumerate}
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
+\section{E. Comparison of \mden{} profiles using \mstar{} from the GAMA survey}
+    \label{app:gama}
+
+    The GAMA survey greatly overlaps with the HSC survey, and it provides carefully 
+    measured \mstar{} for large sample of galaxies (\citealt{Taylor2011}) that help 
+    produce many interesting results (e.g. \citealt{Bauer2013, Ferreras2017}).
+    They use 2-D single-\ser{} model to correct the total luminosity of the galaxy 
+    (\citealt{Kelvin2012}), and derive the \m2l{} through optical-SED fitting 
+    (BC03 model; Chabrier IMF) based on the PSF-matched aperture photometry. 
+    Since the \ser{} model is generally more flexible than the \texttt{cModel} one, 
+    it is therefore interesting to compare with the \rbcg{} and \nbcg{} galaxies 
+    that also have spec-$z$ (at $z < 0.40$) and \mstar{} in GAMA DR2 
+    (\citealt{Liske2015}) and see the impact of deep photometry again.
+
+    We summarize the results in Fig~\ref{fig:gama}.  
+    On the left panel, we compare the differences between \mtot{} and \mgama{}. 
+    HSC survey on average recovers more \mstar{} at high-\mstar{} end, which is 
+    consistent with the expectation from deeper photometry, although the 
+    systematic differences in the estimates of \m2l{} could play a role here. 
+    Meanwhile, it is interesting see that, above \logmtot{}$> 11.8$, \mgama{} 
+    becomes increasingly larger than \mtot{}, and most of these massive 
+    galaxies have very high \ser{} index from the 2-D fitting. 
+    This suggests that the single-\ser{} model is no longer an appropriate one to 
+    describe very massive galaxies as it tends to over-estimate the \mstar{} the 
+    inner and/or outer regions.
+
+    To verify the cause of the difference in \mstar{}, we further select samples 
+    of \rbcg{} and \nbcg{} galaxies with matched \mgama{} and redshift 
+    distributions (at $11.4 <$\logmgama{}$<11.8$; see Appendix \ref{app:match}), 
+    and compare their \mden{} profiles (right panel). 
+    Although these two subsamples are equally massive according to results from 
+    GAMA survey, it is clear that the \rbcg{} galaxy has much more extended 
+    outer envelope, even though its median \mden{} profile is very similar 
+    to the \nbcg{} sample at $< 10$ kpc. 
+    We can reproduce very the same trend with the luminosity density profiles 
+    (with or without $k$-correction), suggesting that the inaccurate \ser{} 
+    model definitely leads to under-estimate of \mstar{}.
+
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %%  
 \bsp

### 2017-07-13 draft/paper2.tex
New abstract

@@
 
-    We use ${\sim}100$ deg$^2$ of deep ($>28.5$ \sb{} in $i$-band), high-quality 
-    (0.6\asec seeing) imaging data from the Hyper Suprime-Cam (HSC) survey 
-    to investigate the halo mass dependence of the surface mass density profiles 
-    and outer stellar envelopes of massive galaxies. 
-    Our sample consists of ${\sim}7000$ massive (\mstar{}$\geq 11.5$) central galaxies 
-    at $0.3 < z < 0.5$. 
-    The depth of the HSC survey reaches ${\sim}4$ magnitudes fainter than SDSS and 
-    enables us to directly trace stellar mass distributions to 100 kpc without 
-    requiring stacking. 
-    For the first time, we conclusively show that at fixed stellar mass, massive central 
-    galaxies display mass density profiles that are not self similar and which 
-    present subtle but systematic differences that correlate with \mhalo{}. 
-    On average, massive central galaxies in more massive haloes have shallower inner 
-    stellar mass density profiles (within ${\sim}10$-$20$ kpc) and more prominent outer 
-    envelopes. 
-    These differences translate into a clear environmental dependence of the mass-size 
-    relation: central galaxies in more massive haloes have larger $R_{\mathrm{50}}$ 
-    at fixed \mtot{}. 
-    Shallow imaging will miss light at the outskirts of galaxies and this has an 
-    important impact on measurements of the galaxy mass function. 
-    Furthermore, because galaxies in larger haloes have more extended envelopes, 
-    the amount of light that is missed will be halo mass dependent. 
-    Finally, at fixed total stellar mass, there is a large (but continuous) diversity 
-    in the amplitude of stellar profiles at 100 kpc. 
-    We argue that ``cD'' galaxies represent the tail end of a distribution and 
-    are not a distinct class of massive galaxies. 
-    Our results are broadly consistent with the two phase formation scenario of 
-    massive galaxies in which outer envelopes are built up at late times from the 
-    accretion of small systems. 
-    Our mass profiles are provided in a convenient tabulated format in order to 
-    facilitate comparisons with predictions from numerical simulations of galaxy 
-    formation. 
-    \song{This is the abstract of old draft, need some works}
+    In \citet{hscMassiveI}, we use deep ($>28.5$ \sb{} in $i$-band), high-quality 
+    (0.6\asec seeing) images of ${\sim}3000$ massive (\mstar{}$\geq 11.5$) central 
+    galaxies at $0.3 < z < 0.5$ from the Hyper Suprime-Cam Subaru Strategic Program 
+    to show that more massive central galaxies display more prominent stellar haloes 
+    with shallower outer stellar mass density profile (\mden) and higher ellipticity. 
+    In this work, we investigate the environment dependence of stellar mass 
+    distributions of massive central galaxies using the same dataset.
+    Treating stellar mass within a 100 kpc elliptical aperture (\mtot{}) as proxy of 
+    total stellar mass, we show that at fixed \mtot{}, massive central galaxies in 
+    \mhalo{}$\geq 10^{14}$\msun{} haloes show slightly shallower \mden{} profiles, 
+    larger half-light radius, and lower fraction of stellar mass within inner 10 kpc 
+    (\minn{}) than the centrals of \mhalo{}$< 10^{14}$\msun{} haloes. 
+    At fixed \minn{}--a tracer of the \textit{in situ} stellar mass, central galaxies 
+    from more massive haloes host much more significant outer stellar haloes despite 
+    their inner \mden{} profiles are very similar with the ones in less massive haloes.
+    These results clearly demonstrate that mass--size relation for central galaxies 
+    indeed depends on environment at high-\mtot{} end. 
+    We also show that the \mtot{}--\minn{} relation can reflect this dependence 
+    better and can help diagnose the assembly of massive galaxies and their haloes.
+    These results suggest more massive haloes favor more efficient growth of stellar 
+    haloes in their central galaxies, which is broadly consistent with the two phase 
+    formation scenario of massive galaxies in which their outer envelopes are 
+    accumulated through accretions of small systems.
 

### 2017-07-14 draft/paper2.tex
Need new discussion

@@
 
-        \item a 10 kpc radii (hereafter noted \minn{}) as proxy of the ``in situ'' 
-            stellar component. 
+        \item a 10 kpc radii (hereafter noted \minn{}) as proxy of the 
+            \textit{in situ} stellar component. 
             This is motivated by recent observations and simulations 
@@
     their subsequent mass assembly?
-    Assuming \minn{} is reasonable tracer of the ``in situ'' mass, we compare the 
+    Assuming \minn{} is reasonable tracer of the \textit{in situ} mass, we compare the 
     \mden{} profiles of \minn{}-matched samples (right panel of Fig~\ref{fig:prof_1}).  
@@
 %% ------------------------------------------------------------------------------------ %% 
+%% Discussion 
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
 \section{Discussion}
@@
 
-    \song{Keep the relevant session from previous draft, need some works.}
-    By using deep imaging from the HSC survey we have shown that the stellar mass 
-    density profiles of massive central galaxies depend systematically on the mass 
-    of their host dark matter haloes. 
-    Here we discuss the physical origin, scientific implications, and potential 
-    caveats of this result.
-
-%% ------------------------------------------------------------------------------------ %%
-
-\subsection{The ``Two phase'' Formation Scenario of Massive Galaxies and the 
-            Build-Up of Outer Envelopes}
-
-    Our results are consistent with the picture that massive central galaxies form via 
-    a ``two-phase'' scenario. 
+    Using the deep images from the HSC survey, we show that the stellar mass 
+    distributions of massive central galaxies at $0.3 < z < 0.5$ depend on their 
+    environment or \mhalo{}. 
+    Here we briefly discuss the physical implications and potential caveats of this 
+    result.
+
+%% ------------------------------------------------------------------------------------ %% 
+\subsection{The Role of Environment in the ``Two--Phase'' Formation of 
+            Massive Central Galaxies}
+
+    Results presented here are broadly consistent with the picture that massive central 
+    galaxies form via a ``two-phase'' picture.
+
     According to this theory, the cores of massive galaxies were formed at $z{\sim} 2$ 
-    during an intense period of in situ star formation. 
+    during an intense period of \textit{in situ} star formation. 
     The outskirts of massive galaxies are then built up via a more gradual second 
@@
 
-    We now investigate to what degree our assumption that the inner 10 kpc \mstar{}
-    corresponds to an in situ mass.    
-    Fig \ref{fig:discussion_1} compares the median \mden{} profiles of the 
-    galaxies in two \mtot{} bins 
-    ($11.4\leq$\logmtot{}$<11.6$ and $11.6\leq$\logmtot{}$<11.8$) with 
-    (1) the median \mden{} profiles of massive ETGs at $1.0 < z < 1.5$ in
-    \citealt{Patel2013} since they are considered as the progenitors of 
-    ${\sim} 10^{11.5} M_{\odot}$ ETGs at $z=0$.    
-    (2) the inner components of $z{\sim} 0$ ellipticals from 2-D decomposition 
-    (\citealt{Huang2013a}).
-    As proxy of the in situ components, \citet{Huang2013b} showed they are 
-    structurally similar to the compact ``red nuggets'' at high-$z$. 
-    (3) the ``in situ'' components of simulated central galaxies in massive haloes 
-    from \citet{Cooper13} (the inner ${\sim} 5$ kpc is quite uncertain due to the 
-    resolution).  
-    The comparison confirms that \minn{} should be reasonable proxy of the 
-    ``in situ'' mass\footnote{We convert these \mden{} profiles to the same 
-    Chabrier IMF; but there are still differences in median \mstar{} and 
-    details in the \m2l{} estimates}.  
-    More importantly, it shows that the \mden{} profile at 
-    $\mathrm{R} > 15$-20 kpc is likely dominated by stars that are not related 
-    to the ``in situ'' processes.
-
-    We also compare with a uniquely massive BCG at high redshift: 
-    a ${\sim} 10^{11.4} M_{\odot}$ BCG with distinctive ``cD''-like envelope at 
-    $z{\sim} 1.1$ (\citealt{Liu2013}).  
-    Its \mden{} profile follows the median profile of $11.6\leq$\logmtot{}$<11.8$ 
-    massive galaxies nicely inside 10-15 kpc, but becomes much steeper in the outskirt.  
-    This unique object may present an interesting case where the inner ``core'' of a 
-    massive BCGs is already in pace at $z{\sim} 1$ when its extended envelope is still
-    under construction.
-    More BCGs like this at $0.5 < z < 1.0$ can shed light on this intriguing 
-    process, and help us confirm whether the environmental dependence of structure 
-    has already emerged within massive galaxies at higher redshift 
-    (e.g. \citealt{Papovich2012})
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %%
-
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
 \subsection{Scatter in Outer Stellar Enveloppes and ``cD'' Galaxies}
@@
    However, until present, it has not been clear whether ``cD'' galaxies are a distinct 
-   and special population, or if they are simply the continum of a smoothly varying 
+   and special population, or if they are simply the conti of a smoothly varying 
    population. 
@@
    by \citealt{Bai2014}. 
-
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
+%% Summary 
 %% ------------------------------------------------------------------------------------ %%
@@
 
-%\acknowledgements
+%% ------------------------------------------------------------------------------------ %% 
+%% Acknowledgements 
+%% ------------------------------------------------------------------------------------ %% 
 \section*{Acknowledgements}
@@
 
-%%%%%%%%%%: Bibliographic Section %%%%%%%%%%
-
+%% ------------------------------------------------------------------------------------ %% 
+%% References  
+%% ------------------------------------------------------------------------------------ %% 
 \bibliographystyle{mnras}

### 2017-07-26 draft/paper2_v3.tex
Edit introduction

--- 2017-07-14 draft/paper2.tex
@@
 % Version 2; preprint format; Edited by Song Huang
+% Version 3; preprint format; Edited by Alexie Leauthaud
 
@@
 \def\logmh{{$\log (M_{\mathrm{200b}}/M_{\odot})$}}
+\def\logmhalo{{$\log (M_{\mathrm{200b}}/M_{\odot})$}}
 
@@
 
+%\title[Structure and Environment of Massive Galaxies]{
+%       A Detection of the Environmental Dependence of the Stelllar and haloes
+%       of Massive Central Galaxies}
+
 \title[Structure and Environment of Massive Galaxies]{
-       A Detection of the Environmental Dependence of the Stellar Profiles and haloes
+       A Detection of the Environmental Dependence of the Sizes and Stellar Haloes
        of Massive Central Galaxies}
@@
 \author[S. Huang et al.]{
-        Song Huang,$^{1,2}$\thanks{E-mail: song.huang@ipmu.jp (SH)}
-        Alexie Leauthaud,$^{2,1}$
-        Jenny Greene,$^{4}$
-        Kevin Bundy,$^{3,1}$
+        Song Huang$^{1,2}$\thanks{E-mail: song.huang@ipmu.jp (SH)},
+        Alexie Leauthaud$^{1}$,
+        Jenny Greene$^{4}$,
+        Kevin Bundy$^{3}$,
         \newauthor
-        Yen-Ting Lin,$^{5}$
-        Masayuki Tanaka,$^{6}$
-        Rachel Mandelbaum,$^{7}$
-        Satoshi Miyazaki,$^{5,8}$
+        Yen-Ting Lin$^{5}$,
+        Masayuki Tanaka$^{6}$,
+        Rachel Mandelbaum$^{7}$,
+        Satoshi Miyazaki$^{5,8}$,
         \newauthor
@@
         \\
-        $^{1}$Kavli-IPMU, The University of Tokyo Institutes for Advanced Study, 
+        $^{1}$Department of Astronomy and Astrophysics, University of California 
+              Santa Cruz, 1156 High St., Santa Cruz, CA 95064, U.S.A\\
+        $^{2}$Kavli-IPMU, The University of Tokyo Institutes for Advanced Study, 
               the University of Tokyo (Kavli IPMU, WPI), Kashiwa 277--8583, Japan\\              
-        $^{2}$Department of Astronomy and Astrophysics, University of California 
-              Santa Cruz, 1156 High St., Santa Cruz, CA 95064, U.S.A\\
         $^{3}$UCO/Lick Observatory, University of California, Santa Cruz,
@@
 
-    One of the most intriguing observations of high-redshift galaxies from the last 
-    decade has been the dramatic structural transformation in massive quiescent 
+    A key discovery in the last 
+    decade has been the dramatic structural transformation of massive quiescent 
     galaxies \citep[e.g.][]{Trujillo2006, vanDokkum2008, Cimatti2008, Damjanov2009, 
-    vanderWel2011, Szomoru2012, Patel2013} from $z \approx 2$ to the present. 
+    vanderWel2011, Szomoru2012, Patel2013} from $z \approx 2$ to the present day. 
     These observations suggest that the progenitors of $z{\sim} 0$ massive early-type 
-    galaxies (ETGs) need to increase their effective radius ($R_{\rm e}$) by factor 
-    of 2--4 in the last 10 Gyrs (e.g. \citealt{Newman2012, vdWel2014}).
-    They have led to a ``two-phase'' scenario for the formation of massive ETGs 
-    (e.g. \citealt{Oser2010, Oser2012}),
-    in which galaxies form a compact central region through highly dissipative 
-    processes (e.g. gas-rich merger or cold gas-accretion; 
-    \citealt{Hopkins2008, Dekel2009}) and then assemble their extended stellar 
-    haloes via dry mergers 
-    \citep[e.g,][]{Naab2006, Khochfar2006, Oser2010, Oser2012}, which allows for 
-    significant growth at late times. 
-    Meanwhile, progenitor bias, which proposes that larger ETGs were quenched more 
-    recently, could also contribute to the apparent size growth, although its 
-    important is under argument (e.g. \citealt{Newman2012, Carollo2013, 
-    Poggianti2013, Belli2015, Keating2015, Fagioli2016}).
-
-    Several previous works have tested the two-phase formation scenario 
-    observationally using galaxies at low redshift, looking at their surface 
-    brightness of mass density profiles (e.g. \citealt{Huang2013a, Huang2013b, 
+    galaxies (ETGs) need to increase their effective radii ($R_{\rm e}$) by a factor 
+    of 2--4 over a time span of 10 Gyrs (e.g. \citealt{Newman2012, vdWel2014}). 
+    This observational result spurred the development of the ``two-phase'' formation
+    scenario for massive ETGs (e.g. \citealt{Oser2010, Oser2012}),
+    in which galaxies form a compact central region at $z\sim 2$ through highly 
+    dissipative processes (e.g. gas-rich merger or cold gas-accretion;
+    \citealt{Hopkins2008, Dekel2009}). 
+    They subsequently assemble extended stellar haloes via dry mergers 
+    \citep[e.g,][]{Naab2006, Khochfar2006, Oser2010, Oser2012} which can cause 
+    significant size growth at late times. 
+    An alternative explanation for size growth, progenitor bias, hypothesizes that 
+    larger ETGs were quenched more recently, but this explanation is still under 
+    active debate (e.g. \citealt{Newman2012, Carollo2013, Poggianti2013, Belli2015,
+    Keating2015, Fagioli2016}).
+
+    There have been multiple observational attempts to test the two-phase 
+    formation scenario using galaxies at low redshift, by investigating surface 
+    brightness or mass density profiles (e.g. \citealt{Huang2013a, Huang2013b, 
     Oh2017}, optical color gradients (e.g. \citealt{LaBarbera2010, LaBarbera2012}), 
@@
     but this picture still face many challenges.
-    One of the most outstanding issues is the extent to which, at fixed stellar mass, 
-    the accreted fraction depends on the surrounding dark matter halo mass.
-
-    According to this two-phase formation scenario, the late time growth of massive 
+    One of the most outstanding issues is the question of whether or not the 
+    fraction of accreted stellar mass displays a dependency on dark matter halos mass.
+
+    According to the two-phase formation scenario, the late time growth of massive 
     ETGs is intrinsically tied to the growth of their host dark matter haloes 
     (e.g. \citealt{Leauthaud2012, Behroozi2013, Shankar2013}). 
-    Massive ETGs that live at the center of more massive haloes should experience 
-    different assembly and should be subject to higher merger rate compared to 
-    ETGs with similar \mstar{} that live in less massive dark matter haloes. 
+    Massive ETGs living at the centers of more massive haloes should be subject to 
+    higher merger rate compared to ETGs with similar \mstar{} but living in less 
+    massive dark matter haloes. 
     A natural prediction of this picture is therefore that the structures of 
     massive ETGs should depend on their ``environment''\footnote{There are 
-    different definitions of ``environment'' in the literature.  
+    multiple definitions of ``environment'' in the literature.  
     In this work, we use ``environment'' and halo mass interchangeably.}.
-    For instance, models based on two-phase scenario predict that the well-know 
-    stellar mass--effective radius relation for ETGs (\mstar{}--$R_{\rm e}$ relation; 
-    e.g., \citealt{Shen2003, Guo2009}) should show environmental dependence: the 
-    $R_{\rm e}$ of massive ETGs in more massive haloes should be larger than those 
-    in less massive haloes at fixed \mstar{} 
+    Theoretical models based on the two-phase formation scenario predict an 
+    environmental dependence of the stellar mass--effective radius relation for 
+    ETGs (\mstar{}--$R_{\rm e}$; 
+    e.g., \citealt{Shen2003, Guo2009}): the sizes of massive ETGs in more massive 
+    haloes should be larger than those in less massive haloes at fixed \mstar{} 
     (e.g. \citealt{Shankar2013, Shankar2014}). 
@@
 
-    To seriously test the environmental dependence of structure in massive ETGs 
-    requires highly sensitive observations extending beyond the inner region of these 
-    galaxies to truly probe the material accreted at late times. 
-    This is very challenging observation as the surface brightness drops rapidly 
-    with radius in massive ETGs.
-
-    In \citet[][Paper I hereafter]{hscMassiveI}, we showed that the deep, 
-    multi-band images from the Subaru Strategic Program (SSP; \citealt{HSC-SSP,
+    Testing this prediction requires deep imaging of ETGs in order to probe the 
+    accreted component (the stellar halo) which can extend to 100 kpc and 
+    beyond \citep[eg.,][]{hscMassiveI}. 
+    This is very challenging observation as the surface brightness profiles of 
+    massive ETGs decline rapidly with typical values of $\mu > 26.0$ \sb{} in 
+    $i$-band at 100 kpc and at $z\sim0.3$. 
+    In \citet[][Paper I hereafter]{hscMassiveI}, we showed that deep, 
+    multi-band imaging from the Subaru Strategic Program (SSP; \citealt{HSC-SSP,
     HSC-DR1}) using Hyper Suprime-Cam (HSC; \citealt{Miyazaki2012}, 
     Miyazaki in~prep.) allows us to extract robust surface stellar
-    mass density (\mden{}) profiles for {\it individual} massive galaxies 
-    at $0.3 < z < 0.5$ out to 100 kpc. 
-    In Paper I, we exploited this sensitivity to show that the \mden{} profiles 
-    and the shapes of the stellar haloes of massive ETGs has a clear \mstar{} 
-    dependence. 
-    And the fraction of accreted stars residing in the extended envelope increases
-    with the total \mstar{} of the galaxy.
-
-    In this paper, we explore how the extended stellar halo in massive central galaxies
-    depends on dark matter halo mass with the help of HSC images of a large sample 
-    of massive ETGs and the \redm{} cluster catalog (e.g.\ \citealt{Rykoff2014}; 
-    \citealt{Rozo2015b}; please see \S \ref{sec:data} for details)
+    mass density (\mden{}) profiles for {\it individual} galaxies with 
+    \logms{}$>11.4$ at $0.3 < z < 0.5$ and out to 100 kpc. 
+    In Paper I, we characterized the stellar mass distributions and mass density 
+    profiles of stellar haloes of massive ETGs, and showed that there is a large 
+    intrinsic scatter in the \mden{} stellar halos of massive galaxies on 100 kpc 
+    scales, and that the fraction of accreted stars residing in the stellar halos 
+    increases as a function of \mstar{}. 
+    In this follow-up paper, we now address a fundamental prediction of the 
+    two-phase formation scenario and conclusively show that the extended stellar 
+    halos of massive central galaxies depend on dark matter halo mass. 
+    In other terms, we reveal the halo mass dependence of the mass-size relation 
+    for massive ETGs.
+
+%    with the help of HSC images of a large sample 
+%    of massive ETGs and the \redm{} cluster catalog (e.g.\ \citealt{Rykoff2014}; 
+%    \citealt{Rozo2015b}; please see \S \ref{sec:data} for details)
 
     This paper is organized as follows. 
-    \S \ref{sec:data} briefly introduce the sample selection and data reduction 
-    processes.  
+    In \S \ref{sec:data} we briefly introduce the sample selection and the data 
+    reduction processes.  
     Please refer to \citet{hscMassiveI} for more technical details.
     Our main results are presented in \S \ref{sec:result} and discussed in 
-    \S \ref{sec:discussion}. 
+    \S \ref{sec:discussion}. Section
     \S \ref{sec:summary} presents our summary and conclusions.
@@
     Stellar mass is denoted \mstar{} and has been derived using a Chabrier Initial Mass 
-    Function (IMF; \citealt{Chabrier2003}).
-
-    Halo mass is defined as $M_{\rm 200b}$ as 
+    Function (IMF; \citealt{Chabrier2003}). Halo mass is defined as $M_{\rm 200b}$ as 
     $M_{\rm 200b}\equiv M(<r_{\rm 200b})=200\bar{\rho} 
@@
     the mean matter density ($\bar{\rho}$). 
-
-    As in \citet{hscMassiveI}, we do not try to separate any potential ``intra-cluster''
-    component (ICL; e.g. \citealt{Carlberg1997, Lin2004, Gonzalez2005, Mihos2005}) from 
-    massive galaxies in our sample for both technical and scientific reasons.  
+    As in \citet{hscMassiveI}, we do not attempt to decompose or distinguish any  
+    potential ``intra-cluster'' 
+    component (ICL; e.g. \citealt{Carlberg1997, Lin2004, Gonzalez2005, Mihos2005}).
+
 %% ------------------------------------------------------------------------------------ %%
@@
           galaxies. 
-          The left panel corresponds to samples matched by ``total'' stellar mass 
+          Left: halo mass dependence of galaxy profiles at fixed ``total'' stellar mass 
           (\mtot{}). 
-          The right panel corresponds to samples matched by ``core-mass'' (\minn{}). 
-          Orange and red lines correspond to central galaxies living in haloes with 
-          \logmh{} $\geq 14.2$. 
-          Black and grey correspond to central galaxies living in haloes with 
+          Right: halo mass dependence of galaxy profiles at fixed ``inner-mass'' 
+          (\minn{}). Orange and red lines correspond to central galaxies living in 
+          haloes with \logmh{} $\geq 14.2$. 
+          Black and grey lines correspond to central galaxies living in haloes with 
           \logmh{} $\leq 14.0$. 
@@
           computed via bootstrap resampling. 
-          The brown line in the bottom panels show the relative difference between 
+          Brown lines in the bottom panels show the relative difference between  
           two median profiles 
           ($\Delta = \log(\mu_{\star, \mathrm{cenHighMh}}) - 
-          \log(\mu_{\star, \mathrm{cenLowMh}})$). 
-          Errors on the difference between the two profiles is computed via bootstrap 
-          too. 
+          \log(\mu_{\star, \mathrm{cenLowMh}}$). 
+          Errors on the difference between the two profiles are also computed 
+          via bootstrap.
           The grey shaded regions show a Monte Carlo test to asses how likely is it to 
@@
           (\rbcg{} and \nbcg{}), then draw sub-samples of galaxies from the mixed 
-          population and compute $\Delta$ in the same fashion as for our fiducial signal. 
+          population and compute $\Delta$ in the same fashion as for our fiducial 
+          signal. 
           We repeat this process 5000 times.  
@@
 
-    The sample selection and data reduction processes are described in detail in 
-    Paper I. 
-    Here we include a short summary for completeness.
-
-    This work makes use of the imaging data from the internal data release 
+    We refer the reader to Paper I for an in-depth description of the sample selection 
+    and data reduction processes. 
+    Here, we briefly summarize the main steps.
+
+    We use imaging data from the HSC internal data release 
     \texttt{S15B}, which is very similar to the Public Data Release 1 
     (\citealt{HSC-DR1} and covers ${\sim} 110$ deg$^2$ in all five-band ($grizy$) to 
-    the required depth. 
-    These images are reduced by \texttt{hscPipe 4.0.2}, a derivative of the 
+    the full depth in the Wide field. The data are reduced by \texttt{hscPipe 4.0.2}, a derivative of the 
     Large Synoptic Survey Telescope (LSST) pipeline (e.g.\ \citealt{Juric2015}; 
@@
     The pixel scale of the reduced image is $0.168$\asec{}.
-    We use the $i$-band image for extracting surface brightness profiles.    
-    The HSC $i$-band image is typically 3--4 mag deeper than the SDSS one in surface 
-    brightness limit and has superb seeing condition (mean FWHM$=0.6$\asec{}).
-
-    In Paper~I, we select large sample of massive galaxies with either spectroscopic 
-    redshift or reliable ``red-sequence'' photometric redshift (\citealt{Rykoff2014}) 
+    We use $i$-band images for extracting surface brightness profiles.
+HSC $i$-band images are typically 3--4 mag deeper than SDSS (spell out here and reference ?????)  and have superb seeing conditions (mean $i$-band seeing has FWHM$=0.6$\asec{}).
+
+    In Paper~I, we select a sample of xxxxx(give number) massive galaxies with spectroscopic 
+    redshifts or reliable ``red-sequence'' photometric redshifts (\citealt{Rykoff2014}) 
     at $0.3<z<0.5$.
-    Within this redshift range, we have large enough volume to achieve reasonable 
-    statistics at very high \mstar{} end, can spatially resolve the inner $\sim 5$ 
-    kpc of massive galaxies ($1.0^{\arcsec}$ corresponds to 4.4 and 6.1 kpc at 
-    $z=0.3$ and 0.5), and can safely ignore any structural evolution. 
+Within this redshift range, we have a large enough volume (xxx give the number here) to sample the galaxy mass function above $M-*>11.6$, we can spatially resolve galaxies profiles to $\sim 5$
+    kpc ($1.0^{\arcsec}$ corresponds to 4.4 and 6.1 kpc at 
+    $z=0.3$ and 0.5), and we can safely ignore structural evolution over our redshift range (give time span in Gyr xxx).
+
     We derive $i$-band surface brightness profiles out to 100 kpc after carefully 
-    masking out any surrounding contaminations and correcting the background 
-    subtraction. 
-    We use the broadband spectral energy distributions (SED) fitting code 
+    masking out surrounding neighbors and accounting for the subtraction of the background light. We use the broadband spectral energy distributions (SED) fitting code 
     \texttt{iSEDFit}\footnote{http://www.sos.siena.edu/~jmoustakas/isedfit/} 
-    (\citealt{Moustakas13}) to measure the average \m2l{} and $k$--correction of 
-    these galaxies using five-band forced \cmodel{} magnitudes from \texttt{hscPipe}.
-    \citet{Chabrier2003} IMF, Flexible Stellar Population 
-    Synthesis\footnote{http://scholar.harvard.edu/cconroy/sps-models}
-    (FSPS; \texttt{v2.4}; \citealt{FSPS}, \citealt{Conroy2010}) model, 
-    \citet{Calzetti2000} extinction law, simple delayed-$\tau$ model for star 
-    formation history (SFH) are assumed here. 
-    Using these information, we obtain reliable \mden{} profiles of these 
-    galaxies out to $> 100$ kpc and \mstar{} integrated to different physical 
-    radius using elliptical apertures.
-
-    As explained in Paper I, here we focus on \mstar{} within
+    (\citealt{Moustakas13}) to measure \m2l{} ratios and $k$--corrections using five-band forced \cmodel{} magnitudes from \texttt{hscPipe}.
+We assume a Chabrier IMF \citep{Chabrier2003}, the Flexible Stellar Population
+    Synthesis models\footnote{http://scholar.harvard.edu/cconroy/sps-models}
+    (FSPS; \texttt{v2.4}; \citealt{FSPS}, \citealt{Conroy2010}), a Calzetti extinction law \citep{Calzetti2000}, and a simple delayed-$\tau$ model for star 
+    formation histories (SFH).
+Using HSC data, we can measure the mass profiles of massive galaxies to $\sim 100$ kpc and we integrate these profiles within isophotal elliptical apertures at different physical radii.
+As explained in Paper I, here focus on the two following metric masses:
 
@@
 
-        \item a 10 kpc radii (hereafter noted \minn{}) as proxy of the 
-            \textit{in situ} stellar component. 
-            This is motivated by recent observations and simulations 
-            (e.g.~\citealt{vanDokkum2010}, \citealt{RodriguezGomez2016}).
-
-        \item a 100 kpc radii (hereafter noted \mtot{}), which is shown to recover 
-            more \mstar{} than the ones based on \cmodel{} photometry, as proxy of the 
-            total \mstar{} of the galaxy.
-
+        \item stellar mass within 10 kpc (hereafter noted \minn{}) which we use as a proxy for the 
+            \textit{in situ} stellar component. This is motivated both by recent observations and simulations 
+            (e.g.~\citealt{vanDokkum2010}, \citealt{RodriguezGomez2016}). The value of 10 kpc that we quote here corresponds to the radius of the major axis of the isophotal ellipse (xxx check).
+        \item stellar mass within 100 kpc (hereafter noted \mtot{}).
+We use \mtot{} as a proxy of the total stellar mass.
+In Paper I we showed that \mtot{} recovers more light compared to HSC \cmodel{} photometry with offsets that can be a large as 0.2 dex in magnitude.
    \end{itemize}
 
-   Although these radius are empirically selected, they help recover the 
-   \mstar{}-dependence of the fraction of accreted stars, and reveal the diversity of 
+   We use these two simple metric masses to explore the 
+   \mstar{}-dependence of the fraction of accreted stars, and reveal to the diversity of 
    stellar envelopes among massive galaxies.
-   In Figure \ref{fig:m100_m10_color}, we demonstrate such diversity by showing 
-   a random subsample of massive galaxies with very similar \minn{} that have large 
+In practice, we also have the full profiles for each galaxy and can also cast our results in terms of the full stellar mass profiles.
+However, in many cases we find it more useful to display figures using the more simple \minn{} and \mtot{} quantities.
+In Figure \ref{fig:m100_m10_color}, we highlight the diversity of galaxies as a function of \minn{} and \mtot{}.
+Figure \ref{fig:m100_m10_color} shows a random subsample of massive galaxies with very similar \minn{} that have large
    range of \mtot{}. 
-   We will use these two apertures\mstar{} to guide the comparisons of massive galaxies 
-   from different environments.
+   We will use these two apertures masses to guide our comparisons of massive galaxies as a function of environments.
 
@@
     In this work, we focus on massive galaxies with \mtot{} $>10^{11.6}$~\msun{}. 
-    In Paper~I, we demonstrate that the \mstar{} completeness above this threshold is 
-    good over the full redshift range using comparisons with stellar mass functions 
-    from more complete samples.
-
-    We also wish to focus on massive galaxies that live at the centers of their own 
-    dark matter haloes-- so-called ``central'' galaxies.  
-    They are uniquely important to the study of galaxy-halo connection and are known 
-    to follow stellar mass--halo mass relation (SHMR; e.g. \citealt{Leauthaud2012, 
-    Behroozi2013, Kravtsov2014, Tinker2017}) at high-\mstar{} end with small scatter.
-    We utilize the \redm{} \texttt{v5.10} \citep{Rykoff2014, Rozo2015b} cluster catalog 
-    to identify central galaxies.
-
-    Firstly, we select 68 massive central galaxies from the \redm{} clusters 
+    In Paper~I, we demonstrate that this sample is almost mass complete over our full redshift range.
+In addition to the mass cut above, we also limit our sample to galaxies that live at the centers of their own
+    dark matter haloes-- so-called ``central'' galaxies. We use the \redm{} \texttt{v5.10} \citep{Rykoff2014, Rozo2015b} cluster catalog to construct a central galaxy sample.
+
+    %Central galaxies are important to the study of galaxy-halo connection and follow stellar mass--halo mass relation (SHMR; e.g. \citealt{Leauthaud2012, 
+    %Behroozi2013, Kravtsov2014, Tinker2017}) at high-\mstar{}.
+
+    Firstly, we select 68 massive central galaxies from \redm{} clusters 
     with $\lambda \geq 30$, $P_{\mathrm{Cen}} \geq 0.7$, and \logmtot{}$>11.5$ 
     at $0.3 < z < 0.5$ (63/69 have \logmtot{}$>11.6$). 
-    This $\lambda$ limit is chosen to mitigate incompleteness of low richness clusters
-    at the high end of our redshift window, and the $P_{\mathrm{Cen}}$ limit is 
-    selected to exclude low probability candidate of central galaxy. 
-    Based on the \mhalo{}-$\lambda$ relation calibrated by \citet{Simet2016}, these 
-    galaxies are the brightest cluster galaxies (BCGs) of clusters with 
-    \mhalo{}$>10^{14.2}$~\msun{}.
-    This calibration is consistent with other works (e.g. \citealt{Saro2015, Farahi2016, 
+    This $\lambda$ limit is chosen to mitigate incompleteness in the cluster catalog
+    at the high end of our redshift window. The $P_{\mathrm{Cen}}$ limit is 
+    selected to exclude low probability central galaxy candidates. 
+    Based on the \mhalo{}-$\lambda$ relation calibrated by \citet{Simet2016}, these corresponds to central galaxies living in halos with \mhalo{}$>10^{14.2}$~\msun{}.
+This calibration is consistent with other works (e.g.
+\citealt{Saro2015, Farahi2016,
     Melchior2016, Murata2017}). 
@@
     (\mhalo{}$\approx 3.0 \times 10^{14}$~\msun{}).
-    We will refer to this sample of \textbf{central galaxies in more massive haloes} as 
+    We will refer to this sample of \textbf{central galaxies in massive haloes} as 
     the \rbcg{} sample.
@@
     Then we estimate the $R_{\mathrm{200b}}$ of each cluster using the method in 
-    \citet{Diemer2015}. 
-    And we exclude all galaxies within a cylinder around each cluster, with the radius
-    equal to $R_{\mathrm{200b}}$ and length equal to twice the value of the photometric 
-    redshift uncertainty (typically around 0.015 to 0.025). 
-    We generally consider this sample as the central galaxies living in haloes with
-    $M_{\mathrm{200b}} < 10^{14}$~\msun{}, and will refer to this sample as \nbcg{}.
-    Initially, we select 3453 galaxies this way with \logmtot{}$> 11.2$ at 
-    $0.3 < z < 0.5$. 
-    Among them, 1564 (833) have \logmtot{}$> 11.5$ (11.6). 
+    \citet{Diemer2015}. We further exclude all galaxies within a cylinder around each cluster, with a radius
+    equal to $R_{\mathrm{200b}}$ and a length equal to twice the value of the photometric 
+    redshift uncertainty of the cluster (typically around 0.015 to 0.025). This second sample will be dominated by central galaxies living in haloes with
+    $M_{\mathrm{200b}} < 10^{14}$~\msun{}, and will refer to this sample as \nbcg{}. There are  833 galaxies with  
+\logmtot{}$> 11.6$ in this sample.
+
+%    Initially, we select 3453 galaxies this way with \logmtot{}$> 11.2$ at 
+%    $0.3 < z < 0.5$ \alexie{Why do we care about this?}. 
+%    Among them, 1564 (833) have \logmtot{}$> 11.5$ (11.6).
+
     Satellite contamination should be relative low at the high-\mtot{} end
@@
     For instance, the model from \citet{Saito2016} predicts a $\sim 7$\% 
-    contamination in the \logmtot{}$>11.6$ sample from satellites from 
-    \logmh$<11.4$ haloes.
+    fraction for galaxies with \logmtot{}$>11.6$ and \logmh$<11.4$ haloes.
 
     In Appendix~\ref{app:basic}, we show the distributions of redshift, \mtot{}, and 
-    \minn{} for \rbcg{} and \nbcg{} samples. 
+    \minn{} for the \rbcg{} and \nbcg{} samples. 
     We also compare these two samples on the \mtot{} - rest-frame $g-r$ color plane. 
-    Both of them follow the same ``red-sequence'' without much contamination from the 
-    ``blue clouds''.
-
-    It is worth noting that we failed to extract 1-D profiles for $\sim10$\% of 
-    \rbcg{} and \nbcg{} galaxies due to physical (e.g. on-going major merger) or 
-    nuisance (e.g.\ nearby foreground galaxy or bright star) reasons. 
-    These situations happen more frequently for lower-\mtot{} galaxies, and should not 
-    affect the results of this work.
+    Both of them follow the same ``red-sequence'' with only a handful of galaxies displaying bluer colors.
+
+    We note that our method fails to extract 1-D profiles for $\sim10$\% of 
+    \rbcg{} and \nbcg{} galaxies due on-going major mergers or projection effects (e.g.\ nearby foreground galaxy or bright stars).
+However, this small failure rate should not affect any of the results in this paper.
 
@@
 
-    As shown in Figure~\ref{fig:m100_m10_color}, massive central galaxies show 
-    intriguing diversity on the \mtot{}-\minn{} plane and in their \mden{} profiles 
-    in the outer haloes.  
-    In Paper~1, we explore the \mstar{}-dependence of the stellar haloes in massive 
-    galaxies, and conclude that the general trends are consistent with the 
-    predictions of two-phase formation scenario. 
-    In the following sections, we will investigate the relation between their 
-    present day halo mass and their stellar haloes using the \mden{} profiles and 
-    scaling relations for massive central galaxies with different $M_{\mathrm{200b}}$ 
-    (\rbcg{} and \nbcg{}).
-
-    We should emphasize again that although a circular aperture is shown on 
-    Fig~\ref{fig:m100_m10_color}, we extract 1-D \mden{} profiles, estimate 
-    \mtot{} and \minn{} using elliptical apertures defined by fluxed-weighted average 
-    isophotal shape. 
-    And, given the narrow \mstar{} and redshift range, we ignore \mstar{} growth 
-    and structural evolution here
-    (no star formation, lower merger rate \etal~e.g.\ \citealt{Bellstedt2016},
-    \citealt{Inagaki2015}; but also see \citealt{Bai2014}).
+    As shown in Figure~\ref{fig:m100_m10_color}, massive central galaxies at fixed  \minn{} display a large diversity in their stellar haloes.
+In Paper~1, we explored the \mstar{}-dependence of the stellar haloes in massive
+    galaxies, and concluded that the general trends are consistent with the 
+    predictions of the two-phase formation scenario.
+In this paper, we now investigate the relation between galaxy profiles, their stellar halos, and dark matter halo mass.
+Here we use \mtot{} as proxy for the ``total'' \mstar{}
+    of massive galaxies and we use \minn{} as a rough proxy for the mass of the 
+    \textit{in situ} component.  We remind the reader that although a circular aperture is shown on 
+    Fig~\ref{fig:m100_m10_color}, in practice we extract 1-D \mden{} profiles and estimate 
+    \mtot{} and \minn{} using elliptical apertures following the average fluxed-weighted isophotal shape.
+
+    % We said this already...
+    %Also,given the narrow \mstar
+    %{} and redshift range, we ignore \mstar{} growth 
+    %and structural evolution.
+
+% Not sure we need this? Seems too off hand
+%    (no star formation, lower merger rate \etal~e.g.\ \citealt{Bellstedt2016},
+%    \citealt{Inagaki2015}; but also see \citealt{Bai2014}).
 
@@
 
-    First, we ask whether the \mden{} profiles of massive central galaxies show 
-    \mhalo{}-dependence within 100 kpc at fixed \mstar{}. 
-    To perform meaning comparison, we build matched samples drawing from \rbcg{} and 
-    \nbcg{} that are carefully matched in \mstar{} and redshift using KDTree algorithm 
-    (please see Appendix~\ref{app:match} and Fig~\ref{fig:match} for details). 
-    The similar distributions of redshift of the matched samples ensure that the 
-    median \mden{} profiles from both samples are affected by seeing and background 
-    subtraction to the same extend. 
-    We address this issue more in Appendix~\ref{app:redshift}.
-
-    We match the \rbcg{} and \nbcg{} samples using both \mtot{} and \minn{} in this
-    work. 
-    As explained in Paper~1, we use \mtot{} as proxy of the ``total'' \mstar{}
-    of massive galaxies while treat \minn{} as a rough indicator of the mass of the 
-    \textit{in situ} component.
-
-%% ------------------------------------------------------------------------------------ %%     
-    Fig~\ref{fig:prof_1} compares the \mden{} profiles of massive central galaxies 
-    in \rbcg{} (orange-red color) and \nbcg{} (grey-black color) at fixed \mtot{} 
-    (left panel) and at fixed \minn{} (right panel). 
-    The top panels show the individual \mden{} profiles along with the median profiles 
-    for both samples. 
-    The bottom panel of Fig~\ref{fig:prof_1} shows the difference between the median 
-    \mden{} profile of \rbcg{} and \nbcg{} samples, with errors computed via bootstrap 
-    resampling.
-    $\Delta = \log(\mu_{\star, \mathrm{cenHighMh}}) - 
-    \log(\mu_{\star, \mathrm{cenLowMh}})$. 
-    This figure presents the main results of this work: \textbf{The \mden{} profiles of 
-    massive central galaxies show \mhalo{}-dependence at both fixed \mtot{} and 
+    First, we ask whether the \mden{} profiles of massive central galaxies depend on halo mass at fixed stellar mass.
+To ask this question, however, we must first define which stellar mass exactly is being fixed in the comparison.
+We will show results both when we fix \mtot{} as well as when we fix \minn{}.
+We also ensure that all comparisons are performed with a fixed underlying redshift distribution by mathcing samples in redshift in addition to stellar mass
+    (please see Appendix~\ref{app:match}, Appendix~\ref{app:redshift}, and Fig~\ref{fig:match} for details).
+
+%    The similar distributions of redshift of the matched samples ensure that the 
+%    median \mden{} profiles from both samples are affected by seeing and background 
+%    subtraction to the same extent.
+
+%% ------------------------------------------------------------------------------------ %%     
+    Fig~\ref{fig:prof_1} compares the \mden{} profiles of massive central galaxies living in low mass dark matter haloes to those living in high mass dark matter haloes at fixed \mtot{} 
+    (left panel) and at fixed \minn{} (right panel). This Figure shows the main result of this paper, namely that \textbf{the \mden{} profiles of 
+    massive central galaxies show a clear dependence on dark matter halo mass at both fixed \mtot{} and 
     \minn{}.}
-    For both \mtot{}-- and \minn{}--matched samples, we see systematic differences
-    between the median \mden{} profile of \rbcg{} galaxies and the one for \nbcg{}
-    galaxies.
-
-    We perform statistical tests to show that the differences we see in the median 
+
+    We perform several statistical tests to demonstrate that the differences we see in the median 
     \mden{} profiles are significant.
-    We also conduct a variety of tests that verify the robustness of these results 
-    against choices of \mtot{} bins, $\lambda$ cut, redshift range, and the proxy
-    of ``total'' or \textit{in situ} stellar mass. 
-    Please see Appendix~\ref{app:robust} for more details about these tests.
-
-    There are several important points to be noticed on the left panel of 
-    Fig~\ref{fig:prof_1}.
+We also conduct a variety of tests that verify the robustness of these results with respect choices regarding \mtot{} bins, our $\lambda$ cut, the redshift range, and the choice of apertures used for the metric masses.
+Please see Appendix~\ref{app:robust} for further details.
+
+    The key features in Figure Fig~\ref{fig:prof_1} are the following:
 
@@
 
-        \item First, for the \mtot{} matched sample, although the difference in 
-            median \mden{} profiles is systematical and robust, the overall difference 
-            is very subtle and only becomes clear in the outskirts at $R>50$ kpc, 
-            which explains why such environment dependence is extremely difficult 
-            for previous works to detect using shallower images.
-
-        \item Second, we find that, at fixed \mtot{}, massive central galaxies in 
-            more massive dark mater haloes display shallower \mden{} profiles that the 
-            ones living in less massive haloes. 
-            This can be seen from the more flattened inner \mden{} profile and more 
-            significant outer stellar haloes.
-
-        \item Third, the median \mden{} profiles of \rbcg{} and \nbcg{} cross each 
-            other at ${\sim} 15$-20 kpc, the expected $R_{\mathrm{e}}$ for massive 
-            ETGs around this \mtot{}.
-
-        \item Finally, such systematic difference in \mden{} profiles may become more 
-            significant at higher \mtot{}.
-            We see evidence of this using the $Delta$ profiles of two \mtot{} 
-            bins (see Fig~\ref{fig:prof_2} and discussion in 
-            Appendix~\ref{app:robust})\footnote{Though the lower \mtot{} bin becomes 
-            somewhat incomplete} and when we discuss the relation between \mtot{} and 
-            \minn{} (see Fig~\ref{fig:scaling_relation}). 
-            This trend has potentially interesting implication that is worth more 
-            investigations later.
-
+        \item For the \mtot{} matched sample, although there is a clear and robust difference between the two median \mden{} profiles, the overall difference is subtle is mainly only apparent on $R>50$ kpc scales.
+This may explain why previous attempts to detect this signal using shallower images were not successful.
+        \item At fixed \mtot{}, central galaxies in high mass dark matter haloes display shallower \mden{} profiles compared to those living in low mass dark matter haloes (they have a flatter inner \mden{} profiles and more significant outer stellar haloes.
+        \item The median \mden{} profiles of the \rbcg{} and \nbcg{} samples cross each 
+            other at ${\sim} 15$-20 kpc, roughly also the scale of the effective radius $R_{\mathrm{e}}$.      
+        \item Finally, the differences between the two sets of profiles becomes more prominent at higher \mtot{}.
+This can be seen further dividing the sample into two \mtot{} bins (see Fig~\ref{fig:prof_2} and discussion in
+            Appendix~\ref{app:robust}) and when we discuss the relation between \mtot{} and 
+            \minn{} (see Fig~\ref{fig:scaling_relation}). This trend has potentially interesting implications \alexie{can we explain in one phrase?} that will be investigated in follow-up work. 
     \end{itemize}
 
+\alexie{lets chat about the following two paragraphs}
     Generally speaking, such subtle environmental dependence of \mden{} profiles in 
@@
 
-    Although the comparisons of \mden{} profiles can reveal the environment dependence 
-    directly, it is not straightforward to compare with other observations, model 
-    predictions or numerical simulations. 
-    In this section, we compare the \rbcg{} and \nbcg{} galaxies on 
-    1) the well-know \mstar{}--$R_{\mathrm{e}}$ relation; 
-    2) the \mtot{}--\minn{} plane.
+    The previous section showed that the \mden{} profiles of massive galaxies show a dependence on the dark matter mass of their host halos.
+In this section, we now turn our attention to the more commonly studied mass size relation  (\mstar{}--$R_{\mathrm{e}}$).
+In addition, we will also consider halo mass dependence in the \mtot{}--\minn{} plane.
 
@@
     vdWel2014}) is one of the most important scaling relation for ETGs. 
-    Despite numerous attempts, previous works failed to demonstrate the impact of 
-    environment to the \mstar{}--$R_{\mathrm{e}}$ relation at low-$z$ 
+    Despite numerous attempts, previous studies have failed to detect the dark matter halo mass dependence of the \mstar{}--$R_{\mathrm{e}}$ relation at low-$z$ 
     (e.g. \citealt{Weinmann2009, Nair2010, HCompany13, Cerbrian2014}; 
@@
 
-    In the last section, we show that the median \mden{} profiles of massive central 
-    galaxies depend on environment. 
-    We therefore expect to also see difference in the \mstar{}--$R_{\mathrm{e}}$ 
-    relations of the \rbcg{} and \nbcg{} samples. 
-    For this purpose, we still use \mtot{} as proxy of ``total'' \mstar{}, and adopt 
-    the radius enclosing 50\% of luminosity within 100 kpc ($R_{\mathrm{50}}$; derived 
-    from the $i$-band curve-of-growth) as ``size''. 
-    This definition of ``effective radius'' is more robust against structural details, 
-    choice of model, and the background subtraction. 
-    Massive galaxies from this sample are large enough so we do not need to worry 
-    about the effects of seeing.
-
-    Left panel of Fig~\ref{fig:scaling_relation} shows the \mtot{}--$R_{\mathrm{50}}$
-    relations for both \rbcg{} (orange--red color) and \nbcg{} (grey--black color). 
-    We fit the \logmtot{}-$\log (R_{\mathrm{50}}/\mathrm{kpc})$ relations at 
-    \logmtot{}$\geq 11.6$ using MCMC method with the help from ensemble sampler 
-    \texttt{emcee} (\citealt{Emcee})\footnote{The initial guesses are based on maximum 
-    likelihood estimates, and we assume reasonable flat priors for parameters.}.
+    The previous section clearly showed that the profiles of massive galaxies depend on the masses of their host dark matter halos.
+We now ask whether or not this dependence is also manifest when considered in terms of the more traditionally studied \mstar{}--$R_{\mathrm{e}}$ relation.
+However, when considering the mass-size relation, there is ambiguity and multiple approaches in terms of defining "sizes".
+This is especially true in the context of massive galaxies with extended stellar haloes (a reason why we prefer to show profiles directly as in the previous section).
+In this section, we still use \mtot{} as proxy of ``total'' \mstar{} and we adopt
+    the radius enclosing 50\% of luminosity \alexie{mass?} within 100 kpc ($R_{\mathrm{50}}$; derived 
+    from the $i$-band curve-of-growth) as the ``size''. This definition of ``effective radius'' is more robust against structural details, 
+    choice of model, and the background subtraction \alexie{compared to what?}. 
+    Massive galaxies from this sample are large enough that the impact of seeing is not a concern.
+
+    The left panel of Fig~\ref{fig:scaling_relation} shows the \mtot{}--$R_{\mathrm{50}}$
+    relations for galaxies in high and low mass dark matter halos.
+We fit the \logmtot{}-$\log (R_{\mathrm{50}}/\mathrm{kpc})$ relations at $\log(M_{\star,100})>11.6$ using the \texttt{emcee} MCMC sampler (\citealt{Emcee})\footnote{The initial guesses are based on maximum
+    likelihood estimates, and we assume flat priors for parameters.}.
+
     The best-fit relation for \rbcg{} is:
@@
         \begin{aligned}
-        \log (R_{\mathrm{50}}/\mathrm{kpc}) = & (0.73\pm0.13) \times \log (M_{\star, 100\ \mathrm{kpc}}/M_{\odot}) \\ & -(7.49\pm1.56)
+        \log (R_{\mathrm{50}}/\mathrm{kpc}) = & (0.74\pm0.13) \times \log (M_{\star, 100\ \mathrm{kpc}}/M_{\odot}) \\ & -(7.56\pm1.56)
         \end{aligned}
@@
 
-    \noindent As shown in the left panel of Fig~\ref{fig:scaling_relation}, the slopes 
-    of the \mtot{}--$R_{\mathrm{50}}$ relations are similar, but their normalizations 
-    show difference between the \rbcg{} and \nbcg{} galaxies. 
-    This result is robust against the ranges of \mstar{}, also against the definitions 
+    \noindent As shown in the left panel of Fig~\ref{fig:scaling_relation}, galaxies in low and high mass haloes live on \mtot{}--$R_{\mathrm{50}}$ relations that have similar slopes but different normalizations.
+This result is robust against the ranges of \mstar{} over which the fit is performed and against the definitions
     of  ``total'' \mstar{} and half-light radius\footnote{Using \mstar{} within 120 or 
-    150 kpc, or using the $R_{\mathrm{50}}$ derived within these apertures will not 
+    150 kpc, or using the $R_{\mathrm{50}}$ derived within these apertures does not 
     change the results.}.
@@
     $12.5 \le$ \logmh{} $< 15$ haloes. 
-    HC13 uses the group catalog by \citet{Yang2007} to estimate \mhalo{}. 
-    They estimate the 2-D $R_{\mathrm{e}}$ using single-\ser{} model fitting to SDSS 
-    images, and derived \mstar{} based on SED fitting using the BC03 (\citealt{BC03}) 
-    synthetic population model. 
-    The \mstar{} estimates are empirically converted from a Kroupa IMF to a Chabrier 
-    IMF by applying a constant -0.05 shift (see \citealt{Bernardi2016}).
-    We add $+0.1$dex to the HSC13 \mstar{} to account for the systematic 
-    difference between their BC03 and our FSPS model (see Appendix~\ref{app:sed}). 
-    The distributions of both \rbcg{} and \nbcg{} galaxies on the 
+    HC13 use the group catalog by \citet{Yang2007} to estimate halo mass. They obtain effective radii from  single-\ser{} model fitting to SDSS 
+    images and \mstar{} based on SED fitting using the BC03 (\citealt{BC03}) 
+    synthetic population model. We convert their \mstar{} estimates from a Kroupa IMF to a Chabrier 
+    IMF by applying a constant -0.05 dex shift (see \citealt{Bernardi2016a}).
+We further add $+0.1$dex to the HSC13 stellar masses to account for a systematic offset between BC03 and our FSPS model (see Paper~1).
+    The distributions of galaxies on the 
     \mtot{}--$R_{\mathrm{50}}$ plane follow the HC13 relation reasonably well 
@@
     In contrast to the present study, HC13 finds no environment dependence in the 
-    mass--size relation for central galaxies from $12.5\le$ \logmh{} $<15.0$ haloes.
-    The \mstar{} and $R_{\mathrm{e}}$ in HC13 are based on much shallower SDSS images
-    that can not constrain the environment-sensitive outer stellar haloes well. 
-    Detailed analysis on this topic is beyond the scope of this work, but we briefly 
+    mass--size relation for central galaxies in the range $12.5\le$ \logmh{} $<15.0$.
+However, HC13 use SDSS which is considerably shallower compared the HSC and hence will not be as sensitive to the outer portions of the profile where we see the largest differences.
+A more detailed comparison is beyond the scope of this work, but we briefly \alexie{we demsontrate what exactly?
+chat about this test}
     demonstrate this using the \rbcg{} and \nbcg{} galaxies that overlap with the GAMA
     survey (please see Appendix~\ref{app:gama} for details).
+
     We matched the two samples using the \mstar{} measured using single-\ser{} 2-D
@@
     central galaxies at $0.3 < z < 0.5$ depends on halo mass. 
-    At fixed \mtot{}, massive central galaxies in denser environment (higher \mhalo{}) 
-    have slightly larger $R_{\mathrm{50}}$ comparing to ones in smaller haloes at fixed 
+    At fixed \mtot{}, massive central galaxies in denser environments (higher \mhalo{}) 
+    have larger $R_{\mathrm{50}}$ comparing to ones in smaller haloes at fixed 
     \mtot{}. 
@@
 
-    Now we investigate the relationship between \mstar{} within two elliptical 
-    apertures (\mtot{} v.s. \minn{}) as alternative tool to help us explore the 
-    structure and assembly of massive galaxies.
-    Comparing to the mass--size relation, this relation is not affected by the 
-    ambiguous definition of ``size'', and it is easier to apply it to larger 
-    samples or numerical simulations.
-
-    The right panel of Fig \ref{fig:scaling_relation} compares the \rbcg{} and \nbcg{}
-    galaxies on the \mtot{}--\minn{} plane.
-    We show that these two samples occupy slightly different locations on this plane,
-    and follow different best--fit \mtot{}--\minn{} relations. 
+    Now we investigate the relationship \mtot{}, \minn{}, and halo mass.
+Compared to the mass--size relation, the \mtot{}--\minn{} relation is not plagued by the ambiguity of galaxy ``size'', and also enables a more straightforward comparison with numerical simulations.
+
+    The right panel of Fig \ref{fig:scaling_relation} compares \rbcg{} and \nbcg{}
+    galaxies on the \mtot{}--\minn{} plane. We find that these two samples are offset when considered in this plane a follow distinct best-fit \mtot{}--\minn{} relations. 
     For \rbcg{} galaxies with \logmtot{}$>11.6$ we find:
@@
 
-    These results are robust against the \mtot{} range for fitting, and they will not 
-    be affected if we replace the \minn{} with \mstar{} within 5 or 15 kpc apertures
-    or replace the \mtot{} with \mstar{} within 120 or 150 kpc apertures.  
-    The \mtot{}--$M_{\star, 5\ \mathrm{kpc}}$ relation actually suggests clearer 
-    \mhalo{}-dependence at high-\mtot{} end, but the $M_{\star, 5\ \mathrm{kpc}}$ 
-    are more vulnerable to the impact from seeing than \minn{}.
-
-    We conclude that: 
-    (1) At fixed \mtot{}, central galaxies in more massive haloes tend to have 
-    lower fractions of \mstar{} stored in the inner region; 
-    (2) For massive galaxies with similar \minn{}, the ones in more massive haloes on 
-    average have more prominent outer envelopes. 
-    The scientific implication of this result is briefly discussed in 
+    These results are robust against the exact choice for the \mtot{} range over which the fit is performed.
+These results are also unchanged if \minn{} is replaced by mass within a 5 or a 15 kpc aperture, or if \mtot{} is replaced with mass within a 120 or a 150 kpc aperture.
+
+%    The \mtot{}--$M_{\star, 5\ \mathrm{kpc}}$ relation actually suggests clearer 
+%    \mhalo{}-dependence at high-\mtot{} end, but the $M_{\star, 5\ \mathrm{kpc}}$ 
+%    are more vulnerable to the impact from seeing than \minn{}.
+
+    From Figure \ref{fig:scaling_relation} we can draw the same conclusions as in the previous section, namely that: at fixed \mtot{}, central galaxies in more massive haloes tend to have less galaxy mass in the inner regions but display more prominent outer envelopes.
+The scientific implication of this result is discussed in
     Section~\ref{sec:discussion}.
+
+\alexie{This seems too detailed. This also belongs in the discusison section}
 
@@
 
-    In Paper~1, we show that the ellipticity of outer stellar halo in massive galaxy 
-    steadily increases with \mtot{}, while the rest--frame color gradients do not show 
-    clear \mtot{}-dependence. 
-    Both these results provide us more insights about the assembly of massive galaxies. 
-    Here we quickly look into the environment dependence of ellipticity and 
-    rest--frame color profiles (Figure~\ref{fig:ell_color}).
-
-    We focus on ellipticity and color profiles within 5--60 kpc where we can safely 
-    ignore differences in sky subtraction and seeing across different bands. 
-    We apply Galactic extinction and $k$-correction to both $(g-r)$ and $(g-i)$ color 
-    profiles.
-    We show the average ellipticity, $g-r$, and $g-i$ color profiles for the 
-    \mtot{}-matched (\minn{}-matched) samples of \rbcg{} and \nbcg{} galaxies on the 
-    left (right) side of \ref{fig:ell_color} along with comparisons with previous 
-    works based on stacked SDSS galaxies 
-    (e.g. \citealt{LaBarbera2010, Tal2011, DSouza2014}).
-
-    These results show:
+    In Paper~1, we show that the ellipticity of the outer stellar halo increases with \mtot{}, while in contrast, rest--frame color gradients do not display any strong \mtot{}-dependencies.
+In this paper, we take this analysis one step further to investigate whether or not either of these quantities display a halo mass dependency.
+We focus on ellipticity and color profiles within 5--60 kpc where we can ignore differences in sky subtraction and seeing across different bands.
+Galactic extinction and $k$-corrections are applied to both $(g-r)$ and $(g-i)$ color profiles.
+
+    Figure \ref{fig:ell_color} shows the average ellipticity, $g-r$, and $g-i$ color profiles for galaxies living in low and high mass haloes both at fixed \mtot{} and at fixed \minn{}.
+We also compared our results with previous studies that stacked SDSS images (e.g.
+\citealt{LaBarbera2010, Tal2011, DSouza2014}).
+Figure \ref{fig:ell_color} shows that:
 
     \begin{itemize}
-
-        \item Once matched at fixed \mtot{}, the \rbcg{} and \nbcg{} galaxies 
-            show similar average ellipticity profiles. 
-            There is hint that suggests the central galaxies from more massive 
+        \item \alexie{discuss here}. Galaxies in low and high mass haloes display similar ellipticity profiles at fixed \mtot{}. There is hint that suggests the central galaxies from more massive 
             haloes become slightly more elongated at $R>50$ kpc than the ones 
@@
             conclusive.              
-
         \item For the \minn{}-matched samples, the \rbcg{} galaxies show higher
@@
             of massive haloes relate to the accreted stars.         
-
-        \item For the rest--frame color gradients, we find shallow and negative 
-            gradients for both \rbcg{} and \nbcg{} galaxies using both colors.
-            We find no significant difference for both the \mtot{}- and 
-            \minn{}--matched samples within 60 kpc.
-
+        \item Galaxies in low and high mass dark matter haloes display similar rest--frame color gradients (at $r<60$ kpc) at fixed \mtot{} and at fixed  \minn{}.    
     \end{itemize}
 
-    Besides these conclusions, these comparisons also suggest:
-
-    \begin{itemize}
-
-        \item The smooth ellipticity profile and its shallow gradient supports 
+    Besides these conclusions, the fact that we find  smooth ellipticity profile and its shallow gradient supports 
             the idea of using the flux-weighted average isophotal shape to 
@@
 
-        \item The similarity of average rest-frame color profiles between the 
+     The similarity of average rest-frame color profiles between the 
             \rbcg{} and \nbcg{} samples suggests that \mden{} profiles based on 
@@
 
-    \end{itemize}
 %% ------------------------------------------------------------------------------------ %%
@@
 
-    Using the deep images from the HSC survey, we show that the stellar mass 
-    distributions of massive central galaxies at $0.3 < z < 0.5$ depend on their 
-    environment or \mhalo{}. 
-    Here we briefly discuss the physical implications and potential caveats of this 
-    result.
+    %Using the deep images from the HSC survey, we show that the stellar mass 
+    %distributions of massive central galaxies at $0.3 < z < 0.5$ depend on their 
+    %environment or \mhalo{}. 
+    %Here we briefly discuss the physical implications and potential caveats of this 
+    %result.
 
@@
 
-    Results presented here are broadly consistent with the picture that massive central 
-    galaxies form via a ``two-phase'' picture.
-
-    According to this theory, the cores of massive galaxies were formed at $z{\sim} 2$ 
-    during an intense period of \textit{in situ} star formation. 
-    The outskirts of massive galaxies are then built up via a more gradual second 
-    phase of evolution (the ``ex-situ'' phase) which is dominated by mass growth via 
-    the accretion of satellite systems. 
-    Non-dissipative minor mergers mostly deposit stars on the outskirts of the 
-    centrals and do not have large impact on the central \mden{} profile 
-    (e.g. \citealt{Oogi2013, Bedorf2013}). 
-    Hence, according to this picture, the outer stellar envelopes of massive centrals 
-    should correlate with the masses of their host haloes, in qualitative agreement with
-    our findings.
-
-    State of the art hydrodynamic simulations suggest that massive dark matter haloes 
-    have central galaxies that have outer stellar envelopes with shallow slopes 
-    (e.g. \citealt{Pillepich2014}). 
-    This is consistent with the results in Fig \ref{fig:prof_1}.
-
-    Meanwhile, these simulation also point out that the fraction of accreted stars 
-    increases steeply with total \mstar{} and that the ``ex-situ'' component
-    starts to dominate the \mden{} profiles around $R_{\mathrm{e}}$ for 
-    \logms{}$\geq 11.5$ galaxies. 
-    In this work, we find that the median \mden{} profiles of \rbcg{} and \nbcg{} 
-    samples start to show differences around 15-20 kpc, which is close to 
-    their $R_{\mathrm{e}}$. 
-    Furthermore, the environmental dependence of our median \mden{} profiles 
-    becomes more significant in our highest \mtot{} bin (see Fig \ref{fig:prof_4}). 
-    These results all align with the picture that the \mhalo{}-dependence of the 
-    \mden{} profiles of massive galaxies is driven by the variations in the 
-    ``ex-situ'' component at large radii.
-
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %% 
-\subsection{Scatter in Outer Stellar Enveloppes and ``cD'' Galaxies}
-
-   The thin lines in Figure \ref{fig:prof_1} show the \mden{} density profiles of 
-   individual galaxies. 
-   In general, we find that any given galaxy has a relatively smooth profile, even out 
-   to large radii, however, on a galax-by-galaxy basis there is a large (but continuous) 
-   variation in the amplitude of \mden{} at large scales. 
-   Traditionally, the so-called ``cD'' galaxies are defined to have large stellar 
-   envelopes and are found at the hearts of massive clusters (\citealt{Matthews1964, 
-   Schombert1988}). 
-   However, until present, it has not been clear whether ``cD'' galaxies are a distinct 
-   and special population, or if they are simply the conti of a smoothly varying 
-   population. 
-   Fig \ref{fig:prof_1} shows that with the help of our deep HSC images, we can directly 
-   map out the variations in \mden{} profiles at large scales. 
-   Instead of a bi-model distribution, we find that the outskirts of massive galaxies 
-   display a smooth but continuous variation. 
-   We can hence conclude that ``cD'' galaxies are simply the extremes of a continuous 
-   population but that do not necessarily form a unique a special class of galaxies. 
-   This suggests that it might not be very physically meaningful to separate these 
-   massive galaxies into two arbitrary morphological classes (``cD'' versus non-``cD''). 
-   This conclusion is similar to those of \citep{Zhao2015} who found that a large 
-   fraction of nearby BCGs (34\%) does not fall into the ``cD'' class. 
-   Our finding that massive galaxies display a diverse range of outer stellar 
-   envelope is also supported by HST observations of BCGs at $0.3 < z <0.9$ 
-   by \citealt{Bai2014}. 
+    Results presented here are broadly consistent with the ``two-phase'' formation
+    scenario of massive central galaxies in a hierarchical universe. 
+    Under this picture, intense dissipative processes at $z > 2$ are responsible for 
+    the formation of the \textit{in situ} stars in massive central galaxies. 
+    After the star formation was quenched, the more gradual second phase of evolution
+    is dominated by non-dissipative mergers of satellite galaxies. 
+    Since dry minor mergers can effectively deposit \textit{ex situ} stars on to the 
+    outskirts of these massive galaxies (e.g. \citealt{Oogi2013, Bedorf2013}), 
+    it is expected that the stellar mass distributions of massive galaxies 
+    show halo mass dependence, as the central galaxies of more massive haloes should
+    experience more mergers.
+
+    \citet{Shankar2014} investigates the environment dependence of galaxy size using 
+    a series of hierarchical semi-analytic models. 
+    All models suggest that, at fixed stellar mass, the median size of galaxies 
+    strongly increases with halo mass. 
+    Although the centrals of more massive halos only experience slightly higher 
+    number of major mergers (mass ratio $>1$:3; e.g. \citealt{Hirschmann2013}), 
+    the number of minor mergers strongly depend on the assumed dynamical friction time. 
+    If short dynamical friction time is favored (e.g. \citealt{Newman2012}), 
+    centrals of more massive haloes can have up to four times more minor mergers 
+    (1:100--1:3). 
+    These extra minor mergers alone can lead to moderate halo mass dependence of 
+    size. 
+    Similarly, \citet{Yoon2017} confirms these theoretical predictions using 
+    semi-analytic model from \citet{Guo2011}.
+
+    These predictions are in general agreement with our findings here as we do see 
+    differences of \mden{} profiles in the outskirts are a major driver of the 
+    halo mass dependence, especially for the \minn{}--matched samples. 
+    At the same same, whether or not the difference in number of mergers can explain 
+    all the environment dependence is yet to be examined.
+
+    Both semi-analytic models and hydrodynamic simulations still have difficulties 
+    reproducing the observed mass--size relation for massive galaxies. 
+    Besides the reasons related to physical recipes, it is not straightforward for 
+    simulations to predict galaxy size in the same way with observations may also 
+    contribute to the problem. 
+    Since the definition of apertures mass is more clear, it would be interesting 
+    to compare with simulations using the \mtot{}--\minn{} relation instead of the 
+    mass--size one.
+
+    More importantly, our results show that the inner region of massive central 
+    galaxies also play a role here. 
+    Both the \mden{} profiles of \mtot{}--matched samples and the \mtot{}--\minn{}
+    plane suggest that, at fixed \mtot{}, centrals of more massive haloes have 
+    slightly shallower inner \mden{} slope and lower \mtot{}.  
+    Minor mergers can not explain such difference as they should not alter the inner 
+    \mden{} profiles. 
+    This is also not caused by the choice of outer aperture to estimate ``total''
+    \mstar{}: assuming that centrals in more massive haloes have more extended 
+    \mden{} profiles, integration out to larger aperture will make the differences 
+    between \rbcg{} and \nbcg{} galaxies on the \mtot{}--\minn{} plane more significant. 
+    The fact that, at fixed \mtot{}, the overall stellar mass distributions of massive
+    central galaxies relate to halo mass may hint us more insights about the connection 
+    between the assembly of massive haloes and their central galaxies, and it is worth 
+    further investigation.
+
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
+\subsection{Comparisons with Mass--Size Relations from Other Works}
+
+    The best-fit mass--size relation derived here suggests that, at $0.3 < z < 0.5$, 
+    central galaxies with \logmtot{}$>11.6$ in \logmhalo{}$>14.0$ haloes are on average
+    $\sim20$\% larger than the centrals from \logmhalo{}$<14.0$ haloes at fixed \mtot{}.
+
+    Previous works on this topic at lower redshift mostly find no environment dependence
+    of mass--size relation (e.g. \citealt{Nair2010, Maltby2010, Cappellari2013, 
+    HCompany13}).  
+    The discrepancy between these results and ours should be explained by limitation of 
+    shallower images, method for estimating galaxy size, differences in \mstar{} and 
+    \mhalo{} ranges. 
+    \citet{Cerbrian2014} finds that ETGs with \logms{}$>11.5$ are slightly larger in 
+    more massive haloes, but they also shows that this environment trend is reversed 
+    at lower \mstar{}. 
+    \citet{Yoon2017} carefully studies a large sample of $z\sim0.1$ SDSS ETGs using  
+    non-parametric method and recovers a clear environment dependence of mass-size 
+    relation at \logms{}$>11.2$. 
+    They conclude that, at the same \mstar{}, massive ETGs from dense environment 
+    are 20--40\% larger than the ones in underdense environment. 
+    The definition of environment, estimates of \mstar{} and sizes in \citet{Yoon2017} 
+    are different with this work, but the results generally agree with ours.
+
+    Although recent results start to agree that mass--size relation of massive
+    ETGs show environment dependence, the situation at higher redshift is complicated. 
+    While certain works find environment dependence of mass--size relation for massive 
+    quiescent or early-type galaxies that is qualitatively consistent with the 
+    low-$z$ results (e.g. \citealt{Papovich2012, Lani2013, Strazzullo2013, 
+    Delaye2014}), there are still observations that suggest otherwise (e.g. 
+    \citealt{Rettura2010, Raichoor2012, Kelkar2015, Allen2015}). 
+    Some of this confusion can be explained by smaller sample size, special environment
+    (high-$z$ massive cluster), or impact of massive star-forming galaxies. 
+    But it also reflects the intrinsic difficulty of measuring \mstar{} and size 
+    of high-$z$ galaxies (e.g. \cite{Price2017}).
+    As we suggested earlier, with the help of deeper observations at higher redshift, 
+    it would be beneficial to directly compare the rest-frame surface brightness 
+    or the stellar mass density profiles instead of using mass--size relation alone 
+    (e.g. \citealt{Szomoru2012, Patel2013, Buitrago2017, Hill2017}).
 %% ------------------------------------------------------------------------------------ %%
@@
           \textbf{Top-left}: The \logms{}-$g-r$ color relation of the \rbcg{} 
-          (red circle; detaield format is the same with the right panel of 
-          Fig~\ref{fig:smf1}) and \nbcg{} (grey dots) samples.
+          (red circle) and \nbcg{} (grey dots) samples.
           We apply the $k$-corrections from \texttt{iSEDFit} fitting to the colors.~~          
@@
         We plot the \logmgama{} against the difference between \logmtot{} and \logmgama{}. 
-        The format is very similar to the left panel of Fig~\ref{fig:smf1}. 
         The two vertical lines highlight the mass range $11.4 \leq$\logmgama{}$<11.8$ 

### 2017-07-26 draft/paper2_v3.tex
Edit sample and data 1

@@
     (\citealt{HSC-DR1} and covers ${\sim} 110$ deg$^2$ in all five-band ($grizy$) to 
-    the full depth in the Wide field. The data are reduced by \texttt{hscPipe 4.0.2}, a derivative of the 
+    the full depth in the Wide field. 
+    The data are reduced by \texttt{hscPipe 4.0.2}, a derivative of the 
     Large Synoptic Survey Telescope (LSST) pipeline (e.g.\ \citealt{Juric2015}; 
@@
     We use $i$-band images for extracting surface brightness profiles. 
-HSC $i$-band images are typically 3--4 mag deeper than SDSS (spell out here and reference ?????)  and have superb seeing conditions (mean $i$-band seeing has FWHM$=0.6$\asec{}).
-
-    In Paper~I, we select a sample of xxxxx(give number) massive galaxies with spectroscopic 
+    HSC $i$-band images are typically 3--4 mag deeper than SDSS 
+    (Sloan Digital Sky Survey; e.g. \citealt{SDSS-DR7, SDSS-DR8, SDSS-DR12})  
+    and have superb seeing conditions (mean $i$-band seeing has FWHM$=0.6$\asec{}).
+
+    In Paper~I, we select a sample of 25286 bright galaxies with spectroscopic 
     redshifts or reliable ``red-sequence'' photometric redshifts (\citealt{Rykoff2014}) 
     at $0.3<z<0.5$. 
-Within this redshift range, we have a large enough volume (xxx give the number here) to sample the galaxy mass function above $M-*>11.6$, we can spatially resolve galaxies profiles to $\sim 5$
-    kpc ($1.0^{\arcsec}$ corresponds to 4.4 and 6.1 kpc at 
-    $z=0.3$ and 0.5), and we can safely ignore structural evolution over our redshift range (give time span in Gyr xxx).
+    Within this redshift range, we have a large enough volume 
+    ($\sim5\times 10^6$ Mpc$^3$) to sample the galaxy stellar mass function above 
+    \logms$>11.6$, we can spatially resolve galaxies profiles to $\sim 5$ kpc 
+    ($1.0^{\arcsec}$ corresponds to 4.4 and 6.1 kpc at $z=0.3$ and 0.5), and we can 
+    safely ignore structural evolution over our redshift range ($\sim$1.5 Gyr of 
+    time span).
 

### 2017-07-26 draft/paper2_v3.tex
Edit data and sample 2

@@
     Our main results are presented in \S \ref{sec:result} and discussed in 
-    \S \ref{sec:discussion}. Section
-    \S \ref{sec:summary} presents our summary and conclusions.
+    \S \ref{sec:discussion}. 
+    Section \S \ref{sec:summary} presents our summary and conclusions.
 
@@
     We derive $i$-band surface brightness profiles out to 100 kpc after carefully 
-    masking out surrounding neighbors and accounting for the subtraction of the background light. We use the broadband spectral energy distributions (SED) fitting code 
+    masking out surrounding neighbors and accounting for the subtraction of the 
+    background light. 
+    We use the broadband spectral energy distributions (SED) fitting code 
     \texttt{iSEDFit}\footnote{http://www.sos.siena.edu/~jmoustakas/isedfit/} 
-    (\citealt{Moustakas13}) to measure \m2l{} ratios and $k$--corrections using five-band forced \cmodel{} magnitudes from \texttt{hscPipe}.
-We assume a Chabrier IMF \citep{Chabrier2003}, the Flexible Stellar Population
+    (\citealt{Moustakas13}) to measure \m2l{} ratios and $k$--corrections using 
+    five-band forced \cmodel{} magnitudes from \texttt{hscPipe}. 
+    We assume a \citet{Chabrier2003} IMF, the Flexible Stellar Population 
     Synthesis models\footnote{http://scholar.harvard.edu/cconroy/sps-models}
-    (FSPS; \texttt{v2.4}; \citealt{FSPS}, \citealt{Conroy2010}), a Calzetti extinction law \citep{Calzetti2000}, and a simple delayed-$\tau$ model for star 
-    formation histories (SFH).
-Using HSC data, we can measure the mass profiles of massive galaxies to $\sim 100$ kpc and we integrate these profiles within isophotal elliptical apertures at different physical radii.
-As explained in Paper I, here focus on the two following metric masses:
+    (FSPS; \texttt{v2.4}; \citealt{FSPS}, \citealt{Conroy2010}), the 
+    \citet{Calzetti2000} extinction law, and a simple delayed-$\tau$ model for 
+    star formation histories (SFH). 
+    Using HSC data, we can measure the \mden{} profiles of massive galaxies to 
+    $\sim 100$ kpc and we integrate these profiles within elliptical isophotal
+    apertures at different physical radii. 
+    As explained in Paper~I, here we focus on the two following metric masses:
 
@@
 
-        \item stellar mass within 10 kpc (hereafter noted \minn{}) which we use as a proxy for the 
-            \textit{in situ} stellar component. This is motivated both by recent observations and simulations 
-            (e.g.~\citealt{vanDokkum2010}, \citealt{RodriguezGomez2016}). The value of 10 kpc that we quote here corresponds to the radius of the major axis of the isophotal ellipse (xxx check).
+        \item stellar mass within 10 kpc (hereafter noted \minn{}) which we use 
+            as a proxy for the stellar mass of the \textit{in situ} stellar 
+            component. 
+            This is motivated both by recent observations and simulations 
+            (e.g.~\citealt{vanDokkum2010}, \citealt{RodriguezGomez2016}). 
+            The value of 10 kpc that we quote here corresponds to the radius of the 
+            major axis of the isophotal ellipse.
+
         \item stellar mass within 100 kpc (hereafter noted \mtot{}). 
-We use \mtot{} as a proxy of the total stellar mass.
-In Paper I we showed that \mtot{} recovers more light compared to HSC \cmodel{} photometry with offsets that can be a large as 0.2 dex in magnitude.
+            We use \mtot{} as a proxy of the ``total'' stellar mass. 
+            In Paper~I we showed that \mtot{} recovers more light compared to 
+            HSC \cmodel{} photometry with offsets that can be a large as 0.2 dex 
+            in magnitude.
+
    \end{itemize}
 
-   We use these two simple metric masses to explore the 
-   \mstar{}-dependence of the fraction of accreted stars, and reveal to the diversity of 
-   stellar envelopes among massive galaxies.
-In practice, we also have the full profiles for each galaxy and can also cast our results in terms of the full stellar mass profiles.
-However, in many cases we find it more useful to display figures using the more simple \minn{} and \mtot{} quantities.
-In Figure \ref{fig:m100_m10_color}, we highlight the diversity of galaxies as a function of \minn{} and \mtot{}.
-Figure \ref{fig:m100_m10_color} shows a random subsample of massive galaxies with very similar \minn{} that have large
-   range of \mtot{}. 
-   We will use these two apertures masses to guide our comparisons of massive galaxies as a function of environments.
+   We use these two simple metric masses to explore the \mstar{}-dependence of the 
+   fraction of accreted stars, and reveal to the diversity of stellar envelopes among 
+   massive galaxies. 
+   In practice, we also have the full profiles for each galaxy and can also cast our 
+   results in terms of the full stellar mass profiles. 
+   However, in many cases we find it more useful to display figures using the more 
+   simple \minn{} and \mtot{} quantities. 
+   In Figure \ref{fig:m100_m10_color}, we highlight the diversity of galaxies as a 
+   function of \minn{} and \mtot{}. 
+   Figure \ref{fig:m100_m10_color} shows a random subsample of massive galaxies with 
+   very similar \minn{} that have large range of \mtot{}. 
+   We will use these two apertures masses to guide our comparisons of massive galaxies 
+   as a function of environments.
 
@@
     In this work, we focus on massive galaxies with \mtot{} $>10^{11.6}$~\msun{}. 
-    In Paper~I, we demonstrate that this sample is almost mass complete over our full redshift range.
-In addition to the mass cut above, we also limit our sample to galaxies that live at the centers of their own
-    dark matter haloes-- so-called ``central'' galaxies. We use the \redm{} \texttt{v5.10} \citep{Rykoff2014, Rozo2015b} cluster catalog to construct a central galaxy sample.
-
-    %Central galaxies are important to the study of galaxy-halo connection and follow stellar mass--halo mass relation (SHMR; e.g. \citealt{Leauthaud2012, 
+    In Paper~I, we demonstrate that this sample is almost mass complete over our full 
+    redshift range. 
+    In addition to the mass cut above, we also limit our sample to galaxies that live 
+    at the centers of their own dark matter haloes-- so-called ``central'' galaxies. 
+    We use the \redm{} \texttt{v5.10} \citep{Rykoff2014, Rozo2015b} cluster catalog 
+    to help us construct a central galaxy sample.
+
+    %Central galaxies are important to the study of galaxy-halo connection and follow 
+    %stellar mass--halo mass relation (SHMR; e.g. \citealt{Leauthaud2012, 
     %Behroozi2013, Kravtsov2014, Tinker2017}) at high-\mstar{}.
@@
     with $\lambda \geq 30$, $P_{\mathrm{Cen}} \geq 0.7$, and \logmtot{}$>11.5$ 
-    at $0.3 < z < 0.5$ (63/69 have \logmtot{}$>11.6$). 
+    at $0.3 < z < 0.5$ (63/68 have \logmtot{}$>11.6$). 
     This $\lambda$ limit is chosen to mitigate incompleteness in the cluster catalog
-    at the high end of our redshift window. The $P_{\mathrm{Cen}}$ limit is 
-    selected to exclude low probability central galaxy candidates. 
-    Based on the \mhalo{}-$\lambda$ relation calibrated by \citet{Simet2016}, these corresponds to central galaxies living in halos with \mhalo{}$>10^{14.2}$~\msun{}.
-This calibration is consistent with other works (e.g.
-\citealt{Saro2015, Farahi2016,
+    at the high end of our redshift window. 
+    The $P_{\mathrm{Cen}}$ limit is selected to exclude low probability candidate of 
+    central galaxy. 
+    Based on the \mhalo{}-$\lambda$ relation calibrated by \citet{Simet2016}, these 
+    correspond to central galaxies living in halos with \mhalo{}$>10^{14.2}$~\msun{}. 
+    This calibration is consistent with other works (e.g. \citealt{Saro2015, Farahi2016, 
     Melchior2016, Murata2017}). 
@@
     Then we estimate the $R_{\mathrm{200b}}$ of each cluster using the method in 
-    \citet{Diemer2015}. We further exclude all galaxies within a cylinder around each cluster, with a radius
-    equal to $R_{\mathrm{200b}}$ and a length equal to twice the value of the photometric 
-    redshift uncertainty of the cluster (typically around 0.015 to 0.025). This second sample will be dominated by central galaxies living in haloes with
-    $M_{\mathrm{200b}} < 10^{14}$~\msun{}, and will refer to this sample as \nbcg{}. There are  833 galaxies with  
-\logmtot{}$> 11.6$ in this sample.
+    \citet{Diemer2015}. 
+    We further exclude all galaxies within a cylinder around each cluster, with a radius
+    equal to $R_{\mathrm{200b}}$ and a length equal to twice the value of the 
+    photometric redshift uncertainty of the cluster (typically around 0.015 to 0.025).
+    This second sample will be dominated by central galaxies living in haloes with
+    $M_{\mathrm{200b}} < 10^{14}$~\msun{}, and will refer to this sample as \nbcg{}. \
+    There are 833 galaxies with \logmtot{}$> 11.6$ in this sample.
 
@@
     \minn{} for the \rbcg{} and \nbcg{} samples. 
-    We also compare these two samples on the \mtot{} - rest-frame $g-r$ color plane. 
-    Both of them follow the same ``red-sequence'' with only a handful of galaxies displaying bluer colors.
+    We also compare these two samples on the \mtot{}--rest frame $g-r$ color plane. 
+    Both of them follow the same ``red-sequence'' with only a handful of galaxies 
+    displaying bluer colors.
 
     We note that our method fails to extract 1-D profiles for $\sim10$\% of 
-    \rbcg{} and \nbcg{} galaxies due on-going major mergers or projection effects (e.g.\ nearby foreground galaxy or bright stars).
+    \rbcg{} and \nbcg{} galaxies due on-going major mergers or projection effects 
+    (e.g.\ nearby foreground galaxy or bright stars). 
     However, this small failure rate should not affect any of the results in this paper.

### 2017-07-26 draft/paper2_v3.tex
Edit result 1

@@
 
-    As shown in Figure~\ref{fig:m100_m10_color}, massive central galaxies at fixed  \minn{} display a large diversity in their stellar haloes.
-In Paper~1, we explored the \mstar{}-dependence of the stellar haloes in massive
-    galaxies, and concluded that the general trends are consistent with the 
-    predictions of the two-phase formation scenario.
-In this paper, we now investigate the relation between galaxy profiles, their stellar halos, and dark matter halo mass.
-Here we use \mtot{} as proxy for the ``total'' \mstar{}
-    of massive galaxies and we use \minn{} as a rough proxy for the mass of the 
-    \textit{in situ} component.  We remind the reader that although a circular aperture is shown on 
-    Fig~\ref{fig:m100_m10_color}, in practice we extract 1-D \mden{} profiles and estimate 
-    \mtot{} and \minn{} using elliptical apertures following the average fluxed-weighted isophotal shape.
-
-    % We said this already...
-    %Also,given the narrow \mstar
-    %{} and redshift range, we ignore \mstar{} growth 
-    %and structural evolution.
+    As shown in Figure~\ref{fig:m100_m10_color}, massive central galaxies at fixed  
+    \minn{} display a large diversity in their stellar haloes. 
+    In Paper~I, we explored the \mstar{}-dependence of the stellar haloes in massive 
+    galaxies, and concluded that the general trends are consistent with the predictions 
+    of the two-phase formation scenario. 
+    In this work, we now investigate the relation between the \mden{} profiles of 
+    massive galaxies, their stellar halos, and dark matter halo mass. 
+    Here we use \mtot{} as proxy for the ``total'' \mstar{} of massive galaxies and 
+    we use \minn{} as a rough proxy for the stellar mass of the \textit{in situ} 
+    component.  
+    We remind the reader that although a circular aperture is shown on 
+    Fig~\ref{fig:m100_m10_color}, in practice we extract 1-D \mden{} profiles and 
+    estimate \mtot{} and \minn{} using elliptical apertures following the average 
+    fluxed-weighted isophotal shape.
 
@@
 
-    First, we ask whether the \mden{} profiles of massive central galaxies depend on halo mass at fixed stellar mass.
-To ask this question, however, we must first define which stellar mass exactly is being fixed in the comparison.
-We will show results both when we fix \mtot{} as well as when we fix \minn{}.
-We also ensure that all comparisons are performed with a fixed underlying redshift distribution by mathcing samples in redshift in addition to stellar mass
-    (please see Appendix~\ref{app:match}, Appendix~\ref{app:redshift}, and Fig~\ref{fig:match} for details).
+    First, we ask whether the \mden{} profiles of massive central galaxies depend on 
+    halo mass at fixed stellar mass. 
+    To ask this question, however, we must first define which stellar mass exactly is 
+    being fixed in the comparison. 
+    We will show comparisons of \mden{} profiles at both fixed \mtot{} as well as fixed 
+    \minn{}. 
+    We also ensure that all comparisons are performed with fixed underlying redshift
+    distribution by matching samples in redshift in addition to stellar mass
+    (please see Appendix~\ref{app:match}, Appendix~\ref{app:redshift}, 
+    and Fig~\ref{fig:match} for details).
 
@@
 %% ------------------------------------------------------------------------------------ %%     
-    Fig~\ref{fig:prof_1} compares the \mden{} profiles of massive central galaxies living in low mass dark matter haloes to those living in high mass dark matter haloes at fixed \mtot{} 
-    (left panel) and at fixed \minn{} (right panel). This Figure shows the main result of this paper, namely that \textbf{the \mden{} profiles of 
-    massive central galaxies show a clear dependence on dark matter halo mass at both fixed \mtot{} and 
-    \minn{}.}
-
-    We perform several statistical tests to demonstrate that the differences we see in the median 
-    \mden{} profiles are significant.
-We also conduct a variety of tests that verify the robustness of these results with respect choices regarding \mtot{} bins, our $\lambda$ cut, the redshift range, and the choice of apertures used for the metric masses.
+    Fig~\ref{fig:prof_1} compares the \mden{} profiles of massive central galaxies 
+    living in less massive dark matter haloes (\logmh$<14.0$) to those living in more 
+    massive dark matter haloes (\logmh$>14.2$) at fixed \mtot{} (left panel) and at 
+    fixed \minn{} (right panel). 
+    This figure shows the main result of this paper, namely that 
+    \textbf{the \mden{} profiles of massive central galaxies show a clear dependence on 
+    dark matter halo mass at both fixed \mtot{} and \minn{}.}
+
+    We perform several statistical tests to demonstrate that the differences we see in 
+    the median \mden{} profiles are significant. 
+    We also conduct a variety of tests that verify the robustness of these results with
+    respect to the choices of \mtot{} bins, $\lambda$ cut, the redshift range, and the 
+    choice of apertures used for the metric masses. 
     Please see Appendix~\ref{app:robust} for further details.
@@
 
-        \item For the \mtot{} matched sample, although there is a clear and robust difference between the two median \mden{} profiles, the overall difference is subtle is mainly only apparent on $R>50$ kpc scales.
-This may explain why previous attempts to detect this signal using shallower images were not successful.
-        \item At fixed \mtot{}, central galaxies in high mass dark matter haloes display shallower \mden{} profiles compared to those living in low mass dark matter haloes (they have a flatter inner \mden{} profiles and more significant outer stellar haloes.
-        \item The median \mden{} profiles of the \rbcg{} and \nbcg{} samples cross each 
-            other at ${\sim} 15$-20 kpc, roughly also the scale of the effective radius $R_{\mathrm{e}}$.      
-        \item Finally, the differences between the two sets of profiles becomes more prominent at higher \mtot{}.
-This can be seen further dividing the sample into two \mtot{} bins (see Fig~\ref{fig:prof_2} and discussion in
-            Appendix~\ref{app:robust}) and when we discuss the relation between \mtot{} and 
-            \minn{} (see Fig~\ref{fig:scaling_relation}). This trend has potentially interesting implications \alexie{can we explain in one phrase?} that will be investigated in follow-up work. 
+        \item For the \mtot{} matched sample, although there is a clear and robust 
+            difference between the two median \mden{} profiles, the overall difference 
+            is subtle is mainly only apparent on $R>50$ kpc scales. 
+            The logarithmic scale of \mden{} on the Y-axis is partially responsible 
+            for the subtle differences we see here.  
+            In Appendix \ref{app:cog} and Figure~\ref{fig:cog}, we present the same
+            comparison using the curve--of--growth of \mstar{} and the fraction of 
+            \mtot{} enclosed in elliptical apertures with different radius. 
+            Both of the illustrate the same results from slightly different angles.
+
+        \item At fixed \mtot{}, central galaxies in more massive dark matter haloes 
+            display shallower \mden{} profiles compared to those living in low mass 
+            dark matter haloes (they have a flatter inner \mden{} profiles and 
+            more significant outer stellar haloes.
+
+        \item The median \mden{} profiles of the \rbcg{} and \nbcg{} samples cross 
+            each other at ${\sim} 15$-20 kpc, roughly the typical effective radius 
+            ($R_{\mathrm{e}}$) of massive galaxies with \logmtot{}$>11.7$--11.8.
+
+        \item Finally, the differences between the two sets of profiles becomes 
+            more prominent at higher \mtot{}. 
+            This can be seen further dividing the sample into two \mtot{} bins 
+            (see Fig~\ref{fig:prof_2} and discussion in Appendix~\ref{app:robust}) 
+            and when we discuss the relation between \mtot{} and 
+            \minn{} (see Fig~\ref{fig:scaling_relation}). 
+            This trend has potentially interesting implications
+
+            \alexie{can we explain in one phrase?} that will be investigated in follow-up work.
+
     \end{itemize}
 
+%This may explain why previous attempts to detect this signal using 
+            %shallower images were not successful. 
 \alexie{lets chat about the following two paragraphs}
@@
 %% ------------------------------------------------------------------------------------ %% 
+\begin{figure}
+    \centering
+    \includegraphics[width=\columnwidth]{fig/redbcg_prof_m100D}
+    \caption{
+        \textbf{Left:} comparison of \mstar{} estimated by the GAMA survey and 
+        the \mtot{} using HSC images in this work. 
+        We plot the \logmgama{} against the difference between \logmtot{} and \logmgama{}. 
+        The two vertical lines highlight the mass range $11.4 \leq$\logmgama{}$<11.8$ 
+        that is used for the comparison.
+        }
+    \label{fig:cog}
+\end{figure}
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
 \section{C. Match the \rbcg{} and \nbcg{} samples in \mstar{} and redshift distributions}
@@
 %% ------------------------------------------------------------------------------------ %% 
-\section{E. Comparison of \mden{} profiles using \mstar{} from the GAMA survey}
+\section{E. Stellar Mass Curve-of-Growth for Massive Central Galaxies} 
+	\label{app:cog}
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
+\section{F. Comparison of \mden{} profiles using \mstar{} from the GAMA survey}
     \label{app:gama}

### 2017-07-26 draft/paper2_v3.tex
Edit result 2

@@
             \minn{} (see Fig~\ref{fig:scaling_relation}). 
-            This trend has potentially interesting implications
-
-            \alexie{can we explain in one phrase?} that will be investigated in follow-up work.
+            This trend potentially indicates that the assembly of stellar haloes in 
+            more massive central galaxies become more sensitive to their 
+            environments or halo mass.
 
@@
             %shallower images were not successful.
-\alexie{lets chat about the following two paragraphs}
+
     Generally speaking, such subtle environmental dependence of \mden{} profiles in 
@@
 
-    The previous section showed that the \mden{} profiles of massive galaxies show a dependence on the dark matter mass of their host halos.
-In this section, we now turn our attention to the more commonly studied mass size relation  (\mstar{}--$R_{\mathrm{e}}$).
-In addition, we will also consider halo mass dependence in the \mtot{}--\minn{} plane.
+    The above section shows that the \mden{} profiles of massive galaxies show a 
+    dependence on the masses of their host dark matter haloes. 
+    In this section, we now turn our attention to the more commonly studied stellar 
+    mass--size relation (\mstar{}--$R_{\mathrm{e}}$). 
+    In addition, we will also consider halo mass dependence on the 
+    \mtot{}--\minn{} plane.
 
@@
     vdWel2014}) is one of the most important scaling relation for ETGs. 
-    Despite numerous attempts, previous studies have failed to detect the dark matter halo mass dependence of the \mstar{}--$R_{\mathrm{e}}$ relation at low-$z$ 
+    Despite numerous attempts, previous studies have failed to detect the 
+    \mhalo{}--dependence of the \mstar{}--$R_{\mathrm{e}}$ relation at low-$z$ 
     (e.g. \citealt{Weinmann2009, Nair2010, HCompany13, Cerbrian2014}; 
-    but see \citealt{Yoon2017}).
-
-    The previous section clearly showed that the profiles of massive galaxies depend on the masses of their host dark matter halos.
-We now ask whether or not this dependence is also manifest when considered in terms of the more traditionally studied \mstar{}--$R_{\mathrm{e}}$ relation.
-However, when considering the mass-size relation, there is ambiguity and multiple approaches in terms of defining "sizes".
-This is especially true in the context of massive galaxies with extended stellar haloes (a reason why we prefer to show profiles directly as in the previous section).
+    except for recent result by \citealt{Yoon2017}).
+
+    The previous section clearly showed that the \mden{} profiles of massive central 
+    galaxies depend on the masses of their host dark matter halos. 
+    We now ask whether or not this dependence is also manifest when considered in 
+    terms of the more traditionally studied \mstar{}--$R_{\mathrm{e}}$ relation. 
+    However, when considering the mass-size relation, there is ambiguity and there are
+    multiple approaches to define ``sizes''. 
+    This is especially relevant in the context of massive galaxies with extended 
+    stellar haloes (a reason why we prefer to show \mden{} profiles directly as in 
+    the previous section). 
     In this section, we still use \mtot{} as proxy of ``total'' \mstar{} and we adopt 
-    the radius enclosing 50\% of luminosity \alexie{mass?} within 100 kpc ($R_{\mathrm{50}}$; derived 
-    from the $i$-band curve-of-growth) as the ``size''. This definition of ``effective radius'' is more robust against structural details, 
-    choice of model, and the background subtraction \alexie{compared to what?}. 
-    Massive galaxies from this sample are large enough that the impact of seeing is not a concern.
+    the radius enclosing 50\% of stellar mass within 100 kpc ($R_{\mathrm{50}}$; 
+    derived from the $i$-band curve-of-growth) as the ``size''. 
+    This definition of ``effective radius'' is more robust against structural details, 
+    choice of model, and the background subtraction comparing to the effective radius 
+    estimated by simple 2-D modeling method (e.g. single-\ser{} model). 
+    Massive galaxies from this sample are large enough that the impact of seeing is 
+    not a concern.
 
@@
 %% ------------------------------------------------------------------------------------ %% 
+\section{Basic Statistical Properties of the Sample} 
+	\label{app:basic}
+
+%% ------------------------------------------------------------------------------------ %% 
   \begin{figure}
@@
 
-%% ------------------------------------------------------------------------------------ %% 
-\section{A. Basic Statistical Properties of the Sample} 
-	\label{app:basic}
-
     On the top-left panel of Fig~\ref{fig:sample_stats}, we show the \mtot{}-color 
@@
 %% ------------------------------------------------------------------------------------ %% 
+\section{Comparisons of \mden{} profiles in different redshift bins}
+    \label{app:redshift}
+
+%% ------------------------------------------------------------------------------------ %% 
 \begin{figure}
@@
 %% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %% 
-\section{B. Comparisons of \mden{} profiles in different redshift bins}
-    \label{app:redshift}
 
@@
 %% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
+\section{Match the \rbcg{} and \nbcg{} samples in \mstar{} and redshift distributions}
+    \label{app:match}
 
@@
 
+    As explained earlier, it is important to make sure the two samples have similar 
+    distributions in both \mstar{} and redshift before comparing their median \mden{} 
+    profiles.  
+    Here we briefly describe the procedure used in this work. 
+    Since the \rbcg{} sample is smaller in size, we always match the \nbcg{} sample to 
+    it by searching for the $N$-nearest neighbours on the $M_{\star}$-redshift plane 
+    using the KDTree algorithm in the \texttt{scikit-learn} Python library 
+    (\citealt{scikit-learn}), and evaluate the quality of the match using the 
+    distributions of both parameters (as shown in Fig~\ref{fig:match}).
+
+    As we only keep the unique \nbcg{} galaxies in the matched sample, we manually 
+    adjust the value of $N$ to achieve the best match. 
+    When the redshift distribution of the \rbcg{} sample becomes bi-model, we also try 
+    to split the sample into two redshift bins and match them separately. 
+    Typically $N$ is between 3 to 8.
+    In Fig~\ref{fig:match}, we demonstrate this procedure using the results for 
+    the \mtot{}-matched (Left) and the \minn{}-matched samples in Fig~\ref{fig:prof_1}
+    (Right), and the two samples are well matched in the distributions of \mtot{}
+    (or \minn{}) and redshift.  
+    For all the comparisons of \mden{} profiles in this work, we match the samples 
+    in the same way, and make sure the match has the same quality. 
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
+\section{Robustness of the \mden{} Differences} 
+	\label{app:robust}
+
 %% ------------------------------------------------------------------------------------ %% 
@@
 
+    In Fig~\ref{fig:prof_1}, we compare the \mden{} profiles of \mtot{}- and 
+    \minn{}-matched samples of \rbcg{} and \nbcg{} galaxies, and here we test the 
+    robustness of the results using a few extra tests that are illustrated in
+    Fig~\ref{fig:prof_2}, Fig~\ref{fig:prof_3}, and Fig~\ref{fig:prof_4}, and 
+    are briefly described here:
+
+    \begin{enumerate}
+
+        \item In Fig~\ref{fig:prof_2}, we group the samples into two \mtot{} bins. 
+            Given the small sample size, we extend slightly toward lower \mtot{} range 
+            ($11.5 \leq \log (M_{\star,\ 10\mathrm{kpc}}/M_{\odot}) < 11.7$ and 
+             $11.7 \leq \log (M_{\star,\ 10\mathrm{kpc}}/M_{\odot}) < 11.9$). 
+            Although the smaller sample leads to larger statistical uncertainties, 
+            we can still see similar structural differences in both \mtot{} bins, 
+            and the difference becomes more significant in the higher \mtot{} bin.  
+            For the lower \mtot{} bin, the difference in the inner region becomes 
+            quite uncertain, while the difference in the outskirt is still visible. 
+            This potentially suggests that the environmental dependence of structure 
+            also varies with \mstar{}, an important implication deserves more 
+            investigations in the future.
+
+        \item On the left panel of Fig~\ref{fig:prof_3}, we match the \rbcg{} and 
+            \nbcg{} samples in a lower redshift bins ($0.30 < z < 0.42$).
+            Despite the larger uncertainties due to smaller samples, we find the 
+            results are the same.
+
+        \item On the middle panel of Fig~\ref{fig:prof_3}, we includes \rbcg{} 
+            galaxies in poorer clusters ($20 < \lambda < 30$), which should result 
+            in overlapped \mhalo{} distributions with the \nbcg{} samples 
+            considering the typical uncertainty of $\lambda$.
+            This makes the difference in the inner region slightly less significant, 
+            but the overall results are the same.
+
+        \item On the right panel of Fig~\ref{fig:prof_3}, in stead of using \mtot{}, 
+            we use the \mmax{}--the maximum \mstar{} by integrating the \mden{} 
+            profiles to the largest radius allowed.  
+            The \mmax{} values are less reliable than \mtot{} due to the 
+            uncertainty of background subtraction and contamination from nearby 
+            bright objects, but they can serve as different estimates of the ``total''
+            \mstar{} of these galaxies.
+            As shown in Section~\ref{sec:discussion}, they on average increase
+            the \mstar{} by a little bit and affect the \rbcg{} more.
+            The differences in the \mden{} profiles still remain very similar.
+
+    \end{enumerate}
+
+    We also test the robustness of the \mtot{}-matched results using the samples with 
+    only spectroscopic redshift, the samples in the three GAMA fields, and the \rbcg{} 
+    samples without the ones in very massive haloes ($\lambda > 40$).  
+    Limited by space, we do not show these results here, but they all verify the 
+    robustness of the results.
+
+    For the results from the \minn{}-matched samples:
+
+    \begin{enumerate}
+
+        \item
+            We match the two samples using both \minn{} and the \mstar{} within 15 kpc 
+            at the same time.  
+            This makes the two median \mden{} profiles very similar inside 10-15 
+            kpc, while the result in the outskirt remains the same (left panel of 
+            Fig~\ref{fig:prof_4}).
+            Use \mstar{} within 5 or 20 kpc leads to the same conclusion.
+
+        \item 
+            To make sure the two samples are comparable in their overall assembly history,
+            we also try to only include the very massive galaxies (\logmtot{}$>11.5$)
+            in both samples. 
+            This excludes the \nbcg{} galaxies that are much less massive and 
+            more ``compact'' in structure. 
+            Yet, the results regarding the structural differences remain the same.
+
+    \end{enumerate}
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
+\section{Stellar Mass Curve-of-Growth for Massive Central Galaxies} 
+	\label{app:cog}
+%% ------------------------------------------------------------------------------------ %%
+
 %% ------------------------------------------------------------------------------------ %% 
@@
 %% ------------------------------------------------------------------------------------ %% 
+\section{Comparison of \mden{} profiles using \mstar{} from the GAMA survey}
+    \label{app:gama}
+
+%% ------------------------------------------------------------------------------------ %% 
 \begin{figure}
@@
 
-%% ------------------------------------------------------------------------------------ %% 
-\section{C. Match the \rbcg{} and \nbcg{} samples in \mstar{} and redshift distributions}
-    \label{app:match}
-
-    As explained earlier, it is important to make sure the two samples have similar 
-    distributions in both \mstar{} and redshift before comparing their median \mden{} 
-    profiles.  
-    Here we briefly describe the procedure used in this work. 
-    Since the \rbcg{} sample is smaller in size, we always match the \nbcg{} sample to 
-    it by searching for the $N$-nearest neighbours on the $M_{\star}$-redshift plane 
-    using the KDTree algorithm in the \texttt{scikit-learn} Python library 
-    (\citealt{scikit-learn}), and evaluate the quality of the match using the 
-    distributions of both parameters (as shown in Fig~\ref{fig:match}).
-
-    As we only keep the unique \nbcg{} galaxies in the matched sample, we manually 
-    adjust the value of $N$ to achieve the best match. 
-    When the redshift distribution of the \rbcg{} sample becomes bi-model, we also try 
-    to split the sample into two redshift bins and match them separately. 
-    Typically $N$ is between 3 to 8.
-    In Fig~\ref{fig:match}, we demonstrate this procedure using the results for 
-    the \mtot{}-matched (Left) and the \minn{}-matched samples in Fig~\ref{fig:prof_1}
-    (Right), and the two samples are well matched in the distributions of \mtot{}
-    (or \minn{}) and redshift.  
-    For all the comparisons of \mden{} profiles in this work, we match the samples 
-    in the same way, and make sure the match has the same quality. 
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %% 
-\section{D. Robustness of the \mden{} Differences} 
-	\label{app:robust}
-
-    In Fig~\ref{fig:prof_1}, we compare the \mden{} profiles of \mtot{}- and 
-    \minn{}-matched samples of \rbcg{} and \nbcg{} galaxies, and here we test the 
-    robustness of the results using a few extra tests that are illustrated in
-    Fig~\ref{fig:prof_2}, Fig~\ref{fig:prof_3}, and Fig~\ref{fig:prof_4}, and 
-    are briefly described here:
-
-    \begin{enumerate}
-
-        \item In Fig~\ref{fig:prof_2}, we group the samples into two \mtot{} bins. 
-            Given the small sample size, we extend slightly toward lower \mtot{} range 
-            ($11.5 \leq \log (M_{\star,\ 10\mathrm{kpc}}/M_{\odot}) < 11.7$ and 
-             $11.7 \leq \log (M_{\star,\ 10\mathrm{kpc}}/M_{\odot}) < 11.9$). 
-            Although the smaller sample leads to larger statistical uncertainties, 
-            we can still see similar structural differences in both \mtot{} bins, 
-            and the difference becomes more significant in the higher \mtot{} bin.  
-            For the lower \mtot{} bin, the difference in the inner region becomes 
-            quite uncertain, while the difference in the outskirt is still visible. 
-            This potentially suggests that the environmental dependence of structure 
-            also varies with \mstar{}, an important implication deserves more 
-            investigations in the future.
-
-        \item On the left panel of Fig~\ref{fig:prof_3}, we match the \rbcg{} and 
-            \nbcg{} samples in a lower redshift bins ($0.30 < z < 0.42$).
-            Despite the larger uncertainties due to smaller samples, we find the 
-            results are the same.
-
-        \item On the middle panel of Fig~\ref{fig:prof_3}, we includes \rbcg{} 
-            galaxies in poorer clusters ($20 < \lambda < 30$), which should result 
-            in overlapped \mhalo{} distributions with the \nbcg{} samples 
-            considering the typical uncertainty of $\lambda$.
-            This makes the difference in the inner region slightly less significant, 
-            but the overall results are the same.
-
-        \item On the right panel of Fig~\ref{fig:prof_3}, in stead of using \mtot{}, 
-            we use the \mmax{}--the maximum \mstar{} by integrating the \mden{} 
-            profiles to the largest radius allowed.  
-            The \mmax{} values are less reliable than \mtot{} due to the 
-            uncertainty of background subtraction and contamination from nearby 
-            bright objects, but they can serve as different estimates of the ``total''
-            \mstar{} of these galaxies.
-            As shown in Section~\ref{sec:discussion}, they on average increase
-            the \mstar{} by a little bit and affect the \rbcg{} more.
-            The differences in the \mden{} profiles still remain very similar.
-
-    \end{enumerate}
-
-    We also test the robustness of the \mtot{}-matched results using the samples with 
-    only spectroscopic redshift, the samples in the three GAMA fields, and the \rbcg{} 
-    samples without the ones in very massive haloes ($\lambda > 40$).  
-    Limited by space, we do not show these results here, but they all verify the 
-    robustness of the results.
-
-    For the results from the \minn{}-matched samples:
-
-    \begin{enumerate}
-
-        \item
-            We match the two samples using both \minn{} and the \mstar{} within 15 kpc 
-            at the same time.  
-            This makes the two median \mden{} profiles very similar inside 10-15 
-            kpc, while the result in the outskirt remains the same (left panel of 
-            Fig~\ref{fig:prof_4}).
-            Use \mstar{} within 5 or 20 kpc leads to the same conclusion.
-
-        \item 
-            To make sure the two samples are comparable in their overall assembly history,
-            we also try to only include the very massive galaxies (\logmtot{}$>11.5$)
-            in both samples. 
-            This excludes the \nbcg{} galaxies that are much less massive and 
-            more ``compact'' in structure. 
-            Yet, the results regarding the structural differences remain the same.
-
-    \end{enumerate}
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %% 
-\section{E. Stellar Mass Curve-of-Growth for Massive Central Galaxies} 
-	\label{app:cog}
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %% 
-\section{F. Comparison of \mden{} profiles using \mstar{} from the GAMA survey}
-    \label{app:gama}
-
     The GAMA survey greatly overlaps with the HSC survey, and it provides carefully 

### 2017-07-26 draft/paper2_v3.tex
Edit result 3

@@
 
-    The left panel of Fig~\ref{fig:scaling_relation} shows the \mtot{}--$R_{\mathrm{50}}$
-    relations for galaxies in high and low mass dark matter halos.
-We fit the \logmtot{}-$\log (R_{\mathrm{50}}/\mathrm{kpc})$ relations at $\log(M_{\star,100})>11.6$ using the \texttt{emcee} MCMC sampler (\citealt{Emcee})\footnote{The initial guesses are based on maximum
+    The left panel of Fig~\ref{fig:scaling_relation} shows the 
+    \mtot{}--$R_{\mathrm{50}}$ relations for galaxies in more and less massive
+    dark matter halos. 
+    We fit the \logmtot{}-$\log (R_{\mathrm{50}}/\mathrm{kpc})$ relations at 
+    $\log(M_{\star,100})>11.6$ using the \texttt{emcee} MCMC sampler 
+    (\citealt{Emcee})\footnote{The initial guesses are based on maximum 
     likelihood estimates, and we assume flat priors for parameters.}.
@@
 
-    \noindent As shown in the left panel of Fig~\ref{fig:scaling_relation}, galaxies in low and high mass haloes live on \mtot{}--$R_{\mathrm{50}}$ relations that have similar slopes but different normalizations.
-This result is robust against the ranges of \mstar{} over which the fit is performed and against the definitions
-    of  ``total'' \mstar{} and half-light radius\footnote{Using \mstar{} within 120 or 
-    150 kpc, or using the $R_{\mathrm{50}}$ derived within these apertures does not 
-    change the results.}.
+    \noindent As shown in the left panel of Fig~\ref{fig:scaling_relation}, galaxies 
+    in more and less massive dark matter haloes lie on \mtot{}--$R_{\mathrm{50}}$ 
+    relations that have similar slopes but different normalizations. 
+    This result is robust against the ranges of \mstar{} over which the fit is performed 
+    and against the definitions of  ``total'' \mstar{} and half-light 
+    radius\footnote{Using \mstar{} within 120 or 150 kpc, or using the 
+    $R_{\mathrm{50}}$ derived within these apertures do not change the results.}.
 
@@
     $12.5 \le$ \logmh{} $< 15$ haloes. 
-    HC13 use the group catalog by \citet{Yang2007} to estimate halo mass. They obtain effective radii from  single-\ser{} model fitting to SDSS 
+    HC13 use the group catalog by \citet{Yang2007} to estimate halo mass. 
+    They obtain effective radii from single-\ser{} model fitting to SDSS 
     images and \mstar{} based on SED fitting using the BC03 (\citealt{BC03}) 
-    synthetic population model. We convert their \mstar{} estimates from a Kroupa IMF to a Chabrier 
+    synthetic population model. 
+    We convert their \mstar{} estimates from a Kroupa IMF to a Chabrier 
     IMF by applying a constant -0.05 dex shift (see \citealt{Bernardi2016a}). 
-We further add $+0.1$dex to the HSC13 stellar masses to account for a systematic offset between BC03 and our FSPS model (see Paper~1).
+    We further add $+0.1$dex to the HSC13 stellar masses to account for a systematic 
+    offset between BC03 and our FSPS model (see Paper~1). 
     The distributions of galaxies on the 
@@
     (with slightly shallower slopes), even at \logmtot{}$< 11.6$ where our samples 
-    start to become incomplete. 
+    start to become incomplete in stellar mass. 
     In contrast to the present study, HC13 finds no environment dependence in the 
     mass--size relation for central galaxies in the range $12.5\le$ \logmh{} $<15.0$.     
-However, HC13 use SDSS which is considerably shallower compared the HSC and hence will not be as sensitive to the outer portions of the profile where we see the largest differences.
-A more detailed comparison is beyond the scope of this work, but we briefly \alexie{we demsontrate what exactly?
-chat about this test}
-    demonstrate this using the \rbcg{} and \nbcg{} galaxies that overlap with the GAMA
-    survey (please see Appendix~\ref{app:gama} for details).
-
-    We matched the two samples using the \mstar{} measured using single-\ser{} 2-D
-    model by the GAMA team (\citealt{Kelvin2012}). 
-    At fixed \mgama{}, the \rbcg{} galaxies display much more significant stellar 
-    halo despite they have very similar inner \mden{} profiles.  
+    However, HC13 use SDSS images that are considerably shallower compared to the HSC 
+    ones and hence will not be as sensitive to the outer portions of the \mden{} 
+    profile where we see the most clear differences. 
+    A more detailed comparison is beyond the scope of this work, but in 
+    Appendix~\ref{app:gama}, we use the \rbcg{} and \nbcg{} galaxies that overlap 
+    with the GAMA survey to briefly demonstrate this point. 
+    We show that, for galaxies with similar \mstar{} derived from single-\ser{} 
+    models using shallower SDSS images (\citealt{Kelvin2012}), the ones in more 
+    massive dark matter halos actually show more prominent outer stellar halos, 
+    hence both of their stellar mass and effective radius are underestimated.  
     This shows again that the deeper HSC images has unique advantage in studying the
@@
 
-    Now we investigate the relationship \mtot{}, \minn{}, and halo mass.
-Compared to the mass--size relation, the \mtot{}--\minn{} relation is not plagued by the ambiguity of galaxy ``size'', and also enables a more straightforward comparison with numerical simulations.
+    Now we investigate the relationship among \mtot{}, \minn{}, and \mhalo{}. 
+    Compared to the mass--size relation, the \mtot{}--\minn{} relation is not plagued 
+    by the ambiguity of galaxy ``size'', and also enables a more straightforward 
+    comparison with numerical simulations.
 
     The right panel of Fig \ref{fig:scaling_relation} compares \rbcg{} and \nbcg{}
-    galaxies on the \mtot{}--\minn{} plane. We find that these two samples are offset when considered in this plane a follow distinct best-fit \mtot{}--\minn{} relations. 
+    galaxies on the \mtot{}--\minn{} plane. 
+    We find that there is an offset between the overall distributions of these two
+    samples and they follow distinct best-fit \mtot{}--\minn{} relations. 
     For \rbcg{} galaxies with \logmtot{}$>11.6$ we find:
@@
 
-    These results are robust against the exact choice for the \mtot{} range over which the fit is performed.
-These results are also unchanged if \minn{} is replaced by mass within a 5 or a 15 kpc aperture, or if \mtot{} is replaced with mass within a 120 or a 150 kpc aperture.
+    These results are robust against the exact choice for the \mtot{} range over which 
+    the fit is performed. 
+    These results also will not be altered when we replace the \minn{} with the stellar 
+    mass within a 5 or a 15 kpc aperture, or if \mtot{} is replaced with stellar mass 
+    within a 120 or a 150 kpc aperture.
 
@@
 
-    From Figure \ref{fig:scaling_relation} we can draw the same conclusions as in the previous section, namely that: at fixed \mtot{}, central galaxies in more massive haloes tend to have less galaxy mass in the inner regions but display more prominent outer envelopes.
-The scientific implication of this result is discussed in
+    From Figure \ref{fig:scaling_relation} we can draw the same conclusions as in 
+    the previous section, namely that: 
+    at fixed \mtot{}, central galaxies in more massive haloes tend to have smaller 
+    fraction of stellar mass in their inner regions and higher \mstar{} in their outer
+    stellar haloes. 
+    Although the HSC images can not resolve the central region of these massive 
+    galaxies, the on average lower \mstar{} within 10 kpc and shallower inner \mden{} 
+    profile for massive central galaxies living in more massive haloes are robust 
+    results and could have interesting physical implications.
+    Meanwhile, at fixed \minn{}--a proxy for the \mstar{} of the ``in situ'' component,
+    central galaxies in more massive haloes tend to be more massive and display more 
+    prominent stellar haloes. 
+    The scientific implication of these results will be discussed in 
     Section~\ref{sec:discussion}.
 
-\alexie{This seems too detailed. This also belongs in the discusison section}
-
-    Meanwhile, we find \rbcg{} galaxy tends to have lower \mstar{} within 10--15 kpc 
-    and shallower inner \mden{} profile than the \nbcg{} one at fixed \mtot{}. 
-    Although the HSC can not resolve the central region of these massive galaxies, 
-    such difference could have interesting physical implications. 
+    \todo{Move to discussion}
     Observations of compact quiescent galaxies at high-$z$ tend to suggest higher 
@@
 
-    In Paper~1, we show that the ellipticity of the outer stellar halo increases with \mtot{}, while in contrast, rest--frame color gradients do not display any strong \mtot{}-dependencies.
-In this paper, we take this analysis one step further to investigate whether or not either of these quantities display a halo mass dependency.
-We focus on ellipticity and color profiles within 5--60 kpc where we can ignore differences in sky subtraction and seeing across different bands.
-Galactic extinction and $k$-corrections are applied to both $(g-r)$ and $(g-i)$ color profiles.
-
-    Figure \ref{fig:ell_color} shows the average ellipticity, $g-r$, and $g-i$ color profiles for galaxies living in low and high mass haloes both at fixed \mtot{} and at fixed \minn{}.
-We also compared our results with previous studies that stacked SDSS images (e.g.
-\citealt{LaBarbera2010, Tal2011, DSouza2014}).
+    In Paper~I, we show that the ellipticity of the outer stellar halo increases with
+    \mtot{}, while in contrast, rest--frame color gradients do not display strong 
+    \mtot{}-dependencies. 
+    In this paper, we take this analysis one step further to investigate whether or 
+    not either of these quantities display a halo mass dependency. 
+    We focus on ellipticity and color profiles within 5--60 kpc where we can ignore
+    differences in sky subtraction and seeing across different filters. 
+    Galactic extinction and $k$-corrections are applied to both $(g-r)$ and $(g-i)$ 
+    color profiles.
+
+    Figure \ref{fig:ell_color} shows the average ellipticity, $g-r$, and $g-i$ color 
+    profiles for galaxies living in more and less massive dark matter haloes both at 
+    fixed \mtot{} and at fixed \minn{}. 
+    We also compared our results with previous studies that are based on stacked SDSS 
+    images (e.g. \citealt{LaBarbera2010, Tal2011, DSouza2014}). 
     Figure \ref{fig:ell_color} shows that:
@@
     \begin{itemize}
-        \item \alexie{discuss here}. Galaxies in low and high mass haloes display similar ellipticity profiles at fixed \mtot{}. There is hint that suggests the central galaxies from more massive 
+        \item \alexie{discuss here}. Massive central galaxies living in more and 
+            less massive haloes display similar ellipticity profiles at fixed \mtot{}. 
+            There is hint that suggests the central galaxies from more massive 
             haloes become slightly more elongated at $R>50$ kpc than the ones 
             in less massive haloes with similar \mtot{}. 
-            However, the uncertainties in the current profiles make it not 
-            conclusive.              
+            However, the uncertainties in the current ellipticity profiles make it 
+            not conclusive.
+
         \item For the \minn{}-matched samples, the \rbcg{} galaxies show higher
             average ellipticity than the \nbcg{} ones at $R > 10$ kpc. 
-            The average ellipticities in the inner region are very similar. 
+            On the other hand, the average ellipticity in the inner region are very 
+            similar. 
             This further suggests that the more elongated outer stellar haloes 
-            of massive haloes relate to the accreted stars.         
-        \item Galaxies in low and high mass dark matter haloes display similar rest--frame color gradients (at $r<60$ kpc) at fixed \mtot{} and at fixed  \minn{}.    
+            of massive haloes may relate to the accreted stars.
+
+        \item Massive central galaxies in more and less massive dark matter haloes 
+            display similar rest--frame color gradients (at $r<60$ kpc) at fixed 
+            \mtot{} and at fixed  \minn{}.
+
     \end{itemize}
 
-    Besides these conclusions, the fact that we find  smooth ellipticity profile and its shallow gradient supports 
-            the idea of using the flux-weighted average isophotal shape to 
-            extract 1-D profiles of massive galaxies.
-
-     The similarity of average rest-frame color profiles between the 
-            \rbcg{} and \nbcg{} samples suggests that \mden{} profiles based on 
-            single average \m2l{} will not bias our comparisons.
+    Besides these conclusions, the fact that we find smooth ellipticity profile and 
+    its shallow gradient favors the idea of using the flux-weighted average isophotal 
+    shape to extract 1-D \mden{} profiles of massive galaxies. 
+    The similarity of average rest-frame color profiles between the \rbcg{} and \nbcg{}
+    samples suggests that \mden{} profiles based on single average \m2l{} will not bias 
+    our comparisons.
 

### 2017-07-26 draft/paper2_v3.tex
Edit result 4

@@
             difference between the two median \mden{} profiles, the overall difference 
-            is subtle is mainly only apparent on $R>50$ kpc scales. 
-            The logarithmic scale of \mden{} on the Y-axis is partially responsible 
-            for the subtle differences we see here.  
-            In Appendix \ref{app:cog} and Figure~\ref{fig:cog}, we present the same
-            comparison using the curve--of--growth of \mstar{} and the fraction of 
-            \mtot{} enclosed in elliptical apertures with different radius. 
-            Both of the illustrate the same results from slightly different angles.
+            is quite subtle, especially in the inner region. 
+            The difference becomes more apparent at $R>50$ kpc scales.
 
@@
 
-%This may explain why previous attempts to detect this signal using 
-            %shallower images were not successful.
-
-    Generally speaking, such subtle environmental dependence of \mden{} profiles in 
-    the \mtot{}-matched samples suggests that environment does not play a major role 
-    in shaping massive galaxies \textbf{at fixed ``total'' stellar mass}.
-    Therefore it is interesting to ask, for massive galaxies that \textbf{contain 
-    similar \mstar{} in the \textit{in situ} component}, how does environment affect 
-    their subsequent mass assembly?
-    Assuming \minn{} is reasonable tracer of the \textit{in situ} mass, we compare the 
-    \mden{} profiles of \minn{}-matched samples (right panel of Fig~\ref{fig:prof_1}).  
+    The logarithmic scale of \mden{} on the Y-axis is partially responsible for the 
+    subtle differences we see in the fixed \mtot{} comparison.  
+    In Appendix \ref{app:cog} and Figure~\ref{fig:cog}, we present the same 
+    comparison using the curve--of--growth of \mstar{} and the fraction of \mtot{} 
+    enclosed in elliptical apertures with different radius. 
+    Both of the illustrate the same results from slightly different angles. 
+    They also both suggest that, at fixed \mtot{}, the environmental dependence of 
+    \mden{} profiles is indeed quite subtle. 
+    This may explain why previous attempts to detect such dependence using shallower 
+    images often failed. 
+    More importantly, this result also suggests that halo mass does not play the 
+    central role in shaping massive central galaxies \textbf{at fixed ``total'' 
+    stellar mass}.
+
+    It is therefore interesting to see the comparison of \mden{} profiles at fixed 
+    \minn{}--a reasonable tracer for the stellar mass in the \textit{in situ}
+    component (right panel of Fig~\ref{fig:prof_1}).  
     Although the median \mden{} profiles are very similar at $R \leq 10$ kpc, the
@@
     stellar halo. 
-
-    Meanwhile, the uniform slope of the \mden{} profile within 10 kpc is in sharp 
-    contrast with the large \textit{intrinsic} scatter in the outskirts. 
-    It hints that these two regions are shaped by distinctive processes, and may 
-    explain why they depend on environment at different levels.  
+    Also, the similar slopes of the \mden{} profiles within 10 kpc are in sharp 
+    contrast with the large \textit{intrinsic} scatter we see in the outer \mden{} 
+    profiles. 
+    This hints that these two regions could be shaped by distinctive physical 
+    processes, and may explain why they depend on halo mass differently.  
     In simulations, intensive dissipative process helps create 
@@
     of more massive halo (e.g. \citealt{Pillepich2014}). 
-    The scatter of halo assembly process at fixed halo mass and the stochastic 
+    The scatter of halo assembly histories at fixed halo mass and the stochastic 
     nature of the galaxy--galaxy mergers also explain the large \textit{intrinsic} 
@@
 
-    \todo{Move to discussion}
-    Observations of compact quiescent galaxies at high-$z$ tend to suggest higher 
-    \mden{} in the central region than their descendants, hence it is necessary to 
-    have certain process to reduce the central \mden{} (e.g. strong adiabatic expansion 
-    induced by powerful AGN feedback; \citealt{Fan2008}) to match the inner \mden{} 
-    profiles of massive central galaxies at low-$z$.
-    Coalesce of super-massive black hoes (SMBHs) at the end of major merger, which is 
-    common in the assembly history of massive galaxies, can also flatten the central 
-    \mden{} profile via efficient scattering effect (e.g. \citealt{Milosavljevi2002}).
-    On the right side of Fig \ref{fig:scaling_relation}, we find a few \rbcg{} galaxies 
-    with very low \minn{} at high \mtot{} end that are apparently not bothered by 
-    problematic photometry or exceptionally bad seeing.  
-    They may be similar to the recently discovered massive BCGs with very large core 
-    (a few kpc; e.g. \citealt{Postman2012, LopezCruz2014}) resulting from SMBH mergers.
-    The impacts of these processes, and their dependence on \mhalo{} is an interesting 
-    topic to investigate in the future.
 %% ------------------------------------------------------------------------------------ %%
@@
     Results presented here are broadly consistent with the ``two-phase'' formation
-    scenario of massive central galaxies in a hierarchical universe. 
+    scenario for massive central galaxies in a hierarchical universe. 
     Under this picture, intense dissipative processes at $z > 2$ are responsible for 
     the formation of the \textit{in situ} stars in massive central galaxies. 
-    After the star formation was quenched, the more gradual second phase of evolution
-    is dominated by non-dissipative mergers of satellite galaxies. 
-    Since dry minor mergers can effectively deposit \textit{ex situ} stars on to the 
-    outskirts of these massive galaxies (e.g. \citealt{Oogi2013, Bedorf2013}), 
+    After the star formation was quenched, a more gradual second phase is dominated 
+    by non-dissipative mergers of satellite galaxies. 
+    Since dry minor mergers can effectively deposit \textit{ex situ} stars in the 
+    outskirts of massive galaxies (e.g. \citealt{Oogi2013, Bedorf2013}), 
     it is expected that the stellar mass distributions of massive galaxies 
@@
     the number of minor mergers strongly depend on the assumed dynamical friction time. 
-    If short dynamical friction time is favored (e.g. \citealt{Newman2012}), 
+    When short dynamical friction time is favored (e.g. \citealt{Newman2012}), 
     centrals of more massive haloes can have up to four times more minor mergers 
@@
     These extra minor mergers alone can lead to moderate halo mass dependence of 
-    size. 
+    galaxy size. 
     Similarly, \citet{Yoon2017} confirms these theoretical predictions using 
@@
     plane suggest that, at fixed \mtot{}, centrals of more massive haloes have 
-    slightly shallower inner \mden{} slope and lower \mtot{}.  
+    slightly shallower inner \mden{} slope and lower fraction of \mtot{} within the 
+    inner 10 kpc.
     Minor mergers can not explain such difference as they should not alter the inner 
@@
     \mden{} profiles, integration out to larger aperture will make the differences 
-    between \rbcg{} and \nbcg{} galaxies on the \mtot{}--\minn{} plane more significant. 
-    The fact that, at fixed \mtot{}, the overall stellar mass distributions of massive
-    central galaxies relate to halo mass may hint us more insights about the connection 
-    between the assembly of massive haloes and their central galaxies, and it is worth 
-    further investigation.
+    between \rbcg{} and \nbcg{} galaxies on the \mtot{}--\minn{} plane more 
+    significant.
+
+    Observations of compact quiescent galaxies at high-$z$ seem to indicate higher 
+    \mden{} in their central regions than their descendants. 
+    Therefore it is necessary to rely on certain processes to reduce the central 
+    \mden{} (e.g. strong adiabatic expansion induced by powerful AGN feedback; 
+    \citealt{Fan2008}) to match the inner \mden{} profiles of massive central galaxies 
+    at lower redshift.
+    Coalesce of super-massive black hoes (SMBHs) at the end of major merger, which 
+    is common in the assembly history of massive galaxies, can also flatten the 
+    central \mden{} profile via efficient scattering effect 
+    (e.g. \citealt{Milosavljevi2002}).
+    On the right side of Fig \ref{fig:scaling_relation}, we find a few \rbcg{} 
+    galaxies with very low \minn{} at high \mtot{} end that are apparently not bothered 
+    by problematic photometry or exceptionally bad seeing.  
+    They may be similar to the recently discovered massive BCGs with very large 
+    depleted cores (a few kpc; e.g. \citealt{Postman2012, LopezCruz2014, Thomas2016,
+    Bonfini2016}) resulting from SMBH mergers.
+    The impacts of these processes, and their dependence on \mhalo{} is an interesting 
+    topic to investigate in the future.
 
@@
     \centering 
-    \includegraphics[width=16cm]{fig/redbcg_match}
+    \includegraphics[width=15.0cm]{fig/redbcg_match}
     \caption{
@@
 	\label{app:cog}
+
+	In \S \ref{ssec:sbp_mtot} and Figure \ref{fig:prof_1}, we show the comparisons 
+	of \mden{} profiles for massive central galaxies from the \rbcg{} and \nbcg{} 
+	samples. 
+	Although the differences in their median \mden{} profiles we revealed are robust 
+	and systematic, they appear to be very subtle, especially in the inner region. 
+	This is partly due to the logarithmic scale on the Y--axis for \mden{} profiles.
+
+	In Figure \ref{fig:cog}, we compare the same two samples after converting the 
+	\mden{} profiles into:
+
+	\begin{enumerate}
+
+	    \item ``Curve--of--growth'' of stellar mass--the cumulative \logms{} profiles
+	        (upper panel).
+
+	    \item Fraction of \mtot{} within different radius (lower panel).
+
+	\end{enumerate}
+
+	These comparisons demonstrate the same results from different angles and 
+	the systematic differences become more clear using the fraction of \mtot{}
+	within different radius.  
+	The comparison of cumulative \logms{} profiles also demonstrates that the 
+	\rbcg{} and \nbcg{} samples have very similar median \mtot{}.  
+    They help confirm that the distributions of stellar mass within 100 kpc indeed 
+    have systematic differences between the massive central galaxies living in more 
+    and less massive dark matter haloes.
+
 %% ------------------------------------------------------------------------------------ %%
@@
     \caption{
-        \textbf{Left:} comparison of \mstar{} estimated by the GAMA survey and 
-        the \mtot{} using HSC images in this work. 
-        We plot the \logmgama{} against the difference between \logmtot{} and \logmgama{}. 
-        The two vertical lines highlight the mass range $11.4 \leq$\logmgama{}$<11.8$ 
-        that is used for the comparison.
+        \textbf{Top:} comparison of the cumulative \mstar{} profiles for 
+        \rbcg{} (orange--red) and \nbcg{} (grey--black) galaxies at fixed \mtot{}.~~
+        \textbf{Bottom:} comparison of the fraction of \mtot{} within different radius 
+        for the same samples at fixed \mtot{}. 
+        Thicker and darker solid lines highlight the median profiles. 
+        Other formats of the figure are similar to Figure \ref{fig:prof_1}. 
+        Besides the region affected by seeing, the 10 and 100 kpc radius, we 
+        also highlight the 50\% and 100\% values using horizontal grey lines on the 
+        bottom panel. 
         }

### 2017-07-31 draft/paper2_v4.tex
New version

--- 2017-07-26 draft/paper2_v3.tex
@@
 
-    In \citet{hscMassiveI}, we use deep ($>28.5$ \sb{} in $i$-band), high-quality 
-    (0.6\asec seeing) images of ${\sim}3000$ massive (\mstar{}$\geq 11.5$) central 
-    galaxies at $0.3 < z < 0.5$ from the Hyper Suprime-Cam Subaru Strategic Program 
-    to show that more massive central galaxies display more prominent stellar haloes 
-    with shallower outer stellar mass density profile (\mden) and higher ellipticity. 
-    In this work, we investigate the environment dependence of stellar mass 
-    distributions of massive central galaxies using the same dataset.
-    Treating stellar mass within a 100 kpc elliptical aperture (\mtot{}) as proxy of 
-    total stellar mass, we show that at fixed \mtot{}, massive central galaxies in 
-    \mhalo{}$\geq 10^{14}$\msun{} haloes show slightly shallower \mden{} profiles, 
-    larger half-light radius, and lower fraction of stellar mass within inner 10 kpc 
-    (\minn{}) than the centrals of \mhalo{}$< 10^{14}$\msun{} haloes. 
-    At fixed \minn{}--a tracer of the \textit{in situ} stellar mass, central galaxies 
-    from more massive haloes host much more significant outer stellar haloes despite 
-    their inner \mden{} profiles are very similar with the ones in less massive haloes.
-    These results clearly demonstrate that mass--size relation for central galaxies 
-    indeed depends on environment at high-\mtot{} end. 
-    We also show that the \mtot{}--\minn{} relation can reflect this dependence 
-    better and can help diagnose the assembly of massive galaxies and their haloes.
-    These results suggest more massive haloes favor more efficient growth of stellar 
-    haloes in their central galaxies, which is broadly consistent with the two phase 
-    formation scenario of massive galaxies in which their outer envelopes are 
-    accumulated through accretions of small systems.
+    We use ${\sim}100$ deg$^2$ of deep ($>28.5$\sb{} in $i$-band), high-quality 
+    (median 0.6\asec seeing) imaging data from the Hyper Suprime-Cam (HSC) survey 
+    to investigate the halo mass dependence of the surface mass density profiles 
+    and outer stellar envelopes of massive galaxies. 
+    The depth of the HSC survey reaches ${\sim}4$ magnitudes fainter than SDSS and 
+    enables us to directly trace stellar mass distributions to 100 kpc without 
+    requiring stacking.  
+    We conclusively show that at fixed stellar mass, the stellar profiles of massive 
+    galaxies depend on the masses of the their dark matter halos. 
+    On average, massive central galaxies in more massive halos have shallower inner 
+    stellar mass density profiles (within ${\sim}10$-$20$ kpc) and more prominent 
+    outer envelopes. 
+    These differences translate into a clear environmental dependence of the 
+    mass-size relation: central galaxies in more massive halos have larger 
+    $R_{\mathrm{50}}$ at fixed \mtot{}. 
+    We further find that the ellipticity of the outer stellar halo also increases 
+    with halo mass. 
+    Our results are broadly consistent with the two phase formation scenario of 
+    massive galaxies in which outer envelopes are built up at late times from the 
+    accretion of small systems.
 
@@
     in which galaxies form a compact central region at $z\sim 2$ through highly 
-    dissipative processes (e.g. gas-rich merger or cold gas-accretion;
+    dissipative processes (e.g. gas-rich mergers or cold gas-accretion;
     \citealt{Hopkins2008, Dekel2009}). 
@@
     Greene2015, Barbosa2016}.
-    These observations are generally consistent with the two-phase scenario, 
-    but this picture still face many challenges.
-    One of the most outstanding issues is the question of whether or not the 
-    fraction of accreted stellar mass displays a dependency on dark matter halos mass.
+Although these observations are generally consistent with the two-phase scenario, this picture still faces a key puzzle: whether or not sizes and profiles of galaxies depend on their mass of their host dark matter halos.
 
@@
     Massive ETGs living at the centers of more massive haloes should be subject to 
-    higher merger rate compared to ETGs with similar \mstar{} but living in less 
+    higher merger rates compared to ETGs with similar stellar mass but living in less 
     massive dark matter haloes. 
@@
     accreted component (the stellar halo) which can extend to 100 kpc and 
-    beyond \citep[eg.,][]{hscMassiveI}. 
-    This is very challenging observation as the surface brightness profiles of 
+    beyond \citep[eg.,][]{hscMassiveI}. This is observationally challenging as the surface brightness profiles of 
     massive ETGs decline rapidly with typical values of $\mu > 26.0$ \sb{} in 
@@
     \logms{}$>11.4$ at $0.3 < z < 0.5$ and out to 100 kpc. 
-    In Paper I, we characterized the stellar mass distributions and mass density 
-    profiles of stellar haloes of massive ETGs, and showed that there is a large 
+    In Paper I, we characterized the stellar mass profiles of massive ETGs, and showed that there is a large 
     intrinsic scatter in the \mden{} stellar halos of massive galaxies on 100 kpc 
-    scales, and that the fraction of accreted stars residing in the stellar halos 
-    increases as a function of \mstar{}. 
-    In this follow-up paper, we now address a fundamental prediction of the 
-    two-phase formation scenario and conclusively show that the extended stellar 
-    halos of massive central galaxies depend on dark matter halo mass. 
+    scales.
+In this paper, we now investigate whether or not the large scatter in the outer profiles of massive galaxies correlate with halo mass.
+We conclusively show that the sizes and stellar halos of massive central galaxies depend on dark matter halo mass.
     In other terms, we reveal the halo mass dependence of the mass-size relation 
@@
     Magnitudes use the AB system (\citealt{Oke1983}), and are corrected for Galactic 
-    extinction using calibrations from \citet{Schlafly11}.
-    In this work, we assume $H_0$ = 70~km~s$^{-1}$ Mpc$^{-1}$, ${\Omega}_{\rm m}=0.3$, 
+    extinction using calibrations from \citet{Schlafly11}. We assume $H_0$ = 70~km~s$^{-1}$ Mpc$^{-1}$, ${\Omega}_{\rm m}=0.3$, 
     and ${\Omega}_{\rm \Lambda}=0.7$.
     Stellar mass is denoted \mstar{} and has been derived using a Chabrier Initial Mass 
-    Function (IMF; \citealt{Chabrier2003}). Halo mass is defined as $M_{\rm 200b}$ as 
+    Function (IMF; \citealt{Chabrier2003}). Halo mass is defined as 
     $M_{\rm 200b}\equiv M(<r_{\rm 200b})=200\bar{\rho} 
@@
 %% ------------------------------------------------------------------------------------ %% 
-\subsection{The Role of Environment in the ``Two--Phase'' Formation of 
-            Massive Central Galaxies}
-
-    Results presented here are broadly consistent with the ``two-phase'' formation
-    scenario for massive central galaxies in a hierarchical universe. 
-    Under this picture, intense dissipative processes at $z > 2$ are responsible for 
-    the formation of the \textit{in situ} stars in massive central galaxies. 
-    After the star formation was quenched, a more gradual second phase is dominated 
-    by non-dissipative mergers of satellite galaxies. 
-    Since dry minor mergers can effectively deposit \textit{ex situ} stars in the 
-    outskirts of massive galaxies (e.g. \citealt{Oogi2013, Bedorf2013}), 
-    it is expected that the stellar mass distributions of massive galaxies 
-    show halo mass dependence, as the central galaxies of more massive haloes should
-    experience more mergers.
-
-    \citet{Shankar2014} investigates the environment dependence of galaxy size using 
+\subsection{The Role of Environment in the ``Two--Phase'' Formation Scenario}
+
+\alexie{This section does not have a good logical flow and needs more work and clarity. Ideas are ``choppy''}.
+
+    Our results are broadly consistent with the ``two-phase'' formation theory for massive central galaxies. According to this scenario, intense dissipative processes at $z > 2$ are responsible for 
+    the formation of \textit{in situ} stars in massive central galaxies.
+In the second phase, star-formation is quenched which limits in-situ star formation and growth becomes dominated by non-dissipative mergers of satellite galaxies.
+Dry minor mergers are efficient at depositing \textit{ex situ} stars in the outskirts of massive galaxies (e.g.
+\citealt{Oogi2013, Bedorf2013}).
+Because central galaxies in massive haloes should experience more mergers compared to those in less massive halos, we expect the stellar mass profiles (and sizes) of massive central galaxies to exhibit dependencies on host halo mass.
+
+    \citet{Shankar2014} studied the environment dependence of galaxy size using 
     a series of hierarchical semi-analytic models.
-    All models suggest that, at fixed stellar mass, the median size of galaxies 
-    strongly increases with halo mass. 
-    Although the centrals of more massive halos only experience slightly higher 
-    number of major mergers (mass ratio $>1$:3; e.g. \citealt{Hirschmann2013}), 
-    the number of minor mergers strongly depend on the assumed dynamical friction time. 
-    When short dynamical friction time is favored (e.g. \citealt{Newman2012}), 
-    centrals of more massive haloes can have up to four times more minor mergers 
-    (1:100--1:3). 
-    These extra minor mergers alone can lead to moderate halo mass dependence of 
-    galaxy size. 
-    Similarly, \citet{Yoon2017} confirms these theoretical predictions using 
-    semi-analytic model from \citet{Guo2011}.
-
-    These predictions are in general agreement with our findings here as we do see 
-    differences of \mden{} profiles in the outskirts are a major driver of the 
-    halo mass dependence, especially for the \minn{}--matched samples. 
-    At the same same, whether or not the difference in number of mergers can explain 
-    all the environment dependence is yet to be examined.
-
-    Both semi-analytic models and hydrodynamic simulations still have difficulties 
-    reproducing the observed mass--size relation for massive galaxies. 
-    Besides the reasons related to physical recipes, it is not straightforward for 
-    simulations to predict galaxy size in the same way with observations may also 
-    contribute to the problem. 
-    Since the definition of apertures mass is more clear, it would be interesting 
-    to compare with simulations using the \mtot{}--\minn{} relation instead of the 
-    mass--size one.
+They predict that at fixed stellar mass, the median size of central galaxies should increase strongly with halo mass.
+The major-merger rate increases slightly with halo mass (mass ratio $>1$:3; e.g.
+\citealt{Hirschmann2013}).
+The minor-merger rate, however, depends strongly on the dynamical friction time.
+If the dynamical friction time is short (e.g.
+\citealt{Newman2012}), then centrals of more massive haloes can have up to four times more minor mergers (1:100--1:3) \alexie{Compare to what?
+Need to give the halo mass numbers here}.
+This increase in the minor-merger rate as a function of halo mass leads to a halo-mass dependence in the mass-size relation.
+The prediction from \citet{Shankar2014} have been confirmed by \citet{Yoon2017} using the semi-analytic model from \citet{Guo2011}.
+Our results are broadly consistent with these predictions.
+Indeed, we find that the outer profiles of massive galaxies ($r>50$ kpc) are the regions that display the strongest variations as a function of halo mass.
+
+    %Whether or not level of difference that we observe is fully consistent with predictions from semi-analytic or hydrodynamic models of galaxy formation is work in progress that will be presented in a follow-up paper.
 
@@
 %% ------------------------------------------------------------------------------------ %% 
-\subsection{Comparisons with Mass--Size Relations from Other Works}
+\subsection{Comparison with Previous Work}
 
@@
 
-    Previous works on this topic at lower redshift mostly find no environment dependence
-    of mass--size relation (e.g. \citealt{Nair2010, Maltby2010, Cappellari2013, 
-    HCompany13}).  
-    The discrepancy between these results and ours should be explained by limitation of 
-    shallower images, method for estimating galaxy size, differences in \mstar{} and 
-    \mhalo{} ranges. 
-    \citet{Cerbrian2014} finds that ETGs with \logms{}$>11.5$ are slightly larger in 
-    more massive haloes, but they also shows that this environment trend is reversed 
-    at lower \mstar{}. 
-    \citet{Yoon2017} carefully studies a large sample of $z\sim0.1$ SDSS ETGs using  
-    non-parametric method and recovers a clear environment dependence of mass-size 
-    relation at \logms{}$>11.2$. 
-    They conclude that, at the same \mstar{}, massive ETGs from dense environment 
-    are 20--40\% larger than the ones in underdense environment. 
-    The definition of environment, estimates of \mstar{} and sizes in \citet{Yoon2017} 
-    are different with this work, but the results generally agree with ours.
-
-    Although recent results start to agree that mass--size relation of massive
-    ETGs show environment dependence, the situation at higher redshift is complicated. 
-    While certain works find environment dependence of mass--size relation for massive 
-    quiescent or early-type galaxies that is qualitatively consistent with the 
-    low-$z$ results (e.g. \citealt{Papovich2012, Lani2013, Strazzullo2013, 
-    Delaye2014}), there are still observations that suggest otherwise (e.g. 
-    \citealt{Rettura2010, Raichoor2012, Kelkar2015, Allen2015}). 
-    Some of this confusion can be explained by smaller sample size, special environment
-    (high-$z$ massive cluster), or impact of massive star-forming galaxies. 
-    But it also reflects the intrinsic difficulty of measuring \mstar{} and size 
-    of high-$z$ galaxies (e.g. \cite{Price2017}).
-    As we suggested earlier, with the help of deeper observations at higher redshift, 
-    it would be beneficial to directly compare the rest-frame surface brightness 
-    or the stellar mass density profiles instead of using mass--size relation alone 
-    (e.g. \citealt{Szomoru2012, Patel2013, Buitrago2017, Hill2017}).
+    Previous work on this topic has sometimes found the mass-size relation to be independent of halo mass (e.g.
+\citealt{Nair2010, Maltby2010, Cappellari2013, HCompany13}).
+There are several reasons that might explain why we reach the opposite conclusion compared to these studies: 1) the impact of imaging depth, 2) the method to estimate galaxy ``size'',  the range in  \mstar{} and \mhalo{}.
+
+    \citet{Cerbrian2014} find that ETGs with \logms{}$>11.5$ are slightly larger in 
+    more massive haloes, but they also shows that this trend is reversed 
+    at lower \mstar{}. \citet{Yoon2017} present a careful study of a large sample of $z\sim0.1$ SDSS ETGs using  
+    a non-parametric method and recover a clear environment dependence of mass-size 
+    relation at \logms{}$>11.2$. They conclude that, at the same \mstar{}, massive ETGs from dense environment 
+    are 20--40\% larger compared to those in underdense environment -- these results are in broad agreement with those presented here.
+    \alexie{Need a sentence abbout the new Mike Hudson paper here}
+
+    While there now appears to be an emerging consensus that the high mass end of the mass-size relation does vary with halo mass, the situation at higher redshift is more complicated.
+Certain studies find an environment dependence of the mass--size relation for massive
+    quiescent or early-type galaxies that is qualitatively consistent with low redshift studies (e.g. \citealt{Papovich2012, Lani2013, Strazzullo2013, 
+    Delaye2014}). However, there are also observations that suggest otherwise (e.g. 
+    \citealt{Rettura2010, Raichoor2012, Kelkar2015, Allen2015}). These differences might be explained by varying sample sizes,  special environments
+    (high-$z$ massive cluster), or the impact of massive star-forming galaxies.
+However, these yet un-reconciled differences, also underscore the  intrinsic difficulty of measuring stellar masses and sizes
+    for high-$z$ galaxies (e.g.
+\cite{Price2017}).
+Instead of using the mass--size relation to compare the high and the low redshift universe, a more robust approach would be to directly compare rest-frame surface brightness
+    or stellar mass density profiles (e.g. \citealt{Szomoru2012, Patel2013, Buitrago2017, Hill2017}).
+
+    \subsection{Towards Consistent Size Definitions}
+
+          Semi-analytic models and hydrodynamic simulations often have difficulties reproducing the  mass--size relation of massive galaxies.
+Galaxy sizes are sensitive to many different physical processes (star-formation, feedback, mergers) and matching the galaxy stellar-mass function does not automatically guarantee a match to the mass-size relation.
+Furthermore, while some effort has been made to use consistent size definitions (cite Bahamas paper), more often than not, comparisons of the mass-size relation often do not use consistent size definitions, or only perform crude size conversions (give an example here?
+3d radius and 2 radius).
+For examples, observers often quote ``sizes" which are the effective radius of an elliptical sersic fit.
+This is a 2d size  corresponding to the major axis of the ellipse that contains 50\% of the light.
+Simulations on the other hand, often employ sizes that correspond to xxx.
+In this paper, we quote masses measured within elliptical apertures of fixed physical size.
+We argue that this approach will allow for a more straightforward comparison between observations and theoretical predictions.
+In follow-up work, we will present comparisons between our observations and predictions from hydrodynamic simulations using the  using the \mtot{}--\minn{} plane instead of the mass-size relation.
+
 %% ------------------------------------------------------------------------------------ %%

### 2017-07-31 draft/paper2_v4.tex
Edited discussion

@@
     $R_{\mathrm{50}}$ at fixed \mtot{}.  
-    We further find that the ellipticity of the outer stellar halo also increases 
-    with halo mass. 
     Our results are broadly consistent with the two phase formation scenario of 
@@
     Greene2015, Barbosa2016}. 
-Although these observations are generally consistent with the two-phase scenario, this picture still faces a key puzzle: whether or not sizes and profiles of galaxies depend on their mass of their host dark matter halos.
+    Although these observations are generally consistent with the two-phase scenario, 
+    this picture still faces a key puzzle: whether or not sizes and profiles of galaxies 
+    depend on their mass of their host dark matter halos.
 
@@
     accreted component (the stellar halo) which can extend to 100 kpc and 
-    beyond \citep[eg.,][]{hscMassiveI}. This is observationally challenging as the surface brightness profiles of 
-    massive ETGs decline rapidly with typical values of $\mu > 26.0$ \sb{} in 
-    $i$-band at 100 kpc and at $z\sim0.3$. 
+    beyond \citep[eg.,][]{hscMassiveI}. 
+    This is observationally challenging as the surface brightness profiles of massive 
+    ETGs decline rapidly with typical values of $\mu > 26.0$ \sb{} in $i$-band at 100 
+    kpc and at $z\sim0.3$. 
     In \citet[][Paper I hereafter]{hscMassiveI}, we showed that deep, 
@@
     \logms{}$>11.4$ at $0.3 < z < 0.5$ and out to 100 kpc. 
-    In Paper I, we characterized the stellar mass profiles of massive ETGs, and showed that there is a large 
-    intrinsic scatter in the \mden{} stellar halos of massive galaxies on 100 kpc 
-    scales.
-In this paper, we now investigate whether or not the large scatter in the outer profiles of massive galaxies correlate with halo mass.
-We conclusively show that the sizes and stellar halos of massive central galaxies depend on dark matter halo mass.
+    In Paper I, we characterized the stellar mass profiles of massive ETGs, and 
+    showed that there is a large intrinsic scatter in the \mden{} stellar halos of
+    massive galaxies on 100 kpc scales. 
+    In this paper, we now investigate whether or not the large scatter in the outer 
+    profiles of massive galaxies correlate with halo mass. 
+    We conclusively show that the sizes and stellar halos of massive central galaxies 
+    depend on dark matter halo mass. 
     In other terms, we reveal the halo mass dependence of the mass-size relation 
@@
     Magnitudes use the AB system (\citealt{Oke1983}), and are corrected for Galactic 
-    extinction using calibrations from \citet{Schlafly11}. We assume $H_0$ = 70~km~s$^{-1}$ Mpc$^{-1}$, ${\Omega}_{\rm m}=0.3$, 
+    extinction using calibrations from \citet{Schlafly11}. 
+    We assume $H_0$ = 70~km~s$^{-1}$ Mpc$^{-1}$, ${\Omega}_{\rm m}=0.3$, 
     and ${\Omega}_{\rm \Lambda}=0.7$.
@@
     \begin{itemize}
-        \item \alexie{discuss here}. Massive central galaxies living in more and 
-            less massive haloes display similar ellipticity profiles at fixed \mtot{}. 
-            There is hint that suggests the central galaxies from more massive 
-            haloes become slightly more elongated at $R>50$ kpc than the ones 
-            in less massive haloes with similar \mtot{}. 
-            However, the uncertainties in the current ellipticity profiles make it 
-            not conclusive.
+        \item Within $R>50$ kpc, we find that the ellipticity profiles of massive 
+            central galaxies do not depend on halo mass at fixed \mtot{}.
 
@@
 
-    %Using the deep images from the HSC survey, we show that the stellar mass 
-    %distributions of massive central galaxies at $0.3 < z < 0.5$ depend on their 
-    %environment or \mhalo{}. 
-    %Here we briefly discuss the physical implications and potential caveats of this 
-    %result.
-
-%% ------------------------------------------------------------------------------------ %% 
-\subsection{The Role of Environment in the ``Two--Phase'' Formation Scenario}
-
-\alexie{This section does not have a good logical flow and needs more work and clarity. Ideas are ``choppy''}.
-
-    Our results are broadly consistent with the ``two-phase'' formation theory for massive central galaxies. According to this scenario, intense dissipative processes at $z > 2$ are responsible for 
-    the formation of \textit{in situ} stars in massive central galaxies.
-In the second phase, star-formation is quenched which limits in-situ star formation and growth becomes dominated by non-dissipative mergers of satellite galaxies.
-Dry minor mergers are efficient at depositing \textit{ex situ} stars in the outskirts of massive galaxies (e.g.
-\citealt{Oogi2013, Bedorf2013}).
-Because central galaxies in massive haloes should experience more mergers compared to those in less massive halos, we expect the stellar mass profiles (and sizes) of massive central galaxies to exhibit dependencies on host halo mass.
+%% ------------------------------------------------------------------------------------ %% 
+\subsection{The Role of Environment in the Two-Phase Formation Scenario}
+
+    Using the deep images from the HSC survey, we show that the stellar mass 
+    distributions of massive central galaxies at $0.3 < z < 0.5$ depend on their 
+    environment or \mhalo{}. 
+    At fixed \mtot{} or \minn{}, we find that the central galaxies from more massive 
+    haloes on average have larger half--light radius and host more prominent outer 
+    stellar haloes.
+
+    These results are broadly consistent with the ``two-phase'' formation theory for 
+    massive central galaxies. 
+    According to this scenario, intense dissipative processes at $z > 2$ are responsible 
+    for the formation of \textit{in situ} stars in massive central galaxies. 
+    In the second phase, star-formation is quenched which limits in-situ star formation 
+    and growth becomes dominated by non-dissipative mergers of satellite galaxies. 
+    Dry minor mergers are efficient at depositing \textit{ex situ} stars in the 
+    outskirts of massive galaxies (e.g. \citealt{Oogi2013, Bedorf2013}). 
+    Because central galaxies in massive haloes should experience more mergers compared 
+    to those in less massive halos, we expect the stellar mass profiles (and sizes) of 
+    massive central galaxies to exhibit dependencies on host halo mass.
 
@@
     a series of hierarchical semi-analytic models. 
-They predict that at fixed stellar mass, the median size of central galaxies should increase strongly with halo mass.
-The major-merger rate increases slightly with halo mass (mass ratio $>1$:3; e.g.
-\citealt{Hirschmann2013}).
+    They predict that at fixed stellar mass, the median size of central galaxies 
+    should increase strongly with halo mass. 
+    The major-merger rate only increases slightly with halo mass (mass ratio $>1$:3; 
+    e.g. \citealt{Hirschmann2013}). 
     The minor-merger rate, however, depends strongly on the dynamical friction time. 
-If the dynamical friction time is short (e.g.
-\citealt{Newman2012}), then centrals of more massive haloes can have up to four times more minor mergers (1:100--1:3) \alexie{Compare to what?
-Need to give the halo mass numbers here}.
-This increase in the minor-merger rate as a function of halo mass leads to a halo-mass dependence in the mass-size relation.
-The prediction from \citet{Shankar2014} have been confirmed by \citet{Yoon2017} using the semi-analytic model from \citet{Guo2011}.
+    If the dynamical friction time is short (e.g. \citealt{Newman2012}), the
+    massive central galaxies with $11.5 <$\logms{}$<12.0$ from more massive haloes 
+    (\logmh{}$>14.0$) can have up to four times more minor mergers (1:100--1:3)
+    comparing to the ones in less massive halos at similar stellar mass. 
+    This increase in the minor-merger rate as a function of halo mass leads to a 
+    halo-mass dependence in the mass-size relation. 
+    The prediction from \citet{Shankar2014} have been confirmed by \citet{Yoon2017} 
+    using the semi-analytic model from \citet{Guo2011}.  
     Our results are broadly consistent with these predictions. 
-Indeed, we find that the outer profiles of massive galaxies ($r>50$ kpc) are the regions that display the strongest variations as a function of halo mass.
-
-    %Whether or not level of difference that we observe is fully consistent with predictions from semi-analytic or hydrodynamic models of galaxy formation is work in progress that will be presented in a follow-up paper.
-
-    More importantly, our results show that the inner region of massive central 
-    galaxies also play a role here. 
-    Both the \mden{} profiles of \mtot{}--matched samples and the \mtot{}--\minn{}
-    plane suggest that, at fixed \mtot{}, centrals of more massive haloes have 
-    slightly shallower inner \mden{} slope and lower fraction of \mtot{} within the 
-    inner 10 kpc.
-    Minor mergers can not explain such difference as they should not alter the inner 
-    \mden{} profiles. 
-    This is also not caused by the choice of outer aperture to estimate ``total''
+    Indeed, we find that the outer profiles of massive galaxies ($r>50$ kpc) are the 
+    regions that display the strongest variations as a function of halo mass.
+
+%% ------------------------------------------------------------------------------------ %% 
+\subsection{Environmental Dependence of the Inner Regions of Massive Galaxies}
+
+    At the same time, from the comparison of median \mden{} profiles of the 
+    \mtot{}--matched samples and from the \mtot{}--\minn{} plane, our results also 
+    show that the centrals of more massive haloes have slightly shallower inner 
+    \mden{} slope and lower fraction of \mtot{} within the inner 10 kpc.
+    It seems that the environmental dependence of stellar mass distributions in 
+    massive central galaxies also affects their central region.
+    Unlike the differences in the outer stellar halo, it is difficult to use minor 
+    mergers to explain such difference as they should not alter the inner \mden{} 
+    profiles. 
+    It is also not caused by the choice of outer aperture to estimate ``total''
     \mstar{}: assuming that centrals in more massive haloes have more extended 
@@
 
-    Observations of compact quiescent galaxies at high-$z$ seem to indicate higher 
-    \mden{} in their central regions than their descendants. 
-    Therefore it is necessary to rely on certain processes to reduce the central 
-    \mden{} (e.g. strong adiabatic expansion induced by powerful AGN feedback; 
-    \citealt{Fan2008}) to match the inner \mden{} profiles of massive central galaxies 
-    at lower redshift.
-    Coalesce of super-massive black hoes (SMBHs) at the end of major merger, which 
-    is common in the assembly history of massive galaxies, can also flatten the 
-    central \mden{} profile via efficient scattering effect 
+    Several physicals processes may help shape the stellar mass distributions in the 
+    inner region. 
+    For instance, strong adiabatic expansion induced by powerful AGN feedback can 
+    lead to more flattened inner \mden{} profile \citealt{Fan2008}. 
+    The violent relaxation process involved in the major dry merger can reshape 
+    stellar mass distributions in the inner region. 
+    In addition, the coalesce of super-massive black hoes (SMBHs) at the end of 
+    major merger, which is common in the assembly history of massive galaxies, can 
+    also flatten the central \mden{} profile via efficient scattering effect 
     (e.g. \citealt{Milosavljevi2002}).
@@
     The impacts of these processes, and their dependence on \mhalo{} is an interesting 
-    topic to investigate in the future.
+    topic to investigate in the future through comparisons with both observations 
+    at high redshift and numerical simulations.
 
@@
 
-    Previous work on this topic has sometimes found the mass-size relation to be independent of halo mass (e.g.
-\citealt{Nair2010, Maltby2010, Cappellari2013, HCompany13}).
-There are several reasons that might explain why we reach the opposite conclusion compared to these studies: 1) the impact of imaging depth, 2) the method to estimate galaxy ``size'',  the range in  \mstar{} and \mhalo{}.
+    Previous work on this topic has sometimes found the mass-size relation to be 
+    independent of halo mass (e.g. \citealt{Nair2010, Maltby2010, Cappellari2013, 
+    HCompany13}). 
+    There are several reasons that might explain why we reach the opposite conclusion 
+    compared to these studies: 1) the impact of imaging depth, 2) the method to estimate 
+    galaxy ``size'',  the range in  \mstar{} and \mhalo{}.
 
@@
     more massive haloes, but they also shows that this trend is reversed 
-    at lower \mstar{}. \citet{Yoon2017} present a careful study of a large sample of $z\sim0.1$ SDSS ETGs using  
-    a non-parametric method and recover a clear environment dependence of mass-size 
-    relation at \logms{}$>11.2$. They conclude that, at the same \mstar{}, massive ETGs from dense environment 
-    are 20--40\% larger compared to those in underdense environment -- these results are in broad agreement with those presented here.
-    \alexie{Need a sentence abbout the new Mike Hudson paper here}
-
-    While there now appears to be an emerging consensus that the high mass end of the mass-size relation does vary with halo mass, the situation at higher redshift is more complicated.
-Certain studies find an environment dependence of the mass--size relation for massive
-    quiescent or early-type galaxies that is qualitatively consistent with low redshift studies (e.g. \citealt{Papovich2012, Lani2013, Strazzullo2013, 
-    Delaye2014}). However, there are also observations that suggest otherwise (e.g. 
-    \citealt{Rettura2010, Raichoor2012, Kelkar2015, Allen2015}). These differences might be explained by varying sample sizes,  special environments
+    at lower \mstar{}. 
+    \citet{Yoon2017} present a careful study of a large sample of $z\sim0.1$ SDSS ETGs 
+    using a non-parametric method and recover a clear environment dependence of 
+    mass-size relation at \logms{}$>11.2$. 
+    They conclude that, at the same \mstar{}, massive ETGs from dense environment 
+    are 20--40\% larger compared to those in underdense environment -- these results are 
+    in broad agreement with those presented here.
+    Recently, \citet{Charlton2017} uses single-\ser{} model for galaxies at 
+    $0.2 < z < 0.8$ in the CFHTLenS (\citealt{Heymans2012}) and their galaxy--galaxy 
+    lensing measurements to show that larger galaxies tend to live in more massive 
+    dark matter haloes.
+
+    While there now appears to be an emerging consensus at low redshift that the 
+    high mass end of the mass-size relation does vary with halo mass, the situation at 
+    higher redshift is more complicated. 
+    Certain studies find an environment dependence of the mass--size relation for 
+    massive quiescent or early-type galaxies that is qualitatively consistent with low 
+    redshift studies (e.g. \citealt{Papovich2012, Lani2013, Strazzullo2013, 
+    Delaye2014}). 
+    However, there are also observations that suggest otherwise (e.g. 
+    \citealt{Rettura2010, Raichoor2012, Kelkar2015, Allen2015}). 
+    These differences might be explained by varying sample sizes, special environments
     (high-$z$ massive cluster), or the impact of massive star-forming galaxies. 
-However, these yet un-reconciled differences, also underscore the  intrinsic difficulty of measuring stellar masses and sizes
-    for high-$z$ galaxies (e.g.
-\cite{Price2017}).
-Instead of using the mass--size relation to compare the high and the low redshift universe, a more robust approach would be to directly compare rest-frame surface brightness
-    or stellar mass density profiles (e.g. \citealt{Szomoru2012, Patel2013, Buitrago2017, Hill2017}).
-
+    However, these yet un-reconciled differences, also underscore the intrinsic 
+    difficulty of measuring stellar masses and sizes for high-$z$ galaxies 
+    (e.g. \cite{Price2017}). 
+    Instead of using the mass--size relation to compare the high and the low redshift 
+    universe, a more robust approach would be to directly compare rest-frame surface 
+    brightness or stellar mass density profiles (e.g. \citealt{Szomoru2012, Patel2013,
+    Buitrago2017, Hill2017}).
+
+%% ------------------------------------------------------------------------------------ %% 
 \subsection{Towards Consistent Size Definitions}
 
-          Semi-analytic models and hydrodynamic simulations often have difficulties reproducing the  mass--size relation of massive galaxies.
-Galaxy sizes are sensitive to many different physical processes (star-formation, feedback, mergers) and matching the galaxy stellar-mass function does not automatically guarantee a match to the mass-size relation.
-Furthermore, while some effort has been made to use consistent size definitions (cite Bahamas paper), more often than not, comparisons of the mass-size relation often do not use consistent size definitions, or only perform crude size conversions (give an example here?
-3d radius and 2 radius).
-For examples, observers often quote ``sizes" which are the effective radius of an elliptical sersic fit.
-This is a 2d size  corresponding to the major axis of the ellipse that contains 50\% of the light.
-Simulations on the other hand, often employ sizes that correspond to xxx.
-In this paper, we quote masses measured within elliptical apertures of fixed physical size.
-We argue that this approach will allow for a more straightforward comparison between observations and theoretical predictions.
-In follow-up work, we will present comparisons between our observations and predictions from hydrodynamic simulations using the  using the \mtot{}--\minn{} plane instead of the mass-size relation.
+    Until recently, semi-analytic models and hydrodynamic simulations still have 
+    difficulties reproducing the mass--size relation of massive galaxies. 
+    Galaxy sizes are sensitive to many different physical processes (star-formation, 
+    feedback, mergers) and matching the galaxy stellar-mass function does not 
+    automatically guarantee a match to the mass-size relation. 
+    Furthermore, while some efforts have been made to use consistent size definitions 
+    (\citealt{McCarthy2017}), more often than not, comparisons of the mass-size relation 
+    often do not use consistent size definitions, or only perform crude size conversions 
+    (e.g. 3--D radius in simulation versus 2--D projected radius in observation; 
+    \citealt{Genel2017}). 
+    Observers often quote ``sizes'' corresponding to the half--light radius along the 
+    major axis using 2--D projected images. 
+    Simulations on the other hand, often employ sizes that correspond to the 3--D 
+    aperture half--mass radius (e.g. \citealt{Price2017}).
+
+    As emphasized earlier, definitions of galaxy ``size'' in observations are also not 
+    always consistent. 
+    Measurement of ``size'' often show dependence on image quality (e.g. seeing, 
+    imaging depth), filter, and the adopted method. 
+    Although elliptical single--\ser{} model is widely adopted in measuring the 
+    size of galaxies of different types and at different redshift, it sometimes leads
+    to biased results as it is no longer appropriate model for certain type of galaxy. 
+    Size derived from 1-D curve--of--growth is more model independent and is shown to 
+    be useful in revealing environmental dependence of mass--size relation 
+    (e.g. \citealt{Yoon2017} and this work), but it does not take the PSF convolution 
+    effect into account and depends on imaging depth and background subtraction.
+
+    In this paper, we quote stellar masses measured within elliptical apertures of 
+    fixed physical size. 
+    We argue that this approach will allow for a more straightforward comparison 
+    between observations and theoretical predictions. 
+    In follow-up work, we will present comparisons between our observations and 
+    predictions from hydrodynamic simulations using the using the \mtot{}--\minn{} 
+    plane instead of the mass--size relation.
 

### 2017-08-08 draft/paper2_v5.tex
Response to Jenny's comments

--- 2017-07-31 draft/paper2_v4.tex
@@
 % Version 3; preprint format; Edited by Alexie Leauthaud
+% Version 4; preprint format; Edited by Song Huang
+% Version 5; preprint format; Edited by Jenny Greene and Song Huang
 
@@
     We conclusively show that at fixed stellar mass, the stellar profiles of massive 
-    galaxies depend on the masses of the their dark matter halos. 
+    galaxies depend on the masses of their dark matter halos. 
     On average, massive central galaxies in more massive halos have shallower inner 
@@
     this picture still faces a key puzzle: whether or not sizes and profiles of galaxies 
-    depend on their mass of their host dark matter halos.
+    depend on the mass of their host dark matter halos.
 
@@
    We use these two simple metric masses to explore the \mstar{}-dependence of the 
-   fraction of accreted stars, and reveal to the diversity of stellar envelopes among 
+   fraction of accreted stars, and reveal the diversity of stellar envelopes among 
    massive galaxies. 
-   In practice, we also have the full profiles for each galaxy and can also cast our 
+   In practice, we also have the full profiles for each galaxy and can cast our 
    results in terms of the full stellar mass profiles. 
@@
    We will use these two apertures masses to guide our comparisons of massive galaxies 
-   as a function of environments.
+   as a function of environment.
 
@@
     Firstly, we select 68 massive central galaxies from \redm{} clusters 
-    with $\lambda \geq 30$, $P_{\mathrm{Cen}} \geq 0.7$, and \logmtot{}$>11.5$ 
+    with richness ($\lambda$) $\geq 30$, and the probability of true central galaxy 
+    ($P_{\mathrm{Cen}}$) $\geq 0.7$, and \logmtot{}$>11.5$ 
     at $0.3 < z < 0.5$ (63/68 have \logmtot{}$>11.6$). 
@@
 
-    We note that our method fails to extract 1-D profiles for $\sim10$\% of 
+    We note that our analysis fails to extract 1-D profiles for $\sim10$\% of 
     \rbcg{} and \nbcg{} galaxies due on-going major mergers or projection effects 
@@
 %% ------------------------------------------------------------------------------------ %% 
-\subsection{Environmental Dependence of the Profiles of Massive Galaxies}
+\subsection{Environmental Dependence of the Stellar Mass Density Profiles of Massive 
+            Galaxies}
     \label{ssec:sbp_mtot}
@@
     halo mass at fixed stellar mass.
-    To ask this question, however, we must first define which stellar mass exactly is 
-    being fixed in the comparison. 
+    %To ask this question, however, we must first define which stellar mass exactly is 
+    %being fixed in the comparison.
+
     We will show comparisons of \mden{} profiles at both fixed \mtot{} as well as fixed 
@@
     fixed \minn{} (right panel). 
+    At fixed \mtot{}, we compare massive galaxies that have similar ``total'' \mstar{}. 
+    On the right side, we use \minn{} as proxy of the \textit{in situ} \mstar{} to 
+    compare the overall \mstar{} distributions of galaxies living in different 
+    environments that have assembled similar amount of stars at high-$z$.
     This figure shows the main result of this paper, namely that 
-    \textbf{the \mden{} profiles of massive central galaxies show a clear dependence on 
+    \emph{the \mden{} profiles of massive central galaxies show a clear dependence on 
     dark matter halo mass at both fixed \mtot{} and \minn{}.}
@@
 
-        \item For the \mtot{} matched sample, although there is a clear and robust 
+        \item For the \mtot{}--matched samples, although there is a clear and robust 
             difference between the two median \mden{} profiles, the overall difference 
@@
             more significant outer stellar haloes. 
-
-        \item The median \mden{} profiles of the \rbcg{} and \nbcg{} samples cross 
+            The median \mden{} profiles of the \rbcg{} and \nbcg{} samples cross 
             each other at ${\sim} 15$-20 kpc, roughly the typical effective radius 
@@
 
-        \item Finally, the differences between the two sets of profiles becomes 
-            more prominent at higher \mtot{}. 
-            This can be seen further dividing the sample into two \mtot{} bins 
-            (see Fig~\ref{fig:prof_2} and discussion in Appendix~\ref{app:robust}) 
-            and when we discuss the relation between \mtot{} and 
-            \minn{} (see Fig~\ref{fig:scaling_relation}). 
-            This trend potentially indicates that the assembly of stellar haloes in 
-            more massive central galaxies become more sensitive to their 
-            environments or halo mass.
+        \item For the \minn{}--matched samples, their median \mden{} profiles 
+            are very similar at $R \leq 10$ kpc. 
+            However, massive galaxies with similar \mstar{} within 10 kpc have quite
+            different \mtot{}, and the massive central galaxies in 
+            more massive haloes host much more prominent outer stellar halo.
+
+        \item Also, for the \minn{}--matched samples, the similar slopes of the 
+            \mden{} profiles within 10 kpc are in sharp contrast with the large
+            \textit{intrinsic} scatter we see in the outer \mden{} profiles.
 
@@
     stellar mass}.
-
-    It is therefore interesting to see the comparison of \mden{} profiles at fixed 
-    \minn{}--a reasonable tracer for the stellar mass in the \textit{in situ}
-    component (right panel of Fig~\ref{fig:prof_1}).  
-    Although the median \mden{} profiles are very similar at $R \leq 10$ kpc, the
-    massive central galaxies in more massive haloes host much more prominent outer 
-    stellar halo. 
-    Also, the similar slopes of the \mden{} profiles within 10 kpc are in sharp 
-    contrast with the large \textit{intrinsic} scatter we see in the outer \mden{} 
-    profiles. 
-    This hints that these two regions could be shaped by distinctive physical 
-    processes, and may explain why they depend on halo mass differently.  
+    Also, the differences in median \mden{} profiles seem to become more prominent 
+    at higher \mtot{}. 
+    This is demonstrated in Appendix~\ref{app:robust} (see Fig~\ref{fig:prof_2}). 
+    Although this trend still needs to be confirmed by larger samples, it 
+    potentially indicates that the assembly of stellar haloes in more massive 
+    central galaxies become more sensitive to their environments.
+
+    Meanwhile, the comparison of \mden{} profiles at fixed \minn{}--a reasonable 
+    tracer for the stellar mass in the \textit{in situ} component (right panel of 
+    Fig~\ref{fig:prof_1}) hints that the inner region ($<10$ kpc) and the outer 
+    stellar halo could be shaped by distinctive physical processes, and may explain 
+    why they depend on halo mass differently.  
     In simulations, intensive dissipative process helps create 
@@
     (environmental dependence) of \mden{} profiles within 100 kpc in massive central 
-    galaxies}. 
+    galaxies. 
     Such dependence seems to be consistent with the expectation of more (minor) 
@@
     profiles, but can build up the outer halo efficiently
-    (e.g. \citealt{Hilz2013}, \citealt{Oogi2013}).
+    (e.g. \citealt{Hilz2013}, \citealt{Oogi2013})}.
 
@@
     This definition of ``effective radius'' is more robust against structural details, 
-    choice of model, and the background subtraction comparing to the effective radius 
+    choice of model, and the background subtraction compared to the effective radius 
     estimated by simple 2-D modeling method (e.g. single-\ser{} model). 
@@
 
-    \noindent As shown in the left panel of Fig~\ref{fig:scaling_relation}, galaxies 
-    in more and less massive dark matter haloes lie on \mtot{}--$R_{\mathrm{50}}$ 
-    relations that have similar slopes but different normalizations. 
-    This result is robust against the ranges of \mstar{} over which the fit is performed 
-    and against the definitions of  ``total'' \mstar{} and half-light 
+    \noindent As shown in the left panel of Fig~\ref{fig:scaling_relation}, 
+    galaxies in more and less massive dark matter haloes lie on 
+    \mtot{}--$R_{\mathrm{50}}$ relations that have similar slopes but 
+    different normalizations. 
+    The best-fit mass--size relations derived here suggests that, 
+    at $0.3 < z < 0.5$, central galaxies with \logmtot{}$>11.6$ in \logmhalo{}$>14.0$
+    haloes are on average $\sim20$\% larger than the centrals from \logmhalo{}$<14.0$
+    haloes at fixed \mtot{}.
+    This result is robust against the ranges of \mstar{} over which the fit is 
+    performed and against the definitions of  ``total'' \mstar{} and half-light 
     radius\footnote{Using \mstar{} within 120 or 150 kpc, or using the 
     $R_{\mathrm{50}}$ derived within these apertures do not change the results.}. 
+    Given the uncertainties of the best-fit parameters, the differences in 
+    mass--size relation is not very significant.  
+    It relates to the relative small sample sizes, uncertainties in \mstar{} and 
+    \mhalo{} estimates, and the limited \mtot{} range used in the fitting.
 
@@
     mass--size relation for central galaxies in the range $12.5\le$ \logmh{} $<15.0$.     
-    However, HC13 use SDSS images that are considerably shallower compared to the HSC 
-    ones and hence will not be as sensitive to the outer portions of the \mden{} 
-    profile where we see the most clear differences. 
-    A more detailed comparison is beyond the scope of this work, but in 
-    Appendix~\ref{app:gama}, we use the \rbcg{} and \nbcg{} galaxies that overlap 
-    with the GAMA survey to briefly demonstrate this point. 
-    We show that, for galaxies with similar \mstar{} derived from single-\ser{} 
-    models using shallower SDSS images (\citealt{Kelvin2012}), the ones in more 
-    massive dark matter halos actually show more prominent outer stellar halos, 
-    hence both of their stellar mass and effective radius are underestimated.  
-    This shows again that the deeper HSC images has unique advantage in studying the
-    connection between the assembly of massive galaxies and their dark matter haloes.
+    Both the considerably shallower SDSS images and the single-\ser{} model could 
+    contribute to this difference, since the most clear environmental differences 
+    are found in the low surface brightness stellar halos that can not be 
+    well-modeled with the inner portion of the \mden{} profile using single-\ser{}
+    profiles.
 
@@
     stellar haloes. 
-    Although the HSC images can not resolve the central region of these massive 
-    galaxies, the on average lower \mstar{} within 10 kpc and shallower inner \mden{} 
-    profile for massive central galaxies living in more massive haloes are robust 
-    results and could have interesting physical implications.
     Meanwhile, at fixed \minn{}--a proxy for the \mstar{} of the ``in situ'' component,
@@
     Section~\ref{sec:discussion}.
+
+    % Although the HSC images can not resolve the central region of these massive 
+    % galaxies, the on average lower \mstar{} within 10 kpc and shallower inner \mden{} 
+    % profile for massive central galaxies living in more massive haloes are robust 
+    % results and could have interesting physical implications.
 
@@
     \begin{itemize}
-        \item Within $R>50$ kpc, we find that the ellipticity profiles of massive 
+        \item Within $R<50$ kpc, we find that the ellipticity profiles of massive 
             central galaxies do not depend on halo mass at fixed \mtot{}.
@@
 
-    Besides these conclusions, the fact that we find smooth ellipticity profile and 
-    its shallow gradient favors the idea of using the flux-weighted average isophotal 
+    Besides these conclusions, the fact that we find smooth ellipticity profiles and 
+    shallow gradients favors the idea of using the flux-weighted average isophotal 
     shape to extract 1-D \mden{} profiles of massive galaxies. 
@@
     massive central galaxies.
-    According to this scenario, intense dissipative processes at $z > 2$ are responsible 
-    for the formation of \textit{in situ} stars in massive central galaxies. 
-    In the second phase, star-formation is quenched which limits in-situ star formation 
-    and growth becomes dominated by non-dissipative mergers of satellite galaxies. 
+    According to this scenario, intense dissipative processes at $z > 2$ are 
+    responsible for the formation of \textit{in situ} stars in massive central 
+    galaxies. 
+    In the second phase, star-formation is quenched which limits in-situ star 
+    formation and growth becomes dominated by non-dissipative mergers of satellite
+    galaxies. 
     Dry minor mergers are efficient at depositing \textit{ex situ} stars in the 
     outskirts of massive galaxies (e.g. \citealt{Oogi2013, Bedorf2013}). 
-    Because central galaxies in massive haloes should experience more mergers compared 
-    to those in less massive halos, we expect the stellar mass profiles (and sizes) of 
-    massive central galaxies to exhibit dependencies on host halo mass.
+    Because central galaxies in massive haloes should experience more mergers 
+    compared to those in less massive halos, we expect the stellar mass profiles 
+    (and sizes) of massive central galaxies to exhibit dependencies on host halo 
+    mass.
 
@@
     (\logmh{}$>14.0$) can have up to four times more minor mergers (1:100--1:3)
-    comparing to the ones in less massive halos at similar stellar mass. 
+    compared to the ones in less massive halos at similar stellar mass. 
     This increase in the minor-merger rate as a function of halo mass leads to a 
     halo-mass dependence in the mass-size relation. 
-    The prediction from \citet{Shankar2014} have been confirmed by \citet{Yoon2017} 
+    The predictions from \citet{Shankar2014} have been confirmed by \citet{Yoon2017} 
     using the semi-analytic model from \citet{Guo2011}.  
@@
     massive central galaxies also affects their central region.
-    Unlike the differences in the outer stellar halo, it is difficult to use minor 
-    mergers to explain such difference as they should not alter the inner \mden{} 
-    profiles. 
-    It is also not caused by the choice of outer aperture to estimate ``total''
+    This is not caused by the choice of outer aperture to estimate ``total''
     \mstar{}: assuming that centrals in more massive haloes have more extended 
@@
     inner region. 
-    For instance, strong adiabatic expansion induced by powerful AGN feedback can 
-    lead to more flattened inner \mden{} profile \citealt{Fan2008}. 
-    The violent relaxation process involved in the major dry merger can reshape 
-    stellar mass distributions in the inner region. 
-    In addition, the coalesce of super-massive black hoes (SMBHs) at the end of 
-    major merger, which is common in the assembly history of massive galaxies, can 
-    also flatten the central \mden{} profile via efficient scattering effect 
+    Major merger can redistribute the inner stellar mass distributions, but major
+    merger rate does not strongly depend on halo mass. 
+    Although recent simulations tend to emphasize the contribution of dry minor 
+    mergers in building up the outer envelope, simulation also shows that minor 
+    mergers can modify the central surface brightness profiles of the remnants
+    (e.g. \citealt{BoylanKolchin2007}). 
+    Depending on the structure and infalling orbit of the satellite, minor merger 
+    can make the inner \mden{} profiles both flattened or steepened.  
+    Interestingly, these authors find, when satellite is accreted from a highly 
+    eccentric and energetic orbit to a core--elliptical galaxy, it tends to reduce 
+    the central \mden{}.  
+    This is relevant here as many massive BCGs are known to be core--elliptical 
+    galaxies. 
+    Also, strong adiabatic expansion induced by powerful AGN feedback can be another 
+    interesting option (e.g. \citealt{Fan2008}). 
+    This proposed efficient mass--loss can expand the central stellar mass 
+    distribution low central \mden{}.  
+    In addition, at smaller scale, the coalesce of super-massive black hoes (SMBHs)  
+    can flatten the central \mden{} profile via efficient scattering effect 
     (e.g. \citealt{Milosavljevi2002}).
@@
 
-    The best-fit mass--size relation derived here suggests that, at $0.3 < z < 0.5$, 
-    central galaxies with \logmtot{}$>11.6$ in \logmhalo{}$>14.0$ haloes are on average
-    $\sim20$\% larger than the centrals from \logmhalo{}$<14.0$ haloes at fixed \mtot{}.
-
-    Previous work on this topic has sometimes found the mass-size relation to be 
-    independent of halo mass (e.g. \citealt{Nair2010, Maltby2010, Cappellari2013, 
-    HCompany13}). 
-    There are several reasons that might explain why we reach the opposite conclusion 
-    compared to these studies: 1) the impact of imaging depth, 2) the method to estimate 
-    galaxy ``size'',  the range in  \mstar{} and \mhalo{}.
-
-    \citet{Cerbrian2014} find that ETGs with \logms{}$>11.5$ are slightly larger in 
-    more massive haloes, but they also shows that this trend is reversed 
-    at lower \mstar{}. 
+    In this work, we demonstrate that the stellar mass distributions and mass--size 
+    relation of massive central galaxies depend on their host dark matter halo masses. 
+    At $0.3 < z < 0.5$, \logmtot{}$>11.6$ galaxies from \logmhalo{}$>14.0$ haloes 
+    are on average $\sim20$\% larger than the ones from smaller haloes at fixed 
+    \mtot{}.
+
+    Many previous works that focused on the mass-size relation found this relation 
+    is independent of halo mass or environment at $z\sim 0.0$ 
+    (e.g. \citealt{Nair2010, Maltby2010, Cappellari2013, HCompany13}). 
+    As mentioned earlier, both the shallower imaging depth and the oversimple model 
+    (e.g. single-\ser{} or de~Vaucouleurs model) used in the fitting can both 
+    contribute to this difference.
+    In Appendix~\ref{app:gama}, we use the \rbcg{} and \nbcg{} galaxies that overlap 
+    with the GAMA survey to briefly demonstrate this point. 
+    We show that, for galaxies with similar \mstar{} derived from single-\ser{} 
+    models using shallower SDSS images (\citealt{Kelvin2012}), the ones in more 
+    massive dark matter halos actually show more prominent outer stellar halos, 
+    hence both of their stellar mass and effective radius are underestimated.  
+    This shows again that the deeper HSC images has unique advantage in studying 
+    the connection between the assembly of massive galaxies and their dark matter 
+    haloes.
+
+    At the same time, \citet{Cerbrian2014} find that ETGs with \logms{}$>11.5$ are 
+    slightly larger in more massive haloes, and they also shows that this trend is 
+    reversed at lower \mstar{}. 
     \citet{Yoon2017} present a careful study of a large sample of $z\sim0.1$ SDSS ETGs 
@@
     They conclude that, at the same \mstar{}, massive ETGs from dense environment 
-    are 20--40\% larger compared to those in underdense environment -- these results are 
-    in broad agreement with those presented here.
+    are 20--40\% larger compared to those in underdense environment.
     Recently, \citet{Charlton2017} uses single-\ser{} model for galaxies at 
@@
     dark matter haloes.
-
-    While there now appears to be an emerging consensus at low redshift that the 
-    high mass end of the mass-size relation does vary with halo mass, the situation at 
+    These results are in broad agreement with those presented here.
+
+    While there appears to be an emerging consensus at low redshift now that the 
+    high--mass end of the mass-size relation does vary with halo mass, the situation at 
     higher redshift is more complicated. 
@@
     difficulty of measuring stellar masses and sizes for high-$z$ galaxies 
-    (e.g. \cite{Price2017}). 
+    (e.g. \citealt{Price2017}). 
     Instead of using the mass--size relation to compare the high and the low redshift 
@@
     Until recently, semi-analytic models and hydrodynamic simulations still have 
-    difficulties reproducing the mass--size relation of massive galaxies. 
+    difficulty reproducing the mass--size relation of massive galaxies. 
     Galaxy sizes are sensitive to many different physical processes (star-formation, 
@@
     (\citealt{McCarthy2017}), more often than not, comparisons of the mass-size relation 
-    often do not use consistent size definitions, or only perform crude size conversions 
+    do not use consistent size definitions, or only perform crude size conversions 
     (e.g. 3--D radius in simulation versus 2--D projected radius in observation; 
@@
     always consistent. 
-    Measurement of ``size'' often show dependence on image quality (e.g. seeing, 
+    Measurement of ``size'' often shows dependence on image quality (e.g. seeing, 
     imaging depth), filter, and the adopted method. 
-    Although elliptical single--\ser{} model is widely adopted in measuring the 
-    size of galaxies of different types and at different redshift, it sometimes leads
-    to biased results as it is no longer appropriate model for certain type of galaxy. 
-    Size derived from 1-D curve--of--growth is more model independent and is shown to 
-    be useful in revealing environmental dependence of mass--size relation 
+    Although the elliptical single--\ser{} model is widely adopted in measuring the 
+    size of galaxies of different types and at different redshifts, it sometimes leads
+    to biased results as it is no longer appropriate model for certain types of galaxy. 
+    Size derived from 1-D curve--of--growth is more model independent and has been 
+    shown to be useful in revealing environmental dependence of the mass--size relation 
     (e.g. \citealt{Yoon2017} and this work), but it does not take the PSF convolution 
@@
 
-    Using the high-quality images from the first $\sim100$ deg$^2$ data of the 
+    Using the high-quality images from the first $\sim100$ deg$^2$ of the 
     Hyper Suprime-Cam Subaru Strategic Program, we group a large sample of massive 
@@
         \item We do not find evidence that suggests the rest-frame color profiles 
-            within 60 kpc depend on environment for neither \mtot{}- nor 
+            within 60 kpc depend on environment for either the \mtot{}- nor 
             \minn{}--matched samples.
@@
     We are currently working on combining the current results with weak lensing 
-    measurements of dark matter haloes around these massive galaxies to gain more physical 
-    insights. 
-    We will also compare our results with cosmological hydro-simulations 
-    such as 
-    \textit{Illustris-TNG} (\citealt{Pillepich2017a, Pillepich2017b, Weinberger2017}, 
-    \textit{Horizon-AGN} (\citealt{Dubois2014}), or 
-    \textit{MassiveBlackII} (\citealt{Khandai2015}).
+    measurements of dark matter haloes around these massive galaxies, and comparing 
+    our results with hydrodynamic simulations to gain more physical insights.
 

### 2017-08-09 draft/paper2_v5.tex
New version

@@
 
-    We use ${\sim}100$ deg$^2$ of deep ($>28.5$\sb{} in $i$-band), high-quality 
-    (median 0.6\asec seeing) imaging data from the Hyper Suprime-Cam (HSC) survey 
+    We use ${\sim}100$ deg$^2$ of deep ($>28.5$ \sb{} in $i$-band), high-quality 
+    (median 0.6\asec seeing) imaging data from the Hyper Suprime--Cam (HSC) survey 
     to investigate the halo mass dependence of the surface mass density profiles 
     and outer stellar envelopes of massive galaxies. 
-    The depth of the HSC survey reaches ${\sim}4$ magnitudes fainter than SDSS and 
-    enables us to directly trace stellar mass distributions to 100 kpc without 
+    The $i$-band images from HSC survey reach ${\sim}4$ magnitudes deeper than SDSS 
+    and enable us to directly trace stellar mass distributions to 100 kpc without 
     requiring stacking.  
@@
     galaxies depend on the masses of their dark matter halos. 
-    On average, massive central galaxies in more massive halos have shallower inner 
-    stellar mass density profiles (within ${\sim}10$-$20$ kpc) and more prominent 
-    outer envelopes. 
-    These differences translate into a clear environmental dependence of the 
-    mass-size relation: central galaxies in more massive halos have larger 
-    $R_{\mathrm{50}}$ at fixed \mtot{}.  
-    Our results are broadly consistent with the two phase formation scenario of 
-    massive galaxies in which outer envelopes are built up at late times from the 
-    accretion of small systems.
+    On average, massive central galaxies with \logmtot{}$>11.6$ in more massive halos 
+    at $0.3 < z < 0.5$ have shallower inner stellar mass density profiles 
+    (within ${\sim}10$-$20$ kpc) and more prominent outer envelopes. 
+    These differences translate into a halo mass dependence of the 
+    mass--size relation: central galaxies in halos with \logmh{}$>14.0$ are 
+    $\sim 20$\% larger in $R_{\mathrm{50}}$ at fixed \mtot{}.  
+    Such dependence is also reflected in the relationship between the stellar mass 
+    within 10 and 100 kpc. 
+    Comparing to the mass--size relation, the \mtot{}--\minn{} relation avoids the 
+    ambiguity in the definition of size, and can be straightforwardly compared with 
+    simulations. 
+    Our results demonstrate that, with deep images from HSC, we can quantify the 
+    connection between halo mass and the outer stellar halo, which may provide new 
+    constraints on the formation and assembly of massive central galaxies.
 
@@
     For instance, the model from \citet{Saito2016} predicts a $\sim 7$\% 
-    fraction for galaxies with \logmtot{}$>11.6$ and \logmh$<11.4$ haloes.
+    fraction for galaxies with \logmtot{}$>11.6$ and \logmh$<14.0$ haloes.
 

### 2017-09-17 draft/paper1_v14.tex
For referee report

--- 2017-07-03 draft/paper1_v13.tex
@@
 % Version 13; MNRAS format; Edited by KB
+% Version 14; MNRAS format; Edited by SH, response to referee report
 
@@
     $i$-band), we present a systematic study of the stellar halos of a sample of more 
-    than $7000$ galaxies at $0.3 < z < 0.5$ with $log M_{\star}/M_{\odot} > 11.4$. 
+    than $7000$ galaxies at $0.3 < z < 0.5$ with $\log M_{\star}/M_{\odot} > 11.4$. 
     Our study is based on high-quality (0.6\asec\ seeing) imaging data from the Hyper 
@@
 
-    % TODO: Move this to Paper II
-    %To ensure a clean separation in \mhalo{}, here we only focus on the central 
-    %galaxies of clusters with $\lambda > 30$. 
-    %According to \citet{Simet2016}, this $\lambda \geq 30$ sample should correspond to 
-    %$M_{\mathrm{halo}}>10^{14.2} M_{\odot}$. 
-    %We have checked that none of the results in this work depend on the choice of this 
-    %$\lambda$ limit.
-
-    %The median $\lambda$ of the clusters associated with the \rbcg{} sample is 
-    %${\sim} 41$, corresponding to halo mass of 
-    %$M_{\mathrm{halo}}{\sim} 2.2\times 10^{14}$ $h^{-1}$ $M_{\odot}$.
-    %Only 44 centrals from the \rbcg{} sample live in clusters with $\lambda \geq 50$
-    %($M_{\mathrm{halo}} {\sim} 3.0\times 10^{14}$ $h^{-1} M_{\odot}$). 
-    %Our \rbcg{} sample therefore corresponds to galaxies in moderate mass halos.
-
     After matching the \texttt{hscZ} sample with the central galaxies of \redm{} 
@@
     $0.3 < z < 0.5$. 
-    At $z\geq0.33$, it starts to miss a small fraction of clusters with $\lambda < 30$, 
+    At $z \geq 0.33$, it starts to miss a small fraction of clusters with $\lambda < 30$, 
     but the main results of this work will not be affected by this.

### 2017-10-16 draft/paper1_v14.tex
For referee report

@@
 % Commenting:
-\newcommand{\xxx}[1]{\textcolor{red}{\textbf{XXX}}}
 \newcommand{\todo}[1]{\textcolor{red}{\textbf{TODO:~#1}}}
@@
 \newcommand{\note}[2]{\textcolor{blue}{\textbf{[Comment (#1): #2]}}}
-\newcommand{\song}[1]{\textcolor{magenta}{\textbf{[Song: #1]}}}
+\newcommand{\song}[1]{\textcolor{cyan}{\textbf{#1}}}
 \newcommand{\alexie}[1]{\textcolor{blue}{\textbf{[Alexie: #1]}}}
@@
 
-    Massive galaxies display extended light profiles that can reach several 
-    hundreds of kilo parsecs. 
-    These stellar halos provide a fossil record of galaxy assembly histories. 
-    Using data that is both wide (${\sim}100$ deg$^2$) and deep ($>28.5$ \sb{} in 
-    $i$-band), we present a systematic study of the stellar halos of a sample of more 
-    than $7000$ galaxies at $0.3 < z < 0.5$ with $\log M_{\star}/M_{\odot} > 11.4$. 
-    Our study is based on high-quality (0.6\asec\ seeing) imaging data from the Hyper 
-    Suprime-Cam (HSC) Subaru Strategic Program (SSP), which enables us to individually 
-    estimate surface mass density profiles to 100 kpc without stacking. 
-    As in previous work, we find that more massive galaxies exhibit more extended outer 
-    profiles.  
-    When this extended light is not properly accounted for as a result of shallow imaging 
-    or inadequate profile modeling, the derived stellar mass function can be 
-    significantly underestimated at the highest masses.  
-    Across our sample, the ellipticity of outer light profiles increases substantially 
-    as we probe larger radii.  
+    \song{
+    The stellar halo of massive galaxy can extend to several hundreds of kilo 
+    parsecs and provide important fossil record of galaxy assembly.
+    Using the wide (${\sim}100$ deg$^2$) and deep ($>28.5$ \sb{} in $i$-band) images 
+    from the Hyper Suprime-Cam (HSC) Subaru Strategic Program (SSP), we study 
+    the stellar halos of a sample of $\sim7000$ massive galaxies at 
+    $0.3 < z < 0.5$ with $\log M_{\star}/M_{\odot} > 11.4$ by tracing their  
+    surface mass density profiles to 100 kpc individually. 
+    The stellar halo of massive galaxy exhibit higher intrinsic diversity in their 
+    outer surface density profile and higher ellipticity than the inner region. 
+    We find that more massive galaxy on average shows more prominent outer stellar 
+    halo with shallower surface density profiles.
     We show for the first time that these ellipticity gradients steepen dramatically as 
     a function of galaxy mass, but we detect no mass-dependence in outer color gradients.
+    }
     Our results support the two-phase formation scenario for massive galaxies in which 
     outer envelopes are built up at late times from a series of merging events.
-    We provide surface mass surface mass density profiles in a convenient tabulated format 
-    to facilitate comparisons with predictions from numerical simulations of 
-    galaxy formation.
+    \song{
+    These results also emphasize the importance of accounting for the the extended 
+    stellar halos of massive galaxies when estimating their stellar masses. 
+    Shallow image or inadequate profile model often leads to significantly 
+    underestimated masses.
+    We provide surface mass surface mass density profiles to facilitate comparisons 
+    with predictions from hydrodynamic simulations and other observations.
+    }
 
@@
             The HSC \texttt{WIDE} layer is $3.0$-$4.0$ magnitudes deeper than SDSS.
-            This added depth is critical in order map the outskirts of ETGs out to 
-            large radii.
+            %This added depth is critical in order map the outskirts of ETGs out to 
+            %large radii.
             }
@@
 
-    Simulations of structure formation within the context of the $\Lambda$-CDM 
-    cosmological model make predictions for the hierarchical growth of dark matter 
-    halos and galaxies (e.g. \citealt{Baugh1996, DeLucia2006}), but there are many 
-    open questions regarding the star-formation history, mass assembly process, and 
-    structural evolution of massive galaxies. 
-    Massive galaxies are thought to grow according to a ``two-phase'' formation 
-    scenario (e.g. \citealt{Oser2010, Oser2012}). 
-    In this scenario, the progenitors of $z{\sim} 0$ massive early-type galaxies 
-    (ETGs) undergo a rapid growth phase at $z{\sim} 2$ triggered either by disk 
-    instabilities or gas-rich mergers (e.g. \citealt{Hopkins2008, Dekel2009}). 
-    Observationally, the progenitors of ETGs are thought to correspond to the 
-    population of massive quiescent galaxies at high redshift that have smaller 
-    average effective radii ($R_{\mathrm{e}}$; e.g. \citealt{Trujillo2006, 
-    vanDokkum2008, Cimatti2008}).  
-    These high redshift galaxies also have slightly higher central velocity dispersions 
-    and stellar mass densities (\mden{}; e.g. \citealt{vandeSande2011, Belli2014}), 
-    and more disk-like morphologies (e.g. \citealt{vanderWel2011}) than low redshift 
-    galaxies (e.g. \citealt{Bezanson2009, vanDokkum2010}) with similar stellar mass.
-
-    Following the initial phase of growth, feedback from stars and/or AGN 
-    (e.g. \citealt{Sijacki2007, Fabian2012}) efficiently quenches star formation in 
-    massive galaxies. 
-    A large fraction of these massive progenitors are already quiescent by $z=1$ 
-    (e.g. \citealt{Bezanson2009, Kriek2016}). 
-    The second phase of their assembly is driven by non-dissipative processes such 
-    as dry mergers with other galaxies (e.g. \citealt{Naab2006, Khochfar2006}). 
-    The ``two-phase'' formation of massive galaxies help explain both the 
-    observed increase in the effective radii ($R_{\mathrm{e}}$) of massive galaxies 
-    (e.g. \citealt{Newman2012, vdWel2014}) and the build-up of stellar 
-    halos  (e.g. \citealt{Szomoru2012, Patel2013}). 
-    It also posits that minor mergers dominate the mass assembly 
-    of massive galaxies at late times 
+    \song{
+    Massive early-type galaxies (ETGs) are predicted to assemble according to a 
+    ``two-phase'' formation scenario 
+    (e.g. \citealt{Oser2010, Oser2012}): A rapid growth phase at high-redshift that 
+    is dominated by intense dissipative \textit{in situ} star formation (e.g.
+    \citealt{Hopkins2008, Dekel2009}), and a second phase that 
+    is driven by non-dissipative processes such as dry mergers 
+    (e.g. \citealt{Naab2006, Khochfar2006}), especially the minor ones 
     (e.g. \citealt{Hilz2012, Hilz2013, Oogi2013, Bedorf2013, Laporte2013}).
-
-    Both numerical simulations (e.g. \citealt{Oser2010}) and 
-    semi-analytic models (SAM; e.g. \citealt{LeeYi2013, LeeYi2017}) agree that the 
-    mass fraction in the accreted component should increase with total galaxy stellar 
-    mass (e.g. \citealt{Lackner2012, Cooper2013, Qu2017}).
+    Both numerical simulations (e.g. \citealt{Oser2010}) and semi-analytic models 
+    (SAM; e.g. \citealt{LeeYi2013, LeeYi2017}) agree that the fraction of stellar 
+    mass accreted in the second phase (\textit{ex situ} component) should increase 
+    with total galaxy stellar mass (e.g. \citealt{Lackner2012, Cooper2013, Qu2017}).
+    }
     For instance, recent results from the 
@@
 
-    Given the success of this two-phase scenario in explaining trends like overall size 
-    growth, it is time to confront this model with additional observations, 
-    in particular, the detailed surface mass density profiles of low redshift massive 
-    galaxies. 
+    \song{
+    Given the success of the ``two-phase'' scenario in explaining the properties of 
+    high-$z$ massive quiescent galaxies (e.g. \citealt{vanDokkum2010, vanderWel2011,
+    vandeSande2011, Belli2014}) and the dramatic increase of their effective radii 
+    ($R_{\mathrm{e}}$; e.g. \citealt{Newman2012, vdWel2014}), it is time to confront 
+    this model with additional observations, in particular, the detailed surface 
+    mass density profiles of low redshift massive galaxies. 
+    }
     Early studies based on one-dimensional light profiles found that the surface 
@@
     Iodice2017}).
-
-    Until now, studies of the surface brightness or mass density profiles of massive 
-    galaxies have been either conducted using large samples but with shallow imaging, 
-    for example the Sloan Digital Sky Survey (SDSS; e.g. \citealt{SDSSDR7, SDSSDR12}), 
-    or with deeper imaging but much smaller sample sizes (e.g \citealt{Gonzalez2005, 
-    Capaccioli2015}). 
-    In this paper, we take advantage of new high-quality (median seeing of
-    FWHM${\sim} 0.6^{\arcsec}$ in $i$-band) and deep ($i$-band surface brightness 
-    limit $> 28.5$~\sb) images from the Hyper Suprime-Cam (HSC) Subaru Strategic 
-    Program \citep[SSP,][]{HSCDR1} to characterize the light profiles of massive 
-    galaxies out to 100 kpc. 
-    The deep imaging depth and excellent seeing conditions of HSC images make them 
-    ideal for mapping the \mstar{} distributions of massive galaxies out to very 
-    large radii. 
+    \song{
+    Until now, deep \mden{} profiles of massive galaxies are rarely available. 
+    Even in the nearby universe, it is not trivial to map the low surface
+    brightness outskirts of massive galaxies (e.g., 
+    \citealt{Capaccioli2015, Iodice2016, Iodice2017, Spavone2017, Mihos2017}). 
+    Some of these measurements are based on image stacking method (e.g. 
+    \citealt{Tal2011, dSouza2015}) that suffers from several systematics. 
+    The number of very massive galaxies is also very limited in the local universe.
+    For example, according to the \texttt{MASSIVE} survey (\citealt{Ma2014}), there
+    are only $\sim 60$-70 massive galaxies with \logms$> 11.6$ (based on K-band 
+    luminosity) within 108 Mpc.
+    }
+
+    \song{
+    Besides the mass density profiles, the radial profile of ellipticity also 
+    contains information about the 3-D geometry (e.g. \citealt{Tremblay1995, 
+    Tremblay1996, Chang2013, RodriguezPadilla2013, Mitsuda2017}) and kinematics 
+    (e.g. \citealt{Cappellari2012, Weijmans2014}) of stars in massive galaxies. 
+    The elliptical profiles of massive galaxies have not been carefully studied 
+    out to large radius except for few works using either image stacking method
+    (e.g. \citealt{Tal2011, dSouza2015}) or small sample of nearby galaxies 
+    (e.g. \citealt{Spavone2017}). 
+    }
+
+    \song{
+    In this paper, we take advantage of the high--quality and deep images from the 
+    Hyper Suprime-Cam (HSC) Subaru Strategic Program \citep[SSP,][]{HSC-DR1} 
+    (see \S~\ref{ssec:hsc} for details) to characterize the light profiles of 
+    massive galaxies out to 100 kpc. 
+    }
     We select a large sample (${\sim} 7000$) of massive central galaxies 
     at $0.3 < z < 0.5$ using ${\sim} 100$ deg$^2$ of data from the HSC wide layer.
-
- %       With the help of reliable spectroscopic and photometric redshift 
- %   (e.g. the ones for \redm{} clusters, \citealt{Rykoff2014}; \citealt{Rozo2015b}),
- %   we select a large sample (${\sim} 7000$) of massive central galaxies at 
- %   $0.3 < z < 0.5$ using ${\sim} 100$ deg$^2$ of data from the HSC wide layer.
 
@@
     distribution.
-
-    % In practice, reliable isolation of a physically meaningful ICL component using 
-    % photometry alone is extremely difficult, if not impossible. 
-    % More importantly, the majority of massive galaxies in our samples are not considered 
-    % as the BCG of a cluster (\mhalo{}$\simgt 10^{14}M_{\star}$) \alexie{CHECK}. 
-    % Only a small fraction of the BCGs in the \rbcg{} sample belong to very 
-    % massive clusters where the strongest photometric evidence of an ICL component is 
-    % often found (\mhalo{}$\simgt 10^{15}M_{\star}$, e.g. \citealt{Presotto2014, 
-    % Burke2015}). 
-    % The virgo cluster is a good  local analog of the typical galaxy in our sample.
-
-    % Ultra-deep images show that the stellar halo of the BCG smoothly extends beyond 
-    % 100 kpc, while the ICL only becomes important outside that radius and is dominated 
-    % by many individual tidal features (e.g. \citealt{Mihos2016}).
-    % Therefore, it is highly unlikely that out main results are driven by the ICL 
-    % component.
-
-    % At the imaging depth of HSC and out to 100 kpc, the \mden{} profiles of massive 
-    % galaxies vary smoothly and we find no evidence for a distinctive ICL component. 
-    % Although the rising stellar velocity dispersion in the outskirt of massive BCG
-    % has been used as evidence of a kinematically separated ICL component (e.g. 
-    % \citealt{Dressler1979, Carter1999, Kelson2002, Bender2015, Longobardi2015}), 
-    % we think it is reasonable to treat the stellar halo of BCG and potential ICL as 
-    % an integrated component. 
-    % They both carry important information regarding the assembly of central galaxy 
-    % and its dark matter halo. 
-    % In recent years, we can start to investigate the origin and evolution of ICL using 
-    % simulations where physical separation of ICL is possible
-    % (e.g. \citealt{SommerLarsen2005, Murante2007, Martel2012, Cui2014, Cooper2015, 
-    % Harris2017}). 
-    % It will be interesting to perform detailed comparisons between these simulations 
-    % and deep HSC observations to look into the contributions from different stellar 
-    % components to the halo of massive galaxy.
 
@@
 
-    The Subaru Strategic Program (SSP, \citealt{HSC_SSP, HSC_DR1}) makes use of the 
+    The Subaru Strategic Program (SSP, \citealt{HSC-SSP, HSC-DR1}) makes use of the 
     new prime-focus camera, the Hyper Suprime-Cam (HSC;~\citealt{Miyazaki2012}, 
@@
     The regions covered by this release overlap with a number of spectroscopic surveys 
-    (e.g.\ SDSS/BOSS: \citealt{Eisenstein2011}, \citealt{Alam2015}; 
+    (e.g.\ SDSS/BOSS: \citealt{Eisenstein2011}, \citealt{SDSS-DR12}; 
     GAMA: \citealt{Driver2011}, \citealt{Liske2015}).
     \texttt{S15B} release has similar sky coverage with the Public Data Release 1
-    (Please see Table 3 in \citealt{HSC_DR1} for detailed comparison).
+    (Please see Table 3 in \citealt{HSC-DR1} for detailed comparison).
 
@@
 
-    The full details of the HSC data processing can be found in \citet{Bosch2017}
+    The full details of the HSC data processing can be found in \citet{HSC-PIPE}
     and are briefly summarized here. 
@@
     For each galaxy, \texttt{hscPipe} measures a \cmodel{} magnitude using an approach 
-    that is similar to SDSS (\citealt{Bosch2017}). 
+    that is similar to SDSS (\citealt{HSC-PIPE}). 
     However, as opposed to SDSS, the HSC \cmodel{} is based on forced multi-band 
@@
     under-estimation of the total flux of massive ETGs (this is discussed further in 
-    \citealt{Bosch2017}).  
+    \citealt{HSC-PIPE}).   
     For these reasons, our results will be based on custom-developed code to measure 
@@
     We also limit our sample to regions that have reached the required depth of 
-    the \texttt{WIDE} survey in $i$-band as defined in \citet{HSC_DR1}.
+    the \texttt{WIDE} survey in $i$-band as defined in \citet{HSC-DR1}.
     %% The SQL search is saved as "sample.sql" 
@@
     It is created by matching HSC objects with a series of publicly available 
-    spectroscopic redshifts (e.g.\ SDSS DR12 \citealt{SDSSDR12}; 
+    spectroscopic redshifts (e.g.\ SDSS DR12 \citealt{SDSS-DR12}; 
     GAMA DR2 \citealt{Liske2015}). 
@@
     flag that indicates secure redshifts.
-    Please see \S~4.4.2 of \citet{HSC_DR1} for details of this catalog.  
+    Please see \S~4.4.2 of \citet{HSC-DR1} for details of this catalog.  
     To ensure reasonable \mstar{}-completeness at the high-\mstar{} end we focus on
@@
     out to $100$ kpc on a galaxy-by-galaxy basis (no stacking). 
+    \song{
+    The 1-D method fails to extract profiles for ${\sim}10$\% of the sample due 
+    to severe contamination of other objects, they are excluded from the analysis.
+    }
     For more technical details of the \texttt{Ellipse} procedure, please see 
@@
 %% ------------------------------------------------------------------------------------ %%
-
-    We cannot extract reliable 1-D profiles for a small fraction of massive galaxies 
-    because they are heavily masked out for either physical 
-    (e.g.\ late-stage major merger) or nuisance (e.g.\ nearby foreground 
-    galaxy or bright star) reasons. 
-    This is an intrinsic limitation of the 1-D method, and it removes ${\sim}10$\% of 
-    the sample.
-    %It affects $18/164$ of the \rbcg{} sample, and a smaller fraction of the 
-    %\nbcg{} sample. 
-    We visually examine the 3-color images of randomly selected galaxies with failed 
-    1-D profiles.  
-    Most of them are relative small galaxies that are severely contaminated by nearby 
-    objects, and will not affect the results of this work.  
-    Meanwhile, it is worth noting that this does exclude most major merging systems 
-    among massive galaxies.
 
@@
     5-band HSC \cmodel{} fluxes.
+    \song{
+    \texttt{iSEDFit} uses a simplified Bayesian approach to estimate the 
+    posterior probability distribution functions (PDF) of key stellar population
+    parameters.
+    }
     Although \cmodel{} tends to underestimate the total fluxes of bright, extended 
@@
     (e.g. \citealt{SynPipe}).
-
-    \texttt{iSEDFit} takes a simplified Bayesian approach. 
-    In short, it first generates a large grid of SEDs from synthetic stellar 
-    population models by drawing randomly from the prior distributions of relevant
-    parameters (e.g. age, metallicity, dust extinction, and star formation history).
-    Based on these models, it uses the observed photometry and redshift to compute 
-    the statistical likelihood, and generates the posterior probability distribution 
-    functions (PDF) for each parameter.  
-    To get the best estimate of a given parameter, \texttt{iSEDFit} integrates the 
-    full PDF over all the other nuisance parameters.
-    Then, the median value and the 1-$\sigma$ uncertainty are derived based on the 
-    marginalized PDF. 
-    Please refer to \citet{Moustakas13} for technical details.
 
@@
 
-	With \mstar{} estimates in hand, we now use the \redm{} galaxy cluster catalog to  
-	create a sample of massive central galaxies. 
-	The ``central'' galaxy is defined as the galaxy that lives in the 
-	center of its own dark matter halo.  
-	In contrast, a galaxy in a sub-halo that is orbiting within the virial radius of a 
-	more massive halo is referred to as a ``satellite''. 
-	To better understand the connection between the structures of massive 
-	galaxies and the assembly history of both their stars and dark matter halos, we 
-	wish to focus on central galaxies in this work.
-
 \subsection{Candidate massive central galaxies}
@@
 
-    Although the central galaxies of dark matter halos have unique importance is 
-    studying galaxy-halo connection, robust identification of central galaxy is 
-    not easy(e.g.\citealt{Yang2007}) in observation.
-    First, based on previous results (\citealt{Reid2014, Hoshino2015, Saito2016}),
-    the satellite fraction at \logmtot{}$> 11.6$ should become quite low 
-    ($\sim 10$\% level). 
-    And, we can further use the \redm{} catalog to identify and exclude massive 
-    satellites in cluster-level dark matter halos--to further reduce contamination
-    from satellite galaxies.
-
-    We use \texttt{v5.10} of the \redm{} cluster  catalog
-    (e.g.\ \citealt{Rykoff2014}; \citealt{Rozo2015b}). 
-    These authors have developed a well-tested red-sequence cluster finder that has 
-    been run on SDSS DR8 (\citealt{SDSSDR8}) images. 
-    For each cluster, the catalog provides a photometric redshift ($z_{\lambda}$), a 
-    cluster richness ($\lambda$), and identifies the most likely central galaxy (the 
-    galaxy with the highest $P_{\mathrm{Cen}}$ value). 
-    The \redm{}{} catalog also provides a list of member galaxies for each cluster and 
-    their associated membership probabilities. 
-    Details about the performance of the \redm{}~cluster catalog can be found in 
-    \citet{Rozo2014}, \citet{Rozo2015a}, and \citet{Rozo2015b}.
-
-    Several studies have published calibrations between the \redm{}~richness estimate, 
-    $\lambda$, and halo mass (e.g.\ \citealt{Saro2015, Farahi2016, Simet2016, 
-    Melchior2016}). 
-    All these studies consistently find that \redm{} clusters with $\lambda > 20$ 
-    generally have $\log (M_{\mathrm{halo}}/M_{\odot}) \geq 14.0$, although the scatter 
-    of \mhalo{} at fixed $\lambda$ cannot be ignored.
-    Therefore the central galaxies of these \redm{} clusters\footnote{We only use 
-    central galaxies with $P_{\mathrm{CEN}} \geq 0.7$} form a sample of massive central 
-    galaxies that live in massive halos as described above.
-    Such information is also very useful in studying the relationship between galaxy
-    structure and environment (Huang\etal in prep.).
-
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %% 
-%\subsection{Massive Central Galaxies in Low and High Mass Halos}
-%    \label{ssec:mass_central}
-
-    %One of the goals of our work is to investigate the halo dependence of the outer 
-    %envelope. Although there is a correlation between $M_{\star}$ and $M_{\mathrm{Halo}}$,
-    %based on recent constraints of $M_{\star}$-$M_{\mathrm{Halo}}$ relation 
-    %(e.g.\ \citealt{Leauthaud2012}, \citealt{Behroozi2013}, \citealt{Kravtsov2014}), 
-    %even though our sample selects very massive galaxies (\logms{}$\geq 11.5$), they 
-    %With the help of the \redm{} catalog, we can broadly separate our sample into two
-    %groups with \logmh{}$<14.0$ and \logmh{}$>14.2$.
-    %live in a fairly broad range of halos masses.
-
-    % We match this sample with the central galaxies of \redm{}~catalogs using a 
-    % $1.0^{\arcsec}$ radius, and it results in 704 galaxies.  
-    %% Saved as "dr1_redbcg_hsc_sdss_gama_1arcsec.fits"
-
+    \song{
+    Typically, ``central'' galaxy is defined as the galaxy locates in the center of 
+    its own dark matter halo, while the galaxy in a sub-halo that is orbiting within 
+    the virial radius of a more massive halo is referred to as a ``satellite'' 
+    (e.g.\citealt{Yang2007}).
+    We wish to focus on massive central galaxies here as they are uniquely important 
+    to the study of galaxy--halo connection.
+    Although the satellite fraction is expected to be very low ($<10$\%; e.g. 
+    \citealt{Reid2014, Hoshino2015, Saito2016}) at \logmtot{}$> 11.6$, we further use 
+    the \redm{} cluster catalog (\texttt{v5.10}; e.g.\ \citealt{Rykoff2014}; 
+    \citealt{Rozo2015b}) based on SDSS DR8 (\citealt{SDSS-DR8}) to help us 
+    identify centrals of cluster--level dark matter halos and reduce satellite
+    contamination.
+    }
+
+    \song{    
     After matching the \texttt{hscZ} sample with the central galaxies of \redm{} 
-    clusters with $\lambda \geq 20$ and $P_{\mathrm{Cen}} \geq 0.7$, we find 164 
-    matched galaxies at $0.3 \leq z \leq 0.5$.
-    This sample of \textbf{central galaxies in more massive halos} will be referred to 
-    as the \rbcg{} sample. 
-    It is also worth pointing out that, due to the depth and resolution of SDSS 
-    images, this \redm{} catalog is not complete down to $\lambda=20$ at 
-    $0.3 < z < 0.5$. 
-    At $z \geq 0.33$, it starts to miss a small fraction of clusters with $\lambda < 30$, 
-    but the main results of this work will not be affected by this.
-    %% Saved as "dr1_redbcg_use_sed5b.fits"
-
-    As a next step, we want to construct a sample of central galaxies living in halos 
-    with \logmh{}$<14.0$. 
-    To achieve this, we identify and remove all galaxies within a cylindrical region 
-    around all \redm{} clusters. 
+    clusters with richness $\lambda \geq 20$\footnote{Due to the depth and 
+    resolution of SDSS images, the \redm{} catalog is not complete down to 
+    $\lambda=20$ at $0.3 < z < 0.5$.  
+    At $z \geq 0.33$, it starts to miss a small fraction of clusters with 
+    $\lambda < 30$, but it will not affect the results in this work.}
+    and central probability $P_{\mathrm{Cen}} \geq 0.7$, we find 164 matched galaxies 
+    at $0.3 \leq z \leq 0.5$.
+    According to available calibration (e.g.\ \citealt{Saro2015, Farahi2016, 
+    Simet2016, Melchior2016}), they represent the central galaxies in dark matter 
+    halos with $\log (M_{\mathrm{halo}}/M_{\odot}) \geq 14.0$, and will be 
+    referred to as the \rbcg{} sample. 
+    }
+
+    \song{
+    As the next step, we identify and remove all galaxies within a cylindrical 
+    region around all \redm{} clusters. 
     We use a radius equal to $R_{\mathrm{200b}}$ and the length of the cylinder is 
-    set to twice the value of the photometric redshift uncertainty of each cluster.
-
-    We convert $\lambda$ of each cluster to $M_{\mathrm{200b}}$ using the calibration 
-    of \citet{Simet2016} and we use the mass-concentration relation from 
-    \citet{Diemer2015} to compute $R_{\mathrm{200b}}$. 
-    At $0.3 < z < 0.5$, the uncertainty of photo-$z$ is between 0.015 to 0.025, and 
-    is enough to exclude cluster members.
-
+    set to twice the value of the photometric redshift ($z_{\lambda}$) uncertainty 
+    of each cluster\footnote{We convert $\lambda$ of each cluster to 
+    $M_{\mathrm{200b}}$ using the calibration of \citet{Simet2016} and use the 
+    mass-concentration relation from \citet{Diemer2015} to compute 
+    $R_{\mathrm{200b}}$.}.
     After removing galaxies associated with \redm{} clusters, the remaining galaxies 
     in our sample will be dominated by central galaxies living in halos with 
-    \logmh{}$< 14.0$. 
-    We will refer to this sample of \textbf{galaxies in less massive halos} as the 
-    \nbcg{} sample. 
-    Because we have rejected satellites in \redm{} clusters, and because above our 
-    galaxy mass cut most satellites reside in halos with 
-    \logmh$>14.0$ (e.g. \citealt{Reid2014, Hoshino2015, Saito2016, vanUitert2016}), 
-    galaxies in the \nbcg{} sample should  be dominated by central galaxies.
+    \logmh{}$< 14.0$, and they will be referred to as the \nbcg{} sample.
     Using the model presented in \citet{Saito2016}, we estimate that in dark matter 
@@
     satellites.
-    This confirms that our sample should have low enough satellite contamination 
-    so that it can be taken as representative massive central galaxies.     
+    }
+    %% Saved as "dr1_redbcg_use_sed5b.fits"  
     %% Saved as "dr1_nonbcg_use_sed5b.fits"
@@
 
-        \item The SMF derived from a SDSS-\textit{GALEX} sample of $z{\sim} 0.1$ 
-            galaxies by \citet{Moustakas13}. 
-            Total luminosities in \citet{Moustakas13} are based on SDSS \cmodel{} 
-            magnitudes. 
-            They use a \m2l{} that is derived via SED fitting using \texttt{iSEDfit} 
-            with similar assumptions as the ones adopted here.
-
-        \item The observed SMF for $z{\sim} 0.1$ SDSS galaxies from \citet{Bernardi2017}.          
-            Total luminosities in \citet{Bernardi2017} are based on 2-D \texttt{SerExp} 
-            models (\ser{}$+$ Exponential disk model; integrated to infinity) that 
-            recover more flux compared to SDSS \cmodel{} magnitudes 
-            (\citealt{Bernardi2013, Meert2015}). 
-            They use a \m2l{} that is adopted from the SED fitting results in
-            \citet{Mendel2014}. 
-            This model also uses the \texttt{FSPS} stellar population model 
-            \citep{FSPS}, assumes a \citet{Chabrier2003} IMF, and considers dust 
-            extinction using the \citet{Calzetti2000} extinction law (the 
-            ``dusty'' model).
+        \item \song{
+            The SMF for SDSS-\textit{GALEX} sample at $z{\sim} 0.1$ using SDSS \cmodel{}
+            photometry and \texttt{iSEDfit} stellar mass based on similar assumptions 
+            (see \citet{Moustakas13} for details). 
+            }
+
+        \item \song{
+            The SMF for $z{\sim} 0.1$ SDSS galaxies using 2-D \texttt{SerExp} 
+            models\footnote{\ser{}$+$ Exponential disk model that can recover more 
+            lights than SDSS \cmodel{}; integrated to infinity.}
+            (\citealt{Bernardi2013, Meert2015}) and stellar mass by 
+            \citet{Mendel2014}\footnote{Use \texttt{FSPS} model, 
+            \citet{Chabrier2003} IMF, and \citet{Calzetti2000} extinction law}.
+            (see \citet{Bernardi2017} for details).
+            }
 
@@
     profiles with results from previous work. 
-    Deep \mden{} profiles of massive galaxies are rarely available. 
-    Even in the nearby universe, it is not trivial to map the low surface
-    brightness outskirts of massive galaxies (e.g., 
-    \citealt{Capaccioli2015, Iodice2016, Iodice2017, Spavone2017, Mihos2017}). 
-    The number of very massive galaxies is also very limited in the local universe.
-    For example, according to the \texttt{MASSIVE} survey (\citealt{Ma2014}), there
-    are only $\sim 60$-70 massive galaxies with \logms$> 11.6$ (based on K-band 
-    luminosity) within 108 Mpc.
-
     Most previous studies have focused on surface brightness profiles instead 
@@
     the radial range of overlap (out to 50 kpc). 
-    CGS images are deeper than SDSS images in the $r$-band, but the median 
-    profiles from \citet{Huang2013a} still only reach to ${\sim} 50$ kpc for 
-    $z<0.02$ massive galaxies.
-    Meanwhile, our deep HSC images can reliably deliver individual \mden{} profiles 
-    for $z{\sim} 0.4$ galaxies out to at least 100 kpc.
+    \song{
+    The median profiles from \citet{Huang2013a} only reach to ${\sim} 50$ kpc for 
+    $z<0.02$ massive galaxies, while our deep HSC images can reliably deliver 
+    individual \mden{} profiles for $z{\sim} 0.4$ galaxies out to at least 100 kpc.
+    }
 
@@
     prominent stellar halo and has much shallower outer slope compared to our data.
-    In future work, we will compare our HSC profiles with predictions from more 
-    advanced hydrodynamic simulations such as \textit{Horizon-AGN} (\citealt{Dubois2014}) 
-    and MassiveBlackII (\citealt{Khandai2015}). 
-    These data will help fine-tune simulations and to understand the physical mechanisms 
-    that drive the assembly of massive galaxies and the build up of stellar halos.
 
@@
 %% ------------------------------------------------------------------------------------ %%
-	%Aforementioned results only use the 1-D \mden{} profiles that are baed on single 
-	%band image and the flux-weighted isophotal shape, while more useful information 
-	%can be gathered from the HSC images of these massive galaxies.
-    So far, we have focused on 1-D \mden{} profiles. 
-    We now consider ellipticity and $k$-corrected optical color profiles.
-	We extract ellipticity profiles using \texttt{Ellipse} by leaving the shape of 
-	each isophote as a free parameter. 
-	We also apply the isophotal information derived in the $i$-band directly to other 
-	filters and extract 1-D $g-r$ and $g-i$ color profiles.
-	We apply the Galactic extinction correction and the \texttt{iSEDFit} $k$-correction 
-	to the color profiles. 
+
+    \song{
+    Now, we look into the ellipticity profile derived by \texttt{Ellipse} in $i$-band 
+    and the $g-r$ and $g-i$ color profiles (Galactic extinction and $k$-corrected). 
+    }
 	Smearing effect of seeing will make the central isophotal shape rounder than the 
@@
 
-	The ellipticity of the isophotes contains information about the 3-D geometry 
-	(e.g. \citealt{Tremblay1995, Tremblay1996, Chang2013, RodriguezPadilla2013, 
-	Mitsuda2017}) and kinematics (e.g. \citealt{Cappellari2012, Weijmans2014}) of 
-	stars in massive galaxies.  
 	The left panel of Fig \ref{fig:ell_color} shows the ellipticity profiles of 
@@
 
-	This is consistent with studies of nearby massive galaxies, both from 1-D 
-	ellipticity profiles and 2-D modeling results \citep{Porter1991, Gonzalez2005, 
-	Zibetti2005, Spavone2017, Huang2013a, Oh2017}. 
+	This is consistent with studies of nearby massive galaxies using different
+	methods (e.g. \citep{Porter1991, Gonzalez2005, Zibetti2005, Huang2013a, Oh2017}). 
+	\song{
+	For instance, \citet{Spavone2017} uses very deep images of 6 nearby massive 
+	galaxies to show that their average ellipticity in $g$-band also increases with 
+	radius in a similar fashion.
+	}
 	However, to the best of our knowledge, our HSC results are the first to show 
@@
 
-    % TODO: Move to Paper II
-    %By using deep imaging from the HSC survey we have shown that the stellar mass 
-    %density profiles of massive central galaxies depend systematically on the mass 
-    %of their host dark matter halos.
-
 %% ------------------------------------------------------------------------------------ %% 
@@
 
-    %The mass-dependent nature we find in the \mden{} and ellipticity profiles of 
-    %massive galaxies are consistent with the two-phase formation scenario. 
     We find that the outer halos of massive elliptical galaxies grow more prominent 
@@
 
-    Recent hydrodynamic simulations of galaxy formation often separate stars in 
-    galaxies into \textit{in situ} and \textit{ex situ} components. 
-    In simulations, the \textit{in situ} component is often defined as the stars 
-    formed in the halo of the ``main progenitor''.  
-    The spatial distribution, kinematic, and stellar population properties of both 
-    components are important theoretical predictions. 
-    Among various predictions, the faction of \textit{ex situ} stars and the scaling 
-    of the \textit{ex situ} fraction with stellar mass is perhaps the first aspect to 
-    test. 
-    However, on the observational side, there is no straightforward way to actually
-    disentangle these two components for massive galaxies. 
-    Disk galaxies are more easily decomposed into multiple components and recently, 
-    deep surveys of nearby disk galaxies have started to provide constraints on 
-    their stellar halos (e.g. \citealt{Courteau2011, Merritt2016, 
+    \song{
+    As mentioned in \S~\ref{sec:intro}, hydrodynamic simulations often predict that 
+    the faction of \textit{ex situ} stars increase with total stellar mass.
+    However, it is still extremely difficult to separate the \textit{in situ} and
+    \textit{ex situ} components observationally, despite that it is the most 
+    important theoretical prediction to be verified. 
+    }
+
+    \song{
+    Recent deep surveys of nearby disk galaxies have started to provide constraints 
+    on their stellar halos (e.g. \citealt{Courteau2011, Merritt2016, 
     Harmsen2017})\footnote{Although it is still not certain that all stellar halos
-    around disk galaxies are made out of \textit{ex situ} stars.}.
-
-    For more massive ETGs, results so far mainly depend on multi-component model 
-    fitting and image stacking analyses (e.g. \citealt{Huang2013a, DSouza2014,
-    Spavone2017}).
+    around disk galaxies are made out of \textit{ex situ} stars.} as it is
+    relatively easier to decompose the stellar halo component. 
+    As for massive ETGs, limited observational constraints still mainly depend on 
+    multi-component model fitting and/or image stacking analyses 
+    (e.g. \citealt{Gonzalez2007, Huang2013a, DSouza2014, Spavone2017}).
+    }
     In this work, we propose that \mstar{} computed within different fixed physical
@@
     Qu2017}). 
-    In future work, we will explore more detailed comparisons between our data and
-    predictions from hydrodynamic simulations and we will investigate to what degree 
-    simple elliptical aperture masses may be used to trace \textit{ex situ} fractions.
-
-    % TODO: Move to Paper II
-    %Meanwhile, these simulation also point out that the fraction of accreted stars 
-    %increases steeply with total \mstar{} and that the ``ex-situ'' component
-    %starts to dominate the \mden{} profiles around $R_{\mathrm{e}}$ for 
-    %\logms{}$\geq 11.5$ galaxies. 
-    %In this work, we find that the median \mden{} profiles of \rbcg{} and \nbcg{} 
-    %samples start to show differences around 15-20 kpc, which is close to 
-    %their $R_{\mathrm{e}}$. 
-    %Furthermore, the environmental dependence of our median \mden{} profiles 
-    %becomes more significant in our highest \mtot{} bin (see Fig \ref{fig:prof_4}). 
-    %These results all align with the picture that the \mhalo{}-dependence of the 
-    %\mden{} profiles of massive galaxies is driven by the variations in the 
-    %``ex-situ'' component at large radii.
-
-    How well justified is our choice of \minn{} as a proxy of the \textit{in-situ} 
-    component?  
-    A full investigation is beyond the scope of this paper. 
-    Here we simply present comparisons between our profiles and  
-    a) several estimates of the \textit{in-situ} component and 
-    b) observations of high redshift massive galaxies that should be dominated by 
+    \song{
+    Furthermore, a few known issues in the original Illustris simulation has been 
+    improved in the new Illustris--TNG version (e.g. \citealt{Genel2017, 
+    Pillepich2017}.
+    In future works, we will explore more comparisons with detailed predictions 
+    from new simulations to see how well we can trace \textit{ex situ} fractions
+    in massive galaxies using simple elliptical aperture masses.
+    }
+
+    \song{
+    Here, we further compare our \mden{} profiles with 
+    a) the profiles of the \textit{in-situ} component estimated from different ways,
+    and b) profiles of high redshift massive galaxies that should be dominated by 
     the \textit{in situ} component.  
+    }
     In particular, we compare with:
@@
 
-    We also compare with a uniquely massive BCG at high redshift: 
-    a \logms{}${\sim} 10^{11.4} M_{\odot}$ BCG with a distinctive ``cD''-like envelope 
-    at $z{\sim} 1.1$ (\citealt{Liu2013}).  
+    \song{
+    Although these naive comparisons support the idea that \minn{} mainly consists 
+    of \textit{in situ} stars whereas mass at $\mathrm{R} > 15$-20 kpc is dominated 
+    by \textit{ex situ} component, they also show that the \texttt{in situ} component 
+    could extend beyond 10 kpc\footnote{We convert these \mden{} profiles to the same 
+    \citealt{Chabrier2003} IMF; but there are still differences in median \mstar{} 
+    and details in the \m2l{} estimates}, and a fraction of mass within 10 kpc could 
+    also come from accretion (see also \citealt{RodriguezGomez2016}). 
+    This is certainly the limitation for using aperture masses as proxies of 
+    \textit{in situ} and \textit{ex situ} masses. 
+    In other works (e.g. \citealt{Huang2013a, Spavone2017}), 
+    the outer component from image decomposition is treated as proxy of the 
+    \textit{ex situ} component. 
+    Since such photometric component extends to the center of the galaxy and can 
+    reach to radius much larger than 100 kpc, it can lead to higher \textit{ex situ}
+    fraction than ours (e.g. \citealt{Spavone2017}). 
+    It will be very interesting to apply similar decomposition method to both the 
+    HSC images and the simulated massive galaxies, to help us understand what is the 
+    best tracer of the \textit{in situ} and \textit{ex situ} mass.
+    }
+
+    \song{
+    We also compare with a uniquely massive galaxy at high redshift: 
+    a \logms{}${\sim} 10^{11.4} M_{\odot}$ galaxy with a distinctive ``cD''-like 
+    envelope at $z{\sim} 1.1$ (\citealt{Liu2013}).  
     This high redshift galaxy has a \mden{} profile that follows the median \mden{} 
-    profile of our $11.6\leq$\logmtot{}$<11.8$ sample nicely at $\mathrm{R} < 20$ 
+    profile of our $11.6\leq$\logmtot{}$<11.8$ sample nicely at $\mathrm{R} < 40$ 
     kpc, but the profile becomes much steeper in the outskirt.
-    This suggests that the inner ``core'' of massive BCGs are already in pace at 
-    $z{\sim} 1$ while the outer halo is still being assembled.
-
-    These simple comparisons certainly support the idea that \minn{} mainly consists 
-    of \textit{in situ} stars whereas mass at $\mathrm{R} > 15$-20 kpc is dominated 
-    by \textit{ex situ} component.  
-    Meanwhile, this comparison also shows that the \texttt{in situ} component may 
-    extend beyond 10 kpc\footnote{We convert these \mden{} profiles to the same 
-    \citealt{Chabrier2003} IMF; but there are still differences in median \mstar{} 
-    and details in the \m2l{} estimates}. 
-    Further comparisons with massive galaxies at high redshift and with 
-    hydrodynamical simulations will help understand which radius is optimal for 
-    probing the \textit{in situ} mass.
-
-%    In line with the prediction from Illustris, this comparison also 
-%    suggests that, at very high-mass end, the accreted component can make significant 
-%    contribution even within the inner 10--20 kpc. 
-%    The nature of these ``accreted'' stars in the center of massive galaxies deserve 
-%    more attention. 
-%    It is possible that they mainly come from major merger and used to be the 
-%    \texttt{in situ} component of another massive galaxy. 
-%    It would be interesting see whether there is an alternative, but also physically 
-%    motivated definition of \textit{in situ} component that can be more easily examined 
-%    by observation.
-
-    % TODO: Move to Paper II
-    %More BCGs like this at $0.5 < z < 1.0$ can shed light on this intriguing 
-    %process, and help us confirm whether the environmental dependence of structure 
-    %has already emerged within massive galaxies at higher redshift 
-    %(e.g. \citealt{Papovich2012})
-
+    It suggests that while the very outskirt of the stellar halo is still being 
+    assembled, some massive high-$z$ galaxies may already have significant fraction 
+    of \textit{ex situ} stars. 
+    In future works, we will also look into the redshift evolution of the outer 
+    \mden{} profiles up to $z\sim 1.0$ using both HSC and other observations. 
+    Comparisons with simulations on this can also tell us how well we can trace
+    the evolution of \textit{ex situ} fraction using aperture masses.
+    }
 %% ------------------------------------------------------------------------------------ %%
@@
     \begin{enumerate}
+
+        \item We show that the \mden{} profiles of massive galaxies are relatively
+            homogenous within 10-20 kpc. 
+            However, there is large scatter in outer profiles of massive galaxies. 
+            Galaxies with higher \mtot{} show more prominent stellar halos and have 
+            shallower outer \mden{} slopes. 
+            Assuming that stellar halos are dominated by accreted stars, this result 
+            is consistent with the two-phase formation picture of massive galaxies.
+
+        \item We show that, on average, massive galaxies have positive ellipticity 
+            gradients out to at least 60 kpc. 
+            The average ellipticity profile also depend on \mtot{}: more massive 
+            galaxies tend to have steeper ellipticity gradients and become more 
+            elongated in stellar halos.
+
+        \item \song{
+            On the other hand, although massive galaxies in all three \mtot{} bins 
+            show clearly negative average color gradients out to 60 kpc, the 
+            average $(g-r)$ and $(g-i)$ color gradients do not show clear dependence 
+            on \mtot{}. 
+            }
+
+        \item \song{
+            We propose that, under reasonable assumptions, stellar masses within 
+            different physical apertures could be used to trace the 
+            \textit{in situ} and \textit{ex situ} components. 
+            Here we show that \minn{} and the \mstar{} between 10 and 100 kpc could 
+            be promising proxies of the two physical components, and can recover the 
+            trend between stellar mass and \textit{ex situ} fraction from simulation.
+            }
 
@@
             topics such as the evolution of the galaxy stellar mass function.
-
-        \item We show that the \mden{} profiles of massive galaxies are relatively
-            homogenous within 10-20 kpc. 
-            However, there is large scatter in outer profiles of massive galaxies. 
-            Galaxies with higher \mtot{} show more prominent stellar halos and have 
-            shallower outer \mden{} slopes. 
-            Assuming that stellar halos are dominated by accreted stars, this result 
-            is consistent with the two-phase formation picture of massive galaxies.
-
-        \item We show that, on average, massive galaxies have positive ellipticity 
-            gradients out to at least 60 kpc. 
-            The average ellipticity profile also depend on \mtot{}: more massive 
-            galaxies tend to have steeper ellipticity gradients and become more 
-            elongated in stellar halos. 
-            On the other hand, the average $(g-r)$ and $(g-i)$ color gradients do 
-            not show clear dependence on \mtot{} within 10-60 kpc.
 
@@
     \S~\ref{sec:ellipse} briefly. 
+    \song{
+    The uncertainties of the surface brightness profiles include the error in 
+    isophotal intensity derived by the \texttt{ellipse} procedure and the 
+    uncertainty from background fluctuation estimated by the distribution of the 
+    rebinned background pixels using the above method. 
+    }
     In practice, the profile at very low surface brightness level is sensitive to 
@@
     color profiles.
+
+    \song{
+    We cannot extract reliable 1-D profiles for a small fraction of massive galaxies 
+    because they are heavily masked out for either physical 
+    (e.g.\ late-stage major merger) or nuisance (e.g.\ nearby foreground 
+    galaxy or bright star) reasons. 
+    This is an intrinsic limitation of the 1-D method, and it removes ${\sim}10$\% of 
+    the sample.
+    We visually examine the 3-color images of randomly selected galaxies with failed 
+    1-D profiles.  
+    Most of them are relative small galaxies that are severely contaminated by nearby 
+    objects, and will not affect the results of this work.  
+    Meanwhile, it is worth noting that this does exclude most major merging systems 
+    among massive galaxies. 
+    }
+
 %% ------------------------------------------------------------------------------------ %%
@@
             }
-        \label{fig:ised}
+        \label{fig:ised_1}
         \end{center}
@@
     the priors used.   
+    \song{
+    \texttt{iSEDFit} takes a simplified Bayesian approach. 
+    In short, it first generates a large grid of SEDs from synthetic stellar 
+    population models by drawing randomly from the prior distributions of relevant
+    parameters (e.g. age, metallicity, dust extinction, and star formation history).
+    Based on these models, it uses the observed photometry and redshift to compute 
+    the statistical likelihood, and generates the posterior probability distribution 
+    functions (PDF) for each parameter.  
+    To get the best estimate of a given parameter, \texttt{iSEDFit} integrates the 
+    full PDF over all the other nuisance parameters.
+    Then, the median value and the 1-$\sigma$ uncertainty are derived based on the 
+    marginalized PDF. 
+    Please refer to \citet{Moustakas13} for technical details. 
+    }
     In Fig~\ref{fig:ised_1}, we show an example of the \texttt{iSEDFit} output by 

### 2017-10-17 draft/response_paper_I.md
For referee report

# Response to Referee Report for Paper I

We thank the referee for the careful reading and detailed comments.  We have re-organized the draft by following most of the referee's suggestions.  The modified parts of the new text are highlighted in cyan color.  Before we will address the referee's each suggestion in details, we now specifically address the main issues raised by the referee:

1. We share the referee's concern that the current paper is quite long and technical.  Following the referee's suggestions, we have shorten the introduction, remove some redundant technical details, and move others to the appendix. Hopefully, the referee would agree that it is easier to access the main results in the current version.  Meanwhile, we also decide to keep some details in the text (will explain in details later).  As the first paper of this series, it will serve as a technical reference for the following ones.  Since we are looking into the very low surface brightness outskirts of massive galaxies, several of these technical details become very important. We think it is responsible to the readers to keep certain level of technical details in the main text.

2. We agree with the referee that it would be much more straightforward to only use the $M_{100 \mathrm{kpc}}$ in the paper.  We do believe that it is a better proxy of "total" stellar mass for massive galaxies, and we do intend to do so in the following papers (one has been submitted and received very positive referee report).  Following the referee's suggestion, we adjust the relevant text accordingly.  However, we would also like to point out that the comparison with CModel stellar mass is one of the **main results** of this work, and we think it deserves to be kept in the main text.  Here are the details reasons: 
	- Ever since it has been adopted by the SDSS survey, CModel photometry has been widely used in numerous studies related to galaxy evolution.  For example, many of the published luminosity and stellar mass functions are based on this photometry.  Since it can take the PSF convolution into account and fit galaxy with a wide range of profiles, it has been considered a better choice for galaxy photometry than simple aperture photometry in the age of multi-band imaging surveys.  And due to its efficiency and flexibility, similar or improved version of CModel are being used in new imaging surveys (e.g. HSC, DES), and will be adopted by future deep surveys too (e.g. LSST).  Therefore, it is important to point out its limitation and remind the users of these survey data to be careful when it comes to the study of galaxy at high-mass end. 
	- The problem with CModel photometry has been pointed out and carefully studied by the group led by Mariangela Bernardi, and has led to many publications (e.g. Bernardi et al. 2013, 2014, 2016, 2017a, 2017b).  Using better reduced SDSS images and more complex models, these authors argue that the CModel photometry tends to miss large fraction of light in massive galaxies.  These works are very well received and have been discussed under many different contexts.  Since these results are still based on shallow SDSS images, their conclusion is still being questioned (e.g. d'Souza et al. 2014).  Our results addressed the same issue.  But with the help of much deeper image and model-independent method, now we can confirm that CModel photometry indeed misses the light in the outskirt of massive galaxies in a mass-dependent (and environment-dependent) fashion.  Although technical, we think it is an important result of this work.

We sincerely wish that the referee could understand our intention. 
We understand that it increases the length of the text and makes the paper more "technical", but we seriously think it is necessary and useful to do so for the benefits of not only our future works, but any people who will use CModel to study topics about massive galaxies.

------

## Major revisions

### Abstract:

> Reduce it. It resembles a "short introduction", saying why it is important to study stellar halos, rather than pointing out the main methods and results of the work.

We have re-organize the abstract to make it emphasizes the main results more.  The length of the abstract has also been slightly reduced.

### Introduction:

>This section is too long. I would suggest to reduce the first 3 paragraphs in few sentences (including references) and starting from “Both numerical simulation....” and to review the up-to-date science on stellar halos.

The referee is right that the first part of the Introduction was unnecessarily long.  We have significantly shortened the first three paragraphs according to the referee's suggestion.

>First paragraph on pag.3 is a repetition of what is already written in sec.2.1

We removed the redundant details of the HSC survey, and refer the reader to Section 2.1 for details.

### Sec 2.2:

> Can the authors explain how the error estimates on the surface brightnesses are derived? Which are the sources that contributes to them? How much is the uncertainty on the sky background?

The uncertainties of the surface brightness profiles are based on the error in isophotal intensity derived by the ```Ellipse``` procedure and the global RMS of the background estimates.  ```Ellipse``` measures the RMS of intensities along each isophote.  This is affected by the intrinsic S/N and the contaminations of fluxes that are from other sources.  We have tested the ```Ellipse``` step size (which influences the S/N at different radius), masks for other objects and sigma-clipping methods during profile extraction (which affects the contaminations from other objects), and come up with an optimized approach.  We also perform our own background estimate after aggressively masking out all objects and rebin the rest of the pixels.  It provides us the RMS of the global background fluctuation.  We did not include the **systematic uncertainties** from background subtraction as it is difficult to estimate at the coadd level for HSC images.  But we empirically correct the large scale background to account for over-subtraction due to nearby bright object and to make sure the intensity profile does not go negative at large radius.  More importantly, we perform tests to show that profiles within 100 kpc are not affected by systematics in background subtraction.

We add more details about the uncertainties of surface brightness profiles to Appendix B and Section 3 to reflect the referee's question.

### Sec 3:

>This section contains a lot of repetitions.
- In the 2nd and 4th paragraphs on page 6, ``We choose the i-band...’’, ``We correct these surface brightness...’’ , are mentioned at least twice in the same section.

We have adjust these paragraphs and remove the repeated parts according to the referee's suggestion.

>The 6th paragraph, starting with ``We cannot extract reliable 1-D profiles....’’ is useless,   since you do not use them in the work.

This is relevant to the completeness of the sample and affects the comparisons of the stellar mass functions at high-mass end later.  Based on the referee's suggestion, we now only briefly mention that ~10% of sample are excluded due to contamination, and move the detailed discussion to Appendix B.

> In this section I would suggest to mention how and why you derive also Mtot, moving here part of the discussion made later in 6.1. This is an important point, since, as you explain, M100kpc is a lower limit for the brightest objects. This is an assumption you make, that is ok, but take in mind that the limiting radius of the surface photometry is the galactocentric distance where the galaxy light blends into the background level (see Polhen & Truijllo 2006). Your Mtot is something similar to this limit, so this estimate is really important, more than that derived with the cModel

We agree with the referee that the background level is important when it comes to estimate the stellar mass and mass density profiles out to very large radius.  The work recommended by the referee has now been cited in our discussion.  As we explain in details in the Appendix B, although the radius we are reaching to is far below the brightness of sky background, we have done a series of tests to make sure that the mass density profiles are robust out to 100 kpc.  Although at this radius, we are still above the limitation of the intrinsic fluctuation of the background, the accuracy of the profile is limited by the systematics in background subtraction and contaminations from the fain outskirts of other objects, we make a conservative choice to only use the reliable part within the inner 100 kpc.

> I would suggest to put in a new section the description of the mass estimates: M(<10kpc), M(<100kpc) and also M*tot

We agree with the referee that the definitions of different stellar masses should be presented in a very clear way.  Inspired by the referee's suggestion, we now merge the last part of Section 3 and Section 4.2 together, and present these definitions in a few bullet points.  Although we still keep Section 4.2, it has been shortened.

###  Sec 4 :

> This section should be reduced to a short paragraph.
> The description of the iSEDfit in the 2nd paragraph should be removed, it is necessary the reference to the code

Based on the referee's suggestion, we now only keep the minimum necessary introduction of ```iSEDFit``` in the main text and move the description to Appendix C.  As there are many different approaches for SED fitting, we still keep brief introduction of ```iSEDFit``` in the Appendix for readers who care about these details.

We also adjust most text in Section 4.1 to make it more concise.

> Remove Sec.4.2: authors can shortly say that they assume a constant M/L, which is reasonably for ETGs, providing references

Since we are comparing mass density profiles out to 100 kpc, we think that the assumption of average M/L should be emphasized as a caveat and examined later using our own color profiles.  But we agree with the referee that this is a reasonable assumption for massive ETGs.  Now move the detailed discussion to Appendix C and point the reader there and to the section about color gradient later.

> Again, remove all comparison and discussion with quantities derived by the cModel, since you do not use them in the final results and discussion

As we explained in the beginning, we sincerely consider the comparison with CModel stellar mass and stellar mass function is the key result of this work.  Not only it clearly demonstrate the advantages of our methods, it also confirms the **intrinsic limitation** of the CModel photometry as it cannot account for the very extended, low surface brightness outskirts of massive galaxies.  This issue **affects many important topics around massive galaxies** (e.g. Evolution of SMF at high mass end; Environmental dependence of galaxy structure; Comparisons between observation and simulations etc.), and **should be taken into serious account as CModel is still a widely adopted photometric method** (including users of HSC data).  In addition, this comparison also serves as important technical reference for our future works.

Based on these reasons, we strongly propose to keep the comparison with CModel in this work.  We will modify the text to make the main message clear and make the text shorter.  We understand that this will make the paper appears to be more "technical", however we seriously consider it as necessary cost for this work.

> Sec 4.3 could be an appendix.

Given that we do want to keep the comparisons with CModel SMF, it is useful to discuss the completeness of the sample in advance.  Also, generally speaking, it is important to understand the completeness of the sample before diving into any scientific comparisons within the sample. In addition, this also serves as an important technical reference for our following works.

Since that Section 4.3 is already a quite short section, we propose to keep it in the main text after shortening it further.

###  Sec 5 :

>As for Sec.4, this section should be reduced to a short paragraph, I would suggest the summary in sec.5.2. The description of the adopted method (redMaPPer) can be moved to the appendix.

We agree with the referee that the first part of Section 5 can be significantly shortened.  
However, as we explained above, 1) The comparison of stellar mass functions and their halo mass dependence is considered as an important result.  Therefore we still want to describe how we separate the sample into two broad halo mass bins here. 2) Such description also serves as the technical reference for the following works that have been submitted.  We rewrite Section 5.1 and make it more concise, while keeping the brief summary in Section 5.2.

### Sec 6 :
> This section should start from sec.6.2 and focusing on the description of Fig.6 and Fig.7, which are the "core" of this work. In detail:
> remove the comparison and discussion of quantities derived from the cModel,so all text up to the beginning of page 6.

As mentioned several times earlier, we sincerely think the comparisons with CModel is a main result of this work.

We adjust the text in Section 6.1 to make it shorter and more clear.s

> the 1st paragraph on page 6, "As discussed in ..." is really important, but the content should be moved in Sec3, as I suggested above

We think the referee means the 1st paragraph on Page 11.  We agree with the referee that it is better to keep this important discussion together.  Right now, we have merge all the relevant discussion to Section 4.2.

> The descriptions of the SMF for SDSS-GALEX galaxies and for the Bernardi et al.sample (bullets points on page 11) are useless, references are enough.

For the comparisons of the SMF, it is crucial to point out the basic photometric method and key assumptions in stellar population modeling.  We think that put these information here could save the reader time to find them in the citations.

Under the referee's suggestion, we shorten the descriptions for these two bullet points, but keep the key information and put a few details in footnotes.

> The last paragraph, where you describe the Fig.5, should be moved in Sec.5, where you  describe the sample and, therefore, how it compares with literature data.

Again, this relates to the strategy about the comparisons with CModel.  We think Figure 5 should stay in this section as it is part of the main results.  The left panel illustrates the differences between our aperture masses and the CModel masses. More importantly, it shows that the difference is apparently more significant for the central galaxies in very massive halos due to their extended stellar halos.  The right panel of Figure 5 not just compares our SMF with literatures, but demonstrate our main point here again: when it comes to the SMF at high-mass end, the photometric method used in stellar mass measurement really matters, and should be carefully taken into account before discussing any physical evolution.

Again, we hope that the referee could understand our intention, and agree that we can keep Figure 5 in Section 6.1 as part of the results.

### Sec 6.2.1:

> the last paragraph, "Deep μ* profiles..." is a review on previous works, move it in the Introduction and here cite that section. In this section you should focus on the description of your results.

The referee is right that this sentence belongs to the Introduction section.  We moved it and merged it into the relevant part of the introduction.

> page12: "CGS images are deeper..." , this is a repetition

We think this is the first time we mention this information.  It is about the comparison between CGS and SDSS, and with HSC.  However, since this is not an important information, we remove it any way based on the referee's point.

> page12: "In future work, we will compare..." , this is not useful for the reader at this point, if you like, you could mention this at the end of the paper

We agree with the referee and this sentence has been removed. We do mention this plan at the end of the paper.

### Sec 6.3:

> remove 1st paragraph, this is a repetition. Start with "We also apply..."

Based on the referee's suggestion, we modify the beginning of this section and makes it shorter.

> 2nd paragraph: "The ellipticity of the isophote.." is an information not needed here, you are describing your results

We delete this sentence here according to the referee's point.  We move it to the introduction section as we think it is still useful to remind the reader that the ellipticity profile contains many useful information.

> May you comment a comparison of the ellipticity and P.A. profiles with those derived by Spavone et al. 2017 for a sample of few ETGs in local universe? They found a similar
trend

We agree with the referee that Spavone et al. 2017 also finds a similar trend using a smaller sample of nearby massive galaxies.  We now cited this work in the introduction section and in the discussion about the ellipticity profile.

> 1st paragraph in the second column: "If accreted stars...", again, this is an information not needed here, it should be moved in the introduction or used in the discussion of the results. Here you are describing them.

The referee is right that this part belongs to the introduction.  We now removed this part and merged it with the relevant text in the Introduction section.

> 2nd paragraph in the second column: "Regarding the color profiles...", this is a repetition, please, delete this sentence

What we meant to say is that we see smooth, negative color gradients as shown in many previous observations and predicted by some simulations. Based on the referee's suggestion, we remove this sentence but incorporate the references here into the presentation of our results.

> Can authors provide an error estimate on the color profiles? usually this increases with radius and with fainter surface brightnesses

The referee is correct that the statistical error of color profile increases quickly with radius.  And, in the outskirts, it is also very sensitive to even a small systematical difference in background subtraction or contaminations from nearby objects.  
We estimate the error by combining the uncertainties of surface brightness from both bands, but as you can see from the figure, the scatters of color profiles in the outskirts are very large and often show unphysical upward or downward turns.  The main reasons are 1) the g-band images are shallower and more noisy, 2) the backgrounds in two bands have not been jointly constrained yet.  Since the comparisons of color gradients are mainly to show that the average color gradients are shallow and do not strongly depend on stellar mass, so that our assumption of single M/L is reasonable here, we only use the average color profiles. More careful investigation of color profile is beyond the scope of this work, and to explore the individual color information in the stellar halo, we think it is necessary to perform multi-band image fitting in the following work.

In line of the referee's question, we add a few lines of discussion about this in the relevant part of the result.

### Sec 7.2 :
> The 1st paragraph is a repetition of some material reviewed in the introduction, shorten it and cite the sec.1

Following the referee's suggestion, the first part of Section 7.2 has been shortened.

> Have you looked at the new Illustris simulations, derived with the new TNG code? Thay appeared on astro-ph past week, see Pillepich et al. 2017 (2017arXiv170703406P) and Genel et al. 2017 (2017arXiv170705327G). The new code improve some limits on the mass estimates given in the former simulations.

The referee is right that the new Illustris-TNG simulation suppose to solve several issues in the original Illustris one, and is very interested to look into.  The results from Illustris-TNG simulation are still not available to the public during the preparation of this work, although the relation with ex-situ fraction does not seem to change much.  We are discussing with members of Illustris-TNG collaboration about careful comparison.  We'd like to mention that in Pillepich+2017, the authors also discuss the stellar masses estimated using different methods and within different apertures, and how they affect the comparisons of stellar mass function with observation.  We feel that it makes more sense to highlight our observational results about this in the main text.

Both paper suggested by the referee are now cited and discussed in this work.

> may you also comment about the mass fraction of the accreted stars compared with simulations and other observations? See also Gonzalez et al. 2007 and again Spavone et al 2017

We thank the referee for suggesting the relevant works, both of them have already been cited in this paper.  In Gonzalez et al. 2005, 2007, the authors use 2-D 2-component fitting method to photometrically isolate the ICL component.  In Spavone et al. 2017, the authors also photometrical decompose the light profiles of a small samples into a few components, and use the fraction of the outer component as proxy of the fraction of accreted stars.  Both are very interesting approaches.  The author of this work also tries the similar approach (Huang et al. 2013a, 2013b).  However, this approach also faces challenges:
	1. It is not clear whether Sersic profile is appropriate to describe the physical in-situ and ex-situ component. 
	2. The decomposition and modeling are sensitive to the background subtraction (as the outer component often extends to very large radius) and internal degeneracies of model parameters.

Still, we are very interested in performing similar decomposition method to our galaxies and compare the results from aperture masses. It is interesting to see that the Spavone et al. 2017 results show higher fraction of accreted stars than ours.  It could be caused by the fraction of mass outside 100 kpc, or could reflect the fact that a significant of mass within 10 kpc is actually accreted (as we try to show in Figure 8b).  We now briefly discuss these points at the end of this section.

> last paragraphs on page 16 (1st column): ``How well justified is our choice...’’, you have already mentioned at this! please, merge all the content in Sec.3 and discuss the similarity with BCGs (last paragraph) in Sec.6

We would like to clarify the purpose of this paragraph.  In Section 3, we simply assume that $M_{10\mathrm{kpc}}$ could be used as proxy of the in-situ mass.  And we want to carefully discuss this choice in this section.  The last paragraph and Figure 8b is meant to show that **although the inner 10 kpc could be indeed dominated by in-situ stars, there are still some uncertainties**.  As mentioned above, the comparisons of profiles show that a fraction of mass within 10 kpc could also come from accretion.  The comparison with the unique z~1 "BCG" is to highlight that massive galaxies may already have a significant fraction of accreted mass.

We think this is more like a discussion of caveat. Therefore, we propose to keep this figure and the discussion here with some modification and additional discussion.

### Sec 8:
> The 1st point in the list (i),should be removed. The comparison with the cModel is not a result and, as I suggested above, it should not be so widely discussed in the paper.

As we explained above, we do think that the comparison of stellar mass using CModel photometry is a key results of this work.  The differences at the high mass end are significant enough so that many recent results using CModel photometry on the topics of massive galaxies could be affected.  Therefore, we think it is appropriate to remind the reader about this in the summary.

We do understand the referee's concern that this is a more technical point. We adjust the order of the bullet points, and put this one at the end.

> your paper focused on the surface density profiles (point ii), about their shape and how they compare with simulations and observations, and on the colors of the stellar
envelope (new point). I would also add, among your results, the estimate of the total accreted mass

As we explained earlier, the measurements of color gradients are still not as reliable as the mass density profiles, and can not reach to the same 100 kpc.  That's why we are hesitate to list it as a separated main result.  Based on the referee's suggestion, we modify it a little and now put it in a separate bullet point.

We also add a new bullet point to summarize our results on using the aperture masses to trace the in-situ and ex-situ components.

-----

## Figures:

> Fig.1: delate the last sentence, this is not a description of the figure.```

It has been removed based on the referee's suggestion.

> Remove Fig.3 and left panel of Fig 5:See the above comments on avoiding discussion on the cModel.

As we have been explained multiple times above, in our opinion, the comparisons with CModel are not only a crucial technical point, but also the key result of this paper.  We propose to keep these two figures and most of the relevant text.

> Left panel of Fig.8 is a COPY of Fig.6, please, merge them

As we explained above, the right panel of Figure 8 serves a different purpose in the discussion section compared to Figure 6.  Also, merging these two figures will make it very busy and hard to see the comparisons in the inner region.  Therefore, we think it should be Ok to keep the right panel of Figure 8 as is.

### 2017-10-17 draft/paper1_v14.tex
For referee report

@@
 
-\def\m2l{{$M_{\star}/L_{\star}$}}
+\def\m2l{{$M_{\star}/L$}}
 \def\s2n{{$\mathrm{S}/\mathrm{N}$}}
@@
     (e.g. \citealt{Cappellari2012, Weijmans2014}) of stars in massive galaxies.
-    The elliptical profiles of massive galaxies have not been carefully studied 
-    out to large radius except for few works using either image stacking method
-    (e.g. \citealt{Tal2011, dSouza2015}) or small sample of nearby galaxies 
-    (e.g. \citealt{Spavone2017}). 
+    If the stellar halos of massive galaxies are indeed dominated by accreted 
+    stars, their ellipticities could be systematically different with the inner 
+    regions and contain clues about the assembly history of massive galaxies 
+    (e.g. average time since last merger, average merger mass ratio).
+    These issues have not been fully explored in both simulation and observation.
+    Certain simulation predicts more massive ETG should have rounder shape
+    (e.g. \citealt{Wu2014}), while others generate massive galaxies with very 
+    elongated haloes (e.g. \citealt{Li2017}).  
+    On the observational side, constraints are only available from few works 
+    using either image stacking method (e.g. \citealt{Tal2011, dSouza2015}) or 
+    small sample of nearby galaxies (e.g. \citealt{Spavone2017}).
     }
@@
 %% ------------------------------------------------------------------------------------ %% 
-  \begin{figure*}
-      \centering 
-      \includegraphics[width=\textwidth]{fig/redbcg_mass_diff_new}
-      \caption{              
-          \textbf{Left:} Difference between \mcmodel{} and \mtot{} for massive
-      	  galaxies (grey dots).
-      	  The running-median of the mass difference is shown by large red hexagons. 
-      	  On average, \mcmodel{} underestimates the total stellar mass of massive 
-          galaxies by 0.1 dex while in some cases, the difference can exceed 0.2 dex.
-          Vertical histograms indicate the mass difference for all galaxies (shaded 
-          histogram) and for the ones with \logmtot{}$>11.6$ (empty histogram).
-          \textbf{Right:} Difference between \mmax{} and \mtot{} in the same format. 
-          The average difference is small (0.02 dex) and with no clear mass--dependence. 
-          \textbf{Please note that the scales of the vertical axes are different 
-            for these two figures.}
-          }
-      \label{fig:mass_diff}
-  \end{figure*}
-
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %% 
 \subsection{Initial Massive Galaxy Sample}
@@
 
-%    By comparing with the Stripe 82 Massive Galaxy Catalog
-%    (\texttt{S82-MGC}; \citealt{Bundy2015}), \citet{Leauthaud2016} have measured the
-%    \mstar{} completeness of the combined BOSS and SDSS samples. 
-%    They estimate that the BOSS spec-$z$ sample is about 80\% complete at 
-%    \logms{}$\geq 11.6$ at $0.3 < z < 0.5$. 
-%    The GAMA survey, which partially overlaps with the HSC footprints, supplements 
-%    our \texttt{hscZ} sample by 14\%. 
-%    Based on \citet{Taylor2011} (e.g.\ their Fig~~6), at $z{\sim} 0.3$, the GAMA 
-%    sample is 80\% complete down to $10^{10.8}$\msun; but only 80\% complete to 
-%    $10^{12.0}$\msun at $z{\sim} 0.5$. 
-%    We can therefore expect our sample to be roughly \mstar{}-complete above 
-%    \logms{}$\geq 11.5$-$11.6$. 
-%    This question will be addressed more carefully using the overlap region between 
-%    HSC and the \texttt{S82-MGC} in Section \ref{ssec:s82}.
-
-%% ------------------------------------------------------------------------------------ %%  
-%\subsection{The \redm{}{} cluster catalog}
-%    \label{ssec:redmapper}
-%    
-%    For now, we wish to focus on galaxies located at the center of their dark matter halos. 
-%    To limit our sample to central galaxies, we use \texttt{v5.10} of the \redm{}{} 
-%    cluster catalog\footnote{See: http://risa.stanford.edu/redmapper/} 
-%    (e.g.\ \citealt{Rykoff2014}; \citealt{Rozo2015b}). 
-%    These authors have developed a well-tested red-sequence cluster finder that has 
-%    been run on SDSS DR8 (\citealt{SDSSDR8}) photometric data. 
-%    For each cluster, the catalog provides a photometric redshift ($z_{\lambda}$), a 
-%    cluster richness ($\lambda$), and identifies the most likely central galaxy (the 
-%    galaxy with the highest $P_{\mathrm{Cen}}$ value). 
-%    The \redm{}{} catalog also provides a list of member galaxies for each cluster and 
-%    their associated membership probabilities. 
-%    Details about the performance of the \redm{}~cluster catalog can be found in 
-%    \citet{Rozo2014}, \citet{Rozo2015a}, and \citet{Rozo2015b}. 
-%    Several studies have published calibrations between the \redm{}~richness estimate, 
-%    $\lambda$, and halo mass (e.g.\ \citealt{Saro2015, Farahi2016, Simet2016, 
-%    Melchior2016}). 
-%    All these studies consistently find that \redm{} clusters with $\lambda > 20$ 
-%    have $\log (M_{\mathrm{halo}}/M_{\odot}) \geq 14.0$. 
-%    The \redm{} catalog therefore helps us group massive central galaxies into 
-%    samples with different average \mhalo{}. 
-%    We will use the central galaxies of \redm{} clusters 
-%    ($P_{\mathrm{CEN}} \geq 0.7$) to form a sample of massive central galaxies that 
-%    live in massive halos.
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %% 
-%\subsection{Massive Central Galaxies in Low and High Mass Halos}
-%    \label{ssec:mass_central}
-%
-%    One of the goals of our work is to investigate the halo dependence of the outer 
-%    envelope. Although there is a correlation between $M_{\star}$ and $M_{\mathrm{Halo}}$,
-%    based on recent constraints of $M_{\star}$-$M_{\mathrm{Halo}}$ relation 
-%    (e.g.\ \citealt{Leauthaud2012}, \citealt{Behroozi2013}, \citealt{Kravtsov2014}), 
-%    even though our sample selects very massive galaxies (\logms{}$\geq 11.5$), they 
-%    With the help of the \redm{} catalog, we can broadly separate our sample into two
-%    groups with \logmh{}$<14.0$ and \logmh{}$>14.2$.
-%    live in a fairly broad range of halos masses.
-%    
-%    % We match this sample with the central galaxies of \redm{}~catalogs using a 
-%    % $1.0^{\arcsec}$ radius, and it results in 704 galaxies.  
-%    %% Saved as "dr1_redbcg_hsc_sdss_gama_1arcsec.fits"
-%    
-%    We match the \texttt{hscZ} sample with the central galaxies of \redm{} clusters 
-%    with $\lambda \geq 30$ and $P_{\mathrm{0.7}} \geq 0.7$, and find 164 matched 
-%    galaxies at $0.3 \leq z \leq 0.5$.
-%    Our sample of \textbf{central galaxies in more massive halos} will be referred to 
-%    as the \rbcg{} sample. 
-%    The median $\lambda$ of the clusters associated with the \rbcg{} sample is 
-%    ${\sim} 41$, corresponding to halo mass of 
-%    $M_{\mathrm{halo}}{\sim} 2.2\times 10^{14}$ $h^{-1}$ $M_{\odot}$.
-%    Only 44 centrals from the \rbcg{} sample live in clusters with $\lambda \geq 50$
-%    ($M_{\mathrm{halo}} {\sim} 3.0\times 10^{14}$ $h^{-1} M_{\odot}$). 
-%    Our \rbcg{} sample therefore corresponds to galaxies in moderate mass halos.
-%    %% Saved as "dr1_redbcg_use_sed5b.fits"
-%    
-%    Out next goal is to construct a sample of central galaxies living in halos with 
-%    \logmh{}$<14.0$. 
-%    We first identify and remove all galaxies within a cylindrical region around all 
-%    \redm{} clusters. 
-%    We use a radius equal to $R_{\mathrm{200b}}$ and the thickness of the cylinder is 
-%    set to twice the uncertainty of the photometric redshift error. 
-%    We convert $\lambda$ to $M_{\mathrm{halo}}$ using the calibration of 
-%    \citet{Simet2016} and we use the mass-concentration relation from 
-%    \citet{Diemer2015} to compute $R_{\mathrm{200b}}$. At $0.3 < z < 0.5$, the 
-%    uncertainty of photo-$z$ is between 0.015 to 0.025, and is enough to exclude 
-%    cluster members.
-%    After removing galaxies associated with \redm{} clusters, the remaining galaxies 
-%    in our sample will be dominated by central galaxies living in halos with 
-%    \logmh{}$\leq 14.0$. 
-%    We will refer to this sample of \textbf{central galaxies in less massive halos}
-%    as the \nbcg{} sample.
-%   
-%    Due to the depth and resolution of SDSS, the \redm{} catalog becomes slightly 
-%    incomplete at lower richness ($\lambda < 40$) at $z > 0.33$. 
-%    To ensure a clean separation in \mhalo{}, here we only focus on the central 
-%    galaxies of clusters with $\lambda > 30$. 
-%    According to \citet{Simet2016}, this $\lambda \geq 30$ sample should correspond to 
-%    $M_{\mathrm{halo}}>10^{14.2} M_{\odot}$. 
-%    We have checked that none of the results in this work depend on the choice of this 
-%    $\lambda$ limit. 
-%    For massive central galaxies that are not in these cluster-level halos, 
-%    we unfortunately can not estimate their \mhalo{} individually, but it is safe 
-%    to assume they will have $\log (M_{\mathrm{halo}}/M_{\odot}) < 14.0$.  
-%    {\bf I am still a bit confused why stellar mass completeness depends on Mh??}
-%
-%    We note that at this stage, our \nbcg{} sample still contains galaxies with a 
-%    wide range of \mstar{} values. 
-%    Later on, once we have more accurate \mstar{} estimates, we will further limit this 
-%    sample to \logms{}$ > 11.5$. 
-%    At this very high mass end, and given that we have rejected satellites in \redm{} 
-%    clusters, any further satellite contamination can be safely neglected 
-%    (e.g. \citealt{Reid2014, Hoshino2015, Saito2016, vanUitert2016}).
-%    %% Saved as "dr1_nonbcg_use_sed5b.fits"
-%    
-% 
-%%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %% 
-%\subsection{Summary of Sample Construction}
-%    \label{ssec:sample}
-%
-%    Using ${\sim} 100$ deg$^2$ of HSC data, we select a large sample of massive central 
-%    galaxies with reliable redshift information, and broadly separate them two 
-%    categories based on $M_{\mathrm{halo}}$.
-%    
-%    The following is a summary of our sample construction.
-%    
-%    \begin{itemize}
-%        \item \texttt{hscPho} sample: this parent sample consists of bright galaxies 
-%            with $i_{\mathrm{cModel}} \leq 21.0$, good quality imaging, and reliable 
-%            \texttt{cModel} photometry in all five HSC bands in the \texttt{S15B} 
-%            data release. 
-%        \item \texttt{hscZ} sample: we limit the \texttt{hscPho} sample to galaxies 
-%            with reliable redshift information. 
-%        \item {\bf Select only central galaxies using RedMapper: total number in full 
-%        sample?}
-%        \item We further divide the sample into an \rbcg{} sample and a \nbcg{} sample, 
-%          with the former roughly having \logmh{}$\geq 14.2$ and the latter having 
-%           \logmh{}$<14.0$.
-%
-%          : we select a sample of 164 galaxies at 
-%            $0.3 \leq z \leq 0.5$ that are the central galaxies 
-%            in $\lambda > 30$ \redm{} clusters. 
-%            They represent the central galaxies in very massive halos 
-%            (\logmh{}$\geq 14.2$). 
-%        \item \nbcg{} sample: after excluding all cluster members from the 
-%            \texttt{hscZ} sample, we have 14661 bright galaxies at 
-%            $0.3 \leq z \leq 0.5$. 
-%            After applying an additional \mstar{} cut (see Section 
-%            \ref{ssec:isedfit}), this sample corresponds to central galaxies in 
-%            halos with \logmh{}$<14.0$.  
-%    \end{itemize}
-%    
-%    We now proceed to measure the luminosities and stellar mass profiles for 
-%    all galaxies in the \rbcg{} and \nbcg{} samples.
-%% ------------------------------------------------------------------------------------ %%
-
 %% ------------------------------------------------------------------------------------ %% 
@@
     de~Vaucouleurs or single-\ser law, especially at the imaging depth of HSC.
-    These models will fail to simultaneously describe the profile in both the inner 
+    These models fail to simultaneously describe the profile in both the inner 
     and the outer regions and also cannot account for any radial variations in 
     ellipticity and position angle. 
-    In principle, massive galaxies can still be described by more complex 
-    models (e.g \citealt{Huang2013a, Huang2013b, Oh2017}), but the results are still 
-    sensitive to the choice of a particular model (e.g. de~Vaucouleurs or \ser{} 
-    profile), the number of components, initial guesses of parameters, and internal 
-    degeneracies among different parameters. 
-    Background subtraction uncertainties can also affect the 2-D model fitting method, 
-    especially for the massive ETGs that make up our sample.
+    \song{
+    Although they can still be described by more complex models 
+    (e.g \citealt{Huang2013a, Huang2013b, Oh2017}), the results will be 
+    sensitive to the choice of model, the number of components, and internal 
+    degeneracies among parameters. 
+    2-D modeling is also very sensitive to background subtraction method, 
+    especially for massive ETGs (e.g. \citealt{Huang2013a}).
+    }
 
@@
 
-    We prepare large $i$-band postage-stamps for each galaxy that extend to 750 kpc 
-    in radius, along with a bad pixel mask and the PSF model. 
-    These postage-stamps include all of the light of the galaxy and are also large 
-    enough to evaluate the background level. We choose to use $i$-band images 
-    because they trace the stellar mass distributions of massive galaxies at 
-    $0.3 \leq z \leq 0.5$ reasonably well 
-    (the observed $i$-band corresponds to a rest-frame $g$ or $r$ band), but also 
-    because they have better seeing and much lower background levels than the $z$ 
-    and $y$ band images (although these in principle may be better tracers of 
-    \mden{}).
-
-    For each cut-out, to overcome the \texttt{hscPipe} ``over-deblending'' issue, 
-    we use a customized procedure to detect and aggressively mask out
+    \song{
+    We generate postage-stamp of each galaxy that extend to 750 kpc in radius, 
+    along with the bad pixel mask and the PSF model. 
+    They postage-stamps are large enough to evaluate the local background. 
+    We choose to use $i$-band images since they trace the stellar mass distributions 
+    of $0.3 \leq z \leq 0.5$ massive galaxies reasonably well 
+    (corresponds to rest-frame $g$ or $r$ band), and also because better seeing 
+    and lower background level than the $z$ and $y$ band images (although these 
+    bands are better tracers of \mden{}). 
+    }
+
+    For each postage-stamp, to overcome the \texttt{hscPipe} ``over-deblending'' 
+    issue, we use a customized procedure to detect and aggressively mask out
     neighbouring objects. 
@@
 
-    Then, we run \texttt{Ellipse} on the background-corrected, masked cut-outs 
+    Then, we run \texttt{Ellipse} on the background-corrected, masked postage-stamp 
     following the methodology of \citet{Li2012}. 
@@
     the mean ellipticity and position angle. 
-    We correct these surface brightness profiles for Galactic extinction and 
-    cosmological dimming, and integrate them to various radii to get the luminosity 
+    We correct these profiles for Galactic extinction and cosmological dimming, 
+    and integrate them to various radii to get the luminosity 
     within different physical (elliptical) apertures. 
@@
 %% ------------------------------------------------------------------------------------ %% 
-
-    Given exquisite profiles extending to 100 kpc, the definition and meaning 
-    of ``total'' magnitude (and stellar mass) becomes nuanced.
-    With the help of the average \m2l{} estimated in the next section 
-    (\S \ref{sec:mstar}), we integrate the profile to a range of radii, and estimate 
-    the stellar mass within these different projected 2-D apertures.  
-    Motivated by the two-phase scenario, we will consider two benchmark physical 
-    apertures throughout this work:
-
-    \begin{itemize}
-
-        \item \textbf{The \mstar{} within the inner 10 kpc} 
-            (hereafter noted \minn{}). 
-            According to the two-phase scenario, the \textit{in situ} star-formation 
-            phase quickly builds up the inner, dense core of massive ETGs.  
-            Based on recent observation (e.g.~\citealt{vanDokkum2010}) and 
-            simulations (e.g. \citealt{RodriguezGomez2016}), the \textit{in situ} 
-            component dominates the \mstar{} within one effective radius 
-            ($R_{\mathrm{e}}$, or 5-10 kpc) of $z{\sim}0$ massive ETGs.
-            We therefore use \minn{} as a proxy for the mass formed during the 
-            \textit{in situ} phase. 
-            Given the quality of the HSC data, we can reliably measure \minn{} over 
-            our redshift range ($1.0^{\arcsec}$ in radius equals 4.4 and 6.1 kpc 
-            at redshifts 0.3 and 0.5 respectively).  
-            It is worth noting that, at the very high-\mstar{} end, accreted stars 
-            may make a significant contribution to the mass within 10 kpc 
-            (e.g. \citealt{RodriguezGomez2016}). 
-            We will further discuss the justification of this assumption in 
-            \ref{ssec:twophase}.
-
-        \item \textbf{The stellar mass within 100 kpc} 
-            (hereafter noted \mtot{}). 
-            For our galaxy sample, a 100 kpc aperture corresponds to 5-10 
-            $\times R_{\mathrm{e}}$. 
-            We show in \S~\ref{ssec:mtotal} that most of the total \mstar{} for 
-            these ETGs lies within a 100 kpc radius and that \mtot{} is 
-            a good proxy for the ``total'' \mstar{}. 
-            Although not perfect, we argue that our measurements of \mtot{} (which are 
-            actually measuring the light directly out to 100 kpc) are a better tracer 
-            of total \mstar{} than model-dependent results from shallower data 
-            (such as SDSS) which rely on extrapolating the light profiles of galaxies 
-            out to large radii.
-
-       \end{itemize}
-
-    We should point out that both \minn{} and \mtot{} are measured after adopting a 
-    isophote with fixed ellipticity and position angle. 
-    The 10 kpc and 100 kpc here refer to the radius along the major axis of the 
-    elliptical isophote.
+  \begin{figure*}
+      \centering 
+      \includegraphics[width=\textwidth]{fig/redbcg_mass_diff_new}
+      \caption{              
+          \textbf{Left:} Difference between \mcmodel{} and \mtot{} for massive
+      	  galaxies (grey dots).
+      	  The running-median of the mass difference is shown by large red hexagons. 
+      	  On average, \mcmodel{} underestimates the total stellar mass of massive 
+          galaxies by 0.1 dex while in some cases, the difference can exceed 0.2 dex.
+          Vertical histograms indicate the mass difference for all galaxies (shaded 
+          histogram) and for the ones with \logmtot{}$>11.6$ (empty histogram).
+          \textbf{Right:} Difference between \mmax{} and \mtot{} in the same format. 
+          The average difference is small (0.02 dex) and with no clear mass--dependence. 
+          \textbf{Please note that the scales of the vertical axes are different 
+            for these two figures.}
+          }
+      \label{fig:mass_diff}
+  \end{figure*}
 
@@
     This is a reasonable assumption considering that they are mostly dominated by 
-    old stellar populations and are known to have only shallow color gradients. 
-    We will further justify this point by measuring their median color profiles in 
-    \S~\ref{ssec:ell_color}.
+    old stellar populations and are known to have only shallow color gradients
+    (e.g.\ \citealt{Carollo1993, Davies1993, LaBarbera2012, DSouza2014}). 
+    \song{
+    We will discussion more about this point in Appendix~\ref{app:sed}, and our own 
+    measurements of color profiles (see \S~\ref{ssec:ell_color}) also demonstrate 
+    this point. 
+    }
 
@@
 
-    In this work, we derive average \m2l{} using the Flexible Stellar Population 
+    \song{
+    Here we estimate average \m2l{} using the Flexible Stellar Population 
     Synthesis\footnote{http://scholar.harvard.edu/cconroy/sps-models}
@@
     MILES\footnote{http://www.iac.es/proyecto/miles/pages/stellar-libraries}
-    (\citealt{MILES1}, \citealt{MILES2}) stellar library and assuming a
-    \citet{Chabrier2003} IMF between 0.1 to 100 \msun. 
-    The star formation history (SFH) is assumed to follow a delayed-$\tau$ model with 
-    stochastic star bursts (see Appendix~\ref{app:sed}). 
-    This SFH is appropriate for massive galaxies at low redshifts 
-    (e.g.\ \citealt{Kauffmann2003}). 
-    For stellar metallicity 
-    ($[\mathrm{M}/\mathrm{H}]=\log\ (\mathrm{Z}/\mathrm{Z}_{\odot})$), we assume a 
-    flat distribution between 0.004 to 0.03 (the highest value allowed by FSPS).
-    We adopt the \citet{Calzetti2000} extinction law with a order two Gamma 
-    distribution of $A_{V}$ between 0 to 2 magnitudes. 
-    The majority of our galaxies are red and quiescent so the results are not 
-    very sensitive to parameters related to the SFH or the internal dust extinction. 
-    To achieve reasonable sampling across these parameters, we generate 250000 
-    models.
+    (\citealt{MILES1}, \citealt{MILES2}) stellar library, with a
+    \citet{Chabrier2003} IMF between 0.1 to 100 \msun and metallicity 
+    ($[\mathrm{M}/\mathrm{H}]=\log\ (\mathrm{Z}/\mathrm{Z}_{\odot})$) between 
+    0.004 to 0.03. 
+    We assume a delayed-$\tau$ model with stochastic star bursts 
+    for the star formation history (SFH; see Appendix~\ref{app:sed}) of low-$z$ 
+    massive galaxies (e.g.\ \citealt{Kauffmann2003}). 
+    The \citet{Calzetti2000} extinction law is adopted in this work.
+    The massive ETGs in our sample are not very sensitive to the SFH shape or the 
+    internal dust extinction. 
+    }
 
@@
     a tight ``red-sequence''.
-    Please see Appendix~\ref{app:sed} for further details.
+
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
+\subsection{Definitions of Different Aperture Stellar Masses}
+    \label{ssec:mtotal}
+
+    \song{
+    \texttt{iSEDFit} help us estimate the best--fit \mstar{} based on the \cmodel{} 
+    photometry (noted as as \mcmodel{}) and the average \m2l{} in the $i$-band. 
+    Then, we can convert the 1-D luminosity density profiles into stellar mass 
+    surface density (\mden{}) profiles with the average \m2l{} and estimate \mstar{} 
+    within different radius through integrating the \mden{} profiles. 
+    Given exquisite \mden{} profiles extending to $>100$ kpc, the definition and meaning 
+    of ``total'' \mstar{} becomes nuanced.
+    At the same time, motivated by the two--phase scenario, \mstar{} within different 
+    radius may help us trace different physical components. 
+    Considering this, here we define a few benchmark physical apertures throughout 
+    this work:   
+    }
+
+%% ------------------------------------------------------------------------------------ %%          
+    \begin{itemize}
+
+        \item \textbf{The \mstar{} within the inner 10 kpc} 
+            \song{
+            (hereafter noted \minn{}). 
+            Suggested by recent observation (e.g.~\citealt{vanDokkum2010}) and 
+            simulation (e.g. \citealt{RodriguezGomez2016}), the \textit{in situ} 
+            component dominates the \mstar{} within one effective radius 
+            ($R_{\mathrm{e}}$, or 5-10 kpc) of $z{\sim}0$ massive ETGs.
+            We therefore use \minn{} as the \mstar{} of the inner ``core'' and as 
+            a proxy for the \textit{in situ} \mstar{}. 
+            The high-quality HSC data enable us to reliably measure \minn{} at 
+            $0.3 < z < 0.5$ ($1.0^{\arcsec}$ in radius equals 4.4 and 6.1 kpc 
+            at redshifts 0.3 and 0.5 respectively).
+            We should point out that, in simulation 
+            (e.g. \citealt{RodriguezGomez2016}), \textit{in situ} component can 
+            extend outside the inner 10 kpc while \textit{ex situ} component may 
+            contribute to \minn{} at the same time.  
+            We will further discuss this assumption in \ref{ssec:twophase}.
+            }
+
+        \item \textbf{The \mstar{} within 100 kpc} 
+            (hereafter noted \mtot{}). 
+            \song{
+            For massive galaxies in our sample, 100 kpc aperture corresponds to 5-10 
+            $\times R_{\mathrm{e}}$ and should contain the majority of the \mstar{}. 
+            Here we use \mtot{} as a measure of the ``total'' \mstar{}. 
+            Although not perfect, we will show that \mtot{} is a better tracer 
+            of total \mstar{} than model-dependent results from shallower images 
+            that rely on extrapolating the light profiles out to large radii. 
+            We should point out that the \s2n{} for surface brightness measurement 
+            at \s2n{} is still above the limit set by the intrinsic fluctuation 
+            of the background for our massive galaxies (e.g. see \citealt{Pohlen2006}). 
+            }
+
+        \item \textbf{The \mstar{} within the largest available aperture} 
+            (hereafter noted \mmax{}).
+            \song{
+            We know that the \mden{} profiles of massive galaxies extend way beyond 
+            100 kpc with no clear sign of truncation
+            (e.g. \citealt{Gonzalez2005, Tal2011, DSouza2014}).
+            Therefore, \mtot{} should be only considered as lower limit of the
+            ``total'' \mstar{}. 
+            Here, we also integrate the \mden{} profile to the edge of the 
+            postage-stamp, and select the isophote that gives us the highest  
+            \mstar{} and define the \mmax{}. 
+            It helps us quantify how much extra \mstar{} may be kept at $>100$ kpc.
+            }
+
+    \end{itemize}
+
+    \song{
+    All aperture \mstar{} are measured after adopting a isophote with fixed 
+    ellipticity and position angle. 
+    And the 10 kpc and 100 kpc here refer to the radius along the major axis of the 
+    elliptical isophote.
+    }
+
+%% ------------------------------------------------------------------------------------ %%
+
+    \song{
+    In Fig~\ref{fig:mass_diff}, we compare the different definitions of \mstar{}. 
+    As expected, directly measure light out to 100 kpc help recover more \mstar{} 
+    compared to \mcmodel{}.
+    At high-\mstar{} end (e.g. \logmtot{}$>11.6$), the average difference is larger 
+    than 0.1 dex and can be as large as 0.2--0.3 dex.  
+    For the \cmodel{} photometry in the current \texttt{hscPipe}, it relates to 
+    both the intrinsic limitations \cmodel{} algorithm and the over-subtracted 
+    background. 
+    In \S~\ref{ssec:sbp_compare}, we use the \mden{} profiles to show that large 
+    fraction of these galaxies have \mden{} profiles shallower than the de~Vaucouleurs 
+    one, it is therefore not surprising that \cmodel{} systematically underestimates 
+    the luminosity.
+    More importantly, the differences clearly depends on total stellar mass as 
+    \mcmodel{} tends to miss more \mstar{} in more massive galaxies.  
+    This relates to the mass-dependent nature of the stellar halos of massive 
+    galaxies (see \S~\ref{ssec:sbp_compare} too).
+    These differences have important implications for estimates of the stellar 
+    mass function and for studies of the environment-dependence of galaxy structure. 
+    }
+
+    \song{
+    The right panel of Fig~\ref{fig:mass_diff} compares \mmax{} and \mtot{}.  
+    Uncertainties in the background subtraction and the impact of neighbouring 
+    objects make \mmax{} more uncertain than \mtot{}. 
+    Nonetheless, we still see that \mmax{} becomes larger than \mtot{}. 
+    The differences are on average very small ($\sim0.02-0.03$ dex) and do not show 
+    strong mass dependence.  
+    This confirms that, at the current depth of HSC images, \mtot{} can be used as 
+    a good proxy of ``total'' stellar mass. 
+    }
 
@@
 %% ------------------------------------------------------------------------------------ %%        
-\subsection{``Total'' Stellar Masses}
-    \label{ssec:mtotal}
-
-    Using the best-fit \mstar{} from \texttt{iSEDFit} (noted as as \mcmodel{}), 
-    we estimate the average \m2l{} in the $i$-band, then use that \m2l{} to convert 
-    our 1-D luminosity density profiles into stellar mass density (\mden{}) profiles. 
-    We also convert our 10 and 100 kpc aperture luminosities into corresponding stellar 
-    mass estimates (noted as \minn{} and \mtot{}).
-
-    For the remainder of this paper, we will use \mtot{} as a proxy of ``total'' 
-    stellar mass. 
-    As expected, the integration of the 1-D profile out to very large radius recovers 
-    more luminosity (stellar mass) compared to the \cmodel{}-based estimates 
-    (Fig \ref{fig:mass_diff}).
-    At the high-\mstar{} end (e.g. \logmtot{}$>11.6$), the average difference is larger 
-    than 0.1 dex and can be as large as 0.2--0.3 dex.  
-    More importantly, the differences between \mtot{} and \mcmodel{} clearly show a 
-    dependence on total stellar mass as \mcmodel{} tends to miss more light in 
-    more massive galaxies.  
-    This relates to the mass-dependent nature of the stellar halos of massive 
-    galaxies and the intrinsic limitation of \cmodel{} method, which we will discuss
-    more in the next section.
-    Such differences also have important implications for estimates of the stellar 
-    mass function and for studies of the environment-dependence of galaxy structure. 
-    These topics will be discussed in \S~\ref{sec:discussion}.
-
-    Although 100 kpc is already a very large radius that should enclose the majority 
-    of stars that belong to these massive galaxies, we know that their \mden{} 
-    profiles extend beyond 100 kpc without showing any signs of truncation
-    (e.g. \citealt{Gonzalez2005, Tal2011, DSouza2014}).
-    Therefore, for massive galaxies, even \mtot{} should be only considered a lower
-    limit on the ``total'' \mstar{}. 
-    In Fig \ref{fig:mass_diff}, we integrate the \mden{} of each galaxy to the 
-    edge of the postage-stamp, and pick the isophote that gives us the highest  
-    luminosity to estimate the \mstar{} within and call this one \mmax{}. 
-    The right panel of Fig \ref{fig:mass_diff} compares \mmax{} and \mtot{}.  
-    Uncertainties in the background subtraction, and the impact of neighbouring 
-    objects, means that \mmax{} is much more uncertain than \mtot{}. 
-    Nonetheless, we do see that \mmax{} is larger than than \mtot{}. 
-    However, the mass differences are on average very small ($\sim0.02-0.03$ dex) and 
-    do not show a strong mass dependence.  
-    This confirms that, at the current depth of HSC images, \mtot{} can be used as 
-    a good proxy of ``total'' stellar mass.
-
-    Our methodology ignores radial variations in \m2l{}. 
-    It is well known that massive ETGs have negative optical color gradients 
-    indicating gradients in \m2l{} (e.g.\ \citealt{Carollo1993, Davies1993, 
-    LaBarbera2012, DSouza2015}). 
-    Assuming all massive galaxies in our sample have negative color gradients, and 
-    there is a simple monotonic relation between optical color and \m2l{}, the
-    average \m2l{} we used should in principle underestimate the \mstar{} in the 
-    center while overestimate the \mstar{} in the outskirt.
-    However, these color gradients are shallow and smooth out to a few times the 
-    effective radius (e.g. \citealt{LaBarbera2010, Tal2011, DSouza2014}, 
-    color gradients at larger radii are not yet well quantified). 
-    Because the gradients are shallow, using an average \m2l{} is unlikely to bias 
-    our results on \mstar{} measurements.  
-    In \citet{Huang2016}, the authors conduct multi-band decomposition for a sample 
-    of very nearby elliptical galaxies, and estimate the \m2l{} of each component 
-    separately. 
-    The sum of all components suggest a slightly higher \mstar{} ($0.05-0.10$ dex 
-    when typical uncertainty of \mstar{} is 0.12-0.15 dex) and the mass differences 
-    show no dependence on \mstar{}.
-
-    Color gradients will be discussed more in \S~\ref{ssec:ell_color}. 
-    In summary, our results about the mass dependence of \mden{} profiles should not 
-    be affected by the assumption of a constant \m2l{} ratio because optical color 
-    gradients in our sample do not show a dependence on stellar mass.
-
-    %Our results looking at the outer envelopes as a function of mass and environment 
-    %will be robust as long as there is \emph{no significant difference in 
-    %the average color gradient between sub-samples}.
-    %We have confirmed that this is indeed the case (see Section~\ref{ssec:ell_color}).
-
-    %We now compare our masses with those from the GAMA survey. Our method for deriving total \mstar{} is similar to the method adopted by the 
-    %GAMA survey (\citealt{Taylor2011, Kelvin2012}), where the average \m2l{} is from 
-    %SED fitting of PSF-matched aperture photometry and the total luminosity comes from 
-    %sing-\ser{} fits to SDSS images.  
-    %To avoid differences in stellar population assumptions, we directly compare the 
-    %total luminosity within 100 kpc and the GAMA single-\ser{} luminosity for the same
-    %galaxies.
-
-    %At high-\mstar{} end, the HSC 1-D profiles still recover more light than the 
-    %single-\ser{} model on average.
-    %It is likely that the GAMA models fail to capture the flux associated with the 
-    %outskirts of galaxies due to the limited depth of SDSS.  
-    %Meanwhile, there are also many cases where the high-\ser{} index of GAMA model leads 
-    %to over-estimated total luminosity. 
-    %We will discuss more of this comparison in the next paper of this series 
-    %(Huang\etal in prep.).
-
-    %We have compared our \mstar{} values with those from GAMA and the results are given 
-    %in Appendix~\ref{app:gama}.
-
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %%        
 \subsection{Stellar Mass Completeness}
@@
     we investigate the \mstar{} completeness of our samples. 
+    \song{
     The \texttt{S82-MGC} sample matches the deeper SDSS photometric data in the 
@@
     Kingdom Infrared Telescope Infrared Deep Sky Survey (UKIDSS; 
-    \citealt{Lawrence2007}). 
-    Comparing to normal SDSS images, the deeper photometry and better photo-$z$s 
-    from \texttt{S82-MGC} make this sample complete to \logms{}$\geq 11.2$ at $z<0.7$ 
+    \citealt{Lawrence2007}), and is complete to \logms{}$\geq 11.2$ at $z<0.7$. 
     which makes it sufficient to evaluate the completeness of our HSC sample. 
-	By comparing with the \texttt{S82-MGC} sample (\citealt{Bundy2015}), 
-	\citet{Leauthaud2016} have measured the \mstar{} completeness of the combined BOSS 
-	and SDSS samples. 
-    They estimate that the BOSS spec-$z$ sample, which is the main source of redshifts 
-    for our sample, is about 80\% complete at 
-    \logms{}$\geq 11.6$ at $0.3 < z < 0.5$. The GAMA survey is 80\% complete down to 
-    $10^{10.8}$\msun{} at $z{\sim} 0.3$, but is only 80\% complete to 
-    $10^{12.0}$\msun{} at $z{\sim} 0.5$ according to \citet{Taylor2011} (e.g.\ 
-    their Fig.~6).
-
-    There are 20453 \texttt{S82-MGC} galaxies that are also in the \texttt{hscPho} 
-    sample at $0.3 \leq z_{\mathrm{s82}} \leq 0.5$.  
-    Because the \texttt{S82-MGC} uses \cmodel{} magnitudes, in this section we use  
-    \mcmodel{} for consistency with the \texttt{S82-MGC} catalog.  
-    The \texttt{S82-MGC} also uses \texttt{iSEDFit} with similar assumptions as 
-    used in this work and we find excellent agreement between HSC \mcmodel{} and 
-    the mass derived by \texttt{S82-MGC} which includes NIR data from UKIDSS.
-
-    Figure~\ref{fig:mass_complete} compares the number density distributions of 
-    galaxies from \texttt{S82-MGC} with those from our sample\footnote{We do not 
-    apply any statistical corrections for completeness and hence we do not use the 
-    term ``stellar mass function'' to avoid confusion;
+    \citet{Leauthaud2016} uses this sample to show that the BOSS spec-$z$ sample, 
+    which is the main source of redshifts for us, is about 80\% complete at 
+    \logms{}$\geq 11.6$ at $0.3 < z < 0.5$.
+    }
+
+    \song{
+    Fig~\ref{fig:mass_complete} compares the number density distributions of 
+    galaxies from \texttt{S82-MGC} with the 20453 galaxies that are also in 
+    our sample\footnote{We do not apply any statistical corrections for completeness 
+    and hence we do not use the term ``stellar mass function'' to avoid confusion;
     Errors on the distributions are estimated via bootstrap resampling.}.
-    Based on Fig.~\ref{fig:mass_complete}, we conclude that our sample of massive 
-    galaxies is reasonably complete down to \logmcmodel{}${\sim} 11.5$ at 
-    $0.3 \leq z \leq 0.5$. 
-    %The \rbcg{} sample is less affected by completeness because we can utilize 
-    %photo-$z$s from \redm{}. 
-    %However, the completeness of the \nbcg{} sample is still limited by the 
-    %availability of spec-$z$s from BOSS.    
+    To be consistent with the \texttt{S82-MGC} catalog, we estimate the \mcmodel{}
+    of these galaxies using \texttt{iSEDFit}.
+    We find excellent agreement between HSC \mcmodel{} and the ones from the
+    \texttt{S82-MGC} catalog.
+    }
+
+    % The GAMA survey is 80\% complete down to 
+    % $10^{10.8}$\msun{} at $z{\sim} 0.3$, but is only 80\% complete to 
+    % $10^{12.0}$\msun{} at $z{\sim} 0.5$ according to \citet{Taylor2011} (e.g.\ 
+    % their Fig.~6).
+
+    \song{
+    We conclude that our sample of massive galaxies is reasonably complete down 
+    to \logmcmodel{}${\sim} 11.5$ at $0.3 \leq z \leq 0.5$.    
     Given the average difference between \mtot{} and \mcmodel{}, we will focus on 
-    galaxies with \logmtot{}$> 11.6$ where our sample shows good completeness. 
-    In our discussion section, we will also show results for massive galaxies 
+    galaxies with \logmtot{}$> 11.6$. 
+    In \S~\ref{sec:discussion}, we will also show results for massive galaxies 
     with $11.4 \le$\logmtot{}$<11.6$ but we caution that our sample is incomplete 
@@
     SDSS/BOSS spec-$z$ (see \citealt{Leauthaud2016}).
-
-    %When comparing \nbcg{} and \rbcg{} we will also always make sure that the two 
-    %samples are well matched both in terms of \mstar{} as well as in terms of redshift. 
-    %Please see the next section and Appendix~\ref{app:match} for more details.
-
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %%  
-\section{The Final Sample}
-    \label{sec:final}
-
-\subsection{Candidate massive central galaxies}
-    \label{ssec:redmapper}
-
-    \song{
-    Typically, ``central'' galaxy is defined as the galaxy locates in the center of 
-    its own dark matter halo, while the galaxy in a sub-halo that is orbiting within 
-    the virial radius of a more massive halo is referred to as a ``satellite'' 
-    (e.g.\citealt{Yang2007}).
-    We wish to focus on massive central galaxies here as they are uniquely important 
-    to the study of galaxy--halo connection.
-    Although the satellite fraction is expected to be very low ($<10$\%; e.g. 
-    \citealt{Reid2014, Hoshino2015, Saito2016}) at \logmtot{}$> 11.6$, we further use 
-    the \redm{} cluster catalog (\texttt{v5.10}; e.g.\ \citealt{Rykoff2014}; 
-    \citealt{Rozo2015b}) based on SDSS DR8 (\citealt{SDSS-DR8}) to help us 
-    identify centrals of cluster--level dark matter halos and reduce satellite
-    contamination.
-    }
-
-    \song{    
-    After matching the \texttt{hscZ} sample with the central galaxies of \redm{} 
-    clusters with richness $\lambda \geq 20$\footnote{Due to the depth and 
-    resolution of SDSS images, the \redm{} catalog is not complete down to 
-    $\lambda=20$ at $0.3 < z < 0.5$.  
-    At $z \geq 0.33$, it starts to miss a small fraction of clusters with 
-    $\lambda < 30$, but it will not affect the results in this work.}
-    and central probability $P_{\mathrm{Cen}} \geq 0.7$, we find 164 matched galaxies 
-    at $0.3 \leq z \leq 0.5$.
-    According to available calibration (e.g.\ \citealt{Saro2015, Farahi2016, 
-    Simet2016, Melchior2016}), they represent the central galaxies in dark matter 
-    halos with $\log (M_{\mathrm{halo}}/M_{\odot}) \geq 14.0$, and will be 
-    referred to as the \rbcg{} sample. 
-    }
-
-    \song{
-    As the next step, we identify and remove all galaxies within a cylindrical 
-    region around all \redm{} clusters. 
-    We use a radius equal to $R_{\mathrm{200b}}$ and the length of the cylinder is 
-    set to twice the value of the photometric redshift ($z_{\lambda}$) uncertainty 
-    of each cluster\footnote{We convert $\lambda$ of each cluster to 
-    $M_{\mathrm{200b}}$ using the calibration of \citet{Simet2016} and use the 
-    mass-concentration relation from \citet{Diemer2015} to compute 
-    $R_{\mathrm{200b}}$.}.
-    After removing galaxies associated with \redm{} clusters, the remaining galaxies 
-    in our sample will be dominated by central galaxies living in halos with 
-    \logmh{}$< 14.0$, and they will be referred to as the \nbcg{} sample.
-    Using the model presented in \citet{Saito2016}, we estimate that in dark matter 
-    halos with \logmh$<11.4$, $\sim 7$\% of galaxies with \logmcmodel{}$>11.5$ are 
-    satellites.
-    }
-    %% Saved as "dr1_redbcg_use_sed5b.fits"  
-    %% Saved as "dr1_nonbcg_use_sed5b.fits"
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %% 
-\subsection{Summary of Sample Construction}
-    \label{ssec:sample}
-
-    Using ${\sim} 100$ deg$^2$ of HSC data, we select a large sample of massive central 
-    galaxies with reliable redshift information, and broadly separate them into two 
-    categories based on $M_{\mathrm{halo}}$.
-
-    The following is a summary of our sample construction.
-
-    \begin{itemize}
-        \item \texttt{hscPho} sample: this parent sample consists of bright galaxies 
-            with $i_{\mathrm{cModel}} \leq 21.0$, good quality imaging, and reliable 
-            \texttt{cModel} photometry in all five HSC bands in the \texttt{S15B} 
-            data release. 
-            This sample is described in \S \ref{ssec:initial}, and it contains 
-            1760845 galaxies. 
-        \item \texttt{hscZ} sample: we limit the \texttt{hscPho} sample to galaxies 
-            with reliable redshift information. 
-            More details of this sample can also be found in \S \ref{ssec:initial}. 
-            It provides us 25286 useful galaxies at $0.3<z<0.5$.
-        \item With the help of the \redm{} cluster catalog, we further select 
-            candidates of massive central galaxies.
-            We broadly divide the sample into central galaxies living in halos
-            with \logmh{}$\geq 14.0$ (\rbcg{}) and \logmh{}$<14.0$ (\nbcg{}).
-            To ensure the sample is \mstar{}-complete and has minimal satellite 
-            contamination, we will further focus on the 950 massive galaxies with 
-            \logmtot{}$>11.6$ in this work\footnote{As reference, there are 
-            2613 massive galaxies with \logmtot{}$>11.5$ in our sample.}.
-
-    \end{itemize}
-
-    The division of our sample into two halo mass bins is mainly relevant for Paper II
-    (Huang \etal in prep.).  
-    For the present paper, we only consider the halo mass dependence on our sample when 
-    we evaluate impact of mass estimates on the SMF in \S \ref{ssec:smf}. 
-    We show the distributions of redshift, \mtot{} and \minn{} of the massive galaxy 
-    sample in Appendix \ref{app:basic}, along with its \mtot{}-$(g-r)$ rest-frame 
-    color relation.
+    }
 
@@
 %% ------------------------------------------------------------------------------------ %%  
+\section{The Final Sample}
+    \label{sec:final}
+
+%% ------------------------------------------------------------------------------------ %%  
+\subsection{Candidate massive central galaxies}
+    \label{ssec:redmapper}
+
+    \song{
+    Typically, ``central'' galaxy is defined as the galaxy locates in the center of 
+    its own dark matter halo, while the galaxy in a sub-halo that is orbiting within 
+    the virial radius of a more massive halo is referred to as a ``satellite'' 
+    (e.g.\citealt{Yang2007}).
+    We wish to focus on massive central galaxies here as they are uniquely important 
+    to the study of galaxy--halo connection.
+    Although the satellite fraction is expected to be very low ($<10$\%; e.g. 
+    \citealt{Reid2014, Hoshino2015, Saito2016}) at \logmtot{}$> 11.6$, we further use 
+    the \redm{} cluster catalog (\texttt{v5.10}; e.g.\ \citealt{Rykoff2014}; 
+    \citealt{Rozo2015b}) based on SDSS DR8 (\citealt{SDSS-DR8}) to help us 
+    identify centrals of cluster--level dark matter halos and reduce satellite
+    contamination.
+    }
+
+    \song{    
+    After matching the \texttt{hscZ} sample with the central galaxies of \redm{} 
+    clusters with richness $\lambda \geq 20$\footnote{Due to the depth and 
+    resolution of SDSS images, the \redm{} catalog is not complete down to 
+    $\lambda=20$ at $0.3 < z < 0.5$.  
+    At $z \geq 0.33$, it starts to miss a small fraction of clusters with 
+    $\lambda < 30$, but it will not affect the results in this work.}
+    and central probability $P_{\mathrm{Cen}} \geq 0.7$, we find 164 matched galaxies 
+    at $0.3 \leq z \leq 0.5$.
+    According to available calibration (e.g.\ \citealt{Saro2015, Farahi2016, 
+    Simet2016, Melchior2016}), they represent the central galaxies in dark matter 
+    halos with $\log (M_{\mathrm{halo}}/M_{\odot}) \geq 14.0$, and will be 
+    referred to as the \rbcg{} sample. 
+    }
+
+    \song{
+    As the next step, we identify and remove all galaxies within a cylindrical 
+    region around all \redm{} clusters. 
+    We use a radius equal to $R_{\mathrm{200b}}$ and the length of the cylinder is 
+    set to twice the value of the photometric redshift ($z_{\lambda}$) uncertainty 
+    of each cluster\footnote{We convert $\lambda$ of each cluster to 
+    $M_{\mathrm{200b}}$ using the calibration of \citet{Simet2016} and use the 
+    mass-concentration relation from \citet{Diemer2015} to compute 
+    $R_{\mathrm{200b}}$.}.
+    After removing galaxies associated with \redm{} clusters, the remaining galaxies 
+    in our sample will be dominated by central galaxies living in halos with 
+    \logmh{}$< 14.0$, and they will be referred to as the \nbcg{} sample.
+    Using the model presented in \citet{Saito2016}, we estimate that in dark matter 
+    halos with \logmh$<11.4$, $\sim 7$\% of galaxies with \logmcmodel{}$>11.5$ are 
+    satellites.
+    }
+    %% Saved as "dr1_redbcg_use_sed5b.fits"  
+    %% Saved as "dr1_nonbcg_use_sed5b.fits"
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
+\subsection{Summary of Sample Construction}
+    \label{ssec:sample}
+
+    Using ${\sim} 100$ deg$^2$ of HSC data, we select a large sample of massive central 
+    galaxies with reliable redshift information, and broadly separate them into two 
+    categories based on $M_{\mathrm{halo}}$.
+
+    The following is a summary of our sample construction.
+
+    \begin{itemize}
+        \item \texttt{hscPho} sample: this parent sample consists of bright galaxies 
+            with $i_{\mathrm{cModel}} \leq 21.0$, good quality imaging, and reliable 
+            \texttt{cModel} photometry in all five HSC bands in the \texttt{S15B} 
+            data release. 
+            This sample is described in \S \ref{ssec:initial}, and it contains 
+            1760845 galaxies. 
+        \item \texttt{hscZ} sample: we limit the \texttt{hscPho} sample to galaxies 
+            with reliable redshift information. 
+            More details of this sample can also be found in \S \ref{ssec:initial}. 
+            It provides us 25286 useful galaxies at $0.3<z<0.5$.
+        \item With the help of the \redm{} cluster catalog, we further select 
+            candidates of massive central galaxies.
+            We broadly divide the sample into central galaxies living in halos
+            with \logmh{}$\geq 14.0$ (\rbcg{}) and \logmh{}$<14.0$ (\nbcg{}).
+            To ensure the sample is \mstar{}-complete and has minimal satellite 
+            contamination, we will further focus on the 950 massive galaxies with 
+            \logmtot{}$>11.6$ in this work\footnote{As reference, there are 
+            2613 massive galaxies with \logmtot{}$>11.5$ in our sample.}.
+
+    \end{itemize}
+
+    The division of our sample into two halo mass bins is mainly relevant for Paper II
+    (Huang \etal in prep.).  
+    For the present paper, we only consider the halo mass dependence on our sample when 
+    we evaluate impact of mass estimates on the SMF in \S \ref{ssec:smf}. 
+    We show the distributions of redshift, \mtot{} and \minn{} of the massive galaxy 
+    sample in Appendix \ref{app:basic}, along with its \mtot{}-$(g-r)$ rest-frame 
+    color relation.
+
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
 \section{Results}
@@
 
-    The Stellar Mass Function (SMF) and its evolution are critical to our understanding 
-    of galaxy evolution. 
-    On average, the integration of our carefully derived non-parametric \mden{} profiles 
-    to 100 kpc (\mtot{}) recovers more light (hence mass) than the \texttt{cModel} method. 
-    At \logmtot{} $>11.6$, the difference can sometimes be larger than 0.2 dex. 
-    More importantly, the average difference steadily increases with \mtot{}. 
-    These differences relate to the intrinsic limitation of the \texttt{cModel} 
-    method and also reflect the fact that more massive ETGs tend to have more 
-    extended stellar mass distributions (e.g. higher-\ser{} index, 
-    \citealt{Graham2003}). Hence, the determination of the ``total luminosities'' of 
-    massive galaxies can result in a significant impact on the high mass end of the 
-    galaxy stellar mass function (e.g. \citealt{Bernardi2013, DSouza2014, DSouza2015,
-    Bernardi2017}).
-
-%    \footnote{To do that, one needs to 
-%    separate the differences in the measurements of luminosity and \m2l{}, and 
-%    take the uncertainties of \mstar{} measurements into account}
-
-    In this paper, we have only measured light profiles for central galaxies. 
-    Also, we cannot extract 1-D profiles for $\sim 11$\% of galaxies (because 
-    contamination from nearby bright object is too severe; or the its in a late-stage
-    on-going merger system). 
-    These two effects will lead to a ${\sim}20$\% uncertainty in the amplitude of 
-    our volume number density distributions. 
-    Both of these effects show dependence on \mtot{} whereas more massive galaxies 
-    suffer slightly less from them.
-    We are currently working to address these limitations in a forthcoming paper. 
-    Our goal in this paper is therefore not to attempt a detailed comparison between 
-    different SMFs \citep[e.g.,][]{Bernardi2013, Bernardi2017}. 
-    Instead, our goal in this section is simply to characterize the impact of various 
-    \mstar{} measurements on the high-mass end of the SMF.   
-    Our volume density distributions (will be referred to as SMF for simplicity) 
-    turn over at the low-mass end where the sample becomes incomplete, and we do not 
-    attempt to apply any completeness correction here.
-
-     Figure \ref{fig:smf} displays the impact of missing light and of different 
-     definitions of \mstar{} on the SMF. 
-     The left panel of Fig.~\ref{fig:smf} shows the SMF computed using \mcmodel{} 
-     and \mtot{} for galaxies that live in low and high mass halos.  
-     Figure \ref{fig:smf} shows that the impact of missing flux is more severe for  
-     galaxies in high mass halos. 
-     In Paper II of this series (Huang\etal in prep.), it will be demonstrated that 
-     this occurs because galaxies in more massive halos have more extended stellar 
-     envelopes than those in lower mass halos at fixed \mtot{}. 
-     Figure \ref{fig:smf} also shows that the use of the HSC \texttt{cModel} 
-     magnitude leads to a severe underestimation of \mstar{} at the high mass end 
-     of SMF. 
-     From the current \texttt{hscPipe}, this problem could relate to the intrinsic 
-     limitation of simply model like \cmodel{} and the issue of over-subtracted 
-     background. 
-     Based on the 1-D surface brightness profiles in $i$-band, background subtraction
-     does not seem to be the most serious problem for these $z>0.3$ galaxies 
-     (at least not within 100 kpc). 
-     And, in the next section, we will show that a significant fraction of these 
-     1-D profiles are more extended in the outskirt than the de~Vaucouleurs profile, 
-     therefore it is not surprising that \cmodel{} will systematically underestimate 
-     their total flux.
-
-     %According to \citet{Wright2017}, the $z{\sim}0.1$ GAMA SMF based on a single-\ser{} model from \citet{Kelvin2012} suffers from similar issues.
-    %appears to have the same issue (\citealt{Wright2017}),
-    %    although the \ser{} model
-    %also can overestimate the luminosity at high-mass end\footnote{Due to 
-    %overestimated \ser{} index and/or effective radius.}.
-
-    As discussed in \S~\ref{ssec:mtotal}, even with deep HSC images,
-    it is not trivial to clearly define and measure the ``total'' \mstar{} for 
-    these massive systems, and the \mden{} profiles of these galaxies often extend 
-    well beyond 100 kpc. 
-    Is our fiducial 100 kpc radius sufficient to capture most of the flux associated 
-    with these galaxies, or does one need to integrate out to even larger radii? 
-    To answer this question, we attempt to capture more flux by integrating our 
-    \mden{} profiles out to the edge of the image and use the highest \mstar{} 
-    achieved during this process as \mmax{}.
-    Although the \mden{} profiles become more uncertain at $>100$ kpc, \mmax{} helps 
-    us quantify how much extra \mstar{} may be contained at radii greater than 100 kpc.  
-    The right hand side of Figure \ref{fig:smf} shows the impact of using \mmax{} 
-    instead of  \mtot{} on the SMF.  
-    We find that a 100 kpc radius captures a majority of the galaxy mass and that the 
-    impact of going from \mtot{} to \mmax{} is relatively small.
-
-    In Figure \ref{fig:smf} we also compare our results with the following previous 
-    studies:
+    \song{
+    The stellar mass function (SMF) is critical to our understanding of 
+    galaxy evolution.
+    Photometric method and definitions of \mstar{} can affect the 
+    high-\mstar{} end of SMF (e.g. \citealt{Bernardi2013, dSouza2015, Bernardi2017}). 
+    Above works show that, despite being widely adopted in literatures, \cmodel{} 
+    photometry can significantly underestimate the \mstar{} of massive galaxies. 
+    But these works are still based on more complex 2-D modeling or stacking of 
+    shallow images that suffer from various systematics.
+    Now, we characterize the impacts of different photometric measurements on the 
+    high-\mstar{} end of the SMF using \mstar{} directly measured out to large 
+    radius on deep images (see Fig~\ref{fig:smf}).
+    }
+
+    \song{
+    The left panel of Fig~\ref{fig:smf} show the volume density distributions 
+    (will be referred to as SMF for simplicity) of massive galaxies using \mcmodel{} 
+    and \mtot{} for both the \rbcg{} and \nbcg{} samples.  
+    As shown in Fig~\ref{fig:mass_diff}, the mass-dependent differences between these
+    two measurements lead to noticeable differences in SMF at high-\mstar{} end.
+    \cmodel{} photometry leads to underestimation of volume density at the high-\mstar{} 
+    end of SMF. 
+    More importantly, it shows that the impact of missing \mstar{} becomes more 
+    significant for central galaxies in very massive halos. 
+    We will demonstrate that this occurs because galaxies in more massive halos 
+    have more extended stellar envelopes than those in lower mass halos at fixed 
+    \mtot{} in a following work (Huang\etal in prep.).
+    On the right panel of Fig~\ref{fig:smf}, we also compare the SMFs using \mtot{} and 
+    \mmax{}. 
+    As mentioned in \S~\ref{ssec:mtotal}, \mtot{} is still a lower limit of the total 
+    \mstar{} of these massive galaxies, and \mmax{} help us check how much \mstar{} 
+    could be left out.  
+    Although there is still visible difference at the high-\mstar{} end, the impact
+    of going from \mtot{} to \mmax{} is relatively small. 
+    It suggests that \mtot{} captures the majority of the total \mstar{}.
+    Here we do not attempt to apply any completeness correction so the SMFs turn over 
+    at the low-\mstar{} end. 
+    For now, we add a constant ${\sim}20$\% uncertainty to the SMF to account for the 
+    satellite galaxies and the ones we fail to extract 1-D profiles 
+    (see Appendix~\ref{app:ellipse}), although these uncertainties should be smaller 
+    at high-\mstar{} end. 
+    }
+
+    \song{
+    On the right panel of Fig~\ref{fig:smf}, we also compare our SMFs with the 
+    following works:
+    }
 
@@
 
-        \item The SMF for $0.15 < z < 0.30$ galaxies from the \texttt{S82-MGC} sample
-            \citep{Leauthaud2016} where \mstar{} is derived using 
-            \texttt{iSEDfit} on PSF-corrected aperture photometry from \texttt{S82}. 
-            They adopt the same IMF, dust model, and star-formation model as we do, 
-            but use the \texttt{BC03} model instead. 
-            Based on the test results in Appendix \ref{app:sed}, we shift this SMF by 
-            0.08 dex to add their data to Figure~\ref{fig:smf}.
+        \item \song{
+            The SMF of $0.15 < z < 0.30$ galaxies from the \texttt{S82-MGC} sample
+            \citep{Leauthaud2016} where \mstar{} is based on PSF--matched aperture
+            photometry and \texttt{iSEDfit} fitting using \texttt{BC03} model.
+            We account for the 0.08 dex average difference with the \texttt{FSPS} ones
+            seen in the Appendix~\ref{app:sed}
+            }
 
@@
 
-    As mentioned above, our current SMF is subject to an additional 20\% uncertainty 
-    that will be addressed in forthcoming work. 
-    Hence, we do not attempt a detailed comparison with respect to previous works on 
-    the SMF, reserving this for a future study. 
-    Here, we simply note that the HSC SMF derived using \mtot{} is close to the one 
-    derived by \citet{Bernardi2017} using SDSS data at $z{\sim}0.1$ and assuming 
-    the \texttt{SerExp} models.  
-    Our sample and the \citet{Bernardi2017} sample have different redshifts. 
-    Without a more in-depth study, we cannot ascertain whether or not the apparent 
-    agreement between the HSC SMF and the \citet{Bernardi2017} SMF indicates a global 
-    lack of evolution in the galaxy SMF, or that other effects are at play 
-    (for example, the difference between \mtot{} masses and \texttt{SerExp} masses) 
-    that have cancelled redshift evolution.  
-    In future work, it will be interesting to perform a more consistent analysis to 
-    search for redshift evolution in the galaxy SMF and to study whether or not 
-    massive galaxies in HSC are well described by \texttt{SerExp} models.
-
-    % TODO: Move this to Paper II
-    %In this work, we have opted to in general use \mtot{} rather than \mmax{} as the 
-    %uncertainty on \mmax{} is larger. 
-    %However, we have checked that none of our results are changed by replacing \mtot{} 
-    %via \mmax{}.
-
-%    The high-mass end of SMF is crucial for tracing the evolution of massive galaxies.  It is also  very sensitive to
-
-%    And due to its sensitivity to physical process like the AGN-feedback, it is also 
-%    important in calibrating simulation and semi-analytic model.
-
-%    Here, using individual \mden{} profiles, we confirm that shallow images and/or
-%    simplified models often lead to underestimated \mstar{} at high-mass end that 
-%    can not be ignored.
+    \song{ 
+    Due to several systematics (see e.g. \citealt{Bernardi2013, Bernardi2017}), we 
+    \emph{do not} attempt to perform detailed comparisons among these SMFs.
+    We are currently working to address these issues in a forthcoming paper. 
+    Here we simply note that the HSC \mtot{} SMF is closer to the one 
+    derived by \citet{Bernardi2017} using SDSS data at $z{\sim}0.1$ and the 
+    \texttt{SerExp} model.
+    Meanwhile, the differences between the HSC \mtot{} SMF with the others are 
+    likely caused by the photometric methods: SDSS \cmodel{} and small aperture 
+    photometry underestimate \mstar{} of massive galaxies.  
+    Even before a more in--depth study, it already illustrates an important issue:
+    \textbf{It is crucial to understand the impacts from photometric data and 
+    methods on the estimates of SMF} before using it to study galaxy evolution or 
+    comparing it with predictions from models and simulation. 
+    This is particularly relevant since method like \cmodel{} will still be widely 
+    adopted in on-going and future imaging surveys.
+    }
+
+    %Without a more in-depth study, we cannot ascertain whether or not the apparent 
+    %agreement between the HSC SMF and the \citet{Bernardi2017} SMF indicates a global 
+    %lack of evolution in the galaxy SMF, or that other effects are at play 
+    %(for example, the difference between \mtot{} masses and \texttt{SerExp} masses) 
+    %that have cancelled redshift evolution.  
+    %In future work, it will be interesting to perform a more consistent analysis to 
+    %search for redshift evolution in the galaxy SMF and to study whether or not 
+    %massive galaxies in HSC are well described by \texttt{SerExp} models.
 
@@
 
-    From Figure~\ref{fig:avg_prof} we can see the galaxies in our sample have 
+    From Fig~\ref{fig:avg_prof} we can see the galaxies in our sample have 
     homogeneous profiles on small radial scales. 
@@
     Schombert2015}; and kinematic: e.g. \citealt{Cappellari13b}) properties.  
-    However, Figure~\ref{fig:avg_prof} reveals a significant diversity in the outer 
+    However, Fig~\ref{fig:avg_prof} reveals a significant diversity in the outer 
     envelopes of massive galaxies.  
     Given the \s2n{} of HSC images at these surface brightness levels, the scatter 
-    shown in Figure~\ref{fig:avg_prof} corresponds to \textbf{intrinsic scatter in 
+    shown in Fig~\ref{fig:avg_prof} corresponds to \textbf{intrinsic scatter in 
     the stellar envelopes of massive galaxies}. 
-    Importantly, Figure~\ref{fig:avg_prof} shows that the global \mden{} profiles 
+    Importantly, Fig~\ref{fig:avg_prof} shows that the global \mden{} profiles 
     of galaxies at these masses are \textbf{clearly not self-similar} out to 100 
@@
     Results can also depend on the stacking technique or the model used to extract 
-    the profile (e.g., \citealt{Tal2011, DSouza2015}). 
+    the profile (e.g., \citealt{Tal2011, DSouza2014}). 
     \citet{Huang2013a} derived \mden{} profiles for a small sample of very nearby 
@@
 	we will discuss this more in Paper II). 
-
-	If accreted stars dominate the stellar halos of massive galaxies, this 
-	mass-dependent ellipticity profile may contain clues about the assembly history 
-	of massive galaxies (e.g. average time since last merger, average merger 
-	mass ratio).
-	Previous simulations often focused on reproducing the rounder average shape 
-	and slow-rotating nature of massive ETGs (e.g. \citealt{Wu2014}), and the 
-	projected ellipticity profiles and their correlations with the kinematic of 
-	stars and merging history have not been carefully explored.
-
-    Regarding the color profiles, it is well known that massive elliptical galaxies 
-    have shallow and negative color gradients that reflect radial variations in their  
-    stellar populations (e.g.\ \citealt{Carollo1993, LaBarbera2012}) and hence contain
-    information about the assembly history of their stellar halos (e.g. 
-    \citealt{Hirschmann2015}). 
-    The right panels of Fig \ref{fig:ell_color} show the $k$-corrected $(g-r)$ and 
-    $(g-i)$ color profiles for all galaxies in our sample, together with the median 
-    profiles in three \mtot{} bins. 
-    We find the the median rest-frame $(g-r)$ and $(g-i)$ color decreases at 
-    larger radii, but there does not appear to be a significant \mstar{} dependence 
+	\song{
+	As mentioned in \S~\ref{sec:intro}, such mass-dependent ellipticity profile
+	could show us more insights about the assembly of stellar halos of massive
+	galaxies. 
+	}
+
+    \song{
+    Regarding the color profiles, the right panels of Fig \ref{fig:ell_color} show 
+    the $k$-corrected $(g-r)$ and $(g-i)$ color profiles for all galaxies in our 
+    sample, together with the median profiles in three \mtot{} bins. 
+    We find the the median rest-frame $(g-r)$ and $(g-i)$ color profiles present 
+    smooth and shallow negative color gradients out to 50--60 kpc, as observed by 
+    many previous works (e.g. \citealt{Carollo1993, LaBarbera2012}) and predicted 
+    by some simulations (e.g. \citealt{Hirschmann2015}). 
+    Meanwhile, there does not appear to be a significant \mstar{} dependence 
     in the gradient of rest-frame optical colors. 
+    }
     We also compare our results with the stacked color profiles from  
@@
     (e.g. \citealt{Wu2005}, \citealt{Tal2011}).  
-    This is due to the fact that the SDSS $i$-band PSF has more prominent wing 
-    than other bands. 
+    This is likely due to the fact that the SDSS $i$-band PSF has more prominent 
+    wing than other bands. 
     Because the PSF model does not capture these wings, this artificially distributes 
@@
     and can be used to determine galaxy colors with higher accuracy. 
-
-%    For the ones from \citet{LaBarbera2010}, uncertainty of $R_{\mathrm{e}}$ 
-%    measurements could also ``smooth'' the color gradients.
-
     Fairly steep color profiles have been observed in several very nearby massive 
@@
 
+    \song{
+    It is worth mentioning that the individual color profiles still show large 
+    scatter and unphysical trends in the outskirt.  
+    Color profile in the low surface brightness region is very sensitive to the 
+    noise level, contamination of other objects, and uncertainties in background 
+    subtraction. 
+    The HSC $g$-band images are relatively shallower and the backgrounds from the
+    two bands are not jointly constrained. 
+    Therefore, we only show the average color profiles here, and will conduct 
+    more careful study of the color profiles in a following work.
+    }
+
     % TODO: Move to discussion
@@
     %\citealt{Vogelsberger2014}, \citealt{Genel2014}) or \textit{Horizon-AGN}
-    %(\citealt{Dubois2014}).
-
-    % TODO: Move this to Paper II 
-    %The ellipticity profiles of the \mtot{}-matched samples are very similar at 
-    %$r<50$ kpc (2-3$\times R_{\mathrm{e}}$ for their \mstar{}). 
-    %However, for the \minn{}-matched samples, the \rbcg{} galaxies have higher 
-    %ellipticity than the \nbcg{} ones at $r > 10$ kpc, while their inner ellipticity 
-    %profiles are very similar.  
-    %This further hints that massive central galaxies in different halos but with 
-    %similar ``in situ'' mass may experience different late-time merging histories. 
-    %Overall, the relative low ellipticity value and the fact that the ellipticity 
-    %gradients are shallow lead us to conclude that the use of an average 
-    %isophotal ellipticity is fine for this present study.
-    %We show the average ellipticity, $g-r$, and $g-i$ color profiles for the 
-    %\mtot{}-matched (\minn{}-matched) samples of \rbcg{} and \nbcg{} galaxies on the 
-    %left (right) side of \ref{fig:ell_color}. 
-    %We also compare our results with previous work based on stacking SDSS galaxies 
-    %(e.g. \citealt{LaBarbera2010, Tal2011, DSouza2014}).
-
-    %In terms of color gradients, we find shallow and negative gradients of median 
-    %$g-r$ and $g-i$ color profiles for both \rbcg{} and \nbcg{} galaxies. 
-    %For both \mtot{}- and \minn{}-matched samples, we find no significant difference
-    %in their median color profiles, which supports the assumption of using single 
-    %average \m2l{} value to estimate \mden{} profiles.
+
 %% ------------------------------------------------------------------------------------ %%
@@
 
-    % TODO: Move to paper II     
-    %State of the art hydrodynamic simulations suggest that massive dark matter halos 
-    %have central galaxies that have outer stellar envelopes with shallow slopes 
-    %(e.g. \citealt{Pillepich2014}). 
-    %This is consistent with the results in Fig \ref{fig:prof_1}.
-
-    %Hence, according to this picture, the outer stellar envelopes of massive centrals 
-    %should correlate with the masses of their host halos, in qualitative agreement with
-    %our findings.
-
 %% ------------------------------------------------------------------------------------ %% 
@@
     our \textit{ex situ} fraction proxy, the almost perfect agreement seen in 
-    Figure \ref{fig:discussion_1} may well be a coincidence.  
+    Fig~\ref{fig:discussion_1} may well be a coincidence.  
     However, it is encouraging to see that our simple proxy for the fraction of 
@@
     $0.3 < z < 0.5$ where the sample is fairly complete in \mtot{}.
-
-    % TODO: Move to Paper II
-    % At fixed \mtot{}, we see little offset in color distributions of the two 
-    % samples, suggesting that both samples consist of quiescent galaxies with 
-    % similar average stellar population properties.  
-    % This is consistent with previous result that suggests the average stellar 
-    % population of massive central galaxy does not depend on \mhalo{} 
-    % (e.g.\ \citealt{Park2007}).  
-    % In this work, we focus on the \mstar{} range of $11.6 \le$\logmtot{}$\le 11.9$, 
-    % where both samples have acceptable completeness, and their \mtot{} distributions 
-    % greatly overlap (see the normalized distributions of \mtot{} in the bottom-left 
-    % panel of Fig~\ref{fig:sample_stats}). 
-    % As for the \minn{} distributions, the two samples overlap the most within 
-    % $11.2 \le$\logmtot{}$\le 11.6$, but now they show quite different
-    % distributions (bottom-right figure).
-
-    % The redshift distributions also show small difference
-    % (upper-right panel) even in the high-\mtot{} bin, where the redshift distribution 
-    % of the \nbcg{} sample skews toward higher-$z$ end due to the contribution of BOSS 
-    % spec-$z$.
 
@@
     \end{enumerate}
+
+    \song{
+    We should also point out that our methodology ignores radial variations in \m2l{}. 
+    It is well known that massive ETGs have negative optical color gradients 
+    indicating gradients in \m2l{} (e.g.\ \citealt{Carollo1993, Davies1993, 
+    LaBarbera2012, DSouza2015}). 
+    Assuming all massive galaxies in our sample have negative color gradients, and 
+    there is a simple monotonic relation between optical color and \m2l{}, the
+    average \m2l{} we used should in principle underestimate the \mstar{} in the 
+    center while overestimate the \mstar{} in the outskirt.
+    However, these color gradients are shallow and smooth out to a few times the 
+    effective radius (e.g. \citealt{LaBarbera2010, Tal2011, DSouza2014}, 
+    color gradients at larger radii are not yet well quantified). 
+    Because the gradients are shallow, using an average \m2l{} is unlikely to bias 
+    our results on \mstar{} measurements.  
+    In \citet{Huang2016}, the authors conduct multi-band decomposition for a sample 
+    of very nearby elliptical galaxies, and estimate the \m2l{} of each component 
+    separately. 
+    The sum of all components suggest a slightly higher \mstar{} ($0.05-0.10$ dex 
+    when typical uncertainty of \mstar{} is 0.12-0.15 dex) and the mass differences 
+    show no dependence on \mstar{}. 
+    Color gradients are discussed in \S~\ref{ssec:ell_color}. 
+    In summary, our results about the mass dependence of \mden{} profiles should not 
+    be affected by the assumption of a constant \m2l{} ratio because optical color 
+    gradients in our sample do not show a dependence on stellar mass.
+    }
+
 %% ------------------------------------------------------------------------------------ %%

### 2017-11-15 draft/paper1_v15.tex
Final edits

--- 2017-10-17 draft/paper1_v14.tex
@@
 
-\documentclass[a4paper,fleqn,usenatbib]{mnras}
+\documentclass[fleqn,usenatbib]{mnras}
 
@@
 \newcommand{\song}[1]{\textcolor{cyan}{\textbf{#1}}}
+\newcommand{\susan}[1]{\textcolor{Bittersweet}{\textbf{#1}}}
 \newcommand{\alexie}[1]{\textcolor{blue}{\textbf{[Alexie: #1]}}}
@@
 %% ------------------------------------------------------------------------------------ %% 
-\title[Mass Dependent Stellar Halos in Massive Galaxies]{Individual Stellar Halos of 
+\title[Mass Dependent Stellar Haloes in Massive Galaxies]{Individual Stellar Haloes of 
 	   Massive Galaxies Measured to 100 kpc at $0.3<z<0.5$ using Hyper Suprime-Cam}
-% \title[Mass Dependent Stellar Halo in Massive Galaxies]{Tracing the Stellar Halos of 
-% 	   Massive Galaxies to 100 kpc at $0.3<z<0.5$ using Hyper Suprime-Cam}
 
@@
     \song{
-    The stellar halo of massive galaxy can extend to several hundreds of kilo 
-    parsecs and provide important fossil record of galaxy assembly.
-    Using the wide (${\sim}100$ deg$^2$) and deep ($>28.5$ \sb{} in $i$-band) images 
-    from the Hyper Suprime-Cam (HSC) Subaru Strategic Program (SSP), we study 
-    the stellar halos of a sample of $\sim7000$ massive galaxies at 
-    $0.3 < z < 0.5$ with $\log M_{\star}/M_{\odot} > 11.4$ by tracing their  
-    surface mass density profiles to 100 kpc individually. 
-    The stellar halo of massive galaxy exhibit higher intrinsic diversity in their 
-    outer surface density profile and higher ellipticity than the inner region. 
-    We find that more massive galaxy on average shows more prominent outer stellar 
-    halo with shallower surface density profiles.
+    Massive galaxies display extended light profiles that can reach several 
+    hundreds of kiloparsecs. 
+    We use data from the Hyper Suprime-Cam (HSC) survey that is simultaneously wide 
+    (${\sim}100$ deg$^2$) and deep ($>28.5$ \sb{} in $i$-band) to study the stellar 
+    haloes of a sample of $7000$ massive galaxies at $z=0.4$. 
+    The depth of the HSC data enables us to measure surface mass density profiles 
+    to 100 kpc for individual galaxies without stacking. 
+    As in previous work, we find that more massive galaxies exhibit more extended outer 
+    profiles than smaller galaxies.  
+    When this extended light is not properly accounted for (because of shallow imaging 
+    and/or inadequate profile modeling), the derived stellar mass function can be 
+    significantly underestimated at the high mass end.  
+    Across our sample, the ellipticity of outer light profiles increases substantially 
+    as we probe larger radii.  
+    }
     We show for the first time that these ellipticity gradients steepen dramatically as 
     a function of galaxy mass, but we detect no mass-dependence in outer color gradients. 
-    }
     Our results support the two-phase formation scenario for massive galaxies in which 
-    outer envelopes are built up at late times from a series of merging events.
-    \song{
-    These results also emphasize the importance of accounting for the the extended 
-    stellar halos of massive galaxies when estimating their stellar masses. 
-    Shallow image or inadequate profile model often leads to significantly 
-    underestimated masses.
-    We provide surface mass surface mass density profiles to facilitate comparisons 
-    with predictions from hydrodynamic simulations and other observations.
-    }
+    outer envelopes are built up at a later time from a series of merging events. 
+    We provide surface mass density profiles in a convenient tabulated format 
+    to facilitate comparisons with predictions from numerical simulations of 
+    galaxy formation.
 
@@
     galaxies: structure -- 
-    galaxies: surveys
+    survey 
 \end{keywords}
@@
     Massive early-type galaxies (ETGs) are predicted to assemble according to a 
-    ``two-phase'' formation scenario 
-    (e.g. \citealt{Oser2010, Oser2012}): A rapid growth phase at high-redshift that 
+    `two-phase' formation scenario 
+    (e.g. \citealt{Oser2010, Oser2012}): a rapid growth phase at high-redshift that 
     is dominated by intense dissipative \textit{in situ} star formation (e.g.
@@
     is driven by non-dissipative processes such as dry mergers 
-    (e.g. \citealt{Naab2006, Khochfar2006}), especially the minor ones 
+    (e.g. \citealt{Naab2006, Khochfar2006}), with an important role played by 
+    minor mergers 
     (e.g. \citealt{Hilz2012, Hilz2013, Oogi2013, Bedorf2013, Laporte2013}).
@@
     (SAM; e.g. \citealt{LeeYi2013, LeeYi2017}) agree that the fraction of stellar 
-    mass accreted in the second phase (\textit{ex situ} component) should increase 
+    mass accreted in the second phase (the \textit{ex situ} component) should increase 
     with total galaxy stellar mass (e.g. \citealt{Lackner2012, Cooper2013, Qu2017}).
@@
     (\citealt{Vogelsberger2014}, \citealt{Genel2014}) predict that the fraction of  
-    accreted stars increases significantly and reaches $f_{\mathrm{accreted}}>0.5$ at 
-    \logms{}$>11.5$ (\citealt{RodriguezGomez2016})\footnote{The Illustris simulation
-    does not reproduce the observed stellar mass function at high \mstar{} end.}. 
-%% ------------------------------------------------------------------------------------ %%
-
-    \song{
-    Given the success of the ``two-phase'' scenario in explaining the properties of 
+    accreted stars increases significantly with galaxy mass, reaching
+    $f_{\mathrm{accreted}}>0.5$ at \logms{}$>11.5$ 
+    (\citealt{RodriguezGomez2016})\footnote{The Illustris simulation
+    does not reproduce the observed stellar mass function at the high mass end.}. 
+%% ------------------------------------------------------------------------------------ %% 
+    \song{
+    Given the success of the `two-phase' scenario in explaining the properties of 
     high-$z$ massive quiescent galaxies (e.g. \citealt{vanDokkum2010, vanderWel2011,
@@
     this model with additional observations, in particular, the detailed surface 
-    mass density profiles of low redshift massive galaxies. 
+    mass density profiles of low-redshift massive galaxies. 
     }
@@
     mass density profiles of nearby ETGs are well described by single-\ser{} profiles 
-    (e.g. \citealt{Kormendy2009}; except for the most central region) and that the 
+    (e.g. \citealt{Kormendy2009}; except for the most central regions) and that the 
     \ser{} index increases with total luminosity 
     (e.g. \citealt{Graham2013}). 
-    However, recently, detailed empirical comparison of surface brightness profiles 
-    revealed a more complicated situation showing that ETGs belong to two families, 
+    A more recent study of the surface brightness profiles of ETGs 
+    revealed that ETGs belong to two families: 
     those that follow single-\ser{} law, versus those that significantly deviate from 
@@
     Two-dimensional analyses have also found that the stellar distributions of massive 
-    ETGs are often better fit by multiple-component models 
+    ETGs are often better described by multiple-component models 
     (e.g. \citealt{Huang2013a, Oh2017}).  
-    \citet{Huang2013b} further suggest a connection between the multi-component 
-    nature of massive galaxies and their two-phase assembly history. 
+    \citet{Huang2013b}, further suggesting a connection between the multi-component 
+    nature of massive galaxies and their two-phase assembly histories.
+
     To further confront the two-phase scenario requires very deep observations of 
     large samples of massive ETGs to correctly estimate their total stellar masses
-    (e.g. \citealt{Bernardi2013, DSouza2014}) as well as to quantify the amplitude and 
+    (e.g. \citealt{Bernardi2013, DSouza2014}), as well as to quantify the amplitude and 
     scatter among outer envelopes (e.g. \citealt{Capaccioli2015, Iodice2016, 
@@
     \song{
-    Until now, deep \mden{} profiles of massive galaxies are rarely available. 
+    To date, large samples of massive galaxies with deep imaging have been lacking. 
     Even in the nearby universe, it is not trivial to map the low surface
@@
     \citealt{Capaccioli2015, Iodice2016, Iodice2017, Spavone2017, Mihos2017}). 
-    Some of these measurements are based on image stacking method (e.g. 
-    \citealt{Tal2011, dSouza2015}) that suffers from several systematics. 
+    Some of these measurements are based on image stacking methods (e.g. 
+    \citealt{Tal2011, dSouza2015}). 
     The number of very massive galaxies is also very limited in the local universe.
@@
     \song{
-    Besides the mass density profiles, the radial profile of ellipticity also 
+    In addition to mass density profiles, the radial profile of ellipticity also 
     contains information about the 3-D geometry (e.g. \citealt{Tremblay1995, 
@@
     (e.g. \citealt{Cappellari2012, Weijmans2014}) of stars in massive galaxies.
-    If the stellar halos of massive galaxies are indeed dominated by accreted 
+    If the stellar haloes of massive galaxies are indeed dominated by accreted 
     stars, their ellipticities could be systematically different with the inner 
-    regions and contain clues about the assembly history of massive galaxies 
+    regions and may contain clues about the assembly history of massive galaxies 
     (e.g. average time since last merger, average merger mass ratio).
     These issues have not been fully explored in both simulation and observation.
-    Certain simulation predicts more massive ETG should have rounder shape
+    Certain simulation predicts that a more massive ETG should have rounder shape
     (e.g. \citealt{Wu2014}), while others generate massive galaxies with very 
     elongated haloes (e.g. \citealt{Li2017}).  
-    On the observational side, constraints are only available from few works 
-    using either image stacking method (e.g. \citealt{Tal2011, dSouza2015}) or 
-    small sample of nearby galaxies (e.g. \citealt{Spavone2017}).
-    }
-
-    \song{
-    In this paper, we take advantage of the high--quality and deep images from the 
-    Hyper Suprime-Cam (HSC) Subaru Strategic Program \citep[SSP,][]{HSC-DR1} 
+    On the observational side, constraints are only available from a few works 
+    that use either an image stacking method (e.g. \citealt{Tal2011, dSouza2015}) 
+    or a small sample of nearby galaxies (e.g. \citealt{Spavone2017}).
+    }
+
+    \song{
+    In this paper, we take advantage of the high-quality deep images from the 
+    Hyper Suprime-Cam (HSC) Subaru Strategic Program (SSP) \citep[SSP,][]{HSC-DR1} 
     (see \S~\ref{ssec:hsc} for details) to characterize  the light profiles of 
@@
     at $0.3 < z < 0.5$ using ${\sim} 100$ deg$^2$ of data from the HSC wide layer. 
-
-    In this paper, we use this sample to 
-    (a) reliably estimate individual surface mass density (\mden{}) profiles of 
+    %\susan{Note that MNRAS requirement is to use British spelling; however, 
+    %they also prefer the -ize variant of word such as recognize, criticize, 
+    %minimize, emphasize, organize, ionize, polarize, parametrize (etc.).}
+
+    We use this sample to 
+    (1) reliably estimate individual surface mass density (\mden{}) profiles of 
     massive galaxies out to 100 kpc, 
-    (b) investigate the dependence of their outer stellar halos on total stellar 
+    (2) investigate the dependence of their outer stellar haloes on total stellar 
     mass, and 
-    (c) examine the implications in terms of evaluating the high mass end of the 
+    (3) examine the implications in terms of evaluating the high mass end of the 
     galaxy stellar mass function (SMF). 
-    In a second paper in this series, we will investigate the environmental 
-    (dark matter halo mass) dependence of the sizes of massive ETGs 
-    (Huang\etal in prep.).
+    In a second paper in this series (Huang \etal in prep.), we will investigate 
+    the environmental (dark matter halo mass) dependence of the sizes of massive 
+    ETGs (Huang\etal in prep.).
 
@@
     \S~\ref{sec:mstar} describes how we estimate stellar mass.
-    \S~\ref{sec:final} summaries the final sample selection procedure. 
+    \S~\ref{sec:final} summarizes the final sample selection procedure. 
     Our main results are presented in \S~\ref{sec:result} and discussed in 
@@
 
-    Magnitudes use the AB system (\citealt{Oke1983}), and are corrected for Galactic 
+    Magnitudes use the AB system (\citealt{Oke1983}), and are corrected for galactic 
     extinction using calibrations from \citet{Schlafly11}.
@@
 
-    Halo mass is defined as $M_{\rm 200b}$ as 
+    Halo mass is defined as 
     $M_{\rm 200b}\equiv M(<r_{\rm 200b})=200\bar{\rho} 
@@
 
-    Finally, we emphasize that in this work, we do not attempt to disentangle the 
-    galaxy light from any ``intra-cluster'' light component (ICL; e.g. 
+    We emphasize that in this work we do not attempt to disentangle the 
+    galaxy light from any `intra-cluster' light component (ICL; e.g. 
     \citealt{Carlberg1997, Lin2004, Gonzalez2005, Mihos2005}). 
@@
     brightest cluster galaxy (BCG)
-    hints at a kinematically separated ICL component (e.g. 
+    hints at a kinematically separated intra--cluster light (ICL) component (e.g. 
     \citealt{Dressler1979, Carter1999, Kelson2002, Bender2015, Longobardi2015}),
-    it is extremely difficult to reliably isolate them photometrically.
-    Moreover, both the stellar halo of main galaxy and the ICL component carry 
-    important information regarding the assembly history of central galaxy and its 
+    it is extremely difficult to reliably isolate it photometrically.
+    Moreover, both the stellar halo of the main galaxy and the ICL component carry 
+    important information regarding the assembly history of the central galaxy and its 
     dark matter halo. 
@@
         \caption{
-            Left: example of the 1-D surface brightness and ellipticity profile 
-            of a massive galaxy at $z=0.23$ in the $i$-band extracted using 
+            \textbf{Left}: Example of the 1-D surface brightness and ellipticity 
+            profile of a massive galaxy at $z=0.23$ in the $i$-band extracted using 
             \texttt{Ellipse}. 
@@
             most strongly affected by seeing.
-            The grey shaded region highlights the region ($r<6$ kpc) that is equivalent 
+            The grey shading highlights the region ($r<6$ kpc) that is equivalent 
             to twice the size of the half-width of a 1\asec{} seeing at $z\sim 0.5$.
-            It is a very conservative estimate of the region that we can not reliable 
-            extract 1-D profile due to the smearing effect of seeing.
+            Because it is a very conservative estimate of the region, we cannot reliably 
+            extract a 1-D profile due to the smearing effect of seeing.
             On the top panel, the dashed line shows the mean ellipticity used for the 
             final isophote. 
-            Right: the three color image of this galaxy with isophotes 
+            \textbf{Right}: The 3-colour image of this galaxy with isophotes 
             extracted by \texttt{Ellipse}. 
@@
     view (FoV;~1.5 deg in diameter) of this camera and will cover $>1000$ deg$^2$ 
-    of sky in 5 broad bands ($grizy$) to a limiting depth of $r {\sim} 26$ mag 
+    of sky in five broad bands ($grizy$) to a limiting depth of $r {\sim} 26$ mag 
     in the \texttt{WIDE} layer. 
     This work is based on the internal data release \texttt{S15B}, which covers 
-    ${\sim} 110$ deg$^2$ in all 5-band to full \texttt{WIDE} depth.  
-    The regions covered by this release overlap with a number of spectroscopic surveys 
-    (e.g.\ SDSS/BOSS: \citealt{Eisenstein2011}, \citealt{SDSS-DR12}; 
-    GAMA: \citealt{Driver2011}, \citealt{Liske2015}).
+    ${\sim} 110$ deg$^2$ in all five bands to full \texttt{WIDE} depth.  
+    The regions covered by this release overlap with a number of spectroscopic 
+    surveys 
+    [e.g.\ Sloan Digital Sky Survey (SDSS)/Baryon Oscillation Spectroscopic Survey 
+    (BOSS): \citealt{Eisenstein2011}, \citealt{SDSS-DR12}; 
+    Galaxy And Mass Assembly (GAMA): \citealt{Driver2011}, \citealt{Liske2015}].
     \texttt{S15B} release has similar sky coverage with the Public Data Release 1
@@
     Fig~\ref{fig:sdss_compare} illustrates the quality of HSC imaging compared to SDSS 
-    for three low redshift ETGs, and shows that HSC survey data are well suited for 
+    for three low-redshift ETGs, and shows that HSC survey data are well suited for 
     mapping the stellar distribution of massive galaxies out to large radii.
@@
 	of strict requirements driven by weak lensing science. 
-    We will therefore use $i$-band images to measure the stellar distributions of 
+    We therefore use $i$-band images to measure the stellar distributions of 
     massive galaxies.
@@
 %% ------------------------------------------------------------------------------------ %% 
-\subsection{HSC Data Processing}
+\subsection{HSC data processing} 
     \label{sec:pipeline}
@@
     \texttt{hscPipe} first performs a number of tasks at the single exposure level 
-    (bias subtraction, flat fielding, background modeling, object detection and 
+    (bias subtraction, flat fielding, background modelling, object detection and 
     measurements). 
@@
     (referred as a \texttt{footprint}) for each source. 
-    Next, \texttt{footprints} and peaks from different bands are merged together before     
+    Next, \texttt{footprints} and peaks from different bands are merged before     
     performing deblending and measurements. 
     Finally, \texttt{hscPipe} selects a reference band for each object based on the 
-    $S/N$ in different bands (for most galaxies in this work, the reference band is 
-    the $i$-band). 
+    $S/N$ in different bands. (For most galaxies in this work, the reference band is 
+    the $i$-band.) 
     After fixing the centroids, shape, and other non-amplitude parameters of each 
@@
     on the \texttt{coadd} image in each band.
-    This forced photometry approach is optimized to yield accurate galaxy colors
+    This forced photometry approach is optimized to yield accurate galaxy colours
     at $i_{\mathrm{CModel}\leq25.0}$ mag (see \citealt{SynPipe}).
@@
     However, as opposed to SDSS, the HSC \cmodel{} is based on forced multi-band 
-    photometry which means that it can accurately measure both the 
-    \textit{fluxes and colors of galaxies}. 
+    photometry, which means that it can accurately measure both the 
+    \textit{fluxes and colours of galaxies}. 
     The HSC \cmodel{} algorithm fits the flux distribution of each object using a 
-    combination of a de~Vaucouleur and an exponential component and accounts for the PSF. 
+    combination of a de~Vaucouleur and an exponential component and accounts for the 
+    point spread function (PSF). 
     The performance of this algorithm has been tested using synthetic objects 
@@
     massive ETGs with extended stellar distributions. 
-    This is caused by an intrinsic limitation of \cmodel{} as it is incapable of
-    modeling profiles with extremely extended outskirts, a problem that is exacerbated 
+    This is caused by an intrinsic limitation of \cmodel{}, as it is incapable of
+    modelling profiles with extremely extended outskirts, a problem that is exacerbated 
     at the depth of the HSC survey. 
-    In addition, at the depth of the HSC survey, accurate deblending in the vicinity of
-    large ETGs where satellites and background galaxies often blend with the low surface 
-    brightness stellar envelope is a challenging problem. 
+    In addition, at the depth of the HSC survey, it is challenging to accurately 
+    deblend in the vicinity of large ETGs, where satellites and background galaxies 
+    often blend with the low surface brightness stellar envelope. 
     The deblending method currently implemented in \texttt{hscPipe} tends to 
-    ``over-deblend'' the outskirts of bright galaxies and leads to an 
-    under-estimation of the total flux of massive ETGs (this is discussed further in 
-    \citealt{HSC-PIPE}).   
-    For these reasons, our results will be based on custom-developed code to measure 
+    `over-deblend' the outskirts of bright galaxies and leads to an 
+    underestimation of the total flux of massive ETGs. (This is discussed further in 
+    \citealt{HSC-PIPE}.)   
+    For these reasons, our results are based on custom-developed code to measure 
     the luminosities and stellar masses of massive galaxies. 
     We use the HSC \texttt{hscPipe} photometry for two purposes: 
-    1) to perform a first broad sample selection, and 2) to estimate the average 
-    color of massive galaxies.
-
-%% ------------------------------------------------------------------------------------ %% 
-\subsection{Initial Massive Galaxy Sample}
+    (1) to perform a first broad sample selection, and (2) to estimate the average 
+    colour of massive galaxies.
+
+%% ------------------------------------------------------------------------------------ %% 
+\subsection{Initial massive galaxy sample}
     \label{ssec:initial}
@@
 
-    We further select extended objects with no deblending errors, with well defined 
+    We further select extended objects with no deblending errors, with well-defined 
     centroids, and with useful \texttt{cModel} magnitudes in all five bands. 
     After removing objects that have pixels affected by saturation, cosmic-rays, or 
-    other optical artifacts\footnote{each criterion removes less than 8\% of the 
-    entire sample.}, this sample corresponds to 1760845 galaxies and will be referred 
+    other optical artefacts\footnote{each criterion removes less than 8\% of the 
+    entire sample.}, this sample corresponds to 1760845 galaxies and is  referred to
     as \texttt{hscPho}. 
@@
 
-    We match the \texttt{hscPho} sample with a spec-$z$ catalog compiled by the HSC 
+    We match the \texttt{hscPho} sample with a spec-$z$ catalogue compiled by the HSC 
     team.
-    It is created by matching HSC objects with a series of publicly available 
-    spectroscopic redshifts (e.g.\ SDSS DR12 \citealt{SDSS-DR12}; 
-    GAMA DR2 \citealt{Liske2015}). 
-    The spec-$z$ quality flags from different catalogs are homogenized into a single 
+    The catalogue is created by matching HSC objects with a series of publicly 
+    available spectroscopic redshifts (e.g.\ SDSS Data Release (DR) 12  
+    \citealt{SDSS-DR12}; GAMA DR2 \citealt{Liske2015}). 
+    The spec-$z$ quality flags from different catalogues are homogenized into a single 
     flag that indicates secure redshifts.
-    Please see \S~4.4.2 of \citet{HSC-DR1} for details of this catalog.  
-    To ensure reasonable \mstar{}-completeness at the high-\mstar{} end we focus on
+    Please see \S~4.4.2 of \citet{HSC-DR1} for details of this catalogue.  
+    To ensure reasonable \mstar{}-completeness at the high-\mstar{} end, we focus on
     the redshift range $0.3 \leq z \leq 0.5$. 
@@
     Objects without a spectroscopic redshift are matched with central 
-    galaxies from the \redm{} SDSS DR8 (\citealt{Rykoff2014}) catalog using a 
+    galaxies from the \redm{} SDSS DR8 (\citealt{Rykoff2014}) catalogue using a 
     $2.0^{\arcsec}$ matching radius. 
@@
     $|z_{\lambda} - z_{\mathrm{Spec}}| {\sim} 0.01$) for our purpose.
-    The \redm{} catalog provides an additional 133 unique redshifts for massive 
+    The \redm{} catalogue provides an additional 133 unique redshifts for massive 
     galaxies in our sample.
@@
     %% Saved as "dr1_wide_galaxy_icmodel_21.5.fits"
-    The majority of our redshifts comes from the BOSS and SDSS ``legacy'' LRG samples. 
+    The majority of our redshifts comes from the BOSS and SDSS `legacy' luminous 
+    red galaxy (LRG) samples. 
     The GAMA survey provides an additional $14$\% of all spectroscopic redshifts.
     Although the GAMA survey only covers parts of the \texttt{S15B} data release, 
-    hence affects the homogeneity of our sample, it will not affect the results of 
-    this work.
-    We will discuss this more in \S \ref{sec:final}.
-
-    We choose the redshift range $0.3 \leq z \leq 0.5$ to make sure that: 
-    (1) The inner region of massive galaxies can be resolved, and \mstar{} within 
+    and hence affects the homogeneity of our sample, it does not affect the results 
+    of this work.
+    We discuss this more in \S \ref{sec:final}.
+
+    We choose the redshift range $0.3 \leq z \leq 0.5$ to make sure that  
+    (1) the inner region of massive galaxies can be resolved, and \mstar{} within 
     10 kpc can be reliably measured; 
-    (2) The background noise and cosmological dimming are not major issues so that the 
-    \mden{} profile can be measured out to $>100$ kpc; 
-    (3) Redshift evolution in the stellar population properties can be largely 
+    (2) the background noise and cosmological dimming are not major issues so that 
+    the \mden{} profile can be measured out to $>100$ kpc; and
+    (3) redshift evolution in the stellar population properties can be largely 
     ignored.  
-    Also at higher redshift, the completeness of the spec-$z$ sample starts to decline. 
-    And finally, the over-subtraction of the background level becomes a more serious 
-    issue at lower redshifts.
-
-    We will now describe our one-dimensional photometric analysis 
+    Also, at higher redshift, the completeness of the spec-$z$ sample starts to 
+    decline; at lower redshifts, the over-subtraction of the background level 
+    becomes a more serious issue.
+
+    We now describe our 1-D photometric analysis 
     (\S \ref{sec:ellipse}) and our stellar mass estimates (\S \ref{sec:mstar}). 
-    We will then define the final sample in \S \ref{sec:final}.
+    We define the final sample in \S \ref{sec:final}.
 
@@
 
-    The surface brightness profiles of massive ETG are not well modeled by the 
+    The surface brightness profiles of massive ETG are not well modelled by the 
     de~Vaucouleurs or single-\ser law, especially at the imaging depth of HSC.
@@
     Although they can still be described by more complex models 
-    (e.g \citealt{Huang2013a, Huang2013b, Oh2017}), the results will be 
+    (e.g \citealt{Huang2013a, Huang2013b, Oh2017}), the results are 
     sensitive to the choice of model, the number of components, and internal 
     degeneracies among parameters. 
-    2-D modeling is also very sensitive to background subtraction method, 
+    2-D modelling is also very sensitive to background subtraction method, 
     especially for massive ETGs (e.g. \citealt{Huang2013a}).
@@
 
-    We therefore perform elliptical isophote fitting using the IRAF \texttt{Ellipse} 
-    algorithm (Jedrzejewski 1987) to estimate the total luminosities of massive 
-    galaxies and to measure their one-dimensional stellar mass surface 
-    density profiles (\mden{}). 
+    We therefore perform elliptical isophote fitting using the Image Reduction 
+    and Analysis Facility (IRAF) \texttt{Ellipse} algorithm (Jedrzejewski 1987) 
+    to estimate the total luminosities of massive galaxies and to measure their 
+    1-D stellar mass surface density profiles (\mden{}). 
     This 1-D method is less affected by the issues mentioned above. 
-    Also, we will only study galaxies in the radial range where we are less 
+    Also, we only study galaxies in the radial range where our results are less 
     sensitive to either the PSF or the background subtraction.
-    We ignore the inner $\sim6$ kpc, which is twice the size of 1\asec{} seeing at 
-    $z=0.5$.
+    We ignore the inner $\sim6$ kpc, which is twice the size of 1\asec{} seeing 
+    at $z=0.5$.
     Using this conservative choice, we can safely ignore the smearing effect of 
     seeing outside this radius.
-    As we will show later, we confirm this by comparing our HSC profiles with 
+    As we discuss below, we confirm this by comparing our HSC profiles with 
     observations with higher spatial resolution. 
-    As for the impact from background subtraction, we will focus on the profiles 
+    As for the impact from background subtraction, we focus on the profiles 
     within 100 kpc. 
-    This is an empirical, but also conservative choice based on the tests we 
+    This is an empirical but also conservative choice based on the tests we 
     conducted on background-corrected postage-stamps. 
@@
     \song{
-    We generate postage-stamp of each galaxy that extend to 750 kpc in radius, 
+    We generate a postage stamp of each galaxy that extends to 750 kpc in radius, 
     along with the bad pixel mask and the PSF model. 
-    They postage-stamps are large enough to evaluate the local background. 
+    The postage stamps are large enough to evaluate the local background. 
     We choose to use $i$-band images since they trace the stellar mass distributions 
     of $0.3 \leq z \leq 0.5$ massive galaxies reasonably well 
-    (corresponds to rest-frame $g$ or $r$ band), and also because better seeing 
-    and lower background level than the $z$ and $y$ band images (although these 
-    bands are better tracers of \mden{}). 
-    }
-
-    For each postage-stamp, to overcome the \texttt{hscPipe} ``over-deblending'' 
-    issue, we use a customized procedure to detect and aggressively mask out
+    (corresponds to rest-frame $g$ or $r$ band). $i$-band images also enable better 
+    seeing and lower background levels than the $z$ and $y$ band images, although 
+    these bands are better tracers of \mden{}. 
+    }
+
+    To overcome the \texttt{hscPipe} `over-deblending' issue, we use a customized 
+    procedure on each postage stamp to detect and aggressively mask out 
     neighbouring objects. 
@@
     These procedures are described in detail in Appendix~\ref{app:ellipse}. 
-    We should point out that we are not using the photometric results from our 
+    We should point out that we do not use the photometric results from our 
     customized process, but simply rely on them for improved local background model
@@
 
-    Then, we run \texttt{Ellipse} on the background-corrected, masked postage-stamp 
+    Then, we run \texttt{Ellipse} on the background-corrected, masked postage stamp 
     following the methodology of \citet{Li2012}. 
@@
     the mean ellipticity and position angle. 
-    We correct these profiles for Galactic extinction and cosmological dimming, 
-    and integrate them to various radii to get the luminosity 
+    We correct these profiles for galactic extinction and cosmological dimming, 
+    and we integrate them to various radii to get the luminosity 
     within different physical (elliptical) apertures. 
@@
 
-    We test our procedure using different mask sizes, different \texttt{Ellipse} 
-    parameters, and with or without our background correction. 
-    Based on these tests, we find that our 1-D surface brightness profiles are reliable 
-    up to surfaces brightness levels of $i{\sim}28.5$ \sb. 
-    Beyond that, some of our profiles shows signs of truncation and/or large 
-    fluctuations which are due to either the uncertainty in the background 
+    We test our procedure using different mask sizes and different \texttt{Ellipse} 
+    parameters; we also test the procedure with and without our background correction. 
+    Based on these tests, we find that our 1-D surface brightness profiles are 
+    reliable up to surface brightness levels of $i{\sim}28.5$ \sb. 
+    Beyond that, some of our profiles show signs of truncation and/or large 
+    fluctuations, which are due to either the uncertainty in the background 
     subtraction or the unmasked flux from other objects.
     We choose to limit our study to surface brightness levels up to ${\sim} 28.5$ \sb. 
-    This is a conservative choice but already enables us to measure light profiles 
-    out to $100$ kpc on a galaxy-by-galaxy basis (no stacking). 
+    This is a conservative choice but is sufficient to enable us to measure light 
+    profiles out to $100$ kpc on a galaxy-by-galaxy basis (no stacking). 
     \song{
     The 1-D method fails to extract profiles for ${\sim}10$\% of the sample due 
-    to severe contamination of other objects, they are excluded from the analysis.
-    }
-    For more technical details of the \texttt{Ellipse} procedure, please see 
+    to severe contamination of other objects; these profiles are excluded from the
+    analysis.
+    }
+    For additional technical details on the \texttt{Ellipse} procedure, please see 
     Appendix~\ref{app:ellipse}.
@@
       	  On average, \mcmodel{} underestimates the total stellar mass of massive 
-          galaxies by 0.1 dex while in some cases, the difference can exceed 0.2 dex.
+          galaxies by 0.1 dex, while in some cases, the difference can exceed 0.2 dex.
           Vertical histograms indicate the mass difference for all galaxies (shaded 
@@
           \textbf{Right:} Difference between \mmax{} and \mtot{} in the same format. 
-          The average difference is small (0.02 dex) and with no clear mass--dependence. 
+          The average difference is small (0.02 dex) and has no clear mass--dependence. 
           \textbf{Please note that the scales of the vertical axes are different 
@@
 %% ------------------------------------------------------------------------------------ %% 
-\subsection{Stellar Masses from SED Fitting}
+\subsection{Stellar masses from SED fitting}
     \label{ssec:isedfit}
@@
     This is a reasonable assumption considering that they are mostly dominated by 
-    old stellar populations and are known to have only shallow color gradients
+    old stellar populations and are known to have only shallow colour gradients
     (e.g.\ \citealt{Carollo1993, Davies1993, LaBarbera2012, DSouza2014}). 
     \song{
-    We will discussion more about this point in Appendix~\ref{app:sed}, and our own 
-    measurements of color profiles (see \S~\ref{ssec:ell_color}) also demonstrate 
+    We discuss more about this point in Appendix~\ref{app:sed}, and our own 
+    measurements of colour profiles (see \S~\ref{ssec:ell_color}) also demonstrate 
     this point. 
@@
 
-    We use the broadband Spectral Energy Distributions (SEDs) fitting 
+    We use the broadband spectral energy distribution (SEDs) fitting 
     (see \citealt{Walcher2011} for a recent review) code 
@@
     (\citealt{Moustakas13}) to estimate the average \m2l{} and $k$-corrections using
-    5-band HSC \cmodel{} fluxes.
+    five-band HSC \cmodel{} fluxes.
     \song{
@@
     Although \cmodel{} tends to underestimate the total fluxes of bright, extended 
-    objects, it can still yield accurate \emph{average} colors thanks to the 
+    objects, it can still yield accurate \emph{average} colours thanks to the 
     forced-photometry method that takes the PSF convolution into account
@@
     using synthetic galaxies, and show that \cmodel{} provides excellent measurements 
-    of five-band colors, which are crucial for reliable \m2l{} estimates.
+    of 5-band colours, which are crucial for reliable \m2l{} estimates.
     The typical uncertainty of \logms{} is around 0.06-0.08 dex at \logms${\sim} 11.5$.
@@
     All these properties behave reasonably for massive galaxies in this sample. 
-    Using the $k$-corrected optical color, we can also confirm that the sample follows 
-    a tight ``red-sequence''.
-
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %% 
-\subsection{Definitions of Different Aperture Stellar Masses}
+    Using the $k$-corrected optical colour, we can also confirm that the sample 
+    follows a tight `red-sequence'.
+
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
+\subsection{Definitions of different aperture stellar masses}
     \label{ssec:mtotal}
@@
     \song{
-    \texttt{iSEDFit} help us estimate the best--fit \mstar{} based on the \cmodel{} 
-    photometry (noted as as \mcmodel{}) and the average \m2l{} in the $i$-band. 
+    \texttt{iSEDFit} helps us estimate the best-fitting \mstar{} based on the \cmodel{} 
+    photometry (noted as \mcmodel{}) and the average \m2l{} in the $i$-band. 
     Then, we can convert the 1-D luminosity density profiles into stellar mass 
     surface density (\mden{}) profiles with the average \m2l{} and estimate \mstar{} 
-    within different radius through integrating the \mden{} profiles. 
+    within different radius by integrating the \mden{} profiles. 
     Given exquisite \mden{} profiles extending to $>100$ kpc, the definition and meaning 
-    of ``total'' \mstar{} becomes nuanced.
-    At the same time, motivated by the two--phase scenario, \mstar{} within different 
+    of `total' \mstar{} becomes nuanced.
+    At the same time, motivated by the two-phase scenario, \mstar{} within different 
     radius may help us trace different physical components. 
@@
             ($R_{\mathrm{e}}$, or 5-10 kpc) of $z{\sim}0$ massive ETGs.
-            We therefore use \minn{} as the \mstar{} of the inner ``core'' and as 
+            We therefore use \minn{} as the \mstar{} of the inner `core' and as 
             a proxy for the \textit{in situ} \mstar{}. 
             The high-quality HSC data enable us to reliably measure \minn{} at 
-            $0.3 < z < 0.5$ ($1.0^{\arcsec}$ in radius equals 4.4 and 6.1 kpc 
-            at redshifts 0.3 and 0.5 respectively).
-            We should point out that, in simulation 
+            $0.3 < z < 0.5$ ($1.0^{\arcsec}$ in radii equal 4.4 and 6.1 kpc 
+            at redshifts 0.3 and 0.5, respectively).
+            We should point out that in simulation an
             (e.g. \citealt{RodriguezGomez2016}), \textit{in situ} component can 
-            extend outside the inner 10 kpc while \textit{ex situ} component may 
+            extend outside the inner 10 kpc, while an \textit{ex situ} component may 
             contribute to \minn{} at the same time.  
-            We will further discuss this assumption in \ref{ssec:twophase}.
+            We further discuss this assumption in \ref{ssec:twophase}.
             }
@@
             \song{
-            For massive galaxies in our sample, 100 kpc aperture corresponds to 5-10 
+            For massive galaxies in our sample, 100 kpc aperture corresponds to 5--10 
             $\times R_{\mathrm{e}}$ and should contain the majority of the \mstar{}. 
-            Here we use \mtot{} as a measure of the ``total'' \mstar{}. 
-            Although not perfect, we will show that \mtot{} is a better tracer 
+            Here we use \mtot{} as a measure of the `total' \mstar{}. 
+            We show that, although not perfect, \mtot{} is a better tracer 
             of total \mstar{} than model-dependent results from shallower images 
@@
             at \s2n{} is still above the limit set by the intrinsic fluctuation 
-            of the background for our massive galaxies (e.g. see \citealt{Pohlen2006}). 
+            of the background for our massive galaxies 
+            (e.g. see \citealt{Pohlen2006}). 
             }
@@
             (e.g. \citealt{Gonzalez2005, Tal2011, DSouza2014}).
-            Therefore, \mtot{} should be only considered as lower limit of the
-            ``total'' \mstar{}. 
+            Therefore, \mtot{} should be only considered as the lower limit of the
+            `total' \mstar{}. 
             Here, we also integrate the \mden{} profile to the edge of the 
-            postage-stamp, and select the isophote that gives us the highest  
+            postage stamp, and we select the isophote that gives us the highest  
             \mstar{} and define the \mmax{}. 
-            It helps us quantify how much extra \mstar{} may be kept at $>100$ kpc.
+            These procedures help us quantify how much extra \mstar{} may be kept 
+            at $>100$ kpc.
             }
@@
     \song{
-    All aperture \mstar{} are measured after adopting a isophote with fixed 
-    ellipticity and position angle. 
-    And the 10 kpc and 100 kpc here refer to the radius along the major axis of the 
-    elliptical isophote.
+    All aperture \mstar{} are measured after adopting an isophote with fixed 
+    ellipticity and position angle, and instances of 10 kpc and 100 kpc refer to 
+    the radius along the major axis of the elliptical isophote.
     }
@@
     In Fig~\ref{fig:mass_diff}, we compare the different definitions of \mstar{}. 
-    As expected, directly measure light out to 100 kpc help recover more \mstar{} 
+    As expected, directly measured light out to 100 kpc helps us recover more \mstar{} 
     compared to \mcmodel{}.
@@
     than 0.1 dex and can be as large as 0.2--0.3 dex.  
-    For the \cmodel{} photometry in the current \texttt{hscPipe}, it relates to 
-    both the intrinsic limitations \cmodel{} algorithm and the over-subtracted 
-    background. 
-    In \S~\ref{ssec:sbp_compare}, we use the \mden{} profiles to show that large 
+    For the \cmodel{} photometry in the current \texttt{hscPipe}, the average 
+    difference relates to both the intrinsic limitations \cmodel{} algorithm and the 
+    over-subtracted background. 
+    In \S~\ref{ssec:sbp_compare}, we use the \mden{} profiles to show that a large 
     fraction of these galaxies have \mden{} profiles shallower than the de~Vaucouleurs 
-    one, it is therefore not surprising that \cmodel{} systematically underestimates 
-    the luminosity.
-    More importantly, the differences clearly depends on total stellar mass as 
+    profile; it is therefore not surprising that \cmodel{} systematically 
+    underestimates the luminosity.
+    More importantly, the differences clearly depend on total stellar mass, as 
     \mcmodel{} tends to miss more \mstar{} in more massive galaxies.  
-    This relates to the mass-dependent nature of the stellar halos of massive 
-    galaxies (see \S~\ref{ssec:sbp_compare} too).
+    This limitation in \mcmodel{} relates to the mass-dependent nature of the 
+    stellar haloes of massive galaxies (see \S~\ref{ssec:sbp_compare} too).
     These differences have important implications for estimates of the stellar 
@@
     objects make \mmax{} more uncertain than \mtot{}. 
-    Nonetheless, we still see that \mmax{} becomes larger than \mtot{}. 
+    None the less, we still see that \mmax{} becomes larger than \mtot{}. 
     The differences are on average very small ($\sim0.02-0.03$ dex) and do not show 
@@
     This confirms that, at the current depth of HSC images, \mtot{} can be used as 
-    a good proxy of ``total'' stellar mass. 
+    a good proxy of `total' stellar mass. 
     }
@@
           for this work (black line) with the one of a much more complete sample
-          from the S82-MGC catalog (green line). 
+          from the S82-MGC catalogue (green line). 
           The grey dashed line shows the number density function of HSC massive 
@@
           shaded regions. 
-          The vertical grey line highlight the \logms{}$=11.6$ limit.  
-          Below it, the HSC massive galaxy sample becomes significantly incomplete in 
+          The vertical grey line highlights the \logms{}$=11.6$ limit.  
+          Below the limit, the HSC massive galaxy sample becomes significantly incomplete in 
           stellar mass. 
@@
 %% ------------------------------------------------------------------------------------ %%        
-\subsection{Stellar Mass Completeness}
+\subsection{Stellar mass completeness}
     \label{ssec:complete}
 
-    With the help of the Stripe82 Massive Galaxy Catalog (\texttt{S82-MGC},
+    With the help of the Stripe82 Massive Galaxy Catalogue (\texttt{S82-MGC},
     \citealt{Bundy2015}
@@
     The \texttt{S82-MGC} sample matches the deeper SDSS photometric data in the 
-    Stripe 82 region (\citealt{Annis2014}) with the near infrared data from the United 
+    Stripe 82 region (\citealt{Annis2014}) with the near-infrared data from the United 
     Kingdom Infrared Telescope Infrared Deep Sky Survey (UKIDSS; 
-    \citealt{Lawrence2007}), and is complete to \logms{}$\geq 11.2$ at $z<0.7$. 
+    \citealt{Lawrence2007}), and is complete to \logms{}$\geq 11.2$ at $z<0.7$, 
     which makes it sufficient to evaluate the completeness of our HSC sample. 
     \citet{Leauthaud2016} uses this sample to show that the BOSS spec-$z$ sample, 
-    which is the main source of redshifts for us, is about 80\% complete at 
+    which is our main source of redshifts, is about 80\% complete at 
     \logms{}$\geq 11.6$ at $0.3 < z < 0.5$.
@@
     our sample\footnote{We do not apply any statistical corrections for completeness 
-    and hence we do not use the term ``stellar mass function'' to avoid confusion;
-    Errors on the distributions are estimated via bootstrap resampling.}.
-    To be consistent with the \texttt{S82-MGC} catalog, we estimate the \mcmodel{}
+    and hence, to avoid confusion, we do not use the term `stellar mass function';
+    errors on the distributions are estimated via bootstrap resampling.}.
+    To be consistent with the \texttt{S82-MGC} catalogue, we estimate the \mcmodel{}
     of these galaxies using \texttt{iSEDFit}.
     We find excellent agreement between HSC \mcmodel{} and the ones from the
-    \texttt{S82-MGC} catalog.
+    \texttt{S82-MGC} catalogue.
     }
@@
     to \logmcmodel{}${\sim} 11.5$ at $0.3 \leq z \leq 0.5$.    
-    Given the average difference between \mtot{} and \mcmodel{}, we will focus on 
+    Given the average difference between \mtot{} and \mcmodel{}, we chose to focus on 
     galaxies with \logmtot{}$> 11.6$. 
-    In \S~\ref{sec:discussion}, we will also show results for massive galaxies 
-    with $11.4 \le$\logmtot{}$<11.6$ but we caution that our sample is incomplete 
+    In \S~\ref{sec:discussion}, we also show results for massive galaxies 
+    with $11.4 \le$\logmtot{}$<11.6$, but we caution that our sample is incomplete 
     in this lower mass bin mainly due to the intrinsic incompleteness of the 
@@
       \caption{
-          \textbf{Left:} Impact of using \mtot{} on the galaxy stellar mass function. 
+          \textbf{(a)} Impact of using \mtot{} on the galaxy stellar mass function. 
           Dashed lines correspond to the observed volume density distribution 
-          computed using \mcmodel{} whereas solid lines correspond to the distribution
+          computed using \mcmodel{}, whereas solid lines correspond to the distribution
           computed using \mtot{}. 
           We do not apply any completeness correction to the distributions here.
-          Here we separate our HSC sample into centrals in halos more massive than
-          \logmh{}$\sim14.2$ (red lines) and centrals in halos with \logmh{}$<14.0$ 
+          We separate our HSC sample into centrals in haloes more massive than
+          \logmh{}$\sim14.2$ (red lines) and centrals in haloes with \logmh{}$<14.0$ 
           (black lines).
           The impact on the SMF can exceed 0.2 dex for massive central galaxies in 
-          very massive halos.
-          \textbf{Right}: The \mstar{} volume density distributions of massive 
+          very massive haloes.
+          \textbf{(b)}: The \mstar{} volume density distributions of massive 
           HSC galaxies, using both \mtot{} (black solid line) and \mmax{} (black dotted 
@@
           of our galaxies. 
-          These issues will be addressed in forthcoming work. 
+          These issues will be addressed in forthcoming work (Huang\etal in prep.). 
           We compare our results with previous studies: 
-          (a): SDSS galaxies at $z{\sim} 0.1$ from \citet{Bernardi2017} with \mstar{} 
+          (1): SDSS galaxies at $z{\sim} 0.1$ from \citet{Bernardi2017} with \mstar{} 
           values based on photometry from 2-D \ser{}$+$Exponential model fitting 
           (purple); 
-          (b): SDSS galaxies at $z{\sim} 0.1$ from \citet{Moustakas13} based on 
+          (2): SDSS galaxies at $z{\sim} 0.1$ from \citet{Moustakas13} based on 
           improved SDSS \texttt{cModel} photometry (blue); 
-          (c): \texttt{S82-MGC} galaxies at $0.15 < z< 0.43$ from 
-          \citet{Leauthaud2016} based on PSF-matched SDSS-UKIDSS photometry (green).
+          (3): \texttt{S82-MGC} galaxies at $0.15 < z< 0.43$ from 
+          \citet{Leauthaud2016} based on PSF-matched SDSS--UKIDSS photometry (green).
           }
@@
     \song{
-    Typically, ``central'' galaxy is defined as the galaxy locates in the center of 
-    its own dark matter halo, while the galaxy in a sub-halo that is orbiting within 
-    the virial radius of a more massive halo is referred to as a ``satellite'' 
+    Typically, a `central' galaxy is defined as a galaxy located in the center of 
+    its own dark matter halo, while a galaxy in a sub-halo orbiting within 
+    the virial radius of a more massive halo is referred to as a `satellite' 
     (e.g.\citealt{Yang2007}).
-    We wish to focus on massive central galaxies here as they are uniquely important 
+    We wish to focus on massive central galaxies here as they are essential
     to the study of galaxy--halo connection.
@@
     \citealt{Reid2014, Hoshino2015, Saito2016}) at \logmtot{}$> 11.6$, we further use 
-    the \redm{} cluster catalog (\texttt{v5.10}; e.g.\ \citealt{Rykoff2014}; 
+    the \redm{} cluster catalogue (\texttt{v5.10}; e.g.\ \citealt{Rykoff2014}; 
     \citealt{Rozo2015b}) based on SDSS DR8 (\citealt{SDSS-DR8}) to help us 
-    identify centrals of cluster--level dark matter halos and reduce satellite
+    identify centrals of cluster-level dark matter haloes and reduce satellite
     contamination.
@@
     clusters with richness $\lambda \geq 20$\footnote{Due to the depth and 
-    resolution of SDSS images, the \redm{} catalog is not complete down to 
+    resolution of SDSS images, the \redm{} catalogue is not complete down to 
     $\lambda=20$ at $0.3 < z < 0.5$.  
     At $z \geq 0.33$, it starts to miss a small fraction of clusters with 
-    $\lambda < 30$, but it will not affect the results in this work.}
+    $\lambda < 30$, but it does not affect the results in this work.}
     and central probability $P_{\mathrm{Cen}} \geq 0.7$, we find 164 matched galaxies 
@@
     Simet2016, Melchior2016}), they represent the central galaxies in dark matter 
-    halos with $\log (M_{\mathrm{halo}}/M_{\odot}) \geq 14.0$, and will be 
-    referred to as the \rbcg{} sample. 
+    haloes with $\log (M_{\mathrm{halo}}/M_{\odot}) \geq 14.0$; we refer to these 
+    galaxies as the \rbcg{} sample. 
     }
@@
     As the next step, we identify and remove all galaxies within a cylindrical 
-    region around all \redm{} clusters. 
-    We use a radius equal to $R_{\mathrm{200b}}$ and the length of the cylinder is 
-    set to twice the value of the photometric redshift ($z_{\lambda}$) uncertainty 
+    region around each \redm{} cluster. 
+    We use a radius equal to $R_{\mathrm{200b}}$ and set the length of the cylinder 
+    to twice the value of the photometric redshift ($z_{\lambda}$) uncertainty 
     of each cluster\footnote{We convert $\lambda$ of each cluster to 
@@
     $R_{\mathrm{200b}}$.}.
-    After removing galaxies associated with \redm{} clusters, the remaining galaxies 
-    in our sample will be dominated by central galaxies living in halos with 
-    \logmh{}$< 14.0$, and they will be referred to as the \nbcg{} sample.
+    After we remove galaxies associated with \redm{} clusters from our sample, 
+    the remaining galaxies are dominated by central galaxies living in haloes with 
+    \logmh{}$< 14.0$; we refer to these galaxies as the \nbcg{} sample.
     Using the model presented in \citet{Saito2016}, we estimate that in dark matter 
-    halos with \logmh$<11.4$, $\sim 7$\% of galaxies with \logmcmodel{}$>11.5$ are 
+    haloes with \logmh$<11.4$, $\sim 7$\% of galaxies with \logmcmodel{}$>11.5$ are 
     satellites.
@@
 %% ------------------------------------------------------------------------------------ %% 
-\subsection{Summary of Sample Construction}
+\subsection{Summary of sample construction}
     \label{ssec:sample}
@@
     \begin{itemize}
-        \item \texttt{hscPho} sample: this parent sample consists of bright galaxies 
+
+        \item \texttt{hscPho} sample. This parent sample consists of bright galaxies 
             with $i_{\mathrm{cModel}} \leq 21.0$, good quality imaging, and reliable 
@@
             1760845 galaxies.
-        \item \texttt{hscZ} sample: we limit the \texttt{hscPho} sample to galaxies 
+
+        \item \texttt{hscZ} sample. We limit this \texttt{hscZ} sample to galaxies 
             with reliable redshift information.
-            More details of this sample can also be found in \S \ref{ssec:initial}. 
+            This sample is described in \S \ref{ssec:initial}. 
             It provides us 25286 useful galaxies at $0.3<z<0.5$.
-        \item With the help of the \redm{} cluster catalog, we further select 
+
+        \item With the help of the \redm{} cluster catalogue, we further select 
             candidates of massive central galaxies.
-            We broadly divide the sample into central galaxies living in halos
-            with \logmh{}$\geq 14.0$ (\rbcg{}) and \logmh{}$<14.0$ (\nbcg{}).
+            We broadly divide the \texttt{hscZ} sample into central galaxies living 
+            in haloes with \logmh{}$\geq 14.0$ (\rbcg{}) and central galaxies from 
+            the haloes with \logmh{}$<14.0$ (\nbcg{}).
             To ensure the sample is \mstar{}-complete and has minimal satellite 
-            contamination, we will further focus on the 950 massive galaxies with 
+            contamination, we further focus on the 950 massive galaxies with 
             \logmtot{}$>11.6$ in this work\footnote{As reference, there are 
@@
 
-    The division of our sample into two halo mass bins is mainly relevant for Paper II
-    (Huang \etal in prep.).  
-    For the present paper, we only consider the halo mass dependence on our sample when 
+    The division of our sample into two halo mass bins is mainly relevant for the 
+    second paper in this series (Huang \etal in prep.).  
+    For the present paper, we consider only the halo mass dependence on our sample when 
     we evaluate impact of mass estimates on the SMF in \S \ref{ssec:smf}. 
-    We show the distributions of redshift, \mtot{} and \minn{} of the massive galaxy 
+    We show the distributions of redshift, \mtot{}, and \minn{} of the massive galaxy 
     sample in Appendix \ref{app:basic}, along with its \mtot{}-$(g-r)$ rest-frame 
-    color relation.
+    colour relation.
 
@@
 %% ------------------------------------------------------------------------------------ %%     
-\subsection{Impact of Missing Light on the Galaxy Stellar Mass Function}
+\subsection{Impact of missing light on the galaxy stellar mass function}
     \label{ssec:smf}
@@
     high-\mstar{} end of SMF (e.g. \citealt{Bernardi2013, dSouza2015, Bernardi2017}). 
-    Above works show that, despite being widely adopted in literatures, \cmodel{} 
-    photometry can significantly underestimate the \mstar{} of massive galaxies. 
-    But these works are still based on more complex 2-D modeling or stacking of 
+    The cited works show that, despite being widely adopted in the literature, 
+    \cmodel{} photometry can significantly underestimate the \mstar{} of massive 
+    galaxies. 
+    Still, these works are based on more complex 2-D modelling or stacking of 
     shallow images that suffer from various systematics.
@@
     The left panel of Fig~\ref{fig:smf} show the volume density distributions 
-    (will be referred to as SMF for simplicity) of massive galaxies using \mcmodel{} 
+    (referred to as SMF for simplicity) of massive galaxies using \mcmodel{} 
     and \mtot{} for both the \rbcg{} and \nbcg{} samples.  
@@
     two measurements lead to noticeable differences in SMF at high-\mstar{} end.
-    \cmodel{} photometry leads to underestimation of volume density at the high-\mstar{} 
-    end of SMF. 
+    \cmodel{} photometry leads to underestimation of volume density at the 
+    high-\mstar{} end of SMF. 
     More importantly, it shows that the impact of missing \mstar{} becomes more 
-    significant for central galaxies in very massive halos. 
-    We will demonstrate that this occurs because galaxies in more massive halos 
-    have more extended stellar envelopes than those in lower mass halos at fixed 
-    \mtot{} in a following work (Huang\etal in prep.).
-    On the right panel of Fig~\ref{fig:smf}, we also compare the SMFs using \mtot{} and 
-    \mmax{}. 
+    significant for central galaxies in very massive haloes. 
+    We demonstrate that this occurs because galaxies in more massive haloes 
+    have more extended stellar envelopes than those in lower mass haloes at fixed 
+    \mtot{} in Huang\etal (in prep.).
+    On the right panel of Fig~\ref{fig:smf}, we also compare the SMFs using \mtot{} 
+    and \mmax{}. 
     As mentioned in \S~\ref{ssec:mtotal}, \mtot{} is still a lower limit of the total 
-    \mstar{} of these massive galaxies, and \mmax{} help us check how much \mstar{} 
+    \mstar{} of these massive galaxies, and \mmax{} helps us check how much \mstar{} 
     could be left out.  
@@
     It suggests that \mtot{} captures the majority of the total \mstar{}.
-    Here we do not attempt to apply any completeness correction so the SMFs turn over 
-    at the low-\mstar{} end. 
-    For now, we add a constant ${\sim}20$\% uncertainty to the SMF to account for the 
-    satellite galaxies and the ones we fail to extract 1-D profiles 
+    Here we do not attempt to apply any completeness correction, so the SMFs turn 
+    over at the low-\mstar{} end. 
+    For now, we add a constant ${\sim}20$\% uncertainty to the SMF to account for 
+    the satellite galaxies and the galaxies for which we fail to extract 1-D profiles 
     (see Appendix~\ref{app:ellipse}), although these uncertainties should be smaller 
@@
             The SMF of $0.15 < z < 0.30$ galaxies from the \texttt{S82-MGC} sample
-            \citep{Leauthaud2016} where \mstar{} is based on PSF--matched aperture
+            \citep{Leauthaud2016}, where \mstar{} is based on PSF-matched aperture
             photometry and \texttt{iSEDfit} fitting using \texttt{BC03} model.
-            We account for the 0.08 dex average difference with the \texttt{FSPS} ones
-            seen in the Appendix~\ref{app:sed}
+            We account for the 0.08 dex average difference with the \texttt{FSPS} 
+            ones seen in the Appendix~\ref{app:sed}
             }
@@
         \item \song{
-            The SMF for SDSS-\textit{GALEX} sample at $z{\sim} 0.1$ using SDSS \cmodel{}
-            photometry and \texttt{iSEDfit} stellar mass based on similar assumptions 
-            (see \citet{Moustakas13} for details). 
+            The SMF for the SDSS-\textit{GALEX} sample at $z{\sim} 0.1$ using 
+            SDSS \cmodel{} photometry and \texttt{iSEDfit} stellar mass based on 
+            similar assumptions (see \citet{Moustakas13} for details). 
             }
@@
             The SMF for $z{\sim} 0.1$ SDSS galaxies using 2-D \texttt{SerExp} 
-            models\footnote{\ser{}$+$ Exponential disk model that can recover more 
+            models\footnote{\ser{}$+$ Exponential disc model that can recover more 
             lights than SDSS \cmodel{}; integrated to infinity.}
             (\citealt{Bernardi2013, Meert2015}) and stellar mass by 
-            \citet{Mendel2014}\footnote{Use \texttt{FSPS} model, 
+            \citet{Mendel2014}\footnote{We use \texttt{FSPS} model, 
             \citet{Chabrier2003} IMF, and \citet{Calzetti2000} extinction law}.
@@
     \emph{do not} attempt to perform detailed comparisons among these SMFs.
-    We are currently working to address these issues in a forthcoming paper. 
+    We are currently working to address these issues in Huang \etal (in prep.). 
     Here we simply note that the HSC \mtot{} SMF is closer to the one 
@@
     Meanwhile, the differences between the HSC \mtot{} SMF with the others are 
-    likely caused by the photometric methods: SDSS \cmodel{} and small aperture 
+    likely caused by the photometric methods: SDSS \cmodel{} and small-aperture 
     photometry underestimate \mstar{} of massive galaxies.  
-    Even before a more in--depth study, it already illustrates an important issue:
+    Even before a more in-depth study, it already illustrates an important issue:
     \textbf{It is crucial to understand the impacts from photometric data and 
-    methods on the estimates of SMF} before using it to study galaxy evolution or 
+    methods on the estimates of SMF} before using HSC \mtot{} SMF to study 
+    galaxy evolution or 
     comparing it with predictions from models and simulation. 
-    This is particularly relevant since method like \cmodel{} will still be widely 
-    adopted in on-going and future imaging surveys.
-    }
-
-    %Without a more in-depth study, we cannot ascertain whether or not the apparent 
-    %agreement between the HSC SMF and the \citet{Bernardi2017} SMF indicates a global 
-    %lack of evolution in the galaxy SMF, or that other effects are at play 
-    %(for example, the difference between \mtot{} masses and \texttt{SerExp} masses) 
-    %that have cancelled redshift evolution.  
-    %In future work, it will be interesting to perform a more consistent analysis to 
-    %search for redshift evolution in the galaxy SMF and to study whether or not 
-    %massive galaxies in HSC are well described by \texttt{SerExp} models.
-
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %%
-\subsection{Surface Mass Density Profiles}
+    This is particularly relevant since a method like \cmodel{} will still be 
+    widely adopted in on-going and future imaging surveys.
+    }
+
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %%
+\subsection{Surface mass density profiles}
     \label{ssec:sbp_compare}
@@
           \textbf{Left}: Median \mden{} profiles in three total stellar mass bins. 
-              Thin grey lines show a random subset of individual profiles.  
+              Thin grey lines in the background show a random subset of individual
+              profiles. 
               The scatter between the thin grey lines reflects the true scatter in 
@@
               The purple short-dashed line shows the median radial stellar distributions 
-              in massive halos from simulation using the particle tagging method
+              in massive haloes from simulation using the particle tagging method
               (\citealt{Cooper2013}).}
@@
 %% ------------------------------------------------------------------------------------ %%
-\subsubsection{General Trends and Comparison with Previous Work}
+\subsubsection{General trends and comparison with previous work}
     \label{sssec:sbp_inter}
@@
     Previous work on the structural evolution of massive galaxies has often focused on 
-    scaling relations such as the ``\mstar{}-size'' relation.  
-    We argue that  comparing \mden{} profiles directly captures more information than
-    the \mstar{}-size relation and has the advantage that it bypasses difficult 
-    questions about how to accurately define and measure galaxy ``sizes'' and 
-    ``masses''.
+    scaling relations such as the `\mstar{}-size' relation.  
+    We argue that by comparing \mden{} profiles directly, we can capture more 
+    information than afforded by the \mstar{}-size relation. T
+    he comparison also has the advantage that it bypasses difficult questions about 
+    how to accurately define and measure galaxy `sizes' and `masses'.
 
@@
     galaxies at $0.3 < z < 0.5$ in three \mtot{} bins.
-    These median profiles along with their uncertainties are derived using bootstrap
-    resampling method. 
-    Note that our sample is not complete in the lowest \mtot{} bin, althaough the 
+    These median profiles along with their uncertainties are derived using the 
+    bootstrap resampling method. 
+    Note that our sample is not complete in the lowest \mtot{} bin, although the 
     median \mden{} profile may not be significantly affected. 
-    As shown in the left panel of Fig~\ref{fig:avg_prof}, we can comfortably trace
-    the \mden{} profiles of these massive galaxies out to 100 kpc \textbf{individually}.  
-    At large scales, some of our \mden{} profiles show signs of unphysical truncation and
-    fluctuation related to inaccurate sky subtraction. 
+    As shown in the left panel of Fig~\ref{fig:avg_prof}, we can confidently trace
+    the \mden{} profiles of these massive galaxies out to 100 kpc 
+    \textbf{individually}.  
+    At large scales, some of our \mden{} profiles show signs of unphysical truncation 
+    and fluctuation related to inaccurate sky subtraction. 
     In this paper, we do not use profiles beyond 100 kpc, even though the median 
-    \mden{} profiles for the two most massive bins behave reasonably out to 
+    \mden{} profiles for the two most massive bins behave reasonably well out to 
     ${\sim} 200$ kpc.
@@
     homogeneous profiles on small radial scales. 
-    The amplitude of \mden{} increases with galaxy mass on 10 kpc scales but the slope 
-    of \mden{} remains similar.  
+    The amplitude of \mden{} increases with galaxy mass on 10 kpc scales but the 
+    slope of \mden{} remains similar.  
     From previous work on this topic, we already know that the inner regions of 
@@
     ellipticals (within 100 Mpc; median \logms{} ${\sim} 11.3$) based on relatively 
-    shallow images from the Carnegie-Irvine Galaxy Survey 
+    shallow images from the Carnegie--Irvine Galaxy Survey 
     (CGS, \citealt{CGS1})\footnote{https://cgs.obs.carnegiescience.edu/CGS/Home.html}.  
@@
     \citet{Huang2013a} galaxies are accurate to smaller scales (down to $r=1$ kpc) 
-    than our HSC ones.  
+    than our HSC profiles.  
     Our \mden{} profiles show good agreement with the \citet{Huang2013a} sample in 
@@
     The median \mstar{} of the \citet{Patel2013} sample is 
-    ${\sim} 10^{11.2} M_{\odot}$ which is lower than our lowest mass bin. 
-    However, \citet{Patel2013} uses the BC03 stellar population model which leads to 
+    ${\sim} 10^{11.2} M_{\odot}$, which is lower than our lowest mass bin. 
+    However, \citet{Patel2013} uses the BC03 stellar population model, which leads to 
     \mstar{} that are roughly 0.1 dex lower than our FSPS estimates 
@@
     The superb resolution of the \textit{HST}/ACS images allows \citet{Patel2013} to 
-    accurately measure \mden{} profile down to 1 kpc without worrying the smearing 
-    effect of seeing. 
-    The good agreement between our profiles and the ones derived from HST imaging 
-    demonstrates that our profiles are robust at $r\geq 3$ kpc so that we can 
-    accurately measure \minn{}.
-
-    Finally, we also compare with the predicted median \mden{} profile of central 
-    galaxies in massive halos ($13.5 < \log M_{200,c} < 14.0$) from a cosmological 
-    simulation where the \mden{} profiles of galaxies are calculated using the 
-    particle-tagging technique (e.g., \citealt{Cooper2010}). 
-    The simulated \mden{} profile is affected by the resolution limit of the simulation 
-    in the inner region, but is in good agreement with our median \mden{} profile for 
-    the $11.6 <$ \logmtot{} $< 11.8$ bin within 40 kpc. 
-    However, outside 40 kpc, the particle tagging method seems to predict a too 
-    prominent stellar halo and has much shallower outer slope compared to our data.
+    accurately measure the \mden{} profile down to 1 kpc without worrying about the
+    smearing effect of seeing. 
+    The good agreement between our profiles and the ones derived from \textit{HST} 
+    imaging demonstrates that our profiles are robust at $r\geq 3$ kpc; therefore, 
+    we can accurately measure \minn{}.
+
+    Finally, we also compare our HSC profiles with the predicted median \mden{} 
+    profile of central galaxies in massive haloes ($13.5 < \log M_{200,c} < 14.0$) 
+    from a cosmological simulation where the \mden{} profiles of galaxies are 
+    calculated using the particle tagging technique (e.g., \citealt{Cooper2010}). 
+    The simulated \mden{} profile is affected by the resolution limit of the 
+    simulation in the inner region but is in good agreement with our median 
+    \mden{} profile for the $11.6 <$ \logmtot{} $< 11.8$ bin within 40 kpc. 
+    However, when compared to our data for the $11.6 <$ \logmtot{} $< 11.8$ bin 
+    outside 40 kpc, the particle tagging method seems to predict an overly  
+    prominent stellar halo that has a much shallower outer slope.
 
@@
     \href{http://www.ucolick.org/\~kbundy/massivegalaxies}{here}:
-    {\url{http://www.ucolick.org/\~kbundy/massivegalaxies}}. (The files will be made 
-    available after the paper is accepted)
-
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %% 
-\subsection{Ellipticity and Color Profiles}
+    {\url{http://www.ucolick.org/\~kbundy/massivegalaxies}}. 
+    (The files will be made available after the paper is accepted)
+
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
+\subsection{Ellipticity and colour profiles}
     \label{ssec:ell_color}
@@
       \caption{
-          Radial profiles of the ellipticty and $k$-corrected rest-frame optical colors 
+          Radial profiles of the ellipticty and $k$-corrected rest-frame optical colours 
           of massive galaxies in our sample. 
@@
           The \textbf{left panel} displays ellipticity profiles, 
-          the \textbf{Upper-right panel} shows $g-r$ color profiles, and  the
-          \textbf{lower-right panel} is for $g-i$ color profiles. 
+          the \textbf{Upper-right panel} shows $g-r$ colour profiles, and  the
+          \textbf{lower-right panel} is for $g-i$ colour profiles. 
           We compare our results with those from (1) \citet{Tal2011} based on stacking 
@@
           \citet[][blue dash lines on the left and upper-right panels]{DSouza2014}, 
-          (3) and the average $g-r$ and $g-i$ color profiles 
+          (3) and the average $g-r$ and $g-i$ colour profiles 
           from a large sample of nearby elliptical galaxies in \citet[][blue, solid 
           lines on both right panels]{LaBarbera2010}.
-          For color profiles, we also compare with deep observations of a few nearby 
-          massive ETGs: the $g-r$ color profiles of NGC 4472 (\citealt{Mihos2013}) 
+          For colour profiles, we also compare with deep observations of a few nearby 
+          massive ETGs: the $g-r$ colour profiles of NGC 4472 (\citealt{Mihos2013}) 
           and NGC 4365 (\citealt{Mihos2017}), and the $g-i$ profile of NGC 1399 
@@
     \song{
-    Now, we look into the ellipticity profile derived by \texttt{Ellipse} in $i$-band 
-    and the $g-r$ and $g-i$ color profiles (Galactic extinction and $k$-corrected). 
-    }
-	Smearing effect of seeing will make the central isophotal shape rounder than the 
-	real value, while seeing differences between filters will bias the central 
-	color\footnote{Since the HSC $i$-band always has better seeing, the central color 
-	will become redder is seeing effects are not accounted for}. 
+    Now we look into the ellipticity profile derived by \texttt{Ellipse} in $i$-band 
+    and the $g-r$ and $g-i$ colour profiles (galactic extinction and $k$-corrected). 
+    }
+	The smearing effect of seeing makes the central isophotal shape rounder than the 
+	real value, while seeing differences between filters bias the central 
+	colour\footnote{Since the HSC $i$-band always has better seeing, the central 
+	colour becomes redder if seeing effects are not accounted for}. 
 	On large scales, it is more difficult to extract reliable ellipticity and 
-	color profiles out to 100 kpc: at low surface brightness levels, the isophotal 
-	shape becomes unstable and is easily affected by contamination. 
-	Color profiles are also more difficult to extract out to large radial scales
-	because getting the color accurately depends on the background subtraction and 
+	colour profiles out to 100 kpc because at low surface brightness levels, the 
+	isophotal shape becomes unstable and is easily affected by contamination. 
+	Colour profiles are also more difficult to extract out to large radial scales
+	because getting the colour accurately depends on the background subtraction and 
 	the noise levels in both bands. 
-	In this paper, we will focus on the median ellipticity and color profiles between 
-	8--60 kpc where we can safely ignore the issues described above.
+	In this paper, we focus on the median ellipticity and colour profiles between 
+	8 and 60 kpc, where we can safely ignore the issues described above.
 
@@
 	massive galaxies and highlights the median profiles for the same three \mtot{} 
-	bins as used in Fig \ref{fig:avg_prof}.  
-	Our results are also compared with previous work based on image stacking techniques 
-	(the PSF-removed $i$-band results from \citealt{Tal2011}, and
-    concentrated galaxies with $11.0<$\logms{}$<11.4$ from \citealt{DSouza2015}).
+	bins shown in Fig \ref{fig:avg_prof}.  
+	Our results are also compared with previous work based on image stacking 
+	techniques (the PSF-removed $i$-band results from \citealt{Tal2011}, and
+    concentrated galaxies with $11.0<$\logms{}$<11.4$ from \citealt{dSouza2015}).
 	As expected, ellipticity profiles from image stacking methods yield results that 
-	are more shallow than when ellipticity can be measured on a galaxy-by-galaxy basis.     
-	Uncertainties in how to align galaxies, and the intrinsic isophotal twist can 
+	are more shallow than ellipticity profiles measured on a galaxy-by-galaxy basis.     
+	Uncertainties in how to align galaxies and the intrinsic isophotal twist can 
 	lead to this effect.
@@
 	clear evidence that:  
-	a) the ellipticity of stellar halo in massive ETGs depends strongly on 
+	(1) the ellipticity of stellar halo in massive ETGs depends strongly on 
 	\mtot{}, and 
-	b) the ellipticity of stellar halo also relates to the slope of the \mden{}
-	profile (see Fig~\ref{fig:avg_prof} and Fig~\ref{fig:ell_color}; 
-	we will discuss this more in Paper II). 
-	\song{
-	As mentioned in \S~\ref{sec:intro}, such mass-dependent ellipticity profile
-	could show us more insights about the assembly of stellar halos of massive
+	(2) the ellipticity of stellar halo also relates to the slope of the \mden{}
+	profile [see Fig~\ref{fig:avg_prof} and Fig~\ref{fig:ell_color}; 
+	we will discuss this more in Huang\etal (in prep.)]. 
+	\song{
+	As mentioned in \S~\ref{sec:intro}, such a mass-dependent ellipticity profile
+	could reveal more insights about the assembly of stellar haloes of massive
 	galaxies. 
@@
     \song{
-    Regarding the color profiles, the right panels of Fig \ref{fig:ell_color} show 
-    the $k$-corrected $(g-r)$ and $(g-i)$ color profiles for all galaxies in our 
+    Regarding the colour profiles, the right panels of Fig \ref{fig:ell_color} show 
+    the $k$-corrected $(g-r)$ and $(g-i)$ colour profiles for all galaxies in our 
     sample, together with the median profiles in three \mtot{} bins. 
-    We find the the median rest-frame $(g-r)$ and $(g-i)$ color profiles present 
-    smooth and shallow negative color gradients out to 50--60 kpc, as observed by 
+    We find that the median rest-frame $(g-r)$ and $(g-i)$ colour profiles present 
+    smooth and shallow negative colour gradients out to 50--60 kpc, as observed by 
     many previous works (e.g. \citealt{Carollo1993, LaBarbera2012}) and predicted 
@@
     Meanwhile, there does not appear to be a significant \mstar{} dependence 
-    in the gradient of rest-frame optical colors. 
-    }
-    We also compare our results with the stacked color profiles from  
-    \citealt{LaBarbera2010}\footnote{We use the median color profiles of high-mass 
-    ETGs; the original profile is in units of $R_{\mathrm{e}}$, we use a typical 
+    in the gradient of rest-frame optical colours. 
+    }
+
+    We also compare our results with the stacked colour profiles from  
+    \citealt{LaBarbera2010}\footnote{We use the median colour profiles of high-mass 
+    ETGs; the original profile is in units of $R_{\mathrm{e}}$, and we use a typical 
     $R_{\mathrm{e}}=8.0$ kpc to convert it into physical kpc.} and 
     \citealt{DSouza2014}.
-    The median color profiles from HSC images are systematically steeper than the 
+    The median colour profiles from HSC images are systematically steeper than the 
     stacked SDSS ones. 
     Considering differences in the response curves between HSC and SDSS filters, 
-    together with the uncertainties of color measurements, the HSC $(g-r)$ color 
+    together with the uncertainties of colour measurements, the HSC $(g-r)$ colour 
     profiles are in fairly good agreement with those from SDSS. 
     However, the $(g-i)$ profiles of HSC galaxies are steeper compared to SDSS. 
-    The SDSS $i$-band suffers from the so-called ``red-halo'' effect
+    The SDSS $i$-band suffers from the so-called `red-halo' effect
     (e.g. \citealt{Wu2005}, \citealt{Tal2011}).  
-    This is likely due to the fact that the SDSS $i$-band PSF has more prominent 
+    This is likely due to the fact that the SDSS $i$-band PSF has a more prominent 
     wing than other bands. 
-    Because the PSF model does not capture these wings, this artificially distributes 
-    more flux to the outskirts, and leads to apparently redder colors in the low 
+    Because the PSF model does not capture these wings, more flux is artificially 
+    distributed to the outskirts, which leads to seemingly redder colours in the low 
     surface brightness outskirts of galaxies. 
     Because HSC uses thick CCDs, HSC $i$-band images do not suffer from this effect 
-    and can be used to determine galaxy colors with higher accuracy. 
-    Fairly steep color profiles have been observed in several very nearby massive 
+    and can be used to determine galaxy colours with higher accuracy. 
+    Fairly steep colour profiles have been observed in several very nearby massive 
     ETGs.  
-    Fig \ref{fig:ell_color} shows the $g-r$ color profiles of NGC 4472 
+    Fig \ref{fig:ell_color} shows the $g-r$ colour profiles of NGC 4472 
     (\citealt{Mihos2013}) and NGC 4365 (\citealt{Mihos2017})\footnote{
-    Both are converted from ($B-V$) colors.}, and the $g-i$ profile of NGC 1399 
+    Both are converted from ($B-V$) colours.}, and the $g-i$ profile of NGC 1399 
     (\citealt{Iodice2016}). 
-    These individual profiles display similar color gradients as our HSC sample.
-
-    \song{
-    It is worth mentioning that the individual color profiles still show large 
+    These individual profiles display colour gradients similar to our HSC sample.
+
+    \song{
+    It is worth mentioning that the individual colour profiles still show large 
     scatter and unphysical trends in the outskirt.  
-    Color profile in the low surface brightness region is very sensitive to the 
-    noise level, contamination of other objects, and uncertainties in background 
+    The colour profile in the low--surface brightness region is very sensitive to 
+    the noise level, contamination of other objects, and uncertainties in background 
     subtraction. 
@@
     two bands are not jointly constrained. 
-    Therefore, we only show the average color profiles here, and will conduct 
-    more careful study of the color profiles in a following work.
+    Therefore, we only show the average colour profiles here, and will conduct 
+    more careful study of the colour profiles in Huang\etal (in prep.).
     }
@@
       \caption{
-          \textbf{Left:} Ratio of the fraction of stars between 10 to 100 kpc to the 
-          total galaxy mass \mtot{}. 
-          We adopt this ratio as a proxy for the fraction of ex-situ stars in our 
-          sample. 
+          \textbf{Left:} Ratio of the fraction of stars between 10 to 100 
+          kpc to the total galaxy mass \mtot{}. 
+          We adopt this ratio as a proxy for the fraction of  \textit{ex situ} stars 
+          in our sample. 
           Typical observational uncertainties are shown in the upper left hand corner. 
@@
           16 and 84 percentile of the distribution. 
-          \textbf{Right:} comparison between our median \mden{} profiles with the 
-          inner component of the structural decomposition of massive elliptical 
-          galaxies at $z<0.02$ from \citet[][Cyan, solid]{Huang2013a}.
+          \textbf{Right:} comparison between our median \mden{} profiles 
+          with the inner component of the structural decomposition of massive 
+          elliptical galaxies at $z<0.02$ from \citet[][Cyan, solid]{Huang2013a}.
           At higher redshifts, the \mden{} profiles of massive galaxies should be 
-          dominated by the in-situ component. 
+          dominated by the  \textit{in situ}  component. 
           We compare our profiles with the median \mden{} profile of massive galaxies 
@@
           It is likely that this object will grow into one of the very massive central
-          galaxy in our sample.
+          galaxies in our sample.
           It is interesting to see that its \mden{} profile is very similar to the 
-          HSC one of the most massive \mtot{} bin in the inner $\sim 20$ kpc, so the 
-          following growth should mostly happen in the outskirt. 
+          HSC profile of the most massive \mtot{} bin in the inner $\sim 20$ kpc, so 
+          the resulting growth should mostly happen in the outskirt. 
           }
@@
 
-    In this paper, we have used data from the HSC survey that is both simultaneously 
+    We have used data from the HSC survey that is both simultaneously 
     deep and wide to trace the stellar mass distributions of $0.3 < z < 0.5$ massive 
     galaxies out to $>100$ kpc and to reveal the mass-dependent nature of their 
-    stellar halos.
+    stellar haloes.
     Here we briefly discuss the scientific implications of our results.
@@
 %% ------------------------------------------------------------------------------------ %% 
-\subsection{The Formation of Massive Galaxies and the Assembly of Their Outer Halos}
+\subsection{The formation of massive galaxies and the assembly of their outer haloes}
     \label{ssec:twophase}
 
-    We find that the outer halos of massive elliptical galaxies grow more prominent 
+    We find that the outer haloes of massive elliptical galaxies grow more prominent 
     and more elliptical with increasing stellar mass.
@@
     The outskirts of massive galaxies are then built up through a more gradual second 
-    phase of evolution (the \textit{ex situ} phase) that is dominated by mass assembly via 
-    accretions.
-    Non-dissipative mergers, especially minor mergers\footnote{Normally minor merger
-    means the one with stellar mass ratio smaller than 1:3 or 1:4}, mostly deposit stars
-    in the outskirts of centrals and do not have a large impact on the central \mden{} 
-    profile (e.g. \citealt{BoylanKolchin2008, Oogi2013, Bedorf2013}).
+    phase of evolution (the \textit{ex situ} phase) that is dominated by mass assembly 
+    via accretions.
+    Non-dissipative mergers, especially minor mergers\footnote{Typically, minor merger
+    means the one with stellar mass ratio smaller than 1:3 or 1:4},  deposit stars
+    mostly in the outskirts of centrals and do not have a large impact on the central
+    \mden{} profile (e.g. \citealt{BoylanKolchin2008, Oogi2013, Bedorf2013}).
     Given the stochastic nature of the merging process, it is easy to understand why 
@@
     that the fraction of accreted stars should strongly increase with stellar 
-    mass and that for very massive galaxies, the \textit{ex-situ} may reach up to 
-    50-90\% of the total galaxy mass (e.g.
+    mass and that for very massive galaxies, the \textit{ex situ} may reach up to 
+    50--90\% of the total galaxy mass (e.g.
     \citealt{Oser2010, Cooper2013, Dubois2013, LeeYi2013, Hirschmann2015,
@@
     This picture is supported by our observations that massive galaxies display more 
-    prominent stellar halos as well as by their  negative color gradients. 
+    prominent stellar haloes as well as by their negative colour gradients. 
     The fact that the outskirts of these galaxies are slightly bluer than the inner
-    regions, is consistent with the picture that stellar halos are built up by 
-    series of minor mergers (average merger mass-ratio between 1:3-1:10; e.g. 
-    \citealt{Huang2016}) as less massive ETGs are typically bluer.
+    regions is consistent with the picture that stellar haloes are built up by a
+    series of minor mergers (average merger mass-ratio between 1:3 and 1:10; e.g. 
+    \citealt{Huang2016}) because less massive ETGs are typically bluer.
 
@@
     dark matter halo. 
-    Simulations show the shape of the stellar and dark matter halos are closely 
-    correlated (e.g. \citealt{Wu2014}) for slowly-rotating massive ETGs having 
-    undergone multiple minor-mergers.
+    Simulations show the shape of the stellar and dark matter haloes are closely 
+    correlated (e.g. \citealt{Wu2014}) for slowly rotating massive ETGs having 
+    undergone multiple minor mergers.
     The more elongated outer halo and the trend between the ellipticity profile and 
-    stellar mass may reflect the orbital properties of accreted satellite. 
-    In simulations, satellite orbits become more radial for more massive halos 
+    stellar mass may reflect the orbital properties of an accreted satellite. 
+    In simulations, satellite orbits become more radial for more massive haloes 
     (e.g. \citealt{Murante2007, Wetzel2011, Jiang2015}. 
     Satellites infalling along radial orbits may help to form elongated stellar 
-    halos.
+    haloes.
     In principle, these results may explain the trend that we see. 
     However, in contrast, simulation from \citet{Wu2014} predict that more massive 
-    galaxies should have \emph{rounder} outskirts which is the opposite trend 
+    galaxies should have \emph{rounder} outskirts, which is the opposite trend 
     compared to HSC. 
@@
 
-    At larger scales, the distribution of satellites galaxies in massive halos is 
+    At larger scales, the distribution of satellite galaxies in massive haloes is 
     found to be aligned with the major axis of the central galaxy 
@@
     This alignment signal is found to be stronger for more luminous galaxies 
-    living in more massive halos (e.g. \citealt{Hirata2007}).
+    living in more massive haloes (e.g. \citealt{Hirata2007}).
     The fact that more massive central galaxies have steeper ellipticity profiles 
-    and become increasingly more elongated in the outskirt may arise because of 
+    and become increasingly more elongated in the outskirt may be due to 
     such alignment. 
@@
     It is interesting to point out that the most recent measurement by 
-    \citet{Shin2017} around SDSS clusters show a halo axis-ratio of ${\sim}0.55$, 
+    \citet{Shin2017} around SDSS clusters shows a halo axis-ratio of ${\sim}0.55$, 
     which is only slightly more elongated than the stellar halo of galaxies in our 
@@
 %% ------------------------------------------------------------------------------------ %% 
-\subsection{Aperture Masses as Proxies of the \textit{In situ} and Accreted Stars}
+\subsection{Aperture masses as proxies of the \textit{in situ} and accreted stars}
     \label{ssec:insitu}
@@
     However, it is still extremely difficult to separate the \textit{in situ} and
-    \textit{ex situ} components observationally, despite that it is the most 
+    \textit{ex situ} components observationally, despite the fact that it is the most 
     important theoretical prediction to be verified. 
@@
     \song{
-    Recent deep surveys of nearby disk galaxies have started to provide constraints 
-    on their stellar halos (e.g. \citealt{Courteau2011, Merritt2016, 
-    Harmsen2017})\footnote{Although it is still not certain that all stellar halos
-    around disk galaxies are made out of \textit{ex situ} stars.} as it is
+    Recent deep surveys of nearby disc galaxies have started to provide constraints 
+    on their stellar haloes (e.g. \citealt{Courteau2011, Merritt2016, 
+    Harmsen2017})\footnote{Although it is still not certain that all stellar haloes
+    around disc galaxies are made out of \textit{ex situ} stars.}, as it is
     relatively easier to decompose the stellar halo component. 
@@
     }
-    In this work, we propose that \mstar{} computed within different fixed physical
-    elliptical apertures are worth exploring as proxies of the \textit{ex situ} 
-    fraction. 
+    In this work, we propose that \mstar{} values computed within different fixed 
+    physical elliptical apertures are worth exploring as proxies of the 
+    \textit{ex situ} fraction. 
     We propose to use the mass within 10 kpc (\minn{}) and 100 kpc (\mtot{}) as 
@@
 
-    On the left panel of Fig \ref{fig:discussion_1} we show the relation between 
-    \mtot{} and the fraction of mass between 10 and 100 kpc (as a proxy of the mass of 
-    the accreted component).
-    We compare this with the fraction of \textit{ex-situ} stars predicted by the 
+    On the left panel of Fig \ref{fig:discussion_1} we show 
+    the relation between \mtot{} and the fraction of mass between 10 and 100 kpc 
+    (as a proxy of the mass of the accreted component).
+    We compare this with the fraction of \textit{ex situ} stars predicted by the 
     Illustris simulation (\citealt{RodriguezGomez2016}).  
@@
     \citet{RodriguezGomez2016}.  
-    Given the limitations of the Illustris simulation, and the imperfect nature of 
+    Given the limitations of the Illustris simulation and the imperfect nature of 
     our \textit{ex situ} fraction proxy, the almost perfect agreement seen in 
@@
     predicted relation.  
-    There exists other hydrodynamic simulations that predict significantly different 
+    There are other hydrodynamic simulations that predict significantly different 
     \textit{ex situ} fractions compared to Illustris (e.g. \citealt{Lackner2012, 
@@
     \song{
-    Furthermore, a few known issues in the original Illustris simulation has been 
-    improved in the new Illustris--TNG version (e.g. \citealt{Genel2017, 
+    Furthermore, a few known issues in the original Illustris simulation have been 
+    resolved in the new Illustris--TNG version (e.g. \citealt{Genel2017, 
     Pillepich2017}.
-    In future works, we will explore more comparisons with detailed predictions 
-    from new simulations to see how well we can trace \textit{ex situ} fractions
-    in massive galaxies using simple elliptical aperture masses.
+    In future works [including Huang\etal (in prep.)], we will explore more 
+    comparisons with detailed predictions from new simulations to see how well we 
+    can trace \textit{ex situ} fractions in massive galaxies using simple 
+    elliptical aperture masses.
     }
@@
     Here, we further compare our \mden{} profiles with 
-    a) the profiles of the \textit{in-situ} component estimated from different ways,
-    and b) profiles of high redshift massive galaxies that should be dominated by 
+    (1) the profiles of the \textit{in situ} component estimated from different ways,
+    and (2) profiles of high-redshift massive galaxies that should be dominated by 
     the \textit{in situ} component.  
     }
-    In particular, we compare with:
-
-    \begin{enumerate}
+    In particular, we compare with the following:
+
+    \begin{itemize}
 
@@
             \citet{Huang2013b} show that this inner component is structurally 
-            similar to the compact ``red nuggets'' at high-$z$.
+            similar to the compact `red nuggets' at high-$z$.
 
         \item The \textit{in situ} components of simulated central galaxies in 
-            massive halos from \citet{Cooper2013} (the inner ${\sim} 5$ kpc is 
+            massive haloes from \citet{Cooper2013} (the inner ${\sim} 5$ kpc is 
             quite uncertain due to the resolution).  
@@
 
-    \end{enumerate}
-
-    \song{
-    Although these naive comparisons support the idea that \minn{} mainly consists 
-    of \textit{in situ} stars whereas mass at $\mathrm{R} > 15$-20 kpc is dominated 
+    \end{itemize}
+
+    \song{
+    Although these simple comparisons support the idea that \minn{} mainly consists 
+    of \textit{in situ} stars whereas mass at $\mathrm{R} > 15$--20 kpc is dominated 
     by \textit{ex situ} component, they also show that the \texttt{in situ} component 
@@
     \textit{ex situ} component. 
-    Since such photometric component extends to the center of the galaxy and can 
-    reach to radius much larger than 100 kpc, it can lead to higher \textit{ex situ}
+    Since such a photometric component extends to the center of the galaxy and can 
+    reach a radius much larger than 100 kpc, it can lead to a higher \textit{ex situ}
     fraction than ours (e.g. \citealt{Spavone2017}). 
-    It will be very interesting to apply similar decomposition method to both the 
-    HSC images and the simulated massive galaxies, to help us understand what is the 
+    It will be very interesting to apply a similar decomposition method to both the 
+    HSC images and the simulated massive galaxies to help us determine the 
     best tracer of the \textit{in situ} and \textit{ex situ} mass.
@@
     \song{
-    We also compare with a uniquely massive galaxy at high redshift: 
-    a \logms{}${\sim} 10^{11.4} M_{\odot}$ galaxy with a distinctive ``cD''-like 
+    We also compare our results with a uniquely massive galaxy at high redshift: 
+    a \logms{}${\sim} 10^{11.4} M_{\odot}$ galaxy with a distinctive `cD'-like 
     envelope at $z{\sim} 1.1$ (\citealt{Liu2013}).  
-    This high redshift galaxy has a \mden{} profile that follows the median \mden{} 
+    This high-redshift galaxy has a \mden{} profile that follows the median \mden{} 
     profile of our $11.6\leq$\logmtot{}$<11.8$ sample nicely at $\mathrm{R} < 40$ 
     kpc, but the profile becomes much steeper in the outskirt.
-    It suggests that while the very outskirt of the stellar halo is still being 
-    assembled, some massive high-$z$ galaxies may already have significant fraction 
-    of \textit{ex situ} stars. 
-    In future works, we will also look into the redshift evolution of the outer 
-    \mden{} profiles up to $z\sim 1.0$ using both HSC and other observations. 
-    Comparisons with simulations on this can also tell us how well we can trace
-    the evolution of \textit{ex situ} fraction using aperture masses.
+    The steeper profile suggests that, while the very outskirt of the stellar halo 
+    is still being assembled, some massive high-$z$ galaxies may already have a
+    significant fraction of \textit{ex situ} stars. 
+    In future works [including Huang\etal (in prep.)], we will also look into the 
+    redshift evolution of the outer \mden{} profiles up to $z\sim 1.0$ using both HSC 
+    and other observations. 
+    Comparisons with relevant simulations  can also tell us how well we can trace
+    the evolution of the \textit{ex situ} fraction of stars using aperture masses.
     }
@@
 
-    In this work, we study how the projected stellar mass density profiles and other 
-    structural properties of massive central galaxies depend on their total stellar 
-    mass using deep images from the Subaru HSC survey. 
-    With the help of this high-quality and wide area data set, we directly map the 
+    In this work, we use deep images from the Subaru HSC survey to study how the 
+    projected stellar mass density profiles and other structural properties of 
+    massive central galaxies depend on their total stellar mass. 
+    With the help of this high-quality, wide-area data set, we directly map the 
     stellar mass distributions of ${\sim}7000$ massive central galaxies at 
@@
 
-    \begin{enumerate}
+    \begin{itemize}
 
         \item We show that the \mden{} profiles of massive galaxies are relatively
-            homogenous within 10-20 kpc. 
+            homogenous within 10--20 kpc. 
             However, there is large scatter in outer profiles of massive galaxies. 
-            Galaxies with higher \mtot{} show more prominent stellar halos and have 
+            Galaxies with higher \mtot{} show more prominent stellar haloes and have 
             shallower outer \mden{} slopes. 
-            Assuming that stellar halos are dominated by accreted stars, this result 
+            Assuming that stellar haloes are dominated by accreted stars, this result 
             is consistent with the two-phase formation picture of massive galaxies.
@@
             gradients out to at least 60 kpc. 
-            The average ellipticity profile also depend on \mtot{}: more massive 
+            The average ellipticity profile also depends on \mtot{}: More massive 
             galaxies tend to have steeper ellipticity gradients and become more 
-            elongated in stellar halos.
+            elongated in stellar haloes.
 
@@
             On the other hand, although massive galaxies in all three \mtot{} bins 
-            show clearly negative average color gradients out to 60 kpc, the 
-            average $(g-r)$ and $(g-i)$ color gradients do not show clear dependence 
-            on \mtot{}. 
+            show clearly negative average colour gradients out to 60 kpc, the 
+            average $(g-r)$ and $(g-i)$ colour gradients do not show clear 
+            dependence on \mtot{}. 
             }
@@
             Here we show that \minn{} and the \mstar{} between 10 and 100 kpc could 
-            be promising proxies of the two physical components, and can recover the 
+            be promising proxies for the two physical components, and can recover the 
             trend between stellar mass and \textit{ex situ} fraction from simulation.
@@
 
-        \item We find that the ``total'' \mstar{} of these massive galaxies can be 
+        \item We find that the `total' \mstar{} of these massive galaxies can be 
             significantly underestimated with shallow imaging data such as SDSS and/or 
@@
             \mtot{}. 
-            Simple model misses more light for massive galaxies because they have 
+            A simple model misses more light for massive galaxies because they have 
             more extended envelopes. 
-            There is also a \mhalo{}-dependence of this effect and naive luminosity
-            estimates will miss more light for BCGs in more massive halos compared 
-            to centrals in less massive halos.
+            There is also an \mhalo{}-dependence of this effect, and simple 
+            luminosity estimates will miss more light for BCGs in more massive 
+            haloes compared to centrals in less massive haloes.
             These effects need to be carefully taken into account when discussing 
@@
 
-    \end{enumerate}
-
-    These results highlight the advantages of wide area, deep, and high-quality imaging 
+    \end{itemize}
+
+    These results highlight the advantages of wide-area, deep, and high-quality imaging 
     for studying the evolution of massive galaxies. 
     At present, the HSC survey has already doubled its sky coverage to 
-    ${\sim} 200$ deg$^2$, and provides a much larger sample of massive central galaxies. 
+    ${\sim} 200$ deg$^2$ and provides a much larger sample of massive central galaxies. 
     In the near future, we will extend this work to lower \mtot{} by using photometric 
-    redshifts, and we will also apply 2-D photometric methods (e.g.\ \citealt{Huang2013a}) 
-    to take advantage of the multi-wavelength nature of the HSC survey 
-    (e.g. \citealt{Huang2016}). 
+    redshifts, and we will also apply 2-D photometric methods 
+    (e.g.\ \citealt{Huang2013a}) to take advantage of the multi-wavelength nature of 
+    the HSC survey (e.g. \citealt{Huang2016}). 
     Our current work can also be combined with weak lensing measurements of the dark 
-    matter halos of massive galaxies and physical insights into the assembly histories 
-    of these galaxies can be gained by comparing with cosmological hydro-simulations 
-    such as Illustris (\citealt{Vogelsberger2014}, \citealt{Genel2014}), 
-    EAGLE (\citealt{Schaye2015}, \citealt{Crain2015}), or \textit{Horizon-AGN} 
-    (\citealt{Dubois2014}).
+    matter haloes of massive galaxies, and physical insights into the assembly histories 
+    of these galaxies can be gained by comparing the measurements with cosmological 
+    hydro-simulations such as Illustris (\citealt{Vogelsberger2014}, 
+    \citealt{Genel2014}), EAGLE (\citealt{Schaye2015}, \citealt{Crain2015}), 
+    or \textit{Horizon-AGN} (\citealt{Dubois2014}).
 
@@
   The authors thank Rachel Mandelbaum and Frank van~den~Bosch for insightful 
-  discussions and comments; 
-  thank Shun Saito for helping us estimate the fraction of satellite 
-  galaxies in our sample;
-  thank Feng-Shan Liu for sharing the \mden{} profile of the $z\sim1$ BCG from 
+  discussions and comments,
+  Shun Saito for helping us estimate the fraction of satellite 
+  galaxies in our sample, and
+  Feng-Shan Liu for sharing the \mden{} profile of the $z\sim1$ BCG from 
   his work.
@@
   The Hyper Suprime-Cam (HSC) collaboration includes the astronomical communities of 
-  Japan and Taiwan, and Princeton University.  The HSC instrumentation and software were
-  developed by the National Astronomical Observatory of Japan (NAOJ), the Kavli Institute
-  for the Physics and Mathematics of the Universe (Kavli IPMU), the University of Tokyo,
-  the High Energy Accelerator Research Organization (KEK), the Academia Sinica Institute
-  for Astronomy and Astrophysics in Taiwan (ASIAA), and Princeton University.  
-  Funding was contributed by the FIRST program from Japanese Cabinet Office, the Ministry 
-  of Education, Culture, Sports, Science and Technology (MEXT), the Japan Society for 
-  the Promotion of Science (JSPS), Japan Science and Technology Agency (JST), the
-  Toray Science Foundation, NAOJ, Kavli IPMU, KEK, ASIAA, and Princeton University.
+  Japan and Taiwan, and Princeton University.  The HSC instrumentation and software 
+  were developed by  National Astronomical Observatory of Japan (NAOJ), Kavli 
+  Institute for the Physics and Mathematics of the Universe (Kavli IPMU), University 
+  of Tokyo, High Energy Accelerator Research Organization (KEK), Academia Sinica 
+  Institute for Astronomy and Astrophysics in Taiwan (ASIAA), and Princeton 
+  University.  
+  Funding was contributed by the FIRST program from the Japanese Cabinet Office;  
+  Ministry of Education, Culture, Sports, Science and Technology (MEXT);  
+  Japan Society for the Promotion of Science (JSPS); 
+  Japan Science and Technology Agency (JST); 
+  Toray Science Foundation; NAOJ; Kavli IPMU; KEK; ASIAA; and Princeton University.
 
   % SDSS part
-  Funding for SDSS-III has been provided by the Alfred P. Sloan Foundation, the
-  Participating Institutions, the National Science Foundation, and the U.S.  Department of
-  Energy. The SDSS-III web site is http://www.sdss3.org.  SDSS-III is managed by the
+  Funding for SDSS-III has been provided by Alfred P. Sloan Foundation, 
+  Participating Institutions, National Science Foundation, and  U.S.  Department of
+  Energy. The SDSS-III web site is http://www.sdss3.org.  SDSS-III is managed by 
   Astrophysical Research Consortium for the Participating Institutions of the SDSS-III
-  Collaboration including the University of Arizona, the Brazilian Participation Group,
+  Collaboration, which includes  University of Arizona,  Brazilian Participation Group,
   Brookhaven National Laboratory, University of Cambridge, University of Florida, the
-  French Participation Group, the German Participation Group, the Instituto de Astrofisica
-  de Canarias, the Michigan State/Notre Dame/JINA Participation Group, Johns Hopkins
+  French Participation Group,  German Participation Group, Instituto de Astrofisica
+  de Canarias,  Michigan State/Notre Dame/JINA Participation Group, Johns Hopkins
   University, Lawrence Berkeley National Laboratory, Max Planck Institute for
@@
   % Pan-STARRS1 part
-  The Pan-STARRS1 Surveys (PS1) have been made possible through contributions of the 
-  Institute for Astronomy, the University of Hawaii, the Pan-STARRS Project Office, 
-  the Max-Planck Society and its participating institutes, the Max Planck Institute 
-  for Astronomy, Heidelberg and the Max Planck Institute for Extraterrestrial Physics, 
-  Garching, The Johns Hopkins University, Durham University, the University of Edinburgh, 
-  Queen's University Belfast, the Harvard-Smithsonian Center for Astrophysics, the Las 
-  Cumbres Observatory Global Telescope Network Incorporated, the National Central 
-  University of Taiwan, the Space Telescope Science Institute, the National Aeronautics 
+  The Pan-STARRS1 Surveys (PS1) have been made possible through contributions of  
+  Institute for Astronomy;  University of Hawaii;  Pan-STARRS Project Office; 
+   Max-Planck Society and its participating institutes:  Max Planck Institute 
+  for Astronomy, Heidelberg, and the Max Planck Institute for Extraterrestrial Physics, 
+  Garching;  Johns Hopkins University; Durham University;  University of Edinburgh; 
+  Queen's University Belfast;  Harvard--Smithsonian Center for Astrophysics;  Las 
+  Cumbres Observatory Global Telescope Network Incorporated;  National Central 
+  University of Taiwan;  Space Telescope Science Institute; National Aeronautics 
   and Space Administration under Grant No. NNX08AR22G issued through the Planetary 
-  Science Division of the NASA Science Mission Directorate, the National Science 
-  Foundation under Grant No. AST-1238877, the University of Maryland, and Eotvos 
-  Lorand University (ELTE).
+  Science Division of the NASA Science Mission Directorate; National Science 
+  Foundation under Grant No. AST-1238877; University of Maryland; and Eötvös Loránd 
+  University (ELTE).
 
@@
   % KITP
-  This research was supported in part by the National Science Foundation under Grant 
+  This research was supported in part by National Science Foundation under Grant 
   No. NSF PHY11-25915.
@@
   This research made use of:
-  \href{http://www.stsci.edu/institute/software_hardware/pyraf/stsci\_python}{\texttt{STSCI\_PYTHON}},
+  \href{http://www.stsci.edu/institute/software_hardware/pyraf/stsci\_python}
+  {\texttt{\small{STSCI\_PYTHON}}},
       a general astronomical data analysis infrastructure in Python. 
-      \texttt{STSCI\_PYTHON} is a product of the Space Telescope Science Institute, 
-      which is operated by AURA for NASA;
+      \texttt{\small{STSCI\_PYTHON}} is a product of the Space Telescope Science
+      Institute, which is operated by Association of Universities for Research 
+      in Astronomy (AURA) for NASA;
   \href{http://www.scipy.org/}{\texttt{SciPy}},
@@
   \href{http://www.astropy.org/}{\texttt{Astropy}}, a community-developed 
-      core Python package for Astronomy (\citealt{AstroPy}); 
+      core Python package for astronomy (\citealt{AstroPy}); 
   \href{http://scikit-learn.org/stable/index.html}{\texttt{scikit-learn}},
@@
   \href{http://www.astroml.org/}{\texttt{astroML}}, 
-      a machine learning library for astrophysics (\citealt{astroML});
+      a machine-learning library for astrophysics (\citealt{astroML});
   \href{https://ipython.org}{\texttt{IPython}}, 
@@
       \caption{
-          \textbf{Top-left}: The \logmtot{}-$(g-r)$ rest-frame color relation for the 
+          \textbf{Top-left}: The \logmtot{}-$(g-r)$ rest-frame colour relation for the 
           HSC massive galaxies.
-          We $k$-correct the color using the \texttt{iSEDFit} fitting results.
-          Massive galaxies form a ``red-sequence'' on this figure, and there is 
+          We $k$-correct the colour using the \texttt{iSEDFit} fitting results.
+          Massive galaxies form a `red-sequence' on this figure, and there is 
           little contamination from blue object at high-mass end.~~          
-          \textbf{Top-right}: the redshift distribution of the massive galaxies. 
+          \textbf{Top-right}: The redshift distribution of the massive galaxies. 
           The filled and empty histograms are for the \logmtot{}$>11.6$ and 
           \logmtot{}$>11.2$ galaxies.
-          The vertical lines highlights the $0.3\leq z \leq 0.5$ redshift range.~~
-          \textbf{Bottom-left}: the distributions of \mtot{} of massive galaxies in 
+          The vertical lines highlight the $0.3\leq z \leq 0.5$ redshift range.~~
+          \textbf{Bottom-left}: The distributions of \mtot{} of massive galaxies in 
           this sample. 
@@
           used in this work. 
-          And the empty histogram shows the distribution for the whole $z>0.2$ sample
+          The empty histogram shows the distribution for the whole $z>0.2$ sample
           as comparison.~~
-          \textbf{Bottom-right}: the distributions of \minn{} in similar format. 
+          \textbf{Bottom-right}: The distributions of \minn{} in similar format. 
       }
@@
 %% ------------------------------------------------------------------------------------ %% 
-\section{A. Basic Statistical Properties of the Sample} 
+    \begin{figure*}
+        \centering 
+        \includegraphics[width=\textwidth]{fig/redbcg_ellipse_tech}
+        \caption{
+            \textbf{Left:} Example of the object-mask built for the \texttt{Ellipse}
+            run for a typical massive galaxy in the sample. 
+            All the shaded regions are masked out. 
+            The three dashed lines (one red inner line and two blue lines) around 
+            the target at the center outlines the three radii we defined using the 
+            flux radius of the target.  
+            We increase the mask size for objects detected in different regions 
+            separated by these apertures (which are outlined by solid, elliptical 
+            apertures with different colours) using slightly different criteria.~~
+            \textbf{Middle:}: The zoom-in intensity profile around very low intensity 
+            value (top panel), and the curve-of-growth of the enclosed magnitude 
+            (bottom panel) of the example galaxy.  
+            To highlight the importance of background correction, we show the profiles 
+            using both images with (red solid line) and without (black dotted line) 
+            background correction. 
+            On the top panel, besides the horizontal line that highlights the zero flux 
+            level, we also show the uncertainty of the sky background estimate using 
+            the grey-shaded region.  
+            On the bottom panel, two horizontal lines indicate the magnitudes 
+            corresponding to total flux (solid) and flux within 100 kpc (dashed).~~
+            \textbf{Right:} Compares the 1-D surface brightness profiles for the same 
+            example galaxy using different masks 
+            (smaller masking region: red dashed line; larger masks: blue dashed line), 
+            or different \texttt{Ellipse} configurations
+            (more aggressive pixel-clipping: cyan dashed line; 
+            larger step in radius: green dashed line; 
+            using mean flux along the isophote instead of median: purple dashed line)
+            with the default one (black solid line).
+            }
+        \label{fig:ell_tech}
+    \end{figure*}
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %%  
+\section{Basic Statistical Properties of the Sample} 
 	\label{app:basic}
@@
     Here we show the basic statistics of the massive galaxies used in this work.
-    On the top-left panel of Fig~\ref{fig:sample_stats}, we show the \mtot{}-color 
-    relation using the $k$-corrected rest-frame $(g-r)$ color. 
-    These massive galaxies form a clear ``red-sequence'' with little contamination 
-    from the ``blue cloud'' at the very high-mass end.
+    On the top-left panel of Fig~\ref{fig:sample_stats}, we show the \mtot{}-colour 
+    relation using the $k$-corrected rest-frame $(g-r)$ colour. 
+    These massive galaxies form a clear `red sequence' with little contamination 
+    from the `blue cloud' at the very high-mass end.
 
@@
 %% ------------------------------------------------------------------------------------ %% 
-\section{B. Extraction of 1-D surface brightness profile} 
+\section{Extraction of 1-D surface brightness profile} 
     \label{app:ellipse}
@@
 
-    To derive reliable 1-D profile, it is important to mask out all the irrelevant 
+    To derive a reliable 1-D profile, it is important to mask out all the irrelevant 
     objects around the target.
@@
     bright objects.  
-    The performance of its deblending process is also not optimized for extended
-    objects. 
+    In addition, the \texttt{hscPipe} deblending process performance is not optimized 
+    for extended objects. 
     For these reasons, we perform \texttt{SExtractor}-like background subtraction and 
@@
     Combining two different local background models and $S/N$ thresholds, we obtain 
-    the centroid, shape, and radius that enclose 90\% of flux for each object, 
-    including the one that is very close to the center of bright galaxy (left panel of 
-    Fig~\ref{fig:ell_tech}). 
-    Based on these information, we then create the mask that covers all contaminating 
+    the centroid, shape, and radius that together encloses 90\% of flux for each 
+    object, including the one that is very close to the center of bright galaxy 
+    (left panel of Fig~\ref{fig:ell_tech}). 
+    Based on this information, we then create the mask that covers all contaminating 
     objects around the target after adaptively increasing the sizes of their masks 
     according to their brightness and distance to the central target. 
-    Generally speaking, we mask out bright objects or objects in the outskirt of the 
-    image more aggressively to reduce their impact on the surface brightness profiles 
-    in the outskirt. 
-    We also create masks that are less and more aggressive than the default one to 
+    Generally speaking, we more aggressively mask out bright objects or objects in 
+    the outskirt of the image to reduce their impact on the surface brightness 
+    profiles in the outskirt. 
+    We also create masks that are less and more aggressive than the default mask to 
     test their impacts on the surface brightness profiles.
@@
     However, as mentioned, we often find evidence of slightly over-subtracted 
-    background for massive galaxies in our sample. 
-    In the current \texttt{hscPipe}, the background on each CCD is modeled with a 
+    backgrounds for massive galaxies in our sample. 
+    In the current \texttt{hscPipe}, the background on each CCD is modelled with a 
     Chebyshev-polynomial that is fit to the smoothed image after excluding pixels 
@@
     sky boxes).
-    This model can account for the slightly over-subtracted background at large scale,
-    and reduce the impact from the low surface brightness ``wings'' of bright 
+    This model can account for the slightly over-subtracted background at large 
+    scale and reduce the impact from the low--surface brightness `wings' of bright 
     neighbors. 
@@
     (more symmetric distribution; median value is closer to 0) and the surface 
-    brightness profile (middle panel of Fig~\ref{app:ellipse}; the negative intensity 
-    and the turn-over of the curve-of-growth in the outskirt of the ``Original'' 
-    profile are successfully corrected) after this correction.
+    brightness profile (middle panel of Fig~\ref{app:ellipse}; the negative 
+    intensity and the turn-over of the curve-of-growth in the outskirt of the 
+    `Original' profile are successfully corrected) after this correction.
     Also, it is worth mentioning that such correction does not often affect the 
@@
     The procedure used to derive 1-D surface brightness profile from the 
-    background-corrected, contamination-masked images is already described in 
-    \S~\ref{sec:ellipse} briefly. 
+    background-corrected, contamination-masked images is  described briefly in 
+    \S~\ref{sec:ellipse}. 
     \song{
@@
     After some tests, we choose to use 0.1 dex in logarithm as the step in semi-major 
-    axis length between successive ellipses, and we use the median pixel value over the
-    elliptical annulus after rejecting outlying pixels via $3\sigma$-clipping three
-    times.
-    We make the above choices to make the final profile less affected by any nearby
-    object, and also test the differences between the profiles derived using larger
+    axis length between successive ellipses, and we use the median pixel value over 
+    the elliptical annulus after rejecting outlying pixels via 3-$\sigma$ clipping 
+    three times.
+    We make these  choices to make the final profile less affected by any nearby
+    object and also to test the differences between the profiles derived using larger
     step, or mean value on the annulus, or fewer times of $\sigma$-clipping. 
@@
     The profile within 100 kpc is very stable, and the only noticable difference 
-    is caused by the less aggressive object-mask in the very outskirt.
-
-    We should also mention that we run \texttt{Ellipse} allowing for more 
+    is caused by the less aggressive object-mask in the outskirt.
+
+    We should also mention that we run \texttt{Ellipse} to allow for more 
     sophisticated shapes than simple ellipse (4th Fourier modes that can make 
-    isophote more ``disky'' or ``boxy'', e.g.\ \citealt{Kormendy2009}) to fit the 
+    isophote more `disky' or `boxy', e.g.\ \citealt{Kormendy2009}) to fit the 
     isophote better.
-    We also apply the isophotes from $i$-band images to other bands in 
-    ``force-photometry'' mode \texttt{Ellipse} run to get initial estimates of 
-    color profiles.
-
-    \song{
-    We cannot extract reliable 1-D profiles for a small fraction of massive galaxies 
-    because they are heavily masked out for either physical 
+    We also apply the isophotes from $i$-band images to other bands in a
+    `force-photometry' mode \texttt{Ellipse} run to get initial estimates of 
+    colour profiles.
+
+    \song{
+    We cannot extract reliable 1-D profiles for a small fraction of massive
+    galaxies because they are heavily masked out for either physical 
     (e.g.\ late-stage major merger) or nuisance (e.g.\ nearby foreground 
     galaxy or bright star) reasons. 
-    This is an intrinsic limitation of the 1-D method, and it removes ${\sim}10$\% of 
-    the sample.
-    We visually examine the 3-color images of randomly selected galaxies with failed 
-    1-D profiles.  
-    Most of them are relative small galaxies that are severely contaminated by nearby 
-    objects, and will not affect the results of this work.  
-    Meanwhile, it is worth noting that this does exclude most major merging systems 
-    among massive galaxies. 
-    }
-
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %% 
-    \begin{figure*}
-        \centering 
-        \includegraphics[width=\textwidth]{fig/redbcg_ellipse_tech}
-        \caption{
-            \textbf{Left:} Example of the object-mask built for the \texttt{Ellipse}
-            run for a typical massive galaxy in the sample. 
-            All the shaded regions are masked out. 
-            The three dash lines (red, inner one and two blue ones) around the target 
-            at the center outlines the three radius we defined using the flux radius 
-            of the target.  
-            We increase the mask size for objects detected in different regions 
-            separated by these apertures (which are outlined by solid, elliptical 
-            apertures with different colors) using slightly different criteria.~~
-            \textbf{Middle:}: The zoom-in intensity profile around very low intensity 
-            value (top panel), and the curve-of-growth of the enclosed magnitude 
-            (bottom panel) of the example galaxy.  
-            To highlight the importance of background correction, we show the profiles 
-            using both images with (red, solid line) and without (black, dotted line) 
-            background correction. 
-            On the top panel, besides the horizontal line that highlights the zero flux 
-            level, we also show the uncertainty of the sky background estimate using 
-            the grey-shaded region.  
-            On the bottom panel, two horizontal lines indicate the magnitudes 
-            corresponding to total flux (solid) and flux within 100 kpc (dash).~~
-            \textbf{Right:} compares the 1-D surface brightness profiles for the same 
-            example galaxy using different masks 
-            (smaller masking region: red, dash line; larger masks: blue, dash line), 
-            or different \texttt{Ellipse} configurations
-            (more aggressive pixel-clipping: cyan, dash line; 
-             larger step in radius: green, dash line; 
-             using mean flux along the isophote instead of median: purple, dash line)
-            with the default one (black, solid line).
-            }
-        \label{fig:ell_tech}
-    \end{figure*}
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %% 
-\section{C. Estimate average {$M_{\star}/L_{\star}$} using \texttt{iSEDFit}} 
+    This is an intrinsic limitation of the 1-D method, and it removes ${\sim}10$\% 
+    of the sample.
+    We visually examine the 3-colour images of randomly selected galaxies with 
+    failed 1-D profiles.  
+    Most of them are relatively small galaxies that are severely contaminated by 
+    nearby objects and do not affect the results of this work.  
+    Meanwhile, it is worth noting that this work does exclude most major merging 
+    systems among massive galaxies. 
+    }
+
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
+\section{Estimate average {$M_{\star}/L_{\star}$} using \texttt{iSEDFit}} 
     \label{app:sed}
@@
             the SED fitting results. 
-            The open-boxes show the observed fluxes in 5-band, and the solid, blue-dots
-            show the best-fitted results, along with the high-resolution spectrum for
-            this model reconstructed using the synthetic spectra from \texttt{FSPS}. 
-            Top-left corner shows the best-fit stellar population parameters, and 
-            bottom-right corner shows the ID, redshift of this object, and reduced 
-            $\chi^2$ of the best-fit model.~~~
-            \textbf{Right:} the Posterior distributions of a few key parameters.
+            The open boxes show the observed fluxes in the five bands, and the solid 
+            blue dots show the best-fitting results, along with the high-resolution
+            spectrum for this model reconstructed using the synthetic spectra from
+            \texttt{FSPS}. 
+            The top-left corner shows the best-fitting stellar population parameters, 
+            and the bottom-right corner shows the ID, redshift of this object, and 
+            reduced $\chi^2$ of the best-fitting model.~~~
+            \textbf{Right:} the posterior distributions of a few key
+            parameters.
             From top-left to bottom right are: 
-            1) stellar mass (\logms{}); 
-            2) age of the population (mass and star-formation rate weighted) in Gyr; 
-            3) star formation rate ($\log\ \mathrm{SFR}\ (M_{\odot}/\mathrm{yr})$; 
+            (1) stellar mass (\logms{}); 
+            (2) age of the population (mass and star-formation rate weighted) in Gyr; 
+            (3) star formation rate ($\log\ \mathrm{SFR}\ (M_{\odot}/\mathrm{yr})$; 
             instant one and the one averaged over the previous 100 Myr; 
-            4) stellar metallicity ($\mathrm{Z}/\mathrm{Z}_{\odot}$); 
-            5) dust extinction ($\mathrm{A}_V$ in mag);
-            6) birthrate parameter ($\log\ b$; averaged over previous 100 and 1000 Myr).
+            (4) stellar metallicity ($\mathrm{Z}/\mathrm{Z}_{\odot}$); 
+            (5) dust extinction ($\mathrm{A}_V$ in mag);
+            (6) birthrate parameter ($\log\ b$; averaged over previous 100 and 
+            1000 Myr).
             }
@@
             The four stellar population properties are: 
-            1) \textbf{Top-left}: \mstar{}-weighted stellar population age in Gyr; 
-            2) \textbf{Bottom-left}: SFR-weighted age in Gyr; 
-            3) \textbf{Top-right}: \mstar{}-weighted stellar metallicity in unit of 
-            Solar value;
-            4) \textbf{bottom-right}: dust extinction value in $V$-band.
+            \textbf{Top-left}: \mstar{}-weighted stellar population age 
+            in Gyr. 
+            \textbf{Bottom-left}: SFR-weighted age in Gyr. 
+            \textbf{Top-right}: \mstar{}-weighted stellar metallicity in 
+            unit of solar value.
+            \textbf{bottom-right}: Dust extinction value in $V$-band.
             As expected, most of the HSC massive galaxies are old, metal-rich, and 
@@
             model assumptions. 
-            In each figure, we plot the \mstar{} from the default model against the
-            differences with other models. 
-            The four models involved are labeled as: 
+            In each panel, we plot the \mstar{} from the default model against the
+            differences with four other models:
             (A): Default model; 
-            (B): Using the Salpeter IMF instead of the Chabrier one 
-                (\textbf{Top panel});
+            (B): Using the Salpeter IMF instead of the Chabrier IMF 
+                (\textbf{Top panel}) ;
             (C): Using the BC03 synthetic population model instead of the FSPS one
@@
             (D): No dust extinction (\textbf{Bottom panel}). 
-            On each panel, the grey shaded region highlights the typical uncertainty 
+            On each panel, the grey-shaded region highlights the typical uncertainty 
             of the $\log($\logms{}$)$.            
-            For each pair of models, we highlight their median $\chi^{2}$ values and 
+            For each pair of models, we highlight the median $\chi^{2}$ values and 
             the fraction of galaxies with $\chi^{2} > 10.0$ at the top. 
@@
     Based on these models, it uses the observed photometry and redshift to compute 
-    the statistical likelihood, and generates the posterior probability distribution 
-    functions (PDF) for each parameter.  
+    the statistical likelihood and generates the posterior PDF for each parameter.  
     To get the best estimate of a given parameter, \texttt{iSEDFit} integrates the 
@@
     In Fig~\ref{fig:ised_1}, we show an example of the \texttt{iSEDFit} output by 
-    visualizing the 5-band HSC SED on top of the best-fit model along with the PDF 
+    visualizing the five-band HSC SED on top of the best-fitting model along with the PDF 
     of the key parameters.
 
-    Although we only use the best-fit \m2l{} in this work, it is necessary to make 
+    Although we only use the best-fitting \m2l{} in this work, it is necessary to make 
     sure the model is reasonable. 
-    We show the relations between \mstar{} and a few key stellar population parameters 
+    We show the relationship between \mstar{} and a few key stellar population parameters 
     derived by \texttt{iSEDFit} in Fig~\ref{fig:ised_2}. 
     Degeneracies among these parameters are inevitable based on only five broad-band
-    photometry, but as expected, most massive galaxies show old stellar age, high
+    photometry; but as expected, most massive galaxies show old stellar age, high
     stellar metallicity ($1.5 \times Z_{\odot}$ is the highest metallicity allowed by 
@@
     For massive galaxies in this sample, the form of the SFH\footnote{We choose 
-    to use the delayed-$\tau$ model for SFH; we adopt flat distribution between 
-    0.5 to 14.0 Gyrs as the prior for the look-back time when the star formation 
+    to use the delayed-$\tau$ model for SFH; we adopt a flat distribution between 
+    0.5 and 14.0 Gyrs as the prior for the look-back time when the star formation 
     turned on. 
     The exponential delayed time-scale ($\tau$) is allowed to change between 
-    0.1 to 3.0 with equal probability}, the contribution from random star 
+    0.1 and 3.0 with equal probability}, and the contribution from random star 
     burst\footnote{The chance of random star burst is set at 0.2 for every 2 Gyrs. 
-    The duration of the star burst is draw from a logarithmic distribution 
-    between 0.03 to 0.3 Gyr; and the mass fraction formed in the burst is from 
+    The duration of the star burst is drawn from a logarithmic distribution 
+    between 0.03 and 0.3 Gyr; and the mass fraction formed in the burst is from 
     a logarithmic distribution between 0.01 and 1.0.} rarely affect the \mstar{}. 
-    But he choices of SSP model, IMF, and dust extinction do systematically impact
-    the estimates of \mstar{}, and therefore we look into this with a few 
+    But the choices of SSP model, IMF, and dust extinction do systematically impact
+    the estimates of \mstar{}; therefore, we look into this with a few 
     additional tests (see Fig~\ref{fig:ised_3}):
 
-    \begin{enumerate}
+    \begin{itemize}
 
@@
             Although there are multiple lines of evidence that favor Salpeter 
-            or even more ``bottom-heavy'' IMF in massive galaxies 
+            or an even more `bottom-heavy' IMF in massive galaxies 
             (e.g.\ \citealt{Conroy2012}; \citealt{Cappellari2012}), we still 
@@
             with lower \mstar{} in the sample, and to be as consistent as possible 
-            with previous works.  
+            with previous work.  
             This choice of IMF does not change the main results qualitatively.
@@
             although it is not \mstar{}-dependent. 
-            The \texttt{BC03} results show better average ${\chi}^2$ than the 
+            The \texttt{BC03} results show a better average ${\chi}^2$ than the 
             \texttt{FSPS} ones. 
@@
             ($2 \times \mathrm{Z}_{\odot}$) allowed by the \texttt{BC03} model, 
-            which help fits the shape of the SED in the red-end slightly better.  
+            which helps fit the shape of the SED in the red-end slightly better.  
             However, the \texttt{BC03} results also show puzzlingly low stellar 
@@
             This could also lead to underestimated \m2l{} values.
-            It is worth noting that, both \texttt{FSPS} and \texttt{BC03} 
+            It is worth noting that both \texttt{FSPS} and \texttt{BC03} 
             models still have difficulties recovering SED at the very red-end 
-            (between $z$ and $y$-band), and reproducing the optical color-color 
+            (between $z$ and $y$-band) and reproducing the optical colour--colour 
             relations for red-sequence galaxies (e.g.\ \citealt{MIUSCAT2}).
@@
             the fiducial one.  
-            Using results based on \texttt{BC03} model will not change any of our 
-            conclusions here.
-
-        \item On the bottom panel of Fig~\ref{fig:ised_3}, we compare with the
-            SED fitting results without considering the dust extinction. 
+            Using results based on the \texttt{BC03} model does not change any of 
+            our conclusions here.
+
+        \item On the bottom panel of Fig~\ref{fig:ised_3}, we compare the default 
+            model with the SED fitting results without considering the dust 
+            extinction. 
             This choice leads to slightly smaller \mstar{} values as expected. 
             Its impact becomes slightly larger at lower \mstar{} end. 
-            It will not change any of our conclusions here.
-
-    \end{enumerate}
+            It does not change any of our conclusions here.
+
+    \end{itemize}
 
@@
     We should also point out that our methodology ignores radial variations in \m2l{}. 
-    It is well known that massive ETGs have negative optical color gradients 
+    It is well known that massive ETGs have negative optical colour gradients, 
     indicating gradients in \m2l{} (e.g.\ \citealt{Carollo1993, Davies1993, 
-    LaBarbera2012, DSouza2015}). 
-    Assuming all massive galaxies in our sample have negative color gradients, and 
-    there is a simple monotonic relation between optical color and \m2l{}, the
-    average \m2l{} we used should in principle underestimate the \mstar{} in the 
-    center while overestimate the \mstar{} in the outskirt.
-    However, these color gradients are shallow and smooth out to a few times the 
+    LaBarbera2012, dSouza2015}). 
+    Assuming all massive galaxies in our sample have negative colour gradients and 
+    there is a simple monotonic relationship between optical colour and \m2l{}, the
+    average \m2l{} we use should in principle underestimate the \mstar{} in the 
+    center while overestimating the \mstar{} in the outskirt.
+    However, these colour gradients are shallow and they smooth out to a few times the 
     effective radius (e.g. \citealt{LaBarbera2010, Tal2011, DSouza2014}, 
-    color gradients at larger radii are not yet well quantified). 
+    colour gradients at larger radii are not yet well quantified). 
     Because the gradients are shallow, using an average \m2l{} is unlikely to bias 
@@
     In \citet{Huang2016}, the authors conduct multi-band decomposition for a sample 
-    of very nearby elliptical galaxies, and estimate the \m2l{} of each component 
+    of very nearby elliptical galaxies and estimate the \m2l{} of each component 
     separately. 
-    The sum of all components suggest a slightly higher \mstar{} ($0.05-0.10$ dex 
-    when typical uncertainty of \mstar{} is 0.12-0.15 dex) and the mass differences 
+    The sum of all components suggests a slightly higher \mstar{} ($0.05-0.10$ dex 
+    when typical uncertainty of \mstar{} is 0.12--0.15 dex) and the mass differences 
     show no dependence on \mstar{}. 
-    Color gradients are discussed in \S~\ref{ssec:ell_color}. 
+    Colour gradients are discussed in \S~\ref{ssec:ell_color}. 
     In summary, our results about the mass dependence of \mden{} profiles should not 
-    be affected by the assumption of a constant \m2l{} ratio because optical color 
+    be affected by the assumption of a constant \m2l{} ratio because optical colour 
     gradients in our sample do not show a dependence on stellar mass.

### 2017-11-16 draft/paper2_v6.tex
Minor changes

--- 2017-08-09 draft/paper2_v5.tex
@@
 \newcommand{\note}[2]{\textcolor{blue}{\textbf{[Comment (#1): #2]}}}
-\newcommand{\song}[1]{\textcolor{magenta}{\textbf{[Song: #1]}}}
+\newcommand{\song}[1]{\textcolor{cyan}{#1}}
 \newcommand{\alexie}[1]{\textcolor{blue}{\textbf{[Alexie: #1]}}}
@@
     We conclusively show that at fixed stellar mass, the stellar profiles of massive 
-    galaxies depend on the masses of their dark matter halos. 
-    On average, massive central galaxies with \logmtot{}$>11.6$ in more massive halos 
+    galaxies depend on the masses of their dark matter haloes. 
+    On average, massive central galaxies with \logmtot{}$>11.6$ in more massive haloes 
     at $0.3 < z < 0.5$ have shallower inner stellar mass density profiles 
@@
     These differences translate into a halo mass dependence of the 
-    mass--size relation: central galaxies in halos with \logmh{}$>14.0$ are 
+    mass--size relation: central galaxies in haloes with \logmh{}$>14.0$ are 
     $\sim 20$\% larger in $R_{\mathrm{50}}$ at fixed \mtot{}.  
@@
     galaxies: structure -- 
-    galaxies: surveys
+    galaxies: haloes
 \end{keywords}
@@
 
-    A key discovery in the last 
-    decade has been the dramatic structural transformation of massive quiescent 
-    galaxies \citep[e.g.][]{Trujillo2006, vanDokkum2008, Cimatti2008, Damjanov2009, 
-    vanderWel2011, Szomoru2012, Patel2013} from $z \approx 2$ to the present day. 
+    A key discovery in the last decade has been the dramatic structural transformation 
+    of massive quiescent galaxies \citep[e.g.][]{Trujillo2006, vanDokkum2008, 
+    Cimatti2008, Damjanov2009, vanderWel2011, Szomoru2012, Patel2013} from 
+    $z \approx 2$ to the present day. 
     These observations suggest that the progenitors of $z{\sim} 0$ massive early-type 
@@
     Greene2015, Barbosa2016}. 
-    Although these observations are generally consistent with the two-phase scenario, 
-    this picture still faces a key puzzle: whether or not sizes and profiles of galaxies 
-    depend on the mass of their host dark matter halos.
-
-    According to the two-phase formation scenario, the late time growth of massive 
-    ETGs is intrinsically tied to the growth of their host dark matter haloes 
+    \song{
+    These observations are generally consistent with the two-phase formation scenario. 
+    However, it is still not clear whether this promising picture can correctly 
+    predict the connection between the stellar mass distributions in massive galaxies 
+    and their dark matter haloes.
+    }
+
+    \song{
+    Under the $\Lambda$CDM cosmology, The assembly of massive ETGs is intrinsically 
+    tied to the hierarchal growth of their host dark matter haloes 
     (e.g. \citealt{Leauthaud2012, Behroozi2013, Shankar2013}). 
-    Massive ETGs living at the centers of more massive haloes should be subject to 
-    higher merger rates compared to ETGs with similar stellar mass but living in less 
-    massive dark matter haloes. 
-    A natural prediction of this picture is therefore that the structures of 
-    massive ETGs should depend on their ``environment''\footnote{There are 
-    multiple definitions of ``environment'' in the literature.  
-    In this work, we use ``environment'' and halo mass interchangeably.}.
-    Theoretical models based on the two-phase formation scenario predict an 
-    environmental dependence of the stellar mass--effective radius relation for 
-    ETGs (\mstar{}--$R_{\rm e}$; 
-    e.g., \citealt{Shen2003, Guo2009}): the sizes of massive ETGs in more massive 
-    haloes should be larger than those in less massive haloes at fixed \mstar{} 
+    Hydrodynamic simulations suggest that the fraction of star accreted through 
+    mergers (\textit{ex situ} component) in central galaxy increases with halo 
+    mass (e.g. \citealt{Pillepich2017b}). 
+    Although the major merger rate is not strong function of progenitor halo mass 
+    (e.g. \citealt{Shankar2015}), minor mergers may still play a more important 
+    role in the assembly of central galaxy of more massive dark matter halos 
+    (e.g. \citealt{Guo2011, Yoon2017}). 
+    As minor merger is more efficient at ``puffing up'' the outskirts of massive 
+    galaxies (e.g. \citealt{Oogi2013, Bedorf2013}), this seems to suggest the 
+    structures of massive ETGs and the well-known stellar mass--effective radius 
+    relation (\mstar{}--$R_{\rm e}$; e.g., \citealt{Shen2003, Guo2009}) should depend 
+    on their ``environment''\footnote{There are multiple definitions of 
+    ``environment'' in the literature.  
+    In this work, we use ``environment'' and halo mass interchangeably.}
     (e.g. \citealt{Shankar2013, Shankar2014}). 
-    Yet, solid evidence of this effect at low redshift is still missing 
-    (e.g. \citealt{Nair2010, HCompany13}; but also see \citealt{Yoon2017}).
-
-    %However, while hints of an environmental dependence in the mass-size relation have 
-    %been spotted at high-$z$ (e.g. \citealt{Papovich2012, Lani2013, Delaye2014}; but 
-    %also see \citealt{Rettura2010}).
-
-	% Song: Actually the Illustris paper suggests that, for massive galaxies, 
-	%       even the inner region is dominated by accreted stars.
-
-    Testing this prediction requires deep imaging of ETGs in order to probe the 
-    accreted component (the stellar halo) which can extend to 100 kpc and 
-    beyond \citep[eg.,][]{hscMassiveI}. 
-    This is observationally challenging as the surface brightness profiles of massive 
-    ETGs decline rapidly with typical values of $\mu > 26.0$ \sb{} in $i$-band at 100 
-    kpc and at $z\sim0.3$. 
+    However, evidence for the environment--dependence of \mstar{}--$R_{\rm e}$
+    at low redshift is still not very solid (\citealt{Nair2010, HCompany13}; 
+    but also see \citealt{Yoon2017}), while the results at higher redshift are 
+    even more confusing (e.g. \citealt{Papovich2012, Lani2013, Delaye2014}; but 
+    also see \citealt{Rettura2010}).
+    }
+
+	\song{
+    Therefore, we think it requires deeper images of these massive galaxies to 
+    better probe their outer stellar mass distributions and test these 
+    predictions. 
+    Unfortunately, this is observationally challenging since the stellar haloes 
+    of massive galaxies can extend to $>100$ kpc (e.g.\citealt{Tal2011, DSouza2014}),
+    and their surface brightness profiles decline rapidly with typical values of 
+    $\mu > 26.0$ \sb{} in $i$-band at 100 kpc and at $z\sim0.3$. 
+    }
     In \citet[][Paper I hereafter]{hscMassiveI}, we showed that deep, 
@@
     In Paper I, we characterized the stellar mass profiles of massive ETGs, and 
-    showed that there is a large intrinsic scatter in the \mden{} stellar halos of
+    showed that there is a large intrinsic scatter in the \mden{} stellar haloes of
     massive galaxies on 100 kpc scales. 
@@
     profiles of massive galaxies correlate with halo mass. 
-    We conclusively show that the sizes and stellar halos of massive central galaxies 
+    We conclusively show that the sizes and stellar haloes of massive central galaxies 
     depend on dark matter halo mass. 
@@
     for massive ETGs.
-
-%    with the help of HSC images of a large sample 
-%    of massive ETGs and the \redm{} cluster catalog (e.g.\ \citealt{Rykoff2014}; 
-%    \citealt{Rozo2015b}; please see \S \ref{sec:data} for details)
 
@@
     \logms$>11.6$, we can spatially resolve galaxies profiles to $\sim 5$ kpc 
-    ($1.0^{\arcsec}$ corresponds to 4.4 and 6.1 kpc at $z=0.3$ and 0.5), and we can 
-    safely ignore structural evolution over our redshift range ($\sim$1.5 Gyr of 
-    time span).
+    ($1.0^{\arcsec}$ corresponds to 4.4 and 6.1 kpc at $z=0.3$ and 0.5). 
+    \song{
+    And massive galaxies should experience little structural evolution and 
+    size growth between $z=0.5$ and 0.3 ($\sim$1.5 Gyr of time span) 
+    based on model prediction (e.g. \citealt{Shankar2015}).
+    }
 
@@
     at the centers of their own dark matter haloes-- so-called ``central'' galaxies. 
-    We use the \redm{} \texttt{v5.10} \citep{Rykoff2014, Rozo2015b} cluster catalog 
+    We use the \redm{} \texttt{v5.10} \citep{Rykoff2014, Rozo2015b} cluster catalogue 
     to help us construct a central galaxy sample.
@@
     at $0.3 < z < 0.5$ (63/68 have \logmtot{}$>11.6$). 
-    This $\lambda$ limit is chosen to mitigate incompleteness in the cluster catalog
+    This $\lambda$ limit is chosen to mitigate incompleteness in the cluster catalogue
     at the high end of our redshift window. 
@@
     central galaxy. 
-    Based on the \mhalo{}-$\lambda$ relation calibrated by \citet{Simet2016}, these 
-    correspond to central galaxies living in halos with \mhalo{}$>10^{14.2}$~\msun{}. 
-    This calibration is consistent with other works (e.g. \citealt{Saro2015, Farahi2016, 
+    \song{
+    \citet{Simet2017} calibrates the \mhalo{}-$\lambda$ relation for the \redm{} 
+    clusters using the SDSS weak lensing data after carefully addressing many 
+    important systematic uncertainties.
+    Based on this calibration, these correspond to central galaxies living in haloes 
+    with \mhalo{}$>10^{14.2}$~\msun{}. 
+    This calibration is consistent with several other independent calibrations 
+    using different methods (e.g. \citealt{Saro2015, Farahi2016, 
     Melchior2016, Murata2017}). 
+    }
     The median richness of the sample is $\lambda \approx 41$ 
@@
     by excluding all galaxies that are in any \redm{} cluster with $\lambda > 20$.
+    \song{
     We convert their $\lambda$ into $M_{\mathrm{200b}}$ using calibration by 
-    \citet{Simet2016}. 
-    Then we estimate the $R_{\mathrm{200b}}$ of each cluster using the method in 
-    \citet{Diemer2015}. 
+    \citet{Simet2017}. 
+    \citet{Diemer2015} systematically investigates the mass density profiles of 
+    dark matter haloes under $\Lambda$CDM cosmology using a suite of dark matter--only
+    simulations.  
+    They provide empirical functions that describe the average density profiles 
+    of dark matters with different halo mass and at different redshifts.  
+    Using the \texttt{Colossus} Python package 
+    (\citealt{Colossus})\footnote{\url{http://www.benediktdiemer.com/code/colossus/}}
+    provided by these authors, we estimate the $R_{\mathrm{200b}}$ of each cluster 
+    given its $M_{\mathrm{200b}}$ and redshift.
+    } 
     We further exclude all galaxies within a cylinder around each cluster, with a radius
@@
 
-%    Initially, we select 3453 galaxies this way with \logmtot{}$> 11.2$ at 
-%    $0.3 < z < 0.5$ \alexie{Why do we care about this?}. 
-%    Among them, 1564 (833) have \logmtot{}$> 11.5$ (11.6).
-
     Satellite contamination should be relative low at the high-\mtot{} end
@@
     In this work, we now investigate the relation between the \mden{} profiles of 
-    massive galaxies, their stellar halos, and dark matter halo mass. 
+    massive galaxies, their stellar haloes, and dark matter halo mass. 
     Here we use \mtot{} as proxy for the ``total'' \mstar{} of massive galaxies and 
@@
     The previous section clearly showed that the \mden{} profiles of massive central 
-    galaxies depend on the masses of their host dark matter halos. 
+    galaxies depend on the masses of their host dark matter haloes. 
     We now ask whether or not this dependence is also manifest when considered in 
@@
     \mtot{}--$R_{\mathrm{50}}$ relations for galaxies in more and less massive
-    dark matter halos. 
+    dark matter haloes. 
     We fit the \logmtot{}-$\log (R_{\mathrm{50}}/\mathrm{kpc})$ relations at 
@@
     $12.5 \le$ \logmh{} $< 15$ haloes. 
-    HC13 use the group catalog by \citet{Yang2007} to estimate halo mass. 
+    HC13 use the group catalogue by \citet{Yang2007} to estimate halo mass. 
     They obtain effective radii from single-\ser{} model fitting to SDSS 
@@
     contribute to this difference, since the most clear environmental differences 
-    are found in the low surface brightness stellar halos that can not be 
+    are found in the low surface brightness stellar haloes that can not be 
     well-modeled with the inner portion of the \mden{} profile using single-\ser{}
@@
 
-    These results are broadly consistent with the ``two-phase'' formation theory for 
-    massive central galaxies.
-    According to this scenario, intense dissipative processes at $z > 2$ are 
+    \song{
+    The two--phase formation scenario can qualitatively explain these results. 
+    Under this picture, intense dissipative processes at $z > 2$ are 
     responsible for the formation of \textit{in situ} stars in massive central 
     galaxies. 
-    In the second phase, star-formation is quenched which limits in-situ star 
-    formation and growth becomes dominated by non-dissipative mergers of satellite
-    galaxies. 
+    After the star-formation was rapidly quenched by certain mechanism, the 
+    assembly of massive galaxies in the second phase is dominated by accretion 
+    of satellite galaxies through (mostly) non-dissipative mergers. 
     Dry minor mergers are efficient at depositing \textit{ex situ} stars in the 
     outskirts of massive galaxies (e.g. \citealt{Oogi2013, Bedorf2013}). 
-    Because central galaxies in massive haloes should experience more mergers 
-    compared to those in less massive halos, we expect the stellar mass profiles 
-    (and sizes) of massive central galaxies to exhibit dependencies on host halo 
-    mass.
+    If minor mergers become more frequent in more massive dark matter halos, 
+    they can result in slightly different stellar mass distributions and larger 
+    effective radius for their massive central galaxies.
+    }
 
@@
     should increase strongly with halo mass. 
-    The major-merger rate only increases slightly with halo mass (mass ratio $>1$:3; 
-    e.g. \citealt{Hirschmann2013}). 
-    The minor-merger rate, however, depends strongly on the dynamical friction time. 
-    If the dynamical friction time is short (e.g. \citealt{Newman2012}), the
-    massive central galaxies with $11.5 <$\logms{}$<12.0$ from more massive haloes 
-    (\logmh{}$>14.0$) can have up to four times more minor mergers (1:100--1:3)
-    compared to the ones in less massive halos at similar stellar mass. 
-    This increase in the minor-merger rate as a function of halo mass leads to a 
+    \song{
+    Although the major-merger rate does not strongly depend on halo mass 
+    (mass ratio $>1$:3; e.g. \citealt{Hirschmann2013, Shankar2015}), minor 
+    merger rate could still increase with halo mass if the dynamical friction time 
+    is short (e.g. \citealt{Newman2012}). 
+    Therefore, massive central galaxies with $11.5 <$\logms{}$<12.0$ from more massive 
+    haloes (\logmh{}$>14.0$) can have up to four times more minor mergers (1:100--1:3)
+    compared to the ones in less massive haloes at similar stellar mass. 
+    Such increase in the minor-merger rate as a function of halo mass leads to a 
     halo-mass dependence in the mass-size relation. 
+    }
     The predictions from \citet{Shankar2014} have been confirmed by \citet{Yoon2017} 
     using the semi-analytic model from \citet{Guo2011}.
-    Our results are broadly consistent with these predictions. 
-    Indeed, we find that the outer profiles of massive galaxies ($r>50$ kpc) are the 
-    regions that display the strongest variations as a function of halo mass.
+
+    \song{
+    Our results are broadly consistent with these predictions and also suggest that 
+    the outer stellar haloes ($r>50$ kpc) of massive galaxies show the strongest 
+    variations with halo mass. 
+    At the same time, we should point out that comparison at low redshift alone 
+    can not rule out some other scenarios.  
+    For instance, \citet{Buchan2016} suggests that central galaxies in more massive 
+    haloes could born with more extended structure. 
+    More careful comparisons at higher redshift should help clarify these situations
+    although recent observations of massive central galaxies of $z>2$ proto--clusters 
+    seem to confirm their compact nature (e.g. \citealt{Kubo2017}).
+    }
 
@@
     models using shallower SDSS images (\citealt{Kelvin2012}), the ones in more 
-    massive dark matter halos actually show more prominent outer stellar halos, 
+    massive dark matter haloes actually show more prominent outer stellar haloes, 
     hence both of their stellar mass and effective radius are underestimated.  
@@
     At the same time, \citet{Cerbrian2014} find that ETGs with \logms{}$>11.5$ are 
-    slightly larger in more massive haloes, and they also shows that this trend is 
+    slightly larger in more massive haloes, and they also show that this trend is 
     reversed at lower \mstar{}. 
@@
             Assuming that \minn{} traces the amount of ``in situ'' stars in massive
-            galaxies, this results is consistent with the picture that more massive 
+            galaxies, this result is consistent with the picture that more massive 
             haloes favor the growth of extended stellar haloes in their central 
@@
 %%%%%%%%%%%%: End of the File %%%%%%%%%%%%
-%% ------------------------------------------------------------------------------------ %%
+%% ------------------------------------------------------------------------------------ %% 

### 2017-11-16 draft/paper2_v6.tex
Major changes

@@
 \def\mhalo{{$M_{\mathrm{200b}}$}}
-\def\logms{{$\log (M_{\star}/M_{\odot})$}}
-\def\logmh{{$\log (M_{\mathrm{200b}}/M_{\odot})$}}
-\def\logmhalo{{$\log (M_{\mathrm{200b}}/M_{\odot})$}}
+\def\logms{{$\log_{10} (M_{\star}/M_{\odot})$}}
+\def\logmh{{$\log_{10} (M_{\mathrm{200b}}/M_{\odot})$}}
+\def\logmhalo{{$\log_{10} (M_{\mathrm{200b}}/M_{\odot})$}}
 
@@
 
-\def\logminn{{$\log (M_{\star,10\mathrm{kpc}}/M_{\odot})$}}
-\def\logmtot{{$\log (M_{\star,100\mathrm{kpc}}/M_{\odot})$}}
-\def\logmout{{$\log (M_{\star,150\mathrm{kpc}}/M_{\odot})$}}
-\def\logmmax{{$\log (M_{\star,\mathrm{Max}}/M_{\odot})$}}
-\def\logmgama{{$\log (M_{\star,\mathrm{GAMA}}/M_{\odot})$}}
-\def\logmcmodel{{$\log (M_{\star,\mathrm{cModel}}/M_{\odot})$}}
+\def\logminn{{$\log_{10} (M_{\star,10\mathrm{kpc}}/M_{\odot})$}}
+\def\logmtot{{$\log_{10} (M_{\star,100\mathrm{kpc}}/M_{\odot})$}}
+\def\logmout{{$\log_{10} (M_{\star,150\mathrm{kpc}}/M_{\odot})$}}
+\def\logmmax{{$\log_{10} (M_{\star,\mathrm{Max}}/M_{\odot})$}}
+\def\logmgama{{$\log_{10} (M_{\star,\mathrm{GAMA}}/M_{\odot})$}}
+\def\logmcmodel{{$\log_{10} (M_{\star,\mathrm{cModel}}/M_{\odot})$}}
 
@@
     \S \ref{sec:discussion}. 
-    Section \S \ref{sec:summary} presents our summary and conclusions.
+    \S \ref{sec:summary} presents our summary and conclusions.
 
@@
           elliptical aperture 
-          ($11.2<\log (M_{\star,10\ \mathrm{kpc}}/M_{\odot})<11.3$). 
+          ($11.2<\log_{10} (M_{\star,10\ \mathrm{kpc}}/M_{\odot})<11.3$). 
           The dash-line circle at the top-left figure indicates $R=$10 kpc.
@@
 
-    % Not sure we need this? Seems too off hand
-    %    (no star formation, lower merger rate \etal~e.g.\ \citealt{Bellstedt2016},
-    %    \citealt{Inagaki2015}; but also see \citealt{Bai2014}).
-
 %% ------------------------------------------------------------------------------------ %% 
@@
     halo mass at fixed stellar mass.    
-    %To ask this question, however, we must first define which stellar mass exactly is 
-    %being fixed in the comparison.
-
     We will show comparisons of \mden{} profiles at both fixed \mtot{} as well as fixed 
@@
     and Fig~\ref{fig:match} for details).
-
-    %    The similar distributions of redshift of the matched samples ensure that the 
-    %    median \mden{} profiles from both samples are affected by seeing and background 
-    %    subtraction to the same extent.
 
@@
 
-    We perform several statistical tests to demonstrate that the differences we see in 
-    the median \mden{} profiles are significant. 
+    \song{
+    We estimate the uncertainties of the median \mden{} profiles using bootstrap 
+    resampling test. 
+    We also perform statistical tests to demonstrate that the differences of \mden{}
+    profiles are more significant than the levels allowed by the intrinsic randomness
+    within the combined \rbcg{} and \nbcg{} sample. 
+    }
     We also conduct a variety of tests that verify the robustness of these results with
@@
 
-        \item For the \mtot{}--matched samples, although there is a clear and robust 
-            difference between the two median \mden{} profiles, the overall difference 
-            is quite subtle, especially in the inner region. 
-            The difference becomes more apparent at $R>50$ kpc scales.
+        \item \song{
+            For the \mtot{}--matched samples, there are some subtle but statistically 
+            significant and robust differences between the two median \mden{} profiles.
+            Due to the logarithmic scale, the difference in the inner region appears 
+            to be very small. 
+            Meanwhile, the difference in \mden{} profile becomes more apparent 
+            at $R>50$ kpc scales.  
+            In Appendix \ref{app:cog} and Figure~\ref{fig:cog}, we compare the same
+            \mtot{}--matched samples using the cumulative \mstar{} profiles 
+            (or `curve of growth') and the fraction of \mtot{} enclosed within 
+            different radius.
+            Both comparisons highlight the differences in median \mden{} profiles 
+            from different angles.
+            }
 
         \item At fixed \mtot{}, central galaxies in more massive dark matter haloes 
-            display shallower \mden{} profiles compared to those living in low mass 
+            display shallower \mden{} profiles compared to those from less massive 
             dark matter haloes (they have a flatter inner \mden{} profiles and 
@@
 
-    The logarithmic scale of \mden{} on the Y-axis is partially responsible for the 
-    subtle differences we see in the fixed \mtot{} comparison.  
-    In Appendix \ref{app:cog} and Figure~\ref{fig:cog}, we present the same 
-    comparison using the curve--of--growth of \mstar{} and the fraction of \mtot{} 
-    enclosed in elliptical apertures with different radius. 
-    Both of the illustrate the same results from slightly different angles. 
-    They also both suggest that, at fixed \mtot{}, the environmental dependence of 
-    \mden{} profiles is indeed quite subtle. 
-    This may explain why previous attempts to detect such dependence using shallower 
-    images often failed. 
+    \song{
+    The subtle differences seen on the left side of Fig \ref{fig:prof_1} suggests
+    that the stellar mass distributions of the most massive central galaxies only
+    weakly depend on their environments. 
+    }
+    This may explain why previous attempts to detect such dependence using 
+    shallower images often failed. 
     More importantly, this result also suggests that halo mass does not play the 
@@
 
-    Meanwhile, the comparison of \mden{} profiles at fixed \minn{}--a reasonable 
-    tracer for the stellar mass in the \textit{in situ} component (right panel of 
+    \song{
+    Meanwhile, the comparison of \mden{} profiles at fixed \minn{}--a potential 
+    tracer of the \mstar{} in the \textit{in situ} component (right panel of 
     Fig~\ref{fig:prof_1}) hints that the inner region ($<10$ kpc) and the outer 
-    stellar halo could be shaped by distinctive physical processes, and may explain 
-    why they depend on halo mass differently.  
-    In simulations, intensive dissipative process helps create 
+    stellar halo are shaped by different physical processes and response to 
+    environment at different levels. 
+    }  
+    In hydrodynamic simulations, intense dissipative processes help create 
     self-similar de~Vaucouleur-like ($n{\sim} 4$) \mden{} profile in the inner part 
@@
     of more massive halo (e.g. \citealt{Pillepich2014}). 
-    The scatter of halo assembly histories at fixed halo mass and the stochastic 
-    nature of the galaxy--galaxy mergers also explain the large \textit{intrinsic} 
-    scatter in the outer \mden{} profiles and the diversity seen on the 
-    \mtot{}--\minn{} plane (Fig~\ref{fig:m100_m10_color}).
+    The intrinsic scatter of halo assembly histories at fixed halo mass and the 
+    stochastic nature of the galaxy--galaxy mergers also explain the large 
+    \textit{intrinsic} scatter in the outer \mden{} profiles and the diversity 
+    seen on the \mtot{}--\minn{} plane (Fig~\ref{fig:m100_m10_color}).
 
@@
     (e.g. \citealt{Hilz2013}, \citealt{Oogi2013})}.
+    \song{
+    As for the inner \mden{} profiles, although the comparison of the \minn{}-matched
+    samples reveals clear differences, we should point out that several physical 
+    processes could alter \minn{} and the \mden{} profiles within 10 kpc during the
+    last 10 Gyrs (e.g., AGN feedback or merger of binary supermassive black holes). 
+    We will further discuss this in \S~\ref{ssec:cen}.
+    }
 
@@
     (e.g. \citealt{Weinmann2009, Nair2010, HCompany13, Cerbrian2014}; 
-    except for recent result by \citealt{Yoon2017}).
-
-    The previous section clearly showed that the \mden{} profiles of massive central 
-    galaxies depend on the masses of their host dark matter haloes. 
-    We now ask whether or not this dependence is also manifest when considered in 
-    terms of the more traditionally studied \mstar{}--$R_{\mathrm{e}}$ relation. 
-    However, when considering the mass-size relation, there is ambiguity and there are
-    multiple approaches to define ``sizes''. 
-    This is especially relevant in the context of massive galaxies with extended 
-    stellar haloes (a reason why we prefer to show \mden{} profiles directly as in 
-    the previous section). 
+    except for the recent result by \citealt{Yoon2017}).
+
+    \song{
+    In the previous section, the differences in the \mden{} profiles already reveals 
+    that the \mtot{}-matched massive galaxies from different environments should have
+    different effective radius (especially see Fig~\ref{fig:cog}). 
+    We now specifically look into the more traditionally studied 
+    \mstar{}--$R_{\mathrm{e}}$ relation.
+    Firstly, we want to point out that `size' is not a well defined parameter for 
+    object like massive galaxies with very extended stellar mass distributions. 
+    In practice, the measurements of `effective radius' or `half--light radius' 
+    not only depends on resolution, depth, and filter of the image, but may also 
+    depend on the adopted model for the light profile.  
+    This makes comparisons of size measurements among different observations 
+    or between observations and models much more uncertain, and is the main reason
+    why we prefer to compare the \mden{} profiles directly.
+    }
     In this section, we still use \mtot{} as proxy of ``total'' \mstar{} and we adopt 
@@
     derived from the $i$-band curve-of-growth) as the ``size''. 
-    This definition of ``effective radius'' is more robust against structural details, 
-    choice of model, and the background subtraction compared to the effective radius 
-    estimated by simple 2-D modeling method (e.g. single-\ser{} model). 
-    Massive galaxies from this sample are large enough that the impact of seeing is 
-    not a concern.
+    Such definition of ``half--light radius'' is more robust against structural 
+    details, choice of model, and the background subtraction compared to the 
+    effective radius measured using 2-D model with oversimplified assumptions 
+    (e.g. single-\ser{} model). 
+    Massive galaxies in this sample are large enough so that the impact of seeing 
+    is not a concern.
 
@@
     dark matter haloes. 
-    We fit the \logmtot{}-$\log (R_{\mathrm{50}}/\mathrm{kpc})$ relations at 
+    We fit the \logmtot{}-$\log_{10} (R_{\mathrm{50}}/\mathrm{kpc})$ relations at 
     $\log(M_{\star,100})>11.6$ using the \texttt{emcee} MCMC sampler 
-    (\citealt{Emcee})\footnote{The initial guesses are based on maximum 
+    (\citealt{Emcee}) \footnote{The initial guesses are based on maximum 
     likelihood estimates, and we assume flat priors for parameters.}.
+    \song{
+    Uncertainties in both \mtot{} and $R_{\mathrm{50}}$ are considered. 
+    For \logmtot{}$>11.6$ galaxies, typical uncertainty for mass is $\sim 0.12$
+    dex.  
+    As for the $R_{\mathrm{50}}$, its uncertainty based on the \mden{} profile
+    is very small due to the high \s2n{} of the profile. 
+    We manually assign 10\% error for $R_{\mathrm{50}}$. 
+    }
 
@@
         \begin{aligned}
-        \log (R_{\mathrm{50}}/\mathrm{kpc}) = & (0.74\pm0.13) \times \log (M_{\star, 100\ \mathrm{kpc}}/M_{\odot}) \\ & -(7.56\pm1.56)
+        \log_{10} (R_{\mathrm{50}}/\mathrm{kpc}) = & (0.74\pm0.13) \times \log_{10} (M_{\star, 100\ \mathrm{kpc}}/M_{\odot}) \\ & -(7.56\pm1.56)
         \end{aligned}
@@
         \begin{aligned}
-        \log (R_{\mathrm{50}}/\mathrm{kpc}) = & (0.68\pm0.06) \times \log (M_{\star, 100\ \mathrm{kpc}}/M_{\odot}) \\ & -(6.88\pm0.75)
+        \log_{10} (R_{\mathrm{50}}/\mathrm{kpc}) = & (0.68\pm0.06) \times \log_{10} (M_{\star, 100\ \mathrm{kpc}}/M_{\odot}) \\ & -(6.88\pm0.75)
         \end{aligned}
@@
     \noindent As shown in the left panel of Fig~\ref{fig:scaling_relation}, 
-    galaxies in more and less massive dark matter haloes lie on 
+    massive central galaxies of more and less massive dark matter haloes lie on 
     \mtot{}--$R_{\mathrm{50}}$ relations that have similar slopes but 
     different normalizations. 
-    The best-fit mass--size relations derived here suggests that, 
-    at $0.3 < z < 0.5$, central galaxies with \logmtot{}$>11.6$ in \logmhalo{}$>14.0$
+    The best--fit mass--size relations derived here suggests that, 
+    at $0.3 < z < 0.5$, central galaxies with \logmtot{}$>11.6$ in \logmhalo{}$>14.2$
     haloes are on average $\sim20$\% larger than the centrals from \logmhalo{}$<14.0$
@@
     $R_{\mathrm{50}}$ derived within these apertures do not change the results.}. 
-    Given the uncertainties of the best-fit parameters, the differences in 
-    mass--size relation is not very significant.  
-    It relates to the relative small sample sizes, uncertainties in \mstar{} and 
-    \mhalo{} estimates, and the limited \mtot{} range used in the fitting.
+    \song{
+    Due to the relative steep slopes for the \mtot{}--$R_{\mathrm{50}}$ relation, 
+    secondary binning (e.g., different halo mass) may induce artificial differences
+    (e.g., \citealt{Sonnenfeld2017}). 
+    We first check the results using the \mtot{}--matched samples and confirm 
+    the above conclusion. 
+    Furthermore, a normalized size parameter ($\gamma$; e.g., \citealt{Newman2012, 
+    HCompany13}) is proposed to control this effect. 
+    We follow the definition of $\gamma$ in \citet{HCompany13}:
+    }
+
+    \begin{equation}
+        \log_{10}(\gamma) = \log_{10} (R_{\mathrm{50}}) + \beta (11 - \log_{10}M_{\star, 100\ \mathrm{kpc}}),
+    \end{equation}
+
+    \song{
+    where $\beta$ is the slope of the mass--size relation.
+    For the \logmtot{}$>11.6$ galaxies, we estimate the average $\gamma$ of both
+    samples using the slopes of their best--fit mtot{}--$R_{\mathrm{50}}$ relations.
+    For the \rbcg{} sample, $<\gamma> = 4.2\pm0.4$; for the \nbcg{} one, 
+    $<\gamma> = 3.8\pm0.3$. 
+    Although the uncertainty is still quite large mainly due to the relative small 
+    sample size, the result also suggests a more significant environmental dependence
+    of $R_{\mathrm{50}}$ at fixed stellar mass compared to the \citet{HCompany13} 
+    one.
+    Given the uncertainties involved, the dependence of $R_{\mathrm{50}}$ of 
+    massive central galaxies at fixed \mtot{} is not very significant and is much 
+    weaker than the predictions of certain models in \citet{Shankar2014}. 
+    But before we rule out these models, we need to mention that the uncertainties 
+    of both mass and size are capable of washing out signals of stronger 
+    environment--dependence as shown in \citet{HCompany13}.
+    Therefore we think the direct comparison of \mden{} profiles or the 
+    \mtot{}--\minn{} relation may be better at tracing the environment dependence
+    of structure in massive galaxies. 
+    }
 
@@
     offset between BC03 and our FSPS model (see Paper~1). 
-    The distributions of galaxies on the 
-    \mtot{}--$R_{\mathrm{50}}$ plane follow the HC13 relation reasonably well 
-    (with slightly shallower slopes), even at \logmtot{}$< 11.6$ where our samples 
-    start to become incomplete in stellar mass. 
+    The distributions of our massive galaxies on the \mtot{}--$R_{\mathrm{50}}$ 
+    plane follow the HC13 relation reasonably well (with slightly shallower slopes), 
+    even at \logmtot{}$< 11.6$ where our samples start to become incomplete in \mtot{}. 
     In contrast to the present study, HC13 finds no environment dependence in the 
     mass--size relation for central galaxies in the range $12.5\le$ \logmh{} $<15.0$. 
-    Both the considerably shallower SDSS images and the single-\ser{} model could 
-    contribute to this difference, since the most clear environmental differences 
-    are found in the low surface brightness stellar haloes that can not be 
-    well-modeled with the inner portion of the \mden{} profile using single-\ser{}
-    profiles.
+    \song{
+    This could relate to the difference in the depth of HSC and SDSS images.
+    The very low surface brightness stellar haloes that show clearly 
+    environment dependence in this work are difficult to see or model on SDSS images.        
+    And, given the much shallower SDSS images used in HC13, it is a little bit 
+    surprised to see that their mass-size relation is not very different with the
+    ones using deeper HSC images. 
+    Besides the systematics in the \m2l{} estimates using different methods, 
+    different photometric methods could be the main reason behinds this 
+    coincidence.
+    For instance, if shallower image leads to systematically underestimated mass, 
+    it could shift the mass--size relation horizontally.  
+    And single-\ser{} is not very accurate model for massive galaxies, hence it 
+    can result in bias of both mass and size measurements (e.g., see 
+    Appendix~\ref{app:gama}). 
+    This further reflects our point that `size' is not straightforward to measure 
+    and compare, also that the mass--size relation may not be the best tool to 
+    investigate environment dependence in massive galaxies. 
+    }
 
     In conclusion, we confirm that the \mtot{}--$R_{\mathrm{50}}$ relation of massive
-    central galaxies at $0.3 < z < 0.5$ depends on halo mass. 
+    central galaxies at $0.3 < z < 0.5$ weakly depends on halo mass. 
     At fixed \mtot{}, massive central galaxies in denser environments (higher \mhalo{}) 
@@
         \begin{aligned}
-        \log (M_{\star, 10\ \mathrm{kpc}}/M_{\odot}) = & (0.48\pm0.06) \times \log (M_{\star, 100\ \mathrm{kpc}}/M_{\odot}) \\ & +(5.72\pm0.75).
+        \log_{10} (M_{\star, 10\ \mathrm{kpc}}/M_{\odot}) = & (0.48\pm0.06) \times \log_{10} (M_{\star, 100\ \mathrm{kpc}}/M_{\odot}) \\ & +(5.72\pm0.75).
         \end{aligned}
@@
         \begin{aligned}
-        \log (M_{\star, 10\ \mathrm{kpc}}/M_{\odot}) = & (0.56\pm0.03) \times \log (M_{\star, 100\ \mathrm{kpc}}/M_{\odot}) \\ & +(4.82\pm0.30).
+        \log_{10} (M_{\star, 10\ \mathrm{kpc}}/M_{\odot}) = & (0.56\pm0.03) \times \log_{10} (M_{\star, 100\ \mathrm{kpc}}/M_{\odot}) \\ & +(4.82\pm0.30).
         \end{aligned}
@@
     within a 120 or a 150 kpc aperture.
-
-%    The \mtot{}--$M_{\star, 5\ \mathrm{kpc}}$ relation actually suggests clearer 
-%    \mhalo{}-dependence at high-\mtot{} end, but the $M_{\star, 5\ \mathrm{kpc}}$ 
-%    are more vulnerable to the impact from seeing than \minn{}.
 
@@
     prominent stellar haloes. 
-    The scientific implication of these results will be discussed in 
-    Section~\ref{sec:discussion}.
-
-    % Although the HSC images can not resolve the central region of these massive 
-    % galaxies, the on average lower \mstar{} within 10 kpc and shallower inner \mden{} 
-    % profile for massive central galaxies living in more massive haloes are robust 
-    % results and could have interesting physical implications.
+    \song{
+    The comparison of \mden{} profiles for \minn{}--matched samples may not directly
+    reflects the environment related processes as other physical mechanisms could 
+    also change the inner \mden{} profiles and their \mtot{} could be quite different. 
+    But the combination of \mtot{} and \minn{} clearly suggests that information of
+    their dark matter haloes or environments is encoded within this simple 2--D plane. 
+    We will discuss more scientific implications of these results in 
+    \S~\ref{sec:discussion}
+    }
 
@@
     our comparisons. 
+    \song{
+    At the same time, we are not certain that similar conclusions apply to the 
+    color or ellipticity profiles within the inner 5--6 kpc due to the smearing effect
+    of the seeing. 
+    Central color gradients may be sensitive to other physical processes and deserves 
+    future investigation using 2-D modelling method and/or image with higher spatial 
+    resolution.
+    }
 
@@
     \mden{} slope and lower fraction of \mtot{} within the inner 10 kpc.
-    It seems that the environmental dependence of stellar mass distributions in 
-    massive central galaxies also affects their central region.
-    This is not caused by the choice of outer aperture to estimate ``total''
-    \mstar{}: assuming that centrals in more massive haloes have more extended 
-    \mden{} profiles, integration out to larger aperture will make the differences 
-    between \rbcg{} and \nbcg{} galaxies on the \mtot{}--\minn{} plane more 
-    significant.
-
-    Several physicals processes may help shape the stellar mass distributions in the 
-    inner region. 
+    \song{
+    This can not be solely explained by the choice of a finite aperture to 
+    estimate ``total'' \mstar{}: assuming that centrals from more massive haloes 
+    have more extended \mden{} profiles, integration out to larger aperture will 
+    make the differences between \rbcg{} and \nbcg{} galaxies on the \mtot{}--\minn{} 
+    plane even more significant.
+    }
+
+    \song{ 
+    Although tempting, it is still too early to conclude that the stellar mass 
+    distributions at the center of massive ETGs also depend on environment. 
+    Many different physicals processes can shape and alter \mden{} profile within 
+    inner 10 kpc, and several of them are not clearly controlled by environment.
+    This is particularly important since progenitors of the massive ETGs in this 
+    work may have higher central \mden{} in the past (e.g., \citealt{Szomoru2012}).
+    } 
     Major merger can redistribute the inner stellar mass distributions, but major
-    merger rate does not strongly depend on halo mass. 
+    merger rate does not strongly depend on halo mass (e.g., \citealt{Shankar2014}). 
     Although recent simulations tend to emphasize the contribution of dry minor 
-    mergers in building up the outer envelope, simulation also shows that minor 
+    mergers in building up the outer envelope, simulations also show that minor 
     mergers can modify the central surface brightness profiles of the remnants
@@
     Depending on the structure and infalling orbit of the satellite, minor merger 
-    can make the inner \mden{} profiles both flattened or steepened.  
+    can make the inner \mden{} profiles either steeper or shallower.  
     Interestingly, these authors find, when satellite is accreted from a highly 
@@
     the central \mden{}.  
-    This is relevant here as many massive BCGs are known to be core--elliptical 
+    This is relevant here as many massive ETGs are known to be core--elliptical 
     galaxies. 
-    Also, strong adiabatic expansion induced by powerful AGN feedback can be another 
-    interesting option (e.g. \citealt{Fan2008}). 
-    This proposed efficient mass--loss can expand the central stellar mass 
-    distribution low central \mden{}.  
+    \song{
+    Meanwhile, strong adiabatic expansion induced by powerful AGN feedback can 
+    be another mechanism (e.g. \citealt{Fan2008}) to modify the inner \mden{}
+    profile.
+    When the induced mass--loss is efficient enough, it can lead to expanded 
+    central stellar mass distribution and can lower the inner \mden{} significantly. 
+    } 
     In addition, at smaller scale, the coalesce of super-massive black hoes (SMBHs)  
@@
     Bonfini2016}) resulting from SMBH mergers.
-    The impacts of these processes, and their dependence on \mhalo{} is an interesting 
-    topic to investigate in the future through comparisons with both observations 
-    at high redshift and numerical simulations.
+
+    \song{
+    The impacts of these processes on the \mden{} profiles and their dependences 
+    on \mhalo{} are important issues that deserve further investigation.  
+    2-D modelling after considering the PSF--convolution and images with higher 
+    spatial resolution will help us connect the central mass distribution with 
+    results of this work. 
+    And comparisons of the \mden{} profiles with massive galaxies in simulation can 
+    help us evaluate the relative importance of these processes.
+    }
 
@@
 
-    At the same time, \citet{Cerbrian2014} find that ETGs with \logms{}$>11.5$ are 
+    At low redshift, \citet{Cerbrian2014} find that ETGs with \logms{}$>11.5$ are 
     slightly larger in more massive haloes, and they also show that this trend is 
     reversed at lower \mstar{}. 
+    \song{
+    \citet{Kuchner2017} uses one massive cluster at $z=0.44$ to show that ETGs in 
+    that cluster has larger size than the ones in the `field'. 
+    }
     \citet{Yoon2017} present a careful study of a large sample of $z\sim0.1$ SDSS ETGs 
@@
     lensing measurements to show that larger galaxies tend to live in more massive 
-    dark matter haloes.
+    dark matter haloes (also see \citealt{Sonnenfeld2017}).
     These results are in broad agreement with those presented here.
+    \song{
+    With the help of weak lensing measurements using HSC images, we will further 
+    explore the connection between the dark matter halo mass and the stellar mass 
+    distributions of their central galaxies. 
+    }
 
     While there appears to be an emerging consensus at low redshift now that the 
-    high--mass end of the mass-size relation does vary with halo mass, the situation at 
-    higher redshift is more complicated. 
+    high--mass end of the mass-size relation does vary with halo mass, the situation 
+    at higher redshift is more complicated. 
     Certain studies find an environment dependence of the mass--size relation for 
     massive quiescent or early-type galaxies that is qualitatively consistent with low 
-    redshift studies (e.g. \citealt{Papovich2012, Lani2013, Strazzullo2013, 
-    Delaye2014}). 
+    redshift studies (e.g. \citealt{Papovich2012, Bassett2013, Lani2013, 
+    Strazzullo2013, Delaye2014}). 
+    \song{
+    It is interesting to see that several of these works report stronger 
+    environment dependence of size at fixed \mstar{} for either ETGs or quiescent 
+    galaxies (30--50\% larger in denser environment).
+    If true, this could indicate that galaxy evolution at high redshift 
+    ($z>2$) is accelerated in denser regions (e.g., proto--clusters; see 
+    \citealt{Wang2016, Shimakawa2018}), while the size evolution of massive 
+    galaxies in richer environment could slow down (e.g., \citealt{Papovich2012, 
+    Andreon2016}.
+    }
     However, there are also observations that suggest otherwise (e.g. 
     \citealt{Rettura2010, Raichoor2012, Kelkar2015, Allen2015}). 
-    These differences might be explained by varying sample sizes, special environments
-    (high-$z$ massive cluster), or the impact of massive star-forming galaxies. 
-    However, these yet un-reconciled differences, also underscore the intrinsic 
-    difficulty of measuring stellar masses and sizes for high-$z$ galaxies 
-    (e.g. \citealt{Price2017}). 
-    Instead of using the mass--size relation to compare the high and the low redshift 
-    universe, a more robust approach would be to directly compare rest-frame surface 
-    brightness or stellar mass density profiles (e.g. \citealt{Szomoru2012, Patel2013,
-    Buitrago2017, Hill2017}).
+    \song{
+    Comparisons with works at high redshift are complicated by many issues. 
+    At high-$z$, these works often rely on small samples or special environments 
+    (rare massive proto-clusters). 
+    Progenitors of massive galaxies in this work may still be star-forming or 
+    late--type galaxies at $z>1$. 
+    And finally, it is just intrinsically more difficult to accurately measure 
+    \mstar{} and size at high redshift (e.g. \citealt{Price2017}).
+    It would be interesting to see whether the current simulations can reproduce 
+    these observed environment dependence and use them to investigate the redshift
+    evolution of such dependence. 
+    Meanwhile, direct comparisons of rest-frame surface brightness or \mden{} 
+    profiles (e.g. \citealt{Szomoru2012, Patel2013, Buitrago2017, Hill2017}) could be 
+    a better approach to compare high- and low-$z$ massive galaxies than the 
+    mass--size relation.
+    }
 
@@
 
-    Given the redshift range for our samples, it is important to evaluate 
-    the impacts from the physical extend of seeing and the imaging depth on the \mden{} 
-    profiles at different redshift. 
-    Under the same seeing, the \mden{} profile of galaxy at higher-$z$ is more 
-    vulnerable to the PSF smearing effect at the center. 
-    It is also harder to reach to the same \mden{} level under the same imaging depth 
-    due to cosmological dimming and background noise.
-
-    In Fig~\ref{fig:avg_prof_z}, we group the \rbcg{} and \nbcg{} galaxies within 
-    $11.6 \le$\logmtot$< 11.9$ into two $z$ bins ($0.3\leq z<0.4$ and $0.4\leq z<0.5$),
-    and compare their \mden{} profiles. 
-    In two redshift bins, the median \mden{} profiles from the same sample follow each 
-    other very well outside 10 kpc, but become visibly different in the central 3-4 kpc,
-    where the effect from seeing kicks in. 
-    Meanwhile, the median \mden{} profiles of \rbcg{} and \nbcg{} in the same $z$ bin 
-    are identical in the central region, which indicates similar average seeing 
-    conditions.       
-    This confirms that \mden{} profile at $> 5$ kpc is safe from the impacts of seeing 
-    and difference in redshift.
-    More importantly, it also suggests that, once the redshift distributions are 
-    carefully matched, the difference of \mden{} profile is likely to be physical 
-    even in the central region.  
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %% 
-\section{Match the \rbcg{} and \nbcg{} samples in \mstar{} and redshift distributions}
-    \label{app:match}
-
 %% ------------------------------------------------------------------------------------ %% 
@@
 \end{figure*}
+
+%% ------------------------------------------------------------------------------------ %% 
+    Given the redshift range for our samples, it is important to evaluate 
+    the impacts from the physical extend of seeing and the imaging depth on the \mden{} 
+    profiles at different redshift. 
+    Under the same seeing, the \mden{} profile of galaxy at higher-$z$ is more 
+    vulnerable to the PSF smearing effect at the center. 
+    It is also harder to reach to the same \mden{} level under the same imaging depth 
+    due to cosmological dimming and background noise.
+
+    In Fig~\ref{fig:avg_prof_z}, we group the \rbcg{} and \nbcg{} galaxies within 
+    $11.6 \le$\logmtot$< 11.9$ into two $z$ bins ($0.3\leq z<0.4$ and $0.4\leq z<0.5$),
+    and compare their \mden{} profiles. 
+    In two redshift bins, the median \mden{} profiles from the same sample follow each 
+    other very well outside 10 kpc, but become visibly different in the central 3-4 kpc,
+    where the effect from seeing kicks in. 
+    Meanwhile, the median \mden{} profiles of \rbcg{} and \nbcg{} in the same $z$ bin 
+    are identical in the central region, which indicates similar average seeing 
+    conditions.       
+    This confirms that \mden{} profile at $> 5$ kpc is safe from the impacts of seeing 
+    and difference in redshift.
+    More importantly, it also suggests that, once the redshift distributions are 
+    carefully matched, the difference of \mden{} profile is likely to be physical 
+    even in the central region.  
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
+\section{Match the \rbcg{} and \nbcg{} samples in \mstar{} and redshift distributions}
+    \label{app:match}
+
 %% ------------------------------------------------------------------------------------ %%
@@
             Given the small sample size, we extend slightly toward lower \mtot{} range 
-            ($11.5 \leq \log (M_{\star,\ 10\mathrm{kpc}}/M_{\odot}) < 11.7$ and 
-             $11.7 \leq \log (M_{\star,\ 10\mathrm{kpc}}/M_{\odot}) < 11.9$). 
+            ($11.5 \leq \log_{10} (M_{\star,\ 10\mathrm{kpc}}/M_{\odot}) < 11.7$ and 
+             $11.7 \leq \log_{10} (M_{\star,\ 10\mathrm{kpc}}/M_{\odot}) < 11.9$). 
             Although the smaller sample leads to larger statistical uncertainties, 
@@
             \mstar{} of these galaxies.
-            As shown in Section~\ref{sec:discussion}, they on average increase
+            As shown in \S~\ref{sec:discussion}, they on average increase
             the \mstar{} by a little bit and affect the \rbcg{} more.
@@
     \centering
-    \includegraphics[width=\columnwidth]{fig/redbcg_prof_m100D}
+    \includegraphics[width=\columnwidth]{fig/redbcg_cog_1}
     \caption{

### 2017-11-16 draft/paper1_v15.tex
Fix figure index in appendix

@@
     (${\sim}100$ deg$^2$) and deep ($>28.5$ \sb{} in $i$-band) to study the stellar 
-    haloes of a sample of $7000$ massive galaxies at $z=0.4$. 
+    haloes of a sample of ${\sim}7000$ massive galaxies at $z{\sim}0.4$. 
     The depth of the HSC data enables us to measure surface mass density profiles 
@@
     significantly underestimated at the high mass end.  
-    Across our sample, the ellipticity of outer light profiles increases substantially 
-    as we probe larger radii.  
+    Across our sample, the ellipticity of outer light profile increases substantially 
+    with radius.  
     }
@@
 %% ------------------------------------------------------------------------------------ %%  
+\section{Basic Statistical Properties of the Sample} 
+	\label{app:basic}
+
+%% ------------------------------------------------------------------------------------ %% 
   \begin{figure}
@@
 
-%% ------------------------------------------------------------------------------------ %%  
-\section{Basic Statistical Properties of the Sample} 
-	\label{app:basic}
-
     Here we show the basic statistics of the massive galaxies used in this work.

### 2017-11-17 draft/paper2.tex
Small change in Section 4.2

@@
 % Version 2; preprint format; Edited by Song Huang
+% Version 3; preprint format; Edited by Alexie Leauthaud
+% Version 4; preprint format; Edited by Song Huang
+% Version 5; preprint format; Edited by Jenny Greene and Song Huang
 
@@
 \def\mhalo{{$M_{\mathrm{200b}}$}}
-\def\logms{{$\log (M_{\star}/M_{\odot})$}}
-\def\logmh{{$\log (M_{\mathrm{200b}}/M_{\odot})$}}
+\def\logms{{$\log_{10} (M_{\star}/M_{\odot})$}}
+\def\logmh{{$\log_{10} (M_{\mathrm{200b}}/M_{\odot})$}}
+\def\logmhalo{{$\log_{10} (M_{\mathrm{200b}}/M_{\odot})$}}
 
@@
 
-    In \citet{hscMassiveI}, we use deep ($>28.5$ \sb{} in $i$-band), high-quality 
-    (0.6\asec seeing) images of ${\sim}3000$ massive (\mstar{}$\geq 11.5$) central 
-    galaxies at $0.3 < z < 0.5$ from the Hyper Suprime-Cam Subaru Strategic Program 
-    to show that more massive central galaxies display more prominent stellar haloes 
-    with shallower outer stellar mass density profile (\mden) and higher ellipticity. 
-    In this work, we investigate the environment dependence of stellar mass 
-    distributions of massive central galaxies using the same dataset.
-    Treating stellar mass within a 100 kpc elliptical aperture (\mtot{}) as proxy of 
-    total stellar mass, we show that at fixed \mtot{}, massive central galaxies in 
-    \mhalo{}$\geq 10^{14}$\msun{} haloes show slightly shallower \mden{} profiles, 
-    larger half-light radius, and lower fraction of stellar mass within inner 10 kpc 
-    (\minn{}) than the centrals of \mhalo{}$< 10^{14}$\msun{} haloes. 
-    At fixed \minn{}--a tracer of the \textit{in situ} stellar mass, central galaxies 
-    from more massive haloes host much more significant outer stellar haloes despite 
-    their inner \mden{} profiles are very similar with the ones in less massive haloes.
-    These results clearly demonstrate that mass--size relation for central galaxies 
-    indeed depends on environment at high-\mtot{} end. 
-    We also show that the \mtot{}--\minn{} relation can reflect this dependence 
-    better and can help diagnose the assembly of massive galaxies and their haloes.
-    These results suggest more massive haloes favor more efficient growth of stellar 
-    haloes in their central galaxies, which is broadly consistent with the two phase 
-    formation scenario of massive galaxies in which their outer envelopes are 
-    accumulated through accretions of small systems.
+    We use ${\sim}100$ deg$^2$ of deep ($>28.5$ \sb{} in $i$-band), high-quality 
+    (median 0.6\asec seeing) imaging data from the Hyper Suprime--Cam (HSC) survey 
+    to investigate the halo mass dependence of the surface mass density profiles 
+    and outer stellar envelopes of massive galaxies. 
+    The $i$-band images from HSC survey reach ${\sim}4$ magnitudes deeper than SDSS 
+    and enable us to directly trace stellar mass distributions to 100 kpc without 
+    requiring stacking.  
+    We conclusively show that at fixed stellar mass, the stellar profiles of massive 
+    galaxies depend on the masses of their dark matter haloes. 
+    On average, massive central galaxies with \logmtot{}$>11.6$ in more massive haloes 
+    at $0.3 < z < 0.5$ have shallower inner stellar mass density profiles 
+    (within ${\sim}10$-$20$ kpc) and more prominent outer envelopes. 
+    These differences translate into a halo mass dependence of the 
+    mass--size relation: central galaxies in haloes with \logmh{}$>14.0$ are 
+    $\sim 20$\% larger in $R_{\mathrm{50}}$ at fixed \mtot{}.  
+    Such dependence is also reflected in the relationship between the stellar mass 
+    within 10 and 100 kpc. 
+    Comparing to the mass--size relation, the \mtot{}--\minn{} relation avoids the 
+    ambiguity in the definition of size, and can be straightforwardly compared with 
+    simulations. 
+    Our results demonstrate that, with deep images from HSC, we can quantify the 
+    connection between halo mass and the outer stellar halo, which may provide new 
+    constraints on the formation and assembly of massive central galaxies.
 
@@
 
-    One of the most intriguing observations of high-redshift galaxies from the last 
-    decade has been the dramatic structural transformation in massive quiescent 
-    galaxies \citep[e.g.][]{Trujillo2006, vanDokkum2008, Cimatti2008, Damjanov2009, 
-    vanderWel2011, Szomoru2012, Patel2013} from $z \approx 2$ to the present. 
+    A key discovery in the last decade has been the dramatic structural transformation 
+    of massive quiescent galaxies \citep[e.g.][]{Trujillo2006, vanDokkum2008, 
+    Cimatti2008, Damjanov2009, vanderWel2011, Szomoru2012, Patel2013} from 
+    $z \approx 2$ to the present day. 
     These observations suggest that the progenitors of $z{\sim} 0$ massive early-type 
-    galaxies (ETGs) need to increase their effective radius ($R_{\rm e}$) by factor 
-    of 2--4 in the last 10 Gyrs (e.g. \citealt{Newman2012, vdWel2014}).
-    They have led to a ``two-phase'' scenario for the formation of massive ETGs 
-    (e.g. \citealt{Oser2010, Oser2012}),
-    in which galaxies form a compact central region through highly dissipative 
-    processes (e.g. gas-rich merger or cold gas-accretion; 
-    \citealt{Hopkins2008, Dekel2009}) and then assemble their extended stellar 
-    haloes via dry mergers 
-    \citep[e.g,][]{Naab2006, Khochfar2006, Oser2010, Oser2012}, which allows for 
-    significant growth at late times. 
-    Meanwhile, progenitor bias, which proposes that larger ETGs were quenched more 
-    recently, could also contribute to the apparent size growth, although its 
-    important is under argument (e.g. \citealt{Newman2012, Carollo2013, 
-    Poggianti2013, Belli2015, Keating2015, Fagioli2016}).
-
-    Several previous works have tested the two-phase formation scenario 
-    observationally using galaxies at low redshift, looking at their surface 
-    brightness of mass density profiles (e.g. \citealt{Huang2013a, Huang2013b, 
+    galaxies (ETGs) need to increase their effective radii ($R_{\rm e}$) by a factor 
+    of 2--4 over a time span of 10 Gyrs (e.g. \citealt{Newman2012, vdWel2014}). 
+    This observational result spurred the development of the ``two-phase'' formation
+    scenario for massive ETGs (e.g. \citealt{Oser2010, Oser2012}),
+    in which galaxies form a compact central region at $z\sim 2$ through highly 
+    dissipative processes (e.g. gas-rich mergers or cold gas-accretion;
+    \citealt{Hopkins2008, Dekel2009}). 
+    They subsequently assemble extended stellar haloes via dry mergers 
+    \citep[e.g,][]{Naab2006, Khochfar2006, Oser2010, Oser2012} which can cause 
+    significant size growth at late times. 
+    An alternative explanation for size growth, progenitor bias, hypothesizes that 
+    larger ETGs were quenched more recently, but this explanation is still under 
+    active debate (e.g. \citealt{Newman2012, Carollo2013, Poggianti2013, Belli2015,
+    Keating2015, Fagioli2016}).
+
+    There have been multiple observational attempts to test the two-phase 
+    formation scenario using galaxies at low redshift, by investigating surface 
+    brightness or mass density profiles (e.g. \citealt{Huang2013a, Huang2013b, 
     Oh2017}, optical color gradients (e.g. \citealt{LaBarbera2010, LaBarbera2012}), 
@@
     Greene2015, Barbosa2016}. 
-    These observations are generally consistent with the two-phase scenario, 
-    but this picture still face many challenges.
-    One of the most outstanding issues is the extent to which, at fixed stellar mass, 
-    the accreted fraction depends on the surrounding dark matter halo mass.
-
-    According to this two-phase formation scenario, the late time growth of massive 
-    ETGs is intrinsically tied to the growth of their host dark matter haloes 
+    \song{
+    These observations are generally consistent with the two-phase formation scenario. 
+    However, it is still not clear whether this promising picture can correctly 
+    predict the connection between the stellar mass distributions in massive galaxies 
+    and their dark matter haloes.
+    }
+
+    \song{
+    Under the $\Lambda$CDM cosmology, The assembly of massive ETGs is intrinsically 
+    tied to the hierarchal growth of their host dark matter haloes 
     (e.g. \citealt{Leauthaud2012, Behroozi2013, Shankar2013}). 
-    Massive ETGs that live at the center of more massive haloes should experience 
-    different assembly and should be subject to higher merger rate compared to 
-    ETGs with similar \mstar{} that live in less massive dark matter haloes. 
-    A natural prediction of this picture is therefore that the structures of 
-    massive ETGs should depend on their ``environment''\footnote{There are 
-    different definitions of ``environment'' in the literature.  
-    In this work, we use ``environment'' and halo mass interchangeably.}.
-    For instance, models based on two-phase scenario predict that the well-know 
-    stellar mass--effective radius relation for ETGs (\mstar{}--$R_{\rm e}$ relation; 
-    e.g., \citealt{Shen2003, Guo2009}) should show environmental dependence: the 
-    $R_{\rm e}$ of massive ETGs in more massive haloes should be larger than those 
-    in less massive haloes at fixed \mstar{} 
+    Hydrodynamic simulations suggest that the fraction of star accreted through 
+    mergers (\textit{ex situ} component) in central galaxy increases with halo 
+    mass (e.g. \citealt{Pillepich2017b}). 
+    Although the major merger rate is not strong function of progenitor halo mass 
+    (e.g. \citealt{Shankar2015}), minor mergers may still play a more important 
+    role in the assembly of central galaxy of more massive dark matter halos 
+    (e.g. \citealt{Guo2011, Yoon2017}). 
+    As minor merger is more efficient at ``puffing up'' the outskirts of massive 
+    galaxies (e.g. \citealt{Oogi2013, Bedorf2013}), this seems to suggest the 
+    structures of massive ETGs and the well-known stellar mass--effective radius 
+    relation (\mstar{}--$R_{\rm e}$; e.g., \citealt{Shen2003, Guo2009}) should depend 
+    on their ``environment''\footnote{There are multiple definitions of 
+    ``environment'' in the literature.  
+    In this work, we use ``environment'' and halo mass interchangeably.}
     (e.g. \citealt{Shankar2013, Shankar2014}). 
-    Yet, solid evidence of this effect at low redshift is still missing 
-    (e.g. \citealt{Nair2010, HCompany13}; but also see \citealt{Yoon2017}).
-
-    %However, while hints of an environmental dependence in the mass-size relation have 
-    %been spotted at high-$z$ (e.g. \citealt{Papovich2012, Lani2013, Delaye2014}; but 
-    %also see \citealt{Rettura2010}).
-
-	% Song: Actually the Illustris paper suggests that, for massive galaxies, 
-	%       even the inner region is dominated by accreted stars.
-
-    To seriously test the environmental dependence of structure in massive ETGs 
-    requires highly sensitive observations extending beyond the inner region of these 
-    galaxies to truly probe the material accreted at late times. 
-    This is very challenging observation as the surface brightness drops rapidly 
-    with radius in massive ETGs.
-
-    In \citet[][Paper I hereafter]{hscMassiveI}, we showed that the deep, 
-    multi-band images from the Subaru Strategic Program (SSP; \citealt{HSC-SSP,
+    However, evidence for the environment--dependence of \mstar{}--$R_{\rm e}$
+    at low redshift is still not very solid (\citealt{Nair2010, HCompany13}; 
+    but also see \citealt{Yoon2017}), while the results at higher redshift are 
+    even more confusing (e.g. \citealt{Papovich2012, Lani2013, Delaye2014}; but 
+    also see \citealt{Rettura2010}).
+    }
+
+	\song{
+    Therefore, we think it requires deeper images of these massive galaxies to 
+    better probe their outer stellar mass distributions and test these 
+    predictions. 
+    Unfortunately, this is observationally challenging since the stellar haloes 
+    of massive galaxies can extend to $>100$ kpc (e.g.\citealt{Tal2011, DSouza2014}),
+    and their surface brightness profiles decline rapidly with typical values of 
+    $\mu > 26.0$ \sb{} in $i$-band at 100 kpc and at $z\sim0.3$. 
+    }
+    In \citet[][Paper I hereafter]{hscMassiveI}, we showed that deep, 
+    multi-band imaging from the Subaru Strategic Program (SSP; \citealt{HSC-SSP,
     HSC-DR1}) using Hyper Suprime-Cam (HSC; \citealt{Miyazaki2012}, 
     Miyazaki in~prep.) allows us to extract robust surface stellar
-    mass density (\mden{}) profiles for {\it individual} massive galaxies 
-    at $0.3 < z < 0.5$ out to 100 kpc. 
-    In Paper I, we exploited this sensitivity to show that the \mden{} profiles 
-    and the shapes of the stellar haloes of massive ETGs has a clear \mstar{} 
-    dependence. 
-    And the fraction of accreted stars residing in the extended envelope increases
-    with the total \mstar{} of the galaxy.
-
-    In this paper, we explore how the extended stellar halo in massive central galaxies
-    depends on dark matter halo mass with the help of HSC images of a large sample 
-    of massive ETGs and the \redm{} cluster catalog (e.g.\ \citealt{Rykoff2014}; 
-    \citealt{Rozo2015b}; please see \S \ref{sec:data} for details)
+    mass density (\mden{}) profiles for {\it individual} galaxies with 
+    \logms{}$>11.4$ at $0.3 < z < 0.5$ and out to 100 kpc. 
+    In Paper I, we characterized the stellar mass profiles of massive ETGs, and 
+    showed that there is a large intrinsic scatter in the \mden{} stellar haloes of
+    massive galaxies on 100 kpc scales. 
+    In this paper, we now investigate whether or not the large scatter in the outer 
+    profiles of massive galaxies correlate with halo mass. 
+    We conclusively show that the sizes and stellar haloes of massive central galaxies 
+    depend on dark matter halo mass. 
+    In other terms, we reveal the halo mass dependence of the mass-size relation 
+    for massive ETGs.
 
     This paper is organized as follows. 
-    \S \ref{sec:data} briefly introduce the sample selection and data reduction 
-    processes.  
+    In \S \ref{sec:data} we briefly introduce the sample selection and the data 
+    reduction processes.  
     Please refer to \citet{hscMassiveI} for more technical details.
@@
     extinction using calibrations from \citet{Schlafly11}. 
-    In this work, we assume $H_0$ = 70~km~s$^{-1}$ Mpc$^{-1}$, ${\Omega}_{\rm m}=0.3$, 
+    We assume $H_0$ = 70~km~s$^{-1}$ Mpc$^{-1}$, ${\Omega}_{\rm m}=0.3$, 
     and ${\Omega}_{\rm \Lambda}=0.7$.
     Stellar mass is denoted \mstar{} and has been derived using a Chabrier Initial Mass 
-    Function (IMF; \citealt{Chabrier2003}).
-
-    Halo mass is defined as $M_{\rm 200b}$ as 
+    Function (IMF; \citealt{Chabrier2003}). Halo mass is defined as 
     $M_{\rm 200b}\equiv M(<r_{\rm 200b})=200\bar{\rho} 
@@
 
-    The sample selection and data reduction processes are described in detail in 
-    Paper I. 
-    Here we include a short summary for completeness.
-
-    This work makes use of the imaging data from the internal data release 
+    We refer the reader to Paper I for an in-depth description of the sample selection 
+    and data reduction processes. 
+    Here, we briefly summarize the main steps.
+
+    We use imaging data from the HSC internal data release 
     \texttt{S15B}, which is very similar to the Public Data Release 1 
     (\citealt{HSC-DR1} and covers ${\sim} 110$ deg$^2$ in all five-band ($grizy$) to 
-    the required depth. 
-    These images are reduced by \texttt{hscPipe 4.0.2}, a derivative of the 
+    the full depth in the Wide field. 
+    The data are reduced by \texttt{hscPipe 4.0.2}, a derivative of the 
     Large Synoptic Survey Telescope (LSST) pipeline (e.g.\ \citealt{Juric2015}; 
@@
     The pixel scale of the reduced image is $0.168$\asec{}.
-    We use the $i$-band image for extracting surface brightness profiles.    
-    The HSC $i$-band image is typically 3--4 mag deeper than the SDSS one in surface 
-    brightness limit and has superb seeing condition (mean FWHM$=0.6$\asec{}).
-
-    In Paper~I, we select large sample of massive galaxies with either spectroscopic 
-    redshift or reliable ``red-sequence'' photometric redshift (\citealt{Rykoff2014}) 
+    We use $i$-band images for extracting surface brightness profiles. 
+    HSC $i$-band images are typically 3--4 mag deeper than SDSS 
+    (Sloan Digital Sky Survey; e.g. \citealt{SDSS-DR7, SDSS-DR8, SDSS-DR12})  
+    and have superb seeing conditions (mean $i$-band seeing has FWHM$=0.6$\asec{}).
+
+    In Paper~I, we select a sample of 25286 bright galaxies with spectroscopic 
+    redshifts or reliable ``red-sequence'' photometric redshifts (\citealt{Rykoff2014}) 
     at $0.3<z<0.5$. 
-    Within this redshift range, we have large enough volume to achieve reasonable 
-    statistics at very high \mstar{} end, can spatially resolve the inner $\sim 5$ 
-    kpc of massive galaxies ($1.0^{\arcsec}$ corresponds to 4.4 and 6.1 kpc at 
-    $z=0.3$ and 0.5), and can safely ignore any structural evolution. 
+    Within this redshift range, we have a large enough volume 
+    ($\sim5\times 10^6$ Mpc$^3$) to sample the galaxy stellar mass function above 
+    \logms$>11.6$, we can spatially resolve galaxies profiles to $\sim 5$ kpc 
+    ($1.0^{\arcsec}$ corresponds to 4.4 and 6.1 kpc at $z=0.3$ and 0.5). 
+    \song{
+    And massive galaxies should experience little structural evolution and 
+    size growth between $z=0.5$ and 0.3 ($\sim$1.5 Gyr of time span) 
+    based on model prediction (e.g. \citealt{Shankar2015}).
+    }
+
     We derive $i$-band surface brightness profiles out to 100 kpc after carefully 
-    masking out any surrounding contaminations and correcting the background 
-    subtraction. 
+    masking out surrounding neighbors and accounting for the subtraction of the 
+    background light. 
     We use the broadband spectral energy distributions (SED) fitting code 
     \texttt{iSEDFit}\footnote{http://www.sos.siena.edu/~jmoustakas/isedfit/} 
-    (\citealt{Moustakas13}) to measure the average \m2l{} and $k$--correction of 
-    these galaxies using five-band forced \cmodel{} magnitudes from \texttt{hscPipe}.
-    \citet{Chabrier2003} IMF, Flexible Stellar Population 
-    Synthesis\footnote{http://scholar.harvard.edu/cconroy/sps-models}
-    (FSPS; \texttt{v2.4}; \citealt{FSPS}, \citealt{Conroy2010}) model, 
-    \citet{Calzetti2000} extinction law, simple delayed-$\tau$ model for star 
-    formation history (SFH) are assumed here. 
-    Using these information, we obtain reliable \mden{} profiles of these 
-    galaxies out to $> 100$ kpc and \mstar{} integrated to different physical 
-    radius using elliptical apertures.
-
-    As explained in Paper I, here we focus on \mstar{} within
+    (\citealt{Moustakas13}) to measure \m2l{} ratios and $k$--corrections using 
+    five-band forced \cmodel{} magnitudes from \texttt{hscPipe}. 
+    We assume a \citet{Chabrier2003} IMF, the Flexible Stellar Population 
+    Synthesis models\footnote{http://scholar.harvard.edu/cconroy/sps-models}
+    (FSPS; \texttt{v2.4}; \citealt{FSPS}, \citealt{Conroy2010}), the 
+    \citet{Calzetti2000} extinction law, and a simple delayed-$\tau$ model for 
+    star formation histories (SFH). 
+    Using HSC data, we can measure the \mden{} profiles of massive galaxies to 
+    $\sim 100$ kpc and we integrate these profiles within elliptical isophotal
+    apertures at different physical radii. 
+    As explained in Paper~I, here we focus on the two following metric masses:
 
@@
 
-        \item a 10 kpc radii (hereafter noted \minn{}) as proxy of the 
-            \textit{in situ} stellar component. 
-            This is motivated by recent observations and simulations 
+        \item stellar mass within 10 kpc (hereafter noted \minn{}) which we use 
+            as a proxy for the stellar mass of the \textit{in situ} stellar 
+            component. 
+            This is motivated both by recent observations and simulations 
             (e.g.~\citealt{vanDokkum2010}, \citealt{RodriguezGomez2016}). 
-
-        \item a 100 kpc radii (hereafter noted \mtot{}), which is shown to recover 
-            more \mstar{} than the ones based on \cmodel{} photometry, as proxy of the 
-            total \mstar{} of the galaxy.
+            The value of 10 kpc that we quote here corresponds to the radius of the 
+            major axis of the isophotal ellipse.
+
+        \item stellar mass within 100 kpc (hereafter noted \mtot{}). 
+            We use \mtot{} as a proxy of the ``total'' stellar mass. 
+            In Paper~I we showed that \mtot{} recovers more light compared to 
+            HSC \cmodel{} photometry with offsets that can be a large as 0.2 dex 
+            in magnitude.
 
@@
 
-   Although these radius are empirically selected, they help recover the 
-   \mstar{}-dependence of the fraction of accreted stars, and reveal the diversity of 
-   stellar envelopes among massive galaxies. 
-   In Figure \ref{fig:m100_m10_color}, we demonstrate such diversity by showing 
-   a random subsample of massive galaxies with very similar \minn{} that have large 
-   range of \mtot{}. 
-   We will use these two apertures\mstar{} to guide the comparisons of massive galaxies 
-   from different environments.
+   We use these two simple metric masses to explore the \mstar{}-dependence of the 
+   fraction of accreted stars, and reveal the diversity of stellar envelopes among 
+   massive galaxies. 
+   In practice, we also have the full profiles for each galaxy and can cast our 
+   results in terms of the full stellar mass profiles. 
+   However, in many cases we find it more useful to display figures using the more 
+   simple \minn{} and \mtot{} quantities. 
+   In Figure \ref{fig:m100_m10_color}, we highlight the diversity of galaxies as a 
+   function of \minn{} and \mtot{}. 
+   Figure \ref{fig:m100_m10_color} shows a random subsample of massive galaxies with 
+   very similar \minn{} that have large range of \mtot{}. 
+   We will use these two apertures masses to guide our comparisons of massive galaxies 
+   as a function of environment.
 
@@
     In this work, we focus on massive galaxies with \mtot{} $>10^{11.6}$~\msun{}. 
-    In Paper~I, we demonstrate that the \mstar{} completeness above this threshold is 
-    good over the full redshift range using comparisons with stellar mass functions 
-    from more complete samples.
-
-    We also wish to focus on massive galaxies that live at the centers of their own 
-    dark matter haloes-- so-called ``central'' galaxies.  
-    They are uniquely important to the study of galaxy-halo connection and are known 
-    to follow stellar mass--halo mass relation (SHMR; e.g. \citealt{Leauthaud2012, 
-    Behroozi2013, Kravtsov2014, Tinker2017}) at high-\mstar{} end with small scatter.
-    We utilize the \redm{} \texttt{v5.10} \citep{Rykoff2014, Rozo2015b} cluster catalog 
-    to identify central galaxies.
-
-    Firstly, we select 68 massive central galaxies from the \redm{} clusters 
-    with $\lambda \geq 30$, $P_{\mathrm{Cen}} \geq 0.7$, and \logmtot{}$>11.5$ 
-    at $0.3 < z < 0.5$ (63/69 have \logmtot{}$>11.6$). 
-    This $\lambda$ limit is chosen to mitigate incompleteness of low richness clusters
-    at the high end of our redshift window, and the $P_{\mathrm{Cen}}$ limit is 
-    selected to exclude low probability candidate of central galaxy. 
-    Based on the \mhalo{}-$\lambda$ relation calibrated by \citet{Simet2016}, these 
-    galaxies are the brightest cluster galaxies (BCGs) of clusters with 
-    \mhalo{}$>10^{14.2}$~\msun{}.
-    This calibration is consistent with other works (e.g. \citealt{Saro2015, Farahi2016, 
+    In Paper~I, we demonstrate that this sample is almost mass complete over our full 
+    redshift range. 
+    In addition to the mass cut above, we also limit our sample to galaxies that live 
+    at the centers of their own dark matter haloes-- so-called ``central'' galaxies. 
+    We use the \redm{} \texttt{v5.10} \citep{Rykoff2014, Rozo2015b} cluster catalogue 
+    to help us construct a central galaxy sample.
+
+    %Central galaxies are important to the study of galaxy-halo connection and follow 
+    %stellar mass--halo mass relation (SHMR; e.g. \citealt{Leauthaud2012, 
+    %Behroozi2013, Kravtsov2014, Tinker2017}) at high-\mstar{}.
+
+    Firstly, we select 68 massive central galaxies from \redm{} clusters 
+    with richness ($\lambda$) $\geq 30$, and the probability of true central galaxy 
+    ($P_{\mathrm{Cen}}$) $\geq 0.7$, and \logmtot{}$>11.5$ 
+    at $0.3 < z < 0.5$ (63/68 have \logmtot{}$>11.6$). 
+    This $\lambda$ limit is chosen to mitigate incompleteness in the cluster catalogue
+    at the high end of our redshift window. 
+    The $P_{\mathrm{Cen}}$ limit is selected to exclude low probability candidate of 
+    central galaxy. 
+    \song{
+    \citet{Simet2017} calibrates the \mhalo{}-$\lambda$ relation for the \redm{} 
+    clusters using the SDSS weak lensing data after carefully addressing many 
+    important systematic uncertainties.
+    Based on this calibration, these correspond to central galaxies living in haloes 
+    with \mhalo{}$>10^{14.2}$~\msun{}. 
+    This calibration is consistent with several other independent calibrations 
+    using different methods (e.g. \citealt{Saro2015, Farahi2016, 
     Melchior2016, Murata2017}). 
+    }
     The median richness of the sample is $\lambda \approx 41$ 
@@
     by excluding all galaxies that are in any \redm{} cluster with $\lambda > 20$.
+    \song{
     We convert their $\lambda$ into $M_{\mathrm{200b}}$ using calibration by 
-    \citet{Simet2016}. 
-    Then we estimate the $R_{\mathrm{200b}}$ of each cluster using the method in 
-    \citet{Diemer2015}. 
-    And we exclude all galaxies within a cylinder around each cluster, with the radius
-    equal to $R_{\mathrm{200b}}$ and length equal to twice the value of the photometric 
-    redshift uncertainty (typically around 0.015 to 0.025). 
-    We generally consider this sample as the central galaxies living in haloes with
-    $M_{\mathrm{200b}} < 10^{14}$~\msun{}, and will refer to this sample as \nbcg{}.
-    Initially, we select 3453 galaxies this way with \logmtot{}$> 11.2$ at 
-    $0.3 < z < 0.5$. 
-    Among them, 1564 (833) have \logmtot{}$> 11.5$ (11.6). 
+    \citet{Simet2017}. 
+    \citet{Diemer2015} systematically investigates the mass density profiles of 
+    dark matter haloes under $\Lambda$CDM cosmology using a suite of dark matter--only
+    simulations.  
+    They provide empirical functions that describe the average density profiles 
+    of dark matters with different halo mass and at different redshifts.  
+    Using the \texttt{Colossus} Python package 
+    (\citealt{Colossus})\footnote{\url{http://www.benediktdiemer.com/code/colossus/}}
+    provided by these authors, we estimate the $R_{\mathrm{200b}}$ of each cluster 
+    given its $M_{\mathrm{200b}}$ and redshift.
+    } 
+    We further exclude all galaxies within a cylinder around each cluster, with a radius
+    equal to $R_{\mathrm{200b}}$ and a length equal to twice the value of the 
+    photometric redshift uncertainty of the cluster (typically around 0.015 to 0.025).
+    This second sample will be dominated by central galaxies living in haloes with
+    $M_{\mathrm{200b}} < 10^{14}$~\msun{}, and will refer to this sample as \nbcg{}. \
+    There are 833 galaxies with \logmtot{}$> 11.6$ in this sample.
+
     Satellite contamination should be relative low at the high-\mtot{} end
@@
     For instance, the model from \citet{Saito2016} predicts a $\sim 7$\% 
-    contamination in the \logmtot{}$>11.6$ sample from satellites from 
-    \logmh$<11.4$ haloes.
+    fraction for galaxies with \logmtot{}$>11.6$ and \logmh$<14.0$ haloes.
 
     In Appendix~\ref{app:basic}, we show the distributions of redshift, \mtot{}, and 
-    \minn{} for \rbcg{} and \nbcg{} samples. 
-    We also compare these two samples on the \mtot{} - rest-frame $g-r$ color plane. 
-    Both of them follow the same ``red-sequence'' without much contamination from the 
-    ``blue clouds''.
-
-    It is worth noting that we failed to extract 1-D profiles for $\sim10$\% of 
-    \rbcg{} and \nbcg{} galaxies due to physical (e.g. on-going major merger) or 
-    nuisance (e.g.\ nearby foreground galaxy or bright star) reasons. 
-    These situations happen more frequently for lower-\mtot{} galaxies, and should not 
-    affect the results of this work.
+    \minn{} for the \rbcg{} and \nbcg{} samples. 
+    We also compare these two samples on the \mtot{}--rest frame $g-r$ color plane. 
+    Both of them follow the same ``red-sequence'' with only a handful of galaxies 
+    displaying bluer colors.
+
+    We note that our analysis fails to extract 1-D profiles for $\sim10$\% of 
+    \rbcg{} and \nbcg{} galaxies due on-going major mergers or projection effects 
+    (e.g.\ nearby foreground galaxy or bright stars). 
+    However, this small failure rate should not affect any of the results in this paper.
 
@@
 
-    As shown in Figure~\ref{fig:m100_m10_color}, massive central galaxies show 
-    intriguing diversity on the \mtot{}-\minn{} plane and in their \mden{} profiles 
-    in the outer haloes.  
-    In Paper~1, we explore the \mstar{}-dependence of the stellar haloes in massive 
-    galaxies, and conclude that the general trends are consistent with the 
-    predictions of two-phase formation scenario. 
-    In the following sections, we will investigate the relation between their 
-    present day halo mass and their stellar haloes using the \mden{} profiles and 
-    scaling relations for massive central galaxies with different $M_{\mathrm{200b}}$ 
-    (\rbcg{} and \nbcg{}).
-
-    We should emphasize again that although a circular aperture is shown on 
-    Fig~\ref{fig:m100_m10_color}, we extract 1-D \mden{} profiles, estimate 
-    \mtot{} and \minn{} using elliptical apertures defined by fluxed-weighted average 
-    isophotal shape. 
-    And, given the narrow \mstar{} and redshift range, we ignore \mstar{} growth 
-    and structural evolution here
-    (no star formation, lower merger rate \etal~e.g.\ \citealt{Bellstedt2016},
-    \citealt{Inagaki2015}; but also see \citealt{Bai2014}).
-
-%% ------------------------------------------------------------------------------------ %% 
-\subsection{Environmental Dependence of the Profiles of Massive Galaxies}
+    As shown in Figure~\ref{fig:m100_m10_color}, massive central galaxies at fixed  
+    \minn{} display a large diversity in their stellar haloes. 
+    In Paper~I, we explored the \mstar{}-dependence of the stellar haloes in massive 
+    galaxies, and concluded that the general trends are consistent with the predictions 
+    of the two-phase formation scenario. 
+    In this work, we now investigate the relation between the \mden{} profiles of 
+    massive galaxies, their stellar haloes, and dark matter halo mass. 
+    Here we use \mtot{} as proxy for the ``total'' \mstar{} of massive galaxies and 
+    we use \minn{} as a rough proxy for the stellar mass of the \textit{in situ} 
+    component.  
+    We remind the reader that although a circular aperture is shown on 
+    Fig~\ref{fig:m100_m10_color}, in practice we extract 1-D \mden{} profiles and 
+    estimate \mtot{} and \minn{} using elliptical apertures following the average 
+    fluxed-weighted isophotal shape.
+
+%% ------------------------------------------------------------------------------------ %% 
+\subsection{Environmental Dependence of the Stellar Mass Density Profiles of Massive 
+            Galaxies}
     \label{ssec:sbp_mtot}
 
-    First, we ask whether the \mden{} profiles of massive central galaxies show 
-    \mhalo{}-dependence within 100 kpc at fixed \mstar{}. 
-    To perform meaning comparison, we build matched samples drawing from \rbcg{} and 
-    \nbcg{} that are carefully matched in \mstar{} and redshift using KDTree algorithm 
-    (please see Appendix~\ref{app:match} and Fig~\ref{fig:match} for details). 
-    The similar distributions of redshift of the matched samples ensure that the 
-    median \mden{} profiles from both samples are affected by seeing and background 
-    subtraction to the same extend. 
-    We address this issue more in Appendix~\ref{app:redshift}.
-
-    We match the \rbcg{} and \nbcg{} samples using both \mtot{} and \minn{} in this
-    work. 
-    As explained in Paper~1, we use \mtot{} as proxy of the ``total'' \mstar{}
-    of massive galaxies while treat \minn{} as a rough indicator of the mass of the 
-    \textit{in situ} component.
+    First, we ask whether the \mden{} profiles of massive central galaxies depend on 
+    halo mass at fixed stellar mass.    
+    We will show comparisons of \mden{} profiles at both fixed \mtot{} as well as fixed 
+    \minn{}. 
+    We also ensure that all comparisons are performed with fixed underlying redshift
+    distribution by matching samples in redshift in addition to stellar mass
+    (please see Appendix~\ref{app:match}, Appendix~\ref{app:redshift}, 
+    and Fig~\ref{fig:match} for details).
 
@@
     Fig~\ref{fig:prof_1} compares the \mden{} profiles of massive central galaxies 
-    in \rbcg{} (orange-red color) and \nbcg{} (grey-black color) at fixed \mtot{} 
-    (left panel) and at fixed \minn{} (right panel). 
-    The top panels show the individual \mden{} profiles along with the median profiles 
-    for both samples. 
-    The bottom panel of Fig~\ref{fig:prof_1} shows the difference between the median 
-    \mden{} profile of \rbcg{} and \nbcg{} samples, with errors computed via bootstrap 
-    resampling.
-    $\Delta = \log(\mu_{\star, \mathrm{cenHighMh}}) - 
-    \log(\mu_{\star, \mathrm{cenLowMh}})$. 
-    This figure presents the main results of this work: \textbf{The \mden{} profiles of 
-    massive central galaxies show \mhalo{}-dependence at both fixed \mtot{} and 
-    \minn{}.}
-    For both \mtot{}-- and \minn{}--matched samples, we see systematic differences
-    between the median \mden{} profile of \rbcg{} galaxies and the one for \nbcg{}
-    galaxies.
-
-    We perform statistical tests to show that the differences we see in the median 
-    \mden{} profiles are significant. 
-    We also conduct a variety of tests that verify the robustness of these results 
-    against choices of \mtot{} bins, $\lambda$ cut, redshift range, and the proxy
-    of ``total'' or \textit{in situ} stellar mass. 
-    Please see Appendix~\ref{app:robust} for more details about these tests.
-
-    There are several important points to be noticed on the left panel of 
-    Fig~\ref{fig:prof_1}.
+    living in less massive dark matter haloes (\logmh$<14.0$) to those living in more 
+    massive dark matter haloes (\logmh$>14.2$) at fixed \mtot{} (left panel) and at 
+    fixed \minn{} (right panel). 
+    At fixed \mtot{}, we compare massive galaxies that have similar ``total'' \mstar{}. 
+    On the right side, we use \minn{} as proxy of the \textit{in situ} \mstar{} to 
+    compare the overall \mstar{} distributions of galaxies living in different 
+    environments that have assembled similar amount of stars at high-$z$.
+    This figure shows the main result of this paper, namely that 
+    \emph{the \mden{} profiles of massive central galaxies show a clear dependence on 
+    dark matter halo mass at both fixed \mtot{} and \minn{}.}
+
+    \song{
+    We estimate the uncertainties of the median \mden{} profiles using bootstrap 
+    resampling test. 
+    We also perform statistical tests to demonstrate that the differences of \mden{}
+    profiles are more significant than the levels allowed by the intrinsic randomness
+    within the combined \rbcg{} and \nbcg{} sample. 
+    }
+    We also conduct a variety of tests that verify the robustness of these results with
+    respect to the choices of \mtot{} bins, $\lambda$ cut, the redshift range, and the 
+    choice of apertures used for the metric masses. 
+    Please see Appendix~\ref{app:robust} for further details.
+
+    The key features in Figure Fig~\ref{fig:prof_1} are the following:
 
@@
 
-        \item First, for the \mtot{} matched sample, although the difference in 
-            median \mden{} profiles is systematical and robust, the overall difference 
-            is very subtle and only becomes clear in the outskirts at $R>50$ kpc, 
-            which explains why such environment dependence is extremely difficult 
-            for previous works to detect using shallower images.
-
-        \item Second, we find that, at fixed \mtot{}, massive central galaxies in 
-            more massive dark mater haloes display shallower \mden{} profiles that the 
-            ones living in less massive haloes. 
-            This can be seen from the more flattened inner \mden{} profile and more 
-            significant outer stellar haloes.
-
-        \item Third, the median \mden{} profiles of \rbcg{} and \nbcg{} cross each 
-            other at ${\sim} 15$-20 kpc, the expected $R_{\mathrm{e}}$ for massive 
-            ETGs around this \mtot{}.
-
-        \item Finally, such systematic difference in \mden{} profiles may become more 
-            significant at higher \mtot{}.
-            We see evidence of this using the $Delta$ profiles of two \mtot{} 
-            bins (see Fig~\ref{fig:prof_2} and discussion in 
-            Appendix~\ref{app:robust})\footnote{Though the lower \mtot{} bin becomes 
-            somewhat incomplete} and when we discuss the relation between \mtot{} and 
-            \minn{} (see Fig~\ref{fig:scaling_relation}). 
-            This trend has potentially interesting implication that is worth more 
-            investigations later.
+        \item \song{
+            For the \mtot{}--matched samples, there are some subtle but statistically 
+            significant and robust differences between the two median \mden{} profiles.
+            Due to the logarithmic scale, the difference in the inner region appears 
+            to be very small. 
+            Meanwhile, the difference in \mden{} profile becomes more apparent 
+            at $R>50$ kpc scales.  
+            In Appendix \ref{app:cog} and Figure~\ref{fig:cog}, we compare the same
+            \mtot{}--matched samples using the cumulative \mstar{} profiles 
+            (or `curve of growth') and the fraction of \mtot{} enclosed within 
+            different radius.
+            Both comparisons highlight the differences in median \mden{} profiles 
+            from different angles.
+            }
+
+        \item At fixed \mtot{}, central galaxies in more massive dark matter haloes 
+            display shallower \mden{} profiles compared to those from less massive 
+            dark matter haloes (they have a flatter inner \mden{} profiles and 
+            more significant outer stellar haloes. 
+            The median \mden{} profiles of the \rbcg{} and \nbcg{} samples cross 
+            each other at ${\sim} 15$-20 kpc, roughly the typical effective radius 
+            ($R_{\mathrm{e}}$) of massive galaxies with \logmtot{}$>11.7$--11.8.
+
+        \item For the \minn{}--matched samples, their median \mden{} profiles 
+            are very similar at $R \leq 10$ kpc. 
+            However, massive galaxies with similar \mstar{} within 10 kpc have quite
+            different \mtot{}, and the massive central galaxies in 
+            more massive haloes host much more prominent outer stellar halo.
+
+        \item Also, for the \minn{}--matched samples, the similar slopes of the 
+            \mden{} profiles within 10 kpc are in sharp contrast with the large
+            \textit{intrinsic} scatter we see in the outer \mden{} profiles.
 
@@
 
-    Generally speaking, such subtle environmental dependence of \mden{} profiles in 
-    the \mtot{}-matched samples suggests that environment does not play a major role 
-    in shaping massive galaxies \textbf{at fixed ``total'' stellar mass}.
-    Therefore it is interesting to ask, for massive galaxies that \textbf{contain 
-    similar \mstar{} in the \textit{in situ} component}, how does environment affect 
-    their subsequent mass assembly?
-    Assuming \minn{} is reasonable tracer of the \textit{in situ} mass, we compare the 
-    \mden{} profiles of \minn{}-matched samples (right panel of Fig~\ref{fig:prof_1}).  
-    Although the median \mden{} profiles are very similar at $R \leq 10$ kpc, the
-    massive central galaxies in more massive haloes host much more prominent outer 
-    stellar halo.
-
-    Meanwhile, the uniform slope of the \mden{} profile within 10 kpc is in sharp 
-    contrast with the large \textit{intrinsic} scatter in the outskirts. 
-    It hints that these two regions are shaped by distinctive processes, and may 
-    explain why they depend on environment at different levels.  
-    In simulations, intensive dissipative process helps create 
+    \song{
+    The subtle differences seen on the left side of Fig \ref{fig:prof_1} suggests
+    that the stellar mass distributions of the most massive central galaxies only
+    weakly depend on their environments. 
+    }
+    This may explain why previous attempts to detect such dependence using 
+    shallower images often failed. 
+    More importantly, this result also suggests that halo mass does not play the 
+    central role in shaping massive central galaxies \textbf{at fixed ``total'' 
+    stellar mass}.
+    Also, the differences in median \mden{} profiles seem to become more prominent 
+    at higher \mtot{}. 
+    This is demonstrated in Appendix~\ref{app:robust} (see Fig~\ref{fig:prof_2}). 
+    Although this trend still needs to be confirmed by larger samples, it 
+    potentially indicates that the assembly of stellar haloes in more massive 
+    central galaxies become more sensitive to their environments.
+
+    \song{
+    Meanwhile, the comparison of \mden{} profiles at fixed \minn{}--a potential 
+    tracer of the \mstar{} in the \textit{in situ} component (right panel of 
+    Fig~\ref{fig:prof_1}) hints that the inner region ($<10$ kpc) and the outer 
+    stellar halo are shaped by different physical processes and response to 
+    environment at different levels. 
+    }  
+    In hydrodynamic simulations, intense dissipative processes help create 
     self-similar de~Vaucouleur-like ($n{\sim} 4$) \mden{} profile in the inner part 
@@
     of more massive halo (e.g. \citealt{Pillepich2014}). 
-    The scatter of halo assembly process at fixed halo mass and the stochastic 
-    nature of the galaxy--galaxy mergers also explain the large \textit{intrinsic} 
-    scatter in the outer \mden{} profiles and the diversity seen on the 
-    \mtot{}--\minn{} plane (Fig~\ref{fig:m100_m10_color}).
+    The intrinsic scatter of halo assembly histories at fixed halo mass and the 
+    stochastic nature of the galaxy--galaxy mergers also explain the large 
+    \textit{intrinsic} scatter in the outer \mden{} profiles and the diversity 
+    seen on the \mtot{}--\minn{} plane (Fig~\ref{fig:m100_m10_color}).
 
@@
     profiles, but can build up the outer halo efficiently
-    (e.g. \citealt{Hilz2013}, \citealt{Oogi2013}).
+    (e.g. \citealt{Hilz2013}, \citealt{Oogi2013})}.
+    \song{
+    As for the inner \mden{} profiles, although the comparison of the \minn{}-matched
+    samples reveals clear differences, we should point out that several physical 
+    processes could alter \minn{} and the \mden{} profiles within 10 kpc during the
+    last 10 Gyrs (e.g., AGN feedback or merger of binary supermassive black holes). 
+    We will further discuss this in \S~\ref{ssec:cen}.
+    }
 
@@
 
-    Although the comparisons of \mden{} profiles can reveal the environment dependence 
-    directly, it is not straightforward to compare with other observations, model 
-    predictions or numerical simulations. 
-    In this section, we compare the \rbcg{} and \nbcg{} galaxies on 
-    1) the well-know \mstar{}--$R_{\mathrm{e}}$ relation; 
-    2) the \mtot{}--\minn{} plane.
+    The above section shows that the \mden{} profiles of massive galaxies show a 
+    dependence on the masses of their host dark matter haloes. 
+    In this section, we now turn our attention to the more commonly studied stellar 
+    mass--size relation (\mstar{}--$R_{\mathrm{e}}$). 
+    In addition, we will also consider halo mass dependence on the 
+    \mtot{}--\minn{} plane.
 
@@
     vdWel2014}) is one of the most important scaling relation for ETGs. 
-    Despite numerous attempts, previous works failed to demonstrate the impact of 
-    environment to the \mstar{}--$R_{\mathrm{e}}$ relation at low-$z$ 
+    Despite numerous attempts, previous studies have failed to detect the 
+    \mhalo{}--dependence of the \mstar{}--$R_{\mathrm{e}}$ relation at low-$z$ 
     (e.g. \citealt{Weinmann2009, Nair2010, HCompany13, Cerbrian2014}; 
-    but see \citealt{Yoon2017}).
-
-    In the last section, we show that the median \mden{} profiles of massive central 
-    galaxies depend on environment. 
-    We therefore expect to also see difference in the \mstar{}--$R_{\mathrm{e}}$ 
-    relations of the \rbcg{} and \nbcg{} samples. 
-    For this purpose, we still use \mtot{} as proxy of ``total'' \mstar{}, and adopt 
-    the radius enclosing 50\% of luminosity within 100 kpc ($R_{\mathrm{50}}$; derived 
-    from the $i$-band curve-of-growth) as ``size''. 
-    This definition of ``effective radius'' is more robust against structural details, 
-    choice of model, and the background subtraction. 
-    Massive galaxies from this sample are large enough so we do not need to worry 
-    about the effects of seeing.
-
-    Left panel of Fig~\ref{fig:scaling_relation} shows the \mtot{}--$R_{\mathrm{50}}$
-    relations for both \rbcg{} (orange--red color) and \nbcg{} (grey--black color). 
-    We fit the \logmtot{}-$\log (R_{\mathrm{50}}/\mathrm{kpc})$ relations at 
-    \logmtot{}$\geq 11.6$ using MCMC method with the help from ensemble sampler 
-    \texttt{emcee} (\citealt{Emcee})\footnote{The initial guesses are based on maximum 
-    likelihood estimates, and we assume reasonable flat priors for parameters.}.
+    except for the recent result by \citealt{Yoon2017}).
+
+    \song{
+    In the previous section, the differences in the \mden{} profiles already reveals 
+    that the \mtot{}-matched massive galaxies from different environments should have
+    different effective radius (especially see Fig~\ref{fig:cog}). 
+    We now specifically look into the more traditionally studied 
+    \mstar{}--$R_{\mathrm{e}}$ relation.
+    Firstly, we want to point out that `size' is not a well defined parameter for 
+    object like massive galaxies with very extended stellar mass distributions. 
+    In practice, the measurements of `effective radius' or `half--light radius' 
+    not only depends on resolution, depth, and filter of the image, but may also 
+    depend on the adopted model for the light profile.  
+    This makes comparisons of size measurements among different observations 
+    or between observations and models much more uncertain, and is the main reason
+    why we prefer to compare the \mden{} profiles directly.
+    }
+    In this section, we still use \mtot{} as proxy of ``total'' \mstar{} and we adopt 
+    the radius enclosing 50\% of stellar mass within 100 kpc ($R_{\mathrm{50}}$; 
+    derived from the $i$-band curve-of-growth) as the ``size''. 
+    Such definition of ``half--light radius'' is more robust against structural 
+    details, choice of model, and the background subtraction compared to the 
+    effective radius measured using 2-D model with oversimplified assumptions 
+    (e.g. single-\ser{} model). 
+    Massive galaxies in this sample are large enough so that the impact of seeing 
+    is not a concern.
+
+    The left panel of Fig~\ref{fig:scaling_relation} shows the 
+    \mtot{}--$R_{\mathrm{50}}$ relations for galaxies in more and less massive
+    dark matter haloes. 
+    We fit the \logmtot{}-$\log_{10} (R_{\mathrm{50}}/\mathrm{kpc})$ relations at 
+    $\log(M_{\star,100})>11.6$ using the \texttt{emcee} MCMC sampler 
+    (\citealt{Emcee}) \footnote{The initial guesses are based on maximum 
+    likelihood estimates, and we assume flat priors for parameters.}.
+    \song{
+    Uncertainties in both \mtot{} and $R_{\mathrm{50}}$ are considered. 
+    For \logmtot{}$>11.6$ galaxies, typical uncertainty for mass is $\sim 0.12$
+    dex.  
+    As for the $R_{\mathrm{50}}$, its uncertainty based on the \mden{} profile
+    is very small due to the high \s2n{} of the profile. 
+    We manually assign 10\% error for $R_{\mathrm{50}}$. 
+    }
+
     The best-fit relation for \rbcg{} is:
@@
         \begin{aligned}
-        \log (R_{\mathrm{50}}/\mathrm{kpc}) = & (0.73\pm0.13) \times \log (M_{\star, 100\ \mathrm{kpc}}/M_{\odot}) \\ & -(7.49\pm1.56)
+        \log_{10} (R_{\mathrm{50}}/\mathrm{kpc}) = & (0.74\pm0.13) \times \log_{10} (M_{\star, 100\ \mathrm{kpc}}/M_{\odot}) \\ & -(7.56\pm1.56)
         \end{aligned}
@@
 
-    \noindent As shown in the left panel of Fig~\ref{fig:scaling_relation}, the slopes 
-    of the \mtot{}--$R_{\mathrm{50}}$ relations are similar, but their normalizations 
-    show difference between the \rbcg{} and \nbcg{} galaxies. 
-    This result is robust against the ranges of \mstar{}, also against the definitions 
-    of  ``total'' \mstar{} and half-light radius\footnote{Using \mstar{} within 120 or 
-    150 kpc, or using the $R_{\mathrm{50}}$ derived within these apertures will not 
-    change the results.}.
+    \noindent As shown in the left panel of Fig~\ref{fig:scaling_relation}, 
+    massive central galaxies of more and less massive dark matter haloes lie on 
+    \mtot{}--$R_{\mathrm{50}}$ relations that have similar slopes but 
+    different normalizations. 
+    The best--fit mass--size relations derived here suggests that, 
+    at $0.3 < z < 0.5$, central galaxies with \logmtot{}$>11.6$ in \logmhalo{}$>14.2$
+    haloes are on average $\sim20$\% larger than the centrals from \logmhalo{}$<14.0$
+    haloes at fixed \mtot{}.
+    This result is robust against the ranges of \mstar{} over which the fit is 
+    performed and against the definitions of  ``total'' \mstar{} and half-light 
+    radius\footnote{Using \mstar{} within 120 or 150 kpc, or using the 
+    $R_{\mathrm{50}}$ derived within these apertures do not change the results.}. 
+    \song{
+    Due to the relative steep slopes for the \mtot{}--$R_{\mathrm{50}}$ relation, 
+    secondary binning (e.g., different halo mass) may induce artificial differences
+    (e.g., \citealt{Sonnenfeld2017}). 
+    We first check the results using the \mtot{}--matched samples and confirm 
+    the above conclusion. 
+    Furthermore, a normalized size parameter ($\gamma$; e.g., \citealt{Newman2012, 
+    HCompany13}) is proposed to control this effect. 
+    We follow the definition of $\gamma$ in \citet{HCompany13}:
+    }
+
+    \begin{equation}
+        \log_{10}(\gamma) = \log_{10} (R_{\mathrm{50}}) + \beta (11 - \log_{10}M_{\star, 100\ \mathrm{kpc}}),
+    \end{equation}
+
+    \song{
+    where $\beta$ is the slope of the mass--size relation.
+    For the \logmtot{}$>11.6$ galaxies, we estimate the average $\gamma$ of both
+    samples using the slopes of their best--fit mtot{}--$R_{\mathrm{50}}$ relations.
+    For the \rbcg{} sample, $<\gamma> = 4.2\pm0.4$; for the \nbcg{} one, 
+    $<\gamma> = 3.8\pm0.3$. 
+    Although the uncertainty is still quite large mainly due to the relative small 
+    sample size, the result also suggests a more significant environmental dependence
+    of $R_{\mathrm{50}}$ at fixed stellar mass compared to the \citet{HCompany13} 
+    one.
+    Given the uncertainties involved, the dependence of $R_{\mathrm{50}}$ of 
+    massive central galaxies at fixed \mtot{} is not very significant and is much 
+    weaker than the predictions of certain models in \citet{Shankar2014}. 
+    But before we rule out these models, we need to mention that the uncertainties 
+    of both mass and size are capable of washing out signals of stronger 
+    environment--dependence as shown in \citet{HCompany13}.
+    Therefore we think the direct comparison of \mden{} profiles or the 
+    \mtot{}--\minn{} relation may be better at tracing the environment dependence
+    of structure in massive galaxies. 
+    }
 
@@
     $12.5 \le$ \logmh{} $< 15$ haloes. 
-    HC13 uses the group catalog by \citet{Yang2007} to estimate \mhalo{}. 
-    They estimate the 2-D $R_{\mathrm{e}}$ using single-\ser{} model fitting to SDSS 
-    images, and derived \mstar{} based on SED fitting using the BC03 (\citealt{BC03}) 
+    HC13 use the group catalogue by \citet{Yang2007} to estimate halo mass. 
+    They obtain effective radii from single-\ser{} model fitting to SDSS 
+    images and \mstar{} based on SED fitting using the BC03 (\citealt{BC03}) 
     synthetic population model. 
-    The \mstar{} estimates are empirically converted from a Kroupa IMF to a Chabrier 
-    IMF by applying a constant -0.05 shift (see \citealt{Bernardi2016}).
-    We add $+0.1$dex to the HSC13 \mstar{} to account for the systematic 
-    difference between their BC03 and our FSPS model (see Appendix~\ref{app:sed}). 
-    The distributions of both \rbcg{} and \nbcg{} galaxies on the 
-    \mtot{}--$R_{\mathrm{50}}$ plane follow the HC13 relation reasonably well 
-    (with slightly shallower slopes), even at \logmtot{}$< 11.6$ where our samples 
-    start to become incomplete. 
+    We convert their \mstar{} estimates from a Kroupa IMF to a Chabrier 
+    IMF by applying a constant -0.05 dex shift (see \citealt{Bernardi2016a}). 
+    We further add $+0.1$dex to the HSC13 stellar masses to account for a systematic 
+    offset between BC03 and our FSPS model (see Paper~1). 
+    The distributions of our massive galaxies on the \mtot{}--$R_{\mathrm{50}}$ 
+    plane follow the HC13 relation reasonably well (with slightly shallower slopes), 
+    even at \logmtot{}$< 11.6$ where our samples start to become incomplete in \mtot{}. 
     In contrast to the present study, HC13 finds no environment dependence in the 
-    mass--size relation for central galaxies from $12.5\le$ \logmh{} $<15.0$ haloes.
-    The \mstar{} and $R_{\mathrm{e}}$ in HC13 are based on much shallower SDSS images
-    that can not constrain the environment-sensitive outer stellar haloes well. 
-    Detailed analysis on this topic is beyond the scope of this work, but we briefly 
-    demonstrate this using the \rbcg{} and \nbcg{} galaxies that overlap with the GAMA
-    survey (please see Appendix~\ref{app:gama} for details). 
-    We matched the two samples using the \mstar{} measured using single-\ser{} 2-D
-    model by the GAMA team (\citealt{Kelvin2012}). 
-    At fixed \mgama{}, the \rbcg{} galaxies display much more significant stellar 
-    halo despite they have very similar inner \mden{} profiles.  
-    This shows again that the deeper HSC images has unique advantage in studying the
-    connection between the assembly of massive galaxies and their dark matter haloes.
+    mass--size relation for central galaxies in the range $12.5\le$ \logmh{} $<15.0$. 
+    \song{
+    This could relate to the difference in the depth of HSC and SDSS images.
+    The very low surface brightness stellar haloes that show clearly 
+    environment dependence in this work are difficult to see or model on SDSS images.        
+    And, given the much shallower SDSS images used in HC13, it is a little bit 
+    surprised to see that their mass-size relation is not very different with the
+    ones using deeper HSC images. 
+    Besides the systematics in the \m2l{} estimates using different methods, 
+    different photometric methods could be the main reason behinds this 
+    coincidence.
+    For instance, if shallower image leads to systematically underestimated mass, 
+    it could shift the mass--size relation horizontally.  
+    And single-\ser{} is not very accurate model for massive galaxies, hence it 
+    can result in bias of both mass and size measurements (e.g., see 
+    Appendix~\ref{app:gama}). 
+    This further reflects our point that `size' is not straightforward to measure 
+    and compare, also that the mass--size relation may not be the best tool to 
+    investigate environment dependence in massive galaxies. 
+    }
 
     In conclusion, we confirm that the \mtot{}--$R_{\mathrm{50}}$ relation of massive
-    central galaxies at $0.3 < z < 0.5$ depends on halo mass. 
-    At fixed \mtot{}, massive central galaxies in denser environment (higher \mhalo{}) 
-    have slightly larger $R_{\mathrm{50}}$ comparing to ones in smaller haloes at fixed 
+    central galaxies at $0.3 < z < 0.5$ weakly depends on halo mass. 
+    At fixed \mtot{}, massive central galaxies in denser environments (higher \mhalo{}) 
+    have larger $R_{\mathrm{50}}$ comparing to ones in smaller haloes at fixed 
     \mtot{}. 
@@
 
-    Now we investigate the relationship between \mstar{} within two elliptical 
-    apertures (\mtot{} v.s. \minn{}) as alternative tool to help us explore the 
-    structure and assembly of massive galaxies.
-    Comparing to the mass--size relation, this relation is not affected by the 
-    ambiguous definition of ``size'', and it is easier to apply it to larger 
-    samples or numerical simulations.
-
-    The right panel of Fig \ref{fig:scaling_relation} compares the \rbcg{} and \nbcg{}
+    Now we investigate the relationship among \mtot{}, \minn{}, and \mhalo{}. 
+    Compared to the mass--size relation, the \mtot{}--\minn{} relation is not plagued 
+    by the ambiguity of galaxy ``size'', and also enables a more straightforward 
+    comparison with numerical simulations.
+
+    The right panel of Fig \ref{fig:scaling_relation} compares \rbcg{} and \nbcg{}
     galaxies on the \mtot{}--\minn{} plane. 
-    We show that these two samples occupy slightly different locations on this plane,
-    and follow different best--fit \mtot{}--\minn{} relations. 
+    We find that there is an offset between the overall distributions of these two
+    samples and they follow distinct best-fit \mtot{}--\minn{} relations. 
     For \rbcg{} galaxies with \logmtot{}$>11.6$ we find:
@@
 
-    These results are robust against the \mtot{} range for fitting, and they will not 
-    be affected if we replace the \minn{} with \mstar{} within 5 or 15 kpc apertures
-    or replace the \mtot{} with \mstar{} within 120 or 150 kpc apertures.  
-    The \mtot{}--$M_{\star, 5\ \mathrm{kpc}}$ relation actually suggests clearer 
-    \mhalo{}-dependence at high-\mtot{} end, but the $M_{\star, 5\ \mathrm{kpc}}$ 
-    are more vulnerable to the impact from seeing than \minn{}.
-
-    We conclude that: 
-    (1) At fixed \mtot{}, central galaxies in more massive haloes tend to have 
-    lower fractions of \mstar{} stored in the inner region; 
-    (2) For massive galaxies with similar \minn{}, the ones in more massive haloes on 
-    average have more prominent outer envelopes. 
-    The scientific implication of this result is briefly discussed in 
-    Section~\ref{sec:discussion}.
-
-    Meanwhile, we find \rbcg{} galaxy tends to have lower \mstar{} within 10--15 kpc 
-    and shallower inner \mden{} profile than the \nbcg{} one at fixed \mtot{}. 
-    Although the HSC can not resolve the central region of these massive galaxies, 
-    such difference could have interesting physical implications. 
-    Observations of compact quiescent galaxies at high-$z$ tend to suggest higher 
-    \mden{} in the central region than their descendants, hence it is necessary to 
-    have certain process to reduce the central \mden{} (e.g. strong adiabatic expansion 
-    induced by powerful AGN feedback; \citealt{Fan2008}) to match the inner \mden{} 
-    profiles of massive central galaxies at low-$z$.
-    Coalesce of super-massive black hoes (SMBHs) at the end of major merger, which is 
-    common in the assembly history of massive galaxies, can also flatten the central 
-    \mden{} profile via efficient scattering effect (e.g. \citealt{Milosavljevi2002}).
-    On the right side of Fig \ref{fig:scaling_relation}, we find a few \rbcg{} galaxies 
-    with very low \minn{} at high \mtot{} end that are apparently not bothered by 
-    problematic photometry or exceptionally bad seeing.  
-    They may be similar to the recently discovered massive BCGs with very large core 
-    (a few kpc; e.g. \citealt{Postman2012, LopezCruz2014}) resulting from SMBH mergers.
-    The impacts of these processes, and their dependence on \mhalo{} is an interesting 
-    topic to investigate in the future.
+    These results are robust against the exact choice for the \mtot{} range over which 
+    the fit is performed. 
+    These results also will not be altered when we replace the \minn{} with the stellar 
+    mass within a 5 or a 15 kpc aperture, or if \mtot{} is replaced with stellar mass 
+    within a 120 or a 150 kpc aperture.
+
+    From Figure \ref{fig:scaling_relation} we can draw the same conclusions as in 
+    the previous section, namely that: 
+    at fixed \mtot{}, central galaxies in more massive haloes tend to have smaller 
+    fraction of stellar mass in their inner regions and higher \mstar{} in their outer
+    stellar haloes. 
+    Meanwhile, at fixed \minn{}--a proxy for the \mstar{} of the ``in situ'' component,
+    central galaxies in more massive haloes tend to be more massive and display more 
+    prominent stellar haloes. 
+    \song{
+    The comparison of \mden{} profiles for \minn{}--matched samples may not directly
+    reflects the environment related processes as other physical mechanisms could 
+    also change the inner \mden{} profiles and their \mtot{} could be quite different. 
+    But the combination of \mtot{} and \minn{} clearly suggests that information of
+    their dark matter haloes or environments is encoded within this simple 2--D plane. 
+    We will discuss more scientific implications of these results in 
+    \S~\ref{sec:discussion}
+    }
+
 %% ------------------------------------------------------------------------------------ %%
@@
 
-    In Paper~1, we show that the ellipticity of outer stellar halo in massive galaxy 
-    steadily increases with \mtot{}, while the rest--frame color gradients do not show 
-    clear \mtot{}-dependence. 
-    Both these results provide us more insights about the assembly of massive galaxies. 
-    Here we quickly look into the environment dependence of ellipticity and 
-    rest--frame color profiles (Figure~\ref{fig:ell_color}).
-
-    We focus on ellipticity and color profiles within 5--60 kpc where we can safely 
-    ignore differences in sky subtraction and seeing across different bands. 
-    We apply Galactic extinction and $k$-correction to both $(g-r)$ and $(g-i)$ color 
-    profiles.
-    We show the average ellipticity, $g-r$, and $g-i$ color profiles for the 
-    \mtot{}-matched (\minn{}-matched) samples of \rbcg{} and \nbcg{} galaxies on the 
-    left (right) side of \ref{fig:ell_color} along with comparisons with previous 
-    works based on stacked SDSS galaxies 
-    (e.g. \citealt{LaBarbera2010, Tal2011, DSouza2014}).
-
-    These results show:
+    In Paper~I, we show that the ellipticity of the outer stellar halo increases with
+    \mtot{}, while in contrast, rest--frame color gradients do not display strong 
+    \mtot{}-dependencies. 
+    In this paper, we take this analysis one step further to investigate whether or 
+    not either of these quantities display a halo mass dependency. 
+    We focus on ellipticity and color profiles within 5--60 kpc where we can ignore
+    differences in sky subtraction and seeing across different filters. 
+    Galactic extinction and $k$-corrections are applied to both $(g-r)$ and $(g-i)$ 
+    color profiles.
+
+    Figure \ref{fig:ell_color} shows the average ellipticity, $g-r$, and $g-i$ color 
+    profiles for galaxies living in more and less massive dark matter haloes both at 
+    fixed \mtot{} and at fixed \minn{}. 
+    We also compared our results with previous studies that are based on stacked SDSS 
+    images (e.g. \citealt{LaBarbera2010, Tal2011, DSouza2014}). 
+    Figure \ref{fig:ell_color} shows that:
 
     \begin{itemize}
-
-        \item Once matched at fixed \mtot{}, the \rbcg{} and \nbcg{} galaxies 
-            show similar average ellipticity profiles. 
-            There is hint that suggests the central galaxies from more massive 
-            haloes become slightly more elongated at $R>50$ kpc than the ones 
-            in less massive haloes with similar \mtot{}. 
-            However, the uncertainties in the current profiles make it not 
-            conclusive.
+        \item Within $R<50$ kpc, we find that the ellipticity profiles of massive 
+            central galaxies do not depend on halo mass at fixed \mtot{}.
 
@@
             average ellipticity than the \nbcg{} ones at $R > 10$ kpc. 
-            The average ellipticities in the inner region are very similar. 
+            On the other hand, the average ellipticity in the inner region are very 
+            similar. 
             This further suggests that the more elongated outer stellar haloes 
-            of massive haloes relate to the accreted stars.
-
-        \item For the rest--frame color gradients, we find shallow and negative 
-            gradients for both \rbcg{} and \nbcg{} galaxies using both colors.
-            We find no significant difference for both the \mtot{}- and 
-            \minn{}--matched samples within 60 kpc.
+            of massive haloes may relate to the accreted stars.
+
+        \item Massive central galaxies in more and less massive dark matter haloes 
+            display similar rest--frame color gradients (at $r<60$ kpc) at fixed 
+            \mtot{} and at fixed  \minn{}.
 
@@
 
-    Besides these conclusions, these comparisons also suggest:
-
-    \begin{itemize}
-
-        \item The smooth ellipticity profile and its shallow gradient supports 
-            the idea of using the flux-weighted average isophotal shape to 
-            extract 1-D profiles of massive galaxies.
-
-        \item The similarity of average rest-frame color profiles between the 
-            \rbcg{} and \nbcg{} samples suggests that \mden{} profiles based on 
-            single average \m2l{} will not bias our comparisons.
-
-    \end{itemize}
+    Besides these conclusions, the fact that we find smooth ellipticity profiles and 
+    shallow gradients favors the idea of using the flux-weighted average isophotal 
+    shape to extract 1-D \mden{} profiles of massive galaxies. 
+    The similarity of average rest-frame color profiles between the \rbcg{} and \nbcg{}
+    samples suggests that \mden{} profiles based on single average \m2l{} will not bias 
+    our comparisons. 
+    \song{
+    At the same time, we are not certain that similar conclusions apply to the 
+    color or ellipticity profiles within the inner 5--6 kpc due to the smearing effect
+    of the seeing. 
+    Central color gradients may be sensitive to other physical processes and deserves 
+    future investigation using 2-D modelling method and/or image with higher spatial 
+    resolution.
+    }
+
 %% ------------------------------------------------------------------------------------ %%
@@
     \label{sec:discussion}
+
+%% ------------------------------------------------------------------------------------ %% 
+\subsection{The Role of Environment in the Two-Phase Formation Scenario}
 
@@
     environment or \mhalo{}. 
-    Here we briefly discuss the physical implications and potential caveats of this 
-    result.
-
-%% ------------------------------------------------------------------------------------ %% 
-\subsection{The Role of Environment in the ``Two--Phase'' Formation of 
-            Massive Central Galaxies}
-
-    Results presented here are broadly consistent with the picture that massive central 
-    galaxies form via a ``two-phase'' picture.
-
-    According to this theory, the cores of massive galaxies were formed at $z{\sim} 2$ 
-    during an intense period of \textit{in situ} star formation. 
-    The outskirts of massive galaxies are then built up via a more gradual second 
-    phase of evolution (the ``ex-situ'' phase) which is dominated by mass growth via 
-    the accretion of satellite systems. 
-    Non-dissipative minor mergers mostly deposit stars on the outskirts of the 
-    centrals and do not have large impact on the central \mden{} profile 
-    (e.g. \citealt{Oogi2013, Bedorf2013}). 
-    Hence, according to this picture, the outer stellar envelopes of massive centrals 
-    should correlate with the masses of their host haloes, in qualitative agreement with
-    our findings.
-
-    State of the art hydrodynamic simulations suggest that massive dark matter haloes 
-    have central galaxies that have outer stellar envelopes with shallow slopes 
-    (e.g. \citealt{Pillepich2014}). 
-    This is consistent with the results in Fig \ref{fig:prof_1}.
-
-    Meanwhile, these simulation also point out that the fraction of accreted stars 
-    increases steeply with total \mstar{} and that the ``ex-situ'' component
-    starts to dominate the \mden{} profiles around $R_{\mathrm{e}}$ for 
-    \logms{}$\geq 11.5$ galaxies. 
-    In this work, we find that the median \mden{} profiles of \rbcg{} and \nbcg{} 
-    samples start to show differences around 15-20 kpc, which is close to 
-    their $R_{\mathrm{e}}$. 
-    Furthermore, the environmental dependence of our median \mden{} profiles 
-    becomes more significant in our highest \mtot{} bin (see Fig \ref{fig:prof_4}). 
-    These results all align with the picture that the \mhalo{}-dependence of the 
-    \mden{} profiles of massive galaxies is driven by the variations in the 
-    ``ex-situ'' component at large radii.
-
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %% 
-\subsection{Scatter in Outer Stellar Enveloppes and ``cD'' Galaxies}
-
-   The thin lines in Figure \ref{fig:prof_1} show the \mden{} density profiles of 
-   individual galaxies. 
-   In general, we find that any given galaxy has a relatively smooth profile, even out 
-   to large radii, however, on a galax-by-galaxy basis there is a large (but continuous) 
-   variation in the amplitude of \mden{} at large scales. 
-   Traditionally, the so-called ``cD'' galaxies are defined to have large stellar 
-   envelopes and are found at the hearts of massive clusters (\citealt{Matthews1964, 
-   Schombert1988}). 
-   However, until present, it has not been clear whether ``cD'' galaxies are a distinct 
-   and special population, or if they are simply the conti of a smoothly varying 
-   population. 
-   Fig \ref{fig:prof_1} shows that with the help of our deep HSC images, we can directly 
-   map out the variations in \mden{} profiles at large scales. 
-   Instead of a bi-model distribution, we find that the outskirts of massive galaxies 
-   display a smooth but continuous variation. 
-   We can hence conclude that ``cD'' galaxies are simply the extremes of a continuous 
-   population but that do not necessarily form a unique a special class of galaxies. 
-   This suggests that it might not be very physically meaningful to separate these 
-   massive galaxies into two arbitrary morphological classes (``cD'' versus non-``cD''). 
-   This conclusion is similar to those of \citep{Zhao2015} who found that a large 
-   fraction of nearby BCGs (34\%) does not fall into the ``cD'' class. 
-   Our finding that massive galaxies display a diverse range of outer stellar 
-   envelope is also supported by HST observations of BCGs at $0.3 < z <0.9$ 
-   by \citealt{Bai2014}. 
+    At fixed \mtot{} or \minn{}, we find that the central galaxies from more massive 
+    haloes on average have larger half--light radius and host more prominent outer 
+    stellar haloes.
+
+    \song{
+    The two--phase formation scenario can qualitatively explain these results. 
+    Under this picture, intense dissipative processes at $z > 2$ are 
+    responsible for the formation of \textit{in situ} stars in massive central 
+    galaxies. 
+    After the star-formation was rapidly quenched by certain mechanism, the 
+    assembly of massive galaxies in the second phase is dominated by accretion 
+    of satellite galaxies through (mostly) non-dissipative mergers. 
+    Dry minor mergers are efficient at depositing \textit{ex situ} stars in the 
+    outskirts of massive galaxies (e.g. \citealt{Oogi2013, Bedorf2013}). 
+    If minor mergers become more frequent in more massive dark matter halos, 
+    they can result in slightly different stellar mass distributions and larger 
+    effective radius for their massive central galaxies.
+    }
+
+    \citet{Shankar2014} studied the environment dependence of galaxy size using 
+    a series of hierarchical semi-analytic models. 
+    They predict that at fixed stellar mass, the median size of central galaxies 
+    should increase strongly with halo mass. 
+    \song{
+    Although the major-merger rate does not strongly depend on halo mass 
+    (mass ratio $>1$:3; e.g. \citealt{Hirschmann2013, Shankar2015}), minor 
+    merger rate could still increase with halo mass if the dynamical friction time 
+    is short (e.g. \citealt{Newman2012}). 
+    Therefore, massive central galaxies with $11.5 <$\logms{}$<12.0$ from more massive 
+    haloes (\logmh{}$>14.0$) can have up to four times more minor mergers (1:100--1:3)
+    compared to the ones in less massive haloes at similar stellar mass. 
+    Such increase in the minor-merger rate as a function of halo mass leads to a 
+    halo-mass dependence in the mass-size relation. 
+    }
+    The predictions from \citet{Shankar2014} have been confirmed by \citet{Yoon2017} 
+    using the semi-analytic model from \citet{Guo2011}.
+
+    \song{
+    Our results are broadly consistent with these predictions and also suggest that 
+    the outer stellar haloes ($r>50$ kpc) of massive galaxies show the strongest 
+    variations with halo mass. 
+    At the same time, we should point out that comparison at low redshift alone 
+    can not rule out some other scenarios.  
+    For instance, \citet{Buchan2016} suggests that central galaxies in more massive 
+    haloes could born with more extended structure. 
+    More careful comparisons at higher redshift should help clarify these situations
+    although recent observations of massive central galaxies of $z>2$ proto--clusters 
+    seem to confirm their compact nature (e.g. \citealt{Kubo2017}).
+    }
+
+%% ------------------------------------------------------------------------------------ %% 
+\subsection{Environmental Dependence of the Inner Regions of Massive Galaxies}
+
+    At the same time, from the comparison of median \mden{} profiles of the 
+    \mtot{}--matched samples and from the \mtot{}--\minn{} plane, our results also 
+    show that the centrals of more massive haloes have slightly shallower inner 
+    \mden{} slope and lower fraction of \mtot{} within the inner 10 kpc.
+    \song{
+    This can not be solely explained by the choice of a finite aperture to 
+    estimate ``total'' \mstar{}: assuming that centrals from more massive haloes 
+    have more extended \mden{} profiles, integration out to larger aperture will 
+    make the differences between \rbcg{} and \nbcg{} galaxies on the \mtot{}--\minn{} 
+    plane even more significant.
+    }
+
+    \song{ 
+    Although tempting, it is still too early to conclude that the stellar mass 
+    distributions at the center of massive ETGs also depend on environment. 
+    Many different physicals processes can shape and alter \mden{} profile within 
+    inner 10 kpc, and several of them are not clearly controlled by environment.
+    This is particularly important since progenitors of the massive ETGs in this 
+    work may have higher central \mden{} in the past (e.g., \citealt{Szomoru2012}).
+    } 
+    Major merger can redistribute the inner stellar mass distributions, but major
+    merger rate does not strongly depend on halo mass (e.g., \citealt{Shankar2014}). 
+    Although recent simulations tend to emphasize the contribution of dry minor 
+    mergers in building up the outer envelope, simulations also show that minor 
+    mergers can modify the central surface brightness profiles of the remnants
+    (e.g. \citealt{BoylanKolchin2007}). 
+    Depending on the structure and infalling orbit of the satellite, minor merger 
+    can make the inner \mden{} profiles either steeper or shallower.  
+    Interestingly, these authors find, when satellite is accreted from a highly 
+    eccentric and energetic orbit to a core--elliptical galaxy, it tends to reduce 
+    the central \mden{}.  
+    This is relevant here as many massive ETGs are known to be core--elliptical 
+    galaxies. 
+    \song{
+    Meanwhile, strong adiabatic expansion induced by powerful AGN feedback can 
+    be another mechanism (e.g. \citealt{Fan2008}) to modify the inner \mden{}
+    profile.
+    When the induced mass--loss is efficient enough, it can lead to expanded 
+    central stellar mass distribution and can lower the inner \mden{} significantly. 
+    } 
+    In addition, at smaller scale, the coalesce of super-massive black hoes (SMBHs)  
+    can flatten the central \mden{} profile via efficient scattering effect 
+    (e.g. \citealt{Milosavljevi2002}).
+    On the right side of Fig \ref{fig:scaling_relation}, we find a few \rbcg{} 
+    galaxies with very low \minn{} at high \mtot{} end that are apparently not bothered 
+    by problematic photometry or exceptionally bad seeing.  
+    They may be similar to the recently discovered massive BCGs with very large 
+    depleted cores (a few kpc; e.g. \citealt{Postman2012, LopezCruz2014, Thomas2016,
+    Bonfini2016}) resulting from SMBH mergers.
+
+    \song{
+    The impacts of these processes on the \mden{} profiles and their dependences 
+    on \mhalo{} are important issues that deserve further investigation.  
+    2-D modelling after considering the PSF--convolution and images with higher 
+    spatial resolution will help us connect the central mass distribution with 
+    results of this work. 
+    And comparisons of the \mden{} profiles with massive galaxies in simulation can 
+    help us evaluate the relative importance of these processes.
+    }
+
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
+\subsection{Comparison with Previous Work}
+
+    In this work, we demonstrate that the stellar mass distributions and mass--size 
+    relation of massive central galaxies depend on their host dark matter halo masses. 
+    At $0.3 < z < 0.5$, \logmtot{}$>11.6$ galaxies from \logmhalo{}$>14.0$ haloes 
+    are on average $\sim20$\% larger than the ones from smaller haloes at fixed 
+    \mtot{}.
+
+    Many previous works that focused on the mass-size relation found this relation 
+    is independent of halo mass or environment at $z\sim 0.0$ 
+    (e.g. \citealt{Nair2010, Maltby2010, Cappellari2013, HCompany13}). 
+    As mentioned earlier, both the shallower imaging depth and the oversimple model 
+    (e.g. single-\ser{} or de~Vaucouleurs model) used in the fitting can both 
+    contribute to this difference.
+    In Appendix~\ref{app:gama}, we use the \rbcg{} and \nbcg{} galaxies that overlap 
+    with the GAMA survey to briefly demonstrate this point. 
+    We show that, for galaxies with similar \mstar{} derived from single-\ser{} 
+    models using shallower SDSS images (\citealt{Kelvin2012}), the ones in more 
+    massive dark matter haloes actually show more prominent outer stellar haloes, 
+    hence both of their stellar mass and effective radius are underestimated.  
+    This shows again that the deeper HSC images has unique advantage in studying 
+    the connection between the assembly of massive galaxies and their dark matter 
+    haloes.
+
+    At low redshift, \citet{Cerbrian2014} find that ETGs with \logms{}$>11.5$ are 
+    slightly larger in more massive haloes, and they also show that this trend is 
+    reversed at lower \mstar{}. 
+    \song{
+    \citet{Kuchner2017} uses one massive cluster at $z=0.44$ to show that ETGs in 
+    that cluster has larger size than the ones in the `field'. 
+    }
+    \citet{Yoon2017} present a careful study of a large sample of $z\sim0.1$ SDSS ETGs 
+    using a non-parametric method and recover a clear environment dependence of 
+    mass-size relation at \logms{}$>11.2$. 
+    They conclude that, at the same \mstar{}, massive ETGs from dense environment 
+    are 20--40\% larger compared to those in underdense environment.
+    Recently, \citet{Charlton2017} uses single-\ser{} model for galaxies at 
+    $0.2 < z < 0.8$ in the CFHTLenS (\citealt{Heymans2012}) and their galaxy--galaxy 
+    lensing measurements to show that larger galaxies tend to live in more massive 
+    dark matter haloes (also see \citealt{Sonnenfeld2017}).
+    These results are in broad agreement with those presented here.
+    \song{
+    With the help of weak lensing measurements using HSC images, we will further 
+    explore the connection between the dark matter halo mass and the stellar mass 
+    distributions of their central galaxies. 
+    }
+
+    While there appears to be an emerging consensus at low redshift now that the 
+    high--mass end of the mass-size relation does vary with halo mass, the situation 
+    at higher redshift is more complicated. 
+    Certain studies find an environment dependence of the mass--size relation for 
+    massive quiescent or early-type galaxies that is qualitatively consistent with low 
+    redshift studies (e.g. \citealt{Papovich2012, Bassett2013, Lani2013, 
+    Strazzullo2013, Delaye2014}). 
+    \song{
+    It is interesting to see that several of these works report stronger 
+    environment dependence of size at fixed \mstar{} for either ETGs or quiescent 
+    galaxies (30--50\% larger in denser environment).
+    As shown in \citet{HCompany13} using Monte Carlo test (see their \S~4.2), 
+    when the uncertainties of mass and size are considered, the size difference at 
+    fixed stellar mass could be even more significant between extremely different
+    environments.
+    If true, it indicates that denser regions at high redshift ($z>2$) could accelerate 
+    galaxy evolution (e.g., proto--clusters; see \citealt{Wang2016, Shimakawa2018}) and 
+    the size evolution of massive galaxies in richer environment gradually slows down
+    toward lower redshift (e.g., \citealt{Papovich2012, Andreon2016}.
+    }
+    However, there are also observations that suggest otherwise (e.g. 
+    \citealt{Rettura2010, Raichoor2012, Kelkar2015, Allen2015}). 
+    \song{
+    Comparisons with works at high redshift are complicated by many issues. 
+    At high-$z$, these works often rely on small samples or special environments 
+    (rare massive proto-clusters). 
+    Progenitors of massive galaxies in this work may still be star-forming or 
+    late--type galaxies at $z>1$. 
+    And finally, it is just intrinsically more difficult to accurately measure 
+    \mstar{} and size at high redshift (e.g. \citealt{Price2017}).
+    It would be interesting to see whether the current simulations can reproduce 
+    these observed environment dependence and use them to investigate the redshift
+    evolution of such dependence. 
+    Meanwhile, direct comparisons of rest-frame surface brightness or \mden{} 
+    profiles (e.g. \citealt{Szomoru2012, Patel2013, Buitrago2017, Hill2017}) could be 
+    a better approach to compare high- and low-$z$ massive galaxies than the 
+    mass--size relation.
+    }
+
+%% ------------------------------------------------------------------------------------ %% 
+\subsection{Towards Consistent Size Definitions}
+
+    Until recently, semi-analytic models and hydrodynamic simulations still have 
+    difficulty reproducing the mass--size relation of massive galaxies. 
+    Galaxy sizes are sensitive to many different physical processes (star-formation, 
+    feedback, mergers) and matching the galaxy stellar-mass function does not 
+    automatically guarantee a match to the mass-size relation. 
+    Furthermore, while some efforts have been made to use consistent size definitions 
+    (\citealt{McCarthy2017}), more often than not, comparisons of the mass-size relation 
+    do not use consistent size definitions, or only perform crude size conversions 
+    (e.g. 3--D radius in simulation versus 2--D projected radius in observation; 
+    \citealt{Genel2017}). 
+    Observers often quote ``sizes'' corresponding to the half--light radius along the 
+    major axis using 2--D projected images. 
+    Simulations on the other hand, often employ sizes that correspond to the 3--D 
+    aperture half--mass radius (e.g. \citealt{Price2017}).
+
+    As emphasized earlier, definitions of galaxy ``size'' in observations are also not 
+    always consistent. 
+    Measurement of ``size'' often shows dependence on image quality (e.g. seeing, 
+    imaging depth), filter, and the adopted method. 
+    Although the elliptical single--\ser{} model is widely adopted in measuring the 
+    size of galaxies of different types and at different redshifts, it sometimes leads
+    to biased results as it is no longer appropriate model for certain types of galaxy. 
+    Size derived from 1-D curve--of--growth is more model independent and has been 
+    shown to be useful in revealing environmental dependence of the mass--size relation 
+    (e.g. \citealt{Yoon2017} and this work), but it does not take the PSF convolution 
+    effect into account and depends on imaging depth and background subtraction.
+
+    In this paper, we quote stellar masses measured within elliptical apertures of 
+    fixed physical size. 
+    We argue that this approach will allow for a more straightforward comparison 
+    between observations and theoretical predictions. 
+    In follow-up work, we will present comparisons between our observations and 
+    predictions from hydrodynamic simulations using the using the \mtot{}--\minn{} 
+    plane instead of the mass--size relation.
+
 %% ------------------------------------------------------------------------------------ %%
@@
 %% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %% 
-\section{A. Basic Statistical Properties of the Sample} 
-	\label{app:basic}
 
@@
 %% ------------------------------------------------------------------------------------ %% 
-\section{B. Comparisons of \mden{} profiles in different redshift bins}
-    \label{app:redshift}
-
-    Given the redshift range for our samples, it is important to evaluate 
-    the impacts from the physical extend of seeing and the imaging depth on the \mden{} 
-    profiles at different redshift. 
-    Under the same seeing, the \mden{} profile of galaxy at higher-$z$ is more 
-    vulnerable to the PSF smearing effect at the center. 
-    It is also harder to reach to the same \mden{} level under the same imaging depth 
-    due to cosmological dimming and background noise.
-
-    In Fig~\ref{fig:avg_prof_z}, we group the \rbcg{} and \nbcg{} galaxies within 
-    $11.6 \le$\logmtot$< 11.9$ into two $z$ bins ($0.3\leq z<0.4$ and $0.4\leq z<0.5$),
-    and compare their \mden{} profiles. 
-    In two redshift bins, the median \mden{} profiles from the same sample follow each 
-    other very well outside 10 kpc, but become visibly different in the central 3-4 kpc,
-    where the effect from seeing kicks in. 
-    Meanwhile, the median \mden{} profiles of \rbcg{} and \nbcg{} in the same $z$ bin 
-    are identical in the central region, which indicates similar average seeing 
-    conditions.       
-    This confirms that \mden{} profile at $> 5$ kpc is safe from the impacts of seeing 
-    and difference in redshift.
-    More importantly, it also suggests that, once the redshift distributions are 
-    carefully matched, the difference of \mden{} profile is likely to be physical 
-    even in the central region.  
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %% 
 \begin{figure*}
     \centering 
-    \includegraphics[width=16cm]{fig/redbcg_match}
+    \includegraphics[width=15.0cm]{fig/redbcg_match}
     \caption{
@@
 \end{figure*}
-%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
+    Given the redshift range for our samples, it is important to evaluate 
+    the impacts from the physical extend of seeing and the imaging depth on the \mden{} 
+    profiles at different redshift. 
+    Under the same seeing, the \mden{} profile of galaxy at higher-$z$ is more 
+    vulnerable to the PSF smearing effect at the center. 
+    It is also harder to reach to the same \mden{} level under the same imaging depth 
+    due to cosmological dimming and background noise.
+
+    In Fig~\ref{fig:avg_prof_z}, we group the \rbcg{} and \nbcg{} galaxies within 
+    $11.6 \le$\logmtot$< 11.9$ into two $z$ bins ($0.3\leq z<0.4$ and $0.4\leq z<0.5$),
+    and compare their \mden{} profiles. 
+    In two redshift bins, the median \mden{} profiles from the same sample follow each 
+    other very well outside 10 kpc, but become visibly different in the central 3-4 kpc,
+    where the effect from seeing kicks in. 
+    Meanwhile, the median \mden{} profiles of \rbcg{} and \nbcg{} in the same $z$ bin 
+    are identical in the central region, which indicates similar average seeing 
+    conditions.       
+    This confirms that \mden{} profile at $> 5$ kpc is safe from the impacts of seeing 
+    and difference in redshift.
+    More importantly, it also suggests that, once the redshift distributions are 
+    carefully matched, the difference of \mden{} profile is likely to be physical 
+    even in the central region.  
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
+\section{Match the \rbcg{} and \nbcg{} samples in \mstar{} and redshift distributions}
+    \label{app:match}
+
+%% ------------------------------------------------------------------------------------ %%
+
+    As explained earlier, it is important to make sure the two samples have similar 
+    distributions in both \mstar{} and redshift before comparing their median \mden{} 
+    profiles.  
+    Here we briefly describe the procedure used in this work. 
+    Since the \rbcg{} sample is smaller in size, we always match the \nbcg{} sample to 
+    it by searching for the $N$-nearest neighbours on the $M_{\star}$-redshift plane 
+    using the KDTree algorithm in the \texttt{scikit-learn} Python library 
+    (\citealt{scikit-learn}), and evaluate the quality of the match using the 
+    distributions of both parameters (as shown in Fig~\ref{fig:match}).
+
+    As we only keep the unique \nbcg{} galaxies in the matched sample, we manually 
+    adjust the value of $N$ to achieve the best match. 
+    When the redshift distribution of the \rbcg{} sample becomes bi-model, we also try 
+    to split the sample into two redshift bins and match them separately. 
+    Typically $N$ is between 3 to 8.
+    In Fig~\ref{fig:match}, we demonstrate this procedure using the results for 
+    the \mtot{}-matched (Left) and the \minn{}-matched samples in Fig~\ref{fig:prof_1}
+    (Right), and the two samples are well matched in the distributions of \mtot{}
+    (or \minn{}) and redshift.  
+    For all the comparisons of \mden{} profiles in this work, we match the samples 
+    in the same way, and make sure the match has the same quality. 
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
+\section{Robustness of the \mden{} Differences} 
+	\label{app:robust}
 
@@
 
+    In Fig~\ref{fig:prof_1}, we compare the \mden{} profiles of \mtot{}- and 
+    \minn{}-matched samples of \rbcg{} and \nbcg{} galaxies, and here we test the 
+    robustness of the results using a few extra tests that are illustrated in
+    Fig~\ref{fig:prof_2}, Fig~\ref{fig:prof_3}, and Fig~\ref{fig:prof_4}, and 
+    are briefly described here:
+
+    \begin{enumerate}
+
+        \item In Fig~\ref{fig:prof_2}, we group the samples into two \mtot{} bins. 
+            Given the small sample size, we extend slightly toward lower \mtot{} range 
+            ($11.5 \leq \log_{10} (M_{\star,\ 10\mathrm{kpc}}/M_{\odot}) < 11.7$ and 
+             $11.7 \leq \log_{10} (M_{\star,\ 10\mathrm{kpc}}/M_{\odot}) < 11.9$). 
+            Although the smaller sample leads to larger statistical uncertainties, 
+            we can still see similar structural differences in both \mtot{} bins, 
+            and the difference becomes more significant in the higher \mtot{} bin.  
+            For the lower \mtot{} bin, the difference in the inner region becomes 
+            quite uncertain, while the difference in the outskirt is still visible. 
+            This potentially suggests that the environmental dependence of structure 
+            also varies with \mstar{}, an important implication deserves more 
+            investigations in the future.
+
+        \item On the left panel of Fig~\ref{fig:prof_3}, we match the \rbcg{} and 
+            \nbcg{} samples in a lower redshift bins ($0.30 < z < 0.42$).
+            Despite the larger uncertainties due to smaller samples, we find the 
+            results are the same.
+
+        \item On the middle panel of Fig~\ref{fig:prof_3}, we includes \rbcg{} 
+            galaxies in poorer clusters ($20 < \lambda < 30$), which should result 
+            in overlapped \mhalo{} distributions with the \nbcg{} samples 
+            considering the typical uncertainty of $\lambda$.
+            This makes the difference in the inner region slightly less significant, 
+            but the overall results are the same.
+
+        \item On the right panel of Fig~\ref{fig:prof_3}, in stead of using \mtot{}, 
+            we use the \mmax{}--the maximum \mstar{} by integrating the \mden{} 
+            profiles to the largest radius allowed.  
+            The \mmax{} values are less reliable than \mtot{} due to the 
+            uncertainty of background subtraction and contamination from nearby 
+            bright objects, but they can serve as different estimates of the ``total''
+            \mstar{} of these galaxies.
+            As shown in \S~\ref{sec:discussion}, they on average increase
+            the \mstar{} by a little bit and affect the \rbcg{} more.
+            The differences in the \mden{} profiles still remain very similar.
+
+    \end{enumerate}
+
+    We also test the robustness of the \mtot{}-matched results using the samples with 
+    only spectroscopic redshift, the samples in the three GAMA fields, and the \rbcg{} 
+    samples without the ones in very massive haloes ($\lambda > 40$).  
+    Limited by space, we do not show these results here, but they all verify the 
+    robustness of the results.
+
+    For the results from the \minn{}-matched samples:
+
+    \begin{enumerate}
+
+        \item
+            We match the two samples using both \minn{} and the \mstar{} within 15 kpc 
+            at the same time.  
+            This makes the two median \mden{} profiles very similar inside 10-15 
+            kpc, while the result in the outskirt remains the same (left panel of 
+            Fig~\ref{fig:prof_4}).
+            Use \mstar{} within 5 or 20 kpc leads to the same conclusion.
+
+        \item 
+            To make sure the two samples are comparable in their overall assembly history,
+            we also try to only include the very massive galaxies (\logmtot{}$>11.5$)
+            in both samples. 
+            This excludes the \nbcg{} galaxies that are much less massive and 
+            more ``compact'' in structure. 
+            Yet, the results regarding the structural differences remain the same.
+
+    \end{enumerate}
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
+\section{Stellar Mass Curve-of-Growth for Massive Central Galaxies} 
+	\label{app:cog}
+
+	In \S \ref{ssec:sbp_mtot} and Figure \ref{fig:prof_1}, we show the comparisons 
+	of \mden{} profiles for massive central galaxies from the \rbcg{} and \nbcg{} 
+	samples. 
+	Although the differences in their median \mden{} profiles we revealed are robust 
+	and systematic, they appear to be very subtle, especially in the inner region. 
+	This is partly due to the logarithmic scale on the Y--axis for \mden{} profiles.
+
+	In Figure \ref{fig:cog}, we compare the same two samples after converting the 
+	\mden{} profiles into:
+
+	\begin{enumerate}
+
+	    \item ``Curve--of--growth'' of stellar mass--the cumulative \logms{} profiles
+	        (upper panel).
+
+	    \item Fraction of \mtot{} within different radius (lower panel).
+
+	\end{enumerate}
+
+	These comparisons demonstrate the same results from different angles and 
+	the systematic differences become more clear using the fraction of \mtot{}
+	within different radius.  
+	The comparison of cumulative \logms{} profiles also demonstrates that the 
+	\rbcg{} and \nbcg{} samples have very similar median \mtot{}.  
+    They help confirm that the distributions of stellar mass within 100 kpc indeed 
+    have systematic differences between the massive central galaxies living in more 
+    and less massive dark matter haloes.
+
+%% ------------------------------------------------------------------------------------ %%
+
 %% ------------------------------------------------------------------------------------ %% 
@@
 %% ------------------------------------------------------------------------------------ %% 
-\section{C. Match the \rbcg{} and \nbcg{} samples in \mstar{} and redshift distributions}
-    \label{app:match}
-
-    As explained earlier, it is important to make sure the two samples have similar 
-    distributions in both \mstar{} and redshift before comparing their median \mden{} 
-    profiles.  
-    Here we briefly describe the procedure used in this work. 
-    Since the \rbcg{} sample is smaller in size, we always match the \nbcg{} sample to 
-    it by searching for the $N$-nearest neighbours on the $M_{\star}$-redshift plane 
-    using the KDTree algorithm in the \texttt{scikit-learn} Python library 
-    (\citealt{scikit-learn}), and evaluate the quality of the match using the 
-    distributions of both parameters (as shown in Fig~\ref{fig:match}).
-
-    As we only keep the unique \nbcg{} galaxies in the matched sample, we manually 
-    adjust the value of $N$ to achieve the best match. 
-    When the redshift distribution of the \rbcg{} sample becomes bi-model, we also try 
-    to split the sample into two redshift bins and match them separately. 
-    Typically $N$ is between 3 to 8.
-    In Fig~\ref{fig:match}, we demonstrate this procedure using the results for 
-    the \mtot{}-matched (Left) and the \minn{}-matched samples in Fig~\ref{fig:prof_1}
-    (Right), and the two samples are well matched in the distributions of \mtot{}
-    (or \minn{}) and redshift.  
-    For all the comparisons of \mden{} profiles in this work, we match the samples 
-    in the same way, and make sure the match has the same quality. 
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %% 
-\section{D. Robustness of the \mden{} Differences} 
-	\label{app:robust}
-
-    In Fig~\ref{fig:prof_1}, we compare the \mden{} profiles of \mtot{}- and 
-    \minn{}-matched samples of \rbcg{} and \nbcg{} galaxies, and here we test the 
-    robustness of the results using a few extra tests that are illustrated in
-    Fig~\ref{fig:prof_2}, Fig~\ref{fig:prof_3}, and Fig~\ref{fig:prof_4}, and 
-    are briefly described here:
-
-    \begin{enumerate}
-
-        \item In Fig~\ref{fig:prof_2}, we group the samples into two \mtot{} bins. 
-            Given the small sample size, we extend slightly toward lower \mtot{} range 
-            ($11.5 \leq \log (M_{\star,\ 10\mathrm{kpc}}/M_{\odot}) < 11.7$ and 
-             $11.7 \leq \log (M_{\star,\ 10\mathrm{kpc}}/M_{\odot}) < 11.9$). 
-            Although the smaller sample leads to larger statistical uncertainties, 
-            we can still see similar structural differences in both \mtot{} bins, 
-            and the difference becomes more significant in the higher \mtot{} bin.  
-            For the lower \mtot{} bin, the difference in the inner region becomes 
-            quite uncertain, while the difference in the outskirt is still visible. 
-            This potentially suggests that the environmental dependence of structure 
-            also varies with \mstar{}, an important implication deserves more 
-            investigations in the future.
-
-        \item On the left panel of Fig~\ref{fig:prof_3}, we match the \rbcg{} and 
-            \nbcg{} samples in a lower redshift bins ($0.30 < z < 0.42$).
-            Despite the larger uncertainties due to smaller samples, we find the 
-            results are the same.
-
-        \item On the middle panel of Fig~\ref{fig:prof_3}, we includes \rbcg{} 
-            galaxies in poorer clusters ($20 < \lambda < 30$), which should result 
-            in overlapped \mhalo{} distributions with the \nbcg{} samples 
-            considering the typical uncertainty of $\lambda$.
-            This makes the difference in the inner region slightly less significant, 
-            but the overall results are the same.
-
-        \item On the right panel of Fig~\ref{fig:prof_3}, in stead of using \mtot{}, 
-            we use the \mmax{}--the maximum \mstar{} by integrating the \mden{} 
-            profiles to the largest radius allowed.  
-            The \mmax{} values are less reliable than \mtot{} due to the 
-            uncertainty of background subtraction and contamination from nearby 
-            bright objects, but they can serve as different estimates of the ``total''
-            \mstar{} of these galaxies.
-            As shown in Section~\ref{sec:discussion}, they on average increase
-            the \mstar{} by a little bit and affect the \rbcg{} more.
-            The differences in the \mden{} profiles still remain very similar.
-
-    \end{enumerate}
-
-    We also test the robustness of the \mtot{}-matched results using the samples with 
-    only spectroscopic redshift, the samples in the three GAMA fields, and the \rbcg{} 
-    samples without the ones in very massive haloes ($\lambda > 40$).  
-    Limited by space, we do not show these results here, but they all verify the 
-    robustness of the results.
-
-    For the results from the \minn{}-matched samples:
-
-    \begin{enumerate}
-
-        \item
-            We match the two samples using both \minn{} and the \mstar{} within 15 kpc 
-            at the same time.  
-            This makes the two median \mden{} profiles very similar inside 10-15 
-            kpc, while the result in the outskirt remains the same (left panel of 
-            Fig~\ref{fig:prof_4}).
-            Use \mstar{} within 5 or 20 kpc leads to the same conclusion.
-
-        \item 
-            To make sure the two samples are comparable in their overall assembly history,
-            we also try to only include the very massive galaxies (\logmtot{}$>11.5$)
-            in both samples. 
-            This excludes the \nbcg{} galaxies that are much less massive and 
-            more ``compact'' in structure. 
-            Yet, the results regarding the structural differences remain the same.
-
-    \end{enumerate}
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %% 
-\section{E. Comparison of \mden{} profiles using \mstar{} from the GAMA survey}
+\section{Comparison of \mden{} profiles using \mstar{} from the GAMA survey}
     \label{app:gama}
+
+%% ------------------------------------------------------------------------------------ %% 
+\begin{figure}
+    \centering
+    \includegraphics[width=\columnwidth]{fig/redbcg_cog_1}
+    \caption{
+        \textbf{Top:} comparison of the cumulative \mstar{} profiles for 
+        \rbcg{} (orange--red) and \nbcg{} (grey--black) galaxies at fixed \mtot{}.~~
+        \textbf{Bottom:} comparison of the fraction of \mtot{} within different radius 
+        for the same samples at fixed \mtot{}. 
+        Thicker and darker solid lines highlight the median profiles. 
+        Other formats of the figure are similar to Figure \ref{fig:prof_1}. 
+        Besides the region affected by seeing, the 10 and 100 kpc radius, we 
+        also highlight the 50\% and 100\% values using horizontal grey lines on the 
+        bottom panel. 
+        }
+    \label{fig:cog}
+\end{figure}
+%% ------------------------------------------------------------------------------------ %%
 

### 2017-11-28 draft/paper2_v7.tex
Address Susan's comments; New scaling relation figure

--- 2017-11-16 draft/paper2_v6.tex
@@
 % Version 5; preprint format; Edited by Jenny Greene and Song Huang
+% Version 6; preprint format; Edited by Susan Foster and Song Huang
 
@@
 \newcommand{\alexie}[1]{\textcolor{blue}{\textbf{[Alexie: #1]}}}
-\newcommand{\jenny}[1]{\textcolor{Bittersweet}{\textbf{[Jenny: #1]}}}
+\newcommand{\susan}[1]{\textcolor{Bittersweet}{\textbf{[Susan: #1]}}}
 \newcommand{\kevin}[1]{\textcolor{green}{\textbf{[Kevin: #1]}}}
@@
         $^{1}$Department of Astronomy and Astrophysics, University of California 
-              Santa Cruz, 1156 High St., Santa Cruz, CA 95064, U.S.A\\
+              Santa Cruz, 1156 High St., Santa Cruz, CA 95064, USA\\
         $^{2}$Kavli-IPMU, The University of Tokyo Institutes for Advanced Study, 
@@
 
-    We use ${\sim}100$ deg$^2$ of deep ($>28.5$ \sb{} in $i$-band), high-quality 
-    (median 0.6\asec seeing) imaging data from the Hyper Suprime--Cam (HSC) survey 
-    to investigate the halo mass dependence of the surface mass density profiles 
-    and outer stellar envelopes of massive galaxies. 
-    The $i$-band images from HSC survey reach ${\sim}4$ magnitudes deeper than SDSS 
-    and enable us to directly trace stellar mass distributions to 100 kpc without 
-    requiring stacking.  
-    We conclusively show that at fixed stellar mass, the stellar profiles of massive 
+    To investigate the halo mass dependence of the surface mass density profiles 
+    and outer stellar envelopes of massive galaxies, we use ${\sim}100$ deg$^2$ of 
+    deep ($>28.5$ \sb{} in $i$-band), high-quality 
+    (median 0.6\asec seeing) imaging data from the Hyper Suprime--Cam (HSC) survey.
+    The $i$-band images from the HSC survey reach ${\sim}4$ magnitudes deeper than 
+    Sloan Digital Sky Survey and enable us to directly trace stellar mass distributions 
+    to 100 kpc without requiring stacking.  
+    We conclusively show that, at fixed stellar mass, the stellar profiles of massive 
     galaxies depend on the masses of their dark matter haloes. 
@@
     at $0.3 < z < 0.5$ have shallower inner stellar mass density profiles 
-    (within ${\sim}10$-$20$ kpc) and more prominent outer envelopes. 
+    (within ${\sim}10$--$20$ kpc) and more prominent outer envelopes. 
     These differences translate into a halo mass dependence of the 
-    mass--size relation: central galaxies in haloes with \logmh{}$>14.0$ are 
+    following mass--size relation: central galaxies in haloes with \logmh{}$>14.0$ are 
     $\sim 20$\% larger in $R_{\mathrm{50}}$ at fixed \mtot{}.  
@@
     of 2--4 over a time span of 10 Gyrs (e.g. \citealt{Newman2012, vdWel2014}). 
-    This observational result spurred the development of the ``two-phase'' formation
+    This observational result spurred the development of the `two-phase' formation
     scenario for massive ETGs (e.g. \citealt{Oser2010, Oser2012}),
@@
     They subsequently assemble extended stellar haloes via dry mergers 
-    \citep[e.g,][]{Naab2006, Khochfar2006, Oser2010, Oser2012} which can cause 
+    \citep[e.g,][]{Naab2006, Khochfar2006, Oser2010, Oser2012}, which can cause 
     significant size growth at late times. 
     An alternative explanation for size growth, progenitor bias, hypothesizes that 
-    larger ETGs were quenched more recently, but this explanation is still under 
+    larger ETGs were quenched more recently; but this explanation is still under 
     active debate (e.g. \citealt{Newman2012, Carollo2013, Poggianti2013, Belli2015,
@@
     brightness or mass density profiles (e.g. \citealt{Huang2013a, Huang2013b, 
-    Oh2017}, optical color gradients (e.g. \citealt{LaBarbera2010, LaBarbera2012}), 
+    Oh2017}, optical colour gradients (e.g. \citealt{LaBarbera2010, LaBarbera2012}), 
     and stellar population gradients \citep[e.g.,][]{Coccato2010, Coccato2011, 
@@
     \song{
-    Under the $\Lambda$CDM cosmology, The assembly of massive ETGs is intrinsically 
-    tied to the hierarchal growth of their host dark matter haloes 
+    Under the $\Lambda$CDM cosmology, the assembly of massive ETGs is intrinsically 
+    tied to the hierarchical growth of their host dark matter haloes 
     (e.g. \citealt{Leauthaud2012, Behroozi2013, Shankar2013}). 
     Hydrodynamic simulations suggest that the fraction of star accreted through 
-    mergers (\textit{ex situ} component) in central galaxy increases with halo 
+    mergers (\textit{ex situ} component) in a central galaxy increases with halo 
     mass (e.g. \citealt{Pillepich2017b}). 
-    Although the major merger rate is not strong function of progenitor halo mass 
+    Although the major merger rate is not a strong function of progenitor halo mass 
     (e.g. \citealt{Shankar2015}), minor mergers may still play a more important 
-    role in the assembly of central galaxy of more massive dark matter halos 
+    role in the assembly of a central galaxy of more massive dark matter haloes 
     (e.g. \citealt{Guo2011, Yoon2017}). 
-    As minor merger is more efficient at ``puffing up'' the outskirts of massive 
-    galaxies (e.g. \citealt{Oogi2013, Bedorf2013}), this seems to suggest the 
+    As a minor merger is more efficient at `puffing up' the outskirts of massive 
+    galaxies (e.g. \citealt{Oogi2013, Bedorf2013}), this seems to suggest that the 
     structures of massive ETGs and the well-known stellar mass--effective radius 
     relation (\mstar{}--$R_{\rm e}$; e.g., \citealt{Shen2003, Guo2009}) should depend 
-    on their ``environment''\footnote{There are multiple definitions of 
-    ``environment'' in the literature.  
-    In this work, we use ``environment'' and halo mass interchangeably.}
+    on their `environment'\footnote{There are multiple definitions of 
+    `environment' in the literature.  
+    In this work, we use `environment' and halo mass interchangeably.}
     (e.g. \citealt{Shankar2013, Shankar2014}). 
-    However, evidence for the environment--dependence of \mstar{}--$R_{\rm e}$
+    However, evidence for the environment-dependence of \mstar{}--$R_{\rm e}$
     at low redshift is still not very solid (\citealt{Nair2010, HCompany13}; 
@@
 	\song{
-    Therefore, we think it requires deeper images of these massive galaxies to 
+    Therefore, we expect that it requires deeper images of these massive galaxies to 
     better probe their outer stellar mass distributions and test these 
@@
     \logms{}$>11.4$ at $0.3 < z < 0.5$ and out to 100 kpc. 
-    In Paper I, we characterized the stellar mass profiles of massive ETGs, and 
+    In Paper I, we characterized the stellar mass profiles of massive ETGs and 
     showed that there is a large intrinsic scatter in the \mden{} stellar haloes of
-    massive galaxies on 100 kpc scales. 
-    In this paper, we now investigate whether or not the large scatter in the outer 
+    massive galaxies on 100-kpc scales. 
+    In this paper, we investigate whether the large scatter in the outer 
     profiles of massive galaxies correlate with halo mass. 
@@
     depend on dark matter halo mass. 
-    In other terms, we reveal the halo mass dependence of the mass-size relation 
+    In other words, we reveal the halo mass dependence of the mass--size relation 
     for massive ETGs.
@@
 
-    Magnitudes use the AB system (\citealt{Oke1983}), and are corrected for Galactic 
+    Magnitudes use the AB system (\citealt{Oke1983}), and are corrected for galactic 
     extinction using calibrations from \citet{Schlafly11}. 
@@
     and ${\Omega}_{\rm \Lambda}=0.7$.
-    Stellar mass is denoted \mstar{} and has been derived using a Chabrier Initial Mass 
-    Function (IMF; \citealt{Chabrier2003}). Halo mass is defined as 
+    Stellar mass is denoted \mstar{} and has been derived using a Chabrier initial mass 
+    function (IMF; \citealt{Chabrier2003}). Halo mass is defined as 
     $M_{\rm 200b}\equiv M(<r_{\rm 200b})=200\bar{\rho} 
-    \frac{4}{3}\pi r_{\rm 200b}^3$ where $r_{\rm 200b}$
+    \frac{4}{3}\pi r_{\rm 200b}^3$, where $r_{\rm 200b}$
     is the radius at which the mean interior density is equal to 200 times
@@
     As in \citet{hscMassiveI}, we do not attempt to decompose or distinguish any  
-    potential ``intra-cluster'' 
+    potential `intra-cluster' 
     component (ICL; e.g. \citealt{Carlberg1997, Lin2004, Gonzalez2005, Mihos2005}).
@@
       \caption{
-          Three-color images for a subsample of massive galaxies at $z{\sim}0.4$. 
-          All of these massive galaxies have very similar \mstar{} within a 10 kpc 
+          Three-colour images for a subsample of massive galaxies at $z{\sim}0.4$. 
+          All of these massive galaxies have very similar \mstar{} within a 10-kpc 
           elliptical aperture 
           ($11.2<\log_{10} (M_{\star,10\ \mathrm{kpc}}/M_{\odot})<11.3$). 
-          The dash-line circle at the top-left figure indicates $R=$10 kpc.
+          The dashed-line circle at the top-left figure indicates $R=$10 kpc.
           These galaxies are rank-ordered from top to bottom and from left to right 
-          by their \mstar{} within a 100 kpc elliptical aperture which varies 
+          by their \mstar{} within a 100-kpc elliptical aperture that varies 
           from $10^{11.2} M_{\odot}$ to $10^{11.7} M_{\odot}$. 
-          At fixed ``inner'' mass (\minn{}), massive galaxies display significant
+          At fixed `inner' mass (\minn{}), massive galaxies display significant
           diversity in their outer profiles. 
@@
           galaxies. 
-          Left: halo mass dependence of galaxy profiles at fixed ``total'' stellar mass 
+          Left: Halo mass dependence of galaxy profiles at fixed `total' stellar mass 
           (\mtot{}). 
-          Right: halo mass dependence of galaxy profiles at fixed ``inner-mass'' 
+          Right: Halo mass dependence of galaxy profiles at fixed `inner-mass' 
           (\minn{}). Orange and red lines correspond to central galaxies living in 
@@
           \logmh{} $\leq 14.0$. 
-          Thin lines show the profiles of individual galaxies while thick lines show 
+          Thin lines show the profiles of individual galaxies, while thick lines show 
           the median profile. 
@@
           Brown lines in the bottom panels show the relative difference between  
-          two median profiles 
+          the two median profiles 
           ($\Delta = \log(\mu_{\star, \mathrm{cenHighMh}}) - 
           \log(\mu_{\star, \mathrm{cenLowMh}}$). 
-          Errors on the difference between the two profiles are also computed 
+          Errors in the difference between the two profiles are also computed 
           via bootstrap.
-          The grey shaded regions show a Monte Carlo test to asses how likely is it to 
+          The grey-shaded regions show a Monte Carlo test to assess how likely it is to 
           obtain $\Delta$ from random sub-samples of the data. 
-          To compute the grey shaded regions, we first mix the two samples 
+          To compute the grey-shaded regions, we first mix the two samples 
           (\rbcg{} and \nbcg{}), then draw sub-samples of galaxies from the mixed 
@@
           We repeat this process 5000 times.  
-          The dark-grey shaded region (light-grey shaded region) shows the 1-$\sigma$ 
+          The dark grey--shaded region (light grey--shaded region) shows the 1-$\sigma$ 
           (3-$\sigma$) fluctuations in $\Delta$ from these 5000 draws.
@@
           Two vertical lines highlight our $11.6<$ \logms{} $<11.9$ mass bin. 
-          The red solid line shows the best fit mass-size relation for \rbcg{} and the 
-          grey dashed line shows the best fit relation for \nbcg{}. 
-          Shaded regions in lighter colors show the 1-$\sigma$ uncertainties
-          from MCMC sampling.  
-          The green dashed line shows the mass-size relation for nearby central 
+          The red solid line shows the best-fitting mass--size relation for \rbcg{} and the 
+          grey dashed line shows the best-fitting relation for \nbcg{}. 
+          Shaded regions in lighter colours show the 1-$\sigma$ uncertainties
+          from Markov chain Monte Carlo (MCMC) sampling.  
+          \song{
+          The green dashed line shows the mass--size relation for $z<0.09$ central 
           galaxies in massive groups from \citet{HCompany13}. 
+          And the cyan dashed line represents the mass--size relation for 
+          $0.2<z<0.5$ ETGs in groups from the COSMOS survey provided by 
+          \citet{HueartasCompany2013b}.
+          }
           \textbf{Right:} The relations between \mtot{} and \minn{} for the 
-          \rbcg{} and \nbcg{} galaxies, along with the best-fit scaling relations for 
+          \rbcg{} and \nbcg{} galaxies, along with the best-fitting scaling relations for 
           both samples.
@@
     (\citealt{HSC-DR1} and covers ${\sim} 110$ deg$^2$ in all five-band ($grizy$) to 
-    the full depth in the Wide field. 
+    the full depth in the wide field. 
     The data are reduced by \texttt{hscPipe 4.0.2}, a derivative of the 
@@
     In Paper~I, we select a sample of 25286 bright galaxies with spectroscopic 
-    redshifts or reliable ``red-sequence'' photometric redshifts (\citealt{Rykoff2014}) 
+    redshifts or reliable `red-sequence' photometric redshifts (\citealt{Rykoff2014}) 
     at $0.3<z<0.5$. 
@@
     ($\sim5\times 10^6$ Mpc$^3$) to sample the galaxy stellar mass function above 
-    \logms$>11.6$, we can spatially resolve galaxies profiles to $\sim 5$ kpc 
+    \logms$>11.6$, and we can spatially resolve galaxies profiles to $\sim 5$ kpc 
     ($1.0^{\arcsec}$ corresponds to 4.4 and 6.1 kpc at $z=0.3$ and 0.5). 
     \song{
-    And massive galaxies should experience little structural evolution and 
+    Massive galaxies should experience little structural evolution and 
     size growth between $z=0.5$ and 0.3 ($\sim$1.5 Gyr of time span) 
@@
 
-    We derive $i$-band surface brightness profiles out to 100 kpc after carefully 
-    masking out surrounding neighbors and accounting for the subtraction of the 
-    background light. 
+    After carefully 
+    masking out surrounding neighbours and accounting for the subtraction of the 
+    background light, we derive $i$-band surface brightness profiles out to 100 kpc. 
     We use the broadband spectral energy distributions (SED) fitting code 
@@
     Using HSC data, we can measure the \mden{} profiles of massive galaxies to 
-    $\sim 100$ kpc and we integrate these profiles within elliptical isophotal
+    $\sim 100$ kpc, and we integrate these profiles within elliptical isophotal
     apertures at different physical radii. 
-    As explained in Paper~I, here we focus on the two following metric masses:
+    As explained in Paper~I, we focus on the two following metric masses:
 
@@
 
-        \item stellar mass within 10 kpc (hereafter noted \minn{}) which we use 
+        \item Stellar mass within 10 kpc (hereafter noted \minn{}), which we use 
             as a proxy for the stellar mass of the \textit{in situ} stellar 
@@
 
-        \item stellar mass within 100 kpc (hereafter noted \mtot{}). 
-            We use \mtot{} as a proxy of the ``total'' stellar mass. 
-            In Paper~I we showed that \mtot{} recovers more light compared to 
-            HSC \cmodel{} photometry with offsets that can be a large as 0.2 dex 
+        \item Stellar mass within 100 kpc (hereafter noted \mtot{}). 
+            We use \mtot{} as a proxy for the `total' stellar mass. 
+            In Paper~I we show that \mtot{} recovers more light compared to 
+            HSC \cmodel{} photometry and has offsets that can be a large as 0.2 dex 
             in magnitude.
@@
    We use these two simple metric masses to explore the \mstar{}-dependence of the 
-   fraction of accreted stars, and reveal the diversity of stellar envelopes among 
+   fraction of accreted stars and to reveal the diversity of stellar envelopes among 
    massive galaxies. 
@@
    results in terms of the full stellar mass profiles. 
-   However, in many cases we find it more useful to display figures using the more 
-   simple \minn{} and \mtot{} quantities. 
+   However, in many cases we find it more useful to display figures using the simpler 
+   \minn{} and \mtot{} quantities. 
    In Figure \ref{fig:m100_m10_color}, we highlight the diversity of galaxies as a 
@@
    Figure \ref{fig:m100_m10_color} shows a random subsample of massive galaxies with 
-   very similar \minn{} that have large range of \mtot{}. 
-   We will use these two apertures masses to guide our comparisons of massive galaxies 
+   very similar \minn{} that have a large range of \mtot{}. 
+   We use these two aperture masses to guide our comparisons of massive galaxies 
    as a function of environment.
@@
     In addition to the mass cut above, we also limit our sample to galaxies that live 
-    at the centers of their own dark matter haloes-- so-called ``central'' galaxies. 
+    at the centers of their own dark matter haloes -- so-called `central' galaxies. 
     We use the \redm{} \texttt{v5.10} \citep{Rykoff2014, Rozo2015b} cluster catalogue 
@@
 
-    Firstly, we select 68 massive central galaxies from \redm{} clusters 
-    with richness ($\lambda$) $\geq 30$, and the probability of true central galaxy 
-    ($P_{\mathrm{Cen}}$) $\geq 0.7$, and \logmtot{}$>11.5$ 
-    at $0.3 < z < 0.5$ (63/68 have \logmtot{}$>11.6$). 
+    First, we select 68 massive central galaxies from \redm{} clusters 
+    with richness ($\lambda$) $\geq 30$, and we assign the probability of true central 
+    galaxy ($P_{\mathrm{Cen}}$) $\geq 0.7$, and \logmtot{}$ >11.5$ 
+    at $0.3 < z < 0.5$ (63/68 have \logmtot{}$ >11.6$). 
     This $\lambda$ limit is chosen to mitigate incompleteness in the cluster catalogue
     at the high end of our redshift window. 
-    The $P_{\mathrm{Cen}}$ limit is selected to exclude low probability candidate of 
-    central galaxy. 
+    The $P_{\mathrm{Cen}}$ limit is selected to exclude a low-probability candidate for 
+    the central galaxy. 
     \song{
     \citet{Simet2017} calibrates the \mhalo{}-$\lambda$ relation for the \redm{} 
-    clusters using the SDSS weak lensing data after carefully addressing many 
+    clusters using the SDSS weak-lensing data after carefully addressing many 
     important systematic uncertainties.
-    Based on this calibration, these correspond to central galaxies living in haloes 
-    with \mhalo{}$>10^{14.2}$~\msun{}. 
+    Based on this calibration, these clusters correspond to central galaxies living 
+    in haloes with \mhalo{}$>10^{14.2}$~\msun{}. 
     This calibration is consistent with several other independent calibrations 
@@
     (\mhalo{}$\approx 3.0 \times 10^{14}$~\msun{}).
-    We will refer to this sample of \textbf{central galaxies in massive haloes} as 
+    We refer to this sample of \textbf{central galaxies in massive haloes} as 
     the \rbcg{} sample.
 
-    Secondly, we build a complementary sample of central galaxies in lower-mass haloes
+    Second, we build a complementary sample of central galaxies in lower mass haloes
     by excluding all galaxies that are in any \redm{} cluster with $\lambda > 20$.
@@
     They provide empirical functions that describe the average density profiles 
-    of dark matters with different halo mass and at different redshifts.  
+    of dark matters with different halo masses and at different redshifts.  
     Using the \texttt{Colossus} Python package 
     (\citealt{Colossus})\footnote{\url{http://www.benediktdiemer.com/code/colossus/}}
-    provided by these authors, we estimate the $R_{\mathrm{200b}}$ of each cluster 
-    given its $M_{\mathrm{200b}}$ and redshift.
+    provided by \citet{Diemer2015}, we estimate the $R_{\mathrm{200b}}$ of each 
+    cluster given its $M_{\mathrm{200b}}$ and redshift.
     } 
@@
     photometric redshift uncertainty of the cluster (typically around 0.015 to 0.025).
-    This second sample will be dominated by central galaxies living in haloes with
-    $M_{\mathrm{200b}} < 10^{14}$~\msun{}, and will refer to this sample as \nbcg{}. \
+    This second sample is dominated by central galaxies living in haloes with
+    $M_{\mathrm{200b}} < 10^{14}$~\msun{}; we refer to this sample as \nbcg{}. \
     There are 833 galaxies with \logmtot{}$> 11.6$ in this sample.
@@
     \minn{} for the \rbcg{} and \nbcg{} samples. 
-    We also compare these two samples on the \mtot{}--rest frame $g-r$ color plane. 
-    Both of them follow the same ``red-sequence'' with only a handful of galaxies 
-    displaying bluer colors.
+    We also compare these two samples on the \mtot{}--rest frame $g-r$ colour plane. 
+    Both of the samples follow the same `red-sequence', with only a handful of galaxies 
+    displaying bluer colours.
 
     We note that our analysis fails to extract 1-D profiles for $\sim10$\% of 
-    \rbcg{} and \nbcg{} galaxies due on-going major mergers or projection effects 
+    \rbcg{} and \nbcg{} galaxies due to ongoing major mergers or projection effects 
     (e.g.\ nearby foreground galaxy or bright stars). 
@@
     \minn{} display a large diversity in their stellar haloes. 
-    In Paper~I, we explored the \mstar{}-dependence of the stellar haloes in massive 
-    galaxies, and concluded that the general trends are consistent with the predictions 
-    of the two-phase formation scenario. 
-    In this work, we now investigate the relation between the \mden{} profiles of 
+    In Paper~I, we explore the \mstar{}-dependence of the stellar haloes in massive 
+    galaxies, and we conclude that the general trends are consistent with the 
+    predictions of the two-phase formation scenario. 
+    In this work, we investigate the relation between the \mden{} profiles of 
     massive galaxies, their stellar haloes, and dark matter halo mass. 
-    Here we use \mtot{} as proxy for the ``total'' \mstar{} of massive galaxies and 
+    Here we use \mtot{} as a proxy for the `total' \mstar{} of massive galaxies, and 
     we use \minn{} as a rough proxy for the stellar mass of the \textit{in situ} 
@@
     estimate \mtot{} and \minn{} using elliptical apertures following the average 
-    fluxed-weighted isophotal shape.
+    flux-weighted isophotal shape.
 
@@
     First, we ask whether the \mden{} profiles of massive central galaxies depend on 
-    halo mass at fixed stellar mass.    
-    We will show comparisons of \mden{} profiles at both fixed \mtot{} as well as fixed 
+   a halo mass at a fixed stellar mass.    
+    We show comparisons of \mden{} profiles at both fixed \mtot{} and fixed 
     \minn{}. 
-    We also ensure that all comparisons are performed with fixed underlying redshift
-    distribution by matching samples in redshift in addition to stellar mass
+    We also ensure that all comparisons are performed with a fixed underlying redshift
+    distribution by matching samples in redshift in addition to a fixed stellar mass
     (please see Appendix~\ref{app:match}, Appendix~\ref{app:redshift}, 
@@
     fixed \minn{} (right panel). 
-    At fixed \mtot{}, we compare massive galaxies that have similar ``total'' \mstar{}. 
-    On the right side, we use \minn{} as proxy of the \textit{in situ} \mstar{} to 
+    At fixed \mtot{}, we compare massive galaxies that have similar `total' \mstar{}. 
+    On the right side, we use \minn{} as a proxy for the \textit{in situ} \mstar{} to 
     compare the overall \mstar{} distributions of galaxies living in different 
-    environments that have assembled similar amount of stars at high-$z$.
+    environments that have assembled a similar amount of stars at high-$z$.
     This figure shows the main result of this paper, namely that 
@@
     \song{
-    We estimate the uncertainties of the median \mden{} profiles using bootstrap 
-    resampling test. 
-    We also perform statistical tests to demonstrate that the differences of \mden{}
-    profiles are more significant than the levels allowed by the intrinsic randomness
-    within the combined \rbcg{} and \nbcg{} sample. 
+    We estimate the uncertainties of the median \mden{} profiles using a bootstrap 
+    resampling test, and we perform statistical tests to demonstrate that the 
+    differences of \mden{} profiles are more significant than the levels allowed by 
+    the intrinsic randomness within the combined \rbcg{} and \nbcg{} sample. 
     }
@@
         \item \song{
-            For the \mtot{}--matched samples, there are some subtle but statistically 
+            For the \mtot{}-matched samples, there are some subtle but statistically 
             significant and robust differences between the two median \mden{} profiles.
@@
             to be very small. 
-            Meanwhile, the difference in \mden{} profile becomes more apparent 
+            Meanwhile, the difference in the \mden{} profile becomes more apparent 
             at $R>50$ kpc scales.  
             In Appendix \ref{app:cog} and Figure~\ref{fig:cog}, we compare the same
-            \mtot{}--matched samples using the cumulative \mstar{} profiles 
+            \mtot{}-matched samples using the cumulative \mstar{} profiles 
             (or `curve of growth') and the fraction of \mtot{} enclosed within 
-            different radius.
+            different radii.
             Both comparisons highlight the differences in median \mden{} profiles 
@@
             display shallower \mden{} profiles compared to those from less massive 
-            dark matter haloes (they have a flatter inner \mden{} profiles and 
-            more significant outer stellar haloes. 
+            dark matter haloes (i.e.they have flatter inner \mden{} profiles and 
+            more significant outer stellar haloes). 
             The median \mden{} profiles of the \rbcg{} and \nbcg{} samples cross 
@@
 
-        \item For the \minn{}--matched samples, their median \mden{} profiles 
+        \item For the \minn{}-matched samples, the median \mden{} profiles 
             are very similar at $R \leq 10$ kpc. 
@@
             different \mtot{}, and the massive central galaxies in 
-            more massive haloes host much more prominent outer stellar halo.
-
-        \item Also, for the \minn{}--matched samples, the similar slopes of the 
+            more massive haloes host much more prominent outer stellar haloes.
+
+        \item Also, for the \minn{}-matched samples, the similar slopes of the 
             \mden{} profiles within 10 kpc are in sharp contrast with the large
@@
     \song{
-    The subtle differences seen on the left side of Fig \ref{fig:prof_1} suggests
+    The subtle differences seen on the left side of Fig \ref{fig:prof_1} suggest
     that the stellar mass distributions of the most massive central galaxies only
@@
     More importantly, this result also suggests that halo mass does not play the 
-    central role in shaping massive central galaxies \textbf{at fixed ``total'' 
+    central role in shaping massive central galaxies \textbf{at fixed `total' 
     stellar mass}.
@@
     Although this trend still needs to be confirmed by larger samples, it 
-    potentially indicates that the assembly of stellar haloes in more massive 
-    central galaxies become more sensitive to their environments.
-
-    \song{
-    Meanwhile, the comparison of \mden{} profiles at fixed \minn{}--a potential 
+    potentially indicates that the process of stellar haloes assembling in more 
+    massive central galaxies becomes more sensitive to their environments.
+
+    \song{
+    Meanwhile, the comparison of \mden{} profiles at fixed \minn{} -- a potential 
     tracer of the \mstar{} in the \textit{in situ} component (right panel of 
-    Fig~\ref{fig:prof_1}) hints that the inner region ($<10$ kpc) and the outer 
-    stellar halo are shaped by different physical processes and response to 
+    Fig~\ref{fig:prof_1}) -- hints that the inner region ($<10$ kpc) and the outer 
+    stellar halo are shaped by different physical processes and responses to 
     environment at different levels. 
@@
     In hydrodynamic simulations, intense dissipative processes help create 
-    self-similar de~Vaucouleur-like ($n{\sim} 4$) \mden{} profile in the inner part 
-    of massive galaxy (e.g. \citealt{Hopkins2008}), and the \mhalo{}-dependent
-    merging history leads to shallower stellar halo profile for central galaxy 
-    of more massive halo (e.g. \citealt{Pillepich2014}). 
+    a self-similar de~Vaucouleurs--like ($n{\sim} 4$) \mden{} profile in the inner part 
+    of a massive galaxy (e.g. \citealt{Hopkins2008}), and the \mhalo{}-dependent
+    merging history leads to shallower stellar halo profile for the central galaxy 
+    of a more massive halo (e.g. \citealt{Pillepich2014}). 
     The intrinsic scatter of halo assembly histories at fixed halo mass and the 
@@
     mergers in more massive dark matter haloes. 
-    Non-dissipative (minor) mergers should not strongly alter the inner \mden{} 
+    Nondissipative (minor) mergers should not strongly alter the inner \mden{} 
     profiles, but can build up the outer halo efficiently
@@
     samples reveals clear differences, we should point out that several physical 
-    processes could alter \minn{} and the \mden{} profiles within 10 kpc during the
-    last 10 Gyrs (e.g., AGN feedback or merger of binary supermassive black holes). 
-    We will further discuss this in \S~\ref{ssec:cen}.
+    processes (e.g. AGN feedback or merger of binary supermassive black holes) could 
+    alter \minn{} and the \mden{} profiles within 10 kpc during the last 10 Gyrs. 
+    We discuss this further in \S~\ref{ssec:cen}.
     }
@@
 
-    The above section shows that the \mden{} profiles of massive galaxies show a 
-    dependence on the masses of their host dark matter haloes. 
-    In this section, we now turn our attention to the more commonly studied stellar 
+    In \S~\ref{ssec:sbp_mtot} we explain that the \mden{} profiles of massive galaxies 
+    show a dependence on the masses of their host dark matter haloes. 
+    In this section, we turn our attention to the more commonly studied stellar 
     mass--size relation (\mstar{}--$R_{\mathrm{e}}$). 
-    In addition, we will also consider halo mass dependence on the 
+    In addition, we consider halo mass dependence on the 
     \mtot{}--\minn{} plane.
@@
 %% ------------------------------------------------------------------------------------ %% 
-\subsubsection{Mass-Size Relation}
+\subsubsection{Mass--Size Relation}
     \label{sssec:mass_size}
@@
     $R_{\mathrm{e}}$ or $R_{\mathrm{50}}$; e.g. \citealt{Shankar2013, Leja2013, 
-    vdWel2014}) is one of the most important scaling relation for ETGs. 
+    vdWel2014}) is one of the most important scaling relationships for ETGs. 
     Despite numerous attempts, previous studies have failed to detect the 
-    \mhalo{}--dependence of the \mstar{}--$R_{\mathrm{e}}$ relation at low-$z$ 
+    \mhalo{}-dependence of the \mstar{}--$R_{\mathrm{e}}$ relation at low-$z$ 
     (e.g. \citealt{Weinmann2009, Nair2010, HCompany13, Cerbrian2014}; 
@@
     \song{
-    In the previous section, the differences in the \mden{} profiles already reveals 
-    that the \mtot{}-matched massive galaxies from different environments should have
-    different effective radius (especially see Fig~\ref{fig:cog}). 
+    As discussed in the previous section, the differences in the \mden{} profiles 
+    reveal that the \mtot{}-matched massive galaxies from different environments 
+    should have different effective radii (especially see Fig~\ref{fig:cog}). 
     We now specifically look into the more traditionally studied 
     \mstar{}--$R_{\mathrm{e}}$ relation.
-    Firstly, we want to point out that `size' is not a well defined parameter for 
-    object like massive galaxies with very extended stellar mass distributions. 
-    In practice, the measurements of `effective radius' or `half--light radius' 
-    not only depends on resolution, depth, and filter of the image, but may also 
+    First, we want to point out that `size' is not a well-defined parameter for 
+    objects like massive galaxies with very extended stellar mass distributions. 
+    In practice, the measurements of `effective radius' or `half-light radius' 
+    not only depend on resolution, depth, and filter of the image, but may also 
     depend on the adopted model for the light profile.  
@@
     }
-    In this section, we still use \mtot{} as proxy of ``total'' \mstar{} and we adopt 
-    the radius enclosing 50\% of stellar mass within 100 kpc ($R_{\mathrm{50}}$; 
-    derived from the $i$-band curve-of-growth) as the ``size''. 
-    Such definition of ``half--light radius'' is more robust against structural 
+    In this section, we still use \mtot{} as a proxy for `total' \mstar{}, and we 
+    adopt the radius enclosing 50\% of stellar mass within 100 kpc ($R_{\mathrm{50}}$; 
+    derived from the $i$-band curve-of-growth) as the `size'. 
+    Such a definition of `half-light radius' is more robust against structural 
     details, choice of model, and the background subtraction compared to the 
-    effective radius measured using 2-D model with oversimplified assumptions 
+    effective radius measured using a 2-D model with oversimplified assumptions 
     (e.g. single-\ser{} model). 
@@
     Uncertainties in both \mtot{} and $R_{\mathrm{50}}$ are considered. 
-    For \logmtot{}$>11.6$ galaxies, typical uncertainty for mass is $\sim 0.12$
+    For \logmtot{}$>11.6$ galaxies, the typical uncertainty for mass is $\sim 0.12$
     dex.  
-    As for the $R_{\mathrm{50}}$, its uncertainty based on the \mden{} profile
+    The $R_{\mathrm{50}}$ uncertainty is based on the \mden{} profile and
     is very small due to the high \s2n{} of the profile. 
@@
 
-    The best-fit relation for \rbcg{} is:
+    The best-fitting relation for \rbcg{} is:
 
@@
     different normalizations. 
-    The best--fit mass--size relations derived here suggests that, 
+    The best-fitting mass--size relation derived here suggests that, 
     at $0.3 < z < 0.5$, central galaxies with \logmtot{}$>11.6$ in \logmhalo{}$>14.2$
@@
     This result is robust against the ranges of \mstar{} over which the fit is 
-    performed and against the definitions of  ``total'' \mstar{} and half-light 
+    performed and against the definitions of  `total' \mstar{} and half-light 
     radius\footnote{Using \mstar{} within 120 or 150 kpc, or using the 
@@
     \song{
-    Due to the relative steep slopes for the \mtot{}--$R_{\mathrm{50}}$ relation, 
-    secondary binning (e.g., different halo mass) may induce artificial differences
-    (e.g., \citealt{Sonnenfeld2017}). 
-    We first check the results using the \mtot{}--matched samples and confirm 
+    Due to the relatively steep slopes for the \mtot{}--$R_{\mathrm{50}}$ relation, 
+    secondary binning (e.g. different halo mass) may induce artificial differences
+    (e.g. \citealt{Sonnenfeld2017}). 
+    We first check the results using the \mtot{}-matched samples and confirm 
     the above conclusion. 
@@
     For the \logmtot{}$>11.6$ galaxies, we estimate the average $\gamma$ of both
-    samples using the slopes of their best--fit mtot{}--$R_{\mathrm{50}}$ relations.
+    samples using the slopes of their best-fitting mtot{}--$R_{\mathrm{50}}$ relations.
     For the \rbcg{} sample, $<\gamma> = 4.2\pm0.4$; for the \nbcg{} one, 
@@
     environment--dependence as shown in \citet{HCompany13}.
-    Therefore we think the direct comparison of \mden{} profiles or the 
+    Therefore, we expect that the direct comparison of \mden{} profiles or the 
     \mtot{}--\minn{} relation may be better at tracing the environment dependence
-    of structure in massive galaxies. 
-    }
-
-    We qualitatively compare our results with \citealt{HCompany13} (HC13; 
-    green solid line) who studied $z\leq 0.09$ central ETGs in 
-    $12.5 \le$ \logmh{} $< 15$ haloes. 
-    HC13 use the group catalogue by \citet{Yang2007} to estimate halo mass. 
+    of structures in massive galaxies. 
+    }
+
+    \song{
+    We qualitatively compare our results with the mass--size relation for 
+    $0.2 < z < 0.5$ group ETGs in the COSMOS survey (
+    \citealt{HueartasCompany2013b}; HC13a; cyan dashed line).
+    HC13a measures luminosity and size of each galaxy by fitting a 2--D 
+    single--\ser{} model to the \textit{HST}/ACS \texttt{F814W} image. 
+    And the stellar mass is derived from SED fitting based on very similar 
+    model assumptions. 
+    HC13a uses circularized effective radius 
+    ($R_{\mathrm{e,Circ}} = R_{\mathrm{e,Fit}} \times \sqrt{b/a}$) in their work. 
+    Here we empirically correct their effective radius to the measured values 
+    assuming an average $<b/a>=0.75$.
+    At similar redshift, the mass-size relation from HC13a lies below the 
+    one in this work, while their slopes are quite similar.
+    }
+
+    \song{
+    We also compare with results from \citealt{HCompany13} (HC13b; green dashed line), 
+    who studied $z\leq 0.09$ central ETGs in $12.5 \le$ \logmh{} $< 15$ haloes. 
+    HC13b use the group catalogue by \citet{Yang2007} to estimate halo mass. 
+    In contrast to the present study, HC13a finds no environment dependence in the 
+    mass--size relation for central galaxies in the range $12.5\le$ \logmh{} $<15.0$. 
     They obtain effective radii from single-\ser{} model fitting to SDSS 
@@
     synthetic population model. 
-    We convert their \mstar{} estimates from a Kroupa IMF to a Chabrier 
-    IMF by applying a constant -0.05 dex shift (see \citealt{Bernardi2016a}). 
+    We convert the HC13b \mstar{} estimates from a Kroupa IMF to a Chabrier 
+    IMF by applying a constant $-0.05$ dex shift (see \citealt{Bernardi2016a}). 
     We further add $+0.1$dex to the HSC13 stellar masses to account for a systematic 
     offset between BC03 and our FSPS model (see Paper~1). 
-    The distributions of our massive galaxies on the \mtot{}--$R_{\mathrm{50}}$ 
-    plane follow the HC13 relation reasonably well (with slightly shallower slopes), 
-    even at \logmtot{}$< 11.6$ where our samples start to become incomplete in \mtot{}. 
-    In contrast to the present study, HC13 finds no environment dependence in the 
-    mass--size relation for central galaxies in the range $12.5\le$ \logmh{} $<15.0$. 
-    \song{
-    This could relate to the difference in the depth of HSC and SDSS images.
-    The very low surface brightness stellar haloes that show clearly 
-    environment dependence in this work are difficult to see or model on SDSS images.        
-    And, given the much shallower SDSS images used in HC13, it is a little bit 
-    surprised to see that their mass-size relation is not very different with the
-    ones using deeper HSC images. 
-    Besides the systematics in the \m2l{} estimates using different methods, 
-    different photometric methods could be the main reason behinds this 
-    coincidence.
-    For instance, if shallower image leads to systematically underestimated mass, 
-    it could shift the mass--size relation horizontally.  
-    And single-\ser{} is not very accurate model for massive galaxies, hence it 
-    can result in bias of both mass and size measurements (e.g., see 
-    Appendix~\ref{app:gama}). 
-    This further reflects our point that `size' is not straightforward to measure 
-    and compare, also that the mass--size relation may not be the best tool to 
-    investigate environment dependence in massive galaxies. 
+    Here we see that our massive galaxies follow the HC13a relation reasonably well
+    (with slightly shallower slopes) despite the differences in redshift. 
+    }
+
+    \song{
+    Both of these comparisons highlight our arguments that `size' is not the most 
+    well-defined property to measure and compare, and that the mass--size relation 
+    may not be the most reliable tool to investigate environment dependence in 
+    massive galaxies.
+    The differences between the HC13a and our results may relate to the differences 
+    in modelling method and the shallower ACS/\texttt{F814W} images. 
+    As for HC13b, it is also possible that the shallower SDSS image hides the
+    environmental dependence.  
+    The low surface--brightness stellar haloes that present the best evidence for 
+    environmental dependence using the deep HSC images are impossible to see and 
+    are extremely difficult to model using the SDSS ones. 
+    Before one can reliably investigate topics such as the environment dependence 
+    of mass--size relation and its redshift evolution, impacts from crucial systematics 
+    like the imaging qualities and model assumptions much be carefully addressed. 
+    Both shallow images and oversimplified model can lead to biased results 
+    (e.g. see Appendix~\ref{app:gama} for the issue with single-\ser{} model 
+    using SDSS images).
     }
@@
     At fixed \mtot{}, massive central galaxies in denser environments (higher \mhalo{}) 
-    have larger $R_{\mathrm{50}}$ comparing to ones in smaller haloes at fixed 
+    have larger $R_{\mathrm{50}}$ compared with ones in smaller haloes at fixed 
     \mtot{}. 
@@
     Compared to the mass--size relation, the \mtot{}--\minn{} relation is not plagued 
-    by the ambiguity of galaxy ``size'', and also enables a more straightforward 
+    by the ambiguity of galaxy `size', and it also enables a more straightforward 
     comparison with numerical simulations.
@@
     We find that there is an offset between the overall distributions of these two
-    samples and they follow distinct best-fit \mtot{}--\minn{} relations. 
+    samples and that they follow distinct best-fitting \mtot{}--\minn{} relations. 
     For \rbcg{} galaxies with \logmtot{}$>11.6$ we find:
@@
 
-    \noindent In the same range of \mtot{}, the best-fit relation for \nbcg{} is:
+    \noindent In the same range of \mtot{}, the best-fitting relation for \nbcg{} is:
 
@@
     These results also will not be altered when we replace the \minn{} with the stellar 
-    mass within a 5 or a 15 kpc aperture, or if \mtot{} is replaced with stellar mass 
-    within a 120 or a 150 kpc aperture.
+    mass within a 5- or 15-kpc aperture, or if \mtot{} is replaced with a stellar mass 
+    within a 120- or 150-kpc aperture.
 
     From Figure \ref{fig:scaling_relation} we can draw the same conclusions as in 
-    the previous section, namely that: 
-    at fixed \mtot{}, central galaxies in more massive haloes tend to have smaller 
+    the previous section, namely that 
+    at fixed \mtot{}, central galaxies in more massive haloes tend to have a smaller 
     fraction of stellar mass in their inner regions and higher \mstar{} in their outer
     stellar haloes. 
-    Meanwhile, at fixed \minn{}--a proxy for the \mstar{} of the ``in situ'' component,
-    central galaxies in more massive haloes tend to be more massive and display more 
-    prominent stellar haloes. 
-    \song{
-    The comparison of \mden{} profiles for \minn{}--matched samples may not directly
-    reflects the environment related processes as other physical mechanisms could 
+    Meanwhile, at fixed \minn{} -- a proxy for the \mstar{} of the `\textit{in situ}' 
+    component -- central galaxies in more massive haloes tend to be more massive and 
+    display more prominent stellar haloes. 
+    \song{
+    The comparison of \mden{} profiles for \minn{}-matched samples may not directly
+    reflect the environment-related processes because other physical mechanisms could 
     also change the inner \mden{} profiles and their \mtot{} could be quite different. 
-    But the combination of \mtot{} and \minn{} clearly suggests that information of
-    their dark matter haloes or environments is encoded within this simple 2--D plane. 
-    We will discuss more scientific implications of these results in 
+    But the combination of \mtot{} and \minn{} clearly suggests that information about
+    their dark matter haloes or environments is encoded within this simple 2-D plane. 
+    We discuss more scientific implications of these results in 
     \S~\ref{sec:discussion}
@@
       \caption{
-          Radial variations in ellipticity and optical colors for massive galaxies. 
+          Radial variations in ellipticity and optical colours for massive galaxies. 
           The format of this figure is similar to the right hand side of 
@@
           large samples of luminous red galaxies in SDSS at $z{\sim} 0.4$ 
-          (solid blue line on top panel). 
-          We also compare with the results from a stacking analysis of nearby massive 
-          galaxies with high concentration index ($C>2.6$) in 
-          \citet[][blue dash lines on the top and middle panels]{DSouza2014}. 
-          Finally, we also compare with the average $g-r$ and $g-i$ color profiles 
+          (solid blue line on top panels). 
+          We also compare our results with those from a stacking analysis of nearby 
+          massive galaxies with high concentration indices ($C>2.6$) in 
+          \citet[][blue dashed lines on the top and middle panels]{DSouza2014}. 
+          We also compare our results with the average $g-r$ and $g-i$ colour profiles 
           from a large sample of nearby elliptical galaxies in \citet[][blue, solid 
@@
 %% ------------------------------------------------------------------------------------ %% 
-\subsection{Ellipticity and Color Profiles}
+\subsection{Ellipticity and Colour Profiles}
     \label{ssec:ell_color}
@@
     In Paper~I, we show that the ellipticity of the outer stellar halo increases with
-    \mtot{}, while in contrast, rest--frame color gradients do not display strong 
-    \mtot{}-dependencies. 
-    In this paper, we take this analysis one step further to investigate whether or 
-    not either of these quantities display a halo mass dependency. 
-    We focus on ellipticity and color profiles within 5--60 kpc where we can ignore
+    \mtot{}, while in contrast, rest-frame colour gradients do not display strong 
+    \mtot{} dependencies. 
+    In this paper, we take this analysis one step further to investigate whether either 
+    of these quantities display a halo mass dependency. 
+    We focus on ellipticity and colour profiles within 5--60 kpc where we can ignore
     differences in sky subtraction and seeing across different filters. 
-    Galactic extinction and $k$-corrections are applied to both $(g-r)$ and $(g-i)$ 
-    color profiles.
-
-    Figure \ref{fig:ell_color} shows the average ellipticity, $g-r$, and $g-i$ color 
-    profiles for galaxies living in more and less massive dark matter haloes both at 
-    fixed \mtot{} and at fixed \minn{}. 
+    Galactic extinction and $k$ corrections are applied to both $(g-r)$ and $(g-i)$ 
+    colour profiles.
+
+    Figure \ref{fig:ell_color} shows the average ellipticity, $g-r$, and $g-i$ colour 
+    profiles for galaxies living in more and less massive dark matter haloes at both 
+    fixed \mtot{} and fixed \minn{}. 
     We also compared our results with previous studies that are based on stacked SDSS 
@@
             average ellipticity than the \nbcg{} ones at $R > 10$ kpc. 
-            On the other hand, the average ellipticity in the inner region are very 
+            On the other hand, the average ellipticity in the inner region is very 
             similar. 
@@
         \item Massive central galaxies in more and less massive dark matter haloes 
-            display similar rest--frame color gradients (at $r<60$ kpc) at fixed 
+            display similar rest-frame colour gradients (at $r<60$ kpc) at fixed 
             \mtot{} and at fixed  \minn{}.
@@
     shape to extract 1-D \mden{} profiles of massive galaxies. 
-    The similarity of average rest-frame color profiles between the \rbcg{} and \nbcg{}
+    The similarity of average rest-frame colour profiles between the \rbcg{} and \nbcg{}
     samples suggests that \mden{} profiles based on single average \m2l{} will not bias 
@@
     At the same time, we are not certain that similar conclusions apply to the 
-    color or ellipticity profiles within the inner 5--6 kpc due to the smearing effect
+    colour or ellipticity profiles within the inner 5--6 kpc due to the smearing effect
     of the seeing. 
-    Central color gradients may be sensitive to other physical processes and deserves 
-    future investigation using 2-D modelling method and/or image with higher spatial 
+    Central colour gradients may be sensitive to other physical processes and deserve 
+    future investigation using a 2-D modelling method and/or images with higher spatial 
     resolution.
@@
     At fixed \mtot{} or \minn{}, we find that the central galaxies from more massive 
-    haloes on average have larger half--light radius and host more prominent outer 
+    haloes on average have a larger half-light radius and host more prominent outer 
     stellar haloes.
@@
     \song{
-    The two--phase formation scenario can qualitatively explain these results. 
-    Under this picture, intense dissipative processes at $z > 2$ are 
+    The two-phase formation scenario can qualitatively explain these results. 
+    In this case, intense dissipative processes at $z > 2$ are 
     responsible for the formation of \textit{in situ} stars in massive central 
     galaxies. 
-    After the star-formation was rapidly quenched by certain mechanism, the 
-    assembly of massive galaxies in the second phase is dominated by accretion 
-    of satellite galaxies through (mostly) non-dissipative mergers. 
+    After the star-formation was rapidly quenched by some mechanisms (e.g., AGN 
+    feedback), the assembly of massive galaxies in the second phase is dominated 
+    by accretion of satellite galaxies through (mostly) nondissipative mergers. 
     Dry minor mergers are efficient at depositing \textit{ex situ} stars in the 
     outskirts of massive galaxies (e.g. \citealt{Oogi2013, Bedorf2013}). 
-    If minor mergers become more frequent in more massive dark matter halos, 
+    If minor mergers become more frequent in more massive dark matter haloes, 
     they can result in slightly different stellar mass distributions and larger 
-    effective radius for their massive central galaxies.
+    effective radii for their massive central galaxies.
     }
@@
     Although the major-merger rate does not strongly depend on halo mass 
-    (mass ratio $>1$:3; e.g. \citealt{Hirschmann2013, Shankar2015}), minor 
-    merger rate could still increase with halo mass if the dynamical friction time 
+    (mass ratio $>1$:3; e.g. \citealt{Hirschmann2013, Shankar2015}), the minor--merger 
+    rate could still increase with halo mass if the dynamical friction time 
     is short (e.g. \citealt{Newman2012}). 
@@
     haloes (\logmh{}$>14.0$) can have up to four times more minor mergers (1:100--1:3)
-    compared to the ones in less massive haloes at similar stellar mass. 
-    Such increase in the minor-merger rate as a function of halo mass leads to a 
-    halo-mass dependence in the mass-size relation. 
+    compared to the ones in less massive haloes at a similar stellar mass. 
+    Such an increase in the minor-merger rate as a function of halo mass leads to a 
+    halo-mass dependence in the mass--size relation. 
     }
@@
     variations with halo mass. 
-    At the same time, we should point out that comparison at low redshift alone 
-    can not rule out some other scenarios.  
+    At the same time, we should point out that the comparison at low redshift alone 
+    cannot rule out some other scenarios.  
     For instance, \citet{Buchan2016} suggests that central galaxies in more massive 
-    haloes could born with more extended structure. 
-    More careful comparisons at higher redshift should help clarify these situations
-    although recent observations of massive central galaxies of $z>2$ proto--clusters 
+    haloes could be born with more extended structures. 
+    More careful comparisons at higher redshift should help clarify these situations,
+    although recent observations of massive central galaxies of $z>2$ proto-clusters 
     seem to confirm their compact nature (e.g. \citealt{Kubo2017}).
@@
     At the same time, from the comparison of median \mden{} profiles of the 
-    \mtot{}--matched samples and from the \mtot{}--\minn{} plane, our results also 
+    \mtot{}-matched samples and from the \mtot{}--\minn{} plane, our results also 
     show that the centrals of more massive haloes have slightly shallower inner 
-    \mden{} slope and lower fraction of \mtot{} within the inner 10 kpc.
-    \song{
-    This can not be solely explained by the choice of a finite aperture to 
-    estimate ``total'' \mstar{}: assuming that centrals from more massive haloes 
-    have more extended \mden{} profiles, integration out to larger aperture will 
+    \mden{} slope and a lower fraction of \mtot{} within the inner 10 kpc.
+    \song{
+    This cannot be solely explained by the choice of a finite aperture to 
+    estimate `total' \mstar{}: Assuming that centrals from more massive haloes 
+    have more extended \mden{} profiles, integration out to a larger aperture will 
     make the differences between \rbcg{} and \nbcg{} galaxies on the \mtot{}--\minn{} 
@@
     distributions at the center of massive ETGs also depend on environment. 
-    Many different physicals processes can shape and alter \mden{} profile within 
-    inner 10 kpc, and several of them are not clearly controlled by environment.
+    Many different physical processes can shape and alter the \mden{} profile within 
+    the inner 10 kpc, and several of them are not clearly controlled by environment.
     This is particularly important since progenitors of the massive ETGs in this 
-    work may have higher central \mden{} in the past (e.g., \citealt{Szomoru2012}).
-    } 
-    Major merger can redistribute the inner stellar mass distributions, but major
-    merger rate does not strongly depend on halo mass (e.g., \citealt{Shankar2014}). 
+    work may have had a higher central \mden{} in the past
+    (e.g. \citealt{Szomoru2012}).
+    } 
+    Major merger can redistribute the inner stellar mass distributions, but 
+    major--merger rate does not strongly depend on halo mass 
+    (e.g. \citealt{Shankar2014}). 
     Although recent simulations tend to emphasize the contribution of dry minor 
@@
     (e.g. \citealt{BoylanKolchin2007}). 
-    Depending on the structure and infalling orbit of the satellite, minor merger 
+    Depending on the structure and infalling orbit of the satellite, a minor merger 
     can make the inner \mden{} profiles either steeper or shallower.  
-    Interestingly, these authors find, when satellite is accreted from a highly 
-    eccentric and energetic orbit to a core--elliptical galaxy, it tends to reduce 
-    the central \mden{}.  
-    This is relevant here as many massive ETGs are known to be core--elliptical 
+    Interestingly, \citet{BoylanKolchin2007} find that when a satellite is accreted 
+    from a highly eccentric and energetic orbit to a core--elliptical galaxy, the 
+    process tends to reduce the central \mden{}.  
+    This is relevant here, as many massive ETGs are known to be core--elliptical 
     galaxies. 
@@
     profile.
-    When the induced mass--loss is efficient enough, it can lead to expanded 
+    When the induced mass loss is efficient enough, it can lead to expanded 
     central stellar mass distribution and can lower the inner \mden{} significantly. 
     } 
-    In addition, at smaller scale, the coalesce of super-massive black hoes (SMBHs)  
-    can flatten the central \mden{} profile via efficient scattering effect 
-    (e.g. \citealt{Milosavljevi2002}).
+    In addition, at a smaller scale, the coalescence of super-massive black holes 
+    (SMBHs) can flatten the central \mden{} profile via an efficient scattering 
+    effect (e.g. \citealt{Milosavljevi2002}).
     On the right side of Fig \ref{fig:scaling_relation}, we find a few \rbcg{} 
-    galaxies with very low \minn{} at high \mtot{} end that are apparently not bothered 
-    by problematic photometry or exceptionally bad seeing.  
-    They may be similar to the recently discovered massive BCGs with very large 
-    depleted cores (a few kpc; e.g. \citealt{Postman2012, LopezCruz2014, Thomas2016,
-    Bonfini2016}) resulting from SMBH mergers.
+    galaxies with very low \minn{} at the high \mtot{} end that are apparently not 
+    bothered by problematic photometry or exceptionally bad seeing.  
+    They may be similar to the recently discovered massive brightest cluster galaxies 
+    (BCGs) with very large depleted cores (a few thousand parsecs; e.g. 
+    \citealt{Postman2012, LopezCruz2014, Thomas2016, Bonfini2016}) resulting from 
+    SMBH mergers.
 
@@
     on \mhalo{} are important issues that deserve further investigation.  
-    2-D modelling after considering the PSF--convolution and images with higher 
-    spatial resolution will help us connect the central mass distribution with 
-    results of this work. 
-    And comparisons of the \mden{} profiles with massive galaxies in simulation can 
-    help us evaluate the relative importance of these processes.
+    2-D modelling after considering the point spread function (PSF) convolution and 
+    images with higher spatial resolution will help us connect the central mass 
+    distribution with results of this work; and comparisons of the \mden{} profiles 
+    with massive galaxies in simulation can help us evaluate the relative importance 
+    of these processes.
     }
@@
 
-    Many previous works that focused on the mass-size relation found this relation 
+    Many previous works that focused on the mass--size relation found this relation 
     is independent of halo mass or environment at $z\sim 0.0$ 
@@
     In Appendix~\ref{app:gama}, we use the \rbcg{} and \nbcg{} galaxies that overlap 
-    with the GAMA survey to briefly demonstrate this point. 
+    with the Galaxy And Mass Assembly (GAMA) survey to briefly demonstrate this point. 
     We show that, for galaxies with similar \mstar{} derived from single-\ser{} 
     models using shallower SDSS images (\citealt{Kelvin2012}), the ones in more 
-    massive dark matter haloes actually show more prominent outer stellar haloes, 
-    hence both of their stellar mass and effective radius are underestimated.  
-    This shows again that the deeper HSC images has unique advantage in studying 
-    the connection between the assembly of massive galaxies and their dark matter 
-    haloes.
+    massive dark matter haloes actually show more prominent outer stellar haloes; 
+    hence, both their stellar mass and effective radius are underestimated.  
+    This shows again that the deeper HSC images give a significant advantage in 
+    studying the connection between the assembly of massive galaxies and their dark 
+    matter haloes.
 
@@
     \citet{Kuchner2017} uses one massive cluster at $z=0.44$ to show that ETGs in 
-    that cluster has larger size than the ones in the `field'. 
-    }
-    \citet{Yoon2017} present a careful study of a large sample of $z\sim0.1$ SDSS ETGs 
-    using a non-parametric method and recover a clear environment dependence of 
-    mass-size relation at \logms{}$>11.2$. 
+    that cluster have larger sizes than ETGs in the `field'. 
+    }
+    \citet{Yoon2017} present a careful study of a large sample of $z\sim0.1$ SDSS 
+    ETGs using a nonparametric method; in their research, they recover a clear 
+    environment dependence of mass--size relation at \logms{}$>11.2$. 
     They conclude that, at the same \mstar{}, massive ETGs from dense environment 
-    are 20--40\% larger compared to those in underdense environment.
-    Recently, \citet{Charlton2017} uses single-\ser{} model for galaxies at 
-    $0.2 < z < 0.8$ in the CFHTLenS (\citealt{Heymans2012}) and their galaxy--galaxy 
+    are 20--40\% larger compared to those in an underdense environment.
+    Recently, \citet{Charlton2017} use a single-\ser{} model for galaxies at 
+    $0.2 < z < 0.8$ in the Canada France Hawaii Lensing Survey (CFHTLenS) 
+    (\citealt{Heymans2012}) and their galaxy--galaxy 
     lensing measurements to show that larger galaxies tend to live in more massive 
@@
     \song{
-    With the help of weak lensing measurements using HSC images, we will further 
-    explore the connection between the dark matter halo mass and the stellar mass 
-    distributions of their central galaxies. 
-    }
-
-    While there appears to be an emerging consensus at low redshift now that the 
-    high--mass end of the mass-size relation does vary with halo mass, the situation 
+    With the help of weak lensing measurements using HSC images, we will in future 
+    work further explore the connection between the dark matter halo mass and the 
+    stellar mass distributions of their central galaxies. 
+    }
+
+    While there appears to be an emerging consensus that at low redshift the 
+    high-mass end of the mass--size relation does vary with halo mass, the situation 
     at higher redshift is more complicated. 
@@
     environment dependence of size at fixed \mstar{} for either ETGs or quiescent 
-    galaxies (30--50\% larger in denser environment).
-    If true, this could indicate that galaxy evolution at high redshift 
-    ($z>2$) is accelerated in denser regions (e.g., proto--clusters; see 
-    \citealt{Wang2016, Shimakawa2018}), while the size evolution of massive 
-    galaxies in richer environment could slow down (e.g., \citealt{Papovich2012, 
-    Andreon2016}.
+    galaxies (30--50\% larger in denser environments).
+    As shown in \citet{HCompany13} using a Monte Carlo test (see their \S~4.2), 
+    when the uncertainties of mass and size are considered, the size difference at 
+    fixed stellar mass could be even more significant between extremely different
+    environments.
+    If true, it indicates that denser regions at high redshift ($z>2$) could accelerate 
+    galaxy evolution (e.g. proto-clusters; see \citealt{Wang2016, Shimakawa2018}), and 
+    the size evolution of massive galaxies in a richer environment gradually slows down
+    toward lower redshift (e.g., \citealt{Papovich2012, Andreon2016}.
     }
@@
     \song{
-    Comparisons with works at high redshift are complicated by many issues. 
+    Comparisons of our results with work done at high redshift are complicated by many 
+    issues. 
     At high-$z$, these works often rely on small samples or special environments 
@@
     Progenitors of massive galaxies in this work may still be star-forming or 
-    late--type galaxies at $z>1$. 
-    And finally, it is just intrinsically more difficult to accurately measure 
+    late-type galaxies at $z>1$. 
+    Finally, it is just intrinsically more difficult to accurately measure 
     \mstar{} and size at high redshift (e.g. \citealt{Price2017}).
     It would be interesting to see whether the current simulations can reproduce 
-    these observed environment dependence and use them to investigate the redshift
+    these observed environment dependencies and use them to investigate the redshift
     evolution of such dependence. 
@@
     profiles (e.g. \citealt{Szomoru2012, Patel2013, Buitrago2017, Hill2017}) could be 
-    a better approach to compare high- and low-$z$ massive galaxies than the 
-    mass--size relation.
+    a better approach than the 
+    mass--size relation to compare high- and low-$z$ mass galaxies.
     }
@@
 
-    Until recently, semi-analytic models and hydrodynamic simulations still have 
+    Until recently, semi-analytic models and hydrodynamic simulations have had
     difficulty reproducing the mass--size relation of massive galaxies. 
     Galaxy sizes are sensitive to many different physical processes (star-formation, 
-    feedback, mergers) and matching the galaxy stellar-mass function does not 
-    automatically guarantee a match to the mass-size relation. 
+    feedback, mergers), and matching the galaxy stellar-mass function does not 
+    automatically guarantee a match to the mass--size relation. 
     Furthermore, while some efforts have been made to use consistent size definitions 
-    (\citealt{McCarthy2017}), more often than not, comparisons of the mass-size relation 
-    do not use consistent size definitions, or only perform crude size conversions 
-    (e.g. 3--D radius in simulation versus 2--D projected radius in observation; 
+    (\citealt{McCarthy2017}), more often than not, comparisons of the mass--size relation 
+    do not use consistent size definitions, or they only perform crude size conversions 
+    (e.g. 3-D radius in simulation versus 2-D projected radius in observation; 
     \citealt{Genel2017}). 
-    Observers often quote ``sizes'' corresponding to the half--light radius along the 
-    major axis using 2--D projected images. 
-    Simulations on the other hand, often employ sizes that correspond to the 3--D 
-    aperture half--mass radius (e.g. \citealt{Price2017}).
-
-    As emphasized earlier, definitions of galaxy ``size'' in observations are also not 
+    Observers often quote `sizes' corresponding to the half-light radius along the 
+    major axis using 2-D projected images. 
+    Simulations, on the other hand, often employ sizes that correspond to the 3-D 
+    aperture half-mass radius (e.g. \citealt{Price2017}).
+
+    As emphasized earlier, definitions of galaxy `size' in observations are also not 
     always consistent. 
-    Measurement of ``size'' often shows dependence on image quality (e.g. seeing, 
+    Measurement of `size' often shows dependence on image quality (e.g. seeing, 
     imaging depth), filter, and the adopted method. 
-    Although the elliptical single--\ser{} model is widely adopted in measuring the 
+    Although the elliptical single-\ser{} model is widely adopted in measuring the 
     size of galaxies of different types and at different redshifts, it sometimes leads
-    to biased results as it is no longer appropriate model for certain types of galaxy. 
-    Size derived from 1-D curve--of--growth is more model independent and has been 
+    to biased results as it is no longer an appropriate model for certain types of galaxies. 
+    Size derived from a 1-D curve-of-growth is more model independent and has been 
     shown to be useful in revealing environmental dependence of the mass--size relation 
     (e.g. \citealt{Yoon2017} and this work), but it does not take the PSF convolution 
-    effect into account and depends on imaging depth and background subtraction.
+    effect into account, and it depends on imaging depth and background subtraction.
 
@@
     In follow-up work, we will present comparisons between our observations and 
-    predictions from hydrodynamic simulations using the using the \mtot{}--\minn{} 
+    predictions from hydrodynamic simulations using the \mtot{}--\minn{} 
     plane instead of the mass--size relation.
@@
     halo mass (\mhalo{}$\simgt 10^{14.2} M_{\odot}$ and 
-    \mhalo{}$\simlt 10^{14} M_{\odot}$), and study how their stellar mass distributions 
+    \mhalo{}$\simlt 10^{14} M_{\odot}$), and we study how their stellar mass distributions 
     out to 100 kpc depend on their environments (or \mhalo{}). 
-    The main results are:
+    The main results are as follows:
 
@@
             profiles that have large intrinsic scatter in the outer stellar haloes and 
-            present subtle but systematic trend with \mhalo{}.
+            present a subtle but systematic trend with \mhalo{}.
             On average, massive central galaxies in more massive haloes have slightly 
@@
             This suggests that the environment affects the assembly of massive central
-            galaxies at fixed ``total'' stellar mass.
+            galaxies at fixed `total' stellar mass.
 
@@
             possess much more extended stellar haloes than the ones in smaller haloes, 
-            despite their median \mden{} profiles at $R < 15$ kpc are very similar. 
-            Assuming that \minn{} traces the amount of ``in situ'' stars in massive
-            galaxies, this result is consistent with the picture that more massive 
-            haloes favor the growth of extended stellar haloes in their central 
+            despite their median \mden{} profiles at $R < 15$ kpc being very similar. 
+            Assuming that \minn{} traces the amount of `\textit{in situ}' stars in 
+            massive galaxies, this result is consistent with the picture that more 
+            massive haloes favor the growth of extended stellar haloes in their central 
             galaxies through more frequent mergers.
@@
         \item We also find that massive central galaxies in different environments
-            follow different relations between their \mtot{} and \minn{}. 
-            Assuming that \mtot{} is a reasonable proxy of ``total'' stellar mass and 
+            follow different relationships between their \mtot{} and \minn{}. 
+            Assuming that \mtot{} is a reasonable proxy for `total' stellar mass and 
             \minn{} reflects the amount of \textit{in situ} stars, we propose that 
             this relation can help diagnose the assembly of massive central galaxies 
-            without using ``size'' with ambiguous definition.
+            without using `size' with ambiguous definition.
 
@@
             do not display strong environment dependence at $R < 60$ kpc. 
-            At fixed \minn{}, the more extended stellar haloes presented in the \rbcg{}
+            At fixed \minn{}, the more extended stellar haloes present in the \rbcg{}
             galaxies also show higher ellipticity than the \nbcg{} galaxies.
 
-        \item We do not find evidence that suggests the rest-frame color profiles 
-            within 60 kpc depend on environment for either the \mtot{}- nor 
-            \minn{}--matched samples.
+        \item We do not find evidence that suggests the rest-frame colour profiles 
+            within 60 kpc depend on environment for either the \mtot{}- or 
+            \minn{}-matched samples.
 
@@
   % Personal 
-  The authors thank Frank van~den~Bosch for insightful discussions and thank 
+  The authors thank Frank van~den~Bosch for insightful discussions and 
   Shun Saito for helping us estimate the fraction of satellite galaxies in our sample.
@@
   Japan and Taiwan, and Princeton University.  The HSC instrumentation and software were
-  developed by the National Astronomical Observatory of Japan (NAOJ), the Kavli Institute
-  for the Physics and Mathematics of the Universe (Kavli IPMU), the University of Tokyo,
-  the High Energy Accelerator Research Organization (KEK), the Academia Sinica Institute
+  developed by National Astronomical Observatory of Japan (NAOJ), Kavli Institute
+  for the Physics and Mathematics of the Universe (Kavli IPMU), University of Tokyo,
+  High Energy Accelerator Research Organization (KEK), Academia Sinica Institute
   for Astronomy and Astrophysics in Taiwan (ASIAA), and Princeton University.  
-  Funding was contributed by the FIRST program from Japanese Cabinet Office, the Ministry 
-  of Education, Culture, Sports, Science and Technology (MEXT), the Japan Society for 
-  the Promotion of Science (JSPS), Japan Science and Technology Agency (JST), the
-  Toray Science Foundation, NAOJ, Kavli IPMU, KEK, ASIAA, and Princeton University.
+  Funding was contributed by the FIRST program from Japanese Cabinet Office,  Ministry 
+  of Education, Culture, Sports, Science and Technology (MEXT), Japan Society for 
+  the Promotion of Science (JSPS), Japan Science and Technology Agency (JST), Toray 
+  Science Foundation, NAOJ, Kavli IPMU, KEK, ASIAA, and Princeton University.
 
   % SDSS part
-  Funding for SDSS-III has been provided by the Alfred P. Sloan Foundation, the
-  Participating Institutions, the National Science Foundation, and the U.S.  Department of
-  Energy. The SDSS-III web site is http://www.sdss3.org.  SDSS-III is managed by the
+  Funding for SDSS-III has been provided by Alfred P. Sloan Foundation, the 
+  Participating Institutions, National Science Foundation, and U.S. Department of
+  Energy. The SDSS-III website is http://www.sdss3.org.  SDSS-III is managed by the
   Astrophysical Research Consortium for the Participating Institutions of the SDSS-III
-  Collaboration including the University of Arizona, the Brazilian Participation Group,
+  Collaboration, including University of Arizona, the Brazilian Participation Group,
   Brookhaven National Laboratory, University of Cambridge, University of Florida, the
-  French Participation Group, the German Participation Group, the Instituto de Astrofisica
+  French Participation Group, the German Participation Group, Instituto de Astrofisica
   de Canarias, the Michigan State/Notre Dame/JINA Participation Group, Johns Hopkins
@@
   % Pan-STARRS1 part
-  The Pan-STARRS1 Surveys (PS1) have been made possible through contributions of the 
-  Institute for Astronomy, the University of Hawaii, the Pan-STARRS Project Office, 
-  the Max-Planck Society and its participating institutes, the Max Planck Institute 
-  for Astronomy, Heidelberg and the Max Planck Institute for Extraterrestrial Physics, 
-  Garching, The Johns Hopkins University, Durham University, the University of Edinburgh, 
-  Queen's University Belfast, the Harvard-Smithsonian Center for Astrophysics, the Las 
-  Cumbres Observatory Global Telescope Network Incorporated, the National Central 
-  University of Taiwan, the Space Telescope Science Institute, the National Aeronautics 
+  The Pan-STARRS1 surveys (PS1) have been made possible through contributions of  
+  Institute for Astronomy; University of Hawaii; the Pan-STARRS Project Office; 
+  the Max-Planck Society and its participating institutes: the Max Planck Institute 
+  for Astronomy, Heidelberg, and the Max Planck Institute for Extraterrestrial Physics, 
+  Garching; Johns Hopkins University; Durham University; University of Edinburgh; 
+  Queen's University Belfast; Harvard-Smithsonian Center for Astrophysics; Las 
+  Cumbres Observatory Global Telescope Network Incorporated; National Central 
+  University of Taiwan; Space Telescope Science Institute; National Aeronautics 
   and Space Administration under Grant No. NNX08AR22G issued through the Planetary 
-  Science Division of the NASA Science Mission Directorate, the National Science 
-  Foundation under Grant No. AST-1238877, the University of Maryland, and Eotvos 
-  Lorand University (ELTE).
+  Science Division of the NASA Science Mission Directorate; National Science 
+  Foundation under Grant No. AST-1238877; University of Maryland, and Eotvos 
+  Lorand University.
 
@@
   This paper makes use of software developed for the Large Synoptic Survey 
-  Telescope. We thank the LSST Project for making their code available as free 
+  Telescope. We thank the LSST project for making their code available as free 
   software at http://dm.lsstcorp.org.
@@
       \texttt{STSCI\_PYTHON} is a product of the Space Telescope Science Institute, 
-      which is operated by AURA for NASA;
+      which is operated by Association of Universities for Research 
+      in Astronomy (AURA) for NASA;
   \href{http://www.scipy.org/}{\texttt{SciPy}},
-      an open source scientific tools for Python (\citealt{SciPy});
+      an open source scientific tool for Python (\citealt{SciPy});
   \href{http://www.numpy.org/}{\texttt{NumPy}}, 
@@
   \href{https://jiffyclub.github.io/palettable/}{\texttt{palettable}},
-      color palettes for Python;
+      colour palettes for Python;
   \href{http://dan.iel.fm/emcee/current/}{\texttt{emcee}}, 
@@
       \caption{
-          \textbf{Top-left}: The \logms{}-$g-r$ color relation of the \rbcg{} 
+          \textbf{Top-left}: The \logms{}-$g-r$ colour relation of the \rbcg{} 
           (red circle) and \nbcg{} (grey dots) samples.
-          We apply the $k$-corrections from \texttt{iSEDFit} fitting to the colors.~~          
+          We apply the $k$-corrections from \texttt{iSEDFit} fitting to the colours.~~          
           \textbf{Top-right}: the histograms of the redshift for the \rbcg{} and 
@@
 
-    On the top-left panel of Fig~\ref{fig:sample_stats}, we show the \mtot{}-color 
-    relations using the $k$-corrected $g-r$ color. 
-    Both samples follow the same tight ``red-sequence'' with little contamination 
-    from the ``blue cloud''.
-    At fixed \mtot{}, we see little offset in color distributions of the two 
+    On the top-left panel of Fig~\ref{fig:sample_stats}, we show the \mtot{}-colour 
+    relations using the $k$-corrected $g-r$ colour. 
+    Both samples follow the same tight `red-sequence' with little contamination 
+    from the `blue cloud'.
+    At fixed \mtot{}, we see little offset in colour distributions of the two 
     samples, suggesting that both samples consist of quiescent galaxies with 
@@
         We show the individual profile in the background using much thinner line, 
-        and highlight the median profiles using thicker line and darker color.
+        and highlight the median profiles using thicker line and darker colour.
         }
@@
         whose size reflects the $P_{\mathrm{Cen}}$ value.  
-        We also color-code them using the richness ($\lambda$) of the host cluster. 
-        The matched \nbcg{} galaxies are highlighted using darker color and bigger dots. 
+        We also colour-code them using the richness ($\lambda$) of the host cluster. 
+        The matched \nbcg{} galaxies are highlighted using darker colour and bigger dots. 
         To further evaluate the matching results, we show the distributions of \mtot{} 
         (middle panel) and redshift (bottom panel) separately. 
-        On both panesl, we show the histograms along with their kernel density 
+        On both panels, we show the histograms along with their kernel density 
         distributions.  
@@
         The formats are in consistent with the right figure of Fig~\ref{fig:prof_1}.
-        The differences are, here, the samples are matched in slightly differnt ways. 
+        The differences are, here, the samples are matched in slightly different ways. 
         From left to right: a) using samples at lower redshift ($0.3 < z < 0.4$); 
@@
             uncertainty of background subtraction and contamination from nearby 
-            bright objects, but they can serve as different estimates of the ``total''
+            bright objects, but they can serve as different estimates of the `total'
             \mstar{} of these galaxies.
@@
             This excludes the \nbcg{} galaxies that are much less massive and 
-            more ``compact'' in structure. 
+            more `compact' in structure. 
             Yet, the results regarding the structural differences remain the same.
@@
 
-	    \item ``Curve--of--growth'' of stellar mass--the cumulative \logms{} profiles
+	    \item `Curve-of-growth' of stellar mass -- the cumulative \logms{} profiles
 	        (upper panel).

### 2017-11-28 draft/response_paper_II.md
Updated response to referee report of Paper II

# Response to Referee Report of Paper II

We are very grateful for the positive referee report and many useful comments from the referee.  We have modified the draft accordingly and have highlighted all the modifications in cyan.

Here we will also address each of the referee's questions in details.

## MODERATE COMMENTS

> 1. First off, a difference of ~20\% is not very large, although a larger difference might be hidden by observational errors in stellar masses, halo masses, and sizes. Some Monte Carlo analysis+discussion on this point should be included (see also point 3 below). Would the Authors expect an intrinsically larger size difference? This is important for models. Although a 20\% systematic difference is predicted by basic hierarchical models (e.g., Shankar et al. 2015), a larger difference of up to a factor of 3 in sizes may be expected if models include processes such as gas dissipation and significant disc instabilities (e.g., Shankar et al. 2014).

The referee is correct that the difference in effective radius is not **very** significant. For the M_100kpc matched samples, we use bootstrap resampling method to see the uncertainties of the average size.  As for the mass-size relation, we use MCMC-Bayesian to fit the relation after considering the uncertainties of both mass and size.  As we show on the figure, the 1-sigma uncertainty regions of the mass-size relations for two samples slightly overlap.

At the same time, we want to emphasize that we consider the direct comparison of mass density profiles (which is the more important results for this work as we can directly map the mass distribution out to >100 kpc) a more reliable and straightforward way to reveal environmental difference.  We also use resampling method and statistical tests to prove that the subtle differences from the comparisons of mass density profiles are robust and significant.  The stellar mass distributions of massive galaxies do depend on halo mass based on our results, although it does not guarantee a very significant difference on the mass-size plane. This is likely because the environment-dependence of mass density profile becomes more significant in the low-density outer halo, but the value of effective radius is not very sensitive to such region.

We do not have any expectation for the size difference at fixed stellar mass.  The comparison of mass density profile seems to show that, although the environment-dependence is significant, environment (or halo mass) still does not play the most crucial role in shaping these massive galaxies.  As for mass-size relation, within the 1-sigma uncertainties allowed by our fitting results, the maximum size difference is still not as significant as predicted by some of the models.

We do appreciate the referee to draw our attention to the Monte-Carlo tests in Huertas-Company+2013. We now mention this critical point in the text.

> 2. When plotting R50 vs Mstar one should also keep in mind that because of the steepness of this relation, any secondary binning (e.g., per Mhalo) may artificially induce spurious differences. A good way to handle this is to follow the procedure by Newman+12 and Huertas-Company+13 who proposed to weigh each size by its median value for its stellar mass ("gamma"). By simply plotting data in this way, gamma vs Mstar or gamma/<gamma> vs Mstar/Mhalo, may erase part of the apparent discrepancy in the R50 vs Mstar plane. It would be nice to see a plot of gamma vs Mhalo, at say fixed M100kpc, if possible...

We thank the referee for the useful suggestion and expand the relevant section to address these issues.  
1) We compare the average differences for the stellar mass and redshift matched samples, and confirm the ~20% size difference.  The mass-matched samples can help handle this issue. 
2) We adopt the definition of gamma in Huertas-Company+13 and estimate the normalized sizes for the two samples using their best-fit slopes of the mass-size relations.  The median gamma for $>10^{14.2}M_{\odot}$ and $<10^{14.0}M_{\odot}$ samples are $4.2\pm0.4$ and $3.8\pm0.3$.  Although the uncertainties are still quite large, it also confirms the result. 
3) Also, we would like to mention that the direct comparison of mass density profiles also confirms the same conclusion.  We do not need to worry about the uncertainty of size there, and only need to consider the uncertainty of the mass-to-light ratio from SED fitting.

Unfortunately, we can only broadly group our sample into two halo mass bins, and we do not have the accurate estimate of the average halo mass for the sample of less massive haloes.  Therefore, it will not be very useful (and reliable) to put them on the figure proposed by the referee.  In the near future, we will use better group catalog and weak lensing measurements from HSC to further look into this relation. Furthermore, we are in the process of building a full forward model of the mass - size - halo mass relation which we are fitting to lensing results. This forward modeling approach has the advantage that it naturally accounts for the secondary binning issues brought up by the referee. Preliminary results from this forward fitting (including lensing) suggest that our results are robust to these effects,

> 3. I find the comparison in Figure 3 (left) with Huertas-Company et al. (2013; HC13) quite intriguing. The median relation by HC13 fits in well with the median relation found by the Authors in higher-mass haloes. If HC13 were missing a large portion of the extra light, I would expect, if anything, a lower median R50-Mstar relation. Besides, as the Authors also point out, HC13 is in good agreement with their results below Mstar~3e11 Msun. Also to note that the background should not be an issue here as Re in centrals and satellites appear similar in HC13 (see their Figure 2 and also Bernardi+17). I am thus not sure why there should be such a systematic difference only in galaxies above 3e11 Msun and in lower mass haloes. More discussion and analysis is needed here.

The referee is right that this is indeed an important point left out in our discussion.  We think that it relates to 1) the redshift difference (HC13 is at z<0.09; our sample has average redshift around 0.4); 2) the uncertainties in both mass and size measurements.  As suggested by the referee, now we include the mass-size relation at similar redshift from Huertas-Company+2013b to the figure, which clearly lies below our mass-size relation.  We would also like to point out that both the stellar mass and effective radius in Huertas-Company+2013 are based on single-Sersic model fitting on shallower SDSS images, which could lead to systematic differences or even bias (as discussed in our Appendix F using the GAMA sample).  It could mean the single-Sersic model on SDSS image could systematically underestimate the mass or overestimate the size (especially for galaxies with high Sersic indices).  This demonstrates the importance of systematics like the imaging depth and model assumption when it comes to the comparisons of mass-size relation.  It is possible that the HC13 result also slightly underestimates the size of z~0 galaxies.  It would be interesting to confirm this using HSC images.  This effort is complicated by issues like saturation on HSC images and over-subtracted background, and is beyond the scope of this work.

In tests which we did not include in the paper, we also fit single-Sersic models to the HSC images.  These models show larger size than the ones measured using 1-D profile for the same massive galaxies, and they often have a very high Sersic index. 
We do not include these results because, at the imaging depth of HSC, the single-Serisc model performs poorly for these galaxies.  We agree with the referee that this point deserves further investigation.  Currently, we are working with a new student to test the mass and size measurements for the same galaxies using different methods and different images.

> 4. HC13b also present results for higher-z galaxies, would it be possible to show some of these in the same Figure?!?  Finally, note that in section 4.2 HC13 state from results of a number of Monte Carlo tests that "...we should be able to detect any size difference greater than a factor of 1.4 between galaxies in extreme environments." This implies that errors could easily wash out a difference of 20\% in their data... All these points must be included in the discussion.

We agree with the referee that comparisons of mass-size relations at different redshifts can greatly help us look into the origin of any environment dependence. 
It is particularly intriguing since several past papers have found a stronger environment dependence of size at high redshift.  We discussed this in Section 4.3, and now we expand the discussion following the referee's suggestion.  We point out that, if these results are robust, it could mean that denser environment at high-redshift accelerate galaxy evolution.

As suggested by the referee, we now try to include the results from Huertas-Company+2013b into the comparison.  On the updated Fig 3, we show the mass-size relation of ETGs in group at 0.2<z<0.5 from Huertas-Company+2013b.  We also correct the systematic difference in stellar population model, and also convert the circulized effective radius into the measured ones after assuming an average b/a of 0.75.  And, regardless of these technical details, we find the Huertas-Company+2013b relation has a similar slope with our results, but shows systematic offset (smaller sizes). This may relate to the fact that the HST/ACS F814W images are much shallower than the HSC ones.  We did not include results from higher redshift, and we think the current figure already demonstrates our concerns for such comparisons:

1) Crucial systematics such as the imaging depth and modeling method must be carefully addressed before we can perform reliable comparison and look into the redshift evolution.  This is beyond the scope of this work. 
2) High redshift observations often use small sample or very special environment (e.g. single massive proto-cluster).
3) It is hard to know the evolutionary connections between the high-z samples and our ones.  Progenitors of our massive galaxies could be disc or star-forming galaxy. 
4) At high redshift, it is even more challenging to measure mass and size reliably.  
5) At the same time, there are also works that find no environment dependent on size for high redshift ETGs.

We think it is probably more straightforward to directly compare the surface brightness or mass density profiles between low- and high-redshift massive galaxies with an evolutionary connection (e.g., using the cumulative number density).  We did compare with stacked profiles of high-z galaxies from Patel+2013 in companion paper (Huang et al. 2016a), and we confirmed that the inner profile does not evolve a lot while the higher redshift galaxy has a steeper outer profile.  Also, we are performing careful comparisons with the massive galaxies in hydrodynamic simulations to see whether they can correctly reproduce the stellar mass distribution and the halo mass dependence.  If so, we will further look into the redshift evolution of the environment dependence using simulations and compare them with results in literature.

The important point based on the Monte Carlo tests now is also emphasized in our discussion.

> 5. I do not think that comparing exactly the same exact M(<10kpc) distributions is necessarily the best way to go to look for possible differences in evolutionary pathways induced by environment. For example, if on average massive galaxies at the centre of clusters are older and/or were born in deeper potential wells, I would expect their inner density distributions to be somewhat steeper at early stages during the cooling phase, or in fact maybe even flatter if at later epochs if and when additional effects such as (stronger?) AGN feedback and/or (more frequent?) SMBH mergers kick in. The situation is complex enough to warrant more investigation in this respect. One way to go could be to fit some Sersic profiles to the mu_star profiles and check whether the Sersic index distributions are different in different environments at fixed Mstar or Mhalo (see e.g. Figure 6 in HC13). Other ways may of course be possible and I leave it to the Authors to device additional routes for more test comparisons between galaxies in different environments. Of course similar comments apply to the comparisons in colour profiles.

We understand and agree on the point made by the referee that the relation between inner profile and the environment is not exactly clear.  We adjust several parts of the text to reflect this point.  And during the discussion in Section 4.2, we now admit that "it is still too early to conclude that the stellar mass distributions at the center of massive ETGs also depend on the environment."  We also briefly discuss the potential impacts of AGN feedback and SMBH merger of the inner mass distributions, although it is not entirely clear that they can affect the stellar mass within ten kpc.  For instance, the largest depleted-core in massive ETGs is still smaller than five kpc.

The reason we emphasize the usage of 10 kpc mass is that we propose to use it as a proxy of the mass formed in the in situ phase.  In our earlier work, we found this assumption is promising when compared with results with recent simulations.  Under the two-phase scenario, it is critical to discuss the assembly of the massive galaxy and the galaxy-halo connection via the angle of the in situ and ex situ components.  It is not an easy task as observational separation of these components is almost impossible.  We wish to use this simple assumption in this work as a starting point, which we are in the process of refining further.  We do see intriguing evidence of halo-mass dependence on the M_100kpc-M_10kpc plane and we are now investigating this using a weak lensing analysis.

As for the Sersic modeling method, we agree with the referee that it could be a useful approach.  As a matter of fact, we did try Serisc fitting to the HSC images of our massive galaxies.  However, at the imaging depth of HSC, we find that single Sersic is a terrible model for these galaxies.  It can not describe the changes of isophotal shape and slope of surface brightness profiles of our massive galaxies.  And the extended low surface brightness stellar haloes seen on the HSC images always drive the Sersic index to very high value, which tends to overestimate the mass in the inner region.  We think the more appropriate approach would be using more complicated or more physically motivated models for these galaxies.  Right now, we are working on this using both real and simulated (from the Illustris simulation) massive galaxies.

## MINOR COMMENTS

> 1. Per se, having more extended sizes/stellar haloes may not necessarily favour the merge hypothesis. One could also argue that galaxies in more massive haloes are simply born more extended (e.g., Buchan & Shankar 2016).

We thank the referee for drawing our attention to the Buchan & Shankar (2016) work.  It is an intriguing idea that the central galaxies of massive haloes could form in a more extreme fashion that leads to their large size.  We expand the discussion a little to include this theory and cite the recommended work.

We think that better observations of massive galaxies at high redshift could help constrain this picture better.  Right now, although there are works that find the significant environmental dependence of mass-size relation at z>1, we think it is still too early to draw any solid conclusion.  Massive central galaxy of high-z proto-cluster often also has very compact size (e.g., Kubo et al. 2017).  In the previous work of this series (Huang et al. 2017; arXiv:1707.01904), we compare our sample with a very massive cD galaxy at z~1 (Liu et al. 2011).  We find its outer profile is still too steep compared to our z~0.4 ones, suggesting latter assembly in the outskirt by minor mergers.

> 2. While reading the introduction I was unclear of how and why the two-phase scenario should be necessarily strictly related to the host halo masses. We know for a fact, for example, that the (unevolved) subhalo mass function is invariant with respect to the host halo mass, and the number of moderate-major mergers is also not a strong function of main progenitor halo mass (e.g., Shankar+15).

The referee is right that in many models and simulations, the moderate-major merger rate does not show a strong correlation with halo mass.  And it is probably too early to say that the frequency of mergers causes the environment dependence on size and structure.  We mentioned the "two-phase" scenario mostly because, in some state-of-art hydrodynamic simulations, the fraction of "ex-situ" or accreted stars around central galaxy increases with halo mass (e.g., see Fig 12 of Pillepich et al. 2017b using the most recent IllustrisTNG simulation).  It seems to suggest that mergers are more important to the mass assembly of central galaxies in more massive halos.  However, it is not entirely clear that mergers can lead to differences in stellar mass distribution at the same total stellar mass.  From simulations, there is evidence that suggests the frequency of minor merger depends on halo mass and could cause the environment dependence of size (e.g., Yoon et al. 2017, use the SAM by Guo et al. 2011).  We already briefly discuss this in Section 4.1 of our work, and acknowledge that this trend still relies on the assumption of the typical time scale for the minor merger).

We rewrite this section of introduction to be more objective and to reflect the point raised by the referee.  We also include Shankar et al. (2015) as citation now.

> 3. A few more words should be included on the methods adopted by Simet+16 and Diemer & Kravtsov15 without forcing the reader to go back to the original papers to get an idea of what these groups are doing...

We have now added more detailed explanations of both works as suggested by the referee.

In short, Simet et al. (2017) calibrate the mass-richness relation for the redMaPPer clusters using the SDSS weak lensing data after carefully addressing all relevant systematic uncertainties.  Diemer & Kravstov (2015) systematically investigates the mass density profiles of dark matter halos under Lambda-CDM cosmology using a suite of dark matter-only numerical simulations.  They provide empirical fitting functions for the relations among halo mass, radius, concentration, and redshift.  We use these functions to estimate the R200 for the haloes of the massive central galaxies in our sample.

> 4. The sentence in Section 2 "...and we can safely ignore structural evolution over our redshift range (~1.5 Gyr of time span)." sounds a little unclear and also out of place in this section presenting the data. Some rewording is required. It is true that models confirm that in this time span not much evolution is expected (e.g., Shankar+15). However, the authors should better emphasize that they do not expect any difference in size induced by environment/time effects in their sample, but this should be provided later on when presenting the results.

Our original intention is to suggest that there should be little size growth or structural evolution during the ~1.5 Gyr between redshift 0.3 and 0.5.  We think it would not be appropriate to look into the environment dependence of structure if we can not ignore the size growth of individual galaxy within the span of the redshift range.

The referee is right that this sentence is not very clear. We changed it into: "...And massive galaxies should experience little structural evolution and size growth between z=0.5 and 0.3 (~1.5 Gyr of time span) based on model prediction (e.g., Shankar et al. 2015)."

> 5. There are some typos around, e.g., "..this results is consistent...", "they also shows that...", etc...

We thank the referee for the careful reading and correct both of these typos.  We have also went through a more careful proof-reading process.

### 2017-11-30 draft/paper2_v8.tex
After editing by Alexie

--- 2017-11-28 draft/paper2_v7.tex
@@
-% Version 0; preprint format; Outline of paper II by Song Huang
-% Version 1; preprint format; Edited by Jenny Greene
-% Version 2; preprint format; Edited by Song Huang
-% Version 3; preprint format; Edited by Alexie Leauthaud
-% Version 4; preprint format; Edited by Song Huang
-% Version 5; preprint format; Edited by Jenny Greene and Song Huang
-% Version 6; preprint format; Edited by Susan Foster and Song Huang
+% Version 1; preprint format; Outline of paper II by Song Huang
+% Version 2; preprint format; Edited by Jenny Greene
+% Version 3; preprint format; Edited by Song Huang
+% Version 4; preprint format; Edited by Alexie Leauthaud
+% Version 5; preprint format; Edited by Song Huang
+% Version 6; preprint format; Edited by Jenny Greene and Song Huang
+% Version 7; preprint format; Edited by Susan Foster and Song Huang
+% Version 8; preprint format; Edited by Alexie Leauthaud and Song Huang
 
@@
     A key discovery in the last decade has been the dramatic structural transformation 
-    of massive quiescent galaxies \citep[e.g.][]{Trujillo2006, vanDokkum2008, 
+    of massive quiescent galaxies \citep[e.g.,][]{Trujillo2006, vanDokkum2008, 
     Cimatti2008, Damjanov2009, vanderWel2011, Szomoru2012, Patel2013} from 
@@
     galaxies (ETGs) need to increase their effective radii ($R_{\rm e}$) by a factor 
-    of 2--4 over a time span of 10 Gyrs (e.g. \citealt{Newman2012, vdWel2014}). 
+    of 2--4 over a time span of 10 Gyrs (e.g., \citealt{Newman2012, vdWel2014}). 
     This observational result spurred the development of the `two-phase' formation
-    scenario for massive ETGs (e.g. \citealt{Oser2010, Oser2012}),
+    scenario for massive ETGs (e.g., \citealt{Oser2010, Oser2012}),
     in which galaxies form a compact central region at $z\sim 2$ through highly 
-    dissipative processes (e.g. gas-rich mergers or cold gas-accretion;
+    dissipative processes (e.g., gas-rich mergers or cold gas-accretion;
     \citealt{Hopkins2008, Dekel2009}). 
     They subsequently assemble extended stellar haloes via dry mergers 
-    \citep[e.g,][]{Naab2006, Khochfar2006, Oser2010, Oser2012}, which can cause 
+    \citep[e.g.,][]{Naab2006, Khochfar2006, Oser2010, Oser2012}, which can cause 
     significant size growth at late times. 
@@
     larger ETGs were quenched more recently; but this explanation is still under 
-    active debate (e.g. \citealt{Newman2012, Carollo2013, Poggianti2013, Belli2015,
+    active debate (e.g., \citealt{Newman2012, Carollo2013, Poggianti2013, Belli2015,
     Keating2015, Fagioli2016}).
@@
     formation scenario using galaxies at low redshift, by investigating surface 
-    brightness or mass density profiles (e.g. \citealt{Huang2013a, Huang2013b, 
-    Oh2017}, optical colour gradients (e.g. \citealt{LaBarbera2010, LaBarbera2012}), 
+    brightness or mass density profiles (e.g., \citealt{Huang2013a, Huang2013b, 
+    Oh2017}, optical colour gradients (e.g., \citealt{LaBarbera2010, LaBarbera2012}), 
     and stellar population gradients \citep[e.g.,][]{Coccato2010, Coccato2011, 
@@
     \song{
-    Under the $\Lambda$CDM cosmology, the assembly of massive ETGs is intrinsically 
+    In the $\Lambda$CDM cosmology, the assembly of massive ETGs is intrinsically 
     tied to the hierarchical growth of their host dark matter haloes 
-    (e.g. \citealt{Leauthaud2012, Behroozi2013, Shankar2013}). 
-    Hydrodynamic simulations suggest that the fraction of star accreted through 
+    (e.g., \citealt{Leauthaud2012, Behroozi2013, Shankar2013}). 
+    Hydrodynamic simulations suggest that the fraction of stars accreted through 
     mergers (\textit{ex situ} component) in a central galaxy increases with halo 
-    mass (e.g. \citealt{Pillepich2017b}). 
-    Although the major merger rate is not a strong function of progenitor halo mass 
-    (e.g. \citealt{Shankar2015}), minor mergers may still play a more important 
-    role in the assembly of a central galaxy of more massive dark matter haloes 
-    (e.g. \citealt{Guo2011, Yoon2017}). 
-    As a minor merger is more efficient at `puffing up' the outskirts of massive 
-    galaxies (e.g. \citealt{Oogi2013, Bedorf2013}), this seems to suggest that the 
+    mass (e.g., \citealt{RodriguezGomez2016, Pillepich2017b}). 
+    The major merger rate is not a strong function of progenitor halo mass 
+    (e.g., \citealt{Shankar2015}) but minor mergers can still play an important 
+    role in determining the structures of central galaxies 
+    (e.g., \citealt{Guo2011, Yoon2017}). 
+    Minor mergers are efficient at `puffing up' the outskirts of massive 
+    galaxies (e.g., \citealt{Oogi2013, Bedorf2013}). 
+    Because the minor merger rate increases with halo mass, the 
     structures of massive ETGs and the well-known stellar mass--effective radius 
-    relation (\mstar{}--$R_{\rm e}$; e.g., \citealt{Shen2003, Guo2009}) should depend 
-    on their `environment'\footnote{There are multiple definitions of 
+    relation (\mstar{}--$R_{\rm e}$; e.g., \citealt{Shen2003, Guo2009}) should 
+    depend on their `environment'\footnote{There are multiple definitions of 
     `environment' in the literature. 
     In this work, we use `environment' and halo mass interchangeably.}
-    (e.g. \citealt{Shankar2013, Shankar2014}). 
+    (e.g., \citealt{Shankar2013, Shankar2014}). 
     However, evidence for the environment-dependence of \mstar{}--$R_{\rm e}$
     at low redshift is still not very solid (\citealt{Nair2010, HCompany13}; 
-    but also see \citealt{Yoon2017}), while the results at higher redshift are 
-    even more confusing (e.g. \citealt{Papovich2012, Lani2013, Delaye2014}; but 
+    but also see \citealt{Yoon2017}), and the results at higher redshift are 
+    even more unclear (e.g., \citealt{Papovich2012, Lani2013, Delaye2014}; but 
     also see \citealt{Rettura2010}).
@@
 	\song{
-    Therefore, we expect that it requires deeper images of these massive galaxies to 
-    better probe their outer stellar mass distributions and test these 
-    predictions. 
+    Deep images of massive galaxies can probe the outer stellar halos of massive 
+    galaxies and test these predictions. 
     Unfortunately, this is observationally challenging since the stellar haloes 
-    of massive galaxies can extend to $>100$ kpc (e.g.\citealt{Tal2011, DSouza2014}),
-    and their surface brightness profiles decline rapidly with typical values of 
-    $\mu > 26.0$ \sb{} in $i$-band at 100 kpc and at $z\sim0.3$. 
+    of massive galaxies can extend to $>100$ kpc (e.g., 
+    \citealt{Tal2011, DSouza2014}), and their surface brightness profiles decline 
+    rapidly with typical values of $\mu > 26.0$ \sb{} in $i$-band at 100 kpc and 
+    at $z\sim0.3$. 
     }
@@
     In this paper, we investigate whether the large scatter in the outer 
-    profiles of massive galaxies correlate with halo mass. 
+    profiles of massive galaxies correlates with halo mass. 
     We conclusively show that the sizes and stellar haloes of massive central galaxies 
@@
     \S \ref{sec:discussion}. 
-    \S \ref{sec:summary} presents our summary and conclusions.
+    Our summary and conclusions are presented in \S \ref{sec:summary}.
 
@@
     potential `intra-cluster' 
-    component (ICL; e.g. \citealt{Carlberg1997, Lin2004, Gonzalez2005, Mihos2005}).
+    component (ICL; e.g., \citealt{Carlberg1997, Lin2004, Gonzalez2005, Mihos2005}).
 
@@
           by their \mstar{} within a 100-kpc elliptical aperture that varies 
-          from $10^{11.2} M_{\odot}$ to $10^{11.7} M_{\odot}$. 
+          from $10^{11.2}\ M_{\odot}$ to $10^{11.7}\ M_{\odot}$. 
           At fixed `inner' mass (\minn{}), massive galaxies display significant
@@
           Red boxes indicate galaxies from dark matter haloes that are more massive 
-          than ${\sim} 10^{14.0} M_{\odot}$. 
+          than ${\sim} 10^{14}\ M_{\odot}$. 
           }
@@
     HSC $i$-band images are typically 3--4 mag deeper than SDSS 
-    (Sloan Digital Sky Survey; e.g. \citealt{SDSS-DR7, SDSS-DR8, SDSS-DR12})  
+    (Sloan Digital Sky Survey; e.g., \citealt{SDSS-DR7, SDSS-DR8, SDSS-DR12})  
     and have superb seeing conditions (mean $i$-band seeing has FWHM$=0.6$\asec{}).
@@
     Massive galaxies should experience little structural evolution and 
-    size growth between $z=0.5$ and 0.3 ($\sim$1.5 Gyr of time span) 
-    based on model prediction (e.g. \citealt{Shankar2015}).
+    size growth between $z=0.5$ and 0.3 ($\sim$1.5 Gyr time span) 
+    based on model prediction (e.g., \citealt{Shankar2015}).
     }
@@
     After carefully 
-    masking out surrounding neighbours and accounting for the subtraction of the 
+    masking out surrounding neighbors and accounting for the subtraction of the 
     background light, we derive $i$-band surface brightness profiles out to 100 kpc. 
@@
    very similar \minn{} that have a large range of \mtot{}. 
-   We use these two aperture masses to guide our comparisons of massive galaxies 
+   We use these two aperture masses to guide our comparison of massive galaxies 
    as a function of environment.
@@
     %Central galaxies are important to the study of galaxy-halo connection and follow 
-    %stellar mass--halo mass relation (SHMR; e.g. \citealt{Leauthaud2012, 
+    %stellar mass--halo mass relation (SHMR; e.g., \citealt{Leauthaud2012, 
     %Behroozi2013, Kravtsov2014, Tinker2017}) at high-\mstar{}.
@@
     First, we select 68 massive central galaxies from \redm{} clusters 
-    with richness ($\lambda$) $\geq 30$, and we assign the probability of true central 
-    galaxy ($P_{\mathrm{Cen}}$) $\geq 0.7$, and \logmtot{}$ >11.5$ 
+    with richness $\lambda \geq 30$, and we assign the probability of true central 
+    galaxy $P_{\mathrm{Cen}} \geq 0.7$, and \logmtot{}$ >11.5$ 
     at $0.3 < z < 0.5$ (63/68 have \logmtot{}$ >11.6$). 
@@
     at the high end of our redshift window. 
-    The $P_{\mathrm{Cen}}$ limit is selected to exclude a low-probability candidate for 
-    the central galaxy. 
+    The $P_{\mathrm{Cen}}$ limit is selected to exclude low-probability candidates for 
+    central galaxy. 
     \song{
@@
     This calibration is consistent with several other independent calibrations 
-    using different methods (e.g. \citealt{Saro2015, Farahi2016, 
+    using different methods (e.g., \citealt{Saro2015, Farahi2016, 
     Melchior2016, Murata2017}). 
@@
     We convert their $\lambda$ into $M_{\mathrm{200b}}$ using calibration by 
-    \citet{Simet2017}. 
-    \citet{Diemer2015} systematically investigates the mass density profiles of 
-    dark matter haloes under $\Lambda$CDM cosmology using a suite of dark matter--only
-    simulations.  
-    They provide empirical functions that describe the average density profiles 
-    of dark matters with different halo masses and at different redshifts.  
-    Using the \texttt{Colossus} Python package 
+    \citet{Simet2017}. Using the \texttt{Colossus} Python package 
     (\citealt{Colossus})\footnote{\url{http://www.benediktdiemer.com/code/colossus/}}
@@
     } 
-    We further exclude all galaxies within a cylinder around each cluster, with a radius
+    We exclude all galaxies within a cylinder around each cluster, with a radius
     equal to $R_{\mathrm{200b}}$ and a length equal to twice the value of the 
@@
     $M_{\mathrm{200b}} < 10^{14}$~\msun{}; we refer to this sample as \nbcg{}. \
-    There are 833 galaxies with \logmtot{}$> 11.6$ in this sample.
+    There are 833 central galaxies with \logmtot{}$> 11.6$ in this sample.
 
     Satellite contamination should be relative low at the high-\mtot{} end
-    (e.g. \citealt{Reid2014, Hoshino2015, Saito2016, vanUitert2016}). 
+    (e.g., \citealt{Reid2014, Hoshino2015, Saito2016, vanUitert2016}). 
     For instance, the model from \citet{Saito2016} predicts a $\sim 7$\% 
-    fraction for galaxies with \logmtot{}$>11.6$ and \logmh$<14.0$ haloes.
+    fraction for satellite galaxies with \logmtot{}$>11.6$ and \logmh$<14.0$ haloes.
 
@@
     \minn{} for the \rbcg{} and \nbcg{} samples. 
-    We also compare these two samples on the \mtot{}--rest frame $g-r$ colour plane. 
-    Both of the samples follow the same `red-sequence', with only a handful of galaxies 
+    We also compare these two samples on a \mtot{} versus rest--frame $(g-r)$ colour 
+    plane. 
+    Both of the samples follow the same red-sequence, with only a handful of galaxies 
     displaying bluer colours.
@@
     In Paper~I, we explore the \mstar{}-dependence of the stellar haloes in massive 
-    galaxies, and we conclude that the general trends are consistent with the 
-    predictions of the two-phase formation scenario. 
-    In this work, we investigate the relation between the \mden{} profiles of 
+    galaxies, we now investigate the relation between the \mden{} profiles of 
     massive galaxies, their stellar haloes, and dark matter halo mass. 
-    Here we use \mtot{} as a proxy for the `total' \mstar{} of massive galaxies, and 
-    we use \minn{} as a rough proxy for the stellar mass of the \textit{in situ} 
-    component.  
+    %Here we use \mtot{} as a proxy for the `total' \mstar{} of massive galaxies, and 
+    %we use \minn{} as a rough proxy for the stellar mass of the \textit{in situ} 
+    %component.  
     We remind the reader that although a circular aperture is shown on 
@@
     First, we ask whether the \mden{} profiles of massive central galaxies depend on 
-   a halo mass at a fixed stellar mass.    
+    halo mass at a fixed stellar mass.    
     We show comparisons of \mden{} profiles at both fixed \mtot{} and fixed 
@@
     Please see Appendix~\ref{app:robust} for further details.
-
-    The key features in Figure Fig~\ref{fig:prof_1} are the following:
+    \song{
+    In Appendix \ref{app:cog} and Figure~\ref{fig:cog}, we compare the same 
+    \mtot{}-matched samples using the cumulative \mstar{} profiles (or `curve of growth') 
+    and the fraction of \mtot{} enclosed within different radii.
+    Both comparisons highlight the differences in median \mden{} profiles 
+    from different angles.   
+    }
+
+    The key features in Figure~\ref{fig:prof_1} are the following:
 
     \begin{itemize}
+
+        \item At fixed \mtot{}, central galaxies in more massive dark matter haloes 
+            display shallower \mden{} profiles compared to those from less massive 
+            dark matter haloes (i.e., they have flatter inner \mden{} profiles and 
+            more significant outer stellar haloes). 
+            The median \mden{} profiles of the \rbcg{} and \nbcg{} samples cross 
+            each other at ${\sim} 15$-20 kpc, roughly the typical effective radius 
+            ($R_{\mathrm{e}}$) of massive galaxies with \logmtot{}$>11.7$--11.8.
 
@@
             at $R>50$ kpc scales.  
-            In Appendix \ref{app:cog} and Figure~\ref{fig:cog}, we compare the same
-            \mtot{}-matched samples using the cumulative \mstar{} profiles 
-            (or `curve of growth') and the fraction of \mtot{} enclosed within 
-            different radii.
-            Both comparisons highlight the differences in median \mden{} profiles 
-            from different angles.
-            }
-
-        \item At fixed \mtot{}, central galaxies in more massive dark matter haloes 
-            display shallower \mden{} profiles compared to those from less massive 
-            dark matter haloes (i.e.they have flatter inner \mden{} profiles and 
-            more significant outer stellar haloes). 
-            The median \mden{} profiles of the \rbcg{} and \nbcg{} samples cross 
-            each other at ${\sim} 15$-20 kpc, roughly the typical effective radius 
-            ($R_{\mathrm{e}}$) of massive galaxies with \logmtot{}$>11.7$--11.8.
-
-        \item For the \minn{}-matched samples, the median \mden{} profiles 
-            are very similar at $R \leq 10$ kpc. 
-            However, massive galaxies with similar \mstar{} within 10 kpc have quite
-            different \mtot{}, and the massive central galaxies in 
-            more massive haloes host much more prominent outer stellar haloes.
-
-        \item Also, for the \minn{}-matched samples, the similar slopes of the 
-            \mden{} profiles within 10 kpc are in sharp contrast with the large
+            }
+
+        \item Massive galaxies with similar \mstar{} within 10 kpc have quite
+            different \mtot{} and massive central galaxies in more massive haloes 
+            host much more prominent outer stellar haloes.
+
+        \item The similar slopes of the \mden{} profiles within 10 kpc for the 
+            \minn{}-matched samples are in sharp contrast with the large 
             \textit{intrinsic} scatter we see in the outer \mden{} profiles. 
+            We will discuss the inner \mden{} profiles further in \S~\ref{ssec:cen}
 
@@
     \song{
-    The subtle differences seen on the left side of Fig \ref{fig:prof_1} suggest
-    that the stellar mass distributions of the most massive central galaxies only
-    weakly depend on their environments. 
+    Fig \ref{fig:prof_1} shows that the environmental dependence of the profiles of m
+    assive central galaxies is a subtle effect.
     }
     This may explain why previous attempts to detect such dependence using 
-    shallower images often failed. 
-    More importantly, this result also suggests that halo mass does not play the 
-    central role in shaping massive central galaxies \textbf{at fixed `total' 
-    stellar mass}.
-    Also, the differences in median \mden{} profiles seem to become more prominent 
-    at higher \mtot{}. 
-    This is demonstrated in Appendix~\ref{app:robust} (see Fig~\ref{fig:prof_2}). 
-    Although this trend still needs to be confirmed by larger samples, it 
-    potentially indicates that the process of stellar haloes assembling in more 
-    massive central galaxies becomes more sensitive to their environments.
-
-    \song{
-    Meanwhile, the comparison of \mden{} profiles at fixed \minn{} -- a potential 
-    tracer of the \mstar{} in the \textit{in situ} component (right panel of 
-    Fig~\ref{fig:prof_1}) -- hints that the inner region ($<10$ kpc) and the outer 
-    stellar halo are shaped by different physical processes and responses to 
-    environment at different levels. 
-    }  
-    In hydrodynamic simulations, intense dissipative processes help create 
-    a self-similar de~Vaucouleurs--like ($n{\sim} 4$) \mden{} profile in the inner part 
-    of a massive galaxy (e.g. \citealt{Hopkins2008}), and the \mhalo{}-dependent
-    merging history leads to shallower stellar halo profile for the central galaxy 
-    of a more massive halo (e.g. \citealt{Pillepich2014}). 
-    The intrinsic scatter of halo assembly histories at fixed halo mass and the 
-    stochastic nature of the galaxy--galaxy mergers also explain the large 
-    \textit{intrinsic} scatter in the outer \mden{} profiles and the diversity 
-    seen on the \mtot{}--\minn{} plane (Fig~\ref{fig:m100_m10_color}).
-
-    \textbf{In summary, we reliably detect subtle, but systematic \mhalo{}-dependence 
-    (environmental dependence) of \mden{} profiles within 100 kpc in massive central 
+    shallower images often failed. In Appendix~\ref{app:robust} (see Fig~\ref{fig:prof_2}) 
+    we demonstrate that the environmental signature becomes more prominent for more massive 
     galaxies.
-    Such dependence seems to be consistent with the expectation of more (minor) 
-    mergers in more massive dark matter haloes. 
+
+    \textbf{In summary, we reliably detect a subtle, but robust halo mass dependence of 
+    the profiles of massive central galaxies. 
+    This dependence could be driven by the fact that massive halos have a larger minor 
+    merger rate compared to less massive haloes. 
     Nondissipative (minor) mergers should not strongly alter the inner \mden{} 
-    profiles, but can build up the outer halo efficiently
-    (e.g. \citealt{Hilz2013}, \citealt{Oogi2013})}.
-    \song{
-    As for the inner \mden{} profiles, although the comparison of the \minn{}-matched
-    samples reveals clear differences, we should point out that several physical 
-    processes (e.g. AGN feedback or merger of binary supermassive black holes) could 
-    alter \minn{} and the \mden{} profiles within 10 kpc during the last 10 Gyrs. 
-    We discuss this further in \S~\ref{ssec:cen}.
-    }
+    profiles, but can efficiently build up the outer halo 
+    (e.g., \citealt{Hilz2013}, \citealt{Oogi2013})}.
 
@@
 
-    In \S~\ref{ssec:sbp_mtot} we explain that the \mden{} profiles of massive galaxies 
+    We have shown that the \mden{} profiles of massive galaxies 
     show a dependence on the masses of their host dark matter haloes. 
@@
     The tight relation between \mstar{} and effective radius (or half-light radius; 
-    $R_{\mathrm{e}}$ or $R_{\mathrm{50}}$; e.g. \citealt{Shankar2013, Leja2013, 
+    $R_{\mathrm{e}}$ or $R_{\mathrm{50}}$; e.g., \citealt{Shankar2013, Leja2013, 
     vdWel2014}) is one of the most important scaling relationships for ETGs. 
@@
     \mhalo{}-dependence of the \mstar{}--$R_{\mathrm{e}}$ relation at low-$z$ 
-    (e.g. \citealt{Weinmann2009, Nair2010, HCompany13, Cerbrian2014}; 
+    (e.g., \citealt{Weinmann2009, Nair2010, HCompany13, Cerbrian2014}; 
     except for the recent result by \citealt{Yoon2017}).
@@
     \song{
-    As discussed in the previous section, the differences in the \mden{} profiles 
-    reveal that the \mtot{}-matched massive galaxies from different environments 
-    should have different effective radii (especially see Fig~\ref{fig:cog}). 
-    We now specifically look into the more traditionally studied 
-    \mstar{}--$R_{\mathrm{e}}$ relation.
-    First, we want to point out that `size' is not a well-defined parameter for 
-    objects like massive galaxies with very extended stellar mass distributions. 
+    We emphasize the fact that `size' is not a well-defined parameter for massive 
+    galaxies with very extended stellar mass distributions. 
     In practice, the measurements of `effective radius' or `half-light radius' 
@@
     }
-    In this section, we still use \mtot{} as a proxy for `total' \mstar{}, and we 
-    adopt the radius enclosing 50\% of stellar mass within 100 kpc ($R_{\mathrm{50}}$; 
-    derived from the $i$-band curve-of-growth) as the `size'. 
+    In this section, we adopt the radius enclosing 50\% of stellar mass within 
+    100 kpc ($R_{\mathrm{50}}$; derived from the $i$-band curve-of-growth) as the 
+    `size' for massive galaxies. 
     Such a definition of `half-light radius' is more robust against structural 
@@
     effective radius measured using a 2-D model with oversimplified assumptions 
-    (e.g. single-\ser{} model). 
+    (e.g., single-\ser{} model). 
     Massive galaxies in this sample are large enough so that the impact of seeing 
@@
     $\log(M_{\star,100})>11.6$ using the \texttt{emcee} MCMC sampler 
-    (\citealt{Emcee}) \footnote{The initial guesses are based on maximum 
+    (\citealt{Emcee})\footnote{The initial guesses are based on maximum 
     likelihood estimates, and we assume flat priors for parameters.}.
@@
     is very small due to the high \s2n{} of the profile. 
-    We manually assign 10\% error for $R_{\mathrm{50}}$. 
+    We manually assign a 10\% error for $R_{\mathrm{50}}$. 
     }
@@
     $R_{\mathrm{50}}$ derived within these apertures do not change the results.}.
-    \song{
-    Due to the relatively steep slopes for the \mtot{}--$R_{\mathrm{50}}$ relation, 
-    secondary binning (e.g. different halo mass) may induce artificial differences
-    (e.g. \citealt{Sonnenfeld2017}). 
-    We first check the results using the \mtot{}-matched samples and confirm 
-    the above conclusion. 
-    Furthermore, a normalized size parameter ($\gamma$; e.g., \citealt{Newman2012, 
-    HCompany13}) is proposed to control this effect. 
-    We follow the definition of $\gamma$ in \citet{HCompany13}:
+
+    \song{
+    Due to the steep slope of the mass--size relation, secondary binning 
+    (e.g., different halo mass) may introduce artificial differences 
+    (e.g., \citealt{Sonnenfeld2017}).
+    Besides the differences in best--fit \mtot{}--$R_{\mathrm{50}}$ relation, the 
+    median $R_{\mathrm{50}}$ of the \mtot{}-matched samples also confirm the above 
+    conclusion. 
+    In addition, we use the normalized size parameter ($\gamma$; e.g., 
+    \citealt{Newman2012, HCompany13}) to further test our results. 
+    In \citet{HCompany13}, $\gamma$ is defined as:
     }
@@
     where $\beta$ is the slope of the mass--size relation.
-    For the \logmtot{}$>11.6$ galaxies, we estimate the average $\gamma$ of both
-    samples using the slopes of their best-fitting mtot{}--$R_{\mathrm{50}}$ relations.
+    We estimate the average $\gamma$ of both samples at \logmtot{}$>11.6$. 
     For the \rbcg{} sample, $<\gamma> = 4.2\pm0.4$; for the \nbcg{} one, 
     $<\gamma> = 3.8\pm0.3$. 
-    Although the uncertainty is still quite large mainly due to the relative small 
-    sample size, the result also suggests a more significant environmental dependence
-    of $R_{\mathrm{50}}$ at fixed stellar mass compared to the \citet{HCompany13} 
-    one.
-    Given the uncertainties involved, the dependence of $R_{\mathrm{50}}$ of 
-    massive central galaxies at fixed \mtot{} is not very significant and is much 
-    weaker than the predictions of certain models in \citet{Shankar2014}. 
-    But before we rule out these models, we need to mention that the uncertainties 
-    of both mass and size are capable of washing out signals of stronger 
-    environment--dependence as shown in \citet{HCompany13}.
-    Therefore, we expect that the direct comparison of \mden{} profiles or the 
-    \mtot{}--\minn{} relation may be better at tracing the environment dependence
-    of structures in massive galaxies. 
+    The environmental dependence of $R_{\mathrm{50}}$ at fixed \mtot{} is more 
+    significant than the \citet{HCompany13} result, although the uncertainty 
+    is large for our small samples. 
+    Such environmental dependence of `size' is much weaker than the certain 
+    model prediction (e.g., \citealt{Shankar2014}).
+    It is important to remember that the uncertainties of both mass and size can 
+    wash out signals of stronger environment--dependence on mass--size plane 
+    (e.g., \citealt{HCompany13}), and direct comparison of \mden{} profiles or 
+    the \mtot{}--\minn{} relation may serve as a better tracer of the environment 
+    dependence. 
     }
@@
     assuming an average $<b/a>=0.75$.
-    At similar redshift, the mass-size relation from HC13a lies below the 
-    one in this work, while their slopes are quite similar.
+    At similar redshift, the mass-size relation from HC13a lies below our 
+    best--fit relation, while the slopes are quite similar.
     }
@@
     HC13b use the group catalogue by \citet{Yang2007} to estimate halo mass. 
-    In contrast to the present study, HC13a finds no environment dependence in the 
+    In contrast to the present study, HC13b find no environment dependence in the 
     mass--size relation for central galaxies in the range $12.5\le$ \logmh{} $<15.0$. 
@@
     \song{
-    Both of these comparisons highlight our arguments that `size' is not the most 
-    well-defined property to measure and compare, and that the mass--size relation 
-    may not be the most reliable tool to investigate environment dependence in 
-    massive galaxies.
-    The differences between the HC13a and our results may relate to the differences 
-    in modelling method and the shallower ACS/\texttt{F814W} images. 
+    Differences between the HC13ab and our results may relate to differences 
+    in modelling methods and the shallower ACS/\texttt{F814W} images. 
     As for HC13b, it is also possible that the shallower SDSS image hides the
@@
     like the imaging qualities and model assumptions much be carefully addressed. 
-    Both shallow images and oversimplified model can lead to biased results 
-    (e.g. see Appendix~\ref{app:gama} for the issue with single-\ser{} model 
+    Both shallow images and oversimplified models can lead to biased results 
+    (e.g., see Appendix~\ref{app:gama} for the issue with single-\ser{} model 
     using SDSS images).
@@
 
-    In conclusion, we confirm that the \mtot{}--$R_{\mathrm{50}}$ relation of massive
-    central galaxies at $0.3 < z < 0.5$ weakly depends on halo mass. 
-    At fixed \mtot{}, massive central galaxies in denser environments (higher \mhalo{}) 
-    have larger $R_{\mathrm{50}}$ compared with ones in smaller haloes at fixed 
-    \mtot{}. 
 %% ------------------------------------------------------------------------------------ %%
@@
 
-    Now we investigate the relationship among \mtot{}, \minn{}, and \mhalo{}. 
+    Now we investigate the relationship between \mtot{}, \minn{}, and \mhalo{}. 
     Compared to the mass--size relation, the \mtot{}--\minn{} relation is not plagued 
@@
     the fit is performed. 
-    These results also will not be altered when we replace the \minn{} with the stellar 
+    These results are also robust when we replace \minn{} with the stellar 
     mass within a 5- or 15-kpc aperture, or if \mtot{} is replaced with a stellar mass 
@@
 
+    \song{
     From Figure \ref{fig:scaling_relation} we can draw the same conclusions as in 
-    the previous section, namely that 
-    at fixed \mtot{}, central galaxies in more massive haloes tend to have a smaller 
-    fraction of stellar mass in their inner regions and higher \mstar{} in their outer
-    stellar haloes. 
-    Meanwhile, at fixed \minn{} -- a proxy for the \mstar{} of the `\textit{in situ}' 
-    component -- central galaxies in more massive haloes tend to be more massive and 
-    display more prominent stellar haloes. 
-    \song{
-    The comparison of \mden{} profiles for \minn{}-matched samples may not directly
-    reflect the environment-related processes because other physical mechanisms could 
-    also change the inner \mden{} profiles and their \mtot{} could be quite different. 
-    But the combination of \mtot{} and \minn{} clearly suggests that information about
-    their dark matter haloes or environments is encoded within this simple 2-D plane. 
-    We discuss more scientific implications of these results in 
-    \S~\ref{sec:discussion}
-    }
+    the previous section, namely that at fixed \mtot{}, central galaxies in more massive 
+    haloes tend to have a smaller fraction of stellar mass in their inner regions and 
+    higher \mstar{} in their outer stellar haloes.  
+    }
+
+    %Meanwhile, at fixed \minn{} -- a proxy for the \mstar{} of the `\textit{in situ}' 
+    %component -- central galaxies in more massive haloes tend to be more massive and 
+    %display more prominent stellar haloes. 
+    %\song{
+    %The comparison of \mden{} profiles for \minn{}-matched samples may not directly
+    %reflect the environment-related processes because other physical mechanisms could 
+    %also change the inner \mden{} profiles and their \mtot{} could be quite different. 
+    %But the combination of \mtot{} and \minn{} clearly suggests that information about
+    %their dark matter haloes or environments is encoded within this simple 2-D plane. 
+    %We discuss more scientific implications of these results in 
+    %\S~\ref{sec:discussion}
+    %}
 
@@
           panels show $g-i$. 
-          We compare our results with those from \citet{Tal2011} based on stacking 
-          large samples of luminous red galaxies in SDSS at $z{\sim} 0.4$ 
+          We compare our results with those from \citet{Tal2011}
           (solid blue line on top panels). 
           We also compare our results with those from a stacking analysis of nearby 
-          massive galaxies with high concentration indices ($C>2.6$) in 
-          \citet[][blue dashed lines on the top and middle panels]{DSouza2014}. 
+          massive galaxies with high concentration indices ($C>2.6$) from 
+          \citet{DSouza2014} (blue dashed lines in top and middle panels). 
           We also compare our results with the average $g-r$ and $g-i$ colour profiles 
-          from a large sample of nearby elliptical galaxies in \citet[][blue, solid 
-          lines on the middle and bottom panels]{LaBarbera2010}.
+          from a large sample of nearby elliptical galaxies for \citet{LaBarbera2010}
+          (blue, solid lines in middle and bottom panels).
           }
@@
     We also compared our results with previous studies that are based on stacked SDSS 
-    images (e.g. \citealt{LaBarbera2010, Tal2011, DSouza2014}). 
+    images (e.g., \citealt{LaBarbera2010, Tal2011, DSouza2014}). 
     Figure \ref{fig:ell_color} shows that:
@@
     \begin{itemize}
-        \item Within $R<50$ kpc, we find that the ellipticity profiles of massive 
-            central galaxies do not depend on halo mass at fixed \mtot{}.
-
-        \item For the \minn{}-matched samples, the \rbcg{} galaxies show higher
-            average ellipticity than the \nbcg{} ones at $R > 10$ kpc. 
-            On the other hand, the average ellipticity in the inner region is very 
-            similar. 
+        \item \song{
+            The ellipticity profiles of massive central galaxies do not depend on 
+            halo mass at fixed \mtot{} at $R<60$ kpc. 
+            }
+
+        \item \song{
+            However, the ellipticities of massive galaxies are different in the 
+            outskirts at fixed \minn{}. 
             This further suggests that the more elongated outer stellar haloes 
-            of massive haloes may relate to the accreted stars.
+            of massive haloes may relate to accreted stars.
+            }
 
@@
 
-    Besides these conclusions, the fact that we find smooth ellipticity profiles and 
-    shallow gradients favors the idea of using the flux-weighted average isophotal 
-    shape to extract 1-D \mden{} profiles of massive galaxies. 
+    The fact that we find smooth ellipticity profiles and shallow gradients favors 
+    the idea of using the flux-weighted average isophotal shape to extract 1-D \mden{} 
+    profiles of massive galaxies. 
     The similarity of average rest-frame colour profiles between the \rbcg{} and \nbcg{}
@@
     our comparisons.
-    \song{
-    At the same time, we are not certain that similar conclusions apply to the 
-    colour or ellipticity profiles within the inner 5--6 kpc due to the smearing effect
-    of the seeing. 
-    Central colour gradients may be sensitive to other physical processes and deserve 
-    future investigation using a 2-D modelling method and/or images with higher spatial 
-    resolution.
+
+    \song{
+    Our work does not address color gradients below 5--6 kpc because we do not deconvolve 
+    for the PSF. 
+    Color gradients on these scales may be sensitive to other physical processes and 
+    deserve future investigation using a 2-D modelling method and/or images with higher 
+    spatial resolution.
     }
@@
 
-    Using the deep images from the HSC survey, we show that the stellar mass 
-    distributions of massive central galaxies at $0.3 < z < 0.5$ depend on their 
-    environment or \mhalo{}. 
-    At fixed \mtot{} or \minn{}, we find that the central galaxies from more massive 
+    Using deep images from the HSC survey, we show that the stellar mass distributions 
+    of massive central galaxies at $0.3 < z < 0.5$ depend on their environment or 
+    \mhalo{}. 
+    At fixed \mtot{} or \minn{}, we find that central galaxies from more massive 
     haloes on average have a larger half-light radius and host more prominent outer 
@@
     The two-phase formation scenario can qualitatively explain these results. 
-    In this case, intense dissipative processes at $z > 2$ are 
-    responsible for the formation of \textit{in situ} stars in massive central 
-    galaxies. 
-    After the star-formation was rapidly quenched by some mechanisms (e.g., AGN 
-    feedback), the assembly of massive galaxies in the second phase is dominated 
-    by accretion of satellite galaxies through (mostly) nondissipative mergers. 
+    In this scenario, intense dissipative processes at $z > 2$ are responsible for the 
+    formation of \textit{in situ} stars in massive central galaxies. 
+    After the rapid quenching of star formation, the assembly of massive galaxies in 
+    the second phase is dominated by accretion of satellite galaxies through (mostly) 
+    non--dissipative mergers. 
     Dry minor mergers are efficient at depositing \textit{ex situ} stars in the 
-    outskirts of massive galaxies (e.g. \citealt{Oogi2013, Bedorf2013}). 
+    outskirts of massive galaxies (e.g., \citealt{Oogi2013, Bedorf2013}). 
     If minor mergers become more frequent in more massive dark matter haloes, 
     they can result in slightly different stellar mass distributions and larger 
-    effective radii for their massive central galaxies.
+    effective radii for massive central galaxies.
     }
@@
     \citet{Shankar2014} studied the environment dependence of galaxy size using 
-    a series of hierarchical semi-analytic models. 
+    different semi-analytic models. 
     They predict that at fixed stellar mass, the median size of central galaxies 
@@
     Although the major-merger rate does not strongly depend on halo mass 
-    (mass ratio $>1$:3; e.g. \citealt{Hirschmann2013, Shankar2015}), the minor--merger 
-    rate could still increase with halo mass if the dynamical friction time 
-    is short (e.g. \citealt{Newman2012}). 
-    Therefore, massive central galaxies with $11.5 <$\logms{}$<12.0$ from more massive 
-    haloes (\logmh{}$>14.0$) can have up to four times more minor mergers (1:100--1:3)
-    compared to the ones in less massive haloes at a similar stellar mass. 
-    Such an increase in the minor-merger rate as a function of halo mass leads to a 
+    (mass ratio $>1$:3; e.g., \citealt{Hirschmann2013, Shankar2015}), the 
+    minor--merger rate could still increase with halo mass if the dynamical friction
+    time is short (e.g., \citealt{Newman2012}). 
+    Therefore, massive central galaxies with $11.5 <$\logms{}$<12.0$ from 
+    massive haloes (\logmh{}$>14.0$) can have up to four times more minor mergers 
+    (1:100--1:3) compared to those in less massive haloes at a similar stellar 
+    mass. 
+    An increase in the minor-merger rate as a function of halo mass can lead to a 
     halo-mass dependence in the mass--size relation. 
@@
     cannot rule out some other scenarios.  
-    For instance, \citet{Buchan2016} suggests that central galaxies in more massive 
-    haloes could be born with more extended structures. 
-    More careful comparisons at higher redshift should help clarify these situations,
-    although recent observations of massive central galaxies of $z>2$ proto-clusters 
-    seem to confirm their compact nature (e.g. \citealt{Kubo2017}).
+    For instance, \citet{Buchan2016} suggest that central galaxies in more massive 
+    haloes could be born with more extended structure. 
+    A more careful comparison with higher redshift observations can distinguish between 
+    these different scenarios.
     }
@@
 
-    At the same time, from the comparison of median \mden{} profiles of the 
-    \mtot{}-matched samples and from the \mtot{}--\minn{} plane, our results also 
-    show that the centrals of more massive haloes have slightly shallower inner 
-    \mden{} slope and a lower fraction of \mtot{} within the inner 10 kpc.
+    Our results also show that the centrals of more massive haloes have slightly 
+    shallower inner \mden{} slopes and a smaller \mtot{} fraction within the inner 
+    10 kpc.
     \song{
@@
     estimate `total' \mstar{}: Assuming that centrals from more massive haloes 
-    have more extended \mden{} profiles, integration out to a larger aperture will 
-    make the differences between \rbcg{} and \nbcg{} galaxies on the \mtot{}--\minn{} 
+    have more extended \mden{} profiles, integration out to a larger aperture makes 
+    the differences between \rbcg{} and \nbcg{} galaxies on the \mtot{}--\minn{} 
     plane even more significant.
-    }
-
-    \song{ 
-    Although tempting, it is still too early to conclude that the stellar mass 
-    distributions at the center of massive ETGs also depend on environment. 
+    However, from this observation alone, we cannot determine which exact physical 
+    process is responsible for differences in the inner regions. 
     Many different physical processes can shape and alter the \mden{} profile within 
-    the inner 10 kpc, and several of them are not clearly controlled by environment.
-    This is particularly important since progenitors of the massive ETGs in this 
-    work may have had a higher central \mden{} in the past
-    (e.g. \citealt{Szomoru2012}).
-    } 
-    Major merger can redistribute the inner stellar mass distributions, but 
-    major--merger rate does not strongly depend on halo mass 
-    (e.g. \citealt{Shankar2014}). 
-    Although recent simulations tend to emphasize the contribution of dry minor 
-    mergers in building up the outer envelope, simulations also show that minor 
-    mergers can modify the central surface brightness profiles of the remnants
-    (e.g. \citealt{BoylanKolchin2007}). 
-    Depending on the structure and infalling orbit of the satellite, a minor merger 
+    the inner 10 kpc.
+    }
+
+    \song{
+    In hydrodynamic simulations, intense dissipative processes help create a 
+    self-similar de~Vaucouleurs--like ($n{\sim} 4$) \mden{} profile in the inner
+    part of massive galaxy (e.g., \citealt{Hopkins2008}).
+    } 
+    Major mergers can redistribute the inner stellar mass distributions, but 
+    the major--merger rate does not strongly depend on halo mass 
+    (e.g., \citealt{Shankar2014}). 
+    However, minor mergers, which do depend on halo mass, can modify the central 
+    surface brightness profiles of the remnants (e.g., \citealt{BoylanKolchin2007}). 
+    Depending on the structure and infalling orbits of satellites, a minor merger 
     can make the inner \mden{} profiles either steeper or shallower.  
@@
     galaxies.
-    \song{
-    Meanwhile, strong adiabatic expansion induced by powerful AGN feedback can 
-    be another mechanism (e.g. \citealt{Fan2008}) to modify the inner \mden{}
-    profile.
+
+    \song{
+    Strong adiabatic expansion induced by powerful AGN feedback is another mechanism 
+    (e.g., \citealt{Fan2008}) that can modify the inner \mden{} profile. \
     When the induced mass loss is efficient enough, it can lead to expanded 
-    central stellar mass distribution and can lower the inner \mden{} significantly. 
-    } 
-    In addition, at a smaller scale, the coalescence of super-massive black holes 
-    (SMBHs) can flatten the central \mden{} profile via an efficient scattering 
-    effect (e.g. \citealt{Milosavljevi2002}).
-    On the right side of Fig \ref{fig:scaling_relation}, we find a few \rbcg{} 
-    galaxies with very low \minn{} at the high \mtot{} end that are apparently not 
-    bothered by problematic photometry or exceptionally bad seeing.  
-    They may be similar to the recently discovered massive brightest cluster galaxies 
-    (BCGs) with very large depleted cores (a few thousand parsecs; e.g. 
-    \citealt{Postman2012, LopezCruz2014, Thomas2016, Bonfini2016}) resulting from 
-    SMBH mergers.
-
-    \song{
-    The impacts of these processes on the \mden{} profiles and their dependences 
-    on \mhalo{} are important issues that deserve further investigation.  
-    2-D modelling after considering the point spread function (PSF) convolution and 
-    images with higher spatial resolution will help us connect the central mass 
-    distribution with results of this work; and comparisons of the \mden{} profiles 
-    with massive galaxies in simulation can help us evaluate the relative importance 
-    of these processes.
+    central stellar mass distribution and can significantly lower the inner \mden{}. 
+    }
+
+    Finally, the coalescence of super-massive black holes (SMBHs) can also flatten 
+    the central \mden{} profile via an efficient scattering effect 
+    (e.g., \citealt{Milosavljevi2002}).
+    On the right side of Fig \ref{fig:scaling_relation}, there are a few candidates 
+    for galaxies with large cores. 
+    These may be similar to the recently discovered massive brightest cluster galaxies 
+    (BCGs) with very large depleted cores (a few thousand parsecs; e.g., 
+    \citealt{Postman2012, LopezCruz2014, Thomas2016, Bonfini2016}) possibly resulting 
+    from SMBH mergers.
+
+    \song{
+    The impact of these processes on the \mden{} profiles and their dependency on 
+    \mhalo{} are important issues that deserve more investigations. 
+    We plan to shed further light on the very inner regions of these massive galaxies 
+    using higher resolution images and 2-D modelling to account for the PSF.
     }
@@
 
-    In this work, we demonstrate that the stellar mass distributions and mass--size 
-    relation of massive central galaxies depend on their host dark matter halo masses. 
-    At $0.3 < z < 0.5$, \logmtot{}$>11.6$ galaxies from \logmhalo{}$>14.0$ haloes 
-    are on average $\sim20$\% larger than the ones from smaller haloes at fixed 
-    \mtot{}.
-
     Many previous works that focused on the mass--size relation found this relation 
-    is independent of halo mass or environment at $z\sim 0.0$ 
-    (e.g. \citealt{Nair2010, Maltby2010, Cappellari2013, HCompany13}). 
-    As mentioned earlier, both the shallower imaging depth and the oversimple model 
-    (e.g. single-\ser{} or de~Vaucouleurs model) used in the fitting can both 
+    to be independent of halo mass or environment at $z\sim 0.0$ 
+    (e.g., \citealt{Nair2010, Maltby2010, Cappellari2013, HCompany13}). 
+    We argue that, both the shallower imaging depth and the oversimple model 
+    (e.g., single-\ser{} or de~Vaucouleurs model) used in the fitting can both 
     contribute to this difference.
     In Appendix~\ref{app:gama}, we use the \rbcg{} and \nbcg{} galaxies that overlap 
-    with the Galaxy And Mass Assembly (GAMA) survey to briefly demonstrate this point. 
+    with the Galaxy And Mass Assembly (GAMA) survey to demonstrate this point. 
     We show that, for galaxies with similar \mstar{} derived from single-\ser{} 
     models using shallower SDSS images (\citealt{Kelvin2012}), the ones in more 
-    massive dark matter haloes actually show more prominent outer stellar haloes; 
-    hence, both their stellar mass and effective radius are underestimated.  
-    This shows again that the deeper HSC images give a significant advantage in 
-    studying the connection between the assembly of massive galaxies and their dark 
-    matter haloes.
+    massive dark matter haloes actually show more prominent outer stellar haloes.
+    \song{
+    These issues complicate the comparisons of mass--size relations derived from 
+    different images or using different methods.
+    }
 
@@
     \song{
-    \citet{Kuchner2017} uses one massive cluster at $z=0.44$ to show that ETGs in 
+    \citet{Kuchner2017} use one massive cluster at $z=0.44$ to show that ETGs in 
     that cluster have larger sizes than ETGs in the `field'. 
@@
 
-    While there appears to be an emerging consensus that at low redshift the 
-    high-mass end of the mass--size relation does vary with halo mass, the situation 
-    at higher redshift is more complicated. 
-    Certain studies find an environment dependence of the mass--size relation for 
-    massive quiescent or early-type galaxies that is qualitatively consistent with low 
-    redshift studies (e.g. \citealt{Papovich2012, Bassett2013, Lani2013, 
-    Strazzullo2013, Delaye2014}). 
-    \song{
-    It is interesting to see that several of these works report stronger 
-    environment dependence of size at fixed \mstar{} for either ETGs or quiescent 
-    galaxies (30--50\% larger in denser environments).
-    As shown in \citet{HCompany13} using a Monte Carlo test (see their \S~4.2), 
-    when the uncertainties of mass and size are considered, the size difference at 
-    fixed stellar mass could be even more significant between extremely different
-    environments.
-    If true, it indicates that denser regions at high redshift ($z>2$) could accelerate 
-    galaxy evolution (e.g. proto-clusters; see \citealt{Wang2016, Shimakawa2018}), and 
-    the size evolution of massive galaxies in a richer environment gradually slows down
-    toward lower redshift (e.g., \citealt{Papovich2012, Andreon2016}.
-    }
-    However, there are also observations that suggest otherwise (e.g. 
+    \song{
+    As it becomes clear that structures of massive galaxies do depend on 
+    environment, the origin of such dependence and its redshift evolution 
+    naturally becomes the focus of future studies. 
+    Several works find strong environment dependence of the mass--size relation 
+    for massive quiescent or early-type galaxies
+    (e.g., \citealt{Papovich2012, Bassett2013, Lani2013, Strazzullo2013, 
+    Delaye2014}), while other observations suggest otherwise (e.g., 
     \citealt{Rettura2010, Raichoor2012, Kelkar2015, Allen2015}). 
-    \song{
-    Comparisons of our results with work done at high redshift are complicated by many 
-    issues. 
-    At high-$z$, these works often rely on small samples or special environments 
-    (rare massive proto-clusters). 
-    Progenitors of massive galaxies in this work may still be star-forming or 
-    late-type galaxies at $z>1$. 
-    Finally, it is just intrinsically more difficult to accurately measure 
-    \mstar{} and size at high redshift (e.g. \citealt{Price2017}).
-    It would be interesting to see whether the current simulations can reproduce 
-    these observed environment dependencies and use them to investigate the redshift
-    evolution of such dependence. 
-    Meanwhile, direct comparisons of rest-frame surface brightness or \mden{} 
-    profiles (e.g. \citealt{Szomoru2012, Patel2013, Buitrago2017, Hill2017}) could be 
-    a better approach than the 
-    mass--size relation to compare high- and low-$z$ mass galaxies.
-    }
+    Comparison with high--redshift results are complicated by many issues and 
+    is beyond the scope of this work, but we want to emphasize again that 
+    direct comparison of \mden{} profile (e.g., \citealt{Szomoru2012, Patel2013, 
+    Buitrago2017, Hill2017}) could better trace the redshift evolution of the
+    environment dependence. 
+    }
+
+    %\song{
+    %It is interesting to see that several of these works report stronger 
+    %environment dependence of size at fixed \mstar{} for either ETGs or quiescent 
+    %galaxies (30--50\% larger in denser environments).
+    %As shown in \citet{HCompany13} using a Monte Carlo test (see their \S~4.2), 
+    %when the uncertainties of mass and size are considered, the size difference at 
+    %fixed stellar mass could be even more significant between extremely different
+    %environments.
+    %If true, it indicates that denser regions at high redshift ($z>2$) could accelerate 
+    %galaxy evolution (e.g., proto-clusters; see \citealt{Wang2016, Shimakawa2018}), and 
+    %the size evolution of massive galaxies in a richer environment gradually slows down
+    %toward lower redshift (e.g., \citealt{Papovich2012, Andreon2016}.
+    %}
+    %However, there are also observations that suggest otherwise (e.g., 
+    %\citealt{Rettura2010, Raichoor2012, Kelkar2015, Allen2015}). 
+    %\song{
+    %Comparisons of our results with work done at high redshift are complicated by many 
+    %issues. 
+    %At high-$z$, these works often rely on small samples or special environments 
+    %(rare massive proto-clusters). 
+    %Progenitors of massive galaxies in this work may still be star-forming or 
+    %late-type galaxies at $z>1$. 
+    %Finally, it is just intrinsically more difficult to accurately measure 
+    %\mstar{} and size at high redshift (e.g., \citealt{Price2017}).
+    %It would be interesting to see whether the current simulations can reproduce 
+    %these observed environment dependencies and use them to investigate the redshift
+    %evolution of such dependence. 
+    %Meanwhile, direct comparisons of rest-frame surface brightness or \mden{} 
+    %profiles (e.g., \citealt{Szomoru2012, Patel2013, Buitrago2017, Hill2017}) could be 
+    %a better approach than the 
+    %mass--size relation to compare high- and low-$z$ mass galaxies.
+    %}
 
@@
     do not use consistent size definitions, or they only perform crude size conversions 
-    (e.g. 3-D radius in simulation versus 2-D projected radius in observation; 
+    (e.g., 3-D radii in simulation versus 2-D projected radii in observation; 
     \citealt{Genel2017}). 
@@
     Simulations, on the other hand, often employ sizes that correspond to the 3-D 
-    aperture half-mass radius (e.g. \citealt{Price2017}).
+    aperture half-mass radius (e.g., \citealt{Price2017}).
 
@@
     always consistent. 
-    Measurement of `size' often shows dependence on image quality (e.g. seeing, 
-    imaging depth), filter, and the adopted method. 
+    Measurements of `size' depend on image quality (e.g., seeing, imaging depth), filter, 
+    and the adopted method. 
     Although the elliptical single-\ser{} model is widely adopted in measuring the 
@@
     to biased results as it is no longer an appropriate model for certain types of galaxies. 
-    Size derived from a 1-D curve-of-growth is more model independent and has been 
+    Sizes derived from a 1-D curve-of-growth is more model independent and has been 
     shown to be useful in revealing environmental dependence of the mass--size relation 
-    (e.g. \citealt{Yoon2017} and this work), but it does not take the PSF convolution 
+    (e.g., \citealt{Yoon2017}, and this work), but it does not take the PSF convolution 
     effect into account, and it depends on imaging depth and background subtraction.
@@
     between observations and theoretical predictions.
-    In follow-up work, we will present comparisons between our observations and 
-    predictions from hydrodynamic simulations using the \mtot{}--\minn{} 
-    plane instead of the mass--size relation.
 
@@
 
-    Using the high-quality images from the first $\sim100$ deg$^2$ of the 
+    Using high-quality images from the first $\sim100$ deg$^2$ of the 
     Hyper Suprime-Cam Subaru Strategic Program, we group a large sample of massive 
@@
     halo mass (\mhalo{}$\simgt 10^{14.2} M_{\odot}$ and 
-    \mhalo{}$\simlt 10^{14} M_{\odot}$), and we study how their stellar mass distributions 
-    out to 100 kpc depend on their environments (or \mhalo{}). 
-    The main results are as follows:
+    \mhalo{}$\simlt 10^{14} M_{\odot}$), and we study how their stellar mass 
+    distributions out to 100 kpc depend on their environments (or \mhalo{}). 
+    Our main results are as follows:
 
@@
         \item At fixed \minn{}, massive central galaxies in more massive haloes 
-            possess much more extended stellar haloes than the ones in smaller haloes, 
-            despite their median \mden{} profiles at $R < 15$ kpc being very similar. 
+            possess much more extended stellar haloes than those in smaller haloes. 
             Assuming that \minn{} traces the amount of `\textit{in situ}' stars in 
@@
 
-        \item The \mtot{}-$R_{\mathrm{50}}$ relation for massive central galaxies 
-            also exhibits environmental dependence. 
-            Central galaxies in more massive haloes have slightly larger
-            $R_{\mathrm{50}}$ than the ones from less massive haloes at fixed \mtot{}.
-
-        \item We also find that massive central galaxies in different environments
-            follow different relationships between their \mtot{} and \minn{}. 
-            Assuming that \mtot{} is a reasonable proxy for `total' stellar mass and 
-            \minn{} reflects the amount of \textit{in situ} stars, we propose that 
-            this relation can help diagnose the assembly of massive central galaxies 
-            without using `size' with ambiguous definition.
-
-        \item At fixed \mtot{}, the ellipticity profiles of massive central galaxies 
-            do not display strong environment dependence at $R < 60$ kpc. 
-            At fixed \minn{}, the more extended stellar haloes present in the \rbcg{}
-            galaxies also show higher ellipticity than the \nbcg{} galaxies.
-
-        \item We do not find evidence that suggests the rest-frame colour profiles 
-            within 60 kpc depend on environment for either the \mtot{}- or 
-            \minn{}-matched samples.
+        \item \song{
+            Such environmental dependence is also reflected on the plane of
+            \mtot{} versus $R_{\mathrm{50}}$, and \mtot{} versus \minn{}. 
+            And we propose that the \mtot{}-\minn{} relation can be a better tool 
+            to diagnose the assembly of massive central galaxies without using `size' 
+            with ambiguous definition.
+            }
+
+        \item \song{
+            At $R < 60$ kpc, the ellipticity and rest--frame colour profiles of 
+            massive galaxies do not depend on halo mass at fixed \mtot{}.
+            And, at fixed \minn{}, massive centrals from more massive haloes tend 
+            to have more elongated outer stellar envelopes.
+            }
 
@@
     measurements of dark matter haloes around these massive galaxies, and comparing 
-    our results with hydrodynamic simulations to gain more physical insights.
+    our results with hydrodynamic simulations to gain more physical insight.
 
@@
     measured \mstar{} for large sample of galaxies (\citealt{Taylor2011}) that help 
-    produce many interesting results (e.g. \citealt{Bauer2013, Ferreras2017}).
+    produce many interesting results (e.g., \citealt{Bauer2013, Ferreras2017}).
     They use 2-D single-\ser{} model to correct the total luminosity of the galaxy 

### 2017-12-04 draft/paper2_v9.tex
New edits from Alexie

--- 2017-11-30 draft/paper2_v8.tex
@@
 
-\begin{abstract}
-
-    To investigate the halo mass dependence of the surface mass density profiles 
-    and outer stellar envelopes of massive galaxies, we use ${\sim}100$ deg$^2$ of 
+\begin{abstract}  We use ${\sim}100$ deg$^2$ of 
     deep ($>28.5$ \sb{} in $i$-band), high-quality 
-    (median 0.6\asec seeing) imaging data from the Hyper Suprime--Cam (HSC) survey.
+    (median 0.6\asec seeing) imaging data from the Hyper Suprime--Cam (HSC) survey to reveal the halo mass dependence of the surface mass density profiles and outer stellar envelopes of massive galaxies.
 The $i$-band images from the HSC survey reach ${\sim}4$ magnitudes deeper than
@@
     (within ${\sim}10$--$20$ kpc) and more prominent outer envelopes. 
-    These differences translate into a halo mass dependence of the 
-    following mass--size relation: central galaxies in haloes with \logmh{}$>14.0$ are 
-    $\sim 20$\% larger in $R_{\mathrm{50}}$ at fixed \mtot{}.  
+    These differences translate into a halo mass dependence of the mass--size relation.
+Central galaxies in haloes with \logmh{}$>14.0$ are $\sim 20$\% larger in $R_{\mathrm{50}}$ at fixed \mtot{}.
 Such dependence is also reflected in the relationship between the stellar mass
-    within 10 and 100 kpc. 
-    Comparing to the mass--size relation, the \mtot{}--\minn{} relation avoids the 
+    within 10 and 100 kpc.  Comparing to the mass--size relation, the \mtot{}--\minn{} relation avoids the 
     ambiguity in the definition of size, and can be straightforwardly compared with 
@@
     These observations are generally consistent with the two-phase formation scenario. 
-    However, it is still not clear whether this promising picture can correctly 
-    predict the connection between the stellar mass distributions in massive galaxies 
-    and their dark matter haloes.
-    }
-
-    \song{
-    In the $\Lambda$CDM cosmology, the assembly of massive ETGs is intrinsically 
+    However, it is still not clear whether this picture correctly 
+    predicts the connection between the stellar mass distributions in massive galaxies 
+    and their dark matter haloes.}
+
+     \song{In the $\Lambda$CDM cosmology, the assembly of massive ETGs is intrinsically 
     tied to the hierarchical growth of their host dark matter haloes 
@@
     Hydrodynamic simulations suggest that the fraction of stars accreted through 
-    mergers (\textit{ex situ} component) in a central galaxy increases with halo 
+    mergers (the \textit{ex situ} component) in central galaxies increases with halo 
     mass (e.g., \citealt{RodriguezGomez2016, Pillepich2017b}). 
@@
     In Paper I, we characterized the stellar mass profiles of massive ETGs and 
-    showed that there is a large intrinsic scatter in the \mden{} stellar haloes of
+    showed that there is a large intrinsic scatter in the stellar haloes of
     massive galaxies on 100-kpc scales. 
@@
     size growth between $z=0.5$ and 0.3 ($\sim$1.5 Gyr time span) 
-    based on model prediction (e.g., \citealt{Shankar2015}).
+    based on model predictions (e.g., \citealt{Shankar2015}).
     }
@@
             component. 
-            This is motivated both by recent observations and simulations 
+            This is motivated both by observations and simulations 
             (e.g.~\citealt{vanDokkum2010}, \citealt{RodriguezGomez2016}). 
@@
             In Paper~I we show that \mtot{} recovers more light compared to 
-            HSC \cmodel{} photometry and has offsets that can be a large as 0.2 dex 
+            HSC \cmodel{} photometry with differences that can be a large as 0.2 dex 
             in magnitude.
@@
    results in terms of the full stellar mass profiles. 
-   However, in many cases we find it more useful to display figures using the simpler 
+   However, in many cases we find it useful to display figures using the simpler 
    \minn{} and \mtot{} quantities. 
@@
     We use the \redm{} \texttt{v5.10} \citep{Rykoff2014, Rozo2015b} cluster catalogue 
-    to help us construct a central galaxy sample.
+    to help us construct two central galaxy samples.
 
@@
 
-    First, we select 68 massive central galaxies from \redm{} clusters 
-    with richness $\lambda \geq 30$, and we assign the probability of true central 
-    galaxy $P_{\mathrm{Cen}} \geq 0.7$, and \logmtot{}$ >11.5$ 
+    First, we build a sample of central galaxies in high mass haloes. We select 68 massive central galaxies from \redm{} clusters 
+    with richness $\lambda \geq 30$, with central probability $P_{\mathrm{Cen}} \geq 0.7$, and \logmtot{}$ >11.5$ 
     at $0.3 < z < 0.5$ (63/68 have \logmtot{}$ >11.6$). 
@@
     at the high end of our redshift window. 
-    The $P_{\mathrm{Cen}}$ limit is selected to exclude low-probability candidates for 
-    central galaxy. 
-    \song{
-    \citet{Simet2017} calibrates the \mhalo{}-$\lambda$ relation for the \redm{} 
-    clusters using the SDSS weak-lensing data after carefully addressing many 
-    important systematic uncertainties.
-    Based on this calibration, these clusters correspond to central galaxies living 
+    The $P_{\mathrm{Cen}}$ limit is imposed to limit our sample to central galaxies. 
+    \song{
+    \citet{Simet2017} present a calibration of the \mhalo{}-$\lambda$ relation for \redm{} 
+    clusters using SDSS weak-lensing. Based on this calibration, our sample corresponds to central galaxies living 
     in haloes with \mhalo{}$>10^{14.2}$~\msun{}. 
@@
     The median richness of the sample is $\lambda \approx 41$ 
-    (\mhalo{}$\approx 2.2 \times 10^{14}$~\msun{}), and there are 
-    only 44 central galaxies in clusters with $\lambda>50$ 
+    (\mhalo{}$\approx 2.2 \times 10^{14}$~\msun{}), and there are 44 central galaxies in clusters with $\lambda>50$ 
     (\mhalo{}$\approx 3.0 \times 10^{14}$~\msun{}).
@@
 
-    Second, we build a complementary sample of central galaxies in lower mass haloes
-    by excluding all galaxies that are in any \redm{} cluster with $\lambda > 20$.
-    \song{
-    We convert their $\lambda$ into $M_{\mathrm{200b}}$ using calibration by 
-    \citet{Simet2017}. Using the \texttt{Colossus} Python package 
+    Second, we build a sample of central galaxies in low mass haloes. We begin by excluding all galaxies in \redm{} clusters with $\lambda > 20$.
+    \song{
+    We convert $\lambda$ to $M_{\mathrm{200b}}$ using the \citet{Simet2017} calibration. For each cluster, we compute $R_{\mathrm{200b}}$ using the \texttt{Colossus} Python package 
     (\citealt{Colossus})\footnote{\url{http://www.benediktdiemer.com/code/colossus/}}
-    provided by \citet{Diemer2015}, we estimate the $R_{\mathrm{200b}}$ of each 
-    cluster given its $M_{\mathrm{200b}}$ and redshift.
-    } 
+    provided by \citet{Diemer2015}} 
     We exclude all galaxies within a cylinder around each cluster, with a radius
-    equal to $R_{\mathrm{200b}}$ and a length equal to twice the value of the 
+    equal to $R_{\mathrm{200b}}$, and a length equal to twice the value of the 
     photometric redshift uncertainty of the cluster (typically around 0.015 to 0.025).
@@
 
-    Satellite contamination should be relative low at the high-\mtot{} end
-    (e.g., \citealt{Reid2014, Hoshino2015, Saito2016, vanUitert2016}). 
-    For instance, the model from \citet{Saito2016} predicts a $\sim 7$\% 
-    fraction for satellite galaxies with \logmtot{}$>11.6$ and \logmh$<14.0$ haloes.
-
-    In Appendix~\ref{app:basic}, we show the distributions of redshift, \mtot{}, and 
-    \minn{} for the \rbcg{} and \nbcg{} samples. 
+    Satellite contamination in our sample should be low (e.g., \citealt{Reid2014, Hoshino2015, Saito2016, vanUitert2016}). 
+    For instance, the model from \citet{Saito2016} predicts that our \rbcg{} sample should only contain $\sim 7$\% satellites (corresponding to satellites with \logmtot{}$>11.6$ and living in haloes with \logmh$<14.0$).
+
+    Appendix~\ref{app:basic} shows the distributions of redshift, \mtot{}, and 
+    \minn{} for the two samples. 
     We also compare these two samples on a \mtot{} versus rest--frame $(g-r)$ colour 
     plane. 
-    Both of the samples follow the same red-sequence, with only a handful of galaxies 
+    Both samples follow the same red-sequence, with only a handful of galaxies 
     displaying bluer colours.
 
-    We note that our analysis fails to extract 1-D profiles for $\sim10$\% of 
+    Our analysis fails to extract 1-D profiles for $\sim10$\% of 
     \rbcg{} and \nbcg{} galaxies due to ongoing major mergers or projection effects 
     (e.g.\ nearby foreground galaxy or bright stars). 
-    However, this small failure rate should not affect any of the results in this paper.
+    However, this small failure rate should not affect any of our results.
 
@@
     \minn{} display a large diversity in their stellar haloes. 
-    In Paper~I, we explore the \mstar{}-dependence of the stellar haloes in massive 
-    galaxies, we now investigate the relation between the \mden{} profiles of 
-    massive galaxies, their stellar haloes, and dark matter halo mass. 
-    %Here we use \mtot{} as a proxy for the `total' \mstar{} of massive galaxies, and 
-    %we use \minn{} as a rough proxy for the stellar mass of the \textit{in situ} 
-    %component.  
+    In Paper~I, we explored the \mstar{}-dependence of these stellar haloes.
+We now investigate the relation between \mden{} profiles, stellar haloes, and dark matter halo mass.
 We remind the reader that although a circular aperture is shown on
@@
     First, we ask whether the \mden{} profiles of massive central galaxies depend on 
-    halo mass at a fixed stellar mass.    
+    halo mass at fixed stellar mass.    
     We show comparisons of \mden{} profiles at both fixed \mtot{} and fixed 
-    \minn{}. 
-    We also ensure that all comparisons are performed with a fixed underlying redshift
-    distribution by matching samples in redshift in addition to a fixed stellar mass
-    (please see Appendix~\ref{app:match}, Appendix~\ref{app:redshift}, 
+    \minn{}. All comparisons are performed with a fixed underlying redshift
+    distribution by matching samples in redshift in addition to stellar mass
+    (see Appendix~\ref{app:match}, Appendix~\ref{app:redshift}, 
     and Fig~\ref{fig:match} for details).
@@
 %% ------------------------------------------------------------------------------------ %%     
-    Fig~\ref{fig:prof_1} compares the \mden{} profiles of massive central galaxies 
-    living in less massive dark matter haloes (\logmh$<14.0$) to those living in more 
-    massive dark matter haloes (\logmh$>14.2$) at fixed \mtot{} (left panel) and at 
-    fixed \minn{} (right panel). 
-    At fixed \mtot{}, we compare massive galaxies that have similar `total' \mstar{}. 
-    On the right side, we use \minn{} as a proxy for the \textit{in situ} \mstar{} to 
-    compare the overall \mstar{} distributions of galaxies living in different 
-    environments that have assembled a similar amount of stars at high-$z$.
+    Fig~\ref{fig:prof_1} compares the \mden{} profiles of massive central galaxies in low mass haloes to those in high mass haloes at fixed \mtot{} (left panel) and at fixed \minn{} (right panel).
+The left panel compares galaxies that have similar `total' stellar mass.
+The right panel uses \minn{} as a proxy for the \textit{in situ} component to
+    compare the profiles of galaxies that presumably have similar early formation histories, but which live in different dark matter haloes today.
 This figure shows the main result of this paper, namely that
@@
     resampling test, and we perform statistical tests to demonstrate that the 
-    differences of \mden{} profiles are more significant than the levels allowed by 
+    difference between the profiles is more significant than the level allowed by 
     the intrinsic randomness within the combined \rbcg{} and \nbcg{} sample. 
@@
     We also conduct a variety of tests that verify the robustness of these results with
-    respect to the choices of \mtot{} bins, $\lambda$ cut, the redshift range, and the 
+    respect to our \mtot{} binning scheme, $\lambda$ cut, the redshift range, and the 
     choice of apertures used for the metric masses. 
     Please see Appendix~\ref{app:robust} for further details.
-    \song{
-    In Appendix \ref{app:cog} and Figure~\ref{fig:cog}, we compare the same 
-    \mtot{}-matched samples using the cumulative \mstar{} profiles (or `curve of growth') 
+    \song{Appendix \ref{app:cog} and Figure~\ref{fig:cog} compares the same 
+    \mtot{}-matched samples using cumulative \mstar{} profiles (`curve of growth') 
     and the fraction of \mtot{} enclosed within different radii.
-    Both comparisons highlight the differences in median \mden{} profiles 
+    Both comparisons highlight the differences in the median \mden{} profiles 
     from different angles.   
@@
 
-        \item At fixed \mtot{}, central galaxies in more massive dark matter haloes 
-            display shallower \mden{} profiles compared to those from less massive 
-            dark matter haloes (i.e., they have flatter inner \mden{} profiles and 
-            more significant outer stellar haloes). 
-            The median \mden{} profiles of the \rbcg{} and \nbcg{} samples cross 
+        \item At fixed \mtot{}, central galaxies in high mass haloes 
+            display shallower \mden{} profiles compared to those in low mass haloes (i.e., they have flatter inner \mden{} profiles and 
+            more significant outer stellar envelopes).
+
+            \item  The median \mden{} profiles of the two samples cross 
             each other at ${\sim} 15$-20 kpc, roughly the typical effective radius 
-            ($R_{\mathrm{e}}$) of massive galaxies with \logmtot{}$>11.7$--11.8.
+            ($R_{\mathrm{e}}$) of galaxies at these masses (\logmtot{}$>11.7$--11.8).
 
             \item \song{
-            For the \mtot{}-matched samples, there are some subtle but statistically 
-            significant and robust differences between the two median \mden{} profiles.
-            Due to the logarithmic scale, the difference in the inner region appears 
-            to be very small. 
-            Meanwhile, the difference in the \mden{} profile becomes more apparent 
-            at $R>50$ kpc scales.  
-            }
-
-        \item Massive galaxies with similar \mstar{} within 10 kpc have quite
-            different \mtot{} and massive central galaxies in more massive haloes 
-            host much more prominent outer stellar haloes.
-
-        \item The similar slopes of the \mden{} profiles within 10 kpc for the 
-            \minn{}-matched samples are in sharp contrast with the large 
-            \textit{intrinsic} scatter we see in the outer \mden{} profiles. 
-            We will discuss the inner \mden{} profiles further in \S~\ref{ssec:cen}
-
+            When matched by \mtot{}, differences in the inner regions appear 
+            to be small, but this is also driven by the use of a logarithmic y-axis. The difference becomes more apparent 
+            at $R>50$ kpc.  
+            }
+
+        \item Massive galaxies matched by \minn{} display a range of  \mtot{} values.
+Those in massive dark matter halos have more prominent outer stellar haloes.
+The scatter in the outer profiles observed in Figure \ref{fig:prof_1} is an \textit{intrinsic} scatter (not measurement error).
     \end{itemize}
@@
     \song{
-    Fig \ref{fig:prof_1} shows that the environmental dependence of the profiles of m
-    assive central galaxies is a subtle effect.
-    }
-    This may explain why previous attempts to detect such dependence using 
-    shallower images often failed. In Appendix~\ref{app:robust} (see Fig~\ref{fig:prof_2}) 
-    we demonstrate that the environmental signature becomes more prominent for more massive 
-    galaxies.
-
-    \textbf{In summary, we reliably detect a subtle, but robust halo mass dependence of 
+    Fig \ref{fig:prof_1} shows that the environmental dependence of the profiles of massive central galaxies is a subtle effect that is most prominent at large radii ($R>50$ kpc).
+    } This may explain why previous attempts to detect this effect using 
+    shallower images have often failed.
+
+    The effect becomes more pronounced for even more massive galaxies. This is shown in Fig~\ref{fig:prof_2} in Appendix~\ref{app:robust}.
+
+    In summary, we detect a subtle, but robust halo mass dependence of 
     the profiles of massive central galaxies. 
@@
     merger rate compared to less massive haloes. 
-    Nondissipative (minor) mergers should not strongly alter the inner \mden{} 
-    profiles, but can efficiently build up the outer halo 
-    (e.g., \citealt{Hilz2013}, \citealt{Oogi2013})}.
+    Nondissipative (minor) mergers should not strongly alter inner 
+    profiles, but can efficiently build up outer haloes 
+    (e.g., \citealt{Hilz2013}, \citealt{Oogi2013}).
 
@@
 
-    We have shown that the \mden{} profiles of massive galaxies 
-    show a dependence on the masses of their host dark matter haloes. 
-    In this section, we turn our attention to the more commonly studied stellar 
+    We have shown that the \mden{} profiles of massive galaxies vary with the masses of their host dark matter haloes. We now turn our attention to the more commonly studied stellar 
     mass--size relation (\mstar{}--$R_{\mathrm{e}}$). 
@@
 
-    \song{
-    We emphasize the fact that `size' is not a well-defined parameter for massive 
+    \song{However, `size' is not a well-defined parameter for massive 
     galaxies with very extended stellar mass distributions. 
-    In practice, the measurements of `effective radius' or `half-light radius' 
-    not only depend on resolution, depth, and filter of the image, but may also 
+    In practice, measurements of the `effective radius', or `half-light radius', depend on resolution, depth, filter, and may also 
     depend on the adopted model for the light profile.  
-    This makes comparisons of size measurements among different observations 
-    or between observations and models much more uncertain, and is the main reason
-    why we prefer to compare the \mden{} profiles directly.
-    }
-    In this section, we adopt the radius enclosing 50\% of stellar mass within 
-    100 kpc ($R_{\mathrm{50}}$; derived from the $i$-band curve-of-growth) as the 
-    `size' for massive galaxies. 
-    Such a definition of `half-light radius' is more robust against structural 
-    details, choice of model, and the background subtraction compared to the 
-    effective radius measured using a 2-D model with oversimplified assumptions 
-    (e.g., single-\ser{} model). 
+    This makes comparisons of size measurements among different observations, 
+    or between observations and models, uncertain. This is the main reason
+    why we prefer to compare \mden{} profiles directly which completely bypasses the need to consider `size'.
+    }
+
+    Nonetheless, to enable comparisons with past work, we now consider the more traditional mass-size relation. We adopt the radius enclosing 50\% of stellar mass within 
+    100 kpc ($R_{\mathrm{50}}$; derived from the $i$-band curve-of-growth) as our 
+    `size' for massive galaxies. This definition of `half-light radius' is more robust against structural 
+    details, model choice, and background subtraction, compared to the 
+    effective radius measured using oversimplified 2-D models such as the single-\ser{} model. 
     Massive galaxies in this sample are large enough so that the impact of seeing 
@@
 
-    The left panel of Fig~\ref{fig:scaling_relation} shows the 
-    \mtot{}--$R_{\mathrm{50}}$ relations for galaxies in more and less massive
-    dark matter haloes. 
-    We fit the \logmtot{}-$\log_{10} (R_{\mathrm{50}}/\mathrm{kpc})$ relations at 
+    The left panel of Fig~\ref{fig:scaling_relation} shows the mass-size relation for our two samples. We fit the \logmtot{}-$\log_{10} (R_{\mathrm{50}}/\mathrm{kpc})$ relations at 
     $\log(M_{\star,100})>11.6$ using the \texttt{emcee} MCMC sampler 
@@
 
-    \noindent As shown in the left panel of Fig~\ref{fig:scaling_relation}, 
-    massive central galaxies of more and less massive dark matter haloes lie on 
+    \noindent As shown in the left panel of Fig~\ref{fig:scaling_relation}, the two samples lie on 
     \mtot{}--$R_{\mathrm{50}}$ relations that have similar slopes but 
-    different normalizations. 
-    The best-fitting mass--size relation derived here suggests that, 
+    different normalizations. The best-fitting mass--size relation derived here suggests that, 
     at $0.3 < z < 0.5$, central galaxies with \logmtot{}$>11.6$ in \logmhalo{}$>14.2$
-    haloes are on average $\sim20$\% larger than the centrals from \logmhalo{}$<14.0$
+    haloes are on average $\sim20$\% larger than centrals in \logmhalo{}$<14.0$
     haloes at fixed \mtot{}.
-    This result is robust against the ranges of \mstar{} over which the fit is 
+    This result is robust against the stellar mass range over which the fit is 
     performed and against the definitions of  `total' \mstar{} and half-light 
     radius\footnote{Using \mstar{} within 120 or 150 kpc, or using the 
-    $R_{\mathrm{50}}$ derived within these apertures do not change the results.}.
+    $R_{\mathrm{50}}$ derived within these apertures does not change the results.}.
 
@@
     We estimate the average $\gamma$ of both samples at \logmtot{}$>11.6$. 
-    For the \rbcg{} sample, $<\gamma> = 4.2\pm0.4$; for the \nbcg{} one, 
+    For \rbcg{}, $<\gamma> = 4.2\pm0.4$ and for \nbcg{}, 
     $<\gamma> = 3.8\pm0.3$. 
     The environmental dependence of $R_{\mathrm{50}}$ at fixed \mtot{} is more 
-    significant than the \citet{HCompany13} result, although the uncertainty 
-    is large for our small samples. 
-    Such environmental dependence of `size' is much weaker than the certain 
-    model prediction (e.g., \citealt{Shankar2014}).
-    It is important to remember that the uncertainties of both mass and size can 
-    wash out signals of stronger environment--dependence on mass--size plane 
-    (e.g., \citealt{HCompany13}), and direct comparison of \mden{} profiles or 
-    the \mtot{}--\minn{} relation may serve as a better tracer of the environment 
-    dependence. 
-    }
+    significant than the \citet{HCompany13} result but weaker than some 
+    model predictions (e.g., \citealt{Shankar2014}).}
+    %It is important to remember that the uncertainties in both mass and size can 
+    %wash out signals of stronger environment--dependence on mass--size plane 
+    %(e.g., \citealt{HCompany13}), and direct comparison of \mden{} profiles or 
+    %the \mtot{}--\minn{} relation may serve as a better tracer of the environment 
+    %dependence. 
+    %}
 
@@
     We qualitatively compare our results with the mass--size relation for 
-    $0.2 < z < 0.5$ group ETGs in the COSMOS survey (
-    \citealt{HueartasCompany2013b}; HC13a; cyan dashed line).
-    HC13a measures luminosity and size of each galaxy by fitting a 2--D 
-    single--\ser{} model to the \textit{HST}/ACS \texttt{F814W} image. 
-    And the stellar mass is derived from SED fitting based on very similar 
-    model assumptions. 
-    HC13a uses circularized effective radius 
-    ($R_{\mathrm{e,Circ}} = R_{\mathrm{e,Fit}} \times \sqrt{b/a}$) in their work. 
-    Here we empirically correct their effective radius to the measured values 
-    assuming an average $<b/a>=0.75$.
-    At similar redshift, the mass-size relation from HC13a lies below our 
-    best--fit relation, while the slopes are quite similar.
+    $0.2 < z < 0.5$ ETGs in group-scale dark matter halos in COSMOS (\citealt{HueartasCompany2013b}; HC13a; cyan dashed line).
+    HC13a measure luminosities and sizes using 2--D 
+    single--\ser{} models applied to \textit{HST}/ACS \texttt{F814W} images. HC13a use circularized effective radii 
+    ($R_{\mathrm{e,Circ}} = R_{\mathrm{e,Fit}} \times \sqrt{b/a}$). We empirically correct their measurements assuming an average $<b/a>=0.75$.
+    At similar redshifts, the mass-size relation from HC13a lies below our 
+    best--fit relation but the slopes are similar.
     }
@@
     who studied $z\leq 0.09$ central ETGs in $12.5 \le$ \logmh{} $< 15$ haloes. 
-    HC13b use the group catalogue by \citet{Yang2007} to estimate halo mass. 
+    HC13b use the \citet{Yang2007} group catalog to estimate halo mass. 
     In contrast to the present study, HC13b find no environment dependence in the 
-    mass--size relation for central galaxies in the range $12.5\le$ \logmh{} $<15.0$. 
+    mass--size relation for central galaxies. 
     They obtain effective radii from single-\ser{} model fitting to SDSS 
-    images and \mstar{} based on SED fitting using the BC03 (\citealt{BC03}) 
+    images and derive stellar mass based on SED fitting using the BC03 (\citealt{BC03}) 
     synthetic population model. 
@@
     We further add $+0.1$dex to the HSC13 stellar masses to account for a systematic 
-    offset between BC03 and our FSPS model (see Paper~1). 
-    Here we see that our massive galaxies follow the HC13a relation reasonably well
-    (with slightly shallower slopes) despite the differences in redshift. 
-    }
+    offset between BC03 and our FSPS model (see Paper~1). Our overall mass-size relation is in good agreement with HC13a.}
 
@@
     Differences between the HC13ab and our results may relate to differences 
-    in modelling methods and the shallower ACS/\texttt{F814W} images. 
-    As for HC13b, it is also possible that the shallower SDSS image hides the
-    environmental dependence.  
-    The low surface--brightness stellar haloes that present the best evidence for 
-    environmental dependence using the deep HSC images are impossible to see and 
-    are extremely difficult to model using the SDSS ones. 
-    Before one can reliably investigate topics such as the environment dependence 
-    of mass--size relation and its redshift evolution, impacts from crucial systematics 
-    like the imaging qualities and model assumptions much be carefully addressed. 
-    Both shallow images and oversimplified models can lead to biased results 
-    (e.g., see Appendix~\ref{app:gama} for the issue with single-\ser{} model 
-    using SDSS images).
+    in modeling methods, and to the shallower ACS/\texttt{F814W} imaging. 
+    As for HC13b, it is also possible that the shallower SDSS image masks the environmental dependence.
+Figure~\ref{fig:prof_1} shows that the most pronounced differences are at $R>50$ kpc -- these would be difficult to detect with shallow imaging.
+Both shallow images and oversimplified models can lead to biased results.
+We highlight such effects in Appendix~\ref{app:gama} by comparing luminosities from HSC to those from single-\ser{} model applied to SDSS.
     }
@@
 
-    Now we investigate the relationship between \mtot{}, \minn{}, and \mhalo{}. 
+    We now investigate the relationship between \mtot{}, \minn{}, and \mhalo{}. 
     Compared to the mass--size relation, the \mtot{}--\minn{} relation is not plagued 
@@
 
-    The right panel of Fig \ref{fig:scaling_relation} compares \rbcg{} and \nbcg{}
-    galaxies on the \mtot{}--\minn{} plane. 
-    We find that there is an offset between the overall distributions of these two
-    samples and that they follow distinct best-fitting \mtot{}--\minn{} relations. 
+    The right panel of Fig \ref{fig:scaling_relation} compares our two samples on the \mtot{}--\minn{} plane. The two samples follow distinct best-fitting \mtot{}--\minn{} relations. 
     For \rbcg{} galaxies with \logmtot{}$>11.6$ we find:
@@
 
-    These results are robust against the exact choice for the \mtot{} range over which 
-    the fit is performed. 
-    These results are also robust when we replace \minn{} with the stellar 
+    These results are robust against the exact choice of the stellar mass range over which 
+    the fit is performed. These results are also unchanged when we replace \minn{} with the stellar 
     mass within a 5- or 15-kpc aperture, or if \mtot{} is replaced with a stellar mass 
@@
     \song{
-    From Figure \ref{fig:scaling_relation} we can draw the same conclusions as in 
+    Figure \ref{fig:scaling_relation} presents the same conclusions as in 
     the previous section, namely that at fixed \mtot{}, central galaxies in more massive 
-    haloes tend to have a smaller fraction of stellar mass in their inner regions and 
-    higher \mstar{} in their outer stellar haloes.  
+    haloes tend to have a smaller fraction of stellar mass in their inner regions and more prominent outer stellar haloes.  
     }
@@
 
-    In Paper~I, we show that the ellipticity of the outer stellar halo increases with
-    \mtot{}, while in contrast, rest-frame colour gradients do not display strong 
-    \mtot{} dependencies. 
+    In Paper~I, we show that the ellipticity of the outer stellar halo increases with stellar mass but that rest-frame colour gradients do not depend strongly on stellar mass.
 In this paper, we take this analysis one step further to investigate whether either
-    of these quantities display a halo mass dependency. 
+    of these quantities depends on halo mass. 
     We focus on ellipticity and colour profiles within 5--60 kpc where we can ignore
@@
     Figure \ref{fig:ell_color} shows the average ellipticity, $g-r$, and $g-i$ colour 
-    profiles for galaxies living in more and less massive dark matter haloes at both 
-    fixed \mtot{} and fixed \minn{}. 
-    We also compared our results with previous studies that are based on stacked SDSS 
-    images (e.g., \citealt{LaBarbera2010, Tal2011, DSouza2014}). 
-    Figure \ref{fig:ell_color} shows that:
+    profiles for galaxies at fixed \mtot{} and fixed \minn{}. Our main findings are:
 
@@
             The ellipticity profiles of massive central galaxies do not depend on 
-            halo mass at fixed \mtot{} at $R<60$ kpc. 
+            halo mass at fixed \mtot{} at $R<60$ kpc (upper left panel). 
             }
@@
         \item \song{
-            However, the ellipticities of massive galaxies are different in the 
-            outskirts at fixed \minn{}. 
-            This further suggests that the more elongated outer stellar haloes 
-            of massive haloes may relate to accreted stars.
-            }
-
-        \item Massive central galaxies in more and less massive dark matter haloes 
-            display similar rest-frame colour gradients (at $r<60$ kpc) at fixed 
-            \mtot{} and at fixed \minn{}.
+            However, we do find that at fixed \minn{}, galaxies in massive halos have more elliptical outer stellar halos compared to galaxies in low mass halos (upper right panel).
+This may be further evidence that elongated outer stellar haloes are built from accreted stars.
+            }
+
+        \item We find no evidence that the rest-frame colour gradients (at $r<60$ kpc) of massive galaxies depend on halo mass.
 
@@
     The fact that we find smooth ellipticity profiles and shallow gradients favors 
-    the idea of using the flux-weighted average isophotal shape to extract 1-D \mden{} 
-    profiles of massive galaxies. 
-    The similarity of average rest-frame colour profiles between the \rbcg{} and \nbcg{}
-    samples suggests that \mden{} profiles based on single average \m2l{} will not bias 
-    our comparisons.
+    the idea of using a flux-weighted average isophotal shape to extract 1-D \mden{} 
+    profiles for massive galaxies.
+The similarity in the average rest-frame colour profiles demonstrates that our results can not simply be explained by differences in radial \m2l{} ratios between the two samples.
 
@@
     Color gradients on these scales may be sensitive to other physical processes and 
-    deserve future investigation using a 2-D modelling method and/or images with higher 
+    deserve future investigation using 2-D modelling methods and/or images with higher 
     spatial resolution.
@@
     Using deep images from the HSC survey, we show that the stellar mass distributions 
-    of massive central galaxies at $0.3 < z < 0.5$ depend on their environment or 
-    \mhalo{}. 
-    At fixed \mtot{} or \minn{}, we find that central galaxies from more massive 
-    haloes on average have a larger half-light radius and host more prominent outer 
-    stellar haloes.
+    of massive central galaxies at $0.3 < z < 0.5$ depend on halo mass. At fixed total galaxy mass, central galaxies in massive halos have larger half-light radii and host more prominent outer 
+    stellar haloes compared to galaxies in low mass haloes. We also find that 
+    the outer stellar haloes ($R>50$ kpc) of massive galaxies show the strongest 
+    variations with halo mass.
 
@@
     formation of \textit{in situ} stars in massive central galaxies. 
-    After the rapid quenching of star formation, the assembly of massive galaxies in 
-    the second phase is dominated by accretion of satellite galaxies through (mostly) 
+    After a rapid quenching of star formation, the subsequent assembly of massive galaxiesis  dominated by the accretion of satellite galaxies through (mostly) 
     non--dissipative mergers. 
     Dry minor mergers are efficient at depositing \textit{ex situ} stars in the 
-    outskirts of massive galaxies (e.g., \citealt{Oogi2013, Bedorf2013}). 
-    If minor mergers become more frequent in more massive dark matter haloes, 
-    they can result in slightly different stellar mass distributions and larger 
-    effective radii for massive central galaxies.
-    }
-
-    \citet{Shankar2014} studied the environment dependence of galaxy size using 
-    different semi-analytic models. 
+    outskirts of massive galaxies (e.g., \citealt{Oogi2013, Bedorf2013}) and hence in building up outer stellar haloes.
+The fact that minor mergers become more frequent in more massive dark matter haloes could lead to the halo mass dependence of galaxy profiles that we identify in Figure~\ref{fig:prof_1}.}
+
+    \citet{Shankar2014} studied the environment dependence of galaxy size using semi-analytic models. 
     They predict that at fixed stellar mass, the median size of central galaxies 
@@
     minor--merger rate could still increase with halo mass if the dynamical friction
-    time is short (e.g., \citealt{Newman2012}). 
-    Therefore, massive central galaxies with $11.5 <$\logms{}$<12.0$ from 
-    massive haloes (\logmh{}$>14.0$) can have up to four times more minor mergers 
-    (1:100--1:3) compared to those in less massive haloes at a similar stellar 
-    mass. 
+    timescale is short (e.g., \citealt{Newman2012}).
+Massive central galaxies with $11.5 <$\logms{}$<12.0$ living in haloes with \logmh{}$>14.0$ can have up to four times more minor mergers (1:100--1:3) compared to those in less massive haloes at fixed galaxy mass.
 An increase in the minor-merger rate as a function of halo mass can lead to a
@@
     \song{
-    Our results are broadly consistent with these predictions and also suggest that 
-    the outer stellar haloes ($r>50$ kpc) of massive galaxies show the strongest 
-    variations with halo mass. 
-    At the same time, we should point out that the comparison at low redshift alone 
-    cannot rule out some other scenarios.  
-    For instance, \citet{Buchan2016} suggest that central galaxies in more massive 
-    haloes could be born with more extended structure. 
-    A more careful comparison with higher redshift observations can distinguish between 
-    these different scenarios.
-    }
-
-%% ------------------------------------------------------------------------------------ %% 
-\subsection{Environmental Dependence of the Inner Regions of Massive Galaxies}
-
-    Our results also show that the centrals of more massive haloes have slightly 
-    shallower inner \mden{} slopes and a smaller \mtot{} fraction within the inner 
-    10 kpc.
-    \song{
-    This cannot be solely explained by the choice of a finite aperture to 
-    estimate `total' \mstar{}: Assuming that centrals from more massive haloes 
-    have more extended \mden{} profiles, integration out to a larger aperture makes 
-    the differences between \rbcg{} and \nbcg{} galaxies on the \mtot{}--\minn{} 
-    plane even more significant.
-    However, from this observation alone, we cannot determine which exact physical 
-    process is responsible for differences in the inner regions. 
-    Many different physical processes can shape and alter the \mden{} profile within 
-    the inner 10 kpc.
-    }
-
-    \song{
-    In hydrodynamic simulations, intense dissipative processes help create a 
-    self-similar de~Vaucouleurs--like ($n{\sim} 4$) \mden{} profile in the inner
-    part of massive galaxy (e.g., \citealt{Hopkins2008}).
-    } 
-    Major mergers can redistribute the inner stellar mass distributions, but 
+    Our results are broadly consistent with these predictions.
+However, our results alone cannot rule out other explanations for this halo mass dependence.
+For instance, \citet{Buchan2016} suggest that central galaxies in more massive haloes have more extended in-situ components.
+Comparisons with higher redshift observations will enable us to distinguish between these two formation scenarios.
+    }
+
+%% ------------------------------------------------------------------------------------ %% 
+\subsection{The Inner Regions of Massive Galaxies}
+
+Figure \ref{fig:scaling_relation} shows that, at fixed total galaxy mass, centrals in high mass haloes have slightly shallower inner \mden{} slopes lower values of \minn{} compared to those in low mass haloes.
+\song{We have tested that this cannot be solely explained by the choice of a finite aperture (100 kpc) to estimate `total' galaxy mass.
+Integrating our profiles our to larger radii makes the differences between \rbcg{} and \nbcg{} galaxies on the \mtot{}--\minn{}
+    plane even more significant \alexie{reference to somewhere in the appendix?}.
+In hydrodynamic simulations, intense dissipative processes help create a self-similar de~Vaucouleurs--like ($n{\sim} 4$) inner density profile (e.g., \citealt{Hopkins2008}).
+However, there are a variety of physical processes that can shape and alter the inner  profile which we now discuss.
+    }
+
+    First, major mergers can redistribute the inner stellar mass distributions, but 
     the major--merger rate does not strongly depend on halo mass 
     (e.g., \citealt{Shankar2014}). 
-    However, minor mergers, which do depend on halo mass, can modify the central 
-    surface brightness profiles of the remnants (e.g., \citealt{BoylanKolchin2007}). 
-    Depending on the structure and infalling orbits of satellites, a minor merger 
+    However, minor mergers, which do depend on halo mass, can also modify central 
+    surface brightness profiles (e.g., \citealt{BoylanKolchin2007}). 
+    Depending on the structure, and the orbits of infalling satellites, a minor merger 
     can make the inner \mden{} profiles either steeper or shallower.  
@@
 
-    \song{
-    Strong adiabatic expansion induced by powerful AGN feedback is another mechanism 
-    (e.g., \citealt{Fan2008}) that can modify the inner \mden{} profile. \
+    \song{Second, strong adiabatic expansion induced by powerful AGN feedback is another mechanism 
+    (e.g., \citealt{Fan2008}) that can modify stellar density profiles. \
     When the induced mass loss is efficient enough, it can lead to expanded 
     central stellar mass distribution and can significantly lower the inner \mden{}. 
-    }
+    } \alexie{Need reference also to Martizzi et al}
 
@@
     \song{
-    The impact of these processes on the \mden{} profiles and their dependency on 
-    \mhalo{} are important issues that deserve more investigations. 
-    We plan to shed further light on the very inner regions of these massive galaxies 
-    using higher resolution images and 2-D modelling to account for the PSF.
-    }
+    The impact of these processes on \mden{} profiles and their dependency on 
+    halo mass are important questions that warrant further investigation.}
 
@@
 
-    Many previous works that focused on the mass--size relation found this relation 
+    Many previous studies that focused on the mass--size relation found this relation 
     to be independent of halo mass or environment at $z\sim 0.0$ 
     (e.g., \citealt{Nair2010, Maltby2010, Cappellari2013, HCompany13}).
-    We argue that, both the shallower imaging depth and the oversimple model 
-    (e.g., single-\ser{} or de~Vaucouleurs model) used in the fitting can both 
-    contribute to this difference.
+Shallow imaging and the use of models which do not necessarily well describe massive galaxies (e.g., single-\ser{} or de~Vaucouleurs models) may of masked the effect revealed in this paper.
 In Appendix~\ref{app:gama}, we use the \rbcg{} and \nbcg{} galaxies that overlap
@@
     massive dark matter haloes actually show more prominent outer stellar haloes.
-    \song{
-    These issues complicate the comparisons of mass--size relations derived from 
-    different images or using different methods.
-    }
-
-    At low redshift, \citet{Cerbrian2014} find that ETGs with \logms{}$>11.5$ are 
-    slightly larger in more massive haloes, and they also show that this trend is 
+    \song{These types of issues complicate the comparisons of mass--size relations derived from different images or using different methods.
+For this reason, we only present a qualitative comparison with previous work}
+
+    At low redshift, \citet{Cerbrian2014} find ETGs with \logms{}$>11.5$ to be slightly larger in more massive haloes, and they also show that this trend is 
     reversed at lower \mstar{}. 
@@
     }
-    \citet{Yoon2017} present a careful study of a large sample of $z\sim0.1$ SDSS 
-    ETGs using a nonparametric method; in their research, they recover a clear 
-    environment dependence of mass--size relation at \logms{}$>11.2$. 
-    They conclude that, at the same \mstar{}, massive ETGs from dense environment 
-    are 20--40\% larger compared to those in an underdense environment.
+    \citet{Yoon2017} present a study of a large sample of $z\sim0.1$ SDSS 
+    ETGs using a nonparametric method. They also find an environmental dependence of the mass--size relation at \logms{}$>11.2$. Similar to our work, they find that massive ETGs in dense environments 
+    are 20--40\% larger compared to those in underdense environments.
     Recently, \citet{Charlton2017} use a single-\ser{} model for galaxies at 
     $0.2 < z < 0.8$ in the Canada France Hawaii Lensing Survey (CFHTLenS) 
-    (\citealt{Heymans2012}) and their galaxy--galaxy 
+    (\citealt{Heymans2012}) together with galaxy--galaxy 
     lensing measurements to show that larger galaxies tend to live in more massive 
@@
     These results are in broad agreement with those presented here.
-    \song{
-    With the help of weak lensing measurements using HSC images, we will in future 
-    work further explore the connection between the dark matter halo mass and the 
-    stellar mass distributions of their central galaxies. 
-    }
-
-    \song{
-    As it becomes clear that structures of massive galaxies do depend on 
-    environment, the origin of such dependence and its redshift evolution 
-    naturally becomes the focus of future studies. 
-    Several works find strong environment dependence of the mass--size relation 
+
+    \alexie{this needs rewritting, redshift evolution ...}\song{With a greater number of studies that are now beginning to reveal the halo mass dependence of the sizes and profiles of massive galaxies, more detailed comparisons with theoretical predictions for this effect will become of increasing interest.
+Some theoretical studies predicts a strong environmental dependence of the mass--size relation
     for massive quiescent or early-type galaxies
@@
     automatically guarantee a match to the mass--size relation. 
-    Furthermore, while some efforts have been made to use consistent size definitions 
+    Furthermore, while some effort have been made to use consistent size definitions 
     (\citealt{McCarthy2017}), more often than not, comparisons of the mass--size relation 
@@
     size of galaxies of different types and at different redshifts, it sometimes leads
-    to biased results as it is no longer an appropriate model for certain types of galaxies. 
-    Sizes derived from a 1-D curve-of-growth is more model independent and has been 
-    shown to be useful in revealing environmental dependence of the mass--size relation 
-    (e.g., \citealt{Yoon2017}, and this work), but it does not take the PSF convolution 
-    effect into account, and it depends on imaging depth and background subtraction.
+    to biased results as it does not universally describe all types of galaxies. Sizes derived from 1-D curves-of-growth are more model independent and have been 
+    shown to be useful in revealing the environmental dependence of the mass--size relation 
+    (e.g., \citealt{Yoon2017}, and this work), but this method does not take the PSF into account. It also depends on imaging depth and background subtraction.
 
@@
     between observations and theoretical predictions.
+Even better, we argue that galaxy mass profiles can be compared directly with predictions from hydrodynamic simulations, bypassing the need completely for `size' estimates.
 
@@
 
+    In this paper, we investigate how the stellar mass profiles of massive galaxies depend on the masses of their host dark matter haloes.
 Using high-quality images from the first $\sim100$ deg$^2$ of the
-    Hyper Suprime-Cam Subaru Strategic Program, we group a large sample of massive 
-    central galaxies at $0.3 < z < 0.5$ into two categories based on their dark matter
-    halo mass (\mhalo{}$\simgt 10^{14.2} M_{\odot}$ and 
-    \mhalo{}$\simlt 10^{14} M_{\odot}$), and we study how their stellar mass 
-    distributions out to 100 kpc depend on their environments (or \mhalo{}). 
+    Hyper Suprime-Cam Subaru Strategic Program, we divide central galaxies at $0.3 < z < 0.5$ into two samples according to dark matter halo mass (\mhalo{}$\simgt 10^{14.2} M_{\odot}$ and 
+    \mhalo{}$\simlt 10^{14} M_{\odot}$). Exquisite data from HSC enables us to extract stellar profiles for individual galaxies in these two samples out to 100 kpc.
+
     Our main results are as follows:
@@
 
-        \item At fixed \mtot{}, we find that massive central galaxies display \mden{} 
-            profiles that have large intrinsic scatter in the outer stellar haloes and 
-            present a subtle but systematic trend with \mhalo{}.
-            On average, massive central galaxies in more massive haloes have slightly 
-            shallower inner \mden{} profiles and more prominent outer haloes. 
-            This suggests that the environment affects the assembly of massive central
-            galaxies at fixed `total' stellar mass.
-
-        \item At fixed \minn{}, massive central galaxies in more massive haloes 
-            possess much more extended stellar haloes than those in smaller haloes. 
-            Assuming that \minn{} traces the amount of `\textit{in situ}' stars in 
-            massive galaxies, this result is consistent with the picture that more 
-            massive haloes favor the growth of extended stellar haloes in their central 
-            galaxies through more frequent mergers.
-
-        \item \song{
-            Such environmental dependence is also reflected on the plane of
-            \mtot{} versus $R_{\mathrm{50}}$, and \mtot{} versus \minn{}. 
-            And we propose that the \mtot{}-\minn{} relation can be a better tool 
-            to diagnose the assembly of massive central galaxies without using `size' 
-            with ambiguous definition.
-            }
-
-        \item \song{
-            At $R < 60$ kpc, the ellipticity and rest--frame colour profiles of 
-            massive galaxies do not depend on halo mass at fixed \mtot{}.
-            And, at fixed \minn{}, massive centrals from more massive haloes tend 
-            to have more elongated outer stellar envelopes.
-            }
+    \item At fixed \mtot{}, central galaxies in high mass haloes 
+            display shallower \mden{} profiles compared to those in low mass haloes: they have flatter inner \mden{} profiles and 
+            more significant outer stellar envelopes.  This trend is most pronounced at $R>50$ kpc and thus would easily be missed with shallow imaging data.
+
+        \item Massive galaxies matched by \minn{} display a range of  \mtot{} values and a large intrinsic scatter in the amplitude of their outer stellar envelopes.
+
+        %\item At fixed \minn{}, massive central galaxies in more massive haloes 
+          %  possess much more extended stellar haloes than those in smaller haloes. 
+         %   Assuming that \minn{} traces the amount of `\textit{in situ}' stars in 
+          %  massive galaxies, this result is consistent with the picture that more 
+          %  massive haloes favor the growth of extended stellar haloes in their central 
+           % galaxies through more frequent mergers.
+
+        \item \song{This environmental dependence is also reflected in the mass-size relation, as well as in the \mtot{}-\minn{} relation.
+We propose that simple elliptical aperture masses such as \mtot{} and\minn{} are better statistics to summarize the properties of galaxy profiles than commonly used `size' estimates such as $R_e$.}
+
+      \item \song{At fixed \minn{}, galaxies in massive halos have more elliptical outer stellar halos compared to galaxies in low mass halos.
+This may be further evidence that elongated outer stellar haloes are built from accreted stars.}
+
+        \item At fixed galaxy mass and at $r<60$ kpc, the rest-frame colour gradients of massive galaxies do not depend on dark matter halo mass.
 
@@
     These results highlight the importance of deep, high-quality images for studying 
-    the assembly of massive haloes and their central galaxies. 
-    We are currently working on combining the current results with weak lensing 
-    measurements of dark matter haloes around these massive galaxies, and comparing 
-    our results with hydrodynamic simulations to gain more physical insight.
-
+    the assembly of massive dark matter haloes and their central galaxies.
+Future work will focus on a comparison between our data and  predictions from various hydrodynamic simulations.
+This will enable us to gain further insight into the physical mechanisms that drive the trends discovered in this paper.
 %% ------------------------------------------------------------------------------------ %%
@@
   SH thanks Feng-Shan Liu for sharing the \mden{} profile of the $z\sim1$ BCG from 
-  his work.
+  his work. This material is based upon work supported by the National Science Foundation under Grant No. 1714610.
 

### 2017-12-05 draft/paper2_v9.tex
New edits for Felipe's and Chris' comments

@@
 
-\begin{abstract}  We use ${\sim}100$ deg$^2$ of 
-    deep ($>28.5$ \sb{} in $i$-band), high-quality 
-    (median 0.6\asec seeing) imaging data from the Hyper Suprime--Cam (HSC) survey to reveal the halo mass dependence of the surface mass density profiles and outer stellar envelopes of massive galaxies.
+\begin{abstract}
+
+    We use ${\sim}100$ deg$^2$ of deep ($>28.5$ \sb{} in $i$-band), high-quality 
+    (median 0.6\asec seeing) imaging data from the Hyper Suprime--Cam (HSC) survey to 
+    reveal the halo mass dependence of the surface mass density profiles and outer 
+    stellar envelopes of massive galaxies. 
     The $i$-band images from the HSC survey reach ${\sim}4$ magnitudes deeper than 
@@
     These differences translate into a halo mass dependence of the mass--size relation. 
-Central galaxies in haloes with \logmh{}$>14.0$ are $\sim 20$\% larger in $R_{\mathrm{50}}$ at fixed \mtot{}.
+    Central galaxies in haloes with \logmh{}$>14.0$ are $\sim 20$\% larger in 
+    $R_{\mathrm{50}}$ at fixed \mtot{}. 
     Such dependence is also reflected in the relationship between the stellar mass 
-    within 10 and 100 kpc.  Comparing to the mass--size relation, the \mtot{}--\minn{} relation avoids the 
+    within 10 and 100 kpc.  
+    Comparing to the mass--size relation, the \mtot{}--\minn{} relation avoids the 
     ambiguity in the definition of size, and can be straightforwardly compared with 
@@
     brightness or mass density profiles (e.g., \citealt{Huang2013a, Huang2013b, 
-    Oh2017}, optical colour gradients (e.g., \citealt{LaBarbera2010, LaBarbera2012}), 
+    Oh2017}), optical colour gradients (e.g., \citealt{LaBarbera2010, LaBarbera2012}), 
     and stellar population gradients \citep[e.g.,][]{Coccato2010, Coccato2011, 
@@
     The major merger rate is not a strong function of progenitor halo mass 
-    (e.g., \citealt{Shankar2015}) but minor mergers can still play an important 
-    role in determining the structures of central galaxies 
-    (e.g., \citealt{Guo2011, Yoon2017}). 
+    (e.g., \citealt{Shankar2015}) but minor mergers rate should increase with 
+    halo mass, hence play an important role in determining the structures of central 
+    galaxies (e.g., \citealt{Guo2011, Yoon2017}). 
     Minor mergers are efficient at `puffing up' the outskirts of massive 
@@
 	\song{
-    Deep images of massive galaxies can probe the outer stellar halos of massive 
+    Deep images of massive galaxies can probe their outer stellar halos of massive 
     galaxies and test these predictions. 
@@
     profiles of massive galaxies correlates with halo mass. 
-    We conclusively show that the sizes and stellar haloes of massive central galaxies 
-    depend on dark matter halo mass. 
+    We conclusively show that the sizes and stellar haloes of massive central 
+    galaxies depend on dark matter halo mass. 
     In other words, we reveal the halo mass dependence of the mass--size relation 
@@
 %% ------------------------------------------------------------------------------------ %% 
+%% Sample Selection and Data Reduction
+%% ------------------------------------------------------------------------------------ %% 
+\section{Sample Selection and Data Reduction}
+    \label{sec:data}
+
+    We refer the reader to Paper I for an in-depth description of the sample selection 
+    and data reduction processes. 
+    Here, we briefly summarize the main steps.
+
+    We use imaging data from the HSC internal data release 
+    \texttt{S15B}, which is very similar to the Public Data Release 1 
+    (\citealt{HSC-DR1} and covers ${\sim} 110$ deg$^2$ in all five-band ($grizy$) to 
+    the full depth in the wide field. 
+    The data are reduced by \texttt{hscPipe 4.0.2}, a derivative of the 
+    Large Synoptic Survey Telescope (LSST) pipeline (e.g.\ \citealt{Juric2015}; 
+    \citealt{Axelrod2010}), modified for HSC (\citealt{HSC-PIPE}).
+    The pixel scale of the reduced image is $0.168$\asec{}.
+    We use $i$-band images for extracting surface brightness profiles. 
+    HSC $i$-band images are typically 3--4 mag deeper than SDSS 
+    (Sloan Digital Sky Survey; e.g., \citealt{SDSS-DR7, SDSS-DR8, SDSS-DR12})  
+    and have superb seeing conditions (mean $i$-band seeing has FWHM$=0.6$\asec{}).
+
+    In Paper~I, we select a sample of 25286 bright galaxies with spectroscopic 
+    redshifts or reliable `red-sequence' photometric redshifts (\citealt{Rykoff2014}) 
+    at $0.3<z<0.5$. 
+    Within this redshift range, we have a large enough volume 
+    ($\sim5\times 10^6$ Mpc$^3$) to sample the galaxy stellar mass function above 
+    \logms$>11.6$, and we can spatially resolve galaxies profiles to $\sim 5$ kpc 
+    ($1.0^{\arcsec}$ corresponds to 4.4 and 6.1 kpc at $z=0.3$ and 0.5, respectively). 
+    \song{
+    Massive galaxies should experience little structural evolution and 
+    size growth between $z=0.5$ and 0.3 ($\sim$1.5 Gyr time span) 
+    based on model predictions (e.g., \citealt{Shankar2015}).
+    }
+
+    After carefully 
+    masking out surrounding neighbors and accounting for the subtraction of the 
+    background light, we derive $i$-band surface brightness profiles out to 100 kpc. 
+    We use the broadband spectral energy distributions (SED) fitting code 
+    \texttt{iSEDFit}\footnote{http://www.sos.siena.edu/~jmoustakas/isedfit/} 
+    (\citealt{Moustakas13}) to measure \m2l{} ratios and $k$--corrections using 
+    five-band forced \cmodel{} magnitudes from \texttt{hscPipe}. 
+    We assume a \citet{Chabrier2003} IMF, the Flexible Stellar Population 
+    Synthesis models\footnote{http://scholar.harvard.edu/cconroy/sps-models}
+    (FSPS; \texttt{v2.4}; \citealt{FSPS}, \citealt{Conroy2010}), the 
+    \citet{Calzetti2000} extinction law, and a simple delayed-$\tau$ model for 
+    star formation histories (SFH). 
+    Using HSC data, we can measure the \mden{} profiles of massive galaxies to 
+    $\sim 100$ kpc, and we integrate these profiles within elliptical isophotal
+    apertures at different physical radii. 
+    As explained in Paper~I, we focus on the two following metric masses:
+
+    \begin{itemize}
+
+        \item Stellar mass within 10 kpc (hereafter noted \minn{}), which we use 
+            as a proxy for the stellar mass of the \textit{in situ} stellar 
+            component. 
+            This is motivated both by observations and simulations 
+            (e.g.~\citealt{vanDokkum2010}, \citealt{RodriguezGomez2016}). 
+            The value of 10 kpc that we quote here corresponds to the radius of the 
+            major axis of the isophotal ellipse.
+
+        \item Stellar mass within 100 kpc (hereafter noted \mtot{}). 
+            We use \mtot{} as a proxy for the `total' stellar mass. 
+            In Paper~I we show that \mtot{} recovers more light compared to 
+            HSC \cmodel{} photometry with differences that can be a large as 0.2 dex 
+            in magnitude.
+
+   \end{itemize}
+
+   We use these two simple metric masses to explore the \mstar{}-dependence of the 
+   fraction of accreted stars and to reveal the diversity of stellar envelopes among 
+   massive galaxies. 
+   In practice, we also have the full profiles for each galaxy and can cast our 
+   results in terms of the full stellar mass profiles. 
+   However, in many cases we find it useful to display figures using the simpler 
+   \minn{} and \mtot{} quantities. 
+   In Figure \ref{fig:m100_m10_color}, we highlight the diversity of galaxies as a 
+   function of \minn{} and \mtot{}. 
+   Figure \ref{fig:m100_m10_color} shows a subsample of massive galaxies with very 
+   similar \minn{} but show a large range of \mtot{}. 
+   We use these two aperture masses to guide our comparison of massive galaxies 
+   as a function of environment.
+
+%% ------------------------------------------------------------------------------------ %% 
   \begin{figure*}
@@
           galaxies. 
-          Left: Halo mass dependence of galaxy profiles at fixed `total' stellar mass 
-          (\mtot{}). 
-          Right: Halo mass dependence of galaxy profiles at fixed `inner-mass' 
-          (\minn{}). Orange and red lines correspond to central galaxies living in 
+          \textbf{Left}: Halo mass dependence of galaxy \mden{} profiles at fixed 
+          `total' stellar mass (\mtot{}). 
+          \textbf{Right}: Halo mass dependence of galaxy \mden{} profiles at fixed 
+          `inner-mass' (\minn{}). 
+          In each plot, we match the two samples so that they share similar 
+          distributions of mass and redshift (Appendix~\ref{app:match}).
+          We use $R^{1/4}$ as $x$--axis to provide a balanced view of both the central 
+          and outer regions of the galaxy.
+          Orange and red lines correspond to central galaxies living in 
           haloes with \logmh{} $\geq 14.2$. 
@@
 %% ------------------------------------------------------------------------------------ %%    
-%% Sample Selection and Data Reduction
-%% ------------------------------------------------------------------------------------ %% 
-\section{Sample Selection and Data Reduction}
-    \label{sec:data}
-
-    We refer the reader to Paper I for an in-depth description of the sample selection 
-    and data reduction processes. 
-    Here, we briefly summarize the main steps.
-
-    We use imaging data from the HSC internal data release 
-    \texttt{S15B}, which is very similar to the Public Data Release 1 
-    (\citealt{HSC-DR1} and covers ${\sim} 110$ deg$^2$ in all five-band ($grizy$) to 
-    the full depth in the wide field. 
-    The data are reduced by \texttt{hscPipe 4.0.2}, a derivative of the 
-    Large Synoptic Survey Telescope (LSST) pipeline (e.g.\ \citealt{Juric2015}; 
-    \citealt{Axelrod2010}), modified for HSC (\citealt{HSC-PIPE}).
-    The pixel scale of the reduced image is $0.168$\asec{}.
-    We use $i$-band images for extracting surface brightness profiles. 
-    HSC $i$-band images are typically 3--4 mag deeper than SDSS 
-    (Sloan Digital Sky Survey; e.g., \citealt{SDSS-DR7, SDSS-DR8, SDSS-DR12})  
-    and have superb seeing conditions (mean $i$-band seeing has FWHM$=0.6$\asec{}).
-
-    In Paper~I, we select a sample of 25286 bright galaxies with spectroscopic 
-    redshifts or reliable `red-sequence' photometric redshifts (\citealt{Rykoff2014}) 
-    at $0.3<z<0.5$. 
-    Within this redshift range, we have a large enough volume 
-    ($\sim5\times 10^6$ Mpc$^3$) to sample the galaxy stellar mass function above 
-    \logms$>11.6$, and we can spatially resolve galaxies profiles to $\sim 5$ kpc 
-    ($1.0^{\arcsec}$ corresponds to 4.4 and 6.1 kpc at $z=0.3$ and 0.5). 
-    \song{
-    Massive galaxies should experience little structural evolution and 
-    size growth between $z=0.5$ and 0.3 ($\sim$1.5 Gyr time span) 
-    based on model predictions (e.g., \citealt{Shankar2015}).
-    }
-
-    After carefully 
-    masking out surrounding neighbors and accounting for the subtraction of the 
-    background light, we derive $i$-band surface brightness profiles out to 100 kpc. 
-    We use the broadband spectral energy distributions (SED) fitting code 
-    \texttt{iSEDFit}\footnote{http://www.sos.siena.edu/~jmoustakas/isedfit/} 
-    (\citealt{Moustakas13}) to measure \m2l{} ratios and $k$--corrections using 
-    five-band forced \cmodel{} magnitudes from \texttt{hscPipe}. 
-    We assume a \citet{Chabrier2003} IMF, the Flexible Stellar Population 
-    Synthesis models\footnote{http://scholar.harvard.edu/cconroy/sps-models}
-    (FSPS; \texttt{v2.4}; \citealt{FSPS}, \citealt{Conroy2010}), the 
-    \citet{Calzetti2000} extinction law, and a simple delayed-$\tau$ model for 
-    star formation histories (SFH). 
-    Using HSC data, we can measure the \mden{} profiles of massive galaxies to 
-    $\sim 100$ kpc, and we integrate these profiles within elliptical isophotal
-    apertures at different physical radii. 
-    As explained in Paper~I, we focus on the two following metric masses:
-
-    \begin{itemize}
-
-        \item Stellar mass within 10 kpc (hereafter noted \minn{}), which we use 
-            as a proxy for the stellar mass of the \textit{in situ} stellar 
-            component. 
-            This is motivated both by observations and simulations 
-            (e.g.~\citealt{vanDokkum2010}, \citealt{RodriguezGomez2016}). 
-            The value of 10 kpc that we quote here corresponds to the radius of the 
-            major axis of the isophotal ellipse.
-
-        \item Stellar mass within 100 kpc (hereafter noted \mtot{}). 
-            We use \mtot{} as a proxy for the `total' stellar mass. 
-            In Paper~I we show that \mtot{} recovers more light compared to 
-            HSC \cmodel{} photometry with differences that can be a large as 0.2 dex 
-            in magnitude.
-
-   \end{itemize}
-
-   We use these two simple metric masses to explore the \mstar{}-dependence of the 
-   fraction of accreted stars and to reveal the diversity of stellar envelopes among 
-   massive galaxies. 
-   In practice, we also have the full profiles for each galaxy and can cast our 
-   results in terms of the full stellar mass profiles. 
-   However, in many cases we find it useful to display figures using the simpler 
-   \minn{} and \mtot{} quantities. 
-   In Figure \ref{fig:m100_m10_color}, we highlight the diversity of galaxies as a 
-   function of \minn{} and \mtot{}. 
-   Figure \ref{fig:m100_m10_color} shows a random subsample of massive galaxies with 
-   very similar \minn{} that have a large range of \mtot{}. 
-   We use these two aperture masses to guide our comparison of massive galaxies 
-   as a function of environment.
-
-%% ------------------------------------------------------------------------------------ %%    
 \subsection{Massive Central Galaxies from Different Environments}
@@
     We use the \redm{} \texttt{v5.10} \citep{Rykoff2014, Rozo2015b} cluster catalogue 
-    to help us construct two central galaxy samples.
+    to help us construct two central galaxy samples: one for high mass haloes, and 
+    one for low mass haloes.
 
@@
 
-    First, we build a sample of central galaxies in high mass haloes. We select 68 massive central galaxies from \redm{} clusters 
-    with richness $\lambda \geq 30$, with central probability $P_{\mathrm{Cen}} \geq 0.7$, and \logmtot{}$ >11.5$ 
-    at $0.3 < z < 0.5$ (63/68 have \logmtot{}$ >11.6$). 
+    First, we build a sample of central galaxies in high mass haloes. 
+    We select 68 massive central galaxies from \redm{} clusters with richness
+    $\lambda \geq 30$, with central probability $P_{\mathrm{Cen}} \geq 0.7$, and 
+    \logmtot{}$ >11.5$ at $0.3 < z < 0.5$ (63/68 have \logmtot{}$ >11.6$). 
     This $\lambda$ limit is chosen to mitigate incompleteness in the cluster catalogue
@@
     \song{
-    \citet{Simet2017} present a calibration of the \mhalo{}-$\lambda$ relation for \redm{} 
-    clusters using SDSS weak-lensing. Based on this calibration, our sample corresponds to central galaxies living 
+    \citet{Simet2017} present a calibration of the \mhalo{}-$\lambda$ relation for 
+    \redm{} clusters using SDSS weak-lensing. 
+    Based on this calibration, our sample corresponds to central galaxies living 
     in haloes with \mhalo{}$>10^{14.2}$~\msun{}. 
@@
     The median richness of the sample is $\lambda \approx 41$ 
-    (\mhalo{}$\approx 2.2 \times 10^{14}$~\msun{}), and there are 44 central galaxies in clusters with $\lambda>50$ 
-    (\mhalo{}$\approx 3.0 \times 10^{14}$~\msun{}).
+    (\logmhalo{}$\approx 10^{14.3}$), and there are 44 central galaxies 
+    in clusters with $\lambda>50$ (\mhalo{}$\approx 10^{14.5}$).
     We refer to this sample of \textbf{central galaxies in massive haloes} as 
@@
 
-    Second, we build a sample of central galaxies in low mass haloes. We begin by excluding all galaxies in \redm{} clusters with $\lambda > 20$.
-    \song{
-    We convert $\lambda$ to $M_{\mathrm{200b}}$ using the \citet{Simet2017} calibration. For each cluster, we compute $R_{\mathrm{200b}}$ using the \texttt{Colossus} Python package 
+    Second, we build a sample of central galaxies in low mass haloes. 
+    We begin by excluding all galaxies in \redm{} clusters with $\lambda > 20$.
+    \song{
+    We convert $\lambda$ to $M_{\mathrm{200b}}$ using the \citet{Simet2017} calibration. 
+    For each cluster, we compute $R_{\mathrm{200b}}$ using the \texttt{Colossus} Python 
+    package 
     (\citealt{Colossus})\footnote{\url{http://www.benediktdiemer.com/code/colossus/}}
-    provided by \citet{Diemer2015}} 
+    provided by \citet{Diemer2015}
+    } 
     We exclude all galaxies within a cylinder around each cluster, with a radius
@@
 
-    Satellite contamination in our sample should be low (e.g., \citealt{Reid2014, Hoshino2015, Saito2016, vanUitert2016}). 
-    For instance, the model from \citet{Saito2016} predicts that our \rbcg{} sample should only contain $\sim 7$\% satellites (corresponding to satellites with \logmtot{}$>11.6$ and living in haloes with \logmh$<14.0$).
+    Given the high stellar mass, satellite contamination in our sample should be 
+    low (e.g., \citealt{Reid2014, Hoshino2015, Saito2016, vanUitert2016}). 
+    For instance, the model from \citet{Saito2016} predicts that our \rbcg{} sample 
+    should only contain $\sim 7$\% satellites (corresponding to satellites with 
+    \logmtot{}$>11.6$ and living in haloes with \logmh$<14.0$).
 
@@
     (e.g.\ nearby foreground galaxy or bright stars). 
-    However, this small failure rate should not affect any of our results.
+    We exclude these galaxies from our analysis and this low failure rate should not 
+    affect any of our results.
 
@@
     In Paper~I, we explored the \mstar{}-dependence of these stellar haloes. 
-We now investigate the relation between \mden{} profiles, stellar haloes, and dark matter halo mass.
+    We now investigate the relation between \mden{} profiles, stellar haloes, and 
+    dark matter halo mass. 
     We remind the reader that although a circular aperture is shown on 
@@
     We show comparisons of \mden{} profiles at both fixed \mtot{} and fixed 
-    \minn{}. All comparisons are performed with a fixed underlying redshift
+    \minn{} (see Figure~\ref{fig:prof_1}). 
+    All comparisons are performed with a fixed underlying redshift
     distribution by matching samples in redshift in addition to stellar mass
@@
 %% ------------------------------------------------------------------------------------ %%     
-    Fig~\ref{fig:prof_1} compares the \mden{} profiles of massive central galaxies in low mass haloes to those in high mass haloes at fixed \mtot{} (left panel) and at fixed \minn{} (right panel).
+    Fig~\ref{fig:prof_1} compares the \mden{} profiles of massive central galaxies in 
+    low mass haloes to those in high mass haloes at fixed \mtot{} (left panel) and at 
+    fixed \minn{} (right panel). 
     The left panel compares galaxies that have similar `total' stellar mass. 
     The right panel uses \minn{} as a proxy for the \textit{in situ} component to 
-    compare the profiles of galaxies that presumably have similar early formation histories, but which live in different dark matter haloes today.
-This figure shows the main result of this paper, namely that
-    \emph{the \mden{} profiles of massive central galaxies show a clear dependence on 
-    dark matter halo mass at both fixed \mtot{} and \minn{}.}
+    compare the profiles of galaxies that presumably have similar early formation 
+    histories, but which live in different dark matter haloes today.
+    This figure shows the main result of this paper, namely that \emph{the \mden{} 
+    profiles of massive central galaxies show a clear dependence on dark matter halo 
+    mass at both fixed \mtot{} and \minn{}.}
 
@@
 
-        \item At fixed \mtot{}, central galaxies in high mass haloes 
-            display shallower \mden{} profiles compared to those in low mass haloes (i.e., they have flatter inner \mden{} profiles and 
-            more significant outer stellar envelopes).
+        \item At fixed \mtot{}, central galaxies in high mass haloes display shallower 
+            \mden{} profiles compared to those in low mass haloes (i.e., they have 
+            flatter inner \mden{} profiles and more significant outer stellar 
+            envelopes).
 
@@
             When matched by \mtot{}, differences in the inner regions appear 
-            to be small, but this is also driven by the use of a logarithmic y-axis. The difference becomes more apparent 
-            at $R>50$ kpc.  
+            to be small, but this is also driven by the use of a logarithmic y-axis. 
+            The difference becomes more apparent at $R>50$ kpc.  
             }
@@
             Those in massive dark matter halos have more prominent outer stellar haloes. 
-The scatter in the outer profiles observed in Figure \ref{fig:prof_1} is an \textit{intrinsic} scatter (not measurement error).
+            The scatter in the outer profiles observed in Figure \ref{fig:prof_1} is 
+            an \textit{intrinsic} scatter (not measurement error).
+
     \end{itemize}
@@
     \song{
-    Fig \ref{fig:prof_1} shows that the environmental dependence of the profiles of massive central galaxies is a subtle effect that is most prominent at large radii ($R>50$ kpc).
-    } This may explain why previous attempts to detect this effect using 
-    shallower images have often failed.
-
-    The effect becomes more pronounced for even more massive galaxies. This is shown in Fig~\ref{fig:prof_2} in Appendix~\ref{app:robust}.
-
-    In summary, we detect a subtle, but robust halo mass dependence of 
-    the profiles of massive central galaxies. 
+    Fig \ref{fig:prof_1} shows that the environmental dependence of the profiles of 
+    massive central galaxies is a subtle effect that is most prominent at large radii 
+    ($R>50$ kpc).
+    } 
+    This may explain why previous attempts to detect this effect using shallower images 
+    have often failed.
+
+    The effect becomes more pronounced for even more massive galaxies. 
+    This is shown in Fig~\ref{fig:prof_2} in Appendix~\ref{app:robust}.
+
+    In summary, we detect a subtle, but robust halo mass dependence of the profiles of 
+    massive central galaxies. 
     This dependence could be driven by the fact that massive halos have a larger minor 
     merger rate compared to less massive haloes. 
-    Nondissipative (minor) mergers should not strongly alter inner 
-    profiles, but can efficiently build up outer haloes 
-    (e.g., \citealt{Hilz2013}, \citealt{Oogi2013}).
+    Non--dissipative (minor) mergers should not strongly alter inner profiles, but can
+    efficiently build up outer haloes (e.g., \citealt{Hilz2013}, \citealt{Oogi2013}).
 
@@
 
-    We have shown that the \mden{} profiles of massive galaxies vary with the masses of their host dark matter haloes. We now turn our attention to the more commonly studied stellar 
-    mass--size relation (\mstar{}--$R_{\mathrm{e}}$). 
-    In addition, we consider halo mass dependence on the 
-    \mtot{}--\minn{} plane.
+    We have shown that the \mden{} profiles of massive galaxies vary with the masses 
+    of their host dark matter haloes. 
+    We now turn our attention to the more commonly studied stellar mass--size relation
+    (\mstar{}--$R_{\mathrm{e}}$). 
+    In addition, we consider halo mass dependence on the \mtot{}--\minn{} plane.
 
@@
 
-    \song{However, `size' is not a well-defined parameter for massive 
-    galaxies with very extended stellar mass distributions. 
-    In practice, measurements of the `effective radius', or `half-light radius', depend on resolution, depth, filter, and may also 
-    depend on the adopted model for the light profile.  
+    \song{
+    However, `size' is not a well-defined parameter for massive galaxies with very 
+    extended stellar mass distributions. 
+    In practice, measurements of the `effective radius', or `half-light radius', depend 
+    on resolution, depth, filter, and may also depend on the adopted model for the 
+    light profile.  
     This makes comparisons of size measurements among different observations, 
-    or between observations and models, uncertain. This is the main reason
-    why we prefer to compare \mden{} profiles directly which completely bypasses the need to consider `size'.
-    }
-
-    Nonetheless, to enable comparisons with past work, we now consider the more traditional mass-size relation. We adopt the radius enclosing 50\% of stellar mass within 
-    100 kpc ($R_{\mathrm{50}}$; derived from the $i$-band curve-of-growth) as our 
-    `size' for massive galaxies. This definition of `half-light radius' is more robust against structural 
-    details, model choice, and background subtraction, compared to the 
-    effective radius measured using oversimplified 2-D models such as the single-\ser{} model. 
+    or between observations and models, uncertain. 
+    This is the main reason why we prefer to compare \mden{} profiles directly which 
+    completely bypasses the need to consider `size'.
+    }
+
+    Nonetheless, to enable comparisons with past work, we now consider the more 
+    traditional mass-size relation. 
+    We adopt the radius enclosing 50\% of stellar mass within 100 kpc 
+    ($R_{\mathrm{50}}$; derived from the $i$-band curve-of-growth) as our `size' for 
+    massive galaxies. 
+    This definition of `half-light radius' is more robust against structural details, 
+    model choice, and background subtraction, compared to the effective radius measured 
+    using oversimplified 2-D models such as the single-\ser{} model. 
     Massive galaxies in this sample are large enough so that the impact of seeing 
@@
 
-    The left panel of Fig~\ref{fig:scaling_relation} shows the mass-size relation for our two samples. We fit the \logmtot{}-$\log_{10} (R_{\mathrm{50}}/\mathrm{kpc})$ relations at 
+    The left panel of Fig~\ref{fig:scaling_relation} shows the mass-size relation for 
+    our two samples. 
+    We fit the \logmtot{}-$\log_{10} (R_{\mathrm{50}}/\mathrm{kpc})$ relations at 
     $\log(M_{\star,100})>11.6$ using the \texttt{emcee} MCMC sampler 
@@
     dex.  
-    The $R_{\mathrm{50}}$ uncertainty is based on the \mden{} profile and
-    is very small due to the high \s2n{} of the profile. 
+    The $R_{\mathrm{50}}$ uncertainty is based on the \mden{} profile and is very small 
+    due to the high \s2n{} of the profile. 
     We manually assign a 10\% error for $R_{\mathrm{50}}$. 
@@
 
-    \noindent As shown in the left panel of Fig~\ref{fig:scaling_relation}, the two samples lie on 
-    \mtot{}--$R_{\mathrm{50}}$ relations that have similar slopes but 
-    different normalizations. The best-fitting mass--size relation derived here suggests that, 
-    at $0.3 < z < 0.5$, central galaxies with \logmtot{}$>11.6$ in \logmhalo{}$>14.2$
+    \noindent As shown in the left panel of Fig~\ref{fig:scaling_relation}, the two 
+    samples lie on \mtot{}--$R_{\mathrm{50}}$ relations that have similar slopes but 
+    different normalizations. The best-fitting mass--size relation derived here suggests 
+    that, at $0.3 < z < 0.5$, central galaxies with \logmtot{}$>11.6$ in \logmhalo{}$>14.2$
     haloes are on average $\sim20$\% larger than centrals in \logmhalo{}$<14.0$
@@
     We qualitatively compare our results with the mass--size relation for 
-    $0.2 < z < 0.5$ ETGs in group-scale dark matter halos in COSMOS (\citealt{HueartasCompany2013b}; HC13a; cyan dashed line).
-    HC13a measure luminosities and sizes using 2--D 
-    single--\ser{} models applied to \textit{HST}/ACS \texttt{F814W} images. HC13a use circularized effective radii 
-    ($R_{\mathrm{e,Circ}} = R_{\mathrm{e,Fit}} \times \sqrt{b/a}$). We empirically correct their measurements assuming an average $<b/a>=0.75$.
+    $0.2 < z < 0.5$ ETGs in group-scale dark matter halos in COSMOS 
+    (\citealt{HueartasCompany2013b}; HC13a; cyan dashed line).
+    HC13a measure luminosities and sizes using 2--D single--\ser{} models applied to 
+    \textit{HST}/ACS \texttt{F814W} images. 
+    HC13a use circularized effective radii 
+    ($R_{\mathrm{e,Circ}} = R_{\mathrm{e,Fit}} \times \sqrt{b/a}$). 
+    We empirically correct their measurements assuming an average $<b/a>=0.75$.
     At similar redshifts, the mass-size relation from HC13a lies below our 
@@
     We further add $+0.1$dex to the HSC13 stellar masses to account for a systematic 
-    offset between BC03 and our FSPS model (see Paper~1). Our overall mass-size relation is in good agreement with HC13a.}
+    offset between BC03 and our FSPS model (see Paper~1). Our overall mass-size relation 
+    is in good agreement with HC13a.
+    }
 
@@
     in modeling methods, and to the shallower ACS/\texttt{F814W} imaging. 
-    As for HC13b, it is also possible that the shallower SDSS image masks the environmental dependence.
-Figure~\ref{fig:prof_1} shows that the most pronounced differences are at $R>50$ kpc -- these would be difficult to detect with shallow imaging.
+    As for HC13b, it is also possible that the shallower SDSS image masks the 
+    environmental dependence. 
+    Figure~\ref{fig:prof_1} shows that the most pronounced differences are at 
+    $R>50$ kpc -- these would be difficult to detect with shallow imaging. 
     Both shallow images and oversimplified models can lead to biased results. 
-We highlight such effects in Appendix~\ref{app:gama} by comparing luminosities from HSC to those from single-\ser{} model applied to SDSS.
+    We highlight such effects in Appendix~\ref{app:gama} by comparing luminosities 
+    from HSC to those from single-\ser{} model applied to SDSS.
     }
@@
 
-    We now investigate the relationship between \mtot{}, \minn{}, and \mhalo{}. 
+    We now explore the environment dependence of galaxy structure using the 
+    \mtot{}-\minn{} relation.
     Compared to the mass--size relation, the \mtot{}--\minn{} relation is not plagued 
@@
 
-    The right panel of Fig \ref{fig:scaling_relation} compares our two samples on the \mtot{}--\minn{} plane. The two samples follow distinct best-fitting \mtot{}--\minn{} relations. 
+    The right panel of Fig \ref{fig:scaling_relation} compares our two samples on the 
+    \mtot{}--\minn{} plane. 
+    The two samples follow distinct best-fitting \mtot{}--\minn{} relations. 
     For \rbcg{} galaxies with \logmtot{}$>11.6$ we find:
@@
 
-    These results are robust against the exact choice of the stellar mass range over which 
-    the fit is performed. These results are also unchanged when we replace \minn{} with the stellar 
+    These results are robust against the exact choice of the stellar mass range over 
+    which the fit is performed.
+    These results are also unchanged when we replace \minn{} with the stellar 
     mass within a 5- or 15-kpc aperture, or if \mtot{} is replaced with a stellar mass 
@@
     \song{
-    Figure \ref{fig:scaling_relation} presents the same conclusions as in 
-    the previous section, namely that at fixed \mtot{}, central galaxies in more massive 
-    haloes tend to have a smaller fraction of stellar mass in their inner regions and more prominent outer stellar haloes.  
-    }
-
-    %Meanwhile, at fixed \minn{} -- a proxy for the \mstar{} of the `\textit{in situ}' 
-    %component -- central galaxies in more massive haloes tend to be more massive and 
-    %display more prominent stellar haloes. 
-    %\song{
-    %The comparison of \mden{} profiles for \minn{}-matched samples may not directly
-    %reflect the environment-related processes because other physical mechanisms could 
-    %also change the inner \mden{} profiles and their \mtot{} could be quite different. 
-    %But the combination of \mtot{} and \minn{} clearly suggests that information about
-    %their dark matter haloes or environments is encoded within this simple 2-D plane. 
-    %We discuss more scientific implications of these results in 
-    %\S~\ref{sec:discussion}
-    %}
+    Figure \ref{fig:scaling_relation} presents the same conclusions as in the previous 
+    section, namely that at fixed \mtot{}, central galaxies in more massive haloes tend 
+    to have a smaller fraction of stellar mass in their inner regions and more prominent 
+    outer stellar haloes.  
+    }
 
@@
 
-    In Paper~I, we show that the ellipticity of the outer stellar halo increases with stellar mass but that rest-frame colour gradients do not depend strongly on stellar mass.
+    In Paper~I, we show that the ellipticity of the outer stellar halo increases with 
+    stellar mass but that rest-frame colour gradients do not depend strongly on 
+    stellar mass. 
     In this paper, we take this analysis one step further to investigate whether either 
@@
     \begin{itemize}
+
         \item \song{
@@
         \item \song{
-            However, we do find that at fixed \minn{}, galaxies in massive halos have more elliptical outer stellar halos compared to galaxies in low mass halos (upper right panel).
-This may be further evidence that elongated outer stellar haloes are built from accreted stars.
-            }
-
-        \item We find no evidence that the rest-frame colour gradients (at $r<60$ kpc) of massive galaxies depend on halo mass.
+            However, we do find that at fixed \minn{}, galaxies in massive halos 
+            have more elliptical outer stellar halos compared to galaxies in low mass 
+            halos (upper right panel).
+            This may be further evidence that elongated outer stellar haloes are 
+            built from accreted stars.
+            }
+
+        \item We find no evidence that the rest-frame colour gradients (at $r<60$ kpc) 
+            of massive galaxies depend on halo mass.
 
@@
     profiles for massive galaxies. 
-The similarity in the average rest-frame colour profiles demonstrates that our results can not simply be explained by differences in radial \m2l{} ratios between the two samples.
-
-    \song{
-    Our work does not address color gradients below 5--6 kpc because we do not deconvolve 
-    for the PSF. 
+    The similarity in the average rest-frame colour profiles demonstrates that our 
+    results can not simply be explained by differences in radial \m2l{} ratios between 
+    the two samples.
+
+    \song{
+    Our work does not address color gradients below 5--6 kpc because we do not 
+    deconvolve for the PSF. 
     Color gradients on these scales may be sensitive to other physical processes and 
@@
     Using deep images from the HSC survey, we show that the stellar mass distributions 
-    of massive central galaxies at $0.3 < z < 0.5$ depend on halo mass. At fixed total galaxy mass, central galaxies in massive halos have larger half-light radii and host more prominent outer 
-    stellar haloes compared to galaxies in low mass haloes. We also find that 
-    the outer stellar haloes ($R>50$ kpc) of massive galaxies show the strongest 
-    variations with halo mass.
+    of massive central galaxies at $0.3 < z < 0.5$ depend on halo mass. 
+    At fixed total galaxy mass, central galaxies in massive halos have larger 
+    half-light radii and host more prominent outer stellar haloes compared to galaxies 
+    in low mass haloes (Figure~\ref{fig: fig:scaling_relation}). 
+    We also find that the outer stellar haloes ($R>50$ kpc) of massive galaxies show 
+    the strongest variations with halo mass.
 
@@
     formation of \textit{in situ} stars in massive central galaxies. 
-    After a rapid quenching of star formation, the subsequent assembly of massive galaxiesis  dominated by the accretion of satellite galaxies through (mostly) 
+    After a rapid quenching of star formation, the subsequent assembly of massive 
+    galaxies is dominated by the accretion of satellite galaxies through (mostly) 
     non--dissipative mergers. 
     Dry minor mergers are efficient at depositing \textit{ex situ} stars in the 
-    outskirts of massive galaxies (e.g., \citealt{Oogi2013, Bedorf2013}) and hence in building up outer stellar haloes.
-The fact that minor mergers become more frequent in more massive dark matter haloes could lead to the halo mass dependence of galaxy profiles that we identify in Figure~\ref{fig:prof_1}.}
-
-    \citet{Shankar2014} studied the environment dependence of galaxy size using semi-analytic models. 
+    outskirts of massive galaxies (e.g., \citealt{Oogi2013, Bedorf2013}) and hence in 
+    building up outer stellar haloes. 
+    The fact that minor mergers become more frequent in more massive dark matter 
+    haloes could lead to the halo mass dependence of galaxy profiles that we identify 
+    in Figure~\ref{fig:prof_1}.
+    }
+
+    \citet{Shankar2014} studied the environment dependence of galaxy size using 
+    semi-analytic models. 
     They predict that at fixed stellar mass, the median size of central galaxies 
@@
     timescale is short (e.g., \citealt{Newman2012}). 
-Massive central galaxies with $11.5 <$\logms{}$<12.0$ living in haloes with \logmh{}$>14.0$ can have up to four times more minor mergers (1:100--1:3) compared to those in less massive haloes at fixed galaxy mass.
+    Massive central galaxies with $11.5 <$\logms{}$<12.0$ living in haloes with 
+    \logmh{}$>14.0$ can have up to four times more minor mergers (1:100--1:3) compared 
+    to those in less massive haloes at fixed galaxy mass. 
     An increase in the minor-merger rate as a function of halo mass can lead to a 
@@
     Our results are broadly consistent with these predictions. 
-However, our results alone cannot rule out other explanations for this halo mass dependence.
-For instance, \citet{Buchan2016} suggest that central galaxies in more massive haloes have more extended in-situ components.
-Comparisons with higher redshift observations will enable us to distinguish between these two formation scenarios.
+    However, our results alone cannot rule out other explanations for this halo mass 
+    dependence. 
+    For instance, \citet{Buchan2016} suggest that central galaxies in more massive 
+    haloes have more extended in-situ components. 
+    Comparisons with higher redshift observations will enable us to distinguish 
+    between these two formation scenarios.
     }
@@
 
-Figure \ref{fig:scaling_relation} shows that, at fixed total galaxy mass, centrals in high mass haloes have slightly shallower inner \mden{} slopes lower values of \minn{} compared to those in low mass haloes.
-\song{We have tested that this cannot be solely explained by the choice of a finite aperture (100 kpc) to estimate `total' galaxy mass.
-Integrating our profiles our to larger radii makes the differences between \rbcg{} and \nbcg{} galaxies on the \mtot{}--\minn{}
-    plane even more significant \alexie{reference to somewhere in the appendix?}.
-In hydrodynamic simulations, intense dissipative processes help create a self-similar de~Vaucouleurs--like ($n{\sim} 4$) inner density profile (e.g., \citealt{Hopkins2008}).
-However, there are a variety of physical processes that can shape and alter the inner  profile which we now discuss.
+    Figure \ref{fig:scaling_relation} shows that, at fixed total galaxy mass, centrals 
+    in high mass haloes have slightly shallower inner \mden{} slopes and lower values 
+    of \minn{} compared to those in low mass haloes. 
+    \song{
+    We have tested that this cannot be solely explained by the choice of a finite 
+    aperture (100 kpc) to estimate `total' galaxy mass. 
+    Integrating our profiles out to larger radii makes the differences between \rbcg{} 
+    and \nbcg{} galaxies on the \mtot{}--\minn{} plane even more significant 
+    (see Appendix~\ref{app:robust}). 
+    In hydrodynamic simulations, intense dissipative processes help create a 
+    self-similar de~Vaucouleurs--like ($n{\sim} 4$) inner density profile 
+    (e.g., \citealt{Hopkins2008}). 
+    However, there are a variety of physical processes that can shape and alter the 
+    inner  profile which we now discuss.
     }
@@
 
-    \song{Second, strong adiabatic expansion induced by powerful AGN feedback is another mechanism 
-    (e.g., \citealt{Fan2008}) that can modify stellar density profiles. \
+    \song{
+    Second, strong adiabatic expansion induced by powerful AGN feedback is 
+    another mechanism (e.g., \citealt{Fan2008, Martizzi2013}) that can modify stellar 
+    density profiles. 
     When the induced mass loss is efficient enough, it can lead to expanded 
     central stellar mass distribution and can significantly lower the inner \mden{}. 
-    } \alexie{Need reference also to Martizzi et al}
+    }
 
@@
     (e.g., \citealt{Nair2010, Maltby2010, Cappellari2013, HCompany13}). 
-Shallow imaging and the use of models which do not necessarily well describe massive galaxies (e.g., single-\ser{} or de~Vaucouleurs models) may of masked the effect revealed in this paper.
+    Shallow imaging and the use of models which do not necessarily well describe 
+    massive galaxies (e.g., single-\ser{} or de~Vaucouleurs models) may have masked 
+    the effect revealed in this paper. 
     In Appendix~\ref{app:gama}, we use the \rbcg{} and \nbcg{} galaxies that overlap 
@@
     massive dark matter haloes actually show more prominent outer stellar haloes.
-    \song{These types of issues complicate the comparisons of mass--size relations derived from different images or using different methods.
+    \song{These types of issues complicate the comparisons of mass--size relations 
+    derived from different images or using different methods. 
     For this reason, we only present a qualitative comparison with previous work}
 
-    At low redshift, \citet{Cerbrian2014} find ETGs with \logms{}$>11.5$ to be slightly larger in more massive haloes, and they also show that this trend is 
-    reversed at lower \mstar{}. 
+    At low redshift, \citet{Cerbrian2014} find ETGs with \logms{}$>11.5$ to be slightly 
+    larger in more massive haloes, and they also show that this trend is reversed at 
+    lower \mstar{}. 
     \song{
@@
     }
-    \citet{Yoon2017} present a study of a large sample of $z\sim0.1$ SDSS 
-    ETGs using a nonparametric method. They also find an environmental dependence of the mass--size relation at \logms{}$>11.2$. Similar to our work, they find that massive ETGs in dense environments 
-    are 20--40\% larger compared to those in underdense environments.
+    \citet{Yoon2017} present a study of a large sample of $z\sim0.1$ SDSS ETGs using 
+    a nonparametric method. 
+    They also find an environmental dependence of the mass--size relation at 
+    \logms{}$>11.2$. 
+    Similar to our work, they find that massive ETGs in dense environments are 
+    20--40\% larger compared to those in underdense environments.
     Recently, \citet{Charlton2017} use a single-\ser{} model for galaxies at 
     $0.2 < z < 0.8$ in the Canada France Hawaii Lensing Survey (CFHTLenS) 
-    (\citealt{Heymans2012}) together with galaxy--galaxy 
-    lensing measurements to show that larger galaxies tend to live in more massive 
-    dark matter haloes (also see \citealt{Sonnenfeld2017}).
+    (\citealt{Heymans2012}) together with galaxy--galaxy lensing measurements to 
+    show that larger galaxies tend to live in more massive dark matter haloes 
+    (also see \citealt{Sonnenfeld2017}).
     These results are in broad agreement with those presented here.
 
-    \alexie{this needs rewritting, redshift evolution ...}\song{With a greater number of studies that are now beginning to reveal the halo mass dependence of the sizes and profiles of massive galaxies, more detailed comparisons with theoretical predictions for this effect will become of increasing interest.
-Some theoretical studies predicts a strong environmental dependence of the mass--size relation
-    for massive quiescent or early-type galaxies
-    (e.g., \citealt{Papovich2012, Bassett2013, Lani2013, Strazzullo2013, 
-    Delaye2014}), while other observations suggest otherwise (e.g., 
+    \song{
+    As the halo mass dependence of the sizes and \mden{} profiles of massive 
+    galaxies is being confirmed at low--redshift, the physical origin and 
+    redshift evolution of such dependence will become of increasing interest.  
+    Right now, some observations find a strong environmental dependence of the 
+    mass--size relation for massive quiescent or early-type galaxies at 
+    high--redshift (e.g., \citealt{Papovich2012, Bassett2013, Lani2013, 
+    Strazzullo2013, Delaye2014}), while other works suggest otherwise (e.g., 
     \citealt{Rettura2010, Raichoor2012, Kelkar2015, Allen2015}). 
     Comparison with high--redshift results are complicated by many issues and 
-    is beyond the scope of this work, but we want to emphasize again that 
-    direct comparison of \mden{} profile (e.g., \citealt{Szomoru2012, Patel2013, 
-    Buitrago2017, Hill2017}) could better trace the redshift evolution of the
-    environment dependence. 
-    }
-
-    %\song{
-    %It is interesting to see that several of these works report stronger 
-    %environment dependence of size at fixed \mstar{} for either ETGs or quiescent 
-    %galaxies (30--50\% larger in denser environments).
-    %As shown in \citet{HCompany13} using a Monte Carlo test (see their \S~4.2), 
-    %when the uncertainties of mass and size are considered, the size difference at 
-    %fixed stellar mass could be even more significant between extremely different
-    %environments.
-    %If true, it indicates that denser regions at high redshift ($z>2$) could accelerate 
-    %galaxy evolution (e.g., proto-clusters; see \citealt{Wang2016, Shimakawa2018}), and 
-    %the size evolution of massive galaxies in a richer environment gradually slows down
-    %toward lower redshift (e.g., \citealt{Papovich2012, Andreon2016}.
-    %}
-    %However, there are also observations that suggest otherwise (e.g., 
-    %\citealt{Rettura2010, Raichoor2012, Kelkar2015, Allen2015}). 
-    %\song{
-    %Comparisons of our results with work done at high redshift are complicated by many 
-    %issues. 
-    %At high-$z$, these works often rely on small samples or special environments 
-    %(rare massive proto-clusters). 
-    %Progenitors of massive galaxies in this work may still be star-forming or 
-    %late-type galaxies at $z>1$. 
-    %Finally, it is just intrinsically more difficult to accurately measure 
-    %\mstar{} and size at high redshift (e.g., \citealt{Price2017}).
-    %It would be interesting to see whether the current simulations can reproduce 
-    %these observed environment dependencies and use them to investigate the redshift
-    %evolution of such dependence. 
-    %Meanwhile, direct comparisons of rest-frame surface brightness or \mden{} 
-    %profiles (e.g., \citealt{Szomoru2012, Patel2013, Buitrago2017, Hill2017}) could be 
-    %a better approach than the 
-    %mass--size relation to compare high- and low-$z$ mass galaxies.
-    %}
+    is beyond the scope of this work, but we want to point out again that 
+    previous works mostly focus on the mass--size relation while direct comparison 
+    of \mden{} profile (e.g., \citealt{Szomoru2012, Patel2013, Buitrago2017, 
+    Hill2017}) could help us trace the redshift evolution of the environment 
+    dependence better. 
+    }
 
@@
     size of galaxies of different types and at different redshifts, it sometimes leads
-    to biased results as it does not universally describe all types of galaxies. Sizes derived from 1-D curves-of-growth are more model independent and have been 
-    shown to be useful in revealing the environmental dependence of the mass--size relation 
-    (e.g., \citealt{Yoon2017}, and this work), but this method does not take the PSF into account. It also depends on imaging depth and background subtraction.
+    to biased results as it does not universally describe all types of galaxies. 
+    Sizes derived from 1-D curves-of-growth are more model independent and have been 
+    shown to be useful in revealing the environmental dependence of the mass--size 
+    relation (e.g., \citealt{Yoon2017}, and this work), but this method does not take 
+    the PSF into account. 
+    It also depends on imaging depth and background subtraction.
 
@@
     between observations and theoretical predictions. 
-Even better, we argue that galaxy mass profiles can be compared directly with predictions from hydrodynamic simulations, bypassing the need completely for `size' estimates.
+    Even better, we argue that galaxy mass profiles can be compared directly with 
+    predictions from hydrodynamic simulations, bypassing the need completely for 
+    `size' estimates.
 
@@
 
-    In this paper, we investigate how the stellar mass profiles of massive galaxies depend on the masses of their host dark matter haloes.
-Using high-quality images from the first $\sim100$ deg$^2$ of the
-    Hyper Suprime-Cam Subaru Strategic Program, we divide central galaxies at $0.3 < z < 0.5$ into two samples according to dark matter halo mass (\mhalo{}$\simgt 10^{14.2} M_{\odot}$ and 
-    \mhalo{}$\simlt 10^{14} M_{\odot}$). Exquisite data from HSC enables us to extract stellar profiles for individual galaxies in these two samples out to 100 kpc.
+    In this paper, we investigate how the stellar mass profiles of massive galaxies 
+    depend on the masses of their host dark matter haloes. 
+    Using high-quality images from the first $\sim100$ deg$^2$ of the Hyper Suprime-Cam 
+    Subaru Strategic Program, we divide central galaxies at $0.3 < z < 0.5$ into two 
+    samples according to dark matter halo mass (\mhalo{}$\simgt 10^{14.2} M_{\odot}$ 
+    and \mhalo{}$\simlt 10^{14} M_{\odot}$). 
+    Exquisite data from HSC enables us to extract stellar profiles for individual 
+    galaxies in these two samples out to 100 kpc.
 
@@
 
-    \item At fixed \mtot{}, central galaxies in high mass haloes 
-            display shallower \mden{} profiles compared to those in low mass haloes: they have flatter inner \mden{} profiles and 
-            more significant outer stellar envelopes.  This trend is most pronounced at $R>50$ kpc and thus would easily be missed with shallow imaging data.
-
-        \item Massive galaxies matched by \minn{} display a range of  \mtot{} values and a large intrinsic scatter in the amplitude of their outer stellar envelopes.
-
-        %\item At fixed \minn{}, massive central galaxies in more massive haloes 
-          %  possess much more extended stellar haloes than those in smaller haloes. 
-         %   Assuming that \minn{} traces the amount of `\textit{in situ}' stars in 
-          %  massive galaxies, this result is consistent with the picture that more 
-          %  massive haloes favor the growth of extended stellar haloes in their central 
-           % galaxies through more frequent mergers.
-
-        \item \song{This environmental dependence is also reflected in the mass-size relation, as well as in the \mtot{}-\minn{} relation.
-We propose that simple elliptical aperture masses such as \mtot{} and\minn{} are better statistics to summarize the properties of galaxy profiles than commonly used `size' estimates such as $R_e$.}
-
-      \item \song{At fixed \minn{}, galaxies in massive halos have more elliptical outer stellar halos compared to galaxies in low mass halos.
-This may be further evidence that elongated outer stellar haloes are built from accreted stars.}
-
-        \item At fixed galaxy mass and at $r<60$ kpc, the rest-frame colour gradients of massive galaxies do not depend on dark matter halo mass.
+    \item At fixed \mtot{}, central galaxies in high mass haloes display shallower 
+        \mden{} profiles compared to those in low mass haloes: they have flatter inner 
+        \mden{} profiles and more significant outer stellar envelopes.  
+        This trend is most pronounced at $R>50$ kpc and thus would easily be missed 
+        with shallow imaging data.
+
+    \item Massive galaxies matched by \minn{} display a range of \mtot{} values and a 
+        large intrinsic scatter in the amplitude of their outer stellar envelopes.
+
+    \item \song{
+        This environmental dependence is also reflected in the mass-size relation, 
+        as well as in the \mtot{}-\minn{} relation. 
+        We propose that simple elliptical aperture masses such as \mtot{} and\minn{} 
+        are better statistics to summarize the properties of galaxy profiles than 
+        commonly used `size' estimates such as $R_e$.
+        }
+
+    \item \song{
+        At fixed \minn{}, galaxies in massive halos have more elliptical outer 
+        stellar halos compared to galaxies in low mass halos. 
+        This may be further evidence that elongated outer stellar haloes are built 
+        from accreted stars.
+        }
+
+    \item At fixed galaxy mass and at $r<60$ kpc, the rest-frame colour gradients 
+        of massive galaxies do not depend on dark matter halo mass.
 
@@
     the assembly of massive dark matter haloes and their central galaxies. 
-Future work will focus on a comparison between our data and  predictions from various hydrodynamic simulations.
-This will enable us to gain further insight into the physical mechanisms that drive the trends discovered in this paper.
+    Future work will focus on a comparison between our data and predictions from 
+    various hydrodynamic simulations. 
+    This will enable us to gain further insight into the physical mechanisms that 
+    drive the trends discovered in this paper.
 %% ------------------------------------------------------------------------------------ %%
@@
   % Personal 
-  The authors thank Frank van~den~Bosch for insightful discussions and 
-  Shun Saito for helping us estimate the fraction of satellite galaxies in our sample.
+  The authors thank Frank van~den~Bosch for insightful discussions and Shun Saito for 
+  helping us estimate the fraction of satellite galaxies in our sample.
+  We also thank Felipe Ardilla and Christopher Bradshaw for useful comments. 
   SH thanks Feng-Shan Liu for sharing the \mden{} profile of the $z\sim1$ BCG from 
-  his work. This material is based upon work supported by the National Science Foundation under Grant No. 1714610.
+  his work. 
+  This material is based upon work supported by the National Science Foundation under 
+  Grant No. 1714610.
 

### 2017-12-06 draft/paper2.tex
Minor typo corrections

@@
-% Version 0; preprint format; Outline of paper II by Song Huang
-% Version 1; preprint format; Edited by Jenny Greene
-% Version 2; preprint format; Edited by Song Huang
-% Version 3; preprint format; Edited by Alexie Leauthaud
-% Version 4; preprint format; Edited by Song Huang
-% Version 5; preprint format; Edited by Jenny Greene and Song Huang
+% Version 1; preprint format; Outline of paper II by Song Huang
+% Version 2; preprint format; Edited by Jenny Greene
+% Version 3; preprint format; Edited by Song Huang
+% Version 4; preprint format; Edited by Alexie Leauthaud
+% Version 5; preprint format; Edited by Song Huang
+% Version 6; preprint format; Edited by Jenny Greene and Song Huang
+% Version 7; preprint format; Edited by Susan Foster and Song Huang
+% Version 8; preprint format; Edited by Alexie Leauthaud and Song Huang
+% Version 9; preprint format; Edited by Song Huang (Comments from Felipe Ardilla and Christopher Bradshaw)
 
@@
     We use ${\sim}100$ deg$^2$ of deep ($>28.5$ \sb{} in $i$-band), high-quality 
-    (median 0.6\asec seeing) imaging data from the Hyper Suprime--Cam (HSC) survey 
-    to investigate the halo mass dependence of the surface mass density profiles 
-    and outer stellar envelopes of massive galaxies. 
-    The $i$-band images from HSC survey reach ${\sim}4$ magnitudes deeper than SDSS 
-    and enable us to directly trace stellar mass distributions to 100 kpc without 
-    requiring stacking.  
-    We conclusively show that at fixed stellar mass, the stellar profiles of massive 
+    (median 0.6\asec seeing) imaging data from the Hyper Suprime--Cam (HSC) survey to 
+    reveal the halo mass dependence of the surface mass density profiles and outer 
+    stellar envelopes of massive galaxies. 
+    The $i$-band images from the HSC survey reach ${\sim}4$ magnitudes deeper than 
+    Sloan Digital Sky Survey and enable us to directly trace stellar mass distributions 
+    to 100 kpc without requiring stacking.  
+    We conclusively show that, at fixed stellar mass, the stellar profiles of massive 
     galaxies depend on the masses of their dark matter haloes. 
@@
     at $0.3 < z < 0.5$ have shallower inner stellar mass density profiles 
-    (within ${\sim}10$-$20$ kpc) and more prominent outer envelopes. 
-    These differences translate into a halo mass dependence of the 
-    mass--size relation: central galaxies in haloes with \logmh{}$>14.0$ are 
-    $\sim 20$\% larger in $R_{\mathrm{50}}$ at fixed \mtot{}.  
+    (within ${\sim}10$--$20$ kpc) and more prominent outer envelopes. 
+    These differences translate into a halo mass dependence of the mass--size relation. 
+    Central galaxies in haloes with \logmh{}$>14.0$ are $\sim 20$\% larger in 
+    $R_{\mathrm{50}}$ at fixed \mtot{}. 
     Such dependence is also reflected in the relationship between the stellar mass 
@@
     galaxies (ETGs) need to increase their effective radii ($R_{\rm e}$) by a factor 
-    of 2--4 over a time span of 10 Gyrs (e.g. \citealt{Newman2012, vdWel2014}). 
-    This observational result spurred the development of the ``two-phase'' formation
-    scenario for massive ETGs (e.g. \citealt{Oser2010, Oser2012}),
+    of 2--4 over a time span of 10 Gyrs (e.g., \citealt{Newman2012, vdWel2014}). 
+    This observational result spurred the development of the `two-phase' formation
+    scenario for massive ETGs (e.g., \citealt{Oser2010, Oser2012}),
     in which galaxies form a compact central region at $z\sim 2$ through highly 
-    dissipative processes (e.g. gas-rich mergers or cold gas-accretion;
+    dissipative processes (e.g., gas-rich mergers or cold gas-accretion;
     \citealt{Hopkins2008, Dekel2009}). 
     They subsequently assemble extended stellar haloes via dry mergers 
-    \citep[e.g,][]{Naab2006, Khochfar2006, Oser2010, Oser2012} which can cause 
+    \citep[e.g.,][]{Naab2006, Khochfar2006, Oser2010, Oser2012}, which can cause 
     significant size growth at late times. 
     An alternative explanation for size growth, progenitor bias, hypothesizes that 
-    larger ETGs were quenched more recently, but this explanation is still under 
-    active debate (e.g. \citealt{Newman2012, Carollo2013, Poggianti2013, Belli2015,
+    larger ETGs were quenched more recently; but this explanation is still under 
+    active debate (e.g., \citealt{Newman2012, Carollo2013, Poggianti2013, Belli2015,
     Keating2015, Fagioli2016}).
@@
     formation scenario using galaxies at low redshift, by investigating surface 
-    brightness or mass density profiles (e.g. \citealt{Huang2013a, Huang2013b, 
-    Oh2017}, optical color gradients (e.g. \citealt{LaBarbera2010, LaBarbera2012}), 
+    brightness or mass density profiles (e.g., \citealt{Huang2013a, Huang2013b, 
+    Oh2017}), optical colour gradients (e.g., \citealt{LaBarbera2010, LaBarbera2012}), 
     and stellar population gradients \citep[e.g.,][]{Coccato2010, Coccato2011, 
@@
     These observations are generally consistent with the two-phase formation scenario. 
-    However, it is still not clear whether this promising picture can correctly 
-    predict the connection between the stellar mass distributions in massive galaxies 
-    and their dark matter haloes.
-    }
-
-    \song{
-    Under the $\Lambda$CDM cosmology, The assembly of massive ETGs is intrinsically 
-    tied to the hierarchal growth of their host dark matter haloes 
-    (e.g. \citealt{Leauthaud2012, Behroozi2013, Shankar2013}). 
-    Hydrodynamic simulations suggest that the fraction of star accreted through 
-    mergers (\textit{ex situ} component) in central galaxy increases with halo 
-    mass (e.g. \citealt{Pillepich2017b}). 
-    Although the major merger rate is not strong function of progenitor halo mass 
-    (e.g. \citealt{Shankar2015}), minor mergers may still play a more important 
-    role in the assembly of central galaxy of more massive dark matter halos 
-    (e.g. \citealt{Guo2011, Yoon2017}). 
-    As minor merger is more efficient at ``puffing up'' the outskirts of massive 
-    galaxies (e.g. \citealt{Oogi2013, Bedorf2013}), this seems to suggest the 
+    However, it is still not clear whether this picture correctly 
+    predicts the connection between the stellar mass distributions in massive galaxies 
+    and their dark matter haloes.}
+
+    \song{In the $\Lambda$CDM cosmology, the assembly of massive ETGs is intrinsically 
+    tied to the hierarchical growth of their host dark matter haloes 
+    (e.g., \citealt{Leauthaud2012, Behroozi2013, Shankar2013}). 
+    Hydrodynamic simulations suggest that the fraction of stars accreted through 
+    mergers (the \textit{ex situ} component) in central galaxies increases with halo 
+    mass (e.g., \citealt{RodriguezGomez2016, Pillepich2017b}). 
+    The major merger rate is not a strong function of progenitor halo mass 
+    (e.g., \citealt{Shankar2015}) but minor mergers rate should increase with 
+    halo mass, hence play an important role in determining the structures of central 
+    galaxies (e.g., \citealt{Guo2011, Yoon2017}). 
+    Minor mergers are efficient at `puffing up' the outskirts of massive 
+    galaxies (e.g., \citealt{Oogi2013, Bedorf2013}). 
+    Because the minor merger rate increases with halo mass, the 
     structures of massive ETGs and the well-known stellar mass--effective radius 
-    relation (\mstar{}--$R_{\rm e}$; e.g., \citealt{Shen2003, Guo2009}) should depend 
-    on their ``environment''\footnote{There are multiple definitions of 
-    ``environment'' in the literature.  
-    In this work, we use ``environment'' and halo mass interchangeably.}
-    (e.g. \citealt{Shankar2013, Shankar2014}). 
-    However, evidence for the environment--dependence of \mstar{}--$R_{\rm e}$
+    relation (\mstar{}--$R_{\rm e}$; e.g., \citealt{Shen2003, Guo2009}) should 
+    depend on their `environment'\footnote{There are multiple definitions of 
+    `environment' in the literature. 
+    In this work, we use `environment' and halo mass interchangeably.}
+    (e.g., \citealt{Shankar2013, Shankar2014}). 
+    However, evidence for the environment-dependence of \mstar{}--$R_{\rm e}$
     at low redshift is still not very solid (\citealt{Nair2010, HCompany13}; 
-    but also see \citealt{Yoon2017}), while the results at higher redshift are 
-    even more confusing (e.g. \citealt{Papovich2012, Lani2013, Delaye2014}; but 
+    but also see \citealt{Yoon2017}), and the results at higher redshift are 
+    even more unclear (e.g., \citealt{Papovich2012, Lani2013, Delaye2014}; but 
     also see \citealt{Rettura2010}).
@@
 	\song{
-    Therefore, we think it requires deeper images of these massive galaxies to 
-    better probe their outer stellar mass distributions and test these 
-    predictions. 
+    Deep images of massive galaxies can probe their outer stellar halos of massive 
+    galaxies and test these predictions. 
     Unfortunately, this is observationally challenging since the stellar haloes 
-    of massive galaxies can extend to $>100$ kpc (e.g.\citealt{Tal2011, DSouza2014}),
-    and their surface brightness profiles decline rapidly with typical values of 
-    $\mu > 26.0$ \sb{} in $i$-band at 100 kpc and at $z\sim0.3$. 
+    of massive galaxies can extend to $>100$ kpc (e.g., 
+    \citealt{Tal2011, DSouza2014}), and their surface brightness profiles decline 
+    rapidly with typical values of $\mu > 26.0$ \sb{} in $i$-band at 100 kpc and 
+    at $z\sim0.3$. 
     }
@@
     \logms{}$>11.4$ at $0.3 < z < 0.5$ and out to 100 kpc. 
-    In Paper I, we characterized the stellar mass profiles of massive ETGs, and 
-    showed that there is a large intrinsic scatter in the \mden{} stellar haloes of
-    massive galaxies on 100 kpc scales. 
-    In this paper, we now investigate whether or not the large scatter in the outer 
-    profiles of massive galaxies correlate with halo mass. 
-    We conclusively show that the sizes and stellar haloes of massive central galaxies 
-    depend on dark matter halo mass. 
-    In other terms, we reveal the halo mass dependence of the mass-size relation 
+    In Paper I, we characterized the stellar mass profiles of massive ETGs and 
+    showed that there is a large intrinsic scatter in the stellar haloes of
+    massive galaxies on 100-kpc scales. 
+    In this paper, we investigate whether the large scatter in the outer 
+    profiles of massive galaxies correlates with halo mass. 
+    We conclusively show that the sizes and stellar haloes of massive central 
+    galaxies depend on dark matter halo mass. 
+    In other words, we reveal the halo mass dependence of the mass--size relation 
     for massive ETGs.
@@
     \S \ref{sec:discussion}. 
-    \S \ref{sec:summary} presents our summary and conclusions.
-
-    Magnitudes use the AB system (\citealt{Oke1983}), and are corrected for Galactic 
+    Our summary and conclusions are presented in \S \ref{sec:summary}.
+
+    Magnitudes use the AB system (\citealt{Oke1983}), and are corrected for galactic 
     extinction using calibrations from \citet{Schlafly11}. 
@@
     As in \citet{hscMassiveI}, we do not attempt to decompose or distinguish any  
-    potential ``intra-cluster'' 
-    component (ICL; e.g. \citealt{Carlberg1997, Lin2004, Gonzalez2005, Mihos2005}).
+    potential `intra-cluster' 
+    component (ICL; e.g., \citealt{Carlberg1997, Lin2004, Gonzalez2005, Mihos2005}).
 
@@
       \caption{
-          Three-color images for a subsample of massive galaxies at $z{\sim}0.4$. 
-          All of these massive galaxies have very similar \mstar{} within a 10 kpc 
+          Three-colour images for a subsample of massive galaxies at $z{\sim}0.4$. 
+          All of these massive galaxies have very similar \mstar{} within a 10-kpc 
           elliptical aperture 
           ($11.2<\log_{10} (M_{\star,10\ \mathrm{kpc}}/M_{\odot})<11.3$). 
-          The dash-line circle at the top-left figure indicates $R=$10 kpc.
+          The dashed-line circle at the top-left figure indicates $R=$10 kpc.
           These galaxies are rank-ordered from top to bottom and from left to right 
-          by their \mstar{} within a 100 kpc elliptical aperture which varies 
-          from $10^{11.2} M_{\odot}$ to $10^{11.7} M_{\odot}$. 
-          At fixed ``inner'' mass (\minn{}), massive galaxies display significant
+          by their \mstar{} within a 100-kpc elliptical aperture that varies 
+          from $10^{11.2}\ M_{\odot}$ to $10^{11.7}\ M_{\odot}$. 
+          At fixed `inner' mass (\minn{}), massive galaxies display significant
           diversity in their outer profiles. 
           Red boxes indicate galaxies from dark matter haloes that are more massive 
-          than ${\sim} 10^{14.0} M_{\odot}$. 
+          than ${\sim} 10^{14}\ M_{\odot}$. 
           }
       \label{fig:m100_m10_color}
-  \end{figure*}
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %% 
-  \begin{figure*}
-      \centering 
-      \includegraphics[width=\textwidth]{fig/redbcg_prof_1}
-      \caption{
-          The environmental dependence of the stellar mass profiles of massive central 
-          galaxies. 
-          Left: halo mass dependence of galaxy profiles at fixed ``total'' stellar mass 
-          (\mtot{}). 
-          Right: halo mass dependence of galaxy profiles at fixed ``inner-mass'' 
-          (\minn{}). Orange and red lines correspond to central galaxies living in 
-          haloes with \logmh{} $\geq 14.2$. 
-          Black and grey lines correspond to central galaxies living in haloes with 
-          \logmh{} $\leq 14.0$. 
-          Thin lines show the profiles of individual galaxies while thick lines show 
-          the median profile. 
-          The uncertainty on the median profile is given by the shaded region and is 
-          computed via bootstrap resampling. 
-          Brown lines in the bottom panels show the relative difference between  
-          two median profiles 
-          ($\Delta = \log(\mu_{\star, \mathrm{cenHighMh}}) - 
-          \log(\mu_{\star, \mathrm{cenLowMh}}$). 
-          Errors on the difference between the two profiles are also computed 
-          via bootstrap.
-          The grey shaded regions show a Monte Carlo test to asses how likely is it to 
-          obtain $\Delta$ from random sub-samples of the data. 
-          To compute the grey shaded regions, we first mix the two samples 
-          (\rbcg{} and \nbcg{}), then draw sub-samples of galaxies from the mixed 
-          population and compute $\Delta$ in the same fashion as for our fiducial 
-          signal. 
-          We repeat this process 5000 times.  
-          The dark-grey shaded region (light-grey shaded region) shows the 1-$\sigma$ 
-          (3-$\sigma$) fluctuations in $\Delta$ from these 5000 draws.
-          }
-      \label{fig:prof_1} 
-  \end{figure*}
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %% 
-  \begin{figure*}
-      \centering 
-      \includegraphics[width=\textwidth]{fig/redbcg_scaling_relation}
-      \caption{
-          \textbf{Left}: The mass-size relations for \rbcg{} (orange squares) and 
-          \nbcg{} (grey dots) galaxies. 
-          Two vertical lines highlight our $11.6<$ \logms{} $<11.9$ mass bin. 
-          The red solid line shows the best fit mass-size relation for \rbcg{} and the 
-          grey dashed line shows the best fit relation for \nbcg{}. 
-          Shaded regions in lighter colors show the 1-$\sigma$ uncertainties
-          from MCMC sampling.  
-          The green dashed line shows the mass-size relation for nearby central 
-          galaxies in massive groups from \citet{HCompany13}. 
-          \textbf{Right:} The relations between \mtot{} and \minn{} for the 
-          \rbcg{} and \nbcg{} galaxies, along with the best-fit scaling relations for 
-          both samples.
-          }
-      \label{fig:scaling_relation} 
   \end{figure*}
@@
     ($\sim5\times 10^6$ Mpc$^3$) to sample the galaxy stellar mass function above 
-    \logms$>11.6$, we can spatially resolve galaxies profiles to $\sim 5$ kpc 
-    ($1.0^{\arcsec}$ corresponds to 4.4 and 6.1 kpc at $z=0.3$ and 0.5). 
-    \song{
-    And massive galaxies should experience little structural evolution and 
-    size growth between $z=0.5$ and 0.3 ($\sim$1.5 Gyr of time span) 
-    based on model prediction (e.g. \citealt{Shankar2015}).
-    }
-
-    We derive $i$-band surface brightness profiles out to 100 kpc after carefully 
+    \logms$>11.6$, and we can spatially resolve galaxies profiles to $\sim 5$ kpc 
+    ($1.0^{\arcsec}$ corresponds to 4.4 and 6.1 kpc at $z=0.3$ and 0.5, respectively). 
+    \song{
+    Massive galaxies should experience little structural evolution and 
+    size growth between $z=0.5$ and 0.3 ($\sim$1.5 Gyr time span) 
+    based on model predictions (e.g., \citealt{Shankar2015}).
+    }
+
+    After carefully 
     masking out surrounding neighbors and accounting for the subtraction of the 
-    background light. 
+    background light, we derive $i$-band surface brightness profiles out to 100 kpc. 
     We use the broadband spectral energy distributions (SED) fitting code 
@@
 
-        \item stellar mass within 10 kpc (hereafter noted \minn{}) which we use 
+        \item Stellar mass within 10 kpc (hereafter noted \minn{}), which we use 
             as a proxy for the stellar mass of the \textit{in situ} stellar 
             component. 
-            This is motivated both by recent observations and simulations 
+            This is motivated both by observations and simulations 
             (e.g.~\citealt{vanDokkum2010}, \citealt{RodriguezGomez2016}). 
@@
 
-        \item stellar mass within 100 kpc (hereafter noted \mtot{}). 
-            We use \mtot{} as a proxy of the ``total'' stellar mass. 
-            In Paper~I we showed that \mtot{} recovers more light compared to 
-            HSC \cmodel{} photometry with offsets that can be a large as 0.2 dex 
+        \item Stellar mass within 100 kpc (hereafter noted \mtot{}). 
+            We use \mtot{} as a proxy for the `total' stellar mass. 
+            In Paper~I we show that \mtot{} recovers more light compared to 
+            HSC \cmodel{} photometry with differences that can be a large as 0.2 dex 
             in magnitude.
@@
    results in terms of the full stellar mass profiles. 
-   However, in many cases we find it more useful to display figures using the more 
-   simple \minn{} and \mtot{} quantities. 
+   However, in many cases we find it useful to display figures using the simpler 
+   \minn{} and \mtot{} quantities. 
    In Figure \ref{fig:m100_m10_color}, we highlight the diversity of galaxies as a 
    function of \minn{} and \mtot{}. 
-   Figure \ref{fig:m100_m10_color} shows a random subsample of massive galaxies with 
-   very similar \minn{} that have large range of \mtot{}. 
-   We will use these two apertures masses to guide our comparisons of massive galaxies 
+   Figure \ref{fig:m100_m10_color} shows a subsample of massive galaxies with very 
+   similar \minn{} but show a large range of \mtot{}. 
+   We use these two aperture masses to guide our comparison of massive galaxies 
    as a function of environment.
+
+%% ------------------------------------------------------------------------------------ %% 
+  \begin{figure*}
+      \centering 
+      \includegraphics[width=\textwidth]{fig/redbcg_prof_1}
+      \caption{
+          The environmental dependence of the stellar mass profiles of massive central 
+          galaxies. 
+          \textbf{Left}: Halo mass dependence of galaxy \mden{} profiles at fixed 
+          `total' stellar mass (\mtot{}). 
+          \textbf{Right}: Halo mass dependence of galaxy \mden{} profiles at fixed 
+          `inner-mass' (\minn{}). 
+          In each plot, we match the two samples so that they share similar 
+          distributions of mass and redshift (Appendix~\ref{app:match}).
+          We use $R^{1/4}$ as $x$--axis to provide a balanced view of both the central 
+          and outer regions of the galaxy.
+          Orange and red lines correspond to central galaxies living in 
+          haloes with \logmh{} $\geq 14.2$. 
+          Black and grey lines correspond to central galaxies living in haloes with 
+          \logmh{} $\leq 14.0$. 
+          Thin lines show the profiles of individual galaxies, while thick lines show 
+          the median profile. 
+          The uncertainty on the median profile is given by the shaded region and is 
+          computed via bootstrap resampling. 
+          Brown lines in the bottom panels show the relative difference between  
+          the two median profiles 
+          ($\Delta = \log(\mu_{\star, \mathrm{cenHighMh}}) - 
+          \log(\mu_{\star, \mathrm{cenLowMh}}$). 
+          Errors in the difference between the two profiles are also computed 
+          via bootstrap.
+          The grey-shaded regions show a Monte Carlo test to assess how likely it is to 
+          obtain $\Delta$ from random sub-samples of the data. 
+          To compute the grey-shaded regions, we first mix the two samples 
+          (\rbcg{} and \nbcg{}), then draw sub-samples of galaxies from the mixed 
+          population and compute $\Delta$ in the same fashion as for our fiducial 
+          signal. 
+          We repeat this process 5000 times.  
+          The dark grey--shaded region (light grey--shaded region) shows the 1-$\sigma$ 
+          (3-$\sigma$) fluctuations in $\Delta$ from these 5000 draws.
+          }
+      \label{fig:prof_1} 
+  \end{figure*}
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
+  \begin{figure*}
+      \centering 
+      \includegraphics[width=\textwidth]{fig/redbcg_scaling_relation}
+      \caption{
+          \textbf{Left}: The mass-size relations for \rbcg{} (orange squares) and 
+          \nbcg{} (grey dots) galaxies. 
+          Two vertical lines highlight our $11.6<$ \logms{} $<11.9$ mass bin. 
+          The red solid line shows the best-fitting mass--size relation for \rbcg{} and the 
+          grey dashed line shows the best-fitting relation for \nbcg{}. 
+          Shaded regions in lighter colours show the 1-$\sigma$ uncertainties
+          from Markov chain Monte Carlo (MCMC) sampling.  
+          \song{
+          The green dashed line shows the mass--size relation for $z<0.09$ central 
+          galaxies in massive groups from \citet{HCompany13}. 
+          And the cyan dashed line represents the mass--size relation for 
+          $0.2<z<0.5$ ETGs in groups from the COSMOS survey provided by 
+          \citet{HueartasCompany2013b}.
+          }
+          \textbf{Right:} The relations between \mtot{} and \minn{} for the 
+          \rbcg{} and \nbcg{} galaxies, along with the best-fitting scaling relations for 
+          both samples.
+          }
+      \label{fig:scaling_relation} 
+  \end{figure*}
+%% ------------------------------------------------------------------------------------ %%
 
@@
     In addition to the mass cut above, we also limit our sample to galaxies that live 
-    at the centers of their own dark matter haloes-- so-called ``central'' galaxies. 
+    at the centers of their own dark matter haloes -- so-called `central' galaxies. 
     We use the \redm{} \texttt{v5.10} \citep{Rykoff2014, Rozo2015b} cluster catalogue 
-    to help us construct a central galaxy sample.
+    to help us construct two central galaxy samples: one for high mass haloes, and 
+    one for low mass haloes.
 
     %Central galaxies are important to the study of galaxy-halo connection and follow 
-    %stellar mass--halo mass relation (SHMR; e.g. \citealt{Leauthaud2012, 
+    %stellar mass--halo mass relation (SHMR; e.g., \citealt{Leauthaud2012, 
     %Behroozi2013, Kravtsov2014, Tinker2017}) at high-\mstar{}.
 
-    Firstly, we select 68 massive central galaxies from \redm{} clusters 
-    with richness ($\lambda$) $\geq 30$, and the probability of true central galaxy 
-    ($P_{\mathrm{Cen}}$) $\geq 0.7$, and \logmtot{}$>11.5$ 
-    at $0.3 < z < 0.5$ (63/68 have \logmtot{}$>11.6$). 
+    First, we build a sample of central galaxies in high mass haloes. 
+    We select 68 massive central galaxies from \redm{} clusters with richness
+    $\lambda \geq 30$, with central probability $P_{\mathrm{Cen}} \geq 0.7$, and 
+    \logmtot{}$ >11.5$ at $0.3 < z < 0.5$ (63/68 have \logmtot{}$ >11.6$). 
     This $\lambda$ limit is chosen to mitigate incompleteness in the cluster catalogue
     at the high end of our redshift window. 
-    The $P_{\mathrm{Cen}}$ limit is selected to exclude low probability candidate of 
-    central galaxy. 
-    \song{
-    \citet{Simet2017} calibrates the \mhalo{}-$\lambda$ relation for the \redm{} 
-    clusters using the SDSS weak lensing data after carefully addressing many 
-    important systematic uncertainties.
-    Based on this calibration, these correspond to central galaxies living in haloes 
-    with \mhalo{}$>10^{14.2}$~\msun{}. 
+    The $P_{\mathrm{Cen}}$ limit is imposed to limit our sample to central galaxies. 
+    \song{
+    \citet{Simet2017} present a calibration of the \mhalo{}-$\lambda$ relation for 
+    \redm{} clusters using SDSS weak-lensing. 
+    Based on this calibration, our sample corresponds to central galaxies living 
+    in haloes with \mhalo{}$>10^{14.2}$~\msun{}. 
     This calibration is consistent with several other independent calibrations 
-    using different methods (e.g. \citealt{Saro2015, Farahi2016, 
+    using different methods (e.g., \citealt{Saro2015, Farahi2016, 
     Melchior2016, Murata2017}). 
@@
     The median richness of the sample is $\lambda \approx 41$ 
-    (\mhalo{}$\approx 2.2 \times 10^{14}$~\msun{}), and there are 
-    only 44 central galaxies in clusters with $\lambda>50$ 
-    (\mhalo{}$\approx 3.0 \times 10^{14}$~\msun{}).
-    We will refer to this sample of \textbf{central galaxies in massive haloes} as 
+    (\logmhalo{}$\approx 10^{14.3}$), and there are 44 central galaxies 
+    in clusters with $\lambda>50$ (\mhalo{}$\approx 10^{14.5}$).
+    We refer to this sample of \textbf{central galaxies in massive haloes} as 
     the \rbcg{} sample.
 
-    Secondly, we build a complementary sample of central galaxies in lower-mass haloes
-    by excluding all galaxies that are in any \redm{} cluster with $\lambda > 20$.
-    \song{
-    We convert their $\lambda$ into $M_{\mathrm{200b}}$ using calibration by 
-    \citet{Simet2017}. 
-    \citet{Diemer2015} systematically investigates the mass density profiles of 
-    dark matter haloes under $\Lambda$CDM cosmology using a suite of dark matter--only
-    simulations.  
-    They provide empirical functions that describe the average density profiles 
-    of dark matters with different halo mass and at different redshifts.  
-    Using the \texttt{Colossus} Python package 
+    Second, we build a sample of central galaxies in low mass haloes. 
+    We begin by excluding all galaxies in \redm{} clusters with $\lambda > 20$.
+    \song{
+    We convert $\lambda$ to $M_{\mathrm{200b}}$ using the \citet{Simet2017} calibration. 
+    For each cluster, we compute $R_{\mathrm{200b}}$ using the \texttt{Colossus} Python 
+    package 
     (\citealt{Colossus})\footnote{\url{http://www.benediktdiemer.com/code/colossus/}}
-    provided by these authors, we estimate the $R_{\mathrm{200b}}$ of each cluster 
-    given its $M_{\mathrm{200b}}$ and redshift.
-    } 
-    We further exclude all galaxies within a cylinder around each cluster, with a radius
-    equal to $R_{\mathrm{200b}}$ and a length equal to twice the value of the 
+    provided by \citet{Diemer2015}
+    } 
+    We exclude all galaxies within a cylinder around each cluster, with a radius
+    equal to $R_{\mathrm{200b}}$, and a length equal to twice the value of the 
     photometric redshift uncertainty of the cluster (typically around 0.015 to 0.025).
-    This second sample will be dominated by central galaxies living in haloes with
-    $M_{\mathrm{200b}} < 10^{14}$~\msun{}, and will refer to this sample as \nbcg{}. \
-    There are 833 galaxies with \logmtot{}$> 11.6$ in this sample.
-
-    Satellite contamination should be relative low at the high-\mtot{} end
-    (e.g. \citealt{Reid2014, Hoshino2015, Saito2016, vanUitert2016}). 
-    For instance, the model from \citet{Saito2016} predicts a $\sim 7$\% 
-    fraction for galaxies with \logmtot{}$>11.6$ and \logmh$<14.0$ haloes.
-
-    In Appendix~\ref{app:basic}, we show the distributions of redshift, \mtot{}, and 
-    \minn{} for the \rbcg{} and \nbcg{} samples. 
-    We also compare these two samples on the \mtot{}--rest frame $g-r$ color plane. 
-    Both of them follow the same ``red-sequence'' with only a handful of galaxies 
-    displaying bluer colors.
-
-    We note that our analysis fails to extract 1-D profiles for $\sim10$\% of 
-    \rbcg{} and \nbcg{} galaxies due on-going major mergers or projection effects 
+    This second sample is dominated by central galaxies living in haloes with
+    $M_{\mathrm{200b}} < 10^{14}$~\msun{}; we refer to this sample as \nbcg{}. \
+    There are 833 central galaxies with \logmtot{}$> 11.6$ in this sample.
+
+    Given the high stellar mass, satellite contamination in our sample should be 
+    low (e.g., \citealt{Reid2014, Hoshino2015, Saito2016, vanUitert2016}). 
+    For instance, the model from \citet{Saito2016} predicts that our \rbcg{} sample 
+    should only contain $\sim 7$\% satellites (corresponding to satellites with 
+    \logmtot{}$>11.6$ and living in haloes with \logmh$<14.0$).
+
+    Appendix~\ref{app:basic} shows the distributions of redshift, \mtot{}, and 
+    \minn{} for the two samples. 
+    We also compare these two samples on a \mtot{} versus rest--frame $(g-r)$ colour 
+    plane. 
+    Both samples follow the same red-sequence, with only a handful of galaxies 
+    displaying bluer colours.
+
+    Our analysis fails to extract 1-D profiles for $\sim10$\% of 
+    \rbcg{} and \nbcg{} galaxies due to ongoing major mergers or projection effects 
     (e.g.\ nearby foreground galaxy or bright stars). 
-    However, this small failure rate should not affect any of the results in this paper.
+    We exclude these galaxies from our analysis and this low failure rate should not 
+    affect any of our results.
 
@@
     \minn{} display a large diversity in their stellar haloes. 
-    In Paper~I, we explored the \mstar{}-dependence of the stellar haloes in massive 
-    galaxies, and concluded that the general trends are consistent with the predictions 
-    of the two-phase formation scenario. 
-    In this work, we now investigate the relation between the \mden{} profiles of 
-    massive galaxies, their stellar haloes, and dark matter halo mass. 
-    Here we use \mtot{} as proxy for the ``total'' \mstar{} of massive galaxies and 
-    we use \minn{} as a rough proxy for the stellar mass of the \textit{in situ} 
-    component.  
+    In Paper~I, we explored the \mstar{}-dependence of these stellar haloes. 
+    We now investigate the relation between \mden{} profiles, stellar haloes, and 
+    dark matter halo mass. 
     We remind the reader that although a circular aperture is shown on 
@@
     halo mass at fixed stellar mass.    
-    We will show comparisons of \mden{} profiles at both fixed \mtot{} as well as fixed 
-    \minn{}. 
-    We also ensure that all comparisons are performed with fixed underlying redshift
+    We show comparisons of \mden{} profiles at both fixed \mtot{} and fixed 
+    \minn{} (see Figure~\ref{fig:prof_1}). 
+    All comparisons are performed with a fixed underlying redshift
     distribution by matching samples in redshift in addition to stellar mass
-    (please see Appendix~\ref{app:match}, Appendix~\ref{app:redshift}, 
+    (see Appendix~\ref{app:match}, Appendix~\ref{app:redshift}, 
     and Fig~\ref{fig:match} for details).
@@
 %% ------------------------------------------------------------------------------------ %%     
-    Fig~\ref{fig:prof_1} compares the \mden{} profiles of massive central galaxies 
-    living in less massive dark matter haloes (\logmh$<14.0$) to those living in more 
-    massive dark matter haloes (\logmh$>14.2$) at fixed \mtot{} (left panel) and at 
+    Fig~\ref{fig:prof_1} compares the \mden{} profiles of massive central galaxies in 
+    low mass haloes to those in high mass haloes at fixed \mtot{} (left panel) and at 
     fixed \minn{} (right panel). 
-    At fixed \mtot{}, we compare massive galaxies that have similar ``total'' \mstar{}. 
-    On the right side, we use \minn{} as proxy of the \textit{in situ} \mstar{} to 
-    compare the overall \mstar{} distributions of galaxies living in different 
-    environments that have assembled similar amount of stars at high-$z$.
-    This figure shows the main result of this paper, namely that 
-    \emph{the \mden{} profiles of massive central galaxies show a clear dependence on 
-    dark matter halo mass at both fixed \mtot{} and \minn{}.}
-
-    \song{
-    We estimate the uncertainties of the median \mden{} profiles using bootstrap 
-    resampling test. 
-    We also perform statistical tests to demonstrate that the differences of \mden{}
-    profiles are more significant than the levels allowed by the intrinsic randomness
-    within the combined \rbcg{} and \nbcg{} sample. 
+    The left panel compares galaxies that have similar `total' stellar mass. 
+    The right panel uses \minn{} as a proxy for the \textit{in situ} component to 
+    compare the profiles of galaxies that presumably have similar early formation 
+    histories, but which live in different dark matter haloes today.
+    This figure shows the main result of this paper, namely that \emph{the \mden{} 
+    profiles of massive central galaxies show a clear dependence on dark matter halo 
+    mass at both fixed \mtot{} and \minn{}.}
+
+    \song{
+    We estimate the uncertainties of the median \mden{} profiles using a bootstrap 
+    resampling test, and we perform statistical tests to demonstrate that the 
+    difference between the profiles is more significant than the level allowed by 
+    the intrinsic randomness within the combined \rbcg{} and \nbcg{} sample. 
     }
     We also conduct a variety of tests that verify the robustness of these results with
-    respect to the choices of \mtot{} bins, $\lambda$ cut, the redshift range, and the 
+    respect to our \mtot{} binning scheme, $\lambda$ cut, the redshift range, and the 
     choice of apertures used for the metric masses. 
     Please see Appendix~\ref{app:robust} for further details.
-
-    The key features in Figure Fig~\ref{fig:prof_1} are the following:
+    \song{Appendix \ref{app:cog} and Figure~\ref{fig:cog} compares the same 
+    \mtot{}-matched samples using cumulative \mstar{} profiles (`curve of growth') 
+    and the fraction of \mtot{} enclosed within different radii.
+    Both comparisons highlight the differences in the median \mden{} profiles 
+    from different angles.   
+    }
+
+    The key features in Figure~\ref{fig:prof_1} are the following:
 
@@
 
+        \item At fixed \mtot{}, central galaxies in high mass haloes display shallower 
+            \mden{} profiles compared to those in low mass haloes (i.e., they have 
+            flatter inner \mden{} profiles and more significant outer stellar 
+            envelopes).
+
+        \item The median \mden{} profiles of the two samples cross 
+            each other at ${\sim} 15$-20 kpc, roughly the typical effective radius 
+            ($R_{\mathrm{e}}$) of galaxies at these masses (\logmtot{}$>11.7$--11.8).
+
         \item \song{
-            For the \mtot{}--matched samples, there are some subtle but statistically 
-            significant and robust differences between the two median \mden{} profiles.
-            Due to the logarithmic scale, the difference in the inner region appears 
-            to be very small. 
-            Meanwhile, the difference in \mden{} profile becomes more apparent 
-            at $R>50$ kpc scales.  
-            In Appendix \ref{app:cog} and Figure~\ref{fig:cog}, we compare the same
-            \mtot{}--matched samples using the cumulative \mstar{} profiles 
-            (or `curve of growth') and the fraction of \mtot{} enclosed within 
-            different radius.
-            Both comparisons highlight the differences in median \mden{} profiles 
-            from different angles.
-            }
-
-        \item At fixed \mtot{}, central galaxies in more massive dark matter haloes 
-            display shallower \mden{} profiles compared to those from less massive 
-            dark matter haloes (they have a flatter inner \mden{} profiles and 
-            more significant outer stellar haloes. 
-            The median \mden{} profiles of the \rbcg{} and \nbcg{} samples cross 
-            each other at ${\sim} 15$-20 kpc, roughly the typical effective radius 
-            ($R_{\mathrm{e}}$) of massive galaxies with \logmtot{}$>11.7$--11.8.
-
-        \item For the \minn{}--matched samples, their median \mden{} profiles 
-            are very similar at $R \leq 10$ kpc. 
-            However, massive galaxies with similar \mstar{} within 10 kpc have quite
-            different \mtot{}, and the massive central galaxies in 
-            more massive haloes host much more prominent outer stellar halo.
-
-        \item Also, for the \minn{}--matched samples, the similar slopes of the 
-            \mden{} profiles within 10 kpc are in sharp contrast with the large
-            \textit{intrinsic} scatter we see in the outer \mden{} profiles.
+            When matched by \mtot{}, differences in the inner regions appear 
+            to be small, but this is also driven by the use of a logarithmic y-axis. 
+            The difference becomes more apparent at $R>50$ kpc.  
+            }
+
+        \item Massive galaxies matched by \minn{} display a range of \mtot{} values. 
+            Those in massive dark matter halos have more prominent outer stellar haloes. 
+            The scatter in the outer profiles observed in Figure \ref{fig:prof_1} is 
+            an \textit{intrinsic} scatter (not measurement error).
 
@@
     \song{
-    The subtle differences seen on the left side of Fig \ref{fig:prof_1} suggests
-    that the stellar mass distributions of the most massive central galaxies only
-    weakly depend on their environments. 
-    }
-    This may explain why previous attempts to detect such dependence using 
-    shallower images often failed. 
-    More importantly, this result also suggests that halo mass does not play the 
-    central role in shaping massive central galaxies \textbf{at fixed ``total'' 
-    stellar mass}.
-    Also, the differences in median \mden{} profiles seem to become more prominent 
-    at higher \mtot{}. 
-    This is demonstrated in Appendix~\ref{app:robust} (see Fig~\ref{fig:prof_2}). 
-    Although this trend still needs to be confirmed by larger samples, it 
-    potentially indicates that the assembly of stellar haloes in more massive 
-    central galaxies become more sensitive to their environments.
-
-    \song{
-    Meanwhile, the comparison of \mden{} profiles at fixed \minn{}--a potential 
-    tracer of the \mstar{} in the \textit{in situ} component (right panel of 
-    Fig~\ref{fig:prof_1}) hints that the inner region ($<10$ kpc) and the outer 
-    stellar halo are shaped by different physical processes and response to 
-    environment at different levels. 
-    }  
-    In hydrodynamic simulations, intense dissipative processes help create 
-    self-similar de~Vaucouleur-like ($n{\sim} 4$) \mden{} profile in the inner part 
-    of massive galaxy (e.g. \citealt{Hopkins2008}), and the \mhalo{}-dependent
-    merging history leads to shallower stellar halo profile for central galaxy 
-    of more massive halo (e.g. \citealt{Pillepich2014}). 
-    The intrinsic scatter of halo assembly histories at fixed halo mass and the 
-    stochastic nature of the galaxy--galaxy mergers also explain the large 
-    \textit{intrinsic} scatter in the outer \mden{} profiles and the diversity 
-    seen on the \mtot{}--\minn{} plane (Fig~\ref{fig:m100_m10_color}).
-
-    \textbf{In summary, we reliably detect subtle, but systematic \mhalo{}-dependence 
-    (environmental dependence) of \mden{} profiles within 100 kpc in massive central 
-    galaxies. 
-    Such dependence seems to be consistent with the expectation of more (minor) 
-    mergers in more massive dark matter haloes. 
-    Non-dissipative (minor) mergers should not strongly alter the inner \mden{} 
-    profiles, but can build up the outer halo efficiently
-    (e.g. \citealt{Hilz2013}, \citealt{Oogi2013})}.
-    \song{
-    As for the inner \mden{} profiles, although the comparison of the \minn{}-matched
-    samples reveals clear differences, we should point out that several physical 
-    processes could alter \minn{} and the \mden{} profiles within 10 kpc during the
-    last 10 Gyrs (e.g., AGN feedback or merger of binary supermassive black holes). 
-    We will further discuss this in \S~\ref{ssec:cen}.
-    }
+    Fig \ref{fig:prof_1} shows that the environmental dependence of the profiles of 
+    massive central galaxies is a subtle effect that is most prominent at large radii 
+    ($R>50$ kpc).
+    } 
+    This may explain why previous attempts to detect this effect using shallower images 
+    have often failed.
+
+    The effect becomes more pronounced for even more massive galaxies. 
+    This is shown in Fig~\ref{fig:prof_2} in Appendix~\ref{app:robust}.
+
+    In summary, we detect a subtle, but robust halo mass dependence of the profiles of 
+    massive central galaxies. 
+    This dependence could be driven by the fact that massive halos have a larger minor 
+    merger rate compared to less massive haloes. 
+    Non--dissipative (minor) mergers should not strongly alter inner profiles, but can
+    efficiently build up outer haloes (e.g., \citealt{Hilz2013}, \citealt{Oogi2013}).
 
@@
 
-    The above section shows that the \mden{} profiles of massive galaxies show a 
-    dependence on the masses of their host dark matter haloes. 
-    In this section, we now turn our attention to the more commonly studied stellar 
-    mass--size relation (\mstar{}--$R_{\mathrm{e}}$). 
-    In addition, we will also consider halo mass dependence on the 
-    \mtot{}--\minn{} plane.
-
-%% ------------------------------------------------------------------------------------ %% 
-\subsubsection{Mass-Size Relation}
+    We have shown that the \mden{} profiles of massive galaxies vary with the masses 
+    of their host dark matter haloes. 
+    We now turn our attention to the more commonly studied stellar mass--size relation
+    (\mstar{}--$R_{\mathrm{e}}$). 
+    In addition, we consider halo mass dependence on the \mtot{}--\minn{} plane.
+
+%% ------------------------------------------------------------------------------------ %% 
+\subsubsection{Mass--Size Relation}
     \label{sssec:mass_size}
@@
     The tight relation between \mstar{} and effective radius (or half-light radius; 
-    $R_{\mathrm{e}}$ or $R_{\mathrm{50}}$; e.g. \citealt{Shankar2013, Leja2013, 
-    vdWel2014}) is one of the most important scaling relation for ETGs. 
+    $R_{\mathrm{e}}$ or $R_{\mathrm{50}}$; e.g., \citealt{Shankar2013, Leja2013, 
+    vdWel2014}) is one of the most important scaling relationships for ETGs. 
     Despite numerous attempts, previous studies have failed to detect the 
-    \mhalo{}--dependence of the \mstar{}--$R_{\mathrm{e}}$ relation at low-$z$ 
-    (e.g. \citealt{Weinmann2009, Nair2010, HCompany13, Cerbrian2014}; 
+    \mhalo{}-dependence of the \mstar{}--$R_{\mathrm{e}}$ relation at low-$z$ 
+    (e.g., \citealt{Weinmann2009, Nair2010, HCompany13, Cerbrian2014}; 
     except for the recent result by \citealt{Yoon2017}).
@@
     \song{
-    In the previous section, the differences in the \mden{} profiles already reveals 
-    that the \mtot{}-matched massive galaxies from different environments should have
-    different effective radius (especially see Fig~\ref{fig:cog}). 
-    We now specifically look into the more traditionally studied 
-    \mstar{}--$R_{\mathrm{e}}$ relation.
-    Firstly, we want to point out that `size' is not a well defined parameter for 
-    object like massive galaxies with very extended stellar mass distributions. 
-    In practice, the measurements of `effective radius' or `half--light radius' 
-    not only depends on resolution, depth, and filter of the image, but may also 
-    depend on the adopted model for the light profile.  
-    This makes comparisons of size measurements among different observations 
-    or between observations and models much more uncertain, and is the main reason
-    why we prefer to compare the \mden{} profiles directly.
-    }
-    In this section, we still use \mtot{} as proxy of ``total'' \mstar{} and we adopt 
-    the radius enclosing 50\% of stellar mass within 100 kpc ($R_{\mathrm{50}}$; 
-    derived from the $i$-band curve-of-growth) as the ``size''. 
-    Such definition of ``half--light radius'' is more robust against structural 
-    details, choice of model, and the background subtraction compared to the 
-    effective radius measured using 2-D model with oversimplified assumptions 
-    (e.g. single-\ser{} model). 
+    However, `size' is not a well-defined parameter for massive galaxies with very 
+    extended stellar mass distributions. 
+    In practice, measurements of the `effective radius', or `half-light radius', depend 
+    on resolution, depth, filter, and may also depend on the adopted model for the 
+    light profile.  
+    This makes comparisons of size measurements among different observations, 
+    or between observations and models, uncertain. 
+    This is the main reason why we prefer to compare \mden{} profiles directly which 
+    completely bypasses the need to consider `size'.
+    }
+
+    Nonetheless, to enable comparisons with past work, we now consider the more 
+    traditional mass-size relation. 
+    We adopt the radius enclosing 50\% of stellar mass within 100 kpc 
+    ($R_{\mathrm{50}}$; derived from the $i$-band curve-of-growth) as our `size' for 
+    massive galaxies. 
+    This definition of `half-light radius' is more robust against structural details, 
+    model choice, and background subtraction, compared to the effective radius measured 
+    using oversimplified 2-D models such as the single-\ser{} model. 
     Massive galaxies in this sample are large enough so that the impact of seeing 
@@
 
-    The left panel of Fig~\ref{fig:scaling_relation} shows the 
-    \mtot{}--$R_{\mathrm{50}}$ relations for galaxies in more and less massive
-    dark matter haloes. 
+    The left panel of Fig~\ref{fig:scaling_relation} shows the mass-size relation for 
+    our two samples. 
     We fit the \logmtot{}-$\log_{10} (R_{\mathrm{50}}/\mathrm{kpc})$ relations at 
     $\log(M_{\star,100})>11.6$ using the \texttt{emcee} MCMC sampler 
-    (\citealt{Emcee}) \footnote{The initial guesses are based on maximum 
+    (\citealt{Emcee})\footnote{The initial guesses are based on maximum 
     likelihood estimates, and we assume flat priors for parameters.}.
@@
     Uncertainties in both \mtot{} and $R_{\mathrm{50}}$ are considered. 
-    For \logmtot{}$>11.6$ galaxies, typical uncertainty for mass is $\sim 0.12$
+    For \logmtot{}$>11.6$ galaxies, the typical uncertainty for mass is $\sim 0.12$
     dex.  
-    As for the $R_{\mathrm{50}}$, its uncertainty based on the \mden{} profile
-    is very small due to the high \s2n{} of the profile. 
-    We manually assign 10\% error for $R_{\mathrm{50}}$. 
-    }
-
-    The best-fit relation for \rbcg{} is:
+    The $R_{\mathrm{50}}$ uncertainty is based on the \mden{} profile and is very small 
+    due to the high \s2n{} of the profile. 
+    We manually assign a 10\% error for $R_{\mathrm{50}}$. 
+    }
+
+    The best-fitting relation for \rbcg{} is:
 
@@
 
-    \noindent As shown in the left panel of Fig~\ref{fig:scaling_relation}, 
-    massive central galaxies of more and less massive dark matter haloes lie on 
-    \mtot{}--$R_{\mathrm{50}}$ relations that have similar slopes but 
-    different normalizations. 
-    The best--fit mass--size relations derived here suggests that, 
-    at $0.3 < z < 0.5$, central galaxies with \logmtot{}$>11.6$ in \logmhalo{}$>14.2$
-    haloes are on average $\sim20$\% larger than the centrals from \logmhalo{}$<14.0$
+    \noindent As shown in the left panel of Fig~\ref{fig:scaling_relation}, the two 
+    samples lie on \mtot{}--$R_{\mathrm{50}}$ relations that have similar slopes but 
+    different normalizations. The best-fitting mass--size relation derived here suggests 
+    that, at $0.3 < z < 0.5$, central galaxies with \logmtot{}$>11.6$ in \logmhalo{}$>14.2$
+    haloes are on average $\sim20$\% larger than centrals in \logmhalo{}$<14.0$
     haloes at fixed \mtot{}.
-    This result is robust against the ranges of \mstar{} over which the fit is 
-    performed and against the definitions of  ``total'' \mstar{} and half-light 
+    This result is robust against the stellar mass range over which the fit is 
+    performed and against the definitions of  `total' \mstar{} and half-light 
     radius\footnote{Using \mstar{} within 120 or 150 kpc, or using the 
-    $R_{\mathrm{50}}$ derived within these apertures do not change the results.}. 
-    \song{
-    Due to the relative steep slopes for the \mtot{}--$R_{\mathrm{50}}$ relation, 
-    secondary binning (e.g., different halo mass) may induce artificial differences
+    $R_{\mathrm{50}}$ derived within these apertures does not change the results.}.
+
+    \song{
+    Due to the steep slope of the mass--size relation, secondary binning 
+    (e.g., different halo mass) may introduce artificial differences 
     (e.g., \citealt{Sonnenfeld2017}).
-    We first check the results using the \mtot{}--matched samples and confirm 
-    the above conclusion. 
-    Furthermore, a normalized size parameter ($\gamma$; e.g., \citealt{Newman2012, 
-    HCompany13}) is proposed to control this effect. 
-    We follow the definition of $\gamma$ in \citet{HCompany13}:
+    Besides the differences in best--fit \mtot{}--$R_{\mathrm{50}}$ relation, the 
+    median $R_{\mathrm{50}}$ of the \mtot{}-matched samples also confirm the above 
+    conclusion. 
+    In addition, we use the normalized size parameter ($\gamma$; e.g., 
+    \citealt{Newman2012, HCompany13}) to further test our results. 
+    In \citet{HCompany13}, $\gamma$ is defined as:
     }
@@
     where $\beta$ is the slope of the mass--size relation.
-    For the \logmtot{}$>11.6$ galaxies, we estimate the average $\gamma$ of both
-    samples using the slopes of their best--fit mtot{}--$R_{\mathrm{50}}$ relations.
-    For the \rbcg{} sample, $<\gamma> = 4.2\pm0.4$; for the \nbcg{} one, 
+    We estimate the average $\gamma$ of both samples at \logmtot{}$>11.6$. 
+    For \rbcg{}, $<\gamma> = 4.2\pm0.4$ and for \nbcg{}, 
     $<\gamma> = 3.8\pm0.3$. 
-    Although the uncertainty is still quite large mainly due to the relative small 
-    sample size, the result also suggests a more significant environmental dependence
-    of $R_{\mathrm{50}}$ at fixed stellar mass compared to the \citet{HCompany13} 
-    one.
-    Given the uncertainties involved, the dependence of $R_{\mathrm{50}}$ of 
-    massive central galaxies at fixed \mtot{} is not very significant and is much 
-    weaker than the predictions of certain models in \citet{Shankar2014}. 
-    But before we rule out these models, we need to mention that the uncertainties 
-    of both mass and size are capable of washing out signals of stronger 
-    environment--dependence as shown in \citet{HCompany13}.
-    Therefore we think the direct comparison of \mden{} profiles or the 
-    \mtot{}--\minn{} relation may be better at tracing the environment dependence
-    of structure in massive galaxies. 
-    }
-
-    We qualitatively compare our results with \citealt{HCompany13} (HC13; 
-    green solid line) who studied $z\leq 0.09$ central ETGs in 
-    $12.5 \le$ \logmh{} $< 15$ haloes. 
-    HC13 use the group catalogue by \citet{Yang2007} to estimate halo mass. 
+    The environmental dependence of $R_{\mathrm{50}}$ at fixed \mtot{} is more 
+    significant than the \citet{HCompany13} result but weaker than some 
+    model predictions (e.g., \citealt{Shankar2014}).}
+    %It is important to remember that the uncertainties in both mass and size can 
+    %wash out signals of stronger environment--dependence on mass--size plane 
+    %(e.g., \citealt{HCompany13}), and direct comparison of \mden{} profiles or 
+    %the \mtot{}--\minn{} relation may serve as a better tracer of the environment 
+    %dependence. 
+    %}
+
+    \song{
+    We qualitatively compare our results with the mass--size relation for 
+    $0.2 < z < 0.5$ ETGs in group-scale dark matter halos in COSMOS 
+    (\citealt{HueartasCompany2013b}; HC13a; cyan dashed line).
+    HC13a measure luminosities and sizes using 2--D single--\ser{} models applied to 
+    \textit{HST}/ACS \texttt{F814W} images. 
+    HC13a use circularized effective radii 
+    ($R_{\mathrm{e,Circ}} = R_{\mathrm{e,Fit}} \times \sqrt{b/a}$). 
+    We empirically correct their measurements assuming an average $<b/a>=0.75$.
+    At similar redshifts, the mass-size relation from HC13a lies below our 
+    best--fit relation but the slopes are similar.
+    }
+
+    \song{
+    We also compare with results from \citealt{HCompany13} (HC13b; green dashed line), 
+    who studied $z\leq 0.09$ central ETGs in $12.5 \le$ \logmh{} $< 15$ haloes. 
+    HC13b use the \citet{Yang2007} group catalog to estimate halo mass. 
+    In contrast to the present study, HC13b find no environment dependence in the 
+    mass--size relation for central galaxies. 
     They obtain effective radii from single-\ser{} model fitting to SDSS 
-    images and \mstar{} based on SED fitting using the BC03 (\citealt{BC03}) 
+    images and derive stellar mass based on SED fitting using the BC03 (\citealt{BC03}) 
     synthetic population model. 
-    We convert their \mstar{} estimates from a Kroupa IMF to a Chabrier 
-    IMF by applying a constant -0.05 dex shift (see \citealt{Bernardi2016a}). 
+    We convert the HC13b \mstar{} estimates from a Kroupa IMF to a Chabrier 
+    IMF by applying a constant $-0.05$ dex shift (see \citealt{Bernardi2016a}). 
     We further add $+0.1$dex to the HSC13 stellar masses to account for a systematic 
-    offset between BC03 and our FSPS model (see Paper~1). 
-    The distributions of our massive galaxies on the \mtot{}--$R_{\mathrm{50}}$ 
-    plane follow the HC13 relation reasonably well (with slightly shallower slopes), 
-    even at \logmtot{}$< 11.6$ where our samples start to become incomplete in \mtot{}. 
-    In contrast to the present study, HC13 finds no environment dependence in the 
-    mass--size relation for central galaxies in the range $12.5\le$ \logmh{} $<15.0$. 
-    \song{
-    This could relate to the difference in the depth of HSC and SDSS images.
-    The very low surface brightness stellar haloes that show clearly 
-    environment dependence in this work are difficult to see or model on SDSS images.        
-    And, given the much shallower SDSS images used in HC13, it is a little bit 
-    surprised to see that their mass-size relation is not very different with the
-    ones using deeper HSC images. 
-    Besides the systematics in the \m2l{} estimates using different methods, 
-    different photometric methods could be the main reason behinds this 
-    coincidence.
-    For instance, if shallower image leads to systematically underestimated mass, 
-    it could shift the mass--size relation horizontally.  
-    And single-\ser{} is not very accurate model for massive galaxies, hence it 
-    can result in bias of both mass and size measurements (e.g., see 
-    Appendix~\ref{app:gama}). 
-    This further reflects our point that `size' is not straightforward to measure 
-    and compare, also that the mass--size relation may not be the best tool to 
-    investigate environment dependence in massive galaxies. 
-    }
-
-    In conclusion, we confirm that the \mtot{}--$R_{\mathrm{50}}$ relation of massive
-    central galaxies at $0.3 < z < 0.5$ weakly depends on halo mass. 
-    At fixed \mtot{}, massive central galaxies in denser environments (higher \mhalo{}) 
-    have larger $R_{\mathrm{50}}$ comparing to ones in smaller haloes at fixed 
-    \mtot{}. 
+    offset between BC03 and our FSPS model (see Paper~1). Our overall mass-size relation 
+    is in good agreement with HC13a.
+    }
+
+    \song{
+    Differences between the HC13ab and our results may relate to differences 
+    in modeling methods, and to the shallower ACS/\texttt{F814W} imaging. 
+    As for HC13b, it is also possible that the shallower SDSS image masks the 
+    environmental dependence. 
+    Figure~\ref{fig:prof_1} shows that the most pronounced differences are at 
+    $R>50$ kpc -- these would be difficult to detect with shallow imaging. 
+    Both shallow images and oversimplified models can lead to biased results. 
+    We highlight such effects in Appendix~\ref{app:gama} by comparing luminosities 
+    from HSC to those from single-\ser{} model applied to SDSS.
+    }
+
 %% ------------------------------------------------------------------------------------ %%
@@
 
-    Now we investigate the relationship among \mtot{}, \minn{}, and \mhalo{}. 
+    We now explore the environment dependence of galaxy structure using the 
+    \mtot{}-\minn{} relation.
     Compared to the mass--size relation, the \mtot{}--\minn{} relation is not plagued 
-    by the ambiguity of galaxy ``size'', and also enables a more straightforward 
+    by the ambiguity of galaxy `size', and it also enables a more straightforward 
     comparison with numerical simulations.
 
-    The right panel of Fig \ref{fig:scaling_relation} compares \rbcg{} and \nbcg{}
-    galaxies on the \mtot{}--\minn{} plane. 
-    We find that there is an offset between the overall distributions of these two
-    samples and they follow distinct best-fit \mtot{}--\minn{} relations. 
+    The right panel of Fig \ref{fig:scaling_relation} compares our two samples on the 
+    \mtot{}--\minn{} plane. 
+    The two samples follow distinct best-fitting \mtot{}--\minn{} relations. 
     For \rbcg{} galaxies with \logmtot{}$>11.6$ we find:
@@
 
-    These results are robust against the exact choice for the \mtot{} range over which 
-    the fit is performed. 
-    These results also will not be altered when we replace the \minn{} with the stellar 
-    mass within a 5 or a 15 kpc aperture, or if \mtot{} is replaced with stellar mass 
-    within a 120 or a 150 kpc aperture.
-
-    From Figure \ref{fig:scaling_relation} we can draw the same conclusions as in 
-    the previous section, namely that: 
-    at fixed \mtot{}, central galaxies in more massive haloes tend to have smaller 
-    fraction of stellar mass in their inner regions and higher \mstar{} in their outer
-    stellar haloes. 
-    Meanwhile, at fixed \minn{}--a proxy for the \mstar{} of the ``in situ'' component,
-    central galaxies in more massive haloes tend to be more massive and display more 
-    prominent stellar haloes. 
-    \song{
-    The comparison of \mden{} profiles for \minn{}--matched samples may not directly
-    reflects the environment related processes as other physical mechanisms could 
-    also change the inner \mden{} profiles and their \mtot{} could be quite different. 
-    But the combination of \mtot{} and \minn{} clearly suggests that information of
-    their dark matter haloes or environments is encoded within this simple 2--D plane. 
-    We will discuss more scientific implications of these results in 
-    \S~\ref{sec:discussion}
+    These results are robust against the exact choice of the stellar mass range over 
+    which the fit is performed.
+    These results are also unchanged when we replace \minn{} with the stellar 
+    mass within a 5- or 15-kpc aperture, or if \mtot{} is replaced with a stellar mass 
+    within a 120- or 150-kpc aperture.
+
+    \song{
+    Figure \ref{fig:scaling_relation} presents the same conclusions as in the previous 
+    section, namely that at fixed \mtot{}, central galaxies in more massive haloes tend 
+    to have a smaller fraction of stellar mass in their inner regions and more prominent 
+    outer stellar haloes.  
     }
@@
           panels show $g-i$. 
-          We compare our results with those from \citet{Tal2011} based on stacking 
-          large samples of luminous red galaxies in SDSS at $z{\sim} 0.4$ 
-          (solid blue line on top panel). 
-          We also compare with the results from a stacking analysis of nearby massive 
-          galaxies with high concentration index ($C>2.6$) in 
-          \citet[][blue dash lines on the top and middle panels]{DSouza2014}. 
-          Finally, we also compare with the average $g-r$ and $g-i$ color profiles 
-          from a large sample of nearby elliptical galaxies in \citet[][blue, solid 
-          lines on the middle and bottom panels]{LaBarbera2010}.
+          We compare our results with those from \citet{Tal2011}
+          (solid blue line on top panels). 
+          We also compare our results with those from a stacking analysis of nearby 
+          massive galaxies with high concentration indices ($C>2.6$) from 
+          \citet{DSouza2014} (blue dashed lines in top and middle panels). 
+          We also compare our results with the average $g-r$ and $g-i$ colour profiles 
+          from a large sample of nearby elliptical galaxies for \citet{LaBarbera2010}
+          (blue, solid lines in middle and bottom panels).
           }
@@
     In Paper~I, we show that the ellipticity of the outer stellar halo increases with 
-    \mtot{}, while in contrast, rest--frame color gradients do not display strong 
-    \mtot{}-dependencies. 
-    In this paper, we take this analysis one step further to investigate whether or 
-    not either of these quantities display a halo mass dependency. 
-    We focus on ellipticity and color profiles within 5--60 kpc where we can ignore
+    stellar mass but that rest-frame colour gradients do not depend strongly on 
+    stellar mass. 
+    In this paper, we take this analysis one step further to investigate whether either 
+    of these quantities depends on halo mass. 
+    We focus on ellipticity and colour profiles within 5--60 kpc where we can ignore
     differences in sky subtraction and seeing across different filters. 
-    Galactic extinction and $k$-corrections are applied to both $(g-r)$ and $(g-i)$ 
-    color profiles.
-
-    Figure \ref{fig:ell_color} shows the average ellipticity, $g-r$, and $g-i$ color 
-    profiles for galaxies living in more and less massive dark matter haloes both at 
-    fixed \mtot{} and at fixed \minn{}. 
-    We also compared our results with previous studies that are based on stacked SDSS 
-    images (e.g. \citealt{LaBarbera2010, Tal2011, DSouza2014}). 
-    Figure \ref{fig:ell_color} shows that:
+    Galactic extinction and $k$ corrections are applied to both $(g-r)$ and $(g-i)$ 
+    colour profiles.
+
+    Figure \ref{fig:ell_color} shows the average ellipticity, $g-r$, and $g-i$ colour 
+    profiles for galaxies at fixed \mtot{} and fixed \minn{}. Our main findings are:
 
     \begin{itemize}
-        \item Within $R<50$ kpc, we find that the ellipticity profiles of massive 
-            central galaxies do not depend on halo mass at fixed \mtot{}.
-
-        \item For the \minn{}-matched samples, the \rbcg{} galaxies show higher
-            average ellipticity than the \nbcg{} ones at $R > 10$ kpc. 
-            On the other hand, the average ellipticity in the inner region are very 
-            similar. 
-            This further suggests that the more elongated outer stellar haloes 
-            of massive haloes may relate to the accreted stars.
-
-        \item Massive central galaxies in more and less massive dark matter haloes 
-            display similar rest--frame color gradients (at $r<60$ kpc) at fixed 
-            \mtot{} and at fixed  \minn{}.
+
+        \item \song{
+            The ellipticity profiles of massive central galaxies do not depend on 
+            halo mass at fixed \mtot{} at $R<60$ kpc (upper left panel). 
+            }
+
+        \item \song{
+            However, we do find that at fixed \minn{}, galaxies in massive halos 
+            have more elliptical outer stellar halos compared to galaxies in low mass 
+            halos (upper right panel).
+            This may be further evidence that elongated outer stellar haloes are 
+            built from accreted stars.
+            }
+
+        \item We find no evidence that the rest-frame colour gradients (at $r<60$ kpc) 
+            of massive galaxies depend on halo mass.
 
@@
 
-    Besides these conclusions, the fact that we find smooth ellipticity profiles and 
-    shallow gradients favors the idea of using the flux-weighted average isophotal 
-    shape to extract 1-D \mden{} profiles of massive galaxies. 
-    The similarity of average rest-frame color profiles between the \rbcg{} and \nbcg{}
-    samples suggests that \mden{} profiles based on single average \m2l{} will not bias 
-    our comparisons. 
-    \song{
-    At the same time, we are not certain that similar conclusions apply to the 
-    color or ellipticity profiles within the inner 5--6 kpc due to the smearing effect
-    of the seeing. 
-    Central color gradients may be sensitive to other physical processes and deserves 
-    future investigation using 2-D modelling method and/or image with higher spatial 
-    resolution.
+    The fact that we find smooth ellipticity profiles and shallow gradients favors 
+    the idea of using a flux-weighted average isophotal shape to extract 1-D \mden{} 
+    profiles for massive galaxies. 
+    The similarity in the average rest-frame colour profiles demonstrates that our 
+    results can not simply be explained by differences in radial \m2l{} ratios between 
+    the two samples.
+
+    \song{
+    Our work does not address color gradients below 5--6 kpc because we do not 
+    deconvolve for the PSF. 
+    Color gradients on these scales may be sensitive to other physical processes and 
+    deserve future investigation using 2-D modelling methods and/or images with higher 
+    spatial resolution.
     }
@@
 
-    Using the deep images from the HSC survey, we show that the stellar mass 
-    distributions of massive central galaxies at $0.3 < z < 0.5$ depend on their 
-    environment or \mhalo{}. 
-    At fixed \mtot{} or \minn{}, we find that the central galaxies from more massive 
-    haloes on average have larger half--light radius and host more prominent outer 
-    stellar haloes.
-
-    \song{
-    The two--phase formation scenario can qualitatively explain these results. 
-    Under this picture, intense dissipative processes at $z > 2$ are 
-    responsible for the formation of \textit{in situ} stars in massive central 
-    galaxies. 
-    After the star-formation was rapidly quenched by certain mechanism, the 
-    assembly of massive galaxies in the second phase is dominated by accretion 
-    of satellite galaxies through (mostly) non-dissipative mergers. 
+    Using deep images from the HSC survey, we show that the stellar mass distributions 
+    of massive central galaxies at $0.3 < z < 0.5$ depend on halo mass. 
+    At fixed total galaxy mass, central galaxies in massive halos have larger 
+    half-light radii and host more prominent outer stellar haloes compared to galaxies 
+    in low mass haloes (Figure~\ref{fig:scaling_relation}). 
+    We also find that the outer stellar haloes ($R>50$ kpc) of massive galaxies show 
+    the strongest variations with halo mass.
+
+    \song{
+    The two-phase formation scenario can qualitatively explain these results. 
+    In this scenario, intense dissipative processes at $z > 2$ are responsible for the 
+    formation of \textit{in situ} stars in massive central galaxies. 
+    After a rapid quenching of star formation, the subsequent assembly of massive 
+    galaxies is dominated by the accretion of satellite galaxies through (mostly) 
+    non--dissipative mergers. 
     Dry minor mergers are efficient at depositing \textit{ex situ} stars in the 
-    outskirts of massive galaxies (e.g. \citealt{Oogi2013, Bedorf2013}). 
-    If minor mergers become more frequent in more massive dark matter halos, 
-    they can result in slightly different stellar mass distributions and larger 
-    effective radius for their massive central galaxies.
+    outskirts of massive galaxies (e.g., \citealt{Oogi2013, Bedorf2013}) and hence in 
+    building up outer stellar haloes. 
+    The fact that minor mergers become more frequent in more massive dark matter 
+    haloes could lead to the halo mass dependence of galaxy profiles that we identify 
+    in Figure~\ref{fig:prof_1}.
     }
@@
     \citet{Shankar2014} studied the environment dependence of galaxy size using 
-    a series of hierarchical semi-analytic models. 
+    semi-analytic models. 
     They predict that at fixed stellar mass, the median size of central galaxies 
@@
     Although the major-merger rate does not strongly depend on halo mass 
-    (mass ratio $>1$:3; e.g. \citealt{Hirschmann2013, Shankar2015}), minor 
-    merger rate could still increase with halo mass if the dynamical friction time 
-    is short (e.g. \citealt{Newman2012}). 
-    Therefore, massive central galaxies with $11.5 <$\logms{}$<12.0$ from more massive 
-    haloes (\logmh{}$>14.0$) can have up to four times more minor mergers (1:100--1:3)
-    compared to the ones in less massive haloes at similar stellar mass. 
-    Such increase in the minor-merger rate as a function of halo mass leads to a 
-    halo-mass dependence in the mass-size relation. 
+    (mass ratio $>1$:3; e.g., \citealt{Hirschmann2013, Shankar2015}), the 
+    minor--merger rate could still increase with halo mass if the dynamical friction
+    timescale is short (e.g., \citealt{Newman2012}). 
+    Massive central galaxies with $11.5 <$\logms{}$<12.0$ living in haloes with 
+    \logmh{}$>14.0$ can have up to four times more minor mergers (1:100--1:3) compared 
+    to those in less massive haloes at fixed galaxy mass. 
+    An increase in the minor-merger rate as a function of halo mass can lead to a 
+    halo-mass dependence in the mass--size relation. 
     }
@@
     \song{
-    Our results are broadly consistent with these predictions and also suggest that 
-    the outer stellar haloes ($r>50$ kpc) of massive galaxies show the strongest 
-    variations with halo mass. 
-    At the same time, we should point out that comparison at low redshift alone 
-    can not rule out some other scenarios.  
-    For instance, \citet{Buchan2016} suggests that central galaxies in more massive 
-    haloes could born with more extended structure. 
-    More careful comparisons at higher redshift should help clarify these situations
-    although recent observations of massive central galaxies of $z>2$ proto--clusters 
-    seem to confirm their compact nature (e.g. \citealt{Kubo2017}).
-    }
-
-%% ------------------------------------------------------------------------------------ %% 
-\subsection{Environmental Dependence of the Inner Regions of Massive Galaxies}
-
-    At the same time, from the comparison of median \mden{} profiles of the 
-    \mtot{}--matched samples and from the \mtot{}--\minn{} plane, our results also 
-    show that the centrals of more massive haloes have slightly shallower inner 
-    \mden{} slope and lower fraction of \mtot{} within the inner 10 kpc.
-    \song{
-    This can not be solely explained by the choice of a finite aperture to 
-    estimate ``total'' \mstar{}: assuming that centrals from more massive haloes 
-    have more extended \mden{} profiles, integration out to larger aperture will 
-    make the differences between \rbcg{} and \nbcg{} galaxies on the \mtot{}--\minn{} 
-    plane even more significant.
-    }
-
-    \song{ 
-    Although tempting, it is still too early to conclude that the stellar mass 
-    distributions at the center of massive ETGs also depend on environment. 
-    Many different physicals processes can shape and alter \mden{} profile within 
-    inner 10 kpc, and several of them are not clearly controlled by environment.
-    This is particularly important since progenitors of the massive ETGs in this 
-    work may have higher central \mden{} in the past (e.g., \citealt{Szomoru2012}).
-    } 
-    Major merger can redistribute the inner stellar mass distributions, but major
-    merger rate does not strongly depend on halo mass (e.g., \citealt{Shankar2014}). 
-    Although recent simulations tend to emphasize the contribution of dry minor 
-    mergers in building up the outer envelope, simulations also show that minor 
-    mergers can modify the central surface brightness profiles of the remnants
-    (e.g. \citealt{BoylanKolchin2007}). 
-    Depending on the structure and infalling orbit of the satellite, minor merger 
+    Our results are broadly consistent with these predictions. 
+    However, our results alone cannot rule out other explanations for this halo mass 
+    dependence. 
+    For instance, \citet{Buchan2016} suggest that central galaxies in more massive 
+    haloes have more extended in-situ components. 
+    Comparisons with higher redshift observations will enable us to distinguish 
+    between these two formation scenarios.
+    }
+
+%% ------------------------------------------------------------------------------------ %% 
+\subsection{The Inner Regions of Massive Galaxies}
+
+    Figure \ref{fig:scaling_relation} shows that, at fixed total galaxy mass, centrals 
+    in high mass haloes have slightly shallower inner \mden{} slopes and lower values 
+    of \minn{} compared to those in low mass haloes. 
+    \song{
+    We have tested that this cannot be solely explained by the choice of a finite 
+    aperture (100 kpc) to estimate `total' galaxy mass. 
+    Integrating our profiles out to larger radii makes the differences between \rbcg{} 
+    and \nbcg{} galaxies on the \mtot{}--\minn{} plane even more significant 
+    (see Appendix~\ref{app:robust}). 
+    In hydrodynamic simulations, intense dissipative processes help create a 
+    self-similar de~Vaucouleurs--like ($n{\sim} 4$) inner density profile 
+    (e.g., \citealt{Hopkins2008}). 
+    However, there are a variety of physical processes that can shape and alter the 
+    inner  profile which we now discuss.
+    }
+
+    First, major mergers can redistribute the inner stellar mass distributions, but 
+    the major--merger rate does not strongly depend on halo mass 
+    (e.g., \citealt{Shankar2014}). 
+    However, minor mergers, which do depend on halo mass, can also modify central 
+    surface brightness profiles (e.g., \citealt{BoylanKolchin2007}). 
+    Depending on the structure, and the orbits of infalling satellites, a minor merger 
     can make the inner \mden{} profiles either steeper or shallower.  
-    Interestingly, these authors find, when satellite is accreted from a highly 
-    eccentric and energetic orbit to a core--elliptical galaxy, it tends to reduce 
-    the central \mden{}.  
-    This is relevant here as many massive ETGs are known to be core--elliptical 
+    Interestingly, \citet{BoylanKolchin2007} find that when a satellite is accreted 
+    from a highly eccentric and energetic orbit to a core--elliptical galaxy, the 
+    process tends to reduce the central \mden{}.  
+    This is relevant here, as many massive ETGs are known to be core--elliptical 
     galaxies.
-    \song{
-    Meanwhile, strong adiabatic expansion induced by powerful AGN feedback can 
-    be another mechanism (e.g. \citealt{Fan2008}) to modify the inner \mden{}
-    profile.
-    When the induced mass--loss is efficient enough, it can lead to expanded 
-    central stellar mass distribution and can lower the inner \mden{} significantly. 
-    } 
-    In addition, at smaller scale, the coalesce of super-massive black hoes (SMBHs)  
-    can flatten the central \mden{} profile via efficient scattering effect 
-    (e.g. \citealt{Milosavljevi2002}).
-    On the right side of Fig \ref{fig:scaling_relation}, we find a few \rbcg{} 
-    galaxies with very low \minn{} at high \mtot{} end that are apparently not bothered 
-    by problematic photometry or exceptionally bad seeing.  
-    They may be similar to the recently discovered massive BCGs with very large 
-    depleted cores (a few kpc; e.g. \citealt{Postman2012, LopezCruz2014, Thomas2016,
-    Bonfini2016}) resulting from SMBH mergers.
-
-    \song{
-    The impacts of these processes on the \mden{} profiles and their dependences 
-    on \mhalo{} are important issues that deserve further investigation.  
-    2-D modelling after considering the PSF--convolution and images with higher 
-    spatial resolution will help us connect the central mass distribution with 
-    results of this work. 
-    And comparisons of the \mden{} profiles with massive galaxies in simulation can 
-    help us evaluate the relative importance of these processes.
-    }
+
+    \song{
+    Second, strong adiabatic expansion induced by powerful AGN feedback is 
+    another mechanism (e.g., \citealt{Fan2008, Martizzi2013}) that can modify stellar 
+    density profiles. 
+    When the induced mass loss is efficient enough, it can lead to expanded 
+    central stellar mass distribution and can significantly lower the inner \mden{}. 
+    }
+
+    Finally, the coalescence of super-massive black holes (SMBHs) can also flatten 
+    the central \mden{} profile via an efficient scattering effect 
+    (e.g., \citealt{Milosavljevi2002}).
+    On the right side of Fig \ref{fig:scaling_relation}, there are a few candidates 
+    for galaxies with large cores. 
+    These may be similar to the recently discovered massive brightest cluster galaxies 
+    (BCGs) with very large depleted cores (a few thousand parsecs; e.g., 
+    \citealt{Postman2012, LopezCruz2014, Thomas2016, Bonfini2016}) possibly resulting 
+    from SMBH mergers.
+
+    \song{
+    The impact of these processes on \mden{} profiles and their dependency on 
+    halo mass are important questions that warrant further investigation.}
 
@@
 
-    In this work, we demonstrate that the stellar mass distributions and mass--size 
-    relation of massive central galaxies depend on their host dark matter halo masses. 
-    At $0.3 < z < 0.5$, \logmtot{}$>11.6$ galaxies from \logmhalo{}$>14.0$ haloes 
-    are on average $\sim20$\% larger than the ones from smaller haloes at fixed 
-    \mtot{}.
-
-    Many previous works that focused on the mass-size relation found this relation 
-    is independent of halo mass or environment at $z\sim 0.0$ 
-    (e.g. \citealt{Nair2010, Maltby2010, Cappellari2013, HCompany13}). 
-    As mentioned earlier, both the shallower imaging depth and the oversimple model 
-    (e.g. single-\ser{} or de~Vaucouleurs model) used in the fitting can both 
-    contribute to this difference.
+    Many previous studies that focused on the mass--size relation found this relation 
+    to be independent of halo mass or environment at $z\sim 0.0$ 
+    (e.g., \citealt{Nair2010, Maltby2010, Cappellari2013, HCompany13}). 
+    Shallow imaging and the use of models which do not necessarily well describe 
+    massive galaxies (e.g., single-\ser{} or de~Vaucouleurs models) may have masked 
+    the effect revealed in this paper. 
     In Appendix~\ref{app:gama}, we use the \rbcg{} and \nbcg{} galaxies that overlap 
-    with the GAMA survey to briefly demonstrate this point. 
+    with the Galaxy And Mass Assembly (GAMA) survey to demonstrate this point. 
     We show that, for galaxies with similar \mstar{} derived from single-\ser{} 
     models using shallower SDSS images (\citealt{Kelvin2012}), the ones in more 
-    massive dark matter haloes actually show more prominent outer stellar haloes, 
-    hence both of their stellar mass and effective radius are underestimated.  
-    This shows again that the deeper HSC images has unique advantage in studying 
-    the connection between the assembly of massive galaxies and their dark matter 
-    haloes.
-
-    At low redshift, \citet{Cerbrian2014} find that ETGs with \logms{}$>11.5$ are 
-    slightly larger in more massive haloes, and they also show that this trend is 
-    reversed at lower \mstar{}. 
-    \song{
-    \citet{Kuchner2017} uses one massive cluster at $z=0.44$ to show that ETGs in 
-    that cluster has larger size than the ones in the `field'. 
-    }
-    \citet{Yoon2017} present a careful study of a large sample of $z\sim0.1$ SDSS ETGs 
-    using a non-parametric method and recover a clear environment dependence of 
-    mass-size relation at \logms{}$>11.2$. 
-    They conclude that, at the same \mstar{}, massive ETGs from dense environment 
-    are 20--40\% larger compared to those in underdense environment.
-    Recently, \citet{Charlton2017} uses single-\ser{} model for galaxies at 
-    $0.2 < z < 0.8$ in the CFHTLenS (\citealt{Heymans2012}) and their galaxy--galaxy 
-    lensing measurements to show that larger galaxies tend to live in more massive 
-    dark matter haloes (also see \citealt{Sonnenfeld2017}).
+    massive dark matter haloes actually show more prominent outer stellar haloes.
+    \song{These types of issues complicate the comparisons of mass--size relations 
+    derived from different images or using different methods. 
+    For this reason, we only present a qualitative comparison with previous work}
+
+    At low redshift, \citet{Cerbrian2014} find ETGs with \logms{}$>11.5$ to be slightly 
+    larger in more massive haloes, and they also show that this trend is reversed at 
+    lower \mstar{}. 
+    \song{
+    \citet{Kuchner2017} use one massive cluster at $z=0.44$ to show that ETGs in 
+    that cluster have larger sizes than ETGs in the `field'. 
+    }
+    \citet{Yoon2017} present a study of a large sample of $z\sim0.1$ SDSS ETGs using 
+    a nonparametric method. 
+    They also find an environmental dependence of the mass--size relation at 
+    \logms{}$>11.2$. 
+    Similar to our work, they find that massive ETGs in dense environments are 
+    20--40\% larger compared to those in underdense environments.
+    Recently, \citet{Charlton2017} use a single-\ser{} model for galaxies at 
+    $0.2 < z < 0.8$ in the Canada France Hawaii Lensing Survey (CFHTLenS) 
+    (\citealt{Heymans2012}) together with galaxy--galaxy lensing measurements to 
+    show that larger galaxies tend to live in more massive dark matter haloes 
+    (also see \citealt{Sonnenfeld2017}).
     These results are in broad agreement with those presented here.
-    \song{
-    With the help of weak lensing measurements using HSC images, we will further 
-    explore the connection between the dark matter halo mass and the stellar mass 
-    distributions of their central galaxies. 
-    }
-
-    While there appears to be an emerging consensus at low redshift now that the 
-    high--mass end of the mass-size relation does vary with halo mass, the situation 
-    at higher redshift is more complicated. 
-    Certain studies find an environment dependence of the mass--size relation for 
-    massive quiescent or early-type galaxies that is qualitatively consistent with low 
-    redshift studies (e.g. \citealt{Papovich2012, Bassett2013, Lani2013, 
-    Strazzullo2013, Delaye2014}). 
-    \song{
-    It is interesting to see that several of these works report stronger 
-    environment dependence of size at fixed \mstar{} for either ETGs or quiescent 
-    galaxies (30--50\% larger in denser environment).
-    As shown in \citet{HCompany13} using Monte Carlo test (see their \S~4.2), 
-    when the uncertainties of mass and size are considered, the size difference at 
-    fixed stellar mass could be even more significant between extremely different
-    environments.
-    If true, it indicates that denser regions at high redshift ($z>2$) could accelerate 
-    galaxy evolution (e.g., proto--clusters; see \citealt{Wang2016, Shimakawa2018}) and 
-    the size evolution of massive galaxies in richer environment gradually slows down
-    toward lower redshift (e.g., \citealt{Papovich2012, Andreon2016}.
-    }
-    However, there are also observations that suggest otherwise (e.g. 
+
+    \song{
+    As the halo mass dependence of the sizes and \mden{} profiles of massive 
+    galaxies is being confirmed at low--redshift, the physical origin and 
+    redshift evolution of such dependence will become of increasing interest.  
+    Right now, some observations find a strong environmental dependence of the 
+    mass--size relation for massive quiescent or early-type galaxies at 
+    high--redshift (e.g., \citealt{Papovich2012, Bassett2013, Lani2013, 
+    Strazzullo2013, Delaye2014}), while other works suggest otherwise (e.g., 
     \citealt{Rettura2010, Raichoor2012, Kelkar2015, Allen2015}). 
-    \song{
-    Comparisons with works at high redshift are complicated by many issues. 
-    At high-$z$, these works often rely on small samples or special environments 
-    (rare massive proto-clusters). 
-    Progenitors of massive galaxies in this work may still be star-forming or 
-    late--type galaxies at $z>1$. 
-    And finally, it is just intrinsically more difficult to accurately measure 
-    \mstar{} and size at high redshift (e.g. \citealt{Price2017}).
-    It would be interesting to see whether the current simulations can reproduce 
-    these observed environment dependence and use them to investigate the redshift
-    evolution of such dependence. 
-    Meanwhile, direct comparisons of rest-frame surface brightness or \mden{} 
-    profiles (e.g. \citealt{Szomoru2012, Patel2013, Buitrago2017, Hill2017}) could be 
-    a better approach to compare high- and low-$z$ massive galaxies than the 
-    mass--size relation.
+    Comparison with high--redshift results are complicated by many issues and 
+    is beyond the scope of this work, but we want to point out again that 
+    previous works mostly focus on the mass--size relation while direct comparison 
+    of \mden{} profile (e.g., \citealt{Szomoru2012, Patel2013, Buitrago2017, 
+    Hill2017}) could help us trace the redshift evolution of the environment 
+    dependence better. 
     }
@@
 
-    Until recently, semi-analytic models and hydrodynamic simulations still have 
+    Until recently, semi-analytic models and hydrodynamic simulations have had
     difficulty reproducing the mass--size relation of massive galaxies. 
     Galaxy sizes are sensitive to many different physical processes (star-formation, 
-    feedback, mergers) and matching the galaxy stellar-mass function does not 
-    automatically guarantee a match to the mass-size relation. 
-    Furthermore, while some efforts have been made to use consistent size definitions 
-    (\citealt{McCarthy2017}), more often than not, comparisons of the mass-size relation 
-    do not use consistent size definitions, or only perform crude size conversions 
-    (e.g. 3--D radius in simulation versus 2--D projected radius in observation; 
+    feedback, mergers), and matching the galaxy stellar-mass function does not 
+    automatically guarantee a match to the mass--size relation. 
+    Furthermore, while some effort have been made to use consistent size definitions 
+    (\citealt{McCarthy2017}), more often than not, comparisons of the mass--size relation 
+    do not use consistent size definitions, or they only perform crude size conversions 
+    (e.g., 3-D radii in simulation versus 2-D projected radii in observation; 
     \citealt{Genel2017}). 
-    Observers often quote ``sizes'' corresponding to the half--light radius along the 
-    major axis using 2--D projected images. 
-    Simulations on the other hand, often employ sizes that correspond to the 3--D 
-    aperture half--mass radius (e.g. \citealt{Price2017}).
-
-    As emphasized earlier, definitions of galaxy ``size'' in observations are also not 
+    Observers often quote `sizes' corresponding to the half-light radius along the 
+    major axis using 2-D projected images. 
+    Simulations, on the other hand, often employ sizes that correspond to the 3-D 
+    aperture half-mass radius (e.g., \citealt{Price2017}).
+
+    As emphasized earlier, definitions of galaxy `size' in observations are also not 
     always consistent. 
-    Measurement of ``size'' often shows dependence on image quality (e.g. seeing, 
-    imaging depth), filter, and the adopted method. 
-    Although the elliptical single--\ser{} model is widely adopted in measuring the 
+    Measurements of `size' depend on image quality (e.g., seeing, imaging depth), filter, 
+    and the adopted method. 
+    Although the elliptical single-\ser{} model is widely adopted in measuring the 
     size of galaxies of different types and at different redshifts, it sometimes leads
-    to biased results as it is no longer appropriate model for certain types of galaxy. 
-    Size derived from 1-D curve--of--growth is more model independent and has been 
-    shown to be useful in revealing environmental dependence of the mass--size relation 
-    (e.g. \citealt{Yoon2017} and this work), but it does not take the PSF convolution 
-    effect into account and depends on imaging depth and background subtraction.
+    to biased results as it does not universally describe all types of galaxies. 
+    Sizes derived from 1-D curves-of-growth are more model independent and have been 
+    shown to be useful in revealing the environmental dependence of the mass--size 
+    relation (e.g., \citealt{Yoon2017}, and this work), but this method does not take 
+    the PSF into account. 
+    It also depends on imaging depth and background subtraction.
 
@@
     between observations and theoretical predictions. 
-    In follow-up work, we will present comparisons between our observations and 
-    predictions from hydrodynamic simulations using the using the \mtot{}--\minn{} 
-    plane instead of the mass--size relation.
+    Even better, we argue that galaxy mass profiles can be compared directly with 
+    predictions from hydrodynamic simulations, bypassing the need completely for 
+    `size' estimates.
 
@@
 
-    Using the high-quality images from the first $\sim100$ deg$^2$ of the 
-    Hyper Suprime-Cam Subaru Strategic Program, we group a large sample of massive 
-    central galaxies at $0.3 < z < 0.5$ into two categories based on their dark matter
-    halo mass (\mhalo{}$\simgt 10^{14.2} M_{\odot}$ and 
-    \mhalo{}$\simlt 10^{14} M_{\odot}$), and study how their stellar mass distributions 
-    out to 100 kpc depend on their environments (or \mhalo{}). 
-    The main results are:
+    In this paper, we investigate how the stellar mass profiles of massive galaxies 
+    depend on the masses of their host dark matter haloes. 
+    Using high-quality images from the first $\sim100$ deg$^2$ of the Hyper Suprime-Cam 
+    Subaru Strategic Program, we divide central galaxies at $0.3 < z < 0.5$ into two 
+    samples according to dark matter halo mass (\mhalo{}$\simgt 10^{14.2} M_{\odot}$ 
+    and \mhalo{}$\simlt 10^{14} M_{\odot}$). 
+    Exquisite data from HSC enables us to extract stellar profiles for individual 
+    galaxies in these two samples out to 100 kpc.
+
+    Our main results are as follows:
 
@@
 
-        \item At fixed \mtot{}, we find that massive central galaxies display \mden{} 
-            profiles that have large intrinsic scatter in the outer stellar haloes and 
-            present subtle but systematic trend with \mhalo{}.
-            On average, massive central galaxies in more massive haloes have slightly 
-            shallower inner \mden{} profiles and more prominent outer haloes. 
-            This suggests that the environment affects the assembly of massive central
-            galaxies at fixed ``total'' stellar mass.
-
-        \item At fixed \minn{}, massive central galaxies in more massive haloes 
-            possess much more extended stellar haloes than the ones in smaller haloes, 
-            despite their median \mden{} profiles at $R < 15$ kpc are very similar. 
-            Assuming that \minn{} traces the amount of ``in situ'' stars in massive
-            galaxies, this result is consistent with the picture that more massive 
-            haloes favor the growth of extended stellar haloes in their central 
-            galaxies through more frequent mergers.
-
-        \item The \mtot{}-$R_{\mathrm{50}}$ relation for massive central galaxies 
-            also exhibits environmental dependence. 
-            Central galaxies in more massive haloes have slightly larger
-            $R_{\mathrm{50}}$ than the ones from less massive haloes at fixed \mtot{}.
-
-        \item We also find that massive central galaxies in different environments
-            follow different relations between their \mtot{} and \minn{}. 
-            Assuming that \mtot{} is a reasonable proxy of ``total'' stellar mass and 
-            \minn{} reflects the amount of \textit{in situ} stars, we propose that 
-            this relation can help diagnose the assembly of massive central galaxies 
-            without using ``size'' with ambiguous definition.
-
-        \item At fixed \mtot{}, the ellipticity profiles of massive central galaxies 
-            do not display strong environment dependence at $R < 60$ kpc. 
-            At fixed \minn{}, the more extended stellar haloes presented in the \rbcg{}
-            galaxies also show higher ellipticity than the \nbcg{} galaxies.
-
-        \item We do not find evidence that suggests the rest-frame color profiles 
-            within 60 kpc depend on environment for either the \mtot{}- nor 
-            \minn{}--matched samples.
+    \item At fixed \mtot{}, central galaxies in high mass haloes display shallower 
+        \mden{} profiles compared to those in low mass haloes: they have flatter inner 
+        \mden{} profiles and more significant outer stellar envelopes.  
+        This trend is most pronounced at $R>50$ kpc and thus would easily be missed 
+        with shallow imaging data.
+
+    \item Massive galaxies matched by \minn{} display a range of \mtot{} values and a 
+        large intrinsic scatter in the amplitude of their outer stellar envelopes.
+
+    \item \song{
+        This environmental dependence is also reflected in the mass-size relation, 
+        as well as in the \mtot{}-\minn{} relation. 
+        We propose that simple elliptical aperture masses such as \mtot{} and\minn{} 
+        are better statistics to summarize the properties of galaxy profiles than 
+        commonly used `size' estimates such as $R_e$.
+        }
+
+    \item \song{
+        At fixed \minn{}, galaxies in massive halos have more elliptical outer 
+        stellar halos compared to galaxies in low mass halos. 
+        This may be further evidence that elongated outer stellar haloes are built 
+        from accreted stars.
+        }
+
+    \item At fixed galaxy mass and at $r<60$ kpc, the rest-frame colour gradients 
+        of massive galaxies do not depend on dark matter halo mass.
 
@@
     These results highlight the importance of deep, high-quality images for studying 
-    the assembly of massive haloes and their central galaxies. 
-    We are currently working on combining the current results with weak lensing 
-    measurements of dark matter haloes around these massive galaxies, and comparing 
-    our results with hydrodynamic simulations to gain more physical insights.
-
+    the assembly of massive dark matter haloes and their central galaxies. 
+    Future work will focus on a comparison between our data and predictions from 
+    various hydrodynamic simulations. 
+    This will enable us to gain further insight into the physical mechanisms that 
+    drive the trends discovered in this paper.
 %% ------------------------------------------------------------------------------------ %%
@@
   % Personal 
-  The authors thank Frank van~den~Bosch for insightful discussions and thank 
-  Shun Saito for helping us estimate the fraction of satellite galaxies in our sample.
+  The authors thank Frank van~den~Bosch for insightful discussions and Shun Saito for 
+  helping us estimate the fraction of satellite galaxies in our sample.
+  We also thank Felipe Ardilla and Christopher Bradshaw for useful comments. 
   SH thanks Feng-Shan Liu for sharing the \mden{} profile of the $z\sim1$ BCG from 
   his work. 
+  This material is based upon work supported by the National Science Foundation under 
+  Grant No. 1714610.
 

### 2017-12-08 draft/paper1.tex
Final edits before resubmitt...again

@@
 % Version 7; MNRAS format; Edited by SH
-
-\documentclass[a4paper,fleqn,usenatbib]{mnras}
+% Version 10; MNRAS format; Edited by AL and JG
+% Version 11; MNRAS format; Edited by SH
+% Version 12; MNRAS format; Edited by SH
+% Version 13; MNRAS format; Edited by KB
+% Version 14; MNRAS format; Edited by SH, response to the referee report
+% Version 15; MNRAS format; Edited by Susan Foster
+% Version 16; MNRAS format; Edited by SH, response the the referee report
+
+\documentclass[fleqn,usenatbib]{mnras}
 
@@
 \newcommand{\note}[2]{\textcolor{blue}{\textbf{[Comment (#1): #2]}}}
-\newcommand{\song}[1]{\textcolor{magenta}{\textbf{[Song: #1]}}}
+\newcommand{\song}[1]{\textcolor{cyan}{\textbf{#1}}}
+\newcommand{\susan}[1]{\textcolor{Bittersweet}{\textbf{#1}}}
 \newcommand{\alexie}[1]{\textcolor{blue}{\textbf{[Alexie: #1]}}}
@@
 %% ------------------------------------------------------------------------------------ %% 
-\title[Mass Dependent Stellar Halo in Massive Galaxies]{Tracing the Stellar Halo of 
-	   Massive Galaxies to 100 kpc at $0.3<z<0.5$ using the Hyper Suprime-Cam}
+\title[Mass Dependent Stellar Haloes in Massive Galaxies]{Individual Stellar Haloes of 
+	   Massive Galaxies Measured to 100 kpc at $0.3<z<0.5$ using Hyper Suprime-Cam}
 
@@
         Masayuki Tanaka,$^{5}$
-        Rachel Mandelbaum,$^{7}$
-        Satoshi Miyazaki,$^{5,8}$
+        Satoshi Miyazaki,$^{5,7}$
         \newauthor
-        Yutaka Komiyama,$^{5,8}$
-        HSC collaboration 
+        Yutaka Komiyama$^{5,7}$
         \\
         $^{1}$Kavli-IPMU, The University of Tokyo Institutes for Advanced Study, 
-              the University of Tokyo (Kavli IPMU, WPI), Kashiwa 277--8583, Japan\\
+              the University of Tokyo, Kashiwa 277--8583, Japan\\
         $^{2}$Department of Astronomy and Astrophysics, University of California 
@@
 
-    Massive galaxies are important to our understanding of galaxy formation, and 
-    their extended stellar halos contain crucial fossil records of their assembly 
-    history. 
-    In this work, we use ${\sim}100$ deg$^2$ of deep ($>28.5$ \sb{} in $i$-band), 
-    high-quality (0.6\asec seeing) imaging data from the Hyper Suprime-Cam (HSC) 
-    survey to investigate the surface mass density profiles and outer stellar halos 
-    of massive galaxies. 
-    Our sample consists of ${\sim}7000$ massive (\mstar{}$\geq 11.5$) central galaxies 
-    at $0.3 < z < 0.5$. 
-    The depth of the HSC survey reaches ${\sim}4$ magnitudes fainter than SDSS and 
-    enables us to directly trace stellar mass distributions to 100 kpc without 
-    requiring stacking. 
-    Shallow images and/or over-simplified models like the \texttt{CModel} tend to 
-    miss the extended stellar halo and result in underestimated stellar mass in a 
-    mass-dependent way.  
-    It will impact important applications like the measurements of the stellar mass 
-    function. 
-    With these deeper data, we explicitly show that at fixed stellar mass,
-    massive central galaxies display surface mass density profiles that are not 
-    self-similar, with the outer-slope becoming shallower and the fraction of mass 
-    in the outskirt increasing with total stellar mass.
-    We also show that the ellipticity of the stellar halo increases with stellar
-    mass, while the optical color gradients do not strongly depend on stellar mass.
-    Our results are broadly consistent with the two phase formation scenario of 
-    massive galaxies in which outer envelopes are built up at late times from the 
-    accretions of small systems. 
-    The surface mass density profiles are provided in a convenient tabulated format 
-    in order to facilitate comparisons with predictions from numerical simulations 
-    of galaxy formation.
+    Massive galaxies display extended light profiles that can reach several 
+    hundreds of kiloparsecs. 
+    We use data from the Hyper Suprime-Cam (HSC) survey that is simultaneously wide 
+    (${\sim}100$ deg$^2$) and deep ($>28.5$ \sb{} in $i$-band) to study the stellar 
+    haloes of a sample of ${\sim}7000$ massive galaxies at $z{\sim}0.4$. 
+    The depth of the HSC data enables us to measure surface mass density profiles 
+    to 100 kpc for individual galaxies without stacking. 
+    As in previous work, we find that more massive galaxies exhibit more extended outer 
+    profiles than smaller galaxies.
+    When this extended light is not properly accounted for (because of shallow imaging 
+    and/or inadequate profile modeling), the derived stellar mass function can be 
+    significantly underestimated at the high mass end.  
+    Across our sample, the ellipticity of outer light profile increases substantially 
+    with radius.  
+    We show for the first time that these ellipticity gradients steepen dramatically as 
+    a function of galaxy mass, but we detect no mass-dependence in outer color gradients. 
+    Our results support the two-phase formation scenario for massive galaxies in which 
+    outer envelopes are built up at a later time from a series of merging events. 
+    We provide surface mass density profiles in a convenient tabulated format 
+    to facilitate comparisons with predictions from numerical simulations of 
+    galaxy formation.
 
@@
 
-    Massive galaxies are fascinating objects that have experienced complex assembly 
-    process and dramatic evolution.  
-    They are crucial for both cosmology and the study of galaxy formation. 
-    Simulations of structure formation within the context of the $\Lambda$-CDM 
-    cosmological model make predictions for the hierarchical growth of dark matter 
-    halos and galaxies (e.g. \citealt{Baugh1996, DeLucia2006}), but there are many 
-    open questions regarding the star-formation history, mass assembly process, and 
-    structural evolution of massive galaxies. 
-    Massive galaxies are thought to grow according to a ``two-phase'' formation 
-    scenario (e.g. \citealt{Oser2010, Oser2012}). 
-    In this scenario, the progenitors of $z{\sim} 0$ massive early-type galaxies 
-    (ETGs) undergo a rapid growth phase at $z{\sim} 2$ triggered either by disk 
-    instabilities or gas-rich mergers (e.g. \citealt{Hopkins2008, Dekel2009}). 
-    Observationally, the progenitors of ETGs are thought to correspond to the 
-    population of massive quiescent galaxies at high redshift that have smaller 
-    average effective radii ($R_{\mathrm{e}}$; e.g. \citealt{Trujillo2006, 
-    vanDokkum2008, Cimatti2008}), slightly higher central velocity dispersion and 
-    stellar mass density (\mden{}; e.g. \citealt{vandeSande2011, Belli2014}), and 
-    more disk-like morphologies (e.g. \citealt{vanderWel2011}) than their local 
-    descendants (e.g. \citealt{Bezanson2009, vanDokkum2010}) with similar stellar 
-    mass.
-
-    Following this initial epoch of early formation, feedback from stars and/or AGN 
-    (e.g. \citealt{Sijacki2007, Fabian2012}) efficiently quench star formation in 
-    massive galaxies. 
-    A large fraction of these massive progenitors became quiescent at $z>1$ 
-    (e.g. \citealt{Bezanson2009, Kriek2016}). 
-    The second phase of their assembly is driven by non-dissipative processes such 
-    as dry mergers with other galaxies (e.g. \citealt{Naab2006, Khochfar2006}). 
-    To explain the observed increase of $R_{\mathrm{e}}$ (e.g. 
-    \citealt{Newman2012, vdWel2014}) as well as the build-up of the outer stellar 
-    halos of ETGs (e.g. \citealt{Szomoru2012, Patel2013}), the ``two-phase'' 
-    scenario suggests that minor mergers should dominate the mass assembly during 
-    the second phase (e.g. \citealt{Hilz2012, Hilz2013, Oogi2013, Bedorf2013, 
-    Laporte2013}).
-    Both numerical simulations (e.g. \citealt{Oser2010}) and 
-    semi-analytic models (SAM; e.g. \citealt{LeeYi2013, LeeYi2017}) agree that the 
-    mass fraction in the accreted component should increase with total stellar mass, 
-    despite their technical differences (e.g. \citealt{Lackner2012, Cooper2013, 
-    Qu2017}).
-    For instance, recent result from the Illustris \footnote{
-    \texttt{http://www.illustris-project.org/}} simulation 
-    (\citealt{Vogelsberger2014}, \citealt{Genel2014}) predicts that the fraction of  
-    accreted stars increases significantly with total stellar mass at \logms{}$>11.0$, 
-    and the accreted component starts to dominate the stellar mass budget 
-    ($f_{\mathrm{accreted}}>0.5$) at \logms{}$>11.5$ (\citealt{RodriguezGomez2016}).
-%% ------------------------------------------------------------------------------------ %%
-
-    Given the success of this two-phase scenario in explaining trends like overall size 
-    growth, it is time to confront their predictions with additional observations, 
-    especially the detailed profiles of surface mass density and shape for low redshift 
-    massive galaxies.  
-    Early one-dimensional analysis of nearby massive ETGs suggest that the 
-    single-\ser{} profile can describe their surface brightness (or surface mass 
-    density) profiles reasonably well (e.g. \citealt{Kormendy2009}; except for the
-    most central region), with the \ser{} index increasing with total luminosity 
+    Massive early-type galaxies (ETGs) are predicted to assemble according to a 
+    `two-phase' formation scenario 
+    (e.g. \citealt{Oser2010, Oser2012}): a rapid growth phase at high-redshift that 
+    is dominated by intense dissipative \textit{in situ} star formation (e.g.
+    \citealt{Hopkins2008, Dekel2009}), and a second phase that 
+    is driven by non-dissipative processes such as dry mergers 
+    (e.g. \citealt{Naab2006, Khochfar2006}), with an important role played by 
+    minor mergers 
+    (e.g. \citealt{Hilz2012, Hilz2013, Oogi2013, Bedorf2013, Laporte2013}).
+    Both numerical simulations (e.g. \citealt{Oser2010}) and semi-analytic models 
+    (SAM; e.g. \citealt{LeeYi2013, LeeYi2017}) agree that the fraction of stellar 
+    mass accreted in the second phase (the \textit{ex situ} component) should increase 
+    with total galaxy stellar mass (e.g. \citealt{Lackner2012, Cooper2013, Qu2017}).
+    For instance, recent results from the 
+    Illustris\footnote{\texttt{http://www.illustris-project.org/}} simulation 
+    (\citealt{Vogelsberger2014}, \citealt{Genel2014}) predict that the fraction of  
+    accreted stars increases significantly with galaxy mass, reaching
+    $f_{\mathrm{accreted}}>0.5$ at \logms{}$>11.5$ 
+    (\citealt{RodriguezGomez2016})\footnote{The Illustris simulation
+    does not reproduce the observed stellar mass function at the high mass end.}. 
+%% ------------------------------------------------------------------------------------ %%
+
+    Given the success of the `two-phase' scenario in explaining the properties of 
+    high-$z$ massive quiescent galaxies (e.g. \citealt{vanDokkum2010, vanderWel2011,
+    vandeSande2011, Belli2014}) and the dramatic increase of their effective radii 
+    ($R_{\mathrm{e}}$; e.g. \citealt{Newman2012, vdWel2014}), it is time to confront 
+    this model with additional observations, in particular, the detailed surface 
+    mass density profiles of low-redshift massive galaxies. 
+    Early studies based on one-dimensional light profiles found that the surface 
+    mass density profiles of nearby ETGs are well described by single-\ser{} profiles 
+    (e.g. \citealt{Kormendy2009}; except for the most central regions) and that the 
+    \ser{} index increases with total luminosity 
     (e.g. \citealt{Graham2013}). 
-	However, the situation is in fact more complicated, with a suggestion from 
-	\citet{Schombert2015} that there are actually two families of light profiles:
-	the ones that follow single-\ser{} law well and the ones show significant 
-	deviation.
-	Two-dimensional analysis, meanwhile, finds that the stellar distributions 
-    of massive ETGs are often better fit by multiple-component models 
+    A more recent study of the surface brightness profiles of ETGs 
+    revealed that ETGs belong to two families: 
+    those that follow single-\ser{} law, versus those that significantly deviate from 
+    the single-\ser{} profile \citep{Schombert2015}.  
+    Two-dimensional analyses have also found that the stellar distributions of massive 
+    ETGs are often better described by multiple-component models 
     (e.g. \citealt{Huang2013a, Oh2017}).  
-    \citet{Huang2013b} further suggests a connection between the multi-component 
-    nature of massive galaxies and their two-phase assembly history. 
+    \citet{Huang2013b}, further suggesting a connection between the multi-component 
+    nature of massive galaxies and their two-phase assembly histories.
+
     To further confront the two-phase scenario requires very deep observations of 
-    large samples of massive ETGs to correctly estimate their total stellar mass 
-    (e.g. \citealt{Bernardi2013, DSouza2014}) and explore their assembly history via 
-    their extended, accreted halos (e.g. \citealt{Capaccioli2015, Iodice2016, 
+    large samples of massive ETGs to correctly estimate their total stellar masses
+    (e.g. \citealt{Bernardi2013, DSouza2014}), as well as to quantify the amplitude and 
+    scatter among outer envelopes (e.g. \citealt{Capaccioli2015, Iodice2016, 
     Iodice2017}).
-    Currently, such work is limited by the depth of imaging from large-area surveys 
-    such as the Sloan Digital Sky Survey (SDSS; e.g. \citealt{SDSSDR7, SDSSDR12}) or
-    the small sample size of massive galaxies with deep images.
-
-    In this paper, we take advantage of new high-quality (median 
-    FWHM${\sim} 0.6^{\arcsec}$ in $i$-band) and deep ($i$-band surface brightness 
-    limit $> 28.5$\sb) images from the Hyper Suprime-Cam (HSC) Subaru Strategic 
-    Program \citep[SSP,][]{HSCDR1} to characterize the outer parts of massive galaxies 
-    as a function of their properties. 
-    The deep imaging depth and excellent seeing conditions of HSC images make them 
-    perfect for mapping the \mstar{} distributions of massive galaxies out to very 
-    large radii. 
-    With the help of reliable spectroscopic and photometric redshift 
-    (e.g. the ones for \redm{} clusters, \citealt{Rykoff2014}; \citealt{Rozo2015b}),
-    we select a large sample (${\sim} 7000$) of massive central galaxies at 
-    $0.3 < z < 0.5$ using ${\sim} 100$ deg$^2$ of data from the HSC wide layer. 
-    In this paper, we use this sample to 
-    (a) reliably measure individual surface mass density (\mden{}) profile of 
-    massive galaxy out to 100 kpc, 
-    (b) investigate the dependence of their outer stellar halos on total stellar 
+    To date, large samples of massive galaxies with deep imaging have been lacking. 
+    Even in the nearby universe, it is not trivial to map the low surface
+    brightness outskirts of massive galaxies (e.g., 
+    \citealt{Capaccioli2015, Iodice2016, Iodice2017, Spavone2017, Mihos2017}). 
+    Some of these measurements are based on image stacking methods (e.g. 
+    \citealt{Tal2011, dSouza2015}). 
+    The number of very massive galaxies is also very limited in the local universe.
+    For example, according to the \texttt{MASSIVE} survey (\citealt{Ma2014}), there
+    are only $\sim 60$-70 massive galaxies with \logms$> 11.6$ (based on K-band 
+    luminosity) within 108 Mpc.
+
+    In addition to mass density profiles, the radial profile of ellipticity also 
+    contains information about the 3-D geometry (e.g. \citealt{Tremblay1995, 
+    Tremblay1996, Chang2013, RodriguezPadilla2013, Mitsuda2017}) and kinematics 
+    (e.g. \citealt{Cappellari2012, Weijmans2014}) of stars in massive galaxies.
+    If the stellar haloes of massive galaxies are indeed dominated by accreted 
+    stars, their ellipticities could be systematically different with the inner 
+    regions and may contain clues about the assembly history of massive galaxies 
+    (e.g. average time since last merger, average merger mass ratio).
+    These issues have not been fully explored in both simulation and observation.
+    Certain simulation predicts that a more massive ETG should have rounder shape
+    (e.g. \citealt{Wu2014}), while others generate massive galaxies with very 
+    elongated haloes (e.g. \citealt{Li2017}).  
+    On the observational side, constraints are only available from a few works 
+    that use either an image stacking method (e.g. \citealt{Tal2011, dSouza2015}) 
+    or a small sample of nearby galaxies (e.g. \citealt{Spavone2017}).
+
+    In this paper, we take advantage of the high-quality deep images from the 
+    Hyper Suprime-Cam (HSC) Subaru Strategic Program (SSP) \citep[SSP,][]{HSC-DR1} 
+    (see \S~\ref{ssec:hsc} for details) to characterize  the light profiles of 
+    massive galaxies out to 100 kpc. 
+    We select a large sample (${\sim} 7000$) of massive central galaxies 
+    at $0.3 < z < 0.5$ using ${\sim} 100$ deg$^2$ of data from the HSC wide layer. 
+    %\susan{Note that MNRAS requirement is to use British spelling; however, 
+    %they also prefer the -ize variant of word such as recognize, criticize, 
+    %minimize, emphasize, organize, ionize, polarize, parametrize (etc.).}
+
+    We use this sample to 
+    (1) reliably estimate individual surface mass density (\mden{}) profiles of 
+    massive galaxies out to 100 kpc, 
+    (2) investigate the dependence of their outer stellar haloes on total stellar 
     mass, and 
-    (c) examine the implications for the stellar mass function (SMF) when the outer 
-    halos of massive galaxies are accounted for.   
-    In a second paper in this series, we will further look into the potential 
-    environmental dependence of structures in massive ETGs (Huang\etal in prep.).
+    (3) examine the implications in terms of evaluating the high mass end of the 
+    galaxy stellar mass function (SMF). 
+    In a second paper in this series (Huang \etal in prep.), we will investigate 
+    the environmental (dark matter halo mass) dependence of the sizes of massive 
+    ETGs (Huang\etal in prep.).
 
     This paper is organized as follows. 
-    Section \ref{sec:data} presents our data and our sample selection. 
-    Section \ref{sec:ellipse} describes our procedure for extracting 1-D surface 
+    \S~\ref{sec:data} presents our data and initial sample selection. 
+    \S~\ref{sec:ellipse} describes our procedure for extracting 1-D surface 
     brightness profiles. 
-    Section \ref{sec:mstar} describes how we estimate stellar mass. 
-    Our main results are presented in Section \ref{sec:result} and discussed in 
-    Section \ref{sec:discussion}. 
-    Section \ref{sec:summary} presents our summary and conclusions.
-
-    Magnitudes use the AB system (\citealt{Oke1983}), and are corrected for Galactic 
+    \S~\ref{sec:mstar} describes how we estimate stellar mass.
+    \S~\ref{sec:final} summarizes the final sample selection procedure. 
+    Our main results are presented in \S~\ref{sec:result} and discussed in 
+    \S~\ref{sec:discussion}. 
+    \S~\ref{sec:summary} presents our summary and conclusions.
+
+    Magnitudes use the AB system (\citealt{Oke1983}), and are corrected for galactic 
     extinction using calibrations from \citet{Schlafly11}.
@@
     and ${\Omega}_{\rm \Lambda}=0.7$.
-    Stellar mass is noted \mstar{} and has been derived using a Chabrier Initial Mass 
+    Stellar mass is denoted \mstar{} and has been derived using a Chabrier Initial Mass 
     Function (IMF; \citealt{Chabrier2003}).
 
-    $M_{\mathrm{halo}}$ denotes halo mass in general whereas $M_{\rm 200b}$ is 
-    explicitly defined as $M_{\rm 200b}\equiv M(<r_{\rm 200b})=200\bar{\rho} 
+    Halo mass is defined as 
+    $M_{\rm 200b}\equiv M(<r_{\rm 200b})=200\bar{\rho} 
     \frac{4}{3}\pi r_{\rm 200b}^3$ where $r_{\rm 200b}$
@@
     the mean matter density ($\bar{\rho}$).
+
+    We emphasize that in this work we do not attempt to disentangle the 
+    galaxy light from any `intra-cluster' light component (ICL; e.g. 
+    \citealt{Carlberg1997, Lin2004, Gonzalez2005, Mihos2005}). 
+    Although the rising stellar velocity dispersion in the outskirts of massive 
+    brightest cluster galaxy (BCG)
+    hints at a kinematically separated intra--cluster light (ICL) component (e.g. 
+    \citealt{Dressler1979, Carter1999, Kelson2002, Bender2015, Longobardi2015}),
+    it is extremely difficult to reliably isolate it photometrically.
+    Moreover, both the stellar halo of the main galaxy and the ICL component carry 
+    important information regarding the assembly history of the central galaxy and its 
+    dark matter halo. 
+    Therefore, we adopt the view that the light of the main galaxy and the 
+    ICL component trace different scales of a single, smooth, and continuous 
+    distribution.
 
@@
         \caption{
-            Left: example of the 1-D surface brightness and ellipticity profile 
-            for a massive galaxy at $z=0.23$ in the $i$-band using \texttt{Ellipse}. 
+            \textbf{Left}: Example of the 1-D surface brightness and ellipticity 
+            profile of a massive galaxy at $z=0.23$ in the $i$-band extracted using 
+            \texttt{Ellipse}. 
             In this work, we always show the radial profile using a $R^{1/4}$ scaling 
@@
             at the central surface brightness of the galaxy to highlight the region 
-            affected by seeing. 
-            The grey shaded region highlights the region most affect by seeing 
-            ($r<3$ kpc).
-            On the top panel, the dash line shows the ellipticity used for the final 
-            isophote. 
-            Right: the three color image of this galaxy with isophotes 
+            most strongly affected by seeing.
+            The grey shading highlights the region ($r<6$ kpc) that is equivalent 
+            to twice the size of the half-width of a 1\asec{} seeing at $z\sim 0.5$.
+            Because it is a very conservative estimate of the region, we cannot reliably 
+            extract a 1-D profile due to the smearing effect of seeing.
+            On the top panel, the dashed line shows the mean ellipticity used for the 
+            final isophote. 
+            \textbf{Right}: The 3-colour image of this galaxy with isophotes 
             extracted by \texttt{Ellipse}. 
@@
 
-    The Subaru Strategic Program (SSP, \citealt{HSC_SSP, HSC_DR1}) makes use of the 
-    new prime-focus camera, the Hyper Suprime-Cam (HSC;~\citealt{Miyazaki2012}), on the 
+    The Subaru Strategic Program (SSP, \citealt{HSC-SSP, HSC-DR1}) makes use of the 
+    new prime-focus camera, the Hyper Suprime-Cam (HSC;~\citealt{Miyazaki2012}, 
+    Miyazaki in~prep.), on the 
     8.2-m Subaru telescope at Mauna Kea. 
@@
     view (FoV;~1.5 deg in diameter) of this camera and will cover $>1000$ deg$^2$ 
-    of sky in 5 broad bands ($grizy$) to a limiting depth of $r {\sim} 26$ mag 
+    of sky in five broad bands ($grizy$) to a limiting depth of $r {\sim} 26$ mag 
     in the \texttt{WIDE} layer. 
     This work is based on the internal data release \texttt{S15B}, which covers 
-    ${\sim} 100$ deg$^2$ in all 5-band to full \texttt{WIDE} depth.  
-    The regions covered by this release overlap with a number of spectroscopic surveys 
-    (e.g.\ SDSS/BOSS: \citealt{Eisenstein2011}, \citealt{Alam2015}; 
-    GAMA: \citealt{Driver2011}, \citealt{Liske2015}).
-
-    The HSC \texttt{WIDE} survey is about $3.0$-$4.0$ magnitudes deeper in the 
-    $i$-band surface brightness limit than SDSS. 
+    ${\sim} 110$ deg$^2$ in all five bands to full \texttt{WIDE} depth.  
+    The regions covered by this release overlap with a number of spectroscopic 
+    surveys 
+    [e.g.\ Sloan Digital Sky Survey (SDSS)/Baryon Oscillation Spectroscopic Survey 
+    (BOSS): \citealt{Eisenstein2011}, \citealt{SDSS-DR12}; 
+    Galaxy And Mass Assembly (GAMA): \citealt{Driver2011}, \citealt{Liske2015}].
+    \texttt{S15B} release has similar sky coverage with the Public Data Release 1
+    (Please see Table 3 in \citealt{HSC-DR1} for detailed comparison).
+
+    The HSC \texttt{WIDE} survey is about $3.0$-$4.0$ magnitudes deeper in terms of 
+    the $i$-band surface brightness limit than SDSS. 
     Combined with the excellent imaging resolution (the median $i$-band seeing is 
-    0.6\asec) and the wide area, the HSC survey represents a tremendous dataset to 
-    perform large statistical study of the surface brightness profiles of massive
-    galaxies out to their very outskirts.     
+    0.6\asec) and the wide area, the HSC survey represents an ideal dataset to perform 
+    statistical studies of the surface brightness profiles of massive galaxies out to 
+    their distant outskirts.  
     Fig~\ref{fig:sdss_compare} illustrates the quality of HSC imaging compared to SDSS 
-    for three low redshift ETGs, and shows that HSC survey data are well suited for 
+    for three low-redshift ETGs, and shows that HSC survey data are well suited for 
     mapping the stellar distribution of massive galaxies out to large radii.
@@
 	of strict requirements driven by weak lensing science. 
-    We will therefore use the $i$-band images to measure the stellar distributions of 
+    We therefore use $i$-band images to measure the stellar distributions of 
     massive galaxies.
@@
 %% ------------------------------------------------------------------------------------ %% 
-\subsection{HSC Data Processing}
+\subsection{HSC data processing} 
     \label{sec:pipeline}
 
-    The full details of the HSC data processing can be found in \citet{Bosch2017}
+    The full details of the HSC data processing can be found in \citet{HSC-PIPE}
     and are briefly summarized here. 
@@
     (referred as a \texttt{footprint}) for each source. 
-    Next, \texttt{footprints} and peaks from different bands are merged together before     
+    Next, \texttt{footprints} and peaks from different bands are merged before     
     performing deblending and measurements. 
     Finally, \texttt{hscPipe} selects a reference band for each object based on the 
-    $S/N$ in different bands (for most galaxies in this work, the reference band is 
-    the $i$-band). 
+    $S/N$ in different bands. (For most galaxies in this work, the reference band is 
+    the $i$-band.) 
     After fixing the centroids, shape, and other non-amplitude parameters of each 
-    object in this reference catalog, \texttt{hscPipe} perform forced photometry 
+    object in this reference catalog, \texttt{hscPipe} performs forced photometry 
     on the \texttt{coadd} image in each band.
-    This forced photometry approach is optimized to yield accurate galaxy colors.
+    This forced photometry approach is optimized to yield accurate galaxy colours
+    at $i_{\mathrm{CModel}\leq25.0}$ mag (see \citealt{SynPipe}).
 
     For each galaxy, \texttt{hscPipe} measures a \cmodel{} magnitude using an approach 
-    that is similar to SDSS (\citealt{Bosch2017}). 
-    However, as opposed to SDSS, the HSC \cmodel{} is based on forced photometry which 
-    means that it can accurately measure both the \textit{fluxes and colors of galaxies}. 
+    that is similar to SDSS (\citealt{HSC-PIPE}). 
+    However, as opposed to SDSS, the HSC \cmodel{} is based on forced multi-band 
+    photometry, which means that it can accurately measure both the 
+    \textit{fluxes and colours of galaxies}. 
     The HSC \cmodel{} algorithm fits the flux distribution of each object using a 
-    combination of a de~Vaucouleur and an exponential component and accounts for the PSF. 
+    combination of a de~Vaucouleur and an exponential component and accounts for the 
+    point spread function (PSF). 
     The performance of this algorithm has been tested using synthetic objects 
@@
     massive ETGs with extended stellar distributions. 
-    This is caused by an intrinsic limitation of \cmodel{} as it is incapable of
-    modeling profiles with extremely extended outskirts, a problem that is exacerbated 
+    This is caused by an intrinsic limitation of \cmodel{}, as it is incapable of
+    modelling profiles with extremely extended outskirts, a problem that is exacerbated 
     at the depth of the HSC survey. 
-    In addition, at the depth of the HSC survey, accurate deblending in the vicinity of
-    large ETGs where satellites and background galaxies often blend with the low surface 
-    brightness stellar envelope is a challenging problem. 
-    The deblending method implemented by the \texttt{hscPipe} currently tends to 
-    ``over-deblend'' the outskirts of bright galaxies and leads to an 
-    under-estimation of the the total flux of massive ETGs (this is discussed further in 
-    \citealt{Bosch2017}).  
-    For these reasons, our results will be based on custom developed code to measure 
+    In addition, at the depth of the HSC survey, it is challenging to accurately 
+    deblend in the vicinity of large ETGs, where satellites and background galaxies 
+    often blend with the low surface brightness stellar envelope. 
+    The deblending method currently implemented in \texttt{hscPipe} tends to 
+    `over-deblend' the outskirts of bright galaxies and leads to an 
+    underestimation of the total flux of massive ETGs. (This is discussed further in 
+    \citealt{HSC-PIPE}.)   
+    For these reasons, our results are based on custom-developed code to measure 
     the luminosities and stellar masses of massive galaxies. 
     We use the HSC \texttt{hscPipe} photometry for two purposes: 
-    1) to perform a first broad sample selection, and 2) to estimate the average 
-    color of massive galaxies.
-
-%% ------------------------------------------------------------------------------------ %% 
-  \begin{figure*}
-      \centering 
-      \includegraphics[width=\textwidth]{fig/redbcg_mass_diff_new}
-      \caption{              
-          \textbf{Left:} Difference between \mcmodel{} and \mtot{} for massive
-      	  galaxies (grey dots).
-      	  The running-median of the mass differences along with the standard deviations
-      	  in a series of mass bins are shown in large red, hexagons with error bars. 
-          On average, \mcmodel{} underestimates the total stellar mass of massive 
-          galaxies by 0.1 dex while in some cases, the difference can exceed 0.2 dex.
-          Vertical histograms indicate the mass difference for all galaxies (shaded 
-          histogram) and for the ones with \logmtot{}$>11.6$ (empty histogram).
-          \textbf{Right:} Difference between \mmax{} and \mtot{} in the same format. 
-          The average difference is small (0.02 dex) and does not show 
-          clear mass--dependence. 
-          }
-      \label{fig:mass_diff}
-  \end{figure*}
-
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %% 
-\subsection{Initial Massive Galaxy Sample}
+    (1) to perform a first broad sample selection, and (2) to estimate the average 
+    colour of massive galaxies.
+
+%% ------------------------------------------------------------------------------------ %% 
+\subsection{Initial massive galaxy sample}
     \label{ssec:initial}
 
-    We begin by using a broad luminosity cut to select an initial sample of massive 
+    We begin by using a broad flux cut to select an initial sample of massive 
     galaxies at $z < 0.5$ from the HSC photometric catalog. 
@@
     define a sample that includes almost all \logms{}$\geq 11.5$ galaxies.    
-    We therefore made a conservative selection of initial sample of massive galaxies
+    We therefore perform an initial conservative selection of massive galaxies
     with $i_{\mathrm{HSC, cModel}} \leq 21.5$\footnote{We neglect small differences
-    between the response curves of SDSS-$i$ and HSC-$i$ filters.}
-    and also limit our sample to regions that have reached the required depth of 
-    the \texttt{WIDE} survey in the $i$-band.
+    between the response curves of the SDSS-$i$ and HSC-$i$ filters.}. 
+    We also limit our sample to regions that have reached the required depth of 
+    the \texttt{WIDE} survey in $i$-band as defined in \citet{HSC-DR1}.
     %% The SQL search is saved as "sample.sql" 
@@
 
-    We further select extended objects with no deblending errors, with well defined 
+    We further select extended objects with no deblending errors, with well-defined 
     centroids, and with useful \texttt{cModel} magnitudes in all five bands. 
     After removing objects that have pixels affected by saturation, cosmic-rays, or 
-    other optical artifacts\footnote{each criterion removes less than 8\% of the 
-    entire sample.}. This sample corresponds to 1760845 galaxies and will be referred 
+    other optical artefacts\footnote{each criterion removes less than 8\% of the 
+    entire sample.}, this sample corresponds to 1760845 galaxies and is  referred to
     as \texttt{hscPho}. 
@@
     (e.g.\ \citealt{Rykoff2014}; \citealt{Rozo2015b}).
-    We match the \texttt{hscPho} sample with a spec-$z$ catalog compiled by the HSC 
-    team\footnote{It is created by matching HSC objects with all publicly available 
-    spectroscopic redshifts (e.g.\ SDSS/BOSS; GAMA). 
-    The spec-$z$ quality flag from different catalogs are homogenized into a single 
-    flag that indicates secure redshifts.}.  
-    To ensure reasonable \mstar{}-completeness at the high-\mstar{} end we focus on
+
+    We match the \texttt{hscPho} sample with a spec-$z$ catalogue compiled by the HSC 
+    team.
+    The catalogue is created by matching HSC objects with a series of publicly 
+    available spectroscopic redshifts (e.g.\ SDSS Data Release (DR) 12  
+    \citealt{SDSS-DR12}; GAMA DR2 \citealt{Liske2015}). 
+    The spec-$z$ quality flags from different catalogues are homogenized into a single 
+    flag that indicates secure redshifts.
+    Please see \S~4.4.2 of \citet{HSC-DR1} for details of this catalogue.  
+    To ensure reasonable \mstar{}-completeness at the high-\mstar{} end, we focus on
     the redshift range $0.3 \leq z \leq 0.5$. 
@@
 
-    Objects without a spectroscopic redshift are matched with the central 
-    galaxies from the \redm{} catalog using a $2.0^{\arcsec}$ matching radius. 
-    We keep the matched objects with useful red-sequence photo-$z$ 
-    ($0.3 \leq z_{\lambda} < 0.5$) in the final sample. 
-    These galaxies are the best candidates for centrals in clusters selected from 
-    SDSS DR8 data (\citealt{SDSSDR8}) via a well-tested red-sequence method. 
+    Objects without a spectroscopic redshift are matched with central 
+    galaxies from the \redm{} SDSS DR8 (\citealt{Rykoff2014}) catalogue using a 
+    $2.0^{\arcsec}$ matching radius. 
+    Matched objects with a red-sequence photo-$z$ ($0.3 \leq z_{\lambda} < 0.5$) are 
+    included in our sample. 
     The accuracy of the red-sequence photo-$z$ is sufficient (median 
-    $|z_{\lambda} - z_{\mathrm{Spec}}| {\sim} 0.01$ for the ones with spec-$z$) 
-    for the goal of this work.
-    The \redm{} catalog provides an additional 133 unique redshifts for massive 
+    $|z_{\lambda} - z_{\mathrm{Spec}}| {\sim} 0.01$) for our purpose.
+    The \redm{} catalogue provides an additional 133 unique redshifts for massive 
     galaxies in our sample.
@@
 
-    In the end, at $0.3 \leq z \leq 0.5$, we gather a sample of 25286 galaxies with 
+    In total, at $0.3 \leq z \leq 0.5$, our sample consists of 25286 galaxies with 
     reliable redshift information (referred as \texttt{hscZ}).
     %% Saved as "dr1_wide_galaxy_icmodel_21.5.fits"
-    Among them, the BOSS and SDSS ``legacy'' LRG samples provide the majority of 
-    spec-$z$. and the GAMA survey provides additional $14$\% of spec-$z$.
-    We choose the redshift range of $0.3 \leq z \leq 0.5$ to make sure that 
-    (1) The inner region of massive galaxies can be resolved, and \mstar{} within 
+    The majority of our redshifts comes from the BOSS and SDSS `legacy' luminous 
+    red galaxy (LRG) samples. 
+    The GAMA survey provides an additional $14$\% of all spectroscopic redshifts.
+    Although the GAMA survey only covers parts of the \texttt{S15B} data release, 
+    and hence affects the homogeneity of our sample, it does not affect the results 
+    of this work.
+    We discuss this more in \S \ref{sec:final}.
+
+    We choose the redshift range $0.3 \leq z \leq 0.5$ to make sure that  
+    (1) the inner region of massive galaxies can be resolved, and \mstar{} within 
     10 kpc can be reliably measured; 
-    (2) The background noise and cosmological dimming are not major issues and the 
-    \mden{} profile can be measured out to $>100$ kpc; 
-    (3) Evolution in structure and stellar population properties can be largely 
+    (2) the background noise and cosmological dimming are not major issues so that 
+    the \mden{} profile can be measured out to $>100$ kpc; and
+    (3) redshift evolution in the stellar population properties can be largely 
     ignored.  
-    At both lower and higher redshift, the completeness of spec-$z$ sample starts 
-    to decline.  
-    Also for bright galaxies at lower redshift, the over-subtraction of background 
+    Also, at higher redshift, the completeness of the spec-$z$ sample starts to 
+    decline; at lower redshifts, the over-subtraction of the background level 
     becomes a more serious issue.
-    Before we can define our mass-complete sample of massive galaxies required for 
-    our analysis, we describe our one-dimensional photometric analysis 
-    (\S \ref{sec:ellipse}) and stellar mass estimations (\S \ref{sec:mstar}). 
-    We then define the final sample in \S \ref{sec:final}.
-
-%    By comparing with the Stripe 82 Massive Galaxy Catalog
-%    (\texttt{S82-MGC}; \citealt{Bundy2015}), \citet{Leauthaud2016} have measured the
-%    \mstar{} completeness of the combined BOSS and SDSS samples. 
-%    They estimate that the BOSS spec-$z$ sample is about 80\% complete at 
-%    \logms{}$\geq 11.6$ at $0.3 < z < 0.5$. 
-%    The GAMA survey, which partially overlaps with the HSC footprints, supplements 
-%    our \texttt{hscZ} sample by 14\%. 
-%    Based on \citet{Taylor2011} (e.g.\ their Fig~~6), at $z{\sim} 0.3$, the GAMA 
-%    sample is 80\% complete down to $10^{10.8}$\msun; but only 80\% complete to 
-%    $10^{12.0}$\msun at $z{\sim} 0.5$. 
-%    We can therefore expect our sample to be roughly \mstar{}-complete above 
-%    \logms{}$\geq 11.5$-$11.6$. 
-%    This question will be addressed more carefully using the overlap region between 
-%    HSC and the \texttt{S82-MGC} in Section \ref{ssec:s82}.
-
-%% ------------------------------------------------------------------------------------ %%  
-%\subsection{The \redm{}{} cluster catalog}
-%    \label{ssec:redmapper}
-%    
-%    For now, we wish to focus on galaxies located at the center of their dark matter halos. 
-%    To limit our sample to central galaxies, we use \texttt{v5.10} of the \redm{}{} 
-%    cluster catalog\footnote{See: http://risa.stanford.edu/redmapper/} 
-%    (e.g.\ \citealt{Rykoff2014}; \citealt{Rozo2015b}). 
-%    These authors have developed a well-tested red-sequence cluster finder that has 
-%    been run on SDSS DR8 (\citealt{SDSSDR8}) photometric data. 
-%    For each cluster, the catalog provides a photometric redshift ($z_{\lambda}$), a 
-%    cluster richness ($\lambda$), and identifies the most likely central galaxy (the 
-%    galaxy with the highest $P_{\mathrm{Cen}}$ value). 
-%    The \redm{}{} catalog also provides a list of member galaxies for each cluster and 
-%    their associated membership probabilities. 
-%    Details about the performance of the \redm{}~cluster catalog can be found in 
-%    \citet{Rozo2014}, \citet{Rozo2015a}, and \citet{Rozo2015b}. 
-%    Several studies have published calibrations between the \redm{}~richness estimate, 
-%    $\lambda$, and halo mass (e.g.\ \citealt{Saro2015, Farahi2016, Simet2016, 
-%    Melchior2016}). 
-%    All these studies consistently find that \redm{} clusters with $\lambda > 20$ 
-%    have $\log (M_{\mathrm{halo}}/M_{\odot}) \geq 14.0$. 
-%    The \redm{} catalog therefore helps us group massive central galaxies into 
-%    samples with different average \mhalo{}. 
-%    We will use the central galaxies of \redm{} clusters 
-%    ($P_{\mathrm{CEN}} \geq 0.7$) to form a sample of massive central galaxies that 
-%    live in massive halos.
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %% 
-%\subsection{Massive Central Galaxies in Low and High Mass Halos}
-%    \label{ssec:mass_central}
-%
-%    One of the goals of our work is to investigate the halo dependence of the outer 
-%    envelope. Although there is a correlation between $M_{\star}$ and $M_{\mathrm{Halo}}$,
-%    based on recent constraints of $M_{\star}$-$M_{\mathrm{Halo}}$ relation 
-%    (e.g.\ \citealt{Leauthaud2012}, \citealt{Behroozi2013}, \citealt{Kravtsov2014}), 
-%    even though our sample selects very massive galaxies (\logms{}$\geq 11.5$), they 
-%    With the help of the \redm{} catalog, we can broadly separate our sample into two
-%    groups with \logmh{}$<14.0$ and \logmh{}$>14.2$.
-%    live in a fairly broad range of halos masses.
-%    
-%    % We match this sample with the central galaxies of \redm{}~catalogs using a 
-%    % $1.0^{\arcsec}$ radius, and it results in 704 galaxies.  
-%    %% Saved as "dr1_redbcg_hsc_sdss_gama_1arcsec.fits"
-%    
-%    We match the \texttt{hscZ} sample with the central galaxies of \redm{} clusters 
-%    with $\lambda \geq 30$ and $P_{\mathrm{0.7}} \geq 0.7$, and find 164 matched 
-%    galaxies at $0.3 \leq z \leq 0.5$.
-%    Our sample of \textbf{central galaxies in more massive halos} will be referred to 
-%    as the \rbcg{} sample. 
-%    The median $\lambda$ of the clusters associated with the \rbcg{} sample is 
-%    ${\sim} 41$, corresponding to halo mass of 
-%    $M_{\mathrm{halo}}{\sim} 2.2\times 10^{14}$ $h^{-1}$ $M_{\odot}$.
-%    Only 44 centrals from the \rbcg{} sample live in clusters with $\lambda \geq 50$
-%    ($M_{\mathrm{halo}} {\sim} 3.0\times 10^{14}$ $h^{-1} M_{\odot}$). 
-%    Our \rbcg{} sample therefore corresponds to galaxies in moderate mass halos.
-%    %% Saved as "dr1_redbcg_use_sed5b.fits"
-%    
-%    Out next goal is to construct a sample of central galaxies living in halos with 
-%    \logmh{}$<14.0$. 
-%    We first identify and remove all galaxies within a cylindrical region around all 
-%    \redm{} clusters. 
-%    We use a radius equal to $R_{\mathrm{200b}}$ and the thickness of the cylinder is 
-%    set to twice the uncertainty of the photometric redshift error. 
-%    We convert $\lambda$ to $M_{\mathrm{halo}}$ using the calibration of 
-%    \citet{Simet2016} and we use the mass-concentration relation from 
-%    \citet{Diemer2015} to compute $R_{\mathrm{200b}}$. At $0.3 < z < 0.5$, the 
-%    uncertainty of photo-$z$ is between 0.015 to 0.025, and is enough to exclude 
-%    cluster members.
-%    After removing galaxies associated with \redm{} clusters, the remaining galaxies 
-%    in our sample will be dominated by central galaxies living in halos with 
-%    \logmh{}$\leq 14.0$. 
-%    We will refer to this sample of \textbf{central galaxies in less massive halos}
-%    as the \nbcg{} sample.
-%   
-%    Due to the depth and resolution of SDSS, the \redm{} catalog becomes slightly 
-%    incomplete at lower richness ($\lambda < 40$) at $z > 0.33$. 
-%    To ensure a clean separation in \mhalo{}, here we only focus on the central 
-%    galaxies of clusters with $\lambda > 30$. 
-%    According to \citet{Simet2016}, this $\lambda \geq 30$ sample should correspond to 
-%    $M_{\mathrm{halo}}>10^{14.2} M_{\odot}$. 
-%    We have checked that none of the results in this work depend on the choice of this 
-%    $\lambda$ limit. 
-%    For massive central galaxies that are not in these cluster-level halos, 
-%    we unfortunately can not estimate their \mhalo{} individually, but it is safe 
-%    to assume they will have $\log (M_{\mathrm{halo}}/M_{\odot}) < 14.0$.  
-%    {\bf I am still a bit confused why stellar mass completeness depends on Mh??}
-%
-%    We note that at this stage, our \nbcg{} sample still contains galaxies with a 
-%    wide range of \mstar{} values. 
-%    Later on, once we have more accurate \mstar{} estimates, we will further limit this 
-%    sample to \logms{}$ > 11.5$. 
-%    At this very high mass end, and given that we have rejected satellites in \redm{} 
-%    clusters, any further satellite contamination can be safely neglected 
-%    (e.g. \citealt{Reid2014, Hoshino2015, Saito2016, vanUitert2016}).
-%    %% Saved as "dr1_nonbcg_use_sed5b.fits"
-%    
-% 
-%%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %% 
-%\subsection{Summary of Sample Construction}
-%    \label{ssec:sample}
-%
-%    Using ${\sim} 100$ deg$^2$ of HSC data, we select a large sample of massive central 
-%    galaxies with reliable redshift information, and broadly separate them two 
-%    categories based on $M_{\mathrm{halo}}$.
-%    
-%    The following is a summary of our sample construction.
-%    
-%    \begin{itemize}
-%        \item \texttt{hscPho} sample: this parent sample consists of bright galaxies 
-%            with $i_{\mathrm{cModel}} \leq 21.0$, good quality imaging, and reliable 
-%            \texttt{cModel} photometry in all five HSC bands in the \texttt{S15B} 
-%            data release. 
-%        \item \texttt{hscZ} sample: we limit the \texttt{hscPho} sample to galaxies 
-%            with reliable redshift information. 
-%        \item {\bf Select only central galaxies using RedMapper: total number in full 
-%        sample?}
-%        \item We further divide the sample into an \rbcg{} sample and a \nbcg{} sample, 
-%          with the former roughly having \logmh{}$\geq 14.2$ and the latter having 
-%           \logmh{}$<14.0$.
-%
-%          : we select a sample of 164 galaxies at 
-%            $0.3 \leq z \leq 0.5$ that are the central galaxies 
-%            in $\lambda > 30$ \redm{} clusters. 
-%            They represent the central galaxies in very massive halos 
-%            (\logmh{}$\geq 14.2$). 
-%        \item \nbcg{} sample: after excluding all cluster members from the 
-%            \texttt{hscZ} sample, we have 14661 bright galaxies at 
-%            $0.3 \leq z \leq 0.5$. 
-%            After applying an additional \mstar{} cut (see Section 
-%            \ref{ssec:isedfit}), this sample corresponds to central galaxies in 
-%            halos with \logmh{}$<14.0$.  
-%    \end{itemize}
-%    
-%    We now proceed to measure the luminosities and stellar mass profiles for 
-%    all galaxies in the \rbcg{} and \nbcg{} samples.
-%% ------------------------------------------------------------------------------------ %%
+
+    We now describe our 1-D photometric analysis 
+    (\S \ref{sec:ellipse}) and our stellar mass estimates (\S \ref{sec:mstar}). 
+    We define the final sample in \S \ref{sec:final}.
 
@@
 
-    The surface brightness profile of massive ETG can not be well modeled by the 
+    The surface brightness profiles of massive ETG are not well modelled by the 
     de~Vaucouleurs or single-\ser law, especially at the imaging depth of HSC.
-    These models will fail to simultaneously describe the profile in both the inner 
+    These models fail to simultaneously describe the profile in both the inner 
     and the outer regions and also cannot account for any radial variations in 
     ellipticity and position angle. 
-    In principle, massive galaxies can still be described by more complex 
-    models (e.g \citealt{Huang2013a, Huang2013b, Oh2017}), but they are still 
-    sensitive to the choices of models (e.g. de~Vaucouleurs or \ser{} profile), 
-    the number of components, initial guesses of parameters, and the internal 
-    degeneracies among different parameters. 
-    Background subtraction uncertainty also affects the 2-D model fitting 
-    dramatically, especially for massive ETGs in our sample. 
-    We therefore perform elliptical isophote fitting using the IRAF \texttt{Ellipse} 
-    algorithm (Jedrzejewski 1987) to estimate the total luminosities of massive 
-    galaxies and measure their one-dimensional profiles of stellar mass surface 
-    density (\mden{}). 
-    This 1-D method we adopt is less affected by the issues mentioned above. 
-    Also, we will only study galaxies in the radial range where we are not 
-    sensitive to either the PSF ($r<3-5$ kpc) or the background subtraction 
-    ($r>100$ kpc).
-
-    We prepare large $i$-band cut-outs for each galaxy that extend to 750 kpc in 
-    radius, along with a bad pixel mask and the PSF model. 
-    These cut-outs include all of the light of the galaxy and are large enough to 
-    also evaluate the background level. 
-    We choose to use $i$-band images because they trace the stellar distributions of 
-    massive galaxies at $0.3 \leq z \leq 0.5$ reasonably well 
-    (the observed i-band corresponds to a rest-frame $g$ or $r$ band), but also 
-    because they have better seeing and much lower background levels than the $z$ 
-    and $y$ band images (although these in principle may be better tracers of 
-    \mden{}).
-
-    For each cut-out, to overcome the \texttt{hscPipe} ``over-deblending'' issue, 
-    we use a customized procedure to detect and aggressively mask out
+    Although they can still be described by more complex models 
+    (e.g \citealt{Huang2013a, Huang2013b, Oh2017}), the results are 
+    sensitive to the choice of model, the number of components, and internal 
+    degeneracies among parameters. 
+    2-D modelling is also very sensitive to background subtraction method, 
+    especially for massive ETGs (e.g. \citealt{Huang2013a}).
+
+    We therefore perform elliptical isophote fitting using the Image Reduction 
+    and Analysis Facility (IRAF) \texttt{Ellipse} algorithm (Jedrzejewski 1987) 
+    to estimate the total luminosities of massive galaxies and to measure their 
+    1-D stellar mass surface density profiles (\mden{}). 
+    This 1-D method is less affected by the issues mentioned above. 
+    Also, we only study galaxies in the radial range where our results are less 
+    sensitive to either the PSF or the background subtraction.
+    We ignore the inner $\sim6$ kpc, which is twice the size of 1\asec{} seeing 
+    at $z=0.5$.
+    Using this conservative choice, we can safely ignore the smearing effect of 
+    seeing outside this radius.
+    As we discuss below, we confirm this by comparing our HSC profiles with 
+    observations with higher spatial resolution. 
+    As for the impact from background subtraction, we focus on the profiles 
+    within 100 kpc. 
+    This is an empirical but also conservative choice based on the tests we 
+    conducted on background-corrected postage-stamps. 
+    Once the surrounding objects are appropriately masked out, the extracted 1-D 
+    surface brightness profiles rarely see unphysical truncation or fluctuation 
+    within 100 kpc, especially for the \logmtot{}$>11.6$ galaxies. 
+    Please see Appendix~\ref{app:ellipse} for more details on these tests.
+
+    We generate a postage stamp of each galaxy that extends to 750 kpc in radius, 
+    along with the bad pixel mask and the PSF model. 
+    The postage stamps are large enough to evaluate the local background. 
+    We choose to use $i$-band images since they trace the stellar mass distributions 
+    of $0.3 \leq z \leq 0.5$ massive galaxies reasonably well 
+    (corresponds to rest-frame $g$ or $r$ band). $i$-band images also enable better 
+    seeing and lower background levels than the $z$ and $y$ band images, although 
+    these bands are better tracers of \mden{}.
+
+    To overcome the \texttt{hscPipe} `over-deblending' issue, we use a customized 
+    procedure on each postage stamp to detect and aggressively mask out 
     neighbouring objects. 
@@
     empirical background correction using \texttt{SExtractor}.
-    Then, we run \texttt{Ellipse} on the background-corrected, masked cut-outs 
+    These procedures are described in detail in Appendix~\ref{app:ellipse}. 
+    We should point out that we do not use the photometric results from our 
+    customized process, but simply rely on them for improved local background model
+    and appropriate object mask.
+
+    Then, we run \texttt{Ellipse} on the background-corrected, masked postage stamp 
     following the methodology of \citet{Li2012}. 
@@
     the mean ellipticity and position angle. 
-    We correct these surface brightness profiles for Galactic extinction and 
-    cosmological dimming, and integrate them to various radii to get the luminosity 
+    We correct these profiles for galactic extinction and cosmological dimming, 
+    and we integrate them to various radii to get the luminosity 
     within different physical (elliptical) apertures. 
@@
 
-    We test our procedure using different mask sizes, different \texttt{Ellipse} 
-    parameters, and with or without our background correction. 
-    Based on these tests, we find that our 1-D surface brightness profiles are reliable 
-    up to surfaces brightness levels of $i{\sim}28.5$ \sb. 
-    Beyond that, some of our profiles shows signs of truncation and/or large 
-    fluctuations which are due to either the uncertainty in the background 
+    We test our procedure using different mask sizes and different \texttt{Ellipse} 
+    parameters; we also test the procedure with and without our background correction. 
+    Based on these tests, we find that our 1-D surface brightness profiles are 
+    reliable up to surface brightness levels of $i{\sim}28.5$ \sb. 
+    Beyond that, some of our profiles show signs of truncation and/or large 
+    fluctuations, which are due to either the uncertainty in the background 
     subtraction or the unmasked flux from other objects.
     We choose to limit our study to surface brightness levels up to ${\sim} 28.5$ \sb. 
-    This is a conservative choice but already enables us to measure light profiles 
-    out to $100$ kpc on a galaxy-by-galaxy basis (no stacking). 
-    For more technical details of the \texttt{Ellipse} procedure, please see 
+    This is a conservative choice but is sufficient to enable us to measure light 
+    profiles out to $100$ kpc on a galaxy-by-galaxy basis (no stacking). 
+    The 1-D method fails to extract profiles for ${\sim}10$\% of the sample due 
+    to severe contamination of other objects; these profiles are excluded from the
+    analysis.
+    For additional technical details on the \texttt{Ellipse} procedure, please see 
     Appendix~\ref{app:ellipse}.
@@
 %% ------------------------------------------------------------------------------------ %% 
-
-    For physical (e.g.\ late-stage major merger) and nuisance (e.g.\ nearby foreground 
-    galaxy or bright star) reasons, we cannot extract reliable 1-D profiles for a small 
-    fraction of massive galaxies because they are heavily masked out. 
-    This is an intrinsic limitation of the 1-D method, and it removes ${\sim}10$\% of 
-    the sample.
-    %It affects $18/164$ of the \rbcg{} sample, and a smaller fraction of the 
-    %\nbcg{} sample. 
-    It is worth noting that this excludes most major-merging massive galaxies.
-
-    Given our exquisite profiles that extend to 100 kpc, the definition and meaning 
-    of ``total'' magnitude (and stellar mass) becomes more nuanced.
-    With the help of the \m2l{} estimated in the next section (\S \ref{sec:mstar}), 
-    we integrate the profile to a range of radii, and estimate the stellar mass 
-    within these different apertures.  
-    Motivated by the two-phase scenario, we will consider two benchmark physical 
-    apertures throughout this work:
-
-    \begin{itemize}
-
-        \item \textbf{The \mstar{} within the inner 10 kpc} 
-            (hereafter noted \minn{}). 
-            According to the two-phase scenario, the \textit{in situ} star-formation 
-            quickly builds up the inner, dense core of massive ETGs.  
-            Based on recent observation (e.g.~\citealt{vanDokkum2010}) and 
-            simulations (e.g. \citealt{RodriguezGomez2016}), the \textit{in situ} 
-            component dominates the \mstar{} within one effective radius 
-            ($R_{\mathrm{e}}$, or 5-10 kpc) of $z{\sim}0$ massive ETGs.
-            We therefore use \minn{} as proxy for the mass forged during the 
-            \textit{in situ} phase. 
-            Given the quality of the HSC data, we can reliably measure \minn{} over 
-            our redshift range ($1.0^{\arcsec}$ in radius equals 4.4 and 6.1 kpc 
-            at redshift 0.3 and 0.5).  
-            It is worth noting that, at very high-\mstar{} end, there can be 
-            significant contribution of accreted stars within 10 kpc 
-            (e.g. \citealt{RodriguezGomez2016}). 
-            We will further discuss the justification of this assumption in 
-            \ref{ssec:twophase}.
-
-        \item \textbf{The stellar mass within 100 kpc} 
-            (hereafter noted \mtot{}). 
-            For our galaxy sample, a 100 kpc aperture corresponds to 5-10 
-            $\times R_{\mathrm{e}}$. 
-            We show in section \ref{ssec:mtotal} that most of the \mstar{} for 
-            these ETGs can be captured by a 100 kpc radius and that \mtot{} is 
-            a good proxy for the ``total'' \mstar{}. 
-            Although not perfect, we argue that our measurements of \mtot{} (which are 
-            actually measuring the light directly out to 100 kpc) are a better tracer 
-            of total \mstar{} than model-dependent results from shallower data 
-            (such as SDSS) which rely on extrapolating the light profiles of galaxies 
-            out to large radii.
-
-       \end{itemize}
+  \begin{figure*}
+      \centering 
+      \includegraphics[width=\textwidth]{fig/redbcg_mass_diff_new}
+      \caption{              
+          \textbf{Left:} Difference between \mcmodel{} and \mtot{} for massive
+      	  galaxies (grey dots).
+      	  The running-median of the mass difference is shown by large red hexagons. 
+      	  On average, \mcmodel{} underestimates the total stellar mass of massive 
+          galaxies by 0.1 dex, while in some cases, the difference can exceed 0.2 dex.
+          Vertical histograms indicate the mass difference for all galaxies (shaded 
+          histogram) and for the ones with \logmtot{}$>11.6$ (empty histogram).
+          \textbf{Right:} Difference between \mmax{} and \mtot{} in the same format. 
+          The average difference is small (0.02 dex) and has no clear mass--dependence. 
+          \textbf{Please note that the scales of the vertical axes are different 
+            for these two figures.}
+          }
+      \label{fig:mass_diff}
+  \end{figure*}
 
@@
     This is a reasonable assumption considering that they are mostly dominated by 
-    old stellar populations and are known to have only shallow color gradients. 
-    We will further justify this point by measuring their median color profiles in 
-    Section \ref{ssec:ell_color}.
-
-    We use the broadband Spectral Energy Distributions (SEDs) fitting 
+    old stellar populations and are known to have only shallow colour gradients
+    (e.g.\ \citealt{Carollo1993, Davies1993, LaBarbera2012, DSouza2014}). 
+    We discuss more about this point in Appendix~\ref{app:sed}, and our own 
+    measurements of colour profiles (see \S~\ref{ssec:ell_color}) also demonstrate 
+    this point.
+
+    We use the broadband spectral energy distribution (SEDs) fitting 
     (see \citealt{Walcher2011} for a recent review) code 
@@
     (\citealt{Moustakas13}) to estimate the average \m2l{} and $k$-corrections using
-    5-band HSC \cmodel{} fluxes.
-    Although \cmodel{} tends to underestimate the total flux for bright, extended 
-    objects, it can still yield accurate \emph{average} colors thanks to the 
+    five-band HSC \cmodel{} fluxes.
+    \texttt{iSEDFit} uses a simplified Bayesian approach to estimate the 
+    posterior probability distribution functions (PDF) of key stellar population
+    parameters.
+    Although \cmodel{} tends to underestimate the total fluxes of bright, extended 
+    objects, it can still yield accurate \emph{average} colours thanks to the 
     forced-photometry method that takes the PSF convolution into account
@@
 
-    \texttt{iSEDFit} takes a simplified Bayesian approach. 
-    In short, it first generates a large grid of SEDs from synthetic stellar 
-    population models by drawing randomly from the prior distributions of relevant
-    parameters (e.g. age, metallicity, dust extinction, and star formation history).
-    Based on these models, it uses the observed photometry and redshift to compute 
-    the statistical likelihood, and generates the posterior probability distribution 
-    functions (PDF) for each parameter.  
-    To get the best estimate of a given parameter, \texttt{iSEDFit} integrates the 
-    full PDF over all the other nuisance parameters.
-    Then, the median value and the 1-$\sigma$ uncertainty are derived based on the 
-    marginalized PDF. 
-    Please refer to \citet{Moustakas13} for technical details.
-
-    In this work, we derive average \m2l{} using the Flexible Stellar Population 
+    Here we estimate average \m2l{} using the Flexible Stellar Population 
     Synthesis\footnote{http://scholar.harvard.edu/cconroy/sps-models}
@@
     MILES\footnote{http://www.iac.es/proyecto/miles/pages/stellar-libraries}
-    (\citealt{MILES1}, \citealt{MILES2}) stellar library and assuming a
-    \citet{Chabrier2003} IMF between 0.1 to 100 \msun. 
-    The star formation history (SFH) is assumed to follow a delayed-$\tau$ model with 
-    stochastic star bursts (see Appendix~\ref{app:sed}). 
-    This SFH is appropriate for massive galaxies at low redshifts 
-    (e.g.\ \citealt{Kauffmann2003}). 
-    For stellar metallicity 
-    ($[\mathrm{M}/\mathrm{H}]=\log\ \mathrm{Z}/\mathrm{Z}_{\odot}$), we assume a flat 
-    distribution between 0.004 to 0.03 (the highest value allowed by FSPS).
-    We adopt the \citet{Calzetti2000} extinction law with a order two Gamma 
-    distribution of $A_{V}$ between 0 to 2 magnitude. 
-    The majority of our galaxies are red and quiescent ones so the results are not 
-    very sensitive to parameters related to the SFH or the internal dust extinction. 
-    To achieve reasonable sampling across these parameters, we generate 250000 models.
-
-    We construct five band SEDs using the forced-photometry \cmodel{} magnitudes 
+    (\citealt{MILES1}, \citealt{MILES2}) stellar library, with a
+    \citet{Chabrier2003} IMF between 0.1 to 100 \msun and metallicity 
+    ($[\mathrm{M}/\mathrm{H}]=\log\ (\mathrm{Z}/\mathrm{Z}_{\odot})$) between 
+    0.004 to 0.03. 
+    We assume a delayed-$\tau$ model with stochastic star bursts 
+    for the star formation history (SFH; see Appendix~\ref{app:sed}) of low-$z$ 
+    massive galaxies (e.g.\ \citealt{Kauffmann2003}). 
+    The \citet{Calzetti2000} extinction law is adopted in this work.
+    The massive ETGs in our sample are not very sensitive to the SFH shape or the 
+    internal dust extinction.
+
+    We construct five-band SEDs using the forced-photometry \cmodel{} magnitudes 
     corrected for Galactic extinction. 
-    \cmodel{} only accounts for the statistical error on the flux measurement but 
-    does not account for systematic uncertainties in the model-fitting process. 
-    It therefore underestimates the flux errors of bright galaxies. 
+    Presently, \cmodel{} only accounts for the statistical error on the flux 
+    measurement and it certainly underestimates the true flux errors of bright 
+    galaxies.  
     For this work, we supply \texttt{iSEDFit} with simplified flux errors assuming 
@@
     background noise).  
-    Although these are still conservative estimates of the systematic uncertainties 
-    involved in the model-fitting, tests using synthetic galaxies show that \cmodel{}
-    provides excellent measurements of five-band colors, which are crucial for 
-    reliable \m2l{} estimates.
+    These empirical \s2n{} choices still only provide lower-limits of the true 
+    systematic uncertainties from the model-fitting process. 
+    In \citealt{SynPipe}, we evaluate the accuracy of HSC \cmodel{} photometry 
+    using synthetic galaxies, and show that \cmodel{} provides excellent measurements 
+    of 5-band colours, which are crucial for reliable \m2l{} estimates.
     The typical uncertainty of \logms{} is around 0.06-0.08 dex at \logms${\sim} 11.5$.
@@
     In Appendix~\ref{app:sed}, we briefly summarize the basic statistics of 
-    the sample, including average stellar age, metallicity, and internal dust 
-    extinction along with their relation with \mtot{}. 
-    All these properties behave reasonably for massive galaxies in this sample despite 
-    that we do not utilize them in this paper. 
-    Using the $k$-corrected optical color, we can also confirm that the sample follows 
-    a tight ``red-sequence''.  
-    Please see Appendix~\ref{app:sed} for further details.
-
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %% 
-\subsection{``Total'' Stellar Masses}
+    the sample by showing the relationships between \mtot{} and stellar age, 
+    metallicity, and internal dust extinction. 
+    All these properties behave reasonably for massive galaxies in this sample. 
+    Using the $k$-corrected optical colour, we can also confirm that the sample 
+    follows a tight `red-sequence'.
+
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
+\subsection{Definitions of different aperture stellar masses}
     \label{ssec:mtotal}
 
-    Using the best-fit \mstar{} from \texttt{iSEDFit} (noted as as \mcmodel{}), 
-    we estimate the average \m2l{} in the $i$-band, then use that \m2l{} to convert 
-    our 1-D luminosity density profiles into stellar mass density (\mden{}) profiles. 
-    We also convert our 10 and 100 kpc aperture luminosities into corresponding stellar 
-    mass estimates (noted as \minn{} and \mtot{}).
-
-    For the remainder of this paper, we will use \mtot{} as a proxy of ``total'' 
-    stellar mass. 
-    As expected, the integration of the 1-D profile out to very large radius recovers 
-    more luminosity (stellar mass) compared to the \cmodel{}-based estimates 
-    (Fig \ref{fig:mass_diff}).
+    \texttt{iSEDFit} helps us estimate the best-fitting \mstar{} based on the \cmodel{} 
+    photometry (noted as \mcmodel{}) and the average \m2l{} in the $i$-band. 
+    Then, we can convert the 1-D luminosity density profiles into stellar mass 
+    surface density (\mden{}) profiles with the average \m2l{} and estimate \mstar{} 
+    within different radius by integrating the \mden{} profiles. 
+    Given exquisite \mden{} profiles extending to $>100$ kpc, the definition and meaning 
+    of `total' \mstar{} becomes nuanced.
+    At the same time, motivated by the two-phase scenario, \mstar{} within different 
+    radius may help us trace different physical components. 
+    Considering this, here we define a few benchmark physical apertures throughout 
+    this work:
+
+%% ------------------------------------------------------------------------------------ %%          
+    \begin{itemize}
+
+        \item \textbf{The \mstar{} within the inner 10 kpc} 
+            (hereafter noted \minn{}). 
+            Suggested by recent observation (e.g.~\citealt{vanDokkum2010}) and 
+            simulation (e.g. \citealt{RodriguezGomez2016}), the \textit{in situ} 
+            component dominates the \mstar{} within one effective radius 
+            ($R_{\mathrm{e}}$, or 5-10 kpc) of $z{\sim}0$ massive ETGs.
+            We therefore use \minn{} as the \mstar{} of the inner `core' and as 
+            a proxy for the \textit{in situ} \mstar{}. 
+            The high-quality HSC data enable us to reliably measure \minn{} at 
+            $0.3 < z < 0.5$ ($1.0^{\arcsec}$ in radii equal 4.4 and 6.1 kpc 
+            at redshifts 0.3 and 0.5, respectively).
+            We should point out that in simulation an
+            (e.g. \citealt{RodriguezGomez2016}), \textit{in situ} component can 
+            extend outside the inner 10 kpc, while an \textit{ex situ} component may 
+            contribute to \minn{} at the same time.  
+            We further discuss this assumption in \ref{ssec:twophase}.
+
+        \item \textbf{The \mstar{} within 100 kpc} 
+            (hereafter noted \mtot{}). 
+            For massive galaxies in our sample, 100 kpc aperture corresponds to 5--10 
+            $\times R_{\mathrm{e}}$ and should contain the majority of the \mstar{}. 
+            Here we use \mtot{} as a measure of the `total' \mstar{}. 
+            We show that, although not perfect, \mtot{} is a better tracer 
+            of total \mstar{} than model-dependent results from shallower images 
+            that rely on extrapolating the light profiles out to large radii. 
+            We should point out that the \s2n{} for surface brightness measurement 
+            at \s2n{} is still above the limit set by the intrinsic fluctuation 
+            of the background for our massive galaxies 
+            (e.g. see \citealt{Pohlen2006}).
+
+        \item \textbf{The \mstar{} within the largest available aperture} 
+            (hereafter noted \mmax{}).
+            We know that the \mden{} profiles of massive galaxies extend way beyond 
+            100 kpc with no clear sign of truncation
+            (e.g. \citealt{Gonzalez2005, Tal2011, DSouza2014}).
+            Therefore, \mtot{} should be only considered as the lower limit of the
+            `total' \mstar{}. 
+            Here, we also integrate the \mden{} profile to the edge of the 
+            postage stamp, and we select the isophote that gives us the highest  
+            \mstar{} and define the \mmax{}. 
+            These procedures help us quantify how much extra \mstar{} may be kept 
+            at $>100$ kpc.
+
+    \end{itemize}
+
+    All aperture \mstar{} are measured after adopting an isophote with fixed 
+    ellipticity and position angle, and instances of 10 kpc and 100 kpc refer to 
+    the radius along the major axis of the elliptical isophote.
+
+%% ------------------------------------------------------------------------------------ %%
+
+    In Fig~\ref{fig:mass_diff}, we compare the different definitions of \mstar{}. 
+    As expected, directly measured light out to 100 kpc helps us recover more \mstar{} 
+    compared to \mcmodel{}.
     At high-\mstar{} end (e.g. \logmtot{}$>11.6$), the average difference is larger 
     than 0.1 dex and can be as large as 0.2--0.3 dex.  
-    More importantly, the differences between \mtot{} and \mcmodel{} clearly show 
-    dependence on total stellar mass as \mcmodel{} tends to miss more light in 
-    more massive galaxies.  
-    This relates to the mass-dependence nature of the stellar halos in massive 
-    galaxies and the intrinsic limitation of \cmodel{} method, which we will discuss
-    more in the next section.
-    Such differences also have important implications in the estimation of stellar 
-    mass function or in the study of environment-dependence of galaxy structure.  
-    We will also discuss these topics in Section \ref{sec:discussion}.
-
-    Although 100 kpc is already a very large radius that should enclose the majority 
-    of stars that belong to these massive galaxies, we know that their \mden{} 
-    profiles extend beyond 100 kpc without showing sign of truncation. 
-    Therefore, for massive galaxies, even \mtot{} should be only considered a lower
-    limit of the ``total'' \mstar{}. 
-    In Fig \ref{fig:mass_diff}, we also integrate the \mden{} of each galaxy to the 
-    outermost radii as \mmax{} and compare their differences with \mtot{} 
-    (right panel).  
-    Although \mmax{} is much more uncertain than \mtot{} due to background subtraction
-    and impacts from nearby objects, we see they do return more \mstar{} than \mtot{}. 
-    However, the mass differences are on average very small ($\sim0.02-0.03$ dex) and 
-    do not show strong mass dependence.  
+    For the \cmodel{} photometry in the current \texttt{hscPipe}, the average 
+    difference relates to both the intrinsic limitations \cmodel{} algorithm and the 
+    over-subtracted background. 
+    In \S~\ref{ssec:sbp_compare}, we use the \mden{} profiles to show that a large 
+    fraction of these galaxies have \mden{} profiles shallower than the de~Vaucouleurs 
+    profile; it is therefore not surprising that \cmodel{} systematically 
+    underestimates the luminosity.
+    More importantly, the differences clearly depend on total stellar mass, as 
+    \mcmodel{} tends to miss more \mstar{} in more massive galaxies.  
+    This limitation in \mcmodel{} relates to the mass-dependent nature of the 
+    stellar haloes of massive galaxies (see \S~\ref{ssec:sbp_compare} too).
+    These differences have important implications for estimates of the stellar 
+    mass function and for studies of the environment-dependence of galaxy structure.
+
+    The right panel of Fig~\ref{fig:mass_diff} compares \mmax{} and \mtot{}.  
+    Uncertainties in the background subtraction and the impact of neighbouring 
+    objects make \mmax{} more uncertain than \mtot{}. 
+    None the less, we still see that \mmax{} becomes larger than \mtot{}. 
+    The differences are on average very small ($\sim0.02-0.03$ dex) and do not show 
+    strong mass dependence.  
     This confirms that, at the current depth of HSC images, \mtot{} can be used as 
-    good proxy of ``total'' stellar mass.
-
-    Our methodology ignores any radial variations in \m2l{}. 
-    It is well known that massive ETGs have negative optical color gradients 
-    indicating gradients in \m2l{} (e.g.\ \citealt{Carollo1993, Davies1993, 
-    LaBarbera2012, DSouza2015}).
-    These color gradients are shallow and smooth out to a few times the effective 
-    radius and color gradients at the outskirts are not yet well quantified.
-    Therefore, using average \m2l{} is unlikely to bias the results on \mstar{}
-    measurements.  
-    We will discuss color gradients more in Section~\ref{ssec:ell_color}. 
-    In summary, we do not find optical color gradient shows dependence on stellar
-    mass, hence the results about the mass-dependence of the \mden{} profiles will 
-    not be affected by it.
-
-    %Our results looking at the outer envelopes as a function of mass and environment 
-    %will be robust as long as there is \emph{no significant difference in 
-    %the average color gradient between sub-samples}.
-    %We have confirmed that this is indeed the case (see Section~\ref{ssec:ell_color}).
-
-    Our method for deriving total \mstar{} is similar to the method adopted by the 
-    GAMA survey (\citealt{Taylor2011, Kelvin2012}), where the average \m2l{} is from 
-    SED fitting of PSF-matched aperture photometry and the total luminosity comes from 
-    sing-\ser{} modeling of the SDSS images. 
-    To avoid the differences in stellar population assumptions, we directly compare the 
-    total luminosity within 100 kpc and the GAMA single-\ser{} luminosity for the same
-    galaxies. 
-    At high-\mstar{} end, the HSC 1-D profiles still recover more light than the 
-    single-\ser{} model on average.
-    It is likely that the GAMA models fail to capture the flux associated with the 
-    outskirts of galaxies due to the limited depth of SDSS.  
-    Meanwhile, there are also many cases where the high-\ser{} index of GAMA model leads 
-    to over-estimated total luminosity. 
-    We will discuss more of this comparison in the next paper of this series 
-    (Huang\etal in prep.).
-
-    %We have compared our \mstar{} values with those from GAMA and the results are given 
-    %in Appendix~\ref{app:gama}.
-
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %%        
-\subsection{Stellar Mass Completeness}
-    \label{ssec:complete}
-
-    With the help of the \texttt{S82-MGC} (\citealt{Bundy2015}), we investigate the 
-    \mstar{} completeness of our samples. 
-    The \texttt{S82-MGC} sample matches the deeper SDSS photometric data in the 
-    Stripe 82 region (\citealt{Annis2014}) with the near infrared data from the United 
-    Kingdom Infrared Telescope Infrared Deep Sky Survey (UKIDSS; 
-    \citealt{Lawrence2007}). 
-    The deeper photometry and better photo-$z$s make the \texttt{S82-MGC} sample 
-    complete to \logms{}$\geq 11.2$ at $z<0.7$ which makes it sufficient to evaluate 
-    the completeness of our HSC sample.   
-	By comparing with the Stripe 82 Massive Galaxy Catalog
-    (\texttt{S82-MGC}; \citealt{Bundy2015}), \citet{Leauthaud2016} have measured the
-    \mstar{} completeness of the combined BOSS and SDSS samples. 
-    They estimate that the BOSS spec-$z$ sample, which is the main contributor of 
-    spec-$z$ in our massive galaxy sample, is about 80\% complete at 
-    \logms{}$\geq 11.6$ at $0.3 < z < 0.5$. 
-    As the secondary contributor, the GAMA survey is 80\% complete down to 
-    $10^{10.8}$\msun at $z{\sim} 0.3$, but is only 80\% complete to 
-    $10^{12.0}$\msun{} at $z{\sim} 0.5$ according to \citet{Taylor2011} (e.g.\ 
-    their Fig~~6).
-
-    There are 20453 \texttt{S82-MGC} galaxies that are also in the \texttt{hscPho} 
-    sample at $0.3 \leq z_{\mathrm{s82}} \leq 0.5$. 
-    We estimate \mcmodel{} values of these galaxies using our fiducial 
-    procedure\footnote{The \mstar{} using HSC photometry is in excellent with the 
-    values derived from the \texttt{S82-MGC} which includes NIR data from UKIDSS; 
-    \texttt{S82-MGC} also uses \texttt{iSEDFit} with similar assumptions.}. 
-    Figure~\ref{fig:mass_complete} compares the volume number density distributions 
-    of galaxies from \texttt{S82-MGC} with the one for galaxies in our 
-    sample\footnote{Since we do not apply any statistical correction on the 
-    completeness, we do not use the term ``stellar mass function'' to avoid confusion;
-    Errors on the distributions are estimated via bootstrap resampling}. 
-    Based on Fig~\ref{fig:mass_complete}, we conclude that our sample of massive 
-    galaxies is reasonably complete down to \logmcmodel{}${\sim} 11.5$ at 
-    $0.3 \leq z \leq 0.5$. 
-    %The \rbcg{} sample is less affected by completeness because we can utilize 
-    %photo-$z$s from \redm{}. 
-    %However, the completeness of the \nbcg{} sample is still limited by the 
-    %availability of spec-$z$s from BOSS.    
-    Given the average difference between \mtot{} and \mcmodel{}, we will focus on 
-    the galaxies with \logmtot{}$> 11.6$ where our sample shows good completeness.
-    The massive galaxies with $11.4 \le$\logmtot{}$<11.6$ are also included in the 
-    discussion since there is no obvious reason to worry about the impact of
-    completeness on the main results of this work.
-
-    %When comparing \nbcg{} and \rbcg{} we will also always make sure that the two 
-    %samples are well matched both in terms of \mstar{} as well as in terms of redshift. 
-    %Please see the next section and Appendix~\ref{app:match} for more details.
-
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %%  
-\section{The Final Sample}
-    \label{sec:final}
-
-	With the different estimates of \mstar{} and the \mden{} profiles in hand, we now 
-	proceed to identify a sample of massive central galaxies with the help from the 
-	\redm{} galaxy cluster catalog. 
-	The ``central'' galaxy can be roughly defined as the galaxy that live in the 
-	center of its own dark matter halo.  
-	In contrast, galaxy in a sub-halo who is orbiting within the virial radius of a 
-	more massive halo is referred to as ``satellite''. 
-	Central galaxy has its unique importance in the study of galaxy evolution and 
-	galaxy-halo coevolution.
-	Therefore, to better understand the connection between the structure of massive 
-	galaxies and the assembly history of stars and halos, we wish to focus on central 
-	galaxies in this work.
-
-\subsection{Candidates of massive central galaxies}
-    \label{ssec:redmapper}
-
-    Identification of central galaxy is not an easy task (e.g. \citealt{Yang2007}).
-    For this purpose, we first use the \redm{} catalog to help us isolate the central 
-    galaxies in massive halos and also exclude the massive satellite galaxies in these
-    haloes.  
-    Assuming the completeness of the \redm{} catalog, we treat the rest of sample as 
-    galaxies from less massive halos.  
-    Given the smaller fraction of satellite galaxies at high-\mstar{} end (e.g. 
-    \citealt{Reid2014, Hoshino2015, Saito2016}), 
-    we further assume that the massive ones (\logmtot{}$>11.4$) among them are likely 
-    to be the central galaxies of these smaller halos.
-
-    In the first step, we make use of the \texttt{v5.10} of the \redm{} cluster 
-    \footnote{See: http://risa.stanford.edu/redmapper/} 
-    (e.g.\ \citealt{Rykoff2014}; \citealt{Rozo2015b}). 
-    These authors have developed a well-tested red-sequence cluster finder that has 
-    been run on SDSS DR8 (\citealt{SDSSDR8}) photometric data. 
-    For each cluster, the catalog provides a photometric redshift ($z_{\lambda}$), a 
-    cluster richness ($\lambda$), and identifies the most likely central galaxy (the 
-    galaxy with the highest $P_{\mathrm{Cen}}$ value). 
-    The \redm{}{} catalog also provides a list of member galaxies for each cluster and 
-    their associated membership probabilities. 
-    Details about the performance of the \redm{}~cluster catalog can be found in 
-    \citet{Rozo2014}, \citet{Rozo2015a}, and \citet{Rozo2015b}.
-
-    Several studies have published calibrations between the \redm{}~richness estimate, 
-    $\lambda$, and halo mass (e.g.\ \citealt{Saro2015, Farahi2016, Simet2016, 
-    Melchior2016}). 
-    All these studies consistently find that \redm{} clusters with $\lambda > 20$ 
-    have $\log (M_{\mathrm{halo}}/M_{\odot}) \geq 14.0$. 
-    Therefore the central galaxies of these \redm{} clusters\footnote{We only use the 
-    central galaxies with $P_{\mathrm{CEN}} \geq 0.7$} form a sample of massive central 
-    galaxies that live in massive halos as described above.
-    Besides the selection of central galaxies, we are also able to link each galaxy
-    with a \mhalo{} using the \redm{} catalog. 
-    Such information is also very useful in studying the relationship between galaxy
-    structure and environment (Huang\etal in prep.).
+    a good proxy of `total' stellar mass.
+
 %% ------------------------------------------------------------------------------------ %%
@@
           for this work (black line) with the one of a much more complete sample
-          from the S82-MGC catalog (green line).  
+          from the S82-MGC catalogue (green line). 
+          The grey dashed line shows the number density function of HSC massive 
+          galaxies in the three GAMA fields for comparison.
           The associated uncertainties derived from bootstrap resampling are shown in 
           shaded regions. 
-          The vertical grey line highlight the \logms{}$=11.6$ limit.  
-          Below it, the HSC massive galaxy sample becomes significantly incomplete in 
+          The vertical grey line highlights the \logms{}$=11.6$ limit.  
+          Below the limit, the HSC massive galaxy sample becomes significantly incomplete in 
           stellar mass. 
@@
 %% ------------------------------------------------------------------------------------ %%        
-%\subsection{Massive Central Galaxies in Low and High Mass Halos}
-%    \label{ssec:mass_central}
-
-    %One of the goals of our work is to investigate the halo dependence of the outer 
-    %envelope. Although there is a correlation between $M_{\star}$ and $M_{\mathrm{Halo}}$,
-    %based on recent constraints of $M_{\star}$-$M_{\mathrm{Halo}}$ relation 
-    %(e.g.\ \citealt{Leauthaud2012}, \citealt{Behroozi2013}, \citealt{Kravtsov2014}), 
-    %even though our sample selects very massive galaxies (\logms{}$\geq 11.5$), they 
-    %With the help of the \redm{} catalog, we can broadly separate our sample into two
-    %groups with \logmh{}$<14.0$ and \logmh{}$>14.2$.
-    %live in a fairly broad range of halos masses.
-
-    % We match this sample with the central galaxies of \redm{}~catalogs using a 
-    % $1.0^{\arcsec}$ radius, and it results in 704 galaxies.  
-    %% Saved as "dr1_redbcg_hsc_sdss_gama_1arcsec.fits"
-
-    % TODO: Move this to Paper II
-    %To ensure a clean separation in \mhalo{}, here we only focus on the central 
-    %galaxies of clusters with $\lambda > 30$. 
-    %According to \citet{Simet2016}, this $\lambda \geq 30$ sample should correspond to 
-    %$M_{\mathrm{halo}}>10^{14.2} M_{\odot}$. 
-    %We have checked that none of the results in this work depend on the choice of this 
-    %$\lambda$ limit.
-
-    %The median $\lambda$ of the clusters associated with the \rbcg{} sample is 
-    %${\sim} 41$, corresponding to halo mass of 
-    %$M_{\mathrm{halo}}{\sim} 2.2\times 10^{14}$ $h^{-1}$ $M_{\odot}$.
-    %Only 44 centrals from the \rbcg{} sample live in clusters with $\lambda \geq 50$
-    %($M_{\mathrm{halo}} {\sim} 3.0\times 10^{14}$ $h^{-1} M_{\odot}$). 
-    %Our \rbcg{} sample therefore corresponds to galaxies in moderate mass halos.
-
-    After matching the \texttt{hscZ} sample with the central galaxies of \redm{} 
-    clusters with $\lambda \geq 20$ and $P_{\mathrm{0.7}} \geq 0.7$, we find 164 
-    matched galaxies at $0.3 \leq z \leq 0.5$.
-    This sample of \textbf{central galaxies in more massive halos} will be referred to 
-    as the \rbcg{} sample. 
-    Due to the depth and resolution of SDSS, the \redm{} catalog becomes slightly 
-    incomplete at lower richness ($\lambda < 40$) at $z > 0.33$, but the main results 
-    of this work are not affected by this.
-    %% Saved as "dr1_redbcg_use_sed5b.fits"
-
-    As the next step, we want to construct a sample of central galaxies living in halos 
-    with \logmh{}$<14.0$. 
-    To achieve this, we identify and remove all galaxies within a cylindrical region 
-    around all \redm{} clusters. 
-    We use a radius equal to $R_{\mathrm{200b}}$ and the thickness of the cylinder is 
-    set to twice the uncertainty of the photometric redshift error of the cluster. 
-    We convert $\lambda$ of each cluster to $M_{\mathrm{halo}}$ using the calibration 
-    of \citet{Simet2016} and we use the mass-concentration relation from 
-    \citet{Diemer2015} to compute $R_{\mathrm{200b}}$. 
-    At $0.3 < z < 0.5$, the uncertainty of photo-$z$ is between 0.015 to 0.025, and 
-    is enough to exclude cluster members.
-
-    After removing galaxies associated with \redm{} clusters, the remaining galaxies 
-    in our sample will be dominated by central galaxies living in halos with 
-    \logmh{}$< 14.0$. 
-    We will refer to this sample of \textbf{potential central galaxies in less 
-    massive halos} as the \nbcg{} sample. 
-    Since we have rejected satellites in \redm{} cluster and the satellite 
-    contamination steadily decreases with stellar mass (e.g. \citealt{Reid2014, 
-    Hoshino2015, Saito2016, vanUitert2016}), the massive galaxies in the \nbcg{} 
-    sample are very likely to be the central galaxies of their own dark matter halos.
-    %% Saved as "dr1_nonbcg_use_sed5b.fits"
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %% 
-\subsection{Summary of Sample Construction}
-    \label{ssec:sample}
-
-    Using ${\sim} 100$ deg$^2$ of HSC data, we select a large sample of massive central 
-    galaxies with reliable redshift information, and broadly separate them two 
-    categories based on $M_{\mathrm{halo}}$.
-
-    The following is a summary of our sample construction.
-
-    \begin{itemize}
-        \item \texttt{hscPho} sample: this parent sample consists of bright galaxies 
-            with $i_{\mathrm{cModel}} \leq 21.0$, good quality imaging, and reliable 
-            \texttt{cModel} photometry in all five HSC bands in the \texttt{S15B} 
-            data release. 
-        \item \texttt{hscZ} sample: we limit the \texttt{hscPho} sample to galaxies 
-            with reliable redshift information. 
-        \item With the help of the \redm{} cluster catalog, we further select 
-            candidates of massive central galaxies in a range of \mhalo{}
-            We broadly divide the sample into the central galaxies living in halos
-            with \logmh{}$\geq 14.0$ (\rbcg{}) and \logmh{}$<14.0$ (\nbcg{}). 
-    \end{itemize}
-
-    To discuss the mass-dependence of galaxy structure, we will combine the \rbcg{}
-    and \nbcg{} samples and group them into three bins of \mtot{}.  
-    In this work, we will only separately discuss the \rbcg{} and \nbcg{} samples 
-    when we look into the impact of \mstar{} definition on the SMF in Section 
-    \ref{ssec:smf}. 
-    We will carefully look into the structural differences between the central galaxies 
-    from these two samples later (Huang\etal~in prep.).  
+\subsection{Stellar mass completeness}
+    \label{ssec:complete}
+
+    With the help of the Stripe82 Massive Galaxy Catalogue (\texttt{S82-MGC},
+    \citealt{Bundy2015}
+    )\footnote{http://www.ucolick.org/\~{}kbundy/massivegalaxies/s82-mgc.html}, 
+    we investigate the \mstar{} completeness of our samples. 
+    The \texttt{S82-MGC} sample matches the deeper SDSS photometric data in the 
+    Stripe 82 region (\citealt{Annis2014}) with the near-infrared data from the United 
+    Kingdom Infrared Telescope Infrared Deep Sky Survey (UKIDSS; 
+    \citealt{Lawrence2007}), and is complete to \logms{}$\geq 11.2$ at $z<0.7$, 
+    which makes it sufficient to evaluate the completeness of our HSC sample. 
+    \citet{Leauthaud2016} uses this sample to show that the BOSS spec-$z$ sample, 
+    which is our main source of redshifts, is about 80\% complete at 
+    \logms{}$\geq 11.6$ at $0.3 < z < 0.5$.
+
+    Fig~\ref{fig:mass_complete} compares the number density distributions of 
+    galaxies from \texttt{S82-MGC} with the 20453 galaxies that are also in 
+    our sample\footnote{We do not apply any statistical corrections for completeness 
+    and hence, to avoid confusion, we do not use the term `stellar mass function';
+    errors on the distributions are estimated via bootstrap resampling.}.
+    To be consistent with the \texttt{S82-MGC} catalogue, we estimate the \mcmodel{}
+    of these galaxies using \texttt{iSEDFit}.
+    We find excellent agreement between HSC \mcmodel{} and the ones from the
+    \texttt{S82-MGC} catalogue.
+
+    We conclude that our sample of massive galaxies is reasonably complete down 
+    to \logmcmodel{}${\sim} 11.5$ at $0.3 \leq z \leq 0.5$.    
+    Given the average difference between \mtot{} and \mcmodel{}, we chose to focus on 
+    galaxies with \logmtot{}$> 11.6$. 
+    In \S~\ref{sec:discussion}, we also show results for massive galaxies 
+    with $11.4 \le$\logmtot{}$<11.6$, but we caution that our sample is incomplete 
+    in this lower mass bin mainly due to the intrinsic incompleteness of the 
+    SDSS/BOSS spec-$z$ (see \citealt{Leauthaud2016}).
+
 %% ------------------------------------------------------------------------------------ %%
@@
       \caption{
-          \textbf{Left:} Impact of using \mtot{} on the galaxy stellar mass function. 
-          Dashed lines correspond to the SMF computed using \mcmodel{} whereas solid 
-          lines correspond to the SMF computed using \mtot{}. 
-          Here we separate the HSC massive galaxies into the central galaxies living 
-          in halos more massive than \logmh{}$\sim14.2$ (red lines) and the ones in 
-          halos with \logmh{}$<14.0$ (black lines).
+          \textbf{(a)} Impact of using \mtot{} on the galaxy stellar mass function. 
+          Dashed lines correspond to the observed volume density distribution 
+          computed using \mcmodel{}, whereas solid lines correspond to the distribution
+          computed using \mtot{}. 
+          We do not apply any completeness correction to the distributions here.
+          We separate our HSC sample into centrals in haloes more massive than
+          \logmh{}$\sim14.2$ (red lines) and centrals in haloes with \logmh{}$<14.0$ 
+          (black lines).
           The impact on the SMF can exceed 0.2 dex for massive central galaxies in 
-          very massive halos.
-          \textbf{Right}: The stellar mass volume density distributions of massive 
+          very massive haloes.
+          \textbf{(b)}: The \mstar{} volume density distributions of massive 
           HSC galaxies, using both \mtot{} (black solid line) and \mmax{} (black dotted 
           line).  
-          The uncertainty of distribution using \mtot{} is shown in grey shaded 
-          region.  
-          Here, we also compare the distributions with SMF from previous works: 
-          (a): SDSS galaxies at $z{\sim} 0.1$ from \citet{Bernardi2017}; the \mstar{} 
-          is based on photometry from 2-D \ser{}$+$Exponential model fitting 
+          Vertical lines on both plots highlight the \logmtot{}$=11.6$ mass limit. 
+          The grey shaded region shows the resampling error on the HSC SMF plus an
+          additional 20\% uncertainty to account for the fact that we do not include 
+          satellite galaxies and that we fail to extract a 1-D profile for $\sim 10$\% 
+          of our galaxies. 
+          These issues will be addressed in forthcoming work (Huang\etal in prep.). 
+          We compare our results with previous studies: 
+          (1): SDSS galaxies at $z{\sim} 0.1$ from \citet{Bernardi2017} with \mstar{} 
+          values based on photometry from 2-D \ser{}$+$Exponential model fitting 
           (purple); 
-          (b): SDSS galaxies at $z{\sim} 0.1$ from \citet{Moustakas13} based on 
+          (2): SDSS galaxies at $z{\sim} 0.1$ from \citet{Moustakas13} based on 
           improved SDSS \texttt{cModel} photometry (blue); 
-          (c): \texttt{S82-MGC} galaxies at $0.15 < z< 0.43$ from 
-          \citet{Leauthaud2016} based on PSF-matched SDSS-UKIDSS photometry (green).
-          Please see text for more details of the comparison.
+          (3): \texttt{S82-MGC} galaxies at $0.15 < z< 0.43$ from 
+          \citet{Leauthaud2016} based on PSF-matched SDSS--UKIDSS photometry (green).
           }
@@
 %% ------------------------------------------------------------------------------------ %%  
+\section{The Final Sample}
+    \label{sec:final}
+
+%% ------------------------------------------------------------------------------------ %%  
+\subsection{Candidate massive central galaxies}
+    \label{ssec:redmapper}
+
+    Typically, a `central' galaxy is defined as a galaxy located in the center of 
+    its own dark matter halo, while a galaxy in a sub-halo orbiting within 
+    the virial radius of a more massive halo is referred to as a `satellite' 
+    (e.g.\citealt{Yang2007}).
+    We wish to focus on massive central galaxies here as they are essential
+    to the study of galaxy--halo connection.
+    Although the satellite fraction is expected to be very low ($<10$\%; e.g. 
+    \citealt{Reid2014, Hoshino2015, Saito2016}) at \logmtot{}$> 11.6$, we further use 
+    the \redm{} cluster catalogue (\texttt{v5.10}; e.g.\ \citealt{Rykoff2014}; 
+    \citealt{Rozo2015b}) based on SDSS DR8 (\citealt{SDSS-DR8}) to help us 
+    identify centrals of cluster-level dark matter haloes and reduce satellite
+    contamination.
+
+    After matching the \texttt{hscZ} sample with the central galaxies of \redm{} 
+    clusters with richness $\lambda \geq 20$\footnote{Due to the depth and 
+    resolution of SDSS images, the \redm{} catalogue is not complete down to 
+    $\lambda=20$ at $0.3 < z < 0.5$.  
+    At $z \geq 0.33$, it starts to miss a small fraction of clusters with 
+    $\lambda < 30$, but it does not affect the results in this work.}
+    and central probability $P_{\mathrm{Cen}} \geq 0.7$, we find 164 matched galaxies 
+    at $0.3 \leq z \leq 0.5$.
+    According to available calibration (e.g.\ \citealt{Saro2015, Farahi2016, 
+    Simet2016, Melchior2016}), they represent the central galaxies in dark matter 
+    haloes with $\log (M_{\mathrm{halo}}/M_{\odot}) \geq 14.0$; we refer to these 
+    galaxies as the \rbcg{} sample.
+
+    As the next step, we identify and remove all galaxies within a cylindrical 
+    region around each \redm{} cluster. 
+    We use a radius equal to $R_{\mathrm{200b}}$ and set the length of the cylinder 
+    to twice the value of the photometric redshift ($z_{\lambda}$) uncertainty 
+    of each cluster\footnote{We convert $\lambda$ of each cluster to 
+    $M_{\mathrm{200b}}$ using the calibration of \citet{Simet2016} and use the 
+    mass-concentration relation from \citet{Diemer2015} to compute 
+    $R_{\mathrm{200b}}$.}.
+    After we remove galaxies associated with \redm{} clusters from our sample, 
+    the remaining galaxies are dominated by central galaxies living in haloes with 
+    \logmh{}$< 14.0$; we refer to these galaxies as the \nbcg{} sample.
+    Using the model presented in \citet{Saito2016}, we estimate that in dark matter 
+    haloes with \logmh$<11.4$, $\sim 7$\% of galaxies with \logmcmodel{}$>11.5$ are 
+    satellites.
+
+    %% Saved as "dr1_redbcg_use_sed5b.fits"  
+    %% Saved as "dr1_nonbcg_use_sed5b.fits"
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
+\subsection{Summary of sample construction}
+    \label{ssec:sample}
+
+    Using ${\sim} 100$ deg$^2$ of HSC data, we select a large sample of massive central 
+    galaxies with reliable redshift information, and broadly separate them into two 
+    categories based on $M_{\mathrm{halo}}$.
+
+    The following is a summary of our sample construction.
+
+    \begin{itemize}
+
+        \item \texttt{hscPho} sample. This parent sample consists of bright galaxies 
+            with $i_{\mathrm{cModel}} \leq 21.0$, good quality imaging, and reliable 
+            \texttt{cModel} photometry in all five HSC bands in the \texttt{S15B} 
+            data release. 
+            This sample is described in \S \ref{ssec:initial}, and it contains 
+            1760845 galaxies.
+
+        \item \texttt{hscZ} sample. We limit this \texttt{hscZ} sample to galaxies 
+            with reliable redshift information.
+            This sample is described in \S \ref{ssec:initial}. 
+            It provides us 25286 useful galaxies at $0.3<z<0.5$.
+
+        \item With the help of the \redm{} cluster catalogue, we further select 
+            candidates of massive central galaxies.
+            We broadly divide the \texttt{hscZ} sample into central galaxies living 
+            in haloes with \logmh{}$\geq 14.0$ (\rbcg{}) and central galaxies from 
+            the haloes with \logmh{}$<14.0$ (\nbcg{}).
+            To ensure the sample is \mstar{}-complete and has minimal satellite 
+            contamination, we further focus on the 950 massive galaxies with 
+            \logmtot{}$>11.6$ in this work\footnote{As reference, there are 
+            2613 massive galaxies with \logmtot{}$>11.5$ in our sample.}.
+
+    \end{itemize}
+
+    The division of our sample into two halo mass bins is mainly relevant for the 
+    second paper in this series (Huang \etal in prep.).  
+    For the present paper, we consider only the halo mass dependence on our sample when 
+    we evaluate impact of mass estimates on the SMF in \S \ref{ssec:smf}. 
+    We show the distributions of redshift, \mtot{}, and \minn{} of the massive galaxy 
+    sample in Appendix \ref{app:basic}, along with its \mtot{}-$(g-r)$ rest-frame 
+    colour relation.
+
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
 \section{Results}
@@
 %% ------------------------------------------------------------------------------------ %%     
-\subsection{Impact of Missing Light on the Galaxy Stellar Mass Function}
+\subsection{Impact of missing light on the galaxy stellar mass function}
     \label{ssec:smf}
 
-    As one of the most fundamental statistics of galaxy population, the Stellar 
-    Mass Function (SMF) and its evolution are critical to our understanding of 
+    The stellar mass function (SMF) is critical to our understanding of 
     galaxy evolution.
-    In Section \ref{ssec:mtotal}, we demonstrate that different methods for estimating
-    ``total'' \mstar{} can lead to quite different results, hence have a large impact 
-    on the high mass end of the galaxy stellar mass function (e.g. 
-    \citealt{Bernardi2013, DSouza2014, DSouza2015, Bernardi2017}).
-    On average, integration of our carefully derived non-parametric \mden{} profile 
-    to 100 kpc (\mtot{}) recovers more light (hence mass) than the \texttt{cModel}
-    method. 
-    At \logmtot{} $>11.6$, the difference sometimes can be larger than 0.2 dex. 
-    More importantly, the average difference steadily increases with \mtot{}. 
-    These differences relates to the intrinsic limitation of the \texttt{cModel} 
-    method and also reflects the fact that more massive ETGs tend to have more 
-    extended stellar mass distributions (e.g. higher-\ser{} index, 
-    \citealt{Graham2003}).
-
-    Although we do not attempt to measure SMF, we use Fig \ref{fig:smf}
-    to demonstrate the impacts from missing light and different definitions of 
-    \mstar{}.
-    The left panel of Fig \ref{fig:smf} shows the SMF\footnote{There are actually
-    the volume density distributions, we refer to them as SMFs for convenience 
-    although the incompleteness and other systematics have not been corrected}
-    computed using \mcmodel{} and \mtot{} for both the \rbcg{} and \nbcg{} samples.
-
-    Generally speaking, the use of \mtot{} instead of the \mcmodel{} shifts the SMF 
-    towards the higher-mass end without significantly modifying the slope at 
-    high-mass end.
-    Interestingly, the impact of missing flux is more prominent for the \rbcg{} 
-    galaxies whose contribution to the very high-mass end is substantial. 
-    This difference between the \rbcg{} and \nbcg{} samples here may hint that 
-    the \rbcg{} galaxies suffer more from missing light. 
-    We will look into this in details in the following work (Huang\etal in prep.).
-
-    As discussed in Section~\ref{ssec:mtotal}, even with much deeper images from HSC,
-    it is non-trivial to clearly define and measure the ``total'' \mstar{} for 
-    these massive systems, and the \mden{} profiles of these galaxies often extend 
-    well beyond 100 kpc. 
-    We measure \mmax{} by integrating the \mden{} profiles out to the detection 
-    limit that is defined by the background noise.
-    Although the \mden{} profile becomes more uncertain at $>100$ kpc, \mmax{} can
-    provide us certain clue about how much extra mass is ``hidden'' there. 
-    Although the average difference we find is small even at high-mass end 
-    (${\sim}0.03$ dex), on the right panel of Fig \ref{fig:smf}, we can still its 
-    influence on the SMF at high-mass end, where the slope becomes slightly 
-    shallower.
-
-    % TODO: Move this to Paper II
-    %In this work, we have opted to in general use \mtot{} rather than \mmax{} as the 
-    %uncertainty on \mmax{} is larger. 
-    %However, we have checked that none of our results are changed by replacing \mtot{} 
-    %via \mmax{}.
-
-    On the same figure, we also compare the HSC results with the ones from following 
-    works:
+    Photometric method and definitions of \mstar{} can affect the 
+    high-\mstar{} end of SMF (e.g. \citealt{Bernardi2013, dSouza2015, Bernardi2017}). 
+    The cited works show that, despite being widely adopted in the literature, 
+    \cmodel{} photometry can significantly underestimate the \mstar{} of massive 
+    galaxies. 
+    Still, these works are based on more complex 2-D modelling or stacking of 
+    shallow images that suffer from various systematics.
+    Now, we characterize the impacts of different photometric measurements on the 
+    high-\mstar{} end of the SMF using \mstar{} directly measured out to large 
+    radius on deep images (see Fig~\ref{fig:smf}).
+
+    The left panel of Fig~\ref{fig:smf} show the volume density distributions 
+    (referred to as SMF for simplicity) of massive galaxies using \mcmodel{} 
+    and \mtot{} for both the \rbcg{} and \nbcg{} samples.  
+    As shown in Fig~\ref{fig:mass_diff}, the mass-dependent differences between these
+    two measurements lead to noticeable differences in SMF at high-\mstar{} end.
+    \cmodel{} photometry leads to underestimation of volume density at the 
+    high-\mstar{} end of SMF. 
+    More importantly, it shows that the impact of missing \mstar{} becomes more 
+    significant for central galaxies in very massive haloes. 
+    We demonstrate that this occurs because galaxies in more massive haloes 
+    have more extended stellar envelopes than those in lower mass haloes at fixed 
+    \mtot{} in Huang\etal (in prep.).
+    On the right panel of Fig~\ref{fig:smf}, we also compare the SMFs using \mtot{} 
+    and \mmax{}. 
+    As mentioned in \S~\ref{ssec:mtotal}, \mtot{} is still a lower limit of the total 
+    \mstar{} of these massive galaxies, and \mmax{} helps us check how much \mstar{} 
+    could be left out.  
+    Although there is still visible difference at the high-\mstar{} end, the impact
+    of going from \mtot{} to \mmax{} is relatively small. 
+    It suggests that \mtot{} captures the majority of the total \mstar{}.
+    Here we do not attempt to apply any completeness correction, so the SMFs turn 
+    over at the low-\mstar{} end. 
+    For now, we add a constant ${\sim}20$\% uncertainty to the SMF to account for 
+    the satellite galaxies and the galaxies for which we fail to extract 1-D profiles 
+    (see Appendix~\ref{app:ellipse}), although these uncertainties should be smaller 
+    at high-\mstar{} end.
+
+    On the right panel of Fig~\ref{fig:smf}, we also compare our SMFs with the 
+    following works:
 
@@
 
-        \item The SMF for $0.15 < z < 0.30$ galaxies from the \texttt{S82-MGC} sample
-            \citep{Leauthaud2016} where the \mstar{} is derived using 
-            \texttt{iSEDfit} on PSF-corrected aperture photometry from 
-            \texttt{S82}.
-            The stellar population model and star-formation history assumptions are 
-            very similar to the ones in this work, except that it uses the 
-            \texttt{BC03} model. 
-            Based on the test results from Appendix \ref{app:sed}, we simply shifts 
-            the SMF to higher \mstar{} by 0.08 dex.
-
-        \item The SMF derived from a SDSS-\textit{GALEX} sample of $z{\sim} 0.1$ 
-            galaxies from \citet{Moustakas13}. 
-            Here, the total luminosity is based on the SDSS \cmodel{} magnitude. 
-            The \m2l{} is derived via SED fitting using \texttt{iSEDfit} with similar 
-            assumptions as in our work.
-
-        \item The observed SMF for $z{\sim} 0.1$ SDSS galaxies from 
-            \citet{Bernardi2017}. 
-            The total luminosity is based on 2-D \texttt{SerExp} models 
-            (\ser{}$+$ Exponential disk model; integrated to infinity) that 
-            recovers much more flux compared to SDSS \cmodel{} magnitudes 
-            (\citealt{Bernardi2013, Meert2015}). 
-            The \m2l{} is adopted from the SED fitting results from the ``dusty'' 
-            model in \citet{Mendel2014} which share similar assumptions of stellar 
-            population models with this work.
+        \item The SMF of $0.15 < z < 0.30$ galaxies from the \texttt{S82-MGC} sample
+            \citep{Leauthaud2016}, where \mstar{} is based on PSF-matched aperture
+            photometry and \texttt{iSEDfit} fitting using \texttt{BC03} model.
+            We account for the 0.08 dex average difference with the \texttt{FSPS} 
+            ones seen in the Appendix~\ref{app:sed}
+
+        \item The SMF for the SDSS-\textit{GALEX} sample at $z{\sim} 0.1$ using 
+            SDSS \cmodel{} photometry and \texttt{iSEDfit} stellar mass based on 
+            similar assumptions (see \citet{Moustakas13} for details).
+
+        \item The SMF for $z{\sim} 0.1$ SDSS galaxies using 2-D \texttt{SerExp} 
+            models\footnote{\ser{}$+$ Exponential disc model that can recover more 
+            lights than SDSS \cmodel{}; integrated to infinity.}
+            (\citealt{Bernardi2013, Meert2015}) and stellar mass by 
+            \citet{Mendel2014}\footnote{We use \texttt{FSPS} model, 
+            \citet{Chabrier2003} IMF, and \citet{Calzetti2000} extinction law}.
+            (see \citet{Bernardi2017} for details).
 
@@
 
-    To appropriately compare SMFs from different works, one needs to carefully 
-    separate the differences in the measurements of luminosity and \m2l{}, and 
-    takes the uncertainties of \mstar{} measurements into account\footnote{
-    Fixed uncertainty of \logms{} can lead to increasingly over-estimated 
-    volume density with \mstar{} due to the very steep slope of SMF at high-mass end.} 
-    (\citealt{Bernardi2010, Bernardi2017}), which is beyond the scope of this work.  
-    Here, we primarily want to visualize the importance of \mstar{} measurements 
-    to the SMF at high-mass end. 
-    All SMFs share similar volume density around \logms{}${\sim}11.0$, but the ones
-    that are based on \texttt{cModel} and small aperture photometry show much 
-    steeper slopes than the HSC \mtot{} one. 
-    The SMF based on single-\ser{} model seems to face the same issue. 
-    We also compare with the $z{\sim}0.1$ SMF from the GAMA survey 
-    (\citealt{Wright2017}) whose luminosity is scaled with the single-\ser{} model
-    from \citet{Kelvin2012}, and its high-mass end behavior is very similar to 
-    the \citet{Leauthaud2016} and the \citet{Moustakas13} ones. 
-    And, once the \m2l{} measurements based on similar assumptions are adopted, 
-    the SDSS SMF using the \texttt{SerExp} models from \citet{Bernardi2017} becomes 
-    surprisingly similar to the HSC \mtot{} one that is not model dependent.
-    Both SMFs highlight the importance of ``missing light'' from different angles. 
-    Right now, the \citet{Bernardi2017} sample and our HSC one have almost no 
-    galaxy in common due to the differences in redshift range, hence it is not 
-    clear whether the \texttt{SerExp} model can indeed describe the flux 
-    distributions of these massive galaxies out to $>100$ kpc. 
-    It would be interesting to look into the application of multi-component 
-    2-D models using HSC images.
-
-    In summary, the result highlights that the SMF at high-mass end is sensitive to 
-    even moderate change of \mstar{}, and illustrates the advantages of deep HSC image
-    and careful 1-D approach in estimating total \mstar{} of massive galaxies.
-    For studies about the SMF or other aspects of galaxy evolution based on 
-    shallow image or simplified model, these effects can not be neglected.
-    Although we only discuss the high-mass end, this \mstar{} range is crucial for 
-    tracing the evolution of massive galaxies and calibrating numerical simulation 
-    and semi-analytic model as it is very sensitive to the AGN-feedback recipe.   
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %%
-\subsection{Surface Mass Density Profiles}
+    Due to several systematics (see e.g. \citealt{Bernardi2013, Bernardi2017}), we 
+    \emph{do not} attempt to perform detailed comparisons among these SMFs.
+    We are currently working to address these issues in Huang \etal (in prep.). 
+    Here we simply note that the HSC \mtot{} SMF is closer to the one 
+    derived by \citet{Bernardi2017} using SDSS data at $z{\sim}0.1$ and the 
+    \texttt{SerExp} model.
+    Meanwhile, the differences between the HSC \mtot{} SMF with the others are 
+    likely caused by the photometric methods: SDSS \cmodel{} and small-aperture 
+    photometry underestimate \mstar{} of massive galaxies.  
+    Even before a more in-depth study, it already illustrates an important issue:
+    \textbf{It is crucial to understand the impacts from photometric data and 
+    methods on the estimates of SMF} before using HSC \mtot{} SMF to study 
+    galaxy evolution or 
+    comparing it with predictions from models and simulation. 
+    This is particularly relevant since a method like \cmodel{} will still be 
+    widely adopted in on-going and future imaging surveys.
+
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %%
+\subsection{Surface mass density profiles}
     \label{ssec:sbp_compare}
@@
           \textbf{Left}: Median \mden{} profiles in three total stellar mass bins. 
-              Thin grey lines show a random subset of individual profiles. 
-              The shaded region highlights the region that could be affected by the PSF. 
+              Thin grey lines in the background show a random subset of individual
+              profiles. 
+              The scatter between the thin grey lines reflects the true scatter in 
+              the profiles of massive galaxies (not measurement error). 
+              The shaded region highlights the region that is most strongly affected 
+              by the seeing. 
               Two vertical lines indicate 10 kpc (thin, dotted line) and
-              100 kpc (thick, dash line). ~~~ 
+              100 kpc (thick, dashed line). ~~~ 
           \textbf{Right}: comparison between our \mden{} profiles, previous observations, 
@@
 %% ------------------------------------------------------------------------------------ %%
-\subsubsection{General Trends and Comparison with Previous Work}
+\subsubsection{General trends and comparison with previous work}
     \label{sssec:sbp_inter}
 
-    Previous discussions about the structural evolution of massive galaxies or the 
-    environmental dependence of their structures often focus on scaling relations,  
-    like the ``\mstar{}-size'' relation. 
-    In this work, we argue that, compared to these scaling relations, the \mden{} 
-    profiles that we have derived capture the full structural information of these 
-    massive galaxies.
-    By studying these \mden{} profiles directly, we can by-pass difficult questions 
-    about how to accurately define and measure the ``sizes'' and ``masses'' of these 
-    massive galaxies.
-
-    Fig~\ref{fig:avg_prof} shows the median \mden{} profiles\footnote{The median 
-    profiles along with their uncertainties are derived using bootstrap resampling 
-    method} of massive central galaxies at $0.3 < z < 0.5$ in three \mtot{} 
-    bins\footnote{The sample is clearly not complete in the lowest \mtot{} bin, 
-    but its median \mden{} profile is still useful to show the overall trend and to 
-    compare with previous work}. 
-    As shown in the left panel of Fig~\ref{fig:avg_prof}, we can comfortably trace
+    Previous work on the structural evolution of massive galaxies has often focused on 
+    scaling relations such as the `\mstar{}-size' relation.  
+    We argue that by comparing \mden{} profiles directly, we can capture more 
+    information than afforded by the \mstar{}-size relation. T
+    he comparison also has the advantage that it bypasses difficult questions about 
+    how to accurately define and measure galaxy `sizes' and `masses'.
+
+    Fig.~\ref{fig:avg_prof} shows the median \mden{} profiles of massive central 
+    galaxies at $0.3 < z < 0.5$ in three \mtot{} bins.
+    These median profiles along with their uncertainties are derived using the 
+    bootstrap resampling method. 
+    Note that our sample is not complete in the lowest \mtot{} bin, although the 
+    median \mden{} profile may not be significantly affected. 
+    As shown in the left panel of Fig~\ref{fig:avg_prof}, we can confidently trace
     the \mden{} profiles of these massive galaxies out to 100 kpc 
     \textbf{individually}.  
-    These median \mden{} profiles have moderate differences in the inner region. 
-    Within inner 10 kpc, the median \mden{} profile of more massive galaxies 
-    shows slightly higher \mden{} value but similar slope. 
-    These massive galaxies ($\ge 10^{11.4} M_{\odot}$) are known to have quite 
-    uniform properties in the inner region. 
-    At these masses, most of them should be ``slow-rotating'' 
-    (e.g.\ \citealt{Cappellari13b})``core''--elliptical galaxies 
-    (e.g.\ \citealt{Lauer07}) that have ``boxy'' inner isophotal shapes and similar 
-    slopes of the inner surface brightness profiles (e.g.\ \citealt{Kormendy2009,
-    Schombert2015}).
-
-    Meanwhile, in the outskirts, we can notice significant differences where more 
-    massive galaxies have gradually more flattened \mden{} profiles and show more 
-    prominent stellar halos.
-    It is also interesting to see that the distributions of \mden{} profiles show 
-    considerably large scatter at large radius. 
-    Given the \s2n{} of the HSC image at these surface brightness levels, these 
-    scatters should reflect the \textbf{intrinsic scatter of the structures of 
-    massive galaxies in their stellar halos}.
-    Overall, the structures of massive galaxies are \textbf{clearly not 
-    self-similar} out to 100 kpc. 
-    Some of our \mden{} profiles show signs of unphysical truncation and fluctuation 
-    related to inaccurate sky subtraction. 
+    At large scales, some of our \mden{} profiles show signs of unphysical truncation 
+    and fluctuation related to inaccurate sky subtraction. 
     In this paper, we do not use profiles beyond 100 kpc, even though the median 
-    \mden{} profiles for the two most massive bins behave reasonably out to 
+    \mden{} profiles for the two most massive bins behave reasonably well out to 
     ${\sim} 200$ kpc.
 
-    The right panel of Fig~\ref{fig:avg_prof} compares our results with several 
-    previous works. 
-    So far, deep \mden{} profiles of massive galaxies are rarely available. 
-    Even in the nearby universe, it is still not easy to reach to the very outskirt
-    of massive galaxy due to technical difficulties (e.g. 
-    \citealt{Capaccioli2015, Iodice2016, Iodice2017, Spavone2017, Mihos2017})
-    The small volume of local universe also limits the number of available 
-    galaxies at high-mass end.
-    Most previous studies often focus more on the surface brightness profiles, 
-    and they also depend on stacking techniques or model-dependent method to 
-    study the structure of massive galaxies in their outskirts (e.g. 
-    \citealt{Tal2011, DSouza2015}), both of which suffer from several systematic 
-    issues.
-
+    From Fig~\ref{fig:avg_prof} we can see the galaxies in our sample have 
+    homogeneous profiles on small radial scales. 
+    The amplitude of \mden{} increases with galaxy mass on 10 kpc scales but the 
+    slope of \mden{} remains similar.  
+    From previous work on this topic, we already know that the inner regions of 
+    massive elliptical galaxies display relatively uniform structural (e.g.
+    \mden{} profile, isophotal shape: e.g. \citealt{Lauer07, Kormendy2009, 
+    Schombert2015}; and kinematic: e.g. \citealt{Cappellari13b}) properties.  
+    However, Fig~\ref{fig:avg_prof} reveals a significant diversity in the outer 
+    envelopes of massive galaxies.  
+    Given the \s2n{} of HSC images at these surface brightness levels, the scatter 
+    shown in Fig~\ref{fig:avg_prof} corresponds to \textbf{intrinsic scatter in 
+    the stellar envelopes of massive galaxies}. 
+    Importantly, Fig~\ref{fig:avg_prof} shows that the global \mden{} profiles 
+    of galaxies at these masses are \textbf{clearly not self-similar} out to 100 
+    kpc and have outskirts with larger scatter.
+
+    In the right-hand side of Fig.~\ref{fig:avg_prof}, we compare our \mden{} 
+    profiles with results from previous work. 
+    Most previous studies have focused on surface brightness profiles instead 
+    of mass density profiles.  
+    Results can also depend on the stacking technique or the model used to extract 
+    the profile (e.g., \citealt{Tal2011, DSouza2014}). 
     \citet{Huang2013a} derived \mden{} profiles for a small sample of very nearby 
-    ellipticals (within 100 Mpc; median \logms{} ${\sim} 11.3$ based on shallower 
-    images) from the Carnegie-Irvine Galaxy Survey (CGS, \citealt{CGS1}). 
-    Because this is a very low redshift sample, these profiles are accurate to 
-    smaller scales, $r=1$ kpc. 
-    The \citet{Huang2013a} \mden{} profiles show good agreement with ours in the 
-    region of overlap and out to 50 kpc although their \m2l{} are derived in 
-    slightly different ways.
-    CGS images are deeper than SDSS images in the $r$-band, but the median 
-    profile from \citet{Huang2013a} still only reaches ${\sim} 50$ kpc for $z{\sim} 0$ 
-    massive galaxies.
-    Meanwhile, our deep HSC images can reliably deliver individual \mden{} profiles 
-    for $z{\sim} 0.4$ galaxies out to at least 100 kpc.
-
-    \citet{Patel2013} extracted a median \mden{} profile of massive ETGs at 
+    ellipticals (within 100 Mpc; median \logms{} ${\sim} 11.3$) based on relatively 
+    shallow images from the Carnegie--Irvine Galaxy Survey 
+    (CGS, \citealt{CGS1})\footnote{https://cgs.obs.carnegiescience.edu/CGS/Home.html}.  
+    This sample is at very low redshift ($z<0.02$), and so the \mden{} profiles from 
+    \citet{Huang2013a} galaxies are accurate to smaller scales (down to $r=1$ kpc) 
+    than our HSC profiles.  
+    Our \mden{} profiles show good agreement with the \citet{Huang2013a} sample in 
+    the radial range of overlap (out to 50 kpc). 
+    The median profiles from \citet{Huang2013a} only reach to ${\sim} 50$ kpc for 
+    $z<0.02$ massive galaxies, while our deep HSC images can reliably deliver 
+    individual \mden{} profiles for $z{\sim} 0.4$ galaxies out to at least 100 kpc.
+
+    \citet{Patel2013} extracted a median \mden{} profile for massive ETGs at 
     $0.25 < z < 0.50$ using stacked \textit{HST}/ACS images. 
@@
     The median \mstar{} of the \citet{Patel2013} sample is 
-    ${\sim} 10^{11.2} M_{\odot}$ which is lower than our lowest mass bin. 
-    However, \citet{Patel2013} use the BC03 SSP model which are roughly 0.1 dex 
-    lower than our FSPS masses (Appendix~\ref{app:sed}). 
-    Furthermore, the \citet{Patel2013} images are shallower than ours meaning 
-    that there masses will be lower than ours because of missing light in the 
+    ${\sim} 10^{11.2} M_{\odot}$, which is lower than our lowest mass bin. 
+    However, \citet{Patel2013} uses the BC03 stellar population model, which leads to 
+    \mstar{} that are roughly 0.1 dex lower than our FSPS estimates 
+    (see Appendix~\ref{app:sed}). 
+    Furthermore, the \citet{Patel2013} images are shallower than ours which means 
+    that their \mstar{} could still be underestimated due to missing light in the 
     outskirts. 
     Given these two considerations, it is reasonable to roughly compare the 
-    \citet{Patel2013} profile with the one in our lowest stellar mass bin. 
-    The superb resolution of the \textit{HST}/ACS image means that the profile in
-    \citet{Patel2013} is unaffected by the seeing even down to 1 kpc. 
-    The good agreement between our profile and the one derived from HST image 
-    shows that our profiles are robust at $r > 3$ kpc and that we can accurately 
-    measure \minn{}.
-
-    Finally, we also compare with the predicted median \mden{} profile of central 
-    galaxies in massive halos ($13.5 < \log M_{200,c} < 14.0$) from cosmological 
-    simulation where the \mden{} profiles of galaxies are calculated using the 
-    particle-tagging technique (e.g. \citealt{Cooper2010}). 
-    The simulated \mden{} profile is also affected by limited resolution in the 
-    center, but it is already quite similar to the median \mden{} profile for 
-    the $11.6 <$ \logmtot{} $< 11.8$ bin within 40 kpc. 
-    However, outside 40 kpc, the particle tagging method seems to predict a too 
-    prominent stellar halo that has much shallower slope compared to our data.
-
-    Although the particle tagging method is not considered the best way to simulate
-    the stellar mass distributions of massive galaxies, this comparison can already 
-    demonstrate the advantages of our \mden{} profiles. 
-    Such comparisons between our HSC data and predictions from more advanced 
-    hydrodynamic simulations will help fine-tune simulations and also investigate 
-    the physical mechanisms that drive the assembly of massive galaxies and the 
-    build up of stellar halos.
+    \citet{Patel2013} profile with the one in our lowest \mtot{} bin. 
+    The superb resolution of the \textit{HST}/ACS images allows \citet{Patel2013} to 
+    accurately measure the \mden{} profile down to 1 kpc without worrying about the
+    smearing effect of seeing. 
+    The good agreement between our profiles and the ones derived from \textit{HST} 
+    imaging demonstrates that our profiles are robust at $r\geq 3$ kpc; therefore, 
+    we can accurately measure \minn{}.
+
+    Finally, we also compare our HSC profiles with the predicted median \mden{} 
+    profile of central galaxies in massive haloes ($13.5 < \log M_{200,c} < 14.0$) 
+    from a cosmological simulation where the \mden{} profiles of galaxies are 
+    calculated using the particle tagging technique (e.g., \citealt{Cooper2010}). 
+    The simulated \mden{} profile is affected by the resolution limit of the 
+    simulation in the inner region but is in good agreement with our median 
+    \mden{} profile for the $11.6 <$ \logmtot{} $< 11.8$ bin within 40 kpc. 
+    However, when compared to our data for the $11.6 <$ \logmtot{} $< 11.8$ bin 
+    outside 40 kpc, the particle tagging method seems to predict an overly  
+    prominent stellar halo that has a much shallower outer slope.
 
     Table~1 provides tabulated values for the median profiles that are 
-    displayed in Fig~\ref{fig:avg_prof}. 
+    displayed in Fig.~\ref{fig:avg_prof}. 
     These profiles are also available  
-    \href{https://github.com/dr-guangtou/hsc_redbcg/tree/master/profiles}{here}:
-    {\url{https://github.com/dr_guangtou/hsc_redbcg/tree/master/profiles/}}.
-
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %% 
-\subsection{Ellipticity and Color Profiles}
+    \href{http://www.ucolick.org/\~kbundy/massivegalaxies}{here}:
+    {\url{http://www.ucolick.org/\~kbundy/massivegalaxies}}. 
+    (The files will be made available after the paper is accepted)
+
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
+\subsection{Ellipticity and colour profiles}
     \label{ssec:ell_color}
@@
       \caption{
-          Radial variations in ellipticity and optical colors for massive galaxies. 
-          The format of this figure is similar to Fig~\ref{fig:avg_prof}. 
-          \textbf{Left panel} shows the ellipticity profiles, 
-          \textbf{Upper-right panel} shows the $g-r$ color profiles, and 
-          \textbf{Lower-right panel} is for $g-i$ color profiles. 
+          Radial profiles of the ellipticty and $k$-corrected rest-frame optical colours 
+          of massive galaxies in our sample. 
+          The general format of this figure is similar to Fig~\ref{fig:avg_prof}.  
+          The \textbf{left panel} displays ellipticity profiles, 
+          the \textbf{Upper-right panel} shows $g-r$ colour profiles, and  the
+          \textbf{lower-right panel} is for $g-i$ colour profiles. 
           We compare our results with those from (1) \citet{Tal2011} based on stacking 
           large samples of luminous red galaxies in SDSS at $z{\sim} 0.4$ 
-          (solid red line on left panel), 
+          (solid red line on the left panel), 
           (2) the results from a stacking analysis of nearby massive 
@@
           \citet[][blue dash lines on the left and upper-right panels]{DSouza2014}, 
-          (3) and the average $g-r$ and $g-i$ color profiles 
+          (3) and the average $g-r$ and $g-i$ colour profiles 
           from a large sample of nearby elliptical galaxies in \citet[][blue, solid 
           lines on both right panels]{LaBarbera2010}.
-          For color profiles, we also compare with deep observations of a few nearby 
-          massive ETGs: the $g-r$ color profiles of NGC 4472 (\citealt{Mihos2013}) 
+          For colour profiles, we also compare with deep observations of a few nearby 
+          massive ETGs: the $g-r$ colour profiles of NGC 4472 (\citealt{Mihos2013}) 
           and NGC 4365 (\citealt{Mihos2017}), and the $g-i$ profile of NGC 1399 
-          (\citealt{Iodice2016})
+          (\citealt{Iodice2016}).
           }
@@
 %% ------------------------------------------------------------------------------------ %%
-	Aforementioned results only use the 1-D \mden{} profiles that are baed on single 
-	band image and the flux-weighted isophotal shape, while more useful information 
-	can be gathered from the HSC images of these massive galaxies.
-	The ellipticity and $k$-corrected optical color profiles are particularly 
-	interesting.
-	We extract ellipticity profile using \texttt{Ellipse} by setting the shape of each 
-	isophote free. 
-	And by applying the $i$-band isophotes to images of other bands in the 
-	forced-photometry way, we can also measure the color profiles too. 
-	We apply Galactic extinction correction and \texttt{iSEDFit} $k$-correction to 
-	both the $g-r$ and $g-i$ color profiles.
-	The PSF smearing effect will make the central isophotal shape rounder than the 
-	real value, while the seeing differences between filters will bias the central 
-	color\footnote{Since the HSC $i$-band always has better seeing, the central color 
-	will become redder when the seeing effect is not corrected.}. 
-	At the same time, it is more difficult to extract reliable ellipticity and 
-	color profiles out to 100 kpc: at low surface brightness region, isophotal shape 
-	becomes unstable and easily affected by any contamination; the color profile in
-	the outskirt also becomes very sensitive to background level and noise level in 
-	either band. 
-	In this work, we will focus on the median ellipticity and color profiles between 
-	8--60 kpc where we can safely ignore the above issues.
-
-	The ellipticity of the isophote contains information about the 3-D geometry 
-	(e.g. \citealt{Chang2013, Mitsuda2017}) and kinematic (e.g. 
-	\citealt{Cappellari2012, Weijmans2014}) of stars in massive galaxies.  
-	The left panel of Fig \ref{fig:ell_color} shows the ellipticity profiles of HSC 
-	massive galaxies and highlight the median profiles for the same three \mtot{} 
-	bins used in Fig \ref{fig:avg_prof}. 
-	In general, the ellipticity of massive galaxy slowly increases with radius.
-	One can even notice this trend by directly comparing the shape of galaxy between 
-	SDSS and HSC images (e.g. Fig \ref{fig:sdss_compare}).  
-	More interestingly, the ellipticity profiles clear depend on \mtot{}: 
-	at ${\sim} 10$ kpc, median ellipticities from all three bins are low and similar 
-	($< 0.2$); but more massive galaxies become increasingly more elongated in their
-	stellar halo. 	
-	For the \logms{}$>11.8$ galaxy, its median ellipticity profile becomes steeper 
-	at $>10$ kpc, and the ellipticity steadily increases from $e\le 0.2$ to 
-	$e{\sim} 0.4$ at 50-60 kpc.
-	This is consistent with studies of nearby massive galaxies, both from 1-D 
-	ellipticity profiles and 2-D modeling results \citep{Gonzalez2005, 
-	Huang2013a, Spavone2017}.
-	Although this phenomenon was well-documented, clear evidence of mass-dependent
-	ellipticity profiles and the potentially anti-correlated slopes of \mden{} and 
-	ellipticity profiles has not been identified.
-	If accreted stars dominate the stellar halos of massive galaxies, this 
-	mass-dependent ellipticity profile may lead us to some insights about the 
-	differences in their assembly history (e.g. average time since last merger, 
-	average merger mass ratio).
-	Previous simulations often focused on reproducing the rounder average shape 
-	and slow-rotating nature of massive ETGs (e.g. \citealt{Wu2014}), the projected 
-	ellipticity profiles and their correlations with the kinematic of stars and 
-	merging history have not been well explored. 
-	We also compare our ellipticity profiles with previous ones that are based on 
-	image stacking techniques (the PSF-removed $i$-band from \citealt{Tal2011}, 
-	the concentration galaxies with $11.0<$\logms{}$<11.4$ from 
-	\citealt{DSouza2015}), 
-	We notice that the stacked image sometimes fails to recover the ellipticity 
-	profile, probably due to the uncertainties in aligning galaxies before the 
-	stacking process.
-
-    As for the color profiles, it is well known that massive elliptical galaxies 
-    have shallow and negative color gradient that reflects radial variation of 
-    stellar population (e.g.\ \citealt{Carollo1993, LaBarbera2012}) and contains 
-    information about the assembly history of stellar halos (e.g. 
-    \citealt{Hirschmann2015}). 
-    The right panels of Fig \ref{fig:ell_color} show the $k$-corrected $g-r$ and 
-    $g-i$ color profiles and the median profiles in three \mtot{} bins. 
-    As expected, all median color profiles show smooth and shallow negative 
-    gradients, but we do not find evidence for mass-dependence here. 
-    We also compare our results with the stacked color profiles from  
-    \citealt{LaBarbera2010}\footnote{Use the median color profiles of high-mass 
-    ETGs; the original profile is in unit of $R_{\mathrm{e}}$, we use a typical 
-    $R_{\mathrm{e}}=8.0$ kpc to convert it into kpc unit.} and 
+
+    Now we look into the ellipticity profile derived by \texttt{Ellipse} in $i$-band 
+    and the $g-r$ and $g-i$ colour profiles (galactic extinction and $k$-corrected). 
+	The smearing effect of seeing makes the central isophotal shape rounder than the 
+	real value, while seeing differences between filters bias the central 
+	colour\footnote{Since the HSC $i$-band always has better seeing, the central 
+	colour becomes redder if seeing effects are not accounted for}. 
+	On large scales, it is more difficult to extract reliable ellipticity and 
+	colour profiles out to 100 kpc because at low surface brightness levels, the 
+	isophotal shape becomes unstable and is easily affected by contamination. 
+	Colour profiles are also more difficult to extract out to large radial scales
+	because getting the colour accurately depends on the background subtraction and 
+	the noise levels in both bands. 
+	In this paper, we focus on the median ellipticity and colour profiles between 
+	8 and 60 kpc, where we can safely ignore the issues described above.
+
+	The left panel of Fig \ref{fig:ell_color} shows the ellipticity profiles of 
+	massive galaxies and highlights the median profiles for the same three \mtot{} 
+	bins shown in Fig \ref{fig:avg_prof}.  
+	Our results are also compared with previous work based on image stacking 
+	techniques (the PSF-removed $i$-band results from \citealt{Tal2011}, and
+    concentrated galaxies with $11.0<$\logms{}$<11.4$ from \citealt{dSouza2015}).
+	As expected, ellipticity profiles from image stacking methods yield results that 
+	are more shallow than ellipticity profiles measured on a galaxy-by-galaxy basis.     
+	Uncertainties in how to align galaxies and the intrinsic isophotal twist can 
+	lead to this effect.
+
+	In general, we find that the ellipticities of massive galaxies slowly increase 
+	with radius. 
+	This trend can even be seen directly "by eye" in HSC images (e.g. 
+	Fig \ref{fig:sdss_compare}). 
+	More interestingly, the ellipticity profiles vary with \mtot{}: 
+	at ${\sim} 10$ kpc, the median ellipticity ($< 0.2$) is similar for all three 
+	redshift bins, but the ellipticity of the outer stellar halo increases with 
+	\mtot{}. 
+	Galaxies with \logmtot{}$>11.8$ have median ellipticity profiles that become 
+	steeper at $>10$ kpc. 
+	The ellipticity of the outer profile steadily increases from 
+	$e\le 0.2$ to $e{\sim} 0.4$ at 50-60 kpc.
+
+	This is consistent with studies of nearby massive galaxies using different
+	methods (e.g. \citep{Porter1991, Gonzalez2005, Zibetti2005, Huang2013a, Oh2017}). 
+	For instance, \citet{Spavone2017} uses very deep images of 6 nearby massive 
+	galaxies to show that their average ellipticity in $g$-band also increases with 
+	radius in a similar fashion.
+	However, to the best of our knowledge, our HSC results are the first to show 
+	clear evidence that:  
+	(1) the ellipticity of stellar halo in massive ETGs depends strongly on 
+	\mtot{}, and 
+	(2) the ellipticity of stellar halo also relates to the slope of the \mden{}
+	profile [see Fig~\ref{fig:avg_prof} and Fig~\ref{fig:ell_color}; 
+	we will discuss this more in Huang\etal (in prep.)]. 
+	As mentioned in \S~\ref{sec:intro}, such a mass-dependent ellipticity profile
+	could reveal more insights about the assembly of stellar haloes of massive
+	galaxies.
+
+    Regarding the colour profiles, the right panels of Fig \ref{fig:ell_color} show 
+    the $k$-corrected $(g-r)$ and $(g-i)$ colour profiles for all galaxies in our 
+    sample, together with the median profiles in three \mtot{} bins. 
+    We find that the median rest-frame $(g-r)$ and $(g-i)$ colour profiles present 
+    smooth and shallow negative colour gradients out to 50--60 kpc, as observed by 
+    many previous works (e.g. \citealt{Carollo1993, LaBarbera2012}) and predicted 
+    by some simulations (e.g. \citealt{Hirschmann2015}). 
+    Meanwhile, there does not appear to be a significant \mstar{} dependence 
+    in the gradient of rest-frame optical colours.
+
+    We also compare our results with the stacked colour profiles from  
+    \citealt{LaBarbera2010}\footnote{We use the median colour profiles of high-mass 
+    ETGs; the original profile is in units of $R_{\mathrm{e}}$, and we use a typical 
+    $R_{\mathrm{e}}=8.0$ kpc to convert it into physical kpc.} and 
     \citealt{DSouza2014}.
-    The median color profiles from HSC images are systematically steeper than the 
+    The median colour profiles from HSC images are systematically steeper than the 
     stacked SDSS ones. 
-    Considering the differences in response curves of HSC and SDSS filters, and 
-    the uncertainties of color measurements, the HSC $g-r$ color profiles are 
-    consistent with those based on SDSS images. 
-    For the $g-i$ profiles, the HSC ones still show steeper gradients. 
-    The SDSS $i$-band suffers from the so-called ``red-halo'' effect of 
-    (e.g. \citealt{Wu2005}, \citealt{Tal2011}) that could lead to redder color in 
-    the low surface brightness outskirt of galaxy.
-    HSC $i$-band image do not suffer from this effect (thanks to thick CCDs), 
-    therefore can help provide more accurate color estimates.
-    For the ones from \citet{LaBarbera2010}, uncertainty of $R_{\mathrm{e}}$ 
-    measurements could also ``smooth'' the color gradients.
-    The relative steeper color profiles have been observed in very nearby massive 
-    ETGs individually.  
-    On Fig \ref{fig:ell_color}, we also compare with the $g-r$ color profiles of 
-    NGC 4472 (\citealt{Mihos2013}) and NGC 4365 (\citealt{Mihos2017})\footnote{
-    Both are converted from $B-V$ colors}, and the $g-i$ profile of NGC 1399 
+    Considering differences in the response curves between HSC and SDSS filters, 
+    together with the uncertainties of colour measurements, the HSC $(g-r)$ colour 
+    profiles are in fairly good agreement with those from SDSS. 
+    However, the $(g-i)$ profiles of HSC galaxies are steeper compared to SDSS. 
+    The SDSS $i$-band suffers from the so-called `red-halo' effect
+    (e.g. \citealt{Wu2005}, \citealt{Tal2011}).  
+    This is likely due to the fact that the SDSS $i$-band PSF has a more prominent 
+    wing than other bands. 
+    Because the PSF model does not capture these wings, more flux is artificially 
+    distributed to the outskirts, which leads to seemingly redder colours in the low 
+    surface brightness outskirts of galaxies. 
+    Because HSC uses thick CCDs, HSC $i$-band images do not suffer from this effect 
+    and can be used to determine galaxy colours with higher accuracy. 
+    Fairly steep colour profiles have been observed in several very nearby massive 
+    ETGs.  
+    Fig \ref{fig:ell_color} shows the $g-r$ colour profiles of NGC 4472 
+    (\citealt{Mihos2013}) and NGC 4365 (\citealt{Mihos2017})\footnote{
+    Both are converted from ($B-V$) colours.}, and the $g-i$ profile of NGC 1399 
     (\citealt{Iodice2016}). 
-    These individual profiles show similar color gradients with the HSC median ones.
+    These individual profiles display colour gradients similar to our HSC sample.
+
+    It is worth mentioning that the individual colour profiles still show large 
+    scatter and unphysical trends in the outskirt.  
+    The colour profile in the low--surface brightness region is very sensitive to 
+    the noise level, contamination of other objects, and uncertainties in background 
+    subtraction. 
+    The HSC $g$-band images are relatively shallower and the backgrounds from the
+    two bands are not jointly constrained. 
+    Therefore, we only show the average colour profiles here, and will conduct 
+    more careful study of the colour profiles in Huang\etal (in prep.).
 
@@
       \caption{
-          \textbf{Left:}
-          Relation between \mtot{} and the fraction of \mstar{} within 10 to 100 kpc, 
-          which is used here as proxy of the fraction of accreted stars. 
-          The typical uncertainties of \mtot{} and the mass fraction are shown in 
-          upper-left corner. 
-          This relation is compared with the relation between \mstar{} and the fraction
-          of accreted stars derived from the Illustris simulation at $z=0$ 
-          (Fig 4 in \citealt{RodriguezGomez2016}; grey solid and dashed lines). 
-          \textbf{Right:}
-          Comparison of the median \mden{} profiles of massive galaxies in the 
-          two lower \mtot{} bins from Fig~\ref{fig:avg_prof} with other observations 
-          and simulations, focusing on the inner region. 
-          The format is similar with the right panel of Fig~\ref{fig:avg_prof}.
-          We include: 
-          1) the median \mden{} profile of inner component from structure 
-          decomposition of massive elliptical galaxies at $z{\sim} 0$ from 
-          \citet[][Cyan, solid]{Huang2013a}; 
-          2) the median \mden{} profile of massive galaxies at $1.0 < z < 1.5$ 
-          from \textit{HST} observations in \citet[][Red, dashed]{Patel2013}; 
-          3) the median \mden{} profile of the \textit{in situ} stellar components in 
-          simulated massive halos from \citet[][Purple, dot-dashed]{Cooper2013};
-          4) the \mden{} profile of the very massive cD galaxy at $z{\sim} 1.1$ 
-          discovered by \citet[][Yellow, dashed]{Liu2013} in the Hubble 
+          \textbf{Left:} Ratio of the fraction of stars between 10 to 100 
+          kpc to the total galaxy mass \mtot{}. 
+          We adopt this ratio as a proxy for the fraction of  \textit{ex situ} stars 
+          in our sample. 
+          Typical observational uncertainties are shown in the upper left hand corner. 
+          The solid grey line shows the predicted relation  derived from the Illustris
+          simulation at $z=0$ (Fig 4 in \citealt{RodriguezGomez2016}). 
+          Regions between the grey dashed lines correspond to the range between the 
+          16 and 84 percentile of the distribution. 
+          \textbf{Right:} comparison between our median \mden{} profiles 
+          with the inner component of the structural decomposition of massive 
+          elliptical galaxies at $z<0.02$ from \citet[][Cyan, solid]{Huang2013a}.
+          At higher redshifts, the \mden{} profiles of massive galaxies should be 
+          dominated by the  \textit{in situ}  component. 
+          We compare our profiles with the median \mden{} profile of massive galaxies 
+          at $1.0 < z < 1.5$ from \textit{HST} observations 
+          \citet[][Red, dashed]{Patel2013}. 
+          Both these comparisons suggest that the \mden{} profile within 10 kpc is 
+          dominated by \textit{in situ} stars, but there are already contributions
+          from the accreted stars at very high \mstar{} end. 
+          We also compare with the \mden{} profile of a very massive cD galaxy at
+          $z{\sim} 1.1$ discovered by \citet[][Yellow, dashed]{Liu2013} in the Hubble 
           Ultra-Deep Field. 
+          It is likely that this object will grow into one of the very massive central
+          galaxies in our sample.
+          It is interesting to see that its \mden{} profile is very similar to the 
+          HSC profile of the most massive \mtot{} bin in the inner $\sim 20$ kpc, so 
+          the resulting growth should mostly happen in the outskirt. 
           }
@@
 
-    With the help of deep HSC images, we trace the stellar mass distributions of 
-    $0.3 < z < 0.5$ massive galaxies out to $>100$ kpc, and reveal the mass-dependent 
-    nature of their stellar halos.
-    Here we briefly discuss the physical origin, scientific implications, and potential 
-    caveats of these results.
-
-    % TODO: Move to Paper II
-    %By using deep imaging from the HSC survey we have shown that the stellar mass 
-    %density profiles of massive central galaxies depend systematically on the mass 
-    %of their host dark matter halos.
-
-%% ------------------------------------------------------------------------------------ %% 
-\subsection{The Formation of Massive Galaxies and the Assembly of Outer Halos}
+    We have used data from the HSC survey that is both simultaneously 
+    deep and wide to trace the stellar mass distributions of $0.3 < z < 0.5$ massive 
+    galaxies out to $>100$ kpc and to reveal the mass-dependent nature of their 
+    stellar haloes.
+    Here we briefly discuss the scientific implications of our results.
+
+%% ------------------------------------------------------------------------------------ %% 
+\subsection{The formation of massive galaxies and the assembly of their outer haloes}
     \label{ssec:twophase}
 
-    The mass-dependent nature we find in the \mden{} and ellipticity profiles of 
-    massive galaxies are consistent with the two-phase formation scenario. 
-    According to this theory, the ``cores'' of massive central galaxies are formed 
-    at $z{\sim} 2$ during an intense period of \textit{in situ} star formation. 
+    We find that the outer haloes of massive elliptical galaxies grow more prominent 
+    and more elliptical with increasing stellar mass.
+    According to the two-phase formation scenario, the inner 5--10 kpc of these 
+    massive central galaxies are formed at $z>1$ during an intense period of 
+    \textit{in situ} star formation. 
     The outskirts of massive galaxies are then built up through a more gradual second 
-    phase of evolution (the \textit{ex situ} phase) that is dominated by mass assembly via 
-    accretion and merger.
-    Non-dissipative mergers, especially the minor ones, mostly deposit stars in the 
-    outskirts of the centrals and do not have large impact on the central \mden{} 
-    profile (e.g. \citealt{Oogi2013, Bedorf2013}).
+    phase of evolution (the \textit{ex situ} phase) that is dominated by mass assembly 
+    via accretions.
+    Non-dissipative mergers, especially minor mergers\footnote{Typically, minor merger
+    means the one with stellar mass ratio smaller than 1:3 or 1:4},  deposit stars
+    mostly in the outskirts of centrals and do not have a large impact on the central
+    \mden{} profile (e.g. \citealt{BoylanKolchin2008, Oogi2013, Bedorf2013}).
     Given the stochastic nature of the merging process, it is easy to understand why 
     the \mden{} profiles of massive galaxies are similar in the inner region but show
-    large and continuous scatter in the outskirt.
+    a large scatter in the outer region.
 
     State of the art hydrodynamic simulations of massive galaxy formation predict 
-    that the fraction of accreted stars should strongly increase with their stellar 
-    mass and the ``ex-situ'' component dominate the stellar halo (e.g.
+    that the fraction of accreted stars should strongly increase with stellar 
+    mass and that for very massive galaxies, the \textit{ex situ} may reach up to 
+    50--90\% of the total galaxy mass (e.g.
     \citealt{Oser2010, Cooper2013, Dubois2013, LeeYi2013, Hirschmann2015,
     RodriguezGomez2016}).
-    This picture is supported by the increasingly more prominent stellar halos in 
-    more massive galaxies and the negative color gradients we see in these massive 
-    galaxies. 
-    The slightly bluer color in their outskirts are consistent with the picture that 
-    the stars there are from less massive galaxies on the ``red-squence''.
-
-    Also under this picture, the shape of the stellar halo should preserve information
-    about the merging history and even the dark matter halos. 
-    Simulations show that, for slow-rotating massive ETGs experienced multiple 
-    minor-mergers, the shape of the stellar and dark matter halos are closely 
-    correlated (e.g. \citealt{Wu2014}). 
-    However, simulation like the one in \citet{Wu2014} predicts that more massive 
-    galaxies should be rounder in the outskirt.
-    This difference deserves more investigations using stellar kinematics and 
-    simulations. 
-    It may reflect the importance of major merger in shaping the most massive 
-    galaxies. 
-    Major merger with central galaxy of massive halo often happens on near-radial 
-    orbits, hence leads to (e.g. \citealt{Murante2007}) radially biassed stellar 
-    orbits and more elongated halo.
-
-    At a larger scale, the distribution of satellites in massive halo is known to 
-    intrinsically align with the central galaxy (e.g. \citealt{Brainerd2005, 
-    Yang2006b, NiedersteOstholt2010, HuangMandelbaum2016}), and the alignment signal
-    is stronger for more massive galaxies (e.g. \citealt{Hirata2007}).
+
+    This picture is supported by our observations that massive galaxies display more 
+    prominent stellar haloes as well as by their negative colour gradients. 
+    The fact that the outskirts of these galaxies are slightly bluer than the inner
+    regions is consistent with the picture that stellar haloes are built up by a
+    series of minor mergers (average merger mass-ratio between 1:3 and 1:10; e.g. 
+    \citealt{Huang2016}) because less massive ETGs are typically bluer.
+
+    Also according to this picture, the shape of the stellar halo should preserve
+    information about the merging history and possibly even about the shape of the 
+    dark matter halo. 
+    Simulations show the shape of the stellar and dark matter haloes are closely 
+    correlated (e.g. \citealt{Wu2014}) for slowly rotating massive ETGs having 
+    undergone multiple minor mergers.
+    The more elongated outer halo and the trend between the ellipticity profile and 
+    stellar mass may reflect the orbital properties of an accreted satellite. 
+    In simulations, satellite orbits become more radial for more massive haloes 
+    (e.g. \citealt{Murante2007, Wetzel2011, Jiang2015}. 
+    Satellites infalling along radial orbits may help to form elongated stellar 
+    haloes.
+    In principle, these results may explain the trend that we see. 
+    However, in contrast, simulation from \citet{Wu2014} predict that more massive 
+    galaxies should have \emph{rounder} outskirts, which is the opposite trend 
+    compared to HSC. 
+    This difference warrants further investigation.
+
+    At larger scales, the distribution of satellite galaxies in massive haloes is 
+    found to be aligned with the major axis of the central galaxy 
+    (e.g. \citealt{Brainerd2005, Yang2006b, NiedersteOstholt2010, 
+    HuangMandelbaum2016}). 
+    This alignment signal is found to be stronger for more luminous galaxies 
+    living in more massive haloes (e.g. \citealt{Hirata2007}).
     The fact that more massive central galaxies have steeper ellipticity profiles 
-    and become increasingly more elongated in the outskirt may help understand 
-    the physical causes of the intrinsic alignment. 
-    Moreover, the shape of the dark matter halo can now be estimated using both 
-    satellite distributions and weak lensing analysis (\citealt{ClampittJain2016}). 
+    and become increasingly more elongated in the outskirt may be due to 
+    such alignment. 
+    Moreover, the shape of the dark matter halo can be estimated by analyzing 
+    satellite distributions and weak lensing profiles (\citealt{ClampittJain2016}). 
     It is interesting to point out that the most recent measurement by 
-    \citet{Shin2017} around SDSS clusters show a halo axis-ratio of ${\sim}0.55$, 
+    \citet{Shin2017} around SDSS clusters shows a halo axis-ratio of ${\sim}0.55$, 
     which is only slightly more elongated than the stellar halo of galaxies in our 
@@
 
-    % TODO: Move to paper II     
-    %State of the art hydrodynamic simulations suggest that massive dark matter halos 
-    %have central galaxies that have outer stellar envelopes with shallow slopes 
-    %(e.g. \citealt{Pillepich2014}). 
-    %This is consistent with the results in Fig \ref{fig:prof_1}.
-
-    %Hence, according to this picture, the outer stellar envelopes of massive centrals 
-    %should correlate with the masses of their host halos, in qualitative agreement with
-    %our findings.
-
-%% ------------------------------------------------------------------------------------ %% 
-\subsection{Aperture Masses as Proxies of the \textit{In situ} and Accreted Stars}
+%% ------------------------------------------------------------------------------------ %% 
+\subsection{Aperture masses as proxies of the \textit{in situ} and accreted stars}
     \label{ssec:insitu}
 
-    Recent hydrodynamic simulations of galaxy formation often separate the stars in 
-    galaxy into the \textit{in situ} and accreted components. 
-    In simulation, the \textit{in situ} component is often defined as the stars formed 
-    in the halo of the ``main progenitor''.  
-    The spatial distribution, kinematic, and stellar population properties of both 
-    components become important theoretical predictions to be examined. 
-    Among them, the fraction of the accreted component and its relation with stellar 
-    mass is the most fundamental one. 
-    However, on the observational side, separation of these two physical components 
-    is extremely difficult. 
-    Recently, deep surveys of nearby disk galaxies start to provide constraints of 
-    their accreted fraction using the distinctive halo components. 
-    For more massive ETGs, efforts so far all depend on multi-component model fitting
-    and image stacking analysis (e.g. \citealt{Huang2013a, dSouza2014, Spavone2017}).
-    In this work, we propose that \mstar{} within different physical apertures could 
-    be explored as potential proxies of masses in \textit{in situ} and accreted 
-    components.  
-    Given the behaviours of the \mden{} profiles shown in Fig \ref{fig:avg_prof}, 
-    we propose to use mass within 10 kpc (\minn{}) and 100 kpc (\mtot{}) as proxies 
-    of the \textit{in situ} and total \mstar{}.
-
-    On the left panel of Fig \ref{fig:discussion_1}, we plot the relation between 
-    \mtot{} and the fraction of mass between 10 and 100 kpc (as proxy of the mass of 
-    the accreted component), and compare with the relation between \mstar{} and 
-    accreted fraction derived from the Illustris simulation 
-    (\citealt{RodriguezGomez2016}). 
-    It is intriguing to see that, our proxy of accreted mass not only strongly 
-    correlates with \mtot{}, the relation is surprisingly consistent with the 
-    prediction from \citet{RodriguezGomez2016}. 
-    Given the limitations of the Illustris simulation and the different definitions
-    of total stellar mass, the almost perfect consistency may well be a coincidence. 
-    However, it is encouraging to see that our arbitrary choices of aperture masses 
-    can already reproduce similar slope and scatter of this relation. 
-    Right now, there are other hydrodynamic simulations that predict significantly 
-    different mass fraction of accreted stars at fixed \mstar{} (e.g. 
-    \citealt{Lackner2012, Qu2017}). 
-    Therefore, it will be very useful to perform more detailed comparisons with 
-    these simulations and explore the possibilities of using certain aperture mass 
-    to trace the \textit{in situ} component.
-
-    % TODO: Move to Paper II
-    %Meanwhile, these simulation also point out that the fraction of accreted stars 
-    %increases steeply with total \mstar{} and that the ``ex-situ'' component
-    %starts to dominate the \mden{} profiles around $R_{\mathrm{e}}$ for 
-    %\logms{}$\geq 11.5$ galaxies. 
-    %In this work, we find that the median \mden{} profiles of \rbcg{} and \nbcg{} 
-    %samples start to show differences around 15-20 kpc, which is close to 
-    %their $R_{\mathrm{e}}$. 
-    %Furthermore, the environmental dependence of our median \mden{} profiles 
-    %becomes more significant in our highest \mtot{} bin (see Fig \ref{fig:prof_4}). 
-    %These results all align with the picture that the \mhalo{}-dependence of the 
-    %\mden{} profiles of massive galaxies is driven by the variations in the 
-    %``ex-situ'' component at large radii.
-
-    To further check whether \minn{} can reasonably represent the \textit{in situ} 
-    mass, we compare the average \mden{} profiles of HSC massive galaxies in two 
-    \mtot{} bins (Left panel of Fig \ref{fig:discussion_1}, 
-    $11.4\leq$\logmtot{}$<11.6$ and $11.6\leq$\logmtot{}$<11.8$) with:
-
-    \begin{enumerate}
-
-        \item The median \mden{} profiles of massive ETGs at $1.0 < z < 1.5$ in
-            \citealt{Patel2013} since they are considered as the progenitors of 
+    As mentioned in \S~\ref{sec:intro}, hydrodynamic simulations often predict that 
+    the faction of \textit{ex situ} stars increase with total stellar mass.
+    However, it is still extremely difficult to separate the \textit{in situ} and
+    \textit{ex situ} components observationally, despite the fact that it is the most 
+    important theoretical prediction to be verified.
+
+    Recent deep surveys of nearby disc galaxies have started to provide constraints 
+    on their stellar haloes (e.g. \citealt{Courteau2011, Merritt2016, 
+    Harmsen2017})\footnote{Although it is still not certain that all stellar haloes
+    around disc galaxies are made out of \textit{ex situ} stars.}, as it is
+    relatively easier to decompose the stellar halo component. 
+    As for massive ETGs, limited observational constraints still mainly depend on 
+    multi-component model fitting and/or image stacking analyses 
+    (e.g. \citealt{Gonzalez2007, Huang2013a, DSouza2014, Spavone2017}).
+    In this work, we propose that \mstar{} values computed within different fixed 
+    physical elliptical apertures are worth exploring as proxies of the 
+    \textit{ex situ} fraction. 
+    We propose to use the mass within 10 kpc (\minn{}) and 100 kpc (\mtot{}) as 
+    proxies for the \textit{in situ} component and for the total \mstar{}.
+
+    On the left panel of Fig \ref{fig:discussion_1} we show 
+    the relation between \mtot{} and the fraction of mass between 10 and 100 kpc 
+    (as a proxy of the mass of the accreted component).
+    We compare this with the fraction of \textit{ex situ} stars predicted by the 
+    Illustris simulation (\citealt{RodriguezGomez2016}).  
+    We find that our proxy for the accreted mass component correlates strongly with  
+    \mtot{} and that this relation is surprisingly consistent with predictions from
+    \citet{RodriguezGomez2016}.  
+    Given the limitations of the Illustris simulation and the imperfect nature of 
+    our \textit{ex situ} fraction proxy, the almost perfect agreement seen in 
+    Fig~\ref{fig:discussion_1} may well be a coincidence.  
+    However, it is encouraging to see that our simple proxy for the fraction of 
+    \textit{ex situ} stars seems to match both the slope and the scatter of the 
+    predicted relation.  
+    There are other hydrodynamic simulations that predict significantly different 
+    \textit{ex situ} fractions compared to Illustris (e.g. \citealt{Lackner2012, 
+    Qu2017}). 
+    Furthermore, a few known issues in the original Illustris simulation have been 
+    resolved in the new Illustris--TNG version (e.g. \citealt{Genel2017, 
+    Pillepich2017}.
+    In future works [including Huang\etal (in prep.)], we will explore more 
+    comparisons with detailed predictions from new simulations to see how well we 
+    can trace \textit{ex situ} fractions in massive galaxies using simple 
+    elliptical aperture masses.
+
+    Here, we further compare our \mden{} profiles with 
+    (1) the profiles of the \textit{in situ} component estimated from different ways,
+    and (2) profiles of high-redshift massive galaxies that should be dominated by 
+    the \textit{in situ} component.  
+    In particular, we compare with the following:
+
+    \begin{itemize}
+
+        \item The median \mden{} profiles of massive ETGs at $1.0 < z < 1.5$ from
+            \citealt{Patel2013}.
+            These are considered to be the progenitors of 
             ${\sim} 10^{11.5} M_{\odot}$ ETGs at $z=0$ and their inner region 
@@
 
-        \item The inner components of $z{\sim} 0$ ellipticals from 2-D 
-            decomposition (\citealt{Huang2013a}).
-            As proxy of the \textit{in situ} component, \citet{Huang2013b} showed 
-            that they are structurally similar to the compact ``red nuggets'' at 
-            high-$z$.
+        \item The inner component of $z{\sim} 0$ ellipticals from the 2-D 
+            decomposition of \citet{Huang2013a}. 
+            \citet{Huang2013b} show that this inner component is structurally 
+            similar to the compact `red nuggets' at high-$z$.
 
         \item The \textit{in situ} components of simulated central galaxies in 
-            massive halos from \citet{Cooper2013} (the inner ${\sim} 5$ kpc is 
+            massive haloes from \citet{Cooper2013} (the inner ${\sim} 5$ kpc is 
             quite uncertain due to the resolution).  
@@
 
-    \end{enumerate}
-
-    We also compare with a uniquely massive BCG at high redshift: 
-    a ${\sim} 10^{11.4} M_{\odot}$ BCG with distinctive ``cD''-like envelope at 
-    $z{\sim} 1.1$ (\citealt{Liu2013}).  
-    Its \mden{} profile follows the median profile of $11.6\leq$\logmtot{}$<11.8$ 
-    massive galaxies nicely inside 10-15 kpc, but becomes steeper in the outskirt.
-    It represents an interesting phase where the inner ``core'' of massive BCG is 
-    already in pace at $z{\sim} 1$ while the outer halo is still being assembled.
-
-    These comparisons certainly support the idea that \minn{} mainly consists of 
-    \textit{in situ} stars and mass at $\mathrm{R} > 15$-20 kpc is dominated by accreted 
-    component.     
-    Meanwhile, they also show that the \texttt{in situ} component 
-    could have steeper \mden{} slope and mass distribution much more extended than 
-    10 kpc\footnote{We convert these \mden{} profiles to the same 
-    Chabrier IMF; but there are still differences in median \mstar{} and 
-    details in the \m2l{} estimates}. 
-    More comparisons with massive galaxies at high redshift and simulated 
-    \textit{in situ} components will help shed light on this.
-
-    In line with the prediction from Illustris, this comparison also 
-    suggests that, at very high-mass end, the accreted component can make significant 
-    contribution even within the inner 10--20 kpc. 
-    The nature of these ``accreted'' stars in the center of massive galaxies deserve 
-    more attention. 
-    It is possible that they mainly come from major merger and used to be the 
-    \texttt{in situ} component of another massive galaxy. 
-    It would be interesting see whether there is an alternative, but also physically 
-    motivated definition of \textit{in situ} component that can be more easily examined 
-    by observation.
-
-    % TODO: Move to Paper II
-    %More BCGs like this at $0.5 < z < 1.0$ can shed light on this intriguing 
-    %process, and help us confirm whether the environmental dependence of structure 
-    %has already emerged within massive galaxies at higher redshift 
-    %(e.g. \citealt{Papovich2012})
-
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %% 
-\subsection{Stellar Halo and Intra-cluster Light}
-
-    Finally, we emphasize that in this work we do not attempt to separate the 
-    potential (and distinct) ``intra-cluster'' light component (ICL; e.g. 
-    \citealt{Carlberg1997, Lin2004, Gonzalez2005, Mihos2005}) from the massive 
-    galaxies. 
-    Instead, we adopt the view that the light of the main galaxy and the 
-    ``intra-cluster''component share a smooth and continuous distribution.
-
-    In practice, reliable isolation of a physically meaningful ICL component using 
-    photometry alone is extremely difficult, if not impossible. 
-    More importantly, he majority of massive galaxies in our samples are not considered 
-    as the BCG of a cluster (\mhalo{}$\simgt 10^{14}M_{\star}$). 
-    Even for BCGs in the \rbcg{} samples, only small fraction of them belong to very 
-    massive clusters where strong evidence of photometric ICL component is 
-    often found (\mhalo{}$\simgt 10^{15}M_{\star}$, e.g. \citealt{Presotto2014, 
-    Burke2015}).
-    For typical \rbcg{} cluster in our sample, the Virgo cluster is a good nearby 
-    example.  
-    Ultra-deep images show that the stellar halo of the BCG smoothly extends beyond 
-    100 kpc, while the ICL only becomes important outside that radius and is dominated 
-    by many individual tidal features (e.g. \citealt{Mihos2016}).
-    Therefore, it is highly unlikely the main results are driven by the ICL component.
-
-    At the imaging depth of HSC and out to 100 kpc, the \mden{} profiles of massive 
-    galaxies vary smoothly and we find no evidence for a distinctive ICL component. 
-    Although the rising stellar velocity dispersion in the outskirt of massive BCG
-    has been used as evidence of a kinematically separated ICL component (e.g. 
-    \citealt{Dressler1979, Carter1999, Kelson2002, Bender2015, Longobardi2015}), 
-    we think it is reasonable to treat the stellar halo of BCG and potential ICL as 
-    an integrate component. 
-    They both carry important information regarding the assembly of central galaxy 
-    and its dark matter halo.
+    \end{itemize}
+
+    Although these simple comparisons support the idea that \minn{} mainly consists 
+    of \textit{in situ} stars whereas mass at $\mathrm{R} > 15$--20 kpc is dominated 
+    by \textit{ex situ} component, they also show that the \texttt{in situ} component 
+    could extend beyond 10 kpc\footnote{We convert these \mden{} profiles to the same 
+    \citealt{Chabrier2003} IMF; but there are still differences in median \mstar{} 
+    and details in the \m2l{} estimates}, and a fraction of mass within 10 kpc could 
+    also come from accretion (see also \citealt{RodriguezGomez2016}). 
+    This is certainly the limitation for using aperture masses as proxies of 
+    \textit{in situ} and \textit{ex situ} masses. 
+    In other works (e.g. \citealt{Huang2013a, Spavone2017}), 
+    the outer component from image decomposition is treated as proxy of the 
+    \textit{ex situ} component. 
+    Since such a photometric component extends to the center of the galaxy and can 
+    reach a radius much larger than 100 kpc, it can lead to a higher \textit{ex situ}
+    fraction than ours (e.g. \citealt{Spavone2017}). 
+    It will be very interesting to apply a similar decomposition method to both the 
+    HSC images and the simulated massive galaxies to help us determine the 
+    best tracer of the \textit{in situ} and \textit{ex situ} mass.
+
+    We also compare our results with a uniquely massive galaxy at high redshift: 
+    a \logms{}${\sim} 10^{11.4} M_{\odot}$ galaxy with a distinctive `cD'-like 
+    envelope at $z{\sim} 1.1$ (\citealt{Liu2013}).  
+    This high-redshift galaxy has a \mden{} profile that follows the median \mden{} 
+    profile of our $11.6\leq$\logmtot{}$<11.8$ sample nicely at $\mathrm{R} < 40$ 
+    kpc, but the profile becomes much steeper in the outskirt.
+    The steeper profile suggests that, while the very outskirt of the stellar halo 
+    is still being assembled, some massive high-$z$ galaxies may already have a
+    significant fraction of \textit{ex situ} stars. 
+    In future works [including Huang\etal (in prep.)], we will also look into the 
+    redshift evolution of the outer \mden{} profiles up to $z\sim 1.0$ using both HSC 
+    and other observations. 
+    Comparisons with relevant simulations  can also tell us how well we can trace
+    the evolution of the \textit{ex situ} fraction of stars using aperture masses.
 
@@
 
-    In this work, we study how the stellar mass density profiles and other structural
-    properties of massive central galaxies depend on their total stellar mass using 
-    deep images from the Subaru HSC survey. 
-    With the help of this high-quality and wide area data set, we directly map the 
+    In this work, we use deep images from the Subaru HSC survey to study how the 
+    projected stellar mass density profiles and other structural properties of 
+    massive central galaxies depend on their total stellar mass. 
+    With the help of this high-quality, wide-area data set, we directly map the 
     stellar mass distributions of ${\sim}7000$ massive central galaxies at 
@@
 
-    \begin{enumerate}
-        \item We find that the ``total'' \mstar{} of these massive galaxies can be 
+    \begin{itemize}
+
+        \item We show that the \mden{} profiles of massive galaxies are relatively
+            homogenous within 10--20 kpc. 
+            However, there is large scatter in outer profiles of massive galaxies. 
+            Galaxies with higher \mtot{} show more prominent stellar haloes and have 
+            shallower outer \mden{} slopes. 
+            Assuming that stellar haloes are dominated by accreted stars, this result 
+            is consistent with the two-phase formation picture of massive galaxies.
+
+        \item We show that, on average, massive galaxies have positive ellipticity 
+            gradients out to at least 60 kpc. 
+            The average ellipticity profile also depends on \mtot{}: More massive 
+            galaxies tend to have steeper ellipticity gradients and become more 
+            elongated in stellar haloes.
+
+        \item On the other hand, although massive galaxies in all three \mtot{} bins 
+            show clearly negative average colour gradients out to 60 kpc, the 
+            average $(g-r)$ and $(g-i)$ colour gradients do not show clear 
+            dependence on \mtot{}.
+
+        \item We propose that, under reasonable assumptions, stellar masses within 
+            different physical apertures could be used to trace the 
+            \textit{in situ} and \textit{ex situ} components. 
+            Here we show that \minn{} and the \mstar{} between 10 and 100 kpc could 
+            be promising proxies for the two physical components, and can recover the 
+            trend between stellar mass and \textit{ex situ} fraction from simulation.
+
+        \item We find that the `total' \mstar{} of these massive galaxies can be 
             significantly underestimated with shallow imaging data such as SDSS and/or 
-            oversimplified model assumption (e.g. the \texttt{cModel} or single-\ser{}). 
+            oversimplified model assumptions (e.g. the \texttt{cModel} or single-\ser). 
             In contrast to previous work, our results do not depend on stacking or any 
             parametric models. 
-            Moreover, the level of such underestimation also depends on their \mtot{}.
-            More massive galaxies tend to have larger amount of light missing in the 
-            outskirt.  
-            The level of underestimation also shows evidence of \mhalo{}-dependence. 
-            The central galaxies of \mhalo{}$\simgt 10^{14.0} M_{\odot}$ halos suffer
-            more from this issue. 
-            This should be carefully taken into account when discussing topics such 
-            as the evolution of the galaxy SMF.
-
-        \item We show that the \mden{} profiles of massive galaxies within inner 
-            10-20 kpc generally show similar slopes and have relative small scatter. 
-            Meanwhile, there is a large but continuous scatter in the outskirts of 
-            \mden{} profiles that suggests the stellar halos of these massive galaxies 
-            are not self-similar. 
-            Galaxies with higher \mtot{} show more prominent stellar halos and have 
-            shallower outer \mden{} slopes than the less massive ones. 
-            Assuming the stellar halos are dominated by accreted stars, the result is 
-            in consistent with the two-phase formation picture of massive galaxies.
-
-        \item We show that, on average, massive galaxies have positive ellipticity 
-            gradient out to at least 60 kpc. 
-            The average ellipticity profiles also depend on \mtot{}: more massive 
-            galaxies tend to have steeper ellipticity gradients and become more 
-            elongated in the accreted stellar halo. 
-            On the other hand, the average $g-r$ and $g-i$ color gradients do not 
-            show clear dependence on \mtot{} within 10-60 kpc.
-
-    \end{enumerate}
-
-    These results highlight the advantages of wide area, deep, and high-quality imaging 
+            Moreover, the degree to which stellar mass is underestimated depends on 
+            \mtot{}. 
+            A simple model misses more light for massive galaxies because they have 
+            more extended envelopes. 
+            There is also an \mhalo{}-dependence of this effect, and simple 
+            luminosity estimates will miss more light for BCGs in more massive 
+            haloes compared to centrals in less massive haloes.
+            These effects need to be carefully taken into account when discussing 
+            topics such as the evolution of the galaxy stellar mass function.
+
+    \end{itemize}
+
+    These results highlight the advantages of wide-area, deep, and high-quality imaging 
     for studying the evolution of massive galaxies. 
-    Upon finishing this work, the HSC survey has already doubled its sky coverage to 
-    ${\sim} 200$ deg$^2$, and provides a much larger sample of massive central galaxies. 
+    At present, the HSC survey has already doubled its sky coverage to 
+    ${\sim} 200$ deg$^2$ and provides a much larger sample of massive central galaxies. 
     In the near future, we will extend this work to lower \mtot{} by using photometric 
-    redshifts, and we will also apply 2-D photometry method (e.g.\ \citealt{Huang2013a}) 
-    to take advantages of the multi-wavelength nature of the HSC survey 
-    (e.g. \citealt{Huang2016}). 
+    redshifts, and we will also apply 2-D photometric methods 
+    (e.g.\ \citealt{Huang2013a}) to take advantage of the multi-wavelength nature of 
+    the HSC survey (e.g. \citealt{Huang2016}). 
     Our current work can also be combined with weak lensing measurements of the dark 
-    matter halos of massive galaxies and physical insights into the assembly histories 
-    of these galaxies can be gained by comparing with cosmological hydro-simulations 
-    such as Illustris (\citealt{Vogelsberger2014}, \citealt{Genel2014}), 
-    EAGLE (\citealt{Schaye2015}, \citealt{Crain2015}), or \textit{Horizon-AGN} 
-    (\citealt{Dubois2014}).
+    matter haloes of massive galaxies, and physical insights into the assembly histories 
+    of these galaxies can be gained by comparing the measurements with cosmological 
+    hydro-simulations such as Illustris (\citealt{Vogelsberger2014}, 
+    \citealt{Genel2014}), EAGLE (\citealt{Schaye2015}, \citealt{Crain2015}), 
+    or \textit{Horizon-AGN} (\citealt{Dubois2014}).
 
@@
   % Personal 
-  SH thanks F.S.Liu for sharing the data from his work.
+  The authors thank Rachel Mandelbaum and Frank van~den~Bosch for insightful 
+  discussions and comments,
+  Shun Saito for helping us estimate the fraction of satellite 
+  galaxies in our sample, and
+  Feng-Shan Liu for sharing the \mden{} profile of the $z\sim1$ BCG from 
+  his work.
+  This material is based upon work supported by the National Science Foundation under 
+  Grant No.~1714610.
 
@@
 
+  % KITP
+  This research was supported in part by National Science Foundation under Grant 
+  No. NSF PHY11-25915.
+
   % Software
   This research made use of:
-  \href{http://www.stsci.edu/institute/software_hardware/pyraf/stsci\_python}{\texttt{STSCI\_PYTHON}},
+  \href{http://www.stsci.edu/institute/software_hardware/pyraf/stsci\_python}
+  {\texttt{\small{STSCI\_PYTHON}}},
       a general astronomical data analysis infrastructure in Python. 
-      \texttt{STSCI\_PYTHON} is a product of the Space Telescope Science Institute, 
-      which is operated by AURA for NASA;
+      \texttt{\small{STSCI\_PYTHON}} is a product of the Space Telescope Science
+      Institute, which is operated by Association of Universities for Research 
+      in Astronomy (AURA) for NASA;
   \href{http://www.scipy.org/}{\texttt{SciPy}},
@@
 %% ------------------------------------------------------------------------------------ %%  
-\section{A. Extraction of 1-D surface brightness profile} 
+\section{Basic Statistical Properties of the Sample} 
+	\label{app:basic}
+
+%% ------------------------------------------------------------------------------------ %% 
+  \begin{figure}
+      \centering 
+      \includegraphics[width=\columnwidth]{fig/redbcg_sample_stats}
+      \caption{
+          \textbf{Top-left}: The \logmtot{}-$(g-r)$ rest-frame colour relation for the 
+          HSC massive galaxies.
+          We $k$-correct the colour using the \texttt{iSEDFit} fitting results.
+          Massive galaxies form a `red-sequence' on this figure, and there is 
+          little contamination from blue object at high-mass end.~~          
+          \textbf{Top-right}: The redshift distribution of the massive galaxies. 
+          The filled and empty histograms are for the \logmtot{}$>11.6$ and 
+          \logmtot{}$>11.2$ galaxies.
+          The vertical lines highlight the $0.3\leq z \leq 0.5$ redshift range.~~
+          \textbf{Bottom-left}: The distributions of \mtot{} of massive galaxies in 
+          this sample. 
+          Filled histogram shows the distribution for $0.3 < z < 0.5$ galaxies 
+          used in this work. 
+          The empty histogram shows the distribution for the whole $z>0.2$ sample
+          as comparison.~~
+          \textbf{Bottom-right}: The distributions of \minn{} in similar format. 
+      }
+      \label{fig:sample_stats}
+  \end{figure}
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
+    \begin{figure*}
+        \centering 
+        \includegraphics[width=\textwidth]{fig/redbcg_ellipse_tech}
+        \caption{
+            \textbf{Left:} Example of the object-mask built for the \texttt{Ellipse}
+            run for a typical massive galaxy in the sample. 
+            All the shaded regions are masked out. 
+            The three dashed lines (one red inner line and two blue lines) around 
+            the target at the center outlines the three radii we defined using the 
+            flux radius of the target.  
+            We increase the mask size for objects detected in different regions 
+            separated by these apertures (which are outlined by solid, elliptical 
+            apertures with different colours) using slightly different criteria.~~
+            \textbf{Middle:}: The zoom-in intensity profile around very low intensity 
+            value (top panel), and the curve-of-growth of the enclosed magnitude 
+            (bottom panel) of the example galaxy.  
+            To highlight the importance of background correction, we show the profiles 
+            using both images with (red solid line) and without (black dotted line) 
+            background correction. 
+            On the top panel, besides the horizontal line that highlights the zero flux 
+            level, we also show the uncertainty of the sky background estimate using 
+            the grey-shaded region.  
+            On the bottom panel, two horizontal lines indicate the magnitudes 
+            corresponding to total flux (solid) and flux within 100 kpc (dashed).~~
+            \textbf{Right:} Compares the 1-D surface brightness profiles for the same 
+            example galaxy using different masks 
+            (smaller masking region: red dashed line; larger masks: blue dashed line), 
+            or different \texttt{Ellipse} configurations
+            (more aggressive pixel-clipping: cyan dashed line; 
+            larger step in radius: green dashed line; 
+            using mean flux along the isophote instead of median: purple dashed line)
+            with the default one (black solid line).
+            }
+        \label{fig:ell_tech}
+    \end{figure*}
+%% ------------------------------------------------------------------------------------ %%
+
+    Here we show the basic statistics of the massive galaxies used in this work.
+    On the top-left panel of Fig~\ref{fig:sample_stats}, we show the \mtot{}-colour 
+    relation using the $k$-corrected rest-frame $(g-r)$ colour. 
+    These massive galaxies form a clear `red sequence' with little contamination 
+    from the `blue cloud' at the very high-mass end.
+
+    In the rest of Fig~\ref{fig:sample_stats}, we also show the distributions of 
+    redshift, \mtot{}, and \minn{}.
+    In this work, we focus on the massive galaxies with \logmtot{}$>11.6$ at 
+    $0.3 < z < 0.5$ where the sample is fairly complete in \mtot{}.
+
+%% ------------------------------------------------------------------------------------ %% 
+\section{Extraction of 1-D surface brightness profile} 
     \label{app:ellipse}
@@
     The procedure used to derive 1-D surface brightness profile from the 
-    background-corrected, contamination-masked images is already described in 
-    Section~\ref{sec:ellipse} briefly. 
+    background-corrected, contamination-masked images is  described briefly in 
+    \S~\ref{sec:ellipse}. 
+    The uncertainties of the surface brightness profiles include the error in 
+    isophotal intensity derived by the \texttt{ellipse} procedure and the 
+    uncertainty from background fluctuation estimated by the distribution of the 
+    rebinned background pixels using the above method. 
     In practice, the profile at very low surface brightness level is sensitive to 
@@
     After some tests, we choose to use 0.1 dex in logarithm as the step in semi-major 
-    axis length between successive ellipses, and we use the median pixel value over the
-    elliptical annulus after rejecting outlying pixels via $3\sigma$-clipping three
-    times.
-    We make the above choices to make the final profile less affected by any nearby
-    object, and also test the differences between the profiles derived using larger
+    axis length between successive ellipses, and we use the median pixel value over 
+    the elliptical annulus after rejecting outlying pixels via 3-$\sigma$ clipping 
+    three times.
+    These choices are made to ensure the final \mden{} profile is less affected by 
+    any nearby object. 
+    We also test the differences between the profiles derived using larger
     step, or mean value on the annulus, or fewer times of $\sigma$-clipping. 
@@
     changes, especially within 100 kpc. 
+    Given our configurations, the typical photometric error is around $5$\% level
+    at $i\sim 26$ \sb{}, and is about $12$\% down to $i\sim 28.5$ \sb{}. 
+    Although we want to point out that at the low surface brightness end, 
+    systematic uncertainties like background subtraction are still more important.
     On the right panel of Fig~\ref{fig:ell_tech}, we compare the surface brightness
@@
     parameters. 
-    The profile within 100 kpc is very stable, and the only noticable difference 
-    is caused by the less aggressive object-mask in the very outskirt.
-
-    We should also mention that we run \texttt{Ellipse} allowing for more 
+    The profile within 100 kpc is very stable, and the only noticeable difference 
+    is caused by the less aggressive object-mask in the outskirt.
+
+    We should also mention that we run \texttt{Ellipse} to allow for more 
     sophisticated shapes than simple ellipse (4th Fourier modes that can make 
-    isophote more ``disky'' or ``boxy'', e.g.\ \citealt{Kormendy2009}) to fit the 
+    isophote more `disky' or `boxy', e.g.\ \citealt{Kormendy2009}) to fit the 
     isophote better.
-    We also apply the isophotes from $i$-band images to other bands in 
-    ``force-photometry'' mode \texttt{Ellipse} run to get initial estimates of 
-    color profiles.  
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %% 
-    \begin{figure*}
-        \centering 
-        \includegraphics[width=\textwidth]{fig/redbcg_ellipse_tech}
-        \caption{
-            \textbf{Left:} Example of the object-mask built for the \texttt{Ellipse}
-            run for a typical massive galaxy in the sample. 
-            All the shaded regions are masked out. 
-            The three dash lines (red, inner one and two blue ones) around the target 
-            at the center outlines the three radius we defined using the flux radius 
-            of the target.  
-            We increase the mask size for objects detected in different regions 
-            separated by these apertures (which are outlined by solid, elliptical 
-            apertures with different colors) using slightly different criteria.~~
-            \textbf{Middle:}: The zoom-in intensity profile around very low intensity 
-            value (top panel), and the curve-of-growth of the enclosed magnitude 
-            (bottom panel) of the example galaxy.  
-            To highlight the importance of background correction, we show the profiles 
-            using both images with (red, solid line) and without (black, dotted line) 
-            background correction. 
-            On the top panel, besides the horizontal line that highlights the zero flux 
-            level, we also show the uncertainty of the sky background estimate using 
-            the grey-shaded region.  
-            On the bottom panel, two horizontal lines indicate the magnitudes 
-            corresponding to total flux (solid) and flux within 100 kpc (dash).~~
-            \textbf{Right:} compares the 1-D surface brightness profiles for the same 
-            example galaxy using different masks 
-            (smaller masking region: red, dash line; larger masks: blue, dash line), 
-            or different \texttt{Ellipse} configurations
-            (more aggressive pixel-clipping: cyan, dash line; 
-             larger step in radius: green, dash line; 
-             using mean flux along the isophote instead of median: purple, dash line)
-            with the default one (black, solid line).
-            }
-        \label{fig:ell_tech}
-    \end{figure*}
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %% 
-\section{B. Estimate average {$M_{\star}/L_{\star}$} using \texttt{iSEDFit}} 
+    We also apply the isophotes from $i$-band images to other bands in a
+    `force-photometry' mode \texttt{Ellipse} run to get initial estimates of 
+    colour profiles.
+
+    We cannot extract reliable 1-D profiles for a small fraction of massive
+    galaxies because they are heavily masked out for either physical 
+    (e.g.\ late-stage major merger) or nuisance (e.g.\ nearby foreground 
+    galaxy or bright star) reasons. 
+    This is an intrinsic limitation of the 1-D method, and it removes ${\sim}10$\% 
+    of the sample.
+    We visually examine the 3-colour images ($gri$-band, like the ones shown in 
+    Figure~\ref{fig:sdss_compare}) of randomly selected galaxies with 
+    failed 1-D profiles.  
+    Most of them are relatively small galaxies that are severely contaminated by 
+    nearby objects and do not affect the results of this work.  
+    Meanwhile, it is worth noting that this work does exclude most major merging 
+    systems among massive galaxies.
+
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %% 
+\section{Estimate average {$M_{\star}/L_{\star}$} using \texttt{iSEDFit}} 
     \label{app:sed}
@@
             the SED fitting results. 
-            The open-boxes show the observed fluxes in 5-band, and the solid, blue-dots
-            show the best-fitted results, along with the high-resolution spectrum for
-            this model reconstructed using the synthetic spectra from \texttt{FSPS}. 
-            Top-left corner shows the best-fit stellar population parameters, and 
-            bottom-right corner shows the ID, redshift of this object, and reduced 
-            $\chi^2$ of the best-fit model.~~~
-            \textbf{Right:} the Posterior distributions of a few key parameters.
+            The open boxes show the observed fluxes in the five bands, and the solid 
+            blue dots show the best-fitting results, along with the high-resolution
+            spectrum for this model reconstructed using the synthetic spectra from
+            \texttt{FSPS}. 
+            The top-left corner shows the best-fitting stellar population parameters, 
+            and the bottom-right corner shows the ID, redshift of this object, and 
+            reduced $\chi^2$ of the best-fitting model.~~~
+            \textbf{Right:} the posterior distributions of a few key
+            parameters.
             From top-left to bottom right are: 
-            1) stellar mass (\logms{}); 
-            2) age of the population (mass and star-formation rate weighted) in Gyr; 
-            3) star formation rate ($\log\ \mathrm{SFR}\ (M_{\odot}/\mathrm{yr})$; 
+            (1) stellar mass (\logms{}); 
+            (2) age of the population (mass and star-formation rate weighted) in Gyr; 
+            (3) star formation rate ($\log\ \mathrm{SFR}\ (M_{\odot}/\mathrm{yr})$; 
             instant one and the one averaged over the previous 100 Myr; 
-            4) stellar metallicity ($\mathrm{Z}/\mathrm{Z}_{\odot}$); 
-            5) dust extinction ($\mathrm{A}_V$ in mag);
-            6) birthrate parameter ($\log\ b$; averaged over previous 100 and 1000 Myr).
+            (4) stellar metallicity ($\mathrm{Z}/\mathrm{Z}_{\odot}$); 
+            (5) dust extinction ($\mathrm{A}_V$ in mag);
+            (6) birthrate parameter ($\log\ b$; averaged over previous 100 and 
+            1000 Myr).
             }
-        \label{fig:ised}
+        \label{fig:ised_1}
         \end{center}
@@
 
-    In Section~\ref{ssec:isedfit}, we briefly explain the SED fitting procedure and 
+    In \S~\ref{ssec:isedfit}, we briefly explain the SED fitting procedure and 
     the priors used.   
+    \texttt{iSEDFit} takes a simplified Bayesian approach. 
+    In short, it first generates a large grid of SEDs from synthetic stellar 
+    population models by drawing randomly from the prior distributions of relevant
+    parameters (e.g. age, metallicity, dust extinction, and star formation history).
+    Based on these models, it uses the observed photometry and redshift to compute 
+    the statistical likelihood and generates the posterior PDF for each parameter.  
+    To get the best estimate of a given parameter, \texttt{iSEDFit} integrates the 
+    full PDF over all the other nuisance parameters.
+    Then, the median value and the 1-$\sigma$ uncertainty are derived based on the 
+    marginalized PDF. 
+    Please refer to \citet{Moustakas13} for technical details. 
     In Fig~\ref{fig:ised_1}, we show an example of the \texttt{iSEDFit} output by 
-    visualizing the 5-band HSC SED on top of the best-fit model along with the PDF 
+    visualizing the five-band HSC SED on top of the best-fitting model along with the PDF 
     of the key parameters.
 
-    Although we only use the best-fit \m2l{} in this work, it is necessary to make 
+    Although we only use the best-fitting \m2l{} in this work, it is necessary to make 
     sure the model is reasonable. 
-    We show the relations between \mstar{} and a few key stellar population parameters 
+    We show the relationship between \mstar{} and a few key stellar population parameters 
     derived by \texttt{iSEDFit} in Fig~\ref{fig:ised_2}. 
     Degeneracies among these parameters are inevitable based on only five broad-band
-    photometry, but as expected, most massive galaxies show old stellar age, high
+    photometry; but as expected, most massive galaxies show old stellar age, high
     stellar metallicity ($1.5 \times Z_{\odot}$ is the highest metallicity allowed by 
@@
             the fiducial one.  
-            Using results based on \texttt{BC03} model will not change any of our 
-            conclusions here.
-
-        \item On the bottom panel of Fig~\ref{fig:ised_3}, we compare with the
-            SED fitting results without considering the dust extinction. 
+            Using results based on the \texttt{BC03} model does not change any of 
+            our conclusions here.
+
+        \item On the bottom panel of Fig~\ref{fig:ised_3}, we compare the default 
+            model with the SED fitting results without considering the dust 
+            extinction. 
             This choice leads to slightly smaller \mstar{} values as expected. 
             Its impact becomes slightly larger at lower \mstar{} end. 
-            It will not change any of our conclusions here.
-
-    \end{enumerate}
+            It does not change any of our conclusions here.
+
+    \end{itemize}
+
+    We should also point out that our methodology ignores radial variations in \m2l{}. 
+    It is well known that massive ETGs have negative optical colour gradients, 
+    indicating gradients in \m2l{} (e.g.\ \citealt{Carollo1993, Davies1993, 
+    LaBarbera2012, dSouza2015}). 
+    Assuming all massive galaxies in our sample have negative colour gradients and 
+    there is a simple monotonic relationship between optical colour and \m2l{}, the
+    average \m2l{} we use should in principle underestimate the \mstar{} in the 
+    center while overestimating the \mstar{} in the outskirt.
+    However, these colour gradients are shallow and they smooth out to a few times the 
+    effective radius (e.g. \citealt{LaBarbera2010, Tal2011, DSouza2014}, 
+    colour gradients at larger radii are not yet well quantified). 
+    Because the gradients are shallow, using an average \m2l{} is unlikely to bias 
+    our results on \mstar{} measurements.  
+    In \citet{Huang2016}, the authors conduct multi-band decomposition for a sample 
+    of very nearby elliptical galaxies and estimate the \m2l{} of each component 
+    separately. 
+    The sum of all components suggests a slightly higher \mstar{} ($0.05-0.10$ dex 
+    when typical uncertainty of \mstar{} is 0.12--0.15 dex) and the mass differences 
+    show no dependence on \mstar{}. 
+    Colour gradients are discussed in \S~\ref{ssec:ell_color}. 
+    In summary, our results about the mass dependence of \mden{} profiles should not 
+    be affected by the assumption of a constant \m2l{} ratio because optical colour 
+    gradients in our sample do not show a dependence on stellar mass.
+
 %% ------------------------------------------------------------------------------------ %%
